### 2019-08-19 Tables/te.tex
Initial git commit

% Table generated by Excel2LaTeX from sheet 'te'
\begin{tabular}{rrrrrrrrrrr}
\toprule
      & \multicolumn{2}{c}{} & \multicolumn{2}{c}{} & \multicolumn{2}{c}{} & \multicolumn{2}{c}{} & \multicolumn{2}{c}{} \\
\midrule
\midrule
\multicolumn{1}{l}{} & \multicolumn{2}{c}{(1)} & \multicolumn{2}{c}{(2)} & \multicolumn{2}{c}{(3)} & \multicolumn{2}{c}{(4)} & \multicolumn{2}{c}{(5)} \\
\midrule
\midrule
\multicolumn{1}{l}{No choice/Fee} & \multicolumn{1}{l}{0.11***} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{-5.88*} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{0.076***} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{0.068*} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{0.11***} & \multicolumn{1}{l}{} \\
\multicolumn{1}{l}{} & \multicolumn{1}{l}{(0.023)} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{(3.20)} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{(0.026)} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{(0.038)} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{(0.015)} & \multicolumn{1}{l}{} \\
\multicolumn{1}{l}{No choice/No fee} & \multicolumn{1}{l}{-0.0048} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{-0.30} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{-0.011} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{0.092*} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{0.053***} & \multicolumn{1}{l}{} \\
\multicolumn{1}{l}{} & \multicolumn{1}{l}{(0.022)} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{(3.71)} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{(0.024)} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{(0.051)} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{(0.014)} & \multicolumn{1}{l}{} \\
      &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} 0.14***} &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} -6.81*} &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} 0.097**} &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} 0.41***} &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} 0.29***} \\
\multicolumn{1}{l}{Choice/Fee} & \multicolumn{1}{l}{-0.0020} & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} (0.037)} & \multicolumn{1}{l}{1.58} & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} (3.82)} & \multicolumn{1}{l}{0.0044} & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} (0.042)} & \multicolumn{1}{l}{0.10**} & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} (0.096)} & \multicolumn{1}{l}{0.029**} & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} (0.034)} \\
\cmidrule{3-3}\cmidrule{5-5}\cmidrule{7-7}\cmidrule{9-9}\cmidrule{11-11}\multicolumn{1}{l}{} & \multicolumn{1}{l}{(0.021)} & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} -0.018} & \multicolumn{1}{l}{(3.32)} & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} 2.89} & \multicolumn{1}{l}{(0.022)} & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} -0.0060} & \multicolumn{1}{l}{(0.039)} & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} 0.065*} & \multicolumn{1}{l}{(0.013)} & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} -0.000012} \\
      &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} (0.021)} &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} (3.49)} &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} (0.022)} &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} (0.039)} &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} (0.012)} \\
\cmidrule{9-9}\cmidrule{11-11}      &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} -0.037} &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} -8.66**} &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} -0.058**} &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} 0.073} &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} 0.082***} \\
\multicolumn{1}{l}{Choice/No fee} & \multicolumn{1}{l}{-0.0066} & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} (0.026)} & \multicolumn{1}{l}{-3.31} & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} (4.09)} & \multicolumn{1}{l}{-0.018} & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} (0.029)} & \multicolumn{1}{l}{-0.0012} & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} (0.057)} & \multicolumn{1}{l}{0.019} & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} (0.018)} \\
\cmidrule{3-3}\cmidrule{5-5}\cmidrule{9-9}\cmidrule{11-11}\multicolumn{1}{l}{} & \multicolumn{1}{l}{(0.022)} & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} 0.0070} & \multicolumn{1}{l}{(3.43)} & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} -1.13} & \multicolumn{1}{l}{(0.023)} & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} -0.00055} & \multicolumn{1}{l}{(0.037)} & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} -0.035} & \multicolumn{1}{l}{(0.011)} & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} -0.010} \\
      &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} (0.025)} &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} (3.88)} &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} (0.026)} &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} (0.038)} &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} (0.012)} \\
      &       &       &       &       &       &       &       &       &       &  \\
\multicolumn{1}{l}{Constant (Control)} & \multicolumn{1}{l}{0.44***} & \multicolumn{1}{l}{0.44***} & \multicolumn{1}{l}{92.4***} & \multicolumn{1}{l}{92.4***} & \multicolumn{1}{l}{-0.35***} & \multicolumn{1}{l}{-0.35***} & \multicolumn{1}{l}{0.99***} & \multicolumn{1}{l}{0.99***} & \multicolumn{1}{l}{0.12***} & \multicolumn{1}{l}{0.12***} \\
\multicolumn{1}{l}{} & \multicolumn{1}{l}{(0.015)} & \multicolumn{1}{l}{(0.015)} & \multicolumn{1}{l}{(2.53)} & \multicolumn{1}{l}{(2.53)} & \multicolumn{1}{l}{(0.017)} & \multicolumn{1}{l}{(0.017)} & \multicolumn{1}{l}{(0.028)} & \multicolumn{1}{l}{(0.028)} & \multicolumn{1}{l}{(0.0085)} & \multicolumn{1}{l}{(0.0085)} \\
      &       &       &       &       &       &       &       &       &       &  \\
\midrule
\multicolumn{1}{l}{Observations} & \multicolumn{1}{l}{13446} & \multicolumn{1}{l}{13446} & \multicolumn{1}{l}{6119} & \multicolumn{1}{l}{6119} & \multicolumn{1}{l}{13446} & \multicolumn{1}{l}{13446} & \multicolumn{1}{l}{13446} & \multicolumn{1}{l}{13446} & \multicolumn{1}{l}{13446} & \multicolumn{1}{l}{13446} \\
\multicolumn{1}{l}{R-sq} & \multicolumn{1}{l}{0.007} & \multicolumn{1}{l}{0.010} & \multicolumn{1}{l}{0.003} & \multicolumn{1}{l}{0.005} & \multicolumn{1}{l}{0.003} & \multicolumn{1}{l}{0.005} & \multicolumn{1}{l}{0.002} & \multicolumn{1}{l}{0.006} & \multicolumn{1}{l}{0.010} & \multicolumn{1}{l}{0.028} \\
\multicolumn{1}{l}{Dependent Var Mean} & \multicolumn{2}{c}{0.46} & \multicolumn{2}{c}{90.8} & \multicolumn{2}{c}{-0.34} & \multicolumn{2}{c}{1.04} & \multicolumn{2}{c}{0.16} \\
\midrule
\midrule
\rowcolor[rgb]{ .929,  .929,  .929} Status-quo & \cellcolor[rgb]{ 1,  1,  1}  & \cellcolor[rgb]{ 1,  1,  1}  & \cellcolor[rgb]{ 1,  1,  1}  & \cellcolor[rgb]{ 1,  1,  1}  & \cellcolor[rgb]{ 1,  1,  1}  & \cellcolor[rgb]{ 1,  1,  1}  & \cellcolor[rgb]{ 1,  1,  1}  & \cellcolor[rgb]{ 1,  1,  1}  & \cellcolor[rgb]{ 1,  1,  1}  & \cellcolor[rgb]{ 1,  1,  1}  \\
\rowcolor[rgb]{ .859,  .859,  .859} Non status-quo & \cellcolor[rgb]{ 1,  1,  1}  & \cellcolor[rgb]{ 1,  1,  1}  & \cellcolor[rgb]{ 1,  1,  1}  & \cellcolor[rgb]{ 1,  1,  1}  & \cellcolor[rgb]{ 1,  1,  1}  & \cellcolor[rgb]{ 1,  1,  1}  & \cellcolor[rgb]{ 1,  1,  1}  & \cellcolor[rgb]{ 1,  1,  1}  & \cellcolor[rgb]{ 1,  1,  1}  & \cellcolor[rgb]{ 1,  1,  1}  \\
\end{tabular}%

### 2019-08-19 main.tex
Initial git commit

 \documentclass[11pt]{article}

\input{preamble.tex}
\usepackage{anyfontsize}
%%% HELPER CODE FOR DEALING WITH EXTERNAL REFERENCES
\usepackage{xr}
\makeatletter
\newcommand*{\addFileDependency}[1]{
  \typeout{(#1)}
  \@addtofilelist{#1}
  \IfFileExists{#1}{}{\typeout{No file #1.}}
}
\makeatother

\newcommand*{\myexternaldocument}[1]{
    \externaldocument{#1}
    \addFileDependency{#1.tex}
    \addFileDependency{#1.aux}
}

%\myexternaldocument{OA}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% DOCUMENT
\begin{document}

\title{Frequent Payment \thanks{}}
\author{Joyce Sadka \and Enrique Seira  }
\date{This draft:  \today \\[2 cm]}

%\vspace{.5in}

\maketitle
\begin{abstract}
XXX 
\end{abstract}

\textbf{Keywords: } XXX.

\textbf{XXX} XXX

\newpage

\section{Introduction}

\section{Conclusion}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\pagebreak
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%BIBLIOGRAPHY

\section{Tables}

\begin{table}[H]
\caption{Summary statistics}
\label{SS}
\begin{center}
\scriptsize{\input{./Tables/SS.tex}}
\end{center}
 \footnotesize
\textit{Notes:}

\textit{Do file: } \texttt{ss.do}
\end{table}

\pagebreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Figures}

\begin{figure}[H]
        \caption{Timeline of the experiment}
    \label{micas}
    \begin{center}
        \centering
        \includegraphics[width=0.70\textwidth]{Figuras/timeline_suc_exp.pdf}
    \end{center}
     \footnotesize \textit{Notes: } 
      \footnotesize{ \textit{Do file: }  \texttt{timeline\_suc\_exp.do}}
\end{figure}

\begin{figure}[H]
        \caption{Experiment arms}
    \label{micas}
    \begin{center}
        \centering
        \includegraphics[width=0.70\textwidth]{Figuras/exp_arms.pdf}
    \end{center}
     \footnotesize \textit{Notes: } 
      \footnotesize{ }
\end{figure}

\begin{figure}[H]
        \caption{Booklet with product information}
    \label{micas}
    \begin{center}
        \centering
        \includegraphics[width=\textwidth]{micas.pdf}
    \end{center}
     \footnotesize \textit{Notes: } 
      \footnotesize{ }
\end{figure}

\begin{figure}[H]
    \caption{Treatment Effect}
    \label{Treatment Effect}
    \begin{center}
    \begin{subfigure}{0.4\textwidth}
        \caption{Paid loan}
        \centering
        \includegraphics[width=\textwidth]{Figuras/te_graph_des_c.pdf}
    \end{subfigure}
    \begin{subfigure}{0.4\textwidth}
        \caption{Number of payments}
        \centering
        \includegraphics[width=\textwidth]{Figuras/te_graph_num_p.pdf}
    \end{subfigure}
     \begin{subfigure}{0.4\textwidth}
      \caption{Percentage of payment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/te_graph_sum_porcp_c.pdf}
    \end{subfigure}
      \begin{subfigure}{0.4\textwidth}
      \caption{Days to un-pledge}
        \centering
        \includegraphics[width=\textwidth]{Figuras/te_graph_dias_al_desempenyo.pdf}
    \end{subfigure}
    \end{center}
     \footnotesize \textit{Notes: } 
      \footnotesize{ \textit{Do file: }  \texttt{te.do}}
\end{figure}

\begin{figure}[H]
        \caption{Reincidence}
    \label{micas}
    \begin{center}
        \centering
        \includegraphics[width=\textwidth]{Figuras/te_graph_reincidence.pdf}
    \end{center}
     \footnotesize \textit{Notes: } 
      \footnotesize{ }
\end{figure}

\begin{figure}[H]
    \caption{Heterogeneous Treatment Effect}
    \label{Treatment Effect}
    \begin{center}
    \begin{subfigure}{0.4\textwidth}
        \caption{Paid loan}
        \centering
        \includegraphics[width=\textwidth]{Figuras/he_dist_des_c.pdf}
    \end{subfigure}
    \begin{subfigure}{0.4\textwidth}
        \caption{Number of payments}
        \centering
        \includegraphics[width=\textwidth]{Figuras/he_dist_num_p.pdf}
    \end{subfigure}
     \begin{subfigure}{0.4\textwidth}
      \caption{Percentage of payment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/he_dist_sum_porcp_c.pdf}
    \end{subfigure}
    \begin{subfigure}{0.4\textwidth}
      \caption{Days to un-pledge}
        \centering
        \includegraphics[width=\textwidth]{Figuras/he_dist_dias_al_desempenyo.pdf}
    \end{subfigure}    
    \end{center}
     \footnotesize \textit{Notes: } 
      \footnotesize{ \textit{Do file: }  \texttt{te.do}}
\end{figure}

\begin{figure}[H]
        \caption{Histogram of payments}
    \label{HistPayments}
    \begin{center}
        \centering
        \includegraphics[width=\textwidth]{hist_payments.pdf}
    \end{center}
     \footnotesize \textit{Notes: } 
      \footnotesize{ \textit{Do file: }  \texttt{hist\_payments.do}}
\end{figure}

\begin{figure}[H]
        \caption{Percentage of payments}
    \label{HistPayments}
    \begin{center}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_perc_payment.pdf}
    \end{center}
     \footnotesize \textit{Notes: } 
      \footnotesize{ \textit{Do file: }  \texttt{hist\_perc\_payment.do}}
\end{figure}

\pagebreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% APPENDIX TABLES

\section{APPENDIX}

\subsection{Tables}

\begin{landscape}
\begin{table}[H]
\caption{Treatment effects results}
\label{te_table}
\begin{center}
\scriptsize{\input{./Tables/te.tex}}
\end{center}
 \footnotesize
\textit{Notes:}

\textit{Do file: } \texttt{te.do}
\end{table}

\end{landscape}

\subsection{Figures}

\begin{figure}[H]
    \caption{Robustness check effect of arms in reincidence}
    \label{Evolution payment}
    \begin{center}
    \begin{subfigure}{0.49\textwidth}
        \caption{ No Choice/Fee}
        \centering
        \includegraphics[width=\textwidth]{Figuras/reincidence_robust_curve_p2.pdf}
    \end{subfigure}
     \begin{subfigure}{0.49\textwidth}
      \caption*{No Choice/No fee}
        \centering
        \includegraphics[width=\textwidth]{Figuras/reincidence_robust_curve_p3.pdf}
    \end{subfigure}

     \begin{subfigure}{0.49\textwidth}
        \caption{Choice/Fee - SQ}
        \centering
        \includegraphics[width=\textwidth]{Figuras/reincidence_robust_curve_p4.pdf}
    \end{subfigure}
     \begin{subfigure}{0.49\textwidth}
      \caption*{Choice/Fee - NSQ}
        \centering
        \includegraphics[width=\textwidth]{Figuras/reincidence_robust_curve_p5.pdf}
    \end{subfigure}

    \begin{subfigure}{0.49\textwidth}
        \caption{Choice/No fee - SQ}
        \centering
        \includegraphics[width=\textwidth]{Figuras/reincidence_robust_curve_p6.pdf}
    \end{subfigure}
     \begin{subfigure}{0.49\textwidth}
      \caption*{Choice/No fee - NSQ}
        \centering
        \includegraphics[width=\textwidth]{Figuras/reincidence_robust_curve_p7.pdf}
    \end{subfigure}
    \end{center}
     \footnotesize \textit{Notes: } 
      \footnotesize{ \textit{Do file: }  \texttt{reincidence\_robust\_effect.do}}
\end{figure}

\pagebreak

\begin{figure}[H]
    \caption{Treatment Effect (conditional to positive payment)}
    \label{Treatment Effect}
    \begin{center}
    \begin{subfigure}{0.4\textwidth}
        \caption{Paid loan}
        \centering
        \includegraphics[width=\textwidth]{Figuras/te_graph_des_c_robust.pdf}
    \end{subfigure}
    \begin{subfigure}{0.4\textwidth}
        \caption{Number of payments}
        \centering
        \includegraphics[width=\textwidth]{Figuras/te_graph_num_p_robust.pdf}
    \end{subfigure}
     \begin{subfigure}{0.4\textwidth}
      \caption{Percentage of payment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/te_graph_sum_porcp_c_robust.pdf}
    \end{subfigure}
      \begin{subfigure}{0.4\textwidth}
      \caption{Days to un-pledge}
        \centering
        \includegraphics[width=\textwidth]{Figuras/te_graph_dias_al_desempenyo_robust.pdf}
    \end{subfigure}
    \end{center}
     \footnotesize \textit{Notes: } 
      \footnotesize{ \textit{Do file: }  \texttt{te.do}}
\end{figure}

\begin{figure}[H]
        \caption{Reincidence (conditional to positive payment)}
    \label{micas}
    \begin{center}
        \centering
        \includegraphics[width=\textwidth]{Figuras/te_graph_reincidence_robust.pdf}
    \end{center}
     \footnotesize \textit{Notes: } 
      \footnotesize{ }
\end{figure}

\begin{figure}[H]
    \caption{Evolution of payment}
    \label{Evolution payment}
    \begin{center}
    \begin{subfigure}{0.49\textwidth}
        \caption{Paid loans}
        \centering
        \includegraphics[width=\textwidth]{Figuras/desempeno_evol.pdf}
    \end{subfigure}
     \begin{subfigure}{0.49\textwidth}
      \caption*{}
        \centering
        \includegraphics[width=\textwidth]{Figuras/desempeno_evol_choice.pdf}
    \end{subfigure}

     \begin{subfigure}{0.49\textwidth}
        \caption{Average percentage of paid loans}
        \centering
        \includegraphics[width=\textwidth]{Figuras/sum_porc_evol.pdf}
    \end{subfigure}
     \begin{subfigure}{0.49\textwidth}
      \caption*{}
        \centering
        \includegraphics[width=\textwidth]{Figuras/sum_porc_evol_choice.pdf}
    \end{subfigure}

    \begin{subfigure}{0.49\textwidth}
        \caption{Average percentage of paid loans (condition on paid loan)}
        \centering
        \includegraphics[width=\textwidth]{Figuras/sum_porc_cond_evol.pdf}
    \end{subfigure}
     \begin{subfigure}{0.49\textwidth}
      \caption*{}
        \centering
        \includegraphics[width=\textwidth]{Figuras/sum_porc_cond_evol_choice.pdf}
    \end{subfigure}
    \end{center}
     \footnotesize \textit{Notes: } 
      \footnotesize{ \textit{Do file: }  \texttt{evol\_payment.do}}
\end{figure}

\end{document}

### 2019-08-19 RScripts/grf.R

@@ -1,0 +1,75 @@
+library(tidyverse)
+library(grf)
+library(ggplot2)
+
+# SET WORKING DIRECTORY
+setwd('C:/Users/xps-seira/Dropbox/Apps/ShareLaTeX/Donde 2019')
+set.seed(5289374)
+
+heterogeneity_effect <- function(data_in,treatment_var,outcome_var) {
+  
+require("dplyr")
+data_frame <- data_in %>%
+  filter(data_in[,treatment_var] == 1 | data_in[,treatment_var] == 0) %>%
+  select(-c( pro_2, pro_3, pro_4, pro_5 , t_producto, NombrePignorante, fecha_inicial, des_c, dias_al_desempenyo , 
+             ganancia  , num_p , sum_porcp_c, reincidence), treatment_var, outcome_var ) %>%
+  drop_na()  
+
+
+# PREPARE VARIABLES
+X <- select(data_frame,-c(outcome_var, treatment_var))
+Y <- select(data_frame,outcome_var)
+W <- as.numeric(data_frame[,treatment_var] == 1)
+
+# ESTIMATE MODEL
+tau.forest = causal_forest(
+  X = model.matrix(~., data = X), 
+  Y = data.matrix(Y), 
+  W = W,
+  honesty = TRUE)
+
+# OVERLAP ASSUMPTION
+propensity.forest = regression_forest(X, W)
+propensity_score = predict(propensity.forest)$predictions
+hist(propensity_score, xlab = "propensity score")
+
+# Estimate treatment effects for the training data using out-of-bag prediction.
+tau_hat_oob = predict(tau.forest, estimate.variance = TRUE)
+hist(tau_hat_oob$predictions)
+
+# Estimate the conditional average treatment effect on the full sample (CATE).
+average_treatment_effect(tau.forest, target.sample = "all")
+
+# Estimate the conditional average treatment effect on the treated sample (CATT).
+# Here, we don't expect much difference between the CATE and the CATT, since
+# treatment assignment was randomized.
+average_treatment_effect(tau.forest, target.sample = "treated")
+
+
+data.out <- add_column(data_frame,tau_hat_oob$predictions,tau_hat_oob$variance.estimates, propensity_score)
+filename <- paste("_aux/grf_", treatment_var,"_",outcome_var, ".csv", sep="") 
+write_csv(data.out,filename)
+}
+
[…]

### 2019-08-19 RScripts/pfv_pred.R

@@ -1,0 +1,46 @@
+library(tidyverse)
+library(grf)
+library(ggplot2)
+
+# SET WORKING DIRECTORY
+setwd('C:/Users/xps-seira/Dropbox/Apps/ShareLaTeX/Donde 2019')
+set.seed(5289374)
+
+
+rf_predict <- function(data_in,take.up) {
+  
+  require("dplyr")
+  data_frame <- data_in %>%
+    filter(data_in[,take.up] == 1 | data_in[,take.up] == 0) %>%
+    select(-c(suc_x_dia, producto, NombrePignorante, fecha_inicial,pago_frec_voluntario_fee,
+              pago_frec_voluntario_nofee,pago_frec_voluntario), take.up ) %>%
+    drop_na()   
+  
+  # PREPARE VARIABLES
+  X <- select(data_frame,-c(take.up))
+  W <- as.numeric(data_frame[,take.up] == 1)
+ 
+  
+  # ESTINATE MODEL
+  propensity.forest = regression_forest(X, W)
+  rf_predict = predict(propensity.forest)$predictions
+  hist(rf_predict, xlab = "predictions")
+  
+  data.out <- add_column(data_frame, rf_predict)
+  filename <- paste("_aux/pred_",take.up,".csv", sep="") 
+  write_csv(data.out,filename)
+}
+
+#####################################################
+
+# READ DATASET
+# Prenda level
+data <- read_csv('C:/Users/xps-seira/Downloads/data_pfv.csv')
+
+
+
+#Heterogeneous Effects
+for (t in c("pago_frec_voluntario")) {
+  rf_predict(data,t) 
+}
+

### 2019-08-20 main.tex
grf

@@
      \footnotesize \textit{Notes: } 
-      \footnotesize{ \textit{Do file: }  \texttt{te.do}}
+      \footnotesize{ \textit{Do file: }  \texttt{analyze\_grf.do}}
+\end{figure}
+
+\begin{figure}[H]
+    \caption{Heterogeneous Treatment Effect for Paid Loan Branches}
+    \label{Treatment Effect branch}
+    \begin{center}
+    \begin{subfigure}{0.3\textwidth}
+        \caption{x}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/he_dist_des_c_pro_2.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.3\textwidth}
+        \caption{x}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_des_c_pro_2.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.3\textwidth}
+        \caption{x}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/he_dist_des_c_pro_3.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.3\textwidth}
+        \caption{x}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_des_c_pro_3.pdf}
+    \end{subfigure}
+     \begin{subfigure}{0.3\textwidth}
+      \caption{x}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/he_dist_des_c_pro_4.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.3\textwidth}
+        \caption{x}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_des_c_pro_4.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.3\textwidth}
+      \caption{x}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/HE/he_dist_des_c_pro_5.pdf}
+    \end{subfigure} 
+    \begin{subfigure}{0.3\textwidth}
+        \caption{x}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_des_c_pro_5.pdf}
+    \end{subfigure}
+    \end{center}
+     \footnotesize \textit{Notes: } 
+      \footnotesize{ \textit{Do file: }  \texttt{analyze\_grf.do}}
 \end{figure}

### 2019-08-30 Tables/te.tex
worked on take up, and on the TE dofile

@@
 \toprule
-      & \multicolumn{2}{c}{} & \multicolumn{2}{c}{} & \multicolumn{2}{c}{} & \multicolumn{2}{c}{} & \multicolumn{2}{c}{} \\
+      & \multicolumn{2}{c}{Un-pledge} & \multicolumn{2}{c}{Days to un-pledge} & \multicolumn{2}{c}{Number of payments} & \multicolumn{2}{c}{Percentage of payment} & \multicolumn{2}{c}{Refrendum} \\
 \midrule
@@
 \midrule
-\multicolumn{1}{l}{No choice/Fee} & \multicolumn{1}{l}{0.11***} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{-5.88*} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{0.076***} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{0.068*} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{0.11***} & \multicolumn{1}{l}{} \\
-\multicolumn{1}{l}{} & \multicolumn{1}{l}{(0.023)} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{(3.20)} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{(0.026)} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{(0.038)} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{(0.015)} & \multicolumn{1}{l}{} \\
-\multicolumn{1}{l}{No choice/No fee} & \multicolumn{1}{l}{-0.0048} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{-0.30} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{-0.011} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{0.092*} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{0.053***} & \multicolumn{1}{l}{} \\
-\multicolumn{1}{l}{} & \multicolumn{1}{l}{(0.022)} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{(3.71)} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{(0.024)} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{(0.051)} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{(0.014)} & \multicolumn{1}{l}{} \\
-      &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} 0.14***} &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} -6.81*} &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} 0.097**} &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} 0.41***} &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} 0.29***} \\
-\multicolumn{1}{l}{Choice/Fee} & \multicolumn{1}{l}{-0.0020} & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} (0.037)} & \multicolumn{1}{l}{1.58} & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} (3.82)} & \multicolumn{1}{l}{0.0044} & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} (0.042)} & \multicolumn{1}{l}{0.10**} & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} (0.096)} & \multicolumn{1}{l}{0.029**} & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} (0.034)} \\
-\cmidrule{3-3}\cmidrule{5-5}\cmidrule{7-7}\cmidrule{9-9}\cmidrule{11-11}\multicolumn{1}{l}{} & \multicolumn{1}{l}{(0.021)} & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} -0.018} & \multicolumn{1}{l}{(3.32)} & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} 2.89} & \multicolumn{1}{l}{(0.022)} & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} -0.0060} & \multicolumn{1}{l}{(0.039)} & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} 0.065*} & \multicolumn{1}{l}{(0.013)} & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} -0.000012} \\
-      &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} (0.021)} &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} (3.49)} &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} (0.022)} &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} (0.039)} &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} (0.012)} \\
-\cmidrule{9-9}\cmidrule{11-11}      &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} -0.037} &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} -8.66**} &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} -0.058**} &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} 0.073} &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} 0.082***} \\
-\multicolumn{1}{l}{Choice/No fee} & \multicolumn{1}{l}{-0.0066} & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} (0.026)} & \multicolumn{1}{l}{-3.31} & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} (4.09)} & \multicolumn{1}{l}{-0.018} & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} (0.029)} & \multicolumn{1}{l}{-0.0012} & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} (0.057)} & \multicolumn{1}{l}{0.019} & \multicolumn{1}{l}{\cellcolor[rgb]{ .929,  .929,  .929} (0.018)} \\
-\cmidrule{3-3}\cmidrule{5-5}\cmidrule{9-9}\cmidrule{11-11}\multicolumn{1}{l}{} & \multicolumn{1}{l}{(0.022)} & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} 0.0070} & \multicolumn{1}{l}{(3.43)} & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} -1.13} & \multicolumn{1}{l}{(0.023)} & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} -0.00055} & \multicolumn{1}{l}{(0.037)} & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} -0.035} & \multicolumn{1}{l}{(0.011)} & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} -0.010} \\
-      &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} (0.025)} &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} (3.88)} &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} (0.026)} &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} (0.038)} &       & \multicolumn{1}{l}{\cellcolor[rgb]{ .859,  .859,  .859} (0.012)} \\
+\multicolumn{1}{l}{No choice/Fee} & \multicolumn{1}{c}{0.11***} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{-8.61***} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{0.74***} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{0.076***} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{-0.058**} & \multicolumn{1}{c}{} \\
+      & \multicolumn{1}{c}{(0.023)} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{(2.83)} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{(0.19)} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{(0.026)} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{(0.022)} & \multicolumn{1}{c}{} \\
+\multicolumn{1}{l}{No choice/Promise} & \multicolumn{1}{c}{-0.0014} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{-0.23} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{0.62***} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{-0.0072} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{0.027} & \multicolumn{1}{c}{} \\
+\multicolumn{1}{l}{} & \multicolumn{1}{c}{(0.021)} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{(3.31)} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{(0.21)} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{(0.025)} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{(0.024)} & \multicolumn{1}{c}{} \\
+      &       & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} -0.0093} &       & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} 1.91} &       & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} 0.28} &       & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} -0.0093} &       & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} 0.0094} \\
+\multicolumn{1}{l}{Choice/Fee} & \multicolumn{1}{c}{0.0064} & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} (0.020)} & \multicolumn{1}{c}{0.97} & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} (3.24)} & \multicolumn{1}{c}{0.71***} & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} (0.21)} & \multicolumn{1}{c}{-0.0025} & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} (0.021)} & \multicolumn{1}{c}{0.019} & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} (0.022)} \\
+\cmidrule{3-3}\cmidrule{5-5}\cmidrule{7-7}\cmidrule{9-9}\cmidrule{11-11}\multicolumn{1}{l}{} & \multicolumn{1}{c}{(0.020)} & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} 0.14***} & \multicolumn{1}{c}{(3.06)} & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} -5.44} & \multicolumn{1}{c}{(0.26)} & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} 4.49***} & \multicolumn{1}{c}{(0.021)} & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} 0.054} & \multicolumn{1}{c}{(0.021)} & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} 0.11***} \\
+      &       & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} (0.038)} &       & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} (4.29)} &       & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} (1.21)} &       & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} (0.042)} &       & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} (0.036)} \\
+      &       & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} 0.014} &       & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} -1.18} &       & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} -0.11} &       & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} -0.0013} &       & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} -0.030} \\
+\multicolumn{1}{l}{Choice/Promise} & \multicolumn{1}{c}{-0.0027} & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} (0.024)} & \multicolumn{1}{c}{-2.87} & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} (3.83)} & \multicolumn{1}{c}{0.26} & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} (0.22)} & \multicolumn{1}{c}{-0.015} & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} (0.026)} & \multicolumn{1}{c}{-0.012} & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} (0.027)} \\
+\cmidrule{3-3}\cmidrule{5-5}\cmidrule{7-7}\cmidrule{9-9}\cmidrule{11-11}\multicolumn{1}{l}{} & \multicolumn{1}{c}{(0.021)} & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} -0.040} & \multicolumn{1}{c}{(3.35)} & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} -6.93*} & \multicolumn{1}{c}{(0.19)} & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} 1.05***} & \multicolumn{1}{c}{(0.024)} & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} -0.045} & \multicolumn{1}{c}{(0.023)} & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} 0.028} \\
+      & \multicolumn{1}{c}{} & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} (0.025)} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} (3.75)} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} (0.30)} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} (0.034)} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} (0.025)} \\
       &       &       &       &       &       &       &       &       &       &  \\
-\multicolumn{1}{l}{Constant (Control)} & \multicolumn{1}{l}{0.44***} & \multicolumn{1}{l}{0.44***} & \multicolumn{1}{l}{92.4***} & \multicolumn{1}{l}{92.4***} & \multicolumn{1}{l}{-0.35***} & \multicolumn{1}{l}{-0.35***} & \multicolumn{1}{l}{0.99***} & \multicolumn{1}{l}{0.99***} & \multicolumn{1}{l}{0.12***} & \multicolumn{1}{l}{0.12***} \\
-\multicolumn{1}{l}{} & \multicolumn{1}{l}{(0.015)} & \multicolumn{1}{l}{(0.015)} & \multicolumn{1}{l}{(2.53)} & \multicolumn{1}{l}{(2.53)} & \multicolumn{1}{l}{(0.017)} & \multicolumn{1}{l}{(0.017)} & \multicolumn{1}{l}{(0.028)} & \multicolumn{1}{l}{(0.028)} & \multicolumn{1}{l}{(0.0085)} & \multicolumn{1}{l}{(0.0085)} \\
+\multicolumn{1}{l}{Constant} & \multicolumn{1}{c}{0.47***} & \multicolumn{1}{c}{0.46***} & \multicolumn{1}{c}{82.5***} & \multicolumn{1}{c}{83.5***} & \multicolumn{1}{c}{1.68***} & \multicolumn{1}{c}{1.32***} & \multicolumn{1}{c}{0.70***} & \multicolumn{1}{c}{0.69***} & \multicolumn{1}{c}{0.26***} & \multicolumn{1}{c}{0.24***} \\
+\multicolumn{1}{l}{} & \multicolumn{1}{c}{(0.029)} & \multicolumn{1}{c}{(0.028)} & \multicolumn{1}{c}{(3.81)} & \multicolumn{1}{c}{(3.82)} & \multicolumn{1}{c}{(0.30)} & \multicolumn{1}{c}{(0.32)} & \multicolumn{1}{c}{(0.031)} & \multicolumn{1}{c}{(0.031)} & \multicolumn{1}{c}{(0.027)} & \multicolumn{1}{c}{(0.027)} \\
       &       &       &       &       &       &       &       &       &       &  \\
 \midrule
-\multicolumn{1}{l}{Observations} & \multicolumn{1}{l}{13446} & \multicolumn{1}{l}{13446} & \multicolumn{1}{l}{6119} & \multicolumn{1}{l}{6119} & \multicolumn{1}{l}{13446} & \multicolumn{1}{l}{13446} & \multicolumn{1}{l}{13446} & \multicolumn{1}{l}{13446} & \multicolumn{1}{l}{13446} & \multicolumn{1}{l}{13446} \\
-\multicolumn{1}{l}{R-sq} & \multicolumn{1}{l}{0.007} & \multicolumn{1}{l}{0.010} & \multicolumn{1}{l}{0.003} & \multicolumn{1}{l}{0.005} & \multicolumn{1}{l}{0.003} & \multicolumn{1}{l}{0.005} & \multicolumn{1}{l}{0.002} & \multicolumn{1}{l}{0.006} & \multicolumn{1}{l}{0.010} & \multicolumn{1}{l}{0.028} \\
-\multicolumn{1}{l}{Dependent Var Mean} & \multicolumn{2}{c}{0.46} & \multicolumn{2}{c}{90.8} & \multicolumn{2}{c}{-0.34} & \multicolumn{2}{c}{1.04} & \multicolumn{2}{c}{0.16} \\
+\multicolumn{1}{l}{Observations} & \multicolumn{1}{c}{13445} & \multicolumn{1}{c}{13445} & \multicolumn{1}{c}{6118} & \multicolumn{1}{c}{6118} & \multicolumn{1}{c}{13445} & \multicolumn{1}{c}{13445} & \multicolumn{1}{c}{13445} & \multicolumn{1}{c}{13445} & \multicolumn{1}{c}{13445} & \multicolumn{1}{c}{13445} \\
+\multicolumn{1}{l}{R-squared} & \multicolumn{1}{c}{0.013} & \multicolumn{1}{c}{0.016} & \multicolumn{1}{c}{0.024} & \multicolumn{1}{c}{0.025} & \multicolumn{1}{c}{0.005} & \multicolumn{1}{c}{0.014} & \multicolumn{1}{c}{0.009} & \multicolumn{1}{c}{0.010} & \multicolumn{1}{c}{0.028} & \multicolumn{1}{c}{0.029} \\
+\multicolumn{1}{l}{Dependent Var Mean} & \multicolumn{1}{c}{0.46} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{91.0} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{2.57} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{0.75} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{0.36} & \multicolumn{1}{c}{} \\
+\multicolumn{1}{l}{Branch FE} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} \\
+\multicolumn{1}{l}{Dow FE} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} \\
 \midrule

### 2019-08-30 main.tex
run do files
worked on take up, and on the TE dofile

@@
         \caption{Timeline of the experiment}
-    \label{micas}
+    \label{timeline}
     \begin{center}
         \centering
-        \includegraphics[width=0.70\textwidth]{Figuras/timeline_suc_exp.pdf}
+        \includegraphics[width=0.70\textwidth]{Figuras/timeline_suc_exp_extended.pdf}
     \end{center}
@@
         \caption{Experiment arms}
-    \label{micas}
+    \label{exp_arms}
     \begin{center}
@@
      \begin{subfigure}{0.4\textwidth}
+      \caption{Refrendum}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/te_graph_ref_c.pdf}
+    \end{subfigure}
+      \begin{subfigure}{0.4\textwidth}
       \caption{Days to un-pledge}
@@
         \caption{Reincidence}
-    \label{micas}
+    \label{reincidence_welfare}
     \begin{center}
@@
     \caption{Heterogeneous Treatment Effect}
-    \label{Treatment Effect}
+    \label{heterogeneous_te}
     \begin{center}
@@
      \begin{subfigure}{0.4\textwidth}
+      \caption{Refrendum}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/he_dist_ref_c.pdf}
+    \end{subfigure}    
+    \begin{subfigure}{0.4\textwidth}
       \caption{Days to un-pledge}
@@
 \begin{figure}[H]
-    \caption{Heterogeneous Treatment Effect for Paid Loan Branches}
-    \label{Treatment Effect branch}
+    \caption{Heterogeneous Treatment Effect for Paid Loan}
+    \label{heterogeneous_paid_loan}
     \begin{center}
@@
 
+\begin{table}[H]
+\caption{Treatment effects results (conditional on positive payment)}
+\label{te_robust_table}
+\begin{center}
+\scriptsize{\input{./Tables/te_robust.tex}}
+\end{center}
+ \footnotesize
+\textit{Notes:}
+
+\textit{Do file: } \texttt{te.do}
+\end{table}
+
 \end{landscape}
@@
     \caption{Robustness check effect of arms in reincidence}
-    \label{Evolution payment}
+    \label{robust_reincidence}
     \begin{center}
@@
     \caption{Treatment Effect (conditional to positive payment)}
-    \label{Treatment Effect}
+    \label{te_robust_table}
     \begin{center}
@@
      \begin{subfigure}{0.4\textwidth}
+      \caption{Referendum}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/te_graph_ref_c_robust.pdf}
+    \end{subfigure}
+      \begin{subfigure}{0.4\textwidth}
       \caption{Days to un-pledge}
@@
         \caption{Reincidence (conditional to positive payment)}
-    \label{micas}
+    \label{reincidence_positive}
     \begin{center}

### 2019-08-30 RScripts/grf.R

@@ -3,8 +3,8 @@ library(grf)
 library(ggplot2)
 
 # SET WORKING DIRECTORY
-#setwd('C:/Users/xps-seira/Dropbox/Apps/ShareLaTeX/Donde 2019')
-setwd("C:\\Users\\Ricardo\\Documents\\SEIRA\\donde2019")
+setwd('C:/Users/xps-seira/Dropbox/Apps/ShareLaTeX/Donde2019')
+#setwd("C:\\Users\\Ricardo\\Documents\\SEIRA\\donde2019")
 set.seed(5289374)
 
 heterogeneity_effect <- function(data_in,treatment_var,outcome_var) {
@@ -12,8 +12,9 @@ heterogeneity_effect <- function(data_in,treatment_var,outcome_var) {
 require("dplyr")
 data_frame <- data_in %>%
   filter(data_in[,treatment_var] == 1 | data_in[,treatment_var] == 0) %>%
-  select(-c( pro_2, pro_3, pro_4, pro_5 , t_producto, NombrePignorante, fecha_inicial, des_c, dias_al_desempenyo , 
-             ganancia  , num_p , sum_porcp_c, reincidence), treatment_var, outcome_var ) %>%
+  select(-c( pro_2, pro_3, pro_4, pro_5 , t_producto, NombrePignorante, fecha_inicial,
+             des_c, dias_al_desempenyo , 
+             ref_c  , num_p , sum_porcp_c, reincidence), treatment_var, outcome_var ) %>%
   drop_na()  
 
 
@@ -56,9 +57,9 @@ write_csv(data.out,filename)
 
 # READ DATASET
 # Prenda level
-#data <- read_csv('C:/Users/xps-seira/Downloads/heterogeneity_grf.csv')
+data <- read_csv('./_aux/heterogeneity_grf.csv')
+#data <- read_csv('C:\\Users\\Ricardo\\Documents\\SEIRA\\donde2019\\_aux\\heterogeneity_grf.csv')
 
-data <- read_csv('C:\\Users\\Ricardo\\Documents\\SEIRA\\donde2019\\_aux\\heterogeneity_grf.csv')
 # Customer level
 data_customer <- data %>% 
   select(-c(dummy_prenda_tipo1, dummy_prenda_tipo2, dummy_prenda_tipo3, dummy_prenda_tipo4,
@@ -70,7 +71,7 @@ data_customer <- data %>%
 
 #Heterogeneous Effects
[…]

### 2019-08-30 RScripts/pfv_pred.R

@@ -3,30 +3,36 @@ library(grf)
 library(ggplot2)
 
 # SET WORKING DIRECTORY
-setwd('C:/Users/xps-seira/Dropbox/Apps/ShareLaTeX/Donde 2019')
+setwd('C:/Users/xps-seira/Dropbox/Apps/ShareLaTeX/Donde2019')
 set.seed(5289374)
 
 
 rf_predict <- function(data_in,take.up) {
   
   require("dplyr")
-  data_frame <- data_in %>%
-    filter(data_in[,take.up] == 1 | data_in[,take.up] == 0) %>%
-    select(-c(suc_x_dia, producto, NombrePignorante, fecha_inicial,pago_frec_voluntario_fee,
-              pago_frec_voluntario_nofee,pago_frec_voluntario), take.up ) %>%
-    drop_na()   
-  
+  data_train <- data_in %>% 
+    filter(insample == 1) 
+
+  data_test <- data_in %>% 
+    select(-c(take.up, nombrepignorante, prenda, insample))
+###################################################################  
+###################################################################  
+
+    
   # PREPARE VARIABLES
-  X <- select(data_frame,-c(take.up))
-  W <- as.numeric(data_frame[,take.up] == 1)
- 
+  X <- select(data_train,-c(take.up, nombrepignorante, prenda, insample))
+  W <- as.numeric(data_train[,take.up] == 1)
+
+###################################################################  
+###################################################################  
+  
   
   # ESTINATE MODEL
-  propensity.forest = regression_forest(X, W)
-  rf_predict = predict(propensity.forest)$predictions
-  hist(rf_predict, xlab = "predictions")
+  pred.forest = regression_forest(X, W)
+  rf_pred = predict(pred.forest,data_test)$predictions
+  hist(rf_pred, xlab = "predictions")
   
-  data.out <- add_column(data_frame, rf_predict)
+  data.out <- add_column(data_in, rf_pred)
   filename <- paste("_aux/pred_",take.up,".csv", sep="") 
   write_csv(data.out,filename)
 }
@@ -35,12 +41,9 @@ rf_predict <- function(data_in,take.up) {
 
 # READ DATASET
 # Prenda level
-data <- read_csv('C:/Users/xps-seira/Downloads/data_pfv.csv')
+data <- read_csv('./_aux/data_pfv_test.csv')
 
-
-
-#Heterogeneous Effects
[…]

### 2020-01-20 Tables/te_pro_2.tex
Work in paper in winter break MX

% Table generated by Excel2LaTeX from sheet 'te_pro_2'
\begin{tabular}{lcccc|c}
\toprule
      & Paid loan & FC admin  & FC  admin disc & \multicolumn{1}{c}{FC subjective} & Number of payment \\
\midrule
\midrule
      & (1)   & (2)   & (3)   & \multicolumn{1}{c}{(4)} & (5) \\
\midrule
\midrule
No Choice/Fee & 0.11*** & -350.2*** & -339.7*** & \multicolumn{1}{c}{-791.1*} & 0.73*** \\
      & (0.022) & (121.7) & (111.2) & \multicolumn{1}{c}{(469.5)} & (0.19) \\
Constant & 0.42*** & 4071.9*** & 3612.2*** & \multicolumn{1}{c}{5449.2***} & 2.69*** \\
      & (0.052) & (309.9) & (278.9) & \multicolumn{1}{c}{(1219.6)} & (0.44) \\
      &       &       &       & \multicolumn{1}{c}{} &  \\
\midrule
Observations & 5085  & 5034  & 5034  & \multicolumn{1}{c}{3954} & 5085 \\
R-sq  & 0.026 & 0.017 & 0.015 & \multicolumn{1}{c}{0.024} & 0.010 \\
Control Mean & 0.44  & 3231.8 & 2915.7 & \multicolumn{1}{c}{4355.7} & 2.08 \\
\midrule
DOW FE & YES   & YES   & YES   & \multicolumn{1}{c}{YES} & YES \\
Branch FE & YES   & YES   & YES   & \multicolumn{1}{c}{YES} & YES \\
Number of pawns FE & YES   & YES   & YES   & \multicolumn{1}{c}{YES} & YES \\
Number of arms FE & YES   & YES   & YES   & \multicolumn{1}{c}{YES} & YES \\
\midrule
\midrule
      &       &       &       & \multicolumn{1}{c}{} &  \\
\midrule
      & \% of payment & Size of payment & Size of payment (disc) & Days to un-pledge & Reincidence \\
\midrule
\midrule
      & (6)   & (7)   & (8)   & (9)   & (10) \\
\midrule
\midrule
No Choice/Fee & 0.081*** & 34.9  & 47.1  & -8.51*** & 0.053*** \\
      & (0.025) & (50.9) & (42.1) & (2.68) & (0.012) \\
Constant & 0.73*** & 835.6*** & 679.3*** & 82.8*** & -0.017 \\
      & (0.063) & (93.8) & (80.0) & (6.14) & (0.017) \\
      &       &       &       &       &  \\
\midrule
Observations & 5062  & 5085  & 5085  & 2490  & 2653 \\
R-sq  & 0.021 & 0.011 & 0.010 & 0.041 & 0.232 \\
Control Mean & 0.73  & 829.6 & 670.9 & 92.7  & 0.092 \\
\midrule
DOW FE & YES   & YES   & YES   & YES   & YES \\
Branch FE & YES   & YES   & YES   & YES   & YES \\
Number of pawns FE & YES   & YES   & YES   & YES   & YES \\
Number of arms FE & YES   & YES   & YES   & YES   & YES \\
\bottomrule
\bottomrule
\end{tabular}%

### 2020-01-20 main.tex
Work in paper in winter break MX

--- 2019-08-19 main.tex
@@
 
-\title{Frequent Payment \thanks{}}
-\author{Joyce Sadka \and Enrique Seira  }
+\title{Tying Odysseus or giving him choice? The demand for and effects of frequent payment commitment contracts \thanks{}}
+\author{Joyce Sadka \and Enrique Seira \and Isaac Meza }
 \date{This draft:  \today \\[2 cm]}
@@
 \begin{abstract}
-XXX 
+
+Many firms restrict individuals' choice but shroud this, suggesting low demand for commitment.
+We show that private paternalism is beneficial in the pawnbroker context we study.
+Forcing people into commitment contracts with financial penalties for not paying on time decreases their fee-including financial cost by about 11\%, and increases their likelihood of recovering their pawn by about 30\%.
+Subsequent buying increases by 10\%.
+However when offered a choice between the commitment vs the status quo contract only 10\% demand the former.
+Using salient personal promises instead of pecuniary penalties as commitment does not work.
+Although it increases take-up of the commitment contract to 31\%, it induces no change in behavior on those who choose it or when forced on everybody in the treatment arm.
+
+%and one of the most understudied.
+In our context more than on half of borrowers default and lose their pawn and whatever they have paid towards recovering it.
+Compared to the status quo pay-at-anytime 3-month contracts, forcing borrowers to pay monthly and charge a penalty if they didn't --i.e.
+a commitment contract-- increased recovery of pawn by about 30\% and financial costs by 10\%.
+However when offered a choice between the two contracts only 10\% took the monthly payment one.
+A pecuniary commitment seems necessary.
+In an alternative arm, we made them promise to pay but removed the pecuniary penalty.
+This increased take up to 31\%, but had zero effect on financing cost or default.
+The forcing contract may be better than choice for naive present biased consumers.
+
 \end{abstract}
@@
 
+\cite{Laibson2018} recently noted that many institutions ---firms, schools, financial contracts--- restrict choice using built-in incentive/commitment mechanisms which help workers/students/borrowers overcome self-control problems.
+``Firms do limit their workers’ freedom with intermediate deadlines, progress reports, production targets, attendance requirements, frequent evaluations'', schools with ``pop quizzes, classroom attendance requirements, cold calling, graded problem sets, deadlines''.
+Similarly, mortgages do so ``with a fixed repayment stream and mandatory principal repayment''.
+However he highlights a \textit{commitment puzzle}, as these same firms shroud these forcing mechanisms and don't market these commitment features.
+Presumably because students, workers and borrowers ``don't welcome these paternalistic\footnote{\cite{Laibson2018} defines paternalism as a policy that advances an individual’s interests by restricting his or her freedom, and private paternalism as paternalism implemented by private institutions.} restrictions.'' If clients were present biased and  sophisticated about their self control problem they should appreciate commitment features and firms should be eager to market them.
+The fact that this is not the case suggests they may be naive about their self control problems or that they don't have any.
+
+This paper studies \textit{private paternalism} in the particular context of pawnbroker borrowing and finds evidence for its benefits.
+Pawnshops offer secured loans using items of personal property as collateral.
+The items pawned are called pledges or pawns.
+Pawn loans are one of the oldest forms of borrowing in the world, they existed in antiquity at least since the Roman Empire, and there are records of it in China about 1,500 years ago (\cite{PawnShops}).
+Although data on their number is scarce, anecdotal evidence suggests they are still very prevalent today, and that many people in the developing world turn to them for financing.
+To give an example, our partner pawnshop (henceforth Lender P) served more than 1 million clients in the last 3 years, with more than 4 million contracts.\footnote{For comparison there are about one and a half million microfinance clients in Mexico.
+We cannot be more precise on the number of total borrowers from Lender P for confidentiality reasons.}  Pawn loans are interesting to study in and on themselves for this reason alone, but moreover, several regulators and practitioners view pawnbrokers as the lenders of last resort for the poor, the ones to which people in desperate need turn to.
+The regulators' concern is that the selection of clients that go to pawnshops may have bad debt management skills, present bias and naivete, and that therefore may be vulnerable to rent extraction.
+
+Indeed, using a survey conducted by us in branches of Lender P, we document some evidence consistent with regulators' concerns: while pawnshop clients predict they will recover their pawn with 93\% probability on average, in reality only 40\% of them do, suggesting naivete.
+Moreover, 68\% report self-control problems in other domains.
+Finally, conditional on paying a positive amount towards pawn recovery, 47\% lose their pawn \textit{and} their payment.
+%and \hl{19\%} do not normally budget monthly expenses.
+At the same time, our subjects are experienced and not uneducated, 66\% have completed at least high school and 90\% have pawned before. %and \hl{38\%} have participated in a Rosca.
+
+Lender P offers a very simple but highly collateralized contract.
+It accepts gold jewelry only as collateral, approves all pawns that are real gold, and gives the client in cash the equivalent of 70\% of the weighted gold value.
+Collateral is highly liquid and the pawnshop has an associated business that sells the gold jewelry at a profit.
+The contract stipulates a 7\% monthly interest rate charged daily, and a term of 90 days plus 15 grace days to pay principal and interest.
+The client has complete flexibility to pay any number of times any amount towards the recovery of her pawn with no penalty.
+However if the total amount of principal plus interest is not covered, she looses her pawn and all the payments that have been done.
+All transactions --appraisal of the piece, loan disbursement and payback-- are conducted at the branch.
+Given the high collateralization one would expect no moral hazard or adverse selection on the part of borrowers.
+This lets us focus more cleanly on behavioral economics aspects.
+
+We implemented a relatively large randomized control trial with close to 10,000 pawnshop clients in 6 branches of Lender P in Mexico City to answer five main questions.
+First, would clients benefit --in terms of recovering their pawn and in terms of paying lower financing cost-- from having a frequent (monthly) payment commitment contract forced on them, instead of the current (status quo) 3-month pay-when-you-want contract?
+That is, we are asking whether \textit{charging} them a 4\% late payment fee for paying late their monthly payment can actually \textit{decrease} total fee-inclusive financing cost.
+Second, would there be demand for such a frequent payment commitment contract vis-a-vis the status quo one if given choice?
+Notice that any payment profile implemented in the commitment contract can be replicated under the status quo contract, but the later has more flexibility to respond to income shocks without incurring in fees.
+Third, what types of clients would demand these contracts that restrict choice?
+Fourth, are late payment fees key to provide commitment or would a non-pecuniary but salient personal promise to pay provide a better mix of commitment vs flexibility?
+On this last question, a large and important lab experiment literature suggest that promises change behavior significantly in games, but we know little about their effect on the field with larger stakes and natural environments.\footnote{\cite{PromisesPartnerships}, \cite{Vanberg}, \cite{Belot2010}, \cite{WhyDoPromises}, \cite{FurtherPromises}, \cite{Ismayilov2017}.} Finally and importantly, does giving choice among contracts better than forcing them into payment commitment contracts in terms of minimizing financing costs incurred and the likelihood of recovering their pawn?
+
+We find that forcing clients into frequent payment commitment contracts causes them on average to save on financing cost and to recover their pawn more.
+The effects are large, financing cost decreases by \hl{11\%} on average, while the likelihood of recovering their pawn increases by \hl{30\%}.
+The reductions in cost survive the inclusion of transport cost of going to the branch plus losing a day's wage for each visit.
+Furthermore, benefits are distributed broadly, as the whole distribution of treatment effects is to the left of zero, this also shows up in quantile regressions.
+The commitment contract also causes payments to start earlier and be more frequent.
+Compared to controls total payments are lower for those that recover the pawn but also for those that lose it.
+From this first comparison we conclude that penalizing borrowers for delinquency in a contract which has already has large penalties from default actually helps borrowers.
+In fact, we find that borrowers assigned to the forced fee-commitment contract are 5pp more likely to be repeat costumers, suggesting that they themselves liked the the commitment contract more after experiencing it.\footnote{As it is well known, \textit{naivete} facilitates their exploitation by firms.
+\cite{Laibson2018} conjectures that this exploitation may be limited if consumers use experienced utility to choose among firms or contracts.}
+
+In spite of these benefits for almost all clients, we find that their demand for the commitment contract is low.
+Only \hl{10\%} of the group offered a choice between the monthly payment fee-commitment contract instead of the current 3-month pay-when-you-want contract chose the former.
+This is consistent with a growing literature (\cite{Laibson2015}, \cite{Laibson2018}, \cite{John}, \cite{Ted}).\footnote{\cite{Alcohol} and \cite{Kremer} are some of the instances of relatively high demand for commitment.
+\cite{Alcohol} speculates that this difference may be explained by their subjects having more experience with their self control problem in their context.}  \cite{Laibson2015} shows that the lost flexibility and the direct cost of paying for commitment can severely limit take-up when agents are naive about their self control.
+
+The 90\% of those that did not experienced no decrease in financing cost and no increase in recovery.
+The other 10\% who did chose it experience effects that are very close to those in the ``forcing'' arm (namely, \hl{XX\%} and \hl{XX\%}).
+Who demands commitment?
+Those higher ease to pay for services and feel less stressed.
+This suggests --along the lines of \cite{John}-- that there may be a trade-off between flexibility to respond to income shocks and commitment.
+Moreover, those who plan their monthly budget in advance and who also ask to be sent reminders, and those with more education also have higher demand.
+%Experience pawning before lowers demand (although only marginally significant statistically).
+Our proxies for self control problems are marginally significant statistically.
+Those we classify as present biased and who self declare to frequently fall into consumption temptations have a  higher demand, although marginally significant statistically.
+Those who report the family commonly ask for money also have a higher demand.
+
+%NO MORAL HAZARD IN THE CONTRACT SINCE FULLY COLLATERALIZED
+%DOUBLE FAILURE: DEMAND LOW, AND DOES NOT WORK BY PEOPLE WHO TAKE IT.
+%PENALIZES THEM EVEN MORE ON SOMETHING THEY WERE ALREADY PENALIZED 
+%PROPENSITY TO CHOSE.
+%PULLING PUNISHMENT FORWARD --CHARGING RIGHT WHEN I MESS UP.
+%MAYBE ONLY IMPATIENT AND NAIVE END IN PAWNSHOPS
+%1) SELECT A RANDOM SAMPLE OF NEIGHBORHOODS, EXTERNAL VALIDITY, THE ONES THEY GO ARE NAIF AND
+%HYPERBOLIC
+%2) ASK TO CHOSE AMONG ALL CONTRACTS
+%3) CLASSIFY SOPHISTICATION AT BASELINE
+%4) HOW TO GET AT SHOCKS.  --BUT DOES NOT SQUARE WITH WHY CHARGING THEM FEES WORKE.
+%do shocks vary across strata, predict shocks.
+%DEEP BEHAVIORAL PAPER -- CAN WE REALLY PREDICT?
+
+Inspired by a significant lab experiment literature on the effects of promises on behavior, we also experimented with a ``psychological commitment'' in the form of a salient promise to pay.
+\cite{PromisesPartnerships}, \cite{FurtherPromises}, \cite{Vanberg}, and \cite{Ismayilov2017} find that the ability to make a promise about behaving a certain way makes the individual more likely to adhere to the promised behavior, and also induces trusting behavior by the recipients of the promise.
+We aim to bring the insights from the lab to bear upon a naturally occurring field environment.
+In a separate treatment arm we made borrowers promise that they would pay one third of the amount in each of the 3 months.
+Because salience is key, we emphasized we were counting on them to deliver, and made them sign a non-legally binding promise.
+Compared to our other arm, in this case failure to pay the monthly payment did not lead to a fee, only the psychological cost of breaking their promise.
+We find that in the choice condition, \hl{30\%} demanded the commitment contract, i.e.
+3 times more than in the fee-commitment.
+One explanation for this higher take up is that clients thought this contract afforded more flexibility while at the same time providing some commitment.
+However, this treatment had a zero causal effect on financing cost or recovery.
+The same zero effect if present whether we forced them into the contract or whether they themselves chose it.
+Promises seem to have not provided any commitment whatsoever.\footnote{This is consistent with \cite{Belot2010}, who emphasize that elicited promised may have lower effects than voluntary ones.}
+
+We can systematically predict who would chose commitment in both choice arms with the survey variables\footnote{Accuracy rates are above 75\% in both arms, \hl{[ISAAC: corregir el accuracy]}.}, suggesting their choice is not purely random.
+The choice was presented in a clear way (see Figure \hl{XXX}) and enumerators made sure borrowers understood the choice by making them explain back the options, so we doubt it this demand is driven by mistakes.
+
+%\cite{Rabin2018} and \cite{Ted} show that naivete may lead to the choice of to little commitment. \hl{[guys, one problem here guys is that this contract did not cost to buy]}.
+
+%Before discussing results, let us mention why these questions are relevant and how they relate to the literature.
+Most of microfinance involves frequent payments/meeting with the group --sometimes weekly-- even though this increases transaction costs.
+Several hypothesis have been postulated to explain this, from increased group's cohesion and monitoring, to forming personal payment habits or serving as a commitment device.
+Most of the literature (e.g.
+\cite{Pande}) find however null effects of increasing frequency on default, and therefore on payment habits, commitment, or peer pressure.
+
+In our case social mechanisms are muted since we work with individual liability contracts, but commitment could certainly be one explanation, if people do indeed demand a monthly payment contract.
+Note that neoclassical consumers could replicate the monthly payment profile by themselves and gain in flexibility, so there would be little reason why they would demand these payments.\footnote{In some context if they are extorted by friends and family commitment could help.}
+
+\section{Context and Data} \label{context}
+
+    \subsection{The pawnshop and the status quo contract}
+
+    We work with one of the oldest and largest pawn shops in Mexico.
+This pawn shop has several hundred branches, spanning multiple States in Mexico.
+Their business model is very simple.
+They take gold jewelry as collateral, and based on its purity (measured in Karats) and its weight they assign a value to the piece, keep the piece as collateral, and give 70\% of the value of the piece instantly and in cash to the costumer.
+The transaction takes less than 10 minutes, is conducted in at the branch, in person between the client and the teller (henceforth the appraiser).
+The appraiser weights the piece and runs tests on its purity, and the former signs a one sheet contract pawning the piece.
+
+    When we started working with them they had only one type of contract.
+The contract stipulated that the interest rate was 7\% \textit{per month} accumulated daily on the outstanding amount, that the loan had a 90 days term with 15 days grace period, and that the client could make payments at anytime with no fees.
+If before those 105 days the client paid the principal plus the accumulated interest, the client received back the her pawn, otherwise the pawnbroker kept the piece and any payments done.
+The pawnshop thus made money in three ways, by reselling the jewelry left as collateral on defaulted loans, by charging interest on non defaulted loans, and by keeping the payments made on defaulted loans.
+
+    This contract was standard in the industry, the clients that pawned understood it (as attested in interviews), and still decided to pawn.
+Partly because they had little or no access to other types of loans, but mostly because this loan was fast and required no documentation and no credit-history check.
+Partly too perhaps because they are overconfident on average about the probability of recovering their pawn, as discussed below.
+
+    However starting about 2010-2011 new competitors started offering a pawn contract with forced monthly payments.
+Our partner pawnshop wanted to know if this contract reduced default and increased profits, and we offered to run an RCT to tests this.
+Given that collateral is relatively liquid and that it easily cover the loan, default is not as harmful to the lender as in other settings.
+However the lender was still concerned with default for two reasons.
+The first is that the collateral may have a sentimental value to the client on top of value of its gold contents, making it inefficient for the lender to keep the piece.
+Second, the pawnshop thought that keeping the piece lowered client satisfaction and made the client less likely to return and pawn again.
+
+    \subsection{Data}
+
+    We worked in 6 branches of differing size and location, although for simplicity all of them in Mexico city.
+For these 6 branches we have two types of data, administrative data that covers the period August 2012 to August 2013, and survey data we collected ourselves for the experiment.
+The administrative data contains a unique identifier of the client, a unique identifier of the piece she is pawning, and the transactions relating to that piece.
+In particular, the value of the piece as assessed by the appraiser, the amount of money lent (70\% of the value in our sample period), and the date when it was pawned, as described below for our experiment we also recorded the type of contract for that pawn.
+After the pawn happened, we are able to follow each transaction related to that piece: when were payments made and for which amounts, and whether there was default (i.e.
+the client lost the piece), and whether any penalty fees (see below) were imposed.
+We have this information for all the pawns that occurred in our 6 branches between August 1st 2012 and August 1st 2013, this includes all the pawns under our experiment but also those that happened before and about 7 months after it ended.
+Figure \ref{timeline} shows the timing of the experiment and our admin data coverage.
+The experiment comprises 13,445 pawns, and our administrative data cover a total of \hl{26,176} pawns.
+
+    We also had a team of enumerators in each branch to collect surveys.
+The enumerators were inside the branch and asked clients to complete a short 5 minutes survey before going to the teller window.
+The survey was necessarily short to avoid discouraging the potential clients from pawning, but at the same time aimed to measure the following: demographics, proxies for income/wealth, education, self control problems/present biased preferences, experience pawning, if the family or friends commonly asked for money, how time consuming and costly was to come to the branch, the subjective probability of recovering their piece that they intended to pawn, subjective value of their piece in money terms (for how much money would they sell it for).
+We were able to survey 7603 clients that pawed\footnote{We also surveyed clients before and after the experiment, so our survey covers a a larger sample that we are not using in this paper.} The appendix describes the survey in more detail and provides summary statistics on variables.
+Here we just want to mention some of the most relevant.
+
+    Table \ref{SS} shows that the average loan size is \hl{ 2171.397} pesos (about \$153 usd).
+The average number of pawns per day per branch is \hl{33.02}.
+About \hl{45\%} of them recover they pawn.
+Conditional on paying back the loan and recovering their piece, most clients pay close to the end of the contract: only \hl{20\%} pay before the \hl{90}th day.
+From the survey data we learn that \hl{74\%} of clients are women, with an average age of \hl{44} years; \hl{66\%} of them have completed high school or more, and \hl{90\%} have pawned before, so that our sample has mostly experienced borrowers.
+Finally the subjective probability of recovery is close to \hl{93\%} on average which contrast with the \hl{45\%} recovery that actually happens.
+Just by this measure borrowers would seem to be highly overconfident on average.
+Finally, the average time they take to come to the branch is \hl{22 minutes}, and the amount of money they spend in transport to do that is \hl{11 pesos} \hl{(\$0.50 usd)}.
+Furthermore, while the appraised gold value of the piece is \hl{xxx} pesos, their subjective value is \hl{6292.579 pesos}  \hl{(\$280 usd)}.
+When asked why they are pawning this piece \hl{5\%} respond with \hl{`lost a family member'}, \hl{11\%} with \hl{`attend a medical situation'}, \hl{71\%} with \hl{`attend an urgent expense'}, and  \hl{13\%} with \hl{`attend an non-urgent expense'}.
+
+\section{Experiment}
+
+\subsection{Treatment arms and randomization}
+
+Starting \hl{August 6th} 2012, we implemented our experiment in 6 branches.
+In four of them the experiment ran for \hl{107} days, and in 2 of them we ran it for a shorter time, simply because we thought we would have the required sample size by focusing on just four of them.
+Thus we eliminated \hl{the smallest} ones.
+Branches are more than \hl{5 km} apart from each other, and there is little substitution among them.\footnote{Only \hl{1\%} of consumers appear in more than one of our branches.
+In general the average distance between all our partner pawnshop's  branches is \hl{XXX} km within Mexico City.}
+
+For the purpose of the experiment we designed a new contract --which we call the monthly payment contract.
+It is identical to the status quo contract in most respects except one.
+It has the same interest rate, is accumulates interest daily and adds it to principal, it has the same loan size/collateral ratio, it has the same loan term, the gold gets appraised in the same way by the same appraisers.
+The difference is that is has a requirement to pay monthly for the 3 month duration of the loan 1/3 of the value of the loan.\footnote{Plus accumulated interest, but interest also accumulates daily on outstanding balance on the status quo loan contract.}
+
+We had to decide on what to do when the required payment was not actually paid by the client.
+In order to make monthly payments meaningful there needed to be some penalty for non-compliance.
+This penalty also could play the role of a commitment device.
+In thinking about the penalty we had to keep some of the costs in mind.
+The population we are working with is economically vulnerable\footnote{\hl{16\%} of them could not pay \hl{either} water, electricity \& gas or rent in the past \hl{6} months}, and they often receive negative income shocks (\hl{87\%} said they are pawning because of an emergency).
+Putting to high a penalty may hurt them.
+After talking to our partner, to a set of clients, and looking at the literature, we decided to have two different types of penalties.
+The first is a pecuniary penalty of 4\% of the monthly amount due if that amount was not paid in full by the deadline.
+The second was a non-pecuniary penalty inspired by the literature on promises.
+As reviewed below, that literature shows that people do not like to break their promises and are willing to incur in pecuniary costs not to break them.
+The workings of the promise are explained below.
+
+Randomization was done at the branch-day level.\footnote{Intra-branch correlation on the probability of default (ICC) is small, at \hl{0.09}, so we don't lose much power vis-a-vis individual level randomization.} Day level randomization limits the problem of people on the teller-line observing other people get different contracts, and also limits manipulation of appraisers, who in the presence of individual level randomization could potentially pick their preferred costumers from the line an reassign them to contracts types.
+We have 5 different experimental arms, which differ in which contract(s) was offered on that branch-day.
+
+\begin{enumerate}
+    \item The first arm --which we call the control group-- consists of branch-days offering the status quo contract described in Section \ref{context}, and only this contract (as was standard).
+We randomly allocated 84 branch-days to this arm.
+    \item The second arm consisted on branch-days when only the monthly payment with fee penalty contract was offered (80 branch-days). 
+    \item The third arm consisted on branch-day which offered monthly payment contract only, but where there was no fee penalty.
+Instead, the client was made to sign a paper which said ``I promise to pay every month the corresponding sum of \_\_\_\_\_\_, on the dates \_\_\_\_\_\_, \_\_\_\_\_\_, and \_\_\_\_\_\_.
+This is \underline{not} a legal document and cannot be used in anyway in courts.
+It is just a \textit{personal promise}.
+If I do not comply I would have broken my word.'' (68 branch-days).
+    \item The fourth arm consisted on branch-days where the client was given \textit{a choice} between the monthly payment with fee contract, and the status quo contract. 
+    \item The fifth arm consisted on branch-days where the client was given \textit{a choice} between the monthly payment with promise contract, and the status quo contract.
+\end{enumerate}
+
+By comparing arms 1 vs 2 or 3, we estimate the causal effect of having monthly payment contracts instead of the status quo pay-when-you-want contract.
+By having arms 4 and 5 we can measure what is the relative demand for contracts with monthly payments.
+Note that a neoclassical consumers (with no intrahousehold/ multi-agent concerns) would not voluntarily restrict her options of payment profiles and be subject to fees if they don't comply with a monthly payment profile.
+They can always replicate the monthly payment profile alone if they chose the status quo contract.
+Thus, the frequent payment contract could only decrease their welfare.
+However, if clients have present biased preferences \textit{and} are sophisticated about them, they may choose the frequent payment contract as it has commitment value.
+This value would be traded off against the value of flexibility (for instance the ability to postpone payment in case a negative income shock happens).
+Finally, by comparing 2 vs 3, and 4 vs 5, we can test if promises are as strong tool to induce compliance as a 4\% pecuniary fee.
+
+    \subsection{Connection to the literature}
+
+    Our study connects with two strands of the literature on microfinance.
+But also to a nascent one that uses RCTs to study to what extent people self-sort to treatments that have larger beneficial treatment effects for them.
+On the microfinance literature the first paper we could find that used an RCT to evaluate the causal effect of frequent payments in loans is \cite{Pande}.
+In a group lending rosca context, they note that most contracts involved frequent repayments --even weekly in many instances-- even when this increases transaction costs.
+They note that clients could benefit from ``the fiscal discipline afforded by the more rigid payments''.
+Frequency could provide a commitment device for clients, could foster a payment habit, or could generate more trust from social interactions among the group of borrowers.
+All these potential benefits apply in our context, except those relating to social interactions, as we work with individualized loans.
+
+\subsection{Process and explanation to costumers}
+
+\section{The Effect of Frequency}
+    \subsection{Treatment effects}
+    \subsection{A simple neo-clasical model}
+    \subsection{Heterogeneity}
+
+\section{Demand for commitment}
+    \subsection{Who demands commitment}
+    \subsection{Model fit with beta-delta model}
+
+\section{}
+
 \section{Conclusion}
@@
 
+\clearpage
+\bibliographystyle{authordate1}
+%\bibliographystyle{amsalpha}
+\bibliography{References}
+%\bibliographystyle{AER}
+
+%\bibliography{RefIxe}
+
+%\FloatBarrier
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Tables}
@@
 \begin{table}[H]
-\caption{Summary statistics}
+\caption{Summary statistics and Balance}
 \label{SS}
@@
 \scriptsize{\input{./Tables/SS.tex}}
+\end{center}
+ \scriptsize
+This table presents balance tests for the administrative data (Panel A) and survey data (Panel B).
+Each column corresponds to an arm of the experiment: control (status quo contract), no choice with fee, no choice with promise, choice among both contracts where the commitment contract has fee, and choice among both contracts where the commitment contract involves only a promise.
+The last column show the p-value of an F-test of the hypothesis that the mean across arms for that variable is the same across the 5 arms.
+Randomization was done at the branch-day level.
+By design the observation are not exactly equal cross arms as we were more interested in detecting effects in the choice-fee arm and less so in the no-choice-promise.
+Loan amount is the peso amount given to the client; Monday is the fraction of loans given on a Monday; number of pledges is the number of loans given in each arm.
+That it is balanced shows that there was no detectable selection across arms when clients found out what was the contract.
+In Panel B: woman indicated whether the client is female, age of the client is measured in years; has pawned before is a dummy=1 if the client declares to have pawned before (although not necessarily with Lender p).
+The subjective probability of recovery was elicited a la Manski, from 0 to 100 what is the probability that you will recoup your pawn.
+High-school is a dummy that indicates if the client has completed high school.
+Finally, the response rate is the percentage of clients in the admin data for whom we have a baseline survey.
+
+\textit{Do file: } \texttt{ss.do}
+\end{table}
+
+\pagebreak
+
+\begin{table}[H]
+\caption{Mechanism effects}
+\label{mechanisms}
+\begin{center}
+\scriptsize{\input{./Tables/mechanism.tex}}
+\end{center}
+ \scriptsize
+This table explores treatment effects in ``intermediate variables''.
+Each column represents a different dependent variable in an OLS regression.
+And each Panel represents a different treatment arm-control comparison.
+All regressions include fixed effects for branch, day of week fixed effects, number of pawns at the time of pawning this particular one, number of different treatment arms experienced before pawning this particular one.
+$R^2$ are not reported, they were less than 0.04 for all but the last column with had $R^2$'s close to 0.6.
+The last row shows the mean of the dependent variable for the control group.
+Dependent variables are as follows: Column (1) measures the number of days elapsed from the pawning date to the first payment done.
+Column (2) records the number of payments done within 150 days of the pawn.
+Column (3) is the average size of the payments for each client.
+Column (4) is self-reported cost to get to the branch plus the imputed loss of a whole day of salary (using the minimum wage in Mexico) multiplied by the number of visits to the branch.
+Column (5) measures the number of days it took to recover the pawn, conditional on recovering.
+The dependent variable in Column (6) is a dummy =1 if the client paid any positive amount within 150 days of the pawn.
+For both Columns (7) and (8) the dependent variable it is the sum of total payments done within 150 days of the pawn divided by the size of the loan, but column (8) includes as a regressor the interaction of treatment with a dummy=1 if the client recovered her pawn.
+
+\textit{Do file: } \texttt{mechanisms.do}
+\end{table}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Figures}
+
+\begin{figure}[H]
+     \caption{Experiment description}
+    \label{exp_description}
+    \begin{center}
+    \begin{subfigure}{.50\textwidth}
+      \caption{Timeline of the experiment}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/timeline_suc_exp_extended.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.45\textwidth}
+    \caption{Experiment arms}
+       \centering
+      \includegraphics[width=\textwidth]{Figuras/exp_arms.PNG}
+    \end{subfigure}
+    \end{center}
+         \scriptsize Panel (a) displays in black arrows the period covered by our administrative data: from \hl{XXX} (\hl{XXX} days before the experiment began) to \hl{XXX}.
+The gray lines arrows correspond to the dates of implementation of the experiment.
+We finished the experiment earlier in branches 1 and 2 because we realized that we would have enough sample size with the remaining branches and save on operational costs.
+Panel (b) shows our 5 treatment arms: control (status quo contract), no choice with fee, no choice with promise, choice among both contracts where the commitment contract has fee, and choice among both contracts where the commitment contract involves only a promise.
+Within each arm it displays the number of observations.
+And  for the Choice groups it splits the sample size into those who chose the commitment contract (shaded blue triangle) and those that did not (un-shaded triangle).
+      \textit{Do file: }  \texttt{timeline\_suc\_exp.do}
+\end{figure}
+
+\begin{figure}[H]
+     \caption{Financial cost}
+    \label{fc_hist}
+    \begin{center}
+    \begin{subfigure}{.45\textwidth}
+      \caption{In pesos}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_fc.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.45\textwidth}
+    \caption{As a fraction of the loan}
+       \centering
+      \includegraphics[width=\textwidth]{Figuras/hist_fc_perc_loan.pdf}
+    \end{subfigure}
+    \end{center}
+         \scriptsize
+         Panel (a) presents a histogram of financial cost for \hl{the control group}.
+Financial cost is defined as the sum of payments made by a client towards recovering her pawn + the cost of the pawn in case she ends up losing it.
+In the paper we use different costs of losing the pawn: its value in gold, and the subjective value given (jewelry may have sentimental value).
+This figure uses the \hl{gold value}.
+We plot separately the financial cost for those who lose the pawn (blue) and those that recover it (transparent).
+Panel (b) is analogous but normalized the financial cost dividing by the loan size.
+Given that the loan lasts close to 90 days, bringing payments to present value makes little difference.
+      \footnotesize{ } \textit{Do file: }  \texttt{hist\_fc.do}
+\end{figure}
+
+\begin{figure}[H]
+    \caption{Behavior of those who lost pawn}
+    \label{proxy_naive}
+    \begin{center}
+    \begin{subfigure}{0.40\textwidth}
+        \caption{Elapsed days to first payment}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_firstdays_default.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.40\textwidth}
+        \caption{Elapsed days to last payment}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_days_default.pdf}
+    \end{subfigure}
+        \begin{subfigure}{0.40\textwidth}
+        \caption{Payments as \% of loan}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_percpay_default.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.40\textwidth}
+        \caption{Number of payments}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_numpay_default.pdf}
+    \end{subfigure}
+    \end{center}
+        \scriptsize 
+        This figure describes behavior for the subsample of clients whose pawn was not recovered.
+Panel (a) shows days elapsed from the pawn to the first payment, while panel (b) displays the days elapsed to last payment.
+Some people pay after the day 105 when the grace period ends because the can ``restart'' the loan if they pay all interest owed.
+It amount to starting a new loan \hl{with the same conditions} and same pawn.
+Panel (c) shows the the fraction of the loan that they paid already, even when they ended up losing the pawn.
+Panel (d) displays the number of times they went to the branch to pay.
+      \textit{Do file: }  \texttt{hist\_den\_default.do}
+\end{figure}
+
+\begin{figure}[H]
+    \caption{The effect of ``forcing'' (with fees)}
+    \label{fc_pro2}
+    \begin{center}
+    \begin{subfigure}{0.45\textwidth}
+        \caption{Financial cost}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/fc_te_pro_2.pdf}
+    \end{subfigure}
+        \begin{subfigure}{0.45\textwidth}
+        \caption{Financial Cost (quantile reg)}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/fc_quantile_pro_2.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.55\textwidth}
+        \caption{Lost Pawn}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/def_te_pro_2.pdf}
+    \end{subfigure}
+    \end{center}
+        \scriptsize
+        This figure shows the estimated treatment effect of ``forcing'' the frequent payment commitment contract compared to the status-quo (control) for our two main outcomes: financial cost (Panel a), quantiles of financial cost (Panel b), and for and an indicator for losing the pawn (Panel c).
+Each dot represents the estimated treatment effect of a different regression (or sub-population) and its 95\% confidence interval.
+In Panel (a), the first effect corresponds to using the gold value of the pawn in the definition of financial cost and discounting the payments to present value; the second uses the subjective value of the pawn in the definition of financial cost; the third is analogous to the second but adds transaction cost (transport+1 day wage) per visit to the cost, to it involves both financial cost and transport + opportunity cost; the fourth conditions on the population that paid any positive amount towards recovery of their pawn; the fifth conditions on the sub-population \hl{of the treatment group} that paid a fee and \hl{compares these to all the control group}; the sixth conditions on the intersection of the previous two sub-populations; the seventh conditions on those we classify as overconfident (by comparing their subjective prediction of recovering their pawn versus a machine learning prediction using observables, both from the baseline survey); the seventh is focuses on non-overconfident; and the last one conditions on those we classify as present biased using the baseline survey.
+Panel (b) plots the effects on   on different quantiles of the distribution of financial cost (\hl{defined using the first definition}): 15th, 25th, 50th, 75th, 85th percentile.
+Panel (c) has to parts and to y-axis scales.
+The left Y-axis measures the effect of treatment on losing their pawn and has 8 coefficients.
+The first coefficient compares all the treatment group vs all the control; the second conditions on the population that paid any positive amount towards recovery of their pawn; the third conditions on having paid at least 30\% of the loan amount; the fourth conditions on the period covering the first cycle of the loan; the fifth on the period of the first cycle and paying any positive amount; the sixth, seventh and eight on overconfident, non-overconfident, and present biased as defined above in this note.
+The right Y-axis of Panel (c) measures the likelihood doing an additional pawn in the period of 75 days and after the pawn in the treatment and control groups.
+That is it measures the effect on ``repeat purchase'' of having been subjected to treatment for at least 75 days.
+      \textit{Do file: }  \texttt{fc\_te.do, def\_te.do, fc\_quantilereg.do}
+\end{figure}
+
+\begin{figure}[H]
+    \caption{Relationship between treatment effects}
+    \label{binscatter}
+    \begin{center}
+    \begin{subfigure}{0.45\textwidth}
+        \caption{\footnotesize{Induced to pay earlier and Induced Lower FC}}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/binscatter_fc_days_pro_2.pdf}
+    \end{subfigure}
+        \begin{subfigure}{0.45\textwidth}
+        \caption{\footnotesize{Induced to pay earlier and Induced Recovery}}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/binscatter_def_days_pro_2.pdf}
+    \end{subfigure}
+    \end{center}
+       \scriptsize 
+       This figure plots relationships between \textit{treatment effects}.
+Both Panels (a) an (b) have the same X-axis, which displays the estimated heterogeneous treatment effect on the outcome ``elapsed days of first payment'', that is how many days elapsed from the day the loan was awarded to the first payment the client made.
+The treatments effects were calculated using Athey and Wagner (\hl{YEAR XXX}).
+We use command \hl{XXX} in $R$ which outputs an estimated treatment effect for each person in treatment and control.
+In Panel (a) the Y-Axis is the \textit{treatment effect} on financial cost.
+In Panel (b) the Y-axis is the \textit{treatment effect} on losing their pawn.
+Panel (a) shows that those induced to pay earlier are also those that have larger savings in financial cost as a result of ``forcing'' the frequent payment commitment contract compared to the status-quo (control).
+Panel (b) shows that those induced to pay earlier are also those that have a larger increase in recovery.
+      \textit{Do file: }  \texttt{binscatter\_hte.do}
+\end{figure}
+
+\begin{figure}[H]
+    \caption{The Effect of choice (with fees)}
+    \label{fc_pro4}
+    \begin{center}
+    \begin{subfigure}{0.45\textwidth}
+        \caption{Financial cost}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/fc_te_pro_4.pdf}
+    \end{subfigure}
+        \begin{subfigure}{0.45\textwidth}
+        \caption{Financial Cost (quantile reg)}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/fc_quantile_pro_4.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.60\textwidth}
+        \caption{Lost Pawn}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/def_te_pro_4.pdf}
+    \end{subfigure}
+    \end{center}
+        \scriptsize
+        This figure is analogous to Figure \ref{fc_pro2}.
+It measures the effect of being given \textit{choice} between the frequent payment commitment contract and the status-quo contract versus being \textit{``forced''} into the status-quo contract (control).
+Again it focuses our two main outcomes: financial cost and an indicator for losing the pawn.
+However, it also presents differences in these two outcomes for those who chose the frequent payment commitment contract versus the whole control group (squares-NSQ), and also for those who chose the status quo contract versus the whole control group (triangles-SQ).
+Note that these two comparisons are not pure causal effects since people who chose the frequent payment commitment contract may be different from those that do not.
+That is: the squares and triangles combine selection and treatment effects.
+Finally, for comparison purposes, the blue diamonds display the effects of forcing them into the frequent payment commitment contract and are just transcribed from Figure \ref{fc_pro2} above.
+      \textit{Do file: }  \texttt{fc\_te\_choice\_dec.do, def\_te\_choice\_dec.do, fc\_quantilereg\_choice\_dec.do}
+\end{figure}
+
+\begin{figure}[H]
+    \caption{Who makes mistakes?}
+    \label{choose_wrong}
+    \begin{center}
+    \begin{subfigure}{0.4\textwidth}
+        \caption{\footnotesize{Effect of losing pawn vs predicted take-up}}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/takeuppr_def.pdf}
+    \end{subfigure}
+        \begin{subfigure}{0.5\textwidth}
+        \caption{\footnotesize{Chose wrong}}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/line_cw_pw_fc_te_cf.pdf}
+    \end{subfigure}
+    \end{center}
+             \scriptsize
+             Panel (a) estimates the treatment effect of forcing the frequent payment commitment contract on the probability of losing the pawn.
+It does this for sub-populations defined in terms of the predicted probability of taking up the frequent payment commitment contract \textit{had they been given the choice}.
+We calculate the probability using observed take up in the choice arm by the method of random forests using baseline survey and admin data.
+Then we extrapolate these predictions to the no-choice arm and group clients (in treatment and control) into 5 groups according to whether their predicted probability $\hat{P(x_i)}$ is in \hl{[0,10],(10,20],(50,70],(30,}.
+For each of these groups separately we estimate the ATE using regression equation \hl{XXX}.
+The non-monotonicity indicates that take up of treatment is \textit{not} strongly correlated with the benefit of treatment.
+\hl{Panel (b) works within the choice-group;} for them we observe take up of treatment.
+We then impute counterfactual treatment effects \hl{estimated in the no-choice group} and extrapolated to the choice-group using the observables.
+So we have an estimate of what would have happened if client $i$ had chosen otherwise.
+More concretely, for each client we calculate two numbers: what fraction would have done better with the contract the did not chose (Y-axis on the left), and how much financial cost would they save with this other contract (Y-axis on the right).
+The X-axis displays the treshold of what we classify as a ``mistake'' The red lines do this for the choice group with fee-commitment and the blue lines do this with the choice group with promise-commitment.
+We estimate that about 10\% made mistakes betwee
+
+             \textit{Do file: }  \texttt{effect\_contr\_takeup.do, choose\_wrong\_quant\_wrong.do}
+\end{figure}
+
+\begin{figure}[H]
+    \caption{“Forced commitment with promise Treatment Effects}
+    \label{fc_pro3}
+    \begin{center}
+    \begin{subfigure}{0.45\textwidth}
+        \caption{Financial cost}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/fc_te_pro_3.pdf}
+    \end{subfigure}
+        \begin{subfigure}{0.45\textwidth}
+        \caption{Quantile regression}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/fc_quantile_pro_3.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.55\textwidth}
+        \caption{Not recovery}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/def_te_pro_3.pdf}
+    \end{subfigure}
+    \end{center}
+             \footnotesize \textit{Notes: } 
+      \footnotesize{ } \textit{Do file: }  \texttt{fc\_te.do, def\_te.do, fc\_quantilereg.do}
+\end{figure}
+
+\begin{figure}[H]
+    \caption{Voluntary commitment with promise” Treatment Effects}
+    \label{fc_pro5}
+    \begin{center}
+    \begin{subfigure}{0.45\textwidth}
+        \caption{Financial cost}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/fc_te_pro_5.pdf}
+    \end{subfigure}
+        \begin{subfigure}{0.45\textwidth}
+        \caption{Quantile regression}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/fc_quantile_pro_5.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.45\textwidth}
+        \caption{Not recovery}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/def_te_pro_5.pdf}
+    \end{subfigure}
+    \end{center}
+             \footnotesize \textit{Notes: } 
+      \footnotesize{ } \textit{Do file: }  \texttt{fc\_te\_choice\_dec.do, def\_te\_choice\_dec.do, fc\_quantilereg\_choice\_dec.do}
+\end{figure}
+
+\pagebreak
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% APPENDIX TABLES
+
+\section{APPENDIX}
+
+\subsection{Tables}
+
+\begin{table}[H]
+    \caption{Out of sample measures of fit}
+    \label{Table_compliance}
+    \begin{subtable}{1\textwidth}
+      \centering
+        \caption{Take up}
+        \scriptsize{\input{./Tables/oos_pago_frec_vol.tex}}
+    \end{subtable}%
+
+    \bigskip
+    \begin{subtable}{1\textwidth}
+      \centering
+        \caption{Take up w/Fee}
+        \scriptsize{\input{./Tables/oos_pago_frec_vol_fee.tex}}
+    \end{subtable}
+
+      \bigskip
+    \begin{subtable}{1\textwidth}
+      \centering
+        \caption{Take up w/promise}
+        \scriptsize{\input{./Tables/oos_pago_frec_vol_promise.tex}}
+    \end{subtable}
+            \scriptsize
+           \\
+           \\
+           \\
+  \textit{Notes:}
+
+     \textit{Scripts: } \texttt{pred\_take\_up.do, pfv\_pred.R}
+\end{table}
+
+\begin{table}[H]
+\caption{Summary statistics (exit survey)}
+\label{SS_exit}
+\begin{center}
+\scriptsize{\input{./Tables/SS_exit.tex}}
 \end{center}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Figures}
+\subsection{Figures}
 
 \begin{figure}[H]
-        \caption{Timeline of the experiment}
-    \label{micas}
+     \caption{Booklet: Choice days}
+    \label{booklet_translate}
     \begin{center}
+    %\begin{subfigure}{0.55\textwidth}
+    %    \centering
+    %    \includegraphics[width=\textwidth]{Figuras/MP_F.pdf}
+    %\end{subfigure}
+    \begin{subfigure}{0.8\textwidth}
         \centering
-        \includegraphics[width=0.70\textwidth]{Figuras/timeline_suc_exp.pdf}
-    \end{center}
-     \footnotesize \textit{Notes: } 
-      \footnotesize{ \textit{Do file: }  \texttt{timeline\_suc\_exp.do}}
-\end{figure}
-
-\begin{figure}[H]
-        \caption{Experiment arms}
-    \label{micas}
-    \begin{center}
-        \centering
-        \includegraphics[width=0.70\textwidth]{Figuras/exp_arms.pdf}
-    \end{center}
-     \footnotesize \textit{Notes: } 
-      \footnotesize{ }
-\end{figure}
-
-\begin{figure}[H]
-        \caption{Booklet with product information}
-    \label{micas}
-    \begin{center}
-        \centering
-        \includegraphics[width=\textwidth]{micas.pdf}
-    \end{center}
-     \footnotesize \textit{Notes: } 
-      \footnotesize{ }
-\end{figure}
-
-\begin{figure}[H]
-    \caption{Treatment Effect}
-    \label{Treatment Effect}
-    \begin{center}
-    \begin{subfigure}{0.4\textwidth}
-        \caption{Paid loan}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/te_graph_des_c.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.4\textwidth}
-        \caption{Number of payments}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/te_graph_num_p.pdf}
-    \end{subfigure}
-     \begin{subfigure}{0.4\textwidth}
-      \caption{Percentage of payment}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/te_graph_sum_porcp_c.pdf}
-    \end{subfigure}
-      \begin{subfigure}{0.4\textwidth}
-      \caption{Days to un-pledge}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/te_graph_dias_al_desempenyo.pdf}
+        \includegraphics[width=\textwidth]{Figuras/MP_2.pdf}
     \end{subfigure}
     \end{center}
-     \footnotesize \textit{Notes: } 
-      \footnotesize{ \textit{Do file: }  \texttt{te.do}}
-\end{figure}
-
-\begin{figure}[H]
-        \caption{Reincidence}
-    \label{micas}
-    \begin{center}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/te_graph_reincidence.pdf}
-    \end{center}
-     \footnotesize \textit{Notes: } 
-      \footnotesize{ }
-\end{figure}
-
-\begin{figure}[H]
-    \caption{Heterogeneous Treatment Effect}
-    \label{Treatment Effect}
-    \begin{center}
-    \begin{subfigure}{0.4\textwidth}
-        \caption{Paid loan}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/he_dist_des_c.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.4\textwidth}
-        \caption{Number of payments}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/he_dist_num_p.pdf}
-    \end{subfigure}
-     \begin{subfigure}{0.4\textwidth}
-      \caption{Percentage of payment}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/he_dist_sum_porcp_c.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.4\textwidth}
-      \caption{Days to un-pledge}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/he_dist_dias_al_desempenyo.pdf}
-    \end{subfigure}    
-    \end{center}
-     \footnotesize \textit{Notes: } 
-      \footnotesize{ \textit{Do file: }  \texttt{te.do}}
 \end{figure}
@@
 \begin{figure}[H]
+        \caption{Types of agents that incur in different FC}
+    \label{components_fc}
+    \begin{center}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/scatter_fc_pay.pdf}
+    \end{center}
+     \footnotesize \textit{Notes: } 
+      \footnotesize{ \textit{Do file: }  \texttt{hist\_fc.do}}
+\end{figure}
+
+\begin{figure}[H]
         \caption{Percentage of payments}
-    \label{HistPayments}
+    \label{Percentage_payments}
     \begin{center}
@@
       \footnotesize{ \textit{Do file: }  \texttt{hist\_perc\_payment.do}}
-\end{figure}
-
-\pagebreak
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% APPENDIX TABLES
-
-\section{APPENDIX}
-
-\subsection{Tables}
-
-\begin{landscape}
-\begin{table}[H]
-\caption{Treatment effects results}
-\label{te_table}
-\begin{center}
-\scriptsize{\input{./Tables/te.tex}}
-\end{center}
- \footnotesize
-\textit{Notes:}
-
-\textit{Do file: } \texttt{te.do}
-\end{table}
-
-\end{landscape}
-
-\subsection{Figures}
-
-\begin{figure}[H]
-    \caption{Robustness check effect of arms in reincidence}
-    \label{Evolution payment}
-    \begin{center}
-    \begin{subfigure}{0.49\textwidth}
-        \caption{ No Choice/Fee}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/reincidence_robust_curve_p2.pdf}
-    \end{subfigure}
-     \begin{subfigure}{0.49\textwidth}
-      \caption*{No Choice/No fee}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/reincidence_robust_curve_p3.pdf}
-    \end{subfigure}
-
-     \begin{subfigure}{0.49\textwidth}
-        \caption{Choice/Fee - SQ}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/reincidence_robust_curve_p4.pdf}
-    \end{subfigure}
-     \begin{subfigure}{0.49\textwidth}
-      \caption*{Choice/Fee - NSQ}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/reincidence_robust_curve_p5.pdf}
-    \end{subfigure}
-
-    \begin{subfigure}{0.49\textwidth}
-        \caption{Choice/No fee - SQ}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/reincidence_robust_curve_p6.pdf}
-    \end{subfigure}
-     \begin{subfigure}{0.49\textwidth}
-      \caption*{Choice/No fee - NSQ}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/reincidence_robust_curve_p7.pdf}
-    \end{subfigure}
-    \end{center}
-     \footnotesize \textit{Notes: } 
-      \footnotesize{ \textit{Do file: }  \texttt{reincidence\_robust\_effect.do}}
-\end{figure}
-
-\pagebreak
-
-\begin{figure}[H]
-    \caption{Treatment Effect (conditional to positive payment)}
-    \label{Treatment Effect}
-    \begin{center}
-    \begin{subfigure}{0.4\textwidth}
-        \caption{Paid loan}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/te_graph_des_c_robust.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.4\textwidth}
-        \caption{Number of payments}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/te_graph_num_p_robust.pdf}
-    \end{subfigure}
-     \begin{subfigure}{0.4\textwidth}
-      \caption{Percentage of payment}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/te_graph_sum_porcp_c_robust.pdf}
-    \end{subfigure}
-      \begin{subfigure}{0.4\textwidth}
-      \caption{Days to un-pledge}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/te_graph_dias_al_desempenyo_robust.pdf}
-    \end{subfigure}
-    \end{center}
-     \footnotesize \textit{Notes: } 
-      \footnotesize{ \textit{Do file: }  \texttt{te.do}}
-\end{figure}
-
-\begin{figure}[H]
-        \caption{Reincidence (conditional to positive payment)}
-    \label{micas}
-    \begin{center}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/te_graph_reincidence_robust.pdf}
-    \end{center}
-     \footnotesize \textit{Notes: } 
-      \footnotesize{ }
 \end{figure}
@@
 
+\begin{figure}[H]
+    \caption{Heterogeneous Treatment Effect - NoChoice/Fee}
+    \label{heterogeneous_te_3}
+    \begin{center}
+    \begin{subfigure}{0.4\textwidth}
+        \caption{Financial cost}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_2.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.4\textwidth}
+        \caption*{}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_fc_admin_disc_pro_2.pdf}
+    \end{subfigure}
+
+    \begin{subfigure}{0.4\textwidth}
+        \caption{Not recovery}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_2.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.4\textwidth}
+        \caption*{}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_def_c_pro_2.pdf}
+    \end{subfigure}
+    \end{center}
+     \footnotesize \textit{Notes: } 
+      \footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}}
+\end{figure}
+
+\begin{figure}[H]
+        \caption{Heterogeneous treatment effect (NoChoice/Fee) decomposed by recovery}
+    \label{hte_dec_rec}
+    \begin{center}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/he_dist_dec_fc_admin_disc_pro_2.pdf}
+    \end{center}
+     \footnotesize \textit{Notes: } 
+        \footnotesize{ } \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do.do}
+\end{figure}
+
+\begin{figure}[H]
+    \caption{Heterogeneous Treatment Effect - NoChoice/Promise}
+    \label{heterogeneous_te_3}
+    \begin{center}
+    \begin{subfigure}{0.4\textwidth}
+        \caption{Financial cost}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_3.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.4\textwidth}
+        \caption*{}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_fc_admin_disc_pro_3.pdf}
+    \end{subfigure}
+
+    \begin{subfigure}{0.4\textwidth}
+        \caption{Not recovery}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_3.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.4\textwidth}
+        \caption*{}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_def_c_pro_3.pdf}
+    \end{subfigure}
+    \end{center}
+     \footnotesize \textit{Notes: } 
+      \footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}}
+\end{figure}
+
+\begin{figure}[H]
+    \caption{Heterogeneous Treatment Effect - Choice/Fee}
+    \label{heterogeneous_te_4}
+    \begin{center}
+    \begin{subfigure}{0.4\textwidth}
+        \caption{Financial cost}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_4.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.4\textwidth}
+        \caption*{}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_fc_admin_disc_pro_4.pdf}
+    \end{subfigure}
+
+    \begin{subfigure}{0.4\textwidth}
+        \caption{Not recovery}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_4.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.4\textwidth}
+        \caption*{}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_def_c_pro_4.pdf}
+    \end{subfigure}
+    \end{center}
+     \footnotesize \textit{Notes: } 
+      \footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}}
+\end{figure}
+
+\begin{figure}[H]
+    \caption{Heterogeneous Treatment Effect - Choice/Promise}
+    \label{heterogeneous_te_5}
+    \begin{center}
+    \begin{subfigure}{0.4\textwidth}
+        \caption{Financial cost}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_5.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.4\textwidth}
+        \caption*{}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_fc_admin_disc_pro_5.pdf}
+    \end{subfigure}
+
+    \begin{subfigure}{0.4\textwidth}
+        \caption{Not recovery}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_5.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.4\textwidth}
+        \caption*{}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_def_c_pro_5.pdf}
+    \end{subfigure}
+    \end{center}
+     \footnotesize \textit{Notes: } 
+      \footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}}
+\end{figure}
+
+\begin{figure}[H]
+    \caption{Take-up Fee against HTE}
+    \label{takeup_hte}
+    \begin{center}
+    \begin{subfigure}{0.45\textwidth}
+        \caption{Paid loan - Fee}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/takeup_he_pro_2_pago_frec_vol_fee_des_c.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.45\textwidth}
+        \caption{Paid loan - Promise}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/takeup_he_pro_3_pago_frec_vol_fee_des_c.pdf}
+    \end{subfigure}
+
+        \begin{subfigure}{0.45\textwidth}
+        \caption{FC subjective - Fee}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/takeup_he_pro_2_pago_frec_vol_fee_fc_survey.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.45\textwidth}
+        \caption{FC subjective - Promise}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/takeup_he_pro_3_pago_frec_vol_fee_fc_survey.pdf}
+    \end{subfigure}
+
+        \begin{subfigure}{0.45\textwidth}
+        \caption{Total Payment - Fee}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/takeup_he_pro_2_pago_frec_vol_fee_sum_p_c.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.45\textwidth}
+        \caption{Total Payment - Promise}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/takeup_he_pro_3_pago_frec_vol_fee_sum_p_c.pdf}
+    \end{subfigure}
+
+    \end{center}
+     \footnotesize \textit{Notes: } 
+      \footnotesize{ \textit{Do file \& RScripts: }  \texttt{heffect\_takeup\_nochoicearm.do, pfv\_pred\_hte.R}}
+\end{figure}
+
+\begin{figure}[H]
+    \caption{Reasons to pawn or not again with monthly payments}
+    \label{reasons}
+    \begin{center}
+    \begin{subfigure}{0.5\textwidth}
+        \caption{Pawn again because:}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/razones_si.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.5\textwidth}
+        \caption{Not pawn because:}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/razones_no.pdf}
+    \end{subfigure}
+    \end{center}
+     \footnotesize \textit{Notes: } 
+      \footnotesize{ \textit{Do file: }  \texttt{ss.do}}
+\end{figure}
+
+\begin{figure}[H]
+    \caption{Voluntary take up of monthly payment}
+    \label{interactions_takeup}
+    \begin{center}
+    \begin{subfigure}{0.8\textwidth}
+        \caption{``with Fee'' Arm}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/pago_frec_vol_fee_interactions_rf.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.8\textwidth}
+        \caption{``with Promise Arm''}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/pago_frec_vol_promise_interactions_rf.pdf}
+    \end{subfigure}
+    \end{center}
+     \footnotesize \textit{Notes: } 
+      \footnotesize{ \textit{Do file: }  \texttt{plot\_take\_up.do}}
+\end{figure}
+
+\begin{figure}[H]
+        \caption{\% of payments conditional on payment $>$ 0 and no item back}
+    \label{HistPayments_pos}
+    \begin{center}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_perc_payment_conditional.pdf}
+    \end{center}
+     \footnotesize \textit{Notes: } 
+      \footnotesize{ \textit{Do file: }  \texttt{hist\_payments.do}}
+\end{figure}
+
+\begin{figure}[H]
+        \caption{Booklet with product information}
+    \label{micas}
+    \begin{center}
+        \centering
+        \includegraphics[width=\textwidth]{micas.pdf}
+    \end{center}
+     \footnotesize \textit{Notes: } 
+      \footnotesize{ }
+\end{figure}
+
+\begin{figure}[H]
+    \caption{Propensity to take up the commitment device}
+    \label{prop_take_up_hte}
+    \begin{center}
+     \begin{subfigure}{0.45\textwidth}
+        \caption{Fee}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/takeup_fee_he.pdf}
+    \end{subfigure}
+     \begin{subfigure}{0.45\textwidth}
+        \caption{Promise}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/takeup_promise_he.pdf}
+    \end{subfigure}
+\end{center}
+     \footnotesize \textit{Notes: } 
+      \footnotesize{ \textit{Do file: }  \texttt{heffect\_takeup.do}}
+\end{figure}
+
+\begin{figure}[H]
+     \caption{Booklet with product information translated}
+    \label{booklet_translate2}
+    \begin{center}
+    \begin{subfigure}{.9\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/MP_F.pdf}
+    \end{subfigure}
+    %\begin{subfigure}{0.55\textwidth}
+    %   \centering
+    %  \includegraphics[width=\textwidth]{Figuras/MP_2.pdf}
+    %\end{subfigure}
+    \end{center}
+\end{figure}
+
 \end{document}

### 2020-01-20 presentations/beamer_applied_lunch.tex
Work in paper in winter break MX

\documentclass[9pt]{beamer}

\input{preamble_beamer.tex}

%\setbeamercolor{section in head/foot}{bg=darkcrimsonred}
\setbeamersize{text margin left=11pt, text margin right=11pt}
%\setbeamertemplate{section in toc}[square]

\begin{document}

\title{Frequent Payments as a Commitment Device?}

%\subtitle{VERY PRELIMINARY!}

\author[]{
Isaac Meza\inst{1}\and Joyce Sadka\inst{2}  \and Enrique Seira\inst{2}}
\institute{ \inst{1} University of California, Berkeley \and
  \inst{2}  Instituto Tecnológico Autónomo de México}

\date{Oct 4, 2019\\\;\;\textsc{Applied Lunch}\\\;\;\textbf{\alert{VERY PRELIMINARY!} }}

\begin{frame}[c, noframenumbering]%{\phantom{title page}}
% The \phantom{title page} is a kludge to get the red bar on top
\titlepage
\end{frame}

\begin{frame}{Motivation}
\begin{itemize}
\vfill \item True story:
    \begin{itemize}
        \item A large Mexican pawn shop (PS) contacted us worried that their default was too high...
        \item ...conjecturing it had to do with contract without frequent payments.
    \end{itemize}
    \pause
\vfill \item Their contract:
    \begin{itemize}
        \item Accepted gold jewelry as collateral, gave you 70\% of the value of gold in cash.
        \item 7\% Monthly interest in outstanding debt.
        \item 3 month term. You could pay principal+interest anytime with no penalty and recover your item. 
        \item Only 33\% paid before day 85th.
        \item if in 90 (+15 days grace) you did not do this, you lose your item.
    \end{itemize}
    \pause
\vfill \item Does forcing them to \textbf{pay monthly} increase payment (decrease default)?
    \begin{itemize}
        \item PS prefers clients recover their item (non-profit mandate).
        \item Higher frequency has costs: $\uparrow$ transaction costs, $\downarrow$  welfare (with neo-classical consumers).
        \item But may help present biased consumers. 
    \end{itemize}
    \vfill
    \pause
    \item \textbf{Is there demand for commitment?}
\end{itemize}
\vfill
\end{frame}

\begin{frame}{Why could frequency decrease default?}
    \begin{itemize}
        \vfill \item Behavioral:
        \begin{itemize}
            \item Commitment device not to spend the money (for present biased consumers).
            \item Creates a habit for saving (or paying) / forces to make a plan (for inattentive consumers).
            \item Sunk cost fallacy (having already paid some).
        \end{itemize}
    \end{itemize}

    \begin{itemize}
        \vfill \item Neoclassical:
        \begin{itemize}    
        \item Increases consumer trust with branch personnel?
        \item Pecuniary/psychological cost from not paying?
        \item Less ``distance to goal''.
         \item Borrows from other lenders to pay $\rightarrow$ more monitoring.
        \end{itemize}
        \vfill
    \item Neoclassical consumers would \textbf{not} tie their hands for free.
        \begin{itemize}
            \item Demand for commitment would signal the presence of present biased consumers.
        \end{itemize}
    \end{itemize}   
    \vfill
\end{frame}

\begin{frame}{What ``punishment'' to use for late payment?}

\begin{itemize}
    \item There needs to be a punishment from not paying in order to have commitment.
    \vfill
    \item But punishment if it is too hard, and there are random shocks to income, even present biased consumers will not demand it.
    \vfill 
    \item Two types of punishment in different arms:
    \begin{itemize}
        \item Monetary fee: $4\%$ of missed payment.
        \item Psychological cost of lying: made promise very salient.
    \end{itemize}
\end{itemize}

\end{frame}

\begin{frame}{Literature in Microfinance}

        \begin{itemize}
        \vfill \item Field and Pande ``\textit{Repayment Frequency and Default in Microfinance}'' JEEA 2008.
            \begin{itemize}
            \item Randomized 100 MFI groups to weekly vs monthly payment.
            \item Found no effect of frequency (default in about 1\% for all).
            \end{itemize}
            \pause
        \vfill \item Field et al ``Repayment flexibility can reduce financial stress'' PLOS 2012
            \begin{itemize}
            \item Randomized ~100 MFI groups to weekly vs monthly payment.
            \item Found those in weekly payment  50\% more likely to report feeling anxious.
            \end{itemize}
            \pause
        \vfill \item Field, Pande, Papp, Rigol ``Does the classic microfinance model discourage entrepreneurship among the poor?'' AER 2013
        \pause
        \vfill \item Ahsarf et al ``Tying odysseus to the mast'' QJE 2006.
               \begin{itemize}
                \item Offered savings where they could not withdraw for a given time /goal (~700 people, 28\% accepted).
                \item Found present biased women  are more 15pp likely to take up.
                \item 80\% increase in savings 1yr later (ITT).
             \end{itemize}
             \vfill

    \end{itemize}

\end{frame}

% LOS SIGUIENTE ES PARA QUE PONGA SECCIONES Y DIVISIONES ENTRE SECCIONES
	\setbeamertemplate{section in toc}{\hypersetup{linkcolor=.}\colorbox{lightash}{\textcolor{white}{\inserttocsectionnumber}}\enskip\inserttocsection}

	\begin{frame}[t]{Steps}
	\hfill
	\parbox[t]{.95\textwidth}{
		\begin{minipage}[c][0.75\textheight]{\textwidth}
			\tableofcontents[hideallsubsections]	
	\end{minipage}}
	\hfill
\end{frame}

\AtBeginSection[]
{
\begin{frame}[t]{Steps}
\hfill
\parbox[t]{.95\textwidth}{
	\begin{minipage}[c][0.75\textheight]{\textwidth}
		\tableofcontents[currentsection,hideallsubsections,sectionstyle=show/shaded]  				
\end{minipage}}
\hfill
\end{frame}
}

%EMPIEZAN LAS SECCIONES

\section{Experiment description}

\begin{frame}{Experimental Arms}
     5 Arms:
        \begin{itemize}
            \item \textbf{Control} = status quo pay any time in 90 days.
            \vfill
            \item \textbf{Frequent payment treatments}: 4 arms in a 2x2 design: 
            \vfill
            \begin{itemize}
                \item ``Forced'' to have the monthly payment contract vs given choice.
                \vfill
                \item  Break promise vs penalty fee (4\%) if delinquent on payment.
            \end{itemize}
            \vfill
            \item Randomization at branch-day level.
                \begin{itemize}
                    \item No difference in number of contracts by arm.
                \end{itemize}
        \end{itemize}
    \vfill
    \begin{center}
        \centering
        \includegraphics[width=0.70\textwidth]{Figuras/exp_arms.PNG}
    \end{center}
\end{frame}

\begin{frame}{Branches and Timeline}
    \begin{itemize}
        \item We worked on 6 branches during 2012
        \item We observe transactions for about 30 days before and 6 months after the experiment ends.
    \end{itemize}
    \begin{center}
        \includegraphics[width=0.80\textwidth]{Figuras/timeline_suc_exp_extended.pdf}
    \end{center}
\end{frame}

\begin{frame}{Data}

\begin{itemize}
    \item Admin data:
    \begin{itemize}
        \item Date of pawning
        \item Value of item --> loan size
        \item Dates of payments and amounts, 
        \item Whether borrower recovered item
        \item Borrower id
    \end{itemize}
    \vfill
    \item Survey data: Own 2 page questionnaire at the branch before pawning
    \begin{itemize}
        \item Some demographics
        \item Vulnerability
        \item Cost of going to branch
        \item 3 ``self control'' questions
        \item ... others.
    \end{itemize}
\end{itemize}

\end{frame}

\begin{frame}{Survey questions}
    \begin{enumerate}
        \item Family
            \begin{itemize}
                \item Common asks - Is it common family or friends ask you for money?
            \end{itemize}
        \item Income 
        \begin{itemize}
            \item In the last six months, did you need money to pay...?
        \end{itemize}
        \item Self-Control
        \begin{itemize}
            \item Makes budget - Do you budget your monthly expenses?
            \item Present bias - Prefers 100 tomorrow over 250 in a month AND 150 in 4 months over 100 in 3 months
            \item Reminder - Would you like to receive free reminders on your cell phone?
            \item Tempt - Has it happened to you that you spend more than you would like because you fall into temptation?
        \end{itemize}
        \item Experience
        \begin{itemize}
            \item Rosca - Do you participate in a \textit{rosca} or in a savings account?
            \item Pawn before - Have you pawn before?
        \end{itemize}
        \item Other
            \begin{itemize}
            \item Low time - Below median in reported time to arrive to the pawn shop.
            \item Low cost - Below median in reported cost spent to arrive to the pawn shop
            \item Prob recovery - From 0 to 100 mark with an X how sure you are to recover your garment
            \item Stressed - How often do you feel stressed by your household economic situation? - 0 when answered `never' and 1 otherwise
        \end{itemize}
    \end{enumerate}
\end{frame}

\begin{frame}{SS Histograms}

\begin{figure}[H]
    \label{nochoicehte_takeup_pred}
    \begin{center}
     \begin{subfigure}{0.45\textwidth}
        \caption{In the last six months, did you need money to pay...?}
        \centering
        \includegraphics[width=\textwidth]{Figuras/perc_utilities.pdf}
    \end{subfigure}
     \begin{subfigure}{0.45\textwidth}
        \caption{Cost and Time to arrive to pawn shop}
        \centering
        \includegraphics[width=\textwidth]{Figuras/cost_time_scatter_hist.png}
    \end{subfigure}
    \end{center}
    \end{figure}

\end{frame}

\begin{frame}{Summary Stats}
    \begin{table}
        \begin{center}
        \tiny{\input{./Tables/SS.tex}}
        \end{center}
    \end{table}
\end{frame}

\section{Results on Payments and Recovery}

\begin{frame}{When do borrowers pay?}
    \begin{center}
        \includegraphics[width=\textwidth]{Figuras/hist_payments.pdf}
    \end{center}
\end{frame}

\begin{frame}{Recovering Piece}

    \begin{center}
        \includegraphics[width=.70\textwidth]{Figuras/te_graph_des_c.pdf}
    \end{center}
\end{frame}

\begin{frame}{Number of Payments}
    \begin{center}
        \includegraphics[width=.70\textwidth]{Figuras/te_graph_num_p.pdf}
    \end{center}
\end{frame}

\begin{frame}{Percentage of Loan paid}
    \begin{center}
        \includegraphics[width=.70\textwidth]{Figuras/te_graph_sum_porcp_c.pdf}
    \end{center}
\end{frame}

\begin{frame}{Days to recover piece | recovering}
    \begin{center}
        \includegraphics[width=.70\textwidth]{Figuras/te_graph_dias_al_desempenyo.pdf}
    \end{center}
\end{frame}

\begin{frame}{Reincidence}
    \begin{center}
        \includegraphics[width=.70\textwidth]{Figuras/te_graph_reincidence.pdf}
    \end{center}
\end{frame}

\begin{frame}[label = hte]{TE heterogeneity in Recovering}
    \begin{center}
        \includegraphics[width=.80\textwidth]{Figuras/he_dist_des_c_pro_2.pdf}
    \end{center}

 Based on \hyperlink{GRF}{\beamerbutton{GRF}}   
\end{frame}

\begin{frame}{Some determinants of TE - The nature of heterogeneity}
    \begin{center}
        \includegraphics[width=.9\textwidth]{Figuras/HE/he_int_des_c_pro_2.pdf}
    \end{center}
\end{frame}

\section{Results on Demand for Commitment}

\begin{frame}{10\% take up with fee: who are they?}
    \begin{center}
        \includegraphics[width=.90\textwidth]{Figuras/pago_frec_vol_fee_interactions_rf.pdf}
    \end{center}
\end{frame}

\begin{frame}{Those taking up are not those with highest TE}
    \begin{center}
        \includegraphics[width=.70\textwidth]{Figuras/takeup_he_pro_2_fee.pdf}
    \end{center}
\end{frame}

\section{Next steps}

\begin{frame}{Next steps}

\begin{itemize}
    \item Can a simple neoclassical model explain quantitatively the results?
    \vfill
    \item Estimate a model and talk about welfare?
    \vfill
    \item What about naive present-biased consumers? Can we separate them?
    \vfill
    \item Does promise commitment work for some people?
    \vfill
    \item Does frequent payment cause lack of payment of basic services or other loans?
\end{itemize}

\end{frame}

\section{Appendix}

\begin{frame}{Explanation in ``choice'' days}
    \begin{center}
        \includegraphics[width=\textwidth]{Figuras/micas.pdf}
    \end{center}
\end{frame}

\begin{frame}{Histograms Percentage Paid}
    \begin{center}
        \includegraphics[width=.9\textwidth]{Figuras/hist_perc_payment.pdf}
    \end{center}
\end{frame}

\begin{frame}{Characteristics of present bias}
\begin{table}[H]
\label{pb_chars}
\begin{center}
\tiny{\input{./Tables/pb_chars.tex}}
\end{center}
\end{table}
\end{frame}

\begin{frame}{30\% take up with promise: Different relation with self control}
    \begin{center}
        \includegraphics[width=.90\textwidth]{Figuras/pago_frec_vol_promise_interactions_rf.pdf}
    \end{center}
\end{frame}

\begin{frame}{ML fit}
    \begin{center}
    \scriptsize
    \input{./Tables/oos_pago_frec_vol_fee.tex}
    \end{center}
\end{frame}

\begin{frame}{Exit survey}
    \begin{center}
    \tiny
    \input{./Tables/SS_exit.tex}
    \end{center}
\end{frame}

\begin{frame}[label = GRF]{Generalized Random Forests}

A method for non-parametric statistical estimation based on RF
for estimating $\theta(x)$ that can be identified as the solution to a set of local moment equations:

\[\mathbb{E}[\psi(Z,\theta,h(x,W))\;|\;X=x]=0\]

where $\psi$ is a known score function and $h$ is an unkown nuisance function also estimated from data.\\

\vspace{5mm}

The main application involves HTE. To achieve this, the method seeks trees that, when combined, produces leaves that maximizes heterogeneity. In other words, it splits the data that produce the biggest difference in TE across leaves, by still producing accurate estimates of the TE. Moreover, the splits are made honest by taking the training data and splitting it into two subsamples: a splitting subsample and an estimating subsample. The estimates being calculated on the latter. \hyperlink{hte}{\beamerbutton{Back}}\\

\end{frame}

\begin{frame}{Honest Causal Tree construction}
Given a dataset with an outcome $Y$, covariates $X$, and a randomized condition $W$ that takes on the value of 0 for control and 1 for treatment:

\begin{enumerate}
\item Split the data into subsample $I$ and subsample $J$

\item Train a decision tree on subsample $I$ predicting $Y$ from $X$, with the requirement that each terminal node has at least $k$ observations from each condition in subsample $J$

\item Apply the decision tree constructed on subsample $I$ to subsample $J$

\item At each terminal node, get the mean of predictions for the $W = 1$ cases from subsample $J$ and subtract the mean of predictions for the $W = 0$ cases from subsample $J$; the resulting difference is the estimated treatment effect.

\end{enumerate}

This is then applied to a causal random forest by using bagging or bootstrapping

\end{frame}
\end{document}

### 2020-01-20 MATLAB/V2.m

@@ -1,0 +1,58 @@
+function [V, pp, d] = V2(y,m,parms)
+% Value function at time period t=2
+beta_belief = parms.beta_belief; delta = parms.delta; 
+val = parms.v; r =parms.r; mu = parms.mu; sigma = parms.sigma;
+
+% Sample to compute V3:
+y_prime = exp(mu + sigma.*randn(parms.rep,1));
+
+% Function to optimize
+% VV1 = @(p) beta*delta*log(y-p) + ...
+%     mean(V3(y_prime,(1+r).*(m-p),parms));
+%%
+
+if (m <= 0)
+   % Value function
+    V = beta_belief*delta*(log(1+val)+log(y)) + ...
+        beta_belief*delta^2*log(1+val) + ...
+        beta_belief*delta^2*mu;
+    pp = zeros(length(y),1);
+    
+else
+    % Discretize grid for policies
+    mn = min(m,y);
+    mx = max(mn);
+    p = linspace(0,mx,parms.gridsize);
+
+    Omega = (1+val)/val;
+    % Value function
+    VV = beta_belief*delta*log(y-p) + ...
+        beta_belief*delta^2*log(1+val).*(1-logncdf((1+r)*(m-p)*Omega,mu,sigma)) + ...
+        beta_belief*delta^2*mean(log(y_prime-(1+r).*max((m-p),0).*(y_prime >= (1+r)*(m-p)*Omega)));
+
+    V = zeros(length(y),1); ind = zeros(length(y),1);
+    for i=1:length(y)
+        % Optimal int point value
+        [V(i),ind(i)] = max(VV(i,imag(VV(i,:))==0));
+    end
+
+    % Optimal int point policy
+    pp = p(ind)';
+
+    %% 
+
+    % Optimum for paying debt at this time period if possible
+    opt = -Inf*ones(length(y),1);
+    opt(m<=y) = beta_belief*delta.*(log(1+val) + log(y(m<=y)-m)) + ...
+            beta_belief*delta^2*(log(1+val) + mu);
+
+
+    %% Optimum values
+    ind_change = V<opt;
+    V(ind_change) = opt(ind_change); pp(ind_change) = m;
+end
+
+    % Paid loan
+    d = (pp==m);
+end
+

### 2020-01-20 MATLAB/V3.m

@@ -1,0 +1,14 @@
+function [V, pp, d] = V3(y,m,parms)
+% Value function at time period t=3
+beta_belief = parms.beta_belief; delta = parms.delta; val = parms.v;
+
+
+pp = m.*((y >= m.*(1+val)./val));
+
+V = beta_belief*delta^2*(log(1+val).*(y >= m.*(1+val)./val)+...
+    log(y-pp));
+
+% Paid loan
+d = (pp==m);
+
+end

### 2020-01-20 MATLAB/scatter_hist.m

@@ -1,0 +1,35 @@
+%% Scatter histograms
+
+
+%% Cost - Time
+clear all
+data = csvread('cost_time.csv');
+
+Cost = data(:,1);
+Time = data(:,2);
+
+gcf = scatterhist(Cost,Time,'Kernel','on','Location', 'SouthEast',...
+    'Direction','out','Color','kbr','LineStyle',{'-','-.',':'},...
+    'LineWidth',[2,2,2],'Marker','+od','MarkerSize',[4,5,6]);
+
+%% Financial Cost Survey - Admin
+clear all
+data = csvread('fc.csv');
+
+Admin = data(:,1);
+Subjective = data(:,2);
+
+gcf = scatterhist(Admin,Subjective,'Kernel','on','Location', 'SouthEast',...
+    'Direction','out','Color','kbr','LineStyle',{'-','-.',':'},...
+    'LineWidth',[2,2,2],'Marker','+od','MarkerSize',[4,5,6]);
+
+%% Financial Cost (log) Survey - Admin
+clear all
+data = csvread('logfc.csv');
+
+Admin = data(:,1);
+Subjective = data(:,2);
+
+gcf = scatterhist(Admin,Subjective,'Kernel','on','Location', 'SouthEast',...
+    'Direction','out','Color','kbr','LineStyle',{'-','-.',':'},...
+    'LineWidth',[2,2,2],'Marker','+od','MarkerSize',[4,5,6]);

### 2020-01-20 RScripts/fc_te_grf.R

@@ -1,0 +1,86 @@
+library(tidyverse)
+library(grf)
+library(ggplot2)
+
+# SET WORKING DIRECTORY
+setwd('C:/Users/xps-seira/Dropbox/Apps/ShareLaTeX/Donde2019')
+#setwd("C:\\Users\\Ricardo\\Documents\\SEIRA\\donde2019")
+set.seed(5289374)
+
+
+
+  data_in <- read_csv('./_aux/fc_te_heterogeneity.csv')
+  
+  
+  require("dplyr")
+  
+  data_train <- data_in %>% 
+    filter(insample == 1) 
+  data_train_fee <- subset(data_train, data_train$fee_arms == 1)
+  data_train_nofee <- subset(data_train, data_train$fee_arms == 0)
+  
+  
+  data_test <- data_in %>% 
+    select(-c(fc_admin, fee_arms, prenda, insample))
+  data_test_tau <- data_in %>% 
+    select(-c(fc_admin, prenda, insample))
+  
+  ###################################################################  
+  ###################################################################  
+  
+  
+  # PREPARE VARIABLES
+  X <- select(data_train,-c(fc_admin, fee_arms, prenda, insample))
+  Y <- select(data_train,fc_admin)
+  W <- as.numeric(data_train$fee_arms == 1)
+  
+  X_full <- select(data_in,-c(fc_admin, fee_arms, prenda, insample))
+  Y_full <- select(data_in,fc_admin)
+  W_full <- as.numeric(data_in$fee_arms == 1)
+  
+  X_fee <- select(data_train_fee,-c(fc_admin, fee_arms, prenda, insample))
+  Y_fee <- as.numeric(data_train_fee$fc_admin)
+  X_nofee <- select(data_train_nofee,-c(fc_admin, fee_arms, prenda, insample))
+  Y_nofee <- as.numeric(data_train_nofee$fc_admin)
+  
+  ###################################################################  
+  ###################################################################  
+  
+
+  # ESTIMATE MODEL
+
+  # Causal Forest
+  tau.forest = causal_forest(
+    X = model.matrix(~., data = X), 
+    Y = data.matrix(Y), 
+    W = W,
+    honesty = TRUE)
+  
+  tau.forest.full = causal_forest(
+    X = model.matrix(~., data = X_full), 
+    Y = data.matrix(Y_full), 
+    W = W_full,
+    honesty = TRUE)  
+  # Regression forest
[…]

### 2020-01-20 RScripts/grf.R

@@ -12,14 +12,13 @@ heterogeneity_effect <- function(data_in,treatment_var,outcome_var) {
 require("dplyr")
 data_frame <- data_in %>%
   filter(data_in[,treatment_var] == 1 | data_in[,treatment_var] == 0) %>%
-  select(-c( pro_2, pro_3, pro_4, pro_5 , t_producto, NombrePignorante, fecha_inicial,
-             des_c, dias_al_desempenyo , 
-             ref_c  , num_p , sum_porcp_c, reincidence), treatment_var, outcome_var ) %>%
+  select(-c( pro_2, pro_3, pro_4, pro_5, pro_6, pro_7, pro_8, pro_9, fee, fecha_inicial,
+             def_c, fc_admin_disc, dias_primer_pago), treatment_var, outcome_var ) %>%
   drop_na()  
 
 
 # PREPARE VARIABLES
-X <- select(data_frame,-c(outcome_var, treatment_var))
+X <- select(data_frame,-c(outcome_var, treatment_var,NombrePignorante, prenda))
 Y <- select(data_frame,outcome_var)
 W <- as.numeric(data_frame[,treatment_var] == 1)
 
@@ -40,12 +39,15 @@ tau_hat_oob = predict(tau.forest, estimate.variance = TRUE)
 hist(tau_hat_oob$predictions)
 
 # Estimate the conditional average treatment effect on the full sample (CATE).
-average_treatment_effect(tau.forest, target.sample = "all")
+print(average_treatment_effect(tau.forest, target.sample = "all"))
 
 # Estimate the conditional average treatment effect on the treated sample (CATT).
 # Here, we don't expect much difference between the CATE and the CATT, since
 # treatment assignment was randomized.
-average_treatment_effect(tau.forest, target.sample = "treated")
+print(average_treatment_effect(tau.forest, target.sample = "treated"))
+
+#The (conditional) average treatment effect on the controls 
+print(average_treatment_effect(tau.forest, target.sample = "control"))
 
 
 data.out <- add_column(data_frame,tau_hat_oob$predictions,tau_hat_oob$variance.estimates, propensity_score)
@@ -70,10 +72,14 @@ data_customer <- data %>%
 
 
 #Heterogeneous Effects
-for (t in c("pro_2", "pro_3", "pro_4", "pro_5")) {
[…]

### 2020-01-20 RScripts/pfv_pred.R

@@ -12,22 +12,22 @@ rf_predict <- function(data_in,take.up) {
   require("dplyr")
   data_train <- data_in %>% 
     filter(insample == 1) 
-
+  
   data_test <- data_in %>% 
     select(-c(take.up, nombrepignorante, prenda, insample))
-###################################################################  
-###################################################################  
-
-    
+  ###################################################################  
+  ###################################################################  
+  
+  
   # PREPARE VARIABLES
   X <- select(data_train,-c(take.up, nombrepignorante, prenda, insample))
   W <- as.numeric(data_train[,take.up] == 1)
-
-###################################################################  
-###################################################################  
+  
+  ###################################################################  
+  ###################################################################  
   
   
-  # ESTINATE MODEL
+  # ESTIMATE MODEL
   pred.forest = regression_forest(X, W)
   rf_pred = predict(pred.forest,data_test)$predictions
   hist(rf_pred, xlab = "predictions")
@@ -41,9 +41,8 @@ rf_predict <- function(data_in,take.up) {
 
 # READ DATASET
 # Prenda level
-data <- read_csv('./_aux/data_pfv_test.csv')
+data_pfv_fee <- read_csv('./_aux/data_pfv_test_pago_frec_vol_fee.csv')
 
 #RF Predictions
-rf_predict(data,"pago_frec_vol") 
-rf_predict(data,"pago_frec_vol_fee")
-rf_predict(data,"pago_frec_vol_promise") 
+rf_predict(data_pfv_fee,"pago_frec_vol_fee")
+

### 2020-01-20 RScripts/pfv_pred_hte.R

@@ -1,0 +1,52 @@
+library(tidyverse)
+library(grf)
+library(ggplot2)
+
+# SET WORKING DIRECTORY
+setwd('C:/Users/xps-seira/Dropbox/Apps/ShareLaTeX/Donde2019')
+set.seed(5289374)
+
+
+rf_predict <- function(data_in,take.up,nme) {
+  
+  require("dplyr")
+  data_train <- data_in %>% 
+    filter(insample == 1) 
+
+  data_test <- data_in %>% 
+    select(-c(take.up, nombrepignorante, prenda, insample, tau_hat_oobpredictions))
+###################################################################  
+###################################################################  
+
+    
+  # PREPARE VARIABLES
+  X <- select(data_train,-c(take.up, nombrepignorante, prenda, insample, tau_hat_oobpredictions))
+  W <- as.numeric(data_train[,take.up] == 1)
+
+###################################################################  
+###################################################################  
+  
+  
+  # ESTIMATE MODEL
+  pred.forest = regression_forest(X, W)
+  rf_pred = predict(pred.forest,data_test)$predictions
+  hist(rf_pred, xlab = "predictions")
+  
+  data.out <- add_column(data_in, rf_pred)
+  filename <- paste("_aux/pred_",nme,".csv", sep="") 
+  write_csv(data.out,filename)
+}
+
+#####################################################
+
+#RF Predictions of no-choice arm
+for (arm in c("pro_2")) {
+  for (pred in c("pago_frec_vol_fee")) {
+    for (effect in c("def_c", "fc_admin_disc")) {
+      filename <- paste("_aux/",arm,"_",pred,"_",effect,".csv", sep="")
+      data <- read_csv(filename)
+      outname <- paste(arm,"_",pred,"_",effect,sep="")
+      rf_predict(data,pred,outname) 
+    }
+  }
+}

### 2020-05-30 main.tex
update before restructure

--- 2019-08-20 main.tex
@@
 
+\usepackage{lmodern} 
+\usepackage{amsmath}
+\usepackage{amssymb}
+\newcommand{\wh}{\widehat}
+\onehalfspacing
+
 %\myexternaldocument{OA}
@@
 
-\title{Frequent Payment \thanks{}}
-\author{Joyce Sadka \and Enrique Seira  }
+\title{The limits of self commitment and private paternalism \thanks{}}
+\author{Joyce Sadka \and Enrique Seira \and Isaac Meza  \thanks{Sadka: ITAM, jsadka@itam.mx;  
+Seira: ITAM, enrique.seira@itam.mx; Meza: University of California at Berkeley, isaac.meza@berkeley.edu} }
 \date{This draft:  \today \\[2 cm]}
@@
 \begin{abstract}
-XXX 
+
+%Many firms provide commitment devices that restrict individuals' choice, but shroud this.
+Shrouding suggests low demand for commitment.
+We show that private paternalism is beneficial in the pawnbroker context we study.
+
+We study the benefits of ``private paternalism'' in the understudied but important pawnbroker context.
+We show that forcing people into commitment contracts with financial penalties for not paying on time decreases their (fee-including) financial cost by \hlgr{11\%}, increases the likelihood of recovering their pawn by \hlgr{23\%}, and increases the likelihood of repeat business by \hlgr{20\%}.
+While virtually all clients would reduce their financing cost with the commitment contract, we show that only 10\% choose it.
+Using salient personal promises instead of pecuniary penalties as commitment triples contract take-of, but has not effect on financial costs or pawn recovery.
+
+%and one of the most understudied.
+In our context more than on half of borrowers default and lose their pawn and whatever they have paid towards recovering it.
+Compared to the status quo pay-at-anytime 3-month contracts, forcing borrowers to pay monthly and charge a penalty if they didn't --i.e.
+a commitment contract-- increased recovery of pawn by about 30\% and financial costs by 10\%.
+However when offered a choice between the two contracts only 10\% took the monthly payment one.
+A pecuniary commitment seems necessary.
+In an alternative arm, we made them promise to pay but removed the pecuniary penalty.
+This increased take up to 31\%, but had zero effect on financing cost or default.
+The forcing contract may be better than choice for naive present biased consumers.
+
 \end{abstract}
 
-\textbf{Keywords: } XXX.
+\textbf{Keywords: } Private paternalism, choice, present bias, commitment, pawnshops.
 
-\textbf{XXX} XXX
+\textbf{JEL codes:} XXX
 
@@
 
+%NO MORAL HAZARD IN THE CONTRACT SINCE FULLY COLLATERALIZED
+%DOUBLE FAILURE: DEMAND LOW, AND DOES NOT WORK BY PEOPLE WHO TAKE IT.
+%PENALIZES THEM EVEN MORE ON SOMETHING THEY WERE ALREADY PENALIZED 
+%PROPENSITY TO CHOSE.
+%PULLING PUNISHMENT FORWARD --CHARGING RIGHT WHEN I MESS UP.
+%MAYBE ONLY IMPATIENT AND NAIVE END IN PAWNSHOPS
+%1) SELECT A RANDOM SAMPLE OF NEIGHBORHOODS, EXTERNAL VALIDITY, THE ONES THEY GO ARE NAIF AND
+%HYPERBOLIC
+%2) ASK TO CHOSE AMONG ALL CONTRACTS
+%3) CLASSIFY SOPHISTICATION AT BASELINE
+%4) HOW TO GET AT SHOCKS.  --BUT DOES NOT SQUARE WITH WHY CHARGING THEM FEES WORKE.
+%do shocks vary across strata, predict shocks.
+%DEEP BEHAVIORAL PAPER -- CAN WE REALLY PREDICT?
+
 \section{Introduction}
 
-\section{Conclusion}
+\cite{Laibson2018} recently noted that many institutions ---firms, schools, financial contracts--- restrict choice using built-in incentive/commitment mechanisms which help workers, students, borrowers overcome self-control problems.
+``Firms do limit their workers' freedom with intermediate deadlines, progress reports, production targets'', schools with ``pop quizzes, classroom attendance requirements, cold calling, graded problem sets, deadlines''.
+Similarly, mortgages do so ``with a fixed repayment stream and mandatory principal repayment''.
+However he notes that these same firms shroud these forcing mechanisms and don't market their commitment features, presumably because students, workers and borrowers ``don't welcome these paternalistic\footnote{\cite{Laibson2018} defines paternalism as a policy that advances an individual's interests by restricting his or her freedom, and private paternalism as paternalism implemented by private institutions.} restrictions''.
+In this, he sees an important \textit{commitment puzzle}: if clients were present biased and  sophisticated about their self control problem they should appreciate commitment features and firms should be eager to market them.
+The fact that this is not the case suggests some clients may be naive about their self control problems, and that \textit{private paternalism}  ---a policy of restricting choice implemented by private firms--- may increase clients' welfare.
+
+This paper studies private paternalism in the context of pawnbroker borrowing and finds evidence for its benefits.
+Pawnshops offer secure loans using items of personal property as collateral.
+The items pawned are called pledges or pawns.
+Pawn loans are one of the oldest forms of borrowing, and although data on their market share is scarce, anecdotal evidence suggests they are very prevalent.
+To give an example, our partner pawnshop (henceforth Lender $P$) served more than 1 million clients in the last 3 years with more than 4 million contracts.\footnote{For comparison there were approximately 2.3 million micro-finance clients in Mexico in 2009 in Mexico (\cite{Pedroza:2010}).
+We cannot be more precise on the number of total borrowers from Lender $P$ for confidentiality reasons.}  Pawn loans are interesting to study in and on themselves for this reason alone.
+But they are also interesting because regulators and practitioners view pawnbrokers as the lenders to which people in desperate need turn to.
+The regulators' concern is that the selection of clients that go to pawnshops may be particularly vulnerable, have bad debt management skills, and are more likely to be present biased and naive about it.\footnote{In 2013 Mexico's Consumer Protection Bureau (Profeco) forced Pawnshops to be more transparent in their pricing, register their contracts with them and issued regulation to protect clients: \url{http://www.diputados.gob.mx/LeyesBiblio/ref/lfpc.htm}.}
+
+Indeed, using a survey conducted by us in branches of Lender $P$, we document some evidence consistent with regulators' concerns: while pawnshop clients predict they will recover their pawn with 93\% probability on average, in reality only 40\% of them do, suggesting naivete.
+Conditional on paying a positive amount towards pawn recovery, 47\% lose their pawn and their payment.
+In our survey 68\% report self-control problems in several domains.%, but only \hlgr{15\%} show inter-temporal inconsistencies in a classical present-bias question, a similar number to \cite{Ashaf}.
+%and \hl{19\%} do not normally budget monthly expenses.
+%While this is suggestive of a present bias problem or overconfidence to save and pay, at the same time our subjects are experienced and not wholly uneducated, 66\% have completed at least high school and 90\% have pawned before.
+%and \hl{38\%} have participated in a Rosca.
+
+Consistent with little client sophistication, Lender $P$ offers a very simple but highly collateralized contract.
+It only accepted gold jewelry as collateral and approves all gold pawns, giving in exchange in cash the equivalent of 70\% of the weighted gold value.
+The contract stipulates a 7\% monthly interest rate charged daily, and a loan term of 90 days plus 15 grace days to pay the principal and the accumulated interest.
+The client has complete flexibility to pay any number of times any amount she desires towards the recovery of her pawn, with no pre-payment penalties.
+However if the total amount of principal plus interest is not covered by the end of the 105 days, she loses her pawn and all the payments that have been done (unless she renews the loan before this).
+All transactions ---appraisal of the piece, loan disbursement and loan servicing--- are conducted at the branch.
+The gold collateral is highly liquid and the pawnshop has an associated business that sells the gold jewelry.
+Given the over-collateralization of the loan one would expect no moral hazard or adverse selection on the part of borrowers.
+%This lets us focus more cleanly on behavioral economics aspects.
+
+To study the benefits of private paternalism, we implemented a relatively large randomized control trial with close to 10,000 pawnshop clients in 6 branches of Lender $P$ in Mexico City.
+We answer five main questions using this experiment.
+First, would clients benefit  ---in terms of recovering their pawn and in terms of incurring in lower financing costs---  from having a frequent (monthly) payment commitment contract \textit{forced} on them, instead of the current 3-month pay-when-you-want contract?
+That is, we are asking whether \textit{charging} them a 2\% late payment fee for not paying their monthly installment on time can actually decrease total fee-inclusive financing cost.
+Second, would there be demand for such a frequent payment commitment contract vis-a-vis the status quo one if given choice?
+Notice that any payment profile implemented in the commitment contract can be replicated under the status quo contract, but the later has more flexibility to respond to income shocks without incurring in fees.
+Third, what types of clients would demand these contracts that restrict choice?
+Fourth, are late payment fees key to provide commitment or would a non-pecuniary but salient personal promise to pay provide a cost-reducing mix of commitment vs flexibility?
+A large and important lab experiment literature suggest that promises change behavior significantly in laboratory settings, but we know little about their effect on the field in natural environments.\footnote{Some important papers in this space are \cite{PromisesPartnerships}, \cite{Vanberg}, \cite{Belot2010}, \cite{WhyDoPromises}, \cite{FurtherPromises}, \cite{Ismayilov2017}.} Finally and importantly, is \textit{giving choice} among contracts better than forcing them into payment-commitment contracts in terms of minimizing financing costs incurred and the likelihood of recovering their pawn?
+
+The experiment involved 5 arms, with randomization happening at the branch-day level.
+It is described in detail in Section \ref{Experiment}.
+Here let us briefly explain the main 3 arms.
+The first one involves a group of clients that were given only the status quo contract (henceforth the \textit{Status-quo group}).
+The second arm (\textit{Fee-forced group}) was assigned into a monthly payment commitment contract, which stipulated that clients had to pay 1/3 of their loan plus accumulated interest in each of the 3 months of the term length.
+Failing to do this would result in a fee of 2\% of the amount due that month.
+A third group (\textit{Fee-choice group}) gave clients a choice between these two contracts.
+
+We find that forcing clients into frequent payment commitment contracts causes them on average to save on financing cost and to recover their pawn more.
+The effects are large: financing cost decreases by \hlgr{11\%} on average, while the likelihood of recovering their pawn increases by \hlgr{19\%}.
+This is robust to including  transport costs of going to the branch plus losing a day's wage for each visit.
+Importantly, the benefits are distributed broadly: the whole distribution of treatment effects shows cost savings.
+The most economically vulnerable, those that report being stressed, and those that asked for a reminder at baseline, experience the largest financial cost savings.
+Those we classify as present biased and those that requested a reminder at baseline experience the largest effects on pawn recovery.
+%The commitment contract also causes payments to start 8 days earlier and be 16\% more frequent, compared to the control group.
+Treatment effects are concentrated on the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery.
+It seems that the fee-commitment contract induces people who would otherwise pay something towards recovery, to pay more and faster and thus recover their pawn more at a cheaper financial cost.
+Finally, we find that borrowers assigned to the forced fee-commitment contract are \hlgr{5pp} (\hlgr{20\%} of the mean) more likely to be repeat costumers than the control group, suggesting that they themselves liked the commitment contract more after experiencing it.
+
+%From this first comparison we conclude that penalizing borrowers for delinquency in a contract which has already has large penalties from default actually helps borrowers.
+In fact, we find that borrowers assigned to the forced fee-commitment contract are 5pp more likely to be repeat costumers, suggesting that they themselves liked the the commitment contract more after experiencing it.\footnote{As it is well known, \textit{naivete} facilitates their exploitation by firms.
+\cite{Laibson2018} conjectures that this exploitation may be limited if consumers use experienced utility to choose among firms or contracts.}
+
+In spite of these estimated benefits for all clients, their actual demand for the fee-commitment contract is low.
+Only \hlgr{10\%} of the group offered a choice between the monthly payment fee-commitment contract and the status-quo one chose the former.
+This is not likely driven by misunderstanding the (already simple) contract.
+We had two assistants from the research team in each of the experiment's branches every day for all branch opening hours, material was developed to explain the differences among the two contracts, and subjects spelled back to assistants the loan differences.
+Furthermore take up is systematically predicted by baseline covarites\footnote{We find that the more educated, those that report that their family typically asks for money, those that make a monthly budget of expenses, and ask for a remainder to payment (and marginally those we classify as present-biased) are more likely to chose the fee-commitment contract if given the choice.
+The opposite holds for those that are more vulnerable (can barely pay for food, electricity, etc) and those that report being more stressed.}, making it less likely that it is just random mistakes.
+Low demand for commitment is consistent with most of the literature (\cite{Laibson2015}, \cite{Laibson2018}, \cite{John}, \cite{Ted}, \cite{Rabin2018}).\footnote{\cite{Alcohol} and \cite{Kremer} are some of the few instances of high demand for commitment.
+\cite{Alcohol} speculates that this difference may be explained by their subjects having more experience with their self control problem.
+Close to ninety percent of our subjects claim to have pawned before.
+We find that experience does not predict positive take up in our sample.} \cite{Laibson2015} shows that the lost flexibility resulting from a commitment contract can severely limit take-up when agents are naive about their self control, even though commitment could we welfare improving for the naive.
+We estimate zero average treatment effects of the \textit{fee-choice} arm on financial cost and on pawn recovery.
+These effects are zero throughout the quantile distribution.
+
+ %Using boosting we can predict who takes up with 92\% accuracy. This fact shows that the choice among contracts is not purely random.
+
+How much money is left on the table by the prevalence of the status-quo choice?
+We calculate that about 80\% of clients in the fee-choice group chose contracts that induced \textit{higher} financial cost.
+On average they spend an extra \hlgr{\$300} pesos, close to 10\% of the average loan value.
+In particular \hlgr{95\%} of those that chose the status-quo contract would have been better in the fee-commitment contract, while only \hlgr{7\%} of those who chose the fee-commitment contract would have been better in the status-quo one.
+This suggests that forcing clients into commitment contacts (i.e.
+private paternalism) may be welfare increasing for the overwhelming majority of clients.
+
+Inspired by a significant lab experiment literature on the effects of promises on behavior, we also implemented a ``psychological commitment'' in the form of a salient promise to pay.
+\cite{PromisesPartnerships}, \cite{FurtherPromises}, \cite{Vanberg}, and \cite{Ismayilov2017} find that the ability to make a promise about behaving a certain way makes the individual more likely to adhere to the promised behavior.
+%and also induces trusting behavior by the recipients of the promise.
+To do this we implemented two other treatment arms.
+A \textit{promise-forced} arm exactly analogous to our \textit{fee-forced arm} except that instead of telling them that there is a fee if they don't pay on time, we made borrowers promise that they would pay one third of the amount in each of the 3 months, and told them that if they didn't they would have broken their promise.
+Because salience is key we made them sign a (non-legally binding) personal promise and emphasized we were counting on them to keep their promise.
+A final arm (\textit{promise-choice arm}) gave clients the opportunity to choose between the \textit{Promise-forced} contract and the \textit{Status-quo} contract.
+
+We document two main results in the promise arms.
+First, demand for the \textit{Promise-forced} contract is three times bigger than for the \textit{Fee-forced} contract, with \hlgr{31\%} take-up.
+This difference between both choice arms suggests that clients are indeed understanding and taking into account the contractual parameters when they choose, and that the fee commitment was probably too strong from their point of view.
+Second, the \textit{Promise-forced} contract had zero effects on average and for an overwhelming fraction of the population on financing cost and pawn recovery.
+The same is true for the \textit{Promise-choice arm}.
+%\footnote{There is a decrease in financial cost in the 50th and 75th quantiles in the forced promise-commitment arm however.}
+Promises did not provide enough commitment so as to be reflected in behavior.
+Contrary to lab evidence, people did not keep the promise, at least the way it could be implemented in the field.\footnote{The government Mexico has created a program called ``Loans on your word'' for uncollateralized borrowing (\url{http://tiny.cc/yfmnmz}), but they rely on group lending, and therefore social collateral is at stake.}
+
+%\footnote{This is consistent with \cite{Belot2010}, who emphasize that elicited promised may have lower effects than voluntary ones.}
+%\cite{Rabin2018} and \cite{Ted} show that naivete may lead to the choice of to little commitment. 
+%Before discussing results, let us mention why these questions are relevant and how they relate to the literature.
+Most of microfinance involves frequent payments/meeting with the group --sometimes weekly-- even though this increases transaction costs.
+Several hypothesis have been postulated to explain this, from increased group's cohesion and monitoring, to forming personal payment habits or serving as a commitment device.
+Most of the literature (e.g.
+\cite{Pande}) find however null effects of increasing frequency on default, and therefore on payment habits, commitment, or peer pressure.
+
+The paper is organized as follows.
+Section \ref{context} provides context and describes the data sources.
+Section \ref{Experiment} describes the experiment and shows pre-treatment balance across arms.
+Section \ref{fee-commitment} estimates the effect of forcing clients into the fee-commitment contract, while Section \ref{fee-choice} studies the effects of choice.
+Section \ref{promises} assesses if promises work in our context as commitment devices.
+Finally, Section \ref{conclusion} concludes.
+
+\section{Context and Data} \label{context}
+
+\subsection{The pawn lender and high default rates}
+
+Pawn borrowing is one of the oldest form of borrowing and one to which people with little access to the formal credit market turn to for ``energency'' loans.
+They existed in antiquity at least since the Roman Empire, and there are records of it in China about 1,500 years ago (\cite{PawnShops}).
+In spite of this, there are extremely few studies in the economics literature about it.
+Why people go, how much it costs, what different contracts can tell us about consumer biases.
+We study such  context with Lender $P$, one of the largest pawn shops in Mexico, with \hl{several hundred} branches spanning multiple States in Mexico.
+
+Lender $P$ was interested in understanding why half of their clients lost their pawn.
+It was concerned with high default rates for two reasons.
+The first is that the pawned piece may have a sentimental value to the client above of its gold value, making it inefficient for the lender to keep the piece.
+We actually find that clients report a subjective value that is almost \hlgr{twice} the value of its gold content.
+Second, it thought that keeping the piece lowered client satisfaction and made the client less likely to return and pawn again.
+They were interested in investigating whether a frequent payment contract would increase pawn recovery and costumer satisfaction, and whether there was demand for such a contract.
+Default is really  in this context  compared to many papers in the microfinance literature.
+\cite{Pande} study of the effect of payment frequency work in a context where the rate of default is close to 1\%.
+\cite{LittleAtAtime} has a baseline default of \hl{XX\%}.
+
+One potential explanation for high default is that clients are really just selling their gold piece.
+This is unlikely for the large majority of people not only because the reported subjective value of the pawn is larger than the loan size for \hlgr{86\%} of them, but also because among that lose their pawn \hlgr{74\%} paid a positive amount towards its recovery.
+This can only be rationalized if they expected to recover their pawn.
+Figure \ref{proxy_naive} focuses on those that ended up losing the pawn in our experiment and plots different measures of engagement with Lender $P$.
+Panel (c) shows total payments that went towards the loan.
+On average clients that lost their pawn paid \hlgr{34\%} of the value their loan.
+Panel (d) shows that while 40\% made zero payments, the rest made one or several payments.
+In fact, panel (b) shows that close to \hlgr{50\%} of clients extended the loan for another cycle and made payments in the second cycle.
+
+\subsection{The status quo contract}
+
+Their business model is very simple.
+They take gold jewelry as collateral in exchange for a fraction of money given instantly in cash.
+The transaction takes less than 10 minutes and is conducted at the branch in person between the client and the appraiser (i.e.
+a teller).
+The appraiser weights the gold piece and runs tests on its purity.
+Based on these he assigns a gold value to the piece, stores it as collateral, and gives 70\% of the gold value of the piece instantly and in cash to the costumer.
+The costumer signs a 2-sheet contract with the main conditions of the contract at the branch and leaves with the cash.
+
+Lender $P$ had only one type of contract.
+It stipulated that the interest rate was 7\% \textit{per month} accumulated daily on the outstanding amount of the loan.
+The loan had a 90 days term with 15 days grace period, and the client could make payments at anytime and no penalty for pre-payment.
+If the client paid the principal plus the accumulated interest before those 105 days, the she received back her pawn, otherwise the pawnbroker kept the piece and any payments done.
+Before the contract expired, the client had the right to renew it (using the same collateral) for another 3 months by going to the pawnshop paying the accumulated interest and signing a new contract with exactly the same terms.
+The pawnshop therefore makes money in three ways: by reselling the jewelry left as collateral on defaulted loans, by charging interest on non defaulted loans, and by keeping the payments made on defaulted loans.
+
+This contract was standard in the industry, the clients that pawned understood its conditions (as we verified in interviews) and still decided to pawn.
+Bear in mind that these clients have little or no access to other types of loans, and also that they value its convenience: the process is fast and requires no documentation or credit-history.
+Potentially they like it also because they are overconfident on average about the probability of recovering their pawn, as discussed below, even though \hlgr{90\%} of them have pawned before.
+
+\section{Data and summary stats}
+
+We worked in 6 branches of Lender $P$ of differing size and location, although for simplicity all of them in Mexico city.
+For these 6 branches we have two types of data, administrative data and survey data we collected ourselves for the experiment.
+
+\subsection{Administrative Data}
+The administrative data contains a unique identifier of the client, an identifier of the piece she is pawning, and the transactions relating to that piece.
+In particular, the value of the piece as assessed by the appraiser, the amount of money lent (70\% of the value), and the date when it was pawned.
+As described below, for our experiment we also recorded the type of contract for that pawn.
+After the pawn happens, we follow each transaction related to that piece in the administrative data: when were payments made and for which amounts, whether there was default (i.e.
+the client lost her pawn), and whether any late-payment fees (active for only some experimental arms) were imposed.
+We have this information for all the pawns that occurred in our 6 branches between \hlgr{August 6th 2012 and August 13th 2013}, this includes all the pawns under our experiment but also those that happened \hlgr{1} month before it started and up to \hlgr{8} months after it ended.
+Figure \ref{exp_description}(a) shows the timing of the experiment and our admin data coverage.
+The black arrow represent the dates for which we have administrative data (before and after the experiment) while the light gray represents the duration of the experiment.
+The experiment comprises \hlgr{13,443} pawns, and our administrative data cover a total of \hlgr{26,181} pawns.
+
+\subsection{Survey Data}
+
+We had a team of enumerators in each branch collect surveys and clearly explain the contract terms to walk-in clients.
+The enumerators were inside the branch and asked clients to complete a short 5 minutes survey before going to the teller window to appraise their piece.
+The survey was necessarily short to avoid discouraging the potential clients from pawning, but at the same time it aimed to measure the following: demographics, proxies for income/wealth, education, self-control problems/present-biased preferences, experience pawning, if the family or friends commonly asked for money, how time consuming and costly was to come to the branch, the subjective probability of recovering their piece that they intended to pawn, the subjective value of their piece in money terms (for how much money would they sell it for), among others.
+We were able to survey \hlgr{7,703} clients (some refused).
+%\footnote{We also surveyed clients before and after the experiment, so our survey covers a larger sample that we are not using in this paper.}.
+\hlgr{The appendix transcribes the questionnaire in English and presents summary stats}.
+Survey response rate is 57\%, \hlgr{the Appendix Table} \ref{balance_response} shows that response is not related to admin data observables.
+
+\subsection{Summary statistics}
+
+Table \ref{SS} presents some summary statistics for the whole sample and by treatment arm.
+Because treatment arms are described below, here we concentrate on the overall average.
+Panel A describes variables from the administrative data.
+It shows that the average loan size is \hlgr{\$1945} pesos (\hlgr{\$105} usd).
+The average number of pawns per day per branch is \hlgr{33}.
+Although not shown in the table, only \hlgr{40\%} of clients recover they pawn within \hlgr{230 days}.
+Even those that recover their pawn tend to pay ir back at the last moment, only \hlgr{20\%} pay before the \hlgr{90}th day.
+
+Panel B reports stats from our survey data.
+We learn that \hlgr{73\%} of clients are women, with an average age of \hlgr{44} years; \hlgr{66\%} of them have completed high school or more, and \hlgr{90\%} have pawned before, so that our sample has mostly experienced borrowers.
+Finally the subjective probability of recovery is close to \hlgr{93\%} on average, which contrast with the \hlgr{44\%} recovery that happens in reality for the pawns \hlgr{in the control group}.
+Just by this measure borrowers seem to be highly overconfident on average.
+It turns out that the average subjective value they report for the pieces is  \hlgr{6292 pesos}, which is much larger than the average appraised gold value (\hlgr{3222 pesos}).
+This makes it inefficient for them to lose it.
+
+Since the main treatment involves making them come to the branch to pay each month, the transaction costs of coming to the branch are important, and we ask two questions around them.
+The average time they take to come to the branch is \hlgr{22 minutes}, and the amount of money they spend in transport to do that is \hlgr{11 pesos} \hlgr{(\$0.60 usd)}.
+The population we are working with is economically vulnerable in the sense that \hlgr{31\%} of them could not pay \hlgr{either} water, electricity \& gas or rent in the past \hlgr{6} months.
+They often receive negative income shocks: \hlgr{87\%} said they are pawning because of an emergency, and only \hlgr{13\%} stated it was to use in a \hlgr{`non-urgent expense'}.
+%When asked why they are pawning this piece \hlgr{5\%} responded \hlgr{`lost a family member'}, \hlgr{`a medical emergency'} (\hlgr{11\%}), \hlgr{`an urgent expense'} (\hlgr{71\%}),
+
+\subsection{Financing cost and Default} \label{FC_def}
+
+Our main dependent variables are loan default and financial cost incurred by the borrower.
+Default is defined as losing the pawn.
+We observe directly when the piece gets appropriated by Lender $P$ and goes on sale.
+
+We define financial cost as the discounted sum of payments toward the loan plus the value of the loan, and substract to it the appraised or subjective discounted value of the pawn when it is recovered: $Financial \; Cost_i = \sum_t \frac{P_{it}}{(1+r)^t} + Pawn \: Value - \frac{\text{I}(Recovered \: Pawn) \times Pawn \: Value}{(1+r)^T}$, with $t$ indexing days, $T$ is the day when the pawn is recovered, I($\cdot$) an indicator function for recovering the pawn, $r$ is a daily interest rate equivalent to a \hlgr{7\%} monthly interest rate.
+Figure \ref{fc_hist}(a) plots a histogram of this cost in pesos conditional on recovering and conditional on not recovering the pawn.
+This cost is calculated for a time period of \hlgr{230 days} after loan origination, as \hlgr{51\%} of clients actually renew the loan one time and \hlgr{26\%} a second time.
+Of those who renew once \hlgr{36\%} lose the pawn, and of those that renew twice \hlgr{15\%} do.
+Figure \ref{fc_hist}(a) suggest that financial cost is significant, even for those that do recover their pawn.
+Panel (b) normalizes the cost by loan size.
+It shows that as a percentage of their pawn, most of the cost comes from clients that do not recover their pawn.
+For them the cost is between 150\% and 250\% of the loan value.
+\hl{The difference between panel (a) and (b) arises since clients who lose their pawn tend to be those that pledge cheaper pieces.} We calculate an APR of \hl{23,000\% on average for the control group.}\footnote{The Annual Percentage Rate is calculated as the internal rate of return $i$ using the following formula \hl{XXX}.}
+
+\section{Experiment} \label{Experiment}
+
+\subsection{Treatment arms and randomization}
+
+\noindent \textit{Selection of branches.} Starting \hlgr{August 6th} 2012, we implemented our experiment in 6 branches of Lender $P$.
+The branches were selected by Lender $P$ to be dispersed across Mexico city and have varying sizes.
+In four of them the experiment ran for \hlgr{107} days, and in 2 of them we ran it for a shorter time to economize on data collection costs since we realized we would not be constrained by sample size.
+%Thus we eliminated \hl{the smallest} ones.
+Branches are more than \hl{5 km} apart from each other, and there is little substitution among them (only \hlgr{1\%} of consumers appear in more than one of our branches).
+
+\vspace{.2in}
+\noindent \textit{The monthly payment contract.} For the purpose of the experiment we designed a new contract that is identical to the status quo contract in all respects except one.
+It has the same interest rate (7\% \textit{per month} which accumulates daily on outstanding debt, it has the same loan size/collateral ratio (70\%), it has the same loan term (90 days), and the gold pawn gets appraised in the same way by the same appraisers.
+The only difference is that it has a requirement that the client has to pay monthly: for the 3 month duration at least 1/3 of the loan value (plus accumulated interest) has to be paid before day 30th, 60th and 90th after loan disbursement.
+Failure to pay these amount triggers a penalty fee of 2\% of this minimum amount due (in some of the treatment arms), which is added to the amount that the client needs to pay to recover their pawn.
+This penalty acts as a commitment device to pay now vs paying later.
+The level of the penalty was determined by Lender $P$ after talking to clients and based on Lender $P$'s experience.
+They deemed 2\% something that was big enough to provide commitment but small enough that if clients had an emergency and could not pay, the fee would not cause the pawn to be unrecoverable.\footnote{As explained below we also experimented with a contract where there was no pecuniary fee for paying late but where we clients made a personal promise to pay monthly.}
+
+\vspace{.2in}
+\noindent \textit{Randomization.} Randomization was done at the branch-day level.
+Each day the system chose which types of contracts were on offer that day in the branch, and therefore which contract the client signed.
+Branch personnel did not know which treatment would happen which day.
+They were told that there were 5 different ``types of contract-days'' and that the system chose randomly which applied any given date, and that it could happen for instance that two consecutive dates had the same contract.
+They were also told that this way of operating was in effect in various Lender $P$'s branches (they did not know which ones), and that it could be in place for several months.
+Randomizing at the day level limits the problem of contamination arising from clients waiting for appraisal observing that other clients get different contracts than theirs.
+It also limits potential  manipulation by appraisers, who in the presence of individual level randomization could potentially pick their preferred costumers from the line or tell them to wait until their desired contract shows up on the screen.
+Intra-branch correlation on the probability of default (ICC) is small, at \hlgr{0.08}, so we don't lose much power vis-a-vis individual level randomization.
+
+\vspace{.2in}
+\noindent \textit{Treatment Arms.} We have 5 different experimental arms, which differ in which contracts were offered on a given branch-day.
+
+\begin{enumerate}
+    \item \textit{Status-quo} arm: consisted of branch-days offering the status quo contract described in Section \ref{context}, and only this contract (as was standard). 
+    \item \textit{Fee-Forcing} arm: consisted of branch-days offering only the monthly payment contract with a fee for late payment. 
+    \item \textit{Fee-Choice} arm: consisted of branch-days where the client was given \textit{a choice} between the monthly payment with fee contract, and the status quo contract.
+    \item \textit{Promise-Forcing} arm: consisted of branch-days which offered the monthly payment contract only, but where there was no fee penalty.
+Instead, the client was made to sign a paper which said ``I promise to pay every month the corresponding sum of \_\_\_\_\_\_, on the dates \_\_\_\_\_\_, \_\_\_\_\_\_, and \_\_\_\_\_\_.
+This is \underline{not} a legal document and cannot be used in courts.
+It is just a \textit{personal promise}.
+If I do not comply I would have broken my word.''.
+After signing, the promise was read to her by the appraiser.
+    \item \textit{Promise-Choice} arm: consisted on branch-days where the client was given \textit{a choice} between the Promise-Forcing and the Status quo contract.\footnote{We did not allocate equal number of days across arms, since we were interested in having more power in some of them.
+The days allocated to each -- in order-- were 84, 80, 93, 68, 82.}
+\end{enumerate}
+
+By comparing the \textit{Fee-Forcing} group vs \textit{Status-quo} group we estimate the causal effect of the commitment contract over the contract where the client can paying whenever they want in a 105 day period.
+On the other hand, having arms where clients could choose among these contracts allows us to study their demand for commitment.
+Note that a neoclassical consumer (with no intra-household concerns) would not voluntarily restrict her options of payment profiles (as in monthly payment contract) and be subject to fees since she can always replicate the monthly payment profile herself under the status quo contract if she so desired.
+The status quo contract gives her extra flexibility to respond to income shocks for instance.
+However, if clients have present biased preferences \textit{and} are sophisticated about them, they may choose the frequent payment contract as it has commitment value.
+This value would be traded off against the value of flexibility.
+This design also allows us to test if promises work in a natural field environment which to our knowledge has not been done.
+Promises could have larger or smaller commitment value that a pecuniary fee, something that we test by comparing behavior in the \textit{Promise-Forcing}  vs \textit{Status-quo} arms.
+
+Panel (b) of Figure \ref{exp_description} shows how many contracts the experiment has on each arm (rectangles).
+And for the choice arms, it displays in blue how many people actually chose the commitment contract.
+
+%\subsection{Connection to the literature}
+%Our study connects with two strands of the literature on microfinance.
+But also to a nascent one that uses RCTs to study to what extent people self-sort to treatments that have larger beneficial treatment effects for them.
+On the microfinance literature the first paper we could find that used an RCT to evaluate the causal effect of frequent payments in loans is \cite{Pande}.
+In a group lending rosca context, they note that most contracts involved frequent repayments --even weekly in many instances-- even when this increases transaction costs.
+They note that clients could benefit from ``the fiscal discipline afforded by the more rigid payments''.
+Frequency could provide a commitment device for clients, could foster a payment habit, or could generate more trust from social interactions among the group of borrowers.
+All these potential benefits apply in our context, except those relating to social interactions, as we work with individualized loans.
+
+\subsection{More on implementation.}
+
+We want to highlight two potential threats to the validity of our experiment.
+The first is that the client can chose to leave the branch after the appraiser values her pawn and tells her the contract terms, generating differential attrition across treatment arms.
+We anticipated this possibility and trained appraiser to say --that whatever was the contract that day-- it was the only available contract for an undetermined amount of time.
+Empirically, attrition was not a problem.
+Table \ref{SS} shows that the number of pawns per branch per day across treatment arms is statistically identical.
+The last column of the table displays the p-value of an $F$ test of equality of means across arms and shows we cannot reject equality for any of the variables (p-value=0.38 for the number of pawns per day per branch).
+There is no evidence for selection across treatment arms for any of the admin or survey variables.
+
+The second threat is clients' understanding of contract terms.
+We realized that we needed the terms to be understood in order for choice to be meaningful, and for the monthly payment commitment to have bite.
+We had two `check-points' to do this.
+First, two ITAM students were present in each branch for the whole day during the duration of our experiment to explain to clients the contract terms.
+One of the aspects emphasized was that the frequent payment contract involved the commitment to pay \underline{each month} a third of the outstanding amount, and that there was a 2\% penalty fee (or the psychological cost of breaking a promise) for failing to do so.
+Figure \ref{ExplanatoryMaterial} translates a piece of the materials we used to explain the contracts (in this case a comparison sheet used in the Promise-Choice days to compare contracts terms side to side).
+The explanation took about 3-5 minutes and was pursued until the client said she understood the contract terms.
+Students then asked clients to explain back the contract terms.
+
+There was a second check point.
+Before the clients signed the contract, the appraiser made them read them the ``Contract Terms Summary'' sheet shown in Figure \ref{PaperSlip}.
+It was a piece of paper given to clients after their piece had been appraised and the size of the loan determined, but before they signed their contract.
+The appraised read it and asked the client to sign it as a proof of understating.
+The sheet clearly indicates that this contract is a monthly payment one (numeral 1), that there is a penalty of 2\% for paying late (numeral 2), and the 3 payment dates (numeral 3).
+Finally, the bottom of the Figure \ref{PaperSlip} shows the paper slip we used for the promise arms.
+The clients had to put their name in a slip of paper where they stated they promised to pay monthly.
+
+We are fairly confident that the overwhelming majority of clients understood the contracts and made informed choices.
+As shows below, different contract terms did generate differential demand and differential behavior.
+Moreover, we can systematically predict demand based on consumer characteristics, beliefs and proxies for present biased preferences.
+
+\section{The effect of forcing into fee-commitment} \label{fee-commitment}
+
+\subsection{The effect of the fee-forcing contract on financial cost and pawn recovery} \label{TE_fee-forcing}
+
+Now we answer our first question.
+Would clients benefit ---in terms of recovering their pawn and in terms of paying lower financing cost--- from having a monthly payment commitment contract \textit{forced} on them, vis-a-vis the status quo pay-when-you-want contract?
+We find they do.
+For each comparison, we separately estimate the regression equation (\ref{basic_reg}) below.
+
+\begin{equation} \label{basic_reg}
+    y_{ij} = \alpha + \beta T_{i} + \gamma X_{ij} + \epsilon_{ij}
+\end{equation}
+
+\noindent where $i$ refers to client, $j$ indexes branch, and $X_{ij}$ are branch and day-of-week fixed effects, as well as dummies for the number of arms a client fell into and number of pieces pawned during the whole experiment\footnote{\hl{ISAAC: puedes incluir en appendix una tabla que muestre en que tratamientos cayeron todas la prendas durante el experimento?
+Y tambien un tab de cuantas personas empeniaron 1, 2, 3...
+piezas durante el experimento?}}.
+Our main outcome variables $y_{ij}$ are measures of financial cost in pesos as defined in Section \ref{FC_def}, as well as an indicator variable for client $i$ losing her pawn.
+In this subsection $T_{i}$ is an indicator for $i$ having got the \textit{fee-forcing} contract, and $\beta$ estimates the average treatment effect.%\footnote{This is an ATE and not just an ITT since take up of treatment is 100\%.}
+
+\vspace{.2in}
+\noindent \textbf{Financial Cost.} Figure \ref{fc_pro2}(a) reports $\beta$ coefficients and their 95\% confidence interval from estimating equation (\ref{basic_reg}) using different definitions of financial cost.
+The leftmost coefficient corresponds to using the appraised gold value of the pawned piece when the client loses it (not discounting makes virtually no difference).
+The second coefficient uses the subjective value of the pawn instead.
+In both cases we find that being assigned to the fee-forcing commitment contract causes a large reduction in the financing cost the client incurred, of \hlgr{11}\% in the fist definition and \hlgr{15\%} in the second one.
+That is, we find that \textit{charging} clients a late payment fee  actually decreases total \textit{fee-inclusive} financing cost.
+
+Financial cost incurred by pawn-shop clients is a key variable to study.
+However it is true that it does not take into account other costs like transportation or the opportunity cost of going in person to the branch.
+Given that the fee-forcing contract makes clients visit the branch more often (monthly), one may want a measure that includes those costs as well.
+Going in that direction, in a broader measure of costs, for each visit we add the self-reported transport cost\footnote{Here we had to restrict \hlgr{93\%} of the sample for which we had information on these.} plus a whole day's wage, multiplied by the number of visits.
+Adding a whole day's wage may be too conservative, but we still observe a reduction of this more comprehensive measure of cost.
+
+\vspace{.2in}
+\noindent \textbf{Heterogeneous Treatment Effects.} Average cost reductions could mask substantial heterogeneity.
+We find that benefits are distributed broadly however.
+Figure \ref{fc_pro2}(b) displays results from quantile regressions at the 15$^{th}$, 25$^{th}$, 50$^{th}$ 75$^{th}$, and 85$^{th}$ percentiles.
+All of them are negative and significant.
+Figure \ref{fc_pro2}(c) uses \cite{atheygrf} generalized random forests methodology to estimate person specific treatment effects and plots the distribution of those treatment effects.\footnote{\cite{atheygrf} use random forest of honest causal trees to estimate personalized treatment effects.
+The trees are such that at each leave (partition determined by covariates) it unbiasedly estimates a treatment effect using treatment and control observations in that leave.
+The optimal partition of leaves is that which minimizes expected mean squared error of treatment effects predictions out-of-sample.
+The tree is honest because it uses one sample to build the tree and another one to estimate treatment effects within that tree.
+After the optimal tree is build, each person in each leave is assigned the treatment effect of that leave.
+\cite{atheygrf} show that their treatment effects are asymptotically normal, which allows us to construct confidence intervals for our treatment estimate in each leave.} We find that virtually all (\hlgr{94\%}) of clients experienced financial cost savings in the fee-forcing group compared to the status-quo group.
+Figure \ref{HTE_fee_forcing}(a) in the Appendix shows that the (causal) cost savings are largest for the more economically vulnerable, %that report at baseline that they have problems paying for services like water, electricity and rent,
+those that report being stressed, those that have to incur in higher transport cost to go to the branch  and that asked to be sent reminders to pay, this later one being one proxy of being inattentive or sophisticated present-biased.
+
+\vspace{.2in}
+\noindent \textbf{Pawn Recovery.} Figure \ref{fc_pro2}(d) plots estimated treatment effects of the fee-forcing commitment contract with the dependent variable being an indicator of losing the pawn in less than \hlgr{230} days.
+The leftmost coefficient shows that the fee-forcing commitment contract increases the likelihood of recovering the pawn by \hlgr{11pp} (\hlgr{25\%} of mean recovery).
+This is a large effect.
+It contrasts for instance with \cite{Pande} who find no effect of payment frequency on default in a group lending microfinance context.
+Figure \ref{HTE_fee_forcing}(b) in the Appendix shows that those we classify as present biased, those that requested to be sent a reminder to pay, and those who have more problems paying for basic services experienced the largest increases on pawn recovery.
+
+%the second conditions on the population that paid any positive amount towards recovery of their pawn; the third conditions on having paid at least 30\% of the loan amount; the fourth conditions on the period covering the first cycle of the loan; the fifth on the period of the first cycle and paying any positive amount.
+
+\vspace{.1in}
+\noindent From this first comparisons we conclude that penalizing borrowers for delinquency in a contract which has already has large penalties from default (losing the collateral in a highly collateralized loan) actually helps borrowers.
+
+\vspace{.2in}
+\noindent \textbf{Effect on other outcomes.} There are other (intermediate) outcomes that are impacted by treatment.
+Table \ref{mechanisms} shows that the first payment happens 8 days earlier (column 1) in the fee-forcing arm than in the status quo one, and that the number of payments increases by 0.19 (column 2).
+Figure \ref{induced_to_pay_early} in the Appendix correlates heterogeneous treatment effects on financing cost and time of first payment and shows that those induced to pay earlier are also those that have larger induced savings in financial cost.
+A second finding is that treatment effects are concentrated on the intensive margin, as treatment does \textit{not} affect the fraction of clients who pay a positive amount (column 6).
+The percentage of the loan paid increases by 8 percentage points on average (column 7).
+Note however is that the percentage of the loan paid is not larger for those that end up losing the pawn (first row of column 8).
+
+\vspace{.2in}
+\noindent \textbf{Other sub-samples.} Going back to Figure \ref{fc_pro2}(a), we estimate some interesting correlations.
+The 4th coefficient from left to right conditions on those who paid a positive amount (in treatment and control).
+Although this is potentially an endogenous population, Table \ref{mechanisms} showed that there is no treatment effect on Pay$>$0.
+We were interested in this population to show that the effect is there for those who are serious about recovering their pawn.
+The fifth coefficient conditions on those that paid a fee in the fee-forcing group.
+In effect comparing this subset in treatment vs all of the control group\footnote{Results are similar if we condition in the control group on those who would have paid a fee given current behavior.
+Again we acknowledge these is an endogenous control and that the estimate is not a causal effect.\hl{ISAAC, puedes checar que sale asi si corrieras esta nueva regression?}}.
+We find even those that paid a fee in the fee-forcing contract end up paying a smaller financial cost that those in the status-quo contract.\footnote{This is not an experimental comparison as who pays a fee in the treatment group is a selected sample, but we found this relationship interesting nonetheless.} Figure \ref{fc_pro2}(c) shows that the increase in pawn recovery is robust to defining recovery using the first 120 days of the contract, or restricting to those paying a positive amount towards pawn recovery.
+
+\subsection{Effects of fee-forcing on repeat pawning}
+
+We have shown that clients are more likely to recover their pawn that virtually all of them incur in a lower financial cost  when assigned a monthly payment commitment contract with fees.
+This however does not necessarily show that they benefited in utility terms, and this is hard to show directly.
+If ---as suggested by \cite{Laibson2018}--- consumers used ``experienced utility'' as a guide to make future purchases, we conjecture that clients in the fee-forcing contract would be more likely to be repeat costumers vis-a-vis those that got status quo contract.
+This is indeed what we find.
+
+Figure \ref{reincidence} presents results of equation (\ref{basic_reg}) where the dependent variable is a dummy for the client to be a repeat costumer.
+We define a client in our experiment as a repeat costumer if, after experiencing at least 75 days of the respective treatment arm, she came back and pawned \hlgr{a different piece}.\footnote{Results are robust to using other number of days besides 75.}  The left most coefficient shows that the causal effect of the fee-forcing contract on repeat pawning is an increase of 5pp in the probability of being a repeat costumer, this is \hlgr{20\%} on a mean re-incidence in the control group, with respect to those that got the status-quo contract.
+This is not explained by clients recovering their first pawn with higher probability in the fee-forcing contract and re-pawning this same one since we make sure it is another piece (besides only \hl{XX\%} recover their piece in the fist 75 days in the fee forcing contract).
+The second coefficient restricts to the population who had larger (treatment effect) financial cost savings in their first pawn, and shows that the effect is twice as large for them.\footnote{\hl{ISAAC, podrias quitar de esta Figure 5 los coeficientes ``| rec.'' y el de ``fnr'' de TODA esta Figura 5?
+Pon como el 2do coeficiente que dice ``| >50th perc.'', esos si dejalos}} That is, those that benefit more from the fee-forcing contract are much more likely to repeat.
+%The coefficient on repeat pawning is just as big when we focus only 2nd pawns happening after the first was recovered (third coefficient ``fnr'').
+This is consistent with \cite{Laibson2018}'s conjecture that clients could be making decisions based on experienced utility.\footnote{The third coefficient conditions on the subsample that did recover their first pawn in both arms and finds a coefficient of 4pp.
+This is not a causal estimate as recovery is influenced by treatment, but we found it telling that the differences were similar to the causal estimate for the full sample.}
+
+We also implemented an exit survey which clients filled when recovering their piece.
+Unfortunately it had low response rates (\hlgr{7\%}), and we take its results with a grain of salt.
+In this survey \hlgr{63\%} said they liked the frequent payment contract more than the status-quo one, and that is allow them avoid unnecessary expenses.
+
+\section{The effect of giving choice} \label{fee-choice}
+
+Section \ref{fee-commitment} showed that the fee-forcing commitment contract reduced financing cost across the board, and that consumers themselves seemed to like it once they tried it.
+In such a case, one would expect a strong demand for it, unless consumers underestimated these benefits.
+
+\subsection{Demand for the fee-forcing commitment contract}
+
+To study demand for commitment, in one experimental arm, we let clients freely choose between the two types of contract: the fee-forcing commitment contract or the status-quo contract.
+The first result here is that in spite of broadly distributed benefits of the fee-forcing commitment contract we documented above, 90\% of clients chose \textit{not} to have it, they instead preferred the status-quo one.
+As explained above we are fairly confident this was not because a lack of understanding of the contracts.
+
+What can explain this low demand?
+This section discusses some hypothesis but lack of data limits what can be tested.
+One neoclassical explanation could be risk.
+Even if the fee forcing contract generates cost savings on average, clients with risk averse preferences may not demand it if they perceive higher risk from it.\footnote{Because they have not experienced the fee-forcing contract before, ambiguity aversion may play a role here too.} Alternatively, even risk-neutral agents may not demand it if the cost of lost flexibility is high.
+If they for example face large and frequent income shocks which make it hard to repay monthly.\footnote{We don't observe income shocks in our data, making is hard to quantify how important they are.
+\hlgr{90\%} of those in the fee-forcing arm incurred a fee, which suggests that shocks are not uncommon (or clients inattentive).} Note that income shocks that affect the ability to pay the entire loan are a worry for both the fee-forcing contract and the status quo one, and should not make one contract more favorable than the other.
+
+\vspace{.1in}
+\noindent \textbf{Lost flexibility.} While we cannot rule out that income shocks combined with lost flexibility of the contract explain the low demand, we think it is unlikely.
+Note that fees for late payment are not that high.
+In an average loan of 2,000 pesos the monthly payment is close to 700 pesos, and a fee of 2\% of that is 14 pesos (less than \$1 dollar).
+This is about \hlgr{1\%} of monthly per capita income of the first 3 deciles of Mexican \hl{household's} income distribution.
+%This compares favorably to the \hlgr{\$11.6 + \$62.3)} pesos transportation / transaction cost of one.
+So even if households experience a negative income shock and cannot pay that month, the cost of paying the fee does not seem too burdensome, especially when compared to the savings they are experiencing.
+To make this more concrete we did this simple back-of-the envelope exercise to compare cost savings against fees.
+We pretended that all clients in the fee forcing contract incurred in \textit{all} potential fees, and added these fees to their financial cost.
+We then re-estimated the quantile treatment effects of Figure \ref{fc_pro2}(b) with this inflated financial cost (keeping all else constant\footnote{Of course behavior may not be constant, but we believe this is a reasonable fist approximation.
+%It could be that having this small fee added to the balance discourages them to pay or makes it harder to pay back the loan.
+But the contrary may also happen, with the fee making them more determined to pay early.
+We would need a structural model of client behavior to estimate a full counterfactual.
+We suspect that such small fees would not generate large changes in behavior in a simple neoclassical model.
+}). \hl{We find that even in this extreme scenario, tilted against the fee-forcing contract, all the estimated effects still imply cost savings from the fee-forcing contract.}
+
+\vspace{.1in}
+\noindent \textbf{Risk aversion.} We do not have measures of risk aversion in our necessarily short survey, which makes it very hard to assess this hypothesis.
+To have a benchmark we implement a very simple calibration exercise in two steps.
+First, we fit a Weibull distribution to the distribution of financing cost, were the scale and shape parameters depend on client's and loan observable characteristics.
+We do this separately for the status quo contract and the fee-forcing contract, obtaining two distributions $f_{sq}(FC|X;\Gamma_1)$ and  $f_{fee}(FC|X;\Gamma_2)$ with different parameters $\Gamma_1$, $\Gamma_2$.
+Second, we assume a representative consumer with a CRRA utility function over financial cost, $u(FC)=\frac{1}{1-\theta}FC^{1-\theta}$.
+We then ask what would $\theta$ have to be for a consumer to prefer the status-quo contract.
+That is for which $\theta$'s would  $\int u(FC|\theta)f_{sq}(FC|X;\Gamma_1) dFC \geq \int u(FC|\theta)f_{fee}(FC|X;\Gamma_2) dFC $ hold?
+It turns out that it holds for risk aversion levels that are too high to be believable.
+That is, with our calibration, it seems unlikely that risk aversion is reducing demand for the fee-forcing contract.\footnote{This of course assumes that clients know the distribution of financial cost outcomes, which is all we can do with our data.}
+
+\vspace{.1in}
+\noindent \textbf{Present bias with naivete /  overconfidence in recovery.} The leading behavioral explanation for low demand for commitment which would is present biased preferences with naivete.
+Of course these may interact with the neoclassical explanations above.
+In fact \cite{Laibson2015} shows that the lost flexibility resulting from a commitment contract can limit take-up specially severely when agents are naive about their self control, even though commitment could be welfare improving for the naive.
+There is some evidence supporting that individuals have incorrect expectations about their recovery probabilities.
+The subjective probability of recovery is close to 93\% on average, while the actual average is 44\% for the pawns in the control group.
+\hl{It turns empirically that overconfidence (OC), defined as the reported subjective probability of recovery minus the predicted probability, $P^s_i-\widehat{P_i(X_i)}$, is a significant predictor of low take up.}.
+Using a definition of intertemporal preference reversal analogous to that if \cite{Ashraf} we find that \hlgr{15\%} of clients are classified as present biased (\hl{similar to the number they find} but small to explain low take up), and that they have lower take-up.
+Another indication of overconfidence is the large number of people that pay a positive amount toward recovery but end up losing their pawn anyway.
+Figure \ref{proxy_naive}(c) showed that on average clients that lost their pawn paid \hlgr{34\%} of the value their loan.
+
+\vspace{.1in}
+\noindent \textbf{Predictors of take up.} Using \hl{random forests} we can predict who takes up the fee-forcing contract with \hl{87}\% accuracy out of sample.\footnote{Correcting for the fact that most chose the status-quo contract using the method of \hl{SMOTE}, \cite{smote} we find an accuracy rate of \hl{XXX\%, ISAAC}.} Which suggests that choice among contracts is not purely random.
+Figure \ref{interactions_takeup} in the Appendix shows that the more educated, those that report that their family typically asks for money, those that make a monthly budget of expenses, and those that ask for a remainder of their due payments (and marginally those we classify as present-biased) are more likely to chose the fee-commitment contract if given the choice.
+The opposite holds for clients that are more economically vulnerable (can barely pay for food, electricity, etc) and those that report being more stressed.
+
+\subsection{The effect of choice on pawn recovery and financial cost} \label{effect_choice}
+
+When preferences or income streams are heterogeneous, and consumers are neoclassical, giving choice among contracts is a welfare increasing strategy.
+Consumers would chose the contract that best fits their needs.
+This holds also in most simple models of present bias preferences if consumers are sophisticated about their present bias.
+%Actually, it could be the case that the opportunity of choosing itself could affect behavior.
+But when consumers are overconfident about their ability to save cash to pay back the loan, free choice could be a sub-optimal policy from the point of view of the client's long run self, and match the clients with a more costly contract.
+
+Even if take up of the commitment-fee contract is low, the sole fact of having choice could potentially change behavior (\cite{Dalboetal:2010}, \cite{Sjostrometal:2018}).
+We find that giving clients the option of choosing among the fee-forcing and the status quo contract does \textit{not} lead to lower financial cost compared to forcing them into the status-quo contract, Figure \ref{fc_pro4}(a) hollow circles.
+Nor does it lead to higher pawn recovery, Figure \ref{fc_pro4}(c).
+The hollow circles in Figure \ref{fc_pro4}(show average effects for the different definitions of financial cost analogous to the ones described above.
+Figure \ref{fc_pro4}(b) shows further that the null effect happens for the 15$^{th}$, 25$^{th}$, 50$^{th}$ 75$^{th}$, and 85$^{th}$ percentiles.\footnote{The few that selected the fee-commitment contract (the solid black squares) do enjoy cost savings of 939 pesos, which compares favorably to the 339 pesos in the fee-forcing arm (as a fraction of the loan the numbers are \hl{XXX} and \hl{XXX}), but this combines the selection and treatment effects.
+We cannot reject the that the ``effect'' on pawn recovery is of the same size for the fee-forcing arm and for those that selected into fee-forcing.} %Figure \ref{heterogeneous_te_4} plots the distribution of treatment effects and finds that the distribution offering choice actually \textit{increased} financial cost and default for about half of clients compared to being assigned the status-quo contract.
+Those tended to be the less economically vulnerable and more educated, \hl{women}, and those whose family typically asks them for money.
+Consistent with these findings, Figure \ref{reincidence} finds no effect on repeat purchases for the choice group.
+
+\subsection{The scope for private paternalism}
+
+This is not the first paper to find low demand for commitment, however it is the first we know of that can compare choice vs forcing.
+The fact that the fee-forcing contract lowers financial costs for all, together with the fact that only 10\% choose it must mean that many consumers are choosing contracts with higher financial costs for them.
+We can ask how many consumers seem to be making a cost increasing choice and how much money are they leaving on the table.
+To do this we conduct two exercises.
+
+\vspace{.2in}
+\noindent \textbf{Are there ``mistakes'' in choice?} Answering this question requires calculating a counterfactual: for each person in the choice arm we want to know how much cost savings a client would have if she chose the fee-commitment contract instead of the status quo contract.
+We do this in two steps.
+First, using the honest causal forests method of \cite{atheygrf} described above we calculate the causal effect on financing cost of getting the fee-forcing contract instead of the status quo contract for a client with characteristics $x_i$ \textit{in the forcing arms}, we call it $TE^{fee}_{i}$.
+There is no selection problem in the forcing arms.
+Second, using these estimates, we predict treatment effects for clients \textit{in the choice arm} using the $x_i$'s, and call it $\widehat{TE}^{fee}_{i}$.
+This is precisely the counterfactual we wanted.\footnote{This extrapolation of the treatment effects assumes that choice itself --conditional on a given contract-- does not affect behavior.
+Given the results in subsection \ref{effect_choice} we are comfortable with this assumption.
+Note that although the extrapolation is to another population, by randomization it is a statistically identical population.} Armed with this, we say that a client made a ``mistake'' if either she chose the status quo contract and her $\widehat{TE}^{fee}_{i}$ is negative (i.e.
+more cost saving from the fee contract), or if she chose the fee-commitment contract and $\widehat{TE}^{fee}_{i}$ is positive, meaning that financial cost are larger for the fee-commitment contract.
+When a client made a choice mistake, we say that the peso-size of it is $|\widehat{TE}^{fee}_{i}|$.
+
+%Using the forcing arms and extrapolating to the choice arms.
+%Then, we predict these treatment effects for everybody in the choice arm using characteristics $x_i$.
+Let $\widehat{TE}^{fee}_{i}$ be the predicted financial cost savings for person $i$ of choosing the fee-forcing contract rather than the status quo one, divided by the size of her loan (i.e.
+the negative value of the predicted treatment effect on financial cost for person $i$).
+$\widehat{TE}^{sq}_{i}$ is the analogous for the status quo contract.
+We define the choice of person $i$ to be a ``mistake'' if
+
+%\begin{equation}
+% \{ i \; \text{chose} \; sq \; \text{and} \; \;  \widehat{TE}^{fee}_{i}>\widehat{TE}^{sq}_{i} + z \} \; \text{or} \; \{ i \; \text{chose} \; fee \; \text{and} \; \;  \widehat{TE}^{fee}_{i}<\widehat{TE}^{sq}_{i} - z \}
+%\end{equation}
+
+Since the prediction of the treatment effect is an estimate and has noise, we do two things.
+First, we normalize $\widehat{TE}^{fee}_{i}$ by the value of the loan of person $i$ and introduce a threshold parameter $z$ and say that a choice is a ``mistake'' if the alternative contract would generate more than $z$ in savings.
+We vary from 0\% to 20\% of the value of the loan.
+Second, we take into account uncertainty in estimation of treatment effects and report results also using the extremes of the 95\% confidence interval bounds for $\widehat{TE}^{fee}_{i}$.
+
+Figure \ref{choose_wrong}(a) plots in the left Y-axis the fraction of clients that made a choice ``mistake'' and on the right Y-axis the peso size of the mistake.
+In the X-axis it varies the threshold $z$ of what we classify as a mistake.
+In this section we are concerned with lines in red color.
+When $z=0$, we calculate that about 83\% of clients in the fee-choice group chose contracts that induced \textit{higher} financial cost (95\% confidence interval [\hlgr{40},\hlgr{93}]).
+Most mistakes are failures to choose the fee-commitment contract (\hlgr{95\%}), while only \hlgr{7\%} of those who chose the fee-commitment contract would have been better in the status-quo one.
+The average mistake in pesos is \hlgr{\$352} (95\% confidence interval [\hlgr{170},\hlgr{534}]).
+Figure \ref{choose_wrong}(b) separates the analysis for those we classify as overconfident about recovering their pawn (\hl{XXX of them} vs the rest.
+It shows that the there are about \hl{20 percentage points} more mistakes in the overconfident population when $z=0$.
+
+All the above suggests that forcing clients into commitment contacts (i.e.
+private paternalism) may be welfare increasing for the overwhelming majority of clients.
+Figure \ref{choose_wrong}(c) calculates what fraction of clients would be made better off if we forced them to the fee-commitment contract: \hl{96\%} when $z=0$, and they would on average have savings of \hl{280} pesos.
+
+\vspace{.2in}
+\noindent \textbf{Is there positive selection on treatment effects?} The previous exercise consisted on extrapolating treatment effects from the no-choice arms to the choice arm.
+Here we do the converse.
+First, we estimate a flexible model of take-up of the fee commitment contract \textit{in the choice arm} using random forests and obtain for a client with characteristics $x_i$ a probability $P(x_i)$ of choosing the fee-forcing contract.
+We then use this model to predict the counterfactual probability of client with characteristics $x_i$ choosing the fee-commitment contract in the no choice-arms if she would have been given the choice, what we call $\widehat{P(x_i)}$.
+Since our model for has a good out-of-sample fit with an \hl{adjusted} AUC of \hl{0.77} and an \hl{adjusted} accuracy rate of \hl{87\%}, we think we are not introducing too much noise by this extrapolation.
+Second, armed with this prediction in the no-choice arms, we can ask the following: is it true that people with larger fee-forcing contract treatment effects (i.e.
+more cost savings) more likely to demand the fee-forcing contract?
+
+Figure \ref{choose_wrong}(d) plots $\widehat{P(x_i)}$ in the X-axis, and the heterogeneous we estimated in section \ref{TE_fee-forcing} in the Y-axis.
+If it was true that those with larger cost savings have larger demand for the fee-commitment contract, we would expect a negative slope (recall that more savings mean lower financial cost in the Y-axis).
+This is not what we find.
+Figure \ref{choose_wrong}(d) is a binscatter that splits the X-axis in 100 percentiles bins of predicted take-up probability and for each bin averaged the financial cost treatment effects.
+Using all clouds we estimate a slope of zero in the relationship.
+Using the 80 right most points, we estimate a \textit{positive} relationship.
+A positive relation means that those more likely to demand commitment are also those that had smaller benefits from commitment.
+This result is similar to \cite{Walters}, who finds that students that select into more effective schools are the ones with smaller treatment effects.
+\cite{Walters} uses distance to school as an instrumental variable for choice, while we use randomization to choice vs no-choice groups as our empirical strategy.
+
+\section{The effect of promises} \label{promises}
+
+One finding of the paper is that a rather small fee of 14 pesos on average changes behavior substantially: on the one hand generates average savings in the order of 300 pesos when forced, but on the other dissuades take up  when client have choice.
+In this context one would want a commitment device that generates higher take up while at the same time providing incentives for paying fast and recovering the pawn.
+One way to go would be to decrease the already small fee to say 1\% or lower.
+We decided to instead experiment with a non-pecuniary penalty, in the form of the psychological cost of breaking a promise.
+As explained in Section \ref{Experiment} the promise contract involved making a salient promise to repay monthly as part of their pawn contract in words and in written, and receive the speech by the appraiser about the importance of keeping her promise of paying monthly.
+
+A substantial literature documents that people don't like to break their promises, and are willing to incur in monetary loses in trying to keep them.
+To our knowledge this result has been replicated several times in laboratory contexts but not in a field setting like ours.
+If breaking a promise is perceived as having a lower cost than paying the 2\% fee, we predict that more people will have demand for the promise-commitment contract.
+We indeed find that take up is higher.
+Is this higher take up associated with smaller treatment effects though?
+Or does the promise have enough commitment power?
+
+\subsection{The demand for promise-commitment contracts and their effects}
+
+\vspace{.2in}
+\noindent \textbf{Demand}.
+It turns out that the demand for monthly payment contracts with a personal promise to pay monthly ---but no pecuniary penalty for not doing so--- induces higher demand by a factor of three compared with fee-commitment contract studied above: 31\% of clients offered a choice between the status quo contract and the promise-commitment contract chose commitment.
+This means that that the pecuniary fee indeed limited demand for commitment.
+In passing this means also that clients are responsive to contract terms and seem to understand the conditions.
+Interestingly however, the set of people who demand the promise-commitment contract are different from those that demanded the fee-commitment one.
+While in both cases the economically vulnerable demand less, in the case of the promise-commitment those that we classify as present biased, those that report that they frequently fall into temptation buying, and those that ask for reminders of payment are \textit{less} likely to demand the promise-commitment contract.
+This suggests that those taking up the promise commitment are not the ones needing the commitment.
+The opposite is true for those who take up the fee-commitment contract (see Figure \ref{interactions_takeup} in the Appendix).
+
+\vspace{.2in}
+\noindent \textbf{Effect of choosing to promise}.
+Figure \ref{fc_pro5}(a) finds that assigning clients to the choice-promise condition has a zero effect on financial cost on average (circles).
+We see no difference even for the endogenous group that chose to promise (squares).
+This null effect happens not only on average, but also by percentiles (not shown in Figure).
+There is also no effect on pawn recovery on (first coefficient in Figure \ref{fc_pro5}(b)), even for those that themselves choose to promise (squares).
+And the null effect carries over if we use the definition of recovery in less than 120 days, or for the (endogenous) subgroups that paid a positive amount or at least a third of their loans.
+Finally, there is no effect on repeat pawning (Figure \ref{reincidence}).
+
+\vspace{.2in}
+\noindent \textbf{Effects of forcing to promise}.
+Giving choice of whether to promise or not has the advantage of making promising an active decision by the client.
+In most of the the experimental literature promising is voluntary.
+But it has the disadvantage that we cannot measure the causal effect of promising, since those that promise are a selected sample.
+To evaluate the causal effect of promising, we compare people allocated to the promise-forcing arm (were all clients were forced to make a promise) against those in the status quo contract arm.
+Figure \ref{fc_pro5} (c) and (d) show the results.
+It documents null average treatment effects for both financial cost and recovering the pawn.
+Also there is no effect on repeat pawning.
+
+\vspace{.2in}
+The evidence presented in this section contrasts sharply with the evidence in laboratory experiments where people choosing to promise has a large effect on behavior and were people keep their promises.
+While clients are more enthusiastic about the promise-commitment contract than the fee-commitment one in the sense of tripling take-up, the promise contract provides no commitment.
+
+%\vspace{.2in}
+%\noindent \textit{Size of ``mistakes''.} Although promises have very muted effects, there is some heterogeneity (see Figure \ref{heterogeneous_te_3}).
+This opens the space for choice mistakes.
+Figure \ref{choose_wrong} shows that indeed there are some mistakes, but these are smaller that for the fee-choice arm.
+When $z=0$, we calculate that about 60\% of clients in the promise-choice group chose contracts that induced \textit{higher} financial cost.
+In particular \hlgr{97\%} of those that chose the status-quo contract would have been better in the promise-commitment contract, while \hlgr{3\%} of those who chose the promise-commitment contract would have been better in the status-quo one.
+On average they spend \$250 pesos on extra financing cost.
+
+\section{Conclusion} \label{conclusion}
+
+In a pawnshop borrowing context, we studied whether forcing borrowers into frequent payment commitment contracts reduces their borrowing costs, compared to a contract that does not provide commitment to pay monthly.
+Even though we are charging them fees, their borrowing cost are actually reduced by 11\%, and they recover their pawn with 23\% higher likelihood.
+Moreover they themselves seem to like this contract, as they are 20\% more likely to come back and pawn again when they get it.
+That is, commitment matters and it seems beneficial.
+Examining treatment heterogeneity we find that almost all clients benefit from the commitment contract.
+
+However when given choice between the commitment and the status quo contract only 10\% choose the former one and thus forgo important benefits.
+This strongly suggests that ``private paternalism'', a policy that advances an individual's interests by restricting her freedom, is beneficial in our context.
+We provide a quantification of the size of unrealized benefits that arise when clients have choice.
+Methodologically, to our knowledge this is the first paper in economics that uses machine learning methods to estimate personalized counterfactual treatment gains and ask whether treatment take up is positively selected.
+
+Needless to say, pawnshop borrowing likely attracts particularly unsophisticated clients (millions of them).
+Choice may fare better in other contexts.
+Choice may also fare better with other contracts besides the fee-commitment one.
+We experimented with a ``softer'' commitment contract in the form of a personal promise, and found that although promise-commitment contracts do indeed elicit more interest they did not cause changes in behavior.
+
+We see three lines of further work that are of interest.
+First, investigate why the fee-commitment contract had such low demand in spite of its across-the-board benefits.
+In particular if naivete about self control problems, biased expectation about income shocks, or ambiguity aversion play a role.
+Second, whether other types of contracts ---for instance less coarse choice menus--- could induce larger demand and better performance.
+Third, whether individuals choosing to borrow from pawnshops are more present biased and naive than similar individuals borrowing from other types of lenders.
 
@@
 
+\clearpage
+\bibliographystyle{authordate1}
+%\bibliographystyle{amsalpha}
+%\bibliographystyle{AER}
+
+\bibliography{References}
+
+%\FloatBarrier
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\singlespacing
+
 \section{Tables}
@@
 \scriptsize{\input{./Tables/SS.tex}}
+\end{center}
+ \scriptsize
+This table presents balance tests for the administrative data (Panel A) and survey data (Panel B).
+Each column corresponds to an arm of the experiment: control (status quo contract), no choice with fee, no choice with promise, choice among both contracts where the commitment contract has fee, and choice among both contracts where the commitment contract involves only a promise.
+The last column show the p-value of an F-test of the hypothesis that the mean across arms for that variable is the same across the 5 arms.
+Randomization was done at the branch-day level.
+By design the observation are not exactly equal cross arms as we were more interested in detecting effects in the choice-fee arm and less so in the no-choice-promise.
+Loan amount is the peso amount given to the client; Monday is the fraction of loans given on a Monday; number of pledges is the number of loans given in each arm.
+That it is balanced shows that there was no detectable selection across arms when clients found out what was the contract.
+In Panel B: woman indicated whether the client is female, age of the client is measured in years; has pawned before is a dummy=1 if the client declares to have pawned before (although not necessarily with Lender $P$).
+The subjective probability of recovery was elicited a la Manski, from 0 to 100 what is the probability that you will recoup your pawn.
+High-school is a dummy that indicates if the client has completed high school.
+Finally, the response rate is the percentage of clients in the admin data for whom we have a baseline survey.
+%\textit{Do file: } \texttt{ss.do}
+\end{table}
+
+\pagebreak
+
+\begin{table}[H]
+\caption{Intermediate outcomes}
+\label{mechanisms}
+\begin{center}
+\scriptsize{\input{./Tables/mechanism.tex}}
+\end{center}
+ \scriptsize
+This table explores treatment effects in ``intermediate variables''.
+Each column represents a different dependent variable in an OLS regression.
+And each Panel represents a different treatment arm-control comparison.
+All regressions include fixed effects for branch, day of week fixed effects, number of pawns at the time of pawning this particular one, number of different treatment arms experienced before pawning this particular one.
+$R^2$ are not reported, they were less than 0.04 for all but the last column \hl{which had $R^2$'s close to 0.6}.
+The last row shows the mean of the dependent variable for the control group.
+Dependent variables are as follows: Column (1) measures the number of days elapsed from the pawning date to the first payment done.
+Column (2) records the number of payments done \hl{within 150 days} of the pawn.
+Column (3) is the average size of the payments for each client in pesos.
+Column (4) is self-reported cost to get to the branch plus the imputed loss of a whole day of salary (using the minimum wage in Mexico) multiplied by the number of visits to the branch.
+Column (5) measures the number of days it took to recover the pawn, conditional on recovering.
+The dependent variable in Column (6) is a dummy =1 if the client paid any positive amount within 150 days of the pawn.
+For Columns (7) and (8) the dependent variable it is the sum of total payments done within 150 days of the pawn divided by the size of the loan, but column (8) includes as regressors a dummy=1 if the client recovered her pawn, and its interaction with treatment.
+
+\textit{Do file: } \texttt{mechanisms.do}
+\end{table}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Figures}
+
+\begin{figure}[H]
+     \caption{Experiment description}
+    \label{exp_description}
+    \begin{center}
+    \begin{subfigure}{.50\textwidth}
+      \caption{Timeline of the experiment}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/timeline_suc_exp_extended.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.45\textwidth}
+    \caption{Experiment arms}
+       \centering
+      \includegraphics[width=\textwidth]{Figuras/exp_arms.PNG}
+    \end{subfigure}
+    \end{center}
+         \scriptsize Panel (a) displays in black arrows the period covered by our administrative data: from \hl{XXX} (\hl{XXX} days before the experiment began) to \hl{XXX}.
+The gray lines arrows correspond to the dates of implementation of the experiment.
+We finished the experiment earlier in branches 1 and 2 because we realized that we would have enough sample size with the remaining branches and save on operational costs.
+Panel (b) shows our 5 treatment arms: control (status quo contract), no choice with fee, no choice with promise, choice among both contracts where the commitment contract has a fee, and choice among both contracts where the commitment contract involves only a promise.
+Within each arm it displays the number of observations.
+And  for the choice groups it splits the sample size into those who chose the commitment contract (shaded blue triangle) and those that did not (un-shaded triangle).
+      \textit{Do file: }  \texttt{timeline\_suc\_exp.do}
+\end{figure}
+
+\begin{figure}[H]
+     \caption{Explanatory Material: Promise-Choice Days}
+    \label{ExplanatoryMaterial}
+    \begin{center}
+    \begin{subfigure}{0.8\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/MicaChoiceDonde.png}
+    \end{subfigure}
+    \end{center}
+    \scriptsize
+        xxx
+\end{figure}
+
+\begin{figure}[H]
+     \caption{Financial cost}
+    \label{fc_hist}
+    \begin{center}
+    \begin{subfigure}{.45\textwidth}
+      \caption{In pesos}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_fc.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.45\textwidth}
+    \caption{As a fraction of the loan}
+       \centering
+      \includegraphics[width=\textwidth]{Figuras/hist_fc_perc_loan.pdf}
+    \end{subfigure}
+    \end{center}
+         \scriptsize
+         Panel (a) presents a histogram of financial cost for the control group.
+Financial cost is defined as the sum of payments made by a client towards recovering her pawn + the cost of the pawned piece when she ends up losing it.
+In the paper we use different costs of losing the pawn: its value in gold, or the self reported subjective (e.g.
+jewelry may have sentimental value).
+This Figure uses the \hlgr{gold value}.
+We plot separately the financial cost for those who lose the pawn (blue) and those that recover it (transparent).
+Panel (b) is analogous but we normalized the financial cost dividing it by the loan size.
+%Given that the loan lasts close to 90 days, bringing payments to present value makes little difference.
+      %\footnotesize{ } \textit{Do file: }  \texttt{hist\_fc.do}
+\end{figure}
+
+\begin{figure}[H]
+    \caption{The effect of the fee-forcing treatment}
+    \label{fc_pro2}
+    \begin{center}
+    \begin{subfigure}{0.45\textwidth}
+        \caption{Financial cost}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/fc_te_pro_2.pdf}
+    \end{subfigure}
+        \begin{subfigure}{0.45\textwidth}
+        \caption{Financial cost (quantile reg)}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/fc_quantile_pro_2.pdf}
+    \end{subfigure}
+
+        \bigskip
+        \bigskip
+
+    \begin{subfigure}{0.45\textwidth}
+        \caption{Financial cost (HTE)}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_2.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.45\textwidth}
+        \caption{Lost pawn}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/def_te_pro_2.pdf}
+    \end{subfigure}
+
+    \end{center}
+        \scriptsize 
+        This figure shows the estimated treatment effect of ``forcing'' the frequent payment commitment contract using fees, compared to the status-quo (control) for  financial cost (Panel a), quantiles of financial cost (Panel b), and for an indicator of losing the pawn (Panel c).
+In Panel (a) each dot represents the estimated treatment effect for a different definition of financing cost, or for a different sub-population, and its 95\% confidence interval.
+From left to right, the first effect corresponds to using the gold value of the pawned piece in the definition of financial cost and discounting the payments to present value using a \hl{XXX} monthly rate; the second uses the subjective value of the pawn; the third is analogous to the second but adds transaction cost (transport+1 day's wage) per visit; the fourth conditions on the population that paid any positive amount towards recovery of their pawn; the fifth conditions on the sub-population \hl{of the treatment group} that paid a fee and \hl{compares these to all the control group}; the sixth conditions on the intersection of the previous two sub-populations.
+Panel (b) plots the effects on different quantiles of the distribution of financial cost (\hl{using the first definition}): 15th, 25th, 50th, 75th, 85th percentile.
+Panel (c) Measures the effect of treatment on the likelihood of losing their pawn.
+The first coefficient compares all the treatment group vs all the control; the second conditions on the population that paid any positive amount towards recovery of their pawn; the third conditions on having paid at least 30\% of the loan amount; the fourth conditions on the period covering the first cycle of the loan; the fifth on the period of the first cycle and paying any positive amount.
+The distribution plots the FC treatment effect for the interval $[\mu-2\sigma,\mu+2\sigma]$ to ignore the outliers.
+Panel (d) plots the distribution of the heterogeneous treatment effects on financial cost, estimated using \hl{Athey Wagner XXX}.
+% the effect on ``repeat purchase''.
+That is likelihood of doing an additional pawn (in treatment vs control) after having been subjected to treatment for at least 75 days.
+The second coefficient estimates the regression conditional on recovering the pawn \hl{in both treatment and control}, and the rightmost coefficient compares those above the median treatment effect in financial cost savings, \hl{versus all the control group.}
+      %\textit{Do file: }  \texttt{fc\_te.do, def\_te.do, fc\_quantilereg.do}
+\end{figure}
+
+\begin{figure}[H]
+        \caption{Effects on repeat purchasing}
+    \label{reincidence}
+    \begin{center}
+        \centering
+        \includegraphics[width=0.6\textwidth]{re_te.pdf}
+    \end{center}
+     \footnotesize \textit{Notes: } 
+      \footnotesize{ \textit{Do file: }  \texttt{re\_te.do}}
+\end{figure}
+
+\begin{figure}[H]
+    \caption{The effect choice between fee-commitment and status quo}
+    \label{fc_pro4}
+    \begin{center}
+    \begin{subfigure}{0.45\textwidth}
+        \caption{Financial cost}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/fc_te_pro_4.pdf}
+    \end{subfigure}
+        \begin{subfigure}{0.45\textwidth}
+        \caption{Financial Cost (quantile reg)}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/fc_quantile_pro_4.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.5\textwidth}
+
+        \bigskip
+        \bigskip
+
+        \caption{Lost Pawn}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/def_te_pro_4.pdf}
+    \end{subfigure}
+    \end{center}
+        \scriptsize
+        This figure is analogous to Figure \ref{fc_pro2}.
+It measures the effect of being given \textit{choice} between the frequent payment commitment contract and the status-quo contract versus being \textit{``forced''} into the status-quo contract (control).
+Again it focuses our two main outcomes: financial cost and an indicator for losing the pawn.
+However, it also presents differences in these two outcomes for those who chose the frequent payment commitment contract versus the whole control group (squares-NSQ), and also for those who chose the status quo contract versus the whole control group (triangles-SQ).
+Note that these two comparisons are not pure causal effects since people who chose the frequent payment commitment contract may be different from those that do not.
+That is: the squares and triangles combine selection and treatment effects.
+Finally, for comparison purposes, the blue diamonds display the effects of forcing them into the frequent payment commitment contract and are just transcribed from Figure \ref{fc_pro2} above.
+      \textit{Do file: }  \texttt{fc\_te\_choice\_dec.do, def\_te\_choice\_dec.do, fc\_quantilereg\_choice\_dec.do}
+\end{figure}
+
+\begin{figure}[H]
+    \caption{Choice of contracts and treatment effects}
+    \label{choose_wrong}
+    \begin{center}
+        \begin{subfigure}{0.45\textwidth}
+        \caption{Chose wrong}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/line_cw_fc_te_cf.pdf}
+
+    \end{subfigure}
+        \begin{subfigure}{0.45\textwidth}
+        \caption{By overconfidence/naivete}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/line_cw_fc_te_cf_OC_fee.pdf}
+
+    \bigskip
+
+    \end{subfigure}
+        \begin{subfigure}{0.45\textwidth}
+        \caption{\% better when forced to fee-commitment}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/line_better_forceall_fc_te_cf.pdf}
+
+    \end{subfigure}
+        \begin{subfigure}{0.45\textwidth}
+        \caption{\footnotesize{Effect of losing pawn vs predicted take-up}}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/takeuppr_def.pdf}
+    \end{subfigure}
+
+    \end{center}
+        \scriptsize
+        \hl{Es correcto esto que escribi isaac?} Panel (a) aims to show that subjects with higher  treatment effect in the no-choice arm (using \hl{Athey and Wagner (XXX) heterogeneous treatment effect estimator ISAAC puedes meter aqui el cite?}) are \textit{not} more likely to chose it if given choice.
+We proceed in three steps: first, within the choice arm, we estimate the probability of taking up the commitment contract ($\widehat{P(x_i)}$) using random forests, the baseline survey and pre-treatment administrative data.
+Second, we extrapolate these predictions to the no-choice and control arms using the $x_i$'s.
+Finally, We allocate subjects into 5 groups according to whether their predicted probability $\widehat{P(x_i)}$ is in \hl{[0,10],(10,20],(50,70],(30,}, and for each of these sub-populations separately we estimate the ATE of the no-choice treatment using regression equation \hl{XXX}.
+We find that take up of treatment is \textit{not} correlated with the benefit of treatment, if anything the correlation is negative.
+Panel (b) does almost the reverse procedure.
+We estimate what the treatment effect of the commitment contract \textit{would have been} for all subjects in the choice arm if they had been forced into it.
+To do this we estimate heterogeneous treatment effects as a function of our $x$'s in the no-choice arm, and extrapolate them to the choice arm.
+With these in hand, we calculate what fraction of subjects in the choice arm incurred in \hl{financial costs that are  $\geq Z$\% than if they had chosen the opposite contract of what they actually chose.} We define $Z$\% as a fraction of the loan in the X-axis.
+The left Y-axis measures the fraction of subjects, and \hl{the right Y-axis measures the amount of money ``left on the table''.}
+        \textit{Do file: }  \texttt{effect\_contr\_takeup.do, choose\_wrong\_quant\_wrong.do, choose\_wrong\_quant\_wrong\_decomposition.do}
+\end{figure}
+
+\begin{figure}[H]
+    \caption{The effect of choice between promise-commitment and status quo}
+    \label{fc_pro5}
+    \begin{center}
+    \begin{subfigure}{0.45\textwidth}
+        \caption{Financial cost -- Choice}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/fc_te_pro_5.pdf}
+    \end{subfigure}
+        %\begin{subfigure}{0.45\textwidth}
+        %\caption{Quantile regression}
+        %\centering
+        %\includegraphics[width=\textwidth]{Figuras/fc_quantile_pro_5.pdf}
+    %\end{subfigure}
+    \begin{subfigure}{0.45\textwidth}
+        \caption{Losing Pawn -- Choice}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/def_te_pro_5.pdf}
+    \end{subfigure}
+
+    \bigskip
+    \bigskip
+
+    \begin{subfigure}{0.45\textwidth}
+        \caption{Financial cost -- Promise-forcing}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/fc_te_pro_3.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.45\textwidth}
+        \caption{Losing Pawn -- Promise-forcing}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/def_te_pro_3.pdf}
+    \end{subfigure}
+    \end{center}
+             \footnotesize \textit{Notes: } 
+      \footnotesize{ } \textit{Do file: }  \texttt{fc\_te\_choice\_dec.do, def\_te\_choice\_dec.do, fc\_quantilereg\_choice\_dec.do}
+\end{figure}
+
+%\begin{figure}[H]
+%    \caption{The effect of the promise-forcing treatment}
+%    \label{fc_pro3}
+%    \begin{center}
+%        \begin{subfigure}{0.45\textwidth}
+%        \caption{Quantile regression}
+%        \centering
+%        \includegraphics[width=\textwidth]{Figuras/fc_quantile_pro_3.pdf}
+%    \end{subfigure}
+%    
+%    \end{center}
+%             \footnotesize \textit{Notes: } 
+%      \footnotesize{ } \textit{Do file: }  \texttt{fc\_te.do, def\_te.do, fc\_quantilereg.do}
+%\end{figure}
+
+\pagebreak
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% APPENDIX TABLES
+
+\setcounter{table}{0}
+\renewcommand{\thetable}{A\arabic{table}}
+
+\setcounter{figure}{0}
+\renewcommand{\thefigure}{A\arabic{figure}}
+
+\setcounter{section}{0}
+\setcounter{subsection}{0}
+\renewcommand\thesection{A\arabic{section}}
+\renewcommand\thesubsection{\thesection\arabic{subsection}}
+
+\appendix
+
+\section{APPENDIX}
+
+\subsection{Tables}
+
+\begin{table}[H]
+\caption{Balance response table}
+\label{balance_response}
+\begin{center}
+\scriptsize{\input{./Tables/balance_response.tex}}
+\end{center}
+ \scriptsize
+%\textit{Do file: } \texttt{balance\_response.do}
+\end{table}
+
+\begin{table}[H]
+    \caption{Out of sample measures of fit}
+    \label{Table_compliance}
+    \begin{subtable}{1\textwidth}
+      \centering
+        \caption{Take up}
+        \scriptsize{\input{./Tables/oos_pago_frec_vol.tex}}
+    \end{subtable}%
+
+    \bigskip
+    \begin{subtable}{1\textwidth}
+      \centering
+        \caption{Take up w/Fee}
+        \scriptsize{\input{./Tables/oos_pago_frec_vol_fee.tex}}
+    \end{subtable}
+
+      \bigskip
+    \begin{subtable}{1\textwidth}
+      \centering
+        \caption{Take up w/promise}
+        \scriptsize{\input{./Tables/oos_pago_frec_vol_promise.tex}}
+    \end{subtable}
+            \scriptsize
+           \\
+           \\
+           \\
+  \textit{Notes:}
+
+     \textit{Scripts: } \texttt{pred\_take\_up.do, pfv\_pred.R}
+\end{table}
+
+\begin{table}[H]
+\caption{Reincidence SS}
+\label{tab_reincidence}
+\begin{center}
+\scriptsize{\input{./Tables/tab_reincidence.tex}}
+\end{center}
+ \scriptsize
+%\textit{Do file: } \texttt{tab\_reincidence.do}
+\end{table}
+
+\begin{table}[H]
+\caption{Summary statistics (exit survey)}
+\label{SS_exit}
+\begin{center}
+\scriptsize{\input{./Tables/SS_exit.tex}}
 \end{center}
@@
 
+\begin{table}[H]
+\caption{Stochastic dominance of fee-forcing contract}
+\label{stochastic_dominance}
+\begin{center}
+\scriptsize{\input{./Tables/dominance.tex}}
+\end{center}
+ \footnotesize
+\textit{Notes:}
+
+\textit{Do file: } \texttt{stoch\_dominance.do}
+\end{table}
+
+\begin{table}[H]
+\caption{OC Regression}
+\label{oc_reg}
+\begin{center}
+\scriptsize{\input{./Tables/oc_reg.tex}}
+\end{center}
+ \footnotesize
+\textit{Notes:}
+
+\textit{Do file: } \texttt{oc.do}
+\end{table}
+
 \pagebreak
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Figures}
+\subsection{Figures}
 
 \begin{figure}[H]
-        \caption{Timeline of the experiment}
-    \label{micas}
+     \caption{Contract Terms Summary, and Promise Slip}
+    \label{PaperSlip}
     \begin{center}
+    \begin{subfigure}{0.75\textwidth}
         \centering
-        \includegraphics[width=0.70\textwidth]{Figuras/timeline_suc_exp.pdf}
+        \includegraphics[width=\textwidth]{Figuras/ContractDonde.png}
+    \end{subfigure}
+    \begin{subfigure}{0.4\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/PersonalPromise.png}
+    \end{subfigure}
     \end{center}
-     \footnotesize \textit{Notes: } 
-      \footnotesize{ \textit{Do file: }  \texttt{timeline\_suc\_exp.do}}
+    \scriptsize
+         xxx 
 \end{figure}
@@
 \begin{figure}[H]
-        \caption{Experiment arms}
-    \label{micas}
+        \caption{ECDF of Financial Cost}
+    \label{ecdf_fc}
     \begin{center}
         \centering
-        \includegraphics[width=0.70\textwidth]{Figuras/exp_arms.pdf}
+        \includegraphics[width=0.5\textwidth]{Figuras/cdf_fc_pro_2.pdf}
     \end{center}
     \footnotesize \textit{Notes: } 
-      \footnotesize{ }
+     \footnotesize{ \textit{Do file: }  \texttt{hist\_fc.do}}
 \end{figure}
@@
 \begin{figure}[H]
-        \caption{Booklet with product information}
-    \label{micas}
+    \caption{Behavior of those who lost pawn}
+    \label{proxy_naive}
     \begin{center}
+    \begin{subfigure}{0.40\textwidth}
+        \caption{Elapsed days to first payment}
         \centering
-        \includegraphics[width=\textwidth]{micas.pdf}
+        \includegraphics[width=\textwidth]{Figuras/hist_firstdays_default.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.40\textwidth}
+        \caption{Elapsed days to last payment}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_days_default.pdf}
+    \end{subfigure}
+        \begin{subfigure}{0.40\textwidth}
+        \caption{Payments as \% of loan}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_percpay_default.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.40\textwidth}
+        \caption{Number of payments}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_numpay_default.pdf}
+    \end{subfigure}
     \end{center}
-     \footnotesize \textit{Notes: } 
-      \footnotesize{ }
+        \scriptsize 
+        This figure describes behavior for the subsample of clients whose pawn was not recovered (\hl{in the control group}).
+Panel (a) shows days elapsed from the pawn to the first payment, while panel (b) displays the days elapsed to last payment.
+Some people pay after the day 105 when the grace period ends because the can ``restart'' the loan if they pay all interest owed.
+It amounts to starting a new loan \hl{with the same conditions} and same pawn.
+Panel (c) shows the fraction of the loan that they paid (even when they ended up losing the pawn).
+Panel (d) displays the number of times they went to the branch to pay.
+      \textit{Do file: }  \texttt{hist\_den\_default.do}
 \end{figure}
 
-\begin{figure}[H]
-    \caption{Treatment Effect}
-    \label{Treatment Effect}
-    \begin{center}
-    \begin{subfigure}{0.4\textwidth}
-        \caption{Paid loan}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/te_graph_des_c.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.4\textwidth}
-        \caption{Number of payments}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/te_graph_num_p.pdf}
-    \end{subfigure}
-     \begin{subfigure}{0.4\textwidth}
-      \caption{Percentage of payment}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/te_graph_sum_porcp_c.pdf}
-    \end{subfigure}
-      \begin{subfigure}{0.4\textwidth}
-      \caption{Days to un-pledge}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/te_graph_dias_al_desempenyo.pdf}
-    \end{subfigure}
-    \end{center}
-     \footnotesize \textit{Notes: } 
-      \footnotesize{ \textit{Do file: }  \texttt{te.do}}
-\end{figure}
+%\begin{figure}[H]
+%        \caption{Booklet with product information}
+%    \label{micas}
+%    \begin{center}
+%        \centering
+%        \includegraphics[width=\textwidth]{micas.pdf}
+%    \end{center}
+%     \footnotesize \textit{Notes: } 
+%      \footnotesize{ }
+%\end{figure}
 
-\begin{figure}[H]
-        \caption{Reincidence}
-    \label{micas}
-    \begin{center}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/te_graph_reincidence.pdf}
-    \end{center}
-     \footnotesize \textit{Notes: } 
-      \footnotesize{ }
-\end{figure}
-
-\begin{figure}[H]
-    \caption{Heterogeneous Treatment Effect}
-    \label{Treatment Effect}
-    \begin{center}
-    \begin{subfigure}{0.4\textwidth}
-        \caption{Paid loan}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/he_dist_des_c.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.4\textwidth}
-        \caption{Number of payments}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/he_dist_num_p.pdf}
-    \end{subfigure}
-     \begin{subfigure}{0.4\textwidth}
-      \caption{Percentage of payment}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/he_dist_sum_porcp_c.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.4\textwidth}
-      \caption{Days to un-pledge}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/he_dist_dias_al_desempenyo.pdf}
-    \end{subfigure}    
-    \end{center}
-     \footnotesize \textit{Notes: } 
-      \footnotesize{ \textit{Do file: }  \texttt{analyze\_grf.do}}
-\end{figure}
-
-\begin{figure}[H]
-    \caption{Heterogeneous Treatment Effect for Paid Loan Branches}
-    \label{Treatment Effect branch}
-    \begin{center}
-    \begin{subfigure}{0.3\textwidth}
-        \caption{x}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/he_dist_des_c_pro_2.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.3\textwidth}
-        \caption{x}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_des_c_pro_2.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.3\textwidth}
-        \caption{x}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/he_dist_des_c_pro_3.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.3\textwidth}
-        \caption{x}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_des_c_pro_3.pdf}
-    \end{subfigure}
-     \begin{subfigure}{0.3\textwidth}
-      \caption{x}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/he_dist_des_c_pro_4.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.3\textwidth}
-        \caption{x}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_des_c_pro_4.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.3\textwidth}
-      \caption{x}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/HE/he_dist_des_c_pro_5.pdf}
-    \end{subfigure} 
-    \begin{subfigure}{0.3\textwidth}
-        \caption{x}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_des_c_pro_5.pdf}
-    \end{subfigure}
-    \end{center}
-     \footnotesize \textit{Notes: } 
-      \footnotesize{ \textit{Do file: }  \texttt{analyze\_grf.do}}
-\end{figure}
+%\begin{figure}[H]
+%     \caption{Booklet with product information translated}
+%    \label{booklet_translate2}
+%    \begin{center}
+%    \begin{subfigure}{.9\textwidth}
+%        \centering
+%        \includegraphics[width=\textwidth]{Figuras/MP_F.pdf}
+%    \end{subfigure}
+    %\begin{subfigure}{0.55\textwidth}
+    %   \centering
+    %  \includegraphics[width=\textwidth]{Figuras/MP_2.pdf}
+    %\end{subfigure}
+%    \end{center}
+%\end{figure}
 
@@
     \begin{center}
+    \begin{subfigure}{.31\textwidth}
+    \caption{Control}
         \centering
-        \includegraphics[width=\textwidth]{hist_payments.pdf}
+        \includegraphics[width=\textwidth]{Figuras/hist_payments_pro_1.pdf}
+    \end{subfigure}
+    \begin{subfigure}{.31\textwidth}
+    \caption{Forcing - fee}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_payments_pro_2.pdf}
+    \end{subfigure}   
+     \begin{subfigure}{.31\textwidth}
+    \caption{Forcing - promise}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_payments_pro_3.pdf}
+    \end{subfigure}  
+     \begin{subfigure}{.31\textwidth}
+    \caption{Choice - fee}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_payments_pro_4.pdf}
+    \end{subfigure}  
+     \begin{subfigure}{.31\textwidth}
+    \caption{Choice - fee - SQ}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_payments_pro_6.pdf}
+    \end{subfigure}    
+     \begin{subfigure}{.31\textwidth}
+    \caption{Choice - fee - NSQ}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_payments_pro_7.pdf}
+    \end{subfigure}    
+     \begin{subfigure}{.31\textwidth}
+    \caption{Choice - promise}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_payments_pro_5.pdf}
+    \end{subfigure}  
+     \begin{subfigure}{.31\textwidth}
+    \caption{Choice - promise - SQ}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_payments_pro_8.pdf}
+    \end{subfigure}    
+     \begin{subfigure}{.31\textwidth}
+    \caption{Choice - promise - NSQ}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_payments_pro_9.pdf}    
+    \end{subfigure}        
+    \end{center}
+     \footnotesize \textit{Notes: } The x-axis shows the elapsed days between initial date and current movement.
+      \footnotesize{ \textit{Do file: }  \texttt{hist\_payments.do}}
+\end{figure}
+
+%\begin{figure}[H]
+%        \caption{Types of agents that incur in different FC}
+%    \label{components_fc}
+%    \begin{center}
+%        \centering
+%        \includegraphics[width=\textwidth]{Figuras/scatter_fc_pay.pdf}
+%    \end{center}
+%     \footnotesize \textit{Notes: } 
+%      \footnotesize{ \textit{Do file: }  \texttt{hist\_fc.do}}
+%\end{figure}
+
+\begin{figure}[H]
+        \caption{Percentage of payments}
+    \label{perc_payments}
+    \begin{center}
+    \begin{subfigure}{.31\textwidth}
+    \caption{Control}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_1.pdf}
+    \end{subfigure}
+    \begin{subfigure}{.31\textwidth}
+    \caption{Forcing - fee}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_2.pdf}
+    \end{subfigure}   
+     \begin{subfigure}{.31\textwidth}
+    \caption{Forcing - promise}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_3.pdf}
+    \end{subfigure}  
+     \begin{subfigure}{.31\textwidth}
+    \caption{Choice - fee}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_4.pdf}
+    \end{subfigure}  
+     \begin{subfigure}{.31\textwidth}
+    \caption{Choice - fee - SQ}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_6.pdf}
+    \end{subfigure}    
+     \begin{subfigure}{.31\textwidth}
+    \caption{Choice - fee - NSQ}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_7.pdf}
+    \end{subfigure}    
+     \begin{subfigure}{.31\textwidth}
+    \caption{Choice - promise}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_5.pdf}
+    \end{subfigure}  
+     \begin{subfigure}{.31\textwidth}
+    \caption{Choice - promise - SQ}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_8.pdf}
+    \end{subfigure}    
+     \begin{subfigure}{.31\textwidth}
+    \caption{Choice - promise - NSQ}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_9.pdf}    
+    \end{subfigure}        
     \end{center}
@@
 \begin{figure}[H]
-        \caption{Percentage of payments}
-    \label{HistPayments}
+        \caption{Percentage of payment conditional on positive payment and Losing Pawn}
+    \label{perc_payments_conditional}
     \begin{center}
+    \begin{subfigure}{.31\textwidth}
+    \caption{Control}
         \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_perc_payment.pdf}
-    \end{center}
-     \footnotesize \textit{Notes: } 
-      \footnotesize{ \textit{Do file: }  \texttt{hist\_perc\_payment.do}}
-\end{figure}
-
-\pagebreak
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% APPENDIX TABLES
-
-\section{APPENDIX}
-
-\subsection{Tables}
-
-\begin{landscape}
-\begin{table}[H]
-\caption{Treatment effects results}
-\label{te_table}
-\begin{center}
-\scriptsize{\input{./Tables/te.tex}}
-\end{center}
- \footnotesize
-\textit{Notes:}
-
-\textit{Do file: } \texttt{te.do}
-\end{table}
-
-\end{landscape}
-
-\subsection{Figures}
-
-\begin{figure}[H]
-    \caption{Robustness check effect of arms in reincidence}
-    \label{Evolution payment}
-    \begin{center}
-    \begin{subfigure}{0.49\textwidth}
-        \caption{ No Choice/Fee}
+        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_1.pdf}
+    \end{subfigure}
+    \begin{subfigure}{.31\textwidth}
+    \caption{Forcing - fee}
         \centering
-        \includegraphics[width=\textwidth]{Figuras/reincidence_robust_curve_p2.pdf}
+        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_2.pdf}
     \end{subfigure}   
-     \begin{subfigure}{0.49\textwidth}
-      \caption*{No Choice/No fee}
+     \begin{subfigure}{.31\textwidth}
+    \caption{Forcing - promise}
         \centering
-        \includegraphics[width=\textwidth]{Figuras/reincidence_robust_curve_p3.pdf}
+        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_3.pdf}
     \end{subfigure}  
-
-     \begin{subfigure}{0.49\textwidth}
-        \caption{Choice/Fee - SQ}
+     \begin{subfigure}{.31\textwidth}
+    \caption{Choice - fee}
         \centering
-        \includegraphics[width=\textwidth]{Figuras/reincidence_robust_curve_p4.pdf}
+        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_4.pdf}
     \end{subfigure}  
-     \begin{subfigure}{0.49\textwidth}
-      \caption*{Choice/Fee - NSQ}
+     \begin{subfigure}{.31\textwidth}
+    \caption{Choice - fee - SQ}
         \centering
-        \includegraphics[width=\textwidth]{Figuras/reincidence_robust_curve_p5.pdf}
+        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_6.pdf}
     \end{subfigure}    
-
-    \begin{subfigure}{0.49\textwidth}
-        \caption{Choice/No fee - SQ}
+     \begin{subfigure}{.31\textwidth}
+    \caption{Choice - fee - NSQ}
         \centering
-        \includegraphics[width=\textwidth]{Figuras/reincidence_robust_curve_p6.pdf}
+        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_7.pdf}
     \end{subfigure}    
-     \begin{subfigure}{0.49\textwidth}
-      \caption*{Choice/No fee - NSQ}
+     \begin{subfigure}{.31\textwidth}
+    \caption{Choice - promise}
         \centering
-        \includegraphics[width=\textwidth]{Figuras/reincidence_robust_curve_p7.pdf}
+        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_5.pdf}
+    \end{subfigure}  
+     \begin{subfigure}{.31\textwidth}
+    \caption{Choice - promise - SQ}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_8.pdf}
+    \end{subfigure}    
+     \begin{subfigure}{.31\textwidth}
+    \caption{Choice - promise - NSQ}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_9.pdf}    
     \end{subfigure}        
@@
      \footnotesize \textit{Notes: } 
-      \footnotesize{ \textit{Do file: }  \texttt{reincidence\_robust\_effect.do}}
+      \footnotesize{ \textit{Do file: }  \texttt{hist\_payments.do}}
 \end{figure}
 
-\pagebreak
+%\begin{figure}[H]
+%    \caption{Evolution of payment}
+%    \label{Evolution payment}
+%    \begin{center}
+%    \begin{subfigure}{0.49\textwidth}
+%        \caption{Paid loans}
+%        \centering
+%        \includegraphics[width=\textwidth]{Figuras/desempeno_evol.pdf}
+%    \end{subfigure}
+%     \begin{subfigure}{0.49\textwidth}
+%      \caption*{}
+%        \centering
+%        \includegraphics[width=\textwidth]{Figuras/desempeno_evol_choice.pdf}
+%    \end{subfigure}
+
+%     \begin{subfigure}{0.49\textwidth}
+%        \caption{Average percentage of paid loans}
+%        \centering
+%        \includegraphics[width=\textwidth]{Figuras/sum_porc_evol.pdf}
+%    \end{subfigure}
+%     \begin{subfigure}{0.49\textwidth}
+%      \caption*{}
+%        \centering
+%        \includegraphics[width=\textwidth]{Figuras/sum_porc_evol_choice.pdf}
+%    \end{subfigure}
+
+%   \begin{subfigure}{0.49\textwidth}
+%        \caption{Average percentage of paid loans | paid}
+%        \centering
+%        \includegraphics[width=\textwidth]{Figuras/sum_porc_cond_evol.pdf}
+%    \end{subfigure}
+%     \begin{subfigure}{0.49\textwidth}
+%      \caption*{}
+%        \centering
+%        \includegraphics[width=\textwidth]{Figuras/sum_porc_cond_evol_choice.pdf}
+%    \end{subfigure}
+%    \end{center}
+%     \footnotesize \textit{Notes: } 
+%      \footnotesize{ \textit{Do file: }  \texttt{evol\_payment.do}}
+%\end{figure}
 
 \begin{figure}[H]
-    \caption{Treatment Effect (conditional to positive payment)}
-    \label{Treatment Effect}
+    \caption{Heterogeneous Treatment Effect: Fee-forcing contract}
+    \label{HTE_fee_forcing}
     \begin{center}
     \begin{subfigure}{0.4\textwidth}
-        \caption{Paid loan}
+        \caption{Financial cost}
         \centering
-        \includegraphics[width=\textwidth]{Figuras/te_graph_des_c_robust.pdf}
+        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_2.pdf}
     \end{subfigure}
     \begin{subfigure}{0.4\textwidth}
-        \caption{Number of payments}
+        \caption*{}
         \centering
-        \includegraphics[width=\textwidth]{Figuras/te_graph_num_p_robust.pdf}
+        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_fc_admin_disc_pro_2.pdf}
+    \end{subfigure}
+
+    \begin{subfigure}{0.4\textwidth}
+        \caption{Losing Pawn}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_2.pdf}
     \end{subfigure}
     \begin{subfigure}{0.4\textwidth}
-      \caption{Percentage of payment}
+        \caption*{}
         \centering
-        \includegraphics[width=\textwidth]{Figuras/te_graph_sum_porcp_c_robust.pdf}
-    \end{subfigure}
-      \begin{subfigure}{0.4\textwidth}
-      \caption{Days to un-pledge}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/te_graph_dias_al_desempenyo_robust.pdf}
+        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_def_c_pro_2.pdf}
     \end{subfigure}
@@
      \footnotesize \textit{Notes: } 
-      \footnotesize{ \textit{Do file: }  \texttt{te.do}}
+      \footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}}
 \end{figure}
@@
 \begin{figure}[H]
-        \caption{Reincidence (conditional to positive payment)}
-    \label{micas}
+    \caption{Relationship between treatment effects}
+    \label{induced_to_pay_early}
     \begin{center}
+    \begin{subfigure}{0.45\textwidth}
+        \caption{\footnotesize{Induced to pay earlier vs Induced Lower FC}}
         \centering
-        \includegraphics[width=\textwidth]{Figuras/te_graph_reincidence_robust.pdf}
+        \includegraphics[width=\textwidth]{Figuras/binscatter_fc_days_pro_2.pdf}
+    \end{subfigure}
+        \begin{subfigure}{0.45\textwidth}
+        \caption{\footnotesize{Induced to pay earlier vs Induced Recovery}}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/binscatter_def_days_pro_2.pdf}
+    \end{subfigure}
     \end{center}
-     \footnotesize \textit{Notes: } 
-      \footnotesize{ }
+       \scriptsize 
+       This figure plots relationships between \textit{treatment effects}.
+Both Panels (a) an (b) have the same X-axis, which displays the estimated heterogeneous treatment effect on the outcome ``elapsed days of first payment'', that is how many days elapsed from the day the loan was awarded to the first payment the client made.
+The treatments effects were calculated using \hl{Athey and Wagner (Isaac, puedes agregar esto en cite format?}).
+We use command \hl{XXX} in $R$ which outputs an estimated treatment effect for each person in treatment and control.
+In Panel (a) the Y-axis is the \textit{treatment effect} on financial cost.
+In Panel (b) the Y-axis is the \textit{treatment effect} on losing their pawn.
+Panel (a) shows that those induced to pay earlier are also those that have larger savings in financial cost as a result of ``forcing'' the frequent payment commitment contract compared to the status-quo (control).
+Panel (b) shows that those induced to pay earlier are also those that have a larger increase in recovery.
+      \textit{Do file: }  \texttt{binscatter\_hte.do}
 \end{figure}
@@
 \begin{figure}[H]
-    \caption{Evolution of payment}
-    \label{Evolution payment}
+        \caption{FC as \% of loan - treatment effect}
+    \label{fc_perc}
     \begin{center}
-    \begin{subfigure}{0.49\textwidth}
-        \caption{Paid loans}
         \centering
-        \includegraphics[width=\textwidth]{Figuras/desempeno_evol.pdf}
+        \includegraphics[width=0.50\textwidth]{Figuras/fc_perc_te_allarms.pdf}
+    \end{center}
+    \footnotesize \textit{Notes: } 
+     \footnotesize{ \textit{Do file: }  \texttt{fc\_perc\_allarms.do}}
+\end{figure}
+
+\begin{figure}[H]
+        \caption{Financial cost effect with all fees}
+    \label{fc_allfee}
+    \begin{center}
+        \centering
+        \includegraphics[width=0.50\textwidth]{Figuras/fc_allfee_quantile_pro_2.pdf}
+    \end{center}
+    \footnotesize \textit{Notes: } 
+     \footnotesize{ \textit{Do file: }  \texttt{fc\_all\_fee.do}}
+\end{figure}
+
+\begin{figure}[H]
+        \caption{Overconfidence histogram}
+    \label{oc_hist}
+    \begin{center}
+        \centering
+        \includegraphics[width=0.50\textwidth]{Figuras/oc_hist.pdf}
+    \end{center}
+    \footnotesize \textit{Notes: } 
+     \footnotesize{ \textit{Do file: }  \texttt{oc.do}}
+\end{figure}
+
+\begin{figure}[H]
+        \caption{FC effect for different discount rates}
+    \label{oc_hist}
+    \begin{center}
+        \centering
+        \includegraphics[width=0.50\textwidth]{Figuras/discount_effect.pdf}
+    \end{center}
+    \footnotesize \textit{Notes: } 
+     \footnotesize{ \textit{Do file: }  \texttt{discounted\_noeffect.do}}
+\end{figure}
+
+\begin{figure}[H]
+    \caption{Predictors of commitment contract take-up}
+    \label{interactions_takeup}
+    \begin{center}
+    \begin{subfigure}{0.45\textwidth}
+        \caption{with Fee Arm}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/pago_frec_vol_fee_interactions_rf.pdf}
     \end{subfigure}
-     \begin{subfigure}{0.49\textwidth}
-      \caption*{}
+    \begin{subfigure}{0.45\textwidth}
+        \caption{with Promise Arm}
         \centering
-        \includegraphics[width=\textwidth]{Figuras/desempeno_evol_choice.pdf}
-    \end{subfigure}
-
-     \begin{subfigure}{0.49\textwidth}
-        \caption{Average percentage of paid loans}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/sum_porc_evol.pdf}
-    \end{subfigure}
-     \begin{subfigure}{0.49\textwidth}
-      \caption*{}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/sum_porc_evol_choice.pdf}
-    \end{subfigure}
-
-    \begin{subfigure}{0.49\textwidth}
-        \caption{Average percentage of paid loans (condition on paid loan)}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/sum_porc_cond_evol.pdf}
-    \end{subfigure}
-     \begin{subfigure}{0.49\textwidth}
-      \caption*{}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/sum_porc_cond_evol_choice.pdf}
+        \includegraphics[width=\textwidth]{Figuras/pago_frec_vol_promise_interactions_rf.pdf}
     \end{subfigure}
@@
      \footnotesize \textit{Notes: } 
-      \footnotesize{ \textit{Do file: }  \texttt{evol\_payment.do}}
+      \footnotesize{ \textit{Do file: }  \texttt{analyze\_fvp.do}}
 \end{figure}
 
+\begin{figure}[H]
+    \caption{Out of sample ROC curve}
+    \label{roc_curve}
+    \begin{center}
+    \begin{subfigure}{0.45\textwidth}
+        \caption{Take-up in Fee Arm}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/Boost/ROC_curve_outsample_pago_frec_vol_fee.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.45\textwidth}
+        \caption{Take-up in Promise Arm}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/Boost/ROC_curve_outsample_pago_frec_vol_promise.pdf}
+    \end{subfigure}
+    \end{center}
+     \footnotesize \textit{Notes: } 
+  \footnotesize{ \textit{Do file: }  \texttt{pred\_take\_up.do}}
+\end{figure}
+
+\begin{figure}[H]
+    \caption{Heterogeneous Treatment Effect - Choice/Fee}
+    \label{heterogeneous_te_4}
+    \begin{center}
+    \begin{subfigure}{0.4\textwidth}
+        \caption{Financial cost}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_4.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.4\textwidth}
+        \caption*{}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_fc_admin_disc_pro_4.pdf}
+    \end{subfigure}
+
+    \begin{subfigure}{0.4\textwidth}
+        \caption{Losing Pawn}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_4.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.4\textwidth}
+        \caption*{}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_def_c_pro_4.pdf}
+    \end{subfigure}
+    \end{center}
+     \footnotesize \textit{Notes: } The distribution plots the FC treatment effect for the interval $[\mu-2\sigma,\mu+2\sigma]$ to ignore the outliers.
+      \footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}}
+\end{figure}
+
+\begin{figure}[H]
+    \caption{Heterogeneous Treatment Effect - Choice/Promise}
+    \label{heterogeneous_te_5}
+    \begin{center}
+    \begin{subfigure}{0.4\textwidth}
+        \caption{Financial cost}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_5.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.4\textwidth}
+        \caption*{}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_fc_admin_disc_pro_5.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.4\textwidth}
+        \caption{Losing Pawn}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_5.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.4\textwidth}
+        \caption*{}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_def_c_pro_5.pdf}
+    \end{subfigure}
+    \end{center}
+     \footnotesize \textit{Notes: } 
+      \footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}}
+\end{figure}
+
+\begin{figure}[H]
+    \caption{Heterogeneous Treatment Effect:  No-Choice/Promise}
+    \label{heterogeneous_te_3}
+    \begin{center}
+    \begin{subfigure}{0.4\textwidth}
+        \caption{Financial cost}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_3.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.4\textwidth}
+        \caption*{}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_fc_admin_disc_pro_3.pdf}
+    \end{subfigure}
+
+    \begin{subfigure}{0.4\textwidth}
+        \caption{Losing Pawn}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_3.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.4\textwidth}
+        \caption*{}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_def_c_pro_3.pdf}
+    \end{subfigure}
+    \end{center}
+     \footnotesize \textit{Notes: } 
+      \footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}}
+\end{figure}
+
+\begin{figure}[H]
+        \caption{Causal tree for HTE}
+    \label{casual_tree}
+    \begin{center}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/crf_pro_2_fc_admin_disc.pdf}
+    \end{center}
+    \footnotesize \textit{Notes: } 
+     \footnotesize{ \textit{RScript: }  \texttt{grf.R}}
+\end{figure}
+
+%\begin{figure}[H]
+%    \caption{Heterogeneous Treatment Effect (FC survey) - All arms}
+%    \label{heterogeneous_te_fcsurvey_all}
+%    \begin{center}
+%    \begin{subfigure}{0.4\textwidth}
+%        \caption{Forcing/Fee}
+%        \centering
+%        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_survey_disc_pro_2.pdf}
+%    \end{subfigure}
+%    \begin{subfigure}{0.4\textwidth}
+%        \caption{Forcing/Promise}
+%        \centering
+%        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_survey_disc_pro_3.pdf}
+%    \end{subfigure}
+
+%    \begin{subfigure}{0.4\textwidth}
+%        \caption{Choice/Fee}
+%        \centering
+%        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_survey_disc_pro_4.pdf}
+%    \end{subfigure}
+%    \begin{subfigure}{0.4\textwidth}
+%        \caption{Choice/Promise}
+%        \centering
+%        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_survey_disc_pro_5.pdf}
+%    \end{subfigure}
+%    \end{center}
+%     \footnotesize \textit{Notes: } 
+%      \footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}}
+%\end{figure}
+
+%\begin{figure}[H]
+%    \caption{Exit Survey: reasons to pawn or not again with monthly payments}
+%    \label{reasons}
+%    \begin{center}
+%    \begin{subfigure}{0.5\textwidth}
+%        \caption{Pawn again because:}
+%        \centering
+%        \includegraphics[width=\textwidth]{Figuras/razones_si.pdf}
+%    \end{subfigure}
+%    \begin{subfigure}{0.5\textwidth}
+%        \caption{Not pawn because:}
+%        \centering
+%        \includegraphics[width=\textwidth]{Figuras/razones_no.pdf}
+%    \end{subfigure}
+%    \end{center}
+%     \footnotesize \textit{Notes: } 
+%      \footnotesize{ \textit{Do file: }  \texttt{ss.do}}
+%\end{figure}
+
+%\begin{figure}[H]
+%    \caption{Decomposition of the mistakes by `Overconfidence' for Promise Arms}
+%    \label{Promise_errors}
+%    \begin{center}
+%    \begin{subfigure}{0.6\textwidth}
+%        \caption{Promise}
+%        \centering
+%        \includegraphics[width=\textwidth]{Figuras/line_cw_fc_te_cf_OC_promise.pdf}
+%    \end{subfigure}
+%    \end{center}
+%     \footnotesize 
+%     \textit{Notes: }  Decomposition of the percentage of mistakes by overconfidence. 
+%       \textit{Do file: }  \texttt{choose\_wrong\_quant\_wrong\_decomposition.do}
+%\end{figure}
+
 \end{document}

### 2020-05-30 MATLAB/eu.m

@@ -1,0 +1,6 @@
+function [y] = eu(x, mu, sigma)
+%Expected utility of log-normal distribution with degree of RRA x
+y = exp((1-x).*mu+0.5*((1-x).*sigma).^2)./(1-x);
+
+end
+

### 2020-05-30 RScripts/fc_te_grf.R

@@ -21,27 +21,27 @@ set.seed(5289374)
   
   
   data_test <- data_in %>% 
-    select(-c(fc_admin, fee_arms, prenda, insample))
+    select(-c(fc_admin_disc, fee_arms, prenda, insample))
   data_test_tau <- data_in %>% 
-    select(-c(fc_admin, prenda, insample))
+    select(-c(fc_admin_disc, prenda, insample))
   
   ###################################################################  
   ###################################################################  
   
   
   # PREPARE VARIABLES
-  X <- select(data_train,-c(fc_admin, fee_arms, prenda, insample))
-  Y <- select(data_train,fc_admin)
+  X <- select(data_train,-c(fc_admin_disc, fee_arms, prenda, insample))
+  Y <- select(data_train,fc_admin_disc)
   W <- as.numeric(data_train$fee_arms == 1)
   
-  X_full <- select(data_in,-c(fc_admin, fee_arms, prenda, insample))
-  Y_full <- select(data_in,fc_admin)
+  X_full <- select(data_in,-c(fc_admin_disc, fee_arms, prenda, insample))
+  Y_full <- select(data_in,fc_admin_disc)
   W_full <- as.numeric(data_in$fee_arms == 1)
   
-  X_fee <- select(data_train_fee,-c(fc_admin, fee_arms, prenda, insample))
-  Y_fee <- as.numeric(data_train_fee$fc_admin)
-  X_nofee <- select(data_train_nofee,-c(fc_admin, fee_arms, prenda, insample))
-  Y_nofee <- as.numeric(data_train_nofee$fc_admin)
+  X_fee <- select(data_train_fee,-c(fc_admin_disc, fee_arms, prenda, insample))
+  Y_fee <- as.numeric(data_train_fee$fc_admin_disc)
+  X_nofee <- select(data_train_nofee,-c(fc_admin_disc, fee_arms, prenda, insample))
+  Y_nofee <- as.numeric(data_train_nofee$fc_admin_disc)
   
   ###################################################################  
   ###################################################################  

### 2020-05-30 RScripts/grf.R

@@ -1,19 +1,24 @@
 library(tidyverse)
 library(grf)
 library(ggplot2)
+library(DiagrammeR)
+library(DiagrammeRsvg)
+library(gdata)
 
 # SET WORKING DIRECTORY
 setwd('C:/Users/xps-seira/Dropbox/Apps/ShareLaTeX/Donde2019')
-#setwd("C:\\Users\\Ricardo\\Documents\\SEIRA\\donde2019")
 set.seed(5289374)
 
-heterogeneity_effect <- function(data_in,treatment_var,outcome_var) {
+source("./RScripts/best_tree.R")
+
+heterogeneity_effect <- function(data_in,treatment_var,outcome_var,writedata) {
   
 require("dplyr")
 data_frame <- data_in %>%
   filter(data_in[,treatment_var] == 1 | data_in[,treatment_var] == 0) %>%
   select(-c( pro_2, pro_3, pro_4, pro_5, pro_6, pro_7, pro_8, pro_9, fee, fecha_inicial,
-             def_c, fc_admin_disc, dias_primer_pago), treatment_var, outcome_var ) %>%
+             def_c, fc_admin_disc, fc_survey_disc, fc_admin, fc_survey, dias_primer_pago), 
+         treatment_var, outcome_var ) %>%
   drop_na()  
 
 
@@ -28,6 +33,11 @@ tau.forest = causal_forest(
   Y = data.matrix(Y), 
   W = W,
   honesty = TRUE)
+
+if (writedata == 0) {
+  # BEST TREE
+  best_tree_info <- find_best_tree(tau.forest, "causal")
+}
 
 # OVERLAP ASSUMPTION
 propensity.forest = regression_forest(X, W)
@@ -49,23 +59,116 @@ print(average_treatment_effect(tau.forest, target.sample = "treated"))
 #The (conditional) average treatment effect on the controls 
 print(average_treatment_effect(tau.forest, target.sample = "control"))
 
-
+#Write data
 data.out <- add_column(data_frame,tau_hat_oob$predictions,tau_hat_oob$variance.estimates, propensity_score)
 filename <- paste("_aux/grf_", treatment_var,"_",outcome_var, ".csv", sep="") 
-write_csv(data.out,filename)
+if (writedata == 1) {
+  write_csv(data.out,filename)
 }
-
+if (writedata == 0) {
[…]

### 2020-05-30 RScripts/pfv_pred.R

@@ -1,6 +1,7 @@
 library(tidyverse)
 library(grf)
 library(ggplot2)
+library(DMwR)
 
 # SET WORKING DIRECTORY
 setwd('C:/Users/xps-seira/Dropbox/Apps/ShareLaTeX/Donde2019')
@@ -37,12 +38,75 @@ rf_predict <- function(data_in,take.up) {
   write_csv(data.out,filename)
 }
 
-#####################################################
 
-# READ DATASET
+
+###################################################################################
+
 # Prenda level
 data_pfv_fee <- read_csv('./_aux/data_pfv_test_pago_frec_vol_fee.csv')
 
+# data_train <- data_pfv_fee %>% 
+#   filter(insample == 1) %>%
+#   as.data.frame() %>%
+#   mutate(pago_frec_vol_fee = as.factor(pago_frec_vol_fee)) 
+# data_test <- data_pfv_fee %>% 
+#   filter(insample == 0)  %>%
+#   as.data.frame() %>%
+#   mutate(pago_frec_vol_fee = as.factor(pago_frec_vol_fee)) 
+# 
+# ## Using SMOTE to create a more "balanced problem"
+# data.smoted <- SMOTE(pago_frec_vol_fee ~ .-nombrepignorante -prenda -insample,
+#                      data_train, k = 2, perc.over = 300, perc.under=200)
+# 
+# data_pfv_fee <- rbind(data.smoted, data_test)
+# write_csv(data_pfv_fee,"_aux/data_pfv_test_smoted_pago_frec_vol_fee.csv")
+
+#################################################################################
+
+# READ DATASET
+data_pfv_promise <- read_csv('./_aux/data_pfv_test_pago_frec_vol_promise.csv')
+
+# data_train <- data_pfv_promise %>% 
+#   filter(insample == 1) %>%
+#   as.data.frame() %>%
+#   mutate(pago_frec_vol_promise = as.factor(pago_frec_vol_promise)) 
+# data_test <- data_pfv_promise %>% 
+#   filter(insample == 0)  %>%
+#   as.data.frame() %>%
+#   mutate(pago_frec_vol_promise = as.factor(pago_frec_vol_promise)) 
+# 
+# ## Using SMOTE to create a more "balanced problem"
+# data.smoted <- SMOTE(pago_frec_vol_promise ~ .-nombrepignorante-prenda-insample,
+#                      data_train, k = 2, perc.over = 300, perc.under=200)
+# 
[…]

### 2020-05-30 RScripts/pfv_pred_hte.R

@@ -5,7 +5,7 @@ library(ggplot2)
 # SET WORKING DIRECTORY
 setwd('C:/Users/xps-seira/Dropbox/Apps/ShareLaTeX/Donde2019')
 set.seed(5289374)
-
+options(digits=18)
 
 rf_predict <- function(data_in,take.up,nme) {
   
@@ -50,3 +50,4 @@ for (arm in c("pro_2")) {
     }
   }
 }
+

### 2020-05-30 oldrepo/IsaacMeza-donde2019-54d6b0d43053/RScripts/grf.R

@@ -1,0 +1,80 @@
+library(tidyverse)
+library(grf)
+library(ggplot2)
+
+# SET WORKING DIRECTORY
+setwd('C:/Users/xps-seira/Dropbox/Apps/ShareLaTeX/Donde2019')
+#setwd("C:\\Users\\Ricardo\\Documents\\SEIRA\\donde2019")
+set.seed(5289374)
+
+heterogeneity_effect <- function(data_in,treatment_var,outcome_var) {
+  
+require("dplyr")
+data_frame <- data_in %>%
+  filter(data_in[,treatment_var] == 1 | data_in[,treatment_var] == 0) %>%
+  select(-c( pro_2, pro_3, pro_4, pro_5 , t_producto, NombrePignorante, fecha_inicial,
+             des_c, dias_al_desempenyo , 
+             ref_c  , num_p , sum_porcp_c, reincidence), treatment_var, outcome_var ) %>%
+  drop_na()  
+
+print(head(data_frame))
+
+# PREPARE VARIABLES
+X <- select(data_frame,-c(outcome_var, treatment_var))
+Y <- select(data_frame,outcome_var)
+W <- as.numeric(data_frame[,treatment_var] == 1)
+
+# ESTIMATE MODEL
+tau.forest = causal_forest(
+  X = model.matrix(~., data = X), 
+  Y = data.matrix(Y), 
+  W = W,
+  honesty = TRUE)
+
+# OVERLAP ASSUMPTION
+propensity.forest = regression_forest(X, W)
+propensity_score = predict(propensity.forest)$predictions
+hist(propensity_score, xlab = "propensity score")
+
+# Estimate treatment effects for the training data using out-of-bag prediction.
+tau_hat_oob = predict(tau.forest, estimate.variance = TRUE)
+hist(tau_hat_oob$predictions)
+
+# Estimate the conditional average treatment effect on the full sample (CATE).
+average_treatment_effect(tau.forest, target.sample = "all")
+
+# Estimate the conditional average treatment effect on the treated sample (CATT).
+# Here, we don't expect much difference between the CATE and the CATT, since
+# treatment assignment was randomized.
+average_treatment_effect(tau.forest, target.sample = "treated")
+
+
+data.out <- add_column(data_frame,tau_hat_oob$predictions,tau_hat_oob$variance.estimates, propensity_score)
[…]

### 2020-05-30 MATLAB/p3.m
Update repo structure

@@ -1,6 +1,0 @@
-function [p] = p3(y,m,parms)
-%Optimal policy at time period t = 3
-
-p = m.*((y >= m.*(1+parms.v)./parms.v));
-end
-

### 2020-05-30 RScripts/best_tree.R

@@ -1,227 +1,0 @@
-#' Function that takes in a list of samples, with the corresponding Y values, and calculates the r_loss, assuming a regression tree.
-#' If a leaf only has one sample, then we return the Y value squared. We choose this value because
-#' we don't want to return 0, which will encourage the tree to keep leaves with 1 sample, but we also
-#' don't want to return a huge value, which will force the tree to never have leaves with 1 sample, even if
-#' the sample is an outlier. But of course we could choose to return something else when there is only
-#' one sample in the leaf, if it makes more sense.
-#'
-#' @param Y The Y values
-#' @param samples The samples on which to calculate the r_loss.
-#' @param W.orig W values that indicate treatment; used for causal forest.
-#' @param W.hat Fitted W.hat for causal forest
-#' @param M.hat M.hat for causal forest
-#' @param Tau.hat Fitten tau values for causal forest
-#'
-#' @return The r_loss of the samples.
-#'
-#' @export
-r_loss <- function(Y, samples, W.orig = NULL, W.hat = NULL, M.hat = NULL, Tau.hat = NULL) {
-  size <- length(samples)
-  if (size == 1) {
-    return(Y[samples[1]]^2)
-  }
-  if (is.null(W.orig)) {
-    unscaled_spread <- sum((Y[samples] - mean(Y[samples]))^2)
-    output <- unscaled_spread * (size^2)/((size - 1)^2)
-  } else {
-    unscaled_spread <- sum((Y[samples] - M.hat[samples] - (W.orig[samples] - W.hat[samples])*mean(Tau.hat[samples]))^2)
-    output <- unscaled_spread * (size^2)/((size - 1)^2)
-  }
-  return(output)
-}
-
-
-
-#' Function that takes as input a tree, and calculates the r_loss of a specific node, specified by the index.
-#'
-#' @param Y The Y values of the data
-#' @param tree The tree on which to calculate r_loss
-#' @param index The index of the specific node whose r_loss we want
-#' @param cost This is the cost that we pay if we do not prune the tree.
-#' @param prune_info This is list that corresponds to nodes of the tree. Each element keeps track of the samples in the node and whether the node is a leaf in the pruned tree.
[…]

### 2020-05-30 RScripts/contrf_nochoice.R

@@ -1,54 +1,0 @@
-library(tidyverse)
-library(grf)
-library(ggplot2)
-
-# SET WORKING DIRECTORY
-setwd('C:/Users/xps-seira/Dropbox/Apps/ShareLaTeX/Donde2019')
-#setwd("C:\\Users\\Ricardo\\Documents\\SEIRA\\donde2019")
-set.seed(5289374)
-
-
-data_in <- read_csv('./_aux/heterogeneity_grf.csv')
-
-require("dplyr")
-data_frame <- data_in %>%
-  filter(data_in[,"pro_2"] == 1 | data_in[,"pro_2"] == 0) %>%
-  select(-c( pro_2, pro_3, pro_4, pro_5, pro_6, pro_7, pro_8, pro_9, fecha_inicial,
-             des_c, sum_p_c, fc_admin, fc_admin_disc, fc_survey,   num_p,  sum_porcp_c, mn_p_c, mn_pdisc_c,
-             dias_al_desempenyo, reincidence), pro_2, des_c ) %>%
-  drop_na()  
-  
-  
-# PREPARE VARIABLES
-X <- select(data_frame,-c(des_c, pro_2,NombrePignorante, prenda))
-Y <- select(data_frame,des_c)
-W <- as.numeric(data_frame[,"pro_2"] == 1)
-  
-# ESTIMATE MODEL
-tau.forest = causal_forest(
-  X = model.matrix(~., data = X), 
-  Y = data.matrix(Y), 
-  W = W,
-  honesty = TRUE)
-  
-
-
-# Estimate treatment effects for the test data using out-of-bag prediction.
-data_test <- data_in %>%
-  filter(data_in[,"pro_4"] == 1 | data_in[,"pro_4"] == 0 | data_in[,"pro_5"] == 1) %>%
-  select(-c( pro_2, pro_3, pro_4, pro_5, pro_6, pro_7, pro_8, pro_9, fecha_inicial,
-             des_c, sum_p_c, fc_admin, fc_admin_disc, fc_survey,   num_p,  sum_porcp_c, mn_p_c, mn_pdisc_c,
-             dias_al_desempenyo, reincidence, NombrePignorante)) %>%
-  drop_na()    
-
-X.test <- select(data_test,-c(prenda))
-
-tau_hat_oob = predict(tau.forest,  model.matrix(~., data = X.test), estimate.variance = TRUE)
-
-data.out <- cbind(data_test$prenda,tau_hat_oob$predictions,
[…]

### 2020-05-30 RScripts/grf.R

@@ -1,189 +1,0 @@
-library(tidyverse)
-library(grf)
-library(ggplot2)
-library(DiagrammeR)
-library(DiagrammeRsvg)
-library(gdata)
-
-# SET WORKING DIRECTORY
-setwd('C:/Users/xps-seira/Dropbox/Apps/ShareLaTeX/Donde2019')
-set.seed(5289374)
-
-source("./RScripts/best_tree.R")
-
-heterogeneity_effect <- function(data_in,treatment_var,outcome_var,writedata) {
-  
-require("dplyr")
-data_frame <- data_in %>%
-  filter(data_in[,treatment_var] == 1 | data_in[,treatment_var] == 0) %>%
-  select(-c( pro_2, pro_3, pro_4, pro_5, pro_6, pro_7, pro_8, pro_9, fee, fecha_inicial,
-             def_c, fc_admin_disc, fc_survey_disc, fc_admin, fc_survey, dias_primer_pago), 
-         treatment_var, outcome_var ) %>%
-  drop_na()  
-
-
-# PREPARE VARIABLES
-X <- select(data_frame,-c(outcome_var, treatment_var,NombrePignorante, prenda))
-Y <- select(data_frame,outcome_var)
-W <- as.numeric(data_frame[,treatment_var] == 1)
-
-# ESTIMATE MODEL
-tau.forest = causal_forest(
-  X = model.matrix(~., data = X), 
-  Y = data.matrix(Y), 
-  W = W,
-  honesty = TRUE)
-
-if (writedata == 0) {
-  # BEST TREE
-  best_tree_info <- find_best_tree(tau.forest, "causal")
-}
-
-# OVERLAP ASSUMPTION
-propensity.forest = regression_forest(X, W)
-propensity_score = predict(propensity.forest)$predictions
-hist(propensity_score, xlab = "propensity score")
-
-# Estimate treatment effects for the training data using out-of-bag prediction.
-tau_hat_oob = predict(tau.forest, estimate.variance = TRUE)
-hist(tau_hat_oob$predictions)
-
-# Estimate the conditional average treatment effect on the full sample (CATE).
-print(average_treatment_effect(tau.forest, target.sample = "all"))
-
-# Estimate the conditional average treatment effect on the treated sample (CATT).
-# Here, we don't expect much difference between the CATE and the CATT, since
[…]

### 2020-05-30 RScripts/pfv_pred.R

@@ -1,112 +1,0 @@
-library(tidyverse)
-library(grf)
-library(ggplot2)
-library(DMwR)
-
-# SET WORKING DIRECTORY
-setwd('C:/Users/xps-seira/Dropbox/Apps/ShareLaTeX/Donde2019')
-set.seed(5289374)
-
-
-rf_predict <- function(data_in,take.up) {
-  
-  require("dplyr")
-  data_train <- data_in %>% 
-    filter(insample == 1) 
-  
-  data_test <- data_in %>% 
-    select(-c(take.up, nombrepignorante, prenda, insample))
-  ###################################################################  
-  ###################################################################  
-  
-  
-  # PREPARE VARIABLES
-  X <- select(data_train,-c(take.up, nombrepignorante, prenda, insample))
-  W <- as.numeric(data_train[,take.up] == 1)
-  
-  ###################################################################  
-  ###################################################################  
-  
-  
-  # ESTIMATE MODEL
-  pred.forest = regression_forest(X, W)
-  rf_pred = predict(pred.forest,data_test)$predictions
-  hist(rf_pred, xlab = "predictions")
-  
-  data.out <- add_column(data_in, rf_pred)
-  filename <- paste("_aux/pred_",take.up,".csv", sep="") 
-  write_csv(data.out,filename)
-}
-
-
-
-###################################################################################
-
-# Prenda level
-data_pfv_fee <- read_csv('./_aux/data_pfv_test_pago_frec_vol_fee.csv')
-
-# data_train <- data_pfv_fee %>% 
-#   filter(insample == 1) %>%
-#   as.data.frame() %>%
-#   mutate(pago_frec_vol_fee = as.factor(pago_frec_vol_fee)) 
-# data_test <- data_pfv_fee %>% 
-#   filter(insample == 0)  %>%
-#   as.data.frame() %>%
-#   mutate(pago_frec_vol_fee = as.factor(pago_frec_vol_fee)) 
-# 
-# ## Using SMOTE to create a more "balanced problem"
-# data.smoted <- SMOTE(pago_frec_vol_fee ~ .-nombrepignorante -prenda -insample,
-#                      data_train, k = 2, perc.over = 300, perc.under=200)
-# 
-# data_pfv_fee <- rbind(data.smoted, data_test)
-# write_csv(data_pfv_fee,"_aux/data_pfv_test_smoted_pago_frec_vol_fee.csv")
[…]

### 2020-05-30 oldrepo/IsaacMeza-donde2019-54d6b0d43053/RScripts/pfv_pred.R

@@ -1,49 +1,0 @@
-library(tidyverse)
-library(grf)
-library(ggplot2)
-
-# SET WORKING DIRECTORY
-setwd('C:/Users/xps-seira/Dropbox/Apps/ShareLaTeX/Donde2019/oldrepo/IsaacMeza-donde2019-54d6b0d43053')
-set.seed(5289374)
-
-
-rf_predict <- function(data_in,take.up) {
-  
-  require("dplyr")
-  data_train <- data_in %>% 
-    filter(insample == 1) 
-
-  data_test <- data_in %>% 
-    select(-c(take.up, nombrepignorante, prenda, insample))
-###################################################################  
-###################################################################  
-
-    
-  # PREPARE VARIABLES
-  X <- select(data_train,-c(take.up, nombrepignorante, prenda, insample))
-  W <- as.numeric(data_train[,take.up] == 1)
-
-###################################################################  
-###################################################################  
-  
-  
-  # ESTINATE MODEL
-  pred.forest = regression_forest(X, W)
-  rf_pred = predict(pred.forest,data_test)$predictions
-  hist(rf_pred, xlab = "predictions")
-  
-  data.out <- add_column(data_in, rf_pred)
-  filename <- paste("_aux/pred_",take.up,".csv", sep="") 
-  write_csv(data.out,filename)
-}
-
-#####################################################
-
-# READ DATASET
-# Prenda level
-data <- read_csv('./_aux/data_pfv_test.csv')
-
-#RF Predictions
-rf_predict(data,"pago_frec_vol") 
-rf_predict(data,"pago_frec_vol_fee")
-rf_predict(data,"pago_frec_vol_promise") 

### 2020-05-30 main.tex
update repo structure

@@
 This table explores treatment effects in ``intermediate variables''.
-Each column represents a different dependent variable in an OLS regression.
-And each Panel represents a different treatment arm-control comparison.
+Each column represents a different dependent variable in an OLS regression, and each panel represents a different treatment arm-control comparison.
 All regressions include fixed effects for branch, day of week fixed effects, number of pawns at the time of pawning this particular one, number of different treatment arms experienced before pawning this particular one.
@@
 
-\textit{Do file: } \texttt{mechanisms.do}
+%\textit{Do file: } \texttt{mechanisms.do}
 \end{table}
@@
 And  for the choice groups it splits the sample size into those who chose the commitment contract (shaded blue triangle) and those that did not (un-shaded triangle).
-      \textit{Do file: }  \texttt{timeline\_suc\_exp.do}
+%\textit{Do file: }  \texttt{timeline\_suc\_exp.do}
 \end{figure}
@@
              \footnotesize \textit{Notes: } 
-      \footnotesize{ } \textit{Do file: }  \texttt{fc\_te\_choice\_dec.do, def\_te\_choice\_dec.do, fc\_quantilereg\_choice\_dec.do}
+      \footnotesize{ } \textit{Do file: }  \texttt{fc\_te\_choice\_dec.do, def\_te\_choice\_dec.do, fc\_te.do, def\_te.do }
 \end{figure}
@@
     \footnotesize \textit{Notes: } 
-     \footnotesize{ \textit{Do file: }  \texttt{hist\_fc.do}}
+     \footnotesize{ \textit{Do file: }  \texttt{ecdf\_fc.do}}
 \end{figure}

### 2020-05-30 oldrepo/IsaacMeza-donde2019-54d6b0d43053/Tables/te_robust.tex
update repo structure

% Table generated by Excel2LaTeX from sheet 'te_robust'
\begin{tabular}{rrrrrrrrrrr}
\toprule
      & \multicolumn{2}{c}{Un-pledge} & \multicolumn{2}{c}{Days to un-pledge} & \multicolumn{2}{c}{Number of payments} & \multicolumn{2}{c}{Percentage of payment} & \multicolumn{2}{c}{Refrendum} \\
\midrule
\midrule
      & \multicolumn{2}{c}{(1)} & \multicolumn{2}{c}{(2)} & \multicolumn{2}{c}{(3)} & \multicolumn{2}{c}{(4)} & \multicolumn{2}{c}{(5)} \\
\midrule
\midrule
\multicolumn{1}{l}{No choice/Fee} & \multicolumn{1}{c}{0.16***} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{-8.61***} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{1.03***} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{0.11***} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{-0.070**} & \multicolumn{1}{c}{} \\
      & \multicolumn{1}{c}{(0.026)} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{(2.83)} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{(0.25)} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{(0.022)} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{(0.029)} & \multicolumn{1}{c}{} \\
\multicolumn{1}{l}{No choice/Promise} & \multicolumn{1}{c}{0.012} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{-0.23} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{0.91***} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{0.013} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{0.049*} & \multicolumn{1}{c}{} \\
\multicolumn{1}{l}{} & \multicolumn{1}{c}{(0.025)} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{(3.31)} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{(0.27)} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{(0.023)} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{(0.027)} & \multicolumn{1}{c}{} \\
      &       & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} -0.0067} &       & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} 1.91} &       & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} 0.40} &       & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} -0.0040} &       & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} 0.015} \\
\multicolumn{1}{l}{Choice/Fee} & \multicolumn{1}{c}{0.015} & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} (0.024)} & \multicolumn{1}{c}{0.97} & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} (3.24)} & \multicolumn{1}{c}{0.97***} & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} (0.29)} & \multicolumn{1}{c}{0.0067} & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} (0.021)} & \multicolumn{1}{c}{0.029} & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} (0.026)} \\
\cmidrule{3-3}\cmidrule{5-5}\cmidrule{7-7}\cmidrule{9-9}\cmidrule{11-11}\multicolumn{1}{l}{} & \multicolumn{1}{c}{(0.023)} & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} 0.21***} & \multicolumn{1}{c}{(3.06)} & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} -5.44} & \multicolumn{1}{c}{(0.35)} & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} 6.32***} & \multicolumn{1}{c}{(0.020)} & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} 0.10***} & \multicolumn{1}{c}{(0.025)} & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} 0.17***} \\
      &       & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} (0.037)} &       & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} (4.29)} &       & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} (1.60)} &       & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} (0.027)} &       & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} (0.042)} \\
      &       & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} 0.025} &       & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} -1.18} &       & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} -0.11} &       & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} 0.0096} &       & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} -0.032} \\
\multicolumn{1}{l}{Choice/Promise} & \multicolumn{1}{c}{0.010} & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} (0.028)} & \multicolumn{1}{c}{-2.87} & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} (3.83)} & \multicolumn{1}{c}{0.42} & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} (0.32)} & \multicolumn{1}{c}{0.0041} & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} (0.025)} & \multicolumn{1}{c}{-0.0013} & \multicolumn{1}{c}{\cellcolor[rgb]{ .949,  .949,  .949} (0.033)} \\
\cmidrule{3-3}\cmidrule{5-5}\cmidrule{7-7}\cmidrule{9-9}\cmidrule{11-11}\multicolumn{1}{l}{} & \multicolumn{1}{c}{(0.024)} & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} -0.023} & \multicolumn{1}{c}{(3.35)} & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} -6.93*} & \multicolumn{1}{c}{(0.26)} & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} 1.65***} & \multicolumn{1}{c}{(0.022)} & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} -0.0085} & \multicolumn{1}{c}{(0.028)} & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} 0.068**} \\
      & \multicolumn{1}{c}{} & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} (0.029)} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} (3.75)} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} (0.43)} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} (0.027)} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{\cellcolor[rgb]{ .816,  .808,  .808} (0.034)} \\
      &       &       &       &       &       &       &       &       &       &  \\
\multicolumn{1}{l}{Constant} & \multicolumn{1}{c}{0.70***} & \multicolumn{1}{c}{0.68***} & \multicolumn{1}{c}{82.5***} & \multicolumn{1}{c}{83.5***} & \multicolumn{1}{c}{2.59***} & \multicolumn{1}{c}{2.02***} & \multicolumn{1}{c}{1.04***} & \multicolumn{1}{c}{1.03***} & \multicolumn{1}{c}{0.38***} & \multicolumn{1}{c}{0.36***} \\
\multicolumn{1}{l}{} & \multicolumn{1}{c}{(0.033)} & \multicolumn{1}{c}{(0.033)} & \multicolumn{1}{c}{(3.81)} & \multicolumn{1}{c}{(3.82)} & \multicolumn{1}{c}{(0.41)} & \multicolumn{1}{c}{(0.44)} & \multicolumn{1}{c}{(0.026)} & \multicolumn{1}{c}{(0.026)} & \multicolumn{1}{c}{(0.035)} & \multicolumn{1}{c}{(0.035)} \\
      &       &       &       &       &       &       &       &       &       &  \\
\midrule
\multicolumn{1}{l}{Observations} & \multicolumn{1}{c}{9983} & \multicolumn{1}{c}{9983} & \multicolumn{1}{c}{6118} & \multicolumn{1}{c}{6118} & \multicolumn{1}{c}{9983} & \multicolumn{1}{c}{9983} & \multicolumn{1}{c}{9983} & \multicolumn{1}{c}{9983} & \multicolumn{1}{c}{9983} & \multicolumn{1}{c}{9983} \\
\multicolumn{1}{l}{R-squared} & \multicolumn{1}{c}{0.029} & \multicolumn{1}{c}{0.034} & \multicolumn{1}{c}{0.024} & \multicolumn{1}{c}{0.025} & \multicolumn{1}{c}{0.007} & \multicolumn{1}{c}{0.020} & \multicolumn{1}{c}{0.031} & \multicolumn{1}{c}{0.033} & \multicolumn{1}{c}{0.033} & \multicolumn{1}{c}{0.036} \\
\multicolumn{1}{l}{Dependent Var Mean} & \multicolumn{1}{c}{0.61} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{91.0} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{3.47} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{1.01} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{0.49} & \multicolumn{1}{c}{} \\
\multicolumn{1}{l}{Branch FE} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} \\
\multicolumn{1}{l}{Dow FE} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} & \multicolumn{1}{c}{YES} \\
\midrule
\midrule
\rowcolor[rgb]{ .929,  .929,  .929} Status-quo & \cellcolor[rgb]{ 1,  1,  1}  & \cellcolor[rgb]{ 1,  1,  1}  & \cellcolor[rgb]{ 1,  1,  1}  & \cellcolor[rgb]{ 1,  1,  1}  & \cellcolor[rgb]{ 1,  1,  1}  & \cellcolor[rgb]{ 1,  1,  1}  & \cellcolor[rgb]{ 1,  1,  1}  & \cellcolor[rgb]{ 1,  1,  1}  & \cellcolor[rgb]{ 1,  1,  1}  & \cellcolor[rgb]{ 1,  1,  1}  \\
\rowcolor[rgb]{ .859,  .859,  .859} Non status-quo & \cellcolor[rgb]{ 1,  1,  1}  & \cellcolor[rgb]{ 1,  1,  1}  & \cellcolor[rgb]{ 1,  1,  1}  & \cellcolor[rgb]{ 1,  1,  1}  & \cellcolor[rgb]{ 1,  1,  1}  & \cellcolor[rgb]{ 1,  1,  1}  & \cellcolor[rgb]{ 1,  1,  1}  & \cellcolor[rgb]{ 1,  1,  1}  & \cellcolor[rgb]{ 1,  1,  1}  & \cellcolor[rgb]{ 1,  1,  1}  \\
\end{tabular}%

### 2020-05-30 presentations/beamer_pola.tex
update repo structure

--- 2020-01-20 presentations/beamer_applied_lunch.tex
@@
 
-\input{preamble_beamer.tex}
+\input{presentations/preamble_beamer.tex}
 
@@
 Isaac Meza\inst{1}\and Joyce Sadka\inst{2}  \and Enrique Seira\inst{2}}
+
 \institute{ \inst{1} University of California, Berkeley \and
@@
 
-\date{Oct 4, 2019\\\;\;\textsc{Applied Lunch}\\\;\;\textbf{\alert{VERY PRELIMINARY!} }}
+\date{Oct, 2019\\\;\;\\\;\;}
 
@@
 \begin{itemize}
-\vfill \item True story:
+\item How the collaboration started
     \begin{itemize}
-        \item A large Mexican pawn shop (PS) contacted us worried that their default was too high...
-        \item ...conjecturing it had to do with contract without frequent payments.
+        \item We were contacted by the organization about their contract.
+        \item Conjectured that frequent payments would lead to higher recovery.
+
     \end{itemize}
     \pause
-\vfill \item Their contract:
+\vfill \item The standard contract:
     \begin{itemize}
@@
         \item 7\% Monthly interest in outstanding debt.
-        \item 3 month term. You could pay principal+interest anytime with no penalty and recover your item. 
-        \item Only 33\% paid before day 85th.
+        \item \textbf{3 month term}. You could pay principal+interest anytime with no penalty and recover your item. 
         \item if in 90 (+15 days grace) you did not do this, you lose your item.
+        \item A bit more than 1/3 lost their pawn.
+        \item Only 33\% paid before day 85th in our data/
     \end{itemize}
     \pause
-\vfill \item Does forcing them to \textbf{pay monthly} increase payment (decrease default)?
+    \end{itemize}
+
+\vfill
+\end{frame}
+
+\begin{frame}{2 Questions}
+        \begin{enumerate}
+ \item Does forcing clients to \textbf{pay monthly} increase payment (decrease default)?
     \begin{itemize}
-        \item PS prefers clients recover their item (non-profit mandate).
-        \item Higher frequency has costs: $\uparrow$ transaction costs, $\downarrow$  welfare (with neo-classical consumers).
+        \item \textbf{Higher frequency has costs}: $\uparrow$ transaction costs, $\downarrow$  welfare (with neo-classical consumers).
         \item But may help present biased consumers. 
     \end{itemize}
+
     \vfill
@@
     \item \textbf{Is there demand for commitment?}
+        \begin{itemize}
+            \item Would clients demand it if given a choice between monthly payments vs at anytime in 3 months?
+            \item Who demands it?
+            \item Neoclassical consumers would \textbf{not} tie their hands for free.
         \end{itemize}
-\vfill
-\end{frame}
-
-\begin{frame}{Why could frequency decrease default?}
-    \begin{itemize}
-        \vfill \item Behavioral:
-        \begin{itemize}
-            \item Commitment device not to spend the money (for present biased consumers).
-            \item Creates a habit for saving (or paying) / forces to make a plan (for inattentive consumers).
-            \item Sunk cost fallacy (having already paid some).
-        \end{itemize}
-    \end{itemize}
-
-    \begin{itemize}
-        \vfill \item Neoclassical:
-        \begin{itemize}    
-        \item Increases consumer trust with branch personnel?
-        \item Pecuniary/psychological cost from not paying?
-        \item Less ``distance to goal''.
-         \item Borrows from other lenders to pay $\rightarrow$ more monitoring.
-        \end{itemize}
-        \vfill
-    \item Neoclassical consumers would \textbf{not} tie their hands for free.
-        \begin{itemize}
-            \item Demand for commitment would signal the presence of present biased consumers.
-        \end{itemize}
-    \end{itemize}   
-    \vfill
+\end{enumerate}
 \end{frame}
@@
     \vfill 
-    \item Two types of punishment in different arms:
+    \item Tried with 2 types of punishment:
     \begin{itemize}
@@
 \end{itemize}
-
-\end{frame}
-
-\begin{frame}{Literature in Microfinance}
-
-        \begin{itemize}
-        \vfill \item Field and Pande ``\textit{Repayment Frequency and Default in Microfinance}'' JEEA 2008.
-            \begin{itemize}
-            \item Randomized 100 MFI groups to weekly vs monthly payment.
-            \item Found no effect of frequency (default in about 1\% for all).
-            \end{itemize}
-            \pause
-        \vfill \item Field et al ``Repayment flexibility can reduce financial stress'' PLOS 2012
-            \begin{itemize}
-            \item Randomized ~100 MFI groups to weekly vs monthly payment.
-            \item Found those in weekly payment  50\% more likely to report feeling anxious.
-            \end{itemize}
-            \pause
-        \vfill \item Field, Pande, Papp, Rigol ``Does the classic microfinance model discourage entrepreneurship among the poor?'' AER 2013
-        \pause
-        \vfill \item Ahsarf et al ``Tying odysseus to the mast'' QJE 2006.
-               \begin{itemize}
-                \item Offered savings where they could not withdraw for a given time /goal (~700 people, 28\% accepted).
-                \item Found present biased women  are more 15pp likely to take up.
-                \item 80\% increase in savings 1yr later (ITT).
-             \end{itemize}
-             \vfill
-
-    \end{itemize}
-
 \end{frame}
@@
         \includegraphics[width=0.70\textwidth]{Figuras/exp_arms.PNG}
+    \end{center}
+\end{frame}
+
+\begin{frame}{Explanation in ``choice'' days}
+    \begin{center}
+        \includegraphics[width=\textwidth]{Figuras/micas.pdf}
     \end{center}
@@
 
+\begin{frame}{Summary Stats}
+    \begin{table}
+        \begin{center}
+        \tiny{\input{./Tables/SS.tex}}
+        \end{center}
+    \end{table}
+\end{frame}
+
 \begin{frame}{SS Histograms}
@@
     \begin{center}
-     \begin{subfigure}{0.45\textwidth}
+     \begin{subfigure}{0.40\textwidth}
         \caption{In the last six months, did you need money to pay...?}
@@
     \end{subfigure}
-     \begin{subfigure}{0.45\textwidth}
+     \begin{subfigure}{0.5\textwidth}
         \caption{Cost and Time to arrive to pawn shop}
@@
 
-\begin{frame}{Summary Stats}
-    \begin{table}
-        \begin{center}
-        \tiny{\input{./Tables/SS.tex}}
-        \end{center}
-    \end{table}
-\end{frame}
-
 \section{Results on Payments and Recovery}
-
-\begin{frame}{When do borrowers pay?}
-    \begin{center}
-        \includegraphics[width=\textwidth]{Figuras/hist_payments.pdf}
-    \end{center}
-\end{frame}
 
@@
         \includegraphics[width=.70\textwidth]{Figuras/te_graph_des_c.pdf}
-    \end{center}
-\end{frame}
-
-\begin{frame}{Number of Payments}
-    \begin{center}
-        \includegraphics[width=.70\textwidth]{Figuras/te_graph_num_p.pdf}
     \end{center}
@@
     \begin{center}
-        \includegraphics[width=.80\textwidth]{Figuras/he_dist_des_c_pro_2.pdf}
+        \includegraphics[width=.80\textwidth]{Figuras/he_dist_des_c.pdf}
     \end{center}
@@
 
-\begin{frame}{Some determinants of TE - The nature of heterogeneity}
+\begin{frame}{A proxy for financial cost to client}
+
+Financial cost is defined as: sum of payments + cost of piece if not recovered
+
     \begin{center}
-        \includegraphics[width=.9\textwidth]{Figuras/HE/he_int_des_c_pro_2.pdf}
+        \includegraphics[width=.7\textwidth]{Figuras/hist_fc.pdf}
+    \end{center}
+\end{frame}
+
+\begin{frame}{Effect of Frequency on Financial Cost}
+
+\begin{itemize}
+    \item Financial cost decreases by 350 pesos, from a mean of 3,200.
+\end{itemize}
+\vspace{.2in}
+\vfill
+    \begin{center}
+        \includegraphics[width=.9\textwidth]{Figuras/FC_table.png}
     \end{center}
@@
 \section{Results on Demand for Commitment}
+
+\begin{frame}{Fit: Machine learning models}
+\begin{itemize}
+    \item 87\% accuracy: we can predict take up well.
+    \vfill
+\end{itemize}
+    \begin{center}
+    \input{./Tables/oos_pago_frec_vol_fee.tex}
+    \end{center}
+\end{frame}
 
@@
 
-\begin{frame}{Those taking up are not those with highest TE}
+\begin{frame}{``Benefit'' positively correlated with predicted take-up}
+
+\begin{itemize}
+    \item Estimate take-up \alert{in Choice fee group} as a function of X's: $f(\beta,X)$.
+    \item Predict take up using $f(\beta,X)$ in \alert{No-choice group}.
+    \item relate predicted take up to effect they really had in \alert{No-choice group}.
+\end{itemize}
+
+\begin{figure}[H]
     \begin{center}
-        \includegraphics[width=.70\textwidth]{Figuras/takeup_he_pro_2_fee.pdf}
+     \begin{subfigure}{0.45\textwidth}
+        \caption{Recovery vs predicted take-up}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/takeup_he_pro_2_pago_frec_vol_fee_des_c.pdf}
+    \end{subfigure}
+     \begin{subfigure}{0.45\textwidth}
+        \caption{FC vs predicted take-up}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/takeup_he_pro_2_pago_frec_vol_fee_fc_survey.pdf}
+    \end{subfigure}
     \end{center}
+    \end{figure}
+
 \end{frame}
@@
 
-\begin{frame}{Next steps}
+\begin{frame}{Potential projects and remaining questions}
 
+\begin{enumerate}
+
+    \item Current project:
+    \begin{enumerate}
+        \item Get historical data to see results by different types of people.
+        \item Replicate experiment in 2 or 3 branches, with improved design.
         \begin{itemize}
-    \item Can a simple neoclassical model explain quantitatively the results?
+            \item Ask preference to all, then randomize.
+            \item Better satisfaction survey.
+            \item Measure preferences better at baseline, and expectations.
+            \item Cross check with bureau and savings.
+            \item Measure mistakes in take up
+        \end{itemize}
+    \end{enumerate}
+
     \vfill
-    \item Estimate a model and talk about welfare?
-    \vfill
-    \item What about naive present-biased consumers? Can we separate them?
-    \vfill
-    \item Does promise commitment work for some people?
-    \vfill
-    \item Does frequent payment cause lack of payment of basic services or other loans?
+    \item Impact of different collateral requirements:
+    \begin{itemize}
+        \item Pilot 65\% and 75\% collateral and measure take up, recovery and profits
     \end{itemize}
 
+    \vfill
+    \item Reporting to Credit Bureau (pilot):
+    \begin{itemize}
+        \item As a way to impose discipline (ex-ante vs ex-post)
+        \item It can be voluntary
+    \end{itemize}
+
+    \vfill
+    \item Optimal auctions to sell the goods in a webpage.
+
+    \vfill
+    \item Tracking by cellphone to screen for bank.
+
+\end{enumerate}
 \end{frame}
@@
 
-\begin{frame}{Explanation in ``choice'' days}
+\begin{frame}{When do borrowers pay?}
     \begin{center}
-        \includegraphics[width=\textwidth]{Figuras/micas.pdf}
+        \includegraphics[width=\textwidth]{Figuras/hist_payments.pdf}
     \end{center}
@@
         \includegraphics[width=.9\textwidth]{Figuras/hist_perc_payment.pdf}
+    \end{center}
+\end{frame}
+
+\begin{frame}{Number of Payments}
+    \begin{center}
+        \includegraphics[width=.70\textwidth]{Figuras/te_graph_num_p.pdf}
+    \end{center}
+\end{frame}
+
+\begin{frame}{Some determinants of TE - The nature of heterogeneity}
+    \begin{center}
+        \includegraphics[width=.9\textwidth]{Figuras/he_int_vertical_des_c_pro_2.pdf}
     \end{center}
@@
         \includegraphics[width=.90\textwidth]{Figuras/pago_frec_vol_promise_interactions_rf.pdf}
-    \end{center}
-\end{frame}
-
-\begin{frame}{ML fit}
-    \begin{center}
-    \scriptsize
-    \input{./Tables/oos_pago_frec_vol_fee.tex}
     \end{center}

### 2020-05-30 MATLAB/V1.m

@@ -1,0 +1,34 @@
+function [V, pp, d] = V1(y,m,parms)
+% Value function at time period t=1
+beta_belief = parms.beta_belief; delta = parms.delta; 
+val = parms.v; r =parms.r; mu = parms.mu; sigma = parms.sigma;
+
+% Sample to compute V2:
+y_prime = exp(mu + sigma.*randn(parms.rep,1));
+
+% Value function:
+VV = @(p) log(y-p) + mean(V2(y_prime,(1+r)*(m-p),parms));
+
+mn = min(m,y); mx = max(mn); grid = linspace(0,mx,parms.gridsize); 
+F = zeros(length(y),parms.gridsize);
+for i = 1:parms.gridsize
+    % Computationally expensive
+    F(:,i) = VV(grid(i));
+end
+
+% Optimal Interior Point Value
+[V,ind] = max(F,[],2);
+% Optimal int point policy
+pp = grid(ind)';
+
+% Optimum for paying debt at this time period if possible
+opt = -Inf*ones(length(y),1);
+opt(m<=y) = log(1+val) + log(y-m) + ...
+    (beta_belief*delta + beta_belief*delta^2)*(log(1+val) + mu);
+
+%% Optimum values
+ind_change = V<opt;
+V(ind_change) = opt(ind_change); pp(ind_change) = m;
+% Paid loan
+d = (pp==m);
+end

### 2020-05-30 MATLAB/simul.m

@@ -1,0 +1,71 @@
+%% Parameter structure
+%
+clear all
+clc
+parms.sigma = 0.4;
+parms.delta=0.8;
+parms.mu = 7;
+parms.r = .2;
+parms.beta_belief=0.9;
+parms.beta=0.8;
+parms.rep = 1000;
+parms.gridsize = 1200;
+parms.simul = 500;
+parms.mu_d = 7.1;
+parms.sigma_d = 0.3;
+
+
+
+
+%% Simulation
+beta_belief = parms.beta_belief; delta = parms.delta; 
+r =parms.r; mu = parms.mu; sigma = parms.sigma;
+mu_d = parms.mu_d; sigma_d = parms.sigma_d;
+
+tic
+m = zeros(parms.simul,4);
+p = zeros(parms.simul,3);
+d = zeros(parms.simul,3);
+
+% Path of payments
+for i = 1:parms.simul
+    i
+    
+    % Draw a lognormal sample
+    y = exp(mu + sigma.*randn(1,3)); 
+    y(2) = y(2) - (rand<0.4)*y(2)*(0.5+0.4*rand);
+    y(3) = y(3) - (rand<0.5)*y(3)*(0.5+0.4*rand);
+    % Draw a debt sample
+    m(i,1) = exp(mu_d + sigma_d.*randn(1));
+    parms.v = m(i,1)/(0.7 + .02*randn(1));
+    c = toc;
+    [~,p(i,1),d(i,1)] = V1(y(1),m(i,1),parms); m(i,2) = (1+r)*(m(i,1)-p(i,1));
+    c = toc-c
+    c = toc;
+    [~,p(i,2),d(i,2)] = V2(y(2),m(i,2),parms); m(i,3) = (1+r)*(m(i,2)-p(i,2));
+    c = toc-c
+    [~,p(i,3),d(i,3)] = V3(y(3),m(i,3),parms); m(i,4) = m(i,3)-p(i,3);
+   
+end
+t= toc
+%% Simulation
+
+% beta_belief = parms.beta_belief; delta = parms.delta; 
+% val = parms.v; r =parms.r; mu = parms.mu; sigma = parms.sigma;
+% mu_d = parms.mu_d; sigma_d = parms.sigma_d;
+% 
+% m = zeros(2,4);
+% p = zeros(2,3);
+% d = zeros(2,3);
+% 
[…]

### 2020-05-30 RScripts/grf.R

@@ -1,0 +1,185 @@
+library(tidyverse)
+library(grf)
+library(ggplot2)
+library(DiagrammeR)
+library(DiagrammeRsvg)
+library(gdata)
+
+# SET WORKING DIRECTORY
+setwd('C:/Users/xps-seira/Dropbox/Apps/ShareLaTeX/Donde2019')
+set.seed(5289374)
+
+source("./RScripts/best_tree.R")
+
+heterogeneity_effect <- function(data_in,treatment_var,outcome_var,writedata) {
+  
+require("dplyr")
+data_frame <- data_in %>%
+  filter(data_in[,treatment_var] == 1 | data_in[,treatment_var] == 0) %>%
+  select(-c( pro_2, pro_3, pro_4, pro_5, pro_6, pro_7, pro_8, pro_9, fee, fecha_inicial,
+             def_c, fc_admin_disc, fc_survey_disc, fc_admin, fc_survey, dias_primer_pago), 
+         treatment_var, outcome_var ) %>%
+  drop_na()  
+
+
+# PREPARE VARIABLES
+X <- select(data_frame,-c(outcome_var, treatment_var,NombrePignorante, prenda))
+Y <- select(data_frame,outcome_var)
+W <- as.numeric(data_frame[,treatment_var] == 1)
+
+# ESTIMATE MODEL
+tau.forest = causal_forest(
+  X = model.matrix(~., data = X), 
+  Y = data.matrix(Y), 
+  W = W,
+  honesty = TRUE)
+
+if (writedata == 0) {
+  # BEST TREE
+  best_tree_info <- find_best_tree(tau.forest, "causal")
+}
+
+# OVERLAP ASSUMPTION
+propensity.forest = regression_forest(X, W)
+propensity_score = predict(propensity.forest)$predictions
+hist(propensity_score, xlab = "propensity score")
+
+# Estimate treatment effects for the training data using out-of-bag prediction.
+tau_hat_oob = predict(tau.forest, estimate.variance = TRUE)
+hist(tau_hat_oob$predictions)
+
+# Estimate the conditional average treatment effect on the full sample (CATE).
+print(average_treatment_effect(tau.forest, target.sample = "all"))
+
+# Estimate the conditional average treatment effect on the treated sample (CATT).
+# Here, we don't expect much difference between the CATE and the CATT, since
[…]

### 2020-05-30 RScripts/pfv_pred.R

@@ -1,0 +1,112 @@
+library(tidyverse)
+library(grf)
+library(ggplot2)
+library(DMwR)
+
+# SET WORKING DIRECTORY
+setwd('C:/Users/xps-seira/Dropbox/Apps/ShareLaTeX/Donde2019')
+set.seed(5289374)
+
+
+rf_predict <- function(data_in,take.up) {
+  
+  require("dplyr")
+  data_train <- data_in %>% 
+    filter(insample == 1) 
+  
+  data_test <- data_in %>% 
+    select(-c(take.up, nombrepignorante, prenda, insample))
+  ###################################################################  
+  ###################################################################  
+  
+  
+  # PREPARE VARIABLES
+  X <- select(data_train,-c(take.up, nombrepignorante, prenda, insample))
+  W <- as.numeric(data_train[,take.up] == 1)
+  
+  ###################################################################  
+  ###################################################################  
+  
+  
+  # ESTIMATE MODEL
+  pred.forest = regression_forest(X, W)
+  rf_pred = predict(pred.forest,data_test)$predictions
+  hist(rf_pred, xlab = "predictions")
+  
+  data.out <- add_column(data_in, rf_pred)
+  filename <- paste("_aux/pred_",take.up,".csv", sep="") 
+  write_csv(data.out,filename)
+}
+
+
+
+###################################################################################
+
+# Prenda level
+data_pfv_fee <- read_csv('./_aux/data_pfv_test_pago_frec_vol_fee.csv')
+
+# data_train <- data_pfv_fee %>% 
+#   filter(insample == 1) %>%
+#   as.data.frame() %>%
+#   mutate(pago_frec_vol_fee = as.factor(pago_frec_vol_fee)) 
+# data_test <- data_pfv_fee %>% 
+#   filter(insample == 0)  %>%
+#   as.data.frame() %>%
+#   mutate(pago_frec_vol_fee = as.factor(pago_frec_vol_fee)) 
+# 
+# ## Using SMOTE to create a more "balanced problem"
+# data.smoted <- SMOTE(pago_frec_vol_fee ~ .-nombrepignorante -prenda -insample,
+#                      data_train, k = 2, perc.over = 300, perc.under=200)
+# 
+# data_pfv_fee <- rbind(data.smoted, data_test)
+# write_csv(data_pfv_fee,"_aux/data_pfv_test_smoted_pago_frec_vol_fee.csv")
[…]

### 2020-05-30 oldrepo/IsaacMeza-donde2019-54d6b0d43053/RScripts/pfv_pred.R

@@ -1,0 +1,49 @@
+library(tidyverse)
+library(grf)
+library(ggplot2)
+
+# SET WORKING DIRECTORY
+setwd('C:/Users/xps-seira/Dropbox/Apps/ShareLaTeX/Donde2019/oldrepo/IsaacMeza-donde2019-54d6b0d43053')
+set.seed(5289374)
+
+
+rf_predict <- function(data_in,take.up) {
+  
+  require("dplyr")
+  data_train <- data_in %>% 
+    filter(insample == 1) 
+
+  data_test <- data_in %>% 
+    select(-c(take.up, nombrepignorante, prenda, insample))
+###################################################################  
+###################################################################  
+
+    
+  # PREPARE VARIABLES
+  X <- select(data_train,-c(take.up, nombrepignorante, prenda, insample))
+  W <- as.numeric(data_train[,take.up] == 1)
+
+###################################################################  
+###################################################################  
+  
+  
+  # ESTINATE MODEL
+  pred.forest = regression_forest(X, W)
+  rf_pred = predict(pred.forest,data_test)$predictions
+  hist(rf_pred, xlab = "predictions")
+  
+  data.out <- add_column(data_in, rf_pred)
+  filename <- paste("_aux/pred_",take.up,".csv", sep="") 
+  write_csv(data.out,filename)
+}
+
+#####################################################
+
+# READ DATASET
+# Prenda level
+data <- read_csv('./_aux/data_pfv_test.csv')
+
+#RF Predictions
+rf_predict(data,"pago_frec_vol") 
+rf_predict(data,"pago_frec_vol_fee")
+rf_predict(data,"pago_frec_vol_promise") 

### 2020-06-16 Tables/baseline_survey3.tex
Update of numbers in paper

% Table generated by Excel2LaTeX from sheet 'baseline_survey'
\begin{tabular}{lrrrr}
\toprule
      &       &       &       &  \\
Para llegar a esta sucursal, ¿Cuanto tardo?  &       & 21.86 & 20.82 & 7013 \\
\midrule
      &       &       &       &  \\
¿Cuanto gasta su familia en una semana normal?  &       & 1554.95 & 1747.44 & 2169 \\
\midrule
      &       &       &       &  \\
¿Cuanto logra ahorrar en una semana normal?  &       & 466.92 & 899.4 & 2103 \\
\midrule
      &       &       &       &  \\
¿Le ha pasado que gasta mas de lo que quisiera porque cae en la tentacion? & \multicolumn{1}{l}{Nunca} & 0.14  & \multicolumn{1}{l}{-} & 7098 \\
      & \multicolumn{1}{l}{Casi nunca} & 0.17  & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} \\
      & \multicolumn{1}{l}{A veces} & 0.57  & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} \\
      & \multicolumn{1}{l}{Muy seguido} & 0.12  & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} \\
\midrule
      &       &       &       &  \\
En los ultimos seis meses, alguna vez falto dinero en su hogar para pagar & \multicolumn{1}{l}{Renta} & 0.14  & 0.34  & 4784 \\
      & \multicolumn{1}{l}{comida } & 1553  & 0     & 0 \\
      & \multicolumn{1}{l}{medicina } & 0.1   & 0.31  & 4786 \\
      & \multicolumn{1}{l}{luz} & 1115  & 0     & 0 \\
      & \multicolumn{1}{l}{gas} & 0.16  & 0.36  & 4762 \\
      & \multicolumn{1}{l}{telefono} & 0     & 0     & 0 \\
      & \multicolumn{1}{l}{agua} & 0.19  & 0.39  & 4841 \\
\midrule
      &       &       &       &  \\
¿Cual preferiria tener?  & \multicolumn{1}{l}{100 pesos en tres meses} & 0.63  & \multicolumn{1}{l}{-} & 4370 \\
      & \multicolumn{1}{l}{150 pesos en cuatro meses} & 0.37  & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} \\
\midrule
      &       &       &       &  \\
¿Le gustaria recibir recordatorios gratuitos en su celular &       & 0.34  & 0.47  & 5082 \\
\bottomrule
\bottomrule
\end{tabular}%

### 2020-06-16 main.tex
Update of numbers in paper

@@
 
+\usepackage{comment}
+\usepackage{subcaption,graphicx}
+
 %\myexternaldocument{OA}
@@
 
-\title{The limits of self commitment and private paternalism \thanks{}}
-\author{Joyce Sadka \and Enrique Seira \and Isaac Meza  \thanks{Sadka: ITAM, jsadka@itam.mx;  
+\title{Private paternalism and the limits of self commitment  \thanks{We want to thank Craig McIntosh and Mauricio Romero for advice and encouragement.
+We want to thank also Ricardo Olivares for excellent research assistance and Erik Molina help with formatting.
+Jose Maria Barrero, Emilio Gutierrez, Aprajit Mahajan, Matt Rabin and seminar participants at ITAM provided very valuable feedback.}}
+\author{Isaac Meza \and Joyce Sadka \and Enrique Seira   \thanks{Sadka: ITAM, jsadka@itam.mx;  
 Seira: ITAM, enrique.seira@itam.mx; Meza: University of California at Berkeley, isaac.meza@berkeley.edu} }
@@
 We study the benefits of ``private paternalism'' in the understudied but important pawnbroker context.
-We show that forcing people into commitment contracts with financial penalties for not paying on time decreases their (fee-including) financial cost by \hlgr{11\%}, increases the likelihood of recovering their pawn by \hlgr{23\%}, and increases the likelihood of repeat business by \hlgr{20\%}.
-While virtually all clients would reduce their financing cost with the commitment contract, we show that only 10\% choose it.
-Using salient personal promises instead of pecuniary penalties as commitment triples contract take-of, but has not effect on financial costs or pawn recovery.
+We show that forcing people into commitment contracts with financial penalties for not paying on time \textit{decreases} their (fee-including) financial cost by 9.5\%, increases the likelihood of recovering their pawn by 25\%, and increases the likelihood of repeat business by 55\%.
+Using the recent machine learning methods for estimating heterogeneous treatment effects, we calculate that more than 90\% clients would reduce their financing cost with the commitment contract, however 10\% choose it.
+Using personal promises instead of fees as commitment triples take-of but has no effects.
 
@@
 
-\textbf{Keywords: } Private paternalism, choice, present bias, commitment, pawnshops.
-
-\textbf{JEL codes:} XXX
+\textbf{Keywords: } Private paternalism, choice, present bias, naivete, overconfidence, commitment, pawnshop.
+
+\textbf{JEL codes:} G41, C93, O16, G21
 
@@
 However he notes that these same firms shroud these forcing mechanisms and don't market their commitment features, presumably because students, workers and borrowers ``don't welcome these paternalistic\footnote{\cite{Laibson2018} defines paternalism as a policy that advances an individual's interests by restricting his or her freedom, and private paternalism as paternalism implemented by private institutions.} restrictions''.
-In this, he sees an important \textit{commitment puzzle}: if clients were present biased and  sophisticated about their self control problem they should appreciate commitment features and firms should be eager to market them.
+In this he sees an important \textit{commitment puzzle}: if clients were present biased and  sophisticated about their self control problem they should appreciate commitment features and firms should be eager to market them.
 The fact that this is not the case suggests some clients may be naive about their self control problems, and that \textit{private paternalism}  ---a policy of restricting choice implemented by private firms--- may increase clients' welfare.
@@
 But they are also interesting because regulators and practitioners view pawnbrokers as the lenders to which people in desperate need turn to.
-The regulators' concern is that the selection of clients that go to pawnshops may be particularly vulnerable, have bad debt management skills, and are more likely to be present biased and naive about it.\footnote{In 2013 Mexico's Consumer Protection Bureau (Profeco) forced Pawnshops to be more transparent in their pricing, register their contracts with them and issued regulation to protect clients: \url{http://www.diputados.gob.mx/LeyesBiblio/ref/lfpc.htm}.}
-
-Indeed, using a survey conducted by us in branches of Lender $P$, we document some evidence consistent with regulators' concerns: while pawnshop clients predict they will recover their pawn with 93\% probability on average, in reality only 40\% of them do, suggesting naivete.
-Conditional on paying a positive amount towards pawn recovery, 47\% lose their pawn and their payment.
-In our survey 68\% report self-control problems in several domains.%, but only \hlgr{15\%} show inter-temporal inconsistencies in a classical present-bias question, a similar number to \cite{Ashaf}.
+The regulators' concern is that the selection of clients that go to pawnshops may be particularly vulnerable, have bad debt management skills, and be more likely to have present biased preferences while being naive about it.\footnote{In 2013 Mexico's Consumer Protection Bureau (Profeco) is concerned about abuse.
+It forced Pawnshops to be more transparent in their pricing, register their contracts with them and issued regulation to protect clients.
+Congress has enacted laws in this regard.
+\url{http://www.diputados.gob.mx/LeyesBiblio/ref/lfpc.htm}.}
+
+Indeed, using a survey conducted by us in branches of Lender $P$, we document some evidence consistent with regulators' concerns: while pawnshop clients predict they will recover their pawn with 93\% probability on average, in reality only 44\% of them do, suggesting naivete.
+Even conditional on paying a positive amount towards pawn recovery, 47\% lose their pawn and their payment.
+In our survey 69\% report self-control problems saying they often fall into temptation spending.
+%, but only \hlgr{15\%} show inter-temporal inconsistencies in a classical present-bias question, a similar number to \cite{Ashaf}.
 %and \hl{19\%} do not normally budget monthly expenses.
@@
 The client has complete flexibility to pay any number of times any amount she desires towards the recovery of her pawn, with no pre-payment penalties.
-However if the total amount of principal plus interest is not covered by the end of the 105 days, she loses her pawn and all the payments that have been done (unless she renews the loan before this).
+However if the total amount of principal plus interest is not covered by the end of the 105 days, she loses her pawn and all the payments that have been done (unless she renews the loan before this by paying all accumulated interest).
 All transactions ---appraisal of the piece, loan disbursement and loan servicing--- are conducted at the branch.
@@
 First, would clients benefit  ---in terms of recovering their pawn and in terms of incurring in lower financing costs---  from having a frequent (monthly) payment commitment contract \textit{forced} on them, instead of the current 3-month pay-when-you-want contract?
-That is, we are asking whether \textit{charging} them a 2\% late payment fee for not paying their monthly installment on time can actually decrease total fee-inclusive financing cost.
+That is, we are asking whether \textit{charging} them a 2\% late payment fee for not paying a monthly installment on time can actually \textit{decrease} total fee-inclusive financing cost.
 Second, would there be demand for such a frequent payment commitment contract vis-a-vis the status quo one if given choice?
-Notice that any payment profile implemented in the commitment contract can be replicated under the status quo contract, but the later has more flexibility to respond to income shocks without incurring in fees.
+Notice that any payment profile implemented in the commitment contract can be replicated by the borrower under the status quo contract, but the later affords more flexibility to respond to income shocks without incurring in fees.
 Third, what types of clients would demand these contracts that restrict choice?
 Fourth, are late payment fees key to provide commitment or would a non-pecuniary but salient personal promise to pay provide a cost-reducing mix of commitment vs flexibility?
-A large and important lab experiment literature suggest that promises change behavior significantly in laboratory settings, but we know little about their effect on the field in natural environments.\footnote{Some important papers in this space are \cite{PromisesPartnerships}, \cite{Vanberg}, \cite{Belot2010}, \cite{WhyDoPromises}, \cite{FurtherPromises}, \cite{Ismayilov2017}.} Finally and importantly, is \textit{giving choice} among contracts better than forcing them into payment-commitment contracts in terms of minimizing financing costs incurred and the likelihood of recovering their pawn?
+A large and important lab experiment literature suggest that promises change behavior significantly in laboratory settings, but we know little about their effect on the field in natural environments.\footnote{Some important papers in this space are \cite{PromisesPartnerships}, \cite{Vanberg}, \cite{Belot2010}, \cite{WhyDoPromises}, \cite{FurtherPromises}, \cite{Ismayilov2017}.
+There is also some actual policy around using promises for loans: the government Mexico has created a program called ``Loans on your word'' for uncollateralized borrowing (\url{http://tiny.cc/yfmnmz}).
+There is little information about them though.} Finally and importantly, is \textit{giving choice} among contracts better than forcing them into payment-commitment contracts in terms of minimizing financing costs incurred and the likelihood of recovering their pawn?
+Or on the contrary, is it better to force the commitment contract
+paternalistically?
 
@@
 Here let us briefly explain the main 3 arms.
-The first one involves a group of clients that were given only the status quo contract (henceforth the \textit{Status-quo group}).
-The second arm (\textit{Fee-forced group}) was assigned into a monthly payment commitment contract, which stipulated that clients had to pay 1/3 of their loan plus accumulated interest in each of the 3 months of the term length.
+The first one involves a group of clients that were given only the status quo contract (henceforth the \textit{status-quo forcing group}).
+The second arm (\textit{fee-forcing group}) was given only a monthly payment commitment contract, which stipulated that clients had to pay 1/3 of their loan plus accumulated interest in each of the 3 months of the term length.
 Failing to do this would result in a fee of 2\% of the amount due that month.
@@
 We find that forcing clients into frequent payment commitment contracts causes them on average to save on financing cost and to recover their pawn more.
-The effects are large: financing cost decreases by \hlgr{11\%} on average, while the likelihood of recovering their pawn increases by \hlgr{19\%}.
-This is robust to including  transport costs of going to the branch plus losing a day's wage for each visit.
+The effects are large: financing cost decreases by 9.5\% on average, while the likelihood of recovering their pawn increases by 25.8\%.
+Results are robust to including in the cost definition transport costs of going to the branch plus losing a day's wage for each visit.
 Importantly, the benefits are distributed broadly: the whole distribution of treatment effects shows cost savings.
@@
 It seems that the fee-commitment contract induces people who would otherwise pay something towards recovery, to pay more and faster and thus recover their pawn more at a cheaper financial cost.
-Finally, we find that borrowers assigned to the forced fee-commitment contract are \hlgr{5pp} (\hlgr{20\%} of the mean) more likely to be repeat costumers than the control group, suggesting that they themselves liked the commitment contract more after experiencing it.
+Finally, we find that borrowers assigned to the forced fee-commitment contract are 5pp (55\% of the mean) more likely to be repeat costumers than the control group, suggesting that they themselves liked the commitment contract more after experiencing it.
 
@@
 In spite of these estimated benefits for all clients, their actual demand for the fee-commitment contract is low.
-Only \hlgr{10\%} of the group offered a choice between the monthly payment fee-commitment contract and the status-quo one chose the former.
-This is not likely driven by misunderstanding the (already simple) contract.
-We had two assistants from the research team in each of the experiment's branches every day for all branch opening hours, material was developed to explain the differences among the two contracts, and subjects spelled back to assistants the loan differences.
-Furthermore take up is systematically predicted by baseline covarites\footnote{We find that the more educated, those that report that their family typically asks for money, those that make a monthly budget of expenses, and ask for a remainder to payment (and marginally those we classify as present-biased) are more likely to chose the fee-commitment contract if given the choice.
-The opposite holds for those that are more vulnerable (can barely pay for food, electricity, etc) and those that report being more stressed.}, making it less likely that it is just random mistakes.
-Low demand for commitment is consistent with most of the literature (\cite{Laibson2015}, \cite{Laibson2018}, \cite{John}, \cite{Ted}, \cite{Rabin2018}).\footnote{\cite{Alcohol} and \cite{Kremer} are some of the few instances of high demand for commitment.
+Only 10\% of the group offered a choice between the monthly payment fee-commitment contract and the status-quo one chose the former.
+This is not likely driven by misunderstanding the (already simple) contract.\footnote{We had two ITAM students in each of the experiment's branches every day for all branch opening hours to carefully explain the contracts; material was developed to explain the differences among the two contracts, and subjects spelled back to our ITAM assistants the loan differences.
+Furthermore take up is systematically predicted by baseline covariates, %\footnote{We find that the more educated, those that report that their family typically asks for money, those that make a monthly budget of expenses, and ask for a remainder to payment (and marginally those we classify as present-biased) are more likely to chose the fee-commitment contract if given the choice.
+The opposite holds for those that are more vulnerable (can barely pay for food, electricity, etc) and those that report being more stressed.},
+making it less likely that it is just random mistakes.} Low demand for commitment is consistent with a large part of the literature of the literature (\cite{Laibson2015}, \cite{Laibson2018}, \cite{John}, \cite{Ted}, \cite{Rabin2018}).%\footnote{\cite{Alcohol} and \cite{Kremer} are some of the few instances of high demand for commitment.
 \cite{Alcohol} speculates that this difference may be explained by their subjects having more experience with their self control problem.
 Close to ninety percent of our subjects claim to have pawned before.
-We find that experience does not predict positive take up in our sample.} \cite{Laibson2015} shows that the lost flexibility resulting from a commitment contract can severely limit take-up when agents are naive about their self control, even though commitment could we welfare improving for the naive.
-We estimate zero average treatment effects of the \textit{fee-choice} arm on financial cost and on pawn recovery.
-These effects are zero throughout the quantile distribution.
+We find that experience does not predict positive take up in our sample.}
+\cite{Laibson2015} shows that the lost flexibility resulting from a commitment contract can severely limit take-up when agents are naive about their self control, even though commitment could be welfare improving for them.
+We estimate zero average treatment effects of the \textit{fee-choice} arm on financial cost and on pawn recovery and throughout the quantile distribution.
 
@@
 We calculate that about 80\% of clients in the fee-choice group chose contracts that induced \textit{higher} financial cost.
-On average they spend an extra \hlgr{\$300} pesos, close to 10\% of the average loan value.
-In particular \hlgr{95\%} of those that chose the status-quo contract would have been better in the fee-commitment contract, while only \hlgr{7\%} of those who chose the fee-commitment contract would have been better in the status-quo one.
+On average they spend an extra \$238 pesos, close to 12\% of the average loan value.
+In particular 92\% of those that chose the status-quo contract would have been better in the fee-commitment contract, while only 8\% of those who chose the fee-commitment contract would have been better in the status-quo one.
 This suggests that forcing clients into commitment contacts (i.e.
@@
 To do this we implemented two other treatment arms.
-A \textit{promise-forced} arm exactly analogous to our \textit{fee-forced arm} except that instead of telling them that there is a fee if they don't pay on time, we made borrowers promise that they would pay one third of the amount in each of the 3 months, and told them that if they didn't they would have broken their promise.
+A \textit{promise-forcing} arm exactly analogous to our \textit{fee-forcing arm} except that instead of telling them that there is a fee if they don't pay on time, we made borrowers promise that they would pay one third of the amount in each of the 3 months, and told them that if they didn't they would have broken their promise and failed their word.
 Because salience is key we made them sign a (non-legally binding) personal promise and emphasized we were counting on them to keep their promise.
@@
 We document two main results in the promise arms.
-First, demand for the \textit{Promise-forced} contract is three times bigger than for the \textit{Fee-forced} contract, with \hlgr{31\%} take-up.
-This difference between both choice arms suggests that clients are indeed understanding and taking into account the contractual parameters when they choose, and that the fee commitment was probably too strong from their point of view.
-Second, the \textit{Promise-forced} contract had zero effects on average and for an overwhelming fraction of the population on financing cost and pawn recovery.
+First, demand for the commitment-promise contract is three times bigger than for the commitment fee contract, with 31\% take-up.
+This difference between both choice arms suggests that clients are indeed understanding and taking into account the contractual parameters in their choice, and that the fee commitment was probably too strong from their point of view.
+Second, the \textit{Promise-forcing} contract had zero effects on average and throughout the distribution on financing cost and pawn recovery.
 The same is true for the \textit{Promise-choice arm}.
@@
 Promises did not provide enough commitment so as to be reflected in behavior.
-Contrary to lab evidence, people did not keep the promise, at least the way it could be implemented in the field.\footnote{The government Mexico has created a program called ``Loans on your word'' for uncollateralized borrowing (\url{http://tiny.cc/yfmnmz}), but they rely on group lending, and therefore social collateral is at stake.}
+This is true both imposed promises and chosen promises.
+Contrary to lab evidence, people did not keep the promise, at least the way it could be implemented in the field.
+
+We contribute to several strands of literature.
+First, to the broad literature on commitment demand.
+A significant literature has shown that demand for commitment exists but is somewhat low in some contexts (\cite{Ashraf}, \cite{Gine}, \cite{Ted}), and high in others (\cite{Kremer},  \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}).
+We add to this literature by showing that very small fees are enough to drastically reduce demand for commitment, even when commitment is beneficial for almost everybody in our sample, and that softer commitments in the form of non-pecuniary personal promises elicit higher demand.\footnote{Our fees are \hl{400\%} higher as a fraction of the loan than those of \cite{John}.} Second, two recent papers show that among those who demand commitment, the extent of commitment needed is underestimated (\cite{Ted}, \cite{John}) and that subjects can hurt themselves by self-imposing too week a commitment.
+We contribute in design ---by not allowing choice of the extent of commitment--- but also on how we infer the underestimation of the value of commitment by subjects.
+While these two papers infer too low commitment from subjects failing to reach the goal ex-post, we infer it by quantifying forgone personalized treatment effects ex-ante.
+Third, we focus on an important new context: pawnshop borrowing.
+Pawnshop borrowing is extremely prevalent in developing countries and very worrisome to regulators, yet severely understudied.
+
+Fourth, we study \textit{both} causal effects and selection into frequent payment commitment loan contracts.
+\cite{Ghatak} state that ``high-frequency repayment, a feature in nearly all microfinance contracts, has been largely overlooked''.\footnote{\cite{LittleAtAtime} also note that ``it is especially surprising that there is so little analytical discussion of the incentive effects of the installment system''.} This paper fills part of this gap.
+\cite{Pande} study the effect of installment frequency on loan default and (surprisingly given their prevalence and the literature above) find null effects, while \cite{Murdoch} study selection into frequent payment microfinance loans, conjecturing that ``such repayment structure is potentially beneficial in fostering discipline among present-biased borrowers''.
+In contrast to \cite{Pande} we find very strong effects of payment frequency on decreased default.\footnote{Possibly because there are high levels of default in our context and not in theirs and because we have more statistical power from larger sample and individual randomization.} \cite{Murdoch}  show that a robust positive correlation exists between having present biased preferences in surveys and selecting into microfinance ---which they interpret as being due to the discipline of frequent payment--- acknowledging that the ``interpretation is suggestive...
+and needs to be confirmed by studies that establish causal links''.
+Our experimental test of this causal link rejects that people like and demand frequent payments (at least in our context).
+In contrast to \cite{Murdoch} we can isolate the pure effect of payment frequency on demand by randomly changing just this aspect of the contract.
+Fifth, we also contribute to the literature on the effect of promises by testing their effect on the field.
+
+More importantly, our unique experimental design, paired with new machine learning methods to estimate heterogeneous treatment effects \cite{atheygrf}, allows us to estimate whether there is positive or negative selection into beneficial contracts, and whether pawnshop clients forgo money by not demanding commitment.
+In consonance with what \cite{Walters} finds in another context, we find that it is not the case that those that benefit most from the contract demand it, consistent with a significant fraction of clients displaying naivete about self control problems (see \cite{Rabin2018}).
+Our context is one in which private paternalism (\cite{Laibson2018}) could work since almost all pawnshop clients would benefit from frequent payment contract yet there it almost no demand for them.
+After our experiment ended, Lender P started to tie in installment payment components to some of their contracts themselves.
 
@@
 
-Pawn borrowing is one of the oldest form of borrowing and one to which people with little access to the formal credit market turn to for ``energency'' loans.
+Pawn borrowing is one of the oldest form of borrowing and one to which people with little access to the formal credit market turn to for ``emergency'' loans.
 They existed in antiquity at least since the Roman Empire, and there are records of it in China about 1,500 years ago (\cite{PawnShops}).
@@
 Why people go, how much it costs, what different contracts can tell us about consumer biases.
-We study such  context with Lender $P$, one of the largest pawn shops in Mexico, with \hl{several hundred} branches spanning multiple States in Mexico.
+We study such  context with Lender $P$, one of the largest pawn shops in Mexico, with dozens of branches spanning multiple States in Mexico.
 
@@
 The first is that the pawned piece may have a sentimental value to the client above of its gold value, making it inefficient for the lender to keep the piece.
-We actually find that clients report a subjective value that is almost \hlgr{twice} the value of its gold content.
+We actually find that clients report a subjective value that is almost twice the value of its gold content.
 Second, it thought that keeping the piece lowered client satisfaction and made the client less likely to return and pawn again.
@@
 \cite{Pande} study of the effect of payment frequency work in a context where the rate of default is close to 1\%.
-\cite{LittleAtAtime} has a baseline default of \hl{XX\%}.
+%\cite{LittleAtAtime} has a baseline default of \hl{XX\%}.
 
 One potential explanation for high default is that clients are really just selling their gold piece.
-This is unlikely for the large majority of people not only because the reported subjective value of the pawn is larger than the loan size for \hlgr{86\%} of them, but also because among that lose their pawn \hlgr{74\%} paid a positive amount towards its recovery.
+This is unlikely for the large majority of people not only because the reported subjective value of the pawn is larger than the loan size for 86\% of them, but also because among those that lose their pawn 74\% paid a positive amount towards its recovery.
 This can only be rationalized if they expected to recover their pawn.
@@
 Panel (c) shows total payments that went towards the loan.
-On average clients that lost their pawn paid \hlgr{34\%} of the value their loan.
+On average clients that lost their pawn paid 34\% of the value of their loan.
 Panel (d) shows that while 40\% made zero payments, the rest made one or several payments.
-In fact, panel (b) shows that close to \hlgr{50\%} of clients extended the loan for another cycle and made payments in the second cycle.
+In fact, panel (b) shows that close to 55\% of clients extended the loan for another cycle and made payments in the second cycle.
 
@@
 The loan had a 90 days term with 15 days grace period, and the client could make payments at anytime and no penalty for pre-payment.
-If the client paid the principal plus the accumulated interest before those 105 days, the she received back her pawn, otherwise the pawnbroker kept the piece and any payments done.
+If the client paid the principal plus the accumulated interest before those 105 days, then she received back her pawn, otherwise the pawnbroker kept the piece and any payments done.
 Before the contract expired, the client had the right to renew it (using the same collateral) for another 3 months by going to the pawnshop paying the accumulated interest and signing a new contract with exactly the same terms.
@@
 Bear in mind that these clients have little or no access to other types of loans, and also that they value its convenience: the process is fast and requires no documentation or credit-history.
-Potentially they like it also because they are overconfident on average about the probability of recovering their pawn, as discussed below, even though \hlgr{90\%} of them have pawned before.
+Potentially they like it also because they are overconfident on average about the probability of recovering their pawn, as discussed below, even though 90\% of them have pawned before.
 
@@
 the client lost her pawn), and whether any late-payment fees (active for only some experimental arms) were imposed.
-We have this information for all the pawns that occurred in our 6 branches between \hlgr{August 6th 2012 and August 13th 2013}, this includes all the pawns under our experiment but also those that happened \hlgr{1} month before it started and up to \hlgr{8} months after it ended.
+We have this information for all the pawns that occurred in our 6 branches between August 2nd 2012 and August 13th 2013, this includes all the pawns under our experiment but also those that happened 1 month before it started and up to 8 months after it ended.
 Figure \ref{exp_description}(a) shows the timing of the experiment and our admin data coverage.
 The black arrow represent the dates for which we have administrative data (before and after the experiment) while the light gray represents the duration of the experiment.
-The experiment comprises \hlgr{13,443} pawns, and our administrative data cover a total of \hlgr{26,181} pawns.
+The experiment comprises 13,444 pawns, and our administrative data cover a total of 26,179 pawns.
 
@@
 The survey was necessarily short to avoid discouraging the potential clients from pawning, but at the same time it aimed to measure the following: demographics, proxies for income/wealth, education, self-control problems/present-biased preferences, experience pawning, if the family or friends commonly asked for money, how time consuming and costly was to come to the branch, the subjective probability of recovering their piece that they intended to pawn, the subjective value of their piece in money terms (for how much money would they sell it for), among others.
-We were able to survey \hlgr{7,703} clients (some refused).
+We were able to survey 7,704 clients (some refused).
 %\footnote{We also surveyed clients before and after the experiment, so our survey covers a larger sample that we are not using in this paper.}.
-\hlgr{The appendix transcribes the questionnaire in English and presents summary stats}.
-Survey response rate is 57\%, \hlgr{the Appendix Table} \ref{balance_response} shows that response is not related to admin data observables.
+The appendix \ref{baseline_survey} transcribes the questionnaire in English and presents summary stats.
+Survey response rate is 57\%, the Appendix Table \ref{balance_response} shows that response is not related to admin data observables.
 
@@
 Panel A describes variables from the administrative data.
-It shows that the average loan size is \hlgr{\$1945} pesos (\hlgr{\$105} usd).
-The average number of pawns per day per branch is \hlgr{33}.
-Although not shown in the table, only \hlgr{40\%} of clients recover they pawn within \hlgr{230 days}.
-Even those that recover their pawn tend to pay ir back at the last moment, only \hlgr{20\%} pay before the \hlgr{90}th day.
+It shows that the average loan size is \$1945 pesos (\$105 usd).
+The average number of pawns per day per branch is 33.
+Although not shown in the table, only 40\% of clients recover they pawn within 230 days.
+Even those that recover their pawn tend to pay it back at the last moment, only 17\% pay before the 90th day.
 
 Panel B reports stats from our survey data.
-We learn that \hlgr{73\%} of clients are women, with an average age of \hlgr{44} years; \hlgr{66\%} of them have completed high school or more, and \hlgr{90\%} have pawned before, so that our sample has mostly experienced borrowers.
-Finally the subjective probability of recovery is close to \hlgr{93\%} on average, which contrast with the \hlgr{44\%} recovery that happens in reality for the pawns \hlgr{in the control group}.
+We learn that 73\% of clients are women, with an average age of 44 years; 66\% of them have completed high school or more, and 90\% have pawned before, so that our sample has mostly experienced borrowers.
+Finally the subjective probability of recovery is close to 93\% on average, which contrast with the 44\% recovery that happens in reality for the pawns in the control group.
 Just by this measure borrowers seem to be highly overconfident on average.
-It turns out that the average subjective value they report for the pieces is  \hlgr{6292 pesos}, which is much larger than the average appraised gold value (\hlgr{3222 pesos}).
+It turns out that the average subjective value they report for the pieces is 3250 pesos, which is much larger than the average appraised gold value (1950 pesos).
 This makes it inefficient for them to lose it.
@@
 Since the main treatment involves making them come to the branch to pay each month, the transaction costs of coming to the branch are important, and we ask two questions around them.
-The average time they take to come to the branch is \hlgr{22 minutes}, and the amount of money they spend in transport to do that is \hlgr{11 pesos} \hlgr{(\$0.60 usd)}.
-The population we are working with is economically vulnerable in the sense that \hlgr{31\%} of them could not pay \hlgr{either} water, electricity \& gas or rent in the past \hlgr{6} months.
-They often receive negative income shocks: \hlgr{87\%} said they are pawning because of an emergency, and only \hlgr{13\%} stated it was to use in a \hlgr{`non-urgent expense'}.
+The average time they take to come to the branch is 22 minutes, and the amount of money they spend in transport to do that is 11 pesos (\$0.60 usd).
+The population we are working with is economically vulnerable in the sense that 31\% of them could not pay either water, electricity \& gas or rent in the past 6 months.
+They often receive negative income shocks: 87\% said they are pawning because of an emergency, and only 13\% stated it was to use in a `non-urgent expense'.
 %When asked why they are pawning this piece \hlgr{5\%} responded \hlgr{`lost a family member'}, \hlgr{`a medical emergency'} (\hlgr{11\%}), \hlgr{`an urgent expense'} (\hlgr{71\%}),
@@
 
-We define financial cost as the discounted sum of payments toward the loan plus the value of the loan, and substract to it the appraised or subjective discounted value of the pawn when it is recovered: $Financial \; Cost_i = \sum_t \frac{P_{it}}{(1+r)^t} + Pawn \: Value - \frac{\text{I}(Recovered \: Pawn) \times Pawn \: Value}{(1+r)^T}$, with $t$ indexing days, $T$ is the day when the pawn is recovered, I($\cdot$) an indicator function for recovering the pawn, $r$ is a daily interest rate equivalent to a \hlgr{7\%} monthly interest rate.
+We define financial cost as the discounted sum of payments toward the loan plus the value of the loan, and substract to it the appraised or subjective discounted value of the pawn when it is recovered: $Financial \; Cost_i = \sum_t \frac{P_{it}}{(1+r)^t} + Pawn \: Value_i - \frac{\text{I}(Recovered \: Pawn_i) \times Pawn \: Value_i}{(1+r)^T}$, with $t$ indexing days, $T$ is the day when the pawn is recovered, I($\cdot$) an indicator function for recovering the pawn, $r$ is a daily interest rate equivalent to a 7\% monthly interest rate.
 Figure \ref{fc_hist}(a) plots a histogram of this cost in pesos conditional on recovering and conditional on not recovering the pawn.
-This cost is calculated for a time period of \hlgr{230 days} after loan origination, as \hlgr{51\%} of clients actually renew the loan one time and \hlgr{26\%} a second time.
-Of those who renew once \hlgr{36\%} lose the pawn, and of those that renew twice \hlgr{15\%} do.
+This cost is calculated for a time period of 230 days after loan origination, as 50\% of clients actually renew the loan one time and 28\% a second time.
+Of those who renew once 34\% lose the pawn, and of those that renew twice 15\% do.
 Figure \ref{fc_hist}(a) suggest that financial cost is significant, even for those that do recover their pawn.
@@
 For them the cost is between 150\% and 250\% of the loan value.
-\hl{The difference between panel (a) and (b) arises since clients who lose their pawn tend to be those that pledge cheaper pieces.} We calculate an APR of \hl{23,000\% on average for the control group.}\footnote{The Annual Percentage Rate is calculated as the internal rate of return $i$ using the following formula \hl{XXX}.}
+%\hl{The difference between panel (a) and (b) arises since clients who lose their pawn tend to be those that pledge cheaper pieces.}
+We calculate an APR of \hl{177\% on average for the control group.}\footnote{The Annual Percentage Rate (for pawn $j$) is calculated as the internal rate of return $i$ such that $\sum_t \frac{P_{jt}}{(1+i)^t} + \frac{\text{I}(Default \: Pawn_j) \times Pawn \: Value_j}{(1+i)^T} - Pawn \: Value_j = 0$, where $T$ is the date the pawn was lost.}
 
@@
 
-\noindent \textit{Selection of branches.} Starting \hlgr{August 6th} 2012, we implemented our experiment in 6 branches of Lender $P$.
+\noindent \textit{Selection of branches.} Starting September 6th 2012, we implemented our experiment in 6 branches of Lender $P$.
 The branches were selected by Lender $P$ to be dispersed across Mexico city and have varying sizes.
-In four of them the experiment ran for \hlgr{107} days, and in 2 of them we ran it for a shorter time to economize on data collection costs since we realized we would not be constrained by sample size.
+In four of them the experiment ran for 107 days, and in 2 of them we ran it for a shorter time to economize on data collection costs since we realized we would not be constrained by sample size.
 %Thus we eliminated \hl{the smallest} ones.
-Branches are more than \hl{5 km} apart from each other, and there is little substitution among them (only \hlgr{1\%} of consumers appear in more than one of our branches).
+Branches are more than 5 km apart from each other, and there is little substitution among them (only 1\% of consumers appear in more than one of our branches).
 
@@
 The level of the penalty was determined by Lender $P$ after talking to clients and based on Lender $P$'s experience.
-They deemed 2\% something that was big enough to provide commitment but small enough that if clients had an emergency and could not pay, the fee would not cause the pawn to be unrecoverable.\footnote{As explained below we also experimented with a contract where there was no pecuniary fee for paying late but where we clients made a personal promise to pay monthly.}
+They deemed 2\% something that was big enough to provide commitment but small enough that if clients had an emergency and could not pay, the fee would not cause the pawn to be unrecoverable.\footnote{As explained below we also experimented with a contract where there was no pecuniary fee for paying late but where we clients made a personal promise to pay monthly.
+In contrast with \cite{John} we don't let the clients choose the size of the fee.
+As that paper shows doing this results in wrong choices by naive present biased consumers.}
 
@@
 It also limits potential  manipulation by appraisers, who in the presence of individual level randomization could potentially pick their preferred costumers from the line or tell them to wait until their desired contract shows up on the screen.
-Intra-branch correlation on the probability of default (ICC) is small, at \hlgr{0.08}, so we don't lose much power vis-a-vis individual level randomization.
+Intra-branch correlation on the probability of default (ICC) is small, at 0.08, so we don't lose much power vis-a-vis individual level randomization.
 
@@
 
-\subsection{More on implementation.}
+\subsection{More on implementation.} \label{implementation}
 
@@
 
-\noindent where $i$ refers to client, $j$ indexes branch, and $X_{ij}$ are branch and day-of-week fixed effects, as well as dummies for the number of arms a client fell into and number of pieces pawned during the whole experiment\footnote{\hl{ISAAC: puedes incluir en appendix una tabla que muestre en que tratamientos cayeron todas la prendas durante el experimento?
-Y tambien un tab de cuantas personas empeniaron 1, 2, 3...
-piezas durante el experimento?}}.
+\noindent where $i$ refers to client, $j$ indexes branch, and $X_{ij}$ are branch and day-of-week fixed effects, as well as dummies for the number of arms a client fell into and number of pieces pawned during the whole experiment\footnote{If we restrict ourselves to pieces that fall in a single-arm (64\%) , then treatment reduces the financial cost by 5.7\%, increases the likelihood of recovering their pawn by 35\%, and increases the likelihood of repeat business by 66\%.
+\hl{ISAAC: me gustaria decir que ls resultados que citamos en el abstract se mantienen muy parecidos si tiramos los que tienen mas de un treatement arm?}}.
 Our main outcome variables $y_{ij}$ are measures of financial cost in pesos as defined in Section \ref{FC_def}, as well as an indicator variable for client $i$ losing her pawn.
@@
 The second coefficient uses the subjective value of the pawn instead.
-In both cases we find that being assigned to the fee-forcing commitment contract causes a large reduction in the financing cost the client incurred, of \hlgr{11}\% in the fist definition and \hlgr{15\%} in the second one.
+In both cases we find that being assigned to the fee-forcing commitment contract causes a large reduction in the financing cost the client incurred, of 9.5\% in the fist definition and 13.3\% in the second one.
 That is, we find that \textit{charging} clients a late payment fee  actually decreases total \textit{fee-inclusive} financing cost.
@@
 Given that the fee-forcing contract makes clients visit the branch more often (monthly), one may want a measure that includes those costs as well.
-Going in that direction, in a broader measure of costs, for each visit we add the self-reported transport cost\footnote{Here we had to restrict \hlgr{93\%} of the sample for which we had information on these.} plus a whole day's wage, multiplied by the number of visits.
+Going in that direction, in a broader measure of costs, for each visit we add the self-reported transport cost\footnote{Here we had to restrict 66\% of the sample for which we had information on these.} plus a whole day's wage, multiplied by the number of visits.
 Adding a whole day's wage may be too conservative, but we still observe a reduction of this more comprehensive measure of cost.
@@
 Figure \ref{fc_pro2}(c) uses \cite{atheygrf} generalized random forests methodology to estimate person specific treatment effects and plots the distribution of those treatment effects.\footnote{\cite{atheygrf} use random forest of honest causal trees to estimate personalized treatment effects.
-The trees are such that at each leave (partition determined by covariates) it unbiasedly estimates a treatment effect using treatment and control observations in that leave.
+The trees are such that at each leaf (partition determined by covariates) it unbiasedly estimates a treatment effect using treatment and control observations in that leaf.
 The optimal partition of leaves is that which minimizes expected mean squared error of treatment effects predictions out-of-sample.
 The tree is honest because it uses one sample to build the tree and another one to estimate treatment effects within that tree.
-After the optimal tree is build, each person in each leave is assigned the treatment effect of that leave.
-\cite{atheygrf} show that their treatment effects are asymptotically normal, which allows us to construct confidence intervals for our treatment estimate in each leave.} We find that virtually all (\hlgr{94\%}) of clients experienced financial cost savings in the fee-forcing group compared to the status-quo group.
+After the optimal tree is build, each person in each leaf is assigned the treatment effect of that leaf.
+\cite{atheygrf} show that their treatment effects are asymptotically normal, which allows us to construct confidence intervals for our treatment estimate in each leaf.
+We use command \texttt{causal\_forest} of the \texttt{grf} library in $R$.
+The parameters used were:
+
+\scriptsize{\textit{causal\_forest(
+  X, 
+  Y, 
+  W, 
+  Y.hat = NULL, 
+  W.hat = NULL, 
+  num.trees = 2000, 
+  sample.weights = NULL, 
+  clusters = NULL, 
+  equalize.cluster.weights = FALSE, 
+  sample.fraction = 0.5, 
+  mtry = min(ceiling(sqrt(ncol(X)) + 20),ncol(X)), 
+  min.node.size = 5, 
+  honesty = TRUE, 
+  honesty.fraction = 0.5, 
+  honesty.prune.leaves = TRUE, 
+  alpha = 0.05, 
+  imbalance.penalty = 0, 
+  stabilize.splits = TRUE, 
+  ci.group.size = 2, 
+  tune.parameters = "none", 
+  tune.num.trees = 200, 
+  tune.num.reps = 50, 
+  tune.num.draws = 1000, 
+  compute.oob.predictions = TRUE, 
+  orthog.boosting = FALSE, 
+  num.threads = NULL
+)}}} We find that virtually all (90\%) of clients experienced financial cost savings in the fee-forcing group compared to the status-quo group.
 Figure \ref{HTE_fee_forcing}(a) in the Appendix shows that the (causal) cost savings are largest for the more economically vulnerable, %that report at baseline that they have problems paying for services like water, electricity and rent,
@@
 \vspace{.2in}
-\noindent \textbf{Pawn Recovery.} Figure \ref{fc_pro2}(d) plots estimated treatment effects of the fee-forcing commitment contract with the dependent variable being an indicator of losing the pawn in less than \hlgr{230} days.
-The leftmost coefficient shows that the fee-forcing commitment contract increases the likelihood of recovering the pawn by \hlgr{11pp} (\hlgr{25\%} of mean recovery).
+\noindent \textbf{Pawn Recovery.} Figure \ref{fc_pro2}(d) plots estimated treatment effects of the fee-forcing commitment contract with the dependent variable being an indicator of losing the pawn in less than 230 days.
+The leftmost coefficient shows that the fee-forcing commitment contract increases the likelihood of recovering the pawn by 11pp (25.8\% of mean recovery).
 This is a large effect.
@@
 The 4th coefficient from left to right conditions on those who paid a positive amount (in treatment and control).
-Although this is potentially an endogenous population, Table \ref{mechanisms} showed that there is no treatment effect on Pay$>$0.
+Although this is potentially an endogenous population, Table \ref{mechanisms} showed that there is no treatment effect on Pay$>0$.
 We were interested in this population to show that the effect is there for those who are serious about recovering their pawn.
@@
 In effect comparing this subset in treatment vs all of the control group\footnote{Results are similar if we condition in the control group on those who would have paid a fee given current behavior.
-Again we acknowledge these is an endogenous control and that the estimate is not a causal effect.\hl{ISAAC, puedes checar que sale asi si corrieras esta nueva regression?}}.
+Again we acknowledge these is an endogenous control and that the estimate is not a causal effect.}.
 We find even those that paid a fee in the fee-forcing contract end up paying a smaller financial cost that those in the status-quo contract.\footnote{This is not an experimental comparison as who pays a fee in the treatment group is a selected sample, but we found this relationship interesting nonetheless.} Figure \ref{fc_pro2}(c) shows that the increase in pawn recovery is robust to defining recovery using the first 120 days of the contract, or restricting to those paying a positive amount towards pawn recovery.
@@
 Figure \ref{reincidence} presents results of equation (\ref{basic_reg}) where the dependent variable is a dummy for the client to be a repeat costumer.
-We define a client in our experiment as a repeat costumer if, after experiencing at least 75 days of the respective treatment arm, she came back and pawned \hlgr{a different piece}.\footnote{Results are robust to using other number of days besides 75.}  The left most coefficient shows that the causal effect of the fee-forcing contract on repeat pawning is an increase of 5pp in the probability of being a repeat costumer, this is \hlgr{20\%} on a mean re-incidence in the control group, with respect to those that got the status-quo contract.
-This is not explained by clients recovering their first pawn with higher probability in the fee-forcing contract and re-pawning this same one since we make sure it is another piece (besides only \hl{XX\%} recover their piece in the fist 75 days in the fee forcing contract).
-The second coefficient restricts to the population who had larger (treatment effect) financial cost savings in their first pawn, and shows that the effect is twice as large for them.\footnote{\hl{ISAAC, podrias quitar de esta Figure 5 los coeficientes ``| rec.'' y el de ``fnr'' de TODA esta Figura 5?
-Pon como el 2do coeficiente que dice ``| >50th perc.'', esos si dejalos}} That is, those that benefit more from the fee-forcing contract are much more likely to repeat.
+We define a client in our experiment as a repeat costumer if, after experiencing at least 75 days of the respective treatment arm, she came back and pawned a different piece.\footnote{Results are robust to using other number of days besides 75.}  The left most coefficient shows that the causal effect of the fee-forcing contract on repeat pawning is an increase of 5pp in the probability of being a repeat costumer, this is 55\% on a mean re-incidence in the control group, with respect to those that got the status-quo contract.
+This is not explained by clients recovering their first pawn with higher probability in the fee-forcing contract and re-pawning this same one since we make sure it is another piece (besides only 37\% recover their piece in the fist 75 days in the fee forcing contract).
+The second coefficient restricts to the population who had larger (treatment effect) financial cost savings in their first pawn, and shows that the effect is twice as large for them.
+That is, those that benefit more from the fee-forcing contract are much more likely to repeat.
 %The coefficient on repeat pawning is just as big when we focus only 2nd pawns happening after the first was recovered (third coefficient ``fnr'').
@@
 We also implemented an exit survey which clients filled when recovering their piece.
-Unfortunately it had low response rates (\hlgr{7\%}), and we take its results with a grain of salt.
-In this survey \hlgr{63\%} said they liked the frequent payment contract more than the status-quo one, and that is allow them avoid unnecessary expenses.
+Unfortunately it had low response rates (7\%), and we take its results with a grain of salt.
+In this survey 63\% said they liked the frequent payment contract more than the status-quo one, and that is allow them avoid unnecessary expenses.
 
@@
 
-\subsection{Demand for the fee-forcing commitment contract}
+\subsection{Demand for the fee-forcing commitment contract} \label{sec:demand}
 
@@
 If they for example face large and frequent income shocks which make it hard to repay monthly.\footnote{We don't observe income shocks in our data, making is hard to quantify how important they are.
-\hlgr{90\%} of those in the fee-forcing arm incurred a fee, which suggests that shocks are not uncommon (or clients inattentive).} Note that income shocks that affect the ability to pay the entire loan are a worry for both the fee-forcing contract and the status quo one, and should not make one contract more favorable than the other.
+90\% of those in the fee-forcing arm incurred a fee, which suggests that shocks are not uncommon (or clients inattentive).} Below we focus on some explanations of low demand, while Section \ref{model} seeks for theories that can explain all the findings, and reaches the conclusion that the present bias with naivete parsimoniously explains more results.
+
+\subsubsection{Behavioral economics explanations}
+
+The leading behavioral explanation in the literature for low demand for commitment is present biased preferences with naivete (e.g.
+\cite{Rabin2018}, \cite{John}, \cite{Laibson2018})  \cite{Laibson2015} shows that the lost flexibility resulting from a commitment contract can limit take-up especially severely when agents are naive about their self control problem.
+In our context if consumers are naive about their present bias, they would plan to save more (or spend less) than what they actually end up saving, thus making it be harder to recover their pawn.
+This under-saving will be mitigated in the fee forcing contract since the fee makes them save money and pay part of the loan periodically.
+Another behavioral explanation is that clients may underestimate the likelihood and severity of negative income shocks.
+Both of this explanations predict that clients will be overconfident about their likelihood of pawn recovery.
+Recall that in the control group the client's subjective probability of recovery is on average 93\%, while actual recovery is just 44\%.
+A further piece of evidence consistent with underestimating negative income shocks is that a large number of people (31\%) in the control group pay a positive amount toward pawn recovery but end up losing their pawn anyway.
+
+So, overconfidence of recovering the pawn is implied by both present bias preferences with naivete and upward bias in their income expectations.
+But does overconfidence actually predict low demand for commitment empirically?
+It does.
+We define as overconfidence as the reported subjective probability of recovery minus the predicted probability based on the client's characteristics, $P^s_i-\widehat{P_i(X_i)}$.\footnote{We predict $\widehat{P_i(X_i)}$ in two steps.
+In step one we use LASSO with with cross validation to tune the regularization parameter to select the most predictive variables.
+In the second step we estimate $\widehat{P_i(X_i)}$ using those variables in a logit model.
+The LASSO selected variables were type of pawn, female, age, has pawned before, has savings, participates in rotating savings, often feels tempted to change plans, would like to have a reminder to pay, and an economic vulnerability index.}  Table \ref{oc_reg} regresses a take-up dummy against an indicator $OC_i:=\mathbbm{1}(P^s_i-\widehat{P_i(X_i)}>0)$ for overconfidence and controls.
+Controls include branch and day of the week dummies, and additionally schooling, whether the client does a monthly budget plan, and a measure of intertemporal preference reversal analogous to that of \cite{Ashraf} as controls.\footnote{We find that 15\% of clients are classified as present biased using this measure of preference reversal.
+This level is similar to the number \cite{Ashraf} find.} Column 2 shows that in the choice-fee arm, being overconfident decreases the likelihood of demanding commitment by 16 percentage points, and column 4 shows that this is robust to including other controls.
+One interpretation of this result is that the overconfident think they do not need commitment, especially if that commitment may have the cost of fees.
+Columns 1 and 3 will be explained in Section \ref{promises}.
+Column 5 and 6 use as a dependent variable the estimated heterogeneous treatment effects of the fee-forcing contract vs the status quo one.
+They show that the overconfident benefit \textit{more} from the commitment contract, with 20\% (=\$24/\$121) more savings.
+
+\subsubsection{Neoclassical Alternatives}
 
 \vspace{.1in}
-\noindent \textbf{Lost flexibility.} While we cannot rule out that income shocks combined with lost flexibility of the contract explain the low demand, we think it is unlikely.
-Note that fees for late payment are not that high.
-In an average loan of 2,000 pesos the monthly payment is close to 700 pesos, and a fee of 2\% of that is 14 pesos (less than \$1 dollar).
-This is about \hlgr{1\%} of monthly per capita income of the first 3 deciles of Mexican \hl{household's} income distribution.
-%This compares favorably to the \hlgr{\$11.6 + \$62.3)} pesos transportation / transaction cost of one.
-So even if households experience a negative income shock and cannot pay that month, the cost of paying the fee does not seem too burdensome, especially when compared to the savings they are experiencing.
-To make this more concrete we did this simple back-of-the envelope exercise to compare cost savings against fees.
-We pretended that all clients in the fee forcing contract incurred in \textit{all} potential fees, and added these fees to their financial cost.
-We then re-estimated the quantile treatment effects of Figure \ref{fc_pro2}(b) with this inflated financial cost (keeping all else constant\footnote{Of course behavior may not be constant, but we believe this is a reasonable fist approximation.
-%It could be that having this small fee added to the balance discourages them to pay or makes it harder to pay back the loan.
-But the contrary may also happen, with the fee making them more determined to pay early.
-We would need a structural model of client behavior to estimate a full counterfactual.
-We suspect that such small fees would not generate large changes in behavior in a simple neoclassical model.
-}). \hl{We find that even in this extreme scenario, tilted against the fee-forcing contract, all the estimated effects still imply cost savings from the fee-forcing contract.}
-
-\vspace{.1in}
-\noindent \textbf{Risk aversion.} We do not have measures of risk aversion in our necessarily short survey, which makes it very hard to assess this hypothesis.
-To have a benchmark we implement a very simple calibration exercise in two steps.
+\noindent \textbf{Risk aversion.} We do not have measures of risk aversion in our necessarily short survey, which makes it hard to assess the hypothesis that risk aversion limits take-up of the fee-forcing contract.
+One way to proceed is to take the empirical distribution of financing cost ---$F_{fee}(FC)$--- as one the client would have faced had she chosen the the fee-commitment contract.
+We could then ask what would risk aversion have to be in order to justify the client choosing the fee-commitment contract distribution of costs over the distribution associated with the status quo contract, $F_{sq}(FC)$.
+We can then assess if the risk aversion needed would be reasonable or too high.
+This exercise of course assumes --as it is common in economics-- that clients know the distribution of financial cost, that it is common across consumers (although this can be relaxed), and that this cost distribution is the only difference among contracts.
+Fortunately for us, since one distribution first-order-stochastically dominates the other we do not need to calibrate a specific utility function or use a parametric distribution function in order to rank them in terms of expected utility.
+We use the fact that if $u(FC)$ is decreasing in $FC$ and $F_{fee}(FC) \geq F_{sq}(FC)$ for all $FC$, then $E_{fee}[u(FC)] \geq E_{sq}[u(FC)]$.
+That is any expected utility maximizer who dislikes paying higher financing cost, regardless of the concavity of his utility function, will prefer the fee-commitment distribution of financial cost.
+Figure \ref{ecdf_fc} in the Appendix shows that indeed $F_{fee}(FC) \geq F_{sq}(FC)$.
+Moreover, Table \ref{stochastic_dominance} shows that this holds also for an overwhelming majority of sub-populations.
+
+%To have a benchmark we implement a very simple calibration exercise in two steps.
 First, we fit a Weibull distribution to the distribution of financing cost, were the scale and shape parameters depend on client's and loan observable characteristics.
@@
 It turns out that it holds for risk aversion levels that are too high to be believable.
-That is, with our calibration, it seems unlikely that risk aversion is reducing demand for the fee-forcing contract.\footnote{This of course assumes that clients know the distribution of financial cost outcomes, which is all we can do with our data.}
+That is, with our calibration, it seems unlikely that risk aversion is reducing demand for the fee-forcing contract.
 
 \vspace{.1in}
-\noindent \textbf{Present bias with naivete /  overconfidence in recovery.} The leading behavioral explanation for low demand for commitment which would is present biased preferences with naivete.
-Of course these may interact with the neoclassical explanations above.
-In fact \cite{Laibson2015} shows that the lost flexibility resulting from a commitment contract can limit take-up specially severely when agents are naive about their self control, even though commitment could be welfare improving for the naive.
-There is some evidence supporting that individuals have incorrect expectations about their recovery probabilities.
-The subjective probability of recovery is close to 93\% on average, while the actual average is 44\% for the pawns in the control group.
-\hl{It turns empirically that overconfidence (OC), defined as the reported subjective probability of recovery minus the predicted probability, $P^s_i-\widehat{P_i(X_i)}$, is a significant predictor of low take up.}.
-Using a definition of intertemporal preference reversal analogous to that if \cite{Ashraf} we find that \hlgr{15\%} of clients are classified as present biased (\hl{similar to the number they find} but small to explain low take up), and that they have lower take-up.
-Another indication of overconfidence is the large number of people that pay a positive amount toward recovery but end up losing their pawn anyway.
-Figure \ref{proxy_naive}(c) showed that on average clients that lost their pawn paid \hlgr{34\%} of the value their loan.
+\noindent \textbf{Lost flexibility.} A second neoclassical explanation for low take up is lost flexibility.
+That is, the fee-commitment contract may provide too much commitment which is costly both, (a) because the client may be forced to incur in late payment fees if he experiences a negative income shock, and also because (b) he may be unable to recover the pawn and his pre-payments.\footnote{Note that income shocks that affect the ability to pay the entire loan are a worry for both the fee-forcing contract and the status quo one, and should not make one contract more favorable than the other.} While we cannot rule out that income shocks combined with lost flexibility of the contract explain the low demand, we think it is unlikely.
+First, we showed above clients report a subjective probability of recovery of 93\% on average, which suggests they are not too worried about income shocks.
+Second, the fear of incurring fees is quantitatively not enough of a concern when compared to the savings they are experiencing.
+%Note that fees for late payment are not that high.
+In an average loan of 2,000 pesos the monthly payment is close to 700 pesos, and a fee of 2\% of that is 14 pesos (less than \$1 dollar).
+This is about \hlgr{1\%} of monthly per capita income of the first 3 deciles of Mexican \hl{household's} income distribution.
+%This compares favorably to the \hlgr{\$11.6 + \$62.3)} pesos transportation / transaction cost of one.
+To make this concrete we calculated what the financing cost of the fee-commitment contract would be if all its clients incurred in \textit{all} potential fees (while keeping payment profiles and pawn recovery constant), thus artificially inflating the cost.
+We then re-estimated the quantile treatment effects analogous to Figure \ref{fc_pro2}(b) with this inflated financial cost.
+%\footnote{Of course behavior may not be constant, but we believe this is a reasonable fist approximation.
+%It could be that having this small fee added to the balance discourages them to pay or makes it harder to pay back the loan.
+But the contrary may also happen, with the fee making them more determined to pay early.
+We would need a structural model of client behavior to estimate a full counterfactual.
+We suspect that such small fees would not generate large changes in behavior in a simple neoclassical model.}).
+Figure \ref{fc_allfee} presents the results.
+We find that even in this extreme scenario, tilted against the fee-forcing contract, the estimated effect still implies cost savings from the fee-forcing contract at the mean, 25$^{th}$, 50$^{th}$, and 75$^{th}$ percentiles.
+Note that the differences in financing cost already takes into account the fact that clients in the fee forcing contract sink more pre-payments than those in the status quo contract, and that those prepayments are lost if the loan is not fully paid back.
+Although these arguments are not definitive, they suggest that low demand for commitment may be driven by be more than the anticipation of lost flexibility.
 
 \vspace{.1in}
-\noindent \textbf{Predictors of take up.} Using \hl{random forests} we can predict who takes up the fee-forcing contract with \hl{87}\% accuracy out of sample.\footnote{Correcting for the fact that most chose the status-quo contract using the method of \hl{SMOTE}, \cite{smote} we find an accuracy rate of \hl{XXX\%, ISAAC}.} Which suggests that choice among contracts is not purely random.
-Figure \ref{interactions_takeup} in the Appendix shows that the more educated, those that report that their family typically asks for money, those that make a monthly budget of expenses, and those that ask for a remainder of their due payments (and marginally those we classify as present-biased) are more likely to chose the fee-commitment contract if given the choice.
-The opposite holds for clients that are more economically vulnerable (can barely pay for food, electricity, etc) and those that report being more stressed.
+\noindent \textbf{High time discounting.} In the summary statistics section we mentioned that clients in the status quo contract tend to wait until the last moment to pay to recover their pawns.
+Even among those that recover their pawn, only 20\% pay before the 90$^{th}$ day.
+Table \ref{mechanisms} showed that clients assigned to the fee-forcing contract front load their payments, starting their first payment earlier and finishing to pay earlier too.
+However, clients may dislike front loading payments if their discount rate is high.
+They may be willing to trade off a higher probability of losing their pawn for more \textit{back} loaded payments.
+This would explain both, why default rates are high and why demand for the fee-commitment contract is low.
+
+What would discount rates have to be in order to offset the reductions in financial cost effects we observe?
+We can calculate this number by looping across a grid of discount rates and reestimating equation \ref{basic_reg} with a financial cost dependent variable that uses the respective discount rate in the grid, and searching for the discount rate that makes $\beta$ equal zero.
+We do this and obtain that the discount rate that rationalizes a zero effect is 8,190 percent per year.
+We find this discount rate implausibly high even for this credit constrained population, and seriously casting doubt on high discount rates as explanation for low demand for commitment.%\footnote{In the baseline survey we give respondents a hypothetical choice between $100$ pesos tomorrow or $150$ pesos in one month (an implicit yearly interest rate of \hl{12,800\%}) and only 30\% chose the later one.}
 
@@
 The hollow circles in Figure \ref{fc_pro4}(show average effects for the different definitions of financial cost analogous to the ones described above.
-Figure \ref{fc_pro4}(b) shows further that the null effect happens for the 15$^{th}$, 25$^{th}$, 50$^{th}$ 75$^{th}$, and 85$^{th}$ percentiles.\footnote{The few that selected the fee-commitment contract (the solid black squares) do enjoy cost savings of 939 pesos, which compares favorably to the 339 pesos in the fee-forcing arm (as a fraction of the loan the numbers are \hl{XXX} and \hl{XXX}), but this combines the selection and treatment effects.
+Figure \ref{fc_pro4}(b) shows further that the null effect happens for the 15$^{th}$, 25$^{th}$, 50$^{th}$ 75$^{th}$, and 85$^{th}$ percentiles.\footnote{The few that selected the fee-commitment contract (the solid black squares) do enjoy cost savings of 1005 pesos, which compares favorably to the 304 pesos in the fee-forcing arm (as a fraction of the loan the numbers are 41.5\% and 12.5\%), but this combines the selection and treatment effects.
 We cannot reject the that the ``effect'' on pawn recovery is of the same size for the fee-forcing arm and for those that selected into fee-forcing.} %Figure \ref{heterogeneous_te_4} plots the distribution of treatment effects and finds that the distribution offering choice actually \textit{increased} financial cost and default for about half of clients compared to being assigned the status-quo contract.
@@
 In this section we are concerned with lines in red color.
-When $z=0$, we calculate that about 83\% of clients in the fee-choice group chose contracts that induced \textit{higher} financial cost (95\% confidence interval [\hlgr{40},\hlgr{93}]).
-Most mistakes are failures to choose the fee-commitment contract (\hlgr{95\%}), while only \hlgr{7\%} of those who chose the fee-commitment contract would have been better in the status-quo one.
-The average mistake in pesos is \hlgr{\$352} (95\% confidence interval [\hlgr{170},\hlgr{534}]).
-Figure \ref{choose_wrong}(b) separates the analysis for those we classify as overconfident about recovering their pawn (\hl{XXX of them} vs the rest.
-It shows that the there are about \hl{20 percentage points} more mistakes in the overconfident population when $z=0$.
+When $z=0$, we calculate that about 80\% of clients in the fee-choice group chose contracts that induced \textit{higher} financial cost (95\% confidence interval [36,95]).
+Most mistakes are failures to choose the fee-commitment contract (92\%), while only 8\% of those who chose the fee-commitment contract would have been better in the status-quo one.
+The average mistake in pesos is \$238 (95\% confidence interval [131,427]).
+Figure \ref{choose_wrong}(b) separates the analysis for those we classify as overconfident about recovering their pawn (96\% of them) vs the rest.
+It shows that there are about 14 percentage points more mistakes in the overconfident population when $z=0$.
 
@@
 private paternalism) may be welfare increasing for the overwhelming majority of clients.
-Figure \ref{choose_wrong}(c) calculates what fraction of clients would be made better off if we forced them to the fee-commitment contract: \hl{96\%} when $z=0$, and they would on average have savings of \hl{280} pesos.
+Figure \ref{choose_wrong}(c) calculates what fraction of clients would be made better off if we forced them to the fee-commitment contract: 92\% when $z=0$, and they would on average have savings of 232 pesos.
+This conclusion is in line with a recent paper by \cite{John}.
+In a savings context, she finds that when commitment in on the menu a majority of subjects wrongly choose to little commitment.
+She concludes this by observing high levels of default even with late payment fees, whereas we work directly with estimated treatment effects.
 
@@
 We then use this model to predict the counterfactual probability of client with characteristics $x_i$ choosing the fee-commitment contract in the no choice-arms if she would have been given the choice, what we call $\widehat{P(x_i)}$.
-Since our model for has a good out-of-sample fit with an \hl{adjusted} AUC of \hl{0.77} and an \hl{adjusted} accuracy rate of \hl{87\%}, we think we are not introducing too much noise by this extrapolation.
+Since our model for has a good out-of-sample fit with an out-of-sample AUC of 0.85 and an accuracy rate of 85\%, we think we are not introducing too much noise by this extrapolation.
 Second, armed with this prediction in the no-choice arms, we can ask the following: is it true that people with larger fee-forcing contract treatment effects (i.e.
@@
 
+\section{Viewing the results through a simple model} \label{model}
+
+This section uses a model to interpret our empirical results.
+The model is stylized but incorporates important features of our context.
+First, it allows for negative income shocks which we think are prevalent in this population (that's why they pawn in the first place)\footnote{71\% say they need the money for an emergency.}.
+The shock generates a cost of committing to monthly payments and could potentially be a reason for low take up.
+Second, it features clients with present biased time preferences and allows for naivete about them.
+As we discuss below these two features parsimoniously explain several facts about the context ---e.g.
+overconfidence in recovering the pawn, and large inefficient default---  and about the results ---e.g.
+forcing commitment seems to help, and that there is also some (although small) demand for commitment at no benefit for neoclassical consumers.
+Third, it incorporates the fact that the pawned piece is more valuable than the loan.
+Fourth, it allows for a simple way to model commitment afforded by late payment fees.
+Nonetheless, the model abstracts from several details of the context.
+Even with these abstraction it allows us to explain our six main results listed in Section \ref{explanations_recap} below.
+
+\subsection{A simple model} \label{model}
+
+We use the model of \cite{John} and refer the reader to that paper for more detail, justification of assumptions and some of the proofs.
+The model has three periods and linear utility.\footnote{This does not map perfectly to our 3 period contract, but it is enough to generate the results we need.} Period $t=0$ is a planning period where the client is either allocated to the status quo, the fee-forcing contract, or a choice between the two.
+In period 1 the client receives her income $y_1=1$, or gets zero with probability $\lambda$.
+She can consume ($c_1$) or save ($s_1$) that income.
+In period 2 the client gets her savings from period 1, and again receives income of either $y_2=1$, or zero with probability $\lambda$.
+In this last period, she decides whether to use income and savings for consumption $c_2$ and/or for paying back the loan of size $p \in(1,2)$ to recover the pawned piece valued at $b>p$.
+In this simple model we will impose a penalty fee $F>0$ in $t=1$ for the fee-commitment contract if the month's payment is not done.
+In period $t=0$ she evaluates her welfare as $E[c_1+c_2]$, were for simplicity we have set the time discount to one.
+We also assume the interest rate is one.
+We introduce present bias preferences by assuming the following utility function $U_t=c_t+\beta \: \sum_{k=t+1}^{2} E[c_k]$, with $\beta<1$ indicating present bias.
+A naive client perceives she is not so present biased and instead of $\beta$ uses $\hat{\beta} \in (\beta,1]$.
+
+Note that under these assumptions it is efficient at $t=0$ to take actions to recover the loan.
+Because $b>1$, paying back the loan requires that there is no negative shock in any period and that $s_1>0$, and because $\beta<1$ at $t=1$ the client will not send savings in excess of what is needed to recover the loan $s_1=p-1$.
+
+\vspace{.1in}
+\noindent \textbf{Result 1: Present bias consumers default more.} Under the status-quo contract, absent shock realizations, present biased clients (sophisticated or naive) with $\beta<\beta_{SQ}<1$ will lose their pawn, while clients with no present bias will not.
+Viewed from $t=0$ losing the pawns when there are no shocks is inefficient as $b>p$.\footnote{$\beta_{SQ}=\frac{p-1}{\lambda(p-1)+(1-\lambda)(b-1)}$.
+See Proposition 1 in \cite{John}.}
+
+\vspace{.1in}
+\noindent \textbf{Result 2: Forcing present-biased clients into the fee-commitment contract reduces default.} Imposing a fee $F>0$ for late payments weakly decreases default (for present biased clients only).
+It strictly decreases default if $F>F_{min}(\beta):=(p-1)-\beta[\lambda(p-1)+(1-\lambda)(b-1)]$.
+The larger the present bias the larger the $F$ required to induce pawn recovery.\footnote{The incentive compatibility constraint to generate savings to recover the pawn can be written as $1-(p-1)+\beta[\lambda(p-1)+(1-\lambda)(b-1)] \geq 1-F+\beta(1-\lambda)$.}
+
+\vspace{.1in}
+\noindent \textbf{Result 3: Demand for commitment.} Given $F>0$, (a) Neoclassical clients will never demand commitment.
+(b) Present-biased sophisticated clients will prefer the fee-forcing contract over the status quo contract $\iff$  $\lambda \: F<(1-\lambda)^2(b-p)$ and $F>F_{min}(\beta)$, that is $\iff$  $\beta \in [\beta_{min},\beta_{SQ}]$.\footnote{$\beta_{SQ}$ was determined in Result 1.
+$\beta_{min}$ is such that $F=F_{min}(\beta_{min})$.} (c) Analogously, naive clients will demand commitment $\iff$ $\hat{\beta} \in [\widehat{\beta_{min}},\beta_{SQ}]$, where $\widehat{\beta_{min}}<\beta_{min}$.
+So strongly naive clients will on the one hand demand more commitment than sophisticated clients since they believe (incorrectly) that a smaller fee will motivate them to pay.
+On the other hand they may demand less commitment since they think they can save and pay on their own.
+Whether they demand more or less than sophisticated clients depends on the empirical distribution of $\beta$ and $\hat{\beta}$.
+
+\vspace{.1in}
+\noindent \textbf{Result 4: Overconfidence.} Only naive clients will be overconfident about the probability of recovery.
+This will be true whether they have the status quo or the fee-forcing contract.
+Overconfidence is increasing in $\hat{\beta}$.
+
+\vspace{.1in}
+\noindent \textbf{Result 5: Welfare.} (a) Neoclassical consumers' welfare strictly decreases when we force clients into the fee-commitment contract instead of the status quo contract, and does not change when we offer a choice between them.
+(b) The welfare of sophisticated present biased consumers weakly increases when we give them choice, and it strictly increases  $\iff$  $\beta \in [\beta_{min},\beta_{SQ}]$, that is when they choose it themselves.
+Forcing them into the fee-commitment contract increases welfare $\iff$  $\beta \in [\beta_{min},\beta_{SQ}]$, otherwise it strictly decreases.
+So choice is better than forcing for sophisticates.
+(c) Forcing can be welfare improving for the naive.
+Indeed if $\hat{\beta}>\beta_{SQ}>\beta$ then forcing the fee-commitment contract increases welfare, and if $\hat{\beta} \in (\widehat{\beta_{min}},\beta_{min})$ then forcing the status quo contract increases welfare.\footnote{This result is different from that in \cite{John}.
+His context has individuals choosing the size of the fee.
+In that context naive clients will always chose the wrong fee size and default, therefore choice is always decreasing for the.
+In our context $F$ is fixed at 2\% of the balance due, and this implies that choice could be welfare improving for some naifs.}
+
+\vspace{.1in}
+\noindent \textbf{Result 6: Welfare and ex-post observed behavior.} If for client $i$ the fee-forcing contract causes higher pawn recovery, then we know the fee $F$ made her IC constraint binding, and therefore that $\hat{\beta_i}>\widehat{\beta_{min}}$.
+If in addition if it was the case that \hl{$\beta<\beta_{SQ}$}\footnote{\hl{Isaac, aqui tengo dos pregutas: (1) si es $\beta$ y no $\hat{\beta}$ verdad?
+(2) Para que una persona naive empeñe en el status quo tiene que ser que cree que va a recuperar no?
+Es decir tiene que ser $\hat{\beta}>\beta_{SQ}$ correcto?}} then the fee-forcing contract would have increased welfare for the naive.
+That is, our finding that the fee-forcing contract increases pawn recovery is a sign of higher welfare.
+
+\subsection{Interpretation}
+
+The model of \cite{John} is very parsimonious but powerful.\footnote{The model is sufficiently stylized that we think we would not gain much from estimating it.
+Furthermore we have no data on income shocks which figure prominently in the model.
+\cite{Ted} and \cite{Aprajit} are two very recent models that combine a field experiment with commitment contracts and estimation of present bias parameters.} First, it can explain why clients are overconfident in our data, namely by virtue of naivete about present bias.
+Under the model naivete is necessary to explain this.
+Second, it can also explain why the fee forcing contract induces lower default, but not for everyone: namely that it makes the IC constraint for the present biased binding while it was not binding in the status quo contract.
+Third, it can also explain why there is low demand for commitment even if it seems to improve welfare: namely that there is a small share of neoclassical and sophisticated clients, and at the same time naifs have  $\hat{\beta}>\beta_{SQ}$ and therefore think they can save on their own.\footnote{By Result 6 we can eliminate $F<F_{min}(\widehat{\beta}$) as an explanation.}.
+Fourth, it can explain why clients exposed to the fee-forcing contract are more likely to come back, namely that $\hat{\beta_i}>\beta_{SQ}>\beta$ and so their welfare increased as a result of being forced into the fee-commitment contract, and they may realize this.
+
+One could also easily introduce overconfidence in income shocks with $\widehat{\lambda} <\lambda$.
+This would leave default unchanged in both the status quo and the fee forcing contract.
+%since $F_{min}(\beta,\widehat{\lambda})<F_{min}(\beta,\lambda)$.
+The effect on demand for commitment is uncertain since on the one hand it decreases $\beta_{SQ}$ decreasing demand, but on the other a smaller $F$ is needed to make the IC binding, making commitment less costly.
+
+\subsection{Other potential explanations: recap} \label{explanations_recap}
+
+There may be other interpretation of the empirical findings. But the bar is high. An alternative explanation will need to explain the facts below:
+
+\begin{enumerate}
+\itemsep0em 
+\item Overconfidence about pawn recovery.
+\item High (although ex-post inefficient) default in status quo contract.
+\item Small demand for commitment...
+\item ...but positive demand for commitment.
+\item Forcing commitment saves money.
+\item Forcing commitment makes clients more likely to come back.
+\end{enumerate}
+
+\vspace{.1in}
+\noindent \textbf{Alternative 1: Strong prevalence of income shocks.} This could explain low demand for commitment (3) and (2), but not why forcing helps (5) and (6), nor why there is overconfidence (1), or why they come to pawn in the first place, try to pay back and then default (2).
+
+\vspace{.1in}
+\noindent \textbf{Alternative 2: High time discounting}.
+This could not explain (1) nor (6) nor (4).
+It could qualitatively explain (3).
+But as we say in section \ref{sec:demand} it cannot quantitatively explain (5) and (3) unless the discount rate is unbelievably high.
+
+\vspace{.1in}
+\noindent \textbf{Alternative 3: Risk aversion.} We already discussed and rejected risk aversion in section \ref{sec:demand}, although using strong assumptions in the process.
+We think this could still play a role and should be investigated in future research.\footnote{For instance by  providing insurance or by measuring risk aversion and using it to predict take up.}
+
+\vspace{.1in}
+\noindent \textbf{Alternative 4: Misunderstanding the contracts.}\footnote{This is a potential criticism of any paper offering choice, and one that is non-falsifiable if the critic has free reign to propose how the contracts are perceived in the subject's mind.} We were very aware of this and in the implementation a very strong effort was made for consumers to understand the contracts (see subsection \ref{implementation}).
+Note however that while clients making random mistakes could explain why 10\% demand commitment ---i.e.
+(3) and (4)--- they would not explain the rest of facts, nor why the promise-commitment (see below) had more take up that the fee-commitment, or why those with present bias and those that want a reminder to pay are more likely to make the ``error'' to demand commitment.\footnote{See Figure \ref{interactions_takeup} and Table \ref{Table_compliance}}
+
+\vspace{.1in}
+\noindent \textbf{Alternative 5: Forgetting to pay.} Frequent payments may act as a reminder to save and recover the pawn.
+This would try to explain (2) by appealing to people forgetting to pay, and (5), (6) and (4) by appealing to frequent payment acting as reminders.
+It would not explain (1) or (3) which are critical in the paper.
+However even for (2) it seems to us a stretch to explain people losing a valuable pawn by forgetting to pay.
+
+\vspace{.1in}
+\noindent \textbf{Alternative 6: Learning that they are more present biased than they thought.} This is essentially the same as our proposed explanation (i.e.
+not an alternative) with the additional prediction that more people will demand commitment if they just experienced it, an specially appealing one in light of finding (6).
+We are sympathetic to the learning hypothesis and in fact it is \cite{Alcohol}'s main conjecture about why he finds strong demand for commitment while most other studies don't.\footnote{Close to ninety percent of our subjects claim to have pawned before.
+We find that experience does not predict positive take up in our sample correlationally.} To test it we would ideally need to give choice to a group of people that randomly experienced the fee-commitment vs those that did not, and test if the former demand it more.\footnote{\hl{Isaac, podemos volver a tratar esto?
+Hace como 1 anio no nos salio pero quiero volver a tratar.}} Unfortunately we did not do this experiment and we have very limited data to try it: \hl{210 (6\%)} clients were given a choice in a second pawns in our experiment after being randomly assigned to the status quo or fee-forcing contract.
+
 \section{The effect of promises} \label{promises}
@@
 \vspace{.2in}
-The evidence presented in this section contrasts sharply with the evidence in laboratory experiments where people choosing to promise has a large effect on behavior and were people keep their promises.
+\noindent The evidence presented in this section contrasts sharply with the evidence in laboratory experiments where people choosing to promise has a large effect on behavior and were people keep their promises.
 While clients are more enthusiastic about the promise-commitment contract than the fee-commitment one in the sense of tripling take-up, the promise contract provides no commitment.
+Results for the promise arms are consistent with \cite{Ted} and \cite{John} who find that people are likely to demand commitment when the commitment is too week to have beneficial effects.
 
@@
 In a pawnshop borrowing context, we studied whether forcing borrowers into frequent payment commitment contracts reduces their borrowing costs, compared to a contract that does not provide commitment to pay monthly.
-Even though we are charging them fees, their borrowing cost are actually reduced by 11\%, and they recover their pawn with 23\% higher likelihood.
-Moreover they themselves seem to like this contract, as they are 20\% more likely to come back and pawn again when they get it.
+Even though we are charging them fees, their borrowing cost are actually reduced by 9.5\%, and they recover their pawn with 25.8\% higher likelihood.
+Moreover they themselves seem to like this contract, as they are 55\% more likely to come back and pawn again when they get it.
 That is, commitment matters and it seems beneficial.
@@
 
+\newpage
 \singlespacing
@@
 All regressions include fixed effects for branch, day of week fixed effects, number of pawns at the time of pawning this particular one, number of different treatment arms experienced before pawning this particular one.
-$R^2$ are not reported, they were less than 0.04 for all but the last column \hl{which had $R^2$'s close to 0.6}.
+$R^2$ are not reported, they were less than 0.04 for all but the last column which had $R^2$'s close to 0.6.
 The last row shows the mean of the dependent variable for the control group.
 Dependent variables are as follows: Column (1) measures the number of days elapsed from the pawning date to the first payment done.
-Column (2) records the number of payments done \hl{within 150 days} of the pawn.
+Column (2) records the number of payments done within 230 days of the pawn.
 Column (3) is the average size of the payments for each client in pesos.
@@
 Column (5) measures the number of days it took to recover the pawn, conditional on recovering.
-The dependent variable in Column (6) is a dummy =1 if the client paid any positive amount within 150 days of the pawn.
-For Columns (7) and (8) the dependent variable it is the sum of total payments done within 150 days of the pawn divided by the size of the loan, but column (8) includes as regressors a dummy=1 if the client recovered her pawn, and its interaction with treatment.
+The dependent variable in Column (6) is a dummy =1 if the client paid any positive amount within 230 days of the pawn.
+For Columns (7) and (8) the dependent variable it is the sum of total payments done within 230 days of the pawn divided by the size of the loan, but column (8) includes as regressors a dummy=1 if the client recovered her pawn, and its interaction with treatment.
 
@@
 
+\begin{table}[H]
+\caption{Overconfidence: Take-up and Treatment Effects}
+\label{oc_reg}
+\begin{center}
+\scriptsize{\input{./Tables/oc_reg.tex}}
+\end{center}
+ \footnotesize This table shows the parameter estimates of $y_i = \alpha + \beta \: OC_i + X_i'\gamma + \epsilon_i$, where $OC_i:=\mathbbm{1}(P^s_i-\widehat{P_i(X_i)}>0)$ is an indicator for the subjective probability of recovery being larger that the predicted one.
+In columns 1-4 $y_i$ is a dummy for whether the client $i$ chose to have the commitment contract in the respective choice arm, and in columns 5 and 6 $y_i$ is the heterogeneous treatment effect for financial cost (in pesos) estimated by comparing the fee-forcing vs status quo arms in Section \ref{TE_fee-forcing}.
+Columns 1 and 3 are estimated for the promise-choice arm, while columns 2 and 4 are estimated for the fee-choice arm.
+%\textit{Do file: } \texttt{oc.do}
+\end{table}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+\newpage
 \section{Figures}
@@
     \end{center}
-         \scriptsize Panel (a) displays in black arrows the period covered by our administrative data: from \hl{XXX} (\hl{XXX} days before the experiment began) to \hl{XXX}.
+         \scriptsize Panel (a) displays in black arrows the period covered by our administrative data: from August 6th 2012 (30 days before the experiment began) to August 13th 2013.
 The gray lines arrows correspond to the dates of implementation of the experiment.
@@
     \scriptsize
-        xxx
+        This is a (translated) sample information mica shown to clients in choice-promise days.
+The real ones were twice the size of this figure and were laminated.
+Different ones were shown in each treatment arm.
+\end{figure}
+
+\begin{figure}[H]
+        \caption{Distribution of Overconfidence}
+    \label{oc_hist}
+    \begin{center}
+        \centering
+        \includegraphics[width=0.55\textwidth]{Figuras/oc_hist.pdf}
+    \end{center}
+    \scriptsize
+     In the baseline survey at the branch, before the client knew the contract of had the pawn appraised, they were asked from 0 to 100, how likely is that they would be able to recover their pawn if pawned.
+We generate a variable we call overconfidence (OC) defined as the reported subjective probability of recovery minus the predicted probability ($P^s_i-\widehat{P_i(X_i)}$).
+We predict $\widehat{P_i(X_i)}$ using LASSO as explained in the text.
+This figure uses all observations for which we have data on $P^s_i$ and $X_i$ from the baseline survey.
+     %\textit{Do file: }  \texttt{oc.do}
+
 \end{figure}
@@
 jewelry may have sentimental value).
-This Figure uses the \hlgr{gold value}.
+This Figure uses the gold value.
 We plot separately the financial cost for those who lose the pawn (blue) and those that recover it (transparent).
@@
 In Panel (a) each dot represents the estimated treatment effect for a different definition of financing cost, or for a different sub-population, and its 95\% confidence interval.
-From left to right, the first effect corresponds to using the gold value of the pawned piece in the definition of financial cost and discounting the payments to present value using a \hl{XXX} monthly rate; the second uses the subjective value of the pawn; the third is analogous to the second but adds transaction cost (transport+1 day's wage) per visit; the fourth conditions on the population that paid any positive amount towards recovery of their pawn; the fifth conditions on the sub-population \hl{of the treatment group} that paid a fee and \hl{compares these to all the control group}; the sixth conditions on the intersection of the previous two sub-populations.
-Panel (b) plots the effects on different quantiles of the distribution of financial cost (\hl{using the first definition}): 15th, 25th, 50th, 75th, 85th percentile.
-Panel (c) Measures the effect of treatment on the likelihood of losing their pawn.
-The first coefficient compares all the treatment group vs all the control; the second conditions on the population that paid any positive amount towards recovery of their pawn; the third conditions on having paid at least 30\% of the loan amount; the fourth conditions on the period covering the first cycle of the loan; the fifth on the period of the first cycle and paying any positive amount.
+From left to right, the first effect corresponds to using the gold value of the pawned piece in the definition of financial cost and discounting the payments to present value using a 7\% monthly rate; the second uses the subjective value of the pawn; the third is analogous to the second but adds transaction cost (transport+1 day's wage) per visit; the fourth conditions on the population that paid any positive amount towards recovery of their pawn; the fifth conditions on the sub-population of the treatment group that paid a fee and compares these to all the control group; the sixth conditions on the intersection of the previous two sub-populations.
+Panel (b) plots the effects on different quantiles of the distribution of financial cost (using the first definition): 15th, 25th, 50th, 75th, 85th percentile.
+        Panel (c) plots the distribution of the heterogeneous treatment effects on financial cost, estimated using \cite{atheygrf}.
 The distribution plots the FC treatment effect for the interval $[\mu-2\sigma,\mu+2\sigma]$ to ignore the outliers.
-Panel (d) plots the distribution of the heterogeneous treatment effects on financial cost, estimated using \hl{Athey Wagner XXX}.
+Panel (d) Measures the effect of treatment on the likelihood of losing their pawn.
+The first coefficient compares all the treatment group vs all the control; the second conditions on the period covering 120 days.
+The third conditions on the population that paid any positive amount towards recovery of their pawn; the fourth conditions on having paid at least 30\% of the loan amount.
 % the effect on ``repeat purchase''.
@@
     \end{center}
-     \footnotesize \textit{Notes: } 
-      \footnotesize{ \textit{Do file: }  \texttt{re\_te.do}}
+     \scriptsize This figure shows the estimated effects on repeat purchasing of the four treatment arms (fee-forcing, choice-fee, fee-promise, choice-promise) compared to the status-quo control group.
+It shows robustness of the effects by focusing on different sub-populations.
+The leftmost coefficient compares all the fee-forcing group against all status quo group.
+The second coefficient conditions on the first pawn not being recovered when the second was pawned.
+The third coefficient uses all clients (in both the fee-forcing and the status-quo arms) who had an estimated heterogeneous treatment effect above the median.
+Conditioning on this set keeps the sample balanced across arms and therefore still allows for a causal interpretation.
+For the choice arm we present three coefficients: coefficients represented by a circle compare all those offered choice to all those in the status quo arm, thus estimating a causal effect.
+Coefficients in triangles and squares represent those that self-select into the fee or promise arms and compare this subset against the whole status quo arm.
+They therefore contain a selection effect together with the treatment effect and cannot be interpreted causally.
+      %\footnotesize{ \textit{Do file: }  \texttt{re\_te.do}
 \end{figure}
@@
         This figure is analogous to Figure \ref{fc_pro2}.
-It measures the effect of being given \textit{choice} between the frequent payment commitment contract and the status-quo contract versus being \textit{``forced''} into the status-quo contract (control).
+It measures the effect of being given \textit{choice} between the frequent payment commitment contract with fees and the status-quo contract, versus being \textit{``forced''} into the status-quo contract (control).
 Again it focuses our two main outcomes: financial cost and an indicator for losing the pawn.
-However, it also presents differences in these two outcomes for those who chose the frequent payment commitment contract versus the whole control group (squares-NSQ), and also for those who chose the status quo contract versus the whole control group (triangles-SQ).
+Circles present the treatment effects.
+The figures also presents differences in these two outcomes for those who chose the frequent payment commitment contract versus the whole control group (squares-NSQ), and also for those who chose the status quo contract versus the whole control group (triangles-SQ).
 Note that these two comparisons are not pure causal effects since people who chose the frequent payment commitment contract may be different from those that do not.
 That is: the squares and triangles combine selection and treatment effects.
-Finally, for comparison purposes, the blue diamonds display the effects of forcing them into the frequent payment commitment contract and are just transcribed from Figure \ref{fc_pro2} above.
-      \textit{Do file: }  \texttt{fc\_te\_choice\_dec.do, def\_te\_choice\_dec.do, fc\_quantilereg\_choice\_dec.do}
+Finally, for comparison purposes, the blue diamond displays the effects of forcing them into the frequent payment commitment contract and are just transcribed from Figure \ref{fc_pro2} above.
+      %\textit{Do file: }  \texttt{fc\_te\_choice\_dec.do, def\_te\_choice\_dec.do, fc\_quantilereg\_choice\_dec.do}
 \end{figure}
@@
         \scriptsize
-        \hl{Es correcto esto que escribi isaac?} Panel (a) aims to show that subjects with higher  treatment effect in the no-choice arm (using \hl{Athey and Wagner (XXX) heterogeneous treatment effect estimator ISAAC puedes meter aqui el cite?}) are \textit{not} more likely to chose it if given choice.
-We proceed in three steps: first, within the choice arm, we estimate the probability of taking up the commitment contract ($\widehat{P(x_i)}$) using random forests, the baseline survey and pre-treatment administrative data.
-Second, we extrapolate these predictions to the no-choice and control arms using the $x_i$'s.
-Finally, We allocate subjects into 5 groups according to whether their predicted probability $\widehat{P(x_i)}$ is in \hl{[0,10],(10,20],(50,70],(30,}, and for each of these sub-populations separately we estimate the ATE of the no-choice treatment using regression equation \hl{XXX}.
-We find that take up of treatment is \textit{not} correlated with the benefit of treatment, if anything the correlation is negative.
-Panel (b) does almost the reverse procedure.
-We estimate what the treatment effect of the commitment contract \textit{would have been} for all subjects in the choice arm if they had been forced into it.
-To do this we estimate heterogeneous treatment effects as a function of our $x$'s in the no-choice arm, and extrapolate them to the choice arm.
-With these in hand, we calculate what fraction of subjects in the choice arm incurred in \hl{financial costs that are  $\geq Z$\% than if they had chosen the opposite contract of what they actually chose.} We define $Z$\% as a fraction of the loan in the X-axis.
-The left Y-axis measures the fraction of subjects, and \hl{the right Y-axis measures the amount of money ``left on the table''.}
-        \textit{Do file: }  \texttt{effect\_contr\_takeup.do, choose\_wrong\_quant\_wrong.do, choose\_wrong\_quant\_wrong\_decomposition.do}
-\end{figure}
-
-\begin{figure}[H]
-    \caption{The effect of choice between promise-commitment and status quo}
+        In Panel (a) we estimate what the treatment effect of the commitment contract \textit{would have been} for all subjects in the choice arm if they had been forced into the fee-commitment contract.
+To do this we proceed in two steps.
+First, we estimate treatment effects in the forcing arm by comparing the fee-forcing arm against the status quo arm.
+We let these effects be heterogeneous as a function of our $x$'s using \cite{atheygrf}'s methodology of causal forests.
+Second, we extrapolate these treatment effects based on the choice arm using the same $x$'s.
+Once we have personalized counterfactual treatment effects in the choice we calculate what fraction of subjects in the choice arm incurred in financial costs that are  $> z$\% than if they had chosen the opposite contract of what they actually chose, were $z$\% is defined as a fraction of the loan.
+$z$\% is a level of tolerance we can vary and we plot it in the X-axis.
+The left Y-axis measures the fraction of subjects that would have been better by a margin of $z$\% if they changed their choice, and the right Y-axis measures the amount of money ``left on the table''.
+The thinly dotted lines represent 95\% confidence intervals.
+Panel (b) is analogous to Panel (a) except that it does the exercise separately for clients we classified as overconfident ($OC_i:=\mathbbm{1}(P^s_i-\widehat{P_i(X_i)}>0))$ and those we classified as not overconfident.
+Panel (c) simulates what percentage would be better by at least $z$ if we forced everybody of those in the fee-choice arm into the fee-commitment contract.
+Panel (d) asks whether it is the case that people with larger causal savings from the fee-forcing contract would be more likely to select that contract.
+To do this we proceed in two steps as well.
+First we estimate a flexible model of take-up of the fee commitment contract \textit{in the choice arm} using random forests, and from this model obtain a probability $P(x_i)$ of choosing the fee-forcing contract for a client with characteristics $x_i$.
+We extrapolate this model to clients in the fee-forcing arm to estimate what would they have chosen if we had given them choice.
+Figure (d) plots $\widehat{P(x_i)}$ in the X-axis using a binscatter that splits the X-axis in 100 percentile bins.
+The Y-axis plots the heterogeneous treatment effects of the fee forcing contract on the probability of losing the pawns (more negative means then more likely to recover it), averaged for the respective x-axis bin.
+Positive assortative selection would mean a negative relationship: those who benefit more by treatment and lose the pawn less are more likely to choose it.
+Using all bins we estimate a slope of zero in the relationship.
+Using the 80 right most points, we estimate a \textit{positive} relationship.
+        %\textit{Do file: }  \texttt{effect\_contr\_takeup.do, choose\_wrong\_quant\_wrong.do, choose\_wrong\_quant\_wrong\_decomposition.do}
+\end{figure}
+
+\begin{figure}[H]
+    \caption{The effect of promises}
     \label{fc_pro5}
     \begin{center}
+
+    \begin{subfigure}{0.45\textwidth}
+        \caption{Financial cost -- Promise-forcing}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/fc_te_pro_3.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.45\textwidth}
+        \caption{Losing Pawn -- Promise-forcing}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/def_te_pro_3.pdf}
+    \end{subfigure}
+
+    \bigskip
+    \bigskip
+
         \begin{subfigure}{0.45\textwidth}
@@
 
-    \bigskip
-    \bigskip
-
-    \begin{subfigure}{0.45\textwidth}
-        \caption{Financial cost -- Promise-forcing}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/fc_te_pro_3.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.45\textwidth}
-        \caption{Losing Pawn -- Promise-forcing}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/def_te_pro_3.pdf}
-    \end{subfigure}
-    \end{center}
-             \footnotesize \textit{Notes: } 
-      \footnotesize{ } \textit{Do file: }  \texttt{fc\_te\_choice\_dec.do, def\_te\_choice\_dec.do, fc\_te.do, def\_te.do }
+    \end{center}
+    \scriptsize
+    Panels (a) and (b) in this figure show the estimated treatment effects of ``forcing'' the frequent payment commitment contract using promises, compared to the status-quo (control) for financial cost (Panel a), and for an indicator of losing the pawn (Panel b).
+Panels (c) and (d) are analogous but focus on the effect of giving choice between frequent payment commitment contract using promises and the status quo contract.
+In Panel (a) each dot represents the estimated treatment effect for a different definition of financing cost, or for a different sub-population, and its 95\% confidence interval.
+From left to right, the first effect corresponds to using the gold value of the pawned piece in the definition of financial cost and discounting the payments to present value using a 7\% monthly rate; the second uses the subjective value of the pawn; the third is analogous to the second but adds transaction cost (transport+1 day's wage) per visit; and the fourth conditions on the population that paid any positive amount towards recovery of their pawn.
+Panel (b) plots the effect of not recovering the pawn: the leftmost coefficients compares all those assigned to the promise-forcing arm vs all those in the status quo contract, where the dependent variable=1 if the client has not recovered the pawn 230 days after pawning.
+The next coefficient defines the dependent variable=1 if the client has not recovered the pawn 120 days after pawning.
+The third coefficient conditions on paying a positive amount, and the fourth conditions on paying at least 30\% of the loan.
+Panels (b) and (c) measure the effect of being given \textit{choice} between the frequent payment commitment contract with promise and the status-quo contract, versus being \textit{``forced''} into the status-quo contract (control).
+Again it focuses our two main outcomes: financial cost and an indicator for losing the pawn.
+Circles present the treatment effects.
+The figures also presents differences in these two outcomes for those who chose the frequent payment commitment contract versus the whole control group (squares-NSQ), and also for those who chose the status quo contract versus the whole control group (triangles-SQ).
+That is: the squares and triangles combine selection and treatment effects.
+      %\footnotesize{ } \textit{Do file: }  \texttt{fc\_te\_choice\_dec.do, def\_te\_choice\_dec.do, fc\_te.do, def\_te.do }
 \end{figure}
@@
 
-\pagebreak
+\newpage
 
@@
 
-\subsection{Tables}
-
-\begin{table}[H]
-\caption{Balance response table}
-\label{balance_response}
-\begin{center}
-\scriptsize{\input{./Tables/balance_response.tex}}
-\end{center}
- \scriptsize
-%\textit{Do file: } \texttt{balance\_response.do}
-\end{table}
-
-\begin{table}[H]
-    \caption{Out of sample measures of fit}
-    \label{Table_compliance}
-    \begin{subtable}{1\textwidth}
-      \centering
-        \caption{Take up}
-        \scriptsize{\input{./Tables/oos_pago_frec_vol.tex}}
-    \end{subtable}%
-
-    \bigskip
-    \begin{subtable}{1\textwidth}
-      \centering
-        \caption{Take up w/Fee}
-        \scriptsize{\input{./Tables/oos_pago_frec_vol_fee.tex}}
-    \end{subtable}
-
-      \bigskip
-    \begin{subtable}{1\textwidth}
-      \centering
-        \caption{Take up w/promise}
-        \scriptsize{\input{./Tables/oos_pago_frec_vol_promise.tex}}
-    \end{subtable}
-            \scriptsize
-           \\
-           \\
-           \\
-  \textit{Notes:}
-
-     \textit{Scripts: } \texttt{pred\_take\_up.do, pfv\_pred.R}
-\end{table}
-
-\begin{table}[H]
-\caption{Reincidence SS}
-\label{tab_reincidence}
-\begin{center}
-\scriptsize{\input{./Tables/tab_reincidence.tex}}
-\end{center}
- \scriptsize
-%\textit{Do file: } \texttt{tab\_reincidence.do}
-\end{table}
-
-\begin{table}[H]
-\caption{Summary statistics (exit survey)}
-\label{SS_exit}
-\begin{center}
-\scriptsize{\input{./Tables/SS_exit.tex}}
-\end{center}
- \footnotesize
-\textit{Notes:}
-
-\textit{Do file: } \texttt{ss.do}
-\end{table}
-
-\begin{table}[H]
-\caption{Stochastic dominance of fee-forcing contract}
-\label{stochastic_dominance}
-\begin{center}
-\scriptsize{\input{./Tables/dominance.tex}}
-\end{center}
- \footnotesize
-\textit{Notes:}
-
-\textit{Do file: } \texttt{stoch\_dominance.do}
-\end{table}
-
-\begin{table}[H]
-\caption{OC Regression}
-\label{oc_reg}
-\begin{center}
-\scriptsize{\input{./Tables/oc_reg.tex}}
-\end{center}
- \footnotesize
-\textit{Notes:}
-
-\textit{Do file: } \texttt{oc.do}
-\end{table}
-
-\pagebreak
-
-\subsection{Figures}
-
+\subsection{Some materials}
+
+\vspace{.1in}
 \begin{figure}[H]
@@
     \begin{center}
-    \begin{subfigure}{0.75\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/ContractDonde.png}
-    \end{subfigure}
-    \begin{subfigure}{0.4\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/PersonalPromise.png}
+    \begin{subfigure}{0.65\textwidth}
+    \caption{Elapsed days to first payment}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/TicketLenderP.png}
+    \end{subfigure}
+
+    \vspace{3ex}
+    \begin{subfigure}{0.45\textwidth}
+    \caption{Elapsed days to first payment}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/Personal Promise.png}
     \end{subfigure}
@@
     \scriptsize
-         xxx 
-\end{figure}
-
-\begin{figure}[H]
-        \caption{ECDF of Financial Cost}
-    \label{ecdf_fc}
-    \begin{center}
-        \centering
-        \includegraphics[width=0.5\textwidth]{Figuras/cdf_fc_pro_2.pdf}
-    \end{center}
-    \footnotesize \textit{Notes: } 
-     \footnotesize{ \textit{Do file: }  \texttt{ecdf\_fc.do}}
-\end{figure}
-
-\begin{figure}[H]
-    \caption{Behavior of those who lost pawn}
-    \label{proxy_naive}
-    \begin{center}
-    \begin{subfigure}{0.40\textwidth}
-        \caption{Elapsed days to first payment}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_firstdays_default.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.40\textwidth}
-        \caption{Elapsed days to last payment}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_days_default.pdf}
-    \end{subfigure}
-        \begin{subfigure}{0.40\textwidth}
-        \caption{Payments as \% of loan}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_percpay_default.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.40\textwidth}
-        \caption{Number of payments}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_numpay_default.pdf}
-    \end{subfigure}
-    \end{center}
-        \scriptsize 
-        This figure describes behavior for the subsample of clients whose pawn was not recovered (\hl{in the control group}).
-Panel (a) shows days elapsed from the pawn to the first payment, while panel (b) displays the days elapsed to last payment.
-Some people pay after the day 105 when the grace period ends because the can ``restart'' the loan if they pay all interest owed.
-It amounts to starting a new loan \hl{with the same conditions} and same pawn.
-Panel (c) shows the fraction of the loan that they paid (even when they ended up losing the pawn).
-Panel (d) displays the number of times they went to the branch to pay.
-      \textit{Do file: }  \texttt{hist\_den\_default.do}
+        The top of this figure is a sample receipt that was given to clients that got assigned to the fee-forcing contract (the font and format were changed to protect Lender's P identity).
+We want to highlight the salience of some items.
+First the title clearly indicated which contract the client has (arrow 1).
+Second, in the case of the fee contract it clearly indicates that there is a fee for paying late equivalent to 4\% of the value of the monthly payment (arrow 2).
+Third, there is a calendar for payments clearly specifying the dates and amounts to pay each month.
+The bottom panel of the figure shows a ``promise slip'', the paper that those who were assigned (or chose) to the monthly payment with promise had to sign to make the promise salient.
+It emphasizes that the client is giving his word, and that the promise is not a legal document.
 \end{figure}
@@
 
-\begin{figure}[H]
-        \caption{Histogram of payments}
-    \label{HistPayments}
-    \begin{center}
-    \begin{subfigure}{.31\textwidth}
-    \caption{Control}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_payments_pro_1.pdf}
-    \end{subfigure}
-    \begin{subfigure}{.31\textwidth}
-    \caption{Forcing - fee}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_payments_pro_2.pdf}
-    \end{subfigure}   
-     \begin{subfigure}{.31\textwidth}
-    \caption{Forcing - promise}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_payments_pro_3.pdf}
-    \end{subfigure}  
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - fee}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_payments_pro_4.pdf}
-    \end{subfigure}  
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - fee - SQ}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_payments_pro_6.pdf}
-    \end{subfigure}    
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - fee - NSQ}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_payments_pro_7.pdf}
-    \end{subfigure}    
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - promise}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_payments_pro_5.pdf}
-    \end{subfigure}  
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - promise - SQ}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_payments_pro_8.pdf}
-    \end{subfigure}    
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - promise - NSQ}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_payments_pro_9.pdf}    
-    \end{subfigure}        
-    \end{center}
-     \footnotesize \textit{Notes: } The x-axis shows the elapsed days between initial date and current movement.
-      \footnotesize{ \textit{Do file: }  \texttt{hist\_payments.do}}
-\end{figure}
-
-%\begin{figure}[H]
-%        \caption{Types of agents that incur in different FC}
-%    \label{components_fc}
-%    \begin{center}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/scatter_fc_pay.pdf}
-%    \end{center}
-%     \footnotesize \textit{Notes: } 
-%      \footnotesize{ \textit{Do file: }  \texttt{hist\_fc.do}}
-%\end{figure}
-
-\begin{figure}[H]
-        \caption{Percentage of payments}
-    \label{perc_payments}
-    \begin{center}
-    \begin{subfigure}{.31\textwidth}
-    \caption{Control}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_1.pdf}
-    \end{subfigure}
-    \begin{subfigure}{.31\textwidth}
-    \caption{Forcing - fee}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_2.pdf}
-    \end{subfigure}   
-     \begin{subfigure}{.31\textwidth}
-    \caption{Forcing - promise}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_3.pdf}
-    \end{subfigure}  
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - fee}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_4.pdf}
-    \end{subfigure}  
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - fee - SQ}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_6.pdf}
-    \end{subfigure}    
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - fee - NSQ}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_7.pdf}
-    \end{subfigure}    
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - promise}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_5.pdf}
-    \end{subfigure}  
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - promise - SQ}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_8.pdf}
-    \end{subfigure}    
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - promise - NSQ}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_9.pdf}    
-    \end{subfigure}        
-    \end{center}
-     \footnotesize \textit{Notes: } 
-      \footnotesize{ \textit{Do file: }  \texttt{hist\_payments.do}}
-\end{figure}
-
-\begin{figure}[H]
-        \caption{Percentage of payment conditional on positive payment and Losing Pawn}
-    \label{perc_payments_conditional}
-    \begin{center}
-    \begin{subfigure}{.31\textwidth}
-    \caption{Control}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_1.pdf}
-    \end{subfigure}
-    \begin{subfigure}{.31\textwidth}
-    \caption{Forcing - fee}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_2.pdf}
-    \end{subfigure}   
-     \begin{subfigure}{.31\textwidth}
-    \caption{Forcing - promise}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_3.pdf}
-    \end{subfigure}  
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - fee}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_4.pdf}
-    \end{subfigure}  
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - fee - SQ}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_6.pdf}
-    \end{subfigure}    
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - fee - NSQ}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_7.pdf}
-    \end{subfigure}    
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - promise}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_5.pdf}
-    \end{subfigure}  
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - promise - SQ}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_8.pdf}
-    \end{subfigure}    
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - promise - NSQ}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_9.pdf}    
-    \end{subfigure}        
-    \end{center}
-     \footnotesize \textit{Notes: } 
-      \footnotesize{ \textit{Do file: }  \texttt{hist\_payments.do}}
-\end{figure}
-
-%\begin{figure}[H]
-%    \caption{Evolution of payment}
-%    \label{Evolution payment}
-%    \begin{center}
-%    \begin{subfigure}{0.49\textwidth}
-%        \caption{Paid loans}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/desempeno_evol.pdf}
-%    \end{subfigure}
-%     \begin{subfigure}{0.49\textwidth}
-%      \caption*{}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/desempeno_evol_choice.pdf}
-%    \end{subfigure}
-
-%     \begin{subfigure}{0.49\textwidth}
-%        \caption{Average percentage of paid loans}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/sum_porc_evol.pdf}
-%    \end{subfigure}
-%     \begin{subfigure}{0.49\textwidth}
-%      \caption*{}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/sum_porc_evol_choice.pdf}
-%    \end{subfigure}
-
-%   \begin{subfigure}{0.49\textwidth}
-%        \caption{Average percentage of paid loans | paid}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/sum_porc_cond_evol.pdf}
-%    \end{subfigure}
-%     \begin{subfigure}{0.49\textwidth}
-%      \caption*{}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/sum_porc_cond_evol_choice.pdf}
-%    \end{subfigure}
-%    \end{center}
-%     \footnotesize \textit{Notes: } 
-%      \footnotesize{ \textit{Do file: }  \texttt{evol\_payment.do}}
-%\end{figure}
-
-\begin{figure}[H]
-    \caption{Heterogeneous Treatment Effect: Fee-forcing contract}
-    \label{HTE_fee_forcing}
-    \begin{center}
-    \begin{subfigure}{0.4\textwidth}
-        \caption{Financial cost}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_2.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.4\textwidth}
-        \caption*{}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_fc_admin_disc_pro_2.pdf}
-    \end{subfigure}
-
-    \begin{subfigure}{0.4\textwidth}
-        \caption{Losing Pawn}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_2.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.4\textwidth}
-        \caption*{}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_def_c_pro_2.pdf}
-    \end{subfigure}
-    \end{center}
-     \footnotesize \textit{Notes: } 
-      \footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}}
+\afterpage{
+\begin{landscape}
+
+\subsection{Surveys}
+
+\begin{table}[H]
+\caption{Baseline survey}
+\label{baseline_survey}
+\begin{center}
+\scriptsize{\input{./Tables/baseline_survey1.tex}}
+\end{center}
+ \scriptsize 
+%\textit{Do file: } \texttt{ss.do}
+\end{table}
+
+\begin{table}[H]
+\begin{center}
+\scriptsize{\input{./Tables/baseline_survey2.tex}}
+\end{center}
+ \scriptsize 
+%\textit{Do file: } \texttt{ss.do}
+\end{table}
+
+\begin{table}[H]
+\begin{center}
+\scriptsize{\input{./Tables/baseline_survey3.tex}}
+\end{center}
+ \scriptsize 
+%\textit{Do file: } \texttt{ss.do}
+\end{table}
+\end{landscape}
+}
+
+\begin{table}[H]
+\caption{Survey's non-response balance}
+\label{balance_response}
+\begin{center}
+\scriptsize{\input{./Tables/balance_response.tex}}
+\end{center}
+ \scriptsize This table shows whether the means of variables in the administrative dataset are different for those that respond the baseline survey vs those that do not.
+We use this as an assessment of external validity.
+Internal validity is guaranteed because the baseline survey was implemented before treatment assignment and therefore response rates are orthogonal to treatment assignments.
+Panel A studies the baseline survey, while Panel B focuses on the exit survey.
+The columns labeled ``p-values'' report p-values for the test that the means of the respective variable are the same for those that responded did not respond the survey.
+%\textit{Do file: } \texttt{balance\_response.do}
+\end{table}
+
+\begin{comment}
+\begin{table}[H]
+\caption{Reincidence SS}
+\label{tab_reincidence}
+\begin{center}
+\scriptsize{\input{./Tables/tab_reincidence.tex}}
+\end{center}
+ \scriptsize
+%\textit{Do file: } \texttt{tab\_reincidence.do}
+\end{table}
+
+\begin{table}[H]
+\caption{Summary statistics (exit survey)}
+\label{SS_exit}
+\begin{center}
+\scriptsize{\input{./Tables/SS_exit.tex}}
+\end{center}
+ \scriptsize We carried out an exit survey.
+It had a small response rate and we don't use it in the paper.
+Here it shows that the characteristics of those that responded it are balanced across arms (Panel B).
+Panel A reports outcomes.
+%\textit{Do file: } \texttt{ss.do}
+\end{table}
+\end{comment}
+
+\newpage
+\subsection{Some more evidence of overconfidence}
+
+\vspace{.2in}
+\begin{figure}[H]
+    \caption{Behavior of those who lost pawn}
+    \label{proxy_naive}
+    \begin{center}
+    \begin{subfigure}{0.40\textwidth}
+        \caption{Elapsed days to first payment}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_firstdays_default.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.40\textwidth}
+        \caption{Elapsed days to last payment}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_days_default.pdf}
+    \end{subfigure}
+        \begin{subfigure}{0.40\textwidth}
+        \caption{Payments as \% of loan}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_percpay_default.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.40\textwidth}
+        \caption{Number of payments}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_numpay_default.pdf}
+    \end{subfigure}
+    \end{center}
+        \scriptsize 
+        This figure describes behavior for the subsample of clients whose pawn was not recovered (in the control group).
+Panel (a) shows days elapsed from the pawn to the first payment, while panel (b) displays the days elapsed to last payment.
+Some people pay after the day 105 when the grace period ends because the can ``restart'' the loan if they pay all interest owed.
+It amounts to starting a new loan with the same conditions and same pawn.
+Panel (c) shows the fraction of the loan that they paid (even when they ended up losing the pawn).
+Panel (d) displays the number of times they went to the branch to pay.
+      %\textit{Do file: }  \texttt{hist\_den\_default.do}
+\end{figure}
+
+\newpage
+\subsection{Main treatment effects: Additional material}
+
+\vspace{.2in}
+\begin{figure}[H]
+        \caption{Financial cost effect: charging all fees}
+    \label{fc_allfee}
+    \begin{center}
+        \centering
+        \includegraphics[width=0.50\textwidth]{Figuras/fc_allfee_quantile_pro_2.pdf}
+    \end{center}
+    \scriptsize
+     This figure is the analogous to Figure \ref{fc_pro2}(b), except that for the fee-forcing contract we pretend that all clients incurred in their late fees, and therefore inflate the financial cost by summing those fees.
+This is intended as a kind of worse case scenario for the financial cost of the fee-forcing contract.
+The circles indicate the quantile treatment effects, while the cross is the (OLS) mean.
+We still find that the financial cost of will be smaller under the fee-forcing contract in spite of artificially inflating it.
+     %\texttt{fc\_all\_fee.do}
+\end{figure}
+
+\begin{figure}[H]
+        \caption{FC as \% of loan - treatment effect}
+    \label{fc_perc}
+    \begin{center}
+        \centering
+        \includegraphics[width=0.50\textwidth]{Figuras/fc_perc_te_allarms.pdf}
+    \end{center}
+     \scriptsize This figure shows the estimated treatment effect of all arms against the status quo, but normalizing the dependent variable by the value of the loan.
+     %\textit{Do file: }  \texttt{fc\_perc\_allarms.do}
 \end{figure}
@@
 Both Panels (a) an (b) have the same X-axis, which displays the estimated heterogeneous treatment effect on the outcome ``elapsed days of first payment'', that is how many days elapsed from the day the loan was awarded to the first payment the client made.
-The treatments effects were calculated using \hl{Athey and Wagner (Isaac, puedes agregar esto en cite format?}).
-We use command \hl{XXX} in $R$ which outputs an estimated treatment effect for each person in treatment and control.
+The treatments effects were calculated using \cite{atheygrf}.
 In Panel (a) the Y-axis is the \textit{treatment effect} on financial cost.
@@
 Panel (b) shows that those induced to pay earlier are also those that have a larger increase in recovery.
-      \textit{Do file: }  \texttt{binscatter\_hte.do}
-\end{figure}
-
-\begin{figure}[H]
-        \caption{FC as \% of loan - treatment effect}
-    \label{fc_perc}
-    \begin{center}
-        \centering
-        \includegraphics[width=0.50\textwidth]{Figuras/fc_perc_te_allarms.pdf}
-    \end{center}
-    \footnotesize \textit{Notes: } 
-     \footnotesize{ \textit{Do file: }  \texttt{fc\_perc\_allarms.do}}
-\end{figure}
-
-\begin{figure}[H]
-        \caption{Financial cost effect with all fees}
-    \label{fc_allfee}
-    \begin{center}
-        \centering
-        \includegraphics[width=0.50\textwidth]{Figuras/fc_allfee_quantile_pro_2.pdf}
-    \end{center}
-    \footnotesize \textit{Notes: } 
-     \footnotesize{ \textit{Do file: }  \texttt{fc\_all\_fee.do}}
-\end{figure}
-
-\begin{figure}[H]
-        \caption{Overconfidence histogram}
-    \label{oc_hist}
-    \begin{center}
-        \centering
-        \includegraphics[width=0.50\textwidth]{Figuras/oc_hist.pdf}
-    \end{center}
-    \footnotesize \textit{Notes: } 
-     \footnotesize{ \textit{Do file: }  \texttt{oc.do}}
-\end{figure}
-
-\begin{figure}[H]
-        \caption{FC effect for different discount rates}
-    \label{oc_hist}
-    \begin{center}
-        \centering
-        \includegraphics[width=0.50\textwidth]{Figuras/discount_effect.pdf}
-    \end{center}
-    \footnotesize \textit{Notes: } 
-     \footnotesize{ \textit{Do file: }  \texttt{discounted\_noeffect.do}}
-\end{figure}
-
-\begin{figure}[H]
-    \caption{Predictors of commitment contract take-up}
-    \label{interactions_takeup}
-    \begin{center}
-    \begin{subfigure}{0.45\textwidth}
-        \caption{with Fee Arm}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/pago_frec_vol_fee_interactions_rf.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.45\textwidth}
-        \caption{with Promise Arm}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/pago_frec_vol_promise_interactions_rf.pdf}
-    \end{subfigure}
-    \end{center}
-     \footnotesize \textit{Notes: } 
-      \footnotesize{ \textit{Do file: }  \texttt{analyze\_fvp.do}}
-\end{figure}
-
-\begin{figure}[H]
-    \caption{Out of sample ROC curve}
-    \label{roc_curve}
-    \begin{center}
-    \begin{subfigure}{0.45\textwidth}
-        \caption{Take-up in Fee Arm}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/Boost/ROC_curve_outsample_pago_frec_vol_fee.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.45\textwidth}
-        \caption{Take-up in Promise Arm}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/Boost/ROC_curve_outsample_pago_frec_vol_promise.pdf}
-    \end{subfigure}
-    \end{center}
-     \footnotesize \textit{Notes: } 
-  \footnotesize{ \textit{Do file: }  \texttt{pred\_take\_up.do}}
-\end{figure}
+      %\textit{Do file: }  \texttt{binscatter\_hte.do}
+\end{figure}
+
+\newpage
+\subsection{FOSD: fee forcing vs status quo financial cost distributions}
+
+\vspace{.2in}
+\begin{figure}[H]
+        \caption{Empirical CDF of Financial Cost: fee-focing vs status-quo}
+    \label{ecdf_fc}
+    \begin{center}
+        \centering
+        \includegraphics[width=0.65\textwidth]{Figuras/cdf_fc_pro_2.pdf}
+    \end{center}
+    \scriptsize This figure plots the empirical cumulative distribution of financial cost.
+It does this separately for the fee-forcing contract and for the status-quo contract.
+The doted line at the bottom is the difference of the status-quo CDF minus the fee-focing CDF.
+It shows that the CDF of the status quo contract is always below that of the fee-forcing (and this difference is significant for the points indicated by the blue line), and therefore that the former first-order stochastically dominates the later for weakly decreasing utility functions; see Proposition \ref{eq_fosd}.
+    % \texttt{ecdf\_fc.do}}
+\end{figure}
+
+\vspace{.2in}
+\begin{table}[H]
+\caption{Clients who should prefer fee-forcing financial cost distribution}
+\label{stochastic_dominance}
+\begin{center}
+\scriptsize{\input{./Tables/dominance.tex}}
+\end{center}
+ \footnotesize
+This table does two things.
+First, it tests whether the observed empirical distribution of financial cost is well approximated by a log normal.
+It does this using two tests, the Anderson-Darling and the Kolmogorov-Smirnoff tests.
+Second, it fits a log normal distribution by maximum likelihood to observed empirical distribution of financial cost, separately for the fee-forcing arm and the status-quo arm.
+Using the fitted log normal, it tests whether the fee-forcing financial cost distribution would be preferred by any expected utility agent using Proposition \ref{lognormal_fosd} below.
+The different rows of the table do this for different sub-populations.
+The first row of the table does it for every client in the fee forcing and status quo arms.
+The ``*'' show that we cannot reject at the 5\% level that both distribution are log normal for any of the two tests.
+The column entitled ``Dominance'' shows whether any client that dislikes higher cost would prefer the fee-forcing cost distribution over the status quo one, with $\succeq_{1}$ meaning he should (with $\succeq_{1}^*$ indicating the difference is statistically significant).
+It turns out to be the case that for the overwhelming majority of sub-populations, the conditions of preferring the fee-forcing distribution hold.
+%\textit{Do file: } \texttt{stoch\_dominance.do}
+\end{table}
+
+\vspace{.2in}
+\begin{prop}
+\label{lognormal_fosd}
+\footnotesize{
+Let $F$ and $G$ be the cumulative distributions of two alternative log-normal prospects. The following are equivalent:
+
+\begin{enumerate}[(a)]
+    \item For every weakly decreasing utility function $u$: $E_{F}(u(FC))\leq E_G(u(FC))$
+    \item $E_F \log(FC)\geq E_G\log(FC)$ and $Var_F \log(FC)= Var_G\log(FC)$
+\end{enumerate}
+}
+\end{prop}
+
+\begin{proof}
+\footnotesize{
+See Theorem 4 in \cite{lognormal_dominance}.
+}
+\end{proof}
+
+\vspace{.1in}
+\begin{prop}
+\label{eq_fosd}
+\footnotesize{
+This is a standard result. 
+\\
+\vspace{.1in}
+The following are equivalent:
+\begin{enumerate}[(a)]
+    \item For every weakly decreasing utility function $u$: $E_{sq}(u(FC))\leq E_{fee}(u(FC))$
+    \item $F_{sq}(FC)\leq F_{fee}(FC)$ 
+\end{enumerate}
+}
+\end{prop}
+\begin{proof} \;
+\footnotesize{
+
+[$(a)\Longrightarrow (b)$] Suppose  $(b)$ does not hold. So there exists $FC^*$ such that $F_{sq}(FC^*)>F_{fee}(FC^*)$, Define $u:=\mathds{1}_{FC\leq FC^*}$. Then
+\[E_{sq}(u(FC)) = \int u(FC)dF_{sq} = F_{sq}(FC^*)>F_{fee}(FC^*)= \int u(FC)dF_{fee} =E_{fee}(u(FC))\]
+which contradicts $(a)$.\\
+
+[$(a)\Longleftarrow (b)$] On the other hand for $u$ weakly decreasing,
+
+\[\int u(y(FC))dF_{sq}(y(FC)) = \int u(y(FC))dF_{fee}(FC) \leq \int u(FC)dF_{fee}(FC)\]
+with $y(FC) = F_{sq}^{-1}F_{fee}(FC)$.
+}
+\end{proof}
+\footnotesize{
+Note the proof was done in the case of absolutely continuous and strictly increasing distribution functions $F_{sq}$ and $F_{fee}$.
+}
+
+\newpage
+\subsection{Causal Random Forest and HTE}
+
+\vspace{.3in}
+\begin{figure}[H]
+        \caption{Honest causal tree for the fee forcing contract heterogenous treatment effects}
+    \label{casual_tree}
+    \begin{center}
+        \centering
+        \includegraphics[width=.8\textwidth]{Figuras/crf_pro_2_fc_admin_disc.pdf}
+    \end{center}
+    \footnotesize 
+    This is one(it is chosen such that it minimizes the pruned cost, that is it is the tree with the smallest root-node impurity) of the honest causal trees in the random forest we use for the estimation of the heterogeneous treatment effect of the fee-forcing contract.
+It is meant only as an example of how these trees look like.
+The forest was such that there are as many estimated treatment effects as there are clients.
+     %\footnotesize{ \textit{RScript: }  \texttt{grf.R}
+\end{figure}
+
+\begin{figure}[H]
+    \caption{Heterogeneous Treatment Effect: Fee-forcing contract}
+    \label{HTE_fee_forcing}
+    \begin{center}
+    \begin{subfigure}{0.4\textwidth}
+        \caption{Financial cost}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_2.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.4\textwidth}
+        \caption*{}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_fc_admin_disc_pro_2.pdf}
+    \end{subfigure}
+
+    \begin{subfigure}{0.4\textwidth}
+        \caption{Losing Pawn}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_2.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.4\textwidth}
+        \caption*{}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_def_c_pro_2.pdf}
+    \end{subfigure}
+    \end{center}
+     \scriptsize  The left hand side of Panel (a) plots the distribution of heterogeneous treatment effects estimated using the methodology of \cite{atheygrf}.
+The right hand side estimates bivariate regressions of those treatment effects against the respective covariate from the baseline survey  $\widehat{hte_i} = \alpha + \beta \: X_i + \epsilon_i$.
+The regressors $X_i$ include (e.g if the family asks for money, if they have savings, if they are overconfident using the definition the text, etc.).
+      %\footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}}
+\end{figure}
+
+\begin{figure}[H]
+    \caption{Heterogeneous Treatment Effect: Promise-forcing contract}
+    \label{heterogeneous_te_3}
+    \begin{center}
+    \begin{subfigure}{0.4\textwidth}
+        \caption{Financial cost}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_3.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.4\textwidth}
+        \caption*{}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_fc_admin_disc_pro_3.pdf}
+    \end{subfigure}
+
+    \begin{subfigure}{0.4\textwidth}
+        \caption{Losing Pawn}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_3.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.4\textwidth}
+        \caption*{}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_def_c_pro_3.pdf}
+    \end{subfigure}
+    \end{center}
+     \scriptsize
+      %\footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}}
+\end{figure}
+
+\begin{comment}
 
@@
 
-\begin{figure}[H]
-    \caption{Heterogeneous Treatment Effect:  No-Choice/Promise}
-    \label{heterogeneous_te_3}
-    \begin{center}
-    \begin{subfigure}{0.4\textwidth}
-        \caption{Financial cost}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_3.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.4\textwidth}
-        \caption*{}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_fc_admin_disc_pro_3.pdf}
-    \end{subfigure}
-
-    \begin{subfigure}{0.4\textwidth}
-        \caption{Losing Pawn}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_3.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.4\textwidth}
-        \caption*{}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_def_c_pro_3.pdf}
-    \end{subfigure}
-    \end{center}
-     \footnotesize \textit{Notes: } 
-      \footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}}
-\end{figure}
-
-\begin{figure}[H]
-        \caption{Causal tree for HTE}
-    \label{casual_tree}
-    \begin{center}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/crf_pro_2_fc_admin_disc.pdf}
-    \end{center}
-    \footnotesize \textit{Notes: } 
-     \footnotesize{ \textit{RScript: }  \texttt{grf.R}}
-\end{figure}
+\end{comment}
 
@@
 %\end{figure}
+
+\pagebreak
+\subsection{Take up}
+
+\begin{table}[H]
+    \caption{Predicting Take-up: Goodness-of-Fit}
+    \label{Table_compliance}
+    %\begin{subtable}{1\textwidth}
+    % \centering
+    %    \caption{Take up}
+    %    \scriptsize{\input{./Tables/oos_pago_frec_vol.tex}}
+    %\end{subtable}%
+
+    %\bigskip
+     \begin{subtable}{1\textwidth}
+      \centering
+        \caption{Take up: Choice-fee Arm}
+        \scriptsize{\input{./Tables/oos_pago_frec_vol_fee.tex}}
+    \end{subtable}
+
+      \bigskip
+    \begin{subtable}{1\textwidth}
+      \centering
+        \caption{Take up: Choice-promise Arm}
+        \scriptsize{\input{./Tables/oos_pago_frec_vol_promise.tex}}
+    \end{subtable}
+            \scriptsize
+           \\
+           \\
+           \\
+
+     %\textit{Scripts: } \texttt{pred\_take\_up.do, pfv\_pred.R}
+\end{table}
+
+\vspace{.1in}
+\begin{figure}[H]
+    \caption{Out of sample ROC curve}
+    \label{roc_curve}
+    \begin{center}
+    \begin{subfigure}{0.45\textwidth}
+        \caption{Take-up in Fee Arm}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/Boost/ROC_curve_outsample_pago_frec_vol_fee.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.45\textwidth}
+        \caption{Take-up in Promise Arm}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/Boost/ROC_curve_outsample_pago_frec_vol_promise.pdf}
+    \end{subfigure}
+    \end{center}
+     \scriptsize 
+  %\footnotesize{ \textit{Do file: }  \texttt{pred\_take\_up.do}}
+\end{figure}
+
+\begin{figure}[H]
+    \caption{Predictors of commitment contract take-up}
+    \label{interactions_takeup}
+    \begin{center}
+    \begin{subfigure}{0.45\textwidth}
+        \caption{with Fee Arm}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/pago_frec_vol_fee_interactions_rf.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.45\textwidth}
+        \caption{with Promise Arm}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/pago_frec_vol_promise_interactions_rf.pdf}
+    \end{subfigure}
+    \end{center}
+     \scriptsize This figure reports bivariate regressions of the form $\widehat{TakeUp} = \alpha + \beta \: X_i + \epsilon_i$, where $\widehat{TakeUp}$ is the prediction using random forests.
+The figure reports the $\beta$ coefficients for different $X_i$'s along with 95\% confidence intervals.
+Panel (a) focuses on take up in the arm where clients could chose among the fee-commitment contract and the status quo contract.
+Panel (b) focuses on the arm where clients could chose among the promise-commitment contract and the status quo contract.
+
+      %\footnotesize{ \textit{Do file: }  \texttt{analyze\_fvp.do}}
+\end{figure}
+
+\vspace{.2in}
+\noindent Using random forests we can predict who takes up the fee-forcing contract with 85\% accuracy out of sample.\footnote{Correcting for the fact that most chose the status-quo contract using the method of SMOTE, \cite{smote} we find an accuracy rate of 75\%.} Which suggests that choice among contracts is not purely random.
+Figure \ref{interactions_takeup} in the Appendix shows that the more educated, those that report that their family typically asks for money, those that make a monthly budget of expenses, and those that ask for a remainder of their due payments (and marginally those we classify as present-biased) are more likely to chose the fee-commitment contract if given the choice.
+The opposite holds for clients that are more economically vulnerable (can barely pay for food, electricity, etc) and those that report being more stressed.
 
@@
 
+\begin{comment}
+\begin{figure}[H]
+        \caption{Histogram of payments}
+    \label{HistPayments}
+    \begin{center}
+    \begin{subfigure}{.31\textwidth}
+    \caption{Control}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_payments_pro_1.pdf}
+    \end{subfigure}
+    \begin{subfigure}{.31\textwidth}
+    \caption{Forcing - fee}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_payments_pro_2.pdf}
+    \end{subfigure}   
+     \begin{subfigure}{.31\textwidth}
+    \caption{Forcing - promise}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_payments_pro_3.pdf}
+    \end{subfigure}  
+     \begin{subfigure}{.31\textwidth}
+    \caption{Choice - fee}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_payments_pro_4.pdf}
+    \end{subfigure}  
+     \begin{subfigure}{.31\textwidth}
+    \caption{Choice - fee - SQ}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_payments_pro_6.pdf}
+    \end{subfigure}    
+     \begin{subfigure}{.31\textwidth}
+    \caption{Choice - fee - NSQ}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_payments_pro_7.pdf}
+    \end{subfigure}    
+     \begin{subfigure}{.31\textwidth}
+    \caption{Choice - promise}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_payments_pro_5.pdf}
+    \end{subfigure}  
+     \begin{subfigure}{.31\textwidth}
+    \caption{Choice - promise - SQ}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_payments_pro_8.pdf}
+    \end{subfigure}    
+     \begin{subfigure}{.31\textwidth}
+    \caption{Choice - promise - NSQ}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_payments_pro_9.pdf}    
+    \end{subfigure}        
+    \end{center}
+     \footnotesize \textit{Notes: } The x-axis shows the elapsed days between initial date and current movement.
+      \footnotesize{ \textit{Do file: }  \texttt{hist\_payments.do}}
+\end{figure}
+\end{comment}
+
+%\begin{figure}[H]
+%        \caption{Types of agents that incur in different FC}
+%    \label{components_fc}
+%    \begin{center}
+%        \centering
+%        \includegraphics[width=\textwidth]{Figuras/scatter_fc_pay.pdf}
+%    \end{center}
+%     \footnotesize \textit{Notes: } 
+%      \footnotesize{ \textit{Do file: }  \texttt{hist\_fc.do}}
+%\end{figure}
+
+\begin{comment}
+\begin{figure}[H]
+        \caption{Percentage of payments}
+    \label{perc_payments}
+    \begin{center}
+    \begin{subfigure}{.31\textwidth}
+    \caption{Control}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_1.pdf}
+    \end{subfigure}
+    \begin{subfigure}{.31\textwidth}
+    \caption{Forcing - fee}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_2.pdf}
+    \end{subfigure}   
+     \begin{subfigure}{.31\textwidth}
+    \caption{Forcing - promise}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_3.pdf}
+    \end{subfigure}  
+     \begin{subfigure}{.31\textwidth}
+    \caption{Choice - fee}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_4.pdf}
+    \end{subfigure}  
+     \begin{subfigure}{.31\textwidth}
+    \caption{Choice - fee - SQ}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_6.pdf}
+    \end{subfigure}    
+     \begin{subfigure}{.31\textwidth}
+    \caption{Choice - fee - NSQ}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_7.pdf}
+    \end{subfigure}    
+     \begin{subfigure}{.31\textwidth}
+    \caption{Choice - promise}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_5.pdf}
+    \end{subfigure}  
+     \begin{subfigure}{.31\textwidth}
+    \caption{Choice - promise - SQ}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_8.pdf}
+    \end{subfigure}    
+     \begin{subfigure}{.31\textwidth}
+    \caption{Choice - promise - NSQ}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_9.pdf}    
+    \end{subfigure}        
+    \end{center}
+     \footnotesize \textit{Notes: } 
+      \footnotesize{ \textit{Do file: }  \texttt{hist\_payments.do}}
+\end{figure}
+
+\begin{figure}[H]
+        \caption{Percentage of payment conditional on positive payment and Losing Pawn}
+    \label{perc_payments_conditional}
+    \begin{center}
+    \begin{subfigure}{.31\textwidth}
+    \caption{Control}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_1.pdf}
+    \end{subfigure}
+    \begin{subfigure}{.31\textwidth}
+    \caption{Forcing - fee}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_2.pdf}
+    \end{subfigure}   
+     \begin{subfigure}{.31\textwidth}
+    \caption{Forcing - promise}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_3.pdf}
+    \end{subfigure}  
+     \begin{subfigure}{.31\textwidth}
+    \caption{Choice - fee}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_4.pdf}
+    \end{subfigure}  
+     \begin{subfigure}{.31\textwidth}
+    \caption{Choice - fee - SQ}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_6.pdf}
+    \end{subfigure}    
+     \begin{subfigure}{.31\textwidth}
+    \caption{Choice - fee - NSQ}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_7.pdf}
+    \end{subfigure}    
+     \begin{subfigure}{.31\textwidth}
+    \caption{Choice - promise}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_5.pdf}
+    \end{subfigure}  
+     \begin{subfigure}{.31\textwidth}
+    \caption{Choice - promise - SQ}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_8.pdf}
+    \end{subfigure}    
+     \begin{subfigure}{.31\textwidth}
+    \caption{Choice - promise - NSQ}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_9.pdf}    
+    \end{subfigure}        
+    \end{center}
+     \footnotesize \textit{Notes: } 
+      \footnotesize{ \textit{Do file: }  \texttt{hist\_payments.do}}
+\end{figure}
+\end{comment}
+
+%\begin{figure}[H]
+%    \caption{Evolution of payment}
+%    \label{Evolution payment}
+%    \begin{center}
+%    \begin{subfigure}{0.49\textwidth}
+%        \caption{Paid loans}
+%        \centering
+%        \includegraphics[width=\textwidth]{Figuras/desempeno_evol.pdf}
+%    \end{subfigure}
+%     \begin{subfigure}{0.49\textwidth}
+%      \caption*{}
+%        \centering
+%        \includegraphics[width=\textwidth]{Figuras/desempeno_evol_choice.pdf}
+%    \end{subfigure}
+
+%     \begin{subfigure}{0.49\textwidth}
+%        \caption{Average percentage of paid loans}
+%        \centering
+%        \includegraphics[width=\textwidth]{Figuras/sum_porc_evol.pdf}
+%    \end{subfigure}
+%     \begin{subfigure}{0.49\textwidth}
+%      \caption*{}
+%        \centering
+%        \includegraphics[width=\textwidth]{Figuras/sum_porc_evol_choice.pdf}
+%    \end{subfigure}
+
+%   \begin{subfigure}{0.49\textwidth}
+%        \caption{Average percentage of paid loans | paid}
+%        \centering
+%        \includegraphics[width=\textwidth]{Figuras/sum_porc_cond_evol.pdf}
+%    \end{subfigure}
+%     \begin{subfigure}{0.49\textwidth}
+%      \caption*{}
+%        \centering
+%        \includegraphics[width=\textwidth]{Figuras/sum_porc_cond_evol_choice.pdf}
+%    \end{subfigure}
+%    \end{center}
+%     \footnotesize \textit{Notes: } 
+%      \footnotesize{ \textit{Do file: }  \texttt{evol\_payment.do}}
+%\end{figure}
+
+\begin{comment}
+
+\begin{figure}[H]
+        \caption{FC effect for different discount rates}
+    \label{oc_hist}
+    \begin{center}
+        \centering
+        \includegraphics[width=0.50\textwidth]{Figuras/discount_effect.pdf}
+    \end{center}
+    \footnotesize \textit{Notes: } 
+     \footnotesize{ \textit{Do file: }  \texttt{discounted\_noeffect.do}}
+\end{figure}
+\end{comment}
+
 \end{document}

### 2020-06-16 main.tex
copy repo

@@
 A significant literature has shown that demand for commitment exists but is somewhat low in some contexts (\cite{Ashraf}, \cite{Gine}, \cite{Ted}), and high in others (\cite{Kremer},  \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}).
-We add to this literature by showing that very small fees are enough to drastically reduce demand for commitment, even when commitment is beneficial for almost everybody in our sample, and that softer commitments in the form of non-pecuniary personal promises elicit higher demand.\footnote{Our fees are \hl{400\%} higher as a fraction of the loan than those of \cite{John}.} Second, two recent papers show that among those who demand commitment, the extent of commitment needed is underestimated (\cite{Ted}, \cite{John}) and that subjects can hurt themselves by self-imposing too week a commitment.
+We add to this literature by showing that very small fees are enough to drastically reduce demand for commitment, even when commitment is beneficial for almost everybody in our sample, and that softer commitments in the form of non-pecuniary personal promises elicit higher demand.\footnote{Our fees are 16 times smaller than than those of \cite{John} as a fraction of the loan/goal, and five times smaller converting peso values using exchange rates.} Second, two recent papers show that among those who demand commitment, the extent of commitment needed is underestimated (\cite{Ted}, \cite{John}) and that subjects can hurt themselves by self-imposing too week a commitment.
 We contribute in design ---by not allowing choice of the extent of commitment--- but also on how we infer the underestimation of the value of commitment by subjects.
@@
 \cite{Ghatak} state that ``high-frequency repayment, a feature in nearly all microfinance contracts, has been largely overlooked''.\footnote{\cite{LittleAtAtime} also note that ``it is especially surprising that there is so little analytical discussion of the incentive effects of the installment system''.} This paper fills part of this gap.
-\cite{Pande} study the effect of installment frequency on loan default and (surprisingly given their prevalence and the literature above) find null effects, while \cite{Murdoch} study selection into frequent payment microfinance loans, conjecturing that ``such repayment structure is potentially beneficial in fostering discipline among present-biased borrowers''.
-In contrast to \cite{Pande} we find very strong effects of payment frequency on decreased default.\footnote{Possibly because there are high levels of default in our context and not in theirs and because we have more statistical power from larger sample and individual randomization.} \cite{Murdoch}  show that a robust positive correlation exists between having present biased preferences in surveys and selecting into microfinance ---which they interpret as being due to the discipline of frequent payment--- acknowledging that the ``interpretation is suggestive...
+\cite{Pande} study the effect of installment payment frequency on loan default and (surprisingly given their prevalence and the literature above) find null effects.
+\cite{Murdoch} study selection into frequent payment microfinance loans, conjecturing that ``such repayment structure is potentially beneficial in fostering discipline among present-biased borrowers'' and may explain why borrowers choose it.
+In contrast to \cite{Pande} we find strong effects of payment frequency on decreased default.\footnote{Possibly because there are high levels of default in our context and not in theirs and because we have more statistical power from a larger sample and individual level randomization.} \cite{Murdoch}  show that a robust positive correlation exists between displaying present biased preferences in surveys and selecting into microfinance ---which they interpret as being due to high demand for the discipline of frequent payments--- acknowledging that the ``interpretation is suggestive...
 and needs to be confirmed by studies that establish causal links''.
-Our experimental test of this causal link rejects that people like and demand frequent payments (at least in our context).
+Our experimental test of this causal link rejects that most people like and demand frequent payments (at least in our context).
 In contrast to \cite{Murdoch} we can isolate the pure effect of payment frequency on demand by randomly changing just this aspect of the contract.
@@
 
-More importantly, our unique experimental design, paired with new machine learning methods to estimate heterogeneous treatment effects \cite{atheygrf}, allows us to estimate whether there is positive or negative selection into beneficial contracts, and whether pawnshop clients forgo money by not demanding commitment.
-In consonance with what \cite{Walters} finds in another context, we find that it is not the case that those that benefit most from the contract demand it, consistent with a significant fraction of clients displaying naivete about self control problems (see \cite{Rabin2018}).
+More importantly, our unique experimental design which combines forcing and choice arms, paired with new machine learning methods to estimate heterogeneous treatment effects (\cite{atheygrf}), allows us to estimate whether there is positive or negative selection into beneficial contracts, and whether pawnshop clients forgo money by not demanding commitment.
+In consonance with what \cite{Walters} finds in another context, we find that it is not the case that those that benefit most from the contract demand it more, consistent with a significant fraction of clients displaying naivete about self control problems (see \cite{Rabin2018}).
 Our context is one in which private paternalism (\cite{Laibson2018}) could work since almost all pawnshop clients would benefit from frequent payment contract yet there it almost no demand for them.
@@
 Section \ref{context} provides context and describes the data sources.
+Section \ref{Data} presents summary statistics and defines our main outcome variables.
 Section \ref{Experiment} describes the experiment and shows pre-treatment balance across arms.
 Section \ref{fee-commitment} estimates the effect of forcing clients into the fee-commitment contract, while Section \ref{fee-choice} studies the effects of choice.
+Section \ref{model} collects all findings and presents a model to rationalize them qualitatively.
 Section \ref{promises} assesses if promises work in our context as commitment devices.
@@
 
-Pawn borrowing is one of the oldest form of borrowing and one to which people with little access to the formal credit market turn to for ``emergency'' loans.
+Pawn borrowing is one of the oldest forms of borrowing and one to which people with little access to the formal credit market turn to for ``emergency'' loans.
 They existed in antiquity at least since the Roman Empire, and there are records of it in China about 1,500 years ago (\cite{PawnShops}).
-In spite of this, there are extremely few studies in the economics literature about it.
-Why people go, how much it costs, what different contracts can tell us about consumer biases.
-We study such  context with Lender $P$, one of the largest pawn shops in Mexico, with dozens of branches spanning multiple States in Mexico.
+As explained above pawn loans involve individuals leaving valuable and liquid assets (typically jewelry) as collateral in exchange for an immediate cash loan.
+We study such  context by partnering with Lender $P$, one of the largest pawn shops in Mexico, with more than one hundred branches spanning multiple States in Mexico.
 
 Lender $P$ was interested in understanding why half of their clients lost their pawn.
-It was concerned with high default rates for two reasons.
+Default is really in this context  compared to many papers in the microfinance literature\footnote{\cite{Pande} study of the effect of payment frequency in a context where the rate of default is close to 1\%.} It was concerned with high default rates for two reasons.
 The first is that the pawned piece may have a sentimental value to the client above of its gold value, making it inefficient for the lender to keep the piece.
 We actually find that clients report a subjective value that is almost twice the value of its gold content.
-Second, it thought that keeping the piece lowered client satisfaction and made the client less likely to return and pawn again.
+Second, keeping the piece may lower client satisfaction and make the client less likely to return and pawn again.
 They were interested in investigating whether a frequent payment contract would increase pawn recovery and costumer satisfaction, and whether there was demand for such a contract.
-Default is really  in this context  compared to many papers in the microfinance literature.
-\cite{Pande} study of the effect of payment frequency work in a context where the rate of default is close to 1\%.
-%\cite{LittleAtAtime} has a baseline default of \hl{XX\%}.
 
 One potential explanation for high default is that clients are really just selling their gold piece.
-This is unlikely for the large majority of people not only because the reported subjective value of the pawn is larger than the loan size for 86\% of them, but also because among those that lose their pawn 74\% paid a positive amount towards its recovery.
-This can only be rationalized if they expected to recover their pawn.
-Figure \ref{proxy_naive} focuses on those that ended up losing the pawn in our experiment and plots different measures of engagement with Lender $P$.
-Panel (c) shows total payments that went towards the loan.
-On average clients that lost their pawn paid 34\% of the value of their loan.
-Panel (d) shows that while 40\% made zero payments, the rest made one or several payments.
-In fact, panel (b) shows that close to 55\% of clients extended the loan for another cycle and made payments in the second cycle.
+This is unlikely for severalreasons: (a)  the reported subjective value of the pawn is larger than the loan size for \hl{86\%} of them, (b) among those that lose their pawn 74\% paid a positive amount towards its recovery --- this can only be rationalized if they expected to recover their pawn, (c) it is typical to find gold purchasing stores close to where the pawnshops are located (see Figure \ref{GoldBuyers}) and they give more than what Lender P gives for the pawn, (d) there is a lot of engagement with the lender after pawning even for those who lost their pawn.
+On average clients that lost their pawn paid 34\% of the value of their loan, and close to 55\% of clients extended the loan for another cycle and made payments in the second cycle (see Figure \ref{proxy_naive} in Appendix).
 
@@
 
-Their business model is very simple.
+Lender P's business model is very simple.
 They take gold jewelry as collateral in exchange for a fraction of money given instantly in cash.
 The transaction takes less than 10 minutes and is conducted at the branch in person between the client and the appraiser (i.e.
-a teller).
+a teller, see Figure \ref{PawnshopPicture}).
 The appraiser weights the gold piece and runs tests on its purity.
@@
 It stipulated that the interest rate was 7\% \textit{per month} accumulated daily on the outstanding amount of the loan.
-The loan had a 90 days term with 15 days grace period, and the client could make payments at anytime and no penalty for pre-payment.
+The loan had a 90 days term with 15 days grace period, and the client could make payments at anytime with no penalty for pre-payment.
 If the client paid the principal plus the accumulated interest before those 105 days, then she received back her pawn, otherwise the pawnbroker kept the piece and any payments done.
-Before the contract expired, the client had the right to renew it (using the same collateral) for another 3 months by going to the pawnshop paying the accumulated interest and signing a new contract with exactly the same terms.
-The pawnshop therefore makes money in three ways: by reselling the jewelry left as collateral on defaulted loans, by charging interest on non defaulted loans, and by keeping the payments made on defaulted loans.
-
-This contract was standard in the industry, the clients that pawned understood its conditions (as we verified in interviews) and still decided to pawn.
-Bear in mind that these clients have little or no access to other types of loans, and also that they value its convenience: the process is fast and requires no documentation or credit-history.
-Potentially they like it also because they are overconfident on average about the probability of recovering their pawn, as discussed below, even though 90\% of them have pawned before.
-
-\section{Data and summary stats}
+Before the contract expired, the client had the right to renew it (using the same collateral) for another 3 months by going to the pawnshop paying the accumulated interest and signing a new contract with exactly the same terms as the original one.
+%The pawnshop therefore makes money in three ways: by reselling the jewelry left as collateral on defaulted loans, by charging interest on non defaulted loans, and by keeping the payments made on defaulted loans.
+
+This contract was standard in the industry, the clients that pawned understood its conditions (as we verified in interviews) and still decided to pawn.\footnote{90\% of clients report in our survey they have pawned before.} Bear in mind that these clients have little or no access to other types of loans, and also that they value its convenience: the process is fast and requires no documentation or credit-history.
+Potentially they like it also because they are overconfident on average about the probability of recovering their pawn, as discussed below.
+
+\section{Data and summary stats} \label{Data}
 
@@
 In particular, the value of the piece as assessed by the appraiser, the amount of money lent (70\% of the value), and the date when it was pawned.
-As described below, for our experiment we also recorded the type of contract for that pawn.
-After the pawn happens, we follow each transaction related to that piece in the administrative data: when were payments made and for which amounts, whether there was default (i.e.
-the client lost her pawn), and whether any late-payment fees (active for only some experimental arms) were imposed.
+As described below, for our experiment the administrative data recorded the type of contract for that pawn.
+After the pawn happens, we follow each transaction related to that piece in the administrative data as well as when were payments made and for which amounts, whether there was default (i.e.
+the client lost her pawn), and whether any late-payment fees (active for the relevant experimental arms) were imposed.
 We have this information for all the pawns that occurred in our 6 branches between August 2nd 2012 and August 13th 2013, this includes all the pawns under our experiment but also those that happened 1 month before it started and up to 8 months after it ended.
@@
 
-We had a team of enumerators in each branch collect surveys and clearly explain the contract terms to walk-in clients.
+We had a team of ITAM student enumerators in each branch collect surveys and clearly explain the contract terms to walk-in clients.
 The enumerators were inside the branch and asked clients to complete a short 5 minutes survey before going to the teller window to appraise their piece.
@@
 Although not shown in the table, only 40\% of clients recover they pawn within 230 days.
-Even those that recover their pawn tend to pay it back at the last moment, only 17\% pay before the 90th day.
+Even those that recover their pawn tend to pay it back at the last moment, with only 17\% paying before the 90th day.
 
@@
 Finally the subjective probability of recovery is close to 93\% on average, which contrast with the 44\% recovery that happens in reality for the pawns in the control group.
-Just by this measure borrowers seem to be highly overconfident on average.
-It turns out that the average subjective value they report for the pieces is 3250 pesos, which is much larger than the average appraised gold value (1950 pesos).
+Just by this measure borrowers seem to be highly overconfident on average (more on this below).
+It turns out that the average subjective value they report for the pieces is 3250 pesos, which is much larger than the average appraised gold value of 1950 pesos.
 This makes it inefficient for them to lose it.
 
-Since the main treatment involves making them come to the branch to pay each month, the transaction costs of coming to the branch are important, and we ask two questions around them.
+Since the main treatment involves making clients come to the branch to pay each month, the transaction costs of coming to the branch are important, and we ask two questions about them.
 The average time they take to come to the branch is 22 minutes, and the amount of money they spend in transport to do that is 11 pesos (\$0.60 usd).
@@
 
-Our main dependent variables are loan default and financial cost incurred by the borrower.
-Default is defined as losing the pawn.
-We observe directly when the piece gets appropriated by Lender $P$ and goes on sale.
-
-We define financial cost as the discounted sum of payments toward the loan plus the value of the loan, and substract to it the appraised or subjective discounted value of the pawn when it is recovered: $Financial \; Cost_i = \sum_t \frac{P_{it}}{(1+r)^t} + Pawn \: Value_i - \frac{\text{I}(Recovered \: Pawn_i) \times Pawn \: Value_i}{(1+r)^T}$, with $t$ indexing days, $T$ is the day when the pawn is recovered, I($\cdot$) an indicator function for recovering the pawn, $r$ is a daily interest rate equivalent to a 7\% monthly interest rate.
-Figure \ref{fc_hist}(a) plots a histogram of this cost in pesos conditional on recovering and conditional on not recovering the pawn.
-This cost is calculated for a time period of 230 days after loan origination, as 50\% of clients actually renew the loan one time and 28\% a second time.
-Of those who renew once 34\% lose the pawn, and of those that renew twice 15\% do.
+Our main dependent variables are loan default and financial cost incurred by the borrower. Default is defined as losing the pawn. We observe directly when the piece gets appropriated by Lender $P$.
+
+We define financial cost as the discounted sum of payments toward the loan plus the value of the pawn, and subtract the subjective discounted value of the pawn when it is recovered: $Financial \; Cost_i = \sum_t \frac{P_{it}}{(1+r)^t} + Pawn \: Value_i - \frac{\text{I}(Recovered \: Pawn_i) \times Pawn \: Value_i}{(1+r)^T}$, with $t$ indexing days, $T$ is the day when the pawn is recovered, I($\cdot$) an indicator function for recovering the pawn, $r$ is a daily interest rate equivalent to a 7\% monthly interest rate.\footnote{We experimented with different interest rates with similar results.
+See section \ref{neoclasical}.} Figure \ref{fc_hist}(a) plots a histogram of this cost in pesos for loans where the pawn was recovered or lost.
+This cost is calculated for a time period of 230 days after loan origination, as 50\% of clients actually renew the loan one time.
+Of those who renew 34\% lose the pawn.
 Figure \ref{fc_hist}(a) suggest that financial cost is significant, even for those that do recover their pawn.
@@
 It shows that as a percentage of their pawn, most of the cost comes from clients that do not recover their pawn.
-For them the cost is between 150\% and 250\% of the loan value.
+For them the cost is between 140\% and 250\% of the loan value.
 %\hl{The difference between panel (a) and (b) arises since clients who lose their pawn tend to be those that pledge cheaper pieces.}
@@
 
-\noindent \textit{Selection of branches.} Starting September 6th 2012, we implemented our experiment in 6 branches of Lender $P$.
+\noindent \textbd{Selection of branches.} Starting September 6th 2012, we implemented our experiment in 6 branches of Lender $P$.
 The branches were selected by Lender $P$ to be dispersed across Mexico city and have varying sizes.
@@
 \vspace{.2in}
-\noindent \textit{The monthly payment contract.} For the purpose of the experiment we designed a new contract that is identical to the status quo contract in all respects except one.
-It has the same interest rate (7\% \textit{per month} which accumulates daily on outstanding debt, it has the same loan size/collateral ratio (70\%), it has the same loan term (90 days), and the gold pawn gets appraised in the same way by the same appraisers.
+\noindent \textbf{The monthly installment contract.} For the purpose of the experiment we designed a new contract that is identical to the status quo contract in all respects except one.
+It has the same interest rate (7\% \textit{per month} which accumulates daily on outstanding debt, it has the same loan size/collateral ratio (70\%), it has the same loan term (90 days, and a grace period of 15 days), and the gold pawn gets appraised in the same way by the same appraisers.
 The only difference is that it has a requirement that the client has to pay monthly: for the 3 month duration at least 1/3 of the loan value (plus accumulated interest) has to be paid before day 30th, 60th and 90th after loan disbursement.
-Failure to pay these amount triggers a penalty fee of 2\% of this minimum amount due (in some of the treatment arms), which is added to the amount that the client needs to pay to recover their pawn.
-This penalty acts as a commitment device to pay now vs paying later.
+Failure to pay this amount triggers a penalty fee of 2\% of this minimum amount due, which is added to the amount that the client needs to pay to recover their pawn.
+This penalty acts as a commitment incentive to pay now vs paying later.
 The level of the penalty was determined by Lender $P$ after talking to clients and based on Lender $P$'s experience.
-They deemed 2\% something that was big enough to provide commitment but small enough that if clients had an emergency and could not pay, the fee would not cause the pawn to be unrecoverable.\footnote{As explained below we also experimented with a contract where there was no pecuniary fee for paying late but where we clients made a personal promise to pay monthly.
-In contrast with \cite{John} we don't let the clients choose the size of the fee.
-As that paper shows doing this results in wrong choices by naive present biased consumers.}
+They deemed 2\% something that was big enough to provide commitment but small enough that if clients had an emergency and could not pay, the fee would not cause the pawn to be unrecoverable.\footnote{In contrast with \cite{John} we don't let the clients choose the size of the fee.
+As that paper shows doing this results in wrong choices by naive present biased consumers.
+Our fee is much smaller than the median in her experiment as explained above.
+We also experimented with a contract where there was no pecuniary fee for paying late but where we clients made a personal promise to pay monthly.}
 
 \vspace{.2in}
-\noindent \textit{Randomization.} Randomization was done at the branch-day level.
+\noindent \textbf{Randomization.} Randomization was done at the branch-day level.
 Each day the system chose which types of contracts were on offer that day in the branch, and therefore which contract the client signed.
@@
 They were told that there were 5 different ``types of contract-days'' and that the system chose randomly which applied any given date, and that it could happen for instance that two consecutive dates had the same contract.
-They were also told that this way of operating was in effect in various Lender $P$'s branches (they did not know which ones), and that it could be in place for several months.
-Randomizing at the day level limits the problem of contamination arising from clients waiting for appraisal observing that other clients get different contracts than theirs.
+They were also told that this way of operating was in place onin various Lender $P$'s branches (they did not know which ones), and that it could be in place for several months.
+Randomizing at the day level limits the problem of contamination arising from clients realizing that other clients get different contracts than theirs.
 It also limits potential  manipulation by appraisers, who in the presence of individual level randomization could potentially pick their preferred costumers from the line or tell them to wait until their desired contract shows up on the screen.
@@
 \vspace{.2in}
-\noindent \textit{Treatment Arms.} We have 5 different experimental arms, which differ in which contracts were offered on a given branch-day.
+\noindent \textbf{Treatment Arms.} We have 5 different experimental arms, which differ in which contracts were offered on a given branch-day.
 
 \begin{enumerate}
-    \item \textit{Status-quo} arm: consisted of branch-days offering the status quo contract described in Section \ref{context}, and only this contract (as was standard). 
-    \item \textit{Fee-Forcing} arm: consisted of branch-days offering only the monthly payment contract with a fee for late payment. 
-    \item \textit{Fee-Choice} arm: consisted of branch-days where the client was given \textit{a choice} between the monthly payment with fee contract, and the status quo contract.
-    \item \textit{Promise-Forcing} arm: consisted of branch-days which offered the monthly payment contract only, but where there was no fee penalty.
+    \item \textit{Status-quo forcing} arm: consisted of branch-days offering the status quo contract described in Section \ref{context}, and only this contract (as was standard). 
+    \item \textit{Fee-Forcing} arm: consisted of branch-days offering only the monthly installment contract with a fee for late payment as described above. 
+    \item \textit{Fee-Choice} arm: consisted of branch-days where the client was given \textit{a choice} between the monthly installment with fee contract, and the status quo contract.
+    \item \textit{Promise-Forcing} arm: consisted of branch-days which offered the monthly payment contract only, but where there was no fee for paying late.
 Instead, the client was made to sign a paper which said ``I promise to pay every month the corresponding sum of \_\_\_\_\_\_, on the dates \_\_\_\_\_\_, \_\_\_\_\_\_, and \_\_\_\_\_\_.
@@
 If I do not comply I would have broken my word.''.
-After signing, the promise was read to her by the appraiser.
-    \item \textit{Promise-Choice} arm: consisted on branch-days where the client was given \textit{a choice} between the Promise-Forcing and the Status quo contract.\footnote{We did not allocate equal number of days across arms, since we were interested in having more power in some of them.
-The days allocated to each -- in order-- were 84, 80, 93, 68, 82.}
+After signing, the promise was read to the client by the appraiser.
+    \item \textit{Promise-Choice} arm: consisted on branch-days where the client was given \textit{a choice} between the promise-forcing and the status quo contract.\footnote{We did not allocate equal number of days across arms, since we were interested in having more power in some of them.
+The branch days allocated to each -- in order-- were 84, 80, 93, 68, 82.}
 \end{enumerate}
 
-By comparing the \textit{Fee-Forcing} group vs \textit{Status-quo} group we estimate the causal effect of the commitment contract over the contract where the client can paying whenever they want in a 105 day period.
-On the other hand, having arms where clients could choose among these contracts allows us to study their demand for commitment.
-Note that a neoclassical consumer (with no intra-household concerns) would not voluntarily restrict her options of payment profiles (as in monthly payment contract) and be subject to fees since she can always replicate the monthly payment profile herself under the status quo contract if she so desired.
-The status quo contract gives her extra flexibility to respond to income shocks for instance.
+By comparing the \textit{fee-forcing} arm vs the \textit{status-quo} arm we estimate the causal effect of mandatory installment frequency which acts as a incentive to pay earlier vis-a-vis the pay-when-you-want contract.
+On the other hand, having arms where clients can choose among these contracts allows us to study client's demand for commitment to pay earlier.
+Note that a neoclassical consumer (with no intra-household concerns) would not voluntarily restrict her options of payment profiles (as in monthly payment contract) by being subject to fees, since she can always replicate the monthly payment profile herself under the status quo contract if she so desired.
+The status quo contract gives her extra flexibility to respond to negative income shocks.
 However, if clients have present biased preferences \textit{and} are sophisticated about them, they may choose the frequent payment contract as it has commitment value.
@@
 This design also allows us to test if promises work in a natural field environment which to our knowledge has not been done.
-Promises could have larger or smaller commitment value that a pecuniary fee, something that we test by comparing behavior in the \textit{Promise-Forcing}  vs \textit{Status-quo} arms.
+Promises could have larger or smaller commitment value that a pecuniary fee, something that we test by comparing behavior in the \textit{promise-forcing}  vs \textit{status-quo} arms.
 
@@
 The second threat is clients' understanding of contract terms.
-We realized that we needed the terms to be understood in order for choice to be meaningful, and for the monthly payment commitment to have bite.
+We realized that we needed the terms to be understood in order for choice to be meaningful, and for the monthly payment commitment contract to have bite.
 We had two `check-points' to do this.
 First, two ITAM students were present in each branch for the whole day during the duration of our experiment to explain to clients the contract terms.
-One of the aspects emphasized was that the frequent payment contract involved the commitment to pay \underline{each month} a third of the outstanding amount, and that there was a 2\% penalty fee (or the psychological cost of breaking a promise) for failing to do so.
+One of the aspects emphasized was that the frequent payment contract involved the commitment to pay \underline{each month} a third of the outstanding amount, and that there was a 2\% penalty fee (or, in the promise arms, the psychological cost of breaking a promise) for failing to do so.
 Figure \ref{ExplanatoryMaterial} translates a piece of the materials we used to explain the contracts (in this case a comparison sheet used in the Promise-Choice days to compare contracts terms side to side).
 The explanation took about 3-5 minutes and was pursued until the client said she understood the contract terms.
-Students then asked clients to explain back the contract terms.
+Students then asked clients to explain back the contract terms and corrected any misunderstandings.
 
@@
 We are fairly confident that the overwhelming majority of clients understood the contracts and made informed choices.
-As shows below, different contract terms did generate differential demand and differential behavior.
+As shown below, different contract terms did generate differential demand and differential behavior.
 Moreover, we can systematically predict demand based on consumer characteristics, beliefs and proxies for present biased preferences.
 
-\section{The effect of forcing into fee-commitment} \label{fee-commitment}
+\section{The effect of forcing clients into fee-commitment} \label{fee-commitment}
 
@@
 
-\noindent where $i$ refers to client, $j$ indexes branch, and $X_{ij}$ are branch and day-of-week fixed effects, as well as dummies for the number of arms a client fell into and number of pieces pawned during the whole experiment\footnote{If we restrict ourselves to pieces that fall in a single-arm (64\%) , then treatment reduces the financial cost by 5.7\%, increases the likelihood of recovering their pawn by 35\%, and increases the likelihood of repeat business by 66\%.
-\hl{ISAAC: me gustaria decir que ls resultados que citamos en el abstract se mantienen muy parecidos si tiramos los que tienen mas de un treatement arm?}}.
+\noindent where $i$ refers to client, $j$ indexes branch, and $X_{ij}$ are branch and day-of-week fixed effects.\footnote{There is a minority of of clients that pawned again and got assigned a different treatment.
+Results are robust to excluding them.
+In the regressions we include them and add a dummy indicating who are these clients.} %\footnote{There If we restrict ourselves to pieces that fall in a single-arm (64\%), then treatment reduces the financial cost by 5.7\%, increases the likelihood of recovering their pawn by 35\%, and increases the likelihood of repeat business by 66\%.}.
 Our main outcome variables $y_{ij}$ are measures of financial cost in pesos as defined in Section \ref{FC_def}, as well as an indicator variable for client $i$ losing her pawn.
@@
 \noindent \textbf{Financial Cost.} Figure \ref{fc_pro2}(a) reports $\beta$ coefficients and their 95\% confidence interval from estimating equation (\ref{basic_reg}) using different definitions of financial cost.
-The leftmost coefficient corresponds to using the appraised gold value of the pawned piece when the client loses it (not discounting makes virtually no difference).
+The leftmost coefficient corresponds to using the appraised gold value of the pawned piece (not discounting makes virtually no difference).
 The second coefficient uses the subjective value of the pawn instead.
-In both cases we find that being assigned to the fee-forcing commitment contract causes a large reduction in the financing cost the client incurred, of 9.5\% in the fist definition and 13.3\% in the second one.
+In both cases we find that being assigned to the fee-forcing commitment contract causes a large reduction in the financing cost the client incurred, of 9.5\% (\hl{\$XXX}) in the fist definition and 13.3\% (\hl{\$XXX}) in the second one.
 That is, we find that \textit{charging} clients a late payment fee  actually decreases total \textit{fee-inclusive} financing cost.
@@
 Given that the fee-forcing contract makes clients visit the branch more often (monthly), one may want a measure that includes those costs as well.
-Going in that direction, in a broader measure of costs, for each visit we add the self-reported transport cost\footnote{Here we had to restrict 66\% of the sample for which we had information on these.} plus a whole day's wage, multiplied by the number of visits.
-Adding a whole day's wage may be too conservative, but we still observe a reduction of this more comprehensive measure of cost.
+Going in that direction, in a broader measure of costs, for each visit we add the self-reported transport cost plus a whole day's wage, multiplied by the number of visits.
+Adding a whole day's wage may exaggerate cost, but we still observe a reduction of this more comprehensive measure of cost caused by the frequent payment contract, although we lose more than 1/3 of the observations and it is more imprecisely estimated.
 
@@
 Figure \ref{fc_pro2}(b) displays results from quantile regressions at the 15$^{th}$, 25$^{th}$, 50$^{th}$ 75$^{th}$, and 85$^{th}$ percentiles.
-All of them are negative and significant.
-Figure \ref{fc_pro2}(c) uses \cite{atheygrf} generalized random forests methodology to estimate person specific treatment effects and plots the distribution of those treatment effects.\footnote{\cite{atheygrf} use random forest of honest causal trees to estimate personalized treatment effects.
-The trees are such that at each leaf (partition determined by covariates) it unbiasedly estimates a treatment effect using treatment and control observations in that leaf.
+All of them are negative.
+Figure \ref{fc_pro2}(c) uses \cite{atheygrf} generalized random forests methodology to estimate person specific treatment effects, and plots the distribution of those treatment effects.\footnote{\cite{atheygrf} use random forests of honest causal trees to estimate personalized treatment effects.
+The trees are such that at each leaf (partition determined by covariates) we obtain an unbiased estimate of a treatment effect using treatment and control observations in that leaf.
 The optimal partition of leaves is that which minimizes expected mean squared error of treatment effects predictions out-of-sample.
@@
 \cite{atheygrf} show that their treatment effects are asymptotically normal, which allows us to construct confidence intervals for our treatment estimate in each leaf.
-We use command \texttt{causal\_forest} of the \texttt{grf} library in $R$.
-The parameters used were:
-
+} We find that more than 90\% of clients experienced financial cost savings in the fee-forcing group compared to the status-quo group.
+Figure \ref{HTE_fee_forcing} in the Appendix shows that the causal cost savings are largest for the more economically vulnerable, %that report at baseline that they have problems paying for services like water, electricity and rent,
+those that report being stressed, women, those take more time to go to the branch, and those displaying overconfidence about recovering their pawn (see Section \ref{behavioral} for our measure of overconfidence).
+%those that have to incur in higher transport cost to go to the branch  and that asked to be sent reminders to pay, this later one being one proxy of being inattentive or sophisticated present-biased.
+
+\vspace{.2in}
+\noindent \textbf{Pawn Recovery.} Figure \ref{fc_pro2}(d) plots estimated treatment effects of the fee-forcing commitment contract with the dependent variable being an indicator of losing the pawn in less than 230 days.
+The leftmost coefficient shows that the fee-forcing commitment contract increases the likelihood of recovering the pawn by 11pp (25.8\% of mean recovery).
+This is a large effect.
+It contrasts for instance with \cite{Pande} who find no effect of payment frequency on default in a group lending microfinance context.
+Figure \ref{fc_pro2}(e) shows the distribution of heterogeneous treatment effects for losing pawn: it shows that \textit{everybody's} likelihood of losing the pawn decreases.
+%Figure \ref{HTE_fee_forcing}(b) in the Appendix shows that those we classify as present biased, those that requested to be sent a reminder to pay, and those who have more problems paying for basic services experienced the largest increases on pawn recovery.
+
+%the second conditions on the population that paid any positive amount towards recovery of their pawn; the third conditions on having paid at least 30\% of the loan amount; the fourth conditions on the period covering the first cycle of the loan; the fifth on the period of the first cycle and paying any positive amount.
+
+\vspace{.2in}
+\noindent We conclude that penalizing borrowers for delinquency in a contract which has already has large penalties from default (losing the collateral in a highly collateralized loan) actually helps borrowers.
+
+\vspace{.2in}
+\noindent \textbf{Effects on other outcomes.} There are other (intermediate) outcomes that are impacted by being assigned to frequent payments.
+Table \ref{mechanisms} shows that the first payment happens 8 days earlier (column 1) in the fee-forcing arm than in the status quo one, and that the number of payments increases by 0.19 (column 2).
+Figure \ref{induced_to_pay_early} in the Appendix correlates heterogeneous treatment effects on financing cost and time of first payment and shows that those induced to pay earlier are also those that have larger induced savings in financial cost.
+A second finding is that treatment effects are concentrated on the intensive margin, as treatment does \textit{not} affect the fraction of clients who pay a positive amount (column 6).
+The percentage of the loan paid increases by 8 percentage points on average (column 7).
+Note however is that the percentage of the loan paid is not larger for those that end up losing the pawn (first row of column 8).
+
+\vspace{.2in}
+\noindent \textbf{Other sub-samples.} Going back to Figure \ref{fc_pro2}(a), we estimate some interesting correlations.
+The 4th coefficient from left to right conditions on those who paid a positive amount (in treatment and control).
+Although this is potentially an endogenous population, Table \ref{mechanisms} showed that there is no treatment effect on Pay$>0$.
+We were interested in this population to show that the effect is there for those who are serious about recovering their pawn.
+The fifth coefficient conditions on those that paid a fee in the fee-forcing group.
+In effect comparing this subset in treatment vs all of the control group\footnote{Results are similar if we condition in the control group on those who would have paid a fee given current behavior.
+Again we acknowledge these is an endogenous control and that the estimate is not a causal effect.}.
+We find even those that paid a fee in the fee-forcing contract end up paying a smaller financial cost that those in the status-quo contract.\footnote{This is not an experimental comparison as who pays a fee in the treatment group is a selected sample, but we found this relationship interesting nonetheless.} Figure \ref{fc_pro2}(c) shows that the increase in pawn recovery is robust to defining recovery using the first 120 days of the contract, or restricting to those paying a positive amount towards pawn recovery.
+
+\subsection{Effects of fee-forcing on repeat pawning}
+
+We have shown that clients are more likely to recover their pawn that virtually all of them incur in a lower financial cost  when assigned a monthly payment commitment contract with fees.
+This however does not necessarily show that they benefited in utility terms, and this is hard to show directly.
+If ---as suggested by \cite{Laibson2018}--- consumers used ``experienced utility'' as a guide to make future purchases, we conjecture that clients in the fee-forcing contract would be more likely to be repeat costumers vis-a-vis those that got status quo contract.
+This is indeed what we find.
+
+Figure \ref{reincidence} presents results of equation (\ref{basic_reg}) where the dependent variable is a dummy for the client to be a repeat costumer.
+We define a client in our experiment as a repeat costumer if, after experiencing at least 75 days of the respective treatment arm, she came back and pawned a different piece.\footnote{Results are robust to using other number of days besides 75.}  The left most coefficient shows that the causal effect of the fee-forcing contract on repeat pawning is an increase of 5pp in the probability of being a repeat costumer, this is 55\% on a mean re-incidence in the control group, with respect to those that got the status-quo contract.
+This is not explained by clients recovering their first pawn with higher probability in the fee-forcing contract and re-pawning this same one since we make sure it is another piece (besides only 37\% recover their piece in the fist 75 days in the fee forcing contract).
+The second coefficient restricts to the population who had larger (treatment effect) financial cost savings in their first pawn, and shows that the effect is twice as large for them.
+That is, those that benefit more from the fee-forcing contract are much more likely to repeat.
+%The coefficient on repeat pawning is just as big when we focus only 2nd pawns happening after the first was recovered (third coefficient ``fnr'').
+This is consistent with \cite{Laibson2018}'s conjecture that clients could be making decisions based on experienced utility.\footnote{The third coefficient conditions on the subsample that did recover their first pawn in both arms and finds a coefficient of 4pp.
+This is not a causal estimate as recovery is influenced by treatment, but we found it telling that the differences were similar to the causal estimate for the full sample.}
+
+We also implemented an exit survey which clients filled when recovering their piece.
+Unfortunately it had low response rates (7\%), and we take its results with a grain of salt.
+In this survey 63\% said they liked the frequent payment contract more than the status-quo one, and that is allow them avoid unnecessary expenses.
+
+\section{The effect of giving choice} \label{fee-choice}
+
+Section \ref{fee-commitment} showed that the fee-forcing commitment contract reduced financing cost across the board, and that consumers themselves seemed to like it once they tried it.
+In such a case, one would expect a strong demand for it, unless consumers underestimated these benefits.
+
+\subsection{Demand for the fee-forcing commitment contract} \label{sec:demand}
+
+To study demand for commitment, in one experimental arm, we let clients freely choose between the two types of contract: the fee-forcing commitment contract or the status-quo contract.
+The first result here is that in spite of broadly distributed benefits of the fee-forcing commitment contract we documented above, 90\% of clients chose \textit{not} to have it, they instead preferred the status-quo one.
+As explained above we are fairly confident this was not because a lack of understanding of the contracts.
+
+What can explain this low demand?
+This section discusses some hypothesis but lack of data limits what can be tested.
+One neoclassical explanation could be risk.
+Even if the fee forcing contract generates cost savings on average, clients with risk averse preferences may not demand it if they perceive higher risk from it.\footnote{Because they have not experienced the fee-forcing contract before, ambiguity aversion may play a role here too.} Alternatively, even risk-neutral agents may not demand it if the cost of lost flexibility is high.
+If they for example face large and frequent income shocks which make it hard to repay monthly.\footnote{We don't observe income shocks in our data, making is hard to quantify how important they are.
+90\% of those in the fee-forcing arm incurred a fee, which suggests that shocks are not uncommon (or clients inattentive).} Below we focus on some explanations of low demand, while Section \ref{model} seeks for theories that can explain all the findings, and reaches the conclusion that the present bias with naivete parsimoniously explains more results.
+
+\subsubsection{Behavioral economics explanations} \label{behavioral}
+
+The leading behavioral explanation in the literature for low demand for commitment is present biased preferences with naivete (e.g.
+\cite{Rabin2018}, \cite{John}, \cite{Laibson2018})  \cite{Laibson2015} shows that the lost flexibility resulting from a commitment contract can limit take-up especially severely when agents are naive about their self control problem.
+In our context if consumers are naive about their present bias, they would plan to save more (or spend less) than what they actually end up saving, thus making it be harder to recover their pawn.
+This under-saving will be mitigated in the fee forcing contract since the fee makes them save money and pay part of the loan periodically.
+Another behavioral explanation is that clients may underestimate the likelihood and severity of negative income shocks.
+Both of this explanations predict that clients will be overconfident about their likelihood of pawn recovery.
+Recall that in the control group the client's subjective probability of recovery is on average 93\%, while actual recovery is just 44\%.
+A further piece of evidence consistent with underestimating negative income shocks is that a large number of people (31\%) in the control group pay a positive amount toward pawn recovery but end up losing their pawn anyway.
+
+So, overconfidence of recovering the pawn is implied by both present bias preferences with naivete and upward bias in their income expectations.
+But does overconfidence actually predict low demand for commitment empirically?
+It does.
+We define as overconfidence as the reported subjective probability of recovery minus the predicted probability based on the client's characteristics, $P^s_i-\widehat{P_i(X_i)}$.\footnote{We predict $\widehat{P_i(X_i)}$ in two steps.
+In step one we use LASSO with with cross validation to tune the regularization parameter to select the most predictive variables.
+In the second step we estimate $\widehat{P_i(X_i)}$ using those variables in a logit model.
+The LASSO selected variables were type of pawn, female, age, has pawned before, has savings, participates in rotating savings, often feels tempted to change plans, would like to have a reminder to pay, and an economic vulnerability index.}  Table \ref{oc_reg} regresses a take-up dummy against an indicator $OC_i:=\mathbbm{1}(P^s_i-\widehat{P_i(X_i)}>0)$ for overconfidence and controls.
+Controls include branch and day of the week dummies, and additionally schooling, whether the client does a monthly budget plan, and a measure of intertemporal preference reversal analogous to that of \cite{Ashraf} as controls.\footnote{We find that 15\% of clients are classified as present biased using this measure of preference reversal.
+This level is similar to the number \cite{Ashraf} find.} Column 2 shows that in the choice-fee arm, being overconfident decreases the likelihood of demanding commitment by 16 percentage points, and column 4 shows that this is robust to including other controls.
+One interpretation of this result is that the overconfident think they do not need commitment, especially if that commitment may have the cost of fees.
+Columns 1 and 3 will be explained in Section \ref{promises}.
+Column 5 and 6 use as a dependent variable the estimated heterogeneous treatment effects of the fee-forcing contract vs the status quo one.
+They show that the overconfident benefit \textit{more} from the commitment contract, with 20\% (=\$24/\$121) more savings.
+
+\subsubsection{Neoclassical Alternatives} \label{neoclasical}
+
+\vspace{.1in}
+\noindent \textbf{Risk aversion.} We do not have measures of risk aversion in our necessarily short survey, which makes it hard to assess the hypothesis that risk aversion limits take-up of the fee-forcing contract.
+One way to proceed is to take the empirical distribution of financing cost ---$F_{fee}(FC)$--- as one the client would have faced had she chosen the the fee-commitment contract.
+We could then ask what would risk aversion have to be in order to justify the client choosing the fee-commitment contract distribution of costs over the distribution associated with the status quo contract, $F_{sq}(FC)$.
+We can then assess if the risk aversion needed would be reasonable or too high.
+This exercise of course assumes --as it is common in economics-- that clients know the distribution of financial cost, that it is common across consumers (although this can be relaxed), and that this cost distribution is the only difference among contracts.
+Fortunately for us, since one distribution first-order-stochastically dominates the other we do not need to calibrate a specific utility function or use a parametric distribution function in order to rank them in terms of expected utility.
+We use the fact that if $u(FC)$ is decreasing in $FC$ and $F_{fee}(FC) \geq F_{sq}(FC)$ for all $FC$, then $E_{fee}[u(FC)] \geq E_{sq}[u(FC)]$.
+That is any expected utility maximizer who dislikes paying higher financing cost, regardless of the concavity of his utility function, will prefer the fee-commitment distribution of financial cost.
+Figure \ref{ecdf_fc} in the Appendix shows that indeed $F_{fee}(FC) \geq F_{sq}(FC)$.
+Moreover, Table \ref{stochastic_dominance} shows that this holds also for an overwhelming majority of sub-populations.
+
+%To have a benchmark we implement a very simple calibration exercise in two steps.
+First, we fit a Weibull distribution to the distribution of financing cost, were the scale and shape parameters depend on client's and loan observable characteristics.
+We do this separately for the status quo contract and the fee-forcing contract, obtaining two distributions $f_{sq}(FC|X;\Gamma_1)$ and  $f_{fee}(FC|X;\Gamma_2)$ with different parameters $\Gamma_1$, $\Gamma_2$.
+Second, we assume a representative consumer with a CRRA utility function over financial cost, $u(FC)=\frac{1}{1-\theta}FC^{1-\theta}$.
+We then ask what would $\theta$ have to be for a consumer to prefer the status-quo contract.
+That is for which $\theta$'s would  $\int u(FC|\theta)f_{sq}(FC|X;\Gamma_1) dFC \geq \int u(FC|\theta)f_{fee}(FC|X;\Gamma_2) dFC $ hold?
+It turns out that it holds for risk aversion levels that are too high to be believable.
+That is, with our calibration, it seems unlikely that risk aversion is reducing demand for the fee-forcing contract.
+
+\vspace{.1in}
+\noindent \textbf{Lost flexibility.} A second neoclassical explanation for low take up is lost flexibility.
+That is, the fee-commitment contract may provide too much commitment which is costly both, (a) because the client may be forced to incur in late payment fees if he experiences a negative income shock, and also because (b) he may be unable to recover the pawn and his pre-payments.\footnote{Note that income shocks that affect the ability to pay the entire loan are a worry for both the fee-forcing contract and the status quo one, and should not make one contract more favorable than the other.} While we cannot rule out that income shocks combined with lost flexibility of the contract explain the low demand, we think it is unlikely.
+First, we showed above clients report a subjective probability of recovery of 93\% on average, which suggests they are not too worried about income shocks.
+Second, the fear of incurring fees is quantitatively not enough of a concern when compared to the savings they are experiencing.
+%Note that fees for late payment are not that high.
+In an average loan of 2,000 pesos the monthly payment is close to 700 pesos, and a fee of 2\% of that is 14 pesos (less than \$1 dollar).
+This is about \hlgr{1\%} of monthly per capita income of the first 3 deciles of Mexican \hl{household's} income distribution.
+%This compares favorably to the \hlgr{\$11.6 + \$62.3)} pesos transportation / transaction cost of one.
+To make this concrete we calculated what the financing cost of the fee-commitment contract would be if all its clients incurred in \textit{all} potential fees (while keeping payment profiles and pawn recovery constant), thus artificially inflating the cost.
+We then re-estimated the quantile treatment effects analogous to Figure \ref{fc_pro2}(b) with this inflated financial cost.
+%\footnote{Of course behavior may not be constant, but we believe this is a reasonable fist approximation.
+%It could be that having this small fee added to the balance discourages them to pay or makes it harder to pay back the loan.
+But the contrary may also happen, with the fee making them more determined to pay early.
+We would need a structural model of client behavior to estimate a full counterfactual.
+We suspect that such small fees would not generate large changes in behavior in a simple neoclassical model.}).
+Figure \ref{fc_allfee} presents the results.
+We find that even in this extreme scenario, tilted against the fee-forcing contract, the estimated effect still implies cost savings from the fee-forcing contract at the mean, 25$^{th}$, 50$^{th}$, and 75$^{th}$ percentiles.
+Note that the differences in financing cost already takes into account the fact that clients in the fee forcing contract sink more pre-payments than those in the status quo contract, and that those prepayments are lost if the loan is not fully paid back.
+Although these arguments are not definitive, they suggest that low demand for commitment may be driven by be more than the anticipation of lost flexibility.
+
+\vspace{.1in}
+\noindent \textbf{High time discounting.} In the summary statistics section we mentioned that clients in the status quo contract tend to wait until the last moment to pay to recover their pawns.
+Even among those that recover their pawn, only 20\% pay before the 90$^{th}$ day.
+Table \ref{mechanisms} showed that clients assigned to the fee-forcing contract front load their payments, starting their first payment earlier and finishing to pay earlier too.
+However, clients may dislike front loading payments if their discount rate is high.
+They may be willing to trade off a higher probability of losing their pawn for more \textit{back} loaded payments.
+This would explain both, why default rates are high and why demand for the fee-commitment contract is low.
+
+What would discount rates have to be in order to offset the reductions in financial cost effects we observe?
+We can calculate this number by looping across a grid of discount rates and reestimating equation \ref{basic_reg} with a financial cost dependent variable that uses the respective discount rate in the grid, and searching for the discount rate that makes $\beta$ equal zero.
+We do this and obtain that the discount rate that rationalizes a zero effect is 8,190 percent per year.
+We find this discount rate implausibly high even for this credit constrained population, and seriously casting doubt on high discount rates as explanation for low demand for commitment.%\footnote{In the baseline survey we give respondents a hypothetical choice between $100$ pesos tomorrow or $150$ pesos in one month (an implicit yearly interest rate of \hl{12,800\%}) and only 30\% chose the later one.}
+
+\subsection{The effect of choice on pawn recovery and financial cost} \label{effect_choice}
+
+When preferences or income streams are heterogeneous, and consumers are neoclassical, giving choice among contracts is a welfare increasing strategy.
+Consumers would chose the contract that best fits their needs.
+This holds also in most simple models of present bias preferences if consumers are sophisticated about their present bias.
+%Actually, it could be the case that the opportunity of choosing itself could affect behavior.
+But when consumers are overconfident about their ability to save cash to pay back the loan, free choice could be a sub-optimal policy from the point of view of the client's long run self, and match the clients with a more costly contract.
+
+Even if take up of the commitment-fee contract is low, the sole fact of having choice could potentially change behavior (\cite{Dalboetal:2010}, \cite{Sjostrometal:2018}).
+We find that giving clients the option of choosing among the fee-forcing and the status quo contract does \textit{not} lead to lower financial cost compared to forcing them into the status-quo contract, Figure \ref{fc_pro4}(a) hollow circles.
+Nor does it lead to higher pawn recovery, Figure \ref{fc_pro4}(c).
+The hollow circles in Figure \ref{fc_pro4}(show average effects for the different definitions of financial cost analogous to the ones described above.
+Figure \ref{fc_pro4}(b) shows further that the null effect happens for the 15$^{th}$, 25$^{th}$, 50$^{th}$ 75$^{th}$, and 85$^{th}$ percentiles.\footnote{The few that selected the fee-commitment contract (the solid black squares) do enjoy cost savings of 1005 pesos, which compares favorably to the 304 pesos in the fee-forcing arm (as a fraction of the loan the numbers are 41.5\% and 12.5\%), but this combines the selection and treatment effects.
+We cannot reject the that the ``effect'' on pawn recovery is of the same size for the fee-forcing arm and for those that selected into fee-forcing.} %Figure \ref{heterogeneous_te_4} plots the distribution of treatment effects and finds that the distribution offering choice actually \textit{increased} financial cost and default for about half of clients compared to being assigned the status-quo contract.
+Those tended to be the less economically vulnerable and more educated, \hl{women}, and those whose family typically asks them for money.
+Consistent with these findings, Figure \ref{reincidence} finds no effect on repeat purchases for the choice group.
+
+\subsection{The scope for private paternalism}
+
+This is not the first paper to find low demand for commitment, however it is the first we know of that can compare choice vs forcing.
+The fact that the fee-forcing contract lowers financial costs for all, together with the fact that only 10\% choose it must mean that many consumers are choosing contracts with higher financial costs for them.
+We can ask how many consumers seem to be making a cost increasing choice and how much money are they leaving on the table.
+To do this we conduct two exercises.
+
+\vspace{.2in}
+\noindent \textbf{Are there ``mistakes'' in choice?} Answering this question requires calculating a counterfactual: for each person in the choice arm we want to know how much cost savings a client would have if she chose the fee-commitment contract instead of the status quo contract.
+We do this in two steps.
+First, using the honest causal forests method of \cite{atheygrf} described above we calculate the causal effect on financing cost of getting the fee-forcing contract instead of the status quo contract for a client with characteristics $x_i$ \textit{in the forcing arms}, we call it $TE^{fee}_{i}$.
+There is no selection problem in the forcing arms.
+Second, using these estimates, we predict treatment effects for clients \textit{in the choice arm} using the $x_i$'s, and call it $\widehat{TE}^{fee}_{i}$.
+This is precisely the counterfactual we wanted.\footnote{This extrapolation of the treatment effects assumes that choice itself --conditional on a given contract-- does not affect behavior.
+Given the results in subsection \ref{effect_choice} we are comfortable with this assumption.
+Note that although the extrapolation is to another population, by randomization it is a statistically identical population.} Armed with this, we say that a client made a ``mistake'' if either she chose the status quo contract and her $\widehat{TE}^{fee}_{i}$ is negative (i.e.
+more cost saving from the fee contract), or if she chose the fee-commitment contract and $\widehat{TE}^{fee}_{i}$ is positive, meaning that financial cost are larger for the fee-commitment contract.
+When a client made a choice mistake, we say that the peso-size of it is $|\widehat{TE}^{fee}_{i}|$.
+
+%Using the forcing arms and extrapolating to the choice arms.
+%Then, we predict these treatment effects for everybody in the choice arm using characteristics $x_i$.
+Let $\widehat{TE}^{fee}_{i}$ be the predicted financial cost savings for person $i$ of choosing the fee-forcing contract rather than the status quo one, divided by the size of her loan (i.e.
+the negative value of the predicted treatment effect on financial cost for person $i$).
+$\widehat{TE}^{sq}_{i}$ is the analogous for the status quo contract.
+We define the choice of person $i$ to be a ``mistake'' if
+
+%\begin{equation}
+% \{ i \; \text{chose} \; sq \; \text{and} \; \;  \widehat{TE}^{fee}_{i}>\widehat{TE}^{sq}_{i} + z \} \; \text{or} \; \{ i \; \text{chose} \; fee \; \text{and} \; \;  \widehat{TE}^{fee}_{i}<\widehat{TE}^{sq}_{i} - z \}
+%\end{equation}
+
+Since the prediction of the treatment effect is an estimate and has noise, we do two things.
+First, we normalize $\widehat{TE}^{fee}_{i}$ by the value of the loan of person $i$ and introduce a threshold parameter $z$ and say that a choice is a ``mistake'' if the alternative contract would generate more than $z$ in savings.
+We vary from 0\% to 20\% of the value of the loan.
+Second, we take into account uncertainty in estimation of treatment effects and report results also using the extremes of the 95\% confidence interval bounds for $\widehat{TE}^{fee}_{i}$.
+
+Figure \ref{choose_wrong}(a) plots in the left Y-axis the fraction of clients that made a choice ``mistake'' and on the right Y-axis the peso size of the mistake.
+In the X-axis it varies the threshold $z$ of what we classify as a mistake.
+In this section we are concerned with lines in red color.
+When $z=0$, we calculate that about 80\% of clients in the fee-choice group chose contracts that induced \textit{higher} financial cost (95\% confidence interval [36,95]).
+Most mistakes are failures to choose the fee-commitment contract (92\%), while only 8\% of those who chose the fee-commitment contract would have been better in the status-quo one.
+The average mistake in pesos is \$238 (95\% confidence interval [131,427]).
+Figure \ref{choose_wrong}(b) separates the analysis for those we classify as overconfident about recovering their pawn (96\% of them) vs the rest.
+It shows that there are about 14 percentage points more mistakes in the overconfident population when $z=0$.
+
+All the above suggests that forcing clients into commitment contacts (i.e.
+private paternalism) may be welfare increasing for the overwhelming majority of clients.
+Figure \ref{choose_wrong}(c) calculates what fraction of clients would be made better off if we forced them to the fee-commitment contract: 92\% when $z=0$, and they would on average have savings of 232 pesos.
+This conclusion is in line with a recent paper by \cite{John}.
+In a savings context, she finds that when commitment in on the menu a majority of subjects wrongly choose to little commitment.
+She concludes this by observing high levels of default even with late payment fees, whereas we work directly with estimated treatment effects.
+
+\vspace{.2in}
+\noindent \textbf{Is there positive selection on treatment effects?} The previous exercise consisted on extrapolating treatment effects from the no-choice arms to the choice arm.
+Here we do the converse.
+First, we estimate a flexible model of take-up of the fee commitment contract \textit{in the choice arm} using random forests and obtain for a client with characteristics $x_i$ a probability $P(x_i)$ of choosing the fee-forcing contract.
+We then use this model to predict the counterfactual probability of client with characteristics $x_i$ choosing the fee-commitment contract in the no choice-arms if she would have been given the choice, what we call $\widehat{P(x_i)}$.
+Since our model for has a good out-of-sample fit with an out-of-sample AUC of 0.85 and an accuracy rate of 85\%, we think we are not introducing too much noise by this extrapolation.
+Second, armed with this prediction in the no-choice arms, we can ask the following: is it true that people with larger fee-forcing contract treatment effects (i.e.
+more cost savings) more likely to demand the fee-forcing contract?
+
+Figure \ref{choose_wrong}(d) plots $\widehat{P(x_i)}$ in the X-axis, and the heterogeneous we estimated in section \ref{TE_fee-forcing} in the Y-axis.
+If it was true that those with larger cost savings have larger demand for the fee-commitment contract, we would expect a negative slope (recall that more savings mean lower financial cost in the Y-axis).
+This is not what we find.
+Figure \ref{choose_wrong}(d) is a binscatter that splits the X-axis in 100 percentiles bins of predicted take-up probability and for each bin averaged the financial cost treatment effects.
+Using all clouds we estimate a slope of zero in the relationship.
+Using the 80 right most points, we estimate a \textit{positive} relationship.
+A positive relation means that those more likely to demand commitment are also those that had smaller benefits from commitment.
+This result is similar to \cite{Walters}, who finds that students that select into more effective schools are the ones with smaller treatment effects.
+\cite{Walters} uses distance to school as an instrumental variable for choice, while we use randomization to choice vs no-choice groups as our empirical strategy.
+
+\section{Viewing the results through a simple model} \label{model}
+
+This section uses a model to interpret our empirical results.
+The model is stylized but incorporates important features of our context.
+First, it allows for negative income shocks which we think are prevalent in this population (that's why they pawn in the first place)\footnote{71\% say they need the money for an emergency.}.
+The shock generates a cost of committing to monthly payments and could potentially be a reason for low take up.
+Second, it features clients with present biased time preferences and allows for naivete about them.
+As we discuss below these two features parsimoniously explain several facts about the context ---e.g.
+overconfidence in recovering the pawn, and large inefficient default---  and about the results ---e.g.
+forcing commitment seems to help, and that there is also some (although small) demand for commitment at no benefit for neoclassical consumers.
+Third, it incorporates the fact that the pawned piece is more valuable than the loan.
+Fourth, it allows for a simple way to model commitment afforded by late payment fees.
+Nonetheless, the model abstracts from several details of the context.
+Even with these abstraction it allows us to explain our six main results listed in Section \ref{explanations_recap} below.
+
+\subsection{A simple model} \label{model}
+
+We use the model of \cite{John} and refer the reader to that paper for more detail, justification of assumptions and some of the proofs.
+The model has three periods and linear utility.\footnote{This does not map perfectly to our 3 period contract, but it is enough to generate the results we need.} Period $t=0$ is a planning period where the client is either allocated to the status quo, the fee-forcing contract, or a choice between the two.
+In period 1 the client receives her income $y_1=1$, or gets zero with probability $\lambda$.
+She can consume ($c_1$) or save ($s_1$) that income.
+In period 2 the client gets her savings from period 1, and again receives income of either $y_2=1$, or zero with probability $\lambda$.
+In this last period, she decides whether to use income and savings for consumption $c_2$ and/or for paying back the loan of size $p \in(1,2)$ to recover the pawned piece valued at $b>p$.
+In this simple model we will impose a penalty fee $F>0$ in $t=1$ for the fee-commitment contract if the month's payment is not done.
+In period $t=0$ she evaluates her welfare as $E[c_1+c_2]$, were for simplicity we have set the time discount to one.
+We also assume the interest rate is one.
+We introduce present bias preferences by assuming the following utility function $U_t=c_t+\beta \: \sum_{k=t+1}^{2} E[c_k]$, with $\beta<1$ indicating present bias.
+A naive client perceives she is not so present biased and instead of $\beta$ uses $\hat{\beta} \in (\beta,1]$.
+
+Note that under these assumptions it is efficient at $t=0$ to take actions to recover the loan.
+Because $b>1$, paying back the loan requires that there is no negative shock in any period and that $s_1>0$, and because $\beta<1$ at $t=1$ the client will not send savings in excess of what is needed to recover the loan $s_1=p-1$.
+
+\vspace{.1in}
+\noindent \textbf{Result 1: Present bias consumers default more.} Under the status-quo contract, absent shock realizations, present biased clients (sophisticated or naive) with $\beta<\beta_{SQ}<1$ will lose their pawn, while clients with no present bias will not.
+Viewed from $t=0$ losing the pawns when there are no shocks is inefficient as $b>p$.\footnote{$\beta_{SQ}=\frac{p-1}{\lambda(p-1)+(1-\lambda)(b-1)}$.
+See Proposition 1 in \cite{John}.}
+
+\vspace{.1in}
+\noindent \textbf{Result 2: Forcing present-biased clients into the fee-commitment contract reduces default.} Imposing a fee $F>0$ for late payments weakly decreases default (for present biased clients only).
+It strictly decreases default if $F>F_{min}(\beta):=(p-1)-\beta[\lambda(p-1)+(1-\lambda)(b-1)]$.
+The larger the present bias the larger the $F$ required to induce pawn recovery.\footnote{The incentive compatibility constraint to generate savings to recover the pawn can be written as $1-(p-1)+\beta[\lambda(p-1)+(1-\lambda)(b-1)] \geq 1-F+\beta(1-\lambda)$.}
+
+\vspace{.1in}
+\noindent \textbf{Result 3: Demand for commitment.} Given $F>0$, (a) Neoclassical clients will never demand commitment.
+(b) Present-biased sophisticated clients will prefer the fee-forcing contract over the status quo contract $\iff$  $\lambda \: F<(1-\lambda)^2(b-p)$ and $F>F_{min}(\beta)$, that is $\iff$  $\beta \in [\beta_{min},\beta_{SQ}]$.\footnote{$\beta_{SQ}$ was determined in Result 1.
+$\beta_{min}$ is such that $F=F_{min}(\beta_{min})$.} (c) Analogously, naive clients will demand commitment $\iff$ $\hat{\beta} \in [\widehat{\beta_{min}},\beta_{SQ}]$, where $\widehat{\beta_{min}}<\beta_{min}$.
+So strongly naive clients will on the one hand demand more commitment than sophisticated clients since they believe (incorrectly) that a smaller fee will motivate them to pay.
+On the other hand they may demand less commitment since they think they can save and pay on their own.
+Whether they demand more or less than sophisticated clients depends on the empirical distribution of $\beta$ and $\hat{\beta}$.
+
+\vspace{.1in}
+\noindent \textbf{Result 4: Overconfidence.} Only naive clients will be overconfident about the probability of recovery.
+This will be true whether they have the status quo or the fee-forcing contract.
+Overconfidence is increasing in $\hat{\beta}$.
+
+\vspace{.1in}
+\noindent \textbf{Result 5: Welfare.} (a) Neoclassical consumers' welfare strictly decreases when we force clients into the fee-commitment contract instead of the status quo contract, and does not change when we offer a choice between them.
+(b) The welfare of sophisticated present biased consumers weakly increases when we give them choice, and it strictly increases  $\iff$  $\beta \in [\beta_{min},\beta_{SQ}]$, that is when they choose it themselves.
+Forcing them into the fee-commitment contract increases welfare $\iff$  $\beta \in [\beta_{min},\beta_{SQ}]$, otherwise it strictly decreases.
+So choice is better than forcing for sophisticates.
+(c) Forcing can be welfare improving for the naive.
+Indeed if $\hat{\beta}>\beta_{SQ}>\beta$ then forcing the fee-commitment contract increases welfare, and if $\hat{\beta} \in (\widehat{\beta_{min}},\beta_{min})$ then forcing the status quo contract increases welfare.\footnote{This result is different from that in \cite{John}.
+His context has individuals choosing the size of the fee.
+In that context naive clients will always chose the wrong fee size and default, therefore choice is always decreasing for the.
+In our context $F$ is fixed at 2\% of the balance due, and this implies that choice could be welfare improving for some naifs.}
+
+\vspace{.1in}
+\noindent \textbf{Result 6: Welfare and ex-post observed behavior.} If for client $i$ the fee-forcing contract causes higher pawn recovery, then we know the fee $F$ made her IC constraint binding, and therefore that $\hat{\beta_i}>\widehat{\beta_{min}}$.
+If in addition if it was the case that \hl{$\beta<\beta_{SQ}$}\footnote{\hl{Isaac, aqui tengo dos pregutas: (1) si es $\beta$ y no $\hat{\beta}$ verdad?
+(2) Para que una persona naive empeñe en el status quo tiene que ser que cree que va a recuperar no?
+Es decir tiene que ser $\hat{\beta}>\beta_{SQ}$ correcto?}} then the fee-forcing contract would have increased welfare for the naive.
+That is, our finding that the fee-forcing contract increases pawn recovery is a sign of higher welfare.
+
+\subsection{Interpretation}
+
+The model of \cite{John} is very parsimonious but powerful.\footnote{The model is sufficiently stylized that we think we would not gain much from estimating it.
+Furthermore we have no data on income shocks which figure prominently in the model.
+\cite{Ted} and \cite{Aprajit} are two very recent models that combine a field experiment with commitment contracts and estimation of present bias parameters.} First, it can explain why clients are overconfident in our data, namely by virtue of naivete about present bias.
+Under the model naivete is necessary to explain this.
+Second, it can also explain why the fee forcing contract induces lower default, but not for everyone: namely that it makes the IC constraint for the present biased binding while it was not binding in the status quo contract.
+Third, it can also explain why there is low demand for commitment even if it seems to improve welfare: namely that there is a small share of neoclassical and sophisticated clients, and at the same time naifs have  $\hat{\beta}>\beta_{SQ}$ and therefore think they can save on their own.\footnote{By Result 6 we can eliminate $F<F_{min}(\widehat{\beta}$) as an explanation.}.
+Fourth, it can explain why clients exposed to the fee-forcing contract are more likely to come back, namely that $\hat{\beta_i}>\beta_{SQ}>\beta$ and so their welfare increased as a result of being forced into the fee-commitment contract, and they may realize this.
+
+One could also easily introduce overconfidence in income shocks with $\widehat{\lambda} <\lambda$.
+This would leave default unchanged in both the status quo and the fee forcing contract.
+%since $F_{min}(\beta,\widehat{\lambda})<F_{min}(\beta,\lambda)$.
+The effect on demand for commitment is uncertain since on the one hand it decreases $\beta_{SQ}$ decreasing demand, but on the other a smaller $F$ is needed to make the IC binding, making commitment less costly.
+
+\subsection{Other potential explanations: recap} \label{explanations_recap}
+
+There may be other interpretation of the empirical findings. But the bar is high. An alternative explanation will need to explain the facts below:
+
+\begin{enumerate}
+\itemsep0em 
+\item Overconfidence about pawn recovery.
+\item High (although ex-post inefficient) default in status quo contract.
+\item Small demand for commitment...
+\item ...but positive demand for commitment.
+\item Forcing commitment saves money.
+\item Forcing commitment makes clients more likely to come back.
+\end{enumerate}
+
+\vspace{.1in}
+\noindent \textbf{Alternative 1: Strong prevalence of income shocks.} This could explain low demand for commitment (3) and (2), but not why forcing helps (5) and (6), nor why there is overconfidence (1), or why they come to pawn in the first place, try to pay back and then default (2).
+
+\vspace{.1in}
+\noindent \textbf{Alternative 2: High time discounting}.
+This could not explain (1) nor (6) nor (4).
+It could qualitatively explain (3).
+But as we say in section \ref{sec:demand} it cannot quantitatively explain (5) and (3) unless the discount rate is unbelievably high.
+
+\vspace{.1in}
+\noindent \textbf{Alternative 3: Risk aversion.} We already discussed and rejected risk aversion in section \ref{sec:demand}, although using strong assumptions in the process.
+We think this could still play a role and should be investigated in future research.\footnote{For instance by  providing insurance or by measuring risk aversion and using it to predict take up.}
+
+\vspace{.1in}
+\noindent \textbf{Alternative 4: Misunderstanding the contracts.}\footnote{This is a potential criticism of any paper offering choice, and one that is non-falsifiable if the critic has free reign to propose how the contracts are perceived in the subject's mind.} We were very aware of this and in the implementation a very strong effort was made for consumers to understand the contracts (see subsection \ref{implementation}).
+Note however that while clients making random mistakes could explain why 10\% demand commitment ---i.e.
+(3) and (4)--- they would not explain the rest of facts, nor why the promise-commitment (see below) had more take up that the fee-commitment, or why those with present bias and those that want a reminder to pay are more likely to make the ``error'' to demand commitment.\footnote{See Figure \ref{interactions_takeup} and Table \ref{Table_compliance}}
+
+\vspace{.1in}
+\noindent \textbf{Alternative 5: Forgetting to pay.} Frequent payments may act as a reminder to save and recover the pawn.
+This would try to explain (2) by appealing to people forgetting to pay, and (5), (6) and (4) by appealing to frequent payment acting as reminders.
+It would not explain (1) or (3) which are critical in the paper.
+However even for (2) it seems to us a stretch to explain people losing a valuable pawn by forgetting to pay.
+
+\vspace{.1in}
+\noindent \textbf{Alternative 6: Learning that they are more present biased than they thought.} This is essentially the same as our proposed explanation (i.e.
+not an alternative) with the additional prediction that more people will demand commitment if they just experienced it, an specially appealing one in light of finding (6).
+We are sympathetic to the learning hypothesis and in fact it is \cite{Alcohol}'s main conjecture about why he finds strong demand for commitment while most other studies don't.\footnote{Close to ninety percent of our subjects claim to have pawned before.
+We find that experience does not predict positive take up in our sample correlationally.} To test it we would ideally need to give choice to a group of people that randomly experienced the fee-commitment vs those that did not, and test if the former demand it more.\footnote{\hl{Isaac, podemos volver a tratar esto?
+Hace como 1 anio no nos salio pero quiero volver a tratar.}} Unfortunately we did not do this experiment and we have very limited data to try it: \hl{210 (6\%)} clients were given a choice in a second pawns in our experiment after being randomly assigned to the status quo or fee-forcing contract.
+
+\section{The effect of promises} \label{promises}
+
+One finding of the paper is that a rather small fee of 14 pesos on average changes behavior substantially: on the one hand generates average savings in the order of 300 pesos when forced, but on the other dissuades take up  when client have choice.
+In this context one would want a commitment device that generates higher take up while at the same time providing incentives for paying fast and recovering the pawn.
+One way to go would be to decrease the already small fee to say 1\% or lower.
+We decided to instead experiment with a non-pecuniary penalty, in the form of the psychological cost of breaking a promise.
+As explained in Section \ref{Experiment} the promise contract involved making a salient promise to repay monthly as part of their pawn contract in words and in written, and receive the speech by the appraiser about the importance of keeping her promise of paying monthly.
+
+A substantial literature documents that people don't like to break their promises, and are willing to incur in monetary loses in trying to keep them.
+To our knowledge this result has been replicated several times in laboratory contexts but not in a field setting like ours.
+If breaking a promise is perceived as having a lower cost than paying the 2\% fee, we predict that more people will have demand for the promise-commitment contract.
+We indeed find that take up is higher.
+Is this higher take up associated with smaller treatment effects though?
+Or does the promise have enough commitment power?
+
+\subsection{The demand for promise-commitment contracts and their effects}
+
+\vspace{.2in}
+\noindent \textbf{Demand}.
+It turns out that the demand for monthly payment contracts with a personal promise to pay monthly ---but no pecuniary penalty for not doing so--- induces higher demand by a factor of three compared with fee-commitment contract studied above: 31\% of clients offered a choice between the status quo contract and the promise-commitment contract chose commitment.
+This means that that the pecuniary fee indeed limited demand for commitment.
+In passing this means also that clients are responsive to contract terms and seem to understand the conditions.
+Interestingly however, the set of people who demand the promise-commitment contract are different from those that demanded the fee-commitment one.
+While in both cases the economically vulnerable demand less, in the case of the promise-commitment those that we classify as present biased, those that report that they frequently fall into temptation buying, and those that ask for reminders of payment are \textit{less} likely to demand the promise-commitment contract.
+This suggests that those taking up the promise commitment are not the ones needing the commitment.
+The opposite is true for those who take up the fee-commitment contract (see Figure \ref{interactions_takeup} in the Appendix).
+
+\vspace{.2in}
+\noindent \textbf{Effect of choosing to promise}.
+Figure \ref{fc_pro5}(a) finds that assigning clients to the choice-promise condition has a zero effect on financial cost on average (circles).
+We see no difference even for the endogenous group that chose to promise (squares).
+This null effect happens not only on average, but also by percentiles (not shown in Figure).
+There is also no effect on pawn recovery on (first coefficient in Figure \ref{fc_pro5}(b)), even for those that themselves choose to promise (squares).
+And the null effect carries over if we use the definition of recovery in less than 120 days, or for the (endogenous) subgroups that paid a positive amount or at least a third of their loans.
+Finally, there is no effect on repeat pawning (Figure \ref{reincidence}).
+
+\vspace{.2in}
+\noindent \textbf{Effects of forcing to promise}.
+Giving choice of whether to promise or not has the advantage of making promising an active decision by the client.
+In most of the the experimental literature promising is voluntary.
+But it has the disadvantage that we cannot measure the causal effect of promising, since those that promise are a selected sample.
+To evaluate the causal effect of promising, we compare people allocated to the promise-forcing arm (were all clients were forced to make a promise) against those in the status quo contract arm.
+Figure \ref{fc_pro5} (c) and (d) show the results.
+It documents null average treatment effects for both financial cost and recovering the pawn.
+Also there is no effect on repeat pawning.
+
+\vspace{.2in}
+\noindent The evidence presented in this section contrasts sharply with the evidence in laboratory experiments where people choosing to promise has a large effect on behavior and were people keep their promises.
+While clients are more enthusiastic about the promise-commitment contract than the fee-commitment one in the sense of tripling take-up, the promise contract provides no commitment.
+Results for the promise arms are consistent with \cite{Ted} and \cite{John} who find that people are likely to demand commitment when the commitment is too week to have beneficial effects.
+
+%\vspace{.2in}
+%\noindent \textit{Size of ``mistakes''.} Although promises have very muted effects, there is some heterogeneity (see Figure \ref{heterogeneous_te_3}).
+This opens the space for choice mistakes.
+Figure \ref{choose_wrong} shows that indeed there are some mistakes, but these are smaller that for the fee-choice arm.
+When $z=0$, we calculate that about 60\% of clients in the promise-choice group chose contracts that induced \textit{higher} financial cost.
+In particular \hlgr{97\%} of those that chose the status-quo contract would have been better in the promise-commitment contract, while \hlgr{3\%} of those who chose the promise-commitment contract would have been better in the status-quo one.
+On average they spend \$250 pesos on extra financing cost.
+
+\section{Conclusion} \label{conclusion}
+
+In a pawnshop borrowing context, we studied whether forcing borrowers into frequent payment commitment contracts reduces their borrowing costs, compared to a contract that does not provide commitment to pay monthly.
+Even though we are charging them fees, their borrowing cost are actually reduced by 9.5\%, and they recover their pawn with 25.8\% higher likelihood.
+Moreover they themselves seem to like this contract, as they are 55\% more likely to come back and pawn again when they get it.
+That is, commitment matters and it seems beneficial.
+Examining treatment heterogeneity we find that almost all clients benefit from the commitment contract.
+
+However when given choice between the commitment and the status quo contract only 10\% choose the former one and thus forgo important benefits.
+This strongly suggests that ``private paternalism'', a policy that advances an individual's interests by restricting her freedom, is beneficial in our context.
+We provide a quantification of the size of unrealized benefits that arise when clients have choice.
+Methodologically, to our knowledge this is the first paper in economics that uses machine learning methods to estimate personalized counterfactual treatment gains and ask whether treatment take up is positively selected.
+
+Needless to say, pawnshop borrowing likely attracts particularly unsophisticated clients (millions of them).
+Choice may fare better in other contexts.
+Choice may also fare better with other contracts besides the fee-commitment one.
+We experimented with a ``softer'' commitment contract in the form of a personal promise, and found that although promise-commitment contracts do indeed elicit more interest they did not cause changes in behavior.
+
+We see three lines of further work that are of interest.
+First, investigate why the fee-commitment contract had such low demand in spite of its across-the-board benefits.
+In particular if naivete about self control problems, biased expectation about income shocks, or ambiguity aversion play a role.
+Second, whether other types of contracts ---for instance less coarse choice menus--- could induce larger demand and better performance.
+Third, whether individuals choosing to borrow from pawnshops are more present biased and naive than similar individuals borrowing from other types of lenders.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\pagebreak
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%BIBLIOGRAPHY
+
+\clearpage
+\bibliographystyle{authordate1}
+%\bibliographystyle{amsalpha}
+%\bibliographystyle{AER}
+
+\bibliography{References}
+
+%\FloatBarrier
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\newpage
+\singlespacing
+
+\section{Tables}
+
+\begin{table}[H]
+\caption{Summary statistics and Balance}
+\label{SS}
+\begin{center}
+\scriptsize{\input{./Tables/SS.tex}}
+\end{center}
+ \scriptsize
+This table presents balance tests for the administrative data (Panel A) and survey data (Panel B).
+Each column corresponds to an arm of the experiment: control (status quo contract), no choice with fee, no choice with promise, choice among both contracts where the commitment contract has fee, and choice among both contracts where the commitment contract involves only a promise.
+The last column show the p-value of an F-test of the hypothesis that the mean across arms for that variable is the same across the 5 arms.
+Randomization was done at the branch-day level.
+By design the observation are not exactly equal cross arms as we were more interested in detecting effects in the choice-fee arm and less so in the no-choice-promise.
+Loan amount is the peso amount given to the client; Monday is the fraction of loans given on a Monday; number of pledges is the number of loans given in each arm.
+That it is balanced shows that there was no detectable selection across arms when clients found out what was the contract.
+In Panel B: woman indicated whether the client is female, age of the client is measured in years; has pawned before is a dummy=1 if the client declares to have pawned before (although not necessarily with Lender $P$).
+The subjective probability of recovery was elicited a la Manski, from 0 to 100 what is the probability that you will recoup your pawn.
+High-school is a dummy that indicates if the client has completed high school.
+Finally, the response rate is the percentage of clients in the admin data for whom we have a baseline survey.
+%\textit{Do file: } \texttt{ss.do}
+\end{table}
+
+\pagebreak
+
+\begin{table}[H]
+\caption{Overconfidence: Take-up and Treatment Effects}
+\label{oc_reg}
+\begin{center}
+\scriptsize{\input{./Tables/oc_reg.tex}}
+\end{center}
+ \footnotesize This table shows the parameter estimates of $y_i = \alpha + \beta \: OC_i + X_i'\gamma + \epsilon_i$, where $OC_i:=\mathbbm{1}(P^s_i-\widehat{P_i(X_i)}>0)$ is an indicator for the subjective probability of recovery being larger that the predicted one.
+In columns 1-4 $y_i$ is a dummy for whether the client $i$ chose to have the commitment contract in the respective choice arm, and in columns 5 and 6 $y_i$ is the heterogeneous treatment effect for financial cost (in pesos) estimated by comparing the fee-forcing vs status quo arms in Section \ref{TE_fee-forcing}.
+Columns 1 and 3 are estimated for the promise-choice arm, while columns 2 and 4 are estimated for the fee-choice arm.
+%\textit{Do file: } \texttt{oc.do}
+\end{table}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\section{Figures}
+
+\begin{figure}[H]
+     \caption{Experiment description}
+    \label{exp_description}
+    \begin{center}
+    \begin{subfigure}{.50\textwidth}
+      \caption{Timeline of the experiment}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/timeline_suc_exp_extended.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.45\textwidth}
+    \caption{Experiment arms}
+       \centering
+      \includegraphics[width=\textwidth]{Figuras/exp_arms.PNG}
+    \end{subfigure}
+    \end{center}
+         \scriptsize Panel (a) displays in black arrows the period covered by our administrative data: from August 6th 2012 (30 days before the experiment began) to August 13th 2013.
+The gray lines arrows correspond to the dates of implementation of the experiment.
+We finished the experiment earlier in branches 1 and 2 because we realized that we would have enough sample size with the remaining branches and save on operational costs.
+Panel (b) shows our 5 treatment arms: control (status quo contract), no choice with fee, no choice with promise, choice among both contracts where the commitment contract has a fee, and choice among both contracts where the commitment contract involves only a promise.
+Within each arm it displays the number of observations.
+And  for the choice groups it splits the sample size into those who chose the commitment contract (shaded blue triangle) and those that did not (un-shaded triangle).
+%\textit{Do file: }  \texttt{timeline\_suc\_exp.do}
+\end{figure}
+
+\begin{figure}[H]
+     \caption{Explanatory Material: Promise-Choice Days}
+    \label{ExplanatoryMaterial}
+    \begin{center}
+    \begin{subfigure}{0.8\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/MicaChoiceDonde.png}
+    \end{subfigure}
+    \end{center}
+    \scriptsize
+        This is a (translated) sample information mica shown to clients in choice-promise days.
+The real ones were twice the size of this figure and were laminated.
+Different ones were shown in each treatment arm.
+\end{figure}
+
+\begin{figure}[H]
+     \caption{Financial cost}
+    \label{fc_hist}
+    \begin{center}
+    \begin{subfigure}{.45\textwidth}
+      \caption{In pesos}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_fc.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.45\textwidth}
+    \caption{As a fraction of the loan}
+       \centering
+      \includegraphics[width=\textwidth]{Figuras/hist_fc_perc_loan.pdf}
+    \end{subfigure}
+    \end{center}
+         \scriptsize
+         Panel (a) presents a histogram of financial cost for the control group.
+Financial cost is defined as the sum of payments made by a client towards recovering her pawn + the cost of the pawned piece when she ends up losing it.
+In the paper we use different costs of losing the pawn: its value in gold, or the self reported subjective (e.g.
+jewelry may have sentimental value).
+This Figure uses the gold value.
+We plot separately the financial cost for those who lose the pawn (blue) and those that recover it (transparent).
+Panel (b) is analogous but we normalized the financial cost dividing it by the loan size.
+%Given that the loan lasts close to 90 days, bringing payments to present value makes little difference.
+      %\footnotesize{ } \textit{Do file: }  \texttt{hist\_fc.do}
+\end{figure}
+
+\begin{figure}[H]
+    \caption{The effect of the fee-forcing treatment}
+    \label{fc_pro2}
+    \begin{center}
+    \begin{subfigure}{0.42\textwidth}
+        \caption{Financial cost}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/fc_te_pro_2.pdf}
+    \end{subfigure}
+        \begin{subfigure}{0.42\textwidth}
+        \caption{Financial cost (quantile reg)}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/fc_quantile_pro_2.pdf}
+    \end{subfigure}
+
+        \bigskip
+
+    \begin{subfigure}{0.42\textwidth}
+        \caption{Financial cost (HTE)}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_2.pdf}
+    \end{subfigure}
+    ~
+    ~
+    \bigskip
+    \begin{subfigure}{0.42\textwidth}
+        \caption{Lost pawn}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/def_te_pro_2.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.42\textwidth}
+    \caption{Losing Pawn}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_2.pdf}
+    \end{subfigure}
+
+    \end{center}
+        \scriptsize 
+        This figure shows the estimated treatment effect of ``forcing'' the frequent payment commitment contract using fees, compared to the status-quo (control) for  financial cost (Panel a), quantiles of financial cost (Panel b), and for an indicator of losing the pawn (Panel c).
+In Panel (a) each dot represents the estimated treatment effect for a different definition of financing cost, or for a different sub-population, and its 95\% confidence interval.
+From left to right, the first effect corresponds to using the gold value of the pawned piece in the definition of financial cost and discounting the payments to present value using a 7\% monthly rate; the second uses the subjective value of the pawn; the third is analogous to the second but adds transaction cost (transport+1 day's wage) per visit; the fourth conditions on the population that paid any positive amount towards recovery of their pawn; the fifth conditions on the sub-population of the treatment group that paid a fee and compares these to all the control group; the sixth conditions on the intersection of the previous two sub-populations.
+Panel (b) plots the effects on different quantiles of the distribution of financial cost (using the first definition): 15th, 25th, 50th, 75th, 85th percentile.
+        Panel (c) plots the distribution of the heterogeneous treatment effects on financial cost, estimated using \cite{atheygrf}.
+The distribution plots the FC treatment effect for the interval $[\mu-2\sigma,\mu+2\sigma]$ to ignore the outliers.
+Panel (d) Measures the effect of treatment on the likelihood of losing their pawn.
+The first coefficient compares all the treatment group vs all the control; the second conditions on the period covering 120 days.
+The third conditions on the population that paid any positive amount towards recovery of their pawn; the fourth conditions on having paid at least 30\% of the loan amount.
+% the effect on ``repeat purchase''.
+That is likelihood of doing an additional pawn (in treatment vs control) after having been subjected to treatment for at least 75 days.
+The second coefficient estimates the regression conditional on recovering the pawn \hl{in both treatment and control}, and the rightmost coefficient compares those above the median treatment effect in financial cost savings, \hl{versus all the control group.}
+      %\textit{Do file: }  \texttt{fc\_te.do, def\_te.do, fc\_quantilereg.do}
+\end{figure}
+
+\begin{figure}[H]
+        \caption{Effects on repeat purchasing}
+    \label{reincidence}
+    \begin{center}
+        \centering
+        \includegraphics[width=0.6\textwidth]{re_te.pdf}
+    \end{center}
+     \scriptsize This figure shows the estimated effects on repeat purchasing of the four treatment arms (fee-forcing, choice-fee, fee-promise, choice-promise) compared to the status-quo control group.
+It shows robustness of the effects by focusing on different sub-populations.
+The leftmost coefficient compares all the fee-forcing group against all status quo group.
+The second coefficient conditions on the first pawn not being recovered when the second was pawned.
+The third coefficient uses all clients (in both the fee-forcing and the status-quo arms) who had an estimated heterogeneous treatment effect above the median.
+Conditioning on this set keeps the sample balanced across arms and therefore still allows for a causal interpretation.
+For the choice arm we present three coefficients: coefficients represented by a circle compare all those offered choice to all those in the status quo arm, thus estimating a causal effect.
+Coefficients in triangles and squares represent those that self-select into the fee or promise arms and compare this subset against the whole status quo arm.
+They therefore contain a selection effect together with the treatment effect and cannot be interpreted causally.
+      %\footnotesize{ \textit{Do file: }  \texttt{re\_te.do}
+\end{figure}
+
+\begin{figure}[H]
+    \caption{The effect of choice between fee-commitment and status quo}
+    \label{fc_pro4}
+    \begin{center}
+    \begin{subfigure}{0.45\textwidth}
+        \caption{Financial cost}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/fc_te_pro_4.pdf}
+    \end{subfigure}
+        \begin{subfigure}{0.45\textwidth}
+        \caption{Financial Cost (quantile reg)}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/fc_quantile_pro_4.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.5\textwidth}
+
+        \bigskip
+        \bigskip
+
+        \caption{Lost Pawn}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/def_te_pro_4.pdf}
+    \end{subfigure}
+    \end{center}
+        \scriptsize
+        This figure is analogous to Figure \ref{fc_pro2}.
+It measures the effect of being given \textit{choice} between the frequent payment commitment contract with fees and the status-quo contract, versus being \textit{``forced''} into the status-quo contract (control).
+Again it focuses our two main outcomes: financial cost and an indicator for losing the pawn.
+Circles present the treatment effects.
+The figures also presents differences in these two outcomes for those who chose the frequent payment commitment contract versus the whole control group (squares-NSQ), and also for those who chose the status quo contract versus the whole control group (triangles-SQ).
+Note that these two comparisons are not pure causal effects since people who chose the frequent payment commitment contract may be different from those that do not.
+That is: the squares and triangles combine selection and treatment effects.
+Finally, for comparison purposes, the blue diamond displays the effects of forcing them into the frequent payment commitment contract and are just transcribed from Figure \ref{fc_pro2} above.
+      %\textit{Do file: }  \texttt{fc\_te\_choice\_dec.do, def\_te\_choice\_dec.do, fc\_quantilereg\_choice\_dec.do}
+\end{figure}
+
+\begin{figure}[H]
+        \caption{Distribution of Overconfidence}
+    \label{oc_hist}
+    \begin{center}
+        \centering
+        \includegraphics[width=0.55\textwidth]{Figuras/oc_hist.pdf}
+    \end{center}
+    \scriptsize
+     In the baseline survey at the branch, before the client knew the contract of had the pawn appraised, they were asked from 0 to 100, how likely is that they would be able to recover their pawn if pawned.
+We generate a variable we call overconfidence (OC) defined as the reported subjective probability of recovery minus the predicted probability ($P^s_i-\widehat{P_i(X_i)}$).
+We predict $\widehat{P_i(X_i)}$ using LASSO as explained in the text.
+This figure uses all observations for which we have data on $P^s_i$ and $X_i$ from the baseline survey.
+     %\textit{Do file: }  \texttt{oc.do}
+
+\end{figure}
+
+\begin{figure}[H]
+    \caption{Choice of contracts and treatment effects}
+    \label{choose_wrong}
+    \begin{center}
+        \begin{subfigure}{0.45\textwidth}
+        \caption{Chose wrong}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/line_cw_fc_te_cf.pdf}
+
+    \end{subfigure}
+        \begin{subfigure}{0.45\textwidth}
+        \caption{By overconfidence/naivete}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/line_cw_fc_te_cf_OC_fee.pdf}
+
+    \bigskip
+
+    \end{subfigure}
+        \begin{subfigure}{0.45\textwidth}
+        \caption{\% better when forced to fee-commitment}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/line_better_forceall_fc_te_cf.pdf}
+
+    \end{subfigure}
+        \begin{subfigure}{0.45\textwidth}
+        \caption{\footnotesize{Effect of losing pawn vs predicted take-up}}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/takeuppr_def.pdf}
+    \end{subfigure}
+
+    \end{center}
+        \scriptsize
+        In Panel (a) we estimate what the treatment effect of the commitment contract \textit{would have been} for all subjects in the choice arm if they had been forced into the fee-commitment contract.
+To do this we proceed in two steps.
+First, we estimate treatment effects in the forcing arm by comparing the fee-forcing arm against the status quo arm.
+We let these effects be heterogeneous as a function of our $x$'s using \cite{atheygrf}'s methodology of causal forests.
+Second, we extrapolate these treatment effects based on the choice arm using the same $x$'s.
+Once we have personalized counterfactual treatment effects in the choice we calculate what fraction of subjects in the choice arm incurred in financial costs that are  $> z$\% than if they had chosen the opposite contract of what they actually chose, were $z$\% is defined as a fraction of the loan.
+$z$\% is a level of tolerance we can vary and we plot it in the X-axis.
+The left Y-axis measures the fraction of subjects that would have been better by a margin of $z$\% if they changed their choice, and the right Y-axis measures the amount of money ``left on the table''.
+The thinly dotted lines represent 95\% confidence intervals.
+Panel (b) is analogous to Panel (a) except that it does the exercise separately for clients we classified as overconfident ($OC_i:=\mathbbm{1}(P^s_i-\widehat{P_i(X_i)}>0))$ and those we classified as not overconfident.
+Panel (c) simulates what percentage would be better by at least $z$ if we forced everybody of those in the fee-choice arm into the fee-commitment contract.
+Panel (d) asks whether it is the case that people with larger causal savings from the fee-forcing contract would be more likely to select that contract.
+To do this we proceed in two steps as well.
+First we estimate a flexible model of take-up of the fee commitment contract \textit{in the choice arm} using random forests, and from this model obtain a probability $P(x_i)$ of choosing the fee-forcing contract for a client with characteristics $x_i$.
+We extrapolate this model to clients in the fee-forcing arm to estimate what would they have chosen if we had given them choice.
+Figure (d) plots $\widehat{P(x_i)}$ in the X-axis using a binscatter that splits the X-axis in 100 percentile bins.
+The Y-axis plots the heterogeneous treatment effects of the fee forcing contract on the probability of losing the pawns (more negative means then more likely to recover it), averaged for the respective x-axis bin.
+Positive assortative selection would mean a negative relationship: those who benefit more by treatment and lose the pawn less are more likely to choose it.
+Using all bins we estimate a slope of zero in the relationship.
+Using the 80 right most points, we estimate a \textit{positive} relationship.
+        %\textit{Do file: }  \texttt{effect\_contr\_takeup.do, choose\_wrong\_quant\_wrong.do, choose\_wrong\_quant\_wrong\_decomposition.do}
+\end{figure}
+
+\begin{figure}[H]
+    \caption{The effect of promises}
+    \label{fc_pro5}
+    \begin{center}
+
+    \begin{subfigure}{0.45\textwidth}
+        \caption{Financial cost -- Promise-forcing}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/fc_te_pro_3.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.45\textwidth}
+        \caption{Losing Pawn -- Promise-forcing}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/def_te_pro_3.pdf}
+    \end{subfigure}
+
+    \bigskip
+    \bigskip
+
+        \begin{subfigure}{0.45\textwidth}
+        \caption{Financial cost -- Choice}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/fc_te_pro_5.pdf}
+    \end{subfigure}
+        %\begin{subfigure}{0.45\textwidth}
+        %\caption{Quantile regression}
+        %\centering
+        %\includegraphics[width=\textwidth]{Figuras/fc_quantile_pro_5.pdf}
+    %\end{subfigure}
+    \begin{subfigure}{0.45\textwidth}
+        \caption{Losing Pawn -- Choice}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/def_te_pro_5.pdf}
+    \end{subfigure}
+
+    \end{center}
+    \scriptsize
+    Panels (a) and (b) in this figure show the estimated treatment effects of ``forcing'' the frequent payment commitment contract using promises, compared to the status-quo (control) for financial cost (Panel a), and for an indicator of losing the pawn (Panel b).
+Panels (c) and (d) are analogous but focus on the effect of giving choice between frequent payment commitment contract using promises and the status quo contract.
+In Panel (a) each dot represents the estimated treatment effect for a different definition of financing cost, or for a different sub-population, and its 95\% confidence interval.
+From left to right, the first effect corresponds to using the gold value of the pawned piece in the definition of financial cost and discounting the payments to present value using a 7\% monthly rate; the second uses the subjective value of the pawn; the third is analogous to the second but adds transaction cost (transport+1 day's wage) per visit; and the fourth conditions on the population that paid any positive amount towards recovery of their pawn.
+Panel (b) plots the effect of not recovering the pawn: the leftmost coefficients compares all those assigned to the promise-forcing arm vs all those in the status quo contract, where the dependent variable=1 if the client has not recovered the pawn 230 days after pawning.
+The next coefficient defines the dependent variable=1 if the client has not recovered the pawn 120 days after pawning.
+The third coefficient conditions on paying a positive amount, and the fourth conditions on paying at least 30\% of the loan.
+Panels (b) and (c) measure the effect of being given \textit{choice} between the frequent payment commitment contract with promise and the status-quo contract, versus being \textit{``forced''} into the status-quo contract (control).
+Again it focuses our two main outcomes: financial cost and an indicator for losing the pawn.
+Circles present the treatment effects.
+The figures also presents differences in these two outcomes for those who chose the frequent payment commitment contract versus the whole control group (squares-NSQ), and also for those who chose the status quo contract versus the whole control group (triangles-SQ).
+That is: the squares and triangles combine selection and treatment effects.
+      %\footnotesize{ } \textit{Do file: }  \texttt{fc\_te\_choice\_dec.do, def\_te\_choice\_dec.do, fc\_te.do, def\_te.do }
+\end{figure}
+
+%\begin{figure}[H]
+%    \caption{The effect of the promise-forcing treatment}
+%    \label{fc_pro3}
+%    \begin{center}
+%        \begin{subfigure}{0.45\textwidth}
+%        \caption{Quantile regression}
+%        \centering
+%        \includegraphics[width=\textwidth]{Figuras/fc_quantile_pro_3.pdf}
+%    \end{subfigure}
+%    
+%    \end{center}
+%             \footnotesize \textit{Notes: } 
+%      \footnotesize{ } \textit{Do file: }  \texttt{fc\_te.do, def\_te.do, fc\_quantilereg.do}
+%\end{figure}
+
+\newpage
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% APPENDIX TABLES
+
+\setcounter{table}{0}
+\renewcommand{\thetable}{A\arabic{table}}
+
+\setcounter{figure}{0}
+\renewcommand{\thefigure}{A\arabic{figure}}
+
+\setcounter{section}{0}
+\setcounter{subsection}{0}
+\renewcommand\thesection{A\arabic{section}}
+\renewcommand\thesubsection{\thesection\arabic{subsection}}
+
+\appendix
+
+\section{APPENDIX}
+
+\subsection{Some materials}
+
+\vspace{.1in}
+\begin{figure}[H]
+     \caption{Contract Terms Summary, and Promise Slip}
+    \label{PaperSlip}
+    \begin{center}
+    \begin{subfigure}{0.65\textwidth}
+    \caption{Elapsed days to first payment}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/TicketLenderP.png}
+    \end{subfigure}
+
+    \vspace{3ex}
+    \begin{subfigure}{0.45\textwidth}
+    \caption{Elapsed days to first payment}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/Personal Promise.png}
+    \end{subfigure}
+    \end{center}
+    \scriptsize
+        The top of this figure is a sample receipt that was given to clients that got assigned to the fee-forcing contract (the font and format were changed to protect Lender's P identity).
+We want to highlight the salience of some items.
+First the title clearly indicated which contract the client has (arrow 1).
+Second, in the case of the fee contract it clearly indicates that there is a fee for paying late equivalent to 4\% of the value of the monthly payment (arrow 2).
+Third, there is a calendar for payments clearly specifying the dates and amounts to pay each month.
+The bottom panel of the figure shows a ``promise slip'', the paper that those who were assigned (or chose) to the monthly payment with promise had to sign to make the promise salient.
+It emphasizes that the client is giving his word, and that the promise is not a legal document.
+\end{figure}
+
+\subsection{Pictures}
+
+\vspace{.1in}
+\begin{figure}[H]
+     \caption{Some Pawnshops}
+    \label{PawnshopPicture}
+    \begin{center}
+    \begin{subfigure}{0.5\textwidth}
+    \caption{Appraiser/tellers inside a pawnshop}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/empenio9.png}
+    \end{subfigure}
+
+    \vspace{3ex}
+    \begin{subfigure}{0.5\textwidth}
+    \caption{Pawnshop}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/empenio2.png}
+    \end{subfigure}
+       \vspace{3ex}
+
+    \begin{subfigure}{0.5\textwidth}
+    \caption{Lost pawns which are for sale}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/empenio3.png}
+    \end{subfigure}
+       \vspace{3ex}
+
+    \begin{subfigure}{0.5\textwidth}
+    \caption{Pawnshop}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/empenio11.png}
+    \end{subfigure}
+
+    \end{center}
+    \scriptsize
+        This figure  shows pictures of pawnshops in Mexico city. They do not necessarily coincide with Lender P for confidentiality. 
+\end{figure}
+
+\vspace{.1in}
+\begin{figure}[H]
+     \caption{Gold buyers next to pawnshops}
+    \label{GoldBuyers}
+    \begin{center}
+    \begin{subfigure}{.8\textwidth}
+    \caption{Gold buyer next to pawnshop 1}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/empenio7.png}
+    \end{subfigure}
+
+    \vspace{3ex}
+    \begin{subfigure}{.8\textwidth}
+    \caption{Gold buyer next to pawnshop 1}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/empenio8.png}
+    \end{subfigure}
+       \vspace{3ex}
+
+    \end{center}
+    \scriptsize
+        This figure shows pictures of gold buyers next to pawnshops in Mexico city. They do not necessarily coincide with Lender P for confidentiality. 
+\end{figure}
+
+\newpage
+
+%\begin{figure}[H]
+%        \caption{Booklet with product information}
+%    \label{micas}
+%    \begin{center}
+%        \centering
+%        \includegraphics[width=\textwidth]{micas.pdf}
+%    \end{center}
+%     \footnotesize \textit{Notes: } 
+%      \footnotesize{ }
+%\end{figure}
+
+%\begin{figure}[H]
+%     \caption{Booklet with product information translated}
+%    \label{booklet_translate2}
+%    \begin{center}
+%    \begin{subfigure}{.9\textwidth}
+%        \centering
+%        \includegraphics[width=\textwidth]{Figuras/MP_F.pdf}
+%    \end{subfigure}
+    %\begin{subfigure}{0.55\textwidth}
+    %   \centering
+    %  \includegraphics[width=\textwidth]{Figuras/MP_2.pdf}
+    %\end{subfigure}
+%    \end{center}
+%\end{figure}
+
+\afterpage{
+\begin{landscape}
+
+\subsection{Surveys}
+
+\begin{table}[H]
+\caption{Baseline survey}
+\label{baseline_survey}
+\begin{center}
+\scriptsize{\input{./Tables/baseline_survey1.tex}}
+\end{center}
+ \scriptsize 
+%\textit{Do file: } \texttt{ss.do}
+\end{table}
+
+\begin{table}[H]
+\begin{center}
+\scriptsize{\input{./Tables/baseline_survey2.tex}}
+\end{center}
+ \scriptsize 
+%\textit{Do file: } \texttt{ss.do}
+\end{table}
+
+\begin{table}[H]
+\begin{center}
+\scriptsize{\input{./Tables/baseline_survey3.tex}}
+\end{center}
+ \scriptsize 
+%\textit{Do file: } \texttt{ss.do}
+\end{table}
+\end{landscape}
+}
+
+\begin{table}[H]
+\caption{Survey's non-response balance}
+\label{balance_response}
+\begin{center}
+\scriptsize{\input{./Tables/balance_response.tex}}
+\end{center}
+ \scriptsize This table shows whether the means of variables in the administrative dataset are different for those that respond the baseline survey vs those that do not.
+We use this as an assessment of external validity.
+Internal validity is guaranteed because the baseline survey was implemented before treatment assignment and therefore response rates are orthogonal to treatment assignments.
+Panel A studies the baseline survey, while Panel B focuses on the exit survey.
+The columns labeled ``p-values'' report p-values for the test that the means of the respective variable are the same for those that responded did not respond the survey.
+%\textit{Do file: } \texttt{balance\_response.do}
+\end{table}
+
+\begin{comment}
+\begin{table}[H]
+\caption{Reincidence SS}
+\label{tab_reincidence}
+\begin{center}
+\scriptsize{\input{./Tables/tab_reincidence.tex}}
+\end{center}
+ \scriptsize
+%\textit{Do file: } \texttt{tab\_reincidence.do}
+\end{table}
+
+\begin{table}[H]
+\caption{Summary statistics (exit survey)}
+\label{SS_exit}
+\begin{center}
+\scriptsize{\input{./Tables/SS_exit.tex}}
+\end{center}
+ \scriptsize We carried out an exit survey.
+It had a small response rate and we don't use it in the paper.
+Here it shows that the characteristics of those that responded it are balanced across arms (Panel B).
+Panel A reports outcomes.
+%\textit{Do file: } \texttt{ss.do}
+\end{table}
+\end{comment}
+
+\newpage
+\subsection{Some more evidence of overconfidence}
+
+\vspace{.2in}
+\begin{figure}[H]
+    \caption{Behavior of those who lost pawn}
+    \label{proxy_naive}
+    \begin{center}
+    \begin{subfigure}{0.40\textwidth}
+        \caption{Elapsed days to first payment}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_firstdays_default.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.40\textwidth}
+        \caption{Elapsed days to last payment}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_days_default.pdf}
+    \end{subfigure}
+        \begin{subfigure}{0.40\textwidth}
+        \caption{Payments as \% of loan}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_percpay_default.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.40\textwidth}
+        \caption{Number of payments}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_numpay_default.pdf}
+    \end{subfigure}
+    \end{center}
+        \scriptsize 
+        This figure describes behavior for the subsample of clients whose pawn was not recovered (in the control group).
+Panel (a) shows days elapsed from the pawn to the first payment, while panel (b) displays the days elapsed to last payment.
+Some people pay after the day 105 when the grace period ends because the can ``restart'' the loan if they pay all interest owed.
+It amounts to starting a new loan with the same conditions and same pawn.
+Panel (c) shows the fraction of the loan that they paid (even when they ended up losing the pawn).
+Panel (d) displays the number of times they went to the branch to pay.
+      %\textit{Do file: }  \texttt{hist\_den\_default.do}
+\end{figure}
+
+\newpage
+\subsection{Main treatment effects: Additional material}
+
+\vspace{.2in}
+\begin{figure}[H]
+        \caption{Financial cost effect: charging all fees}
+    \label{fc_allfee}
+    \begin{center}
+        \centering
+        \includegraphics[width=0.50\textwidth]{Figuras/fc_allfee_quantile_pro_2.pdf}
+    \end{center}
+    \scriptsize
+     This figure is the analogous to Figure \ref{fc_pro2}(b), except that for the fee-forcing contract we pretend that all clients incurred in their late fees, and therefore inflate the financial cost by summing those fees.
+This is intended as a kind of worse case scenario for the financial cost of the fee-forcing contract.
+The circles indicate the quantile treatment effects, while the cross is the (OLS) mean.
+We still find that the financial cost of will be smaller under the fee-forcing contract in spite of artificially inflating it.
+     %\texttt{fc\_all\_fee.do}
+\end{figure}
+
+\begin{figure}[H]
+        \caption{FC as \% of loan - treatment effect}
+    \label{fc_perc}
+    \begin{center}
+        \centering
+        \includegraphics[width=0.50\textwidth]{Figuras/fc_perc_te_allarms.pdf}
+    \end{center}
+     \scriptsize This figure shows the estimated treatment effect of all arms against the status quo, but normalizing the dependent variable by the value of the loan.
+     %\textit{Do file: }  \texttt{fc\_perc\_allarms.do}
+\end{figure}
+
+\begin{figure}[H]
+    \caption{Relationship between treatment effects}
+    \label{induced_to_pay_early}
+    \begin{center}
+    \begin{subfigure}{0.45\textwidth}
+        \caption{\footnotesize{Induced to pay earlier vs Induced Lower FC}}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/binscatter_fc_days_pro_2.pdf}
+    \end{subfigure}
+        \begin{subfigure}{0.45\textwidth}
+        \caption{\footnotesize{Induced to pay earlier vs Induced Recovery}}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/binscatter_def_days_pro_2.pdf}
+    \end{subfigure}
+    \end{center}
+       \scriptsize 
+       This figure plots relationships between \textit{treatment effects}.
+Both Panels (a) an (b) have the same X-axis, which displays the estimated heterogeneous treatment effect on the outcome ``elapsed days of first payment'', that is how many days elapsed from the day the loan was awarded to the first payment the client made.
+The treatments effects were calculated using \cite{atheygrf}.
+In Panel (a) the Y-axis is the \textit{treatment effect} on financial cost.
+In Panel (b) the Y-axis is the \textit{treatment effect} on losing their pawn.
+Panel (a) shows that those induced to pay earlier are also those that have larger savings in financial cost as a result of ``forcing'' the frequent payment commitment contract compared to the status-quo (control).
+Panel (b) shows that those induced to pay earlier are also those that have a larger increase in recovery.
+      %\textit{Do file: }  \texttt{binscatter\_hte.do}
+\end{figure}
+
+\newpage
+
+\begin{table}[H]
+\caption{Intermediate outcomes}
+\label{mechanisms}
+\begin{center}
+\scriptsize{\input{./Tables/mechanism.tex}}
+\end{center}
+ \scriptsize
+This table explores treatment effects in ``intermediate variables''.
+Each column represents a different dependent variable in an OLS regression, and each panel represents a different treatment arm-control comparison.
+All regressions include fixed effects for branch, day of week fixed effects, number of pawns at the time of pawning this particular one, number of different treatment arms experienced before pawning this particular one.
+$R^2$ are not reported, they were less than 0.04 for all but the last column which had $R^2$'s close to 0.6.
+The last row shows the mean of the dependent variable for the control group.
+Dependent variables are as follows: Column (1) measures the number of days elapsed from the pawning date to the first payment done.
+Column (2) records the number of payments done within 230 days of the pawn.
+Column (3) is the average size of the payments for each client in pesos.
+Column (4) is self-reported cost to get to the branch plus the imputed loss of a whole day of salary (using the minimum wage in Mexico) multiplied by the number of visits to the branch.
+Column (5) measures the number of days it took to recover the pawn, conditional on recovering.
+The dependent variable in Column (6) is a dummy =1 if the client paid any positive amount within 230 days of the pawn.
+For Columns (7) and (8) the dependent variable it is the sum of total payments done within 230 days of the pawn divided by the size of the loan, but column (8) includes as regressors a dummy=1 if the client recovered her pawn, and its interaction with treatment.
+
+%\textit{Do file: } \texttt{mechanisms.do}
+\end{table}
+
+\newpage
+\subsection{FOSD: fee forcing vs status quo financial cost distributions}
+
+\vspace{.2in}
+\begin{figure}[H]
+        \caption{Empirical CDF of Financial Cost: fee-focing vs status-quo}
+    \label{ecdf_fc}
+    \begin{center}
+        \centering
+        \includegraphics[width=0.65\textwidth]{Figuras/cdf_fc_pro_2.pdf}
+    \end{center}
+    \scriptsize This figure plots the empirical cumulative distribution of financial cost.
+It does this separately for the fee-forcing contract and for the status-quo contract.
+The doted line at the bottom is the difference of the status-quo CDF minus the fee-focing CDF.
+It shows that the CDF of the status quo contract is always below that of the fee-forcing (and this difference is significant for the points indicated by the blue line), and therefore that the former first-order stochastically dominates the later for weakly decreasing utility functions; see Proposition \ref{eq_fosd}.
+    % \texttt{ecdf\_fc.do}}
+\end{figure}
+
+\vspace{.2in}
+\begin{table}[H]
+\caption{Clients who should prefer fee-forcing financial cost distribution}
+\label{stochastic_dominance}
+\begin{center}
+\scriptsize{\input{./Tables/dominance.tex}}
+\end{center}
+ \footnotesize
+This table does two things.
+First, it tests whether the observed empirical distribution of financial cost is well approximated by a log normal.
+It does this using two tests, the Anderson-Darling and the Kolmogorov-Smirnoff tests.
+Second, it fits a log normal distribution by maximum likelihood to observed empirical distribution of financial cost, separately for the fee-forcing arm and the status-quo arm.
+Using the fitted log normal, it tests whether the fee-forcing financial cost distribution would be preferred by any expected utility agent using Proposition \ref{lognormal_fosd} below.
+The different rows of the table do this for different sub-populations.
+The first row of the table does it for every client in the fee forcing and status quo arms.
+The ``*'' show that we cannot reject at the 5\% level that both distribution are log normal for any of the two tests.
+The column entitled ``Dominance'' shows whether any client that dislikes higher cost would prefer the fee-forcing cost distribution over the status quo one, with $\succeq_{1}$ meaning he should (with $\succeq_{1}^*$ indicating the difference is statistically significant).
+It turns out to be the case that for the overwhelming majority of sub-populations, the conditions of preferring the fee-forcing distribution hold.
+%\textit{Do file: } \texttt{stoch\_dominance.do}
+\end{table}
+
+\vspace{.2in}
+\begin{prop}
+\label{lognormal_fosd}
+\footnotesize{
+Let $F$ and $G$ be the cumulative distributions of two alternative log-normal prospects. The following are equivalent:
+
+\begin{enumerate}[(a)]
+    \item For every weakly decreasing utility function $u$: $E_{F}(u(FC))\leq E_G(u(FC))$
+    \item $E_F \log(FC)\geq E_G\log(FC)$ and $Var_F \log(FC)= Var_G\log(FC)$
+\end{enumerate}
+}
+\end{prop}
+
+\begin{proof}
+\footnotesize{
+See Theorem 4 in \cite{lognormal_dominance}.
+}
+\end{proof}
+
+\vspace{.1in}
+\begin{prop}
+\label{eq_fosd}
+\footnotesize{
+This is a standard result. 
+\\
+\vspace{.1in}
+The following are equivalent:
+\begin{enumerate}[(a)]
+    \item For every weakly decreasing utility function $u$: $E_{sq}(u(FC))\leq E_{fee}(u(FC))$
+    \item $F_{sq}(FC)\leq F_{fee}(FC)$ 
+\end{enumerate}
+}
+\end{prop}
+\begin{proof} \;
+\footnotesize{
+
+[$(a)\Longrightarrow (b)$] Suppose  $(b)$ does not hold. So there exists $FC^*$ such that $F_{sq}(FC^*)>F_{fee}(FC^*)$, Define $u:=\mathds{1}_{FC\leq FC^*}$. Then
+\[E_{sq}(u(FC)) = \int u(FC)dF_{sq} = F_{sq}(FC^*)>F_{fee}(FC^*)= \int u(FC)dF_{fee} =E_{fee}(u(FC))\]
+which contradicts $(a)$.\\
+
+[$(a)\Longleftarrow (b)$] On the other hand for $u$ weakly decreasing,
+
+\[\int u(y(FC))dF_{sq}(y(FC)) = \int u(y(FC))dF_{fee}(FC) \leq \int u(FC)dF_{fee}(FC)\]
+with $y(FC) = F_{sq}^{-1}F_{fee}(FC)$.
+}
+\end{proof}
+\footnotesize{
+Note the proof was done in the case of absolutely continuous and strictly increasing distribution functions $F_{sq}$ and $F_{fee}$.
+}
+
+\newpage
+\subsection{Causal Random Forest and HTE}
+
+\vspace{.3in}
+\begin{figure}[H]
+        \caption{Honest causal tree for the fee forcing contract heterogenous treatment effects}
+    \label{casual_tree}
+    \begin{center}
+        \centering
+        \includegraphics[width=.8\textwidth]{Figuras/crf_pro_2_fc_admin_disc.pdf}
+    \end{center}
+    \footnotesize 
+    This is one(it is chosen such that it minimizes the pruned cost, that is it is the tree with the smallest root-node impurity) of the honest causal trees in the random forest we use for the estimation of the heterogeneous treatment effect of the fee-forcing contract.
+It is meant only as an example of how these trees look like.
+The forest was such that there are as many estimated treatment effects as there are clients.
+     %\footnotesize{ \textit{RScript: }  \texttt{grf.R}
+\end{figure}
+
+We use \cite{atheygrf} the \texttt{causal\_forest} of the \texttt{grf} library in $R$. The parameters used were:
 \scriptsize{\textit{causal\_forest(
@@
   orthog.boosting = FALSE, 
-  num.threads = NULL
-)}}} We find that virtually all (90\%) of clients experienced financial cost savings in the fee-forcing group compared to the status-quo group.
-Figure \ref{HTE_fee_forcing}(a) in the Appendix shows that the (causal) cost savings are largest for the more economically vulnerable, %that report at baseline that they have problems paying for services like water, electricity and rent,
-those that report being stressed, those that have to incur in higher transport cost to go to the branch  and that asked to be sent reminders to pay, this later one being one proxy of being inattentive or sophisticated present-biased.
-
-\vspace{.2in}
-\noindent \textbf{Pawn Recovery.} Figure \ref{fc_pro2}(d) plots estimated treatment effects of the fee-forcing commitment contract with the dependent variable being an indicator of losing the pawn in less than 230 days.
-The leftmost coefficient shows that the fee-forcing commitment contract increases the likelihood of recovering the pawn by 11pp (25.8\% of mean recovery).
-This is a large effect.
-It contrasts for instance with \cite{Pande} who find no effect of payment frequency on default in a group lending microfinance context.
-Figure \ref{HTE_fee_forcing}(b) in the Appendix shows that those we classify as present biased, those that requested to be sent a reminder to pay, and those who have more problems paying for basic services experienced the largest increases on pawn recovery.
-
-%the second conditions on the population that paid any positive amount towards recovery of their pawn; the third conditions on having paid at least 30\% of the loan amount; the fourth conditions on the period covering the first cycle of the loan; the fifth on the period of the first cycle and paying any positive amount.
-
-\vspace{.1in}
-\noindent From this first comparisons we conclude that penalizing borrowers for delinquency in a contract which has already has large penalties from default (losing the collateral in a highly collateralized loan) actually helps borrowers.
-
-\vspace{.2in}
-\noindent \textbf{Effect on other outcomes.} There are other (intermediate) outcomes that are impacted by treatment.
-Table \ref{mechanisms} shows that the first payment happens 8 days earlier (column 1) in the fee-forcing arm than in the status quo one, and that the number of payments increases by 0.19 (column 2).
-Figure \ref{induced_to_pay_early} in the Appendix correlates heterogeneous treatment effects on financing cost and time of first payment and shows that those induced to pay earlier are also those that have larger induced savings in financial cost.
-A second finding is that treatment effects are concentrated on the intensive margin, as treatment does \textit{not} affect the fraction of clients who pay a positive amount (column 6).
-The percentage of the loan paid increases by 8 percentage points on average (column 7).
-Note however is that the percentage of the loan paid is not larger for those that end up losing the pawn (first row of column 8).
-
-\vspace{.2in}
-\noindent \textbf{Other sub-samples.} Going back to Figure \ref{fc_pro2}(a), we estimate some interesting correlations.
-The 4th coefficient from left to right conditions on those who paid a positive amount (in treatment and control).
-Although this is potentially an endogenous population, Table \ref{mechanisms} showed that there is no treatment effect on Pay$>0$.
-We were interested in this population to show that the effect is there for those who are serious about recovering their pawn.
-The fifth coefficient conditions on those that paid a fee in the fee-forcing group.
-In effect comparing this subset in treatment vs all of the control group\footnote{Results are similar if we condition in the control group on those who would have paid a fee given current behavior.
-Again we acknowledge these is an endogenous control and that the estimate is not a causal effect.}.
-We find even those that paid a fee in the fee-forcing contract end up paying a smaller financial cost that those in the status-quo contract.\footnote{This is not an experimental comparison as who pays a fee in the treatment group is a selected sample, but we found this relationship interesting nonetheless.} Figure \ref{fc_pro2}(c) shows that the increase in pawn recovery is robust to defining recovery using the first 120 days of the contract, or restricting to those paying a positive amount towards pawn recovery.
-
-\subsection{Effects of fee-forcing on repeat pawning}
-
-We have shown that clients are more likely to recover their pawn that virtually all of them incur in a lower financial cost  when assigned a monthly payment commitment contract with fees.
-This however does not necessarily show that they benefited in utility terms, and this is hard to show directly.
-If ---as suggested by \cite{Laibson2018}--- consumers used ``experienced utility'' as a guide to make future purchases, we conjecture that clients in the fee-forcing contract would be more likely to be repeat costumers vis-a-vis those that got status quo contract.
-This is indeed what we find.
-
-Figure \ref{reincidence} presents results of equation (\ref{basic_reg}) where the dependent variable is a dummy for the client to be a repeat costumer.
-We define a client in our experiment as a repeat costumer if, after experiencing at least 75 days of the respective treatment arm, she came back and pawned a different piece.\footnote{Results are robust to using other number of days besides 75.}  The left most coefficient shows that the causal effect of the fee-forcing contract on repeat pawning is an increase of 5pp in the probability of being a repeat costumer, this is 55\% on a mean re-incidence in the control group, with respect to those that got the status-quo contract.
-This is not explained by clients recovering their first pawn with higher probability in the fee-forcing contract and re-pawning this same one since we make sure it is another piece (besides only 37\% recover their piece in the fist 75 days in the fee forcing contract).
-The second coefficient restricts to the population who had larger (treatment effect) financial cost savings in their first pawn, and shows that the effect is twice as large for them.
-That is, those that benefit more from the fee-forcing contract are much more likely to repeat.
-%The coefficient on repeat pawning is just as big when we focus only 2nd pawns happening after the first was recovered (third coefficient ``fnr'').
-This is consistent with \cite{Laibson2018}'s conjecture that clients could be making decisions based on experienced utility.\footnote{The third coefficient conditions on the subsample that did recover their first pawn in both arms and finds a coefficient of 4pp.
-This is not a causal estimate as recovery is influenced by treatment, but we found it telling that the differences were similar to the causal estimate for the full sample.}
-
-We also implemented an exit survey which clients filled when recovering their piece.
-Unfortunately it had low response rates (7\%), and we take its results with a grain of salt.
-In this survey 63\% said they liked the frequent payment contract more than the status-quo one, and that is allow them avoid unnecessary expenses.
-
-\section{The effect of giving choice} \label{fee-choice}
-
-Section \ref{fee-commitment} showed that the fee-forcing commitment contract reduced financing cost across the board, and that consumers themselves seemed to like it once they tried it.
-In such a case, one would expect a strong demand for it, unless consumers underestimated these benefits.
-
-\subsection{Demand for the fee-forcing commitment contract} \label{sec:demand}
-
-To study demand for commitment, in one experimental arm, we let clients freely choose between the two types of contract: the fee-forcing commitment contract or the status-quo contract.
-The first result here is that in spite of broadly distributed benefits of the fee-forcing commitment contract we documented above, 90\% of clients chose \textit{not} to have it, they instead preferred the status-quo one.
-As explained above we are fairly confident this was not because a lack of understanding of the contracts.
-
-What can explain this low demand?
-This section discusses some hypothesis but lack of data limits what can be tested.
-One neoclassical explanation could be risk.
-Even if the fee forcing contract generates cost savings on average, clients with risk averse preferences may not demand it if they perceive higher risk from it.\footnote{Because they have not experienced the fee-forcing contract before, ambiguity aversion may play a role here too.} Alternatively, even risk-neutral agents may not demand it if the cost of lost flexibility is high.
-If they for example face large and frequent income shocks which make it hard to repay monthly.\footnote{We don't observe income shocks in our data, making is hard to quantify how important they are.
-90\% of those in the fee-forcing arm incurred a fee, which suggests that shocks are not uncommon (or clients inattentive).} Below we focus on some explanations of low demand, while Section \ref{model} seeks for theories that can explain all the findings, and reaches the conclusion that the present bias with naivete parsimoniously explains more results.
-
-\subsubsection{Behavioral economics explanations}
-
-The leading behavioral explanation in the literature for low demand for commitment is present biased preferences with naivete (e.g.
-\cite{Rabin2018}, \cite{John}, \cite{Laibson2018})  \cite{Laibson2015} shows that the lost flexibility resulting from a commitment contract can limit take-up especially severely when agents are naive about their self control problem.
-In our context if consumers are naive about their present bias, they would plan to save more (or spend less) than what they actually end up saving, thus making it be harder to recover their pawn.
-This under-saving will be mitigated in the fee forcing contract since the fee makes them save money and pay part of the loan periodically.
-Another behavioral explanation is that clients may underestimate the likelihood and severity of negative income shocks.
-Both of this explanations predict that clients will be overconfident about their likelihood of pawn recovery.
-Recall that in the control group the client's subjective probability of recovery is on average 93\%, while actual recovery is just 44\%.
-A further piece of evidence consistent with underestimating negative income shocks is that a large number of people (31\%) in the control group pay a positive amount toward pawn recovery but end up losing their pawn anyway.
-
-So, overconfidence of recovering the pawn is implied by both present bias preferences with naivete and upward bias in their income expectations.
-But does overconfidence actually predict low demand for commitment empirically?
-It does.
-We define as overconfidence as the reported subjective probability of recovery minus the predicted probability based on the client's characteristics, $P^s_i-\widehat{P_i(X_i)}$.\footnote{We predict $\widehat{P_i(X_i)}$ in two steps.
-In step one we use LASSO with with cross validation to tune the regularization parameter to select the most predictive variables.
-In the second step we estimate $\widehat{P_i(X_i)}$ using those variables in a logit model.
-The LASSO selected variables were type of pawn, female, age, has pawned before, has savings, participates in rotating savings, often feels tempted to change plans, would like to have a reminder to pay, and an economic vulnerability index.}  Table \ref{oc_reg} regresses a take-up dummy against an indicator $OC_i:=\mathbbm{1}(P^s_i-\widehat{P_i(X_i)}>0)$ for overconfidence and controls.
-Controls include branch and day of the week dummies, and additionally schooling, whether the client does a monthly budget plan, and a measure of intertemporal preference reversal analogous to that of \cite{Ashraf} as controls.\footnote{We find that 15\% of clients are classified as present biased using this measure of preference reversal.
-This level is similar to the number \cite{Ashraf} find.} Column 2 shows that in the choice-fee arm, being overconfident decreases the likelihood of demanding commitment by 16 percentage points, and column 4 shows that this is robust to including other controls.
-One interpretation of this result is that the overconfident think they do not need commitment, especially if that commitment may have the cost of fees.
-Columns 1 and 3 will be explained in Section \ref{promises}.
-Column 5 and 6 use as a dependent variable the estimated heterogeneous treatment effects of the fee-forcing contract vs the status quo one.
-They show that the overconfident benefit \textit{more} from the commitment contract, with 20\% (=\$24/\$121) more savings.
-
-\subsubsection{Neoclassical Alternatives}
-
-\vspace{.1in}
-\noindent \textbf{Risk aversion.} We do not have measures of risk aversion in our necessarily short survey, which makes it hard to assess the hypothesis that risk aversion limits take-up of the fee-forcing contract.
-One way to proceed is to take the empirical distribution of financing cost ---$F_{fee}(FC)$--- as one the client would have faced had she chosen the the fee-commitment contract.
-We could then ask what would risk aversion have to be in order to justify the client choosing the fee-commitment contract distribution of costs over the distribution associated with the status quo contract, $F_{sq}(FC)$.
-We can then assess if the risk aversion needed would be reasonable or too high.
-This exercise of course assumes --as it is common in economics-- that clients know the distribution of financial cost, that it is common across consumers (although this can be relaxed), and that this cost distribution is the only difference among contracts.
-Fortunately for us, since one distribution first-order-stochastically dominates the other we do not need to calibrate a specific utility function or use a parametric distribution function in order to rank them in terms of expected utility.
-We use the fact that if $u(FC)$ is decreasing in $FC$ and $F_{fee}(FC) \geq F_{sq}(FC)$ for all $FC$, then $E_{fee}[u(FC)] \geq E_{sq}[u(FC)]$.
-That is any expected utility maximizer who dislikes paying higher financing cost, regardless of the concavity of his utility function, will prefer the fee-commitment distribution of financial cost.
-Figure \ref{ecdf_fc} in the Appendix shows that indeed $F_{fee}(FC) \geq F_{sq}(FC)$.
-Moreover, Table \ref{stochastic_dominance} shows that this holds also for an overwhelming majority of sub-populations.
-
-%To have a benchmark we implement a very simple calibration exercise in two steps.
-First, we fit a Weibull distribution to the distribution of financing cost, were the scale and shape parameters depend on client's and loan observable characteristics.
-We do this separately for the status quo contract and the fee-forcing contract, obtaining two distributions $f_{sq}(FC|X;\Gamma_1)$ and  $f_{fee}(FC|X;\Gamma_2)$ with different parameters $\Gamma_1$, $\Gamma_2$.
-Second, we assume a representative consumer with a CRRA utility function over financial cost, $u(FC)=\frac{1}{1-\theta}FC^{1-\theta}$.
-We then ask what would $\theta$ have to be for a consumer to prefer the status-quo contract.
-That is for which $\theta$'s would  $\int u(FC|\theta)f_{sq}(FC|X;\Gamma_1) dFC \geq \int u(FC|\theta)f_{fee}(FC|X;\Gamma_2) dFC $ hold?
-It turns out that it holds for risk aversion levels that are too high to be believable.
-That is, with our calibration, it seems unlikely that risk aversion is reducing demand for the fee-forcing contract.
-
-\vspace{.1in}
-\noindent \textbf{Lost flexibility.} A second neoclassical explanation for low take up is lost flexibility.
-That is, the fee-commitment contract may provide too much commitment which is costly both, (a) because the client may be forced to incur in late payment fees if he experiences a negative income shock, and also because (b) he may be unable to recover the pawn and his pre-payments.\footnote{Note that income shocks that affect the ability to pay the entire loan are a worry for both the fee-forcing contract and the status quo one, and should not make one contract more favorable than the other.} While we cannot rule out that income shocks combined with lost flexibility of the contract explain the low demand, we think it is unlikely.
-First, we showed above clients report a subjective probability of recovery of 93\% on average, which suggests they are not too worried about income shocks.
-Second, the fear of incurring fees is quantitatively not enough of a concern when compared to the savings they are experiencing.
-%Note that fees for late payment are not that high.
-In an average loan of 2,000 pesos the monthly payment is close to 700 pesos, and a fee of 2\% of that is 14 pesos (less than \$1 dollar).
-This is about \hlgr{1\%} of monthly per capita income of the first 3 deciles of Mexican \hl{household's} income distribution.
-%This compares favorably to the \hlgr{\$11.6 + \$62.3)} pesos transportation / transaction cost of one.
-To make this concrete we calculated what the financing cost of the fee-commitment contract would be if all its clients incurred in \textit{all} potential fees (while keeping payment profiles and pawn recovery constant), thus artificially inflating the cost.
-We then re-estimated the quantile treatment effects analogous to Figure \ref{fc_pro2}(b) with this inflated financial cost.
-%\footnote{Of course behavior may not be constant, but we believe this is a reasonable fist approximation.
-%It could be that having this small fee added to the balance discourages them to pay or makes it harder to pay back the loan.
-But the contrary may also happen, with the fee making them more determined to pay early.
-We would need a structural model of client behavior to estimate a full counterfactual.
-We suspect that such small fees would not generate large changes in behavior in a simple neoclassical model.}).
-Figure \ref{fc_allfee} presents the results.
-We find that even in this extreme scenario, tilted against the fee-forcing contract, the estimated effect still implies cost savings from the fee-forcing contract at the mean, 25$^{th}$, 50$^{th}$, and 75$^{th}$ percentiles.
-Note that the differences in financing cost already takes into account the fact that clients in the fee forcing contract sink more pre-payments than those in the status quo contract, and that those prepayments are lost if the loan is not fully paid back.
-Although these arguments are not definitive, they suggest that low demand for commitment may be driven by be more than the anticipation of lost flexibility.
-
-\vspace{.1in}
-\noindent \textbf{High time discounting.} In the summary statistics section we mentioned that clients in the status quo contract tend to wait until the last moment to pay to recover their pawns.
-Even among those that recover their pawn, only 20\% pay before the 90$^{th}$ day.
-Table \ref{mechanisms} showed that clients assigned to the fee-forcing contract front load their payments, starting their first payment earlier and finishing to pay earlier too.
-However, clients may dislike front loading payments if their discount rate is high.
-They may be willing to trade off a higher probability of losing their pawn for more \textit{back} loaded payments.
-This would explain both, why default rates are high and why demand for the fee-commitment contract is low.
-
-What would discount rates have to be in order to offset the reductions in financial cost effects we observe?
-We can calculate this number by looping across a grid of discount rates and reestimating equation \ref{basic_reg} with a financial cost dependent variable that uses the respective discount rate in the grid, and searching for the discount rate that makes $\beta$ equal zero.
-We do this and obtain that the discount rate that rationalizes a zero effect is 8,190 percent per year.
-We find this discount rate implausibly high even for this credit constrained population, and seriously casting doubt on high discount rates as explanation for low demand for commitment.%\footnote{In the baseline survey we give respondents a hypothetical choice between $100$ pesos tomorrow or $150$ pesos in one month (an implicit yearly interest rate of \hl{12,800\%}) and only 30\% chose the later one.}
-
-\subsection{The effect of choice on pawn recovery and financial cost} \label{effect_choice}
-
-When preferences or income streams are heterogeneous, and consumers are neoclassical, giving choice among contracts is a welfare increasing strategy.
-Consumers would chose the contract that best fits their needs.
-This holds also in most simple models of present bias preferences if consumers are sophisticated about their present bias.
-%Actually, it could be the case that the opportunity of choosing itself could affect behavior.
-But when consumers are overconfident about their ability to save cash to pay back the loan, free choice could be a sub-optimal policy from the point of view of the client's long run self, and match the clients with a more costly contract.
-
-Even if take up of the commitment-fee contract is low, the sole fact of having choice could potentially change behavior (\cite{Dalboetal:2010}, \cite{Sjostrometal:2018}).
-We find that giving clients the option of choosing among the fee-forcing and the status quo contract does \textit{not} lead to lower financial cost compared to forcing them into the status-quo contract, Figure \ref{fc_pro4}(a) hollow circles.
-Nor does it lead to higher pawn recovery, Figure \ref{fc_pro4}(c).
-The hollow circles in Figure \ref{fc_pro4}(show average effects for the different definitions of financial cost analogous to the ones described above.
-Figure \ref{fc_pro4}(b) shows further that the null effect happens for the 15$^{th}$, 25$^{th}$, 50$^{th}$ 75$^{th}$, and 85$^{th}$ percentiles.\footnote{The few that selected the fee-commitment contract (the solid black squares) do enjoy cost savings of 1005 pesos, which compares favorably to the 304 pesos in the fee-forcing arm (as a fraction of the loan the numbers are 41.5\% and 12.5\%), but this combines the selection and treatment effects.
-We cannot reject the that the ``effect'' on pawn recovery is of the same size for the fee-forcing arm and for those that selected into fee-forcing.} %Figure \ref{heterogeneous_te_4} plots the distribution of treatment effects and finds that the distribution offering choice actually \textit{increased} financial cost and default for about half of clients compared to being assigned the status-quo contract.
-Those tended to be the less economically vulnerable and more educated, \hl{women}, and those whose family typically asks them for money.
-Consistent with these findings, Figure \ref{reincidence} finds no effect on repeat purchases for the choice group.
-
-\subsection{The scope for private paternalism}
-
-This is not the first paper to find low demand for commitment, however it is the first we know of that can compare choice vs forcing.
-The fact that the fee-forcing contract lowers financial costs for all, together with the fact that only 10\% choose it must mean that many consumers are choosing contracts with higher financial costs for them.
-We can ask how many consumers seem to be making a cost increasing choice and how much money are they leaving on the table.
-To do this we conduct two exercises.
-
-\vspace{.2in}
-\noindent \textbf{Are there ``mistakes'' in choice?} Answering this question requires calculating a counterfactual: for each person in the choice arm we want to know how much cost savings a client would have if she chose the fee-commitment contract instead of the status quo contract.
-We do this in two steps.
-First, using the honest causal forests method of \cite{atheygrf} described above we calculate the causal effect on financing cost of getting the fee-forcing contract instead of the status quo contract for a client with characteristics $x_i$ \textit{in the forcing arms}, we call it $TE^{fee}_{i}$.
-There is no selection problem in the forcing arms.
-Second, using these estimates, we predict treatment effects for clients \textit{in the choice arm} using the $x_i$'s, and call it $\widehat{TE}^{fee}_{i}$.
-This is precisely the counterfactual we wanted.\footnote{This extrapolation of the treatment effects assumes that choice itself --conditional on a given contract-- does not affect behavior.
-Given the results in subsection \ref{effect_choice} we are comfortable with this assumption.
-Note that although the extrapolation is to another population, by randomization it is a statistically identical population.} Armed with this, we say that a client made a ``mistake'' if either she chose the status quo contract and her $\widehat{TE}^{fee}_{i}$ is negative (i.e.
-more cost saving from the fee contract), or if she chose the fee-commitment contract and $\widehat{TE}^{fee}_{i}$ is positive, meaning that financial cost are larger for the fee-commitment contract.
-When a client made a choice mistake, we say that the peso-size of it is $|\widehat{TE}^{fee}_{i}|$.
-
-%Using the forcing arms and extrapolating to the choice arms.
-%Then, we predict these treatment effects for everybody in the choice arm using characteristics $x_i$.
-Let $\widehat{TE}^{fee}_{i}$ be the predicted financial cost savings for person $i$ of choosing the fee-forcing contract rather than the status quo one, divided by the size of her loan (i.e.
-the negative value of the predicted treatment effect on financial cost for person $i$).
-$\widehat{TE}^{sq}_{i}$ is the analogous for the status quo contract.
-We define the choice of person $i$ to be a ``mistake'' if
-
-%\begin{equation}
-% \{ i \; \text{chose} \; sq \; \text{and} \; \;  \widehat{TE}^{fee}_{i}>\widehat{TE}^{sq}_{i} + z \} \; \text{or} \; \{ i \; \text{chose} \; fee \; \text{and} \; \;  \widehat{TE}^{fee}_{i}<\widehat{TE}^{sq}_{i} - z \}
-%\end{equation}
-
-Since the prediction of the treatment effect is an estimate and has noise, we do two things.
-First, we normalize $\widehat{TE}^{fee}_{i}$ by the value of the loan of person $i$ and introduce a threshold parameter $z$ and say that a choice is a ``mistake'' if the alternative contract would generate more than $z$ in savings.
-We vary from 0\% to 20\% of the value of the loan.
-Second, we take into account uncertainty in estimation of treatment effects and report results also using the extremes of the 95\% confidence interval bounds for $\widehat{TE}^{fee}_{i}$.
-
-Figure \ref{choose_wrong}(a) plots in the left Y-axis the fraction of clients that made a choice ``mistake'' and on the right Y-axis the peso size of the mistake.
-In the X-axis it varies the threshold $z$ of what we classify as a mistake.
-In this section we are concerned with lines in red color.
-When $z=0$, we calculate that about 80\% of clients in the fee-choice group chose contracts that induced \textit{higher} financial cost (95\% confidence interval [36,95]).
-Most mistakes are failures to choose the fee-commitment contract (92\%), while only 8\% of those who chose the fee-commitment contract would have been better in the status-quo one.
-The average mistake in pesos is \$238 (95\% confidence interval [131,427]).
-Figure \ref{choose_wrong}(b) separates the analysis for those we classify as overconfident about recovering their pawn (96\% of them) vs the rest.
-It shows that there are about 14 percentage points more mistakes in the overconfident population when $z=0$.
-
-All the above suggests that forcing clients into commitment contacts (i.e.
-private paternalism) may be welfare increasing for the overwhelming majority of clients.
-Figure \ref{choose_wrong}(c) calculates what fraction of clients would be made better off if we forced them to the fee-commitment contract: 92\% when $z=0$, and they would on average have savings of 232 pesos.
-This conclusion is in line with a recent paper by \cite{John}.
-In a savings context, she finds that when commitment in on the menu a majority of subjects wrongly choose to little commitment.
-She concludes this by observing high levels of default even with late payment fees, whereas we work directly with estimated treatment effects.
-
-\vspace{.2in}
-\noindent \textbf{Is there positive selection on treatment effects?} The previous exercise consisted on extrapolating treatment effects from the no-choice arms to the choice arm.
-Here we do the converse.
-First, we estimate a flexible model of take-up of the fee commitment contract \textit{in the choice arm} using random forests and obtain for a client with characteristics $x_i$ a probability $P(x_i)$ of choosing the fee-forcing contract.
-We then use this model to predict the counterfactual probability of client with characteristics $x_i$ choosing the fee-commitment contract in the no choice-arms if she would have been given the choice, what we call $\widehat{P(x_i)}$.
-Since our model for has a good out-of-sample fit with an out-of-sample AUC of 0.85 and an accuracy rate of 85\%, we think we are not introducing too much noise by this extrapolation.
-Second, armed with this prediction in the no-choice arms, we can ask the following: is it true that people with larger fee-forcing contract treatment effects (i.e.
-more cost savings) more likely to demand the fee-forcing contract?
-
-Figure \ref{choose_wrong}(d) plots $\widehat{P(x_i)}$ in the X-axis, and the heterogeneous we estimated in section \ref{TE_fee-forcing} in the Y-axis.
-If it was true that those with larger cost savings have larger demand for the fee-commitment contract, we would expect a negative slope (recall that more savings mean lower financial cost in the Y-axis).
-This is not what we find.
-Figure \ref{choose_wrong}(d) is a binscatter that splits the X-axis in 100 percentiles bins of predicted take-up probability and for each bin averaged the financial cost treatment effects.
-Using all clouds we estimate a slope of zero in the relationship.
-Using the 80 right most points, we estimate a \textit{positive} relationship.
-A positive relation means that those more likely to demand commitment are also those that had smaller benefits from commitment.
-This result is similar to \cite{Walters}, who finds that students that select into more effective schools are the ones with smaller treatment effects.
-\cite{Walters} uses distance to school as an instrumental variable for choice, while we use randomization to choice vs no-choice groups as our empirical strategy.
-
-\section{Viewing the results through a simple model} \label{model}
-
-This section uses a model to interpret our empirical results.
-The model is stylized but incorporates important features of our context.
-First, it allows for negative income shocks which we think are prevalent in this population (that's why they pawn in the first place)\footnote{71\% say they need the money for an emergency.}.
-The shock generates a cost of committing to monthly payments and could potentially be a reason for low take up.
-Second, it features clients with present biased time preferences and allows for naivete about them.
-As we discuss below these two features parsimoniously explain several facts about the context ---e.g.
-overconfidence in recovering the pawn, and large inefficient default---  and about the results ---e.g.
-forcing commitment seems to help, and that there is also some (although small) demand for commitment at no benefit for neoclassical consumers.
-Third, it incorporates the fact that the pawned piece is more valuable than the loan.
-Fourth, it allows for a simple way to model commitment afforded by late payment fees.
-Nonetheless, the model abstracts from several details of the context.
-Even with these abstraction it allows us to explain our six main results listed in Section \ref{explanations_recap} below.
-
-\subsection{A simple model} \label{model}
-
-We use the model of \cite{John} and refer the reader to that paper for more detail, justification of assumptions and some of the proofs.
-The model has three periods and linear utility.\footnote{This does not map perfectly to our 3 period contract, but it is enough to generate the results we need.} Period $t=0$ is a planning period where the client is either allocated to the status quo, the fee-forcing contract, or a choice between the two.
-In period 1 the client receives her income $y_1=1$, or gets zero with probability $\lambda$.
-She can consume ($c_1$) or save ($s_1$) that income.
-In period 2 the client gets her savings from period 1, and again receives income of either $y_2=1$, or zero with probability $\lambda$.
-In this last period, she decides whether to use income and savings for consumption $c_2$ and/or for paying back the loan of size $p \in(1,2)$ to recover the pawned piece valued at $b>p$.
-In this simple model we will impose a penalty fee $F>0$ in $t=1$ for the fee-commitment contract if the month's payment is not done.
-In period $t=0$ she evaluates her welfare as $E[c_1+c_2]$, were for simplicity we have set the time discount to one.
-We also assume the interest rate is one.
-We introduce present bias preferences by assuming the following utility function $U_t=c_t+\beta \: \sum_{k=t+1}^{2} E[c_k]$, with $\beta<1$ indicating present bias.
-A naive client perceives she is not so present biased and instead of $\beta$ uses $\hat{\beta} \in (\beta,1]$.
-
-Note that under these assumptions it is efficient at $t=0$ to take actions to recover the loan.
-Because $b>1$, paying back the loan requires that there is no negative shock in any period and that $s_1>0$, and because $\beta<1$ at $t=1$ the client will not send savings in excess of what is needed to recover the loan $s_1=p-1$.
-
-\vspace{.1in}
-\noindent \textbf{Result 1: Present bias consumers default more.} Under the status-quo contract, absent shock realizations, present biased clients (sophisticated or naive) with $\beta<\beta_{SQ}<1$ will lose their pawn, while clients with no present bias will not.
-Viewed from $t=0$ losing the pawns when there are no shocks is inefficient as $b>p$.\footnote{$\beta_{SQ}=\frac{p-1}{\lambda(p-1)+(1-\lambda)(b-1)}$.
-See Proposition 1 in \cite{John}.}
-
-\vspace{.1in}
-\noindent \textbf{Result 2: Forcing present-biased clients into the fee-commitment contract reduces default.} Imposing a fee $F>0$ for late payments weakly decreases default (for present biased clients only).
-It strictly decreases default if $F>F_{min}(\beta):=(p-1)-\beta[\lambda(p-1)+(1-\lambda)(b-1)]$.
-The larger the present bias the larger the $F$ required to induce pawn recovery.\footnote{The incentive compatibility constraint to generate savings to recover the pawn can be written as $1-(p-1)+\beta[\lambda(p-1)+(1-\lambda)(b-1)] \geq 1-F+\beta(1-\lambda)$.}
-
-\vspace{.1in}
-\noindent \textbf{Result 3: Demand for commitment.} Given $F>0$, (a) Neoclassical clients will never demand commitment.
-(b) Present-biased sophisticated clients will prefer the fee-forcing contract over the status quo contract $\iff$  $\lambda \: F<(1-\lambda)^2(b-p)$ and $F>F_{min}(\beta)$, that is $\iff$  $\beta \in [\beta_{min},\beta_{SQ}]$.\footnote{$\beta_{SQ}$ was determined in Result 1.
-$\beta_{min}$ is such that $F=F_{min}(\beta_{min})$.} (c) Analogously, naive clients will demand commitment $\iff$ $\hat{\beta} \in [\widehat{\beta_{min}},\beta_{SQ}]$, where $\widehat{\beta_{min}}<\beta_{min}$.
-So strongly naive clients will on the one hand demand more commitment than sophisticated clients since they believe (incorrectly) that a smaller fee will motivate them to pay.
-On the other hand they may demand less commitment since they think they can save and pay on their own.
-Whether they demand more or less than sophisticated clients depends on the empirical distribution of $\beta$ and $\hat{\beta}$.
-
-\vspace{.1in}
-\noindent \textbf{Result 4: Overconfidence.} Only naive clients will be overconfident about the probability of recovery.
-This will be true whether they have the status quo or the fee-forcing contract.
-Overconfidence is increasing in $\hat{\beta}$.
-
-\vspace{.1in}
-\noindent \textbf{Result 5: Welfare.} (a) Neoclassical consumers' welfare strictly decreases when we force clients into the fee-commitment contract instead of the status quo contract, and does not change when we offer a choice between them.
-(b) The welfare of sophisticated present biased consumers weakly increases when we give them choice, and it strictly increases  $\iff$  $\beta \in [\beta_{min},\beta_{SQ}]$, that is when they choose it themselves.
-Forcing them into the fee-commitment contract increases welfare $\iff$  $\beta \in [\beta_{min},\beta_{SQ}]$, otherwise it strictly decreases.
-So choice is better than forcing for sophisticates.
-(c) Forcing can be welfare improving for the naive.
-Indeed if $\hat{\beta}>\beta_{SQ}>\beta$ then forcing the fee-commitment contract increases welfare, and if $\hat{\beta} \in (\widehat{\beta_{min}},\beta_{min})$ then forcing the status quo contract increases welfare.\footnote{This result is different from that in \cite{John}.
-His context has individuals choosing the size of the fee.
-In that context naive clients will always chose the wrong fee size and default, therefore choice is always decreasing for the.
-In our context $F$ is fixed at 2\% of the balance due, and this implies that choice could be welfare improving for some naifs.}
-
-\vspace{.1in}
-\noindent \textbf{Result 6: Welfare and ex-post observed behavior.} If for client $i$ the fee-forcing contract causes higher pawn recovery, then we know the fee $F$ made her IC constraint binding, and therefore that $\hat{\beta_i}>\widehat{\beta_{min}}$.
-If in addition if it was the case that \hl{$\beta<\beta_{SQ}$}\footnote{\hl{Isaac, aqui tengo dos pregutas: (1) si es $\beta$ y no $\hat{\beta}$ verdad?
-(2) Para que una persona naive empeñe en el status quo tiene que ser que cree que va a recuperar no?
-Es decir tiene que ser $\hat{\beta}>\beta_{SQ}$ correcto?}} then the fee-forcing contract would have increased welfare for the naive.
-That is, our finding that the fee-forcing contract increases pawn recovery is a sign of higher welfare.
-
-\subsection{Interpretation}
-
-The model of \cite{John} is very parsimonious but powerful.\footnote{The model is sufficiently stylized that we think we would not gain much from estimating it.
-Furthermore we have no data on income shocks which figure prominently in the model.
-\cite{Ted} and \cite{Aprajit} are two very recent models that combine a field experiment with commitment contracts and estimation of present bias parameters.} First, it can explain why clients are overconfident in our data, namely by virtue of naivete about present bias.
-Under the model naivete is necessary to explain this.
-Second, it can also explain why the fee forcing contract induces lower default, but not for everyone: namely that it makes the IC constraint for the present biased binding while it was not binding in the status quo contract.
-Third, it can also explain why there is low demand for commitment even if it seems to improve welfare: namely that there is a small share of neoclassical and sophisticated clients, and at the same time naifs have  $\hat{\beta}>\beta_{SQ}$ and therefore think they can save on their own.\footnote{By Result 6 we can eliminate $F<F_{min}(\widehat{\beta}$) as an explanation.}.
-Fourth, it can explain why clients exposed to the fee-forcing contract are more likely to come back, namely that $\hat{\beta_i}>\beta_{SQ}>\beta$ and so their welfare increased as a result of being forced into the fee-commitment contract, and they may realize this.
-
-One could also easily introduce overconfidence in income shocks with $\widehat{\lambda} <\lambda$.
-This would leave default unchanged in both the status quo and the fee forcing contract.
-%since $F_{min}(\beta,\widehat{\lambda})<F_{min}(\beta,\lambda)$.
-The effect on demand for commitment is uncertain since on the one hand it decreases $\beta_{SQ}$ decreasing demand, but on the other a smaller $F$ is needed to make the IC binding, making commitment less costly.
-
-\subsection{Other potential explanations: recap} \label{explanations_recap}
-
-There may be other interpretation of the empirical findings. But the bar is high. An alternative explanation will need to explain the facts below:
-
-\begin{enumerate}
-\itemsep0em 
-\item Overconfidence about pawn recovery.
-\item High (although ex-post inefficient) default in status quo contract.
-\item Small demand for commitment...
-\item ...but positive demand for commitment.
-\item Forcing commitment saves money.
-\item Forcing commitment makes clients more likely to come back.
-\end{enumerate}
-
-\vspace{.1in}
-\noindent \textbf{Alternative 1: Strong prevalence of income shocks.} This could explain low demand for commitment (3) and (2), but not why forcing helps (5) and (6), nor why there is overconfidence (1), or why they come to pawn in the first place, try to pay back and then default (2).
-
-\vspace{.1in}
-\noindent \textbf{Alternative 2: High time discounting}.
-This could not explain (1) nor (6) nor (4).
-It could qualitatively explain (3).
-But as we say in section \ref{sec:demand} it cannot quantitatively explain (5) and (3) unless the discount rate is unbelievably high.
-
-\vspace{.1in}
-\noindent \textbf{Alternative 3: Risk aversion.} We already discussed and rejected risk aversion in section \ref{sec:demand}, although using strong assumptions in the process.
-We think this could still play a role and should be investigated in future research.\footnote{For instance by  providing insurance or by measuring risk aversion and using it to predict take up.}
-
-\vspace{.1in}
-\noindent \textbf{Alternative 4: Misunderstanding the contracts.}\footnote{This is a potential criticism of any paper offering choice, and one that is non-falsifiable if the critic has free reign to propose how the contracts are perceived in the subject's mind.} We were very aware of this and in the implementation a very strong effort was made for consumers to understand the contracts (see subsection \ref{implementation}).
-Note however that while clients making random mistakes could explain why 10\% demand commitment ---i.e.
-(3) and (4)--- they would not explain the rest of facts, nor why the promise-commitment (see below) had more take up that the fee-commitment, or why those with present bias and those that want a reminder to pay are more likely to make the ``error'' to demand commitment.\footnote{See Figure \ref{interactions_takeup} and Table \ref{Table_compliance}}
-
-\vspace{.1in}
-\noindent \textbf{Alternative 5: Forgetting to pay.} Frequent payments may act as a reminder to save and recover the pawn.
-This would try to explain (2) by appealing to people forgetting to pay, and (5), (6) and (4) by appealing to frequent payment acting as reminders.
-It would not explain (1) or (3) which are critical in the paper.
-However even for (2) it seems to us a stretch to explain people losing a valuable pawn by forgetting to pay.
-
-\vspace{.1in}
-\noindent \textbf{Alternative 6: Learning that they are more present biased than they thought.} This is essentially the same as our proposed explanation (i.e.
-not an alternative) with the additional prediction that more people will demand commitment if they just experienced it, an specially appealing one in light of finding (6).
-We are sympathetic to the learning hypothesis and in fact it is \cite{Alcohol}'s main conjecture about why he finds strong demand for commitment while most other studies don't.\footnote{Close to ninety percent of our subjects claim to have pawned before.
-We find that experience does not predict positive take up in our sample correlationally.} To test it we would ideally need to give choice to a group of people that randomly experienced the fee-commitment vs those that did not, and test if the former demand it more.\footnote{\hl{Isaac, podemos volver a tratar esto?
-Hace como 1 anio no nos salio pero quiero volver a tratar.}} Unfortunately we did not do this experiment and we have very limited data to try it: \hl{210 (6\%)} clients were given a choice in a second pawns in our experiment after being randomly assigned to the status quo or fee-forcing contract.
-
-\section{The effect of promises} \label{promises}
-
-One finding of the paper is that a rather small fee of 14 pesos on average changes behavior substantially: on the one hand generates average savings in the order of 300 pesos when forced, but on the other dissuades take up  when client have choice.
-In this context one would want a commitment device that generates higher take up while at the same time providing incentives for paying fast and recovering the pawn.
-One way to go would be to decrease the already small fee to say 1\% or lower.
-We decided to instead experiment with a non-pecuniary penalty, in the form of the psychological cost of breaking a promise.
-As explained in Section \ref{Experiment} the promise contract involved making a salient promise to repay monthly as part of their pawn contract in words and in written, and receive the speech by the appraiser about the importance of keeping her promise of paying monthly.
-
-A substantial literature documents that people don't like to break their promises, and are willing to incur in monetary loses in trying to keep them.
-To our knowledge this result has been replicated several times in laboratory contexts but not in a field setting like ours.
-If breaking a promise is perceived as having a lower cost than paying the 2\% fee, we predict that more people will have demand for the promise-commitment contract.
-We indeed find that take up is higher.
-Is this higher take up associated with smaller treatment effects though?
-Or does the promise have enough commitment power?
-
-\subsection{The demand for promise-commitment contracts and their effects}
-
-\vspace{.2in}
-\noindent \textbf{Demand}.
-It turns out that the demand for monthly payment contracts with a personal promise to pay monthly ---but no pecuniary penalty for not doing so--- induces higher demand by a factor of three compared with fee-commitment contract studied above: 31\% of clients offered a choice between the status quo contract and the promise-commitment contract chose commitment.
-This means that that the pecuniary fee indeed limited demand for commitment.
-In passing this means also that clients are responsive to contract terms and seem to understand the conditions.
-Interestingly however, the set of people who demand the promise-commitment contract are different from those that demanded the fee-commitment one.
-While in both cases the economically vulnerable demand less, in the case of the promise-commitment those that we classify as present biased, those that report that they frequently fall into temptation buying, and those that ask for reminders of payment are \textit{less} likely to demand the promise-commitment contract.
-This suggests that those taking up the promise commitment are not the ones needing the commitment.
-The opposite is true for those who take up the fee-commitment contract (see Figure \ref{interactions_takeup} in the Appendix).
-
-\vspace{.2in}
-\noindent \textbf{Effect of choosing to promise}.
-Figure \ref{fc_pro5}(a) finds that assigning clients to the choice-promise condition has a zero effect on financial cost on average (circles).
-We see no difference even for the endogenous group that chose to promise (squares).
-This null effect happens not only on average, but also by percentiles (not shown in Figure).
-There is also no effect on pawn recovery on (first coefficient in Figure \ref{fc_pro5}(b)), even for those that themselves choose to promise (squares).
-And the null effect carries over if we use the definition of recovery in less than 120 days, or for the (endogenous) subgroups that paid a positive amount or at least a third of their loans.
-Finally, there is no effect on repeat pawning (Figure \ref{reincidence}).
-
-\vspace{.2in}
-\noindent \textbf{Effects of forcing to promise}.
-Giving choice of whether to promise or not has the advantage of making promising an active decision by the client.
-In most of the the experimental literature promising is voluntary.
-But it has the disadvantage that we cannot measure the causal effect of promising, since those that promise are a selected sample.
-To evaluate the causal effect of promising, we compare people allocated to the promise-forcing arm (were all clients were forced to make a promise) against those in the status quo contract arm.
-Figure \ref{fc_pro5} (c) and (d) show the results.
-It documents null average treatment effects for both financial cost and recovering the pawn.
-Also there is no effect on repeat pawning.
-
-\vspace{.2in}
-\noindent The evidence presented in this section contrasts sharply with the evidence in laboratory experiments where people choosing to promise has a large effect on behavior and were people keep their promises.
-While clients are more enthusiastic about the promise-commitment contract than the fee-commitment one in the sense of tripling take-up, the promise contract provides no commitment.
-Results for the promise arms are consistent with \cite{Ted} and \cite{John} who find that people are likely to demand commitment when the commitment is too week to have beneficial effects.
-
-%\vspace{.2in}
-%\noindent \textit{Size of ``mistakes''.} Although promises have very muted effects, there is some heterogeneity (see Figure \ref{heterogeneous_te_3}).
-This opens the space for choice mistakes.
-Figure \ref{choose_wrong} shows that indeed there are some mistakes, but these are smaller that for the fee-choice arm.
-When $z=0$, we calculate that about 60\% of clients in the promise-choice group chose contracts that induced \textit{higher} financial cost.
-In particular \hlgr{97\%} of those that chose the status-quo contract would have been better in the promise-commitment contract, while \hlgr{3\%} of those who chose the promise-commitment contract would have been better in the status-quo one.
-On average they spend \$250 pesos on extra financing cost.
-
-\section{Conclusion} \label{conclusion}
-
-In a pawnshop borrowing context, we studied whether forcing borrowers into frequent payment commitment contracts reduces their borrowing costs, compared to a contract that does not provide commitment to pay monthly.
-Even though we are charging them fees, their borrowing cost are actually reduced by 9.5\%, and they recover their pawn with 25.8\% higher likelihood.
-Moreover they themselves seem to like this contract, as they are 55\% more likely to come back and pawn again when they get it.
-That is, commitment matters and it seems beneficial.
-Examining treatment heterogeneity we find that almost all clients benefit from the commitment contract.
-
-However when given choice between the commitment and the status quo contract only 10\% choose the former one and thus forgo important benefits.
-This strongly suggests that ``private paternalism'', a policy that advances an individual's interests by restricting her freedom, is beneficial in our context.
-We provide a quantification of the size of unrealized benefits that arise when clients have choice.
-Methodologically, to our knowledge this is the first paper in economics that uses machine learning methods to estimate personalized counterfactual treatment gains and ask whether treatment take up is positively selected.
-
-Needless to say, pawnshop borrowing likely attracts particularly unsophisticated clients (millions of them).
-Choice may fare better in other contexts.
-Choice may also fare better with other contracts besides the fee-commitment one.
-We experimented with a ``softer'' commitment contract in the form of a personal promise, and found that although promise-commitment contracts do indeed elicit more interest they did not cause changes in behavior.
-
-We see three lines of further work that are of interest.
-First, investigate why the fee-commitment contract had such low demand in spite of its across-the-board benefits.
-In particular if naivete about self control problems, biased expectation about income shocks, or ambiguity aversion play a role.
-Second, whether other types of contracts ---for instance less coarse choice menus--- could induce larger demand and better performance.
-Third, whether individuals choosing to borrow from pawnshops are more present biased and naive than similar individuals borrowing from other types of lenders.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\pagebreak
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%BIBLIOGRAPHY
-
-\clearpage
-\bibliographystyle{authordate1}
-%\bibliographystyle{amsalpha}
-%\bibliographystyle{AER}
-
-\bibliography{References}
-
-%\FloatBarrier
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\newpage
-\singlespacing
-
-\section{Tables}
-
-\begin{table}[H]
-\caption{Summary statistics and Balance}
-\label{SS}
-\begin{center}
-\scriptsize{\input{./Tables/SS.tex}}
-\end{center}
- \scriptsize
-This table presents balance tests for the administrative data (Panel A) and survey data (Panel B).
-Each column corresponds to an arm of the experiment: control (status quo contract), no choice with fee, no choice with promise, choice among both contracts where the commitment contract has fee, and choice among both contracts where the commitment contract involves only a promise.
-The last column show the p-value of an F-test of the hypothesis that the mean across arms for that variable is the same across the 5 arms.
-Randomization was done at the branch-day level.
-By design the observation are not exactly equal cross arms as we were more interested in detecting effects in the choice-fee arm and less so in the no-choice-promise.
-Loan amount is the peso amount given to the client; Monday is the fraction of loans given on a Monday; number of pledges is the number of loans given in each arm.
-That it is balanced shows that there was no detectable selection across arms when clients found out what was the contract.
-In Panel B: woman indicated whether the client is female, age of the client is measured in years; has pawned before is a dummy=1 if the client declares to have pawned before (although not necessarily with Lender $P$).
-The subjective probability of recovery was elicited a la Manski, from 0 to 100 what is the probability that you will recoup your pawn.
-High-school is a dummy that indicates if the client has completed high school.
-Finally, the response rate is the percentage of clients in the admin data for whom we have a baseline survey.
-%\textit{Do file: } \texttt{ss.do}
-\end{table}
-
-\pagebreak
-
-\begin{table}[H]
-\caption{Intermediate outcomes}
-\label{mechanisms}
-\begin{center}
-\scriptsize{\input{./Tables/mechanism.tex}}
-\end{center}
- \scriptsize
-This table explores treatment effects in ``intermediate variables''.
-Each column represents a different dependent variable in an OLS regression, and each panel represents a different treatment arm-control comparison.
-All regressions include fixed effects for branch, day of week fixed effects, number of pawns at the time of pawning this particular one, number of different treatment arms experienced before pawning this particular one.
-$R^2$ are not reported, they were less than 0.04 for all but the last column which had $R^2$'s close to 0.6.
-The last row shows the mean of the dependent variable for the control group.
-Dependent variables are as follows: Column (1) measures the number of days elapsed from the pawning date to the first payment done.
-Column (2) records the number of payments done within 230 days of the pawn.
-Column (3) is the average size of the payments for each client in pesos.
-Column (4) is self-reported cost to get to the branch plus the imputed loss of a whole day of salary (using the minimum wage in Mexico) multiplied by the number of visits to the branch.
-Column (5) measures the number of days it took to recover the pawn, conditional on recovering.
-The dependent variable in Column (6) is a dummy =1 if the client paid any positive amount within 230 days of the pawn.
-For Columns (7) and (8) the dependent variable it is the sum of total payments done within 230 days of the pawn divided by the size of the loan, but column (8) includes as regressors a dummy=1 if the client recovered her pawn, and its interaction with treatment.
-
-%\textit{Do file: } \texttt{mechanisms.do}
-\end{table}
-
-\begin{table}[H]
-\caption{Overconfidence: Take-up and Treatment Effects}
-\label{oc_reg}
-\begin{center}
-\scriptsize{\input{./Tables/oc_reg.tex}}
-\end{center}
- \footnotesize This table shows the parameter estimates of $y_i = \alpha + \beta \: OC_i + X_i'\gamma + \epsilon_i$, where $OC_i:=\mathbbm{1}(P^s_i-\widehat{P_i(X_i)}>0)$ is an indicator for the subjective probability of recovery being larger that the predicted one.
-In columns 1-4 $y_i$ is a dummy for whether the client $i$ chose to have the commitment contract in the respective choice arm, and in columns 5 and 6 $y_i$ is the heterogeneous treatment effect for financial cost (in pesos) estimated by comparing the fee-forcing vs status quo arms in Section \ref{TE_fee-forcing}.
-Columns 1 and 3 are estimated for the promise-choice arm, while columns 2 and 4 are estimated for the fee-choice arm.
-%\textit{Do file: } \texttt{oc.do}
-\end{table}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-\section{Figures}
-
-\begin{figure}[H]
-     \caption{Experiment description}
-    \label{exp_description}
-    \begin{center}
-    \begin{subfigure}{.50\textwidth}
-      \caption{Timeline of the experiment}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/timeline_suc_exp_extended.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.45\textwidth}
-    \caption{Experiment arms}
-       \centering
-      \includegraphics[width=\textwidth]{Figuras/exp_arms.PNG}
-    \end{subfigure}
-    \end{center}
-         \scriptsize Panel (a) displays in black arrows the period covered by our administrative data: from August 6th 2012 (30 days before the experiment began) to August 13th 2013.
-The gray lines arrows correspond to the dates of implementation of the experiment.
-We finished the experiment earlier in branches 1 and 2 because we realized that we would have enough sample size with the remaining branches and save on operational costs.
-Panel (b) shows our 5 treatment arms: control (status quo contract), no choice with fee, no choice with promise, choice among both contracts where the commitment contract has a fee, and choice among both contracts where the commitment contract involves only a promise.
-Within each arm it displays the number of observations.
-And  for the choice groups it splits the sample size into those who chose the commitment contract (shaded blue triangle) and those that did not (un-shaded triangle).
-%\textit{Do file: }  \texttt{timeline\_suc\_exp.do}
-\end{figure}
-
-\begin{figure}[H]
-     \caption{Explanatory Material: Promise-Choice Days}
-    \label{ExplanatoryMaterial}
-    \begin{center}
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/MicaChoiceDonde.png}
-    \end{subfigure}
-    \end{center}
-    \scriptsize
-        This is a (translated) sample information mica shown to clients in choice-promise days.
-The real ones were twice the size of this figure and were laminated.
-Different ones were shown in each treatment arm.
-\end{figure}
-
-\begin{figure}[H]
-        \caption{Distribution of Overconfidence}
-    \label{oc_hist}
-    \begin{center}
-        \centering
-        \includegraphics[width=0.55\textwidth]{Figuras/oc_hist.pdf}
-    \end{center}
-    \scriptsize
-     In the baseline survey at the branch, before the client knew the contract of had the pawn appraised, they were asked from 0 to 100, how likely is that they would be able to recover their pawn if pawned.
-We generate a variable we call overconfidence (OC) defined as the reported subjective probability of recovery minus the predicted probability ($P^s_i-\widehat{P_i(X_i)}$).
-We predict $\widehat{P_i(X_i)}$ using LASSO as explained in the text.
-This figure uses all observations for which we have data on $P^s_i$ and $X_i$ from the baseline survey.
-     %\textit{Do file: }  \texttt{oc.do}
-
-\end{figure}
-
-\begin{figure}[H]
-     \caption{Financial cost}
-    \label{fc_hist}
-    \begin{center}
-    \begin{subfigure}{.45\textwidth}
-      \caption{In pesos}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_fc.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.45\textwidth}
-    \caption{As a fraction of the loan}
-       \centering
-      \includegraphics[width=\textwidth]{Figuras/hist_fc_perc_loan.pdf}
-    \end{subfigure}
-    \end{center}
-         \scriptsize
-         Panel (a) presents a histogram of financial cost for the control group.
-Financial cost is defined as the sum of payments made by a client towards recovering her pawn + the cost of the pawned piece when she ends up losing it.
-In the paper we use different costs of losing the pawn: its value in gold, or the self reported subjective (e.g.
-jewelry may have sentimental value).
-This Figure uses the gold value.
-We plot separately the financial cost for those who lose the pawn (blue) and those that recover it (transparent).
-Panel (b) is analogous but we normalized the financial cost dividing it by the loan size.
-%Given that the loan lasts close to 90 days, bringing payments to present value makes little difference.
-      %\footnotesize{ } \textit{Do file: }  \texttt{hist\_fc.do}
-\end{figure}
-
-\begin{figure}[H]
-    \caption{The effect of the fee-forcing treatment}
-    \label{fc_pro2}
-    \begin{center}
-    \begin{subfigure}{0.45\textwidth}
-        \caption{Financial cost}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/fc_te_pro_2.pdf}
-    \end{subfigure}
-        \begin{subfigure}{0.45\textwidth}
-        \caption{Financial cost (quantile reg)}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/fc_quantile_pro_2.pdf}
-    \end{subfigure}
-
-        \bigskip
-        \bigskip
-
-    \begin{subfigure}{0.45\textwidth}
-        \caption{Financial cost (HTE)}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_2.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.45\textwidth}
-        \caption{Lost pawn}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/def_te_pro_2.pdf}
-    \end{subfigure}
-
-    \end{center}
-        \scriptsize 
-        This figure shows the estimated treatment effect of ``forcing'' the frequent payment commitment contract using fees, compared to the status-quo (control) for  financial cost (Panel a), quantiles of financial cost (Panel b), and for an indicator of losing the pawn (Panel c).
-In Panel (a) each dot represents the estimated treatment effect for a different definition of financing cost, or for a different sub-population, and its 95\% confidence interval.
-From left to right, the first effect corresponds to using the gold value of the pawned piece in the definition of financial cost and discounting the payments to present value using a 7\% monthly rate; the second uses the subjective value of the pawn; the third is analogous to the second but adds transaction cost (transport+1 day's wage) per visit; the fourth conditions on the population that paid any positive amount towards recovery of their pawn; the fifth conditions on the sub-population of the treatment group that paid a fee and compares these to all the control group; the sixth conditions on the intersection of the previous two sub-populations.
-Panel (b) plots the effects on different quantiles of the distribution of financial cost (using the first definition): 15th, 25th, 50th, 75th, 85th percentile.
-        Panel (c) plots the distribution of the heterogeneous treatment effects on financial cost, estimated using \cite{atheygrf}.
-The distribution plots the FC treatment effect for the interval $[\mu-2\sigma,\mu+2\sigma]$ to ignore the outliers.
-Panel (d) Measures the effect of treatment on the likelihood of losing their pawn.
-The first coefficient compares all the treatment group vs all the control; the second conditions on the period covering 120 days.
-The third conditions on the population that paid any positive amount towards recovery of their pawn; the fourth conditions on having paid at least 30\% of the loan amount.
-% the effect on ``repeat purchase''.
-That is likelihood of doing an additional pawn (in treatment vs control) after having been subjected to treatment for at least 75 days.
-The second coefficient estimates the regression conditional on recovering the pawn \hl{in both treatment and control}, and the rightmost coefficient compares those above the median treatment effect in financial cost savings, \hl{versus all the control group.}
-      %\textit{Do file: }  \texttt{fc\_te.do, def\_te.do, fc\_quantilereg.do}
-\end{figure}
-
-\begin{figure}[H]
-        \caption{Effects on repeat purchasing}
-    \label{reincidence}
-    \begin{center}
-        \centering
-        \includegraphics[width=0.6\textwidth]{re_te.pdf}
-    \end{center}
-     \scriptsize This figure shows the estimated effects on repeat purchasing of the four treatment arms (fee-forcing, choice-fee, fee-promise, choice-promise) compared to the status-quo control group.
-It shows robustness of the effects by focusing on different sub-populations.
-The leftmost coefficient compares all the fee-forcing group against all status quo group.
-The second coefficient conditions on the first pawn not being recovered when the second was pawned.
-The third coefficient uses all clients (in both the fee-forcing and the status-quo arms) who had an estimated heterogeneous treatment effect above the median.
-Conditioning on this set keeps the sample balanced across arms and therefore still allows for a causal interpretation.
-For the choice arm we present three coefficients: coefficients represented by a circle compare all those offered choice to all those in the status quo arm, thus estimating a causal effect.
-Coefficients in triangles and squares represent those that self-select into the fee or promise arms and compare this subset against the whole status quo arm.
-They therefore contain a selection effect together with the treatment effect and cannot be interpreted causally.
-      %\footnotesize{ \textit{Do file: }  \texttt{re\_te.do}
-\end{figure}
-
-\begin{figure}[H]
-    \caption{The effect choice between fee-commitment and status quo}
-    \label{fc_pro4}
-    \begin{center}
-    \begin{subfigure}{0.45\textwidth}
-        \caption{Financial cost}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/fc_te_pro_4.pdf}
-    \end{subfigure}
-        \begin{subfigure}{0.45\textwidth}
-        \caption{Financial Cost (quantile reg)}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/fc_quantile_pro_4.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.5\textwidth}
-
-        \bigskip
-        \bigskip
-
-        \caption{Lost Pawn}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/def_te_pro_4.pdf}
-    \end{subfigure}
-    \end{center}
-        \scriptsize
-        This figure is analogous to Figure \ref{fc_pro2}.
-It measures the effect of being given \textit{choice} between the frequent payment commitment contract with fees and the status-quo contract, versus being \textit{``forced''} into the status-quo contract (control).
-Again it focuses our two main outcomes: financial cost and an indicator for losing the pawn.
-Circles present the treatment effects.
-The figures also presents differences in these two outcomes for those who chose the frequent payment commitment contract versus the whole control group (squares-NSQ), and also for those who chose the status quo contract versus the whole control group (triangles-SQ).
-Note that these two comparisons are not pure causal effects since people who chose the frequent payment commitment contract may be different from those that do not.
-That is: the squares and triangles combine selection and treatment effects.
-Finally, for comparison purposes, the blue diamond displays the effects of forcing them into the frequent payment commitment contract and are just transcribed from Figure \ref{fc_pro2} above.
-      %\textit{Do file: }  \texttt{fc\_te\_choice\_dec.do, def\_te\_choice\_dec.do, fc\_quantilereg\_choice\_dec.do}
-\end{figure}
-
-\begin{figure}[H]
-    \caption{Choice of contracts and treatment effects}
-    \label{choose_wrong}
-    \begin{center}
-        \begin{subfigure}{0.45\textwidth}
-        \caption{Chose wrong}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/line_cw_fc_te_cf.pdf}
-
-    \end{subfigure}
-        \begin{subfigure}{0.45\textwidth}
-        \caption{By overconfidence/naivete}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/line_cw_fc_te_cf_OC_fee.pdf}
-
-    \bigskip
-
-    \end{subfigure}
-        \begin{subfigure}{0.45\textwidth}
-        \caption{\% better when forced to fee-commitment}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/line_better_forceall_fc_te_cf.pdf}
-
-    \end{subfigure}
-        \begin{subfigure}{0.45\textwidth}
-        \caption{\footnotesize{Effect of losing pawn vs predicted take-up}}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/takeuppr_def.pdf}
-    \end{subfigure}
-
-    \end{center}
-        \scriptsize
-        In Panel (a) we estimate what the treatment effect of the commitment contract \textit{would have been} for all subjects in the choice arm if they had been forced into the fee-commitment contract.
-To do this we proceed in two steps.
-First, we estimate treatment effects in the forcing arm by comparing the fee-forcing arm against the status quo arm.
-We let these effects be heterogeneous as a function of our $x$'s using \cite{atheygrf}'s methodology of causal forests.
-Second, we extrapolate these treatment effects based on the choice arm using the same $x$'s.
-Once we have personalized counterfactual treatment effects in the choice we calculate what fraction of subjects in the choice arm incurred in financial costs that are  $> z$\% than if they had chosen the opposite contract of what they actually chose, were $z$\% is defined as a fraction of the loan.
-$z$\% is a level of tolerance we can vary and we plot it in the X-axis.
-The left Y-axis measures the fraction of subjects that would have been better by a margin of $z$\% if they changed their choice, and the right Y-axis measures the amount of money ``left on the table''.
-The thinly dotted lines represent 95\% confidence intervals.
-Panel (b) is analogous to Panel (a) except that it does the exercise separately for clients we classified as overconfident ($OC_i:=\mathbbm{1}(P^s_i-\widehat{P_i(X_i)}>0))$ and those we classified as not overconfident.
-Panel (c) simulates what percentage would be better by at least $z$ if we forced everybody of those in the fee-choice arm into the fee-commitment contract.
-Panel (d) asks whether it is the case that people with larger causal savings from the fee-forcing contract would be more likely to select that contract.
-To do this we proceed in two steps as well.
-First we estimate a flexible model of take-up of the fee commitment contract \textit{in the choice arm} using random forests, and from this model obtain a probability $P(x_i)$ of choosing the fee-forcing contract for a client with characteristics $x_i$.
-We extrapolate this model to clients in the fee-forcing arm to estimate what would they have chosen if we had given them choice.
-Figure (d) plots $\widehat{P(x_i)}$ in the X-axis using a binscatter that splits the X-axis in 100 percentile bins.
-The Y-axis plots the heterogeneous treatment effects of the fee forcing contract on the probability of losing the pawns (more negative means then more likely to recover it), averaged for the respective x-axis bin.
-Positive assortative selection would mean a negative relationship: those who benefit more by treatment and lose the pawn less are more likely to choose it.
-Using all bins we estimate a slope of zero in the relationship.
-Using the 80 right most points, we estimate a \textit{positive} relationship.
-        %\textit{Do file: }  \texttt{effect\_contr\_takeup.do, choose\_wrong\_quant\_wrong.do, choose\_wrong\_quant\_wrong\_decomposition.do}
-\end{figure}
-
-\begin{figure}[H]
-    \caption{The effect of promises}
-    \label{fc_pro5}
-    \begin{center}
-
-    \begin{subfigure}{0.45\textwidth}
-        \caption{Financial cost -- Promise-forcing}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/fc_te_pro_3.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.45\textwidth}
-        \caption{Losing Pawn -- Promise-forcing}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/def_te_pro_3.pdf}
-    \end{subfigure}
-
-    \bigskip
-    \bigskip
-
-        \begin{subfigure}{0.45\textwidth}
-        \caption{Financial cost -- Choice}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/fc_te_pro_5.pdf}
-    \end{subfigure}
-        %\begin{subfigure}{0.45\textwidth}
-        %\caption{Quantile regression}
-        %\centering
-        %\includegraphics[width=\textwidth]{Figuras/fc_quantile_pro_5.pdf}
-    %\end{subfigure}
-    \begin{subfigure}{0.45\textwidth}
-        \caption{Losing Pawn -- Choice}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/def_te_pro_5.pdf}
-    \end{subfigure}
-
-    \end{center}
-    \scriptsize
-    Panels (a) and (b) in this figure show the estimated treatment effects of ``forcing'' the frequent payment commitment contract using promises, compared to the status-quo (control) for financial cost (Panel a), and for an indicator of losing the pawn (Panel b).
-Panels (c) and (d) are analogous but focus on the effect of giving choice between frequent payment commitment contract using promises and the status quo contract.
-In Panel (a) each dot represents the estimated treatment effect for a different definition of financing cost, or for a different sub-population, and its 95\% confidence interval.
-From left to right, the first effect corresponds to using the gold value of the pawned piece in the definition of financial cost and discounting the payments to present value using a 7\% monthly rate; the second uses the subjective value of the pawn; the third is analogous to the second but adds transaction cost (transport+1 day's wage) per visit; and the fourth conditions on the population that paid any positive amount towards recovery of their pawn.
-Panel (b) plots the effect of not recovering the pawn: the leftmost coefficients compares all those assigned to the promise-forcing arm vs all those in the status quo contract, where the dependent variable=1 if the client has not recovered the pawn 230 days after pawning.
-The next coefficient defines the dependent variable=1 if the client has not recovered the pawn 120 days after pawning.
-The third coefficient conditions on paying a positive amount, and the fourth conditions on paying at least 30\% of the loan.
-Panels (b) and (c) measure the effect of being given \textit{choice} between the frequent payment commitment contract with promise and the status-quo contract, versus being \textit{``forced''} into the status-quo contract (control).
-Again it focuses our two main outcomes: financial cost and an indicator for losing the pawn.
-Circles present the treatment effects.
-The figures also presents differences in these two outcomes for those who chose the frequent payment commitment contract versus the whole control group (squares-NSQ), and also for those who chose the status quo contract versus the whole control group (triangles-SQ).
-That is: the squares and triangles combine selection and treatment effects.
-      %\footnotesize{ } \textit{Do file: }  \texttt{fc\_te\_choice\_dec.do, def\_te\_choice\_dec.do, fc\_te.do, def\_te.do }
-\end{figure}
-
-%\begin{figure}[H]
-%    \caption{The effect of the promise-forcing treatment}
-%    \label{fc_pro3}
-%    \begin{center}
-%        \begin{subfigure}{0.45\textwidth}
-%        \caption{Quantile regression}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/fc_quantile_pro_3.pdf}
-%    \end{subfigure}
-%    
-%    \end{center}
-%             \footnotesize \textit{Notes: } 
-%      \footnotesize{ } \textit{Do file: }  \texttt{fc\_te.do, def\_te.do, fc\_quantilereg.do}
-%\end{figure}
-
-\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% APPENDIX TABLES
-
-\setcounter{table}{0}
-\renewcommand{\thetable}{A\arabic{table}}
-
-\setcounter{figure}{0}
-\renewcommand{\thefigure}{A\arabic{figure}}
-
-\setcounter{section}{0}
-\setcounter{subsection}{0}
-\renewcommand\thesection{A\arabic{section}}
-\renewcommand\thesubsection{\thesection\arabic{subsection}}
-
-\appendix
-
-\section{APPENDIX}
-
-\subsection{Some materials}
-
-\vspace{.1in}
-\begin{figure}[H]
-     \caption{Contract Terms Summary, and Promise Slip}
-    \label{PaperSlip}
-    \begin{center}
-    \begin{subfigure}{0.65\textwidth}
-    \caption{Elapsed days to first payment}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/TicketLenderP.png}
-    \end{subfigure}
-
-    \vspace{3ex}
-    \begin{subfigure}{0.45\textwidth}
-    \caption{Elapsed days to first payment}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/Personal Promise.png}
-    \end{subfigure}
-    \end{center}
-    \scriptsize
-        The top of this figure is a sample receipt that was given to clients that got assigned to the fee-forcing contract (the font and format were changed to protect Lender's P identity).
-We want to highlight the salience of some items.
-First the title clearly indicated which contract the client has (arrow 1).
-Second, in the case of the fee contract it clearly indicates that there is a fee for paying late equivalent to 4\% of the value of the monthly payment (arrow 2).
-Third, there is a calendar for payments clearly specifying the dates and amounts to pay each month.
-The bottom panel of the figure shows a ``promise slip'', the paper that those who were assigned (or chose) to the monthly payment with promise had to sign to make the promise salient.
-It emphasizes that the client is giving his word, and that the promise is not a legal document.
-\end{figure}
-
-%\begin{figure}[H]
-%        \caption{Booklet with product information}
-%    \label{micas}
-%    \begin{center}
-%        \centering
-%        \includegraphics[width=\textwidth]{micas.pdf}
-%    \end{center}
-%     \footnotesize \textit{Notes: } 
-%      \footnotesize{ }
-%\end{figure}
-
-%\begin{figure}[H]
-%     \caption{Booklet with product information translated}
-%    \label{booklet_translate2}
-%    \begin{center}
-%    \begin{subfigure}{.9\textwidth}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/MP_F.pdf}
-%    \end{subfigure}
-    %\begin{subfigure}{0.55\textwidth}
-    %   \centering
-    %  \includegraphics[width=\textwidth]{Figuras/MP_2.pdf}
-    %\end{subfigure}
-%    \end{center}
-%\end{figure}
-
-\afterpage{
-\begin{landscape}
-
-\subsection{Surveys}
-
-\begin{table}[H]
-\caption{Baseline survey}
-\label{baseline_survey}
-\begin{center}
-\scriptsize{\input{./Tables/baseline_survey1.tex}}
-\end{center}
- \scriptsize 
-%\textit{Do file: } \texttt{ss.do}
-\end{table}
-
-\begin{table}[H]
-\begin{center}
-\scriptsize{\input{./Tables/baseline_survey2.tex}}
-\end{center}
- \scriptsize 
-%\textit{Do file: } \texttt{ss.do}
-\end{table}
-
-\begin{table}[H]
-\begin{center}
-\scriptsize{\input{./Tables/baseline_survey3.tex}}
-\end{center}
- \scriptsize 
-%\textit{Do file: } \texttt{ss.do}
-\end{table}
-\end{landscape}
-}
-
-\begin{table}[H]
-\caption{Survey's non-response balance}
-\label{balance_response}
-\begin{center}
-\scriptsize{\input{./Tables/balance_response.tex}}
-\end{center}
- \scriptsize This table shows whether the means of variables in the administrative dataset are different for those that respond the baseline survey vs those that do not.
-We use this as an assessment of external validity.
-Internal validity is guaranteed because the baseline survey was implemented before treatment assignment and therefore response rates are orthogonal to treatment assignments.
-Panel A studies the baseline survey, while Panel B focuses on the exit survey.
-The columns labeled ``p-values'' report p-values for the test that the means of the respective variable are the same for those that responded did not respond the survey.
-%\textit{Do file: } \texttt{balance\_response.do}
-\end{table}
-
-\begin{comment}
-\begin{table}[H]
-\caption{Reincidence SS}
-\label{tab_reincidence}
-\begin{center}
-\scriptsize{\input{./Tables/tab_reincidence.tex}}
-\end{center}
- \scriptsize
-%\textit{Do file: } \texttt{tab\_reincidence.do}
-\end{table}
-
-\begin{table}[H]
-\caption{Summary statistics (exit survey)}
-\label{SS_exit}
-\begin{center}
-\scriptsize{\input{./Tables/SS_exit.tex}}
-\end{center}
- \scriptsize We carried out an exit survey.
-It had a small response rate and we don't use it in the paper.
-Here it shows that the characteristics of those that responded it are balanced across arms (Panel B).
-Panel A reports outcomes.
-%\textit{Do file: } \texttt{ss.do}
-\end{table}
-\end{comment}
-
-\newpage
-\subsection{Some more evidence of overconfidence}
-
-\vspace{.2in}
-\begin{figure}[H]
-    \caption{Behavior of those who lost pawn}
-    \label{proxy_naive}
-    \begin{center}
-    \begin{subfigure}{0.40\textwidth}
-        \caption{Elapsed days to first payment}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_firstdays_default.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.40\textwidth}
-        \caption{Elapsed days to last payment}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_days_default.pdf}
-    \end{subfigure}
-        \begin{subfigure}{0.40\textwidth}
-        \caption{Payments as \% of loan}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_percpay_default.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.40\textwidth}
-        \caption{Number of payments}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_numpay_default.pdf}
-    \end{subfigure}
-    \end{center}
-        \scriptsize 
-        This figure describes behavior for the subsample of clients whose pawn was not recovered (in the control group).
-Panel (a) shows days elapsed from the pawn to the first payment, while panel (b) displays the days elapsed to last payment.
-Some people pay after the day 105 when the grace period ends because the can ``restart'' the loan if they pay all interest owed.
-It amounts to starting a new loan with the same conditions and same pawn.
-Panel (c) shows the fraction of the loan that they paid (even when they ended up losing the pawn).
-Panel (d) displays the number of times they went to the branch to pay.
-      %\textit{Do file: }  \texttt{hist\_den\_default.do}
-\end{figure}
-
-\newpage
-\subsection{Main treatment effects: Additional material}
-
-\vspace{.2in}
-\begin{figure}[H]
-        \caption{Financial cost effect: charging all fees}
-    \label{fc_allfee}
-    \begin{center}
-        \centering
-        \includegraphics[width=0.50\textwidth]{Figuras/fc_allfee_quantile_pro_2.pdf}
-    \end{center}
-    \scriptsize
-     This figure is the analogous to Figure \ref{fc_pro2}(b), except that for the fee-forcing contract we pretend that all clients incurred in their late fees, and therefore inflate the financial cost by summing those fees.
-This is intended as a kind of worse case scenario for the financial cost of the fee-forcing contract.
-The circles indicate the quantile treatment effects, while the cross is the (OLS) mean.
-We still find that the financial cost of will be smaller under the fee-forcing contract in spite of artificially inflating it.
-     %\texttt{fc\_all\_fee.do}
-\end{figure}
-
-\begin{figure}[H]
-        \caption{FC as \% of loan - treatment effect}
-    \label{fc_perc}
-    \begin{center}
-        \centering
-        \includegraphics[width=0.50\textwidth]{Figuras/fc_perc_te_allarms.pdf}
-    \end{center}
-     \scriptsize This figure shows the estimated treatment effect of all arms against the status quo, but normalizing the dependent variable by the value of the loan.
-     %\textit{Do file: }  \texttt{fc\_perc\_allarms.do}
-\end{figure}
-
-\begin{figure}[H]
-    \caption{Relationship between treatment effects}
-    \label{induced_to_pay_early}
-    \begin{center}
-    \begin{subfigure}{0.45\textwidth}
-        \caption{\footnotesize{Induced to pay earlier vs Induced Lower FC}}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/binscatter_fc_days_pro_2.pdf}
-    \end{subfigure}
-        \begin{subfigure}{0.45\textwidth}
-        \caption{\footnotesize{Induced to pay earlier vs Induced Recovery}}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/binscatter_def_days_pro_2.pdf}
-    \end{subfigure}
-    \end{center}
-       \scriptsize 
-       This figure plots relationships between \textit{treatment effects}.
-Both Panels (a) an (b) have the same X-axis, which displays the estimated heterogeneous treatment effect on the outcome ``elapsed days of first payment'', that is how many days elapsed from the day the loan was awarded to the first payment the client made.
-The treatments effects were calculated using \cite{atheygrf}.
-In Panel (a) the Y-axis is the \textit{treatment effect} on financial cost.
-In Panel (b) the Y-axis is the \textit{treatment effect} on losing their pawn.
-Panel (a) shows that those induced to pay earlier are also those that have larger savings in financial cost as a result of ``forcing'' the frequent payment commitment contract compared to the status-quo (control).
-Panel (b) shows that those induced to pay earlier are also those that have a larger increase in recovery.
-      %\textit{Do file: }  \texttt{binscatter\_hte.do}
-\end{figure}
-
-\newpage
-\subsection{FOSD: fee forcing vs status quo financial cost distributions}
-
-\vspace{.2in}
-\begin{figure}[H]
-        \caption{Empirical CDF of Financial Cost: fee-focing vs status-quo}
-    \label{ecdf_fc}
-    \begin{center}
-        \centering
-        \includegraphics[width=0.65\textwidth]{Figuras/cdf_fc_pro_2.pdf}
-    \end{center}
-    \scriptsize This figure plots the empirical cumulative distribution of financial cost.
-It does this separately for the fee-forcing contract and for the status-quo contract.
-The doted line at the bottom is the difference of the status-quo CDF minus the fee-focing CDF.
-It shows that the CDF of the status quo contract is always below that of the fee-forcing (and this difference is significant for the points indicated by the blue line), and therefore that the former first-order stochastically dominates the later for weakly decreasing utility functions; see Proposition \ref{eq_fosd}.
-    % \texttt{ecdf\_fc.do}}
-\end{figure}
-
-\vspace{.2in}
-\begin{table}[H]
-\caption{Clients who should prefer fee-forcing financial cost distribution}
-\label{stochastic_dominance}
-\begin{center}
-\scriptsize{\input{./Tables/dominance.tex}}
-\end{center}
- \footnotesize
-This table does two things.
-First, it tests whether the observed empirical distribution of financial cost is well approximated by a log normal.
-It does this using two tests, the Anderson-Darling and the Kolmogorov-Smirnoff tests.
-Second, it fits a log normal distribution by maximum likelihood to observed empirical distribution of financial cost, separately for the fee-forcing arm and the status-quo arm.
-Using the fitted log normal, it tests whether the fee-forcing financial cost distribution would be preferred by any expected utility agent using Proposition \ref{lognormal_fosd} below.
-The different rows of the table do this for different sub-populations.
-The first row of the table does it for every client in the fee forcing and status quo arms.
-The ``*'' show that we cannot reject at the 5\% level that both distribution are log normal for any of the two tests.
-The column entitled ``Dominance'' shows whether any client that dislikes higher cost would prefer the fee-forcing cost distribution over the status quo one, with $\succeq_{1}$ meaning he should (with $\succeq_{1}^*$ indicating the difference is statistically significant).
-It turns out to be the case that for the overwhelming majority of sub-populations, the conditions of preferring the fee-forcing distribution hold.
-%\textit{Do file: } \texttt{stoch\_dominance.do}
-\end{table}
-
-\vspace{.2in}
-\begin{prop}
-\label{lognormal_fosd}
-\footnotesize{
-Let $F$ and $G$ be the cumulative distributions of two alternative log-normal prospects. The following are equivalent:
-
-\begin{enumerate}[(a)]
-    \item For every weakly decreasing utility function $u$: $E_{F}(u(FC))\leq E_G(u(FC))$
-    \item $E_F \log(FC)\geq E_G\log(FC)$ and $Var_F \log(FC)= Var_G\log(FC)$
-\end{enumerate}
-}
-\end{prop}
-
-\begin{proof}
-\footnotesize{
-See Theorem 4 in \cite{lognormal_dominance}.
-}
-\end{proof}
-
-\vspace{.1in}
-\begin{prop}
-\label{eq_fosd}
-\footnotesize{
-This is a standard result. 
-\\
-\vspace{.1in}
-The following are equivalent:
-\begin{enumerate}[(a)]
-    \item For every weakly decreasing utility function $u$: $E_{sq}(u(FC))\leq E_{fee}(u(FC))$
-    \item $F_{sq}(FC)\leq F_{fee}(FC)$ 
-\end{enumerate}
-}
-\end{prop}
-\begin{proof} \;
-\footnotesize{
-
-[$(a)\Longrightarrow (b)$] Suppose  $(b)$ does not hold. So there exists $FC^*$ such that $F_{sq}(FC^*)>F_{fee}(FC^*)$, Define $u:=\mathds{1}_{FC\leq FC^*}$. Then
-\[E_{sq}(u(FC)) = \int u(FC)dF_{sq} = F_{sq}(FC^*)>F_{fee}(FC^*)= \int u(FC)dF_{fee} =E_{fee}(u(FC))\]
-which contradicts $(a)$.\\
-
-[$(a)\Longleftarrow (b)$] On the other hand for $u$ weakly decreasing,
-
-\[\int u(y(FC))dF_{sq}(y(FC)) = \int u(y(FC))dF_{fee}(FC) \leq \int u(FC)dF_{fee}(FC)\]
-with $y(FC) = F_{sq}^{-1}F_{fee}(FC)$.
-}
-\end{proof}
-\footnotesize{
-Note the proof was done in the case of absolutely continuous and strictly increasing distribution functions $F_{sq}$ and $F_{fee}$.
-}
-
-\newpage
-\subsection{Causal Random Forest and HTE}
-
-\vspace{.3in}
-\begin{figure}[H]
-        \caption{Honest causal tree for the fee forcing contract heterogenous treatment effects}
-    \label{casual_tree}
-    \begin{center}
-        \centering
-        \includegraphics[width=.8\textwidth]{Figuras/crf_pro_2_fc_admin_disc.pdf}
-    \end{center}
-    \footnotesize 
-    This is one(it is chosen such that it minimizes the pruned cost, that is it is the tree with the smallest root-node impurity) of the honest causal trees in the random forest we use for the estimation of the heterogeneous treatment effect of the fee-forcing contract.
-It is meant only as an example of how these trees look like.
-The forest was such that there are as many estimated treatment effects as there are clients.
-     %\footnotesize{ \textit{RScript: }  \texttt{grf.R}
-\end{figure}
+  num.threads = NULL)}}
 
@@
     \begin{center}
+    %\begin{subfigure}{0.4\textwidth}
+    %    \caption{Financial cost}
+    %    \centering
+    %    \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_2.pdf}
+    %\end{subfigure}
+    \begin{subfigure}{0.7\textwidth}
+        \caption{Determinants of effects}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_fc_admin_disc_pro_2.pdf}
+    \end{subfigure}
+
+    %\begin{subfigure}{0.4\textwidth}
+    %    \caption{Losing Pawn}
+    %    \centering
+    %    \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_2.pdf}
+    %\end{subfigure}
+    %\begin{subfigure}{0.4\textwidth}
+    %    \caption*{}
+    %    \centering
+    %    \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_def_c_pro_2.pdf}
+    %\end{subfigure}
+    \end{center}
+     \scriptsize  This figure estimates bivariate regressions of the estimated client-level heterogeneous treatment effects against the respective covariate from the baseline survey  $\widehat{hte_i} = \alpha + \beta \: X_i + \epsilon_i$.
+The regressors $X_i$ include (e.g if the family asks for money, if they have savings, if they are overconfident using the definition the text, etc.
+See this appendix for a transcription of the survey).
+      %\footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}}
+\end{figure}
+
+\begin{comment}
+\begin{figure}[H]
+    \caption{Heterogeneous Treatment Effect: Promise-forcing contract}
+    \label{heterogeneous_te_3}
+    \begin{center}
     \begin{subfigure}{0.4\textwidth}
@@
         \centering
-        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_2.pdf}
+        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_3.pdf}
     \end{subfigure}
@@
         \centering
-        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_fc_admin_disc_pro_2.pdf}
+        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_fc_admin_disc_pro_3.pdf}
     \end{subfigure}
@@
         \centering
-        \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_2.pdf}
+        \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_3.pdf}
     \end{subfigure}
@@
         \centering
-        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_def_c_pro_2.pdf}
-    \end{subfigure}
-    \end{center}
-     \scriptsize  The left hand side of Panel (a) plots the distribution of heterogeneous treatment effects estimated using the methodology of \cite{atheygrf}.
-The right hand side estimates bivariate regressions of those treatment effects against the respective covariate from the baseline survey  $\widehat{hte_i} = \alpha + \beta \: X_i + \epsilon_i$.
-The regressors $X_i$ include (e.g if the family asks for money, if they have savings, if they are overconfident using the definition the text, etc.).
-      %\footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}}
-\end{figure}
-
-\begin{figure}[H]
-    \caption{Heterogeneous Treatment Effect: Promise-forcing contract}
-    \label{heterogeneous_te_3}
-    \begin{center}
-    \begin{subfigure}{0.4\textwidth}
-        \caption{Financial cost}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_3.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.4\textwidth}
-        \caption*{}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_fc_admin_disc_pro_3.pdf}
-    \end{subfigure}
-
-    \begin{subfigure}{0.4\textwidth}
-        \caption{Losing Pawn}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_3.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.4\textwidth}
-        \caption*{}
-        \centering
         \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_def_c_pro_3.pdf}
@@
 \end{figure}
+\end{comment}
 

### 2020-06-16 main.tex
author edit

@@
 Jose Maria Barrero, Emilio Gutierrez, Aprajit Mahajan, Matt Rabin and seminar participants at ITAM provided very valuable feedback.}}
-\author{Isaac Meza \and Joyce Sadka \and Enrique Seira   \thanks{Sadka: ITAM, jsadka@itam.mx;  
-Seira: ITAM, enrique.seira@itam.mx; Meza: University of California at Berkeley, isaac.meza@berkeley.edu} }
+\author{Isaac Meza \and Joyce Sadka \and Enrique Seira   \thanks{Meza: University of California at Berkeley, isaac.meza@berkeley.edu; Sadka: ITAM, jsadka@itam.mx;  
+Seira: ITAM, enrique.seira@itam.mx} }
 \date{This draft:  \today \\[2 cm]}

### 2020-06-18 MATLAB/V1.m
first draft

@@ -1,34 +1,0 @@
-function [V, pp, d] = V1(y,m,parms)
-% Value function at time period t=1
-beta_belief = parms.beta_belief; delta = parms.delta; 
-val = parms.v; r =parms.r; mu = parms.mu; sigma = parms.sigma;
-
-% Sample to compute V2:
-y_prime = exp(mu + sigma.*randn(parms.rep,1));
-
-% Value function:
-VV = @(p) log(y-p) + mean(V2(y_prime,(1+r)*(m-p),parms));
-
-mn = min(m,y); mx = max(mn); grid = linspace(0,mx,parms.gridsize); 
-F = zeros(length(y),parms.gridsize);
-for i = 1:parms.gridsize
-    % Computationally expensive
-    F(:,i) = VV(grid(i));
-end
-
-% Optimal Interior Point Value
-[V,ind] = max(F,[],2);
-% Optimal int point policy
-pp = grid(ind)';
-
-% Optimum for paying debt at this time period if possible
-opt = -Inf*ones(length(y),1);
-opt(m<=y) = log(1+val) + log(y-m) + ...
-    (beta_belief*delta + beta_belief*delta^2)*(log(1+val) + mu);
-
-%% Optimum values
-ind_change = V<opt;
-V(ind_change) = opt(ind_change); pp(ind_change) = m;
-% Paid loan
-d = (pp==m);
-end

### 2020-06-18 MATLAB/V2.m

@@ -1,58 +1,0 @@
-function [V, pp, d] = V2(y,m,parms)
-% Value function at time period t=2
-beta_belief = parms.beta_belief; delta = parms.delta; 
-val = parms.v; r =parms.r; mu = parms.mu; sigma = parms.sigma;
-
-% Sample to compute V3:
-y_prime = exp(mu + sigma.*randn(parms.rep,1));
-
-% Function to optimize
-% VV1 = @(p) beta*delta*log(y-p) + ...
-%     mean(V3(y_prime,(1+r).*(m-p),parms));
-%%
-
-if (m <= 0)
-   % Value function
-    V = beta_belief*delta*(log(1+val)+log(y)) + ...
-        beta_belief*delta^2*log(1+val) + ...
-        beta_belief*delta^2*mu;
-    pp = zeros(length(y),1);
-    
-else
-    % Discretize grid for policies
-    mn = min(m,y);
-    mx = max(mn);
-    p = linspace(0,mx,parms.gridsize);
-
-    Omega = (1+val)/val;
-    % Value function
-    VV = beta_belief*delta*log(y-p) + ...
-        beta_belief*delta^2*log(1+val).*(1-logncdf((1+r)*(m-p)*Omega,mu,sigma)) + ...
-        beta_belief*delta^2*mean(log(y_prime-(1+r).*max((m-p),0).*(y_prime >= (1+r)*(m-p)*Omega)));
-
-    V = zeros(length(y),1); ind = zeros(length(y),1);
-    for i=1:length(y)
-        % Optimal int point value
-        [V(i),ind(i)] = max(VV(i,imag(VV(i,:))==0));
-    end
-
-    % Optimal int point policy
-    pp = p(ind)';
-
-    %% 
-
-    % Optimum for paying debt at this time period if possible
-    opt = -Inf*ones(length(y),1);
-    opt(m<=y) = beta_belief*delta.*(log(1+val) + log(y(m<=y)-m)) + ...
-            beta_belief*delta^2*(log(1+val) + mu);
-
-
-    %% Optimum values
-    ind_change = V<opt;
-    V(ind_change) = opt(ind_change); pp(ind_change) = m;
-end
-
-    % Paid loan
-    d = (pp==m);
-end
-

### 2020-06-18 MATLAB/V2_beta.m

@@ -1,58 +1,0 @@
-function [V, pp, d] = V2_beta(y,m,parms)
-% Value function at time period t=2
-beta_belief = parms.beta_belief; delta = parms.delta; 
-val = parms.v; r =parms.r; mu = parms.mu; sigma = parms.sigma;
-
-% Sample to compute V3:
-y_prime = exp(mu + sigma.*randn(parms.rep,1));
-
-% Function to optimize
-% VV1 = @(p) beta*delta*log(y-p) + ...
-%     mean(V3(y_prime,(1+r).*(m-p),parms));
-%%
-
-if (m == 0)
-   % Value function
-    V = beta_belief*delta*(log(1+val)+log(y)) + ...
-        beta_belief*delta^2*log(1+val) + ...
-        beta_belief*delta^2*mu;
-    pp = zeros(length(y),1);
-    
-else
-    % Discretize grid for policies
-    mn = min(m,y);
-    mx = max(mn);
-    p = linspace(0,mx,parms.gridsize);
-
-    Omega = (1+val)/val;
-    % Value function
-    VV = beta_belief*delta*log(y-p) + ...
-        beta_belief*delta^2*log(1+val).*(1-logncdf((1+r)*(m-p)*Omega,mu,sigma)) + ...
-        beta_belief*delta^2*mean(log(y_prime-(1+r).*(m-p).*(y_prime >= (1+r)*(m-p)*Omega)));
-
-    V = zeros(length(y),1); ind = zeros(length(y),1);
-    for i=1:length(y)
-        % Optimal int point value
-        [V(i),ind(i)] = max(VV(i,imag(VV(i,:))==0));
-    end
-
-    % Optimal int point policy
-    pp = p(ind)';
-
-    %% 
-
-    % Optimum for paying debt at this time period if possible
-    opt = -Inf*ones(length(y),1);
-    opt(m<=y) = beta_belief*delta.*(log(1+val) + log(y(m<=y)-m)) + ...
-            beta_belief*delta^2*(log(1+val) + mu);
-
-
-    %% Optimum values
-    ind_change = V<opt;
-    V(ind_change) = opt(ind_change); pp(ind_change) = m;
-end
-
-    % Paid loan
-    d = (pp==m);
-end
-

### 2020-06-18 MATLAB/V3.m

@@ -1,14 +1,0 @@
-function [V, pp, d] = V3(y,m,parms)
-% Value function at time period t=3
-beta_belief = parms.beta_belief; delta = parms.delta; val = parms.v;
-
-
-pp = m.*((y >= m.*(1+val)./val));
-
-V = beta_belief*delta^2*(log(1+val).*(y >= m.*(1+val)./val)+...
-    log(y-pp));
-
-% Paid loan
-d = (pp==m);
-
-end

### 2020-06-18 MATLAB/scatter_hist.m

@@ -1,35 +1,0 @@
-%% Scatter histograms
-
-
-%% Cost - Time
-clear all
-data = csvread('cost_time.csv');
-
-Cost = data(:,1);
-Time = data(:,2);
-
-gcf = scatterhist(Cost,Time,'Kernel','on','Location', 'SouthEast',...
-    'Direction','out','Color','kbr','LineStyle',{'-','-.',':'},...
-    'LineWidth',[2,2,2],'Marker','+od','MarkerSize',[4,5,6]);
-
-%% Financial Cost Survey - Admin
-clear all
-data = csvread('fc.csv');
-
-Admin = data(:,1);
-Subjective = data(:,2);
-
-gcf = scatterhist(Admin,Subjective,'Kernel','on','Location', 'SouthEast',...
-    'Direction','out','Color','kbr','LineStyle',{'-','-.',':'},...
-    'LineWidth',[2,2,2],'Marker','+od','MarkerSize',[4,5,6]);
-
-%% Financial Cost (log) Survey - Admin
-clear all
-data = csvread('logfc.csv');
-
-Admin = data(:,1);
-Subjective = data(:,2);
-
-gcf = scatterhist(Admin,Subjective,'Kernel','on','Location', 'SouthEast',...
-    'Direction','out','Color','kbr','LineStyle',{'-','-.',':'},...
-    'LineWidth',[2,2,2],'Marker','+od','MarkerSize',[4,5,6]);

### 2020-06-18 MATLAB/simul.m

@@ -1,71 +1,0 @@
-%% Parameter structure
-%
-clear all
-clc
-parms.sigma = 0.4;
-parms.delta=0.8;
-parms.mu = 7;
-parms.r = .2;
-parms.beta_belief=0.9;
-parms.beta=0.8;
-parms.rep = 1000;
-parms.gridsize = 1200;
-parms.simul = 500;
-parms.mu_d = 7.1;
-parms.sigma_d = 0.3;
-
-
-
-
-%% Simulation
-beta_belief = parms.beta_belief; delta = parms.delta; 
-r =parms.r; mu = parms.mu; sigma = parms.sigma;
-mu_d = parms.mu_d; sigma_d = parms.sigma_d;
-
-tic
-m = zeros(parms.simul,4);
-p = zeros(parms.simul,3);
-d = zeros(parms.simul,3);
-
-% Path of payments
-for i = 1:parms.simul
-    i
-    
-    % Draw a lognormal sample
-    y = exp(mu + sigma.*randn(1,3)); 
-    y(2) = y(2) - (rand<0.4)*y(2)*(0.5+0.4*rand);
-    y(3) = y(3) - (rand<0.5)*y(3)*(0.5+0.4*rand);
-    % Draw a debt sample
-    m(i,1) = exp(mu_d + sigma_d.*randn(1));
-    parms.v = m(i,1)/(0.7 + .02*randn(1));
-    c = toc;
-    [~,p(i,1),d(i,1)] = V1(y(1),m(i,1),parms); m(i,2) = (1+r)*(m(i,1)-p(i,1));
-    c = toc-c
-    c = toc;
-    [~,p(i,2),d(i,2)] = V2(y(2),m(i,2),parms); m(i,3) = (1+r)*(m(i,2)-p(i,2));
-    c = toc-c
-    [~,p(i,3),d(i,3)] = V3(y(3),m(i,3),parms); m(i,4) = m(i,3)-p(i,3);
-   
-end
-t= toc
-%% Simulation
-
-% beta_belief = parms.beta_belief; delta = parms.delta; 
-% val = parms.v; r =parms.r; mu = parms.mu; sigma = parms.sigma;
-% mu_d = parms.mu_d; sigma_d = parms.sigma_d;
-% 
-% m = zeros(2,4);
-% p = zeros(2,3);
-% d = zeros(2,3);
-% 
[…]

### 2020-06-18 RScripts/fc_te_grf.R

@@ -1,86 +1,0 @@
-library(tidyverse)
-library(grf)
-library(ggplot2)
-
-# SET WORKING DIRECTORY
-setwd('C:/Users/xps-seira/Dropbox/Apps/ShareLaTeX/Donde2019')
-#setwd("C:\\Users\\Ricardo\\Documents\\SEIRA\\donde2019")
-set.seed(5289374)
-
-
-
-  data_in <- read_csv('./_aux/fc_te_heterogeneity.csv')
-  
-  
-  require("dplyr")
-  
-  data_train <- data_in %>% 
-    filter(insample == 1) 
-  data_train_fee <- subset(data_train, data_train$fee_arms == 1)
-  data_train_nofee <- subset(data_train, data_train$fee_arms == 0)
-  
-  
-  data_test <- data_in %>% 
-    select(-c(fc_admin_disc, fee_arms, prenda, insample))
-  data_test_tau <- data_in %>% 
-    select(-c(fc_admin_disc, prenda, insample))
-  
-  ###################################################################  
-  ###################################################################  
-  
-  
-  # PREPARE VARIABLES
-  X <- select(data_train,-c(fc_admin_disc, fee_arms, prenda, insample))
-  Y <- select(data_train,fc_admin_disc)
-  W <- as.numeric(data_train$fee_arms == 1)
-  
-  X_full <- select(data_in,-c(fc_admin_disc, fee_arms, prenda, insample))
-  Y_full <- select(data_in,fc_admin_disc)
-  W_full <- as.numeric(data_in$fee_arms == 1)
-  
-  X_fee <- select(data_train_fee,-c(fc_admin_disc, fee_arms, prenda, insample))
-  Y_fee <- as.numeric(data_train_fee$fc_admin_disc)
-  X_nofee <- select(data_train_nofee,-c(fc_admin_disc, fee_arms, prenda, insample))
-  Y_nofee <- as.numeric(data_train_nofee$fc_admin_disc)
-  
-  ###################################################################  
-  ###################################################################  
-  
-
-  # ESTIMATE MODEL
-
-  # Causal Forest
-  tau.forest = causal_forest(
-    X = model.matrix(~., data = X), 
-    Y = data.matrix(Y), 
-    W = W,
-    honesty = TRUE)
-  
-  tau.forest.full = causal_forest(
-    X = model.matrix(~., data = X_full), 
-    Y = data.matrix(Y_full), 
-    W = W_full,
[…]

### 2020-06-18 RScripts/grf.R

@@ -1,185 +1,0 @@
-library(tidyverse)
-library(grf)
-library(ggplot2)
-library(DiagrammeR)
-library(DiagrammeRsvg)
-library(gdata)
-
-# SET WORKING DIRECTORY
-setwd('C:/Users/xps-seira/Dropbox/Apps/ShareLaTeX/Donde2019')
-set.seed(5289374)
-
-source("./RScripts/best_tree.R")
-
-heterogeneity_effect <- function(data_in,treatment_var,outcome_var,writedata) {
-  
-require("dplyr")
-data_frame <- data_in %>%
-  filter(data_in[,treatment_var] == 1 | data_in[,treatment_var] == 0) %>%
-  select(-c( pro_2, pro_3, pro_4, pro_5, pro_6, pro_7, pro_8, pro_9, fee, fecha_inicial,
-             def_c, fc_admin_disc, fc_survey_disc, fc_admin, fc_survey, dias_primer_pago), 
-         treatment_var, outcome_var ) %>%
-  drop_na()  
-
-
-# PREPARE VARIABLES
-X <- select(data_frame,-c(outcome_var, treatment_var,NombrePignorante, prenda))
-Y <- select(data_frame,outcome_var)
-W <- as.numeric(data_frame[,treatment_var] == 1)
-
-# ESTIMATE MODEL
-tau.forest = causal_forest(
-  X = model.matrix(~., data = X), 
-  Y = data.matrix(Y), 
-  W = W,
-  honesty = TRUE)
-
-if (writedata == 0) {
-  # BEST TREE
-  best_tree_info <- find_best_tree(tau.forest, "causal")
-}
-
-# OVERLAP ASSUMPTION
-propensity.forest = regression_forest(X, W)
-propensity_score = predict(propensity.forest)$predictions
-hist(propensity_score, xlab = "propensity score")
-
-# Estimate treatment effects for the training data using out-of-bag prediction.
-tau_hat_oob = predict(tau.forest, estimate.variance = TRUE)
-hist(tau_hat_oob$predictions)
-
-# Estimate the conditional average treatment effect on the full sample (CATE).
-print(average_treatment_effect(tau.forest, target.sample = "all"))
-
-# Estimate the conditional average treatment effect on the treated sample (CATT).
-# Here, we don't expect much difference between the CATE and the CATT, since
[…]

### 2020-06-18 RScripts/pfv_pred_hte.R

@@ -1,53 +1,0 @@
-library(tidyverse)
-library(grf)
-library(ggplot2)
-
-# SET WORKING DIRECTORY
-setwd('C:/Users/xps-seira/Dropbox/Apps/ShareLaTeX/Donde2019')
-set.seed(5289374)
-options(digits=18)
-
-rf_predict <- function(data_in,take.up,nme) {
-  
-  require("dplyr")
-  data_train <- data_in %>% 
-    filter(insample == 1) 
-
-  data_test <- data_in %>% 
-    select(-c(take.up, nombrepignorante, prenda, insample, tau_hat_oobpredictions))
-###################################################################  
-###################################################################  
-
-    
-  # PREPARE VARIABLES
-  X <- select(data_train,-c(take.up, nombrepignorante, prenda, insample, tau_hat_oobpredictions))
-  W <- as.numeric(data_train[,take.up] == 1)
-
-###################################################################  
-###################################################################  
-  
-  
-  # ESTIMATE MODEL
-  pred.forest = regression_forest(X, W)
-  rf_pred = predict(pred.forest,data_test)$predictions
-  hist(rf_pred, xlab = "predictions")
-  
-  data.out <- add_column(data_in, rf_pred)
-  filename <- paste("_aux/pred_",nme,".csv", sep="") 
-  write_csv(data.out,filename)
-}
-
-#####################################################
-
-#RF Predictions of no-choice arm
-for (arm in c("pro_2")) {
-  for (pred in c("pago_frec_vol_fee")) {
-    for (effect in c("def_c", "fc_admin_disc")) {
-      filename <- paste("_aux/",arm,"_",pred,"_",effect,".csv", sep="")
-      data <- read_csv(filename)
-      outname <- paste(arm,"_",pred,"_",effect,sep="")
-      rf_predict(data,pred,outname) 
-    }
-  }
-}
-

### 2020-06-18 Tables/baseline_survey2.tex
preparation for first draft

% Table generated by Excel2LaTeX from sheet 'baseline_survey'
\begin{tabular}{lrrrr}
\toprule
      &       &       &       &  \\
¿Que tan seguido se siente usted estresado por la situacion economica de su hogar?  & \multicolumn{1}{l}{Siempre} & 0.1   & \multicolumn{1}{l}{-} & 7363 \\
      & \multicolumn{1}{l}{Muy seguido} & 0.16  & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} \\
      & \multicolumn{1}{l}{A veces} & 0.65  & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} \\
      & \multicolumn{1}{l}{Nunca} & 0.08  & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} \\
\midrule
      &       &       &       &  \\
La razon principal por la que usted quiere empeñar una prenda & \multicolumn{1}{l}{Necesito el dinero porque alguien en mi familia perdio su empleo } & 0.05  & \multicolumn{1}{l}{-} & 5307 \\
      & \multicolumn{1}{l}{Necesito el dinero para atender una enfermedad mia o de un familiar } & 0.11  & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} \\
      & \multicolumn{1}{l}{Necesito el dinero para un gasto urgente} & 0.71  & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} \\
      & \multicolumn{1}{l}{Necesito el dinero para un gasto que no es urgente} & 0.13  & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} \\
\midrule
      &       &       &       &  \\
¿Quu tan estresado se siente usted por la situacion que lo hace requerir este prestamo? & \multicolumn{1}{l}{Muy estresado} & 0.23  & \multicolumn{1}{l}{-} & 5189 \\
      & \multicolumn{1}{l}{Algo estresado} & 0.44  & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} \\
      & \multicolumn{1}{l}{Poco estresado} & 0.19  & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} \\
      & \multicolumn{1}{l}{Nada estresado} & 0.14  & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} \\
\midrule
      &       &       &       &  \\
En 3 meses, usted espera tener una situacion economica: & \multicolumn{1}{l}{Mejor} & 0.89  & \multicolumn{1}{l}{-} & 5214 \\
      & \multicolumn{1}{l}{La misma} & 0.11  & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} \\
      & \multicolumn{1}{l}{Peor} & 0.01  & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} \\
\midrule
      &       &       &       &  \\
¿Ha empeniado antes? &       & 0.9   & 0.3   & 7189 \\
\midrule
      &       &       &       &  \\
Si usted esta guardando dinero, y un familiar lo quiere usar para algo diferente: & \multicolumn{1}{l}{Siempre} & 0.37  & \multicolumn{1}{l}{-} & 3462 \\
      & \multicolumn{1}{l}{A veces} & 0.12  & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} \\
      & \multicolumn{1}{l}{Dificilmente} & 0.05  & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} \\
      & \multicolumn{1}{l}{Nunca} & 0.02  & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} \\
      & \multicolumn{1}{l}{Ningun familiar pediria usar su dinero} & 0.44  & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} \\
\midrule
      &       &       &       &  \\
¿Usted hace un presupuesto de sus gastos del mes?   & \multicolumn{1}{l}{No} & 0.19  & \multicolumn{1}{l}{-} & 7129 \\
      & \multicolumn{1}{l}{Casi siempre} & 0.17  & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} \\
      & \multicolumn{1}{l}{Si} & 0.64  & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} \\
\midrule
      &       &       &       &  \\
¿Usted tiene otras prendas que podría empeñar? &       & 0.68  & 0.47  & 5191 \\
\midrule
      &       &       &       &  \\
¿Usted tiene ahorros?  &       & 0.37  & 0.48  & 5200 \\
\midrule
      &       &       &       &  \\
¿Usted participa en una tanda o en una caja de ahorro?  &       & 0.39  & 0.49  & 5204 \\
\midrule
      &       &       &       &  \\
¿Es común que sus familiares o amigos le pidan dinero? &       & 0.31  & 0.46  & 5188 \\
\midrule
      &       &       &       &  \\
Para llegar a esta sucursal, ¿Cuanto gasto?   &       & 10.58 & 27.53 & 6913 \\
\bottomrule
\end{tabular}%

### 2020-06-18 Tables/transcribed.tex
preparation for first draft

% Table generated by Excel2LaTeX from sheet 'transcribed'
\begin{tabular}{cl}
\toprule
      & \textbf{Baseline Survey} \\
\midrule
\midrule
1     & \textbf{Your pawn was:} \\
      & (a) Inherite, (b) a gift, (c) bought by me, (d) lend to me, (e) other \_\_\_\_\_\_\_\_\_\_\_\_ \\
2     & \textbf{Mark with an "X" in the line below how likely is that you recover your pawn. } \\
      & \textbf{Where 0 is impossible and 100 is completely certain} \\
      &  \\
      &  \\
3     & \textbf{How much would you sell the item you want to pawn for?       \_\_\_\_\_\_\_\_\_\_\_\_\_\_ pesos} \\
4     & \textbf{Gender      } \\
5     & \textbf{Age} \\
6     & \textbf{Civil Status } \\
      & (a) married, (b) single, (c) divorced, (d) widowed \\
7     & \textbf{Work status} \\
      & (a) employed, (b) own business, (c) houseshores, (d) don't work, (e) retired, (f) study \\
8     & \textbf{Education} \\
      & (a) no formal education, (b) primary, (c) middle school, (d) highschool, (e) more than highschool \\
9     & \textbf{In the last month, did a friend or family member asked you for money?} \\
      & (a) yes  (b) no \\
10    & \textbf{What would you like to have: 100 pesos tomorrow or 150 pesos in one month?} \\
11    & \textbf{How often do you feel stressed by your economic situation?} \\
      & (a) always, (b) very often, (c) sometimes, (d) never \\
12    & \textbf{What is the main reason you want to pawn?} \\
      & (a) Need the money because somebody in my family lost his/her job \\
      & (b) Need the money to pay for a sickness in the family \\
      & (c) Need the money for an urgent expense \\
      & (d) Need the money for some non urgent expense. \\
13    & \textbf{How stressed do you feel from the situation that led to to pawn?} \\
      & (a) very stressed, (b) somwhat stressed, (c) a little stressed, (d) not stressed  \\
14    & \textbf{In 3 months, I expect to have a  \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ situation} \\
      & (a) better, (b) similar,  (c) worse \\
15    & \textbf{Have you panwned before?} \\
      & (a) yes  (b) no \\
16    & \textbf{How many times have you pawned on a Lender P branch?} \\
      & (a) NO\_\_\_    (b)  1-2 times \_\_\_    (c) 3-5 times\_\_\_\_   (d) More than 5\_\_\_\_ \\
17    & \textbf{If you are saving money and a family member wants to use it for something } \\
      & (a) I would only give him the money for an urgent expenze \\
      & (b) I would give him the money even if it was not an urgent expense \\
      & (c) I would not give him/her the money regardless \\
      & (d) No one would ask me for my money \\
18    & \textbf{Do you make an expenses budget for the month ahead of time?} \\
      & (a) always, (b) very often, (c) sometimes, (d) never \\
19    & \textbf{Do you have other items you could pawn?} \\
      & (a) yes  (b) no \\
20    & \textbf{Do you have savings?} \\
      & (a) yes  (b) no \\
21    & \textbf{Do you participate in a ROSCA?} \\
      & (a) yes  (b) no \\
22    & \textbf{Is it common that family or friends ask for money?} \\
      & (a) yes  (b) no \\
23    & \textbf{How much did you spend to come to the branch today?    \$\_\_\_\_\_\_\_\_\_\_\_\_\_\_ pesos} \\
24    & \textbf{How much time does it usually take to come to this branch?    \_\_\_\_\_\_\_\_\_\_\_} \\
25    & \textbf{How much does your family spend in a normal week?   \$\_\_\_\_\_\_\_\_\_\_\_\_\_\_ pesos} \\
26    & \textbf{How much do you manage to save in a normal week?   \$\_\_\_\_\_\_\_\_\_\_\_\_\_\_ pesos} \\
27    & \textbf{Does it happen to you that you spend more than you wanted because you fall into temptation?} \\
      & (a) never, (b) almost never, (c) sometimes, (d) very often \\
28    & \textbf{In the last 6 months, has it happened that at some point you lacked money to pay} \\
      & (a) rent?    (b) food    (c)food   (d) medicine  (e) electricity   (f) heating   (g) telephone    (i) water \\
29    & \textbf{What would you like to have: 100 pesos in 3 months or 150 pesos in four months?} \\
30    & \textbf{Would you like to receive (free) reminders for upcomming payments?} \\
      & (a) yes  (b) no \\
\bottomrule
\end{tabular}%

### 2020-06-18 main.tex
preparation for first draft

@@
 \title{Private paternalism and the limits of self commitment  \thanks{We want to thank Craig McIntosh and Mauricio Romero for advice and encouragement.
-We want to thank also Ricardo Olivares for excellent research assistance and Erik Molina help with formatting.
-Jose Maria Barrero, Emilio Gutierrez, Aprajit Mahajan, Matt Rabin and seminar participants at ITAM provided very valuable feedback.}}
+We want to thank also Ricardo Olivares for excellent research assistance and Erick Molina help with formatting.
+Jose Maria Barrero, Emilio Gutierrez, Aprajit Mahajan, Matt Rabin, and seminar participants at ITAM provided very valuable feedback.}}
 \author{Isaac Meza \and Joyce Sadka \and Enrique Seira   \thanks{Meza: University of California at Berkeley, isaac.meza@berkeley.edu; Sadka: ITAM, jsadka@itam.mx;  
@@
 
-Indeed, using a survey conducted by us in branches of Lender $P$, we document some evidence consistent with regulators' concerns: while pawnshop clients predict they will recover their pawn with 93\% probability on average, in reality only 44\% of them do, suggesting naivete.
-Even conditional on paying a positive amount towards pawn recovery, 47\% lose their pawn and their payment.
+Indeed, using a survey conducted by us in branches of Lender $P$, we document some evidence consistent with regulators' concerns: while pawnshop clients predict they will recover their pawn with 93\% probability on average, in reality only 40\% of them do, suggesting naivete.
+Even conditional on paying a positive amount towards pawn recovery, 53\% lose their pawn and their payment.
 In our survey 69\% report self-control problems saying they often fall into temptation spending.
@@
 We find that forcing clients into frequent payment commitment contracts causes them on average to save on financing cost and to recover their pawn more.
-The effects are large: financing cost decreases by 9.5\% on average, while the likelihood of recovering their pawn increases by 25.8\%.
+The effects are large: financing cost decreases by 9.5\% on average, while the likelihood of recovering their pawn increases by 25\%.
 Results are robust to including in the cost definition transport costs of going to the branch plus losing a day's wage for each visit.
@@
 We calculate that about 80\% of clients in the fee-choice group chose contracts that induced \textit{higher} financial cost.
-On average they spend an extra \$238 pesos, close to 12\% of the average loan value.
+On average they spend an extra \$238 pesos, close to 11\% of the average loan value.
 In particular 92\% of those that chose the status-quo contract would have been better in the fee-commitment contract, while only 8\% of those who chose the fee-commitment contract would have been better in the status-quo one.
@@
 One potential explanation for high default is that clients are really just selling their gold piece.
-This is unlikely for severalreasons: (a)  the reported subjective value of the pawn is larger than the loan size for \hl{86\%} of them, (b) among those that lose their pawn 74\% paid a positive amount towards its recovery --- this can only be rationalized if they expected to recover their pawn, (c) it is typical to find gold purchasing stores close to where the pawnshops are located (see Figure \ref{GoldBuyers}) and they give more than what Lender P gives for the pawn, (d) there is a lot of engagement with the lender after pawning even for those who lost their pawn.
-On average clients that lost their pawn paid 34\% of the value of their loan, and close to 55\% of clients extended the loan for another cycle and made payments in the second cycle (see Figure \ref{proxy_naive} in Appendix).
+This is unlikely for several reasons: (a)  the reported subjective value of the pawn is larger than the loan size for \hl{86\%} of them, (b) among those that lose their pawn 58\% paid a positive amount towards its recovery --- this can only be rationalized if they expected to recover their pawn, (c) it is typical to find gold purchasing stores close to where the pawnshops are located (see Figure \ref{GoldBuyers}) and they give more than what Lender P gives for the pawn, (d) there is a lot of engagement with the lender after pawning even for those who lost their pawn.
+On average clients that lost their pawn paid 34\% of the value of their loan, and close to 42\% of clients extended the loan for another cycle and made payments in the second cycle (see Figure \ref{proxy_naive} in Appendix).
 
@@
 %\footnote{We also surveyed clients before and after the experiment, so our survey covers a larger sample that we are not using in this paper.}.
-The appendix \ref{baseline_survey} transcribes the questionnaire in English and presents summary stats.
+The appendix \ref{baseline_survey} transcribes the questionnaire in English \hl{and presents summary stats}.
 Survey response rate is 57\%, the Appendix Table \ref{balance_response} shows that response is not related to admin data observables.
@@
 Panel A describes variables from the administrative data.
-It shows that the average loan size is \$1945 pesos (\$105 usd).
+It shows that the average loan size is \$2171 pesos (\$105 usd).
 The average number of pawns per day per branch is 33.
@@
 The average time they take to come to the branch is 22 minutes, and the amount of money they spend in transport to do that is 11 pesos (\$0.60 usd).
-The population we are working with is economically vulnerable in the sense that 31\% of them could not pay either water, electricity \& gas or rent in the past 6 months.
+The population we are working with is economically vulnerable in the sense that 30\% of them could not pay either water, electricity \& gas or rent in the past 6 months.
 They often receive negative income shocks: 87\% said they are pawning because of an emergency, and only 13\% stated it was to use in a `non-urgent expense'.
@@
 See section \ref{neoclasical}.} Figure \ref{fc_hist}(a) plots a histogram of this cost in pesos for loans where the pawn was recovered or lost.
-This cost is calculated for a time period of 230 days after loan origination, as 50\% of clients actually renew the loan one time.
-Of those who renew 34\% lose the pawn.
+This cost is calculated for a time period of 230 days after loan origination, as 60\% of clients actually renew the loan one time.
+Of those who renew 83\% lose the pawn.
 Figure \ref{fc_hist}(a) suggest that financial cost is significant, even for those that do recover their pawn.
@@
 
-\noindent \textbd{Selection of branches.} Starting September 6th 2012, we implemented our experiment in 6 branches of Lender $P$.
+\noindent \textbf{Selection of branches.} Starting September 6th 2012, we implemented our experiment in 6 branches of Lender $P$.
 The branches were selected by Lender $P$ to be dispersed across Mexico city and have varying sizes.
@@
 As that paper shows doing this results in wrong choices by naive present biased consumers.
-Our fee is much smaller than the median in her experiment as explained above.
+\hl{Our fee is much smaller than the median in her} experiment as explained above.
 We also experimented with a contract where there was no pecuniary fee for paying late but where we clients made a personal promise to pay monthly.}
@@
 Results are robust to excluding them.
-In the regressions we include them and add a dummy indicating who are these clients.} %\footnote{There If we restrict ourselves to pieces that fall in a single-arm (64\%), then treatment reduces the financial cost by 5.7\%, increases the likelihood of recovering their pawn by 35\%, and increases the likelihood of repeat business by 66\%.}.
+In the regressions we include them and add a dummy indicating who are these clients.} %\footnote{If we restrict ourselves to pieces that fall in a single-arm (64\%), then treatment reduces the financial cost by 5.7\%, increases the likelihood of recovering their pawn by 35\%, and increases the likelihood of repeat business by 66\%.}.
 Our main outcome variables $y_{ij}$ are measures of financial cost in pesos as defined in Section \ref{FC_def}, as well as an indicator variable for client $i$ losing her pawn.
@@
 The second coefficient uses the subjective value of the pawn instead.
-In both cases we find that being assigned to the fee-forcing commitment contract causes a large reduction in the financing cost the client incurred, of 9.5\% (\hl{\$XXX}) in the fist definition and 13.3\% (\hl{\$XXX}) in the second one.
+In both cases we find that being assigned to the fee-forcing commitment contract causes a large reduction in the financing cost the client incurred, of 9.5\% (\hl{\$304}) in the fist definition and 13.3\% (\hl{\$478}) in the second one.
 That is, we find that \textit{charging} clients a late payment fee  actually decreases total \textit{fee-inclusive} financing cost.
@@
 \noindent \textbf{Pawn Recovery.} Figure \ref{fc_pro2}(d) plots estimated treatment effects of the fee-forcing commitment contract with the dependent variable being an indicator of losing the pawn in less than 230 days.
-The leftmost coefficient shows that the fee-forcing commitment contract increases the likelihood of recovering the pawn by 11pp (25.8\% of mean recovery).
+The leftmost coefficient shows that the fee-forcing commitment contract increases the likelihood of recovering the pawn by 11pp (25\% of mean recovery).
 This is a large effect.
@@
 Table \ref{mechanisms} shows that the first payment happens 8 days earlier (column 1) in the fee-forcing arm than in the status quo one, and that the number of payments increases by 0.19 (column 2).
-Figure \ref{induced_to_pay_early} in the Appendix correlates heterogeneous treatment effects on financing cost and time of first payment and shows that those induced to pay earlier are also those that have larger induced savings in financial cost.
+Figure \ref{induced_to_pay_early} in the Appendix correlates heterogeneous treatment effects on financing cost and time of first payment and shows that those induced to pay earlier are also those that have larger induced reduction in financial cost.
 A second finding is that treatment effects are concentrated on the intensive margin, as treatment does \textit{not} affect the fraction of clients who pay a positive amount (column 6).
@@
 The 4th coefficient from left to right conditions on those who paid a positive amount (in treatment and control).
-Although this is potentially an endogenous population, Table \ref{mechanisms} showed that there is no treatment effect on Pay$>0$.
+Although this is potentially an a selected subsample, Table \ref{mechanisms} showed that there is no treatment effect on pay$>0$.
 We were interested in this population to show that the effect is there for those who are serious about recovering their pawn.
-The fifth coefficient conditions on those that paid a fee in the fee-forcing group.
-In effect comparing this subset in treatment vs all of the control group\footnote{Results are similar if we condition in the control group on those who would have paid a fee given current behavior.
-Again we acknowledge these is an endogenous control and that the estimate is not a causal effect.}.
-We find even those that paid a fee in the fee-forcing contract end up paying a smaller financial cost that those in the status-quo contract.\footnote{This is not an experimental comparison as who pays a fee in the treatment group is a selected sample, but we found this relationship interesting nonetheless.} Figure \ref{fc_pro2}(c) shows that the increase in pawn recovery is robust to defining recovery using the first 120 days of the contract, or restricting to those paying a positive amount towards pawn recovery.
+The fifth coefficient conditions on those that paid a fee in the fee-forcing group, comparing this subset in treatment vs all of the control group.\footnote{Results are similar if we condition in the control group on those who would have paid a fee given current behavior.
+Again we acknowledge these is an endogenous sample and that the estimate may not be a causal effect.} We find that even those that paid a fee in the fee-forcing contract end up paying a smaller financial cost that those in the status-quo contract.
+Figure \ref{fc_pro2}(c) shows that the increase in pawn recovery is robust to defining recovery using the first 120 days of the contract, or restricting to those paying a positive amount towards pawn recovery.
 
@@
 
-We have shown that clients are more likely to recover their pawn that virtually all of them incur in a lower financial cost  when assigned a monthly payment commitment contract with fees.
+We have shown that all clients are more likely to recover their pawn and almost all of them incur in a lower financial cost  when assigned to a monthly payment commitment contract.
 This however does not necessarily show that they benefited in utility terms, and this is hard to show directly.
@@
 
-Figure \ref{reincidence} presents results of equation (\ref{basic_reg}) where the dependent variable is a dummy for the client to be a repeat costumer.
-We define a client in our experiment as a repeat costumer if, after experiencing at least 75 days of the respective treatment arm, she came back and pawned a different piece.\footnote{Results are robust to using other number of days besides 75.}  The left most coefficient shows that the causal effect of the fee-forcing contract on repeat pawning is an increase of 5pp in the probability of being a repeat costumer, this is 55\% on a mean re-incidence in the control group, with respect to those that got the status-quo contract.
-This is not explained by clients recovering their first pawn with higher probability in the fee-forcing contract and re-pawning this same one since we make sure it is another piece (besides only 37\% recover their piece in the fist 75 days in the fee forcing contract).
-The second coefficient restricts to the population who had larger (treatment effect) financial cost savings in their first pawn, and shows that the effect is twice as large for them.
-That is, those that benefit more from the fee-forcing contract are much more likely to repeat.
-%The coefficient on repeat pawning is just as big when we focus only 2nd pawns happening after the first was recovered (third coefficient ``fnr'').
+Figure \ref{reincidence} presents results of equation (\ref{basic_reg}) where the dependent variable is a dummy for the client being a repeat costumer.
+We define a client as a repeat costumer if, after experiencing at least 75 days of the respective treatment arm, she came back and pawned a \textit{different} piece.\footnote{Results are robust to using other number of days besides 75.
+We know its a different piece from them having a different weight.}  The left most coefficient shows that the causal effect of the fee-forcing contract on repeat pawning is an increase of 5pp in the probability of being a repeat costumer, this is 55\% increase on a mean re-incidence with respect to those that got the status-quo contract.
+This effect is not explained by clients recovering their first pawn with higher probability in the fee-forcing contract and re-pawning this same one since we make sure it is another piece (only \hl{16\%} recover their piece in the fist 75 days in the fee forcing contract).
+The second coefficient restricts the sample in the regression to those that had not recovered their pawn in the first 75 days and finds similar result.
+Finally, the third coefficient focuses on the subsample who experienced a financial cost savings treatment effect above the median treatment effect in their first pawn.
+It shows that for these clients the likelihood of coming back is twice as large (although imprecise).
+That is, those that benefit more from the fee-forcing contract are more likely to repeat.\footnote{We also implemented an exit survey which clients filled when recovering their piece.
+Unfortunately it had low response rates (7\%), and we take its results with a grain of salt.
+In this survey 63\% said they liked the frequent payment contract more than the status-quo one, and that is allow them avoid unnecessary expenses.} %The coefficient on repeat pawning is just as big when we focus only 2nd pawns happening after the first was recovered (third coefficient ``fnr'').
 This is consistent with \cite{Laibson2018}'s conjecture that clients could be making decisions based on experienced utility.\footnote{The third coefficient conditions on the subsample that did recover their first pawn in both arms and finds a coefficient of 4pp.
@@
 
-We also implemented an exit survey which clients filled when recovering their piece.
-Unfortunately it had low response rates (7\%), and we take its results with a grain of salt.
-In this survey 63\% said they liked the frequent payment contract more than the status-quo one, and that is allow them avoid unnecessary expenses.
-
 \section{The effect of giving choice} \label{fee-choice}
@@
 Section \ref{fee-commitment} showed that the fee-forcing commitment contract reduced financing cost across the board, and that consumers themselves seemed to like it once they tried it.
-In such a case, one would expect a strong demand for it, unless consumers underestimated these benefits.
+In such a case, one would expect a strong demand for it.
 
@@
 To study demand for commitment, in one experimental arm, we let clients freely choose between the two types of contract: the fee-forcing commitment contract or the status-quo contract.
-The first result here is that in spite of broadly distributed benefits of the fee-forcing commitment contract we documented above, 90\% of clients chose \textit{not} to have it, they instead preferred the status-quo one.
+In spite of broadly distributed benefits of the fee-forcing commitment contract we documented above, 90\% of clients chose \textit{not} to have it, they instead preferred the status-quo one.
 As explained above we are fairly confident this was not because a lack of understanding of the contracts.
@@
 What can explain this low demand?
-This section discusses some hypothesis but lack of data limits what can be tested.
+This section discusses some hypothesis but data limits what can be tested.
 One neoclassical explanation could be risk.
-Even if the fee forcing contract generates cost savings on average, clients with risk averse preferences may not demand it if they perceive higher risk from it.\footnote{Because they have not experienced the fee-forcing contract before, ambiguity aversion may play a role here too.} Alternatively, even risk-neutral agents may not demand it if the cost of lost flexibility is high.
-If they for example face large and frequent income shocks which make it hard to repay monthly.\footnote{We don't observe income shocks in our data, making is hard to quantify how important they are.
-90\% of those in the fee-forcing arm incurred a fee, which suggests that shocks are not uncommon (or clients inattentive).} Below we focus on some explanations of low demand, while Section \ref{model} seeks for theories that can explain all the findings, and reaches the conclusion that the present bias with naivete parsimoniously explains more results.
-
-\subsubsection{Behavioral economics explanations} \label{behavioral}
+Even if the fee forcing contract generates cost savings on average, clients with risk averse preferences may not demand it if they perceive higher risk from it.
+Alternatively, even risk-neutral agents may not demand it if the cost of lost flexibility is high.
+If clients, for instance, face large and frequent income shocks which make it hard to repay monthly.\footnote{We don't observe income shocks in our data, making is hard to quantify how important they are.
+91\% of those in the fee-forcing arm incurred a fee, which suggests that shocks are not uncommon.} Below we focus on some explanations of low demand, while Section \ref{model} seeks theories that can explain all the findings at the same time.
+
+\subsubsection{Behavioral explanations} \label{behavioral}
 
@@
 In our context if consumers are naive about their present bias, they would plan to save more (or spend less) than what they actually end up saving, thus making it be harder to recover their pawn.
-This under-saving will be mitigated in the fee forcing contract since the fee makes them save money and pay part of the loan periodically.
+This under-saving will be mitigated in the fee forcing contract since the fee makes them save money to pay part of the loan periodically.
+Section \ref{model} formalizes this in a model.
 Another behavioral explanation is that clients may underestimate the likelihood and severity of negative income shocks.
-Both of this explanations predict that clients will be overconfident about their likelihood of pawn recovery.
+Both of these explanations predict that clients will be overconfident about their likelihood of pawn recovery.
 Recall that in the control group the client's subjective probability of recovery is on average 93\%, while actual recovery is just 44\%.
@@
 We define as overconfidence as the reported subjective probability of recovery minus the predicted probability based on the client's characteristics, $P^s_i-\widehat{P_i(X_i)}$.\footnote{We predict $\widehat{P_i(X_i)}$ in two steps.
-In step one we use LASSO with with cross validation to tune the regularization parameter to select the most predictive variables.
+In step one we use Lasso with with cross validation to tune the regularization parameter to select the most predictive variables $X$.
+The typical present bias question as in \cite{Ashraf} was eliminated in this step.
 In the second step we estimate $\widehat{P_i(X_i)}$ using those variables in a logit model.
-The LASSO selected variables were type of pawn, female, age, has pawned before, has savings, participates in rotating savings, often feels tempted to change plans, would like to have a reminder to pay, and an economic vulnerability index.}  Table \ref{oc_reg} regresses a take-up dummy against an indicator $OC_i:=\mathbbm{1}(P^s_i-\widehat{P_i(X_i)}>0)$ for overconfidence and controls.
-Controls include branch and day of the week dummies, and additionally schooling, whether the client does a monthly budget plan, and a measure of intertemporal preference reversal analogous to that of \cite{Ashraf} as controls.\footnote{We find that 15\% of clients are classified as present biased using this measure of preference reversal.
-This level is similar to the number \cite{Ashraf} find.} Column 2 shows that in the choice-fee arm, being overconfident decreases the likelihood of demanding commitment by 16 percentage points, and column 4 shows that this is robust to including other controls.
-One interpretation of this result is that the overconfident think they do not need commitment, especially if that commitment may have the cost of fees.
-Columns 1 and 3 will be explained in Section \ref{promises}.
+The Lasso selected variables were type of pawn, female, age, has pawned before, has savings, participates in rotating savings, often feels tempted to change plans, would like to have a reminder to pay, and an economic vulnerability index.
+We are careful not to include these variables as controls in Table  \ref{oc_reg}.} There is an impressive amount of overconfidence in our context.
+Figure \ref{oc_hist} plots a histogram of $OC_i$ and shows that the overwhelming majority display overconfidence, and a large fraction overestimate recovery by more than 50 percentage points.
+
+Table \ref{oc_reg} regresses an indicator of take up of the monthly payment contract against an indicator for overconfidence $OC_i:=\mathbbm{1}(P^s_i-\widehat{P_i(X_i)}>0)$ and controls.
+Controls $Z$ include branch and day of the week dummies, schooling, whether the client does a monthly budget plan, among others.
+We are careful not to include controls that were in $X$.
+% and a measure of intertemporal preference reversal analogous to that of \cite{Ashraf} as controls.\
+Column \hl{1} shows that in the choice-fee arm, being overconfident decreases the likelihood of demanding commitment by 16 percentage points, and column \hl{2} shows that this is robust to including controls.
+Columns \hl{3} and \hl{4} which use the promise-choice arm are intended as a placebo comparison.
+Overconfidence it not predictive of take up of the promise-commitment contract.
+One interpretation of the results is that the overconfident think they do not need commitment, and its demand decreases as soon as there is even a small fee but not when the contract involves a free commitment, as if the promise for them was cheap.
 Column 5 and 6 use as a dependent variable the estimated heterogeneous treatment effects of the fee-forcing contract vs the status quo one.
 They show that the overconfident benefit \textit{more} from the commitment contract, with 20\% (=\$24/\$121) more savings.
+Thus while we predict the overconfident benefit more from commitment, they demand less.
+
+We think our measure of overconfidence is useful especially when there is limited time for a detailed survey.\footnote{It may be more useful than a simple elicitation of present bias as in \cite{Ashraf}.
+We find that 15\% of clients are classified as present biased using this measure of preference reversal.
+This level is similar to the number \cite{Ashraf} find but small to explain no take-up of commitment for 90\% of clients.
+This measure was not correlated with take up of commitment in our sample.} First it is very prevalent, which makes it promising to explain the overwhelming prevalence of low take up.
+Second, it is easy to measure and showed predictive value for take-up.
+It is also implied by present bias with naivete but also by biased expectations of negative income shocks, thus capturing both kinds of bias.
 
@@
 \vspace{.1in}
-\noindent \textbf{Risk aversion.} We do not have measures of risk aversion in our necessarily short survey, which makes it hard to assess the hypothesis that risk aversion limits take-up of the fee-forcing contract.
+\noindent \textbf{Risk aversion.} We do not have measures of risk aversion in our necessarily short survey, which makes it hard to assess the hypothesis that risk aversion limits take-up of the fee frequent payment contract.
 One way to proceed is to take the empirical distribution of financing cost ---$F_{fee}(FC)$--- as one the client would have faced had she chosen the the fee-commitment contract.
 We could then ask what would risk aversion have to be in order to justify the client choosing the fee-commitment contract distribution of costs over the distribution associated with the status quo contract, $F_{sq}(FC)$.
-We can then assess if the risk aversion needed would be reasonable or too high.
+Framed as a choice among cost distributions, we can calculate what risk aversion is needed to rationalize the choice of the status quo contract.
 This exercise of course assumes --as it is common in economics-- that clients know the distribution of financial cost, that it is common across consumers (although this can be relaxed), and that this cost distribution is the only difference among contracts.
-Fortunately for us, since one distribution first-order-stochastically dominates the other we do not need to calibrate a specific utility function or use a parametric distribution function in order to rank them in terms of expected utility.
-We use the fact that if $u(FC)$ is decreasing in $FC$ and $F_{fee}(FC) \geq F_{sq}(FC)$ for all $FC$, then $E_{fee}[u(FC)] \geq E_{sq}[u(FC)]$.
-That is any expected utility maximizer who dislikes paying higher financing cost, regardless of the concavity of his utility function, will prefer the fee-commitment distribution of financial cost.
+Fortunately for us it turns out that one distribution first-order-stochastically dominates the other, we do not need to calibrate a specific utility function or use a parametric distribution function in order to rank them in terms of expected utility.
+We use the fact that if the utility $u(FC)$ is decreasing in $FC$ and $F_{fee}(FC) \geq F_{sq}(FC)$ for all $FC$, then $E_{fee}[u(FC)] \geq E_{sq}[u(FC)]$.\footnote{See the appendix for the proof.} That is any expected utility maximizer who dislikes paying higher financing cost, regardless of the concavity of his utility function, will prefer the fee-commitment distribution of financial cost.
 Figure \ref{ecdf_fc} in the Appendix shows that indeed $F_{fee}(FC) \geq F_{sq}(FC)$.
@@
 \noindent \textbf{Lost flexibility.} A second neoclassical explanation for low take up is lost flexibility.
-That is, the fee-commitment contract may provide too much commitment which is costly both, (a) because the client may be forced to incur in late payment fees if he experiences a negative income shock, and also because (b) he may be unable to recover the pawn and his pre-payments.\footnote{Note that income shocks that affect the ability to pay the entire loan are a worry for both the fee-forcing contract and the status quo one, and should not make one contract more favorable than the other.} While we cannot rule out that income shocks combined with lost flexibility of the contract explain the low demand, we think it is unlikely.
+That is, the fee-commitment contract may provide too much commitment which is costly because the client may be forced to incur in late payment fees if he experiences a negative income shock.\footnote{Note that income shocks that affect the ability to pay the entire loan are a worry for both the fee-forcing contract and the status quo one, and should not make one contract more favorable than the other.} While we cannot rule out that income shocks combined with lost flexibility of the contract explain the low demand, we think it is unlikely.
 First, we showed above clients report a subjective probability of recovery of 93\% on average, which suggests they are not too worried about income shocks.
@@
 %This compares favorably to the \hlgr{\$11.6 + \$62.3)} pesos transportation / transaction cost of one.
-To make this concrete we calculated what the financing cost of the fee-commitment contract would be if all its clients incurred in \textit{all} potential fees (while keeping payment profiles and pawn recovery constant), thus artificially inflating the cost.
+To make this concrete, we calculated what the financing cost of the fee-commitment contract would be if all its clients incurred in \textit{all} potential fees (while keeping payment profiles and pawn recovery constant) and added these fictitious fees to financing cost for those in the fee-forcing arm, thus artificially inflating their cost.
 We then re-estimated the quantile treatment effects analogous to Figure \ref{fc_pro2}(b) with this inflated financial cost.
@@
 Figure \ref{fc_allfee} presents the results.
-We find that even in this extreme scenario, tilted against the fee-forcing contract, the estimated effect still implies cost savings from the fee-forcing contract at the mean, 25$^{th}$, 50$^{th}$, and 75$^{th}$ percentiles.
-Note that the differences in financing cost already takes into account the fact that clients in the fee forcing contract sink more pre-payments than those in the status quo contract, and that those prepayments are lost if the loan is not fully paid back.
-Although these arguments are not definitive, they suggest that low demand for commitment may be driven by be more than the anticipation of lost flexibility.
+We find that even in this extreme scenario, tilted against the fee-forcing contract, the estimated effect still implies cost savings from the fee-forcing contract at the mean, 25$^{th}$, 50$^{th}$, and 75$^{th}$ percentiles.\footnote{Recall that the differences in financing cost already takes into account the fact that clients in the fee forcing contract sink more pre-payments than those in the status quo contract, and that those prepayments are lost if the loan is not fully paid back.}  Although these arguments are not definitive, they suggest that low demand for commitment may be driven by more than the anticipation of lost flexibility.
 
 \vspace{.1in}
-\noindent \textbf{High time discounting.} In the summary statistics section we mentioned that clients in the status quo contract tend to wait until the last moment to pay to recover their pawns.
-Even among those that recover their pawn, only 20\% pay before the 90$^{th}$ day.
-Table \ref{mechanisms} showed that clients assigned to the fee-forcing contract front load their payments, starting their first payment earlier and finishing to pay earlier too.
-However, clients may dislike front loading payments if their discount rate is high.
+\noindent \textbf{High time discounting.} We mentioned above that clients in the status quo contract tend to wait until the last moment to pay to recover their pawns.
+Even among those that recover their pawn, only 42\% pay before the 90$^{th}$ day.
+Table \ref{mechanisms} shows that clients assigned to the fee-forcing contract front load their payments, starting their first payment earlier and finishing to pay earlier too.
+However, clients may dislike front loading payments if their time preference discount rate is high.
 They may be willing to trade off a higher probability of losing their pawn for more \textit{back} loaded payments.
-This would explain both, why default rates are high and why demand for the fee-commitment contract is low.
-
-What would discount rates have to be in order to offset the reductions in financial cost effects we observe?
-We can calculate this number by looping across a grid of discount rates and reestimating equation \ref{basic_reg} with a financial cost dependent variable that uses the respective discount rate in the grid, and searching for the discount rate that makes $\beta$ equal zero.
-We do this and obtain that the discount rate that rationalizes a zero effect is 8,190 percent per year.
-We find this discount rate implausibly high even for this credit constrained population, and seriously casting doubt on high discount rates as explanation for low demand for commitment.%\footnote{In the baseline survey we give respondents a hypothetical choice between $100$ pesos tomorrow or $150$ pesos in one month (an implicit yearly interest rate of \hl{12,800\%}) and only 30\% chose the later one.}
+
+What would discount rates have to be in order for back loaded payments to offset the reductions in financial cost effects we observe?
+We can calculate this number by looping across a grid of discount rates, incorporating this higher discount rate in the definition of financial cost, and reestimating equation \ref{basic_reg} with this modified financial cost measure as the dependent variable in equation 1, searching for the discount rate that makes $\beta$ equal zero.
+We did this and obtained that the discount rate that rationalizes a zero effect is a staggering 8,190 percent per year.
+We find this discount rate implausibly high even for this credit constrained population\footnote{Just for comparison, \cite{Levin} find that a discount rate of 1,415 per year for subprime borrowers in the US is too high to be believable.}, seriously casting doubt on high discount rates as explanation for low demand for commitment.
+%\footnote{In the baseline survey we give respondents a hypothetical choice between $100$ pesos tomorrow or $150$ pesos in one month (an implicit yearly interest rate of \hl{12,800\%}) and only 30\% chose the later one.}
+
+\vspace{.2in}
+\noindent It seems to us that present bias with naivete is the more likely explanation for low commitment demand in our case.
+Moreover, Section \ref{model} shows that present bias with naivete is able to qualitatively explain all the main findings of the paper, not just low demand for commitment.
 
@@
 
-When preferences or income streams are heterogeneous, and consumers are neoclassical, giving choice among contracts is a welfare increasing strategy.
+When preferences or income streams are heterogeneous, and consumers are neoclassical, giving choice among contracts is often a welfare increasing strategy.
 Consumers would chose the contract that best fits their needs.
@@
 But when consumers are overconfident about their ability to save cash to pay back the loan, free choice could be a sub-optimal policy from the point of view of the client's long run self, and match the clients with a more costly contract.
-
-Even if take up of the commitment-fee contract is low, the sole fact of having choice could potentially change behavior (\cite{Dalboetal:2010}, \cite{Sjostrometal:2018}).
-We find that giving clients the option of choosing among the fee-forcing and the status quo contract does \textit{not} lead to lower financial cost compared to forcing them into the status-quo contract, Figure \ref{fc_pro4}(a) hollow circles.
-Nor does it lead to higher pawn recovery, Figure \ref{fc_pro4}(c).
-The hollow circles in Figure \ref{fc_pro4}(show average effects for the different definitions of financial cost analogous to the ones described above.
-Figure \ref{fc_pro4}(b) shows further that the null effect happens for the 15$^{th}$, 25$^{th}$, 50$^{th}$ 75$^{th}$, and 85$^{th}$ percentiles.\footnote{The few that selected the fee-commitment contract (the solid black squares) do enjoy cost savings of 1005 pesos, which compares favorably to the 304 pesos in the fee-forcing arm (as a fraction of the loan the numbers are 41.5\% and 12.5\%), but this combines the selection and treatment effects.
-We cannot reject the that the ``effect'' on pawn recovery is of the same size for the fee-forcing arm and for those that selected into fee-forcing.} %Figure \ref{heterogeneous_te_4} plots the distribution of treatment effects and finds that the distribution offering choice actually \textit{increased} financial cost and default for about half of clients compared to being assigned the status-quo contract.
+Defenders of choice make another subtler point: that even if take up of the commitment-fee contract is low, the sole fact of having choice could potentially change behavior (\cite{Dalboetal:2010}, \cite{Sjostrometal:2018}, \cite{Tlaxcala}).
+
+We find that giving clients the option of choosing among the fee-forcing and the status quo contract does \textit{not} lead to lower financial cost compared to forcing them into the status-quo contract.
+Nor does it lead to higher pawn recovery.
+The hollow circles in Figure \ref{fc_pro4}(a) show zero average effects for the different definitions of financial cost analogous to the ones described above.
+Figure \ref{fc_pro4}(b) shows further that the null effect happens for the 15$^{th}$, 25$^{th}$, 50$^{th}$ 75$^{th}$, and 85$^{th}$ percentiles.\footnote{The few that selected the fee-commitment contract (the solid black squares) do enjoy cost savings of 1005 pesos, which compares favorably to the 304 pesos in the fee-forcing arm (as a fraction of the loan the numbers are 41.5\% and 12.5\%), but this combines the selection and treatment effects.} %Figure \ref{heterogeneous_te_4} plots the distribution of treatment effects and finds that the distribution offering choice actually \textit{increased} financial cost and default for about half of clients compared to being assigned the status-quo contract.
 Those tended to be the less economically vulnerable and more educated, \hl{women}, and those whose family typically asks them for money.
-Consistent with these findings, Figure \ref{reincidence} finds no effect on repeat purchases for the choice group.
+Figure \ref{fc_pro4}(c) finds null effects for pawn recovery. Consistent with these findings, Figure \ref{reincidence} finds no effect on repeat purchases for the fee-choice group.
 
@@
 
-This is not the first paper to find low demand for commitment, however it is the first we know of that can compare choice vs forcing.
-The fact that the fee-forcing contract lowers financial costs for all, together with the fact that only 10\% choose it must mean that many consumers are choosing contracts with higher financial costs for them.
+This is not the first paper to find low demand for commitment, however \hl{it is the first we know of that can compare choice vs forcing}.
+The fact that the fee-forcing contract lowers financial costs for almost all clients, together with the fact that only 10\% choose it must mean that many consumers are choosing contracts with higher financial costs for them.
 We can ask how many consumers seem to be making a cost increasing choice and how much money are they leaving on the table.
-To do this we conduct two exercises.
+We conduct two exercises.
 
 \vspace{.2in}
-\noindent \textbf{Are there ``mistakes'' in choice?} Answering this question requires calculating a counterfactual: for each person in the choice arm we want to know how much cost savings a client would have if she chose the fee-commitment contract instead of the status quo contract.
+\noindent \textbf{Are there ``mistakes'' in choice?} Answering this question requires calculating a counterfactual: for each client in the choice arm we want to know how much cost savings she would have had she chosen the opposite contract.
 We do this in two steps.
-First, using the honest causal forests method of \cite{atheygrf} described above we calculate the causal effect on financing cost of getting the fee-forcing contract instead of the status quo contract for a client with characteristics $x_i$ \textit{in the forcing arms}, we call it $TE^{fee}_{i}$.
-There is no selection problem in the forcing arms.
-Second, using these estimates, we predict treatment effects for clients \textit{in the choice arm} using the $x_i$'s, and call it $\widehat{TE}^{fee}_{i}$.
+First, using the honest causal forests method of \cite{atheygrf} described above we calculate the causal effect on financing cost of getting the fee-forcing contract instead of the status quo contract for a client with characteristics $x_i$ \textit{in the forcing arms}, we call it $TE^{fee}_{i}(x_i)$.
+Recall that \cite{atheygrf}'s method uses causal trees to generate a partition of the space of characteristics $x$, where each element of the partition is a leaf, and each leaf contains treatment and control clients with similar characteristics $x$ which are used to calculate unbiased honest treatment effects for that leaf.
+Second, we predict treatment effects for clients \textit{in the choice arm} using the partition into leaves and the treatment effect associated with the leaf obtained in step 1, that is client $j$  is imputed the treatment effect of the leaf corresponding to her characteristics $x_j$.
+We call this counterfactual treatment effect $\widehat{TE}^{fee}_{i}(x_j)$.
 This is precisely the counterfactual we wanted.\footnote{This extrapolation of the treatment effects assumes that choice itself --conditional on a given contract-- does not affect behavior.
 Given the results in subsection \ref{effect_choice} we are comfortable with this assumption.
-Note that although the extrapolation is to another population, by randomization it is a statistically identical population.} Armed with this, we say that a client made a ``mistake'' if either she chose the status quo contract and her $\widehat{TE}^{fee}_{i}$ is negative (i.e.
+Note that although the extrapolation is to another population, by randomization it is a statistically identical population with common support.} Armed with this, we say that a client made a ``mistake'' if either she chose the status quo contract and her $\widehat{TE}^{fee}_{i}$ is negative (i.e.
 more cost saving from the fee contract), or if she chose the fee-commitment contract and $\widehat{TE}^{fee}_{i}$ is positive, meaning that financial cost are larger for the fee-commitment contract.
@@
 Since the prediction of the treatment effect is an estimate and has noise, we do two things.
-First, we normalize $\widehat{TE}^{fee}_{i}$ by the value of the loan of person $i$ and introduce a threshold parameter $z$ and say that a choice is a ``mistake'' if the alternative contract would generate more than $z$ in savings.
-We vary from 0\% to 20\% of the value of the loan.
-Second, we take into account uncertainty in estimation of treatment effects and report results also using the extremes of the 95\% confidence interval bounds for $\widehat{TE}^{fee}_{i}$.
+First, we normalize $\widehat{TE}^{fee}_{i}$ by the value of the loan of person $i$ and introduce a threshold parameter $z$ and say that a choice is a ``mistake'' if the alternative contract would generate greater than $z$ in savings.
+That is, we introduce a threshold that we vary from 0\% to \hl{15}\% of the value of the loan.
+Second, we take into account uncertainty in estimation of treatment effects and report results using the extremes of the \hl{90\%} confidence interval bounds for $\widehat{TE}^{fee}_{i}$.
 
@@
 In the X-axis it varies the threshold $z$ of what we classify as a mistake.
-In this section we are concerned with lines in red color.
-When $z=0$, we calculate that about 80\% of clients in the fee-choice group chose contracts that induced \textit{higher} financial cost (95\% confidence interval [36,95]).
+When $z=0$, we calculate that about 80\% of clients in the fee-choice group chose contracts that induced \textit{higher} financial cost (90\% confidence interval \hl{[45,94]}).
 Most mistakes are failures to choose the fee-commitment contract (92\%), while only 8\% of those who chose the fee-commitment contract would have been better in the status-quo one.
-The average mistake in pesos is \$238 (95\% confidence interval [131,427]).
-Figure \ref{choose_wrong}(b) separates the analysis for those we classify as overconfident about recovering their pawn (96\% of them) vs the rest.
-It shows that there are about 14 percentage points more mistakes in the overconfident population when $z=0$.
+The average mistake in pesos is \$238 (90\% confidence interval \hl{[140,390]}).
+Figure \ref{choose_wrong}(b) separates the analysis for those we classify as overconfident about recovering their pawn vs the rest.
+It shows that there are about \hl{11} percentage points more mistakes in the overconfident population (when $z=0$).
 
@@
 This conclusion is in line with a recent paper by \cite{John}.
-In a savings context, she finds that when commitment in on the menu a majority of subjects wrongly choose to little commitment.
-She concludes this by observing high levels of default even with late payment fees, whereas we work directly with estimated treatment effects.
+In a savings context, she finds that when commitment is on the menu a majority of subjects wrongly choose to little commitment.
+She concludes this by observing high levels of default even with late payment fees, whereas we work directly with estimated counterfactual treatment effects.
 
@@
 First, we estimate a flexible model of take-up of the fee commitment contract \textit{in the choice arm} using random forests and obtain for a client with characteristics $x_i$ a probability $P(x_i)$ of choosing the fee-forcing contract.
-We then use this model to predict the counterfactual probability of client with characteristics $x_i$ choosing the fee-commitment contract in the no choice-arms if she would have been given the choice, what we call $\widehat{P(x_i)}$.
-Since our model for has a good out-of-sample fit with an out-of-sample AUC of 0.85 and an accuracy rate of 85\%, we think we are not introducing too much noise by this extrapolation.
-Second, armed with this prediction in the no-choice arms, we can ask the following: is it true that people with larger fee-forcing contract treatment effects (i.e.
-more cost savings) more likely to demand the fee-forcing contract?
-
-Figure \ref{choose_wrong}(d) plots $\widehat{P(x_i)}$ in the X-axis, and the heterogeneous we estimated in section \ref{TE_fee-forcing} in the Y-axis.
+We then use this model to predict the counterfactual probability of a client with characteristics $x_j$ choosing the fee-commitment contract in the no choice-arms if she would have been given the choice, what we call $\widehat{P(x_j)}$.\footnote{Our random forest take-up model has a good out-of-sample fit with an out-of-sample AUC of 0.85.
+We think we are not introducing too much noise by this extrapolation.} Second, armed with this prediction in the no-choice arms, we can ask the following: is it true that people with larger fee-forcing contract treatment effects (i.e.
+more cost savings) are more likely to have demanded the fee-forcing contract if choice had been given to them?
+
+Figure \ref{choose_wrong}(d) plots $\widehat{P(x_i)}$ in the X-axis, and the heterogeneous treatment effects we estimated in section \ref{TE_fee-forcing} in the Y-axis.
 If it was true that those with larger cost savings have larger demand for the fee-commitment contract, we would expect a negative slope (recall that more savings mean lower financial cost in the Y-axis).
 This is not what we find.
-Figure \ref{choose_wrong}(d) is a binscatter that splits the X-axis in 100 percentiles bins of predicted take-up probability and for each bin averaged the financial cost treatment effects.
+Figure \ref{choose_wrong}(d) is a binscatter that splits the X-axis in 100 percentiles bins of predicted take-up probability and for each bin averages the financial cost treatment effects.
 Using all clouds we estimate a slope of zero in the relationship.
@@
 A positive relation means that those more likely to demand commitment are also those that had smaller benefits from commitment.
-This result is similar to \cite{Walters}, who finds that students that select into more effective schools are the ones with smaller treatment effects.
-\cite{Walters} uses distance to school as an instrumental variable for choice, while we use randomization to choice vs no-choice groups as our empirical strategy.
+This result is similar to \cite{Walters}, who finds that students that select into more effective schools are the ones with smaller treatment effects from attending.\footnote{\cite{Walters} uses distance to school as an instrumental variable for choice, while we use randomization to choice vs no-choice groups as our empirical strategy.}
 
@@
 
-\subsection{A simple model} \label{model}
+\subsection{A simple model} \label{model_detail}
 
@@
 The model has three periods and linear utility.\footnote{This does not map perfectly to our 3 period contract, but it is enough to generate the results we need.} Period $t=0$ is a planning period where the client is either allocated to the status quo, the fee-forcing contract, or a choice between the two.
+Period $t=1$ is the savings decision period, and $t=2$ in the pawn recovery (loan payment) period.
 In period 1 the client receives her income $y_1=1$, or gets zero with probability $\lambda$.
-She can consume ($c_1$) or save ($s_1$) that income.
-In period 2 the client gets her savings from period 1, and again receives income of either $y_2=1$, or zero with probability $\lambda$.
+She can consume ($c_1$) or save ($s_1$) part that income.
+In period 2 the client gets her savings from period 1, and again receives income of either $y_2=1$, or zero with independent probability $\lambda$.
 In this last period, she decides whether to use income and savings for consumption $c_2$ and/or for paying back the loan of size $p \in(1,2)$ to recover the pawned piece valued at $b>p$.
-In this simple model we will impose a penalty fee $F>0$ in $t=1$ for the fee-commitment contract if the month's payment is not done.
+In this simple set up we model the fee-commitment contract as a contract that imposes a fee of size $F$ if the client fails at $t=1$ to save $s1=p-1$ pesos, which is what is needed to pay the loan back when there are no shocks.
 In period $t=0$ she evaluates her welfare as $E[c_1+c_2]$, were for simplicity we have set the time discount to one.
 We also assume the interest rate is one.
-We introduce present bias preferences by assuming the following utility function $U_t=c_t+\beta \: \sum_{k=t+1}^{2} E[c_k]$, with $\beta<1$ indicating present bias.
+We introduce present biased preferences by assuming the following utility function $U_t=c_t+\beta \: \sum_{k=t+1}^{2} E[c_k]$, with $\beta<1$ indicating present bias.
 A naive client perceives she is not so present biased and instead of $\beta$ uses $\hat{\beta} \in (\beta,1]$.
 
-Note that under these assumptions it is efficient at $t=0$ to take actions to recover the loan.
-Because $b>1$, paying back the loan requires that there is no negative shock in any period and that $s_1>0$, and because $\beta<1$ at $t=1$ the client will not send savings in excess of what is needed to recover the loan $s_1=p-1$.
-
-\vspace{.1in}
-\noindent \textbf{Result 1: Present bias consumers default more.} Under the status-quo contract, absent shock realizations, present biased clients (sophisticated or naive) with $\beta<\beta_{SQ}<1$ will lose their pawn, while clients with no present bias will not.
-Viewed from $t=0$ losing the pawns when there are no shocks is inefficient as $b>p$.\footnote{$\beta_{SQ}=\frac{p-1}{\lambda(p-1)+(1-\lambda)(b-1)}$.
+Note that under these assumptions it is efficient at $t=0$ to recover the loan since $b>p$ and since there is no discounting at $t=0$.
+Because $b>1$, paying back the loan requires that there is no negative shock in any period and that $s_1>0$.
+Because $\beta<1$ at $t=1$ the client will not send savings in excess of what is needed to recover the loan: $s_1=p-1$.
+This parsimonious model implies the following results:
+
+\vspace{.2in}
+\noindent \textbf{Result 1: Present biased clients default more.} Under the status-quo contract, absent shock realizations, present biased clients (sophisticated or naive) with $\beta<\beta_{SQ}<1$ will lose their pawn, while clients with no present bias will not.\footnote{$\beta_{SQ}=\frac{p-1}{\lambda(p-1)+(1-\lambda)(b-1)}$.
 See Proposition 1 in \cite{John}.}
@@
 It strictly decreases default if $F>F_{min}(\beta):=(p-1)-\beta[\lambda(p-1)+(1-\lambda)(b-1)]$.
-The larger the present bias the larger the $F$ required to induce pawn recovery.\footnote{The incentive compatibility constraint to generate savings to recover the pawn can be written as $1-(p-1)+\beta[\lambda(p-1)+(1-\lambda)(b-1)] \geq 1-F+\beta(1-\lambda)$.}
+The larger the present bias the larger the $F$ required to induce pawn recovery.\footnote{$F_{min}(\beta)$ is derived from the incentive compatibility constraint needed to generate savings at $t=1$ to recover the pawn can be written as $1-(p-1)+\beta[\lambda(p-1)+(1-\lambda)(b-1)] \geq 1-F+\beta(1-\lambda)$.}
 
@@
 \noindent \textbf{Result 5: Welfare.} (a) Neoclassical consumers' welfare strictly decreases when we force clients into the fee-commitment contract instead of the status quo contract, and does not change when we offer a choice between them.
-(b) The welfare of sophisticated present biased consumers weakly increases when we give them choice, and it strictly increases  $\iff$  $\beta \in [\beta_{min},\beta_{SQ}]$, that is when they choose it themselves.
-Forcing them into the fee-commitment contract increases welfare $\iff$  $\beta \in [\beta_{min},\beta_{SQ}]$, otherwise it strictly decreases.
+(b) The welfare of sophisticated present biased consumers weakly increases when we give them choice, and it strictly increases  $\iff$  $\beta \in [\beta_{min},\beta_{SQ}]$, that is when they would choose the fee-commitment contract themselves.
+Forcing them into the fee-commitment contract increases welfare $\iff$  $\beta \in [\beta_{min},\beta_{SQ}]$, otherwise it strictly decreases it.
 So choice is better than forcing for sophisticates.
@@
 Indeed if $\hat{\beta}>\beta_{SQ}>\beta$ then forcing the fee-commitment contract increases welfare, and if $\hat{\beta} \in (\widehat{\beta_{min}},\beta_{min})$ then forcing the status quo contract increases welfare.\footnote{This result is different from that in \cite{John}.
-His context has individuals choosing the size of the fee.
-In that context naive clients will always chose the wrong fee size and default, therefore choice is always decreasing for the.
+Her context has individuals choosing the size of the fee.
+In that context naive clients will \textit{always} chose the wrong fee size and default later, therefore choice is always decreasing for the naive.
 In our context $F$ is fixed at 2\% of the balance due, and this implies that choice could be welfare improving for some naifs.}
@@
 \vspace{.1in}
-\noindent \textbf{Result 6: Welfare and ex-post observed behavior.} If for client $i$ the fee-forcing contract causes higher pawn recovery, then we know the fee $F$ made her IC constraint binding, and therefore that $\hat{\beta_i}>\widehat{\beta_{min}}$.
-If in addition if it was the case that \hl{$\beta<\beta_{SQ}$}\footnote{\hl{Isaac, aqui tengo dos pregutas: (1) si es $\beta$ y no $\hat{\beta}$ verdad?
-(2) Para que una persona naive empeñe en el status quo tiene que ser que cree que va a recuperar no?
-Es decir tiene que ser $\hat{\beta}>\beta_{SQ}$ correcto?}} then the fee-forcing contract would have increased welfare for the naive.
-That is, our finding that the fee-forcing contract increases pawn recovery is a sign of higher welfare.
+\noindent \textbf{Result 6: Welfare and ex-post observed behavior.} If for a naive client $i$ the fee-forcing contract causes higher pawn recovery, then we know the fee $F$ made her IC constraint binding, and therefore that $\hat{\beta}_i>\widehat{\beta}_{min}$.
+If in addition if it was the case that $\beta_i<\beta_{SQ}$.
+%\footnote{\hl{Isaac, aqui tengo dos pregutas: (1) si es $\beta$ y no $\hat{\beta}$ verdad?
+(2) Para que una persona naive empenie en el status quo tiene que ser que cree que va a recuperar no?
+Es decir tiene que ser $\hat{\beta}>\beta_{SQ}$ correcto?}}
+then the fee-forcing contract would have increased welfare for the naive.
+That is, our finding that the fee-forcing contract increases pawn recovery is a sign of higher welfare (although not a sufficient condition).\footnote{It is not sufficient since ex-ante the commitment $F$ may have been too expensive given the income shocks, i.e.
+if $\lambda \: F>(1-\lambda)^2(b-p)$.}
 
@@
 
-The model of \cite{John} is very parsimonious but powerful.\footnote{The model is sufficiently stylized that we think we would not gain much from estimating it.
+The model of \cite{John} is very parsimonious but powerful and it can potentially explain all facts qualitatively.\footnote{The model is sufficiently stylized that we think we would not gain much from estimating it.
 Furthermore we have no data on income shocks which figure prominently in the model.
-\cite{Ted} and \cite{Aprajit} are two very recent models that combine a field experiment with commitment contracts and estimation of present bias parameters.} First, it can explain why clients are overconfident in our data, namely by virtue of naivete about present bias.
+\cite{Ted} and \cite{Aprajit} are two very recent models that combine a field experiment with commitment contracts and estimation of present bias parameters.} First, it can explain why default is high in the status-quo contract, namely that clients are present biased and have no commitment devices.
+Second, it can explain why clients are overconfident in our data, namely by virtue of naivete about present bias.
 Under the model naivete is necessary to explain this.
-Second, it can also explain why the fee forcing contract induces lower default, but not for everyone: namely that it makes the IC constraint for the present biased binding while it was not binding in the status quo contract.
-Third, it can also explain why there is low demand for commitment even if it seems to improve welfare: namely that there is a small share of neoclassical and sophisticated clients, and at the same time naifs have  $\hat{\beta}>\beta_{SQ}$ and therefore think they can save on their own.\footnote{By Result 6 we can eliminate $F<F_{min}(\widehat{\beta}$) as an explanation.}.
-Fourth, it can explain why clients exposed to the fee-forcing contract are more likely to come back, namely that $\hat{\beta_i}>\beta_{SQ}>\beta$ and so their welfare increased as a result of being forced into the fee-commitment contract, and they may realize this.
-
-One could also easily introduce overconfidence in income shocks with $\widehat{\lambda} <\lambda$.
-This would leave default unchanged in both the status quo and the fee forcing contract.
-%since $F_{min}(\beta,\widehat{\lambda})<F_{min}(\beta,\lambda)$.
-The effect on demand for commitment is uncertain since on the one hand it decreases $\beta_{SQ}$ decreasing demand, but on the other a smaller $F$ is needed to make the IC binding, making commitment less costly.
+Third, it can also explain why the fee forcing contract induces lower default, but not for everyone: namely that it makes the IC constraint for the present biased binding while it was not binding in the status quo contract.
+Fourth, it can also explain why there is low demand for commitment even if it seems to improve welfare: namely that there is a small share of neoclassical and sophisticated clients, and at the same time naifs have  $\hat{\beta}>\beta_{SQ}$ and therefore think they can save on their own.\footnote{By Result 6 we can eliminate $F<F_{min}(\widehat{\beta}$) as an explanation.} Fifth, it explains non-zero demand for commitment for a set of clients.
+Sixth, it can explain why clients exposed to the fee-forcing contract are more likely to come back, namely that $\hat{\beta_i}>\beta_{SQ}>\beta$ and so their welfare increased as a result of being forced into the fee-commitment contract, and they realized this after experiencing it.
 
@@
 
-There may be other interpretation of the empirical findings. But the bar is high. An alternative explanation will need to explain the facts below:
+There may be other interpretation of the empirical findings. But the bar is high. An alternative explanation will need to explain the 6 facts below:
 
@@
 \itemsep0em 
+\item High (although ex-post inefficient) default in status quo contract.
 \item Overconfidence about pawn recovery.
-\item High (although ex-post inefficient) default in status quo contract.
+\item Forcing commitment increases pawn recovery.
 \item Small demand for commitment...
 \item ...but positive demand for commitment.
-\item Forcing commitment saves money.
 \item Forcing commitment makes clients more likely to come back.
@@
 
+Let us consider alternative explanations in isolation (i.e. just considering one change or feature at a time with respect to a neoclassical model):
+
 \vspace{.1in}
-\noindent \textbf{Alternative 1: Strong prevalence of income shocks.} This could explain low demand for commitment (3) and (2), but not why forcing helps (5) and (6), nor why there is overconfidence (1), or why they come to pawn in the first place, try to pay back and then default (2).
+\noindent \textbf{Alternative 1: Strong prevalence of income shocks.} This could explain low demand for commitment (4) and (1), but not why forcing helps (3) and (6), nor why there is overconfidence (1), or why they come to pawn in the first place and then default (2) as they would weight in on the high chance of losing the pawn.
 
@@
 \vspace{.1in}
-\noindent \textbf{Alternative 4: Misunderstanding the contracts.}\footnote{This is a potential criticism of any paper offering choice, and one that is non-falsifiable if the critic has free reign to propose how the contracts are perceived in the subject's mind.} We were very aware of this and in the implementation a very strong effort was made for consumers to understand the contracts (see subsection \ref{implementation}).
-Note however that while clients making random mistakes could explain why 10\% demand commitment ---i.e.
-(3) and (4)--- they would not explain the rest of facts, nor why the promise-commitment (see below) had more take up that the fee-commitment, or why those with present bias and those that want a reminder to pay are more likely to make the ``error'' to demand commitment.\footnote{See Figure \ref{interactions_takeup} and Table \ref{Table_compliance}}
+\noindent \textbf{Alternative 4: Misunderstanding the contracts.}\footnote{This is a potential criticism of \textit{any} paper offering choice, and one that is non-falsifiable if the critic has free reign to propose how the contracts are perceived in the subject's mind.} We were very aware of the importance of clients understanding the contract in order to infer preferences from choice.
+That is why we made a strong effort for clients to understand the contracts (see subsection \ref{implementation}).
+Note however that while clients making purely random mistakes could explain why 10\% demand commitment ---i.e.
+(4) and (5)--- it would not explain the rest of the findings, nor why the promise-commitment (see below) had more take up that the fee-commitment, or why those with measured present bias and those that want a reminder to pay are more likely to make the ``error'' to demand commitment.\footnote{See Figure \ref{interactions_takeup} and Table \ref{Table_compliance}}
 
@@
 \noindent \textbf{Alternative 5: Forgetting to pay.} Frequent payments may act as a reminder to save and recover the pawn.
-This would try to explain (2) by appealing to people forgetting to pay, and (5), (6) and (4) by appealing to frequent payment acting as reminders.
-It would not explain (1) or (3) which are critical in the paper.
-However even for (2) it seems to us a stretch to explain people losing a valuable pawn by forgetting to pay.
-
+This would try to explain (1) by appealing to people forgetting to pay, and (3), (5) and (6) by appealing to frequent payment acting as reminders (i.e.
+there being demand for reminders).
+It would not explain (2) or (4) which are critical in the paper.
+However even for (1) it seems to us a stretch to explain people losing a valuable pawn by forgetting to pay it.
+
+\vspace{.1in}
+\noindent \textbf{Alternative 6 (behavioral): Income shocks overconfidence}.
+One could also easily introduce in the overconfidence in income shocks with $\widehat{\lambda} <\lambda$ in the model of section \ref{model_detail}.
+This would leave default unchanged in both the status quo and the fee forcing contract thus would not explain (3), %since $F_{min}(\beta,\widehat{\lambda})<F_{min}(\beta,\lambda)$.
+but the effect on demand for commitment is uncertain since on the one hand it decreases $\beta_{SQ}$ decreasing demand, but on the other a smaller $F$ is needed to make the IC binding, making commitment less costly.
+$\widehat{\lambda} <\lambda$ alone would not explain the (5) or (6) as demand for commitment would be zero without present bias.
+
+\begin{comment}
 \vspace{.1in}
@@
 We are sympathetic to the learning hypothesis and in fact it is \cite{Alcohol}'s main conjecture about why he finds strong demand for commitment while most other studies don't.\footnote{Close to ninety percent of our subjects claim to have pawned before.
-We find that experience does not predict positive take up in our sample correlationally.} To test it we would ideally need to give choice to a group of people that randomly experienced the fee-commitment vs those that did not, and test if the former demand it more.\footnote{\hl{Isaac, podemos volver a tratar esto?
-Hace como 1 anio no nos salio pero quiero volver a tratar.}} Unfortunately we did not do this experiment and we have very limited data to try it: \hl{210 (6\%)} clients were given a choice in a second pawns in our experiment after being randomly assigned to the status quo or fee-forcing contract.
+We find that experience does not predict positive take up in our sample correlationally.} To test it we would ideally need to give choice to a group of people that randomly experienced the fee-commitment vs those that did not, and test if the former demand it more.
+Unfortunately we did not do this experiment and we have very limited data to try it: \hl{210 (6\%)} clients were given a choice in a second pawns in our experiment after being randomly assigned to the status quo or fee-forcing contract.
+\end{comment}
+
+\vspace{.1in}
+We do not claim that the model in section \ref{model_detail} is the only possible explanation of our findings, but it is a parsimonious explanation of all of them and a lens for interpretation.
 
@@
 
-One finding of the paper is that a rather small fee of 14 pesos on average changes behavior substantially: on the one hand generates average savings in the order of 300 pesos when forced, but on the other dissuades take up  when client have choice.
+One finding of the paper is that a rather small fee of 14 pesos on average changes behavior substantially: on the one hand generates average savings for almost everybody (and in the order of \hl{230} pesos on average) when forced, but on the other dissuades take up when clients have choice.
 In this context one would want a commitment device that generates higher take up while at the same time providing incentives for paying fast and recovering the pawn.
-One way to go would be to decrease the already small fee to say 1\% or lower.
-We decided to instead experiment with a non-pecuniary penalty, in the form of the psychological cost of breaking a promise.
-As explained in Section \ref{Experiment} the promise contract involved making a salient promise to repay monthly as part of their pawn contract in words and in written, and receive the speech by the appraiser about the importance of keeping her promise of paying monthly.
+One way to go would be to decrease the already small fee say to 1\% or lower.
+We decided to instead experiment with a non-pecuniary penalty, in the form of a psychological cost of breaking a promise.
+As explained in Section \ref{Experiment} the promise contract involved making a salient promise to repay monthly, and receive a short speech by the appraiser about the importance of keeping her promise of paying monthly.
 
@@
 To our knowledge this result has been replicated several times in laboratory contexts but not in a field setting like ours.
-If breaking a promise is perceived as having a lower cost than paying the 2\% fee, we predict that more people will have demand for the promise-commitment contract.
-We indeed find that take up is higher.
-Is this higher take up associated with smaller treatment effects though?
-Or does the promise have enough commitment power?
+If breaking a promise is perceived as having a lower cost than paying the 2\% fee and at the same time help as a commitment, we predict that more people will have demand for the promise-commitment contract.
 
@@
 
-\vspace{.2in}
+\vspace{.1in}
 \noindent \textbf{Demand}.
-It turns out that the demand for monthly payment contracts with a personal promise to pay monthly ---but no pecuniary penalty for not doing so--- induces higher demand by a factor of three compared with fee-commitment contract studied above: 31\% of clients offered a choice between the status quo contract and the promise-commitment contract chose commitment.
-This means that that the pecuniary fee indeed limited demand for commitment.
+It turns out that the demand for monthly payment contracts with a personal promise to pay monthly ---but no pecuniary penalty for not doing so--- induces higher demand by a factor of three compared with fee-commitment contract: 31\% of clients offered a choice between the status quo contract and the promise-commitment contract chose commitment.
+This means that the pecuniary fee indeed limited demand for commitment.
 In passing this means also that clients are responsive to contract terms and seem to understand the conditions.
@@
 This suggests that those taking up the promise commitment are not the ones needing the commitment.
-The opposite is true for those who take up the fee-commitment contract (see Figure \ref{interactions_takeup} in the Appendix).
+The opposite is weakly true for those who take up the fee-commitment contract (see Figure \ref{interactions_takeup} in the Appendix).
 
@@
 Figure \ref{fc_pro5}(a) finds that assigning clients to the choice-promise condition has a zero effect on financial cost on average (circles).
-We see no difference even for the endogenous group that chose to promise (squares).
+We see no difference even for the endogenous group that \textit{chose} to promise (squares).
 This null effect happens not only on average, but also by percentiles (not shown in Figure).
-There is also no effect on pawn recovery on (first coefficient in Figure \ref{fc_pro5}(b)), even for those that themselves choose to promise (squares).
-And the null effect carries over if we use the definition of recovery in less than 120 days, or for the (endogenous) subgroups that paid a positive amount or at least a third of their loans.
+There is also no effect on pawn recovery on (first coefficient in Figure \ref{fc_pro5}(b)), even for those that themselves choose to promise.
+And the null effect carries over if we use the definition of recovery in less than 120 days, or for the (endogenous) subgroups that paid a positive amount.
 Finally, there is no effect on repeat pawning (Figure \ref{reincidence}).
@@
 \vspace{.2in}
-\noindent The evidence presented in this section contrasts sharply with the evidence in laboratory experiments where people choosing to promise has a large effect on behavior and were people keep their promises.
+\noindent The evidence presented in this section contrasts sharply with the evidence in laboratory experiments where people choosing to promise has a large effects on behavior, and were people keep their promises.
 While clients are more enthusiastic about the promise-commitment contract than the fee-commitment one in the sense of tripling take-up, the promise contract provides no commitment.
@@
 In a pawnshop borrowing context, we studied whether forcing borrowers into frequent payment commitment contracts reduces their borrowing costs, compared to a contract that does not provide commitment to pay monthly.
-Even though we are charging them fees, their borrowing cost are actually reduced by 9.5\%, and they recover their pawn with 25.8\% higher likelihood.
+Even though we are charging them fees, their borrowing cost are actually reduced by 9.5\%, and they recover their pawn with 25\% higher likelihood.
 Moreover they themselves seem to like this contract, as they are 55\% more likely to come back and pawn again when they get it.
@@
 However when given choice between the commitment and the status quo contract only 10\% choose the former one and thus forgo important benefits.
+A simple model shows that present bias with naivete parsimoniously explains all findings.
 This strongly suggests that ``private paternalism'', a policy that advances an individual's interests by restricting her freedom, is beneficial in our context.
-We provide a quantification of the size of unrealized benefits that arise when clients have choice.
-Methodologically, to our knowledge this is the first paper in economics that uses machine learning methods to estimate personalized counterfactual treatment gains and ask whether treatment take up is positively selected.
+We provide a quantification of the size of unrealized benefits that arise when clients have choice and calculate that 92\% of clients would benefit with more recovery and lower financial cost from being forced into the fee-commitment contract.
+
+Methodologically, to our knowledge this is the first paper in economics that uses machine learning methods to estimate personalized counterfactual treatment gains and ask whether treatment take up is positively selected on benefits, using treatment effects in forcing arms to calculate benefits in choice arms.
 
@@
 We see three lines of further work that are of interest.
-First, investigate why the fee-commitment contract had such low demand in spite of its across-the-board benefits.
-In particular if naivete about self control problems, biased expectation about income shocks, or ambiguity aversion play a role.
-Second, whether other types of contracts ---for instance less coarse choice menus--- could induce larger demand and better performance.
+First, investigate why the fee-commitment contract had such low demand in spite of its across-the-board benefits and very low fees.
+In particular tease out the roles of naivete about self control problems, biased expectations about income shocks, and ambiguity aversion with better direct baseline measurements.
+Second, whether other types of contracts ---for instance those that provide some insurance against shocks--- could induce larger demand and better performance.
 Third, whether individuals choosing to borrow from pawnshops are more present biased and naive than similar individuals borrowing from other types of lenders.
@@
 
-\pagebreak
+\newpage
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{center}
- \footnotesize This table shows the parameter estimates of $y_i = \alpha + \beta \: OC_i + X_i'\gamma + \epsilon_i$, where $OC_i:=\mathbbm{1}(P^s_i-\widehat{P_i(X_i)}>0)$ is an indicator for the subjective probability of recovery being larger that the predicted one.
+ \footnotesize This table shows the parameter estimates of $y_i = \alpha + \beta \: OC_i + Z_i'\gamma + \epsilon_i$, where $OC_i:=\mathbbm{1}(P^s_i-\widehat{P_i(X_i)}>0)$ is an indicator for the subjective probability of recovery being larger that the predicted one.
 In columns 1-4 $y_i$ is a dummy for whether the client $i$ chose to have the commitment contract in the respective choice arm, and in columns 5 and 6 $y_i$ is the heterogeneous treatment effect for financial cost (in pesos) estimated by comparing the fee-forcing vs status quo arms in Section \ref{TE_fee-forcing}.
 Columns 1 and 3 are estimated for the promise-choice arm, while columns 2 and 4 are estimated for the fee-choice arm.
+The low number of observations results from  our use of  covariates for $\widehat{P(x)}$ and in $Z$ in the regression, given that some of them are missing.
 %\textit{Do file: } \texttt{oc.do}
@@
 We finished the experiment earlier in branches 1 and 2 because we realized that we would have enough sample size with the remaining branches and save on operational costs.
-Panel (b) shows our 5 treatment arms: control (status quo contract), no choice with fee, no choice with promise, choice among both contracts where the commitment contract has a fee, and choice among both contracts where the commitment contract involves only a promise.
+Panel (b) shows our 5 treatment arms: control (status quo contract), no fee-forcing, promise-forcing, choice among status quo and fee-commitment, and choice among status quo promise-commitment.
 Within each arm it displays the number of observations.
@@
     \begin{subfigure}{0.42\textwidth}
-        \caption{Financial cost}
+        \caption{Financial cost (pesos)}
         \centering
@@
         \scriptsize
-        This figure shows the estimated treatment effect of ``forcing'' the frequent payment commitment contract using fees, compared to the status-quo (control) for  financial cost (Panel a), quantiles of financial cost (Panel b), and for an indicator of losing the pawn (Panel c).
+
+      %\textit{Do file: }  \texttt{fc\_te.do, def\_te.do, fc\_quantilereg.do}
+\end{figure}
+
+\scriptsize {
+\noindent This figure shows the estimated treatment effect of ``forcing'' the frequent payment commitment contract using fees, compared to the status-quo (control).
 In Panel (a) each dot represents the estimated treatment effect for a different definition of financing cost, or for a different sub-population, and its 95\% confidence interval.
-From left to right, the first effect corresponds to using the gold value of the pawned piece in the definition of financial cost and discounting the payments to present value using a 7\% monthly rate; the second uses the subjective value of the pawn; the third is analogous to the second but adds transaction cost (transport+1 day's wage) per visit; the fourth conditions on the population that paid any positive amount towards recovery of their pawn; the fifth conditions on the sub-population of the treatment group that paid a fee and compares these to all the control group; the sixth conditions on the intersection of the previous two sub-populations.
+From left to right, the first effect corresponds to using the gold value of the pawned piece in the definition of financial cost and discounting the payments to present value using a 7\% monthly rate; the second uses the subjective value of the pawn; the third is analogous to the second but adds transaction cost (transport+1 day's wage) per visit; the fourth conditions on the population that paid any positive amount towards recovery of their pawn; the fifth conditions on the sub-population of the treatment group that paid a fee and compares these to all the control group.
 Panel (b) plots the effects on different quantiles of the distribution of financial cost (using the first definition): 15th, 25th, 50th, 75th, 85th percentile.
 Panel (c) plots the distribution of the heterogeneous treatment effects on financial cost, estimated using \cite{atheygrf}.
-The distribution plots the FC treatment effect for the interval $[\mu-2\sigma,\mu+2\sigma]$ to ignore the outliers.
 Panel (d) Measures the effect of treatment on the likelihood of losing their pawn.
-The first coefficient compares all the treatment group vs all the control; the second conditions on the period covering 120 days.
-The third conditions on the population that paid any positive amount towards recovery of their pawn; the fourth conditions on having paid at least 30\% of the loan amount.
+The first coefficient compares all the treatment group vs all the control using 230 days after pawning to define the dependent variable; the second defines it using 120 days.
+The third coefficient from the left conditions on the population that paid any positive amount towards recovery of their pawn (which in theory may be endogenous but empirically we showed not to be affected by treatment).
+Finally, Panel (e) shows the distribution of heterogeneous treatment effects of the probability of losing the pawn.
 % the effect on ``repeat purchase''.
@@
 The second coefficient estimates the regression conditional on recovering the pawn \hl{in both treatment and control}, and the rightmost coefficient compares those above the median treatment effect in financial cost savings, \hl{versus all the control group.}
-      %\textit{Do file: }  \texttt{fc\_te.do, def\_te.do, fc\_quantilereg.do}
-\end{figure}
+}
+
+\vspace{3ex}
 
@@
 The figures also presents differences in these two outcomes for those who chose the frequent payment commitment contract versus the whole control group (squares-NSQ), and also for those who chose the status quo contract versus the whole control group (triangles-SQ).
-Note that these two comparisons are not pure causal effects since people who chose the frequent payment commitment contract may be different from those that do not.
+Note that these two comparisons are not pure causal effects since people who chose the frequent payment commitment contract are different from those that do not.
 That is: the squares and triangles combine selection and treatment effects.
@@
 The left Y-axis measures the fraction of subjects that would have been better by a margin of $z$\% if they changed their choice, and the right Y-axis measures the amount of money ``left on the table''.
-The thinly dotted lines represent 95\% confidence intervals.
+The thinly dotted lines represent 90\% confidence intervals.
 Panel (b) is analogous to Panel (a) except that it does the exercise separately for clients we classified as overconfident ($OC_i:=\mathbbm{1}(P^s_i-\widehat{P_i(X_i)}>0))$ and those we classified as not overconfident.
@@
         \begin{subfigure}{0.45\textwidth}
-        \caption{Financial cost -- Promise-forcing}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/fc_te_pro_3.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.45\textwidth}
-        \caption{Losing Pawn -- Promise-forcing}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/def_te_pro_3.pdf}
-    \end{subfigure}
-
-    \bigskip
-    \bigskip
-
-        \begin{subfigure}{0.45\textwidth}
         \caption{Financial cost -- Choice}
@@
         \includegraphics[width=\textwidth]{Figuras/def_te_pro_5.pdf}
+    \end{subfigure}
+
+    \bigskip
+    \bigskip
+
+        \begin{subfigure}{0.45\textwidth}
+        \caption{Financial cost -- Promise-forcing}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/fc_te_pro_3.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.45\textwidth}
+        \caption{Losing Pawn -- Promise-forcing}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/def_te_pro_3.pdf}
     \end{subfigure}
@@
 
-% APPENDIX TABLES
+% APPENDIX
 
@@
     \begin{subfigure}{0.65\textwidth}
-    \caption{Elapsed days to first payment}
+    \caption{Receipt for client}
         \centering
@@
     \vspace{3ex}
-    \begin{subfigure}{0.45\textwidth}
-    \caption{Elapsed days to first payment}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/Personal Promise.png}
+    \begin{subfigure}{0.65\textwidth}
+    \caption{Personal promise signed by client}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/Personal Promise2.png}
     \end{subfigure}
@@
 
-\vspace{.1in}
 \begin{figure}[H]
@@
     \begin{center}
-    \begin{subfigure}{0.5\textwidth}
+    \begin{subfigure}{0.42\textwidth}
     \caption{Appraiser/tellers inside a pawnshop}
@@
     \end{subfigure}
+        \begin{subfigure}{0.45\textwidth}
+    \caption{Pawnshop}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/empenio11.png}
+    \end{subfigure}
 
         \vspace{3ex}
-    \begin{subfigure}{0.5\textwidth}
+
+    \begin{subfigure}{0.45\textwidth}
     \caption{Pawnshop}
@@
     \end{subfigure}
-       \vspace{3ex}
-
-    \begin{subfigure}{0.5\textwidth}
+    \begin{subfigure}{0.42\textwidth}
     \caption{Lost pawns which are for sale}
@@
         \includegraphics[width=\textwidth]{Figuras/empenio3.png}
-    \end{subfigure}
-       \vspace{3ex}
-
-    \begin{subfigure}{0.5\textwidth}
-    \caption{Pawnshop}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/empenio11.png}
     \end{subfigure}
@@
     \begin{center}
-    \begin{subfigure}{.8\textwidth}
+    \begin{subfigure}{.49\textwidth}
     \caption{Gold buyer next to pawnshop 1}
@@
     \end{subfigure}
-
-    \vspace{3ex}
-    \begin{subfigure}{.8\textwidth}
+    \begin{subfigure}{.49\textwidth}
     \caption{Gold buyer next to pawnshop 1}
@@
 \end{figure}
-
-\newpage
 
@@
 
+\subsection{Surveys}
 \afterpage{
-\begin{landscape}
-
-\subsection{Surveys}
-
 \begin{table}[H]
@@
 \begin{center}
-\scriptsize{\input{./Tables/baseline_survey1.tex}}
-\end{center}
- \scriptsize 
-%\textit{Do file: } \texttt{ss.do}
+\scriptsize{\input{./Tables/transcribed.tex}}
+\end{center}
 \end{table}
-
-\begin{table}[H]
-\begin{center}
-\scriptsize{\input{./Tables/baseline_survey2.tex}}
-\end{center}
- \scriptsize 
-%\textit{Do file: } \texttt{ss.do}
-\end{table}
-
-\begin{table}[H]
-\begin{center}
-\scriptsize{\input{./Tables/baseline_survey3.tex}}
-\end{center}
- \scriptsize 
-%\textit{Do file: } \texttt{ss.do}
-\end{table}
-\end{landscape}
 }
@@
 \end{proof}
+
+\newpage
 
@@
 
-We use \cite{atheygrf} the \texttt{causal\_forest} of the \texttt{grf} library in $R$. The parameters used were:
+We use \cite{atheygrf} \texttt{causal\_forest} of the \texttt{grf} library in $R$. The parameters used were:
 \scriptsize{\textit{causal\_forest(
@@
 
-\pagebreak
 \subsection{Take up}
@@
     \end{center}
-     \scriptsize This figure reports bivariate regressions of the form $\widehat{TakeUp} = \alpha + \beta \: X_i + \epsilon_i$, where $\widehat{TakeUp}$ is the prediction using random forests.
+     \scriptsize
+      %\footnotesize{ \textit{Do file: }  \texttt{analyze\_fvp.do}}
+\end{figure}
+
+\scriptsize {
+\noindent This figure reports bivariate regressions of the form $\widehat{TakeUp} = \alpha + \beta \: X_i + \epsilon_i$, where $\widehat{TakeUp}$ is the prediction using random forests.
 The figure reports the $\beta$ coefficients for different $X_i$'s along with 95\% confidence intervals.
@@
 Panel (b) focuses on the arm where clients could chose among the promise-commitment contract and the status quo contract.
-
-      %\footnotesize{ \textit{Do file: }  \texttt{analyze\_fvp.do}}
-\end{figure}
-
-\vspace{.2in}
-\noindent Using random forests we can predict who takes up the fee-forcing contract with 85\% accuracy out of sample.\footnote{Correcting for the fact that most chose the status-quo contract using the method of SMOTE, \cite{smote} we find an accuracy rate of 75\%.} Which suggests that choice among contracts is not purely random.
-Figure \ref{interactions_takeup} in the Appendix shows that the more educated, those that report that their family typically asks for money, those that make a monthly budget of expenses, and those that ask for a remainder of their due payments (and marginally those we classify as present-biased) are more likely to chose the fee-commitment contract if given the choice.
+Using random forests we can predict who takes up the fee-forcing contract with 85\% accuracy out of sample.\footnote{Correcting for the fact that most chose the status-quo contract using the method of SMOTE, \cite{smote} we find an accuracy rate of 75\%.} Which suggests that choice among contracts is not purely random.
+This figure shows that the more educated, those that report that their family typically asks for money, those that make a monthly budget of expenses, and those that ask for a remainder of their due payments (and marginally those we classify as present-biased) are more likely to chose the fee-commitment contract if given the choice.
 The opposite holds for clients that are more economically vulnerable (can barely pay for food, electricity, etc) and those that report being more stressed.
+}
 

### 2020-06-18 MATLAB/V2_beta.m

@@ -1,0 +1,58 @@
+function [V, pp, d] = V2_beta(y,m,parms)
+% Value function at time period t=2
+beta_belief = parms.beta_belief; delta = parms.delta; 
+val = parms.v; r =parms.r; mu = parms.mu; sigma = parms.sigma;
+
+% Sample to compute V3:
+y_prime = exp(mu + sigma.*randn(parms.rep,1));
+
+% Function to optimize
+% VV1 = @(p) beta*delta*log(y-p) + ...
+%     mean(V3(y_prime,(1+r).*(m-p),parms));
+%%
+
+if (m == 0)
+   % Value function
+    V = beta_belief*delta*(log(1+val)+log(y)) + ...
+        beta_belief*delta^2*log(1+val) + ...
+        beta_belief*delta^2*mu;
+    pp = zeros(length(y),1);
+    
+else
+    % Discretize grid for policies
+    mn = min(m,y);
+    mx = max(mn);
+    p = linspace(0,mx,parms.gridsize);
+
+    Omega = (1+val)/val;
+    % Value function
+    VV = beta_belief*delta*log(y-p) + ...
+        beta_belief*delta^2*log(1+val).*(1-logncdf((1+r)*(m-p)*Omega,mu,sigma)) + ...
+        beta_belief*delta^2*mean(log(y_prime-(1+r).*(m-p).*(y_prime >= (1+r)*(m-p)*Omega)));
+
+    V = zeros(length(y),1); ind = zeros(length(y),1);
+    for i=1:length(y)
+        % Optimal int point value
+        [V(i),ind(i)] = max(VV(i,imag(VV(i,:))==0));
+    end
+
+    % Optimal int point policy
+    pp = p(ind)';
+
+    %% 
+
+    % Optimum for paying debt at this time period if possible
+    opt = -Inf*ones(length(y),1);
+    opt(m<=y) = beta_belief*delta.*(log(1+val) + log(y(m<=y)-m)) + ...
+            beta_belief*delta^2*(log(1+val) + mu);
+
+
+    %% Optimum values
+    ind_change = V<opt;
+    V(ind_change) = opt(ind_change); pp(ind_change) = m;
+end
+
+    % Paid loan
+    d = (pp==m);
+end
+

### 2020-06-18 MATLAB/lognormal_fit.m

@@ -1,0 +1,48 @@
+clear all 
+close all
+clc
+FC = readmatrix('../_aux/fc_admin_disc.csv');
+log_FC = log(FC); 
+
+%% MLE
+[pHat,pCI] = lognfit(FC,0.05);
+params.mu = pHat(1); params.sigma = pHat(2);
+[~,pCov] = lognlike(pHat,FC);
+
+%% Empirical/Theoretical CDF
+x_values = linspace(min(FC),max(FC));
+[p,pLo,pUp] = logncdf(x_values,params.mu,params.sigma,pCov);
+
+figure;
+hold on
+ecdf = cdfplot(FC);
+plot(x_values,p,'r-')
+plot(x_values,pLo,'r--')
+plot(x_values,pUp,'r--')
+legend('Empirical CDF','Log-normal CDF','Hi','Lo','Location','best')
+hold off
+
+%% Kolmogorov-Smirnov / Anderson-Darling
+log_FC_std = (log_FC-params.mu)/params.sigma;
+[h1,p1] = kstest(log_FC_std);
+[h2,p2] = adtest(log_FC);
+
+%% Expected Utlity
+eta = linspace(0,1,1000);
+U = eu(eta,params.mu,params.sigma);
+U1 = eu(eta,pCI(1,1),pCI(1,2)); U2 = eu(eta,pCI(1,1),pCI(2,2));
+U3 = eu(eta,pCI(2,1),pCI(1,2)); U4 = eu(eta,pCI(2,1),pCI(2,2));
+
+
+figure;
+hold on
+p = plot(eta,U,'b-');
+p1 = plot(eta,U1,'b--');
+p2 = plot(eta,U2,'b--');
+p3 = plot(eta,U3,'b--');
+p4 = plot(eta,U4,'b--');
+xlabel('RRA degree');
+ylabel('FC');
+hold off
+
+

### 2020-06-18 MATLAB/p3.m

@@ -1,0 +1,6 @@
+function [p] = p3(y,m,parms)
+%Optimal policy at time period t = 3
+
+p = m.*((y >= m.*(1+parms.v)./parms.v));
+end
+

### 2020-06-18 MATLAB/value_func.m

@@ -1,0 +1,15 @@
+function [z] = value_func(p, y, v, shocks, parms)
+% Value function
+
+if (p >= m)
+    val = parms.V;
+else
+    val = 0;
+end
+
+% Interpolation
+v_interp = chebfun(v,[0,1],'equi');
+z = val + log(y-p) + parms.delta*mean(v_interp(parms.mu + parms.rho*y + shocks));
+
+end
+

### 2020-06-18 RScripts/best_tree.R

@@ -1,0 +1,227 @@
+#' Function that takes in a list of samples, with the corresponding Y values, and calculates the r_loss, assuming a regression tree.
+#' If a leaf only has one sample, then we return the Y value squared. We choose this value because
+#' we don't want to return 0, which will encourage the tree to keep leaves with 1 sample, but we also
+#' don't want to return a huge value, which will force the tree to never have leaves with 1 sample, even if
+#' the sample is an outlier. But of course we could choose to return something else when there is only
+#' one sample in the leaf, if it makes more sense.
+#'
+#' @param Y The Y values
+#' @param samples The samples on which to calculate the r_loss.
+#' @param W.orig W values that indicate treatment; used for causal forest.
+#' @param W.hat Fitted W.hat for causal forest
+#' @param M.hat M.hat for causal forest
+#' @param Tau.hat Fitten tau values for causal forest
+#'
+#' @return The r_loss of the samples.
+#'
+#' @export
+r_loss <- function(Y, samples, W.orig = NULL, W.hat = NULL, M.hat = NULL, Tau.hat = NULL) {
+  size <- length(samples)
+  if (size == 1) {
+    return(Y[samples[1]]^2)
+  }
+  if (is.null(W.orig)) {
+    unscaled_spread <- sum((Y[samples] - mean(Y[samples]))^2)
+    output <- unscaled_spread * (size^2)/((size - 1)^2)
+  } else {
+    unscaled_spread <- sum((Y[samples] - M.hat[samples] - (W.orig[samples] - W.hat[samples])*mean(Tau.hat[samples]))^2)
+    output <- unscaled_spread * (size^2)/((size - 1)^2)
+  }
+  return(output)
+}
+
+
+
+#' Function that takes as input a tree, and calculates the r_loss of a specific node, specified by the index.
+#'
+#' @param Y The Y values of the data
+#' @param tree The tree on which to calculate r_loss
+#' @param index The index of the specific node whose r_loss we want
+#' @param cost This is the cost that we pay if we do not prune the tree.
+#' @param prune_info This is list that corresponds to nodes of the tree. Each element keeps track of the samples in the node and whether the node is a leaf in the pruned tree.
[…]

### 2020-06-18 RScripts/fc_te_grf.R

@@ -1,0 +1,86 @@
+library(tidyverse)
+library(grf)
+library(ggplot2)
+
+# SET WORKING DIRECTORY
+setwd('C:/Users/xps-seira/Dropbox/Apps/ShareLaTeX/Donde2019')
+#setwd("C:\\Users\\Ricardo\\Documents\\SEIRA\\donde2019")
+set.seed(5289374)
+
+
+
+  data_in <- read_csv('./_aux/fc_te_heterogeneity.csv')
+  
+  
+  require("dplyr")
+  
+  data_train <- data_in %>% 
+    filter(insample == 1) 
+  data_train_fee <- subset(data_train, data_train$fee_arms == 1)
+  data_train_nofee <- subset(data_train, data_train$fee_arms == 0)
+  
+  
+  data_test <- data_in %>% 
+    select(-c(fc_admin_disc, fee_arms, prenda, insample))
+  data_test_tau <- data_in %>% 
+    select(-c(fc_admin_disc, prenda, insample))
+  
+  ###################################################################  
+  ###################################################################  
+  
+  
+  # PREPARE VARIABLES
+  X <- select(data_train,-c(fc_admin_disc, fee_arms, prenda, insample))
+  Y <- select(data_train,fc_admin_disc)
+  W <- as.numeric(data_train$fee_arms == 1)
+  
+  X_full <- select(data_in,-c(fc_admin_disc, fee_arms, prenda, insample))
+  Y_full <- select(data_in,fc_admin_disc)
+  W_full <- as.numeric(data_in$fee_arms == 1)
+  
+  X_fee <- select(data_train_fee,-c(fc_admin_disc, fee_arms, prenda, insample))
+  Y_fee <- as.numeric(data_train_fee$fc_admin_disc)
+  X_nofee <- select(data_train_nofee,-c(fc_admin_disc, fee_arms, prenda, insample))
+  Y_nofee <- as.numeric(data_train_nofee$fc_admin_disc)
+  
+  ###################################################################  
+  ###################################################################  
+  
+
+  # ESTIMATE MODEL
+
+  # Causal Forest
+  tau.forest = causal_forest(
+    X = model.matrix(~., data = X), 
+    Y = data.matrix(Y), 
+    W = W,
+    honesty = TRUE)
+  
+  tau.forest.full = causal_forest(
+    X = model.matrix(~., data = X_full), 
+    Y = data.matrix(Y_full), 
+    W = W_full,
[…]

### 2020-06-18 RScripts/old/contrf_nochoice.R

@@ -1,0 +1,54 @@
+library(tidyverse)
+library(grf)
+library(ggplot2)
+
+# SET WORKING DIRECTORY
+setwd('C:/Users/xps-seira/Dropbox/Apps/ShareLaTeX/Donde2019')
+#setwd("C:\\Users\\Ricardo\\Documents\\SEIRA\\donde2019")
+set.seed(5289374)
+
+
+data_in <- read_csv('./_aux/heterogeneity_grf.csv')
+
+require("dplyr")
+data_frame <- data_in %>%
+  filter(data_in[,"pro_2"] == 1 | data_in[,"pro_2"] == 0) %>%
+  select(-c( pro_2, pro_3, pro_4, pro_5, pro_6, pro_7, pro_8, pro_9, fecha_inicial,
+             des_c, sum_p_c, fc_admin, fc_admin_disc, fc_survey,   num_p,  sum_porcp_c, mn_p_c, mn_pdisc_c,
+             dias_al_desempenyo, reincidence), pro_2, des_c ) %>%
+  drop_na()  
+  
+  
+# PREPARE VARIABLES
+X <- select(data_frame,-c(des_c, pro_2,NombrePignorante, prenda))
+Y <- select(data_frame,des_c)
+W <- as.numeric(data_frame[,"pro_2"] == 1)
+  
+# ESTIMATE MODEL
+tau.forest = causal_forest(
+  X = model.matrix(~., data = X), 
+  Y = data.matrix(Y), 
+  W = W,
+  honesty = TRUE)
+  
+
+
+# Estimate treatment effects for the test data using out-of-bag prediction.
+data_test <- data_in %>%
+  filter(data_in[,"pro_4"] == 1 | data_in[,"pro_4"] == 0 | data_in[,"pro_5"] == 1) %>%
+  select(-c( pro_2, pro_3, pro_4, pro_5, pro_6, pro_7, pro_8, pro_9, fecha_inicial,
+             des_c, sum_p_c, fc_admin, fc_admin_disc, fc_survey,   num_p,  sum_porcp_c, mn_p_c, mn_pdisc_c,
+             dias_al_desempenyo, reincidence, NombrePignorante)) %>%
+  drop_na()    
+
+X.test <- select(data_test,-c(prenda))
+
+tau_hat_oob = predict(tau.forest,  model.matrix(~., data = X.test), estimate.variance = TRUE)
+
+data.out <- cbind(data_test$prenda,tau_hat_oob$predictions,
[…]

### 2020-06-18 RScripts/pfv_pred_hte.R

@@ -1,0 +1,53 @@
+library(tidyverse)
+library(grf)
+library(ggplot2)
+
+# SET WORKING DIRECTORY
+setwd('C:/Users/xps-seira/Dropbox/Apps/ShareLaTeX/Donde2019')
+set.seed(5289374)
+options(digits=18)
+
+rf_predict <- function(data_in,take.up,nme) {
+  
+  require("dplyr")
+  data_train <- data_in %>% 
+    filter(insample == 1) 
+
+  data_test <- data_in %>% 
+    select(-c(take.up, nombrepignorante, prenda, insample, tau_hat_oobpredictions))
+###################################################################  
+###################################################################  
+
+    
+  # PREPARE VARIABLES
+  X <- select(data_train,-c(take.up, nombrepignorante, prenda, insample, tau_hat_oobpredictions))
+  W <- as.numeric(data_train[,take.up] == 1)
+
+###################################################################  
+###################################################################  
+  
+  
+  # ESTIMATE MODEL
+  pred.forest = regression_forest(X, W)
+  rf_pred = predict(pred.forest,data_test)$predictions
+  hist(rf_pred, xlab = "predictions")
+  
+  data.out <- add_column(data_in, rf_pred)
+  filename <- paste("_aux/pred_",nme,".csv", sep="") 
+  write_csv(data.out,filename)
+}
+
+#####################################################
+
+#RF Predictions of no-choice arm
+for (arm in c("pro_2")) {
+  for (pred in c("pago_frec_vol_fee")) {
+    for (effect in c("def_c", "fc_admin_disc")) {
+      filename <- paste("_aux/",arm,"_",pred,"_",effect,".csv", sep="")
+      data <- read_csv(filename)
+      outname <- paste(arm,"_",pred,"_",effect,sep="")
+      rf_predict(data,pred,outname) 
+    }
+  }
+}
+

### 2020-08-14 main.tex
appendix B and updates in paper

@@
 
+%para esconder columnas en tablas (enrique)
+\usepackage{array}
+\newcolumntype{H}{>{\setbox0=\hbox\bgroup}c<{\egroup}@{}}
+
 %\myexternaldocument{OA}
@@
 
-\title{Private paternalism and the limits of self commitment  \thanks{We want to thank Craig McIntosh and Mauricio Romero for advice and encouragement.
-We want to thank also Ricardo Olivares for excellent research assistance and Erick Molina help with formatting.
-Jose Maria Barrero, Emilio Gutierrez, Aprajit Mahajan, Matt Rabin, and seminar participants at ITAM provided very valuable feedback.}}
+\title{The limits of self-commitment and private paternalism \thanks{We want to thank Craig McIntosh and Mauricio Romero for advice and encouragement.
+We want to thank also Ricardo Olivares for excellent research assistance and Erick Molina's help with formatting.
+Jose Maria Barrero, Andrei Gomberg, Emilio Gutierrez, David Laibson, Aprajit Mahajan, Matt Rabin, Charlie Sprenger, and seminar participants at ITAM provided valuable feedback.}}
 \author{Isaac Meza \and Joyce Sadka \and Enrique Seira   \thanks{Meza: University of California at Berkeley, isaac.meza@berkeley.edu; Sadka: ITAM, jsadka@itam.mx;  
-Seira: ITAM, enrique.seira@itam.mx} }
+Seira: ITAM, enrique.seira@gmail.com} }
 \date{This draft:  \today \\[2 cm]}
@@
 \maketitle
+\thispagestyle{empty}
 \begin{abstract}
@@
 
-We study the benefits of ``private paternalism'' in the understudied but important pawnbroker context.
-We show that forcing people into commitment contracts with financial penalties for not paying on time \textit{decreases} their (fee-including) financial cost by 9.5\%, increases the likelihood of recovering their pawn by 25\%, and increases the likelihood of repeat business by 55\%.
-Using the recent machine learning methods for estimating heterogeneous treatment effects, we calculate that more than 90\% clients would reduce their financing cost with the commitment contract, however 10\% choose it.
-Using personal promises instead of fees as commitment triples take-of but has no effects.
+In the context of pawnbroker lending, we show that forcing people into commitment contracts with financial penalties for not paying on time \textit{decreases} their (fee-including) financial cost by 9.5\%, increases the likelihood of recovering their pawn by 25\%, and increases the likelihood of repeat business by 55\%.
+Using machine learning methods for estimating heterogeneous treatment effects, we find that more than 90\% clients would reduce their financing cost with the commitment contract, however only 10\% choose it.
+Relying on personal promises instead of fees as commitment triples take-up but has no effects on outcomes.
 
@@
 
-\textbf{Keywords: } Private paternalism, choice, present bias, naivete, overconfidence, commitment, pawnshop.
+\vspace{.3in}
+
+\textbf{Keywords: } Private paternalism, choice, present bias, naivete, overconfidence, commitment, heterogeneous treatment effects.
 
@@
 \newpage
+
+\pagenumbering{arabic}
 
@@
 
-\cite{Laibson2018} recently noted that many institutions ---firms, schools, financial contracts--- restrict choice using built-in incentive/commitment mechanisms which help workers, students, borrowers overcome self-control problems.
-``Firms do limit their workers' freedom with intermediate deadlines, progress reports, production targets'', schools with ``pop quizzes, classroom attendance requirements, cold calling, graded problem sets, deadlines''.
-Similarly, mortgages do so ``with a fixed repayment stream and mandatory principal repayment''.
-However he notes that these same firms shroud these forcing mechanisms and don't market their commitment features, presumably because students, workers and borrowers ``don't welcome these paternalistic\footnote{\cite{Laibson2018} defines paternalism as a policy that advances an individual's interests by restricting his or her freedom, and private paternalism as paternalism implemented by private institutions.} restrictions''.
-In this he sees an important \textit{commitment puzzle}: if clients were present biased and  sophisticated about their self control problem they should appreciate commitment features and firms should be eager to market them.
-The fact that this is not the case suggests some clients may be naive about their self control problems, and that \textit{private paternalism}  ---a policy of restricting choice implemented by private firms--- may increase clients' welfare.
-
-This paper studies private paternalism in the context of pawnbroker borrowing and finds evidence for its benefits.
-Pawnshops offer secure loans using items of personal property as collateral.
-The items pawned are called pledges or pawns.
-Pawn loans are one of the oldest forms of borrowing, and although data on their market share is scarce, anecdotal evidence suggests they are very prevalent.
-To give an example, our partner pawnshop (henceforth Lender $P$) served more than 1 million clients in the last 3 years with more than 4 million contracts.\footnote{For comparison there were approximately 2.3 million micro-finance clients in Mexico in 2009 in Mexico (\cite{Pedroza:2010}).
-We cannot be more precise on the number of total borrowers from Lender $P$ for confidentiality reasons.}  Pawn loans are interesting to study in and on themselves for this reason alone.
-But they are also interesting because regulators and practitioners view pawnbrokers as the lenders to which people in desperate need turn to.
-The regulators' concern is that the selection of clients that go to pawnshops may be particularly vulnerable, have bad debt management skills, and be more likely to have present biased preferences while being naive about it.\footnote{In 2013 Mexico's Consumer Protection Bureau (Profeco) is concerned about abuse.
+Many institutions ---firms, schools, financial contracts--- restrict choice using built-in commitment mechanisms which help workers, students, borrowers overcome self-control problems.
+For instance, mortgages restrict choice ``with a fixed repayment stream and mandatory principal repayment \citep{Laibson2018}''.\footnote{\cite{Laibson2018} also mentions that ``Firms do limit their workers' freedom with intermediate deadlines, progress reports, production targets'', and schools with ``pop quizzes, classroom attendance requirements, cold calling, graded problem sets, deadlines''.} At the same time  these same firms shroud these forcing mechanisms and don't market their commitment features, presumably because students, workers and borrowers ``don't welcome these paternalistic restrictions'' (\cite{Laibson2018}).
+\cite{Laibson2018} argues that this presents an important commitment puzzle: if clients were present biased and sophisticated about their self control problem they should appreciate commitment features and firms should be eager to market them.
+That this is not so suggests some clients may be naive about their self control problems, and that private paternalism may be beneficial.\footnote{\cite{Laibson2018} defines paternalism as a policy that advances an individual's interests by restricting his or her freedom, and private paternalism as paternalism implemented by private institutions.
+In this paper we will study the effect of restricting freedom of choice on pawn recovery and financing cost, not overall welfare.}
+
+This paper studies the benefits of restricting choice in the context of pawnbroker lending.
+Pawn loans are one of the oldest, understudied, and most prevalent forms of borrowing.
+There are more than 11,000 pawn shops across the US with 30 million clients and \$14 billion yearly revenues (in China is a 43 billion industry).\footnote{\url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.} Our partner pawn lender (henceforth Lender $P$) alone served more than 1 million clients in the last 3 years with more than 4 million contracts.\footnote{For comparison there were 2.3 million micro-finance clients in Mexico in 2009 (\cite{Pedroza:2010}).} The key characteristic of pawn loans is that the borrower leaves personal property (a pawn) as collateral in exchange of an immediate cash loan of a smaller value.
+In our case Lender $P$ only accepts gold jewelry as collateral and approves all pawns, giving cash the equivalent of 70\% of the pawn's appraised value.
+The contract stipulates a 7\% monthly interest rate charged daily, a loan term of 90 days, and the flexibility to pay back the loan at anytime before the loan is due.
+In spite of this flexibility, most people lose their pawn, and among those that recover it almost all of them pay in the last days, just before the loan elapses.\footnote{In the US default is also high at 15\% (\url{https://tinyurl.com/yc2x5bjf}).}
+
+% About 85\% of borrower lose their pawn\footnote{https://nationalpawnbrokers.org/2017/06/19/pawnbroking-around-the-world/}
+
+%different prices: https://priceonomics.com/the-economics-of-pawn-shops/
+
+% pawnshops help the poor https://tinyurl.com/y9qr43j8
+%, with annual percentage rates above or close to 200\%.
+
+% Limite statustics and knowledge of pawnshops. World bank mentions them in passing: https://tinyurl.com/ydgob8pv
+
+%Borrowers typically turn to these loans when in desperate need to pay for an emergency.
+The vulnerability of these borrowers has sparked regulator's interest.\footnote{In 2013 Mexico's Consumer Protection Bureau (Profeco) is concerned about abuse.
 It forced Pawnshops to be more transparent in their pricing, register their contracts with them and issued regulation to protect clients.
 Congress has enacted laws in this regard.
-\url{http://www.diputados.gob.mx/LeyesBiblio/ref/lfpc.htm}.}
-
-Indeed, using a survey conducted by us in branches of Lender $P$, we document some evidence consistent with regulators' concerns: while pawnshop clients predict they will recover their pawn with 93\% probability on average, in reality only 40\% of them do, suggesting naivete.
-Even conditional on paying a positive amount towards pawn recovery, 53\% lose their pawn and their payment.
+\url{http://www.diputados.gob.mx/LeyesBiblio/ref/lfpc.htm}.} One concern is that borrowers selecting into these loans may exhibit particularly strong behavioral biases.
+%Using a survey conducted by us in branches of Lender $P$, we indeed document some evidence consistent with these concerns: while pawnshop clients predict they will recover their pawn with 93\% probability on average, in reality only 40\% of them do, suggesting naivete.
+%Even conditional on paying a positive amount towards pawn recovery, 53\% lose their pawn and their payment.
 In our survey 69\% report self-control problems saying they often fall into temptation spending.
@@
 
-Consistent with little client sophistication, Lender $P$ offers a very simple but highly collateralized contract.
-It only accepted gold jewelry as collateral and approves all gold pawns, giving in exchange in cash the equivalent of 70\% of the weighted gold value.
+\begin{comment}
+Lender $P$ offers a very simple but highly collateralized contract.
+It only accepts gold jewelry as collateral and approves all gold pawns, giving in cash the equivalent of 70\% of the weighted gold value.
 The contract stipulates a 7\% monthly interest rate charged daily, and a loan term of 90 days plus 15 grace days to pay the principal and the accumulated interest.
@@
 %This lets us focus more cleanly on behavioral economics aspects.
-
-To study the benefits of private paternalism, we implemented a relatively large randomized control trial with close to 10,000 pawnshop clients in 6 branches of Lender $P$ in Mexico City.
+\end{comment}
+
+We implemented a large randomized control trial with close to 10,000 pawnshop clients in 6 branches of Lender $P$ in Mexico City.
 We answer five main questions using this experiment.
 First, would clients benefit  ---in terms of recovering their pawn and in terms of incurring in lower financing costs---  from having a frequent (monthly) payment commitment contract \textit{forced} on them, instead of the current 3-month pay-when-you-want contract?
-That is, we are asking whether \textit{charging} them a 2\% late payment fee for not paying a monthly installment on time can actually \textit{decrease} total fee-inclusive financing cost.
+That is, we are asking whether \textit{charging} them a 2\% late payment fee for not paying a monthly installment on time can actually \textit{decrease} total (fee-inclusive) financing cost.
 Second, would there be demand for such a frequent payment commitment contract vis-a-vis the status quo one if given choice?
-Notice that any payment profile implemented in the commitment contract can be replicated by the borrower under the status quo contract, but the later affords more flexibility to respond to income shocks without incurring in fees.
+Any payment profile implemented in the commitment contract can be replicated by the borrower under the status quo contract, but the later affords more flexibility to respond to income shocks without incurring in fees.
 Third, what types of clients would demand these contracts that restrict choice?
 Fourth, are late payment fees key to provide commitment or would a non-pecuniary but salient personal promise to pay provide a cost-reducing mix of commitment vs flexibility?
-A large and important lab experiment literature suggest that promises change behavior significantly in laboratory settings, but we know little about their effect on the field in natural environments.\footnote{Some important papers in this space are \cite{PromisesPartnerships}, \cite{Vanberg}, \cite{Belot2010}, \cite{WhyDoPromises}, \cite{FurtherPromises}, \cite{Ismayilov2017}.
-There is also some actual policy around using promises for loans: the government Mexico has created a program called ``Loans on your word'' for uncollateralized borrowing (\url{http://tiny.cc/yfmnmz}).
-There is little information about them though.} Finally and importantly, is \textit{giving choice} among contracts better than forcing them into payment-commitment contracts in terms of minimizing financing costs incurred and the likelihood of recovering their pawn?
+Promises change behavior significantly in laboratory settings, but we know little about their effect in natural environments.\footnote{Some papers in this space are \cite{PromisesPartnerships}, \cite{Vanberg}, \cite{Belot2010}, \cite{WhyDoPromises}, \cite{FurtherPromises}, \cite{Ismayilov2017}.
+There is also some actual policy around using promises for loans: the government Mexico has created a program called ``Loans on your word'' for uncollateralized borrowing (\url{http://tiny.cc/yfmnmz}), but unfortunately there is little information about them.} Finally, is \textit{giving choice} among contracts better than forcing them into payment-commitment contracts in terms of minimizing financing costs incurred and the likelihood of recovering their pawn?
 Or on the contrary, is it better to force the commitment contract
@@
 The first one involves a group of clients that were given only the status quo contract (henceforth the \textit{status-quo forcing group}).
-The second arm (\textit{fee-forcing group}) was given only a monthly payment commitment contract, which stipulated that clients had to pay 1/3 of their loan plus accumulated interest in each of the 3 months of the term length.
+The second arm (\textit{fee-forcing group}) was given a monthly payment commitment contract, which stipulated that clients had to pay 1/3 of their loan plus accumulated interest in each of the 3 months of the term length.
 Failing to do this would result in a fee of 2\% of the amount due that month.
@@
 
-We find that forcing clients into frequent payment commitment contracts causes them on average to save on financing cost and to recover their pawn more.
-The effects are large: financing cost decreases by 9.5\% on average, while the likelihood of recovering their pawn increases by 25\%.
-Results are robust to including in the cost definition transport costs of going to the branch plus losing a day's wage for each visit.
-Importantly, the benefits are distributed broadly: the whole distribution of treatment effects shows cost savings.
-The most economically vulnerable, those that report being stressed, and those that asked for a reminder at baseline, experience the largest financial cost savings.
-Those we classify as present biased and those that requested a reminder at baseline experience the largest effects on pawn recovery.
+Forcing clients into frequent payment commitment contracts causes them on average to save on financing cost and to recover their pawn more.
+The effects are large: financing cost decreases by 9.5\% on average, from \$3161 to \$2857 MXN, while the likelihood of recovering their pawn increases by 25\%, from 43\% to 54\%.
+Results are robust to including transport costs of going to the branch plus losing a day's wage for each visit.
+Importantly, the benefits are distributed broadly: almost the whole distribution of treatment effects shows cost savings; however those most economically vulnerable, those that report being stressed, and those we classify as overconfident experience larger gains.
 %The commitment contract also causes payments to start 8 days earlier and be 16\% more frequent, compared to the control group.
 Treatment effects are concentrated on the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery.
-It seems that the fee-commitment contract induces people who would otherwise pay something towards recovery, to pay more and faster and thus recover their pawn more at a cheaper financial cost.
-Finally, we find that borrowers assigned to the forced fee-commitment contract are 5pp (55\% of the mean) more likely to be repeat costumers than the control group, suggesting that they themselves liked the commitment contract more after experiencing it.
+The fee-commitment contract induces people who would otherwise pay something towards recovery, to pay more and faster and thus recover their pawn more at a cheaper financial cost.
+Finally, borrowers assigned to the forced fee-commitment contract are 5 percentage points (55\% of the mean) more likely than the control group to ask for another loan in the future, suggesting that they liked the commitment contract more after experiencing it.
 
@@
 
-In spite of these estimated benefits for all clients, their actual demand for the fee-commitment contract is low.
+In spite of these estimated benefits for almost all clients, actual demand for the fee-commitment contract is low.
 Only 10\% of the group offered a choice between the monthly payment fee-commitment contract and the status-quo one chose the former.
-This is not likely driven by misunderstanding the (already simple) contract.\footnote{We had two ITAM students in each of the experiment's branches every day for all branch opening hours to carefully explain the contracts; material was developed to explain the differences among the two contracts, and subjects spelled back to our ITAM assistants the loan differences.
-Furthermore take up is systematically predicted by baseline covariates, %\footnote{We find that the more educated, those that report that their family typically asks for money, those that make a monthly budget of expenses, and ask for a remainder to payment (and marginally those we classify as present-biased) are more likely to chose the fee-commitment contract if given the choice.
-The opposite holds for those that are more vulnerable (can barely pay for food, electricity, etc) and those that report being more stressed.},
-making it less likely that it is just random mistakes.} Low demand for commitment is consistent with a large part of the literature of the literature (\cite{Laibson2015}, \cite{Laibson2018}, \cite{John}, \cite{Ted}, \cite{Rabin2018}).%\footnote{\cite{Alcohol} and \cite{Kremer} are some of the few instances of high demand for commitment.
+This is not likely driven by misunderstanding the (already simple) contract.\footnote{We posted two persons in each of the experiment's branches every day for all branch opening hours to carefully explain the contracts; material was developed to explain the differences among the two contracts, and subjects spelled back to our team the loan differences.
+Furthermore take up is systematically predicted by baseline covariates, making it less likely that it is just random mistakes.} Low demand for commitment is consistent with a large literature (\cite{Laibson2015}, \cite{Laibson2018}, \cite{John}, \cite{Ted}, \cite{Rabin2018}).
+%\footnote{\cite{Alcohol} and \cite{Kremer} are some of the few instances of high demand for commitment.
 \cite{Alcohol} speculates that this difference may be explained by their subjects having more experience with their self control problem.
@@
 We find that experience does not predict positive take up in our sample.}
-\cite{Laibson2015} shows that the lost flexibility resulting from a commitment contract can severely limit take-up when agents are naive about their self control, even though commitment could be welfare improving for them.
-We estimate zero average treatment effects of the \textit{fee-choice} arm on financial cost and on pawn recovery and throughout the quantile distribution.
+%\cite{Laibson2015} shows that the lost flexibility resulting from a commitment contract can severely limit take-up when agents are naive about their self control, even though commitment could be welfare improving for them.
+Owing to this low take-up, we estimate zero average treatment effects of the \textit{fee-choice} arm on financial cost and on pawn recovery and throughout the quantile distribution.
 
@@
 
-How much money is left on the table by the prevalence of the status-quo choice?
+Combining the forcing and the choice arms ---a unique feature of our experiment--- allows us to estimate the counterfactuals to answer the following question how much money is left on the table by the prevalence of the status-quo choice?
 We calculate that about 80\% of clients in the fee-choice group chose contracts that induced \textit{higher} financial cost.
-On average they spend an extra \$238 pesos, close to 11\% of the average loan value.
+On average they spend an extra \$238 MXN, close to 11\% of the average loan value.
 In particular 92\% of those that chose the status-quo contract would have been better in the fee-commitment contract, while only 8\% of those who chose the fee-commitment contract would have been better in the status-quo one.
 This suggests that forcing clients into commitment contacts (i.e.
-private paternalism) may be welfare increasing for the overwhelming majority of clients.
-
-Inspired by a significant lab experiment literature on the effects of promises on behavior, we also implemented a ``psychological commitment'' in the form of a salient promise to pay.
+private paternalism) may be beneficial for the overwhelming majority of clients.
+After seeing our results Lender $P$ introduced frequent payment contracts in their loans portfolio.
+
+We want to clarify that in the paper we are using the word ``paternalism'' in a restricted sense, meaning only that a large majority of clients would incur in lower financial costs from being forced into commitment contracts instead of letting them chose.
+We are not making claims about overall welfare which is a slippery concept once we accept the possibility of biased beliefs and preferences.
+
+Inspired by a significant lab experiment literature on the effects of promises on behavior, and by research showing that a small fee could drastically reduce demand for commitment of naive present-biased borrowers (\cite{Laibson2015}), we implemented a ``psychological commitment'' in the form of a salient promise to pay.
 \cite{PromisesPartnerships}, \cite{FurtherPromises}, \cite{Vanberg}, and \cite{Ismayilov2017} find that the ability to make a promise about behaving a certain way makes the individual more likely to adhere to the promised behavior.
 %and also induces trusting behavior by the recipients of the promise.
-To do this we implemented two other treatment arms.
+To measure the causal effect of promises we implemented two other treatment arms.
 A \textit{promise-forcing} arm exactly analogous to our \textit{fee-forcing arm} except that instead of telling them that there is a fee if they don't pay on time, we made borrowers promise that they would pay one third of the amount in each of the 3 months, and told them that if they didn't they would have broken their promise and failed their word.
 Because salience is key we made them sign a (non-legally binding) personal promise and emphasized we were counting on them to keep their promise.
-A final arm (\textit{promise-choice arm}) gave clients the opportunity to choose between the \textit{Promise-forced} contract and the \textit{Status-quo} contract.
+A final arm (\textit{promise-choice arm}) gave clients the opportunity to choose between the \textit{Promise} contract and the \textit{Status-quo} contract.
 
@@
 This difference between both choice arms suggests that clients are indeed understanding and taking into account the contractual parameters in their choice, and that the fee commitment was probably too strong from their point of view.
-Second, the \textit{Promise-forcing} contract had zero effects on average and throughout the distribution on financing cost and pawn recovery.
-The same is true for the \textit{Promise-choice arm}.
+In spite of this much higher take-up, the \textit{Promise-choice arm} had no effect on outcomes on average, or even for those who selected into promising.
+Second, being forced in to the \textit{Promise} contract also had zero effects on average and throughout the distribution on financing cost and pawn recovery.
 %\footnote{There is a decrease in financial cost in the 50th and 75th quantiles in the forced promise-commitment arm however.}
 Promises did not provide enough commitment so as to be reflected in behavior.
-This is true both imposed promises and chosen promises.
-Contrary to lab evidence, people did not keep the promise, at least the way it could be implemented in the field.
-
-We contribute to several strands of literature.
+
+This paper contributes to several strands of literature.
 First, to the broad literature on commitment demand.
-A significant literature has shown that demand for commitment exists but is somewhat low in some contexts (\cite{Ashraf}, \cite{Gine}, \cite{Ted}), and high in others (\cite{Kremer},  \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}).
-We add to this literature by showing that very small fees are enough to drastically reduce demand for commitment, even when commitment is beneficial for almost everybody in our sample, and that softer commitments in the form of non-pecuniary personal promises elicit higher demand.\footnote{Our fees are 16 times smaller than than those of \cite{John} as a fraction of the loan/goal, and five times smaller converting peso values using exchange rates.} Second, two recent papers show that among those who demand commitment, the extent of commitment needed is underestimated (\cite{Ted}, \cite{John}) and that subjects can hurt themselves by self-imposing too week a commitment.
-We contribute in design ---by not allowing choice of the extent of commitment--- but also on how we infer the underestimation of the value of commitment by subjects.
-While these two papers infer too low commitment from subjects failing to reach the goal ex-post, we infer it by quantifying forgone personalized treatment effects ex-ante.
+A significant literature has shown that demand for commitment exists but is somewhat low in some contexts (\cite{Ashraf}, \cite{Gine}, \cite{Ted}, \cite{Royer}, \cite{Sprenger}), and high in others (\cite{Kremer},  \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}, \cite{Pascaline}).
+We add to this literature by showing that very small fees are enough to drastically reduce demand for commitment, even when commitment is beneficial, and that softer commitments in the form of non-pecuniary personal promises elicit higher demand.\footnote{Our fees are 16 times smaller than than those of \cite{John} as a fraction of the loan/goal, and five times smaller converting peso values using exchange rates.} Second, \cite{Ted} and \cite{John} show the extent of commitment needed is underestimated even among those that buy it, and that subjects hurt themselves by self-imposing too weak a commitment in the intensive margin.
+We contribute in design by not allowing choice of the extent of commitment, and methodologically by inferring subjects underestimation of the value of commitment ex-ante from forgone treatment savings, instead of from subjects failing to reach their goal ex-post.
 Third, we focus on an important new context: pawnshop borrowing.
-Pawnshop borrowing is extremely prevalent in developing countries and very worrisome to regulators, yet severely understudied.
+Pawnshop borrowing is extremely prevalent in developing countries and very worrisome to regulators, yet severely understudied.\footnote{The World Bank's CGAP recognizes the importance of pawnshop borrowing worldwide but provides no statistics or analysis on it: \url{https://tinyurl.com/ydgob8pv}.}
 
 Fourth, we study \textit{both} causal effects and selection into frequent payment commitment loan contracts.
-\cite{Ghatak} state that ``high-frequency repayment, a feature in nearly all microfinance contracts, has been largely overlooked''.\footnote{\cite{LittleAtAtime} also note that ``it is especially surprising that there is so little analytical discussion of the incentive effects of the installment system''.} This paper fills part of this gap.
-\cite{Pande} study the effect of installment payment frequency on loan default and (surprisingly given their prevalence and the literature above) find null effects.
-\cite{Murdoch} study selection into frequent payment microfinance loans, conjecturing that ``such repayment structure is potentially beneficial in fostering discipline among present-biased borrowers'' and may explain why borrowers choose it.
-In contrast to \cite{Pande} we find strong effects of payment frequency on decreased default.\footnote{Possibly because there are high levels of default in our context and not in theirs and because we have more statistical power from a larger sample and individual level randomization.} \cite{Murdoch}  show that a robust positive correlation exists between displaying present biased preferences in surveys and selecting into microfinance ---which they interpret as being due to high demand for the discipline of frequent payments--- acknowledging that the ``interpretation is suggestive...
+\cite{Ghatak} state that ``high-frequency repayment, a feature in nearly all microfinance contracts, has been largely overlooked''.
+%\footnote{\cite{LittleAtAtime} also note that ``it is especially surprising that there is so little analytical discussion of the incentive effects of the installment system''.}
+This paper fills part of this gap.
+Studying causal effects of installment payment frequency \cite{Pande} find null effects loan default, a surprising result given the prevalence of frequent payment contracts.
+In contrast  we find strong effects of payment frequency on decreased default.\footnote{There are many differences in context between the papers which may explain the different result.
+\cite{Pande} focus on group lending with very little default to start with (less than 1\%), while in our case almost half of loans end in default.
+We also have a larger sample and we focus on individualized loans, which may afford us stronger statistical power to detect effects.} Our result is consistent with \cite{Field} who show that delaying payment in microfinance loans increases default.\footnote{\cite{Craig} use the discipline of regular loan repayments in microfinance to remind people to save and make a savings plan, and find large increases in savings.} On the other hand, studying selection into frequent payment microfinance loans, \cite{Murdoch} conjecture that ``[frequent installment payment] structure is potentially beneficial in fostering discipline among present-biased borrowers'' and may explain why borrowers choose it.
+They show that a robust positive correlation exists between displaying present biased preferences in surveys and selecting into microfinance, which they interpret as being due to high demand for the discipline imposed by frequent payments.
+However they acknowledge that this ``interpretation is suggestive...
 and needs to be confirmed by studies that establish causal links''.
-Our experimental test of this causal link rejects that most people like and demand frequent payments (at least in our context).
-In contrast to \cite{Murdoch} we can isolate the pure effect of payment frequency on demand by randomly changing just this aspect of the contract.
+Our experimental \textit{is} a test of this causal link.
+We can isolate the pure effect of payment frequency on demand by randomly changing just this aspect of the contract.
+Our experimental results reject the hypothesis that microfinance (pawnshop) clients like and demand frequent payments, at least in our context.
+Importantly, our unique experimental design which simultaneously combines forcing and choice arms, paired with new machine learning methods to estimate heterogeneous treatment effects (\cite{atheygrf}), allows us to estimate whether there is positive or negative selection into beneficial contracts, and whether pawnshop clients forgo money by not demanding commitment.
+In consonance with what \cite{Walters} finds in another context, we find that it is not the case that those that benefit most from the contract demand it more.
+\cite{Sprenger} find a result that is similar to ours: that people how most need commitment (in our case the overconfident who show the greatest financial cost savings) are less likely to demand it.
+In contrast to \cite{Sprenger}, our context allows us to focus on money savings instead of estimated utility to proxy for benefits of commitment, a narrower but simpler measure.
+This allows us to measure effects on cost outcomes beyond take up and behavior.
+Our larger sample allow us to estimate heterogeneous treatment effects non-parametrically and perform counterfactuals this way.
+Finally, as in \cite{Rabin2018} we are able to contrasts subjects predictions of their behavior with their actual behavior, and how these map to outcomes, but we do it in a natural setting.
+
 Fifth, we also contribute to the literature on the effect of promises by testing their effect on the field.
-
-More importantly, our unique experimental design which combines forcing and choice arms, paired with new machine learning methods to estimate heterogeneous treatment effects (\cite{atheygrf}), allows us to estimate whether there is positive or negative selection into beneficial contracts, and whether pawnshop clients forgo money by not demanding commitment.
-In consonance with what \cite{Walters} finds in another context, we find that it is not the case that those that benefit most from the contract demand it more, consistent with a significant fraction of clients displaying naivete about self control problems (see \cite{Rabin2018}).
+In consonance to this literature we find that people are willing and indeed voluntarily choose to make promises.
+In contrast to lab evidence however measured behavior was unchanged by promising and people did not keep their promise.\footnote{This is of course not a refutation of this literature.
+%not least because the laboratory literature is implemented on more tightly controlled environments and focused on subtler aspects of promising, like their effects on second order beliefs and guilt aversion.
+The context is also different since
+The lab literature has focused mostly on very concrete investment games between two players and looked at the effects of promises on trust and cooperation in those games.
+However our results do provide a first piece of evidence on the limitations of using promises to change behavior in the field.}
+
+%, consistent with a significant fraction of clients displaying naivete about self control problems (see \cite{Rabin2018}).
 Our context is one in which private paternalism (\cite{Laibson2018}) could work since almost all pawnshop clients would benefit from frequent payment contract yet there it almost no demand for them.
@@
 
-The paper is organized as follows.
+%The paper is organized as follows.
 Section \ref{context} provides context and describes the data sources.
@@
 
-Lender $P$ was interested in understanding why half of their clients lost their pawn.
-Default is really in this context  compared to many papers in the microfinance literature\footnote{\cite{Pande} study of the effect of payment frequency in a context where the rate of default is close to 1\%.} It was concerned with high default rates for two reasons.
-The first is that the pawned piece may have a sentimental value to the client above of its gold value, making it inefficient for the lender to keep the piece.
-We actually find that clients report a subjective value that is almost twice the value of its gold content.
-Second, keeping the piece may lower client satisfaction and make the client less likely to return and pawn again.
-They were interested in investigating whether a frequent payment contract would increase pawn recovery and costumer satisfaction, and whether there was demand for such a contract.
+%Lender $P$ was interested in understanding why half of their clients lost their pawn.
+Default is high in this context  compared to many papers in the microfinance literature.\footnote{\cite{Pande} study of the effect of payment frequency in a context where the rate of default is close to 1\%.}
+We study a context with high borrower default.
+60\% of clients lose their pawn in a time span of 230 from the day of pawning.
+This default is likely inefficient since clients report a subjective value that is almost twice its gold value on average.
+It may also be detrimental from the lender's point of view since it may reduce the likelihood that the client becomes a return costumer, this may explain why Lender $P$ was interested in investigating whether a frequent payment contract would increase pawn recovery and costumer satisfaction, and whether there was demand for such a contract.
 
 One potential explanation for high default is that clients are really just selling their gold piece.
-This is unlikely for several reasons: (a)  the reported subjective value of the pawn is larger than the loan size for \hl{86\%} of them, (b) among those that lose their pawn 58\% paid a positive amount towards its recovery --- this can only be rationalized if they expected to recover their pawn, (c) it is typical to find gold purchasing stores close to where the pawnshops are located (see Figure \ref{GoldBuyers}) and they give more than what Lender P gives for the pawn, (d) there is a lot of engagement with the lender after pawning even for those who lost their pawn.
+This is unlikely for several reasons: (a) the reported subjective value of the pawn is larger than the loan size for 86\% of them, (b) among those that lose their pawn 58\% paid a positive amount towards its recovery and  34\% of the value of their loan (see Figure \ref{proxy_naive} in Appendix) --- this can only be rationalized if they expected to recover their pawn, (c) clients can easily sell the gold and obtain a higher amount of instant cash at gold buying stores located close to almost all our pawnshops (see Figure \ref{GoldBuyers}).
+%(d) there is a lot of engagement with the lender after pawning even for those who lost their pawn.
 On average clients that lost their pawn paid 34\% of the value of their loan, and close to 42\% of clients extended the loan for another cycle and made payments in the second cycle (see Figure \ref{proxy_naive} in Appendix).
@@
 
-Lender P's business model is very simple.
-They take gold jewelry as collateral in exchange for a fraction of money given instantly in cash.
+Lender P's business model is simple.
+They take gold jewelry as collateral in exchange for a fraction the value of the piece, in cash.
+No other collateral and no credit history checks are needed.
 The transaction takes less than 10 minutes and is conducted at the branch in person between the client and the appraiser (i.e.
@@
 The appraiser weights the gold piece and runs tests on its purity.
-Based on these he assigns a gold value to the piece, stores it as collateral, and gives 70\% of the gold value of the piece instantly and in cash to the costumer.
-The costumer signs a 2-sheet contract with the main conditions of the contract at the branch and leaves with the cash.
+Based on these he assigns a gold value to the piece, stores it as collateral, and gives 70\% of the gold value of the piece in cash to the client.
+The borrower signs a 2-sheet contract with the main conditions of the contract at the branch and leaves with the cash.
 
@@
 
-This contract was standard in the industry, the clients that pawned understood its conditions (as we verified in interviews) and still decided to pawn.\footnote{90\% of clients report in our survey they have pawned before.} Bear in mind that these clients have little or no access to other types of loans, and also that they value its convenience: the process is fast and requires no documentation or credit-history.
-Potentially they like it also because they are overconfident on average about the probability of recovering their pawn, as discussed below.
+This contract was standard in the industry, but other lenders also had contracts involving frequent installment payments.
+The clients that pawned understood its conditions (as we verified in interviews) and still decided to pawn.\footnote{90\% of clients report in our survey they have pawned before.} These clients have little or no access to other types of loans and value the convenience of pawn borrowing.
+Potentially borrowers like it also because they are overconfident about the probability of recovering their pawn, as discussed below.
 
@@
 
-We worked in 6 branches of Lender $P$ of differing size and location, although for simplicity all of them in Mexico city.
-For these 6 branches we have two types of data, administrative data and survey data we collected ourselves for the experiment.
+We worked in 6 branches of Lender $P$ of differing size and location, although for ease of implementation all of them in Mexico city.
+For these 6 branches we have two types of data, administrative data and survey data we collected for the experiment.
 
@@
 As described below, for our experiment the administrative data recorded the type of contract for that pawn.
-After the pawn happens, we follow each transaction related to that piece in the administrative data as well as when were payments made and for which amounts, whether there was default (i.e.
+After the pawn happens, we follow each transaction related to that piece in the administrative data: when were payments made and for which amounts, whether there was default (i.e.
 the client lost her pawn), and whether any late-payment fees (active for the relevant experimental arms) were imposed.
-We have this information for all the pawns that occurred in our 6 branches between August 2nd 2012 and August 13th 2013, this includes all the pawns under our experiment but also those that happened 1 month before it started and up to 8 months after it ended.
+We have this information for all the pawns that occurred in the experiment's 6 branches between August 2nd 2012 and August 13th 2013, this includes all the pawns under our experiment but also those that happened 1 month before it started and up to 8 months after it ended.
 Figure \ref{exp_description}(a) shows the timing of the experiment and our admin data coverage.
@@
 
-We had a team of ITAM student enumerators in each branch collect surveys and clearly explain the contract terms to walk-in clients.
+We had a team of enumerators in each branch collect surveys and clearly explain the contract terms to walk-in clients.
 The enumerators were inside the branch and asked clients to complete a short 5 minutes survey before going to the teller window to appraise their piece.
-The survey was necessarily short to avoid discouraging the potential clients from pawning, but at the same time it aimed to measure the following: demographics, proxies for income/wealth, education, self-control problems/present-biased preferences, experience pawning, if the family or friends commonly asked for money, how time consuming and costly was to come to the branch, the subjective probability of recovering their piece that they intended to pawn, the subjective value of their piece in money terms (for how much money would they sell it for), among others.
-We were able to survey 7,704 clients (some refused).
+The survey was short to avoid discouraging the potential clients from pawning, but at the same time it aimed to measure the following: demographics, proxies for income/wealth, education, self-control problems/present-biased preferences, experience pawning, if the family or friends commonly asked for money, how time consuming and costly was to come to the branch, the subjective probability of recovering their piece that they intended to pawn, the subjective value of their piece in money terms (for how much money would they sell it for), among others.
+We surveyed 7,704 clients (some refused).
 %\footnote{We also surveyed clients before and after the experiment, so our survey covers a larger sample that we are not using in this paper.}.
-The appendix \ref{baseline_survey} transcribes the questionnaire in English \hl{and presents summary stats}.
-Survey response rate is 57\%, the Appendix Table \ref{balance_response} shows that response is not related to admin data observables.
+The appendix \ref{baseline_survey} transcribes the questionnaire in English.
+Survey response rate is 57\%, and response is not related to admin data observables (details in Table \ref{balance_response} in the Appendix).
 
@@
 Panel A describes variables from the administrative data.
-It shows that the average loan size is \$2171 pesos (\$105 usd).
+The average loan size is \$2171 MXN (\$105 USD).
 The average number of pawns per day per branch is 33.
-Although not shown in the table, only 40\% of clients recover they pawn within 230 days.
+Although not shown in the table, only 40\% of clients recover their pawn within 230 days.
 Even those that recover their pawn tend to pay it back at the last moment, with only 17\% paying before the 90th day.
@@
 Panel B reports stats from our survey data.
-We learn that 73\% of clients are women, with an average age of 44 years; 66\% of them have completed high school or more, and 90\% have pawned before, so that our sample has mostly experienced borrowers.
+73\% of clients are women, with an average age of 44 years; 66\% of them have completed high school or more, and 90\% have pawned before, so that our sample has mostly experienced borrowers.
 Finally the subjective probability of recovery is close to 93\% on average, which contrast with the 44\% recovery that happens in reality for the pawns in the control group.
-Just by this measure borrowers seem to be highly overconfident on average (more on this below).
-It turns out that the average subjective value they report for the pieces is 3250 pesos, which is much larger than the average appraised gold value of 1950 pesos.
+Borrowers seem to be highly overconfident on average (more on this below).
+The average subjective value they report for the pieces is 3265 MXN, which is much larger than the average appraised gold value of 2171 MXN.
 This makes it inefficient for them to lose it.
 
-Since the main treatment involves making clients come to the branch to pay each month, the transaction costs of coming to the branch are important, and we ask two questions about them.
-The average time they take to come to the branch is 22 minutes, and the amount of money they spend in transport to do that is 11 pesos (\$0.60 usd).
+Since the main treatment involves making clients come to the branch to pay each month, the transaction costs of coming to the branch are important.
+The average time they take to come to the branch is 22 minutes, and the amount of money they spend in transport to do that is 11 MXN (\$0.60 USD).
 The population we are working with is economically vulnerable in the sense that 30\% of them could not pay either water, electricity \& gas or rent in the past 6 months.
@@
 
-Our main dependent variables are loan default and financial cost incurred by the borrower. Default is defined as losing the pawn. We observe directly when the piece gets appropriated by Lender $P$.
-
-We define financial cost as the discounted sum of payments toward the loan plus the value of the pawn, and subtract the subjective discounted value of the pawn when it is recovered: $Financial \; Cost_i = \sum_t \frac{P_{it}}{(1+r)^t} + Pawn \: Value_i - \frac{\text{I}(Recovered \: Pawn_i) \times Pawn \: Value_i}{(1+r)^T}$, with $t$ indexing days, $T$ is the day when the pawn is recovered, I($\cdot$) an indicator function for recovering the pawn, $r$ is a daily interest rate equivalent to a 7\% monthly interest rate.\footnote{We experimented with different interest rates with similar results.
-See section \ref{neoclasical}.} Figure \ref{fc_hist}(a) plots a histogram of this cost in pesos for loans where the pawn was recovered or lost.
-This cost is calculated for a time period of 230 days after loan origination, as 60\% of clients actually renew the loan one time.
-Of those who renew 83\% lose the pawn.
+Our main dependent variables are loan default and financial cost incurred by the borrower.
+Default is defined as losing the pawn.
+We define financial cost as the discounted sum of payments toward the loan plus the appraised value of the pawn, and subtract the appraised value of the pawn when it is recovered: $Financial \; Cost_i = \sum_t \frac{P_{it}}{(1+r)^t} + Pawn \: Value_i - \frac{\text{I}(Recovered \: Pawn_i) \times Pawn \: Value_i}{(1+r)^T}$, with $t$ indexing days, $T$ is the day when the pawn is recovered, I($\cdot$) an indicator function for recovering the pawn, $r$ is a daily interest rate equivalent to a 7\% monthly interest rate.\footnote{We experimented with different interest rates with similar results.
+See section \ref{neoclasical}.
+We also report result using the subjective value of the pawn reported by the borrower in the survey with similar results.} Figure \ref{fc_hist}(a) plots a histogram of this cost in pesos for loans where the pawn was recovered or lost.
+This cost is calculated for a time period of 230 days after loan origination, as %60\% of clients actually renew the loan one time.
+some clients renew the loan.\footnote{Figure \ref{fc_pro_2_115} reports results using the first 115 days only finding similar results.} Of those who renew 83\% lose the pawn.
 Figure \ref{fc_hist}(a) suggest that financial cost is significant, even for those that do recover their pawn.
@@
 %\hl{The difference between panel (a) and (b) arises since clients who lose their pawn tend to be those that pledge cheaper pieces.}
-We calculate an APR of \hl{177\% on average for the control group.}\footnote{The Annual Percentage Rate (for pawn $j$) is calculated as the internal rate of return $i$ such that $\sum_t \frac{P_{jt}}{(1+i)^t} + \frac{\text{I}(Default \: Pawn_j) \times Pawn \: Value_j}{(1+i)^T} - Pawn \: Value_j = 0$, where $T$ is the date the pawn was lost.}
-
+We calculate an APR of 218\% on average for the control group.\footnote{The Annual Percentage Rate (for pawn $j$) is calculated as the internal rate of return $i$ such that $\sum_t \frac{P_{jt}}{(1+i)^t} + \frac{\text{I}(Default \: Pawn_j) \times Pawn \: Value_j}{(1+i)^T} - Pawn \: Value_j = 0$, where $T$ is the date the pawn was lost.}
+
+\newpage
 \section{Experiment} \label{Experiment}
@@
 
-\noindent \textbf{Selection of branches.} Starting September 6th 2012, we implemented our experiment in 6 branches of Lender $P$.
+\noindent \textbf{Selection of branches.} Starting September 6th 2012, we implemented the experiment in 6 branches of Lender $P$.
 The branches were selected by Lender $P$ to be dispersed across Mexico city and have varying sizes.
-In four of them the experiment ran for 107 days, and in 2 of them we ran it for a shorter time to economize on data collection costs since we realized we would not be constrained by sample size.
+In four of them the experiment ran for 107 days, and in 2 of them we ran it for a shorter time to economize on data collection costs once we realized we would not be constrained by sample size.
 %Thus we eliminated \hl{the smallest} ones.
@@
 \noindent \textbf{The monthly installment contract.} For the purpose of the experiment we designed a new contract that is identical to the status quo contract in all respects except one.
-It has the same interest rate (7\% \textit{per month} which accumulates daily on outstanding debt, it has the same loan size/collateral ratio (70\%), it has the same loan term (90 days, and a grace period of 15 days), and the gold pawn gets appraised in the same way by the same appraisers.
+It has the same interest rate (7\% \textit{per month}) which accumulates daily on outstanding debt, it has the same loan size/collateral ratio (70\%), it has the same loan term (90 days, and a grace period of 15 days), and the gold pawn gets appraised in the same way by the same appraisers.
 The only difference is that it has a requirement that the client has to pay monthly: for the 3 month duration at least 1/3 of the loan value (plus accumulated interest) has to be paid before day 30th, 60th and 90th after loan disbursement.
@@
 As that paper shows doing this results in wrong choices by naive present biased consumers.
-\hl{Our fee is much smaller than the median in her} experiment as explained above.
+Our fee is much smaller than the median in her experiment as explained above.
 We also experimented with a contract where there was no pecuniary fee for paying late but where we clients made a personal promise to pay monthly.}
@@
 They were told that there were 5 different ``types of contract-days'' and that the system chose randomly which applied any given date, and that it could happen for instance that two consecutive dates had the same contract.
-They were also told that this way of operating was in place onin various Lender $P$'s branches (they did not know which ones), and that it could be in place for several months.
+They were also told that this way of operating was in place in various Lender $P$'s branches (they did not know which ones), and that it could be in place for several months.
 Randomizing at the day level limits the problem of contamination arising from clients realizing that other clients get different contracts than theirs.
 It also limits potential  manipulation by appraisers, who in the presence of individual level randomization could potentially pick their preferred costumers from the line or tell them to wait until their desired contract shows up on the screen.
-Intra-branch correlation on the probability of default (ICC) is small, at 0.08, so we don't lose much power vis-a-vis individual level randomization.
+Intra-branch day correlation on the probability of default (ICC) is small, at 0.08, so we don't lose much power vis-a-vis individual level randomization.
 
@@
 On the other hand, having arms where clients can choose among these contracts allows us to study client's demand for commitment to pay earlier.
-Note that a neoclassical consumer (with no intra-household concerns) would not voluntarily restrict her options of payment profiles (as in monthly payment contract) by being subject to fees, since she can always replicate the monthly payment profile herself under the status quo contract if she so desired.
+A neoclassical consumer (with no intra-household concerns) would not voluntarily restrict her options of payment profiles (as in monthly payment contract) by being subject to fees, since she can always replicate the monthly payment profile herself under the status quo contract if she so desired.
 The status quo contract gives her extra flexibility to respond to negative income shocks.
@@
 This value would be traded off against the value of flexibility.
+
 This design also allows us to test if promises work in a natural field environment which to our knowledge has not been done.
-Promises could have larger or smaller commitment value that a pecuniary fee, something that we test by comparing behavior in the \textit{promise-forcing}  vs \textit{status-quo} arms.
-
+Promises could have larger or smaller commitment vaWe have 5 different experimental arms, which differ in which contracts were offered on a given branch-day.
+
+\begin{enumerate}
+    \item \textit{Status-quo forcing} arm: consisted of branch-days offering the status quo contract described in Section \ref{context}, and only this contract (as was standard). 
+    \item \textit{Fee-Forcing} arm: consisted of branch-days offering only the monthly installment contract with a fee for late payment as described above. 
+    \item \textit{Fee-Choice} arm: consisted of branch-days where the client was given \textit{a choice} between the monthly installment with fee contract, and the status quo contract.
+    \item \textit{Promise-Forcing} arm: consisted of branch-days which offered the monthly payment contract only, but where there was no fee for paying late.
+Instead, the client was made to sign a paper which said ``I promise to pay every month the corresponding sum of \_\_\_\_\_\_, on the dates \_\_\_\_\_\_, \_\_\_\_\_\_, and \_\_\_\_\_\_.
+This is \underline{not} a legal document and cannot be used in courts.
+It is just a \textit{personal promise}.
+If I do not comply I would have broken my word.''.
+After signing, the promise was read to the client by the appraiser.
+    \item \textit{Promise-Choice} arm: consisted on branch-days where the client was given \textit{a choice} between the promise-forcing and the status quo contract.\footnote{We did not allocate equal number of days across arms, since we were interested in having more power in some of them.
+The branch days allocated to each -- in order-- were 84, 80, 93, 68, 82.}
+\end{enumerate}
+
+By comparing the \textit{fee-forcing} arm vs the \textit{status-quo} arm we estimate the causal effect of mandatory installment frequency which acts as a incentive to pay earlier vis-a-vis the pay-when-you-want contract.
+On the other hand, having arms where clients can choose among these contracts allows us to study client's demand for commitment to pay earlier.
+A neoclassical consumer (with no intra-household concerns) would not voluntarily restrict her options of payment profiles (as in monthly payment contract) by being subject to fees, since she can always replicate the monthly payment profile herself under the status quo contract if she so desired.
+The status quo contract gives her extra flexibility to respond to negative income shocks.
+However, if clients have present biased preferences \textit{and} are sophisticated about them, they may choose the frequent payment contract as it has commitment value.
+This value would be traded off against the value of flexibility.
+
+This design also allows us to test if promises work in a natural field environmentlue that a pecuniary fee, something that we test by comparing behavior in the \textit{promise-forcing}  vs \textit{status-quo} arms.
 Panel (b) of Figure \ref{exp_description} shows how many contracts the experiment has on each arm (rectangles).
@@
 
-\subsection{More on implementation.} \label{implementation}
+\subsection{More on implementation} \label{implementation}
 
@@
 The second threat is clients' understanding of contract terms.
-We realized that we needed the terms to be understood in order for choice to be meaningful, and for the monthly payment commitment contract to have bite.
+The terms need to be understood in order for choice to be meaningful, and for the monthly payment commitment contract to bite.
 We had two `check-points' to do this.
-First, two ITAM students were present in each branch for the whole day during the duration of our experiment to explain to clients the contract terms.
+First, two enumerators were present in each branch for the whole day during the duration of our experiment to explain to clients the contract terms.
 One of the aspects emphasized was that the frequent payment contract involved the commitment to pay \underline{each month} a third of the outstanding amount, and that there was a 2\% penalty fee (or, in the promise arms, the psychological cost of breaking a promise) for failing to do so.
@@
 
-We are fairly confident that the overwhelming majority of clients understood the contracts and made informed choices.
+We are confident the overwhelming majority of clients understood the contracts and made informed choices.
 As shown below, different contract terms did generate differential demand and differential behavior.
@@
 
-Now we answer our first question.
 Would clients benefit ---in terms of recovering their pawn and in terms of paying lower financing cost--- from having a monthly payment commitment contract \textit{forced} on them, vis-a-vis the status quo pay-when-you-want contract?
@@
 Our main outcome variables $y_{ij}$ are measures of financial cost in pesos as defined in Section \ref{FC_def}, as well as an indicator variable for client $i$ losing her pawn.
-In this subsection $T_{i}$ is an indicator for $i$ having got the \textit{fee-forcing} contract, and $\beta$ estimates the average treatment effect.%\footnote{This is an ATE and not just an ITT since take up of treatment is 100\%.}
+In this subsection $T_{i}$ is an indicator for $i$ having got the \textit{fee-forcing} contract, and $\beta$ estimates the average treatment effect.
+We cluster errors at the branch-day level.%\footnote{This is an ATE and not just an ITT since take up of treatment is 100\%.}
 
@@
 \noindent \textbf{Financial Cost.} Figure \ref{fc_pro2}(a) reports $\beta$ coefficients and their 95\% confidence interval from estimating equation (\ref{basic_reg}) using different definitions of financial cost.
-The leftmost coefficient corresponds to using the appraised gold value of the pawned piece (not discounting makes virtually no difference).
+The leftmost coefficient corresponds to using the discounted appraised gold value of the pawned piece.
 The second coefficient uses the subjective value of the pawn instead.
-In both cases we find that being assigned to the fee-forcing commitment contract causes a large reduction in the financing cost the client incurred, of 9.5\% (\hl{\$304}) in the fist definition and 13.3\% (\hl{\$478}) in the second one.
-That is, we find that \textit{charging} clients a late payment fee  actually decreases total \textit{fee-inclusive} financing cost.
+In both cases we find that being assigned to the fee-forcing commitment contract causes a large reduction in the financing cost the client incurred, of 9.5\% (\$304) in the fist definition and 13.3\% (\$478) in the second one.
+That is, we find that \textit{charging} clients a late payment decreases total \textit{fee-inclusive} financing cost.
 
 Financial cost incurred by pawn-shop clients is a key variable to study.
-However it is true that it does not take into account other costs like transportation or the opportunity cost of going in person to the branch.
+However it does not take into account transportation cost or the opportunity cost of going in person to the branch.
 Given that the fee-forcing contract makes clients visit the branch more often (monthly), one may want a measure that includes those costs as well.
@@
 \noindent \textbf{Heterogeneous Treatment Effects.} Average cost reductions could mask substantial heterogeneity.
-We find that benefits are distributed broadly however.
+Benefits are distributed broadly however.
 Figure \ref{fc_pro2}(b) displays results from quantile regressions at the 15$^{th}$, 25$^{th}$, 50$^{th}$ 75$^{th}$, and 85$^{th}$ percentiles.
 All of them are negative.
-Figure \ref{fc_pro2}(c) uses \cite{atheygrf} generalized random forests methodology to estimate person specific treatment effects, and plots the distribution of those treatment effects.\footnote{\cite{atheygrf} use random forests of honest causal trees to estimate personalized treatment effects.
+Figure \ref{fc_pro2}(c) uses \cite{atheygrf} generalized random forests methodology to estimate individual treatment effects, and plots the distribution of those treatment effects.\footnote{\cite{atheygrf} use random forests of honest causal trees to estimate personalized treatment effects.
 The trees are such that at each leaf (partition determined by covariates) we obtain an unbiased estimate of a treatment effect using treatment and control observations in that leaf.
@@
 \cite{atheygrf} show that their treatment effects are asymptotically normal, which allows us to construct confidence intervals for our treatment estimate in each leaf.
-} We find that more than 90\% of clients experienced financial cost savings in the fee-forcing group compared to the status-quo group.
+} More than 90\% of clients experienced financial cost savings in the fee-forcing group compared to the status-quo group.
 Figure \ref{HTE_fee_forcing} in the Appendix shows that the causal cost savings are largest for the more economically vulnerable, %that report at baseline that they have problems paying for services like water, electricity and rent,
@@
 \noindent \textbf{Pawn Recovery.} Figure \ref{fc_pro2}(d) plots estimated treatment effects of the fee-forcing commitment contract with the dependent variable being an indicator of losing the pawn in less than 230 days.
-The leftmost coefficient shows that the fee-forcing commitment contract increases the likelihood of recovering the pawn by 11pp (25\% of mean recovery).
-This is a large effect.
-It contrasts for instance with \cite{Pande} who find no effect of payment frequency on default in a group lending microfinance context.
-Figure \ref{fc_pro2}(e) shows the distribution of heterogeneous treatment effects for losing pawn: it shows that \textit{everybody's} likelihood of losing the pawn decreases.
+The leftmost coefficient shows that the fee-forcing commitment contract increases the likelihood of recovering the pawn by 11 percentage points (25\% of mean recovery).
+This result stands in contrast with \cite{Pande} who find no effect of payment frequency on default in a group lending microfinance context.
+Figure \ref{fc_pro2}(e) shows the distribution of heterogeneous treatment effects for losing the pawn: it shows that \textit{everybody's} likelihood of losing the pawn decreases.
 %Figure \ref{HTE_fee_forcing}(b) in the Appendix shows that those we classify as present biased, those that requested to be sent a reminder to pay, and those who have more problems paying for basic services experienced the largest increases on pawn recovery.
@@
 Figure \ref{induced_to_pay_early} in the Appendix correlates heterogeneous treatment effects on financing cost and time of first payment and shows that those induced to pay earlier are also those that have larger induced reduction in financial cost.
-A second finding is that treatment effects are concentrated on the intensive margin, as treatment does \textit{not} affect the fraction of clients who pay a positive amount (column 6).
+Treatment effects are concentrated on the intensive margin, as treatment does \textit{not} affect the fraction of clients who pay a positive amount (column 6).
 The percentage of the loan paid increases by 8 percentage points on average (column 7).
-Note however is that the percentage of the loan paid is not larger for those that end up losing the pawn (first row of column 8).
+However the percentage of the loan paid is not larger for those that end up losing the pawn (first row of column 8).
 
 \vspace{.2in}
-\noindent \textbf{Other sub-samples.} Going back to Figure \ref{fc_pro2}(a), we estimate some interesting correlations.
-The 4th coefficient from left to right conditions on those who paid a positive amount (in treatment and control).
-Although this is potentially an a selected subsample, Table \ref{mechanisms} showed that there is no treatment effect on pay$>0$.
+\noindent \textbf{Other sub-samples.}  Results survive if we focus on those that paid a positive amount (in treatment and control) towards loan recovery.\footnote{Although this is potentially a selected subsample, Table \ref{mechanisms} showed that there is no treatment effect the extensive margin, i.e.
+in $pay>0$.} We find that even those that paid a fee in the fee-forcing contract end up paying a smaller financial cost that those in the status-quo contract (Figure \ref{fc_pro2}a).\footnote{This conditions on those that paid a fee in the fee-forcing group, comparing this subset in treatment vs all of the control group.
+Results are similar if we condition in the control group on those who would have paid a fee given current behavior.
+Again we acknowledge these is an endogenous sample and that the estimate may not be a causal effect.}  Figure \ref{fc_pro2}d shows that the increase in pawn recovery is robust to defining recovery using the first 120 days of the contract, or restricting to those paying a positive amount towards pawn recovery.
+
+%we The 4th coefficient from left to right conditions on those who paid a positive amount (in treatment and control).
+Although this is potentially a selected subsample, Table \ref{mechanisms} showed that there is no treatment effect on pay$>0$.
 We were interested in this population to show that the effect is there for those who are serious about recovering their pawn.
-The fifth coefficient conditions on those that paid a fee in the fee-forcing group, comparing this subset in treatment vs all of the control group.\footnote{Results are similar if we condition in the control group on those who would have paid a fee given current behavior.
+The fifth coefficient conditions on those that paid a fee in the fee-forcing group, comparing this subset in treatment vs all of the control group.
+Results are similar if we condition in the control group on those who would have paid a fee given current behavior.
 Again we acknowledge these is an endogenous sample and that the estimate may not be a causal effect.} We find that even those that paid a fee in the fee-forcing contract end up paying a smaller financial cost that those in the status-quo contract.
-Figure \ref{fc_pro2}(c) shows that the increase in pawn recovery is robust to defining recovery using the first 120 days of the contract, or restricting to those paying a positive amount towards pawn recovery.
 
@@
 
-We have shown that all clients are more likely to recover their pawn and almost all of them incur in a lower financial cost  when assigned to a monthly payment commitment contract.
+All clients are more likely to recover their pawn and almost all of them incur in a lower financial cost when assigned to a monthly payment commitment contract.
 This however does not necessarily show that they benefited in utility terms, and this is hard to show directly.
@@
 Figure \ref{reincidence} presents results of equation (\ref{basic_reg}) where the dependent variable is a dummy for the client being a repeat costumer.
-We define a client as a repeat costumer if, after experiencing at least 75 days of the respective treatment arm, she came back and pawned a \textit{different} piece.\footnote{Results are robust to using other number of days besides 75.
-We know its a different piece from them having a different weight.}  The left most coefficient shows that the causal effect of the fee-forcing contract on repeat pawning is an increase of 5pp in the probability of being a repeat costumer, this is 55\% increase on a mean re-incidence with respect to those that got the status-quo contract.
-This effect is not explained by clients recovering their first pawn with higher probability in the fee-forcing contract and re-pawning this same one since we make sure it is another piece (only \hl{16\%} recover their piece in the fist 75 days in the fee forcing contract).
+We define a client as a repeat costumer if, after experiencing at least 75 days of the respective treatment arm, she came back and pawned a \textit{different} piece.\footnote{Results are robust to using number of days experiencing the contract larger than 75.
+We know its a different piece from it having a different weight/value.}  The left most coefficient shows that the causal effect of the fee-forcing contract on repeat pawning is an increase of 5 percentage points in the probability of being a repeat costumer, this is 55\% increase on a mean re-incidence with respect to those that got the status-quo contract.
+This effect is not explained by clients recovering their first pawn with higher probability in the fee-forcing contract and re-pawning this same one since we make sure it is another piece (only 16\% recover their piece in the fist 75 days in the fee forcing contract).
 The second coefficient restricts the sample in the regression to those that had not recovered their pawn in the first 75 days and finds similar result.
-Finally, the third coefficient focuses on the subsample who experienced a financial cost savings treatment effect above the median treatment effect in their first pawn.
+The third coefficient conditions on clients who recovered the pawn in both arms.
+The fourth coefficient focuses on the subsample who had or would have had a financial cost savings treatment effect above the median treatment effect in their first pawn.
 It shows that for these clients the likelihood of coming back is twice as large (although imprecise).
-That is, those that benefit more from the fee-forcing contract are more likely to repeat.\footnote{We also implemented an exit survey which clients filled when recovering their piece.
-Unfortunately it had low response rates (7\%), and we take its results with a grain of salt.
-In this survey 63\% said they liked the frequent payment contract more than the status-quo one, and that is allow them avoid unnecessary expenses.} %The coefficient on repeat pawning is just as big when we focus only 2nd pawns happening after the first was recovered (third coefficient ``fnr'').
+That is, those that benefit more from the fee-forcing contract are more likely to repeat.\footnote{The second and third estimate must be interpreted with care as we are conditioning on a variable that may be affected by treatment.
+We view these as suggestive correlations.
+The fourth coefficient does not have that problem as it conditions on clients that by their pre-determined covariates are predicted to have above the median treatment effects (in both arms).} Experience with the frequent payment contract seems to be necessary as there is no effect of the monthly payment contract on repeat pawning in the first 30 or 60 days of the contract (see Figure \ref{reincidence_before} in the Appendix.
+%We also implemented an exit survey which clients filled when recovering their piece.
+Unfortunately it had low response rate (7\%), and we take its results with a grain of salt.
+In this survey 63\% of clients said they liked the frequent payment contract more than the status-quo one, and that it allowed them to avoid unnecessary expenses.
+%The coefficient on repeat pawning is just as big when we focus only 2nd pawns happening after the first was recovered (third coefficient ``fnr'').
 This is consistent with \cite{Laibson2018}'s conjecture that clients could be making decisions based on experienced utility.\footnote{The third coefficient conditions on the subsample that did recover their first pawn in both arms and finds a coefficient of 4pp.
@@
 
+We view this result as strong evidence that after experiencing the contract demand for it increases, consistent with \cite{Alcohol}'s conjecture that demand for commitment increases with experience with it.
+However there is an alternative explanation for this result, namely that forcing frequent payments effectively means awarding a smaller loan, and thus that clients may pawn again to compensate for the smaller loan.
+We are skeptical about this interpretation for several reasons.
+%First, typically the emergencies that trigger a pawn are short lived (e.g.
+needing to go to the hospital), and it is unclear why clients in the frequent payment arm wait for several months to re-pawn -- there is no effect of the monthly payment contract on repeat pawning in the first 30 or 60 days of the contract, (see Figure \ref{reincidence_before} in Appendix).
+First,  there are many alternatives lenders in this market, and if they did not like frequent payments why do they come back to Lender $P$ for another loan?
+Second, the fee is really small at 2\% of 1/3 of the value of the loan.
+The transaction costs of obtaining another loan are likely larger than incurring in this fee.
+So of the monthly payment makes the current loan ``smaller'' it is probably better to skip the monthly payment and incur in a fee than to get an additional loan.
+Third, we find larger effects of repeat buying for clients that experienced larger treatment effects, which the alternative explanation cannot explain.
+Fifth, the effect is present if we condition on clients that recovered their pawn (so its not driven by pawn recovery)\footnote{This in effect conditions on treatment and control clients that recovered their pawn.
+We are aware that we are conditioning on an endogenous variable and this must be interpreted as a correlation only.}.
+Finally, we were able to obtain observational data for all Lender $P$'s branches for the period January 2016 to May 2020, during which Lender $P$ expanded the new frequent payment contract.
+Using an instrumental variable strategy that exploits the expansion and availability of the frequent payment contract across branches, we show that being exposed to the frequent payment contract leads to an increase of 50 percentage points in the likelihood that in the subsequent pawn the frequent payment contract is chosen when both the status-quo one and the frequent payment contract are available  (see Appendix \ref{appendix_b}).
+This choice cannot be explained by the need of another loan, since it is about \textit{which specific type} of loan the clients chooses conditional on getting one.
+
 \section{The effect of giving choice} \label{fee-choice}
@@
 In such a case, one would expect a strong demand for it.
+This is not the case.
 
@@
 What can explain this low demand?
-This section discusses some hypothesis but data limits what can be tested.
-One neoclassical explanation could be risk.
+In the spirit of \cite{Blumenstock} we try to differentiate between explanations.
+One explanation could be risk.
 Even if the fee forcing contract generates cost savings on average, clients with risk averse preferences may not demand it if they perceive higher risk from it.
@@
 If clients, for instance, face large and frequent income shocks which make it hard to repay monthly.\footnote{We don't observe income shocks in our data, making is hard to quantify how important they are.
-91\% of those in the fee-forcing arm incurred a fee, which suggests that shocks are not uncommon.} Below we focus on some explanations of low demand, while Section \ref{model} seeks theories that can explain all the findings at the same time.
+91\% of those in the fee-forcing arm incurred a fee, which suggests that shocks are not uncommon.} Below we focus on some explanations of low demand, while Section \ref{model} explores theories that can explain all the findings at the same time.
 
@@
 The Lasso selected variables were type of pawn, female, age, has pawned before, has savings, participates in rotating savings, often feels tempted to change plans, would like to have a reminder to pay, and an economic vulnerability index.
-We are careful not to include these variables as controls in Table  \ref{oc_reg}.} There is an impressive amount of overconfidence in our context.
+We are careful not to include these variables as controls in Table  \ref{oc_reg}.} There is a large amount of overconfidence in our context.
 Figure \ref{oc_hist} plots a histogram of $OC_i$ and shows that the overwhelming majority display overconfidence, and a large fraction overestimate recovery by more than 50 percentage points.
 
-Table \ref{oc_reg} regresses an indicator of take up of the monthly payment contract against an indicator for overconfidence $OC_i:=\mathbbm{1}(P^s_i-\widehat{P_i(X_i)}>0)$ and controls.
+\cite{Sprenger} have argued that it is critical to understand the link between beliefs and demand for commitment, yet the evidence is scarce.
+Table \ref{oc_reg} does this: it regresses an indicator of take up of the monthly payment contract against an indicator for overconfidence $OC_i:=\mathbbm{1}(P^s_i-\widehat{P_i(X_i)}>0)$ and controls.
 Controls $Z$ include branch and day of the week dummies, schooling, whether the client does a monthly budget plan, among others.
-We are careful not to include controls that were in $X$.
+We are careful not to include controls that were used in $\widehat{P_i(X_i)}$.
 % and a measure of intertemporal preference reversal analogous to that of \cite{Ashraf} as controls.\
-Column \hl{1} shows that in the choice-fee arm, being overconfident decreases the likelihood of demanding commitment by 16 percentage points, and column \hl{2} shows that this is robust to including controls.
-Columns \hl{3} and \hl{4} which use the promise-choice arm are intended as a placebo comparison.
-Overconfidence it not predictive of take up of the promise-commitment contract.
-One interpretation of the results is that the overconfident think they do not need commitment, and its demand decreases as soon as there is even a small fee but not when the contract involves a free commitment, as if the promise for them was cheap.
-Column 5 and 6 use as a dependent variable the estimated heterogeneous treatment effects of the fee-forcing contract vs the status quo one.
-They show that the overconfident benefit \textit{more} from the commitment contract, with 20\% (=\$24/\$121) more savings.
+In the choice-fee arm, being overconfident decreases the likelihood of demanding commitment by 12 percentage points a result that this is robust to including controls  (columns 1 and 2).
+While overconfidence predicts lower take up in the fee-choice arm, this is not the case in the promise-choice arm (columns 3 and 4).
+One interpretation of the results is that the overconfident borrowers think they do not need commitment, and their demand decreases sharply as soon as there is even a small fee, and at the same time they perceive the promise as a low cost option.
+This provides evidence for \cite{Sprenger}'s conjecture that ``tepid demand for commitment outside controlled experimental settings is consistent with broad unawareness [of biases]''.
+
+How does overconfidence map to cost outcomes?
+Theory predicts that the more overconfident (naive) may be at the same time those that benefit more from commitment.
+Extrapolating individual treatment effects of the fee-forcing contract vs the status quo one to the choice arm (see below for more detail), and using them as a dependent variable we find that overconfident borrowers benefit \textit{more} from the commitment contract, with 24.8\% (=\$30/\$121) more savings (columns 5 and 6).
 Thus while we predict the overconfident benefit more from commitment, they demand less.
 
-We think our measure of overconfidence is useful especially when there is limited time for a detailed survey.\footnote{It may be more useful than a simple elicitation of present bias as in \cite{Ashraf}.
+\vspace{.2in}
+Our measure of overconfidence is useful especially when there is limited time for a detailed survey.\footnote{It may be more useful than a simple elicitation of present bias as in \cite{Ashraf}.
 We find that 15\% of clients are classified as present biased using this measure of preference reversal.
@@
 This measure was not correlated with take up of commitment in our sample.} First it is very prevalent, which makes it promising to explain the overwhelming prevalence of low take up.
-Second, it is easy to measure and showed predictive value for take-up.
-It is also implied by present bias with naivete but also by biased expectations of negative income shocks, thus capturing both kinds of bias.
+Second, it is easy to measure.
+Third, it is predictive of take-up in an intuitive way.
+Finally, overconfidence in recovery is implied by present bias with naivete but also by biased expectations of negative income shocks, thus capturing both kinds of bias.
 
@@
 \vspace{.1in}
-\noindent \textbf{Risk aversion.} We do not have measures of risk aversion in our necessarily short survey, which makes it hard to assess the hypothesis that risk aversion limits take-up of the fee frequent payment contract.
+\noindent \textbf{Risk aversion.} We do not have measures of risk aversion in our short survey, which makes it hard to assess the hypothesis that risk aversion limits take-up of the fee frequent payment contract.
 One way to proceed is to take the empirical distribution of financing cost ---$F_{fee}(FC)$--- as one the client would have faced had she chosen the the fee-commitment contract.
@@
 \vspace{.1in}
-\noindent \textbf{Lost flexibility.} A second neoclassical explanation for low take up is lost flexibility.
+\noindent \textbf{Lost flexibility.} A second explanation for low take up is lost flexibility.
 That is, the fee-commitment contract may provide too much commitment which is costly because the client may be forced to incur in late payment fees if he experiences a negative income shock.\footnote{Note that income shocks that affect the ability to pay the entire loan are a worry for both the fee-forcing contract and the status quo one, and should not make one contract more favorable than the other.} While we cannot rule out that income shocks combined with lost flexibility of the contract explain the low demand, we think it is unlikely.
@@
 What would discount rates have to be in order for back loaded payments to offset the reductions in financial cost effects we observe?
-We can calculate this number by looping across a grid of discount rates, incorporating this higher discount rate in the definition of financial cost, and reestimating equation \ref{basic_reg} with this modified financial cost measure as the dependent variable in equation 1, searching for the discount rate that makes $\beta$ equal zero.
-We did this and obtained that the discount rate that rationalizes a zero effect is a staggering 8,190 percent per year.
-We find this discount rate implausibly high even for this credit constrained population\footnote{Just for comparison, \cite{Levin} find that a discount rate of 1,415 per year for subprime borrowers in the US is too high to be believable.}, seriously casting doubt on high discount rates as explanation for low demand for commitment.
+%We can calculate this number by looping across a grid of discount rates, incorporating this higher discount rate in the definition of financial cost, and reestimating equation \ref{basic_reg} with this modified financial cost measure as the dependent variable in equation 1, searching for the discount rate that makes $\beta$ equal zero.
+We did this and obtained
+The discount rate that rationalizes a zero effect is a staggering 8,190 percent per year.
+We find this discount rate implausibly high even for this credit constrained population\footnote{For comparison, \cite{Levin} find that a discount rate of 1,415 per year for subprime borrowers in the US is too high to be believable.}, casting doubt on high discount rates as explanation for low demand for commitment.
 %\footnote{In the baseline survey we give respondents a hypothetical choice between $100$ pesos tomorrow or $150$ pesos in one month (an implicit yearly interest rate of \hl{12,800\%}) and only 30\% chose the later one.}
@@
 \vspace{.2in}
-\noindent It seems to us that present bias with naivete is the more likely explanation for low commitment demand in our case.
+\noindent All in all, present bias with naivete is the more likely explanation for low commitment demand in our case.
 Moreover, Section \ref{model} shows that present bias with naivete is able to qualitatively explain all the main findings of the paper, not just low demand for commitment.
@@
 
-We find that giving clients the option of choosing among the fee-forcing and the status quo contract does \textit{not} lead to lower financial cost compared to forcing them into the status-quo contract.
+Giving clients the option of choosing among the fee-forcing and the status quo contract does \textit{not} lead to lower financial cost compared to forcing them into the status-quo contract.
 Nor does it lead to higher pawn recovery.
 The hollow circles in Figure \ref{fc_pro4}(a) show zero average effects for the different definitions of financial cost analogous to the ones described above.
-Figure \ref{fc_pro4}(b) shows further that the null effect happens for the 15$^{th}$, 25$^{th}$, 50$^{th}$ 75$^{th}$, and 85$^{th}$ percentiles.\footnote{The few that selected the fee-commitment contract (the solid black squares) do enjoy cost savings of 1005 pesos, which compares favorably to the 304 pesos in the fee-forcing arm (as a fraction of the loan the numbers are 41.5\% and 12.5\%), but this combines the selection and treatment effects.} %Figure \ref{heterogeneous_te_4} plots the distribution of treatment effects and finds that the distribution offering choice actually \textit{increased} financial cost and default for about half of clients compared to being assigned the status-quo contract.
+Figure \ref{fc_pro4}(b) shows further that the null effect happens for the 15$^{th}$, 25$^{th}$, 50$^{th}$ 75$^{th}$, and 85$^{th}$ percentiles.\footnote{The few that selected the fee-commitment contract (the solid black squares) do enjoy cost savings of 1005 MXN, which compares favorably to the 304 MXN in the fee-forcing arm (as a fraction of the loan the numbers are 41.5\% and 12.5\%), but this combines the selection and treatment effects.} %Figure \ref{heterogeneous_te_4} plots the distribution of treatment effects and finds that the distribution offering choice actually \textit{increased} financial cost and default for about half of clients compared to being assigned the status-quo contract.
 Those tended to be the less economically vulnerable and more educated, \hl{women}, and those whose family typically asks them for money.
@@
 
-This is not the first paper to find low demand for commitment, however \hl{it is the first we know of that can compare choice vs forcing}.
+This is not the first paper to find low demand for commitment, however it is the first we know of that can compare choice vs forcing.
 The fact that the fee-forcing contract lowers financial costs for almost all clients, together with the fact that only 10\% choose it must mean that many consumers are choosing contracts with higher financial costs for them.
@@
 First, we normalize $\widehat{TE}^{fee}_{i}$ by the value of the loan of person $i$ and introduce a threshold parameter $z$ and say that a choice is a ``mistake'' if the alternative contract would generate greater than $z$ in savings.
-That is, we introduce a threshold that we vary from 0\% to \hl{15}\% of the value of the loan.
-Second, we take into account uncertainty in estimation of treatment effects and report results using the extremes of the \hl{90\%} confidence interval bounds for $\widehat{TE}^{fee}_{i}$.
+That is, we introduce a threshold that we vary from 0\% to 15\% of the value of the loan.
+Second, we take into account uncertainty in estimation of treatment effects and report results using the extremes of the 90\% confidence interval bounds for $\widehat{TE}^{fee}_{i}$.
 
@@
 In the X-axis it varies the threshold $z$ of what we classify as a mistake.
-When $z=0$, we calculate that about 80\% of clients in the fee-choice group chose contracts that induced \textit{higher} financial cost (90\% confidence interval \hl{[45,94]}).
+When $z=0$, we calculate that about 80\% of clients in the fee-choice group chose contracts that induced \textit{higher} financial cost (90\% confidence interval [45,94]).
 Most mistakes are failures to choose the fee-commitment contract (92\%), while only 8\% of those who chose the fee-commitment contract would have been better in the status-quo one.
-The average mistake in pesos is \$238 (90\% confidence interval \hl{[140,390]}).
+The average mistake in pesos is \$238 (90\% confidence interval [140,390]).
 Figure \ref{choose_wrong}(b) separates the analysis for those we classify as overconfident about recovering their pawn vs the rest.
-It shows that there are about \hl{11} percentage points more mistakes in the overconfident population (when $z=0$).
-
-All the above suggests that forcing clients into commitment contacts (i.e.
-private paternalism) may be welfare increasing for the overwhelming majority of clients.
-Figure \ref{choose_wrong}(c) calculates what fraction of clients would be made better off if we forced them to the fee-commitment contract: 92\% when $z=0$, and they would on average have savings of 232 pesos.
+It shows that there are about 11 percentage points more mistakes in the overconfident population (when $z=0$).
+
+All the above suggests that forcing clients into commitment contacts may reduce financial cost for the overwhelming majority of clients.
+Figure \ref{choose_wrong}(c) calculates what fraction of clients would be made better off if we forced them to the fee-commitment contract: 92\% when $z=0$, and they would on average have savings of 232 MXN.
 This conclusion is in line with a recent paper by \cite{John}.
@@
 Figure \ref{choose_wrong}(d) is a binscatter that splits the X-axis in 100 percentiles bins of predicted take-up probability and for each bin averages the financial cost treatment effects.
-Using all clouds we estimate a slope of zero in the relationship.
+Using all clouds we estimate a slope close to zero in the relationship.
 Using the 80 right most points, we estimate a \textit{positive} relationship.
@@
 
-One finding of the paper is that a rather small fee of 14 pesos on average changes behavior substantially: on the one hand generates average savings for almost everybody (and in the order of \hl{230} pesos on average) when forced, but on the other dissuades take up when clients have choice.
+One finding of the paper is that a rather small fee of 14 MXN on average changes behavior substantially: on the one hand generates average savings for almost everybody (and in the order of 200-300 pesos on average) when forced, but on the other dissuades take up when clients have choice.
 In this context one would want a commitment device that generates higher take up while at the same time providing incentives for paying fast and recovering the pawn.
@@
 A simple model shows that present bias with naivete parsimoniously explains all findings.
-This strongly suggests that ``private paternalism'', a policy that advances an individual's interests by restricting her freedom, is beneficial in our context.
-We provide a quantification of the size of unrealized benefits that arise when clients have choice and calculate that 92\% of clients would benefit with more recovery and lower financial cost from being forced into the fee-commitment contract.
-
-Methodologically, to our knowledge this is the first paper in economics that uses machine learning methods to estimate personalized counterfactual treatment gains and ask whether treatment take up is positively selected on benefits, using treatment effects in forcing arms to calculate benefits in choice arms.
+This strongly suggests that it is possible in our context to advance an individual's interests by restricting her freedom ---although we caution that our outcome measure focuses on financing cost and is not comprehensive measure of welfare.
+These results spurred --although we cannot show it caused-- Lender $P$ to offer frequent payment contacts.
+Although Lender $P$ was not as bold as to force these contracts on clients.
+They hoped that clients would eventually learn which contract was better for them.
 
@@
 
-We see three lines of further work that are of interest.
-First, investigate why the fee-commitment contract had such low demand in spite of its across-the-board benefits and very low fees.
-In particular tease out the roles of naivete about self control problems, biased expectations about income shocks, and ambiguity aversion with better direct baseline measurements.
-Second, whether other types of contracts ---for instance those that provide some insurance against shocks--- could induce larger demand and better performance.
-Third, whether individuals choosing to borrow from pawnshops are more present biased and naive than similar individuals borrowing from other types of lenders.
+Methodologically, to our knowledge this is the first paper in economics that uses machine learning methods and a combination of choice and forcing arms to estimate personalized counterfactual treatment gains to ask whether treatment take up is positively selected on benefits.
+
+Our results leave open several avenues for research.
+First, it would be useful to tease out the roles played by naivete about self control problems, biased expectations about income shocks, and ambiguity aversion in driving low demand for commitment, using more detailed direct baseline measurements.
+Second, one could ask whether other types of contracts ---for instance those that provide some insurance against shocks---  induce larger demand and better performance than the ones we tried.
+Third, it is likely individuals choosing to borrow from pawnshops are more present biased and naive than similar individuals borrowing from other types of lenders, meriting differential regulation.
+Testing and quantifying this selection across lenders is important.
+Fourth, collecting broader measures of welfare to use as outcomes --e.g.
+subjective well being, consumption, being able to pay for essential services-- would help to make broader claims about welfare that we can make in this paper.
+Finally, one would like to know which interventions could debias consumers, or whether learning alone would do the work.
 
@@
 
+\vspace{.2in}
 \begin{figure}[H]
@@
     \begin{subfigure}{.45\textwidth}
-      \caption{In pesos}
+      \caption{In pesos MXN}
         \centering
@@
     \begin{subfigure}{0.42\textwidth}
-        \caption{Financial cost (pesos)}
+        \caption{Financial cost (MXN)}
         \centering
@@
 
+\vspace{.3in}
 \begin{figure}[H]
@@
 The second coefficient conditions on the first pawn not being recovered when the second was pawned.
-The third coefficient uses all clients (in both the fee-forcing and the status-quo arms) who had an estimated heterogeneous treatment effect above the median.
+The third coefficient conditions on clients who pawned again after having recovered the pawn in the experiment.
+The fourth coefficient uses all clients (in both the fee-forcing and the status-quo arms) who had an estimated heterogeneous treatment effect above the median.
 Conditioning on this set keeps the sample balanced across arms and therefore still allows for a causal interpretation.
@@
 \setcounter{table}{0}
-\renewcommand{\thetable}{A\arabic{table}}
+\renewcommand{\thetable}{\thesection.\arabic{table}}
 
 \setcounter{figure}{0}
-\renewcommand{\thefigure}{A\arabic{figure}}
+\renewcommand{\thefigure}{\thesection.\arabic{figure}}
 
@@
 
-\section{APPENDIX}
+\section{APPENDIX A}
+\vspace{.2in}
 
@@
 \subsection{Surveys}
-\afterpage{
-\begin{table}[H]
-\caption{Baseline survey}
-\label{baseline_survey}
-\begin{center}
-\scriptsize{\input{./Tables/transcribed.tex}}
-\end{center}
-\end{table}
-}
 
@@
 \end{table}
+
+\afterpage{
+\begin{table}[H]
+\caption{Baseline survey}
+\label{baseline_survey}
+\begin{center}
+\scriptsize{\input{./Tables/transcribed.tex}}
+\end{center}
+\end{table}
+}
 
@@
 \vspace{.2in}
+
+\begin{figure}[H]
+        \caption{FC as \% of loan - treatment effect}
+    \label{fc_pro_2_115}
+    \begin{center}
+        \centering
+        \includegraphics[width=0.50\textwidth]{Figuras/fc_te_115_pro_2.pdf}
+    \end{center}
+     \scriptsize This figure is the same as in Figure \ref{fc_pro2} Panel (a), but with the subsample restricted to the first 115 days.
+     %\textit{Do file: }  \texttt{fc\_te\_115.do}
+\end{figure}
+
 \begin{figure}[H]
@@
       %\textit{Do file: }  \texttt{binscatter\_hte.do}
+\end{figure}
+
+\begin{figure}[H]
+        \caption{Repeat purchase before 30/60 days}
+    \label{reincidence_before}
+    \begin{center}
+        \centering
+        \includegraphics[width=0.50\textwidth]{Figuras/re_te_earlydays.pdf}
+    \end{center}
+     \scriptsize This figure shows the estimated treatment effect of repeat purchase before 30 \& 60 days.
+     %\textit{Do file: }  \texttt{re\_te\_earlydays.do}
 \end{figure}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% APPENDIX B
+\setcounter{table}{0}
+\setcounter{figure}{0}
+
+\newpage
+\section{APPENDIX B: Observational analysis}
+\label{appendix_b}
+\vspace{.2in}
+\normalsize
+
+The objective of this appendix is to conduct one test aiming to assess if there is learning in choosing the frequent payment FP) contract.
+In particular if being endogenously induced to have a FP contract causes the client to chose a FP in subsequent pawn.
+The identification strategy is not as strong as in a randomized control trial ---having to rely on an instrumental variable strategy using changes in the supply of the FP contract-- and this is why we chose to locate it in a separate appendix.
+However we believe we find a strong case for learning causing higher demand for the FP contract.
+
+In what follows we will describe the identifying variation and use the richness of the observational data to control for possible confounds.
+We will use hundreds of branches and hundreds of thousands of pawns covering more than 4 years to estimate (under the identification assumptions) the causal effect of having had a FP on the conditional demand for the FP type of contract.
+
+\vspace{.in}
+
+\subsection{Variation in branches' use of frequent payment contract}
+
+After our experiment ended, Lender $P$ started offering frequent payment contracts along their traditional ones.
+We were not able to get data for the dates of the first expansion, but we have data for the period January 2016 through May 2020.
+During this period some branches where offering the frequent payment contract while others were just starting to do this.
+Some branches also stopped offering the frequent payment contracts.
+Out of all branches 2\% never offered the FP contract, 29\% always offered it, while 69\% offered for only part of our sample period.
+Our identification strategy will mostly rely on these later group, as we include branch fixed effects in our regressions.
+\\
+
+To show the reader a glimpse of this variation in availability of the contract we randomly selected 20 branches and plotted which months had a frequent payment contract active in their IT system.
+Figure \ref{variation_pf_suc} shows a time plot for each branch, where each observation is a month.
+The Y-axis takes the value of 1 if in that month the FP contract was available in that branch and zero otherwise.
+So it is a ``supply side'' variable.
+
+\vspace{.1in}
+\begin{figure}[H]
+        \caption{Existence of FP per branch}
+    \label{variation_pf_suc}
+    \begin{center}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/active_pf_suc.pdf}
+    \end{center}
+     \scriptsize This Figure shows the presence of the frequent payment (FP) contract in 20 randomly chosen branches of Lender $P$ for a span of more than 4 years.
+A y value =1 means that in that month the FP contract was available in that branch.
+     %\textit{Do file: }  \texttt{active\_pf\_suc.do}
+\end{figure}
+\vspace{.1in}
+
+In conversations with Lender $P$ about this variability they said that it is driven by three things: the expansion of the frequent payment product is done gradually, the IT system of a branch sometimes fails, and they often do experiments themselves turning on and off the existing of the frequent payment contract as this was a relatively new type of contract.\footnote{Unfortunately the had no documentation on how these experiments were implemented.} We did verify that there are no frequent payment contracts when they said it was turned off in their IT system.
+
+\paragraph{Orthogonality of FP supply.} We will use the availability of the FP contract as an instrument for the client choosing a FP contract when she pawns.
+Clearly one cannot choose a FP when it does not exist, so that this instrument allows would-be-FP choosers to obtain a FP contract.
+We verify that indeed it has a statistically powerful first statge.
+One may be concerned that this instrument may not satisfy the exclusion restriction however.
+As we will explain below we will use this instrument in an specification that controls for branch and client fixed effects, taking into advantage that many clients do pawn repeatedly (See Figure \ref{hist_num_pawns} below).
+These control for any characteristic of the client that is fixed across time, and therefore is a strong control for selection of clients across branch or across contracts.
+We also control for calendar of the month fixed effects, thereby absorbing common time trends that affect all clients, like macroeconomic shocks.
+We describe the exact specification below, but for now we want to note that we need only for the exogeneity of the instrument to hold conditional on these extensive set thousands of fixed effects.
+
+    \vspace{.1in}
+\begin{figure}[H]
+        \caption{Number of pawns per client}
+    \label{hist_num_pawns}
+    \begin{center}
+        \centering
+        \includegraphics[width=0.6\textwidth]{Figuras/hist_num_pawns.pdf}
+    \end{center}
+     \scriptsize This figure plots a histogram of the number of pawns per client during our sample period (January 2016 through May 2020).
+A large fraction of clients have more than one pawn, and many have several pawns.
+We use these repeat clients to identify learning below.
+     %\textit{Do file: }  \texttt{hist\_num\_pawns.do}
+\end{figure}
+\vspace{.1in}
+
+Having said this in Table \ref{instrument_random} we assess to what extent we can predict whether a given branch activates the FP contract in its IT system in a given week or a given month.
+It turns out that we cannot predict in which weeks a given branch uses the FP contract with our observables controlling for branch fixed effects.
+The observables include fraction female clients last week (or last month), the age of these clients, number of pawns last week (or last month), average size of those loans, the percentage of pawns last week (or last month) that were jewelry, the percentage of loan recoveries --the opposite of default-- last week (or last month).
+The same is true if we use one month prior instead of one week.
+The $R^2$ shows that the \textit{additional} variance explained by the covariates beyond branch and calendar week fixed effects is low: going from 0.154 to 0.157 when we add all regressors.
+The $AUC$ and the \textit{Accuracy Rate} give a similar picture, with out-of-sample $AUC$ around 0.72 and Accuracy rates around 66\%.\footnote{\cite{Finanzia} say that for predicting loan default for instance AUC's from 0.80 to 0.95 are common.} \\ %\hl{Appraisers could potentially have an effect on what contract people choose conditional on the contract existing in the system.
+We test for this and find XXX...}
+
+Quantitatively the correlations are small: an increase of 1 years of the mean age of clients is associated with an increase of 0.008 percentage points in introducing FP, an increase in the size of the loan by 1000 pesos increases it by 0.002, an increase of 10 pawns per day increases it by less than 0.0002 percentage points.
+Having 10\% less women as clients in the past increases it by 1 percentage point.
+This result of low correlation between important observable variables and the supply of FP contract in a given branch makes us more comfortable with the assumption that the instrument satisfies the exclusion restriction.
+The presence of the FP contract in a given week in a given branch seems almost random from this perspective.
+
+\begin{table}[H]
+\caption{Predicting the supply of FP contracts within branch across time}
+\label{instrument_random}
+\begin{center}
+\footnotesize{\input{./Tables/instrument_random.tex}}
+\end{center}
+ \scriptsize
+This table uses OLS regressions to predict whether branch $j$ in week $t$ had a FP available.
+So the dependent variable is an indicator for this event $\mathbbm{1}(\text{Branch Had FP})_{jt}$, and the explanatory variables are measures of performance of that branch and the characteristics of the clients either the week previous to $t$ or 4 weeks previous to week $t$.
+We allow for two time periods since the branch manager or central offices may take time to react to information.
+Column 1 includes branch and week fixed effects, while Column 2 adds the covariates displayed measured the week previous to $t$.
+Column 3 is analogous to column 2 except that the values of the displayed covariates are averaged across the 4 weeks prior to week $t$.
+The bottom panel shows measures of predictive power like $R^2$, as well as area under the ROC curve ($AUC$), and the Accuracy Rate.
+It also shows F-test of the null hypothesis that the branch (week) fixed effects, or the other regressors have coefficients equal to zero.
+%\textit{Do file: } \texttt{instrument\_random.do, pred\_instrument.do}
+\end{table}
+
+\vspace{.1in}
+
+\subsection{Experiencing FP causes future demand for FP to increase}
+
+This subsection uses the existence of a FP contract in the branch as an instrument for a client \textit{having} a FP contract if she visited that branch that week to pawn.
+Using this instrumental variable strategy we estimate the effect of having had a FP in the previous pawn.
+More concretely, Table \ref{iv_pf} reports results from a two-stage least squares estimate of the effect of having a FP contract on subsequent demand for FP contracts.
+We estimate the following regression:
+
+\begin{equation}
+    \mathbbm{1}(\text{Has FP})_{ijt} = \alpha_i + \gamma_t + \beta \mathbbm{1}(\text{Had FP previously})_{ij't'} + \delta X_{ij} + \epsilon_{ijk}
+    \label{eqn:IV}
+\end{equation}
+\vspace{.1in}
+
+\noindent where $i,j,t,k$ index client, branch, and month respectively.
+$\mathbbm{1}(\text{Has FP})_{ijt}$ is an indicator for client $i$ pawning in branch $j$ in month $t$ using a FP contract, given that both FP and traditional contracts were available at the branch at the time of pawning, so that there is a choice to be made among these.\footnote{When a FP is not available in branch $j$ in month $t$ the variable takes the value of missing, and is therefore not considered in the regression.
+That is, we only include observations when the client had a choice between FP and traditional contracts.} We include client fixed effect $\alpha_i$ as well as calendar month fixed effects (we have 53 months) $\gamma_t$.
+The variable of interest is denoted by $\mathbbm{1}(\text{Had FP previously})_{ij't'}$, and is a an indicator for the client's previous loan (so long as it happened in the past period from $t'$ to $t$) being FP loan.
+We experimented with the time between the current loan and the immediately prior ($t'$ to $t$) being either 6 weeks or 12 weeks and report both estimates.
+The controls $X_{ij}$ include how assiduous a client is: the number of times she has pawned in the 12 months previous to $t$, as well as a dummy of having made a pawn a Lender $P$ in the period from $t'$ to $t$:   $\mathbbm{1}(\text{Had any loan previously})_{ij't'}$.
+Note that the only difference between this last control variable and our main explanatory variable is that the former does not specify which type of contract this previous loan had.
+This means that the variation identifying $\beta$ is \textit{which type} of loan the client had conditional on having had one.\\
+
+Having client fixed effects in the regression means that we only use variation across time (across subsequent pawns) to identify the effect of experience, and avoid the selection problems that come from comparing across clients.
+That is, they control for the fact that different types of clients may select different types of contracts.
+Repeat pawning is common and this helps for identification.
+Figure \ref{hist_num_pawns} shows a histogram of the fraction of clients that had $1, 2, 3,\ldots, 60$ pawns in our sample.
+We have more than one hundred thousand clients that got two loans within 3 or less months from each other\footnote{We give a small lower bound to keep the identity of Lender $P$ confidential}, and for 37\% of those clients the immediately sequentially preceding loan was taken when the branch had FP available.\\
+
+However, even with client fixed effects, idiosyncratic unobserved shocks across time may induce spurious correlation between choosing a FP last month and choosing FP today.
+The variable $\mathbbm{1}(\text{Had FP previously})_{ij't'}$ is therefore still potentially endogenous.
+To deal with this we instrument $\mathbbm{1}(\text{Had FP previously})_{ij't'}$ with the \textit{availability} of the contract in branch $j'$ at past week $t'$ when the client previously went to pawn the immediately prior pawn, $\mathbbm{1}(\text{FP Avail})_{ij't'}$.
+This is basically using a supply shifter to identify demand.
+We showed above that availability of FP contracts has close to a zero correlation to a battery of observables.
+The IV strategy assumes that availability of the FP contract in a given week in a given is uncorrelated with $\epsilon_{ijk}$ --- i.e.
+that after conditioning on thousands of client, branch and month fixed effects and the client having pawned recently, there is no omitted variable driving both: the branch having FP contracts on, and the client subsequent pawn using a FP contract.
+Note that including branch fixed effects means that identification comes from a given branch sometimes having the FP and some times not.
+\\
+
+The exclusion restriction for an instrument is untestable, but note that we are comparing clients that go to the same branch, who have the same pawning frequency, but where one of them arrived to the branch to pawn on a week where the FP contract was available and the other arrived on a week where the same branch had no FP contract available.\footnote{We also tried specifications restricting the sample to 4 weeks adjacent to the FP contract becoming available or becoming unavailable in a branch and obtain similar results.
+This strategy is close in spirit to a regression discontinuity or event-study design, comparing clients that go to the same branch with the difference that one went there 2 weeks before the FP contract becoming available.} The exclusion restriction could be violated for example if the branch manager makes FP available as a function of clients that will come in that week and therefore reaches a certain type of client that is more likely in-and-of themselves to prefer FP contracts now and in the future.
+We find this unlikely.
+It is hard to predict who will come on a given week and if they are more likely to like the PF contract: Table \ref{instrument_random} strongly suggests that the branch manager is not turning the FP contract on and off as result of which clients are coming to the branch or how the branch is doing.
+Having said this, we acknowledge that the exclusion restriction could be violated even in this very tightly controlled specification.\\
+
+Table \ref{iv_pf} shows the first and the second stage regressions for equation \ref{eqn:IV}.
+All columns have client, branch, and calendar month fixed effects as well as the controls explained above.
+Columns 1 and 3 show strong first stages (t-stats above 50).
+The availability and unavailability of the FP contract has an incidence on its use.
+Under our identification assumptions, Columns 2 and 4 show strong causal effects: having  been induced by the instrument to have a FP contract in the previous loan causes the client to a FP for her subsequent pawn by 50 percentage points (column 4).
+The difference between the first two and last two columns is the time period considered.
+Columns 1 and 2 define $\mathbbm{1}(\text{Had FP previously})_{ij't'}$ as having it in the previous 6 weeks, while columns 3 and 4 define it using the previous 12 weeks.
+
+\vspace{.2in}
+\begin{table}[H]
+\caption{Experience with frequent payment contract raises future demand for it}
+\label{iv_pf}
+\begin{center}
+\footnotesize{\input{./Tables/iv_reg_demand_pf.tex}}
+\end{center}
+ \scriptsize
+This table shows resulting estimates of variants of equation  \ref{eqn:IV} above.
+They regress a dummy for the client choosing a frequent payment contract (when both the traditional one and the FP are available) on whether the previous loan was under a FP contract.
+All columns have client, branch, and calendar month fixed effects.
+All of them control for the number of times the client has pawned in the 12 months previous to the current pawn, as well as a dummy for the having pawned in the period $t'$ to $t$.
+The main regressor of interest is having had a FP loan in the past from $t'$ to $t$  which measures experiencing a FP contract recently.
+Column 1 reports the result of first stage where the supply side instrument is an indicator for the branch having had a FP available when the client showed to pawn the previous pawn.
+Column 2 presents the two-stage least square estimate.
+Columns 3 and 4 are analogous, but instead of looking clients who pawned in the 6 weeks previous, it looks at those that had pawned in the previous 12 months.
+We do not report the exact number of observations to keep Lender $P$ identity confidential and instead give a lower bound.
+%\textit{Do file: } \texttt{iv\_reg\_demand\_pf.do}
+\end{table}
+
+% \subsubsection{Experiencing FP causes repeat pawning}
+
+% Using experimental variation the paper find that being forced into a FP contract increases the likelihood of the client coming back and pawning again.
+Here we see if that result generalizes for all branches using the instrumental variable strategy described above, where we use $\mathbbm{1}(\text{Repeated Pawning})_{ijt}$ as a dependent variable instead in equation \ref{eqn:IV}.
+
+% Table \hl{XXX} has the same structure as Table  \hl{XXX} above.
+It finds that the experimental result is qualitatively replicated with this different sample and different identification strategy.
+Having had a previous FP loan induced by its availability is associated with an increase of \hl{XXX} in the probability of pawning again \hl{in the next 3 months}.
+
+% \subsubsection{Pawn recovery and FP contracts}
+
+% Using the individual fixed effects specification, as well as the instrumental variable strategy defined above, Table \hl{XXX} finds that FP are \hl{XX\%} more likely to recover their pawns.
+
 \end{document}

### 2020-08-14 RScripts/fc_te_grf.R

@@ -3,7 +3,7 @@ library(grf)
 library(ggplot2)
 
 # SET WORKING DIRECTORY
-setwd('C:/Users/xps-seira/Dropbox/Apps/ShareLaTeX/Donde2019')
+setwd('C:/Users/xps-seira/Dropbox/Apps/ShareLaTeX/Donde2020')
 #setwd("C:\\Users\\Ricardo\\Documents\\SEIRA\\donde2019")
 set.seed(5289374)
 

### 2020-08-14 RScripts/grf.R

@@ -6,7 +6,7 @@ library(DiagrammeRsvg)
 library(gdata)
 
 # SET WORKING DIRECTORY
-setwd('C:/Users/xps-seira/Dropbox/Apps/ShareLaTeX/Donde2019')
+setwd('C:/Users/xps-seira/Dropbox/Apps/ShareLaTeX/Donde2020')
 set.seed(5289374)
 
 source("./RScripts/best_tree.R")

### 2020-08-14 RScripts/instrument_pred.R

@@ -1,0 +1,52 @@
+library(tidyverse)
+library(grf)
+library(ggplot2)
+library(DMwR)
+
+# SET WORKING DIRECTORY
+setwd('C:/Users/xps-seira/Dropbox/Apps/ShareLaTeX/Donde2020')
+set.seed(5289374)
+
+
+rf_predict <- function(data_in,pf) {
+  
+  require("dplyr")
+  data_train <- data_in %>% 
+    filter(insample == 1) 
+  
+  data_test <- data_in %>% 
+    select(-c(pf, insample))
+  ###################################################################  
+  ###################################################################  
+  
+  
+  # PREPARE VARIABLES
+  X <- select(data_train,-c(pf, insample))
+  W <- as.numeric(data_train[,pf] == 1)
+  
+  ###################################################################  
+  ###################################################################  
+  
+  
+  # ESTIMATE MODEL
+  pred.forest = regression_forest(X, W)
+  rf_pred = predict(pred.forest,data_test)$predictions
+  hist(rf_pred, xlab = "predictions")
+  
+  data.out <- add_column(data_in, rf_pred)
+  filename <- paste("_aux/pred_",pf,".csv", sep="") 
+  write_csv(data.out,filename)
+}
+
+
+
+###################################################################################
+
+# Branch x week - Predictions
+rf_predict(read_csv('./_aux/instrument_1.csv'),"pf_suc_1")
+
+# Branch x week - Predictions
+rf_predict(read_csv('./_aux/instrument_2.csv'),"pf_suc_2")
+
+# Branch x week - Predictions
+rf_predict(read_csv('./_aux/instrument_3.csv'),"pf_suc_3")

### 2020-08-14 RScripts/pfv_pred.R

@@ -4,7 +4,7 @@ library(ggplot2)
 library(DMwR)
 
 # SET WORKING DIRECTORY
-setwd('C:/Users/xps-seira/Dropbox/Apps/ShareLaTeX/Donde2019')
+setwd('C:/Users/xps-seira/Dropbox/Apps/ShareLaTeX/Donde2020')
 set.seed(5289374)
 
 

### 2020-08-14 RScripts/pfv_pred_hte.R

@@ -3,7 +3,7 @@ library(grf)
 library(ggplot2)
 
 # SET WORKING DIRECTORY
-setwd('C:/Users/xps-seira/Dropbox/Apps/ShareLaTeX/Donde2019')
+setwd('C:/Users/xps-seira/Dropbox/Apps/ShareLaTeX/Donde2020')
 set.seed(5289374)
 options(digits=18)
 

### 2020-08-14 main.tex
final edits to iv_pf table

@@
- \documentclass[11pt]{article}
+ \documentclass[oneside,11pt]{article}
 
 \input{preamble.tex}
-\usepackage{anyfontsize}
 %%% HELPER CODE FOR DEALING WITH EXTERNAL REFERENCES
@@
 
-\usepackage{lmodern} 
-\usepackage{amsmath}
-\usepackage{amssymb}
-\newcommand{\wh}{\widehat}
-\onehalfspacing
-
-\usepackage{comment}
-\usepackage{subcaption,graphicx}
-
-%para esconder columnas en tablas (enrique)
-\usepackage{array}
-\newcolumntype{H}{>{\setbox0=\hbox\bgroup}c<{\egroup}@{}}
-
 %\myexternaldocument{OA}
@@
 \pagenumbering{arabic}
+\etocdepthtag.toc{mtchapter}
+\etocsettagdepth{mtchapter}{subsection}
+\etocsettagdepth{mtappendix}{none}
 
@@
 
-\section{Introduction}
+% \section{Introduction}
 
@@
 
-\newpage
 \section{Experiment} \label{Experiment}
@@
 We view these as suggestive correlations.
-The fourth coefficient does not have that problem as it conditions on clients that by their pre-determined covariates are predicted to have above the median treatment effects (in both arms).} Experience with the frequent payment contract seems to be necessary as there is no effect of the monthly payment contract on repeat pawning in the first 30 or 60 days of the contract (see Figure \ref{reincidence_before} in the Appendix.
+The fourth coefficient does not have that problem as it conditions on clients that by their pre-determined covariates are predicted to have above the median treatment effects (in both arms).} Experience with the frequent payment contract seems to be necessary as there is no effect of the monthly payment contract on repeat pawning in the first 30 or 60 days of the contract (see Figure \ref{reincidence_before} in the Appendix).
 %We also implemented an exit survey which clients filled when recovering their piece.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
+
 \section{Figures}
@@
     \begin{center}
-    \begin{subfigure}{.50\textwidth}
+    \begin{subfigure}{.40\textwidth}
       \caption{Timeline of the experiment}
@@
     \end{subfigure}
-    \begin{subfigure}{0.45\textwidth}
+    \begin{subfigure}{0.40\textwidth}
     \caption{Experiment arms}
@@
 % APPENDIX 
-
 \setcounter{table}{0}
-\renewcommand{\thetable}{\thesection.\arabic{table}}
-
 \setcounter{figure}{0}
-\renewcommand{\thefigure}{\thesection.\arabic{figure}}
-
 \setcounter{section}{0}
-\setcounter{subsection}{0}
-\renewcommand\thesection{A\arabic{section}}
-\renewcommand\thesubsection{\thesection\arabic{subsection}}
-
-\appendix
-
-\section{APPENDIX A}
+\pagenumbering{gobble}
+
+\begin{center}
+	\LARGE The limits of self-commitment and private paternalism \\[0.5em]
+	\Large{Appendix $-$ For Online Publication} \\[1em]
+	\large \author{Isaac Meza \and Joyce Sadka \and Enrique Seira}
+\end{center}
+
+%\renewcommand{\cftparskip}{0em} % NOT NEEDED
+\renewcommand\cftsecdotsep{\cftdotsep}
+\renewcommand\cftsubsecdotsep{\cftnodots}
+\renewcommand{\cftsecnumwidth}{6em}
+ \renewcommand{\cftpnumalign}{r}
+%\renewcommand{\cftsecleader}{\normalfont\cftdotfill{\cftsecdotsep}}
+
+\renewcommand{\cftsecleader}{\cftdotfill{\cftsecdotsep}\hspace{1.8em}}
+%\renewcommand{\cftsecpagefont}{20em}
+%\renewcommand{\cftfignumwidth}{6em}
+%\renewcommand{\cfttabnumwidth}{3.3em}
+
+%\tableofcontents
+\etocdepthtag.toc{mtappendix}
+\etocsettagdepth{mtchapter}{none}
+\etocsettagdepth{mtappendix}{subsection}
+
+\setstretch{0.9}
+%\renewcommand\contentsname{} % the empty name
+
+\begingroup
+\let\clearpage\relax
+%\vspace{-1.5em} % the removed space. Set as appropriate
+\tableofcontents
+\endgroup
+
+\newpage
+\pagenumbering{arabic}
+\renewcommand\thefigure{OA-\arabic{figure}}
+\renewcommand\thetable{OA-\arabic{table}}
+\renewcommand*{\thepage}{OA - \arabic{page}}
+\renewcommand\thesection{Appendix \Alph{section}.}
+\renewcommand\thesubsection{\Alph{section}.\arabic{subsection}}
+
+\section{ Further results}
 \vspace{.2in}
@@
 \end{center}
- \scriptsize
-This table explores treatment effects in ``intermediate variables''.
+
+%\textit{Do file: } \texttt{mechanisms.do}
+\end{table}
+
+\scriptsize {
+\noindent This table explores treatment effects in ``intermediate variables''.
 Each column represents a different dependent variable in an OLS regression, and each panel represents a different treatment arm-control comparison.
@@
 For Columns (7) and (8) the dependent variable it is the sum of total payments done within 230 days of the pawn divided by the size of the loan, but column (8) includes as regressors a dummy=1 if the client recovered her pawn, and its interaction with treatment.
-
-%\textit{Do file: } \texttt{mechanisms.do}
-\end{table}
-
-\newpage
+}
+
+\vspace{3ex}
+
+\vspace{.3in}
+
 \subsection{FOSD: fee forcing vs status quo financial cost distributions}
@@
 % APPENDIX B
-\setcounter{table}{0}
-\setcounter{figure}{0}
 
 \newpage
-\section{APPENDIX B: Observational analysis}
+\section{ Observational analysis}
 \label{appendix_b}
@@
 \normalsize
+\linespread{1.25}
 
@@
         \centering
-        \includegraphics[width=\textwidth]{Figuras/active_pf_suc.pdf}
+        \includegraphics[width=0.9\textwidth]{Figuras/active_pf_suc.pdf}
     \end{center}
      \scriptsize This Figure shows the presence of the frequent payment (FP) contract in 20 randomly chosen branches of Lender $P$ for a span of more than 4 years.
-A y value =1 means that in that month the FP contract was available in that branch.
+A $y$ value $=1$ means that in that month the FP contract was available in that branch.
      %\textit{Do file: }  \texttt{active\_pf\_suc.do}
@@
 
-\vspace{.2in}
 \begin{table}[H]

### 2020-09-01 main.tex
table ss with pre-experiment data

@@
 
-\title{The limits of self-commitment and private paternalism \thanks{We want to thank Craig McIntosh and Mauricio Romero for advice and encouragement.
-We want to thank also Ricardo Olivares for excellent research assistance and Erick Molina's help with formatting.
+\title{The limits of self-commitment and private paternalism \thanks{We want to thank Craig McIntosh, Mauricio Romero, and Anett John for advice and encouragement.
+Ricardo Olivares, Gerardo Melendez, and Alonso de Gortari provided excellent research assistance and Erick Molina helped with formatting.
 Jose Maria Barrero, Andrei Gomberg, Emilio Gutierrez, David Laibson, Aprajit Mahajan, Matt Rabin, Charlie Sprenger, and seminar participants at ITAM provided valuable feedback.}}
-\author{Isaac Meza \and Joyce Sadka \and Enrique Seira   \thanks{Meza: University of California at Berkeley, isaac.meza@berkeley.edu; Sadka: ITAM, jsadka@itam.mx;  
-Seira: ITAM, enrique.seira@gmail.com} }
+\author{Isaac Meza \and Joyce Sadka \and Enrique Seira   \thanks{Seira: ITAM, enrique.seira@gmail.com (corresponding author); Meza: University of California at Berkeley, isaac.meza@berkeley.edu; Sadka: ITAM, jsadka@itam.mx} }
 \date{This draft:  \today \\[2 cm]}
@@
 Many institutions ---firms, schools, financial contracts--- restrict choice using built-in commitment mechanisms which help workers, students, borrowers overcome self-control problems.
-For instance, mortgages restrict choice ``with a fixed repayment stream and mandatory principal repayment \citep{Laibson2018}''.\footnote{\cite{Laibson2018} also mentions that ``Firms do limit their workers' freedom with intermediate deadlines, progress reports, production targets'', and schools with ``pop quizzes, classroom attendance requirements, cold calling, graded problem sets, deadlines''.} At the same time  these same firms shroud these forcing mechanisms and don't market their commitment features, presumably because students, workers and borrowers ``don't welcome these paternalistic restrictions'' (\cite{Laibson2018}).
-\cite{Laibson2018} argues that this presents an important commitment puzzle: if clients were present biased and sophisticated about their self control problem they should appreciate commitment features and firms should be eager to market them.
-That this is not so suggests some clients may be naive about their self control problems, and that private paternalism may be beneficial.\footnote{\cite{Laibson2018} defines paternalism as a policy that advances an individual's interests by restricting his or her freedom, and private paternalism as paternalism implemented by private institutions.
-In this paper we will study the effect of restricting freedom of choice on pawn recovery and financing cost, not overall welfare.}
+For instance, ``[mortgages restrict choice] with a fixed repayment stream and mandatory principal repayment'' \citep{Laibson2018}.\footnote{\cite{Laibson2018} also mentions that ``Firms do limit their workers' freedom with intermediate deadlines, progress reports, production targets'', and schools with ``pop quizzes, classroom attendance requirements, cold calling, graded problem sets, deadlines''.} At the same time  these same firms shroud these forcing mechanisms and don't market their commitment features, presumably because students, workers and borrowers ``don't welcome these paternalistic restrictions''.
+\cite{Laibson2018} argues that this presents an important puzzle: clients that benefit from commitment although may underestimate its value and this have low demand for it.
+In such a case private paternalism may be beneficial.\footnote{\cite{Laibson2018} defines paternalism as a policy that advances an individual's interests by restricting his or her freedom, and private paternalism as paternalism implemented by private institutions.
+In this paper we will study the effect of restricting freedom of contract choice on two outcomes: pawn recovery and financing cost, not overall welfare.}
 
 This paper studies the benefits of restricting choice in the context of pawnbroker lending.
-Pawn loans are one of the oldest, understudied, and most prevalent forms of borrowing.
-There are more than 11,000 pawn shops across the US with 30 million clients and \$14 billion yearly revenues (in China is a 43 billion industry).\footnote{\url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.} Our partner pawn lender (henceforth Lender $P$) alone served more than 1 million clients in the last 3 years with more than 4 million contracts.\footnote{For comparison there were 2.3 million micro-finance clients in Mexico in 2009 (\cite{Pedroza:2010}).} The key characteristic of pawn loans is that the borrower leaves personal property (a pawn) as collateral in exchange of an immediate cash loan of a smaller value.
+Pawn loans are one of the oldest, most understudied, and most prevalent forms of borrowing.
+There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues (in China it is a 43 billion dollar industry).\footnote{\url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.} Our partner pawn lender (henceforth Lender $P$) alone served more than 1 million clients in the last 3 years with more than 4 million contracts.\footnote{For comparison there were 2.3 million micro-finance clients in Mexico in 2009 (\cite{Pedroza:2010}).} The key characteristic of pawn loans is that the borrower leaves personal property (a pawn) as collateral in exchange for an immediate cash loan of a smaller value.
 In our case Lender $P$ only accepts gold jewelry as collateral and approves all pawns, giving cash the equivalent of 70\% of the pawn's appraised value.
@@
 
-\begin{comment}
-Lender $P$ offers a very simple but highly collateralized contract.
-It only accepts gold jewelry as collateral and approves all gold pawns, giving in cash the equivalent of 70\% of the weighted gold value.
-The contract stipulates a 7\% monthly interest rate charged daily, and a loan term of 90 days plus 15 grace days to pay the principal and the accumulated interest.
-The client has complete flexibility to pay any number of times any amount she desires towards the recovery of her pawn, with no pre-payment penalties.
-However if the total amount of principal plus interest is not covered by the end of the 105 days, she loses her pawn and all the payments that have been done (unless she renews the loan before this by paying all accumulated interest).
-All transactions ---appraisal of the piece, loan disbursement and loan servicing--- are conducted at the branch.
-The gold collateral is highly liquid and the pawnshop has an associated business that sells the gold jewelry.
-Given the over-collateralization of the loan one would expect no moral hazard or adverse selection on the part of borrowers.
-%This lets us focus more cleanly on behavioral economics aspects.
-\end{comment}
-
 We implemented a large randomized control trial with close to 10,000 pawnshop clients in 6 branches of Lender $P$ in Mexico City.
@@
 That is, we are asking whether \textit{charging} them a 2\% late payment fee for not paying a monthly installment on time can actually \textit{decrease} total (fee-inclusive) financing cost.
-Second, would there be demand for such a frequent payment commitment contract vis-a-vis the status quo one if given choice?
-Any payment profile implemented in the commitment contract can be replicated by the borrower under the status quo contract, but the later affords more flexibility to respond to income shocks without incurring in fees.
-Third, what types of clients would demand these contracts that restrict choice?
+Second, would there be demand for such an installment contract vis-a-vis the status quo one if given choice?
+Any payment profile implemented in the commitment contract can be replicated by the borrower under the status quo contract, but the former provides commitment.
+Third, would clients who benefit from commitment the most (e.g.
+the present biased or overconfident) demand it more?
 Fourth, are late payment fees key to provide commitment or would a non-pecuniary but salient personal promise to pay provide a cost-reducing mix of commitment vs flexibility?
-Promises change behavior significantly in laboratory settings, but we know little about their effect in natural environments.\footnote{Some papers in this space are \cite{PromisesPartnerships}, \cite{Vanberg}, \cite{Belot2010}, \cite{WhyDoPromises}, \cite{FurtherPromises}, \cite{Ismayilov2017}.
-There is also some actual policy around using promises for loans: the government Mexico has created a program called ``Loans on your word'' for uncollateralized borrowing (\url{http://tiny.cc/yfmnmz}), but unfortunately there is little information about them.} Finally, is \textit{giving choice} among contracts better than forcing them into payment-commitment contracts in terms of minimizing financing costs incurred and the likelihood of recovering their pawn?
-Or on the contrary, is it better to force the commitment contract
+Promises change behavior significantly in laboratory settings, but we know little about their effect in natural environments.\footnote{%Some papers in this space are \cite{PromisesPartnerships}, \cite{Vanberg}, \cite{Belot2010}, \cite{WhyDoPromises}, \cite{FurtherPromises}, \cite{Ismayilov2017}.
+There is some actual policy around using promises for loans: the government Mexico has created a program called ``Loans on your word'' for uncollateralized borrowing (\url{http://tiny.cc/yfmnmz}), but unfortunately there is little information about them.} Finally, is \textit{giving choice} among contracts better than forcing clients into payment-commitment contracts in terms of minimizing financing costs incurred and the likelihood of recovering their pawn?
+Or on the contrary, is it better to force the installment contract
 paternalistically?
@@
 Forcing clients into frequent payment commitment contracts causes them on average to save on financing cost and to recover their pawn more.
-The effects are large: financing cost decreases by 9.5\% on average, from \$3161 to \$2857 MXN, while the likelihood of recovering their pawn increases by 25\%, from 43\% to 54\%.
-Results are robust to including transport costs of going to the branch plus losing a day's wage for each visit.
-Importantly, the benefits are distributed broadly: almost the whole distribution of treatment effects shows cost savings; however those most economically vulnerable, those that report being stressed, and those we classify as overconfident experience larger gains.
+The effects are large: financing cost decreases by 9.5\% on average (from \$3161 to \$2857 MXN), while the likelihood of recovering their pawn increases by 25\% (from 43\% to 54\%).
+Results are robust qualitatively to including transport costs of going to the branch plus losing a day's wage for each visit.
+Importantly, the benefits are distributed broadly: almost the whole distribution of treatment effects shows cost savings; however those most economically vulnerable, and notably, those we classify as overconfident, experience larger gains.
 %The commitment contract also causes payments to start 8 days earlier and be 16\% more frequent, compared to the control group.
-Treatment effects are concentrated on the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery.
+Treatment effects are concentrated in the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery.
 The fee-commitment contract induces people who would otherwise pay something towards recovery, to pay more and faster and thus recover their pawn more at a cheaper financial cost.
-Finally, borrowers assigned to the forced fee-commitment contract are 5 percentage points (55\% of the mean) more likely than the control group to ask for another loan in the future, suggesting that they liked the commitment contract more after experiencing it.
+Finally, borrowers assigned to the forced fee-commitment contract are 5 percentage points (55\% of the mean) more likely than the control group to ask for another loan in the future, suggesting that they liked the commitment contract after experiencing it.
 
@@
 Only 10\% of the group offered a choice between the monthly payment fee-commitment contract and the status-quo one chose the former.
-This is not likely driven by misunderstanding the (already simple) contract.\footnote{We posted two persons in each of the experiment's branches every day for all branch opening hours to carefully explain the contracts; material was developed to explain the differences among the two contracts, and subjects spelled back to our team the loan differences.
-Furthermore take up is systematically predicted by baseline covariates, making it less likely that it is just random mistakes.} Low demand for commitment is consistent with a large literature (\cite{Laibson2015}, \cite{Laibson2018}, \cite{John}, \cite{Ted}, \cite{Rabin2018}).
+This is not likely driven by misunderstanding the (already simple) contract.\footnote{We posted two project assistants in each of the experimental branches every day for all branch opening hours to carefully explain the contracts; material was developed to explain the differences among the two contracts, and subjects spelled back to our team the loan differences.
+Furthermore take up is systematically predicted by baseline covariates, making it less likely that these are just random mistakes.} We show further that clients that most benefit from the contract (those who are overconfident about recovering) are \textit{less} likely to demand it, echoing a result by \cite{Sprenger}.
+%is Low demand for commitment is consistent with a large literature (\cite{Laibson2015}, \cite{Laibson2018}, \cite{John}, \cite{Ted}, \cite{Rabin2018}).
 %\footnote{\cite{Alcohol} and \cite{Kremer} are some of the few instances of high demand for commitment.
@@
 %\cite{Laibson2015} shows that the lost flexibility resulting from a commitment contract can severely limit take-up when agents are naive about their self control, even though commitment could be welfare improving for them.
-Owing to this low take-up, we estimate zero average treatment effects of the \textit{fee-choice} arm on financial cost and on pawn recovery and throughout the quantile distribution.
+Owing to this low take-up, we estimate zero average treatment effects of the \textit{fee-choice} arm on financial cost and on pawn recovery throughout the quantile distribution.
 
@@
 
-Combining the forcing and the choice arms ---a unique feature of our experiment--- allows us to estimate the counterfactuals to answer the following question how much money is left on the table by the prevalence of the status-quo choice?
+Combining the forcing and the choice arms ---a unique feature of our experiment--- allows us to estimate the counterfactuals to answer the question of how much money is left on the table by giving choice to clients.
 We calculate that about 80\% of clients in the fee-choice group chose contracts that induced \textit{higher} financial cost.
@@
 
-We want to clarify that in the paper we are using the word ``paternalism'' in a restricted sense, meaning only that a large majority of clients would incur in lower financial costs from being forced into commitment contracts instead of letting them chose.
-We are not making claims about overall welfare which is a slippery concept once we accept the possibility of biased beliefs and preferences.
-
-Inspired by a significant lab experiment literature on the effects of promises on behavior, and by research showing that a small fee could drastically reduce demand for commitment of naive present-biased borrowers (\cite{Laibson2015}), we implemented a ``psychological commitment'' in the form of a salient promise to pay.
+We want to clarify that in the paper we are using the word ``paternalism'' in a restricted sense, meaning only that a large majority of clients would incur in lower financial costs from being forced into installment contracts instead of letting them choose.
+We are not making claims about overall welfare which is a slippery concept if we take into account the possibility of biased beliefs and preferences.
+
+Inspired by a significant lab experiment literature on the effects of promises on behavior, and by research showing that a small fee could drastically reduce demand for commitment of (partly) naive present-biased borrowers (\cite{Laibson2015}), we implemented a ``psychological commitment'' in the form of a salient promise to pay.
 \cite{PromisesPartnerships}, \cite{FurtherPromises}, \cite{Vanberg}, and \cite{Ismayilov2017} find that the ability to make a promise about behaving a certain way makes the individual more likely to adhere to the promised behavior.
@@
 To measure the causal effect of promises we implemented two other treatment arms.
-A \textit{promise-forcing} arm exactly analogous to our \textit{fee-forcing arm} except that instead of telling them that there is a fee if they don't pay on time, we made borrowers promise that they would pay one third of the amount in each of the 3 months, and told them that if they didn't they would have broken their promise and failed their word.
-Because salience is key we made them sign a (non-legally binding) personal promise and emphasized we were counting on them to keep their promise.
+A \textit{promise-forcing} arm exactly analogous to our \textit{fee-forcing arm} except that instead of telling them that there was a fee if they didn't pay on time, we made borrowers promise that they would pay one third of the amount in each of the 3 months, and told them that if they didn't they would have broken their promise and not kept their word.
+Because salience is key we made them sign a (legally non-binding) personal promise and emphasized that we were counting on them to keep their promise.
 A final arm (\textit{promise-choice arm}) gave clients the opportunity to choose between the \textit{Promise} contract and the \textit{Status-quo} contract.
@@
 We document two main results in the promise arms.
-First, demand for the commitment-promise contract is three times bigger than for the commitment fee contract, with 31\% take-up.
+First, demand for the commitment-promise contract is three times larger than for the commitment fee contract, with 31\% take-up.
 This difference between both choice arms suggests that clients are indeed understanding and taking into account the contractual parameters in their choice, and that the fee commitment was probably too strong from their point of view.
@@
 This paper contributes to several strands of literature.
-First, to the broad literature on commitment demand.
-A significant literature has shown that demand for commitment exists but is somewhat low in some contexts (\cite{Ashraf}, \cite{Gine}, \cite{Ted}, \cite{Royer}, \cite{Sprenger}), and high in others (\cite{Kremer},  \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}, \cite{Pascaline}).
-We add to this literature by showing that very small fees are enough to drastically reduce demand for commitment, even when commitment is beneficial, and that softer commitments in the form of non-pecuniary personal promises elicit higher demand.\footnote{Our fees are 16 times smaller than than those of \cite{John} as a fraction of the loan/goal, and five times smaller converting peso values using exchange rates.} Second, \cite{Ted} and \cite{John} show the extent of commitment needed is underestimated even among those that buy it, and that subjects hurt themselves by self-imposing too weak a commitment in the intensive margin.
-We contribute in design by not allowing choice of the extent of commitment, and methodologically by inferring subjects underestimation of the value of commitment ex-ante from forgone treatment savings, instead of from subjects failing to reach their goal ex-post.
-Third, we focus on an important new context: pawnshop borrowing.
-Pawnshop borrowing is extremely prevalent in developing countries and very worrisome to regulators, yet severely understudied.\footnote{The World Bank's CGAP recognizes the importance of pawnshop borrowing worldwide but provides no statistics or analysis on it: \url{https://tinyurl.com/ydgob8pv}.}
-
-Fourth, we study \textit{both} causal effects and selection into frequent payment commitment loan contracts.
-\cite{Ghatak} state that ``high-frequency repayment, a feature in nearly all microfinance contracts, has been largely overlooked''.
-%\footnote{\cite{LittleAtAtime} also note that ``it is especially surprising that there is so little analytical discussion of the incentive effects of the installment system''.}
-This paper fills part of this gap.
-Studying causal effects of installment payment frequency \cite{Pande} find null effects loan default, a surprising result given the prevalence of frequent payment contracts.
+First, we focus on an important new context: pawnshop borrowing.
+Pawnshop borrowing is extremely prevalent in developing countries and very worrisome to regulators, yet severely understudied.\footnote{The World Bank's CGAP recognizes the importance of pawnshop borrowing worldwide but provides no statistics or analysis on it (\url{https://tinyurl.com/ydgob8pv}).
+We could not find peer-reviewed papers about it either.} It is different from microfinance in that it deals with emergency loans, and not loans for productive investment.
+Because of this, it may draw on a more vulnerable (and potentially more unsophisticated) population.
+Moreover, the trade-off between loan rigidity and investment found for microfinance \citep{Field} may not be there for pawn borrowing.
+Second, a significant literature has shown that demand for commitment exists but is somewhat low in some contexts (\cite{Ashraf}, \cite{Gine}, \cite{Ted}, \cite{Royer}, \cite{Sprenger}), and high in others (\cite{Kremer},  \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}, \cite{Pascaline}).
+We add to this literature by showing --although we may not be the only ones-- that very small fees\footnote{For instance our fees are 16 times smaller than than those of \cite{John} as a fraction of the loan/goal, and 5 times smaller converting peso values using exchange rates.} are enough to drastically reduce demand for commitment, even when commitment is cost-reducing.
+We also show that softer commitments in the form of non-pecuniary personal promises elicit higher demand but do not affect behavior or financing costs.
+
+Third, \cite{John} and \cite{Ted} show that the extent of commitment needed is underestimated even among those that purchase commitment mechanisms, and that subjects hurt themselves by self-imposing too weak a commitment in the intensive margin.
+We contribute in design by not allowing choice of the extent of commitment, and methodologically by inferring subjects underestimation of the value of commitment ex-ante from forgone treatment savings, instead of from subjects failing to reach a goal ex-post.
+In consonance with \cite{Sprenger} but in our very different context, we find that people who most need commitment (in our case the overconfident, as they have the larger treatment effects) are also the ones less likely to demand it when given choice.
+In contrast to \cite{Sprenger}, our context allows us to focus on money savings instead of estimated utility to proxy for benefits of commitment, a narrower but more transparent measure.
+This allows us to measure effects on cost outcomes beyond take up.
+As in \cite{Rabin2018} we are able to contrast subjects' \textit{own predictions} of their behavior with their actual behavior, and how these map to outcomes, but we do it in a natural setting.
+
+Fourth, and most importantly, we study both causal effects and selection into frequent payment commitment loan contracts at the same time and for the same population in a single experiment.
+We know of no other experiment in the credit market which simultaneously combines forcing and choice arms.
+This feature, when paired with new machine learning methods to estimate heterogeneous treatment effects (\cite{atheygrf}), allows us to show whether there is positive or negative selection into beneficial contracts, and whether pawnshop clients forego money by not demanding commitment.
+In consonance with what \cite{Walters} finds in the school choice context, we find that it is \textit{not}  those who benefit most from the contract that demand it more.
+
+Studying causal effects of installment payment frequency, \cite{Pande} find null effects on loan default, a surprising result given the prevalence of frequent payment contracts.
 In contrast we find strong effects of payment frequency on decreased default.\footnote{There are many differences in context between the papers which may explain the different result.
 \cite{Pande} focus on group lending with very little default to start with (less than 1\%), while in our case almost half of loans end in default.
-We also have a larger sample and we focus on individualized loans, which may afford us stronger statistical power to detect effects.} Our result is consistent with \cite{Field} who show that delaying payment in microfinance loans increases default.\footnote{\cite{Craig} use the discipline of regular loan repayments in microfinance to remind people to save and make a savings plan, and find large increases in savings.} On the other hand, studying selection into frequent payment microfinance loans, \cite{Murdoch} conjecture that ``[frequent installment payment] structure is potentially beneficial in fostering discipline among present-biased borrowers'' and may explain why borrowers choose it.
-They show that a robust positive correlation exists between displaying present biased preferences in surveys and selecting into microfinance, which they interpret as being due to high demand for the discipline imposed by frequent payments.
+We also have a larger sample and we focus on individualized loans, which may afford us stronger statistical power to detect effects.} Our result is consistent with \cite{Field} who show that delaying payment in microfinance loans increases default.\footnote{\cite{Craig} use the discipline of regular loan repayments in microfinance to remind people to save and make a savings plan, and find large increases in savings.} On the other hand, studying selection into frequent payment microfinance loans, \cite{Murdoch} show that a robust positive correlation exists between displaying present biased preferences in surveys and selecting into microfinance, which they interpret as being due to high demand for the discipline imposed by frequent payments.
 However they acknowledge that this ``interpretation is suggestive...
 and needs to be confirmed by studies that establish causal links''.
-Our experimental \textit{is} a test of this causal link.
-We can isolate the pure effect of payment frequency on demand by randomly changing just this aspect of the contract.
-Our experimental results reject the hypothesis that microfinance (pawnshop) clients like and demand frequent payments, at least in our context.
-Importantly, our unique experimental design which simultaneously combines forcing and choice arms, paired with new machine learning methods to estimate heterogeneous treatment effects (\cite{atheygrf}), allows us to estimate whether there is positive or negative selection into beneficial contracts, and whether pawnshop clients forgo money by not demanding commitment.
-In consonance with what \cite{Walters} finds in another context, we find that it is not the case that those that benefit most from the contract demand it more.
-\cite{Sprenger} find a result that is similar to ours: that people how most need commitment (in our case the overconfident who show the greatest financial cost savings) are less likely to demand it.
-In contrast to \cite{Sprenger}, our context allows us to focus on money savings instead of estimated utility to proxy for benefits of commitment, a narrower but simpler measure.
-This allows us to measure effects on cost outcomes beyond take up and behavior.
-Our larger sample allow us to estimate heterogeneous treatment effects non-parametrically and perform counterfactuals this way.
-Finally, as in \cite{Rabin2018} we are able to contrasts subjects predictions of their behavior with their actual behavior, and how these map to outcomes, but we do it in a natural setting.
-
-Fifth, we also contribute to the literature on the effect of promises by testing their effect on the field.
-In consonance to this literature we find that people are willing and indeed voluntarily choose to make promises.
-In contrast to lab evidence however measured behavior was unchanged by promising and people did not keep their promise.\footnote{This is of course not a refutation of this literature.
+Our experiment is a test of this causal link, and it rejects the hypothesis that the majority of microfinance (pawnshop) clients demand frequent payments contracts, at least in our context.
+
+%\cite{Ghatak} state that ``high-frequency repayment, a feature in nearly all microfinance contracts, has been largely overlooked''.
+%\footnote{\cite{LittleAtAtime} also note that ``it is especially surprising that there is so little analytical discussion of the incentive effects of the installment system''.}
+%This paper fills part of this gap.
+
+Finally, even though personal promises feature prominently in microfinance guidelines\footnote{e.g.
+\url{https://grameenfoundation.org/documents/GrameenGuidelines.pdf}, p.36.} we know of no other study that has tried to isolate their effects on loan repayment.
+In concordance with this literature we find that people are willing and indeed voluntarily choose to make promises.
+We find however that measured behavior was unchanged by promising.\footnote{This is of course not a refutation of this literature by any means.
 %not least because the laboratory literature is implemented on more tightly controlled environments and focused on subtler aspects of promising, like their effects on second order beliefs and guilt aversion.
 The context is also different since
-The lab literature has focused mostly on very concrete investment games between two players and looked at the effects of promises on trust and cooperation in those games.
-However our results do provide a first piece of evidence on the limitations of using promises to change behavior in the field.}
+The lab literature has focused mostly on very structured investment games between two players and looked at the effects of promises on trust and cooperation through guilt aversion and cost of lying channels.
+In our case the bank is not a strategic player that responds to the promise or a person (although the teller is).
+However, our results do provide a first piece of evidence on the limitations of using promises to change behavior in loan contracts.}
 
@@
 
-\section{Context and Data} \label{context}
-
-\subsection{The pawn lender and high default rates}
+\section{Context} \label{context}
+
+\subsection{Pawnshop borrowing}
 
@@
 They existed in antiquity at least since the Roman Empire, and there are records of it in China about 1,500 years ago (\cite{PawnShops}).
-As explained above pawn loans involve individuals leaving valuable and liquid assets (typically jewelry) as collateral in exchange for an immediate cash loan.
-We study such  context by partnering with Lender $P$, one of the largest pawn shops in Mexico, with more than one hundred branches spanning multiple States in Mexico.
+As explained above, pawn loans involve individuals leaving valuable and liquid assets (typically jewelry) as collateral in exchange for an immediate cash loan, which is typically used to pay for emergencies.
 
@@
 Default is high in this context  compared to many papers in the microfinance literature.\footnote{\cite{Pande} study of the effect of payment frequency in a context where the rate of default is close to 1\%.}
-We study a context with high borrower default.
-60\% of clients lose their pawn in a time span of 230 from the day of pawning.
+
+In spite of it high prevalence, pawnshop borrowing has not received much attention in the economics literature.
+The closest product studied is payday loans.
+In developing countries, however payday, lending is likely small compared to pawnshop lending; the latter is faster and requires less documentation, allowing access to informal sector workers who receive their salaries in cash .
+According to \cite{Payday} to get a payday loan: ``All that a prospective borrower typically needs is a home address; a valid checking account; a driver’s license and Social Security number; a couple of pay stubs to verify employment; wages and pay dates; and minimum earnings of at least \$1,000 a month''.
+Although the author meant this list as an instance of low requirements, they would render virtually all poor households in the developing countries ineligible.
+
+Payday lending is controversial and regulators have concerns with the sophistication of borrowers using it.
+The US congress has actually banned the payday lending industry from serving active military personnel, and some states in the US have imposed zoning restrictions, interest caps, and restrictions on serial borrowing as consumer protection measures against payday lending \citep{Payday}.
+The main source of concern is whether consumers that use these loans suffer from behavioral and cognitive biases which imply sub-optimal choices, and there is some evidence for this.\footnote{\cite{Bertrand} write that ``Under the view that the people borrowing from payday lenders are making an informed, utility-maximizing choice given the constraints that they face, one  would not expect additional information disclosure about the payday product to  alter their borrowing behavior'', but to the contrary they find that simply disclosing how financing costs add up reduced demand by 11\%.
+%\cite{Meltzer} finds that payday loan access leads to increased difficulty paying mortgage, rent and utilities bills.
+} Similar concerns apply to pawnshop borrowing.
+
+\subsection{The pawn lender and high default rates}
+
+We study pawnshop borroing by partnering with Lender $P$, one of the largest pawn shops in Mexico, with more than one hundred branches spanning multiple States in Mexico.
+Our context is one with high borrower default: 60\% of clients lose their pawn in a time span of 230 days from the date of pawning.
 This default is likely inefficient since clients report a subjective value that is almost twice its gold value on average.
-It may also be detrimental from the lender's point of view since it may reduce the likelihood that the client becomes a return costumer, this may explain why Lender $P$ was interested in investigating whether a frequent payment contract would increase pawn recovery and costumer satisfaction, and whether there was demand for such a contract.
+It can also be detrimental from the lender's point of view since it may reduce the likelihood that the client becomes a return costumer; this would explain why Lender $P$ was interested in investigating whether a frequent payment contract would increase pawn recovery and costumer satisfaction, and whether there was demand for such a contract.
 
 One potential explanation for high default is that clients are really just selling their gold piece.
-This is unlikely for several reasons: (a) the reported subjective value of the pawn is larger than the loan size for 86\% of them, (b) among those that lose their pawn 58\% paid a positive amount towards its recovery and  34\% of the value of their loan (see Figure \ref{proxy_naive} in Appendix) --- this can only be rationalized if they expected to recover their pawn, (c) clients can easily sell the gold and obtain a higher amount of instant cash at gold buying stores located close to almost all our pawnshops (see Figure \ref{GoldBuyers}).
+This is unlikely for several reasons: (a) the reported subjective value of the pawn is larger than the loan size for 86\% of them, (b) among those that lose their pawn 58\% paid a positive amount towards its recovery and on average paid 34\% of the value of their loan (see Figure \ref{proxy_naive} in Appendix) --- this can only be rationalized if they expected to recover their pawn, (c) clients can easily sell the gold and obtain a higher amount of instant cash at gold buying stores located close to almost all our pawnshop branches (see Figure \ref{GoldBuyers}).
 %(d) there is a lot of engagement with the lender after pawning even for those who lost their pawn.
@@
 a teller, see Figure \ref{PawnshopPicture}).
-The appraiser weights the gold piece and runs tests on its purity.
-Based on these he assigns a gold value to the piece, stores it as collateral, and gives 70\% of the gold value of the piece in cash to the client.
-The borrower signs a 2-sheet contract with the main conditions of the contract at the branch and leaves with the cash.
+The appraiser weighs the gold piece and runs tests on its purity.
+Based on these she assigns a gold value to the piece, stores it as collateral, and gives 70\% of the gold value of the piece in cash to the client.
+The borrower signs a 2-page contract with the conditions of the loan and leaves with the cash.
 
@@
 It stipulated that the interest rate was 7\% \textit{per month} accumulated daily on the outstanding amount of the loan.
-The loan had a 90 days term with 15 days grace period, and the client could make payments at anytime with no penalty for pre-payment.
-If the client paid the principal plus the accumulated interest before those 105 days, then she received back her pawn, otherwise the pawnbroker kept the piece and any payments done.
+The loan had a 90 days term with 15 days' grace period, and the client could make payments at anytime with no penalty for pre-payment.
+If the client paid the principal plus the accumulated interest in less than 105 days, then she received back her pawn, otherwise the pawnbroker kept the piece and any payments made.
 Before the contract expired, the client had the right to renew it (using the same collateral) for another 3 months by going to the pawnshop paying the accumulated interest and signing a new contract with exactly the same terms as the original one.
@@
 
-This contract was standard in the industry, but other lenders also had contracts involving frequent installment payments.
-The clients that pawned understood its conditions (as we verified in interviews) and still decided to pawn.\footnote{90\% of clients report in our survey they have pawned before.} These clients have little or no access to other types of loans and value the convenience of pawn borrowing.
+This contract was standard in the industry.
+The clients that pawned understood its conditions (as we verified in interviews) and still decided to pawn.\footnote{90\% of clients report in our survey that they have pawned before.} These clients have little or no access to other types of loans and value the convenience of pawn borrowing.
 Potentially borrowers like it also because they are overconfident about the probability of recovering their pawn, as discussed below.
@@
 
-We worked in 6 branches of Lender $P$ of differing size and location, although for ease of implementation all of them in Mexico city.
+We worked in 6 branches of Lender $P$, of differing size and location, although for ease of implementation all of them in Mexico city.
 For these 6 branches we have two types of data, administrative data and survey data we collected for the experiment.
@@
 The administrative data contains a unique identifier of the client, an identifier of the piece she is pawning, and the transactions relating to that piece.
-In particular, the value of the piece as assessed by the appraiser, the amount of money lent (70\% of the value), and the date when it was pawned.
+In particular, the value of the piece as assessed by the appraiser, the amount of money loaned (70\% of the value), and the date of the pawn transaction.
 As described below, for our experiment the administrative data recorded the type of contract for that pawn.
-After the pawn happens, we follow each transaction related to that piece in the administrative data: when were payments made and for which amounts, whether there was default (i.e.
+After the pawn happened, we followed each transaction related to that piece in the administrative data: when payments were made and for what amounts, whether there was default (i.e.
 the client lost her pawn), and whether any late-payment fees (active for the relevant experimental arms) were imposed.
-We have this information for all the pawns that occurred in the experiment's 6 branches between August 2nd 2012 and August 13th 2013, this includes all the pawns under our experiment but also those that happened 1 month before it started and up to 8 months after it ended.
+We have this information for all the pawns that occurred in the experiment's 6 branches between August 2, 2012 and August 13, 2013, this includes all the pawns under our experiment but also those that happened 1 month before it started and up to 8 months after it ended.
 Figure \ref{exp_description}(a) shows the timing of the experiment and our admin data coverage.
-The black arrow represent the dates for which we have administrative data (before and after the experiment) while the light gray represents the duration of the experiment.
+The black arrows represent the dates for which we have administrative data (before and after the experiment) for each branch, while the light gray segments represent the duration of the experiment.
 The experiment comprises 13,444 pawns, and our administrative data cover a total of 26,179 pawns.
@@
 We had a team of enumerators in each branch collect surveys and clearly explain the contract terms to walk-in clients.
-The enumerators were inside the branch and asked clients to complete a short 5 minutes survey before going to the teller window to appraise their piece.
-The survey was short to avoid discouraging the potential clients from pawning, but at the same time it aimed to measure the following: demographics, proxies for income/wealth, education, self-control problems/present-biased preferences, experience pawning, if the family or friends commonly asked for money, how time consuming and costly was to come to the branch, the subjective probability of recovering their piece that they intended to pawn, the subjective value of their piece in money terms (for how much money would they sell it for), among others.
+The enumerators were inside the branch and asked clients to complete a 5 minute survey before going to the teller window to appraise their piece.
+The survey was implemented at the entrance of the branch before clients knew the contact that applied that day.
+It was short to avoid discouraging the potential clients from pawning, but at the same time it aimed to measure the following: demographics, proxies for income/wealth, education, self-control problems/present-biased preferences, experience pawning, if family or friends commonly asked for money, how time consuming and costly it was to come to the branch, the subjective probability of recovering the piece that they intended to pawn, the subjective value of their piece in money terms (how much money they would sell it for), among others.
 We surveyed 7,704 clients (some refused).
 %\footnote{We also surveyed clients before and after the experiment, so our survey covers a larger sample that we are not using in this paper.}.
-The appendix \ref{baseline_survey} transcribes the questionnaire in English.
-Survey response rate is 57\%, and response is not related to admin data observables (details in Table \ref{balance_response} in the Appendix).
+The Appendix \ref{baseline_survey} transcribes the questionnaire in English.
+Survey response rate is 78\%, and response is not related to admin data observables (details in Table \ref{balance_response} in the Appendix).
 
@@
 Panel A describes variables from the administrative data.
-The average loan size is \$2171 MXN (\$105 USD).
+The average loan size is \$2197 MXN (\$105 USD).
 The average number of pawns per day per branch is 33.
-Although not shown in the table, only 40\% of clients recover their pawn within 230 days.
+Only 40\% of clients recover their pawn within 230 days.
 Even those that recover their pawn tend to pay it back at the last moment, with only 17\% paying before the 90th day.
@@
 Panel B reports stats from our survey data.
-73\% of clients are women, with an average age of 44 years; 66\% of them have completed high school or more, and 90\% have pawned before, so that our sample has mostly experienced borrowers.
-Finally the subjective probability of recovery is close to 93\% on average, which contrast with the 44\% recovery that happens in reality for the pawns in the control group.
-Borrowers seem to be highly overconfident on average (more on this below).
-The average subjective value they report for the pieces is 3265 MXN, which is much larger than the average appraised gold value of 2171 MXN.
+73\% of clients are women, with an average age of 43 years; 66\% of them have completed high school or more, and 90\% have pawned before, so that our sample has mostly experienced borrowers.
+Finally the subjective probability of recovery is close to 93\% on average, which contrasts with the 44\% recovery that happens in reality for the pawns in the control group.
+Borrowers seem to be highly overconfident on average.
+The average subjective value they report for the pieces is 3069 MXN, which is much larger than the average appraised gold value of 2197 MXN.
 This makes it inefficient for them to lose it.
@@
 The population we are working with is economically vulnerable in the sense that 30\% of them could not pay either water, electricity \& gas or rent in the past 6 months.
-They often receive negative income shocks: 87\% said they are pawning because of an emergency, and only 13\% stated it was to use in a `non-urgent expense'.
+They often receive negative income shocks: 87\% said they are pawning because of an emergency, and only 13\% stated it was to use in a 'non-urgent expense'.
 %When asked why they are pawning this piece \hlgr{5\%} responded \hlgr{`lost a family member'}, \hlgr{`a medical emergency'} (\hlgr{11\%}), \hlgr{`an urgent expense'} (\hlgr{71\%}),
@@
 See section \ref{neoclasical}.
-We also report result using the subjective value of the pawn reported by the borrower in the survey with similar results.} Figure \ref{fc_hist}(a) plots a histogram of this cost in pesos for loans where the pawn was recovered or lost.
+We also report results using the subjective value of the pawn reported by the borrower in the survey with similar results.} Figure \ref{fc_hist}(a) plots a histogram of this cost in pesos for loans where the pawn was recovered or lost.
 This cost is calculated for a time period of 230 days after loan origination, as %60\% of clients actually renew the loan one time.
-some clients renew the loan.\footnote{Figure \ref{fc_pro_2_115} reports results using the first 115 days only finding similar results.} Of those who renew 83\% lose the pawn.
+some clients renew the loan.\footnote{Figure \ref{fc_pro_2_115} reports results using only the first 115 days, with similar results.} Of those who renew, 83\% lose the pawn.
 Figure \ref{fc_hist}(a) suggest that financial cost is significant, even for those that do recover their pawn.
@@
 
-\noindent \textbf{Selection of branches.} Starting September 6th 2012, we implemented the experiment in 6 branches of Lender $P$.
+\noindent \textbf{Selection of branches.} Starting September 6, 2012, we implemented the experiment in 6 branches of Lender $P$.
 The branches were selected by Lender $P$ to be dispersed across Mexico city and have varying sizes.
@@
 It has the same interest rate (7\% \textit{per month}) which accumulates daily on outstanding debt, it has the same loan size/collateral ratio (70\%), it has the same loan term (90 days, and a grace period of 15 days), and the gold pawn gets appraised in the same way by the same appraisers.
-The only difference is that it has a requirement that the client has to pay monthly: for the 3 month duration at least 1/3 of the loan value (plus accumulated interest) has to be paid before day 30th, 60th and 90th after loan disbursement.
+The only difference is that it has a requirement that the client has to pay monthly: for the 3 month duration at least 1/3 of the loan value (plus accumulated interest) has to be paid before day 30, 60 and 90 after loan disbursement.
 Failure to pay this amount triggers a penalty fee of 2\% of this minimum amount due, which is added to the amount that the client needs to pay to recover their pawn.
@@
 They deemed 2\% something that was big enough to provide commitment but small enough that if clients had an emergency and could not pay, the fee would not cause the pawn to be unrecoverable.\footnote{In contrast with \cite{John} we don't let the clients choose the size of the fee.
-As that paper shows doing this results in wrong choices by naive present biased consumers.
-Our fee is much smaller than the median in her experiment as explained above.
+That paper shows that doing this results in wrong choices by (partially) naive present biased consumers.
+Our fee is much smaller than the median in her experiment, as explained above.
 We also experimented with a contract where there was no pecuniary fee for paying late but where we clients made a personal promise to pay monthly.}
@@
 Each day the system chose which types of contracts were on offer that day in the branch, and therefore which contract the client signed.
-Branch personnel did not know which treatment would happen which day.
-They were told that there were 5 different ``types of contract-days'' and that the system chose randomly which applied any given date, and that it could happen for instance that two consecutive dates had the same contract.
+Branch personnel did not know which treatment would happen on which day.
+They were told that there were 5 different ``types of contract-days'' and that the system chose randomly which applied on any given date, and that it could happen for instance that two consecutive dates had the same contract.
 They were also told that this way of operating was in place in various Lender $P$'s branches (they did not know which ones), and that it could be in place for several months.
@@
 \vspace{.2in}
-\noindent \textbf{Treatment Arms.} We have 5 different experimental arms, which differ in which contracts were offered on a given branch-day.
+\noindent \textbf{Treatment Arms.} We have 5 different experimental arms, randomized at the branch-day level.
 
@@
     \item \textit{Fee-Forcing} arm: consisted of branch-days offering only the monthly installment contract with a fee for late payment as described above. 
-    \item \textit{Fee-Choice} arm: consisted of branch-days where the client was given \textit{a choice} between the monthly installment with fee contract, and the status quo contract.
+    \item \textit{Fee-Choice} arm: consisted of branch-days offering the client \textit{a choice} between the monthly installment with fee contract, and the status quo contract.
     \item \textit{Promise-Forcing} arm: consisted of branch-days which offered the monthly payment contract only, but where there was no fee for paying late.
@@
 It is just a \textit{personal promise}.
-If I do not comply I would have broken my word.''.
-After signing, the promise was read to the client by the appraiser.
-    \item \textit{Promise-Choice} arm: consisted on branch-days where the client was given \textit{a choice} between the promise-forcing and the status quo contract.\footnote{We did not allocate equal number of days across arms, since we were interested in having more power in some of them.
+If I do not comply I will not have kept my word''.
+After signing, the promise was read to the client by the appraiser.\footnote{Our setting does not allow us to separate if the client is making a promise to the bank teller or whether she is mentally interpreting this as an internal promise to herself as a goal.
+We thank Anett John for pointing this out.}
+
+    \item \textit{Promise-Choice} arm: consisted of branch-days on which the client was given \textit{a choice} between the promise-forcing and the status quo contract.\footnote{We did not allocate equal number of days across arms, since we were interested in having more power in some of them.
 The branch days allocated to each -- in order-- were 84, 80, 93, 68, 82.}
@@
 
-By comparing the \textit{fee-forcing} arm vs the \textit{status-quo} arm we estimate the causal effect of mandatory installment frequency which acts as a incentive to pay earlier vis-a-vis the pay-when-you-want contract.
-On the other hand, having arms where clients can choose among these contracts allows us to study client's demand for commitment to pay earlier.
+By comparing the \textit{fee-forcing} arm vs the \textit{status-quo} arm we estimate the causal effect of mandatory installment frequency that acts as a incentive to pay earlier vis-a-vis the pay-when-you-want contract.
+On the other hand, having arms where clients can choose among these contracts allows us to study clients' demand for commitment to pay earlier.
 A neoclassical consumer (with no intra-household concerns) would not voluntarily restrict her options of payment profiles (as in monthly payment contract) by being subject to fees, since she can always replicate the monthly payment profile herself under the status quo contract if she so desired.
@@
 This design also allows us to test if promises work in a natural field environment which to our knowledge has not been done.
-Promises could have larger or smaller commitment vaWe have 5 different experimental arms, which differ in which contracts were offered on a given branch-day.
-
-\begin{enumerate}
-    \item \textit{Status-quo forcing} arm: consisted of branch-days offering the status quo contract described in Section \ref{context}, and only this contract (as was standard). 
-    \item \textit{Fee-Forcing} arm: consisted of branch-days offering only the monthly installment contract with a fee for late payment as described above. 
-    \item \textit{Fee-Choice} arm: consisted of branch-days where the client was given \textit{a choice} between the monthly installment with fee contract, and the status quo contract.
-    \item \textit{Promise-Forcing} arm: consisted of branch-days which offered the monthly payment contract only, but where there was no fee for paying late.
-Instead, the client was made to sign a paper which said ``I promise to pay every month the corresponding sum of \_\_\_\_\_\_, on the dates \_\_\_\_\_\_, \_\_\_\_\_\_, and \_\_\_\_\_\_.
-This is \underline{not} a legal document and cannot be used in courts.
-It is just a \textit{personal promise}.
-If I do not comply I would have broken my word.''.
-After signing, the promise was read to the client by the appraiser.
-    \item \textit{Promise-Choice} arm: consisted on branch-days where the client was given \textit{a choice} between the promise-forcing and the status quo contract.\footnote{We did not allocate equal number of days across arms, since we were interested in having more power in some of them.
-The branch days allocated to each -- in order-- were 84, 80, 93, 68, 82.}
-\end{enumerate}
-
-By comparing the \textit{fee-forcing} arm vs the \textit{status-quo} arm we estimate the causal effect of mandatory installment frequency which acts as a incentive to pay earlier vis-a-vis the pay-when-you-want contract.
-On the other hand, having arms where clients can choose among these contracts allows us to study client's demand for commitment to pay earlier.
-A neoclassical consumer (with no intra-household concerns) would not voluntarily restrict her options of payment profiles (as in monthly payment contract) by being subject to fees, since she can always replicate the monthly payment profile herself under the status quo contract if she so desired.
-The status quo contract gives her extra flexibility to respond to negative income shocks.
-However, if clients have present biased preferences \textit{and} are sophisticated about them, they may choose the frequent payment contract as it has commitment value.
-This value would be traded off against the value of flexibility.
-
-This design also allows us to test if promises work in a natural field environmentlue that a pecuniary fee, something that we test by comparing behavior in the \textit{promise-forcing}  vs \textit{status-quo} arms.
-Panel (b) of Figure \ref{exp_description} shows how many contracts the experiment has on each arm (rectangles).
+Promises could have larger or smaller commitment value than a pecuniary fee, something that we test by comparing behavior in the \textit{promise-forcing} vs \textit{status quo} arms.
+Panel (b) of Figure \ref{exp_description} shows how many contracts the experiment has in each arm (rectangles).
 And for the choice arms, it displays in blue how many people actually chose the commitment contract.
@@
 
+\vspace{.2in}
+\noindent \textbf{Balance.} Table \ref{SS} shows that randomization worked to achieve balance across clients in the different experimental arms.
+One concern was that after learning the conditions of the contract clients could decide not to pawn.
+If they were differentially responsive to the different conditions, we could end up having different kinds of clients in the different arms.
+It turns out this was not the case.
+
+Our enumerators informed us that potential clients rarely left the branch without pawning, and that it was even less common that they did so as a function of the treatment contract.
+Lender $P$ also never complained to us that our different treatments were hurting sales.
+The data support this story as well.
+First, we cannot reject that the number of pawns per branch-day is the same across arms (Panel A).
+Panel C shows that about 97\% of people who answered our baseline survey also pawned, and that this ratio is balanced across arms.
+Second, not only are the number and shares of pawns the same across arms, but also the characteristics of clients and their pawned pieces are statistically the same across arms.
+Panel A of Table \ref{SS} tests this with administrative data, Panel B using baseline survey data for those that pawned and C without conditioning on pawning.
+.
+%The difference is that Panel B compares people that pawned, while \hl{Panel C uses clients that did not pawn.}
+Third, the characteristics of those who pawned before our experiment began are statistically the same as those during the experiment (Panel C).
+
+Finally, we also tested if the number of pawns per day for the 6 branches that participated in the experiment was different 1 month before the experiment started or 1 month after the experiment ended, relative to the days the experiment was active.
+To this end we estimated the regression\footnote{We cluster the standard errors by branch.} $Pawns \: per \: day_{jt} = \alpha_j + \gamma f(t) + \beta_b \mathbbm{1}(t \in MB)_{t} +\beta_a \mathbbm{1}(t \in MA)_{t}$, where $\alpha_j$ are branch fixed effects, $f(t)$ is a third degree polynomial in time, $\beta_b$ measures a level effect in the number of pawns per branch a month before the experiment started, and $\beta_a$ a month after.
+We estimate no difference in the number of pawns, showing that people are not leaving the branch without pawning at larger rates during the experiment ($\beta_a=-0.60$, $\beta_b=1.1$, with p-values 0.83 and 0.16, respectively).
+
+All the pieces of evidence indicate that there was no selection across arms and that experimental comparisons are internally valid.
+
 \subsection{More on implementation} \label{implementation}
@@
 We want to highlight two potential threats to the validity of our experiment.
-The first is that the client can chose to leave the branch after the appraiser values her pawn and tells her the contract terms, generating differential attrition across treatment arms.
-We anticipated this possibility and trained appraiser to say --that whatever was the contract that day-- it was the only available contract for an undetermined amount of time.
-Empirically, attrition was not a problem.
+The first discussed already is that the client can choose to leave the branch after the appraiser values her pawn and tells her the contract terms, generating differential attrition across treatment arms.
+We anticipated this possibility and trained appraisers to say --that whatever was the contract that day-- it was the only available contract for an undetermined amount of time.
+As we tested above the evidence supports the hypothesis of no differential selection.
+% Empirically, attrition was not a problem.
 Table \ref{SS} shows that the number of pawns per branch per day across treatment arms is statistically identical.
@@
 
-The second threat is clients' understanding of contract terms.
+Another threat is clients' understanding of contract terms.
 The terms need to be understood in order for choice to be meaningful, and for the monthly payment commitment contract to bite.
-We had two `check-points' to do this.
-First, two enumerators were present in each branch for the whole day during the duration of our experiment to explain to clients the contract terms.
-One of the aspects emphasized was that the frequent payment contract involved the commitment to pay \underline{each month} a third of the outstanding amount, and that there was a 2\% penalty fee (or, in the promise arms, the psychological cost of breaking a promise) for failing to do so.
+We had two 'check-points' to do this.
+First, two enumerators were present in each branch for the whole day during the duration of our experiment to explain the contract terms to clients.
+One of the aspects emphasized was that the frequent payment contract involved the commitment to pay \underline{each month} a third of the outstanding amount, and that there was a 2\% penalty fee (or, in the promise arms, the breaking of a promise) involved in failing to do so.
 Figure \ref{ExplanatoryMaterial} translates a piece of the materials we used to explain the contracts (in this case a comparison sheet used in the Promise-Choice days to compare contracts terms side to side).
 The explanation took about 3-5 minutes and was pursued until the client said she understood the contract terms.
-Students then asked clients to explain back the contract terms and corrected any misunderstandings.
+Enumerators then asked clients to explain back the contract terms and corrected any misunderstandings.
 
@@
 It was a piece of paper given to clients after their piece had been appraised and the size of the loan determined, but before they signed their contract.
-The appraised read it and asked the client to sign it as a proof of understating.
+The appraiser read it and asked the client to sign it as a proof of understating.
 The sheet clearly indicates that this contract is a monthly payment one (numeral 1), that there is a penalty of 2\% for paying late (numeral 2), and the 3 payment dates (numeral 3).
 Finally, the bottom of the Figure \ref{PaperSlip} shows the paper slip we used for the promise arms.
-The clients had to put their name in a slip of paper where they stated they promised to pay monthly.
+The clients had to put their name on a slip of paper where they stated they promised to pay monthly.
 
@@
 Results are robust to excluding them.
-In the regressions we include them and add a dummy indicating who are these clients.} %\footnote{If we restrict ourselves to pieces that fall in a single-arm (64\%), then treatment reduces the financial cost by 5.7\%, increases the likelihood of recovering their pawn by 35\%, and increases the likelihood of repeat business by 66\%.}.
+In the regressions we include them and add a dummy indicating clients who has more than one treatment in the experimental period.} %\footnote{If we restrict ourselves to pieces that fall in a single-arm (64\%), then treatment reduces the financial cost by 5.7\%, increases the likelihood of recovering their pawn by 35\%, and increases the likelihood of repeat business by 66\%.}.
 Our main outcome variables $y_{ij}$ are measures of financial cost in pesos as defined in Section \ref{FC_def}, as well as an indicator variable for client $i$ losing her pawn.
@@
 The second coefficient uses the subjective value of the pawn instead.
-In both cases we find that being assigned to the fee-forcing commitment contract causes a large reduction in the financing cost the client incurred, of 9.5\% (\$304) in the fist definition and 13.3\% (\$478) in the second one.
+In both cases we find that being assigned to the fee-forcing commitment contract causes a large reduction in the financing cost the client incurred, of 9.5\% (\$304) under the first definition and 13.3\% (\$478) under the second one.
 That is, we find that \textit{charging} clients a late payment decreases total \textit{fee-inclusive} financing cost.
@@
 Going in that direction, in a broader measure of costs, for each visit we add the self-reported transport cost plus a whole day's wage, multiplied by the number of visits.
-Adding a whole day's wage may exaggerate cost, but we still observe a reduction of this more comprehensive measure of cost caused by the frequent payment contract, although we lose more than 1/3 of the observations and it is more imprecisely estimated.
+Adding a whole day's wage may exaggerate cost, but we still observe a reduction of this more comprehensive measure of cost caused by the frequent payment contract, although we lose more than 1/3 of the observations and some precision.
 
@@
 All of them are negative.
-Figure \ref{fc_pro2}(c) uses \cite{atheygrf} generalized random forests methodology to estimate individual treatment effects, and plots the distribution of those treatment effects.\footnote{\cite{atheygrf} use random forests of honest causal trees to estimate personalized treatment effects.
-The trees are such that at each leaf (partition determined by covariates) we obtain an unbiased estimate of a treatment effect using treatment and control observations in that leaf.
-The optimal partition of leaves is that which minimizes expected mean squared error of treatment effects predictions out-of-sample.
+This motivated us to implement a finer measure of treatment effects.
+We used  \cite{atheygrf}'s generalized random forests methodology.
+The methodology uses random forests of honest causal trees to estimate personalized treatment effects.
+The method generates a partition of the space of characteristics $X$, where each element of the partition is a leaf, and each leaf contains treatment and control clients with similar characteristics $x \in X$ which are used to calculate unbiased honest treatment effects for that leaf.
+The optimal partition is that which minimizes expected mean squared error of treatment effects predictions out-of-sample.
 The tree is honest because it uses one sample to build the tree and another one to estimate treatment effects within that tree.
-After the optimal tree is build, each person in each leaf is assigned the treatment effect of that leaf.
+The trees are such that at each leaf we obtain an unbiased estimate of a treatment effect using treatment and control observations in that leaf.
 \cite{atheygrf} show that their treatment effects are asymptotically normal, which allows us to construct confidence intervals for our treatment estimate in each leaf.
-} More than 90\% of clients experienced financial cost savings in the fee-forcing group compared to the status-quo group.
-Figure \ref{HTE_fee_forcing} in the Appendix shows that the causal cost savings are largest for the more economically vulnerable, %that report at baseline that they have problems paying for services like water, electricity and rent,
-those that report being stressed, women, those take more time to go to the branch, and those displaying overconfidence about recovering their pawn (see Section \ref{behavioral} for our measure of overconfidence).
+
+Figure \ref{fc_pro2}(c) plots the distribution of those treatment effects using this machine learning methodology.
+It shows that more than 90\% of clients experienced financial cost savings in the fee-forcing group compared to the status-quo group.
+Figure \ref{HTE_fee_forcing} in the Appendix displays that the causal cost savings are larger for the more economically vulnerable, %that report at baseline that they have problems paying for services like water, electricity and rent,
+and those displaying overconfidence about recovering their pawn (see Section \ref{behavioral} for our measure of overconfidence).
 %those that have to incur in higher transport cost to go to the branch  and that asked to be sent reminders to pay, this later one being one proxy of being inattentive or sophisticated present-biased.
@@
 This result stands in contrast with \cite{Pande} who find no effect of payment frequency on default in a group lending microfinance context.
-Figure \ref{fc_pro2}(e) shows the distribution of heterogeneous treatment effects for losing the pawn: it shows that \textit{everybody's} likelihood of losing the pawn decreases.
+Figure \ref{fc_pro2}(e) shows the distribution of heterogeneous treatment effects for losing the pawn: \textit{everybody's} likelihood of losing the pawn decreases.
 %Figure \ref{HTE_fee_forcing}(b) in the Appendix shows that those we classify as present biased, those that requested to be sent a reminder to pay, and those who have more problems paying for basic services experienced the largest increases on pawn recovery.
@@
 Results are similar if we condition in the control group on those who would have paid a fee given current behavior.
-Again we acknowledge these is an endogenous sample and that the estimate may not be a causal effect.}  Figure \ref{fc_pro2}d shows that the increase in pawn recovery is robust to defining recovery using the first 120 days of the contract, or restricting to those paying a positive amount towards pawn recovery.
+Again we acknowledge this is an endogenous sample and that the estimate may not be a causal effect.}  Figure \ref{fc_pro2}(d) shows that the increase in pawn recovery is robust to defining recovery using the first 120 days of the contract, or restricting to those paying a positive amount towards pawn recovery.
 
@@
 We define a client as a repeat costumer if, after experiencing at least 75 days of the respective treatment arm, she came back and pawned a \textit{different} piece.\footnote{Results are robust to using number of days experiencing the contract larger than 75.
-We know its a different piece from it having a different weight/value.}  The left most coefficient shows that the causal effect of the fee-forcing contract on repeat pawning is an increase of 5 percentage points in the probability of being a repeat costumer, this is 55\% increase on a mean re-incidence with respect to those that got the status-quo contract.
+We know it is a different piece from it having a different weight/value.}  The leftmost coefficient shows that the causal effect of the fee-forcing contract on repeat pawning is an increase of 5 percentage points in the probability of being a repeat customer, this is 55\% increase on a mean re-incidence with respect to those that got the status-quo contract.
 This effect is not explained by clients recovering their first pawn with higher probability in the fee-forcing contract and re-pawning this same one since we make sure it is another piece (only 16\% recover their piece in the fist 75 days in the fee forcing contract).
-The second coefficient restricts the sample in the regression to those that had not recovered their pawn in the first 75 days and finds similar result.
+The second coefficient restricts the sample in the regression to those that had not recovered their pawn in the first 75 days and finds similar results.
 The third coefficient conditions on clients who recovered the pawn in both arms.
@@
 That is, those that benefit more from the fee-forcing contract are more likely to repeat.\footnote{The second and third estimate must be interpreted with care as we are conditioning on a variable that may be affected by treatment.
-We view these as suggestive correlations.
+We view these 2 coefficients as suggestive correlations only.
 The fourth coefficient does not have that problem as it conditions on clients that by their pre-determined covariates are predicted to have above the median treatment effects (in both arms).} Experience with the frequent payment contract seems to be necessary as there is no effect of the monthly payment contract on repeat pawning in the first 30 or 60 days of the contract (see Figure \ref{reincidence_before} in the Appendix).
@@
 The transaction costs of obtaining another loan are likely larger than incurring in this fee.
-So of the monthly payment makes the current loan ``smaller'' it is probably better to skip the monthly payment and incur in a fee than to get an additional loan.
+So if the monthly payment made the current loan ``smaller'' it is probably better to skip the monthly payment and incur in a fee than to get an additional loan.
 Third, we find larger effects of repeat buying for clients that experienced larger treatment effects, which the alternative explanation cannot explain.
-Fifth, the effect is present if we condition on clients that recovered their pawn (so its not driven by pawn recovery)\footnote{This in effect conditions on treatment and control clients that recovered their pawn.
-We are aware that we are conditioning on an endogenous variable and this must be interpreted as a correlation only.}.
+Fourth, the effect is present if we condition on clients that recovered their pawn (so it's not driven by pawn recovery).
 Finally, we were able to obtain observational data for all Lender $P$'s branches for the period January 2016 to May 2020, during which Lender $P$ expanded the new frequent payment contract.
-Using an instrumental variable strategy that exploits the expansion and availability of the frequent payment contract across branches, we show that being exposed to the frequent payment contract leads to an increase of 50 percentage points in the likelihood that in the subsequent pawn the frequent payment contract is chosen when both the status-quo one and the frequent payment contract are available  (see Appendix \ref{appendix_b}).
+Using an instrumental variable strategy that exploits the expansion and availability of the frequent payment contract across branches, we show that being exposed to the frequent payment contract leads to an increase of 50 percentage points in the likelihood that in the subsequent pawn the frequent payment contract is chosen when both the status-quo one and the frequent payment contract are available (see \ref{appendix_b}).
 This choice cannot be explained by the need of another loan, since it is about \textit{which specific type} of loan the clients chooses conditional on getting one.
@@
 This is not the case.
+We also find that clients in the choice arm achieved no better outcomes than those in the status quo group.
 
@@
 
-To study demand for commitment, in one experimental arm, we let clients freely choose between the two types of contract: the fee-forcing commitment contract or the status-quo contract.
-In spite of broadly distributed benefits of the fee-forcing commitment contract we documented above, 90\% of clients chose \textit{not} to have it, they instead preferred the status-quo one.
+\noindent \textbf{Low demand for commitment:} To study demand for commitment, in one experimental arm, we let clients freely choose between the two types of contract: the fee-forcing commitment contract or the status-quo contract.
+In spite of broadly distributed benefits of the fee-forcing commitment contract we documented above, 90\% of clients chose \textit{not} to have it, preferring the status-quo contract.
 As explained above we are fairly confident this was not because a lack of understanding of the contracts.
 
-What can explain this low demand?
+\vspace{.1in}
+\noindent What can explain this low demand?
 In the spirit of \cite{Blumenstock} we try to differentiate between explanations.
@@
 Even if the fee forcing contract generates cost savings on average, clients with risk averse preferences may not demand it if they perceive higher risk from it.
-Alternatively, even risk-neutral agents may not demand it if the cost of lost flexibility is high.
-If clients, for instance, face large and frequent income shocks which make it hard to repay monthly.\footnote{We don't observe income shocks in our data, making is hard to quantify how important they are.
-91\% of those in the fee-forcing arm incurred a fee, which suggests that shocks are not uncommon.} Below we focus on some explanations of low demand, while Section \ref{model} explores theories that can explain all the findings at the same time.
-
-\subsubsection{Behavioral explanations} \label{behavioral}
+Alternatively, even risk-neutral agents may not demand it if the cost of lost flexibility is high or if they have high temporal discount rates and prefer to pay later.
+%If clients, for instance, face large and frequent income shocks which make it hard to repay monthly.\footnote{We don't observe income shocks in our data, making is hard to quantify how important they are.
+91\% of those in the fee-forcing arm incurred a fee, which suggests that shocks are not uncommon.}
+Although the evidence that follows undermines several explanations, the tests we can conduct given the data are not sharp enough to leave a single explanation standing.
+Section \ref{model} lays our a simple theory (namely present bias with partial naivete) which fits all the 6 main findings of the paper.
+Given its parsimony and explanatory power, we submit that it is the most suitable explanation for our results.
+
+\subsubsection{Behavioral: overconfident borrowers demand less (but benefit more)} \label{behavioral}
 
 The leading behavioral explanation in the literature for low demand for commitment is present biased preferences with naivete (e.g.
-\cite{Rabin2018}, \cite{John}, \cite{Laibson2018})  \cite{Laibson2015} shows that the lost flexibility resulting from a commitment contract can limit take-up especially severely when agents are naive about their self control problem.
-In our context if consumers are naive about their present bias, they would plan to save more (or spend less) than what they actually end up saving, thus making it be harder to recover their pawn.
+\cite{Rabin2018}, \cite{John}, \cite{Laibson2018})  \cite{Laibson2015} shows that the lost flexibility resulting from a commitment contract can limit take-up especially severely when agents are (partially) naive about their self control problem.
+In our context if consumers are (partially) naive about their present bias, they would plan to save more (or spend less) than what they actually end up saving, thus making it be harder to recover their pawn.
 This under-saving will be mitigated in the fee forcing contract since the fee makes them save money to pay part of the loan periodically.
-Section \ref{model} formalizes this in a model.
+\ref{appendix_c} formalizes this in a model.
 Another behavioral explanation is that clients may underestimate the likelihood and severity of negative income shocks.
@@
 Recall that in the control group the client's subjective probability of recovery is on average 93\%, while actual recovery is just 44\%.
-A further piece of evidence consistent with underestimating negative income shocks is that a large number of people (31\%) in the control group pay a positive amount toward pawn recovery but end up losing their pawn anyway.
+A further piece of evidence consistent with underestimating negative income shocks and with present bias with partial naivete is that a large number of people (31\%) in the control group pay a positive amount toward pawn recovery but end up losing their pawn anyway.
 
@@
 We define as overconfidence as the reported subjective probability of recovery minus the predicted probability based on the client's characteristics, $P^s_i-\widehat{P_i(X_i)}$.\footnote{We predict $\widehat{P_i(X_i)}$ in two steps.
-In step one we use Lasso with with cross validation to tune the regularization parameter to select the most predictive variables $X$.
+In step one we use Lasso with cross validation to tune the regularization parameter to select the most predictive variables $X$.
 The typical present bias question as in \cite{Ashraf} was eliminated in this step.
@@
 Figure \ref{oc_hist} plots a histogram of $OC_i$ and shows that the overwhelming majority display overconfidence, and a large fraction overestimate recovery by more than 50 percentage points.
+Our measure of overconfidence is useful especially when there is limited time for a detailed survey.\footnote{It may be more useful than a simple elicitation of present bias as in \cite{Ashraf}.
+We find that 15\% of clients are classified as present biased using this measure of preference reversal.
+This level is similar to the number \cite{Ashraf} find but small to explain no take-up of commitment for 90\% of clients.
+This measure was not correlated with take up of commitment in our sample.} First it is very prevalent, which makes it promising to explain the overwhelming prevalence of low take up.
+Second, it is easy to measure.
+Third, it is predictive of take-up in an intuitive way.
+Finally, overconfidence in recovery is implied by present bias with (partial) naivete but also by biased expectations of negative income shocks, thus capturing both kinds of bias.
 
@@
 Extrapolating individual treatment effects of the fee-forcing contract vs the status quo one to the choice arm (see below for more detail), and using them as a dependent variable we find that overconfident borrowers benefit \textit{more} from the commitment contract, with 24.8\% (=\$30/\$121) more savings (columns 5 and 6).
-Thus while we predict the overconfident benefit more from commitment, they demand less.
-
-\vspace{.2in}
-Our measure of overconfidence is useful especially when there is limited time for a detailed survey.\footnote{It may be more useful than a simple elicitation of present bias as in \cite{Ashraf}.
-We find that 15\% of clients are classified as present biased using this measure of preference reversal.
-This level is similar to the number \cite{Ashraf} find but small to explain no take-up of commitment for 90\% of clients.
-This measure was not correlated with take up of commitment in our sample.} First it is very prevalent, which makes it promising to explain the overwhelming prevalence of low take up.
-Second, it is easy to measure.
-Third, it is predictive of take-up in an intuitive way.
-Finally, overconfidence in recovery is implied by present bias with naivete but also by biased expectations of negative income shocks, thus capturing both kinds of bias.
+Thus while we predict the overconfident benefit more from commitment, they demand less of it.
 
@@
 We could then ask what would risk aversion have to be in order to justify the client choosing the fee-commitment contract distribution of costs over the distribution associated with the status quo contract, $F_{sq}(FC)$.
-Framed as a choice among cost distributions, we can calculate what risk aversion is needed to rationalize the choice of the status quo contract.
-This exercise of course assumes --as it is common in economics-- that clients know the distribution of financial cost, that it is common across consumers (although this can be relaxed), and that this cost distribution is the only difference among contracts.
-Fortunately for us it turns out that one distribution first-order-stochastically dominates the other, we do not need to calibrate a specific utility function or use a parametric distribution function in order to rank them in terms of expected utility.
-We use the fact that if the utility $u(FC)$ is decreasing in $FC$ and $F_{fee}(FC) \geq F_{sq}(FC)$ for all $FC$, then $E_{fee}[u(FC)] \geq E_{sq}[u(FC)]$.\footnote{See the appendix for the proof.} That is any expected utility maximizer who dislikes paying higher financing cost, regardless of the concavity of his utility function, will prefer the fee-commitment distribution of financial cost.
+Framed as a choice among cost distributions, we can calculate what risk aversion is needed to rationalize the overwhelming choice of the status quo contract over the fee-commitment contract.
+This exercise of course assumes --as is common in economics-- that clients know the distribution of financial cost, that the distribution is common across consumers (although this can be relaxed), and that this cost distribution is the only difference among contracts.
+
+Fortunately for us, it turns out that one distribution first-order-stochastically dominates the other, obviating the need to calibrate a specific utility function or use a parametric distribution function in order to rank them in terms of expected utility.
+We use the fact that if the utility $u(FC)$ is decreasing in $FC$ (i.e.
+clients dislike paying higher financing cost) and $F_{fee}(FC) \geq F_{sq}(FC)$ for all $FC$, which we actually verify in our data, then $E_{fee}[u(FC)] \geq E_{sq}[u(FC)]$, that is any expected utility maximizing client risk averse consumer should choose the fee-forcing contract as a result of the distribution of cost payoffs.\footnote{See the Appendix for the proof.
 Figure \ref{ecdf_fc} in the Appendix shows that indeed $F_{fee}(FC) \geq F_{sq}(FC)$.
-Moreover, Table \ref{stochastic_dominance} shows that this holds also for an overwhelming majority of sub-populations.
+Table \ref{stochastic_dominance} shows that this holds also for sub-populations of different characteristics.}.
+Thus, risk aversion cannot explain the low demand for commitment under the assumptions of this exercise.
 
@@
 That is, the fee-commitment contract may provide too much commitment which is costly because the client may be forced to incur in late payment fees if he experiences a negative income shock.\footnote{Note that income shocks that affect the ability to pay the entire loan are a worry for both the fee-forcing contract and the status quo one, and should not make one contract more favorable than the other.} While we cannot rule out that income shocks combined with lost flexibility of the contract explain the low demand, we think it is unlikely.
-First, we showed above clients report a subjective probability of recovery of 93\% on average, which suggests they are not too worried about income shocks.
+First, we showed above that clients report a subjective probability of recovery of 93\% on average, which suggests they are not too worried about income shocks.
 Second, the fear of incurring fees is quantitatively not enough of a concern when compared to the savings they are experiencing.
@@
 %This compares favorably to the \hlgr{\$11.6 + \$62.3)} pesos transportation / transaction cost of one.
-To make this concrete, we calculated what the financing cost of the fee-commitment contract would be if all its clients incurred in \textit{all} potential fees (while keeping payment profiles and pawn recovery constant) and added these fictitious fees to financing cost for those in the fee-forcing arm, thus artificially inflating their cost.
+
+To make this concrete, we calculated what the financing cost of the fee-commitment contract would be if \textit{all} its clients incurred in \textit{all} potential fees (while keeping payment profiles and pawn recovery constant) and added these fictitious fees to financing cost for those in the fee-forcing arm, thus artificially inflating their cost.
 We then re-estimated the quantile treatment effects analogous to Figure \ref{fc_pro2}(b) with this inflated financial cost.
@@
 Figure \ref{fc_allfee} presents the results.
-We find that even in this extreme scenario, tilted against the fee-forcing contract, the estimated effect still implies cost savings from the fee-forcing contract at the mean, 25$^{th}$, 50$^{th}$, and 75$^{th}$ percentiles.\footnote{Recall that the differences in financing cost already takes into account the fact that clients in the fee forcing contract sink more pre-payments than those in the status quo contract, and that those prepayments are lost if the loan is not fully paid back.}  Although these arguments are not definitive, they suggest that low demand for commitment may be driven by more than the anticipation of lost flexibility.
+We find that even in this extreme scenario, tilted against the fee-forcing contract, the estimated effect still implies cost savings from the fee-forcing contract at the mean, 25$^{th}$, 50$^{th}$, and 75$^{th}$ percentiles.\footnote{Recall that the differences in financing cost already takes into account the fact that clients in the fee forcing contract sink more pre-payments than those in the status quo contract, and that those prepayments are lost if the loan is not fully paid back.}  Although these arguments are not definitive, they suggest that low demand for commitment may be driven by more than the anticipation of lost flexibility implied by a small fee.
 
@@
 Even among those that recover their pawn, only 42\% pay before the 90$^{th}$ day.
-Table \ref{mechanisms} shows that clients assigned to the fee-forcing contract front load their payments, starting their first payment earlier and finishing to pay earlier too.
+Table \ref{mechanisms} shows that clients assigned to the fee-commitment contract front load their payments, starting their first payment earlier and finishing paying earlier too.
 However, clients may dislike front loading payments if their time preference discount rate is high.
@@
 We did this and obtained
-The discount rate that rationalizes a zero effect is a staggering 8,190 percent per year.
+We calculate that the discount rate that is necessary to compensate for the savings in financial cost (i.e.
+that makes the estimated $\beta$ in equation \ref{basic_reg} equal to zero when financing cost --using different $r$'s-- is the dependent variable) is a staggering 8,190 percent per year.
 We find this discount rate implausibly high even for this credit constrained population\footnote{For comparison, \cite{Levin} find that a discount rate of 1,415 per year for subprime borrowers in the US is too high to be believable.}, casting doubt on high discount rates as explanation for low demand for commitment.
@@
 
+%\vspace{.2in}
+%\noindent All in all, present bias with (partial) naivete is the more likely explanation for low commitment demand in our case.
+Moreover, Section \ref{model} shows that present bias with (partial) naivete is able to qualitatively explain all the main findings of the paper, not just low demand for commitment.
+
 \vspace{.2in}
-\noindent All in all, present bias with naivete is the more likely explanation for low commitment demand in our case.
-Moreover, Section \ref{model} shows that present bias with naivete is able to qualitatively explain all the main findings of the paper, not just low demand for commitment.
-
 \subsection{The effect of choice on pawn recovery and financial cost} \label{effect_choice}
@@
 When preferences or income streams are heterogeneous, and consumers are neoclassical, giving choice among contracts is often a welfare increasing strategy.
-Consumers would chose the contract that best fits their needs.
+Consumers would choose the contract that best fits their needs.
 This holds also in most simple models of present bias preferences if consumers are sophisticated about their present bias.
 %Actually, it could be the case that the opportunity of choosing itself could affect behavior.
-But when consumers are overconfident about their ability to save cash to pay back the loan, free choice could be a sub-optimal policy from the point of view of the client's long run self, and match the clients with a more costly contract.
-Defenders of choice make another subtler point: that even if take up of the commitment-fee contract is low, the sole fact of having choice could potentially change behavior (\cite{Dalboetal:2010}, \cite{Sjostrometal:2018}, \cite{Tlaxcala}).
-
-Giving clients the option of choosing among the fee-forcing and the status quo contract does \textit{not} lead to lower financial cost compared to forcing them into the status-quo contract.
+But when consumers are overconfident about their ability to save to pay back the loan, free choice could be a sub-optimal policy from the point of view of the client's long run self, and could match clients with  more costly contracts.
+Defenders of choice make another subtler point: that even if take up of the commitment-fee contract is low, the sole fact of \textit{having} choice could potentially change behavior or welfare (\cite{Dalboetal:2010}, \cite{Sjostrometal:2018}, \cite{Tlaxcala}).
+
+\vspace{.2in}
+\noindent \textbf{Choice has no effect on pawn recovery or financial cost.} We find that giving clients the option of choosing among the fee-commitment and the status quo contract does \textit{not} lead to lower financial cost compared to forcing them into the status-quo contract.
 Nor does it lead to higher pawn recovery.
 The hollow circles in Figure \ref{fc_pro4}(a) show zero average effects for the different definitions of financial cost analogous to the ones described above.
-Figure \ref{fc_pro4}(b) shows further that the null effect happens for the 15$^{th}$, 25$^{th}$, 50$^{th}$ 75$^{th}$, and 85$^{th}$ percentiles.\footnote{The few that selected the fee-commitment contract (the solid black squares) do enjoy cost savings of 1005 MXN, which compares favorably to the 304 MXN in the fee-forcing arm (as a fraction of the loan the numbers are 41.5\% and 12.5\%), but this combines the selection and treatment effects.} %Figure \ref{heterogeneous_te_4} plots the distribution of treatment effects and finds that the distribution offering choice actually \textit{increased} financial cost and default for about half of clients compared to being assigned the status-quo contract.
+Figure \ref{fc_pro4}(b) shows further that the null effect happens for the 15$^{th}$, 25$^{th}$, 50$^{th}$ 75$^{th}$, and 85$^{th}$ percentiles.\footnote{The few clients that selected the fee-commitment contract (the solid black squares) do enjoy cost savings of 1005 MXN, which compares favorably to the 304 MXN in the fee-forcing arm (as a fraction of the loan the numbers are 41.5\% and 12.5\%), but this combines the selection and treatment effects.} %Figure \ref{heterogeneous_te_4} plots the distribution of treatment effects and finds that the distribution offering choice actually \textit{increased} financial cost and default for about half of clients compared to being assigned the status-quo contract.
 Those tended to be the less economically vulnerable and more educated, \hl{women}, and those whose family typically asks them for money.
@@
 This is not the first paper to find low demand for commitment, however it is the first we know of that can compare choice vs forcing.
-The fact that the fee-forcing contract lowers financial costs for almost all clients, together with the fact that only 10\% choose it must mean that many consumers are choosing contracts with higher financial costs for them.
-We can ask how many consumers seem to be making a cost increasing choice and how much money are they leaving on the table.
+The fact that the fee-forcing contract lowers financial costs for almost all clients, together with the fact that only 10\% choose it must mean that many consumers are choosing contracts with higher financial costs for themselves.
+We now present an estimation of how many consumers seem to be making a cost increasing choice, and how much money they seem to be leaving on the table.
 We conduct two exercises.
@@
 \vspace{.2in}
-\noindent \textbf{Are there ``mistakes'' in choice?} Answering this question requires calculating a counterfactual: for each client in the choice arm we want to know how much cost savings she would have had she chosen the opposite contract.
+\noindent \textbf{Do choices increase financing cost?} Answering this question requires calculating a counterfactual: for each client in the choice arm we want to know how much cost savings would she have gained had she chosen the opposite contract.
 We do this in two steps.
-First, using the honest causal forests method of \cite{atheygrf} described above we calculate the causal effect on financing cost of getting the fee-forcing contract instead of the status quo contract for a client with characteristics $x_i$ \textit{in the forcing arms}, we call it $TE^{fee}_{i}(x_i)$.
-Recall that \cite{atheygrf}'s method uses causal trees to generate a partition of the space of characteristics $x$, where each element of the partition is a leaf, and each leaf contains treatment and control clients with similar characteristics $x$ which are used to calculate unbiased honest treatment effects for that leaf.
-Second, we predict treatment effects for clients \textit{in the choice arm} using the partition into leaves and the treatment effect associated with the leaf obtained in step 1, that is client $j$  is imputed the treatment effect of the leaf corresponding to her characteristics $x_j$.
-We call this counterfactual treatment effect $\widehat{TE}^{fee}_{i}(x_j)$.
+Step 1, using the honest causal forests method of \cite{atheygrf} described above and the two forcing arms we calculate the causal effect on financing cost of getting the fee-commitment contract instead of the status quo contract for a client $i$ with characteristics $x_i$; call it $TE^{fee}_{i}(x_i)$.
+Then in step 2 we predict treatment effects for clients \textit{in the choice arm} using the partition into leaves and the treatment effect from step 1, that is client $j$ is imputed the treatment effect of the leaf corresponding to her characteristics $x_j$.
+We call this counterfactual treatment effect $\widehat{TE}^{fee}_{j}(x_j)$.
 This is precisely the counterfactual we wanted.\footnote{This extrapolation of the treatment effects assumes that choice itself --conditional on a given contract-- does not affect behavior.
@@
 Note that although the extrapolation is to another population, by randomization it is a statistically identical population with common support.} Armed with this, we say that a client made a ``mistake'' if either she chose the status quo contract and her $\widehat{TE}^{fee}_{i}$ is negative (i.e.
-more cost saving from the fee contract), or if she chose the fee-commitment contract and $\widehat{TE}^{fee}_{i}$ is positive, meaning that financial cost are larger for the fee-commitment contract.
-When a client made a choice mistake, we say that the peso-size of it is $|\widehat{TE}^{fee}_{i}|$.
+more cost saving from the fee contract), or if she chose the fee-commitment contract and $\widehat{TE}^{fee}_{i}$ is positive, (i.e.
+financial costs are larger for the fee-commitment contract).
+When a client made a choice mistake, we say that its peso-size is $|\widehat{TE}^{fee}_{i}|$.
 
@@
 
-Figure \ref{choose_wrong}(a) plots in the left Y-axis the fraction of clients that made a choice ``mistake'' and on the right Y-axis the peso size of the mistake.
-In the X-axis it varies the threshold $z$ of what we classify as a mistake.
-When $z=0$, we calculate that about 80\% of clients in the fee-choice group chose contracts that induced \textit{higher} financial cost (90\% confidence interval [45,94]).
+Figure \ref{choose_wrong}(a) plots on the left Y-axis the fraction of clients that made a choice ``mistake'' and on the right Y-axis its size in pesos.
+On the X-axis it varies the threshold $z$.
+When $z=0$, we calculate that about 80\% of clients in the fee-choice group chose contracts that induced \textit{higher} financial cost.
+%(90\% confidence interval [45,94]).
 Most mistakes are failures to choose the fee-commitment contract (92\%), while only 8\% of those who chose the fee-commitment contract would have been better in the status-quo one.
-The average mistake in pesos is \$238 (90\% confidence interval [140,390]).
-Figure \ref{choose_wrong}(b) separates the analysis for those we classify as overconfident about recovering their pawn vs the rest.
-It shows that there are about 11 percentage points more mistakes in the overconfident population (when $z=0$).
-
-All the above suggests that forcing clients into commitment contacts may reduce financial cost for the overwhelming majority of clients.
-Figure \ref{choose_wrong}(c) calculates what fraction of clients would be made better off if we forced them to the fee-commitment contract: 92\% when $z=0$, and they would on average have savings of 232 MXN.
+The average mistake in pesos is \$238.
+%(90\% confidence interval [140,390]).
+Figure \ref{choose_wrong}(b) plots the same curve, but separately for overconfident and non-overconfident clients, using the definition of overconfidence in Section \ref{behavioral}.
+It shows that there are about 11 percentage points more mistakes in the overconfident population (when $z=0$), an important difference.
+
+The findings above suggest that forcing clients into commitment contacts may reduce financial cost for the overwhelming majority of clients.
+Figure \ref{choose_wrong}(c) calculates what fraction of clients would be made better off if we forced them into the fee-commitment contract.
+We find that 92\% would be better off (using $z=0$), and they would on average have savings of 232MXN.
 This conclusion is in line with a recent paper by \cite{John}.
-In a savings context, she finds that when commitment is on the menu a majority of subjects wrongly choose to little commitment.
-She concludes this by observing high levels of default even with late payment fees, whereas we work directly with estimated counterfactual treatment effects.
+In a savings context, she finds that when commitment is on the menu a majority of subjects wrongly choose too little commitment and fail to reach their savings goals.
+It is also in line with \cite{Sprenger} who show that the more naive about their present bias are the ones who demand less commitment.
 
 \vspace{.2in}
-\noindent \textbf{Is there positive selection on treatment effects?} The previous exercise consisted on extrapolating treatment effects from the no-choice arms to the choice arm.
-Here we do the converse.
+\noindent \textbf{Is there positive selection on treatment effects?} The previous exercise consisted of extrapolating treatment effects from the no-choice arms to the choice arm.
+Here we do the reverse.
 First, we estimate a flexible model of take-up of the fee commitment contract \textit{in the choice arm} using random forests and obtain for a client with characteristics $x_i$ a probability $P(x_i)$ of choosing the fee-forcing contract.
-We then use this model to predict the counterfactual probability of a client with characteristics $x_j$ choosing the fee-commitment contract in the no choice-arms if she would have been given the choice, what we call $\widehat{P(x_j)}$.\footnote{Our random forest take-up model has a good out-of-sample fit with an out-of-sample AUC of 0.85.
-We think we are not introducing too much noise by this extrapolation.} Second, armed with this prediction in the no-choice arms, we can ask the following: is it true that people with larger fee-forcing contract treatment effects (i.e.
+We then use this model to predict the counterfactual probability of a client with characteristics $x_j$ choosing the fee-commitment contract \textit{in the no choice-arms} if she would have been given the choice, what we call $\widehat{P(x_j)}$.\footnote{Our random forest take-up model has a good out-of-sample fit with an out-of-sample AUC of 0.85.} Second, armed with this prediction in the forcing arms, we can ask the following: is it true that people with larger fee-forcing contract treatment effects (i.e.
 more cost savings) are more likely to have demanded the fee-forcing contract if choice had been given to them?
 
-Figure \ref{choose_wrong}(d) plots $\widehat{P(x_i)}$ in the X-axis, and the heterogeneous treatment effects we estimated in section \ref{TE_fee-forcing} in the Y-axis.
+Figure \ref{choose_wrong}(d) plots $\widehat{P(x_i)}$ on the X-axis, and the heterogeneous treatment effects we estimated in Section \ref{TE_fee-forcing} on the Y-axis.
+It plots a binscatter that splits the X-axis into 100 percentiles bins of predicted take-up probability and for each bin averages the financial cost treatment effects.
 If it was true that those with larger cost savings have larger demand for the fee-commitment contract, we would expect a negative slope (recall that more savings mean lower financial cost in the Y-axis).
 This is not what we find.
-Figure \ref{choose_wrong}(d) is a binscatter that splits the X-axis in 100 percentiles bins of predicted take-up probability and for each bin averages the financial cost treatment effects.
 Using all clouds we estimate a slope close to zero in the relationship.
@@
 
-This section uses a model to interpret our empirical results.
+Although the empirical results are striking and stand alone, this section refers to the model of \cite{John} to interpret our empirical results.
 The model is stylized but incorporates important features of our context.
-First, it allows for negative income shocks which we think are prevalent in this population (that's why they pawn in the first place)\footnote{71\% say they need the money for an emergency.}.
-The shock generates a cost of committing to monthly payments and could potentially be a reason for low take up.
-Second, it features clients with present biased time preferences and allows for naivete about them.
-As we discuss below these two features parsimoniously explain several facts about the context ---e.g.
-overconfidence in recovering the pawn, and large inefficient default---  and about the results ---e.g.
-forcing commitment seems to help, and that there is also some (although small) demand for commitment at no benefit for neoclassical consumers.
-Third, it incorporates the fact that the pawned piece is more valuable than the loan.
-Fourth, it allows for a simple way to model commitment afforded by late payment fees.
-Nonetheless, the model abstracts from several details of the context.
+It allows for negative income shocks which we think are prevalent in this population.
+%The shock generates a cost of committing to monthly payments and could potentially be a reason for low take up.
+It also features clients with present biased time preferences --allowing for partial naivete-- choosing to save to pay for an expense, and with the opportunity to make a commitment to save and pay.
+These two features parsimoniously explain several facts about the context --like overconfidence in recovering the pawn--, and about the results --e.g.
+that forcing commitment seems to help.
+We intend the model only as a very stylized approximation to our context, and we use it only to help us organize the interpretation of the empirical results, not as a literal description of reality.
+%Third, it allows for a simple way to model commitment afforded by late payment fees.
+%Nonetheless, the model abstracts from several details of the context.
 Even with these abstraction it allows us to explain our six main results listed in Section \ref{explanations_recap} below.
 
-\subsection{A simple model} \label{model_detail}
-
-We use the model of \cite{John} and refer the reader to that paper for more detail, justification of assumptions and some of the proofs.
-The model has three periods and linear utility.\footnote{This does not map perfectly to our 3 period contract, but it is enough to generate the results we need.} Period $t=0$ is a planning period where the client is either allocated to the status quo, the fee-forcing contract, or a choice between the two.
-Period $t=1$ is the savings decision period, and $t=2$ in the pawn recovery (loan payment) period.
-In period 1 the client receives her income $y_1=1$, or gets zero with probability $\lambda$.
-She can consume ($c_1$) or save ($s_1$) part that income.
-In period 2 the client gets her savings from period 1, and again receives income of either $y_2=1$, or zero with independent probability $\lambda$.
-In this last period, she decides whether to use income and savings for consumption $c_2$ and/or for paying back the loan of size $p \in(1,2)$ to recover the pawned piece valued at $b>p$.
-In this simple set up we model the fee-commitment contract as a contract that imposes a fee of size $F$ if the client fails at $t=1$ to save $s1=p-1$ pesos, which is what is needed to pay the loan back when there are no shocks.
-In period $t=0$ she evaluates her welfare as $E[c_1+c_2]$, were for simplicity we have set the time discount to one.
-We also assume the interest rate is one.
-We introduce present biased preferences by assuming the following utility function $U_t=c_t+\beta \: \sum_{k=t+1}^{2} E[c_k]$, with $\beta<1$ indicating present bias.
-A naive client perceives she is not so present biased and instead of $\beta$ uses $\hat{\beta} \in (\beta,1]$.
-
-Note that under these assumptions it is efficient at $t=0$ to recover the loan since $b>p$ and since there is no discounting at $t=0$.
-Because $b>1$, paying back the loan requires that there is no negative shock in any period and that $s_1>0$.
-Because $\beta<1$ at $t=1$ the client will not send savings in excess of what is needed to recover the loan: $s_1=p-1$.
-This parsimonious model implies the following results:
-
-\vspace{.2in}
-\noindent \textbf{Result 1: Present biased clients default more.} Under the status-quo contract, absent shock realizations, present biased clients (sophisticated or naive) with $\beta<\beta_{SQ}<1$ will lose their pawn, while clients with no present bias will not.\footnote{$\beta_{SQ}=\frac{p-1}{\lambda(p-1)+(1-\lambda)(b-1)}$.
-See Proposition 1 in \cite{John}.}
-
-\vspace{.1in}
-\noindent \textbf{Result 2: Forcing present-biased clients into the fee-commitment contract reduces default.} Imposing a fee $F>0$ for late payments weakly decreases default (for present biased clients only).
-It strictly decreases default if $F>F_{min}(\beta):=(p-1)-\beta[\lambda(p-1)+(1-\lambda)(b-1)]$.
-The larger the present bias the larger the $F$ required to induce pawn recovery.\footnote{$F_{min}(\beta)$ is derived from the incentive compatibility constraint needed to generate savings at $t=1$ to recover the pawn can be written as $1-(p-1)+\beta[\lambda(p-1)+(1-\lambda)(b-1)] \geq 1-F+\beta(1-\lambda)$.}
-
-\vspace{.1in}
-\noindent \textbf{Result 3: Demand for commitment.} Given $F>0$, (a) Neoclassical clients will never demand commitment.
-(b) Present-biased sophisticated clients will prefer the fee-forcing contract over the status quo contract $\iff$  $\lambda \: F<(1-\lambda)^2(b-p)$ and $F>F_{min}(\beta)$, that is $\iff$  $\beta \in [\beta_{min},\beta_{SQ}]$.\footnote{$\beta_{SQ}$ was determined in Result 1.
-$\beta_{min}$ is such that $F=F_{min}(\beta_{min})$.} (c) Analogously, naive clients will demand commitment $\iff$ $\hat{\beta} \in [\widehat{\beta_{min}},\beta_{SQ}]$, where $\widehat{\beta_{min}}<\beta_{min}$.
-So strongly naive clients will on the one hand demand more commitment than sophisticated clients since they believe (incorrectly) that a smaller fee will motivate them to pay.
-On the other hand they may demand less commitment since they think they can save and pay on their own.
-Whether they demand more or less than sophisticated clients depends on the empirical distribution of $\beta$ and $\hat{\beta}$.
-
-\vspace{.1in}
-\noindent \textbf{Result 4: Overconfidence.} Only naive clients will be overconfident about the probability of recovery.
+The model has three periods.
+In period $0$ the client is either allocated to the status quo, the fee-forcing contract, or a choice between the two.
+In period  $1$ the client decides to save to pay the monthly installment or not save, and in period $2$ the client makes the payment to recover her pawn (or not).
+\ref{appendix_c} provides detail; here we just summarize results.
+The results have to be interpreted conditional on consumers going to Lender $P$'s branch to get a loan and being randomly allocated to the different contracts.
+%We do not model selection into pawnshop borrowing.
+
+\vspace{.1in}
+\noindent \textbf{Result 1}: Present biased clients default more in the status quo contract.
+
+\vspace{.1in}
+\noindent \textbf{Result 2}: Imposing a fee  for late payments as in the frequent payment contract weakly decreases default (for present biased clients only), and strictly decreases default for a high enough fee.
+
+\vspace{.1in}
+\noindent \textbf{Result 3}: Demand for commitment.
+Given a fee for late installment payment, (a) Neoclassical clients will never demand commitment; (b) Present-biased sophisticated clients will prefer the fee-forcing contract over the status quo contract for intermediate values of present bias; (c) naive clients will demand commitment also for intermediate but different values of present bias, and depending on parameter values may demand less commitment than sophisticated clients.\footnote{Partially naive clients will on the one hand demand more commitment than sophisticated clients since they believe (incorrectly) that a smaller fee will motivate them to pay, while on the other hand they may demand less commitment since they think they can save and pay on their own.
+In the light of this model we seem to be finding that the latter effect dominates.
+%Whether they demand more or less than sophisticated clients depends on the empirical distribution of $\beta$ and $\hat{\beta}$.
+}
+
+\vspace{.1in}
+\noindent \textbf{Result 4}: Overconfidence.
+Only naive clients will be overconfident about the probability of recovery.
 This will be true whether they have the status quo or the fee-forcing contract.
-Overconfidence is increasing in $\hat{\beta}$.
-
-\vspace{.1in}
-\noindent \textbf{Result 5: Welfare.} (a) Neoclassical consumers' welfare strictly decreases when we force clients into the fee-commitment contract instead of the status quo contract, and does not change when we offer a choice between them.
-(b) The welfare of sophisticated present biased consumers weakly increases when we give them choice, and it strictly increases  $\iff$  $\beta \in [\beta_{min},\beta_{SQ}]$, that is when they would choose the fee-commitment contract themselves.
-Forcing them into the fee-commitment contract increases welfare $\iff$  $\beta \in [\beta_{min},\beta_{SQ}]$, otherwise it strictly decreases it.
-So choice is better than forcing for sophisticates.
-(c) Forcing can be welfare improving for the naive.
-Indeed if $\hat{\beta}>\beta_{SQ}>\beta$ then forcing the fee-commitment contract increases welfare, and if $\hat{\beta} \in (\widehat{\beta_{min}},\beta_{min})$ then forcing the status quo contract increases welfare.\footnote{This result is different from that in \cite{John}.
-Her context has individuals choosing the size of the fee.
-In that context naive clients will \textit{always} chose the wrong fee size and default later, therefore choice is always decreasing for the naive.
-In our context $F$ is fixed at 2\% of the balance due, and this implies that choice could be welfare improving for some naifs.}
-
-\vspace{.1in}
-\noindent \textbf{Result 6: Welfare and ex-post observed behavior.} If for a naive client $i$ the fee-forcing contract causes higher pawn recovery, then we know the fee $F$ made her IC constraint binding, and therefore that $\hat{\beta}_i>\widehat{\beta}_{min}$.
-If in addition if it was the case that $\beta_i<\beta_{SQ}$.
-%\footnote{\hl{Isaac, aqui tengo dos pregutas: (1) si es $\beta$ y no $\hat{\beta}$ verdad?
-(2) Para que una persona naive empenie en el status quo tiene que ser que cree que va a recuperar no?
-Es decir tiene que ser $\hat{\beta}>\beta_{SQ}$ correcto?}}
-then the fee-forcing contract would have increased welfare for the naive.
-That is, our finding that the fee-forcing contract increases pawn recovery is a sign of higher welfare (although not a sufficient condition).\footnote{It is not sufficient since ex-ante the commitment $F$ may have been too expensive given the income shocks, i.e.
-if $\lambda \: F>(1-\lambda)^2(b-p)$.}
+Overconfidence is increasing in the degree of partial naivete.
+
+\vspace{.1in}
+\noindent \textbf{Result 5}: Welfare.
+(a) Neoclassical consumers' welfare strictly decreases when we force clients into the fee-commitment contract instead of the status quo contract, because we expose them to risk of them not being able to pay for the installment; and does not change when we offer them a choice between the contracts.
+(b) The welfare of sophisticated present biased consumers weakly increases when we give them choice, and it strictly increases  under intermediate values of present bias (when they would choose the fee-commitment contract themselves).
+Forcing them into the fee-commitment contract increases welfare only if they themselves would chose it.
+(c) Forcing can be welfare improving for the naive under some parameter values (see Appendix).
+
+\vspace{.1in}
+\noindent \textbf{Result 6}: Welfare and ex-post observed behavior.
+Our finding that the fee-forcing contract increases pawn recovery is ``a sign'' of higher welfare (although not a sufficient condition).
 
@@
 
-The model of \cite{John} is very parsimonious but powerful and it can potentially explain all facts qualitatively.\footnote{The model is sufficiently stylized that we think we would not gain much from estimating it.
+The model is very parsimonious but powerful and it can potentially explain all our empirical findings qualitatively.\footnote{The model is sufficiently stylized that we think we would not gain much from estimating it.
 Furthermore we have no data on income shocks which figure prominently in the model.
@@
 Under the model naivete is necessary to explain this.
-Third, it can also explain why the fee forcing contract induces lower default, but not for everyone: namely that it makes the IC constraint for the present biased binding while it was not binding in the status quo contract.
-Fourth, it can also explain why there is low demand for commitment even if it seems to improve welfare: namely that there is a small share of neoclassical and sophisticated clients, and at the same time naifs have  $\hat{\beta}>\beta_{SQ}$ and therefore think they can save on their own.\footnote{By Result 6 we can eliminate $F<F_{min}(\widehat{\beta}$) as an explanation.} Fifth, it explains non-zero demand for commitment for a set of clients.
-Sixth, it can explain why clients exposed to the fee-forcing contract are more likely to come back, namely that $\hat{\beta_i}>\beta_{SQ}>\beta$ and so their welfare increased as a result of being forced into the fee-commitment contract, and they realized this after experiencing it.
+Third, it can also explain why the fee forcing contract induces lower default, but not for everyone: namely that it makes the incentive compatibility constraint for payment binding for the present biased, while it was not binding in the status quo contract.
+Fourth, it can also explain why there is low demand for commitment even if it seems to improve welfare: namely that there is a small share of neoclassical and sophisticated clients, and at the same time naifs have a present biased parameters values in the region in which they think they can save on their own.
+Fifth, it explains non-zero demand for commitment for a set of clients.
+Sixth, it can explain why clients exposed to the fee-forcing contract are more likely to come back namely those naifs whose welfare increased as a result of being forced into the fee-commitment contract.\footnote{Those with $\hat{\beta_i}>\beta_{SQ}>\beta$.}
 
@@
 
-There may be other interpretation of the empirical findings. But the bar is high. An alternative explanation will need to explain the 6 facts below:
+There may be other interpretations of the empirical findings, but the bar is high. An alternative explanation will need to explain the 6 facts below:
 
@@
 \vspace{.1in}
-\noindent \textbf{Alternative 1: Strong prevalence of income shocks.} This could explain low demand for commitment (4) and (1), but not why forcing helps (3) and (6), nor why there is overconfidence (1), or why they come to pawn in the first place and then default (2) as they would weight in on the high chance of losing the pawn.
+\noindent \textbf{Alternative 1: Strong prevalence of income shocks.} This could explain (4) and (1), but not why forcing helps, (3) and (6), nor why there is overconfidence, (1).
+It would also not explain why clients come to pawn in the first place and then default, (2), as they would weight in on the high chance of losing the pawn.
 
@@
 \noindent \textbf{Alternative 2: High time discounting}.
-This could not explain (1) nor (6) nor (4).
-It could qualitatively explain (3).
-But as we say in section \ref{sec:demand} it cannot quantitatively explain (5) and (3) unless the discount rate is unbelievably high.
+This could not explain (1) nor (5) nor (6).
+It could qualitatively explain (4), but as we say in section \ref{sec:demand} quantitatively it would require unbelievably high discount rates.
 
@@
 \noindent \textbf{Alternative 3: Risk aversion.} We already discussed and rejected risk aversion in section \ref{sec:demand}, although using strong assumptions in the process.
-We think this could still play a role and should be investigated in future research.\footnote{For instance by  providing insurance or by measuring risk aversion and using it to predict take up.}
+Risk or ambiguity aversion could still play a role in explaining 4 and should be investigated in future research.
+However it would hardly explain (1), (2), (5), or (6).
 
@@
 Note however that while clients making purely random mistakes could explain why 10\% demand commitment ---i.e.
-(4) and (5)--- it would not explain the rest of the findings, nor why the promise-commitment (see below) had more take up that the fee-commitment, or why those with measured present bias and those that want a reminder to pay are more likely to make the ``error'' to demand commitment.\footnote{See Figure \ref{interactions_takeup} and Table \ref{Table_compliance}}
-
-\vspace{.1in}
-\noindent \textbf{Alternative 5: Forgetting to pay.} Frequent payments may act as a reminder to save and recover the pawn.
-This would try to explain (1) by appealing to people forgetting to pay, and (3), (5) and (6) by appealing to frequent payment acting as reminders (i.e.
+(4) and (5)--- it would not explain the rest of the findings, nor why the promise-commitment (see below) had more take up that the fee-commitment, or why we can statistically predict take-up with significant accuracy (see Figure \ref{interactions_takeup} and Table \ref{Table_compliance}).
+
+\vspace{.1in}
+\noindent \textbf{Alternative 5 (behavioral): Forgetting to pay/salience.} Frequent payments may act as a reminder to save and recover the pawn.
+This would try to explain (1) by appealing to people forgetting to pay, and (3), (5), and (6) by appealing to frequent payment acting as reminders (i.e.
 there being demand for reminders).
@@
 However even for (1) it seems to us a stretch to explain people losing a valuable pawn by forgetting to pay it.
+Since the promise-commitment installment contract did not change behavior (as shown below) this explanation would also require us to posit that only fees acts as reminders, not promises.
 
@@
 \noindent \textbf{Alternative 6 (behavioral): Income shocks overconfidence}.
-One could also easily introduce in the overconfidence in income shocks with $\widehat{\lambda} <\lambda$ in the model of section \ref{model_detail}.
+One could also easily introduce in the overconfidence about income shocks in the model of \ref{appendix_c}\footnote{Say with $\widehat{\lambda} <\lambda$.
+The effect on demand for commitment is uncertain since on the one hand it decreases $\beta_{SQ}$ decreasing demand, but on the other a smaller $F$ is needed to make the IC binding, making commitment less costly.}.
 This would leave default unchanged in both the status quo and the fee forcing contract thus would not explain (3), %since $F_{min}(\beta,\widehat{\lambda})<F_{min}(\beta,\lambda)$.
-but the effect on demand for commitment is uncertain since on the one hand it decreases $\beta_{SQ}$ decreasing demand, but on the other a smaller $F$ is needed to make the IC binding, making commitment less costly.
-$\widehat{\lambda} <\lambda$ alone would not explain the (5) or (6) as demand for commitment would be zero without present bias.
-
-\begin{comment}
-\vspace{.1in}
-\noindent \textbf{Alternative 6: Learning that they are more present biased than they thought.} This is essentially the same as our proposed explanation (i.e.
+% $\widehat{\lambda} <\lambda$ alone 
+It would not explain (5) or (6) either as demand for commitment would be zero without present bias.
+
+%\vspace{.1in}
+%\noindent \textbf{Alternative 6: Learning that they are more present biased than they thought.} This is essentially the same as our proposed explanation (i.e.
 not an alternative) with the additional prediction that more people will demand commitment if they just experienced it, an specially appealing one in light of finding (6).
@@
 Unfortunately we did not do this experiment and we have very limited data to try it: \hl{210 (6\%)} clients were given a choice in a second pawns in our experiment after being randomly assigned to the status quo or fee-forcing contract.
-\end{comment}
-
-\vspace{.1in}
-We do not claim that the model in section \ref{model_detail} is the only possible explanation of our findings, but it is a parsimonious explanation of all of them and a lens for interpretation.
+%\end{comment}
+
+\vspace{.1in}
+We do not claim that the model in the Appendix is the only possible explanation of our empirical findings, but it is a parsimonious explanation of all of them.
 
@@
 
-One finding of the paper is that a rather small fee of 14 MXN on average changes behavior substantially: on the one hand generates average savings for almost everybody (and in the order of 200-300 pesos on average) when forced, but on the other dissuades take up when clients have choice.
-In this context one would want a commitment device that generates higher take up while at the same time providing incentives for paying fast and recovering the pawn.
+One finding of the paper is that a rather small fee of 14 MXN on average changes behavior substantially.
+On the one hand it generates average savings for almost everybody (on the order of 200-300 pesos on average) when forced.
+But on the other hand it dissuades take up when clients have choice.
+One would want a commitment device that generates higher take-up while at the same time providing incentives for recovering the pawn.
+
 One way to go would be to decrease the already small fee say to 1\% or lower.
@@
 As explained in Section \ref{Experiment} the promise contract involved making a salient promise to repay monthly, and receive a short speech by the appraiser about the importance of keeping her promise of paying monthly.
-
-A substantial literature documents that people don't like to break their promises, and are willing to incur in monetary loses in trying to keep them.
-To our knowledge this result has been replicated several times in laboratory contexts but not in a field setting like ours.
-If breaking a promise is perceived as having a lower cost than paying the 2\% fee and at the same time help as a commitment, we predict that more people will have demand for the promise-commitment contract.
+Promises are not foreign to microfinance lending: Grameen bank for instance makes clients recite a promise at each center weekly meeting.\footnote{The exact promise repeated by clients live is this: ``\textit{We pledge to attend regularly the weekly Center meetings, to utilize our loans for the purpose approved, to save and pay our installments weekly, to use our increased incomes for the benefit of our families, to ensure that other members of our group and Center do likewise and to take collective responsibility if they do not.''}}
+
+A substantial literature documents that people don't like to break their promises, and are willing to incur in monetary losses in trying to keep them.
+To our knowledge this type of result has been replicated several times in laboratory contexts but not in a field setting like ours.
+If breaking a promise is perceived as having a lower cost than paying the 2\% fee and at the same time helps as a commitment device we could achieve better outcomes: more people would demand the promise-commitment contract.
 
@@
 \noindent \textbf{Demand}.
-It turns out that the demand for monthly payment contracts with a personal promise to pay monthly ---but no pecuniary penalty for not doing so--- induces higher demand by a factor of three compared with fee-commitment contract: 31\% of clients offered a choice between the status quo contract and the promise-commitment contract chose commitment.
+It turns out that the demand for the promise-commitment contract  is higher than for the fee-commitment contract by a factor of 3: 31\% of clients offered a choice between the status quo contract and the promise-commitment contract chose commitment.
 This means that the pecuniary fee indeed limited demand for commitment.
 In passing this means also that clients are responsive to contract terms and seem to understand the conditions.
-Interestingly however, the set of people who demand the promise-commitment contract are different from those that demanded the fee-commitment one.
+Interestingly, the set of people who demand the promise-commitment contract are different from those that demanded the fee-commitment one.
 While in both cases the economically vulnerable demand less, in the case of the promise-commitment those that we classify as present biased, those that report that they frequently fall into temptation buying, and those that ask for reminders of payment are \textit{less} likely to demand the promise-commitment contract.
-This suggests that those taking up the promise commitment are not the ones needing the commitment.
-The opposite is weakly true for those who take up the fee-commitment contract (see Figure \ref{interactions_takeup} in the Appendix).
+This suggests that those taking up the promise commitment are not the ones needing the commitment (see Figure \ref{interactions_takeup} in the Appendix).
 
@@
 \vspace{.2in}
-\noindent The evidence presented in this section contrasts sharply with the evidence in laboratory experiments where people choosing to promise has a large effects on behavior, and were people keep their promises.
+\noindent The evidence presented in this section contrasts sharply with the evidence in laboratory experiments where people choosing to promise has a large effects on behavior, and wHere people keep their promises.
 While clients are more enthusiastic about the promise-commitment contract than the fee-commitment one in the sense of tripling take-up, the promise contract provides no commitment.
-Results for the promise arms are consistent with \cite{Ted} and \cite{John} who find that people are likely to demand commitment when the commitment is too week to have beneficial effects.
+Results for the promise arms are consistent with \cite{Ted} and \cite{John} who find that people are likely to demand commitment when the commitment is too weak to have beneficial effects.
 
@@
 
-In a pawnshop borrowing context, we studied whether forcing borrowers into frequent payment commitment contracts reduces their borrowing costs, compared to a contract that does not provide commitment to pay monthly.
-Even though we are charging them fees, their borrowing cost are actually reduced by 9.5\%, and they recover their pawn with 25\% higher likelihood.
+In a pawnshop borrowing context, we study whether forcing borrowers into frequent payment commitment contracts reduces their borrowing costs, compared to a contract that does not provide commitment to pay monthly.
+Even though we are charging them fees, their borrowing costs are actually reduced by 9.5\%, and they recover their pawn with 25\% higher likelihood.
 Moreover they themselves seem to like this contract, as they are 55\% more likely to come back and pawn again when they get it.
@@
 Examining treatment heterogeneity we find that almost all clients benefit from the commitment contract.
-
 However when given choice between the commitment and the status quo contract only 10\% choose the former one and thus forgo important benefits.
+We also find that overconfident clients experience larger treatment effect cost savings from the commitment contract but at the same time have smaller demand for it.
+
 A simple model shows that present bias with naivete parsimoniously explains all findings.
-This strongly suggests that it is possible in our context to advance an individual's interests by restricting her freedom ---although we caution that our outcome measure focuses on financing cost and is not comprehensive measure of welfare.
-These results spurred --although we cannot show it caused-- Lender $P$ to offer frequent payment contacts.
-Although Lender $P$ was not as bold as to force these contracts on clients.
+This suggests that it is possible in our context to advance an individual's interests by restricting her freedom of choice ---although we caution that our outcome measure focuses on financing cost and is not a comprehensive measure of welfare.
+These results spurred --although we cannot show they caused-- Lender $P$ to offer frequent payment contacts, although Lender $P$ was uncomfortable forcing these contracts on clients.
 They hoped that clients would eventually learn which contract was better for them.
 
-Needless to say, pawnshop borrowing likely attracts particularly unsophisticated clients (millions of them).
-Choice may fare better in other contexts.
-Choice may also fare better with other contracts besides the fee-commitment one.
+Methodologically, to our knowledge this is the first paper in economics that uses machine learning methods and a combination of choice and forcing arms to estimate personalized counterfactual treatment gains to ask whether treatment take up is positively selected on benefits, a hypothesis we reject.
+
+Pawnshop borrowing may attract particularly unsophisticated clients and freedom of choice may fare better in other contexts.
+Choice may also fare better with other contracts besides the fee-commitment one we used.
 We experimented with a ``softer'' commitment contract in the form of a personal promise, and found that although promise-commitment contracts do indeed elicit more interest they did not cause changes in behavior.
 
-Methodologically, to our knowledge this is the first paper in economics that uses machine learning methods and a combination of choice and forcing arms to estimate personalized counterfactual treatment gains to ask whether treatment take up is positively selected on benefits.
-
-Our results leave open several avenues for research.
-First, it would be useful to tease out the roles played by naivete about self control problems, biased expectations about income shocks, and ambiguity aversion in driving low demand for commitment, using more detailed direct baseline measurements.
+Our results suggest several avenues for future research.
+First, it would be useful to tease out the roles played by naivete about self control problems and biased expectations about income shocks in driving low demand for commitment.
 Second, one could ask whether other types of contracts ---for instance those that provide some insurance against shocks---  induce larger demand and better performance than the ones we tried.
-Third, it is likely individuals choosing to borrow from pawnshops are more present biased and naive than similar individuals borrowing from other types of lenders, meriting differential regulation.
-Testing and quantifying this selection across lenders is important.
+Third, testing and quantifying selection to pawnshop lenders based on sophistication could be important for regulators.
 Fourth, collecting broader measures of welfare to use as outcomes --e.g.
-subjective well being, consumption, being able to pay for essential services-- would help to make broader claims about welfare that we can make in this paper.
+subjective well being and consumption-- would help to make broader claims about welfare than we can make in this paper.
 Finally, one would like to know which interventions could debias consumers, or whether learning alone would do the work.
@@
  \scriptsize
-This table presents balance tests for the administrative data (Panel A) and survey data (Panel B).
-Each column corresponds to an arm of the experiment: control (status quo contract), no choice with fee, no choice with promise, choice among both contracts where the commitment contract has fee, and choice among both contracts where the commitment contract involves only a promise.
-The last column show the p-value of an F-test of the hypothesis that the mean across arms for that variable is the same across the 5 arms.
+
+%\textit{Do file: } \texttt{ss.do}
+\end{table}
+
+\scriptsize {
+\noindent This table presents balance tests for the administrative data (Panel A) and survey data for those that pawned (Panel B) and for all (Panel C).
+The first column ``Overall'' presents data for all arms together.
+The second column shows summary stats for one month before the experiment.
+The remaining columns present summary stats  for each arm separately.
+The last column shows the p-value of an F-test of the hypothesis that the mean across arms for that variable is the same across the 5 arms.
 Randomization was done at the branch-day level.
-By design the observation are not exactly equal cross arms as we were more interested in detecting effects in the choice-fee arm and less so in the no-choice-promise.
-Loan amount is the peso amount given to the client; Monday is the fraction of loans given on a Monday; number of pledges is the number of loans given in each arm.
-That it is balanced shows that there was no detectable selection across arms when clients found out what was the contract.
+By design the observations are not exactly equal across arms as we were more interested in detecting effects in the choice-fee arm and less so in the no-choice-promise.
+Loan amount is the peso amount given to the client; Monday is the fraction of loans given on a Monday; Number of branch-day pawns is the number of loans given in each arm per day per branch.
 In Panel B: woman indicated whether the client is female, age of the client is measured in years; has pawned before is a dummy=1 if the client declares to have pawned before (although not necessarily with Lender $P$).
@@
 High-school is a dummy that indicates if the client has completed high school.
-Finally, the response rate is the percentage of clients in the admin data for whom we have a baseline survey.
-%\textit{Do file: } \texttt{ss.do}
-\end{table}
-
-\newpage
+Finally, the survey response rate is the percentage of clients in the admin data for whom we have a baseline survey.
+Panel C has the same variables, except for the last one.
+``\% ended up pawning'' measures the fraction of those that answered the survey that ended up pawning that day in that branch.
+P-values in Panel C test whether the 5 columns for treatment arms \textit{and} the column of pre-experiment have different means.
+}
+
+\vspace{3ex}
+
+\vspace{.3in}
 
@@
 \end{center}
- \footnotesize This table shows the parameter estimates of $y_i = \alpha + \beta \: OC_i + Z_i'\gamma + \epsilon_i$, where $OC_i:=\mathbbm{1}(P^s_i-\widehat{P_i(X_i)}>0)$ is an indicator for the subjective probability of recovery being larger that the predicted one.
+ \footnotesize This table shows the parameter estimates of $y_i = \alpha + \beta \: OC_i + Z_i'\gamma + \epsilon_i$, where $OC_i:=\mathbbm{1}(P^s_i-\widehat{P_i(X_i)}>0)$ is an indicator for the subjective probability of recovery being larger than the predicted one.
 In columns 1-4 $y_i$ is a dummy for whether the client $i$ chose to have the commitment contract in the respective choice arm, and in columns 5 and 6 $y_i$ is the heterogeneous treatment effect for financial cost (in pesos) estimated by comparing the fee-forcing vs status quo arms in Section \ref{TE_fee-forcing}.
@@
          \scriptsize Panel (a) displays in black arrows the period covered by our administrative data: from August 6th 2012 (30 days before the experiment began) to August 13th 2013.
-The gray lines arrows correspond to the dates of implementation of the experiment.
-We finished the experiment earlier in branches 1 and 2 because we realized that we would have enough sample size with the remaining branches and save on operational costs.
+The gray lines correspond to the dates of implementation of the experiment.
+We finished the experiment earlier in branches 1 and 2 because we realized that we would have enough sample size with the remaining branches and wanted to save on operational costs.
 Panel (b) shows our 5 treatment arms: control (status quo contract), no fee-forcing, promise-forcing, choice among status quo and fee-commitment, and choice among status quo promise-commitment.
 Within each arm it displays the number of observations.
-And  for the choice groups it splits the sample size into those who chose the commitment contract (shaded blue triangle) and those that did not (un-shaded triangle).
+For the choice groups it splits the sample size into those who chose the commitment contract (shaded blue triangle) and those that did not (un-shaded triangle).
 %\textit{Do file: }  \texttt{timeline\_suc\_exp.do}
@@
     \begin{center}
-    \begin{subfigure}{0.8\textwidth}
+    \begin{subfigure}{0.75\textwidth}
         \centering
@@
     \scriptsize
-        This is a (translated) sample information mica shown to clients in choice-promise days.
+        This is a (translated) sample information slide shown to clients in choice-promise days.
 The real ones were twice the size of this figure and were laminated.
-Different ones were shown in each treatment arm.
+Different ones were shown for each treatment arm.
 \end{figure}
@@
 We plot separately the financial cost for those who lose the pawn (blue) and those that recover it (transparent).
-Panel (b) is analogous but we normalized the financial cost dividing it by the loan size.
+Panel (b) is analogous but we normalized the financial cost, dividing it by the loan size.
 %Given that the loan lasts close to 90 days, bringing payments to present value makes little difference.
@@
     \scriptsize
-     In the baseline survey at the branch, before the client knew the contract of had the pawn appraised, they were asked from 0 to 100, how likely is that they would be able to recover their pawn if pawned.
+     In the baseline survey at the branch, before the client knew the contract or had the pawn appraised, they were asked from 0 to 100, how likely it was that they would be able to recover their pawn if pawned.
 We generate a variable we call overconfidence (OC) defined as the reported subjective probability of recovery minus the predicted probability ($P^s_i-\widehat{P_i(X_i)}$).
@@
 Second, we extrapolate these treatment effects based on the choice arm using the same $x$'s.
-Once we have personalized counterfactual treatment effects in the choice we calculate what fraction of subjects in the choice arm incurred in financial costs that are  $> z$\% than if they had chosen the opposite contract of what they actually chose, were $z$\% is defined as a fraction of the loan.
+Once we have personalized counterfactual treatment effects in the choice arm we calculate what fraction of subjects in the choice arm incurred in financial costs that are  $> z$\% than if they had chosen the opposite contract of what they actually chose, were $z$\% is defined as a fraction of the loan.
 $z$\% is a level of tolerance we can vary and we plot it in the X-axis.
@@
 
+\appendix
+\pagenumbering{arabic}
+\renewcommand\thefigure{OA-\arabic{figure}}
+\renewcommand\thetable{OA-\arabic{table}}
+\renewcommand*{\thepage}{OA - \arabic{page}}
+\renewcommand\thesection{Appendix \Alph{section}.}
+\renewcommand\thesubsection{\Alph{section}.\arabic{subsection}}
+
 %\renewcommand{\cftparskip}{0em} % NOT NEEDED
@@
 \newpage
-\pagenumbering{arabic}
-\renewcommand\thefigure{OA-\arabic{figure}}
-\renewcommand\thetable{OA-\arabic{table}}
-\renewcommand*{\thepage}{OA - \arabic{page}}
-\renewcommand\thesection{Appendix \Alph{section}.}
-\renewcommand\thesubsection{\Alph{section}.\arabic{subsection}}
 
@@
 The regressors $X_i$ include (e.g if the family asks for money, if they have savings, if they are overconfident using the definition the text, etc.
-See this appendix for a transcription of the survey).
+See this Appendix for a transcription of the survey).
       %\footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}}
@@
 \linespread{1.25}
-
-The objective of this appendix is to conduct one test aiming to assess if there is learning in choosing the frequent payment FP) contract.
+%Really force it to normal size and linespread
+\normalsize
+\linespread{1.25}
+
+The objective of this Appendix is to conduct one test aiming to assess if there is learning in choosing the frequent payment FP) contract.
 In particular if being endogenously induced to have a FP contract causes the client to chose a FP in subsequent pawn.
-The identification strategy is not as strong as in a randomized control trial ---having to rely on an instrumental variable strategy using changes in the supply of the FP contract-- and this is why we chose to locate it in a separate appendix.
+The identification strategy is not as strong as in a randomized control trial ---having to rely on an instrumental variable strategy using changes in the supply of the FP contract-- and this is why we chose to locate it in a separate Appendix.
 However we believe we find a strong case for learning causing higher demand for the FP contract.
@@
 
-Having said this in Table \ref{instrument_random} we assess to what extent we can predict whether a given branch activates the FP contract in its IT system in a given week or a given month.
+Having said this, in Table \ref{instrument_random} we assess to what extent we can predict whether a given branch activates the FP contract in its IT system in a given week or a given month.
 It turns out that we cannot predict in which weeks a given branch uses the FP contract with our observables controlling for branch fixed effects.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% APPENDIX C
+
+\newpage
+\section{ A simple model}
+\label{appendix_c}
+\vspace{.2in}
+\normalsize
+\linespread{1.25}
+
+We use the model of \cite{John} and refer the reader to that paper for more detail, justification of assumptions and some of the proofs.
+The model has three periods and linear utility.\footnote{This does not map perfectly to our 3 period contract, but it is enough to generate the results we need.
+We also assume that the amount of the loan is used up to pay for the emergency.
+\cite{John_theory} provides a more general treatment.} Period $t=0$ is a planning period where the client is either allocated to the status quo, the fee-forcing contract, or a choice between the two.
+Period $t=1$ is the saving-for-the-monthly-payment  period, and $t=2$ in the pawn recovery (loan payment) period.
+In period 1 the client receives her income $y_1=1$, or gets zero with probability $\lambda$.
+She can consume ($c_1$) or save ($s_1$) part that income.
+In period 2 the client gets her savings from period 1, and again receives income of either $y_2=1$, or zero with independent probability $\lambda$.
+In this last period, she decides whether to use income and savings for consumption $c_2$ and/or for paying back the loan of size $p \in(1,2)$ to recover the pawned piece valued at $b>p$.
+In this simple set up we model the fee-commitment contract as a contract that imposes a fee of size $F$ if the client fails at $t=1$ to save $s_1=p-1$ pesos, which is what is needed to pay the loan back when there are no shocks.
+In period $t=0$ she evaluates her welfare as $E[c_1+c_2]$, were for simplicity we have set the time discount to one.
+We also assume the interest rate is one.
+We introduce present biased preferences by assuming the following utility function $U_t=c_t+\beta \: \sum_{k=t+1}^{2} E[c_k]$, with $\beta<1$ indicating present bias.
+A naive client perceives she is not so present biased and instead of $\beta$ uses $\hat{\beta} \in (\beta,1]$.
+
+Note that under these assumptions it is efficient at $t=0$ to recover the loan since $b>p$ and since there is no discounting at $t=0$.
+Because $b>1$, paying back the loan requires that there is no negative shock in any period and that $s_1>0$.
+Because $\beta<1$ at $t=1$ the client will not send savings in excess of what is needed to recover the loan: $s_1=p-1$.
+This parsimonious model implies the following results:
+
+\vspace{.2in}
+\noindent \textbf{Result 1: Present biased clients default more.} Under the status-quo contract, absent shock realizations, present biased clients (sophisticated or naive) with $\beta<\beta_{SQ}<1$ will lose their pawn, while clients with no present bias will not.\footnote{$\beta_{SQ}=\frac{p-1}{\lambda(p-1)+(1-\lambda)(b-1)}$.
+See Proposition 1 in \cite{John}.}
+
+\vspace{.1in}
+\noindent \textbf{Result 2: Forcing present-biased clients into the fee-commitment contract reduces default.} Imposing a fee $F>0$ for late payments weakly decreases default (for present biased clients only).
+It strictly decreases default if $F>F_{min}(\beta):=(p-1)-\beta[\lambda(p-1)+(1-\lambda)(b-1)]$.
+The larger the present bias the larger the $F$ required to induce pawn recovery.\footnote{$F_{min}(\beta)$ is derived from the incentive compatibility constraint needed to generate savings at $t=1$ to recover the pawn can be written as $1-(p-1)+\beta[\lambda(p-1)+(1-\lambda)(b-1)] \geq 1-F+\beta(1-\lambda)$.}
+
+\vspace{.1in}
+\noindent \textbf{Result 3: Demand for commitment.} Given $F>0$, (a) Neoclassical clients will never demand commitment.
+(b) Present-biased sophisticated clients will prefer the fee-forcing contract over the status quo contract $\iff$  $\lambda \: F<(1-\lambda)^2(b-p)$ and $F>F_{min}(\beta)$, that is $\iff$  $\beta \in [\beta_{min},\beta_{SQ}]$.\footnote{$\beta_{SQ}$ was determined in Result 1.
+$\beta_{min}$ is such that $F=F_{min}(\beta_{min})$.} (c) Analogously, naive clients will demand commitment $\iff$ $\hat{\beta} \in [\widehat{\beta_{min}},\beta_{SQ}]$, where $\widehat{\beta_{min}}<\beta_{min}$.
+So strongly naive clients will on the one hand demand more commitment than sophisticated clients since they believe (incorrectly) that a smaller fee will motivate them to pay.
+On the other hand they may demand less commitment since they think they can save and pay on their own.
+Whether they demand more or less than sophisticated clients depends on the empirical distribution of $\beta$ and $\hat{\beta}$.
+
+\vspace{.1in}
+\noindent \textbf{Result 4: Overconfidence.} Only naive clients will be overconfident about the probability of recovery.
+This will be true whether they have the status quo or the fee-forcing contract.
+Overconfidence is increasing in $\hat{\beta}$.
+
+\vspace{.1in}
+\noindent \textbf{Result 5: Welfare.} (a) Neoclassical consumers' welfare strictly decreases when we force clients into the fee-commitment contract instead of the status quo contract because of the risk of them not being able to pay for the installment, and does not change when we offer a choice between them.
+(b) The welfare of sophisticated present biased consumers weakly increases when we give them choice, and it strictly increases  $\iff$  $\beta \in [\beta_{min},\beta_{SQ}]$, that is when they would choose the fee-commitment contract themselves.
+Forcing them into the fee-commitment contract increases welfare $\iff$  $\beta \in [\beta_{min},\beta_{SQ}]$, otherwise it strictly decreases it.
+So choice is better than forcing for sophisticates.
+(c) Forcing can be welfare improving for the naive.
+Indeed if $\hat{\beta}>\beta_{SQ}>\beta$ then forcing the fee-commitment contract increases welfare, and if $\hat{\beta} \in (\widehat{\beta_{min}},\beta_{min})$ then forcing the status quo contract increases welfare.\footnote{This result is different from that in \cite{John}.
+Her context has individuals choosing the size of the fee.
+In that context naive clients will \textit{always} chose the wrong fee size and default later, therefore choice is always decreasing for the naive.
+In our context $F$ is fixed at 2\% of the balance due, and this implies that choice could be welfare improving for some naifs.} We want to highlight that only under certain parameters will forcing installment payments improve welfare, and that welfare will likely decrease for those with no present bias and the sophisticated present biased consumers.
+
+\vspace{.1in}
+\noindent \textbf{Result 6: Welfare and ex-post observed behavior.} If for a naive client $i$ the fee-forcing contract causes higher pawn recovery, then we know the fee $F$ made her IC constraint binding, and therefore that $\hat{\beta}_i>\widehat{\beta}_{min}$.
+If in addition if it was the case that $\beta_i<\beta_{SQ}$.
+%\footnote{\hl{Isaac, aqui tengo dos pregutas: (1) si es $\beta$ y no $\hat{\beta}$ verdad?
+(2) Para que una persona naive empenie en el status quo tiene que ser que cree que va a recuperar no?
+Es decir tiene que ser $\hat{\beta}>\beta_{SQ}$ correcto?}}
+then the fee-forcing contract would have increased welfare for the naive.
+That is, our finding that the fee-forcing contract increases pawn recovery is a sign of higher welfare (although not a sufficient condition).\footnote{It is not sufficient since ex-ante the commitment $F$ may have been too expensive given the income shocks, i.e.
+if $\lambda \: F>(1-\lambda)^2(b-p)$.}
+
 \end{document}

### 2021-01-13 main.tex
Bootstrap chosse_wrong figure

@@
 The closest product studied is payday loans.
-In developing countries, however payday, lending is likely small compared to pawnshop lending; the latter is faster and requires less documentation, allowing access to informal sector workers who receive their salaries in cash .
+In developing countries, however, payday lending is likely small compared to pawnshop lending; the latter is faster and requires less documentation, allowing access to informal sector workers who receive their salaries in cash.
 According to \cite{Payday} to get a payday loan: ``All that a prospective borrower typically needs is a home address; a valid checking account; a driver’s license and Social Security number; a couple of pay stubs to verify employment; wages and pay dates; and minimum earnings of at least \$1,000 a month''.
@@
 It was short to avoid discouraging the potential clients from pawning, but at the same time it aimed to measure the following: demographics, proxies for income/wealth, education, self-control problems/present-biased preferences, experience pawning, if family or friends commonly asked for money, how time consuming and costly it was to come to the branch, the subjective probability of recovering the piece that they intended to pawn, the subjective value of their piece in money terms (how much money they would sell it for), among others.
-We surveyed 7,704 clients (some refused).
+We surveyed 10,431 clients (some refused).
 %\footnote{We also surveyed clients before and after the experiment, so our survey covers a larger sample that we are not using in this paper.}.
@@
 The population we are working with is economically vulnerable in the sense that 30\% of them could not pay either water, electricity \& gas or rent in the past 6 months.
-They often receive negative income shocks: 87\% said they are pawning because of an emergency, and only 13\% stated it was to use in a 'non-urgent expense'.
+They often receive negative income shocks: 87\% said they are pawning because of an emergency, and only 13\% stated it was to use in a `non-urgent expense'.
 %When asked why they are pawning this piece \hlgr{5\%} responded \hlgr{`lost a family member'}, \hlgr{`a medical emergency'} (\hlgr{11\%}), \hlgr{`an urgent expense'} (\hlgr{71\%}),

### 2021-03-09 OA.tex
review of the paper, major revisions
Former-commit-id: f0ba952ceba4dcebac4f60c80e3534421325c165

--- 2020-08-14 main.tex
@@
 
-\title{The limits of self-commitment and private paternalism \thanks{We want to thank Craig McIntosh and Mauricio Romero for advice and encouragement.
-We want to thank also Ricardo Olivares for excellent research assistance and Erick Molina's help with formatting.
-Jose Maria Barrero, Andrei Gomberg, Emilio Gutierrez, David Laibson, Aprajit Mahajan, Matt Rabin, Charlie Sprenger, and seminar participants at ITAM provided valuable feedback.}}
-\author{Isaac Meza \and Joyce Sadka \and Enrique Seira   \thanks{Meza: University of California at Berkeley, isaac.meza@berkeley.edu; Sadka: ITAM, jsadka@itam.mx;  
-Seira: ITAM, enrique.seira@gmail.com} }
-\date{This draft:  \today \\[2 cm]}
-
-%\vspace{.5in}
-
-\maketitle
-\thispagestyle{empty}
-\begin{abstract}
-
-%Many firms provide commitment devices that restrict individuals' choice, but shroud this.
-Shrouding suggests low demand for commitment.
-We show that private paternalism is beneficial in the pawnbroker context we study.
-
-In the context of pawnbroker lending, we show that forcing people into commitment contracts with financial penalties for not paying on time \textit{decreases} their (fee-including) financial cost by 9.5\%, increases the likelihood of recovering their pawn by 25\%, and increases the likelihood of repeat business by 55\%.
-Using machine learning methods for estimating heterogeneous treatment effects, we find that more than 90\% clients would reduce their financing cost with the commitment contract, however only 10\% choose it.
-Relying on personal promises instead of fees as commitment triples take-up but has no effects on outcomes.
-
-%and one of the most understudied.
-In our context more than on half of borrowers default and lose their pawn and whatever they have paid towards recovering it.
-Compared to the status quo pay-at-anytime 3-month contracts, forcing borrowers to pay monthly and charge a penalty if they didn't --i.e.
-a commitment contract-- increased recovery of pawn by about 30\% and financial costs by 10\%.
-However when offered a choice between the two contracts only 10\% took the monthly payment one.
-A pecuniary commitment seems necessary.
-In an alternative arm, we made them promise to pay but removed the pecuniary penalty.
-This increased take up to 31\%, but had zero effect on financing cost or default.
-The forcing contract may be better than choice for naive present biased consumers.
-
-\end{abstract}
-
-\vspace{.3in}
-
-\textbf{Keywords: } Private paternalism, choice, present bias, naivete, overconfidence, commitment, heterogeneous treatment effects.
-
-\textbf{JEL codes:} G41, C93, O16, G21
-
-\newpage
-
-\pagenumbering{arabic}
-\etocdepthtag.toc{mtchapter}
-\etocsettagdepth{mtchapter}{subsection}
-\etocsettagdepth{mtappendix}{none}
-
-%NO MORAL HAZARD IN THE CONTRACT SINCE FULLY COLLATERALIZED
-%DOUBLE FAILURE: DEMAND LOW, AND DOES NOT WORK BY PEOPLE WHO TAKE IT.
-%PENALIZES THEM EVEN MORE ON SOMETHING THEY WERE ALREADY PENALIZED 
-%PROPENSITY TO CHOSE.
-%PULLING PUNISHMENT FORWARD --CHARGING RIGHT WHEN I MESS UP.
-%MAYBE ONLY IMPATIENT AND NAIVE END IN PAWNSHOPS
-%1) SELECT A RANDOM SAMPLE OF NEIGHBORHOODS, EXTERNAL VALIDITY, THE ONES THEY GO ARE NAIF AND
-%HYPERBOLIC
-%2) ASK TO CHOSE AMONG ALL CONTRACTS
-%3) CLASSIFY SOPHISTICATION AT BASELINE
-%4) HOW TO GET AT SHOCKS.  --BUT DOES NOT SQUARE WITH WHY CHARGING THEM FEES WORKE.
-%do shocks vary across strata, predict shocks.
-%DEEP BEHAVIORAL PAPER -- CAN WE REALLY PREDICT?
-
-% \section{Introduction}
-
-Many institutions ---firms, schools, financial contracts--- restrict choice using built-in commitment mechanisms which help workers, students, borrowers overcome self-control problems.
-For instance, mortgages restrict choice ``with a fixed repayment stream and mandatory principal repayment \citep{Laibson2018}''.\footnote{\cite{Laibson2018} also mentions that ``Firms do limit their workers' freedom with intermediate deadlines, progress reports, production targets'', and schools with ``pop quizzes, classroom attendance requirements, cold calling, graded problem sets, deadlines''.} At the same time  these same firms shroud these forcing mechanisms and don't market their commitment features, presumably because students, workers and borrowers ``don't welcome these paternalistic restrictions'' (\cite{Laibson2018}).
-\cite{Laibson2018} argues that this presents an important commitment puzzle: if clients were present biased and sophisticated about their self control problem they should appreciate commitment features and firms should be eager to market them.
-That this is not so suggests some clients may be naive about their self control problems, and that private paternalism may be beneficial.\footnote{\cite{Laibson2018} defines paternalism as a policy that advances an individual's interests by restricting his or her freedom, and private paternalism as paternalism implemented by private institutions.
-In this paper we will study the effect of restricting freedom of choice on pawn recovery and financing cost, not overall welfare.}
-
-This paper studies the benefits of restricting choice in the context of pawnbroker lending.
-Pawn loans are one of the oldest, understudied, and most prevalent forms of borrowing.
-There are more than 11,000 pawn shops across the US with 30 million clients and \$14 billion yearly revenues (in China is a 43 billion industry).\footnote{\url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.} Our partner pawn lender (henceforth Lender $P$) alone served more than 1 million clients in the last 3 years with more than 4 million contracts.\footnote{For comparison there were 2.3 million micro-finance clients in Mexico in 2009 (\cite{Pedroza:2010}).} The key characteristic of pawn loans is that the borrower leaves personal property (a pawn) as collateral in exchange of an immediate cash loan of a smaller value.
-In our case Lender $P$ only accepts gold jewelry as collateral and approves all pawns, giving cash the equivalent of 70\% of the pawn's appraised value.
-The contract stipulates a 7\% monthly interest rate charged daily, a loan term of 90 days, and the flexibility to pay back the loan at anytime before the loan is due.
-In spite of this flexibility, most people lose their pawn, and among those that recover it almost all of them pay in the last days, just before the loan elapses.\footnote{In the US default is also high at 15\% (\url{https://tinyurl.com/yc2x5bjf}).}
-
-% About 85\% of borrower lose their pawn\footnote{https://nationalpawnbrokers.org/2017/06/19/pawnbroking-around-the-world/}
-
-%different prices: https://priceonomics.com/the-economics-of-pawn-shops/
-
-% pawnshops help the poor https://tinyurl.com/y9qr43j8
-%, with annual percentage rates above or close to 200\%.
-
-% Limite statustics and knowledge of pawnshops. World bank mentions them in passing: https://tinyurl.com/ydgob8pv
-
-%Borrowers typically turn to these loans when in desperate need to pay for an emergency.
-The vulnerability of these borrowers has sparked regulator's interest.\footnote{In 2013 Mexico's Consumer Protection Bureau (Profeco) is concerned about abuse.
-It forced Pawnshops to be more transparent in their pricing, register their contracts with them and issued regulation to protect clients.
-Congress has enacted laws in this regard.
-\url{http://www.diputados.gob.mx/LeyesBiblio/ref/lfpc.htm}.} One concern is that borrowers selecting into these loans may exhibit particularly strong behavioral biases.
-%Using a survey conducted by us in branches of Lender $P$, we indeed document some evidence consistent with these concerns: while pawnshop clients predict they will recover their pawn with 93\% probability on average, in reality only 40\% of them do, suggesting naivete.
-%Even conditional on paying a positive amount towards pawn recovery, 53\% lose their pawn and their payment.
-In our survey 69\% report self-control problems saying they often fall into temptation spending.
-%, but only \hlgr{15\%} show inter-temporal inconsistencies in a classical present-bias question, a similar number to \cite{Ashaf}.
-%and \hl{19\%} do not normally budget monthly expenses.
-%While this is suggestive of a present bias problem or overconfidence to save and pay, at the same time our subjects are experienced and not wholly uneducated, 66\% have completed at least high school and 90\% have pawned before.
-%and \hl{38\%} have participated in a Rosca.
-
-\begin{comment}
-Lender $P$ offers a very simple but highly collateralized contract.
-It only accepts gold jewelry as collateral and approves all gold pawns, giving in cash the equivalent of 70\% of the weighted gold value.
-The contract stipulates a 7\% monthly interest rate charged daily, and a loan term of 90 days plus 15 grace days to pay the principal and the accumulated interest.
-The client has complete flexibility to pay any number of times any amount she desires towards the recovery of her pawn, with no pre-payment penalties.
-However if the total amount of principal plus interest is not covered by the end of the 105 days, she loses her pawn and all the payments that have been done (unless she renews the loan before this by paying all accumulated interest).
-All transactions ---appraisal of the piece, loan disbursement and loan servicing--- are conducted at the branch.
-The gold collateral is highly liquid and the pawnshop has an associated business that sells the gold jewelry.
-Given the over-collateralization of the loan one would expect no moral hazard or adverse selection on the part of borrowers.
-%This lets us focus more cleanly on behavioral economics aspects.
-\end{comment}
-
-We implemented a large randomized control trial with close to 10,000 pawnshop clients in 6 branches of Lender $P$ in Mexico City.
-We answer five main questions using this experiment.
-First, would clients benefit  ---in terms of recovering their pawn and in terms of incurring in lower financing costs---  from having a frequent (monthly) payment commitment contract \textit{forced} on them, instead of the current 3-month pay-when-you-want contract?
-That is, we are asking whether \textit{charging} them a 2\% late payment fee for not paying a monthly installment on time can actually \textit{decrease} total (fee-inclusive) financing cost.
-Second, would there be demand for such a frequent payment commitment contract vis-a-vis the status quo one if given choice?
-Any payment profile implemented in the commitment contract can be replicated by the borrower under the status quo contract, but the later affords more flexibility to respond to income shocks without incurring in fees.
-Third, what types of clients would demand these contracts that restrict choice?
-Fourth, are late payment fees key to provide commitment or would a non-pecuniary but salient personal promise to pay provide a cost-reducing mix of commitment vs flexibility?
-Promises change behavior significantly in laboratory settings, but we know little about their effect in natural environments.\footnote{Some papers in this space are \cite{PromisesPartnerships}, \cite{Vanberg}, \cite{Belot2010}, \cite{WhyDoPromises}, \cite{FurtherPromises}, \cite{Ismayilov2017}.
-There is also some actual policy around using promises for loans: the government Mexico has created a program called ``Loans on your word'' for uncollateralized borrowing (\url{http://tiny.cc/yfmnmz}), but unfortunately there is little information about them.} Finally, is \textit{giving choice} among contracts better than forcing them into payment-commitment contracts in terms of minimizing financing costs incurred and the likelihood of recovering their pawn?
-Or on the contrary, is it better to force the commitment contract
-paternalistically?
-
-The experiment involved 5 arms, with randomization happening at the branch-day level.
-It is described in detail in Section \ref{Experiment}.
-Here let us briefly explain the main 3 arms.
-The first one involves a group of clients that were given only the status quo contract (henceforth the \textit{status-quo forcing group}).
-The second arm (\textit{fee-forcing group}) was given a monthly payment commitment contract, which stipulated that clients had to pay 1/3 of their loan plus accumulated interest in each of the 3 months of the term length.
-Failing to do this would result in a fee of 2\% of the amount due that month.
-A third group (\textit{Fee-choice group}) gave clients a choice between these two contracts.
-
-Forcing clients into frequent payment commitment contracts causes them on average to save on financing cost and to recover their pawn more.
-The effects are large: financing cost decreases by 9.5\% on average, from \$3161 to \$2857 MXN, while the likelihood of recovering their pawn increases by 25\%, from 43\% to 54\%.
-Results are robust to including transport costs of going to the branch plus losing a day's wage for each visit.
-Importantly, the benefits are distributed broadly: almost the whole distribution of treatment effects shows cost savings; however those most economically vulnerable, those that report being stressed, and those we classify as overconfident experience larger gains.
-%The commitment contract also causes payments to start 8 days earlier and be 16\% more frequent, compared to the control group.
-Treatment effects are concentrated on the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery.
-The fee-commitment contract induces people who would otherwise pay something towards recovery, to pay more and faster and thus recover their pawn more at a cheaper financial cost.
-Finally, borrowers assigned to the forced fee-commitment contract are 5 percentage points (55\% of the mean) more likely than the control group to ask for another loan in the future, suggesting that they liked the commitment contract more after experiencing it.
-
-%From this first comparison we conclude that penalizing borrowers for delinquency in a contract which has already has large penalties from default actually helps borrowers.
-In fact, we find that borrowers assigned to the forced fee-commitment contract are 5pp more likely to be repeat costumers, suggesting that they themselves liked the the commitment contract more after experiencing it.\footnote{As it is well known, \textit{naivete} facilitates their exploitation by firms.
-\cite{Laibson2018} conjectures that this exploitation may be limited if consumers use experienced utility to choose among firms or contracts.}
-
-In spite of these estimated benefits for almost all clients, actual demand for the fee-commitment contract is low.
-Only 10\% of the group offered a choice between the monthly payment fee-commitment contract and the status-quo one chose the former.
-This is not likely driven by misunderstanding the (already simple) contract.\footnote{We posted two persons in each of the experiment's branches every day for all branch opening hours to carefully explain the contracts; material was developed to explain the differences among the two contracts, and subjects spelled back to our team the loan differences.
-Furthermore take up is systematically predicted by baseline covariates, making it less likely that it is just random mistakes.} Low demand for commitment is consistent with a large literature (\cite{Laibson2015}, \cite{Laibson2018}, \cite{John}, \cite{Ted}, \cite{Rabin2018}).
-%\footnote{\cite{Alcohol} and \cite{Kremer} are some of the few instances of high demand for commitment.
-\cite{Alcohol} speculates that this difference may be explained by their subjects having more experience with their self control problem.
-Close to ninety percent of our subjects claim to have pawned before.
-We find that experience does not predict positive take up in our sample.}
-%\cite{Laibson2015} shows that the lost flexibility resulting from a commitment contract can severely limit take-up when agents are naive about their self control, even though commitment could be welfare improving for them.
-Owing to this low take-up, we estimate zero average treatment effects of the \textit{fee-choice} arm on financial cost and on pawn recovery and throughout the quantile distribution.
-
- %Using boosting we can predict who takes up with 92\% accuracy. This fact shows that the choice among contracts is not purely random.
-
-Combining the forcing and the choice arms ---a unique feature of our experiment--- allows us to estimate the counterfactuals to answer the following question how much money is left on the table by the prevalence of the status-quo choice?
-We calculate that about 80\% of clients in the fee-choice group chose contracts that induced \textit{higher} financial cost.
-On average they spend an extra \$238 MXN, close to 11\% of the average loan value.
-In particular 92\% of those that chose the status-quo contract would have been better in the fee-commitment contract, while only 8\% of those who chose the fee-commitment contract would have been better in the status-quo one.
-This suggests that forcing clients into commitment contacts (i.e.
-private paternalism) may be beneficial for the overwhelming majority of clients.
-After seeing our results Lender $P$ introduced frequent payment contracts in their loans portfolio.
-
-We want to clarify that in the paper we are using the word ``paternalism'' in a restricted sense, meaning only that a large majority of clients would incur in lower financial costs from being forced into commitment contracts instead of letting them chose.
-We are not making claims about overall welfare which is a slippery concept once we accept the possibility of biased beliefs and preferences.
-
-Inspired by a significant lab experiment literature on the effects of promises on behavior, and by research showing that a small fee could drastically reduce demand for commitment of naive present-biased borrowers (\cite{Laibson2015}), we implemented a ``psychological commitment'' in the form of a salient promise to pay.
-\cite{PromisesPartnerships}, \cite{FurtherPromises}, \cite{Vanberg}, and \cite{Ismayilov2017} find that the ability to make a promise about behaving a certain way makes the individual more likely to adhere to the promised behavior.
-%and also induces trusting behavior by the recipients of the promise.
-To measure the causal effect of promises we implemented two other treatment arms.
-A \textit{promise-forcing} arm exactly analogous to our \textit{fee-forcing arm} except that instead of telling them that there is a fee if they don't pay on time, we made borrowers promise that they would pay one third of the amount in each of the 3 months, and told them that if they didn't they would have broken their promise and failed their word.
-Because salience is key we made them sign a (non-legally binding) personal promise and emphasized we were counting on them to keep their promise.
-A final arm (\textit{promise-choice arm}) gave clients the opportunity to choose between the \textit{Promise} contract and the \textit{Status-quo} contract.
-
-We document two main results in the promise arms.
-First, demand for the commitment-promise contract is three times bigger than for the commitment fee contract, with 31\% take-up.
-This difference between both choice arms suggests that clients are indeed understanding and taking into account the contractual parameters in their choice, and that the fee commitment was probably too strong from their point of view.
-In spite of this much higher take-up, the \textit{Promise-choice arm} had no effect on outcomes on average, or even for those who selected into promising.
-Second, being forced in to the \textit{Promise} contract also had zero effects on average and throughout the distribution on financing cost and pawn recovery.
-%\footnote{There is a decrease in financial cost in the 50th and 75th quantiles in the forced promise-commitment arm however.}
-Promises did not provide enough commitment so as to be reflected in behavior.
-
-This paper contributes to several strands of literature.
-First, to the broad literature on commitment demand.
-A significant literature has shown that demand for commitment exists but is somewhat low in some contexts (\cite{Ashraf}, \cite{Gine}, \cite{Ted}, \cite{Royer}, \cite{Sprenger}), and high in others (\cite{Kremer},  \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}, \cite{Pascaline}).
-We add to this literature by showing that very small fees are enough to drastically reduce demand for commitment, even when commitment is beneficial, and that softer commitments in the form of non-pecuniary personal promises elicit higher demand.\footnote{Our fees are 16 times smaller than than those of \cite{John} as a fraction of the loan/goal, and five times smaller converting peso values using exchange rates.} Second, \cite{Ted} and \cite{John} show the extent of commitment needed is underestimated even among those that buy it, and that subjects hurt themselves by self-imposing too weak a commitment in the intensive margin.
-We contribute in design by not allowing choice of the extent of commitment, and methodologically by inferring subjects underestimation of the value of commitment ex-ante from forgone treatment savings, instead of from subjects failing to reach their goal ex-post.
-Third, we focus on an important new context: pawnshop borrowing.
-Pawnshop borrowing is extremely prevalent in developing countries and very worrisome to regulators, yet severely understudied.\footnote{The World Bank's CGAP recognizes the importance of pawnshop borrowing worldwide but provides no statistics or analysis on it: \url{https://tinyurl.com/ydgob8pv}.}
-
-Fourth, we study \textit{both} causal effects and selection into frequent payment commitment loan contracts.
-\cite{Ghatak} state that ``high-frequency repayment, a feature in nearly all microfinance contracts, has been largely overlooked''.
-%\footnote{\cite{LittleAtAtime} also note that ``it is especially surprising that there is so little analytical discussion of the incentive effects of the installment system''.}
-This paper fills part of this gap.
-Studying causal effects of installment payment frequency \cite{Pande} find null effects loan default, a surprising result given the prevalence of frequent payment contracts.
-In contrast  we find strong effects of payment frequency on decreased default.\footnote{There are many differences in context between the papers which may explain the different result.
-\cite{Pande} focus on group lending with very little default to start with (less than 1\%), while in our case almost half of loans end in default.
-We also have a larger sample and we focus on individualized loans, which may afford us stronger statistical power to detect effects.} Our result is consistent with \cite{Field} who show that delaying payment in microfinance loans increases default.\footnote{\cite{Craig} use the discipline of regular loan repayments in microfinance to remind people to save and make a savings plan, and find large increases in savings.} On the other hand, studying selection into frequent payment microfinance loans, \cite{Murdoch} conjecture that ``[frequent installment payment] structure is potentially beneficial in fostering discipline among present-biased borrowers'' and may explain why borrowers choose it.
-They show that a robust positive correlation exists between displaying present biased preferences in surveys and selecting into microfinance, which they interpret as being due to high demand for the discipline imposed by frequent payments.
-However they acknowledge that this ``interpretation is suggestive...
-and needs to be confirmed by studies that establish causal links''.
-Our experimental \textit{is} a test of this causal link.
-We can isolate the pure effect of payment frequency on demand by randomly changing just this aspect of the contract.
-Our experimental results reject the hypothesis that microfinance (pawnshop) clients like and demand frequent payments, at least in our context.
-Importantly, our unique experimental design which simultaneously combines forcing and choice arms, paired with new machine learning methods to estimate heterogeneous treatment effects (\cite{atheygrf}), allows us to estimate whether there is positive or negative selection into beneficial contracts, and whether pawnshop clients forgo money by not demanding commitment.
-In consonance with what \cite{Walters} finds in another context, we find that it is not the case that those that benefit most from the contract demand it more.
-\cite{Sprenger} find a result that is similar to ours: that people how most need commitment (in our case the overconfident who show the greatest financial cost savings) are less likely to demand it.
-In contrast to \cite{Sprenger}, our context allows us to focus on money savings instead of estimated utility to proxy for benefits of commitment, a narrower but simpler measure.
-This allows us to measure effects on cost outcomes beyond take up and behavior.
-Our larger sample allow us to estimate heterogeneous treatment effects non-parametrically and perform counterfactuals this way.
-Finally, as in \cite{Rabin2018} we are able to contrasts subjects predictions of their behavior with their actual behavior, and how these map to outcomes, but we do it in a natural setting.
-
-Fifth, we also contribute to the literature on the effect of promises by testing their effect on the field.
-In consonance to this literature we find that people are willing and indeed voluntarily choose to make promises.
-In contrast to lab evidence however measured behavior was unchanged by promising and people did not keep their promise.\footnote{This is of course not a refutation of this literature.
-%not least because the laboratory literature is implemented on more tightly controlled environments and focused on subtler aspects of promising, like their effects on second order beliefs and guilt aversion.
-The context is also different since
-The lab literature has focused mostly on very concrete investment games between two players and looked at the effects of promises on trust and cooperation in those games.
-However our results do provide a first piece of evidence on the limitations of using promises to change behavior in the field.}
-
-%, consistent with a significant fraction of clients displaying naivete about self control problems (see \cite{Rabin2018}).
-Our context is one in which private paternalism (\cite{Laibson2018}) could work since almost all pawnshop clients would benefit from frequent payment contract yet there it almost no demand for them.
-After our experiment ended, Lender P started to tie in installment payment components to some of their contracts themselves.
-
-%\footnote{This is consistent with \cite{Belot2010}, who emphasize that elicited promised may have lower effects than voluntary ones.}
-%\cite{Rabin2018} and \cite{Ted} show that naivete may lead to the choice of to little commitment. 
-%Before discussing results, let us mention why these questions are relevant and how they relate to the literature.
-Most of microfinance involves frequent payments/meeting with the group --sometimes weekly-- even though this increases transaction costs.
-Several hypothesis have been postulated to explain this, from increased group's cohesion and monitoring, to forming personal payment habits or serving as a commitment device.
-Most of the literature (e.g.
-\cite{Pande}) find however null effects of increasing frequency on default, and therefore on payment habits, commitment, or peer pressure.
-
-%The paper is organized as follows.
-Section \ref{context} provides context and describes the data sources.
-Section \ref{Data} presents summary statistics and defines our main outcome variables.
-Section \ref{Experiment} describes the experiment and shows pre-treatment balance across arms.
-Section \ref{fee-commitment} estimates the effect of forcing clients into the fee-commitment contract, while Section \ref{fee-choice} studies the effects of choice.
-Section \ref{model} collects all findings and presents a model to rationalize them qualitatively.
-Section \ref{promises} assesses if promises work in our context as commitment devices.
-Finally, Section \ref{conclusion} concludes.
-
-\section{Context and Data} \label{context}
-
-\subsection{The pawn lender and high default rates}
-
-Pawn borrowing is one of the oldest forms of borrowing and one to which people with little access to the formal credit market turn to for ``emergency'' loans.
-They existed in antiquity at least since the Roman Empire, and there are records of it in China about 1,500 years ago (\cite{PawnShops}).
-As explained above pawn loans involve individuals leaving valuable and liquid assets (typically jewelry) as collateral in exchange for an immediate cash loan.
-We study such  context by partnering with Lender $P$, one of the largest pawn shops in Mexico, with more than one hundred branches spanning multiple States in Mexico.
-
-%Lender $P$ was interested in understanding why half of their clients lost their pawn.
-Default is high in this context  compared to many papers in the microfinance literature.\footnote{\cite{Pande} study of the effect of payment frequency in a context where the rate of default is close to 1\%.}
-We study a context with high borrower default.
-60\% of clients lose their pawn in a time span of 230 from the day of pawning.
-This default is likely inefficient since clients report a subjective value that is almost twice its gold value on average.
-It may also be detrimental from the lender's point of view since it may reduce the likelihood that the client becomes a return costumer, this may explain why Lender $P$ was interested in investigating whether a frequent payment contract would increase pawn recovery and costumer satisfaction, and whether there was demand for such a contract.
-
-One potential explanation for high default is that clients are really just selling their gold piece.
-This is unlikely for several reasons: (a) the reported subjective value of the pawn is larger than the loan size for 86\% of them, (b) among those that lose their pawn 58\% paid a positive amount towards its recovery and  34\% of the value of their loan (see Figure \ref{proxy_naive} in Appendix) --- this can only be rationalized if they expected to recover their pawn, (c) clients can easily sell the gold and obtain a higher amount of instant cash at gold buying stores located close to almost all our pawnshops (see Figure \ref{GoldBuyers}).
-%(d) there is a lot of engagement with the lender after pawning even for those who lost their pawn.
-On average clients that lost their pawn paid 34\% of the value of their loan, and close to 42\% of clients extended the loan for another cycle and made payments in the second cycle (see Figure \ref{proxy_naive} in Appendix).
-
-\subsection{The status quo contract}
-
-Lender P's business model is simple.
-They take gold jewelry as collateral in exchange for a fraction the value of the piece, in cash.
-No other collateral and no credit history checks are needed.
-The transaction takes less than 10 minutes and is conducted at the branch in person between the client and the appraiser (i.e.
-a teller, see Figure \ref{PawnshopPicture}).
-The appraiser weights the gold piece and runs tests on its purity.
-Based on these he assigns a gold value to the piece, stores it as collateral, and gives 70\% of the gold value of the piece in cash to the client.
-The borrower signs a 2-sheet contract with the main conditions of the contract at the branch and leaves with the cash.
-
-Lender $P$ had only one type of contract.
-It stipulated that the interest rate was 7\% \textit{per month} accumulated daily on the outstanding amount of the loan.
-The loan had a 90 days term with 15 days grace period, and the client could make payments at anytime with no penalty for pre-payment.
-If the client paid the principal plus the accumulated interest before those 105 days, then she received back her pawn, otherwise the pawnbroker kept the piece and any payments done.
-Before the contract expired, the client had the right to renew it (using the same collateral) for another 3 months by going to the pawnshop paying the accumulated interest and signing a new contract with exactly the same terms as the original one.
-%The pawnshop therefore makes money in three ways: by reselling the jewelry left as collateral on defaulted loans, by charging interest on non defaulted loans, and by keeping the payments made on defaulted loans.
-
-This contract was standard in the industry, but other lenders also had contracts involving frequent installment payments.
-The clients that pawned understood its conditions (as we verified in interviews) and still decided to pawn.\footnote{90\% of clients report in our survey they have pawned before.} These clients have little or no access to other types of loans and value the convenience of pawn borrowing.
-Potentially borrowers like it also because they are overconfident about the probability of recovering their pawn, as discussed below.
-
-\section{Data and summary stats} \label{Data}
-
-We worked in 6 branches of Lender $P$ of differing size and location, although for ease of implementation all of them in Mexico city.
-For these 6 branches we have two types of data, administrative data and survey data we collected for the experiment.
-
-\subsection{Administrative Data}
-The administrative data contains a unique identifier of the client, an identifier of the piece she is pawning, and the transactions relating to that piece.
-In particular, the value of the piece as assessed by the appraiser, the amount of money lent (70\% of the value), and the date when it was pawned.
-As described below, for our experiment the administrative data recorded the type of contract for that pawn.
-After the pawn happens, we follow each transaction related to that piece in the administrative data: when were payments made and for which amounts, whether there was default (i.e.
-the client lost her pawn), and whether any late-payment fees (active for the relevant experimental arms) were imposed.
-We have this information for all the pawns that occurred in the experiment's 6 branches between August 2nd 2012 and August 13th 2013, this includes all the pawns under our experiment but also those that happened 1 month before it started and up to 8 months after it ended.
-Figure \ref{exp_description}(a) shows the timing of the experiment and our admin data coverage.
-The black arrow represent the dates for which we have administrative data (before and after the experiment) while the light gray represents the duration of the experiment.
-The experiment comprises 13,444 pawns, and our administrative data cover a total of 26,179 pawns.
-
-\subsection{Survey Data}
-
-We had a team of enumerators in each branch collect surveys and clearly explain the contract terms to walk-in clients.
-The enumerators were inside the branch and asked clients to complete a short 5 minutes survey before going to the teller window to appraise their piece.
-The survey was short to avoid discouraging the potential clients from pawning, but at the same time it aimed to measure the following: demographics, proxies for income/wealth, education, self-control problems/present-biased preferences, experience pawning, if the family or friends commonly asked for money, how time consuming and costly was to come to the branch, the subjective probability of recovering their piece that they intended to pawn, the subjective value of their piece in money terms (for how much money would they sell it for), among others.
-We surveyed 7,704 clients (some refused).
-%\footnote{We also surveyed clients before and after the experiment, so our survey covers a larger sample that we are not using in this paper.}.
-The appendix \ref{baseline_survey} transcribes the questionnaire in English.
-Survey response rate is 57\%, and response is not related to admin data observables (details in Table \ref{balance_response} in the Appendix).
-
-\subsection{Summary statistics}
-
-Table \ref{SS} presents some summary statistics for the whole sample and by treatment arm.
-Because treatment arms are described below, here we concentrate on the overall average.
-Panel A describes variables from the administrative data.
-The average loan size is \$2171 MXN (\$105 USD).
-The average number of pawns per day per branch is 33.
-Although not shown in the table, only 40\% of clients recover their pawn within 230 days.
-Even those that recover their pawn tend to pay it back at the last moment, with only 17\% paying before the 90th day.
-
-Panel B reports stats from our survey data.
-73\% of clients are women, with an average age of 44 years; 66\% of them have completed high school or more, and 90\% have pawned before, so that our sample has mostly experienced borrowers.
-Finally the subjective probability of recovery is close to 93\% on average, which contrast with the 44\% recovery that happens in reality for the pawns in the control group.
-Borrowers seem to be highly overconfident on average (more on this below).
-The average subjective value they report for the pieces is 3265 MXN, which is much larger than the average appraised gold value of 2171 MXN.
-This makes it inefficient for them to lose it.
-
-Since the main treatment involves making clients come to the branch to pay each month, the transaction costs of coming to the branch are important.
-The average time they take to come to the branch is 22 minutes, and the amount of money they spend in transport to do that is 11 MXN (\$0.60 USD).
-The population we are working with is economically vulnerable in the sense that 30\% of them could not pay either water, electricity \& gas or rent in the past 6 months.
-They often receive negative income shocks: 87\% said they are pawning because of an emergency, and only 13\% stated it was to use in a `non-urgent expense'.
-%When asked why they are pawning this piece \hlgr{5\%} responded \hlgr{`lost a family member'}, \hlgr{`a medical emergency'} (\hlgr{11\%}), \hlgr{`an urgent expense'} (\hlgr{71\%}),
-
-\subsection{Financing cost and Default} \label{FC_def}
-
-Our main dependent variables are loan default and financial cost incurred by the borrower.
-Default is defined as losing the pawn.
-We define financial cost as the discounted sum of payments toward the loan plus the appraised value of the pawn, and subtract the appraised value of the pawn when it is recovered: $Financial \; Cost_i = \sum_t \frac{P_{it}}{(1+r)^t} + Pawn \: Value_i - \frac{\text{I}(Recovered \: Pawn_i) \times Pawn \: Value_i}{(1+r)^T}$, with $t$ indexing days, $T$ is the day when the pawn is recovered, I($\cdot$) an indicator function for recovering the pawn, $r$ is a daily interest rate equivalent to a 7\% monthly interest rate.\footnote{We experimented with different interest rates with similar results.
-See section \ref{neoclasical}.
-We also report result using the subjective value of the pawn reported by the borrower in the survey with similar results.} Figure \ref{fc_hist}(a) plots a histogram of this cost in pesos for loans where the pawn was recovered or lost.
-This cost is calculated for a time period of 230 days after loan origination, as %60\% of clients actually renew the loan one time.
-some clients renew the loan.\footnote{Figure \ref{fc_pro_2_115} reports results using the first 115 days only finding similar results.} Of those who renew 83\% lose the pawn.
-Figure \ref{fc_hist}(a) suggest that financial cost is significant, even for those that do recover their pawn.
-Panel (b) normalizes the cost by loan size.
-It shows that as a percentage of their pawn, most of the cost comes from clients that do not recover their pawn.
-For them the cost is between 140\% and 250\% of the loan value.
-%\hl{The difference between panel (a) and (b) arises since clients who lose their pawn tend to be those that pledge cheaper pieces.}
-We calculate an APR of 218\% on average for the control group.\footnote{The Annual Percentage Rate (for pawn $j$) is calculated as the internal rate of return $i$ such that $\sum_t \frac{P_{jt}}{(1+i)^t} + \frac{\text{I}(Default \: Pawn_j) \times Pawn \: Value_j}{(1+i)^T} - Pawn \: Value_j = 0$, where $T$ is the date the pawn was lost.}
-
-\section{Experiment} \label{Experiment}
-
-\subsection{Treatment arms and randomization}
-
-\noindent \textbf{Selection of branches.} Starting September 6th 2012, we implemented the experiment in 6 branches of Lender $P$.
-The branches were selected by Lender $P$ to be dispersed across Mexico city and have varying sizes.
-In four of them the experiment ran for 107 days, and in 2 of them we ran it for a shorter time to economize on data collection costs once we realized we would not be constrained by sample size.
-%Thus we eliminated \hl{the smallest} ones.
-Branches are more than 5 km apart from each other, and there is little substitution among them (only 1\% of consumers appear in more than one of our branches).
-
-\vspace{.2in}
-\noindent \textbf{The monthly installment contract.} For the purpose of the experiment we designed a new contract that is identical to the status quo contract in all respects except one.
-It has the same interest rate (7\% \textit{per month}) which accumulates daily on outstanding debt, it has the same loan size/collateral ratio (70\%), it has the same loan term (90 days, and a grace period of 15 days), and the gold pawn gets appraised in the same way by the same appraisers.
-The only difference is that it has a requirement that the client has to pay monthly: for the 3 month duration at least 1/3 of the loan value (plus accumulated interest) has to be paid before day 30th, 60th and 90th after loan disbursement.
-Failure to pay this amount triggers a penalty fee of 2\% of this minimum amount due, which is added to the amount that the client needs to pay to recover their pawn.
-This penalty acts as a commitment incentive to pay now vs paying later.
-The level of the penalty was determined by Lender $P$ after talking to clients and based on Lender $P$'s experience.
-They deemed 2\% something that was big enough to provide commitment but small enough that if clients had an emergency and could not pay, the fee would not cause the pawn to be unrecoverable.\footnote{In contrast with \cite{John} we don't let the clients choose the size of the fee.
-As that paper shows doing this results in wrong choices by naive present biased consumers.
-Our fee is much smaller than the median in her experiment as explained above.
-We also experimented with a contract where there was no pecuniary fee for paying late but where we clients made a personal promise to pay monthly.}
-
-\vspace{.2in}
-\noindent \textbf{Randomization.} Randomization was done at the branch-day level.
-Each day the system chose which types of contracts were on offer that day in the branch, and therefore which contract the client signed.
-Branch personnel did not know which treatment would happen which day.
-They were told that there were 5 different ``types of contract-days'' and that the system chose randomly which applied any given date, and that it could happen for instance that two consecutive dates had the same contract.
-They were also told that this way of operating was in place in various Lender $P$'s branches (they did not know which ones), and that it could be in place for several months.
-Randomizing at the day level limits the problem of contamination arising from clients realizing that other clients get different contracts than theirs.
-It also limits potential  manipulation by appraisers, who in the presence of individual level randomization could potentially pick their preferred costumers from the line or tell them to wait until their desired contract shows up on the screen.
-Intra-branch day correlation on the probability of default (ICC) is small, at 0.08, so we don't lose much power vis-a-vis individual level randomization.
-
-\vspace{.2in}
-\noindent \textbf{Treatment Arms.} We have 5 different experimental arms, which differ in which contracts were offered on a given branch-day.
-
-\begin{enumerate}
-    \item \textit{Status-quo forcing} arm: consisted of branch-days offering the status quo contract described in Section \ref{context}, and only this contract (as was standard). 
-    \item \textit{Fee-Forcing} arm: consisted of branch-days offering only the monthly installment contract with a fee for late payment as described above. 
-    \item \textit{Fee-Choice} arm: consisted of branch-days where the client was given \textit{a choice} between the monthly installment with fee contract, and the status quo contract.
-    \item \textit{Promise-Forcing} arm: consisted of branch-days which offered the monthly payment contract only, but where there was no fee for paying late.
-Instead, the client was made to sign a paper which said ``I promise to pay every month the corresponding sum of \_\_\_\_\_\_, on the dates \_\_\_\_\_\_, \_\_\_\_\_\_, and \_\_\_\_\_\_.
-This is \underline{not} a legal document and cannot be used in courts.
-It is just a \textit{personal promise}.
-If I do not comply I would have broken my word.''.
-After signing, the promise was read to the client by the appraiser.
-    \item \textit{Promise-Choice} arm: consisted on branch-days where the client was given \textit{a choice} between the promise-forcing and the status quo contract.\footnote{We did not allocate equal number of days across arms, since we were interested in having more power in some of them.
-The branch days allocated to each -- in order-- were 84, 80, 93, 68, 82.}
-\end{enumerate}
-
-By comparing the \textit{fee-forcing} arm vs the \textit{status-quo} arm we estimate the causal effect of mandatory installment frequency which acts as a incentive to pay earlier vis-a-vis the pay-when-you-want contract.
-On the other hand, having arms where clients can choose among these contracts allows us to study client's demand for commitment to pay earlier.
-A neoclassical consumer (with no intra-household concerns) would not voluntarily restrict her options of payment profiles (as in monthly payment contract) by being subject to fees, since she can always replicate the monthly payment profile herself under the status quo contract if she so desired.
-The status quo contract gives her extra flexibility to respond to negative income shocks.
-However, if clients have present biased preferences \textit{and} are sophisticated about them, they may choose the frequent payment contract as it has commitment value.
-This value would be traded off against the value of flexibility.
-
-This design also allows us to test if promises work in a natural field environment which to our knowledge has not been done.
-Promises could have larger or smaller commitment vaWe have 5 different experimental arms, which differ in which contracts were offered on a given branch-day.
-
-\begin{enumerate}
-    \item \textit{Status-quo forcing} arm: consisted of branch-days offering the status quo contract described in Section \ref{context}, and only this contract (as was standard). 
-    \item \textit{Fee-Forcing} arm: consisted of branch-days offering only the monthly installment contract with a fee for late payment as described above. 
-    \item \textit{Fee-Choice} arm: consisted of branch-days where the client was given \textit{a choice} between the monthly installment with fee contract, and the status quo contract.
-    \item \textit{Promise-Forcing} arm: consisted of branch-days which offered the monthly payment contract only, but where there was no fee for paying late.
-Instead, the client was made to sign a paper which said ``I promise to pay every month the corresponding sum of \_\_\_\_\_\_, on the dates \_\_\_\_\_\_, \_\_\_\_\_\_, and \_\_\_\_\_\_.
-This is \underline{not} a legal document and cannot be used in courts.
-It is just a \textit{personal promise}.
-If I do not comply I would have broken my word.''.
-After signing, the promise was read to the client by the appraiser.
-    \item \textit{Promise-Choice} arm: consisted on branch-days where the client was given \textit{a choice} between the promise-forcing and the status quo contract.\footnote{We did not allocate equal number of days across arms, since we were interested in having more power in some of them.
-The branch days allocated to each -- in order-- were 84, 80, 93, 68, 82.}
-\end{enumerate}
-
-By comparing the \textit{fee-forcing} arm vs the \textit{status-quo} arm we estimate the causal effect of mandatory installment frequency which acts as a incentive to pay earlier vis-a-vis the pay-when-you-want contract.
-On the other hand, having arms where clients can choose among these contracts allows us to study client's demand for commitment to pay earlier.
-A neoclassical consumer (with no intra-household concerns) would not voluntarily restrict her options of payment profiles (as in monthly payment contract) by being subject to fees, since she can always replicate the monthly payment profile herself under the status quo contract if she so desired.
-The status quo contract gives her extra flexibility to respond to negative income shocks.
-However, if clients have present biased preferences \textit{and} are sophisticated about them, they may choose the frequent payment contract as it has commitment value.
-This value would be traded off against the value of flexibility.
-
-This design also allows us to test if promises work in a natural field environmentlue that a pecuniary fee, something that we test by comparing behavior in the \textit{promise-forcing}  vs \textit{status-quo} arms.
-Panel (b) of Figure \ref{exp_description} shows how many contracts the experiment has on each arm (rectangles).
-And for the choice arms, it displays in blue how many people actually chose the commitment contract.
-
-%\subsection{Connection to the literature}
-%Our study connects with two strands of the literature on microfinance.
-But also to a nascent one that uses RCTs to study to what extent people self-sort to treatments that have larger beneficial treatment effects for them.
-On the microfinance literature the first paper we could find that used an RCT to evaluate the causal effect of frequent payments in loans is \cite{Pande}.
-In a group lending rosca context, they note that most contracts involved frequent repayments --even weekly in many instances-- even when this increases transaction costs.
-They note that clients could benefit from ``the fiscal discipline afforded by the more rigid payments''.
-Frequency could provide a commitment device for clients, could foster a payment habit, or could generate more trust from social interactions among the group of borrowers.
-All these potential benefits apply in our context, except those relating to social interactions, as we work with individualized loans.
-
-\subsection{More on implementation} \label{implementation}
-
-We want to highlight two potential threats to the validity of our experiment.
-The first is that the client can chose to leave the branch after the appraiser values her pawn and tells her the contract terms, generating differential attrition across treatment arms.
-We anticipated this possibility and trained appraiser to say --that whatever was the contract that day-- it was the only available contract for an undetermined amount of time.
-Empirically, attrition was not a problem.
-Table \ref{SS} shows that the number of pawns per branch per day across treatment arms is statistically identical.
-The last column of the table displays the p-value of an $F$ test of equality of means across arms and shows we cannot reject equality for any of the variables (p-value=0.38 for the number of pawns per day per branch).
-There is no evidence for selection across treatment arms for any of the admin or survey variables.
-
-The second threat is clients' understanding of contract terms.
-The terms need to be understood in order for choice to be meaningful, and for the monthly payment commitment contract to bite.
-We had two `check-points' to do this.
-First, two enumerators were present in each branch for the whole day during the duration of our experiment to explain to clients the contract terms.
-One of the aspects emphasized was that the frequent payment contract involved the commitment to pay \underline{each month} a third of the outstanding amount, and that there was a 2\% penalty fee (or, in the promise arms, the psychological cost of breaking a promise) for failing to do so.
-Figure \ref{ExplanatoryMaterial} translates a piece of the materials we used to explain the contracts (in this case a comparison sheet used in the Promise-Choice days to compare contracts terms side to side).
-The explanation took about 3-5 minutes and was pursued until the client said she understood the contract terms.
-Students then asked clients to explain back the contract terms and corrected any misunderstandings.
-
-There was a second check point.
-Before the clients signed the contract, the appraiser made them read them the ``Contract Terms Summary'' sheet shown in Figure \ref{PaperSlip}.
-It was a piece of paper given to clients after their piece had been appraised and the size of the loan determined, but before they signed their contract.
-The appraised read it and asked the client to sign it as a proof of understating.
-The sheet clearly indicates that this contract is a monthly payment one (numeral 1), that there is a penalty of 2\% for paying late (numeral 2), and the 3 payment dates (numeral 3).
-Finally, the bottom of the Figure \ref{PaperSlip} shows the paper slip we used for the promise arms.
-The clients had to put their name in a slip of paper where they stated they promised to pay monthly.
-
-We are confident the overwhelming majority of clients understood the contracts and made informed choices.
-As shown below, different contract terms did generate differential demand and differential behavior.
-Moreover, we can systematically predict demand based on consumer characteristics, beliefs and proxies for present biased preferences.
-
-\section{The effect of forcing clients into fee-commitment} \label{fee-commitment}
-
-\subsection{The effect of the fee-forcing contract on financial cost and pawn recovery} \label{TE_fee-forcing}
-
-Would clients benefit ---in terms of recovering their pawn and in terms of paying lower financing cost--- from having a monthly payment commitment contract \textit{forced} on them, vis-a-vis the status quo pay-when-you-want contract?
-We find they do.
-For each comparison, we separately estimate the regression equation (\ref{basic_reg}) below.
-
-\begin{equation} \label{basic_reg}
-    y_{ij} = \alpha + \beta T_{i} + \gamma X_{ij} + \epsilon_{ij}
-\end{equation}
-
-\noindent where $i$ refers to client, $j$ indexes branch, and $X_{ij}$ are branch and day-of-week fixed effects.\footnote{There is a minority of of clients that pawned again and got assigned a different treatment.
-Results are robust to excluding them.
-In the regressions we include them and add a dummy indicating who are these clients.} %\footnote{If we restrict ourselves to pieces that fall in a single-arm (64\%), then treatment reduces the financial cost by 5.7\%, increases the likelihood of recovering their pawn by 35\%, and increases the likelihood of repeat business by 66\%.}.
-Our main outcome variables $y_{ij}$ are measures of financial cost in pesos as defined in Section \ref{FC_def}, as well as an indicator variable for client $i$ losing her pawn.
-In this subsection $T_{i}$ is an indicator for $i$ having got the \textit{fee-forcing} contract, and $\beta$ estimates the average treatment effect.
-We cluster errors at the branch-day level.%\footnote{This is an ATE and not just an ITT since take up of treatment is 100\%.}
-
-\vspace{.2in}
-\noindent \textbf{Financial Cost.} Figure \ref{fc_pro2}(a) reports $\beta$ coefficients and their 95\% confidence interval from estimating equation (\ref{basic_reg}) using different definitions of financial cost.
-The leftmost coefficient corresponds to using the discounted appraised gold value of the pawned piece.
-The second coefficient uses the subjective value of the pawn instead.
-In both cases we find that being assigned to the fee-forcing commitment contract causes a large reduction in the financing cost the client incurred, of 9.5\% (\$304) in the fist definition and 13.3\% (\$478) in the second one.
-That is, we find that \textit{charging} clients a late payment decreases total \textit{fee-inclusive} financing cost.
-
-Financial cost incurred by pawn-shop clients is a key variable to study.
-However it does not take into account transportation cost or the opportunity cost of going in person to the branch.
-Given that the fee-forcing contract makes clients visit the branch more often (monthly), one may want a measure that includes those costs as well.
-Going in that direction, in a broader measure of costs, for each visit we add the self-reported transport cost plus a whole day's wage, multiplied by the number of visits.
-Adding a whole day's wage may exaggerate cost, but we still observe a reduction of this more comprehensive measure of cost caused by the frequent payment contract, although we lose more than 1/3 of the observations and it is more imprecisely estimated.
-
-\vspace{.2in}
-\noindent \textbf{Heterogeneous Treatment Effects.} Average cost reductions could mask substantial heterogeneity.
-Benefits are distributed broadly however.
-Figure \ref{fc_pro2}(b) displays results from quantile regressions at the 15$^{th}$, 25$^{th}$, 50$^{th}$ 75$^{th}$, and 85$^{th}$ percentiles.
-All of them are negative.
-Figure \ref{fc_pro2}(c) uses \cite{atheygrf} generalized random forests methodology to estimate individual treatment effects, and plots the distribution of those treatment effects.\footnote{\cite{atheygrf} use random forests of honest causal trees to estimate personalized treatment effects.
-The trees are such that at each leaf (partition determined by covariates) we obtain an unbiased estimate of a treatment effect using treatment and control observations in that leaf.
-The optimal partition of leaves is that which minimizes expected mean squared error of treatment effects predictions out-of-sample.
-The tree is honest because it uses one sample to build the tree and another one to estimate treatment effects within that tree.
-After the optimal tree is build, each person in each leaf is assigned the treatment effect of that leaf.
-\cite{atheygrf} show that their treatment effects are asymptotically normal, which allows us to construct confidence intervals for our treatment estimate in each leaf.
-} More than 90\% of clients experienced financial cost savings in the fee-forcing group compared to the status-quo group.
-Figure \ref{HTE_fee_forcing} in the Appendix shows that the causal cost savings are largest for the more economically vulnerable, %that report at baseline that they have problems paying for services like water, electricity and rent,
-those that report being stressed, women, those take more time to go to the branch, and those displaying overconfidence about recovering their pawn (see Section \ref{behavioral} for our measure of overconfidence).
-%those that have to incur in higher transport cost to go to the branch  and that asked to be sent reminders to pay, this later one being one proxy of being inattentive or sophisticated present-biased.
-
-\vspace{.2in}
-\noindent \textbf{Pawn Recovery.} Figure \ref{fc_pro2}(d) plots estimated treatment effects of the fee-forcing commitment contract with the dependent variable being an indicator of losing the pawn in less than 230 days.
-The leftmost coefficient shows that the fee-forcing commitment contract increases the likelihood of recovering the pawn by 11 percentage points (25\% of mean recovery).
-This result stands in contrast with \cite{Pande} who find no effect of payment frequency on default in a group lending microfinance context.
-Figure \ref{fc_pro2}(e) shows the distribution of heterogeneous treatment effects for losing the pawn: it shows that \textit{everybody's} likelihood of losing the pawn decreases.
-%Figure \ref{HTE_fee_forcing}(b) in the Appendix shows that those we classify as present biased, those that requested to be sent a reminder to pay, and those who have more problems paying for basic services experienced the largest increases on pawn recovery.
-
-%the second conditions on the population that paid any positive amount towards recovery of their pawn; the third conditions on having paid at least 30\% of the loan amount; the fourth conditions on the period covering the first cycle of the loan; the fifth on the period of the first cycle and paying any positive amount.
-
-\vspace{.2in}
-\noindent We conclude that penalizing borrowers for delinquency in a contract which has already has large penalties from default (losing the collateral in a highly collateralized loan) actually helps borrowers.
-
-\vspace{.2in}
-\noindent \textbf{Effects on other outcomes.} There are other (intermediate) outcomes that are impacted by being assigned to frequent payments.
-Table \ref{mechanisms} shows that the first payment happens 8 days earlier (column 1) in the fee-forcing arm than in the status quo one, and that the number of payments increases by 0.19 (column 2).
-Figure \ref{induced_to_pay_early} in the Appendix correlates heterogeneous treatment effects on financing cost and time of first payment and shows that those induced to pay earlier are also those that have larger induced reduction in financial cost.
-Treatment effects are concentrated on the intensive margin, as treatment does \textit{not} affect the fraction of clients who pay a positive amount (column 6).
-The percentage of the loan paid increases by 8 percentage points on average (column 7).
-However the percentage of the loan paid is not larger for those that end up losing the pawn (first row of column 8).
-
-\vspace{.2in}
-\noindent \textbf{Other sub-samples.}  Results survive if we focus on those that paid a positive amount (in treatment and control) towards loan recovery.\footnote{Although this is potentially a selected subsample, Table \ref{mechanisms} showed that there is no treatment effect the extensive margin, i.e.
-in $pay>0$.} We find that even those that paid a fee in the fee-forcing contract end up paying a smaller financial cost that those in the status-quo contract (Figure \ref{fc_pro2}a).\footnote{This conditions on those that paid a fee in the fee-forcing group, comparing this subset in treatment vs all of the control group.
-Results are similar if we condition in the control group on those who would have paid a fee given current behavior.
-Again we acknowledge these is an endogenous sample and that the estimate may not be a causal effect.}  Figure \ref{fc_pro2}d shows that the increase in pawn recovery is robust to defining recovery using the first 120 days of the contract, or restricting to those paying a positive amount towards pawn recovery.
-
-%we The 4th coefficient from left to right conditions on those who paid a positive amount (in treatment and control).
-Although this is potentially a selected subsample, Table \ref{mechanisms} showed that there is no treatment effect on pay$>0$.
-We were interested in this population to show that the effect is there for those who are serious about recovering their pawn.
-The fifth coefficient conditions on those that paid a fee in the fee-forcing group, comparing this subset in treatment vs all of the control group.
-Results are similar if we condition in the control group on those who would have paid a fee given current behavior.
-Again we acknowledge these is an endogenous sample and that the estimate may not be a causal effect.} We find that even those that paid a fee in the fee-forcing contract end up paying a smaller financial cost that those in the status-quo contract.
-
-\subsection{Effects of fee-forcing on repeat pawning}
-
-All clients are more likely to recover their pawn and almost all of them incur in a lower financial cost when assigned to a monthly payment commitment contract.
-This however does not necessarily show that they benefited in utility terms, and this is hard to show directly.
-If ---as suggested by \cite{Laibson2018}--- consumers used ``experienced utility'' as a guide to make future purchases, we conjecture that clients in the fee-forcing contract would be more likely to be repeat costumers vis-a-vis those that got status quo contract.
-This is indeed what we find.
-
-Figure \ref{reincidence} presents results of equation (\ref{basic_reg}) where the dependent variable is a dummy for the client being a repeat costumer.
-We define a client as a repeat costumer if, after experiencing at least 75 days of the respective treatment arm, she came back and pawned a \textit{different} piece.\footnote{Results are robust to using number of days experiencing the contract larger than 75.
-We know its a different piece from it having a different weight/value.}  The left most coefficient shows that the causal effect of the fee-forcing contract on repeat pawning is an increase of 5 percentage points in the probability of being a repeat costumer, this is 55\% increase on a mean re-incidence with respect to those that got the status-quo contract.
-This effect is not explained by clients recovering their first pawn with higher probability in the fee-forcing contract and re-pawning this same one since we make sure it is another piece (only 16\% recover their piece in the fist 75 days in the fee forcing contract).
-The second coefficient restricts the sample in the regression to those that had not recovered their pawn in the first 75 days and finds similar result.
-The third coefficient conditions on clients who recovered the pawn in both arms.
-The fourth coefficient focuses on the subsample who had or would have had a financial cost savings treatment effect above the median treatment effect in their first pawn.
-It shows that for these clients the likelihood of coming back is twice as large (although imprecise).
-That is, those that benefit more from the fee-forcing contract are more likely to repeat.\footnote{The second and third estimate must be interpreted with care as we are conditioning on a variable that may be affected by treatment.
-We view these as suggestive correlations.
-The fourth coefficient does not have that problem as it conditions on clients that by their pre-determined covariates are predicted to have above the median treatment effects (in both arms).} Experience with the frequent payment contract seems to be necessary as there is no effect of the monthly payment contract on repeat pawning in the first 30 or 60 days of the contract (see Figure \ref{reincidence_before} in the Appendix).
-%We also implemented an exit survey which clients filled when recovering their piece.
-Unfortunately it had low response rate (7\%), and we take its results with a grain of salt.
-In this survey 63\% of clients said they liked the frequent payment contract more than the status-quo one, and that it allowed them to avoid unnecessary expenses.
-%The coefficient on repeat pawning is just as big when we focus only 2nd pawns happening after the first was recovered (third coefficient ``fnr'').
-This is consistent with \cite{Laibson2018}'s conjecture that clients could be making decisions based on experienced utility.\footnote{The third coefficient conditions on the subsample that did recover their first pawn in both arms and finds a coefficient of 4pp.
-This is not a causal estimate as recovery is influenced by treatment, but we found it telling that the differences were similar to the causal estimate for the full sample.}
-
-We view this result as strong evidence that after experiencing the contract demand for it increases, consistent with \cite{Alcohol}'s conjecture that demand for commitment increases with experience with it.
-However there is an alternative explanation for this result, namely that forcing frequent payments effectively means awarding a smaller loan, and thus that clients may pawn again to compensate for the smaller loan.
-We are skeptical about this interpretation for several reasons.
-%First, typically the emergencies that trigger a pawn are short lived (e.g.
-needing to go to the hospital), and it is unclear why clients in the frequent payment arm wait for several months to re-pawn -- there is no effect of the monthly payment contract on repeat pawning in the first 30 or 60 days of the contract, (see Figure \ref{reincidence_before} in Appendix).
-First,  there are many alternatives lenders in this market, and if they did not like frequent payments why do they come back to Lender $P$ for another loan?
-Second, the fee is really small at 2\% of 1/3 of the value of the loan.
-The transaction costs of obtaining another loan are likely larger than incurring in this fee.
-So of the monthly payment makes the current loan ``smaller'' it is probably better to skip the monthly payment and incur in a fee than to get an additional loan.
-Third, we find larger effects of repeat buying for clients that experienced larger treatment effects, which the alternative explanation cannot explain.
-Fifth, the effect is present if we condition on clients that recovered their pawn (so its not driven by pawn recovery)\footnote{This in effect conditions on treatment and control clients that recovered their pawn.
-We are aware that we are conditioning on an endogenous variable and this must be interpreted as a correlation only.}.
-Finally, we were able to obtain observational data for all Lender $P$'s branches for the period January 2016 to May 2020, during which Lender $P$ expanded the new frequent payment contract.
-Using an instrumental variable strategy that exploits the expansion and availability of the frequent payment contract across branches, we show that being exposed to the frequent payment contract leads to an increase of 50 percentage points in the likelihood that in the subsequent pawn the frequent payment contract is chosen when both the status-quo one and the frequent payment contract are available  (see Appendix \ref{appendix_b}).
-This choice cannot be explained by the need of another loan, since it is about \textit{which specific type} of loan the clients chooses conditional on getting one.
-
-\section{The effect of giving choice} \label{fee-choice}
-
-Section \ref{fee-commitment} showed that the fee-forcing commitment contract reduced financing cost across the board, and that consumers themselves seemed to like it once they tried it.
-In such a case, one would expect a strong demand for it.
-This is not the case.
-
-\subsection{Demand for the fee-forcing commitment contract} \label{sec:demand}
-
-To study demand for commitment, in one experimental arm, we let clients freely choose between the two types of contract: the fee-forcing commitment contract or the status-quo contract.
-In spite of broadly distributed benefits of the fee-forcing commitment contract we documented above, 90\% of clients chose \textit{not} to have it, they instead preferred the status-quo one.
-As explained above we are fairly confident this was not because a lack of understanding of the contracts.
-
-What can explain this low demand?
-In the spirit of \cite{Blumenstock} we try to differentiate between explanations.
-One explanation could be risk.
-Even if the fee forcing contract generates cost savings on average, clients with risk averse preferences may not demand it if they perceive higher risk from it.
-Alternatively, even risk-neutral agents may not demand it if the cost of lost flexibility is high.
-If clients, for instance, face large and frequent income shocks which make it hard to repay monthly.\footnote{We don't observe income shocks in our data, making is hard to quantify how important they are.
-91\% of those in the fee-forcing arm incurred a fee, which suggests that shocks are not uncommon.} Below we focus on some explanations of low demand, while Section \ref{model} explores theories that can explain all the findings at the same time.
-
-\subsubsection{Behavioral explanations} \label{behavioral}
-
-The leading behavioral explanation in the literature for low demand for commitment is present biased preferences with naivete (e.g.
-\cite{Rabin2018}, \cite{John}, \cite{Laibson2018})  \cite{Laibson2015} shows that the lost flexibility resulting from a commitment contract can limit take-up especially severely when agents are naive about their self control problem.
-In our context if consumers are naive about their present bias, they would plan to save more (or spend less) than what they actually end up saving, thus making it be harder to recover their pawn.
-This under-saving will be mitigated in the fee forcing contract since the fee makes them save money to pay part of the loan periodically.
-Section \ref{model} formalizes this in a model.
-Another behavioral explanation is that clients may underestimate the likelihood and severity of negative income shocks.
-Both of these explanations predict that clients will be overconfident about their likelihood of pawn recovery.
-Recall that in the control group the client's subjective probability of recovery is on average 93\%, while actual recovery is just 44\%.
-A further piece of evidence consistent with underestimating negative income shocks is that a large number of people (31\%) in the control group pay a positive amount toward pawn recovery but end up losing their pawn anyway.
-
-So, overconfidence of recovering the pawn is implied by both present bias preferences with naivete and upward bias in their income expectations.
-But does overconfidence actually predict low demand for commitment empirically?
-It does.
-We define as overconfidence as the reported subjective probability of recovery minus the predicted probability based on the client's characteristics, $P^s_i-\widehat{P_i(X_i)}$.\footnote{We predict $\widehat{P_i(X_i)}$ in two steps.
-In step one we use Lasso with with cross validation to tune the regularization parameter to select the most predictive variables $X$.
-The typical present bias question as in \cite{Ashraf} was eliminated in this step.
-In the second step we estimate $\widehat{P_i(X_i)}$ using those variables in a logit model.
-The Lasso selected variables were type of pawn, female, age, has pawned before, has savings, participates in rotating savings, often feels tempted to change plans, would like to have a reminder to pay, and an economic vulnerability index.
-We are careful not to include these variables as controls in Table  \ref{oc_reg}.} There is a large amount of overconfidence in our context.
-Figure \ref{oc_hist} plots a histogram of $OC_i$ and shows that the overwhelming majority display overconfidence, and a large fraction overestimate recovery by more than 50 percentage points.
-
-\cite{Sprenger} have argued that it is critical to understand the link between beliefs and demand for commitment, yet the evidence is scarce.
-Table \ref{oc_reg} does this: it regresses an indicator of take up of the monthly payment contract against an indicator for overconfidence $OC_i:=\mathbbm{1}(P^s_i-\widehat{P_i(X_i)}>0)$ and controls.
-Controls $Z$ include branch and day of the week dummies, schooling, whether the client does a monthly budget plan, among others.
-We are careful not to include controls that were used in $\widehat{P_i(X_i)}$.
-% and a measure of intertemporal preference reversal analogous to that of \cite{Ashraf} as controls.\
-In the choice-fee arm, being overconfident decreases the likelihood of demanding commitment by 12 percentage points a result that this is robust to including controls  (columns 1 and 2).
-While overconfidence predicts lower take up in the fee-choice arm, this is not the case in the promise-choice arm (columns 3 and 4).
-One interpretation of the results is that the overconfident borrowers think they do not need commitment, and their demand decreases sharply as soon as there is even a small fee, and at the same time they perceive the promise as a low cost option.
-This provides evidence for \cite{Sprenger}'s conjecture that ``tepid demand for commitment outside controlled experimental settings is consistent with broad unawareness [of biases]''.
-
-How does overconfidence map to cost outcomes?
-Theory predicts that the more overconfident (naive) may be at the same time those that benefit more from commitment.
-Extrapolating individual treatment effects of the fee-forcing contract vs the status quo one to the choice arm (see below for more detail), and using them as a dependent variable we find that overconfident borrowers benefit \textit{more} from the commitment contract, with 24.8\% (=\$30/\$121) more savings (columns 5 and 6).
-Thus while we predict the overconfident benefit more from commitment, they demand less.
-
-\vspace{.2in}
-Our measure of overconfidence is useful especially when there is limited time for a detailed survey.\footnote{It may be more useful than a simple elicitation of present bias as in \cite{Ashraf}.
-We find that 15\% of clients are classified as present biased using this measure of preference reversal.
-This level is similar to the number \cite{Ashraf} find but small to explain no take-up of commitment for 90\% of clients.
-This measure was not correlated with take up of commitment in our sample.} First it is very prevalent, which makes it promising to explain the overwhelming prevalence of low take up.
-Second, it is easy to measure.
-Third, it is predictive of take-up in an intuitive way.
-Finally, overconfidence in recovery is implied by present bias with naivete but also by biased expectations of negative income shocks, thus capturing both kinds of bias.
-
-\subsubsection{Neoclassical Alternatives} \label{neoclasical}
-
-\vspace{.1in}
-\noindent \textbf{Risk aversion.} We do not have measures of risk aversion in our short survey, which makes it hard to assess the hypothesis that risk aversion limits take-up of the fee frequent payment contract.
-One way to proceed is to take the empirical distribution of financing cost ---$F_{fee}(FC)$--- as one the client would have faced had she chosen the the fee-commitment contract.
-We could then ask what would risk aversion have to be in order to justify the client choosing the fee-commitment contract distribution of costs over the distribution associated with the status quo contract, $F_{sq}(FC)$.
-Framed as a choice among cost distributions, we can calculate what risk aversion is needed to rationalize the choice of the status quo contract.
-This exercise of course assumes --as it is common in economics-- that clients know the distribution of financial cost, that it is common across consumers (although this can be relaxed), and that this cost distribution is the only difference among contracts.
-Fortunately for us it turns out that one distribution first-order-stochastically dominates the other, we do not need to calibrate a specific utility function or use a parametric distribution function in order to rank them in terms of expected utility.
-We use the fact that if the utility $u(FC)$ is decreasing in $FC$ and $F_{fee}(FC) \geq F_{sq}(FC)$ for all $FC$, then $E_{fee}[u(FC)] \geq E_{sq}[u(FC)]$.\footnote{See the appendix for the proof.} That is any expected utility maximizer who dislikes paying higher financing cost, regardless of the concavity of his utility function, will prefer the fee-commitment distribution of financial cost.
-Figure \ref{ecdf_fc} in the Appendix shows that indeed $F_{fee}(FC) \geq F_{sq}(FC)$.
-Moreover, Table \ref{stochastic_dominance} shows that this holds also for an overwhelming majority of sub-populations.
-
-%To have a benchmark we implement a very simple calibration exercise in two steps.
-First, we fit a Weibull distribution to the distribution of financing cost, were the scale and shape parameters depend on client's and loan observable characteristics.
-We do this separately for the status quo contract and the fee-forcing contract, obtaining two distributions $f_{sq}(FC|X;\Gamma_1)$ and  $f_{fee}(FC|X;\Gamma_2)$ with different parameters $\Gamma_1$, $\Gamma_2$.
-Second, we assume a representative consumer with a CRRA utility function over financial cost, $u(FC)=\frac{1}{1-\theta}FC^{1-\theta}$.
-We then ask what would $\theta$ have to be for a consumer to prefer the status-quo contract.
-That is for which $\theta$'s would  $\int u(FC|\theta)f_{sq}(FC|X;\Gamma_1) dFC \geq \int u(FC|\theta)f_{fee}(FC|X;\Gamma_2) dFC $ hold?
-It turns out that it holds for risk aversion levels that are too high to be believable.
-That is, with our calibration, it seems unlikely that risk aversion is reducing demand for the fee-forcing contract.
-
-\vspace{.1in}
-\noindent \textbf{Lost flexibility.} A second explanation for low take up is lost flexibility.
-That is, the fee-commitment contract may provide too much commitment which is costly because the client may be forced to incur in late payment fees if he experiences a negative income shock.\footnote{Note that income shocks that affect the ability to pay the entire loan are a worry for both the fee-forcing contract and the status quo one, and should not make one contract more favorable than the other.} While we cannot rule out that income shocks combined with lost flexibility of the contract explain the low demand, we think it is unlikely.
-First, we showed above clients report a subjective probability of recovery of 93\% on average, which suggests they are not too worried about income shocks.
-Second, the fear of incurring fees is quantitatively not enough of a concern when compared to the savings they are experiencing.
-%Note that fees for late payment are not that high.
-In an average loan of 2,000 pesos the monthly payment is close to 700 pesos, and a fee of 2\% of that is 14 pesos (less than \$1 dollar).
-This is about \hlgr{1\%} of monthly per capita income of the first 3 deciles of Mexican \hl{household's} income distribution.
-%This compares favorably to the \hlgr{\$11.6 + \$62.3)} pesos transportation / transaction cost of one.
-To make this concrete, we calculated what the financing cost of the fee-commitment contract would be if all its clients incurred in \textit{all} potential fees (while keeping payment profiles and pawn recovery constant) and added these fictitious fees to financing cost for those in the fee-forcing arm, thus artificially inflating their cost.
-We then re-estimated the quantile treatment effects analogous to Figure \ref{fc_pro2}(b) with this inflated financial cost.
-%\footnote{Of course behavior may not be constant, but we believe this is a reasonable fist approximation.
-%It could be that having this small fee added to the balance discourages them to pay or makes it harder to pay back the loan.
-But the contrary may also happen, with the fee making them more determined to pay early.
-We would need a structural model of client behavior to estimate a full counterfactual.
-We suspect that such small fees would not generate large changes in behavior in a simple neoclassical model.}).
-Figure \ref{fc_allfee} presents the results.
-We find that even in this extreme scenario, tilted against the fee-forcing contract, the estimated effect still implies cost savings from the fee-forcing contract at the mean, 25$^{th}$, 50$^{th}$, and 75$^{th}$ percentiles.\footnote{Recall that the differences in financing cost already takes into account the fact that clients in the fee forcing contract sink more pre-payments than those in the status quo contract, and that those prepayments are lost if the loan is not fully paid back.}  Although these arguments are not definitive, they suggest that low demand for commitment may be driven by more than the anticipation of lost flexibility.
-
-\vspace{.1in}
-\noindent \textbf{High time discounting.} We mentioned above that clients in the status quo contract tend to wait until the last moment to pay to recover their pawns.
-Even among those that recover their pawn, only 42\% pay before the 90$^{th}$ day.
-Table \ref{mechanisms} shows that clients assigned to the fee-forcing contract front load their payments, starting their first payment earlier and finishing to pay earlier too.
-However, clients may dislike front loading payments if their time preference discount rate is high.
-They may be willing to trade off a higher probability of losing their pawn for more \textit{back} loaded payments.
-
-What would discount rates have to be in order for back loaded payments to offset the reductions in financial cost effects we observe?
-%We can calculate this number by looping across a grid of discount rates, incorporating this higher discount rate in the definition of financial cost, and reestimating equation \ref{basic_reg} with this modified financial cost measure as the dependent variable in equation 1, searching for the discount rate that makes $\beta$ equal zero.
-We did this and obtained
-The discount rate that rationalizes a zero effect is a staggering 8,190 percent per year.
-We find this discount rate implausibly high even for this credit constrained population\footnote{For comparison, \cite{Levin} find that a discount rate of 1,415 per year for subprime borrowers in the US is too high to be believable.}, casting doubt on high discount rates as explanation for low demand for commitment.
-%\footnote{In the baseline survey we give respondents a hypothetical choice between $100$ pesos tomorrow or $150$ pesos in one month (an implicit yearly interest rate of \hl{12,800\%}) and only 30\% chose the later one.}
-
-\vspace{.2in}
-\noindent All in all, present bias with naivete is the more likely explanation for low commitment demand in our case.
-Moreover, Section \ref{model} shows that present bias with naivete is able to qualitatively explain all the main findings of the paper, not just low demand for commitment.
-
-\subsection{The effect of choice on pawn recovery and financial cost} \label{effect_choice}
-
-When preferences or income streams are heterogeneous, and consumers are neoclassical, giving choice among contracts is often a welfare increasing strategy.
-Consumers would chose the contract that best fits their needs.
-This holds also in most simple models of present bias preferences if consumers are sophisticated about their present bias.
-%Actually, it could be the case that the opportunity of choosing itself could affect behavior.
-But when consumers are overconfident about their ability to save cash to pay back the loan, free choice could be a sub-optimal policy from the point of view of the client's long run self, and match the clients with a more costly contract.
-Defenders of choice make another subtler point: that even if take up of the commitment-fee contract is low, the sole fact of having choice could potentially change behavior (\cite{Dalboetal:2010}, \cite{Sjostrometal:2018}, \cite{Tlaxcala}).
-
-Giving clients the option of choosing among the fee-forcing and the status quo contract does \textit{not} lead to lower financial cost compared to forcing them into the status-quo contract.
-Nor does it lead to higher pawn recovery.
-The hollow circles in Figure \ref{fc_pro4}(a) show zero average effects for the different definitions of financial cost analogous to the ones described above.
-Figure \ref{fc_pro4}(b) shows further that the null effect happens for the 15$^{th}$, 25$^{th}$, 50$^{th}$ 75$^{th}$, and 85$^{th}$ percentiles.\footnote{The few that selected the fee-commitment contract (the solid black squares) do enjoy cost savings of 1005 MXN, which compares favorably to the 304 MXN in the fee-forcing arm (as a fraction of the loan the numbers are 41.5\% and 12.5\%), but this combines the selection and treatment effects.} %Figure \ref{heterogeneous_te_4} plots the distribution of treatment effects and finds that the distribution offering choice actually \textit{increased} financial cost and default for about half of clients compared to being assigned the status-quo contract.
-Those tended to be the less economically vulnerable and more educated, \hl{women}, and those whose family typically asks them for money.
-Figure \ref{fc_pro4}(c) finds null effects for pawn recovery. Consistent with these findings, Figure \ref{reincidence} finds no effect on repeat purchases for the fee-choice group.
-
-\subsection{The scope for private paternalism}
-
-This is not the first paper to find low demand for commitment, however it is the first we know of that can compare choice vs forcing.
-The fact that the fee-forcing contract lowers financial costs for almost all clients, together with the fact that only 10\% choose it must mean that many consumers are choosing contracts with higher financial costs for them.
-We can ask how many consumers seem to be making a cost increasing choice and how much money are they leaving on the table.
-We conduct two exercises.
-
-\vspace{.2in}
-\noindent \textbf{Are there ``mistakes'' in choice?} Answering this question requires calculating a counterfactual: for each client in the choice arm we want to know how much cost savings she would have had she chosen the opposite contract.
-We do this in two steps.
-First, using the honest causal forests method of \cite{atheygrf} described above we calculate the causal effect on financing cost of getting the fee-forcing contract instead of the status quo contract for a client with characteristics $x_i$ \textit{in the forcing arms}, we call it $TE^{fee}_{i}(x_i)$.
-Recall that \cite{atheygrf}'s method uses causal trees to generate a partition of the space of characteristics $x$, where each element of the partition is a leaf, and each leaf contains treatment and control clients with similar characteristics $x$ which are used to calculate unbiased honest treatment effects for that leaf.
-Second, we predict treatment effects for clients \textit{in the choice arm} using the partition into leaves and the treatment effect associated with the leaf obtained in step 1, that is client $j$  is imputed the treatment effect of the leaf corresponding to her characteristics $x_j$.
-We call this counterfactual treatment effect $\widehat{TE}^{fee}_{i}(x_j)$.
-This is precisely the counterfactual we wanted.\footnote{This extrapolation of the treatment effects assumes that choice itself --conditional on a given contract-- does not affect behavior.
-Given the results in subsection \ref{effect_choice} we are comfortable with this assumption.
-Note that although the extrapolation is to another population, by randomization it is a statistically identical population with common support.} Armed with this, we say that a client made a ``mistake'' if either she chose the status quo contract and her $\widehat{TE}^{fee}_{i}$ is negative (i.e.
-more cost saving from the fee contract), or if she chose the fee-commitment contract and $\widehat{TE}^{fee}_{i}$ is positive, meaning that financial cost are larger for the fee-commitment contract.
-When a client made a choice mistake, we say that the peso-size of it is $|\widehat{TE}^{fee}_{i}|$.
-
-%Using the forcing arms and extrapolating to the choice arms.
-%Then, we predict these treatment effects for everybody in the choice arm using characteristics $x_i$.
-Let $\widehat{TE}^{fee}_{i}$ be the predicted financial cost savings for person $i$ of choosing the fee-forcing contract rather than the status quo one, divided by the size of her loan (i.e.
-the negative value of the predicted treatment effect on financial cost for person $i$).
-$\widehat{TE}^{sq}_{i}$ is the analogous for the status quo contract.
-We define the choice of person $i$ to be a ``mistake'' if
-
-%\begin{equation}
-% \{ i \; \text{chose} \; sq \; \text{and} \; \;  \widehat{TE}^{fee}_{i}>\widehat{TE}^{sq}_{i} + z \} \; \text{or} \; \{ i \; \text{chose} \; fee \; \text{and} \; \;  \widehat{TE}^{fee}_{i}<\widehat{TE}^{sq}_{i} - z \}
-%\end{equation}
-
-Since the prediction of the treatment effect is an estimate and has noise, we do two things.
-First, we normalize $\widehat{TE}^{fee}_{i}$ by the value of the loan of person $i$ and introduce a threshold parameter $z$ and say that a choice is a ``mistake'' if the alternative contract would generate greater than $z$ in savings.
-That is, we introduce a threshold that we vary from 0\% to 15\% of the value of the loan.
-Second, we take into account uncertainty in estimation of treatment effects and report results using the extremes of the 90\% confidence interval bounds for $\widehat{TE}^{fee}_{i}$.
-
-Figure \ref{choose_wrong}(a) plots in the left Y-axis the fraction of clients that made a choice ``mistake'' and on the right Y-axis the peso size of the mistake.
-In the X-axis it varies the threshold $z$ of what we classify as a mistake.
-When $z=0$, we calculate that about 80\% of clients in the fee-choice group chose contracts that induced \textit{higher} financial cost (90\% confidence interval [45,94]).
-Most mistakes are failures to choose the fee-commitment contract (92\%), while only 8\% of those who chose the fee-commitment contract would have been better in the status-quo one.
-The average mistake in pesos is \$238 (90\% confidence interval [140,390]).
-Figure \ref{choose_wrong}(b) separates the analysis for those we classify as overconfident about recovering their pawn vs the rest.
-It shows that there are about 11 percentage points more mistakes in the overconfident population (when $z=0$).
-
-All the above suggests that forcing clients into commitment contacts may reduce financial cost for the overwhelming majority of clients.
-Figure \ref{choose_wrong}(c) calculates what fraction of clients would be made better off if we forced them to the fee-commitment contract: 92\% when $z=0$, and they would on average have savings of 232 MXN.
-This conclusion is in line with a recent paper by \cite{John}.
-In a savings context, she finds that when commitment is on the menu a majority of subjects wrongly choose to little commitment.
-She concludes this by observing high levels of default even with late payment fees, whereas we work directly with estimated counterfactual treatment effects.
-
-\vspace{.2in}
-\noindent \textbf{Is there positive selection on treatment effects?} The previous exercise consisted on extrapolating treatment effects from the no-choice arms to the choice arm.
-Here we do the converse.
-First, we estimate a flexible model of take-up of the fee commitment contract \textit{in the choice arm} using random forests and obtain for a client with characteristics $x_i$ a probability $P(x_i)$ of choosing the fee-forcing contract.
-We then use this model to predict the counterfactual probability of a client with characteristics $x_j$ choosing the fee-commitment contract in the no choice-arms if she would have been given the choice, what we call $\widehat{P(x_j)}$.\footnote{Our random forest take-up model has a good out-of-sample fit with an out-of-sample AUC of 0.85.
-We think we are not introducing too much noise by this extrapolation.} Second, armed with this prediction in the no-choice arms, we can ask the following: is it true that people with larger fee-forcing contract treatment effects (i.e.
-more cost savings) are more likely to have demanded the fee-forcing contract if choice had been given to them?
-
-Figure \ref{choose_wrong}(d) plots $\widehat{P(x_i)}$ in the X-axis, and the heterogeneous treatment effects we estimated in section \ref{TE_fee-forcing} in the Y-axis.
-If it was true that those with larger cost savings have larger demand for the fee-commitment contract, we would expect a negative slope (recall that more savings mean lower financial cost in the Y-axis).
-This is not what we find.
-Figure \ref{choose_wrong}(d) is a binscatter that splits the X-axis in 100 percentiles bins of predicted take-up probability and for each bin averages the financial cost treatment effects.
-Using all clouds we estimate a slope close to zero in the relationship.
-Using the 80 right most points, we estimate a \textit{positive} relationship.
-A positive relation means that those more likely to demand commitment are also those that had smaller benefits from commitment.
-This result is similar to \cite{Walters}, who finds that students that select into more effective schools are the ones with smaller treatment effects from attending.\footnote{\cite{Walters} uses distance to school as an instrumental variable for choice, while we use randomization to choice vs no-choice groups as our empirical strategy.}
-
-\section{Viewing the results through a simple model} \label{model}
-
-This section uses a model to interpret our empirical results.
-The model is stylized but incorporates important features of our context.
-First, it allows for negative income shocks which we think are prevalent in this population (that's why they pawn in the first place)\footnote{71\% say they need the money for an emergency.}.
-The shock generates a cost of committing to monthly payments and could potentially be a reason for low take up.
-Second, it features clients with present biased time preferences and allows for naivete about them.
-As we discuss below these two features parsimoniously explain several facts about the context ---e.g.
-overconfidence in recovering the pawn, and large inefficient default---  and about the results ---e.g.
-forcing commitment seems to help, and that there is also some (although small) demand for commitment at no benefit for neoclassical consumers.
-Third, it incorporates the fact that the pawned piece is more valuable than the loan.
-Fourth, it allows for a simple way to model commitment afforded by late payment fees.
-Nonetheless, the model abstracts from several details of the context.
-Even with these abstraction it allows us to explain our six main results listed in Section \ref{explanations_recap} below.
-
-\subsection{A simple model} \label{model_detail}
-
-We use the model of \cite{John} and refer the reader to that paper for more detail, justification of assumptions and some of the proofs.
-The model has three periods and linear utility.\footnote{This does not map perfectly to our 3 period contract, but it is enough to generate the results we need.} Period $t=0$ is a planning period where the client is either allocated to the status quo, the fee-forcing contract, or a choice between the two.
-Period $t=1$ is the savings decision period, and $t=2$ in the pawn recovery (loan payment) period.
-In period 1 the client receives her income $y_1=1$, or gets zero with probability $\lambda$.
-She can consume ($c_1$) or save ($s_1$) part that income.
-In period 2 the client gets her savings from period 1, and again receives income of either $y_2=1$, or zero with independent probability $\lambda$.
-In this last period, she decides whether to use income and savings for consumption $c_2$ and/or for paying back the loan of size $p \in(1,2)$ to recover the pawned piece valued at $b>p$.
-In this simple set up we model the fee-commitment contract as a contract that imposes a fee of size $F$ if the client fails at $t=1$ to save $s1=p-1$ pesos, which is what is needed to pay the loan back when there are no shocks.
-In period $t=0$ she evaluates her welfare as $E[c_1+c_2]$, were for simplicity we have set the time discount to one.
-We also assume the interest rate is one.
-We introduce present biased preferences by assuming the following utility function $U_t=c_t+\beta \: \sum_{k=t+1}^{2} E[c_k]$, with $\beta<1$ indicating present bias.
-A naive client perceives she is not so present biased and instead of $\beta$ uses $\hat{\beta} \in (\beta,1]$.
-
-Note that under these assumptions it is efficient at $t=0$ to recover the loan since $b>p$ and since there is no discounting at $t=0$.
-Because $b>1$, paying back the loan requires that there is no negative shock in any period and that $s_1>0$.
-Because $\beta<1$ at $t=1$ the client will not send savings in excess of what is needed to recover the loan: $s_1=p-1$.
-This parsimonious model implies the following results:
-
-\vspace{.2in}
-\noindent \textbf{Result 1: Present biased clients default more.} Under the status-quo contract, absent shock realizations, present biased clients (sophisticated or naive) with $\beta<\beta_{SQ}<1$ will lose their pawn, while clients with no present bias will not.\footnote{$\beta_{SQ}=\frac{p-1}{\lambda(p-1)+(1-\lambda)(b-1)}$.
-See Proposition 1 in \cite{John}.}
-
-\vspace{.1in}
-\noindent \textbf{Result 2: Forcing present-biased clients into the fee-commitment contract reduces default.} Imposing a fee $F>0$ for late payments weakly decreases default (for present biased clients only).
-It strictly decreases default if $F>F_{min}(\beta):=(p-1)-\beta[\lambda(p-1)+(1-\lambda)(b-1)]$.
-The larger the present bias the larger the $F$ required to induce pawn recovery.\footnote{$F_{min}(\beta)$ is derived from the incentive compatibility constraint needed to generate savings at $t=1$ to recover the pawn can be written as $1-(p-1)+\beta[\lambda(p-1)+(1-\lambda)(b-1)] \geq 1-F+\beta(1-\lambda)$.}
-
-\vspace{.1in}
-\noindent \textbf{Result 3: Demand for commitment.} Given $F>0$, (a) Neoclassical clients will never demand commitment.
-(b) Present-biased sophisticated clients will prefer the fee-forcing contract over the status quo contract $\iff$  $\lambda \: F<(1-\lambda)^2(b-p)$ and $F>F_{min}(\beta)$, that is $\iff$  $\beta \in [\beta_{min},\beta_{SQ}]$.\footnote{$\beta_{SQ}$ was determined in Result 1.
-$\beta_{min}$ is such that $F=F_{min}(\beta_{min})$.} (c) Analogously, naive clients will demand commitment $\iff$ $\hat{\beta} \in [\widehat{\beta_{min}},\beta_{SQ}]$, where $\widehat{\beta_{min}}<\beta_{min}$.
-So strongly naive clients will on the one hand demand more commitment than sophisticated clients since they believe (incorrectly) that a smaller fee will motivate them to pay.
-On the other hand they may demand less commitment since they think they can save and pay on their own.
-Whether they demand more or less than sophisticated clients depends on the empirical distribution of $\beta$ and $\hat{\beta}$.
-
-\vspace{.1in}
-\noindent \textbf{Result 4: Overconfidence.} Only naive clients will be overconfident about the probability of recovery.
-This will be true whether they have the status quo or the fee-forcing contract.
-Overconfidence is increasing in $\hat{\beta}$.
-
-\vspace{.1in}
-\noindent \textbf{Result 5: Welfare.} (a) Neoclassical consumers' welfare strictly decreases when we force clients into the fee-commitment contract instead of the status quo contract, and does not change when we offer a choice between them.
-(b) The welfare of sophisticated present biased consumers weakly increases when we give them choice, and it strictly increases  $\iff$  $\beta \in [\beta_{min},\beta_{SQ}]$, that is when they would choose the fee-commitment contract themselves.
-Forcing them into the fee-commitment contract increases welfare $\iff$  $\beta \in [\beta_{min},\beta_{SQ}]$, otherwise it strictly decreases it.
-So choice is better than forcing for sophisticates.
-(c) Forcing can be welfare improving for the naive.
-Indeed if $\hat{\beta}>\beta_{SQ}>\beta$ then forcing the fee-commitment contract increases welfare, and if $\hat{\beta} \in (\widehat{\beta_{min}},\beta_{min})$ then forcing the status quo contract increases welfare.\footnote{This result is different from that in \cite{John}.
-Her context has individuals choosing the size of the fee.
-In that context naive clients will \textit{always} chose the wrong fee size and default later, therefore choice is always decreasing for the naive.
-In our context $F$ is fixed at 2\% of the balance due, and this implies that choice could be welfare improving for some naifs.}
-
-\vspace{.1in}
-\noindent \textbf{Result 6: Welfare and ex-post observed behavior.} If for a naive client $i$ the fee-forcing contract causes higher pawn recovery, then we know the fee $F$ made her IC constraint binding, and therefore that $\hat{\beta}_i>\widehat{\beta}_{min}$.
-If in addition if it was the case that $\beta_i<\beta_{SQ}$.
-%\footnote{\hl{Isaac, aqui tengo dos pregutas: (1) si es $\beta$ y no $\hat{\beta}$ verdad?
-(2) Para que una persona naive empenie en el status quo tiene que ser que cree que va a recuperar no?
-Es decir tiene que ser $\hat{\beta}>\beta_{SQ}$ correcto?}}
-then the fee-forcing contract would have increased welfare for the naive.
-That is, our finding that the fee-forcing contract increases pawn recovery is a sign of higher welfare (although not a sufficient condition).\footnote{It is not sufficient since ex-ante the commitment $F$ may have been too expensive given the income shocks, i.e.
-if $\lambda \: F>(1-\lambda)^2(b-p)$.}
-
-\subsection{Interpretation}
-
-The model of \cite{John} is very parsimonious but powerful and it can potentially explain all facts qualitatively.\footnote{The model is sufficiently stylized that we think we would not gain much from estimating it.
-Furthermore we have no data on income shocks which figure prominently in the model.
-\cite{Ted} and \cite{Aprajit} are two very recent models that combine a field experiment with commitment contracts and estimation of present bias parameters.} First, it can explain why default is high in the status-quo contract, namely that clients are present biased and have no commitment devices.
-Second, it can explain why clients are overconfident in our data, namely by virtue of naivete about present bias.
-Under the model naivete is necessary to explain this.
-Third, it can also explain why the fee forcing contract induces lower default, but not for everyone: namely that it makes the IC constraint for the present biased binding while it was not binding in the status quo contract.
-Fourth, it can also explain why there is low demand for commitment even if it seems to improve welfare: namely that there is a small share of neoclassical and sophisticated clients, and at the same time naifs have  $\hat{\beta}>\beta_{SQ}$ and therefore think they can save on their own.\footnote{By Result 6 we can eliminate $F<F_{min}(\widehat{\beta}$) as an explanation.} Fifth, it explains non-zero demand for commitment for a set of clients.
-Sixth, it can explain why clients exposed to the fee-forcing contract are more likely to come back, namely that $\hat{\beta_i}>\beta_{SQ}>\beta$ and so their welfare increased as a result of being forced into the fee-commitment contract, and they realized this after experiencing it.
-
-\subsection{Other potential explanations: recap} \label{explanations_recap}
-
-There may be other interpretation of the empirical findings. But the bar is high. An alternative explanation will need to explain the 6 facts below:
-
-\begin{enumerate}
-\itemsep0em 
-\item High (although ex-post inefficient) default in status quo contract.
-\item Overconfidence about pawn recovery.
-\item Forcing commitment increases pawn recovery.
-\item Small demand for commitment...
-\item ...but positive demand for commitment.
-\item Forcing commitment makes clients more likely to come back.
-\end{enumerate}
-
-Let us consider alternative explanations in isolation (i.e. just considering one change or feature at a time with respect to a neoclassical model):
-
-\vspace{.1in}
-\noindent \textbf{Alternative 1: Strong prevalence of income shocks.} This could explain low demand for commitment (4) and (1), but not why forcing helps (3) and (6), nor why there is overconfidence (1), or why they come to pawn in the first place and then default (2) as they would weight in on the high chance of losing the pawn.
-
-\vspace{.1in}
-\noindent \textbf{Alternative 2: High time discounting}.
-This could not explain (1) nor (6) nor (4).
-It could qualitatively explain (3).
-But as we say in section \ref{sec:demand} it cannot quantitatively explain (5) and (3) unless the discount rate is unbelievably high.
-
-\vspace{.1in}
-\noindent \textbf{Alternative 3: Risk aversion.} We already discussed and rejected risk aversion in section \ref{sec:demand}, although using strong assumptions in the process.
-We think this could still play a role and should be investigated in future research.\footnote{For instance by  providing insurance or by measuring risk aversion and using it to predict take up.}
-
-\vspace{.1in}
-\noindent \textbf{Alternative 4: Misunderstanding the contracts.}\footnote{This is a potential criticism of \textit{any} paper offering choice, and one that is non-falsifiable if the critic has free reign to propose how the contracts are perceived in the subject's mind.} We were very aware of the importance of clients understanding the contract in order to infer preferences from choice.
-That is why we made a strong effort for clients to understand the contracts (see subsection \ref{implementation}).
-Note however that while clients making purely random mistakes could explain why 10\% demand commitment ---i.e.
-(4) and (5)--- it would not explain the rest of the findings, nor why the promise-commitment (see below) had more take up that the fee-commitment, or why those with measured present bias and those that want a reminder to pay are more likely to make the ``error'' to demand commitment.\footnote{See Figure \ref{interactions_takeup} and Table \ref{Table_compliance}}
-
-\vspace{.1in}
-\noindent \textbf{Alternative 5: Forgetting to pay.} Frequent payments may act as a reminder to save and recover the pawn.
-This would try to explain (1) by appealing to people forgetting to pay, and (3), (5) and (6) by appealing to frequent payment acting as reminders (i.e.
-there being demand for reminders).
-It would not explain (2) or (4) which are critical in the paper.
-However even for (1) it seems to us a stretch to explain people losing a valuable pawn by forgetting to pay it.
-
-\vspace{.1in}
-\noindent \textbf{Alternative 6 (behavioral): Income shocks overconfidence}.
-One could also easily introduce in the overconfidence in income shocks with $\widehat{\lambda} <\lambda$ in the model of section \ref{model_detail}.
-This would leave default unchanged in both the status quo and the fee forcing contract thus would not explain (3), %since $F_{min}(\beta,\widehat{\lambda})<F_{min}(\beta,\lambda)$.
-but the effect on demand for commitment is uncertain since on the one hand it decreases $\beta_{SQ}$ decreasing demand, but on the other a smaller $F$ is needed to make the IC binding, making commitment less costly.
-$\widehat{\lambda} <\lambda$ alone would not explain the (5) or (6) as demand for commitment would be zero without present bias.
-
-\begin{comment}
-\vspace{.1in}
-\noindent \textbf{Alternative 6: Learning that they are more present biased than they thought.} This is essentially the same as our proposed explanation (i.e.
-not an alternative) with the additional prediction that more people will demand commitment if they just experienced it, an specially appealing one in light of finding (6).
-We are sympathetic to the learning hypothesis and in fact it is \cite{Alcohol}'s main conjecture about why he finds strong demand for commitment while most other studies don't.\footnote{Close to ninety percent of our subjects claim to have pawned before.
-We find that experience does not predict positive take up in our sample correlationally.} To test it we would ideally need to give choice to a group of people that randomly experienced the fee-commitment vs those that did not, and test if the former demand it more.
-Unfortunately we did not do this experiment and we have very limited data to try it: \hl{210 (6\%)} clients were given a choice in a second pawns in our experiment after being randomly assigned to the status quo or fee-forcing contract.
-\end{comment}
-
-\vspace{.1in}
-We do not claim that the model in section \ref{model_detail} is the only possible explanation of our findings, but it is a parsimonious explanation of all of them and a lens for interpretation.
-
-\section{The effect of promises} \label{promises}
-
-One finding of the paper is that a rather small fee of 14 MXN on average changes behavior substantially: on the one hand generates average savings for almost everybody (and in the order of 200-300 pesos on average) when forced, but on the other dissuades take up when clients have choice.
-In this context one would want a commitment device that generates higher take up while at the same time providing incentives for paying fast and recovering the pawn.
-One way to go would be to decrease the already small fee say to 1\% or lower.
-We decided to instead experiment with a non-pecuniary penalty, in the form of a psychological cost of breaking a promise.
-As explained in Section \ref{Experiment} the promise contract involved making a salient promise to repay monthly, and receive a short speech by the appraiser about the importance of keeping her promise of paying monthly.
-
-A substantial literature documents that people don't like to break their promises, and are willing to incur in monetary loses in trying to keep them.
-To our knowledge this result has been replicated several times in laboratory contexts but not in a field setting like ours.
-If breaking a promise is perceived as having a lower cost than paying the 2\% fee and at the same time help as a commitment, we predict that more people will have demand for the promise-commitment contract.
-
-\subsection{The demand for promise-commitment contracts and their effects}
-
-\vspace{.1in}
-\noindent \textbf{Demand}.
-It turns out that the demand for monthly payment contracts with a personal promise to pay monthly ---but no pecuniary penalty for not doing so--- induces higher demand by a factor of three compared with fee-commitment contract: 31\% of clients offered a choice between the status quo contract and the promise-commitment contract chose commitment.
-This means that the pecuniary fee indeed limited demand for commitment.
-In passing this means also that clients are responsive to contract terms and seem to understand the conditions.
-Interestingly however, the set of people who demand the promise-commitment contract are different from those that demanded the fee-commitment one.
-While in both cases the economically vulnerable demand less, in the case of the promise-commitment those that we classify as present biased, those that report that they frequently fall into temptation buying, and those that ask for reminders of payment are \textit{less} likely to demand the promise-commitment contract.
-This suggests that those taking up the promise commitment are not the ones needing the commitment.
-The opposite is weakly true for those who take up the fee-commitment contract (see Figure \ref{interactions_takeup} in the Appendix).
-
-\vspace{.2in}
-\noindent \textbf{Effect of choosing to promise}.
-Figure \ref{fc_pro5}(a) finds that assigning clients to the choice-promise condition has a zero effect on financial cost on average (circles).
-We see no difference even for the endogenous group that \textit{chose} to promise (squares).
-This null effect happens not only on average, but also by percentiles (not shown in Figure).
-There is also no effect on pawn recovery on (first coefficient in Figure \ref{fc_pro5}(b)), even for those that themselves choose to promise.
-And the null effect carries over if we use the definition of recovery in less than 120 days, or for the (endogenous) subgroups that paid a positive amount.
-Finally, there is no effect on repeat pawning (Figure \ref{reincidence}).
-
-\vspace{.2in}
-\noindent \textbf{Effects of forcing to promise}.
-Giving choice of whether to promise or not has the advantage of making promising an active decision by the client.
-In most of the the experimental literature promising is voluntary.
-But it has the disadvantage that we cannot measure the causal effect of promising, since those that promise are a selected sample.
-To evaluate the causal effect of promising, we compare people allocated to the promise-forcing arm (were all clients were forced to make a promise) against those in the status quo contract arm.
-Figure \ref{fc_pro5} (c) and (d) show the results.
-It documents null average treatment effects for both financial cost and recovering the pawn.
-Also there is no effect on repeat pawning.
-
-\vspace{.2in}
-\noindent The evidence presented in this section contrasts sharply with the evidence in laboratory experiments where people choosing to promise has a large effects on behavior, and were people keep their promises.
-While clients are more enthusiastic about the promise-commitment contract than the fee-commitment one in the sense of tripling take-up, the promise contract provides no commitment.
-Results for the promise arms are consistent with \cite{Ted} and \cite{John} who find that people are likely to demand commitment when the commitment is too week to have beneficial effects.
-
-%\vspace{.2in}
-%\noindent \textit{Size of ``mistakes''.} Although promises have very muted effects, there is some heterogeneity (see Figure \ref{heterogeneous_te_3}).
-This opens the space for choice mistakes.
-Figure \ref{choose_wrong} shows that indeed there are some mistakes, but these are smaller that for the fee-choice arm.
-When $z=0$, we calculate that about 60\% of clients in the promise-choice group chose contracts that induced \textit{higher} financial cost.
-In particular \hlgr{97\%} of those that chose the status-quo contract would have been better in the promise-commitment contract, while \hlgr{3\%} of those who chose the promise-commitment contract would have been better in the status-quo one.
-On average they spend \$250 pesos on extra financing cost.
-
-\section{Conclusion} \label{conclusion}
-
-In a pawnshop borrowing context, we studied whether forcing borrowers into frequent payment commitment contracts reduces their borrowing costs, compared to a contract that does not provide commitment to pay monthly.
-Even though we are charging them fees, their borrowing cost are actually reduced by 9.5\%, and they recover their pawn with 25\% higher likelihood.
-Moreover they themselves seem to like this contract, as they are 55\% more likely to come back and pawn again when they get it.
-That is, commitment matters and it seems beneficial.
-Examining treatment heterogeneity we find that almost all clients benefit from the commitment contract.
-
-However when given choice between the commitment and the status quo contract only 10\% choose the former one and thus forgo important benefits.
-A simple model shows that present bias with naivete parsimoniously explains all findings.
-This strongly suggests that it is possible in our context to advance an individual's interests by restricting her freedom ---although we caution that our outcome measure focuses on financing cost and is not comprehensive measure of welfare.
-These results spurred --although we cannot show it caused-- Lender $P$ to offer frequent payment contacts.
-Although Lender $P$ was not as bold as to force these contracts on clients.
-They hoped that clients would eventually learn which contract was better for them.
-
-Needless to say, pawnshop borrowing likely attracts particularly unsophisticated clients (millions of them).
-Choice may fare better in other contexts.
-Choice may also fare better with other contracts besides the fee-commitment one.
-We experimented with a ``softer'' commitment contract in the form of a personal promise, and found that although promise-commitment contracts do indeed elicit more interest they did not cause changes in behavior.
-
-Methodologically, to our knowledge this is the first paper in economics that uses machine learning methods and a combination of choice and forcing arms to estimate personalized counterfactual treatment gains to ask whether treatment take up is positively selected on benefits.
-
-Our results leave open several avenues for research.
-First, it would be useful to tease out the roles played by naivete about self control problems, biased expectations about income shocks, and ambiguity aversion in driving low demand for commitment, using more detailed direct baseline measurements.
-Second, one could ask whether other types of contracts ---for instance those that provide some insurance against shocks---  induce larger demand and better performance than the ones we tried.
-Third, it is likely individuals choosing to borrow from pawnshops are more present biased and naive than similar individuals borrowing from other types of lenders, meriting differential regulation.
-Testing and quantifying this selection across lenders is important.
-Fourth, collecting broader measures of welfare to use as outcomes --e.g.
-subjective well being, consumption, being able to pay for essential services-- would help to make broader claims about welfare that we can make in this paper.
-Finally, one would like to know which interventions could debias consumers, or whether learning alone would do the work.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\newpage
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%BIBLIOGRAPHY
-
-\clearpage
-\bibliographystyle{authordate1}
-%\bibliographystyle{amsalpha}
-%\bibliographystyle{AER}
-
-\bibliography{References}
-
-%\FloatBarrier
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\newpage
-\singlespacing
-
-\section{Tables}
-
-\begin{table}[H]
-\caption{Summary statistics and Balance}
-\label{SS}
-\begin{center}
-\scriptsize{\input{./Tables/SS.tex}}
-\end{center}
- \scriptsize
-This table presents balance tests for the administrative data (Panel A) and survey data (Panel B).
-Each column corresponds to an arm of the experiment: control (status quo contract), no choice with fee, no choice with promise, choice among both contracts where the commitment contract has fee, and choice among both contracts where the commitment contract involves only a promise.
-The last column show the p-value of an F-test of the hypothesis that the mean across arms for that variable is the same across the 5 arms.
-Randomization was done at the branch-day level.
-By design the observation are not exactly equal cross arms as we were more interested in detecting effects in the choice-fee arm and less so in the no-choice-promise.
-Loan amount is the peso amount given to the client; Monday is the fraction of loans given on a Monday; number of pledges is the number of loans given in each arm.
-That it is balanced shows that there was no detectable selection across arms when clients found out what was the contract.
-In Panel B: woman indicated whether the client is female, age of the client is measured in years; has pawned before is a dummy=1 if the client declares to have pawned before (although not necessarily with Lender $P$).
-The subjective probability of recovery was elicited a la Manski, from 0 to 100 what is the probability that you will recoup your pawn.
-High-school is a dummy that indicates if the client has completed high school.
-Finally, the response rate is the percentage of clients in the admin data for whom we have a baseline survey.
-%\textit{Do file: } \texttt{ss.do}
-\end{table}
-
-\newpage
-
-\begin{table}[H]
-\caption{Overconfidence: Take-up and Treatment Effects}
-\label{oc_reg}
-\begin{center}
-\scriptsize{\input{./Tables/oc_reg.tex}}
-\end{center}
- \footnotesize This table shows the parameter estimates of $y_i = \alpha + \beta \: OC_i + Z_i'\gamma + \epsilon_i$, where $OC_i:=\mathbbm{1}(P^s_i-\widehat{P_i(X_i)}>0)$ is an indicator for the subjective probability of recovery being larger that the predicted one.
-In columns 1-4 $y_i$ is a dummy for whether the client $i$ chose to have the commitment contract in the respective choice arm, and in columns 5 and 6 $y_i$ is the heterogeneous treatment effect for financial cost (in pesos) estimated by comparing the fee-forcing vs status quo arms in Section \ref{TE_fee-forcing}.
-Columns 1 and 3 are estimated for the promise-choice arm, while columns 2 and 4 are estimated for the fee-choice arm.
-The low number of observations results from  our use of  covariates for $\widehat{P(x)}$ and in $Z$ in the regression, given that some of them are missing.
-%\textit{Do file: } \texttt{oc.do}
-\end{table}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Figures}
-
-\begin{figure}[H]
-     \caption{Experiment description}
-    \label{exp_description}
-    \begin{center}
-    \begin{subfigure}{.40\textwidth}
-      \caption{Timeline of the experiment}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/timeline_suc_exp_extended.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.40\textwidth}
-    \caption{Experiment arms}
-       \centering
-      \includegraphics[width=\textwidth]{Figuras/exp_arms.PNG}
-    \end{subfigure}
-    \end{center}
-         \scriptsize Panel (a) displays in black arrows the period covered by our administrative data: from August 6th 2012 (30 days before the experiment began) to August 13th 2013.
-The gray lines arrows correspond to the dates of implementation of the experiment.
-We finished the experiment earlier in branches 1 and 2 because we realized that we would have enough sample size with the remaining branches and save on operational costs.
-Panel (b) shows our 5 treatment arms: control (status quo contract), no fee-forcing, promise-forcing, choice among status quo and fee-commitment, and choice among status quo promise-commitment.
-Within each arm it displays the number of observations.
-And  for the choice groups it splits the sample size into those who chose the commitment contract (shaded blue triangle) and those that did not (un-shaded triangle).
-%\textit{Do file: }  \texttt{timeline\_suc\_exp.do}
-\end{figure}
-
-\begin{figure}[H]
-     \caption{Explanatory Material: Promise-Choice Days}
-    \label{ExplanatoryMaterial}
-    \begin{center}
-    \begin{subfigure}{0.8\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/MicaChoiceDonde.png}
-    \end{subfigure}
-    \end{center}
-    \scriptsize
-        This is a (translated) sample information mica shown to clients in choice-promise days.
-The real ones were twice the size of this figure and were laminated.
-Different ones were shown in each treatment arm.
-\end{figure}
-
-\vspace{.2in}
-\begin{figure}[H]
-     \caption{Financial cost}
-    \label{fc_hist}
-    \begin{center}
-    \begin{subfigure}{.45\textwidth}
-      \caption{In pesos MXN}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_fc.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.45\textwidth}
-    \caption{As a fraction of the loan}
-       \centering
-      \includegraphics[width=\textwidth]{Figuras/hist_fc_perc_loan.pdf}
-    \end{subfigure}
-    \end{center}
-         \scriptsize
-         Panel (a) presents a histogram of financial cost for the control group.
-Financial cost is defined as the sum of payments made by a client towards recovering her pawn + the cost of the pawned piece when she ends up losing it.
-In the paper we use different costs of losing the pawn: its value in gold, or the self reported subjective (e.g.
-jewelry may have sentimental value).
-This Figure uses the gold value.
-We plot separately the financial cost for those who lose the pawn (blue) and those that recover it (transparent).
-Panel (b) is analogous but we normalized the financial cost dividing it by the loan size.
-%Given that the loan lasts close to 90 days, bringing payments to present value makes little difference.
-      %\footnotesize{ } \textit{Do file: }  \texttt{hist\_fc.do}
-\end{figure}
-
-\begin{figure}[H]
-    \caption{The effect of the fee-forcing treatment}
-    \label{fc_pro2}
-    \begin{center}
-    \begin{subfigure}{0.42\textwidth}
-        \caption{Financial cost (MXN)}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/fc_te_pro_2.pdf}
-    \end{subfigure}
-        \begin{subfigure}{0.42\textwidth}
-        \caption{Financial cost (quantile reg)}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/fc_quantile_pro_2.pdf}
-    \end{subfigure}
-
-        \bigskip
-
-    \begin{subfigure}{0.42\textwidth}
-        \caption{Financial cost (HTE)}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_2.pdf}
-    \end{subfigure}
-    ~
-    ~
-    \bigskip
-    \begin{subfigure}{0.42\textwidth}
-        \caption{Lost pawn}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/def_te_pro_2.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.42\textwidth}
-    \caption{Losing Pawn}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_2.pdf}
-    \end{subfigure}
-
-    \end{center}
-        \scriptsize
-
-      %\textit{Do file: }  \texttt{fc\_te.do, def\_te.do, fc\_quantilereg.do}
-\end{figure}
-
-\scriptsize {
-\noindent This figure shows the estimated treatment effect of ``forcing'' the frequent payment commitment contract using fees, compared to the status-quo (control).
-In Panel (a) each dot represents the estimated treatment effect for a different definition of financing cost, or for a different sub-population, and its 95\% confidence interval.
-From left to right, the first effect corresponds to using the gold value of the pawned piece in the definition of financial cost and discounting the payments to present value using a 7\% monthly rate; the second uses the subjective value of the pawn; the third is analogous to the second but adds transaction cost (transport+1 day's wage) per visit; the fourth conditions on the population that paid any positive amount towards recovery of their pawn; the fifth conditions on the sub-population of the treatment group that paid a fee and compares these to all the control group.
-Panel (b) plots the effects on different quantiles of the distribution of financial cost (using the first definition): 15th, 25th, 50th, 75th, 85th percentile.
-Panel (c) plots the distribution of the heterogeneous treatment effects on financial cost, estimated using \cite{atheygrf}.
-Panel (d) Measures the effect of treatment on the likelihood of losing their pawn.
-The first coefficient compares all the treatment group vs all the control using 230 days after pawning to define the dependent variable; the second defines it using 120 days.
-The third coefficient from the left conditions on the population that paid any positive amount towards recovery of their pawn (which in theory may be endogenous but empirically we showed not to be affected by treatment).
-Finally, Panel (e) shows the distribution of heterogeneous treatment effects of the probability of losing the pawn.
-% the effect on ``repeat purchase''.
-That is likelihood of doing an additional pawn (in treatment vs control) after having been subjected to treatment for at least 75 days.
-The second coefficient estimates the regression conditional on recovering the pawn \hl{in both treatment and control}, and the rightmost coefficient compares those above the median treatment effect in financial cost savings, \hl{versus all the control group.}
-}
-
-\vspace{3ex}
-
-\vspace{.3in}
-\begin{figure}[H]
-        \caption{Effects on repeat purchasing}
-    \label{reincidence}
-    \begin{center}
-        \centering
-        \includegraphics[width=0.6\textwidth]{re_te.pdf}
-    \end{center}
-     \scriptsize This figure shows the estimated effects on repeat purchasing of the four treatment arms (fee-forcing, choice-fee, fee-promise, choice-promise) compared to the status-quo control group.
-It shows robustness of the effects by focusing on different sub-populations.
-The leftmost coefficient compares all the fee-forcing group against all status quo group.
-The second coefficient conditions on the first pawn not being recovered when the second was pawned.
-The third coefficient conditions on clients who pawned again after having recovered the pawn in the experiment.
-The fourth coefficient uses all clients (in both the fee-forcing and the status-quo arms) who had an estimated heterogeneous treatment effect above the median.
-Conditioning on this set keeps the sample balanced across arms and therefore still allows for a causal interpretation.
-For the choice arm we present three coefficients: coefficients represented by a circle compare all those offered choice to all those in the status quo arm, thus estimating a causal effect.
-Coefficients in triangles and squares represent those that self-select into the fee or promise arms and compare this subset against the whole status quo arm.
-They therefore contain a selection effect together with the treatment effect and cannot be interpreted causally.
-      %\footnotesize{ \textit{Do file: }  \texttt{re\_te.do}
-\end{figure}
-
-\begin{figure}[H]
-    \caption{The effect of choice between fee-commitment and status quo}
-    \label{fc_pro4}
-    \begin{center}
-    \begin{subfigure}{0.45\textwidth}
-        \caption{Financial cost}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/fc_te_pro_4.pdf}
-    \end{subfigure}
-        \begin{subfigure}{0.45\textwidth}
-        \caption{Financial Cost (quantile reg)}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/fc_quantile_pro_4.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.5\textwidth}
-
-        \bigskip
-        \bigskip
-
-        \caption{Lost Pawn}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/def_te_pro_4.pdf}
-    \end{subfigure}
-    \end{center}
-        \scriptsize
-        This figure is analogous to Figure \ref{fc_pro2}.
-It measures the effect of being given \textit{choice} between the frequent payment commitment contract with fees and the status-quo contract, versus being \textit{``forced''} into the status-quo contract (control).
-Again it focuses our two main outcomes: financial cost and an indicator for losing the pawn.
-Circles present the treatment effects.
-The figures also presents differences in these two outcomes for those who chose the frequent payment commitment contract versus the whole control group (squares-NSQ), and also for those who chose the status quo contract versus the whole control group (triangles-SQ).
-Note that these two comparisons are not pure causal effects since people who chose the frequent payment commitment contract are different from those that do not.
-That is: the squares and triangles combine selection and treatment effects.
-Finally, for comparison purposes, the blue diamond displays the effects of forcing them into the frequent payment commitment contract and are just transcribed from Figure \ref{fc_pro2} above.
-      %\textit{Do file: }  \texttt{fc\_te\_choice\_dec.do, def\_te\_choice\_dec.do, fc\_quantilereg\_choice\_dec.do}
-\end{figure}
-
-\begin{figure}[H]
-        \caption{Distribution of Overconfidence}
-    \label{oc_hist}
-    \begin{center}
-        \centering
-        \includegraphics[width=0.55\textwidth]{Figuras/oc_hist.pdf}
-    \end{center}
-    \scriptsize
-     In the baseline survey at the branch, before the client knew the contract of had the pawn appraised, they were asked from 0 to 100, how likely is that they would be able to recover their pawn if pawned.
-We generate a variable we call overconfidence (OC) defined as the reported subjective probability of recovery minus the predicted probability ($P^s_i-\widehat{P_i(X_i)}$).
-We predict $\widehat{P_i(X_i)}$ using LASSO as explained in the text.
-This figure uses all observations for which we have data on $P^s_i$ and $X_i$ from the baseline survey.
-     %\textit{Do file: }  \texttt{oc.do}
-
-\end{figure}
-
-\begin{figure}[H]
-    \caption{Choice of contracts and treatment effects}
-    \label{choose_wrong}
-    \begin{center}
-        \begin{subfigure}{0.45\textwidth}
-        \caption{Chose wrong}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/line_cw_fc_te_cf.pdf}
-
-    \end{subfigure}
-        \begin{subfigure}{0.45\textwidth}
-        \caption{By overconfidence/naivete}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/line_cw_fc_te_cf_OC_fee.pdf}
-
-    \bigskip
-
-    \end{subfigure}
-        \begin{subfigure}{0.45\textwidth}
-        \caption{\% better when forced to fee-commitment}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/line_better_forceall_fc_te_cf.pdf}
-
-    \end{subfigure}
-        \begin{subfigure}{0.45\textwidth}
-        \caption{\footnotesize{Effect of losing pawn vs predicted take-up}}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/takeuppr_def.pdf}
-    \end{subfigure}
-
-    \end{center}
-        \scriptsize
-        In Panel (a) we estimate what the treatment effect of the commitment contract \textit{would have been} for all subjects in the choice arm if they had been forced into the fee-commitment contract.
-To do this we proceed in two steps.
-First, we estimate treatment effects in the forcing arm by comparing the fee-forcing arm against the status quo arm.
-We let these effects be heterogeneous as a function of our $x$'s using \cite{atheygrf}'s methodology of causal forests.
-Second, we extrapolate these treatment effects based on the choice arm using the same $x$'s.
-Once we have personalized counterfactual treatment effects in the choice we calculate what fraction of subjects in the choice arm incurred in financial costs that are  $> z$\% than if they had chosen the opposite contract of what they actually chose, were $z$\% is defined as a fraction of the loan.
-$z$\% is a level of tolerance we can vary and we plot it in the X-axis.
-The left Y-axis measures the fraction of subjects that would have been better by a margin of $z$\% if they changed their choice, and the right Y-axis measures the amount of money ``left on the table''.
-The thinly dotted lines represent 90\% confidence intervals.
-Panel (b) is analogous to Panel (a) except that it does the exercise separately for clients we classified as overconfident ($OC_i:=\mathbbm{1}(P^s_i-\widehat{P_i(X_i)}>0))$ and those we classified as not overconfident.
-Panel (c) simulates what percentage would be better by at least $z$ if we forced everybody of those in the fee-choice arm into the fee-commitment contract.
-Panel (d) asks whether it is the case that people with larger causal savings from the fee-forcing contract would be more likely to select that contract.
-To do this we proceed in two steps as well.
-First we estimate a flexible model of take-up of the fee commitment contract \textit{in the choice arm} using random forests, and from this model obtain a probability $P(x_i)$ of choosing the fee-forcing contract for a client with characteristics $x_i$.
-We extrapolate this model to clients in the fee-forcing arm to estimate what would they have chosen if we had given them choice.
-Figure (d) plots $\widehat{P(x_i)}$ in the X-axis using a binscatter that splits the X-axis in 100 percentile bins.
-The Y-axis plots the heterogeneous treatment effects of the fee forcing contract on the probability of losing the pawns (more negative means then more likely to recover it), averaged for the respective x-axis bin.
-Positive assortative selection would mean a negative relationship: those who benefit more by treatment and lose the pawn less are more likely to choose it.
-Using all bins we estimate a slope of zero in the relationship.
-Using the 80 right most points, we estimate a \textit{positive} relationship.
-        %\textit{Do file: }  \texttt{effect\_contr\_takeup.do, choose\_wrong\_quant\_wrong.do, choose\_wrong\_quant\_wrong\_decomposition.do}
-\end{figure}
-
-\begin{figure}[H]
-    \caption{The effect of promises}
-    \label{fc_pro5}
-    \begin{center}
-
-        \begin{subfigure}{0.45\textwidth}
-        \caption{Financial cost -- Choice}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/fc_te_pro_5.pdf}
-    \end{subfigure}
-        %\begin{subfigure}{0.45\textwidth}
-        %\caption{Quantile regression}
-        %\centering
-        %\includegraphics[width=\textwidth]{Figuras/fc_quantile_pro_5.pdf}
-    %\end{subfigure}
-    \begin{subfigure}{0.45\textwidth}
-        \caption{Losing Pawn -- Choice}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/def_te_pro_5.pdf}
-    \end{subfigure}
-
-    \bigskip
-    \bigskip
-
-        \begin{subfigure}{0.45\textwidth}
-        \caption{Financial cost -- Promise-forcing}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/fc_te_pro_3.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.45\textwidth}
-        \caption{Losing Pawn -- Promise-forcing}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/def_te_pro_3.pdf}
-    \end{subfigure}
-
-    \end{center}
-    \scriptsize
-    Panels (a) and (b) in this figure show the estimated treatment effects of ``forcing'' the frequent payment commitment contract using promises, compared to the status-quo (control) for financial cost (Panel a), and for an indicator of losing the pawn (Panel b).
-Panels (c) and (d) are analogous but focus on the effect of giving choice between frequent payment commitment contract using promises and the status quo contract.
-In Panel (a) each dot represents the estimated treatment effect for a different definition of financing cost, or for a different sub-population, and its 95\% confidence interval.
-From left to right, the first effect corresponds to using the gold value of the pawned piece in the definition of financial cost and discounting the payments to present value using a 7\% monthly rate; the second uses the subjective value of the pawn; the third is analogous to the second but adds transaction cost (transport+1 day's wage) per visit; and the fourth conditions on the population that paid any positive amount towards recovery of their pawn.
-Panel (b) plots the effect of not recovering the pawn: the leftmost coefficients compares all those assigned to the promise-forcing arm vs all those in the status quo contract, where the dependent variable=1 if the client has not recovered the pawn 230 days after pawning.
-The next coefficient defines the dependent variable=1 if the client has not recovered the pawn 120 days after pawning.
-The third coefficient conditions on paying a positive amount, and the fourth conditions on paying at least 30\% of the loan.
-Panels (b) and (c) measure the effect of being given \textit{choice} between the frequent payment commitment contract with promise and the status-quo contract, versus being \textit{``forced''} into the status-quo contract (control).
-Again it focuses our two main outcomes: financial cost and an indicator for losing the pawn.
-Circles present the treatment effects.
-The figures also presents differences in these two outcomes for those who chose the frequent payment commitment contract versus the whole control group (squares-NSQ), and also for those who chose the status quo contract versus the whole control group (triangles-SQ).
-That is: the squares and triangles combine selection and treatment effects.
-      %\footnotesize{ } \textit{Do file: }  \texttt{fc\_te\_choice\_dec.do, def\_te\_choice\_dec.do, fc\_te.do, def\_te.do }
-\end{figure}
-
-%\begin{figure}[H]
-%    \caption{The effect of the promise-forcing treatment}
-%    \label{fc_pro3}
-%    \begin{center}
-%        \begin{subfigure}{0.45\textwidth}
-%        \caption{Quantile regression}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/fc_quantile_pro_3.pdf}
-%    \end{subfigure}
-%    
-%    \end{center}
-%             \footnotesize \textit{Notes: } 
-%      \footnotesize{ } \textit{Do file: }  \texttt{fc\_te.do, def\_te.do, fc\_quantilereg.do}
-%\end{figure}
-
-\newpage
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{center}
+
+\appendix
+\pagenumbering{arabic}
+\renewcommand\thefigure{OA-\arabic{figure}}
+\renewcommand\thetable{OA-\arabic{table}}
+\renewcommand*{\thepage}{OA - \arabic{page}}
+\renewcommand\thesection{Appendix \Alph{section}.}
+\renewcommand\thesubsection{\Alph{section}.\arabic{subsection}}
 
@@
 
+%---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
+
+\newpage
+
+\subsection{New results}
+\begin{figure}[H]
+        \caption{Financial cost for different discount rates}
+    \label{fc_discount_rates}
+    \begin{center}
+        \centering
+        \includegraphics[width=0.55\textwidth]{Figuras/discount_effect.pdf}
+    \end{center}
+     \scriptsize This Figure estimates the treatment effect on financial cost with different discount rates.  
+     %\textit{Do file: }  \texttt{discounted\_noeffect.do}
+\end{figure}
+
+\begin{figure}[H]
+    \caption{Treatment effects pooling all arms}
+    \label{pooled_arms_te}
+    \begin{center}
+    \begin{subfigure}{0.45\textwidth}
+        \caption{Financial Cost}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/te_allarms_fc_admin_disc.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.45\textwidth}
+        \caption{Lost Pawn}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/te_allarms_def_c.pdf}
+    \end{subfigure}
+    \end{center}
+     \scriptsize
+      %\footnotesize{ \textit{Do file: }  \texttt{te\_allarms.do}}
+\end{figure}
+
+\scriptsize {
+\noindent This Figure shows the treatment effects for the main outcomes when pooling all arms in the same regression.
+}
+
+\begin{figure}[H]
+        \caption{Treatment effect decomposition of the Financial Cost }
+    \label{reg_int_pro_2}
+    \begin{center}
+        \centering
+        \includegraphics[width=0.60\textwidth]{Figuras/int_te_pro_2.pdf}
+    \end{center}
+     \scriptsize This Figure is a "close-up" for the estimates found in Figure \ref{fc_pro2} - Panel (a).
+It shows the treatment effects on payed \& incurred interest, the former defined as the actual interest payed, and the latter is the sum of all potential interests (for those pawns that were lost we calculate the interest generated until day 230).
+In the right axis we show the treatment effect on the payed fees.
+Finally, we analyze this effect for the subsamples that recovers or loses the pawn.
+     %\textit{Do file: }  \texttt{reg_\int.do}
+\end{figure}
+
+\begin{figure}[H]
+        \caption{Frequency of renewals}
+    \label{ref_dist}
+    \begin{center}
+        \centering
+        \includegraphics[width=0.60\textwidth]{Figuras/ref_dist.pdf}
+    \end{center}
+     \scriptsize  This Figure shows the occurrence and frequency of renewals.
+It locates in time, respective to the day the loan started, when the renewal occurs for both the first and second renewal.
+Note that the first renewal is concentrated around 100 days, while the second is concentrated around the 200 days, corresponding to the first and second cycle.
+     %\textit{Do file: }  \texttt{ref_\dist.do}
+\end{figure}
+
+\begin{figure}[H]
+        \caption{Probability of recovery by arm}
+    \label{survival_graph}
+    \begin{center}
+        \centering
+        \includegraphics[width=0.60\textwidth]{Figuras/survival_graph_unpledge.pdf}
+    \end{center}
+     \scriptsize  This Figure shows the accumulated percentage of recovery in time by treatment arm. 
+     %\textit{Do file: }  \texttt{survival\_graph.do}
+\end{figure}
+
 %\begin{figure}[H]
@@
         \centering
-        \includegraphics[width=0.9\textwidth]{Figuras/active_pf_suc.pdf}
+        \includegraphics[width=0.80\textwidth]{Figuras/active_pf_suc.pdf}
     \end{center}
@@
 \begin{equation}
-    \mathbbm{1}(\text{Has FP})_{ijt} = \alpha_i + \gamma_t + \beta \mathbbm{1}(\text{Had FP previously})_{ij't'} + \delta X_{ij} + \epsilon_{ijk}
+    \mathbbm{1}(\text{Has FP})_{ijt} = \alpha_i + \gamma_t + \beta \mathbbm{1}(\text{Had FP previously})_{ijt}  + \epsilon_{ijt}
     \label{eqn:IV}
 \end{equation}
-\vspace{.1in}
-
-\noindent where $i,j,t,k$ index client, branch, and month respectively.
-$\mathbbm{1}(\text{Has FP})_{ijt}$ is an indicator for client $i$ pawning in branch $j$ in month $t$ using a FP contract, given that both FP and traditional contracts were available at the branch at the time of pawning, so that there is a choice to be made among these.\footnote{When a FP is not available in branch $j$ in month $t$ the variable takes the value of missing, and is therefore not considered in the regression.
-That is, we only include observations when the client had a choice between FP and traditional contracts.} We include client fixed effect $\alpha_i$ as well as calendar month fixed effects (we have 53 months) $\gamma_t$.
-The variable of interest is denoted by $\mathbbm{1}(\text{Had FP previously})_{ij't'}$, and is a an indicator for the client's previous loan (so long as it happened in the past period from $t'$ to $t$) being FP loan.
-We experimented with the time between the current loan and the immediately prior ($t'$ to $t$) being either 6 weeks or 12 weeks and report both estimates.
-The controls $X_{ij}$ include how assiduous a client is: the number of times she has pawned in the 12 months previous to $t$, as well as a dummy of having made a pawn a Lender $P$ in the period from $t'$ to $t$:   $\mathbbm{1}(\text{Had any loan previously})_{ij't'}$.
+
+\noindent where $i,j,t$ index client, branch, and week respectively.
+$\mathbbm{1}(\text{Has FP})_{ijt}$ is an indicator for client $i$ pawning in branch $j$ in week $t$ using a FP contract, given that both FP and traditional contracts were available at the branch at the time of pawning, so that there is a choice to be made among these.\footnote{When a FP is not available in branch $j$ in week $t$ the variable takes the value of missing, and is therefore not considered in the regression.
+That is, we only include observations when the client had a choice between FP and traditional contracts.} Moreover we restrict the sample to pawns where the immediate previous pawn is already closed at the moment of opening the new one\footnote{We do this to avoid making the conclusion that clients are re-pawning in order to meet their past debt.}.
+We estimate a regression with calendar week fixed effects (we have 212 weeks) $\gamma_t$, and also include client fixed effect $\alpha_i$.
+The variable of interest is denoted by $\mathbbm{1}(\text{Had FP previously})_{ijt}$, and is an indicator for the client's immediate previous loan\footnote{We consider only the immediate previous loan, following a ``Markov's'' assumption, in which only the present state determines the future.} being FP loan.
+% The controls $X_{ij}$ include how assiduous a client is: the number of times she has pawned in the 12 months previous to $t$, as well as a dummy of having made a pawn a Lender $P$ in the period from $t'$ to $t$:   $\mathbbm{1}(\text{Had any loan previously})_{ij't'}$.
 Note that the only difference between this last control variable and our main explanatory variable is that the former does not specify which type of contract this previous loan had.
@@
 
-However, even with client fixed effects, idiosyncratic unobserved shocks across time may induce spurious correlation between choosing a FP last month and choosing FP today.
-The variable $\mathbbm{1}(\text{Had FP previously})_{ij't'}$ is therefore still potentially endogenous.
-To deal with this we instrument $\mathbbm{1}(\text{Had FP previously})_{ij't'}$ with the \textit{availability} of the contract in branch $j'$ at past week $t'$ when the client previously went to pawn the immediately prior pawn, $\mathbbm{1}(\text{FP Avail})_{ij't'}$.
+However, even with client fixed effects, idiosyncratic unobserved shocks across time may induce spurious correlation between choosing a FP last week and choosing FP today.
+The variable $\mathbbm{1}(\text{Had FP previously})_{ijt}$ is therefore still potentially endogenous.
+To deal with this we instrument $\mathbbm{1}(\text{Had FP previously})_{ijt}$ with the \textit{availability} of the contract in branch $j$  when the client previously went to pawn the immediately prior pawn with respect to $t$, $\mathbbm{1}(\text{FP Avail})_{ijt}$.
 This is basically using a supply shifter to identify demand.
 We showed above that availability of FP contracts has close to a zero correlation to a battery of observables.
-The IV strategy assumes that availability of the FP contract in a given week in a given is uncorrelated with $\epsilon_{ijk}$ --- i.e.
-that after conditioning on thousands of client, branch and month fixed effects and the client having pawned recently, there is no omitted variable driving both: the branch having FP contracts on, and the client subsequent pawn using a FP contract.
-Note that including branch fixed effects means that identification comes from a given branch sometimes having the FP and some times not.
+The IV strategy assumes that availability of the FP contract in a given week in a given is uncorrelated with $\epsilon_{ijt}$ --- i.e.
+that after conditioning on thousands of client, branch and week fixed effects and the client having pawned recently, there is no omitted variable driving both: the branch having FP contracts on, and the client subsequent pawn using a FP contract.
+Note that including branch fixed effects means that identification comes from a given branch sometimes having the FP and sometimes not.
 \\
 
-The exclusion restriction for an instrument is untestable, but note that we are comparing clients that go to the same branch, who have the same pawning frequency, but where one of them arrived to the branch to pawn on a week where the FP contract was available and the other arrived on a week where the same branch had no FP contract available.\footnote{We also tried specifications restricting the sample to 4 weeks adjacent to the FP contract becoming available or becoming unavailable in a branch and obtain similar results.
-This strategy is close in spirit to a regression discontinuity or event-study design, comparing clients that go to the same branch with the difference that one went there 2 weeks before the FP contract becoming available.} The exclusion restriction could be violated for example if the branch manager makes FP available as a function of clients that will come in that week and therefore reaches a certain type of client that is more likely in-and-of themselves to prefer FP contracts now and in the future.
+The exclusion restriction for an instrument is untestable, but note that we are comparing clients that go to the same branch, who have the same pawning frequency, but where one of them arrived to the branch to pawn on a week where the FP contract was available and the other arrived on a week where the same branch had no FP contract available.%\footnote{We also tried specifications restricting the sample to 4-12 weeks adjacent to the FP contract becoming available or becoming unavailable in a branch and obtain similar results.
+This strategy is close in spirit to a regression discontinuity or event-study design, comparing clients that go to the same branch with the difference that one went there 2 weeks before the FP contract becoming available.}
+The exclusion restriction could be violated for example if the branch manager makes FP available as a function of clients that will come in that week and therefore reaches a certain type of client that is more likely in-and-of themselves to prefer FP contracts now and in the future.
 We find this unlikely.
-It is hard to predict who will come on a given week and if they are more likely to like the PF contract: Table \ref{instrument_random} strongly suggests that the branch manager is not turning the FP contract on and off as result of which clients are coming to the branch or how the branch is doing.
+It is hard to predict who will come on a given week and if they are more likely to like the FP contract: Table \ref{instrument_random} strongly suggests that the branch manager is not turning the FP contract on and off as result of which clients are coming to the branch or how the branch is doing.
 Having said this, we acknowledge that the exclusion restriction could be violated even in this very tightly controlled specification.\\
@@
 Table \ref{iv_pf} shows the first and the second stage regressions for equation \ref{eqn:IV}.
-All columns have client, branch, and calendar month fixed effects as well as the controls explained above.
-Columns 1 and 3 show strong first stages (t-stats above 50).
+All columns have branch, and calendar week fixed effects, and standard errors are clustered by client.
+Columns 1 and 4 show strong first stages (t-stats above 50).
 The availability and unavailability of the FP contract has an incidence on its use.
-Under our identification assumptions, Columns 2 and 4 show strong causal effects: having  been induced by the instrument to have a FP contract in the previous loan causes the client to a FP for her subsequent pawn by 50 percentage points (column 4).
-The difference between the first two and last two columns is the time period considered.
-Columns 1 and 2 define $\mathbbm{1}(\text{Had FP previously})_{ij't'}$ as having it in the previous 6 weeks, while columns 3 and 4 define it using the previous 12 weeks.
+Under our identification assumptions, Columns 2-3 (and 5-6) show strong causal effects: having  been induced by the instrument to have a FP contract in the previous loan causes the client to a FP for her subsequent pawn by 50 percentage points (column 2).
+The difference between columns 2 and 3 (and 4-5) is the sub-sample considered: in the first one we only condition the immediate previous pawn to be closed at the time of opening a new one, the second one not only considers previous pawns being closed, but having at least one week closed.
 
@@
 They regress a dummy for the client choosing a frequent payment contract (when both the traditional one and the FP are available) on whether the previous loan was under a FP contract.
-All columns have client, branch, and calendar month fixed effects.
-All of them control for the number of times the client has pawned in the 12 months previous to the current pawn, as well as a dummy for the having pawned in the period $t'$ to $t$.
-The main regressor of interest is having had a FP loan in the past from $t'$ to $t$  which measures experiencing a FP contract recently.
-Column 1 reports the result of first stage where the supply side instrument is an indicator for the branch having had a FP available when the client showed to pawn the previous pawn.
-Column 2 presents the two-stage least square estimate.
-Columns 3 and 4 are analogous, but instead of looking clients who pawned in the 6 weeks previous, it looks at those that had pawned in the previous 12 months.
+All columns have branch, and calendar month fixed effects, and the standard errors are clustered by client.
+The main regressor of interest is having had a FP loan in the immediate past of $t$ which measures experiencing a FP contract.
+Columns 1 and 4 report the result of first stage where the supply side instrument is an indicator for the branch having had a FP available when the client showed to pawn the previous pawn.
+Column 2 \& 5 presents the two-stage least square estimate.
+Columns 3 \& 6 are analogous, but instead of looking clients whose previous pawn is already closed, it looks at those whose previous pawn has at least one week of being closed.
 We do not report the exact number of observations to keep Lender $P$ identity confidential and instead give a lower bound.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% APPENDIX C
+
+\newpage
+\section{ A simple model}
+\label{appendix_c}
+\vspace{.2in}
+\normalsize
+\linespread{1.25}
+
+We use the model of \cite{John} and refer the reader to that paper for more detail, justification of assumptions and some of the proofs.
+The model has three periods and linear utility.\footnote{This does not map perfectly to our 3 period contract, but it is enough to generate the results we need.
+We also assume that the amount of the loan is used up to pay for the emergency.
+\cite{John_theory} provides a more general treatment.} Period $t=0$ is a planning period where the client is either allocated to the status quo, the fee-forcing contract, or a choice between the two.
+Period $t=1$ is the saving-for-the-monthly-payment  period, and $t=2$ in the pawn recovery (loan payment) period.
+In period 1 the client receives her income $y_1=1$, or gets zero with probability $\lambda$.
+She can consume ($c_1$) or save ($s_1$) part that income.
+In period 2 the client gets her savings from period 1, and again receives income of either $y_2=1$, or zero with independent probability $\lambda$.
+In this last period, she decides whether to use income and savings for consumption $c_2$ and/or for paying back the loan of size $p \in(1,2)$ to recover the pawned piece valued at $b>p$.
+In this simple set up we model the fee-commitment contract as a contract that imposes a fee of size $F$ if the client fails at $t=1$ to save $s_1=p-1$ pesos, which is what is needed to pay the loan back when there are no shocks.
+In period $t=0$ she evaluates her welfare as $E[c_1+c_2]$, were for simplicity we have set the time discount to one.
+We also assume the interest rate is one.
+We introduce present biased preferences by assuming the following utility function $U_t=c_t+\beta \: \sum_{k=t+1}^{2} E[c_k]$, with $\beta<1$ indicating present bias.
+A naive client perceives she is not so present biased and instead of $\beta$ uses $\hat{\beta} \in (\beta,1]$.
+
+Note that under these assumptions it is efficient at $t=0$ to recover the loan since $b>p$ and since there is no discounting at $t=0$.
+Because $b>1$, paying back the loan requires that there is no negative shock in any period and that $s_1>0$.
+Because $\beta<1$ at $t=1$ the client will not send savings in excess of what is needed to recover the loan: $s_1=p-1$.
+This parsimonious model implies the following results:
+
+\vspace{.2in}
+\noindent \textbf{Result 1: Present biased clients default more.} Under the status-quo contract, absent shock realizations, present biased clients (sophisticated or naive) with $\beta<\beta_{SQ}<1$ will lose their pawn, while clients with no present bias will not.\footnote{$\beta_{SQ}=\frac{p-1}{\lambda(p-1)+(1-\lambda)(b-1)}$.
+See Proposition 1 in \cite{John}.}
+
+\vspace{.1in}
+\noindent \textbf{Result 2: Forcing present-biased clients into the fee-commitment contract reduces default.} Imposing a fee $F>0$ for late payments weakly decreases default (for present biased clients only).
+It strictly decreases default if $F>F_{min}(\beta):=(p-1)-\beta[\lambda(p-1)+(1-\lambda)(b-1)]$.
+The larger the present bias the larger the $F$ required to induce pawn recovery.\footnote{$F_{min}(\beta)$ is derived from the incentive compatibility constraint needed to generate savings at $t=1$ to recover the pawn can be written as $1-(p-1)+\beta[\lambda(p-1)+(1-\lambda)(b-1)] \geq 1-F+\beta(1-\lambda)$.}
+
+\vspace{.1in}
+\noindent \textbf{Result 3: Demand for commitment.} Given $F>0$, (a) Neoclassical clients will never demand commitment.
+(b) Present-biased sophisticated clients will prefer the fee-forcing contract over the status quo contract $\iff$  $\lambda \: F<(1-\lambda)^2(b-p)$ and $F>F_{min}(\beta)$, that is $\iff$  $\beta \in [\beta_{min},\beta_{SQ}]$.\footnote{$\beta_{SQ}$ was determined in Result 1.
+$\beta_{min}$ is such that $F=F_{min}(\beta_{min})$.} (c) Analogously, naive clients will demand commitment $\iff$ $\hat{\beta} \in [\widehat{\beta_{min}},\beta_{SQ}]$, where $\widehat{\beta_{min}}<\beta_{min}$.
+So strongly naive clients will on the one hand demand more commitment than sophisticated clients since they believe (incorrectly) that a smaller fee will motivate them to pay.
+On the other hand they may demand less commitment since they think they can save and pay on their own.
+Whether they demand more or less than sophisticated clients depends on the empirical distribution of $\beta$ and $\hat{\beta}$.
+
+\vspace{.1in}
+\noindent \textbf{Result 4: Overconfidence.} Only naive clients will be overconfident about the probability of recovery.
+This will be true whether they have the status quo or the fee-forcing contract.
+Overconfidence is increasing in $\hat{\beta}$.
+
+\vspace{.1in}
+\noindent \textbf{Result 5: Welfare.} (a) Neoclassical consumers' welfare strictly decreases when we force clients into the fee-commitment contract instead of the status quo contract because of the risk of them not being able to pay for the installment, and does not change when we offer a choice between them.
+(b) The welfare of sophisticated present biased consumers weakly increases when we give them choice, and it strictly increases  $\iff$  $\beta \in [\beta_{min},\beta_{SQ}]$, that is when they would choose the fee-commitment contract themselves.
+Forcing them into the fee-commitment contract increases welfare $\iff$  $\beta \in [\beta_{min},\beta_{SQ}]$, otherwise it strictly decreases it.
+So choice is better than forcing for sophisticates.
+(c) Forcing can be welfare improving for the naive.
+Indeed if $\hat{\beta}>\beta_{SQ}>\beta$ then forcing the fee-commitment contract increases welfare, and if $\hat{\beta} \in (\widehat{\beta_{min}},\beta_{min})$ then forcing the status quo contract increases welfare.\footnote{This result is different from that in \cite{John}.
+Her context has individuals choosing the size of the fee.
+In that context naive clients will \textit{always} chose the wrong fee size and default later, therefore choice is always decreasing for the naive.
+In our context $F$ is fixed at 2\% of the balance due, and this implies that choice could be welfare improving for some naifs.} We want to highlight that only under certain parameters will forcing installment payments improve welfare, and that welfare will likely decrease for those with no present bias and the sophisticated present biased consumers.
+
+\vspace{.1in}
+\noindent \textbf{Result 6: Welfare and ex-post observed behavior.} If for a naive client $i$ the fee-forcing contract causes higher pawn recovery, then we know the fee $F$ made her IC constraint binding, and therefore that $\hat{\beta}_i>\widehat{\beta}_{min}$.
+If in addition if it was the case that $\beta_i<\beta_{SQ}$.
+%\footnote{\hl{Isaac, aqui tengo dos pregutas: (1) si es $\beta$ y no $\hat{\beta}$ verdad?
+(2) Para que una persona naive empenie en el status quo tiene que ser que cree que va a recuperar no?
+Es decir tiene que ser $\hat{\beta}>\beta_{SQ}$ correcto?}}
+then the fee-forcing contract would have increased welfare for the naive.
+That is, our finding that the fee-forcing contract increases pawn recovery is a sign of higher welfare (although not a sufficient condition).\footnote{It is not sufficient since ex-ante the commitment $F$ may have been too expensive given the income shocks, i.e.
+if $\lambda \: F>(1-\lambda)^2(b-p)$.}
+
+\clearpage
+\bibliographystyle{authordate1}
+%\bibliographystyle{amsalpha}
+%\bibliographystyle{AER}
+
+\bibliography{References}
+
 \end{document}

### 2021-03-09 main.tex
review of the paper, major revisions
Former-commit-id: f0ba952ceba4dcebac4f60c80e3534421325c165

@@
 
-In the context of pawnbroker lending, we show that forcing people into commitment contracts with financial penalties for not paying on time \textit{decreases} their (fee-including) financial cost by 9.5\%, increases the likelihood of recovering their pawn by 25\%, and increases the likelihood of repeat business by 55\%.
-Using machine learning methods for estimating heterogeneous treatment effects, we find that more than 90\% clients would reduce their financing cost with the commitment contract, however only 10\% choose it.
+In the context of pawnbroker lending, we show that forcing people into commitment contracts with financial penalties for not paying on time \textit{decreases} their (fee-including) financial cost by 9.4\%, increases the likelihood of recovering their pawn by 26\%, and increases the likelihood of repeat business by almost 100\%.
+Using machine learning methods for estimating heterogeneous treatment effects, we find that more than \hl{90}\% clients would reduce their financing cost with the commitment contract, however only 10\% choose it.
 Relying on personal promises instead of fees as commitment triples take-up but has no effects on outcomes.
@@
 Forcing clients into frequent payment commitment contracts causes them on average to save on financing cost and to recover their pawn more.
-The effects are large: financing cost decreases by 9.5\% on average (from \$3161 to \$2857 MXN), while the likelihood of recovering their pawn increases by 25\% (from 43\% to 54\%).
+The effects are large: financing cost decreases by 9.4\% on average (from \$3157 to \$2860 MXN), while the likelihood of recovering their pawn increases by 26\% (from 43\% to 55\%).
 Results are robust qualitatively to including transport costs of going to the branch plus losing a day's wage for each visit.
@@
 The fee-commitment contract induces people who would otherwise pay something towards recovery, to pay more and faster and thus recover their pawn more at a cheaper financial cost.
-Finally, borrowers assigned to the forced fee-commitment contract are 5 percentage points (55\% of the mean) more likely than the control group to ask for another loan in the future, suggesting that they liked the commitment contract after experiencing it.
+Finally, borrowers assigned to the forced fee-commitment contract are 5 percentage points (100\% of the mean) more likely than the control group to ask for another loan in the future, suggesting that they liked the commitment contract after experiencing it.
 
@@
 Combining the forcing and the choice arms ---a unique feature of our experiment--- allows us to estimate the counterfactuals to answer the question of how much money is left on the table by giving choice to clients.
-We calculate that about 80\% of clients in the fee-choice group chose contracts that induced \textit{higher} financial cost.
-On average they spend an extra \$238 MXN, close to 11\% of the average loan value.
-In particular 92\% of those that chose the status-quo contract would have been better in the fee-commitment contract, while only 8\% of those who chose the fee-commitment contract would have been better in the status-quo one.
+We calculate that about \hl{80}\% of clients in the fee-choice group chose contracts that induced \textit{higher} financial cost.
+On average they spend an extra \$\hl{238} MXN, close to \hl{11}\% of the average loan value.
+In particular \hl{92}\% of those that chose the status-quo contract would have been better in the fee-commitment contract, while only \hl{8}\% of those who chose the fee-commitment contract would have been better in the status-quo one.
 This suggests that forcing clients into commitment contacts (i.e.
@@
 We document two main results in the promise arms.
-First, demand for the commitment-promise contract is three times larger than for the commitment fee contract, with 31\% take-up.
+First, demand for the commitment-promise contract is three times larger than for the commitment fee contract, with \hl{31}\% take-up.
 This difference between both choice arms suggests that clients are indeed understanding and taking into account the contractual parameters in their choice, and that the fee commitment was probably too strong from their point of view.
@@
 
-We study pawnshop borroing by partnering with Lender $P$, one of the largest pawn shops in Mexico, with more than one hundred branches spanning multiple States in Mexico.
+We study pawnshop borrowing by partnering with Lender $P$, one of the largest pawn shops in Mexico, with more than one hundred branches spanning multiple States in Mexico.
 Our context is one with high borrower default: 60\% of clients lose their pawn in a time span of 230 days from the date of pawning.
@@
 One potential explanation for high default is that clients are really just selling their gold piece.
-This is unlikely for several reasons: (a) the reported subjective value of the pawn is larger than the loan size for 86\% of them, (b) among those that lose their pawn 58\% paid a positive amount towards its recovery and on average paid 34\% of the value of their loan (see Figure \ref{proxy_naive} in Appendix) --- this can only be rationalized if they expected to recover their pawn, (c) clients can easily sell the gold and obtain a higher amount of instant cash at gold buying stores located close to almost all our pawnshop branches (see Figure \ref{GoldBuyers}).
+This is unlikely for several reasons: (a) the reported subjective value of the pawn is larger than the loan size for 86\% of them, (b) among those that lose their pawn 48\% paid a positive amount towards its recovery and on average paid 42\% of the value of their loan (see Figure \ref{proxy_naive} in Appendix) --- this can only be rationalized if they expected to recover their pawn, (c) clients can easily sell the gold and obtain a higher amount of instant cash at gold buying stores located close to almost all our pawnshop branches (see Figure \ref{GoldBuyers}).
 %(d) there is a lot of engagement with the lender after pawning even for those who lost their pawn.
@@
 If the client paid the principal plus the accumulated interest in less than 105 days, then she received back her pawn, otherwise the pawnbroker kept the piece and any payments made.
-Before the contract expired, the client had the right to renew it (using the same collateral) for another 3 months by going to the pawnshop paying the accumulated interest and signing a new contract with exactly the same terms as the original one.
+Before the contract expired, the client had the right to renew it\footnote{Only 26\% renews twice or more.
+} (using the same collateral) for another 3 months by going to the pawnshop paying the accumulated interest and signing a new contract with exactly the same terms as the original one.
 %The pawnshop therefore makes money in three ways: by reselling the jewelry left as collateral on defaulted loans, by charging interest on non defaulted loans, and by keeping the payments made on defaulted loans.
@@
 The black arrows represent the dates for which we have administrative data (before and after the experiment) for each branch, while the light gray segments represent the duration of the experiment.
-The experiment comprises 13,444 pawns, and our administrative data cover a total of 26,179 pawns.
+The experiment comprises 13,446 pawns, and our administrative data cover a total of 23,974 pawns.
 
@@
 It was short to avoid discouraging the potential clients from pawning, but at the same time it aimed to measure the following: demographics, proxies for income/wealth, education, self-control problems/present-biased preferences, experience pawning, if family or friends commonly asked for money, how time consuming and costly it was to come to the branch, the subjective probability of recovering the piece that they intended to pawn, the subjective value of their piece in money terms (how much money they would sell it for), among others.
-We surveyed 10,431 clients (some refused).
+We surveyed 10,437 clients (some refused).
 %\footnote{We also surveyed clients before and after the experiment, so our survey covers a larger sample that we are not using in this paper.}.
@@
 The average loan size is \$2197 MXN (\$105 USD).
-The average number of pawns per day per branch is 33.
-Only 40\% of clients recover their pawn within 230 days.
-Even those that recover their pawn tend to pay it back at the last moment, with only 17\% paying before the 90th day.
+The average number of pawns per day per branch is 34.
+Only 42\% of clients recover their pawn within 230 days.
+Even those that recover their pawn tend to pay it back at the last moment, with only 40\% paying before the 90th day.
 
@@
 Default is defined as losing the pawn.
-We define financial cost as the discounted sum of payments toward the loan plus the appraised value of the pawn, and subtract the appraised value of the pawn when it is recovered: $Financial \; Cost_i = \sum_t \frac{P_{it}}{(1+r)^t} + Pawn \: Value_i - \frac{\text{I}(Recovered \: Pawn_i) \times Pawn \: Value_i}{(1+r)^T}$, with $t$ indexing days, $T$ is the day when the pawn is recovered, I($\cdot$) an indicator function for recovering the pawn, $r$ is a daily interest rate equivalent to a 7\% monthly interest rate.\footnote{We experimented with different interest rates with similar results.
+Let $P^c$, $P^f$, and $P^i$ the payments to principal, fees, and interest respectively.
+We define financial cost as the discounted sum of payments toward the loan, plus the discounted payment of fees, plus payments to interest, plus the appraised value of the pawn, and subtract the appraised value of the pawn when it is recovered:
+\begin{align*}
+    Financial \; Cost_i =& \underbrace{\sum_t \frac{P^c_{it}}{(1+r)^t}}_{\text{Discounted payments to capital}} + \underbrace{\sum_t \frac{P^f_{it}}{(1+r)^t}}_{\text{Payed fees}}  +\underbrace{\sum_t \frac{P^i_{it}}{(1+r)^t}}_{\text{Payed interests}} \\
+    &\quad\qquad + \underbrace{Pawn \: Value_i - \frac{\text{I}(Recovered \: Pawn_i) \times Pawn \: Value_i}{(1+r)^T}}_{\text{Cost of losing pawn}}
+\end{align*}
+, with $t$ indexing days, $T$ is the day when the pawn is recovered, I($\cdot$) an indicator function for recovering the pawn, $r$ is a daily interest rate equivalent to a 7\% monthly interest rate.\footnote{We experimented with different interest rates with similar results.
 See section \ref{neoclasical}.
@@
 %\hl{The difference between panel (a) and (b) arises since clients who lose their pawn tend to be those that pledge cheaper pieces.}
-We calculate an APR of 218\% on average for the control group.\footnote{The Annual Percentage Rate (for pawn $j$) is calculated as the internal rate of return $i$ such that $\sum_t \frac{P_{jt}}{(1+i)^t} + \frac{\text{I}(Default \: Pawn_j) \times Pawn \: Value_j}{(1+i)^T} - Pawn \: Value_j = 0$, where $T$ is the date the pawn was lost.}
+We calculate an APR of 218\% on average for the control group.\footnote{The Annual Percentage Rate (for pawn $j$) is calculated as the internal rate of return $i$ such that $\sum_t \frac{P_{jt}}{(1+i)^t} + \frac{\text{I}(Default \: Pawn_j) \times Pawn \: Value_j}{(1+i)^T} - Pawn \: Value_j = 0$, where $T$ is the date the pawn was lost, and $P_{jt} =P_{jt}^c+P_{jt}^f+P_{jt}^i $ is the sum of all payments.}
 
@@
 It also limits potential manipulation by appraisers, who in the presence of individual level randomization could potentially pick their preferred costumers from the line or tell them to wait until their desired contract shows up on the screen.
-Intra-branch day correlation on the probability of default (ICC) is small, at 0.08, so we don't lose much power vis-a-vis individual level randomization.
+Intra-branch day correlation on the probability of default (ICC) is small, at \hl{0.08}, so we don't lose much power vis-a-vis individual level randomization.
 
@@
 First, we cannot reject that the number of pawns per branch-day is the same across arms (Panel A).
-Panel C shows that about 97\% of people who answered our baseline survey also pawned, and that this ratio is balanced across arms.
+Panel C shows that about 89\% of people who answered our baseline survey also pawned, and that this ratio is balanced across arms.
 Second, not only are the number and shares of pawns the same across arms, but also the characteristics of clients and their pawned pieces are statistically the same across arms.
@@
 To this end we estimated the regression\footnote{We cluster the standard errors by branch.} $Pawns \: per \: day_{jt} = \alpha_j + \gamma f(t) + \beta_b \mathbbm{1}(t \in MB)_{t} +\beta_a \mathbbm{1}(t \in MA)_{t}$, where $\alpha_j$ are branch fixed effects, $f(t)$ is a third degree polynomial in time, $\beta_b$ measures a level effect in the number of pawns per branch a month before the experiment started, and $\beta_a$ a month after.
-We estimate no difference in the number of pawns, showing that people are not leaving the branch without pawning at larger rates during the experiment ($\beta_a=-0.60$, $\beta_b=1.1$, with p-values 0.83 and 0.16, respectively).
+We estimate no difference in the number of pawns, showing that people are not leaving the branch without pawning at larger rates during the experiment ($\beta_a=1.32$, $\beta_b=-0.65$, with p-values 0.11 and 0.83, respectively).
 
@@
 The second coefficient uses the subjective value of the pawn instead.
-In both cases we find that being assigned to the fee-forcing commitment contract causes a large reduction in the financing cost the client incurred, of 9.5\% (\$304) under the first definition and 13.3\% (\$478) under the second one.
+In both cases we find that being assigned to the fee-forcing commitment contract causes a large reduction in the financing cost the client incurred, of 9.4\% (\$297) under the first definition and 13.2\% (\$472) under the second one.
 That is, we find that \textit{charging} clients a late payment decreases total \textit{fee-inclusive} financing cost.
@@
 Figure \ref{fc_pro2}(c) plots the distribution of those treatment effects using this machine learning methodology.
-It shows that more than 90\% of clients experienced financial cost savings in the fee-forcing group compared to the status-quo group.
+It shows that more than 70\% of clients experienced financial cost savings in the fee-forcing group compared to the status-quo group.
 Figure \ref{HTE_fee_forcing} in the Appendix displays that the causal cost savings are larger for the more economically vulnerable, %that report at baseline that they have problems paying for services like water, electricity and rent,
@@
 \noindent \textbf{Pawn Recovery.} Figure \ref{fc_pro2}(d) plots estimated treatment effects of the fee-forcing commitment contract with the dependent variable being an indicator of losing the pawn in less than 230 days.
-The leftmost coefficient shows that the fee-forcing commitment contract increases the likelihood of recovering the pawn by 11 percentage points (25\% of mean recovery).
+The leftmost coefficient shows that the fee-forcing commitment contract increases the likelihood of recovering the pawn by 11 percentage points (26\% of mean recovery).
 This result stands in contrast with \cite{Pande} who find no effect of payment frequency on default in a group lending microfinance context.
-Figure \ref{fc_pro2}(e) shows the distribution of heterogeneous treatment effects for losing the pawn: \textit{everybody's} likelihood of losing the pawn decreases.
+Figure \ref{fc_pro2}(e) shows the distribution of heterogeneous treatment effects for losing the pawn: The likelihood of losing the pawn decreases for 82\% of the population.
 %Figure \ref{HTE_fee_forcing}(b) in the Appendix shows that those we classify as present biased, those that requested to be sent a reminder to pay, and those who have more problems paying for basic services experienced the largest increases on pawn recovery.
@@
 We define a client as a repeat costumer if, after experiencing at least 75 days of the respective treatment arm, she came back and pawned a \textit{different} piece.\footnote{Results are robust to using number of days experiencing the contract larger than 75.
-We know it is a different piece from it having a different weight/value.}  The leftmost coefficient shows that the causal effect of the fee-forcing contract on repeat pawning is an increase of 5 percentage points in the probability of being a repeat customer, this is 55\% increase on a mean re-incidence with respect to those that got the status-quo contract.
+We know it is a different piece from it having a different weight/value.}  The leftmost coefficient shows that the causal effect of the fee-forcing contract on repeat pawning is an increase of 5 percentage points in the probability of being a repeat customer, this is 100\% increase on a mean re-incidence with respect to those that got the status-quo contract.
 This effect is not explained by clients recovering their first pawn with higher probability in the fee-forcing contract and re-pawning this same one since we make sure it is another piece (only 16\% recover their piece in the fist 75 days in the fee forcing contract).
@@
 Recall that in the control group the client's subjective probability of recovery is on average 93\%, while actual recovery is just 44\%.
-A further piece of evidence consistent with underestimating negative income shocks and with present bias with partial naivete is that a large number of people (31\%) in the control group pay a positive amount toward pawn recovery but end up losing their pawn anyway.
+A further piece of evidence consistent with underestimating negative income shocks and with present bias with partial naivete is that a large number of people (25\%) in the control group pay a positive amount toward pawn recovery but end up losing their pawn anyway.
 
@@
 Theory predicts that the more overconfident (naive) may be at the same time those that benefit more from commitment.
-Extrapolating individual treatment effects of the fee-forcing contract vs the status quo one to the choice arm (see below for more detail), and using them as a dependent variable we find that overconfident borrowers benefit \textit{more} from the commitment contract, with 24.8\% (=\$30/\$121) more savings (columns 5 and 6).
+Extrapolating individual treatment effects of the fee-forcing contract vs the status quo one to the choice arm (see below for more detail), and using them as a dependent variable we find that overconfident borrowers benefit \textit{more} from the commitment contract, with \hl{24.8}\% (=\$\hl{30}/\$\hl{121}) more savings (columns 5 and 6).
 Thus while we predict the overconfident benefit more from commitment, they demand less of it.
@@
 \noindent \textbf{High time discounting.} We mentioned above that clients in the status quo contract tend to wait until the last moment to pay to recover their pawns.
-Even among those that recover their pawn, only 42\% pay before the 90$^{th}$ day.
+Even among those that recover their pawn, only 40\% pay before the 90$^{th}$ day.
 Table \ref{mechanisms} shows that clients assigned to the fee-commitment contract front load their payments, starting their first payment earlier and finishing paying earlier too.
@@
 That is, we introduce a threshold that we vary from 0\% to 15\% of the value of the loan.
-Second, we take into account uncertainty in estimation of treatment effects and report results using the extremes of the 90\% confidence interval bounds for $\widehat{TE}^{fee}_{i}$.
+\hl{Second, we take into account uncertainty in estimation of treatment effects and report results using the extremes of the 95\% confidence interval bounds for $\widehat{TE}^{fee}_{i}$.}
 
@@
 On the X-axis it varies the threshold $z$.
-When $z=0$, we calculate that about 80\% of clients in the fee-choice group chose contracts that induced \textit{higher} financial cost.
+When $z=0$, we calculate that about 75\% of clients in the fee-choice group chose contracts that induced \textit{higher} financial cost.
 %(90\% confidence interval [45,94]).
-Most mistakes are failures to choose the fee-commitment contract (92\%), while only 8\% of those who chose the fee-commitment contract would have been better in the status-quo one.
-The average mistake in pesos is \$238.
+Most mistakes are failures to choose the fee-commitment contract (\hl{85}\%), while only \hl{15}\% of those who chose the fee-commitment contract would have been better in the status-quo one.
+The average mistake in pesos is \$250.
 %(90\% confidence interval [140,390]).
 Figure \ref{choose_wrong}(b) plots the same curve, but separately for overconfident and non-overconfident clients, using the definition of overconfidence in Section \ref{behavioral}.
-It shows that there are about 11 percentage points more mistakes in the overconfident population (when $z=0$), an important difference.
+\hl{It shows that there are about 11 percentage points more mistakes in the overconfident population (when $z=0$), an important difference.}
 
@@
 Figure \ref{choose_wrong}(c) calculates what fraction of clients would be made better off if we forced them into the fee-commitment contract.
-We find that 92\% would be better off (using $z=0$), and they would on average have savings of 232MXN.
+We find that 85\% would be better off (using $z=0$), and they would on average have savings of 250MXN.
 This conclusion is in line with a recent paper by \cite{John}.
@@
 Forcing them into the fee-commitment contract increases welfare only if they themselves would chose it.
-(c) Forcing can be welfare improving for the naive under some parameter values (see Appendix).
+(c) Forcing can be welfare improving for the naive under some parameter values (see Appendix \ref{appendix_c}).
 
@@
 \noindent \textbf{Demand}.
-It turns out that the demand for the promise-commitment contract  is higher than for the fee-commitment contract by a factor of 3: 31\% of clients offered a choice between the status quo contract and the promise-commitment contract chose commitment.
+It turns out that the demand for the promise-commitment contract  is higher than for the fee-commitment contract by a factor of 3: \hl{31}\% of clients offered a choice between the status quo contract and the promise-commitment contract chose commitment.
 This means that the pecuniary fee indeed limited demand for commitment.
@@
 In a pawnshop borrowing context, we study whether forcing borrowers into frequent payment commitment contracts reduces their borrowing costs, compared to a contract that does not provide commitment to pay monthly.
-Even though we are charging them fees, their borrowing costs are actually reduced by 9.5\%, and they recover their pawn with 25\% higher likelihood.
-Moreover they themselves seem to like this contract, as they are 55\% more likely to come back and pawn again when they get it.
+Even though we are charging them fees, their borrowing costs are actually reduced by 9.4\%, and they recover their pawn with 26\% higher likelihood.
+Moreover they themselves seem to like this contract, as they are 100\% more likely to come back and pawn again when they get it.
 That is, commitment matters and it seems beneficial.
@@
 In Panel (a) each dot represents the estimated treatment effect for a different definition of financing cost, or for a different sub-population, and its 95\% confidence interval.
-From left to right, the first effect corresponds to using the gold value of the pawned piece in the definition of financial cost and discounting the payments to present value using a 7\% monthly rate; the second uses the subjective value of the pawn; the third is analogous to the second but adds transaction cost (transport+1 day's wage) per visit; the fourth conditions on the population that paid any positive amount towards recovery of their pawn; the fifth conditions on the sub-population of the treatment group that paid a fee and compares these to all the control group.
+From left to right, the first effect corresponds to using the gold value of the pawned piece in the definition of financial cost and discounting the payments to present value using a 7\% monthly rate - to the left we have a decomposition of the financial cost in its four components from left to right (1) Discounted payments to capital, (2) Payed fees, (3) Payed interest, (4) Cost of losing pawn; the second uses the subjective value of the pawn; the third is analogous to the second but adds transaction cost (transport+1 day's wage) per visit; the fourth conditions on the population that paid any positive amount towards recovery of their pawn; the fifth conditions on the sub-population of the treatment group that paid a fee and compares these to all the control group.
 Panel (b) plots the effects on different quantiles of the distribution of financial cost (using the first definition): 15th, 25th, 50th, 75th, 85th percentile.
@@
 The left Y-axis measures the fraction of subjects that would have been better by a margin of $z$\% if they changed their choice, and the right Y-axis measures the amount of money ``left on the table''.
-The thinly dotted lines represent 90\% confidence intervals.
+We use bootstrap to tighten the confidence intervals (CIs).
+\cite{atheygrf}'s heterogeneous treatment effect using GRF is asymptotically normal.
+We compute the HTE ($\mu$) together with standard errors ($\sigma$) .
+For every pledge, we draw a random effect from a normal distribution with parameters ($\mu$,$\sigma^2$), and compute via bootstrap the percentage that choose wrong, along normal-approximation CIs (results are robust if we use instead percentile CIs or bias-corrected CIs) .
+This allows us to estimate a distribution for the upper and lower bound CIs, which we then use to obtain a 95\% CI.
 Panel (b) is analogous to Panel (a) except that it does the exercise separately for clients we classified as overconfident ($OC_i:=\mathbbm{1}(P^s_i-\widehat{P_i(X_i)}>0))$ and those we classified as not overconfident.

### 2021-03-09 RScripts/fc_te_grf.R

@@ -3,7 +3,7 @@ library(grf)
 library(ggplot2)
 
 # SET WORKING DIRECTORY
-setwd('C:/Users/xps-seira/Dropbox/Apps/ShareLaTeX/Donde2020')
+setwd('C:/Users/isaac/Dropbox/Apps/ShareLaTeX/Donde2020')
 #setwd("C:\\Users\\Ricardo\\Documents\\SEIRA\\donde2019")
 set.seed(5289374)
 

### 2021-03-09 RScripts/grf.R

@@ -6,12 +6,12 @@ library(DiagrammeRsvg)
 library(gdata)
 
 # SET WORKING DIRECTORY
-setwd('C:/Users/xps-seira/Dropbox/Apps/ShareLaTeX/Donde2020')
+setwd('C:/Users/isaac/Dropbox/Apps/ShareLaTeX/Donde2020')
 set.seed(5289374)
 
 source("./RScripts/best_tree.R")
 
-heterogeneity_effect <- function(data_in,treatment_var,outcome_var,writedata) {
+heterogeneity_effect <- function(data_in,treatment_var,outcome_var,writedata,extendedsample) {
   
 require("dplyr")
 data_frame <- data_in %>%
@@ -60,23 +60,28 @@ print(average_treatment_effect(tau.forest, target.sample = "treated"))
 print(average_treatment_effect(tau.forest, target.sample = "control"))
 
 #Write data
-data.out <- add_column(data_frame,tau_hat_oob$predictions,tau_hat_oob$variance.estimates, propensity_score)
-filename <- paste("_aux/grf_", treatment_var,"_",outcome_var, ".csv", sep="") 
 if (writedata == 1) {
+  data.out <- add_column(data_frame,tau_hat_oob$predictions,tau_hat_oob$variance.estimates, propensity_score)
+  if (extendedsample == 1) {
+    filename <- paste("_aux/grf_extended_", treatment_var,"_",outcome_var, ".csv", sep="") 
+  } else {
+    filename <- paste("_aux/grf_", treatment_var,"_",outcome_var, ".csv", sep="") 
+  }
   write_csv(data.out,filename)
-}
-if (writedata == 0) {
+} else {
   # Tree Plot
   tree.plot = plot(get_tree(tau.forest, best_tree_info$best_tree))
   filename_pl <- paste("Figuras/crf_", treatment_var,"_",outcome_var, ".svg", sep="") 
   cat(DiagrammeRsvg::export_svg(tree.plot), file=filename_pl)
 }
+
 }
 #####################################################
 
 # READ DATASET
 # Prenda level
 data <- read_csv('./_aux/heterogeneity_grf.csv')
+data_extended <- read_csv('./_aux/heterogeneity_te.csv')
 # Data with names in english
 data_copy <- data
 data_copy <- rename.vars(data_copy, c(
[…]

### 2021-03-09 RScripts/oc_pred.R

@@ -1,0 +1,31 @@
+library(tidyverse)
+library(grf)
+library(ggplot2)
+
+
+# SET WORKING DIRECTORY
+setwd('C:/Users/isaac/Dropbox/Apps/ShareLaTeX/Donde2020')
+set.seed(5289374)
+
+
+# READ DATASET
+data_oc <- read_csv('./_aux/data_oc.csv')
+data_test <- data_oc %>% 
+  select(-c(prenda, producto, des_c))
+
+
+# PREPARE VARIABLES
+X <- select(data_oc,-c(prenda, producto, des_c))
+Y <- as.numeric(data_oc$des_c == 1)
+  
+###################################################################  
+###################################################################  
+  
+# ESTIMATE MODEL
+pred.forest = regression_forest(X, Y)
+rf_des_c_pred = predict(pred.forest,data_test)$predictions
+hist(rf_des_c_pred, xlab = "predictions")
+  
+data.out <- add_column(data_oc, rf_des_c_pred)
+write_csv(data.out,"_aux/pred_oc.csv")
+

### 2021-09-10 donde.tex
Redefine definition of financial cost as effective cost/loan ratio
Former-commit-id: 6ca64d61c64e073a31eb2db5a471af41f2c3e9a6

--- 2021-03-09 main.tex
@@
 
-\title{The limits of self-commitment and private paternalism \thanks{We want to thank Craig McIntosh, Mauricio Romero, and Anett John for advice and encouragement.
+\title{The limits of self-commitment and private paternalism \thanks{We want to thank Mauricio Romero and Anett John for advice and encouragement.
 Ricardo Olivares, Gerardo Melendez, and Alonso de Gortari provided excellent research assistance and Erick Molina helped with formatting.
 Jose Maria Barrero, Andrei Gomberg, Emilio Gutierrez, David Laibson, Aprajit Mahajan, Matt Rabin, Charlie Sprenger, and seminar participants at ITAM provided valuable feedback.}}
-\author{Isaac Meza \and Joyce Sadka \and Enrique Seira   \thanks{Seira: ITAM, enrique.seira@gmail.com (corresponding author); Meza: University of California at Berkeley, isaac.meza@berkeley.edu; Sadka: ITAM, jsadka@itam.mx} }
+\author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira   \thanks{Seira: ITAM, enrique.seira@gmail.com (corresponding author); Meza: University of California at Berkeley, isaac.meza@berkeley.edu; Sadka: ITAM, jsadka@itam.mx} }
 \date{This draft:  \today \\[2 cm]}
@@
 In the context of pawnbroker lending, we show that forcing people into commitment contracts with financial penalties for not paying on time \textit{decreases} their (fee-including) financial cost by 9.4\%, increases the likelihood of recovering their pawn by 26\%, and increases the likelihood of repeat business by almost 100\%.
-Using machine learning methods for estimating heterogeneous treatment effects, we find that more than \hl{90}\% clients would reduce their financing cost with the commitment contract, however only 10\% choose it.
+Using machine learning methods for estimating heterogeneous treatment effects, we find that more than {70}\% clients would reduce their financing cost with the commitment contract, however only 10\% choose it.
+Those that \textit{don't} choose it are predicted to be the ones who would benefit more.
 Relying on personal promises instead of fees as commitment triples take-up but has no effects on outcomes.
@@
 Many institutions ---firms, schools, financial contracts--- restrict choice using built-in commitment mechanisms which help workers, students, borrowers overcome self-control problems.
-For instance, ``[mortgages restrict choice] with a fixed repayment stream and mandatory principal repayment'' \citep{Laibson2018}.\footnote{\cite{Laibson2018} also mentions that ``Firms do limit their workers' freedom with intermediate deadlines, progress reports, production targets'', and schools with ``pop quizzes, classroom attendance requirements, cold calling, graded problem sets, deadlines''.} At the same time  these same firms shroud these forcing mechanisms and don't market their commitment features, presumably because students, workers and borrowers ``don't welcome these paternalistic restrictions''.
-\cite{Laibson2018} argues that this presents an important puzzle: clients that benefit from commitment although may underestimate its value and this have low demand for it.
-In such a case private paternalism may be beneficial.\footnote{\cite{Laibson2018} defines paternalism as a policy that advances an individual's interests by restricting his or her freedom, and private paternalism as paternalism implemented by private institutions.
-In this paper we will study the effect of restricting freedom of contract choice on two outcomes: pawn recovery and financing cost, not overall welfare.}
+For instance, ``[mortgages restrict choice] with a fixed repayment stream and mandatory principal repayment'' \citep{Laibson2018}.\footnote{\cite{Laibson2018} also mentions that ``Firms do limit their workers' freedom with intermediate deadlines, progress reports, production targets'', and schools with ``pop quizzes, classroom attendance requirements, cold calling, graded problem sets, deadlines''.} At the same time  these same firms shroud and don't market these commitment features, presumably because students, workers and borrowers don't welcome these restrictions.
+\cite{Laibson2018} argues that this presents an important puzzle: clients that would benefit from commitment underestimate its value and thus have low demand for it.
+In such a case private paternalism may be beneficial.\footnote{Laibson defines paternalism as a policy that advances an individual's interests by restricting his or her freedom, and private paternalism as paternalism implemented by private institutions.
+%In this paper we will study the effect of restricting freedom of contract choice on two outcomes: pawn recovery and financing cost, not overall welfare.
+We want to clarify that we are using the word ``paternalism'' in a restricted sense, meaning only that a large majority of clients would incur in lower financial costs from being forced into installment contracts instead of letting them choose.
+We are not making claims about overall welfare which is a slippery concept if we take into account the possibility of biased beliefs and preferences.}
 
@@
 Pawn loans are one of the oldest, most understudied, and most prevalent forms of borrowing.
-There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues (in China it is a 43 billion dollar industry).\footnote{\url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.} Our partner pawn lender (henceforth Lender $P$) alone served more than 1 million clients in the last 3 years with more than 4 million contracts.\footnote{For comparison there were 2.3 million micro-finance clients in Mexico in 2009 (\cite{Pedroza:2010}).} The key characteristic of pawn loans is that the borrower leaves personal property (a pawn) as collateral in exchange for an immediate cash loan of a smaller value.
+There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues.
+In China it is a 43 billion dollar industry.\footnote{\url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.} Our partner pawn lender (henceforth Lender $P$) alone served more than 1 million clients in the last 3 years with more than 4 million contracts.
+The key characteristic of pawn loans is that the borrower leaves personal property (a pawn) as collateral in exchange for an immediate cash loan of a smaller value.
 In our case Lender $P$ only accepts gold jewelry as collateral and approves all pawns, giving cash the equivalent of 70\% of the pawn's appraised value.
 The contract stipulates a 7\% monthly interest rate charged daily, a loan term of 90 days, and the flexibility to pay back the loan at anytime before the loan is due.
-In spite of this flexibility, most people lose their pawn, and among those that recover it almost all of them pay in the last days, just before the loan elapses.\footnote{In the US default is also high at 15\% (\url{https://tinyurl.com/yc2x5bjf}).}
+In spite of this flexibility ---or perhaps because of it--- 60\% of clients lose their pawn\footnote{In the US default is also high at 15\% (\url{https://tinyurl.com/yc2x5bjf}).}, and among those that recover it almost all of them pay in the days just before the loan elapses.
 
@@
 In our survey 69\% report self-control problems saying they often fall into temptation spending.
-%, but only \hlgr{15\%} show inter-temporal inconsistencies in a classical present-bias question, a similar number to \cite{Ashaf}.
-%and \hl{19\%} do not normally budget monthly expenses.
+%, but only gr{15\%} show inter-temporal inconsistencies in a classical present-bias question, a similar number to \cite{Ashaf}.
+%and {19\%} do not normally budget monthly expenses.
 %While this is suggestive of a present bias problem or overconfidence to save and pay, at the same time our subjects are experienced and not wholly uneducated, 66\% have completed at least high school and 90\% have pawned before.
-%and \hl{38\%} have participated in a Rosca.
+%and {38\%} have participated in a Rosca.
 
@@
 That is, we are asking whether \textit{charging} them a 2\% late payment fee for not paying a monthly installment on time can actually \textit{decrease} total (fee-inclusive) financing cost.
-Second, would there be demand for such an installment contract vis-a-vis the status quo one if given choice?
-Any payment profile implemented in the commitment contract can be replicated by the borrower under the status quo contract, but the former provides commitment.
+Second, would there be demand for such an installment contract vis-a-vis the status quo one if given the choice?
+Note that any payment profile implemented in the commitment contract can be replicated by the borrower under the status quo contract, but the former provides commitment.
 Third, would clients who benefit from commitment the most (e.g.
@@
 Here let us briefly explain the main 3 arms.
-The first one involves a group of clients that were given only the status quo contract (henceforth the \textit{status-quo forcing group}).
+The first one involves a group of clients that were given only the status quo flexible payments contract (henceforth the \textit{status-quo forcing group}).
 The second arm (\textit{fee-forcing group}) was given a monthly payment commitment contract, which stipulated that clients had to pay 1/3 of their loan plus accumulated interest in each of the 3 months of the term length.
@@
 
-Forcing clients into frequent payment commitment contracts causes them on average to save on financing cost and to recover their pawn more.
+Results are striking.
+First, we find that forcing clients into frequent payment commitment contracts causes them on average to save on financing cost and to recover their pawn more.
 The effects are large: financing cost decreases by 9.4\% on average (from \$3157 to \$2860 MXN), while the likelihood of recovering their pawn increases by 26\% (from 43\% to 55\%).
@@
 Treatment effects are concentrated in the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery.
-The fee-commitment contract induces people who would otherwise pay something towards recovery, to pay more and faster and thus recover their pawn more at a cheaper financial cost.
+That is, the fee-commitment contract induces people who would otherwise pay something towards recovery, to pay more and faster and thus recover their pawn more at a cheaper financial cost.
 Finally, borrowers assigned to the forced fee-commitment contract are 5 percentage points (100\% of the mean) more likely than the control group to ask for another loan in the future, suggesting that they liked the commitment contract after experiencing it.
@@
 
-In spite of these estimated benefits for almost all clients, actual demand for the fee-commitment contract is low.
+Second, in spite of these estimated benefits for almost all clients, actual demand for the fee-commitment contract is low.
 Only 10\% of the group offered a choice between the monthly payment fee-commitment contract and the status-quo one chose the former.
 This is not likely driven by misunderstanding the (already simple) contract.\footnote{We posted two project assistants in each of the experimental branches every day for all branch opening hours to carefully explain the contracts; material was developed to explain the differences among the two contracts, and subjects spelled back to our team the loan differences.
-Furthermore take up is systematically predicted by baseline covariates, making it less likely that these are just random mistakes.} We show further that clients that most benefit from the contract (those who are overconfident about recovering) are \textit{less} likely to demand it, echoing a result by \cite{Sprenger}.
+Furthermore take up is systematically predicted by baseline covariates, making it less likely that these are just random mistakes.} We show further that clients that most benefit from the contract (those who are overconfident about recovering) are \textit{less} likely to demand it, echoing a result by \cite{Sprenger} for grocery purchases and \cite{Walters} for schools.
 %is Low demand for commitment is consistent with a large literature (\cite{Laibson2015}, \cite{Laibson2018}, \cite{John}, \cite{Ted}, \cite{Rabin2018}).
@@
 
-Combining the forcing and the choice arms ---a unique feature of our experiment--- allows us to estimate the counterfactuals to answer the question of how much money is left on the table by giving choice to clients.
-We calculate that about \hl{80}\% of clients in the fee-choice group chose contracts that induced \textit{higher} financial cost.
-On average they spend an extra \$\hl{238} MXN, close to \hl{11}\% of the average loan value.
-In particular \hl{92}\% of those that chose the status-quo contract would have been better in the fee-commitment contract, while only \hl{8}\% of those who chose the fee-commitment contract would have been better in the status-quo one.
-This suggests that forcing clients into commitment contacts (i.e.
-private paternalism) may be beneficial for the overwhelming majority of clients.
+Third, combining the forcing and the choice arms ---a unique feature of our experiment--- allows us to estimate the counterfactuals to answer the question of how much money is left on the table by giving choice to clients.
+We calculate that about {80}\% of clients in the fee-choice group chose contracts that induced \textit{higher} financial cost.
+On average they spend an extra \${238} MXN, close to {11}\% of the average loan value.
+In particular {92}\% of those that chose the status-quo contract would have been better in the fee-commitment contract, while only {8}\% of those who chose the fee-commitment contract would have been better in the status-quo one.
+This suggests that forcing clients into commitment contacts ---private paternalism--- may be beneficial for the overwhelming majority of clients.
 After seeing our results Lender $P$ introduced frequent payment contracts in their loans portfolio.
 
-We want to clarify that in the paper we are using the word ``paternalism'' in a restricted sense, meaning only that a large majority of clients would incur in lower financial costs from being forced into installment contracts instead of letting them choose.
-We are not making claims about overall welfare which is a slippery concept if we take into account the possibility of biased beliefs and preferences.
-
-Inspired by a significant lab experiment literature on the effects of promises on behavior, and by research showing that a small fee could drastically reduce demand for commitment of (partly) naive present-biased borrowers (\cite{Laibson2015}), we implemented a ``psychological commitment'' in the form of a salient promise to pay.
+Inspired by a significant lab experiment literature on the effects of promises on behavior, and by research showing that a small fee could drastically reduce demand for commitment of (partly) naive present-biased borrowers (\cite{Laibson2015}), we implemented a ``psychological commitment'' product in the form of a salient promise to pay.
 \cite{PromisesPartnerships}, \cite{FurtherPromises}, \cite{Vanberg}, and \cite{Ismayilov2017} find that the ability to make a promise about behaving a certain way makes the individual more likely to adhere to the promised behavior.
 %and also induces trusting behavior by the recipients of the promise.
+
 To measure the causal effect of promises we implemented two other treatment arms.
@@
 
-We document two main results in the promise arms.
-First, demand for the commitment-promise contract is three times larger than for the commitment fee contract, with \hl{31}\% take-up.
-This difference between both choice arms suggests that clients are indeed understanding and taking into account the contractual parameters in their choice, and that the fee commitment was probably too strong from their point of view.
-In spite of this much higher take-up, the \textit{Promise-choice arm} had no effect on outcomes on average, or even for those who selected into promising.
-Second, being forced in to the \textit{Promise} contract also had zero effects on average and throughout the distribution on financing cost and pawn recovery.
+We document three main results in the promise arms.
+First, demand for the promise-commitment contract is three times larger than for the fee-commitment contract, with {31}\% take-up.
+This difference shows that clients are indeed taking into account the contractual parameters when they choose, and that the fee commitment was probably too strong from their point of view.
+Second, in spite of this much higher take-up, the \textit{Promise-choice arm} had no effect on outcomes on average, or even for those who selected into promising.
+Third, being forced in to the \textit{Promise} contract also had zero effects on average and throughout the distribution on financing cost and pawn recovery.
 %\footnote{There is a decrease in financial cost in the 50th and 75th quantiles in the forced promise-commitment arm however.}
 Promises did not provide enough commitment so as to be reflected in behavior.
+This is one of the first  experiments using promises in the field, and results are in striking contrast with those in the lab.
 
@@
 We could not find peer-reviewed papers about it either.} It is different from microfinance in that it deals with emergency loans, and not loans for productive investment.
-Because of this, it may draw on a more vulnerable (and potentially more unsophisticated) population.
-Moreover, the trade-off between loan rigidity and investment found for microfinance \citep{Field} may not be there for pawn borrowing.
-Second, a significant literature has shown that demand for commitment exists but is somewhat low in some contexts (\cite{Ashraf}, \cite{Gine}, \cite{Ted}, \cite{Royer}, \cite{Sprenger}), and high in others (\cite{Kremer},  \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}, \cite{Pascaline}).
-We add to this literature by showing --although we may not be the only ones-- that very small fees\footnote{For instance our fees are 16 times smaller than than those of \cite{John} as a fraction of the loan/goal, and 5 times smaller converting peso values using exchange rates.} are enough to drastically reduce demand for commitment, even when commitment is cost-reducing.
-We also show that softer commitments in the form of non-pecuniary personal promises elicit higher demand but do not affect behavior or financing costs.
-
-Third, \cite{John} and \cite{Ted} show that the extent of commitment needed is underestimated even among those that purchase commitment mechanisms, and that subjects hurt themselves by self-imposing too weak a commitment in the intensive margin.
-We contribute in design by not allowing choice of the extent of commitment, and methodologically by inferring subjects underestimation of the value of commitment ex-ante from forgone treatment savings, instead of from subjects failing to reach a goal ex-post.
-In consonance with \cite{Sprenger} but in our very different context, we find that people who most need commitment (in our case the overconfident, as they have the larger treatment effects) are also the ones less likely to demand it when given choice.
+Because of this, it may draw on a more vulnerable (and potentially more unsophisticated) population, and because it is not typically used for productive investment, the trade-off between loan rigidity and investment found for microfinance \citep{Field} may not be there.
+
+Second, a significant literature has shown that demand for commitment exists.
+But while it is low in some contexts (\cite{Ashraf}, \cite{Gine}, \cite{Ted}, \cite{Royer}, \cite{Sprenger}), it is high in others (\cite{Kremer},  \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}, \cite{Pascaline}).
+We add to this literature by adding evidence from another market.
+Demand for commitment  is low, and very small fees\footnote{For instance our fees are 16 times smaller than than those of \cite{John} as a fraction of the loan/goal, and 5 times smaller converting peso values using exchange rates.} are enough to drastically reduce demand for commitment, even when commitment is cost-reducing.
+Softer commitment contracts in the form of promises do increase demand but did not change outcomes.
+%We also show that softer commitments in the form of non-pecuniary personal promises elicit higher demand but do not affect behavior or financing costs.
+
+Third, and most importantly, we study both causal effects and selection into frequent payment commitment loan contracts at the same time and for the same population in a single experiment.
+We know of no other experiment in the credit market which simultaneously combines forcing and choice arms.
+This feature, when paired with new machine learning methods to estimate heterogeneous treatment effects \citep{atheygrf}, allows us to show whether there is positive or negative selection into beneficial contracts, and whether pawnshop clients forego money by not demanding commitment.
+In consonance with what \cite{Walters} finds in the school choice context, we find that it is \textit{not} those who benefit most from the contract that demand it more.
+\cite{Sprenger} find similar result in the context of grocery purchases.
 In contrast to \cite{Sprenger}, our context allows us to focus on money savings instead of estimated utility to proxy for benefits of commitment, a narrower but more transparent measure.
-This allows us to measure effects on cost outcomes beyond take up.
-As in \cite{Rabin2018} we are able to contrast subjects' \textit{own predictions} of their behavior with their actual behavior, and how these map to outcomes, but we do it in a natural setting.
-
-Fourth, and most importantly, we study both causal effects and selection into frequent payment commitment loan contracts at the same time and for the same population in a single experiment.
-We know of no other experiment in the credit market which simultaneously combines forcing and choice arms.
-This feature, when paired with new machine learning methods to estimate heterogeneous treatment effects (\cite{atheygrf}), allows us to show whether there is positive or negative selection into beneficial contracts, and whether pawnshop clients forego money by not demanding commitment.
-In consonance with what \cite{Walters} finds in the school choice context, we find that it is \textit{not}  those who benefit most from the contract that demand it more.
-
-Studying causal effects of installment payment frequency, \cite{Pande} find null effects on loan default, a surprising result given the prevalence of frequent payment contracts.
-In contrast we find strong effects of payment frequency on decreased default.\footnote{There are many differences in context between the papers which may explain the different result.
+This allows us to measure effects on cost outcomes beyond take up.\footnote{\cite{John} and \cite{Ted} show that the extent of commitment needed is underestimated.
+In contrast to them, we infer subjects underestimation of the value of commitment from their forgone treatment savings, instead of from subjects failing to reach a goal.}
+
+%Third, in consonance with \cite{Sprenger} and \cite{Walters} but in our very different context, we find that people who most need commitment (in our case the overconfident, as they have the larger treatment effects) are also the ones less likely to demand it when given choice.
+
+Fourth, we provide new evidence on the payment frequency debate.
+The literature has found null effects on installment frequency loan default \cite{Pande}.
+This result is at odds with the prevalence of frequent payment contracts in markets.
+We find strong effects of payment frequency on decreased default.\footnote{There are many differences in context between the papers which may explain the different result.
 \cite{Pande} focus on group lending with very little default to start with (less than 1\%), while in our case almost half of loans end in default.
-We also have a larger sample and we focus on individualized loans, which may afford us stronger statistical power to detect effects.} Our result is consistent with \cite{Field} who show that delaying payment in microfinance loans increases default.\footnote{\cite{Craig} use the discipline of regular loan repayments in microfinance to remind people to save and make a savings plan, and find large increases in savings.} On the other hand, studying selection into frequent payment microfinance loans, \cite{Murdoch} show that a robust positive correlation exists between displaying present biased preferences in surveys and selecting into microfinance, which they interpret as being due to high demand for the discipline imposed by frequent payments.
+We also have a larger sample and we focus on individualized loans, which may afford us stronger statistical power to detect effects.} Our result is consistent with \cite{Field} who show that delaying payment in microfinance loans increases default.\footnote{\cite{Craig} use the discipline of regular loan repayments in microfinance to remind people to save and make a savings plan, and find large increases in savings.}
+
+We believe that taken together, our results (commitment matters, small fees have large effects on behavior, people don't choose the cost reducing contract) call for a behavioral explanation.
+Most of the literature tries to connect commitment problems with measures present biased preferences.
+Results are mixed, which is not surprising given how hard is to measure present bias naivete for instance.
+Instead of trying to measure those we focus on measuring biased predictions about payment, what we call overconfidence.
+Not only is it easier to measure, but also more general in the sense of being implied by present bias but not conversely.
+As in \cite{Rabin2018} we contrast subjects' \textit{own predictions} of their behavior with their actual behavior, but we do it in a natural setting.
+\cite{Murdoch} show that a robust positive correlation exists between displaying present biased preferences in surveys and selecting into microfinance, which they interpret as being due to high demand for the discipline imposed by frequent payments.
 However they acknowledge that this ``interpretation is suggestive...
 and needs to be confirmed by studies that establish causal links''.
-Our experiment is a test of this causal link, and it rejects the hypothesis that the majority of microfinance (pawnshop) clients demand frequent payments contracts, at least in our context.
+Our experiment is a test of this causal link.
 
@@
 In concordance with this literature we find that people are willing and indeed voluntarily choose to make promises.
-We find however that measured behavior was unchanged by promising.\footnote{This is of course not a refutation of this literature by any means.
+We find however that measured behavior was unchanged by promising.\footnote{This is of course not a refutation of the laboratory literature.
 %not least because the laboratory literature is implemented on more tightly controlled environments and focused on subtler aspects of promising, like their effects on second order beliefs and guilt aversion.
 The context is also different since
-The lab literature has focused mostly on very structured investment games between two players and looked at the effects of promises on trust and cooperation through guilt aversion and cost of lying channels.
-In our case the bank is not a strategic player that responds to the promise or a person (although the teller is).
+The lab literature has focused on very structured investment games between two players and looked at the effects of promises on trust and cooperation.
+In our case the bank is not a strategic player that responds to the promise, or a person to which the client can feel guilt towards (although the teller is).
 However, our results do provide a first piece of evidence on the limitations of using promises to change behavior in loan contracts.}
@@
 
-Pawn borrowing is one of the oldest forms of borrowing and one to which people with little access to the formal credit market turn to for ``emergency'' loans.
-They existed in antiquity at least since the Roman Empire, and there are records of it in China about 1,500 years ago (\cite{PawnShops}).
-As explained above, pawn loans involve individuals leaving valuable and liquid assets (typically jewelry) as collateral in exchange for an immediate cash loan, which is typically used to pay for emergencies.
+Pawn loans involve individuals leaving valuable and liquid assets, typically jewelry, as collateral in exchange for an immediate cash loan.
+Collateral is typically much larger than the loan, which allows lenders to skip the checking of credit history and give the loan immediately.
+This makes pawn loans popular to get cash to pay for emergencies.
+In fact, they are one of the most prevalent forms of borrowing.
+There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues.\footnote{\url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.} Our partner pawn lender alone served more than 1 million clients in the last 3 years with more than 4 million contracts.
+For comparison there were 2.3 million micro-finance clients in Mexico in 2009 \citep{Pedroza:2010}.
+
+Pawn borrowing is also one of the oldest forms of borrowing.
+Pawn loans existed in antiquity at least since the Roman Empire, and there are records of it in China about 1,500 years ago \citep{PawnShops}.
 
@@
 
-In spite of it high prevalence, pawnshop borrowing has not received much attention in the economics literature.
-The closest product studied is payday loans.
+In spite of the high prevalence and long history, pawnshop borrowing has not received much attention in the economics literature.
+The closest product studied is probably payday loans.
 In developing countries, however, payday lending is likely small compared to pawnshop lending; the latter is faster and requires less documentation, allowing access to informal sector workers who receive their salaries in cash.
@@
 
-Payday lending is controversial and regulators have concerns with the sophistication of borrowers using it.
-The US congress has actually banned the payday lending industry from serving active military personnel, and some states in the US have imposed zoning restrictions, interest caps, and restrictions on serial borrowing as consumer protection measures against payday lending \citep{Payday}.
-The main source of concern is whether consumers that use these loans suffer from behavioral and cognitive biases which imply sub-optimal choices, and there is some evidence for this.\footnote{\cite{Bertrand} write that ``Under the view that the people borrowing from payday lenders are making an informed, utility-maximizing choice given the constraints that they face, one  would not expect additional information disclosure about the payday product to  alter their borrowing behavior'', but to the contrary they find that simply disclosing how financing costs add up reduced demand by 11\%.
+As with payday lending, pawnshop lending is controversial.
+Regulators have concerns with the sophistication of borrowers using it.
+The US congress has actually banned the payday lending industry from serving active military personnel, and some States in the US have imposed zoning restrictions, interest caps, and restrictions on serial borrowing as consumer protection measures against payday lending \citep{Payday}.
+The main source of concern is whether consumers that use these loans suffer from behavioral and cognitive biases which imply sub-optimal choices.
+There is some evidence  in support of this view.\footnote{\cite{Bertrand} write that ``Under the view that the people borrowing from payday lenders are making an informed, utility-maximizing choice given the constraints that they face, one  would not expect additional information disclosure about the payday product to  alter their borrowing behavior'', but to the contrary they find that simply disclosing how financing costs add up reduced demand by 11\%.
 %\cite{Meltzer} finds that payday loan access leads to increased difficulty paying mortgage, rent and utilities bills.
-} Similar concerns apply to pawnshop borrowing.
-
-\subsection{The pawn lender and high default rates}
+}
+
+\subsection{Lender P and the status quo contract}
 
 We study pawnshop borrowing by partnering with Lender $P$, one of the largest pawn shops in Mexico, with more than one hundred branches spanning multiple States in Mexico.
-Our context is one with high borrower default: 60\% of clients lose their pawn in a time span of 230 days from the date of pawning.
-This default is likely inefficient since clients report a subjective value that is almost twice its gold value on average.
-It can also be detrimental from the lender's point of view since it may reduce the likelihood that the client becomes a return costumer; this would explain why Lender $P$ was interested in investigating whether a frequent payment contract would increase pawn recovery and costumer satisfaction, and whether there was demand for such a contract.
-
-One potential explanation for high default is that clients are really just selling their gold piece.
-This is unlikely for several reasons: (a) the reported subjective value of the pawn is larger than the loan size for 86\% of them, (b) among those that lose their pawn 48\% paid a positive amount towards its recovery and on average paid 42\% of the value of their loan (see Figure \ref{proxy_naive} in Appendix) --- this can only be rationalized if they expected to recover their pawn, (c) clients can easily sell the gold and obtain a higher amount of instant cash at gold buying stores located close to almost all our pawnshop branches (see Figure \ref{GoldBuyers}).
-%(d) there is a lot of engagement with the lender after pawning even for those who lost their pawn.
-On average clients that lost their pawn paid 34\% of the value of their loan, and close to 42\% of clients extended the loan for another cycle and made payments in the second cycle (see Figure \ref{proxy_naive} in Appendix).
-
-\subsection{The status quo contract}
 
@@
 
-Lender $P$ had only one type of contract.
+Lender P had only one type of contract, henceforth the \textit{status quo} contract.
 It stipulated that the interest rate was 7\% \textit{per month} accumulated daily on the outstanding amount of the loan.
@@
 The clients that pawned understood its conditions (as we verified in interviews) and still decided to pawn.\footnote{90\% of clients report in our survey that they have pawned before.} These clients have little or no access to other types of loans and value the convenience of pawn borrowing.
-Potentially borrowers like it also because they are overconfident about the probability of recovering their pawn, as discussed below.
+We conjectured that potentially borrowers also like it because they are overconfident about the probability of recovering their pawn, as we show below.
+
+\subsection{High default rates}
+Our context is one with high borrower default: 60\% of clients lose their pawn in a time span of 230 days from the date of pawning.
+This default is likely inefficient since clients report a subjective value that is almost twice its gold value on average.
+High default could be also detrimental from the lender's point of view since it may reduce the likelihood that the client becomes a return costumer.
+This could explain why Lender P was interested in  partnering with us to investigate whether a frequent payment contract would increase pawn recovery and costumer satisfaction, and whether there was demand for such a contract.
+
+One potential explanation for high default is that clients are really just selling their gold piece.
+This is unlikely for several reasons: (a) the reported subjective value of the pawn is larger than the loan size for 86\% of clients, (b) among those that lose their pawn 48\% paid a positive amount towards its recovery and on average paid 42\% of the value of their loan (see Figure \ref{proxy_naive} in Appendix) --- this can only be rationalized if they expected to recover their pawn, (c) clients can easily sell the gold and obtain a higher amount of instant cash at gold buying stores located close to almost all our pawnshop branches (see Figure \ref{GoldBuyers}).
+%(d) there is a lot of engagement with the lender after pawning even for those who lost their pawn.
+On average clients that lost their pawn paid 34\% of the value of their loan, and close to 42\% of clients extended the loan for another cycle and made payments in the second cycle (see Figure \ref{proxy_naive} in Appendix).
 
@@
 We had a team of enumerators in each branch collect surveys and clearly explain the contract terms to walk-in clients.
-The enumerators were inside the branch and asked clients to complete a 5 minute survey before going to the teller window to appraise their piece.
-The survey was implemented at the entrance of the branch before clients knew the contact that applied that day.
+The enumerators were inside the branch and asked clients to complete a 5 minute survey before going to the teller window to appraise their piece and before they were told contract terms (i.e.
+before treatment status was known).
 It was short to avoid discouraging the potential clients from pawning, but at the same time it aimed to measure the following: demographics, proxies for income/wealth, education, self-control problems/present-biased preferences, experience pawning, if family or friends commonly asked for money, how time consuming and costly it was to come to the branch, the subjective probability of recovering the piece that they intended to pawn, the subjective value of their piece in money terms (how much money they would sell it for), among others.
-We surveyed 10,437 clients (some refused).
-%\footnote{We also surveyed clients before and after the experiment, so our survey covers a larger sample that we are not using in this paper.}.
-The Appendix \ref{baseline_survey} transcribes the questionnaire in English.
+We surveyed 10,437 clients.\footnote{The Appendix \ref{baseline_survey} transcribes the questionnaire in English.} %\footnote{We also surveyed clients before and after the experiment, so our survey covers a larger sample that we are not using in this paper.}.
 Survey response rate is 78\%, and response is not related to admin data observables (details in Table \ref{balance_response} in the Appendix).
@@
 The average number of pawns per day per branch is 34.
-Only 42\% of clients recover their pawn within 230 days.
+Only 42\% of clients recover their pawn.
 Even those that recover their pawn tend to pay it back at the last moment, with only 40\% paying before the 90th day.
@@
 73\% of clients are women, with an average age of 43 years; 66\% of them have completed high school or more, and 90\% have pawned before, so that our sample has mostly experienced borrowers.
-Finally the subjective probability of recovery is close to 93\% on average, which contrasts with the 44\% recovery that happens in reality for the pawns in the control group.
+Finally the subjective probability of recovery is close to 93\% on average, which contrasts with the 51 points lower actual recovery.
 Borrowers seem to be highly overconfident on average.
-The average subjective value they report for the pieces is 3069 MXN, which is much larger than the average appraised gold value of 2197 MXN.
-This makes it inefficient for them to lose it.
+The average subjective value they report for the pieces is 3069 MXN, much larger than the average appraised gold value of 2197 MXN.
+%This makes it inefficient for them to lose it.
 
@@
 They often receive negative income shocks: 87\% said they are pawning because of an emergency, and only 13\% stated it was to use in a `non-urgent expense'.
-%When asked why they are pawning this piece \hlgr{5\%} responded \hlgr{`lost a family member'}, \hlgr{`a medical emergency'} (\hlgr{11\%}), \hlgr{`an urgent expense'} (\hlgr{71\%}),
+%When asked why they are pawning this piece gr{5\%} responded gr{`lost a family member'}, gr{`a medical emergency'} (gr{11\%}), gr{`an urgent expense'} (gr{71\%}),
 
@@
 \end{align*}
-, with $t$ indexing days, $T$ is the day when the pawn is recovered, I($\cdot$) an indicator function for recovering the pawn, $r$ is a daily interest rate equivalent to a 7\% monthly interest rate.\footnote{We experimented with different interest rates with similar results.
+
+\noindent $t$ indexes days, $T$ is the day when the pawn is recovered, I($\cdot$) an indicator function for recovering the pawn, $r$ is a daily interest rate equivalent to a 7\% monthly interest rate.\footnote{We experimented with different interest rates with similar results.
 See section \ref{neoclasical}.
-We also report results using the subjective value of the pawn reported by the borrower in the survey with similar results.} Figure \ref{fc_hist}(a) plots a histogram of this cost in pesos for loans where the pawn was recovered or lost.
-This cost is calculated for a time period of 230 days after loan origination, as %60\% of clients actually renew the loan one time.
-some clients renew the loan.\footnote{Figure \ref{fc_pro_2_115} reports results using only the first 115 days, with similar results.} Of those who renew, 83\% lose the pawn.
+We also report results using the subjective value of the pawn reported by the borrower in the survey again with similar results.
+This cost is calculated for a time period of 230 days after loan origination.
+Figure \ref{fc_pro_2_115} reports results using only the first 115 days.} Figure \ref{fc_hist}(a) plots a histogram of this financial cost in pesos for loans where the pawn was either recovered or lost.
+%Of those who renew, 83\% lose the pawn.
 Figure \ref{fc_hist}(a) suggest that financial cost is significant, even for those that do recover their pawn.
@@
 For them the cost is between 140\% and 250\% of the loan value.
-%\hl{The difference between panel (a) and (b) arises since clients who lose their pawn tend to be those that pledge cheaper pieces.}
-We calculate an APR of 218\% on average for the control group.\footnote{The Annual Percentage Rate (for pawn $j$) is calculated as the internal rate of return $i$ such that $\sum_t \frac{P_{jt}}{(1+i)^t} + \frac{\text{I}(Default \: Pawn_j) \times Pawn \: Value_j}{(1+i)^T} - Pawn \: Value_j = 0$, where $T$ is the date the pawn was lost, and $P_{jt} =P_{jt}^c+P_{jt}^f+P_{jt}^i $ is the sum of all payments.}
+%{The difference between panel (a) and (b) arises since clients who lose their pawn tend to be those that pledge cheaper pieces.}
+We calculate an APR of 218\% on average for the control group.%\footnote{The Annual Percentage Rate (for pawn $j$) is calculated as the internal rate of return $i$ such that $\sum_t \frac{P_{jt}}{(1+i)^t} + \frac{\text{I}(Default \: Pawn_j) \times Pawn \: Value_j}{(1+i)^T} - Pawn \: Value_j = 0$, where $T$ is the date the pawn was lost, and $P_{jt} =P_{jt}^c+P_{jt}^f+P_{jt}^i $ is the sum of all payments.}
 
@@
 In four of them the experiment ran for 107 days, and in 2 of them we ran it for a shorter time to economize on data collection costs once we realized we would not be constrained by sample size.
-%Thus we eliminated \hl{the smallest} ones.
-Branches are more than 5 km apart from each other, and there is little substitution among them (only 1\% of consumers appear in more than one of our branches).
+%Thus we eliminated {the smallest} ones.
+Branches are more than 5 km apart from each other, and there is little substitution among them; only 1\% of consumers appear in more than one of our branches.
 
@@
 It has the same interest rate (7\% \textit{per month}) which accumulates daily on outstanding debt, it has the same loan size/collateral ratio (70\%), it has the same loan term (90 days, and a grace period of 15 days), and the gold pawn gets appraised in the same way by the same appraisers.
-The only difference is that it has a requirement that the client has to pay monthly: for the 3 month duration at least 1/3 of the loan value (plus accumulated interest) has to be paid before day 30, 60 and 90 after loan disbursement.
+The only difference is that it has a requirement that the client has to pay monthly: for the 3 month duration of the contract, at least 1/3 of the loan value (plus accumulated interest) has to be paid before day 30, 60 and 90 after loan disbursement.
 Failure to pay this amount triggers a penalty fee of 2\% of this minimum amount due, which is added to the amount that the client needs to pay to recover their pawn.
 This penalty acts as a commitment incentive to pay now vs paying later.
-The level of the penalty was determined by Lender $P$ after talking to clients and based on Lender $P$'s experience.
+The level of the penalty was determined by Lender P after talking to clients and based on Lender P's experience.
 They deemed 2\% something that was big enough to provide commitment but small enough that if clients had an emergency and could not pay, the fee would not cause the pawn to be unrecoverable.\footnote{In contrast with \cite{John} we don't let the clients choose the size of the fee.
 That paper shows that doing this results in wrong choices by (partially) naive present biased consumers.
-Our fee is much smaller than the median in her experiment, as explained above.
+Our fee is much smaller than the median in her experiment, as explained in the introduction.
 We also experimented with a contract where there was no pecuniary fee for paying late but where we clients made a personal promise to pay monthly.}
@@
 They were told that there were 5 different ``types of contract-days'' and that the system chose randomly which applied on any given date, and that it could happen for instance that two consecutive dates had the same contract.
-They were also told that this way of operating was in place in various Lender $P$'s branches (they did not know which ones), and that it could be in place for several months.
+They were also told that this way of operating was in place in various Lender P's branches (they did not know which ones), and that it could be in place for several months.
 Randomizing at the day level limits the problem of contamination arising from clients realizing that other clients get different contracts than theirs.
 It also limits potential manipulation by appraisers, who in the presence of individual level randomization could potentially pick their preferred costumers from the line or tell them to wait until their desired contract shows up on the screen.
-Intra-branch day correlation on the probability of default (ICC) is small, at \hl{0.08}, so we don't lose much power vis-a-vis individual level randomization.
+Intra-branch day correlation on the probability of default (ICC) is small, at {0.08}, so we don't lose much power vis-a-vis individual level randomization.
 
 \vspace{.2in}
-\noindent \textbf{Treatment Arms.} We have 5 different experimental arms, randomized at the branch-day level.
+\noindent \textbf{Treatment Arms.} We have 5 different experimental arms:
 
 \begin{enumerate}
-    \item \textit{Status-quo forcing} arm: consisted of branch-days offering the status quo contract described in Section \ref{context}, and only this contract (as was standard). 
+    \item \textit{Status-quo forcing} arm: consisted of branch-days offering the status quo contract described in Section \ref{context}, and only this contract, as was standard. 
     \item \textit{Fee-Forcing} arm: consisted of branch-days offering only the monthly installment contract with a fee for late payment as described above. 
@@
 On the other hand, having arms where clients can choose among these contracts allows us to study clients' demand for commitment to pay earlier.
-A neoclassical consumer (with no intra-household concerns) would not voluntarily restrict her options of payment profiles (as in monthly payment contract) by being subject to fees, since she can always replicate the monthly payment profile herself under the status quo contract if she so desired.
+A neoclassical consumer with no intra-household concerns would not voluntarily restrict her options of payment profiles (as in the monthly installment contract) by being subject to fees, since she can always replicate the monthly payment profile herself under the status quo contract if she so desired.
 The status quo contract gives her extra flexibility to respond to negative income shocks.
 However, if clients have present biased preferences \textit{and} are sophisticated about them, they may choose the frequent payment contract as it has commitment value.
-This value would be traded off against the value of flexibility.
+This value would be traded off against the value of lost flexibility.
 
@@
 Panel (b) of Figure \ref{exp_description} shows how many contracts the experiment has in each arm (rectangles).
-And for the choice arms, it displays in blue how many people actually chose the commitment contract.
+And for the choice arms, it displays in blue how many people actually chose the respective commitment contract.
 
@@
 \noindent \textbf{Balance.} Table \ref{SS} shows that randomization worked to achieve balance across clients in the different experimental arms.
-One concern was that after learning the conditions of the contract clients could decide not to pawn.
-If they were differentially responsive to the different conditions, we could end up having different kinds of clients in the different arms.
+One concern was that after learning the conditions of the contract, clients could decide not to pawn.
+If they were deferentially responsive to the different conditions, we could end up having different kinds of clients in the different arms.
 It turns out this was not the case.
 
-Our enumerators informed us that potential clients rarely left the branch without pawning, and that it was even less common that they did so as a function of the treatment contract.
-Lender $P$ also never complained to us that our different treatments were hurting sales.
+Our enumerators informed us that potential clients rarely left the branch without pawning, and that it was even less common that they did so when hearing about monthly installments.
+It turns out that only \hl{XXX\%} of those surveyed ended up not pawning and appearing in the administrative data.
+Lender P also never complained to us that our different treatments were hurting sales.
 The data support this story as well.
 First, we cannot reject that the number of pawns per branch-day is the same across arms (Panel A).
-Panel C shows that about 89\% of people who answered our baseline survey also pawned, and that this ratio is balanced across arms.
+Panel C shows that about 98\% of people who answered our baseline survey also pawned, and that this ratio is balanced across arms.
 Second, not only are the number and shares of pawns the same across arms, but also the characteristics of clients and their pawned pieces are statistically the same across arms.
-Panel A of Table \ref{SS} tests this with administrative data, Panel B using baseline survey data for those that pawned and C without conditioning on pawning.
-.
-%The difference is that Panel B compares people that pawned, while \hl{Panel C uses clients that did not pawn.}
-Third, the characteristics of those who pawned before our experiment began are statistically the same as those during the experiment (Panel C).
+Panel A of Table \ref{SS} tests this with administrative data, while Panel B tests it using baseline survey data for those that pawned, and Panel C does it without conditioning on pawning.
+%The difference is that Panel B compares people that pawned, while {Panel C uses clients that did not pawn.}
+Third, the characteristics of those who pawned before our experiment began are statistically the same as those during the experiment, as documented in the first and second column of Panel C.
 
@@
 The terms need to be understood in order for choice to be meaningful, and for the monthly payment commitment contract to bite.
-We had two 'check-points' to do this.
+We had two `check-points' to do this.
 First, two enumerators were present in each branch for the whole day during the duration of our experiment to explain the contract terms to clients.
@@
 As shown below, different contract terms did generate differential demand and differential behavior.
-Moreover, we can systematically predict demand based on consumer characteristics, beliefs and proxies for present biased preferences.
+Moreover, we can systematically predict demand based on consumer characteristics and measured beliefs.
 
@@
 \noindent \textbf{Financial Cost.} Figure \ref{fc_pro2}(a) reports $\beta$ coefficients and their 95\% confidence interval from estimating equation (\ref{basic_reg}) using different definitions of financial cost.
-The leftmost coefficient corresponds to using the discounted appraised gold value of the pawned piece.
+The leftmost coefficient corresponds to plugging into the formula of section \ref{FC_def} the appraised gold value of the pawned piece.
 The second coefficient uses the subjective value of the pawn instead.
@@
 Going in that direction, in a broader measure of costs, for each visit we add the self-reported transport cost plus a whole day's wage, multiplied by the number of visits.
-Adding a whole day's wage may exaggerate cost, but we still observe a reduction of this more comprehensive measure of cost caused by the frequent payment contract, although we lose more than 1/3 of the observations and some precision.
+Adding a whole day's wage may exaggerate cost, but we still observe a reduction of this more comprehensive measure of cost caused by the frequent payment contract, although we lose more than 1/3 of the observations and some precision from missing data on transportation costs.
 
 \vspace{.2in}
-\noindent \textbf{Heterogeneous Treatment Effects.} Average cost reductions could mask substantial heterogeneity.
+\noindent \textbf{Heterogeneous Treatment Effects (HTE).} Average cost reductions could mask substantial heterogeneity.
 Benefits are distributed broadly however.
@@
 This motivated us to implement a finer measure of treatment effects.
-We used  \cite{atheygrf}'s generalized random forests methodology.
-The methodology uses random forests of honest causal trees to estimate personalized treatment effects.
-The method generates a partition of the space of characteristics $X$, where each element of the partition is a leaf, and each leaf contains treatment and control clients with similar characteristics $x \in X$ which are used to calculate unbiased honest treatment effects for that leaf.
-The optimal partition is that which minimizes expected mean squared error of treatment effects predictions out-of-sample.
-The tree is honest because it uses one sample to build the tree and another one to estimate treatment effects within that tree.
-The trees are such that at each leaf we obtain an unbiased estimate of a treatment effect using treatment and control observations in that leaf.
+We used  \cite{atheygrf}'s generalized random forests methodology.\footnote{The methodology uses random forests of honest causal trees to estimate personalized treatment effects.
+The method generates a partition of the space of characteristics $X$, where each element of the partition is a leaf, and each leaf contains treatment and control clients with similar characteristics $x \in X$ which are used to calculate unbiased treatment effects for that leaf.
+The optimal partition is that which minimizes expected mean squared error of treatment effects predictions out-of-sample.} %The tree is honest because it uses one sample to build the tree and another one to estimate treatment effects within that tree.
 \cite{atheygrf} show that their treatment effects are asymptotically normal, which allows us to construct confidence intervals for our treatment estimate in each leaf.
@@
 It shows that more than 70\% of clients experienced financial cost savings in the fee-forcing group compared to the status-quo group.
-Figure \ref{HTE_fee_forcing} in the Appendix displays that the causal cost savings are larger for the more economically vulnerable, %that report at baseline that they have problems paying for services like water, electricity and rent,
-and those displaying overconfidence about recovering their pawn (see Section \ref{behavioral} for our measure of overconfidence).
+The causal cost savings are larger for the more economically vulnerable, %that report at baseline that they have problems paying for services like water, electricity and rent,
+and those displaying overconfidence\footnote{see Section \ref{behavioral} for our measure of overconfidence.} about recovering their pawn, Figure \ref{HTE_fee_forcing}.
 %those that have to incur in higher transport cost to go to the branch  and that asked to be sent reminders to pay, this later one being one proxy of being inattentive or sophisticated present-biased.
@@
 \vspace{.2in}
-\noindent \textbf{Effects on other outcomes.} There are other (intermediate) outcomes that are impacted by being assigned to frequent payments.
+\noindent \textbf{Effects on other outcomes.} There are other intermediate outcomes that are impacted by being assigned to frequent payments.
 Table \ref{mechanisms} shows that the first payment happens 8 days earlier (column 1) in the fee-forcing arm than in the status quo one, and that the number of payments increases by 0.19 (column 2).
-Figure \ref{induced_to_pay_early} in the Appendix correlates heterogeneous treatment effects on financing cost and time of first payment and shows that those induced to pay earlier are also those that have larger induced reduction in financial cost.
+Figure \ref{induced_to_pay_early} in the correlates HTE on financing cost with the HTE time of first payment and shows that those induced to pay earlier are also those that have larger induced reduction in financial cost.
 Treatment effects are concentrated on the intensive margin, as treatment does \textit{not} affect the fraction of clients who pay a positive amount (column 6).
@@
 \vspace{.2in}
-\noindent \textbf{Other sub-samples.}  Results survive if we focus on those that paid a positive amount (in treatment and control) towards loan recovery.\footnote{Although this is potentially a selected subsample, Table \ref{mechanisms} showed that there is no treatment effect the extensive margin, i.e.
-in $pay>0$.} We find that even those that paid a fee in the fee-forcing contract end up paying a smaller financial cost that those in the status-quo contract (Figure \ref{fc_pro2}a).\footnote{This conditions on those that paid a fee in the fee-forcing group, comparing this subset in treatment vs all of the control group.
-Results are similar if we condition in the control group on those who would have paid a fee given current behavior.
+\noindent \textbf{Other sub-samples.}  Results survive if we focus on those that paid a positive amount in treatment and control.\footnote{Although this is potentially a selected subsample, Table \ref{mechanisms} showed that there is no treatment effect the extensive margin, i.e.
+in $pay>0$.} We find that even those that paid a fee in the fee-forcing contract end up paying a smaller financial cost that those in the status-quo contract (Figure \ref{fc_pro2}a).\footnote{This regression conditions on those that paid a fee in the fee-forcing group, and compares this subset in treatment vs all of the control group.
+Results are similar if we condition in the control group on those who would have paid a fee  if they were in the treatment group given their observed payment behavior.
 Again we acknowledge this is an endogenous sample and that the estimate may not be a causal effect.}  Figure \ref{fc_pro2}(d) shows that the increase in pawn recovery is robust to defining recovery using the first 120 days of the contract, or restricting to those paying a positive amount towards pawn recovery.
@@
 
-All clients are more likely to recover their pawn and almost all of them incur in a lower financial cost when assigned to a monthly payment commitment contract.
-This however does not necessarily show that they benefited in utility terms, and this is hard to show directly.
-If ---as suggested by \cite{Laibson2018}--- consumers used ``experienced utility'' as a guide to make future purchases, we conjecture that clients in the fee-forcing contract would be more likely to be repeat costumers vis-a-vis those that got status quo contract.
-This is indeed what we find.
-
-Figure \ref{reincidence} presents results of equation (\ref{basic_reg}) where the dependent variable is a dummy for the client being a repeat costumer.
+Although we have shown that compared to the status quo, being assigned to installment payments reduces financial cost and increases pawn recovery, this does not imply that welfare increases.
+Clients could have disutility from the stress of having monthly installments for instance.
+We don't need to make the strong claim of welfare for the purposes of this paper.
+The financing cost results are striking enough.
+But we conjecture that if clients exposed to the installment contract like it, they will be more likely to come back vis-a-vis those that got status quo contract.\footnote{\cite{Laibson2018} hypothesizes that consumers use ``experienced utility'' as a guide to make future purchases in this way.} This is indeed what we find in the data.
+
+The panel labeled ``Fee-forcing'' in Figure \ref{reincidence} presents results of estimating equation (\ref{basic_reg}) with the dependent variable being a dummy for the client being a repeat costumer.
 We define a client as a repeat costumer if, after experiencing at least 75 days of the respective treatment arm, she came back and pawned a \textit{different} piece.\footnote{Results are robust to using number of days experiencing the contract larger than 75.
-We know it is a different piece from it having a different weight/value.}  The leftmost coefficient shows that the causal effect of the fee-forcing contract on repeat pawning is an increase of 5 percentage points in the probability of being a repeat customer, this is 100\% increase on a mean re-incidence with respect to those that got the status-quo contract.
-This effect is not explained by clients recovering their first pawn with higher probability in the fee-forcing contract and re-pawning this same one since we make sure it is another piece (only 16\% recover their piece in the fist 75 days in the fee forcing contract).
-The second coefficient restricts the sample in the regression to those that had not recovered their pawn in the first 75 days and finds similar results.
-The third coefficient conditions on clients who recovered the pawn in both arms.
-The fourth coefficient focuses on the subsample who had or would have had a financial cost savings treatment effect above the median treatment effect in their first pawn.
-It shows that for these clients the likelihood of coming back is twice as large (although imprecise).
-That is, those that benefit more from the fee-forcing contract are more likely to repeat.\footnote{The second and third estimate must be interpreted with care as we are conditioning on a variable that may be affected by treatment.
+We know it is a different piece from it having a different weight/value.}  The leftmost coefficient shows that the causal effect of the fee-forcing contract on repeat pawning is an increase of 5 percentage points in the probability of being a repeat customer, this is twice the repeat purchasing happening in the status quo group.
+This effect is not explained by clients recovering their first pawn with higher probability in the fee-forcing contract and re-pawning this same one since we make sure it is another piece; besides only 16\% recover their piece in the fist 75 days in the fee forcing contract.
+Experience with the frequent payment contract seems to be necessary as there is no effect of the monthly payment contract on repeat pawning in the first 30 or 60 days of the contract (see Figure \ref{reincidence_before} in the Appendix).
+
+\hl{The second coefficient from the left focuses on the subsample who are predicted would have a treatment effect on financial cost savings above the median} treatment effect in their first pawn.\footnote{Since this is predicted using \cite{atheygrf} based on pre-determined covariates for treatment and control clients it is valid to split the sample this way.} It shows that for these clients the likelihood of coming back is twice as large.
+That is, those that benefit more from the fee-forcing contract are more likely to repeat compare to their control group.
+The remaining coefficients of the ``Fee-forcing'' panel condition on endogenous outcomes and should be interpreted with care.
+The \hl{third} coefficient from the left restricts the sample to those that had not recovered their pawn in the first 75 days in both groups and finds similar results.
+The \hl{fourth} coefficient conditions on clients who recovered their pawn of the experiment, again on in both arms.
+Results from these two endogenous samples are similar to those for the whole sample.
+
+%The fourth coefficient \footnote{The second and third estimate must be interpreted with care as we are conditioning on a variable that may be affected by treatment.
 We view these 2 coefficients as suggestive correlations only.
-The fourth coefficient does not have that problem as it conditions on clients that by their pre-determined covariates are predicted to have above the median treatment effects (in both arms).} Experience with the frequent payment contract seems to be necessary as there is no effect of the monthly payment contract on repeat pawning in the first 30 or 60 days of the contract (see Figure \ref{reincidence_before} in the Appendix).
+The fourth coefficient does not have that problem as it conditions on clients that by their pre-determined covariates are predicted to have above the median treatment effects (in both arms).}
+
 %We also implemented an exit survey which clients filled when recovering their piece.
@@
 Third, it is predictive of take-up in an intuitive way.
-Finally, overconfidence in recovery is implied by present bias with (partial) naivete but also by biased expectations of negative income shocks, thus capturing both kinds of bias.
+Finally, overconfidence in recovery is implied by present bias with (partial) naivete but also by biased expectations of negative income shocks, thus capturing both kinds of bias.\footnote{\textcolor{red}{Another indication of overconfidence is that in our data, of those who renew, 83\% lose the pawn anyway.
+Our measure of overconfidence has a correlation of \hl{xxx}\% with a dummy for renewing and losing the pawn.
+}}
 
@@
 Theory predicts that the more overconfident (naive) may be at the same time those that benefit more from commitment.
-Extrapolating individual treatment effects of the fee-forcing contract vs the status quo one to the choice arm (see below for more detail), and using them as a dependent variable we find that overconfident borrowers benefit \textit{more} from the commitment contract, with \hl{24.8}\% (=\$\hl{30}/\$\hl{121}) more savings (columns 5 and 6).
+Extrapolating individual treatment effects of the fee-forcing contract vs the status quo one to the choice arm (see below for more detail), and using them as a dependent variable we find that overconfident borrowers benefit \textit{more} from the commitment contract, with {24.8}\% (=\${30}/\${121}) more savings (columns 5 and 6).
 Thus while we predict the overconfident benefit more from commitment, they demand less of it.
@@
 In an average loan of 2,000 pesos the monthly payment is close to 700 pesos, and a fee of 2\% of that is 14 pesos (less than \$1 dollar).
-This is about \hlgr{1\%} of monthly per capita income of the first 3 deciles of Mexican \hl{household's} income distribution.
-%This compares favorably to the \hlgr{\$11.6 + \$62.3)} pesos transportation / transaction cost of one.
+This is about gr{1\%} of monthly per capita income of the first 3 deciles of Mexican {household's} income distribution.
+%This compares favorably to the gr{\$11.6 + \$62.3)} pesos transportation / transaction cost of one.
 
@@
 We find this discount rate implausibly high even for this credit constrained population\footnote{For comparison, \cite{Levin} find that a discount rate of 1,415 per year for subprime borrowers in the US is too high to be believable.}, casting doubt on high discount rates as explanation for low demand for commitment.
-%\footnote{In the baseline survey we give respondents a hypothetical choice between $100$ pesos tomorrow or $150$ pesos in one month (an implicit yearly interest rate of \hl{12,800\%}) and only 30\% chose the later one.}
+%\footnote{In the baseline survey we give respondents a hypothetical choice between $100$ pesos tomorrow or $150$ pesos in one month (an implicit yearly interest rate of {12,800\%}) and only 30\% chose the later one.}
 
@@
 Figure \ref{fc_pro4}(b) shows further that the null effect happens for the 15$^{th}$, 25$^{th}$, 50$^{th}$ 75$^{th}$, and 85$^{th}$ percentiles.\footnote{The few clients that selected the fee-commitment contract (the solid black squares) do enjoy cost savings of 1005 MXN, which compares favorably to the 304 MXN in the fee-forcing arm (as a fraction of the loan the numbers are 41.5\% and 12.5\%), but this combines the selection and treatment effects.} %Figure \ref{heterogeneous_te_4} plots the distribution of treatment effects and finds that the distribution offering choice actually \textit{increased} financial cost and default for about half of clients compared to being assigned the status-quo contract.
-Those tended to be the less economically vulnerable and more educated, \hl{women}, and those whose family typically asks them for money.
+Those tended to be the less economically vulnerable and more educated, {women}, and those whose family typically asks them for money.
 Figure \ref{fc_pro4}(c) finds null effects for pawn recovery. Consistent with these findings, Figure \ref{reincidence} finds no effect on repeat purchases for the fee-choice group.
@@
 That is, we introduce a threshold that we vary from 0\% to 15\% of the value of the loan.
-\hl{Second, we take into account uncertainty in estimation of treatment effects and report results using the extremes of the 95\% confidence interval bounds for $\widehat{TE}^{fee}_{i}$.}
+{Second, we take into account uncertainty in estimation of treatment effects and report results using the extremes of the 95\% confidence interval bounds for $\widehat{TE}^{fee}_{i}$.}
 
@@
 %(90\% confidence interval [45,94]).
-Most mistakes are failures to choose the fee-commitment contract (\hl{85}\%), while only \hl{15}\% of those who chose the fee-commitment contract would have been better in the status-quo one.
+Most mistakes are failures to choose the fee-commitment contract ({85}\%), while only {15}\% of those who chose the fee-commitment contract would have been better in the status-quo one.
 The average mistake in pesos is \$250.
@@
 Figure \ref{choose_wrong}(b) plots the same curve, but separately for overconfident and non-overconfident clients, using the definition of overconfidence in Section \ref{behavioral}.
-\hl{It shows that there are about 11 percentage points more mistakes in the overconfident population (when $z=0$), an important difference.}
+{It shows that there are about 11 percentage points more mistakes in the overconfident population (when $z=0$), an important difference.}
 
@@
 Forcing them into the fee-commitment contract increases welfare only if they themselves would chose it.
-(c) Forcing can be welfare improving for the naive under some parameter values (see Appendix \ref{appendix_c}).
+(c) Forcing can be welfare improving for the naive under some parameter values (see \ref{appendix_c}).
 
@@
 We find that experience does not predict positive take up in our sample correlationally.} To test it we would ideally need to give choice to a group of people that randomly experienced the fee-commitment vs those that did not, and test if the former demand it more.
-Unfortunately we did not do this experiment and we have very limited data to try it: \hl{210 (6\%)} clients were given a choice in a second pawns in our experiment after being randomly assigned to the status quo or fee-forcing contract.
+Unfortunately we did not do this experiment and we have very limited data to try it: {210 (6\%)} clients were given a choice in a second pawns in our experiment after being randomly assigned to the status quo or fee-forcing contract.
 %\end{comment}
@@
 \noindent \textbf{Demand}.
-It turns out that the demand for the promise-commitment contract  is higher than for the fee-commitment contract by a factor of 3: \hl{31}\% of clients offered a choice between the status quo contract and the promise-commitment contract chose commitment.
+It turns out that the demand for the promise-commitment contract  is higher than for the fee-commitment contract by a factor of 3: {31}\% of clients offered a choice between the status quo contract and the promise-commitment contract chose commitment.
 This means that the pecuniary fee indeed limited demand for commitment.
@@
 \vspace{.2in}
-\noindent The evidence presented in this section contrasts sharply with the evidence in laboratory experiments where people choosing to promise has a large effects on behavior, and wHere people keep their promises.
+\noindent The evidence presented in this section contrasts sharply with the evidence in laboratory experiments where people choosing to promise has a large effects on behavior, and where people keep their promises.
 While clients are more enthusiastic about the promise-commitment contract than the fee-commitment one in the sense of tripling take-up, the promise contract provides no commitment.
@@
 When $z=0$, we calculate that about 60\% of clients in the promise-choice group chose contracts that induced \textit{higher} financial cost.
-In particular \hlgr{97\%} of those that chose the status-quo contract would have been better in the promise-commitment contract, while \hlgr{3\%} of those who chose the promise-commitment contract would have been better in the status-quo one.
+In particular gr{97\%} of those that chose the status-quo contract would have been better in the promise-commitment contract, while gr{3\%} of those who chose the promise-commitment contract would have been better in the status-quo one.
 On average they spend \$250 pesos on extra financing cost.
@@
 subjective well being and consumption-- would help to make broader claims about welfare than we can make in this paper.
-Finally, one would like to know which interventions could debias consumers, or whether learning alone would do the work.
+Finally, one would like to know which interventions could de-bias consumers, or whether learning alone would do the work.
 
@@
     \end{center}
-         \scriptsize Panel (a) displays in black arrows the period covered by our administrative data: from August 6th 2012 (30 days before the experiment began) to August 13th 2013.
+         \scriptsize Panel (a) displays in black arrows the period covered by our administrative data: from August 6th 2012 (30 days before the experiment began : pre-experiment period) to August 13th 2013.
 The gray lines correspond to the dates of implementation of the experiment.
@@
       \includegraphics[width=\textwidth]{Figuras/hist_fc_perc_loan.pdf}
+    \end{subfigure}
+     \begin{subfigure}{0.45\textwidth}
+    \caption{Effective cost-loan ratio}
+       \centering
+      \includegraphics[width=\textwidth]{Figuras/hist_eff.pdf}
     \end{subfigure}
@@
 %Given that the loan lasts close to 90 days, bringing payments to present value makes little difference.
-      %\footnotesize{ } \textit{Do file: }  \texttt{hist\_fc.do}
+      %\footnotesize{ } \textit{Do file: }  \texttt{hist\_eff.do}
 \end{figure}
@@
 That is likelihood of doing an additional pawn (in treatment vs control) after having been subjected to treatment for at least 75 days.
-The second coefficient estimates the regression conditional on recovering the pawn \hl{in both treatment and control}, and the rightmost coefficient compares those above the median treatment effect in financial cost savings, \hl{versus all the control group.}
+The second coefficient estimates the regression conditional on recovering the pawn {in both treatment and control}, and the rightmost coefficient compares those above the median treatment effect in financial cost savings, {versus all the control group.}
 }
+
+\begin{figure}[H]
+    \caption{The effect of the fee-forcing treatment}
+    \label{fc_pro2}
+    \begin{center}
+    \begin{subfigure}{0.42\textwidth}
+        \caption{Effective cost/loan ratio}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/eff_te_pro_2.pdf}
+    \end{subfigure}
+        \begin{subfigure}{0.42\textwidth}
+        \caption{Financial cost (quantile reg)}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/eff_quantile_pro_2.pdf}
+    \end{subfigure}
+
+        \bigskip
+
+     \begin{subfigure}{0.42\textwidth}
+         \caption{Financial cost (HTE)}
+         \centering
+         \includegraphics[width=\textwidth]{Figuras/he_dist_eff_cost_loan_pro_2.pdf}
+     \end{subfigure}
+    ~
+    ~
+    \bigskip
+    \begin{subfigure}{0.42\textwidth}
+        \caption{Lost pawn}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/def_te_pro_2.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.42\textwidth}
+    \caption{Losing Pawn}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_2.pdf}
+    \end{subfigure}
+
+    \end{center}
+        \scriptsize
+
+      %\textit{Do file: }  \texttt{eff\_te.do, def\_te.do, eff\_quantilereg.do}
+\end{figure}
 
@@
 \begin{figure}[H]
-        \caption{FC as \% of loan - treatment effect}
+        \caption{FC conditional on first 115 days - treatment effect}
     \label{fc_pro_2_115}
@@
 \end{center}
- \footnotesize
+ \scriptsize
 This table does two things.
@@
 \subsection{New results}
+
+\begin{table}[H]
+\caption{Summary statistics and Balance}
+\label{SS}
+\begin{center}
+\scriptsize{\input{./Tables/SS_appendix.tex}}
+\end{center}
+ \scriptsize
+
+%\textit{Do file: } \texttt{SS\_appendix.do}
+\end{table}
+
 \begin{figure}[H]
@@
 Some branches also stopped offering the frequent payment contracts.
-Out of all branches 2\% never offered the FP contract, 29\% always offered it, while 69\% offered for only part of our sample period.
+Out of all branches only 2\% never offered the FP contract, and the rest offered it for only part of our sample period.
 Our identification strategy will mostly rely on these later group, as we include branch fixed effects in our regressions.
@@
 The $R^2$ shows that the \textit{additional} variance explained by the covariates beyond branch and calendar week fixed effects is low: going from 0.154 to 0.157 when we add all regressors.
-The $AUC$ and the \textit{Accuracy Rate} give a similar picture, with out-of-sample $AUC$ around 0.72 and Accuracy rates around 66\%.\footnote{\cite{Finanzia} say that for predicting loan default for instance AUC's from 0.80 to 0.95 are common.} \\ %\hl{Appraisers could potentially have an effect on what contract people choose conditional on the contract existing in the system.
+The $AUC$ and the \textit{Accuracy Rate} give a similar picture, with out-of-sample $AUC$ around 0.72 and Accuracy rates around 66\%.\footnote{\cite{Finanzia} say that for predicting loan default for instance AUC's from 0.80 to 0.95 are common.} \\ %{Appraisers could potentially have an effect on what contract people choose conditional on the contract existing in the system.
 We test for this and find XXX...}
@@
 
-% Table \hl{XXX} has the same structure as Table  \hl{XXX} above.
+% Table {XXX} has the same structure as Table  {XXX} above.
 It finds that the experimental result is qualitatively replicated with this different sample and different identification strategy.
-Having had a previous FP loan induced by its availability is associated with an increase of \hl{XXX} in the probability of pawning again \hl{in the next 3 months}.
+Having had a previous FP loan induced by its availability is associated with an increase of {XXX} in the probability of pawning again {in the next 3 months}.
 
@@
 
-% Using the individual fixed effects specification, as well as the instrumental variable strategy defined above, Table \hl{XXX} finds that FP are \hl{XX\%} more likely to recover their pawns.
+% Using the individual fixed effects specification, as well as the instrumental variable strategy defined above, Table {XXX} finds that FP are {XX\%} more likely to recover their pawns.
 
@@
 If in addition if it was the case that $\beta_i<\beta_{SQ}$.
-%\footnote{\hl{Isaac, aqui tengo dos pregutas: (1) si es $\beta$ y no $\hat{\beta}$ verdad?
+%\footnote{{Isaac, aqui tengo dos pregutas: (1) si es $\beta$ y no $\hat{\beta}$ verdad?
 (2) Para que una persona naive empenie en el status quo tiene que ser que cree que va a recuperar no?

### 2021-09-10 old.tex
Redefine definition of financial cost as effective cost/loan ratio
Former-commit-id: 6ca64d61c64e073a31eb2db5a471af41f2c3e9a6

--- 2021-03-09 main.tex
@@
 In the context of pawnbroker lending, we show that forcing people into commitment contracts with financial penalties for not paying on time \textit{decreases} their (fee-including) financial cost by 9.4\%, increases the likelihood of recovering their pawn by 26\%, and increases the likelihood of repeat business by almost 100\%.
-Using machine learning methods for estimating heterogeneous treatment effects, we find that more than \hl{90}\% clients would reduce their financing cost with the commitment contract, however only 10\% choose it.
+Using machine learning methods for estimating heterogeneous treatment effects, we find that more than 90 clients would reduce their financing cost with the commitment contract, however only 10\% choose it.
 Relying on personal promises instead of fees as commitment triples take-up but has no effects on outcomes.

### 2021-09-10 RScripts/eff_te_grf.R

@@ -1,0 +1,86 @@
+library(tidyverse)
+library(grf)
+library(ggplot2)
+
+# SET WORKING DIRECTORY
+setwd('C:/Users/isaac/Dropbox/Apps/ShareLaTeX/Donde2020')
+#setwd("C:\\Users\\Ricardo\\Documents\\SEIRA\\donde2019")
+set.seed(5289374)
+
+
+
+data_in <- read_csv('./_aux/eff_te_heterogeneity.csv')
+
+
+require("dplyr")
+
+data_train <- data_in %>% 
+  filter(insample == 1) 
+data_train_fee <- subset(data_train, data_train$fee_arms == 1)
+data_train_nofee <- subset(data_train, data_train$fee_arms == 0)
+
+
+data_test <- data_in %>% 
+  select(-c(eff_cost_loan, fee_arms, prenda, insample))
+data_test_tau <- data_in %>% 
+  select(-c(eff_cost_loan, prenda, insample))
+
+###################################################################  
+###################################################################  
+
+
+# PREPARE VARIABLES
+X <- select(data_train,-c(eff_cost_loan, fee_arms, prenda, insample))
+Y <- select(data_train,eff_cost_loan)
+W <- as.numeric(data_train$fee_arms == 1)
+
+X_full <- select(data_in,-c(eff_cost_loan, fee_arms, prenda, insample))
+Y_full <- select(data_in,eff_cost_loan)
+W_full <- as.numeric(data_in$fee_arms == 1)
+
+X_fee <- select(data_train_fee,-c(eff_cost_loan, fee_arms, prenda, insample))
+Y_fee <- as.numeric(data_train_fee$eff_cost_loan)
+X_nofee <- select(data_train_nofee,-c(eff_cost_loan, fee_arms, prenda, insample))
+Y_nofee <- as.numeric(data_train_nofee$eff_cost_loan)
+
+###################################################################  
+###################################################################  
+
+
+# ESTIMATE MODEL
+
+# Causal Forest
+tau.forest = causal_forest(
+  X = model.matrix(~., data = X), 
+  Y = data.matrix(Y), 
+  W = W,
+  honesty = TRUE)
+
+tau.forest.full = causal_forest(
+  X = model.matrix(~., data = X_full), 
+  Y = data.matrix(Y_full), 
+  W = W_full,
+  honesty = TRUE)  
+# Regression forest
+pred.forest.fee = regression_forest(X_fee, Y_fee)
[…]

### 2021-09-10 RScripts/grf.R

@@ -13,68 +13,68 @@ source("./RScripts/best_tree.R")
 
 heterogeneity_effect <- function(data_in,treatment_var,outcome_var,writedata,extendedsample) {
   
-require("dplyr")
-data_frame <- data_in %>%
-  filter(data_in[,treatment_var] == 1 | data_in[,treatment_var] == 0) %>%
-  select(-c( pro_2, pro_3, pro_4, pro_5, pro_6, pro_7, pro_8, pro_9, fee, fecha_inicial,
-             def_c, fc_admin_disc, fc_survey_disc, fc_admin, fc_survey, dias_primer_pago), 
-         treatment_var, outcome_var ) %>%
-  drop_na()  
-
-
-# PREPARE VARIABLES
-X <- select(data_frame,-c(outcome_var, treatment_var,NombrePignorante, prenda))
-Y <- select(data_frame,outcome_var)
-W <- as.numeric(data_frame[,treatment_var] == 1)
-
-# ESTIMATE MODEL
-tau.forest = causal_forest(
-  X = model.matrix(~., data = X), 
-  Y = data.matrix(Y), 
-  W = W,
-  honesty = TRUE)
-
-if (writedata == 0) {
-  # BEST TREE
-  best_tree_info <- find_best_tree(tau.forest, "causal")
-}
-
-# OVERLAP ASSUMPTION
-propensity.forest = regression_forest(X, W)
-propensity_score = predict(propensity.forest)$predictions
-hist(propensity_score, xlab = "propensity score")
-
-# Estimate treatment effects for the training data using out-of-bag prediction.
-tau_hat_oob = predict(tau.forest, estimate.variance = TRUE)
-hist(tau_hat_oob$predictions)
-
-# Estimate the conditional average treatment effect on the full sample (CATE).
-print(average_treatment_effect(tau.forest, target.sample = "all"))
-
-# Estimate the conditional average treatment effect on the treated sample (CATT).
-# Here, we don't expect much difference between the CATE and the CATT, since
-# treatment assignment was randomized.
-print(average_treatment_effect(tau.forest, target.sample = "treated"))
-
-#The (conditional) average treatment effect on the controls 
-print(average_treatment_effect(tau.forest, target.sample = "control"))
-
-#Write data
-if (writedata == 1) {
[…]

### 2021-09-10 RScripts/pfv_pred.R

@@ -1,10 +1,10 @@
 library(tidyverse)
 library(grf)
 library(ggplot2)
-library(DMwR)
+
 
 # SET WORKING DIRECTORY
-setwd('C:/Users/xps-seira/Dropbox/Apps/ShareLaTeX/Donde2020')
+setwd('C:/Users/isaac/Dropbox/Apps/ShareLaTeX/Donde2020')
 set.seed(5289374)
 
 
@@ -45,63 +45,18 @@ rf_predict <- function(data_in,take.up) {
 # Prenda level
 data_pfv_fee <- read_csv('./_aux/data_pfv_test_pago_frec_vol_fee.csv')
 
-# data_train <- data_pfv_fee %>% 
-#   filter(insample == 1) %>%
-#   as.data.frame() %>%
-#   mutate(pago_frec_vol_fee = as.factor(pago_frec_vol_fee)) 
-# data_test <- data_pfv_fee %>% 
-#   filter(insample == 0)  %>%
-#   as.data.frame() %>%
-#   mutate(pago_frec_vol_fee = as.factor(pago_frec_vol_fee)) 
-# 
-# ## Using SMOTE to create a more "balanced problem"
-# data.smoted <- SMOTE(pago_frec_vol_fee ~ .-nombrepignorante -prenda -insample,
-#                      data_train, k = 2, perc.over = 300, perc.under=200)
-# 
-# data_pfv_fee <- rbind(data.smoted, data_test)
-# write_csv(data_pfv_fee,"_aux/data_pfv_test_smoted_pago_frec_vol_fee.csv")
 
 #################################################################################
 
 # READ DATASET
 data_pfv_promise <- read_csv('./_aux/data_pfv_test_pago_frec_vol_promise.csv')
 
-# data_train <- data_pfv_promise %>% 
-#   filter(insample == 1) %>%
-#   as.data.frame() %>%
-#   mutate(pago_frec_vol_promise = as.factor(pago_frec_vol_promise)) 
-# data_test <- data_pfv_promise %>% 
-#   filter(insample == 0)  %>%
-#   as.data.frame() %>%
-#   mutate(pago_frec_vol_promise = as.factor(pago_frec_vol_promise)) 
-# 
-# ## Using SMOTE to create a more "balanced problem"
-# data.smoted <- SMOTE(pago_frec_vol_promise ~ .-nombrepignorante-prenda-insample,
[…]

### 2021-09-10 RScripts/pfv_pred_hte.R

@@ -3,7 +3,7 @@ library(grf)
 library(ggplot2)
 
 # SET WORKING DIRECTORY
-setwd('C:/Users/xps-seira/Dropbox/Apps/ShareLaTeX/Donde2020')
+setwd('C:/Users/isaac/Dropbox/Apps/ShareLaTeX/Donde2020')
 set.seed(5289374)
 options(digits=18)
 
@@ -42,7 +42,7 @@ rf_predict <- function(data_in,take.up,nme) {
 #RF Predictions of no-choice arm
 for (arm in c("pro_2")) {
   for (pred in c("pago_frec_vol_fee")) {
-    for (effect in c("def_c", "fc_admin_disc")) {
+    for (effect in c("def_c")) {
       filename <- paste("_aux/",arm,"_",pred,"_",effect,".csv", sep="")
       data <- read_csv(filename)
       outname <- paste(arm,"_",pred,"_",effect,sep="")

### 2021-09-19 RScripts/des_te_grf.R
decomposition of mistakes for eff cost-loan & revert
Former-commit-id: 72bb2640dd188d84486f1b88b4697f81604b5b0c

@@ -9,7 +9,7 @@ set.seed(5289374)
 
 
 
-data_in <- read_csv('./_aux/eff_te_heterogeneity.csv')
+data_in <- read_csv('./_aux/des_te_heterogeneity.csv')
 
 
 require("dplyr")
@@ -21,25 +21,25 @@ data_train_nofee <- subset(data_train, data_train$fee_arms == 0)
 
 
 data_test <- data_in %>% 
-  select(-c(eff_cost_loan, fee_arms, prenda, insample))
+  select(-c(des_c, fee_arms, prenda, insample))
 
 ###################################################################  
 ###################################################################  
 
 
 # PREPARE VARIABLES
-X <- select(data_train,-c(eff_cost_loan, fee_arms, prenda, insample))
-Y <- select(data_train,eff_cost_loan)
+X <- select(data_train,-c(des_c, fee_arms, prenda, insample))
+Y <- select(data_train,des_c)
 W <- as.numeric(data_train$fee_arms == 1)
 
-X_full <- select(data_in,-c(eff_cost_loan, fee_arms, prenda, insample))
-Y_full <- select(data_in,eff_cost_loan)
+X_full <- select(data_in,-c(des_c, fee_arms, prenda, insample))
+Y_full <- select(data_in,des_c)
 W_full <- as.numeric(data_in$fee_arms == 1)
 
-X_fee <- select(data_train_fee,-c(eff_cost_loan, fee_arms, prenda, insample))
-Y_fee <- as.numeric(data_train_fee$eff_cost_loan)
-X_nofee <- select(data_train_nofee,-c(eff_cost_loan, fee_arms, prenda, insample))
-Y_nofee <- as.numeric(data_train_nofee$eff_cost_loan)
+X_fee <- select(data_train_fee,-c(des_c, fee_arms, prenda, insample))
+Y_fee <- as.numeric(data_train_fee$des_c)
+X_nofee <- select(data_train_nofee,-c(des_c, fee_arms, prenda, insample))
+Y_nofee <- as.numeric(data_train_nofee$des_c)
 
 ###################################################################  
 ###################################################################  
@@ -78,7 +78,5 @@ hist(rf_pred_nofee)
 data.out <- add_column(data_in, rf_pred_fee, rf_pred_nofee, 
                        tau_hat_oob$predictions, tau_hat_oob$variance.estimates,
[…]

### 2021-09-19 RScripts/fc_te_grf.R

@@ -22,8 +22,6 @@ set.seed(5289374)
   
   data_test <- data_in %>% 
     select(-c(fc_admin_disc, fee_arms, prenda, insample))
-  data_test_tau <- data_in %>% 
-    select(-c(fc_admin_disc, prenda, insample))
   
   ###################################################################  
   ###################################################################  
@@ -66,7 +64,7 @@ set.seed(5289374)
   pred.forest.nofee = regression_forest(X_nofee, Y_nofee)
 
   # Estimate treatment effects for the training data using out-of-bag prediction.
-  tau_hat_oob = predict(tau.forest, data_test_tau, estimate.variance = TRUE)
+  tau_hat_oob = predict(tau.forest, model.matrix(~., data = data_test), estimate.variance = TRUE)
   hist(tau_hat_oob$predictions)
   tau_hat_oob_full = predict(tau.forest.full, estimate.variance = TRUE)
   hist(tau_hat_oob_full$predictions)

### 2021-09-19 RScripts/sumporcp_te_grf.R

@@ -9,7 +9,7 @@ set.seed(5289374)
 
 
 
-data_in <- read_csv('./_aux/eff_te_heterogeneity.csv')
+data_in <- read_csv('./_aux/sumporcp_te_heterogeneity.csv')
 
 
 require("dplyr")
@@ -21,25 +21,25 @@ data_train_nofee <- subset(data_train, data_train$fee_arms == 0)
 
 
 data_test <- data_in %>% 
-  select(-c(eff_cost_loan, fee_arms, prenda, insample))
+  select(-c(sum_porcp_c, fee_arms, prenda, insample))
 
 ###################################################################  
 ###################################################################  
 
 
 # PREPARE VARIABLES
-X <- select(data_train,-c(eff_cost_loan, fee_arms, prenda, insample))
-Y <- select(data_train,eff_cost_loan)
+X <- select(data_train,-c(sum_porcp_c, fee_arms, prenda, insample))
+Y <- select(data_train,sum_porcp_c)
 W <- as.numeric(data_train$fee_arms == 1)
 
-X_full <- select(data_in,-c(eff_cost_loan, fee_arms, prenda, insample))
-Y_full <- select(data_in,eff_cost_loan)
+X_full <- select(data_in,-c(sum_porcp_c, fee_arms, prenda, insample))
+Y_full <- select(data_in,sum_porcp_c)
 W_full <- as.numeric(data_in$fee_arms == 1)
 
-X_fee <- select(data_train_fee,-c(eff_cost_loan, fee_arms, prenda, insample))
-Y_fee <- as.numeric(data_train_fee$eff_cost_loan)
-X_nofee <- select(data_train_nofee,-c(eff_cost_loan, fee_arms, prenda, insample))
-Y_nofee <- as.numeric(data_train_nofee$eff_cost_loan)
+X_fee <- select(data_train_fee,-c(sum_porcp_c, fee_arms, prenda, insample))
+Y_fee <- as.numeric(data_train_fee$sum_porcp_c)
+X_nofee <- select(data_train_nofee,-c(sum_porcp_c, fee_arms, prenda, insample))
+Y_nofee <- as.numeric(data_train_nofee$sum_porcp_c)
 
 ###################################################################  
 ###################################################################  
@@ -78,7 +78,5 @@ hist(rf_pred_nofee)
 data.out <- add_column(data_in, rf_pred_fee, rf_pred_nofee, 
[…]

### 2021-09-19 donde.tex
modification figure effect_contr_trakeup
Former-commit-id: de9c9ab193f7b524ead4995f4b70df412208be4b

@@
         \centering
-        \includegraphics[width=\textwidth]{Figuras/line_cw_fc_te_cf.pdf}
+        \includegraphics[width=\textwidth]{Figuras/line_cw_eff_te_cf.pdf}
 
@@
         \centering
-        \includegraphics[width=\textwidth]{Figuras/line_cw_fc_te_cf_OC_fee.pdf}
+        \includegraphics[width=\textwidth]{Figuras/line_cw_eff_te_cf_OC_fee.pdf}
 
@@
         \centering
-        \includegraphics[width=\textwidth]{Figuras/line_better_forceall_fc_te_cf.pdf}
+        \includegraphics[width=\textwidth]{Figuras/line_better_forceall_eff_te_cf.pdf}
 

### 2021-10-22 choice_benefit.tex
benefit_vs_choice analysis & corrections in causal forests
Former-commit-id: a94e41dada3d0ce771362fc224735b66a8842aa5

 \documentclass[oneside,11pt]{article}

\input{preamble.tex}
%%% HELPER CODE FOR DEALING WITH EXTERNAL REFERENCES
\usepackage{xr}
\makeatletter
\newcommand*{\addFileDependency}[1]{
  \typeout{(#1)}
  \@addtofilelist{#1}
  \IfFileExists{#1}{}{\typeout{No file #1.}}
}
\makeatother

\newcommand*{\myexternaldocument}[1]{
    \externaldocument{#1}
    \addFileDependency{#1.tex}
    \addFileDependency{#1.aux}
}

%\myexternaldocument{OA}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% DOCUMENT
\begin{document}

We investigate the relation between choice (commitment) and benefit. First, we compute the Treatment Effect benefit in the control vs fee arm. Then, we calculate a propensity to choose commitment, and analyze the correlation between this two variables.

\begin{figure}[H]
    \caption{}
    \label{}
    \begin{center}
    %\begin{subfigure}{0.4\textwidth}
    %    \caption{Financial cost}
    %    \centering
    %    \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_2.pdf}
    %\end{subfigure}
    \begin{subfigure}{0.475\textwidth}
        \caption{Effective cost/loan benefit}
        \centering
        \includegraphics[width=\textwidth]{Figuras/benefit_choice.pdf}
    \end{subfigure}
    \begin{subfigure}{0.475\textwidth}
        \caption{Repayment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/benefit_choice_des.pdf}
    \end{subfigure}

    \end{center}
     \scriptsize    Binscatter of propensity to choose commitment vs treatment effect of frequent payments.
          %\footnotesize{ \textit{Do file: }  \texttt{benefit\_choice.do}}
\end{figure}

We estimate demand for commitment with a Gradient Boosted Classification algorithm (accuracy 97\% in-sample and 90\% out-of-sample).

Now we want to identify who are the ones who benefit more from being forced, and those who would demand commitment.

\begin{figure}[H]
    \caption{}
    \label{}
    \begin{center}
    %\begin{subfigure}{0.4\textwidth}
    %    \caption{Financial cost}
    %    \centering
    %    \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_2.pdf}
    %\end{subfigure}
    \begin{subfigure}{0.475\textwidth}
        \caption{Determinants of HTE}
        \centering
        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_eff_cost_loan_pro_2.pdf}
    \end{subfigure}
    \begin{subfigure}{0.475\textwidth}
        \caption{Determinants of PS}
        \centering
        \includegraphics[width=\textwidth]{Figuras/HE/ps_int_vertical_pr_gbc_1.pdf}
    \end{subfigure}

    \end{center}
     \scriptsize  (a): This figure estimates bivariate regressions of the estimated client-level heterogeneous treatment effects against the respective covariate from the baseline survey  $\widehat{hte_i} = \alpha + \beta \: X_i + \epsilon_i$. The regressors $X_i$ include (e.g if the family asks for money, if they have savings, if they are overconfident using the definition the text, etc. See this Appendix for a transcription of the survey). \\
     (b) :  
      %\footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}} \texttt{benefit\_choice.do}}
\end{figure}

\subsection{Are the people who benefit most from commitment, the ones who demand it?}

We estimate the following model

We would like to make a distinction of the people that benefit most from being forced. Our conjecture is that this are the naive individuals.

We assume the following structural model.

Each individual $i$ is of type  $k\in\{1, 2\}$ with probability $\alpha_{i,k}$. We assume it follows a logit distribution:
\begin{align*}
\label{dist_alpha}
    \alpha_{i,k} = \Pr(\text{Type}_i = k \;|\; \mathbf{W}_{i}) = \frac{e^{\gamma_{k}\mathbf{W}_i}}{\sum_{j=1}^{K} e^{\gamma_{j}\mathbf{W}_i}}
\end{align*}

where $\mathbf{W}_i$ are observable characteristics. This characteristics include choice for commitment, present bias, subjective probability of recovery, etc, which might be indicators of naivete vs sophistication.

Now, given their type, each individual makes a choice to default or not $c_{i,k} \in \{1,2\}$, based on other set of observable characteristics $\mathbf{X}_i$ (subjective \& objective value of the loan). We will assume there is a continuous latent variable $Y_{i,k,c}$ distributed as
\[Y_{i,k,c} = \beta_{c,k}\mathbf{X}_{i} +\epsilon_{c,k}\]
with\footnote{We can impose other errors, and even impose a covariance structure, for instance if $(\epsilon_{c,k})_{c}\sim\mathcal{N}(0,\Sigma_k)$, we arrive to the Multinomial Probit.} $\epsilon_{c;k}\sim\operatorname{EV}(0,1)$. This latent variable can be thought of as the utility associated with individual $i$, being type $k$, making choice $c$.

Thus, the density for each individual $i$ being type $k$ is
\[f(c_i,\mathbf{X}_i; \bm\beta_{k}) = \prod_{c=1}^4\left(\frac{e^{\beta_{c,k} \mathbf{X}_i}}{\sum_{j=1}^{4} e^{\beta_{j,k}  \mathbf{X}_i}}\right)^{[c_i=4]}\]

Finally, the generative model is then a mixture model with density given by,
\begin{align*}
    f(c_i ,\mathbf{W}_i, \mathbf{X}_i; \bm{\gamma},\bm{\beta}) &= \sum_{k=1}^K \alpha_k f(c_i,\mathbf{X}_i; \bm\beta_{k}) \\
    &= \sum_{k=1}^K \alpha_k \prod_{c=1}^4\left(\frac{e^{\beta_{c,k} \mathbf{X}_i}}{\sum_{j=1}^{4} e^{\beta_{j,k}  \mathbf{X}_i}}\right)^{[c_i=c]} 
\end{align*}

where $\alpha\sim \operatorname{Categorical}$, and $\gamma_{K} = \beta_{4,k}=0$ for identification purposes.

Then the (incomplete) log-likelihood function is
\begin{align*}
    \ell(\bm{\gamma}, \bm{\beta}; c, \mathbf{W},  \mathbf{X}) = \sum_{i=1}^n \log\sum_{k=1}^K \alpha_k \prod_{c=1}^4\left(\frac{e^{\beta_{c,k} \mathbf{X}_i}}{\sum_{j=1}^{4} e^{\beta_{j,k}  \mathbf{X}_i}}\right)^{[c_i=c]} 
\end{align*}

, thus we estimate parameters $(\bm{\gamma}, \bm{\beta})$ with an EM algorithm using choice (default)
\& observable characteristics: $(c_i,\mathbf{W}_i,\mathbf{X}_i)$.

The results are the following:

\begin{table}[H]
\caption{FMM}
\label{iv_pf}
\begin{center}
\scriptsize{\input{./Tables/fmm_types.tex}}
\end{center}
 \scriptsize

%\textit{Do file: } \texttt{fmm.do}
\end{table}

The class (type) which is positively correlated with demand for commitment might be identified with the \emph{sophisticated} individuals (Type 2). The hypothesis is that this class is the less benefit from being forced, and so (Type 1) individuals are the most benefited from being forced.

\begin{figure}[H]
    \caption{Probability of being Type 1 vs HTE}
    \label{}
    \begin{center}
    \begin{subfigure}{0.475\textwidth}
        \caption{Prior Probability}
        \centering
        \includegraphics[width=\textwidth]{Figuras/binscatter_tau_classpr.pdf}
    \end{subfigure}
    \begin{subfigure}{0.475\textwidth}
        \caption{Posterior Probability}
        \centering
        \includegraphics[width=\textwidth]{Figuras/binscatter_tau_classpost.pdf}
    \end{subfigure}

    \end{center}
     \scriptsize 
      %\footnotesize{ \textit{Do file: }  \texttt{fmm.do}} 
\end{figure}

A negative relation indicates that being Type 1 has more benefits from being forced.

\begin{figure}[H]
    \caption{Type 1 class vs HTE}
    \label{}
    \begin{center}
    \begin{subfigure}{0.475\textwidth}
        \caption{Prior Probability}
        \centering
        \includegraphics[width=\textwidth]{Figuras/benefit_type1.pdf}
    \end{subfigure}
    \begin{subfigure}{0.475\textwidth}
        \caption{Posterior Probability}
        \centering
        \includegraphics[width=\textwidth]{Figuras/benefit_type1p.pdf}
    \end{subfigure}

    \end{center}
     \scriptsize 
      %\footnotesize{ \textit{Do file: }  \texttt{fmm.do}} 
\end{figure}

Moreover we find a strong correlation between the Type 1 individuals and the individuals that ``choose wrong" according to Figure 8 \ref{choose_wrong}.\\

\emph{This exercise is stronger in the sense that when we divide by type, choice is the core divider.} This emphasizes how important choice is as a segregator.

\subsection{Observational Study}

Paternalism  with learning : We generate more learning through forcing than through choice.

It is possible that the wrong people choose and they learn not through choosing, but rather through not choosing (and it did not work). We then partition our sample in the observational study, based on whether you committed the first time, and we want to show that learning happened in the "wrong group" : not choosers.

We want to show that the TE is localized within one of the groups in that endogenous split.

We then estimate the following two-stage specification.

\begin{equation}
    \mathbbm{1}(\text{Had FP})_{ijt} = \alpha_i + \gamma_t + \beta \mathbbm{1}(\text{FP Avail})_{ijt}  + \epsilon_{ijt}
    \label{eqn:fs}
\end{equation}

\begin{equation}
    \mathbbm{1}(\text{Has FP})_{ijt} = \widehat{\alpha_i }+ \widehat{\gamma_t} + \widehat{\beta }(\widehat{\text{Had FP }})_{ijt}  + \epsilon_{ijt}
    \label{eqn:2s}
\end{equation}

where $i,j,t$ index client, branch, and week respectively. $\mathbbm{1}(\text{Has FP})_{ijt}$ is an indicator for client $i$ pawning in branch $j$ in week $t$ using a FP contract, given that both FP and traditional contracts were available at the branch at the time of pawning, so that there is a choice to be made among these. We instrument $\mathbbm{1}(\text{Had FP previously})_{ijt}$ with the \textit{availability} of the contract in branch $j$  when the client previously went to pawn the immediately prior pawn with respect to $t$, $\mathbbm{1}(\text{FP Avail})_{ijt}$. However, the second stage only uses the subsample of the not choosers.

\begin{table}[H]
\caption{Outcome in 2S : Choose FP contract}
\label{iv_pf}
\begin{center}
\scriptsize{\input{./Tables/iv_reg_demand_pf_notchoosing.tex}}
\end{center}
 \scriptsize

%\textit{Do file: } \texttt{iv\_reg\_demand\_pf\_notchoosing.do}
\end{table}

Thus the learning mechanism is due to the not choosers having failed.

\begin{table}[H]
\caption{Outcome in 2S : Default}
\label{iv_def}
\begin{center}
\scriptsize{\input{./Tables/iv_reg_def_notchoosing.tex}}
\end{center}
 \scriptsize

%\textit{Do file: } \texttt{iv\_reg\_demand\_pf\_notchoosing.do}
\end{table}

\begin{table}[H]
\caption{Outcome in 2S : Default}
\label{iv_def_decomp}
\begin{center}
\scriptsize{\input{./Tables/iv_reg_def_nc_nr.tex}}
\end{center}
 \scriptsize

%\textit{Do file: } \texttt{iv\_reg\_demand\_pf\_notchoosing.do}
\end{table}

\section{LATE}

\begin{table}[H]
\caption{}
\label{tot_tut}
\begin{center}
\scriptsize{\input{./Tables/tot_tut_iv.tex}}
\end{center}
 \scriptsize
%\textit{Do file: } \texttt{tot\_tut.do}
\end{table}

\begin{figure}[H]
     \caption{TOT-TUT Histogram}
    \label{}
    \begin{center}
    \begin{subfigure}{0.75\textwidth}
        \centering
        \includegraphics[width=\textwidth]{Figuras/dif_tot_tut.pdf}
    \end{subfigure}
    \end{center}
    \scriptsize
        Histogram for the difference of the conditional (heterogeneous) TOT-TUT
          %\footnotesize{ \textit{Do file: }  \texttt{tot\_tut\_insforest.do}}
\end{figure}

\begin{figure}[H]
     \caption{TOT-TUT CDF}
    \label{ExplanatoryMaterial}
    \begin{center}
    \begin{subfigure}{0.75\textwidth}
        \centering
        \includegraphics[width=\textwidth]{Figuras/cdf_tot_tut.pdf}
    \end{subfigure}
    \end{center}
    \scriptsize
        ECDF of the conditional (heterogeneous) TOT \& TUT, alogn with the difference and a test for the difference in means (which is significant).
          %\footnotesize{ \textit{Do file: }  \texttt{tot\_tut\_insforest.do}}
\end{figure}

\newpage
\section{Appendix : Mixture Model}
Mixing distributions and mixture models are able to approximate the density function of any unknown distribution to arbitrary degrees of accuracy, provided that the mixing or mixture distribution  is  sufficiently  complex \cite{nguyen}. In fact, \cite{mcfadden} demonstrated that any random utility model can be approximated to any degree of accuracy by a mixed logit with the appropriate specification of variables and mixing distribution. We follow the approach by \cite{TRAIN200840}.\\

\subsection{Estimation}

The EM algorithm following \cite{em,em_seq} but most importantly \cite{TRAIN200840}, is in our setting :

\begin{algorithm}[H]
\SetKwInOut{Input}{input}\SetKwInOut{Output}{output}

\caption{EM}\label{EM}
\small{
\Input{$(c_i, \mathbf{W}_i,  \mathbf{X}_i)$}
\Output{$\hat{\bm\gamma}, \hat{\bm{\beta}}, \widetilde{\alpha_{i,k}}, \widetilde{\alpha_{k}}$}
\BlankLine
Initialize $\gamma_{k}^{(0)}, \beta_k^{(0)}$

Update the predicted probability (weight) for individual $i$, type $k$: \;
$\widehat{\alpha_{i,k}^{(0)}} = \frac{e^{\gamma_{k}^{(0)}\mathbf{W}_i}}{\sum_{j=1}^{K} e^{\gamma_{j}^{(0)}\mathbf{W}_i}} $
% $\alpha_{i}^{(0)}\sim \operatorname{Categorical}$, following (\ref{dist_alpha})

Update the shares of types:\;
$\widehat{\alpha_k^{(0)}} = \frac{\sum_{i=1}^n\widehat{\alpha_{i,k}^{(0)}}}{\sum_{k=1}^{K}\sum_{i=1}^n\widehat{\alpha_{i,k}^{(0)}}}$\;

\textbf{E-step :}

Compute predicted posterior probability  for the $k$ type: \;
$\widetilde{\alpha_{i,k}^{(0)}} = \frac{\widehat{\alpha_k^{(0)}}f(c_i,\mathbf{X}_i; \bm\beta_{k}^{(0)})}{\sum_{k=1}^K\widehat{\alpha_k^{(0)}}f(c_i,\mathbf{X}_i; \bm\beta_{k}^{(0)})}$\;

\While{$||(\bm\gamma^{(t)},\bm\beta^{(t)})-(\bm\gamma^{(t-1)},\bm\beta^{(t-1)})||>\operatorname{tol}$}{

\textbf{M-step :}

$\bm\beta_{k}^{(t+1)}  = \operatorname{argmax}_{\bm\beta_{k}} \sum_{i=1}^n \widetilde{\alpha_{i,k}^{(t)}} \log \prod_{c=1}^4\left(\frac{e^{\beta_{c,k} \mathbf{X}_i}}{\sum_{j=1}^{4} e^{\beta_{j,k}  \mathbf{X}_i}}\right)^{[c_i=c]} $\;
\scriptsize{(Run a multinomial-logit model with weighted observations, with weights given by the conditional probabilities of type membership)}\;
\small

$\bm\gamma_{k}^{(t+1)} = \operatorname{argmax}_{\bm\gamma_{k}} \sum_{i=1}^n\sum_{k=1}^K \widetilde{\alpha_{i,k}^{(t)}} \log \left(\frac{e^{\gamma_{k}\mathbf{W}_i}}{\sum_{j=1}^{K} e^{\gamma_{j}\mathbf{W}_i}}\right) $\;

\scriptsize{(Grouped-data log likelihood, where we have used a multinomial-logit specification)}\;

\small

Update the predicted probability (weight) for individual $i$, type $k$: \;
$\widehat{\alpha_{i,k}^{(t+1)}} = \frac{e^{\gamma_{k}^{(t+1)}\mathbf{W}_i}}{\sum_{j=1}^{K} e^{\gamma_{j}^{(t+1)}\mathbf{W}_i}} $
% $\alpha_{i}^{(0)}\sim \operatorname{Categorical}$, following (\ref{dist_alpha})

Update the shares of types:\;
$\widehat{\alpha_k^{(t+1)}} = \frac{\sum_{i=1}^n\widehat{\alpha_{i,k}^{(t+1)}}}{\sum_{k=1}^{K}\sum_{i=1}^n\widehat{\alpha_{i,k}^{(t+1)}}}$\;

\textbf{E-step :}

Compute predicted posterior probability  for the $k$ type: \;
$\widetilde{\alpha_{i,k}^{(t+1)}} = \frac{\widehat{\alpha_k^{(t+1)}}f(c_i,\mathbf{X}_i; \bm\beta_{k}^{(t+1)})}{\sum_{k=1}^K\widehat{\alpha_k^{(t+1)}}f(c_i,\mathbf{X}_i; \bm\beta_{k}^{(t+1)})}$\;

}
Update the posterior shares of types:\;
$\widetilde{\alpha_k^{(t+1)}} = \frac{\sum_{i=1}^n\widetilde{\alpha_{i,k}^{(t+1)}}}{\sum_{k=1}^{K}\sum_{i=1}^n\widetilde{\alpha_{i,k}^{(t+1)}}}$\;
}
\end{algorithm}

\subsection{Extensions}

A stochastic version\footnote{See \cite{nielsen}.} of the estimation above consists, at iteration $t$, in replacing the probability of the unknown types $k$ by a sequence sampled from a Categorical distribution
\[\widehat{\alpha_{i}^{(t)}}\sim \operatorname{Categorical}\left(\frac{\widehat{\alpha_k^{(t+1)}}f(c_i,\mathbf{X}_i; \bm\beta_{k}^{(t+1)})}{\sum_{k=1}^K\widehat{\alpha_k^{(t+1)}}f(c_i,\mathbf{X}_i; \bm\beta_{k}^{(t+1)})}\right)\] 
We call this the \textbf{SE-step}. We can then use these sampled labels for updating the estimation in the \textbf{M-step} by maximizing the \emph{complete} maximum likelihood.

\subsubsection{Degrees of naivete}
We can model degrees of naivete assuming every individual $i$ has a (continuous) propensity of being of each type. We model this by making the predicted probability of each individual follow a Dirichlet regression $\alpha_{i} \sim \operatorname{DirichletReg}$.

\subsection{Identifiability}
\cite{grun} analyze the identifiability of a general class of finite mixtures of multinomial logits.

\newpage
\clearpage
\bibliographystyle{authordate1}
%\bibliographystyle{amsalpha}
%\bibliographystyle{AER}

\bibliography{References_aux.bib}

\end{document}

### 2021-10-22 donde.tex
benefit_vs_choice analysis & corrections in causal forests
Former-commit-id: a94e41dada3d0ce771362fc224735b66a8842aa5

@@
 Panel (c) simulates what percentage would be better by at least $z$ if we forced everybody of those in the fee-choice arm into the fee-commitment contract.
-Panel (d) asks whether it is the case that people with larger causal savings from the fee-forcing contract would be more likely to select that contract.
+Panel (d) asks whether it is the case that people with larger causal benefits from the fee-forcing contract would be more likely to select that contract.
 To do this we proceed in two steps as well.
@@
 The Y-axis plots the heterogeneous treatment effects of the fee forcing contract on the probability of losing the pawns (more negative means then more likely to recover it), averaged for the respective x-axis bin.
-Positive assortative selection would mean a negative relationship: those who benefit more by treatment and lose the pawn less are more likely to choose it.
+Positive assortative selection would mean a negative relationship: those who benefit more by treatment and lose the pawn less are \emph{less} likely to choose it.
 Using all bins we estimate a slope of zero in the relationship.

### 2021-10-22 RScripts/def_te_grf.R

@@ -1,0 +1,82 @@
+library(tidyverse)
+library(grf)
+library(ggplot2)
+
+# SET WORKING DIRECTORY
+setwd('C:/Users/isaac/Dropbox/Apps/ShareLaTeX/Donde2020')
+set.seed(5289374)
+
+
+
+data_in <- read_csv('./_aux/def_te_heterogeneity.csv') %>%
+  mutate_all(~ifelse(is.na(.), median(., na.rm = TRUE), .))
+
+
+require("dplyr")
+
+data_train <- data_in %>% 
+  filter(insample == 1) 
+data_train_fee <- subset(data_train, data_train$fee_arms == 1)
+data_train_nofee <- subset(data_train, data_train$fee_arms == 0)
+
+
+data_test <- data_in %>% 
+  select(-c(def_c, fee_arms, prenda, insample))
+
+###################################################################  
+###################################################################  
+
+
+# PREPARE VARIABLES
+X <- select(data_train,-c(def_c, fee_arms, prenda, insample))
+Y <- select(data_train,def_c)
+W <- as.numeric(data_train$fee_arms == 1)
+
+X_full <- select(data_in,-c(def_c, fee_arms, prenda, insample))
+Y_full <- select(data_in,def_c)
+W_full <- as.numeric(data_in$fee_arms == 1)
+
+X_fee <- select(data_train_fee,-c(def_c, fee_arms, prenda, insample))
+Y_fee <- as.numeric(data_train_fee$def_c)
+X_nofee <- select(data_train_nofee,-c(def_c, fee_arms, prenda, insample))
+Y_nofee <- as.numeric(data_train_nofee$def_c)
+
+###################################################################  
+###################################################################  
+
+
+# ESTIMATE MODEL
+
+# Causal Forest
+tau.forest = causal_forest(
+  X = model.matrix(~., data = X), 
+  Y = data.matrix(Y), 
+  W = W,
+  honesty = TRUE)
+
+tau.forest.full = causal_forest(
+  X = model.matrix(~., data = X_full), 
+  Y = data.matrix(Y_full), 
+  W = W_full,
+  honesty = TRUE)  
+# Regression forest
+pred.forest.fee = regression_forest(X_fee, Y_fee)
+pred.forest.nofee = regression_forest(X_nofee, Y_nofee)
+
+# Estimate treatment effects for the training data using out-of-bag prediction.
[…]

### 2021-10-22 RScripts/des_te_grf.R

@@ -4,12 +4,12 @@ library(ggplot2)
 
 # SET WORKING DIRECTORY
 setwd('C:/Users/isaac/Dropbox/Apps/ShareLaTeX/Donde2020')
-#setwd("C:\\Users\\Ricardo\\Documents\\SEIRA\\donde2019")
 set.seed(5289374)
 
 
 
-data_in <- read_csv('./_aux/des_te_heterogeneity.csv')
+data_in <- read_csv('./_aux/des_te_heterogeneity.csv') %>%
+  mutate_all(~ifelse(is.na(.), median(., na.rm = TRUE), .))
 
 
 require("dplyr")

### 2021-10-22 RScripts/eff_te_grf.R

@@ -1,24 +1,95 @@
+library(gdata)
 library(tidyverse)
 library(grf)
 library(ggplot2)
+library(ggthemes)
+library(causalTree)
+library(DiagrammeR)
+library(DiagrammeRsvg)
+library(rattle)
+library(broom)
 
 # SET WORKING DIRECTORY
 setwd('C:/Users/isaac/Dropbox/Apps/ShareLaTeX/Donde2020')
-#setwd("C:\\Users\\Ricardo\\Documents\\SEIRA\\donde2019")
 set.seed(5289374)
 
 
 
-data_in <- read_csv('./_aux/eff_te_heterogeneity.csv')
-
+data_in <- read_csv('./_aux/eff_te_heterogeneity.csv') %>%
+  mutate_all(~ifelse(is.na(.), median(., na.rm = TRUE), .))  
+data_in <- rename.vars(data_in, c(
+  "dummy_dow1",
+  "dummy_dow2",
+  "dummy_dow3",
+  "dummy_dow4",
+  "dummy_dow5",
+  "dummy_dow6",
+  "dummy_suc1",
+  "dummy_suc2",
+  "dummy_suc3",
+  "dummy_suc4",
+  "dummy_suc5",
+  "dummy_suc6",
+  "num_arms_d3",
+  "num_arms_d4",
+  "num_arms_d5",
+  "num_arms_d6", 
+  "visit_number_d2", 
+  "visit_number_d3", 
+  "visit_number_d4", 
+  "visit_number_d5", 
+  "visit_number_d6", 
+  "visit_number_d7",
+  "log_prestamo",
+  "pr_recup",
+  "edad",
+  "faltas",
+  "val_pren_std",
+  "genero",
+  "pres_antes",
+  "plan_gasto_bin",
+  "masqueprepa",
+  "pb"
+),
+c(
+  "monday",
+  "tuesday",
+  "wednesday",
+  "thurdsay",
+  "friday",
+  "saturday",
+  "branch.1",
+  "branch.2",
+  "branch.3",
+  "branch.4",
+  "branch.5",
+  "branch.6",
+  "num.exp.arms.3",
+  "num.exp.arms.4",
+  "num.exp.arms.5",
+  "num.exp.arms.6",
+  "visit.number.2",
+  "visit.number.3",
+  "visit.number.4",
+  "visit.number.5",
+  "visit.number.6",
+  "visit.number.7",
+  "log.loan",
+  "subj.pr",
+  "age",
[…]

### 2021-10-22 RScripts/grf.R

@@ -1,15 +1,28 @@
+library(gdata)
 library(tidyverse)
 library(grf)
 library(ggplot2)
+library(ggthemes)
+library(causalTree)
 library(DiagrammeR)
 library(DiagrammeRsvg)
-library(gdata)
+library(rattle)
+library(broom)
 
 # SET WORKING DIRECTORY
 setwd('C:/Users/isaac/Dropbox/Apps/ShareLaTeX/Donde2020')
-set.seed(5289374)
+set.seed(5289364)
 
 source("./RScripts/best_tree.R")
+
+fun_threshold_alpha = function(alpha, g) {
+  lambda = 1/(alpha*(1-alpha))
+  ind = (g<=lambda)
+  den = sum(ind)
+  num = ind*g
+  return((2*sum(num)/den-lambda)^2)
+}
+
 
 heterogeneity_effect <- function(data_in,treatment_var,outcome_var,writedata,extendedsample) {
   
@@ -17,62 +30,244 @@ heterogeneity_effect <- function(data_in,treatment_var,outcome_var,writedata,ext
   data_frame <- data_in %>%
     filter(data_in[,treatment_var] == 1 | data_in[,treatment_var] == 0) %>%
     select(-c( pro_2, pro_3, pro_4, pro_5, pro_6, pro_7, pro_8, pro_9, fee, fecha_inicial,
-               eff_cost_loan, def_c, fc_admin_disc, fc_survey_disc, fc_admin, fc_survey, dias_primer_pago), 
+               eff_cost_loan, def_c, des_c, fc_admin_disc, fc_survey_disc, fc_admin, fc_survey, dias_primer_pago), 
            treatment_var, outcome_var ) %>%
-    drop_na()  
+    mutate_all(~ifelse(is.na(.), median(., na.rm = TRUE), .))  
+  data_copy <- data_frame
   
+  if (extendedsample == 0) {
+    # Data with names in english
+    data_frame <- rename.vars(data_frame, c(
+      "dummy_dow1",
+      "dummy_dow2",
+      "dummy_dow3",
+      "dummy_dow4",
+      "dummy_dow5",
+      "dummy_dow6",
+      "dummy_suc1",
+      "dummy_suc2",
+      "dummy_suc3",
+      "dummy_suc4",
+      "dummy_suc5",
+      "dummy_suc6",
+      "num_arms_d3",
+      "num_arms_d4",
+      "num_arms_d5",
+      "num_arms_d6", 
[…]

### 2021-10-22 RScripts/pfv_pred_hte.R

@@ -42,7 +42,7 @@ rf_predict <- function(data_in,take.up,nme) {
 #RF Predictions of no-choice arm
 for (arm in c("pro_2")) {
   for (pred in c("pago_frec_vol_fee")) {
-    for (effect in c("def_c")) {
+    for (effect in c("def_c", "des_c")) {
       filename <- paste("_aux/",arm,"_",pred,"_",effect,".csv", sep="")
       data <- read_csv(filename)
       outname <- paste(arm,"_",pred,"_",effect,sep="")

### 2021-10-22 RScripts/sumporcp_te_grf.R

@@ -4,12 +4,12 @@ library(ggplot2)
 
 # SET WORKING DIRECTORY
 setwd('C:/Users/isaac/Dropbox/Apps/ShareLaTeX/Donde2020')
-#setwd("C:\\Users\\Ricardo\\Documents\\SEIRA\\donde2019")
 set.seed(5289374)
 
 
 
-data_in <- read_csv('./_aux/sumporcp_te_heterogeneity.csv')
+data_in <- read_csv('./_aux/sumporcp_te_heterogeneity.csv') %>%
+  mutate_all(~ifelse(is.na(.), median(., na.rm = TRUE), .))
 
 
 require("dplyr")

### 2021-10-22 RScripts/te_grf.R

@@ -1,0 +1,260 @@
+library(gdata)
+library(tidyverse)
+library(grf)
+library(ggplot2)
+library(ggthemes)
+library(causalTree)
+library(DiagrammeR)
+library(DiagrammeRsvg)
+library(rattle)
+library(broom)
+
+# SET WORKING DIRECTORY
+setwd('C:/Users/isaac/Dropbox/Apps/ShareLaTeX/Donde2020')
+set.seed(5289174)
+
+fun_threshold_alpha = function(alpha, g) {
+  lambda = 1/(alpha*(1-alpha))
+  ind = (g<=lambda)
+  den = sum(ind)
+  num = ind*g
+  return((2*sum(num)/den-lambda)^2)
+}
+
+
+te_grf <- function(data_in, outcome_var, name) {
+  
+  require("dplyr")
+  data_in <- data_in %>%
+    mutate_all(~ifelse(is.na(.), median(., na.rm = TRUE), .))  
+  data_copy <- data_in
+  data_in <- rename.vars(data_in, c(
+    "dummy_dow1",
+    "dummy_dow2",
+    "dummy_dow3",
+    "dummy_dow4",
+    "dummy_dow5",
+    "dummy_dow6",
+    "dummy_suc1",
+    "dummy_suc2",
+    "dummy_suc3",
+    "dummy_suc4",
+    "dummy_suc5",
+    "dummy_suc6",
+    "num_arms_d3",
+    "num_arms_d4",
+    "num_arms_d5",
+    "num_arms_d6", 
+    "visit_number_d2", 
+    "visit_number_d3", 
+    "visit_number_d4", 
+    "visit_number_d5", 
+    "visit_number_d6", 
+    "visit_number_d7",
+    "edad",
+    "faltas",
+    "val_pren_std",
+    "genero",
+    "masqueprepa"
+  ),
+  c(
+    "monday",
+    "tuesday",
+    "wednesday",
+    "thurdsay",
+    "friday",
+    "saturday",
+    "branch.1",
+    "branch.2",
+    "branch.3",
+    "branch.4",
+    "branch.5",
+    "branch.6",
+    "num.exp.arms.3",
+    "num.exp.arms.4",
+    "num.exp.arms.5",
+    "num.exp.arms.6",
+    "visit.number.2",
+    "visit.number.3",
+    "visit.number.4",
+    "visit.number.5",
+    "visit.number.6",
+    "visit.number.7",
+    "age",
+    "income.index",
[…]

### 2021-10-22 RScripts/tot_tut_instr_forest.R

@@ -1,0 +1,190 @@
+library(gdata)
+library(tidyverse)
+library(grf)
+library(ggplot2)
+library(ggthemes)
+library(causalTree)
+library(DiagrammeR)
+library(DiagrammeRsvg)
+library(rattle)
+library(broom)
+
+# SET WORKING DIRECTORY
+setwd('C:/Users/isaac/Dropbox/Apps/ShareLaTeX/Donde2020')
+set.seed(5289174)
+
+
+rename_var = function(df) { 
+  df <- rename.vars(df, c(
+    "dummy_dow1",
+    "dummy_dow2",
+    "dummy_dow3",
+    "dummy_dow4",
+    "dummy_dow5",
+    "dummy_dow6",
+    "dummy_suc1",
+    "dummy_suc2",
+    "dummy_suc3",
+    "dummy_suc4",
+    "dummy_suc5",
+    "dummy_suc6",
+    "num_arms_d3",
+    "num_arms_d4",
+    "num_arms_d5",
+    "num_arms_d6", 
+    "visit_number_d2", 
+    "visit_number_d3", 
+    "visit_number_d4", 
+    "visit_number_d5", 
+    "visit_number_d6", 
+    "visit_number_d7",
+    "edad",
+    "faltas",
+    "val_pren_std",
+    "genero",
+    "masqueprepa"
+  ),
+  c(
+    "monday",
+    "tuesday",
+    "wednesday",
+    "thurdsay",
+    "friday",
+    "saturday",
+    "branch.1",
+    "branch.2",
+    "branch.3",
+    "branch.4",
+    "branch.5",
+    "branch.6",
+    "num.exp.arms.3",
+    "num.exp.arms.4",
+    "num.exp.arms.5",
+    "num.exp.arms.6",
+    "visit.number.2",
+    "visit.number.3",
+    "visit.number.4",
+    "visit.number.5",
+    "visit.number.6",
+    "visit.number.7",
+    "age",
+    "income.index",
+    "subj.loan.value",
+    "female",
+    "more.high.school"
+  ))
+}
+
+fun_threshold_alpha = function(alpha, g) {
+  lambda = 1/(alpha*(1-alpha))
+  ind = (g<=lambda)
+  den = sum(ind)
+  num = ind*g
+  return((2*sum(num)/den-lambda)^2)
+}
+
+opt_alfa = function(xvar, wvar) {
+  propensity.forest = regression_forest(xvar, wvar)
[…]

### 2021-10-22 oldrepo/IsaacMeza-donde2019-54d6b0d43053/RScripts/grf.R
removed oldrepo files
Former-commit-id: f38ad4427e5f8f5c2cd76873f956f03cf6bc7903

@@ -1,80 +1,0 @@
-library(tidyverse)
-library(grf)
-library(ggplot2)
-
-# SET WORKING DIRECTORY
-setwd('C:/Users/xps-seira/Dropbox/Apps/ShareLaTeX/Donde2019')
-#setwd("C:\\Users\\Ricardo\\Documents\\SEIRA\\donde2019")
-set.seed(5289374)
-
-heterogeneity_effect <- function(data_in,treatment_var,outcome_var) {
-  
-require("dplyr")
-data_frame <- data_in %>%
-  filter(data_in[,treatment_var] == 1 | data_in[,treatment_var] == 0) %>%
-  select(-c( pro_2, pro_3, pro_4, pro_5 , t_producto, NombrePignorante, fecha_inicial,
-             des_c, dias_al_desempenyo , 
-             ref_c  , num_p , sum_porcp_c, reincidence), treatment_var, outcome_var ) %>%
-  drop_na()  
-
-print(head(data_frame))
-
-# PREPARE VARIABLES
-X <- select(data_frame,-c(outcome_var, treatment_var))
-Y <- select(data_frame,outcome_var)
-W <- as.numeric(data_frame[,treatment_var] == 1)
-
-# ESTIMATE MODEL
-tau.forest = causal_forest(
-  X = model.matrix(~., data = X), 
-  Y = data.matrix(Y), 
-  W = W,
-  honesty = TRUE)
-
-# OVERLAP ASSUMPTION
-propensity.forest = regression_forest(X, W)
-propensity_score = predict(propensity.forest)$predictions
-hist(propensity_score, xlab = "propensity score")
-
-# Estimate treatment effects for the training data using out-of-bag prediction.
-tau_hat_oob = predict(tau.forest, estimate.variance = TRUE)
-hist(tau_hat_oob$predictions)
-
-# Estimate the conditional average treatment effect on the full sample (CATE).
-average_treatment_effect(tau.forest, target.sample = "all")
-
-# Estimate the conditional average treatment effect on the treated sample (CATT).
-# Here, we don't expect much difference between the CATE and the CATT, since
-# treatment assignment was randomized.
-average_treatment_effect(tau.forest, target.sample = "treated")
-
-
-data.out <- add_column(data_frame,tau_hat_oob$predictions,tau_hat_oob$variance.estimates, propensity_score)
[…]

### 2021-11-13 choice_benefit.tex
Learning by not doing regressions

@@
         \centering
-        \includegraphics[width=\textwidth]{Figuras/benefit_choice.pdf}
+        \includegraphics[width=\textwidth]{Figuras/benefit_choice_tau_eff.pdf}
     \end{subfigure}
@@
         \centering
-        \includegraphics[width=\textwidth]{Figuras/benefit_choice_des.pdf}
+        \includegraphics[width=\textwidth]{Figuras/benefit_choice_tau_des.pdf}
     \end{subfigure}
@@
 Now we want to identify who are the ones who benefit more from being forced, and those who would demand commitment.
+
+Based of the propensity score, we predict the two categories : choosers \& non-choosers, such that the proportions match the observed data.
+
+\begin{figure}[H]
+    \caption{}
+    \label{}
+    \begin{center}
+    %\begin{subfigure}{0.4\textwidth}
+    %    \caption{Financial cost}
+    %    \centering
+    %    \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_2.pdf}
+    %\end{subfigure}
+    \begin{subfigure}{0.475\textwidth}
+        \caption{Effective cost/loan benefit}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/cdf_predchoose_tau_eff.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.475\textwidth}
+        \caption{Repayment}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/cdf_predchoose_tau_des.pdf}
+    \end{subfigure}
+
+    \end{center}
+     \scriptsize    CDF of the heterogeneous treatment effect for choosers vs non-choosers.
+The dotted line below indicates the points where the difference in the distributions is significant.
+Instead of a single global null hypothesis (that the two CDFs are identical), there is a continuum of individual null hypotheses of CDF equality at each point.
+The methodology was proposed by \cite{GOLDMAN2018143}.
+
+          %\footnotesize{ \textit{Do file: }  \texttt{benefit\_choice.do}}
+\end{figure}
+
+We find a surprising \emh{significant} stochastic dominance between the two CDF's.
 
@@
     \begin{center}
-    \begin{subfigure}{0.475\textwidth}
-        \caption{Prior Probability}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/binscatter_tau_classpr.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.475\textwidth}
+    \begin{subfigure}{0.7\textwidth}
         \caption{Posterior Probability}
@@
     \begin{center}
-    \begin{subfigure}{0.475\textwidth}
-        \caption{Prior Probability}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/benefit_type1.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.475\textwidth}
+    \begin{subfigure}{0.7\textwidth}
         \caption{Posterior Probability}
@@
 \begin{center}
-\scriptsize{\input{./Tables/iv_reg_demand_pf_notchoosing.tex}}
+\scriptsize{\input{./Tables/iv_reg_pago_fijo_detailed.tex}}
 \end{center}
@@
 
-%\textit{Do file: } \texttt{iv\_reg\_demand\_pf\_notchoosing.do}
+%\textit{Do file: } \texttt{iv\_reg\_detailed.do}
 \end{table}
@@
 
+We drop murky cases:
+
 \begin{table}[H]
-\caption{Outcome in 2S : Default}
-\label{iv_def}
+\caption{Keeping only first two observations}
 \begin{center}
-\scriptsize{\input{./Tables/iv_reg_def_notchoosing.tex}}
+\scriptsize{\input{./Tables/iv_reg_pago_fijo_detailed_twoca.tex}}
 \end{center}
@@
 \begin{table}[H]
-\caption{Outcome in 2S : Default}
-\label{iv_def_decomp}
+\caption{Collapsing observations}
 \begin{center}
-\scriptsize{\input{./Tables/iv_reg_def_nc_nr.tex}}
+\scriptsize{\input{./Tables/iv_reg_pago_fijo_detailed_colla.tex}}
 \end{center}
@@
 
-%\textit{Do file: } \texttt{iv\_reg\_demand\_pf\_notchoosing.do}
+%\textit{Do file: } \texttt{iv\_reg\_detailed.do}
+\end{table}
+
+\begin{table}[H]
+\caption{Interacting with number of decision epochs}
+\begin{center}
+\scriptsize{\input{./Tables/iv_reg_pago_fijo_detailed_inter.tex}}
+\end{center}
+ \scriptsize
+
+%\textit{Do file: } \texttt{iv\_reg\_detailed.do}
+\end{table}
+Learning is stronger after some experience.\\
+
+What about the impact of the previous outcome (default) on learning?
+
+We estimate the following specification:
+
+\begin{align*}
+    \mathbbm{1}(\text{Has FP})_{ijt} &= \alpha_i + \gamma_t + \beta_1\mathbbm{1}(\text{Had FP})_{ijt} \\
+    & \qquad \quad + \beta_2\mathbbm{1}(\text{Defaulted})_{ijt} \\
+    & \qquad \quad  + \beta_3\mathbbm{1}(\text{Had FP})_{ijt}\mathbbm{1}(\text{Defaulted})_{ijt}   + \epsilon_{ijt}
+\end{align*}
+
+\begin{table}[H]
+\caption{Interaction with default in the past}
+\begin{center}
+\scriptsize{\input{./Tables/iv_reg_pago_fijo_def_detailed.tex}}
+\end{center}
+ \scriptsize
+
+%\textit{Do file: } \texttt{iv\_reg\_intdef\_detailed.do}
+\end{table}
+
+And as before we can also get rid of the `murky' cases:
+
+% \begin{table}[H]
+% \caption{Keeping only first two observations}
+% \begin{center}
+% \scriptsize{\input{./Tables/iv_reg_pago_fijo_def_twocases.tex}}
+% \end{center}
+%  \scriptsize
+
+% %\textit{Do file: } \texttt{iv\_reg\_intdef\_detailed.do}
+% \end{table}
+
+\begin{table}[H]
+\caption{Collapsing}
+\begin{center}
+\scriptsize{\input{./Tables/iv_reg_pago_fijo_def_collapsed.tex}}
+\end{center}
+ \scriptsize
+
+%\textit{Do file: } \texttt{iv\_reg\_intdef\_detailed.do}
+\end{table}
+
+\subsection{Learning in the experiment}
+
+\begin{table}[H]
+\caption{Summary statistics table of learning by not doing (OLS)}
+\begin{center}
+\scriptsize{\input{./Tables/SS_learning_OLS.tex}}
+\end{center}
+ \scriptsize
+
+%\textit{Do file: } \texttt{learning\_exp.do}
+\end{table}
+
+The above means can be recovered from the following specification
+
+\begin{align*}
+    \text{Choose Fee}_{i} &=  \alpha +  \beta_1\mathds{1}(\text{Default past})_{i} +\sum_{j=1}^{4}\beta_{2,j}\mathds{1}(\text{Past contract}=j)_{i} \\
+   &\qquad\quad  +\sum_{j=1}^{4}\beta_{3,j}\mathds{1}(\text{Past contract}=j)_{i}\mathds{1}(\text{Default past})_{i} + \epsilon_i
+\end{align*}
+for those individuals $i$ that had the option to choose after experiencing contract $j$, this could be control, forced fee, or choice.
+
+So what if we add fixed effects to the above? In order to capture variation within individuals in line with our previous specifications in the observational study.
+
+\begin{table}[H]
+\caption{Summary statistics table of learning by not doing (FE)}
+\begin{center}
+\scriptsize{\input{./Tables/SS_learning_FE.tex}}
+\end{center}
+ \scriptsize
+
+%\textit{Do file: } \texttt{learning\_exp.do}
+\end{table}
+
+\begin{table}[H]
+\caption{Learning by not doing (experimental)}
+\begin{center}
+\scriptsize{\input{./Tables/learning_exp.tex}}
+\end{center}
+ \scriptsize
+
+%\textit{Do file: } \texttt{learning\_exp.do}
 \end{table}
@@
 \end{table}
+
+\begin{figure}[H]
+    \caption{Bootstrap inference for the difference between TOT-TUT}
+    \label{}
+    \begin{center}
+    \begin{subfigure}{0.475\textwidth}
+        \caption{Simple}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/tot_tut_btsp1.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.475\textwidth}
+        \caption{Admin controls}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/tot_tut_btsp2.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.475\textwidth}
+        \caption{Survey controls}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/tot_tut_btsp3.pdf}
+    \end{subfigure}
+
+    \end{center}
+     \scriptsize    Binscatter of propensity to choose commitment vs treatment effect of frequent payments.
+          %\footnotesize{ \textit{Do file: }  \texttt{tot\_tut.do}}
+\end{figure}
 
@@
      \caption{TOT-TUT CDF}
-    \label{ExplanatoryMaterial}
     \begin{center}
@@
           %\footnotesize{ \textit{Do file: }  \texttt{tot\_tut\_insforest.do}}
+\end{figure}
+
+We test the exclusion restriction
+
+\begin{figure}[H]
+     \caption{Exclusion restriction}
+    \begin{center}
+    \begin{subfigure}{0.75\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/exclusion_restriction.pdf}
+    \end{subfigure}
+    \end{center}
+    \scriptsize
+
+          %\footnotesize{ \textit{Do file: }  \texttt{exclusion\_restriction.do}}
 \end{figure}

### 2021-11-13 choice_benefit_summary.tex
Learning by not doing regressions

--- 2021-11-13 choice_benefit.tex
@@
 \begin{document}
-
-We investigate the relation between choice (commitment) and benefit.
-First, we compute the Treatment Effect benefit in the control vs fee arm.
-Then, we calculate a propensity to choose commitment, and analyze the correlation between this two variables.
-
-\begin{figure}[H]
-    \caption{}
-    \label{}
-    \begin{center}
-    %\begin{subfigure}{0.4\textwidth}
-    %    \caption{Financial cost}
-    %    \centering
-    %    \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_2.pdf}
-    %\end{subfigure}
-    \begin{subfigure}{0.475\textwidth}
-        \caption{Effective cost/loan benefit}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/benefit_choice_tau_eff.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.475\textwidth}
-        \caption{Repayment}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/benefit_choice_tau_des.pdf}
-    \end{subfigure}
-
-    \end{center}
-     \scriptsize    Binscatter of propensity to choose commitment vs treatment effect of frequent payments.
-          %\footnotesize{ \textit{Do file: }  \texttt{benefit\_choice.do}}
-\end{figure}
 
@@
 
-\begin{figure}[H]
-    \caption{}
-    \label{}
-    \begin{center}
-    %\begin{subfigure}{0.4\textwidth}
-    %    \caption{Financial cost}
-    %    \centering
-    %    \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_2.pdf}
-    %\end{subfigure}
-    \begin{subfigure}{0.475\textwidth}
-        \caption{Determinants of HTE}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_eff_cost_loan_pro_2.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.475\textwidth}
-        \caption{Determinants of PS}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/HE/ps_int_vertical_pr_gbc_1.pdf}
-    \end{subfigure}
+\newpage
 
-    \end{center}
-     \scriptsize  (a): This figure estimates bivariate regressions of the estimated client-level heterogeneous treatment effects against the respective covariate from the baseline survey  $\widehat{hte_i} = \alpha + \beta \: X_i + \epsilon_i$.
-The regressors $X_i$ include (e.g if the family asks for money, if they have savings, if they are overconfident using the definition the text, etc.
-See this Appendix for a transcription of the survey).
-\\
-     (b) :  
-      %\footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}} \texttt{benefit\_choice.do}}
-\end{figure}
+\section{Observational Study}
 
-\subsection{Are the people who benefit most from commitment, the ones who demand it?}
-
-We estimate the following model
-
-We would like to make a distinction of the people that benefit most from being forced. Our conjecture is that this are the naive individuals.
-
-We assume the following structural model.
-
-Each individual $i$ is of type  $k\in\{1, 2\}$ with probability $\alpha_{i,k}$. We assume it follows a logit distribution:
-\begin{align*}
-\label{dist_alpha}
-    \alpha_{i,k} = \Pr(\text{Type}_i = k \;|\; \mathbf{W}_{i}) = \frac{e^{\gamma_{k}\mathbf{W}_i}}{\sum_{j=1}^{K} e^{\gamma_{j}\mathbf{W}_i}}
-\end{align*}
-
-where $\mathbf{W}_i$ are observable characteristics.
-This characteristics include choice for commitment, present bias, subjective probability of recovery, etc, which might be indicators of naivete vs sophistication.
-
-Now, given their type, each individual makes a choice to default or not $c_{i,k} \in \{1,2\}$, based on other set of observable characteristics $\mathbf{X}_i$ (subjective \& objective value of the loan).
-We will assume there is a continuous latent variable $Y_{i,k,c}$ distributed as
-\[Y_{i,k,c} = \beta_{c,k}\mathbf{X}_{i} +\epsilon_{c,k}\]
-with\footnote{We can impose other errors, and even impose a covariance structure, for instance if $(\epsilon_{c,k})_{c}\sim\mathcal{N}(0,\Sigma_k)$, we arrive to the Multinomial Probit.} $\epsilon_{c;k}\sim\operatorname{EV}(0,1)$.
-This latent variable can be thought of as the utility associated with individual $i$, being type $k$, making choice $c$.
-
-Thus, the density for each individual $i$ being type $k$ is
-\[f(c_i,\mathbf{X}_i; \bm\beta_{k}) = \prod_{c=1}^4\left(\frac{e^{\beta_{c,k} \mathbf{X}_i}}{\sum_{j=1}^{4} e^{\beta_{j,k}  \mathbf{X}_i}}\right)^{[c_i=4]}\]
-
-Finally, the generative model is then a mixture model with density given by,
-\begin{align*}
-    f(c_i ,\mathbf{W}_i, \mathbf{X}_i; \bm{\gamma},\bm{\beta}) &= \sum_{k=1}^K \alpha_k f(c_i,\mathbf{X}_i; \bm\beta_{k}) \\
-    &= \sum_{k=1}^K \alpha_k \prod_{c=1}^4\left(\frac{e^{\beta_{c,k} \mathbf{X}_i}}{\sum_{j=1}^{4} e^{\beta_{j,k}  \mathbf{X}_i}}\right)^{[c_i=c]} 
-\end{align*}
-
-where $\alpha\sim \operatorname{Categorical}$, and $\gamma_{K} = \beta_{4,k}=0$ for identification purposes.
-
-Then the (incomplete) log-likelihood function is
-\begin{align*}
-    \ell(\bm{\gamma}, \bm{\beta}; c, \mathbf{W},  \mathbf{X}) = \sum_{i=1}^n \log\sum_{k=1}^K \alpha_k \prod_{c=1}^4\left(\frac{e^{\beta_{c,k} \mathbf{X}_i}}{\sum_{j=1}^{4} e^{\beta_{j,k}  \mathbf{X}_i}}\right)^{[c_i=c]}
-\end{align*}
-
-, thus we estimate parameters $(\bm{\gamma}, \bm{\beta})$ with an EM algorithm using choice (default)
-\& observable characteristics: $(c_i,\mathbf{W}_i,\mathbf{X}_i)$.
-
-The results are the following:
-
-\begin{table}[H]
-\caption{FMM}
-\label{iv_pf}
-\begin{center}
-\scriptsize{\input{./Tables/fmm_types.tex}}
-\end{center}
- \scriptsize
-
-%\textit{Do file: } \texttt{fmm.do}
-\end{table}
-
-The class (type) which is positively correlated with demand for commitment might be identified with the \emph{sophisticated} individuals (Type 2).
-The hypothesis is that this class is the less benefit from being forced, and so (Type 1) individuals are the most benefited from being forced.
-
-\begin{figure}[H]
-    \caption{Probability of being Type 1 vs HTE}
-    \label{}
-    \begin{center}
-    \begin{subfigure}{0.7\textwidth}
-        \caption{Posterior Probability}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/binscatter_tau_classpost.pdf}
-    \end{subfigure}
-
-    \end{center}
-     \scriptsize 
-      %\footnotesize{ \textit{Do file: }  \texttt{fmm.do}} 
-\end{figure}
-
-A negative relation indicates that being Type 1 has more benefits from being forced.
-
-\begin{figure}[H]
-    \caption{Type 1 class vs HTE}
-    \label{}
-    \begin{center}
-    \begin{subfigure}{0.7\textwidth}
-        \caption{Posterior Probability}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/benefit_type1p.pdf}
-    \end{subfigure}
-
-    \end{center}
-     \scriptsize 
-      %\footnotesize{ \textit{Do file: }  \texttt{fmm.do}} 
-\end{figure}
-
-Moreover we find a strong correlation between the Type 1 individuals and the individuals that ``choose wrong" according to Figure 8 \ref{choose_wrong}.\\
-
-\emph{This exercise is stronger in the sense that when we divide by type, choice is the core divider.} This emphasizes how important choice is as a segregator.
-
-\subsection{Observational Study}
-
-Paternalism  with learning : We generate more learning through forcing than through choice.
+\subsection*{Paternalism  with learning : We generate more learning through forcing than through choice.}
 
 It is possible that the wrong people choose and they learn not through choosing, but rather through not choosing (and it did not work).
-We then partition our sample in the observational study, based on whether you committed the first time, and we want to show that learning happened in the "wrong group" : not choosers.
+We then partition our sample in the observational study, based on whether you committed the first time, and we want to show that learning happened in the ``wrong group" : not choosers.\\
 
-We want to show that the TE is localized within one of the groups in that endogenous split.
-
-We then estimate the following two-stage specification.
+We want to show that the TE is localized within one of the groups in that endogenous split. With that in mind, we estimate the following two-stage specification.
 
@@
 
-We drop murky cases:
+\newpage
+
+\subsection*{The results are robust when dropping `` murky" cases:}
 
@@
 
+\subsection*{Learning is stronger after some experience.}
+
 \begin{table}[H]
@@
 \end{table}
-Learning is stronger after some experience.\\
 
-What about the impact of the previous outcome (default) on learning?
+\subsection*{What about the impact of the previous outcome (default) on learning?}
 
-We estimate the following specification:
+We estimate the following specification, instrumenting the previous contract with the availability of the product as before.
 
@@
 
-\subsection{Learning in the experiment}
+\section{Learning with experimantal data}
 
@@
 
+This might look discouraging, but what if we exploit individual variation?
+
 The above means can be recovered from the following specification
@@
 So what if we add fixed effects to the above? In order to capture variation within individuals in line with our previous specifications in the observational study.
+
+\subsection*{We find there is learning, and also learning by not doing!}
 
@@
 
+\newpage
+
 \section{LATE}
@@
     \begin{center}
-    \begin{subfigure}{0.475\textwidth}
+    \begin{subfigure}{0.45\textwidth}
         \caption{Simple}
@@
     \end{subfigure}
-    \begin{subfigure}{0.475\textwidth}
+    \begin{subfigure}{0.45\textwidth}
         \caption{Admin controls}
@@
     \end{subfigure}
-    \begin{subfigure}{0.475\textwidth}
+    \begin{subfigure}{0.45\textwidth}
         \caption{Survey controls}
@@
     \end{center}
-     \scriptsize    Binscatter of propensity to choose commitment vs treatment effect of frequent payments.
+     \scriptsize   
           %\footnotesize{ \textit{Do file: }  \texttt{tot\_tut.do}}
@@
     \begin{center}
-    \begin{subfigure}{0.75\textwidth}
+    \begin{subfigure}{0.5\textwidth}
         \centering
@@
     \begin{center}
-    \begin{subfigure}{0.75\textwidth}
+    \begin{subfigure}{0.7\textwidth}
         \centering
@@
 \newpage
-\section{Appendix : Mixture Model}
-Mixing distributions and mixture models are able to approximate the density function of any unknown distribution to arbitrary degrees of accuracy, provided that the mixing or mixture distribution  is  sufficiently  complex \cite{nguyen}.
-In fact, \cite{mcfadden} demonstrated that any random utility model can be approximated to any degree of accuracy by a mixed logit with the appropriate specification of variables and mixing distribution.
-We follow the approach by \cite{TRAIN200840}.\\
-
-\subsection{Estimation}
-
-The EM algorithm following \cite{em,em_seq} but most importantly \cite{TRAIN200840}, is in our setting :
-
-\begin{algorithm}[H]
-\SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
-
-\caption{EM}\label{EM}
-\small{
-\Input{$(c_i, \mathbf{W}_i,  \mathbf{X}_i)$}
-\Output{$\hat{\bm\gamma}, \hat{\bm{\beta}}, \widetilde{\alpha_{i,k}}, \widetilde{\alpha_{k}}$}
-\BlankLine
-Initialize $\gamma_{k}^{(0)}, \beta_k^{(0)}$
-
-Update the predicted probability (weight) for individual $i$, type $k$: \;
-$\widehat{\alpha_{i,k}^{(0)}} = \frac{e^{\gamma_{k}^{(0)}\mathbf{W}_i}}{\sum_{j=1}^{K} e^{\gamma_{j}^{(0)}\mathbf{W}_i}} $
-% $\alpha_{i}^{(0)}\sim \operatorname{Categorical}$, following (\ref{dist_alpha})
-
-Update the shares of types:\;
-$\widehat{\alpha_k^{(0)}} = \frac{\sum_{i=1}^n\widehat{\alpha_{i,k}^{(0)}}}{\sum_{k=1}^{K}\sum_{i=1}^n\widehat{\alpha_{i,k}^{(0)}}}$\;
-
-\textbf{E-step :}
-
-Compute predicted posterior probability  for the $k$ type: \;
-$\widetilde{\alpha_{i,k}^{(0)}} = \frac{\widehat{\alpha_k^{(0)}}f(c_i,\mathbf{X}_i; \bm\beta_{k}^{(0)})}{\sum_{k=1}^K\widehat{\alpha_k^{(0)}}f(c_i,\mathbf{X}_i; \bm\beta_{k}^{(0)})}$\;
-
-\While{$||(\bm\gamma^{(t)},\bm\beta^{(t)})-(\bm\gamma^{(t-1)},\bm\beta^{(t-1)})||>\operatorname{tol}$}{
-
-\textbf{M-step :}
-
-$\bm\beta_{k}^{(t+1)}  = \operatorname{argmax}_{\bm\beta_{k}} \sum_{i=1}^n \widetilde{\alpha_{i,k}^{(t)}} \log \prod_{c=1}^4\left(\frac{e^{\beta_{c,k} \mathbf{X}_i}}{\sum_{j=1}^{4} e^{\beta_{j,k}  \mathbf{X}_i}}\right)^{[c_i=c]} $\;
-\scriptsize{(Run a multinomial-logit model with weighted observations, with weights given by the conditional probabilities of type membership)}\;
-\small
-
-$\bm\gamma_{k}^{(t+1)} = \operatorname{argmax}_{\bm\gamma_{k}} \sum_{i=1}^n\sum_{k=1}^K \widetilde{\alpha_{i,k}^{(t)}} \log \left(\frac{e^{\gamma_{k}\mathbf{W}_i}}{\sum_{j=1}^{K} e^{\gamma_{j}\mathbf{W}_i}}\right) $\;
-
-\scriptsize{(Grouped-data log likelihood, where we have used a multinomial-logit specification)}\;
-
-\small
-
-Update the predicted probability (weight) for individual $i$, type $k$: \;
-$\widehat{\alpha_{i,k}^{(t+1)}} = \frac{e^{\gamma_{k}^{(t+1)}\mathbf{W}_i}}{\sum_{j=1}^{K} e^{\gamma_{j}^{(t+1)}\mathbf{W}_i}} $
-% $\alpha_{i}^{(0)}\sim \operatorname{Categorical}$, following (\ref{dist_alpha})
-
-Update the shares of types:\;
-$\widehat{\alpha_k^{(t+1)}} = \frac{\sum_{i=1}^n\widehat{\alpha_{i,k}^{(t+1)}}}{\sum_{k=1}^{K}\sum_{i=1}^n\widehat{\alpha_{i,k}^{(t+1)}}}$\;
-
-\textbf{E-step :}
-
-Compute predicted posterior probability  for the $k$ type: \;
-$\widetilde{\alpha_{i,k}^{(t+1)}} = \frac{\widehat{\alpha_k^{(t+1)}}f(c_i,\mathbf{X}_i; \bm\beta_{k}^{(t+1)})}{\sum_{k=1}^K\widehat{\alpha_k^{(t+1)}}f(c_i,\mathbf{X}_i; \bm\beta_{k}^{(t+1)})}$\;
-
-}
-Update the posterior shares of types:\;
-$\widetilde{\alpha_k^{(t+1)}} = \frac{\sum_{i=1}^n\widetilde{\alpha_{i,k}^{(t+1)}}}{\sum_{k=1}^{K}\sum_{i=1}^n\widetilde{\alpha_{i,k}^{(t+1)}}}$\;
-}
-\end{algorithm}
-
-\subsection{Extensions}
-
-A stochastic version\footnote{See \cite{nielsen}.} of the estimation above consists, at iteration $t$, in replacing the probability of the unknown types $k$ by a sequence sampled from a Categorical distribution
-\[\widehat{\alpha_{i}^{(t)}}\sim \operatorname{Categorical}\left(\frac{\widehat{\alpha_k^{(t+1)}}f(c_i,\mathbf{X}_i; \bm\beta_{k}^{(t+1)})}{\sum_{k=1}^K\widehat{\alpha_k^{(t+1)}}f(c_i,\mathbf{X}_i; \bm\beta_{k}^{(t+1)})}\right)\]
-We call this the \textbf{SE-step}. We can then use these sampled labels for updating the estimation in the \textbf{M-step} by maximizing the \emph{complete} maximum likelihood.
-
-\subsubsection{Degrees of naivete}
-We can model degrees of naivete assuming every individual $i$ has a (continuous) propensity of being of each type.
-We model this by making the predicted probability of each individual follow a Dirichlet regression $\alpha_{i} \sim \operatorname{DirichletReg}$.
-
-\subsection{Identifiability}
-\cite{grun} analyze the identifiability of a general class of finite mixtures of multinomial logits.
-
-\newpage
 \clearpage

### 2021-11-13 RScripts/grf.R

@@ -190,7 +190,10 @@ heterogeneity_effect <- function(data_in,treatment_var,outcome_var,writedata,ext
   # (on held-out data) as well as the mean forest prediction as the sole two regressors.
   # A coefficient of 1 for 'mean.forest.prediction' suggests that the mean forest 
   # prediction is correct, whereas a coefficient of 1 for 'differential.forest.prediction'
-  # additionally suggests that the forest has captured heterogeneity in the underlying signal. 
+  # additionally suggests that the forest has captured heterogeneity in the underlying signal.
+  # The p-value of the ‘differential.forest.prediction‘coefficient also acts as an omnibus test 
+  # the presence of heterogeneity: If the coefficient is significantly greater than 0, 
+  # then we can reject the null of no heterogeneity.
   
   tc <- tidy(test_calibration(tau.forest))
   print(tc)

### 2021-11-13 RScripts/te_grf.R

@@ -228,6 +228,9 @@ te_grf <- function(data_in, outcome_var, name) {
   # A coefficient of 1 for 'mean.forest.prediction' suggests that the mean forest 
   # prediction is correct, whereas a coefficient of 1 for 'differential.forest.prediction'
   # additionally suggests that the forest has captured heterogeneity in the underlying signal. 
+  # The p-value of the ‘differential.forest.prediction‘coefficient also acts as an omnibus test 
+  # the presence of heterogeneity: If the coefficient is significantly greater than 0, 
+  # then we can reject the null of no heterogeneity.
   
   tc <- tidy(test_calibration(tau.forest))
   print(tc)

### 2022-01-26 OA.tex
checkpoint before edits of tables and figues

@@
 It does this separately for the fee-forcing contract and for the status-quo contract.
-The doted line at the bottom is the difference of the status-quo CDF minus the fee-focing CDF.
+The doted line at the bottom is the difference of the status-quo CDF minus the fee-forcing CDF.
+It shows that the CDF of the status quo contract is always below that of the fee-forcing (and this difference is significant for the points indicated by the blue line), and therefore that the former first-order stochastically dominates the later for weakly decreasing utility functions; see Proposition \ref{eq_fosd}.
+    % \texttt{ecdf\_fc.do}}
+\end{figure}
+
+\begin{figure}[H]
+        \caption{Empirical CDF of Financial Cost: fee-focing vs status-quo}
+    \label{ecdf_fc}
+    \begin{center}
+        \centering
+        \includegraphics[width=0.65\textwidth]{Figuras/cdf_eff_pro_2.pdf}
+    \end{center}
+    \scriptsize This figure plots the empirical cumulative distribution of financial cost.
+It does this separately for the fee-forcing contract and for the status-quo contract.
+The doted line at the bottom is the difference of the status-quo CDF minus the fee-forcing CDF.
 It shows that the CDF of the status quo contract is always below that of the fee-forcing (and this difference is significant for the points indicated by the blue line), and therefore that the former first-order stochastically dominates the later for weakly decreasing utility functions; see Proposition \ref{eq_fosd}.
@@
 
+\newpage
+
+\subsection{Selection on gains}
+
+\begin{figure}[H]
+    \caption{Determinants of treatment effects and probability of choosing commitment}
+    \label{determinants_ps_hte}
+    \begin{center}
+    \begin{subfigure}{0.475\textwidth}
+        \caption{Determinants of HTE}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_eff_cost_loan_pro_2.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.475\textwidth}
+        \caption{Determinants of propensity score}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/HE/ps_int_vertical_pr_gbc_1.pdf}
+    \end{subfigure}
+
+    \end{center}
+     \scriptsize   This figure estimates bivariate regressions of the estimated client-level (a) heterogeneous treatment effects, (b) propensity score, against the respective covariate from the baseline survey  $\widehat{HTE_i}, \widehat{P_i} = \alpha + \beta \: X_i + \epsilon_i$.
+The regressors $X_i$ include (e.g if the family asks for money, if they have savings, if they are overconfident using the definition the text, etc.
+See this Appendix for a transcription of the survey).
+\\
+      %\footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}} \texttt{benefit\_choice.do}}
+\end{figure}
+
+\subsubsection{Finite mixture model }\label{fmm_section}
+
+\vspace{.2in}
+\normalsize
+\linespread{1.25}
+
+We assume the following structural model : Each individual $i$ is of type  $k\in\{1, 2\}$ with probability $\alpha_{i,k}$. We assume it follows a logit distribution:
+\begin{align*}
+\label{dist_alpha}
+    \alpha_{i,k} = \Pr(\text{Type}_i = k \;|\; \mathbf{W}_{i}) = \frac{e^{\gamma_{k}\mathbf{W}_i}}{\sum_{j=1}^{K} e^{\gamma_{j}\mathbf{W}_i}}
+\end{align*}
+
+where $\mathbf{W}_i$ are observable characteristics.
+This characteristics include choice for commitment, present bias, subjective probability of recovery, etc, which might be indicators of naivete vs sophistication.
+
+Now, given their type, each individual makes a choice to default or not $c_{i,k} \in \{1,2\}$, based on other set of observable characteristics $\mathbf{X}_i$ (subjective \& objective value of the loan).
+We will assume there is a continuous latent variable $Y_{i,k,c}$ distributed as
+\[Y_{i,k,c} = \beta_{c,k}\mathbf{X}_{i} +\epsilon_{c,k}\]
+with\footnote{We can impose other errors, and even impose a covariance structure, for instance if $(\epsilon_{c,k})_{c}\sim\mathcal{N}(0,\Sigma_k)$, we arrive to the Multinomial Probit.} $\epsilon_{c;k}\sim\operatorname{EV}(0,1)$.
+This latent variable can be thought of as the utility associated with individual $i$, being type $k$, making choice $c$.
+
+Thus, the density for each individual $i$ being type $k$ is
+\[f(c_i,\mathbf{X}_i; \bm\beta_{k}) = \prod_{c=1}^4\left(\frac{e^{\beta_{c,k} \mathbf{X}_i}}{\sum_{j=1}^{4} e^{\beta_{j,k}  \mathbf{X}_i}}\right)^{[c_i=4]}\]
+
+Finally, the generative model is then a mixture model with density given by,
+\begin{align*}
+    f(c_i ,\mathbf{W}_i, \mathbf{X}_i; \bm{\gamma},\bm{\beta}) &= \sum_{k=1}^K \alpha_k f(c_i,\mathbf{X}_i; \bm\beta_{k}) \\
+    &= \sum_{k=1}^K \alpha_k \prod_{c=1}^4\left(\frac{e^{\beta_{c,k} \mathbf{X}_i}}{\sum_{j=1}^{4} e^{\beta_{j,k}  \mathbf{X}_i}}\right)^{[c_i=c]} 
+\end{align*}
+
+where $\alpha\sim \operatorname{Categorical}$, and $\gamma_{K} = \beta_{4,k}=0$ for identification purposes.
+
+Then the (incomplete) log-likelihood function is
+\begin{align*}
+    \ell(\bm{\gamma}, \bm{\beta}; c, \mathbf{W},  \mathbf{X}) = \sum_{i=1}^n \log\sum_{k=1}^K \alpha_k \prod_{c=1}^4\left(\frac{e^{\beta_{c,k} \mathbf{X}_i}}{\sum_{j=1}^{4} e^{\beta_{j,k}  \mathbf{X}_i}}\right)^{[c_i=c]}
+\end{align*}
+
+, thus we estimate parameters $(\bm{\gamma}, \bm{\beta})$ with an EM algorithm using choice (default), and observable characteristics: $(c_i,\mathbf{W}_i,\mathbf{X}_i)$.
+
+\begin{table}[H]
+\caption{FMM}
+\label{fmm_table}
+\begin{center}
+\scriptsize{\input{./Tables/fmm_types.tex}}
+\end{center}
+ \scriptsize
+
+%\textit{Do file: } \texttt{fmm.do}
+\end{table}
+
+\begin{figure}[H]
+    \caption{Treatment effect of Type 1 individuals}
+    \label{fmm_hte}
+    \begin{center}
+    \begin{subfigure}{0.475\textwidth}       
+            \caption{Probability of Type 1 vs HTE}
+            \centering
+        \includegraphics[width=\textwidth]{Figuras/binscatter_tau_classpost.pdf}
+    \end{subfigure}
+   \begin{subfigure}{0.475\textwidth}
+        \caption{Type 1 vs HTE}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/benefit_type1p.pdf}
+    \end{subfigure}
+    \end{center}
+     \scriptsize 
+     After estimating the FMM, we compute the probability for each individual of belonging to each class, the x-axis represents the probability of being Type $1$, while the y-axis shows the HTE.
+A positive relation indicates that Type $1$ individuals are more benefited from commitment.
+      %\footnotesize{ \textit{Do file: }  \texttt{fmm.do}} 
+\end{figure}
+
+\subsubsection{LATE: TOT \& TUT}
+\vspace{.2in}
+\normalsize
+\linespread{1.25}
+
+ Recall that $Z_i$ is the observed, randomly assigned experimental allocation, where $Z_i=0$ denotes the control arm, $Z_i=1$ denotes the forced-fee arm, and $Z_i=2$ is the choice arm.
+Let $T_i$ be the unobserved choice type.
+$T_i=0$ when individual $i$ does not choose commitment  given the choice and $T_i=1$ when chooses commitment given the choice.
+Finally, $D_i = Z_i\times \mathds{1}(Z_i\neq 2) + T_i\times \mathds{1}(Z_i=2)$ is the observed treatment indicator, and $Y(d,z)$ is the potential outcome function for $d=0,1$, and $z=0,1,2$.
+
+ To identify assortative selection we first need to estimate the following quantities: $\mathbb{E}(Y_1-Y_0\;|\;T=1)$ the Treatment on the Treated (TOT), and $\mathbb{E}(Y_1-Y_0\;|\;T=0)$ the Treatment on the Untreated (TUT).
+
+ To point identify the above quantities, we make the following assumptions.
+
+ \begin{assumption}[Exclusion Restriction]
+$Z$ only affects $Y$ through its effect on $D$ : $Y(d,z) = Y(d)$
+ \end{assumption}
+
+  \begin{assumption}[Independence Assumption]
+$Z \perp (Y_0, Y_1, T)$
+ \end{assumption}
+
+The following intermediate Lemmas will help us derive that both TOT and TUT are point identified.
+
+\begin{lem}
+$\Pr(T=1) = \E[D\;|\;Z=2]$
+\end{lem}
+\begin{proof}
+Since $T\perp Z$, 
+$$\E[D\;|\;Z=2] = \E[Z\times \mathds{1}(Z\neq 2)+ T\times\mathds{1}(Z=2)\;|Z=2] = \E[T\;|\;Z=2] = \E[T] = \Pr(T=1)$$
+\end{proof}
+
+\begin{lem}
+$\E[Y_0] = \E[Y\;|\;Z=0]$
+\end{lem}
+\begin{proof}
+Since $Z\perp Y_0$, 
+\begin{align*}
+\E[Y\;|\;Z=0] =& \E[\mathds{1}(Z=0)Y_0+\mathds{1}(Z=1)Y_1+\mathds{1}(Z=2)\{(1-T)Y_0+TY_1\})\;|\;Z=0]\\   
+=&\E[Y_0\;|\;Z=0] = \E[Y_0]
+\end{align*}
+\end{proof}
+
+\begin{lem}
+$\E[Y_1] = \E[Y\;|\;Z=1]$
+\end{lem}
+\begin{proof}
+Since $Z\perp Y_1$, 
+\begin{align*}
+\E[Y\;|\;Z=1] =\E[Y_1\;|\;Z=1] = \E[Y_1]
+\end{align*}
+\end{proof}
+
+\begin{lem}
+$\E[Y_0\;|\;T=0] = \E[Y\;|\; D=0,Z=2]$
+\end{lem}
+\begin{proof}
+If $Z=2$, then $D=0$ if and only if $T=0$. Hence,
+\[\E[Y\;|\;D=0, Z=2] = \E[Y_0\;|\;D=0, Z=2] = E[Y_0\;|\;T=0, Z=2]=\E[Y_0\;|\;T=0]\]
+since $Y_0\perp T\;|\;Z$
+\end{proof}
+
+\begin{lem}
+$\E[Y_1\;|\;T=1] = \E[Y\;|\; D=1,Z=2]$
+\end{lem}
+\begin{proof}
+If $Z=2$, then $D=1$ if and only if $T=1$. Hence,
+\[\E[Y\;|\;D=1, Z=2] = \E[Y_1\;|\;D=1, Z=2] = E[Y_1\;|\;T=1, Z=2]=\E[Y_1\;|\;T=1]\]
+since $Y_1\perp T\;|\;Z$
+\end{proof}
+
+\begin{theorem} $\E[Y_1-Y_0\;|\; T=1]$ is point identified
+\end{theorem}
+
+\begin{proof}
+Since $\E[Y_1\;|\; T=1] = \E[Y\;|\; D=1, Z=2]$ by Lemma 5, it suffices to show that $\E[Y_1\;|\;T=0]$ is point identified. By iterated expectations:
+\[E[Y_0] = \E_T\E[Y_0\;|\;T] = (1-p)\E[Y_0\;|\;T=0]+p\E[Y_0\;|\;T=1]\]
+where $p:=\E[T]=\Pr(T=1)$, and re-arranging,
+\[\E[Y_0\;|\;T=1] = \frac{1}{p}\left(E[Y_0] -(1-p)\E[Y_0\;|\;T=0]\right)\]
+Finally, substituting the result of Lemmas 1, 2, and 4, we obtain
+\[\E[Y_0\;|\;T=1] =\frac{1}{\E[D\;|\;Z=2]}\left\{\E[Y\;|\;Z=0]-(1-\E[D\;|\;Z=2])\E[Y\;|\;D=0, Z=2]\right\}\]
+and the RHS is a function of observed data only.
+\end{proof}
+
+\begin{theorem} $\E[Y_1-Y_0\;|\; T=0]$ is point identified
+\end{theorem}
+
+\begin{proof}
+Since $\E[Y_0\;|\; T=0] = \E[Y\;|\; D=0, Z=2]$ by Lemma 4, it suffices to show that $\E[Y_0\;|\;T=1]$ is point identified. By iterated expectations:
+\[E[Y_1] = \E_T\E[Y_1\;|\;T] = (1-p)\E[Y_1\;|\;T=0]+p\E[Y_1\;|\;T=1]\]
+where $p:=\E[T]=\Pr(T=1)$, and re-arranging,
+\[\E[Y_1\;|\;T=0] = \frac{1}{1-p}\left(E[Y_1] -p\E[Y_1\;|\;T=1]\right)\]
+Finally, substituting the result of Lemmas 1, 3, and 5, we obtain
+\[\E[Y_1\;|\;T=0] =\frac{1}{1-\E[D\;|\;Z=2]}\left\{\E[Y\;|\;Z=1]-\E[D\;|\;Z=2]\E[Y\;|\;D=1, Z=2]\right\}\]
+and the RHS is a function of observed data only.
+\end{proof}
+
+\begin{figure}[H]
+    \caption{Bootstrap inference for the difference between TOT-TUT}
+    \label{bootstrap_tot_tut}
+    \begin{center}
+    \begin{subfigure}{0.31\textwidth}
+        \caption{Simple}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/tot_tut_btsp1.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.31\textwidth}
+        \caption{Admin controls}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/tot_tut_btsp2.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.31\textwidth}
+        \caption{Admin + Survey controls}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/tot_tut_btsp3.pdf}
+    \end{subfigure}
+
+    \end{center}
+     \scriptsize  Given that all of the arms are effectively randomly sampled form the same pool, we can also estimate the TOT and TUT with the pooled regression: $Y_i = \beta_0\mathds{1}(Z_i=0)+\beta_1\mathds{1}(Z_i=1)+\beta_2\mathds{1}(Z_i=2)+ \epsilon_i$, and then this test statistic just becomes the F-test on $\frac{\widehat{\beta_2}-\widehat{\beta_0}}{p}$ for the TOT, $\frac{\widehat{\beta_1}-\widehat{\beta_2}}{1-p}$ for the TUT, and an F-test on the difference between these two quantities to test whether the gains are different between compliers and non-compliers.
+Recognizing the stochastic nature of the compliance rate, we also bootstrap this quantity before running the previous regression.
+The red line shows the point estimate for the difference between TOT-TUT, and the gray bar in the x-axis shows a 95\% confidence interval for this difference.
+Panel (a) shows the difference between the TOT and TUT without any controls, while panel (b) and (c) adds admin controls and admin + survey controls respectively.
+          %\footnotesize{ \textit{Do file: }  \texttt{tot\_tut.do}}
+\end{figure}
+
+\begin{figure}[H]
+     \caption{TOT-TUT CDF}
+     \label{tot_tut_ecdf}
+    \begin{center}
+    \begin{subfigure}{0.6\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/cdf_tot_tut.pdf}
+    \end{subfigure}
+    \end{center}
+    \scriptsize
+       Equipped with estimates for the TOT and TUT for each individual $i$ from an Instrumental Random Forest we compute the ECDF for this quantities.
+The solid line is the ECDF for the TOT, the dashed line is the ECDF for the TUT, and the dotted line plots the difference between the TOT and the TUT - the blue dashed line in the x-axis shows the points where this difference is significant.
+The bold black interval at the bottom of the graph is the mean for the TOT distribution (0.07), while the gray interval shows the mean for the TUT distribution (0.10).
+
+          %\footnotesize{ \textit{Do file: }  \texttt{tot\_tut\_insforest.do}}
+\end{figure}
+
+\begin{figure}[H]
+     \caption{Exclusion restriction}
+     \label{exclusion_restriction}
+    \begin{center}
+    \begin{subfigure}{0.6\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/exclusion_restriction.pdf}
+    \end{subfigure}
+    \end{center}
+    \scriptsize This figure serves as a test for the exclusion restriction in the point identification for the TOT and the TUT.
+It shows the effect on the effective cost/loan ratio for the forced-fee arm and the choice arm, together with the decomposition of the choosers and non-choosers.
+Note that a) being forced into the treatment (Forced fee) has the same effect as choosing it (Choosers), and b) not choosing the treatment (Non chooser) has no effect with respect to the control.
+
+          %\footnotesize{ \textit{Do file: }  \texttt{exclusion\_restriction.do}}
+\end{figure}
+
 %---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------

### 2022-01-26 donde.tex
Figure 8 - panel (d)
checkpoint before edits of tables and figues

@@
 Jose Maria Barrero, Andrei Gomberg, Emilio Gutierrez, David Laibson, Aprajit Mahajan, Matt Rabin, Charlie Sprenger, and seminar participants at ITAM provided valuable feedback.}}
-\author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira   \thanks{Seira: ITAM, enrique.seira@gmail.com (corresponding author); Meza: University of California at Berkeley, isaac.meza@berkeley.edu; Sadka: ITAM, jsadka@itam.mx} }
+\author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira   \thanks{Seira: ITAM, enrique.seira@gmail.com (corresponding author); McIntosh:  University of California San Diego, ctmcintosh@ucsd.edu; Meza: University of California at Berkeley, isaac.meza@berkeley.edu; Sadka: ITAM, jsadka@itam.mx} }
 \date{This draft:  \today \\[2 cm]}
@@
 
-% \section{Introduction}
-
-Many institutions ---firms, schools, financial contracts--- restrict choice using built-in commitment mechanisms which help workers, students, borrowers overcome self-control problems.
+\section{Introduction}
+Many people have a difficult time accumulating and retaining capital unless they are provided a structure within which to do so.
+The behavioral lens on intertemporal financial services has provided critical insights on this problem, suggesting that saving from cash-in-hand is challenging \citep{Ashraf, Pascaline}, that credit may be preferred to savings as a way of accumulating capital simply because credit repayment contracts provide more structure \cite{Murdoch}, and even that the absence of structured financial contracts may be a key barrier preventing the poor from climbing out of poverty \citep{bertrand2004behavioral, collins2009portfolios}.
+A large behavioral literature has illustrated that the addition of commitment-style product features improves the ability to accumulate savings \citep{thaler2004save, prina2015banking, brune2016facilitating, callen2019headwaters} and to retire debt \citep{Bertrand, heidhues2010exploiting}.
+As a consequence, credit markets featuring limited-liability loans such as small-business financing or microfinance typically take a highly structured approach to credit contracts with frequent repayments and reminders as a way of inducing repayment.
+As pointed out by \cite{Laibson2018}, because many of these forms of commitment may be desirable to principals but not demanded by agents (or by the right agents), these mechanisms are often ‘shrouded’, meaning that commitment is embedded in products in ways that are not advertised to clients as such.
+
+In this paper we examine pawn contracts, an understudied form of credit despite their relative ubiquity \citep{carter2012pawnshops}, and a major vehicle through which poor households may dis-accumulate savings.
+There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues.
+In China it is a 43 billion dollar industry.\footnote{\url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.} Our partner, a Mexican pawn lender (henceforth Lender $P$) alone served more than 1 million clients in the last 3 years with more than 4 million contracts.
+Pawnshop lending presents an inverted lending case:  since these loans are over-capitalized, the principal in the lending contract stands to gain the most when agents default.
+Our collaborating lender gave only 70\% of the value of the pawn in credit, and charged a monthly interest rate of 7\% for loans of a three-month duration, with a flexible no-reminders contract typical of the industry that can be paid back anytime before the loan comes due.
+This combination of features means that the lender makes 90\% more profit over three months for a borrower who defaults than one who repays (30\% of collateral value recovered under default, 15.8\% of collateral value paid in interest if loan fully repaid).
+While an older literature considers the exploitative potential in over-collateralization and underpricing of collateral \citep{basu1984implicit}, the implication of such contracts has not been analyzed in the behavioral literature.
+When the lender desires default, the repayment-inducing features of commitment-style repayment contracts become undesirable and there may be incentives for the principal to create contracts with no structure, no reminders, and simple balloon payments that represent the opposite of what the behavioral literature tells us will induce repayment.
+To repurpose the language of \cite{Laibson2018}, we suggest that pawn contracts effectively shroud their \textit{lack} of commitment to induce default in a manner not obvious to borrowers.
+Given that pawnshops, moneylenders, and paycheck lending institutions are likely to face client pools disproportionately made up of impatient and time-inconsistent individuals, the design of such contracts may have first-order consequences for the financial lives of the poor.
+
+Against this backdrop, we implement a multi-arm randomized control trial covering close to 10,000 pawnshop clients in 6 branches of Lender $P$ in Mexico City, using a design built to test the demand for and impact of commitment in pawn repayment contracts.
+Our control arm illustrates the costs of the status quo contract; fully 57\% of borrowers default and so lose their pawn.
+We then implement a `commitment choice’ arm, in which borrowers are able at the time of taking a loan to opt in to a structured repayment contract, in which they are asked to make three monthly payments rather than one balloon payment at the end, with each monthly payment including the accrued interest at that time, and borrowers levied a nominal fee of 2\% of that month's payment in case of delinquency as a reminder/reinforcement of the importance of these interim payments.
+In addition, we include a `forced commitment’ arm, in which all borrowers are required to repay using the commitment structure.
+The combination of voluntary and forced commitment in the same study allows us to address several key questions.
+First, does using more structured repayment contracts help pawnshop borrowers to achieve higher repayment rates, thereby saving them money?
+Second, do borrowers recognize this benefit, demanding commitment in sufficient numbers to meaningfully change repayment behavior?
+Finally, and most uniquely, because we incorporate the forced commitment arm, we are able to ask whether the \textit{right} borrowers voluntarily demand commitment, gaining point identification for the treatment on compliers and the treatment on non-compliers by comparison across the control, choice, and forced arms.
+
+Our results suggest that the structure of the commitment is strongly effective in preventing default, with the average individual in the forced arm paying financing costs inclusive of fees that are 9.4\% lower than the control (from \$3157 to \$2860 MXN), while the likelihood of recovering their pawn increases by 26\% (from 43\% to 55\%).
+Results are robust qualitatively to including transport costs of going to the branch plus losing a day's wage for each visit, suggesting that in the context of a commitment structure it is possible to save borrowers money by charging them fees!
+Importantly, the benefits are distributed broadly: almost the whole distribution of treatment effects shows cost savings; however those most economically vulnerable, and those most overconfident about their probability of repayment, experience larger gains.\footnote{As in \cite{Rabin2018} we contrast subjects' \textit{own predictions} of their behavior with their actual behavior, but we do it in a natural setting.}  Treatment effects are concentrated in the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery.
+That is, the commitment contract induces people who would otherwise pay something towards recovery, to pay more and faster and thus recover their pawn more at a cheaper financial cost.
+
+Borrowers assigned to the forced commitment contract are 5 percentage points (100\% of the mean) more likely than the control group to ask for another loan in the future, suggesting that they liked the commitment contract after experiencing it.
+However, when offered the choice of commitment, very few borrowers elect to commit voluntarily.
+Only 10\% of the choice arm takes up the contract, and none of the core study outcomes are significantly improved by the ability to choose commitment.
+
+Most importantly, our multi-arm design allows us to show that the \textit{wrong} people choose commitment when offered it.
+We illustrate this point in three distinct ways.
+First, we use a Random Forest algorithm \citep{atheygrf} to estimate individual-level treatment effects for the forced versus control arm, and show the benefits of forcing to be significantly negatively correlated with the propensity to choose commitment estimated from the choice arm.
+93\% of those who did not opt for the commitment contract would have been better off with it, while only 1\% of those who chose commitment would have been better off without it.
+Second, a Boosted Classification Algorithm arrives at a similar answer, showing that the borrowers naturally cluster into two groups, one of which is likely to choose commitment and does not benefit from it, and the other the reverse.
+Finally, estimating LATEs on compliers and non-compliers alike we show that the estimated treatment effect on non-compliers is larger than the treatment effect on compliers.
+That is, those choosing commitment benefit less from commitment than those not choosing it.
+Hence our results show clearly that a paternalistic policy forcing borrowers into a more rigid and structured repayment regimen is uniquely beneficial to them.
+While this perverse relationship between choice and benefits from commitment echo closely the findings of \cite{Sprenger} we are the first to be able to examine this relationship using a high-stakes, money-metric outcome in a natural field environment.
+
+Additional evidence of the importance of paternalism in pawnshop commitment is provided by two additional study arms offering variants of `soft' commitment.
+In one arm all borrowers were asked to commit to make three monthly payments instead of a single balloon payment, but no external reminders or fees were imposed.
+In a second borrowers were given the ability to choose whether to engage in this form of soft commitment.
+Both of these arms are completely ineffective, suggesting that it is the combination of external imposition of the contract along with the teeth provided by the reminder and fees that generate the savings to borrowers relative to the status quo contract.
+
+What explains the persistence of a contract so contrary to borrowers’ interests?
+First, we show substantial levels of over-optimism among borrowers.
+Those most likely to benefit from the commitment contract and \textit{not} choose it are the individuals who most systematically over-estimate their own probability of repayment at the time of taking the loan.
+Second, the existence of commitment-style repayment contracts in pawnshop lending is novel in Mexico.
+While forcing individuals into commitment does not cause them to demand it in subsequent loans, \textcolor{red}{in Table \ref{iv_pf}} we show observational evidence of `learning by not doing’:  individuals offered commitment who elect not to take it and subsequently default \textit{do} learn about the benefits of commitment, demanding commitment loans at higher rates on subsequent pawn contracts when given the choice.
+Finally, while we are working with a lender who has a social mission and is interested in understanding how to help borrowers, there is no free lunch.
+The dramatic improvements in borrower income arising from the commitment contract come directly from the pockets of lenders, reinforcing that the pawn industry as a whole has a strong interest in retaining the status quo.
+
+Our results suggest that pawn lending markets capture borrower wealth in ways not well summarized by interest rates.
+By overcollateralizing and then structuring loan contracts in a manner encouraging of default, lenders are able to extract substantial value independent of the interest charged.
+Further, the `nudge’ approach generally favored by the behavioral literature (voluntary commitment) may not be adequate; we estimate that over 50\% of the borrowers in our study are naïve hyperbolics in the sense that they would benefit from commitment but will not choose it.
+While our results are driven by the intersection of overcollateralization and a potential selection of the borrower pool towards myopia and short-term financial thinking, these attributes are likely to be present in many types of pro-poor financial markets where individuals lack the credit histories to be able to leverage short-term credit without collateral.
+This suggests that regulators of such markets would do well to consider the broader financial costs of lending products, including what is paid through equilibrium default, and to consider imposing more structured lending products that tilt the scales towards allowing borrowers to repay.
+While commitment-style repayment contracts decrease effective liquidity by requiring faster repayment of a given loan, the improvement in expected borrower returns are so substantial as to prove welfare improving at all but the most astronomical discount rates.
+
+These conclusions speak to several strands of the literature.
+First, they suggest consequential ways in which different financial services draw client pools with distinct behavioral biases.
+While research in microfinance markets has not found the same benefits from providing a more regularized repayment environment \citep{Pande}, those experiments are performed over the top of highly structured contracts and among borrower pools who may have selected into that type of lending precisely because it provides structure.
+Second, we broaden the analysis of the extent to which voluntary commitment mechanisms are desirable.
+Like our study, commitment demand has been found to be low in a number of contexts (\cite{Ashraf}, \cite{Gine}, \cite{Ted}, \cite{Royer}, \cite{Sprenger}), and by illustrating a mechanism for the failure of self-commitment (over-optimism) we may help contextualize those studies in which demand has been found to be more robust (\cite{Kremer},  \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}, \cite{Pascaline}).
+Finally, we provide only the second case in the literature, and the first in the analysis of financial products, to illustrate the perverse result that those who opt into commitment are precisely the individuals who do not need it \citep{Sprenger}.
+
+The remainder of the paper is structured as follows:  section \ref{context} provides context and describes the data sources.
+Section \ref{Data} presents summary statistics and defines our main outcome variables.
+Section \ref{Experiment} describes the experiment and shows pre-treatment balance across arms.
+Section \ref{fee-commitment} estimates the effect of forcing clients into the fee-commitment contract, while Section \ref{fee-choice} studies the effects of choice.
+Section \ref{conclusion} concludes.
+
+%\section{Old Introduction}
+
+%Many institutions ---firms, schools, financial contracts--- restrict choice using built-in commitment mechanisms which help workers, students, borrowers overcome self-control problems.
 For instance, ``[mortgages restrict choice] with a fixed repayment stream and mandatory principal repayment'' \citep{Laibson2018}.\footnote{\cite{Laibson2018} also mentions that ``Firms do limit their workers' freedom with intermediate deadlines, progress reports, production targets'', and schools with ``pop quizzes, classroom attendance requirements, cold calling, graded problem sets, deadlines''.} At the same time  these same firms shroud and don't market these commitment features, presumably because students, workers and borrowers don't welcome these restrictions.
@@
 %In this paper we will study the effect of restricting freedom of contract choice on two outcomes: pawn recovery and financing cost, not overall welfare.
-We want to clarify that we are using the word ``paternalism'' in a restricted sense, meaning only that a large majority of clients would incur in lower financial costs from being forced into installment contracts instead of letting them choose.
+%We want to clarify that we are using the word ``paternalism'' in a restricted sense, meaning only that a large majority of clients would incur in lower financial costs from being forced into installment contracts instead of letting them choose.
 We are not making claims about overall welfare which is a slippery concept if we take into account the possibility of biased beliefs and preferences.}
 
-This paper studies the benefits of restricting choice in the context of pawnbroker lending.
+%This paper studies the benefits of restricting choice in the context of pawnbroker lending.
 Pawn loans are one of the oldest, most understudied, and most prevalent forms of borrowing.
@@
 
-We implemented a large randomized control trial with close to 10,000 pawnshop clients in 6 branches of Lender $P$ in Mexico City.
+%We implemented a large randomized control trial with close to 10,000 pawnshop clients in 6 branches of Lender $P$ in Mexico City.
 We answer five main questions using this experiment.
@@
 Promises change behavior significantly in laboratory settings, but we know little about their effect in natural environments.\footnote{%Some papers in this space are \cite{PromisesPartnerships}, \cite{Vanberg}, \cite{Belot2010}, \cite{WhyDoPromises}, \cite{FurtherPromises}, \cite{Ismayilov2017}.
-There is some actual policy around using promises for loans: the government Mexico has created a program called ``Loans on your word'' for uncollateralized borrowing (\url{http://tiny.cc/yfmnmz}), but unfortunately there is little information about them.} Finally, is \textit{giving choice} among contracts better than forcing clients into payment-commitment contracts in terms of minimizing financing costs incurred and the likelihood of recovering their pawn?
-Or on the contrary, is it better to force the installment contract
-paternalistically?
-
-The experiment involved 5 arms, with randomization happening at the branch-day level.
+%There is some actual policy around using promises for loans: the government Mexico has created a program called ``Loans on your word'' for uncollateralized borrowing (\url{http://tiny.cc/yfmnmz}), but unfortunately there is little information about them.} Finally, is \textit{giving choice} among contracts better than forcing clients into payment-commitment contracts in terms of minimizing financing costs incurred and the likelihood of recovering their pawn?
+Or on the contrary, is it better to force the installment contract paternalistically?
+
+%The experiment involved 5 arms, with randomization happening at the branch-day level.
 It is described in detail in Section \ref{Experiment}.
@@
 The first one involves a group of clients that were given only the status quo flexible payments contract (henceforth the \textit{status-quo forcing group}).
-The second arm (\textit{fee-forcing group}) was given a monthly payment commitment contract, which stipulated that clients had to pay 1/3 of their loan plus accumulated interest in each of the 3 months of the term length.
+The second arm (\textit{Forced Commitment group}) was given a monthly payment commitment contract, which stipulated that clients had to pay 1/3 of their loan plus accumulated interest in each of the 3 months of the term length.
 Failing to do this would result in a fee of 2\% of the amount due that month.
-A third group (\textit{Fee-choice group}) gave clients a choice between these two contracts.
-
-Results are striking.
+A third group (\textit{Commitment Choice group}) gave clients a choice between these two contracts.
+
+%Results are striking.
 First, we find that forcing clients into frequent payment commitment contracts causes them on average to save on financing cost and to recover their pawn more.
@@
 %The commitment contract also causes payments to start 8 days earlier and be 16\% more frequent, compared to the control group.
-Treatment effects are concentrated in the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery.
+%Treatment effects are concentrated in the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery.
 That is, the fee-commitment contract induces people who would otherwise pay something towards recovery, to pay more and faster and thus recover their pawn more at a cheaper financial cost.
@@
 
-Second, in spite of these estimated benefits for almost all clients, actual demand for the fee-commitment contract is low.
+%Second, in spite of these estimated benefits for almost all clients, actual demand for the fee-commitment contract is low.
 Only 10\% of the group offered a choice between the monthly payment fee-commitment contract and the status-quo one chose the former.
@@
 %\cite{Laibson2015} shows that the lost flexibility resulting from a commitment contract can severely limit take-up when agents are naive about their self control, even though commitment could be welfare improving for them.
-Owing to this low take-up, we estimate zero average treatment effects of the \textit{fee-choice} arm on financial cost and on pawn recovery throughout the quantile distribution.
+%Owing to this low take-up, we estimate zero average treatment effects of the \textit{Commitment Choice} arm on financial cost and on pawn recovery throughout the quantile distribution.
 
@@
 
-Third, combining the forcing and the choice arms ---a unique feature of our experiment--- allows us to estimate the counterfactuals to answer the question of how much money is left on the table by giving choice to clients.
-We calculate that about {80}\% of clients in the fee-choice group chose contracts that induced \textit{higher} financial cost.
+%Third, combining the forcing and the choice arms ---a unique feature of our experiment--- allows us to estimate the counterfactuals to answer the question of how much money is left on the table by giving choice to clients.
+We calculate that about {80}\% of clients in the Commitment Choice group chose contracts that induced \textit{higher} financial cost.
 On average they spend an extra \${238} MXN, close to {11}\% of the average loan value.
@@
 
-Inspired by a significant lab experiment literature on the effects of promises on behavior, and by research showing that a small fee could drastically reduce demand for commitment of (partly) naive present-biased borrowers (\cite{Laibson2015}), we implemented a ``psychological commitment'' product in the form of a salient promise to pay.
+%Inspired by a significant lab experiment literature on the effects of promises on behavior, and by research showing that a small fee could drastically reduce demand for commitment of (partly) naive present-biased borrowers (\cite{Laibson2015}), we implemented a ``psychological commitment'' product in the form of a salient promise to pay.
 \cite{PromisesPartnerships}, \cite{FurtherPromises}, \cite{Vanberg}, and \cite{Ismayilov2017} find that the ability to make a promise about behaving a certain way makes the individual more likely to adhere to the promised behavior.
@@
 
-To measure the causal effect of promises we implemented two other treatment arms.
-A \textit{promise-forcing} arm exactly analogous to our \textit{fee-forcing arm} except that instead of telling them that there was a fee if they didn't pay on time, we made borrowers promise that they would pay one third of the amount in each of the 3 months, and told them that if they didn't they would have broken their promise and not kept their word.
+%To measure the causal effect of promises we implemented two other treatment arms.
+A \textit{promise-forcing} arm exactly analogous to our \textit{Forced Commitment arm} except that instead of telling them that there was a fee if they didn't pay on time, we made borrowers promise that they would pay one third of the amount in each of the 3 months, and told them that if they didn't they would have broken their promise and not kept their word.
 Because salience is key we made them sign a (legally non-binding) personal promise and emphasized that we were counting on them to keep their promise.
@@
 
-We document three main results in the promise arms.
-First, demand for the promise-commitment contract is three times larger than for the fee-commitment contract, with {31}\% take-up.
+%We document three main results in the promise arms.
+First, demand for the Soft Commitment contract is three times larger than for the fee-commitment contract, with {31}\% take-up.
 This difference shows that clients are indeed taking into account the contractual parameters when they choose, and that the fee commitment was probably too strong from their point of view.
@@
 Third, being forced in to the \textit{Promise} contract also had zero effects on average and throughout the distribution on financing cost and pawn recovery.
-%\footnote{There is a decrease in financial cost in the 50th and 75th quantiles in the forced promise-commitment arm however.}
-Promises did not provide enough commitment so as to be reflected in behavior.
+%\footnote{There is a decrease in financial cost in the 50th and 75th quantiles in the forced Soft Commitment arm however.} Promises did not provide enough commitment so as to be reflected in behavior.
 This is one of the first  experiments using promises in the field, and results are in striking contrast with those in the lab.
 
-This paper contributes to several strands of literature.
+%This paper contributes to several strands of literature.
 First, we focus on an important new context: pawnshop borrowing.
@@
 
-Second, a significant literature has shown that demand for commitment exists.
+%Second, a significant literature has shown that demand for commitment exists.
 But while it is low in some contexts (\cite{Ashraf}, \cite{Gine}, \cite{Ted}, \cite{Royer}, \cite{Sprenger}), it is high in others (\cite{Kremer},  \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}, \cite{Pascaline}).
@@
 
-Third, and most importantly, we study both causal effects and selection into frequent payment commitment loan contracts at the same time and for the same population in a single experiment.
+%Third, and most importantly, we study both causal effects and selection into frequent payment commitment loan contracts at the same time and for the same population in a single experiment.
 We know of no other experiment in the credit market which simultaneously combines forcing and choice arms.
@@
 
-Fourth, we provide new evidence on the payment frequency debate.
+%Fourth, we provide new evidence on the payment frequency debate.
 The literature has found null effects on installment frequency loan default \cite{Pande}.
@@
 
-We believe that taken together, our results (commitment matters, small fees have large effects on behavior, people don't choose the cost reducing contract) call for a behavioral explanation.
+%We believe that taken together, our results (commitment matters, small fees have large effects on behavior, people don't choose the cost reducing contract) call for a behavioral explanation.
 Most of the literature tries to connect commitment problems with measures present biased preferences.
@@
 
-Finally, even though personal promises feature prominently in microfinance guidelines\footnote{e.g.
+%Finally, even though personal promises feature prominently in microfinance guidelines\footnote{e.g.
 \url{https://grameenfoundation.org/documents/GrameenGuidelines.pdf}, p.36.} we know of no other study that has tried to isolate their effects on loan repayment.
@@
 %not least because the laboratory literature is implemented on more tightly controlled environments and focused on subtler aspects of promising, like their effects on second order beliefs and guilt aversion.
-The context is also different since
-The lab literature has focused on very structured investment games between two players and looked at the effects of promises on trust and cooperation.
+The context is also different since The lab literature has focused on very structured investment games between two players and looked at the effects of promises on trust and cooperation.
 In our case the bank is not a strategic player that responds to the promise, or a person to which the client can feel guilt towards (although the teller is).
@@
 Section \ref{Experiment} describes the experiment and shows pre-treatment balance across arms.
-Section \ref{fee-commitment} estimates the effect of forcing clients into the fee-commitment contract, while Section \ref{fee-choice} studies the effects of choice.
+Section \ref{fee-commitment} estimates the effect of forcing clients into the fee-commitment contract, while Section \ref{Commitment Choice} studies the effects of choice.
 Section \ref{model} collects all findings and presents a model to rationalize them qualitatively.
@@
 Pawn loans existed in antiquity at least since the Roman Empire, and there are records of it in China about 1,500 years ago \citep{PawnShops}.
-
-%Lender $P$ was interested in understanding why half of their clients lost their pawn.
-Default is high in this context  compared to many papers in the microfinance literature.\footnote{\cite{Pande} study of the effect of payment frequency in a context where the rate of default is close to 1\%.}
-
 In spite of the high prevalence and long history, pawnshop borrowing has not received much attention in the economics literature.
@@
 Although the author meant this list as an instance of low requirements, they would render virtually all poor households in the developing countries ineligible.
+
+%Lender $P$ was interested in understanding why half of their clients lost their pawn.
+Default is high in this context  compared to many papers in the microfinance literature.\footnote{\cite{Pande} study of the effect of payment frequency in a context where the rate of default is close to 1\%.}
 
@@
 
-\subsection{Lender P and the status quo contract}
-
-We study pawnshop borrowing by partnering with Lender $P$, one of the largest pawn shops in Mexico, with more than one hundred branches spanning multiple States in Mexico.
-
-Lender P's business model is simple.
+\subsection{Status Quo Pawn Contracts}
+
+To study this market, we partnered with one of the largest pawn shops in Mexico, an institution with more than one hundred branches spanning multiple States in Mexico.
+This lender (whom we refer to as `Lender P') has a simple and typical business model.
 They take gold jewelry as collateral in exchange for a fraction the value of the piece, in cash.
@@
 Lender P had only one type of contract, henceforth the \textit{status quo} contract.
-It stipulated that the interest rate was 7\% \textit{per month} accumulated daily on the outstanding amount of the loan.
+It stipulated that the interest rate was 7\% \textit{per month} compounded daily on the outstanding amount of the loan.
 The loan had a 90 days term with 15 days' grace period, and the client could make payments at anytime with no penalty for pre-payment.
 If the client paid the principal plus the accumulated interest in less than 105 days, then she received back her pawn, otherwise the pawnbroker kept the piece and any payments made.
-Before the contract expired, the client had the right to renew it\footnote{Only 26\% renews twice or more.
-} (using the same collateral) for another 3 months by going to the pawnshop paying the accumulated interest and signing a new contract with exactly the same terms as the original one.
-%The pawnshop therefore makes money in three ways: by reselling the jewelry left as collateral on defaulted loans, by charging interest on non defaulted loans, and by keeping the payments made on defaulted loans.
-
+Before the contract expired, the client had the right to renew it  using the same collateral for another 3 months by going to the pawnshop paying the accumulated interest and signing a new contract with exactly the same terms as the original one.
+Only 26\% of borrowers renew twice or more.
 This contract was standard in the industry.
-The clients that pawned understood its conditions (as we verified in interviews) and still decided to pawn.\footnote{90\% of clients report in our survey that they have pawned before.} These clients have little or no access to other types of loans and value the convenience of pawn borrowing.
-We conjectured that potentially borrowers also like it because they are overconfident about the probability of recovering their pawn, as we show below.
-
-\subsection{High default rates}
+
+The clients that pawned understood its conditions (as we verified in interviews) and still decided to pawn.
+\footnote{90\% of clients report in our survey that they have pawned before.} These clients have little or no access to other types of loans and value the convenience of pawn borrowing.The population we are working with is economically vulnerable in the sense that 30\% of them could not pay either water, electricity \& gas or rent in the past 6 months.
+They often receive negative income shocks: 87\% said they are pawning because of an emergency, and only 13\% stated it was to use in a `non-urgent expense'.
+When asked why they are pawning this piece gr{5\%} responded gr{`lost a family member'}, gr{`a medical emergency'} (gr{11\%}), gr{`an urgent expense'} (gr{71\%}),
+
 Our context is one with high borrower default: 60\% of clients lose their pawn in a time span of 230 days from the date of pawning.
-This default is likely inefficient since clients report a subjective value that is almost twice its gold value on average.
-High default could be also detrimental from the lender's point of view since it may reduce the likelihood that the client becomes a return costumer.
-This could explain why Lender P was interested in  partnering with us to investigate whether a frequent payment contract would increase pawn recovery and costumer satisfaction, and whether there was demand for such a contract.
-
 One potential explanation for high default is that clients are really just selling their gold piece.
@@
 On average clients that lost their pawn paid 34\% of the value of their loan, and close to 42\% of clients extended the loan for another cycle and made payments in the second cycle (see Figure \ref{proxy_naive} in Appendix).
-
-\section{Data and summary stats} \label{Data}
-
-We worked in 6 branches of Lender $P$, of differing size and location, although for ease of implementation all of them in Mexico city.
-For these 6 branches we have two types of data, administrative data and survey data we collected for the experiment.
-
-\subsection{Administrative Data}
-The administrative data contains a unique identifier of the client, an identifier of the piece she is pawning, and the transactions relating to that piece.
-In particular, the value of the piece as assessed by the appraiser, the amount of money loaned (70\% of the value), and the date of the pawn transaction.
-As described below, for our experiment the administrative data recorded the type of contract for that pawn.
-After the pawn happened, we followed each transaction related to that piece in the administrative data: when payments were made and for what amounts, whether there was default (i.e.
-the client lost her pawn), and whether any late-payment fees (active for the relevant experimental arms) were imposed.
-We have this information for all the pawns that occurred in the experiment's 6 branches between August 2, 2012 and August 13, 2013, this includes all the pawns under our experiment but also those that happened 1 month before it started and up to 8 months after it ended.
-Figure \ref{exp_description}(a) shows the timing of the experiment and our admin data coverage.
-The black arrows represent the dates for which we have administrative data (before and after the experiment) for each branch, while the light gray segments represent the duration of the experiment.
-The experiment comprises 13,446 pawns, and our administrative data cover a total of 23,974 pawns.
-
-\subsection{Survey Data}
-
-We had a team of enumerators in each branch collect surveys and clearly explain the contract terms to walk-in clients.
-The enumerators were inside the branch and asked clients to complete a 5 minute survey before going to the teller window to appraise their piece and before they were told contract terms (i.e.
-before treatment status was known).
-It was short to avoid discouraging the potential clients from pawning, but at the same time it aimed to measure the following: demographics, proxies for income/wealth, education, self-control problems/present-biased preferences, experience pawning, if family or friends commonly asked for money, how time consuming and costly it was to come to the branch, the subjective probability of recovering the piece that they intended to pawn, the subjective value of their piece in money terms (how much money they would sell it for), among others.
-We surveyed 10,437 clients.\footnote{The Appendix \ref{baseline_survey} transcribes the questionnaire in English.} %\footnote{We also surveyed clients before and after the experiment, so our survey covers a larger sample that we are not using in this paper.}.
-Survey response rate is 78\%, and response is not related to admin data observables (details in Table \ref{balance_response} in the Appendix).
-
-\subsection{Summary statistics}
-
-Table \ref{SS} presents some summary statistics for the whole sample and by treatment arm.
-Because treatment arms are described below, here we concentrate on the overall average.
-Panel A describes variables from the administrative data.
-The average loan size is \$2197 MXN (\$105 USD).
-The average number of pawns per day per branch is 34.
-Only 42\% of clients recover their pawn.
-Even those that recover their pawn tend to pay it back at the last moment, with only 40\% paying before the 90th day.
-
-Panel B reports stats from our survey data.
-73\% of clients are women, with an average age of 43 years; 66\% of them have completed high school or more, and 90\% have pawned before, so that our sample has mostly experienced borrowers.
-Finally the subjective probability of recovery is close to 93\% on average, which contrasts with the 51 points lower actual recovery.
-Borrowers seem to be highly overconfident on average.
-The average subjective value they report for the pieces is 3069 MXN, much larger than the average appraised gold value of 2197 MXN.
-%This makes it inefficient for them to lose it.
-
-Since the main treatment involves making clients come to the branch to pay each month, the transaction costs of coming to the branch are important.
-The average time they take to come to the branch is 22 minutes, and the amount of money they spend in transport to do that is 11 MXN (\$0.60 USD).
-The population we are working with is economically vulnerable in the sense that 30\% of them could not pay either water, electricity \& gas or rent in the past 6 months.
-They often receive negative income shocks: 87\% said they are pawning because of an emergency, and only 13\% stated it was to use in a `non-urgent expense'.
-%When asked why they are pawning this piece gr{5\%} responded gr{`lost a family member'}, gr{`a medical emergency'} (gr{11\%}), gr{`an urgent expense'} (gr{71\%}),
-
-\subsection{Financing cost and Default} \label{FC_def}
-
-Our main dependent variables are loan default and financial cost incurred by the borrower.
+High default could be also detrimental from the lender's point of view since it may reduce the likelihood that the client becomes a return costumer.
+Lender P was explicitly interested in  partnering with us to investigate whether a frequent payment contract would increase pawn recovery, costumer satisfaction, and repeat borrowing, and to explore whether there was demand for such a contract.
+
+The pawnshop therefore makes money in three ways: by reselling the jewelry left as collateral on defaulted loans, by charging interest on non defaulted loans, and by keeping the payments made on defaulted loans.
+The interest rate typically used to calculate borrower APRs is thus a very inadequate measure of the effective cost of pawn loans.
+
+\subsection{Measurement of the Cost to Pawning} \label{Data}
+
+We now develop the measures of net financial costs to the borrower that are used as our core pecuniary outcomes.
+The two key measures are loan default, and the effective financial cost incurred by the borrower.
 Default is defined as losing the pawn.
@@
 We also report results using the subjective value of the pawn reported by the borrower in the survey again with similar results.
-This cost is calculated for a time period of 230 days after loan origination.
-Figure \ref{fc_pro_2_115} reports results using only the first 115 days.} Figure \ref{fc_hist}(a) plots a histogram of this financial cost in pesos for loans where the pawn was either recovered or lost.
-%Of those who renew, 83\% lose the pawn.
+This cost is calculated for a time period of 230 days after loan origination.}
+
+%Since the main treatment involves making clients come to the branch to pay each month, the transaction costs of coming to the branch are important.
+The average time they take to come to the branch is 22 minutes, and the amount of money they spend in transport to do that is 11 MXN (\$0.60 USD).
+
+We can use the control group for the study to present summary statistics on these core measures of default and financial cost.
+Figure \ref{fc_pro_2_115} reports results using only the first 115 days.
+Figure \ref{fc_hist}(a) plots a histogram of this financial cost in pesos for loans where the pawn was either recovered or lost.
+Of those who renew, 83\% lose the pawn.
 Figure \ref{fc_hist}(a) suggest that financial cost is significant, even for those that do recover their pawn.
@@
 
-\section{Experiment} \label{Experiment}
+\section{Experimental Design} \label{Experiment}
 
@@
 
-\noindent \textbf{Selection of branches.} Starting September 6, 2012, we implemented the experiment in 6 branches of Lender $P$.
+\vspace{.2in}
+\noindent \textbf{The Commitment Contract.} For the purpose of the experiment we designed a new contract that is identical to the status quo contract except that it enhances the regularity and salience of payments.
+It has the same interest rate (7\% \textit{per month}) which accumulates daily on outstanding debt, it has the same loan size/collateral ratio (70\%), it has the same loan term (90 days, and a grace period of 15 days), and the gold pawn gets appraised in the same way by the same appraisers.
+The Commitment contract however requires the client to make regular monthly payments for the duration of the contract, with the principal and interest payments split evenly across the three months of the contract (day 30, 60 and 90 after loan disbursement).
+The importance of this monthly payment was reinforced in two ways; first by reminders issued to any borrower delinquent on the monthly payments that they were supposed to be made, and secondly by the levying of a nominal fee (2\% of minimum due) that would be levied on individuals behind in their payments.\footnote{This fee was set by the lender, being deemed to be large enough to reinforce commitment but small enough that if clients had an emergency and could not pay, the fee would not cause the pawn to be unrecoverable.
+In contrast with \cite{John} we don't let the clients choose the size of the fee.
+That paper shows that doing this results in wrong choices by (partially) naive present biased consumers.
+Our fee is much smaller than the median in her experiment, as explained in the introduction.
+%We also experimented with a contract where there was no pecuniary fee for paying late but where we clients made a personal promise to pay monthly.
+}
+
+\vspace{.2in}
+\noindent \textbf{Treatment Arms.} Randomization was done at the branch-day level.
+Each day we randomly assigned which types of contracts were on offer that day in the branch, and therefore which contract the client signed.
+We have 5 different experimental arms:
+
+\begin{enumerate}
+    \item \textit{Control} arm: consisted of branch-days offering the status quo contract described in Section \ref{context}, and only this contract. 
+    \item \textit{Forced Commitment} arm: consisted of branch-days requiring all borrowers to use the Commitment contract described above.  
+    \item \textit{Commitment Choice} arm: consisted of branch-days offering the client \textit{a choice} between the Commitment contract, and the status quo contract.
+    \item \textit{Forced Soft Commitment} arm: consisted of branch-days in which borrowers were asked to sign a non-binding written commitment to pay monthly as in the Commitment contract, but no reminders or fees were imposed if they did not.\footnote{The client was made to sign a paper which said ``I promise to pay every month the corresponding sum of \_\_\_\_\_\_, on the dates \_\_\_\_\_\_, \_\_\_\_\_\_, and \_\_\_\_\_\_.
+This is \underline{not} a legal document and cannot be used in courts.
+It is just a \textit{personal promise}.
+If I do not comply I will not have kept my word''.
+After signing, the promise was read to the client by the appraiser.}%\footnote{Our setting does not allow us to separate if the client is making a promise to the bank teller or whether she is mentally interpreting this as an internal promise to herself as a goal.
+We thank Anett John for pointing this out.}
+    \item \textit{Soft Commitment Choice} arm: consisted of branch-days on which the client was given \textit{a choice} between the Soft Commitment and the status quo contract.
+\end{enumerate}
+
+We did not allocate equal number of days across arms, since we were interested in having more power in some of them.
+The number of branch days allocated to each were 84, 80, 93, 68, and 82, respectively.
+
+\vspace{.2in}
+\noindent \textbf{Randomization.}  Starting September 6, 2012, we implemented the experiment in 6 branches of Lender $P$.
 The branches were selected by Lender $P$ to be dispersed across Mexico city and have varying sizes.
@@
 
-\vspace{.2in}
-\noindent \textbf{The monthly installment contract.} For the purpose of the experiment we designed a new contract that is identical to the status quo contract in all respects except one.
-It has the same interest rate (7\% \textit{per month}) which accumulates daily on outstanding debt, it has the same loan size/collateral ratio (70\%), it has the same loan term (90 days, and a grace period of 15 days), and the gold pawn gets appraised in the same way by the same appraisers.
-The only difference is that it has a requirement that the client has to pay monthly: for the 3 month duration of the contract, at least 1/3 of the loan value (plus accumulated interest) has to be paid before day 30, 60 and 90 after loan disbursement.
-Failure to pay this amount triggers a penalty fee of 2\% of this minimum amount due, which is added to the amount that the client needs to pay to recover their pawn.
-This penalty acts as a commitment incentive to pay now vs paying later.
-The level of the penalty was determined by Lender P after talking to clients and based on Lender P's experience.
-They deemed 2\% something that was big enough to provide commitment but small enough that if clients had an emergency and could not pay, the fee would not cause the pawn to be unrecoverable.\footnote{In contrast with \cite{John} we don't let the clients choose the size of the fee.
-That paper shows that doing this results in wrong choices by (partially) naive present biased consumers.
-Our fee is much smaller than the median in her experiment, as explained in the introduction.
-We also experimented with a contract where there was no pecuniary fee for paying late but where we clients made a personal promise to pay monthly.}
-
-\vspace{.2in}
-\noindent \textbf{Randomization.} Randomization was done at the branch-day level.
-Each day the system chose which types of contracts were on offer that day in the branch, and therefore which contract the client signed.
  Branch personnel did not know which treatment would happen on which day.
@@
 
-\vspace{.2in}
-\noindent \textbf{Treatment Arms.} We have 5 different experimental arms:
-
-\begin{enumerate}
-    \item \textit{Status-quo forcing} arm: consisted of branch-days offering the status quo contract described in Section \ref{context}, and only this contract, as was standard. 
-    \item \textit{Fee-Forcing} arm: consisted of branch-days offering only the monthly installment contract with a fee for late payment as described above. 
-    \item \textit{Fee-Choice} arm: consisted of branch-days offering the client \textit{a choice} between the monthly installment with fee contract, and the status quo contract.
-    \item \textit{Promise-Forcing} arm: consisted of branch-days which offered the monthly payment contract only, but where there was no fee for paying late.
-Instead, the client was made to sign a paper which said ``I promise to pay every month the corresponding sum of \_\_\_\_\_\_, on the dates \_\_\_\_\_\_, \_\_\_\_\_\_, and \_\_\_\_\_\_.
-This is \underline{not} a legal document and cannot be used in courts.
-It is just a \textit{personal promise}.
-If I do not comply I will not have kept my word''.
-After signing, the promise was read to the client by the appraiser.\footnote{Our setting does not allow us to separate if the client is making a promise to the bank teller or whether she is mentally interpreting this as an internal promise to herself as a goal.
-We thank Anett John for pointing this out.}
-
-    \item \textit{Promise-Choice} arm: consisted of branch-days on which the client was given \textit{a choice} between the promise-forcing and the status quo contract.\footnote{We did not allocate equal number of days across arms, since we were interested in having more power in some of them.
-The branch days allocated to each -- in order-- were 84, 80, 93, 68, 82.}
-\end{enumerate}
-
-By comparing the \textit{fee-forcing} arm vs the \textit{status-quo} arm we estimate the causal effect of mandatory installment frequency that acts as a incentive to pay earlier vis-a-vis the pay-when-you-want contract.
-On the other hand, having arms where clients can choose among these contracts allows us to study clients' demand for commitment to pay earlier.
+By comparing the \textit{Forced Commitment} arm vs the \textit{Control} arm we estimate the causal effect of mandatory installment frequency that acts as a incentive to pay earlier vis-a-vis the pay-when-you-want contract.
+On the other hand, having arms where clients can choose among these contracts allows us to study clients' demand for commitment to pay earlier, and the nature of selection into this choice.
 A neoclassical consumer with no intra-household concerns would not voluntarily restrict her options of payment profiles (as in the monthly installment contract) by being subject to fees, since she can always replicate the monthly payment profile herself under the status quo contract if she so desired.
@@
 This value would be traded off against the value of lost flexibility.
-
-This design also allows us to test if promises work in a natural field environment which to our knowledge has not been done.
-Promises could have larger or smaller commitment value than a pecuniary fee, something that we test by comparing behavior in the \textit{promise-forcing} vs \textit{status quo} arms.
+This design also allows us to test the extent to which commitment must be externally imposed and reinforced to be effective, relative to softer and more self-directed forms of commitment.
+%Promises could have larger or smaller commitment value than a pecuniary fee, something that we test by comparing behavior in the \textit{promise-forcing} vs \textit{status quo} arms.
+
 Panel (b) of Figure \ref{exp_description} shows how many contracts the experiment has in each arm (rectangles).
@@
 
-%\subsection{Connection to the literature}
-%Our study connects with two strands of the literature on microfinance.
-But also to a nascent one that uses RCTs to study to what extent people self-sort to treatments that have larger beneficial treatment effects for them.
-On the microfinance literature the first paper we could find that used an RCT to evaluate the causal effect of frequent payments in loans is \cite{Pande}.
-In a group lending rosca context, they note that most contracts involved frequent repayments --even weekly in many instances-- even when this increases transaction costs.
-They note that clients could benefit from ``the fiscal discipline afforded by the more rigid payments''.
-Frequency could provide a commitment device for clients, could foster a payment habit, or could generate more trust from social interactions among the group of borrowers.
-All these potential benefits apply in our context, except those relating to social interactions, as we work with individualized loans.
-
-\vspace{.2in}
-\noindent \textbf{Balance.} Table \ref{SS} shows that randomization worked to achieve balance across clients in the different experimental arms.
-One concern was that after learning the conditions of the contract, clients could decide not to pawn.
+For the experiment to be meaningful, it is critical that clients understood the contract terms clearly.
+To ensure this, we built two `check-points'.
+First, two enumerators were present in each branch for the whole day during the duration of our experiment to explain the contract terms to clients.
+One of the aspects emphasized was that the frequent payment contract involved the commitment to pay \underline{each month} a third of the outstanding amount, and the nature of the reminders and fees associated with the Commitment arm.
+Figure \ref{ExplanatoryMaterial} translates a piece of the materials we used to explain the contracts (in this case a comparison sheet used in the Promise-Choice days to compare contracts terms side to side).
+The explanation took about 3-5 minutes and was pursued until the client said she understood the contract terms.
+Enumerators then asked clients to explain back the contract terms and corrected any misunderstandings.
+
+The second check-point was that before the clients signed the contract, the appraiser made them read them the ``Contract Terms Summary'' sheet shown in Figure \ref{PaperSlip}.
+It was a piece of paper given to clients after their piece had been appraised and the size of the loan determined, but before they signed their contract.
+The appraiser read it and asked the client to sign it as a proof of understating.
+%The sheet clearly indicates that this contract is a monthly payment one (numeral 1), that there is a penalty of 2\% for paying late (numeral 2), and the 3 payment dates (numeral 3).
+Finally, the bottom of the Figure \ref{PaperSlip} shows the paper slip we used for the promise arms.
+The clients had to put their name on a slip of paper where they stated they promised to pay monthly.
+
+We are confident the overwhelming majority of clients understood the contracts and made informed choices.
+As shown below, different contract terms did generate differential demand and differential behavior.
+Moreover, we can systematically predict demand based on consumer characteristics and measured beliefs.
+
+\subsection{Survey Data and Summary Statistics}
+
+The study exploits two forms of data; administrative data from the lender and a short survey we conducted of experimental clients.
+
+The administrative data contains a unique identifier of the client, an identifier of the piece she is pawning, and the transactions relating to that piece.
+In particular, the value of the piece as assessed by the appraiser, the amount of money loaned (70\% of the value), the date of the pawn transaction, and the type of contract for that pawn.
+Within the period fo the loan, we followed each transaction related to that piece in the administrative data: when payments were made and for what amounts, whether there was default (i.e.
+the client lost her pawn), and whether any late-payment fees (active for the relevant experimental arms) were imposed.
+After the experimental loan, we are able to track subsequent behavior and to see whether that borrower took a subsequent loan.
+We have this information for all the pawns that occurred in the experiment's 6 branches between August 2, 2012 and August 13, 2013, this includes all the pawns under our experiment but also those that happened 1 month before it started and up to 8 months after it ended.
+Figure \ref{exp_description}(a) shows the timing of the experiment and our admin data coverage.
+The black arrows represent the dates for which we have administrative data (before and after the experiment) for each branch, while the light gray segments represent the duration of the experiment.
+The experiment comprises 13,446 pawns, and our administrative data cover a total of 23,974 pawn
+
+In addition, we had a team of enumerators in each branch collect surveys and clearly explain the contract terms to walk-in clients.
+The enumerators were inside the branch and asked clients to complete a 5 minute survey \textit{before} going to the teller window to appraise their piece and before they were told contract terms (i.e.
+before treatment status was known).
+It was short to avoid discouraging the potential clients from pawning, but at the same time it aimed to measure the following: demographics, proxies for income/wealth, education, self-control problems/present-biased preferences, experience pawning, if family or friends commonly asked for money, how time consuming and costly it was to come to the branch, the subjective probability of recovering the piece that they intended to pawn, the subjective value of their piece in money terms (how much money they would sell it for), among others.
+We surveyed 10,437 clients.\footnote{The Appendix \ref{baseline_survey} transcribes the questionnaire in English.} %\footnote{We also surveyed clients before and after the experiment, so our survey covers a larger sample that we are not using in this paper.}.
+Survey response rate is 78\%, and response is not related to admin data observables (details in Table \ref{balance_response} in the Appendix).
+
+%We worked in 6 branches of Lender $P$, of differing size and location, although for ease of implementation all of them in Mexico city.
+For these 6 branches we have two types of data, administrative data and survey data we collected for the experiment.
+
+\subsection{Attrition}
+
+The study is subject to two potential forms of attrition.
+The more serious is that clients would change their pawning decisions in response to the treatment arms.
+If this were the case, our study would still recover internally valid estimates of the impacts of the treatment arms for the lender, but would not provide \textit{ceteris paribus} impacts on a comparable pool of individuals.
+We anticipated this possibility and trained appraisers to say --that whatever was the contract that day-- it was the only available contract for an undetermined amount of time.
+Because we do not observe refusals directly, we address this issue by examining the number of borrowers per day, and the number of borrowers who were surveyed but then did not pawn.
+
+% Empirically, attrition was not a problem.
+Table \ref{SS} shows that the number of pawns per branch per day across treatment arms is statistically identical.
+The last column of the table displays the p-value of an $F$ test of equality of means across arms and shows we cannot reject equality for any of the variables (p-value=0.38 for the number of pawns per day per branch).
+There is no evidence for selection across treatment arms for any of the admin or survey variables.
+
+%One concern was that after learning the conditions of the contract, clients could decide not to pawn.
 If they were deferentially responsive to the different conditions, we could end up having different kinds of clients in the different arms.
@@
 
+A second form of attrition would be differential refusal to answer the survey questions.
+This is less of a concern, both because the survey was done before treatment status was revealed, and because we still have institutional data for the universe of borrowers.
+Nonetheless, to test the internal validity of any measures in the study that use survey data, we test for differential attrition here as well.
+
 All the pieces of evidence indicate that there was no selection across arms and that experimental comparisons are internally valid.
 
-\subsection{More on implementation} \label{implementation}
-
-We want to highlight two potential threats to the validity of our experiment.
-The first discussed already is that the client can choose to leave the branch after the appraiser values her pawn and tells her the contract terms, generating differential attrition across treatment arms.
-We anticipated this possibility and trained appraisers to say --that whatever was the contract that day-- it was the only available contract for an undetermined amount of time.
-As we tested above the evidence supports the hypothesis of no differential selection.
-% Empirically, attrition was not a problem.
-Table \ref{SS} shows that the number of pawns per branch per day across treatment arms is statistically identical.
-The last column of the table displays the p-value of an $F$ test of equality of means across arms and shows we cannot reject equality for any of the variables (p-value=0.38 for the number of pawns per day per branch).
-There is no evidence for selection across treatment arms for any of the admin or survey variables.
-
-Another threat is clients' understanding of contract terms.
-The terms need to be understood in order for choice to be meaningful, and for the monthly payment commitment contract to bite.
-We had two `check-points' to do this.
-First, two enumerators were present in each branch for the whole day during the duration of our experiment to explain the contract terms to clients.
-One of the aspects emphasized was that the frequent payment contract involved the commitment to pay \underline{each month} a third of the outstanding amount, and that there was a 2\% penalty fee (or, in the promise arms, the breaking of a promise) involved in failing to do so.
-Figure \ref{ExplanatoryMaterial} translates a piece of the materials we used to explain the contracts (in this case a comparison sheet used in the Promise-Choice days to compare contracts terms side to side).
-The explanation took about 3-5 minutes and was pursued until the client said she understood the contract terms.
-Enumerators then asked clients to explain back the contract terms and corrected any misunderstandings.
-
-There was a second check point.
-Before the clients signed the contract, the appraiser made them read them the ``Contract Terms Summary'' sheet shown in Figure \ref{PaperSlip}.
-It was a piece of paper given to clients after their piece had been appraised and the size of the loan determined, but before they signed their contract.
-The appraiser read it and asked the client to sign it as a proof of understating.
-The sheet clearly indicates that this contract is a monthly payment one (numeral 1), that there is a penalty of 2\% for paying late (numeral 2), and the 3 payment dates (numeral 3).
-Finally, the bottom of the Figure \ref{PaperSlip} shows the paper slip we used for the promise arms.
-The clients had to put their name on a slip of paper where they stated they promised to pay monthly.
-
-We are confident the overwhelming majority of clients understood the contracts and made informed choices.
-As shown below, different contract terms did generate differential demand and differential behavior.
-Moreover, we can systematically predict demand based on consumer characteristics and measured beliefs.
-
-\section{The effect of forcing clients into fee-commitment} \label{fee-commitment}
-
-\subsection{The effect of the fee-forcing contract on financial cost and pawn recovery} \label{TE_fee-forcing}
+\textcolor{red}{Need to build Attrition Table}
+
+%\subsection{Connection to the literature}
+%Our study connects with two strands of the literature on microfinance.
+But also to a nascent one that uses RCTs to study to what extent people self-sort to treatments that have larger beneficial treatment effects for them.
+On the microfinance literature the first paper we could find that used an RCT to evaluate the causal effect of frequent payments in loans is \cite{Pande}.
+In a group lending rosca context, they note that most contracts involved frequent repayments --even weekly in many instances-- even when this increases transaction costs.
+They note that clients could benefit from ``the fiscal discipline afforded by the more rigid payments''.
+Frequency could provide a commitment device for clients, could foster a payment habit, or could generate more trust from social interactions among the group of borrowers.
+All these potential benefits apply in our context, except those relating to social interactions, as we work with individualized loans.
+
+%\subsection{More on implementation} %\label{implementation}
+
+\subsection{Balance in the Experimental Sample}
+Table \ref{SS} presents summary statistics for the sample of actual borrowers across arms, and illustrates that randomization worked to achieve balance across clients in the different experimental arms.
+Panel A describes variables from the administrative data.
+The average loan size is \$2197 MXN (\$105 USD).
+The average number of pawns per day per branch is 34.
+Only 42\% of clients recover their pawn.
+Even those that recover their pawn tend to pay it back at the last moment, with only 40\% paying before the 90th day.
+
+Panel B reports stats from our survey data.
+73\% of clients are women, with an average age of 43 years; 66\% of them have completed high school or more, and 90\% have pawned before, so that our sample has mostly experienced borrowers.
+Finally the subjective probability of recovery is close to 93\% on average, which contrasts with the 51 points lower actual recovery.
+Borrowers seem to be highly overconfident on average.
+The average subjective value they report for the pieces is 3069 MXN, much larger than the average appraised gold value of 2197 MXN.
+%This makes it inefficient for them to lose it.
+
+\textcolor{red}{Imbalance in survey data needs to be addressed?}
+
+\section{Experimental Analysis} \label{experiment}
+
+\subsection{The Choice of Commitment}
+\label{choice_commitment}
+
+%Section \ref{fee-commitment} showed that the Forced Commitment commitment contract reduced financing cost across the board, and that consumers themselves seemed to like it once they tried it.
+In such a case, one would expect a strong demand for it.
+This is not the case.
+We also find that clients in the choice arm achieved no better outcomes than those in the status quo group.
+
+%\subsection{Demand for the Forced Commitment commitment contract} \label{sec:demand}
+
+%\noindent \textbf{Low demand for commitment:} 
+A starting point in the analysis of commitment in pawn lending contracts is to look at the demand that manifested itself in the Commitment Choice arm.
+
+When preferences or income streams are heterogeneous, and consumers are neoclassical, giving choice among contracts is often a welfare increasing strategy.
+Consumers would choose the contract that best fits their needs.
+This holds also in most simple models of present bias preferences if consumers are sophisticated about their present bias.
+%Actually, it could be the case that the opportunity of choosing itself could affect behavior.
+But when consumers are overconfident about their ability to save to pay back the loan, free choice could be a sub-optimal policy from the point of view of the client's long run self, and could match clients with  more costly contracts.
+Defenders of choice make another subtler point: that even if take up of the commitment-fee contract is low, the sole fact of \textit{having} choice could potentially change behavior or welfare (\cite{Dalboetal:2010}, \cite{Sjostrometal:2018}, \cite{Tlaxcala}).
+
+\textcolor{red}{If we are to lead with this section we need a simple 'determinants' table that looks at who chooses commitment, this section to discuss results.}
+
+%In spite of broadly distributed benefits of the Forced Commitment commitment contract we documented above, 90\% of clients chose \textit{not} to have it, preferring the status-quo contract.
+As explained above we are fairly confident this was not because a lack of understanding of the contracts.
+
+%\vspace{.1in}
+%\noindent What can explain this low demand?
+In the spirit of \cite{Blumenstock} we try to differentiate between explanations.
+One explanation could be risk.
+Even if the fee forcing contract generates cost savings on average, clients with risk averse preferences may not demand it if they perceive higher risk from it.
+Alternatively, even risk-neutral agents may not demand it if the cost of lost flexibility is high or if they have high temporal discount rates and prefer to pay later.
+%If clients, for instance, face large and frequent income shocks which make it hard to repay monthly.\footnote{We don't observe income shocks in our data, making is hard to quantify how important they are.
+91\% of those in the Forced Commitment arm incurred a fee, which suggests that shocks are not uncommon.}
+%Although the evidence that follows undermines several explanations, the tests we can conduct given the data are not sharp enough to leave a single explanation standing.
+Section \ref{model} lays our a simple theory (namely present bias with partial naivete) which fits all the 6 main findings of the paper.
+Given its parsimony and explanatory power, we submit that it is the most suitable explanation for our results.
+
+\subsection{Forced versus Chosen Commitment} \label{forced_vs_choice}
+
+%Following two  paragraphs moved from old 'behavioral' choice section towards end of paper
+%\vspace{.2in}
+%\subsection{The effect of choice on pawn recovery and financial cost} \label{effect_choice}
+
+We now present the core experimental results, illustrating how the Commitment Choice and Forced Commitment arms differ from the control.
 
@@
 
+The Intention to Treat (ITT) results are very clear:  giving clients the option of choosing commitment is not effective, and forcing them into the commitment contract is.
+Choice does \textit{not} lead to lower financial cost compared to the status-quo contract.
+Nor does it lead to higher pawn recovery.
+The hollow circles in Figure \ref{fc_pro4}(a) show zero average effects for the different definitions of financial cost analogous to the ones described above.
+Figure \ref{fc_pro4}(b) shows further that the null effect happens for the 15$^{th}$, 25$^{th}$, 50$^{th}$ 75$^{th}$, and 85$^{th}$ percentiles.\footnote{The few clients that chose the Commitment contract (the solid black squares) do enjoy cost savings of 1005 MXN, which compares favorably to the 304 MXN in the Forced arm (as a fraction of the loan the numbers are 41.5\% and 12.5\%), but this combines the selection and treatment effects.} %Figure \ref{heterogeneous_te_4} plots the distribution of treatment effects and finds that the distribution offering choice actually \textit{increased} financial cost and default for about half of clients compared to being assigned the status-quo contract.
+Those tended to be the less economically vulnerable and more educated, {women}, and those whose family typically asks them for money.
+Figure \ref{fc_pro4}(c) finds null effects for pawn recovery. Consistent with these findings, Figure \ref{reincidence} finds no effect on repeat purchases for the Commitment Choice group.
+
 \vspace{.2in}
@@
 The second coefficient uses the subjective value of the pawn instead.
-In both cases we find that being assigned to the fee-forcing commitment contract causes a large reduction in the financing cost the client incurred, of 9.4\% (\$297) under the first definition and 13.2\% (\$472) under the second one.
+In both cases we find that being assigned to the Forced Commitment commitment contract causes a large reduction in the financing cost the client incurred, of 9.4\% (\$297) under the first definition and 13.2\% (\$472) under the second one.
 That is, we find that \textit{charging} clients a late payment decreases total \textit{fee-inclusive} financing cost.
@@
 However it does not take into account transportation cost or the opportunity cost of going in person to the branch.
-Given that the fee-forcing contract makes clients visit the branch more often (monthly), one may want a measure that includes those costs as well.
+Given that the Forced Commitment contract makes clients visit the branch more often (monthly), one may want a measure that includes those costs as well.
 Going in that direction, in a broader measure of costs, for each visit we add the self-reported transport cost plus a whole day's wage, multiplied by the number of visits.
 Adding a whole day's wage may exaggerate cost, but we still observe a reduction of this more comprehensive measure of cost caused by the frequent payment contract, although we lose more than 1/3 of the observations and some precision from missing data on transportation costs.
+We conclude that penalizing borrowers for delinquency in a contract which has already has large penalties from default (losing the collateral in a highly collateralized loan) actually helps borrowers.
 
 \vspace{.2in}
-\noindent \textbf{Heterogeneous Treatment Effects (HTE).} Average cost reductions could mask substantial heterogeneity.
-Benefits are distributed broadly however.
-Figure \ref{fc_pro2}(b) displays results from quantile regressions at the 15$^{th}$, 25$^{th}$, 50$^{th}$ 75$^{th}$, and 85$^{th}$ percentiles.
-All of them are negative.
-This motivated us to implement a finer measure of treatment effects.
-We used  \cite{atheygrf}'s generalized random forests methodology.\footnote{The methodology uses random forests of honest causal trees to estimate personalized treatment effects.
-The method generates a partition of the space of characteristics $X$, where each element of the partition is a leaf, and each leaf contains treatment and control clients with similar characteristics $x \in X$ which are used to calculate unbiased treatment effects for that leaf.
-The optimal partition is that which minimizes expected mean squared error of treatment effects predictions out-of-sample.} %The tree is honest because it uses one sample to build the tree and another one to estimate treatment effects within that tree.
-\cite{atheygrf} show that their treatment effects are asymptotically normal, which allows us to construct confidence intervals for our treatment estimate in each leaf.
-
-Figure \ref{fc_pro2}(c) plots the distribution of those treatment effects using this machine learning methodology.
-It shows that more than 70\% of clients experienced financial cost savings in the fee-forcing group compared to the status-quo group.
-The causal cost savings are larger for the more economically vulnerable, %that report at baseline that they have problems paying for services like water, electricity and rent,
-and those displaying overconfidence\footnote{see Section \ref{behavioral} for our measure of overconfidence.} about recovering their pawn, Figure \ref{HTE_fee_forcing}.
-%those that have to incur in higher transport cost to go to the branch  and that asked to be sent reminders to pay, this later one being one proxy of being inattentive or sophisticated present-biased.
-
-\vspace{.2in}
-\noindent \textbf{Pawn Recovery.} Figure \ref{fc_pro2}(d) plots estimated treatment effects of the fee-forcing commitment contract with the dependent variable being an indicator of losing the pawn in less than 230 days.
-The leftmost coefficient shows that the fee-forcing commitment contract increases the likelihood of recovering the pawn by 11 percentage points (26\% of mean recovery).
+\noindent \textbf{Pawn Recovery.} Figure \ref{fc_pro2}(d) plots estimated treatment effects of the Forced Commitment commitment contract with the dependent variable being an indicator of losing the pawn in less than 230 days.
+The leftmost coefficient shows that the Forced Commitment commitment contract increases the likelihood of recovering the pawn by 11 percentage points (26\% of mean recovery).
 This result stands in contrast with \cite{Pande} who find no effect of payment frequency on default in a group lending microfinance context.
@@
 \vspace{.2in}
-\noindent We conclude that penalizing borrowers for delinquency in a contract which has already has large penalties from default (losing the collateral in a highly collateralized loan) actually helps borrowers.
-
-\vspace{.2in}
 \noindent \textbf{Effects on other outcomes.} There are other intermediate outcomes that are impacted by being assigned to frequent payments.
-Table \ref{mechanisms} shows that the first payment happens 8 days earlier (column 1) in the fee-forcing arm than in the status quo one, and that the number of payments increases by 0.19 (column 2).
+Table \ref{mechanisms} shows that the first payment happens 8 days earlier (column 1) in the Forced Commitment arm than in the status quo one, and that the number of payments increases by 0.19 (column 2).
 Figure \ref{induced_to_pay_early} in the correlates HTE on financing cost with the HTE time of first payment and shows that those induced to pay earlier are also those that have larger induced reduction in financial cost.
@@
 \noindent \textbf{Other sub-samples.}  Results survive if we focus on those that paid a positive amount in treatment and control.\footnote{Although this is potentially a selected subsample, Table \ref{mechanisms} showed that there is no treatment effect the extensive margin, i.e.
-in $pay>0$.} We find that even those that paid a fee in the fee-forcing contract end up paying a smaller financial cost that those in the status-quo contract (Figure \ref{fc_pro2}a).\footnote{This regression conditions on those that paid a fee in the fee-forcing group, and compares this subset in treatment vs all of the control group.
+in $pay>0$.} We find that even those that paid a fee in the Forced Commitment contract end up paying a smaller financial cost that those in the status-quo contract (Figure \ref{fc_pro2}a).\footnote{This regression conditions on those that paid a fee in the Forced Commitment group, and compares this subset in treatment vs all of the control group.
 Results are similar if we condition in the control group on those who would have paid a fee  if they were in the treatment group given their observed payment behavior.
@@
 We were interested in this population to show that the effect is there for those who are serious about recovering their pawn.
-The fifth coefficient conditions on those that paid a fee in the fee-forcing group, comparing this subset in treatment vs all of the control group.
+The fifth coefficient conditions on those that paid a fee in the Forced Commitment group, comparing this subset in treatment vs all of the control group.
 Results are similar if we condition in the control group on those who would have paid a fee given current behavior.
-Again we acknowledge these is an endogenous sample and that the estimate may not be a causal effect.} We find that even those that paid a fee in the fee-forcing contract end up paying a smaller financial cost that those in the status-quo contract.
-
-\subsection{Effects of fee-forcing on repeat pawning}
-
-Although we have shown that compared to the status quo, being assigned to installment payments reduces financial cost and increases pawn recovery, this does not imply that welfare increases.
+Again we acknowledge these is an endogenous sample and that the estimate may not be a causal effect.} We find that even those that paid a fee in the Forced Commitment contract end up paying a smaller financial cost that those in the status-quo contract.
+
+\subsection{Analysis of repeat pawning}
+
+Although we have shown that Forced Commitment reduces financial cost and increases pawn recovery, this does not imply that welfare increases.
 Clients could have disutility from the stress of having monthly installments for instance.
-We don't need to make the strong claim of welfare for the purposes of this paper.
-The financing cost results are striking enough.
-But we conjecture that if clients exposed to the installment contract like it, they will be more likely to come back vis-a-vis those that got status quo contract.\footnote{\cite{Laibson2018} hypothesizes that consumers use ``experienced utility'' as a guide to make future purchases in this way.} This is indeed what we find in the data.
-
-The panel labeled ``Fee-forcing'' in Figure \ref{reincidence} presents results of estimating equation (\ref{basic_reg}) with the dependent variable being a dummy for the client being a repeat costumer.
-We define a client as a repeat costumer if, after experiencing at least 75 days of the respective treatment arm, she came back and pawned a \textit{different} piece.\footnote{Results are robust to using number of days experiencing the contract larger than 75.
-We know it is a different piece from it having a different weight/value.}  The leftmost coefficient shows that the causal effect of the fee-forcing contract on repeat pawning is an increase of 5 percentage points in the probability of being a repeat customer, this is twice the repeat purchasing happening in the status quo group.
-This effect is not explained by clients recovering their first pawn with higher probability in the fee-forcing contract and re-pawning this same one since we make sure it is another piece; besides only 16\% recover their piece in the fist 75 days in the fee forcing contract.
+%We don't need to make the strong claim of welfare for the purposes of this paper. The financing cost results are striking enough. But we 
+A simple way to move towards a consideration of borrower welfare is the conjecture that if clients exposed to the installment contract like it, they will be more likely to come back vis-a-vis those that got status quo contract.\footnote{\cite{Laibson2018} hypothesizes that consumers use ``experienced utility'' as a guide to make future purchases in this way.} This is indeed what we find in the data.
+
+The panel labeled Forced Commitment in Figure \ref{reincidence} presents results of estimating equation (\ref{basic_reg}) with the dependent variable being a dummy for the client being a repeat customer.
+We define a client as a repeat customer if, after experiencing at least 75 days of the respective treatment arm, she came back and pawned a \textit{different} piece.\footnote{Results are robust to using number of days experiencing the contract larger than 75.
+We know it is a different piece from it having a different weight/value.}  The leftmost coefficient shows that the causal effect of the Forced Commitment contract on repeat pawning is an increase of 5 percentage points in the probability of being a repeat customer, this is twice the repeat purchasing happening in the status quo group.
+This effect is not explained by clients recovering their first pawn with higher probability in the Forced Commitment contract and re-pawning this same one since we make sure it is another piece; besides only 16\% recover their piece in the fist 75 days in the fee forcing contract.
 Experience with the frequent payment contract seems to be necessary as there is no effect of the monthly payment contract on repeat pawning in the first 30 or 60 days of the contract (see Figure \ref{reincidence_before} in the Appendix).
@@
 \hl{The second coefficient from the left focuses on the subsample who are predicted would have a treatment effect on financial cost savings above the median} treatment effect in their first pawn.\footnote{Since this is predicted using \cite{atheygrf} based on pre-determined covariates for treatment and control clients it is valid to split the sample this way.} It shows that for these clients the likelihood of coming back is twice as large.
-That is, those that benefit more from the fee-forcing contract are more likely to repeat compare to their control group.
-The remaining coefficients of the ``Fee-forcing'' panel condition on endogenous outcomes and should be interpreted with care.
+That is, those that benefit more from the Forced Commitment contract are more likely to repeat compare to their control group.
+The remaining coefficients of the ``Forced Commitment'' panel condition on endogenous outcomes and should be interpreted with care.
 The \hl{third} coefficient from the left restricts the sample to those that had not recovered their pawn in the first 75 days in both groups and finds similar results.
@@
 
-\section{The effect of giving choice} \label{fee-choice}
-
-Section \ref{fee-commitment} showed that the fee-forcing commitment contract reduced financing cost across the board, and that consumers themselves seemed to like it once they tried it.
-In such a case, one would expect a strong demand for it.
-This is not the case.
-We also find that clients in the choice arm achieved no better outcomes than those in the status quo group.
-
-\subsection{Demand for the fee-forcing commitment contract} \label{sec:demand}
-
-\noindent \textbf{Low demand for commitment:} To study demand for commitment, in one experimental arm, we let clients freely choose between the two types of contract: the fee-forcing commitment contract or the status-quo contract.
-In spite of broadly distributed benefits of the fee-forcing commitment contract we documented above, 90\% of clients chose \textit{not} to have it, preferring the status-quo contract.
-As explained above we are fairly confident this was not because a lack of understanding of the contracts.
-
-\vspace{.1in}
-\noindent What can explain this low demand?
-In the spirit of \cite{Blumenstock} we try to differentiate between explanations.
-One explanation could be risk.
-Even if the fee forcing contract generates cost savings on average, clients with risk averse preferences may not demand it if they perceive higher risk from it.
-Alternatively, even risk-neutral agents may not demand it if the cost of lost flexibility is high or if they have high temporal discount rates and prefer to pay later.
-%If clients, for instance, face large and frequent income shocks which make it hard to repay monthly.\footnote{We don't observe income shocks in our data, making is hard to quantify how important they are.
-91\% of those in the fee-forcing arm incurred a fee, which suggests that shocks are not uncommon.}
-Although the evidence that follows undermines several explanations, the tests we can conduct given the data are not sharp enough to leave a single explanation standing.
-Section \ref{model} lays our a simple theory (namely present bias with partial naivete) which fits all the 6 main findings of the paper.
-Given its parsimony and explanatory power, we submit that it is the most suitable explanation for our results.
-
-\subsubsection{Behavioral: overconfident borrowers demand less (but benefit more)} \label{behavioral}
+\subsection{Soft Commitment}
+
+%\section{The effect of promises} \label{promises}
+
+%One finding of the paper is that a rather small fee of 14 MXN on average changes behavior substantially.
+On the one hand it generates average savings for almost everybody (on the order of 200-300 pesos on average) when forced.
+But on the other hand it dissuades take up when clients have choice.
+One would want a commitment device that generates higher take-up while at the same time providing incentives for recovering the pawn.
+
+The results from the two arms of the study that feature `soft' commitment further reinforce the centrality of externally imposed commitment in this context.  
+%One way to go would be to decrease the already small fee say to 1\% or lower.
+We decided to instead experiment with a non-pecuniary penalty, in the form of a psychological cost of breaking a promise.
+As explained in Section \ref{Experiment} the promise contract involved making a salient promise to repay monthly, and receive a short speech by the appraiser about the importance of keeping her promise of paying monthly.
+A substantial literature documents that people don't like to break their promises, and are willing to incur in monetary losses in trying to keep them.
+This provides a potentially very attractive way to drive better repayment behavior at low pecuniary cost to clients.
+To our knowledge this type of result has been replicated several times in laboratory contexts but not in a field setting like ours.\footnote{Promises are not foreign to microfinance lending: Grameen bank for instance makes clients recite a promise at each center weekly meeting.The exact promise repeated by clients live is this: ``\textit{We pledge to attend regularly the weekly Center meetings, to utilize our loans for the purpose approved, to save and pay our installments weekly, to use our increased incomes for the benefit of our families, to ensure that other members of our group and Center do likewise and to take collective responsibility if they do not.''}}
+%If breaking a promise is perceived as having a lower cost than paying the 2\% fee and at the same time helps as a commitment device we could achieve better outcomes: more people would demand the Soft Commitment contract.
+
+Demand for the Soft Commitment contract  is higher than for the Forced Commitment contract by a factor of 3: {31}\% of clients offered a choice between the status quo contract and the Soft Commitment contract chose commitment.
+Interestingly, the set of people who demand the Soft Commitment contract are different from those that demanded the Forced Commitment one.
+While in both cases the economically vulnerable demand less, in the case of the Soft Commitment those that we classify as present biased, those that report that they frequently fall into temptation buying, and those that ask for reminders of payment are \textit{less} likely to demand the Soft Commitment contract.
+This suggests that those taking up the promise commitment are not the ones needing the commitment (see Figure \ref{interactions_takeup} in the Appendix).
+
+Nonetheless, we find Soft Commitment, whether chosen or induced, to be completely ineffective in this environment.
+Figure \ref{fc_pro5}(a) finds that assigning clients to the choice-promise condition has a zero effect on financial cost on average (circles).
+We see no difference even for the endogenous group that \textit{chose} to promise (squares).
+This null effect happens not only on average, but also by percentiles (not shown in Figure).
+There is also no effect on pawn recovery on (first coefficient in Figure \ref{fc_pro5}(b)), even for those that themselves choose to promise.
+And the null effect carries over if we use the definition of recovery in less than 120 days, or for the (endogenous) subgroups that paid a positive amount.
+Finally, there is no effect on repeat pawning (Figure \ref{reincidence}).
+
+Giving choice of whether to promise or not has the advantage of making promising an active decision by the client.
+In most of the the experimental literature promising is voluntary.
+But it has the disadvantage that we cannot measure the causal effect of promising, since those that promise are a selected sample.
+To evaluate the causal effect of promising, we compare people allocated to the promise-forcing arm (were all clients were forced to make a promise) against those in the status quo contract arm.
+Figure \ref{fc_pro5} (c) and (d) show the results.
+It documents null average treatment effects for both financial cost and recovering the pawn.
+Also there is no effect on repeat pawning.
+
+\vspace{.2in}
+\noindent The evidence presented in this section contrasts sharply with the evidence in laboratory experiments where people choosing to promise has a large effects on behavior, and where people keep their promises.
+While clients are more enthusiastic about the Soft Commitment contract than the Forced Commitment one in the sense of tripling take-up, the promise contract provides no commitment.
+Results for the promise arms are consistent with \cite{Ted} and \cite{John} who find that people are likely to demand commitment when the commitment is too weak to have beneficial effects.
+
+%\vspace{.2in}
+%\noindent \textit{Size of ``mistakes''.} Although promises have very muted effects, there is some heterogeneity (see Figure \ref{heterogeneous_te_3}).
+This opens the space for choice mistakes.
+Figure \ref{choose_wrong} shows that indeed there are some mistakes, but these are smaller that for the Commitment Choice arm.
+When $z=0$, we calculate that about 60\% of clients in the promise-choice group chose contracts that induced \textit{higher} financial cost.
+In particular gr{97\%} of those that chose the status-quo contract would have been better in the Soft Commitment contract, while gr{3\%} of those who chose the Soft Commitment contract would have been better in the status-quo one.
+On average they spend \$250 pesos on extra financing cost.
+
+\section{Exploring the Importance of Paternalism}
+\label{exploring}
+
+\subsection{Heterogeneous Treatment Effects}
+
+\textcolor{red}{Propose to move all of the content of this section either up to ITTs (if quantile effects) or to the next section on paternalism (if Random Forest HTEs) and eliminate this section here.}
+
+\vspace{.2in}
+\noindent \textbf{Heterogeneous Treatment Effects (HTE).} Average cost reductions could mask substantial heterogeneity.
+Benefits are distributed broadly however.
+Figure \ref{fc_pro2}(b) displays results from quantile regressions at the 15$^{th}$, 25$^{th}$, 50$^{th}$ 75$^{th}$, and 85$^{th}$ percentiles.
+All of them are negative.
+This motivated us to implement a finer measure of treatment effects.
+We used  \cite{atheygrf}'s generalized random forests methodology.\footnote{The methodology uses random forests of honest causal trees to estimate personalized treatment effects.
+The method generates a partition of the space of characteristics $X$, where each element of the partition is a leaf, and each leaf contains treatment and control clients with similar characteristics $x \in X$ which are used to calculate unbiased treatment effects for that leaf.
+The optimal partition is that which minimizes expected mean squared error of treatment effects predictions out-of-sample.} %The tree is honest because it uses one sample to build the tree and another one to estimate treatment effects within that tree.
+\cite{atheygrf} show that their treatment effects are asymptotically normal, which allows us to construct confidence intervals for our treatment estimate in each leaf.
+
+Figure \ref{fc_pro2}(c) plots the distribution of those treatment effects using this machine learning methodology.
+It shows that more than 70\% of clients experienced financial cost savings in the Forced Commitment group compared to the status-quo group.
+The causal cost savings are larger for the more economically vulnerable, %that report at baseline that they have problems paying for services like water, electricity and rent,
+and those displaying overconfidence\footnote{see Section \ref{behavioral} for our measure of overconfidence.} about recovering their pawn, Figure \ref{HTE_fee_forcing}.
+%those that have to incur in higher transport cost to go to the branch  and that asked to be sent reminders to pay, this later one being one proxy of being inattentive or sophisticated present-biased.
+
+\subsection{The Wrong People Choose Commitment}
+
+This is not the first paper to find low demand for commitment, however it is the first we know of that can compare choice vs forcing.
+The fact that the Forced Commitment contract lowers financial costs for almost all clients, together with the fact that only 10\% choose it must mean that many consumers are choosing contracts with higher financial costs for themselves.
+We now present an estimation of how many consumers seem to be making a cost increasing choice, and how much money they seem to be leaving on the table.
+We conduct two exercises.
+
+\vspace{.2in}
+\noindent \textbf{Do choices increase financing cost?} Answering this question requires calculating a counterfactual: for each client in the choice arm we want to know how much cost savings would she have gained had she chosen the opposite contract.
+We do this in two steps.
+Step 1, using the honest causal forests method of \cite{atheygrf} described above and the two forcing arms we calculate the causal effect on financing cost of getting the Forced Commitment contract instead of the status quo contract for a client $i$ with characteristics $x_i$; call it $TE^{For}_{i}(x_i)$.
+Then in step 2 we predict treatment effects for clients \textit{in the Choice arm} using the partition into leaves and the treatment effect from step 1, that is client $j$ is imputed the treatment effect of the leaf corresponding to her characteristics $x_j$.
+We call this counterfactual treatment effect $\widehat{TE}^{For}_{j}(x_j)$.
+This is precisely the counterfactual we wanted.\footnote{This extrapolation of the treatment effects assumes that choice itself --conditional on a given contract-- does not affect behavior.
+Given the results in subsection \ref{effect_choice} we are comfortable with this assumption.
+Note that although the extrapolation is to another population, by randomization it is a statistically identical population with common support.} Armed with this, we say that a client made a ``mistake'' if either she chose the status quo contract and her $\widehat{TE}^{fee}_{i}$ is negative (i.e.
+more cost saving from the Forced contract), or if she chose the Commitment contract and $\widehat{TE}^{fee}_{i}$ is positive, (i.e.
+financial costs are larger for the Commitment contract).
+When a client made a choice mistake, we say that its peso-size is $|\widehat{TE}^{fee}_{i}|$.
+
+%Using the forcing arms and extrapolating to the choice arms.
+%Then, we predict these treatment effects for everybody in the choice arm using characteristics $x_i$.
+Let $\widehat{TE}^{fee}_{i}$ be the predicted financial cost savings for person $i$ of choosing the Forced Commitment contract rather than the status quo one, divided by the size of her loan (i.e.
+the negative value of the predicted treatment effect on financial cost for person $i$).
+$\widehat{TE}^{sq}_{i}$ is the analogous for the status quo contract.
+We define the choice of person $i$ to be a ``mistake'' if
+
+%\begin{equation}
+% \{ i \; \text{chose} \; sq \; \text{and} \; \;  \widehat{TE}^{fee}_{i}>\widehat{TE}^{sq}_{i} + z \} \; \text{or} \; \{ i \; \text{chose} \; fee \; \text{and} \; \;  \widehat{TE}^{fee}_{i}<\widehat{TE}^{sq}_{i} - z \}
+%\end{equation}
+
+Since the prediction of the treatment effect is an estimate and has noise, we do two things.
+First, we normalize $\widehat{TE}^{fee}_{i}$ by the value of the loan of person $i$ and introduce a threshold parameter $z$ and say that a choice is a ``mistake'' if the alternative contract would generate greater than $z$ in savings.
+That is, we introduce a threshold that we vary from 0\% to 15\% of the value of the loan.
+{Second, we take into account uncertainty in estimation of treatment effects and report results using the extremes of the 95\% confidence interval bounds for $\widehat{TE}^{fee}_{i}$.}
+
+Figure \ref{choose_wrong}(a) plots on the left Y-axis the fraction of clients that made a choice ``mistake'' and on the right Y-axis its size in pesos.
+On the X-axis it varies the threshold $z$.
+When $z=0$, we calculate that about 75\% of clients in the Commitment Choice group chose contracts that induced \textit{higher} financial cost.
+%(90\% confidence interval [45,94]).
+Most mistakes are failures to choose the fee-commitment contract ({85}\%), while only {15}\% of those who chose the fee-commitment contract would have been better in the status-quo one.
+The average mistake in pesos is \$250.
+%(90\% confidence interval [140,390]).
+Figure \ref{choose_wrong}(b) plots the same curve, but separately for overconfident and non-overconfident clients, using the definition of overconfidence in Section \ref{behavioral}.
+{It shows that there are about 11 percentage points more mistakes in the overconfident population (when $z=0$), an important difference.}
+
+The findings above suggest that forcing clients into commitment contacts may reduce financial cost for the overwhelming majority of clients.
+Figure \ref{choose_wrong}(c) calculates what fraction of clients would be made better off if we forced them into the fee-commitment contract.
+We find that 85\% would be better off (using $z=0$), and they would on average have savings of 250MXN.
+This conclusion is in line with a recent paper by \cite{John}.
+In a savings context, she finds that when commitment is on the menu a majority of subjects wrongly choose too little commitment and fail to reach their savings goals.
+It is also in line with \cite{Sprenger} who show that the more naive about their present bias are the ones who demand less commitment.
+
+% Figure \ref{choose_wrong}(d) plots $\widehat{P(x_i)}$ on the X-axis, and the heterogeneous treatment effects we estimated in Section \ref{TE_fee-forcing} on the Y-axis.
+It plots a binscatter that splits the X-axis into 100 percentiles bins of predicted take-up probability and for each bin averages the financial cost treatment effects.
+If it was true that those with larger cost savings have larger demand for the fee-commitment contract, we would expect a negative slope (recall that more savings mean lower financial cost in the Y-axis).
+This is not what we find.
+Using all clouds we estimate a slope close to zero in the relationship.
+Using the 80 right most points, we estimate a \textit{positive} relationship.
+A positive relation means that those more likely to demand commitment are also those that had smaller benefits from commitment.
+This result is similar to \cite{Walters}, who finds that students that select into more effective schools are the ones with smaller treatment effects from attending.\footnote{\cite{Walters} uses distance to school as an instrumental variable for choice, while we use randomization to choice vs no-choice groups as our empirical strategy.}
+
+\subsection{Boosted Classification Algorithm}
+
+\vspace{.2in}
+\noindent \textbf{Is there positive selection on treatment effects?} The previous exercise consisted of extrapolating treatment effects from the no-choice arms to the choice arm.
+Here we do the reverse.
+First, we estimate a flexible model of take-up of the fee commitment contract \textit{in the choice arm} using \textcolor{red}{gradient boosting classification}\footnote{\textcolor{red}{Results are robust to other classification methods like Random Forest, SVM, etc.}} and obtain for a client with characteristics $x_i$ a \textcolor{red}{calibrated} probability $P(x_i)$ of choosing the Forced Commitment contract.
+We then use this model to predict the counterfactual probability of a client with characteristics $x_j$ choosing the fee-commitment contract \textit{in the no choice-arms} if she would have been given the choice, what we call $\widehat{P(x_j)}$.\footnote{Our \textcolor{red}{gradient boosting} take-up model has a good out-of-sample fit with an out-of-sample AUC of \colorbox{yellow}{0.85}.
+(accuracy 97\% in-sample and 90\% out-of-sample)} Second, armed with this prediction in the forcing arms, we can ask the following: is it true that people with larger Forced Commitment contract treatment effects (i.e.
+more cost savings) are more likely to have demanded the Forced Commitment contract if choice had been given to them?
+
+Based on the propensity score, we predict the two categories: choosers \& non-choosers, such that the proportions match the observed data, then we compute cumulative distribution functions of the heterogeneous conditional average treatment effect we estimated in Section \ref{TE_fee-forcing} using the Causal Random Forest.
+Figure \ref{benefit_vs_choice_cdf} shows there is a first order stochastic dominance in treatment effects between the two predicted categories.
+This means those more likely to demand commitment are also those that had smaller benefits from commitment.
+This result is similar to \cite{Walters}, who finds that students that select into more effective schools are the ones with smaller treatment effects from attending.\footnote{\cite{Walters} uses distance to school as an instrumental variable for choice, while we use randomization to choice vs no-choice groups as our empirical strategy.}
+
+On an attempt to characterize the class that benefits more from commitment, we develop a finite mixture model with two latent types.
+After estimation of this FMM, we find that the class more benefited from being forced is negatively correlated with demand for commitment (see Figure \ref{fmm_hte} in the appendix).
+We identify this class with the naive individuals, since choice is the core divider, and this class is predicted to default more (see Table \ref{fmm_table} in the appendix).
+This exercise emphasizes how important choice is as a segregator.
+
+\subsection{LATEs for Compliers and Non-Compliers}
+
+The prior approaches to heterogeneity analysis did not use information about the actual outcomes in the complier group in the choice arm, only assuming that the decision to choose can be modeled.
+An alternate approach assumes nothing about the decision to choose (other than random sampling) and instead makes the couple of exclusion restriction-style assumptions typical of Local Average Treatment Effect (LATE) analysis.
+Namely, a) the typical LATE assumption that an individual not choosing the treatment has the same potential outcome as one not offered it, then the mirror image assumption for the Forcing arm that b) an individual forced to take Commitment has the same potential outcome as an individual choosing it, and c_ no spillovers from chooser to non-choosers in the choice arm.\footnote{Figure \ref{exclusion_restriction} in the appendix tests this assumptions.
+\hl{For robustness we also try a Manski-type monotone IV approach with similar results.}}
+
+Let $Z_i$ be the observed, randomly assigned experimental allocation, where $Z_i=0$ denotes the control arm, $Z_i=1$ denotes the forced-fee arm, and $Z_i=2$ is the choice arm.
+Let $T_i$ be the unobserved choice type.
+$T_i=0$ when individual $i$ does not choose commitment  given the choice and $T_i=1$ when chooses commitment given the choice.
+Finally, $D_i = Z_i\times \mathds{1}(Z_i\neq 2) + T_i\times \mathds{1}(Z_i=2)$ is the observed treatment indicator, and $Y(d,z)$ is the potential outcome function for $d=0,1$, and $z=0,1,2$.
+
+To test the difference between gains for choosers versus gains from non-choosers we need to identify: $\mathbb{E}[Y_1-Y_0\;|\;T=1]$ the Treatment on the Treated (TOT), and $\mathbb{E}[Y_1-Y_0\;|\;T=0]$ the Treatment on the Untreated (TUT).
+
+Given that what we really want to understand is the differential outcomes, we have
+\begin{align*}
+\mathbb{E}[Y_1 - Y_0 \;\mid\; T=1]  &=   \frac{\mathbb{E}[Y \;\mid\; Z=2] - \mathbb{E}[Y \;\mid\; Z=0)}{p} \\
+\mathbb{E}[Y_1 - Y_0 \;\mid \;T=0]  &=  \frac{\mathbb{E}[Y \;\mid\; Z=1] - \mathbb{E}[Y \;\mid\; Z=2]}{(1-p)} 
+\end{align*}
+
+where $p$ is analogous to a compliance (in the choice arm) indicator in a one-sided non-compliance problem.
+
+Note that the TOT is the LATE with one-sided non-compliance between the choice and control arm.
+The TUT is the LATE between the forced and choice arms, and think of the forced arm as an instrument for NOT complying with the treatment.
+In other words, is just the LATE on non-compliers.
+This effectively draws a distinction between unobserved "choice types" ($T = 0, 1$) and observed treatment take-ups ($D = 0, 1$)
+
+Table \ref{tot_tut} shows that TUT is greater than the TOT.
+Although the difference is not significant (Figure \ref{bootstrap_tot_tut}) since we have a low (15\%) compliance rate in the choice arm, which results in low power, we also estimate an Instrumental Random Forest following \cite{atheygrf}.
+The Instrumental Random Forest allows us to compute conditional heterogeneous treatment effects, which effectively lets us estimate for each individual with characteristics $X_i$ the quantities $TOT_i:=\mathbb{E}[Y_1-Y_0\; |\; T_i=1, X_i]$, and $TUT_i:=\mathbb{E}[Y_1-Y_0 \;|\; T_i=0, X_i]$.
+Figure \ref{tot_tut_ecdf} plots the ECDF for this quantities, together with the difference $TOT-TUT$.
+When testing for the difference in means between this two distributions we find a significant difference of \hl{0.03 points} at the 95\% level.
+
+Hence, we pursue three quite different techniques and all arrive at the same result.
+Whether we model the choice of Commitment and analyze heterogeneity using a random forest, use a PCM-style technique to categorize borrower types in a flexible way, or exploit the point-identification of LATEs for compliers and non-compliers enabled by the Forcing arm, the results are consistent:  the wrong people are choosing commitment.
+
+\subsection{Optimism, Over-Optimism, and the Failure of Self-Commitment}
+\label{overconfidence}
+
+\textcolor{red}{Need to decide whether we want to try to plant our feet on Confidence/Overconfidence as the core `why' of the previous result
+.}
+%\subsubsection{Behavioral: overconfident borrowers demand less (but benefit more)} \label{behavioral}
 
@@
 In the choice-fee arm, being overconfident decreases the likelihood of demanding commitment by 12 percentage points a result that this is robust to including controls  (columns 1 and 2).
-While overconfidence predicts lower take up in the fee-choice arm, this is not the case in the promise-choice arm (columns 3 and 4).
+While overconfidence predicts lower take up in the Commitment Choice arm, this is not the case in the promise-choice arm (columns 3 and 4).
 One interpretation of the results is that the overconfident borrowers think they do not need commitment, and their demand decreases sharply as soon as there is even a small fee, and at the same time they perceive the promise as a low cost option.
@@
 Theory predicts that the more overconfident (naive) may be at the same time those that benefit more from commitment.
-Extrapolating individual treatment effects of the fee-forcing contract vs the status quo one to the choice arm (see below for more detail), and using them as a dependent variable we find that overconfident borrowers benefit \textit{more} from the commitment contract, with {24.8}\% (=\${30}/\${121}) more savings (columns 5 and 6).
+Extrapolating individual treatment effects of the Forced Commitment contract vs the status quo one to the choice arm (see below for more detail), and using them as a dependent variable we find that overconfident borrowers benefit \textit{more} from the commitment contract, with {24.8}\% (=\${30}/\${121}) more savings (columns 5 and 6).
 Thus while we predict the overconfident benefit more from commitment, they demand less of it.
 
+\subsection{Dynamic Effects:  Learning-by-not-doing}
+
+\textcolor{red}{Need to decide on table and write this section of the paper.}
+
+\section{Old Mechanisms Section of Paper}
+
+\textcolor{red}{Which of these pieces do we want to keep?  Delete whole section?.}
 \subsubsection{Neoclassical Alternatives} \label{neoclasical}
@@
 We use the fact that if the utility $u(FC)$ is decreasing in $FC$ (i.e.
-clients dislike paying higher financing cost) and $F_{fee}(FC) \geq F_{sq}(FC)$ for all $FC$, which we actually verify in our data, then $E_{fee}[u(FC)] \geq E_{sq}[u(FC)]$, that is any expected utility maximizing client risk averse consumer should choose the fee-forcing contract as a result of the distribution of cost payoffs.\footnote{See the Appendix for the proof.
+clients dislike paying higher financing cost) and $F_{fee}(FC) \geq F_{sq}(FC)$ for all $FC$, which we actually verify in our data, then $E_{fee}[u(FC)] \geq E_{sq}[u(FC)]$, that is any expected utility maximizing client risk averse consumer should choose the Forced Commitment contract as a result of the distribution of cost payoffs.\footnote{See the Appendix for the proof.
 Figure \ref{ecdf_fc} in the Appendix shows that indeed $F_{fee}(FC) \geq F_{sq}(FC)$.
@@
 First, we fit a Weibull distribution to the distribution of financing cost, were the scale and shape parameters depend on client's and loan observable characteristics.
-We do this separately for the status quo contract and the fee-forcing contract, obtaining two distributions $f_{sq}(FC|X;\Gamma_1)$ and  $f_{fee}(FC|X;\Gamma_2)$ with different parameters $\Gamma_1$, $\Gamma_2$.
+We do this separately for the status quo contract and the Forced Commitment contract, obtaining two distributions $f_{sq}(FC|X;\Gamma_1)$ and  $f_{fee}(FC|X;\Gamma_2)$ with different parameters $\Gamma_1$, $\Gamma_2$.
 Second, we assume a representative consumer with a CRRA utility function over financial cost, $u(FC)=\frac{1}{1-\theta}FC^{1-\theta}$.
@@
 It turns out that it holds for risk aversion levels that are too high to be believable.
-That is, with our calibration, it seems unlikely that risk aversion is reducing demand for the fee-forcing contract.
+That is, with our calibration, it seems unlikely that risk aversion is reducing demand for the Forced Commitment contract.
 
@@
 \noindent \textbf{Lost flexibility.} A second explanation for low take up is lost flexibility.
-That is, the fee-commitment contract may provide too much commitment which is costly because the client may be forced to incur in late payment fees if he experiences a negative income shock.\footnote{Note that income shocks that affect the ability to pay the entire loan are a worry for both the fee-forcing contract and the status quo one, and should not make one contract more favorable than the other.} While we cannot rule out that income shocks combined with lost flexibility of the contract explain the low demand, we think it is unlikely.
+That is, the fee-commitment contract may provide too much commitment which is costly because the client may be forced to incur in late payment fees if he experiences a negative income shock.\footnote{Note that income shocks that affect the ability to pay the entire loan are a worry for both the Forced Commitment contract and the status quo one, and should not make one contract more favorable than the other.} While we cannot rule out that income shocks combined with lost flexibility of the contract explain the low demand, we think it is unlikely.
 First, we showed above that clients report a subjective probability of recovery of 93\% on average, which suggests they are not too worried about income shocks.
@@
 
-To make this concrete, we calculated what the financing cost of the fee-commitment contract would be if \textit{all} its clients incurred in \textit{all} potential fees (while keeping payment profiles and pawn recovery constant) and added these fictitious fees to financing cost for those in the fee-forcing arm, thus artificially inflating their cost.
+To make this concrete, we calculated what the financing cost of the fee-commitment contract would be if \textit{all} its clients incurred in \textit{all} potential fees (while keeping payment profiles and pawn recovery constant) and added these fictitious fees to financing cost for those in the Forced Commitment arm, thus artificially inflating their cost.
 We then re-estimated the quantile treatment effects analogous to Figure \ref{fc_pro2}(b) with this inflated financial cost.
@@
 Figure \ref{fc_allfee} presents the results.
-We find that even in this extreme scenario, tilted against the fee-forcing contract, the estimated effect still implies cost savings from the fee-forcing contract at the mean, 25$^{th}$, 50$^{th}$, and 75$^{th}$ percentiles.\footnote{Recall that the differences in financing cost already takes into account the fact that clients in the fee forcing contract sink more pre-payments than those in the status quo contract, and that those prepayments are lost if the loan is not fully paid back.}  Although these arguments are not definitive, they suggest that low demand for commitment may be driven by more than the anticipation of lost flexibility implied by a small fee.
+We find that even in this extreme scenario, tilted against the Forced Commitment contract, the estimated effect still implies cost savings from the Forced Commitment contract at the mean, 25$^{th}$, 50$^{th}$, and 75$^{th}$ percentiles.\footnote{Recall that the differences in financing cost already takes into account the fact that clients in the fee forcing contract sink more pre-payments than those in the status quo contract, and that those prepayments are lost if the loan is not fully paid back.}  Although these arguments are not definitive, they suggest that low demand for commitment may be driven by more than the anticipation of lost flexibility implied by a small fee.
 
@@
 
-\vspace{.2in}
-\subsection{The effect of choice on pawn recovery and financial cost} \label{effect_choice}
-
-When preferences or income streams are heterogeneous, and consumers are neoclassical, giving choice among contracts is often a welfare increasing strategy.
-Consumers would choose the contract that best fits their needs.
-This holds also in most simple models of present bias preferences if consumers are sophisticated about their present bias.
-%Actually, it could be the case that the opportunity of choosing itself could affect behavior.
-But when consumers are overconfident about their ability to save to pay back the loan, free choice could be a sub-optimal policy from the point of view of the client's long run self, and could match clients with  more costly contracts.
-Defenders of choice make another subtler point: that even if take up of the commitment-fee contract is low, the sole fact of \textit{having} choice could potentially change behavior or welfare (\cite{Dalboetal:2010}, \cite{Sjostrometal:2018}, \cite{Tlaxcala}).
-
-\vspace{.2in}
-\noindent \textbf{Choice has no effect on pawn recovery or financial cost.} We find that giving clients the option of choosing among the fee-commitment and the status quo contract does \textit{not} lead to lower financial cost compared to forcing them into the status-quo contract.
-Nor does it lead to higher pawn recovery.
-The hollow circles in Figure \ref{fc_pro4}(a) show zero average effects for the different definitions of financial cost analogous to the ones described above.
-Figure \ref{fc_pro4}(b) shows further that the null effect happens for the 15$^{th}$, 25$^{th}$, 50$^{th}$ 75$^{th}$, and 85$^{th}$ percentiles.\footnote{The few clients that selected the fee-commitment contract (the solid black squares) do enjoy cost savings of 1005 MXN, which compares favorably to the 304 MXN in the fee-forcing arm (as a fraction of the loan the numbers are 41.5\% and 12.5\%), but this combines the selection and treatment effects.} %Figure \ref{heterogeneous_te_4} plots the distribution of treatment effects and finds that the distribution offering choice actually \textit{increased} financial cost and default for about half of clients compared to being assigned the status-quo contract.
-Those tended to be the less economically vulnerable and more educated, {women}, and those whose family typically asks them for money.
-Figure \ref{fc_pro4}(c) finds null effects for pawn recovery. Consistent with these findings, Figure \ref{reincidence} finds no effect on repeat purchases for the fee-choice group.
-
-\subsection{The scope for private paternalism}
-
-This is not the first paper to find low demand for commitment, however it is the first we know of that can compare choice vs forcing.
-The fact that the fee-forcing contract lowers financial costs for almost all clients, together with the fact that only 10\% choose it must mean that many consumers are choosing contracts with higher financial costs for themselves.
-We now present an estimation of how many consumers seem to be making a cost increasing choice, and how much money they seem to be leaving on the table.
-We conduct two exercises.
-
-\vspace{.2in}
-\noindent \textbf{Do choices increase financing cost?} Answering this question requires calculating a counterfactual: for each client in the choice arm we want to know how much cost savings would she have gained had she chosen the opposite contract.
-We do this in two steps.
-Step 1, using the honest causal forests method of \cite{atheygrf} described above and the two forcing arms we calculate the causal effect on financing cost of getting the fee-commitment contract instead of the status quo contract for a client $i$ with characteristics $x_i$; call it $TE^{fee}_{i}(x_i)$.
-Then in step 2 we predict treatment effects for clients \textit{in the choice arm} using the partition into leaves and the treatment effect from step 1, that is client $j$ is imputed the treatment effect of the leaf corresponding to her characteristics $x_j$.
-We call this counterfactual treatment effect $\widehat{TE}^{fee}_{j}(x_j)$.
-This is precisely the counterfactual we wanted.\footnote{This extrapolation of the treatment effects assumes that choice itself --conditional on a given contract-- does not affect behavior.
-Given the results in subsection \ref{effect_choice} we are comfortable with this assumption.
-Note that although the extrapolation is to another population, by randomization it is a statistically identical population with common support.} Armed with this, we say that a client made a ``mistake'' if either she chose the status quo contract and her $\widehat{TE}^{fee}_{i}$ is negative (i.e.
-more cost saving from the fee contract), or if she chose the fee-commitment contract and $\widehat{TE}^{fee}_{i}$ is positive, (i.e.
-financial costs are larger for the fee-commitment contract).
-When a client made a choice mistake, we say that its peso-size is $|\widehat{TE}^{fee}_{i}|$.
-
-%Using the forcing arms and extrapolating to the choice arms.
-%Then, we predict these treatment effects for everybody in the choice arm using characteristics $x_i$.
-Let $\widehat{TE}^{fee}_{i}$ be the predicted financial cost savings for person $i$ of choosing the fee-forcing contract rather than the status quo one, divided by the size of her loan (i.e.
-the negative value of the predicted treatment effect on financial cost for person $i$).
-$\widehat{TE}^{sq}_{i}$ is the analogous for the status quo contract.
-We define the choice of person $i$ to be a ``mistake'' if
-
-%\begin{equation}
-% \{ i \; \text{chose} \; sq \; \text{and} \; \;  \widehat{TE}^{fee}_{i}>\widehat{TE}^{sq}_{i} + z \} \; \text{or} \; \{ i \; \text{chose} \; fee \; \text{and} \; \;  \widehat{TE}^{fee}_{i}<\widehat{TE}^{sq}_{i} - z \}
-%\end{equation}
-
-Since the prediction of the treatment effect is an estimate and has noise, we do two things.
-First, we normalize $\widehat{TE}^{fee}_{i}$ by the value of the loan of person $i$ and introduce a threshold parameter $z$ and say that a choice is a ``mistake'' if the alternative contract would generate greater than $z$ in savings.
-That is, we introduce a threshold that we vary from 0\% to 15\% of the value of the loan.
-{Second, we take into account uncertainty in estimation of treatment effects and report results using the extremes of the 95\% confidence interval bounds for $\widehat{TE}^{fee}_{i}$.}
-
-Figure \ref{choose_wrong}(a) plots on the left Y-axis the fraction of clients that made a choice ``mistake'' and on the right Y-axis its size in pesos.
-On the X-axis it varies the threshold $z$.
-When $z=0$, we calculate that about 75\% of clients in the fee-choice group chose contracts that induced \textit{higher} financial cost.
-%(90\% confidence interval [45,94]).
-Most mistakes are failures to choose the fee-commitment contract ({85}\%), while only {15}\% of those who chose the fee-commitment contract would have been better in the status-quo one.
-The average mistake in pesos is \$250.
-%(90\% confidence interval [140,390]).
-Figure \ref{choose_wrong}(b) plots the same curve, but separately for overconfident and non-overconfident clients, using the definition of overconfidence in Section \ref{behavioral}.
-{It shows that there are about 11 percentage points more mistakes in the overconfident population (when $z=0$), an important difference.}
-
-The findings above suggest that forcing clients into commitment contacts may reduce financial cost for the overwhelming majority of clients.
-Figure \ref{choose_wrong}(c) calculates what fraction of clients would be made better off if we forced them into the fee-commitment contract.
-We find that 85\% would be better off (using $z=0$), and they would on average have savings of 250MXN.
-This conclusion is in line with a recent paper by \cite{John}.
-In a savings context, she finds that when commitment is on the menu a majority of subjects wrongly choose too little commitment and fail to reach their savings goals.
-It is also in line with \cite{Sprenger} who show that the more naive about their present bias are the ones who demand less commitment.
-
-\vspace{.2in}
-\noindent \textbf{Is there positive selection on treatment effects?} The previous exercise consisted of extrapolating treatment effects from the no-choice arms to the choice arm.
-Here we do the reverse.
-First, we estimate a flexible model of take-up of the fee commitment contract \textit{in the choice arm} using random forests and obtain for a client with characteristics $x_i$ a probability $P(x_i)$ of choosing the fee-forcing contract.
-We then use this model to predict the counterfactual probability of a client with characteristics $x_j$ choosing the fee-commitment contract \textit{in the no choice-arms} if she would have been given the choice, what we call $\widehat{P(x_j)}$.\footnote{Our random forest take-up model has a good out-of-sample fit with an out-of-sample AUC of 0.85.} Second, armed with this prediction in the forcing arms, we can ask the following: is it true that people with larger fee-forcing contract treatment effects (i.e.
-more cost savings) are more likely to have demanded the fee-forcing contract if choice had been given to them?
-
-Figure \ref{choose_wrong}(d) plots $\widehat{P(x_i)}$ on the X-axis, and the heterogeneous treatment effects we estimated in Section \ref{TE_fee-forcing} on the Y-axis.
-It plots a binscatter that splits the X-axis into 100 percentiles bins of predicted take-up probability and for each bin averages the financial cost treatment effects.
-If it was true that those with larger cost savings have larger demand for the fee-commitment contract, we would expect a negative slope (recall that more savings mean lower financial cost in the Y-axis).
-This is not what we find.
-Using all clouds we estimate a slope close to zero in the relationship.
-Using the 80 right most points, we estimate a \textit{positive} relationship.
-A positive relation means that those more likely to demand commitment are also those that had smaller benefits from commitment.
-This result is similar to \cite{Walters}, who finds that students that select into more effective schools are the ones with smaller treatment effects from attending.\footnote{\cite{Walters} uses distance to school as an instrumental variable for choice, while we use randomization to choice vs no-choice groups as our empirical strategy.}
-
 \section{Viewing the results through a simple model} \label{model}
+
+\textcolor{red}{Need to decide Whether we keep this section or no.}
 
@@
 The model has three periods.
-In period $0$ the client is either allocated to the status quo, the fee-forcing contract, or a choice between the two.
+In period $0$ the client is either allocated to the status quo, the Forced Commitment contract, or a choice between the two.
 In period  $1$ the client decides to save to pay the monthly installment or not save, and in period $2$ the client makes the payment to recover her pawn (or not).
@@
 \noindent \textbf{Result 3}: Demand for commitment.
-Given a fee for late installment payment, (a) Neoclassical clients will never demand commitment; (b) Present-biased sophisticated clients will prefer the fee-forcing contract over the status quo contract for intermediate values of present bias; (c) naive clients will demand commitment also for intermediate but different values of present bias, and depending on parameter values may demand less commitment than sophisticated clients.\footnote{Partially naive clients will on the one hand demand more commitment than sophisticated clients since they believe (incorrectly) that a smaller fee will motivate them to pay, while on the other hand they may demand less commitment since they think they can save and pay on their own.
+Given a fee for late installment payment, (a) Neoclassical clients will never demand commitment; (b) Present-biased sophisticated clients will prefer the Forced Commitment contract over the status quo contract for intermediate values of present bias; (c) naive clients will demand commitment also for intermediate but different values of present bias, and depending on parameter values may demand less commitment than sophisticated clients.\footnote{Partially naive clients will on the one hand demand more commitment than sophisticated clients since they believe (incorrectly) that a smaller fee will motivate them to pay, while on the other hand they may demand less commitment since they think they can save and pay on their own.
 In the light of this model we seem to be finding that the latter effect dominates.
@@
 Only naive clients will be overconfident about the probability of recovery.
-This will be true whether they have the status quo or the fee-forcing contract.
+This will be true whether they have the status quo or the Forced Commitment contract.
 Overconfidence is increasing in the degree of partial naivete.
@@
 \noindent \textbf{Result 6}: Welfare and ex-post observed behavior.
-Our finding that the fee-forcing contract increases pawn recovery is ``a sign'' of higher welfare (although not a sufficient condition).
+Our finding that the Forced Commitment contract increases pawn recovery is ``a sign'' of higher welfare (although not a sufficient condition).
 
@@
 Fifth, it explains non-zero demand for commitment for a set of clients.
-Sixth, it can explain why clients exposed to the fee-forcing contract are more likely to come back namely those naifs whose welfare increased as a result of being forced into the fee-commitment contract.\footnote{Those with $\hat{\beta_i}>\beta_{SQ}>\beta$.}
+Sixth, it can explain why clients exposed to the Forced Commitment contract are more likely to come back namely those naifs whose welfare increased as a result of being forced into the fee-commitment contract.\footnote{Those with $\hat{\beta_i}>\beta_{SQ}>\beta$.}
 
@@
 Note however that while clients making purely random mistakes could explain why 10\% demand commitment ---i.e.
-(4) and (5)--- it would not explain the rest of the findings, nor why the promise-commitment (see below) had more take up that the fee-commitment, or why we can statistically predict take-up with significant accuracy (see Figure \ref{interactions_takeup} and Table \ref{Table_compliance}).
+(4) and (5)--- it would not explain the rest of the findings, nor why the Soft Commitment (see below) had more take up that the fee-commitment, or why we can statistically predict take-up with significant accuracy (see Figure \ref{interactions_takeup} and Table \ref{Table_compliance}).
 
@@
 However even for (1) it seems to us a stretch to explain people losing a valuable pawn by forgetting to pay it.
-Since the promise-commitment installment contract did not change behavior (as shown below) this explanation would also require us to posit that only fees acts as reminders, not promises.
+Since the Soft Commitment installment contract did not change behavior (as shown below) this explanation would also require us to posit that only fees acts as reminders, not promises.
 
@@
 We find that experience does not predict positive take up in our sample correlationally.} To test it we would ideally need to give choice to a group of people that randomly experienced the fee-commitment vs those that did not, and test if the former demand it more.
-Unfortunately we did not do this experiment and we have very limited data to try it: {210 (6\%)} clients were given a choice in a second pawns in our experiment after being randomly assigned to the status quo or fee-forcing contract.
+Unfortunately we did not do this experiment and we have very limited data to try it: {210 (6\%)} clients were given a choice in a second pawns in our experiment after being randomly assigned to the status quo or Forced Commitment contract.
 %\end{comment}
@@
 We do not claim that the model in the Appendix is the only possible explanation of our empirical findings, but it is a parsimonious explanation of all of them.
-
-\section{The effect of promises} \label{promises}
-
-One finding of the paper is that a rather small fee of 14 MXN on average changes behavior substantially.
-On the one hand it generates average savings for almost everybody (on the order of 200-300 pesos on average) when forced.
-But on the other hand it dissuades take up when clients have choice.
-One would want a commitment device that generates higher take-up while at the same time providing incentives for recovering the pawn.
-
-One way to go would be to decrease the already small fee say to 1\% or lower.
-We decided to instead experiment with a non-pecuniary penalty, in the form of a psychological cost of breaking a promise.
-As explained in Section \ref{Experiment} the promise contract involved making a salient promise to repay monthly, and receive a short speech by the appraiser about the importance of keeping her promise of paying monthly.
-Promises are not foreign to microfinance lending: Grameen bank for instance makes clients recite a promise at each center weekly meeting.\footnote{The exact promise repeated by clients live is this: ``\textit{We pledge to attend regularly the weekly Center meetings, to utilize our loans for the purpose approved, to save and pay our installments weekly, to use our increased incomes for the benefit of our families, to ensure that other members of our group and Center do likewise and to take collective responsibility if they do not.''}}
-
-A substantial literature documents that people don't like to break their promises, and are willing to incur in monetary losses in trying to keep them.
-To our knowledge this type of result has been replicated several times in laboratory contexts but not in a field setting like ours.
-If breaking a promise is perceived as having a lower cost than paying the 2\% fee and at the same time helps as a commitment device we could achieve better outcomes: more people would demand the promise-commitment contract.
-
-\subsection{The demand for promise-commitment contracts and their effects}
-
-\vspace{.1in}
-\noindent \textbf{Demand}.
-It turns out that the demand for the promise-commitment contract  is higher than for the fee-commitment contract by a factor of 3: {31}\% of clients offered a choice between the status quo contract and the promise-commitment contract chose commitment.
-This means that the pecuniary fee indeed limited demand for commitment.
-In passing this means also that clients are responsive to contract terms and seem to understand the conditions.
-Interestingly, the set of people who demand the promise-commitment contract are different from those that demanded the fee-commitment one.
-While in both cases the economically vulnerable demand less, in the case of the promise-commitment those that we classify as present biased, those that report that they frequently fall into temptation buying, and those that ask for reminders of payment are \textit{less} likely to demand the promise-commitment contract.
-This suggests that those taking up the promise commitment are not the ones needing the commitment (see Figure \ref{interactions_takeup} in the Appendix).
-
-\vspace{.2in}
-\noindent \textbf{Effect of choosing to promise}.
-Figure \ref{fc_pro5}(a) finds that assigning clients to the choice-promise condition has a zero effect on financial cost on average (circles).
-We see no difference even for the endogenous group that \textit{chose} to promise (squares).
-This null effect happens not only on average, but also by percentiles (not shown in Figure).
-There is also no effect on pawn recovery on (first coefficient in Figure \ref{fc_pro5}(b)), even for those that themselves choose to promise.
-And the null effect carries over if we use the definition of recovery in less than 120 days, or for the (endogenous) subgroups that paid a positive amount.
-Finally, there is no effect on repeat pawning (Figure \ref{reincidence}).
-
-\vspace{.2in}
-\noindent \textbf{Effects of forcing to promise}.
-Giving choice of whether to promise or not has the advantage of making promising an active decision by the client.
-In most of the the experimental literature promising is voluntary.
-But it has the disadvantage that we cannot measure the causal effect of promising, since those that promise are a selected sample.
-To evaluate the causal effect of promising, we compare people allocated to the promise-forcing arm (were all clients were forced to make a promise) against those in the status quo contract arm.
-Figure \ref{fc_pro5} (c) and (d) show the results.
-It documents null average treatment effects for both financial cost and recovering the pawn.
-Also there is no effect on repeat pawning.
-
-\vspace{.2in}
-\noindent The evidence presented in this section contrasts sharply with the evidence in laboratory experiments where people choosing to promise has a large effects on behavior, and where people keep their promises.
-While clients are more enthusiastic about the promise-commitment contract than the fee-commitment one in the sense of tripling take-up, the promise contract provides no commitment.
-Results for the promise arms are consistent with \cite{Ted} and \cite{John} who find that people are likely to demand commitment when the commitment is too weak to have beneficial effects.
-
-%\vspace{.2in}
-%\noindent \textit{Size of ``mistakes''.} Although promises have very muted effects, there is some heterogeneity (see Figure \ref{heterogeneous_te_3}).
-This opens the space for choice mistakes.
-Figure \ref{choose_wrong} shows that indeed there are some mistakes, but these are smaller that for the fee-choice arm.
-When $z=0$, we calculate that about 60\% of clients in the promise-choice group chose contracts that induced \textit{higher} financial cost.
-In particular gr{97\%} of those that chose the status-quo contract would have been better in the promise-commitment contract, while gr{3\%} of those who chose the promise-commitment contract would have been better in the status-quo one.
-On average they spend \$250 pesos on extra financing cost.
 
@@
 Choice may also fare better with other contracts besides the fee-commitment one we used.
-We experimented with a ``softer'' commitment contract in the form of a personal promise, and found that although promise-commitment contracts do indeed elicit more interest they did not cause changes in behavior.
+We experimented with a ``softer'' commitment contract in the form of a personal promise, and found that although Soft Commitment contracts do indeed elicit more interest they did not cause changes in behavior.
 
@@
  \footnotesize This table shows the parameter estimates of $y_i = \alpha + \beta \: OC_i + Z_i'\gamma + \epsilon_i$, where $OC_i:=\mathbbm{1}(P^s_i-\widehat{P_i(X_i)}>0)$ is an indicator for the subjective probability of recovery being larger than the predicted one.
-In columns 1-4 $y_i$ is a dummy for whether the client $i$ chose to have the commitment contract in the respective choice arm, and in columns 5 and 6 $y_i$ is the heterogeneous treatment effect for financial cost (in pesos) estimated by comparing the fee-forcing vs status quo arms in Section \ref{TE_fee-forcing}.
-Columns 1 and 3 are estimated for the promise-choice arm, while columns 2 and 4 are estimated for the fee-choice arm.
+In columns 1-4 $y_i$ is a dummy for whether the client $i$ chose to have the commitment contract in the respective choice arm, and in columns 5 and 6 $y_i$ is the heterogeneous treatment effect for financial cost (in pesos) estimated by comparing the Forced Commitment vs status quo arms in Section \ref{TE_fee-forcing}.
+Columns 1 and 3 are estimated for the promise-choice arm, while columns 2 and 4 are estimated for the Commitment Choice arm.
 The low number of observations results from  our use of  covariates for $\widehat{P(x)}$ and in $Z$ in the regression, given that some of them are missing.
@@
 
+\begin{table}[H]
+\caption{Overconfidence: Take-up and Treatment Effects}
+\label{oc_reg}
+\begin{center}
+\scriptsize{\input{./Tables/oc_reg_dec.tex}}
+\end{center}
+ \footnotesize This table shows the parameter estimates of $y_i = \alpha + \beta \: OC_i + Z_i'\gamma + \epsilon_i$, where $OC_i:=\mathbbm{1}(P^s_i-\widehat{P_i(X_i)}>0)$ is an indicator for the subjective probability of recovery being larger than the predicted one.
+In columns 1-4 $y_i$ is a dummy for whether the client $i$ chose to have the commitment contract in the respective choice arm, and in columns 5 and 6 $y_i$ is the heterogeneous treatment effect for financial cost (in pesos) estimated by comparing the Forced Commitment vs status quo arms in Section \ref{TE_fee-forcing}.
+Columns 1 and 3 are estimated for the promise-choice arm, while columns 2 and 4 are estimated for the Commitment Choice arm.
+The low number of observations results from  our use of  covariates for $\widehat{P(x)}$ and in $Z$ in the regression, given that some of them are missing.
+%\textit{Do file: } \texttt{oc.do}
+\end{table}
+
+\begin{table}[H]
+\caption{Outcome in 2S : Choose FP contract}
+\label{iv_pf}
+\begin{center}
+\scriptsize{\input{./Tables/iv_reg_pago_fijo_detailed.tex}}
+\end{center}
+ \scriptsize
+
+%\textit{Do file: } \texttt{iv\_reg\_detailed.do}
+\end{table}
+
+\begin{table}[H]
+\caption{Collapsing observations}
+\begin{center}
+\scriptsize{\input{./Tables/iv_reg_pago_fijo_detailed_colla.tex}}
+\end{center}
+ \scriptsize
+
+%\textit{Do file: } \texttt{iv\_reg\_detailed.do}
+\end{table}
+
+\begin{table}[H]
+\caption{Interaction with default in the past}
+\begin{center}
+\scriptsize{\input{./Tables/iv_reg_pago_fijo_def_collapsed.tex}}
+\end{center}
+ \scriptsize
+
+%\textit{Do file: } \texttt{iv\_reg\_intdef\_detailed.do}
+\end{table}
+
+\begin{table}[H]
+\caption{Gains for choosers versus gains from non-choosers (TOT \& TUT)}
+\label{tot_tut}
+\begin{center}
+\scriptsize{\input{./Tables/tot_tut_iv.tex}}
+\end{center}
+ \scriptsize This table shows estimates of the TOT and the TUT with an IV-LATE framework.
+The TOT (columns (1)-(3)) is computed as the usual LATE with one-sided non-compliance between the choice and control arm, and the TUT (columns (4)-(6)) is the LATE on non-compliers.
+Columns (6) and (7) estimates the effect of the compliers on the estimated HTE calculated with the Causal Random Forest.
+%\textit{Do file: } \texttt{tot\_tut.do}
+\end{table}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 We finished the experiment earlier in branches 1 and 2 because we realized that we would have enough sample size with the remaining branches and wanted to save on operational costs.
-Panel (b) shows our 5 treatment arms: control (status quo contract), no fee-forcing, promise-forcing, choice among status quo and fee-commitment, and choice among status quo promise-commitment.
+Panel (b) shows our 5 treatment arms: control (status quo contract), no Forced Commitment, promise-forcing, choice among status quo and fee-commitment, and choice among status quo Soft Commitment.
 Within each arm it displays the number of observations.
@@
 \begin{figure}[H]
-    \caption{The effect of the fee-forcing treatment}
+    \caption{The effect of the Forced Commitment treatment}
     \label{fc_pro2}
@@
     \end{center}
-     \scriptsize This figure shows the estimated effects on repeat purchasing of the four treatment arms (fee-forcing, choice-fee, fee-promise, choice-promise) compared to the status-quo control group.
+     \scriptsize This figure shows the estimated effects on repeat purchasing of the four treatment arms (Forced Commitment, choice-fee, fee-promise, choice-promise) compared to the status-quo control group.
 It shows robustness of the effects by focusing on different sub-populations.
-The leftmost coefficient compares all the fee-forcing group against all status quo group.
+The leftmost coefficient compares all the Forced Commitment group against all status quo group.
 The second coefficient conditions on the first pawn not being recovered when the second was pawned.
 The third coefficient conditions on clients who pawned again after having recovered the pawn in the experiment.
-The fourth coefficient uses all clients (in both the fee-forcing and the status-quo arms) who had an estimated heterogeneous treatment effect above the median.
+The fourth coefficient uses all clients (in both the Forced Commitment and the status-quo arms) who had an estimated heterogeneous treatment effect above the median.
 Conditioning on this set keeps the sample balanced across arms and therefore still allows for a causal interpretation.
@@
     \end{subfigure}
-        \begin{subfigure}{0.45\textwidth}
-        \caption{\footnotesize{Effect of losing pawn vs predicted take-up}}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/takeuppr_def.pdf}
-    \end{subfigure}
+    %     \begin{subfigure}{0.45\textwidth}
+    %     \caption{\footnotesize{Effect of CATE benefit vs predicted take-up}}
+    %     \centering
+    %     \includegraphics[width=\textwidth]{Figuras/benefit_choice.pdf}% takeuppr_def.pdf 
+    % \end{subfigure}
 
@@
 To do this we proceed in two steps.
-First, we estimate treatment effects in the forcing arm by comparing the fee-forcing arm against the status quo arm.
+First, we estimate treatment effects in the forcing arm by comparing the Forced Commitment arm against the status quo arm.
 We let these effects be heterogeneous as a function of our $x$'s using \cite{atheygrf}'s methodology of causal forests.
@@
 Panel (b) is analogous to Panel (a) except that it does the exercise separately for clients we classified as overconfident ($OC_i:=\mathbbm{1}(P^s_i-\widehat{P_i(X_i)}>0))$ and those we classified as not overconfident.
-Panel (c) simulates what percentage would be better by at least $z$ if we forced everybody of those in the fee-choice arm into the fee-commitment contract.
-Panel (d) asks whether it is the case that people with larger causal benefits from the fee-forcing contract would be more likely to select that contract.
+Panel (c) simulates what percentage would be better by at least $z$ if we forced everybody of those in the Commitment Choice arm into the fee-commitment contract.
+        % Panel (d) asks whether it is the case that people with larger causal benefits from the Forced Commitment contract would be more likely to select that contract.
 To do this we proceed in two steps as well.
-First we estimate a flexible model of take-up of the fee commitment contract \textit{in the choice arm} using random forests, and from this model obtain a probability $P(x_i)$ of choosing the fee-forcing contract for a client with characteristics $x_i$.
-We extrapolate this model to clients in the fee-forcing arm to estimate what would they have chosen if we had given them choice.
-Figure (d) plots $\widehat{P(x_i)}$ in the X-axis using a binscatter that splits the X-axis in 100 percentile bins.
+First we estimate a flexible model of take-up of the fee commitment contract \textit{in the choice arm} using random forests, and from this model obtain a probability $P(x_i)$ of choosing the Forced Commitment contract for a client with characteristics $x_i$.
+We extrapolate this model to clients in the Forced Commitment arm to estimate what would they have chosen if we had given them choice.
+        % Figure (d) plots $\widehat{P(x_i)}$ in the X-axis using a binscatter that splits the X-axis in 100 percentile bins.
 The Y-axis plots the heterogeneous treatment effects of the fee forcing contract on the probability of losing the pawns (more negative means then more likely to recover it), averaged for the respective x-axis bin.
@@
         %\textit{Do file: }  \texttt{effect\_contr\_takeup.do, choose\_wrong\_quant\_wrong.do, choose\_wrong\_quant\_wrong\_decomposition.do}
+\end{figure}
+
+\begin{figure}[H]
+    \caption{Effect of CATE benefit vs predicted take-up}
+    \label{}
+    \begin{center}
+    \begin{subfigure}{0.475\textwidth}
+        \caption{Effective cost/loan benefit}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/benefit_choice_tau_eff.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.475\textwidth}
+        \caption{Repayment}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/benefit_choice_tau_des.pdf}
+    \end{subfigure}
+
+    \end{center}
+     \scriptsize   This figure asks whether it is the case that people with larger causal benefits from the Forced Commitment contract would be more likely to select that contract.
+To do this we proceed in two steps.
+First we estimate a flexible model of take-up of the fee commitment contract \textit{in the choice arm} using gradient boosting classification, and from this model obtain a probability $P(x_i)$ of choosing the Forced Commitment contract for a client with characteristics $x_i$.
+We extrapolate this model to clients in the Forced Commitment arm to estimate what would they have chosen if we had given them choice.
+We plot $\widehat{P(x_i)}$ in the X-axis using a binscatter that splits the X-axis in 100 percentile bins.
+The Y-axis plots the heterogeneous treatment effects of the (a) effective cost/loan benefit and (b) repayment, averaged for the respective x-axis bin.
+Positive assortative selection would mean a negative relationship: those who benefit more by treatment and lose the pawn less are \emph{less} likely to choose it.
+          %\footnotesize{ \textit{Do file: }  \texttt{benefit\_choice.do}}
+\end{figure}
+
+\begin{figure}[H]
+    \caption{Negative selection on treatment effects}
+    \label{benefit_vs_choice_cdf}
+    \begin{center}
+    %\begin{subfigure}{0.4\textwidth}
+    %    \caption{Financial cost}
+    %    \centering
+    %    \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_2.pdf}
+    %\end{subfigure}
+    \begin{subfigure}{0.475\textwidth}
+        \caption{Effective cost/loan benefit}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/cdf_predchoose_tau_eff.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.475\textwidth}
+        \caption{Repayment}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/cdf_predchoose_tau_des.pdf}
+    \end{subfigure}
+
+    \end{center}
+     \scriptsize    CDF of the heterogeneous treatment effect for choosers vs non-choosers.
+The dotted line below indicates the points where the difference in the distributions is significant.
+Instead of a single global null hypothesis (that the two CDFs are identical), there is a continuum of individual null hypotheses of CDF equality at each point.
+This methodology was proposed by \cite{GOLDMAN2018143}.
+          %\footnotesize{ \textit{Do file: }  \texttt{benefit\_choice.do}}
 \end{figure}
@@
 
+\end{document}
+
 \newpage
@@
 	\Large{Appendix $-$ For Online Publication} \\[1em]
-	\large \author{Isaac Meza \and Joyce Sadka \and Enrique Seira}
+	\large \author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira}
 \end{center}
@@
     \scriptsize
-        The top of this figure is a sample receipt that was given to clients that got assigned to the fee-forcing contract (the font and format were changed to protect Lender's P identity).
+        The top of this figure is a sample receipt that was given to clients that got assigned to the Forced Commitment contract (the font and format were changed to protect Lender's P identity).
 We want to highlight the salience of some items.
@@
     \scriptsize
-     This figure is the analogous to Figure \ref{fc_pro2}(b), except that for the fee-forcing contract we pretend that all clients incurred in their late fees, and therefore inflate the financial cost by summing those fees.
-This is intended as a kind of worse case scenario for the financial cost of the fee-forcing contract.
+     This figure is the analogous to Figure \ref{fc_pro2}(b), except that for the Forced Commitment contract we pretend that all clients incurred in their late fees, and therefore inflate the financial cost by summing those fees.
+This is intended as a kind of worse case scenario for the financial cost of the Forced Commitment contract.
 The circles indicate the quantile treatment effects, while the cross is the (OLS) mean.
-We still find that the financial cost of will be smaller under the fee-forcing contract in spite of artificially inflating it.
+We still find that the financial cost of will be smaller under the Forced Commitment contract in spite of artificially inflating it.
      %\texttt{fc\_all\_fee.do}
@@
     \scriptsize This figure plots the empirical cumulative distribution of financial cost.
-It does this separately for the fee-forcing contract and for the status-quo contract.
+It does this separately for the Forced Commitment contract and for the status-quo contract.
 The doted line at the bottom is the difference of the status-quo CDF minus the fee-focing CDF.
-It shows that the CDF of the status quo contract is always below that of the fee-forcing (and this difference is significant for the points indicated by the blue line), and therefore that the former first-order stochastically dominates the later for weakly decreasing utility functions; see Proposition \ref{eq_fosd}.
+It shows that the CDF of the status quo contract is always below that of the Forced Commitment (and this difference is significant for the points indicated by the blue line), and therefore that the former first-order stochastically dominates the later for weakly decreasing utility functions; see Proposition \ref{eq_fosd}.
     % \texttt{ecdf\_fc.do}}
@@
 \begin{table}[H]
-\caption{Clients who should prefer fee-forcing financial cost distribution}
+\caption{Clients who should prefer Forced Commitment financial cost distribution}
 \label{stochastic_dominance}
@@
 It does this using two tests, the Anderson-Darling and the Kolmogorov-Smirnoff tests.
-Second, it fits a log normal distribution by maximum likelihood to observed empirical distribution of financial cost, separately for the fee-forcing arm and the status-quo arm.
-Using the fitted log normal, it tests whether the fee-forcing financial cost distribution would be preferred by any expected utility agent using Proposition \ref{lognormal_fosd} below.
+Second, it fits a log normal distribution by maximum likelihood to observed empirical distribution of financial cost, separately for the Forced Commitment arm and the status-quo arm.
+Using the fitted log normal, it tests whether the Forced Commitment financial cost distribution would be preferred by any expected utility agent using Proposition \ref{lognormal_fosd} below.
 The different rows of the table do this for different sub-populations.
@@
 The ``*'' show that we cannot reject at the 5\% level that both distribution are log normal for any of the two tests.
-The column entitled ``Dominance'' shows whether any client that dislikes higher cost would prefer the fee-forcing cost distribution over the status quo one, with $\succeq_{1}$ meaning he should (with $\succeq_{1}^*$ indicating the difference is statistically significant).
-It turns out to be the case that for the overwhelming majority of sub-populations, the conditions of preferring the fee-forcing distribution hold.
+The column entitled ``Dominance'' shows whether any client that dislikes higher cost would prefer the Forced Commitment cost distribution over the status quo one, with $\succeq_{1}$ meaning he should (with $\succeq_{1}^*$ indicating the difference is statistically significant).
+It turns out to be the case that for the overwhelming majority of sub-populations, the conditions of preferring the Forced Commitment distribution hold.
 %\textit{Do file: } \texttt{stoch\_dominance.do}
@@
     \footnotesize 
-    This is one(it is chosen such that it minimizes the pruned cost, that is it is the tree with the smallest root-node impurity) of the honest causal trees in the random forest we use for the estimation of the heterogeneous treatment effect of the fee-forcing contract.
+    This is one(it is chosen such that it minimizes the pruned cost, that is it is the tree with the smallest root-node impurity) of the honest causal trees in the random forest we use for the estimation of the heterogeneous treatment effect of the Forced Commitment contract.
 It is meant only as an example of how these trees look like.
@@
 \begin{figure}[H]
-    \caption{Heterogeneous Treatment Effect: Fee-forcing contract}
+    \caption{Heterogeneous Treatment Effect: Forced Commitment contract}
     \label{HTE_fee_forcing}
@@
 Panel (a) focuses on take up in the arm where clients could chose among the fee-commitment contract and the status quo contract.
-Panel (b) focuses on the arm where clients could chose among the promise-commitment contract and the status quo contract.
-Using random forests we can predict who takes up the fee-forcing contract with 85\% accuracy out of sample.\footnote{Correcting for the fact that most chose the status-quo contract using the method of SMOTE, \cite{smote} we find an accuracy rate of 75\%.} Which suggests that choice among contracts is not purely random.
+Panel (b) focuses on the arm where clients could chose among the Soft Commitment contract and the status quo contract.
+Using random forests we can predict who takes up the Forced Commitment contract with 85\% accuracy out of sample.\footnote{Correcting for the fact that most chose the status-quo contract using the method of SMOTE, \cite{smote} we find an accuracy rate of 75\%.} Which suggests that choice among contracts is not purely random.
 This figure shows that the more educated, those that report that their family typically asks for money, those that make a monthly budget of expenses, and those that ask for a remainder of their due payments (and marginally those we classify as present-biased) are more likely to chose the fee-commitment contract if given the choice.
@@
 We also assume that the amount of the loan is used up to pay for the emergency.
-\cite{John_theory} provides a more general treatment.} Period $t=0$ is a planning period where the client is either allocated to the status quo, the fee-forcing contract, or a choice between the two.
+\cite{John_theory} provides a more general treatment.} Period $t=0$ is a planning period where the client is either allocated to the status quo, the Forced Commitment contract, or a choice between the two.
 Period $t=1$ is the saving-for-the-monthly-payment  period, and $t=2$ in the pawn recovery (loan payment) period.
@@
 \noindent \textbf{Result 3: Demand for commitment.} Given $F>0$, (a) Neoclassical clients will never demand commitment.
-(b) Present-biased sophisticated clients will prefer the fee-forcing contract over the status quo contract $\iff$  $\lambda \: F<(1-\lambda)^2(b-p)$ and $F>F_{min}(\beta)$, that is $\iff$  $\beta \in [\beta_{min},\beta_{SQ}]$.\footnote{$\beta_{SQ}$ was determined in Result 1.
+(b) Present-biased sophisticated clients will prefer the Forced Commitment contract over the status quo contract $\iff$  $\lambda \: F<(1-\lambda)^2(b-p)$ and $F>F_{min}(\beta)$, that is $\iff$  $\beta \in [\beta_{min},\beta_{SQ}]$.\footnote{$\beta_{SQ}$ was determined in Result 1.
 $\beta_{min}$ is such that $F=F_{min}(\beta_{min})$.} (c) Analogously, naive clients will demand commitment $\iff$ $\hat{\beta} \in [\widehat{\beta_{min}},\beta_{SQ}]$, where $\widehat{\beta_{min}}<\beta_{min}$.
@@
 \noindent \textbf{Result 4: Overconfidence.} Only naive clients will be overconfident about the probability of recovery.
-This will be true whether they have the status quo or the fee-forcing contract.
+This will be true whether they have the status quo or the Forced Commitment contract.
 Overconfidence is increasing in $\hat{\beta}$.
@@
 \vspace{.1in}
-\noindent \textbf{Result 6: Welfare and ex-post observed behavior.} If for a naive client $i$ the fee-forcing contract causes higher pawn recovery, then we know the fee $F$ made her IC constraint binding, and therefore that $\hat{\beta}_i>\widehat{\beta}_{min}$.
+\noindent \textbf{Result 6: Welfare and ex-post observed behavior.} If for a naive client $i$ the Forced Commitment contract causes higher pawn recovery, then we know the fee $F$ made her IC constraint binding, and therefore that $\hat{\beta}_i>\widehat{\beta}_{min}$.
 If in addition if it was the case that $\beta_i<\beta_{SQ}$.
@@
 Es decir tiene que ser $\hat{\beta}>\beta_{SQ}$ correcto?}}
-then the fee-forcing contract would have increased welfare for the naive.
-That is, our finding that the fee-forcing contract increases pawn recovery is a sign of higher welfare (although not a sufficient condition).\footnote{It is not sufficient since ex-ante the commitment $F$ may have been too expensive given the income shocks, i.e.
+then the Forced Commitment contract would have increased welfare for the naive.
+That is, our finding that the Forced Commitment contract increases pawn recovery is a sign of higher welfare (although not a sufficient condition).\footnote{It is not sufficient since ex-ante the commitment $F$ may have been too expensive given the income shocks, i.e.
 if $\lambda \: F>(1-\lambda)^2(b-p)$.}

### 2022-01-26 old.tex
checkpoint before edits of tables and figues

@@
 Combining the forcing and the choice arms ---a unique feature of our experiment--- allows us to estimate the counterfactuals to answer the question of how much money is left on the table by giving choice to clients.
-We calculate that about \hl{80}\% of clients in the fee-choice group chose contracts that induced \textit{higher} financial cost.
-On average they spend an extra \$\hl{238} MXN, close to \hl{11}\% of the average loan value.
-In particular \hl{92}\% of those that chose the status-quo contract would have been better in the fee-commitment contract, while only \hl{8}\% of those who chose the fee-commitment contract would have been better in the status-quo one.
+We calculate that about 80\% of clients in the fee-choice group chose contracts that induced \textit{higher} financial cost.
+On average they spend an extra \$238 MXN, close to 11\% of the average loan value.
+In particular 92\% of those that chose the status-quo contract would have been better in the fee-commitment contract, while only 8\% of those who chose the fee-commitment contract would have been better in the status-quo one.
 This suggests that forcing clients into commitment contacts (i.e.
@@
 We document two main results in the promise arms.
-First, demand for the commitment-promise contract is three times larger than for the commitment fee contract, with \hl{31}\% take-up.
+First, demand for the commitment-promise contract is three times larger than for the commitment fee contract, with 31\% take-up.
 This difference between both choice arms suggests that clients are indeed understanding and taking into account the contractual parameters in their choice, and that the fee commitment was probably too strong from their point of view.
@@
 It also limits potential manipulation by appraisers, who in the presence of individual level randomization could potentially pick their preferred costumers from the line or tell them to wait until their desired contract shows up on the screen.
-Intra-branch day correlation on the probability of default (ICC) is small, at \hl{0.08}, so we don't lose much power vis-a-vis individual level randomization.
+Intra-branch day correlation on the probability of default (ICC) is small, at 0.08, so we don't lose much power vis-a-vis individual level randomization.
 
@@
 Theory predicts that the more overconfident (naive) may be at the same time those that benefit more from commitment.
-Extrapolating individual treatment effects of the fee-forcing contract vs the status quo one to the choice arm (see below for more detail), and using them as a dependent variable we find that overconfident borrowers benefit \textit{more} from the commitment contract, with \hl{24.8}\% (=\$\hl{30}/\$\hl{121}) more savings (columns 5 and 6).
+Extrapolating individual treatment effects of the fee-forcing contract vs the status quo one to the choice arm (see below for more detail), and using them as a dependent variable we find that overconfident borrowers benefit \textit{more} from the commitment contract, with 24.8\% (=\$30/\$121) more savings (columns 5 and 6).
 Thus while we predict the overconfident benefit more from commitment, they demand less of it.
@@
 That is, we introduce a threshold that we vary from 0\% to 15\% of the value of the loan.
-\hl{Second, we take into account uncertainty in estimation of treatment effects and report results using the extremes of the 95\% confidence interval bounds for $\widehat{TE}^{fee}_{i}$.}
+Second, we take into account uncertainty in estimation of treatment effects and report results using the extremes of the 95\% confidence interval bounds for $\widehat{TE}^{fee}_{i}$.
 
@@
 %(90\% confidence interval [45,94]).
-Most mistakes are failures to choose the fee-commitment contract (\hl{85}\%), while only \hl{15}\% of those who chose the fee-commitment contract would have been better in the status-quo one.
+Most mistakes are failures to choose the fee-commitment contract (85\%), while only 15\% of those who chose the fee-commitment contract would have been better in the status-quo one.
 The average mistake in pesos is \$250.
@@
 Figure \ref{choose_wrong}(b) plots the same curve, but separately for overconfident and non-overconfident clients, using the definition of overconfidence in Section \ref{behavioral}.
-\hl{It shows that there are about 11 percentage points more mistakes in the overconfident population (when $z=0$), an important difference.}
+It shows that there are about 11 percentage points more mistakes in the overconfident population (when $z=0$), an important difference.
 
@@
 \noindent \textbf{Demand}.
-It turns out that the demand for the promise-commitment contract  is higher than for the fee-commitment contract by a factor of 3: \hl{31}\% of clients offered a choice between the status quo contract and the promise-commitment contract chose commitment.
+It turns out that the demand for the promise-commitment contract  is higher than for the fee-commitment contract by a factor of 3: 31\% of clients offered a choice between the status quo contract and the promise-commitment contract chose commitment.
 This means that the pecuniary fee indeed limited demand for commitment.

### 2022-01-26 RScripts/grf.R

@@ -284,7 +284,7 @@ data <- read_csv('./_aux/heterogeneity_grf.csv')
 
 #Heterogeneous Effects
 for (arm in c("pro_2","pro_3")){
-  for (dep in c("eff_cost_loan", "def_c", "des_c")){
+  for (dep in c("eff_cost_loan", "def_c", "des_c", "fc_admin")){
     heterogeneity_effect(data_extended,arm,dep,1,1) 
     heterogeneity_effect(data,arm,dep,1,0) 
   }

### 2022-01-26 RScripts/te_grf.R

@@ -51,11 +51,16 @@ te_grf <- function(data_in, outcome_var, name) {
     "visit_number_d5", 
     "visit_number_d6", 
     "visit_number_d7",
+    "log_prestamo",
+    "pr_recup",
     "edad",
     "faltas",
     "val_pren_std",
     "genero",
-    "masqueprepa"
+    "pres_antes",
+    "plan_gasto_bin",
+    "masqueprepa",
+    "pb"
   ),
   c(
     "monday",
@@ -80,11 +85,16 @@ te_grf <- function(data_in, outcome_var, name) {
     "visit.number.5",
     "visit.number.6",
     "visit.number.7",
+    "log.loan",
+    "subj.pr",
     "age",
     "income.index",
     "subj.loan.value",
     "female",
-    "more.high.school"
+    "pawn.before",
+    "makes.budget",
+    "more.high.school",
+    "pb"
   ))
   
   require("dplyr")

### 2022-01-29 Tables/Attrition.tex
changes to main tables and figures

% Table generated by Excel2LaTeX from sheet 'Attrition'
\begin{tabular}{lccccccccc}
\toprule
      & \multicolumn{9}{c}{Attrition Table} \\
\midrule
      &       &       &       &       & \multicolumn{2}{c}{Fee arms} & \multicolumn{2}{c}{Promise arms} &  \\
\midrule
\midrule
      & \multicolumn{1}{p{4.045em}}{Overall} & \multicolumn{1}{p{5.59em}}{Pre-experiment} & \multicolumn{1}{p{6.455em}}{Pre-exp vs Exp (p-value)} & \multicolumn{1}{p{4.045em}}{Control} & \multicolumn{1}{p{5em}}{Forced-fee} & \multicolumn{1}{p{4.045em}}{Choice} & \multicolumn{1}{p{4.045em}}{Forced} & \multicolumn{1}{p{4.045em}}{Choice } & \multicolumn{1}{p{4.045em}}{p-value} \\
\midrule
\midrule
Number of branch-day pawns & 34    & 36    & 0.71  & 31    & 31    & 37    & 32    & 34    & 0.38 \\
      & (0.8) & (1.3) &       & (2.2) & (2.3) & (2.6) & (2.4) & (1.7) &  \\
Survey response rate &       & 0.78  &       & 0.77  & 0.75  & 0.77  & 0.8   & 0.79  & 0.46 \\
      &       & (0.01) &       & (0.02) & (0.03) & (0.02) & (0.02) & (0.02) &  \\
\% ended up pawning &       & 0.98  &       & 0.97  & 0.96  & 0.97  & 0.98  & 0.99  & 0.03 \\
      &       & (0.003) &       & (0.004) & (0.008) & (0.006) & (0.004) & (0.003) &  \\
Number of branch-days & -     & 180   &       & 84    & 80    & 93    & 68    & 82    &  \\
\midrule
Obs   & 13534 & 180   &       & 2585  & 2465  & 3406  & 2143  & 2755  &  \\
\bottomrule
\bottomrule
\end{tabular}%

### 2022-01-29 donde.tex
changes to main tables and figures

@@
 An alternate approach assumes nothing about the decision to choose (other than random sampling) and instead makes the couple of exclusion restriction-style assumptions typical of Local Average Treatment Effect (LATE) analysis.
-Namely, a) the typical LATE assumption that an individual not choosing the treatment has the same potential outcome as one not offered it, then the mirror image assumption for the Forcing arm that b) an individual forced to take Commitment has the same potential outcome as an individual choosing it, and c_ no spillovers from chooser to non-choosers in the choice arm.\footnote{Figure \ref{exclusion_restriction} in the appendix tests this assumptions.
+Namely, a) the typical LATE assumption that an individual not choosing the treatment has the same potential outcome as one not offered it, then the mirror image assumption for the Forcing arm that b) an individual forced to take Commitment has the same potential outcome as an individual choosing it, and c) no spillovers from chooser to non-choosers in the choice arm.\footnote{Figure \ref{exclusion_restriction} in the appendix tests this assumptions.
 \hl{For robustness we also try a Manski-type monotone IV approach with similar results.}}
@@
      \begin{subfigure}{0.45\textwidth}
-    \caption{As a fraction of the loan}
-       \centering
-      \includegraphics[width=\textwidth]{Figuras/hist_fc_perc_loan.pdf}
-    \end{subfigure}
-     \begin{subfigure}{0.45\textwidth}
-    \caption{Effective cost-loan ratio}
+    \caption{APR}
        \centering
@@
 Financial cost is defined as the sum of payments made by a client towards recovering her pawn + the cost of the pawned piece when she ends up losing it.
-In the paper we use different costs of losing the pawn: its value in gold, or the self reported subjective (e.g.
-jewelry may have sentimental value).
-This Figure uses the gold value.
 We plot separately the financial cost for those who lose the pawn (blue) and those that recover it (transparent).
@@
 %Given that the loan lasts close to 90 days, bringing payments to present value makes little difference.
-      %\footnotesize{ } \textit{Do file: }  \texttt{hist\_eff.do}
-\end{figure}
-
-\begin{figure}[H]
-    \caption{The effect of the Forced Commitment treatment}
-    \label{fc_pro2}
-    \begin{center}
-    \begin{subfigure}{0.42\textwidth}
-        \caption{Financial cost (MXN)}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/fc_te_pro_2.pdf}
-    \end{subfigure}
-        \begin{subfigure}{0.42\textwidth}
-        \caption{Financial cost (quantile reg)}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/fc_quantile_pro_2.pdf}
-    \end{subfigure}
-
-        \bigskip
-
-    \begin{subfigure}{0.42\textwidth}
-        \caption{Financial cost (HTE)}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_2.pdf}
-    \end{subfigure}
-    ~
-    ~
-    \bigskip
-    \begin{subfigure}{0.42\textwidth}
-        \caption{Lost pawn}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/def_te_pro_2.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.42\textwidth}
-    \caption{Losing Pawn}
+      %\footnotesize{ } \textit{Do file: }  \texttt{hist\_fc.do, hist\_eff.do}
+\end{figure}
+
+\begin{figure}[H]
+     \caption{Main treatment effects}
+    \label{main_te}
+    \begin{center}
+    \begin{subfigure}{0.75\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/main_te.pdf}
+    \end{subfigure}
+    \end{center}
+    \scriptsize
+    This figure shows the estimated treatment effect of ``forcing'' the frequent payment commitment contract using fees, compared to the control, and the effect of the choice arm, compared to the control, for the main outcomes of interest.
+The treatment effects are indicated in standard deviations, together with 95\% confidence intervals.
+\end{figure}
+
+\begin{figure}[H]
+     \caption{Quantile regressions}
+    \label{qregs}
+    \begin{center}
+    \begin{subfigure}{.45\textwidth}
+      \caption{Financial cost (in MXN)}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/qreg_fc_admin.pdf}
+    \end{subfigure}
+     \begin{subfigure}{0.45\textwidth}
+    \caption{APR}
+       \centering
+      \includegraphics[width=\textwidth]{Figuras/qreg_eff_cost_loan.pdf}
+    \end{subfigure}
+    \end{center}
+         \scriptsize
+     This figure plots the effects on different quantiles (15th, 25th, 50th, 75th, 85th percentile) of the distribution of financial cost, and APR, for the Forced-fee and Choice arms.
+      %\footnotesize{ } \textit{Do file: }  \texttt{main\_qreg.do}
+\end{figure}
+
+\begin{figure}[H]
+     \caption{Heterogeneous Treatment Effects}
+    \label{qregs}
+    \begin{center}
+    \begin{subfigure}{.45\textwidth}
+      \caption{Financial cost (in MXN)}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_pro_2.pdf}
+    \end{subfigure}
+     \begin{subfigure}{0.45\textwidth}
+    \caption{APR}
+       \centering
+      \includegraphics[width=\textwidth]{Figuras/he_dist_eff_cost_loan_pro_2.pdf}
+    \end{subfigure}
+     \begin{subfigure}{0.45\textwidth}
+    \caption{Default}
        \centering
@@
     \end{subfigure}    
-
     \end{center}
          \scriptsize
-
-      %\textit{Do file: }  \texttt{fc\_te.do, def\_te.do, fc\_quantilereg.do}
-\end{figure}
-
-\scriptsize {
-\noindent This figure shows the estimated treatment effect of ``forcing'' the frequent payment commitment contract using fees, compared to the status-quo (control).
+     plots the distribution of the heterogeneous treatment effects on financial cost, estimated using \cite{atheygrf}.
+      %\footnotesize{ } \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}
+\end{figure}
+
+% \begin{figure}[H]
+%     \caption{The effect of the Forced Commitment treatment}
+%     \label{fc_pro2}
+%     \begin{center}
+%     \begin{subfigure}{0.42\textwidth}
+%         \caption{Financial cost (MXN)}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/fc_te_pro_2.pdf}
+%     \end{subfigure}
+%         \begin{subfigure}{0.42\textwidth}
+%         \caption{Financial cost (quantile reg)}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/fc_quantile_pro_2.pdf}
+%     \end{subfigure}
+
+%         \bigskip
+
+%     \begin{subfigure}{0.42\textwidth}
+%         \caption{Financial cost (HTE)}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_2.pdf}
+%     \end{subfigure}
+%     ~
+%     ~
+%     \bigskip
+%     \begin{subfigure}{0.42\textwidth}
+%         \caption{Lost pawn}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/def_te_pro_2.pdf}
+%     \end{subfigure}
+%     \begin{subfigure}{0.42\textwidth}
+%     \caption{Losing Pawn}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_2.pdf}
+%     \end{subfigure}
+
+%     \end{center}
+%         \scriptsize
+
+%       %\textit{Do file: }  \texttt{fc\_te.do, def\_te.do, fc\_quantilereg.do}
+% \end{figure}
+
+% \scriptsize {
+% \noindent This figure shows the estimated treatment effect of ``forcing'' the frequent payment commitment contract using fees, compared to the status-quo (control).
 In Panel (a) each dot represents the estimated treatment effect for a different definition of financing cost, or for a different sub-population, and its 95\% confidence interval.
@@
 The second coefficient estimates the regression conditional on recovering the pawn {in both treatment and control}, and the rightmost coefficient compares those above the median treatment effect in financial cost savings, {versus all the control group.}
-}
-
-\begin{figure}[H]
-    \caption{The effect of the Forced Commitment treatment}
-    \label{fc_pro2}
-    \begin{center}
-    \begin{subfigure}{0.42\textwidth}
-        \caption{Effective cost/loan ratio}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/eff_te_pro_2.pdf}
-    \end{subfigure}
-        \begin{subfigure}{0.42\textwidth}
-        \caption{Financial cost (quantile reg)}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/eff_quantile_pro_2.pdf}
-    \end{subfigure}
-
-        \bigskip
-
-     \begin{subfigure}{0.42\textwidth}
-         \caption{Financial cost (HTE)}
-         \centering
-         \includegraphics[width=\textwidth]{Figuras/he_dist_eff_cost_loan_pro_2.pdf}
-     \end{subfigure}
-    ~
-    ~
-    \bigskip
-    \begin{subfigure}{0.42\textwidth}
-        \caption{Lost pawn}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/def_te_pro_2.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.42\textwidth}
-    \caption{Losing Pawn}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_2.pdf}
-    \end{subfigure}
-
-    \end{center}
-        \scriptsize
-
-      %\textit{Do file: }  \texttt{eff\_te.do, def\_te.do, eff\_quantilereg.do}
-\end{figure}
+% }
+
+% \begin{figure}[H]
+%     \caption{The effect of the Forced Commitment treatment}
+%     \label{fc_pro2}
+%     \begin{center}
+%     \begin{subfigure}{0.42\textwidth}
+%         \caption{Effective cost/loan ratio}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/eff_te_pro_2.pdf}
+%     \end{subfigure}
+%         \begin{subfigure}{0.42\textwidth}
+%         \caption{Financial cost (quantile reg)}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/eff_quantile_pro_2.pdf}
+%     \end{subfigure}
+
+%         \bigskip
+
+%      \begin{subfigure}{0.42\textwidth}
+%          \caption{Financial cost (HTE)}
+%          \centering
+%          \includegraphics[width=\textwidth]{Figuras/he_dist_eff_cost_loan_pro_2.pdf}
+%      \end{subfigure}
+%     ~
+%     ~
+%     \bigskip
+%     \begin{subfigure}{0.42\textwidth}
+%         \caption{Lost pawn}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/def_te_pro_2.pdf}
+%     \end{subfigure}
+%     \begin{subfigure}{0.42\textwidth}
+%     \caption{Losing Pawn}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_2.pdf}
+%     \end{subfigure}
+
+%     \end{center}
+%         \scriptsize
+
+%       %\textit{Do file: }  \texttt{eff\_te.do, def\_te.do, eff\_quantilereg.do}
+% \end{figure}
 

### 2022-01-29 RScripts/grf.R

@@ -283,7 +283,7 @@ data <- read_csv('./_aux/heterogeneity_grf.csv')
 
 
 #Heterogeneous Effects
-for (arm in c("pro_2","pro_3")){
+for (arm in c("pro_2")){
   for (dep in c("eff_cost_loan", "def_c", "des_c", "fc_admin")){
     heterogeneity_effect(data_extended,arm,dep,1,1) 
     heterogeneity_effect(data,arm,dep,1,0) 

### 2022-01-29 RScripts/te_grf.R

@@ -51,16 +51,11 @@ te_grf <- function(data_in, outcome_var, name) {
     "visit_number_d5", 
     "visit_number_d6", 
     "visit_number_d7",
-    "log_prestamo",
-    "pr_recup",
     "edad",
     "faltas",
     "val_pren_std",
     "genero",
-    "pres_antes",
-    "plan_gasto_bin",
-    "masqueprepa",
-    "pb"
+    "masqueprepa"
   ),
   c(
     "monday",
@@ -85,16 +80,11 @@ te_grf <- function(data_in, outcome_var, name) {
     "visit.number.5",
     "visit.number.6",
     "visit.number.7",
-    "log.loan",
-    "subj.pr",
     "age",
     "income.index",
     "subj.loan.value",
     "female",
-    "pawn.before",
-    "makes.budget",
-    "more.high.school",
-    "pb"
+    "more.high.school"
   ))
   
   require("dplyr")
@@ -257,7 +247,7 @@ te_grf <- function(data_in, outcome_var, name) {
 #####################################################
 
 # READ DATASET
-
+fc <- read_csv('./_aux/fc_te_heterogeneity.csv') 
 eff <- read_csv('./_aux/eff_te_heterogeneity.csv') 
 def <- read_csv('./_aux/def_te_heterogeneity.csv') 
 des <- read_csv('./_aux/des_te_heterogeneity.csv') 
@@ -266,6 +256,7 @@ sumporcp <- read_csv('./_aux/sumporcp_te_heterogeneity.csv')
 
 #####################################################
 
+te_grf(fc,"fc_admin","fc") 
 te_grf(eff,"eff_cost_loan","eff") 
 te_grf(def,"def_c","def") 
 te_grf(des,"des_c","des") 

### 2022-01-29 Tables/Attrition.tex
update tex file

@@
 \midrule
-      & \multicolumn{1}{p{4.045em}}{Overall} & \multicolumn{1}{p{5.59em}}{Pre-experiment} & \multicolumn{1}{p{6.455em}}{Pre-exp vs Exp (p-value)} & \multicolumn{1}{p{4.045em}}{Control} & \multicolumn{1}{p{5em}}{Forced-fee} & \multicolumn{1}{p{4.045em}}{Choice} & \multicolumn{1}{p{4.045em}}{Forced} & \multicolumn{1}{p{4.045em}}{Choice } & \multicolumn{1}{p{4.045em}}{p-value} \\
+      & \multicolumn{1}{p{4.045em}}{Overall} & \multicolumn{1}{p{3.5em}}{Pre-exp} & \multicolumn{1}{p{3.365em}}{p-value} & \multicolumn{1}{p{3.275em}}{Control} & \multicolumn{1}{p{4.775em}}{Forced-fee} & \multicolumn{1}{p{3em}}{Choice} & \multicolumn{1}{p{3em}}{Forced} & \multicolumn{1}{p{3em}}{Choice } & \multicolumn{1}{p{3.365em}}{p-value} \\
 \midrule

### 2022-01-29 donde.tex
update tex file

@@
 \begin{align*}
-    Financial \; Cost_i =& \underbrace{\sum_t \frac{P^c_{it}}{(1+r)^t}}_{\text{Discounted payments to capital}} + \underbrace{\sum_t \frac{P^f_{it}}{(1+r)^t}}_{\text{Payed fees}}  +\underbrace{\sum_t \frac{P^i_{it}}{(1+r)^t}}_{\text{Payed interests}} \\
-    &\quad\qquad + \underbrace{Pawn \: Value_i - \frac{\text{I}(Recovered \: Pawn_i) \times Pawn \: Value_i}{(1+r)^T}}_{\text{Cost of losing pawn}}
+    Financial \; Cost_i =& \underbrace{\sum_t P^c_{it}}_{\text{Discounted payments to capital}} + \underbrace{\sum_t P^f_{it}}_{\text{Payed fees}}  +\underbrace{\sum_t P^i_{it}}_{\text{Payed interests}} \\
+    &\quad\qquad + \underbrace{Pawn \: Value_i - \text{I}(Recovered \: Pawn_i) \times Pawn \: Value_i}_{\text{Cost of losing pawn}}
 \end{align*}
@@
 \begin{table}[H]
+\caption{Attrition table}
+\label{attrition_table}
+\begin{center}
+\scriptsize{\input{./Tables/Attrition.tex}}
+\end{center}
+ \scriptsize 
+%\textit{Do file: } \texttt{ss\_att.do}
+\end{table}
+
+\begin{table}[H]
 \caption{Summary statistics and Balance}
@@
 
-%\textit{Do file: } \texttt{ss.do}
+%\textit{Do file: } \texttt{ss\_att.do}
 \end{table}
@@
 \begin{center}
-    \begin{subfigure}{.40\textwidth}
-      \caption{Timeline of the experiment}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/timeline_suc_exp_extended.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.40\textwidth}
-    \caption{Experiment arms}
-       \centering
-      \includegraphics[width=\textwidth]{Figuras/exp_arms.PNG}
-    \end{subfigure}
+  \begin{minipage}[b]{1.0\linewidth}
+    \subcaption{Timeline of the experiment}
+    \centering
+        \includegraphics[width=0.4\textwidth]{Figuras/timeline_suc_exp_extended.pdf}
+        \subcaption{Experiment arms}
+\centering        
+\scriptsize{\input{./Tables/exp_arms.tex}}
+  \end{minipage}
   \end{center}
@@
 We finished the experiment earlier in branches 1 and 2 because we realized that we would have enough sample size with the remaining branches and wanted to save on operational costs.
-Panel (b) shows our 5 treatment arms: control (status quo contract), no Forced Commitment, promise-forcing, choice among status quo and fee-commitment, and choice among status quo Soft Commitment.
-Within each arm it displays the number of observations.
-For the choice groups it splits the sample size into those who chose the commitment contract (shaded blue triangle) and those that did not (un-shaded triangle).
+Panel (b) shows our 5 treatment arms.
+It shows the number of observations in each arm together with the observations for the surveys.
 %\textit{Do file: }  \texttt{timeline\_suc\_exp.do}
@@
 \newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% APPENDIX 
-\setcounter{table}{0}
-\setcounter{figure}{0}
-\setcounter{section}{0}
-\pagenumbering{gobble}
-
-\begin{center}
-	\LARGE The limits of self-commitment and private paternalism \\[0.5em]
-	\Large{Appendix $-$ For Online Publication} \\[1em]
-	\large \author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira}
-\end{center}
-
-\appendix
-\pagenumbering{arabic}
-\renewcommand\thefigure{OA-\arabic{figure}}
-\renewcommand\thetable{OA-\arabic{table}}
-\renewcommand*{\thepage}{OA - \arabic{page}}
-\renewcommand\thesection{Appendix \Alph{section}.}
-\renewcommand\thesubsection{\Alph{section}.\arabic{subsection}}
-
-%\renewcommand{\cftparskip}{0em} % NOT NEEDED
-\renewcommand\cftsecdotsep{\cftdotsep}
-\renewcommand\cftsubsecdotsep{\cftnodots}
-\renewcommand{\cftsecnumwidth}{6em}
- \renewcommand{\cftpnumalign}{r}
-%\renewcommand{\cftsecleader}{\normalfont\cftdotfill{\cftsecdotsep}}
-
-\renewcommand{\cftsecleader}{\cftdotfill{\cftsecdotsep}\hspace{1.8em}}
-%\renewcommand{\cftsecpagefont}{20em}
-%\renewcommand{\cftfignumwidth}{6em}
-%\renewcommand{\cfttabnumwidth}{3.3em}
-
-%\tableofcontents
-\etocdepthtag.toc{mtappendix}
-\etocsettagdepth{mtchapter}{none}
-\etocsettagdepth{mtappendix}{subsection}
-
-\setstretch{0.9}
-%\renewcommand\contentsname{} % the empty name
-
-\begingroup
-\let\clearpage\relax
-%\vspace{-1.5em} % the removed space. Set as appropriate
-\tableofcontents
-\endgroup
-
-\newpage
-
-\section{ Further results}
-\vspace{.2in}
-
-\subsection{Some materials}
-
-\vspace{.1in}
-\begin{figure}[H]
-     \caption{Contract Terms Summary, and Promise Slip}
-    \label{PaperSlip}
-    \begin{center}
-    \begin{subfigure}{0.65\textwidth}
-    \caption{Receipt for client}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/TicketLenderP.png}
-    \end{subfigure}
-
-    \vspace{3ex}
-    \begin{subfigure}{0.65\textwidth}
-    \caption{Personal promise signed by client}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/Personal Promise2.png}
-    \end{subfigure}
-    \end{center}
-    \scriptsize
-        The top of this figure is a sample receipt that was given to clients that got assigned to the Forced Commitment contract (the font and format were changed to protect Lender's P identity).
-We want to highlight the salience of some items.
-First the title clearly indicated which contract the client has (arrow 1).
-Second, in the case of the fee contract it clearly indicates that there is a fee for paying late equivalent to 4\% of the value of the monthly payment (arrow 2).
-Third, there is a calendar for payments clearly specifying the dates and amounts to pay each month.
-The bottom panel of the figure shows a ``promise slip'', the paper that those who were assigned (or chose) to the monthly payment with promise had to sign to make the promise salient.
-It emphasizes that the client is giving his word, and that the promise is not a legal document.
-\end{figure}
-
-\subsection{Pictures}
-
-\begin{figure}[H]
-     \caption{Some Pawnshops}
-    \label{PawnshopPicture}
-    \begin{center}
-    \begin{subfigure}{0.42\textwidth}
-    \caption{Appraiser/tellers inside a pawnshop}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/empenio9.png}
-    \end{subfigure}
-        \begin{subfigure}{0.45\textwidth}
-    \caption{Pawnshop}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/empenio11.png}
-    \end{subfigure}
-
-        \vspace{3ex}
-
-    \begin{subfigure}{0.45\textwidth}
-    \caption{Pawnshop}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/empenio2.png}
-    \end{subfigure}
-    \begin{subfigure}{0.42\textwidth}
-    \caption{Lost pawns which are for sale}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/empenio3.png}
-    \end{subfigure}
-
-    \end{center}
-    \scriptsize
-        This figure  shows pictures of pawnshops in Mexico city. They do not necessarily coincide with Lender P for confidentiality. 
-\end{figure}
-
-\vspace{.1in}
-\begin{figure}[H]
-     \caption{Gold buyers next to pawnshops}
-    \label{GoldBuyers}
-    \begin{center}
-    \begin{subfigure}{.49\textwidth}
-    \caption{Gold buyer next to pawnshop 1}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/empenio7.png}
-    \end{subfigure}
-    \begin{subfigure}{.49\textwidth}
-    \caption{Gold buyer next to pawnshop 1}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/empenio8.png}
-    \end{subfigure}
-       \vspace{3ex}
-
-    \end{center}
-    \scriptsize
-        This figure shows pictures of gold buyers next to pawnshops in Mexico city. They do not necessarily coincide with Lender P for confidentiality. 
-\end{figure}
-
-%\begin{figure}[H]
-%        \caption{Booklet with product information}
-%    \label{micas}
-%    \begin{center}
-%        \centering
-%        \includegraphics[width=\textwidth]{micas.pdf}
-%    \end{center}
-%     \footnotesize \textit{Notes: } 
-%      \footnotesize{ }
-%\end{figure}
-
-%\begin{figure}[H]
-%     \caption{Booklet with product information translated}
-%    \label{booklet_translate2}
-%    \begin{center}
-%    \begin{subfigure}{.9\textwidth}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/MP_F.pdf}
-%    \end{subfigure}
-    %\begin{subfigure}{0.55\textwidth}
-    %   \centering
-    %  \includegraphics[width=\textwidth]{Figuras/MP_2.pdf}
-    %\end{subfigure}
-%    \end{center}
-%\end{figure}
-
-\subsection{Surveys}
-
-\begin{table}[H]
-\caption{Survey's non-response balance}
-\label{balance_response}
-\begin{center}
-\scriptsize{\input{./Tables/balance_response.tex}}
-\end{center}
- \scriptsize This table shows whether the means of variables in the administrative dataset are different for those that respond the baseline survey vs those that do not.
-We use this as an assessment of external validity.
-Internal validity is guaranteed because the baseline survey was implemented before treatment assignment and therefore response rates are orthogonal to treatment assignments.
-Panel A studies the baseline survey, while Panel B focuses on the exit survey.
-The columns labeled ``p-values'' report p-values for the test that the means of the respective variable are the same for those that responded did not respond the survey.
-%\textit{Do file: } \texttt{balance\_response.do}
-\end{table}
-
-\afterpage{
-\begin{table}[H]
-\caption{Baseline survey}
-\label{baseline_survey}
-\begin{center}
-\scriptsize{\input{./Tables/transcribed.tex}}
-\end{center}
-\end{table}
-}
-
-\begin{comment}
-\begin{table}[H]
-\caption{Reincidence SS}
-\label{tab_reincidence}
-\begin{center}
-\scriptsize{\input{./Tables/tab_reincidence.tex}}
-\end{center}
- \scriptsize
-%\textit{Do file: } \texttt{tab\_reincidence.do}
-\end{table}
-
-\begin{table}[H]
-\caption{Summary statistics (exit survey)}
-\label{SS_exit}
-\begin{center}
-\scriptsize{\input{./Tables/SS_exit.tex}}
-\end{center}
- \scriptsize We carried out an exit survey.
-It had a small response rate and we don't use it in the paper.
-Here it shows that the characteristics of those that responded it are balanced across arms (Panel B).
-Panel A reports outcomes.
-%\textit{Do file: } \texttt{ss.do}
-\end{table}
-\end{comment}
-
-\newpage
-\subsection{Some more evidence of overconfidence}
-
-\vspace{.2in}
-\begin{figure}[H]
-    \caption{Behavior of those who lost pawn}
-    \label{proxy_naive}
-    \begin{center}
-    \begin{subfigure}{0.40\textwidth}
-        \caption{Elapsed days to first payment}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_firstdays_default.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.40\textwidth}
-        \caption{Elapsed days to last payment}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_days_default.pdf}
-    \end{subfigure}
-        \begin{subfigure}{0.40\textwidth}
-        \caption{Payments as \% of loan}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_percpay_default.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.40\textwidth}
-        \caption{Number of payments}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_numpay_default.pdf}
-    \end{subfigure}
-    \end{center}
-        \scriptsize 
-        This figure describes behavior for the subsample of clients whose pawn was not recovered (in the control group).
-Panel (a) shows days elapsed from the pawn to the first payment, while panel (b) displays the days elapsed to last payment.
-Some people pay after the day 105 when the grace period ends because the can ``restart'' the loan if they pay all interest owed.
-It amounts to starting a new loan with the same conditions and same pawn.
-Panel (c) shows the fraction of the loan that they paid (even when they ended up losing the pawn).
-Panel (d) displays the number of times they went to the branch to pay.
-      %\textit{Do file: }  \texttt{hist\_den\_default.do}
-\end{figure}
-
-\newpage
-\subsection{Main treatment effects: Additional material}
-
-\vspace{.2in}
-
-\begin{figure}[H]
-        \caption{FC conditional on first 115 days - treatment effect}
-    \label{fc_pro_2_115}
-    \begin{center}
-        \centering
-        \includegraphics[width=0.50\textwidth]{Figuras/fc_te_115_pro_2.pdf}
-    \end{center}
-     \scriptsize This figure is the same as in Figure \ref{fc_pro2} Panel (a), but with the subsample restricted to the first 115 days.
-     %\textit{Do file: }  \texttt{fc\_te\_115.do}
-\end{figure}
-
-\begin{figure}[H]
-        \caption{Financial cost effect: charging all fees}
-    \label{fc_allfee}
-    \begin{center}
-        \centering
-        \includegraphics[width=0.50\textwidth]{Figuras/fc_allfee_quantile_pro_2.pdf}
-    \end{center}
-    \scriptsize
-     This figure is the analogous to Figure \ref{fc_pro2}(b), except that for the Forced Commitment contract we pretend that all clients incurred in their late fees, and therefore inflate the financial cost by summing those fees.
-This is intended as a kind of worse case scenario for the financial cost of the Forced Commitment contract.
-The circles indicate the quantile treatment effects, while the cross is the (OLS) mean.
-We still find that the financial cost of will be smaller under the Forced Commitment contract in spite of artificially inflating it.
-     %\texttt{fc\_all\_fee.do}
-\end{figure}
-
-\begin{figure}[H]
-        \caption{FC as \% of loan - treatment effect}
-    \label{fc_perc}
-    \begin{center}
-        \centering
-        \includegraphics[width=0.50\textwidth]{Figuras/fc_perc_te_allarms.pdf}
-    \end{center}
-     \scriptsize This figure shows the estimated treatment effect of all arms against the status quo, but normalizing the dependent variable by the value of the loan.
-     %\textit{Do file: }  \texttt{fc\_perc\_allarms.do}
-\end{figure}
-
-\begin{figure}[H]
-    \caption{Relationship between treatment effects}
-    \label{induced_to_pay_early}
-    \begin{center}
-    \begin{subfigure}{0.45\textwidth}
-        \caption{\footnotesize{Induced to pay earlier vs Induced Lower FC}}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/binscatter_fc_days_pro_2.pdf}
-    \end{subfigure}
-        \begin{subfigure}{0.45\textwidth}
-        \caption{\footnotesize{Induced to pay earlier vs Induced Recovery}}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/binscatter_def_days_pro_2.pdf}
-    \end{subfigure}
-    \end{center}
-       \scriptsize 
-       This figure plots relationships between \textit{treatment effects}.
-Both Panels (a) an (b) have the same X-axis, which displays the estimated heterogeneous treatment effect on the outcome ``elapsed days of first payment'', that is how many days elapsed from the day the loan was awarded to the first payment the client made.
-The treatments effects were calculated using \cite{atheygrf}.
-In Panel (a) the Y-axis is the \textit{treatment effect} on financial cost.
-In Panel (b) the Y-axis is the \textit{treatment effect} on losing their pawn.
-Panel (a) shows that those induced to pay earlier are also those that have larger savings in financial cost as a result of ``forcing'' the frequent payment commitment contract compared to the status-quo (control).
-Panel (b) shows that those induced to pay earlier are also those that have a larger increase in recovery.
-      %\textit{Do file: }  \texttt{binscatter\_hte.do}
-\end{figure}
-
-\begin{figure}[H]
-        \caption{Repeat purchase before 30/60 days}
-    \label{reincidence_before}
-    \begin{center}
-        \centering
-        \includegraphics[width=0.50\textwidth]{Figuras/re_te_earlydays.pdf}
-    \end{center}
-     \scriptsize This figure shows the estimated treatment effect of repeat purchase before 30 \& 60 days.
-     %\textit{Do file: }  \texttt{re\_te\_earlydays.do}
-\end{figure}
-
-\newpage
-
-\begin{table}[H]
-\caption{Intermediate outcomes}
-\label{mechanisms}
-\begin{center}
-\scriptsize{\input{./Tables/mechanism.tex}}
-\end{center}
-
-%\textit{Do file: } \texttt{mechanisms.do}
-\end{table}
-
-\scriptsize {
-\noindent This table explores treatment effects in ``intermediate variables''.
-Each column represents a different dependent variable in an OLS regression, and each panel represents a different treatment arm-control comparison.
-All regressions include fixed effects for branch, day of week fixed effects, number of pawns at the time of pawning this particular one, number of different treatment arms experienced before pawning this particular one.
-$R^2$ are not reported, they were less than 0.04 for all but the last column which had $R^2$'s close to 0.6.
-The last row shows the mean of the dependent variable for the control group.
-Dependent variables are as follows: Column (1) measures the number of days elapsed from the pawning date to the first payment done.
-Column (2) records the number of payments done within 230 days of the pawn.
-Column (3) is the average size of the payments for each client in pesos.
-Column (4) is self-reported cost to get to the branch plus the imputed loss of a whole day of salary (using the minimum wage in Mexico) multiplied by the number of visits to the branch.
-Column (5) measures the number of days it took to recover the pawn, conditional on recovering.
-The dependent variable in Column (6) is a dummy =1 if the client paid any positive amount within 230 days of the pawn.
-For Columns (7) and (8) the dependent variable it is the sum of total payments done within 230 days of the pawn divided by the size of the loan, but column (8) includes as regressors a dummy=1 if the client recovered her pawn, and its interaction with treatment.
-}
-
-\vspace{3ex}
-
-\vspace{.3in}
-
-\subsection{FOSD: fee forcing vs status quo financial cost distributions}
-
-\vspace{.2in}
-\begin{figure}[H]
-        \caption{Empirical CDF of Financial Cost: fee-focing vs status-quo}
-    \label{ecdf_fc}
-    \begin{center}
-        \centering
-        \includegraphics[width=0.65\textwidth]{Figuras/cdf_fc_pro_2.pdf}
-    \end{center}
-    \scriptsize This figure plots the empirical cumulative distribution of financial cost.
-It does this separately for the Forced Commitment contract and for the status-quo contract.
-The doted line at the bottom is the difference of the status-quo CDF minus the fee-focing CDF.
-It shows that the CDF of the status quo contract is always below that of the Forced Commitment (and this difference is significant for the points indicated by the blue line), and therefore that the former first-order stochastically dominates the later for weakly decreasing utility functions; see Proposition \ref{eq_fosd}.
-    % \texttt{ecdf\_fc.do}}
-\end{figure}
-
-\vspace{.2in}
-\begin{table}[H]
-\caption{Clients who should prefer Forced Commitment financial cost distribution}
-\label{stochastic_dominance}
-\begin{center}
-\scriptsize{\input{./Tables/dominance.tex}}
-\end{center}
- \scriptsize
-This table does two things.
-First, it tests whether the observed empirical distribution of financial cost is well approximated by a log normal.
-It does this using two tests, the Anderson-Darling and the Kolmogorov-Smirnoff tests.
-Second, it fits a log normal distribution by maximum likelihood to observed empirical distribution of financial cost, separately for the Forced Commitment arm and the status-quo arm.
-Using the fitted log normal, it tests whether the Forced Commitment financial cost distribution would be preferred by any expected utility agent using Proposition \ref{lognormal_fosd} below.
-The different rows of the table do this for different sub-populations.
-The first row of the table does it for every client in the fee forcing and status quo arms.
-The ``*'' show that we cannot reject at the 5\% level that both distribution are log normal for any of the two tests.
-The column entitled ``Dominance'' shows whether any client that dislikes higher cost would prefer the Forced Commitment cost distribution over the status quo one, with $\succeq_{1}$ meaning he should (with $\succeq_{1}^*$ indicating the difference is statistically significant).
-It turns out to be the case that for the overwhelming majority of sub-populations, the conditions of preferring the Forced Commitment distribution hold.
-%\textit{Do file: } \texttt{stoch\_dominance.do}
-\end{table}
-
-\vspace{.2in}
-\begin{prop}
-\label{lognormal_fosd}
-\footnotesize{
-Let $F$ and $G$ be the cumulative distributions of two alternative log-normal prospects. The following are equivalent:
-
-\begin{enumerate}[(a)]
-    \item For every weakly decreasing utility function $u$: $E_{F}(u(FC))\leq E_G(u(FC))$
-    \item $E_F \log(FC)\geq E_G\log(FC)$ and $Var_F \log(FC)= Var_G\log(FC)$
-\end{enumerate}
-}
-\end{prop}
-
-\begin{proof}
-\footnotesize{
-See Theorem 4 in \cite{lognormal_dominance}.
-}
-\end{proof}
-
-\newpage
-
-\vspace{.1in}
-\begin{prop}
-\label{eq_fosd}
-\footnotesize{
-This is a standard result. 
-\\
-\vspace{.1in}
-The following are equivalent:
-\begin{enumerate}[(a)]
-    \item For every weakly decreasing utility function $u$: $E_{sq}(u(FC))\leq E_{fee}(u(FC))$
-    \item $F_{sq}(FC)\leq F_{fee}(FC)$ 
-\end{enumerate}
-}
-\end{prop}
-\begin{proof} \;
-\footnotesize{
-
-[$(a)\Longrightarrow (b)$] Suppose  $(b)$ does not hold. So there exists $FC^*$ such that $F_{sq}(FC^*)>F_{fee}(FC^*)$, Define $u:=\mathds{1}_{FC\leq FC^*}$. Then
-\[E_{sq}(u(FC)) = \int u(FC)dF_{sq} = F_{sq}(FC^*)>F_{fee}(FC^*)= \int u(FC)dF_{fee} =E_{fee}(u(FC))\]
-which contradicts $(a)$.\\
-
-[$(a)\Longleftarrow (b)$] On the other hand for $u$ weakly decreasing,
-
-\[\int u(y(FC))dF_{sq}(y(FC)) = \int u(y(FC))dF_{fee}(FC) \leq \int u(FC)dF_{fee}(FC)\]
-with $y(FC) = F_{sq}^{-1}F_{fee}(FC)$.
-}
-\end{proof}
-\footnotesize{
-Note the proof was done in the case of absolutely continuous and strictly increasing distribution functions $F_{sq}$ and $F_{fee}$.
-}
-
-\newpage
-\subsection{Causal Random Forest and HTE}
-
-\vspace{.3in}
-\begin{figure}[H]
-        \caption{Honest causal tree for the fee forcing contract heterogenous treatment effects}
-    \label{casual_tree}
-    \begin{center}
-        \centering
-        \includegraphics[width=.8\textwidth]{Figuras/crf_pro_2_fc_admin_disc.pdf}
-    \end{center}
-    \footnotesize 
-    This is one(it is chosen such that it minimizes the pruned cost, that is it is the tree with the smallest root-node impurity) of the honest causal trees in the random forest we use for the estimation of the heterogeneous treatment effect of the Forced Commitment contract.
-It is meant only as an example of how these trees look like.
-The forest was such that there are as many estimated treatment effects as there are clients.
-     %\footnotesize{ \textit{RScript: }  \texttt{grf.R}
-\end{figure}
-
-We use \cite{atheygrf} \texttt{causal\_forest} of the \texttt{grf} library in $R$. The parameters used were:
-\scriptsize{\textit{causal\_forest(
-  X, 
-  Y, 
-  W, 
-  Y.hat = NULL, 
-  W.hat = NULL, 
-  num.trees = 2000, 
-  sample.weights = NULL, 
-  clusters = NULL, 
-  equalize.cluster.weights = FALSE, 
-  sample.fraction = 0.5, 
-  mtry = min(ceiling(sqrt(ncol(X)) + 20),ncol(X)), 
-  min.node.size = 5, 
-  honesty = TRUE, 
-  honesty.fraction = 0.5, 
-  honesty.prune.leaves = TRUE, 
-  alpha = 0.05, 
-  imbalance.penalty = 0, 
-  stabilize.splits = TRUE, 
-  ci.group.size = 2, 
-  tune.parameters = "none", 
-  tune.num.trees = 200, 
-  tune.num.reps = 50, 
-  tune.num.draws = 1000, 
-  compute.oob.predictions = TRUE, 
-  orthog.boosting = FALSE, 
-  num.threads = NULL)}}
-
-\begin{figure}[H]
-    \caption{Heterogeneous Treatment Effect: Forced Commitment contract}
-    \label{HTE_fee_forcing}
-    \begin{center}
-    %\begin{subfigure}{0.4\textwidth}
-    %    \caption{Financial cost}
-    %    \centering
-    %    \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_2.pdf}
-    %\end{subfigure}
-    \begin{subfigure}{0.7\textwidth}
-        \caption{Determinants of effects}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_fc_admin_disc_pro_2.pdf}
-    \end{subfigure}
-
-    %\begin{subfigure}{0.4\textwidth}
-    %    \caption{Losing Pawn}
-    %    \centering
-    %    \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_2.pdf}
-    %\end{subfigure}
-    %\begin{subfigure}{0.4\textwidth}
-    %    \caption*{}
-    %    \centering
-    %    \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_def_c_pro_2.pdf}
-    %\end{subfigure}
-    \end{center}
-     \scriptsize  This figure estimates bivariate regressions of the estimated client-level heterogeneous treatment effects against the respective covariate from the baseline survey  $\widehat{hte_i} = \alpha + \beta \: X_i + \epsilon_i$.
-The regressors $X_i$ include (e.g if the family asks for money, if they have savings, if they are overconfident using the definition the text, etc.
-See this Appendix for a transcription of the survey).
-      %\footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}}
-\end{figure}
-
-\begin{comment}
-\begin{figure}[H]
-    \caption{Heterogeneous Treatment Effect: Promise-forcing contract}
-    \label{heterogeneous_te_3}
-    \begin{center}
-    \begin{subfigure}{0.4\textwidth}
-        \caption{Financial cost}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_3.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.4\textwidth}
-        \caption*{}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_fc_admin_disc_pro_3.pdf}
-    \end{subfigure}
-
-    \begin{subfigure}{0.4\textwidth}
-        \caption{Losing Pawn}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_3.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.4\textwidth}
-        \caption*{}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_def_c_pro_3.pdf}
-    \end{subfigure}
-    \end{center}
-     \scriptsize
-      %\footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}}
-\end{figure}
-\end{comment}
-
-\begin{comment}
-
-\begin{figure}[H]
-    \caption{Heterogeneous Treatment Effect - Choice/Fee}
-    \label{heterogeneous_te_4}
-    \begin{center}
-    \begin{subfigure}{0.4\textwidth}
-        \caption{Financial cost}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_4.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.4\textwidth}
-        \caption*{}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_fc_admin_disc_pro_4.pdf}
-    \end{subfigure}
-
-    \begin{subfigure}{0.4\textwidth}
-        \caption{Losing Pawn}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_4.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.4\textwidth}
-        \caption*{}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_def_c_pro_4.pdf}
-    \end{subfigure}
-    \end{center}
-     \footnotesize \textit{Notes: } The distribution plots the FC treatment effect for the interval $[\mu-2\sigma,\mu+2\sigma]$ to ignore the outliers.
-      \footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}}
-\end{figure}
-
-\begin{figure}[H]
-    \caption{Heterogeneous Treatment Effect - Choice/Promise}
-    \label{heterogeneous_te_5}
-    \begin{center}
-    \begin{subfigure}{0.4\textwidth}
-        \caption{Financial cost}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_5.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.4\textwidth}
-        \caption*{}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_fc_admin_disc_pro_5.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.4\textwidth}
-        \caption{Losing Pawn}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_5.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.4\textwidth}
-        \caption*{}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_def_c_pro_5.pdf}
-    \end{subfigure}
-    \end{center}
-     \footnotesize \textit{Notes: } 
-      \footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}}
-\end{figure}
-
-\end{comment}
-
-%\begin{figure}[H]
-%    \caption{Heterogeneous Treatment Effect (FC survey) - All arms}
-%    \label{heterogeneous_te_fcsurvey_all}
-%    \begin{center}
-%    \begin{subfigure}{0.4\textwidth}
-%        \caption{Forcing/Fee}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_survey_disc_pro_2.pdf}
-%    \end{subfigure}
-%    \begin{subfigure}{0.4\textwidth}
-%        \caption{Forcing/Promise}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_survey_disc_pro_3.pdf}
-%    \end{subfigure}
-
-%    \begin{subfigure}{0.4\textwidth}
-%        \caption{Choice/Fee}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_survey_disc_pro_4.pdf}
-%    \end{subfigure}
-%    \begin{subfigure}{0.4\textwidth}
-%        \caption{Choice/Promise}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_survey_disc_pro_5.pdf}
-%    \end{subfigure}
-%    \end{center}
-%     \footnotesize \textit{Notes: } 
-%      \footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}}
-%\end{figure}
-
-\subsection{Take up}
-
-\begin{table}[H]
-    \caption{Predicting Take-up: Goodness-of-Fit}
-    \label{Table_compliance}
-    %\begin{subtable}{1\textwidth}
-    % \centering
-    %    \caption{Take up}
-    %    \scriptsize{\input{./Tables/oos_pago_frec_vol.tex}}
-    %\end{subtable}%
-
-    %\bigskip
-     \begin{subtable}{1\textwidth}
-      \centering
-        \caption{Take up: Choice-fee Arm}
-        \scriptsize{\input{./Tables/oos_pago_frec_vol_fee.tex}}
-    \end{subtable}
-
-      \bigskip
-    \begin{subtable}{1\textwidth}
-      \centering
-        \caption{Take up: Choice-promise Arm}
-        \scriptsize{\input{./Tables/oos_pago_frec_vol_promise.tex}}
-    \end{subtable}
-            \scriptsize
-           \\
-           \\
-           \\
-
-     %\textit{Scripts: } \texttt{pred\_take\_up.do, pfv\_pred.R}
-\end{table}
-
-\vspace{.1in}
-\begin{figure}[H]
-    \caption{Out of sample ROC curve}
-    \label{roc_curve}
-    \begin{center}
-    \begin{subfigure}{0.45\textwidth}
-        \caption{Take-up in Fee Arm}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/Boost/ROC_curve_outsample_pago_frec_vol_fee.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.45\textwidth}
-        \caption{Take-up in Promise Arm}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/Boost/ROC_curve_outsample_pago_frec_vol_promise.pdf}
-    \end{subfigure}
-    \end{center}
-     \scriptsize 
-  %\footnotesize{ \textit{Do file: }  \texttt{pred\_take\_up.do}}
-\end{figure}
-
-\begin{figure}[H]
-    \caption{Predictors of commitment contract take-up}
-    \label{interactions_takeup}
-    \begin{center}
-    \begin{subfigure}{0.45\textwidth}
-        \caption{with Fee Arm}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/pago_frec_vol_fee_interactions_rf.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.45\textwidth}
-        \caption{with Promise Arm}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/pago_frec_vol_promise_interactions_rf.pdf}
-    \end{subfigure}
-    \end{center}
-     \scriptsize
-      %\footnotesize{ \textit{Do file: }  \texttt{analyze\_fvp.do}}
-\end{figure}
-
-\scriptsize {
-\noindent This figure reports bivariate regressions of the form $\widehat{TakeUp} = \alpha + \beta \: X_i + \epsilon_i$, where $\widehat{TakeUp}$ is the prediction using random forests.
-The figure reports the $\beta$ coefficients for different $X_i$'s along with 95\% confidence intervals.
-Panel (a) focuses on take up in the arm where clients could chose among the fee-commitment contract and the status quo contract.
-Panel (b) focuses on the arm where clients could chose among the Soft Commitment contract and the status quo contract.
-Using random forests we can predict who takes up the Forced Commitment contract with 85\% accuracy out of sample.\footnote{Correcting for the fact that most chose the status-quo contract using the method of SMOTE, \cite{smote} we find an accuracy rate of 75\%.} Which suggests that choice among contracts is not purely random.
-This figure shows that the more educated, those that report that their family typically asks for money, those that make a monthly budget of expenses, and those that ask for a remainder of their due payments (and marginally those we classify as present-biased) are more likely to chose the fee-commitment contract if given the choice.
-The opposite holds for clients that are more economically vulnerable (can barely pay for food, electricity, etc) and those that report being more stressed.
-}
-
-%---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
-
-\newpage
-
-\subsection{New results}
-
-\begin{table}[H]
-\caption{Summary statistics and Balance}
-\label{SS}
-\begin{center}
-\scriptsize{\input{./Tables/SS_appendix.tex}}
-\end{center}
- \scriptsize
-
-%\textit{Do file: } \texttt{SS\_appendix.do}
-\end{table}
-
-\begin{figure}[H]
-        \caption{Financial cost for different discount rates}
-    \label{fc_discount_rates}
-    \begin{center}
-        \centering
-        \includegraphics[width=0.55\textwidth]{Figuras/discount_effect.pdf}
-    \end{center}
-     \scriptsize This Figure estimates the treatment effect on financial cost with different discount rates.  
-     %\textit{Do file: }  \texttt{discounted\_noeffect.do}
-\end{figure}
-
-\begin{figure}[H]
-    \caption{Treatment effects pooling all arms}
-    \label{pooled_arms_te}
-    \begin{center}
-    \begin{subfigure}{0.45\textwidth}
-        \caption{Financial Cost}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/te_allarms_fc_admin_disc.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.45\textwidth}
-        \caption{Lost Pawn}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/te_allarms_def_c.pdf}
-    \end{subfigure}
-    \end{center}
-     \scriptsize
-      %\footnotesize{ \textit{Do file: }  \texttt{te\_allarms.do}}
-\end{figure}
-
-\scriptsize {
-\noindent This Figure shows the treatment effects for the main outcomes when pooling all arms in the same regression.
-}
-
-\begin{figure}[H]
-        \caption{Treatment effect decomposition of the Financial Cost }
-    \label{reg_int_pro_2}
-    \begin{center}
-        \centering
-        \includegraphics[width=0.60\textwidth]{Figuras/int_te_pro_2.pdf}
-    \end{center}
-     \scriptsize This Figure is a "close-up" for the estimates found in Figure \ref{fc_pro2} - Panel (a).
-It shows the treatment effects on payed \& incurred interest, the former defined as the actual interest payed, and the latter is the sum of all potential interests (for those pawns that were lost we calculate the interest generated until day 230).
-In the right axis we show the treatment effect on the payed fees.
-Finally, we analyze this effect for the subsamples that recovers or loses the pawn.
-     %\textit{Do file: }  \texttt{reg_\int.do}
-\end{figure}
-
-\begin{figure}[H]
-        \caption{Frequency of renewals}
-    \label{ref_dist}
-    \begin{center}
-        \centering
-        \includegraphics[width=0.60\textwidth]{Figuras/ref_dist.pdf}
-    \end{center}
-     \scriptsize  This Figure shows the occurrence and frequency of renewals.
-It locates in time, respective to the day the loan started, when the renewal occurs for both the first and second renewal.
-Note that the first renewal is concentrated around 100 days, while the second is concentrated around the 200 days, corresponding to the first and second cycle.
-     %\textit{Do file: }  \texttt{ref_\dist.do}
-\end{figure}
-
-\begin{figure}[H]
-        \caption{Probability of recovery by arm}
-    \label{survival_graph}
-    \begin{center}
-        \centering
-        \includegraphics[width=0.60\textwidth]{Figuras/survival_graph_unpledge.pdf}
-    \end{center}
-     \scriptsize  This Figure shows the accumulated percentage of recovery in time by treatment arm. 
-     %\textit{Do file: }  \texttt{survival\_graph.do}
-\end{figure}
-
-%\begin{figure}[H]
-%    \caption{Exit Survey: reasons to pawn or not again with monthly payments}
-%    \label{reasons}
-%    \begin{center}
-%    \begin{subfigure}{0.5\textwidth}
-%        \caption{Pawn again because:}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/razones_si.pdf}
-%    \end{subfigure}
-%    \begin{subfigure}{0.5\textwidth}
-%        \caption{Not pawn because:}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/razones_no.pdf}
-%    \end{subfigure}
-%    \end{center}
-%     \footnotesize \textit{Notes: } 
-%      \footnotesize{ \textit{Do file: }  \texttt{ss.do}}
-%\end{figure}
-
-%\begin{figure}[H]
-%    \caption{Decomposition of the mistakes by `Overconfidence' for Promise Arms}
-%    \label{Promise_errors}
-%    \begin{center}
-%    \begin{subfigure}{0.6\textwidth}
-%        \caption{Promise}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/line_cw_fc_te_cf_OC_promise.pdf}
-%    \end{subfigure}
-%    \end{center}
-%     \footnotesize 
-%     \textit{Notes: }  Decomposition of the percentage of mistakes by overconfidence. 
-%       \textit{Do file: }  \texttt{choose\_wrong\_quant\_wrong\_decomposition.do}
-%\end{figure}
-
-\begin{comment}
-\begin{figure}[H]
-        \caption{Histogram of payments}
-    \label{HistPayments}
-    \begin{center}
-    \begin{subfigure}{.31\textwidth}
-    \caption{Control}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_payments_pro_1.pdf}
-    \end{subfigure}
-    \begin{subfigure}{.31\textwidth}
-    \caption{Forcing - fee}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_payments_pro_2.pdf}
-    \end{subfigure}   
-     \begin{subfigure}{.31\textwidth}
-    \caption{Forcing - promise}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_payments_pro_3.pdf}
-    \end{subfigure}  
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - fee}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_payments_pro_4.pdf}
-    \end{subfigure}  
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - fee - SQ}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_payments_pro_6.pdf}
-    \end{subfigure}    
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - fee - NSQ}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_payments_pro_7.pdf}
-    \end{subfigure}    
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - promise}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_payments_pro_5.pdf}
-    \end{subfigure}  
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - promise - SQ}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_payments_pro_8.pdf}
-    \end{subfigure}    
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - promise - NSQ}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_payments_pro_9.pdf}    
-    \end{subfigure}        
-    \end{center}
-     \footnotesize \textit{Notes: } The x-axis shows the elapsed days between initial date and current movement.
-      \footnotesize{ \textit{Do file: }  \texttt{hist\_payments.do}}
-\end{figure}
-\end{comment}
-
-%\begin{figure}[H]
-%        \caption{Types of agents that incur in different FC}
-%    \label{components_fc}
-%    \begin{center}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/scatter_fc_pay.pdf}
-%    \end{center}
-%     \footnotesize \textit{Notes: } 
-%      \footnotesize{ \textit{Do file: }  \texttt{hist\_fc.do}}
-%\end{figure}
-
-\begin{comment}
-\begin{figure}[H]
-        \caption{Percentage of payments}
-    \label{perc_payments}
-    \begin{center}
-    \begin{subfigure}{.31\textwidth}
-    \caption{Control}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_1.pdf}
-    \end{subfigure}
-    \begin{subfigure}{.31\textwidth}
-    \caption{Forcing - fee}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_2.pdf}
-    \end{subfigure}   
-     \begin{subfigure}{.31\textwidth}
-    \caption{Forcing - promise}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_3.pdf}
-    \end{subfigure}  
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - fee}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_4.pdf}
-    \end{subfigure}  
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - fee - SQ}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_6.pdf}
-    \end{subfigure}    
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - fee - NSQ}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_7.pdf}
-    \end{subfigure}    
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - promise}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_5.pdf}
-    \end{subfigure}  
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - promise - SQ}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_8.pdf}
-    \end{subfigure}    
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - promise - NSQ}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_9.pdf}    
-    \end{subfigure}        
-    \end{center}
-     \footnotesize \textit{Notes: } 
-      \footnotesize{ \textit{Do file: }  \texttt{hist\_payments.do}}
-\end{figure}
-
-\begin{figure}[H]
-        \caption{Percentage of payment conditional on positive payment and Losing Pawn}
-    \label{perc_payments_conditional}
-    \begin{center}
-    \begin{subfigure}{.31\textwidth}
-    \caption{Control}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_1.pdf}
-    \end{subfigure}
-    \begin{subfigure}{.31\textwidth}
-    \caption{Forcing - fee}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_2.pdf}
-    \end{subfigure}   
-     \begin{subfigure}{.31\textwidth}
-    \caption{Forcing - promise}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_3.pdf}
-    \end{subfigure}  
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - fee}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_4.pdf}
-    \end{subfigure}  
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - fee - SQ}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_6.pdf}
-    \end{subfigure}    
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - fee - NSQ}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_7.pdf}
-    \end{subfigure}    
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - promise}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_5.pdf}
-    \end{subfigure}  
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - promise - SQ}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_8.pdf}
-    \end{subfigure}    
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - promise - NSQ}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_9.pdf}    
-    \end{subfigure}        
-    \end{center}
-     \footnotesize \textit{Notes: } 
-      \footnotesize{ \textit{Do file: }  \texttt{hist\_payments.do}}
-\end{figure}
-\end{comment}
-
-%\begin{figure}[H]
-%    \caption{Evolution of payment}
-%    \label{Evolution payment}
-%    \begin{center}
-%    \begin{subfigure}{0.49\textwidth}
-%        \caption{Paid loans}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/desempeno_evol.pdf}
-%    \end{subfigure}
-%     \begin{subfigure}{0.49\textwidth}
-%      \caption*{}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/desempeno_evol_choice.pdf}
-%    \end{subfigure}
-
-%     \begin{subfigure}{0.49\textwidth}
-%        \caption{Average percentage of paid loans}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/sum_porc_evol.pdf}
-%    \end{subfigure}
-%     \begin{subfigure}{0.49\textwidth}
-%      \caption*{}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/sum_porc_evol_choice.pdf}
-%    \end{subfigure}
-
-%   \begin{subfigure}{0.49\textwidth}
-%        \caption{Average percentage of paid loans | paid}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/sum_porc_cond_evol.pdf}
-%    \end{subfigure}
-%     \begin{subfigure}{0.49\textwidth}
-%      \caption*{}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/sum_porc_cond_evol_choice.pdf}
-%    \end{subfigure}
-%    \end{center}
-%     \footnotesize \textit{Notes: } 
-%      \footnotesize{ \textit{Do file: }  \texttt{evol\_payment.do}}
-%\end{figure}
-
-\begin{comment}
-
-\begin{figure}[H]
-        \caption{FC effect for different discount rates}
-    \label{oc_hist}
-    \begin{center}
-        \centering
-        \includegraphics[width=0.50\textwidth]{Figuras/discount_effect.pdf}
-    \end{center}
-    \footnotesize \textit{Notes: } 
-     \footnotesize{ \textit{Do file: }  \texttt{discounted\_noeffect.do}}
-\end{figure}
-\end{comment}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% APPENDIX B
-
-\newpage
-\section{ Observational analysis}
-\label{appendix_b}
-\vspace{.2in}
-\normalsize
-\linespread{1.25}
-%Really force it to normal size and linespread
-\normalsize
-\linespread{1.25}
-
-The objective of this Appendix is to conduct one test aiming to assess if there is learning in choosing the frequent payment FP) contract.
-In particular if being endogenously induced to have a FP contract causes the client to chose a FP in subsequent pawn.
-The identification strategy is not as strong as in a randomized control trial ---having to rely on an instrumental variable strategy using changes in the supply of the FP contract-- and this is why we chose to locate it in a separate Appendix.
-However we believe we find a strong case for learning causing higher demand for the FP contract.
-
-In what follows we will describe the identifying variation and use the richness of the observational data to control for possible confounds.
-We will use hundreds of branches and hundreds of thousands of pawns covering more than 4 years to estimate (under the identification assumptions) the causal effect of having had a FP on the conditional demand for the FP type of contract.
-
-\vspace{.in}
-
-\subsection{Variation in branches' use of frequent payment contract}
-
-After our experiment ended, Lender $P$ started offering frequent payment contracts along their traditional ones.
-We were not able to get data for the dates of the first expansion, but we have data for the period January 2016 through May 2020.
-During this period some branches where offering the frequent payment contract while others were just starting to do this.
-Some branches also stopped offering the frequent payment contracts.
-Out of all branches only 2\% never offered the FP contract, and the rest offered it for only part of our sample period.
-Our identification strategy will mostly rely on these later group, as we include branch fixed effects in our regressions.
-\\
-
-To show the reader a glimpse of this variation in availability of the contract we randomly selected 20 branches and plotted which months had a frequent payment contract active in their IT system.
-Figure \ref{variation_pf_suc} shows a time plot for each branch, where each observation is a month.
-The Y-axis takes the value of 1 if in that month the FP contract was available in that branch and zero otherwise.
-So it is a ``supply side'' variable.
-
-\vspace{.1in}
-\begin{figure}[H]
-        \caption{Existence of FP per branch}
-    \label{variation_pf_suc}
-    \begin{center}
-        \centering
-        \includegraphics[width=0.80\textwidth]{Figuras/active_pf_suc.pdf}
-    \end{center}
-     \scriptsize This Figure shows the presence of the frequent payment (FP) contract in 20 randomly chosen branches of Lender $P$ for a span of more than 4 years.
-A $y$ value $=1$ means that in that month the FP contract was available in that branch.
-     %\textit{Do file: }  \texttt{active\_pf\_suc.do}
-\end{figure}
-\vspace{.1in}
-
-In conversations with Lender $P$ about this variability they said that it is driven by three things: the expansion of the frequent payment product is done gradually, the IT system of a branch sometimes fails, and they often do experiments themselves turning on and off the existing of the frequent payment contract as this was a relatively new type of contract.\footnote{Unfortunately the had no documentation on how these experiments were implemented.} We did verify that there are no frequent payment contracts when they said it was turned off in their IT system.
-
-\paragraph{Orthogonality of FP supply.} We will use the availability of the FP contract as an instrument for the client choosing a FP contract when she pawns.
-Clearly one cannot choose a FP when it does not exist, so that this instrument allows would-be-FP choosers to obtain a FP contract.
-We verify that indeed it has a statistically powerful first statge.
-One may be concerned that this instrument may not satisfy the exclusion restriction however.
-As we will explain below we will use this instrument in an specification that controls for branch and client fixed effects, taking into advantage that many clients do pawn repeatedly (See Figure \ref{hist_num_pawns} below).
-These control for any characteristic of the client that is fixed across time, and therefore is a strong control for selection of clients across branch or across contracts.
-We also control for calendar of the month fixed effects, thereby absorbing common time trends that affect all clients, like macroeconomic shocks.
-We describe the exact specification below, but for now we want to note that we need only for the exogeneity of the instrument to hold conditional on these extensive set thousands of fixed effects.
-
-    \vspace{.1in}
-\begin{figure}[H]
-        \caption{Number of pawns per client}
-    \label{hist_num_pawns}
-    \begin{center}
-        \centering
-        \includegraphics[width=0.6\textwidth]{Figuras/hist_num_pawns.pdf}
-    \end{center}
-     \scriptsize This figure plots a histogram of the number of pawns per client during our sample period (January 2016 through May 2020).
-A large fraction of clients have more than one pawn, and many have several pawns.
-We use these repeat clients to identify learning below.
-     %\textit{Do file: }  \texttt{hist\_num\_pawns.do}
-\end{figure}
-\vspace{.1in}
-
-Having said this, in Table \ref{instrument_random} we assess to what extent we can predict whether a given branch activates the FP contract in its IT system in a given week or a given month.
-It turns out that we cannot predict in which weeks a given branch uses the FP contract with our observables controlling for branch fixed effects.
-The observables include fraction female clients last week (or last month), the age of these clients, number of pawns last week (or last month), average size of those loans, the percentage of pawns last week (or last month) that were jewelry, the percentage of loan recoveries --the opposite of default-- last week (or last month).
-The same is true if we use one month prior instead of one week.
-The $R^2$ shows that the \textit{additional} variance explained by the covariates beyond branch and calendar week fixed effects is low: going from 0.154 to 0.157 when we add all regressors.
-The $AUC$ and the \textit{Accuracy Rate} give a similar picture, with out-of-sample $AUC$ around 0.72 and Accuracy rates around 66\%.\footnote{\cite{Finanzia} say that for predicting loan default for instance AUC's from 0.80 to 0.95 are common.} \\ %{Appraisers could potentially have an effect on what contract people choose conditional on the contract existing in the system.
-We test for this and find XXX...}
-
-Quantitatively the correlations are small: an increase of 1 years of the mean age of clients is associated with an increase of 0.008 percentage points in introducing FP, an increase in the size of the loan by 1000 pesos increases it by 0.002, an increase of 10 pawns per day increases it by less than 0.0002 percentage points.
-Having 10\% less women as clients in the past increases it by 1 percentage point.
-This result of low correlation between important observable variables and the supply of FP contract in a given branch makes us more comfortable with the assumption that the instrument satisfies the exclusion restriction.
-The presence of the FP contract in a given week in a given branch seems almost random from this perspective.
-
-\begin{table}[H]
-\caption{Predicting the supply of FP contracts within branch across time}
-\label{instrument_random}
-\begin{center}
-\footnotesize{\input{./Tables/instrument_random.tex}}
-\end{center}
- \scriptsize
-This table uses OLS regressions to predict whether branch $j$ in week $t$ had a FP available.
-So the dependent variable is an indicator for this event $\mathbbm{1}(\text{Branch Had FP})_{jt}$, and the explanatory variables are measures of performance of that branch and the characteristics of the clients either the week previous to $t$ or 4 weeks previous to week $t$.
-We allow for two time periods since the branch manager or central offices may take time to react to information.
-Column 1 includes branch and week fixed effects, while Column 2 adds the covariates displayed measured the week previous to $t$.
-Column 3 is analogous to column 2 except that the values of the displayed covariates are averaged across the 4 weeks prior to week $t$.
-The bottom panel shows measures of predictive power like $R^2$, as well as area under the ROC curve ($AUC$), and the Accuracy Rate.
-It also shows F-test of the null hypothesis that the branch (week) fixed effects, or the other regressors have coefficients equal to zero.
-%\textit{Do file: } \texttt{instrument\_random.do, pred\_instrument.do}
-\end{table}
-
-\vspace{.1in}
-
-\subsection{Experiencing FP causes future demand for FP to increase}
-
-This subsection uses the existence of a FP contract in the branch as an instrument for a client \textit{having} a FP contract if she visited that branch that week to pawn.
-Using this instrumental variable strategy we estimate the effect of having had a FP in the previous pawn.
-More concretely, Table \ref{iv_pf} reports results from a two-stage least squares estimate of the effect of having a FP contract on subsequent demand for FP contracts.
-We estimate the following regression:
-
-\begin{equation}
-    \mathbbm{1}(\text{Has FP})_{ijt} = \alpha_i + \gamma_t + \beta \mathbbm{1}(\text{Had FP previously})_{ijt}  + \epsilon_{ijt}
-    \label{eqn:IV}
-\end{equation}
-
-\noindent where $i,j,t$ index client, branch, and week respectively.
-$\mathbbm{1}(\text{Has FP})_{ijt}$ is an indicator for client $i$ pawning in branch $j$ in week $t$ using a FP contract, given that both FP and traditional contracts were available at the branch at the time of pawning, so that there is a choice to be made among these.\footnote{When a FP is not available in branch $j$ in week $t$ the variable takes the value of missing, and is therefore not considered in the regression.
-That is, we only include observations when the client had a choice between FP and traditional contracts.} Moreover we restrict the sample to pawns where the immediate previous pawn is already closed at the moment of opening the new one\footnote{We do this to avoid making the conclusion that clients are re-pawning in order to meet their past debt.}.
-We estimate a regression with calendar week fixed effects (we have 212 weeks) $\gamma_t$, and also include client fixed effect $\alpha_i$.
-The variable of interest is denoted by $\mathbbm{1}(\text{Had FP previously})_{ijt}$, and is an indicator for the client's immediate previous loan\footnote{We consider only the immediate previous loan, following a ``Markov's'' assumption, in which only the present state determines the future.} being FP loan.
-% The controls $X_{ij}$ include how assiduous a client is: the number of times she has pawned in the 12 months previous to $t$, as well as a dummy of having made a pawn a Lender $P$ in the period from $t'$ to $t$:   $\mathbbm{1}(\text{Had any loan previously})_{ij't'}$.
-Note that the only difference between this last control variable and our main explanatory variable is that the former does not specify which type of contract this previous loan had.
-This means that the variation identifying $\beta$ is \textit{which type} of loan the client had conditional on having had one.\\
-
-Having client fixed effects in the regression means that we only use variation across time (across subsequent pawns) to identify the effect of experience, and avoid the selection problems that come from comparing across clients.
-That is, they control for the fact that different types of clients may select different types of contracts.
-Repeat pawning is common and this helps for identification.
-Figure \ref{hist_num_pawns} shows a histogram of the fraction of clients that had $1, 2, 3,\ldots, 60$ pawns in our sample.
-We have more than one hundred thousand clients that got two loans within 3 or less months from each other\footnote{We give a small lower bound to keep the identity of Lender $P$ confidential}, and for 37\% of those clients the immediately sequentially preceding loan was taken when the branch had FP available.\\
-
-However, even with client fixed effects, idiosyncratic unobserved shocks across time may induce spurious correlation between choosing a FP last week and choosing FP today.
-The variable $\mathbbm{1}(\text{Had FP previously})_{ijt}$ is therefore still potentially endogenous.
-To deal with this we instrument $\mathbbm{1}(\text{Had FP previously})_{ijt}$ with the \textit{availability} of the contract in branch $j$  when the client previously went to pawn the immediately prior pawn with respect to $t$, $\mathbbm{1}(\text{FP Avail})_{ijt}$.
-This is basically using a supply shifter to identify demand.
-We showed above that availability of FP contracts has close to a zero correlation to a battery of observables.
-The IV strategy assumes that availability of the FP contract in a given week in a given is uncorrelated with $\epsilon_{ijt}$ --- i.e.
-that after conditioning on thousands of client, branch and week fixed effects and the client having pawned recently, there is no omitted variable driving both: the branch having FP contracts on, and the client subsequent pawn using a FP contract.
-Note that including branch fixed effects means that identification comes from a given branch sometimes having the FP and sometimes not.
-\\
-
-The exclusion restriction for an instrument is untestable, but note that we are comparing clients that go to the same branch, who have the same pawning frequency, but where one of them arrived to the branch to pawn on a week where the FP contract was available and the other arrived on a week where the same branch had no FP contract available.%\footnote{We also tried specifications restricting the sample to 4-12 weeks adjacent to the FP contract becoming available or becoming unavailable in a branch and obtain similar results.
-This strategy is close in spirit to a regression discontinuity or event-study design, comparing clients that go to the same branch with the difference that one went there 2 weeks before the FP contract becoming available.}
-The exclusion restriction could be violated for example if the branch manager makes FP available as a function of clients that will come in that week and therefore reaches a certain type of client that is more likely in-and-of themselves to prefer FP contracts now and in the future.
-We find this unlikely.
-It is hard to predict who will come on a given week and if they are more likely to like the FP contract: Table \ref{instrument_random} strongly suggests that the branch manager is not turning the FP contract on and off as result of which clients are coming to the branch or how the branch is doing.
-Having said this, we acknowledge that the exclusion restriction could be violated even in this very tightly controlled specification.\\
-
-Table \ref{iv_pf} shows the first and the second stage regressions for equation \ref{eqn:IV}.
-All columns have branch, and calendar week fixed effects, and standard errors are clustered by client.
-Columns 1 and 4 show strong first stages (t-stats above 50).
-The availability and unavailability of the FP contract has an incidence on its use.
-Under our identification assumptions, Columns 2-3 (and 5-6) show strong causal effects: having  been induced by the instrument to have a FP contract in the previous loan causes the client to a FP for her subsequent pawn by 50 percentage points (column 2).
-The difference between columns 2 and 3 (and 4-5) is the sub-sample considered: in the first one we only condition the immediate previous pawn to be closed at the time of opening a new one, the second one not only considers previous pawns being closed, but having at least one week closed.
-
-\begin{table}[H]
-\caption{Experience with frequent payment contract raises future demand for it}
-\label{iv_pf}
-\begin{center}
-\footnotesize{\input{./Tables/iv_reg_demand_pf.tex}}
-\end{center}
- \scriptsize
-This table shows resulting estimates of variants of equation  \ref{eqn:IV} above.
-They regress a dummy for the client choosing a frequent payment contract (when both the traditional one and the FP are available) on whether the previous loan was under a FP contract.
-All columns have branch, and calendar month fixed effects, and the standard errors are clustered by client.
-The main regressor of interest is having had a FP loan in the immediate past of $t$ which measures experiencing a FP contract.
-Columns 1 and 4 report the result of first stage where the supply side instrument is an indicator for the branch having had a FP available when the client showed to pawn the previous pawn.
-Column 2 \& 5 presents the two-stage least square estimate.
-Columns 3 \& 6 are analogous, but instead of looking clients whose previous pawn is already closed, it looks at those whose previous pawn has at least one week of being closed.
-We do not report the exact number of observations to keep Lender $P$ identity confidential and instead give a lower bound.
-%\textit{Do file: } \texttt{iv\_reg\_demand\_pf.do}
-\end{table}
-
-% \subsubsection{Experiencing FP causes repeat pawning}
-
-% Using experimental variation the paper find that being forced into a FP contract increases the likelihood of the client coming back and pawning again.
-Here we see if that result generalizes for all branches using the instrumental variable strategy described above, where we use $\mathbbm{1}(\text{Repeated Pawning})_{ijt}$ as a dependent variable instead in equation \ref{eqn:IV}.
-
-% Table {XXX} has the same structure as Table  {XXX} above.
-It finds that the experimental result is qualitatively replicated with this different sample and different identification strategy.
-Having had a previous FP loan induced by its availability is associated with an increase of {XXX} in the probability of pawning again {in the next 3 months}.
-
-% \subsubsection{Pawn recovery and FP contracts}
-
-% Using the individual fixed effects specification, as well as the instrumental variable strategy defined above, Table {XXX} finds that FP are {XX\%} more likely to recover their pawns.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% APPENDIX C
-
-\newpage
-\section{ A simple model}
-\label{appendix_c}
-\vspace{.2in}
-\normalsize
-\linespread{1.25}
-
-We use the model of \cite{John} and refer the reader to that paper for more detail, justification of assumptions and some of the proofs.
-The model has three periods and linear utility.\footnote{This does not map perfectly to our 3 period contract, but it is enough to generate the results we need.
-We also assume that the amount of the loan is used up to pay for the emergency.
-\cite{John_theory} provides a more general treatment.} Period $t=0$ is a planning period where the client is either allocated to the status quo, the Forced Commitment contract, or a choice between the two.
-Period $t=1$ is the saving-for-the-monthly-payment  period, and $t=2$ in the pawn recovery (loan payment) period.
-In period 1 the client receives her income $y_1=1$, or gets zero with probability $\lambda$.
-She can consume ($c_1$) or save ($s_1$) part that income.
-In period 2 the client gets her savings from period 1, and again receives income of either $y_2=1$, or zero with independent probability $\lambda$.
-In this last period, she decides whether to use income and savings for consumption $c_2$ and/or for paying back the loan of size $p \in(1,2)$ to recover the pawned piece valued at $b>p$.
-In this simple set up we model the fee-commitment contract as a contract that imposes a fee of size $F$ if the client fails at $t=1$ to save $s_1=p-1$ pesos, which is what is needed to pay the loan back when there are no shocks.
-In period $t=0$ she evaluates her welfare as $E[c_1+c_2]$, were for simplicity we have set the time discount to one.
-We also assume the interest rate is one.
-We introduce present biased preferences by assuming the following utility function $U_t=c_t+\beta \: \sum_{k=t+1}^{2} E[c_k]$, with $\beta<1$ indicating present bias.
-A naive client perceives she is not so present biased and instead of $\beta$ uses $\hat{\beta} \in (\beta,1]$.
-
-Note that under these assumptions it is efficient at $t=0$ to recover the loan since $b>p$ and since there is no discounting at $t=0$.
-Because $b>1$, paying back the loan requires that there is no negative shock in any period and that $s_1>0$.
-Because $\beta<1$ at $t=1$ the client will not send savings in excess of what is needed to recover the loan: $s_1=p-1$.
-This parsimonious model implies the following results:
-
-\vspace{.2in}
-\noindent \textbf{Result 1: Present biased clients default more.} Under the status-quo contract, absent shock realizations, present biased clients (sophisticated or naive) with $\beta<\beta_{SQ}<1$ will lose their pawn, while clients with no present bias will not.\footnote{$\beta_{SQ}=\frac{p-1}{\lambda(p-1)+(1-\lambda)(b-1)}$.
-See Proposition 1 in \cite{John}.}
-
-\vspace{.1in}
-\noindent \textbf{Result 2: Forcing present-biased clients into the fee-commitment contract reduces default.} Imposing a fee $F>0$ for late payments weakly decreases default (for present biased clients only).
-It strictly decreases default if $F>F_{min}(\beta):=(p-1)-\beta[\lambda(p-1)+(1-\lambda)(b-1)]$.
-The larger the present bias the larger the $F$ required to induce pawn recovery.\footnote{$F_{min}(\beta)$ is derived from the incentive compatibility constraint needed to generate savings at $t=1$ to recover the pawn can be written as $1-(p-1)+\beta[\lambda(p-1)+(1-\lambda)(b-1)] \geq 1-F+\beta(1-\lambda)$.}
-
-\vspace{.1in}
-\noindent \textbf{Result 3: Demand for commitment.} Given $F>0$, (a) Neoclassical clients will never demand commitment.
-(b) Present-biased sophisticated clients will prefer the Forced Commitment contract over the status quo contract $\iff$  $\lambda \: F<(1-\lambda)^2(b-p)$ and $F>F_{min}(\beta)$, that is $\iff$  $\beta \in [\beta_{min},\beta_{SQ}]$.\footnote{$\beta_{SQ}$ was determined in Result 1.
-$\beta_{min}$ is such that $F=F_{min}(\beta_{min})$.} (c) Analogously, naive clients will demand commitment $\iff$ $\hat{\beta} \in [\widehat{\beta_{min}},\beta_{SQ}]$, where $\widehat{\beta_{min}}<\beta_{min}$.
-So strongly naive clients will on the one hand demand more commitment than sophisticated clients since they believe (incorrectly) that a smaller fee will motivate them to pay.
-On the other hand they may demand less commitment since they think they can save and pay on their own.
-Whether they demand more or less than sophisticated clients depends on the empirical distribution of $\beta$ and $\hat{\beta}$.
-
-\vspace{.1in}
-\noindent \textbf{Result 4: Overconfidence.} Only naive clients will be overconfident about the probability of recovery.
-This will be true whether they have the status quo or the Forced Commitment contract.
-Overconfidence is increasing in $\hat{\beta}$.
-
-\vspace{.1in}
-\noindent \textbf{Result 5: Welfare.} (a) Neoclassical consumers' welfare strictly decreases when we force clients into the fee-commitment contract instead of the status quo contract because of the risk of them not being able to pay for the installment, and does not change when we offer a choice between them.
-(b) The welfare of sophisticated present biased consumers weakly increases when we give them choice, and it strictly increases  $\iff$  $\beta \in [\beta_{min},\beta_{SQ}]$, that is when they would choose the fee-commitment contract themselves.
-Forcing them into the fee-commitment contract increases welfare $\iff$  $\beta \in [\beta_{min},\beta_{SQ}]$, otherwise it strictly decreases it.
-So choice is better than forcing for sophisticates.
-(c) Forcing can be welfare improving for the naive.
-Indeed if $\hat{\beta}>\beta_{SQ}>\beta$ then forcing the fee-commitment contract increases welfare, and if $\hat{\beta} \in (\widehat{\beta_{min}},\beta_{min})$ then forcing the status quo contract increases welfare.\footnote{This result is different from that in \cite{John}.
-Her context has individuals choosing the size of the fee.
-In that context naive clients will \textit{always} chose the wrong fee size and default later, therefore choice is always decreasing for the naive.
-In our context $F$ is fixed at 2\% of the balance due, and this implies that choice could be welfare improving for some naifs.} We want to highlight that only under certain parameters will forcing installment payments improve welfare, and that welfare will likely decrease for those with no present bias and the sophisticated present biased consumers.
-
-\vspace{.1in}
-\noindent \textbf{Result 6: Welfare and ex-post observed behavior.} If for a naive client $i$ the Forced Commitment contract causes higher pawn recovery, then we know the fee $F$ made her IC constraint binding, and therefore that $\hat{\beta}_i>\widehat{\beta}_{min}$.
-If in addition if it was the case that $\beta_i<\beta_{SQ}$.
-%\footnote{{Isaac, aqui tengo dos pregutas: (1) si es $\beta$ y no $\hat{\beta}$ verdad?
-(2) Para que una persona naive empenie en el status quo tiene que ser que cree que va a recuperar no?
-Es decir tiene que ser $\hat{\beta}>\beta_{SQ}$ correcto?}}
-then the Forced Commitment contract would have increased welfare for the naive.
-That is, our finding that the Forced Commitment contract increases pawn recovery is a sign of higher welfare (although not a sufficient condition).\footnote{It is not sufficient since ex-ante the commitment $F$ may have been too expensive given the income shocks, i.e.
-if $\lambda \: F>(1-\lambda)^2(b-p)$.}
-
-\end{document}

### 2022-02-11 Tables/Attrition.tex
annualize apr and effects in std deviations

@@
 % Table generated by Excel2LaTeX from sheet 'Attrition'
-\begin{tabular}{lccccccccc}
+\begin{tabular}{lccccccc}
 \toprule
-      & \multicolumn{9}{c}{Attrition Table} \\
+      & \multicolumn{7}{c}{} \\
 \midrule
-      &       &       &       &       & \multicolumn{2}{c}{Fee arms} & \multicolumn{2}{c}{Promise arms} &  \\
+      &       & \multicolumn{3}{c}{Commitment arms} & \multicolumn{3}{c}{Soft arms} \\
 \midrule
 \midrule
-      & \multicolumn{1}{p{4.045em}}{Overall} & \multicolumn{1}{p{3.5em}}{Pre-exp} & \multicolumn{1}{p{3.365em}}{p-value} & \multicolumn{1}{p{3.275em}}{Control} & \multicolumn{1}{p{4.775em}}{Forced-fee} & \multicolumn{1}{p{3em}}{Choice} & \multicolumn{1}{p{3em}}{Forced} & \multicolumn{1}{p{3em}}{Choice } & \multicolumn{1}{p{3.365em}}{p-value} \\
+      & Control & Forced & Choice & p-value & Forced & Choice  & p-value \\
 \midrule
 \midrule
-Number of branch-day pawns & 34    & 36    & 0.71  & 31    & 31    & 37    & 32    & 34    & 0.38 \\
-      & (0.8) & (1.3) &       & (2.2) & (2.3) & (2.6) & (2.4) & (1.7) &  \\
-Survey response rate &       & 0.78  &       & 0.77  & 0.75  & 0.77  & 0.8   & 0.79  & 0.46 \\
-      &       & (0.01) &       & (0.02) & (0.03) & (0.02) & (0.02) & (0.02) &  \\
-\% ended up pawning &       & 0.98  &       & 0.97  & 0.96  & 0.97  & 0.98  & 0.99  & 0.03 \\
-      &       & (0.003) &       & (0.004) & (0.008) & (0.006) & (0.004) & (0.003) &  \\
-Number of branch-days & -     & 180   &       & 84    & 80    & 93    & 68    & 82    &  \\
+Number of branch-day pawns & 31    & 31    & 37    & 0.16  & 32    & 34    & 0.57 \\
+      & (2.2) & (2.3) & (2.6) &       & (2.4) & (1.7) &  \\
+Survey response rate & 0.77  & 0.75  & 0.77  & 0.73  & 0.8   & 0.79  & 0.44 \\
+      & (0.02) & (0.03) & (0.02) &       & (0.02) & (0.02) &  \\
+\% ended up pawning & 0.97  & 0.96  & 0.97  & 0.59  & 0.98  & 0.99  & 0.11 \\
+      & (0.004) & (0.008) & (0.006) &       & (0.004) & (0.003) &  \\
 \midrule
-Obs   & 13534 & 180   &       & 2585  & 2465  & 3406  & 2143  & 2755  &  \\
+Obs   & 2585  & 2465  & 3406  &       & 2143  & 2753  &  \\
 \bottomrule

### 2022-02-11 donde.tex
annualize apr and effects in std deviations

@@
 Ricardo Olivares, Gerardo Melendez, and Alonso de Gortari provided excellent research assistance and Erick Molina helped with formatting.
-Jose Maria Barrero, Andrei Gomberg, Emilio Gutierrez, David Laibson, Aprajit Mahajan, Matt Rabin, Charlie Sprenger, and seminar participants at ITAM provided valuable feedback.}}
+Jose Maria Barrero, Francis DiTraglia, Andrei Gomberg, Emilio Gutierrez, David Laibson, Aprajit Mahajan, Matt Rabin, Charlie Sprenger, and seminar participants at ITAM provided valuable feedback.}}
 \author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira   \thanks{Seira: ITAM, enrique.seira@gmail.com (corresponding author); McIntosh:  University of California San Diego, ctmcintosh@ucsd.edu; Meza: University of California at Berkeley, isaac.meza@berkeley.edu; Sadka: ITAM, jsadka@itam.mx} }
@@
 \noindent \textbf{Treatment Arms.} Randomization was done at the branch-day level.
-Each day we randomly assigned which types of contracts were on offer that day in the branch, and therefore which contract the client signed.
+Each day a computer randomly assigned which types of contracts were on offer that day in the branch, and therefore which contract the client signed.
 We have 5 different experimental arms:
@@
 We anticipated this possibility and trained appraisers to say --that whatever was the contract that day-- it was the only available contract for an undetermined amount of time.
-Because we do not observe refusals directly, we address this issue by examining the number of borrowers per day, and the number of borrowers who were surveyed but then did not pawn.
+Because we do not observe refusals directly, we address this issue by examining the number of borrowers per day.\footnote{Our enumerators informed us that potential clients rarely left the branch without pawning, and that it was even less common that they did so when hearing about monthly installments.
+Lender P also never complained to us that our different treatments were hurting sales.
+The data support this story as well.}
+
+A second form of attrition would be differential refusal to answer the survey questions.
+This is less of a concern, both because the survey was done before treatment status was revealed, and because we still have institutional data for the universe of borrowers.
+Nonetheless, to test the internal validity of any measures in the study that use survey data, we test for differential attrition here as well.
+A third way of examining attrition is to look at the fraction of borrowers who do respond to the survey and then do not end up taking a loan subsequent to completing the survey.
 
@@
 
-Our enumerators informed us that potential clients rarely left the branch without pawning, and that it was even less common that they did so when hearing about monthly installments.
-It turns out that only \hl{XXX\%} of those surveyed ended up not pawning and appearing in the administrative data.
-Lender P also never complained to us that our different treatments were hurting sales.
-The data support this story as well.
-First, we cannot reject that the number of pawns per branch-day is the same across arms (Panel A).
+Table \ref{attrition_table} presents tests for these core forms of attrition.
+Most importantly, the top row shows that there is no difference between the Control and Forced Commitment arms in terms of the number of pawns per day, suggesting that there has been no differential refusal when borrowers were defaulted into the Commitment contract.
+The Choice arm appears to have a somewhat larger number of borrowers than the Control arm, but given that there is no reason to think that we would have seen differential uptake for this arm (where the status quo contract is freely available) we view this as a chance occurrence.
+The survey response rate is broadly similar across arms (about 77 percent) as is the fraction of those surveyed who then go on to take a loan (97 percent).
+
+%First, we cannot reject that the number of pawns per branch-day is the same across arms (Panel A).
 Panel C shows that about 98\% of people who answered our baseline survey also pawned, and that this ratio is balanced across arms.
 Second, not only are the number and shares of pawns the same across arms, but also the characteristics of clients and their pawned pieces are statistically the same across arms.
-Panel A of Table \ref{SS} tests this with administrative data, while Panel B tests it using baseline survey data for those that pawned, and Panel C does it without conditioning on pawning.
-%The difference is that Panel B compares people that pawned, while {Panel C uses clients that did not pawn.}
-Third, the characteristics of those who pawned before our experiment began are statistically the same as those during the experiment, as documented in the first and second column of Panel C.
+Panel A of Table \ref{SS} tests this with administrative data, while
 
@@
 
-A second form of attrition would be differential refusal to answer the survey questions.
-This is less of a concern, both because the survey was done before treatment status was revealed, and because we still have institutional data for the universe of borrowers.
-Nonetheless, to test the internal validity of any measures in the study that use survey data, we test for differential attrition here as well.
-
 All the pieces of evidence indicate that there was no selection across arms and that experimental comparisons are internally valid.
-
-\textcolor{red}{Need to build Attrition Table}
 
@@
 Table \ref{SS} presents summary statistics for the sample of actual borrowers across arms, and illustrates that randomization worked to achieve balance across clients in the different experimental arms.
-Panel A describes variables from the administrative data.
+
+Panel A uses administrative data for the universe of borrowers in each arm, and shows that loan balances and the days on the week on which individuals pawned are comparable across arms.
 The average loan size is \$2197 MXN (\$105 USD).
+
+Panel B of Table \ref{SS} reports summary statistics across arms from our survey data.
+73\% of clients are women, with an average age of 43 years; 66\% of them have completed high school or more, and 90\% have pawned before, so that our sample has mostly experienced borrowers.
+Finally the subjective probability of recovery is close to 93\% on average, which makes a stark contrast to the actual rate of recovery (42\%).
+In other words, borrowers are highly overconfident on average.
+The average subjective value they report for the pieces is 3069 MXN, much larger than the average appraised gold value of 2197 MXN.
+While this could arise either from overconfidence in valuation or from undervaluation by the lender, in any case it is \textit{prima facie} evidence that loss of the pawn should be undesirable relative to the quantity of liquidity leveraged by the asset.
+
+Panel C repeats the exercise in Panel B, but now only for those borrowers answered the survey and then went on to take a loan.
+Since we have aready shown that the attrition rate of borrowers after completing the survey was very low (3\% on average) it is unsurprising that these two panels are similar.
+Overall, we find both the loan attributes and the survey attributes of borrowers to be similar across arms.
+The experiment appears to have been successful in generating a balanced sample for analysis.
+
+%Panel A describes variables from the administrative data.
 The average number of pawns per day per branch is 34.
@@
 Even those that recover their pawn tend to pay it back at the last moment, with only 40\% paying before the 90th day.
-
-Panel B reports stats from our survey data.
-73\% of clients are women, with an average age of 43 years; 66\% of them have completed high school or more, and 90\% have pawned before, so that our sample has mostly experienced borrowers.
-Finally the subjective probability of recovery is close to 93\% on average, which contrasts with the 51 points lower actual recovery.
-Borrowers seem to be highly overconfident on average.
-The average subjective value they report for the pieces is 3069 MXN, much larger than the average appraised gold value of 2197 MXN.
-%This makes it inefficient for them to lose it.
-
-\textcolor{red}{Imbalance in survey data needs to be addressed?}
 
@@
 We now present the core experimental results, illustrating how the Commitment Choice and Forced Commitment arms differ from the control.
+This comparison is particularly illuminating on the role of self-selection in Commitment, because if this self-selection mechanism works perfectly (as it would in a Roy model with all hyperbolics sophisticated) then the Forced and Choice arms will have an identical effect.
+Deviations between the impacts of these two arms therefore are implicitly a test of the optimatlity of the choices made in the choice arm.
 
@@
 Nor does it lead to higher pawn recovery.
-The hollow circles in Figure \ref{fc_pro4}(a) show zero average effects for the different definitions of financial cost analogous to the ones described above.
-Figure \ref{fc_pro4}(b) shows further that the null effect happens for the 15$^{th}$, 25$^{th}$, 50$^{th}$ 75$^{th}$, and 85$^{th}$ percentiles.\footnote{The few clients that chose the Commitment contract (the solid black squares) do enjoy cost savings of 1005 MXN, which compares favorably to the 304 MXN in the Forced arm (as a fraction of the loan the numbers are 41.5\% and 12.5\%), but this combines the selection and treatment effects.} %Figure \ref{heterogeneous_te_4} plots the distribution of treatment effects and finds that the distribution offering choice actually \textit{increased} financial cost and default for about half of clients compared to being assigned the status-quo contract.
-Those tended to be the less economically vulnerable and more educated, {women}, and those whose family typically asks them for money.
-Figure \ref{fc_pro4}(c) finds null effects for pawn recovery. Consistent with these findings, Figure \ref{reincidence} finds no effect on repeat purchases for the Commitment Choice group.
+Figure \ref{main_te} gives the standardized effect sizes (in standard deviations) of the two main study arms for three outcomes:  default, the financial cost of the loan, and the effective interest rate paid to acquire the borrowed capital.
+Very clearly, the Forced arm is significant for all three outcomes, with very substantial treatment effects in magnitudes for default and APR, and the commitment arm is never significant.
+
+\textcolor{red}{Include here table that has regressions from Eq. 1 underlying the figure above.}
 
 \vspace{.2in}
-\noindent \textbf{Financial Cost.} Figure \ref{fc_pro2}(a) reports $\beta$ coefficients and their 95\% confidence interval from estimating equation (\ref{basic_reg}) using different definitions of financial cost.
+\noindent \textbf{Detailed analysis of financial cost.} Figure \ref{fc_pro4} digs in more detail into the sources of variation underlying the main effects in Figure \ref{main_te}.
+$\beta$ coefficients and their 95\% confidence interval from estimating equation (\ref{basic_reg}) using different definitions of financial cost.
 The leftmost coefficient corresponds to plugging into the formula of section \ref{FC_def} the appraised gold value of the pawned piece.
@@
 We conclude that penalizing borrowers for delinquency in a contract which has already has large penalties from default (losing the collateral in a highly collateralized loan) actually helps borrowers.
+
+\textcolor{red}{Beginning of discussion on Quantile Effects:.}
+The hollow circles in Figure \ref{fc_pro4}(a) show zero average effects for the different definitions of financial cost analogous to the ones described above.
+Figure \ref{fc_pro4}(b) shows further that the null effect happens for the 15$^{th}$, 25$^{th}$, 50$^{th}$ 75$^{th}$, and 85$^{th}$ percentiles.\footnote{The few clients that chose the Commitment contract (the solid black squares) do enjoy cost savings of 1005 MXN, which compares favorably to the 304 MXN in the Forced arm (as a fraction of the loan the numbers are 41.5\% and 12.5\%), but this combines the selection and treatment effects.} %Figure \ref{heterogeneous_te_4} plots the distribution of treatment effects and finds that the distribution offering choice actually \textit{increased} financial cost and default for about half of clients compared to being assigned the status-quo contract.
+Those tended to be the less economically vulnerable and more educated, {women}, and those whose family typically asks them for money.
+Figure \ref{fc_pro4}(c) finds null effects for pawn recovery. Consistent with these findings, Figure \ref{reincidence} finds no effect on repeat purchases for the Commitment Choice group.
 
@@
 Here we do the reverse.
-First, we estimate a flexible model of take-up of the fee commitment contract \textit{in the choice arm} using \textcolor{red}{gradient boosting classification}\footnote{\textcolor{red}{Results are robust to other classification methods like Random Forest, SVM, etc.}} and obtain for a client with characteristics $x_i$ a \textcolor{red}{calibrated} probability $P(x_i)$ of choosing the Forced Commitment contract.
+First, we estimate a flexible model of take-up of the commitment-fee contract \textit{in the choice arm} using \textcolor{red}{gradient boosting classification}\footnote{\textcolor{red}{Results are robust to other classification methods like Random Forest, SVM, etc.}} and obtain for a client with characteristics $x_i$ a \textcolor{red}{calibrated} probability $P(x_i)$ of choosing the Forced Commitment contract.
 We then use this model to predict the counterfactual probability of a client with characteristics $x_j$ choosing the fee-commitment contract \textit{in the no choice-arms} if she would have been given the choice, what we call $\widehat{P(x_j)}$.\footnote{Our \textcolor{red}{gradient boosting} take-up model has a good out-of-sample fit with an out-of-sample AUC of \colorbox{yellow}{0.85}.
@@
 
-Let $Z_i$ be the observed, randomly assigned experimental allocation, where $Z_i=0$ denotes the control arm, $Z_i=1$ denotes the forced-fee arm, and $Z_i=2$ is the choice arm.
+Let $Z_i$ be the observed, randomly assigned experimental allocation, where $Z_i=0$ denotes the control arm, $Z_i=1$ denotes the Commitment-fee arm, and $Z_i=2$ is the choice arm.
 Let $T_i$ be the unobserved choice type.
@@
 
+\begin{table}[H]
+\caption{Determinants of Choice}
+\label{det_choose}
+\begin{center}
+\scriptsize{\input{./Tables/determinants_choose.tex}}
+\end{center}
+ \scriptsize
+
+%\textit{Do file: } \texttt{determinants\_choose.do}
+\end{table}
+
+\scriptsize {
+\noindent 
+}
+
 \vspace{.3in}
@@
 \begin{figure}[H]
+     \caption{Several definitions of FC}
+    \label{robustness_fc}
+    \begin{center}
+    \begin{subfigure}{0.75\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/fc_robustness.pdf}
+    \end{subfigure}
+    \end{center}
+    \scriptsize
+    This figure shows treatment effects using several measures of cost.
+The first definition is our main definition of cost, which uses the appraised value of the pawn.
+The second definition uses the subjective (self-reported) value for the pawn.
+The third and fourth definition adds the travel cost for the treatment arms.
+We also compute APR versions of the above measures.
+    Finally, `APR - interests' is a version of the APR that doesn't include the interest that is mechanically saved by paying early since this is the piece of the commitment-fee contract that has a foregone liquidity cost for the borrower.
+The treatment effects are indicated in standard deviations, together with 95\% confidence intervals.
+\end{figure}
+
+\begin{figure}[H]
+    \caption{Detailed comparison of Forced and Choice Commitment arms}
+    \label{fc_pro4}
+    \begin{center}
+    \begin{subfigure}{0.45\textwidth}
+        \caption{Financial cost}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/fc_te_pro_4.pdf}
+    \end{subfigure}
+        \begin{subfigure}{0.45\textwidth}
+        \caption{Financial Cost (quantile reg)}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/fc_quantile_pro_4.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.5\textwidth}
+
+        \bigskip
+        \bigskip
+
+        \caption{Lost Pawn}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/def_te_pro_4.pdf}
+    \end{subfigure}
+    \end{center}
+        \scriptsize
+        This figure is analogous to Figure \ref{fc_pro2}.
+It measures the effect of being given \textit{choice} between the frequent payment commitment contract with fees and the status-quo contract, versus being \textit{``forced''} into the status-quo contract (control).
+Again it focuses our two main outcomes: financial cost and an indicator for losing the pawn.
+Circles present the treatment effects.
+The figures also presents differences in these two outcomes for those who chose the frequent payment commitment contract versus the whole control group (squares-NSQ), and also for those who chose the status quo contract versus the whole control group (triangles-SQ).
+Note that these two comparisons are not pure causal effects since people who chose the frequent payment commitment contract are different from those that do not.
+That is: the squares and triangles combine selection and treatment effects.
+Finally, for comparison purposes, the blue diamond displays the effects of forcing them into the frequent payment commitment contract and are just transcribed from Figure \ref{fc_pro2} above.
+      %\textit{Do file: }  \texttt{fc\_te\_choice\_dec.do, def\_te\_choice\_dec.do, fc\_quantilereg\_choice\_dec.do}
+\end{figure}
+
+\begin{figure}[H]
+    \caption{The effect of promises}
+    \label{fc_pro5}
+    \begin{center}
+
+        \begin{subfigure}{0.45\textwidth}
+        \caption{Financial cost -- Choice}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/fc_te_pro_5.pdf}
+    \end{subfigure}
+        %\begin{subfigure}{0.45\textwidth}
+        %\caption{Quantile regression}
+        %\centering
+        %\includegraphics[width=\textwidth]{Figuras/fc_quantile_pro_5.pdf}
+    %\end{subfigure}
+    \begin{subfigure}{0.45\textwidth}
+        \caption{Losing Pawn -- Choice}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/def_te_pro_5.pdf}
+    \end{subfigure}
+
+    \bigskip
+    \bigskip
+
+        \begin{subfigure}{0.45\textwidth}
+        \caption{Financial cost -- Promise-forcing}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/fc_te_pro_3.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.45\textwidth}
+        \caption{Losing Pawn -- Promise-forcing}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/def_te_pro_3.pdf}
+    \end{subfigure}
+
+    \end{center}
+    \scriptsize
+    Panels (a) and (b) in this figure show the estimated treatment effects of ``forcing'' the frequent payment commitment contract using promises, compared to the status-quo (control) for financial cost (Panel a), and for an indicator of losing the pawn (Panel b).
+Panels (c) and (d) are analogous but focus on the effect of giving choice between frequent payment commitment contract using promises and the status quo contract.
+In Panel (a) each dot represents the estimated treatment effect for a different definition of financing cost, or for a different sub-population, and its 95\% confidence interval.
+From left to right, the first effect corresponds to using the gold value of the pawned piece in the definition of financial cost and discounting the payments to present value using a 7\% monthly rate; the second uses the subjective value of the pawn; the third is analogous to the second but adds transaction cost (transport+1 day's wage) per visit; and the fourth conditions on the population that paid any positive amount towards recovery of their pawn.
+Panel (b) plots the effect of not recovering the pawn: the leftmost coefficients compares all those assigned to the promise-forcing arm vs all those in the status quo contract, where the dependent variable=1 if the client has not recovered the pawn 230 days after pawning.
+The next coefficient defines the dependent variable=1 if the client has not recovered the pawn 120 days after pawning.
+The third coefficient conditions on paying a positive amount, and the fourth conditions on paying at least 30\% of the loan.
+Panels (b) and (c) measure the effect of being given \textit{choice} between the frequent payment commitment contract with promise and the status-quo contract, versus being \textit{``forced''} into the status-quo contract (control).
+Again it focuses our two main outcomes: financial cost and an indicator for losing the pawn.
+Circles present the treatment effects.
+The figures also presents differences in these two outcomes for those who chose the frequent payment commitment contract versus the whole control group (squares-NSQ), and also for those who chose the status quo contract versus the whole control group (triangles-SQ).
+That is: the squares and triangles combine selection and treatment effects.
+      %\footnotesize{ } \textit{Do file: }  \texttt{fc\_te\_choice\_dec.do, def\_te\_choice\_dec.do, fc\_te.do, def\_te.do }
+\end{figure}
+
+\begin{figure}[H]
      \caption{Quantile regressions}
@@
          \scriptsize
-     This figure plots the effects on different quantiles (15th, 25th, 50th, 75th, 85th percentile) of the distribution of financial cost, and APR, for the Forced-fee and Choice arms.
+     This figure plots the effects on different quantiles (15th, 25th, 50th, 75th, 85th percentile) of the distribution of financial cost, and APR, for the Commitment-fee and Commitment-choice arms.
       %\footnotesize{ } \textit{Do file: }  \texttt{main\_qreg.do}
@@
       %\footnotesize{ \textit{Do file: }  \texttt{re\_te.do}
-\end{figure}
-
-\begin{figure}[H]
-    \caption{The effect of choice between fee-commitment and status quo}
-    \label{fc_pro4}
-    \begin{center}
-    \begin{subfigure}{0.45\textwidth}
-        \caption{Financial cost}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/fc_te_pro_4.pdf}
-    \end{subfigure}
-        \begin{subfigure}{0.45\textwidth}
-        \caption{Financial Cost (quantile reg)}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/fc_quantile_pro_4.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.5\textwidth}
-
-        \bigskip
-        \bigskip
-
-        \caption{Lost Pawn}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/def_te_pro_4.pdf}
-    \end{subfigure}
-    \end{center}
-        \scriptsize
-        This figure is analogous to Figure \ref{fc_pro2}.
-It measures the effect of being given \textit{choice} between the frequent payment commitment contract with fees and the status-quo contract, versus being \textit{``forced''} into the status-quo contract (control).
-Again it focuses our two main outcomes: financial cost and an indicator for losing the pawn.
-Circles present the treatment effects.
-The figures also presents differences in these two outcomes for those who chose the frequent payment commitment contract versus the whole control group (squares-NSQ), and also for those who chose the status quo contract versus the whole control group (triangles-SQ).
-Note that these two comparisons are not pure causal effects since people who chose the frequent payment commitment contract are different from those that do not.
-That is: the squares and triangles combine selection and treatment effects.
-Finally, for comparison purposes, the blue diamond displays the effects of forcing them into the frequent payment commitment contract and are just transcribed from Figure \ref{fc_pro2} above.
-      %\textit{Do file: }  \texttt{fc\_te\_choice\_dec.do, def\_te\_choice\_dec.do, fc\_quantilereg\_choice\_dec.do}
 \end{figure}
@@
 To do this we proceed in two steps.
-First we estimate a flexible model of take-up of the fee commitment contract \textit{in the choice arm} using gradient boosting classification, and from this model obtain a probability $P(x_i)$ of choosing the Forced Commitment contract for a client with characteristics $x_i$.
+First we estimate a flexible model of take-up of the commitment-fee contract \textit{in the choice arm} using gradient boosting classification, and from this model obtain a probability $P(x_i)$ of choosing the Forced Commitment contract for a client with characteristics $x_i$.
 We extrapolate this model to clients in the Forced Commitment arm to estimate what would they have chosen if we had given them choice.
@@
           %\footnotesize{ \textit{Do file: }  \texttt{benefit\_choice.do}}
-\end{figure}
-
-\begin{figure}[H]
-    \caption{The effect of promises}
-    \label{fc_pro5}
-    \begin{center}
-
-        \begin{subfigure}{0.45\textwidth}
-        \caption{Financial cost -- Choice}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/fc_te_pro_5.pdf}
-    \end{subfigure}
-        %\begin{subfigure}{0.45\textwidth}
-        %\caption{Quantile regression}
-        %\centering
-        %\includegraphics[width=\textwidth]{Figuras/fc_quantile_pro_5.pdf}
-    %\end{subfigure}
-    \begin{subfigure}{0.45\textwidth}
-        \caption{Losing Pawn -- Choice}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/def_te_pro_5.pdf}
-    \end{subfigure}
-
-    \bigskip
-    \bigskip
-
-        \begin{subfigure}{0.45\textwidth}
-        \caption{Financial cost -- Promise-forcing}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/fc_te_pro_3.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.45\textwidth}
-        \caption{Losing Pawn -- Promise-forcing}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/def_te_pro_3.pdf}
-    \end{subfigure}
-
-    \end{center}
-    \scriptsize
-    Panels (a) and (b) in this figure show the estimated treatment effects of ``forcing'' the frequent payment commitment contract using promises, compared to the status-quo (control) for financial cost (Panel a), and for an indicator of losing the pawn (Panel b).
-Panels (c) and (d) are analogous but focus on the effect of giving choice between frequent payment commitment contract using promises and the status quo contract.
-In Panel (a) each dot represents the estimated treatment effect for a different definition of financing cost, or for a different sub-population, and its 95\% confidence interval.
-From left to right, the first effect corresponds to using the gold value of the pawned piece in the definition of financial cost and discounting the payments to present value using a 7\% monthly rate; the second uses the subjective value of the pawn; the third is analogous to the second but adds transaction cost (transport+1 day's wage) per visit; and the fourth conditions on the population that paid any positive amount towards recovery of their pawn.
-Panel (b) plots the effect of not recovering the pawn: the leftmost coefficients compares all those assigned to the promise-forcing arm vs all those in the status quo contract, where the dependent variable=1 if the client has not recovered the pawn 230 days after pawning.
-The next coefficient defines the dependent variable=1 if the client has not recovered the pawn 120 days after pawning.
-The third coefficient conditions on paying a positive amount, and the fourth conditions on paying at least 30\% of the loan.
-Panels (b) and (c) measure the effect of being given \textit{choice} between the frequent payment commitment contract with promise and the status-quo contract, versus being \textit{``forced''} into the status-quo contract (control).
-Again it focuses our two main outcomes: financial cost and an indicator for losing the pawn.
-Circles present the treatment effects.
-The figures also presents differences in these two outcomes for those who chose the frequent payment commitment contract versus the whole control group (squares-NSQ), and also for those who chose the status quo contract versus the whole control group (triangles-SQ).
-That is: the squares and triangles combine selection and treatment effects.
-      %\footnotesize{ } \textit{Do file: }  \texttt{fc\_te\_choice\_dec.do, def\_te\_choice\_dec.do, fc\_te.do, def\_te.do }
 \end{figure}
@@
 
+\newpage
+
+\input{OA.tex}
+
 \end{document}
-
-\newpage

### 2022-02-14 donde.tex
annualize apr & FC robustness

@@
 Let $P^c$, $P^f$, and $P^i$ the payments to principal, fees, and interest respectively.
-We define financial cost as the discounted sum of payments toward the loan, plus the discounted payment of fees, plus payments to interest, plus the appraised value of the pawn, and subtract the appraised value of the pawn when it is recovered:
+We define financial cost as the sum of payments toward the loan, plus the payment of fees, plus payments to interest, plus the appraised value of the pawn when the borrower falls into default:
 \begin{align*}
-    Financial \; Cost_i =& \underbrace{\sum_t P^c_{it}}_{\text{Discounted payments to capital}} + \underbrace{\sum_t P^f_{it}}_{\text{Payed fees}}  +\underbrace{\sum_t P^i_{it}}_{\text{Payed interests}} \\
-    &\quad\qquad + \underbrace{Pawn \: Value_i - \text{I}(Recovered \: Pawn_i) \times Pawn \: Value_i}_{\text{Cost of losing pawn}}
+    Financial \; Cost_i =& \underbrace{\sum_t P^c_{it}}_{\text{Payments to capital}} + \underbrace{\sum_t P^f_{it}}_{\text{Payments of fees}}  +\underbrace{\sum_t P^i_{it}}_{\text{Payments to interests}} \\
+    &\quad\qquad + \underbrace{\mathds{1}(Default_i) \times Pawn \: Value_i}_{\text{Cost of losing pawn}}
 \end{align*}
 
-\noindent $t$ indexes days, $T$ is the day when the pawn is recovered, I($\cdot$) an indicator function for recovering the pawn, $r$ is a daily interest rate equivalent to a 7\% monthly interest rate.\footnote{We experimented with different interest rates with similar results.
-See section \ref{neoclasical}.
-We also report results using the subjective value of the pawn reported by the borrower in the survey again with similar results.
-This cost is calculated for a time period of 230 days after loan origination.}
-
-%Since the main treatment involves making clients come to the branch to pay each month, the transaction costs of coming to the branch are important.
-The average time they take to come to the branch is 22 minutes, and the amount of money they spend in transport to do that is 11 MXN (\$0.60 USD).
+\noindent $t$ indexes days, and $\mathds{1}(Default_i)$ is an indicator function for defaulting\footnote{This cost is calculated for a time period of 230 days after loan origination.}.
+We also report results using the subjective value of the pawn reported by the borrower in place of the appraised value, and a measure of financial cost that adds the travel expense, since the main treatment involves making clients come to the branch to pay each month.
+
+As a second measure of cost we use the Annual Percentage Rate (APR) of the previous Financial Cost.
+In particular, the APR is defined to be the rate that solves the following amortization equation for a 3 period monthly payment:
+
+\begin{align*}
+    \frac{Financial\;Cost_i}{3} =& Appraised\; Value_i \times \frac{\frac{APR}{100(12)}\left(1+\frac{APR}{100(12)}\right)^3}{\left(1+\frac{APR}{100(12)}\right)^3-1}     
+\end{align*}
 
@@
 Figure \ref{fc_pro_2_115} reports results using only the first 115 days.
-Figure \ref{fc_hist}(a) plots a histogram of this financial cost in pesos for loans where the pawn was either recovered or lost.
-Of those who renew, 83\% lose the pawn.
+Figure \ref{fc_hist}(a) plots a histogram of this financial cost in pesos for loans where the pawn was either recovered or lost, while panel (b) shows the APR.
+It shows that most of the cost comes from clients that do not recover their pawn.
+%Of those who renew, 83\% lose the pawn.
 Figure \ref{fc_hist}(a) suggest that financial cost is significant, even for those that do recover their pawn.
@@
 %{The difference between panel (a) and (b) arises since clients who lose their pawn tend to be those that pledge cheaper pieces.}
-We calculate an APR of 218\% on average for the control group.%\footnote{The Annual Percentage Rate (for pawn $j$) is calculated as the internal rate of return $i$ such that $\sum_t \frac{P_{jt}}{(1+i)^t} + \frac{\text{I}(Default \: Pawn_j) \times Pawn \: Value_j}{(1+i)^T} - Pawn \: Value_j = 0$, where $T$ is the date the pawn was lost, and $P_{jt} =P_{jt}^c+P_{jt}^f+P_{jt}^i $ is the sum of all payments.}
+
+%We calculate an APR of 218\% on average for the control group.%\footnote{The Annual Percentage Rate (for pawn $j$) is calculated as the internal rate of return $i$ such that $\sum_t \frac{P_{jt}}{(1+i)^t} + \frac{\text{I}(Default \: Pawn_j) \times Pawn \: Value_j}{(1+i)^T} - Pawn \: Value_j = 0$, where $T$ is the date the pawn was lost, and $P_{jt} =P_{jt}^c+P_{jt}^f+P_{jt}^i $ is the sum of all payments.}
 
@@
 
-\subsection{The Choice of Commitment}
-\label{choice_commitment}
+*\subsection{The Choice of Commitment}
+*\label{choice_commitment}
 
@@
 %\noindent \textbf{Low demand for commitment:} 
-A starting point in the analysis of commitment in pawn lending contracts is to look at the demand that manifested itself in the Commitment Choice arm.
+We begin our empirical analysis with a comparison of the Forced Commitment and Commitment Choice arms to the control.  Before presenting experimental ITT results,
 
@@
 Defenders of choice make another subtler point: that even if take up of the commitment-fee contract is low, the sole fact of \textit{having} choice could potentially change behavior or welfare (\cite{Dalboetal:2010}, \cite{Sjostrometal:2018}, \cite{Tlaxcala}).
-
-\textcolor{red}{If we are to lead with this section we need a simple 'determinants' table that looks at who chooses commitment, this section to discuss results.}
 
@@
 \begin{figure}[H]
-     \caption{Several definitions of FC}
+     \caption{Several definitions of cost}
     \label{robustness_fc}
@@
 We also compute APR versions of the above measures.
-    Finally, `APR - interests' is a version of the APR that doesn't include the interest that is mechanically saved by paying early since this is the piece of the commitment-fee contract that has a foregone liquidity cost for the borrower.
+    Finally, `APR - interests' is a version of the APR that doesn't include the interest that is mechanically saved by paying early since this is the piece of the Forced-commitment contract that has a foregone liquidity cost for the borrower.
 The treatment effects are indicated in standard deviations, together with 95\% confidence intervals.
@@
          \scriptsize
-     This figure plots the effects on different quantiles (15th, 25th, 50th, 75th, 85th percentile) of the distribution of financial cost, and APR, for the Commitment-fee and Commitment-choice arms.
+     This figure plots the effects on different quantiles (15th, 25th, 50th, 75th, 85th percentile) of the distribution of financial cost, and APR, for the Forced-commitment and Choice-commitment arms.
       %\footnotesize{ } \textit{Do file: }  \texttt{main\_qreg.do}

### 2022-02-15 OA.tex
update tex file
annualize apr and effects in std deviations
description of experiment figs

@@
- \documentclass[oneside,11pt]{article}
-
-\input{preamble.tex}
-%%% HELPER CODE FOR DEALING WITH EXTERNAL REFERENCES
-\usepackage{xr}
-\makeatletter
-\newcommand*{\addFileDependency}[1]{
-  \typeout{(#1)}
-  \@addtofilelist{#1}
-  \IfFileExists{#1}{}{\typeout{No file #1.}}
-}
-\makeatother
-
-\newcommand*{\myexternaldocument}[1]{
-    \externaldocument{#1}
-    \addFileDependency{#1.tex}
-    \addFileDependency{#1.aux}
-}
-
-%\myexternaldocument{OA}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% DOCUMENT
-\begin{document}
+%  \documentclass[oneside,11pt]{article}
+
+% \input{preamble.tex}
+% %%% HELPER CODE FOR DEALING WITH EXTERNAL REFERENCES
+% \usepackage{xr}
+% \makeatletter
+% \newcommand*{\addFileDependency}[1]{
+%   \typeout{(#1)}
+%   \@addtofilelist{#1}
+%   \IfFileExists{#1}{}{\typeout{No file #1.}}
+% }
+% \makeatother
+
+% \newcommand*{\myexternaldocument}[1]{
+%     \externaldocument{#1}
+%     \addFileDependency{#1.tex}
+%     \addFileDependency{#1.aux}
+% }
+
+% %\myexternaldocument{OA}
+
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% DOCUMENT
+% \begin{document}
 
@@
 
+\begin{table}[H]
+\caption{Number of pawns balance before and after the experiment}
+\label{num_pawns_bal}
+\begin{center}
+\scriptsize{\input{./Tables/num_pawns_bal.tex}}
+\end{center}
+ \scriptsize 
+%\textit{Do file: } \texttt{num\_pawns\_bal.do}
+\end{table}
+
 \subsection{Some materials}
@@
 \vspace{.1in}
-\begin{figure}[H]
-     \caption{Contract Terms Summary, and Promise Slip}
-    \label{PaperSlip}
-    \begin{center}
-    \begin{subfigure}{0.65\textwidth}
-    \caption{Receipt for client}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/TicketLenderP.png}
-    \end{subfigure}
-
-    \vspace{3ex}
-    \begin{subfigure}{0.65\textwidth}
-    \caption{Personal promise signed by client}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/Personal Promise2.png}
-    \end{subfigure}
-    \end{center}
-    \scriptsize
-        The top of this figure is a sample receipt that was given to clients that got assigned to the fee-forcing contract (the font and format were changed to protect Lender's P identity).
-We want to highlight the salience of some items.
-First the title clearly indicated which contract the client has (arrow 1).
-Second, in the case of the fee contract it clearly indicates that there is a fee for paying late equivalent to 4\% of the value of the monthly payment (arrow 2).
-Third, there is a calendar for payments clearly specifying the dates and amounts to pay each month.
-The bottom panel of the figure shows a ``promise slip'', the paper that those who were assigned (or chose) to the monthly payment with promise had to sign to make the promise salient.
-It emphasizes that the client is giving his word, and that the promise is not a legal document.
-\end{figure}
 
@@
 \end{figure}
-
-\newpage
-\subsection{Main treatment effects: Additional material}
-
-\vspace{.2in}
 
@@
 
-\end{document}
+% \end{document}

### 2022-02-15 Tables/Attrition.tex
description of experiment figs

@@
 % Table generated by Excel2LaTeX from sheet 'Attrition'
-\begin{tabular}{lccccccc}
+\begin{tabular}{lcccccccc}
 \toprule
-      & \multicolumn{7}{c}{} \\
-\midrule
-      &       & \multicolumn{3}{c}{Commitment arms} & \multicolumn{3}{c}{Soft arms} \\
+      &       & \multicolumn{3}{c}{Commitment arms} &       & \multicolumn{3}{c}{Soft arms} \\
+\cmidrule{3-5}\cmidrule{7-9}      & Control & Forced & Choice & p-value &       & Forced & Choice  & p-value \\
 \midrule
 \midrule
-      & Control & Forced & Choice & p-value & Forced & Choice  & p-value \\
+Number of branch-day pawns & 31    & 31    & 37    & 0.16  &       & 32    & 34    & 0.57 \\
+      & (2.2) & (2.3) & (2.6) &       &       & (2.4) & (1.7) &  \\
+Survey response rate & 0.77  & 0.75  & 0.77  & 0.73  &       & 0.8   & 0.79  & 0.44 \\
+      & (0.02) & (0.03) & (0.02) &       &       & (0.02) & (0.02) &  \\
+\% ended up pawning & 0.97  & 0.96  & 0.97  & 0.59  &       & 0.98  & 0.99  & 0.11 \\
+      & (0.004) & (0.008) & (0.006) &       &       & (0.004) & (0.003) &  \\
 \midrule
-\midrule
-Number of branch-day pawns & 31    & 31    & 37    & 0.16  & 32    & 34    & 0.57 \\
-      & (2.2) & (2.3) & (2.6) &       & (2.4) & (1.7) &  \\
-Survey response rate & 0.77  & 0.75  & 0.77  & 0.73  & 0.8   & 0.79  & 0.44 \\
-      & (0.02) & (0.03) & (0.02) &       & (0.02) & (0.02) &  \\
-\% ended up pawning & 0.97  & 0.96  & 0.97  & 0.59  & 0.98  & 0.99  & 0.11 \\
-      & (0.004) & (0.008) & (0.006) &       & (0.004) & (0.003) &  \\
-\midrule
-Obs   & 2585  & 2465  & 3406  &       & 2143  & 2753  &  \\
+Obs   & 2585  & 2465  & 3406  &       &       & 2143  & 2753  &  \\
 \bottomrule

### 2022-02-15 donde.tex
description of experiment figs

@@
 
-*\subsection{The Choice of Commitment}
-*\label{choice_commitment}
+\subsection{Forced versus Chosen Commitment} \label{forced_vs_choice}
+
+%\subsection{The Choice of Commitment}
+%\label{choice_commitment}
 
@@
 %\noindent \textbf{Low demand for commitment:} 
-We begin our empirical analysis with a comparison of the Forced Commitment and Commitment Choice arms to the control.  Before presenting experimental ITT results,
-
+We begin our empirical analysis with a comparison of the Forced Commitment and Commitment Choice arms to the control.
+In the Forced arm, all individuals received the Commitment product.
+In the Choice arm, 11\% of individuals offered the product selected it.
 When preferences or income streams are heterogeneous, and consumers are neoclassical, giving choice among contracts is often a welfare increasing strategy.
@@
 This holds also in most simple models of present bias preferences if consumers are sophisticated about their present bias.
-%Actually, it could be the case that the opportunity of choosing itself could affect behavior.
 But when consumers are overconfident about their ability to save to pay back the loan, free choice could be a sub-optimal policy from the point of view of the client's long run self, and could match clients with  more costly contracts.
-Defenders of choice make another subtler point: that even if take up of the commitment-fee contract is low, the sole fact of \textit{having} choice could potentially change behavior or welfare (\cite{Dalboetal:2010}, \cite{Sjostrometal:2018}, \cite{Tlaxcala}).
+In this sense, if this self-selection mechanism works perfectly (as it would in a Roy model with all hyperbolics sophisticated) then the Forced and Choice arms will have an identical effect.
+Deviations between the impacts of these two arms therefore are implicitly a test of the optimality of the choices made in the choice arm.
+
+%Defenders of choice make another subtler point: that even if take up of the commitment-fee contract is low, the sole fact of \textit{having} choice could potentially change behavior or welfare (\cite{Dalboetal:2010}, \cite{Sjostrometal:2018}, \cite{Tlaxcala}).
 
@@
 
-\subsection{Forced versus Chosen Commitment} \label{forced_vs_choice}
-
 %Following two  paragraphs moved from old 'behavioral' choice section towards end of paper
@@
 %\subsection{The effect of choice on pawn recovery and financial cost} \label{effect_choice}
-
-We now present the core experimental results, illustrating how the Commitment Choice and Forced Commitment arms differ from the control.
-This comparison is particularly illuminating on the role of self-selection in Commitment, because if this self-selection mechanism works perfectly (as it would in a Roy model with all hyperbolics sophisticated) then the Forced and Choice arms will have an identical effect.
-Deviations between the impacts of these two arms therefore are implicitly a test of the optimatlity of the choices made in the choice arm.
 
@@
 
-\begin{table}[H]
-\caption{Determinants of Choice}
-\label{det_choose}
-\begin{center}
-\scriptsize{\input{./Tables/determinants_choose.tex}}
-\end{center}
- \scriptsize
+%\begin{table}[H]
+%\caption{Determinants of Choice}
+%\label{det_choose}
+%\begin{center}
+%\scriptsize{\input{./Tables/determinants_choose.tex}}
+%\end{center}
+% \scriptsize
 
 %\textit{Do file: } \texttt{determinants\_choose.do}
-\end{table}
+%\end{table}
 
@@
 }
+
+\newpage
+\subsection{Main treatment effects: Additional material}
+
+\vspace{.2in}
+
+\begin{table}[H]
+\caption{Decomposition of main treatment effects}
+\label{mechanisms}
+\begin{center}
+\scriptsize{\input{./Tables/decomposition_main_te.tex}}
+\end{center}
+
+%\textit{Do file: } \texttt{decomposition\_main\_te.do}
+\end{table}
 
@@
 \begin{center}
-  \begin{minipage}[b]{1.0\linewidth}
-    \subcaption{Timeline of the experiment}
-    \centering
-        \includegraphics[width=0.4\textwidth]{Figuras/timeline_suc_exp_extended.pdf}
-        \subcaption{Experiment arms}
-\centering        
-\scriptsize{\input{./Tables/exp_arms.tex}}
-  \end{minipage}
-  \end{center}
-    \scriptsize Panel (a) displays in black arrows the period covered by our administrative data: from August 6th 2012 (30 days before the experiment began : pre-experiment period) to August 13th 2013.
-The gray lines correspond to the dates of implementation of the experiment.
-We finished the experiment earlier in branches 1 and 2 because we realized that we would have enough sample size with the remaining branches and wanted to save on operational costs.
-Panel (b) shows our 5 treatment arms.
-It shows the number of observations in each arm together with the observations for the surveys.
-%\textit{Do file: }  \texttt{timeline\_suc\_exp.do}
+\begin{subfigure}{\textwidth}
+        \includegraphics[width=\textwidth]{Figuras/consort.pdf}
+    \end{subfigure}
+  \end{center}
+    \scriptsize 
+%\textit{Do file: }  \texttt{ss\_att.do}
 \end{figure}
@@
 \begin{figure}[H]
-     \caption{Explanatory Material: Promise-Choice Days}
+     \caption{Explanatory Material}
     \label{ExplanatoryMaterial}
     \begin{center}
-    \begin{subfigure}{0.75\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/MicaChoiceDonde.png}
+    \begin{subfigure}{\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/micas.pdf}
     \end{subfigure}
@@
     \scriptsize
-        This is a (translated) sample information slide shown to clients in choice-promise days.
-The real ones were twice the size of this figure and were laminated.
-Different ones were shown for each treatment arm.
+        This is a (translated) sample information slide shown to clients. The real ones were twice the size of this figure and were laminated. Different ones were shown for each treatment arm.
+\end{figure}
+
+\begin{figure}[H]
+     \caption{Contract Terms Summary, and Promise Slip}
+    \label{PaperSlip}
+    \begin{center}
+    \begin{subfigure}{0.65\textwidth}
+    \caption{Receipt for client}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/TicketLenderP.png}
+    \end{subfigure}
+
+    \vspace{3ex}
+    \begin{subfigure}{0.65\textwidth}
+    \caption{Personal promise signed by client}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/Personal Promise2.png}
+    \end{subfigure}
+    \end{center}
+    \scriptsize
+        The top of this figure is a sample receipt that was given to clients that got assigned to the fee-forcing contract (the font and format were changed to protect Lender's P identity).
+We want to highlight the salience of some items.
+First the title clearly indicated which contract the client has (arrow 1).
+Second, in the case of the fee contract it clearly indicates that there is a fee for paying late equivalent to 4\% of the value of the monthly payment (arrow 2).
+Third, there is a calendar for payments clearly specifying the dates and amounts to pay each month.
+The bottom panel of the figure shows a ``promise slip'', the paper that those who were assigned (or chose) to the monthly payment with promise had to sign to make the promise salient.
+It emphasizes that the client is giving his word, and that the promise is not a legal document.
 \end{figure}

### 2022-02-17 donde.tex
Analysis for email feb16

@@
 Pawn loans involve individuals leaving valuable and liquid assets, typically jewelry, as collateral in exchange for an immediate cash loan.
-Collateral is typically much larger than the loan, which allows lenders to skip the checking of credit history and give the loan immediately.
-This makes pawn loans popular to get cash to pay for emergencies.
+Collateral is typically larger than the loan, which allows lenders to skip the checking of credit history and give the loan immediately.
+This makes pawn loans a popular way to get cash to pay for emergencies.
 In fact, they are one of the most prevalent forms of borrowing.
 There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues.\footnote{\url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.} Our partner pawn lender alone served more than 1 million clients in the last 3 years with more than 4 million contracts.
-For comparison there were 2.3 million micro-finance clients in Mexico in 2009 \citep{Pedroza:2010}.
-
-Pawn borrowing is also one of the oldest forms of borrowing.
-Pawn loans existed in antiquity at least since the Roman Empire, and there are records of it in China about 1,500 years ago \citep{PawnShops}.
+For comparison there were 2.3 million micro-finance clients across all lenders in Mexico in 2009 \citep{Pedroza:2010}.
+
+Pawning is also one of the oldest forms of borrowing.
+Pawn lending existed in antiquity at least since the Roman Empire, and there are records of it in China about 1,500 years ago \citep{PawnShops}.
 In spite of the high prevalence and long history, pawnshop borrowing has not received much attention in the economics literature.
-The closest product studied is probably payday loans.
+The closest product widely studied is payday loans.
 In developing countries, however, payday lending is likely small compared to pawnshop lending; the latter is faster and requires less documentation, allowing access to informal sector workers who receive their salaries in cash.
@@
 There is some evidence  in support of this view.\footnote{\cite{Bertrand} write that ``Under the view that the people borrowing from payday lenders are making an informed, utility-maximizing choice given the constraints that they face, one  would not expect additional information disclosure about the payday product to  alter their borrowing behavior'', but to the contrary they find that simply disclosing how financing costs add up reduced demand by 11\%.
-%\cite{Meltzer} finds that payday loan access leads to increased difficulty paying mortgage, rent and utilities bills.
-}
+\cite{Meltzer} finds that payday loan access leads to increased difficulty paying mortgage, rent and utilities bills.}   Our study reinforces the idea that a lack of sophistication may be an integral part of that way that standard pawn contracts are structured.
 
@@
 The loan had a 90 days term with 15 days' grace period, and the client could make payments at anytime with no penalty for pre-payment.
-If the client paid the principal plus the accumulated interest in less than 105 days, then she received back her pawn, otherwise the pawnbroker kept the piece and any payments made.
+No reminders or interim contact exists between the lender and the borrower.
+If the client returns to pay the principal plus the accumulated interest within 105 days, she received back her pawn, otherwise the pawnbroker kept the piece and any payments made.
 Before the contract expired, the client had the right to renew it  using the same collateral for another 3 months by going to the pawnshop paying the accumulated interest and signing a new contract with exactly the same terms as the original one.
-Only 26\% of borrowers renew twice or more.
+26\% of borrowers renew at least once with a given pawn.
 This contract was standard in the industry.
 
-The clients that pawned understood its conditions (as we verified in interviews) and still decided to pawn.
-\footnote{90\% of clients report in our survey that they have pawned before.} These clients have little or no access to other types of loans and value the convenience of pawn borrowing.The population we are working with is economically vulnerable in the sense that 30\% of them could not pay either water, electricity \& gas or rent in the past 6 months.
+The clients that pawned understood these terms well (as we verified in interviews).
+\footnote{90\% of clients report in our survey that they have pawned before.} These clients have little or no access to other types of loans and they value the convenience of pawn borrowing.
+This population of pawn borrowers is economically vulnerable:  30\% of them could not pay either water, electricity \& gas or rent in the past 6 months.
 They often receive negative income shocks: 87\% said they are pawning because of an emergency, and only 13\% stated it was to use in a `non-urgent expense'.
-When asked why they are pawning this piece gr{5\%} responded gr{`lost a family member'}, gr{`a medical emergency'} (gr{11\%}), gr{`an urgent expense'} (gr{71\%}),
-
-Our context is one with high borrower default: 60\% of clients lose their pawn in a time span of 230 days from the date of pawning.
-One potential explanation for high default is that clients are really just selling their gold piece.
-This is unlikely for several reasons: (a) the reported subjective value of the pawn is larger than the loan size for 86\% of clients, (b) among those that lose their pawn 48\% paid a positive amount towards its recovery and on average paid 42\% of the value of their loan (see Figure \ref{proxy_naive} in Appendix) --- this can only be rationalized if they expected to recover their pawn, (c) clients can easily sell the gold and obtain a higher amount of instant cash at gold buying stores located close to almost all our pawnshop branches (see Figure \ref{GoldBuyers}).
-%(d) there is a lot of engagement with the lender after pawning even for those who lost their pawn.
-On average clients that lost their pawn paid 34\% of the value of their loan, and close to 42\% of clients extended the loan for another cycle and made payments in the second cycle (see Figure \ref{proxy_naive} in Appendix).
+When asked why they are pawning this piece 5\% responded `lost a family member', `a medical emergency' (11\%), or `an urgent expense' (71\%).
+
+Our context is also one with high borrower default: 60\% of clients lose their pawn in a time span of 230 days from the date of pawning.
+One potential explanation for high default is that clients are really just knowingly selling their gold piece through a pawn contract on which they intend to default.
+This appears unlikely for several reasons: (a) clients can easily sell the gold and obtain a higher amount of instant cash at gold buying stores located close to almost all our pawnshop branches (see Figure \ref{GoldBuyers}), (b) the reported subjective value of the pawn is larger than the loan size for 86\% of clients, (c) among those that lose their pawn 48\% paid a positive amount towards its recovery and on average paid 42\% of the value of their loan (see Figure \ref{proxy_naive} in Appendix) --- this can only be rationalized if they expected to recover their pawn, and (d) 74\% of borrowers report in our baseline survey that they anticipate recovering the pawn at the time they take the loan.
 High default could be also detrimental from the lender's point of view since it may reduce the likelihood that the client becomes a return costumer.
@@
 
-The pawnshop therefore makes money in three ways: by reselling the jewelry left as collateral on defaulted loans, by charging interest on non defaulted loans, and by keeping the payments made on defaulted loans.
-The interest rate typically used to calculate borrower APRs is thus a very inadequate measure of the effective cost of pawn loans.
+Pawnshops therefore makes money in three ways: by reselling the jewelry left as collateral on defaulted loans, by charging interest on non defaulted loans, and by keeping the payments made on defaulted loans.
+In this way the interest rate typically used to calculate borrower APRs is thus a very inadequate measure of the effective cost of pawn loans.
 
@@
 \vspace{.2in}
-\noindent \textbf{The Commitment Contract.} For the purpose of the experiment we designed a new contract that is identical to the status quo contract except that it enhances the regularity and salience of payments.
+\noindent \textbf{The Commitment Contract.} For the purpose of the experiment we designed a new contract that is identical to the status quo contract except that, informed by the behavioral literature on the ways to improve repayment in credit contracts, it enhances the regularity and salience of payments.
 It has the same interest rate (7\% \textit{per month}) which accumulates daily on outstanding debt, it has the same loan size/collateral ratio (70\%), it has the same loan term (90 days, and a grace period of 15 days), and the gold pawn gets appraised in the same way by the same appraisers.
@@
 }
+
+As is typical in the behavioral literature we include an arm that allows borrowers to opt in to the commitment contract if they choose.
+If, however, a lack of sophistication is an issue with borrowers in pawn contracts, then this process of self-selection may not assign commitment to the `right' people.
+To examine this issue, we include an arm  that assigns all individuals to the commitment contract so that we are able in essence to form three counterfactual outcomes; no commitment, commitment, and the chosen commitment.
+This design allows us to investigate the repercussions of choice not only for those who \textit{do} choose (as is the case in a standard LATE design), but also the implications of choice for those who \textit{do not} choose.
+This turns out to be key for what we can learn from this experiment.
+In order to explore lower-cost forms of structure, we also include arms that feature `soft' commitment, asking or requiring individuals to follow the more regular payment structure of the commitment contract but then providing no reminders or repercussions for failing to do so.
 
@@
 The number of branch days allocated to each were 84, 80, 93, 68, and 82, respectively.
+See Figure \ref{exp_description} for a CONSORT-style diagram of the study design and recruitment.
 
@@
 \noindent \textbf{Randomization.}  Starting September 6, 2012, we implemented the experiment in 6 branches of Lender $P$.
-The branches were selected by Lender $P$ to be dispersed across Mexico city and have varying sizes.
+The branches were selected by Lender $P$ to be dispersed across Mexico City and have varying sizes.
 In four of them the experiment ran for 107 days, and in 2 of them we ran it for a shorter time to economize on data collection costs once we realized we would not be constrained by sample size.
@@
 It also limits potential manipulation by appraisers, who in the presence of individual level randomization could potentially pick their preferred costumers from the line or tell them to wait until their desired contract shows up on the screen.
-Intra-branch day correlation on the probability of default (ICC) is small, at {0.08}, so we don't lose much power vis-a-vis individual level randomization.
-
-By comparing the \textit{Forced Commitment} arm vs the \textit{Control} arm we estimate the causal effect of mandatory installment frequency that acts as a incentive to pay earlier vis-a-vis the pay-when-you-want contract.
-On the other hand, having arms where clients can choose among these contracts allows us to study clients' demand for commitment to pay earlier, and the nature of selection into this choice.
-A neoclassical consumer with no intra-household concerns would not voluntarily restrict her options of payment profiles (as in the monthly installment contract) by being subject to fees, since she can always replicate the monthly payment profile herself under the status quo contract if she so desired.
-The status quo contract gives her extra flexibility to respond to negative income shocks.
-However, if clients have present biased preferences \textit{and} are sophisticated about them, they may choose the frequent payment contract as it has commitment value.
-This value would be traded off against the value of lost flexibility.
-This design also allows us to test the extent to which commitment must be externally imposed and reinforced to be effective, relative to softer and more self-directed forms of commitment.
-%Promises could have larger or smaller commitment value than a pecuniary fee, something that we test by comparing behavior in the \textit{promise-forcing} vs \textit{status quo} arms.
+Intra-branch day correlation on the probability of default (ICC) is small, at {0.08}, so we lose little power vis-a-vis individual-level randomization.
 
@@
 
-The administrative data contains a unique identifier of the client, an identifier of the piece she is pawning, and the transactions relating to that piece.
+The administrative data contains a unique identifier for the client, an identifier for the piece she is pawning, and the transactions relating to that piece.
 In particular, the value of the piece as assessed by the appraiser, the amount of money loaned (70\% of the value), the date of the pawn transaction, and the type of contract for that pawn.
-Within the period fo the loan, we followed each transaction related to that piece in the administrative data: when payments were made and for what amounts, whether there was default (i.e.
-the client lost her pawn), and whether any late-payment fees (active for the relevant experimental arms) were imposed.
+Within the period of the loan, we followed each transaction related to that piece in the administrative data: when payments were made and for what amounts, whether there was default (i.e.
+the client lost her pawn), and whether any late-payment fees were imposed.
 After the experimental loan, we are able to track subsequent behavior and to see whether that borrower took a subsequent loan.
 We have this information for all the pawns that occurred in the experiment's 6 branches between August 2, 2012 and August 13, 2013, this includes all the pawns under our experiment but also those that happened 1 month before it started and up to 8 months after it ended.
-Figure \ref{exp_description}(a) shows the timing of the experiment and our admin data coverage.
-The black arrows represent the dates for which we have administrative data (before and after the experiment) for each branch, while the light gray segments represent the duration of the experiment.
+Figure \ref{exp_description} shows the design and timing of the experiment, along with the sample sizes in each arm.
 The experiment comprises 13,446 pawns, and our administrative data cover a total of 23,974 pawn
@@
 It was short to avoid discouraging the potential clients from pawning, but at the same time it aimed to measure the following: demographics, proxies for income/wealth, education, self-control problems/present-biased preferences, experience pawning, if family or friends commonly asked for money, how time consuming and costly it was to come to the branch, the subjective probability of recovering the piece that they intended to pawn, the subjective value of their piece in money terms (how much money they would sell it for), among others.
-We surveyed 10,437 clients.\footnote{The Appendix \ref{baseline_survey} transcribes the questionnaire in English.} %\footnote{We also surveyed clients before and after the experiment, so our survey covers a larger sample that we are not using in this paper.}.
-Survey response rate is 78\%, and response is not related to admin data observables (details in Table \ref{balance_response} in the Appendix).
+We surveyed 10,437 clients, and the survey response rate is 78\%.\footnote{The Appendix \ref{baseline_survey} transcribes the questionnaire in English.} %\footnote{We also surveyed clients before and after the experiment, so our survey covers a larger sample that we are not using in this paper.}.
+%Survey response rate is 78\%, and response is not related to admin data observables (details in Table \ref{balance_response} in the Appendix).
 
@@
 We anticipated this possibility and trained appraisers to say --that whatever was the contract that day-- it was the only available contract for an undetermined amount of time.
-Because we do not observe refusals directly, we address this issue by examining the number of borrowers per day.\footnote{Our enumerators informed us that potential clients rarely left the branch without pawning, and that it was even less common that they did so when hearing about monthly installments.
+Because we do not observe refusals directly, we address this issue by examining the number of borrowers per day, with specific attention to whether the Forced Commitment arm led to a lower number of borrowers per day.\footnote{Our enumerators informed us that potential clients rarely left the branch without pawning, and that it was even less common that they did so when hearing about monthly installments.
 Lender P also never complained to us that our different treatments were hurting sales.
@@
 We estimate no difference in the number of pawns, showing that people are not leaving the branch without pawning at larger rates during the experiment ($\beta_a=1.32$, $\beta_b=-0.65$, with p-values 0.11 and 0.83, respectively).
-
-All the pieces of evidence indicate that there was no selection across arms and that experimental comparisons are internally valid.
+Table \ref{num_pawns_bal} shows the beta coefficients from these regressions, which are nowhere significant.
+Hence we begin the analysis confident that differential attrition has not occurred.
 
@@
 
-%\subsection{The Choice of Commitment}
-%\label{choice_commitment}
-
-%Section \ref{fee-commitment} showed that the Forced Commitment commitment contract reduced financing cost across the board, and that consumers themselves seemed to like it once they tried it.
-In such a case, one would expect a strong demand for it.
-This is not the case.
-We also find that clients in the choice arm achieved no better outcomes than those in the status quo group.
-
-%\subsection{Demand for the Forced Commitment commitment contract} \label{sec:demand}
-
-%\noindent \textbf{Low demand for commitment:} 
-We begin our empirical analysis with a comparison of the Forced Commitment and Commitment Choice arms to the control.
-In the Forced arm, all individuals received the Commitment product.
-In the Choice arm, 11\% of individuals offered the product selected it.
-When preferences or income streams are heterogeneous, and consumers are neoclassical, giving choice among contracts is often a welfare increasing strategy.
-Consumers would choose the contract that best fits their needs.
-This holds also in most simple models of present bias preferences if consumers are sophisticated about their present bias.
-But when consumers are overconfident about their ability to save to pay back the loan, free choice could be a sub-optimal policy from the point of view of the client's long run self, and could match clients with  more costly contracts.
-In this sense, if this self-selection mechanism works perfectly (as it would in a Roy model with all hyperbolics sophisticated) then the Forced and Choice arms will have an identical effect.
+the comparison of the \textit{Commitment Choice} arm to the \texit{Control} arm provides the test of self-selection that is standard in the behavioral literature.
+A lack of impact in this comparison would be consistent either with a population of neo-classical borrowers, for whom the commitment feature is superfluous, or with a population of time-inconsistent borrowers who lack sophistication over their own behavioral problems.
+The key to distinguishing these two stories is the treatment effect of commitment on those who would not choose it; this counterfactual is revealed through the comparison of the \textit{Forced Commitment} arm to the \textit{Control}.
+So while the forcing of commitment cuts against the grain of a behavioral literature that has largely promoted `nudges', it reveals important additional information that will be particularly relevant in borrower populations that are both hyperbolic and naive.
+
+As a starting point for the empirical analysis, in the Choice arm only 11\% of individuals offered the product selected it.
+This is initial evidence either that we are dealing with a population of largely time consistent individuals who do not need commitment, or of a population with many naive individuals who do not know that they need it.
+If this self-selection mechanism works perfectly (as it would in a Roy model with all hyperbolics sophisticated) then the Forced and Choice arms will have an identical effect.
 Deviations between the impacts of these two arms therefore are implicitly a test of the optimality of the choices made in the choice arm.
+
+We pose this question using the standard Intention to Treat analysis equation (\ref{basic_reg}) across arms.
+
+\begin{equation} \label{basic_reg}
+    y_{ij} = \alpha + \beta^F T_{i}^F + \beta^C T_{i}^C + \gamma X_{ij} + \epsilon_{ij}
+\end{equation}
+
+\noindent where $i$ refers to client, $j$ indexes branch, $T_{i}^F$ and $T_{i}^C$ are indicator variables for receiving the Fixed or Choice arms, $X_{ij}$ are branch and day-of-week fixed effects.\footnote{There is a minority of of clients that pawned again and got assigned a different treatment.
+Results are robust to excluding them.
+In the regressions we include them and add a dummy indicating clients who has more than one treatment in the experimental period.} We cluster errors at the branch-day level.
+%\footnote{If we restrict ourselves to pieces that fall in a single-arm (64\%), then treatment reduces the financial cost by 5.7\%, increases the likelihood of recovering their pawn by 35\%, and increases the likelihood of repeat business by 66\%.}.
+Our main outcome variables $y_{ij}$ are measures of financial cost in pesos as defined in Section \ref{FC_def}, which we further decompose into its component costs:  payments to capital, fees, interest, and the cost of losing the pawn.
+We then cast each of these costs as an Annual Percentage Rate (APR).
+as well as an indicator variable for client $i$ losing her pawn.
+In this subsection $T_{i}$ is an indicator for $i$ having got the \textit{fee-forcing} contract, and $\beta$ estimates the average treatment effect.%\footnote{This is an ATE and not just an ITT since take up of treatment is 100\%.}
 
@@
 
-Would clients benefit ---in terms of recovering their pawn and in terms of paying lower financing cost--- from having a monthly payment commitment contract \textit{forced} on them, vis-a-vis the status quo pay-when-you-want contract?
-We find they do.
-For each comparison, we separately estimate the regression equation (\ref{basic_reg}) below.
-
-\begin{equation} \label{basic_reg}
-    y_{ij} = \alpha + \beta T_{i} + \gamma X_{ij} + \epsilon_{ij}
-\end{equation}
-
-\noindent where $i$ refers to client, $j$ indexes branch, and $X_{ij}$ are branch and day-of-week fixed effects.\footnote{There is a minority of of clients that pawned again and got assigned a different treatment.
-Results are robust to excluding them.
-In the regressions we include them and add a dummy indicating clients who has more than one treatment in the experimental period.} %\footnote{If we restrict ourselves to pieces that fall in a single-arm (64\%), then treatment reduces the financial cost by 5.7\%, increases the likelihood of recovering their pawn by 35\%, and increases the likelihood of repeat business by 66\%.}.
-Our main outcome variables $y_{ij}$ are measures of financial cost in pesos as defined in Section \ref{FC_def}, as well as an indicator variable for client $i$ losing her pawn.
-In this subsection $T_{i}$ is an indicator for $i$ having got the \textit{fee-forcing} contract, and $\beta$ estimates the average treatment effect.
-We cluster errors at the branch-day level.%\footnote{This is an ATE and not just an ITT since take up of treatment is 100\%.}
-
-The Intention to Treat (ITT) results are very clear:  giving clients the option of choosing commitment is not effective, and forcing them into the commitment contract is.
-Choice does \textit{not} lead to lower financial cost compared to the status-quo contract.
-Nor does it lead to higher pawn recovery.
+The Intention to Treat (ITT) results, presented in Table \ref{main_impact_table} and graphically in Figure \ref{main_te}, are extremely stark.
+The Choice arm fails to deliver improvements on any measure (with the exception of an increase in fees, for which we are very powered since this outcome is always zero in the control).
+In sharp contrast, the Forced Commitment arm yields very strongly significant decreases in the financial cost of loans to clients.
+Despite causing a 106 peso increase in payments to capital and a 28 peso increase in fees, the Forced arm leads to a 100 peso decline in interest payments and an enormous decline in the expected pawn losses (almost 500 pesos), driven by a 12\% decrease in the probability of default.
+The bottom panel of the figure casts these costs as APRs, and shows that while the Choice arm actually leads to a slight \textit{increase} in the APR, the Forced arm decreases the effective annualized interest rate of pawn lending by 40\%.
 Figure \ref{main_te} gives the standardized effect sizes (in standard deviations) of the two main study arms for three outcomes:  default, the financial cost of the loan, and the effective interest rate paid to acquire the borrowed capital.
 Very clearly, the Forced arm is significant for all three outcomes, with very substantial treatment effects in magnitudes for default and APR, and the commitment arm is never significant.
-
-\textcolor{red}{Include here table that has regressions from Eq. 1 underlying the figure above.}
-
-\vspace{.2in}
-\noindent \textbf{Detailed analysis of financial cost.} Figure \ref{fc_pro4} digs in more detail into the sources of variation underlying the main effects in Figure \ref{main_te}.
-$\beta$ coefficients and their 95\% confidence interval from estimating equation (\ref{basic_reg}) using different definitions of financial cost.
-The leftmost coefficient corresponds to plugging into the formula of section \ref{FC_def} the appraised gold value of the pawned piece.
-The second coefficient uses the subjective value of the pawn instead.
-In both cases we find that being assigned to the Forced Commitment commitment contract causes a large reduction in the financing cost the client incurred, of 9.4\% (\$297) under the first definition and 13.2\% (\$472) under the second one.
-That is, we find that \textit{charging} clients a late payment decreases total \textit{fee-inclusive} financing cost.
-
-Financial cost incurred by pawn-shop clients is a key variable to study.
-However it does not take into account transportation cost or the opportunity cost of going in person to the branch.
-Given that the Forced Commitment contract makes clients visit the branch more often (monthly), one may want a measure that includes those costs as well.
-Going in that direction, in a broader measure of costs, for each visit we add the self-reported transport cost plus a whole day's wage, multiplied by the number of visits.
-Adding a whole day's wage may exaggerate cost, but we still observe a reduction of this more comprehensive measure of cost caused by the frequent payment contract, although we lose more than 1/3 of the observations and some precision from missing data on transportation costs.
-We conclude that penalizing borrowers for delinquency in a contract which has already has large penalties from default (losing the collateral in a highly collateralized loan) actually helps borrowers.
-
-\textcolor{red}{Beginning of discussion on Quantile Effects:.}
-The hollow circles in Figure \ref{fc_pro4}(a) show zero average effects for the different definitions of financial cost analogous to the ones described above.
-Figure \ref{fc_pro4}(b) shows further that the null effect happens for the 15$^{th}$, 25$^{th}$, 50$^{th}$ 75$^{th}$, and 85$^{th}$ percentiles.\footnote{The few clients that chose the Commitment contract (the solid black squares) do enjoy cost savings of 1005 MXN, which compares favorably to the 304 MXN in the Forced arm (as a fraction of the loan the numbers are 41.5\% and 12.5\%), but this combines the selection and treatment effects.} %Figure \ref{heterogeneous_te_4} plots the distribution of treatment effects and finds that the distribution offering choice actually \textit{increased} financial cost and default for about half of clients compared to being assigned the status-quo contract.
-Those tended to be the less economically vulnerable and more educated, {women}, and those whose family typically asks them for money.
-Figure \ref{fc_pro4}(c) finds null effects for pawn recovery. Consistent with these findings, Figure \ref{reincidence} finds no effect on repeat purchases for the Commitment Choice group.
-
-\vspace{.2in}
-\noindent \textbf{Pawn Recovery.} Figure \ref{fc_pro2}(d) plots estimated treatment effects of the Forced Commitment commitment contract with the dependent variable being an indicator of losing the pawn in less than 230 days.
-The leftmost coefficient shows that the Forced Commitment commitment contract increases the likelihood of recovering the pawn by 11 percentage points (26\% of mean recovery).
-This result stands in contrast with \cite{Pande} who find no effect of payment frequency on default in a group lending microfinance context.
-Figure \ref{fc_pro2}(e) shows the distribution of heterogeneous treatment effects for losing the pawn: The likelihood of losing the pawn decreases for 82\% of the population.
-%Figure \ref{HTE_fee_forcing}(b) in the Appendix shows that those we classify as present biased, those that requested to be sent a reminder to pay, and those who have more problems paying for basic services experienced the largest increases on pawn recovery.
-
-%the second conditions on the population that paid any positive amount towards recovery of their pawn; the third conditions on having paid at least 30\% of the loan amount; the fourth conditions on the period covering the first cycle of the loan; the fifth on the period of the first cycle and paying any positive amount.
-
-\vspace{.2in}
-\noindent \textbf{Effects on other outcomes.} There are other intermediate outcomes that are impacted by being assigned to frequent payments.
-Table \ref{mechanisms} shows that the first payment happens 8 days earlier (column 1) in the Forced Commitment arm than in the status quo one, and that the number of payments increases by 0.19 (column 2).
-Figure \ref{induced_to_pay_early} in the correlates HTE on financing cost with the HTE time of first payment and shows that those induced to pay earlier are also those that have larger induced reduction in financial cost.
+In other words, voluntary commitment is ineffective but the use of forced commitment saves the average borrower an amount of money almost twice the APR of a normal US credit card loan.
+
+There are other intermediate outcomes that are impacted by being assigned to frequent payments.
+Table \ref{mechanisms} shows that the first payment happens 8 days earlier (column 1) in the Forced Commitment arm than in the status quo one, and that the number of payments increases by 0.19 (column 2).% Figure \ref{induced_to_pay_early} in the correlates HTE on financing cost with the HTE time of first payment and shows that those induced to pay earlier are also those that have larger induced reduction in financial cost.
 Treatment effects are concentrated on the intensive margin, as treatment does \textit{not} affect the fraction of clients who pay a positive amount (column 6).
@@
 
-\vspace{.2in}
-\noindent \textbf{Other sub-samples.}  Results survive if we focus on those that paid a positive amount in treatment and control.\footnote{Although this is potentially a selected subsample, Table \ref{mechanisms} showed that there is no treatment effect the extensive margin, i.e.
-in $pay>0$.} We find that even those that paid a fee in the Forced Commitment contract end up paying a smaller financial cost that those in the status-quo contract (Figure \ref{fc_pro2}a).\footnote{This regression conditions on those that paid a fee in the Forced Commitment group, and compares this subset in treatment vs all of the control group.
-Results are similar if we condition in the control group on those who would have paid a fee  if they were in the treatment group given their observed payment behavior.
-Again we acknowledge this is an endogenous sample and that the estimate may not be a causal effect.}  Figure \ref{fc_pro2}(d) shows that the increase in pawn recovery is robust to defining recovery using the first 120 days of the contract, or restricting to those paying a positive amount towards pawn recovery.
-
-%we The 4th coefficient from left to right conditions on those who paid a positive amount (in treatment and control).
-Although this is potentially a selected subsample, Table \ref{mechanisms} showed that there is no treatment effect on pay$>0$.
-We were interested in this population to show that the effect is there for those who are serious about recovering their pawn.
-The fifth coefficient conditions on those that paid a fee in the Forced Commitment group, comparing this subset in treatment vs all of the control group.
-Results are similar if we condition in the control group on those who would have paid a fee given current behavior.
-Again we acknowledge these is an endogenous sample and that the estimate may not be a causal effect.} We find that even those that paid a fee in the Forced Commitment contract end up paying a smaller financial cost that those in the status-quo contract.
-
-\subsection{Analysis of repeat pawning}
-
-Although we have shown that Forced Commitment reduces financial cost and increases pawn recovery, this does not imply that welfare increases.
+While the mechanical financial cost and APR incurred by pawn-shop clients are key outcomes, it is worth deepening the analysis with a set of additional drivers relevant to the subjective costs perceived by borrowers.
+Figure \ref{robustness_fc} shows the results of these robustness checks.
+First, rather than using the appraised value of the pawn from the lender, we can assess costs using the subjective value of the pawn reported by the borrower.
+Second, because the Commitment contract requires more frequent visits to the branch, there are travel costs incurred relative to the status quo payment structure that we can include in the costs of commitment.
+For each visit we add the self-reported transport cost plus a whole day's wage, multiplied by the number of visits.
+Adding a whole day's wage may exaggerate cost, but we still observe a reduction of this more comprehensive measure of cost caused by the frequent payment contract, although we lose more than 1/3 of the observations and some precision from missing data on transportation costs.
+Finally, we can adjust for the fact that the early payment induced by the commitment contract actually reduces the effective liquidity received by borrowers.
+Taking the interest rate as the opportunity cost of capital, the interest payments averted are not really `saved' given that the liquidity is itself foregone.
+So our final adjustment removes the saved interest payments from the calculation of the benefits across arms.
+The figure shows the effects of each of these adjustments on the estimate of financial cost and APR, and illustrates that even when we make all of these adjustment simultaneously the Forced arm generates benefits of 0.11 standard deviations.
+
+A simple way to move towards a consideration of borrower welfare is the conjecture that if clients exposed to the installment contract like it, they will be more likely to come back vis-a-vis those that got status quo contract.\footnote{\cite{Laibson2018} hypothesizes that consumers use ``experienced utility'' as a guide to make future purchases in this way.} This is indeed what we find in the data.
+We consider this outcome in Table \ref{X}.
+We can first ask whether the individual ever takes a loan after the initial study loan, an analysis which is simply experimental.
+The results show that the Choice arm is no more likely to pawn again, which the Forced arm is X\% more likely to take a second loan.
+While this appears to be \texit{prima facie} evidence of greater satisfaction with the lender, interpretation here is complicated by the fact that they were so much more likely to have recovered their pawn and hence to be able to pawn it again.
+We can explore this possibility in a number of ways.
+First, we can consider the probability that the borrower ever takes another loan using a \textit{different} pawn, an outcome that if anything would be biased downward in the Forced arm.
+Finally, we can conduct an endogenous sample split and examine the treatment effects within the sample that does, and does not, recover their pawn from the first loan.
+Results indicate that .
+.
+.
+
+%Although we have shown that Forced Commitment reduces financial cost and increases pawn recovery, this does not imply that welfare increases.
 Clients could have disutility from the stress of having monthly installments for instance.
 %We don't need to make the strong claim of welfare for the purposes of this paper. The financing cost results are striking enough. But we
-A simple way to move towards a consideration of borrower welfare is the conjecture that if clients exposed to the installment contract like it, they will be more likely to come back vis-a-vis those that got status quo contract.\footnote{\cite{Laibson2018} hypothesizes that consumers use ``experienced utility'' as a guide to make future purchases in this way.} This is indeed what we find in the data.
-
-The panel labeled Forced Commitment in Figure \ref{reincidence} presents results of estimating equation (\ref{basic_reg}) with the dependent variable being a dummy for the client being a repeat customer.
+
+%The panel labeled Forced Commitment in Figure \ref{reincidence} presents results of estimating equation (\ref{basic_reg}) with the dependent variable being a dummy for the client being a repeat customer.
 We define a client as a repeat customer if, after experiencing at least 75 days of the respective treatment arm, she came back and pawned a \textit{different} piece.\footnote{Results are robust to using number of days experiencing the contract larger than 75.
@@
 
-\hl{The second coefficient from the left focuses on the subsample who are predicted would have a treatment effect on financial cost savings above the median} treatment effect in their first pawn.\footnote{Since this is predicted using \cite{atheygrf} based on pre-determined covariates for treatment and control clients it is valid to split the sample this way.} It shows that for these clients the likelihood of coming back is twice as large.
+%\hl{The second coefficient from the left focuses on the subsample who are predicted would have a treatment effect on financial cost savings above the median} treatment effect in their first pawn.\footnote{Since this is predicted using \cite{atheygrf} based on pre-determined covariates for treatment and control clients it is valid to split the sample this way.} It shows that for these clients the likelihood of coming back is twice as large.
 That is, those that benefit more from the Forced Commitment contract are more likely to repeat compare to their control group.
@@
 
-%We also implemented an exit survey which clients filled when recovering their piece.
-Unfortunately it had low response rate (7\%), and we take its results with a grain of salt.
-In this survey 63\% of clients said they liked the frequent payment contract more than the status-quo one, and that it allowed them to avoid unnecessary expenses.
+.
 %The coefficient on repeat pawning is just as big when we focus only 2nd pawns happening after the first was recovered (third coefficient ``fnr'').
@@
 
+We also implemented an exit survey which clients filled when recovering their piece.
+Unfortunately it had low response rate (7\%), and we take its results with a grain of salt.
+In this survey 63\% of clients said they liked the frequent payment contract more than the status-quo one, and that it allowed them to avoid unnecessary expenses
+
 \subsection{Soft Commitment}
@@
 
-The results from the two arms of the study that feature `soft' commitment further reinforce the centrality of externally imposed commitment in this context.  
 %One way to go would be to decrease the already small fee say to 1\% or lower.
 We decided to instead experiment with a non-pecuniary penalty, in the form of a psychological cost of breaking a promise.
-As explained in Section \ref{Experiment} the promise contract involved making a salient promise to repay monthly, and receive a short speech by the appraiser about the importance of keeping her promise of paying monthly.
+%As explained in Section \ref{Experiment} the promise contract involved making a salient promise to repay monthly, and receive a short speech by the appraiser about the importance of keeping her promise of paying monthly.
+We now turn to the impact of the two arms that featured forms of soft commitment.
 A substantial literature documents that people don't like to break their promises, and are willing to incur in monetary losses in trying to keep them.
 This provides a potentially very attractive way to drive better repayment behavior at low pecuniary cost to clients.
-To our knowledge this type of result has been replicated several times in laboratory contexts but not in a field setting like ours.\footnote{Promises are not foreign to microfinance lending: Grameen bank for instance makes clients recite a promise at each center weekly meeting.The exact promise repeated by clients live is this: ``\textit{We pledge to attend regularly the weekly Center meetings, to utilize our loans for the purpose approved, to save and pay our installments weekly, to use our increased incomes for the benefit of our families, to ensure that other members of our group and Center do likewise and to take collective responsibility if they do not.''}}
+To our knowledge this type of result has been replicated several times in laboratory contexts but not in a field setting like ours.
+Promises are not foreign to microfinance lending, and various forms of soft commitment have been shown to be effective at changing financial behavior \citep{Craig}.\footnote{Grameen Bank for instance makes clients recite a promise at each center weekly meeting.The exact promise repeated by clients live is this: ``\textit{We pledge to attend regularly the weekly Center meetings, to utilize our loans for the purpose approved, to save and pay our installments weekly, to use our increased incomes for the benefit of our families, to ensure that other members of our group and Center do likewise and to take collective responsibility if they do not.''}}
 %If breaking a promise is perceived as having a lower cost than paying the 2\% fee and at the same time helps as a commitment device we could achieve better outcomes: more people would demand the Soft Commitment contract.
 
+In the pawn lending context, however, the results from the two arms of the study that feature `soft' commitment further reinforce the centrality of externally imposed commitment. 
 Demand for the Soft Commitment contract  is higher than for the Forced Commitment contract by a factor of 3: {31}\% of clients offered a choice between the status quo contract and the Soft Commitment contract chose commitment.
-Interestingly, the set of people who demand the Soft Commitment contract are different from those that demanded the Forced Commitment one.
+%Interestingly, the set of people who demand the Soft Commitment contract are different from those that demanded the Forced Commitment one.
 While in both cases the economically vulnerable demand less, in the case of the Soft Commitment those that we classify as present biased, those that report that they frequently fall into temptation buying, and those that ask for reminders of payment are \textit{less} likely to demand the Soft Commitment contract.
 This suggests that those taking up the promise commitment are not the ones needing the commitment (see Figure \ref{interactions_takeup} in the Appendix).
-
 Nonetheless, we find Soft Commitment, whether chosen or induced, to be completely ineffective in this environment.
@@
 
-Giving choice of whether to promise or not has the advantage of making promising an active decision by the client.
+%Giving choice of whether to promise or not has the advantage of making promising an active decision by the client.
 In most of the the experimental literature promising is voluntary.
@@
 
-\subsection{Heterogeneous Treatment Effects}
-
-\textcolor{red}{Propose to move all of the content of this section either up to ITTs (if quantile effects) or to the next section on paternalism (if Random Forest HTEs) and eliminate this section here.}
-
-\vspace{.2in}
-\noindent \textbf{Heterogeneous Treatment Effects (HTE).} Average cost reductions could mask substantial heterogeneity.
+Our core impacts show that forced commitment is uniquely effective, a result that can only arise if those who would not have freely chosen commitment benefit from it.
+We now delve more deeply into this result.
+
+\subsection{Quantile Treatment Effects}
+
+A simple way of interrogating the distribution of treatment effects is to use quantile regression.
 Benefits are distributed broadly however.
@@
 All of them are negative.
-This motivated us to implement a finer measure of treatment effects.
+%This motivated us to implement a finer measure of treatment effects.
 We used  \cite{atheygrf}'s generalized random forests methodology.\footnote{The methodology uses random forests of honest causal trees to estimate personalized treatment effects.
@@
 The optimal partition is that which minimizes expected mean squared error of treatment effects predictions out-of-sample.} %The tree is honest because it uses one sample to build the tree and another one to estimate treatment effects within that tree.
-\cite{atheygrf} show that their treatment effects are asymptotically normal, which allows us to construct confidence intervals for our treatment estimate in each leaf.
-
-Figure \ref{fc_pro2}(c) plots the distribution of those treatment effects using this machine learning methodology.
+%\cite{atheygrf} show that their treatment effects are asymptotically normal, which allows us to construct confidence intervals for our treatment estimate in each leaf.
+
+%Figure \ref{fc_pro2}(c) plots the distribution of those treatment effects using this machine learning methodology.
 It shows that more than 70\% of clients experienced financial cost savings in the Forced Commitment group compared to the status-quo group.
 The causal cost savings are larger for the more economically vulnerable, %that report at baseline that they have problems paying for services like water, electricity and rent,
-and those displaying overconfidence\footnote{see Section \ref{behavioral} for our measure of overconfidence.} about recovering their pawn, Figure \ref{HTE_fee_forcing}.
+%and those displaying overconfidence\footnote{see Section \ref{behavioral} for our measure of overconfidence.} about recovering their pawn, Figure \ref{HTE_fee_forcing}.
 %those that have to incur in higher transport cost to go to the branch  and that asked to be sent reminders to pay, this later one being one proxy of being inattentive or sophisticated present-biased.
 
-\subsection{The Wrong People Choose Commitment}
-
-This is not the first paper to find low demand for commitment, however it is the first we know of that can compare choice vs forcing.
-The fact that the Forced Commitment contract lowers financial costs for almost all clients, together with the fact that only 10\% choose it must mean that many consumers are choosing contracts with higher financial costs for themselves.
+Figure \ref{fc_pro4} digs in more detail into the sources of variation underlying the main effects in Figure \ref{main_te}.
+$\beta$ coefficients and their 95\% confidence interval from estimating equation (\ref{basic_reg}) using different definitions of financial cost.
+The leftmost coefficient corresponds to plugging into the formula of section \ref{FC_def} the appraised gold value of the pawned piece.
+The second coefficient uses the subjective value of the pawn instead.
+In both cases we find that being assigned to the Forced Commitment commitment contract causes a large reduction in the financing cost the client incurred, of 9.4\% (\$297) under the first definition and 13.2\% (\$472) under the second one.
+That is, we find that \textit{charging} clients a late payment decreases total \textit{fee-inclusive} financing cost.
+
+The hollow circles in Figure \ref{fc_pro4}(a) show zero average effects for the different definitions of financial cost analogous to the ones described above.
+Figure \ref{fc_pro4}(b) shows further that the null effect happens for the 15$^{th}$, 25$^{th}$, 50$^{th}$ 75$^{th}$, and 85$^{th}$ percentiles.\footnote{The few clients that chose the Commitment contract (the solid black squares) do enjoy cost savings of 1005 MXN, which compares favorably to the 304 MXN in the Forced arm (as a fraction of the loan the numbers are 41.5\% and 12.5\%), but this combines the selection and treatment effects.} %Figure \ref{heterogeneous_te_4} plots the distribution of treatment effects and finds that the distribution offering choice actually \textit{increased} financial cost and default for about half of clients compared to being assigned the status-quo contract.
+Those tended to be the less economically vulnerable and more educated, {women}, and those whose family typically asks them for money.
+Figure \ref{fc_pro4}(c) finds null effects for pawn recovery. Consistent with these findings, Figure \ref{reincidence} finds no effect on repeat purchases for the Commitment Choice group.
+
+ Figure \ref{fc_pro2}(d) plots estimated treatment effects of the Forced Commitment commitment contract with the dependent variable being an indicator of losing the pawn in less than 230 days.
+The leftmost coefficient shows that the Forced Commitment commitment contract increases the likelihood of recovering the pawn by 11 percentage points (26\% of mean recovery).
+This result stands in contrast with \cite{Pande} who find no effect of payment frequency on default in a group lending microfinance context.
+Figure \ref{fc_pro2}(e) shows the distribution of heterogeneous treatment effects for losing the pawn: The likelihood of losing the pawn decreases for 82\% of the population.
+%Figure \ref{HTE_fee_forcing}(b) in the Appendix shows that those we classify as present biased, those that requested to be sent a reminder to pay, and those who have more problems paying for basic services experienced the largest increases on pawn recovery.
+
+%the second conditions on the population that paid any positive amount towards recovery of their pawn; the third conditions on having paid at least 30\% of the loan amount; the fourth conditions on the period covering the first cycle of the loan; the fifth on the period of the first cycle and paying any positive amount.
+
+ Results survive if we focus on those that paid a positive amount in treatment and control.\footnote{Although this is potentially a selected subsample, Table \ref{mechanisms} showed that there is no treatment effect in the extensive margin, i.e.
+in $pay>0$.} We find that even those that paid a fee in the Forced Commitment contract end up paying a smaller financial cost that those in the status-quo contract (Figure \ref{fc_pro2}a).\footnote{This regression conditions on those that paid a fee in the Forced Commitment group, and compares this subset in treatment vs all of the control group.
+Results are similar if we condition in the control group on those who would have paid a fee  if they were in the treatment group given their observed payment behavior.
+Again we acknowledge this is an endogenous sample and that the estimate may not be a causal effect.}  Figure \ref{fc_pro2}(d) shows that the increase in pawn recovery is robust to defining recovery using the first 120 days of the contract, or restricting to those paying a positive amount towards pawn recovery.
+
+%we The 4th coefficient from left to right conditions on those who paid a positive amount (in treatment and control).
+Although this is potentially a selected subsample, Table \ref{mechanisms} showed that there is no treatment effect on pay$>0$.
+We were interested in this population to show that the effect is there for those who are serious about recovering their pawn.
+The fifth coefficient conditions on those that paid a fee in the Forced Commitment group, comparing this subset in treatment vs all of the control group.
+Results are similar if we condition in the control group on those who would have paid a fee given current behavior.
+Again we acknowledge these is an endogenous sample and that the estimate may not be a causal effect.} We find that even those that paid a fee in the Forced Commitment contract end up paying a smaller financial cost that those in the status-quo contract.
+
+\subsection{Mistakes in the Choice of Commitment}
+
+This is not the first paper to find low demand for commitment, however it is the first we know of that can compare choice vs forcing with a money-metric outcome such as loan repayment.
+The fact that the Forced Commitment contract lowers financial costs for almost all clients, together with the fact that only 11\% choose it must mean that many consumers are choosing contracts with higher financial costs for themselves.
 We now present an estimation of how many consumers seem to be making a cost increasing choice, and how much money they seem to be leaving on the table.
@@
 
-\subsection{Boosted Classification Algorithm}
-
-\vspace{.2in}
-\noindent \textbf{Is there positive selection on treatment effects?} The previous exercise consisted of extrapolating treatment effects from the no-choice arms to the choice arm.
+\subsection{Relating Choice Probabilities to Benefits}
+
+The previous exercise consisted of extrapolating treatment effects from the no-choice arms to the choice arm.
 Here we do the reverse.
-First, we estimate a flexible model of take-up of the commitment-fee contract \textit{in the choice arm} using \textcolor{red}{gradient boosting classification}\footnote{\textcolor{red}{Results are robust to other classification methods like Random Forest, SVM, etc.}} and obtain for a client with characteristics $x_i$ a \textcolor{red}{calibrated} probability $P(x_i)$ of choosing the Forced Commitment contract.
-We then use this model to predict the counterfactual probability of a client with characteristics $x_j$ choosing the fee-commitment contract \textit{in the no choice-arms} if she would have been given the choice, what we call $\widehat{P(x_j)}$.\footnote{Our \textcolor{red}{gradient boosting} take-up model has a good out-of-sample fit with an out-of-sample AUC of \colorbox{yellow}{0.85}.
+First, we estimate a flexible model of take-up of the commitment-fee contract \textit{in the choice arm} using gradient boosting classification\footnote{Results are robust to other classification methods like Random Forest, SVM, etc.} and obtain for a client with characteristics $x_i$ a calibrated probability $P(x_i)$ of choosing the Forced Commitment contract.
+We then use this model to predict the counterfactual probability of a client with characteristics $x_j$ choosing the fee-commitment contract \textit{in the no choice-arms} if she would have been given the choice, what we call $\widehat{P(x_j)}$.\footnote{Our gradient boosting take-up model has a good out-of-sample fit with an out-of-sample AUC of \colorbox{yellow}{0.85}.
 (accuracy 97\% in-sample and 90\% out-of-sample)} Second, armed with this prediction in the forcing arms, we can ask the following: is it true that people with larger Forced Commitment contract treatment effects (i.e.
@@
 
-Based on the propensity score, we predict the two categories: choosers \& non-choosers, such that the proportions match the observed data, then we compute cumulative distribution functions of the heterogeneous conditional average treatment effect we estimated in Section \ref{TE_fee-forcing} using the Causal Random Forest.
+Based on the propensity score, can then represent the estimated HTEs from commitment against the likelihood to choose it in several ways.
+Most straightforward is Figure \ref{HTE_vs_propensity}, which plots the individually-estimated treatment effect from Forced versus Control treatments on the Y-axis, and the predicted probability of choosing commitment on the X axis.
+The HTEs are very strongly downward-sloping over the part of the distribution that has heterogeneity in predicted propensities.
+The sample with the lowest propensity of choosing commitment has a smoothed benefit of roughly twice those with a .2 change of choosing, measured both in terms of benefit/cost and in terms of probability of repayment.
+Hence the very large heterogeneous treatment effects are almost completely localized to the individuals who have the very lowest probability to select commitment.
+
+Second, we can predict the two categories: choosers \& non-choosers, such that the proportions match the observed data, then we compute cumulative distribution functions of the heterogeneous conditional average treatment effect we estimated in Section \ref{TE_fee-forcing} using the Causal Random Forest.
 Figure \ref{benefit_vs_choice_cdf} shows there is a first order stochastic dominance in treatment effects between the two predicted categories.
-This means those more likely to demand commitment are also those that had smaller benefits from commitment.
-This result is similar to \cite{Walters}, who finds that students that select into more effective schools are the ones with smaller treatment effects from attending.\footnote{\cite{Walters} uses distance to school as an instrumental variable for choice, while we use randomization to choice vs no-choice groups as our empirical strategy.}
-
-On an attempt to characterize the class that benefits more from commitment, we develop a finite mixture model with two latent types.
+This means those more likely to demand commitment are also those that had smaller benefits from commitment.\footnote{This result is similar to \cite{Walters}, who finds that students that select into more effective schools are the ones with smaller treatment effects from attending.
+That paper uses distance to school as an instrumental variable for choice, while we use randomization to choice vs no-choice groups as our empirical strategy.}
+
+A completely different approach to relating choice to HTEs arrives at a similar conclusion.
+We attempt to characterize the class that benefits more from commitment using a finite mixture model with two latent types.
 After estimation of this FMM, we find that the class more benefited from being forced is negatively correlated with demand for commitment (see Figure \ref{fmm_hte} in the appendix).
@@
 \newpage
-\subsection{Main treatment effects: Additional material}
 
@@
 \begin{table}[H]
-\caption{Decomposition of main treatment effects}
-\label{mechanisms}
+\caption{Main treatment effects}
+\label{main_impact_table}
 \begin{center}
@@
     \caption{Effect of CATE benefit vs predicted take-up}
-    \label{}
+    \label{HTE_vs_propensity}
     \begin{center}

### 2022-02-26 OA.tex
Analysis for email feb16
apr update and tot_tut analysis

@@
 
-\begin{table}[H]
-\caption{Survey's non-response balance}
-\label{balance_response}
-\begin{center}
-\scriptsize{\input{./Tables/balance_response.tex}}
-\end{center}
- \scriptsize This table shows whether the means of variables in the administrative dataset are different for those that respond the baseline survey vs those that do not.
+%\begin{table}[H]
+%\caption{Survey's non-response balance}
+%\label{balance_response}
+%\begin{center}
+%\scriptsize{\input{./Tables/balance_response.tex}}
+%\end{center}
+% \scriptsize This table shows whether the means of variables in the administrative dataset are different for those that respond the baseline survey vs those that do not.
 We use this as an assessment of external validity.
@@
 %\textit{Do file: } \texttt{balance\_response.do}
-\end{table}
+%\end{table}
 
@@
 \end{figure}
+
+\newpage
+\subsection{Main treatment effects: Additional material}
 
@@
 \end{figure}
-
-\newpage
-
-\begin{table}[H]
-\caption{Intermediate outcomes}
-\label{mechanisms}
-\begin{center}
-\scriptsize{\input{./Tables/mechanism.tex}}
-\end{center}
-
-%\textit{Do file: } \texttt{mechanisms.do}
-\end{table}
-
-\scriptsize {
-\noindent This table explores treatment effects in ``intermediate variables''.
-Each column represents a different dependent variable in an OLS regression, and each panel represents a different treatment arm-control comparison.
-All regressions include fixed effects for branch, day of week fixed effects, number of pawns at the time of pawning this particular one, number of different treatment arms experienced before pawning this particular one.
-$R^2$ are not reported, they were less than 0.04 for all but the last column which had $R^2$'s close to 0.6.
-The last row shows the mean of the dependent variable for the control group.
-Dependent variables are as follows: Column (1) measures the number of days elapsed from the pawning date to the first payment done.
-Column (2) records the number of payments done within 230 days of the pawn.
-Column (3) is the average size of the payments for each client in pesos.
-Column (4) is self-reported cost to get to the branch plus the imputed loss of a whole day of salary (using the minimum wage in Mexico) multiplied by the number of visits to the branch.
-Column (5) measures the number of days it took to recover the pawn, conditional on recovering.
-The dependent variable in Column (6) is a dummy =1 if the client paid any positive amount within 230 days of the pawn.
-For Columns (7) and (8) the dependent variable it is the sum of total payments done within 230 days of the pawn divided by the size of the loan, but column (8) includes as regressors a dummy=1 if the client recovered her pawn, and its interaction with treatment.
-}
-
-\vspace{3ex}
 
@@
 
-\subsubsection{LATE: TOT \& TUT}
+\subsubsection{LATE: ToT \& TuT}
 \vspace{.2in}
@@
  Recall that $Z_i$ is the observed, randomly assigned experimental allocation, where $Z_i=0$ denotes the control arm, $Z_i=1$ denotes the forced-fee arm, and $Z_i=2$ is the choice arm.
-Let $T_i$ be the unobserved choice type.
-$T_i=0$ when individual $i$ does not choose commitment  given the choice and $T_i=1$ when chooses commitment given the choice.
+Let $C_i$ be the unobserved choice type.
+$C_i=0$ when individual $i$ does not choose commitment  given the choice and $C_i=1$ when chooses commitment given the choice.
 Finally, $D_i = Z_i\times \mathds{1}(Z_i\neq 2) + T_i\times \mathds{1}(Z_i=2)$ is the observed treatment indicator, and $Y(d,z)$ is the potential outcome function for $d=0,1$, and $z=0,1,2$.
 
- To identify assortative selection we first need to estimate the following quantities: $\mathbb{E}(Y_1-Y_0\;|\;T=1)$ the Treatment on the Treated (TOT), and $\mathbb{E}(Y_1-Y_0\;|\;T=0)$ the Treatment on the Untreated (TUT).
+ To identify assortative selection we first need to estimate the following quantities: $\mathbb{E}(Y_1-Y_0\;|\;C=1)$ the Treatment on the Treated (ToT), and $\mathbb{E}(Y_1-Y_0\;|\;C=0)$ the Treatment on the Untreated (TuT).
 
@@
  \begin{assumption}[Exclusion Restriction]
-$Z$ only affects $Y$ through its effect on $D$ : $Y(d,z) = Y(d)$
+$Z$ only affects $Y$ through its effect on $D$ : $C(d,z) = C(d)$
  \end{assumption}
@@
   \begin{assumption}[Independence Assumption]
-$Z \perp (Y_0, Y_1, T)$
+$Z \perp (Y_0, Y_1, C)$
  \end{assumption}
 
-The following intermediate Lemmas will help us derive that both TOT and TUT are point identified.
+The following intermediate Lemmas will help us derive that both ToT and TuT are point identified.
 
 \begin{lem}
-$\Pr(T=1) = \E[D\;|\;Z=2]$
+$\Pr(C=1) = \E[D\;|\;Z=2]$
 \end{lem}
 \begin{proof}
-Since $T\perp Z$, 
-$$\E[D\;|\;Z=2] = \E[Z\times \mathds{1}(Z\neq 2)+ T\times\mathds{1}(Z=2)\;|Z=2] = \E[T\;|\;Z=2] = \E[T] = \Pr(T=1)$$
+Since $C\perp Z$, 
+$$\E[D\;|\;Z=2] = \E[Z\times \mathds{1}(Z\neq 2)+ C\times\mathds{1}(Z=2)\;|Z=2] = \E[C\;|\;Z=2] = \E[C] = \Pr(C=1)$$
 \end{proof}
@@
 \begin{align*}
-\E[Y\;|\;Z=0] =& \E[\mathds{1}(Z=0)Y_0+\mathds{1}(Z=1)Y_1+\mathds{1}(Z=2)\{(1-T)Y_0+TY_1\})\;|\;Z=0]\\   
+\E[Y\;|\;Z=0] =& \E[\mathds{1}(Z=0)Y_0+\mathds{1}(Z=1)Y_1+\mathds{1}(Z=2)\{(1-C)Y_0+CY_1\})\;|\;Z=0]\\   
 =&\E[Y_0\;|\;Z=0] = \E[Y_0]
@@
 \begin{lem}
-$\E[Y_0\;|\;T=0] = \E[Y\;|\; D=0,Z=2]$
+$\E[Y_0\;|\;C=0] = \E[Y\;|\; D=0,Z=2]$
 \end{lem}
 \begin{proof}
-If $Z=2$, then $D=0$ if and only if $T=0$. Hence,
-\[\E[Y\;|\;D=0, Z=2] = \E[Y_0\;|\;D=0, Z=2] = E[Y_0\;|\;T=0, Z=2]=\E[Y_0\;|\;T=0]\]
-since $Y_0\perp T\;|\;Z$
+If $Z=2$, then $D=0$ if and only if $C=0$. Hence,
+\[\E[Y\;|\;D=0, Z=2] = \E[Y_0\;|\;D=0, Z=2] = E[Y_0\;|\;C=0, Z=2]=\E[Y_0\;|\;C=0]\]
+since $Y_0\perp C\;|\;Z$
 \end{proof}
@@
 \begin{lem}
-$\E[Y_1\;|\;T=1] = \E[Y\;|\; D=1,Z=2]$
+$\E[Y_1\;|\;C=1] = \E[Y\;|\; D=1,Z=2]$
 \end{lem}
 \begin{proof}
-If $Z=2$, then $D=1$ if and only if $T=1$. Hence,
-\[\E[Y\;|\;D=1, Z=2] = \E[Y_1\;|\;D=1, Z=2] = E[Y_1\;|\;T=1, Z=2]=\E[Y_1\;|\;T=1]\]
-since $Y_1\perp T\;|\;Z$
+If $Z=2$, then $D=1$ if and only if $C=1$. Hence,
+\[\E[Y\;|\;D=1, Z=2] = \E[Y_1\;|\;D=1, Z=2] = E[Y_1\;|\;C=1, Z=2]=\E[Y_1\;|\;C=1]\]
+since $Y_1\perp C\;|\;Z$
 \end{proof}
 
-\begin{theorem} $\E[Y_1-Y_0\;|\; T=1]$ is point identified
+\begin{theorem} $\E[Y_1-Y_0\;|\; C=1]$ is point identified
 \end{theorem}
@@
 \begin{proof}
-Since $\E[Y_1\;|\; T=1] = \E[Y\;|\; D=1, Z=2]$ by Lemma 5, it suffices to show that $\E[Y_1\;|\;T=0]$ is point identified. By iterated expectations:
-\[E[Y_0] = \E_T\E[Y_0\;|\;T] = (1-p)\E[Y_0\;|\;T=0]+p\E[Y_0\;|\;T=1]\]
-where $p:=\E[T]=\Pr(T=1)$, and re-arranging,
-\[\E[Y_0\;|\;T=1] = \frac{1}{p}\left(E[Y_0] -(1-p)\E[Y_0\;|\;T=0]\right)\]
+Since $\E[Y_1\;|\; C=1] = \E[Y\;|\; D=1, Z=2]$ by Lemma 5, it suffices to show that $\E[Y_1\;|\;C=0]$ is point identified. By iterated expectations:
+\[E[Y_0] = \E_C\E[Y_0\;|\;C] = (1-p)\E[Y_0\;|\;C=0]+p\E[Y_0\;|\;C=1]\]
+where $p:=\E[C]=\Pr(C=1)$, and re-arranging,
+\[\E[Y_0\;|\;C=1] = \frac{1}{p}\left(E[Y_0] -(1-p)\E[Y_0\;|\;C=0]\right)\]
 Finally, substituting the result of Lemmas 1, 2, and 4, we obtain
-\[\E[Y_0\;|\;T=1] =\frac{1}{\E[D\;|\;Z=2]}\left\{\E[Y\;|\;Z=0]-(1-\E[D\;|\;Z=2])\E[Y\;|\;D=0, Z=2]\right\}\]
+\[\E[Y_0\;|\;C=1] =\frac{1}{\E[D\;|\;Z=2]}\left\{\E[Y\;|\;Z=0]-(1-\E[D\;|\;Z=2])\E[Y\;|\;D=0, Z=2]\right\}\]
 and the RHS is a function of observed data only.
@@
 
-\begin{theorem} $\E[Y_1-Y_0\;|\; T=0]$ is point identified
+\begin{theorem} $\E[Y_1-Y_0\;|\; C=0]$ is point identified
 \end{theorem}
@@
 \begin{proof}
-Since $\E[Y_0\;|\; T=0] = \E[Y\;|\; D=0, Z=2]$ by Lemma 4, it suffices to show that $\E[Y_0\;|\;T=1]$ is point identified. By iterated expectations:
-\[E[Y_1] = \E_T\E[Y_1\;|\;T] = (1-p)\E[Y_1\;|\;T=0]+p\E[Y_1\;|\;T=1]\]
-where $p:=\E[T]=\Pr(T=1)$, and re-arranging,
-\[\E[Y_1\;|\;T=0] = \frac{1}{1-p}\left(E[Y_1] -p\E[Y_1\;|\;T=1]\right)\]
+Since $\E[Y_0\;|\; C=0] = \E[Y\;|\; D=0, Z=2]$ by Lemma 4, it suffices to show that $\E[Y_0\;|\;C=1]$ is point identified. By iterated expectations:
+\[E[Y_1] = \E_C\E[Y_1\;|\;C] = (1-p)\E[Y_1\;|\;C=0]+p\E[Y_1\;|\;C=1]\]
+where $p:=\E[C]=\Pr(C=1)$, and re-arranging,
+\[\E[Y_1\;|\;C=0] = \frac{1}{1-p}\left(E[Y_1] -p\E[Y_1\;|\;C=1]\right)\]
 Finally, substituting the result of Lemmas 1, 3, and 5, we obtain
-\[\E[Y_1\;|\;T=0] =\frac{1}{1-\E[D\;|\;Z=2]}\left\{\E[Y\;|\;Z=1]-\E[D\;|\;Z=2]\E[Y\;|\;D=1, Z=2]\right\}\]
+\[\E[Y_1\;|\;C=0] =\frac{1}{1-\E[D\;|\;Z=2]}\left\{\E[Y\;|\;Z=1]-\E[D\;|\;Z=2]\E[Y\;|\;D=1, Z=2]\right\}\]
 and the RHS is a function of observed data only.
@@
 \begin{figure}[H]
-    \caption{Bootstrap inference for the difference between TOT-TUT}
+    \caption{Bootstrap inference for the difference between ToT-TuT}
     \label{bootstrap_tot_tut}
@@
     \end{center}
-     \scriptsize  Given that all of the arms are effectively randomly sampled form the same pool, we can also estimate the TOT and TUT with the pooled regression: $Y_i = \beta_0\mathds{1}(Z_i=0)+\beta_1\mathds{1}(Z_i=1)+\beta_2\mathds{1}(Z_i=2)+ \epsilon_i$, and then this test statistic just becomes the F-test on $\frac{\widehat{\beta_2}-\widehat{\beta_0}}{p}$ for the TOT, $\frac{\widehat{\beta_1}-\widehat{\beta_2}}{1-p}$ for the TUT, and an F-test on the difference between these two quantities to test whether the gains are different between compliers and non-compliers.
+     \scriptsize  Given that all of the arms are effectively randomly sampled form the same pool, we can also estimate the ToT and TuT with the pooled regression: $Y_i = \beta_0\mathds{1}(Z_i=0)+\beta_1\mathds{1}(Z_i=1)+\beta_2\mathds{1}(Z_i=2)+ \epsilon_i$, and then this test statistic just becomes the F-test on $\frac{\widehat{\beta_2}-\widehat{\beta_0}}{p}$ for the ToT, $\frac{\widehat{\beta_1}-\widehat{\beta_2}}{1-p}$ for the TuT, and an F-test on the difference between these two quantities to test whether the gains are different between compliers and non-compliers.
 Recognizing the stochastic nature of the compliance rate, we also bootstrap this quantity before running the previous regression.
-The red line shows the point estimate for the difference between TOT-TUT, and the gray bar in the x-axis shows a 95\% confidence interval for this difference.
-Panel (a) shows the difference between the TOT and TUT without any controls, while panel (b) and (c) adds admin controls and admin + survey controls respectively.
+The red line shows the point estimate for the difference between ToT-TuT, and the gray bar in the x-axis shows a 95\% confidence interval for this difference.
+Panel (a) shows the difference between the ToT and TuT without any controls, while panel (b) and (c) adds admin controls and admin + survey controls respectively.
           %\footnotesize{ \textit{Do file: }  \texttt{tot\_tut.do}}
@@
 \begin{figure}[H]
-     \caption{TOT-TUT CDF}
+     \caption{ToT-TuT CDF}
      \label{tot_tut_ecdf}
@@
     \scriptsize
-       Equipped with estimates for the TOT and TUT for each individual $i$ from an Instrumental Random Forest we compute the ECDF for this quantities.
-The solid line is the ECDF for the TOT, the dashed line is the ECDF for the TUT, and the dotted line plots the difference between the TOT and the TUT - the blue dashed line in the x-axis shows the points where this difference is significant.
-The bold black interval at the bottom of the graph is the mean for the TOT distribution (0.07), while the gray interval shows the mean for the TUT distribution (0.10).
+       Equipped with estimates for the ToT and TuT for each individual $i$ from an Instrumental Random Forest we compute the ECDF for this quantities.
+The solid line is the ECDF for the ToT, the dashed line is the ECDF for the TuT, and the dotted line plots the difference between the ToT and the TuT - the blue dashed line in the x-axis shows the points where this difference is significant.
+The bold black interval at the bottom of the graph is the mean for the ToT distribution (0.07), while the gray interval shows the mean for the TuT distribution (0.10).
 
@@
     \end{center}
-    \scriptsize This figure serves as a test for the exclusion restriction in the point identification for the TOT and the TUT.
+    \scriptsize This figure serves as a test for the exclusion restriction in the point identification for the ToT and the TuT.
 It shows the effect on the effective cost/loan ratio for the forced-fee arm and the choice arm, together with the decomposition of the choosers and non-choosers.
@@
 
-\begin{figure}[H]
-        \caption{Frequency of renewals}
-    \label{ref_dist}
-    \begin{center}
-        \centering
-        \includegraphics[width=0.60\textwidth]{Figuras/ref_dist.pdf}
-    \end{center}
-     \scriptsize  This Figure shows the occurrence and frequency of renewals.
+% \begin{figure}[H]
+%         \caption{Frequency of renewals}
+%     \label{ref_dist}
+%     \begin{center}
+%         \centering
+%         \includegraphics[width=0.60\textwidth]{Figuras/ref_dist.pdf}
+%     \end{center}
+%      \scriptsize  This Figure shows the occurrence and frequency of renewals.
 It locates in time, respective to the day the loan started, when the renewal occurs for both the first and second renewal.
 Note that the first renewal is concentrated around 100 days, while the second is concentrated around the 200 days, corresponding to the first and second cycle.
-     %\textit{Do file: }  \texttt{ref_\dist.do}
-\end{figure}
-
-\begin{figure}[H]
-        \caption{Probability of recovery by arm}
+%      %\textit{Do file: }  \texttt{ref_\dist.do}
+% \end{figure}
+
+\begin{figure}[H]
+    \caption{Histogram of payments}
+    \label{hist_payments}
+    \begin{center}
+    \begin{subfigure}{0.31\textwidth}
+        \caption{Status-quo}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_payments_sq.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.31\textwidth}
+        \caption{Forced commitment}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_payments_fc.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.31\textwidth}
+        \caption{Choice commitment}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_payments_cc.pdf}
+    \end{subfigure}    
+        \begin{subfigure}{0.31\textwidth}
+        \caption{Forced soft}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_payments_fs.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.31\textwidth}
+        \caption{Choice soft}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_payments_cs.pdf}
+    \end{subfigure} 
+    \end{center}
+     \scriptsize
+      %\footnotesize{ \textit{Do file: }  \texttt{hist\_payments.do}}
+\end{figure}
+
+\begin{figure}[H]
+        \caption{Survival graphs}
     \label{survival_graph}
     \begin{center}
-        \centering
-        \includegraphics[width=0.60\textwidth]{Figuras/survival_graph_unpledge.pdf}
+   \begin{subfigure}{0.45\textwidth}
+        \caption{Closed contracts}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/survival_graph_ended.pdf}
+    \end{subfigure} 
+       \begin{subfigure}{0.45\textwidth}
+        \caption{Recovery}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/survival_graph_unpledge.pdf}
+    \end{subfigure} 
     \end{center}
@@
 %\end{figure}
-
-\begin{comment}
-\begin{figure}[H]
-        \caption{Histogram of payments}
-    \label{HistPayments}
-    \begin{center}
-    \begin{subfigure}{.31\textwidth}
-    \caption{Control}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_payments_pro_1.pdf}
-    \end{subfigure}
-    \begin{subfigure}{.31\textwidth}
-    \caption{Forcing - fee}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_payments_pro_2.pdf}
-    \end{subfigure}   
-     \begin{subfigure}{.31\textwidth}
-    \caption{Forcing - promise}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_payments_pro_3.pdf}
-    \end{subfigure}  
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - fee}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_payments_pro_4.pdf}
-    \end{subfigure}  
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - fee - SQ}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_payments_pro_6.pdf}
-    \end{subfigure}    
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - fee - NSQ}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_payments_pro_7.pdf}
-    \end{subfigure}    
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - promise}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_payments_pro_5.pdf}
-    \end{subfigure}  
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - promise - SQ}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_payments_pro_8.pdf}
-    \end{subfigure}    
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - promise - NSQ}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_payments_pro_9.pdf}    
-    \end{subfigure}        
-    \end{center}
-     \footnotesize \textit{Notes: } The x-axis shows the elapsed days between initial date and current movement.
-      \footnotesize{ \textit{Do file: }  \texttt{hist\_payments.do}}
-\end{figure}
-\end{comment}
 

### 2022-02-26 Tables/Attrition.tex
apr update and tot_tut analysis

@@
 Number of branch-day pawns & 31    & 31    & 37    & 0.16  &       & 32    & 34    & 0.57 \\
-      & (2.2) & (2.3) & (2.6) &       &       & (2.4) & (1.7) &  \\
-Survey response rate & 0.77  & 0.75  & 0.77  & 0.73  &       & 0.8   & 0.79  & 0.44 \\
+      & (2.2) & (2.3) & (2.6) &       &       & (2.4) & (1.8) &  \\
+Survey response rate & 0.77  & 0.75  & 0.77  & 0.74  &       & 0.8   & 0.79  & 0.5 \\
       & (0.02) & (0.03) & (0.02) &       &       & (0.02) & (0.02) &  \\
-\% ended up pawning & 0.97  & 0.96  & 0.97  & 0.59  &       & 0.98  & 0.99  & 0.11 \\
-      & (0.004) & (0.008) & (0.006) &       &       & (0.004) & (0.003) &  \\
+\% ended up pawning & 0.98  & 0.97  & 0.98  & 0.43  &       & 0.99  & 0.99  & 0.49 \\
+      & (0.004) & (0.007) & (0.006) &       &       & (0.003) & (0.003) &  \\
 \midrule
-Obs   & 2585  & 2465  & 3406  &       &       & 2143  & 2753  &  \\
+Obs   & 2600  & 2484  & 3435  &       &       & 2157  & 2768  &  \\
 \bottomrule

### 2022-02-26 donde.tex
apr update and tot_tut analysis

@@
 In one arm all borrowers were asked to commit to make three monthly payments instead of a single balloon payment, but no external reminders or fees were imposed.
-In a second borrowers were given the ability to choose whether to engage in this form of soft commitment.
+In a second arm borrowers were given the ability to choose whether to engage in this form of soft commitment.
 Both of these arms are completely ineffective, suggesting that it is the combination of external imposition of the contract along with the teeth provided by the reminder and fees that generate the savings to borrowers relative to the status quo contract.
@@
 One potential explanation for high default is that clients are really just knowingly selling their gold piece through a pawn contract on which they intend to default.
-This appears unlikely for several reasons: (a) clients can easily sell the gold and obtain a higher amount of instant cash at gold buying stores located close to almost all our pawnshop branches (see Figure \ref{GoldBuyers}), (b) the reported subjective value of the pawn is larger than the loan size for 86\% of clients, (c) among those that lose their pawn 48\% paid a positive amount towards its recovery and on average paid 42\% of the value of their loan (see Figure \ref{proxy_naive} in Appendix) --- this can only be rationalized if they expected to recover their pawn, and (d) 74\% of borrowers report in our baseline survey that they anticipate recovering the pawn at the time they take the loan.
+This appears unlikely for several reasons: (a) clients can easily sell the gold and obtain a higher amount of instant cash at gold buying stores located close to almost all our pawnshop branches (see Figure \ref{GoldBuyers}), (b) the reported subjective value of the pawn is larger than the loan size for 86\% of clients, (c) among those that lose their pawn 48\% paid a positive amount towards its recovery and on average paid 42\% of the value of their loan (see Figure \ref{proxy_naive} in Appendix) --- this can only be rationalized if they expected to recover their pawn, and (d) 74\% of borrowers report a 100\% probability of repaying their loan (and 98\% at least a 50\% chance of repaying) in our baseline our baseline survey at the time they take the loan.
+So it does appear that a large share of default is not `planned' in a simple ex-ante sense.
 High default could be also detrimental from the lender's point of view since it may reduce the likelihood that the client becomes a return costumer.
@@
 
-\subsection{Measurement of the Cost to Pawning} \label{Data}
+\subsection{Measurement of the Cost to Pawning} \label{costs}
 
@@
 We surveyed 10,437 clients, and the survey response rate is 78\%.\footnote{The Appendix \ref{baseline_survey} transcribes the questionnaire in English.} %\footnote{We also surveyed clients before and after the experiment, so our survey covers a larger sample that we are not using in this paper.}.
-%Survey response rate is 78\%, and response is not related to admin data observables (details in Table \ref{balance_response} in the Appendix).
-
-%We worked in 6 branches of Lender $P$, of differing size and location, although for ease of implementation all of them in Mexico city.
-For these 6 branches we have two types of data, administrative data and survey data we collected for the experiment.
 
@@
 
-% Empirically, attrition was not a problem.
-Table \ref{SS} shows that the number of pawns per branch per day across treatment arms is statistically identical.
-The last column of the table displays the p-value of an $F$ test of equality of means across arms and shows we cannot reject equality for any of the variables (p-value=0.38 for the number of pawns per day per branch).
-There is no evidence for selection across treatment arms for any of the admin or survey variables.
-
-%One concern was that after learning the conditions of the contract, clients could decide not to pawn.
-If they were deferentially responsive to the different conditions, we could end up having different kinds of clients in the different arms.
-It turns out this was not the case.
-
 Table \ref{attrition_table} presents tests for these core forms of attrition.
@@
 The survey response rate is broadly similar across arms (about 77 percent) as is the fraction of those surveyed who then go on to take a loan (97 percent).
-
-%First, we cannot reject that the number of pawns per branch-day is the same across arms (Panel A).
-Panel C shows that about 98\% of people who answered our baseline survey also pawned, and that this ratio is balanced across arms.
-Second, not only are the number and shares of pawns the same across arms, but also the characteristics of clients and their pawned pieces are statistically the same across arms.
-Panel A of Table \ref{SS} tests this with administrative data, while
 
@@
 
-the comparison of the \textit{Commitment Choice} arm to the \texit{Control} arm provides the test of self-selection that is standard in the behavioral literature.
-A lack of impact in this comparison would be consistent either with a population of neo-classical borrowers, for whom the commitment feature is superfluous, or with a population of time-inconsistent borrowers who lack sophistication over their own behavioral problems.
-The key to distinguishing these two stories is the treatment effect of commitment on those who would not choose it; this counterfactual is revealed through the comparison of the \textit{Forced Commitment} arm to the \textit{Control}.
-So while the forcing of commitment cuts against the grain of a behavioral literature that has largely promoted `nudges', it reveals important additional information that will be particularly relevant in borrower populations that are both hyperbolic and naive.
-
-As a starting point for the empirical analysis, in the Choice arm only 11\% of individuals offered the product selected it.
+The comparison of the Commitment Choice arm to the Control arm provides the test of self-selection that is standard in the behavioral literature.
+A lack of impact in this comparison would be consistent either with a population of neo-classical borrowers, for whom the commitment feature is superfluous, or with a population of time-inconsistent borrowers who lack sophistication over their own behavioral problems and so do not choose commitment even though they would benefit from it.
+The key to distinguishing these two stories is the treatment effect of commitment on those who would not choose it; this counterfactual is revealed through the additional impact of the Forced Commitment arm over the Choice arm.
+So while the forcing of commitment cuts against the grain of a behavioral literature that has largely promoted `nudges', it reveals important additional information that may be particularly relevant in borrower populations that are both hyperbolic and naive.
+
+In the Choice arm, only 11\% of individuals offered the product selected it.
 This is initial evidence either that we are dealing with a population of largely time consistent individuals who do not need commitment, or of a population with many naive individuals who do not know that they need it.
@@
 
-We pose this question using the standard Intention to Treat analysis equation (\ref{basic_reg}) across arms.
+We pose these comparative questions using the standard pooled experimental equation (\ref{basic_reg}):
 
@@
 
-\noindent where $i$ refers to client, $j$ indexes branch, $T_{i}^F$ and $T_{i}^C$ are indicator variables for receiving the Fixed or Choice arms, $X_{ij}$ are branch and day-of-week fixed effects.\footnote{There is a minority of of clients that pawned again and got assigned a different treatment.
-Results are robust to excluding them.
-In the regressions we include them and add a dummy indicating clients who has more than one treatment in the experimental period.} We cluster errors at the branch-day level.
+\noindent where $i$ refers to client, $j$ indexes branch, $T_{i}^F$ and $T_{i}^C$ are indicator variables for receiving the Forced or Choice arms, $X_{ij}$ are branch and day-of-week fixed effects.\footnote{There is a minority of of clients that pawned again and got assigned a different treatment.
+Results are robust to excluding them, or to using only the first treatment status assigned, as we show later.
+In the main regressions we include them and add a dummy indicating clients who has more than one treatment in the experimental period.} We cluster errors at the branch-day level, the unit of treatment assignment.
 %\footnote{If we restrict ourselves to pieces that fall in a single-arm (64\%), then treatment reduces the financial cost by 5.7\%, increases the likelihood of recovering their pawn by 35\%, and increases the likelihood of repeat business by 66\%.}.
-Our main outcome variables $y_{ij}$ are measures of financial cost in pesos as defined in Section \ref{FC_def}, which we further decompose into its component costs:  payments to capital, fees, interest, and the cost of losing the pawn.
+Our main outcome variables $y_{ij}$ are measures of financial cost in pesos as defined in Section \ref{costs}, which we further decompose into its component costs:  payments to capital, fees, interest, and the cost of losing the pawn.
 We then cast each of these costs as an Annual Percentage Rate (APR).
 as well as an indicator variable for client $i$ losing her pawn.
-In this subsection $T_{i}$ is an indicator for $i$ having got the \textit{fee-forcing} contract, and $\beta$ estimates the average treatment effect.%\footnote{This is an ATE and not just an ITT since take up of treatment is 100\%.}
+$\beta^F$ estimates the Average Treatment Effect of the Forced arm (since compliance is 100\%), and  $\beta^C$ the Intention to Treat of the Choice arm (since it is not).
 
@@
 
-The Intention to Treat (ITT) results, presented in Table \ref{main_impact_table} and graphically in Figure \ref{main_te}, are extremely stark.
-The Choice arm fails to deliver improvements on any measure (with the exception of an increase in fees, for which we are very powered since this outcome is always zero in the control).
-In sharp contrast, the Forced Commitment arm yields very strongly significant decreases in the financial cost of loans to clients.
-Despite causing a 106 peso increase in payments to capital and a 28 peso increase in fees, the Forced arm leads to a 100 peso decline in interest payments and an enormous decline in the expected pawn losses (almost 500 pesos), driven by a 12\% decrease in the probability of default.
-The bottom panel of the figure casts these costs as APRs, and shows that while the Choice arm actually leads to a slight \textit{increase} in the APR, the Forced arm decreases the effective annualized interest rate of pawn lending by 40\%.
-Figure \ref{main_te} gives the standardized effect sizes (in standard deviations) of the two main study arms for three outcomes:  default, the financial cost of the loan, and the effective interest rate paid to acquire the borrowed capital.
-Very clearly, the Forced arm is significant for all three outcomes, with very substantial treatment effects in magnitudes for default and APR, and the commitment arm is never significant.
-In other words, voluntary commitment is ineffective but the use of forced commitment saves the average borrower an amount of money almost twice the APR of a normal US credit card loan.
+The core results, presented in Table \ref{main_impact_table} and graphically in Figure \ref{main_te}, are extremely stark.
+The Choice arm fails to deliver significant changes in any measure (with the exception of an increase in fees, for which we are highly powered since this outcome is always zero in the control).
+In sharp contrast, the Forced Commitment arm yields strongly significant decreases in the financial cost of loans to clients.
+Despite causing an increase in payments to capital and fees, the Forced arm leads to a sharp decrease in overall costs of borrowing, driven by a 12 percentage point decrease in the probability of default (more than a 25\% reduction off a base of 44\% default).
+The bottom panel of the figure casts these costs as APRs, and shows that while the Choice arm actually leads to a slight \textit{increase} in the APR, the Forced arm decreases the effective annualized interest cost of pawn lending by 40 percentage points.
+A credit product that has an effective average APR of 249\% in the status quo arm is reduced to a cost of 209\% through the imposition of a more regularized payment structure.
+
+Table \ref{main_impact_table} decomposes the savings from the Forced and Choice arms into their component parts.
+The Forced arm increases fees very significantly relative to a control mean of 0, but the monetary value of the fees imposed is small (28 pesos).
+Payments towards capital also rise by 167 pesos because the arm is so effective at improving the fraction of individuals actually repaying their loans.
+Because the regular repayment structure moves the timing of payment forward it saves borrowers an average of 109 pesos in interest costs.
+The very large majority of the overall treatment effect, however, stems from the 491 pesos in retained collateral value induced by the falling probability of default.
+
+Figure \ref{main_te} gives the  effect sizes (in standard deviations) of the two main study arms for three outcomes:  default, the financial cost of the loan, and the effective interest rate paid to acquire the borrowed capital.
+Very clearly, the Forced arm is significant for all three outcomes, with very substantial treatment effects in magnitudes for default and APR, and the commitment arm is never significant.\footnote{The slight increase in APR for the Choice arm seen in this picture arises from the fact that the APR calculation has the arm-specific loan size in the denominator, and the loans in the Choice arm turn out to be slightly larger on average than the Control.}    In other words, voluntary commitment is ineffective but the use of forced commitment saves the average borrower an amount of money almost twice the APR of a normal US credit card loan.
 
@@
 However the percentage of the loan paid is not larger for those that end up losing the pawn (first row of column 8).
-
-While the mechanical financial cost and APR incurred by pawn-shop clients are key outcomes, it is worth deepening the analysis with a set of additional drivers relevant to the subjective costs perceived by borrowers.
-Figure \ref{robustness_fc} shows the results of these robustness checks.
+This last point is critical; this intervention has the potential to do financial harm if it caused individuals to make more payments on loans for which they would end up defaulting.
+This result shows that instead what the Forced arm does is allow individuals who would have made partial payment and defaulted to instead recover their pawn.
+
+Can we overturn these results by incorporating additional factors that would explain the subjective choices made by individuals?
+We now examine whether features such as the perceived value of the pawn, travel costs, or discounting might alter the story of comparative impact.
+Figure \ref{robustness_fc} shows the results of these robustness checks, and the numbers underlying the figure are shown in Table \ref{table_robustness_fc}.
 First, rather than using the appraised value of the pawn from the lender, we can assess costs using the subjective value of the pawn reported by the borrower.
+Because borrower valuations are both larger on average and much more variable, this adjustment causes the average impact on financial cost to rise, and the impact on APR in standard deviations to shrink, but both remain significant.
 Second, because the Commitment contract requires more frequent visits to the branch, there are travel costs incurred relative to the status quo payment structure that we can include in the costs of commitment.
-For each visit we add the self-reported transport cost plus a whole day's wage, multiplied by the number of visits.
-Adding a whole day's wage may exaggerate cost, but we still observe a reduction of this more comprehensive measure of cost caused by the frequent payment contract, although we lose more than 1/3 of the observations and some precision from missing data on transportation costs.
+For each visit we add the self-reported transport cost (or the mean if we are missing this from the individual survey) plus a whole day's wage, multiplied by the number of additional visits from Table \ref{mechanisms}.
+Adding a whole day's wage may exaggerate cost, but we still observe a reduction of this more comprehensive measure of cost caused by the frequent payment contract.
 Finally, we can adjust for the fact that the early payment induced by the commitment contract actually reduces the effective liquidity received by borrowers.
@@
 So our final adjustment removes the saved interest payments from the calculation of the benefits across arms.
-The figure shows the effects of each of these adjustments on the estimate of financial cost and APR, and illustrates that even when we make all of these adjustment simultaneously the Forced arm generates benefits of 0.11 standard deviations.
-
-A simple way to move towards a consideration of borrower welfare is the conjecture that if clients exposed to the installment contract like it, they will be more likely to come back vis-a-vis those that got status quo contract.\footnote{\cite{Laibson2018} hypothesizes that consumers use ``experienced utility'' as a guide to make future purchases in this way.} This is indeed what we find in the data.
-We consider this outcome in Table \ref{X}.
+The figure shows the effects of each of these adjustments on the estimate of financial cost and APR, and illustrates that even when we make all of these adjustment simultaneously the Forced arm generates benefits of 0.11 standard deviations, significant at the 95\% level.
+
+Another way to push the analysis towards a consideration of borrower welfare is the conjecture that if clients exposed to the installment contract like it, they will be more likely to come back vis-a-vis those that got status quo contract.\footnote{\cite{Laibson2018} hypothesizes that consumers use ``experienced utility'' as a guide to make future purchases in this way.} This is indeed what we find in the data.
+We consider this outcome in Table \ref{repeat_loans}.
 We can first ask whether the individual ever takes a loan after the initial study loan, an analysis which is simply experimental.
@@
 
+\textcolor{red}{A final important robustness check is to consider clients who pawn more than once within the experiment.
+38\% of borrowers take more than one loan within the study period, and 19\% are assigned multiple treatment statuses on their different loans.
+The issue of sequential endogenous treatments has been extensively studied in the context of school lotteries, where the convention is to use the treatment status from the first exposure \citep{abdulkadirouglu2011accountability}.\footnote{That context provides a particularly severe version of the endogenous re-entry problem because only the losers from initial lotteries re-enter subsequent ones.
+Our selection problem is less draconian, but still potentially relevant since we do find treatment effects on pace of repayment and of pawning again}  So in Table \ref{multiple_loans} we provide two straightforward robustness checks for the influence of this problem.
+Columns 1-2 repeat the main analysis of financial cost and APR using the baseline approach from our main results, including dummies for the order of pawns for an individual, essentially making the identification within-order.
+Columns 3-4 drop all loans other than the first, and Columns 5-6 pursue the ITT strategy of always assigning the first treatment status to all subsequent pawns.
+The core treatment effects are robust to any of these ways of handling repeat pawning, and the effect on the APR actually become larger.
+}
+
 \subsection{Soft Commitment}
@@
 Nonetheless, we find Soft Commitment, whether chosen or induced, to be completely ineffective in this environment.
-Figure \ref{fc_pro5}(a) finds that assigning clients to the choice-promise condition has a zero effect on financial cost on average (circles).
+Table \ref{impact_soft} and  Figure \ref{fc_pro5}(a) finds that assigning clients to the choice-promise condition has a zero effect on financial cost on average (circles).
 We see no difference even for the endogenous group that \textit{chose} to promise (squares).
@@
 
+This is not the first paper to find low demand for commitment, however it is the first we know of that can compare choice vs forcing with a money-metric outcome such as loan repayment.
+The fact that the Forced Commitment contract lowers financial costs for almost all clients, together with the fact that only 11\% choose it must mean that many consumers are choosing contracts with higher financial costs for themselves.
+We now use several different techniques to shed further light on the idea that the wrong people are choosing commitment.
+
 \section{Exploring the Importance of Paternalism}
@@
 
+\subsection{Treatment Effects for Compliers and Non-Compliers}
+
+A unique feature of our design is the randomized assignment to treatment, control, and choice of treatment.
+This structure allows us to observe the average value of both the treated and untreated potential outcomes, as well as the selection into treatment that would occur under choice.
+A starting point for how to exploit this structure is to apply the logic usually used to estimate the Treatment on the Treated (ToT) to also recover the Treatment on the Untreated (TuT).
+This approach assumes nothing about the decision to choose (other than random sampling generating counterfactual compliance rates that would have been the same in every arm), but imposes three exclusion restriction-style assumptions typical of Local Average Treatment Effect (LATE) analysis.
+Namely, a) the typical assumption that an individual not choosing the treatment has the same potential outcome as one not offered it, then b) the mirror image assumption for the Forcing arm that an individual forced to take Commitment has the same potential outcome as an individual freely choosing it, and c) no spillovers from chooser to non-choosers in the choice arm.\footnote{\hl{For robustness we also try a Manski-type monotone IV approach with similar results.}}
+
+More formally, let $Z_i$ be the observed, randomly assigned experimental allocation, where $Z_i=0$ denotes the control arm, $Z_i=1$ denotes the Forced arm, and $Z_i=2$ is the Choice arm.
+Let $C_i$ be the choice type; $C_i=0$ when individual $i$ does not choose commitment and $C_i=1$ when chooses commitment, observed only in the Choice arm.
+A fraction $p$ of individuals chooses the treatment in the Choice arm.
+Finally, $D_i = Z_i\times \mathds{1}(Z_i\neq 2) + C_i\times \mathds{1}(Z_i=2)$ is the observed treatment indicator, and $Y(d,z)$ is the potential outcome function for $d=0,1$, and $z=0,1,2$.
+
+To test the difference between gains for choosers versus gains from non-choosers we need to identify $\mathbb{E}[Y_1-Y_0\;|\;C=1]$ (the Treatment on the Treated), and $\mathbb{E}[Y_1-Y_0\;|\;C=0]$ (the Treatment on the Untreated).
+The observed outcome in the Choice arm is the weighted average of the treated and untreated outcomes; $p \times\mathbb{E}[Y_1\;|\;C=1] + (1-p)\times\mathbb{E}[Y_0\;|\;C=0]$.
+Given assumptions a) and c) above we can recover the ToT from the difference between the Choice and Control arms as is standard, and then symmetrically we can invoke b) and c) to recover the TuT from the difference between the Forced and Choice arms as follows:
+
+\begin{align*}
+ToT \equiv \mathbb{E}[Y_1 - Y_0 \;\mid\; C=1]  &=   \frac{\mathbb{E}[Y \;\mid\; Z=2] - \mathbb{E}[Y \;\mid\; Z=0)}{p} \\
+TuT \equiv \mathbb{E}[Y_1 - Y_0 \;\mid \;C=0]  &=  \frac{\mathbb{E}[Y \;\mid\; Z=1] - \mathbb{E}[Y \;\mid\; Z=2]}{(1-p)} 
+\end{align*}
+
+This estimate of the ToT is the standard one that would result from instrumenting for compliance with the offering of treatment as in \cite{angrist1996identification}.
+The TuT is the analogous estimator, which could be recovered in a regression pooling the forced and choice arms and instrumenting for \textit{not} complying with being assigned to the choice arm (for a more formal development, see the appendix).
+The advantage of representing the estimands via division of the relevant ITT by the compliance (non-compliance) rate is that it allows us to estimate all the necessary terms from the single pooled regression Equation \ref{basic_reg}, from which the significance levels for the ToT, the TuT, and the difference between them can all be estimated as single-equation F-tests:
+
+$$ToT = \frac{\beta^C}{p}; \hspace{15} TuT = \frac{(\beta^F - \beta^C)}{(1-p)}; \hspace{15} (ToT-TuT) = \frac{\beta^C}{p}- \frac{(\beta^F - \beta^C)}{(1-p)}. $$
+
+Table \ref{tot_tut} shows the results of this analysis.
+Across the board, the TuT is greater than the ToT which illustrates that the `wrong' people are choosing commitment in terms of direct financial cost.\footnote{It is worth noting that the statistical power of these estimands is driven by the compliance rate; given our low overall compliance we are better powered to measure the TuT than the ToT, and the power for the difference between the two would be highest with a compliance rate of 50\%.}
+
+\textcolor{red}{Discussion to be fortified with updated table}
+
 \subsection{Quantile Treatment Effects}
 
+We now want to move away from the experimental consideration of the arms as a whole, and dive into the individual heterogeneity to learn more about the relationship between choice and outcomes.
 A simple way of interrogating the distribution of treatment effects is to use quantile regression.
-Benefits are distributed broadly however.
+Figure \ref{qregs} plots treatment effects on financial cost and APR at the 15$^{th}$, 25$^{th}$, 50$^{th}$ 75$^{th}$, and 85$^{th}$ percentile of the outcome variables for the Forced and Choice arms.
+It illustrates that a) there is substantial internal heterogeneity in the Forced arm, meaning that some people benefit from forcing and some do not, and that b) taken as a whole the Choice arm has no significant benefit in any part of the distribution.
+Therefore, within the group being forced to take commitment we find large heterogeneity in the impacts.
+
+We can explore the heterogeneity within the Choice arm in a non-experimental but suggestive way by breaking apart the choosers and non-choosers and separately estimating quantile effects relative to the control for these two groups.
+This analysis, shown in Figure \ref{qreg_chooser_nonchooser}, plots the quantile effects for the choosers only (circles), and non-choosers only (squares).
+It shows two important features of the observed impacts.
+First, the non-choosers in the choice arm never look different from the control, as should be the case if the exclusion restriction invoked in the prior section is true.
+Second, all of the heterogeneity that exists within the Choice arm arises from within the Chooser group, and this heterogeneity looks qualitatively similar to (although smaller than) the heterogeneity observed in the Forced arm.
+This analysis is observational because it splits the data on an endogenous variable (choice), but is nonetheless suggestive that substantial heterogeneity in treatment effects exists for all individuals exposed to the Commitment product, and that there are no obvious violations of the exclusion restrictions around forced versus chosen compliance.
+
+%Benefits are distributed broadly however.
 Figure \ref{fc_pro2}(b) displays results from quantile regressions at the 15$^{th}$, 25$^{th}$, 50$^{th}$ 75$^{th}$, and 85$^{th}$ percentiles.
@@
 %This motivated us to implement a finer measure of treatment effects.
-We used  \cite{atheygrf}'s generalized random forests methodology.\footnote{The methodology uses random forests of honest causal trees to estimate personalized treatment effects.
-The method generates a partition of the space of characteristics $X$, where each element of the partition is a leaf, and each leaf contains treatment and control clients with similar characteristics $x \in X$ which are used to calculate unbiased treatment effects for that leaf.
-The optimal partition is that which minimizes expected mean squared error of treatment effects predictions out-of-sample.} %The tree is honest because it uses one sample to build the tree and another one to estimate treatment effects within that tree.
-%\cite{atheygrf} show that their treatment effects are asymptotically normal, which allows us to construct confidence intervals for our treatment estimate in each leaf.
 
@@
 
-Figure \ref{fc_pro4} digs in more detail into the sources of variation underlying the main effects in Figure \ref{main_te}.
+%Figure \ref{fc_pro4} digs in more detail into the sources of variation underlying the main effects in Figure \ref{main_te}.
 $\beta$ coefficients and their 95\% confidence interval from estimating equation (\ref{basic_reg}) using different definitions of financial cost.
@@
 
-The hollow circles in Figure \ref{fc_pro4}(a) show zero average effects for the different definitions of financial cost analogous to the ones described above.
+%The hollow circles in Figure \ref{fc_pro4}(a) show zero average effects for the different definitions of financial cost analogous to the ones described above.
 Figure \ref{fc_pro4}(b) shows further that the null effect happens for the 15$^{th}$, 25$^{th}$, 50$^{th}$ 75$^{th}$, and 85$^{th}$ percentiles.\footnote{The few clients that chose the Commitment contract (the solid black squares) do enjoy cost savings of 1005 MXN, which compares favorably to the 304 MXN in the Forced arm (as a fraction of the loan the numbers are 41.5\% and 12.5\%), but this combines the selection and treatment effects.} %Figure \ref{heterogeneous_te_4} plots the distribution of treatment effects and finds that the distribution offering choice actually \textit{increased} financial cost and default for about half of clients compared to being assigned the status-quo contract.
-Those tended to be the less economically vulnerable and more educated, {women}, and those whose family typically asks them for money.
-Figure \ref{fc_pro4}(c) finds null effects for pawn recovery. Consistent with these findings, Figure \ref{reincidence} finds no effect on repeat purchases for the Commitment Choice group.
-
- Figure \ref{fc_pro2}(d) plots estimated treatment effects of the Forced Commitment commitment contract with the dependent variable being an indicator of losing the pawn in less than 230 days.
+Those tended to be the less economically vulnerable and more educated, {women}, and those whose family typically asks them for money.Figure \ref{fc_pro4}(c) finds null effects for pawn recovery.
+Consistent with these findings, Figure \ref{reincidence} finds no effect on repeat purchases for the Commitment Choice group.
+
+ %Figure \ref{fc_pro2}(d) plots estimated treatment effects of the Forced Commitment commitment contract with the dependent variable being an indicator of losing the pawn in less than 230 days.
 The leftmost coefficient shows that the Forced Commitment commitment contract increases the likelihood of recovering the pawn by 11 percentage points (26\% of mean recovery).
@@
 
- Results survive if we focus on those that paid a positive amount in treatment and control.\footnote{Although this is potentially a selected subsample, Table \ref{mechanisms} showed that there is no treatment effect in the extensive margin, i.e.
+% Results survive if we focus on those that paid a positive amount in treatment and control.\footnote{Although this is potentially a selected subsample, Table \ref{mechanisms} showed that there is no treatment effect in the extensive margin, i.e.
 in $pay>0$.} We find that even those that paid a fee in the Forced Commitment contract end up paying a smaller financial cost that those in the status-quo contract (Figure \ref{fc_pro2}a).\footnote{This regression conditions on those that paid a fee in the Forced Commitment group, and compares this subset in treatment vs all of the control group.
@@
 
-\subsection{Mistakes in the Choice of Commitment}
-
-This is not the first paper to find low demand for commitment, however it is the first we know of that can compare choice vs forcing with a money-metric outcome such as loan repayment.
-The fact that the Forced Commitment contract lowers financial costs for almost all clients, together with the fact that only 11\% choose it must mean that many consumers are choosing contracts with higher financial costs for themselves.
-We now present an estimation of how many consumers seem to be making a cost increasing choice, and how much money they seem to be leaving on the table.
-We conduct two exercises.
-
-\vspace{.2in}
-\noindent \textbf{Do choices increase financing cost?} Answering this question requires calculating a counterfactual: for each client in the choice arm we want to know how much cost savings would she have gained had she chosen the opposite contract.
+\subsection{Relating Random Forest Impacts to Observed Choice}
+
+To more directly interrogate self-selection in this context, we would like to be able to relate \textit{individual} choices over commitment to the \textit{individual} counterfactual outcomes that borrowers would have realized in different states of nature.
+To achieve this, we can use the honest causal forest method to impute borrower-specific treatment effects of the assignment to Commitment, and then map this estimate to the choices individuals make in the Choice arm.
+
+Specifically, for each client in the choice arm we want to know how much cost savings would she have gained had she chosen the opposite contract.
 We do this in two steps.
-Step 1, using the honest causal forests method of \cite{atheygrf} described above and the two forcing arms we calculate the causal effect on financing cost of getting the Forced Commitment contract instead of the status quo contract for a client $i$ with characteristics $x_i$; call it $TE^{For}_{i}(x_i)$.
+First, we use  \cite{atheygrf}'s generalized random forests methodology to estimate the impact of the Forced arm relative to the control at the individual level.
+The method generates a partition of the space of characteristics $X$, where each element of the partition is a leaf, and each leaf contains treatment and control clients with similar characteristics $x \in X$ which are used to calculate unbiased treatment effects for that leaf.
+The optimal partition is that which minimizes expected mean squared error of treatment effects predictions out-of-sample.
+The tree is honest because it uses one sample to build the tree and another one to estimate treatment effects within that tree.
+\cite{atheygrf} show that their treatment effects are asymptotically normal, which allows us to construct confidence intervals for our treatment estimate in each leaf.
+This method gives us the causal effect on financing cost of getting the Forced Commitment contract instead of the status quo contract for a client $i$ with characteristics $x_i$; call it $TE^{F}_{i}(x_i)$.
+Figure \ref{heterogeneous_effects} presents the PDFs of the estimated individual-level treatment effects for our three main outcomes, showing the estimated effect as well as the distributions of the upper and lower bounds.
+The figures illustrate the substantial impact of the Forced arm particularly on APR, for which more than 90\% of the individuals have positive treatment effects and even in the upper bound confidence interval more than half of individuals benefit.
+
 Then in step 2 we predict treatment effects for clients \textit{in the Choice arm} using the partition into leaves and the treatment effect from step 1, that is client $j$ is imputed the treatment effect of the leaf corresponding to her characteristics $x_j$.
-We call this counterfactual treatment effect $\widehat{TE}^{For}_{j}(x_j)$.
-This is precisely the counterfactual we wanted.\footnote{This extrapolation of the treatment effects assumes that choice itself --conditional on a given contract-- does not affect behavior.
-Given the results in subsection \ref{effect_choice} we are comfortable with this assumption.
-Note that although the extrapolation is to another population, by randomization it is a statistically identical population with common support.} Armed with this, we say that a client made a ``mistake'' if either she chose the status quo contract and her $\widehat{TE}^{fee}_{i}$ is negative (i.e.
-more cost saving from the Forced contract), or if she chose the Commitment contract and $\widehat{TE}^{fee}_{i}$ is positive, (i.e.
+We call this counterfactual treatment effect $\widehat{TE}^{F}_{j}(x_j)$.
+This is precisely the counterfactual we wanted, because it lets us relate observed individual choices with estimated individual-level treatment effects.\footnote{This extrapolation of the treatment effects assumes that choice itself --conditional on a given contract-- does not affect behavior (note the evidence in the prior section suggesting this is the case).
+Although the extrapolation is to another population, by randomization it is a statistically identical population with common support.} Armed with this, we say that a client made a ``mistake'' if either she chose the status quo contract and her $\widehat{TE}^{F}_{i}$ is negative (i.e.
+more cost saving from the Forced contract), or if she chose the Commitment contract and $\widehat{TE}^{F}_{i}$ is positive, (i.e.
 financial costs are larger for the Commitment contract).
-When a client made a choice mistake, we say that its peso-size is $|\widehat{TE}^{fee}_{i}|$.
+When a client made a choice mistake, we say that its money-metric values is the absolute value of $|\widehat{TE}^{F}_{i}|$.
 
@@
 Since the prediction of the treatment effect is an estimate and has noise, we do two things.
-First, we normalize $\widehat{TE}^{fee}_{i}$ by the value of the loan of person $i$ and introduce a threshold parameter $z$ and say that a choice is a ``mistake'' if the alternative contract would generate greater than $z$ in savings.
-That is, we introduce a threshold that we vary from 0\% to 15\% of the value of the loan.
-{Second, we take into account uncertainty in estimation of treatment effects and report results using the extremes of the 95\% confidence interval bounds for $\widehat{TE}^{fee}_{i}$.}
-
+First, we normalize $\widehat{TE}^{F}_{i}$ by the value of the loan of person $i$ and introduce a threshold parameter $z$ and say that a choice is a ``mistake'' if the alternative contract would generate greater than $z$ in savings.
+We vary this threshold from 0\% to 15\% of the value of the loan.
+Second, we take into account uncertainty in estimation of treatment effects and report results using the extremes of the 95\% confidence interval bounds for $\widehat{TE}^{F}_{i}$.
+
+\textcolor{red}{rewrite following paragraph with updated figure in hand.}
 Figure \ref{choose_wrong}(a) plots on the left Y-axis the fraction of clients that made a choice ``mistake'' and on the right Y-axis its size in pesos.
@@
 %(90\% confidence interval [140,390]).
-Figure \ref{choose_wrong}(b) plots the same curve, but separately for overconfident and non-overconfident clients, using the definition of overconfidence in Section \ref{behavioral}.
-{It shows that there are about 11 percentage points more mistakes in the overconfident population (when $z=0$), an important difference.}
-
-The findings above suggest that forcing clients into commitment contacts may reduce financial cost for the overwhelming majority of clients.
-Figure \ref{choose_wrong}(c) calculates what fraction of clients would be made better off if we forced them into the fee-commitment contract.
-We find that 85\% would be better off (using $z=0$), and they would on average have savings of 250MXN.
-This conclusion is in line with a recent paper by \cite{John}.
-In a savings context, she finds that when commitment is on the menu a majority of subjects wrongly choose too little commitment and fail to reach their savings goals.
-It is also in line with \cite{Sprenger} who show that the more naive about their present bias are the ones who demand less commitment.
 
@@
 
+%The following text brought in from the prior ToT/TuT section; do we want to include?
+
+%.
+Although the difference is not significant (Figure \ref{bootstrap_tot_tut}) since we have a low (15\%) compliance rate in the choice arm, which results in low power, we also estimate an Instrumental Random Forest following \cite{atheygrf}.
+The Instrumental Random Forest allows us to compute conditional heterogeneous treatment effects, which effectively lets us estimate for each individual with characteristics $X_i$ the quantities $ToT_i:=\mathbb{E}[Y_1-Y_0\; |\; T_i=1, X_i]$, and $TuT_i:=\mathbb{E}[Y_1-Y_0 \;|\; T_i=0, X_i]$.
+Figure \ref{tot_tut_ecdf} plots the ECDF for this quantities, together with the difference $ToT-TuT$.
+When testing for the difference in means between this two distributions we find a significant difference of \hl{0.03 points} at the 95\% level.
+
 \subsection{Relating Choice Probabilities to Benefits}
 
-The previous exercise consisted of extrapolating treatment effects from the no-choice arms to the choice arm.
+The previous exercise consisted of extrapolating treatment effects from the no-choice arms to the Choice arm.
 Here we do the reverse.
-First, we estimate a flexible model of take-up of the commitment-fee contract \textit{in the choice arm} using gradient boosting classification\footnote{Results are robust to other classification methods like Random Forest, SVM, etc.} and obtain for a client with characteristics $x_i$ a calibrated probability $P(x_i)$ of choosing the Forced Commitment contract.
-We then use this model to predict the counterfactual probability of a client with characteristics $x_j$ choosing the fee-commitment contract \textit{in the no choice-arms} if she would have been given the choice, what we call $\widehat{P(x_j)}$.\footnote{Our gradient boosting take-up model has a good out-of-sample fit with an out-of-sample AUC of \colorbox{yellow}{0.85}.
-(accuracy 97\% in-sample and 90\% out-of-sample)} Second, armed with this prediction in the forcing arms, we can ask the following: is it true that people with larger Forced Commitment contract treatment effects (i.e.
-more cost savings) are more likely to have demanded the Forced Commitment contract if choice had been given to them?
-
-Based on the propensity score, can then represent the estimated HTEs from commitment against the likelihood to choose it in several ways.
+First, we estimate a flexible model of take-up of the commitment-fee contract \textit{in the Choice arm} using gradient boosting classification\footnote{Results are robust to other classification methods like Random Forest, SVM, etc.} and obtain for a client with characteristics $x_i$ a calibrated probability $P(x_i)$ of choosing the commitment contract.
+We then use this model to predict the counterfactual probability of a client with characteristics $x_j$ choosing the Commitment contract in the Forced arm if she had been given the choice, what we call $\widehat{P(x_j)}$.\footnote{Our gradient boosting take-up model has a good out-of-sample fit with an out-of-sample AUC of \colorbox{yellow}{0.85}.
+(accuracy 97\% in-sample and 90\% out-of-sample)} Now, armed with this propensity score in the Forced arm, we can ask whether people with larger Random Forest-estimated individual treatment effects (i.e.
+more cost savings) would have been more likely to choose it, as we would expect from a Roy model of treatment selection.
+
+We can represent the relationship between the HTEs from commitment and propensity scores in several ways.
 Most straightforward is Figure \ref{HTE_vs_propensity}, which plots the individually-estimated treatment effect from Forced versus Control treatments on the Y-axis, and the predicted probability of choosing commitment on the X axis.
-The HTEs are very strongly downward-sloping over the part of the distribution that has heterogeneity in predicted propensities.
+The HTEs are very strongly downward-sloping over the part of the distribution that has heterogeneity in predicted propensities, the opposite of what we would expect from Roy-type selection.
 The sample with the lowest propensity of choosing commitment has a smoothed benefit of roughly twice those with a .2 change of choosing, measured both in terms of benefit/cost and in terms of probability of repayment.
@@
 
-Second, we can predict the two categories: choosers \& non-choosers, such that the proportions match the observed data, then we compute cumulative distribution functions of the heterogeneous conditional average treatment effect we estimated in Section \ref{TE_fee-forcing} using the Causal Random Forest.
+Second, we can turn the continuous propensity score into a binary predicted choice, such that the proportion of choosers matches the observed data, and then compute cumulative distribution functions of the heterogeneous conditional average treatment effects we estimated using the Causal Random Forest.
 Figure \ref{benefit_vs_choice_cdf} shows there is a first order stochastic dominance in treatment effects between the two predicted categories.
-This means those more likely to demand commitment are also those that had smaller benefits from commitment.\footnote{This result is similar to \cite{Walters}, who finds that students that select into more effective schools are the ones with smaller treatment effects from attending.
-That paper uses distance to school as an instrumental variable for choice, while we use randomization to choice vs no-choice groups as our empirical strategy.}
-
-A completely different approach to relating choice to HTEs arrives at a similar conclusion.
+This means those more likely to demand commitment are also those that had smaller benefits from commitment.
+
+Finally, a completely different approach to relating choice to HTEs arrives at a similar conclusion.
 We attempt to characterize the class that benefits more from commitment using a finite mixture model with two latent types.
@@
 
-\subsection{LATEs for Compliers and Non-Compliers}
-
-The prior approaches to heterogeneity analysis did not use information about the actual outcomes in the complier group in the choice arm, only assuming that the decision to choose can be modeled.
-An alternate approach assumes nothing about the decision to choose (other than random sampling) and instead makes the couple of exclusion restriction-style assumptions typical of Local Average Treatment Effect (LATE) analysis.
-Namely, a) the typical LATE assumption that an individual not choosing the treatment has the same potential outcome as one not offered it, then the mirror image assumption for the Forcing arm that b) an individual forced to take Commitment has the same potential outcome as an individual choosing it, and c) no spillovers from chooser to non-choosers in the choice arm.\footnote{Figure \ref{exclusion_restriction} in the appendix tests this assumptions.
-\hl{For robustness we also try a Manski-type monotone IV approach with similar results.}}
-
-Let $Z_i$ be the observed, randomly assigned experimental allocation, where $Z_i=0$ denotes the control arm, $Z_i=1$ denotes the Commitment-fee arm, and $Z_i=2$ is the choice arm.
-Let $T_i$ be the unobserved choice type.
-$T_i=0$ when individual $i$ does not choose commitment  given the choice and $T_i=1$ when chooses commitment given the choice.
-Finally, $D_i = Z_i\times \mathds{1}(Z_i\neq 2) + T_i\times \mathds{1}(Z_i=2)$ is the observed treatment indicator, and $Y(d,z)$ is the potential outcome function for $d=0,1$, and $z=0,1,2$.
-
-To test the difference between gains for choosers versus gains from non-choosers we need to identify: $\mathbb{E}[Y_1-Y_0\;|\;T=1]$ the Treatment on the Treated (TOT), and $\mathbb{E}[Y_1-Y_0\;|\;T=0]$ the Treatment on the Untreated (TUT).
-
-Given that what we really want to understand is the differential outcomes, we have
-\begin{align*}
-\mathbb{E}[Y_1 - Y_0 \;\mid\; T=1]  &=   \frac{\mathbb{E}[Y \;\mid\; Z=2] - \mathbb{E}[Y \;\mid\; Z=0)}{p} \\
-\mathbb{E}[Y_1 - Y_0 \;\mid \;T=0]  &=  \frac{\mathbb{E}[Y \;\mid\; Z=1] - \mathbb{E}[Y \;\mid\; Z=2]}{(1-p)} 
-\end{align*}
-
-where $p$ is analogous to a compliance (in the choice arm) indicator in a one-sided non-compliance problem.
-
-Note that the TOT is the LATE with one-sided non-compliance between the choice and control arm.
-The TUT is the LATE between the forced and choice arms, and think of the forced arm as an instrument for NOT complying with the treatment.
-In other words, is just the LATE on non-compliers.
-This effectively draws a distinction between unobserved "choice types" ($T = 0, 1$) and observed treatment take-ups ($D = 0, 1$)
-
-Table \ref{tot_tut} shows that TUT is greater than the TOT.
-Although the difference is not significant (Figure \ref{bootstrap_tot_tut}) since we have a low (15\%) compliance rate in the choice arm, which results in low power, we also estimate an Instrumental Random Forest following \cite{atheygrf}.
-The Instrumental Random Forest allows us to compute conditional heterogeneous treatment effects, which effectively lets us estimate for each individual with characteristics $X_i$ the quantities $TOT_i:=\mathbb{E}[Y_1-Y_0\; |\; T_i=1, X_i]$, and $TUT_i:=\mathbb{E}[Y_1-Y_0 \;|\; T_i=0, X_i]$.
-Figure \ref{tot_tut_ecdf} plots the ECDF for this quantities, together with the difference $TOT-TUT$.
-When testing for the difference in means between this two distributions we find a significant difference of \hl{0.03 points} at the 95\% level.
-
-Hence, we pursue three quite different techniques and all arrive at the same result.
-Whether we model the choice of Commitment and analyze heterogeneity using a random forest, use a PCM-style technique to categorize borrower types in a flexible way, or exploit the point-identification of LATEs for compliers and non-compliers enabled by the Forcing arm, the results are consistent:  the wrong people are choosing commitment.
+Hence, we pursue several quite different techniques and all arrive at the same result.
+All of the treatment heterogeneity is found among individuals who did receive the Commitment contract, whether chosen or forced.
+Whether we exploit the point-identification of LATEs for compliers and non-compliers enabled by the Forcing arm, use HTEs to examine the `mistakes' made by choosers versus non-choosers in the Choice arm, estimate propensities and relate these to HTEs in the Forced arm, or use a non-parametric finite mixture model, the overall story is the same:  the wrong people are choosing commitment.
+
+These findings suggest that forcing clients into commitment contacts may reduce financial cost for the overwhelming majority of clients. 
+%Figure \ref{choose_wrong}(c) calculates what fraction of clients would be made better off if we forced them into the fee-commitment contract.
+We find that 85\% would be better off (using $z=0$), and they would on average have savings of 250MXN.
+This conclusion is in line with a recent paper by \cite{John}.
+In a savings context, she finds that when commitment is on the menu a majority of subjects wrongly choose too little commitment and fail to reach their savings goals.
+It is also in line with \cite{Sprenger} who show that the more naive about their present bias are the ones who demand less commitment.\footnote{This result is also similar to \cite{Walters}, who finds that students that select into more effective schools are the ones with smaller treatment effects from attending.
+That paper uses distance to school as an instrumental variable for choice, while we use randomization to choice vs no-choice groups as our empirical strategy.}
+
+\subsection{Dynamic Effects:  Learning-by-not-doing}
+
+\textcolor{red}{Need to decide on table and write this section of the paper.}
+
+\section{Old Mechanisms Section of Paper}
+
+\textcolor{red}{Which of these pieces do we want to keep?  Delete whole section?.}
 
@@
 
-\subsection{Dynamic Effects:  Learning-by-not-doing}
-
-\textcolor{red}{Need to decide on table and write this section of the paper.}
-
-\section{Old Mechanisms Section of Paper}
-
-\textcolor{red}{Which of these pieces do we want to keep?  Delete whole section?.}
 \subsubsection{Neoclassical Alternatives} \label{neoclasical}
@@
 \newpage
-
+\begin{landscape}
 \vspace{.2in}
@@
 
+\newpage
+
+\begin{table}[H]
+\caption{Intermediate outcomes}
+\label{mechanisms}
+\begin{center}
+\scriptsize{\input{./Tables/mechanism.tex}}
+\end{center}
+
+%\textit{Do file: } \texttt{mechanisms.do}
+\end{table}
+
+\scriptsize {
+\noindent This table explores treatment effects in ``intermediate variables''. Each column represents a different dependent variable following the main specification \ref{basic_reg}.
+an OLS regression, and each panel represents a different treatment arm-control comparison.
+All regressions include fixed effects for branch, day of week fixed effects, number of pawns at the time of pawning this particular one, number of different treatment arms experienced before pawning this particular one.
+$R^2$ are not reported, they were less than 0.04 for all but the last column which had $R^2$'s close to 0.6.
+The last row shows the mean of the dependent variable for the control group.
+Dependent variables are as follows: Column (1) measures the number of days elapsed from the pawning date to the first payment done.
+Column (2) records the number of payments done within 230 days of the pawn.
+Column (3) is the average size of the payments for each client in pesos.
+Column (4) is self-reported cost to get to the branch plus the imputed loss of a whole day of salary (using the minimum wage in Mexico) multiplied by the number of visits to the branch.
+Column (5) measures the number of days it took to recover the pawn, conditional on recovering.
+The dependent variable in Column (6) is a dummy =1 if the client paid any positive amount within 230 days of the pawn.
+For Columns (7) and (8) the dependent variable it is the sum of total payments done within 230 days of the pawn divided by the size of the loan, but column (8) includes as regressors a dummy=1 if the client recovered her pawn, and its interaction with treatment.
+}
+
+\vspace{3ex}
+
+\end{landscape}
+
+\begin{table}[H]
+\caption{Effects on several definitions of cost}
+\label{table_robustness_fc}
+\begin{center}
+\scriptsize{\input{./Tables/fc_robustness.tex}}
+\end{center}
+ \scriptsize
+
+%\textit{Do file: } \texttt{fc\_robustness.do}
+\end{table}
+
+\begin{table}[H]
+\caption{Treatment effects on the soft arms}
+\label{impact_soft}
+\begin{center}
+\scriptsize{\input{./Tables/decomposition_te_soft.tex}}
+\end{center}
+ \scriptsize
+
+%\textit{Do file: } \texttt{decomposition\_te\_soft.do}
+\end{table}
+
+\begin{table}[H]
+\caption{Effects on several definitions of cost - Soft arms}
+\label{table_robustness_fc_soft}
+\begin{center}
+\scriptsize{\input{./Tables/fc_robustness_soft.tex}}
+\end{center}
+ \scriptsize
+
+%\textit{Do file: } \texttt{fc\_robustness\_soft.do}
+\end{table}
+
+\begin{landscape}
+
+\begin{table}[H]
+\caption{Intermediate outcomes - Soft arms}
+\label{mechanisms_soft}
+\begin{center}
+\scriptsize{\input{./Tables/mechanism_soft.tex}}
+\end{center}
+
+%\textit{Do file: } \texttt{mechanisms\_soft.do}
+\end{table}
+
+\end{landscape}
+
+\cleardoublepage
+
+\begin{table}[H]
+\caption{Multiple-loans robustness check}
+\label{multiple_loans}
+\begin{center}
+\scriptsize{\input{./Tables/multiple_loans.tex}}
+\end{center}
+ \scriptsize
+
+%\textit{Do file: } \texttt{multiple\_loans.do}
+\end{table}
+
+\cleardoublepage
+
+\begin{table}[H]
+\caption{Gains for choosers versus gains from non-choosers (ToT \& TuT)}
+\label{tot_tut}
+\begin{center}
+\scriptsize{\input{./Tables/tot_tut_iv.tex}}
+\end{center}
+ \scriptsize This table shows estimates of the ToT and the TuT with an IV-LATE framework.
+The ToT (columns (1)-(3)) is computed as the usual LATE with one-sided non-compliance between the choice and control arm, and the TuT (columns (4)-(6)) is the LATE on non-compliers.
+Columns (6) and (7) estimates the effect of the compliers on the estimated HTE calculated with the Causal Random Forest.
+%\textit{Do file: } \texttt{tot\_tut\_reg.do}
+\end{table}
+
 \vspace{.3in}
 
-\begin{table}[H]
-\caption{Overconfidence: Take-up and Treatment Effects}
-\label{oc_reg}
-\begin{center}
-\scriptsize{\input{./Tables/oc_reg.tex}}
-\end{center}
- \footnotesize This table shows the parameter estimates of $y_i = \alpha + \beta \: OC_i + Z_i'\gamma + \epsilon_i$, where $OC_i:=\mathbbm{1}(P^s_i-\widehat{P_i(X_i)}>0)$ is an indicator for the subjective probability of recovery being larger than the predicted one.
+%\begin{table}[H]
+%\caption{Overconfidence: Take-up and Treatment Effects}
+%\label{oc_reg}
+%\begin{center}
+%\scriptsize{\input{./Tables/oc_reg.tex}}
+%\end{center}
+% \footnotesize This table shows the parameter estimates of $y_i = \alpha + \beta \: OC_i + Z_i'\gamma + \epsilon_i$, where $OC_i:=\mathbbm{1}(P^s_i-\widehat{P_i(X_i)}>0)$ is an indicator for the subjective probability of recovery being larger than the predicted one.
 In columns 1-4 $y_i$ is a dummy for whether the client $i$ chose to have the commitment contract in the respective choice arm, and in columns 5 and 6 $y_i$ is the heterogeneous treatment effect for financial cost (in pesos) estimated by comparing the Forced Commitment vs status quo arms in Section \ref{TE_fee-forcing}.
@@
 %\textit{Do file: } \texttt{oc.do}
-\end{table}
-
-\begin{table}[H]
-\caption{Overconfidence: Take-up and Treatment Effects}
-\label{oc_reg}
-\begin{center}
-\scriptsize{\input{./Tables/oc_reg_dec.tex}}
-\end{center}
- \footnotesize This table shows the parameter estimates of $y_i = \alpha + \beta \: OC_i + Z_i'\gamma + \epsilon_i$, where $OC_i:=\mathbbm{1}(P^s_i-\widehat{P_i(X_i)}>0)$ is an indicator for the subjective probability of recovery being larger than the predicted one.
+%\end{table}
+
+%\begin{table}[H]
+%\caption{Overconfidence: Take-up and Treatment Effects}
+%\label{oc_reg}
+%\begin{center}
+%\scriptsize{\input{./Tables/oc_reg_dec.tex}}
+%\end{center}
+% \footnotesize This table shows the parameter estimates of $y_i = \alpha + \beta \: OC_i + Z_i'\gamma + \epsilon_i$, where $OC_i:=\mathbbm{1}(P^s_i-\widehat{P_i(X_i)}>0)$ is an indicator for the subjective probability of recovery being larger than the predicted one.
 In columns 1-4 $y_i$ is a dummy for whether the client $i$ chose to have the commitment contract in the respective choice arm, and in columns 5 and 6 $y_i$ is the heterogeneous treatment effect for financial cost (in pesos) estimated by comparing the Forced Commitment vs status quo arms in Section \ref{TE_fee-forcing}.
@@
 %\textit{Do file: } \texttt{oc.do}
-\end{table}
+%\end{table}
 
@@
 %\textit{Do file: } \texttt{iv\_reg\_intdef\_detailed.do}
-\end{table}
-
-\begin{table}[H]
-\caption{Gains for choosers versus gains from non-choosers (TOT \& TUT)}
-\label{tot_tut}
-\begin{center}
-\scriptsize{\input{./Tables/tot_tut_iv.tex}}
-\end{center}
- \scriptsize This table shows estimates of the TOT and the TUT with an IV-LATE framework.
-The TOT (columns (1)-(3)) is computed as the usual LATE with one-sided non-compliance between the choice and control arm, and the TUT (columns (4)-(6)) is the LATE on non-compliers.
-Columns (6) and (7) estimates the effect of the compliers on the estimated HTE calculated with the Causal Random Forest.
-%\textit{Do file: } \texttt{tot\_tut.do}
 \end{table}
@@
      \begin{subfigure}{0.45\textwidth}
-    \caption{APR}
-       \centering
-      \includegraphics[width=\textwidth]{Figuras/hist_eff.pdf}
+    \caption{Effective APR}
+       \centering
+      \includegraphics[width=\textwidth]{Figuras/hist_apr.pdf}
     \end{subfigure}
@@
 
+\cleardoublepage
+
 \begin{figure}[H]
@@
 The third and fourth definition adds the travel cost for the treatment arms.
+The last definition is a `fully adjusted' scenario that doesn't include the interest that is mechanically saved by paying early since this is the piece of the Forced-commitment contract that has a foregone liquidity cost for the borrower, on top of adding travel costs.
 We also compute APR versions of the above measures.
-    Finally, `APR - interests' is a version of the APR that doesn't include the interest that is mechanically saved by paying early since this is the piece of the Forced-commitment contract that has a foregone liquidity cost for the borrower.
+    Finally, `APR - interests'  The treatment effects are indicated in standard deviations, together with 95\% confidence intervals.
+\end{figure}
+
+\begin{figure}[H]
+     \caption{Effect of promises}
+    \label{effect_promises}
+    \begin{center}
+    \begin{subfigure}{0.45\textwidth}
+        \caption{Main outcomes}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/soft_te.pdf}
+    \end{subfigure}
+        \begin{subfigure}{0.45\textwidth}
+            \caption{Several definitions of cost}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/fc_robustness_soft.pdf}
+    \end{subfigure}
+       \begin{subfigure}{0.45\textwidth}
+       \caption{Q-regs on Financial Cost (in MXN)}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/soft_qreg_fc_admin.pdf}
+    \end{subfigure}
+        \begin{subfigure}{0.45\textwidth}
+         \caption{Q-regs on effective APR}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/soft_qreg_apr.pdf}
+    \end{subfigure}
+    \end{center}
+    \scriptsize
+    Panel (a) shows the main outcomes for the soft arms.
 The treatment effects are indicated in standard deviations, together with 95\% confidence intervals.
+Panel (b) shows the treatment effects on the several definitions of cost for the soft arms.
+Panels (c) \& (d) show treatment effects on different quantiles for the Financial Cost and APR.
 \end{figure}
@@
 \begin{figure}[H]
-    \caption{Detailed comparison of Forced and Choice Commitment arms}
-    \label{fc_pro4}
-    \begin{center}
+     \caption{Quantile regressions}
+    \label{qregs}
+    \begin{center}
+    \begin{subfigure}{.45\textwidth}
+      \caption{Financial cost (in MXN)}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/qreg_fc_admin.pdf}
+    \end{subfigure}
      \begin{subfigure}{0.45\textwidth}
-        \caption{Financial cost}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/fc_te_pro_4.pdf}
+    \caption{Effective APR}
+       \centering
+      \includegraphics[width=\textwidth]{Figuras/qreg_apr.pdf}
+    \end{subfigure}
+    \end{center}
+         \scriptsize
+     This figure plots the effects on different quantiles (15th, 25th, 50th, 75th, 85th percentile) of the distribution of financial cost, and APR, for the Forced-commitment and Choice-commitment arms.
+      %\footnotesize{ } \textit{Do file: }  \texttt{main\_qreg.do}
+\end{figure}
+
+\begin{figure}[H]
+    \caption{Non-experimental analysis of Choosers and Non-Choosers}
+    \label{qreg_chooser_nonchooser}
+    \begin{center}
+    \begin{subfigure}{.45\textwidth}
+      \caption{Financial Cost (Hard commitment)}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/qreg_hard_fc_admin.pdf}
     \end{subfigure}
      \begin{subfigure}{0.45\textwidth}
-        \caption{Financial Cost (quantile reg)}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/fc_quantile_pro_4.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.5\textwidth}
-
-        \bigskip
-        \bigskip
-
-        \caption{Lost Pawn}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/def_te_pro_4.pdf}
+      \caption{APR (Hard commitment)}
+       \centering
+      \includegraphics[width=\textwidth]{Figuras/qreg_hard_apr.pdf}
+    \end{subfigure}
+    \begin{subfigure}{.45\textwidth}
+      \caption{Financial Cost (Soft commitment)}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/qreg_soft_fc_admin.pdf}
+    \end{subfigure}
+     \begin{subfigure}{0.45\textwidth}
+      \caption{APR (Soft commitment)}
+       \centering
+      \includegraphics[width=\textwidth]{Figuras/qreg_soft_apr.pdf}
     \end{subfigure}    
@@
 \begin{figure}[H]
-    \caption{The effect of promises}
-    \label{fc_pro5}
-    \begin{center}
-
-        \begin{subfigure}{0.45\textwidth}
-        \caption{Financial cost -- Choice}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/fc_te_pro_5.pdf}
-    \end{subfigure}
-        %\begin{subfigure}{0.45\textwidth}
-        %\caption{Quantile regression}
-        %\centering
-        %\includegraphics[width=\textwidth]{Figuras/fc_quantile_pro_5.pdf}
-    %\end{subfigure}
-    \begin{subfigure}{0.45\textwidth}
-        \caption{Losing Pawn -- Choice}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/def_te_pro_5.pdf}
-    \end{subfigure}
-
-    \bigskip
-    \bigskip
-
-        \begin{subfigure}{0.45\textwidth}
-        \caption{Financial cost -- Promise-forcing}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/fc_te_pro_3.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.45\textwidth}
-        \caption{Losing Pawn -- Promise-forcing}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/def_te_pro_3.pdf}
-    \end{subfigure}
-
-    \end{center}
-    \scriptsize
-    Panels (a) and (b) in this figure show the estimated treatment effects of ``forcing'' the frequent payment commitment contract using promises, compared to the status-quo (control) for financial cost (Panel a), and for an indicator of losing the pawn (Panel b).
-Panels (c) and (d) are analogous but focus on the effect of giving choice between frequent payment commitment contract using promises and the status quo contract.
-In Panel (a) each dot represents the estimated treatment effect for a different definition of financing cost, or for a different sub-population, and its 95\% confidence interval.
-From left to right, the first effect corresponds to using the gold value of the pawned piece in the definition of financial cost and discounting the payments to present value using a 7\% monthly rate; the second uses the subjective value of the pawn; the third is analogous to the second but adds transaction cost (transport+1 day's wage) per visit; and the fourth conditions on the population that paid any positive amount towards recovery of their pawn.
-Panel (b) plots the effect of not recovering the pawn: the leftmost coefficients compares all those assigned to the promise-forcing arm vs all those in the status quo contract, where the dependent variable=1 if the client has not recovered the pawn 230 days after pawning.
-The next coefficient defines the dependent variable=1 if the client has not recovered the pawn 120 days after pawning.
-The third coefficient conditions on paying a positive amount, and the fourth conditions on paying at least 30\% of the loan.
-Panels (b) and (c) measure the effect of being given \textit{choice} between the frequent payment commitment contract with promise and the status-quo contract, versus being \textit{``forced''} into the status-quo contract (control).
-Again it focuses our two main outcomes: financial cost and an indicator for losing the pawn.
-Circles present the treatment effects.
-The figures also presents differences in these two outcomes for those who chose the frequent payment commitment contract versus the whole control group (squares-NSQ), and also for those who chose the status quo contract versus the whole control group (triangles-SQ).
-That is: the squares and triangles combine selection and treatment effects.
-      %\footnotesize{ } \textit{Do file: }  \texttt{fc\_te\_choice\_dec.do, def\_te\_choice\_dec.do, fc\_te.do, def\_te.do }
-\end{figure}
-
-\begin{figure}[H]
-     \caption{Quantile regressions}
-    \label{qregs}
+     \caption{Heterogeneous Treatment Effects}
+    \label{heterogeneous_effects}
     \begin{center}
@@
         \centering
-        \includegraphics[width=\textwidth]{Figuras/qreg_fc_admin.pdf}
+        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_pro_2.pdf}
     \end{subfigure}
      \begin{subfigure}{0.45\textwidth}
-    \caption{APR}
-       \centering
-      \includegraphics[width=\textwidth]{Figuras/qreg_eff_cost_loan.pdf}
-    \end{subfigure}
-    \end{center}
-         \scriptsize
-     This figure plots the effects on different quantiles (15th, 25th, 50th, 75th, 85th percentile) of the distribution of financial cost, and APR, for the Forced-commitment and Choice-commitment arms.
-      %\footnotesize{ } \textit{Do file: }  \texttt{main\_qreg.do}
-\end{figure}
-
-\begin{figure}[H]
-     \caption{Heterogeneous Treatment Effects}
-    \label{qregs}
-    \begin{center}
-    \begin{subfigure}{.45\textwidth}
-      \caption{Financial cost (in MXN)}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_pro_2.pdf}
-    \end{subfigure}
-     \begin{subfigure}{0.45\textwidth}
-    \caption{APR}
+    \caption{Effective APR}
        \centering
@@
 
-% \begin{figure}[H]
-%     \caption{The effect of the Forced Commitment treatment}
-%     \label{fc_pro2}
-%     \begin{center}
-%     \begin{subfigure}{0.42\textwidth}
-%         \caption{Financial cost (MXN)}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/fc_te_pro_2.pdf}
-%     \end{subfigure}
-%         \begin{subfigure}{0.42\textwidth}
-%         \caption{Financial cost (quantile reg)}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/fc_quantile_pro_2.pdf}
-%     \end{subfigure}
-
-%         \bigskip
-
-%     \begin{subfigure}{0.42\textwidth}
-%         \caption{Financial cost (HTE)}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_2.pdf}
-%     \end{subfigure}
-%     ~
-%     ~
-%     \bigskip
-%     \begin{subfigure}{0.42\textwidth}
-%         \caption{Lost pawn}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/def_te_pro_2.pdf}
-%     \end{subfigure}
-%     \begin{subfigure}{0.42\textwidth}
-%     \caption{Losing Pawn}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_2.pdf}
-%     \end{subfigure}
-
-%     \end{center}
-%         \scriptsize
-
-%       %\textit{Do file: }  \texttt{fc\_te.do, def\_te.do, fc\_quantilereg.do}
-% \end{figure}
-
-% \scriptsize {
-% \noindent This figure shows the estimated treatment effect of ``forcing'' the frequent payment commitment contract using fees, compared to the status-quo (control).
-In Panel (a) each dot represents the estimated treatment effect for a different definition of financing cost, or for a different sub-population, and its 95\% confidence interval.
-From left to right, the first effect corresponds to using the gold value of the pawned piece in the definition of financial cost and discounting the payments to present value using a 7\% monthly rate - to the left we have a decomposition of the financial cost in its four components from left to right (1) Discounted payments to capital, (2) Payed fees, (3) Payed interest, (4) Cost of losing pawn; the second uses the subjective value of the pawn; the third is analogous to the second but adds transaction cost (transport+1 day's wage) per visit; the fourth conditions on the population that paid any positive amount towards recovery of their pawn; the fifth conditions on the sub-population of the treatment group that paid a fee and compares these to all the control group.
-Panel (b) plots the effects on different quantiles of the distribution of financial cost (using the first definition): 15th, 25th, 50th, 75th, 85th percentile.
-Panel (c) plots the distribution of the heterogeneous treatment effects on financial cost, estimated using \cite{atheygrf}.
-Panel (d) Measures the effect of treatment on the likelihood of losing their pawn.
-The first coefficient compares all the treatment group vs all the control using 230 days after pawning to define the dependent variable; the second defines it using 120 days.
-The third coefficient from the left conditions on the population that paid any positive amount towards recovery of their pawn (which in theory may be endogenous but empirically we showed not to be affected by treatment).
-Finally, Panel (e) shows the distribution of heterogeneous treatment effects of the probability of losing the pawn.
-% the effect on ``repeat purchase''.
-That is likelihood of doing an additional pawn (in treatment vs control) after having been subjected to treatment for at least 75 days.
-The second coefficient estimates the regression conditional on recovering the pawn {in both treatment and control}, and the rightmost coefficient compares those above the median treatment effect in financial cost savings, {versus all the control group.}
-% }
-
-% \begin{figure}[H]
-%     \caption{The effect of the Forced Commitment treatment}
-%     \label{fc_pro2}
-%     \begin{center}
-%     \begin{subfigure}{0.42\textwidth}
-%         \caption{Effective cost/loan ratio}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/eff_te_pro_2.pdf}
-%     \end{subfigure}
-%         \begin{subfigure}{0.42\textwidth}
-%         \caption{Financial cost (quantile reg)}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/eff_quantile_pro_2.pdf}
-%     \end{subfigure}
-
-%         \bigskip
-
-%      \begin{subfigure}{0.42\textwidth}
-%          \caption{Financial cost (HTE)}
-%          \centering
-%          \includegraphics[width=\textwidth]{Figuras/he_dist_eff_cost_loan_pro_2.pdf}
-%      \end{subfigure}
-%     ~
-%     ~
-%     \bigskip
-%     \begin{subfigure}{0.42\textwidth}
-%         \caption{Lost pawn}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/def_te_pro_2.pdf}
-%     \end{subfigure}
-%     \begin{subfigure}{0.42\textwidth}
-%     \caption{Losing Pawn}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_2.pdf}
-%     \end{subfigure}
-
-%     \end{center}
-%         \scriptsize
-
-%       %\textit{Do file: }  \texttt{eff\_te.do, def\_te.do, eff\_quantilereg.do}
-% \end{figure}
-
-\vspace{3ex}
-
-\vspace{.3in}
-\begin{figure}[H]
-        \caption{Effects on repeat purchasing}
-    \label{reincidence}
-    \begin{center}
-        \centering
-        \includegraphics[width=0.6\textwidth]{re_te.pdf}
-    \end{center}
-     \scriptsize This figure shows the estimated effects on repeat purchasing of the four treatment arms (Forced Commitment, choice-fee, fee-promise, choice-promise) compared to the status-quo control group.
-It shows robustness of the effects by focusing on different sub-populations.
-The leftmost coefficient compares all the Forced Commitment group against all status quo group.
-The second coefficient conditions on the first pawn not being recovered when the second was pawned.
-The third coefficient conditions on clients who pawned again after having recovered the pawn in the experiment.
-The fourth coefficient uses all clients (in both the Forced Commitment and the status-quo arms) who had an estimated heterogeneous treatment effect above the median.
-Conditioning on this set keeps the sample balanced across arms and therefore still allows for a causal interpretation.
-For the choice arm we present three coefficients: coefficients represented by a circle compare all those offered choice to all those in the status quo arm, thus estimating a causal effect.
-Coefficients in triangles and squares represent those that self-select into the fee or promise arms and compare this subset against the whole status quo arm.
-They therefore contain a selection effect together with the treatment effect and cannot be interpreted causally.
-      %\footnotesize{ \textit{Do file: }  \texttt{re\_te.do}
-\end{figure}
-
-\begin{figure}[H]
-        \caption{Distribution of Overconfidence}
-    \label{oc_hist}
-    \begin{center}
-        \centering
-        \includegraphics[width=0.55\textwidth]{Figuras/oc_hist.pdf}
-    \end{center}
-    \scriptsize
-     In the baseline survey at the branch, before the client knew the contract or had the pawn appraised, they were asked from 0 to 100, how likely it was that they would be able to recover their pawn if pawned.
-We generate a variable we call overconfidence (OC) defined as the reported subjective probability of recovery minus the predicted probability ($P^s_i-\widehat{P_i(X_i)}$).
-We predict $\widehat{P_i(X_i)}$ using LASSO as explained in the text.
-This figure uses all observations for which we have data on $P^s_i$ and $X_i$ from the baseline survey.
-     %\textit{Do file: }  \texttt{oc.do}
-
-\end{figure}
-
 \begin{figure}[H]
@@
         \begin{subfigure}{0.45\textwidth}
-        \caption{Chose wrong}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/line_cw_eff_te_cf.pdf}
+        \caption{Mistakes in choice arm}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/line_cw_apr_te_cf.pdf}
 
@@
         \begin{subfigure}{0.45\textwidth}
-        \caption{By overconfidence/naivete}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/line_cw_eff_te_cf_OC_fee.pdf}
+        \caption{Financial value of mistake}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/money_cw_apr_te_cf.pdf}
 
@@
         \begin{subfigure}{0.45\textwidth}
-        \caption{\% better when forced to fee-commitment}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/line_better_forceall_eff_te_cf.pdf}
+        \caption{\% better when forced to Hard commitment}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/line_better_forceall_apr_te_cf.pdf}
 
@@
     \begin{subfigure}{0.475\textwidth}
-        \caption{Effective cost/loan benefit}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/benefit_choice_tau_eff.pdf}
+        \caption{Effective APR}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/benefit_choice_tau_apr.pdf}
     \end{subfigure}
@@
 We plot $\widehat{P(x_i)}$ in the X-axis using a binscatter that splits the X-axis in 100 percentile bins.
-The Y-axis plots the heterogeneous treatment effects of the (a) effective cost/loan benefit and (b) repayment, averaged for the respective x-axis bin.
+The Y-axis plots the heterogeneous treatment effects of the (a) effective APR (in the positive scale) and (b) repayment, averaged for the respective x-axis bin.
 Positive assortative selection would mean a negative relationship: those who benefit more by treatment and lose the pawn less are \emph{less} likely to choose it.
@@
     \begin{center}
-    %\begin{subfigure}{0.4\textwidth}
-    %    \caption{Financial cost}
-    %    \centering
-    %    \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_2.pdf}
-    %\end{subfigure}
     \begin{subfigure}{0.475\textwidth}
-        \caption{Effective cost/loan benefit}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/cdf_predchoose_tau_eff.pdf}
+        \caption{Effective APR benefit}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/cdf_predchoose_tau_apr.pdf}
     \end{subfigure}
@@
 \end{figure}
+
+%\begin{figure}[H]
+  %  \caption{Non-experimental analysis of Choosers and Non-Choosers}
+   % \label{fc_pro4}
+    %\begin{center}
+    %\begin{subfigure}{0.45\textwidth}
+     %   \caption{Financial cost}
+    %    \centering
+   %    \includegraphics[width=\textwidth]{Figuras/fc_te_pro_4.pdf}
+  %  \end{subfigure}
+   %     \begin{subfigure}{0.45\textwidth}
+  %      \caption{Financial Cost (quantile reg)}
+ %       \centering
+  %      \includegraphics[width=\textwidth]{Figuras/fc_quantile_pro_4.pdf}
+%    \end{subfigure}
+%    \begin{subfigure}{0.5\textwidth}
+
+  %      \bigskip
+  %      \bigskip
+
+ %       \caption{Lost Pawn}
+ %       \centering
+%        \includegraphics[width=\textwidth]{Figuras/def_te_pro_4.pdf}
+ %   \end{subfigure}
+ %   \end{center}
+ %       \scriptsize
+ %       This figure is analogous to Figure \ref{fc_pro2}.
+It measures the effect of being given \textit{choice} between the frequent payment commitment contract with fees and the status-quo contract, versus being \textit{``forced''} into the status-quo contract (control).
+Again it focuses our two main outcomes: financial cost and an indicator for losing the pawn.
+Circles present the treatment effects.
+The figures also presents differences in these two outcomes for those who chose the frequent payment commitment contract versus the whole control group (squares-NSQ), and also for those who chose the status quo contract versus the whole control group (triangles-SQ).
+Note that these two comparisons are not pure causal effects since people who chose the frequent payment commitment contract are different from those that do not.
+That is: the squares and triangles combine selection and treatment effects.
+Finally, for comparison purposes, the blue diamond displays the effects of forcing them into the frequent payment commitment contract and are just transcribed from Figure \ref{fc_pro2} above.
+      %\textit{Do file: }  \texttt{fc\_te\_choice\_dec.do, def\_te\_choice\_dec.do, fc\_quantilereg\_choice\_dec.do}
+%\end{figure}
+
+%\begin{figure}[H]
+ %   \caption{The effect of promises}
+ %   \label{fc_pro5}
+ %   \begin{center}
+
+ %       \begin{subfigure}{0.45\textwidth}
+%        \caption{Financial cost -- Choice}
+%        \centering
+%        \includegraphics[width=\textwidth]{Figuras/fc_te_pro5_5.pdf}
+%    \end{subfigure}
+        %\begin{subfigure}{0.45\textwidth}
+        %\caption{Quantile regression}
+        %\centering
+        %\includegraphics[width=\textwidth]{Figuras/fc_quantile_pro_5.pdf}
+    %\end{subfigure}
+ %   \begin{subfigure}{0.45\textwidth}
+ %       \caption{Losing Pawn -- Choice}
+ %       \centering
+ %       \includegraphics[width=\textwidth]{Figuras/def_te_pro_5.pdf}
+ %   \end{subfigure}
+
+%    \bigskip
+ %   \bigskip
+
+  %      \begin{subfigure}{0.45\textwidth}
+   %     \caption{Financial cost -- Promise-forcing}
+    %%    \centering
+ %       \includegraphics[width=\textwidth]{Figuras/fc_te_pro_3.pdf}
+%    \end{subfigure}
+%    \begin{subfigure}{0.45\textwidth}
+%        \caption{Losing Pawn -- Promise-forcing}
+%        \centering
+%        \includegraphics[width=\textwidth]{Figuras/def_te_pro_3.pdf}
+%    \end{subfigure}
+
+ %   \end{center}
+ %   \scriptsize
+  %  Panels (a) and (b) in this figure show the estimated treatment effects of ``forcing'' the frequent payment commitment contract using promises, compared to the status-quo (control) for financial cost (Panel a), and for an indicator of losing the pawn (Panel b).
+Panels (c) and (d) are analogous but focus on the effect of giving choice between frequent payment commitment contract using promises and the status quo contract.
+In Panel (a) each dot represents the estimated treatment effect for a different definition of financing cost, or for a different sub-population, and its 95\% confidence interval.
+From left to right, the first effect corresponds to using the gold value of the pawned piece in the definition of financial cost and discounting the payments to present value using a 7\% monthly rate; the second uses the subjective value of the pawn; the third is analogous to the second but adds transaction cost (transport+1 day's wage) per visit; and the fourth conditions on the population that paid any positive amount towards recovery of their pawn.
+Panel (b) plots the effect of not recovering the pawn: the leftmost coefficients compares all those assigned to the promise-forcing arm vs all those in the status quo contract, where the dependent variable=1 if the client has not recovered the pawn 230 days after pawning.
+The next coefficient defines the dependent variable=1 if the client has not recovered the pawn 120 days after pawning.
+The third coefficient conditions on paying a positive amount, and the fourth conditions on paying at least 30\% of the loan.
+Panels (b) and (c) measure the effect of being given \textit{choice} between the frequent payment commitment contract with promise and the status-quo contract, versus being \textit{``forced''} into the status-quo contract (control).
+Again it focuses our two main outcomes: financial cost and an indicator for losing the pawn.
+Circles present the treatment effects.
+The figures also presents differences in these two outcomes for those who chose the frequent payment commitment contract versus the whole control group (squares-NSQ), and also for those who chose the status quo contract versus the whole control group (triangles-SQ).
+That is: the squares and triangles combine selection and treatment effects.
+      %\footnotesize{ } \textit{Do file: }  \texttt{fc\_te\_choice\_dec.do, def\_te\_choice\_dec.do, fc\_te.do, def\_te.do }
+%\end{figure}
+
+% \begin{figure}[H]
+%     \caption{The effect of the Forced Commitment treatment}
+%     \label{fc_pro2}
+%     \begin{center}
+%     \begin{subfigure}{0.42\textwidth}
+%         \caption{Financial cost (MXN)}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/fc_te_pro_2.pdf}
+%     \end{subfigure}
+%         \begin{subfigure}{0.42\textwidth}
+%         \caption{Financial cost (quantile reg)}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/fc_quantile_pro_2.pdf}
+%     \end{subfigure}
+
+%         \bigskip
+
+%     \begin{subfigure}{0.42\textwidth}
+%         \caption{Financial cost (HTE)}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_2.pdf}
+%     \end{subfigure}
+%     ~
+%     ~
+%     \bigskip
+%     \begin{subfigure}{0.42\textwidth}
+%         \caption{Lost pawn}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/def_te_pro_2.pdf}
+%     \end{subfigure}
+%     \begin{subfigure}{0.42\textwidth}
+%     \caption{Losing Pawn}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_2.pdf}
+%     \end{subfigure}
+
+%     \end{center}
+%         \scriptsize
+
+%       %\textit{Do file: }  \texttt{fc\_te.do, def\_te.do, fc\_quantilereg.do}
+% \end{figure}
+
+% \scriptsize {
+% \noindent This figure shows the estimated treatment effect of ``forcing'' the frequent payment commitment contract using fees, compared to the status-quo (control).
+In Panel (a) each dot represents the estimated treatment effect for a different definition of financing cost, or for a different sub-population, and its 95\% confidence interval.
+From left to right, the first effect corresponds to using the gold value of the pawned piece in the definition of financial cost and discounting the payments to present value using a 7\% monthly rate - to the left we have a decomposition of the financial cost in its four components from left to right (1) Discounted payments to capital, (2) Payed fees, (3) Payed interest, (4) Cost of losing pawn; the second uses the subjective value of the pawn; the third is analogous to the second but adds transaction cost (transport+1 day's wage) per visit; the fourth conditions on the population that paid any positive amount towards recovery of their pawn; the fifth conditions on the sub-population of the treatment group that paid a fee and compares these to all the control group.
+Panel (b) plots the effects on different quantiles of the distribution of financial cost (using the first definition): 15th, 25th, 50th, 75th, 85th percentile.
+Panel (c) plots the distribution of the heterogeneous treatment effects on financial cost, estimated using \cite{atheygrf}.
+Panel (d) Measures the effect of treatment on the likelihood of losing their pawn.
+The first coefficient compares all the treatment group vs all the control using 230 days after pawning to define the dependent variable; the second defines it using 120 days.
+The third coefficient from the left conditions on the population that paid any positive amount towards recovery of their pawn (which in theory may be endogenous but empirically we showed not to be affected by treatment).
+Finally, Panel (e) shows the distribution of heterogeneous treatment effects of the probability of losing the pawn.
+% the effect on ``repeat purchase''.
+That is likelihood of doing an additional pawn (in treatment vs control) after having been subjected to treatment for at least 75 days.
+The second coefficient estimates the regression conditional on recovering the pawn {in both treatment and control}, and the rightmost coefficient compares those above the median treatment effect in financial cost savings, {versus all the control group.}
+% }
+
+% \begin{figure}[H]
+%     \caption{The effect of the Forced Commitment treatment}
+%     \label{fc_pro2}
+%     \begin{center}
+%     \begin{subfigure}{0.42\textwidth}
+%         \caption{Effective cost/loan ratio}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/eff_te_pro_2.pdf}
+%     \end{subfigure}
+%         \begin{subfigure}{0.42\textwidth}
+%         \caption{Financial cost (quantile reg)}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/eff_quantile_pro_2.pdf}
+%     \end{subfigure}
+
+%         \bigskip
+
+%      \begin{subfigure}{0.42\textwidth}
+%          \caption{Financial cost (HTE)}
+%          \centering
+%          \includegraphics[width=\textwidth]{Figuras/he_dist_eff_cost_loan_pro_2.pdf}
+%      \end{subfigure}
+%     ~
+%     ~
+%     \bigskip
+%     \begin{subfigure}{0.42\textwidth}
+%         \caption{Lost pawn}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/def_te_pro_2.pdf}
+%     \end{subfigure}
+%     \begin{subfigure}{0.42\textwidth}
+%     \caption{Losing Pawn}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_2.pdf}
+%     \end{subfigure}
+
+%     \end{center}
+%         \scriptsize
+
+%       %\textit{Do file: }  \texttt{eff\_te.do, def\_te.do, eff\_quantilereg.do}
+% \end{figure}
+
+\vspace{3ex}
+
+\vspace{.3in}
+\begin{figure}[H]
+        \caption{Effects on repeat purchasing}
+    \label{reincidence}
+    \begin{center}
+        \centering
+        \includegraphics[width=0.6\textwidth]{re_te.pdf}
+    \end{center}
+     \scriptsize This figure shows the estimated effects on repeat purchasing of the four treatment arms (Forced Commitment, choice-fee, fee-promise, choice-promise) compared to the status-quo control group.
+It shows robustness of the effects by focusing on different sub-populations.
+The leftmost coefficient compares all the Forced Commitment group against all status quo group.
+The second coefficient conditions on the first pawn not being recovered when the second was pawned.
+The third coefficient conditions on clients who pawned again after having recovered the pawn in the experiment.
+The fourth coefficient uses all clients (in both the Forced Commitment and the status-quo arms) who had an estimated heterogeneous treatment effect above the median.
+Conditioning on this set keeps the sample balanced across arms and therefore still allows for a causal interpretation.
+For the choice arm we present three coefficients: coefficients represented by a circle compare all those offered choice to all those in the status quo arm, thus estimating a causal effect.
+Coefficients in triangles and squares represent those that self-select into the fee or promise arms and compare this subset against the whole status quo arm.
+They therefore contain a selection effect together with the treatment effect and cannot be interpreted causally.
+      %\footnotesize{ \textit{Do file: }  \texttt{re\_te.do}
+\end{figure}
+
+%\begin{figure}[H]
+%        \caption{Distribution of Overconfidence}
+%    \label{oc_hist}
+%    \begin{center}
+%        \centering
+%        \includegraphics[width=0.55\textwidth]{Figuras/oc_hist.pdf}
+%    \end{center}
+%    \scriptsize
+%     In the baseline survey at the branch, before the client knew the contract or had the pawn appraised, they were asked from 0 to 100, how likely it was that they would be able to recover their pawn if pawned.
+We generate a variable we call overconfidence (OC) defined as the reported subjective probability of recovery minus the predicted probability ($P^s_i-\widehat{P_i(X_i)}$).
+We predict $\widehat{P_i(X_i)}$ using LASSO as explained in the text.
+This figure uses all observations for which we have data on $P^s_i$ and $X_i$ from the baseline survey.
+     %\textit{Do file: }  \texttt{oc.do}
+
+%\end{figure}
 

### 2022-02-26 RScripts/te_grf.R

@@ -249,6 +249,7 @@ te_grf <- function(data_in, outcome_var, name) {
 # READ DATASET
 fc <- read_csv('./_aux/fc_te_heterogeneity.csv') 
 eff <- read_csv('./_aux/eff_te_heterogeneity.csv') 
+apr <- read_csv('./_aux/apr_te_heterogeneity.csv') 
 def <- read_csv('./_aux/def_te_heterogeneity.csv') 
 des <- read_csv('./_aux/des_te_heterogeneity.csv') 
 sumporcp <- read_csv('./_aux/sumporcp_te_heterogeneity.csv') 
@@ -258,6 +259,7 @@ sumporcp <- read_csv('./_aux/sumporcp_te_heterogeneity.csv')
 
 te_grf(fc,"fc_admin","fc") 
 te_grf(eff,"eff_cost_loan","eff") 
+te_grf(apr,"apr","apr") 
 te_grf(def,"def_c","def") 
 te_grf(des,"des_c","des") 
 te_grf(sumporcp,"sum_porcp_c","sumporcp") 

### 2022-03-10 OA.tex
Learning by not doing analysis & replace eff_cost_loan with APR

@@
 
-\begin{figure}[H]
-        \caption{FC as \% of loan - treatment effect}
-    \label{fc_pro_2_115}
-    \begin{center}
-        \centering
-        \includegraphics[width=0.50\textwidth]{Figuras/fc_te_115_pro_2.pdf}
-    \end{center}
-     \scriptsize This figure is the same as in Figure \ref{fc_pro2} Panel (a), but with the subsample restricted to the first 115 days.
-     %\textit{Do file: }  \texttt{fc\_te\_115.do}
-\end{figure}
-
-\begin{figure}[H]
-        \caption{Financial cost effect: charging all fees}
-    \label{fc_allfee}
-    \begin{center}
-        \centering
-        \includegraphics[width=0.50\textwidth]{Figuras/fc_allfee_quantile_pro_2.pdf}
-    \end{center}
-    \scriptsize
-     This figure is the analogous to Figure \ref{fc_pro2}(b), except that for the fee-forcing contract we pretend that all clients incurred in their late fees, and therefore inflate the financial cost by summing those fees.
+% \begin{figure}[H]
+%         \caption{FC restricted to 115 days}
+%     \label{fc_pro_2_115}
+%     \begin{center}
+%         \centering
+%         \includegraphics[width=0.50\textwidth]{Figuras/fc_te_115_pro_2.pdf}
+%     \end{center}
+%      \scriptsize This figure is the same as in Figure \ref{fc_pro2} Panel (a), but with the subsample restricted to the first 115 days.
+%      %\textit{Do file: }  \texttt{fc\_te\_115.do}
+% \end{figure}
+
+% \begin{figure}[H]
+%         \caption{Financial cost effect: charging all fees}
+%     \label{fc_allfee}
+%     \begin{center}
+%         \centering
+%         \includegraphics[width=0.50\textwidth]{Figuras/fc_allfee_quantile_pro_2.pdf}
+%     \end{center}
+%     \scriptsize
+%      This figure is the analogous to Figure \ref{fc_pro2}(b), except that for the fee-forcing contract we pretend that all clients incurred in their late fees, and therefore inflate the financial cost by summing those fees.
 This is intended as a kind of worse case scenario for the financial cost of the fee-forcing contract.
@@
 We still find that the financial cost of will be smaller under the fee-forcing contract in spite of artificially inflating it.
-     %\texttt{fc\_all\_fee.do}
-\end{figure}
-
-\begin{figure}[H]
-        \caption{FC as \% of loan - treatment effect}
-    \label{fc_perc}
-    \begin{center}
-        \centering
-        \includegraphics[width=0.50\textwidth]{Figuras/fc_perc_te_allarms.pdf}
-    \end{center}
-     \scriptsize This figure shows the estimated treatment effect of all arms against the status quo, but normalizing the dependent variable by the value of the loan.
-     %\textit{Do file: }  \texttt{fc\_perc\_allarms.do}
-\end{figure}
+%      %\texttt{fc\_all\_fee.do}
+% \end{figure}
+
+% \begin{figure}[H]
+%         \caption{FC as \% of loan - treatment effect}
+%     \label{fc_perc}
+%     \begin{center}
+%         \centering
+%         \includegraphics[width=0.50\textwidth]{Figuras/fc_perc_te_allarms.pdf}
+%     \end{center}
+%      \scriptsize This figure shows the estimated treatment effect of all arms against the status quo, but normalizing the dependent variable by the value of the loan.
+%      %\textit{Do file: }  \texttt{fc\_perc\_allarms.do}
+% \end{figure}
 
@@
 \begin{figure}[H]
-        \caption{Empirical CDF of Financial Cost: fee-focing vs status-quo}
+        \caption{Empirical CDF of APR: fee-focing vs status-quo}
     \label{ecdf_fc}
@@
 \begin{figure}[H]
-        \caption{Honest causal tree for the fee forcing contract heterogenous treatment effects}
+        \caption{Honest causal tree for the Forced-commitment contract heterogeneous treatment effects}
     \label{casual_tree}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{Figuras/crf_pro_2_fc_admin_disc.pdf}
+        \includegraphics[width=\textwidth]{Figuras/crf_pro_2_apr.pdf}
     \end{center}
@@
 \begin{figure}[H]
-    \caption{Heterogeneous Treatment Effect: Fee-forcing contract}
-    \label{HTE_fee_forcing}
-    \begin{center}
-    %\begin{subfigure}{0.4\textwidth}
-    %    \caption{Financial cost}
-    %    \centering
-    %    \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_2.pdf}
-    %\end{subfigure}
-    \begin{subfigure}{0.7\textwidth}
-        \caption{Determinants of effects}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_fc_admin_disc_pro_2.pdf}
-    \end{subfigure}
-
-    %\begin{subfigure}{0.4\textwidth}
-    %    \caption{Losing Pawn}
-    %    \centering
-    %    \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_2.pdf}
-    %\end{subfigure}
-    %\begin{subfigure}{0.4\textwidth}
-    %    \caption*{}
-    %    \centering
-    %    \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_def_c_pro_2.pdf}
-    %\end{subfigure}
-    \end{center}
-     \scriptsize  This figure estimates bivariate regressions of the estimated client-level heterogeneous treatment effects against the respective covariate from the baseline survey  $\widehat{hte_i} = \alpha + \beta \: X_i + \epsilon_i$.
+        \caption{Single causal tree for the Forced-commitment contract heterogeneous treatment effects}
+    \label{casual_tree}
+    \begin{center}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/ct_pro_2_apr.pdf}
+    \end{center}
+    \footnotesize
+
+     %\footnotesize{ \textit{RScript: }  \texttt{grf.R}
+\end{figure}
+
+% \begin{figure}[H]
+%     \caption{Heterogeneous Treatment Effect: Fee-forcing contract}
+%     \label{HTE_fee_forcing}
+%     \begin{center}
+%     %\begin{subfigure}{0.4\textwidth}
+%     %    \caption{Financial cost}
+%     %    \centering
+%     %    \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_2.pdf}
+%     %\end{subfigure}
+%     \begin{subfigure}{0.7\textwidth}
+%         \caption{Determinants of effects}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_fc_admin_disc_pro_2.pdf}
+%     \end{subfigure}
+
+%     %\begin{subfigure}{0.4\textwidth}
+%     %    \caption{Losing Pawn}
+%     %    \centering
+%     %    \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_2.pdf}
+%     %\end{subfigure}
+%     %\begin{subfigure}{0.4\textwidth}
+%     %    \caption*{}
+%     %    \centering
+%     %    \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_def_c_pro_2.pdf}
+%     %\end{subfigure}
+%     \end{center}
+%      \scriptsize  This figure estimates bivariate regressions of the estimated client-level heterogeneous treatment effects against the respective covariate from the baseline survey  $\widehat{hte_i} = \alpha + \beta \: X_i + \epsilon_i$.
 The regressors $X_i$ include (e.g if the family asks for money, if they have savings, if they are overconfident using the definition the text, etc.
 See this Appendix for a transcription of the survey).
-      %\footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}}
-\end{figure}
+%       %\footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}}
+% \end{figure}
 
@@
         \centering
-        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_eff_cost_loan_pro_2.pdf}
+        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_apr_pro_2.pdf}
     \end{subfigure}
@@
 
-\begin{figure}[H]
-    \caption{Treatment effects pooling all arms}
-    \label{pooled_arms_te}
-    \begin{center}
-    \begin{subfigure}{0.45\textwidth}
-        \caption{Financial Cost}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/te_allarms_fc_admin_disc.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.45\textwidth}
-        \caption{Lost Pawn}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/te_allarms_def_c.pdf}
-    \end{subfigure}
-    \end{center}
-     \scriptsize
-      %\footnotesize{ \textit{Do file: }  \texttt{te\_allarms.do}}
-\end{figure}
+% \begin{figure}[H]
+%     \caption{Treatment effects pooling all arms}
+%     \label{pooled_arms_te}
+%     \begin{center}
+%     \begin{subfigure}{0.45\textwidth}
+%         \caption{Financial Cost}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/te_allarms_fc_admin_disc.pdf}
+%     \end{subfigure}
+%     \begin{subfigure}{0.45\textwidth}
+%         \caption{Lost Pawn}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/te_allarms_def_c.pdf}
+%     \end{subfigure}
+%     \end{center}
+%      \scriptsize
+%       %\footnotesize{ \textit{Do file: }  \texttt{te\_allarms.do}}
+% \end{figure}
 

### 2022-03-10 donde.tex
Learning by not doing analysis & replace eff_cost_loan with APR

@@
 Second, the existence of commitment-style repayment contracts in pawnshop lending is novel in Mexico.
-While forcing individuals into commitment does not cause them to demand it in subsequent loans, \textcolor{red}{in Table \ref{iv_pf}} we show observational evidence of `learning by not doing’:  individuals offered commitment who elect not to take it and subsequently default \textit{do} learn about the benefits of commitment, demanding commitment loans at higher rates on subsequent pawn contracts when given the choice.
+While forcing individuals into commitment does not cause them to demand it in subsequent loans, \textcolor{red}{in Table \ref{iv_pf}} we show observational evidence of `learning by not doing’:  individuals offered commitment who elect not to take it \textcolor{red}{and subsequently default} \textit{do} learn about the benefits of commitment, demanding commitment loans at higher rates on subsequent pawn contracts when given the choice.
 Finally, while we are working with a lender who has a social mission and is interested in understanding how to help borrowers, there is no free lunch.
@@
 Figure \ref{main_te} gives the  effect sizes (in standard deviations) of the two main study arms for three outcomes:  default, the financial cost of the loan, and the effective interest rate paid to acquire the borrowed capital.
-Very clearly, the Forced arm is significant for all three outcomes, with very substantial treatment effects in magnitudes for default and APR, and the commitment arm is never significant.\footnote{The slight increase in APR for the Choice arm seen in this picture arises from the fact that the APR calculation has the arm-specific loan size in the denominator, and the loans in the Choice arm turn out to be slightly larger on average than the Control.}    In other words, voluntary commitment is ineffective but the use of forced commitment saves the average borrower an amount of money almost twice the APR of a normal US credit card loan.
+Very clearly, the Forced arm is significant for all three outcomes, with very substantial treatment effects in magnitudes for default and APR, and the commitment arm is never significant.\footnote{The slight increase in APR for the Choice arm seen in this picture arises from the fact that the APR calculation has the arm-specific loan size in the denominator, and the loans in the Choice arm turn out to be slightly smaller (although statistically equal) on average than the Control.}    In other words, voluntary commitment is ineffective but the use of forced commitment saves the average borrower an amount of money almost twice the APR of a normal US credit card loan.
 
 There are other intermediate outcomes that are impacted by being assigned to frequent payments.
-Table \ref{mechanisms} shows that the first payment happens 8 days earlier (column 1) in the Forced Commitment arm than in the status quo one, and that the number of payments increases by 0.19 (column 2).% Figure \ref{induced_to_pay_early} in the correlates HTE on financing cost with the HTE time of first payment and shows that those induced to pay earlier are also those that have larger induced reduction in financial cost.
-Treatment effects are concentrated on the intensive margin, as treatment does \textit{not} affect the fraction of clients who pay a positive amount (column 6).
-The percentage of the loan paid increases by 8 percentage points on average (column 7).
-However the percentage of the loan paid is not larger for those that end up losing the pawn (first row of column 8).
+Table \ref{mechanisms} shows that the first payment happens 8 days earlier (column 1) in the Forced Commitment arm than in the status quo one, and that the number of payments increases by 0.19 (column 4).
+Treatment effects are concentrated on the intensive margin, as treatment does \textit{not} affect the fraction of clients who pay nothing (column 12).
+The percentage of the loan paid increases by 9 percentage points on average (column 9).
+Moreover, the percentage of the loan paid is even smaller for those that end up losing the pawn (first row of column 9).
 This last point is critical; this intervention has the potential to do financial harm if it caused individuals to make more payments on loans for which they would end up defaulting.
@@
 The results show that the Choice arm is no more likely to pawn again, which the Forced arm is X\% more likely to take a second loan.
-While this appears to be \texit{prima facie} evidence of greater satisfaction with the lender, interpretation here is complicated by the fact that they were so much more likely to have recovered their pawn and hence to be able to pawn it again.
+While this appears to be \textit{prima facie} evidence of greater satisfaction with the lender, interpretation here is complicated by the fact that they were so much more likely to have recovered their pawn and hence to be able to pawn it again.
 We can explore this possibility in a number of ways.
@@
 needing to go to the hospital), and it is unclear why clients in the frequent payment arm wait for several months to re-pawn -- there is no effect of the monthly payment contract on repeat pawning in the first 30 or 60 days of the contract, (see Figure \ref{reincidence_before} in Appendix).
-First,  there are many alternatives lenders in this market, and if they did not like frequent payments why do they come back to Lender $P$ for another loan?
+First,  there are many alternative lenders in this market, and if they did not like frequent payments why do they come back to Lender $P$ for another loan?
 Second, the fee is really small at 2\% of 1/3 of the value of the loan.
@@
 Nonetheless, we find Soft Commitment, whether chosen or induced, to be completely ineffective in this environment.
-Table \ref{impact_soft} and  Figure \ref{fc_pro5}(a) finds that assigning clients to the choice-promise condition has a zero effect on financial cost on average (circles).
-We see no difference even for the endogenous group that \textit{chose} to promise (squares).
-This null effect happens not only on average, but also by percentiles (not shown in Figure).
-There is also no effect on pawn recovery on (first coefficient in Figure \ref{fc_pro5}(b)), even for those that themselves choose to promise.
+Table \ref{impact_soft} and  Figure \ref{effect_promises} finds that assigning clients to the choice-promise condition has a zero effect on financial cost, recovery, and the effective APR on average (Panel (a)).
+We see no difference even for the endogenous group that \textit{chose} to promise.
+This null effect happens not only on average, but also by percentiles (Figure \ref{qreg_chooser_nonchooser}, panels (c) \& (d)).
+% There is also no effect on pawn recovery on (first coefficient in Figure \ref{fc_pro5}(b)), even for those that themselves choose to promise.
 And the null effect carries over if we use the definition of recovery in less than 120 days, or for the (endogenous) subgroups that paid a positive amount.
@@
 
-$$ToT = \frac{\beta^C}{p}; \hspace{15} TuT = \frac{(\beta^F - \beta^C)}{(1-p)}; \hspace{15} (ToT-TuT) = \frac{\beta^C}{p}- \frac{(\beta^F - \beta^C)}{(1-p)}. $$
+\[ToT = \frac{\beta^C}{p}; \hspace{15} TuT = \frac{(\beta^F - \beta^C)}{(1-p)}; \hspace{15} (ToT-TuT) = \frac{\beta^C}{p}- \frac{(\beta^F - \beta^C)}{(1-p)}. \]
 
@@
 
-\textcolor{red}{Discussion to be fortified with updated table}
+\textcolor{red}{Discussion to be fortified with updated table}\ref{tot_tut}
 
@@
 \begin{center}
-\scriptsize{\input{./Tables/tot_tut_iv.tex}}
+\scriptsize{\input{./Tables/tot_tut_reg.tex}}
 \end{center}
  \scriptsize This table shows estimates of the ToT and the TuT with an IV-LATE framework.
-The ToT (columns (1)-(3)) is computed as the usual LATE with one-sided non-compliance between the choice and control arm, and the TuT (columns (4)-(6)) is the LATE on non-compliers.
-Columns (6) and (7) estimates the effect of the compliers on the estimated HTE calculated with the Causal Random Forest.
+The ToT is computed as the usual LATE with one-sided non-compliance between the choice and control arm, and the TuT is the LATE on non-compliers.
 %\textit{Do file: } \texttt{tot\_tut\_reg.do}
+\end{table}
+
+\begin{table}[H]
+\caption{Learning analysis with experimental data}
+\label{learning_reg}
+\begin{center}
+\scriptsize{\input{./Tables/learning_exp.tex}}
+\end{center}
+ \scriptsize This table shows choice after experience of an experimental arm in the previous loan.
+Columns (1)-(4) restrict the sample to borrowers whose second loan falls in the Choice commitment arm.
+Dependent variable in columns (5)-(8) is `ever chooses commitment', a dummy variable defined to be $0$ if borrower didn't take a loan, or if borrower took a loan and didn't choose commitment, and it is $1$ only when borrower took a loan and chose commitment.
+%\textit{Do file: } \texttt{learning\_reg.do}
+\end{table}
+
+\begin{table}[H]
+\caption{Differential attrition}
+\label{diff_att}
+\begin{center}
+\scriptsize{\input{./Tables/differential_attrition.tex}}
+\end{center}
+ \scriptsize This table shows differential attrition in the experimental arms for (1) experiencing a second arm and (2) when the second loan is a Choice commitment arm.
+%\textit{Do file: } \texttt{learning\_reg.do}
 \end{table}
@@
 \begin{figure}[H]
+     \caption{Quantile regressions}
+    \label{qregs}
+    \begin{center}
+    \begin{subfigure}{.45\textwidth}
+      \caption{Financial cost (in MXN)}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/qreg_fc_admin.pdf}
+    \end{subfigure}
+     \begin{subfigure}{0.45\textwidth}
+    \caption{Effective APR}
+       \centering
+      \includegraphics[width=\textwidth]{Figuras/qreg_apr.pdf}
+    \end{subfigure}
+    \end{center}
+         \scriptsize
+     This figure plots the effects on different quantiles (15th, 25th, 50th, 75th, 85th percentile) of the distribution of financial cost, and APR, for the Forced-commitment and Choice-commitment arms.
+      %\footnotesize{ } \textit{Do file: }  \texttt{main\_qreg.do}
+\end{figure}
+
+\begin{figure}[H]
      \caption{Effect of promises}
@@
 Panels (c) \& (d) show treatment effects on different quantiles for the Financial Cost and APR.
-\end{figure}
-
-\begin{figure}[H]
-     \caption{Quantile regressions}
-    \label{qregs}
-    \begin{center}
-    \begin{subfigure}{.45\textwidth}
-      \caption{Financial cost (in MXN)}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/qreg_fc_admin.pdf}
-    \end{subfigure}
-     \begin{subfigure}{0.45\textwidth}
-    \caption{Effective APR}
-       \centering
-      \includegraphics[width=\textwidth]{Figuras/qreg_apr.pdf}
-    \end{subfigure}
-    \end{center}
-         \scriptsize
-     This figure plots the effects on different quantiles (15th, 25th, 50th, 75th, 85th percentile) of the distribution of financial cost, and APR, for the Forced-commitment and Choice-commitment arms.
-      %\footnotesize{ } \textit{Do file: }  \texttt{main\_qreg.do}
 \end{figure}
@@
        \centering
-      \includegraphics[width=\textwidth]{Figuras/he_dist_eff_cost_loan_pro_2.pdf}
+      \includegraphics[width=\textwidth]{Figuras/he_dist_apr_pro_2.pdf}
     \end{subfigure}

### 2022-03-10 RScripts/grf.R

@@ -30,7 +30,7 @@ heterogeneity_effect <- function(data_in,treatment_var,outcome_var,writedata,ext
   data_frame <- data_in %>%
     filter(data_in[,treatment_var] == 1 | data_in[,treatment_var] == 0) %>%
     select(-c( pro_2, pro_3, pro_4, pro_5, pro_6, pro_7, pro_8, pro_9, fee, fecha_inicial,
-               eff_cost_loan, def_c, des_c, fc_admin_disc, fc_survey_disc, fc_admin, fc_survey, dias_primer_pago), 
+               apr, eff_cost_loan, def_c, des_c, fc_admin), 
            treatment_var, outcome_var ) %>%
     mutate_all(~ifelse(is.na(.), median(., na.rm = TRUE), .))  
   data_copy <- data_frame
@@ -284,7 +284,7 @@ data <- read_csv('./_aux/heterogeneity_grf.csv')
 
 #Heterogeneous Effects
 for (arm in c("pro_2")){
-  for (dep in c("eff_cost_loan", "def_c", "des_c", "fc_admin")){
+  for (dep in c("apr", "eff_cost_loan", "def_c", "des_c", "fc_admin")){
     heterogeneity_effect(data_extended,arm,dep,1,1) 
     heterogeneity_effect(data,arm,dep,1,0) 
   }
@@ -292,5 +292,5 @@ for (arm in c("pro_2")){
 
 
 # Plot tree with names in english
-heterogeneity_effect(data,"pro_2","eff_cost_loan",0,0) 
+heterogeneity_effect(data,"pro_2","apr",0,0) 
 

### 2022-03-17 donde.tex
tot tut graph
repeat loans analysis

@@
 \begin{align*}
-ToT \equiv \mathbb{E}[Y_1 - Y_0 \;\mid\; C=1]  &=   \frac{\mathbb{E}[Y \;\mid\; Z=2] - \mathbb{E}[Y \;\mid\; Z=0)}{p} \\
+ToT \equiv \mathbb{E}[Y_1 - Y_0 \;\mid\; C=1]  &=   \frac{\mathbb{E}[Y \;\mid\; Z=2] - \mathbb{E}[Y \;\mid\; Z=0]}{p} \\
 TuT \equiv \mathbb{E}[Y_1 - Y_0 \;\mid \;C=0]  &=  \frac{\mathbb{E}[Y \;\mid\; Z=1] - \mathbb{E}[Y \;\mid\; Z=2]}{(1-p)} 
@@
 Table \ref{tot_tut} shows the results of this analysis.
-Across the board, the TuT is greater than the ToT which illustrates that the `wrong' people are choosing commitment in terms of direct financial cost.\footnote{It is worth noting that the statistical power of these estimands is driven by the compliance rate; given our low overall compliance we are better powered to measure the TuT than the ToT, and the power for the difference between the two would be highest with a compliance rate of 50\%.}
-
-\textcolor{red}{Discussion to be fortified with updated table}\ref{tot_tut}
+Given that the ITT results for the Choice arm imply an insignificant worsening of outcomes relative to the control, our estimates of the Treatment on the Treated in the first row of the bottom panel show negative results that are larger in absolute magnitude (multiplied by \~9, the inverse of the compliance rate) and similarly insignificant.
+The Treatment on the Untreated (TuT), conversely, is strongly positive across the board, and indicates a significant improvement for all outcomes (here ITTs are multiplied by 1.12, the inverse of the non-compliance rate).
+Most novel is the ability to form a test of the difference between the ToT and the TuT, which is conducted in the bottom rows of the table.
+We provide four different ways of estimating p-values; the standard clustered estimates motivated by the experimental design, normal and percentile bootstraps, and randomization inference.
+The differences between treatment effects for compliers and non-compliers are of borderline significance in some of the unadjusted specifications, but are not significant once adjusted.\footnote{It is worth noting that the statistical power of these estimands is driven by the compliance rate; given our low overall compliance we are better powered to measure the TuT than the ToT, and the power for the difference between the two would be highest with a compliance rate of 50\%.}
 
@@
 
-\begin{table}[H]
-\caption{Learning analysis with experimental data}
-\label{learning_reg}
-\begin{center}
-\scriptsize{\input{./Tables/learning_exp.tex}}
-\end{center}
- \scriptsize This table shows choice after experience of an experimental arm in the previous loan.
+% \begin{table}[H]
+% \caption{Learning analysis with experimental data}
+% \label{learning_reg}
+% \begin{center}
+% \scriptsize{\input{./Tables/learning_exp.tex}}
+% \end{center}
+%  \scriptsize This table shows choice after experience of an experimental arm in the previous loan.
 Columns (1)-(4) restrict the sample to borrowers whose second loan falls in the Choice commitment arm.
 Dependent variable in columns (5)-(8) is `ever chooses commitment', a dummy variable defined to be $0$ if borrower didn't take a loan, or if borrower took a loan and didn't choose commitment, and it is $1$ only when borrower took a loan and chose commitment.
-%\textit{Do file: } \texttt{learning\_reg.do}
-\end{table}
-
-\begin{table}[H]
-\caption{Differential attrition}
-\label{diff_att}
-\begin{center}
-\scriptsize{\input{./Tables/differential_attrition.tex}}
-\end{center}
- \scriptsize This table shows differential attrition in the experimental arms for (1) experiencing a second arm and (2) when the second loan is a Choice commitment arm.
-%\textit{Do file: } \texttt{learning\_reg.do}
-\end{table}
+% %\textit{Do file: } \texttt{learning\_reg.do}
+% \end{table}
+
+% \begin{table}[H]
+% \caption{Differential attrition}
+% \label{diff_att}
+% \begin{center}
+% \scriptsize{\input{./Tables/differential_attrition.tex}}
+% \end{center}
+%  \scriptsize This table shows differential attrition in the experimental arms for (1) experiencing a second arm and (2) when the second loan is a Choice commitment arm.
+% %\textit{Do file: } \texttt{learning\_reg.do}
+% \end{table}
 
@@
       %\textit{Do file: }  \texttt{fc\_te\_choice\_dec.do, def\_te\_choice\_dec.do, fc\_quantilereg\_choice\_dec.do}
+\end{figure}
+
+\begin{figure}[H]
+     \caption{ToT \& TuT as LATE}
+    \label{tot_tut_graph}
+    \begin{center}
+    \begin{subfigure}{0.9\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/tot_tut_apr.eps}
+    \end{subfigure}
+    \end{center}
+    \scriptsize
+    This figure shows 
 \end{figure}
@@
 
-\newpage
-
-\input{OA.tex}
+%\newpage
+
+%\input{OA.tex}
 

### 2022-03-24 OA.tex
_learning over time & fix choose_wrong & fix distcomp_

@@
 
+\begin{table}[H]
+\caption{Effects on several definitions of cost - Soft arms}
+\label{table_robustness_fc_soft}
+\begin{center}
+\scriptsize{\input{./Tables/fc_robustness_soft.tex}}
+\end{center}
+ \scriptsize
+
+%\textit{Do file: } \texttt{fc\_robustness\_soft.do}
+\end{table}
+
+\begin{landscape}
+
+\begin{table}[H]
+\caption{Intermediate outcomes - Soft arms}
+\label{mechanisms_soft}
+\begin{center}
+\scriptsize{\input{./Tables/mechanism_soft.tex}}
+\end{center}
+
+%\textit{Do file: } \texttt{mechanisms\_soft.do}
+\end{table}
+
+\end{landscape}
+
+\cleardoublepage
+
 % \begin{figure}[H]
@@
 
-\begin{figure}[H]
-        \caption{Repeat purchase before 30/60 days}
-    \label{reincidence_before}
-    \begin{center}
-        \centering
-        \includegraphics[width=0.50\textwidth]{Figuras/re_te_earlydays.pdf}
-    \end{center}
-     \scriptsize This figure shows the estimated treatment effect of repeat purchase before 30 \& 60 days.
-     %\textit{Do file: }  \texttt{re\_te\_earlydays.do}
-\end{figure}
+% \begin{figure}[H]
+%         \caption{Repeat purchase before 30/60 days}
+%     \label{reincidence_before}
+%     \begin{center}
+%         \centering
+%         \includegraphics[width=0.50\textwidth]{Figuras/re_te_earlydays.pdf}
+%     \end{center}
+%      \scriptsize This figure shows the estimated treatment effect of repeat purchase before 30 \& 60 days.
+%      %\textit{Do file: }  \texttt{re\_te\_earlydays.do}
+% \end{figure}
 
@@
 
-\begin{comment}
-\begin{figure}[H]
-    \caption{Heterogeneous Treatment Effect: Promise-forcing contract}
-    \label{heterogeneous_te_3}
-    \begin{center}
-    \begin{subfigure}{0.4\textwidth}
-        \caption{Financial cost}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_3.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.4\textwidth}
-        \caption*{}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_fc_admin_disc_pro_3.pdf}
-    \end{subfigure}
-
-    \begin{subfigure}{0.4\textwidth}
-        \caption{Losing Pawn}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_3.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.4\textwidth}
-        \caption*{}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_def_c_pro_3.pdf}
-    \end{subfigure}
-    \end{center}
-     \scriptsize
-      %\footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}}
-\end{figure}
-\end{comment}
-
-\begin{comment}
-
-\begin{figure}[H]
-    \caption{Heterogeneous Treatment Effect - Choice/Fee}
-    \label{heterogeneous_te_4}
-    \begin{center}
-    \begin{subfigure}{0.4\textwidth}
-        \caption{Financial cost}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_4.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.4\textwidth}
-        \caption*{}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_fc_admin_disc_pro_4.pdf}
-    \end{subfigure}
-
-    \begin{subfigure}{0.4\textwidth}
-        \caption{Losing Pawn}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_4.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.4\textwidth}
-        \caption*{}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_def_c_pro_4.pdf}
-    \end{subfigure}
-    \end{center}
-     \footnotesize \textit{Notes: } The distribution plots the FC treatment effect for the interval $[\mu-2\sigma,\mu+2\sigma]$ to ignore the outliers.
-      \footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}}
-\end{figure}
-
-\begin{figure}[H]
-    \caption{Heterogeneous Treatment Effect - Choice/Promise}
-    \label{heterogeneous_te_5}
-    \begin{center}
-    \begin{subfigure}{0.4\textwidth}
-        \caption{Financial cost}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_5.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.4\textwidth}
-        \caption*{}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_fc_admin_disc_pro_5.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.4\textwidth}
-        \caption{Losing Pawn}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_5.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.4\textwidth}
-        \caption*{}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_def_c_pro_5.pdf}
-    \end{subfigure}
-    \end{center}
-     \footnotesize \textit{Notes: } 
-      \footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}}
-\end{figure}
-
-\end{comment}
+% \begin{figure}[H]
+%     \caption{Heterogeneous Treatment Effect: Promise-forcing contract}
+%     \label{heterogeneous_te_3}
+%     \begin{center}
+%     \begin{subfigure}{0.4\textwidth}
+%         \caption{Financial cost}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_3.pdf}
+%     \end{subfigure}
+%     \begin{subfigure}{0.4\textwidth}
+%         \caption*{}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_fc_admin_disc_pro_3.pdf}
+%     \end{subfigure}
+
+%     \begin{subfigure}{0.4\textwidth}
+%         \caption{Losing Pawn}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_3.pdf}
+%     \end{subfigure}
+%     \begin{subfigure}{0.4\textwidth}
+%         \caption*{}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_def_c_pro_3.pdf}
+%     \end{subfigure}
+%     \end{center}
+%      \scriptsize
+%       %\footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}}
+% \end{figure}
+
+% \begin{figure}[H]
+%     \caption{Heterogeneous Treatment Effect - Choice/Fee}
+%     \label{heterogeneous_te_4}
+%     \begin{center}
+%     \begin{subfigure}{0.4\textwidth}
+%         \caption{Financial cost}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_4.pdf}
+%     \end{subfigure}
+%     \begin{subfigure}{0.4\textwidth}
+%         \caption*{}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_fc_admin_disc_pro_4.pdf}
+%     \end{subfigure}
+
+%     \begin{subfigure}{0.4\textwidth}
+%         \caption{Losing Pawn}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_4.pdf}
+%     \end{subfigure}
+%     \begin{subfigure}{0.4\textwidth}
+%         \caption*{}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_def_c_pro_4.pdf}
+%     \end{subfigure}
+%     \end{center}
+%      \footnotesize \textit{Notes: } The distribution plots the FC treatment effect for the interval $[\mu-2\sigma,\mu+2\sigma]$ to ignore the outliers.
+%       \footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}}
+% \end{figure}
+
+% \begin{figure}[H]
+%     \caption{Heterogeneous Treatment Effect - Choice/Promise}
+%     \label{heterogeneous_te_5}
+%     \begin{center}
+%     \begin{subfigure}{0.4\textwidth}
+%         \caption{Financial cost}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_5.pdf}
+%     \end{subfigure}
+%     \begin{subfigure}{0.4\textwidth}
+%         \caption*{}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_fc_admin_disc_pro_5.pdf}
+%     \end{subfigure}
+%     \begin{subfigure}{0.4\textwidth}
+%         \caption{Losing Pawn}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_5.pdf}
+%     \end{subfigure}
+%     \begin{subfigure}{0.4\textwidth}
+%         \caption*{}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_def_c_pro_5.pdf}
+%     \end{subfigure}
+%     \end{center}
+%      \footnotesize \textit{Notes: } 
+%       \footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}}
+% \end{figure}
 
@@
 \subsection{New results}
-\begin{figure}[H]
-        \caption{Financial cost for different discount rates}
-    \label{fc_discount_rates}
-    \begin{center}
-        \centering
-        \includegraphics[width=0.55\textwidth]{Figuras/discount_effect.pdf}
-    \end{center}
-     \scriptsize This Figure estimates the treatment effect on financial cost with different discount rates.  
-     %\textit{Do file: }  \texttt{discounted\_noeffect.do}
-\end{figure}
 
@@
 
-\scriptsize {
-\noindent This Figure shows the treatment effects for the main outcomes when pooling all arms in the same regression.
-}
-
-\begin{figure}[H]
-        \caption{Treatment effect decomposition of the Financial Cost }
-    \label{reg_int_pro_2}
-    \begin{center}
-        \centering
-        \includegraphics[width=0.60\textwidth]{Figuras/int_te_pro_2.pdf}
-    \end{center}
-     \scriptsize This Figure is a "close-up" for the estimates found in Figure \ref{fc_pro2} - Panel (a).
+% \begin{figure}[H]
+%         \caption{Treatment effect decomposition of the Financial Cost }
+%     \label{reg_int_pro_2}
+%     \begin{center}
+%         \centering
+%         \includegraphics[width=0.60\textwidth]{Figuras/int_te_pro_2.pdf}
+%     \end{center}
+%      \scriptsize This Figure is a "close-up" for the estimates found in Figure \ref{fc_pro2} - Panel (a).
 It shows the treatment effects on payed \& incurred interest, the former defined as the actual interest payed, and the latter is the sum of all potential interests (for those pawns that were lost we calculate the interest generated until day 230).
@@
 Finally, we analyze this effect for the subsamples that recovers or loses the pawn.
-     %\textit{Do file: }  \texttt{reg_\int.do}
-\end{figure}
+%      %\textit{Do file: }  \texttt{reg_\int.do}
+% \end{figure}
 
@@
 
-\begin{figure}[H]
-    \caption{Histogram of payments}
-    \label{hist_payments}
-    \begin{center}
-    \begin{subfigure}{0.31\textwidth}
-        \caption{Status-quo}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_payments_sq.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.31\textwidth}
-        \caption{Forced commitment}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_payments_fc.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.31\textwidth}
-        \caption{Choice commitment}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_payments_cc.pdf}
-    \end{subfigure}    
-        \begin{subfigure}{0.31\textwidth}
-        \caption{Forced soft}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_payments_fs.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.31\textwidth}
-        \caption{Choice soft}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_payments_cs.pdf}
-    \end{subfigure} 
-    \end{center}
-     \scriptsize
-      %\footnotesize{ \textit{Do file: }  \texttt{hist\_payments.do}}
-\end{figure}
-
-\begin{figure}[H]
-        \caption{Survival graphs}
-    \label{survival_graph}
-    \begin{center}
-   \begin{subfigure}{0.45\textwidth}
-        \caption{Closed contracts}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/survival_graph_ended.pdf}
-    \end{subfigure} 
-       \begin{subfigure}{0.45\textwidth}
-        \caption{Recovery}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/survival_graph_unpledge.pdf}
-    \end{subfigure} 
-    \end{center}
-     \scriptsize  This Figure shows the accumulated percentage of recovery in time by treatment arm. 
-     %\textit{Do file: }  \texttt{survival\_graph.do}
-\end{figure}
-
 %\begin{figure}[H]
@@
 
-\begin{comment}
-\begin{figure}[H]
-        \caption{Percentage of payments}
-    \label{perc_payments}
-    \begin{center}
-    \begin{subfigure}{.31\textwidth}
-    \caption{Control}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_1.pdf}
-    \end{subfigure}
-    \begin{subfigure}{.31\textwidth}
-    \caption{Forcing - fee}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_2.pdf}
-    \end{subfigure}   
-     \begin{subfigure}{.31\textwidth}
-    \caption{Forcing - promise}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_3.pdf}
-    \end{subfigure}  
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - fee}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_4.pdf}
-    \end{subfigure}  
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - fee - SQ}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_6.pdf}
-    \end{subfigure}    
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - fee - NSQ}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_7.pdf}
-    \end{subfigure}    
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - promise}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_5.pdf}
-    \end{subfigure}  
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - promise - SQ}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_8.pdf}
-    \end{subfigure}    
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - promise - NSQ}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_9.pdf}    
-    \end{subfigure}        
-    \end{center}
-     \footnotesize \textit{Notes: } 
-      \footnotesize{ \textit{Do file: }  \texttt{hist\_payments.do}}
-\end{figure}
-
-\begin{figure}[H]
-        \caption{Percentage of payment conditional on positive payment and Losing Pawn}
-    \label{perc_payments_conditional}
-    \begin{center}
-    \begin{subfigure}{.31\textwidth}
-    \caption{Control}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_1.pdf}
-    \end{subfigure}
-    \begin{subfigure}{.31\textwidth}
-    \caption{Forcing - fee}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_2.pdf}
-    \end{subfigure}   
-     \begin{subfigure}{.31\textwidth}
-    \caption{Forcing - promise}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_3.pdf}
-    \end{subfigure}  
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - fee}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_4.pdf}
-    \end{subfigure}  
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - fee - SQ}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_6.pdf}
-    \end{subfigure}    
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - fee - NSQ}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_7.pdf}
-    \end{subfigure}    
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - promise}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_5.pdf}
-    \end{subfigure}  
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - promise - SQ}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_8.pdf}
-    \end{subfigure}    
-     \begin{subfigure}{.31\textwidth}
-    \caption{Choice - promise - NSQ}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_9.pdf}    
-    \end{subfigure}        
-    \end{center}
-     \footnotesize \textit{Notes: } 
-      \footnotesize{ \textit{Do file: }  \texttt{hist\_payments.do}}
-\end{figure}
-\end{comment}
+% \begin{figure}[H]
+%         \caption{Percentage of payments}
+%     \label{perc_payments}
+%     \begin{center}
+%     \begin{subfigure}{.31\textwidth}
+%     \caption{Control}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_1.pdf}
+%     \end{subfigure}
+%     \begin{subfigure}{.31\textwidth}
+%     \caption{Forcing - fee}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_2.pdf}
+%     \end{subfigure}   
+%      \begin{subfigure}{.31\textwidth}
+%     \caption{Forcing - promise}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_3.pdf}
+%     \end{subfigure}  
+%      \begin{subfigure}{.31\textwidth}
+%     \caption{Choice - fee}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_4.pdf}
+%     \end{subfigure}  
+%      \begin{subfigure}{.31\textwidth}
+%     \caption{Choice - fee - SQ}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_6.pdf}
+%     \end{subfigure}    
+%      \begin{subfigure}{.31\textwidth}
+%     \caption{Choice - fee - NSQ}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_7.pdf}
+%     \end{subfigure}    
+%      \begin{subfigure}{.31\textwidth}
+%     \caption{Choice - promise}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_5.pdf}
+%     \end{subfigure}  
+%      \begin{subfigure}{.31\textwidth}
+%     \caption{Choice - promise - SQ}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_8.pdf}
+%     \end{subfigure}    
+%      \begin{subfigure}{.31\textwidth}
+%     \caption{Choice - promise - NSQ}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_9.pdf}    
+%     \end{subfigure}        
+%     \end{center}
+%      \footnotesize \textit{Notes: } 
+%       \footnotesize{ \textit{Do file: }  \texttt{hist\_payments.do}}
+% \end{figure}
+
+% \begin{figure}[H]
+%         \caption{Percentage of payment conditional on positive payment and Losing Pawn}
+%     \label{perc_payments_conditional}
+%     \begin{center}
+%     \begin{subfigure}{.31\textwidth}
+%     \caption{Control}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_1.pdf}
+%     \end{subfigure}
+%     \begin{subfigure}{.31\textwidth}
+%     \caption{Forcing - fee}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_2.pdf}
+%     \end{subfigure}   
+%      \begin{subfigure}{.31\textwidth}
+%     \caption{Forcing - promise}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_3.pdf}
+%     \end{subfigure}  
+%      \begin{subfigure}{.31\textwidth}
+%     \caption{Choice - fee}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_4.pdf}
+%     \end{subfigure}  
+%      \begin{subfigure}{.31\textwidth}
+%     \caption{Choice - fee - SQ}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_6.pdf}
+%     \end{subfigure}    
+%      \begin{subfigure}{.31\textwidth}
+%     \caption{Choice - fee - NSQ}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_7.pdf}
+%     \end{subfigure}    
+%      \begin{subfigure}{.31\textwidth}
+%     \caption{Choice - promise}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_5.pdf}
+%     \end{subfigure}  
+%      \begin{subfigure}{.31\textwidth}
+%     \caption{Choice - promise - SQ}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_8.pdf}
+%     \end{subfigure}    
+%      \begin{subfigure}{.31\textwidth}
+%     \caption{Choice - promise - NSQ}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_9.pdf}    
+%     \end{subfigure}        
+%     \end{center}
+%      \footnotesize \textit{Notes: } 
+%       \footnotesize{ \textit{Do file: }  \texttt{hist\_payments.do}}
+% \end{figure}
 
@@
 
-\begin{comment}
-
-\begin{figure}[H]
-        \caption{FC effect for different discount rates}
-    \label{oc_hist}
-    \begin{center}
-        \centering
-        \includegraphics[width=0.50\textwidth]{Figuras/discount_effect.pdf}
-    \end{center}
-    \footnotesize \textit{Notes: } 
-     \footnotesize{ \textit{Do file: }  \texttt{discounted\_noeffect.do}}
-\end{figure}
-\end{comment}
+% \begin{figure}[H]
+%         \caption{FC effect for different discount rates}
+%     \label{oc_hist}
+%     \begin{center}
+%         \centering
+%         \includegraphics[width=0.50\textwidth]{Figuras/discount_effect.pdf}
+%     \end{center}
+%     \footnotesize \textit{Notes: } 
+%      \footnotesize{ \textit{Do file: }  \texttt{discounted\_noeffect.do}}
+% \end{figure}
 

### 2022-03-24 donde.tex
_learning over time & fix choose_wrong & fix distcomp_

@@
 
-\vspace{.2in}
 \noindent \textbf{The Commitment Contract.} For the purpose of the experiment we designed a new contract that is identical to the status quo contract except that, informed by the behavioral literature on the ways to improve repayment in credit contracts, it enhances the regularity and salience of payments.
@@
 This turns out to be key for what we can learn from this experiment.
+
 In order to explore lower-cost forms of structure, we also include arms that feature `soft' commitment, asking or requiring individuals to follow the more regular payment structure of the commitment contract but then providing no reminders or repercussions for failing to do so.
+A substantial literature documents that people are averse to to breaking their promises, and are willing to incur in monetary losses in trying to keep them.
+This provides a potentially very attractive way to drive better repayment behavior at low pecuniary cost to clients.
+Numerous lab experiments and at least one field experiment on financial services show that such soft commitment can work \citep{Craig}.\footnote{Grameen Bank for instance makes clients recite a promise at each center weekly meeting.The exact promise repeated by clients live is this: ``\textit{We pledge to attend regularly the weekly Center meetings, to utilize our loans for the purpose approved, to save and pay our installments weekly, to use our increased incomes for the benefit of our families, to ensure that other members of our group and Center do likewise and to take collective responsibility if they do not.''}}  The soft treatments mimic the commitment arms as closely as possible without imposing external remainders or pecuniary consequences for failing to meet terms.
 
@@
 A lack of impact in this comparison would be consistent either with a population of neo-classical borrowers, for whom the commitment feature is superfluous, or with a population of time-inconsistent borrowers who lack sophistication over their own behavioral problems and so do not choose commitment even though they would benefit from it.
-The key to distinguishing these two stories is the treatment effect of commitment on those who would not choose it; this counterfactual is revealed through the additional impact of the Forced Commitment arm over the Choice arm.
+The keys to distinguishing these two stories is the treatment effect of commitment on those who would not choose it; this counterfactual is revealed through the additional impact of the Forced Commitment arm over the Choice arm.
 So while the forcing of commitment cuts against the grain of a behavioral literature that has largely promoted `nudges', it reveals important additional information that may be particularly relevant in borrower populations that are both hyperbolic and naive.
@@
 Our main outcome variables $y_{ij}$ are measures of financial cost in pesos as defined in Section \ref{costs}, which we further decompose into its component costs:  payments to capital, fees, interest, and the cost of losing the pawn.
-We then cast each of these costs as an Annual Percentage Rate (APR).
-as well as an indicator variable for client $i$ losing her pawn.
+We then examine an indicator variable for client $i$ losing her pawn.
+Next we cast each of the cost drivers as an effective Annual Percentage Rate (APR), including the costs of lost collateral under default as a component of the overall APR of pawn borrowing.
 $\beta^F$ estimates the Average Treatment Effect of the Forced arm (since compliance is 100\%), and  $\beta^C$ the Intention to Treat of the Choice arm (since it is not).
@@
 
-The core results, presented in Table \ref{main_impact_table} and graphically in Figure \ref{main_te}, are extremely stark.
-The Choice arm fails to deliver significant changes in any measure (with the exception of an increase in fees, for which we are highly powered since this outcome is always zero in the control).
+The core results, presented in Table \ref{main_impact_table} and Figure \ref{main_te}, are extremely stark.
+The Choice arm fails to deliver significant changes in any measure (with the exception of an increase in fees, for which we are highly powered since this outcome is zero by definition in the control).
 In sharp contrast, the Forced Commitment arm yields strongly significant decreases in the financial cost of loans to clients.
@@
 The bottom panel of the figure casts these costs as APRs, and shows that while the Choice arm actually leads to a slight \textit{increase} in the APR, the Forced arm decreases the effective annualized interest cost of pawn lending by 40 percentage points.
-A credit product that has an effective average APR of 249\% in the status quo arm is reduced to a cost of 209\% through the imposition of a more regularized payment structure.
+A credit product that has an effective average APR of 249\% in the status quo arm (inclusive of default) is reduced to a cost of 209\% through the imposition of a more regularized payment structure.
 
@@
 Because the regular repayment structure moves the timing of payment forward it saves borrowers an average of 109 pesos in interest costs.
-The very large majority of the overall treatment effect, however, stems from the 491 pesos in retained collateral value induced by the falling probability of default.
-
-Figure \ref{main_te} gives the  effect sizes (in standard deviations) of the two main study arms for three outcomes:  default, the financial cost of the loan, and the effective interest rate paid to acquire the borrowed capital.
-Very clearly, the Forced arm is significant for all three outcomes, with very substantial treatment effects in magnitudes for default and APR, and the commitment arm is never significant.\footnote{The slight increase in APR for the Choice arm seen in this picture arises from the fact that the APR calculation has the arm-specific loan size in the denominator, and the loans in the Choice arm turn out to be slightly smaller (although statistically equal) on average than the Control.}    In other words, voluntary commitment is ineffective but the use of forced commitment saves the average borrower an amount of money almost twice the APR of a normal US credit card loan.
-
-There are other intermediate outcomes that are impacted by being assigned to frequent payments.
-Table \ref{mechanisms} shows that the first payment happens 8 days earlier (column 1) in the Forced Commitment arm than in the status quo one, and that the number of payments increases by 0.19 (column 4).
+The very large majority of the overall treatment effect, however, stems from the 492 pesos in retained collateral value induced by the falling probability of default.
+
+Figure \ref{main_te} represents the  effect sizes (in standard deviations) of the two main study arms for three outcomes:  default, the financial cost of the loan, and the effective interest rate paid to acquire the borrowed capital.
+The Forced arm is significant for all three outcomes, with very substantial treatment effects in magnitudes for default and APR, and the commitment arm is never significant.\footnote{The slight increase in APR for the Choice arm seen in this picture arises from the fact that the APR calculation has the arm-specific loan size in the denominator, and the loans in the Choice arm turn out to be slightly smaller (although statistically equal) on average than the Control.}    In other words, voluntary commitment is ineffective but the use of forced commitment saves the average borrower an amount of money almost twice the APR of a normal US credit card loan.
+
+Other intermediate outcomes are impacted by assignment to frequent payments.
+Table \ref{mechanisms} shows that the first payment happens 8 days earlier in the Forced Commitment arm than in status quo (column 1), and that the number of payments increases by 0.19 (column 4).
 Treatment effects are concentrated on the intensive margin, as treatment does \textit{not} affect the fraction of clients who pay nothing (column 12).
@@
 Moreover, the percentage of the loan paid is even smaller for those that end up losing the pawn (first row of column 9).
-This last point is critical; this intervention has the potential to do financial harm if it caused individuals to make more payments on loans for which they would end up defaulting.
-This result shows that instead what the Forced arm does is allow individuals who would have made partial payment and defaulted to instead recover their pawn.
-
-Can we overturn these results by incorporating additional factors that would explain the subjective choices made by individuals?
-We now examine whether features such as the perceived value of the pawn, travel costs, or discounting might alter the story of comparative impact.
+This last point is critical; this intervention has the potential to do financial harm if it caused individuals to increase fruitless payments on loans for which they would end up defaulting.
+This result shows that the Forced arm drives individuals who would otherwise have made partial payment and defaulted to instead recover their pawn.
+
+Can subjective perceptions of the loan, such as perceived collateral value, discounting, or the opportunity cost of time, rationalize these results?
 Figure \ref{robustness_fc} shows the results of these robustness checks, and the numbers underlying the figure are shown in Table \ref{table_robustness_fc}.
@@
 The figure shows the effects of each of these adjustments on the estimate of financial cost and APR, and illustrates that even when we make all of these adjustment simultaneously the Forced arm generates benefits of 0.11 standard deviations, significant at the 95\% level.
+Hence forcing individuals into commitment generates benefit even when we incorporate multiple subjective dimensions of the loan.
 
@@
 We can first ask whether the individual ever takes a loan after the initial study loan, an analysis which is simply experimental.
-The results show that the Choice arm is no more likely to pawn again, which the Forced arm is X\% more likely to take a second loan.
-While this appears to be \textit{prima facie} evidence of greater satisfaction with the lender, interpretation here is complicated by the fact that they were so much more likely to have recovered their pawn and hence to be able to pawn it again.
+The results show that the Choice arm is no more likely to pawn again, which the Forced arm is 6\% more likely to take a second loan.
+While this appears to be \textit{prima facie} evidence of greater satisfaction with the lender, interpretation here is complicated by the fact that they were more likely to have recovered their pawn and hence to be able to pawn it again.
 We can explore this possibility in a number of ways.
-First, we can consider the probability that the borrower ever takes another loan using a \textit{different} pawn, an outcome that if anything would be biased downward in the Forced arm.
-Finally, we can conduct an endogenous sample split and examine the treatment effects within the sample that does, and does not, recover their pawn from the first loan.
-Results indicate that .
-.
-.
+First, we can (endogenously) split the sample according to whether the individual defaulted on the experimental loan; here we find that the increase in subsequent borrowing is restricted to those who repaid the first one.
+Then, we can examine whether the probability that they take another loan using different collateral from the first, and while not significant we find that the Forced arm elevates the probability of re-pawning with new collateral.
+We can also separately examine the likelihood to take a new loan after the contract period of the original experimental loan (column 5) or after it (column 6) and we find that the increase in subsequent pawning is coming afterwards, significantly increasing the time to the subsequent loan (column 7).
+
+\textcolor{red}{Figure} \ref{prob_ever_pawn} provides a visual take on the probability of re-pawning as a function of original treatment status.
 
@@
 
-.
 %The coefficient on repeat pawning is just as big when we focus only 2nd pawns happening after the first was recovered (third coefficient ``fnr'').
@@
 
-We view this result as strong evidence that after experiencing the contract demand for it increases, consistent with \cite{Alcohol}'s conjecture that demand for commitment increases with experience with it.
-However there is an alternative explanation for this result, namely that forcing frequent payments effectively means awarding a smaller loan, and thus that clients may pawn again to compensate for the smaller loan.
+All of this evidence suggests that the effect on subsequent demand is `real' and not an artifact of improved retention of the collateral, consistent with \cite{Alcohol}'s conjecture that demand for commitment increases with experience with it.
+However, it remains possible that the additional demand for subsequent pawning comes from the fact that forcing earlier payments effectively reduces the credit available during the contract, and thus that clients may pawn again to compensate for the smaller loan.
 We are skeptical about this interpretation for several reasons.
@@
 First,  there are many alternative lenders in this market, and if they did not like frequent payments why do they come back to Lender $P$ for another loan?
-Second, the fee is really small at 2\% of 1/3 of the value of the loan.
-The transaction costs of obtaining another loan are likely larger than incurring in this fee.
-So if the monthly payment made the current loan ``smaller'' it is probably better to skip the monthly payment and incur in a fee than to get an additional loan.
-Third, we find larger effects of repeat buying for clients that experienced larger treatment effects, which the alternative explanation cannot explain.
+Second, the fee itself is mostly symbolic (2\% of 1/3 of the value of the loan) and so it is likely that if there were real financial costs to making an intermediate payment it would simply be skipped and the fee incurred.
+We also implemented an exit survey which clients filled when recovering their piece.
+Unfortunately it had low response rate (7\%), and we take its results with a grain of salt; however in this survey 63\% of clients said they liked the frequent payment contract more than the status-quo one, and that it allowed them to avoid unnecessary expenses.
+Finally and most importantly, the treatment effects on re-pawning are entirely confined to the period after the original loan term and so there is no obvious link between intermediate liquidity and demand for new credit.
+%Third, we find larger effects of repeat buying for clients that experienced larger treatment effects, which the alternative explanation cannot explain.
 Fourth, the effect is present if we condition on clients that recovered their pawn (so it's not driven by pawn recovery).
@@
 
-We also implemented an exit survey which clients filled when recovering their piece.
-Unfortunately it had low response rate (7\%), and we take its results with a grain of salt.
-In this survey 63\% of clients said they liked the frequent payment contract more than the status-quo one, and that it allowed them to avoid unnecessary expenses
-
-\textcolor{red}{A final important robustness check is to consider clients who pawn more than once within the experiment.
+An additional empirical issue generated by repeat pawning is the question of how to handle the treatment status of those who take multiple loans within the experiment.
 38\% of borrowers take more than one loan within the study period, and 19\% are assigned multiple treatment statuses on their different loans.
-The issue of sequential endogenous treatments has been extensively studied in the context of school lotteries, where the convention is to use the treatment status from the first exposure \citep{abdulkadirouglu2011accountability}.\footnote{That context provides a particularly severe version of the endogenous re-entry problem because only the losers from initial lotteries re-enter subsequent ones.
-Our selection problem is less draconian, but still potentially relevant since we do find treatment effects on pace of repayment and of pawning again}  So in Table \ref{multiple_loans} we provide two straightforward robustness checks for the influence of this problem.
+The issue of sequential endogenous treatments has been extensively studied in the context of school lotteries, where the convention is to use the treatment status from the first exposure \citep{cullen2006effect, abdulkadirouglu2011accountability}.\footnote{That context provides a particularly severe version of the endogenous re-entry problem because only the losers from initial lotteries re-enter subsequent ones.
+Our selection problem is less draconian, but still potentially relevant since we do find treatment effects on pace of repayment and of pawning again.}  While our main impact tables simply use the assigned treatment status for every loan, in Table \ref{multiple_loans} we provide two straightforward robustness checks for the influence of this problem.
 Columns 1-2 repeat the main analysis of financial cost and APR using the baseline approach from our main results, including dummies for the order of pawns for an individual, essentially making the identification within-order.
 Columns 3-4 drop all loans other than the first, and Columns 5-6 pursue the ITT strategy of always assigning the first treatment status to all subsequent pawns.
-The core treatment effects are robust to any of these ways of handling repeat pawning, and the effect on the APR actually become larger.
-}
+The core treatment effects are robust to any of these ways of handling repeat pawning, and the effect on the APR is actually larger when we consider first loans only.
+Hence endogenous re-entry to the experiment does not appear to be driving our results.
 
@@
 
-%\section{The effect of promises} \label{promises}
-
-%One finding of the paper is that a rather small fee of 14 MXN on average changes behavior substantially.
-On the one hand it generates average savings for almost everybody (on the order of 200-300 pesos on average) when forced.
-But on the other hand it dissuades take up when clients have choice.
-One would want a commitment device that generates higher take-up while at the same time providing incentives for recovering the pawn.
-
-%One way to go would be to decrease the already small fee say to 1\% or lower.
-We decided to instead experiment with a non-pecuniary penalty, in the form of a psychological cost of breaking a promise.
-%As explained in Section \ref{Experiment} the promise contract involved making a salient promise to repay monthly, and receive a short speech by the appraiser about the importance of keeping her promise of paying monthly.
-We now turn to the impact of the two arms that featured forms of soft commitment.
-A substantial literature documents that people don't like to break their promises, and are willing to incur in monetary losses in trying to keep them.
-This provides a potentially very attractive way to drive better repayment behavior at low pecuniary cost to clients.
-To our knowledge this type of result has been replicated several times in laboratory contexts but not in a field setting like ours.
-Promises are not foreign to microfinance lending, and various forms of soft commitment have been shown to be effective at changing financial behavior \citep{Craig}.\footnote{Grameen Bank for instance makes clients recite a promise at each center weekly meeting.The exact promise repeated by clients live is this: ``\textit{We pledge to attend regularly the weekly Center meetings, to utilize our loans for the purpose approved, to save and pay our installments weekly, to use our increased incomes for the benefit of our families, to ensure that other members of our group and Center do likewise and to take collective responsibility if they do not.''}}
-%If breaking a promise is perceived as having a lower cost than paying the 2\% fee and at the same time helps as a commitment device we could achieve better outcomes: more people would demand the Soft Commitment contract.
-
-In the pawn lending context, however, the results from the two arms of the study that feature `soft' commitment further reinforce the centrality of externally imposed commitment. 
-Demand for the Soft Commitment contract  is higher than for the Forced Commitment contract by a factor of 3: {31}\% of clients offered a choice between the status quo contract and the Soft Commitment contract chose commitment.
+We now turn to the impact of the two arms that featured forms of `soft' commitment.  These results further reinforce the centrality of externally imposed commitment. 
+Demand for the Soft Commitment contract  is higher than for the Forced Commitment contract by a factor of three: {31}\% of clients offered a choice between the status quo contract and the Soft Commitment contract chose commitment.
 %Interestingly, the set of people who demand the Soft Commitment contract are different from those that demanded the Forced Commitment one.
@@
 Nonetheless, we find Soft Commitment, whether chosen or induced, to be completely ineffective in this environment.
-Table \ref{impact_soft} and  Figure \ref{effect_promises} finds that assigning clients to the choice-promise condition has a zero effect on financial cost, recovery, and the effective APR on average (Panel (a)).
-We see no difference even for the endogenous group that \textit{chose} to promise.
+Table \ref{impact_soft} and  Figure \ref{effect_promises} finds that assigning clients to the choice-promise condition has a zero effect on financial cost, recovery, and the effective APR on average (Panel (a)), or on any sub-component of cost (Panel (b), and Tables \ref{table_robustness_fc_soft} and \ref{mechanisms_soft}).
+These results contrast sharply with the (lower-stakes, more short-term) evidence in laboratory experiments where promises have large effects on behavior.
+While clients are more enthusiastic about the Soft Commitment contract than the Forced Commitment one in the sense of tripling take-up, the promise contract provides no commitment.
+Results for the promise arms are consistent with \cite{Ted} and \cite{John} who find that people are likely to demand commitment when the commitment is too weak to have beneficial effects.
+In short, not only is chosen hard commitment ineffective, but both forced and chosen soft commitment similarly fail to improve outcomes.
+Only an externally imposed commitment product with reminders, imposed on people who would not have chosen it, decreases costs to borrowers.
+
+%We see no difference even for the endogenous group that \textit{chose} to promise.
 This null effect happens not only on average, but also by percentiles (Figure \ref{qreg_chooser_nonchooser}, panels (c) \& (d)).
@@
 
-\vspace{.2in}
-\noindent The evidence presented in this section contrasts sharply with the evidence in laboratory experiments where people choosing to promise has a large effects on behavior, and where people keep their promises.
-While clients are more enthusiastic about the Soft Commitment contract than the Forced Commitment one in the sense of tripling take-up, the promise contract provides no commitment.
-Results for the promise arms are consistent with \cite{Ted} and \cite{John} who find that people are likely to demand commitment when the commitment is too weak to have beneficial effects.
-
 %\vspace{.2in}
@@
 
+\section{Exploring the Importance of Paternalism}
+\label{exploring}
+
 This is not the first paper to find low demand for commitment, however it is the first we know of that can compare choice vs forcing with a money-metric outcome such as loan repayment.
 The fact that the Forced Commitment contract lowers financial costs for almost all clients, together with the fact that only 11\% choose it must mean that many consumers are choosing contracts with higher financial costs for themselves.
-We now use several different techniques to shed further light on the idea that the wrong people are choosing commitment.
-
-\section{Exploring the Importance of Paternalism}
-\label{exploring}
-
-Our core impacts show that forced commitment is uniquely effective, a result that can only arise if those who would not have freely chosen commitment benefit from it.
-We now delve more deeply into this result.
+We now use several different techniques to shed further light on the idea that the `wrong' people are choosing commitment.
 
@@
 More formally, let $Z_i$ be the observed, randomly assigned experimental allocation, where $Z_i=0$ denotes the control arm, $Z_i=1$ denotes the Forced arm, and $Z_i=2$ is the Choice arm.
-Let $C_i$ be the choice type; $C_i=0$ when individual $i$ does not choose commitment and $C_i=1$ when chooses commitment, observed only in the Choice arm.
+Let $C_i$ be the choice type; $C_i=0$ when individual $i$ does not choose commitment and $C_i=1$ when chooses commitment, observed in the Choice arm and latent in the other two arms.
 A fraction $p$ of individuals chooses the treatment in the Choice arm.
@@
 
-\[ToT = \frac{\beta^C}{p}; \hspace{15} TuT = \frac{(\beta^F - \beta^C)}{(1-p)}; \hspace{15} (ToT-TuT) = \frac{\beta^C}{p}- \frac{(\beta^F - \beta^C)}{(1-p)}. \]
+\[ToT = \frac{\beta^C}{p}; \qquad\quad TuT = \frac{(\beta^F - \beta^C)}{(1-p)}; \qquad\quad (ToT-TuT) = \frac{\beta^C}{p}- \frac{(\beta^F - \beta^C)}{(1-p)}. \]
 
 Table \ref{tot_tut} shows the results of this analysis.
-Given that the ITT results for the Choice arm imply an insignificant worsening of outcomes relative to the control, our estimates of the Treatment on the Treated in the first row of the bottom panel show negative results that are larger in absolute magnitude (multiplied by \~9, the inverse of the compliance rate) and similarly insignificant.
-The Treatment on the Untreated (TuT), conversely, is strongly positive across the board, and indicates a significant improvement for all outcomes (here ITTs are multiplied by 1.12, the inverse of the non-compliance rate).
+Given that the ITT results for the Choice arm imply an insignificant worsening of outcomes relative to the control, our estimates of the Treatment on the Treated in the first row of the bottom panel show negative results that are larger in absolute magnitude (multiplied by ~9, the inverse of the compliance rate) and similarly insignificant.
+The Treatment on the Untreated (TuT), conversely, is strongly positive across the board, and indicates a significant improvement for all outcomes (here ITTs are effectively multiplied by 1.12, the inverse of the non-compliance rate).
 Most novel is the ability to form a test of the difference between the ToT and the TuT, which is conducted in the bottom rows of the table.
-We provide four different ways of estimating p-values; the standard clustered estimates motivated by the experimental design, normal and percentile bootstraps, and randomization inference.
-The differences between treatment effects for compliers and non-compliers are of borderline significance in some of the unadjusted specifications, but are not significant once adjusted.\footnote{It is worth noting that the statistical power of these estimands is driven by the compliance rate; given our low overall compliance we are better powered to measure the TuT than the ToT, and the power for the difference between the two would be highest with a compliance rate of 50\%.}
+We provide four different ways of estimating p-values for this comparison; the standard clustered estimates motivated by the experimental design, normal and percentile bootstraps, and randomization inference.
+The differences between treatment effects for compliers and non-compliers are of borderline significance in some of the unadjusted specifications, but are not significant once adjusted.\footnote{It is worth noting that the statistical power of these estimands is driven by the compliance rate; given our low overall compliance we are better powered to measure the TuT than the ToT, and the power for the difference between the two would be highest with a compliance rate of 50\%.}   Because of the large standard errors on the ToT coming from the low compliance rate in the Choice arm we are unable to state with statistical confidence that the TuT is higher than the ToT, but the TuT is strongly positive while the ToT is weakly negative, and so in both relative and absolute terms the choices being made are `wrong' relative to the potential outcomes.
 
@@
 
-\textcolor{red}{rewrite following paragraph with updated figure in hand.}
-Figure \ref{choose_wrong}(a) plots on the left Y-axis the fraction of clients that made a choice ``mistake'' and on the right Y-axis its size in pesos.
-On the X-axis it varies the threshold $z$.
-When $z=0$, we calculate that about 75\% of clients in the Commitment Choice group chose contracts that induced \textit{higher} financial cost.
-%(90\% confidence interval [45,94]).
-Most mistakes are failures to choose the fee-commitment contract ({85}\%), while only {15}\% of those who chose the fee-commitment contract would have been better in the status-quo one.
+Figure \ref{choose_wrong}(a) plots on the Y axis the fraction of clients that made a choice ``mistake'' and on the X axis the threshold $z$.
+When $z=0$, we calculate that about 82\% of clients in the Choice arm chose contracts that induced \textit{higher} financial cost.
+Most mistakes are failures to choose the fee-commitment contract ({97}\%), while only {4}\% of those who chose the fee-commitment contract would have been better in the status-quo one.
 The average mistake in pesos is \$250.
 %(90\% confidence interval [140,390]).
+As we increase the threshold on the size of the mistake necessary to be classified as having made the wrong choice, by definition the share in both groups falls, and among Choosers the number making an error falls quite quickly to zero.
+However, the fraction of non-choosers making a mistake remains almost 20\% even at the highest threshold used (\$80 pesos), and panel b shows the \textcolor{red}{Complete this when understand figure}.
+Panel C conducts a related but distinct exercise, showing the fraction of the entire control sample who would do better if assigned to the Forced arm; using the smallest threshold this fraction is over 95\%, showing that in this context there is an almost across-the board welfare benefit arising from this arm.
+Since the only potential financial cost of the forced arm arises from individuals who would be induced to partially repay but then default anyways, this result suggests that very few such borrowers exist.
 
@@
 We can represent the relationship between the HTEs from commitment and propensity scores in several ways.
-Most straightforward is Figure \ref{HTE_vs_propensity}, which plots the individually-estimated treatment effect from Forced versus Control treatments on the Y-axis, and the predicted probability of choosing commitment on the X axis.
+Most straightforward is Figure \ref{HTE_vs_propensity}, which plots the individually-estimated treatment effect from Forced versus Control treatments on the Y-axis, and the predicted probability of choosing commitment on the x-axis.
 The HTEs are very strongly downward-sloping over the part of the distribution that has heterogeneity in predicted propensities, the opposite of what we would expect from Roy-type selection.
@@
 
+\cleardoublepage
+\begin{landscape}
+
+\begin{table}[H]
+\caption{Ever pawning again}
+\label{repeat_loans}
+\begin{center}
+\scriptsize{\input{./Tables/repeat_loans.tex}}
+\end{center}
+ \scriptsize
+
+%\textit{Do file: } \texttt{repeat\_loans.do}
+\end{table}
+\end{landscape}
+
+\cleardoublepage
+
+\begin{table}[H]
+\caption{Multiple-loans robustness check}
+\label{multiple_loans}
+\begin{center}
+\scriptsize{\input{./Tables/multiple_loans.tex}}
+\end{center}
+ \scriptsize
+
+%\textit{Do file: } \texttt{multiple\_loans.do}
+\end{table}
+
+\cleardoublepage
+
 \begin{table}[H]
@@
 
-\begin{table}[H]
-\caption{Effects on several definitions of cost - Soft arms}
-\label{table_robustness_fc_soft}
-\begin{center}
-\scriptsize{\input{./Tables/fc_robustness_soft.tex}}
-\end{center}
- \scriptsize
-
-%\textit{Do file: } \texttt{fc\_robustness\_soft.do}
-\end{table}
-
 \begin{landscape}
-
-\begin{table}[H]
-\caption{Intermediate outcomes - Soft arms}
-\label{mechanisms_soft}
-\begin{center}
-\scriptsize{\input{./Tables/mechanism_soft.tex}}
-\end{center}
-
-%\textit{Do file: } \texttt{mechanisms\_soft.do}
-\end{table}
-
-\end{landscape}
-
-\cleardoublepage
-
-\begin{table}[H]
-\caption{Multiple-loans robustness check}
-\label{multiple_loans}
-\begin{center}
-\scriptsize{\input{./Tables/multiple_loans.tex}}
-\end{center}
- \scriptsize
-
-%\textit{Do file: } \texttt{multiple\_loans.do}
-\end{table}
-
-\cleardoublepage
 
@@
 %\textit{Do file: } \texttt{tot\_tut\_reg.do}
+\end{table}
+
+\end{landscape}
+
+\begin{table}[H]
+\caption{Experience with frequent payment contract raises future demand for it}
+\label{learning_not_doing}
+\begin{center}
+\scriptsize{\input{./Tables/learning_not_doing.tex}}
+\end{center}
+ \scriptsize 
+%\textit{Do file: } \texttt{learning\_not\_doing.do}
 \end{table}
@@
 
-\begin{table}[H]
-\caption{Outcome in 2S : Choose FP contract}
-\label{iv_pf}
-\begin{center}
-\scriptsize{\input{./Tables/iv_reg_pago_fijo_detailed.tex}}
-\end{center}
- \scriptsize
-
-%\textit{Do file: } \texttt{iv\_reg\_detailed.do}
-\end{table}
-
-\begin{table}[H]
-\caption{Collapsing observations}
-\begin{center}
-\scriptsize{\input{./Tables/iv_reg_pago_fijo_detailed_colla.tex}}
-\end{center}
- \scriptsize
-
-%\textit{Do file: } \texttt{iv\_reg\_detailed.do}
-\end{table}
-
-\begin{table}[H]
-\caption{Interaction with default in the past}
-\begin{center}
-\scriptsize{\input{./Tables/iv_reg_pago_fijo_def_collapsed.tex}}
-\end{center}
- \scriptsize
-
-%\textit{Do file: } \texttt{iv\_reg\_intdef\_detailed.do}
-\end{table}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+\begin{figure}[H]
+    \caption{Histogram of payments}
+    \label{hist_payments}
+    \begin{center}
+    \begin{subfigure}{0.31\textwidth}
+        \caption{Status-quo}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_payments_sq.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.31\textwidth}
+        \caption{Forced commitment}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_payments_fc.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.31\textwidth}
+        \caption{Choice commitment}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_payments_cc.pdf}
+    \end{subfigure}    
+    \end{center}
+     \scriptsize
+      %\footnotesize{ \textit{Do file: }  \texttt{hist\_payments.do}}
+\end{figure}
+
+\begin{figure}[H]
+        \caption{Survival graph}
+    \label{survival_graph}
+    \begin{center}
+   \begin{subfigure}{0.49\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/survival_graph_ended.pdf}
+    \end{subfigure} 
+    \end{center}
+     \scriptsize  This Figure shows the accumulated percentage of recovery in time by treatment arm. 
+     %\textit{Do file: }  \texttt{survival\_graph.do}
+\end{figure}
+
+\begin{figure}[H]
+        \caption{\% of payment over time}
+    \label{survival_graph}
+    \begin{center}
+   \begin{subfigure}{0.49\textwidth}
+        \caption{Unconditional}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/cumulative_porc_pay_time.pdf}
+    \end{subfigure} 
+   \begin{subfigure}{0.49\textwidth}
+        \caption{Conditional on default}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/cumulative_porc_pay_time_default.pdf}
+    \end{subfigure}     
+    \end{center}
+     \scriptsize  This Figure shows the accumulated percentage of recovery in time by treatment arm. 
+     %\textit{Do file: }  \texttt{survival\_graph.do}
+\end{figure}
+
 \cleardoublepage
@@
 
+\cleardoublepage
+
 \begin{figure}[H]
-     \caption{Quantile regressions}
-    \label{qregs}
-    \begin{center}
-    \begin{subfigure}{.45\textwidth}
-      \caption{Financial cost (in MXN)}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/qreg_fc_admin.pdf}
-    \end{subfigure}
-     \begin{subfigure}{0.45\textwidth}
-    \caption{Effective APR}
-       \centering
-      \includegraphics[width=\textwidth]{Figuras/qreg_apr.pdf}
+     \caption{Probability of ever pawning again}
+    \label{prob_ever_pawn}
+    \begin{center}
+  \begin{subfigure}{0.49\textwidth}
+     \caption{Reincidence after $n$ days}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/prob_reincidence_after.pdf}
+    \end{subfigure}        
+    \begin{subfigure}{0.49\textwidth}
+     \caption{Reincidence within $n$ days}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/prob_reincidence_within.pdf}
     \end{subfigure}
@@
     \scriptsize
-     This figure plots the effects on different quantiles (15th, 25th, 50th, 75th, 85th percentile) of the distribution of financial cost, and APR, for the Forced-commitment and Choice-commitment arms.
-      %\footnotesize{ } \textit{Do file: }  \texttt{main\_qreg.do}
+    This figure shows
+      %\textit{Do file: }  \texttt{repeat\_loans.do}
 \end{figure}
 
+\cleardoublepage
+
 \begin{figure}[H]
-     \caption{Effect of promises}
+     \caption{Effect of Soft Commitment Arms}
     \label{effect_promises}
@@
     \end{subfigure}
-       \begin{subfigure}{0.45\textwidth}
-       \caption{Q-regs on Financial Cost (in MXN)}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/soft_qreg_fc_admin.pdf}
-    \end{subfigure}
-        \begin{subfigure}{0.45\textwidth}
-         \caption{Q-regs on effective APR}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/soft_qreg_apr.pdf}
-    \end{subfigure}
+     %  \begin{subfigure}{0.45\textwidth}
+     %  \caption{Q-regs on Financial Cost (in MXN)}
+     %   \centering
+     %   \includegraphics[width=\textwidth]{Figuras/soft_qreg_fc_admin.pdf}
+    %\end{subfigure}
+     %   \begin{subfigure}{0.45\textwidth}
+     %    \caption{Q-regs on effective APR}
+     %   \centering
+     %   \includegraphics[width=\textwidth]{Figuras/soft_qreg_apr.pdf}
+    %\end{subfigure}
     \end{center}
@@
 Panel (b) shows the treatment effects on the several definitions of cost for the soft arms.
-Panels (c) \& (d) show treatment effects on different quantiles for the Financial Cost and APR.
+\end{figure}
+
+\cleardoublepage
+
+\begin{figure}[H]
+     \caption{Quantile regressions}
+    \label{qregs}
+    \begin{center}
+    \begin{subfigure}{.45\textwidth}
+      \caption{Financial cost (in MXN)}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/qreg_fc_admin.pdf}
+    \end{subfigure}
+     \begin{subfigure}{0.45\textwidth}
+    \caption{Effective APR}
+       \centering
+      \includegraphics[width=\textwidth]{Figuras/qreg_apr.pdf}
+    \end{subfigure}
+    \end{center}
+         \scriptsize
+     This figure plots the effects on different quantiles (15th, 25th, 50th, 75th, 85th percentile) of the distribution of financial cost, and APR, for the Forced-commitment and Choice-commitment arms.
+      %\footnotesize{ } \textit{Do file: }  \texttt{main\_qreg.do}
 \end{figure}
@@
     This figure shows 
+     %\textit{Do file: }  \texttt{tot\_tut\_graph.do}
 \end{figure}
@@
 
+\begin{figure}[H]
+        \caption{Financial cost for different discount rates}
+    \label{fc_discount_rates}
+    \begin{center}
+        \centering
+        \includegraphics[width=0.55\textwidth]{Figuras/discount_effect.pdf}
+    \end{center}
+     \scriptsize This Figure estimates the treatment effect on financial cost with different discount rates.  
+     %\textit{Do file: }  \texttt{discounted\_noeffect.do}
+\end{figure}
+
 \vspace{.3in}
@@
 
-%\newpage
-
-%\input{OA.tex}
+\newpage
+\input{OA.tex}
 

### 2022-03-24 donde-2022-03-18-115935025.tex
restore comments from overleaf

--- 2022-03-24 donde.tex
@@
 
-\textcolor{red}{Figure} \ref{prob_ever_pawn} provides a visual take on the probability of re-pawning as a function of original treatment status.
+\textcolor{red}{Figure \ref{prob_ever_pawn} provides a visual take on the probability of re-pawning as a function of original treatment status.}
 
@@
 We now turn to the impact of the two arms that featured forms of `soft' commitment.  These results further reinforce the centrality of externally imposed commitment. 
-Demand for the Soft Commitment contract  is higher than for the Forced Commitment contract by a factor of three: {31}\% of clients offered a choice between the status quo contract and the Soft Commitment contract chose commitment.
+Demand for the Soft Commitment contract  is higher than for the Forced Commitment contract by a factor of 3: {31}\% of clients offered a choice between the status quo contract and the Soft Commitment contract chose commitment.
 %Interestingly, the set of people who demand the Soft Commitment contract are different from those that demanded the Forced Commitment one.
@@
 Nonetheless, we find Soft Commitment, whether chosen or induced, to be completely ineffective in this environment.
-Table \ref{impact_soft} and  Figure \ref{effect_promises} finds that assigning clients to the choice-promise condition has a zero effect on financial cost, recovery, and the effective APR on average (Panel (a)), or on any sub-component of cost (Panel (b), and Tables \ref{table_robustness_fc_soft} and \ref{mechanisms_soft}).
+Table \ref{impact_soft} and  Figure \ref{effect_promises} finds that assigning clients to the choice-promise condition has a zero effect on financial cost, recovery, and the effective APR on average (Panel (a)), or on any sub-component of cost (Panel (b)).
 These results contrast sharply with the (lower-stakes, more short-term) evidence in laboratory experiments where promises have large effects on behavior.
@@
 
-This is not the first paper to find low demand for commitment, however it is the first we know of that can compare choice vs forcing with a money-metric outcome such as loan repayment.
-The fact that the Forced Commitment contract lowers financial costs for almost all clients, together with the fact that only 11\% choose it must mean that many consumers are choosing contracts with higher financial costs for themselves.
-We now use several different techniques to shed further light on the idea that the `wrong' people are choosing commitment.
+Our core impacts show that forced commitment is uniquely effective, a result that can only arise if those who would not have freely chosen commitment benefit from it.
+We now delve more deeply into this result.
 
@@
 More formally, let $Z_i$ be the observed, randomly assigned experimental allocation, where $Z_i=0$ denotes the control arm, $Z_i=1$ denotes the Forced arm, and $Z_i=2$ is the Choice arm.
-Let $C_i$ be the choice type; $C_i=0$ when individual $i$ does not choose commitment and $C_i=1$ when chooses commitment, observed in the Choice arm and latent in the other two arms.
+Let $C_i$ be the choice type; $C_i=0$ when individual $i$ does not choose commitment and $C_i=1$ when chooses commitment, observed only in the Choice arm.
 A fraction $p$ of individuals chooses the treatment in the Choice arm.
@@
 
-\[ToT = \frac{\beta^C}{p}; \qquad\quad TuT = \frac{(\beta^F - \beta^C)}{(1-p)}; \qquad\quad (ToT-TuT) = \frac{\beta^C}{p}- \frac{(\beta^F - \beta^C)}{(1-p)}. \]
+\[ToT = \frac{\beta^C}{p}; \hspace{15} TuT = \frac{(\beta^F - \beta^C)}{(1-p)}; \hspace{15} (ToT-TuT) = \frac{\beta^C}{p}- \frac{(\beta^F - \beta^C)}{(1-p)}. \]
 
 Table \ref{tot_tut} shows the results of this analysis.
-Given that the ITT results for the Choice arm imply an insignificant worsening of outcomes relative to the control, our estimates of the Treatment on the Treated in the first row of the bottom panel show negative results that are larger in absolute magnitude (multiplied by ~9, the inverse of the compliance rate) and similarly insignificant.
-The Treatment on the Untreated (TuT), conversely, is strongly positive across the board, and indicates a significant improvement for all outcomes (here ITTs are effectively multiplied by 1.12, the inverse of the non-compliance rate).
+Given that the ITT results for the Choice arm imply an insignificant worsening of outcomes relative to the control, our estimates of the Treatment on the Treated in the first row of the bottom panel show negative results that are larger in absolute magnitude (multiplied by \~9, the inverse of the compliance rate) and similarly insignificant.
+The Treatment on the Untreated (TuT), conversely, is strongly positive across the board, and indicates a significant improvement for all outcomes (here ITTs are multiplied by 1.12, the inverse of the non-compliance rate).
 Most novel is the ability to form a test of the difference between the ToT and the TuT, which is conducted in the bottom rows of the table.
-We provide four different ways of estimating p-values for this comparison; the standard clustered estimates motivated by the experimental design, normal and percentile bootstraps, and randomization inference.
-The differences between treatment effects for compliers and non-compliers are of borderline significance in some of the unadjusted specifications, but are not significant once adjusted.\footnote{It is worth noting that the statistical power of these estimands is driven by the compliance rate; given our low overall compliance we are better powered to measure the TuT than the ToT, and the power for the difference between the two would be highest with a compliance rate of 50\%.}   Because of the large standard errors on the ToT coming from the low compliance rate in the Choice arm we are unable to state with statistical confidence that the TuT is higher than the ToT, but the TuT is strongly positive while the ToT is weakly negative, and so in both relative and absolute terms the choices being made are `wrong' relative to the potential outcomes.
+We provide four different ways of estimating p-values; the standard clustered estimates motivated by the experimental design, normal and percentile bootstraps, and randomization inference.
+The differences between treatment effects for compliers and non-compliers are of borderline significance in some of the unadjusted specifications, but are not significant once adjusted.\footnote{It is worth noting that the statistical power of these estimands is driven by the compliance rate; given our low overall compliance we are better powered to measure the TuT than the ToT, and the power for the difference between the two would be highest with a compliance rate of 50\%.}
 
@@
 
-Figure \ref{choose_wrong}(a) plots on the Y axis the fraction of clients that made a choice ``mistake'' and on the X axis the threshold $z$.
-When $z=0$, we calculate that about 82\% of clients in the Choice arm chose contracts that induced \textit{higher} financial cost.
-Most mistakes are failures to choose the fee-commitment contract ({97}\%), while only {4}\% of those who chose the fee-commitment contract would have been better in the status-quo one.
+\textcolor{red}{rewrite following paragraph with updated figure in hand.}
+Figure \ref{choose_wrong}(a) plots on the left Y-axis the fraction of clients that made a choice ``mistake'' and on the right Y-axis its size in pesos.
+On the X-axis it varies the threshold $z$.
+When $z=0$, we calculate that about 75\% of clients in the Commitment Choice group chose contracts that induced \textit{higher} financial cost.
+%(90\% confidence interval [45,94]).
+Most mistakes are failures to choose the fee-commitment contract ({85}\%), while only {15}\% of those who chose the fee-commitment contract would have been better in the status-quo one.
 The average mistake in pesos is \$250.
 %(90\% confidence interval [140,390]).
-As we increase the threshold on the size of the mistake necessary to be classified as having made the wrong choice, by definition the share in both groups falls, and among Choosers the number making an error falls quite quickly to zero.
-However, the fraction of non-choosers making a mistake remains almost 20\% even at the highest threshold used (\$80 pesos), and panel b shows the \textcolor{red}{Complete this when understand figure}.
-Panel C conducts a related but distinct exercise, showing the fraction of the entire control sample who would do better if assigned to the Forced arm; using the smallest threshold this fraction is over 95\%, showing that in this context there is an almost across-the board welfare benefit arising from this arm.
-Since the only potential financial cost of the forced arm arises from individuals who would be induced to partially repay but then default anyways, this result suggests that very few such borrowers exist.
 
@@
 We can represent the relationship between the HTEs from commitment and propensity scores in several ways.
-Most straightforward is Figure \ref{HTE_vs_propensity}, which plots the individually-estimated treatment effect from Forced versus Control treatments on the Y-axis, and the predicted probability of choosing commitment on the x-axis.
+Most straightforward is Figure \ref{HTE_vs_propensity}, which plots the individually-estimated treatment effect from Forced versus Control treatments on the Y-axis, and the predicted probability of choosing commitment on the X axis.
 The HTEs are very strongly downward-sloping over the part of the distribution that has heterogeneity in predicted propensities, the opposite of what we would expect from Roy-type selection.
@@
 
+\begin{table}[H]
+\caption{Effects on several definitions of cost - Soft arms}
+\label{table_robustness_fc_soft}
+\begin{center}
+\scriptsize{\input{./Tables/fc_robustness_soft.tex}}
+\end{center}
+ \scriptsize
+
+%\textit{Do file: } \texttt{fc\_robustness\_soft.do}
+\end{table}
+
+\begin{landscape}
+
+\begin{table}[H]
+\caption{Intermediate outcomes - Soft arms}
+\label{mechanisms_soft}
+\begin{center}
+\scriptsize{\input{./Tables/mechanism_soft.tex}}
+\end{center}
+
+%\textit{Do file: } \texttt{mechanisms\_soft.do}
+\end{table}
+
+\end{landscape}
+
+\cleardoublepage
+
 \begin{landscape}
@@
     \begin{subfigure}{0.49\textwidth}
-     \caption{Reincidence after $n$ days}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/prob_reincidence_after.pdf}
+     \caption{after taking first loan}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/prob_reincidence.pdf}
     \end{subfigure}
     \begin{subfigure}{0.49\textwidth}
-     \caption{Reincidence within $n$ days}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/prob_reincidence_within.pdf}
+     \caption{after recovery of first loan}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/prob_reincidence_des.pdf}
     \end{subfigure}    
@@
 
-\begin{figure}[H]
-        \caption{Financial cost for different discount rates}
-    \label{fc_discount_rates}
-    \begin{center}
-        \centering
-        \includegraphics[width=0.55\textwidth]{Figuras/discount_effect.pdf}
-    \end{center}
-     \scriptsize This Figure estimates the treatment effect on financial cost with different discount rates.  
-     %\textit{Do file: }  \texttt{discounted\_noeffect.do}
-\end{figure}
-
 \vspace{.3in}
@@
 
-\newpage
+%\newpage
+
 \input{OA.tex}

### 2022-03-24 donde.tex
restore comments (2)

@@
 We now use several different techniques to shed further light on the idea that the `wrong' people are choosing commitment.
+
+Our core impacts show that forced commitment is uniquely effective, a result that can only arise if those who would not have freely chosen commitment benefit from it.
+We now delve more deeply into this result.
 

### 2022-04-28 OA.tex
Fan & Park Bounds

@@
 $C_i=0$ when individual $i$ does not choose commitment  given the choice and $C_i=1$ when chooses commitment given the choice.
-Finally, $D_i = Z_i\times \mathds{1}(Z_i\neq 2) + T_i\times \mathds{1}(Z_i=2)$ is the observed treatment indicator, and $Y(d,z)$ is the potential outcome function for $d=0,1$, and $z=0,1,2$.
+Finally, $D_i = Z_i\times \mathds{1}(Z_i\neq 2) + C_i\times \mathds{1}(Z_i=2)$ is the observed treatment indicator, and $Y(d,z)$ is the potential outcome function for $d=0,1$, and $z=0,1,2$.
 
@@
 \subsection{New results}
+
+\begin{table}[H]
+\caption{Effect of frequent payment in observational data}
+\label{attrition_table}
+\begin{center}
+\scriptsize{\input{./Tables/def_te_obs.tex}}
+\end{center}
+ \scriptsize 
+%\textit{Do file: } \texttt{def\_te\_obs.do}
+\end{table}
 

### 2022-04-28 bounds.tex
Fan & Park Bounds

 \documentclass[oneside,11pt]{article}

\input{preamble.tex}
%%% HELPER CODE FOR DEALING WITH EXTERNAL REFERENCES
\usepackage{xr}
\makeatletter
\newcommand*{\addFileDependency}[1]{
  \typeout{(#1)}
  \@addtofilelist{#1}
  \IfFileExists{#1}{}{\typeout{No file #1.}}
}
\makeatother

\newcommand*{\myexternaldocument}[1]{
    \externaldocument{#1}
    \addFileDependency{#1.tex}
    \addFileDependency{#1.aux}
}

%\myexternaldocument{OA}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% DOCUMENT
\begin{document}

\section{Heterogeneity}

For a test of heterogeneity we compute the best linear fit of the target estimand using the forest prediction (on held-out data) as well as the mean forest prediction as the sole two regressors. A coefficient of 1 for 'mean.forest.prediction' suggests that the mean forest prediction is correct, whereas a coefficient of 1 for 'differential.forest.prediction' additionally suggests that the forest has captured heterogeneity in the underlying signal.

The p-value of the ‘differential.forest.prediction‘coefficient also acts as an omnibus test the presence of heterogeneity: If the coefficient is significantly greater than 0, then we can reject the null of no heterogeneity.

\begin{table}[H]
\caption{}
\label{}
\begin{center}
\scriptsize{\input{./Tables/test_calibration.tex}}
\end{center}

\end{table}

Many tests for heterogeneity:

\cite{a3}  use of a heuristic support-vector-machine method with lasso penalization for classification of heterogeneous treatments into positive and negative ones

\begin{thebibliography}{2}

\bibitem{a1} Generic Machine Learning Inference on Heterogenous Treatment Effects in Randomized Experiments. Chernozhukov, Victor, Mert Demirer, Esther Duflo, and Ivan Fernandez-Val

\bibitem{a3} Estimating Treatment Effect Heterogeneity In Randomized Program Evaluation. Kosuke Imai, Ratkovic

\bibitem{a4} Testing for Essential Heterogeneity. Heckman
\bibitem{a12} Nonparametric  Tests  for Treatment  Effect  Heterogeneity. Crump et.al

\bibitem{a5} Treatment Effect Heterogeneity In Theory And Practice . Angrist

\bibitem{a6} Evaluating Treatment Prioritization Rules via Rank-Weighted Average Treatment Effects. Wager et. al.

\bibitem{a2} Brand, J. E., Y. Xie (2010). Who Benefits Most From College?Evidence for Negative Selection in Heterogeneous Economic Returns to Higher Education

\end{thebibliography}

\subsection{Some points}

\begin{itemize}
    \item Doubts of how to construct a sharp bound for the variance of a treatment effect of Heckman et al. (1997). $->$ This in order to argue there is heterogeneity.

    \item I am currently trying to implement Empirical deconvolution of Heckman et al. (1997).
\end{itemize}

% Table generated by Excel2LaTeX from sheet 'grf_pro_2_apr_ate'
\begin{tabular}{rrl}
\multicolumn{1}{l}{beta} & \multicolumn{1}{l}{se} & target\_sample \\
-38.0631 & 3.793024 & all \\
-37.2934 & 4.438196 & overlap \\
-34.4718 & 4.344636 & treated \\
-41.0618 & 4.279213 & control \\
\end{tabular}%

\newpage

\section{Bounds}

\begin{table}[H]
\caption{Gains for choosers versus gains from non-choosers (ToT \& TuT)}
\label{tot_tut}
\begin{center}
\scriptsize{\input{./Tables/tot_tut_reg.tex}}
\end{center}
 \scriptsize This table shows estimates of the ToT and the TuT with an IV-LATE framework. The ToT is computed as the usual LATE with one-sided non-compliance between the choice and control arm, and the TuT is the LATE on non-compliers. 
%\textit{Do file: } \texttt{tot\_tut\_reg.do}
\end{table}

The Huber \& Mellace (2015) bounds for the TOT \& TUT APR are respectively:
$[-481.8, 483.7]$ , $[-17.9, 90.6]$. \\

\subsection{Question:}

\textit{IV validity implies that the mean outcome of the treated receiving the instrument is equal to that of the treated not receiving the instrument. This can be easily tested by difference-of-means tests. An analogous result holds for the never takers and the compliers under non treatment}

\textbf{Isn't this then a test for the above?}

\begin{figure}[H]
     \caption{Exclusion restriction}
     \label{exclusion_restriction}
    \begin{center}
    \begin{subfigure}{0.6\textwidth}
        \centering
        \includegraphics[width=\textwidth]{Figuras/exclusion_restriction.pdf}
    \end{subfigure}
    \end{center}
    \scriptsize This figure serves as a test for the exclusion restriction in the point identification for the ToT and the TuT. It shows the effect on the effective cost/loan ratio for the forced-fee arm and the choice arm, together with the decomposition of the choosers and non-choosers. Note that a) being forced into the treatment (Forced fee) has the same effect as choosing it (Choosers), and b) not choosing the treatment (Non chooser) has no effect with respect to the control.

          %\footnotesize{ \textit{Do file: }  \texttt{exclusion\_restriction.do}}
\end{figure}

The next figure implements the  Fan \& Park (2010) bounds for the TE

\begin{figure}[H]
    \caption{}
    \label{}
    \begin{center}

    \begin{subfigure}{0.475\textwidth}
        \caption{APR}
        \centering
        \includegraphics[width=\textwidth]{Figuras/fan_park_bounds_apr.pdf}
    \end{subfigure}
    \begin{subfigure}{0.475\textwidth}
        \caption{Financial Cost}
        \centering
        \includegraphics[width=\textwidth]{Figuras/fan_park_bounds_fc_admin.pdf}
    \end{subfigure}
    \begin{subfigure}{0.475\textwidth}
        \caption{Recovery}
        \centering
        \includegraphics[width=\textwidth]{Figuras/fan_park_bounds_des_c.pdf}
    \end{subfigure}    
    \end{center}
\end{figure}

The next is a figure for the bounds for the QTE

\begin{figure}[H]
    \caption{}
    \label{}
    \begin{center}

    \begin{subfigure}{0.475\textwidth}
        \caption{APR}
        \centering
        \includegraphics[width=\textwidth]{Figuras/fan_park_qbounds_apr.pdf}
    \end{subfigure}
    \begin{subfigure}{0.475\textwidth}
        \caption{Financial Cost}
        \centering
        \includegraphics[width=\textwidth]{Figuras/fan_park_qbounds_fc_admin.pdf}
    \end{subfigure}

    \end{center}
\end{figure}

\subsection{Question:}

\textbf{Should we, and more importantly, can we do this for the TOT \& TUT?}

\section{Machine Learning exercises}

\subsection{First ML exercise}

\begin{figure}[H]
    \caption{Choice of contracts and treatment effects using TOT \& TUT}
    \label{choose_wrong}
    \begin{center}
        \begin{subfigure}{0.45\textwidth}
        \caption{Mistakes in choice arm}
        \centering
        \includegraphics[width=\textwidth]{Figuras/line_cw_apr_tot_tut.pdf}

    \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
        \caption{Financial value of mistake}
        \centering
        \includegraphics[width=\textwidth]{Figuras/money_cw_apr_tot_tut.pdf}
 \end{subfigure}
    \bigskip

    \end{center}

\end{figure}

\subsection{Second ML exercise}

\begin{figure}[H]
    \caption{}
    \label{choose_wrong}
    \begin{center}
        \begin{subfigure}{0.45\textwidth}
        \caption{Gradient Boosting}
        \centering
        \includegraphics[width=\textwidth]{Figuras/ps_te_apr.pdf}

    \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
        \caption{KNN}
        \centering
        \includegraphics[width=\textwidth]{Figuras/ps_te_apr1.pdf}
 \end{subfigure}
    \bigskip

    \end{center}

\end{figure}

\subsubsection{Question:}
\textit{As in the previous exercise, I think it might be worth trying to say something about the conditional TUT without invoking Assumption 3, and I think we can do this using a conditional LATE, given our design.}

\newpage
\clearpage

\end{document}

### 2022-04-28 donde.tex
Fan & Park Bounds

@@
         \begin{subfigure}{0.45\textwidth}
-        \caption{\% better when forced to Hard commitment}
+        \caption{\% better when forced to forced commitment}
         \centering
@@
 
+\begin{figure}[H]
+        \caption{Learning over time}
+    \label{fc_discount_rates}
+    \begin{center}
+        \centering
+        \includegraphics[width=0.55\textwidth]{Figuras/learning_over_time.pdf}
+    \end{center}
+     \scriptsize This Figure shows the evolution of default over time as borrowers have more options to choose the frequent payment contract. This uses the observational data. 
+     %\textit{Do file: }  \texttt{learning\_over\_time.do}
+\end{figure}
+
 \vspace{.3in}

### 2022-04-28 RScripts/tot_tut_instr_forest.R

@@ -140,7 +140,7 @@ fit_instr_forest = function(xvar, wvar, yvar, zvar, dta, nme) {
 
 require("dplyr")
 
-tot_tut <- read_csv('./_aux/tot_tut_eff_cost_loan.csv') 
+tot_tut <- read_csv('./_aux/tot_tut_apr.csv') 
 
 data_in <- tot_tut %>%
   mutate_all(~ifelse(is.na(.), median(., na.rm = TRUE), .))  
@@ -161,15 +161,15 @@ rename_var(tut)
 
 
 # PREPARE VARIABLES
-X_tot <- select(tot,-c(eff_cost_loan, choice_nsq, choice_nonsq, forced_fee_vs_choice, choice_vs_control,
+X_tot <- select(tot,-c(apr, choice_nsq, choice_nonsq, forced_fee_vs_choice, choice_vs_control,
                        esample_tot, esample_tut, prenda))
-Y_tot <- select(tot,eff_cost_loan)
+Y_tot <- select(tot,apr)
 W_tot <- as.numeric(tot$choice_nsq == 1)
 Z_tot <- as.numeric(tot$choice_vs_control == 1)
 
-X_tut <- select(tut,-c(eff_cost_loan, choice_nsq, choice_nonsq, forced_fee_vs_choice, choice_vs_control,
+X_tut <- select(tut,-c(apr, choice_nsq, choice_nonsq, forced_fee_vs_choice, choice_vs_control,
                        esample_tot, esample_tut, prenda))
-Y_tut <- select(tut,eff_cost_loan)
+Y_tut <- select(tut,apr)
 W_tut <- as.numeric(tut$choice_nonsq == 1)
 Z_tut <- as.numeric(tut$forced_fee_vs_choice == 1)
 

### 2022-06-09 RScripts/grf.R
change scheme in figures

@@ -30,7 +30,7 @@ heterogeneity_effect <- function(data_in,treatment_var,outcome_var,writedata,ext
   data_frame <- data_in %>%
     filter(data_in[,treatment_var] == 1 | data_in[,treatment_var] == 0) %>%
     select(-c( pro_2, pro_3, pro_4, pro_5, pro_6, pro_7, pro_8, pro_9, fee, fecha_inicial,
-               apr, eff_cost_loan, def_c, des_c, fc_admin), 
+               apr, eff_cost_loan, def_c, des_c, fc_admin, dias_primer_pago), 
            treatment_var, outcome_var ) %>%
     mutate_all(~ifelse(is.na(.), median(., na.rm = TRUE), .))  
   data_copy <- data_frame

### 2022-07-15 OA.tex
change scheme in figures
tot vs tut inference analysis

@@
 It shows that the CDF of the status quo contract is always below that of the fee-forcing (and this difference is significant for the points indicated by the blue line), and therefore that the former first-order stochastically dominates the later for weakly decreasing utility functions; see Proposition \ref{eq_fosd}.
-    % \texttt{ecdf\_fc.do}}
+    % \texttt{ecdf\_eff.do}}
 \end{figure}
@@
 
-\scriptsize {
+\scriptsize 
 \noindent This figure reports bivariate regressions of the form $\widehat{TakeUp} = \alpha + \beta \: X_i + \epsilon_i$, where $\widehat{TakeUp}$ is the prediction using random forests.
@@
 The opposite holds for clients that are more economically vulnerable (can barely pay for food, electricity, etc) and those that report being more stressed.
-}
+
+\newpage
+
+\subsection{Bounding ToT \& TuT} \label{bound_tot_tut_appendix}
+
+\vspace{.2in}
+\normalsize
+\linespread{1.25}
+%Really force it to normal size and linespread
+\normalsize
+\linespread{1.25}
+
+Even without the exclusion restriction, it’s possible to bound $\mathbb{E}[Y_1-Y_0\;|\;T=0]$ and $\mathbb{E}[Y_1-Y_0\;|\;T=1]$ using observed outcomes in the forced arm and observed take-up in the choice arm.
+It should also be possible to create bounds conditional on covariates.
+The basic approach is similar to that of \cite{huber_mellace}.
+\\
+
+From the $Z=0$ arm we identify the distribution $F_0$ of $Y_0$, the potential outcome when forced into the no-commitment contract.
+Now, from the choice arm we know that around 90\% of people are $T=0$ types.
+Because choice was randomly assigned, the 90\% figure holds for all arms in the experiment.
+This tells us that $F_0$ is a 90\%-10\% mixture of $Y_0\;|\;T=0$ and $Y_0\;|\;T=1$.
+Cut out the bottom 10\% of $F_0$ and calculate the mean of this new distribution.
+Then cut out the top 10\% of $F_0$ and compute the mean of this new distribution.
+The result is an upper and lower bound for $\mathbb{E}[Y_0\;|\;T=0]$ that does not rely on the exclusion restriction.
+We can apply similar reasoning to bound $\mathbb{E}[Y_1\;|\;T=0]$ Combining the previous bounds gives a bound for the TuT that does not rely on the exclusion restriction, and analogous we can bound the ToT.
+\\
+
+The \cite{huber_mellace} bounds for the ToT \& TuT APR are respectively:
+\[\text{ToT} : [-481.8, 483.7]\quad\quad\quad\text{TuT} : [-17.9, 90.6]\]
+
+Note that since both TuT and ToT estimates from the LATE approach lies inside these bounds, we do not falsify the exclusion restriction.
 
@@
 \linespread{1.25}
+%Really force it to normal size and linespread
+\normalsize
+\linespread{1.25}
 
@@
 \vspace{.2in}
+\normalsize
+\linespread{1.25}
+%Really force it to normal size and linespread
 \normalsize
@@
 \caption{Effect of frequent payment in observational data}
-\label{attrition_table}
+\label{te_obs}
 \begin{center}

### 2022-07-15 donde.tex
change scheme in figures
tot vs tut inference analysis

@@
 
-This is not the first paper to find low demand for commitment, however it is the first we know of that can compare choice vs forcing with a money-metric outcome such as loan repayment.
-The fact that the Forced Commitment contract lowers financial costs for almost all clients, together with the fact that only 11\% choose it must mean that many consumers are choosing contracts with higher financial costs for themselves.
+\todo[inline]{Issac: At different points in the paper we use different conventions for whether a positive treatment effect is ``good'' or ``bad.'' We should pick one and stick with it throught to avoid confusion.
+(E.g.
+ToT/TuT tables treat positive as good but figure 15 treats negative as good.)}
+
+\todo[inline]{Think more carefully about the ``mistake'' wording here.
+There's a difference between an ex-ante mistake and an ex-post mistake.
+Need to think more carefully about this.
+This also relates to the question about what information to use in the first machine learning exercise.
+I think if we use the $\text{ATE}(X)$ that's closer to an ex ante measure than if we use, say, $\mathbm{E}[Y_1|X] - Y_0$.}
+
+This is not the first paper to find low demand for commitment, however it is the first we know of that can compare choice versus forcing with a money-metric outcome such as loan repayment.
+As discussed above, a policy of forced commitment substantially lowers financial costs on average, both compared to a baseline no-commitment contract and a policy in which borrowers are free to choose their preferred contract.
+In spite of this, only 11\% of those in the choice arm choose commitment.
+In a world of heterogeneous treatment effects, this could nevertheless be consistent with individual rationality.
+So do the the other 89\% know something about their personal situations that we as researchers do not, or are most people in the choice arm making a costly mistake?
+We now present a range of econometric exercises that shed light on this question.
+Taken together, they cast considerable doubt on the notion of ``selection on gains,'' as embodied in the traditional Roy model.
+While we find evidence of substantial treatment effect heterogeneity, most borrowers would experience lower financial costs under a commitment contract.
+Indeed, leveraging a unique feature of our experimental design, we show that the average effect of commitment for the \emph{untreated}, those who would not voluntarily choose commitment, is large and negative.
+In an important sense the ``wrong'' people are choosing commitment.
+
+\subsection{Potential Outcomes and Exclusion}
+
+To interpret our evidence on the importance of paternalism presented below, it is important to be precise about the potential outcomes in our empirical setting.
+This requires introducing some notation.
+Let $Z_i \in \{0, 1, 2\}$ denote the treatment arm to which to participant $i$ was assigned: $Z_i = 0$ denotes the forced no-commitment arm, $Z_i = 1$ denotes the forced commitment arm, and $Z_i = 2$ denotes the choice arm.
+Now let $D_i$ be the treatment that participant $i$ actually \emph{received}, where $D_i = 0$ denotes no-commitment and $D_i = 1$ denotes commitment.
+By design, our experiment features perfect compliance in the $Z_i = 0$ and $Z_i = 1$ arms.
+It is only in the $Z_i = 2$ arm that participants are free to choose between alternative contracts.
+Let $C_i \in \{0, 1 \}$ denote a participant's ``choice type.'' If $C_i = 1$ then participant $i$ \emph{would choose commitment}, given the choice; if $C_i = 0$ she would not.
+Whereas a participant's choice type $C_i$ is only observed if she is allocated to the choice arm ($Z_i = 2$), her treatment $D_i$ and experimental arm $Z_i$ are always observed.
+Given the design of our experiment, these quantities are related by
+\begin{equation}
+D_i = \mathbbm{1}(Z_i \neq 2) Z_i + \mathbbm{1}(Z_i = 2) C_i.
+\label{eq:potentialTreatments}
+\end{equation}
+
+We maintain the stable unit treatment value assumption (SUTVA) throughout.
+This means that participant $i$'s outcomes depend only on her \emph{own} values of $Z_i$ and $D_i$, not those of any other person in the experiment: there are no \emph{spillovers}.
+Under this assumption, a fully general model for the potential outcomes in our experiment would take the form $Y_i(d, z)$ for $d\in \{0,1\}$ and $z \in \{0, 1, 2\}$, allowing participant $i$'s potential outcome to depend \emph{both} on the treatment she actually receives, $D_i$, and the experimental arm to which she is assigned, $Z_i$.
+This model is too general, however, to allow us to explore the importance of paternalism.
+Accordingly, we impose the following standard exclusion restriction:
+\begin{equation}
+Y_i(d=0, z=0) = Y_i(d=0, z=2) \equiv Y_{i0}, \quad
+Y_i(d=1, z=1) = Y_i(d=1, z=2) \equiv Y_{i1}.
+\label{eq:exclusion}
+\end{equation}
+\Eqref{eq:exclusion} says that each participant's potential outcome is the same regardless of whether she \emph{chooses} a particular treatment $D=d$ or is \emph{assigned} the same treatment.
+Viewing $Z_i$ as an instrumental variable (IV) for the treatment $D_i$, this nothing more than the usual IV exclusion restriction.\footnote{\cite{chamberlain2011bayesian} uses an identical assumption to develop a theory of optimal treatment choice for an individual who has access to data from an RCT.} \Eqref{eq:exclusion} is plausible in our empirical setting and has testable implications that we fail to reject: see Appendix \todo{Fill in}{???} for details.
+Under \eqref{eq:exclusion}, each participant's observed outcome $Y_i$ is related to her potential outcomes $(Y_{i0}, Y_{i1})$ according to
+\todo[inline]{Issac: add a section \ref{bound_tot_tut_appendix} to the appendix and drop in the results for the Huber \& Mellace stuff; Frank: follow-up and draft that section of the appendix.}
+\begin{equation}
+    Y_i = \mathbbm{1}(Z_i =0) Y_{i0} + \mathbbm{1}(Z_i = 1)  Y_{i1}  + \mathbbm{1}(Z_i = 2) \left[(1 - C_i) Y_{i0} + C_i Y_{i1} \right].
+\label{eq:potentialOutcomes}
+\end{equation}
+
+\Eqref{eq:potentialOutcomes} is the key to understanding the results that follows.
+By randomly assigning $Z_i=0$ and $Z_i = 1$, our experiment identifies the marginal distributions of $Y_{i0}$ and $Y_{i1}$ in the population as a whole.
+By randomly assigning $Z_i=2$, it likewise identifies the share of people with $C_i = 1$ (the treated), the distribution of $Y_{i1}$ for these individuals, and the distribution of $Y_{i0}$ for those with $C_i = 0$ (the untreated).
+Because $Z_i$ is assigned independently of pre-treatment covariates $X_i$, our design also identifies the corresponding \emph{conditional} distributions of $Y_{i0}$ and $Y_{i1}$ given $X_i$.
+These distributions are the ingredients that we use below to explore the importance of paternalism.
+
+%The fact that the Forced Commitment contract lowers financial costs for almost all clients, together with the fact that only 11\% choose it must mean that many consumers are choosing contracts with higher financial costs for themselves.
 We now use several different techniques to shed further light on the idea that the `wrong' people are choosing commitment.
 
-Our core impacts show that forced commitment is uniquely effective, a result that can only arise if those who would not have freely chosen commitment benefit from it.
+%Our core impacts show that forced commitment is uniquely effective, a result that can only arise if those who would not have freely chosen commitment benefit from it.
 We now delve more deeply into this result.
 
-\subsection{Treatment Effects for Compliers and Non-Compliers}
-
-A unique feature of our design is the randomized assignment to treatment, control, and choice of treatment.
-This structure allows us to observe the average value of both the treated and untreated potential outcomes, as well as the selection into treatment that would occur under choice.
+\subsection{Treatment Effect Heterogeneity}
+\todo[inline]{There's a connection between homogeneous treatment effects and predictability. In a homogeneous world, the treatment effect is perfectly predictable from the ATE.}
+
+If the effect of commitment were homogeneous, there would be nothing more to say on the topic of paternalism.
+Our estimates of $\mathbbm{E}(Y_{i1} - Y_{i0}) = \mathbbm{E}(Y_i|Z_i=1) - \mathbbm{E}(Y_i|Z_i=0)$ presented above are large and statistically significant.
+If $\Delta_i \equiv Y_{i1} - Y_{i0}$ were constant across $i$, this would be enough to conclude that the 89\% who do not choose commitment would have been better off if they had.
+As we now show, however, the effect of commitment varies considerably across individuals.
+Our approach relies on the following simple observation: if $\Delta_i$ is constant across $i$ then we must have
+\[
+\text{ATE}(X_i) \equiv \mathbbm{E}[\Delta_i |X_i] = \mathbbm{E}[\Delta_i] \equiv \text{ATE}
+\]
+for any covariates $X_i$ that vary across $i$.
+If, on the other hand, $\text{ATE}(X_i)$ can be predicted using some scalar function $\tau(\cdot)$ of $X_i$, then the average treatment effect function is not constant so there must be treatment effect heterogeneity.
+
+We operationalize this idea using a two-step approach proposed by \cite{chernozhukov2018generic}.
+We begin by randomly dividing the participants in the forced arms of the experiment ($Z_i \neq 2$) into two groups: a ``training set'' and a \todo{80/20 split?}{``test set.''} In the first step, we apply random forests to the training set to estimate two proxy predictors: $\psi(\cdot|\text{Training})$ approximates the untreated potential outcome function, $\mathbbm{E}[Y_{i0}|X_i] = \mathbbm{E}[Y_i|Z_i=0,X_i]$, while  $\tau(\cdot|\text{Training})$, approximates the average treatment effect function
+\[
+\text{ATE}(X_i) = \mathbbm{E}[Y_i|Z_i=1,X_i] - \mathbbm{E}[Y_i|Z_i=0, X_i].
+\]
+The proxy predictors need not be unbiased or even consistent estimators of the functions they aim to approximate: the goal of this exercise is merely to find a scalar function of $X_i$ that \emph{accurately predicts} $\text{ATE}(X_i)$.
+
+In the second step we fit a linear regression model to data from the training set using regressors constructed from the proxy functions $\psi(\cdot|\text{Training})$ and $\tau(\cdot|\text{Training})$ constructed in the first step.
+In particular, we estimate
+\begin{equation}
+Y_i = \alpha_0 + \alpha_1 \psi_i + \beta_1 (Z_i - \mathbbm{E}[Z_i]) + \beta_2 (Z_i - \mathbbm{E}[Z_i])(\tau_i - \mathbbm{E}[\tau_i]) + \epsilon_i
+\label{eq:chernreg}
+\end{equation}
+where $\psi_i \equiv \psi(X_i|\text{Training})$ and $\tau_i \equiv \tau(X_i|\text{Training})$.\footnote{This is a slightly simpler regression than the one proposed in equation (3.1) of \cite{chernozhukov2018generic}, which involves propensity score weights.
+Because the random assignment of $Z$ in our experiment does \emph{not} condition on $X$, the propensity score weights in our case are constant over $X$ and hence drop out.} As shown by \cite{chernozhukov2018generic}, the coefficients $\beta_1$ and $\beta_2$ from \eqref{eq:chernreg} identify the \emph{best linear predictor} of the conditional ATE based on $\tau(\cdot|\text{Training})$, namely
+\[
+\beta_1 = \mathbbm{E}[\text{ATE}(X_i)] = \text{ATE}, \quad
+\beta_2 = \frac{\text{Cov}[\text{ATE}(X_i), \tau_i]}{\text{Var}(\tau_i)}.
+\]
+If treatment effects are homogeneous we must have $\beta_2 = 0$.
+Rejecting this hypothesis establishes that $\tau_i$ predicts $\text{ATE}(X_i)$ and hence that $\Delta_i$ varies.
+Since $\tau_i$ and $\psi_i$ do not depend on the test set, inference for the regression in \eqref{eq:chernreg} is straightforward conditional on the Training/Test split.
+
+\todo[inline]{Discuss the results here.}
+
+\todo[inline]{Issac: re-run this exercise with removing the propensity score weights $p(Z)$. Presumably it shouldn't change anything, but it's simpler to explain what we do and probably less noisy
+
+\begin{table}[H]
+\begin{center}
+\scriptsize{\input{./Tables/test_calibration_2.tex}}
+\end{center}
+\end{table}
+
+}
+
+\todo[inline]{Some Questions for Issac: (1) How are we carrying out the sample splitting?
+If we cluster standard errors at the branch-day level, we should take this into account when we split.
+(2) How are you carrying out inference for $\beta_2$?
+Chernozhukov et al discuss two approaches: ``conditional'' and ``variational.'' The former is simpler as it conditions on the training/test split.
+The latter is a bit more involved, since one accounts for uncertainty arising from different splits.
+(3) What are the details of the random forest procedure employed here?
+(Tuning parameters choice, etc.) We should put them into the appendix.}
+
+\subsection{Bounding the Distribution of Treatment Effects}
+
+As explained above, our experimental design identifies the marginal distributions of $Y_{i0}$ and $Y_{i1}$, call them $F_0$ and $F_1$.
+We can estimate them using the empirical CDF of $Y_i$ for $Z_i=0$ and $Z_i = 1$ respectively.
+Because we can never observe both treated and untreated potential outcomes for the same person, however, the distribution $F_\Delta$ of the individual treatment effects $\Delta_i \equiv Y_{i1} - Y_{i0}$ cannot be identified.
+It can, however, be bounded.
+\cite{fan2010sharp} show that the best possible pointwise bounds for $F_\Delta$ are given by $\underline{F}(\delta) \leq F_\Delta(\delta) \leq \overline{F}(\delta)$ where the bounding functions $\underline{F}$ and $\overline{F}$ are defined as
+\[
+\underline{F}(\delta) \equiv \max \left\{0, \sup_y F_1(y) - F_0(y - \delta)  \right\}, \quad
+\overline{F}(\delta) \equiv 1 + \min \left\{0, \inf_y F_1(y) - F_0(y-\delta) \right\}.
+\]
+These bounds are simple to compute, and can be surprisingly informative.
+Here we use them to bound the fraction of borrowers who benefit from commitment.
+Given the way that we have defined our outcome variables, this is the share of borrowers whose treatment effect is \emph{negative}, i.e.\ $F_\Delta(0)$.
+To construct the sharp bounds for this quantity, we simply substitute $\delta = 0$ into the preceding equations and estimate $F_0$ and $F_1$ using their empirical analogues constructed from the forced commitment and forced no-commitment arms of the experiment.
+
+\todo[inline]{Issac: add in the confidence interval at $\delta = 0$ along with the figure \ref{fan_park_bounds}; Frank follow-up to add 1-2 sentences discussing the results.
+Presumably we find that $F_\Delta(0) > 0.11$ this means that at least some people who choose not to commit \emph{must} be making a mistake, although we don't know who they are and this doesn't tell us how large the mistake is.}
+
+An alternative way of presenting the \cite{fan2010sharp} bounds is in terms of quantiles of the distribution of $\Delta$.
+Let $0 < q < 1$, and define $Q_0, Q_1, Q$ to be the quantile functions corresponding to $F_0, F_1$ and $F_\Delta$.\footnote{In other words, $Q_0(q) \equiv \inf \{x | F(x) \geq q\}$ and so on.} Then the sharp bound for $Q_\Delta(q)$ is given by $\underline{Q}(q) \leq Q(q) \leq \overline{Q}(q)$ where
+\[
+\overline{Q}(q) \equiv \inf_{u \in [q,1]} [Q_1(u) - Q_0(u - q)], \quad
+\underline{Q}(q) \equiv \sup_{u\in [0,q]} [Q_1(u) - Q_0(1 + u - q)]
+\]
+By substituting $q = 0.11$, these expressions allow us to bound the 11th percentile of the distribution of $\Delta$.
+Under a stylized Roy model in which borrowers with the largest (negative) treatment effects choose commitment, $Q(0.11)$ equals the treatment effect for the borrower at the margin of indifference between choosing commitment.
+
+\todo[inline]{Issac: add the interval for $Q(0.11)$.
+Maybe we don't need a second figure with the confidence bands for the whole quantile function.
+(Overkill?) Frank: add a sentence or two discussing the results.
+Presumably the aforementioned quantile is indeed negative and fairly large.}
+
+Taken together, these bounds suggest that at least some borrowers who would benefit from commitment do not choose it when offered.
+
+\subsection{Treatment on the Treated and Untreated}
+In the preceding section, we used outcome data from the forced arms ($Z_i\neq 2$) along with the commitment take-up rate in the choice arm ($Z_i = 2$) to argue that at least some of the 89\% of participants who did \emph{not} choose commitment would have been better off if they had.
+By additionally examining \emph{outcome data} in the choice arm, it is possible to say more.
+We now show how our experimental design can be used to identify the average effect of commitment for both those who would choose it (the treated) and those who would not (the untreated).
+In particular, we identify the treatment on the treated (ToT) and treatment on the untreated (TuT) effects, defined as follows:
+\[
+\text{ToT} \equiv \mathbbm{E}(Y_{i1} - Y_{i0} | C_i = 1), \quad
+\text{TuT} \equiv \mathbbm{E}(Y_{i1} - Y_{i0} | C_i = 0).
+\]
+The TuT and ToT effects are particularly interesting for understanding the importance of paternalism.
+If the TuT is positive, this means that someone who did not choose commitment would have been experienced a better outcome \emph{on average} if she had.
+In a canonical Roy model, the ToT should exceed both the TuT and average treatment effect (ATE).
+Because our design identifies all three quantities, it allows us to test this implication directly.
+If the ToT is statistically distinguishable from and substantially larger than the TuT, this provides empirical support for the relevance of selection-on-gains in real-world decision-making.
+
+A number of recent papers compare estimates of the ToT and TuT to better understand who selects into treatment and why, e.g.\ \cite{cornelissen2018benefits} and \cite{Walters}.
+While valuable and interesting, this line of work relies, at least to some extent, upon structural modeling assumptions to extrapolate from the reduced-form quantities that are identified by the data alone to more interesting, and economically relevant, causal parameters.\footnote{While the marginal treatment effects (MTE) approach \citep{heckman2007econometric} can in principle be used to identify the ToT and TuT without parametric restrictions, doing so requires an instrumental variable $Z$ with sufficiently rich support that the probability of treatment take-up given $Z$ varies continuously between zero and one.
+In practice, instrumental variables are usually discrete and, even when continuous, typically have a more modest effect on take-up.} An alternative approach aims to avoid structural assumptions by calculating conditional local average treatment effects (LATE) given observed covariates $X$ and reweighting these according to the distribution of $X$ in some population of interest \citep{aronow2013beyond,angrist2013extrapolate}.
+For example, one might re-weight using the distribution of $X$ in the population as a whole, rather than the sub-population of compliers, to extrapolate from LATE to ATE.
+But you can't squeeze blood from a stone.
+This ``LATE-and-reweight'' approach relies upon assumptions of its own, most crucially the assumption that there is \emph{no selection-on-gains} conditional on $X$, i.e.\ that the conditional LATE equals the conditional ATE.
+As far as we are aware, ours is the only paper in the literature to identify the ToT and TuT without ruling out unobserved selection-on-gains or relying on additional structural modeling assumptions.
+This is possible because of the unique design of our experiment.
+
+\todo[inline]{Presumably we want to say something about this design potentially being applicable to other settings?}
+
+The key insight can be read directly from \eqref{eq:potentialTreatments} and \eqref{eq:potentialOutcomes}.
+Viewing $Z_i$ as an instrumental variable, our design can be interpreted as a \emph{pair} of RCTs, each subject to one-sided non-compliance.\footnote{For a full derivation, see Appendix ???.} The first of these compares $Z_i=0$ to $Z_i = 2$.
+For each individual with $Z_i = 0$ we have $D_i = 0$ and observe $Y_{i0}$.
+For those with $Z_i = 2$ we have $D_i = C_i$ and observe $(1 - C_i) Y_{i0} + C_i Y_{i1}$.
+This is identical to a ``randomized encouragement'' design in which treatment is only available to those who are encouraged: $Z_i = 2$.
+Under this interpretation, those with $C_i = 1$ are ``the compliers'' and it follows that
+\begin{equation}
+\frac{\mathbbm{E}(Y_i|Z_i=2) - \mathbbm{E}(Y_i|Z_i =0)}{\mathbbm{E}(D_i|Z_i=2)-\mathbbm{E}(D_i|Z_i=0)} = 
+\frac{\mathbbm{E}(Y_i|Z_i=2) - \mathbbm{E}(Y_i|Z_i =0)}{\mathbbm{E}(D_i|Z_i=2)} = \mathbbm{E}(Y_{i1} - Y_{i0}|C_i = 1)
+\label{eq:ToT}
+\end{equation}
+since $\mathbbm{E}(D_i|Z_i=0)=0$ by \eqref{eq:potentialTreatments}.
+
+A closely related if slightly less intuitive argument can be used to construct a Wald estimand that identifies the TuT.
+Here we consider $Z_i = 1$ to be the ``encouragement'' and compare the outcomes for these individuals to those with $Z_i = 2$.
+If $Z_i = 1$ then $D_i = 1$ and we observe $Y_{i1}$; If $Z_i = 2$ then $D_i = C_i$ and we observe $(1 - C_i) Y_{i0} + C_i Y_{i1}$.
+Again, we can view this as an experiment with one-sided non-compliance, but now the situation is reversed.
+Everyone with $Z_i = 1$ is treated, but some people with $Z_i = 2$ are ``always-takers'' who obtain the treatment ($D_i = 1$) despite having been allocated to the ``control'' arm $Z_i=2$.
+Under this interpretation, the ``compliers'' are those with $C_i = 0$: when $Z_i=1$ they take the treatment, and when $Z_i=2$, they do not.
+Thus,
+\begin{equation}
+\frac{\mathbbm{E}(Y_i|Z_i=1) - \mathbbm{E}(Y_i|Z_i =2)}{\mathbbm{E}(D_i|Z_i=1)-\mathbbm{E}(D_i|Z_i=2)} = 
+\frac{\mathbbm{E}(Y_i|Z_i=1) - \mathbbm{E}(Y_i|Z_i =0)}{1 - \mathbbm{E}(D_i|Z_i=2)} = \mathbbm{E}(Y_{i1} - Y_{i0} | C_i = 0)
+\label{eq:TuT}
+\end{equation}
+since $\mathbbm{E}(D_i|Z_i = 1)= 1$ by \eqref{eq:potentialTreatments}.
+
+\Eqref{eq:ToT} and \eqref{eq:TuT} are useful for understanding why our design identifies the ToT and TuT, but they are less convenient for estimation and inference.
+In Appendix \todo{Frank: fill in}{???}, we show that
+\begin{align}
+\label{eq:ToTreg}
+Y_i &= \mathbbm{E}(Y_{i0}) + (\text{ATE}) \mathbbm{1}(Z_i = 1) + (\text{ToT}) \left[\mathbbm{1}(Z_i = 2) \times D_i\right] + U_i \\
+\label{eq:TuTreg}
+Y_i &= \mathbbm{E}(Y_{i1}) + (\text{ATE}) \left[ -\mathbbm{1}(Z_i = 0)\right] + (\text{TuT}) \left[ -\mathbbm{1}(Z_i = 2) \times (1 - D_i)\right] + V_i 
+\end{align}
+where the error terms $U_i$ and $V_i$ satisfy 
+\[
+\mathbbm{E}(V_i) = \mathbbm{E}(U_i) = \mathbbm{E}[U_i \mathbbm{1}(Z_i = z)] = \mathbbm{E}[V_i \mathbbm{1}(Z_i = z)] = 0, \quad z = 0, 1, 2.
+\]
+It follows that a pair of just-identified, linear instrumental variables regressions can be used to estimate and carry out inference for each of our quantities of interest.
+To identify the ATE and ToT, run IV on \eqref{eq:ToTreg} with instruments $\mathbbm{1}(Z_i = 1)$ and $\mathbbm{1}(Z_i=2)$.
+An F-test based on this regression can then be used to test the restriction $\text{ATE} = \text{ToT}$, and the usual IV output can be used to carry out inference for the ToT.
+No programming is required.
+Similarly, to identify the ATE and TuT run IV on \ref{eq:TuTreg} with instruments $\mathbbm{1}(Z_i = 0)$ and $\mathbbm{1}(Z_i = 2)$.
+An F-test based on this regression can then be used to test the restriction $\text{ATE} = \text{TuT}$, and the usual IV output can be used to carry out inference for the TuT.
+Again, no programming or special software is required.
+
+As explained above, a canonical Roy model would suggest that $\text{TuT} \leq \text{ATE} \leq \text{ToT}$.
+For this reason it is particularly interesting to consider inference for the \emph{difference} $(\text{ToT} - \text{TuT})$.
+The point estimate of this difference can be constructed directly from the results of the IV regressions described above.
+Because the respective estimates appear in different equations, however, a bit more work is required to obtain a standard error for $(\text{ToT} - \text{TuT})$.
+Define the shorthand
+\[
+p_0 \equiv \mathbbm{P}(Z_i=0), \quad p_1 \equiv \mathbbm{P}(Z_i = 1), \quad q_0 \equiv \mathbbm{E}[\mathbbm{1}(Z_i = 2)(1 - D_i)], \quad q_1 \equiv \mathbbm{E}[\mathbbm{1}(Z_i = 2) D_i].
+\]
+As shown in Appendix \todo{Frank: fill in}{???}, the asymptotic variance of $(\text{Tot} - \text{TuT})$ is given by
+\[
+\text{AVAR}(\text{ToT} - \text{TuT}) = \boldsymbol{\omega}' \boldsymbol{\Sigma} \boldsymbol{\omega}, \quad
+\boldsymbol{\omega}' \equiv \displaystyle \begin{bmatrix}
+-\frac{1}{q_1} & \frac{1}{q_0} & \left(\frac{p_1 - 1}{p_0q_1} - \frac{1}{q_0}\right) & -\frac{1}{q_1} - \frac{1 - p_0}{p_1 q_0}
+\end{bmatrix}
+\]
+where $\boldsymbol{\Sigma}$ is a covariance matrix that can be estimated from the residuals of \eqref{eq:ToTreg} and \eqref{eq:TuTreg}. Under iid observations,
+
+\todo[inline]{Explain two leading forms that $\Sigma$ can take: heterosked and cluster}
+
+\todo[inline]{Frank: give an overview of how to do the comparison of TuT and ToT.
+Want it to be ``idiot proof'' -- easy to do in standard software, etc.
+Details in the appendix but want the contribution to be clear.
+Cluster at the level of the randomization.
+(Almost WLOG for experiments).
+Can put some additional details in the appendix.}
+
+\todo[inline]{Issac: add the table of TuT/ATE/ToT results without covariates. For the moment I suppose we \emph{don't} have the ToT/TuT comparison. (See Frank todo above!)}
+
+\todo[inline]{Because they appear in different equations, testing TuT = ToT is slightly more involved. Explain how to do it here, but put additional details in the appendix.}
+
+\todo[inline]{Frank: after the preceding todo notes, revise the text below that discusses the ToT/TuT etc results.
+Think about how to compare/contrast/relate to the bounding exercises above as well as the ITT results.}
+
+%A unique feature of our design is the randomized assignment to treatment (forced commitment), control (forced no-commitment), and choice of treatment.
+
+%This structure allows us to observe the average value of both the treated and untreated potential outcomes, as well as the selection into treatment that would occur under choice.
 A starting point for how to exploit this structure is to apply the logic usually used to estimate the Treatment on the Treated (ToT) to also recover the Treatment on the Untreated (TuT).
@@
 
-More formally, let $Z_i$ be the observed, randomly assigned experimental allocation, where $Z_i=0$ denotes the control arm, $Z_i=1$ denotes the Forced arm, and $Z_i=2$ is the Choice arm.
+%More formally, let $Z_i$ be the observed, randomly assigned experimental allocation, where $Z_i=0$ denotes the control arm, $Z_i=1$ denotes the Forced arm, and $Z_i=2$ is the Choice arm.
 Let $C_i$ be the choice type; $C_i=0$ when individual $i$ does not choose commitment and $C_i=1$ when chooses commitment, observed in the Choice arm and latent in the other two arms.
@@
 
-To test the difference between gains for choosers versus gains from non-choosers we need to identify $\mathbb{E}[Y_1-Y_0\;|\;C=1]$ (the Treatment on the Treated), and $\mathbb{E}[Y_1-Y_0\;|\;C=0]$ (the Treatment on the Untreated).
+%To test the difference between gains for choosers versus gains from non-choosers we need to identify $\mathbb{E}[Y_1-Y_0\;|\;C=1]$ (the Treatment on the Treated), and $\mathbb{E}[Y_1-Y_0\;|\;C=0]$ (the Treatment on the Untreated).
 The observed outcome in the Choice arm is the weighted average of the treated and untreated outcomes; $p \times\mathbb{E}[Y_1\;|\;C=1] + (1-p)\times\mathbb{E}[Y_0\;|\;C=0]$.
@@
 
-\begin{align*}
-ToT \equiv \mathbb{E}[Y_1 - Y_0 \;\mid\; C=1]  &=   \frac{\mathbb{E}[Y \;\mid\; Z=2] - \mathbb{E}[Y \;\mid\; Z=0]}{p} \\
-TuT \equiv \mathbb{E}[Y_1 - Y_0 \;\mid \;C=0]  &=  \frac{\mathbb{E}[Y \;\mid\; Z=1] - \mathbb{E}[Y \;\mid\; Z=2]}{(1-p)} 
-\end{align*}
-
-This estimate of the ToT is the standard one that would result from instrumenting for compliance with the offering of treatment as in \cite{angrist1996identification}.
+%\begin{align*}
+%ToT \equiv \mathbb{E}[Y_1 - Y_0 \;\mid\; C=1]  &=   \frac{\mathbb{E}[Y \;\mid\; Z=2] - \mathbb{E}[Y \;\mid\; Z=0]}{p} \\
+%TuT \equiv \mathbb{E}[Y_1 - Y_0 \;\mid \;C=0]  &=  \frac{\mathbb{E}[Y \;\mid\; Z=1] - \mathbb{E}[Y \;\mid\; Z=2]}{(1-p)} 
+%\end{align*}
+
+%This estimate of the ToT is the standard one that would result from instrumenting for compliance with the offering of treatment as in \cite{angrist1996identification}.
 The TuT is the analogous estimator, which could be recovered in a regression pooling the forced and choice arms and instrumenting for \textit{not} complying with being assigned to the choice arm (for a more formal development, see the appendix).
@@
 
-\[ToT = \frac{\beta^C}{p}; \qquad\quad TuT = \frac{(\beta^F - \beta^C)}{(1-p)}; \qquad\quad (ToT-TuT) = \frac{\beta^C}{p}- \frac{(\beta^F - \beta^C)}{(1-p)}. \]
+%\[ToT = \frac{\beta^C}{p}; \qquad\quad TuT = \frac{(\beta^F - \beta^C)}{(1-p)}; \qquad\quad (ToT-TuT) = \frac{\beta^C}{p}- \frac{(\beta^F - \beta^C)}{(1-p)}. \]
+
+\todo[inline]{This next paragraph needs to be edited a bit. I think there's one more number that we need to put in the table of results: the SE for the ToT versus TuT?}
 
@@
 
+\todo[inline]{Frank: cut this section.}
+
 We now want to move away from the experimental consideration of the arms as a whole, and dive into the individual heterogeneity to learn more about the relationship between choice and outcomes.
@@
 \subsection{Relating Random Forest Impacts to Observed Choice}
+
+\todo[inline]{Frank/Issac: need to discuss confidence interval construction for the mistakes exercise.
+I'm not 100\% sure about it.
+There's question of what we can actually infer from the random forest exercise.
+We can't learn the distribution of treatment effects within a ``bin'' but we can learn the ATE in the bin along with its standard error, and we can treat that as approximately normal.
+Another issue concerns whether we do or do not use the observed outcomes for the people in the choice arm.
+At present we're not using this.
+But you might say that we should.
+This would entail predicting their \emph{counterfactual} outcome.
+What I mean here is that $\text{ATE}(X)$ is what you would use to assign someone to a particular treatment, given that you have observed their $X$.
+But what we have is a little different.
+We observe both their $X$ and either $Y_1$ or $Y_0$.
+I think there's an interesting question here about whether we're interested in something \emph{ex ante} or \emph{ex post}.
+It relates to the issue of ``mistakes.'' We should discuss briefly as a group so Frank \& Issac can make the appropriate adjustments if needed.}
+
+\todo[inline]{Issac: add in the picture for the ToT/TuT version of the ``mistakes'' exercise \& histograms of treatment effects by groups.
+We already have the histogram in figure 15 for the ATE.
+Is it possible to say something about the covariates of the choosers for whom we estimate a negative ToT?}
+
+\todo[inline]{Frank draft: The first exercise looks at ``mistakes.'' These are defined by predicting treatment effects for the people in the \emph{choice} arm using their covariates.
+If the treatment effect is positive and they don't choose treatment, this is a mistake.
+If the treatment effect is negative and they choose treatment this is a mistake.
+There are two ways of carrying out this exercise.
+The first way assumes that, conditional on $X$, there is no selection on gains.
+This version uses a model of heterogeneous treatment effects estimated using only people from the forced arms to create predicted ATEs for people in the choice arm.
+The second version calculates ToT and TuT versions of the same thing, but this involves using data from the choice arm, so it's less efficient because sample-splitting is required so we have to discard some people from the choice arm when calculating ``mistakes.'' Issac implements this with 5 partitions of 20/80, repeating five times and averaging over the result.
+Comparing the results of the two versions we find something interesting.
+For the non-choosers, the results are similar in both versions.
+Lots of mistakes and pretty big.
+For the choosers, we find very little evidence of mistakes using the ATE version and much more using the ToT version.
+What does this mean?
+It suggests some form of perverse selection on gains.
+These must be people who think commitment will help them but it actually hurts them.
+Question: what are their covariates like?
+What kind of people are they?
+This gets to Craig's question about who is hurt in each treatment regime.
+There aren't very many choosers (only 11\%) and something between 15 and 35\%, depending on the threshold, of them are ``hurt'' according to our model.
+So quantitatively it's not many people.
+What about with the ATE: what fraction of people \emph{overall} do we predict are hurt by the treatment?
+(We bounded it above, but now we have a model.) Seems like this is around 1-2\%.}
 
@@
 
+\begin{table}[H]
+\caption{Gains for choosers versus gains from non-choosers (ToT \& TuT)}
+\label{tot_tut}
+\begin{center}
+\scriptsize{\input{./Tables/tot_tut_se.tex}}
+\end{center}
+ \scriptsize This table shows estimates of the ToT and the TuT with an IV-LATE framework.
+The ToT is computed as the usual LATE with one-sided non-compliance between the choice and control arm, and the TuT is the LATE on non-compliers.
+%\textit{Do file: } \texttt{tot\_tut\_reg.do}
+\end{table}
+
 \end{landscape}
@@
      \scriptsize  This Figure shows the accumulated percentage of recovery in time by treatment arm. 
-     %\textit{Do file: }  \texttt{survival\_graph.do}
+     %\textit{Do file: }  \texttt{cumulative\_porc\_pay\_time.do}
 \end{figure}
@@
 \begin{figure}[H]
+    \caption{Fan \& Park bounds}
+    \label{fan_park_bounds}
+    \begin{center}
+
+    \begin{subfigure}{0.475\textwidth}
+        \caption{APR}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/fan_park_bounds_apr.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.475\textwidth}
+        \caption{Financial Cost}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/fan_park_bounds_fc_admin.pdf}
+    \end{subfigure}
+    \end{center}
+\end{figure}
+
+\begin{figure}[H]
      \caption{Quantile regressions}
@@
 Finally, for comparison purposes, the blue diamond displays the effects of forcing them into the frequent payment commitment contract and are just transcribed from Figure \ref{fc_pro2} above.
-      %\textit{Do file: }  \texttt{fc\_te\_choice\_dec.do, def\_te\_choice\_dec.do, fc\_quantilereg\_choice\_dec.do}
+      %\textit{Do file: }  \texttt{soft\_qreg.do, qregs\_choosers\_nonchoosers.do}
 \end{figure}
@@
 Using the 80 right most points, we estimate a \textit{positive} relationship.
-        %\textit{Do file: }  \texttt{effect\_contr\_takeup.do, choose\_wrong\_quant\_wrong.do, choose\_wrong\_quant\_wrong\_decomposition.do}
+        %\textit{Do file: }  \texttt{choose\_wrong\_quant\_wrong.do, choose\_wrong\_quant\_wrong\_decomposition.do}
 \end{figure}

### 2022-07-15 RScripts/eff_te_grf.R

@@ -40,16 +40,11 @@ data_in <- rename.vars(data_in, c(
   "visit_number_d5", 
   "visit_number_d6", 
   "visit_number_d7",
-  "log_prestamo",
-  "pr_recup",
   "edad",
   "faltas",
   "val_pren_std",
   "genero",
-  "pres_antes",
-  "plan_gasto_bin",
-  "masqueprepa",
-  "pb"
+  "masqueprepa"
 ),
 c(
   "monday",
@@ -74,16 +69,11 @@ c(
   "visit.number.5",
   "visit.number.6",
   "visit.number.7",
-  "log.loan",
-  "subj.pr",
   "age",
   "income.index",
   "subj.loan.value",
   "female",
-  "pawn.before",
-  "makes.budget",
-  "more.high.school",
-  "pb"
+  "more.high.school"
 ))
 
 require("dplyr")
@@ -132,7 +122,7 @@ fun_threshold_alpha = function(alpha, g) {
   return((2*sum(num)/den-lambda)^2)
 }
 
-alfa = optimize(fun_threshold_alpha, g, interval=c(0.001, 0.49))$minimum
+alfa = optimize(fun_threshold_alpha, g, interval=c(0.001, 0.499))$minimum
 
 X <- X[propensity_score>=alfa & propensity_score<=(1-alfa),]
 Y <- Y[propensity_score>=alfa & propensity_score<=(1-alfa),]
@@ -233,6 +223,49 @@ write_csv(blp, file = "_aux/blp_eff_te_grf.csv")
 
 tc <- tidy(test_calibration(tau.forest))
 print(tc)
+
+
+observation_weights <- function(forest) {
+  # Case 1: No sample.weights
+  if (is.null(forest$sample.weights)) {
+    if (length(forest$clusters) == 0 || !forest$equalize.cluster.weights) {
+      raw.weights <- rep(1, NROW(forest$Y.orig))
+    } else {
+      # If clustering with no sample.weights provided and equalize.cluster.weights = TRUE, then
+      # give each observation weight 1/cluster size, so that the total weight of each cluster is the same.
+      clust.factor <- factor(forest$clusters)
+      inverse.counts <- 1 / as.numeric(Matrix::colSums(Matrix::sparse.model.matrix(~ clust.factor + 0)))
+      raw.weights <- inverse.counts[as.numeric(clust.factor)]
+    }
+  }
+  
+  # Case 2: sample.weights provided
+  if (!is.null(forest$sample.weights)) {
[…]

### 2022-07-15 RScripts/grf.R

@@ -129,7 +129,7 @@ heterogeneity_effect <- function(data_in,treatment_var,outcome_var,writedata,ext
   # Equivalently the first value of alpha (in increasing order) such that the constraint is achieved by equality
   # (as the constraint is a monotone increasing function in alpha)
   
-  alfa = optimize(fun_threshold_alpha, g, interval=c(0.001, 0.49))$minimum
+  alfa = optimize(fun_threshold_alpha, g, interval=c(0.001, 0.499))$minimum
 
   X <- X[propensity_score>=alfa & propensity_score<=(1-alfa),]
   Y <- Y[propensity_score>=alfa & propensity_score<=(1-alfa),]
@@ -284,7 +284,7 @@ data <- read_csv('./_aux/heterogeneity_grf.csv')
 
 #Heterogeneous Effects
 for (arm in c("pro_2")){
-  for (dep in c("apr", "eff_cost_loan", "def_c", "des_c", "fc_admin")){
+  for (dep in c("apr", "eff_cost_loan", "def_c", "des_c", "fc_admin", "dias_primer_pago")){
     heterogeneity_effect(data_extended,arm,dep,1,1) 
     heterogeneity_effect(data,arm,dep,1,0) 
   }

### 2022-07-15 RScripts/te_grf.R

@@ -125,7 +125,7 @@ te_grf <- function(data_in, outcome_var, name) {
   # Equivalently the first value of alpha (in increasing order) such that the constraint is achieved by equality
   # (as the constraint is a monotone increasing function in alpha)
   
-  alfa = optimize(fun_threshold_alpha, g, interval=c(0.001, 0.49))$minimum
+  alfa = optimize(fun_threshold_alpha, g, interval=c(0.001, 0.499))$minimum
   
   X <- X[propensity_score>=alfa & propensity_score<=(1-alfa),]
   Y <- Y[propensity_score>=alfa & propensity_score<=(1-alfa),]

### 2022-08-10 donde.tex
consolidate multiple loans and first visit as outcomes

@@
 
-\todo[inline]{Issac: At different points in the paper we use different conventions for whether a positive treatment effect is ``good'' or ``bad.'' We should pick one and stick with it throught to avoid confusion.
+\todo[inline]{Issac: At different points in the paper we use different conventions for whether a positive treatment effect is ``good'' or ``bad.'' We should pick one and stick with it through to avoid confusion.
 (E.g.
@@
 This also relates to the question about what information to use in the first machine learning exercise.
-I think if we use the $\text{ATE}(X)$ that's closer to an ex ante measure than if we use, say, $\mathbm{E}[Y_1|X] - Y_0$.}
+I think if we use the $\text{ATE}(X)$ that's closer to an ex ante measure than if we use, say, $\mathbbm{E}[Y_1|X] - Y_0$.}
 
@@
 
+\begin{figure}[H]
+    \caption{Choice of contracts and treatment effects (ToT \& TuT)}
+    \label{choose_wrong}
+    \begin{center}
+        \begin{subfigure}{0.45\textwidth}
+        \caption{Mistakes in choice arm}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/line_cw_apr_tot_tut.pdf}
+
+    \end{subfigure}
+        \begin{subfigure}{0.45\textwidth}
+        \caption{Financial value of mistake}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/money_cw_apr_tot_tut.pdf}
+
+    \bigskip
+
+    \end{subfigure}
+        \begin{subfigure}{0.45\textwidth}
+        \caption{\% better when forced to forced commitment}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/line_better_forceall_apr_te_cf.pdf}
+
+    \end{subfigure}
+    %     \begin{subfigure}{0.45\textwidth}
+    %     \caption{\footnotesize{Effect of CATE benefit vs predicted take-up}}
+    %     \centering
+    %     \includegraphics[width=\textwidth]{Figuras/benefit_choice.pdf}% takeuppr_def.pdf 
+    % \end{subfigure}
+
+    \end{center}
+        \scriptsize
+        In Panel (a) we estimate what the treatment effect of the commitment contract \textit{would have been} for all subjects in the choice arm if they had been forced into the fee-commitment contract.
+To do this we proceed in two steps.
+First, we estimate treatment effects in the forcing arm by comparing the Forced Commitment arm against the status quo arm.
+We let these effects be heterogeneous as a function of our $x$'s using \cite{atheygrf}'s methodology of causal forests.
+Second, we extrapolate these treatment effects based on the choice arm using the same $x$'s.
+Once we have personalized counterfactual treatment effects in the choice arm we calculate what fraction of subjects in the choice arm incurred in financial costs that are  $> z$\% than if they had chosen the opposite contract of what they actually chose, were $z$\% is defined as a fraction of the loan.
+$z$\% is a level of tolerance we can vary and we plot it in the X-axis.
+The left Y-axis measures the fraction of subjects that would have been better by a margin of $z$\% if they changed their choice, and the right Y-axis measures the amount of money ``left on the table''.
+We use bootstrap to tighten the confidence intervals (CIs).
+\cite{atheygrf}'s heterogeneous treatment effect using GRF is asymptotically normal.
+We compute the HTE ($\mu$) together with standard errors ($\sigma$) .
+For every pledge, we draw a random effect from a normal distribution with parameters ($\mu$,$\sigma^2$), and compute via bootstrap the percentage that choose wrong, along normal-approximation CIs (results are robust if we use instead percentile CIs or bias-corrected CIs) .
+This allows us to estimate a distribution for the upper and lower bound CIs, which we then use to obtain a 95\% CI.
+Panel (b) is analogous to Panel (a) except that it does the exercise separately for clients we classified as overconfident ($OC_i:=\mathbbm{1}(P^s_i-\widehat{P_i(X_i)}>0))$ and those we classified as not overconfident.
+Panel (c) simulates what percentage would be better by at least $z$ if we forced everybody of those in the Commitment Choice arm into the fee-commitment contract.
+        % Panel (d) asks whether it is the case that people with larger causal benefits from the Forced Commitment contract would be more likely to select that contract.
+To do this we proceed in two steps as well.
+First we estimate a flexible model of take-up of the fee commitment contract \textit{in the choice arm} using random forests, and from this model obtain a probability $P(x_i)$ of choosing the Forced Commitment contract for a client with characteristics $x_i$.
+We extrapolate this model to clients in the Forced Commitment arm to estimate what would they have chosen if we had given them choice.
+        % Figure (d) plots $\widehat{P(x_i)}$ in the X-axis using a binscatter that splits the X-axis in 100 percentile bins.
+The Y-axis plots the heterogeneous treatment effects of the fee forcing contract on the probability of losing the pawns (more negative means then more likely to recover it), averaged for the respective x-axis bin.
+Positive assortative selection would mean a negative relationship: those who benefit more by treatment and lose the pawn less are \emph{less} likely to choose it.
+Using all bins we estimate a slope of zero in the relationship.
+Using the 80 right most points, we estimate a \textit{positive} relationship.
+        %\textit{Do file: }  \texttt{choose\_wrong\_quant\_wrong.do, choose\_wrong\_quant\_wrong\_decomposition.do}
+\end{figure}
+
 \cleardoublepage

### 2022-09-12 donde_old.tex
restoring comments in overlaf

--- 2022-08-10 donde.tex
@@
     Financial \; Cost_i =& \underbrace{\sum_t P^c_{it}}_{\text{Payments to capital}} + \underbrace{\sum_t P^f_{it}}_{\text{Payments of fees}}  +\underbrace{\sum_t P^i_{it}}_{\text{Payments to interests}} \\
-    &\quad\qquad + \underbrace{\mathds{1}(Default_i) \times Pawn \: Value_i}_{\text{Cost of losing pawn}}
+    &\quad\qquad + \underbrace{\mathds{1}(Default_i) \times Appraised \: Value_i}_{\text{Cost of losing pawn}}
 \end{align*}

### 2022-10-03 Tables/Attrition.tex
update of results using corrected deinition of apr

@@
 \midrule
-Number of branch-day pawns & 31    & 31    & 37    & 0.16  &       & 32    & 34    & 0.57 \\
-      & (2.2) & (2.3) & (2.6) &       &       & (2.4) & (1.8) &  \\
-Survey response rate & 0.77  & 0.75  & 0.77  & 0.74  &       & 0.8   & 0.79  & 0.5 \\
-      & (0.02) & (0.03) & (0.02) &       &       & (0.02) & (0.02) &  \\
-\% ended up pawning & 0.98  & 0.97  & 0.98  & 0.43  &       & 0.99  & 0.99  & 0.49 \\
-      & (0.004) & (0.007) & (0.006) &       &       & (0.003) & (0.003) &  \\
+Number of branch-day pawns & 31    & 33    & 40    & 0.14  &       & 33    & 34    & 0.76 \\
+      & (3)   & (2.7) & (3.3) &       &       & (3.2) & (2.2) &  \\
+Survey response rate & 0.78  & 0.75  & 0.77  & 0.59  &       & 0.8   & 0.81  & 0.69 \\
+      & (0.02) & (0.03) & (0.03) &       &       & (0.03) & (0.02) &  \\
 \midrule
-Obs   & 2600  & 2484  & 3435  &       &       & 2157  & 2768  &  \\
+Obs   & 1770  & 1954  & 2580  &       &       & 1470  & 1904  &  \\
 \bottomrule

### 2022-10-03 donde.tex
update of results using corrected deinition of apr

@@
 
+\begin{landscape}
+
 \begin{table}[H]
@@
 \end{table}
+
+\end{landscape}
 
@@
 %Given that the loan lasts close to 90 days, bringing payments to present value makes little difference.
-      %\footnotesize{ } \textit{Do file: }  \texttt{hist\_fc.do, hist\_eff.do}
+      %\footnotesize{ } \textit{Do file: }  \texttt{hist\_fc.do}
 \end{figure}
@@
    \begin{subfigure}{0.49\textwidth}
+   \caption{Ended contract}
         \centering
         \includegraphics[width=\textwidth]{Figuras/survival_graph_ended.pdf}
+    \end{subfigure} 
+   \begin{subfigure}{0.49\textwidth}
+   \caption{Recovery}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/survival_graph_unpledge.pdf}
     \end{subfigure}     
@@
         \caption{\% of payment over time}
-    \label{survival_graph}
+    \label{porc_payment_over_time}
     \begin{center}
@@
     Finally, `APR - interests'  The treatment effects are indicated in standard deviations, together with 95\% confidence intervals.
+
+%\textit{Do file: } \texttt{fc\_robustness.do}
 \end{figure}
@@
 Panel (b) shows the treatment effects on the several definitions of cost for the soft arms.
+
+%\textit{Do file: } \texttt{soft\_te,do, fc\_robustness\_soft.do}    
 \end{figure}
@@
     \begin{center}
-
-    \begin{subfigure}{0.475\textwidth}
+    \begin{subfigure}{0.675\textwidth}
         \caption{APR}
@@
     \end{subfigure}
-    \begin{subfigure}{0.475\textwidth}
-        \caption{Financial Cost}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/fan_park_bounds_fc_admin.pdf}
-    \end{subfigure}
-    \end{center}
+    \end{center}
+
+%\textit{Do file: } \texttt{fan\_park\_bnds,do}       
 \end{figure}

### 2022-10-04 donde.tex
refinement of ML exercises

@@
 Jose Maria Barrero, Francis DiTraglia, Andrei Gomberg, Emilio Gutierrez, David Laibson, Aprajit Mahajan, Matt Rabin, Charlie Sprenger, and seminar participants at ITAM provided valuable feedback.}}
-\author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira   \thanks{Seira: ITAM, enrique.seira@gmail.com (corresponding author); McIntosh:  University of California San Diego, ctmcintosh@ucsd.edu; Meza: University of California at Berkeley, isaac.meza@berkeley.edu; Sadka: ITAM, jsadka@itam.mx} }
+\author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira \and Frank DiTraglia   \thanks{Seira: ITAM/MSU, enrique.seira@gmail.com (corresponding author); McIntosh:  University of California San Diego, ctmcintosh@ucsd.edu; Meza: University of California at Berkeley, isaac.meza@berkeley.edu; Sadka: ITAM, jsadka@itam.mx; DiTraglia: Oxford, frank@ditraglia.com} }
 \date{This draft:  \today \\[2 cm]}
@@
 This ``LATE-and-reweight'' approach relies upon assumptions of its own, most crucially the assumption that there is \emph{no selection-on-gains} conditional on $X$, i.e.\ that the conditional LATE equals the conditional ATE.
-As far as we are aware, ours is the only paper in the literature to identify the ToT and TuT without ruling out unobserved selection-on-gains or relying on additional structural modeling assumptions.
+As far as we are aware, ours is the only paper in the literature to simultaneously point identify the ATE, ToT and TuT without ruling out unobserved selection-on-gains or relying on additional structural modeling assumptions.
 This is possible because of the unique design of our experiment.
 
-\todo[inline]{Presumably we want to say something about this design potentially being applicable to other settings?}
+\todo[inline]{Somewhere in the paper we'll want to talk about when this kind of design could be useful in a bit more detail.}
 
@@
 As explained above, a canonical Roy model would suggest that $\text{TuT} \leq \text{ATE} \leq \text{ToT}$.
-For this reason it is particularly interesting to consider inference for the \emph{difference} $(\text{ToT} - \text{TuT})$.
+For this reason it is particularly interesting to consider inference for the difference $(\text{ToT} - \text{TuT})$, namely the \emph{average selection on gains}:
+\[
+\text{ASG} \equiv \mathbbm{E}[Y_{i1} - Y_{i0}|C_i = 1] - \mathbb{E}[Y_{i1} - Y_{i0} | C_i = 0] = \text{ToT} - \text{TuT}.
+\]
 The point estimate of this difference can be constructed directly from the results of the IV regressions described above.
 Because the respective estimates appear in different equations, however, a bit more work is required to obtain a standard error for $(\text{ToT} - \text{TuT})$.
-Define the shorthand
+The details are straightforward but somewhat tedious, so we present them in Appendix \todo{!!!}{???}.
+A companion STATA package accompanying this paper provides cluster robust inference for the average selection on gains, along with two related quantities: the average selection bias (ASB) and average selection on levels (ASL)
 \[
-p_0 \equiv \mathbbm{P}(Z_i=0), \quad p_1 \equiv \mathbbm{P}(Z_i = 1), \quad q_0 \equiv \mathbbm{E}[\mathbbm{1}(Z_i = 2)(1 - D_i)], \quad q_1 \equiv \mathbbm{E}[\mathbbm{1}(Z_i = 2) D_i].
+\text{ASB} \equiv \mathbbm{E}[Y_{i0}|C_i = 1] - \mathbbm{E}[Y_{i0}|C_i = 0], \quad 
+\text{ASL} \equiv \mathbbm{E}[Y_{i1}|C_i = 1] - \mathbbm{E}[Y_{i1}|C_i = 0].
 \]
-As shown in Appendix \todo{Frank: fill in}{???}, the asymptotic variance of $(\text{Tot} - \text{TuT})$ is given by
-\[
-\text{AVAR}(\text{ToT} - \text{TuT}) = \boldsymbol{\omega}' \boldsymbol{\Sigma} \boldsymbol{\omega}, \quad
-\boldsymbol{\omega}' \equiv \displaystyle \begin{bmatrix}
--\frac{1}{q_1} & \frac{1}{q_0} & \left(\frac{p_1 - 1}{p_0q_1} - \frac{1}{q_0}\right) & -\frac{1}{q_1} - \frac{1 - p_0}{p_1 q_0}
-\end{bmatrix}
-\]
-where $\boldsymbol{\Sigma}$ is a covariance matrix that can be estimated from the residuals of \eqref{eq:ToTreg} and \eqref{eq:TuTreg}. Under iid observations,
-
-\todo[inline]{Explain two leading forms that $\Sigma$ can take: heterosked and cluster}
-
-\todo[inline]{Frank: give an overview of how to do the comparison of TuT and ToT.
+We show that these latter two quantities are point identified in Appendix \todo{!!!}{???}.
+
+%Define the shorthand
+%\[
+%p_0 \equiv \mathbbm{P}(Z_i=0), \quad p_1 \equiv \mathbbm{P}(Z_i = 1), \quad q_0 \equiv \mathbbm{E}[\mathbbm{1}(Z_i = 2)(1 - D_i)], \quad q_1 \equiv \mathbbm{E}[\mathbbm{1}(Z_i = 2) D_i].
+%\]
+%As shown in Appendix \todo{Frank: fill in}{???}, the asymptotic variance of $(\text{Tot} - \text{TuT})$ is given by
+%\[
+%\text{AVAR}(\text{ToT} - \text{TuT}) = \boldsymbol{\omega}' \boldsymbol{\Sigma} \boldsymbol{\omega}, \quad
+%\boldsymbol{\omega}' \equiv \displaystyle \begin{bmatrix}
+%-\frac{1}{q_1} & \frac{1}{q_0} & \left(\frac{p_1 - 1}{p_0q_1} - \frac{1}{q_0}\right) & -\frac{1}{q_1} - \frac{1 - p_0}{p_1 q_0}
+%\end{bmatrix}
+%\]
+%where $\boldsymbol{\Sigma}$ is a covariance matrix that can be estimated from the residuals of \eqref{eq:ToTreg} and \eqref{eq:TuTreg}. Under iid observations, 
+%
+%\todo[inline]{Explain two leading forms that $\Sigma$ can take: heterosked and cluster}
+
+%\todo[inline]{Frank: give an overview of how to do the comparison of TuT and ToT.
 Want it to be ``idiot proof'' -- easy to do in standard software, etc.
@@
 
-\todo[inline]{Because they appear in different equations, testing TuT = ToT is slightly more involved. Explain how to do it here, but put additional details in the appendix.}
+%\todo[inline]{Because they appear in different equations, testing TuT = ToT is slightly more involved. Explain how to do it here, but put additional details in the appendix.}
 
@@
 The differences between treatment effects for compliers and non-compliers are of borderline significance in some of the unadjusted specifications, but are not significant once adjusted.\footnote{It is worth noting that the statistical power of these estimands is driven by the compliance rate; given our low overall compliance we are better powered to measure the TuT than the ToT, and the power for the difference between the two would be highest with a compliance rate of 50\%.}   Because of the large standard errors on the ToT coming from the low compliance rate in the Choice arm we are unable to state with statistical confidence that the TuT is higher than the ToT, but the TuT is strongly positive while the ToT is weakly negative, and so in both relative and absolute terms the choices being made are `wrong' relative to the potential outcomes.
+
+\subsection{Marginal Treatment Effects}
+As described above, our experimental design point identifies the ATE, TUT, and TOT without the need to carry out a marginal treatment effects (MTE) analysis that would rely, to some extent, on structural assumptions or shape restrictions.
+Nonetheless, researchers who are interested in learning more about essential heterogeneity can combine our design with an MTE approach.
+\todo[inline]{Need to flesh out a bit more, but in short: (1) can extend the results of Mogstad et al (2017) to use our ATE, TUT, and TOT as additional inequality restrictions that constrain partial identification bounds for MTEs; (2) Could allow more flexibility in the approach of Carneiro et al (2011) by recovering $\mu_0(x)$ and $\mu_1(x)$ from the forced arm.
+This permits richer forms of observed heterogeneity than the linear specification that is typically used in applied MTE papers.
+One could also combine (1) and (2) or use (1) as a specification test for (2).}
 
@@
 
-\begin{landscape}
-
 \begin{table}[H]
@@
 \begin{center}
-\scriptsize{\input{./Tables/tot_tut_reg.tex}}
+\scriptsize{\input{./Tables/tot_tut.tex}}
 \end{center}
@@
 The ToT is computed as the usual LATE with one-sided non-compliance between the choice and control arm, and the TuT is the LATE on non-compliers.
-%\textit{Do file: } \texttt{tot\_tut\_reg.do}
+%\textit{Do file: } \texttt{tot\_tut.do}
 \end{table}
-
-\begin{table}[H]
-\caption{Gains for choosers versus gains from non-choosers (ToT \& TuT)}
-\label{tot_tut}
-\begin{center}
-\scriptsize{\input{./Tables/tot_tut_se.tex}}
-\end{center}
- \scriptsize This table shows estimates of the ToT and the TuT with an IV-LATE framework.
-The ToT is computed as the usual LATE with one-sided non-compliance between the choice and control arm, and the TuT is the LATE on non-compliers.
-%\textit{Do file: } \texttt{tot\_tut\_reg.do}
-\end{table}
-
-\end{landscape}
 
@@
 \begin{figure}[H]
-    \caption{Fan \& Park bounds}
+    \caption{Fan \& Park bounds for benefit in APR\% }
     \label{fan_park_bounds}
@@
       \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_2.pdf}
+    \end{subfigure}  
+     \begin{subfigure}{0.45\textwidth}
+    \caption{Recovery}
+       \centering
+      \includegraphics[width=\textwidth]{Figuras/he_dist_des_c_pro_2.pdf}
     \end{subfigure}      
@@
     \end{subfigure}
-
+     \begin{subfigure}{0.475\textwidth}
+        \caption{Default}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/benefit_choice_tau_def.pdf}
+    \end{subfigure} 
     \end{center}
@@
     \end{subfigure}
-
+    \begin{subfigure}{0.475\textwidth}
+        \caption{Default}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/cdf_predchoose_tau_def.pdf}
+    \end{subfigure}
     \end{center}

### 2022-10-04 RScripts/grf.R

@@ -10,8 +10,8 @@ library(rattle)
 library(broom)
 
 # SET WORKING DIRECTORY
-setwd('C:/Users/isaac/Dropbox/Apps/ShareLaTeX/Donde2020')
-set.seed(5289364)
+setwd('C:/Users/isaac/Dropbox/Apps/Overleaf/Donde2020')
+set.seed(1)
 
 source("./RScripts/best_tree.R")
 
@@ -30,7 +30,7 @@ heterogeneity_effect <- function(data_in,treatment_var,outcome_var,writedata,ext
   data_frame <- data_in %>%
     filter(data_in[,treatment_var] == 1 | data_in[,treatment_var] == 0) %>%
     select(-c( pro_2, pro_3, pro_4, pro_5, pro_6, pro_7, pro_8, pro_9, fee, fecha_inicial,
-               apr, eff_cost_loan, def_c, des_c, fc_admin, dias_primer_pago), 
+               apr, def_c, des_c, fc_admin), 
            treatment_var, outcome_var ) %>%
     mutate_all(~ifelse(is.na(.), median(., na.rm = TRUE), .))  
   data_copy <- data_frame
@@ -38,64 +38,48 @@ heterogeneity_effect <- function(data_in,treatment_var,outcome_var,writedata,ext
   if (extendedsample == 0) {
     # Data with names in english
     data_frame <- rename.vars(data_frame, c(
-      "dummy_dow1",
       "dummy_dow2",
       "dummy_dow3",
       "dummy_dow4",
       "dummy_dow5",
       "dummy_dow6",
-      "dummy_suc1",
       "dummy_suc2",
       "dummy_suc3",
       "dummy_suc4",
       "dummy_suc5",
       "dummy_suc6",
+      "num_arms_d2",
       "num_arms_d3",
       "num_arms_d4",
       "num_arms_d5",
       "num_arms_d6", 
-      "visit_number_d2", 
-      "visit_number_d3", 
-      "visit_number_d4", 
-      "visit_number_d5", 
-      "visit_number_d6", 
-      "visit_number_d7",
-      "log_prestamo",
-      "pr_recup",
+      "suc_x_dia",
       "edad",
       "faltas",
       "val_pren_std",
       "genero",
       "pres_antes",
-      "plan_gasto_bin",
+      "plan_gasto",
       "masqueprepa",
       "pb"
     ),
     c(
-      "monday",
       "tuesday",
       "wednesday",
       "thurdsay",
       "friday",
       "saturday",
-      "branch.1",
[…]

### 2022-10-04 RScripts/te_grf.R

@@ -10,8 +10,8 @@ library(rattle)
 library(broom)
 
 # SET WORKING DIRECTORY
-setwd('C:/Users/isaac/Dropbox/Apps/ShareLaTeX/Donde2020')
-set.seed(5289174)
+setwd('C:/Users/isaac/Dropbox/Apps/Overleaf/Donde2020')
+set.seed(1)
 
 fun_threshold_alpha = function(alpha, g) {
   lambda = 1/(alpha*(1-alpha))
@@ -29,62 +29,54 @@ te_grf <- function(data_in, outcome_var, name) {
     mutate_all(~ifelse(is.na(.), median(., na.rm = TRUE), .))  
   data_copy <- data_in
   data_in <- rename.vars(data_in, c(
-    "dummy_dow1",
     "dummy_dow2",
     "dummy_dow3",
     "dummy_dow4",
     "dummy_dow5",
     "dummy_dow6",
-    "dummy_suc1",
     "dummy_suc2",
     "dummy_suc3",
     "dummy_suc4",
     "dummy_suc5",
     "dummy_suc6",
+    "num_arms_d2",
     "num_arms_d3",
     "num_arms_d4",
     "num_arms_d5",
     "num_arms_d6", 
-    "visit_number_d2", 
-    "visit_number_d3", 
-    "visit_number_d4", 
-    "visit_number_d5", 
-    "visit_number_d6", 
-    "visit_number_d7",
     "edad",
     "faltas",
     "val_pren_std",
     "genero",
-    "masqueprepa"
+    "pres_antes",
+    "plan_gasto",
+    "masqueprepa",
+    "pb"
   ),
   c(
-    "monday",
     "tuesday",
     "wednesday",
     "thurdsay",
     "friday",
     "saturday",
-    "branch.1",
     "branch.2",
     "branch.3",
     "branch.4",
     "branch.5",
     "branch.6",
+    "num.exp.arms.2",
     "num.exp.arms.3",
     "num.exp.arms.4",
     "num.exp.arms.5",
     "num.exp.arms.6",
-    "visit.number.2",
-    "visit.number.3",
-    "visit.number.4",
-    "visit.number.5",
-    "visit.number.6",
-    "visit.number.7",
     "age",
     "income.index",
     "subj.loan.value",
     "female",
-    "more.high.school"
+    "pawn.before",
+    "makes.budget",
+    "more.high.school",
+    "p.bias"
   ))
   
   require("dplyr")
[…]

### 2022-10-04 RScripts/tot_tut_instr_forest.R

@@ -10,68 +10,60 @@ library(rattle)
 library(broom)
 
 # SET WORKING DIRECTORY
-setwd('C:/Users/isaac/Dropbox/Apps/ShareLaTeX/Donde2020')
-set.seed(5289174)
+setwd('C:/Users/isaac/Dropbox/Apps/Overleaf/Donde2020')
+set.seed(1)
 
 
 rename_var = function(df) { 
   df <- rename.vars(df, c(
-    "dummy_dow1",
     "dummy_dow2",
     "dummy_dow3",
     "dummy_dow4",
     "dummy_dow5",
     "dummy_dow6",
-    "dummy_suc1",
     "dummy_suc2",
     "dummy_suc3",
     "dummy_suc4",
     "dummy_suc5",
     "dummy_suc6",
+    "num_arms_d2",
     "num_arms_d3",
     "num_arms_d4",
     "num_arms_d5",
     "num_arms_d6", 
-    "visit_number_d2", 
-    "visit_number_d3", 
-    "visit_number_d4", 
-    "visit_number_d5", 
-    "visit_number_d6", 
-    "visit_number_d7",
     "edad",
     "faltas",
     "val_pren_std",
     "genero",
-    "masqueprepa"
+    "pres_antes",
+    "plan_gasto",
+    "masqueprepa",
+    "pb"
   ),
   c(
-    "monday",
     "tuesday",
     "wednesday",
     "thurdsay",
     "friday",
     "saturday",
-    "branch.1",
     "branch.2",
     "branch.3",
     "branch.4",
     "branch.5",
     "branch.6",
+    "num.exp.arms.2",
     "num.exp.arms.3",
     "num.exp.arms.4",
     "num.exp.arms.5",
     "num.exp.arms.6",
-    "visit.number.2",
-    "visit.number.3",
-    "visit.number.4",
-    "visit.number.5",
-    "visit.number.6",
-    "visit.number.7",
     "age",
     "income.index",
     "subj.loan.value",
     "female",
-    "more.high.school"
+    "pawn.before",
+    "makes.budget",
+    "more.high.school",
+    "p.bias"
   ))
 }
 
@@ -110,7 +102,26 @@ fit_instr_forest = function(xvar, wvar, yvar, zvar, dta, nme) {
     X = model.matrix(~., data = xvar), 
     Y = data.matrix(yvar), 
     W = wvar,
-    Z = zvar)
+    Z = zvar,
+    num.trees = 5000,
+    sample.weights = NULL,
[…]

### 2022-11-12 donde.tex
who makes mistakes based on ml models on ps and hte
start analysis on asl and asb

@@
 Ricardo Olivares, Gerardo Melendez, and Alonso de Gortari provided excellent research assistance and Erick Molina helped with formatting.
-Jose Maria Barrero, Francis DiTraglia, Andrei Gomberg, Emilio Gutierrez, David Laibson, Aprajit Mahajan, Matt Rabin, Charlie Sprenger, and seminar participants at ITAM provided valuable feedback.}}
+Jose Maria Barrero, Andrei Gomberg, Emilio Gutierrez, David Laibson, Aprajit Mahajan, Matt Rabin, Charlie Sprenger, and seminar participants at ITAM provided valuable feedback.}}
 \author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira \and Frank DiTraglia   \thanks{Seira: ITAM/MSU, enrique.seira@gmail.com (corresponding author); McIntosh:  University of California San Diego, ctmcintosh@ucsd.edu; Meza: University of California at Berkeley, isaac.meza@berkeley.edu; Sadka: ITAM, jsadka@itam.mx; DiTraglia: Oxford, frank@ditraglia.com} }
@@
 The key insight can be read directly from \eqref{eq:potentialTreatments} and \eqref{eq:potentialOutcomes}.
-Viewing $Z_i$ as an instrumental variable, our design can be interpreted as a \emph{pair} of RCTs, each subject to one-sided non-compliance.\footnote{For a full derivation, see Appendix ???.} The first of these compares $Z_i=0$ to $Z_i = 2$.
+Viewing $Z_i$ as an instrumental variable, our design can be interpreted as a \emph{pair} of RCTs, each subject to one-sided non-compliance.\footnote{For a full derivation, see \hl{Appendix ???}.} The first of these compares $Z_i=0$ to $Z_i = 2$.
 For each individual with $Z_i = 0$ we have $D_i = 0$ and observe $Y_{i0}$.
@@
     \begin{subfigure}{0.475\textwidth}
-        \caption{Effective APR}
+        \caption{APR benefit}
         \centering
@@
     \begin{subfigure}{0.475\textwidth}
-        \caption{Effective APR benefit}
+        \caption{APR benefit}
         \centering

### 2022-11-12 RScripts/te_grf.R

@@ -99,6 +99,59 @@ te_grf <- function(data_in, outcome_var, name) {
   ###################################################################  
   ###################################################################  
   
+  # Estimation of E[Y | X , W = 1] and E[Y | X , W = 0]
+  X1 = X[W==1,]
+  X0 = X[W==0,]
+  Y1 = as.numeric(unlist(Y[W==1,]))
+  Y0 = as.numeric(unlist(Y[W==0,]))
+  
+  mu.1 = regression_forest(X1,Y1,
+    num.trees = 3000,
+    sample.weights = NULL,
+    clusters = NULL,
+    equalize.cluster.weights = FALSE,
+    sample.fraction = 0.5,
+    mtry = min(ceiling(sqrt(ncol(X)) + 20), ncol(X)),
+    min.node.size = 5,
+    honesty = TRUE,
+    honesty.fraction = 0.5,
+    honesty.prune.leaves = TRUE,
+    alpha = 0.05,
+    imbalance.penalty = 0,
+    ci.group.size = 2,
+    tune.parameters = c("alpha", "imbalance.penalty"),
+    tune.num.trees = 500,
+    tune.num.reps = 200,
+    tune.num.draws = 2000,
+    compute.oob.predictions = TRUE,
+    num.threads = NULL,
+    seed = 1)
+  
+  pr_mu1 = predict(mu.1, data_test, estimate.variance = TRUE)
+  
+  mu.0 = regression_forest(X0,Y0,
+    num.trees = 3000,
+    sample.weights = NULL,
+    clusters = NULL,
+    equalize.cluster.weights = FALSE,
+    sample.fraction = 0.5,
+    mtry = min(ceiling(sqrt(ncol(X)) + 20), ncol(X)),
+    min.node.size = 5,
+    honesty = TRUE,
+    honesty.fraction = 0.5,
+    honesty.prune.leaves = TRUE,
+    alpha = 0.05,
+    imbalance.penalty = 0,
+    ci.group.size = 2,
+    tune.parameters = c("alpha", "imbalance.penalty"),
+    tune.num.trees = 500,
+    tune.num.reps = 200,
+    tune.num.draws = 2000,
+    compute.oob.predictions = TRUE,
+    num.threads = NULL,
+    seed = 1)
+  
+  pr_mu0 = predict(mu.0, data_test, estimate.variance = TRUE)
   
   # OVERLAP ASSUMPTION
   propensity.forest = regression_forest(X, W)
[…]

### 2022-11-14 donde.tex
change eqref to ref, problem of extra {

@@
 \end{equation}
-\Eqref{eq:exclusion} says that each participant's potential outcome is the same regardless of whether she \emph{chooses} a particular treatment $D=d$ or is \emph{assigned} the same treatment.
-Viewing $Z_i$ as an instrumental variable (IV) for the treatment $D_i$, this nothing more than the usual IV exclusion restriction.\footnote{\cite{chamberlain2011bayesian} uses an identical assumption to develop a theory of optimal treatment choice for an individual who has access to data from an RCT.} \Eqref{eq:exclusion} is plausible in our empirical setting and has testable implications that we fail to reject: see Appendix \todo{Fill in}{???} for details.
-Under \eqref{eq:exclusion}, each participant's observed outcome $Y_i$ is related to her potential outcomes $(Y_{i0}, Y_{i1})$ according to
+\ref{eq:exclusion} says that each participant's potential outcome is the same regardless of whether she \emph{chooses} a particular treatment $D=d$ or is \emph{assigned} the same treatment.
+Viewing $Z_i$ as an instrumental variable (IV) for the treatment $D_i$, this nothing more than the usual IV exclusion restriction.\footnote{\cite{chamberlain2011bayesian} uses an identical assumption to develop a theory of optimal treatment choice for an individual who has access to data from an RCT.} \ref{eq:exclusion} is plausible in our empirical setting and has testable implications that we fail to reject: see Appendix \todo{Fill in}{???} for details.
+Under \ref{eq:exclusion}, each participant's observed outcome $Y_i$ is related to her potential outcomes $(Y_{i0}, Y_{i1})$ according to
 \todo[inline]{Issac: add a section \ref{bound_tot_tut_appendix} to the appendix and drop in the results for the Huber \& Mellace stuff; Frank: follow-up and draft that section of the appendix.}
@@
 
-\Eqref{eq:potentialOutcomes} is the key to understanding the results that follows.
+\ref{eq:potentialOutcomes} is the key to understanding the results that follows.
 By randomly assigning $Z_i=0$ and $Z_i = 1$, our experiment identifies the marginal distributions of $Y_{i0}$ and $Y_{i1}$ in the population as a whole.
@@
 where $\psi_i \equiv \psi(X_i|\text{Training})$ and $\tau_i \equiv \tau(X_i|\text{Training})$.\footnote{This is a slightly simpler regression than the one proposed in equation (3.1) of \cite{chernozhukov2018generic}, which involves propensity score weights.
-Because the random assignment of $Z$ in our experiment does \emph{not} condition on $X$, the propensity score weights in our case are constant over $X$ and hence drop out.} As shown by \cite{chernozhukov2018generic}, the coefficients $\beta_1$ and $\beta_2$ from \eqref{eq:chernreg} identify the \emph{best linear predictor} of the conditional ATE based on $\tau(\cdot|\text{Training})$, namely
+Because the random assignment of $Z$ in our experiment does \emph{not} condition on $X$, the propensity score weights in our case are constant over $X$ and hence drop out.} As shown by \cite{chernozhukov2018generic}, the coefficients $\beta_1$ and $\beta_2$ from \ref{eq:chernreg} identify the \emph{best linear predictor} of the conditional ATE based on $\tau(\cdot|\text{Training})$, namely
 \[
@@
 Rejecting this hypothesis establishes that $\tau_i$ predicts $\text{ATE}(X_i)$ and hence that $\Delta_i$ varies.
-Since $\tau_i$ and $\psi_i$ do not depend on the test set, inference for the regression in \eqref{eq:chernreg} is straightforward conditional on the Training/Test split.
+Since $\tau_i$ and $\psi_i$ do not depend on the test set, inference for the regression in \ref{eq:chernreg} is straightforward conditional on the Training/Test split.
 
@@
 
-The key insight can be read directly from \eqref{eq:potentialTreatments} and \eqref{eq:potentialOutcomes}.
+The key insight can be read directly from \ref{eq:potentialTreatments} and \ref{eq:potentialOutcomes}.
 Viewing $Z_i$ as an instrumental variable, our design can be interpreted as a \emph{pair} of RCTs, each subject to one-sided non-compliance.\footnote{For a full derivation, see \hl{Appendix ???}.} The first of these compares $Z_i=0$ to $Z_i = 2$.
@@
 \end{equation}
-since $\mathbbm{E}(D_i|Z_i=0)=0$ by \eqref{eq:potentialTreatments}.
+since $\mathbbm{E}(D_i|Z_i=0)=0$ by \ref{eq:potentialTreatments}.
 
@@
 \end{equation}
-since $\mathbbm{E}(D_i|Z_i = 1)= 1$ by \eqref{eq:potentialTreatments}.
-
-\Eqref{eq:ToT} and \eqref{eq:TuT} are useful for understanding why our design identifies the ToT and TuT, but they are less convenient for estimation and inference.
+since $\mathbbm{E}(D_i|Z_i = 1)= 1$ by \ref{eq:potentialTreatments}.
+
+\ref{eq:ToT} and \ref{eq:TuT} are useful for understanding why our design identifies the ToT and TuT, but they are less convenient for estimation and inference.
 In Appendix \todo{Frank: fill in}{???}, we show that
@@
 It follows that a pair of just-identified, linear instrumental variables regressions can be used to estimate and carry out inference for each of our quantities of interest.
-To identify the ATE and ToT, run IV on \eqref{eq:ToTreg} with instruments $\mathbbm{1}(Z_i = 1)$ and $\mathbbm{1}(Z_i=2)$.
+To identify the ATE and ToT, run IV on \ref{eq:ToTreg} with instruments $\mathbbm{1}(Z_i = 1)$ and $\mathbbm{1}(Z_i=2)$.
 An F-test based on this regression can then be used to test the restriction $\text{ATE} = \text{ToT}$, and the usual IV output can be used to carry out inference for the ToT.
@@
 %\]
-%where $\boldsymbol{\Sigma}$ is a covariance matrix that can be estimated from the residuals of \eqref{eq:ToTreg} and \eqref{eq:TuTreg}. Under iid observations, 
+%where $\boldsymbol{\Sigma}$ is a covariance matrix that can be estimated from the residuals of \ref{eq:ToTreg} and \ref{eq:TuTreg}. Under iid observations, 
 %

### 2022-11-14 donde.tex
remove conflicting packages to resolve eqref issue

--- 2022-11-12 donde.tex
@@
 \end{equation}
-\Eqref{eq:exclusion} says that each participant's potential outcome is the same regardless of whether she \emph{chooses} a particular treatment $D=d$ or is \emph{assigned} the same treatment.
-Viewing $Z_i$ as an instrumental variable (IV) for the treatment $D_i$, this nothing more than the usual IV exclusion restriction.\footnote{\cite{chamberlain2011bayesian} uses an identical assumption to develop a theory of optimal treatment choice for an individual who has access to data from an RCT.} \Eqref{eq:exclusion} is plausible in our empirical setting and has testable implications that we fail to reject: see Appendix \todo{Fill in}{???} for details.
+\eqref{eq:exclusion} says that each participant's potential outcome is the same regardless of whether she \emph{chooses} a particular treatment $D=d$ or is \emph{assigned} the same treatment.
+Viewing $Z_i$ as an instrumental variable (IV) for the treatment $D_i$, this nothing more than the usual IV exclusion restriction.\footnote{\cite{chamberlain2011bayesian} uses an identical assumption to develop a theory of optimal treatment choice for an individual who has access to data from an RCT.} \eqref{eq:exclusion} is plausible in our empirical setting and has testable implications that we fail to reject: see Appendix \todo{Fill in}{???} for details.
 Under \eqref{eq:exclusion}, each participant's observed outcome $Y_i$ is related to her potential outcomes $(Y_{i0}, Y_{i1})$ according to
@@
 
-\Eqref{eq:potentialOutcomes} is the key to understanding the results that follows.
+\eqref{eq:potentialOutcomes} is the key to understanding the results that follows.
 By randomly assigning $Z_i=0$ and $Z_i = 1$, our experiment identifies the marginal distributions of $Y_{i0}$ and $Y_{i1}$ in the population as a whole.
@@
 
-\Eqref{eq:ToT} and \eqref{eq:TuT} are useful for understanding why our design identifies the ToT and TuT, but they are less convenient for estimation and inference.
+\eqref{eq:ToT} and \eqref{eq:TuT} are useful for understanding why our design identifies the ToT and TuT, but they are less convenient for estimation and inference.
 In Appendix \todo{Frank: fill in}{???}, we show that

### 2022-12-20 OA.tex
revision of text by enrique, frank and isaac

@@
 
-\section{ Further results}
+\section{ }
 \vspace{.2in}
+
+\vspace{.1in}
+
+\begin{figure}[H]
+     \caption{Some Pawnshops}
+    \label{PawnshopPicture}
+    \begin{center}
+    \begin{subfigure}{0.42\textwidth}
+    \caption{Appraiser/tellers inside a pawnshop}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/empenio9.png}
+    \end{subfigure}
+        \begin{subfigure}{0.45\textwidth}
+    \caption{Pawnshop}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/empenio11.png}
+    \end{subfigure}
+
+        \vspace{3ex}
+
+    \begin{subfigure}{0.45\textwidth}
+    \caption{Pawnshop}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/empenio2.png}
+    \end{subfigure}
+    \begin{subfigure}{0.42\textwidth}
+    \caption{Lost pawns which are for sale}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/empenio3.png}
+    \end{subfigure}
+    \end{center}
+    \scriptsize
+        This figure  shows pictures of pawnshops in Mexico city. They do not necessarily coincide with Lender P for confidentiality. 
+\end{figure}
+
+\vspace{.1in}
+\begin{figure}[H]
+     \caption{Gold buyers next to pawnshops}
+    \label{GoldBuyers}
+    \begin{center}
+    \begin{subfigure}{.49\textwidth}
+    \caption{Gold buyer next to pawnshop 1}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/empenio7.png}
+    \end{subfigure}
+    \begin{subfigure}{.49\textwidth}
+    \caption{Gold buyer next to pawnshop 1}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/empenio8.png}
+    \end{subfigure}
+       \vspace{3ex}
+
+    \end{center}
+    \scriptsize
+        This figure shows pictures of gold buyers next to pawnshops in Mexico city. They do not necessarily coincide with Lender P for confidentiality. 
+\end{figure}
 
@@
 
-\subsection{Some materials}
-
-\vspace{.1in}
-
-\subsection{Pictures}
-
-\begin{figure}[H]
-     \caption{Some Pawnshops}
-    \label{PawnshopPicture}
-    \begin{center}
-    \begin{subfigure}{0.42\textwidth}
-    \caption{Appraiser/tellers inside a pawnshop}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/empenio9.png}
-    \end{subfigure}
-        \begin{subfigure}{0.45\textwidth}
-    \caption{Pawnshop}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/empenio11.png}
-    \end{subfigure}
-
-        \vspace{3ex}
-
-    \begin{subfigure}{0.45\textwidth}
-    \caption{Pawnshop}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/empenio2.png}
-    \end{subfigure}
-    \begin{subfigure}{0.42\textwidth}
-    \caption{Lost pawns which are for sale}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/empenio3.png}
-    \end{subfigure}
-
-    \end{center}
-    \scriptsize
-        This figure  shows pictures of pawnshops in Mexico city. They do not necessarily coincide with Lender P for confidentiality. 
-\end{figure}
-
-\vspace{.1in}
-\begin{figure}[H]
-     \caption{Gold buyers next to pawnshops}
-    \label{GoldBuyers}
-    \begin{center}
-    \begin{subfigure}{.49\textwidth}
-    \caption{Gold buyer next to pawnshop 1}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/empenio7.png}
-    \end{subfigure}
-    \begin{subfigure}{.49\textwidth}
-    \caption{Gold buyer next to pawnshop 1}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/empenio8.png}
-    \end{subfigure}
-       \vspace{3ex}
-
-    \end{center}
-    \scriptsize
-        This figure shows pictures of gold buyers next to pawnshops in Mexico city. They do not necessarily coincide with Lender P for confidentiality. 
-\end{figure}
-
-%\begin{figure}[H]
-%        \caption{Booklet with product information}
-%    \label{micas}
-%    \begin{center}
-%        \centering
-%        \includegraphics[width=\textwidth]{micas.pdf}
-%    \end{center}
-%     \footnotesize \textit{Notes: } 
-%      \footnotesize{ }
-%\end{figure}
-
-%\begin{figure}[H]
-%     \caption{Booklet with product information translated}
-%    \label{booklet_translate2}
-%    \begin{center}
-%    \begin{subfigure}{.9\textwidth}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/MP_F.pdf}
-%    \end{subfigure}
-    %\begin{subfigure}{0.55\textwidth}
-    %   \centering
-    %  \includegraphics[width=\textwidth]{Figuras/MP_2.pdf}
-    %\end{subfigure}
-%    \end{center}
-%\end{figure}
-
 \subsection{Surveys}
-
-%\begin{table}[H]
-%\caption{Survey's non-response balance}
-%\label{balance_response}
-%\begin{center}
-%\scriptsize{\input{./Tables/balance_response.tex}}
-%\end{center}
-% \scriptsize This table shows whether the means of variables in the administrative dataset are different for those that respond the baseline survey vs those that do not.
-We use this as an assessment of external validity.
-Internal validity is guaranteed because the baseline survey was implemented before treatment assignment and therefore response rates are orthogonal to treatment assignments.
-Panel A studies the baseline survey, while Panel B focuses on the exit survey.
-The columns labeled ``p-values'' report p-values for the test that the means of the respective variable are the same for those that responded did not respond the survey.
-%\textit{Do file: } \texttt{balance\_response.do}
-%\end{table}
 
@@
 }
-
-\begin{comment}
-\begin{table}[H]
-\caption{Reincidence SS}
-\label{tab_reincidence}
-\begin{center}
-\scriptsize{\input{./Tables/tab_reincidence.tex}}
-\end{center}
- \scriptsize
-%\textit{Do file: } \texttt{tab\_reincidence.do}
-\end{table}
-
-\begin{table}[H]
-\caption{Summary statistics (exit survey)}
-\label{SS_exit}
-\begin{center}
-\scriptsize{\input{./Tables/SS_exit.tex}}
-\end{center}
- \scriptsize We carried out an exit survey.
-It had a small response rate and we don't use it in the paper.
-Here it shows that the characteristics of those that responded it are balanced across arms (Panel B).
-Panel A reports outcomes.
-%\textit{Do file: } \texttt{ss.do}
-\end{table}
-\end{comment}
 
@@
 
+\begin{figure}[H]
+        \caption{Financial cost for different discount rates}
+    \label{fc_discount_rates}
+    \begin{center}
+        \centering
+        \includegraphics[width=0.55\textwidth]{Figuras/discount_effect.pdf}
+    \end{center}
+     \scriptsize This Figure estimates the treatment effect on financial cost with different discount rates.  
+     %\textit{Do file: }  \texttt{discounted\_noeffect.do}
+\end{figure}
+
+\begin{landscape}
+
 \begin{table}[H]
-\caption{Effects on several definitions of cost - Soft arms}
-\label{table_robustness_fc_soft}
-\begin{center}
-\scriptsize{\input{./Tables/fc_robustness_soft.tex}}
+\caption{Multiple-loans robustness check}
+\label{multiple_loans}
+\begin{center}
+\scriptsize{\input{./Tables/multiple_loans.tex}}
 \end{center}
@@
 
-%\textit{Do file: } \texttt{fc\_robustness\_soft.do}
+%\textit{Do file: } \texttt{multiple\_loans.do}
 \end{table}
 
-\begin{landscape}
-
-\begin{table}[H]
-\caption{Intermediate outcomes - Soft arms}
-\label{mechanisms_soft}
-\begin{center}
-\scriptsize{\input{./Tables/mechanism_soft.tex}}
-\end{center}
-
-%\textit{Do file: } \texttt{mechanisms\_soft.do}
-\end{table}
-
 \end{landscape}
 
+\begin{figure}[H]
+        \caption{Survival graph}
+    \label{survival_graph}
+    \begin{center}
+   \begin{subfigure}{0.49\textwidth}
+   \caption{Ended contract}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/survival_graph_ended.pdf}
+    \end{subfigure} 
+   \begin{subfigure}{0.49\textwidth}
+   \caption{Recovery}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/survival_graph_unpledge.pdf}
+    \end{subfigure}     
+    \end{center}
+     \scriptsize  This Figure shows the accumulated percentage of recovery in time by treatment arm. 
+     %\textit{Do file: }  \texttt{survival\_graph.do}
+\end{figure}
+
+\begin{figure}[H]
+        \caption{\% of payment over time}
+    \label{porc_payment_over_time}
+    \begin{center}
+   \begin{subfigure}{0.49\textwidth}
+        \caption{Unconditional}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/cumulative_porc_pay_time.pdf}
+    \end{subfigure} 
+   \begin{subfigure}{0.49\textwidth}
+        \caption{Conditional on default}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/cumulative_porc_pay_time_default.pdf}
+    \end{subfigure}     
+    \end{center}
+     \scriptsize  This Figure shows the accumulated percentage of recovery in time by treatment arm. 
+     %\textit{Do file: }  \texttt{cumulative\_porc\_pay\_time.do}
+\end{figure}
+
 \cleardoublepage
-
-% \begin{figure}[H]
-%         \caption{FC restricted to 115 days}
-%     \label{fc_pro_2_115}
-%     \begin{center}
-%         \centering
-%         \includegraphics[width=0.50\textwidth]{Figuras/fc_te_115_pro_2.pdf}
-%     \end{center}
-%      \scriptsize This figure is the same as in Figure \ref{fc_pro2} Panel (a), but with the subsample restricted to the first 115 days.
-%      %\textit{Do file: }  \texttt{fc\_te\_115.do}
-% \end{figure}
-
-% \begin{figure}[H]
-%         \caption{Financial cost effect: charging all fees}
-%     \label{fc_allfee}
-%     \begin{center}
-%         \centering
-%         \includegraphics[width=0.50\textwidth]{Figuras/fc_allfee_quantile_pro_2.pdf}
-%     \end{center}
-%     \scriptsize
-%      This figure is the analogous to Figure \ref{fc_pro2}(b), except that for the fee-forcing contract we pretend that all clients incurred in their late fees, and therefore inflate the financial cost by summing those fees.
-This is intended as a kind of worse case scenario for the financial cost of the fee-forcing contract.
-The circles indicate the quantile treatment effects, while the cross is the (OLS) mean.
-We still find that the financial cost of will be smaller under the fee-forcing contract in spite of artificially inflating it.
-%      %\texttt{fc\_all\_fee.do}
-% \end{figure}
-
-% \begin{figure}[H]
-%         \caption{FC as \% of loan - treatment effect}
-%     \label{fc_perc}
-%     \begin{center}
-%         \centering
-%         \includegraphics[width=0.50\textwidth]{Figuras/fc_perc_te_allarms.pdf}
-%     \end{center}
-%      \scriptsize This figure shows the estimated treatment effect of all arms against the status quo, but normalizing the dependent variable by the value of the loan.
-%      %\textit{Do file: }  \texttt{fc\_perc\_allarms.do}
-% \end{figure}
-
-\begin{figure}[H]
-    \caption{Relationship between treatment effects}
-    \label{induced_to_pay_early}
-    \begin{center}
-    \begin{subfigure}{0.45\textwidth}
-        \caption{\footnotesize{Induced to pay earlier vs Induced Lower FC}}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/binscatter_fc_days_pro_2.pdf}
-    \end{subfigure}
-        \begin{subfigure}{0.45\textwidth}
-        \caption{\footnotesize{Induced to pay earlier vs Induced Recovery}}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/binscatter_def_days_pro_2.pdf}
-    \end{subfigure}
-    \end{center}
-       \scriptsize 
-       This figure plots relationships between \textit{treatment effects}.
-Both Panels (a) an (b) have the same X-axis, which displays the estimated heterogeneous treatment effect on the outcome ``elapsed days of first payment'', that is how many days elapsed from the day the loan was awarded to the first payment the client made.
-The treatments effects were calculated using \cite{atheygrf}.
-In Panel (a) the Y-axis is the \textit{treatment effect} on financial cost.
-In Panel (b) the Y-axis is the \textit{treatment effect} on losing their pawn.
-Panel (a) shows that those induced to pay earlier are also those that have larger savings in financial cost as a result of ``forcing'' the frequent payment commitment contract compared to the status-quo (control).
-Panel (b) shows that those induced to pay earlier are also those that have a larger increase in recovery.
-      %\textit{Do file: }  \texttt{binscatter\_hte.do}
-\end{figure}
-
-% \begin{figure}[H]
-%         \caption{Repeat purchase before 30/60 days}
-%     \label{reincidence_before}
-%     \begin{center}
-%         \centering
-%         \includegraphics[width=0.50\textwidth]{Figuras/re_te_earlydays.pdf}
-%     \end{center}
-%      \scriptsize This figure shows the estimated treatment effect of repeat purchase before 30 \& 60 days.
-%      %\textit{Do file: }  \texttt{re\_te\_earlydays.do}
-% \end{figure}
-
-\vspace{.3in}
-
-\subsection{FOSD: fee forcing vs status quo financial cost distributions}
 
@@
 
+\newpage
+
+\subsection{Testing for heterogeneity}
+Our approach relies on the following simple observation: if $\Delta_i$ is constant across $i$ then we must have 
+\[
+\text{ATE}(X_i) \equiv \mathbbm{E}[\Delta_i |X_i] = \mathbbm{E}[\Delta_i] \equiv \text{ATE}
+\]
+for any covariates $X_i$ that vary across $i$.
+If, on the other hand, $\text{ATE}(X_i)$ can be predicted using some scalar function $\tau(\cdot)$ of $X_i$, then the average treatment effect function is not constant so there must be treatment effect heterogeneity.
+
+We operationalize this idea using a two-step approach proposed by \cite{chernozhukov2018generic}.
+We begin by randomly dividing the participants in the forced arms of the experiment ($Z_i \neq 2$) into two groups: a ``training set'' and a \todo{80/20 split?}{``test set.''} In the first step, we apply random forests to the training set to estimate two proxy predictors: $\psi(\cdot|\text{Training})$ approximates the untreated potential outcome function, $\mathbbm{E}[Y_{i0}|X_i] = \mathbbm{E}[Y_i|Z_i=0,X_i]$, while  $\tau(\cdot|\text{Training})$, approximates the average treatment effect function
+\[
+\text{ATE}(X_i) = \mathbbm{E}[Y_i|Z_i=1,X_i] - \mathbbm{E}[Y_i|Z_i=0, X_i].
+\]
+The proxy predictors need not be unbiased or even consistent estimators of the functions they aim to approximate: the goal of this exercise is merely to find a scalar function of $X_i$ that \emph{accurately predicts} $\text{ATE}(X_i)$.
+
+In the second step we fit a linear regression model to data from the training set using regressors constructed from the proxy functions $\psi(\cdot|\text{Training})$ and $\tau(\cdot|\text{Training})$ constructed in the first step.
+In particular, we estimate
+\begin{equation}
+Y_i = \alpha_0 + \alpha_1 \psi_i + \beta_1 (Z_i - \mathbbm{E}[Z_i]) + \beta_2 (Z_i - \mathbbm{E}[Z_i])(\tau_i - \mathbbm{E}[\tau_i]) + \epsilon_i
+\label{eq:chernreg}
+\end{equation}
+where $\psi_i \equiv \psi(X_i|\text{Training})$ and $\tau_i \equiv \tau(X_i|\text{Training})$.\footnote{This is a slightly simpler regression than the one proposed in equation (3.1) of \cite{chernozhukov2018generic}, which involves propensity score weights.
+Because the random assignment of $Z$ in our experiment does \emph{not} condition on $X$, the propensity score weights in our case are constant over $X$ and hence drop out.} As shown by \cite{chernozhukov2018generic}, the coefficients $\beta_1$ and $\beta_2$ from \eqref{eq:chernreg} identify the \emph{best linear predictor} of the conditional ATE based on $\tau(\cdot|\text{Training})$, namely
+\[
+\beta_1 = \mathbbm{E}[\text{ATE}(X_i)] = \text{ATE}, \quad
+\beta_2 = \frac{\text{Cov}[\text{ATE}(X_i), \tau_i]}{\text{Var}(\tau_i)}.
+\]
+If treatment effects are homogeneous we must have $\beta_2 = 0$.
+Rejecting this hypothesis establishes that $\tau_i$ predicts $\text{ATE}(X_i)$ and hence that $\Delta_i$ varies.
+Since $\tau_i$ and $\psi_i$ do not depend on the test set, inference for the regression in \eqref{eq:chernreg} is straightforward conditional on the Training/Test split.
+
+\todo[inline]{Discuss the results here.}
+
+\todo[inline]{Issac: re-run this exercise with removing the propensity score weights $p(Z)$. Presumably it shouldn't change anything, but it's simpler to explain what we do and probably less noisy
+
+\begin{table}[H]
+\begin{center}
+\scriptsize{\input{./Tables/test_calibration_2.tex}}
+\end{center}
+\end{table}
+
+}
+
+\todo[inline]{Some Questions for Issac: (1) How are we carrying out the sample splitting?
+If we cluster standard errors at the branch-day level, we should take this into account when we split.
+(2) How are you carrying out inference for $\beta_2$?
+Chernozhukov et al discuss two approaches: ``conditional'' and ``variational.'' The former is simpler as it conditions on the training/test split.
+The latter is a bit more involved, since one accounts for uncertainty arising from different splits.
+(3) What are the details of the random forest procedure employed here?
+(Tuning parameters choice, etc.) We should put them into the appendix.}
+
+\newpage
+
+\subsection{Bounding ToT \& TuT} \label{bound_tot_tut_appendix}
+
+\vspace{.2in}
+\normalsize
+\linespread{1.25}
+%Really force it to normal size and linespread
+\normalsize
+\linespread{1.25}
+
+Even without the exclusion restriction, it’s possible to bound $\mathbb{E}[Y_1-Y_0\;|\;T=0]$ and $\mathbb{E}[Y_1-Y_0\;|\;T=1]$ using observed outcomes in the forced arm and observed take-up in the choice arm.
+It should also be possible to create bounds conditional on covariates.
+The basic approach is similar to that of \cite{huber_mellace}.
+\\
+
+From the $Z=0$ arm we identify the distribution $F_0$ of $Y_0$, the potential outcome when forced into the no-commitment contract.
+Now, from the choice arm we know that around 90\% of people are $T=0$ types.
+Because choice was randomly assigned, the 90\% figure holds for all arms in the experiment.
+This tells us that $F_0$ is a 90\%-10\% mixture of $Y_0\;|\;T=0$ and $Y_0\;|\;T=1$.
+Cut out the bottom 10\% of $F_0$ and calculate the mean of this new distribution.
+Then cut out the top 10\% of $F_0$ and compute the mean of this new distribution.
+The result is an upper and lower bound for $\mathbb{E}[Y_0\;|\;T=0]$ that does not rely on the exclusion restriction.
+We can apply similar reasoning to bound $\mathbb{E}[Y_1\;|\;T=0]$ Combining the previous bounds gives a bound for the TuT that does not rely on the exclusion restriction, and analogous we can bound the ToT.
+\\
+
+The \cite{huber_mellace} bounds for the ToT \& TuT APR are respectively:
+\[\text{ToT} : [-481.8, 483.7]\quad\quad\quad\text{TuT} : [-17.9, 90.6]\]
+
+Note that since both TuT and ToT estimates from the LATE approach lies inside these bounds, we do not falsify the exclusion restriction.
+
+\newpage
+
+\subsection{LATE: ToT \& TuT}
+\vspace{.2in}
+\normalsize
+\linespread{1.25}
+%Really force it to normal size and linespread
+\normalsize
+\linespread{1.25}
+
+ Recall that $Z_i$ is the observed, randomly assigned experimental allocation, where $Z_i=0$ denotes the control arm, $Z_i=1$ denotes the forced-fee arm, and $Z_i=2$ is the choice arm.
+Let $C_i$ be the unobserved choice type.
+$C_i=0$ when individual $i$ does not choose commitment  given the choice and $C_i=1$ when chooses commitment given the choice.
+Finally, $D_i = Z_i\times \mathds{1}(Z_i\neq 2) + C_i\times \mathds{1}(Z_i=2)$ is the observed treatment indicator, and $Y(d,z)$ is the potential outcome function for $d=0,1$, and $z=0,1,2$.
+
+ To identify assortative selection we first need to estimate the following quantities: $\mathbb{E}(Y_1-Y_0\;|\;C=1)$ the Treatment on the Treated (ToT), and $\mathbb{E}(Y_1-Y_0\;|\;C=0)$ the Treatment on the Untreated (TuT).
+
+ To point identify the above quantities, we make the following assumptions.
+
+ \begin{assumption}[Exclusion Restriction]
+$Z$ only affects $Y$ through its effect on $D$ : $C(d,z) = C(d)$
+ \end{assumption}
+
+  \begin{assumption}[Independence Assumption]
+$Z \perp (Y_0, Y_1, C)$
+ \end{assumption}
+
+The following intermediate Lemmas will help us derive that both ToT and TuT are point identified.
+
+\begin{lem}
+$\Pr(C=1) = \E[D\;|\;Z=2]$
+\end{lem}
+\begin{proof}
+Since $C\perp Z$, 
+$$\E[D\;|\;Z=2] = \E[Z\times \mathds{1}(Z\neq 2)+ C\times\mathds{1}(Z=2)\;|Z=2] = \E[C\;|\;Z=2] = \E[C] = \Pr(C=1)$$
+\end{proof}
+
+\begin{lem}
+$\E[Y_0] = \E[Y\;|\;Z=0]$
+\end{lem}
+\begin{proof}
+Since $Z\perp Y_0$, 
+\begin{align*}
+\E[Y\;|\;Z=0] =& \E[\mathds{1}(Z=0)Y_0+\mathds{1}(Z=1)Y_1+\mathds{1}(Z=2)\{(1-C)Y_0+CY_1\})\;|\;Z=0]\\   
+=&\E[Y_0\;|\;Z=0] = \E[Y_0]
+\end{align*}
+\end{proof}
+
+\begin{lem}
+$\E[Y_1] = \E[Y\;|\;Z=1]$
+\end{lem}
+\begin{proof}
+Since $Z\perp Y_1$, 
+\begin{align*}
+\E[Y\;|\;Z=1] =\E[Y_1\;|\;Z=1] = \E[Y_1]
+\end{align*}
+\end{proof}
+
+\begin{lem}
+$\E[Y_0\;|\;C=0] = \E[Y\;|\; D=0,Z=2]$
+\end{lem}
+\begin{proof}
+If $Z=2$, then $D=0$ if and only if $C=0$. Hence,
+\[\E[Y\;|\;D=0, Z=2] = \E[Y_0\;|\;D=0, Z=2] = E[Y_0\;|\;C=0, Z=2]=\E[Y_0\;|\;C=0]\]
+since $Y_0\perp C\;|\;Z$
+\end{proof}
+
+\begin{lem}
+$\E[Y_1\;|\;C=1] = \E[Y\;|\; D=1,Z=2]$
+\end{lem}
+\begin{proof}
+If $Z=2$, then $D=1$ if and only if $C=1$. Hence,
+\[\E[Y\;|\;D=1, Z=2] = \E[Y_1\;|\;D=1, Z=2] = E[Y_1\;|\;C=1, Z=2]=\E[Y_1\;|\;C=1]\]
+since $Y_1\perp C\;|\;Z$
+\end{proof}
+
+\begin{theorem} $\E[Y_1-Y_0\;|\; C=1]$ is point identified
+\end{theorem}
+
+\begin{proof}
+Since $\E[Y_1\;|\; C=1] = \E[Y\;|\; D=1, Z=2]$ by Lemma 5, it suffices to show that $\E[Y_1\;|\;C=0]$ is point identified. By iterated expectations:
+\[E[Y_0] = \E_C\E[Y_0\;|\;C] = (1-p)\E[Y_0\;|\;C=0]+p\E[Y_0\;|\;C=1]\]
+where $p:=\E[C]=\Pr(C=1)$, and re-arranging,
+\[\E[Y_0\;|\;C=1] = \frac{1}{p}\left(E[Y_0] -(1-p)\E[Y_0\;|\;C=0]\right)\]
+Finally, substituting the result of Lemmas 1, 2, and 4, we obtain
+\[\E[Y_0\;|\;C=1] =\frac{1}{\E[D\;|\;Z=2]}\left\{\E[Y\;|\;Z=0]-(1-\E[D\;|\;Z=2])\E[Y\;|\;D=0, Z=2]\right\}\]
+and the RHS is a function of observed data only.
+\end{proof}
+
+\begin{theorem} $\E[Y_1-Y_0\;|\; C=0]$ is point identified
+\end{theorem}
+
+\begin{proof}
+Since $\E[Y_0\;|\; C=0] = \E[Y\;|\; D=0, Z=2]$ by Lemma 4, it suffices to show that $\E[Y_0\;|\;C=1]$ is point identified. By iterated expectations:
+\[E[Y_1] = \E_C\E[Y_1\;|\;C] = (1-p)\E[Y_1\;|\;C=0]+p\E[Y_1\;|\;C=1]\]
+where $p:=\E[C]=\Pr(C=1)$, and re-arranging,
+\[\E[Y_1\;|\;C=0] = \frac{1}{1-p}\left(E[Y_1] -p\E[Y_1\;|\;C=1]\right)\]
+Finally, substituting the result of Lemmas 1, 3, and 5, we obtain
+\[\E[Y_1\;|\;C=0] =\frac{1}{1-\E[D\;|\;Z=2]}\left\{\E[Y\;|\;Z=1]-\E[D\;|\;Z=2]\E[Y\;|\;D=1, Z=2]\right\}\]
+and the RHS is a function of observed data only.
+\end{proof}
+
+\begin{figure}[H]
+    \caption{Bootstrap inference for the difference between ToT-TuT}
+    \label{bootstrap_tot_tut}
+    \begin{center}
+    \begin{subfigure}{0.31\textwidth}
+        \caption{Simple}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/tot_tut_btsp1.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.31\textwidth}
+        \caption{Admin controls}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/tot_tut_btsp2.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.31\textwidth}
+        \caption{Admin + Survey controls}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/tot_tut_btsp3.pdf}
+    \end{subfigure}
+
+    \end{center}
+     \scriptsize  Given that all of the arms are effectively randomly sampled form the same pool, we can also estimate the ToT and TuT with the pooled regression: $Y_i = \beta_0\mathds{1}(Z_i=0)+\beta_1\mathds{1}(Z_i=1)+\beta_2\mathds{1}(Z_i=2)+ \epsilon_i$, and then this test statistic just becomes the F-test on $\frac{\widehat{\beta_2}-\widehat{\beta_0}}{p}$ for the ToT, $\frac{\widehat{\beta_1}-\widehat{\beta_2}}{1-p}$ for the TuT, and an F-test on the difference between these two quantities to test whether the gains are different between compliers and non-compliers.
+Recognizing the stochastic nature of the compliance rate, we also bootstrap this quantity before running the previous regression.
+The red line shows the point estimate for the difference between ToT-TuT, and the gray bar in the x-axis shows a 95\% confidence interval for this difference.
+Panel (a) shows the difference between the ToT and TuT without any controls, while panel (b) and (c) adds admin controls and admin + survey controls respectively.
+          %\footnotesize{ \textit{Do file: }  \texttt{tot\_tut.do}}
+\end{figure}
+
+\begin{figure}[H]
+     \caption{ToT-TuT CDF}
+     \label{tot_tut_ecdf}
+    \begin{center}
+    \begin{subfigure}{0.6\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/cdf_tot_tut.pdf}
+    \end{subfigure}
+    \end{center}
+    \scriptsize
+       Equipped with estimates for the ToT and TuT for each individual $i$ from an Instrumental Random Forest we compute the ECDF for this quantities.
+The solid line is the ECDF for the ToT, the dashed line is the ECDF for the TuT, and the dotted line plots the difference between the ToT and the TuT - the blue dashed line in the x-axis shows the points where this difference is significant.
+The bold black interval at the bottom of the graph is the mean for the ToT distribution (0.07), while the gray interval shows the mean for the TuT distribution (0.10).
+
+          %\footnotesize{ \textit{Do file: }  \texttt{tot\_tut\_insforest.do}}
+\end{figure}
+
+\begin{figure}[H]
+     \caption{Exclusion restriction}
+     \label{exclusion_restriction}
+    \begin{center}
+    \begin{subfigure}{0.6\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/exclusion_restriction.pdf}
+    \end{subfigure}
+    \end{center}
+    \scriptsize This figure serves as a test for the exclusion restriction in the point identification for the ToT and the TuT.
+It shows the effect on the effective cost/loan ratio for the forced-fee arm and the choice arm, together with the decomposition of the choosers and non-choosers.
+Note that a) being forced into the treatment (Forced fee) has the same effect as choosing it (Choosers), and b) not choosing the treatment (Non chooser) has no effect with respect to the control.
+
+          %\footnotesize{ \textit{Do file: }  \texttt{exclusion\_restriction.do}}
+\end{figure}
+
+%---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
+
+\newpage 
 \newpage
@@
 
-% \begin{figure}[H]
-%     \caption{Heterogeneous Treatment Effect: Fee-forcing contract}
-%     \label{HTE_fee_forcing}
-%     \begin{center}
-%     %\begin{subfigure}{0.4\textwidth}
-%     %    \caption{Financial cost}
-%     %    \centering
-%     %    \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_2.pdf}
-%     %\end{subfigure}
-%     \begin{subfigure}{0.7\textwidth}
-%         \caption{Determinants of effects}
+\begin{figure}[H]
+    \caption{Choice of contracts and treatment effects}
+    \label{choose_wrong}
+    \begin{center}
+        \begin{subfigure}{0.45\textwidth}
+        \caption{Mistakes in choice arm}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/line_cw_apr_te_cf.pdf}
+
+    \end{subfigure}
+        \begin{subfigure}{0.45\textwidth}
+        \caption{Financial value of mistake}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/money_cw_apr_te_cf.pdf}
+
+    \bigskip
+
+    \end{subfigure}
+        \begin{subfigure}{0.45\textwidth}
+        \caption{\% better when forced to forced commitment}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/line_better_forceall_apr_te_cf.pdf}
+
+    \end{subfigure}
+    %     \begin{subfigure}{0.45\textwidth}
+    %     \caption{\footnotesize{Effect of CATE benefit vs predicted take-up}}
     %     \centering
-%         \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_fc_admin_disc_pro_2.pdf}
+    %     \includegraphics[width=\textwidth]{Figuras/benefit_choice.pdf}% takeuppr_def.pdf 
     % \end{subfigure}
 
-%     %\begin{subfigure}{0.4\textwidth}
-%     %    \caption{Losing Pawn}
-%     %    \centering
-%     %    \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_2.pdf}
-%     %\end{subfigure}
-%     %\begin{subfigure}{0.4\textwidth}
-%     %    \caption*{}
-%     %    \centering
-%     %    \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_def_c_pro_2.pdf}
-%     %\end{subfigure}
-%     \end{center}
-%      \scriptsize  This figure estimates bivariate regressions of the estimated client-level heterogeneous treatment effects against the respective covariate from the baseline survey  $\widehat{hte_i} = \alpha + \beta \: X_i + \epsilon_i$.
-The regressors $X_i$ include (e.g if the family asks for money, if they have savings, if they are overconfident using the definition the text, etc.
-See this Appendix for a transcription of the survey).
-%       %\footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}}
-% \end{figure}
-
-% \begin{figure}[H]
-%     \caption{Heterogeneous Treatment Effect: Promise-forcing contract}
-%     \label{heterogeneous_te_3}
-%     \begin{center}
-%     \begin{subfigure}{0.4\textwidth}
-%         \caption{Financial cost}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_3.pdf}
-%     \end{subfigure}
-%     \begin{subfigure}{0.4\textwidth}
-%         \caption*{}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_fc_admin_disc_pro_3.pdf}
-%     \end{subfigure}
-
-%     \begin{subfigure}{0.4\textwidth}
-%         \caption{Losing Pawn}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_3.pdf}
-%     \end{subfigure}
-%     \begin{subfigure}{0.4\textwidth}
-%         \caption*{}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_def_c_pro_3.pdf}
-%     \end{subfigure}
-%     \end{center}
-%      \scriptsize
-%       %\footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}}
-% \end{figure}
-
-% \begin{figure}[H]
-%     \caption{Heterogeneous Treatment Effect - Choice/Fee}
-%     \label{heterogeneous_te_4}
-%     \begin{center}
-%     \begin{subfigure}{0.4\textwidth}
-%         \caption{Financial cost}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_4.pdf}
-%     \end{subfigure}
-%     \begin{subfigure}{0.4\textwidth}
-%         \caption*{}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_fc_admin_disc_pro_4.pdf}
-%     \end{subfigure}
-
-%     \begin{subfigure}{0.4\textwidth}
-%         \caption{Losing Pawn}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_4.pdf}
-%     \end{subfigure}
-%     \begin{subfigure}{0.4\textwidth}
-%         \caption*{}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_def_c_pro_4.pdf}
-%     \end{subfigure}
-%     \end{center}
-%      \footnotesize \textit{Notes: } The distribution plots the FC treatment effect for the interval $[\mu-2\sigma,\mu+2\sigma]$ to ignore the outliers.
-%       \footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}}
-% \end{figure}
-
-% \begin{figure}[H]
-%     \caption{Heterogeneous Treatment Effect - Choice/Promise}
-%     \label{heterogeneous_te_5}
-%     \begin{center}
-%     \begin{subfigure}{0.4\textwidth}
-%         \caption{Financial cost}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_5.pdf}
-%     \end{subfigure}
-%     \begin{subfigure}{0.4\textwidth}
-%         \caption*{}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_fc_admin_disc_pro_5.pdf}
-%     \end{subfigure}
-%     \begin{subfigure}{0.4\textwidth}
-%         \caption{Losing Pawn}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_5.pdf}
-%     \end{subfigure}
-%     \begin{subfigure}{0.4\textwidth}
-%         \caption*{}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_def_c_pro_5.pdf}
-%     \end{subfigure}
-%     \end{center}
-%      \footnotesize \textit{Notes: } 
-%       \footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}}
-% \end{figure}
-
-%\begin{figure}[H]
-%    \caption{Heterogeneous Treatment Effect (FC survey) - All arms}
-%    \label{heterogeneous_te_fcsurvey_all}
-%    \begin{center}
-%    \begin{subfigure}{0.4\textwidth}
-%        \caption{Forcing/Fee}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_survey_disc_pro_2.pdf}
-%    \end{subfigure}
-%    \begin{subfigure}{0.4\textwidth}
-%        \caption{Forcing/Promise}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_survey_disc_pro_3.pdf}
-%    \end{subfigure}
-
-%    \begin{subfigure}{0.4\textwidth}
-%        \caption{Choice/Fee}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_survey_disc_pro_4.pdf}
-%    \end{subfigure}
-%    \begin{subfigure}{0.4\textwidth}
-%        \caption{Choice/Promise}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_survey_disc_pro_5.pdf}
-%    \end{subfigure}
-%    \end{center}
-%     \footnotesize \textit{Notes: } 
-%      \footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}}
-%\end{figure}
+    \end{center}
+        \scriptsize
+        In Panel (a) we estimate what the treatment effect of the commitment contract \textit{would have been} for all subjects in the choice arm if they had been forced into the fee-commitment contract.
+To do this we proceed in two steps.
+First, we estimate treatment effects in the forcing arm by comparing the Forced Commitment arm against the status quo arm.
+We let these effects be heterogeneous as a function of our $x$'s using \cite{atheygrf}'s methodology of causal forests.
+Second, we extrapolate these treatment effects based on the choice arm using the same $x$'s.
+Once we have personalized counterfactual treatment effects in the choice arm we calculate what fraction of subjects in the choice arm incurred in financial costs that are  $> z$\% than if they had chosen the opposite contract of what they actually chose, were $z$\% is defined as a fraction of the loan.
+$z$\% is a level of tolerance we can vary and we plot it in the X-axis.
+The left Y-axis measures the fraction of subjects that would have been better by a margin of $z$\% if they changed their choice, and the right Y-axis measures the amount of money ``left on the table''.
+We use bootstrap to tighten the confidence intervals (CIs).
+\cite{atheygrf}'s heterogeneous treatment effect using GRF is asymptotically normal.
+We compute the HTE ($\mu$) together with standard errors ($\sigma$) .
+For every pledge, we draw a random effect from a normal distribution with parameters ($\mu$,$\sigma^2$), and compute via bootstrap the percentage that choose wrong, along normal-approximation CIs (results are robust if we use instead percentile CIs or bias-corrected CIs) .
+This allows us to estimate a distribution for the upper and lower bound CIs, which we then use to obtain a 95\% CI.
+Panel (b) is analogous to Panel (a) except that it does the exercise separately for clients we classified as overconfident ($OC_i:=\mathbbm{1}(P^s_i-\widehat{P_i(X_i)}>0))$ and those we classified as not overconfident.
+Panel (c) simulates what percentage would be better by at least $z$ if we forced everybody of those in the Commitment Choice arm into the fee-commitment contract.
+        % Panel (d) asks whether it is the case that people with larger causal benefits from the Forced Commitment contract would be more likely to select that contract.
+To do this we proceed in two steps as well.
+First we estimate a flexible model of take-up of the fee commitment contract \textit{in the choice arm} using random forests, and from this model obtain a probability $P(x_i)$ of choosing the Forced Commitment contract for a client with characteristics $x_i$.
+We extrapolate this model to clients in the Forced Commitment arm to estimate what would they have chosen if we had given them choice.
+        % Figure (d) plots $\widehat{P(x_i)}$ in the X-axis using a binscatter that splits the X-axis in 100 percentile bins.
+The Y-axis plots the heterogeneous treatment effects of the fee forcing contract on the probability of losing the pawns (more negative means then more likely to recover it), averaged for the respective x-axis bin.
+Positive assortative selection would mean a negative relationship: those who benefit more by treatment and lose the pawn less are \emph{less} likely to choose it.
+Using all bins we estimate a slope of zero in the relationship.
+Using the 80 right most points, we estimate a \textit{positive} relationship.
+        %\textit{Do file: }  \texttt{choose\_wrong\_quant\_wrong.do, choose\_wrong\_quant\_wrong\_decomposition.do}
+\end{figure}
 
@@
 
-\newpage
-
-\subsection{Bounding ToT \& TuT} \label{bound_tot_tut_appendix}
-
-\vspace{.2in}
-\normalsize
-\linespread{1.25}
-%Really force it to normal size and linespread
-\normalsize
-\linespread{1.25}
-
-Even without the exclusion restriction, it’s possible to bound $\mathbb{E}[Y_1-Y_0\;|\;T=0]$ and $\mathbb{E}[Y_1-Y_0\;|\;T=1]$ using observed outcomes in the forced arm and observed take-up in the choice arm.
-It should also be possible to create bounds conditional on covariates.
-The basic approach is similar to that of \cite{huber_mellace}.
-\\
-
-From the $Z=0$ arm we identify the distribution $F_0$ of $Y_0$, the potential outcome when forced into the no-commitment contract.
-Now, from the choice arm we know that around 90\% of people are $T=0$ types.
-Because choice was randomly assigned, the 90\% figure holds for all arms in the experiment.
-This tells us that $F_0$ is a 90\%-10\% mixture of $Y_0\;|\;T=0$ and $Y_0\;|\;T=1$.
-Cut out the bottom 10\% of $F_0$ and calculate the mean of this new distribution.
-Then cut out the top 10\% of $F_0$ and compute the mean of this new distribution.
-The result is an upper and lower bound for $\mathbb{E}[Y_0\;|\;T=0]$ that does not rely on the exclusion restriction.
-We can apply similar reasoning to bound $\mathbb{E}[Y_1\;|\;T=0]$ Combining the previous bounds gives a bound for the TuT that does not rely on the exclusion restriction, and analogous we can bound the ToT.
-\\
-
-The \cite{huber_mellace} bounds for the ToT \& TuT APR are respectively:
-\[\text{ToT} : [-481.8, 483.7]\quad\quad\quad\text{TuT} : [-17.9, 90.6]\]
-
-Note that since both TuT and ToT estimates from the LATE approach lies inside these bounds, we do not falsify the exclusion restriction.
-
-\newpage
-
 \subsection{Selection on gains}
@@
 
-\subsubsection{Finite mixture model }\label{fmm_section}
-
-\vspace{.2in}
-\normalsize
-\linespread{1.25}
-%Really force it to normal size and linespread
-\normalsize
-\linespread{1.25}
-
-We assume the following structural model : Each individual $i$ is of type  $k\in\{1, 2\}$ with probability $\alpha_{i,k}$. We assume it follows a logit distribution:
-\begin{align*}
-\label{dist_alpha}
-    \alpha_{i,k} = \Pr(\text{Type}_i = k \;|\; \mathbf{W}_{i}) = \frac{e^{\gamma_{k}\mathbf{W}_i}}{\sum_{j=1}^{K} e^{\gamma_{j}\mathbf{W}_i}}
-\end{align*}
-
-where $\mathbf{W}_i$ are observable characteristics.
-This characteristics include choice for commitment, present bias, subjective probability of recovery, etc, which might be indicators of naivete vs sophistication.
-
-Now, given their type, each individual makes a choice to default or not $c_{i,k} \in \{1,2\}$, based on other set of observable characteristics $\mathbf{X}_i$ (subjective \& objective value of the loan).
-We will assume there is a continuous latent variable $Y_{i,k,c}$ distributed as
-\[Y_{i,k,c} = \beta_{c,k}\mathbf{X}_{i} +\epsilon_{c,k}\]
-with\footnote{We can impose other errors, and even impose a covariance structure, for instance if $(\epsilon_{c,k})_{c}\sim\mathcal{N}(0,\Sigma_k)$, we arrive to the Multinomial Probit.} $\epsilon_{c;k}\sim\operatorname{EV}(0,1)$.
-This latent variable can be thought of as the utility associated with individual $i$, being type $k$, making choice $c$.
-
-Thus, the density for each individual $i$ being type $k$ is
-\[f(c_i,\mathbf{X}_i; \bm\beta_{k}) = \prod_{c=1}^4\left(\frac{e^{\beta_{c,k} \mathbf{X}_i}}{\sum_{j=1}^{4} e^{\beta_{j,k}  \mathbf{X}_i}}\right)^{[c_i=4]}\]
-
-Finally, the generative model is then a mixture model with density given by,
-\begin{align*}
-    f(c_i ,\mathbf{W}_i, \mathbf{X}_i; \bm{\gamma},\bm{\beta}) &= \sum_{k=1}^K \alpha_k f(c_i,\mathbf{X}_i; \bm\beta_{k}) \\
-    &= \sum_{k=1}^K \alpha_k \prod_{c=1}^4\left(\frac{e^{\beta_{c,k} \mathbf{X}_i}}{\sum_{j=1}^{4} e^{\beta_{j,k}  \mathbf{X}_i}}\right)^{[c_i=c]} 
-\end{align*}
-
-where $\alpha\sim \operatorname{Categorical}$, and $\gamma_{K} = \beta_{4,k}=0$ for identification purposes.
-
-Then the (incomplete) log-likelihood function is
-\begin{align*}
-    \ell(\bm{\gamma}, \bm{\beta}; c, \mathbf{W},  \mathbf{X}) = \sum_{i=1}^n \log\sum_{k=1}^K \alpha_k \prod_{c=1}^4\left(\frac{e^{\beta_{c,k} \mathbf{X}_i}}{\sum_{j=1}^{4} e^{\beta_{j,k}  \mathbf{X}_i}}\right)^{[c_i=c]}
-\end{align*}
-
-, thus we estimate parameters $(\bm{\gamma}, \bm{\beta})$ with an EM algorithm using choice (default), and observable characteristics: $(c_i,\mathbf{W}_i,\mathbf{X}_i)$.
-
-\begin{table}[H]
-\caption{FMM}
-\label{fmm_table}
-\begin{center}
-\scriptsize{\input{./Tables/fmm_types.tex}}
-\end{center}
- \scriptsize
-
-%\textit{Do file: } \texttt{fmm.do}
-\end{table}
-
-\begin{figure}[H]
-    \caption{Treatment effect of Type 1 individuals}
-    \label{fmm_hte}
-    \begin{center}
-    \begin{subfigure}{0.475\textwidth}       
-            \caption{Probability of Type 1 vs HTE}
-            \centering
-        \includegraphics[width=\textwidth]{Figuras/binscatter_tau_classpost.pdf}
-    \end{subfigure}
-   \begin{subfigure}{0.475\textwidth}
-        \caption{Type 1 vs HTE}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/benefit_type1p.pdf}
-    \end{subfigure}
-    \end{center}
-     \scriptsize 
-     After estimating the FMM, we compute the probability for each individual of belonging to each class, the x-axis represents the probability of being Type $1$, while the y-axis shows the HTE.
-A positive relation indicates that Type $1$ individuals are more benefited from commitment.
-      %\footnotesize{ \textit{Do file: }  \texttt{fmm.do}} 
-\end{figure}
-
-\subsubsection{LATE: ToT \& TuT}
-\vspace{.2in}
-\normalsize
-\linespread{1.25}
-%Really force it to normal size and linespread
-\normalsize
-\linespread{1.25}
-
- Recall that $Z_i$ is the observed, randomly assigned experimental allocation, where $Z_i=0$ denotes the control arm, $Z_i=1$ denotes the forced-fee arm, and $Z_i=2$ is the choice arm.
-Let $C_i$ be the unobserved choice type.
-$C_i=0$ when individual $i$ does not choose commitment  given the choice and $C_i=1$ when chooses commitment given the choice.
-Finally, $D_i = Z_i\times \mathds{1}(Z_i\neq 2) + C_i\times \mathds{1}(Z_i=2)$ is the observed treatment indicator, and $Y(d,z)$ is the potential outcome function for $d=0,1$, and $z=0,1,2$.
-
- To identify assortative selection we first need to estimate the following quantities: $\mathbb{E}(Y_1-Y_0\;|\;C=1)$ the Treatment on the Treated (ToT), and $\mathbb{E}(Y_1-Y_0\;|\;C=0)$ the Treatment on the Untreated (TuT).
-
- To point identify the above quantities, we make the following assumptions.
-
- \begin{assumption}[Exclusion Restriction]
-$Z$ only affects $Y$ through its effect on $D$ : $C(d,z) = C(d)$
- \end{assumption}
-
-  \begin{assumption}[Independence Assumption]
-$Z \perp (Y_0, Y_1, C)$
- \end{assumption}
-
-The following intermediate Lemmas will help us derive that both ToT and TuT are point identified.
-
-\begin{lem}
-$\Pr(C=1) = \E[D\;|\;Z=2]$
-\end{lem}
-\begin{proof}
-Since $C\perp Z$, 
-$$\E[D\;|\;Z=2] = \E[Z\times \mathds{1}(Z\neq 2)+ C\times\mathds{1}(Z=2)\;|Z=2] = \E[C\;|\;Z=2] = \E[C] = \Pr(C=1)$$
-\end{proof}
-
-\begin{lem}
-$\E[Y_0] = \E[Y\;|\;Z=0]$
-\end{lem}
-\begin{proof}
-Since $Z\perp Y_0$, 
-\begin{align*}
-\E[Y\;|\;Z=0] =& \E[\mathds{1}(Z=0)Y_0+\mathds{1}(Z=1)Y_1+\mathds{1}(Z=2)\{(1-C)Y_0+CY_1\})\;|\;Z=0]\\   
-=&\E[Y_0\;|\;Z=0] = \E[Y_0]
-\end{align*}
-\end{proof}
-
-\begin{lem}
-$\E[Y_1] = \E[Y\;|\;Z=1]$
-\end{lem}
-\begin{proof}
-Since $Z\perp Y_1$, 
-\begin{align*}
-\E[Y\;|\;Z=1] =\E[Y_1\;|\;Z=1] = \E[Y_1]
-\end{align*}
-\end{proof}
-
-\begin{lem}
-$\E[Y_0\;|\;C=0] = \E[Y\;|\; D=0,Z=2]$
-\end{lem}
-\begin{proof}
-If $Z=2$, then $D=0$ if and only if $C=0$. Hence,
-\[\E[Y\;|\;D=0, Z=2] = \E[Y_0\;|\;D=0, Z=2] = E[Y_0\;|\;C=0, Z=2]=\E[Y_0\;|\;C=0]\]
-since $Y_0\perp C\;|\;Z$
-\end{proof}
-
-\begin{lem}
-$\E[Y_1\;|\;C=1] = \E[Y\;|\; D=1,Z=2]$
-\end{lem}
-\begin{proof}
-If $Z=2$, then $D=1$ if and only if $C=1$. Hence,
-\[\E[Y\;|\;D=1, Z=2] = \E[Y_1\;|\;D=1, Z=2] = E[Y_1\;|\;C=1, Z=2]=\E[Y_1\;|\;C=1]\]
-since $Y_1\perp C\;|\;Z$
-\end{proof}
-
-\begin{theorem} $\E[Y_1-Y_0\;|\; C=1]$ is point identified
-\end{theorem}
-
-\begin{proof}
-Since $\E[Y_1\;|\; C=1] = \E[Y\;|\; D=1, Z=2]$ by Lemma 5, it suffices to show that $\E[Y_1\;|\;C=0]$ is point identified. By iterated expectations:
-\[E[Y_0] = \E_C\E[Y_0\;|\;C] = (1-p)\E[Y_0\;|\;C=0]+p\E[Y_0\;|\;C=1]\]
-where $p:=\E[C]=\Pr(C=1)$, and re-arranging,
-\[\E[Y_0\;|\;C=1] = \frac{1}{p}\left(E[Y_0] -(1-p)\E[Y_0\;|\;C=0]\right)\]
-Finally, substituting the result of Lemmas 1, 2, and 4, we obtain
-\[\E[Y_0\;|\;C=1] =\frac{1}{\E[D\;|\;Z=2]}\left\{\E[Y\;|\;Z=0]-(1-\E[D\;|\;Z=2])\E[Y\;|\;D=0, Z=2]\right\}\]
-and the RHS is a function of observed data only.
-\end{proof}
-
-\begin{theorem} $\E[Y_1-Y_0\;|\; C=0]$ is point identified
-\end{theorem}
-
-\begin{proof}
-Since $\E[Y_0\;|\; C=0] = \E[Y\;|\; D=0, Z=2]$ by Lemma 4, it suffices to show that $\E[Y_0\;|\;C=1]$ is point identified. By iterated expectations:
-\[E[Y_1] = \E_C\E[Y_1\;|\;C] = (1-p)\E[Y_1\;|\;C=0]+p\E[Y_1\;|\;C=1]\]
-where $p:=\E[C]=\Pr(C=1)$, and re-arranging,
-\[\E[Y_1\;|\;C=0] = \frac{1}{1-p}\left(E[Y_1] -p\E[Y_1\;|\;C=1]\right)\]
-Finally, substituting the result of Lemmas 1, 3, and 5, we obtain
-\[\E[Y_1\;|\;C=0] =\frac{1}{1-\E[D\;|\;Z=2]}\left\{\E[Y\;|\;Z=1]-\E[D\;|\;Z=2]\E[Y\;|\;D=1, Z=2]\right\}\]
-and the RHS is a function of observed data only.
-\end{proof}
-
-\begin{figure}[H]
-    \caption{Bootstrap inference for the difference between ToT-TuT}
-    \label{bootstrap_tot_tut}
-    \begin{center}
-    \begin{subfigure}{0.31\textwidth}
-        \caption{Simple}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/tot_tut_btsp1.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.31\textwidth}
-        \caption{Admin controls}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/tot_tut_btsp2.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.31\textwidth}
-        \caption{Admin + Survey controls}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/tot_tut_btsp3.pdf}
-    \end{subfigure}
-
-    \end{center}
-     \scriptsize  Given that all of the arms are effectively randomly sampled form the same pool, we can also estimate the ToT and TuT with the pooled regression: $Y_i = \beta_0\mathds{1}(Z_i=0)+\beta_1\mathds{1}(Z_i=1)+\beta_2\mathds{1}(Z_i=2)+ \epsilon_i$, and then this test statistic just becomes the F-test on $\frac{\widehat{\beta_2}-\widehat{\beta_0}}{p}$ for the ToT, $\frac{\widehat{\beta_1}-\widehat{\beta_2}}{1-p}$ for the TuT, and an F-test on the difference between these two quantities to test whether the gains are different between compliers and non-compliers.
-Recognizing the stochastic nature of the compliance rate, we also bootstrap this quantity before running the previous regression.
-The red line shows the point estimate for the difference between ToT-TuT, and the gray bar in the x-axis shows a 95\% confidence interval for this difference.
-Panel (a) shows the difference between the ToT and TuT without any controls, while panel (b) and (c) adds admin controls and admin + survey controls respectively.
-          %\footnotesize{ \textit{Do file: }  \texttt{tot\_tut.do}}
-\end{figure}
-
-\begin{figure}[H]
-     \caption{ToT-TuT CDF}
-     \label{tot_tut_ecdf}
-    \begin{center}
-    \begin{subfigure}{0.6\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/cdf_tot_tut.pdf}
-    \end{subfigure}
-    \end{center}
-    \scriptsize
-       Equipped with estimates for the ToT and TuT for each individual $i$ from an Instrumental Random Forest we compute the ECDF for this quantities.
-The solid line is the ECDF for the ToT, the dashed line is the ECDF for the TuT, and the dotted line plots the difference between the ToT and the TuT - the blue dashed line in the x-axis shows the points where this difference is significant.
-The bold black interval at the bottom of the graph is the mean for the ToT distribution (0.07), while the gray interval shows the mean for the TuT distribution (0.10).
-
-          %\footnotesize{ \textit{Do file: }  \texttt{tot\_tut\_insforest.do}}
-\end{figure}
-
-\begin{figure}[H]
-     \caption{Exclusion restriction}
-     \label{exclusion_restriction}
-    \begin{center}
-    \begin{subfigure}{0.6\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/exclusion_restriction.pdf}
-    \end{subfigure}
-    \end{center}
-    \scriptsize This figure serves as a test for the exclusion restriction in the point identification for the ToT and the TuT.
-It shows the effect on the effective cost/loan ratio for the forced-fee arm and the choice arm, together with the decomposition of the choosers and non-choosers.
-Note that a) being forced into the treatment (Forced fee) has the same effect as choosing it (Choosers), and b) not choosing the treatment (Non chooser) has no effect with respect to the control.
-
-          %\footnotesize{ \textit{Do file: }  \texttt{exclusion\_restriction.do}}
-\end{figure}
-
-%---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
-
-\newpage
-
-\subsection{New results}
-
-\begin{table}[H]
-\caption{Effect of frequent payment in observational data}
-\label{te_obs}
-\begin{center}
-\scriptsize{\input{./Tables/def_te_obs.tex}}
-\end{center}
- \scriptsize 
-%\textit{Do file: } \texttt{def\_te\_obs.do}
-\end{table}
-
-% \begin{figure}[H]
-%     \caption{Treatment effects pooling all arms}
-%     \label{pooled_arms_te}
-%     \begin{center}
-%     \begin{subfigure}{0.45\textwidth}
-%         \caption{Financial Cost}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/te_allarms_fc_admin_disc.pdf}
-%     \end{subfigure}
-%     \begin{subfigure}{0.45\textwidth}
-%         \caption{Lost Pawn}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/te_allarms_def_c.pdf}
-%     \end{subfigure}
-%     \end{center}
-%      \scriptsize
-%       %\footnotesize{ \textit{Do file: }  \texttt{te\_allarms.do}}
-% \end{figure}
-
-% \begin{figure}[H]
-%         \caption{Treatment effect decomposition of the Financial Cost }
-%     \label{reg_int_pro_2}
-%     \begin{center}
-%         \centering
-%         \includegraphics[width=0.60\textwidth]{Figuras/int_te_pro_2.pdf}
-%     \end{center}
-%      \scriptsize This Figure is a "close-up" for the estimates found in Figure \ref{fc_pro2} - Panel (a).
-It shows the treatment effects on payed \& incurred interest, the former defined as the actual interest payed, and the latter is the sum of all potential interests (for those pawns that were lost we calculate the interest generated until day 230).
-In the right axis we show the treatment effect on the payed fees.
-Finally, we analyze this effect for the subsamples that recovers or loses the pawn.
-%      %\textit{Do file: }  \texttt{reg_\int.do}
-% \end{figure}
-
-% \begin{figure}[H]
-%         \caption{Frequency of renewals}
-%     \label{ref_dist}
-%     \begin{center}
-%         \centering
-%         \includegraphics[width=0.60\textwidth]{Figuras/ref_dist.pdf}
-%     \end{center}
-%      \scriptsize  This Figure shows the occurrence and frequency of renewals.
-It locates in time, respective to the day the loan started, when the renewal occurs for both the first and second renewal.
-Note that the first renewal is concentrated around 100 days, while the second is concentrated around the 200 days, corresponding to the first and second cycle.
-%      %\textit{Do file: }  \texttt{ref_\dist.do}
-% \end{figure}
-
-%\begin{figure}[H]
-%    \caption{Exit Survey: reasons to pawn or not again with monthly payments}
-%    \label{reasons}
-%    \begin{center}
-%    \begin{subfigure}{0.5\textwidth}
-%        \caption{Pawn again because:}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/razones_si.pdf}
-%    \end{subfigure}
-%    \begin{subfigure}{0.5\textwidth}
-%        \caption{Not pawn because:}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/razones_no.pdf}
-%    \end{subfigure}
-%    \end{center}
-%     \footnotesize \textit{Notes: } 
-%      \footnotesize{ \textit{Do file: }  \texttt{ss.do}}
-%\end{figure}
-
-%\begin{figure}[H]
-%    \caption{Decomposition of the mistakes by `Overconfidence' for Promise Arms}
-%    \label{Promise_errors}
-%    \begin{center}
-%    \begin{subfigure}{0.6\textwidth}
-%        \caption{Promise}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/line_cw_fc_te_cf_OC_promise.pdf}
-%    \end{subfigure}
-%    \end{center}
-%     \footnotesize 
-%     \textit{Notes: }  Decomposition of the percentage of mistakes by overconfidence. 
-%       \textit{Do file: }  \texttt{choose\_wrong\_quant\_wrong\_decomposition.do}
-%\end{figure}
-
-%\begin{figure}[H]
-%        \caption{Types of agents that incur in different FC}
-%    \label{components_fc}
-%    \begin{center}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/scatter_fc_pay.pdf}
-%    \end{center}
-%     \footnotesize \textit{Notes: } 
-%      \footnotesize{ \textit{Do file: }  \texttt{hist\_fc.do}}
-%\end{figure}
-
-% \begin{figure}[H]
-%         \caption{Percentage of payments}
-%     \label{perc_payments}
-%     \begin{center}
-%     \begin{subfigure}{.31\textwidth}
-%     \caption{Control}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_1.pdf}
-%     \end{subfigure}
-%     \begin{subfigure}{.31\textwidth}
-%     \caption{Forcing - fee}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_2.pdf}
-%     \end{subfigure}   
-%      \begin{subfigure}{.31\textwidth}
-%     \caption{Forcing - promise}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_3.pdf}
-%     \end{subfigure}  
-%      \begin{subfigure}{.31\textwidth}
-%     \caption{Choice - fee}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_4.pdf}
-%     \end{subfigure}  
-%      \begin{subfigure}{.31\textwidth}
-%     \caption{Choice - fee - SQ}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_6.pdf}
-%     \end{subfigure}    
-%      \begin{subfigure}{.31\textwidth}
-%     \caption{Choice - fee - NSQ}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_7.pdf}
-%     \end{subfigure}    
-%      \begin{subfigure}{.31\textwidth}
-%     \caption{Choice - promise}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_5.pdf}
-%     \end{subfigure}  
-%      \begin{subfigure}{.31\textwidth}
-%     \caption{Choice - promise - SQ}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_8.pdf}
-%     \end{subfigure}    
-%      \begin{subfigure}{.31\textwidth}
-%     \caption{Choice - promise - NSQ}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_pro_9.pdf}    
-%     \end{subfigure}        
-%     \end{center}
-%      \footnotesize \textit{Notes: } 
-%       \footnotesize{ \textit{Do file: }  \texttt{hist\_payments.do}}
-% \end{figure}
-
-% \begin{figure}[H]
-%         \caption{Percentage of payment conditional on positive payment and Losing Pawn}
-%     \label{perc_payments_conditional}
-%     \begin{center}
-%     \begin{subfigure}{.31\textwidth}
-%     \caption{Control}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_1.pdf}
-%     \end{subfigure}
-%     \begin{subfigure}{.31\textwidth}
-%     \caption{Forcing - fee}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_2.pdf}
-%     \end{subfigure}   
-%      \begin{subfigure}{.31\textwidth}
-%     \caption{Forcing - promise}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_3.pdf}
-%     \end{subfigure}  
-%      \begin{subfigure}{.31\textwidth}
-%     \caption{Choice - fee}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_4.pdf}
-%     \end{subfigure}  
-%      \begin{subfigure}{.31\textwidth}
-%     \caption{Choice - fee - SQ}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_6.pdf}
-%     \end{subfigure}    
-%      \begin{subfigure}{.31\textwidth}
-%     \caption{Choice - fee - NSQ}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_7.pdf}
-%     \end{subfigure}    
-%      \begin{subfigure}{.31\textwidth}
-%     \caption{Choice - promise}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_5.pdf}
-%     \end{subfigure}  
-%      \begin{subfigure}{.31\textwidth}
-%     \caption{Choice - promise - SQ}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_8.pdf}
-%     \end{subfigure}    
-%      \begin{subfigure}{.31\textwidth}
-%     \caption{Choice - promise - NSQ}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/hist_porc_pay_cond_pro_9.pdf}    
-%     \end{subfigure}        
-%     \end{center}
-%      \footnotesize \textit{Notes: } 
-%       \footnotesize{ \textit{Do file: }  \texttt{hist\_payments.do}}
-% \end{figure}
-
-%\begin{figure}[H]
-%    \caption{Evolution of payment}
-%    \label{Evolution payment}
-%    \begin{center}
-%    \begin{subfigure}{0.49\textwidth}
-%        \caption{Paid loans}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/desempeno_evol.pdf}
-%    \end{subfigure}
-%     \begin{subfigure}{0.49\textwidth}
-%      \caption*{}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/desempeno_evol_choice.pdf}
-%    \end{subfigure}
-
-%     \begin{subfigure}{0.49\textwidth}
-%        \caption{Average percentage of paid loans}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/sum_porc_evol.pdf}
-%    \end{subfigure}
-%     \begin{subfigure}{0.49\textwidth}
-%      \caption*{}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/sum_porc_evol_choice.pdf}
-%    \end{subfigure}
-
-%   \begin{subfigure}{0.49\textwidth}
-%        \caption{Average percentage of paid loans | paid}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/sum_porc_cond_evol.pdf}
-%    \end{subfigure}
-%     \begin{subfigure}{0.49\textwidth}
-%      \caption*{}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/sum_porc_cond_evol_choice.pdf}
-%    \end{subfigure}
-%    \end{center}
-%     \footnotesize \textit{Notes: } 
-%      \footnotesize{ \textit{Do file: }  \texttt{evol\_payment.do}}
-%\end{figure}
-
-% \begin{figure}[H]
-%         \caption{FC effect for different discount rates}
-%     \label{oc_hist}
-%     \begin{center}
-%         \centering
-%         \includegraphics[width=0.50\textwidth]{Figuras/discount_effect.pdf}
-%     \end{center}
-%     \footnotesize \textit{Notes: } 
-%      \footnotesize{ \textit{Do file: }  \texttt{discounted\_noeffect.do}}
-% \end{figure}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\newpage
-\section{ Observational analysis}
-\label{appendix_b}
-\vspace{.2in}
-\normalsize
-\linespread{1.25}
-%Really force it to normal size and linespread
-\normalsize
-\linespread{1.25}
-
-The objective of this Appendix is to conduct one test aiming to assess if there is learning in choosing the frequent payment FP) contract.
-In particular if being endogenously induced to have a FP contract causes the client to chose a FP in subsequent pawn.
-The identification strategy is not as strong as in a randomized control trial ---having to rely on an instrumental variable strategy using changes in the supply of the FP contract-- and this is why we chose to locate it in a separate Appendix.
-However we believe we find a strong case for learning causing higher demand for the FP contract.
-
-In what follows we will describe the identifying variation and use the richness of the observational data to control for possible confounds.
-We will use hundreds of branches and hundreds of thousands of pawns covering more than 4 years to estimate (under the identification assumptions) the causal effect of having had a FP on the conditional demand for the FP type of contract.
-
-\vspace{.in}
-
-\subsection{Variation in branches' use of frequent payment contract}
-
-After our experiment ended, Lender $P$ started offering frequent payment contracts along their traditional ones.
-We were not able to get data for the dates of the first expansion, but we have data for the period January 2016 through May 2020.
-During this period some branches where offering the frequent payment contract while others were just starting to do this.
-Some branches also stopped offering the frequent payment contracts.
-Out of all branches 2\% never offered the FP contract, 29\% always offered it, while 69\% offered for only part of our sample period.
-Our identification strategy will mostly rely on these later group, as we include branch fixed effects in our regressions.
-\\
-
-To show the reader a glimpse of this variation in availability of the contract we randomly selected 20 branches and plotted which months had a frequent payment contract active in their IT system.
-Figure \ref{variation_pf_suc} shows a time plot for each branch, where each observation is a month.
-The Y-axis takes the value of 1 if in that month the FP contract was available in that branch and zero otherwise.
-So it is a ``supply side'' variable.
-
-\vspace{.1in}
-\begin{figure}[H]
-        \caption{Existence of FP per branch}
-    \label{variation_pf_suc}
-    \begin{center}
-        \centering
-        \includegraphics[width=0.80\textwidth]{Figuras/active_pf_suc.pdf}
-    \end{center}
-     \scriptsize This Figure shows the presence of the frequent payment (FP) contract in 20 randomly chosen branches of Lender $P$ for a span of more than 4 years.
-A $y$ value $=1$ means that in that month the FP contract was available in that branch.
-     %\textit{Do file: }  \texttt{active\_pf\_suc.do}
-\end{figure}
-\vspace{.1in}
-
-In conversations with Lender $P$ about this variability they said that it is driven by three things: the expansion of the frequent payment product is done gradually, the IT system of a branch sometimes fails, and they often do experiments themselves turning on and off the existing of the frequent payment contract as this was a relatively new type of contract.\footnote{Unfortunately the had no documentation on how these experiments were implemented.} We did verify that there are no frequent payment contracts when they said it was turned off in their IT system.
-
-\paragraph{Orthogonality of FP supply.} We will use the availability of the FP contract as an instrument for the client choosing a FP contract when she pawns.
-Clearly one cannot choose a FP when it does not exist, so that this instrument allows would-be-FP choosers to obtain a FP contract.
-We verify that indeed it has a statistically powerful first statge.
-One may be concerned that this instrument may not satisfy the exclusion restriction however.
-As we will explain below we will use this instrument in an specification that controls for branch and client fixed effects, taking into advantage that many clients do pawn repeatedly (See Figure \ref{hist_num_pawns} below).
-These control for any characteristic of the client that is fixed across time, and therefore is a strong control for selection of clients across branch or across contracts.
-We also control for calendar of the month fixed effects, thereby absorbing common time trends that affect all clients, like macroeconomic shocks.
-We describe the exact specification below, but for now we want to note that we need only for the exogeneity of the instrument to hold conditional on these extensive set thousands of fixed effects.
-
-    \vspace{.1in}
-\begin{figure}[H]
-        \caption{Number of pawns per client}
-    \label{hist_num_pawns}
-    \begin{center}
-        \centering
-        \includegraphics[width=0.6\textwidth]{Figuras/hist_num_pawns.pdf}
-    \end{center}
-     \scriptsize This figure plots a histogram of the number of pawns per client during our sample period (January 2016 through May 2020).
-A large fraction of clients have more than one pawn, and many have several pawns.
-We use these repeat clients to identify learning below.
-     %\textit{Do file: }  \texttt{hist\_num\_pawns.do}
-\end{figure}
-\vspace{.1in}
-
-Having said this, in Table \ref{instrument_random} we assess to what extent we can predict whether a given branch activates the FP contract in its IT system in a given week or a given month.
-It turns out that we cannot predict in which weeks a given branch uses the FP contract with our observables controlling for branch fixed effects.
-The observables include fraction female clients last week (or last month), the age of these clients, number of pawns last week (or last month), average size of those loans, the percentage of pawns last week (or last month) that were jewelry, the percentage of loan recoveries --the opposite of default-- last week (or last month).
-The same is true if we use one month prior instead of one week.
-The $R^2$ shows that the \textit{additional} variance explained by the covariates beyond branch and calendar week fixed effects is low: going from 0.154 to 0.157 when we add all regressors.
-The $AUC$ and the \textit{Accuracy Rate} give a similar picture, with out-of-sample $AUC$ around 0.72 and Accuracy rates around 66\%.\footnote{\cite{Finanzia} say that for predicting loan default for instance AUC's from 0.80 to 0.95 are common.} \\ %\hl{Appraisers could potentially have an effect on what contract people choose conditional on the contract existing in the system.
-We test for this and find XXX...}
-
-Quantitatively the correlations are small: an increase of 1 years of the mean age of clients is associated with an increase of 0.008 percentage points in introducing FP, an increase in the size of the loan by 1000 pesos increases it by 0.002, an increase of 10 pawns per day increases it by less than 0.0002 percentage points.
-Having 10\% less women as clients in the past increases it by 1 percentage point.
-This result of low correlation between important observable variables and the supply of FP contract in a given branch makes us more comfortable with the assumption that the instrument satisfies the exclusion restriction.
-The presence of the FP contract in a given week in a given branch seems almost random from this perspective.
-
-\begin{table}[H]
-\caption{Predicting the supply of FP contracts within branch across time}
-\label{instrument_random}
-\begin{center}
-\footnotesize{\input{./Tables/instrument_random.tex}}
-\end{center}
- \scriptsize
-This table uses OLS regressions to predict whether branch $j$ in week $t$ had a FP available.
-So the dependent variable is an indicator for this event $\mathbbm{1}(\text{Branch Had FP})_{jt}$, and the explanatory variables are measures of performance of that branch and the characteristics of the clients either the week previous to $t$ or 4 weeks previous to week $t$.
-We allow for two time periods since the branch manager or central offices may take time to react to information.
-Column 1 includes branch and week fixed effects, while Column 2 adds the covariates displayed measured the week previous to $t$.
-Column 3 is analogous to column 2 except that the values of the displayed covariates are averaged across the 4 weeks prior to week $t$.
-The bottom panel shows measures of predictive power like $R^2$, as well as area under the ROC curve ($AUC$), and the Accuracy Rate.
-It also shows F-test of the null hypothesis that the branch (week) fixed effects, or the other regressors have coefficients equal to zero.
-%\textit{Do file: } \texttt{instrument\_random.do, pred\_instrument.do}
-\end{table}
-
-\vspace{.1in}
-
-\subsection{Experiencing FP causes future demand for FP to increase}
-
-This subsection uses the existence of a FP contract in the branch as an instrument for a client \textit{having} a FP contract if she visited that branch that week to pawn.
-Using this instrumental variable strategy we estimate the effect of having had a FP in the previous pawn.
-More concretely, Table \ref{iv_pf} reports results from a two-stage least squares estimate of the effect of having a FP contract on subsequent demand for FP contracts.
-We estimate the following regression:
-
-\begin{equation}
-    \mathbbm{1}(\text{Has FP})_{ijt} = \alpha_i + \gamma_t + \beta \mathbbm{1}(\text{Had FP previously})_{ijt}  + \epsilon_{ijt}
-    \label{eqn:IV}
-\end{equation}
-
-\noindent where $i,j,t$ index client, branch, and week respectively.
-$\mathbbm{1}(\text{Has FP})_{ijt}$ is an indicator for client $i$ pawning in branch $j$ in week $t$ using a FP contract, given that both FP and traditional contracts were available at the branch at the time of pawning, so that there is a choice to be made among these.\footnote{When a FP is not available in branch $j$ in week $t$ the variable takes the value of missing, and is therefore not considered in the regression.
-That is, we only include observations when the client had a choice between FP and traditional contracts.} Moreover we restrict the sample to pawns where the immediate previous pawn is already closed at the moment of opening the new one\footnote{We do this to avoid making the conclusion that clients are re-pawning in order to meet their past debt.}.
-We estimate a regression with calendar week fixed effects (we have 212 weeks) $\gamma_t$, and also include client fixed effect $\alpha_i$.
-The variable of interest is denoted by $\mathbbm{1}(\text{Had FP previously})_{ijt}$, and is an indicator for the client's immediate previous loan\footnote{We consider only the immediate previous loan, following a ``Markov's'' assumption, in which only the present state determines the future.} being FP loan.
-% The controls $X_{ij}$ include how assiduous a client is: the number of times she has pawned in the 12 months previous to $t$, as well as a dummy of having made a pawn a Lender $P$ in the period from $t'$ to $t$:   $\mathbbm{1}(\text{Had any loan previously})_{ij't'}$.
-Note that the only difference between this last control variable and our main explanatory variable is that the former does not specify which type of contract this previous loan had.
-This means that the variation identifying $\beta$ is \textit{which type} of loan the client had conditional on having had one.\\
-
-Having client fixed effects in the regression means that we only use variation across time (across subsequent pawns) to identify the effect of experience, and avoid the selection problems that come from comparing across clients.
-That is, they control for the fact that different types of clients may select different types of contracts.
-Repeat pawning is common and this helps for identification.
-Figure \ref{hist_num_pawns} shows a histogram of the fraction of clients that had $1, 2, 3,\ldots, 60$ pawns in our sample.
-We have more than one hundred thousand clients that got two loans within 3 or less months from each other\footnote{We give a small lower bound to keep the identity of Lender $P$ confidential}, and for 37\% of those clients the immediately sequentially preceding loan was taken when the branch had FP available.\\
-
-However, even with client fixed effects, idiosyncratic unobserved shocks across time may induce spurious correlation between choosing a FP last week and choosing FP today.
-The variable $\mathbbm{1}(\text{Had FP previously})_{ijt}$ is therefore still potentially endogenous.
-To deal with this we instrument $\mathbbm{1}(\text{Had FP previously})_{ijt}$ with the \textit{availability} of the contract in branch $j$  when the client previously went to pawn the immediately prior pawn with respect to $t$, $\mathbbm{1}(\text{FP Avail})_{ijt}$.
-This is basically using a supply shifter to identify demand.
-We showed above that availability of FP contracts has close to a zero correlation to a battery of observables.
-The IV strategy assumes that availability of the FP contract in a given week in a given is uncorrelated with $\epsilon_{ijt}$ --- i.e.
-that after conditioning on thousands of client, branch and week fixed effects and the client having pawned recently, there is no omitted variable driving both: the branch having FP contracts on, and the client subsequent pawn using a FP contract.
-Note that including branch fixed effects means that identification comes from a given branch sometimes having the FP and sometimes not.
-\\
-
-The exclusion restriction for an instrument is untestable, but note that we are comparing clients that go to the same branch, who have the same pawning frequency, but where one of them arrived to the branch to pawn on a week where the FP contract was available and the other arrived on a week where the same branch had no FP contract available.%\footnote{We also tried specifications restricting the sample to 4-12 weeks adjacent to the FP contract becoming available or becoming unavailable in a branch and obtain similar results.
-This strategy is close in spirit to a regression discontinuity or event-study design, comparing clients that go to the same branch with the difference that one went there 2 weeks before the FP contract becoming available.}
-The exclusion restriction could be violated for example if the branch manager makes FP available as a function of clients that will come in that week and therefore reaches a certain type of client that is more likely in-and-of themselves to prefer FP contracts now and in the future.
-We find this unlikely.
-It is hard to predict who will come on a given week and if they are more likely to like the FP contract: Table \ref{instrument_random} strongly suggests that the branch manager is not turning the FP contract on and off as result of which clients are coming to the branch or how the branch is doing.
-Having said this, we acknowledge that the exclusion restriction could be violated even in this very tightly controlled specification.\\
-
-Table \ref{iv_pf} shows the first and the second stage regressions for equation \ref{eqn:IV}.
-All columns have branch, and calendar week fixed effects, and standard errors are clustered by client.
-Columns 1 and 4 show strong first stages (t-stats above 50).
-The availability and unavailability of the FP contract has an incidence on its use.
-Under our identification assumptions, Columns 2-3 (and 5-6) show strong causal effects: having  been induced by the instrument to have a FP contract in the previous loan causes the client to a FP for her subsequent pawn by 50 percentage points (column 2).
-The difference between columns 2 and 3 (and 4-5) is the sub-sample considered: in the first one we only condition the immediate previous pawn to be closed at the time of opening a new one, the second one not only considers previous pawns being closed, but having at least one week closed.
-
-\begin{table}[H]
-\caption{Experience with frequent payment contract raises future demand for it}
-\label{iv_pf}
-\begin{center}
-\footnotesize{\input{./Tables/iv_reg_demand_pf.tex}}
-\end{center}
- \scriptsize
-This table shows resulting estimates of variants of equation  \ref{eqn:IV} above.
-They regress a dummy for the client choosing a frequent payment contract (when both the traditional one and the FP are available) on whether the previous loan was under a FP contract.
-All columns have branch, and calendar month fixed effects, and the standard errors are clustered by client.
-The main regressor of interest is having had a FP loan in the immediate past of $t$ which measures experiencing a FP contract.
-Columns 1 and 4 report the result of first stage where the supply side instrument is an indicator for the branch having had a FP available when the client showed to pawn the previous pawn.
-Column 2 \& 5 presents the two-stage least square estimate.
-Columns 3 \& 6 are analogous, but instead of looking clients whose previous pawn is already closed, it looks at those whose previous pawn has at least one week of being closed.
-We do not report the exact number of observations to keep Lender $P$ identity confidential and instead give a lower bound.
-%\textit{Do file: } \texttt{iv\_reg\_demand\_pf.do}
-\end{table}
-
-% \subsubsection{Experiencing FP causes repeat pawning}
-
-% Using experimental variation the paper find that being forced into a FP contract increases the likelihood of the client coming back and pawning again.
-Here we see if that result generalizes for all branches using the instrumental variable strategy described above, where we use $\mathbbm{1}(\text{Repeated Pawning})_{ijt}$ as a dependent variable instead in equation \ref{eqn:IV}.
-
-% Table \hl{XXX} has the same structure as Table  \hl{XXX} above.
-It finds that the experimental result is qualitatively replicated with this different sample and different identification strategy.
-Having had a previous FP loan induced by its availability is associated with an increase of \hl{XXX} in the probability of pawning again \hl{in the next 3 months}.
-
-% \subsubsection{Pawn recovery and FP contracts}
-
-% Using the individual fixed effects specification, as well as the instrumental variable strategy defined above, Table \hl{XXX} finds that FP are \hl{XX\%} more likely to recover their pawns.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Mechanisms }
+
+\subsection{Optimism, Over-Optimism, and the Failure of Self-Commitment}
+\label{overconfidence}
+
+\textcolor{red}{Need to decide whether we want to try to plant our feet on Confidence/Overconfidence as the core `why' of the previous result
+.}
+%\subsubsection{Behavioral: overconfident borrowers demand less (but benefit more)} \label{behavioral}
+
+The leading behavioral explanation in the literature for low demand for commitment is present biased preferences with naivete (e.g.
+\cite{Rabin2018}, \cite{John}, \cite{Laibson2018})  \cite{Laibson2015} shows that the lost flexibility resulting from a commitment contract can limit take-up especially severely when agents are (partially) naive about their self control problem.
+In our context if consumers are (partially) naive about their present bias, they would plan to save more (or spend less) than what they actually end up saving, thus making it be harder to recover their pawn.
+This under-saving will be mitigated in the fee forcing contract since the fee makes them save money to pay part of the loan periodically.
+\ref{appendix_c} formalizes this in a model.
+Another behavioral explanation is that clients may underestimate the likelihood and severity of negative income shocks.
+Both of these explanations predict that clients will be overconfident about their likelihood of pawn recovery.
+Recall that in the control group the client's subjective probability of recovery is on average 93\%, while actual recovery is just 44\%.
+A further piece of evidence consistent with underestimating negative income shocks and with present bias with partial naivete is that a large number of people (25\%) in the control group pay a positive amount toward pawn recovery but end up losing their pawn anyway.
+
+So, overconfidence of recovering the pawn is implied by both present bias preferences with naivete and upward bias in their income expectations.
+But does overconfidence actually predict low demand for commitment empirically?
+It does.
+We define as overconfidence as the reported subjective probability of recovery minus the predicted probability based on the client's characteristics, $P^s_i-\widehat{P_i(X_i)}$.\footnote{We predict $\widehat{P_i(X_i)}$ in two steps.
+In step one we use Lasso with cross validation to tune the regularization parameter to select the most predictive variables $X$.
+The typical present bias question as in \cite{Ashraf} was eliminated in this step.
+In the second step we estimate $\widehat{P_i(X_i)}$ using those variables in a logit model.
+The Lasso selected variables were type of pawn, female, age, has pawned before, has savings, participates in rotating savings, often feels tempted to change plans, would like to have a reminder to pay, and an economic vulnerability index.
+We are careful not to include these variables as controls in Table  \ref{oc_reg}.} There is a large amount of overconfidence in our context.
+Figure \ref{oc_hist} plots a histogram of $OC_i$ and shows that the overwhelming majority display overconfidence, and a large fraction overestimate recovery by more than 50 percentage points.
+Our measure of overconfidence is useful especially when there is limited time for a detailed survey.\footnote{It may be more useful than a simple elicitation of present bias as in \cite{Ashraf}.
+We find that 15\% of clients are classified as present biased using this measure of preference reversal.
+This level is similar to the number \cite{Ashraf} find but small to explain no take-up of commitment for 90\% of clients.
+This measure was not correlated with take up of commitment in our sample.} First it is very prevalent, which makes it promising to explain the overwhelming prevalence of low take up.
+Second, it is easy to measure.
+Third, it is predictive of take-up in an intuitive way.
+Finally, overconfidence in recovery is implied by present bias with (partial) naivete but also by biased expectations of negative income shocks, thus capturing both kinds of bias.\footnote{\textcolor{red}{Another indication of overconfidence is that in our data, of those who renew, 83\% lose the pawn anyway.
+Our measure of overconfidence has a correlation of \hl{xxx}\% with a dummy for renewing and losing the pawn.
+}}
+
+\cite{Sprenger} have argued that it is critical to understand the link between beliefs and demand for commitment, yet the evidence is scarce.
+Table \ref{oc_reg} does this: it regresses an indicator of take up of the monthly payment contract against an indicator for overconfidence $OC_i:=\mathbbm{1}(P^s_i-\widehat{P_i(X_i)}>0)$ and controls.
+Controls $Z$ include branch and day of the week dummies, schooling, whether the client does a monthly budget plan, among others.
+We are careful not to include controls that were used in $\widehat{P_i(X_i)}$.
+% and a measure of intertemporal preference reversal analogous to that of \cite{Ashraf} as controls.\
+In the choice-fee arm, being overconfident decreases the likelihood of demanding commitment by 12 percentage points a result that this is robust to including controls  (columns 1 and 2).
+While overconfidence predicts lower take up in the Commitment Choice arm, this is not the case in the promise-choice arm (columns 3 and 4).
+One interpretation of the results is that the overconfident borrowers think they do not need commitment, and their demand decreases sharply as soon as there is even a small fee, and at the same time they perceive the promise as a low cost option.
+This provides evidence for \cite{Sprenger}'s conjecture that ``tepid demand for commitment outside controlled experimental settings is consistent with broad unawareness [of biases]''.
+
+How does overconfidence map to cost outcomes?
+Theory predicts that the more overconfident (naive) may be at the same time those that benefit more from commitment.
+Extrapolating individual treatment effects of the Forced Commitment contract vs the status quo one to the choice arm (see below for more detail), and using them as a dependent variable we find that overconfident borrowers benefit \textit{more} from the commitment contract, with {24.8}\% (=\${30}/\${121}) more savings (columns 5 and 6).
+Thus while we predict the overconfident benefit more from commitment, they demand less of it.
+
+\subsubsection{Neoclassical Alternatives} \label{neoclasical}
+
+\vspace{.1in}
+\noindent \textbf{Risk aversion.} We do not have measures of risk aversion in our short survey, which makes it hard to assess the hypothesis that risk aversion limits take-up of the fee frequent payment contract.
+One way to proceed is to take the empirical distribution of financing cost ---$F_{fee}(FC)$--- as one the client would have faced had she chosen the the fee-commitment contract.
+We could then ask what would risk aversion have to be in order to justify the client choosing the fee-commitment contract distribution of costs over the distribution associated with the status quo contract, $F_{sq}(FC)$.
+Framed as a choice among cost distributions, we can calculate what risk aversion is needed to rationalize the overwhelming choice of the status quo contract over the fee-commitment contract.
+This exercise of course assumes --as is common in economics-- that clients know the distribution of financial cost, that the distribution is common across consumers (although this can be relaxed), and that this cost distribution is the only difference among contracts.
+
+Fortunately for us, it turns out that one distribution first-order-stochastically dominates the other, obviating the need to calibrate a specific utility function or use a parametric distribution function in order to rank them in terms of expected utility.
+We use the fact that if the utility $u(FC)$ is decreasing in $FC$ (i.e.
+clients dislike paying higher financing cost) and $F_{fee}(FC) \geq F_{sq}(FC)$ for all $FC$, which we actually verify in our data, then $E_{fee}[u(FC)] \geq E_{sq}[u(FC)]$, that is any expected utility maximizing client risk averse consumer should choose the Forced Commitment contract as a result of the distribution of cost payoffs.\footnote{See the Appendix for the proof.
+Figure \ref{ecdf_fc} in the Appendix shows that indeed $F_{fee}(FC) \geq F_{sq}(FC)$.
+Table \ref{stochastic_dominance} shows that this holds also for sub-populations of different characteristics.}.
+Thus, risk aversion cannot explain the low demand for commitment under the assumptions of this exercise.
+
+\vspace{.1in}
+\noindent \textbf{Lost flexibility.} A second explanation for low take up is lost flexibility.
+That is, the fee-commitment contract may provide too much commitment which is costly because the client may be forced to incur in late payment fees if he experiences a negative income shock.\footnote{Note that income shocks that affect the ability to pay the entire loan are a worry for both the Forced Commitment contract and the status quo one, and should not make one contract more favorable than the other.} While we cannot rule out that income shocks combined with lost flexibility of the contract explain the low demand, we think it is unlikely.
+First, we showed above that clients report a subjective probability of recovery of 93\% on average, which suggests they are not too worried about income shocks.
+Second, the fear of incurring fees is quantitatively not enough of a concern when compared to the savings they are experiencing.
+%Note that fees for late payment are not that high.
+In an average loan of 2,000 pesos the monthly payment is close to 700 pesos, and a fee of 2\% of that is 14 pesos (less than \$1 dollar).
+This is about gr{1\%} of monthly per capita income of the first 3 deciles of Mexican {household's} income distribution.
+%This compares favorably to the gr{\$11.6 + \$62.3)} pesos transportation / transaction cost of one.
+
+To make this concrete, we calculated what the financing cost of the fee-commitment contract would be if \textit{all} its clients incurred in \textit{all} potential fees (while keeping payment profiles and pawn recovery constant) and added these fictitious fees to financing cost for those in the Forced Commitment arm, thus artificially inflating their cost.
+We then re-estimated the quantile treatment effects analogous to Figure \ref{fc_pro2}(b) with this inflated financial cost.
+%\footnote{Of course behavior may not be constant, but we believe this is a reasonable fist approximation.
+%It could be that having this small fee added to the balance discourages them to pay or makes it harder to pay back the loan.
+But the contrary may also happen, with the fee making them more determined to pay early.
+We would need a structural model of client behavior to estimate a full counterfactual.
+We suspect that such small fees would not generate large changes in behavior in a simple neoclassical model.}).
+Figure \ref{fc_allfee} presents the results.
+We find that even in this extreme scenario, tilted against the Forced Commitment contract, the estimated effect still implies cost savings from the Forced Commitment contract at the mean, 25$^{th}$, 50$^{th}$, and 75$^{th}$ percentiles.\footnote{Recall that the differences in financing cost already takes into account the fact that clients in the fee forcing contract sink more pre-payments than those in the status quo contract, and that those prepayments are lost if the loan is not fully paid back.}  Although these arguments are not definitive, they suggest that low demand for commitment may be driven by more than the anticipation of lost flexibility implied by a small fee.
+
+\vspace{.1in}
+\noindent \textbf{High time discounting.} We mentioned above that clients in the status quo contract tend to wait until the last moment to pay to recover their pawns.
+Even among those that recover their pawn, only 40\% pay before the 90$^{th}$ day.
+Table \ref{mechanisms} shows that clients assigned to the fee-commitment contract front load their payments, starting their first payment earlier and finishing paying earlier too.
+However, clients may dislike front loading payments if their time preference discount rate is high.
+They may be willing to trade off a higher probability of losing their pawn for more \textit{back} loaded payments.
+
+What would discount rates have to be in order for back loaded payments to offset the reductions in financial cost effects we observe?
+%We can calculate this number by looping across a grid of discount rates, incorporating this higher discount rate in the definition of financial cost, and reestimating equation \ref{basic_reg} with this modified financial cost measure as the dependent variable in equation 1, searching for the discount rate that makes $\beta$ equal zero.
+We did this and obtained
+We calculate that the discount rate that is necessary to compensate for the savings in financial cost (i.e.
+that makes the estimated $\beta$ in equation \ref{basic_reg} equal to zero when financing cost --using different $r$'s-- is the dependent variable) is a staggering 8,190 percent per year.
+We find this discount rate implausibly high even for this credit constrained population\footnote{For comparison, \cite{Levin} find that a discount rate of 1,415 per year for subprime borrowers in the US is too high to be believable.}, casting doubt on high discount rates as explanation for low demand for commitment.
+%\footnote{In the baseline survey we give respondents a hypothetical choice between $100$ pesos tomorrow or $150$ pesos in one month (an implicit yearly interest rate of {12,800\%}) and only 30\% chose the later one.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \linespread{1.25}
+
+Although the empirical results are striking and stand alone, this section refers to the model of \cite{John} to interpret our empirical results.
+The model is stylized but incorporates important features of our context.
+It allows for negative income shocks which we think are prevalent in this population.
+%The shock generates a cost of committing to monthly payments and could potentially be a reason for low take up.
+It also features clients with present biased time preferences --allowing for partial naivete-- choosing to save to pay for an expense, and with the opportunity to make a commitment to save and pay.
+These two features parsimoniously explain several facts about the context --like overconfidence in recovering the pawn--, and about the results --e.g.
+that forcing commitment seems to help.
+We intend the model only as a very stylized approximation to our context, and we use it only to help us organize the interpretation of the empirical results, not as a literal description of reality.
+%Third, it allows for a simple way to model commitment afforded by late payment fees.
+%Nonetheless, the model abstracts from several details of the context.
+Even with these abstraction it allows us to explain our six main results listed in Section \ref{explanations_recap} below.
 
@@
 
+\subsection{Interpretation}
+
+The model is very parsimonious but powerful and it can potentially explain all our empirical findings qualitatively.\footnote{The model is sufficiently stylized that we think we would not gain much from estimating it.
+Furthermore we have no data on income shocks which figure prominently in the model.
+\cite{Ted} and \cite{Aprajit} are two very recent models that combine a field experiment with commitment contracts and estimation of present bias parameters.} First, it can explain why default is high in the status-quo contract, namely that clients are present biased and have no commitment devices.
+Second, it can explain why clients are overconfident in our data, namely by virtue of naivete about present bias.
+Under the model naivete is necessary to explain this.
+Third, it can also explain why the fee forcing contract induces lower default, but not for everyone: namely that it makes the incentive compatibility constraint for payment binding for the present biased, while it was not binding in the status quo contract.
+Fourth, it can also explain why there is low demand for commitment even if it seems to improve welfare: namely that there is a small share of neoclassical and sophisticated clients, and at the same time naifs have a present biased parameters values in the region in which they think they can save on their own.
+Fifth, it explains non-zero demand for commitment for a set of clients.
+Sixth, it can explain why clients exposed to the Forced Commitment contract are more likely to come back namely those naifs whose welfare increased as a result of being forced into the fee-commitment contract.\footnote{Those with $\hat{\beta_i}>\beta_{SQ}>\beta$.}
+
+\subsection{Other potential explanations: recap} \label{explanations_recap}
+
+There may be other interpretations of the empirical findings, but the bar is high. An alternative explanation will need to explain the 6 facts below:
+
+\begin{enumerate}
+\itemsep0em 
+\item High (although ex-post inefficient) default in status quo contract.
+\item Overconfidence about pawn recovery.
+\item Forcing commitment increases pawn recovery.
+\item Small demand for commitment...
+\item ...but positive demand for commitment.
+\item Forcing commitment makes clients more likely to come back.
+\end{enumerate}
+
+Let us consider alternative explanations in isolation (i.e. just considering one change or feature at a time with respect to a neoclassical model):
+
+\vspace{.1in}
+\noindent \textbf{Alternative 1: Strong prevalence of income shocks.} This could explain (4) and (1), but not why forcing helps, (3) and (6), nor why there is overconfidence, (1).
+It would also not explain why clients come to pawn in the first place and then default, (2), as they would weight in on the high chance of losing the pawn.
+
+\vspace{.1in}
+\noindent \textbf{Alternative 2: High time discounting}.
+This could not explain (1) nor (5) nor (6).
+It could qualitatively explain (4), but as we say in section \ref{sec:demand} quantitatively it would require unbelievably high discount rates.
+
+\vspace{.1in}
+\noindent \textbf{Alternative 3: Risk aversion.} We already discussed and rejected risk aversion in section \ref{sec:demand}, although using strong assumptions in the process.
+Risk or ambiguity aversion could still play a role in explaining 4 and should be investigated in future research.
+However it would hardly explain (1), (2), (5), or (6).
+
+\vspace{.1in}
+\noindent \textbf{Alternative 4: Misunderstanding the contracts.}\footnote{This is a potential criticism of \textit{any} paper offering choice, and one that is non-falsifiable if the critic has free reign to propose how the contracts are perceived in the subject's mind.} We were very aware of the importance of clients understanding the contract in order to infer preferences from choice.
+That is why we made a strong effort for clients to understand the contracts (see subsection \ref{implementation}).
+Note however that while clients making purely random mistakes could explain why 10\% demand commitment ---i.e.
+(4) and (5)--- it would not explain the rest of the findings, nor why the Soft Commitment (see below) had more take up that the fee-commitment, or why we can statistically predict take-up with significant accuracy (see Figure \ref{interactions_takeup} and Table \ref{Table_compliance}).
+
+\vspace{.1in}
+\noindent \textbf{Alternative 5 (behavioral): Forgetting to pay/salience.} Frequent payments may act as a reminder to save and recover the pawn.
+This would try to explain (1) by appealing to people forgetting to pay, and (3), (5), and (6) by appealing to frequent payment acting as reminders (i.e.
+there being demand for reminders).
+It would not explain (2) or (4) which are critical in the paper.
+However even for (1) it seems to us a stretch to explain people losing a valuable pawn by forgetting to pay it.
+Since the Soft Commitment installment contract did not change behavior (as shown below) this explanation would also require us to posit that only fees acts as reminders, not promises.
+
+\vspace{.1in}
+\noindent \textbf{Alternative 6 (behavioral): Income shocks overconfidence}.
+One could also easily introduce in the overconfidence about income shocks in the model of \ref{appendix_c}\footnote{Say with $\widehat{\lambda} <\lambda$.
+The effect on demand for commitment is uncertain since on the one hand it decreases $\beta_{SQ}$ decreasing demand, but on the other a smaller $F$ is needed to make the IC binding, making commitment less costly.}.
+This would leave default unchanged in both the status quo and the fee forcing contract thus would not explain (3), %since $F_{min}(\beta,\widehat{\lambda})<F_{min}(\beta,\lambda)$.
+% $\widehat{\lambda} <\lambda$ alone 
+It would not explain (5) or (6) either as demand for commitment would be zero without present bias.
+
+\vspace{.1in}
+We do not claim that the model in the Appendix is the only possible explanation of our empirical findings, but it is a parsimonious explanation of all of them.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \clearpage

### 2022-12-20 donde.tex
revision of text by enrique, frank and isaac

@@
 Jose Maria Barrero, Andrei Gomberg, Emilio Gutierrez, David Laibson, Aprajit Mahajan, Matt Rabin, Charlie Sprenger, and seminar participants at ITAM provided valuable feedback.}}
-\author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira \and Frank DiTraglia   \thanks{Seira: ITAM/MSU, enrique.seira@gmail.com (corresponding author); McIntosh:  University of California San Diego, ctmcintosh@ucsd.edu; Meza: University of California at Berkeley, isaac.meza@berkeley.edu; Sadka: ITAM, jsadka@itam.mx; DiTraglia: Oxford, frank@ditraglia.com} }
+\author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira \and Francis J.\ DiTraglia   \thanks{Seira: ITAM/MSU, \url{enrique.seira@gmail.com} (corresponding author); McIntosh:  University of California San Diego, \url{ctmcintosh@ucsd.edu}; Meza: Harvard University, \url{isaacmezalopez@g.harvard.edu}; Sadka: ITAM, \url{jsadka@itam.mx}; DiTraglia: Oxford, \url{francis.ditraglia@economics.ox.ac.uk}} }
 \date{This draft:  \today \\[2 cm]}
@@
 To repurpose the language of \cite{Laibson2018}, we suggest that pawn contracts effectively shroud their \textit{lack} of commitment to induce default in a manner not obvious to borrowers.
-Given that pawnshops, moneylenders, and paycheck lending institutions are likely to face client pools disproportionately made up of impatient and time-inconsistent individuals, the design of such contracts may have first-order consequences for the financial lives of the poor.
+Given that pawnshops, moneylenders, and paycheck lending institutions are likely to face client pools disproportionately made up of impatient and time-inconsistent individuals, the design of such contracts may have serious consequences for the financial lives of the poor.
 
@@
 Importantly, the benefits are distributed broadly: almost the whole distribution of treatment effects shows cost savings; however those most economically vulnerable, and those most overconfident about their probability of repayment, experience larger gains.\footnote{As in \cite{Rabin2018} we contrast subjects' \textit{own predictions} of their behavior with their actual behavior, but we do it in a natural setting.}  Treatment effects are concentrated in the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery.
-That is, the commitment contract induces people who would otherwise pay something towards recovery, to pay more and faster and thus recover their pawn more at a cheaper financial cost.
+That is, the commitment contract induces people who would otherwise pay something towards recovery, to pay more and faster, making them more likely to recover their pawn at a lower financial cost.
 
@@
 Only 10\% of the choice arm takes up the contract, and none of the core study outcomes are significantly improved by the ability to choose commitment.
+
+%This is not the first paper to find low demand for commitment, however it is the first we know of that can compare choice versus forcing with a money-metric outcome such as loan repayment.
 
@@
 Second, the existence of commitment-style repayment contracts in pawnshop lending is novel in Mexico.
-While forcing individuals into commitment does not cause them to demand it in subsequent loans, \textcolor{red}{in Table \ref{iv_pf}} we show observational evidence of `learning by not doing’:  individuals offered commitment who elect not to take it \textcolor{red}{and subsequently default} \textit{do} learn about the benefits of commitment, demanding commitment loans at higher rates on subsequent pawn contracts when given the choice.
+While forcing individuals into commitment does not cause them to demand it in subsequent loans, \textcolor{red}{in Table \ref{iv_pf}} we show observational evidence of `learning by not doing’:  individuals offered commitment who elect not to take it and subsequently default \textit{do} learn about the benefits of commitment, demanding commitment loans at higher rates on subsequent pawn contracts when given the choice.
 Finally, while we are working with a lender who has a social mission and is interested in understanding how to help borrowers, there is no free lunch.
@@
 
-The remainder of the paper is structured as follows:  section \ref{context} provides context and describes the data sources.
-Section \ref{Data} presents summary statistics and defines our main outcome variables.
-Section \ref{Experiment} describes the experiment and shows pre-treatment balance across arms.
-Section \ref{fee-commitment} estimates the effect of forcing clients into the fee-commitment contract, while Section \ref{fee-choice} studies the effects of choice.
+The remainder of the paper is structured as follows:  section \ref{context} provides context and defines our main outcome variables.
+Section \ref{Experiment} describes the experiment, data sources, and shows pre-treatment balance across arms.
+Section \hl{???} estimates the effect of forcing clients into the fee-commitment contract, while Section \hl{???} studies the effects of choice.
 Section \ref{conclusion} concludes.
@@
 %From this first comparison we conclude that penalizing borrowers for delinquency in a contract which has already has large penalties from default actually helps borrowers.
-In fact, we find that borrowers assigned to the forced fee-commitment contract are 5pp more likely to be repeat costumers, suggesting that they themselves liked the the commitment contract more after experiencing it.\footnote{As it is well known, \textit{naivete} facilitates their exploitation by firms.
+In fact, we find that borrowers assigned to the forced fee-commitment contract are 5pp more likely to be repeat customer, suggesting that they themselves liked the the commitment contract more after experiencing it.\footnote{As it is well known, \textit{naivete} facilitates their exploitation by firms.
 \cite{Laibson2018} conjectures that this exploitation may be limited if consumers use experienced utility to choose among firms or contracts.}
@@
 
-The clients that pawned understood these terms well (as we verified in interviews).
-\footnote{90\% of clients report in our survey that they have pawned before.} These clients have little or no access to other types of loans and they value the convenience of pawn borrowing.
+The clients that pawned understood these terms well (as we verified in interviews).\footnote{90\% of clients report in our survey that they have pawned before.} These clients have little or no access to other types of loans and they value the convenience of pawn borrowing.
 This population of pawn borrowers is economically vulnerable:  30\% of them could not pay either water, electricity \& gas or rent in the past 6 months.
@@
 So it does appear that a large share of default is not `planned' in a simple ex-ante sense.
-High default could be also detrimental from the lender's point of view since it may reduce the likelihood that the client becomes a return costumer.
-Lender P was explicitly interested in  partnering with us to investigate whether a frequent payment contract would increase pawn recovery, costumer satisfaction, and repeat borrowing, and to explore whether there was demand for such a contract.
-
-Pawnshops therefore makes money in three ways: by reselling the jewelry left as collateral on defaulted loans, by charging interest on non defaulted loans, and by keeping the payments made on defaulted loans.
+High default could be also detrimental from the lender's point of view since it may reduce the likelihood that the client becomes a return customer.
+Lender P was explicitly interested in  partnering with us to investigate whether a frequent payment contract would increase pawn recovery, customer satisfaction, and repeat borrowing, and to explore whether there was demand for such a contract.
+
+Pawnshops therefore make money in three ways: by reselling the jewelry left as collateral on defaulted loans, by charging interest on non defaulted loans, and by keeping the payments made on defaulted loans.
 In this way the interest rate typically used to calculate borrower APRs is thus a very inadequate measure of the effective cost of pawn loans.
 
-\subsection{Measurement of the Cost to Pawning} \label{costs}
+\subsection{Measuring the Cost of Pawning} \label{costs}
 
@@
 Default is defined as losing the pawn.
-Let $P^c$, $P^f$, and $P^i$ the payments to principal, fees, and interest respectively.
-We define financial cost as the sum of payments toward the loan, plus the payment of fees, plus payments to interest, plus the appraised value of the pawn when the borrower falls into default:
+The administrative records show three types of payments made toward recovery of the pawn: payments to principal $P^c$, payments on generated interests $P^i$, and payments on penalty fees $P^f$.
+We define financial cost according to its default status.
+Financial cost for default loans is the sum of all payments, and the lost value of the collateral.
+For recovered loans, financial cost only consists on the sum of interest payments and fees, since payments to principal were allocated to the recovery of the collateral we are not counting it as a cost.
+Hence the formula for financial cost is :
+
 \begin{align*}
-    Financial \; Cost_i =& \underbrace{\sum_t P^c_{it}}_{\text{Payments to capital}} + \underbrace{\sum_t P^f_{it}}_{\text{Payments of fees}}  +\underbrace{\sum_t P^i_{it}}_{\text{Payments to interests}} \\
-    &\quad\qquad + \underbrace{\mathds{1}(Default_i) \times Appraised \: Value_i}_{\text{Cost of losing pawn}}
+    (\text{Financial Cost})_i =&  \underbrace{\sum_t P^f_{it}}_{\text{Payments of fees}}  +\underbrace{\sum_t P^i_{it}}_{\text{Payments to interests}} \\
+    &\quad\qquad + \underbrace{\mathds{1}(\text{Default}_i) \times (\text{Appraised Value}_i}_{\text{Cost of losing pawn}} + \underbrace{\sum_t P^c_{it}}_{\text{Payments to capital}})
 \end{align*}
 
-\noindent $t$ indexes days, and $\mathds{1}(Default_i)$ is an indicator function for defaulting\footnote{This cost is calculated for a time period of 230 days after loan origination.}.
-We also report results using the subjective value of the pawn reported by the borrower in place of the appraised value, and a measure of financial cost that adds the travel expense, since the main treatment involves making clients come to the branch to pay each month.
-
-As a second measure of cost we use the Annual Percentage Rate (APR) of the previous Financial Cost.
-In particular, the APR is defined to be the rate that solves the following amortization equation for a 3 period monthly payment:
+\noindent $t$ indexes days, and $\mathds{1}(\text{Default}_i)$ is an indicator function for defaulting.
+We also report results using the subjective value of the pawn reported by the borrower in place of the appraised value, and a measure of financial costs that adds travel expenses, since the treatment involves making clients come to the branch to pay each month.
+
+As a second measure of cost we convert that Financial Cost outcome from above to an Annual Percentage Rate (APR).
+The APR is defined as\footnote{To keep in spirit with the way we are handling incomplete loans, we just say that the loan duration for those is the time that we did observe, so we are adding up all interest and fees over the whole time that loan (including refinancing) has been observed.} :
 
 \begin{align*}
-    \frac{Financial\;Cost_i}{3} =& Appraised\; Value_i \times \frac{\frac{APR}{100(12)}\left(1+\frac{APR}{100(12)}\right)^3}{\left(1+\frac{APR}{100(12)}\right)^3-1}     
+    (\text{APR})_i =&\left( 1 + \frac{\frac{\text{Financial Cost}_i}{\text{Appraised Value}_i}}{\text{loan duration}}\right)^{\text{loan duration}}-1 
 \end{align*}
@@
 We can use the control group for the study to present summary statistics on these core measures of default and financial cost.
-Figure \ref{fc_pro_2_115} reports results using only the first 115 days.
 Figure \ref{fc_hist}(a) plots a histogram of this financial cost in pesos for loans where the pawn was either recovered or lost, while panel (b) shows the APR.
-It shows that most of the cost comes from clients that do not recover their pawn.
+This shows that most of the costs come from clients that do not recover their pawn.
 %Of those who renew, 83\% lose the pawn.
@@
 The Commitment contract however requires the client to make regular monthly payments for the duration of the contract, with the principal and interest payments split evenly across the three months of the contract (day 30, 60 and 90 after loan disbursement).
-The importance of this monthly payment was reinforced in two ways; first by reminders issued to any borrower delinquent on the monthly payments that they were supposed to be made, and secondly by the levying of a nominal fee (2\% of minimum due) that would be levied on individuals behind in their payments.\footnote{This fee was set by the lender, being deemed to be large enough to reinforce commitment but small enough that if clients had an emergency and could not pay, the fee would not cause the pawn to be unrecoverable.
+The importance of this monthly payment was reinforced in two ways; first by reminders issued to any borrower delinquent on the monthly payments that were supposed to be made, and secondly by the levying of a nominal fee (2\% of minimum due) on individuals who fell behind in their payments.\footnote{This fee was set by the lender, being deemed large enough to reinforce commitment but small enough that if clients had an emergency and could not pay, the fee would not cause the pawn to be unrecoverable.
 In contrast with \cite{John} we don't let the clients choose the size of the fee.
@@
 
-In order to explore lower-cost forms of structure, we also include arms that feature `soft' commitment, asking or requiring individuals to follow the more regular payment structure of the commitment contract but then providing no reminders or repercussions for failing to do so.
+%In order to explore lower-cost forms of structure, we also include arms that feature `soft' commitment, asking or requiring individuals to follow the more regular payment structure of the commitment contract but then providing no reminders or repercussions for failing to do so.
 A substantial literature documents that people are averse to to breaking their promises, and are willing to incur in monetary losses in trying to keep them.
@@
 \vspace{.2in}
-\noindent \textbf{Treatment Arms.} Randomization was done at the branch-day level.
+\noindent \textbf{Treatment Arms.} Treatments were randomized at the branch-day level.
 Each day a computer randomly assigned which types of contracts were on offer that day in the branch, and therefore which contract the client signed.
-We have 5 different experimental arms:
+We have 3 different experimental arms\footnote{The experiment included other arms that involved no fee penalties and did not emphasize the structure of payments.
+These are being analyzed in a separate paper}:
 
@@
     \item \textit{Commitment Choice} arm: consisted of branch-days offering the client \textit{a choice} between the Commitment contract, and the status quo contract.
-    \item \textit{Forced Soft Commitment} arm: consisted of branch-days in which borrowers were asked to sign a non-binding written commitment to pay monthly as in the Commitment contract, but no reminders or fees were imposed if they did not.\footnote{The client was made to sign a paper which said ``I promise to pay every month the corresponding sum of \_\_\_\_\_\_, on the dates \_\_\_\_\_\_, \_\_\_\_\_\_, and \_\_\_\_\_\_.
+    %\item \textit{Forced Soft Commitment} arm: consisted of branch-days in which borrowers were asked to sign a non-binding written commitment to pay monthly as in the Commitment contract, but no reminders or fees were imposed if they did not.\footnote{The client was made to sign a paper which said ``I promise to pay every month the corresponding sum of \_\_\_\_\_\_, on the dates \_\_\_\_\_\_, \_\_\_\_\_\_, and \_\_\_\_\_\_.
 This is \underline{not} a legal document and cannot be used in courts.
@@
 We thank Anett John for pointing this out.}
-    \item \textit{Soft Commitment Choice} arm: consisted of branch-days on which the client was given \textit{a choice} between the Soft Commitment and the status quo contract.
+    %\item \textit{Soft Commitment Choice} arm: consisted of branch-days on which the client was given \textit{a choice} between the Soft Commitment and the status quo contract.
 \end{enumerate}
@@
  Branch personnel did not know which treatment would happen on which day.
-They were told that there were 5 different ``types of contract-days'' and that the system chose randomly which applied on any given date, and that it could happen for instance that two consecutive dates had the same contract.
-They were also told that this way of operating was in place in various Lender P's branches (they did not know which ones), and that it could be in place for several months.
+They were told that there were 3 different ``types of contract-days'' and that the system chose randomly which applied on any given date, and that it could happen for instance that two consecutive dates had the same contract.
+They were also told that this way of operating was in place in several of Lender P's branches (they did not know which ones), and that it would be in place for several months.
 Randomizing at the day level limits the problem of contamination arising from clients realizing that other clients get different contracts than theirs.
-It also limits potential manipulation by appraisers, who in the presence of individual level randomization could potentially pick their preferred costumers from the line or tell them to wait until their desired contract shows up on the screen.
+It also limits potential manipulation by appraisers, who in the presence of individual level randomization could potentially pick their preferred customer from the line or tell them to wait until their desired contract shows up on the screen.
 Intra-branch day correlation on the probability of default (ICC) is small, at {0.08}, so we lose little power vis-a-vis individual-level randomization.
@@
 First, two enumerators were present in each branch for the whole day during the duration of our experiment to explain the contract terms to clients.
-One of the aspects emphasized was that the frequent payment contract involved the commitment to pay \underline{each month} a third of the outstanding amount, and the nature of the reminders and fees associated with the Commitment arm.
+One of the aspects emphasized was that the frequent payment contract involved the commitment to pay a third of the outstanding amount \underline{each month}, and the nature of the reminders and fees associated with the Commitment arm.
 Figure \ref{ExplanatoryMaterial} translates a piece of the materials we used to explain the contracts (in this case a comparison sheet used in the Promise-Choice days to compare contracts terms side to side).
@@
 %The sheet clearly indicates that this contract is a monthly payment one (numeral 1), that there is a penalty of 2\% for paying late (numeral 2), and the 3 payment dates (numeral 3).
-Finally, the bottom of the Figure \ref{PaperSlip} shows the paper slip we used for the promise arms.
+%Finally, the bottom of the Figure \ref{PaperSlip} shows the paper slip we used for the promise arms.
 The clients had to put their name on a slip of paper where they stated they promised to pay monthly.
 
-We are confident the overwhelming majority of clients understood the contracts and made informed choices.
+We are confident the overwhelming majority of clients understood the contracts and that those in the choice arm made informed choices.
 As shown below, different contract terms did generate differential demand and differential behavior.
@@
 
-The administrative data contains a unique identifier for the client, an identifier for the piece she is pawning, and the transactions relating to that piece.
+\todo[inline]{Somewhere in here we need to explain how we handle repeat pawns.
+If I recall correctly, we've settled on including only data for each person's first visit.
+This visit may include multiple pawns, but this is fine since we cluster at the branch-day level.}
+
+The administrative data contains a unique identifier for each client, an identifier for the piece she is pawning, and the transactions relating to that piece.
 In particular, the value of the piece as assessed by the appraiser, the amount of money loaned (70\% of the value), the date of the pawn transaction, and the type of contract for that pawn.
-Within the period of the loan, we followed each transaction related to that piece in the administrative data: when payments were made and for what amounts, whether there was default (i.e.
-the client lost her pawn), and whether any late-payment fees were imposed.
+Within the period of the loan, we followed each transaction related to that piece in the administrative data: when payments were made and for what amounts, whether there was default (i.e.\ the client lost her pawn), and whether any late-payment fees were imposed.
 After the experimental loan, we are able to track subsequent behavior and to see whether that borrower took a subsequent loan.
@@
 Figure \ref{exp_description} shows the design and timing of the experiment, along with the sample sizes in each arm.
-The experiment comprises 13,446 pawns, and our administrative data cover a total of 23,974 pawn
+The experiment comprises 13,446 pawns, and our administrative data cover a total of 23,974 pawns.
 
@@
 It was short to avoid discouraging the potential clients from pawning, but at the same time it aimed to measure the following: demographics, proxies for income/wealth, education, self-control problems/present-biased preferences, experience pawning, if family or friends commonly asked for money, how time consuming and costly it was to come to the branch, the subjective probability of recovering the piece that they intended to pawn, the subjective value of their piece in money terms (how much money they would sell it for), among others.
-We surveyed 10,437 clients, and the survey response rate is 78\%.\footnote{The Appendix \ref{baseline_survey} transcribes the questionnaire in English.} %\footnote{We also surveyed clients before and after the experiment, so our survey covers a larger sample that we are not using in this paper.}.
+We surveyed 10,437 clients, and the survey response rate was 78\%.\footnote{The Appendix \ref{baseline_survey} transcribes the questionnaire in English.} %\footnote{We also surveyed clients before and after the experiment, so our survey covers a larger sample that we are not using in this paper.}.
 
@@
 
-The study is subject to two potential forms of attrition.
-The more serious is that clients would change their pawning decisions in response to the treatment arms.
+There are two main channels through which attrition could complicate the interpretation of our results.
+The first, and more serious, is the possibility that clients might change their pawning decisions in response to the treatment arms.
 If this were the case, our study would still recover internally valid estimates of the impacts of the treatment arms for the lender, but would not provide \textit{ceteris paribus} impacts on a comparable pool of individuals.
-We anticipated this possibility and trained appraisers to say --that whatever was the contract that day-- it was the only available contract for an undetermined amount of time.
+We anticipated this possibility and trained appraisers to say that whatever was offered on that day was the only available contract for an undetermined length of time.
 Because we do not observe refusals directly, we address this issue by examining the number of borrowers per day, with specific attention to whether the Forced Commitment arm led to a lower number of borrowers per day.\footnote{Our enumerators informed us that potential clients rarely left the branch without pawning, and that it was even less common that they did so when hearing about monthly installments.
@@
 The data support this story as well.}
+
+Finally, we also tested if the number of pawns per day for the 6 branches that participated in the experiment was different 1 month before the experiment started or 1 month after the experiment ended, relative to the days the experiment was active.
+To this end we estimated the regression\footnote{We cluster the standard errors by branch.} $Pawns \: per \: day_{jt} = \alpha_j + \gamma f(t) + \beta_b \mathbbm{1}(t \in MB)_{t} +\beta_a \mathbbm{1}(t \in MA)_{t}$, where $\alpha_j$ are branch fixed effects, $f(t)$ is a third degree polynomial in time, $\beta_b$ measures a level effect in the number of pawns per branch a month before the experiment started, and $\beta_a$ a month after.
+We estimate no difference in the number of pawns, showing that people are not leaving the branch without pawning at larger rates during the experiment ($\beta_a=1.32$, $\beta_b=-0.65$, with p-values 0.11 and 0.83, respectively).
+Table \ref{num_pawns_bal} shows the beta coefficients from these regressions, which are nowhere significant.
 
@@
 
-Finally, we also tested if the number of pawns per day for the 6 branches that participated in the experiment was different 1 month before the experiment started or 1 month after the experiment ended, relative to the days the experiment was active.
-To this end we estimated the regression\footnote{We cluster the standard errors by branch.} $Pawns \: per \: day_{jt} = \alpha_j + \gamma f(t) + \beta_b \mathbbm{1}(t \in MB)_{t} +\beta_a \mathbbm{1}(t \in MA)_{t}$, where $\alpha_j$ are branch fixed effects, $f(t)$ is a third degree polynomial in time, $\beta_b$ measures a level effect in the number of pawns per branch a month before the experiment started, and $\beta_a$ a month after.
-We estimate no difference in the number of pawns, showing that people are not leaving the branch without pawning at larger rates during the experiment ($\beta_a=1.32$, $\beta_b=-0.65$, with p-values 0.11 and 0.83, respectively).
-Table \ref{num_pawns_bal} shows the beta coefficients from these regressions, which are nowhere significant.
 Hence we begin the analysis confident that differential attrition has not occurred.
@@
 
-\section{Experimental Analysis} \label{experiment}
-
-\subsection{Forced versus Chosen Commitment} \label{forced_vs_choice}
-
-The comparison of the Commitment Choice arm to the Control arm provides the test of self-selection that is standard in the behavioral literature.
-A lack of impact in this comparison would be consistent either with a population of neo-classical borrowers, for whom the commitment feature is superfluous, or with a population of time-inconsistent borrowers who lack sophistication over their own behavioral problems and so do not choose commitment even though they would benefit from it.
-The keys to distinguishing these two stories is the treatment effect of commitment on those who would not choose it; this counterfactual is revealed through the additional impact of the Forced Commitment arm over the Choice arm.
-So while the forcing of commitment cuts against the grain of a behavioral literature that has largely promoted `nudges', it reveals important additional information that may be particularly relevant in borrower populations that are both hyperbolic and naive.
-
-In the Choice arm, only 11\% of individuals offered the product selected it.
-This is initial evidence either that we are dealing with a population of largely time consistent individuals who do not need commitment, or of a population with many naive individuals who do not know that they need it.
-If this self-selection mechanism works perfectly (as it would in a Roy model with all hyperbolics sophisticated) then the Forced and Choice arms will have an identical effect.
-Deviations between the impacts of these two arms therefore are implicitly a test of the optimality of the choices made in the choice arm.
-
-We pose these comparative questions using the standard pooled experimental equation (\ref{basic_reg}):
-
+%\section{Experimental Analysis} \label{experiment}
+\section{Average Treatment Effects} \label{experiment}
+
+\todo[inline]{We should add some discussion here about the take-up rate of commitment here.
+Need to think more carefully about how to do it.
+Don't want to get too bogged down and start talking about why people are choosing at this point in the paper.}
+
+%\subsection{Average Treatment Effects}
+
+\paragraph{Specification.} Table \ref{main_impact_table} presents estimates and standard errors from a standard pooled experimental regression 
 \begin{equation} \label{basic_reg}
@@
 \end{equation}
-
-\noindent where $i$ refers to client, $j$ indexes branch, $T_{i}^F$ and $T_{i}^C$ are indicator variables for receiving the Forced or Choice arms, $X_{ij}$ are branch and day-of-week fixed effects.\footnote{There is a minority of of clients that pawned again and got assigned a different treatment.
-Results are robust to excluding them, or to using only the first treatment status assigned, as we show later.
-In the main regressions we include them and add a dummy indicating clients who has more than one treatment in the experimental period.} We cluster errors at the branch-day level, the unit of treatment assignment.
-%\footnote{If we restrict ourselves to pieces that fall in a single-arm (64\%), then treatment reduces the financial cost by 5.7\%, increases the likelihood of recovering their pawn by 35\%, and increases the likelihood of repeat business by 66\%.}.
-Our main outcome variables $y_{ij}$ are measures of financial cost in pesos as defined in Section \ref{costs}, which we further decompose into its component costs:  payments to capital, fees, interest, and the cost of losing the pawn.
-We then examine an indicator variable for client $i$ losing her pawn.
-Next we cast each of the cost drivers as an effective Annual Percentage Rate (APR), including the costs of lost collateral under default as a component of the overall APR of pawn borrowing.
-$\beta^F$ estimates the Average Treatment Effect of the Forced arm (since compliance is 100\%), and  $\beta^C$ the Intention to Treat of the Choice arm (since it is not).
-
-%Defenders of choice make another subtler point: that even if take up of the commitment-fee contract is low, the sole fact of \textit{having} choice could potentially change behavior or welfare (\cite{Dalboetal:2010}, \cite{Sjostrometal:2018}, \cite{Tlaxcala}).
-
-%In spite of broadly distributed benefits of the Forced Commitment commitment contract we documented above, 90\% of clients chose \textit{not} to have it, preferring the status-quo contract.
-As explained above we are fairly confident this was not because a lack of understanding of the contracts.
-
-%\vspace{.1in}
-%\noindent What can explain this low demand?
-In the spirit of \cite{Blumenstock} we try to differentiate between explanations.
-One explanation could be risk.
-Even if the fee forcing contract generates cost savings on average, clients with risk averse preferences may not demand it if they perceive higher risk from it.
-Alternatively, even risk-neutral agents may not demand it if the cost of lost flexibility is high or if they have high temporal discount rates and prefer to pay later.
-%If clients, for instance, face large and frequent income shocks which make it hard to repay monthly.\footnote{We don't observe income shocks in our data, making is hard to quantify how important they are.
-91\% of those in the Forced Commitment arm incurred a fee, which suggests that shocks are not uncommon.}
-%Although the evidence that follows undermines several explanations, the tests we can conduct given the data are not sharp enough to leave a single explanation standing.
-Section \ref{model} lays our a simple theory (namely present bias with partial naivete) which fits all the 6 main findings of the paper.
-Given its parsimony and explanatory power, we submit that it is the most suitable explanation for our results.
-
-%Following two  paragraphs moved from old 'behavioral' choice section towards end of paper
-%\vspace{.2in}
-%\subsection{The effect of choice on pawn recovery and financial cost} \label{effect_choice}
-
-The core results, presented in Table \ref{main_impact_table} and Figure \ref{main_te}, are extremely stark.
-The Choice arm fails to deliver significant changes in any measure (with the exception of an increase in fees, for which we are highly powered since this outcome is zero by definition in the control).
-In sharp contrast, the Forced Commitment arm yields strongly significant decreases in the financial cost of loans to clients.
-Despite causing an increase in payments to capital and fees, the Forced arm leads to a sharp decrease in overall costs of borrowing, driven by a 12 percentage point decrease in the probability of default (more than a 25\% reduction off a base of 44\% default).
-The bottom panel of the figure casts these costs as APRs, and shows that while the Choice arm actually leads to a slight \textit{increase} in the APR, the Forced arm decreases the effective annualized interest cost of pawn lending by 40 percentage points.
-A credit product that has an effective average APR of 249\% in the status quo arm (inclusive of default) is reduced to a cost of 209\% through the imposition of a more regularized payment structure.
-
-Table \ref{main_impact_table} decomposes the savings from the Forced and Choice arms into their component parts.
-The Forced arm increases fees very significantly relative to a control mean of 0, but the monetary value of the fees imposed is small (28 pesos).
-Payments towards capital also rise by 167 pesos because the arm is so effective at improving the fraction of individuals actually repaying their loans.
+where $i$ indexes client, $j$ indexes branch, $T_{i}^F$ and $T_{i}^C$ are indicator variables for receiving the Forced or Choice arms, $X_{ij}$ are branch and day-of-week fixed effects.
+Standard errors are clustered at the branch-day level, the unit of treatment assignment\footnote{A minority of clients pawned on more than one day during the experiment.
+To avoid contamination from earlier treatments to which these individuals were exposed, we restrict our sample to each client's \emph{first visit}.
+Note that a client may pawn multiple items her first visit.
+We include these as separate observations.
+Because our standard errors are clustered at the branch-day level, they automatically account for any dependence in error terms arising from multiple pawns by the same client on her first visit.}.
+The coefficients $\beta^F$ and $\beta^C$ are the ATEs of the forced commitment and choice treatments, respectively, on the outcome variable $y_{ij}$.\footnote{Note that $\beta^C$ can be viewed in two ways: as the the ATE of \emph{offering clients a choice} between the status quo and commitment contract or as the intent-to-treat effect of the commitment contract \emph{itself}.
+Here we adopt the former interpretation; below we use the latter to consider the relevance of selection-on-gains.}
+Our two primary outcome variables are financial cost in pesos and Annual Percentage Rate (APR), as defined in Section \ref{costs}. 
+Results for these outcomes appear in columns (1) and (6) of Table \ref{main_impact_table}.
+The remaining columns decompose the financial cost and APR outcomes into their components: payments to capital, fees, interest, and the cost of losing the pawn. 
+Columns (2)--(5) correspond to financial cost while columns (7)--(10) correspond to APR.
+
+\todo[inline]{Add a column with losing pawn. What about re-pawning?}
+
+\todo[inline]{How did we decide to deal with censoring?}
+
+\paragraph{Results.} The results are extremely stark.
+The Forced Commitment arm yields large and significant decreases in the cost of loans to clients, as measured either by financial cost or APR. 
+Despite causing an increase in payments to capital and fees, the Forced arm leads to a sharp decrease in overall costs of borrowing, driven by a XX percentage point decrease in the probability of default (more than a XX\% reduction from a baseline of XX\% default).
+A credit product that has an effective average APR of XXX\% in the status quo arm (inclusive of default) is reduced to a cost of XXX\% through the imposition of a more regularized payment structure.  
+While the Forced arm increases fees significantly relative to a control mean of 0, the monetary value of the fees imposed is small (28 pesos).  
+Payments towards capital also rise by XXX pesos because the arm is so effective at improving the fraction of individuals actually repaying their loans.  
 Because the regular repayment structure moves the timing of payment forward it saves borrowers an average of 109 pesos in interest costs.  
-The very large majority of the overall treatment effect, however, stems from the 492 pesos in retained collateral value induced by the falling probability of default.
-
-Figure \ref{main_te} represents the  effect sizes (in standard deviations) of the two main study arms for three outcomes:  default, the financial cost of the loan, and the effective interest rate paid to acquire the borrowed capital.
-The Forced arm is significant for all three outcomes, with very substantial treatment effects in magnitudes for default and APR, and the commitment arm is never significant.\footnote{The slight increase in APR for the Choice arm seen in this picture arises from the fact that the APR calculation has the arm-specific loan size in the denominator, and the loans in the Choice arm turn out to be slightly smaller (although statistically equal) on average than the Control.}    In other words, voluntary commitment is ineffective but the use of forced commitment saves the average borrower an amount of money almost twice the APR of a normal US credit card loan.
-
-Other intermediate outcomes are impacted by assignment to frequent payments.
-Table \ref{mechanisms} shows that the first payment happens 8 days earlier in the Forced Commitment arm than in status quo (column 1), and that the number of payments increases by 0.19 (column 4).
-Treatment effects are concentrated on the intensive margin, as treatment does \textit{not} affect the fraction of clients who pay nothing (column 12).
-The percentage of the loan paid increases by 9 percentage points on average (column 9).
-Moreover, the percentage of the loan paid is even smaller for those that end up losing the pawn (first row of column 9).
-This last point is critical; this intervention has the potential to do financial harm if it caused individuals to increase fruitless payments on loans for which they would end up defaulting.
-This result shows that the Forced arm drives individuals who would otherwise have made partial payment and defaulted to instead recover their pawn.
-
-Can subjective perceptions of the loan, such as perceived collateral value, discounting, or the opportunity cost of time, rationalize these results?
-Figure \ref{robustness_fc} shows the results of these robustness checks, and the numbers underlying the figure are shown in Table \ref{table_robustness_fc}.
-First, rather than using the appraised value of the pawn from the lender, we can assess costs using the subjective value of the pawn reported by the borrower.
-Because borrower valuations are both larger on average and much more variable, this adjustment causes the average impact on financial cost to rise, and the impact on APR in standard deviations to shrink, but both remain significant.
-Second, because the Commitment contract requires more frequent visits to the branch, there are travel costs incurred relative to the status quo payment structure that we can include in the costs of commitment.
-For each visit we add the self-reported transport cost (or the mean if we are missing this from the individual survey) plus a whole day's wage, multiplied by the number of additional visits from Table \ref{mechanisms}.
-Adding a whole day's wage may exaggerate cost, but we still observe a reduction of this more comprehensive measure of cost caused by the frequent payment contract.
-Finally, we can adjust for the fact that the early payment induced by the commitment contract actually reduces the effective liquidity received by borrowers.
-Taking the interest rate as the opportunity cost of capital, the interest payments averted are not really `saved' given that the liquidity is itself foregone.
-So our final adjustment removes the saved interest payments from the calculation of the benefits across arms.
-The figure shows the effects of each of these adjustments on the estimate of financial cost and APR, and illustrates that even when we make all of these adjustment simultaneously the Forced arm generates benefits of 0.11 standard deviations, significant at the 95\% level.
-Hence forcing individuals into commitment generates benefit even when we incorporate multiple subjective dimensions of the loan.
-
-Another way to push the analysis towards a consideration of borrower welfare is the conjecture that if clients exposed to the installment contract like it, they will be more likely to come back vis-a-vis those that got status quo contract.\footnote{\cite{Laibson2018} hypothesizes that consumers use ``experienced utility'' as a guide to make future purchases in this way.} This is indeed what we find in the data.
+The vast majority of the overall treatment effect, however, stems from the XXX pesos from not losing the pawn. 
+In contrast, the Choice arm fails to deliver significant changes in any measure, with the exception of an increase in fees, for which we are highly powered since this outcome is zero for every control observation.
+
+\paragraph{Intermediate outcomes.} To shed light on the mechanisms behind the ATEs discussed above, Table \ref{mechanisms} shows how treatment affects a number of intermediate outcomes. 
+Column (1) shows that borrowers' first payment occurs 8 days earlier on average in the Forced Commitment arm than under the status quo.
+Column 4 shows that the number of payments increases by 0.19.
+Treatment effects are concentrated on the intensive margin, as treatment does \emph{not} affect the fraction of clients who fail to make any payments (Column 12). 
+The percentage of the loan paid increases by 9 percentage points on average (Column 9). 
+Moreover, the percentage of the loan paid is even smaller for those who end up losing the pawn (first row of column 9). 
+This last point is critical. 
+Forced commitment could be financially harmful if it caused individuals to make fruitless payments on loans for which they later defaulted. 
+In contrast, we find that forced commitment causes individuals who would otherwise have made partial payments but ultimately defaulted to instead recover their pawn.
+
+\todo[inline]{We need to add a bit of lead-in here to make clear why we're going all these robustness exercises.
+Basically we're trying to foreclose possible explanations for why the treatment could be harmful.
+We should say something here like ``when we say mistake below, what we mean by this is X and we're going to show you right now that explanations A, B, and C are not operative here.''}
+
+\paragraph{Robustness.} We have shown that forcing borrowers to take the monthly payment contract significantly reduced financial cost.
+Although the paper focuses on financial cost, here we consider two additions to the cost and benefit calculation.
+We include the cost of going to the branch, and we consider the value of the pawn as perceived by the borrower instead of its gold value.
+
+Columns (1) and (6) replicate our previous results for comparability.
+Columns (2) and (7) of Table \ref{table_robustness_fc} use the subjective value of the pawn reported by the borrower rather than its appraised value.
+Columns (3) and (8) adjust for self-reported transport costs from the individual survey plus an entire day's wage, multiplied by the number of individual \hl{additional} visits\footnote{For clients who did not complete the individual survey, we adjust using the mean self-reported transport cost among respondents.}.
+Although adding a whole day's wage almost certainly exaggerates the travel costs associated with commitment contracts, we still find that forced commitment reduces both financial costs and APR. 
+Columns (4) and (9) adjust for both travel costs and use the subjective rather than appraised value of the pawn.
+Finally, columns (5) and (10) remove saved interest payments from the calculation of the benefits.
+The rationale is that forcing borrowers to pay earlier reduces their  liquidity, and they may need to borrow.
+We assume they borrow at the same interest rate.
+Thus considering other loans, they may not be paying less interest.
+The exercises in Table \ref{table_robustness_fc} show that results are quite robust to the inclusion and exclusion of components of benefits and costs.
+
+%Figure \label{fc_discount_rates} shows the effects of each of these adjustments on the estimate of financial cost and APR, and illustrates that even when we make all of these adjustment simultaneously the Forced arm generates benefits of 0.11 standard deviations, significant at the 95\% level.
+Forced commitment lowers financial costs even when we incorporate multiple subjective dimensions of the loan.
+
+\todo[inline]{``fully adjusted'' in the table removes interest payments from the cost measure.
+Not totally clear what this exercise tells us.
+Overall, the point of the table is to remove alternative explanations one-by-one.
+(I added a paragraph now to make this clearer, ES)}
+
+\todo[inline]{I think the re-pawn table should only have 4 columns.
+Remove variables 3,4, and 7.
+In terms of the order: keep column 1, make 5 and 6  the new columns 2 and 3, and make the current column 2 the new column 4.
+I am goint to write the paragraphs assuming this.}
+
+\paragraph{Repeat Pawns.}
+%Another way to push the analysis towards a consideration of borrower welfare is the conjecture that if clients exposed to the installment contract like it, they will be more likely to come back vis-a-vis those that got status quo contract.\footnote{\cite{Laibson2018} hypothesizes that consumers use ``experienced utility'' as a guide to make future purchases in this way.} This is indeed what we find in the data.
 We consider this outcome in Table \ref{repeat_loans}.
 We can first ask whether the individual ever takes a loan after the initial study loan, an analysis which is simply experimental.
-The results show that the Choice arm is no more likely to pawn again, which the Forced arm is 6\% more likely to take a second loan.
-While this appears to be \textit{prima facie} evidence of greater satisfaction with the lender, interpretation here is complicated by the fact that they were more likely to have recovered their pawn and hence to be able to pawn it again.
+Table \ref{repeat_loans} explores the effects of treatment on future pawning behavior.
+Column (1) shows that participants assigned to the the forced arm are 6.7\% more likely to be repeat clients.
+Those in the choice arm are 4\% more likely to pawn again and is not statistically distinct from zero.
+While this appears to be \emph{prima facie} evidence of greater satisfaction, the interpretation is complicated by the fact that monthly payments may themselves trigger more borrowing to pay them.
+This is unlikely to be the case given that the effect on re-pawning comes after 90 days (during the period of contract demanded payments) and not before  (see columns 2 and 3).
+Column 4 focuses on the (endogenous) subsample of those recovering their pawn in both arms of the experiment.
+This means that both have the pawn to re-pawn and also that the liquidity demands from the monthly contract are not longer binding as the contract has been terminated.
+Twice as many choose to pawn again in the commitment contract (column 4).
+
+%clients assigned to the forced commitment arm were more likely to recover their pawn, allowing them to re-pawn the same item in the future.
 We can explore this possibility in a number of ways.
 First, we can (endogenously) split the sample according to whether the individual defaulted on the experimental loan; here we find that the increase in subsequent borrowing is restricted to those who repaid the first one.
-Then, we can examine whether the probability that they take another loan using different collateral from the first, and while not significant we find that the Forced arm elevates the probability of re-pawning with new collateral.
-We can also separately examine the likelihood to take a new loan after the contract period of the original experimental loan (column 5) or after it (column 6) and we find that the increase in subsequent pawning is coming afterwards, significantly increasing the time to the subsequent loan (column 7).
-
-\textcolor{red}{Figure \ref{prob_ever_pawn} provides a visual take on the probability of re-pawning as a function of original treatment status.}
-
-%Although we have shown that Forced Commitment reduces financial cost and increases pawn recovery, this does not imply that welfare increases.
-Clients could have disutility from the stress of having monthly installments for instance.
-%We don't need to make the strong claim of welfare for the purposes of this paper. The financing cost results are striking enough. But we
-
-%The panel labeled Forced Commitment in Figure \ref{reincidence} presents results of estimating equation (\ref{basic_reg}) with the dependent variable being a dummy for the client being a repeat customer.
-We define a client as a repeat customer if, after experiencing at least 75 days of the respective treatment arm, she came back and pawned a \textit{different} piece.\footnote{Results are robust to using number of days experiencing the contract larger than 75.
-We know it is a different piece from it having a different weight/value.}  The leftmost coefficient shows that the causal effect of the Forced Commitment contract on repeat pawning is an increase of 5 percentage points in the probability of being a repeat customer, this is twice the repeat purchasing happening in the status quo group.
-This effect is not explained by clients recovering their first pawn with higher probability in the Forced Commitment contract and re-pawning this same one since we make sure it is another piece; besides only 16\% recover their piece in the fist 75 days in the fee forcing contract.
-Experience with the frequent payment contract seems to be necessary as there is no effect of the monthly payment contract on repeat pawning in the first 30 or 60 days of the contract (see Figure \ref{reincidence_before} in the Appendix).
-
-%\hl{The second coefficient from the left focuses on the subsample who are predicted would have a treatment effect on financial cost savings above the median} treatment effect in their first pawn.\footnote{Since this is predicted using \cite{atheygrf} based on pre-determined covariates for treatment and control clients it is valid to split the sample this way.} It shows that for these clients the likelihood of coming back is twice as large.
-That is, those that benefit more from the Forced Commitment contract are more likely to repeat compare to their control group.
-The remaining coefficients of the ``Forced Commitment'' panel condition on endogenous outcomes and should be interpreted with care.
-The \hl{third} coefficient from the left restricts the sample to those that had not recovered their pawn in the first 75 days in both groups and finds similar results.
-The \hl{fourth} coefficient conditions on clients who recovered their pawn of the experiment, again on in both arms.
-Results from these two endogenous samples are similar to those for the whole sample.
-
-%The fourth coefficient \footnote{The second and third estimate must be interpreted with care as we are conditioning on a variable that may be affected by treatment.
-We view these 2 coefficients as suggestive correlations only.
-The fourth coefficient does not have that problem as it conditions on clients that by their pre-determined covariates are predicted to have above the median treatment effects (in both arms).}
-
-%The coefficient on repeat pawning is just as big when we focus only 2nd pawns happening after the first was recovered (third coefficient ``fnr'').
-This is consistent with \cite{Laibson2018}'s conjecture that clients could be making decisions based on experienced utility.\footnote{The third coefficient conditions on the subsample that did recover their first pawn in both arms and finds a coefficient of 4pp.
-This is not a causal estimate as recovery is influenced by treatment, but we found it telling that the differences were similar to the causal estimate for the full sample.}
-
+Next, we can examine whether the probability that participants take another loan using \emph{different} collateral from the first.
+While the difference is not statistically significant, we find that the Forced arm elevates the probability of re-pawning with new collateral.
+We can also separately examine the probability of taking a new loan after the contract period of the original experimental loan (column 5) or before it (column 6).
+Here we find that the increase in subsequent pawning comes \emph{later}, significantly increasing the time to the subsequent loan (column 7).
 All of this evidence suggests that the effect on subsequent demand is `real' and not an artifact of improved retention of the collateral, consistent with \cite{Alcohol}'s conjecture that demand for commitment increases with experience with it.
@@
 
-An additional empirical issue generated by repeat pawning is the question of how to handle the treatment status of those who take multiple loans within the experiment.
+%An additional empirical issue generated by repeat pawning is the question of how to handle the treatment status of those who take multiple loans within the experiment.
 38\% of borrowers take more than one loan within the study period, and 19\% are assigned multiple treatment statuses on their different loans.
@@
 
-\subsection{Soft Commitment}
-
-We now turn to the impact of the two arms that featured forms of `soft' commitment.  These results further reinforce the centrality of externally imposed commitment. 
-Demand for the Soft Commitment contract  is higher than for the Forced Commitment contract by a factor of three: {31}\% of clients offered a choice between the status quo contract and the Soft Commitment contract chose commitment.
-%Interestingly, the set of people who demand the Soft Commitment contract are different from those that demanded the Forced Commitment one.
-While in both cases the economically vulnerable demand less, in the case of the Soft Commitment those that we classify as present biased, those that report that they frequently fall into temptation buying, and those that ask for reminders of payment are \textit{less} likely to demand the Soft Commitment contract.
-This suggests that those taking up the promise commitment are not the ones needing the commitment (see Figure \ref{interactions_takeup} in the Appendix).
-Nonetheless, we find Soft Commitment, whether chosen or induced, to be completely ineffective in this environment.
-Table \ref{impact_soft} and  Figure \ref{effect_promises} finds that assigning clients to the choice-promise condition has a zero effect on financial cost, recovery, and the effective APR on average (Panel (a)), or on any sub-component of cost (Panel (b), and Tables \ref{table_robustness_fc_soft} and \ref{mechanisms_soft}).
-These results contrast sharply with the (lower-stakes, more short-term) evidence in laboratory experiments where promises have large effects on behavior.
-While clients are more enthusiastic about the Soft Commitment contract than the Forced Commitment one in the sense of tripling take-up, the promise contract provides no commitment.
-Results for the promise arms are consistent with \cite{Ted} and \cite{John} who find that people are likely to demand commitment when the commitment is too weak to have beneficial effects.
-In short, not only is chosen hard commitment ineffective, but both forced and chosen soft commitment similarly fail to improve outcomes.
-Only an externally imposed commitment product with reminders, imposed on people who would not have chosen it, decreases costs to borrowers.
-
-%We see no difference even for the endogenous group that \textit{chose} to promise.
-This null effect happens not only on average, but also by percentiles (Figure \ref{qreg_chooser_nonchooser}, panels (c) \& (d)).
-% There is also no effect on pawn recovery on (first coefficient in Figure \ref{fc_pro5}(b)), even for those that themselves choose to promise.
-And the null effect carries over if we use the definition of recovery in less than 120 days, or for the (endogenous) subgroups that paid a positive amount.
-Finally, there is no effect on repeat pawning (Figure \ref{reincidence}).
-
-%Giving choice of whether to promise or not has the advantage of making promising an active decision by the client.
-In most of the the experimental literature promising is voluntary.
-But it has the disadvantage that we cannot measure the causal effect of promising, since those that promise are a selected sample.
-To evaluate the causal effect of promising, we compare people allocated to the promise-forcing arm (were all clients were forced to make a promise) against those in the status quo contract arm.
-Figure \ref{fc_pro5} (c) and (d) show the results.
-It documents null average treatment effects for both financial cost and recovering the pawn.
-Also there is no effect on repeat pawning.
-
-%\vspace{.2in}
-%\noindent \textit{Size of ``mistakes''.} Although promises have very muted effects, there is some heterogeneity (see Figure \ref{heterogeneous_te_3}).
-This opens the space for choice mistakes.
-Figure \ref{choose_wrong} shows that indeed there are some mistakes, but these are smaller that for the Commitment Choice arm.
-When $z=0$, we calculate that about 60\% of clients in the promise-choice group chose contracts that induced \textit{higher} financial cost.
-In particular gr{97\%} of those that chose the status-quo contract would have been better in the Soft Commitment contract, while gr{3\%} of those who chose the Soft Commitment contract would have been better in the status-quo one.
-On average they spend \$250 pesos on extra financing cost.
-
-\section{Exploring the Importance of Paternalism}
-\label{exploring}
-
-\todo[inline]{Issac: At different points in the paper we use different conventions for whether a positive treatment effect is ``good'' or ``bad.'' We should pick one and stick with it through to avoid confusion.
-(E.g.
-ToT/TuT tables treat positive as good but figure 15 treats negative as good.)}
-
-\todo[inline]{Think more carefully about the ``mistake'' wording here.
-There's a difference between an ex-ante mistake and an ex-post mistake.
-Need to think more carefully about this.
-This also relates to the question about what information to use in the first machine learning exercise.
-I think if we use the $\text{ATE}(X)$ that's closer to an ex ante measure than if we use, say, $\mathbbm{E}[Y_1|X] - Y_0$.}
-
-This is not the first paper to find low demand for commitment, however it is the first we know of that can compare choice versus forcing with a money-metric outcome such as loan repayment.
-As discussed above, a policy of forced commitment substantially lowers financial costs on average, both compared to a baseline no-commitment contract and a policy in which borrowers are free to choose their preferred contract.
-In spite of this, only 11\% of those in the choice arm choose commitment.
-In a world of heterogeneous treatment effects, this could nevertheless be consistent with individual rationality.
-So do the the other 89\% know something about their personal situations that we as researchers do not, or are most people in the choice arm making a costly mistake?
-We now present a range of econometric exercises that shed light on this question.
-Taken together, they cast considerable doubt on the notion of ``selection on gains,'' as embodied in the traditional Roy model.
+\section{Choice and Heterogeneous Treatment Effects}
+\label{sec:choice}
+
+The results from Section \ref{experiment} show that commitment \emph{works}: clients who were assigned to the forced commitment arm experienced substantially lower financial costs on average.
+In spite of this, given the opportunity, only 11\% of borrowers chose commitment. 
+If the effect of commitment were homogeneous, this would be enough to conclude that the \hl{89\%} who did not choose it would have been financially better-off if they had.
+In a world of heterogeneous treatment effects, however, low demand for commitment could still be consistent with individual rationality. 
+Following the methodology of \cite{chernozhukov2018generic} we test and reject the null hypothesis of homogeneous treatment effects \hl{P-value = XXX}.\footnote{See Appendix \hl{???} for details.} 
+Indeed, the effect of commitment varies considerably across individuals. 
+So do the 89\% who do not choose commitment know something about their personal situations that we as researchers do not, or are most people in the choice arm making a costly mistake? 
+We now present a range of econometric exercises that shed light on this question, leveraging unique features of our experimental design. 
+%Taken together, they cast considerable doubt on the notion of ``selection on gains,'' as embodied in the traditional Roy model. 
 While we find evidence of substantial treatment effect heterogeneity, most borrowers would experience lower financial costs under a commitment contract. 
-Indeed, leveraging a unique feature of our experimental design, we show that the average effect of commitment for the \emph{untreated}, those who would not voluntarily choose commitment, is large and negative.
-In an important sense the ``wrong'' people are choosing commitment.
+Among other results, we show that the average effect of commitment for the \emph{untreated}, those who would not voluntarily choose commitment, is large and negative. 
+%In an important sense the ``wrong'' people are choosing commitment.
 
 \subsection{Potential Outcomes and Exclusion}
-
-To interpret our evidence on the importance of paternalism presented below, it is important to be precise about the potential outcomes in our empirical setting.
-This requires introducing some notation.
+\label{sec:potentialOutcomes}
+
+To understand the relationship between choice and heterogeneous treatment effects, it is important to be precise about the potential outcomes in our empirical setting.
 Let $Z_i \in \{0, 1, 2\}$ denote the treatment arm to which to participant $i$ was assigned: $Z_i = 0$ denotes the forced no-commitment arm, $Z_i = 1$ denotes the forced commitment arm, and $Z_i = 2$ denotes the choice arm.
@@
 Under this assumption, a fully general model for the potential outcomes in our experiment would take the form $Y_i(d, z)$ for $d\in \{0,1\}$ and $z \in \{0, 1, 2\}$, allowing participant $i$'s potential outcome to depend \emph{both} on the treatment she actually receives, $D_i$, and the experimental arm to which she is assigned, $Z_i$.
-This model is too general, however, to allow us to explore the importance of paternalism.
+This model is too general, however, to identify meaningful causal effects. 
 Accordingly, we impose the following standard exclusion restriction:
@@
 \eqref{eq:exclusion} says that each participant's potential outcome is the same regardless of whether she \emph{chooses} a particular treatment $D=d$ or is \emph{assigned} the same treatment.
-Viewing $Z_i$ as an instrumental variable (IV) for the treatment $D_i$, this nothing more than the usual IV exclusion restriction.\footnote{\cite{chamberlain2011bayesian} uses an identical assumption to develop a theory of optimal treatment choice for an individual who has access to data from an RCT.} \eqref{eq:exclusion} is plausible in our empirical setting and has testable implications that we fail to reject: see Appendix \todo{Fill in}{???} for details.
+Viewing $Z_i$ as an instrumental variable (IV) for the treatment $D_i$, this nothing more than the usual IV exclusion restriction.\footnote{\cite{chamberlain2011bayesian} uses an identical assumption to develop a theory of optimal treatment choice for an individual who has access to data from an RCT.} \eqref{eq:exclusion} is plausible in our empirical setting and has testable implications that we fail to reject: see Appendix \hl{???} for details.
 Under \eqref{eq:exclusion}, each participant's observed outcome $Y_i$ is related to her potential outcomes $(Y_{i0}, Y_{i1})$ according to
-\todo[inline]{Issac: add a section \ref{bound_tot_tut_appendix} to the appendix and drop in the results for the Huber \& Mellace stuff; Frank: follow-up and draft that section of the appendix.}
+%\todo[inline]{Issac: add a section \ref{bound_tot_tut_appendix} to the appendix and drop in the results for the Huber \& Mellace stuff; Frank: follow-up and draft that section of the appendix.}
 \begin{equation}
@@
 Because $Z_i$ is assigned independently of pre-treatment covariates $X_i$, our design also identifies the corresponding \emph{conditional} distributions of $Y_{i0}$ and $Y_{i1}$ given $X_i$. 
-These distributions are the ingredients that we use below to explore the importance of paternalism.
+%These distributions are the ingredients that we use below to explore the importance of paternalism.
 
@@
 
-\subsection{Treatment Effect Heterogeneity}
-\todo[inline]{There's a connection between homogeneous treatment effects and predictability. In a homogeneous world, the treatment effect is perfectly predictable from the ATE.}
-
-If the effect of commitment were homogeneous, there would be nothing more to say on the topic of paternalism.
-Our estimates of $\mathbbm{E}(Y_{i1} - Y_{i0}) = \mathbbm{E}(Y_i|Z_i=1) - \mathbbm{E}(Y_i|Z_i=0)$ presented above are large and statistically significant.
-If $\Delta_i \equiv Y_{i1} - Y_{i0}$ were constant across $i$, this would be enough to conclude that the 89\% who do not choose commitment would have been better off if they had.
-As we now show, however, the effect of commitment varies considerably across individuals.
-Our approach relies on the following simple observation: if $\Delta_i$ is constant across $i$ then we must have
-\[
-\text{ATE}(X_i) \equiv \mathbbm{E}[\Delta_i |X_i] = \mathbbm{E}[\Delta_i] \equiv \text{ATE}
-\]
-for any covariates $X_i$ that vary across $i$.
-If, on the other hand, $\text{ATE}(X_i)$ can be predicted using some scalar function $\tau(\cdot)$ of $X_i$, then the average treatment effect function is not constant so there must be treatment effect heterogeneity.
-
-We operationalize this idea using a two-step approach proposed by \cite{chernozhukov2018generic}.
-We begin by randomly dividing the participants in the forced arms of the experiment ($Z_i \neq 2$) into two groups: a ``training set'' and a \todo{80/20 split?}{``test set.''} In the first step, we apply random forests to the training set to estimate two proxy predictors: $\psi(\cdot|\text{Training})$ approximates the untreated potential outcome function, $\mathbbm{E}[Y_{i0}|X_i] = \mathbbm{E}[Y_i|Z_i=0,X_i]$, while  $\tau(\cdot|\text{Training})$, approximates the average treatment effect function
-\[
-\text{ATE}(X_i) = \mathbbm{E}[Y_i|Z_i=1,X_i] - \mathbbm{E}[Y_i|Z_i=0, X_i].
-\]
-The proxy predictors need not be unbiased or even consistent estimators of the functions they aim to approximate: the goal of this exercise is merely to find a scalar function of $X_i$ that \emph{accurately predicts} $\text{ATE}(X_i)$.
-
-In the second step we fit a linear regression model to data from the training set using regressors constructed from the proxy functions $\psi(\cdot|\text{Training})$ and $\tau(\cdot|\text{Training})$ constructed in the first step.
-In particular, we estimate
-\begin{equation}
-Y_i = \alpha_0 + \alpha_1 \psi_i + \beta_1 (Z_i - \mathbbm{E}[Z_i]) + \beta_2 (Z_i - \mathbbm{E}[Z_i])(\tau_i - \mathbbm{E}[\tau_i]) + \epsilon_i
-\label{eq:chernreg}
-\end{equation}
-where $\psi_i \equiv \psi(X_i|\text{Training})$ and $\tau_i \equiv \tau(X_i|\text{Training})$.\footnote{This is a slightly simpler regression than the one proposed in equation (3.1) of \cite{chernozhukov2018generic}, which involves propensity score weights.
-Because the random assignment of $Z$ in our experiment does \emph{not} condition on $X$, the propensity score weights in our case are constant over $X$ and hence drop out.} As shown by \cite{chernozhukov2018generic}, the coefficients $\beta_1$ and $\beta_2$ from \eqref{eq:chernreg} identify the \emph{best linear predictor} of the conditional ATE based on $\tau(\cdot|\text{Training})$, namely
-\[
-\beta_1 = \mathbbm{E}[\text{ATE}(X_i)] = \text{ATE}, \quad
-\beta_2 = \frac{\text{Cov}[\text{ATE}(X_i), \tau_i]}{\text{Var}(\tau_i)}.
-\]
-If treatment effects are homogeneous we must have $\beta_2 = 0$.
-Rejecting this hypothesis establishes that $\tau_i$ predicts $\text{ATE}(X_i)$ and hence that $\Delta_i$ varies.
-Since $\tau_i$ and $\psi_i$ do not depend on the test set, inference for the regression in \eqref{eq:chernreg} is straightforward conditional on the Training/Test split.
-
-\todo[inline]{Discuss the results here.}
-
-\todo[inline]{Issac: re-run this exercise with removing the propensity score weights $p(Z)$. Presumably it shouldn't change anything, but it's simpler to explain what we do and probably less noisy
-
-\begin{table}[H]
-\begin{center}
-\scriptsize{\input{./Tables/test_calibration_2.tex}}
-\end{center}
-\end{table}
-
-}
-
-\todo[inline]{Some Questions for Issac: (1) How are we carrying out the sample splitting?
-If we cluster standard errors at the branch-day level, we should take this into account when we split.
-(2) How are you carrying out inference for $\beta_2$?
-Chernozhukov et al discuss two approaches: ``conditional'' and ``variational.'' The former is simpler as it conditions on the training/test split.
-The latter is a bit more involved, since one accounts for uncertainty arising from different splits.
-(3) What are the details of the random forest procedure employed here?
-(Tuning parameters choice, etc.) We should put them into the appendix.}
+%\subsection{Treatment Effect Heterogeneity}
 
@@
 
+As seen above in Section \ref{experiment}, the average treatment effect of forced commitment is economically and statistically significant. 
+Using the notation of Section \ref{sec:potentialOutcomes}, our estimate of $\mathbbm{E}[Y_{i1} - Y_{i0}]$ is \emph{negative}: commitment lowers financial costs overall. 
+But this is only an average effect.
+The ATE could still be negative if the individual treatment effects $\Delta_i = Y_{i1} - Y_{i0}$ are zero or positive for most people in the experiment.
+Perhaps commitment is extremely helpful for a small minority of borrowers, and slightly harmful for everyone else.
+Can this explanation rationalize the very low take-up rate of commitment in the choice arm (11\%) along with the ATE of commitment estimated from the forced arm? 
+We could easily answer this question if the distribution $F_\Delta$ of individual treatment effects $\Delta_i$ were known: simply calculate $\mathbbm{P}(\Delta_i < 0)$.
+But because we can never observe both $Y_{i0}$ and $Y_{i1}$ for the same person, $F_\Delta$ cannot be identified. 
+It can, however, be bounded. 
+Using these bounds, we now show that more than 11\% of individual borrowers benefit from commitment.
+
 As explained above, our experimental design identifies the marginal distributions of $Y_{i0}$ and $Y_{i1}$, call them $F_0$ and $F_1$.
-We can estimate them using the empirical CDF of $Y_i$ for $Z_i=0$ and $Z_i = 1$ respectively.
-Because we can never observe both treated and untreated potential outcomes for the same person, however, the distribution $F_\Delta$ of the individual treatment effects $\Delta_i \equiv Y_{i1} - Y_{i0}$ cannot be identified.
-It can, however, be bounded.
-\cite{fan2010sharp} show that the best possible pointwise bounds for $F_\Delta$ are given by $\underline{F}(\delta) \leq F_\Delta(\delta) \leq \overline{F}(\delta)$ where the bounding functions $\underline{F}$ and $\overline{F}$ are defined as
+Now, define the functions $\underline{F}$ and $\overline{F}$ as follows:
 \[
@@
 \]
+Since $F_0$ and $F_1$ are point identified, so are $\underline{F}$ and $\overline{F}$.
+\cite{fan2010sharp} show that the sharp (best possible) pointwise bounds for $F_\Delta$ are given by $\underline{F}(\delta) \leq F_\Delta(\delta) \leq \overline{F}(\delta)$
 These bounds are simple to compute, and can be surprisingly informative. 
 Here we use them to bound the fraction of borrowers who benefit from commitment. 
-Given the way that we have defined our outcome variables, this is the share of borrowers whose treatment effect is \emph{negative}, i.e.\ $F_\Delta(0)$.
+Given the way that we have defined our outcome variables, this is the share of borrowers whose treatment effect is \hl{\emph{negative}}, i.e.\ $F_\Delta(0)$. 
 To construct the sharp bounds for this quantity, we simply substitute $\delta = 0$ into the preceding equations and estimate $F_0$ and $F_1$ using their empirical analogues constructed from the forced commitment and forced no-commitment arms of the experiment.
@@
 Maybe we don't need a second figure with the confidence bands for the whole quantile function.
-(Overkill?) Frank: add a sentence or two discussing the results.
+Frank: add a sentence or two discussing the results.
 Presumably the aforementioned quantile is indeed negative and fairly large.}
 
-Taken together, these bounds suggest that at least some borrowers who would benefit from commitment do not choose it when offered.
-
-\subsection{Treatment on the Treated and Untreated}
-In the preceding section, we used outcome data from the forced arms ($Z_i\neq 2$) along with the commitment take-up rate in the choice arm ($Z_i = 2$) to argue that at least some of the 89\% of participants who did \emph{not} choose commitment would have been better off if they had.
+Taken together, these bounds show that at least some borrowers who would benefit from commitment \emph{do not choose it} when offered.
+
+%Defenders of choice make another subtler point: that even if take up of the commitment-fee contract is low, the sole fact of \textit{having} choice could potentially change behavior or welfare (\cite{Dalboetal:2010}, \cite{Sjostrometal:2018}, \cite{Tlaxcala}).
+
+%In spite of broadly distributed benefits of the Forced Commitment commitment contract we documented above, 90\% of clients chose \textit{not} to have it, preferring the status-quo contract.
+As explained above we are fairly confident this was not because a lack of understanding of the contracts.
+
+%\vspace{.1in}
+%\noindent What can explain this low demand?
+In the spirit of \cite{Blumenstock} we try to differentiate between explanations.
+One explanation could be risk.
+Even if the fee forcing contract generates cost savings on average, clients with risk averse preferences may not demand it if they perceive higher risk from it.
+Alternatively, even risk-neutral agents may not demand it if the cost of lost flexibility is high or if they have high temporal discount rates and prefer to pay later.
+%If clients, for instance, face large and frequent income shocks which make it hard to repay monthly.\footnote{We don't observe income shocks in our data, making is hard to quantify how important they are.
+91\% of those in the Forced Commitment arm incurred a fee, which suggests that shocks are not uncommon.}
+%Although the evidence that follows undermines several explanations, the tests we can conduct given the data are not sharp enough to leave a single explanation standing.
+Section \ref{model} lays our a simple theory (namely present bias with partial naivete) which fits all the 6 main findings of the paper.
+Given its parsimony and explanatory power, we submit that it is the most suitable explanation for our results.
+
+%Following two  paragraphs moved from old 'behavioral' choice section towards end of paper
+%\vspace{.2in}
+%\subsection{The effect of choice on pawn recovery and financial cost} \label{effect_choice}
+
+%Figure \ref{main_te} represents the  effect sizes (in standard deviations) of the two main study arms for three outcomes:  default, the financial cost of the loan, and the effective interest rate paid to acquire the borrowed capital.
+The Forced arm is significant for all three outcomes, with very substantial treatment effects in magnitudes for default and APR, and the commitment arm is never significant.\footnote{The slight increase in APR for the Choice arm seen in this picture arises from the fact that the APR calculation has the arm-specific loan size in the denominator, and the loans in the Choice arm turn out to be slightly smaller (although statistically equal) on average than the Control.}    In other words, voluntary commitment is ineffective but the use of forced commitment saves the average borrower an amount of money almost twice the APR of a normal US credit card loan.
+
+%Although we have shown that Forced Commitment reduces financial cost and increases pawn recovery, this does not imply that welfare increases.
+Clients could have disutility from the stress of having monthly installments for instance.
+%We don't need to make the strong claim of welfare for the purposes of this paper. The financing cost results are striking enough. But we
+
+%The panel labeled Forced Commitment in Figure \ref{reincidence} presents results of estimating equation (\ref{basic_reg}) with the dependent variable being a dummy for the client being a repeat customer.
+We define a client as a repeat customer if, after experiencing at least 75 days of the respective treatment arm, she came back and pawned a \textit{different} piece.\footnote{Results are robust to using number of days experiencing the contract larger than 75.
+We know it is a different piece from it having a different weight/value.}  The leftmost coefficient shows that the causal effect of the Forced Commitment contract on repeat pawning is an increase of 5 percentage points in the probability of being a repeat customer, this is twice the repeat purchasing happening in the status quo group.
+This effect is not explained by clients recovering their first pawn with higher probability in the Forced Commitment contract and re-pawning this same one since we make sure it is another piece; besides only 16\% recover their piece in the fist 75 days in the fee forcing contract.
+Experience with the frequent payment contract seems to be necessary as there is no effect of the monthly payment contract on repeat pawning in the first 30 or 60 days of the contract (see Figure \ref{reincidence_before} in the Appendix).
+
+%\hl{The second coefficient from the left focuses on the subsample who are predicted would have a treatment effect on financial cost savings above the median} treatment effect in their first pawn.\footnote{Since this is predicted using \cite{atheygrf} based on pre-determined covariates for treatment and control clients it is valid to split the sample this way.} It shows that for these clients the likelihood of coming back is twice as large.
+That is, those that benefit more from the Forced Commitment contract are more likely to repeat compare to their control group.
+The remaining coefficients of the ``Forced Commitment'' panel condition on endogenous outcomes and should be interpreted with care.
+The \hl{third} coefficient from the left restricts the sample to those that had not recovered their pawn in the first 75 days in both groups and finds similar results.
+The \hl{fourth} coefficient conditions on clients who recovered their pawn of the experiment, again on in both arms.
+Results from these two endogenous samples are similar to those for the whole sample.
+
+%The fourth coefficient \footnote{The second and third estimate must be interpreted with care as we are conditioning on a variable that may be affected by treatment.
+We view these 2 coefficients as suggestive correlations only.
+The fourth coefficient does not have that problem as it conditions on clients that by their pre-determined covariates are predicted to have above the median treatment effects (in both arms).}
+
+%The coefficient on repeat pawning is just as big when we focus only 2nd pawns happening after the first was recovered (third coefficient ``fnr'').
+This is consistent with \cite{Laibson2018}'s conjecture that clients could be making decisions based on experienced utility.\footnote{The third coefficient conditions on the subsample that did recover their first pawn in both arms and finds a coefficient of 4pp.
+This is not a causal estimate as recovery is influenced by treatment, but we found it telling that the differences were similar to the causal estimate for the full sample.}
+
+\subsection{The ``Randomized Choice'' Design}
+
+Above we used outcome data from the forced arms ($Z_i\neq 2$) along with the commitment take-up rate in the choice arm ($Z_i = 2$) to argue that at least some of the 89\% of participants who did \emph{not} choose commitment would have been better off if they had.
 By additionally examining \emph{outcome data} in the choice arm, it is possible to say more. 
-We now show how our experimental design can be used to identify the average effect of commitment for both those who would choose it (the treated) and those who would not (the untreated).
-In particular, we identify the treatment on the treated (ToT) and treatment on the untreated (TuT) effects, defined as follows:
+We now show how our experimental design, henceforth the ``randomized choice design,'' point identifies a number of interesting and economically-relevant causal quantities without the need for additional structural restrictions.
+First we identify the treatment on the treated (ToT) and treatment on the untreated (TuT) effects, defined as follows:
 \[
@@
 \]
-The TuT and ToT effects are particularly interesting for understanding the importance of paternalism.
+%The TuT and ToT effects are particularly interesting for understanding the importance of paternalism. 
 If the TuT is positive, this means that someone who did not choose commitment would have been experienced a better outcome \emph{on average} if she had. 
 In a canonical Roy model, the ToT should exceed both the TuT and average treatment effect (ATE).
-Because our design identifies all three quantities, it allows us to test this implication directly.
 If the ToT is statistically distinguishable from and substantially larger than the TuT, this provides empirical support for the relevance of selection-on-gains in real-world decision-making.
+Because our design identifies all three quantities, it allows us to test this implication directly and to calculate the average selection on gains (ASG):
+\[
+\text{ASG} \equiv \mathbbm{E}[Y_{i1} - Y_{i0}|C_i = 1] - \mathbb{E}[Y_{i1} - Y_{i0} | C_i = 0] = \text{ToT} - \text{TuT}.
+\]
+The randomized choice design also identifies both the average selection bias (ASB) and the average selection on levels (ASL). 
+\[
+\text{ASB} \equiv \mathbbm{E}[Y_{i0}|C_i = 1] - \mathbbm{E}[Y_{i0}|C_i = 0], \quad 
+\text{ASL} \equiv \mathbbm{E}[Y_{i1}|C_i = 1] - \mathbbm{E}[Y_{i1}|C_i = 0].
+\]
+A companion STATA package accompanying this paper provides estimators of the ToT, TUT, ASG, ASB, and ASL, along with cluster-robust standard errors.\footnote{\hl{Provide a url?}}
 
 A number of recent papers compare estimates of the ToT and TuT to better understand who selects into treatment and why, e.g.\ \cite{cornelissen2018benefits} and \cite{Walters}. 
-While valuable and interesting, this line of work relies, at least to some extent, upon structural modeling assumptions to extrapolate from the reduced-form quantities that are identified by the data alone to more interesting, and economically relevant, causal parameters.\footnote{While the marginal treatment effects (MTE) approach \citep{heckman2007econometric} can in principle be used to identify the ToT and TuT without parametric restrictions, doing so requires an instrumental variable $Z$ with sufficiently rich support that the probability of treatment take-up given $Z$ varies continuously between zero and one.
-In practice, instrumental variables are usually discrete and, even when continuous, typically have a more modest effect on take-up.} An alternative approach aims to avoid structural assumptions by calculating conditional local average treatment effects (LATE) given observed covariates $X$ and reweighting these according to the distribution of $X$ in some population of interest \citep{aronow2013beyond,angrist2013extrapolate}.
-For example, one might re-weight using the distribution of $X$ in the population as a whole, rather than the sub-population of compliers, to extrapolate from LATE to ATE.
-But you can't squeeze blood from a stone.
-This ``LATE-and-reweight'' approach relies upon assumptions of its own, most crucially the assumption that there is \emph{no selection-on-gains} conditional on $X$, i.e.\ that the conditional LATE equals the conditional ATE.
-As far as we are aware, ours is the only paper in the literature to simultaneously point identify the ATE, ToT and TuT without ruling out unobserved selection-on-gains or relying on additional structural modeling assumptions.
-This is possible because of the unique design of our experiment.
-
-\todo[inline]{Somewhere in the paper we'll want to talk about when this kind of design could be useful in a bit more detail.}
+This line of work relies, at least to some extent, upon structural modeling assumptions to extrapolate from the reduced-form quantities that are identified by the data alone to more interesting, and economically relevant, causal parameters.\footnote{While the marginal treatment effects (MTE) approach \citep{heckman2007econometric} can in principle be used to identify the ToT and TuT without parametric restrictions, doing so requires an instrumental variable $Z$ with sufficiently rich support that the probability of treatment take-up given $Z$ varies continuously between zero and one.
+In practice, instrumental variables are usually discrete and, even when continuous, typically have a more modest effect on take-up.}
+An alternative approach aims to avoid structural assumptions by calculating conditional local average treatment effects (LATE) given observed covariates $X$ and reweighting these according to the distribution of $X$ in some population of interest \citep{aronow2013beyond,angrist2013extrapolate}.
+%For example, one might re-weight using the distribution of $X$ in the population as a whole, rather than the sub-population of compliers, to extrapolate from LATE to ATE. 
+But there is no free lunch: this ``LATE-and-reweight'' approach relies upon assumptions of its own, most crucially the assumption that there is \emph{no selection-on-gains} conditional on $X$, i.e.\ that the conditional LATE equals the conditional ATE.
+In contrast to both approaches, the randomized choice design uses exogenous experimental variation to point identify the ATE, ToT, and TuT without ruling out unobserved selection-on-gains or relying on additional structural modeling assumptions.
 
 The key insight can be read directly from \eqref{eq:potentialTreatments} and \eqref{eq:potentialOutcomes}. 
-Viewing $Z_i$ as an instrumental variable, our design can be interpreted as a \emph{pair} of RCTs, each subject to one-sided non-compliance.\footnote{For a full derivation, see \hl{Appendix ???}.} The first of these compares $Z_i=0$ to $Z_i = 2$.
+Viewing $Z_i$ as an instrumental variable, our design can be interpreted as a \emph{pair} of RCTs, each subject to one-sided non-compliance.
+The first of these compares $Z_i=0$ to $Z_i = 2$.
 For each individual with $Z_i = 0$ we have $D_i = 0$ and observe $Y_{i0}$.
@@
 since $\mathbbm{E}(D_i|Z_i=0)=0$ by \eqref{eq:potentialTreatments}. 
-
-A closely related if slightly less intuitive argument can be used to construct a Wald estimand that identifies the TuT.
+A closely related argument can be used to construct a Wald estimand that identifies the TuT.
 Here we consider $Z_i = 1$ to be the ``encouragement'' and compare the outcomes for these individuals to those with $Z_i = 2$.
@@
 since $\mathbbm{E}(D_i|Z_i = 1)= 1$ by \eqref{eq:potentialTreatments}.
-
-\eqref{eq:ToT} and \eqref{eq:TuT} are useful for understanding why our design identifies the ToT and TuT, but they are less convenient for estimation and inference.
-In Appendix \todo{Frank: fill in}{???}, we show that
+Equations \eqref{eq:ToT} and \eqref{eq:TuT} are useful for understanding why the randomized choice design identifies the ToT and TuT, but they are less convenient for estimation and inference.
+In Appendix \hl{???}, we show that
 \begin{align}
@@
 
-As explained above, a canonical Roy model would suggest that $\text{TuT} \leq \text{ATE} \leq \text{ToT}$.
-For this reason it is particularly interesting to consider inference for the difference $(\text{ToT} - \text{TuT})$, namely the \emph{average selection on gains}:
-\[
-\text{ASG} \equiv \mathbbm{E}[Y_{i1} - Y_{i0}|C_i = 1] - \mathbb{E}[Y_{i1} - Y_{i0} | C_i = 0] = \text{ToT} - \text{TuT}.
-\]
-The point estimate of this difference can be constructed directly from the results of the IV regressions described above.
-Because the respective estimates appear in different equations, however, a bit more work is required to obtain a standard error for $(\text{ToT} - \text{TuT})$.
-The details are straightforward but somewhat tedious, so we present them in Appendix \todo{!!!}{???}.
-A companion STATA package accompanying this paper provides cluster robust inference for the average selection on gains, along with two related quantities: the average selection bias (ASB) and average selection on levels (ASL)
-\[
-\text{ASB} \equiv \mathbbm{E}[Y_{i0}|C_i = 1] - \mathbbm{E}[Y_{i0}|C_i = 0], \quad 
-\text{ASL} \equiv \mathbbm{E}[Y_{i1}|C_i = 1] - \mathbbm{E}[Y_{i1}|C_i = 0].
-\]
-We show that these latter two quantities are point identified in Appendix \todo{!!!}{???}.
-
-%Define the shorthand
-%\[
-%p_0 \equiv \mathbbm{P}(Z_i=0), \quad p_1 \equiv \mathbbm{P}(Z_i = 1), \quad q_0 \equiv \mathbbm{E}[\mathbbm{1}(Z_i = 2)(1 - D_i)], \quad q_1 \equiv \mathbbm{E}[\mathbbm{1}(Z_i = 2) D_i].
-%\]
-%As shown in Appendix \todo{Frank: fill in}{???}, the asymptotic variance of $(\text{Tot} - \text{TuT})$ is given by
-%\[
-%\text{AVAR}(\text{ToT} - \text{TuT}) = \boldsymbol{\omega}' \boldsymbol{\Sigma} \boldsymbol{\omega}, \quad
-%\boldsymbol{\omega}' \equiv \displaystyle \begin{bmatrix}
-%-\frac{1}{q_1} & \frac{1}{q_0} & \left(\frac{p_1 - 1}{p_0q_1} - \frac{1}{q_0}\right) & -\frac{1}{q_1} - \frac{1 - p_0}{p_1 q_0}
-%\end{bmatrix}
-%\]
-%where $\boldsymbol{\Sigma}$ is a covariance matrix that can be estimated from the residuals of \eqref{eq:ToTreg} and \eqref{eq:TuTreg}. Under iid observations, 
-%
-%\todo[inline]{Explain two leading forms that $\Sigma$ can take: heterosked and cluster}
-
-%\todo[inline]{Frank: give an overview of how to do the comparison of TuT and ToT.
-Want it to be ``idiot proof'' -- easy to do in standard software, etc.
-Details in the appendix but want the contribution to be clear.
-Cluster at the level of the randomization.
-(Almost WLOG for experiments).
-Can put some additional details in the appendix.}
-
-\todo[inline]{Issac: add the table of TuT/ATE/ToT results without covariates. For the moment I suppose we \emph{don't} have the ToT/TuT comparison. (See Frank todo above!)}
-
-%\todo[inline]{Because they appear in different equations, testing TuT = ToT is slightly more involved. Explain how to do it here, but put additional details in the appendix.}
-
-\todo[inline]{Frank: after the preceding todo notes, revise the text below that discusses the ToT/TuT etc results.
-Think about how to compare/contrast/relate to the bounding exercises above as well as the ITT results.}
+\todo[inline]{Add a paragraph briefly explaining which IV regressions to run to get the ingredients for the ASB and ASL, and directing the reader to an appendix that describes how to carry out inference when you need to combine estimates from two separate IVs.}
+
+\todo[inline]{Perhaps mention some other settings in which a design like this might be helpful?}
 
@@
 
-\todo[inline]{This next paragraph needs to be edited a bit. I think there's one more number that we need to put in the table of results: the SE for the ToT versus TuT?}
+\todo[inline]{This next paragraph needs to be re-written.}
 
@@
 
-\subsection{Marginal Treatment Effects}
-As described above, our experimental design point identifies the ATE, TUT, and TOT without the need to carry out a marginal treatment effects (MTE) analysis that would rely, to some extent, on structural assumptions or shape restrictions.
-Nonetheless, researchers who are interested in learning more about essential heterogeneity can combine our design with an MTE approach.
-\todo[inline]{Need to flesh out a bit more, but in short: (1) can extend the results of Mogstad et al (2017) to use our ATE, TUT, and TOT as additional inequality restrictions that constrain partial identification bounds for MTEs; (2) Could allow more flexibility in the approach of Carneiro et al (2011) by recovering $\mu_0(x)$ and $\mu_1(x)$ from the forced arm.
-This permits richer forms of observed heterogeneity than the linear specification that is typically used in applied MTE papers.
-One could also combine (1) and (2) or use (1) as a specification test for (2).}
-
-\subsection{Quantile Treatment Effects}
-
-\todo[inline]{Frank: cut this section.}
-
-We now want to move away from the experimental consideration of the arms as a whole, and dive into the individual heterogeneity to learn more about the relationship between choice and outcomes.
-A simple way of interrogating the distribution of treatment effects is to use quantile regression.
-Figure \ref{qregs} plots treatment effects on financial cost and APR at the 15$^{th}$, 25$^{th}$, 50$^{th}$ 75$^{th}$, and 85$^{th}$ percentile of the outcome variables for the Forced and Choice arms.
-It illustrates that a) there is substantial internal heterogeneity in the Forced arm, meaning that some people benefit from forcing and some do not, and that b) taken as a whole the Choice arm has no significant benefit in any part of the distribution.
-Therefore, within the group being forced to take commitment we find large heterogeneity in the impacts.
-
-We can explore the heterogeneity within the Choice arm in a non-experimental but suggestive way by breaking apart the choosers and non-choosers and separately estimating quantile effects relative to the control for these two groups.
-This analysis, shown in Figure \ref{qreg_chooser_nonchooser}, plots the quantile effects for the choosers only (circles), and non-choosers only (squares).
-It shows two important features of the observed impacts.
-First, the non-choosers in the choice arm never look different from the control, as should be the case if the exclusion restriction invoked in the prior section is true.
-Second, all of the heterogeneity that exists within the Choice arm arises from within the Chooser group, and this heterogeneity looks qualitatively similar to (although smaller than) the heterogeneity observed in the Forced arm.
-This analysis is observational because it splits the data on an endogenous variable (choice), but is nonetheless suggestive that substantial heterogeneity in treatment effects exists for all individuals exposed to the Commitment product, and that there are no obvious violations of the exclusion restrictions around forced versus chosen compliance.
-
-%Benefits are distributed broadly however.
-Figure \ref{fc_pro2}(b) displays results from quantile regressions at the 15$^{th}$, 25$^{th}$, 50$^{th}$ 75$^{th}$, and 85$^{th}$ percentiles.
-All of them are negative.
-%This motivated us to implement a finer measure of treatment effects.
-
-%Figure \ref{fc_pro2}(c) plots the distribution of those treatment effects using this machine learning methodology.
-It shows that more than 70\% of clients experienced financial cost savings in the Forced Commitment group compared to the status-quo group.
-The causal cost savings are larger for the more economically vulnerable, %that report at baseline that they have problems paying for services like water, electricity and rent,
-%and those displaying overconfidence\footnote{see Section \ref{behavioral} for our measure of overconfidence.} about recovering their pawn, Figure \ref{HTE_fee_forcing}.
-%those that have to incur in higher transport cost to go to the branch  and that asked to be sent reminders to pay, this later one being one proxy of being inattentive or sophisticated present-biased.
-
-%Figure \ref{fc_pro4} digs in more detail into the sources of variation underlying the main effects in Figure \ref{main_te}.
-$\beta$ coefficients and their 95\% confidence interval from estimating equation (\ref{basic_reg}) using different definitions of financial cost.
-The leftmost coefficient corresponds to plugging into the formula of section \ref{FC_def} the appraised gold value of the pawned piece.
-The second coefficient uses the subjective value of the pawn instead.
-In both cases we find that being assigned to the Forced Commitment commitment contract causes a large reduction in the financing cost the client incurred, of 9.4\% (\$297) under the first definition and 13.2\% (\$472) under the second one.
-That is, we find that \textit{charging} clients a late payment decreases total \textit{fee-inclusive} financing cost.
-
-%The hollow circles in Figure \ref{fc_pro4}(a) show zero average effects for the different definitions of financial cost analogous to the ones described above.
-Figure \ref{fc_pro4}(b) shows further that the null effect happens for the 15$^{th}$, 25$^{th}$, 50$^{th}$ 75$^{th}$, and 85$^{th}$ percentiles.\footnote{The few clients that chose the Commitment contract (the solid black squares) do enjoy cost savings of 1005 MXN, which compares favorably to the 304 MXN in the Forced arm (as a fraction of the loan the numbers are 41.5\% and 12.5\%), but this combines the selection and treatment effects.} %Figure \ref{heterogeneous_te_4} plots the distribution of treatment effects and finds that the distribution offering choice actually \textit{increased} financial cost and default for about half of clients compared to being assigned the status-quo contract.
-Those tended to be the less economically vulnerable and more educated, {women}, and those whose family typically asks them for money.Figure \ref{fc_pro4}(c) finds null effects for pawn recovery.
-Consistent with these findings, Figure \ref{reincidence} finds no effect on repeat purchases for the Commitment Choice group.
-
- %Figure \ref{fc_pro2}(d) plots estimated treatment effects of the Forced Commitment commitment contract with the dependent variable being an indicator of losing the pawn in less than 230 days.
-The leftmost coefficient shows that the Forced Commitment commitment contract increases the likelihood of recovering the pawn by 11 percentage points (26\% of mean recovery).
-This result stands in contrast with \cite{Pande} who find no effect of payment frequency on default in a group lending microfinance context.
-Figure \ref{fc_pro2}(e) shows the distribution of heterogeneous treatment effects for losing the pawn: The likelihood of losing the pawn decreases for 82\% of the population.
-%Figure \ref{HTE_fee_forcing}(b) in the Appendix shows that those we classify as present biased, those that requested to be sent a reminder to pay, and those who have more problems paying for basic services experienced the largest increases on pawn recovery.
-
-%the second conditions on the population that paid any positive amount towards recovery of their pawn; the third conditions on having paid at least 30\% of the loan amount; the fourth conditions on the period covering the first cycle of the loan; the fifth on the period of the first cycle and paying any positive amount.
-
-% Results survive if we focus on those that paid a positive amount in treatment and control.\footnote{Although this is potentially a selected subsample, Table \ref{mechanisms} showed that there is no treatment effect in the extensive margin, i.e.
-in $pay>0$.} We find that even those that paid a fee in the Forced Commitment contract end up paying a smaller financial cost that those in the status-quo contract (Figure \ref{fc_pro2}a).\footnote{This regression conditions on those that paid a fee in the Forced Commitment group, and compares this subset in treatment vs all of the control group.
-Results are similar if we condition in the control group on those who would have paid a fee  if they were in the treatment group given their observed payment behavior.
-Again we acknowledge this is an endogenous sample and that the estimate may not be a causal effect.}  Figure \ref{fc_pro2}(d) shows that the increase in pawn recovery is robust to defining recovery using the first 120 days of the contract, or restricting to those paying a positive amount towards pawn recovery.
-
-%we The 4th coefficient from left to right conditions on those who paid a positive amount (in treatment and control).
-Although this is potentially a selected subsample, Table \ref{mechanisms} showed that there is no treatment effect on pay$>0$.
-We were interested in this population to show that the effect is there for those who are serious about recovering their pawn.
-The fifth coefficient conditions on those that paid a fee in the Forced Commitment group, comparing this subset in treatment vs all of the control group.
-Results are similar if we condition in the control group on those who would have paid a fee given current behavior.
-Again we acknowledge these is an endogenous sample and that the estimate may not be a causal effect.} We find that even those that paid a fee in the Forced Commitment contract end up paying a smaller financial cost that those in the status-quo contract.
+\section{Is there space for paternalism?}
+\label{exploring}
+
+\paragraph{Causal forest heterogeneous treatment effects.}
+
+\hl{Here we will put Athey' stuff}
 
@@
 
-% Figure \ref{choose_wrong}(d) plots $\widehat{P(x_i)}$ on the X-axis, and the heterogeneous treatment effects we estimated in Section \ref{TE_fee-forcing} on the Y-axis.
-It plots a binscatter that splits the X-axis into 100 percentiles bins of predicted take-up probability and for each bin averages the financial cost treatment effects.
-If it was true that those with larger cost savings have larger demand for the fee-commitment contract, we would expect a negative slope (recall that more savings mean lower financial cost in the Y-axis).
-This is not what we find.
-Using all clouds we estimate a slope close to zero in the relationship.
-Using the 80 right most points, we estimate a \textit{positive} relationship.
-A positive relation means that those more likely to demand commitment are also those that had smaller benefits from commitment.
-This result is similar to \cite{Walters}, who finds that students that select into more effective schools are the ones with smaller treatment effects from attending.\footnote{\cite{Walters} uses distance to school as an instrumental variable for choice, while we use randomization to choice vs no-choice groups as our empirical strategy.}
-
-%The following text brought in from the prior ToT/TuT section; do we want to include?
-
-%.
-Although the difference is not significant (Figure \ref{bootstrap_tot_tut}) since we have a low (15\%) compliance rate in the choice arm, which results in low power, we also estimate an Instrumental Random Forest following \cite{atheygrf}.
-The Instrumental Random Forest allows us to compute conditional heterogeneous treatment effects, which effectively lets us estimate for each individual with characteristics $X_i$ the quantities $ToT_i:=\mathbb{E}[Y_1-Y_0\; |\; T_i=1, X_i]$, and $TuT_i:=\mathbb{E}[Y_1-Y_0 \;|\; T_i=0, X_i]$.
-Figure \ref{tot_tut_ecdf} plots the ECDF for this quantities, together with the difference $ToT-TuT$.
-When testing for the difference in means between this two distributions we find a significant difference of \hl{0.03 points} at the 95\% level.
+\paragraph{Who chooses commitment?}
+
+we estimate a flexible model of take-up of the commitment-fee contract \textit{in the Choice arm} using gradient boosting classification\footnote{Results are robust to other classification methods like Random Forest, SVM, etc.} and obtain for a client with characteristics $x_i$ a calibrated probability $P(x_i)$ of choosing the commitment contract.
+
+\hl{To be completed}
+
+\subsection{Marginal Treatment Effects}
+As described above, our experimental design point identifies the ATE, TUT, and TOT without the need to carry out a marginal treatment effects (MTE) analysis that would rely, to some extent, on structural assumptions or shape restrictions.
+Nonetheless, researchers who are interested in learning more about essential heterogeneity can combine our design with an MTE approach.
+\todo[inline]{Need to flesh out a bit more, but in short: (1) can extend the results of Mogstad et al (2017) to use our ATE, TUT, and TOT as additional inequality restrictions that constrain partial identification bounds for MTEs; (2) Could allow more flexibility in the approach of Carneiro et al (2011) by recovering $\mu_0(x)$ and $\mu_1(x)$ from the forced arm.
+This permits richer forms of observed heterogeneity than the linear specification that is typically used in applied MTE papers.
+One could also combine (1) and (2) or use (1) as a specification test for (2).}
+
+\begin{comment}
 
@@
 
-\subsection{Dynamic Effects:  Learning-by-not-doing}
-
-\textcolor{red}{Need to decide on table and write this section of the paper.}
-
-\section{Old Mechanisms Section of Paper}
-
-\textcolor{red}{Which of these pieces do we want to keep?  Delete whole section?.}
-
-\subsection{Optimism, Over-Optimism, and the Failure of Self-Commitment}
-\label{overconfidence}
-
-\textcolor{red}{Need to decide whether we want to try to plant our feet on Confidence/Overconfidence as the core `why' of the previous result
-.}
-%\subsubsection{Behavioral: overconfident borrowers demand less (but benefit more)} \label{behavioral}
-
-The leading behavioral explanation in the literature for low demand for commitment is present biased preferences with naivete (e.g.
-\cite{Rabin2018}, \cite{John}, \cite{Laibson2018})  \cite{Laibson2015} shows that the lost flexibility resulting from a commitment contract can limit take-up especially severely when agents are (partially) naive about their self control problem.
-In our context if consumers are (partially) naive about their present bias, they would plan to save more (or spend less) than what they actually end up saving, thus making it be harder to recover their pawn.
-This under-saving will be mitigated in the fee forcing contract since the fee makes them save money to pay part of the loan periodically.
-\ref{appendix_c} formalizes this in a model.
-Another behavioral explanation is that clients may underestimate the likelihood and severity of negative income shocks.
-Both of these explanations predict that clients will be overconfident about their likelihood of pawn recovery.
-Recall that in the control group the client's subjective probability of recovery is on average 93\%, while actual recovery is just 44\%.
-A further piece of evidence consistent with underestimating negative income shocks and with present bias with partial naivete is that a large number of people (25\%) in the control group pay a positive amount toward pawn recovery but end up losing their pawn anyway.
-
-So, overconfidence of recovering the pawn is implied by both present bias preferences with naivete and upward bias in their income expectations.
-But does overconfidence actually predict low demand for commitment empirically?
-It does.
-We define as overconfidence as the reported subjective probability of recovery minus the predicted probability based on the client's characteristics, $P^s_i-\widehat{P_i(X_i)}$.\footnote{We predict $\widehat{P_i(X_i)}$ in two steps.
-In step one we use Lasso with cross validation to tune the regularization parameter to select the most predictive variables $X$.
-The typical present bias question as in \cite{Ashraf} was eliminated in this step.
-In the second step we estimate $\widehat{P_i(X_i)}$ using those variables in a logit model.
-The Lasso selected variables were type of pawn, female, age, has pawned before, has savings, participates in rotating savings, often feels tempted to change plans, would like to have a reminder to pay, and an economic vulnerability index.
-We are careful not to include these variables as controls in Table  \ref{oc_reg}.} There is a large amount of overconfidence in our context.
-Figure \ref{oc_hist} plots a histogram of $OC_i$ and shows that the overwhelming majority display overconfidence, and a large fraction overestimate recovery by more than 50 percentage points.
-Our measure of overconfidence is useful especially when there is limited time for a detailed survey.\footnote{It may be more useful than a simple elicitation of present bias as in \cite{Ashraf}.
-We find that 15\% of clients are classified as present biased using this measure of preference reversal.
-This level is similar to the number \cite{Ashraf} find but small to explain no take-up of commitment for 90\% of clients.
-This measure was not correlated with take up of commitment in our sample.} First it is very prevalent, which makes it promising to explain the overwhelming prevalence of low take up.
-Second, it is easy to measure.
-Third, it is predictive of take-up in an intuitive way.
-Finally, overconfidence in recovery is implied by present bias with (partial) naivete but also by biased expectations of negative income shocks, thus capturing both kinds of bias.\footnote{\textcolor{red}{Another indication of overconfidence is that in our data, of those who renew, 83\% lose the pawn anyway.
-Our measure of overconfidence has a correlation of \hl{xxx}\% with a dummy for renewing and losing the pawn.
-}}
-
-\cite{Sprenger} have argued that it is critical to understand the link between beliefs and demand for commitment, yet the evidence is scarce.
-Table \ref{oc_reg} does this: it regresses an indicator of take up of the monthly payment contract against an indicator for overconfidence $OC_i:=\mathbbm{1}(P^s_i-\widehat{P_i(X_i)}>0)$ and controls.
-Controls $Z$ include branch and day of the week dummies, schooling, whether the client does a monthly budget plan, among others.
-We are careful not to include controls that were used in $\widehat{P_i(X_i)}$.
-% and a measure of intertemporal preference reversal analogous to that of \cite{Ashraf} as controls.\
-In the choice-fee arm, being overconfident decreases the likelihood of demanding commitment by 12 percentage points a result that this is robust to including controls  (columns 1 and 2).
-While overconfidence predicts lower take up in the Commitment Choice arm, this is not the case in the promise-choice arm (columns 3 and 4).
-One interpretation of the results is that the overconfident borrowers think they do not need commitment, and their demand decreases sharply as soon as there is even a small fee, and at the same time they perceive the promise as a low cost option.
-This provides evidence for \cite{Sprenger}'s conjecture that ``tepid demand for commitment outside controlled experimental settings is consistent with broad unawareness [of biases]''.
-
-How does overconfidence map to cost outcomes?
-Theory predicts that the more overconfident (naive) may be at the same time those that benefit more from commitment.
-Extrapolating individual treatment effects of the Forced Commitment contract vs the status quo one to the choice arm (see below for more detail), and using them as a dependent variable we find that overconfident borrowers benefit \textit{more} from the commitment contract, with {24.8}\% (=\${30}/\${121}) more savings (columns 5 and 6).
-Thus while we predict the overconfident benefit more from commitment, they demand less of it.
-
-\subsubsection{Neoclassical Alternatives} \label{neoclasical}
-
-\vspace{.1in}
-\noindent \textbf{Risk aversion.} We do not have measures of risk aversion in our short survey, which makes it hard to assess the hypothesis that risk aversion limits take-up of the fee frequent payment contract.
-One way to proceed is to take the empirical distribution of financing cost ---$F_{fee}(FC)$--- as one the client would have faced had she chosen the the fee-commitment contract.
-We could then ask what would risk aversion have to be in order to justify the client choosing the fee-commitment contract distribution of costs over the distribution associated with the status quo contract, $F_{sq}(FC)$.
-Framed as a choice among cost distributions, we can calculate what risk aversion is needed to rationalize the overwhelming choice of the status quo contract over the fee-commitment contract.
-This exercise of course assumes --as is common in economics-- that clients know the distribution of financial cost, that the distribution is common across consumers (although this can be relaxed), and that this cost distribution is the only difference among contracts.
-
-Fortunately for us, it turns out that one distribution first-order-stochastically dominates the other, obviating the need to calibrate a specific utility function or use a parametric distribution function in order to rank them in terms of expected utility.
-We use the fact that if the utility $u(FC)$ is decreasing in $FC$ (i.e.
-clients dislike paying higher financing cost) and $F_{fee}(FC) \geq F_{sq}(FC)$ for all $FC$, which we actually verify in our data, then $E_{fee}[u(FC)] \geq E_{sq}[u(FC)]$, that is any expected utility maximizing client risk averse consumer should choose the Forced Commitment contract as a result of the distribution of cost payoffs.\footnote{See the Appendix for the proof.
-Figure \ref{ecdf_fc} in the Appendix shows that indeed $F_{fee}(FC) \geq F_{sq}(FC)$.
-Table \ref{stochastic_dominance} shows that this holds also for sub-populations of different characteristics.}.
-Thus, risk aversion cannot explain the low demand for commitment under the assumptions of this exercise.
-
-%To have a benchmark we implement a very simple calibration exercise in two steps.
-First, we fit a Weibull distribution to the distribution of financing cost, were the scale and shape parameters depend on client's and loan observable characteristics.
-We do this separately for the status quo contract and the Forced Commitment contract, obtaining two distributions $f_{sq}(FC|X;\Gamma_1)$ and  $f_{fee}(FC|X;\Gamma_2)$ with different parameters $\Gamma_1$, $\Gamma_2$.
-Second, we assume a representative consumer with a CRRA utility function over financial cost, $u(FC)=\frac{1}{1-\theta}FC^{1-\theta}$.
-We then ask what would $\theta$ have to be for a consumer to prefer the status-quo contract.
-That is for which $\theta$'s would  $\int u(FC|\theta)f_{sq}(FC|X;\Gamma_1) dFC \geq \int u(FC|\theta)f_{fee}(FC|X;\Gamma_2) dFC $ hold?
-It turns out that it holds for risk aversion levels that are too high to be believable.
-That is, with our calibration, it seems unlikely that risk aversion is reducing demand for the Forced Commitment contract.
-
-\vspace{.1in}
-\noindent \textbf{Lost flexibility.} A second explanation for low take up is lost flexibility.
-That is, the fee-commitment contract may provide too much commitment which is costly because the client may be forced to incur in late payment fees if he experiences a negative income shock.\footnote{Note that income shocks that affect the ability to pay the entire loan are a worry for both the Forced Commitment contract and the status quo one, and should not make one contract more favorable than the other.} While we cannot rule out that income shocks combined with lost flexibility of the contract explain the low demand, we think it is unlikely.
-First, we showed above that clients report a subjective probability of recovery of 93\% on average, which suggests they are not too worried about income shocks.
-Second, the fear of incurring fees is quantitatively not enough of a concern when compared to the savings they are experiencing.
-%Note that fees for late payment are not that high.
-In an average loan of 2,000 pesos the monthly payment is close to 700 pesos, and a fee of 2\% of that is 14 pesos (less than \$1 dollar).
-This is about gr{1\%} of monthly per capita income of the first 3 deciles of Mexican {household's} income distribution.
-%This compares favorably to the gr{\$11.6 + \$62.3)} pesos transportation / transaction cost of one.
-
-To make this concrete, we calculated what the financing cost of the fee-commitment contract would be if \textit{all} its clients incurred in \textit{all} potential fees (while keeping payment profiles and pawn recovery constant) and added these fictitious fees to financing cost for those in the Forced Commitment arm, thus artificially inflating their cost.
-We then re-estimated the quantile treatment effects analogous to Figure \ref{fc_pro2}(b) with this inflated financial cost.
-%\footnote{Of course behavior may not be constant, but we believe this is a reasonable fist approximation.
-%It could be that having this small fee added to the balance discourages them to pay or makes it harder to pay back the loan.
-But the contrary may also happen, with the fee making them more determined to pay early.
-We would need a structural model of client behavior to estimate a full counterfactual.
-We suspect that such small fees would not generate large changes in behavior in a simple neoclassical model.}).
-Figure \ref{fc_allfee} presents the results.
-We find that even in this extreme scenario, tilted against the Forced Commitment contract, the estimated effect still implies cost savings from the Forced Commitment contract at the mean, 25$^{th}$, 50$^{th}$, and 75$^{th}$ percentiles.\footnote{Recall that the differences in financing cost already takes into account the fact that clients in the fee forcing contract sink more pre-payments than those in the status quo contract, and that those prepayments are lost if the loan is not fully paid back.}  Although these arguments are not definitive, they suggest that low demand for commitment may be driven by more than the anticipation of lost flexibility implied by a small fee.
-
-\vspace{.1in}
-\noindent \textbf{High time discounting.} We mentioned above that clients in the status quo contract tend to wait until the last moment to pay to recover their pawns.
-Even among those that recover their pawn, only 40\% pay before the 90$^{th}$ day.
-Table \ref{mechanisms} shows that clients assigned to the fee-commitment contract front load their payments, starting their first payment earlier and finishing paying earlier too.
-However, clients may dislike front loading payments if their time preference discount rate is high.
-They may be willing to trade off a higher probability of losing their pawn for more \textit{back} loaded payments.
-
-What would discount rates have to be in order for back loaded payments to offset the reductions in financial cost effects we observe?
-%We can calculate this number by looping across a grid of discount rates, incorporating this higher discount rate in the definition of financial cost, and reestimating equation \ref{basic_reg} with this modified financial cost measure as the dependent variable in equation 1, searching for the discount rate that makes $\beta$ equal zero.
-We did this and obtained
-We calculate that the discount rate that is necessary to compensate for the savings in financial cost (i.e.
-that makes the estimated $\beta$ in equation \ref{basic_reg} equal to zero when financing cost --using different $r$'s-- is the dependent variable) is a staggering 8,190 percent per year.
-We find this discount rate implausibly high even for this credit constrained population\footnote{For comparison, \cite{Levin} find that a discount rate of 1,415 per year for subprime borrowers in the US is too high to be believable.}, casting doubt on high discount rates as explanation for low demand for commitment.
-%\footnote{In the baseline survey we give respondents a hypothetical choice between $100$ pesos tomorrow or $150$ pesos in one month (an implicit yearly interest rate of {12,800\%}) and only 30\% chose the later one.}
-
-%\vspace{.2in}
-%\noindent All in all, present bias with (partial) naivete is the more likely explanation for low commitment demand in our case.
-Moreover, Section \ref{model} shows that present bias with (partial) naivete is able to qualitatively explain all the main findings of the paper, not just low demand for commitment.
-
-\section{Viewing the results through a simple model} \label{model}
-
-\textcolor{red}{Need to decide Whether we keep this section or no.}
-
-Although the empirical results are striking and stand alone, this section refers to the model of \cite{John} to interpret our empirical results.
-The model is stylized but incorporates important features of our context.
-It allows for negative income shocks which we think are prevalent in this population.
-%The shock generates a cost of committing to monthly payments and could potentially be a reason for low take up.
-It also features clients with present biased time preferences --allowing for partial naivete-- choosing to save to pay for an expense, and with the opportunity to make a commitment to save and pay.
-These two features parsimoniously explain several facts about the context --like overconfidence in recovering the pawn--, and about the results --e.g.
-that forcing commitment seems to help.
-We intend the model only as a very stylized approximation to our context, and we use it only to help us organize the interpretation of the empirical results, not as a literal description of reality.
-%Third, it allows for a simple way to model commitment afforded by late payment fees.
-%Nonetheless, the model abstracts from several details of the context.
-Even with these abstraction it allows us to explain our six main results listed in Section \ref{explanations_recap} below.
-
-The model has three periods.
-In period $0$ the client is either allocated to the status quo, the Forced Commitment contract, or a choice between the two.
-In period  $1$ the client decides to save to pay the monthly installment or not save, and in period $2$ the client makes the payment to recover her pawn (or not).
-\ref{appendix_c} provides detail; here we just summarize results.
-The results have to be interpreted conditional on consumers going to Lender $P$'s branch to get a loan and being randomly allocated to the different contracts.
-%We do not model selection into pawnshop borrowing.
-
-\vspace{.1in}
-\noindent \textbf{Result 1}: Present biased clients default more in the status quo contract.
-
-\vspace{.1in}
-\noindent \textbf{Result 2}: Imposing a fee  for late payments as in the frequent payment contract weakly decreases default (for present biased clients only), and strictly decreases default for a high enough fee.
-
-\vspace{.1in}
-\noindent \textbf{Result 3}: Demand for commitment.
-Given a fee for late installment payment, (a) Neoclassical clients will never demand commitment; (b) Present-biased sophisticated clients will prefer the Forced Commitment contract over the status quo contract for intermediate values of present bias; (c) naive clients will demand commitment also for intermediate but different values of present bias, and depending on parameter values may demand less commitment than sophisticated clients.\footnote{Partially naive clients will on the one hand demand more commitment than sophisticated clients since they believe (incorrectly) that a smaller fee will motivate them to pay, while on the other hand they may demand less commitment since they think they can save and pay on their own.
-In the light of this model we seem to be finding that the latter effect dominates.
-%Whether they demand more or less than sophisticated clients depends on the empirical distribution of $\beta$ and $\hat{\beta}$.
-}
-
-\vspace{.1in}
-\noindent \textbf{Result 4}: Overconfidence.
-Only naive clients will be overconfident about the probability of recovery.
-This will be true whether they have the status quo or the Forced Commitment contract.
-Overconfidence is increasing in the degree of partial naivete.
-
-\vspace{.1in}
-\noindent \textbf{Result 5}: Welfare.
-(a) Neoclassical consumers' welfare strictly decreases when we force clients into the fee-commitment contract instead of the status quo contract, because we expose them to risk of them not being able to pay for the installment; and does not change when we offer them a choice between the contracts.
-(b) The welfare of sophisticated present biased consumers weakly increases when we give them choice, and it strictly increases  under intermediate values of present bias (when they would choose the fee-commitment contract themselves).
-Forcing them into the fee-commitment contract increases welfare only if they themselves would chose it.
-(c) Forcing can be welfare improving for the naive under some parameter values (see \ref{appendix_c}).
-
-\vspace{.1in}
-\noindent \textbf{Result 6}: Welfare and ex-post observed behavior.
-Our finding that the Forced Commitment contract increases pawn recovery is ``a sign'' of higher welfare (although not a sufficient condition).
-
-\subsection{Interpretation}
-
-The model is very parsimonious but powerful and it can potentially explain all our empirical findings qualitatively.\footnote{The model is sufficiently stylized that we think we would not gain much from estimating it.
-Furthermore we have no data on income shocks which figure prominently in the model.
-\cite{Ted} and \cite{Aprajit} are two very recent models that combine a field experiment with commitment contracts and estimation of present bias parameters.} First, it can explain why default is high in the status-quo contract, namely that clients are present biased and have no commitment devices.
-Second, it can explain why clients are overconfident in our data, namely by virtue of naivete about present bias.
-Under the model naivete is necessary to explain this.
-Third, it can also explain why the fee forcing contract induces lower default, but not for everyone: namely that it makes the incentive compatibility constraint for payment binding for the present biased, while it was not binding in the status quo contract.
-Fourth, it can also explain why there is low demand for commitment even if it seems to improve welfare: namely that there is a small share of neoclassical and sophisticated clients, and at the same time naifs have a present biased parameters values in the region in which they think they can save on their own.
-Fifth, it explains non-zero demand for commitment for a set of clients.
-Sixth, it can explain why clients exposed to the Forced Commitment contract are more likely to come back namely those naifs whose welfare increased as a result of being forced into the fee-commitment contract.\footnote{Those with $\hat{\beta_i}>\beta_{SQ}>\beta$.}
-
-\subsection{Other potential explanations: recap} \label{explanations_recap}
-
-There may be other interpretations of the empirical findings, but the bar is high. An alternative explanation will need to explain the 6 facts below:
-
-\begin{enumerate}
-\itemsep0em 
-\item High (although ex-post inefficient) default in status quo contract.
-\item Overconfidence about pawn recovery.
-\item Forcing commitment increases pawn recovery.
-\item Small demand for commitment...
-\item ...but positive demand for commitment.
-\item Forcing commitment makes clients more likely to come back.
-\end{enumerate}
-
-Let us consider alternative explanations in isolation (i.e. just considering one change or feature at a time with respect to a neoclassical model):
-
-\vspace{.1in}
-\noindent \textbf{Alternative 1: Strong prevalence of income shocks.} This could explain (4) and (1), but not why forcing helps, (3) and (6), nor why there is overconfidence, (1).
-It would also not explain why clients come to pawn in the first place and then default, (2), as they would weight in on the high chance of losing the pawn.
-
-\vspace{.1in}
-\noindent \textbf{Alternative 2: High time discounting}.
-This could not explain (1) nor (5) nor (6).
-It could qualitatively explain (4), but as we say in section \ref{sec:demand} quantitatively it would require unbelievably high discount rates.
-
-\vspace{.1in}
-\noindent \textbf{Alternative 3: Risk aversion.} We already discussed and rejected risk aversion in section \ref{sec:demand}, although using strong assumptions in the process.
-Risk or ambiguity aversion could still play a role in explaining 4 and should be investigated in future research.
-However it would hardly explain (1), (2), (5), or (6).
-
-\vspace{.1in}
-\noindent \textbf{Alternative 4: Misunderstanding the contracts.}\footnote{This is a potential criticism of \textit{any} paper offering choice, and one that is non-falsifiable if the critic has free reign to propose how the contracts are perceived in the subject's mind.} We were very aware of the importance of clients understanding the contract in order to infer preferences from choice.
-That is why we made a strong effort for clients to understand the contracts (see subsection \ref{implementation}).
-Note however that while clients making purely random mistakes could explain why 10\% demand commitment ---i.e.
-(4) and (5)--- it would not explain the rest of the findings, nor why the Soft Commitment (see below) had more take up that the fee-commitment, or why we can statistically predict take-up with significant accuracy (see Figure \ref{interactions_takeup} and Table \ref{Table_compliance}).
-
-\vspace{.1in}
-\noindent \textbf{Alternative 5 (behavioral): Forgetting to pay/salience.} Frequent payments may act as a reminder to save and recover the pawn.
-This would try to explain (1) by appealing to people forgetting to pay, and (3), (5), and (6) by appealing to frequent payment acting as reminders (i.e.
-there being demand for reminders).
-It would not explain (2) or (4) which are critical in the paper.
-However even for (1) it seems to us a stretch to explain people losing a valuable pawn by forgetting to pay it.
-Since the Soft Commitment installment contract did not change behavior (as shown below) this explanation would also require us to posit that only fees acts as reminders, not promises.
-
-\vspace{.1in}
-\noindent \textbf{Alternative 6 (behavioral): Income shocks overconfidence}.
-One could also easily introduce in the overconfidence about income shocks in the model of \ref{appendix_c}\footnote{Say with $\widehat{\lambda} <\lambda$.
-The effect on demand for commitment is uncertain since on the one hand it decreases $\beta_{SQ}$ decreasing demand, but on the other a smaller $F$ is needed to make the IC binding, making commitment less costly.}.
-This would leave default unchanged in both the status quo and the fee forcing contract thus would not explain (3), %since $F_{min}(\beta,\widehat{\lambda})<F_{min}(\beta,\lambda)$.
-% $\widehat{\lambda} <\lambda$ alone 
-It would not explain (5) or (6) either as demand for commitment would be zero without present bias.
-
-%\vspace{.1in}
-%\noindent \textbf{Alternative 6: Learning that they are more present biased than they thought.} This is essentially the same as our proposed explanation (i.e.
-not an alternative) with the additional prediction that more people will demand commitment if they just experienced it, an specially appealing one in light of finding (6).
-We are sympathetic to the learning hypothesis and in fact it is \cite{Alcohol}'s main conjecture about why he finds strong demand for commitment while most other studies don't.\footnote{Close to ninety percent of our subjects claim to have pawned before.
-We find that experience does not predict positive take up in our sample correlationally.} To test it we would ideally need to give choice to a group of people that randomly experienced the fee-commitment vs those that did not, and test if the former demand it more.
-Unfortunately we did not do this experiment and we have very limited data to try it: {210 (6\%)} clients were given a choice in a second pawns in our experiment after being randomly assigned to the status quo or Forced Commitment contract.
-%\end{comment}
-
-\vspace{.1in}
-We do not claim that the model in the Appendix is the only possible explanation of our empirical findings, but it is a parsimonious explanation of all of them.
+\end{comment}
 
@@
  \scriptsize
+
+ \noindent \hl{ISAAC, CAN YOU EXPLAIN IN THE NOTE WHAT THIS TABLE IS? HOW ARE VARIABLES DEFINED, AND WHAT ARE THE COLUMNS AND THE SAMPLE }
 %\textit{Do file: } \texttt{ss\_att.do}
@@
 \end{table}
-
+\vspace{-.3in}
 \scriptsize {
-\noindent This table presents balance tests for the administrative data (Panel A) and survey data for those that pawned (Panel B) and for all (Panel C).
+\noindent This table presents balance tests for the administrative data (Panel A) and survey data for those that pawned (Panel B).
 The first column ``Overall'' presents data for all arms together.
@@
 Finally, the survey response rate is the percentage of clients in the admin data for whom we have a baseline survey.
-Panel C has the same variables, except for the last one.
+%Panel C has the same variables, except for the last one.
 ``\% ended up pawning'' measures the fraction of those that answered the survey that ended up pawning that day in that branch.
@@
 
-\vspace{3ex}
-
-%\begin{table}[H]
-%\caption{Determinants of Choice}
-%\label{det_choose}
-%\begin{center}
-%\scriptsize{\input{./Tables/determinants_choose.tex}}
-%\end{center}
-% \scriptsize
-
-%\textit{Do file: } \texttt{determinants\_choose.do}
-%\end{table}
-
-\scriptsize {
-\noindent 
-}
-
 \newpage
-\begin{landscape}
+
 \vspace{.2in}
@@
 \end{center}
-
+\noindent \hl{ISAAC, CAN YOU EXPLAIN IN THE NOTE WHAT THIS TABLE IS? HOW ARE VARIABLES DEFINED, AND WHAT ARE THE COLUMNS AND THE SAMPLE }
 %\textit{Do file: } \texttt{decomposition\_main\_te.do}
@@
 \newpage
-
+\begin{landscape}
 \begin{table}[H]
@@
  \scriptsize
-
 %\textit{Do file: } \texttt{fc\_robustness.do}
@@
 \cleardoublepage
-\begin{landscape}
+
+%\begin{landscape}
 
@@
 \end{table}
-\end{landscape}
+%\end{landscape}
 
 \cleardoublepage
-
-\begin{landscape}
-
-\begin{table}[H]
-\caption{Multiple-loans robustness check}
-\label{multiple_loans}
-\begin{center}
-\scriptsize{\input{./Tables/multiple_loans.tex}}
-\end{center}
- \scriptsize
-
-%\textit{Do file: } \texttt{multiple\_loans.do}
-\end{table}
-
-\end{landscape}
-
-\cleardoublepage
-
-\begin{table}[H]
-\caption{Treatment effects on the soft arms}
-\label{impact_soft}
-\begin{center}
-\scriptsize{\input{./Tables/decomposition_te_soft.tex}}
-\end{center}
- \scriptsize
-
-%\textit{Do file: } \texttt{decomposition\_te\_soft.do}
-\end{table}
 
@@
 The ToT is computed as the usual LATE with one-sided non-compliance between the choice and control arm, and the TuT is the LATE on non-compliers.
+ \hl{ISAAC: NEED TO ADD THE OTHER TWO TREATMENT EFFECTS THAT FRANK DESCRIBED}
 %\textit{Do file: } \texttt{tot\_tut.do}
 \end{table}
-
-\begin{table}[H]
-\caption{Experience with frequent payment contract raises future demand for it}
-\label{learning_not_doing}
-\begin{center}
-\scriptsize{\input{./Tables/learning_not_doing.tex}}
-\end{center}
- \scriptsize 
-%\textit{Do file: } \texttt{learning\_not\_doing.do}
-\end{table}
-
-% \begin{table}[H]
-% \caption{Learning analysis with experimental data}
-% \label{learning_reg}
-% \begin{center}
-% \scriptsize{\input{./Tables/learning_exp.tex}}
-% \end{center}
-%  \scriptsize This table shows choice after experience of an experimental arm in the previous loan.
-Columns (1)-(4) restrict the sample to borrowers whose second loan falls in the Choice commitment arm.
-Dependent variable in columns (5)-(8) is `ever chooses commitment', a dummy variable defined to be $0$ if borrower didn't take a loan, or if borrower took a loan and didn't choose commitment, and it is $1$ only when borrower took a loan and chose commitment.
-% %\textit{Do file: } \texttt{learning\_reg.do}
-% \end{table}
-
-% \begin{table}[H]
-% \caption{Differential attrition}
-% \label{diff_att}
-% \begin{center}
-% \scriptsize{\input{./Tables/differential_attrition.tex}}
-% \end{center}
-%  \scriptsize This table shows differential attrition in the experimental arms for (1) experiencing a second arm and (2) when the second loan is a Choice commitment arm.
-% %\textit{Do file: } \texttt{learning\_reg.do}
-% \end{table}
 
@@
 \begin{figure}[H]
-     \caption{Contract Terms Summary, and Promise Slip}
+     \caption{Contract Terms Summary}
     \label{PaperSlip}
     \begin{center}
-    \begin{subfigure}{0.65\textwidth}
-    \caption{Receipt for client}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/TicketLenderP.png}
-    \end{subfigure}
-
-    \vspace{3ex}
-    \begin{subfigure}{0.65\textwidth}
-    \caption{Personal promise signed by client}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/Personal Promise2.png}
-    \end{subfigure}
+    %\begin{subfigure}{0.65\textwidth}
+    %\caption{Receipt for client}
+     %   \centering
+        \includegraphics[width=0.65\textwidth]{Figuras/TicketLenderP.png}
+    %\end{subfigure}
+
+    %\vspace{3ex}
+    %\begin{subfigure}{0.65\textwidth}
+    %\caption{Personal promise signed by client}
+     %   \centering
+    %    \includegraphics[width=\textwidth]{Figuras/Personal Promise2.png}
+    %\end{subfigure}
     \end{center}
     \scriptsize
-        The top of this figure is a sample receipt that was given to clients that got assigned to the fee-forcing contract (the font and format were changed to protect Lender's P identity).
+        We show a sample receipt that was given to clients that got assigned to the fee-forcing contract (the font and format were changed to protect Lender's P identity).
 We want to highlight the salience of some items.
@@
 Third, there is a calendar for payments clearly specifying the dates and amounts to pay each month.
-The bottom panel of the figure shows a ``promise slip'', the paper that those who were assigned (or chose) to the monthly payment with promise had to sign to make the promise salient.
+%The bottom panel of the figure shows a ``promise slip'', the paper that those who were assigned (or chose) to the monthly payment with promise had to sign to make the promise salient.
 It emphasizes that the client is giving his word, and that the promise is not a legal document.
@@
 Financial cost is defined as the sum of payments made by a client towards recovering her pawn + the cost of the pawned piece when she ends up losing it.
-We plot separately the financial cost for those who lose the pawn (blue) and those that recover it (transparent).
-Panel (b) is analogous but we normalized the financial cost, dividing it by the loan size.
+We plot separately the financial cost for those who lose the pawn (blue) and those that recover it (transparent), and those who after many cycles have refinanced a continuing loan (pink).
+Panel (b) is analogous but displays the APR.
 %Given that the loan lasts close to 90 days, bringing payments to present value makes little difference.
+         \hl{ISAAC: ARE THESE USING ALL THE DATA PERIODS? OR JUST 115 DAYS?}
       %\footnotesize{ } \textit{Do file: }  \texttt{hist\_fc.do}
@@
      \scriptsize
+     \hl{ISAAC: CAN YOU DESCRIBE THESE? ALSO: I THINK IT IS BETTER TO USE PERCENT INSTEAD OF COUNT}
       %\footnotesize{ \textit{Do file: }  \texttt{hist\_payments.do}}
@@
 
-\begin{figure}[H]
-        \caption{Survival graph}
-    \label{survival_graph}
-    \begin{center}
-   \begin{subfigure}{0.49\textwidth}
-   \caption{Ended contract}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/survival_graph_ended.pdf}
-    \end{subfigure} 
-   \begin{subfigure}{0.49\textwidth}
-   \caption{Recovery}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/survival_graph_unpledge.pdf}
-    \end{subfigure}     
-    \end{center}
-     \scriptsize  This Figure shows the accumulated percentage of recovery in time by treatment arm. 
-     %\textit{Do file: }  \texttt{survival\_graph.do}
-\end{figure}
-
-\begin{figure}[H]
-        \caption{\% of payment over time}
-    \label{porc_payment_over_time}
-    \begin{center}
-   \begin{subfigure}{0.49\textwidth}
-        \caption{Unconditional}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/cumulative_porc_pay_time.pdf}
-    \end{subfigure} 
-   \begin{subfigure}{0.49\textwidth}
-        \caption{Conditional on default}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/cumulative_porc_pay_time_default.pdf}
-    \end{subfigure}     
-    \end{center}
-     \scriptsize  This Figure shows the accumulated percentage of recovery in time by treatment arm. 
-     %\textit{Do file: }  \texttt{cumulative\_porc\_pay\_time.do}
-\end{figure}
-
 \cleardoublepage
-
-\begin{figure}[H]
-     \caption{Main treatment effects}
-    \label{main_te}
-    \begin{center}
-    \begin{subfigure}{0.75\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/main_te.pdf}
-    \end{subfigure}
-    \end{center}
-    \scriptsize
-    This figure shows the estimated treatment effect of ``forcing'' the frequent payment commitment contract using fees, compared to the control, and the effect of the choice arm, compared to the control, for the main outcomes of interest.
-The treatment effects are indicated in standard deviations, together with 95\% confidence intervals.
-\end{figure}
-
-\begin{figure}[H]
-     \caption{Several definitions of cost}
-    \label{robustness_fc}
-    \begin{center}
-    \begin{subfigure}{0.75\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/fc_robustness.pdf}
-    \end{subfigure}
-    \end{center}
-    \scriptsize
-    This figure shows treatment effects using several measures of cost.
-The first definition is our main definition of cost, which uses the appraised value of the pawn.
-The second definition uses the subjective (self-reported) value for the pawn.
-The third and fourth definition adds the travel cost for the treatment arms.
-The last definition is a `fully adjusted' scenario that doesn't include the interest that is mechanically saved by paying early since this is the piece of the Forced-commitment contract that has a foregone liquidity cost for the borrower, on top of adding travel costs.
-We also compute APR versions of the above measures.
-    Finally, `APR - interests'  The treatment effects are indicated in standard deviations, together with 95\% confidence intervals.
-
-%\textit{Do file: } \texttt{fc\_robustness.do}
-\end{figure}
-
-\cleardoublepage
-
-\begin{figure}[H]
-     \caption{Probability of ever pawning again}
-    \label{prob_ever_pawn}
-    \begin{center}
-  \begin{subfigure}{0.49\textwidth}
-     \caption{Reincidence after $n$ days}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/prob_reincidence_after.pdf}
-    \end{subfigure}        
-    \begin{subfigure}{0.49\textwidth}
-     \caption{Reincidence within $n$ days}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/prob_reincidence_within.pdf}
-    \end{subfigure}
-    \end{center}
-    \scriptsize
-    This figure shows
-      %\textit{Do file: }  \texttt{repeat\_loans.do}
-\end{figure}
-
-\cleardoublepage
-
-\begin{figure}[H]
-     \caption{Effect of Soft Commitment Arms}
-    \label{effect_promises}
-    \begin{center}
-    \begin{subfigure}{0.45\textwidth}
-        \caption{Main outcomes}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/soft_te.pdf}
-    \end{subfigure}
-        \begin{subfigure}{0.45\textwidth}
-            \caption{Several definitions of cost}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/fc_robustness_soft.pdf}
-    \end{subfigure}
-     %  \begin{subfigure}{0.45\textwidth}
-     %  \caption{Q-regs on Financial Cost (in MXN)}
-     %   \centering
-     %   \includegraphics[width=\textwidth]{Figuras/soft_qreg_fc_admin.pdf}
-    %\end{subfigure}
-     %   \begin{subfigure}{0.45\textwidth}
-     %    \caption{Q-regs on effective APR}
-     %   \centering
-     %   \includegraphics[width=\textwidth]{Figuras/soft_qreg_apr.pdf}
-    %\end{subfigure}
-    \end{center}
-    \scriptsize
-    Panel (a) shows the main outcomes for the soft arms.
-The treatment effects are indicated in standard deviations, together with 95\% confidence intervals.
-Panel (b) shows the treatment effects on the several definitions of cost for the soft arms.
-
-%\textit{Do file: } \texttt{soft\_te,do, fc\_robustness\_soft.do}    
-\end{figure}
-
-\cleardoublepage
-
-\begin{figure}[H]
-    \caption{Fan \& Park bounds for benefit in APR\% }
-    \label{fan_park_bounds}
-    \begin{center}
-    \begin{subfigure}{0.675\textwidth}
-        \caption{APR}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/fan_park_bounds_apr.pdf}
-    \end{subfigure}
-    \end{center}
-
-%\textit{Do file: } \texttt{fan\_park\_bnds,do}       
-\end{figure}
-
-\begin{figure}[H]
-     \caption{Quantile regressions}
-    \label{qregs}
-    \begin{center}
-    \begin{subfigure}{.45\textwidth}
-      \caption{Financial cost (in MXN)}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/qreg_fc_admin.pdf}
-    \end{subfigure}
-     \begin{subfigure}{0.45\textwidth}
-    \caption{Effective APR}
-       \centering
-      \includegraphics[width=\textwidth]{Figuras/qreg_apr.pdf}
-    \end{subfigure}
-    \end{center}
-         \scriptsize
-     This figure plots the effects on different quantiles (15th, 25th, 50th, 75th, 85th percentile) of the distribution of financial cost, and APR, for the Forced-commitment and Choice-commitment arms.
-      %\footnotesize{ } \textit{Do file: }  \texttt{main\_qreg.do}
-\end{figure}
-
-\begin{figure}[H]
-    \caption{Non-experimental analysis of Choosers and Non-Choosers}
-    \label{qreg_chooser_nonchooser}
-    \begin{center}
-    \begin{subfigure}{.45\textwidth}
-      \caption{Financial Cost (Hard commitment)}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/qreg_hard_fc_admin.pdf}
-    \end{subfigure}
-     \begin{subfigure}{0.45\textwidth}
-      \caption{APR (Hard commitment)}
-       \centering
-      \includegraphics[width=\textwidth]{Figuras/qreg_hard_apr.pdf}
-    \end{subfigure}
-    \begin{subfigure}{.45\textwidth}
-      \caption{Financial Cost (Soft commitment)}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/qreg_soft_fc_admin.pdf}
-    \end{subfigure}
-     \begin{subfigure}{0.45\textwidth}
-      \caption{APR (Soft commitment)}
-       \centering
-      \includegraphics[width=\textwidth]{Figuras/qreg_soft_apr.pdf}
-    \end{subfigure}    
-    \end{center}
-        \scriptsize
-        This figure is analogous to Figure \ref{fc_pro2}.
-It measures the effect of being given \textit{choice} between the frequent payment commitment contract with fees and the status-quo contract, versus being \textit{``forced''} into the status-quo contract (control).
-Again it focuses our two main outcomes: financial cost and an indicator for losing the pawn.
-Circles present the treatment effects.
-The figures also presents differences in these two outcomes for those who chose the frequent payment commitment contract versus the whole control group (squares-NSQ), and also for those who chose the status quo contract versus the whole control group (triangles-SQ).
-Note that these two comparisons are not pure causal effects since people who chose the frequent payment commitment contract are different from those that do not.
-That is: the squares and triangles combine selection and treatment effects.
-Finally, for comparison purposes, the blue diamond displays the effects of forcing them into the frequent payment commitment contract and are just transcribed from Figure \ref{fc_pro2} above.
-      %\textit{Do file: }  \texttt{soft\_qreg.do, qregs\_choosers\_nonchoosers.do}
-\end{figure}
 
@@
 \begin{figure}[H]
-     \caption{Heterogeneous Treatment Effects}
-    \label{heterogeneous_effects}
+    \caption{Fan \& Park bounds for benefit in APR\% }
+    \label{fan_park_bounds}
     \begin{center}
-    \begin{subfigure}{.45\textwidth}
-      \caption{Financial cost (in MXN)}
+    \begin{subfigure}{0.6\textwidth}
+        \caption{APR}
         \centering
-        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_pro_2.pdf}
-    \end{subfigure}
-     \begin{subfigure}{0.45\textwidth}
-    \caption{Effective APR}
-       \centering
-      \includegraphics[width=\textwidth]{Figuras/he_dist_apr_pro_2.pdf}
-    \end{subfigure}
-     \begin{subfigure}{0.45\textwidth}
-    \caption{Default}
-       \centering
-      \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_2.pdf}
-    \end{subfigure}  
-     \begin{subfigure}{0.45\textwidth}
-    \caption{Recovery}
-       \centering
-      \includegraphics[width=\textwidth]{Figuras/he_dist_des_c_pro_2.pdf}
+        \includegraphics[width=\textwidth]{Figuras/fan_park_bounds_apr.pdf}
     \end{subfigure}
     \end{center}
-         \scriptsize
-     plots the distribution of the heterogeneous treatment effects on financial cost, estimated using \cite{atheygrf}.
-  %\footnotesize{ } \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}
+
+%\textit{Do file: } \texttt{fan\_park\_bnds,do}       
 \end{figure}
@@
 \begin{figure}[H]
-    \caption{Choice of contracts and treatment effects}
+    \caption{Choice of contracts and treatment effects (ToT \& TuT)}
     \label{choose_wrong}
@@
         \centering
-        \includegraphics[width=\textwidth]{Figuras/line_cw_apr_te_cf.pdf}
+        \includegraphics[width=\textwidth]{Figuras/line_cw_apr_tot_tut.pdf}
 
@@
         \centering
-        \includegraphics[width=\textwidth]{Figuras/money_cw_apr_te_cf.pdf}
+        \includegraphics[width=\textwidth]{Figuras/money_cw_apr_tot_tut.pdf}
 
@@
 
-\begin{figure}[H]
-    \caption{Choice of contracts and treatment effects (ToT \& TuT)}
-    \label{choose_wrong}
-    \begin{center}
-        \begin{subfigure}{0.45\textwidth}
-        \caption{Mistakes in choice arm}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/line_cw_apr_tot_tut.pdf}
-
-    \end{subfigure}
-        \begin{subfigure}{0.45\textwidth}
-        \caption{Financial value of mistake}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/money_cw_apr_tot_tut.pdf}
-
-    \bigskip
-
-    \end{subfigure}
-        \begin{subfigure}{0.45\textwidth}
-        \caption{\% better when forced to forced commitment}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/line_better_forceall_apr_te_cf.pdf}
-
-    \end{subfigure}
-    %     \begin{subfigure}{0.45\textwidth}
-    %     \caption{\footnotesize{Effect of CATE benefit vs predicted take-up}}
-    %     \centering
-    %     \includegraphics[width=\textwidth]{Figuras/benefit_choice.pdf}% takeuppr_def.pdf 
-    % \end{subfigure}
-
-    \end{center}
-        \scriptsize
-        In Panel (a) we estimate what the treatment effect of the commitment contract \textit{would have been} for all subjects in the choice arm if they had been forced into the fee-commitment contract.
-To do this we proceed in two steps.
-First, we estimate treatment effects in the forcing arm by comparing the Forced Commitment arm against the status quo arm.
-We let these effects be heterogeneous as a function of our $x$'s using \cite{atheygrf}'s methodology of causal forests.
-Second, we extrapolate these treatment effects based on the choice arm using the same $x$'s.
-Once we have personalized counterfactual treatment effects in the choice arm we calculate what fraction of subjects in the choice arm incurred in financial costs that are  $> z$\% than if they had chosen the opposite contract of what they actually chose, were $z$\% is defined as a fraction of the loan.
-$z$\% is a level of tolerance we can vary and we plot it in the X-axis.
-The left Y-axis measures the fraction of subjects that would have been better by a margin of $z$\% if they changed their choice, and the right Y-axis measures the amount of money ``left on the table''.
-We use bootstrap to tighten the confidence intervals (CIs).
-\cite{atheygrf}'s heterogeneous treatment effect using GRF is asymptotically normal.
-We compute the HTE ($\mu$) together with standard errors ($\sigma$) .
-For every pledge, we draw a random effect from a normal distribution with parameters ($\mu$,$\sigma^2$), and compute via bootstrap the percentage that choose wrong, along normal-approximation CIs (results are robust if we use instead percentile CIs or bias-corrected CIs) .
-This allows us to estimate a distribution for the upper and lower bound CIs, which we then use to obtain a 95\% CI.
-Panel (b) is analogous to Panel (a) except that it does the exercise separately for clients we classified as overconfident ($OC_i:=\mathbbm{1}(P^s_i-\widehat{P_i(X_i)}>0))$ and those we classified as not overconfident.
-Panel (c) simulates what percentage would be better by at least $z$ if we forced everybody of those in the Commitment Choice arm into the fee-commitment contract.
-        % Panel (d) asks whether it is the case that people with larger causal benefits from the Forced Commitment contract would be more likely to select that contract.
-To do this we proceed in two steps as well.
-First we estimate a flexible model of take-up of the fee commitment contract \textit{in the choice arm} using random forests, and from this model obtain a probability $P(x_i)$ of choosing the Forced Commitment contract for a client with characteristics $x_i$.
-We extrapolate this model to clients in the Forced Commitment arm to estimate what would they have chosen if we had given them choice.
-        % Figure (d) plots $\widehat{P(x_i)}$ in the X-axis using a binscatter that splits the X-axis in 100 percentile bins.
-The Y-axis plots the heterogeneous treatment effects of the fee forcing contract on the probability of losing the pawns (more negative means then more likely to recover it), averaged for the respective x-axis bin.
-Positive assortative selection would mean a negative relationship: those who benefit more by treatment and lose the pawn less are \emph{less} likely to choose it.
-Using all bins we estimate a slope of zero in the relationship.
-Using the 80 right most points, we estimate a \textit{positive} relationship.
-        %\textit{Do file: }  \texttt{choose\_wrong\_quant\_wrong.do, choose\_wrong\_quant\_wrong\_decomposition.do}
-\end{figure}
-
 \cleardoublepage
-
-\begin{figure}[H]
-    \caption{Effect of CATE benefit vs predicted take-up}
-    \label{HTE_vs_propensity}
-    \begin{center}
-    \begin{subfigure}{0.475\textwidth}
-        \caption{APR benefit}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/benefit_choice_tau_apr.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.475\textwidth}
-        \caption{Repayment}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/benefit_choice_tau_des.pdf}
-    \end{subfigure}
-     \begin{subfigure}{0.475\textwidth}
-        \caption{Default}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/benefit_choice_tau_def.pdf}
-    \end{subfigure} 
-    \end{center}
-     \scriptsize   This figure asks whether it is the case that people with larger causal benefits from the Forced Commitment contract would be more likely to select that contract.
-To do this we proceed in two steps.
-First we estimate a flexible model of take-up of the commitment-fee contract \textit{in the choice arm} using gradient boosting classification, and from this model obtain a probability $P(x_i)$ of choosing the Forced Commitment contract for a client with characteristics $x_i$.
-We extrapolate this model to clients in the Forced Commitment arm to estimate what would they have chosen if we had given them choice.
-We plot $\widehat{P(x_i)}$ in the X-axis using a binscatter that splits the X-axis in 100 percentile bins.
-The Y-axis plots the heterogeneous treatment effects of the (a) effective APR (in the positive scale) and (b) repayment, averaged for the respective x-axis bin.
-Positive assortative selection would mean a negative relationship: those who benefit more by treatment and lose the pawn less are \emph{less} likely to choose it.
-          %\footnotesize{ \textit{Do file: }  \texttt{benefit\_choice.do}}
-\end{figure}
 
@@
 
-%\begin{figure}[H]
-  %  \caption{Non-experimental analysis of Choosers and Non-Choosers}
-   % \label{fc_pro4}
-    %\begin{center}
-    %\begin{subfigure}{0.45\textwidth}
-     %   \caption{Financial cost}
-    %    \centering
-   %    \includegraphics[width=\textwidth]{Figuras/fc_te_pro_4.pdf}
-  %  \end{subfigure}
-   %     \begin{subfigure}{0.45\textwidth}
-  %      \caption{Financial Cost (quantile reg)}
- %       \centering
-  %      \includegraphics[width=\textwidth]{Figuras/fc_quantile_pro_4.pdf}
-%    \end{subfigure}
-%    \begin{subfigure}{0.5\textwidth}
-
-  %      \bigskip
-  %      \bigskip
-
- %       \caption{Lost Pawn}
- %       \centering
-%        \includegraphics[width=\textwidth]{Figuras/def_te_pro_4.pdf}
- %   \end{subfigure}
- %   \end{center}
- %       \scriptsize
- %       This figure is analogous to Figure \ref{fc_pro2}.
-It measures the effect of being given \textit{choice} between the frequent payment commitment contract with fees and the status-quo contract, versus being \textit{``forced''} into the status-quo contract (control).
-Again it focuses our two main outcomes: financial cost and an indicator for losing the pawn.
-Circles present the treatment effects.
-The figures also presents differences in these two outcomes for those who chose the frequent payment commitment contract versus the whole control group (squares-NSQ), and also for those who chose the status quo contract versus the whole control group (triangles-SQ).
-Note that these two comparisons are not pure causal effects since people who chose the frequent payment commitment contract are different from those that do not.
-That is: the squares and triangles combine selection and treatment effects.
-Finally, for comparison purposes, the blue diamond displays the effects of forcing them into the frequent payment commitment contract and are just transcribed from Figure \ref{fc_pro2} above.
-      %\textit{Do file: }  \texttt{fc\_te\_choice\_dec.do, def\_te\_choice\_dec.do, fc\_quantilereg\_choice\_dec.do}
-%\end{figure}
-
-%\begin{figure}[H]
- %   \caption{The effect of promises}
- %   \label{fc_pro5}
- %   \begin{center}
-
- %       \begin{subfigure}{0.45\textwidth}
-%        \caption{Financial cost -- Choice}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/fc_te_pro5_5.pdf}
-%    \end{subfigure}
-        %\begin{subfigure}{0.45\textwidth}
-        %\caption{Quantile regression}
-        %\centering
-        %\includegraphics[width=\textwidth]{Figuras/fc_quantile_pro_5.pdf}
-    %\end{subfigure}
- %   \begin{subfigure}{0.45\textwidth}
- %       \caption{Losing Pawn -- Choice}
- %       \centering
- %       \includegraphics[width=\textwidth]{Figuras/def_te_pro_5.pdf}
- %   \end{subfigure}
-
-%    \bigskip
- %   \bigskip
-
-  %      \begin{subfigure}{0.45\textwidth}
-   %     \caption{Financial cost -- Promise-forcing}
-    %%    \centering
- %       \includegraphics[width=\textwidth]{Figuras/fc_te_pro_3.pdf}
-%    \end{subfigure}
-%    \begin{subfigure}{0.45\textwidth}
-%        \caption{Losing Pawn -- Promise-forcing}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/def_te_pro_3.pdf}
-%    \end{subfigure}
-
- %   \end{center}
- %   \scriptsize
-  %  Panels (a) and (b) in this figure show the estimated treatment effects of ``forcing'' the frequent payment commitment contract using promises, compared to the status-quo (control) for financial cost (Panel a), and for an indicator of losing the pawn (Panel b).
-Panels (c) and (d) are analogous but focus on the effect of giving choice between frequent payment commitment contract using promises and the status quo contract.
-In Panel (a) each dot represents the estimated treatment effect for a different definition of financing cost, or for a different sub-population, and its 95\% confidence interval.
-From left to right, the first effect corresponds to using the gold value of the pawned piece in the definition of financial cost and discounting the payments to present value using a 7\% monthly rate; the second uses the subjective value of the pawn; the third is analogous to the second but adds transaction cost (transport+1 day's wage) per visit; and the fourth conditions on the population that paid any positive amount towards recovery of their pawn.
-Panel (b) plots the effect of not recovering the pawn: the leftmost coefficients compares all those assigned to the promise-forcing arm vs all those in the status quo contract, where the dependent variable=1 if the client has not recovered the pawn 230 days after pawning.
-The next coefficient defines the dependent variable=1 if the client has not recovered the pawn 120 days after pawning.
-The third coefficient conditions on paying a positive amount, and the fourth conditions on paying at least 30\% of the loan.
-Panels (b) and (c) measure the effect of being given \textit{choice} between the frequent payment commitment contract with promise and the status-quo contract, versus being \textit{``forced''} into the status-quo contract (control).
-Again it focuses our two main outcomes: financial cost and an indicator for losing the pawn.
-Circles present the treatment effects.
-The figures also presents differences in these two outcomes for those who chose the frequent payment commitment contract versus the whole control group (squares-NSQ), and also for those who chose the status quo contract versus the whole control group (triangles-SQ).
-That is: the squares and triangles combine selection and treatment effects.
-      %\footnotesize{ } \textit{Do file: }  \texttt{fc\_te\_choice\_dec.do, def\_te\_choice\_dec.do, fc\_te.do, def\_te.do }
-%\end{figure}
-
-% \begin{figure}[H]
-%     \caption{The effect of the Forced Commitment treatment}
-%     \label{fc_pro2}
-%     \begin{center}
-%     \begin{subfigure}{0.42\textwidth}
-%         \caption{Financial cost (MXN)}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/fc_te_pro_2.pdf}
-%     \end{subfigure}
-%         \begin{subfigure}{0.42\textwidth}
-%         \caption{Financial cost (quantile reg)}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/fc_quantile_pro_2.pdf}
-%     \end{subfigure}
-
-%         \bigskip
-
-%     \begin{subfigure}{0.42\textwidth}
-%         \caption{Financial cost (HTE)}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_disc_pro_2.pdf}
-%     \end{subfigure}
-%     ~
-%     ~
-%     \bigskip
-%     \begin{subfigure}{0.42\textwidth}
-%         \caption{Lost pawn}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/def_te_pro_2.pdf}
-%     \end{subfigure}
-%     \begin{subfigure}{0.42\textwidth}
-%     \caption{Losing Pawn}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_2.pdf}
-%     \end{subfigure}
-
-%     \end{center}
-%         \scriptsize
-
-%       %\textit{Do file: }  \texttt{fc\_te.do, def\_te.do, fc\_quantilereg.do}
-% \end{figure}
-
-% \scriptsize {
-% \noindent This figure shows the estimated treatment effect of ``forcing'' the frequent payment commitment contract using fees, compared to the status-quo (control).
-In Panel (a) each dot represents the estimated treatment effect for a different definition of financing cost, or for a different sub-population, and its 95\% confidence interval.
-From left to right, the first effect corresponds to using the gold value of the pawned piece in the definition of financial cost and discounting the payments to present value using a 7\% monthly rate - to the left we have a decomposition of the financial cost in its four components from left to right (1) Discounted payments to capital, (2) Payed fees, (3) Payed interest, (4) Cost of losing pawn; the second uses the subjective value of the pawn; the third is analogous to the second but adds transaction cost (transport+1 day's wage) per visit; the fourth conditions on the population that paid any positive amount towards recovery of their pawn; the fifth conditions on the sub-population of the treatment group that paid a fee and compares these to all the control group.
-Panel (b) plots the effects on different quantiles of the distribution of financial cost (using the first definition): 15th, 25th, 50th, 75th, 85th percentile.
-Panel (c) plots the distribution of the heterogeneous treatment effects on financial cost, estimated using \cite{atheygrf}.
-Panel (d) Measures the effect of treatment on the likelihood of losing their pawn.
-The first coefficient compares all the treatment group vs all the control using 230 days after pawning to define the dependent variable; the second defines it using 120 days.
-The third coefficient from the left conditions on the population that paid any positive amount towards recovery of their pawn (which in theory may be endogenous but empirically we showed not to be affected by treatment).
-Finally, Panel (e) shows the distribution of heterogeneous treatment effects of the probability of losing the pawn.
-% the effect on ``repeat purchase''.
-That is likelihood of doing an additional pawn (in treatment vs control) after having been subjected to treatment for at least 75 days.
-The second coefficient estimates the regression conditional on recovering the pawn {in both treatment and control}, and the rightmost coefficient compares those above the median treatment effect in financial cost savings, {versus all the control group.}
-% }
-
-% \begin{figure}[H]
-%     \caption{The effect of the Forced Commitment treatment}
-%     \label{fc_pro2}
-%     \begin{center}
-%     \begin{subfigure}{0.42\textwidth}
-%         \caption{Effective cost/loan ratio}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/eff_te_pro_2.pdf}
-%     \end{subfigure}
-%         \begin{subfigure}{0.42\textwidth}
-%         \caption{Financial cost (quantile reg)}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/eff_quantile_pro_2.pdf}
-%     \end{subfigure}
-
-%         \bigskip
-
-%      \begin{subfigure}{0.42\textwidth}
-%          \caption{Financial cost (HTE)}
-%          \centering
-%          \includegraphics[width=\textwidth]{Figuras/he_dist_eff_cost_loan_pro_2.pdf}
-%      \end{subfigure}
-%     ~
-%     ~
-%     \bigskip
-%     \begin{subfigure}{0.42\textwidth}
-%         \caption{Lost pawn}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/def_te_pro_2.pdf}
-%     \end{subfigure}
-%     \begin{subfigure}{0.42\textwidth}
-%     \caption{Losing Pawn}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_2.pdf}
-%     \end{subfigure}
-
-%     \end{center}
-%         \scriptsize
-
-%       %\textit{Do file: }  \texttt{eff\_te.do, def\_te.do, eff\_quantilereg.do}
-% \end{figure}
-
-\vspace{3ex}
-
-\begin{figure}[H]
-        \caption{Financial cost for different discount rates}
-    \label{fc_discount_rates}
-    \begin{center}
-        \centering
-        \includegraphics[width=0.55\textwidth]{Figuras/discount_effect.pdf}
-    \end{center}
-     \scriptsize This Figure estimates the treatment effect on financial cost with different discount rates.  
-     %\textit{Do file: }  \texttt{discounted\_noeffect.do}
-\end{figure}
-
-\begin{figure}[H]
-        \caption{Learning over time}
-    \label{fc_discount_rates}
-    \begin{center}
-        \centering
-        \includegraphics[width=0.55\textwidth]{Figuras/learning_over_time.pdf}
-    \end{center}
-     \scriptsize This Figure shows the evolution of default over time as borrowers have more options to choose the frequent payment contract. This uses the observational data. 
-     %\textit{Do file: }  \texttt{learning\_over\_time.do}
-\end{figure}
-
-\vspace{.3in}
-\begin{figure}[H]
-        \caption{Effects on repeat purchasing}
-    \label{reincidence}
-    \begin{center}
-        \centering
-        \includegraphics[width=0.6\textwidth]{re_te.pdf}
-    \end{center}
-     \scriptsize This figure shows the estimated effects on repeat purchasing of the four treatment arms (Forced Commitment, choice-fee, fee-promise, choice-promise) compared to the status-quo control group.
-It shows robustness of the effects by focusing on different sub-populations.
-The leftmost coefficient compares all the Forced Commitment group against all status quo group.
-The second coefficient conditions on the first pawn not being recovered when the second was pawned.
-The third coefficient conditions on clients who pawned again after having recovered the pawn in the experiment.
-The fourth coefficient uses all clients (in both the Forced Commitment and the status-quo arms) who had an estimated heterogeneous treatment effect above the median.
-Conditioning on this set keeps the sample balanced across arms and therefore still allows for a causal interpretation.
-For the choice arm we present three coefficients: coefficients represented by a circle compare all those offered choice to all those in the status quo arm, thus estimating a causal effect.
-Coefficients in triangles and squares represent those that self-select into the fee or promise arms and compare this subset against the whole status quo arm.
-They therefore contain a selection effect together with the treatment effect and cannot be interpreted causally.
-      %\footnotesize{ \textit{Do file: }  \texttt{re\_te.do}
-\end{figure}
-
-%\begin{figure}[H]
-%        \caption{Distribution of Overconfidence}
-%    \label{oc_hist}
-%    \begin{center}
-%        \centering
-%        \includegraphics[width=0.55\textwidth]{Figuras/oc_hist.pdf}
-%    \end{center}
-%    \scriptsize
-%     In the baseline survey at the branch, before the client knew the contract or had the pawn appraised, they were asked from 0 to 100, how likely it was that they would be able to recover their pawn if pawned.
-We generate a variable we call overconfidence (OC) defined as the reported subjective probability of recovery minus the predicted probability ($P^s_i-\widehat{P_i(X_i)}$).
-We predict $\widehat{P_i(X_i)}$ using LASSO as explained in the text.
-This figure uses all observations for which we have data on $P^s_i$ and $X_i$ from the baseline survey.
-     %\textit{Do file: }  \texttt{oc.do}
-
-%\end{figure}
-
-%\begin{figure}[H]
-%    \caption{The effect of the promise-forcing treatment}
-%    \label{fc_pro3}
-%    \begin{center}
-%        \begin{subfigure}{0.45\textwidth}
-%        \caption{Quantile regression}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/fc_quantile_pro_3.pdf}
-%    \end{subfigure}
-%    
-%    \end{center}
-%             \footnotesize \textit{Notes: } 
-%      \footnotesize{ } \textit{Do file: }  \texttt{fc\_te.do, def\_te.do, fc\_quantilereg.do}
-%\end{figure}
-
 \newpage

### 2022-12-20 donde.tex
revision of text

@@
 \begin{align*}
-    (\text{APR})_i =&\left( 1 + \frac{\frac{\text{Financial Cost}_i}{\text{Appraised Value}_i}}{\text{loan duration}}\right)^{\text{loan duration}}-1 
+    (\text{APR})_i =&\left( 1 + \frac{\frac{\text{Financial Cost}_i}{\text{Appraised Value}_i}}{\text{loan duration}_i}\right)^{\text{loan duration}_i}-1 
 \end{align*}

### 2023-01-18 OA.tex
remove soft arms, edit ss, and main table results

@@
 }
+
+\begin{table}[H]
+\caption{Balance table conditional on survey \& response rates}
+\label{SS_cond_survet}
+\begin{center}
+\scriptsize{\input{./Tables/SS_cond_survey.tex}}
+\end{center}
+
+%\textit{Do file: } \texttt{ss\_att.do}
+\end{table}
 
@@
 (Tuning parameters choice, etc.) We should put them into the appendix.}
+
+\newpage
+
+\subsection{Derivations for Section \ref{sec:randchoice}}
+
+This appendix provides formal proofs of the results described in Section \ref{sec:randchoice}, using the notation and assumptions described in Section \ref{sec:potentialOutcomes}.
+To simplify the presentation, we omit $i$ subscripts throughout this section.
+The following assumption collects our exclusion restriction and the key features of our experimental design.
+
+\begin{assumption}\mbox{}
+   \begin{enumerate}[(i)]
+   \item $Z$ is independent of $(Y_{0}, Y_{1}, C)$
+   \item $D = \mathbbm{1}(Z \neq 2)Z + \mathbbm{1}(Z = 2)C$
+   \item $Y = \mathbbm{1}(Z = 0) Y_{0} + \mathbbm{1}(Z = 1) Y_{1} + \mathbbm{1}(Z = 2) [ (1 - C) Y_{0} + C Y_{1}]$
+   \end{enumerate}
+   \label{assump:randchoice}
+\end{assumption}
+
+\begin{lem}\mbox{}
+   \begin{enumerate}[(i)]
+       \item $\mathbbm{E}(D|Z=2) = \mathbb{P}(C=1)$
+       \item $\mathbbm{E}(Y|Z=0) = \mathbbm{E}(Y_0)$
+       \item $\mathbbm{E}(Y|Z=1) = \mathbbm{E}(Y_1)$
+       \item $\mathbbm{E}(Y|D=0,Z=2) = \mathbbm{E}(Y_0|C=0)$
+       \item $\mathbbm{E}(Y|D=1,Z=2) = \mathbbm{E}(Y_1|C=1)$
+   \end{enumerate} 
+   \label{lem:randchoice}
+\end{lem}
+
+\begin{proof}
+Part (i) follows because $Z=2$ implies $D=C$ and $Z$ is independent of $C$.  
+Parts (ii) and (iii) follow similarly: given $Z=0$ we have $Y = Y_0$, given $Z=1$ we have $Y = Y_1$, and $Z$ is independent of $(Y_0,Y_1)$.
+For parts (iv) and (v), first note that Assumption \ref{assump:randchoice} (iii) implies that $Z$ is conditionally independent of $(Y_0,Y_1)$ given $C$.
+Now, $Z=2$ implies that $D=0$ if and only if $C=0$. Hence,
+\[
+\mathbbm{E}(Y|D=0, Z=2) = \mathbbm{E}(Y_0|D=0, Z=2) = \mathbbm{E}(Y_0|C=0, Z=2)=\mathbbm{E}(Y_0|C=0)
+\]
+establishing part (iv).
+Similarly, $Z=2$ implies that $D=1$ if and only if $C=1$ and hence
+\[
+\mathbbm{E}(Y|D=1, Z=2) = \mathbbm{E}(Y_1|D=1, Z=2) = \mathbbm{E}(Y_1|C=1, Z=2)= \mathbbm{E}(Y_1|C=1)
+\]
+establishing part (v).
+\end{proof}
+
+\begin{prop} \mbox{}
+    \begin{enumerate}[(i)]
+        \item $\text{ToT} \equiv \mathbbm{E}(Y_1 - Y_0|C=1)  = \displaystyle \frac{\mathbbm{E}(Y|Z=2) - \mathbbm{E}(Y|Z=0)}{\mathbbm{E}(D|Z=2)}$
+        \item $\text{TuT} \equiv \mathbbm{E}(Y_1 - Y_0|C=0) = \displaystyle \frac{\mathbbm{E}(Y|Z=1) - \mathbbm{E}(Y|Z=2)}{1 - \mathbbm{E}(D|Z=2)}$
+        \item $\text{ASB} \equiv \mathbbm{E}(Y_0|C=1) - \mathbbm{E}(Y_0|C=0) = \displaystyle \frac{\mathbbm{E}(Y|Z=0) - \mathbbm{E}(Y|Z=2,D=0)}{\mathbbm{E}(D|Z=2)}$
+        \item $\text{ASL} \equiv \mathbbm{E}(Y_1|C=1) - \mathbbm{E}(Y_1|C=0) = \displaystyle \frac{\mathbbm{E}(Y|Z=2,D=1) - \mathbbm{E}(Y|Z=1)}{1 - \mathbbm{E}(D|Z=2)}$
+    \end{enumerate}
+\end{prop}
+
+\begin{proof}
+For parts (i) and (iii) we require an expression for $\mathbbm{E}(Y_0|C=1)$ in terms of the observables $(Y, D, Z)$.
+By Lemma \ref{lem:randchoice}(ii) and iterated expectations
+\[
+\mathbbm{E}(Y|Z=0) = \mathbbm{E}(Y_0) = \mathbbm{E}(Y_0|C=0) \mathbbm{P}(C=0) + \mathbbm{E}(Y_0|C=1) \mathbbm{P}(C=1).
+\]
+Re-arranging and substituting Lemma \ref{lem:randchoice}(i) and (iv),
+\begin{equation}
+\mathbbm{E}(Y_0|C=1)  = \frac{\mathbbm{E}(Y|Z=0) - \mathbbm{E}(Y_0|C=0) \mathbbm{P}(C=0)}{\mathbbm{P}(C=1)} =  \frac{\mathbbm{E}(Y|Z=0) - \mathbbm{E}(Y|Z=2,D=0) \mathbbm{E}(1 - D|Z=2)}{\mathbbm{E}(D|Z=2)}.
+\label{eq:Y0C1}
+\end{equation}
+Part (i) follows by combining \eqref{eq:Y0C1} with Lemma \ref{lem:randchoice}(v) and simplifying; part (iii) follows by combining \eqref{eq:Y0C1} with Lemma \ref{lem:randchoice}(iv) and simplifying.
+Similarly, for parts (ii) and (iv) we require an expression for $\mathbbm{E}(Y_1|C=0)$ in terms of observables.
+By Lemma \ref{lem:randchoice}(iii) and iterated expectations,
+\[
+\mathbbm{E}(Y|Z=1) = \mathbbm{E}(Y_1) = \mathbbm{E}(Y_1|C=0)\mathbbm{P}(C=0) + \mathbbm{E}(Y_1|C=1) \mathbbm{P}(C=1).
+\]
+Re-arranging and substituting Lemma \ref{lem:randchoice}(i) and (v),
+\begin{equation}
+\mathbbm{E}(Y_1|C=0) 
+= \frac{\mathbbm{E}(Y|Z=1) - \mathbbm{E}(Y_1|C=1)\mathbbm{P}(C=1)}{\mathbb{P}(D=0)} =\frac{\mathbbm{E}(Y|Z=1) - \mathbbm{E}(Y|Z=2,D=1)\mathbbm{E}(D|Z=2)}{\mathbb{E}(1-D|Z=2)}.
+\label{eq:Y1C0}
+\end{equation}
+Part (ii) follows by combining \eqref{eq:Y1C0} with Lemma \ref{lem:randchoice}(iv) and simplifying; part (iv) follows by combining \eqref{eq:Y1C0} with Lemma \ref{lem:randchoice}(v) and simplifying.
+\end{proof}
+
+%\begin{proof}
+%For part (iii), note that 
+%\[
+%\mathbbm{E}(Y|Z=0) = \mathbbm{E}(Y_0) = \mathbbm{E}(Y_0|C=0) \mathbbm{P}(C=0) + \mathbbm{E}(Y_0|C=1) \mathbbm{P}(C=1)
+%\]
+%by Lemma \ref{lem:randchoice}(ii) and iterated expectations.
+%Re-arranging, 
+%\[
+%\mathbbm{E}(Y_0|C=1) = \frac{\mathbbm{E}(Y|Z=0) - \mathbbm{E}(Y_0|C=0) \mathbbm{P}(C=0)}{\mathbbm{P}(C=1)}.
+%\]
+%Therefore, by Lemma \ref{lem:randchoice} (i) and (iv)
+%\begin{align*}
+%\mathbbm{E}(Y_0|C=1) - \mathbbm{E}(Y_0|C=0) &= \frac{\mathbbm{E}(Y|Z=0) - \mathbbm{E}(Y|Z=2,D=0) \mathbbm{E}(1 - D|Z=2)}{\mathbbm{E}(D|Z=2)} - \mathbbm{E}(Y|Z=2, D=0)\\
+%&= \frac{\mathbbm{E}(Y|Z=0) - \mathbbm{E}(Y|Z=2,D=0)}{\mathbbm{E}(D|Z=2)}.
+%\end{align*}
+%
+%Similarly, for part (iv) note that
+%\[
+%\mathbbm{E}(Y|Z=1) = \mathbbm{E}(Y_1) = \mathbbm{E}(Y_1|C=0)\mathbbm{P}(C=0) + \mathbbm{E}(Y_1|C=1) \mathbbm{P}(C=1)
+%\]
+%by Lemma \ref{lem:randchoice}(iii) and iterated expectations.
+%Rearranging,
+%\[
+%\mathbbm{E}(Y_1|C=0) = \frac{\mathbbm{E}(Y|Z=1) - \mathbbm{E}(Y_1|C=1)\mathbbm{P}(C=1)}{\mathbb{P}(C=0)}.
+%\]
+%Therefore, by Lemma \ref{lem:randchoice} (i) and (v),
+%\begin{align*}
+%\mathbbm{E}(Y_1|C=1) - \mathbbm{E}(Y_1|C=0) &= \mathbbm{E}(Y|Z=2, D=1) - \frac{\mathbbm{E}(Y|Z=1) - \mathbbm{E}(Y|Z=2, D=1)\mathbbm{E}(D|Z=2)}{\mathbb{P}(C=0)} \\
+%&= \frac{\mathbbm{E}(Y|Z=2,D=1) - \mathbbm{E}(Y|Z=1)}{1 - \mathbbm{E}(D|Z=2)}.
+%\end{align*}
+%\end{proof}
 

### 2023-01-18 Tables/Attrition.tex
remove soft arms, edit ss, and main table results

@@
 % Table generated by Excel2LaTeX from sheet 'Attrition'
-\begin{tabular}{lcccccccc}
+\begin{tabular}{lcccc}
 \toprule
-      &       & \multicolumn{3}{c}{Commitment arms} &       & \multicolumn{3}{c}{Soft arms} \\
-\cmidrule{3-5}\cmidrule{7-9}      & Control & Forced & Choice & p-value &       & Forced & Choice  & p-value \\
+      &       & \multicolumn{3}{c}{Commitment arms} \\
+\cmidrule{3-5}      & Control & Forced & Choice & p-value \\
 \midrule
 \midrule
-Number of branch-day pawns & 31    & 33    & 40    & 0.14  &       & 33    & 34    & 0.76 \\
-      & (3)   & (2.7) & (3.3) &       &       & (3.2) & (2.2) &  \\
-Survey response rate & 0.78  & 0.75  & 0.77  & 0.59  &       & 0.8   & 0.81  & 0.69 \\
-      & (0.02) & (0.03) & (0.03) &       &       & (0.03) & (0.02) &  \\
+Number of branch-day pawns & 34    & 34    & 36    & 0.52 \\
+      & (3)   & (2.9) & (1.8) &  \\
+\multicolumn{1}{p{12.82em}}{Ended up pawning} & 0.98  & 0.97  & 0.97  & 0.62 \\
+      & (0.01) & (0.01) & (0.01) &  \\
+Survey response rate & 0.79  & 0.76  & 0.77  & 0.62 \\
+      & (0.02) & (0.02) & (0.01) &  \\
 \midrule
-Obs   & 1770  & 1954  & 2580  &       &       & 1470  & 1904  &  \\
+Obs   & 1770  & 1954  & 2580  &  \\
 \bottomrule

### 2023-01-18 donde.tex
remove soft arms, edit ss, and main table results

--- 2022-12-20 donde.tex
@@
 
-Pawn loans involve individuals leaving valuable and liquid assets, typically jewelry, as collateral in exchange for an immediate cash loan.
-Collateral is typically larger than the loan, which allows lenders to skip the checking of credit history and give the loan immediately.
+Pawn loans involve individuals leaving valuable liquid assets, typically jewelry, as collateral in exchange for an immediate cash loan.
+Collateral is typically larger than the loan, allowing lenders to skip the checking of credit history and give the loan immediately.
 This makes pawn loans a popular way to get cash to pay for emergencies.
@@
 In spite of the high prevalence and long history, pawnshop borrowing has not received much attention in the economics literature.
-The closest product widely studied is payday loans.
-In developing countries, however, payday lending is likely small compared to pawnshop lending; the latter is faster and requires less documentation, allowing access to informal sector workers who receive their salaries in cash.
-According to \cite{Payday} to get a payday loan: ``All that a prospective borrower typically needs is a home address; a valid checking account; a driver’s license and Social Security number; a couple of pay stubs to verify employment; wages and pay dates; and minimum earnings of at least \$1,000 a month''.
+The closest widely studied product is payday loans.
+In developing countries, however, payday lending is likely small compared to pawnshop lending; the latter is faster and requires less documentation, making it more accessible to informal sector workers who receive their salaries in cash.
+%According to \cite{Payday} to get a payday loan: ``All that a prospective borrower typically needs is a home address; a valid checking account; a driver’s license and Social Security number; a couple of pay stubs to verify employment; wages and pay dates; and minimum earnings of at least \$1,000 a month''.
 Although the author meant this list as an instance of low requirements, they would render virtually all poor households in the developing countries ineligible.
@@
 As with payday lending, pawnshop lending is controversial.
-Regulators have concerns with the sophistication of borrowers using it.
-The US congress has actually banned the payday lending industry from serving active military personnel, and some States in the US have imposed zoning restrictions, interest caps, and restrictions on serial borrowing as consumer protection measures against payday lending \citep{Payday}.
-The main source of concern is whether consumers that use these loans suffer from behavioral and cognitive biases which imply sub-optimal choices.
-There is some evidence  in support of this view.\footnote{\cite{Bertrand} write that ``Under the view that the people borrowing from payday lenders are making an informed, utility-maximizing choice given the constraints that they face, one  would not expect additional information disclosure about the payday product to  alter their borrowing behavior'', but to the contrary they find that simply disclosing how financing costs add up reduced demand by 11\%.
+Regulators have concerns with the sophistication of borrowers using it\footnote{The US congress has actually banned the payday lending industry from serving active military personnel, and some States in the US have imposed zoning restrictions, interest caps, and restrictions on serial borrowing as consumer protection measures against payday lending \citep{Payday}.} speculating they may suffer from behavioral and cognitive deficiencies which lead to make sub-optimal choices.
+There is some evidence in support of this view for payday borrowers.\footnote{\cite{Bertrand} write that ``Under the view that the people borrowing from payday lenders are making an informed, utility-maximizing choice given the constraints that they face, one would not expect additional information disclosure about the payday product to alter their borrowing behavior'', but to the contrary, they find that simply disclosing how financing costs add up reduced demand by 11\%.
 \cite{Meltzer} finds that payday loan access leads to increased difficulty paying mortgage, rent and utilities bills.}  Our study reinforces the idea that a lack of sophistication may be an integral part of that way that standard pawn contracts are structured.
 
-\subsection{Status Quo Pawn Contracts}
+\subsection{Pawning Logistics and Contracts}
 
@@
 This lender (whom we refer to as `Lender P') has a simple and typical business model.
-They take gold jewelry as collateral in exchange for a fraction the value of the piece, in cash.
+
+\paragraph{Appraising and lending.} They take gold jewelry as collateral in exchange for a fraction the value of the piece, in cash.
 No other collateral and no credit history checks are needed.
@@
 
-Lender P had only one type of contract, henceforth the \textit{status quo} contract.
+\paragraph{Contract.} Lender P had only one type of contract, henceforth the \textit{status quo} contract.
 It stipulated that the interest rate was 7\% \textit{per month} compounded daily on the outstanding amount of the loan.
-The loan had a 90 days term with 15 days' grace period, and the client could make payments at anytime with no penalty for pre-payment.
+The loan had a 90 days term with 15 days' grace period.
+The client could make payments at the branch at anytime with no penalty for pre-payment.
 No reminders or interim contact exists between the lender and the borrower.
-If the client returns to pay the principal plus the accumulated interest within 105 days, she received back her pawn, otherwise the pawnbroker kept the piece and any payments made.
-Before the contract expired, the client had the right to renew it  using the same collateral for another 3 months by going to the pawnshop paying the accumulated interest and signing a new contract with exactly the same terms as the original one.
-26\% of borrowers renew at least once with a given pawn.
+If the client returns to pay the principal plus the accumulated interest within 105 days, she received back her pawn, otherwise the pawnbroker kept the piece \textit{and} any payments made.
+Before the contract expired, the client had the right to renew for another 3 months by going to the pawnshop, paying the accumulated interest, and signing a new contract with exactly the same terms and same piece as the original one a (26\% of borrowers renew at least once with a given pawn).
 This contract was standard in the industry.
-
-The clients that pawned understood these terms well (as we verified in interviews).\footnote{90\% of clients report in our survey that they have pawned before.} These clients have little or no access to other types of loans and they value the convenience of pawn borrowing.
-This population of pawn borrowers is economically vulnerable:  30\% of them could not pay either water, electricity \& gas or rent in the past 6 months.
-They often receive negative income shocks: 87\% said they are pawning because of an emergency, and only 13\% stated it was to use in a `non-urgent expense'.
-When asked why they are pawning this piece 5\% responded `lost a family member', `a medical emergency' (11\%), or `an urgent expense' (71\%).
-
-Our context is also one with high borrower default: 60\% of clients lose their pawn in a time span of 230 days from the date of pawning.
+Pawnshops make money in three ways: by reselling the jewelry left as collateral on defaulted loans, by charging interest on non-defaulted loans, and by keeping the payments made on defaulted loans.
+
+\paragraph{Borrowers.} The clients that pawned understood these terms well (as we verified in interviews).\footnote{90\% of clients report in our survey that they have pawned before.} These clients have little or no access to other types of loans and they value the convenience of pawn borrowing.
+This population of pawn borrowers is economically vulnerable:  30\% of them could not pay either water, electricity \& gas or rent in the past 6 months; 87\% said they are pawning because of an emergency, and only 13\% stated it was to use in a `non-urgent expense'.
+When asked why they are pawning this piece, 5\% responded `lost a family member', `a medical emergency' (11\%), or `an urgent expense' (71\%).
+
+\paragraph{Most borrowers lose their pawn.} Our context is also one with high borrower default: 60\% of clients lose their pawn in a time span of 230 days from the date of pawning.
 One potential explanation for high default is that clients are really just knowingly selling their gold piece through a pawn contract on which they intend to default.
-This appears unlikely for several reasons: (a) clients can easily sell the gold and obtain a higher amount of instant cash at gold buying stores located close to almost all our pawnshop branches (see Figure \ref{GoldBuyers}), (b) the reported subjective value of the pawn is larger than the loan size for 86\% of clients, (c) among those that lose their pawn 48\% paid a positive amount towards its recovery and on average paid 42\% of the value of their loan (see Figure \ref{proxy_naive} in Appendix) --- this can only be rationalized if they expected to recover their pawn, and (d) 74\% of borrowers report a 100\% probability of repaying their loan (and 98\% at least a 50\% chance of repaying) in our baseline our baseline survey at the time they take the loan.
-So it does appear that a large share of default is not `planned' in a simple ex-ante sense.
-High default could be also detrimental from the lender's point of view since it may reduce the likelihood that the client becomes a return customer.
-Lender P was explicitly interested in  partnering with us to investigate whether a frequent payment contract would increase pawn recovery, customer satisfaction, and repeat borrowing, and to explore whether there was demand for such a contract.
-
-Pawnshops therefore make money in three ways: by reselling the jewelry left as collateral on defaulted loans, by charging interest on non defaulted loans, and by keeping the payments made on defaulted loans.
-In this way the interest rate typically used to calculate borrower APRs is thus a very inadequate measure of the effective cost of pawn loans.
-
-\subsection{Measuring the Cost of Pawning} \label{costs}
-
-We now develop the measures of net financial costs to the borrower that are used as our core pecuniary outcomes.
-The two key measures are loan default, and the effective financial cost incurred by the borrower.
-Default is defined as losing the pawn.
-The administrative records show three types of payments made toward recovery of the pawn: payments to principal $P^c$, payments on generated interests $P^i$, and payments on penalty fees $P^f$.
-We define financial cost according to its default status.
-Financial cost for default loans is the sum of all payments, and the lost value of the collateral.
-For recovered loans, financial cost only consists on the sum of interest payments and fees, since payments to principal were allocated to the recovery of the collateral we are not counting it as a cost.
-Hence the formula for financial cost is :
+This appears unlikely for several reasons: (a) clients can easily sell the gold and obtain a higher amount of instant cash at gold buying stores located close to almost all our pawnshop branches (see Figure \ref{GoldBuyers}), (b) the reported subjective value of the pawn is larger than the loan size for 86\% of clients, (c) among those that lose their pawn, 48\% paid a positive amount towards its recovery and on average paid 42\% of the value of their loan (see Figure \ref{proxy_naive} in Appendix) --- this can only be rationalized if they expected to recover their pawn, and (d) 74\% of borrowers report a 100\% probability of repaying their loan (and 98\% at least a 50\% chance of repaying) in our baseline survey at the time they take the loan.
+Note that high default could be detrimental from the lender's point of view, since it may reduce the likelihood that the client becomes a return customer.
+Lender P was in fact explicitly interested in partnering with us to investigate how to reduce loan default, customer satisfaction, and repeat borrowing.
+
+\subsection{Measuring Borrowers Financial Costs} \label{costs}
+
+Borrowers' financial costs are composed of two main categories: the cost of losing their collateral, and the interest incurred during the life of the loan.
+For each given loan we observe if the client lost her pawn ($\mathds{1}(\text{Default}_i)$) and when.
+If the client has renewed her loan several times such that the loan is continuing but has not defaulted, we code default as zero.
+In our data \hl{XX\%} of experimental loans are continuing (i.e.
+censored) when the data period ends.
+Regarding interest, the administrative data classifies payments made in three types according to their payment allocation rules: payments to principal $P^c$, payments on generated interests $P^i$, and payments on penalty fees $P^f$.
+We observe each and every payment made under each category, its amount and date.
+
+We define a borrower's financial cost as the \textcolor{red}{outflow --in cash or pawn value-- from the borrower to the lender.} This includes all payments the borrower made toward interest and fees, but also the value of the pawn when there is default.
+When there is no default the borrower gets her pawn back and there is no loss of value for the borrower.
+Payments towards capital are considered a cost only when the borrower defaults, as she does not get reimbursed for these.
+Note however that when she does not default payments to capital are not an actual outflow, as they sum up to the value of the loan the lender disbursed in the first place.
+The formula for financial cost for person $i$ is thus as follows:
 
 \begin{align*}
-    (\text{Financial Cost})_i =&  \underbrace{\sum_t P^f_{it}}_{\text{Payments of fees}}  +\underbrace{\sum_t P^i_{it}}_{\text{Payments to interests}} \\
+    \text{Financial Cost}_i =&  \underbrace{\sum_t P^i_{it}}_{\text{Payments to interests}} + \underbrace{\sum_t P^f_{it}}_{\text{Payments of fees}}   \\
     &\quad\qquad + \underbrace{\mathds{1}(\text{Default}_i) \times (\text{Appraised Value}_i}_{\text{Cost of losing pawn}} + \underbrace{\sum_t P^c_{it}}_{\text{Payments to capital}})
@@
 
-\noindent $t$ indexes days, and $\mathds{1}(\text{Default}_i)$ is an indicator function for defaulting.
-We also report results using the subjective value of the pawn reported by the borrower in place of the appraised value, and a measure of financial costs that adds travel expenses, since the treatment involves making clients come to the branch to pay each month.
-
-As a second measure of cost we convert that Financial Cost outcome from above to an Annual Percentage Rate (APR).
-The APR is defined as\footnote{To keep in spirit with the way we are handling incomplete loans, we just say that the loan duration for those is the time that we did observe, so we are adding up all interest and fees over the whole time that loan (including refinancing) has been observed.} :
+\noindent where $t$ indexes days, and $\mathds{1}(\text{Default}_i)$ is an indicator function for defaulting.
+Even though we observe transactions at the day level, \textcolor{red}{we don't use discounting} since the period of loan is only 90 days.
+\textcolor{red}{In robustness checks we do show that results are virtually unchanged when applying a wide range of time discounting factors.}
+
+We believe the above measure captures financial cost in pesos accurately.
+However, we will also report results incorporating two costs that are not financial: (i) using the subjective value of the pawn reported by the borrower in place of its appraised gold value, and (ii) adding a measure of travel expenses and the opportunity cost of time, as clients have to go to the branch in order to make payments.
+
+As a second measure of cost we calculate the Annual Percentage Rate (APR) in order to express the cost as a percentage of the loan, per year.\footnote{Loan term takes into account all the loan period, including those extended through refinancing}.
+The standard definition is given in the following formula:
 
 \begin{align*}
-    (\text{APR})_i =&\left( 1 + \frac{\frac{\text{Financial Cost}_i}{\text{Appraised Value}_i}}{\text{loan duration}}\right)^{\text{loan duration}}-1 
+    (\text{APR})_i =&\left( 1 + \frac{\frac{\text{Financial Cost}_i}{\text{Appraised Value}_i}}{\text{loan term}_i}\right)^{\text{loan term}_i}-1 
 \end{align*}
 
-We can use the control group for the study to present summary statistics on these core measures of default and financial cost.
-Figure \ref{fc_hist}(a) plots a histogram of this financial cost in pesos for loans where the pawn was either recovered or lost, while panel (b) shows the APR.
-This shows that most of the costs come from clients that do not recover their pawn.
+\vspace{.1in}
+
+Figure \ref{fc_hist}(a) plots a histogram of this financial cost in pesos for all loans in the experiment, distinguishing by whether we observed they defaulted (\hl{XXX\%}), recovered their pawn (\hl{XXX\%}), or whether they are censored in our data (\hl{XXX\%}).
+The first thing to note is that those that default incur in higher costs; part of this is mechanical as losing their collateral is part of the cost.
+The second thing to note is that those that are not closed at the end of our sample period have already incurred in substantial financial cost, even though they have not defaulted yet.
+Panel (b) shows the APR, which is normalized by loan size; most of the APR costs come from clients that do not recover their pawn.
 %Of those who renew, 83\% lose the pawn.
@@
 The Commitment contract however requires the client to make regular monthly payments for the duration of the contract, with the principal and interest payments split evenly across the three months of the contract (day 30, 60 and 90 after loan disbursement).
-The importance of this monthly payment was reinforced in two ways; first by reminders issued to any borrower delinquent on the monthly payments that were supposed to be made, and secondly by the levying of a nominal fee (2\% of minimum due) on individuals who fell behind in their payments.\footnote{This fee was set by the lender, being deemed large enough to reinforce commitment but small enough that if clients had an emergency and could not pay, the fee would not cause the pawn to be unrecoverable.
+The importance of this monthly payment was %reinforced in two ways; first by reminders issued to any borrower delinquent on the monthly payments that were supposed to be made, and secondly
+made salient in the contract and payment receipts (see Figure \ref{PaperSlip}), and by the levying of a nominal fee (2\% of minimum due) on individuals who fell behind in their payments.
+The propose of the small fee was to mainly to make the structured schedule salient, not to be a large disincentive to be late.
+Transportation cost to go to the branch to pay is on the same order of magnitude as the fee in average.\footnote{The lender was worried that if the fee was large, forgetting to pay could make the pawn unrecoverable.
 In contrast with \cite{John} we don't let the clients choose the size of the fee.
-That paper shows that doing this results in wrong choices by (partially) naive present biased consumers.
-Our fee is much smaller than the median in her experiment, as explained in the introduction.
+\cite{John} shows that doing this results in costly choices by (partially) naive present biased consumers.
+Our fee is much smaller than the median in her experiment.
 %We also experimented with a contract where there was no pecuniary fee for paying late but where we clients made a personal promise to pay monthly.
-}
-
-As is typical in the behavioral literature we include an arm that allows borrowers to opt in to the commitment contract if they choose.
-If, however, a lack of sophistication is an issue with borrowers in pawn contracts, then this process of self-selection may not assign commitment to the `right' people.
-To examine this issue, we include an arm  that assigns all individuals to the commitment contract so that we are able in essence to form three counterfactual outcomes; no commitment, commitment, and the chosen commitment.
-This design allows us to investigate the repercussions of choice not only for those who \textit{do} choose (as is the case in a standard LATE design), but also the implications of choice for those who \textit{do not} choose.
-This turns out to be key for what we can learn from this experiment.
+} To elicit demand for the monthly payment contract, we include an arm that allows borrowers to opt into this contract if they choose.
+The existence of both a non-optional ``forcing'' arm, and a choice arm in our design is key to estimate a battery of treatment effects above an average treatment effect under fairly mild assumptions.
 
@@
 
-We did not allocate equal number of days across arms, since we were interested in having more power in some of them.
-The number of branch days allocated to each were 84, 80, 93, 68, and 82, respectively.
+We did not allocate an equal number of days across arms, since we were interested in having more power in some of them.
+The number of branch days allocated to each were 84 to control, 80 to forced commitment, and 93 to choice.
 See Figure \ref{exp_description} for a CONSORT-style diagram of the study design and recruitment.
+
+The existence of a choice arm allows us not only to measure if there is demand for such a contract, but who demands it, not only in demographic terms, but in terms of potential treatment effects.
+One may worry for instance that low sophistication from pawn-loans users could lead to the `wrong' people choosing the structured commitment contract.
+To examine this issue, we included an arm that assigns all individuals to the commitment contract so that we are able in essence to form three counterfactual outcomes; no commitment, commitment, and the chosen commitment.
+This design allows us to investigate the repercussions of choice not only for those who \textit{do} choose (as is the case in a standard LATE design), but also the implications of choice for those who \textit{do not} choose.
+This design is innovative and critical for our purposes, as it enables us to explore whether or not forcing people into a structured payment contract could be more beneficial than allowing choice for a significant fraction of them.
 
@@
 
- Branch personnel did not know which treatment would happen on which day.
-They were told that there were 3 different ``types of contract-days'' and that the system chose randomly which applied on any given date, and that it could happen for instance that two consecutive dates had the same contract.
+Branch personnel did not know which treatment would happen on which day and were blind to the objective of the intervention.
+They were told that there were 3 different ``types of contract-days'', that the system chose randomly which applied on any given date, and that it could happen for instance that two consecutive dates had the same contract.
 They were also told that this way of operating was in place in several of Lender P's branches (they did not know which ones), and that it would be in place for several months.
 Randomizing at the day level limits the problem of contamination arising from clients realizing that other clients get different contracts than theirs.
-It also limits potential manipulation by appraisers, who in the presence of individual level randomization could potentially pick their preferred customer from the line or tell them to wait until their desired contract shows up on the screen.
+It also limits potential manipulation by appraisers, who in the presence of individual-level randomization could potentially pick their preferred customer from the line or tell them to wait until their desired contract shows up on the screen.
 Intra-branch day correlation on the probability of default (ICC) is small, at {0.08}, so we lose little power vis-a-vis individual-level randomization.
 
-Panel (b) of Figure \ref{exp_description} shows how many contracts the experiment has in each arm (rectangles).
-And for the choice arms, it displays in blue how many people actually chose the respective commitment contract.
-
-For the experiment to be meaningful, it is critical that clients understood the contract terms clearly.
+%\todo[inline]{Somewhere in here we need to explain how we handle repeat pawns.
+If I recall correctly, we've settled on including only data for each person's first visit.
+This visit may include multiple pawns, but this is fine since we cluster at the branch-day level.}
+
+Some clients pawned more than one time during the duration of the experiment, with \hl{XXX\%} pawning 2 times and \hl{XXX\%} more than 2 times.
+To have a clean comparison we are considering only the first pawn in the experiment.
+It is also the case that \hl{XXX\%} of those first pawns involve more than 1 loan, as 2 or more pieces of gold were submitted.
+We treat each of them as separate loans.
+
+\paragraph{Timeline.} Figure \ref{exp_description}(a) \textcolor{red}{shows the timeline when the experiment happens and also the length of time for which we observe payments}.
+For contracts in the first week, we observe up to \hl{XXX} days, with \hl{XXX\%} of contracts ending during our sample period (in default or recovery).
+For contracts in the last week we observe up to \hl{XXX} days, and \hl{XXX\%} of contracts ending observed.
+Figure \ref{exp_description}(b) shows the number branch-days per arm, the number of contracts, and the number of surveys.
+%Not every contract has a survey for several reasons, we have survey information for \hl{XXX\%} of them.
+There were two reasons: \hl{XXX}.
+
+\paragraph{Explanation.} Since we are interested in measuring the effect of different contract terms on client behavior, it is important that clients understand them.
 To ensure this, we built two `check-points'.
 First, two enumerators were present in each branch for the whole day during the duration of our experiment to explain the contract terms to clients.
-One of the aspects emphasized was that the frequent payment contract involved the commitment to pay a third of the outstanding amount \underline{each month}, and the nature of the reminders and fees associated with the Commitment arm.
+One of the aspects emphasized was that the frequent payment contract involved the commitment to pay a third of the outstanding amount \underline{each month}, and the nature of the fees associated with the Commitment arm.
 Figure \ref{ExplanatoryMaterial} translates a piece of the materials we used to explain the contracts (in this case a comparison sheet used in the Promise-Choice days to compare contracts terms side to side).
@@
 Enumerators then asked clients to explain back the contract terms and corrected any misunderstandings.
-
-The second check-point was that before the clients signed the contract, the appraiser made them read them the ``Contract Terms Summary'' sheet shown in Figure \ref{PaperSlip}.
+The second check-point was that before the clients signed the contract, the appraiser made them read the ``Contract Terms Summary'' sheet shown in Figure \ref{PaperSlip}.
 It was a piece of paper given to clients after their piece had been appraised and the size of the loan determined, but before they signed their contract.
-The appraiser read it and asked the client to sign it as a proof of understating.
+The appraiser read it and asked the client to sign it as proof of understating.
 %The sheet clearly indicates that this contract is a monthly payment one (numeral 1), that there is a penalty of 2\% for paying late (numeral 2), and the 3 payment dates (numeral 3).
@@
 The clients had to put their name on a slip of paper where they stated they promised to pay monthly.
-
-We are confident the overwhelming majority of clients understood the contracts and that those in the choice arm made informed choices.
-As shown below, different contract terms did generate differential demand and differential behavior.
-Moreover, we can systematically predict demand based on consumer characteristics and measured beliefs.
-
-\subsection{Survey Data and Summary Statistics}
-
-The study exploits two forms of data; administrative data from the lender and a short survey we conducted of experimental clients.
-
-\todo[inline]{Somewhere in here we need to explain how we handle repeat pawns.
-If I recall correctly, we've settled on including only data for each person's first visit.
-This visit may include multiple pawns, but this is fine since we cluster at the branch-day level.}
-
+We are confident the overwhelming majority of clients understood the contracts and that those in the choice arm made informed choices.\footnote{That we can systematically predict demand based on consumer characteristics and measured beliefs suggest that take up is not random.}
+
+\subsection{Data}
+
+\paragraph{Administrative data.} The study exploits two types of data: administrative data from the lender, and a short survey we implemented.
 The administrative data contains a unique identifier for each client, an identifier for the piece she is pawning, and the transactions relating to that piece.
-In particular, the value of the piece as assessed by the appraiser, the amount of money loaned (70\% of the value), the date of the pawn transaction, and the type of contract for that pawn.
+In particular, the value of the item as assessed by the appraiser, the amount of money loaned (70\% of the value), the date of the pawn transaction, and the type of contract for that pawn.
 Within the period of the loan, we followed each transaction related to that piece in the administrative data: when payments were made and for what amounts, whether there was default (i.e.\ the client lost her pawn), and whether any late-payment fees were imposed.
@@
 
-In addition, we had a team of enumerators in each branch collect surveys and clearly explain the contract terms to walk-in clients.
-The enumerators were inside the branch and asked clients to complete a 5 minute survey \textit{before} going to the teller window to appraise their piece and before they were told contract terms (i.e.
-before treatment status was known).
-It was short to avoid discouraging the potential clients from pawning, but at the same time it aimed to measure the following: demographics, proxies for income/wealth, education, self-control problems/present-biased preferences, experience pawning, if family or friends commonly asked for money, how time consuming and costly it was to come to the branch, the subjective probability of recovering the piece that they intended to pawn, the subjective value of their piece in money terms (how much money they would sell it for), among others.
-We surveyed 10,437 clients, and the survey response rate was 78\%.\footnote{The Appendix \ref{baseline_survey} transcribes the questionnaire in English.} %\footnote{We also surveyed clients before and after the experiment, so our survey covers a larger sample that we are not using in this paper.}.
-
-\subsection{Attrition}
-
-There are two main channels through which attrition could complicate the interpretation of our results.
-The first, and more serious, is the possibility that clients might change their pawning decisions in response to the treatment arms.
-If this were the case, our study would still recover internally valid estimates of the impacts of the treatment arms for the lender, but would not provide \textit{ceteris paribus} impacts on a comparable pool of individuals.
-We anticipated this possibility and trained appraisers to say that whatever was offered on that day was the only available contract for an undetermined length of time.
-Because we do not observe refusals directly, we address this issue by examining the number of borrowers per day, with specific attention to whether the Forced Commitment arm led to a lower number of borrowers per day.\footnote{Our enumerators informed us that potential clients rarely left the branch without pawning, and that it was even less common that they did so when hearing about monthly installments.
-Lender P also never complained to us that our different treatments were hurting sales.
-The data support this story as well.}
-
-Finally, we also tested if the number of pawns per day for the 6 branches that participated in the experiment was different 1 month before the experiment started or 1 month after the experiment ended, relative to the days the experiment was active.
+\paragraph{Survey data.} In addition, we had a team of enumerators in each branch collect surveys and clearly explain the contract terms to walk-in clients.
+The enumerators were inside the branch and asked clients to complete a 5-minute survey \textit{before} going to the teller window to appraise their piece and before treatment status was known to them.
+The survey was intentionally short to avoid discouraging the potential clients from pawning, but at the same time it aimed to measure the following: demographics, proxies for income/wealth, education, present-biased preferences, experience pawning, if family or friends commonly asked for money, how time consuming and costly it was to come to the branch, the subjective probability of recovering the piece that they intended to pawn, the subjective value of their piece in money terms (how much money they would sell it for), among others.
+We surveyed 10,437 clients, and the survey response rate was 78\%.\footnote{Appendix \ref{baseline_survey} transcribes the questionnaire in English.} %\footnote{We also surveyed clients before and after the experiment, so our survey covers a larger sample that we are not using in this paper.}.
+
+\subsection{Experimental Integrity}
+
+\paragraph{Attrition.} There are two main channels through which attrition could complicate the interpretation of our results.
+The first, and more serious, is the possibility that clients might change their pawning decisions in response to the treatment they encounter in a given branch on the day they enter.
+If this occurred it would introduce a self-selection dimension which would still reflect the overall impact of a treatment for the lender's portfolio but would no longer deliver \textit{ceteris paribus} effects of treatments on the same individual borrower.
+Narrative reports and the way the treatment was implemented make us believe that this is unlikely.\footnote{Potential clients did not know that different days could have different contracts.
+If they asked, appraisers said that whatever was offered on that day was the only available contract for an undetermined length of time.
+Anecdotally, appraisers told us that they did not think refusals differed across arms, and our enumerators informed us that potential clients rarely left the branch without pawning.
+Lender P also never complained to us that our different treatments were hurting sales.} If the treatments had induced demand-side selection, we would expect to see that the number of pawns successfully conducted differ in a systematic way across arms.
+To test for this, we examine the number of loans given per branch-day, with specific attention to whether the Forced Commitment arm led to a lower number of borrowers per day.
+The \hl{first} row of Table \ref{attrition_table} shows there is no difference between the Control and Forced Commitment arm in terms of the number of pawns per branch-day, suggesting that there has been no differential refusal.\footnote{The Choice arm appears to have a somewhat larger number of borrowers than the Control arm (p-value=\hl{XXX}), but we cannot reject equality with the Forced Commitment arm (p-value=\hl{XXX}), or across all arms (p-value=\hl{XXX}).}  Therefore it appears that the treatments have not induced any endogenous shifts in the composition of borrowers.
+
+A less critical form of attrition would be a differential refusal to answer the survey questions.
+The survey was done before treatment status was revealed, and we observe loan outcomes regardless of whether the survey was conducted.
+Our core experimental estimates do not use the survey data as covariates, but the Random Forest analysis is restricted to the subset of borrowers who answered at least some survey questions.
+The top row of Table \ref{attrition_table} shows that the survey response rate is broadly similar across arms (about 77 percent).
+We can also examine differences in the fraction of borrowers who do respond to the survey and then do not end up taking a loan subsequent to completing the survey, we find that the share is close to as is the fraction of those 97\% across arms (p-value=\hl{XXX}).\footnote{We also tested if the number of pawns per day for the 6 branches that participated in the experiment was different 1 month before the experiment started or 1 month after the experiment ended, relative to the days the experiment was active.
 To this end we estimated the regression\footnote{We cluster the standard errors by branch.} $Pawns \: per \: day_{jt} = \alpha_j + \gamma f(t) + \beta_b \mathbbm{1}(t \in MB)_{t} +\beta_a \mathbbm{1}(t \in MA)_{t}$, where $\alpha_j$ are branch fixed effects, $f(t)$ is a third degree polynomial in time, $\beta_b$ measures a level effect in the number of pawns per branch a month before the experiment started, and $\beta_a$ a month after.
 We estimate no difference in the number of pawns, showing that people are not leaving the branch without pawning at larger rates during the experiment ($\beta_a=1.32$, $\beta_b=-0.65$, with p-values 0.11 and 0.83, respectively).
-Table \ref{num_pawns_bal} shows the beta coefficients from these regressions, which are nowhere significant.
-
-A second form of attrition would be differential refusal to answer the survey questions.
-This is less of a concern, both because the survey was done before treatment status was revealed, and because we still have institutional data for the universe of borrowers.
-Nonetheless, to test the internal validity of any measures in the study that use survey data, we test for differential attrition here as well.
-A third way of examining attrition is to look at the fraction of borrowers who do respond to the survey and then do not end up taking a loan subsequent to completing the survey.
-
-Table \ref{attrition_table} presents tests for these core forms of attrition.
-Most importantly, the top row shows that there is no difference between the Control and Forced Commitment arms in terms of the number of pawns per day, suggesting that there has been no differential refusal when borrowers were defaulted into the Commitment contract.
-The Choice arm appears to have a somewhat larger number of borrowers than the Control arm, but given that there is no reason to think that we would have seen differential uptake for this arm (where the status quo contract is freely available) we view this as a chance occurrence.
-The survey response rate is broadly similar across arms (about 77 percent) as is the fraction of those surveyed who then go on to take a loan (97 percent).
-
-Hence we begin the analysis confident that differential attrition has not occurred.
+Table \ref{num_pawns_bal} shows the beta coefficients from these regressions, which are nowhere significant.}  Hence while survey response was not universal, there is no evidence that it was differential across arms.
+
+Two more subtle form of sample selection arise if the treatments induce borrowers to repawn in different ways (which they do), or to pay off loans at a different rate (which they do as well).
+We pursue a simple approach to these problems, by using only the first experimental pawn taken by a given borrower during the study window (ignoring all subsequent loans), and by defining outcomes in a manner that is consistent whether or not the loan had been closed at the time that the study observation window ends (e.g., `loan was repaid', which is defined even if the loan had not been completed, versus `loan defaulted', which is not).
+We return in the subsequent section to more detailed analysis of the implications of these two issues.
 
@@
 
-\subsection{Balance in the Experimental Sample}
-Table \ref{SS} presents summary statistics for the sample of actual borrowers across arms, and illustrates that randomization worked to achieve balance across clients in the different experimental arms.
-
+\paragraph{Balance.} Table \ref{SS} presents summary statistics for the sample of actual borrowers across arms, and illustrates that randomization worked to achieve balance across clients in the different experimental arms.
 Panel A uses administrative data for the universe of borrowers in each arm, and shows that loan balances and the days on the week on which individuals pawned are comparable across arms.
-The average loan size is \$2197 MXN (\$105 USD).
-
+The average loan size is \hl{\$2197} MXN (\$105 USD).
 Panel B of Table \ref{SS} reports summary statistics across arms from our survey data.
-73\% of clients are women, with an average age of 43 years; 66\% of them have completed high school or more, and 90\% have pawned before, so that our sample has mostly experienced borrowers.
-Finally the subjective probability of recovery is close to 93\% on average, which makes a stark contrast to the actual rate of recovery (42\%).
-In other words, borrowers are highly overconfident on average.
-The average subjective value they report for the pieces is 3069 MXN, much larger than the average appraised gold value of 2197 MXN.
+\hl{73\%} of clients are women, with an average age of \hl{43} years; \hl{66\%} of them have completed high school or more, and \hl{90\%} have pawned before, so that our sample has mostly experienced borrowers.
+Finally, the subjective probability of recovery is close to \hl{93\%} on average, which makes a stark contrast to the actual rate of recovery of \hl{42\%}; borrowers are highly overconfident on average.
+The average subjective value they report for the items they pawn is \hl{3069} MXN, much larger than the average appraised gold value of \hl{2197} MXN.
 While this could arise either from overconfidence in valuation or from undervaluation by the lender, in any case it is \textit{prima facie} evidence that loss of the pawn should be undesirable relative to the quantity of liquidity leveraged by the asset.
 
-Panel C repeats the exercise in Panel B, but now only for those borrowers answered the survey and then went on to take a loan.
+%Panel C repeats the exercise in Panel B, but now only for those borrowers answered the survey and then went on to take a loan.
 Since we have aready shown that the attrition rate of borrowers after completing the survey was very low (3\% on average) it is unsurprising that these two panels are similar.
@@
 
-%\section{Experimental Analysis} \label{experiment}
 \section{Average Treatment Effects} \label{experiment}
 
-\todo[inline]{We should add some discussion here about the take-up rate of commitment here.
-Need to think more carefully about how to do it.
-Don't want to get too bogged down and start talking about why people are choosing at this point in the paper.}
+We start by estimating average treatment effects for those assigned to the Forced commitment and the Choice arms, compared to those assigned to the Control group.
+As we explain below, only about \hl{XXX\%} of those in the choice arm chose the monthly payment option.
 
@@
 \todo[inline]{Add a column with losing pawn. What about re-pawning?}
-
 \todo[inline]{How did we decide to deal with censoring?}
+
+As we explained above, loans can be extended for an additional 3 months by paying the interest owed and restarting the loan under the same treatment conditions.
+This means that some loans extend for more than 3 months.
+We consider the cost
 
@@
 Columns (2) and (7) of Table \ref{table_robustness_fc} use the subjective value of the pawn reported by the borrower rather than its appraised value.
-Columns (3) and (8) adjust for self-reported transport costs from the individual survey plus an entire day's wage, multiplied by the number of individual \hl{additional} visits\footnote{For clients who did not complete the individual survey, we adjust using the mean self-reported transport cost among respondents.}.
+Columns (3) and (8) adjust for self-reported transport costs from the individual survey plus an entire day's wage, multiplied by the number of individual visits\footnote{For clients who did not complete the individual survey, we adjust using the mean self-reported transport cost among respondents.}.
 Although adding a whole day's wage almost certainly exaggerates the travel costs associated with commitment contracts, we still find that forced commitment reduces both financial costs and APR. 
@@
 \subsection{The ``Randomized Choice'' Design}
+\label{sec:randchoice}
 
@@
 The key insight can be read directly from \eqref{eq:potentialTreatments} and \eqref{eq:potentialOutcomes}. 
-Viewing $Z_i$ as an instrumental variable, our design can be interpreted as a \emph{pair} of RCTs, each subject to one-sided non-compliance.
+Viewing $Z_i$ as an instrumental variable, the randomized choice design can be interpreted as a \emph{pair} of RCTs, each subject to one-sided non-compliance.
 The first of these compares $Z_i=0$ to $Z_i = 2$.
@@
 \frac{\mathbbm{E}(Y_i|Z_i=1) - \mathbbm{E}(Y_i|Z_i =2)}{\mathbbm{E}(D_i|Z_i=1)-\mathbbm{E}(D_i|Z_i=2)} = 
-\frac{\mathbbm{E}(Y_i|Z_i=1) - \mathbbm{E}(Y_i|Z_i =0)}{1 - \mathbbm{E}(D_i|Z_i=2)} = \mathbbm{E}(Y_{i1} - Y_{i0} | C_i = 0)
+\frac{\mathbbm{E}(Y_i|Z_i=1) - \mathbbm{E}(Y_i|Z_i =2)}{1 - \mathbbm{E}(D_i|Z_i=2)} = \mathbbm{E}(Y_{i1} - Y_{i0} | C_i = 0)
 \label{eq:TuT}
@@
 \]
-It follows that a pair of just-identified, linear instrumental variables regressions can be used to estimate and carry out inference for each of our quantities of interest.
+It follows that a pair of just-identified, linear instrumental variables regressions can be used to estimate and carry out inference for the ATE, ToT, and TuT.
 To identify the ATE and ToT, run IV on \eqref{eq:ToTreg} with instruments $\mathbbm{1}(Z_i = 1)$ and $\mathbbm{1}(Z_i=2)$.
 An F-test based on this regression can then be used to test the restriction $\text{ATE} = \text{ToT}$, and the usual IV output can be used to carry out inference for the ToT.
-No programming is required.
 Similarly, to identify the ATE and TuT run IV on \ref{eq:TuTreg} with instruments $\mathbbm{1}(Z_i = 0)$ and $\mathbbm{1}(Z_i = 2)$.
 An F-test based on this regression can then be used to test the restriction $\text{ATE} = \text{TuT}$, and the usual IV output can be used to carry out inference for the TuT.
-Again, no programming or special software is required.
-
-\todo[inline]{Add a paragraph briefly explaining which IV regressions to run to get the ingredients for the ASB and ASL, and directing the reader to an appendix that describes how to carry out inference when you need to combine estimates from two separate IVs.}
-
-\todo[inline]{Perhaps mention some other settings in which a design like this might be helpful?}
+
+Because they identify both the ToT and TuT, \eqref{eq:ToTreg} and \eqref{eq:TuTreg} also identify the average selection on gains: $\text{ASG} = \text{ToT} - \text{TuT}$.
+Carrying out inference for this quantity is a bit more involved, because $\text{ASG}$ a difference of coefficients from two separate IV regressions. 
+In Appendix \hl{???} we show how to use the residuals from \eqref{eq:TuTreg} and \eqref{eq:ToTreg} to carry out cluster-robust inference for $\text{ASG}$. 
+Our companion STATA package automates this procedure.
+As mentioned above, the randomized choice design also identifies the average selection bias (ASB) and average selection on levels (ASL).
+In particular,
+\begin{align}
+\label{eq:ASB}
+    \text{ASB} &\equiv \mathbbm{E}(Y_{i0}|C_i=1) - \mathbbm{E}(Y_{i0}|C_i = 0) = \frac{\mathbbm{E}(Y|Z=0) - \mathbbm{E}(Y|Z=2,D=0)}{\mathbbm{E}(D|Z=2)}\\
+    \label{eq:ASL}
+    \text{ASL} &\equiv \mathbbm{E}(Y_{i1}|C_i = 1) - \mathbbm{E}(Y_{i1}|C_i=0) = \frac{\mathbbm{E}(Y|Z=2,D=1) - \mathbbm{E}(Y|Z=1)}{1 - \mathbbm{E}(D|Z=2)}
+\end{align}
+as we show in Appendix \hl{???}.
+For purposes of inference, both the ASB and ASL can be re-written as the difference of coefficients from a pair of just-identified linear IV regressions, namely
+\begin{align}
+\label{eq:ASB0}
+    \mathbbm{1}(Z_i\neq 1) (1 - D_i) Y_i &= \mathbbm{E}(Y_{i0}) \mathbbm{1}(Z_i = 0) + \mathbbm{E}(Y_{i0}|C_i=0)(1 - D_i)\mathbbm{1}(Z_i=2) + U_{i0}\\
+\label{eq:ASB1}
+    \mathbbm{1}(Z_i\neq 1) (1 - D_i) Y_i &= \mathbbm{E}(Y_{i0}) \mathbbm{1}(Z_i = 0) + \mathbbm{E}(Y_{i0}|C_i=1)(-D_i)\mathbbm{1}(Z_i = 2) + U_{i1}\\
+\label{eq:ASL0}
+    \mathbbm{1}(Z_i\neq 0) D_i Y_i &= \mathbbm{E}(Y_{i1}) \mathbbm{1}(Z_i = 1) + \mathbbm{E}(Y_{i1}|C_i=0)(D_i - 1)\mathbbm{1}(Z_i = 2) + V_{i0}\\
+\label{eq:ASL1}
+    \mathbbm{1}(Z_i\neq 0) D_i Y_i &= \mathbbm{E}(Y_{i1}) \mathbbm{1}(Z_i = 1) + \mathbbm{E}(Y_{i1}|C_i=1)D_i \mathbbm{1}(Z_i = 2) + V_{i1}
+\end{align}
+where the error terms $(U_{i0}, U_{i1})$ and $(V_{i0}, V_{i1})$ satisfy
+\[
+\mathbbm{E}
+\begin{pmatrix}
+V_{i0} \\ 
+V_{i1} \\ 
+\end{pmatrix} = 
+\mathbbm{E}\begin{pmatrix}
+U_{i0} \\ 
+U_{i1} \\ 
+\end{pmatrix}
+= \mathbbm{E}\left[
+\begin{pmatrix}
+V_{i0} \\ 
+V_{i1} \\ 
+\end{pmatrix} \mathbbm{1}(Z_i = z)
+\right]
+= \mathbbm{E}\left[
+\begin{pmatrix}
+U_{i0} \\ 
+U_{i1} \\ 
+\end{pmatrix} \mathbbm{1}(Z_i = z)
+\right] = 0
+, \quad z = 0, 1, 2.
+\]
+As in the case of the ASG from above, inference for the ASB and ASL can be carried out by saving the residuals from \eqref{eq:ASB0}--\eqref{eq:ASL1}. 
+These calculations are also automated in our companion STATA package.
+For details, see Appendix \hl{???}.
+
+\todo[inline]{Perhaps mention some other settings in which a design like this might be helpful? Need to hink about this.}
 
@@
 
-\todo[inline]{This next paragraph needs to be re-written.}
+\todo[inline]{This next paragraph needs to be removed and/or re-written. Perhaps we want to break to a new subsection before discussing these results?}
 
@@
 \end{center}
- \scriptsize
-
- \noindent \hl{ISAAC, CAN YOU EXPLAIN IN THE NOTE WHAT THIS TABLE IS? HOW ARE VARIABLES DEFINED, AND WHAT ARE THE COLUMNS AND THE SAMPLE }
+ \scriptsize This table shows the survey response rate in the first row, while the second row displays the number of pawns in each arm.
+The fourth column shows a p-value of an F-test of equality of means, showing that both the response rate and the number of pawns is balanced across arms.
 %\textit{Do file: } \texttt{ss\_att.do}
@@
 \end{center}
- \scriptsize
 
@@
 \noindent This table presents balance tests for the administrative data (Panel A) and survey data for those that pawned (Panel B).
-The first column ``Overall'' presents data for all arms together.
-The second column shows summary stats for one month before the experiment.
-The remaining columns present summary stats  for each arm separately.
-The last column shows the p-value of an F-test of the hypothesis that the mean across arms for that variable is the same across the 5 arms.
+The first three columns shows summary stats for each arm separately.
+The last column shows the p-value of an F-test of the hypothesis that the mean across arms for that variable is the same across the three arms.
 Randomization was done at the branch-day level.
-By design the observations are not exactly equal across arms as we were more interested in detecting effects in the choice-fee arm and less so in the no-choice-promise.
-Loan amount is the peso amount given to the client; Monday is the fraction of loans given on a Monday; Number of branch-day pawns is the number of loans given in each arm per day per branch.
-In Panel B: woman indicated whether the client is female, age of the client is measured in years; has pawned before is a dummy=1 if the client declares to have pawned before (although not necessarily with Lender $P$).
+By design the observations are not exactly equal across arms as we were more interested in detecting effects in the choice-commitment arm.
+Loan amount is the peso amount given to the client; Weekday is the fraction of loans given on a weekday, as opposed to weekends.
+In Panel B: woman indicated whether the client is female, age of the client is measured in years; subjective value is the self-reported value of the item, has pawned before is a dummy=1 if the client declares to have pawned before (although not necessarily with Lender $P$).
 The subjective probability of recovery was elicited a la Manski, from 0 to 100 what is the probability that you will recoup your pawn.
-High-school is a dummy that indicates if the client has completed high school.
-Finally, the survey response rate is the percentage of clients in the admin data for whom we have a baseline survey.
-%Panel C has the same variables, except for the last one.
-``\% ended up pawning'' measures the fraction of those that answered the survey that ended up pawning that day in that branch.
-P-values in Panel C test whether the 5 columns for treatment arms \textit{and} the column of pre-experiment have different means.
++High-school is a dummy that indicates if the client has completed high school.
 }
@@
 \end{center}
-\noindent \hl{ISAAC, CAN YOU EXPLAIN IN THE NOTE WHAT THIS TABLE IS? HOW ARE VARIABLES DEFINED, AND WHAT ARE THE COLUMNS AND THE SAMPLE }
+\scriptsize This table shows the treatment effects for our core pecuniary outcomes.
+Columns (1) \& (7) analyses this core measure.
+Further columns decomposes the core measure in all of its components, according to the different costs we measure :
+
+\begin{align*}
+    \underbrace{\text{Financial Cost}_i}_{(1)} =&  \underbrace{\sum_t P^i_{it}}_{\underset{(2)}{\text{Payments to interests}}}  +\underbrace{\sum_t P^f_{it}}_{\underset{(3)}{\text{Payments of fees}}} + \underbrace{\overbrace{\mathds{1}(\text{Default}_i)}^{(6)}\times (\text{Appraised Value}_i}_{\underset{(5)}{\text{Cost of losing pawn}}} + \underbrace{\sum_t P^c_{it}}_{\underset{(4)}{\text{Payments to capital}}})
+\end{align*}
+
+Each regression includes branch and day-of-week FE. Standard errors are clustered at the branch-day level.
+
 %\textit{Do file: } \texttt{decomposition\_main\_te.do}
@@
 \begin{center}
+\resizebox{1.45\textwidth}{!}{
 \scriptsize{\input{./Tables/mechanism.tex}}
+}
 \end{center}
@@
 \scriptsize {
-\noindent This table explores treatment effects in ``intermediate variables''. Each column represents a different dependent variable following the main specification \ref{basic_reg}.
-an OLS regression, and each panel represents a different treatment arm-control comparison.
-All regressions include fixed effects for branch, day of week fixed effects, number of pawns at the time of pawning this particular one, number of different treatment arms experienced before pawning this particular one.
-$R^2$ are not reported, they were less than 0.04 for all but the last column which had $R^2$'s close to 0.6.
+\noindent This table explores treatment effects in ``intermediate variables''.
+Each column represents a different dependent variable following the main specification  (\ref{basic_reg}).
 The last row shows the mean of the dependent variable for the control group.
-Dependent variables are as follows: Column (1) measures the number of days elapsed from the pawning date to the first payment done.
-Column (2) records the number of payments done within 230 days of the pawn.
-Column (3) is the average size of the payments for each client in pesos.
-Column (4) is self-reported cost to get to the branch plus the imputed loss of a whole day of salary (using the minimum wage in Mexico) multiplied by the number of visits to the branch.
-Column (5) measures the number of days it took to recover the pawn, conditional on recovering.
-The dependent variable in Column (6) is a dummy =1 if the client paid any positive amount within 230 days of the pawn.
-For Columns (7) and (8) the dependent variable it is the sum of total payments done within 230 days of the pawn divided by the size of the loan, but column (8) includes as regressors a dummy=1 if the client recovered her pawn, and its interaction with treatment.
-}
+Dependent variables are as follows: Column (1) shows the effect on the percentage of payments during the first visit.
+Column (2) records the probability of recovery in the first visit.
+Column (3) is the overall percentage of payment as fraction of the loan.
+Column (4) is the probability of making a positive payment and defaulting.
+Column (5) is the percentage of payments conditional on defaulting.
+Column (6) is the probability of ``selling'' the pawn, defined as not making any payment towards recovery of the item.
+Column (7) reports the probability of selling the pawn, conditional on defaulting.
+The bottom panel focuses on time related variables: Column (8) indicates the elapsed days toward the first payment.
+Column (9), (10), and (11) are related to the number of visits made to make payments, and columns (12), (13) speak on the loan duration.
+
+In sum, we find that the Forced commitment contract clients pays 13.8 days earlier in average, during this first visit, clients pay 7.9\% more of the loan amount, with a 8\% increase probability of recovery.
+Moreover, the forced commitment contract reduces the probability of defaulting and making a positive payment by 7\%, thus another channel for savings is that treatment helps avoid making payments toward recovery but defaulting.
+However, we see no effect in the number of visits and the probability of selling the pawn.}
 
@@
  \scriptsize
+
 %\textit{Do file: } \texttt{fc\_robustness.do}
@@
 \section{Figures}
-
-\begin{figure}[H]
-     \caption{Experiment description}
-    \label{exp_description}
-\begin{center}
-\begin{subfigure}{\textwidth}
-        \includegraphics[width=\textwidth]{Figuras/consort.pdf}
-    \end{subfigure}
-  \end{center}
-    \scriptsize 
-%\textit{Do file: }  \texttt{ss\_att.do}
-\end{figure}
-
-\begin{figure}[H]
-     \caption{Explanatory Material}
-    \label{ExplanatoryMaterial}
-    \begin{center}
-    \begin{subfigure}{\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/micas.pdf}
-    \end{subfigure}
-    \end{center}
-    \scriptsize
-        This is a (translated) sample information slide shown to clients. The real ones were twice the size of this figure and were laminated. Different ones were shown for each treatment arm.
-\end{figure}
-
-\begin{figure}[H]
-     \caption{Contract Terms Summary}
-    \label{PaperSlip}
-    \begin{center}
-    %\begin{subfigure}{0.65\textwidth}
-    %\caption{Receipt for client}
-     %   \centering
-        \includegraphics[width=0.65\textwidth]{Figuras/TicketLenderP.png}
-    %\end{subfigure}
-
-    %\vspace{3ex}
-    %\begin{subfigure}{0.65\textwidth}
-    %\caption{Personal promise signed by client}
-     %   \centering
-    %    \includegraphics[width=\textwidth]{Figuras/Personal Promise2.png}
-    %\end{subfigure}
-    \end{center}
-    \scriptsize
-        We show a sample receipt that was given to clients that got assigned to the fee-forcing contract (the font and format were changed to protect Lender's P identity).
-We want to highlight the salience of some items.
-First the title clearly indicated which contract the client has (arrow 1).
-Second, in the case of the fee contract it clearly indicates that there is a fee for paying late equivalent to 4\% of the value of the monthly payment (arrow 2).
-Third, there is a calendar for payments clearly specifying the dates and amounts to pay each month.
-%The bottom panel of the figure shows a ``promise slip'', the paper that those who were assigned (or chose) to the monthly payment with promise had to sign to make the promise salient.
-It emphasizes that the client is giving his word, and that the promise is not a legal document.
-\end{figure}
 
@@
 %Given that the loan lasts close to 90 days, bringing payments to present value makes little difference.
-         \hl{ISAAC: ARE THESE USING ALL THE DATA PERIODS? OR JUST 115 DAYS?}
+
       %\footnotesize{ } \textit{Do file: }  \texttt{hist\_fc.do}
+\end{figure}
+
+\begin{figure}[H]
+     \caption{Contract Terms Summary}
+    \label{PaperSlip}
+    \begin{center}
+    %\begin{subfigure}{0.65\textwidth}
+    %\caption{Receipt for client}
+     %   \centering
+        \includegraphics[width=0.65\textwidth]{Figuras/TicketLenderP.png}
+    %\end{subfigure}
+
+    %\vspace{3ex}
+    %\begin{subfigure}{0.65\textwidth}
+    %\caption{Personal promise signed by client}
+     %   \centering
+    %    \includegraphics[width=\textwidth]{Figuras/Personal Promise2.png}
+    %\end{subfigure}
+    \end{center}
+    \scriptsize
+        We show a sample receipt that was given to clients that got assigned to the fee-forcing contract (the font and format were changed to protect Lender's P identity).
+We want to highlight the salience of some items.
+First the title clearly indicated which contract the client has (arrow 1).
+Second, in the case of the fee contract it clearly indicates that there is a fee for paying late equivalent to 4\% of the value of the monthly payment (arrow 2).
+Third, there is a calendar for payments clearly specifying the dates and amounts to pay each month.
+%The bottom panel of the figure shows a ``promise slip'', the paper that those who were assigned (or chose) to the monthly payment with promise had to sign to make the promise salient.
+It emphasizes that the client is giving his word, and that the promise is not a legal document.
+\end{figure}
+
+\begin{figure}[H]
+     \caption{Experiment description}
+    \label{exp_description}
+\begin{center}
+\begin{subfigure}{\textwidth}
+        \includegraphics[width=\textwidth]{Figuras/consort.pdf}
+    \end{subfigure}
+  \end{center}
+    \scriptsize 
+%\textit{Do file: }  \texttt{ss\_att.do}
+\end{figure}
+
+\begin{figure}[H]
+     \caption{Explanatory Material}
+    \label{ExplanatoryMaterial}
+    \begin{center}
+    \begin{subfigure}{\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/micas.pdf}
+    \end{subfigure}
+    \end{center}
+    \scriptsize
+        This is a (translated) sample information slide shown to clients. The real ones were twice the size of this figure and were laminated. Different ones were shown for each treatment arm.
 \end{figure}

### 2023-01-26 OA.tex
bounding censoring te & other results

@@
 \subsection{Main treatment effects: Additional material}
+
+\begin{table}[H]
+\caption{Bounding censoring}
+\label{bounding_censoring}
+\begin{center}
+\resizebox{0.9\textwidth}{!}{
+\scriptsize{\input{./Tables/censoring_imp.tex}}
+}
+\end{center}
+ \scriptsize 
+%\textit{Do file: } \texttt{censoring_imp.do, censoring_imp_pr.do}
+\end{table}
+
+\begin{figure}[H]
+        \caption{Interpolation on bounding censoring}
+    \label{interpolation_censoring_imp}
+    \begin{center}
+   \begin{subfigure}{0.49\textwidth}
+   \caption{Significance area for Default }
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/frontera_sig_def_imp.pdf}
+    \end{subfigure} 
+   \begin{subfigure}{0.49\textwidth}
+   \caption{Significance area for APR}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/frontera_sig_apr.pdf}
+    \end{subfigure}     
+    \end{center}
+     \scriptsize  The next figure aims to answer the following question: For how many loans in the control arm can we impute recovery, and for how many in the treatment arm can we impute default and still have significance?
+     This figure shows exactly the boundary separating significance when we vary the percentage of imputed censored loans with recovery and default respectively for control and treatment.
+Each corner in the square will correspond to one of the panels from the Table \ref{bounding_censoring}.
+For instance, the origin is the best-case scenario (Panel C) and the point (100,100) (Panel D) is the worst-case scenario.
+Thus we can think of this graph as an `interpolation' from the four extreme cases.
+The `x' indicates the proportions imputed by the lasso-logit model, and the different lines correspond to setting different significance levels.
+
+     %\textit{Do file: }  \texttt{interpolation_{censoring_imp.do}
+\end{figure}
 
@@
 \vspace{.3in}
+
+\begin{figure}[H]
+     \caption{Heterogeneous Treatment Effects}
+    \label{heterogeneous_effects}
+    \begin{center}
+    \begin{subfigure}{.45\textwidth}
+      \caption{Financial cost (in MXN)}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_pro_2.pdf}
+    \end{subfigure}
+     \begin{subfigure}{0.45\textwidth}
+    \caption{Effective APR}
+       \centering
+      \includegraphics[width=\textwidth]{Figuras/he_dist_apr_pro_2.pdf}
+    \end{subfigure}
+     \begin{subfigure}{0.45\textwidth}
+    \caption{Default}
+       \centering
+      \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_2.pdf}
+    \end{subfigure}  
+     \begin{subfigure}{0.45\textwidth}
+    \caption{Recovery}
+       \centering
+      \includegraphics[width=\textwidth]{Figuras/he_dist_des_c_pro_2.pdf}
+    \end{subfigure}      
+    \end{center}
+         \scriptsize
+     plots the distribution of the heterogeneous treatment effects on financial cost, estimated using \cite{atheygrf}.
+  %\footnotesize{ } \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}
+\end{figure}
+
 \begin{figure}[H]
@@
 
-\section{Mechanisms }
+\section{ Mechanisms }
 

### 2023-01-26 donde.tex
bounding censoring te & other results

@@
 
-We define a borrower's financial cost as the \textcolor{red}{outflow --in cash or pawn value-- from the borrower to the lender.} This includes all payments the borrower made toward interest and fees, but also the value of the pawn when there is default.
+We define a borrower's financial cost as the total monetary outflow --in cash or pawn value-- from the borrower to the lender.
+This includes all payments the borrower made toward interest and fees, but also the value of the pawn when there is default.
 When there is no default the borrower gets her pawn back and there is no loss of value for the borrower.
@@
 \noindent where $t$ indexes days, and $\mathds{1}(\text{Default}_i)$ is an indicator function for defaulting.
-Even though we observe transactions at the day level, \textcolor{red}{we don't use discounting} since the period of loan is only 90 days.
-\textcolor{red}{In robustness checks we do show that results are virtually unchanged when applying a wide range of time discounting factors.}
+Because the period of the loan is only 90 days we do not use discounting in calculating costs.
+In robustness checks we show that results are virtually unchanged when applying a wide range of time discounting factors.
 
@@
 
-As a second measure of cost we calculate the Annual Percentage Rate (APR) in order to express the cost as a percentage of the loan, per year.\footnote{Loan term takes into account all the loan period, including those extended through refinancing}.
+As a second measure of cost we calculate the Annual Percentage Rate (APR) in order to express the cost as a percentage of the loan, per year, inclusive of default costs.\footnote{Loan term takes into account all the loan period, including those extended through refinancing}.
 The standard definition is given in the following formula:
@@
 
-\noindent \textbf{The Commitment Contract.} For the purpose of the experiment we designed a new contract that is identical to the status quo contract except that, informed by the behavioral literature on the ways to improve repayment in credit contracts, it enhances the regularity and salience of payments.
+\noindent \textbf{The Commitment Contract.} For the purpose of the experiment we designed a new contract that is identical to the status quo contract except that, informed by the designed of micro-lending contracts, it enhances the regularity and salience of payments as a way to encourage repayment \citep{morduch1999microfinance, bauer2012behavioral}.
 It has the same interest rate (7\% \textit{per month}) which accumulates daily on outstanding debt, it has the same loan size/collateral ratio (70\%), it has the same loan term (90 days, and a grace period of 15 days), and the gold pawn gets appraised in the same way by the same appraisers.
 The Commitment contract however requires the client to make regular monthly payments for the duration of the contract, with the principal and interest payments split evenly across the three months of the contract (day 30, 60 and 90 after loan disbursement).
-The importance of this monthly payment was %reinforced in two ways; first by reminders issued to any borrower delinquent on the monthly payments that were supposed to be made, and secondly
-made salient in the contract and payment receipts (see Figure \ref{PaperSlip}), and by the levying of a nominal fee (2\% of minimum due) on individuals who fell behind in their payments.
+The importance of this monthly payment was made salient in the contract and payment receipts (see Figure \ref{PaperSlip}), and by the levying of a nominal fee (2\% of minimum due) on individuals who fell behind in their payments.
 The propose of the small fee was to mainly to make the structured schedule salient, not to be a large disincentive to be late.
@@
 
-%\todo[inline]{Somewhere in here we need to explain how we handle repeat pawns.
-If I recall correctly, we've settled on including only data for each person's first visit.
-This visit may include multiple pawns, but this is fine since we cluster at the branch-day level.}
-
 Some clients pawned more than one time during the duration of the experiment, with \hl{XXX\%} pawning 2 times and \hl{XXX\%} more than 2 times.
@@
 
-\paragraph{Timeline.} Figure \ref{exp_description}(a) \textcolor{red}{shows the timeline when the experiment happens and also the length of time for which we observe payments}.
+\paragraph{Timeline.} Figure \ref{exp_description}(a) shows the timeline when the experiment happens and also the length of time for which we observe payments.
 For contracts in the first week, we observe up to \hl{XXX} days, with \hl{XXX\%} of contracts ending during our sample period (in default or recovery).
@@
 To test for this, we examine the number of loans given per branch-day, with specific attention to whether the Forced Commitment arm led to a lower number of borrowers per day.
-The \hl{first} row of Table \ref{attrition_table} shows there is no difference between the Control and Forced Commitment arm in terms of the number of pawns per branch-day, suggesting that there has been no differential refusal.\footnote{The Choice arm appears to have a somewhat larger number of borrowers than the Control arm (p-value=\hl{XXX}), but we cannot reject equality with the Forced Commitment arm (p-value=\hl{XXX}), or across all arms (p-value=\hl{XXX}).}  Therefore it appears that the treatments have not induced any endogenous shifts in the composition of borrowers.
+The \hl{first} row of Table \ref{attrition_table} shows there is no difference between the Control and Forced Commitment arm in terms of the number of pawns per branch-day.\footnote{The Choice arm appears to have a somewhat larger number of borrowers than the Control arm (p-value=\hl{XXX}), but we cannot reject equality with the Forced Commitment arm (p-value=\hl{XXX}), or across all arms (p-value=\hl{XXX}).}  The second row makes the same point in a more focused way, given that the surveys were conducted prior to the revelation of treatment status.
+In no arm did more than three percent of individuals refuse loans subsequent to the survey, and neither these rates nor the rate of survey response are different across arms.
+Therefore it appears that the treatments have not induced any endogenous shifts in the composition of borrowers.
 
@@
 
-Two more subtle form of sample selection arise if the treatments induce borrowers to repawn in different ways (which they do), or to pay off loans at a different rate (which they do as well).
-We pursue a simple approach to these problems, by using only the first experimental pawn taken by a given borrower during the study window (ignoring all subsequent loans), and by defining outcomes in a manner that is consistent whether or not the loan had been closed at the time that the study observation window ends (e.g., `loan was repaid', which is defined even if the loan had not been completed, versus `loan defaulted', which is not).
-We return in the subsequent section to more detailed analysis of the implications of these two issues.
+A more subtle form of sample selection could arise if the treatments induce borrowers to re-pawn in different ways, especially given that their treatment status on subsequent loan/days may not be the same as that initially assigned.
+To handle this issue our analysis uses only the first loan taken by each individual during the experimental window.
 
@@
 Results for these outcomes appear in columns (1) and (6) of Table \ref{main_impact_table}.
-The remaining columns decompose the financial cost and APR outcomes into their components: payments to capital, fees, interest, and the cost of losing the pawn. 
-Columns (2)--(5) correspond to financial cost while columns (7)--(10) correspond to APR.
+The remaining columns decompose the financial cost and APR outcomes into their components: interest payments (col 2), payment towards any fees incurred (col 3), payments toward the principal (col 4).
+It is of interest to this research and to Lender P whether structured frequent payment decrease default.
+In column 6 the dependent variable is a dummy indicating default.
+Column 5 shows the value of lost pawn conditional on losing it.
+Finally, column 7 rescales financial cost as a function of loan size to estimate causal effects on incurred APR.\footnote{As we explained above, loans can be extended for an additional 3 months by paying the interest owed and restarting the loan under the same treatment conditions.
+This means that some loans extend for more than 3 months.
+We consider the entire flow of cost from the duration of our sample.}
 
@@
 
-As we explained above, loans can be extended for an additional 3 months by paying the interest owed and restarting the loan under the same treatment conditions.
-This means that some loans extend for more than 3 months.
-We consider the cost
-
-\paragraph{Results.} The results are extremely stark.
+\paragraph{Results.} The results are stark.
 The Forced Commitment arm yields large and significant decreases in the cost of loans to clients, as measured either by financial cost or APR.
-Despite causing an increase in payments to capital and fees, the Forced arm leads to a sharp decrease in overall costs of borrowing, driven by a XX percentage point decrease in the probability of default (more than a XX\% reduction from a baseline of XX\% default).
-A credit product that has an effective average APR of XXX\% in the status quo arm (inclusive of default) is reduced to a cost of XXX\% through the imposition of a more regularized payment structure.  
-While the Forced arm increases fees significantly relative to a control mean of 0, the monetary value of the fees imposed is small (28 pesos).  
-Payments towards capital also rise by XXX pesos because the arm is so effective at improving the fraction of individuals actually repaying their loans.  
-Because the regular repayment structure moves the timing of payment forward it saves borrowers an average of 109 pesos in interest costs.  
-The vast majority of the overall treatment effect, however, stems from the XXX pesos from not losing the pawn. 
-In contrast, the Choice arm fails to deliver significant changes in any measure, with the exception of an increase in fees, for which we are highly powered since this outcome is zero for every control observation.
+Despite causing an increase in fees, the Forced arm leads to a decrease of 379 pesos in the costs of borrowing (out of a group mean of 1851 in the status quo), that is equivalent to 20\% reduction as a fraction of mean cost.
+These cost savings arise from a 6.5 percentage point (pp) decrease in the probability of default (out of a baseline mean of 44pp), which implies cost savings of 254 pesos.
+But also from lower interest payments, since as we will document the treatment is effective at speeding up payments, with the benefits that the interest rate applies to a smaller principal.
+This translates into a large reduction in APR.
+A credit product that has an effective average APR of 184\% in the status quo arm (inclusive of default) is reduced to a cost of 34\% through the imposition of a more regularized payment structure.
+
+In contrast, to the impressive effectiveness of the Forced commitment arm, the Choice arm fails to deliver significant changes in any measure, with the exception of an increase in fees, for which we are highly powered since this outcome is zero for every control observation.
+Giving borrowers the choice of contract did not decrease financial cost, whereas forcing them into a structured payment contract dramatically reduced it.
+As we explore later in the paper, the null effect of the Choice arm arises because few people had demand for it, with \hl{XXX\%} choosing the less effective status-quo contract.
 
 \paragraph{Intermediate outcomes.} To shed light on the mechanisms behind the ATEs discussed above, Table \ref{mechanisms} shows how treatment affects a number of intermediate outcomes.
-Column (1) shows that borrowers' first payment occurs 8 days earlier on average in the Forced Commitment arm than under the status quo.
-Column 4 shows that the number of payments increases by 0.19.
-Treatment effects are concentrated on the intensive margin, as treatment does \emph{not} affect the fraction of clients who fail to make any payments (Column 12). 
-The percentage of the loan paid increases by 9 percentage points on average (Column 9). 
-Moreover, the percentage of the loan paid is even smaller for those who end up losing the pawn (first row of column 9). 
-This last point is critical. 
-Forced commitment could be financially harmful if it caused individuals to make fruitless payments on loans for which they later defaulted. 
-In contrast, we find that forced commitment causes individuals who would otherwise have made partial payments but ultimately defaulted to instead recover their pawn.
-
-\todo[inline]{We need to add a bit of lead-in here to make clear why we're going all these robustness exercises.
-Basically we're trying to foreclose possible explanations for why the treatment could be harmful.
-We should say something here like ``when we say mistake below, what we mean by this is X and we're going to show you right now that explanations A, B, and C are not operative here.''}
-
-\paragraph{Robustness.} We have shown that forcing borrowers to take the monthly payment contract significantly reduced financial cost.
-Although the paper focuses on financial cost, here we consider two additions to the cost and benefit calculation.
-We include the cost of going to the branch, and we consider the value of the pawn as perceived by the borrower instead of its gold value.
+One can group the types of intermediate outcomes into two categories: measures of the speed of pawn recovery, and measures of the decision of when to default.
+While the first payment for borrowers in the status-quo contract occurs on average only on day 82 (on a 90 days contract), borrowers in the forced commitment arm start paying 13.8 days earlier on average (col 1).
+Not only do they start paying earlier, the first payment is also 7.9\% larger (col 2), and a larger fraction of 7.9\% actually pay in full and recover their pawn in the first payment , compared to 30\% in the status quo contract (col 3).
+The resolution of the loan (either by payment or default) is shortened by 27.9 days (col 4), and conditional on recovery (an endogenous control) by 17.9 days (col 5).
+
+A very undesirable outcome from the borrower's perspective is to pay towards the loan without paying in full, i.e.
+defaulting on the loan.
+In this case, they lose both the collateral and any payments made toward recovery.
+One could be concerned that by encouraging them to pay monthly, more borrowers could end up in this dire scenario in the Forced commitment contract.
+Column 6 shows this is not the case.
+On the contrary,  7 percentage points fewer borrowers end up in this situation, compared to 12 percent in the status quo contract.
+Conditional on defaulting those assigned to the Force commitment contract have paid 3.9\% less of their loan (col 7), and 14 percentage higher proportion of borrowers pay zero conditional on defaulting, an outcome analogous to selling their pawn (col 8).
+One interpretation of these results is that the Forced commitment contract forces borrowers to think earlier about whether they will indeed be able to eventually recover their pawn, and separates borrowers into those ``selling'' their pawn and those recovering it, reducing the share of undecided borrowers that end up paying interest and end up losing the pawn anyway.
+This mechanism may also help to explain why the Forced commitment contract does not increase the number of visits to the branch to pay (col 9): those recovering their pawn visit more, but those defaulting have 0.19 less visits (col 10).
+
+\paragraph{Other costs.} We have shown that forcing borrowers to take the monthly payment contract significantly reduces financial cost.
+Although the paper focuses on financial cost, we consider three additional costs here.
+First, We include the cost of going to the branch.
+This includes the self-reported transport cost (most use public transport), as well as the opportunity cost of time.
+To err on the conservative side, we subtract a whole day's minimum wage the day of the visit, instead of just the wage corresponding to a couple of hours.
+Second, we consider a rough proxy of the value of liquidity they lose by paying earlier.
+We act as if each payment they make comes from an additional loan they take, which incurs interest at the same rate as Lender P's loan (7\% per month).
+So far we have valued the collateral at the gold value appraised by the lender, but the piece may be worth more to the borrower than its gold value.
+For many of them the pawned jewelry has sentimental value as well.
+This is reflected in the subjective valuation they reported in the survey\footnote{The minimum peso amount at which they would sell the piece.} which is \hl{XXX\%} higher on average.
+Our third extra cost considers this higher value.
+
+Table \ref{table_robustness_fc} shows results. We present results
 
@@
 Hence endogenous re-entry to the experiment does not appear to be driving our results.
+
+\subsection{Censoring of Loan Completion}
+
+The window of time during which we were able to observe borrower behavior was limited in each branch, meaning that there were loans that we do not see completed (particularly those pawns that were rolled over for one or two further 90-day spells).
+Overall, XX\% of all experimental loans are censored, meaning that they neither default nor repay within the observation window.
+In the prior analysis we handle this issue by using outcomes such as `did not default' which are defined even when we do not observe the completion of the loan, and only considering costs that we observe directly.
+We have also showed, however, that one effect of the forcing arm is to accelerate repayment, meaning that it is less likely for loans in this arm to be censored.
+This issue is illustrated in Figure \ref{survival_graph}, which shows the CDF of loan completion (Panel (a)) and loan recovery (Panel (b)) by the number of days since first pawn.
+Two features of these graphs are salient for our analysis.
+The first is the extent to which loan outcomes are observed more quickly in the forcing arm.
+This is primarily due to the the substantially higher rate of repayment of Forced Commitment loans at 120 days (~15 pp higher than the other arms).
+The second is the very low rate at which loans are recovered in any arm after 120 days.
+In the 180 day window after the second rollover period we see a further ~10 percent of loans repaid in all arms, but these loans are largely dormant, suggesting that many of the censored loans will in fact be defaulted upon.
+
+The confluence of censoring and a treatment effect on censoring is problematic from an experimental point of view.
+The approach taken so far is a conservative one in that it inherently assumes that all of the loans outstanding at the end of the observation window will be repaid, making it so that the acceleration of payment observed in the Forced arm does not translate mechanically into a treatment effect on default.
+Given the centrality of this issue to the observed costs, we now delve into it more detail.
+One way of considering the effect that this issue could have on our results is to make extreme assumptions about the outcome of these loans in the treatment and control so as to bound the possible influence of censoring.
+In Table \ref{mns} we compare the Forced and Control arms, making the bracketing assumptions about repayment on censored loans.
+Panel A assumes all censored loans are repaid, and Panel D that all default.
+Panel B provides the lower bound for the treatment effect by assuming censored control loans are always repaid and treatment loans never are, and Panel C the upper bound by making the reverse assumption.
+Comfortingly, even with these extreme assumptions the significance on the main treatment effects never flips and treatment effects on financial cost and interests payments remain negative and significant in all scenarios.
+So there appears to be no scope for the censoring issue to overturn our main results.
+
+Finally, Panel E of this table conducts a logit prediction model that uses all of the available information on loans that were completed to predict the outcome of loans that were not.
+This is a best guess of the outcome on censored loans.
+Using this prediction, we replicate the main experimental results and find that the treatment effect on financial cost increases from -378 (main results) to -525 (censored loans predicted), and the APR from -34\% to -62\%.
+Hence, while the censoring issue does have a substantial influence on the magnitude of our estimated treatment effects, these  checks confirm that a) the core results are robust to censoring, and b) the headline approach that we take to the issue is conservative and is likely understating the true magnitude of impacts.
 
@@
 \label{eq:ASB1}
-    \mathbbm{1}(Z_i\neq 1) (1 - D_i) Y_i &= \mathbbm{E}(Y_{i0}) \mathbbm{1}(Z_i = 0) + \mathbbm{E}(Y_{i0}|C_i=1)(-D_i)\mathbbm{1}(Z_i = 2) + U_{i1}\\
+    \mathbbm{1}(Z_i\neq 1) (1 - D_i) Y_i &= \mathbbm{E}(Y_{i0}) \mathbbm{1}(Z_i \neq 1) + \mathbbm{E}(Y_{i0}|C_i=1)(-D_i)\mathbbm{1}(Z_i = 2) + U_{i1}\\
 \label{eq:ASL0}
-    \mathbbm{1}(Z_i\neq 0) D_i Y_i &= \mathbbm{E}(Y_{i1}) \mathbbm{1}(Z_i = 1) + \mathbbm{E}(Y_{i1}|C_i=0)(D_i - 1)\mathbbm{1}(Z_i = 2) + V_{i0}\\
+    \mathbbm{1}(Z_i\neq 0) D_i Y_i &= \mathbbm{E}(Y_{i1}) \mathbbm{1}(Z_i \neq 0) + \mathbbm{E}(Y_{i1}|C_i=0)(D_i - 1)\mathbbm{1}(Z_i = 2) + V_{i0}\\
 \label{eq:ASL1}
@@
 
-\todo[inline]{Perhaps mention some other settings in which a design like this might be helpful? Need to hink about this.}
+\todo[inline]{Perhaps mention some other settings in which a design like this might be helpful? Need to think about this.}
 
@@
 \begin{center}
-\resizebox{1.45\textwidth}{!}{
+\resizebox{1.30\textwidth}{!}{
 \scriptsize{\input{./Tables/mechanism.tex}}
@@
 The last row shows the mean of the dependent variable for the control group.
-Dependent variables are as follows: Column (1) shows the effect on the percentage of payments during the first visit.
-Column (2) records the probability of recovery in the first visit.
-Column (3) is the overall percentage of payment as fraction of the loan.
-Column (4) is the probability of making a positive payment and defaulting.
-Column (5) is the percentage of payments conditional on defaulting.
-Column (6) is the probability of ``selling'' the pawn, defined as not making any payment towards recovery of the item.
-Column (7) reports the probability of selling the pawn, conditional on defaulting.
-The bottom panel focuses on time related variables: Column (8) indicates the elapsed days toward the first payment.
-Column (9), (10), and (11) are related to the number of visits made to make payments, and columns (12), (13) speak on the loan duration.
-
-In sum, we find that the Forced commitment contract clients pays 13.8 days earlier in average, during this first visit, clients pay 7.9\% more of the loan amount, with a 8\% increase probability of recovery.
-Moreover, the forced commitment contract reduces the probability of defaulting and making a positive payment by 7\%, thus another channel for savings is that treatment helps avoid making payments toward recovery but defaulting.
-However, we see no effect in the number of visits and the probability of selling the pawn.}
+Panel A talks about the speed of payment.
+Column (1) indicates the elapsed days toward the first payment.
+Column (2) shows the effect on the percentage of payments during the first visit.
+Column (3) records the probability of recovery in the first visit, and columns (4), (5) speak on the loan duration.
+Panel B are variables related to default.
+Column (6) is the probability of making a positive payment and defaulting.
+Column (7) is the percentage of payments conditional on defaulting.
+Column (8) reports the probability of selling the pawn, conditional on defaulting.
+Finally Panel C is related to the number of visits made to make payments.
+
+In sum, we find that the Forced commitment contract clients pays 13.8 days earlier in average, during this first visit, clients pay 7.7\% more of the loan amount, with a 8\% increase probability of recovery.
+Moreover, the forced commitment contract reduces the probability of defaulting and making a positive payment by 7\%, thus another channel for savings is that treatment helps avoid making payments toward recovery but defaulting.}
 
@@
     \scriptsize 
+    \hl{Add timeline figure}
 %\textit{Do file: }  \texttt{ss\_att.do}
@@
     \scriptsize
-    This figure shows 
+   \hl{This is an outdated figure. Need to update}
      %\textit{Do file: }  \texttt{tot\_tut\_graph.do}
@@
 
-\cleardoublepage
-
 \begin{figure}[H]
@@
 This methodology was proposed by \cite{GOLDMAN2018143}.
+
+     \hl{Isaac : If I recall correctly we agreed to not work with the propensities.
+Besides this is giving us different results(?) - this was due to not using actual choosers and the prop.
+score model not being very good.
+Thus this will be removed?
+}
           %\footnotesize{ \textit{Do file: }  \texttt{benefit\_choice.do}}

### 2023-02-28 OA.tex
presentation

@@
 
+\newpage
 \vspace{.2in}
@@
 \end{proof}
-
-\newpage
 
@@
 
+\normalsize
+\linespread{1.25}
+%Really force it to normal size and linespread
+\normalsize
+\linespread{1.25}
+
 \subsection{Testing for heterogeneity}
+\label{append:chernozhukov}
 Our approach relies on the following simple observation: if $\Delta_i$ is constant across $i$ then we must have 
@@
 \subsection{Derivations for Section \ref{sec:randchoice}}
+\label{append:randchoice}
 
@@
 \begin{assumption}\mbox{}
+\label{assump:randchoice}
    \begin{enumerate}[(i)]
@@
    \end{enumerate}
-   \label{assump:randchoice}
 \end{assumption}
@@
 \begin{lem}\mbox{}
+\label{lem_randchoice}
    \begin{enumerate}[(i)]
@@
    \end{enumerate} 
-   \label{lem:randchoice}
 \end{lem}
@@
 For parts (i) and (iii) we require an expression for $\mathbbm{E}(Y_0|C=1)$ in terms of the observables $(Y, D, Z)$.
-By Lemma \ref{lem:randchoice}(ii) and iterated expectations
+By Lemma \ref{lem_randchoice}(ii) and iterated expectations 
 \[
@@
 \]
-Re-arranging and substituting Lemma \ref{lem:randchoice}(i) and (iv),
+Re-arranging and substituting Lemma \ref{lem_randchoice}(i) and (iv),
 \begin{equation}
@@
 \end{equation}
-Part (i) follows by combining \eqref{eq:Y0C1} with Lemma \ref{lem:randchoice}(v) and simplifying; part (iii) follows by combining \eqref{eq:Y0C1} with Lemma \ref{lem:randchoice}(iv) and simplifying.
+Part (i) follows by combining \eqref{eq:Y0C1} with Lemma \ref{lem_randchoice}(v) and simplifying; part (iii) follows by combining \eqref{eq:Y0C1} with Lemma \ref{lem_randchoice}(iv) and simplifying.
 Similarly, for parts (ii) and (iv) we require an expression for $\mathbbm{E}(Y_1|C=0)$ in terms of observables.
-By Lemma \ref{lem:randchoice}(iii) and iterated expectations,
+By Lemma \ref{lem_randchoice}(iii) and iterated expectations,
 \[
@@
 \]
-Re-arranging and substituting Lemma \ref{lem:randchoice}(i) and (v),
+Re-arranging and substituting Lemma \ref{lem_randchoice}(i) and (v),
 \begin{equation}
@@
 \end{equation}
-Part (ii) follows by combining \eqref{eq:Y1C0} with Lemma \ref{lem:randchoice}(iv) and simplifying; part (iv) follows by combining \eqref{eq:Y1C0} with Lemma \ref{lem:randchoice}(v) and simplifying.
+Part (ii) follows by combining \eqref{eq:Y1C0} with Lemma \ref{lem_randchoice}(iv) and simplifying; part (iv) follows by combining \eqref{eq:Y1C0} with Lemma \ref{lem_randchoice}(v) and simplifying.
 \end{proof}
@@
 %\]
-%by Lemma \ref{lem:randchoice}(ii) and iterated expectations.
+%by Lemma \ref{lem_randchoice}(ii) and iterated expectations.
 %Re-arranging, 
@@
 %\]
-%Therefore, by Lemma \ref{lem:randchoice} (i) and (iv)
+%Therefore, by Lemma \ref{lem_randchoice} (i) and (iv)
 %\begin{align*}
@@
 %\]
-%by Lemma \ref{lem:randchoice}(iii) and iterated expectations.
+%by Lemma \ref{lem_randchoice}(iii) and iterated expectations.
 %Rearranging,
@@
 %\]
-%Therefore, by Lemma \ref{lem:randchoice} (i) and (v),
+%Therefore, by Lemma \ref{lem_randchoice} (i) and (v),
 %\begin{align*}
@@
 
-\subsection{Bounding ToT \& TuT} \label{bound_tot_tut_appendix}
-
-\vspace{.2in}
+\subsection{Testable Implications of the Exclusion Restriction}
+\label{append:exclusion}
+
 \normalsize
@@
 
-Even without the exclusion restriction, it’s possible to bound $\mathbb{E}[Y_1-Y_0\;|\;T=0]$ and $\mathbb{E}[Y_1-Y_0\;|\;T=1]$ using observed outcomes in the forced arm and observed take-up in the choice arm.
-It should also be possible to create bounds conditional on covariates.
-The basic approach is similar to that of \cite{huber_mellace}.
-\\
-
-From the $Z=0$ arm we identify the distribution $F_0$ of $Y_0$, the potential outcome when forced into the no-commitment contract.
+This section describes the testable implications of our exclusion restrictions: \eqref{eq:exclusion0} and \eqref{eq:exclusion1} from Section \ref{sec:potentialOutcomes}. 
+To consider possible violations of these conditions, it is helpful to introduce some additional notation.
+As in the body of the text, let $Y_0 \equiv Y(d=0,z=0)$ and $Y_1 \equiv Y(d=1,z=1)$ denote the potential outcomes under \emph{forced treatment}: $Y_0$ is the potential outcome when forced into the status quo contract and $Y_1$ when forced into the commitment contract.
+Further let $Y_{0,2} \equiv Y(d=0,z=2)$ and $Y_{1,2} \equiv Y(d=1,z=2)$ denote the potential outcomes under \emph{free choice of treatment}: $Y_{0,2}$ is the potential outcome when choosing the status quo contract and $Y_{1,2}$ when choosing the commitment contract.
+Using this notation, \eqref{eq:exclusion0} becomes $Y_0 = Y_{0,2}$ and while \eqref{eq:exclusion1} becomes $Y_1 = Y_{1,2}$.
+If we do not impose this pair of equalities, part (iii) of Assumption \ref{assump:randchoice} becomes 
+\[
+Y = \mathbbm{1}(Z =0) Y_{0} + \mathbbm{1}(Z = 1)  Y_{1}  + \mathbbm{1}(Z = 2) \left[(1 - C) Y_{0,2} + C Y_{1,2} \right]
+\]
+but parts (i) and (ii) continue to hold.
+Accordingly, parts (i)--(iii) of \ref{lem_randchoice} are unchanged, while parts (iv) and (v) become
+\[
+\mathbbm{E}(Y|D=0,Z=2) = \mathbbm{E}(Y_{0,2}|C=0), \quad
+\mathbbm{E}(Y|D=1,Z=2) = \mathbbm{E}(Y_{0,1}|C=1).
+\]
+Using these expressions, the testable restrictions we consider here are 
+\[
+\mathbbm{E}(Y_0|C=0) = \mathbbm{E}(Y_{0,2}|C=0) \text{ and } \mathbbm{E}(Y_1|C=1) = \mathbbm{E}(Y_{1,2}|C=1).
+\]
+\todo[inline]{Need to talk about how why these are restrictions for choosers and non-choosers respectively. It's because they're the only people we can observe in the relevant $Y{d,2}$ state.}
+
+Because our approach is closely related to that of \cite{huber_mellace}, the following is a heuristic explanation rather than a fully-rigorous proof.
+
+To begin, define the shorthand $p \equiv \mathbbm{E}(C=1) = \mathbbm{P}(D=1|Z=2)$.
+Because $Z$ was randomly assigned, a fraction $p$ of participants with $Z = 1$ have $C = 1$ and the distribution of $Y|Z=1$ is a mixture of $Y_1|C=1$ and $Y_1|C=0$ with mixing weights $p$ and $1 -p$.
+The participants with $C = 1$ must lie \emph{somewhere} in the distribution of $Y_0|Z=1$ so consider the two most extreme cases: they could occupy the bottom or the top $p\times 100\%$ of the distribution.
+It follows that
+\[
+\mathbbm{E}(Y|Z=1,Y\leq y^1_{p}) \leq \mathbbm{E}(Y_1|C=1) \leq \mathbbm{E}(Y|Z=1,Y \geq y^1_{1-p})
+\]
+where $y^1_p$ and $y^1_{1-p}$ are the $p$ and $1 - p$ quantiles of the distribution of $Y_1$.
+These quantiles are point identified since $Y|Z=1$ has the same distribution as $Y_1$ under random assignment of $Z$.
+If $Y_{1,2} = Y_1$ then it follows that $\mathbbm{E}(Y|D=1,Z=2) = \mathbbm{E}(Y_1|C=1)$ yielding the bounds
+\[
+\mathbbm{E}(Y|Z=1,Y\leq y^1_{p}) \leq \mathbbm{E}(Y|D=1,Z=2) \leq \mathbbm{E}(Y|Z=1,Y \geq y^1_{1-p}).
+\]
+If either of these is violated, the exclusion restriction does not hold.
+
+\todo[inline]{Update from here down.}
+\[
+\mathbbm{E}(Y|Z=1,Y\leq ?) \leq \mathbbm{E}(Y|D=1,Z=2) \leq \mathbbm{E}(Y|Z=1,Y \geq ?)
+\]
+\[
+\mathbbm{E}(Y|Z=0,Y\leq ?) \leq \mathbbm{E}(Y|D=0,Z=2) \leq \mathbbm{E}(Y|Z=0,Y \geq ?)
+\]
+
+If $Y_1 = Y_{1,2}$ then $\mathbbm{E}(Y|D=1, Z=2)$ point identifies $\mathbbm{E}(Y_1|C=1)$.
+
+$D = 1, Z=2$ means $C = 1$; $D = 0, Z=2$ means $C = 0$;
+
+\todo[inline]{Update below here}
+Because the basic approach is similar to that of \cite{huber_mellace}, we give only a heuristic explanation here rather than a formal proof.
+
+In the absence of the exclusion restriction, the $Z=0$ arm of the experiment point identifies the distribution $F_{00}$ of $Y(d=0,z=0)$.
+This is a person's potential outcome when \emph{forced} into the no-commitment contract.
+Similarly, the $Z=1$ arm point identifies the distribution $F_{11}$ of $Y(d=1,z=0)$, the potential outcome when forced into the commitment contract.
+The $Z = 2$ arm point identifies $p_C \equiv \mathbbm{E}(C)$, the share of individuals who \emph{would choose commitment}, given the option.
+
+Because $Z$ is randomly assigned, $p_C = \mathbbm{E}(C) = \mathbbm{E}(C|Z=z)$ for any arm $z\in \{0, 1, 2\}$ of the experiment.
+This tells us that $F_{00}$ is a mixture distribution: a $p_C$
+
+\todo[inline]{Finish cleaning this up later...}
+This observation is useful for two reasons. First it allows us to bound the TuT and ToT effects without imposing the exclusion restriction.
+Second, by checking whether the TuT and ToT effects calculated under our exclusion restriction lie within the bounds, it allows us to potentially falsify \hl{XXXX}.
+
 Now, from the choice arm we know that around 90\% of people are $T=0$ types.
@@
 
+\todo[inline]{Presumably the numerical results and sentence that follows it need to be updated now that we've changed how we deal with censoring etc, yes? Which outcome are we looking at here} 
 The \cite{huber_mellace} bounds for the ToT \& TuT APR are respectively:
@@
 
-Note that since both TuT and ToT estimates from the LATE approach lies inside these bounds, we do not falsify the exclusion restriction.
+Because the Note that since both TuT and ToT estimates from the LATE approach lies inside these bounds, we do not falsify the exclusion restriction.
 

### 2023-02-28 Slides.tex
presentation

\documentclass[8pt]{beamer}

\usetheme{Singapore}
\usefonttheme{serif} 
\input{preambleBeamer.tex}
\setbeamercovered{transparent}

\title{The limits of self-commitment and private paternalism \\
Preliminary --comments welcome}
\author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira \and Francis J.\ DiTraglia }

\date{February 2023}

%\setbeamercolor{section in head/foot}{bg=darkcrimsonred}
\setbeamersize{text margin left=11pt, text margin right=11pt}
%\setbeamertemplate{section in toc}[square]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{frame}[c, noframenumbering]%{\phantom{title page}}
% The \phantom{title page} is a kludge to get the red bar on top
\titlepage
\end{frame}

\section{Motivation}

\begin{frame}{Motivation: Private paternalism}
\begin{itemize}
    \vfill \item Many institutions —firms, schools, financial contracts— restrict choice using built-in commitment mechanisms which help workers, students, borrowers overcome self-control problems
    \begin{itemize}
        \item Loans with fixed repayment schemes, homework due dates, etc.
    \end{itemize}
    \vfill\item At the same time these firms hide these forcing mechanisms and don’t market their commitment features, potentially because demand for them is low.
    \vfill \item  Laibson (2018) argues that clients that benefit from commitment may underestimate its value, and that in such cases private paternalism could be beneficial.
    \vfill \item  We study the benefits of imposing a fixed payment structure in loans, whether there is demand for it, and whether non-takers of such a commitment product would benefit from taking it.
\end{itemize}

\end{frame}

\begin{frame}{Context}
\begin{itemize}
    \vfill \item Pawn loans involve borrowers leaving valuable liquid assets as collateral in exchange for an immediate cash loan
    \vfill \item Because the loan is overcollateralized and collateral is liquid, the lender approve loans in a few minutes without income or credit history check $\rightarrow$ used for emergencies.
    \vfill \item This may explain why they are highly popular: $>$11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues.
    \begin{itemize}
        \item Our partner pawn lender alone approved 4 million loans in \hl{2017-2020}.
        \item Pawn lending has existed at least since the Roman empire.
    \end{itemize} 
    \vfill \item Controversial: interest rates and default rates are high, and used by people in distress.
    \vfill \item Regulators believe mostly unsophisticated borrowers use it.
\end{itemize}
\end{frame}

\begin{frame}{Methodological Contribution}
\begin{itemize}
    \vfill \item How do treatment effects relate to selection?  Key question in many literatures:
	\begin{itemize} 
		\item HTEs, MTE, LATEs, what is learned from IV regressions (Heckman \& Vytlacil, 2005).
		\item Health effects of universal versus elective interventions
		\item Optimal targeting (Alatas et al. 2012)
	\end{itemize}
     \vfill \item A context of particular interest to behavioral literature:  the demand for commitment in financial contracts (Laibson 1997, Bryan et al. 2010).
     \vfill \item Key quantity in debate about paternalism:  impacts on those who wouldn't elect to take the program versus impacts on those that do.
     \vfill \item Three-arm design:  Control, Choice (voluntary takeup=ITT), Forcing (universal=ATE).  We illustrate how to use standard exclusion restrictions for point identification:
    \begin{itemize}
        \item Treatment on the Treated (ToT) and 
        \item Treatment on the Untreated (TUT), also (ToT-TUT)
	\item Average Selection Bias, and Average Selection on Levels
    \end{itemize} 
   \vfill   \item Consider winners and losers from paternalism using bounding, Random Forest estimation of individual treatment effects. 
\end{itemize}
\end{frame}

\begin{frame}{Our partner: logistics, contract, stats}
    \begin{itemize}
        \item Partnered with one of the largest pawn lender in Mexico (hundreds of branches)
        \vfill\item Logistics: 
        \begin{itemize}
            \vfill\item Appraising:  gold jewelry as collateral the appraiser tests and weights the gold and assesses its value (5 mins).
           \vfill \item Loan: if the borrower agrees to leave the piece the appraiser gives 70\% of the gold value in cash, no checking of credit history or income.
           \vfill \item Contract (Standard in industry): 
           \begin{itemize}
               \vfill\item Interest rate = 7\% \textit{per month} compounded daily on the outstanding amount. No reminders.
               \vfill\item To recover pawn need to pay principal plus the accumulated interest. If this does not happen, pawnbroker keeps the piece and any payments made.
               \vfill\item  Client can renew for 3 months paying the accumulated interest and signing a new contract.
           \end{itemize}
        \end{itemize}

    \end{itemize}
\end{frame}

\begin{frame}{Context}
\begin{columns}
\begin{column}{.45\textwidth}

\begin{figure}[H]
    \begin{center}
    \caption{Pawnshop}
        \includegraphics[width=0.95\textwidth]{Figuras/empenio2.png}
    \end{center}
    \end{figure}
\begin{figure}[H]
    \begin{center}
    \caption{Appraiser/tellers inside a pawnshop}
        \includegraphics[width=0.95\textwidth]{Figuras/empenio9.png}
    \end{center}
    \end{figure}

    \end{column}

\begin{column}{.45\textwidth}

\begin{figure}[H]
    \begin{center}
    \caption{Pawnshop}
        \includegraphics[width=0.95\textwidth]{Figuras/empenio11.png}
    \end{center}
    \end{figure}
\begin{figure}[H]
    \begin{center}
    \caption{Lost pawns which are for sale}
        \includegraphics[width=0.95\textwidth]{Figuras/empenio3.png}
    \end{center}
    \end{figure}

    \end{column}    
    \end{columns}
\end{frame}

\begin{frame}{Lenders incentives}
    \begin{itemize}
        \item Because the loan is overcollateralized and collateral is liquid, the lender may gain if the borrower defaults on the loan, especially if the borrower pays towards recovery on the way to default.
        \item In fact, 60\% of clients lose their pawn in a time span of 230 days.
        \item Among those that lose their pawn, 48\% paid a positive amount towards its recovery and on average paid 42\% of loan.
        \item This happens in spite (or because?) of 74\% of borrowers reporting a 100\% subjective probability recovery ex-ante. 
        \item XXX of borrowers are classified as present biased using the simple standard question.
        \item In such an environment, one may ask if putting more structure in payments may help borrowers recover their pawn.
        \item We may particularly care about this if borrowers are vulnerable: 30\% of them could not pay either water, electricity \& gas or rent in the past 6 months; 87\% said they are pawning because of an emergency.
    \end{itemize}
\end{frame}

\begin{frame}{Structured payments contract}
   \begin{itemize}
       \vfill \item We designed a new contract that is identical to the status quo contract except that it enhances the regularity and salience of payments as a way to encourage repayment.
       \vfill\item The contract requires 3 equal payments in the 30th, 60th, ad 90th days of the loan, with the imposition of a 2\% fee of the amount owed if the client fails to pay.
       \vfill\item The propose of the small fee was to mainly to make the structured schedule salient, not to be a large disincentive to be late. 
       \begin{itemize}
           \item Transportation cost to go to the branch to pay is on the same order of magnitude as the fee in average.
       \end{itemize}
       \vfill\item  The empirical literature provides some guidance that such a contract may decrease default and elicit demand.
       \begin{itemize}
           \item Field \& Pande (2008) find null effects of payment frequency on loan default for group lending (but samples are small and there almost no default in the control). 
           \item XXX CITE PAPERS where frequency helps
        \item  Bauer et al. (2012) estimate a positive correlation between measured present bias and and selecting into microfinance, which they interpret demand for structured payments.
       \end{itemize}

   \end{itemize}

\end{frame}

\section{Measures}

\begin{frame}{Data}
\begin{itemize}
    \item Administrative data: XX months before and XX months after the experiment ended
    \begin{itemize}
        \item Unique identifier for each client and for the piece.
        \item Value of the item, money loaned (70\%), date of pawning
        \item For all payments: date and amounts
        \item Fees incurred
        \item Whether the client lost the pawn, renewed the contract
    \end{itemize}

    \vfill \item Survey data
    \begin{itemize}
        \item During experiment, we asked clients to complete a 5-minute survey before going to the teller window to appraise their piece and before treatment status was known to them.
        \item Demographics, proxies for income/wealth, education, present-biased preferences, experience pawning, if family or friends commonly asked for money, cost of going to branch, the subjective probability of recovering, the subjective value, etc.
    \end{itemize}
\end{itemize}    
\end{frame}

\begin{frame}{Main outcomes: financial cost and default}

\begin{itemize}
    \item We are interested in measuring the financial cost of borrowing, which very saliently includes the cost of defaulting on the loan and losing the pawn.
    \item We will measure loan default using an indicator $\mathds{1}(\text{Default}_i)$, and the cost in pesos using the following definition that capture borrower outlays:
\end{itemize}

   \begin{equation*}
    \text{Financial Cost}_i =  \underbrace{\sum_t P^i_{it}}_{\text{Pay to Interest}} + \underbrace{\sum_t P^f_{it}}_{\text{Pay to Fees}}  + \mathds{1}(\text{Default}_i) \times \left[\text{Pawn Val}_i + \underbrace{\sum_t P^c_{it}}_{\text{Pay to Capital}} \right]
   \end{equation*}

\begin{itemize}
    \vfill \item Towards the end of the presentation we will show results that apply a time discount factor.

\end{itemize}
\end{frame}

\begin{frame}{Distribution of financial cost (\$MXN)}
    \begin{figure}
     \centering
        \includegraphics[width=.8\textwidth]{Figuras/hist_fc.pdf}
    \end{figure}
\end{frame}

\begin{frame}{Distribution of APR}
\vspace{.2in}
\begin{equation*}
    (\text{APR})_i =\left( 1 + \frac{\frac{\text{Financial Cost}_i}{\text{Appraised Value}_i}}{\text{loan term}_i}\right)^{\text{loan term}_i}-1
\end{equation*}
\vspace{.2in}
\begin{figure}
     \centering
        \includegraphics[width=.75\textwidth]{Figuras/hist_apr.pdf}
    \end{figure}
\end{frame}

%\begin{frame}{Measuring Borrowers Financial Cost}
%\begin{columns}
%\begin{column}{.5\textwidth}
%    \begin{figure}[H]
%     \caption{Financial cost (MXN)}
%    \begin{center}
%    \includegraphics[width=\textwidth]{Figuras/hist_fc.pdf}
%    \end{center}
%    \end{figure}
%    \resizebox{1.0\linewidth}{!}{
%  \begin{minipage}{\linewidth}
%    \tiny{
    %\begin{align*}
    %\text{Financial Cost}_i =&  \underbrace{\sum_t P^i_{it}}_{\text{Pymnts to interests}} + \underbrace{\sum_t P^f_{it}}_{\text{Pymnts of fees}} \\
  %& + \underbrace{\mathds{1}(\text{Default}_i) \times (\text{Appraised Value}_i}_{\text{Cost of losing pawn}} + \underbrace{\sum_t P^c_{it}}_{\text{Pymnts to capital}})
%\end{align*}
%}
%  \end{minipage}
%}

%\end{column}
%\begin{column}{.5\textwidth}
%    \begin{figure}[H]
%     \caption{Effective APR}
%    \begin{center}
%    \includegraphics[width=\textwidth]{Figuras/hist_apr.pdf}
%    \end{center}
%    \end{figure}
%    \resizebox{.95\linewidth}{!}{
%  \begin{minipage}{\linewidth}    
%    \tiny{
    %\begin{align*}
    %(\text{APR})_i =&\left( 1 + \frac{\frac{\text{Financial Cost}_i}{\text{Appraised Value}_i}}{\text{loan term}_i}\right)^{\text{loan term}_i}-1 \\
   % & \\
   % & \\
   % & \\
   % &
%\end{align*}
%}
 % \end{minipage}
%}
%\end{column}
%\end{columns}
%\end{frame}

\section{Design}

\begin{frame}{Treatment arms}
   \begin{itemize}
    \vfill \item Randomization at the branch-day level. 
    \begin{itemize}
        \vfill \item Control arm 
       \vfill \item Forced Commitment arm
       \vfill \item Choice Commitment arm
    \end{itemize}
    \vfill \item The  existence  of  a  choice  arm  allows  us  not  only  to  measure  if  there  is  demand  for  such  a contract, but who demands it, not only in demographic terms, but in terms of potential treatment effects.
   \vfill \item  This design is innovative and critical for our purposes, as it enables us to explore whether or not forcing people into a structured payment contract could be more beneficial than allowing choice for a significant fraction of them
\end{itemize}
\end{frame}

\begin{frame}{Description}

\begin{figure}[H]
     \caption{Experiment description}
    \label{exp_description}
\begin{center}
        \includegraphics[width=0.85\textwidth]{Figuras/consort.pdf}
  \end{center}
\end{figure}

\end{frame}

\begin{frame}{Experimental integrity}
    \begin{table}[H]
\caption{Attrition table}
\label{attrition_table}
\begin{center}
\scriptsize{\input{./Tables/Attrition.tex}}
\end{center}
\end{table}
\end{frame}

\begin{frame}{Balance}

\vfill ISAAC: can you put the balance table here?

\end{frame}

\section{Results}
\begin{frame}{Main results}

 \begin{equation*} \label{basic_reg}
    y_{ij} = \alpha + \beta^F T_{i}^F + \beta^C T_{i}^C + \gamma X_{ij} + \epsilon_{ij}
\end{equation*}

\begin{table}[H]
\caption{Main treatment effects}
\label{main_impact_table}
\begin{center}
\resizebox{0.95\textwidth}{!}{
\scriptsize{\input{./Tables/decomposition_main_te_pres.tex}}
}
\end{center}
%\textit{Do file: } \texttt{decomposition\_main\_te.do}
\end{table}
\end{frame}

\begin{frame}{Mechanisms}

\only<1>{
\begin{table}[H]
\caption{Intermediate outcomes}
\label{mechanisms}
\begin{center}
\resizebox{0.7\textwidth}{!}{
\scriptsize{\input{./Tables/mechanism1_pres.tex}}
}
\end{center}
\end{table}
}
\only<2>{
\begin{table}[H]
\caption{Intermediate outcomes}
\label{mechanisms}
\begin{center}

\scriptsize{\input{./Tables/mechanism2_pres.tex}}

\end{center}
\end{table}
}

\only<3>{
\begin{table}[H]
\caption{Intermediate outcomes}
\label{mechanisms}
\begin{center}

\scriptsize{\input{./Tables/mechanism3_pres.tex}}

\end{center}
\end{table}
}
\end{frame}

\begin{frame}{Effects of treatment on future pawning behavior}

\begin{table}[H]
\caption{Repeat Pawns}
\label{repeat_loans}
\begin{center}
\scriptsize{\input{./Tables/repeat_loans.tex}}
\end{center}

\end{table}    
\end{frame}

\begin{frame}{Censoring}
    \begin{table}[H]
\caption{Bounding censoring}
\label{bounding_censoring}
\begin{center}
\resizebox{0.9\textwidth}{!}{
\scriptsize{\input{./Tables/censoring_imp_pres.tex}}
}
\end{center}
 \scriptsize 
%\textit{Do file: } \texttt{censoring_imp.do, censoring_imp_pr.do}
\end{table}
\end{frame}

\section{Heterogeneity}
\begin{frame}{Choice and Heterogeneous Treatment Effects}
\label{choice_hte}
    \begin{itemize}
    \vfill    \item   Commitment works.   In spite of this, given the  opportunity,  only 11\%  of  borrowers  chose  commitment.   If  the  effect  of  commitment  were homogeneous, this would be enough to conclude that the 89\% who did not choose it would have been financially better-off if they had.

    \vfill \item We test and reject the null hypothesis of homogeneous treatment effects (Chernozhuvok et. al. (2018).

    \vfill \item The borrowers who did not choose commitment could simply be those who don’t need it?

    \begin{itemize}
        \item More than 11\% of individual borrowers benefit from commitment (30\%) \hyperlink{fan_park_bounds}{\beamerbutton{Fan \& Park bounds}}
        \item Commitment increases average financial benefit even for the subset of borrowers who would not choose to commit voluntarily : $\operatorname{TUT}=\mathbb{E}[Y_1-Y_0\,|\, T=0]>0$
        \item Despite substantial treatment effect heterogeneity, most borrowers would experience higher financial benefits under a commitment contract : $F_{\operatorname{TUT}}^{-1}(xxx)>0$
    \end{itemize}
    \end{itemize}
\end{frame}

\begin{frame}{The `Randomized Choice' Design}
\label{rc_design}
\begin{itemize}
    \vfill \item  Large literature estimating ToT and TuT to better understand who selects  into  treatment  and  why : \begin{itemize}
        \item “LATE-and-reweight" : Aronow \& Carnegie (2013); Angrist \& Fernandez—Val (2013)  - no selection on gains.  
        \item Cornelissen et. al. (2018); Walters (2018)  - Modeling assumptions to extrapolate from the reduced-form quantities
        %TUT and ATE implied by LATE-and-reweight differ sharply from his model-based estimates
        \item Heckman \& Vytlacil MTE - no parametric  restrictions,  but  an  instrumental  variable $Z$ with sufficiently rich support.
        \item Brinch et. al. (2017) - discrete $Z$ but under some additivity restrictions on the MTE curve
        \item Mogstad, Santos \& Torgovitsky (2018) - No parametric form assumption on MTE curve but only partial identification.
    \end{itemize}

    \vfill \item Our “randomized choice design,” point identifies a number of interesting and economically-relevant causal quantities  without  the  need  for  additional  structural  restrictions.  \hyperlink{identification_randomized_choice}{\beamerbutton{Identification}} %Only assuming mean exclusion

\end{itemize}
\end{frame}

\begin{frame}{Causal Parameters}
\begin{table}[H]
\caption{Causal TE}
\label{tot_tut}
\begin{center}
\scriptsize{\input{./Tables/tot_tut_pres.tex}}
\end{center}
\end{table}

 The “right people” choose to commit:  those who are most likely to benefit from it and those whose outcomes are most adverse under the status quo.
\end{frame}

\section{Paternalism}

\begin{frame}{If commitment works, why don't people choose it?}
    \begin{itemize}
        \onslide<1>{\item Discounting}
        \onslide<2>{\item Hyperbolicity}
         \onslide<3>{\item Overconfidence}
    \end{itemize}

\only<1>{  
\begin{figure}[H]
        \caption{Financial cost for different discount rates}
    \label{fc_discount_rates}
    \begin{center}
        \centering
        \includegraphics[width=0.45\textwidth]{Figuras/discount_effect.pdf}
    \end{center}
\end{figure}   
    \begin{itemize}
    \item   Commitment contract imposes up-front costs for later benefits (collateral recovery).  
    \item Can impatience explain why not take up a contract that decreases overall cost?
    \item  Requires a rate of ~2,000\% to make NPV cost effect insignificant. 
    \end{itemize}
}

\only<2>{

    \begin{itemize}
    \item   Standard behavioral angle:  compliers are sophisticated time-consistent, non-compliers are a mix of naifs and the time consistent (who don't need commitment).  
    \item We have survey measure of time inconsistency taken at baseline.
    \item  Effect of Forcing should be entirely among the time-inconsistent.  Is this true? 
    \end{itemize}
}

\only<3>{

    \begin{itemize}
    \item   Asked question prior to assignment, borrowing about subjective probability of recovering.  
    \item Mean of prior prediction is XX\%, true recovery in control is YY\%.
    \item  Use prediction of default in control, subjective priors to measure overconfidence.  Does this explain large TUT? 
    \end{itemize}
}
\end{frame}

\begin{frame}{Paternalism and learning}

    \begin{itemize}
    \item   Are those with a greater experience of pawning less over-confident?  
    \begin{itemize}
        \item Observational analysis of overconfidence by number of prior pawns.
    \end{itemize}  
    \item   Do people learn from Forced exposure to the program that they benefit from it?  
    \begin{itemize}
        \item Subsequent to the experimental loan, those exposed to different treatments returned to branches where they were offered Choice.  What did they do?
    \end{itemize}

    \end{itemize}

\end{frame}

\begin{frame}{Winners and losers:  Bounding}
    \begin{itemize}
        \item Bounding exercise
    \end{itemize}

\end{frame}

\begin{frame}{Winners and losers:  Conditional TUTs}
     \begin{itemize}
        \item Conditional TUTs
    \end{itemize}

\end{frame}

\section{Conclusion}
\begin{frame}{Conclusion}
    \begin{itemize}
        \item Results suggest selection on gains, but still large effects of imposing commitment on non-compliers.
        \item  Default-inclusive APR falls from XX\% in the Control to YY\% in the Forced arm
        \item Mystery of low takeup combined with large TUT seems best explained by over-confidence among pawnshop customers.
        \item  This is a market where lenders profit from default.  If competitive, interest rates would have to rise to compensate for improved repayment.  Holding demand and repayment fixed, current 75\% would have to rise to XX\%.  Welfare transfer from repayers in the control state to those who are helped to repay by commitment.
        \item Laibson has spoken of `veiled paternalism' in contexts where principals desire reliability; here we have a case of `veiled non-paternalism' where features encouraging default are embedded.
        \item Suggests mandated commitment-based contract structures in payday/pawnshop loans as a form of pro-poor regulation?
    \end{itemize}  
\end{frame}

\appendix

\section{Appendix}

\begin{frame}{Difference number in pawns}
    \[Pawns \: per \: day_{jt} = \alpha_j + \gamma f(t) + \beta_b \mathbbm{1}(t \in MB)_{t} +\beta_a \mathbbm{1}(t \in MA)_{t}\]

    \begin{table}[H]
\caption{Number of pawns balance before and after the experiment}
\label{num_pawns_bal}
\begin{center}
\scriptsize{\input{./Tables/num_pawns_bal.tex}}
\end{center}
\end{table}
\end{frame}

\begin{frame}{Balance and Summary statistics}
    \begin{table}[H]
\caption{Summary statistics and Balance}
\label{SS}
\begin{center}
\resizebox{.65\textwidth}{!}{
\scriptsize{\input{./Tables/SS.tex}}
}
\end{center}

%\textit{Do file: } \texttt{ss\_att.do}
\end{table}
\end{frame}

\begin{frame}{Histogram of payments}

\begin{columns}
\begin{column}{.33\textwidth}
    \begin{figure}[H]
    \caption{Status-quo}
    \begin{center}
        \includegraphics[width=\textwidth]{Figuras/hist_payments_sq.pdf}
    \end{center}
\end{figure}
\end{column}

\begin{column}{.33\textwidth}
    \begin{figure}[H]
    \caption{Forced commitment}
    \begin{center}
        \includegraphics[width=\textwidth]{Figuras/hist_payments_fc.pdf}
    \end{center}
\end{figure}
\end{column}

\begin{column}{.33\textwidth}
    \begin{figure}[H]
    \caption{Choice commitment}
    \begin{center}
        \includegraphics[width=\textwidth]{Figuras/hist_payments_cc.pdf}
    \end{center}
\end{figure}
\end{column}
\end{columns}

\end{frame}

\begin{frame}{Several definitions of cost}

\begin{table}[H]
\caption{Effects on several definitions of cost}
\label{table_robustness_fc}
\begin{center}
\resizebox{0.95\textwidth}{!}{
\scriptsize{\input{./Tables/fc_robustness.tex}}
}
\end{center}
 \scriptsize

%\textit{Do file: } \texttt{fc\_robustness.do}
\end{table}

\end{frame}

\begin{frame}{Contract terms}

\begin{figure}[H]
     \caption{Contract Terms Summary}
    \label{PaperSlip}
    \begin{center}
        \includegraphics[width=0.65\textwidth]{Figuras/TicketLenderP.png}

    \end{center}

\end{figure}

\end{frame}

\begin{frame}{Explanatory material}
    \begin{figure}[H]
     \caption{Explanatory Material}
    \label{ExplanatoryMaterial}
    \begin{center}
        \includegraphics[width=0.9\textwidth]{Figuras/micas.pdf}
    \end{center}
\end{figure}
\end{frame}

\begin{frame}{Survival Graph}

\begin{figure}[H]
        \caption{Recovery}
    \label{survival_graph}
    \begin{center}
        \centering
        \includegraphics[width=0.75\textwidth]{Figuras/survival_graph_unpledge.pdf}
    \end{center}
\end{figure}   
\end{frame}

\begin{frame}{Interpolation on bounding censoring}

\begin{figure}[H]
        \caption{Significance area for Default}
    \label{interpolation_censoring_imp}
    \begin{center}
        \includegraphics[width=0.75\textwidth]{Figuras/frontera_sig_def_imp.pdf}
    \end{center}
\end{figure}
\end{frame}

\begin{frame}{Bounding Individual Treatment Effects}
\label{fan_park_bounds}

\begin{figure}[H]
    \caption{Fan \& Park bounds for benefit in APR\% }

    \begin{center}
        \includegraphics[width=0.75\textwidth]{Figuras/fan_park_bounds_apr.pdf}
    \end{center}

\end{figure}
 \hyperlink{choice_hte}{\beamerbutton{Back}}
\end{frame}

\begin{frame}{Identification of treatment parameters}
\label{identification_randomized_choice}
\begin{equation*}
    Y_i = \mathbbm{1}(Z_i =0) Y_{i0} + \mathbbm{1}(Z_i = 1)  Y_{i1}  + \mathbbm{1}(Z_i = 2) \left[(1 - C_i) Y_{i0} + C_i Y_{i1} \right].
\label{eq:potentialOutcomes}
\end{equation*}

    Viewing $Z_i$ as an instrumental variable, the randomized choice design can be interpreted as a \emph{pair} of RCTs, each subject to one-sided non-compliance. \\
    \begin{itemize}
        \item The first of these compares $Z_i=0$ to $Z_i = 2$.  This setting is identical to a ``randomized encouragement'' design in which treatment is only available to those who are encouraged: $Z_i = 2$. Under this interpretation, those with $C_i = 1$ are ``the compliers'' and it follows that 
\begin{equation*}
\frac{\mathbbm{E}(Y_i|Z_i=2) - \mathbbm{E}(Y_i|Z_i =0)}{\mathbbm{E}(D_i|Z_i=2)-\mathbbm{E}(D_i|Z_i=0)}  = \mathbbm{E}(Y_{i1} - Y_{i0}|C_i = 1)
\label{eq:ToT}
\end{equation*}

\item The second considers $Z_i = 1$ to be the ``encouragement'' and compare the outcomes for these individuals to those with $Z_i = 2$.
\begin{equation*}
\frac{\mathbbm{E}(Y_i|Z_i=1) - \mathbbm{E}(Y_i|Z_i =2)}{\mathbbm{E}(D_i|Z_i=1)-\mathbbm{E}(D_i|Z_i=2)}  = \mathbbm{E}(Y_{i1} - Y_{i0} | C_i = 0)
\label{eq:TuT}
\end{equation*}
    \end{itemize}

\hyperlink{rc_design}{\beamerbutton{Back}}

\end{frame}

\end{document}

\begin{figure}[H]
    \caption{Choice of contracts and treatment effects (ToT \& TuT)}
    \label{choose_wrong}
    \begin{center}
        \begin{subfigure}{0.45\textwidth}
        \caption{Mistakes in choice arm}
        \centering
        \includegraphics[width=\textwidth]{Figuras/line_cw_apr_tot_tut.pdf}

    \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
        \caption{Financial value of mistake}
        \centering
        \includegraphics[width=\textwidth]{Figuras/money_cw_apr_tot_tut.pdf}

    \bigskip

    \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
        \caption{\% better when forced to forced commitment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/line_better_forceall_apr_te_cf.pdf}

    \end{subfigure}

    \end{center}
\end{figure}

### 2023-02-28 Tables/decomposition_main_te_pres1.tex
presentation

% Table generated by Excel2LaTeX from sheet 'decomposition_main_te_pres1'
\begin{tabular}{lcccccc}
\toprule
      &       & \multicolumn{5}{c}{Components of FC} \\
\cmidrule{3-7}      & FC    & \textcolor[rgb]{ .749,  .749,  .749}{Int. pymnt} & \textcolor[rgb]{ .749,  .749,  .749}{Fee pymnt} & \textcolor[rgb]{ .749,  .749,  .749}{Princ. pymnt} & \textcolor[rgb]{ .749,  .749,  .749}{Lost pawn val} & Default \\
\midrule
      & (1)   & \textcolor[rgb]{ .749,  .749,  .749}{(2)} & \textcolor[rgb]{ .749,  .749,  .749}{(3)} & \textcolor[rgb]{ .749,  .749,  .749}{(4)} & \textcolor[rgb]{ .749,  .749,  .749}{(5)} & (6) \\
\midrule
\midrule
Forced cmit & \boxit{0.5in} -379.7*** & \textcolor[rgb]{ .749,  .749,  .749}{-157.3***} & \textcolor[rgb]{ .749,  .749,  .749}{32.1***} & \textcolor[rgb]{ .749,  .749,  .749}{-0.57} & \textcolor[rgb]{ .749,  .749,  .749}{-254.5**} & \boxit{0.5in} -0.065*** \\
      & (111.4) & \textcolor[rgb]{ .749,  .749,  .749}{(34.9)} & \textcolor[rgb]{ .749,  .749,  .749}{(1.43)} & \textcolor[rgb]{ .749,  .749,  .749}{(3.03)} & \textcolor[rgb]{ .749,  .749,  .749}{(104.8)} & (0.023) \\
Choice cmit & -84.9 & \textcolor[rgb]{ .749,  .749,  .749}{-24.9} & \textcolor[rgb]{ .749,  .749,  .749}{1.34**} & \textcolor[rgb]{ .749,  .749,  .749}{-3.98} & \textcolor[rgb]{ .749,  .749,  .749}{-61.4} & -0.025 \\
      & (114.6) & \textcolor[rgb]{ .749,  .749,  .749}{(38.4)} & \textcolor[rgb]{ .749,  .749,  .749}{(0.54)} & \textcolor[rgb]{ .749,  .749,  .749}{(2.47)} & \textcolor[rgb]{ .749,  .749,  .749}{(109.2)} & (0.021) \\
      &       & \textcolor[rgb]{ .749,  .749,  .749}{} & \textcolor[rgb]{ .749,  .749,  .749}{} & \textcolor[rgb]{ .749,  .749,  .749}{} & \textcolor[rgb]{ .749,  .749,  .749}{} &  \\
\midrule
Observations & 6304  & \textcolor[rgb]{ .749,  .749,  .749}{6304} & \textcolor[rgb]{ .749,  .749,  .749}{6304} & \textcolor[rgb]{ .749,  .749,  .749}{6304} & \textcolor[rgb]{ .749,  .749,  .749}{6304} & 6304 \\
R-squared & 0.007 & \textcolor[rgb]{ .749,  .749,  .749}{0.022} & \textcolor[rgb]{ .749,  .749,  .749}{0.151} & \textcolor[rgb]{ .749,  .749,  .749}{0.003} & \textcolor[rgb]{ .749,  .749,  .749}{0.007} & 0.013 \\
Control Mean & 1851.0 & \textcolor[rgb]{ .749,  .749,  .749}{545.9} & \textcolor[rgb]{ .749,  .749,  .749}{0} & \textcolor[rgb]{ .749,  .749,  .749}{5.82} & \textcolor[rgb]{ .749,  .749,  .749}{1305.1} & 0.44 \\
\bottomrule
\bottomrule
\end{tabular}%

### 2023-02-28 donde.tex
presentation

@@
 \subsection{Experimental Integrity}
+\label{sec:integrity}
 
@@
 The first, and more serious, is the possibility that clients might change their pawning decisions in response to the treatment they encounter in a given branch on the day they enter.
-If this occurred it would introduce a self-selection dimension which would still reflect the overall impact of a treatment for the lender's portfolio but would no longer deliver \textit{ceteris paribus} effects of treatments on the same individual borrower.
-Narrative reports and the way the treatment was implemented make us believe that this is unlikely.\footnote{Potential clients did not know that different days could have different contracts.
+If this occurred it would introduce a self-selection dimension which would still reflect the overall impact of a treatment for the lender's portfolio but would no longer deliver \textit{ceteris paribus} effects of treatments on individual borrowers.
+Narrative reports and the way the treatment was implemented make us believe that selection into treatment is unlikely.\footnote{Potential clients did not know that different days could have different contracts.
 If they asked, appraisers said that whatever was offered on that day was the only available contract for an undetermined length of time.
@@
 For many of them the pawned jewelry has sentimental value as well.
-This is reflected in the subjective valuation they reported in the survey\footnote{The minimum peso amount at which they would sell the piece.} which is \hl{XXX\%} higher on average.
+This is reflected in the subjective valuation they reported in the survey which is \hl{XXX\%} higher on average.
 Our third extra cost considers this higher value.
 
-Table \ref{table_robustness_fc} shows results. We present results
-
+Table \ref{table_robustness_fc} shows results.
+Panel A reports financial cost in pesos, while Panel B shows APR.
 Columns (1) and (6) replicate our previous results for comparability.
 Columns (2) and (7) of Table \ref{table_robustness_fc} use the subjective value of the pawn reported by the borrower rather than its appraised value.
-Columns (3) and (8) adjust for self-reported transport costs from the individual survey plus an entire day's wage, multiplied by the number of individual visits\footnote{For clients who did not complete the individual survey, we adjust using the mean self-reported transport cost among respondents.}.
-Although adding a whole day's wage almost certainly exaggerates the travel costs associated with commitment contracts, we still find that forced commitment reduces both financial costs and APR. 
+Columns (3) and (8) adjust for self-reported transport costs per visit plus an entire day's wage, both multiplied by the number of individual visits\footnote{For clients who did not complete the individual survey, we adjust using the mean self-reported transport cost among respondents of the respective branch.}.
+Columns (4) and (9) adjust for our measure of liquidity cost.
+Finally columns (5) and (10) include all three changes together.
+The main takeaway from the table is that results are quite robust to including a much expanded measure of costs.
+
+%Although adding a whole day's wage almost certainly exaggerates the travel costs associated with commitment contracts, we still find that forced commitment reduces both financial costs and APR.
 Columns (4) and (9) adjust for both travel costs and use the subjective rather than appraised value of the pawn.
@@
 
-\todo[inline]{``fully adjusted'' in the table removes interest payments from the cost measure.
-Not totally clear what this exercise tells us.
-Overall, the point of the table is to remove alternative explanations one-by-one.
-(I added a paragraph now to make this clearer, ES)}
-
 \todo[inline]{I think the re-pawn table should only have 4 columns.
@@
 Column (1) shows that participants assigned to the the forced arm are 6.7\% more likely to be repeat clients.
-Those in the choice arm are 4\% more likely to pawn again and is not statistically distinct from zero.
+%Those in the choice arm are 4\% more likely to pawn again and is not statistically distinct from zero.
 While this appears to be \emph{prima facie} evidence of greater satisfaction, the interpretation is complicated by the fact that monthly payments may themselves trigger more borrowing to pay them.
 This is unlikely to be the case given that the effect on re-pawning comes after 90 days (during the period of contract demanded payments) and not before  (see columns 2 and 3).
-Column 4 focuses on the (endogenous) subsample of those recovering their pawn in both arms of the experiment.
-This means that both have the pawn to re-pawn and also that the liquidity demands from the monthly contract are not longer binding as the contract has been terminated.
-Twice as many choose to pawn again in the commitment contract (column 4).
+Column 3 only considers new loans which use different collateral from that of the initial one.
+We do this to foreclose the explanation that those in the Forced arm repeat more because they are more likely to have collateral, as they recover the collateral of the first loan more often.
+Column 5 focuses on the (endogenous) subsample of those recovering their pawn in both arms of the experiment.
+This means that both have the pawn to re-pawn and also that the liquidity demands from the monthly contract are not longer binding as the contract has been closed.
+We find that the difference between the Forcing contract and the status quo is even larger in this subsample, with the former having 11pp higher likelihood of being a repeat client during our sample period.
 
@@
 The window of time during which we were able to observe borrower behavior was limited in each branch, meaning that there were loans that we do not see completed (particularly those pawns that were rolled over for one or two further 90-day spells).
-Overall, XX\% of all experimental loans are censored, meaning that they neither default nor repay within the observation window.
+Overall, \hl{XX\%} of all experimental loans are censored, meaning that they neither default nor repay within the observation window.
 In the prior analysis we handle this issue by using outcomes such as `did not default' which are defined even when we do not observe the completion of the loan, and only considering costs that we observe directly.
@@
 The results from Section \ref{experiment} show that commitment \emph{works}: clients who were assigned to the forced commitment arm experienced substantially lower financial costs on average.
-In spite of this, given the opportunity, only 11\% of borrowers chose commitment. 
+In spite of this, given the opportunity, only \hl{11\%} of borrowers chose commitment. 
 If the effect of commitment were homogeneous, this would be enough to conclude that the \hl{89\%} who did not choose it would have been financially better-off if they had.
 In a world of heterogeneous treatment effects, however, low demand for commitment could still be consistent with individual rationality.
-Following the methodology of \cite{chernozhukov2018generic} we test and reject the null hypothesis of homogeneous treatment effects \hl{P-value = XXX}.\footnote{See Appendix \hl{???} for details.} 
-Indeed, the effect of commitment varies considerably across individuals. 
-So do the 89\% who do not choose commitment know something about their personal situations that we as researchers do not, or are most people in the choice arm making a costly mistake? 
-We now present a range of econometric exercises that shed light on this question, leveraging unique features of our experimental design. 
-%Taken together, they cast considerable doubt on the notion of ``selection on gains,'' as embodied in the traditional Roy model. 
-While we find evidence of substantial treatment effect heterogeneity, most borrowers would experience lower financial costs under a commitment contract. 
-Among other results, we show that the average effect of commitment for the \emph{untreated}, those who would not voluntarily choose commitment, is large and negative. 
-%In an important sense the ``wrong'' people are choosing commitment.
+The borrowers who did not choose commitment could simply be those who don't need it. 
+Indeed, we find strong evidence that the effect of forced commitment varies substantially across individuals in our experiment: Appendix \ref{append:chernozhukov} tests and rejects the null hypothesis of homogeneous treatment effects, following the methodology of \cite{chernozhukov2018generic}.
+So the question remains: do the \hl{89\%} who do not choose commitment know something about their personal situations that we as researchers do not, or are most people in the choice arm making a costly mistake?
+In this section we now present a range of econometric exercises that shed light on this question, leveraging unique features of our experimental design. 
+Despite substantial treatment effect heterogeneity, most borrowers would experience lower financial costs under a commitment contract. 
+Indeed, commitment lowers average financial costs even for the subset of borrowers who would \emph{not} choose to commit voluntarily.
+To simplify the exposition in this and all sections that follow, we re-define all outcome variables so that \emph{beneficial} treatment effects are \emph{positive}.
+Using this convention, a positive treatment effect of commitment on financial cost, for example, reflects the average cost \emph{savings} caused by commitment.
 
@@
 Now let $D_i$ be the treatment that participant $i$ actually \emph{received}, where $D_i = 0$ denotes no-commitment and $D_i = 1$ denotes commitment. 
-By design, our experiment features perfect compliance in the $Z_i = 0$ and $Z_i = 1$ arms. 
+We assume perfect compliance in the $Z_i = 0$ and $Z_i = 1$ arms.\footnote{For more discussion on this point, see Section \ref{sec:integrity} above.}
 It is only in the $Z_i = 2$ arm that participants are free to choose between alternative contracts. 
-Let $C_i \in \{0, 1 \}$ denote a participant's ``choice type.'' If $C_i = 1$ then participant $i$ \emph{would choose commitment}, given the choice; if $C_i = 0$ she would not. 
+Let $C_i \in \{0, 1 \}$ denote a participant's ``choice type.'' If $C_i = 1$ then participant $i$ \emph{would choose commitment}, given the option; if $C_i = 0$ she would not. 
+As shorthand, we call borrowers with $C_i = 1$ ``choosers'' and those with $C_i = 0$ ``non-choosers.''
 Whereas a participant's choice type $C_i$ is only observed if she is allocated to the choice arm ($Z_i = 2$), her treatment $D_i$ and experimental arm $Z_i$ are always observed. 
@@
 We maintain the stable unit treatment value assumption (SUTVA) throughout. 
-This means that participant $i$'s outcomes depend only on her \emph{own} values of $Z_i$ and $D_i$, not those of any other person in the experiment: there are no \emph{spillovers}. 
+This means that borrower $i$'s outcomes depend only on her \emph{own} values of $Z_i$ and $D_i$, not those of any other person in the experiment: there are no \emph{spillovers}. 
 Under this assumption, a fully general model for the potential outcomes in our experiment would take the form $Y_i(d, z)$ for $d\in \{0,1\}$ and $z \in \{0, 1, 2\}$, allowing participant $i$'s potential outcome to depend \emph{both} on the treatment she actually receives, $D_i$, and the experimental arm to which she is assigned, $Z_i$.
 This model is too general, however, to identify meaningful causal effects. 
-Accordingly, we impose the following standard exclusion restriction:
+For this reason, we impose two exclusion restrictions.
+Before stating them, we first define some additional notation.
+In particular, because any anyone with $Z_i = 0$ has $D_i = 0$ under our experimental design, we abbreviate the potential outcome $Y_i(d=0,z=0)$ as $Y_{i0}$. 
+Similarly, as anyone with $Z_i = 1$ has $D_i = 1$, we abbreviate $Y_i(d=1,z=1)$ as $Y_{i1}$. 
+Our first exclusion restriction is relevant only for non-choosers, individuals with $C_i = 0$, because they are the only borrowers for whom $D_i = 0$ when $Z_i = 2$.
+We assume that
 \begin{equation}
-Y_i(d=0, z=0) = Y_i(d=0, z=2) \equiv Y_{i0}, \quad
-Y_i(d=1, z=1) = Y_i(d=1, z=2) \equiv Y_{i1}.
-\label{eq:exclusion}
+Y_i(d=0,z=2) = Y_i(d=0,z=0) \equiv Y_{i0}.
+\label{eq:exclusion0}
 \end{equation}
-\eqref{eq:exclusion} says that each participant's potential outcome is the same regardless of whether she \emph{chooses} a particular treatment $D=d$ or is \emph{assigned} the same treatment.
-Viewing $Z_i$ as an instrumental variable (IV) for the treatment $D_i$, this nothing more than the usual IV exclusion restriction.\footnote{\cite{chamberlain2011bayesian} uses an identical assumption to develop a theory of optimal treatment choice for an individual who has access to data from an RCT.} \eqref{eq:exclusion} is plausible in our empirical setting and has testable implications that we fail to reject: see Appendix \hl{???} for details.
+Equation \ref{eq:exclusion0} implies that every non-chooser experiences the same potential outcome when assigned to the control arm as when assigned to the choice arm. 
+Our second exclusion is relevant only for choosers, individuals $C_i =1$, because they are the only borrowers for whom $D_i = 1$ when $Z_i = 2$.
+We assume that 
+\begin{equation}
+Y_i(d=1,z=2) = Y_i(d=1,z=1)\equiv Y_{i1}.
+\label{eq:exclusion1}
+\end{equation}
+Equation \ref{eq:exclusion1} implies that every chooser experiences the same potential outcome when assigned to the treatment arm as when assigned to the choice arm. 
+Mathematically \eqref{eq:exclusion0} and \eqref{eq:exclusion0} have the same structure as the standard LATE exclusion restriction that $Y_i(d,z)$ depends only on $d$, not on $z$. 
+Substantively, however, they are slightly different as there is no analogue of the ``chosen'' versus ``forced'' treatment distinction in the usual LATE setting.\footnote{See \cite{chamberlain2011bayesian}, who uses an assumption very similar to our exclusion restrictions to develop a theory of optimal treatment choice for an individual who has access to data from an RCT.}
+Both \eqref{eq:exclusion0} and \eqref{eq:exclusion1} are plausible in our empirical setting. 
+Moreover, each has testable implications that we fail to reject: see Appendix \ref{append:exclusion} for details.
 Under \eqref{eq:exclusion}, each participant's observed outcome $Y_i$ is related to her potential outcomes $(Y_{i0}, Y_{i1})$ according to
-%\todo[inline]{Issac: add a section \ref{bound_tot_tut_appendix} to the appendix and drop in the results for the Huber \& Mellace stuff; Frank: follow-up and draft that section of the appendix.}
 \begin{equation}
@@
 \end{equation}
-
-\eqref{eq:potentialOutcomes} is the key to understanding the results that follows. 
+%\todo[inline]{Fix labels!}
+%Accordingly, we impose the following standard exclusion restriction:
+%\begin{equation}
+%Y_i(d=0, z=0) = Y_i(d=0, z=2) \equiv Y_{i0}, \quad
+%Y_i(d=1, z=1) = Y_i(d=1, z=2) \equiv Y_{i1}.
+%\label{eq:exclusion}
+%\end{equation}
+%Equation \ref{eq:exclusion} says that each participant's potential outcome is the same regardless of whether she \emph{chooses} a particular treatment $D=d$ or is \emph{assigned} the same treatment.
+Viewing $Z_i$ as an instrumental variable (IV) for the treatment $D_i$, \eqref{eq:exclusion} amounts to the usual IV exclusion restriction.
+%
+%\todo[inline]{END Fix labels!}
+Equation \ref{eq:potentialOutcomes} is the key to understanding the results that follows. 
 By randomly assigning $Z_i=0$ and $Z_i = 1$, our experiment identifies the marginal distributions of $Y_{i0}$ and $Y_{i1}$ in the population as a whole. 
-By randomly assigning $Z_i=2$, it likewise identifies the share of people with $C_i = 1$ (the treated), the distribution of $Y_{i1}$ for these individuals, and the distribution of $Y_{i0}$ for those with $C_i = 0$ (the untreated).
+By randomly assigning $Z_i=2$, it likewise identifies the share of choosers ($C_i = 1$), the distribution of $Y_{i1}$ for choosers, and the distribution of $Y_{i0}$ for non-choosers ($C_i = 0$).
 Because $Z_i$ is assigned independently of pre-treatment covariates $X_i$, our design also identifies the corresponding \emph{conditional} distributions of $Y_{i0}$ and $Y_{i1}$ given $X_i$. 
@@
 \subsection{Bounding the Distribution of Treatment Effects}
-
+\todo[inline]{Unless I'm missing something obvious, this section does not rely on the exclusion restriction. We should think of a way to highlight this.}
 As seen above in Section \ref{experiment}, the average treatment effect of forced commitment is economically and statistically significant. 
-Using the notation of Section \ref{sec:potentialOutcomes}, our estimate of $\mathbbm{E}[Y_{i1} - Y_{i0}]$ is \emph{negative}: commitment lowers financial costs overall. 
+Using the notation of Section \ref{sec:potentialOutcomes}, our estimate of $\mathbbm{E}[Y_{i1} - Y_{i0}]$ is positive: commitment lowers financial costs overall.\footnote{Recall from above that in this section we define all outcome variables so that beneficial treatment effects are \emph{positive}.}
 But this is only an average effect.
@@
 Perhaps commitment is extremely helpful for a small minority of borrowers, and slightly harmful for everyone else.
-Can this explanation rationalize the very low take-up rate of commitment in the choice arm (11\%) along with the ATE of commitment estimated from the forced arm? 
+Can this explanation rationalize the very low take-up rate of commitment in the choice arm (\hl{11\%}) along with the ATE of commitment estimated from the forced arm? 
 We could easily answer this question if the distribution $F_\Delta$ of individual treatment effects $\Delta_i$ were known: simply calculate $\mathbbm{P}(\Delta_i < 0)$.
@@
 It can, however, be bounded. 
-Using these bounds, we now show that more than 11\% of individual borrowers benefit from commitment.
+Using these bounds, we now show that more than \hl{11\%} of individual borrowers benefit from commitment.
 
@@
 Here we use them to bound the fraction of borrowers who benefit from commitment. 
-Given the way that we have defined our outcome variables, this is the share of borrowers whose treatment effect is \hl{\emph{negative}}, i.e.\ $F_\Delta(0)$. 
+Given the way that we have defined our outcome variables, this is the share of borrowers whose treatment effect is \emph{positive}, i.e.\ $1 - F_\Delta(0)$. 
 To construct the sharp bounds for this quantity, we simply substitute $\delta = 0$ into the preceding equations and estimate $F_0$ and $F_1$ using their empirical analogues constructed from the forced commitment and forced no-commitment arms of the experiment.
 
-\todo[inline]{Issac: add in the confidence interval at $\delta = 0$ along with the figure \ref{fan_park_bounds}; Frank follow-up to add 1-2 sentences discussing the results.
+Figure \ref{fig:FanPark} plots the sharp bounds for $F_{\delta}$ based on the APR outcome defined above in Section \ref{costs}.
+Our point estimates of $\underline{F}(0)$ and $\overline{F}_0$ are \hl{XXXX} and \hl{XXXX} respectively, with associated 95\% confidence intervals of \hl{XXXX} and \hl{XXXX}.\footnote{Confidence intervals are constructed using \hl{XXXX} bootstrap.
+See \cite{fan2010sharp} for details.}
+%\todo[inline]{Issac: add in the confidence interval at $\delta = 0$ along with the figure \ref{fan_park_bounds}.
+These need to be the results that do not use covariates and we need to be careful about the sign convention for our effects.
+Frank follow-up to add 1-2 sentences discussing the results.
 Presumably we find that $F_\Delta(0) > 0.11$ this means that at least some people who choose not to commit \emph{must} be making a mistake, although we don't know who they are and this doesn't tell us how large the mistake is.}
-
 An alternative way of presenting the \cite{fan2010sharp} bounds is in terms of quantiles of the distribution of $\Delta$.
@@
 Under a stylized Roy model in which borrowers with the largest (negative) treatment effects choose commitment, $Q(0.11)$ equals the treatment effect for the borrower at the margin of indifference between choosing commitment.
-
-\todo[inline]{Issac: add the interval for $Q(0.11)$.
+Our point estimates for the lower and upper bounds $\underline{Q}(0.11)$ and $\overline{Q}(0.11)$ are \hl{XXXX} and \hl{XXXX} with corresponding 95\% confidence intervals \hl{XXXX} and \hl{XXXX}.\footnote{Again, confidence intervals are constructed using \hl{XXXX} bootstrap as describe in \cite{fan2010sharp}.}
+%\todo[inline]{Issac: add the interval for $Q(0.11)$.
+Again, this needs to be without covariates and we need to be careful about the sign convention for our effects.
 Maybe we don't need a second figure with the confidence bands for the whole quantile function.
@@
 Presumably the aforementioned quantile is indeed negative and fairly large.}
-
-Taken together, these bounds show that at least some borrowers who would benefit from commitment \emph{do not choose it} when offered.
+Both ways of presenting the bounds yield the same conclusion: at least some borrowers who would benefit from commitment \emph{do not choose it} when offered.
 
@@
 
-\subsection{The ``Randomized Choice'' Design}
+\subsection{The ``Controlled Choice'' Design}
 \label{sec:randchoice}
 
-Above we used outcome data from the forced arms ($Z_i\neq 2$) along with the commitment take-up rate in the choice arm ($Z_i = 2$) to argue that at least some of the 89\% of participants who did \emph{not} choose commitment would have been better off if they had.
+Above we used outcome data from the forced arms ($Z_i\neq 2$) along with the commitment take-up rate in the choice arm ($Z_i = 2$) to argue that at least some of the \hl{89\%} of participants who did \emph{not} choose commitment would have been better off if they had.
 By additionally examining \emph{outcome data} in the choice arm, it is possible to say more. 
-We now show how our experimental design, henceforth the ``randomized choice design,'' point identifies a number of interesting and economically-relevant causal quantities without the need for additional structural restrictions.
+We now show how our experimental design, henceforth the ``controlled choice design,'' point identifies a number of interesting and economically-relevant causal quantities without the need for additional structural restrictions.
 First we identify the treatment on the treated (ToT) and treatment on the untreated (TuT) effects, defined as follows:
@@
 %The TuT and ToT effects are particularly interesting for understanding the importance of paternalism. 
-If the TuT is positive, this means that someone who did not choose commitment would have been experienced a better outcome \emph{on average} if she had. 
+If the TuT is positive, this means that those who did not choose commitment would have experienced better outcomes, \emph{on average}, if they had. 
 In a canonical Roy model, the ToT should exceed both the TuT and average treatment effect (ATE).
@@
 \]
-The randomized choice design also identifies both the average selection bias (ASB) and the average selection on levels (ASL). 
+The controlled choice design also identifies both the average selection bias (ASB) and the average selection on levels (ASL). 
 \[
@@
 \]
-A companion STATA package accompanying this paper provides estimators of the ToT, TUT, ASG, ASB, and ASL, along with cluster-robust standard errors.\footnote{\hl{Provide a url?}}
+A companion STATA package accompanying this paper provides estimators of the ToT, TUT, ASG, ASB, and ASL, along with cluster-robust standard errors for each.\footnote{See Appendix \ref{append:randchoice} for more details.}
 
@@
 But there is no free lunch: this ``LATE-and-reweight'' approach relies upon assumptions of its own, most crucially the assumption that there is \emph{no selection-on-gains} conditional on $X$, i.e.\ that the conditional LATE equals the conditional ATE.
-In contrast to both approaches, the randomized choice design uses exogenous experimental variation to point identify the ATE, ToT, and TuT without ruling out unobserved selection-on-gains or relying on additional structural modeling assumptions.
+In contrast to both approaches, the controlled choice design uses exogenous experimental variation to point identify the ATE, ToT, and TuT without ruling out unobserved selection-on-gains or relying on additional structural modeling assumptions.
 
 The key insight can be read directly from \eqref{eq:potentialTreatments} and \eqref{eq:potentialOutcomes}. 
-Viewing $Z_i$ as an instrumental variable, the randomized choice design can be interpreted as a \emph{pair} of RCTs, each subject to one-sided non-compliance.
+Viewing $Z_i$ as an instrumental variable, the controlled choice design can be interpreted as a \emph{pair} of RCTs, each subject to one-sided non-compliance.
 The first of these compares $Z_i=0$ to $Z_i = 2$.
@@
 since $\mathbbm{E}(D_i|Z_i = 1)= 1$ by \eqref{eq:potentialTreatments}.
-Equations \eqref{eq:ToT} and \eqref{eq:TuT} are useful for understanding why the randomized choice design identifies the ToT and TuT, but they are less convenient for estimation and inference.
-In Appendix \hl{???}, we show that
+Equations \eqref{eq:ToT} and \eqref{eq:TuT} are useful for understanding why the controlled choice design identifies the ToT and TuT, but they are less convenient for estimation and inference.
+In Appendix \ref{append:randchoice}, we show that
 \begin{align}
@@
 Carrying out inference for this quantity is a bit more involved, because $\text{ASG}$ a difference of coefficients from two separate IV regressions. 
-In Appendix \hl{???} we show how to use the residuals from \eqref{eq:TuTreg} and \eqref{eq:ToTreg} to carry out cluster-robust inference for $\text{ASG}$. 
-Our companion STATA package automates this procedure.
-As mentioned above, the randomized choice design also identifies the average selection bias (ASB) and average selection on levels (ASL).
+In Appendix \ref{append:randchoice} we show how to use the residuals from \eqref{eq:TuTreg} and \eqref{eq:ToTreg} to carry out cluster-robust inference for $\text{ASG}$, a procedure that is automated in our companion STATA package.
+As mentioned above, the controlled choice design also identifies the average selection bias (ASB) and average selection on levels (ASL).
 In particular,
@@
 \end{align}
-as we show in Appendix \hl{???}.
+as we show in Appendix \ref{append:randchoice}.
 For purposes of inference, both the ASB and ASL can be re-written as the difference of coefficients from a pair of just-identified linear IV regressions, namely
@@
 These calculations are also automated in our companion STATA package.
-For details, see Appendix \hl{???}.
-
-\todo[inline]{Perhaps mention some other settings in which a design like this might be helpful? Need to think about this.}
+For details, see Appendix \ref{append:randchoice}.
+
+\todo[inline]{Possibly add some discussion here of Craig's idea: using the controlled choice design to study ``targeting''}
 
@@
 
-\todo[inline]{This next paragraph needs to be removed and/or re-written. Perhaps we want to break to a new subsection before discussing these results?}
-
-Table \ref{tot_tut} shows the results of this analysis.
-Given that the ITT results for the Choice arm imply an insignificant worsening of outcomes relative to the control, our estimates of the Treatment on the Treated in the first row of the bottom panel show negative results that are larger in absolute magnitude (multiplied by ~9, the inverse of the compliance rate) and similarly insignificant.
+Table \ref{tot_tut} calculates the causal quantities described above--ToT, TuT, ASG, ASB, and ASL--for our experimental data, along with robust standard errors for each. 
+For purposes of comparison, the table also presents the ATE results from Section \hl{XXXX} above (row 1), along with the corresponding average potential outcomes $\mathbbm{E}[Y_0]$ and $\mathbbm{E}[Y_1]$ (rows 4--5).
+The columns of the table correspond to different outcome variables, defined as in Section \hl{XXXX} above.
+For all four outcome definitions, the TuT effect is positive, statistically and economically significant, and comparable in magnitude to the ATE.
+In other words: commitment is \emph{beneficial}, on average, to the people who \emph{would not choose it}, and these benefits are large.
+The estimated ToT effects are positive and larger still.
+Although we cannot quite reject the null hypothesis that the TuT and ToT effects are equal--our power is limited because of the low take-up rate of commitment in the choice arm--the pattern of coefficients is consistent with some degree of selection-on-gains.
+Commitment is more beneficial to people who are willing to choose it than it is to people who are not.
+For the APR benefit and (1 - Default) outcomes, we have sufficient precision to conclude that the average selection bias (ASB) is large and \emph{negative}.
+This means that borrowers who choose commitment would have faced a \emph{higher} APR and probability of default under the status quo contract than borrowers who do not choose commitment. 
+Overall, Table \ref{tot_tut} suggests that commitment works and the ``right people'' choose to commit: those who are most likely to benefit from it and those whose outcomes are most adverse under the status quo.
+At the same time, \emph{not enough} people choose to commit: the commitment contract is beneficial on average even to those who would \emph{not} choose it voluntarily.
+Below we explore possible explanations for this result.
+
+%Given that the ITT results for the Choice arm imply an insignificant worsening of outcomes relative to the control, our estimates of the Treatment on the Treated in the first row of the bottom panel show negative results that are larger in absolute magnitude (multiplied by ~9, the inverse of the compliance rate) and similarly insignificant.
 The Treatment on the Untreated (TuT), conversely, is strongly positive across the board, and indicates a significant improvement for all outcomes (here ITTs are effectively multiplied by 1.12, the inverse of the non-compliance rate).
@@
 
+\paragraph{Rough outline based on Craig's email and our conversations: 2023-02-16}
+\begin{enumerate}
+    \item What is the economic explanation for our results from above and what implications do they have for policy?
+Can discounting explain the low take-up of commitment despite its clear benefits, even to those who don't choose it?
+No: see Figure OA-5.
+Remaining exercises will use baseline survey data.
+Explain why we think this is ok: treatment effects don't change much when restricting the sample.
+(Refer to tables)
+    \item Does present bias (hyperbolic discounting) explain the results?
+Cite some literature here about why it might matter.
+Questions 10 and 29 from our survey allow us to construct a dummy variable $H$ for present bias: prefer 100 pesos tomorrow rather than 150 in a month, but prefer 150 pesos in four months rather than 100 pesos in three months.
+This isn't a perfect measure but it's standard in the literature.
+(Citations).
+If present bias explains the results, then ``sophisticated'' people with $H = 1$ will choose commitment, but there doesn't seem to be any correlation between $H$ and $C$ in the choice arm.
+Moreover, if present bias explains the results, the ATE for $H=0$ should be zero (or negative) but it's large and positive.
+Compare it to the ATE for $H=1$.
+(add discussion of Craig's regression: regress outcome on forced, hyperbolic and interaction).
+    \item Another possible explanation is \emph{overconfidence}.
+Cite some literature about why and how it might matter.
+Survey question 2 elicits the subjective probability that borrowers will recover their pawn.
+We use this to construct an individual-level measure of overconfidence.
+Using data for the control group, we build a model to predict recovery based on covariates \emph{excluding} question 2.
+Why the control group?
+When completing the baseline survey borrowers don't know anything about the commitment contract, so we have elicited their recovery probability under the status quo contract.
+We compare the elicited probability to the predicted recovery probability for each person, given her covariates.
+For borrowers in the control group, we leave out their own observation when constructing these predictions.
+(Possibly overkill given our sample size but worth checking anyway.) We define overconfidence as the difference of elicited minus predicted recovery probability.
+There is a lot of over-confidence: plot the distribution.
+Are overconfident people more likely to choose commitment?
+How do treatment effects vary with overconfidence?
+Here the leave-one-out aspect is very important to prevent there from being a ``mechanical'' relationship.
+Variant of Craig's suggested regression from above?
+Fan regression?
+    \item Now talk about paternalism.
+First, are people learning?
+Is it the case that people who have borrowed more in the past are less overconfident?
+Do people who were randomized into forced commitment later decide to choose commitment?
+Finally: how to target and who would be hurt if we instituted paternalism?
+The relevant counterfactual here it the TuT, since this is the causal effect of forcing the people who wouldn't choose voluntarily.
+Break down by covariates.
+Do we see any interesting patterns?
+\end{enumerate}
+
+\todo[inline]{Old stuff below...}
 \paragraph{Causal forest heterogeneous treatment effects.}
@@
 \begin{table}[H]
-\caption{Gains for choosers versus gains from non-choosers (ToT \& TuT)}
+\caption{Treatment on the Treated (ToT), Treatment on the Untreated (TuT), Selection-on-gains (ToT - TuT), Average Selection Bias (ASB), and Average Selection Bias, calculated using the results from Section \ref{sec:randchoice}.}
 \label{tot_tut}
@@
 \end{center}
- \scriptsize This table shows estimates of the ToT and the TuT with an IV-LATE framework.
+ %\scriptsize This table shows estimates of the ToT and the TuT with an IV-LATE framework.
 The ToT is computed as the usual LATE with one-sided non-compliance between the choice and control arm, and the TuT is the LATE on non-compliers.
- \hl{ISAAC: NEED TO ADD THE OTHER TWO TREATMENT EFFECTS THAT FRANK DESCRIBED}
 %\textit{Do file: } \texttt{tot\_tut.do}
@@
     \scriptsize
-   \hl{This is an outdated figure. Need to update}
+   \hl{The above figure is outdated figure. Need to update}
      %\textit{Do file: }  \texttt{tot\_tut\_graph.do}
@@
 \begin{figure}[H]
-    \caption{Fan \& Park bounds for benefit in APR\% }
-    \label{fan_park_bounds}
+    \caption{Fan \& Park bounds for benefit in APR\% \hl{Is this without covariates? Are we going to show bounds for the other outcomes?}}
+    \label{fig:FanPark}
     \begin{center}

### 2023-02-28 ws.tex
presentation

--- 2023-02-28 Slides.tex
@@
+%\documentclass[handout, 8pt]{beamer}
 \documentclass[8pt]{beamer}
@@
     \end{itemize}
-    \vfill\item At the same time these firms hide these forcing mechanisms and don’t market their commitment features, potentially because demand for them is low.
+    \vfill \pause\item At the same time these firms hide these forcing mechanisms and don’t market their commitment features, potentially because demand for them is low.
     \vfill  \item  Laibson (2018) argues that clients that benefit from commitment may underestimate its value, and that in such cases private paternalism could be beneficial.
-    \vfill \item  We study the benefits of imposing a fixed payment structure in loans, whether there is demand for it, and whether non-takers of such a commitment product would benefit from taking it.
+    \vfill  \pause\item  We study the benefits of imposing a structured repayment contract, whether there is demand for it, and whether non-takers of such a commitment product would benefit from taking it.
 \end{itemize}
@@
 
-\begin{frame}{Context}
+\section{Context}
+\begin{frame}{Context - \textbf{Pawn}shops}
 \begin{itemize}
     \vfill \item Pawn loans involve borrowers leaving valuable liquid assets as collateral in exchange for an immediate cash loan
-    \vfill \item Because the loan is overcollateralized and collateral is liquid, the lender approve loans in a few minutes without income or credit history check $\rightarrow$ used for emergencies.
-    \vfill \item This may explain why they are highly popular: $>$11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues.
+    \vfill \pause \item The loan is overcollateralized (loan is 70\% of appraised value) and collateral is liquid.
     \begin{itemize}
-        \item Our partner pawn lender alone approved 4 million loans in \hl{2017-2020}.
-        \item Pawn lending has existed at least since the Roman empire.
-    \end{itemize} 
-    \vfill \item Controversial: interest rates and default rates are high, and used by people in distress.
-    \vfill \item Regulators believe mostly unsophisticated borrowers use it.
-\end{itemize}
-\end{frame}
-
-\begin{frame}{Methodological Contribution}
-\begin{itemize}
-    \vfill \item How do treatment effects relate to selection?  Key question in many literatures:
-	\begin{itemize} 
-		\item HTEs, MTE, LATEs, what is learned from IV regressions (Heckman \& Vytlacil, 2005).
-		\item Health effects of universal versus elective interventions
-		\item Optimal targeting (Alatas et al. 2012)
-	\end{itemize}
-     \vfill \item A context of particular interest to behavioral literature:  the demand for commitment in financial contracts (Laibson 1997, Bryan et al. 2010).
-     \vfill \item Key quantity in debate about paternalism:  impacts on those who wouldn't elect to take the program versus impacts on those that do.
-     \vfill \item Three-arm design:  Control, Choice (voluntary takeup=ITT), Forcing (universal=ATE).  We illustrate how to use standard exclusion restrictions for point identification:
-    \begin{itemize}
-        \item Treatment on the Treated (ToT) and 
-        \item Treatment on the Untreated (TUT), also (ToT-TUT)
-	\item Average Selection Bias, and Average Selection on Levels
-    \end{itemize} 
-   \vfill   \item Consider winners and losers from paternalism using bounding, Random Forest estimation of individual treatment effects. 
-\end{itemize}
-\end{frame}
-
-\begin{frame}{Our partner: logistics, contract, stats}
-    \begin{itemize}
-        \item Partnered with one of the largest pawn lender in Mexico (hundreds of branches)
-        \vfill\item Logistics: 
-        \begin{itemize}
-            \vfill\item Appraising:  gold jewelry as collateral the appraiser tests and weights the gold and assesses its value (5 mins).
-           \vfill \item Loan: if the borrower agrees to leave the piece the appraiser gives 70\% of the gold value in cash, no checking of credit history or income.
-           \vfill \item Contract (Standard in industry): 
-           \begin{itemize}
-               \vfill\item Interest rate = 7\% \textit{per month} compounded daily on the outstanding amount. No reminders.
-               \vfill\item To recover pawn need to pay principal plus the accumulated interest. If this does not happen, pawnbroker keeps the piece and any payments made.
-               \vfill\item  Client can renew for 3 months paying the accumulated interest and signing a new contract.
-           \end{itemize}
+        \item The lender approve loans in a few minutes without income or credit history check $\rightarrow$ used for emergencies.
     \end{itemize}
 
+    \vfill \pause \item Controversial: interest rates and default rates are high, and used by people in distress.
+    \vfill \pause \item Regulators believe mostly unsophisticated borrowers use it.
 \end{itemize}
@@
 
-\begin{frame}{Lenders incentives}
-    \begin{itemize}
-        \item Because the loan is overcollateralized and collateral is liquid, the lender may gain if the borrower defaults on the loan, especially if the borrower pays towards recovery on the way to default.
-        \item In fact, 60\% of clients lose their pawn in a time span of 230 days.
-        \item Among those that lose their pawn, 48\% paid a positive amount towards its recovery and on average paid 42\% of loan.
-        \item This happens in spite (or because?) of 74\% of borrowers reporting a 100\% subjective probability recovery ex-ante. 
-        \item XXX of borrowers are classified as present biased using the simple standard question.
-        \item In such an environment, one may ask if putting more structure in payments may help borrowers recover their pawn.
-        \item We may particularly care about this if borrowers are vulnerable: 30\% of them could not pay either water, electricity \& gas or rent in the past 6 months; 87\% said they are pawning because of an emergency.
-    \end{itemize}
+\begin{frame}{Pawn contract}
+    \begin{figure}[H]
+    \label{ExplanatoryMaterial}
+    \begin{center}
+        \includegraphics[width=0.45\textwidth]{Figuras/sq_contract.png}
+    \end{center}
+\end{figure}
 \end{frame}
@@
        \vfill \item We designed a new contract that is identical to the status quo contract except that it enhances the regularity and salience of payments as a way to encourage repayment.
-       \vfill\item The contract requires 3 equal payments in the 30th, 60th, ad 90th days of the loan, with the imposition of a 2\% fee of the amount owed if the client fails to pay.
-       \vfill\item The propose of the small fee was to mainly to make the structured schedule salient, not to be a large disincentive to be late. 
-       \begin{itemize}
-           \item Transportation cost to go to the branch to pay is on the same order of magnitude as the fee in average.
-       \end{itemize}
-       \vfill\item  The empirical literature provides some guidance that such a contract may decrease default and elicit demand.
-       \begin{itemize}
-           \item Field \& Pande (2008) find null effects of payment frequency on loan default for group lending (but samples are small and there almost no default in the control). 
-           \item XXX CITE PAPERS where frequency helps
-        \item  Bauer et al. (2012) estimate a positive correlation between measured present bias and and selecting into microfinance, which they interpret demand for structured payments.
-       \end{itemize}
+         \begin{figure}[H]
+    \label{ExplanatoryMaterial}
+    \begin{center}
+        \includegraphics[width=0.40\textwidth]{Figuras/fc_contract.png}
+    \end{center}
+\end{figure}
 
@@
 
-\section{Measures}
+\section{Contribution}
 
-\begin{frame}{Data}
+\begin{frame}{Methodological Contribution}
 \begin{itemize}
-    \item Administrative data: XX months before and XX months after the experiment ended
+ \vfill \item A context of particular interest to behavioral literature:  the demand for commitment in financial contracts (Laibson 1997, Bryan et al. 2010).
+
+   \vfill \pause  \item How do treatment effects relate to selection?  Key question in many literatures:
 	\begin{itemize} 
-        \item Unique identifier for each client and for the piece.
-        \item Value of the item, money loaned (70\%), date of pawning
-        \item For all payments: date and amounts
-        \item Fees incurred
-        \item Whether the client lost the pawn, renewed the contract
+		\item HTEs, MTE, LATEs, what is learned from IV regressions (Heckman \& Vytlacil, 2005).
+		\item Health effects of universal versus elective interventions
+		\item Optimal targeting (Alatas et al. 2012)
 	\end{itemize}
 
-    \vfill \item Survey data
+  \vfill \pause  \item Three-arm design:  Control, Choice (voluntary takeup=ITT), Forcing (universal=ATE).  We illustrate how to use standard exclusion restrictions for point identification:
     \begin{itemize}
-        \item During experiment, we asked clients to complete a 5-minute survey before going to the teller window to appraise their piece and before treatment status was known to them.
-        \item Demographics, proxies for income/wealth, education, present-biased preferences, experience pawning, if family or friends commonly asked for money, cost of going to branch, the subjective probability of recovering, the subjective value, etc.
+        \item Treatment on the Treated (ToT) and 
+        \item Treatment on the Untreated (TUT), also
+	\item Average Selection on Gains, Average Selection Bias, and Average Selection on Levels
     \end{itemize}
+
+     \vfill \pause  \item Key quantity in debate about paternalism:  impacts on those who wouldn't elect to take the program versus impacts on those that do.
+
+   \vfill   \pause  \item Consider winners and losers from paternalism 
 \end{itemize}
@@
 
+\section{Design}
+
+% \begin{frame}{Data}
+% \begin{itemize}
+%     \item Administrative data: XX months before and XX months after the experiment ended
+%     \begin{itemize}
+%         \item Unique identifier for each client and for the piece.
+%         \item Value of the item, money loaned (70\%), date of pawning
+%         \item For all payments: date and amounts
+%         \item Fees incurred
+%         \item Whether the client lost the pawn, renewed the contract
+%     \end{itemize}
+
+%     \vfill \item Survey data
+%     \begin{itemize}
+%         \item During experiment, we asked clients to complete a 5-minute survey before going to the teller window to appraise their piece and before treatment status was known to them.
+%         \item Demographics, proxies for income/wealth, education, present-biased preferences, experience pawning, if family or friends commonly asked for money, cost of going to branch, the subjective probability of recovering, the subjective value, etc.
+%     \end{itemize}
+% \end{itemize}    
+% \end{frame}
+
 \begin{frame}{Main outcomes: financial cost and default}
-
+\label{fc_cost}
 \begin{itemize}
-    \item We are interested in measuring the financial cost of borrowing, which very saliently includes the cost of defaulting on the loan and losing the pawn.
-    \item We will measure loan default using an indicator $\mathds{1}(\text{Default}_i)$, and the cost in pesos using the following definition that capture borrower outlays:
+    \item We are interested in measuring the   \hyperlink{fc_dist}{\beamerbutton{financial cost}}  of borrowing, which very saliently includes the cost of defaulting on the loan and losing the pawn.
+    % \item We will measure loan default using an indicator $\mathds{1}(\text{Default}_i)$, and the cost in pesos using the following definition that capture borrower outlays:
 \end{itemize}
@@
 
-\begin{itemize}
-    \vfill \item Towards the end of the presentation we will show results that apply a time discount factor.
+% \begin{itemize}
+%     \vfill \item Towards the end of the presentation we will show results that apply a time discount factor.
 
-\end{itemize}
+% \end{itemize}
 \end{frame}
 
-\begin{frame}{Distribution of financial cost (\$MXN)}
-    \begin{figure}
-     \centering
-        \includegraphics[width=.8\textwidth]{Figuras/hist_fc.pdf}
-    \end{figure}
-\end{frame}
-
-\begin{frame}{Distribution of APR}
-\vspace{.2in}
-\begin{equation*}
-    (\text{APR})_i =\left( 1 + \frac{\frac{\text{Financial Cost}_i}{\text{Appraised Value}_i}}{\text{loan term}_i}\right)^{\text{loan term}_i}-1
-\end{equation*}
-\vspace{.2in}
-\begin{figure}
-     \centering
-        \includegraphics[width=.75\textwidth]{Figuras/hist_apr.pdf}
-    \end{figure}
-\end{frame}
+% \begin{frame}{Distribution of APR}
+% \vspace{.2in}
+% \begin{equation*}
+%     (\text{APR})_i =\left( 1 + \frac{\frac{\text{Financial Cost}_i}{\text{Appraised Value}_i}}{\text{loan term}_i}\right)^{\text{loan term}_i}-1
+% \end{equation*}
+% \vspace{.2in}
+% \begin{figure}
+%      \centering
+%         \includegraphics[width=.75\textwidth]{Figuras/hist_apr.pdf}
+%     \end{figure}
+% \end{frame}
 
@@
 
-\section{Design}
-
 \begin{frame}{Treatment arms}
@@
     \end{itemize}
-    \vfill \item The  existence  of  a  choice  arm  allows  us  not  only  to  measure  if  there  is  demand  for  such  a contract, but who demands it, not only in demographic terms, but in terms of potential treatment effects.
-   \vfill \item  This design is innovative and critical for our purposes, as it enables us to explore whether or not forcing people into a structured payment contract could be more beneficial than allowing choice for a significant fraction of them
+    \vfill \pause \item The  existence  of  a  choice  arm  allows  us  not  only  to  measure  if  there  is  demand  for  such  a contract, but who demands it, not only in demographic terms, but in terms of potential treatment effects.
+   \vfill \pause \item  This design is innovative and critical for our purposes, as it enables us to explore whether or not forcing people into a structured payment contract could be more beneficial than allowing choice for a significant fraction of them.
 \end{itemize}
@@
 
-\begin{frame}{Description}
+% \begin{frame}{Description}
 
-\begin{figure}[H]
-     \caption{Experiment description}
-    \label{exp_description}
-\begin{center}
-        \includegraphics[width=0.85\textwidth]{Figuras/consort.pdf}
-  \end{center}
-\end{figure}
+% \begin{figure}[H]
+%      \caption{Experiment description}
+%     \label{exp_description}
+% \begin{center}
+%         \includegraphics[width=0.85\textwidth]{Figuras/consort.pdf}
+%   \end{center}
+% \end{figure}
 
-\end{frame}
+% \end{frame}
 
-\begin{frame}{Experimental integrity}
-    \begin{table}[H]
-\caption{Attrition table}
-\label{attrition_table}
-\begin{center}
-\scriptsize{\input{./Tables/Attrition.tex}}
-\end{center}
-\end{table}
-\end{frame}
-
-\begin{frame}{Balance}
-
-\vfill ISAAC: can you put the balance table here?
-
-\end{frame}
-
-\section{Results}
+\section{Main Results}
 \begin{frame}{Main results}
-
- \begin{equation*} \label{basic_reg}
-    y_{ij} = \alpha + \beta^F T_{i}^F + \beta^C T_{i}^C + \gamma X_{ij} + \epsilon_{ij}
-\end{equation*}
 
@@
 \resizebox{0.95\textwidth}{!}{
-\scriptsize{\input{./Tables/decomposition_main_te_pres.tex}}
+\scriptsize{\input{./Tables/decomposition_main_te_pres1.tex}}
 }
 \end{center}
-%\textit{Do file: } \texttt{decomposition\_main\_te.do}
 \end{table}
@@
 \begin{frame}{Mechanisms}
+\label{intermediate_outcomes}
+ \begin{itemize}
+     \item Borrowers in the Forced commitment contract pay earlier (-13.8 days), make larger payment in their first visit (+7.9\%), and a larger fraction (+7.9\%) pay in full.
 
-\only<1>{
-\begin{table}[H]
-\caption{Intermediate outcomes}
-\label{mechanisms}
-\begin{center}
-\resizebox{0.7\textwidth}{!}{
-\scriptsize{\input{./Tables/mechanism1_pres.tex}}
-}
-\end{center}
-\end{table}
-}
-\only<2>{
-\begin{table}[H]
-\caption{Intermediate outcomes}
-\label{mechanisms}
-\begin{center}
+        \item Decreases probability of making a payment and not recovering by 7pp.
+    \end{itemize}
 
-\scriptsize{\input{./Tables/mechanism2_pres.tex}}
+   \vfill
 
-\end{center}
-\end{table}
-}
-
-\only<3>{
-\begin{table}[H]
-\caption{Intermediate outcomes}
-\label{mechanisms}
-\begin{center}
-
-\scriptsize{\input{./Tables/mechanism3_pres.tex}}
-
-\end{center}
-\end{table}
-}
-\end{frame}
-
-\begin{frame}{Effects of treatment on future pawning behavior}
-
-\begin{table}[H]
-\caption{Repeat Pawns}
-\label{repeat_loans}
-\begin{center}
-\scriptsize{\input{./Tables/repeat_loans.tex}}
-\end{center}
-
-\end{table}    
-\end{frame}
-
-\begin{frame}{Censoring}
-    \begin{table}[H]
-\caption{Bounding censoring}
-\label{bounding_censoring}
-\begin{center}
-\resizebox{0.9\textwidth}{!}{
-\scriptsize{\input{./Tables/censoring_imp_pres.tex}}
-}
-\end{center}
- \scriptsize 
-%\textit{Do file: } \texttt{censoring_imp.do, censoring_imp_pr.do}
-\end{table}
+   \hyperlink{mechanism_appendix}{\beamerbutton{Details}}
 \end{frame}
@@
     \begin{itemize}
-    \vfill    \item   Commitment works.
-In spite of this, given the  opportunity,  only 11\%  of  borrowers  chose  commitment.
-If  the  effect  of  commitment  were homogeneous, this would be enough to conclude that the 89\% who did not choose it would have been financially better-off if they had.
+    \vfill    \item   Commitment works.   In spite of this, given the  opportunity,  only 11\%  of  borrowers  chose  commitment.   
+    \begin{itemize}
+       \pause \item If  the  effect  of  commitment  were homogeneous, this would be enough to conclude that the 89\% who did not choose it would have been financially better-off if they had.
+    \end{itemize}
 
-    \vfill \item We test and reject the null hypothesis of homogeneous treatment effects (Chernozhuvok et. al. (2018).
+    \vfill \pause \item We test and reject the null hypothesis of homogeneous treatment effects (Chernozhuvok et. al. (2018).
 
-    \vfill \item The borrowers who did not choose commitment could simply be those who don’t need it?
+    \vfill \pause \item The borrowers who did not choose commitment could simply be those who don’t need it?
 
     \begin{itemize}
-        \item More than 11\% of individual borrowers benefit from commitment (30\%) \hyperlink{fan_park_bounds}{\beamerbutton{Fan \& Park bounds}}
-        \item Commitment increases average financial benefit even for the subset of borrowers who would not choose to commit voluntarily : $\operatorname{TUT}=\mathbb{E}[Y_1-Y_0\,|\, T=0]>0$
-        \item Despite substantial treatment effect heterogeneity, most borrowers would experience higher financial benefits under a commitment contract : $F_{\operatorname{TUT}}^{-1}(xxx)>0$
+       \pause \item At least 30\% of individual borrowers benefit from commitment \hyperlink{fan_park_bounds}{\beamerbutton{Fan \& Park bounds}}
+       \pause \item Commitment increases average financial benefit even for the subset of borrowers who would not choose to commit voluntarily : $\operatorname{TUT}=\mathbb{E}[Y_1-Y_0\,|\, T=0]>0$ \hyperlink{rc_design}{\beamerbutton{The `Randomized Choice' Design}}
+       \pause \item Despite substantial treatment effect heterogeneity, most borrowers would experience higher financial benefits under a commitment contract : $F_{\operatorname{TUT}}^{-1}(0.72)>0$
     \end{itemize}
     \end{itemize}
-\end{frame}
-
-\begin{frame}{The `Randomized Choice' Design}
-\label{rc_design}
-\begin{itemize}
-    \vfill \item  Large literature estimating ToT and TuT to better understand who selects  into  treatment  and  why : \begin{itemize}
-        \item “LATE-and-reweight" : Aronow \& Carnegie (2013); Angrist \& Fernandez—Val (2013)  - no selection on gains.  
-        \item Cornelissen et. al. (2018); Walters (2018)  - Modeling assumptions to extrapolate from the reduced-form quantities
-        %TUT and ATE implied by LATE-and-reweight differ sharply from his model-based estimates
-        \item Heckman \& Vytlacil MTE - no parametric  restrictions,  but  an  instrumental  variable $Z$ with sufficiently rich support.
-        \item Brinch et. al. (2017) - discrete $Z$ but under some additivity restrictions on the MTE curve
-        \item Mogstad, Santos \& Torgovitsky (2018) - No parametric form assumption on MTE curve but only partial identification.
-    \end{itemize}
-
-    \vfill \item Our “randomized choice design,” point identifies a number of interesting and economically-relevant causal quantities  without  the  need  for  additional  structural  restrictions.
-\hyperlink{identification_randomized_choice}{\beamerbutton{Identification}} %Only assuming mean exclusion
-
-\end{itemize}
-\end{frame}
-
-\begin{frame}{Causal Parameters}
-\begin{table}[H]
-\caption{Causal TE}
-\label{tot_tut}
-\begin{center}
-\scriptsize{\input{./Tables/tot_tut_pres.tex}}
-\end{center}
-\end{table}
-
- The “right people” choose to commit:  those who are most likely to benefit from it and those whose outcomes are most adverse under the status quo.
 \end{frame}
@@
 \begin{frame}{If commitment works, why don't people choose it?}
+\label{explanations}
+\only<1>{
     \begin{itemize}
-        \onslide<1>{\item Discounting}
-        \onslide<2>{\item Hyperbolicity}
-         \onslide<3>{\item Overconfidence}
-    \end{itemize}
-
-\only<1>{  
-\begin{figure}[H]
-        \caption{Financial cost for different discount rates}
-    \label{fc_discount_rates}
-    \begin{center}
-        \centering
-        \includegraphics[width=0.45\textwidth]{Figuras/discount_effect.pdf}
-    \end{center}
-\end{figure}   
-    \begin{itemize}
-    \item   Commitment contract imposes up-front costs for later benefits (collateral recovery).  
-    \item Can impatience explain why not take up a contract that decreases overall cost?
-    \item  Requires a rate of ~2,000\% to make NPV cost effect insignificant. 
+         \item Discounting
+         \item Hyperbolicity
+         \item Overconfidence
     \end{itemize}
     }
-
 \only<2>{    
-
     \begin{itemize}
-    \item   Standard behavioral angle:  compliers are sophisticated time-consistent, non-compliers are a mix of naifs and the time consistent (who don't need commitment).  
-    \item We have survey measure of time inconsistency taken at baseline.
-    \item  Effect of Forcing should be entirely among the time-inconsistent.  Is this true? 
+         \item \sout{Discounting}
+         \item \sout{Hyperbolicity}
+         \item Overconfidence
     \end{itemize}    
     }
-
-\only<3>{
-
-    \begin{itemize}
-    \item   Asked question prior to assignment, borrowing about subjective probability of recovering.  
-    \item Mean of prior prediction is XX\%, true recovery in control is YY\%.
-    \item  Use prediction of default in control, subjective priors to measure overconfidence.  Does this explain large TUT? 
-    \end{itemize}
-}
+    \vfill
+\hyperlink{explanations_detailed}{\beamerbutton{Details}}
 \end{frame}
 
-\begin{frame}{Paternalism and learning}
+% \begin{frame}{Winners and losers:  Bounding}
+%     \begin{itemize}
+%         \item Bounding exercise
+%     \end{itemize}
 
-    \begin{itemize}
-    \item   Are those with a greater experience of pawning less over-confident?  
-    \begin{itemize}
-        \item Observational analysis of overconfidence by number of prior pawns.
-    \end{itemize}  
-    \item   Do people learn from Forced exposure to the program that they benefit from it?  
-    \begin{itemize}
-        \item Subsequent to the experimental loan, those exposed to different treatments returned to branches where they were offered Choice.  What did they do?
-    \end{itemize}
+% \end{frame}
 
-    \end{itemize}
+% \begin{frame}{Winners and losers:  Conditional TUTs}
+%      \begin{itemize}
+%         \item Conditional TUTs
+%     \end{itemize}
 
-\end{frame}
-
-\begin{frame}{Winners and losers:  Bounding}
-    \begin{itemize}
-        \item Bounding exercise
-    \end{itemize}
-
-\end{frame}
-
-\begin{frame}{Winners and losers:  Conditional TUTs}
-     \begin{itemize}
-        \item Conditional TUTs
-    \end{itemize}
-
-\end{frame}
+% \end{frame}
 
@@
     \begin{itemize}
+
+        \item  Financial cost reduced in 20\% in the Forced arm
+
         \item Results suggest selection on gains, but still large effects of imposing commitment on non-compliers.
-        \item  Default-inclusive APR falls from XX\% in the Control to YY\% in the Forced arm
+
         \item Mystery of low takeup combined with large TUT seems best explained by over-confidence among pawnshop customers.
-        \item  This is a market where lenders profit from default.
-If competitive, interest rates would have to rise to compensate for improved repayment.
-Holding demand and repayment fixed, current 75\% would have to rise to XX\%.
-Welfare transfer from repayers in the control state to those who are helped to repay by commitment.
+
         \item Laibson has spoken of `veiled paternalism' in contexts where principals desire reliability; here we have a case of `veiled non-paternalism' where features encouraging default are embedded.
+
         \item Suggests mandated commitment-based contract structures in payday/pawnshop loans as a form of pro-poor regulation?
@@
 \section{Appendix}
-
-\begin{frame}{Difference number in pawns}
-    \[Pawns \: per \: day_{jt} = \alpha_j + \gamma f(t) + \beta_b \mathbbm{1}(t \in MB)_{t} +\beta_a \mathbbm{1}(t \in MA)_{t}\]
-
-    \begin{table}[H]
-\caption{Number of pawns balance before and after the experiment}
-\label{num_pawns_bal}
-\begin{center}
-\scriptsize{\input{./Tables/num_pawns_bal.tex}}
-\end{center}
-\end{table}
-\end{frame}
 
@@
 \end{table}
+\end{frame}
+
+\begin{frame}{Experimental integrity}
+    \begin{table}[H]
+\caption{Attrition table}
+\label{attrition_table}
+\begin{center}
+\scriptsize{\input{./Tables/Attrition.tex}}
+\end{center}
+\end{table}
+\end{frame}
+
+\begin{frame}{Distribution of financial cost (\$MXN)}
+\label{fc_dist}
+    \begin{figure}
+     \centering
+        \includegraphics[width=.8\textwidth]{Figuras/hist_fc.pdf}
+    \end{figure}
+    \hyperlink{fc_cost}{\beamerbutton{Back}}
 \end{frame}
@@
 
-\begin{frame}{Several definitions of cost}
+% \begin{frame}{Difference number in pawns}
+%     \[Pawns \: per \: day_{jt} = \alpha_j + \gamma f(t) + \beta_b \mathbbm{1}(t \in MB)_{t} +\beta_a \mathbbm{1}(t \in MA)_{t}\]
+
+%     \begin{table}[H]
+% \caption{Number of pawns balance before and after the experiment}
+% \label{num_pawns_bal}
+% \begin{center}
+% \scriptsize{\input{./Tables/num_pawns_bal.tex}}
+% \end{center}
+% \end{table}
+% \end{frame}
+
+% \begin{frame}{Several definitions of cost}
+
+% \begin{table}[H]
+% \caption{Effects on several definitions of cost}
+% \label{table_robustness_fc}
+% \begin{center}
+% \resizebox{0.95\textwidth}{!}{
+% \scriptsize{\input{./Tables/fc_robustness.tex}}
+% }
+% \end{center}
+%  \scriptsize
+
+% %\textit{Do file: } \texttt{fc\_robustness.do}
+% \end{table}
+
+% \end{frame}
+
+% \begin{frame}{Contract terms}
+
+% \begin{figure}[H]
+%      \caption{Contract Terms Summary}
+%     \label{PaperSlip}
+%     \begin{center}
+%         \includegraphics[width=0.65\textwidth]{Figuras/TicketLenderP.png}
+
+%     \end{center}
+
+% \end{figure}
+% \end{frame}
+
+\begin{frame}{Mechanism}
+\label{mechanism_appendix}
 
 \begin{table}[H]
-\caption{Effects on several definitions of cost}
-\label{table_robustness_fc}
+\caption{Intermediate outcomes}
 \begin{center}
-\resizebox{0.95\textwidth}{!}{
-\scriptsize{\input{./Tables/fc_robustness.tex}}
+\resizebox{0.7\textwidth}{!}{
+\scriptsize{\input{./Tables/mechanism1_pres.tex}}
 }
 \end{center}
- \scriptsize
-
-%\textit{Do file: } \texttt{fc\_robustness.do}
 \end{table}
-
+\vfill
+\hyperlink{intermediate_outcomes}{\beamerbutton{Back}}
 \end{frame}
 
-\begin{frame}{Contract terms}
+\begin{frame}{Mechanisms}
 
-\begin{figure}[H]
-     \caption{Contract Terms Summary}
-    \label{PaperSlip}
+\begin{table}[H]
+\caption{Intermediate outcomes}
 \begin{center}
-        \includegraphics[width=0.65\textwidth]{Figuras/TicketLenderP.png}
+\scriptsize{\input{./Tables/mechanism2_pres.tex}}
+\end{center}
+\end{table}
+\vfill
+\hyperlink{intermediate_outcomes}{\beamerbutton{Back}}
+\end{frame}
 
+\begin{frame}{Mechanisms}
+
+    \begin{table}[H]
+\caption{Intermediate outcomes}
+\begin{center}
+\scriptsize{\input{./Tables/mechanism3_pres.tex}}
+\end{center}
+\end{table}
+\vfill
+\hyperlink{intermediate_outcomes}{\beamerbutton{Back}}
+\end{frame}
+
+\begin{frame}{Effects of treatment on future pawning behavior}
+
+\begin{table}[H]
+\caption{Repeat Pawns}
+\label{repeat_loans}
+\begin{center}
+\scriptsize{\input{./Tables/repeat_loans.tex}}
 \end{center}
 
-\end{figure}
-
-\end{frame}
-
-\begin{frame}{Explanatory material}
-    \begin{figure}[H]
-     \caption{Explanatory Material}
-    \label{ExplanatoryMaterial}
-    \begin{center}
-        \includegraphics[width=0.9\textwidth]{Figuras/micas.pdf}
-    \end{center}
-\end{figure}
+\end{table}    
 \end{frame}
@@
 \end{figure}   
+\end{frame}
+
+\begin{frame}{Censoring}
+    \begin{table}[H]
+\caption{Bounding censoring}
+\label{bounding_censoring}
+\begin{center}
+\resizebox{0.9\textwidth}{!}{
+\scriptsize{\input{./Tables/censoring_imp_pres.tex}}
+}
+\end{center}
+ \scriptsize 
+%\textit{Do file: } \texttt{censoring_imp.do, censoring_imp_pr.do}
+\end{table}
 \end{frame}
@@
 \begin{figure}[H]
-    \caption{Fan \& Park bounds for benefit in APR\% }
+    \caption{Fan \& Park bounds for benefit in effective FC }
 
     \begin{center}
-        \includegraphics[width=0.75\textwidth]{Figuras/fan_park_bounds_apr.pdf}
+        \includegraphics[width=0.75\textwidth]{Figuras/fan_park_bounds_fc_admin.pdf}
     \end{center}
@@
  \hyperlink{choice_hte}{\beamerbutton{Back}}
+\end{frame}
+
+\begin{frame}{The `Randomized Choice' Design}
+\label{rc_design}
+\begin{itemize}
+    \vfill \item  Large literature estimating ToT and TuT to better understand who selects  into  treatment  and  why : \begin{itemize}
+        \item “LATE-and-reweight" : Aronow \& Carnegie (2013); Angrist \& Fernandez—Val (2013)  - no selection on gains.  
+        \item Cornelissen et. al. (2018); Walters (2018)  - Modeling assumptions to extrapolate from the reduced-form quantities
+        %TUT and ATE implied by LATE-and-reweight differ sharply from his model-based estimates
+        \item Heckman \& Vytlacil MTE - no parametric  restrictions,  but  an  instrumental  variable $Z$ with sufficiently rich support.
+        \item Brinch et. al. (2017) - discrete $Z$ but under some additivity restrictions on the MTE curve
+        \item Mogstad, Santos \& Torgovitsky (2018) - No parametric form assumption on MTE curve but only partial identification.
+    \end{itemize}
+
+    \vfill \item Our “randomized choice design,” point identifies a number of interesting and economically-relevant causal quantities  without  the  need  for  additional  structural  restrictions.
+\hyperlink{identification_randomized_choice}{\beamerbutton{Identification}} %Only assuming mean exclusion
+    \hyperlink{choice_hte}{\beamerbutton{Back}}
+\end{itemize}
+\end{frame}
+
+\begin{frame}{Causal Parameters}
+\begin{table}[H]
+\caption{Causal TE}
+\label{tot_tut}
+\begin{center}
+\scriptsize{\input{./Tables/tot_tut_pres1.tex}}
+\end{center}
+\end{table}
+
+\begin{itemize}
+    \item Commitment is beneficial to people who would not choose it. 
+    \item The “right people” choose to commit:  those who are most likely to benefit from it and those whose outcomes are most adverse under the status quo.
+\end{itemize}
+
 \end{frame}
@@
 
-\end{document}
+\begin{frame}{If commitment works, why don't people choose it?}
+\label{explanations_detailed}
+    \begin{itemize}
+         \onslide<1>{\item Discounting}
+         \onslide<2>{\item Hyperbolicity}
+          \onslide<3>{\item Overconfidence}
+    \end{itemize}
 
+\only<1>{  
 \begin{figure}[H]
-    \caption{Choice of contracts and treatment effects (ToT \& TuT)}
-    \label{choose_wrong}
+        \caption{Financial cost for different discount rates}
+    \label{fc_discount_rates}
     \begin{center}
-        \begin{subfigure}{0.45\textwidth}
-        \caption{Mistakes in choice arm}
         \centering
-        \includegraphics[width=\textwidth]{Figuras/line_cw_apr_tot_tut.pdf}
-
-    \end{subfigure}
-        \begin{subfigure}{0.45\textwidth}
-        \caption{Financial value of mistake}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/money_cw_apr_tot_tut.pdf}
-
-    \bigskip
-
-    \end{subfigure}
-        \begin{subfigure}{0.45\textwidth}
-        \caption{\% better when forced to forced commitment}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/line_better_forceall_apr_te_cf.pdf}
-
-    \end{subfigure}
-
+        \includegraphics[width=0.45\textwidth]{Figuras/discount_effect.pdf}
     \end{center}
 \end{figure}   
+    \begin{itemize}
+    \item   Commitment contract imposes up-front costs for later benefits (collateral recovery).  
+    \item Can impatience explain why not take up a contract that decreases overall cost?
+    \item  Requires a rate of ~2,000\% to make NPV cost effect insignificant. 
+    \end{itemize}
+}
+
+\only<2>{
+
+    \begin{itemize}
+   \vfill \item   Standard behavioral angle:  compliers are sophisticated time-inconsistent, non-compliers are a mix of naifs and the time consistent (who don't need commitment).  
+   \vfill \item We have survey measure of time inconsistency taken at baseline.
+   \vfill \item  Effect of Forcing should be entirely among the time-inconsistent.  Is this true? 
+    \end{itemize}
+}
+
+\only<3>{
+
+    \begin{itemize}
+   \vfill \item   Asked question prior to assignment, borrowing about subjective probability of recovering.  
+   \vfill \item Mean of prior prediction is XX\%, true recovery in control is YY\%.
+   \vfill \item  Use prediction of default in control, subjective priors to measure overconfidence.  Does this explain large TUT? 
+    \end{itemize}
+}
+
+\hyperlink{explanations}{\beamerbutton{Back}}
+
+\end{frame}
+
+\begin{frame}{Paternalism and learning}
+
+    \begin{itemize}
+    \item   Are those with a greater experience of pawning less over-confident?  
+    \begin{itemize}
+        \item Observational analysis of overconfidence by number of prior pawns.
+    \end{itemize}  
+    \item   Do people learn from Forced exposure to the program that they benefit from it?  
+    \begin{itemize}
+        \item Subsequent to the experimental loan, those exposed to different treatments returned to branches where they were offered Choice.  What did they do?
+    \end{itemize}
+
+    \end{itemize}
+
+\end{frame}
+
+\end{document}

### 2023-04-20 OA.tex
changes after presentation(s)...rewriting of text

@@
 \begin{figure}[H]
-        \caption{Financial cost for different discount rates}
+        \caption{Financial cost TUT effect for different discount rates}
     \label{fc_discount_rates}
@@
         \centering
-        \includegraphics[width=0.55\textwidth]{Figuras/discount_effect.pdf}
-    \end{center}
-     \scriptsize This Figure estimates the treatment effect on financial cost with different discount rates.  
+        \includegraphics[width=0.55\textwidth]{Figuras/discount_effect_tut.pdf}
+    \end{center}
+     \scriptsize This Figure estimates the treatment effect on financial cost for the untreated with different discount rates.  
      %\textit{Do file: }  \texttt{discounted\_noeffect.do}
 \end{figure}
+
+\begin{figure}[H]
+    \caption{Partitoin of TuT \& ToT effect by behavioral variables.}
+    \label{tut_beh_partition}
+    \begin{center}
+    \begin{subfigure}{0.475\textwidth}
+        \caption{TuT}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/tut_beh_partition.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.475\textwidth}
+        \caption{ToT}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/tot_beh_partition.pdf}
+    \end{subfigure}
+
+    \end{center}
+     \scriptsize    \\
+      %\footnotesize{ \textit{Do file: }  \texttt{partition_tot_tut.do}
+\end{figure}
+
+\cleardoublepage
 

### 2023-04-20 Tables/decomposition_main_te_pres1.tex
changes after presentation(s)...rewriting of text

@@
 % Table generated by Excel2LaTeX from sheet 'decomposition_main_te_pres1'
-\begin{tabular}{lcccccc}
+\begin{tabular}{lcccccccc}
 \toprule
-      &       & \multicolumn{5}{c}{Components of FC} \\
+      &       & \multicolumn{5}{c}{Components of FC}  &       &  \\
 \cmidrule{3-7}      & FC    & \textcolor[rgb]{ .749,  .749,  .749}{Int.
 pymnt} & \textcolor[rgb]{ .749,  .749,  .749}{Fee pymnt} & \textcolor[rgb]{ .749,  .749,  .749}{Princ.
-pymnt} & \textcolor[rgb]{ .749,  .749,  .749}{Lost pawn val} & Default \\
+pymnt} & \textcolor[rgb]{ .749,  .749,  .749}{Lost pawn val} & Default &       & APR \\
 \midrule
-      & (1)   & \textcolor[rgb]{ .749,  .749,  .749}{(2)} & \textcolor[rgb]{ .749,  .749,  .749}{(3)} & \textcolor[rgb]{ .749,  .749,  .749}{(4)} & \textcolor[rgb]{ .749,  .749,  .749}{(5)} & (6) \\
+      & (1)   & \textcolor[rgb]{ .749,  .749,  .749}{(2)} & \textcolor[rgb]{ .749,  .749,  .749}{(3)} & \textcolor[rgb]{ .749,  .749,  .749}{(4)} & \textcolor[rgb]{ .749,  .749,  .749}{(5)} & (6)   &       & (7) \\
 \midrule
 \midrule
-Forced cmit & \boxit{0.5in} -379.7*** & \textcolor[rgb]{ .749,  .749,  .749}{-157.3***} & \textcolor[rgb]{ .749,  .749,  .749}{32.1***} & \textcolor[rgb]{ .749,  .749,  .749}{-0.57} & \textcolor[rgb]{ .749,  .749,  .749}{-254.5**} & \boxit{0.5in} -0.065*** \\
-      & (111.4) & \textcolor[rgb]{ .749,  .749,  .749}{(34.9)} & \textcolor[rgb]{ .749,  .749,  .749}{(1.43)} & \textcolor[rgb]{ .749,  .749,  .749}{(3.03)} & \textcolor[rgb]{ .749,  .749,  .749}{(104.8)} & (0.023) \\
-Choice cmit & -84.9 & \textcolor[rgb]{ .749,  .749,  .749}{-24.9} & \textcolor[rgb]{ .749,  .749,  .749}{1.34**} & \textcolor[rgb]{ .749,  .749,  .749}{-3.98} & \textcolor[rgb]{ .749,  .749,  .749}{-61.4} & -0.025 \\
-      & (114.6) & \textcolor[rgb]{ .749,  .749,  .749}{(38.4)} & \textcolor[rgb]{ .749,  .749,  .749}{(0.54)} & \textcolor[rgb]{ .749,  .749,  .749}{(2.47)} & \textcolor[rgb]{ .749,  .749,  .749}{(109.2)} & (0.021) \\
-      &       & \textcolor[rgb]{ .749,  .749,  .749}{} & \textcolor[rgb]{ .749,  .749,  .749}{} & \textcolor[rgb]{ .749,  .749,  .749}{} & \textcolor[rgb]{ .749,  .749,  .749}{} &  \\
+Forced cmit & \boxit{0.35in} -379.7*** & \textcolor[rgb]{ .749,  .749,  .749}{-157.3***} & \textcolor[rgb]{ .749,  .749,  .749}{32.1***} & \textcolor[rgb]{ .749,  .749,  .749}{-0.57} & \textcolor[rgb]{ .749,  .749,  .749}{-254.5**} & \boxit{0.35in} -0.065*** &       & \boxit{0.35in} -0.34*** \\
+      & (111.4) & \textcolor[rgb]{ .749,  .749,  .749}{(34.9)} & \textcolor[rgb]{ .749,  .749,  .749}{(1.43)} & \textcolor[rgb]{ .749,  .749,  .749}{(3.03)} & \textcolor[rgb]{ .749,  .749,  .749}{(104.8)} & (0.023) &       & (0.080) \\
+Choice cmit & -84.9 & \textcolor[rgb]{ .749,  .749,  .749}{-24.9} & \textcolor[rgb]{ .749,  .749,  .749}{1.34**} & \textcolor[rgb]{ .749,  .749,  .749}{-3.98} & \textcolor[rgb]{ .749,  .749,  .749}{-61.4} & -0.025 &       & -0.12 \\
+      & (114.6) & \textcolor[rgb]{ .749,  .749,  .749}{(38.4)} & \textcolor[rgb]{ .749,  .749,  .749}{(0.54)} & \textcolor[rgb]{ .749,  .749,  .749}{(2.47)} & \textcolor[rgb]{ .749,  .749,  .749}{(109.2)} & (0.021) &       & (0.073) \\
+      &       & \textcolor[rgb]{ .749,  .749,  .749}{} & \textcolor[rgb]{ .749,  .749,  .749}{} & \textcolor[rgb]{ .749,  .749,  .749}{} & \textcolor[rgb]{ .749,  .749,  .749}{} &       &       &  \\
 \midrule
-Observations & 6304  & \textcolor[rgb]{ .749,  .749,  .749}{6304} & \textcolor[rgb]{ .749,  .749,  .749}{6304} & \textcolor[rgb]{ .749,  .749,  .749}{6304} & \textcolor[rgb]{ .749,  .749,  .749}{6304} & 6304 \\
-R-squared & 0.007 & \textcolor[rgb]{ .749,  .749,  .749}{0.022} & \textcolor[rgb]{ .749,  .749,  .749}{0.151} & \textcolor[rgb]{ .749,  .749,  .749}{0.003} & \textcolor[rgb]{ .749,  .749,  .749}{0.007} & 0.013 \\
-Control Mean & 1851.0 & \textcolor[rgb]{ .749,  .749,  .749}{545.9} & \textcolor[rgb]{ .749,  .749,  .749}{0} & \textcolor[rgb]{ .749,  .749,  .749}{5.82} & \textcolor[rgb]{ .749,  .749,  .749}{1305.1} & 0.44 \\
+Observations & 6304  & \textcolor[rgb]{ .749,  .749,  .749}{6304} & \textcolor[rgb]{ .749,  .749,  .749}{6304} & \textcolor[rgb]{ .749,  .749,  .749}{6304} & \textcolor[rgb]{ .749,  .749,  .749}{6304} & 6304  &       & 6304 \\
+R-squared & 0.007 & \textcolor[rgb]{ .749,  .749,  .749}{0.022} & \textcolor[rgb]{ .749,  .749,  .749}{0.151} & \textcolor[rgb]{ .749,  .749,  .749}{0.003} & \textcolor[rgb]{ .749,  .749,  .749}{0.007} & 0.013 &       & 0.011 \\
+Control Mean & 1851.0 & \textcolor[rgb]{ .749,  .749,  .749}{545.9} & \textcolor[rgb]{ .749,  .749,  .749}{0} & \textcolor[rgb]{ .749,  .749,  .749}{5.82} & \textcolor[rgb]{ .749,  .749,  .749}{1305.1} & 0.44  &       & 1.84 \\
 \bottomrule

### 2023-04-20 donde.tex
changes after presentation(s)...rewriting of text

@@
 \section{Introduction}
-Many people have a difficult time accumulating and retaining capital unless they are provided a structure within which to do so.
+
+Restrictions of choice are often surreptitiously imposed on consumers.
+Firms limit their worker's freedom by requiring time-consuming progress reports,  schools impose deadlines and pop quizzes, and loan contracts often require monthly repayment.
+As pointed out by \cite{Laibson2018}, although these choice-restricting mechanisms may be beneficial to firms and clients, they are often disliked by the latter, and therefore ‘shrouded’ by firms, i.e.
+not advertised but nonetheless embedded in products.
+\cite{Laibson2018} coins the term ``private paternalism'' for cases when restrictions on the freedom of choice is implemented by a firm in a way that advances a client's interests.
+
+Although the examples above are plausible, substantiating a case for private paternalism is not easy.
+It involves comparing the causal effect of forcing a certain product characteristic versus the effect of letting people choose on that characteristic.
+This is not an easy task because a given person wither has or does not have choice, and because choice induces selection, potentially biasing causal estimates.
+A large behavioral literature has illustrated that allocating borrowers to a commitment-savings product increase savings \citep{thaler2004save, prina2015banking, brune2016facilitating, callen2019headwaters, Pascaline, Ashraf}, but this literature does not show that commitment would not be chosen by those that would benefit from it, that is, that the Treatment Effect on the Untreated (TuT) is positive.
+In fact, selection on gains has such wide acceptance that economists often impose it in their models \hl{CITES}.
+In microfinance, a context close to ours, \citep{Murdoch} claim that there exists positive selection, citing a positive correlation between displaying present biased preferences in surveys and selecting into microfinance as evidence of borrowers' actually demanding the discipline imposed by frequent payments.
+However, they are unable to show that borrowers indeed benefit or that they indeed positively select based on treatment effects.
+
+%Many people have a difficult time accumulating and retaining capital unless they are provided a structure within which to do so.
 The behavioral lens on intertemporal financial services has provided critical insights on this problem, suggesting that saving from cash-in-hand is challenging \citep{Ashraf, Pascaline}, that credit may be preferred to savings as a way of accumulating capital simply because credit repayment contracts provide more structure \cite{Murdoch}, and even that the absence of structured financial contracts may be a key barrier preventing the poor from climbing out of poverty \citep{bertrand2004behavioral, collins2009portfolios}.
@@
 
-In this paper we examine pawn contracts, an understudied form of credit despite their relative ubiquity \citep{carter2012pawnshops}, and a major vehicle through which poor households may dis-accumulate savings.
+This paper studies the benefits of restricting choice in the context of pawnbroker lending.
+Pawn loans are one of the oldest, most understudied, and most prevalent forms of borrowing \citep{carter2012pawnshops}.
+There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues (in China it is a 43 billion dollar industry).\footnote{\url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.} Our partner pawn lender (henceforth Lender $P$) alone served more than 1 million clients in the last 3 years with more than 4 million contracts.\footnote{For comparison there were 2.3 million micro-finance clients in Mexico in 2009 (\cite{Pedroza:2010}).} Pawnshop lending presents an inverted lending case: since these loans are over-capitalized, the principal in the lending contract stands to gain the most when agents default.
+
+Our collaborating pawn lender (henceforth Lender P) gave 70\% of the value of the pawn in credit, and charged a monthly interest rate of 7\% for loans of a three-month duration, with a flexible no-reminders contract typical of the industry that can be paid back anytime before the loan comes due at no penalty.
+This combination of features, and the fact that the gold pawn is highly liquid, means that the lender makes 90\% more profit over three months for a borrower who defaults than one who repays (30\% of collateral value recovered under default, 15.8\% of collateral value paid in interest if loan fully repaid).
+While an older literature considers the exploitative potential in over-collateralization and underpricing of collateral \citep{basu1984implicit}, the implication of such contracts has not been analyzed in the behavioral literature.
+%When the lender desires default, the repayment-inducing features of commitment-style repayment contracts become undesirable and there may be incentives for the principal to create contracts with no structure, no reminders, and simple balloon payments.
+To repurpose the language of \cite{Laibson2018}, we suggest that pawn contracts effectively shroud their \textit{lack} of commitment features to induce default in a manner not obvious to borrowers.
+Given that pawnshops, moneylenders, and paycheck lending institutions are likely to face client pools disproportionately made up of impatient and time-inconsistent individuals, the design of such contracts may have serious consequences for the financial lives of the poor.
+
+%clients lose their pawn, and among those that recover it almost all of them pay in the last days, just before the loan elapses.\footnote{In the US default is also high at 15\% (\url{https://tinyurl.com/yc2x5bjf}).}
+
+%In this paper we examine pawn contracts, an understudied form of credit despite their relative ubiquity \citep{carter2012pawnshops}, and a major vehicle through which poor households may dis-accumulate savings.
 There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues.
 In China it is a 43 billion dollar industry.\footnote{\url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.} Our partner, a Mexican pawn lender (henceforth Lender $P$) alone served more than 1 million clients in the last 3 years with more than 4 million contracts.
-Pawnshop lending presents an inverted lending case:  since these loans are over-capitalized, the principal in the lending contract stands to gain the most when agents default.
-Our collaborating lender gave only 70\% of the value of the pawn in credit, and charged a monthly interest rate of 7\% for loans of a three-month duration, with a flexible no-reminders contract typical of the industry that can be paid back anytime before the loan comes due.
-This combination of features means that the lender makes 90\% more profit over three months for a borrower who defaults than one who repays (30\% of collateral value recovered under default, 15.8\% of collateral value paid in interest if loan fully repaid).
-While an older literature considers the exploitative potential in over-collateralization and underpricing of collateral \citep{basu1984implicit}, the implication of such contracts has not been analyzed in the behavioral literature.
-When the lender desires default, the repayment-inducing features of commitment-style repayment contracts become undesirable and there may be incentives for the principal to create contracts with no structure, no reminders, and simple balloon payments that represent the opposite of what the behavioral literature tells us will induce repayment.
-To repurpose the language of \cite{Laibson2018}, we suggest that pawn contracts effectively shroud their \textit{lack} of commitment to induce default in a manner not obvious to borrowers.
-Given that pawnshops, moneylenders, and paycheck lending institutions are likely to face client pools disproportionately made up of impatient and time-inconsistent individuals, the design of such contracts may have serious consequences for the financial lives of the poor.
-
-Against this backdrop, we implement a multi-arm randomized control trial covering close to 10,000 pawnshop clients in 6 branches of Lender $P$ in Mexico City, using a design built to test the demand for and impact of commitment in pawn repayment contracts.
-Our control arm illustrates the costs of the status quo contract; fully 57\% of borrowers default and so lose their pawn.
-We then implement a `commitment choice’ arm, in which borrowers are able at the time of taking a loan to opt in to a structured repayment contract, in which they are asked to make three monthly payments rather than one balloon payment at the end, with each monthly payment including the accrued interest at that time, and borrowers levied a nominal fee of 2\% of that month's payment in case of delinquency as a reminder/reinforcement of the importance of these interim payments.
-In addition, we include a `forced commitment’ arm, in which all borrowers are required to repay using the commitment structure.
-The combination of voluntary and forced commitment in the same study allows us to address several key questions.
-First, does using more structured repayment contracts help pawnshop borrowers to achieve higher repayment rates, thereby saving them money?
-Second, do borrowers recognize this benefit, demanding commitment in sufficient numbers to meaningfully change repayment behavior?
-Finally, and most uniquely, because we incorporate the forced commitment arm, we are able to ask whether the \textit{right} borrowers voluntarily demand commitment, gaining point identification for the treatment on compliers and the treatment on non-compliers by comparison across the control, choice, and forced arms.
-
-Our results suggest that the structure of the commitment is strongly effective in preventing default, with the average individual in the forced arm paying financing costs inclusive of fees that are 9.4\% lower than the control (from \$3157 to \$2860 MXN), while the likelihood of recovering their pawn increases by 26\% (from 43\% to 55\%).
-Results are robust qualitatively to including transport costs of going to the branch plus losing a day's wage for each visit, suggesting that in the context of a commitment structure it is possible to save borrowers money by charging them fees!
-Importantly, the benefits are distributed broadly: almost the whole distribution of treatment effects shows cost savings; however those most economically vulnerable, and those most overconfident about their probability of repayment, experience larger gains.\footnote{As in \cite{Rabin2018} we contrast subjects' \textit{own predictions} of their behavior with their actual behavior, but we do it in a natural setting.}  Treatment effects are concentrated in the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery.
-That is, the commitment contract induces people who would otherwise pay something towards recovery, to pay more and faster, making them more likely to recover their pawn at a lower financial cost.
-
-Borrowers assigned to the forced commitment contract are 5 percentage points (100\% of the mean) more likely than the control group to ask for another loan in the future, suggesting that they liked the commitment contract after experiencing it.
+
+Against this backdrop, we implement a multi-arm randomized control trial covering close to 10,000 pawnshop clients in 6 branches of Lender $P$ in Mexico City, using a design built to test the demand for and impact of payment structure in pawn repayment contracts.
+Our control arm illustrates the costs of the status quo contract; fully 57\% of borrowers default and so lose their pawn.\footnote{These high default rates are not uncommon, in the US default is also high at 15\% (\url{https://tinyurl.com/yc2x5bjf}).} We then implement a `commitment choice’ arm, in which borrowers are able at the time of taking a loan to opt in to a structured repayment contract, in which they are asked to make three monthly payments rather than one balloon payment at the end, with each monthly payment including the accrued interest at that time, and borrowers levied a nominal fee of 2\% of that month's payment in case of delinquency as a reminder/reinforcement of the importance of these interim payments.
+In addition, we include a `forced commitment’ arm, in which all borrowers are required to repay using the monthly payment structure.
+
+The combination of voluntary and forced commitment within the RCT allows us to address several key questions.
+First, does using more structured repayment contracts help pawnshop borrowers to save on financing cost.
+Second, do borrowers recognize this benefit, demanding commitment in sufficient numbers?
+Finally, and most uniquely, because we incorporate the forced commitment arm, we are able to ask whether the \textit{right} borrowers voluntarily demand commitment, gaining point identification for the Treatment on the Treated (ToT) and the Treatment on the Untreated (TuT), using the control, choice, and forced arms.
+
+Our results suggest that the structure of the commitment is strongly effective in preventing default, with the average individual in the forced arm paying financing costs inclusive of fees that are \hl{20\%} lower than the control, while default decreases by 6.5 percentage points (15\% of the mean).
+In terms of Annual Percentage Rates, the financial cost of borrowing is reduced by 34 percentage points.
+That is, imposing commitment structure it is possible to save borrowers money by charging them fees!
+These results are robust qualitatively to including transport costs of going to the branch plus losing a day's wage for each visit, using the subjective instead of the gold value of the pawn, and imputing some adjustment for liquidity lost by requiring monthly payments.
+
+The monthly payment contract seems to be achieving these cost savings by speeding up payments and by generating an early bifurcation of borrowers into those that will recover the pawn and those that will not, saving the later payments towards recovery.
+In the treatment group, the first payment occurs 13 days earlier, the fraction recovering on the first visit by is 7.9 percentage point higher.
+Commitment contract decreases fraction of borrowers making a payment and not recovering by 7 percentage points.
+\hl{Treatment effects are concentrated in the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery.
+That is, the commitment contract induces people who would otherwise pay something towards recovery, to pay more and faster, making them more likely to recover their pawn at a lower financial cost.}
+
+In spite of a large average treatment effect documenting financial cost savings, given the opportunity in the choice arm, only 11\% of borrowers actually choose commitment.
+If the effect of commitment were homogeneous, this would be enough to conclude that the 89\%
+who did not choose it would have been financially better off if they had.
+However, we test and reject the null hypothesis of homogeneous treatment effects using the method of \cite{chernozhukov2018generic}.
+Can the borrowers who did not choose commitment be those who simply don’t need it?
+We address this question by sequentially imposing more structure in the problem.
+
+\hl{We start by bounding the distribution of treatment effects $Y_{1i}-Y_{0i}$ using the two marginal distribution } in the treatment and control arms as in \cite{fan2010sharp}.
+We find that at least 30\% of individual borrowers benefit from commitment, implying many borrowers did not demand even though the treatment effect would be positive for them.
+Then, we impose the mild exclusion restriction that the effect of the contract does not depend on how they got it, that is: choosing a contract has the same treatment effect as being assigned to the contract.\footnote{This is a frequently used assumption even if often implicit.
+For instance, a significant literature uses schooling compulsory laws to estimate the return of one more year of school, and then often interprets that schooling, in general, has this return.} We show that in this case our 3-armed experiment point identifies the TuT.
+We then estimate that the financial cost savings of the TuT is large, at \$356 pesos, equivalent to 24 percentage point savings in APR.
+That is, on average borrowers that did \textit{not} choose the frequent payment contract would have benefited from having that contract.\footnote{We estimate a positive ToT that is larger than the TuT, but it is imprecise\footnote{This results from the smaller sample size, given that few chose the monthly payment contract.}, and the hypothesis of ToT=TuT is rejeted only with 13 percent confidence for the APR and 12 percent confidence for default.}  We also estimate that those that would not choose if given the opportunity would have lower status-quo outcomes (i.e.
+the average selection bias is negative).
+Finally, assuming the exclusion restriction for subsets of observable characteristics splits generated by a causal forest allows us to establish that \hl{70\%} of would-be non-choosers would save on financial cost by being assigned to frequent payments.
+That is, the benefits of imposing a monthly payment are distributed broadly.
+\hl{TuT benefits are particularly large for XXX CHARACTERISTICS, and ToT benefits for those with XXX.}
+
+\textcolor{brown}{In a final step, we use the Causal Random Forest algorithm of \cite{atheygrf} to estimate individual-level treatment effects for the forced versus control arm, and show the benefits of forcing to be significantly negatively correlated with the propensity to choose commitment estimated from the choice arm.
+93\% of those who did not opt for the commitment contract would have been better off with it, while only 1\% of those who chose commitment would have been better off without it.} \textcolor{blue}{Targeting frequent payment products to those that benefit the most is a policy that should be explored.
+In this context we calculate \hl{XXX}.}
+
+%however those most economically vulnerable, and those most overconfident about their probability of repayment, experience larger gains.
+
+%\footnote{As in \cite{Rabin2018} we contrast subjects' \textit{own predictions} of their behavior with their actual behavior, but we do it in a natural setting.}
+
+%Borrowers assigned to the forced commitment contract are 5 percentage points (100\% of the mean) more likely than the control group to ask for another loan in the future, suggesting that they liked the commitment contract after experiencing it.
 However, when offered the choice of commitment, very few borrowers elect to commit voluntarily.
@@
 
-Most importantly, our multi-arm design allows us to show that the \textit{wrong} people choose commitment when offered it.
+%Most importantly, our multi-arm design allows us to show that the \textit{wrong} people choose commitment when offered it.
 We illustrate this point in three distinct ways.
@@
 
-Additional evidence of the importance of paternalism in pawnshop commitment is provided by two additional study arms offering variants of `soft' commitment.
-In one arm all borrowers were asked to commit to make three monthly payments instead of a single balloon payment, but no external reminders or fees were imposed.
-In a second arm borrowers were given the ability to choose whether to engage in this form of soft commitment.
-Both of these arms are completely ineffective, suggesting that it is the combination of external imposition of the contract along with the teeth provided by the reminder and fees that generate the savings to borrowers relative to the status quo contract.
-
 What explains the persistence of a contract so contrary to borrowers’ interests?
 First, we show substantial levels of over-optimism among borrowers.
-Those most likely to benefit from the commitment contract and \textit{not} choose it are the individuals who most systematically over-estimate their own probability of repayment at the time of taking the loan.
-Second, the existence of commitment-style repayment contracts in pawnshop lending is novel in Mexico.
-While forcing individuals into commitment does not cause them to demand it in subsequent loans, \textcolor{red}{in Table \ref{iv_pf}} we show observational evidence of `learning by not doing’:  individuals offered commitment who elect not to take it and subsequently default \textit{do} learn about the benefits of commitment, demanding commitment loans at higher rates on subsequent pawn contracts when given the choice.
+Those most likely to benefit from the commitment contract and \textit{not} choose it are the individuals who most systematically over-estimate their own probability of repayment at the time of taking the loan.\footnote{More generally \hl{demand for commitment is higher among those with XXX characteristics.}}  Second, the existence of commitment-style repayment contracts in pawnshop lending is novel in Mexico.
+The dramatic improvements in borrower income arising from the commitment contract come directly from the pockets of lenders, reinforcing that the pawn industry as a whole has a strong interest in retaining the status quo.
+
+Does learning eventually overcome the low demand for commitment?
+For learning to happen clients would need to experiment the frequent payment contract, and this was not the typical contract in the industry.
+But even if the contract was experienced, borrower may fail to learn or learn only slowly.
+We find that those who are forced to the monthly payment product are 6.7 percentage points more likely to become repeat costumers than those assigned to the status-quo contract.
+One way to interpret this is that that having experienced the frequent payment contract (and the lower financial cost of borrowing that come with it), they want to borrow more.\footnote{A second intepretation is that the iliquidity created by the monthly payment contract makes them want obtain second loan to pay the first one.
+This second explanation is unlikely since borrowers obtain a second loan not within the first 90 days of the first loan when payments are due; moreover, the correlation is also present conditional on having paid down the first loan.
+Borrowers tend to pledge a different piece for the second loan, so that recovery of the first pawn is also an unlikely explanation.} However, a stronger test of liking the monthly payment contract is whether conditional on coming again, they would choose frequent payments.
+We test this and we cannot reject that demand is not higher after experiencing the monthly payment contract, however sample sizes are small and \hl{the minimum detectable effect is XXX.}
+
+%While forcing individuals into commitment does not cause them to demand it in subsequent loans, \textcolor{red}{in Table \ref{iv_pf}} we show observational evidence of `learning by not doing’:  individuals offered commitment who elect not to take it and subsequently default \textit{do} learn about the benefits of commitment, demanding commitment loans at higher rates on subsequent pawn contracts when given the choice.
 Finally, while we are working with a lender who has a social mission and is interested in understanding how to help borrowers, there is no free lunch.
@@
 By overcollateralizing and then structuring loan contracts in a manner encouraging of default, lenders are able to extract substantial value independent of the interest charged.
-Further, the `nudge’ approach generally favored by the behavioral literature (voluntary commitment) may not be adequate; we estimate that over 50\% of the borrowers in our study are naïve hyperbolics in the sense that they would benefit from commitment but will not choose it.
+Further, the `nudge’ approach generally favored by the behavioral literature (voluntary commitment) may not be adequate.
+We hesitate to give precise policy recommendations since we don't have good measures of welfare.
+Even though the monthly payment contract dramatically reduces financial cost, it could potentially generate lower (or higher) anxiety.
+Moreover, frequent payment requirements may decrease welfare of highly impatient borrowers.\footnote{The paper presents an back of the envelope exercise that suggests annual discount rates of 4000 are necessary to nullify the reductions in financial cost we estimate.
+\hl{Note also that since the fee for skipping payment is 2\%, the iliquidity imposed by the contract is bounded.}} %Second, given the non-standard nature of the finding, it is likely that we would have to adopt and estimate a particular behavioral model of demand for commitment, which we don't need to do to make the point that TuT is positive.
+
+%we estimate that over 50\% of the borrowers in our study are naïve hyperbolics in the sense that they would benefit from commitment but will not choose it.
 While our results are driven by the intersection of overcollateralization and a potential selection of the borrower pool towards myopia and short-term financial thinking, these attributes are likely to be present in many types of pro-poor financial markets where individuals lack the credit histories to be able to leverage short-term credit without collateral.
-This suggests that regulators of such markets would do well to consider the broader financial costs of lending products, including what is paid through equilibrium default, and to consider imposing more structured lending products that tilt the scales towards allowing borrowers to repay.
+This suggests that regulators of such markets should include what is paid through equilibrium default as part of the financing cost (not done now), and to consider imposing structured lending products that tilt the scales towards allowing borrowers to repay.
 While commitment-style repayment contracts decrease effective liquidity by requiring faster repayment of a given loan, the improvement in expected borrower returns are so substantial as to prove welfare improving at all but the most astronomical discount rates.
 
-These conclusions speak to several strands of the literature.
-First, they suggest consequential ways in which different financial services draw client pools with distinct behavioral biases.
-While research in microfinance markets has not found the same benefits from providing a more regularized repayment environment \citep{Pande}, those experiments are performed over the top of highly structured contracts and among borrower pools who may have selected into that type of lending precisely because it provides structure.
-Second, we broaden the analysis of the extent to which voluntary commitment mechanisms are desirable.
-Like our study, commitment demand has been found to be low in a number of contexts (\cite{Ashraf}, \cite{Gine}, \cite{Ted}, \cite{Royer}, \cite{Sprenger}), and by illustrating a mechanism for the failure of self-commitment (over-optimism) we may help contextualize those studies in which demand has been found to be more robust (\cite{Kremer},  \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}, \cite{Pascaline}).
-Finally, we provide only the second case in the literature, and the first in the analysis of financial products, to illustrate the perverse result that those who opt into commitment are precisely the individuals who do not need it \citep{Sprenger}.
+Our paper speaks to several strands of the literature.   %First, they suggest consequential ways in which different financial services draw client pools with distinct behavioral biases. 
+First, to research in microfinance studying the effect of payment frequency.
+While research in microfinance markets has not found the same benefits from providing a more regularized repayment environment \citep{Pande}, those experiments are performed on top of highly structured contracts and among borrower pools who may have selected into that type of lending precisely because it provides structure.
+This may explain why there is almost no default in the control group in \citep{Pande}.
+Second, we broaden the analysis of the extent to which voluntary commitment mechanisms are taken up and effective.
+Like our study, commitment demand has been found to be low in a number of contexts (\cite{Ashraf}, \cite{Gine}, \cite{Ted}, \cite{Royer}, \cite{Sprenger}).
+Other papers have found more robust demand for commitment (\cite{Kremer},  \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}, \cite{Pascaline}).
+But unlike all these papers we can point identify the benefit the non-takers would have had if they had taken up and the benefit for the takers, and thus can talk more rigorously about private paternalism in this context.
+
+%Finally, we provide only the second case in the literature, and the first in the analysis of financial products, to illustrate the perverse result that those who opt into commitment are precisely the individuals who do not need it \citep{Sprenger}.
+
+Two recent papers that shed some light into private paternalism.
+In the context of food choice, \cite{Sprenger} elicit dynamic inconsistencies, and then find that demand for commitment is negatively correlated with such inconsistency.
+In the context of school choice, \cite{Walters} finds that students that select into more effective schools have smaller treatment effects from attending than those that select out.
+Besides being very different contexts from ours, we rely on very different methods.
+In contrast to \cite{Sprenger} we will directly point identify the TuT, obviating the need for elicitation of preferences to test for negative selection.
+In contrast to \cite{Walters} we use randomization while he needs a structural model and distance to school as an instrument.
+\hl{FRANK, can I say something more precise than ``a structural model''?}
+
+Methodologically we contribute to the large literature on treatment effect heterogeneity by showing how an experimental design with two forcing arms and one choice arm allows for identification of the ToT, the TuT and other important parameters under minimal assumptions.
+\cite{aronow2013beyond} and \cite{angrist2013extrapolate} assume no selection on gains to estimate \hl{XXX}.
+\cite{Walters} achieve identification of the TuT by using parametric model and a distance instrument, which requires the model to be correct and the instrument to be valid.
+TUT and ATE implied by LATE-and-re-weight differ sharply from his model-based estimates.
+The method of
+\cite{heckman2007econometric} and \cite{cornelissen2018benefits} require the availability of instrumental variable with rich support, and separability of observed and unobserved determinants of treatment effects.
 
@@
 The importance of this monthly payment was made salient in the contract and payment receipts (see Figure \ref{PaperSlip}), and by the levying of a nominal fee (2\% of minimum due) on individuals who fell behind in their payments.
-The propose of the small fee was to mainly to make the structured schedule salient, not to be a large disincentive to be late.
-Transportation cost to go to the branch to pay is on the same order of magnitude as the fee in average.\footnote{The lender was worried that if the fee was large, forgetting to pay could make the pawn unrecoverable.
+The idea that the fee itself is not driving the treatment is reinforced later in the paper where we show financial benefits many times larger than the fee, as well as treatment effects even on those who would fail to recover pawns and hence not pay the fee.
+Transportation cost to go to the branch to pay is on the same order of magnitude as the fee on average.\footnote{%The lender was worried that if the fee was large, forgetting to pay could make the pawn unrecoverable.
 In contrast with \cite{John} we don't let the clients choose the size of the fee.
@@
 The administrative data contains a unique identifier for each client, an identifier for the piece she is pawning, and the transactions relating to that piece.
-In particular, the value of the item as assessed by the appraiser, the amount of money loaned (70\% of the value), the date of the pawn transaction, and the type of contract for that pawn.
+These transactions include the value of the item as assessed by the appraiser, the amount of money loaned (70\% of the value), the date of the pawn transaction, and the type of contract for that pawn.
 Within the period of the loan, we followed each transaction related to that piece in the administrative data: when payments were made and for what amounts, whether there was default (i.e.\ the client lost her pawn), and whether any late-payment fees were imposed.
@@
 
+\paragraph{Who chooses commitment?}
+
+we estimate a flexible model of take-up of the commitment-fee contract \textit{in the Choice arm} using gradient boosting classification\footnote{Results are robust to other classification methods like Random Forest, SVM, etc.} and obtain for a client with characteristics $x_i$ a calibrated probability $P(x_i)$ of choosing the commitment contract.
+
 \paragraph{Balance.} Table \ref{SS} presents summary statistics for the sample of actual borrowers across arms, and illustrates that randomization worked to achieve balance across clients in the different experimental arms.
@@
 
-\section{Average Treatment Effects} \label{experiment}
-
-We start by estimating average treatment effects for those assigned to the Forced commitment and the Choice arms, compared to those assigned to the Control group.
+\section{Average Treatment Effects} 
+\label{experiment}
+
+We begin by estimating average treatment effects of assignment to the Forced commitment and the Choice arms, relative to those assigned to the Control arm.
 As we explain below, only about \hl{XXX\%} of those in the choice arm chose the monthly payment option.
@@
 where $i$ indexes client, $j$ indexes branch, $T_{i}^F$ and $T_{i}^C$ are indicator variables for receiving the Forced or Choice arms, $X_{ij}$ are branch and day-of-week fixed effects.
-Standard errors are clustered at the branch-day level, the unit of treatment assignment\footnote{A minority of clients pawned on more than one day during the experiment.
+Standard errors are clustered at the branch-day level, the unit of treatment assignment\footnote{A minority of clients pawned on more than one day during the experiment: 15\% pawned on two distinct days, and 7.5\% on three or more days.
 To avoid contamination from earlier treatments to which these individuals were exposed, we restrict our sample to each client's \emph{first visit}.
@@
 Columns (2) and (7) of Table \ref{table_robustness_fc} use the subjective value of the pawn reported by the borrower rather than its appraised value.
-Columns (3) and (8) adjust for self-reported transport costs per visit plus an entire day's wage, both multiplied by the number of individual visits\footnote{For clients who did not complete the individual survey, we adjust using the mean self-reported transport cost among respondents of the respective branch.}.
-Columns (4) and (9) adjust for our measure of liquidity cost.
+Columns (3) and (8) adjust for self-reported transport costs per visit plus an entire day's wage, both multiplied by the number of visits that each individual made.\footnote{For clients who did not complete the individual survey, we adjust using the mean self-reported transport cost among respondents of the respective branch.} Columns (4) and (9) adjust for our measure of liquidity cost.
 Finally columns (5) and (10) include all three changes together.
@@
 %Those in the choice arm are 4\% more likely to pawn again and is not statistically distinct from zero.
-While this appears to be \emph{prima facie} evidence of greater satisfaction, the interpretation is complicated by the fact that monthly payments may themselves trigger more borrowing to pay them.
+While this appears to be \emph{prima facie} evidence of greater satisfaction among borrowers in the forced arm, the interpretation is complicated by the fact that monthly payments may themselves trigger more borrowing to pay them.
 This is unlikely to be the case given that the effect on re-pawning comes after 90 days (during the period of contract demanded payments) and not before  (see columns 2 and 3).
@@
 
+\subsubsection{Bounding the Distribution of Individual Treatment Effects}
+
+If we knew the distribution $F_\Delta$ of individual treatment effects $\Delta_i \equiv Y_{i1} - Y_{i0}$, it would be easy assess how many individuals would win and lose under paternalism, along with the magnitude of any individual harm.
+%simply calculate $\mathbbm{P}(\Delta_i < 0)$.
+Because we can never observe both $Y_{i0}$ and $Y_{i1}$ for the same borrower, $F_\Delta$ cannot be identified. 
+It can, however, be bounded. 
+%Using these bounds, we now show that more than \hl{11\%} of individual borrowers benefit from commitment.
+Because it randomly assigns borrowers to the control and forced arms, our experimental design point identifies the marginal distributions of $Y_{i0}$ and $Y_{i1}$, call them $F_0$ and $F_1$.
+Now, define the functions $\underline{F}$ and $\overline{F}$ as follows:
+\[
+\underline{F}(\delta) \equiv \max \left\{0, \sup_y F_1(y) - F_0(y - \delta)  \right\}, \quad
+\overline{F}(\delta) \equiv 1 + \min \left\{0, \inf_y F_1(y) - F_0(y-\delta) \right\}.
+\]
+Since $F_0$ and $F_1$ are point identified, so are $\underline{F}$ and $\overline{F}$.
+\cite{fan2010sharp} show that the sharp (best possible) pointwise bounds for $F_\Delta$ are given by $\underline{F}(\delta) \leq F_\Delta(\delta) \leq \overline{F}(\delta)$
+These bounds are simple to compute, and can be surprisingly informative. 
+Here we use them to bound the fraction of borrowers who benefit from commitment. 
+Given the way that we have defined our outcome variables, this is the share of borrowers whose treatment effect is \emph{positive}, i.e.\ $1 - F_\Delta(0)$. 
+To construct the sharp bounds for this quantity, we simply substitute $\delta = 0$ into the preceding equations and estimate $F_0$ and $F_1$ using their empirical analogues constructed from the forced commitment and forced no-commitment arms of the experiment.
+
+Figure \ref{fig:FanPark} plots the sharp bounds for $F_{\delta}$ based on the APR outcome defined above in Section \ref{costs}.
+Our point estimates of $\underline{F}(0)$ and $\overline{F}_0$ are \hl{XXXX} and \hl{XXXX} respectively, with associated 95\% confidence intervals of \hl{XXXX} and \hl{XXXX}.\footnote{Confidence intervals are constructed using \hl{XXXX} bootstrap.
+See \cite{fan2010sharp} for details.}
+%\todo[inline]{Issac: add in the confidence interval at $\delta = 0$ along with the figure \ref{fan_park_bounds}.
+These need to be the results that do not use covariates and we need to be careful about the sign convention for our effects.
+Frank follow-up to add 1-2 sentences discussing the results.
+Presumably we find that $F_\Delta(0) > 0.11$ this means that at least some people who choose not to commit \emph{must} be making a mistake, although we don't know who they are and this doesn't tell us how large the mistake is.}
+An alternative way of presenting the \cite{fan2010sharp} bounds is in terms of quantiles of the distribution of $\Delta$.
+Let $0 < q < 1$, and define $Q_0, Q_1, Q$ to be the quantile functions corresponding to $F_0, F_1$ and $F_\Delta$.\footnote{In other words, $Q_0(q) \equiv \inf \{x | F(x) \geq q\}$ and so on.} Then the sharp bound for $Q_\Delta(q)$ is given by $\underline{Q}(q) \leq Q(q) \leq \overline{Q}(q)$ where
+\[
+\overline{Q}(q) \equiv \inf_{u \in [q,1]} [Q_1(u) - Q_0(u - q)], \quad
+\underline{Q}(q) \equiv \sup_{u\in [0,q]} [Q_1(u) - Q_0(1 + u - q)]
+\]
+By substituting $q = 0.11$, these expressions allow us to bound the 11th percentile of the distribution of $\Delta$.
+Under a stylized Roy model in which borrowers with the largest (negative) treatment effects choose commitment, $Q(0.11)$ equals the treatment effect for the borrower at the margin of indifference between choosing commitment.
+Our point estimates for the lower and upper bounds $\underline{Q}(0.11)$ and $\overline{Q}(0.11)$ are \hl{XXXX} and \hl{XXXX} with corresponding 95\% confidence intervals \hl{XXXX} and \hl{XXXX}.\footnote{Again, confidence intervals are constructed using \hl{XXXX} bootstrap as describe in \cite{fan2010sharp}.}
+%\todo[inline]{Issac: add the interval for $Q(0.11)$.
+Again, this needs to be without covariates and we need to be careful about the sign convention for our effects.
+Maybe we don't need a second figure with the confidence bands for the whole quantile function.
+Frank: add a sentence or two discussing the results.
+Presumably the aforementioned quantile is indeed negative and fairly large.}
+Both ways of presenting the bounds yield the same conclusion: at least some borrowers who would benefit from commitment \emph{do not choose it} when offered.
+
 \subsection{Potential Outcomes and Exclusion}
@@
 Equation \ref{eq:exclusion1} implies that every chooser experiences the same potential outcome when assigned to the treatment arm as when assigned to the choice arm. 
-Mathematically \eqref{eq:exclusion0} and \eqref{eq:exclusion0} have the same structure as the standard LATE exclusion restriction that $Y_i(d,z)$ depends only on $d$, not on $z$. 
+Mathematically \eqref{eq:exclusion0} and \eqref{eq:exclusion0} have the same structure as the standard TOT or LATE exclusion restriction that $Y_i(d,z)$ depends only on $d$, not on $z$. 
 Substantively, however, they are slightly different as there is no analogue of the ``chosen'' versus ``forced'' treatment distinction in the usual LATE setting.\footnote{See \cite{chamberlain2011bayesian}, who uses an assumption very similar to our exclusion restrictions to develop a theory of optimal treatment choice for an individual who has access to data from an RCT.}
@@
 Moreover, each has testable implications that we fail to reject: see Appendix \ref{append:exclusion} for details.
-Under \eqref{eq:exclusion}, each participant's observed outcome $Y_i$ is related to her potential outcomes $(Y_{i0}, Y_{i1})$ according to
+Under \eqref{eq:exclusion0} and \eqref{eq:exclusion1}, each participant's observed outcome $Y_i$ is related to her potential outcomes $(Y_{i0}, Y_{i1})$ according to
 \begin{equation}
@@
 %\subsection{Treatment Effect Heterogeneity}
-
-\subsection{Bounding the Distribution of Treatment Effects}
-\todo[inline]{Unless I'm missing something obvious, this section does not rely on the exclusion restriction. We should think of a way to highlight this.}
-As seen above in Section \ref{experiment}, the average treatment effect of forced commitment is economically and statistically significant. 
-Using the notation of Section \ref{sec:potentialOutcomes}, our estimate of $\mathbbm{E}[Y_{i1} - Y_{i0}]$ is positive: commitment lowers financial costs overall.\footnote{Recall from above that in this section we define all outcome variables so that beneficial treatment effects are \emph{positive}.}
-But this is only an average effect.
-The ATE could still be negative if the individual treatment effects $\Delta_i = Y_{i1} - Y_{i0}$ are zero or positive for most people in the experiment.
-Perhaps commitment is extremely helpful for a small minority of borrowers, and slightly harmful for everyone else.
-Can this explanation rationalize the very low take-up rate of commitment in the choice arm (\hl{11\%}) along with the ATE of commitment estimated from the forced arm? 
-We could easily answer this question if the distribution $F_\Delta$ of individual treatment effects $\Delta_i$ were known: simply calculate $\mathbbm{P}(\Delta_i < 0)$.
-But because we can never observe both $Y_{i0}$ and $Y_{i1}$ for the same person, $F_\Delta$ cannot be identified. 
-It can, however, be bounded. 
-Using these bounds, we now show that more than \hl{11\%} of individual borrowers benefit from commitment.
-
-As explained above, our experimental design identifies the marginal distributions of $Y_{i0}$ and $Y_{i1}$, call them $F_0$ and $F_1$.
-Now, define the functions $\underline{F}$ and $\overline{F}$ as follows:
-\[
-\underline{F}(\delta) \equiv \max \left\{0, \sup_y F_1(y) - F_0(y - \delta)  \right\}, \quad
-\overline{F}(\delta) \equiv 1 + \min \left\{0, \inf_y F_1(y) - F_0(y-\delta) \right\}.
-\]
-Since $F_0$ and $F_1$ are point identified, so are $\underline{F}$ and $\overline{F}$.
-\cite{fan2010sharp} show that the sharp (best possible) pointwise bounds for $F_\Delta$ are given by $\underline{F}(\delta) \leq F_\Delta(\delta) \leq \overline{F}(\delta)$
-These bounds are simple to compute, and can be surprisingly informative. 
-Here we use them to bound the fraction of borrowers who benefit from commitment. 
-Given the way that we have defined our outcome variables, this is the share of borrowers whose treatment effect is \emph{positive}, i.e.\ $1 - F_\Delta(0)$. 
-To construct the sharp bounds for this quantity, we simply substitute $\delta = 0$ into the preceding equations and estimate $F_0$ and $F_1$ using their empirical analogues constructed from the forced commitment and forced no-commitment arms of the experiment.
-
-Figure \ref{fig:FanPark} plots the sharp bounds for $F_{\delta}$ based on the APR outcome defined above in Section \ref{costs}.
-Our point estimates of $\underline{F}(0)$ and $\overline{F}_0$ are \hl{XXXX} and \hl{XXXX} respectively, with associated 95\% confidence intervals of \hl{XXXX} and \hl{XXXX}.\footnote{Confidence intervals are constructed using \hl{XXXX} bootstrap.
-See \cite{fan2010sharp} for details.}
-%\todo[inline]{Issac: add in the confidence interval at $\delta = 0$ along with the figure \ref{fan_park_bounds}.
-These need to be the results that do not use covariates and we need to be careful about the sign convention for our effects.
-Frank follow-up to add 1-2 sentences discussing the results.
-Presumably we find that $F_\Delta(0) > 0.11$ this means that at least some people who choose not to commit \emph{must} be making a mistake, although we don't know who they are and this doesn't tell us how large the mistake is.}
-An alternative way of presenting the \cite{fan2010sharp} bounds is in terms of quantiles of the distribution of $\Delta$.
-Let $0 < q < 1$, and define $Q_0, Q_1, Q$ to be the quantile functions corresponding to $F_0, F_1$ and $F_\Delta$.\footnote{In other words, $Q_0(q) \equiv \inf \{x | F(x) \geq q\}$ and so on.} Then the sharp bound for $Q_\Delta(q)$ is given by $\underline{Q}(q) \leq Q(q) \leq \overline{Q}(q)$ where
-\[
-\overline{Q}(q) \equiv \inf_{u \in [q,1]} [Q_1(u) - Q_0(u - q)], \quad
-\underline{Q}(q) \equiv \sup_{u\in [0,q]} [Q_1(u) - Q_0(1 + u - q)]
-\]
-By substituting $q = 0.11$, these expressions allow us to bound the 11th percentile of the distribution of $\Delta$.
-Under a stylized Roy model in which borrowers with the largest (negative) treatment effects choose commitment, $Q(0.11)$ equals the treatment effect for the borrower at the margin of indifference between choosing commitment.
-Our point estimates for the lower and upper bounds $\underline{Q}(0.11)$ and $\overline{Q}(0.11)$ are \hl{XXXX} and \hl{XXXX} with corresponding 95\% confidence intervals \hl{XXXX} and \hl{XXXX}.\footnote{Again, confidence intervals are constructed using \hl{XXXX} bootstrap as describe in \cite{fan2010sharp}.}
-%\todo[inline]{Issac: add the interval for $Q(0.11)$.
-Again, this needs to be without covariates and we need to be careful about the sign convention for our effects.
-Maybe we don't need a second figure with the confidence bands for the whole quantile function.
-Frank: add a sentence or two discussing the results.
-Presumably the aforementioned quantile is indeed negative and fairly large.}
-Both ways of presenting the bounds yield the same conclusion: at least some borrowers who would benefit from commitment \emph{do not choose it} when offered.
 
@@
 In practice, instrumental variables are usually discrete and, even when continuous, typically have a more modest effect on take-up.}
-An alternative approach aims to avoid structural assumptions by calculating conditional local average treatment effects (LATE) given observed covariates $X$ and reweighting these according to the distribution of $X$ in some population of interest \citep{aronow2013beyond,angrist2013extrapolate}.
+An alternative approach aims to avoid structural assumptions by calculating conditional local average treatment effects (LATE) given observed covariates $X$ and re-weighting them according to the distribution of covariates in some population of interest to yield, for example, an average treatment effect \citep{aronow2013beyond,angrist2013extrapolate}.
 %For example, one might re-weight using the distribution of $X$ in the population as a whole, rather than the sub-population of compliers, to extrapolate from LATE to ATE. 
@@
 
-\paragraph{Rough outline based on Craig's email and our conversations: 2023-02-16}
-\begin{enumerate}
-    \item What is the economic explanation for our results from above and what implications do they have for policy?
-Can discounting explain the low take-up of commitment despite its clear benefits, even to those who don't choose it?
-No: see Figure OA-5.
-Remaining exercises will use baseline survey data.
-Explain why we think this is ok: treatment effects don't change much when restricting the sample.
-(Refer to tables)
-    \item Does present bias (hyperbolic discounting) explain the results?
-Cite some literature here about why it might matter.
-Questions 10 and 29 from our survey allow us to construct a dummy variable $H$ for present bias: prefer 100 pesos tomorrow rather than 150 in a month, but prefer 150 pesos in four months rather than 100 pesos in three months.
-This isn't a perfect measure but it's standard in the literature.
-(Citations).
-If present bias explains the results, then ``sophisticated'' people with $H = 1$ will choose commitment, but there doesn't seem to be any correlation between $H$ and $C$ in the choice arm.
-Moreover, if present bias explains the results, the ATE for $H=0$ should be zero (or negative) but it's large and positive.
-Compare it to the ATE for $H=1$.
-(add discussion of Craig's regression: regress outcome on forced, hyperbolic and interaction).
-    \item Another possible explanation is \emph{overconfidence}.
-Cite some literature about why and how it might matter.
-Survey question 2 elicits the subjective probability that borrowers will recover their pawn.
-We use this to construct an individual-level measure of overconfidence.
-Using data for the control group, we build a model to predict recovery based on covariates \emph{excluding} question 2.
-Why the control group?
-When completing the baseline survey borrowers don't know anything about the commitment contract, so we have elicited their recovery probability under the status quo contract.
-We compare the elicited probability to the predicted recovery probability for each person, given her covariates.
-For borrowers in the control group, we leave out their own observation when constructing these predictions.
-(Possibly overkill given our sample size but worth checking anyway.) We define overconfidence as the difference of elicited minus predicted recovery probability.
-There is a lot of over-confidence: plot the distribution.
-Are overconfident people more likely to choose commitment?
-How do treatment effects vary with overconfidence?
-Here the leave-one-out aspect is very important to prevent there from being a ``mechanical'' relationship.
-Variant of Craig's suggested regression from above?
-Fan regression?
-    \item Now talk about paternalism.
+\subsection{Why is paternalism working in this context?}
+\label{why_paternalism}
+
+The behavioral literature has highlighted voluntary commitment as an attractive way of allowing the `right' people to self-select.
+A discussion of compulsory commitment is necessarily paternalistic, and by its nature focuses on impacts among those who would not have selected commitment voluntarily.
+From the lens of rational choice it is unsurprising that we find the $\text{ToT}>\text{TuT}$, but the argument for compulsory treatment centers on the more  surprising result that we find $\text{TuT}>0$.
+Hence an investigation of the case for paternalism requires that we delve into understanding why individuals who should apparently have chosen the intervention did not do so.
+
+Discounting is one explanation for our results.
+Using no discounting we find a decrease in the financial cost of credit, but the intervention inherently imposes up-front costs (early payment) in return for delayed benefits (recovery of pawn).
+Highly impatient individuals might therefore rationally choose not comply although our measure would show a benefit for them.
+To investigate this we can calculate the Net Present Value of the $TUT$ on financial cost given the average timing of repayment and pawn recovery at different discount rates.
+Figure \ref{fc_discount_rates} shows the results of this exercise, illustrating that non-choosers continue to see significant decreases in NPV financial costs up to monthly discount rates of 40\%, and the NPV remains negative for rates up to 90\% per month.
+Given that only 30\% of the sample reports a monthly discount rate above 50\%, we think that discounting is unlikely to explain non-compliance among those who appear to benefit.
+
+%Remaining exercises will use baseline survey data. Explain why we think this is ok: treatment effects don't change much when restricting the sample.
+
+If commitment benefits among non-compliers cannot be explained by rational choice, the canonical behavioral story would center on time inconsistency.
+While commitment is useful to anyone with hyperbolic time preferences, only those who are sophisticated will demand it.
+A large share of naive hyperbolics in the population could therefore drive a large $TUT$.
+Our baseline survey included standard questions about discount rates between today and a month in the future versus discount rates between three and four months in the future.
+This allows us to classify borrowers who display more impatience over immediate delays as time inconsistent.
+This measure of financial hyperbolicity is widely used in survey research, although it is not without problems.\footnote{Our measure is dichotomous, and is not incentivized.
+Recent empirical work has shown the superiority of more sophisticated measures such as Convex Time Budgets \citep{andreoni2015measuring} as well as questioning the interpretation of measures of hyperbolicity not based on consumption \citep{andreoni2012estimating, cohen2020measuring}, suggesting that real effort tasks provide a better measure \citep{augenblick2015working}.
+Given that we had only a few minutes to interview real pawnshop clients prior to a commercial transaction, our simple measure was a necessary compromise.}
+
+If measurement of hyperbolicity were perfect, the sample should then be comprised of three groups:  the sophisticated hyperbolics who chose commitment, the time-consistent non-compliers (for whom forcing will not be effective) and the naive hyperbolic non-compliers (for whom it will).
+This would imply that the forcing effect should arise entirely from within hyperbolic non-compliers, a fact which can be checked by estimating the $TUT$ conditional on hyperbolicity.
+
+We can calculate the relative contributions of any two groups $X_i=1$ or $X_i=1$ to the TUT among the non-compliers as follows:
+
+    \begin{align*}
+        1=& \frac{\mathbb{E}[Y_{1i}-Y_{0i} | D_i=0, X_i=1]}{TuT}\Pr(X_i=1 | D_i=0) \\
+        \quad &+ \frac{\mathbb{E}[Y_{1i}-Y_{0i}| D_i=0, X_i=0]}{TuT}\Pr(X_i=0 | D_i=0)
+    \end{align*}
+
+If, as theory would predict, the $TUT$ arises solely from hyperbolics then the former term will be 1 and the latter 0.
+
+A second behavioral explanation may arise from the fact that  \hl{XX\%} of the control participants believe they have a 100\% chance of recovering their pawn, while in truth only 56\% will do so.
+This suggests a market characterized by over-optimism.
+Incorrect expectations about recovery probabilities can explain low take-up in that individuals who believe they will repay are rationally uninterested in incurring costs to induce repayment.
+Hence over-optimistic expectations in recovery probabilities will translate directly into under-adoption of preventive measures.
+Similar to the definition of hyperbolicity above, we define a binary attribute we call `sure-confidence' which is individuals who say at the time of borrowing that they have a 100\% probability of recovering the loan.
+
+Figure \ref{tut_beh_partition} shows the relative contributions of present bias and sure-confidence for the $TUT$, and Figure \ref{tot_beh_partition} the analagous contributions for the $TOT$.
+In each figure the orange bar represents the contribution from those who do not possess the attribute, and the blue bar from those that do.
+Looking first at the $TUT$, we see that the forcing effect is localized mostly to those who are \textit{not} time inconsistent, contradicting naive hyperbolicity as the justification for paternalism.
+Instead, we see sure-confidence being a category that completely isolates the $TUT$, suggesting that forcing works for those who do not consider repayment structure because they don't think they need it.
+Turning to the $TOT$, sure-confidence reverses its contribution in an intuitive way:  having chosen the intervention, it is mostly those who understand they may not repay that benefit.\footnote{The contribution of present bias to the $TOT$ is hard to parse in that we might expect the compliers to be entirely sophisticated hyperbolics.
+This attribute is strongly correlated with compliance, but the TOT is mostly generated by the time consistent among choosers.}  Our measure of hyperbolicity is based on unincentivized responses in a short survey and so is likely to be noisy; nonetheless we see no evidence here that it drives the forcing effect.
+Rather, this analysis suggests that paternalism is effective in this case is because of a group of overconfident borrowers who, heedless of the possibility of default, do not choose commitment and yet would benefit substantially from receiving it.
+
+\subsection{Who are the winners and losers from paternalism?}
+
+%Moving more deeply into heterogeneity in treatment effects, we can try to understand the gains or losses from forcing at the individual level.
+To investigate this, we first use completely flexible non-parametric bounds, then add structure on to the individual heterogeneity via a random forest estimation, and finally we consider the optimal targeting of forced compliance.
+
+As shown above in Section \ref{experiment}, the ATE of the commitment contract from the forced arm is positive and significant, both economically and statistically.
+But this is only an average effect: a positive ATE is still consistent with negative individual treatment effects for some borrowers. 
+Unless she is a strict utilitarian, any policymaker who is considering outlawing the \emph{status quo} contract in favor of the commitment contract needs to consider the extent and magnitude of harm that such a paternalistic policy will cause to \emph{individual} borrowers.
+Our TuT and ToT results from Section \ref{sec:randchoice} partially address this concern.
+In particular, our TuT estimates show that even those borrowers on whom a policy of paternalism would impose a binding constraint stand to benefit, on average, from commitment.
+Again, however, this is only an average effect: a positive TuT is perfectly consistent with negative treatment effects for \emph{some} of the untreated.
+This section takes a closer look at treatment effect heterogeneity, to better understand the gains and losses from a policy of forced commitment at the individual.
+First, we explore heterogeneity in the average effects reported in Sections \ref{experiment} and \ref{sec:randchoice} using random forests.
+Then we consider the problem of optimal targeting: how accurately can we determine which kinds of borrowers would benefit from commitment, based on their observed characteristics?
+
+%Now talk about paternalism.
 First, are people learning?
@@
 Do we see any interesting patterns?
-\end{enumerate}
-
-\todo[inline]{Old stuff below...}
-\paragraph{Causal forest heterogeneous treatment effects.}
-
-\hl{Here we will put Athey' stuff}
+
+\subsubsection{Random Forest Bounds on Treatment Effects}
 
@@
 
-\paragraph{Who chooses commitment?}
-
-we estimate a flexible model of take-up of the commitment-fee contract \textit{in the Choice arm} using gradient boosting classification\footnote{Results are robust to other classification methods like Random Forest, SVM, etc.} and obtain for a client with characteristics $x_i$ a calibrated probability $P(x_i)$ of choosing the commitment contract.
-
-\hl{To be completed}
-
+\begin{comment}
 \subsection{Marginal Treatment Effects}
@@
 One could also combine (1) and (2) or use (1) as a specification test for (2).}
-
-\begin{comment}
 

### 2023-04-20 presentation.tex
changes after presentation(s)...rewriting of text

%\documentclass[handout, 8pt]{beamer}
\documentclass[8pt]{beamer}

%\usetheme{Singapore}
%\usefonttheme{serif} 
\input{preambleBeamer.tex}

\title{The Controlled Choice Design and Paternalism in Pawnshop Borrowing? \\
Preliminary --comments welcome}
\author{Craig McIntosh\inst{1} \and Isaac Meza\inst{2} \and Joyce Sadka\inst{3} \and Enrique Seira\inst{4} \and Francis J. DiTraglia\inst{5} }
\institute[UTran]{\inst{1} UCSD, \inst{2} Harvard , \inst{3} ITAM , \inst{4} MSU , \inst{5} Oxford}

\date{April 2023}

%\setbeamercolor{section in head/foot}{bg=darkcrimsonred}
\setbeamersize{text margin left=11pt, text margin right=11pt}
%\setbeamertemplate{section in toc}[square]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{frame}[c, noframenumbering]%{\phantom{title page}}
% The \phantom{title page} is a kludge to get the red bar on top
\titlepage
\end{frame}

\section{Motivation}

\begin{frame}{Motivation: Private paternalism}
\begin{itemize}
    \vfill \item Many institutions —firms, schools, financial contracts— restrict choice using built-in commitment mechanisms which help workers, students, borrowers overcome self-control problems
    \begin{itemize}
        \item Loans with fixed repayment schemes, homework due dates, etc.
    \end{itemize}
    \vfill \pause\item At the same time these firms hide these forcing mechanisms and don’t market their commitment features, potentially because demand for them is low.
    \vfill  \item  Laibson (2018) argues that clients that benefit from commitment may underestimate its value, and that in such cases private paternalism (i.e. allocating them to commitment) could be beneficial.
    \vfill  \pause\item  \textbf{We study the (a) benefits of imposing a structured repayment contract on financing cost, (b) whether there is demand for such structure, and (c) whether non-takers of such a commitment product would benefit from taking it.}
\end{itemize}

\end{frame}

\section{Context}

\begin{frame}{Context}
\begin{columns}
\begin{column}{.45\textwidth}
\begin{figure}[H]
    \begin{center}
    \caption{Pawnshop}
        \includegraphics[width=0.95\textwidth]{Figuras/empenio2.png}
    \end{center}
    \end{figure}
\begin{figure}[H]
    \begin{center}
    \caption{Appraisers  inside a pawnshop}
        \includegraphics[width=0.95\textwidth]{Figuras/empenio9.png}
    \end{center}
    \end{figure}    
    \end{column}
\begin{column}{.45\textwidth}
\begin{figure}[H]
    \begin{center}
    \caption{Waiting for appraisal}
        \includegraphics[width=0.95\textwidth]{Figuras/empenio11.png}
    \end{center}
    \end{figure}
\begin{figure}[H]
    \begin{center}
    \caption{Lost pawns which are for sale}
        \includegraphics[width=0.95\textwidth]{Figuras/empenio3.png}
    \end{center}
    \end{figure}    
    \end{column}    
    \end{columns}
\end{frame}

\begin{frame}{Context}
\begin{itemize}
    \vfill \item Pawn loans involve borrowers leaving valuable liquid assets as collateral in exchange for an immediate cash loan
    \vfill \pause \item The loan is overcollateralized (loan is 70\% of appraised value) and collateral is liquid.
    \begin{itemize}
        \item The lender approves loans in a few minutes without income or credit history check $\rightarrow$ used for emergencies.
    \end{itemize}
  \vfill \pause \item Because the loan is overcollateralized and collateral is liquid, the lender may gain if the borrower defaults on the loan, especially if the borrower pays towards recovery on the way to default.
    \vfill \pause  \item Among those that lose their pawn (60\%), 48\% paid a positive amount towards its recovery and on average paid 42\% of loan.
    \vfill      \item This happens in spite (or because?) of 74\% of borrowers reporting a 100\% subjective probability recovery ex-ante. 
    %\vfill   \item 13\% of borrowers are classified as present biased using the simple standard question.
     \vfill \pause    \item In such an environment, one may ask if putting more structure/committment in payments may help borrowers recover their pawn.
     \vfill \pause    \item Not only that: Will the structure/commitment be demanded by all (or most) people who benefit?

\end{itemize}
\end{frame}

\section{Contribution}

\begin{frame}{Methodological Contribution}
\begin{itemize}
 %\vfill \item A context of particular interest to behavioral literature:  the demand for commitment in financial contracts (Laibson 1997, Bryan et al. 2010), and many more.

   \vfill   \item Key quantity in debate about paternalism:  impacts on those who wouldn't elect to take the program versus impacts on those that do.  %How do treatment effects relate to selection?

    %Broadly speaking there are two approaches: the structural approach and the reduced form approach.

    %The structural approach combines instruments with a generalized Roy model and uses behavioral and statistical restrictions to extrapolate the causal effects for different sub-populations

    %The structural approach allows both selection on unobservables and selection on gains at the cost of modeling these channels. In contrast, the reduced form approach assumes that there is no selection on gains after conditioning on a set of covariates

    \vfill \item  Large literature TE heterogeneity: \begin{itemize}
        \item LATE-and-reweight:  Aronow \& Carnegie (2013); Angrist \& Fernandez Val (2013). \alert{Assume no selection on gains}
        \item Structurally model selection:  Walters (2018) \alert{Need their parametric models to be correct}.
        %TUT and ATE implied by LATE-and-re-weight differ sharply from his model-based estimates
        \item MTE: Heckman \& Vytlacil MTE; Cornelissen et. al. (2018). \alert{Need instrumental variable with rich support, and separability of observed and unobserved determinants of TE.}
        %\item Brinch et. al. (2017) - discrete $Z$ but under some additivity restrictions on the MTE curve
        %\item Mogstad, Santos \& Torgovitsky (2018) - No parametric form assumption on MTE curve but only partial identification.
    \end{itemize}

    \vfill \item Our ``Controlled Choice'' design point identifies a number of relevant TE with mild assumptions
    \begin{itemize}
        \item Because we have two forcing-arms and a choice arm, we can use one IV to get at ToT, and a second IV to get at TuT.
    \end{itemize}

   \vfill  \item Consider winners and losers from paternalism.

%   \vfill \pause  \item Three-arm design:  Control, Choice (voluntary takeup=ITT), Forcing (universal=ATE).  We illustrate how to use standard exclusion restrictions to point identify:
%     \begin{itemize}
%         \item Treatment on the Treated (ToT) and 
%         \item Treatment on the Untreated (TUT), also
% 	\item Average Selection on Gains, Average Selection Bias, and Average Selection on Levels
%     \end{itemize}

\end{itemize}
\end{frame}

\section{Outline}
\begin{frame}{Outline}
     \begin{itemize}
         \vfill\item \textbf{Experimental Design}
         \vfill\item Main results
         \vfill\item Paternalism (...working on it)
     \end{itemize}
\end{frame}

\section{Design}

\begin{frame}{Pawn contract}
    \begin{figure}[H]
    \label{ExplanatoryMaterial}
    \begin{center}
        \includegraphics[width=0.45\textwidth]{Figuras/sq_contract.png}
    \end{center}
\end{figure}
\end{frame}

\begin{frame}{Structured payments contract}
   \begin{itemize}
       \vfill \item We designed a new contract that is identical to the status quo contract except that it enhances the regularity and salience of payments as a way to encourage repayment.
         \begin{figure}[H]
    \label{ExplanatoryMaterial}
    \begin{center}
        \includegraphics[width=0.40\textwidth]{Figuras/fc_contract.png}
    \end{center}
\end{figure}

   \end{itemize}

\end{frame}

% \begin{frame}{Structured payments contract}
%   \begin{itemize}

%       \vfill\item The purpose of the small fee was to mainly to make the structured schedule salient, not to be a large disincentive to be late. 
%       \begin{itemize}
%           \item Transportation cost to go to the branch to pay is on the same order of magnitude as the fee in average.
%       \end{itemize}
%       \vfill\item  The empirical literature provides some guidance that such a contract may decrease default and elicit demand.
%       \begin{itemize}
%           \item Field \& Pande (2008) find null effects of payment frequency on loan default for group lending (but samples are small and there is almost no default in the control).

%         \item  Bauer et al. (2012) estimate a positive correlation between measured present bias and selecting into microfinance, which they interpret as demand for structured payments.
%       \end{itemize}

%   \end{itemize}

% \end{frame}

\begin{frame}{Data}
\label{data}
\begin{itemize}
    \item Administrative data: 1 month before and 8 months after the experiment ended
    \begin{itemize}
        \item Unique identifier for each client and each pawn.
        \item Value of the item, money loaned (70\%), date of pawning
        \item For all payments: date and amounts
        \item Fees incurred
        \item Whether the client lost the pawn, renewed the contract
    \end{itemize}

    \vfill \item Survey data
    \begin{itemize}
        \item During experiment, we asked clients to complete a 5-minute survey before going to the teller window to appraise their piece and before treatment status was known to them.
        \item Demographics, proxies for income/wealth, education, present-biased preferences, experience pawning, if family or friends commonly asked for money, cost of going to branch, the subjective probability of recovering, the subjective value, etc.
    \end{itemize}
\end{itemize}    
\end{frame}

\begin{frame}{Main outcomes: financial cost and default}
\label{fc_outcome}
\begin{itemize}
    \item We are interested in measuring the financial cost of borrowing, which very saliently includes the cost of defaulting on the loan and losing the pawn.
    \item We will measure loan default using an indicator $\mathds{1}(\text{Default}_i)$, and the cost in pesos using the following definition that capture borrower outlays:
\end{itemize}

   \begin{equation*}
    \text{Financial Cost}_i =  \underbrace{\sum_t P^i_{it}}_{\text{Pay to Interest}} + \underbrace{\sum_t P^f_{it}}_{\text{Pay to Fees}}  + \mathds{1}(\text{Default}_i) \times \left[\text{Pawn Val}_i + \underbrace{\sum_t P^c_{it}}_{\text{Pay to Capital}} \right]
   \end{equation*}

\vspace{.2in}
\: \: \: \: APR: equivalent yearly interest generated by sum of payments:
   \begin{equation*}
    (\text{APR})_i =\left( 1 + \frac{\frac{\text{Financial Cost}_i}{\text{Appraised Value}_i}}{\text{loan term}_i}\right)^{\text{loan term}_i}-1 
\end{equation*}

   \vspace{.2in}
\begin{itemize}
    \item We \alert{will not talk about welfare}, only financial cost.
    \begin{itemize}
        \item Welfare would depend on reduced liquidity, anxiety from monthly payments, cost of going to branch, etc. We don't observe these.
    \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}{Treatment arms}
\label{treatment_arms}
   \begin{itemize}
    \vfill \item Randomization at the branch-day level.  Analysis at the pawn level.
    \begin{itemize}
        \vfill \item Control arm (1770 obs)
       \vfill \item Forced Commitment arm (1954 obs)
       \vfill \item Choice Commitment arm (2580 obs)
    \end{itemize}
    \vfill \item The existence of a choice arm allows us not only to measure if there is demand for such a contract, but who demands it, not only in demographic terms, but in terms of potential treatment effects (which include unobservables).
   \vfill \item  This design is innovative and critical for our purposes, as it enables us to explore whether or not forcing people into a structured payment contract could be more beneficial than allowing choice for a significant fraction of them.
\end{itemize}
\end{frame}

% \begin{frame}{Description}
% \label{consort}
% \begin{figure}[H]
%      \caption{Experiment description}
%     \label{exp_description}
% \begin{center}
%         \includegraphics[width=0.80\textwidth]{Figuras/consort.pdf}
%   \end{center}
% \end{figure}
% \hyperlink{experimental_integrity}{\beamerbutton{Details}}

% \end{frame}

\begin{frame}{Experimental integrity}
\label{experimental_integrity}
    \begin{table}[H]
\caption{Attrition table}
\label{attrition_table}
\begin{center}
\small{\input{./Tables/Attrition.tex}}
\end{center}
\end{table}
\end{frame}

\begin{frame}{Balance and Summary statistics}
    \begin{table}[H]
%\caption{Summary statistics and Balance}
\label{SS}
\begin{center}
\resizebox{.65\textwidth}{!}{
\scriptsize{\input{./Tables/SS.tex}}
}
\end{center}
%\textit{Do file: } \texttt{ss\_att.do}
\end{table}
% \hyperlink{data}{\beamerbutton{Back}}
\end{frame}

\begin{frame}{Outline}
     \begin{itemize}
         \vfill\item Experimental Design
         \vfill\item \textbf{Main results}
         \vfill\item Paternalism (...working on it)
     \end{itemize}
\end{frame}

\section{Main Results}
\begin{frame}{Main results: ITT}
\label{main_results}

\begin{itemize}
    \item Financial cost reduced by \$379 pesos (20\% of mean). That is: charging fee + structure \textit{decreased} cost.
    \item Default decreases by 6.5pp (15\% of mean).
    \item APR decreases by 34 points, from mean of 184.
\end{itemize}
\vspace{.3in}
\begin{table}[H]
\begin{center}
\resizebox{0.95\textwidth}{!}{
\small{\input{./Tables/decomposition_main_te_pres1.tex}}
}
\end{center}
\end{table}

   \vfill 
  \hyperlink{several_def_cost}{\beamerbutton{More}}

\end{frame}

\begin{frame}{Intermediate outcomes: forced-commitment}
\label{intermediate_outcomes}
 \begin{itemize}
     \item \vfill \textbf{Speed of payment:} The first payment of the forced commitment contract  occurs 13 days earlier, increasing the fraction who recover on the first visit by 7.9 pp. Conditional on recovering, they recover 28 days faster.

    \item \vfill \textbf{Separating those who will not pay:} Commitment contract decreases fraction of borrowers making a payment and \textit{not} recovering by 7pp.
    \begin{itemize}
        \item Actually, among those that default, those in the forced commitment arm are 14pp less likely to have paid towards recovery. They also visit the branch less: as if the commitment contract makes them realize they will end up losing pawn anyway, and stop paying early on.
    \end{itemize}
    \end{itemize}

   \vfill

   \hyperlink{mechanism_appendix}{\beamerbutton{Details}}
\end{frame}

\section{Paternalism}
\begin{frame}{Choice and Heterogeneous Treatment Effects}
\label{choice_hte}
    \begin{itemize}
    \vfill \item  So, forcing commitment decreases APR dramatically.

    \vfill \item \textbf{Low demand:} In spite of this, given the opportunity, only 11\% of borrowers chose commitment.   
    \begin{itemize}
       \pause \item If the effect of commitment were homogeneous, this would be enough to conclude that the 89\% who did not choose it would have been financially better off if they had.
       \item However, we test and reject the null hypothesis of homogeneous treatment effects (Chernozhuvok et. al. 2018).
    \end{itemize}

    \vfill \item The borrowers who did not choose commitment could simply be those who don’t need it?
    \pause \vfill \ item The distribution of TE (i.e. $Y_{1i}-Y_{0i}$) is not identified, as one person is only observed in one treatment. However, it can be bounded using the two marginal dist $F_1$ and $F_0$. \hyperlink{fan_park_bounds}{\beamerbutton{Fan \& Park bounds}}
    \vfill \item \textbf{Many with benefits did not demand:} We find that at least 30\% of individual borrowers benefit from commitment $\implies$ many did not demand even though TE is positive for them.
    \vfill \item Given our 3-armed experiment (+ imposing a mean exclusion restriction) allow us to estimate average TuT$>0$. %Furthermore, imposing the restriction for each cell of covariates and using Causal Forests gets us $F_{TUT}^{-1}(0.72)>0$.
    \end{itemize}
\end{frame}

\begin{frame}{Identification afforded by experiment}

\vspace{.2in}
Notation: 
\begin{itemize}
    \item Potential outcomes $(Y_0,Y_1,C)$
    \item Assignment: $Z \in \{0,1,2\}$, i.e. \{SQ,Com,Choice\}.  
    \item Treatment: $D \in \{0,1\} $, i.e. \{SQ,Com\}.
\end{itemize}

\vspace{.2in}
Assumptions:

\begin{itemize}
    \item $Z \independent (Y_0,Y_1,C)$, achieved by randomization
    \item $D = \mathbbm{1}(Z_i \neq 2) Z + \mathbbm{1}(Z_i=2) C$, i.e. \alert{being assigned to a contract has same effect as choosing it} (e.g. used in compulsory school attendance and returns to schooling lit).
\end{itemize}

\vspace{.2in}
Therefore:
\begin{itemize}
    \item  $Y_i = \mathbbm{1}(Z_i =0) Y_{i0} + \mathbbm{1}(Z_i = 1)  Y_{i1}  + \mathbbm{1}(Z_i = 2) \left[(1 - C_i) Y_{i0} + C_i Y_{i1} \right].$
\end{itemize}

\vspace{.2in}
Prop:
\begin{itemize}
    \item ToT := $\mathbbm{E}(Y_{i1} - Y_{i0} | C_i = 1)$ is point-identified, and equals $\frac{\mathbbm{E}(Y_i|Z_i=2) - \mathbbm{E}(Y_i|Z_i =0)}{\mathbbm{E}(D_i|Z_i=2)} $
     \item TuT := $\mathbbm{E}(Y_{i1} - Y_{i0} | C_i = 0)$ is point-identified, and equals $\frac{\mathbbm{E}(Y_i|Z_i=1) - \mathbbm{E}(Y_i|Z_i =2)}{1-\mathbbm{E}(D_i|Z_i=2)} $
     \item Also identified: $ASG:=ToT-TuT$, $ASB:= \E[Y_0 | C=1]-\E[Y_0 | C=0]$, and $ASL:= \E[Y_1 | C=1]-\E[Y_1 | C=0]$. 
\end{itemize}
\end{frame}

\begin{frame}{The ``Controlled Choice'' Design}
\label{cc_design}
\begin{itemize}
    \item Recall that under one-sided non-compliance (no always-takers), LATE=ToT.
\end{itemize}
\vspace{.2in}
\begin{figure}[H]
    \begin{center}
        \centering
        \includegraphics[width=1.0\textwidth]{Figuras/tot_tut_intuition.png}
    \end{center}
\end{figure}   
 \vfill
\hyperlink{identification_randomized_choice}{\beamerbutton{Identification}}
\end{frame}

\begin{frame}{On avg. those that do not choose would benefit: TuT $>$ 0}
\begin{itemize}
    \vfill \item Commitment increases average financial benefit even for the subset of borrowers who \alert{don't choose to commit voluntarily}.
    \vfill \item Coefficient ToT>TuT, but cannot reject equality due to large s.e. in ToT.
    \vfill \item Results hold when imputing transport cost and lost wages per visit, and charge interest in amount paid (as a proxy for liquidity lost).
\end{itemize}
\vspace{.2in}
\begin{table}[H]
%those who are most likely to benefit from it and those whose outcomes are most adverse under the status quo.
\label{tot_tut}
\begin{center}
\small{\input{./Tables/tot_tut_pres1.tex}}
\end{center}
\end{table}
\end{frame}

% Despite substantial treatment effect heterogeneity, most borrowers would experience higher financial benefits under a commitment contract : $F_{\operatorname{TUT}}^{-1}(0.72)>0$

\begin{frame}{Effects on clients coming back}

\begin{itemize}
    \item Client forced into commitment is 20\% more likely to come back again and pawn.
    \item Not mechanically from having recovered the pawned, since also pawn other pieces.
    \item Not within the life of the loan, but after. So unlikely that is a liquidity story.
    \item Conditional on recovery (endogenous), ``effect'' twice as big.
\end{itemize}

\vspace{.2in}
\begin{table}[H]
\begin{center}
\footnotesize{\input{./Tables/repeat_loans.tex}}
\end{center}
\end{table}    
\end{frame}

\begin{frame}{Learning}
    \label{learning_table}
    \begin{itemize}
    \item  Do people learn from Forced exposure to the program that they benefit from it?  
    \vspace{.1in}
    \item  Small sample (small power): focus on those that, after being either forced to commitment contract or to status quo, come back within a few months and are subject to choice arm.
    \vspace{.1in}
    \item  \textbf{No learning?} We don't find that being forced to the commitment contract makes them more likely to voluntarily chose commitment later.
    %\vfill \item Are people learning? \hyperlink{learning_table}{\beamerbutton{Table}}
 \end{itemize}  
 \vspace{.2in}
\begin{table}[H]
\begin{center}
\small{\input{./Tables/learning_exp_pres.tex}}
\end{center}
\end{table}
 %\hyperlink{learning}{\beamerbutton{Back}}
\end{frame}

\begin{frame}{Fraction that forgo benefit}

\vspace{.4in}
    \centering Working on this...
\end{frame}

\begin{frame}{If commitment works, why don't people choose it?}
    \begin{itemize}
        \onslide<1>{\item Discounting}
        \onslide<2-3>{\item Present-Bias}
    \end{itemize}
\vfill
\only<1>{  
 \begin{itemize}
 \item Can impatience explain why not take up a contract that decreases overall cost?
     \end{itemize}
\begin{figure}[H]
        \caption{Financial cost for different discount rates}
    \label{fc_discount_rates}
    \begin{center}
        \centering
        \includegraphics[width=0.50\textwidth]{Figuras/discount_effect_tut.pdf}
    \end{center}
\end{figure}   
    \begin{itemize}
    \item   Commitment contract imposes up-front costs for later benefits (collateral recovery).

    \item  Requires an interest rate > 4,000\% to make NPV TuT insignificant. 
    \end{itemize}
}

\only<2>{

    \begin{itemize}
    \item   Standard behavioral angle:  compliers are sophisticated time-inconsistent, non-compliers are a mix of naifs and the time consistent (who don't need commitment).  
    \end{itemize}
\begin{figure}[H]
    \begin{center}
        \centering
        \includegraphics[width=0.65\textwidth]{Figuras/hyperbolicity_strata.png}
    \end{center}
\end{figure}   
    \begin{itemize}
    \item We have a survey measure of time inconsistency taken at baseline.
    \item  Effect of forcing commitment should be entirely among the time-inconsistent.  Is this true?  No, but PB measure may not be good.
    \end{itemize}
}

\only<3>{

    \begin{itemize}
    \item   We estimate the TuT conditional on $X_i=1 or X_i=1$ (say $X_i= PB_i$ or $=Confidence_i$) and see which subpouplations have larger TuT.

\vspace{.3in}
    \begin{align*}
        1=& \frac{\mathbb{E}[Y_{1i}-Y_{0i} | D_i=0, X_i=1]}{TuT}\Pr(X_i=1 | D_i=0) \\
        \quad &+ \frac{\mathbb{E}[Y_{1i}-Y_{0i}| D_i=0, X_i=0]}{TuT}\Pr(X_i=0 | D_i=0)
    \end{align*}

%and we will say that the variable $B_i$ explains the ToT whenever one of the terms (ratio weighted by the probability) is statistically significant from zero, (close to one), and the other term is statistically zero.
    \end{itemize}
}
\end{frame}

\begin{frame}{Possible Behavioral explanations : TuT \& ToT by groups}

\begin{itemize}
    \item The TuT effect is concentrated on those that say they have 100\% of recovery. This is what we would expect if the Sure-confident don't demand because they think they don't need it (but are wrong).
    \item Also on those with no PB (as measured by us).
\end{itemize}
\begin{columns}
\begin{column}{.45\textwidth}
    \begin{figure}[H]
    \caption{TuT}
        \includegraphics[width=1.1\textwidth]{Figuras/tut_beh_partition.pdf}
\end{figure}
\end{column}

\begin{column}{.45\textwidth}
    \begin{figure}[H]
    \caption{ToT}
        \includegraphics[width=1.1\textwidth]{Figuras/tot_beh_partition.pdf}
\end{figure}
\end{column}
\end{columns}
\end{frame}

\begin{frame}{Predictors of take-up : $\Pr(Take-up)$}

\begin{figure}[H]
    \begin{center}
        \includegraphics[width=0.9\textwidth]{Figuras/determinants_takeup_reg.pdf}
    \end{center}
    \end{figure}
\end{frame}

\section{Conclusion}
\begin{frame}{Conclusion}
    \begin{itemize}
     \vfill \item Laibson has spoken of `veiled paternalism' in contexts where principals desire reliability; here we have a case of `veiled non-paternalism' where features encouraging default might be embedded.
     \vfill \item Novel design to study essential heterogeneity: ``Controlled Choice''
        %\begin{itemize}
         %   \item Combine ``Controlled Choice'' with MTE: Can we extend results of Mogstad et al (2017) to use our ATE, TUT, and TOT as additional inequality restrictions that constrain partial identification bounds for MTEs?
        %\end{itemize}
        \vfill \item  APR reduced by 34\% in the commitment arm
        \vfill  \item Results suggest selection on gains, but still large effects of imposing commitment on non-takers.
        \vfill \item Mystery of low take-up combined with large TuT seems best explained by sure-confidence among pawnshop customers.

        %\vfill \item   Are those with a greater experience of pawning less sure-confident?  
        \vfill \item Suggests mandated commitment-based contract structures in payday/pawnshop loans as a form of pro-poor regulation?
        \vfill\item Finally:  how to target and who would be hurt if we instituted  paternalism?

    \end{itemize}  
\end{frame}

\appendix

\section{Appendix}

\begin{frame}{Appendix}
\vfill \centering APPENDIX
\end{frame}

\begin{frame}{Difference number in pawns}
    \[Pawns \: per \: day_{jt} = \alpha_j + \gamma f(t) + \beta_b \mathbbm{1}(t \in MB)_{t} +\beta_a \mathbbm{1}(t \in MA)_{t}\]

    \begin{table}[H]
\caption{Number of pawns balance before and after the experiment}
\label{num_pawns_bal}
\begin{center}
\small{\input{./Tables/num_pawns_bal.tex}}
\end{center}
\end{table}

\hyperlink{consort}{\beamerbutton{Back}}
\end{frame}

\begin{frame}{Histogram of payments}

\begin{columns}
\begin{column}{.33\textwidth}
    \begin{figure}[H]
    \caption{Status-quo}
    \begin{center}
        \includegraphics[width=\textwidth]{Figuras/hist_payments_sq.pdf}
    \end{center}
\end{figure}
\end{column}

\begin{column}{.33\textwidth}
    \begin{figure}[H]
    \caption{Forced commitment}
    \begin{center}
        \includegraphics[width=\textwidth]{Figuras/hist_payments_fc.pdf}
    \end{center}
\end{figure}
\end{column}

\begin{column}{.33\textwidth}
    \begin{figure}[H]
    \caption{Choice commitment}
    \begin{center}
        \includegraphics[width=\textwidth]{Figuras/hist_payments_cc.pdf}
    \end{center}
\end{figure}
\end{column}
\end{columns}

    \hyperlink{treatment_arms}{\beamerbutton{Back}}
\end{frame}

\begin{frame}{Distribution of financial cost (\$MXN)}
    \begin{figure}
     \centering
        \includegraphics[width=.8\textwidth]{Figuras/hist_fc.pdf}
    \end{figure}

    \hyperlink{fc_outcome}{\beamerbutton{Back}}

\end{frame}

\begin{frame}{Appraiser FE}
\label{clerk_fe}
\begin{table}[H]
\begin{center}
\resizebox{0.95\textwidth}{!}{
\small{\input{./Tables/clerk_fe.tex}}
}
\end{center}
 \scriptsize

%\textit{Do file: } \texttt{clerk\_fe.do}
\end{table}
    \hyperlink{main_results}{\beamerbutton{Back}}

\end{frame}

\begin{frame}{Several definitions of cost}
\label{several_def_cost}
\begin{table}[H]
\caption{Effects on several definitions of cost}
\label{table_robustness_fc}
\begin{center}
\resizebox{0.95\textwidth}{!}{
\small{\input{./Tables/fc_robustness_pres.tex}}
}
\end{center}
 \scriptsize

%\textit{Do file: } \texttt{fc\_robustness.do}
\end{table}
    \hyperlink{main_results}{\beamerbutton{Back}}

\end{frame}

\begin{frame}{Survival Graph}
   \label{interpolation_censoring_imp}

\begin{columns}
\begin{column}{.45\textwidth}

\begin{figure}[H]
    \begin{center}
    \caption{Ended}
        \includegraphics[width=1.1\textwidth]{Figuras/survival_graph_ended.pdf}
    \end{center}
    \end{figure}

    \end{column}

\begin{column}{.45\textwidth}

\begin{figure}[H]
    \begin{center}
    \caption{Recovery}
        \includegraphics[width=1.1\textwidth]{Figuras/survival_graph_unpledge.pdf}
    \end{center}
    \end{figure}

    \end{column}    
    \end{columns}
\end{frame}

\begin{frame}{Censoring}
\label{censoring}
    \begin{table}[H]
\caption{Bounding censoring}
\label{bounding_censoring}
\begin{center}
\resizebox{0.9\textwidth}{!}{
\footnotesize{\input{./Tables/censoring_imp_pres.tex}}
}
\end{center}
 \scriptsize 
%\textit{Do file: } \texttt{censoring_imp.do, censoring_imp_pr.do}
\end{table}

\end{frame}

\begin{frame}{Interpolation on bounding censoring}

\begin{figure}[H]
        \caption{Significance area for Default}

    \begin{center}
        \includegraphics[width=0.75\textwidth]{Figuras/frontera_sig_def_imp.pdf}
    \end{center}
\end{figure}
 \hyperlink{main_results}{\beamerbutton{Back}}
\end{frame}

% \begin{frame}{Contract terms}

% \begin{figure}[H]
%      \caption{Contract Terms Summary}
%     \label{PaperSlip}
%     \begin{center}
%         \includegraphics[width=0.65\textwidth]{Figuras/TicketLenderP.png}

%     \end{center}

% \end{figure}
% \end{frame}

\begin{frame}{Intermediate outcomes}
\label{mechanism_appendix}

\begin{table}[H]
\caption{Intermediate outcomes}
\begin{center}
\footnotesize{\input{./Tables/mechanism1_pres.tex}}
\end{center}
\end{table}
\vfill
\hyperlink{intermediate_outcomes}{\beamerbutton{Back}}
\end{frame}

\begin{frame}{Intermediate outcomes}

\begin{table}[H]
\caption{Intermediate outcomes}
\begin{center}
\footnotesize{\input{./Tables/mechanism2_pres.tex}}
\end{center}
\end{table}
\vfill
\hyperlink{intermediate_outcomes}{\beamerbutton{Back}}
\end{frame}

\begin{frame}{Intermediate outcomes}

    \begin{table}[H]
\caption{Intermediate outcomes}
\begin{center}
\footnotesize{\input{./Tables/mechanism3_pres.tex}}
\end{center}
\end{table}
\vfill
\hyperlink{intermediate_outcomes}{\beamerbutton{Back}}
\end{frame}

\begin{frame}{Bounding Individual Treatment Effects}
\label{fan_park_bounds}

\begin{figure}[H]
    \caption{Fan \& Park bounds for benefit in effective FC }

    \begin{center}
        \includegraphics[width=0.75\textwidth]{Figuras/fan_park_bounds_fc_admin.pdf}
    \end{center}

\end{figure}
 \hyperlink{choice_hte}{\beamerbutton{Back}}
\end{frame}

\begin{frame}{Identification of treatment parameters}
\label{identification_randomized_choice}
\begin{equation*}
    Y_i = \mathbbm{1}(Z_i =0) Y_{i0} + \mathbbm{1}(Z_i = 1)  Y_{i1}  + \mathbbm{1}(Z_i = 2) \left[(1 - C_i) Y_{i0} + C_i Y_{i1} \right].
\label{eq:potentialOutcomes}
\end{equation*}

    Viewing $Z_i$ as an instrumental variable, the randomized choice design can be interpreted as a \emph{pair} of RCTs, each subject to one-sided non-compliance. \\
    \begin{itemize}
        \item The first of these compares $Z_i=0$ to $Z_i = 2$.  This setting is identical to a ``randomized encouragement'' design in which treatment is only available to those who are encouraged: $Z_i = 2$. Under this interpretation, those with $C_i = 1$ are ``the compliers'' and it follows that 
\begin{equation*}
\frac{\mathbbm{E}(Y_i|Z_i=2) - \mathbbm{E}(Y_i|Z_i =0)}{\mathbbm{E}(D_i|Z_i=2)-\mathbbm{E}(D_i|Z_i=0)}  = \mathbbm{E}(Y_{i1} - Y_{i0}|C_i = 1)
\label{eq:ToT}
\end{equation*}

\item The second considers $Z_i = 1$ to be the ``encouragement'' and compare the outcomes for these individuals to those with $Z_i = 2$.
\begin{equation*}
\frac{\mathbbm{E}(Y_i|Z_i=1) - \mathbbm{E}(Y_i|Z_i =2)}{\mathbbm{E}(D_i|Z_i=1)-\mathbbm{E}(D_i|Z_i=2)}  = \mathbbm{E}(Y_{i1} - Y_{i0} | C_i = 0)
\label{eq:TuT}
\end{equation*}

\item Because non-compliance is one-sided only, LATE=ToT in one case (since treated=compliers+always takers, but there are no always takers, as they cannot take without being assigned) and LATE=TuT in the other.

\end{itemize}
\hyperlink{cc_design}{\beamerbutton{Back}}

\end{frame}

\end{document}

### 2023-05-02 OA.tex
cdf analysis of tut(x)

@@
 \begin{figure}[H]
-    \caption{Partitoin of TuT \& ToT effect by behavioral variables.}
+    \caption{Partition of TuT \& ToT effect by behavioral variables.}
     \label{tut_beh_partition}
@@
     \begin{subfigure}{0.45\textwidth}
-        \caption{with Fee Arm}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/pago_frec_vol_fee_interactions_rf.pdf}
+        \caption{PLM}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/determinants_takeup_reg.pdf}
     \end{subfigure}
     \begin{subfigure}{0.45\textwidth}
-        \caption{with Promise Arm}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/pago_frec_vol_promise_interactions_rf.pdf}
+        \caption{Logit}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/determinants_takeup_logit.pdf}
     \end{subfigure}
@@
      \scriptsize
-      %\footnotesize{ \textit{Do file: }  \texttt{analyze\_fvp.do}}
+      %\footnotesize{ \textit{Do file: }  \texttt{determinants_takeup.do}}
 \end{figure}
@@
 \scriptsize 
-\noindent This figure reports bivariate regressions of the form $\widehat{TakeUp} = \alpha + \beta \: X_i + \epsilon_i$, where $\widehat{TakeUp}$ is the prediction using random forests.
+\noindent This figure reports bivariate (and multivariate) regressions of the form $TakeUp = \alpha + \beta \: X_i + \epsilon_i$.
 The figure reports the $\beta$ coefficients for different $X_i$'s along with 95\% confidence intervals.
-Panel (a) focuses on take up in the arm where clients could chose among the fee-commitment contract and the status quo contract.
-Panel (b) focuses on the arm where clients could chose among the promise-commitment contract and the status quo contract.
-Using random forests we can predict who takes up the fee-forcing contract with 85\% accuracy out of sample.\footnote{Correcting for the fact that most chose the status-quo contract using the method of SMOTE, \cite{smote} we find an accuracy rate of 75\%.} Which suggests that choice among contracts is not purely random.
-This figure shows that the more educated, those that report that their family typically asks for money, those that make a monthly budget of expenses, and those that ask for a remainder of their due payments (and marginally those we classify as present-biased) are more likely to chose the fee-commitment contract if given the choice.
-The opposite holds for clients that are more economically vulnerable (can barely pay for food, electricity, etc) and those that report being more stressed.
+Panel (a) uses a linear model.
+Panel (b) specifies a logit model.
 

### 2023-05-02 donde.tex
cdf analysis of tut(x)

@@
 
-\title{The limits of self-commitment and private paternalism \thanks{We want to thank Mauricio Romero and Anett John for advice and encouragement.
+\title{The controlled choice design and private paternalism in pawnshop borrowing\thanks{We want to thank Mauricio Romero and Anett John for advice and encouragement.
 Ricardo Olivares, Gerardo Melendez, and Alonso de Gortari provided excellent research assistance and Erick Molina helped with formatting.
-Jose Maria Barrero, Andrei Gomberg, Emilio Gutierrez, David Laibson, Aprajit Mahajan, Matt Rabin, Charlie Sprenger, and seminar participants at ITAM provided valuable feedback.}}
+Jose Maria Barrero, Andrei Gomberg, Emilio Gutierrez, David Laibson, Aprajit Mahajan, Matt Rabin, Charlie Sprenger, and seminar participants at ITAM, USC, and UCSD provided valuable feedback.}}
 \author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira \and Francis J.\ DiTraglia   \thanks{Seira: ITAM/MSU, \url{enrique.seira@gmail.com} (corresponding author); McIntosh:  University of California San Diego, \url{ctmcintosh@ucsd.edu}; Meza: Harvard University, \url{isaacmezalopez@g.harvard.edu}; Sadka: ITAM, \url{jsadka@itam.mx}; DiTraglia: Oxford, \url{francis.ditraglia@economics.ox.ac.uk}} }
@@
 
-In the context of pawnbroker lending, we show that forcing people into commitment contracts with financial penalties for not paying on time \textit{decreases} their (fee-including) financial cost by 9.4\%, increases the likelihood of recovering their pawn by 26\%, and increases the likelihood of repeat business by almost 100\%.
+In the context of pawnbroker lending, we show that forcing people into commitment contracts with a regular repayment structure decreases their (fee-including) financial cost by 6\%, increases the likelihood of recovering their pawn by 15\%, and increases the likelihood of repeat business by 20\%.
+Using a multi-armed RCT that includes both a voluntary and a forced arm, we illustrate how to point-identify both the Treatment on the Untreated and the Treatment and the Treated.
+We find modest selection on gains but nonetheless significant positive benefits of commitment even for those who would not have chosen it.
+The justification for paternalistic commitment in this context appears to be over-optimism; 74\% of clients say they will certainly recover their pawn while in fact only 43\% do so.
+
+%In the context of pawnbroker lending, we show that forcing people into commitment contracts with financial penalties for not paying on time \textit{decreases} their (fee-including) financial cost by 9.4\%, increases the likelihood of recovering their pawn by 26\%, and increases the likelihood of repeat business by almost 100\%.
 Using machine learning methods for estimating heterogeneous treatment effects, we find that more than {70}\% clients would reduce their financing cost with the commitment contract, however only 10\% choose it.
@@
 
-Although the examples above are plausible, substantiating a case for private paternalism is not easy.
-It involves comparing the causal effect of forcing a certain product characteristic versus the effect of letting people choose on that characteristic.
-This is not an easy task because a given person wither has or does not have choice, and because choice induces selection, potentially biasing causal estimates.
-A large behavioral literature has illustrated that allocating borrowers to a commitment-savings product increase savings \citep{thaler2004save, prina2015banking, brune2016facilitating, callen2019headwaters, Pascaline, Ashraf}, but this literature does not show that commitment would not be chosen by those that would benefit from it, that is, that the Treatment Effect on the Untreated (TuT) is positive.
-In fact, selection on gains has such wide acceptance that economists often impose it in their models \hl{CITES}.
-In microfinance, a context close to ours, \citep{Murdoch} claim that there exists positive selection, citing a positive correlation between displaying present biased preferences in surveys and selecting into microfinance as evidence of borrowers' actually demanding the discipline imposed by frequent payments.
-However, they are unable to show that borrowers indeed benefit or that they indeed positively select based on treatment effects.
+Substantiating a case for private paternalism is not easy.
+It involves comparing the causal effect of forcing a certain product characteristic versus the effect of letting people choose it.
+This is not a straightforward task because choice will be driven by unobservable factors, and to address the question fully we would want a counterfactual for the outcome of both choosers and non-choosers.
+A large behavioral literature has illustrated that allowing borrowers or savers to choose commitment-style products increase savings in an Intention-to-Treat sense \citep{thaler2004save, prina2015banking, brune2016facilitating, callen2019headwaters, Pascaline, Ashraf}, but this literature has rarely inquired about the benefits of imposing commitment.\footnote{Selection on gains has such wide acceptance that economists often impose it in their models (for example, in the study of migration \cite{chiquiar2005international} and occupational choice \cite{heckman1990empirical}.
+In microfinance, a context close to ours, \citep{Murdoch} claims that positive selection exists, citing a positive correlation between displaying present biased preferences in surveys and selecting into microfinance as evidence of borrowers' actually demanding the discipline imposed by frequent payments.}   In this paper we illustrate how a three-armed, `controlled choice' design can be used to form counterfactuals for both choosers and non-choosers of commitment, providing a high-stakes and policy-relevant environment in which to test selection-on-gains as well as isolating the impact of paternalistic policies.
 
@@
 
-This paper studies the benefits of restricting choice in the context of pawnbroker lending.
+Here we study the benefits of private paternalism in the context of pawnbroker lending.
 Pawn loans are one of the oldest, most understudied, and most prevalent forms of borrowing \citep{carter2012pawnshops}.
@@
 
-The combination of voluntary and forced commitment within the RCT allows us to address several key questions.
+We call this randomization of voluntary and forced commitment a controlled choice design, and it allows us to address several key questions.
 First, does using more structured repayment contracts help pawnshop borrowers to save on financing cost.
 Second, do borrowers recognize this benefit, demanding commitment in sufficient numbers?
-Finally, and most uniquely, because we incorporate the forced commitment arm, we are able to ask whether the \textit{right} borrowers voluntarily demand commitment, gaining point identification for the Treatment on the Treated (ToT) and the Treatment on the Untreated (TuT), using the control, choice, and forced arms.
+Finally, and most uniquely, because we incorporate the forced commitment arm, we are able to ask whether the \textit{right} borrowers voluntarily demand commitment, gaining point identification for the Treatment on the Treated (ToT), the Treatment on the Untreated (TuT), and the average selection on gains.
 
@@
 Commitment contract decreases fraction of borrowers making a payment and not recovering by 7 percentage points.
-\hl{Treatment effects are concentrated in the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery.
-That is, the commitment contract induces people who would otherwise pay something towards recovery, to pay more and faster, making them more likely to recover their pawn at a lower financial cost.}
+Treatment effects are concentrated in the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery.
+Instead, the commitment contract induces people who would otherwise pay something towards recovery to pay more and faster, as well as inducing others who would have made partial payments and anyways defaulted to instead pay nothing.
+Both groups save money.
 
@@
 
-\hl{We start by bounding the distribution of treatment effects $Y_{1i}-Y_{0i}$ using the two marginal distribution } in the treatment and control arms as in \cite{fan2010sharp}.
-We find that at least 30\% of individual borrowers benefit from commitment, implying many borrowers did not demand even though the treatment effect would be positive for them.
-Then, we impose the mild exclusion restriction that the effect of the contract does not depend on how they got it, that is: choosing a contract has the same treatment effect as being assigned to the contract.\footnote{This is a frequently used assumption even if often implicit.
-For instance, a significant literature uses schooling compulsory laws to estimate the return of one more year of school, and then often interprets that schooling, in general, has this return.} We show that in this case our 3-armed experiment point identifies the TuT.
-We then estimate that the financial cost savings of the TuT is large, at \$356 pesos, equivalent to 24 percentage point savings in APR.
-That is, on average borrowers that did \textit{not} choose the frequent payment contract would have benefited from having that contract.\footnote{We estimate a positive ToT that is larger than the TuT, but it is imprecise\footnote{This results from the smaller sample size, given that few chose the monthly payment contract.}, and the hypothesis of ToT=TuT is rejeted only with 13 percent confidence for the APR and 12 percent confidence for default.}  We also estimate that those that would not choose if given the opportunity would have lower status-quo outcomes (i.e.
+We start by bounding the distribution of individual treatment effects as in \cite{fan2010sharp} and find that at least 30\% of individual borrowers benefit from commitment, implying many borrowers did not demand even though the treatment effect would be positive for them.
+Then, we impose the twin exclusion restrictions necessary for estimation of the ToT and Tut (that the effect of choosing or not choosing is the same as being assigned or not assigned the contract).\footnote{This is a frequently used assumption even if often implicit.
+For instance, a significant literature uses schooling compulsory laws to estimate the return of one more year of school, and then often interprets that schooling, in general, has this return.}  With these assumptions, both treatment effects are point identified as well as the average selection on gains, average selection on levels, and average selection bias.
+Our results indicate that while selection on gains are present in our sample, the financial cost savings of the TuT is still large (at \$356 pesos, it is equivalent to 24 percentage point savings in APR).
+Hence, on average borrowers that did \textit{not} choose the frequent payment contract would have benefited from having that contract.\footnote{While our estimated ToT is roughly twice the TuT, it is imprecisely estimated due to the low compliance rate, and the hypothesis of ToT=TuT is rejected only with 13 percent confidence for the APR and 12 percent confidence for default.}  We also estimate that those that would not choose if given the opportunity would have lower status-quo outcomes (i.e.
 the average selection bias is negative).
-Finally, assuming the exclusion restriction for subsets of observable characteristics splits generated by a causal forest allows us to establish that \hl{70\%} of would-be non-choosers would save on financial cost by being assigned to frequent payments.
+Finally, assuming the exclusion restriction for subsets of observable characteristics splits generated by a causal forest allows us to establish that more than \hl{70\%} of would-be non-choosers would save on financial cost by being assigned to frequent payments.
 That is, the benefits of imposing a monthly payment are distributed broadly.
@@
 
-\textcolor{brown}{In a final step, we use the Causal Random Forest algorithm of \cite{atheygrf} to estimate individual-level treatment effects for the forced versus control arm, and show the benefits of forcing to be significantly negatively correlated with the propensity to choose commitment estimated from the choice arm.
+%\textcolor{brown}{In a final step, we use the Causal Random Forest algorithm of \cite{atheygrf} to estimate individual-level treatment effects for the forced versus control arm, and show the benefits of forcing to be significantly negatively correlated with the propensity to choose commitment estimated from the choice arm.
 93\% of those who did not opt for the commitment contract would have been better off with it, while only 1\% of those who chose commitment would have been better off without it.} \textcolor{blue}{Targeting frequent payment products to those that benefit the most is a policy that should be explored.
@@
 What explains the persistence of a contract so contrary to borrowers’ interests?
-First, we show substantial levels of over-optimism among borrowers.
-Those most likely to benefit from the commitment contract and \textit{not} choose it are the individuals who most systematically over-estimate their own probability of repayment at the time of taking the loan.\footnote{More generally \hl{demand for commitment is higher among those with XXX characteristics.}}  Second, the existence of commitment-style repayment contracts in pawnshop lending is novel in Mexico.
+First, we investigate whether simple impatience could explain the dissonance (our formula for financial does not use discounting, and the contract features near-term costs in return for longer-term benefits).
+A simple simulation exercise suggests that at discount rates up to 4,000 percent per annum our core impacts on financial cost remains significantly negative, suggesting that discounting is unlikely to explain our results.
+Next, we look at time inconsistent preferences, the workhorse behavioral explanation for the benefits of commitment.
+In our context, not only is time inconsistency only a weak driver of selection into commitment, but the TuT of forcing commitment arises almost entirely among those who are \textit{not} time inconsistent.
+In this pawnbroking sample we document substantial levels of over-optimism among borrowers, the attribute which we believe explains our results.
+Not only do 74\% of borrowers say that they will recover their pawn with perfect certainty (whereas only 43\% actually do), but the impact of forcing on those who would not choose commitment is almost perfectly confined to the sub-sample who reported sure confidence in recovery.
+Hence, in this context it appears that the explanation for low demand for commitment among those who benefit arises from an incorrect belief that one has no need to work to avoid default.
+
+%Those most likely to benefit from the commitment contract and \textit{not} choose it are the individuals who most systematically over-estimate their own probability of repayment at the time of taking the loan.\footnote{More generally \hl{demand for commitment is higher among those with XXX characteristics.}}  Second, the existence of commitment-style repayment contracts in pawnshop lending is novel in Mexico.
 The dramatic improvements in borrower income arising from the commitment contract come directly from the pockets of lenders, reinforcing that the pawn industry as a whole has a strong interest in retaining the status quo.
 
+%do we want this paragraph on learning?
 Does learning eventually overcome the low demand for commitment?
 For learning to happen clients would need to experiment the frequent payment contract, and this was not the typical contract in the industry.
-But even if the contract was experienced, borrower may fail to learn or learn only slowly.
-We find that those who are forced to the monthly payment product are 6.7 percentage points more likely to become repeat costumers than those assigned to the status-quo contract.
+But even if the contract was experienced, borrowers may fail to learn or learn only slowly.
+We find that those who are forced to the monthly payment product are 6.7 percentage points more likely to become repeat customers than those assigned to the status-quo contract.
 One way to interpret this is that that having experienced the frequent payment contract (and the lower financial cost of borrowing that come with it), they want to borrow more.\footnote{A second intepretation is that the iliquidity created by the monthly payment contract makes them want obtain second loan to pay the first one.
@@
 
+%Replace this paragraph with discussion of optimal targeting of paternalism
 Our results suggest that pawn lending markets capture borrower wealth in ways not well summarized by interest rates.
-By overcollateralizing and then structuring loan contracts in a manner encouraging of default, lenders are able to extract substantial value independent of the interest charged.
+By over-collateralizing and then structuring loan contracts in a manner encouraging of default, lenders are able to extract substantial value independent of the interest charged.
 Further, the `nudge’ approach generally favored by the behavioral literature (voluntary commitment) may not be adequate.
@@
 
-Our paper speaks to several strands of the literature.   %First, they suggest consequential ways in which different financial services draw client pools with distinct behavioral biases. 
-First, to research in microfinance studying the effect of payment frequency.
+Our paper speaks to several strands of the literature.
+First, we contribute methodologically to the large literature on treatment effect heterogeneity by showing how an experimental design with two forcing arms and one choice arm allows for identification of the ToT, the TuT and other important parameters under minimal assumptions.
+A large literature inspired by \cite{heckman1979sample} and \cite{angrist1996identification} has used an exclusion restriction to instrument for the LATE; rarer are studies that have compared forcing to choice to instrument for the TUT (such as looking at compulsory high school requirements \citep{oreopoulos2006estimating}, and one at technology that defaults individuals into variable pricing of electricity \citep{fowlie2021default}.
+When the three arms (control, choice, and forcing) are randomized in the same environment we gain a clear and policy-relevant window into how selection into treatment relates to heterogeneity in treatment effects.
+This comparison of treatment effects across the compliance distribution is closely related to the evaluation of Marginal Treatment Effects, and hence speaks to the large observational literature using parametric assumptions and continuous instruments to estimate MTEs , such as \cite{heckman2007econometric} and \cite{cornelissen2018benefits}, and \cite{Walters}.
+
+%\cite{aronow2013beyond} and \cite{angrist2013extrapolate} assume no selection on gains to estimate \hl{XXX}.
+\cite{Walters} achieve identification of the TuT by using parametric model and a distance instrument, which requires the model to be correct and the instrument
+
+Second, we join a more nacent literature shedding light into private paternalism.
+In the context of food choice, \cite{Sprenger} elicit dynamic inconsistencies, and then find that demand for commitment is negatively correlated with such inconsistency.
+In the context of school choice, \cite{Walters} finds that students that select into more effective schools have smaller treatment effects from attending than those that select out.
+Besides being very different contexts from ours, we rely on very different methods.
+In contrast to \cite{Sprenger} we will directly point identify the TuT, obviating the need for elicitation of preferences to test for negative selection.
+In contrast to \cite{Walters} we use randomization while he needs a structural model and distance to school as an instrument.
+\hl{FRANK, can I say something more precise than ``a structural model''?}
+
+Finally, our results speak to the financial literature that examines the effect of contract structure on repayment.
 While research in microfinance markets has not found the same benefits from providing a more regularized repayment environment \citep{Pande}, those experiments are performed on top of highly structured contracts and among borrower pools who may have selected into that type of lending precisely because it provides structure.
@@
 %Finally, we provide only the second case in the literature, and the first in the analysis of financial products, to illustrate the perverse result that those who opt into commitment are precisely the individuals who do not need it \citep{Sprenger}.
-
-Two recent papers that shed some light into private paternalism.
-In the context of food choice, \cite{Sprenger} elicit dynamic inconsistencies, and then find that demand for commitment is negatively correlated with such inconsistency.
-In the context of school choice, \cite{Walters} finds that students that select into more effective schools have smaller treatment effects from attending than those that select out.
-Besides being very different contexts from ours, we rely on very different methods.
-In contrast to \cite{Sprenger} we will directly point identify the TuT, obviating the need for elicitation of preferences to test for negative selection.
-In contrast to \cite{Walters} we use randomization while he needs a structural model and distance to school as an instrument.
-\hl{FRANK, can I say something more precise than ``a structural model''?}
-
-Methodologically we contribute to the large literature on treatment effect heterogeneity by showing how an experimental design with two forcing arms and one choice arm allows for identification of the ToT, the TuT and other important parameters under minimal assumptions.
-\cite{aronow2013beyond} and \cite{angrist2013extrapolate} assume no selection on gains to estimate \hl{XXX}.
-\cite{Walters} achieve identification of the TuT by using parametric model and a distance instrument, which requires the model to be correct and the instrument to be valid.
-TUT and ATE implied by LATE-and-re-weight differ sharply from his model-based estimates.
-The method of
-\cite{heckman2007econometric} and \cite{cornelissen2018benefits} require the availability of instrumental variable with rich support, and separability of observed and unobserved determinants of treatment effects.
 

### 2023-05-02 presentation.tex
cdf analysis of tut(x)

@@
 
-\title{The Controlled Choice Design and Paternalism in Pawnshop Borrowing? \\
-Preliminary --comments welcome}
+\title{The Controlled Choice Design and Paternalism in Pawnshop Borrowing}
 \author{Craig McIntosh\inst{1} \and Isaac Meza\inst{2} \and Joyce Sadka\inst{3} \and Enrique Seira\inst{4} \and Francis J. DiTraglia\inst{5} }
@@
 
-   \vfill   \item Key quantity in debate about paternalism:  impacts on those who wouldn't elect to take the program versus impacts on those that do.  %How do treatment effects relate to selection?
+   \vfill   \item Key quantity in debate about paternalism:  impacts on those who wouldn't elect to take the program versus impacts on those that do.   \begin{itemize}
+       \item Oreopoulos 2006: effect of mandatory high school laws.
+       \item Fowlie et al. 2021: defaulting customers into variable electricity pricing.
+   \end{itemize}
+
+   %How do treatment effects relate to selection?
 
@@
          \vfill\item Main results
-         \vfill\item Paternalism (...working on it)
+         \vfill\item Paternalism
      \end{itemize}
@@
 
+\begin{frame}
+\textbf{Predictors of take-up : $\Pr(Take-up)$}
+
+\begin{figure}[H]
+    \begin{center}
+        \includegraphics[width=0.9\textwidth]{Figuras/determinants_takeup_reg.pdf}
+    \end{center}
+    \end{figure}
+\end{frame}
+
 \begin{frame}{Outline}
@@
          \vfill\item \textbf{Main results}
-         \vfill\item Paternalism (...working on it)
+         \vfill\item Paternalism 
      \end{itemize}
@@
 
+\begin{frame}{Fraction that forgo benefit}
+
+    \label{choose_wrong}
+
+        \begin{figure}{\textwidth}
+        \caption{Mistakes in choice arm}
+        \centering
+        \includegraphics[width=0.65\textwidth]{Figuras/line_cw_apr_tot_tut.pdf}
+        \end{figure}
+
+\begin{itemize}
+    \item   Use Random Forest to estimate ToT, TUT conditional on covariates.
+    \item $>$ 70\% of non-choosers would have seen some benefit from assignment to commitment.
+    \item  $<$ 20\% of choosers made a mistake.
+\end{itemize}
+
+\end{frame}
+
 \begin{frame}{Effects on clients coming back}
@@
  %\hyperlink{learning}{\beamerbutton{Back}}
-\end{frame}
-
-\begin{frame}{Fraction that forgo benefit}
-
-\vspace{.4in}
-    \centering Working on this...
 \end{frame}
@@
 \end{columns}
-\end{frame}
-
-\begin{frame}{Predictors of take-up : $\Pr(Take-up)$}
-
-\begin{figure}[H]
-    \begin{center}
-        \includegraphics[width=0.9\textwidth]{Figuras/determinants_takeup_reg.pdf}
-    \end{center}
-    \end{figure}
 \end{frame}

### 2023-06-08 donde.tex
targeting paternalism rules

@@
 Moreover, frequent payment requirements may decrease welfare of highly impatient borrowers.\footnote{The paper presents an back of the envelope exercise that suggests annual discount rates of 4000 are necessary to nullify the reductions in financial cost we estimate.
-\hl{Note also that since the fee for skipping payment is 2\%, the iliquidity imposed by the contract is bounded.}} %Second, given the non-standard nature of the finding, it is likely that we would have to adopt and estimate a particular behavioral model of demand for commitment, which we don't need to do to make the point that TuT is positive.
+\hl{Note also that since the fee for skipping payment is 2\%, the illiquidity imposed by the contract is bounded.}} %Second, given the non-standard nature of the finding, it is likely that we would have to adopt and estimate a particular behavioral model of demand for commitment, which we don't need to do to make the point that TuT is positive.
 
@@
 So the question remains: do the \hl{89\%} who do not choose commitment know something about their personal situations that we as researchers do not, or are most people in the choice arm making a costly mistake?
-In this section we now present a range of econometric exercises that shed light on this question, leveraging unique features of our experimental design. 
+In this section we present a number of econometric exercises that shed light on this question, leveraging unique features of our experimental design. 
 Despite substantial treatment effect heterogeneity, most borrowers would experience lower financial costs under a commitment contract. 
@@
 
-\subsubsection{Bounding the Distribution of Individual Treatment Effects}
-
-If we knew the distribution $F_\Delta$ of individual treatment effects $\Delta_i \equiv Y_{i1} - Y_{i0}$, it would be easy assess how many individuals would win and lose under paternalism, along with the magnitude of any individual harm.
-%simply calculate $\mathbbm{P}(\Delta_i < 0)$.
-Because we can never observe both $Y_{i0}$ and $Y_{i1}$ for the same borrower, $F_\Delta$ cannot be identified. 
+\subsection{Bounding the Distribution of Individual Treatment Effects}
+\label{sec:bounds}
+
+If we knew the distribution of individual treatment effects, it would be easy assess how many individuals would win and lose under a policy of universal forced commitment, along with the magnitude of any individual harm.
+Because we can never simultaneously observe the same borrower in both the control and commitment arms, however, the distribution of individual treatment effects cannot be point identified.
 It can, however, be bounded.
-%Using these bounds, we now show that more than \hl{11\%} of individual borrowers benefit from commitment.
+We begin our exploration of heterogeneous treatment effects by computing assumption-free bounds on the share of individuals who benefit from forced commitment.
+
+Let $Y_{i0}$ be borrower $i$'s potential outcome under the control condition, $Y_{i1}$ be her potential outcome under forced commitment, and $\Delta_i \equiv Y_{i0} - Y_{i1}$.
 Because it randomly assigns borrowers to the control and forced arms, our experimental design point identifies the marginal distributions of $Y_{i0}$ and $Y_{i1}$, call them $F_0$ and $F_1$.
@@
 These bounds are simple to compute, and can be surprisingly informative. 
-Here we use them to bound the fraction of borrowers who benefit from commitment. 
-Given the way that we have defined our outcome variables, this is the share of borrowers whose treatment effect is \emph{positive}, i.e.\ $1 - F_\Delta(0)$. 
+Here we use them to bound the fraction of borrowers who benefit from forced commitment. 
+Given the way that we have defined our outcome variables, this is the share of borrowers whose treatment effect is positive, i.e.\ $\mathbb{P}(\Delta_i > 0) = 1 - F_\Delta(0)$. 
 To construct the sharp bounds for this quantity, we simply substitute $\delta = 0$ into the preceding equations and estimate $F_0$ and $F_1$ using their empirical analogues constructed from the forced commitment and forced no-commitment arms of the experiment.
@@
 See \cite{fan2010sharp} for details.}
-%\todo[inline]{Issac: add in the confidence interval at $\delta = 0$ along with the figure \ref{fan_park_bounds}.
-These need to be the results that do not use covariates and we need to be careful about the sign convention for our effects.
-Frank follow-up to add 1-2 sentences discussing the results.
-Presumably we find that $F_\Delta(0) > 0.11$ this means that at least some people who choose not to commit \emph{must} be making a mistake, although we don't know who they are and this doesn't tell us how large the mistake is.}
-An alternative way of presenting the \cite{fan2010sharp} bounds is in terms of quantiles of the distribution of $\Delta$.
+\todo[inline]{Need a sentence saying what the results are: at least such and such percent benefit from forced commitment}
+
+%An alternative way of presenting the \cite{fan2010sharp} bounds is in terms of quantiles of the distribution of $\Delta$.
 Let $0 < q < 1$, and define $Q_0, Q_1, Q$ to be the quantile functions corresponding to $F_0, F_1$ and $F_\Delta$.\footnote{In other words, $Q_0(q) \equiv \inf \{x | F(x) \geq q\}$ and so on.} Then the sharp bound for $Q_\Delta(q)$ is given by $\underline{Q}(q) \leq Q(q) \leq \overline{Q}(q)$ where
-\[
-\overline{Q}(q) \equiv \inf_{u \in [q,1]} [Q_1(u) - Q_0(u - q)], \quad
-\underline{Q}(q) \equiv \sup_{u\in [0,q]} [Q_1(u) - Q_0(1 + u - q)]
-\]
-By substituting $q = 0.11$, these expressions allow us to bound the 11th percentile of the distribution of $\Delta$.
+%\[
+%\overline{Q}(q) \equiv \inf_{u \in [q,1]} [Q_1(u) - Q_0(u - q)], \quad
+%\underline{Q}(q) \equiv \sup_{u\in [0,q]} [Q_1(u) - Q_0(1 + u - q)]
+%\]
+%By substituting $q = 0.11$, these expressions allow us to bound the 11th percentile of the distribution of $\Delta$.
 Under a stylized Roy model in which borrowers with the largest (negative) treatment effects choose commitment, $Q(0.11)$ equals the treatment effect for the borrower at the margin of indifference between choosing commitment.
-Our point estimates for the lower and upper bounds $\underline{Q}(0.11)$ and $\overline{Q}(0.11)$ are \hl{XXXX} and \hl{XXXX} with corresponding 95\% confidence intervals \hl{XXXX} and \hl{XXXX}.\footnote{Again, confidence intervals are constructed using \hl{XXXX} bootstrap as describe in \cite{fan2010sharp}.}
-%\todo[inline]{Issac: add the interval for $Q(0.11)$.
+%Our point estimates for the lower and upper bounds $\underline{Q}(0.11)$ and $\overline{Q}(0.11)$ are \hl{XXXX} and \hl{XXXX} with corresponding 95\% confidence intervals \hl{XXXX} and \hl{XXXX}.\footnote{Again, confidence intervals are constructed using \hl{XXXX} bootstrap as describe in \cite{fan2010sharp}.}
+%%\todo[inline]{Issac: add the interval for $Q(0.11)$.
 Again, this needs to be without covariates and we need to be careful about the sign convention for our effects.
@@
 Presumably the aforementioned quantile is indeed negative and fairly large.}
-Both ways of presenting the bounds yield the same conclusion: at least some borrowers who would benefit from commitment \emph{do not choose it} when offered.
+%Both ways of presenting the bounds yield the same conclusion: at least some borrowers who would benefit from commitment \emph{do not choose it} when offered.
 
@@
 
-To understand the relationship between choice and heterogeneous treatment effects, it is important to be precise about the potential outcomes in our empirical setting.
+Our assumption-free bounds from the preceding section show that more than 11\% of borrowers would benefit from a policy of forced commitment. 
+Intuitively, this seems to suggest that some of the 89\% of borrowers in the choice arm who did \emph{not} choose commitment would have faced lower borrowing costs if they had.
+Making this intuition precise, however, requires a careful consideration of the relationship between choice and heterogeneous treatment effects. 
+To this end, we now provide a full definition of the potential outcomes in our empirical setting, and introduce a pair of assumptions that will allow us to go beyond the assumption-free bounds from above.
+
 Let $Z_i \in \{0, 1, 2\}$ denote the treatment arm to which to participant $i$ was assigned: $Z_i = 0$ denotes the forced no-commitment arm, $Z_i = 1$ denotes the forced commitment arm, and $Z_i = 2$ denotes the choice arm.
@@
 Under this assumption, a fully general model for the potential outcomes in our experiment would take the form $Y_i(d, z)$ for $d\in \{0,1\}$ and $z \in \{0, 1, 2\}$, allowing participant $i$'s potential outcome to depend \emph{both} on the treatment she actually receives, $D_i$, and the experimental arm to which she is assigned, $Z_i$.
-This model is too general, however, to identify meaningful causal effects. 
-For this reason, we impose two exclusion restrictions.
-Before stating them, we first define some additional notation.
-In particular, because any anyone with $Z_i = 0$ has $D_i = 0$ under our experimental design, we abbreviate the potential outcome $Y_i(d=0,z=0)$ as $Y_{i0}$. 
-Similarly, as anyone with $Z_i = 1$ has $D_i = 1$, we abbreviate $Y_i(d=1,z=1)$ as $Y_{i1}$. 
-Our first exclusion restriction is relevant only for non-choosers, individuals with $C_i = 0$, because they are the only borrowers for whom $D_i = 0$ when $Z_i = 2$.
-We assume that
+This model is too general, however, to point identify meaningful causal effects. 
+For this reason, we consider two exclusion restrictions.
+
+Before stating these restrictions, we first define some additional notation.
+Because our experimental design implies that any borrower with with $Z_i = 0$ has $D_i = 0$, we abbreviate the potential outcome $Y_i(d=0,z=0)$ as $Y_{i0}$. 
+Similarly, since any borrower with $Z_i = 1$ has $D_i = 1$, we abbreviate $Y_i(d=1,z=1)$ as $Y_{i1}$. 
+This is in keeping with our notation from section \ref{sec:bounds} above.
+Using this notation, our first exclusion restriction is given by
 \begin{equation}
@@
 \end{equation}
-Equation \ref{eq:exclusion0} implies that every non-chooser experiences the same potential outcome when assigned to the control arm as when assigned to the choice arm.  
-Our second exclusion is relevant only for choosers, individuals $C_i =1$, because they are the only borrowers for whom $D_i = 1$ when $Z_i = 2$.
-We assume that 
+Equation \ref{eq:exclusion0} only restricts the potential outcomes of non-choosers,  individuals with $C_i = 0$, because they are the only borrowers for whom $D_i = 0$ when $Z_i = 2$.
+In words, this condition assumes that every non-chooser experiences the same potential outcome regardless of whether she is assigned to the choice arm or the control arm.
+Similarly, our second exclusion restriction is given by
 \begin{equation}
@@
 \end{equation}
-Equation \ref{eq:exclusion1} implies that every chooser experiences the same potential outcome when assigned to the treatment arm as when assigned to the choice arm. 
-Mathematically \eqref{eq:exclusion0} and \eqref{eq:exclusion0} have the same structure as the standard TOT or LATE exclusion restriction that $Y_i(d,z)$ depends only on $d$, not on $z$. 
-Substantively, however, they are slightly different as there is no analogue of the ``chosen'' versus ``forced'' treatment distinction in the usual LATE setting.\footnote{See \cite{chamberlain2011bayesian}, who uses an assumption very similar to our exclusion restrictions to develop a theory of optimal treatment choice for an individual who has access to data from an RCT.}
-Both \eqref{eq:exclusion0} and \eqref{eq:exclusion1} are plausible in our empirical setting. 
-Moreover, each has testable implications that we fail to reject: see Appendix \ref{append:exclusion} for details.
-Under \eqref{eq:exclusion0} and \eqref{eq:exclusion1}, each participant's observed outcome $Y_i$ is related to her potential outcomes $(Y_{i0}, Y_{i1})$ according to
+Equation \ref{eq:exclusion1} only restricts the potential outcomes of choosers, individuals with $C_i =1$, because they are the only borrowers for whom $D_i = 1$ when $Z_i = 2$.
+In words, this condition assumes that every chooser experiences the same potential outcome regardless of whether she is assigned to the treatment arm or the choice arm.
+
+Mathematically \eqref{eq:exclusion0} and \eqref{eq:exclusion1} have the same structure as the standard LATE exclusion restriction that $Y_i(d,z)$ depends only on $d$, not on $z$. 
+Substantively, however, they are slightly different, given that there is no explicit reference to the ``chosen'' versus ``forced'' treatment distinction in the usual LATE setup.\footnote{For related discussion, see \cite{chamberlain2011bayesian} who uses an assumption similar to our exclusion restrictions to develop a theory of optimal treatment choice for an individual who has access to data from an RCT.}
+In essence, \eqref{eq:exclusion0} and \eqref{eq:exclusion1} assume that being assigned a particular treatment has the same result as choosing it for yourself, provided that you are assigned the same treatment that you \emph{would have chosen}.
+If the mere fact of having been given a choice has a direct effect on outcomes, one or both of our exclusion restrictions will be violated.
+One can imagine situations in which this might be the case.
+For example, even someone who would have voluntarily chosen to undergo drug rehabilitation, given the choice, might respond differently when coerced.
+In our empirical setting, however, both \eqref{eq:exclusion0} and \eqref{eq:exclusion1} are plausible. 
+Moreover, each has testable implications that we fail to reject.
+For details, see Appendix \ref{append:exclusion}.
+
+Under the exclusion restrictions from \eqref{eq:exclusion0} and \eqref{eq:exclusion1}, each participant's observed outcome $Y_i$ is related to her potential outcomes $(Y_{i0}, Y_{i1})$ according to  
 \begin{equation}
@@
 \end{equation}
-%\todo[inline]{Fix labels!}
-%Accordingly, we impose the following standard exclusion restriction:
-%\begin{equation}
-%Y_i(d=0, z=0) = Y_i(d=0, z=2) \equiv Y_{i0}, \quad
-%Y_i(d=1, z=1) = Y_i(d=1, z=2) \equiv Y_{i1}.
-%\label{eq:exclusion}
-%\end{equation}
-%Equation \ref{eq:exclusion} says that each participant's potential outcome is the same regardless of whether she \emph{chooses} a particular treatment $D=d$ or is \emph{assigned} the same treatment.
-Viewing $Z_i$ as an instrumental variable (IV) for the treatment $D_i$, \eqref{eq:exclusion} amounts to the usual IV exclusion restriction.
-%
-%\todo[inline]{END Fix labels!}
 Equation \ref{eq:potentialOutcomes} is the key to understanding the results that follows. 
-By randomly assigning $Z_i=0$ and $Z_i = 1$, our experiment identifies the marginal distributions of $Y_{i0}$ and $Y_{i1}$ in the population as a whole. 
-By randomly assigning $Z_i=2$, it likewise identifies the share of choosers ($C_i = 1$), the distribution of $Y_{i1}$ for choosers, and the distribution of $Y_{i0}$ for non-choosers ($C_i = 0$).
+As noted above, by randomly assigning $Z_i=0$ and $Z_i = 1$ our experiment identifies the marginal distributions of $Y_{i0}$ and $Y_{i1}$ in the population as a whole. 
+By randomly assigning $Z_i=2$, it likewise point identifies the share of choosers ($C_i = 1$), the distribution of $Y_{i1}$ for choosers, and the distribution of $Y_{i0}$ for non-choosers ($C_i = 0$).
 Because $Z_i$ is assigned independently of pre-treatment covariates $X_i$, our design also identifies the corresponding \emph{conditional} distributions of $Y_{i0}$ and $Y_{i1}$ given $X_i$. 
@@
 
-Above we used outcome data from the forced arms ($Z_i\neq 2$) along with the commitment take-up rate in the choice arm ($Z_i = 2$) to argue that at least some of the \hl{89\%} of participants who did \emph{not} choose commitment would have been better off if they had.
-By additionally examining \emph{outcome data} in the choice arm, it is possible to say more. 
-We now show how our experimental design, henceforth the ``controlled choice design,'' point identifies a number of interesting and economically-relevant causal quantities without the need for additional structural restrictions.
+%Above we used outcome data from the forced arms ($Z_i\neq 2$) along with the commitment take-up rate in the choice arm ($Z_i = 2$) to argue that at least some of the \hl{89\%} of participants who did \emph{not} choose commitment would have been better off if they had.
+%By additionally examining \emph{outcome data} in the choice arm, it is possible to say more. 
+We now show how our experimental design, henceforth the ``controlled choice design,'' combined with the exclusion restrictions from \eqref{eq:exclusion0} and \eqref{eq:exclution1} can be used to point identify a number of interesting and economically-relevant causal quantities without the need for additional structural restrictions.
 First we identify the treatment on the treated (ToT) and treatment on the untreated (TuT) effects, defined as follows:
@@
 
-\todo[inline]{Possibly add some discussion here of Craig's idea: using the controlled choice design to study ``targeting''}
+%\todo[inline]{Possibly add some discussion here of Craig's idea: using the controlled choice design to study ``targeting''}
 
@@
 Table \ref{tot_tut} calculates the causal quantities described above--ToT, TuT, ASG, ASB, and ASL--for our experimental data, along with robust standard errors for each. 
-For purposes of comparison, the table also presents the ATE results from Section \hl{XXXX} above (row 1), along with the corresponding average potential outcomes $\mathbbm{E}[Y_0]$ and $\mathbbm{E}[Y_1]$ (rows 4--5).
-The columns of the table correspond to different outcome variables, defined as in Section \hl{XXXX} above.
+For purposes of comparison, the table also presents the ATE results from Section \ref{experiment} above (row 1), along with the corresponding average potential outcomes $\mathbbm{E}[Y_0]$ and $\mathbbm{E}[Y_1]$ (rows 4--5).
+The columns of the table correspond to different outcome variables, defined as in Section \ref{costs} above.
 For all four outcome definitions, the TuT effect is positive, statistically and economically significant, and comparable in magnitude to the ATE.
@@
         This is a (translated) sample information slide shown to clients. The real ones were twice the size of this figure and were laminated. Different ones were shown for each treatment arm.
+\end{figure}
+
+\begin{figure}[H]
+    \caption{Determinants of choice}
+    \label{determinants_choose}
+    \begin{center}
+    \begin{subfigure}{0.75\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/determinants_choose_commitment.pdf}
+    \end{subfigure}
+    \end{center}
+      \scriptsize
+
+      The above figure shows the determinants in a bivariate and multivariate OLS regression of choosing commitment.
+Choice commitment is a binary variable equal to one, whenever subjects choose the forced commitment contract in the choice arm.
+%\textit{Do file: } \texttt{determinants_choice_sure_confidence.do}       
 \end{figure}
@@
 
-%\textit{Do file: } \texttt{fan\_park\_bnds,do}       
+%\textit{Do file: } \texttt{fan\_park\_bnds.do}       
+\end{figure}
+
+\begin{figure}[H]
+    \caption{Determinants sure confidence}
+    \label{determinants_sure}
+    \begin{center}
+    \begin{subfigure}{0.75\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/determinants_confidence_100.pdf}
+    \end{subfigure}
+    \end{center}
+      \scriptsize
+
+      The above figure shows the determinants in a bivariate and multivariate OLS regression of sure confidence among the non-choosers.
+Sure confidence is a binary variable defined to be one when people report a 100\% probability of recovery.
+%\textit{Do file: } \texttt{determinants_choice_sure_confidence.do}       
 \end{figure}
@@
 \begin{figure}[H]
-    \caption{Negative selection on treatment effects}
-    \label{benefit_vs_choice_cdf}
+    \caption{Wide and narrow forests}
+    \label{wide_narrow_forests}
     \begin{center}
-    \begin{subfigure}{0.475\textwidth}
-        \caption{APR benefit}
+    \begin{subfigure}{0.75\textwidth}
         \centering
-        \includegraphics[width=\textwidth]{Figuras/cdf_predchoose_tau_apr.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.475\textwidth}
-        \caption{Repayment}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/cdf_predchoose_tau_des.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.475\textwidth}
-        \caption{Default}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/cdf_predchoose_tau_def.pdf}
+        \includegraphics[width=\textwidth]{Figuras/scatter_hist_wide_narrow.pdf}
     \end{subfigure}
     \end{center}
-     \scriptsize    CDF of the heterogeneous treatment effect for choosers vs non-choosers.
+      \scriptsize
+
+%\textit{Do file: } \texttt{wide_narrow_forests.do}       
+\end{figure}
+
+\begin{figure}[H]
+    \caption{Targeting rules}
+    \label{targeting_rules}
+    \begin{center}
+    \begin{subfigure}{0.75\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/wide_narrow_rule.pdf}
+    \end{subfigure}
+    \end{center}
+      \scriptsize
+
+%\textit{Do file: } \texttt{wide_narrow_forests.do}       
+\end{figure}
+
+% \begin{figure}[H]
+%     \caption{Negative selection on treatment effects}
+%     \label{benefit_vs_choice_cdf}
+%     \begin{center}
+%     \begin{subfigure}{0.475\textwidth}
+%         \caption{APR benefit}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/cdf_predchoose_tau_apr.pdf}
+%     \end{subfigure}
+%     \begin{subfigure}{0.475\textwidth}
+%         \caption{Repayment}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/cdf_predchoose_tau_des.pdf}
+%     \end{subfigure}
+%     \begin{subfigure}{0.475\textwidth}
+%         \caption{Default}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/cdf_predchoose_tau_def.pdf}
+%     \end{subfigure}
+%     \end{center}
+%      \scriptsize    CDF of the heterogeneous treatment effect for choosers vs non-choosers.
 The dotted line below indicates the points where the difference in the distributions is significant.
@@
 
-     \hl{Isaac : If I recall correctly we agreed to not work with the propensities.
+%      \hl{Isaac : If I recall correctly we agreed to not work with the propensities.
 Besides this is giving us different results(?) - this was due to not using actual choosers and the prop.
@@
 }
-          %\footnotesize{ \textit{Do file: }  \texttt{benefit\_choice.do}}
-\end{figure}
+%           %\footnotesize{ \textit{Do file: }  \texttt{benefit\_choice.do}}
+% \end{figure}
 

### 2023-06-08 presentation.tex
targeting paternalism rules

@@
 
-\date{April 2023}
+\date{June 2023}
 
@@
          \vfill\item Main results
+          \vfill\item Exploiting the Controlled Choice Design
          \vfill\item Paternalism
@@
 
-% \begin{frame}{Description}
-% \label{consort}
-% \begin{figure}[H]
-%      \caption{Experiment description}
-%     \label{exp_description}
-% \begin{center}
-%         \includegraphics[width=0.80\textwidth]{Figuras/consort.pdf}
-%   \end{center}
-% \end{figure}
-% \hyperlink{experimental_integrity}{\beamerbutton{Details}}
+ \begin{frame}{Description}
+ \label{consort}
+ \begin{figure}[H]
+      \caption{Experiment description}
+     \label{exp_description}
+ \begin{center}
+         \includegraphics[width=0.80\textwidth]{Figuras/consort.pdf}
+   \end{center}
+ \end{figure}
+ %\hyperlink{experimental_integrity}{\beamerbutton{Details}}
 
-% \end{frame}
+ \end{frame}
 
@@
 
-\begin{frame}
-\textbf{Predictors of take-up : $\Pr(Take-up)$}
-
-\begin{figure}[H]
-    \begin{center}
-        \includegraphics[width=0.9\textwidth]{Figuras/determinants_takeup_reg.pdf}
-    \end{center}
-    \end{figure}
-\end{frame}
-
 \begin{frame}{Outline}
@@
          \vfill\item \textbf{Main results}
+          \vfill\item Exploiting the Controlled Choice Design
          \vfill\item Paternalism 
      \end{itemize}
+\end{frame}
+
+\begin{frame}
+\textbf{Predictors of take-up : $\Pr(Take up)=11\%$} on average.
+
+\begin{figure}[H]
+    \begin{center}
+        \includegraphics[width=0.9\textwidth]{Figuras/determinants_choose_commitment.pdf}
+    \end{center}
+    \end{figure}
 \end{frame}
@@
    \vfill 
-  \hyperlink{several_def_cost}{\beamerbutton{More}}
+  %\hyperlink{several_def_cost}{\beamerbutton{More}}
 
@@
 
-\begin{frame}{Intermediate outcomes: forced-commitment}
-\label{intermediate_outcomes}
+\begin{frame}{Intermediate outcomes (1)}
+\label{mechanism_appendix}
+
+\begin{table}[H]
+\caption{Intermediate outcomes}
+\begin{center}
+\scriptsize{\input{./Tables/mechanism1_pres.tex}}
+\end{center}
+\end{table}
+\vfill
+%\hyperlink{intermediate_outcomes}{\beamerbutton{Back}}
  \begin{itemize}
-     \item \vfill \textbf{Speed of payment:} The first payment of the forced commitment contract  occurs 13 days earlier, increasing the fraction who recover on the first visit by 7.9 pp.
+     \item \textbf{Speed of payment:} The first payment of the forced commitment contract  occurs 13 days earlier, increasing the fraction who recover on the first visit by 7.9 pp.
 Conditional on recovering, they recover 28 days faster.
+\end{itemize}
+\end{frame}
 
-    \item \vfill \textbf{Separating those who will not pay:} Commitment contract decreases fraction of borrowers making a payment and \textit{not} recovering by 7pp.
+\begin{frame}{Intermediate outcomes (2)}
+
+\begin{table}[H]
+\caption{Intermediate outcomes}
+\begin{center}
+\footnotesize{\input{./Tables/mechanism2_pres.tex}}
+\end{center}
+\end{table}
+
+%\hyperlink{intermediate_outcomes}{\beamerbutton{Back}}
+   \vfill \item  \textbf{Separating those who will not pay:} Commitment contract decreases fraction of borrowers making a payment and \textit{not} recovering by 7pp.
     \begin{itemize}
@@
     \end{itemize}
+\end{frame}
+
+\begin{frame}{Intermediate outcomes (3)}
+
+    \begin{table}[H]
+\caption{Intermediate outcomes}
+\begin{center}
+\footnotesize{\input{./Tables/mechanism3_pres.tex}}
+\end{center}
+\end{table}
+\vfill
+%\hyperlink{intermediate_outcomes}{\beamerbutton{Back}}
+ \begin{itemize}
+     \item \vfill \textbf{Frequency of visits:} Commitment induces a `parting of the waters' whereby those who were going to default visit the branch subsequently .2 fewer times.
+\end{itemize}
+\end{frame}
+
+%\begin{frame}{Intermediate outcomes: forced-commitment}
+%\label{intermediate_outcomes}
+% \begin{itemize}
+ %    \item \vfill \textbf{Speed of payment:} The first payment of the forced commitment contract  occurs 13 days earlier, increasing the fraction who recover on the first visit by 7.9 pp.
+Conditional on recovering, they recover 28 days faster.
+
+  %  \item \vfill \textbf{Separating those who will not pay:} Commitment contract decreases fraction of borrowers making a payment and \textit{not} recovering by 7pp.
+   % \begin{itemize}
+    %    \item Actually, among those that default, those in the forced commitment arm are 14pp less likely to have paid towards recovery.
+They also visit the branch less: as if the commitment contract makes them realize they will end up losing pawn anyway, and stop paying early on.
+    %\end{itemize}
+    %\end{itemize}
+
+  % \vfill
+
+%   \hyperlink{mechanism_appendix}{\beamerbutton{Details}}
+%\end{frame}
+
+\begin{frame}{Costs fall from Forcing by multiple measures}
+\label{several_def_cost}
+\begin{table}[H]
+\caption{Effects on several definitions of cost}
+\label{table_robustness_fc}
+\begin{center}
+\resizebox{0.95\textwidth}{!}{
+\small{\input{./Tables/fc_robustness_pres.tex}}
+}
+\end{center}
+ \scriptsize
+
+%\textit{Do file: } \texttt{fc\_robustness.do}
+\end{table}
+   % \hyperlink{main_results}{\beamerbutton{Back}}
+ \begin{itemize}
+     \item \vfill Significantly reduced costs even when we include:
+     \begin{itemize}
+         \item Subjective rather than objective value of pawn.
+         \item Travel costs.
+         \item Valuing lost liquidity using the interest rate.
+         \item All three at once.
+     \end{itemize}
+\end{itemize}
+\end{frame}
+
+\begin{frame}{Do borrowers value Forcing as measured by repeat business?}
+
+\vspace{.2in}
+\begin{table}[H]
+\begin{center}
+\footnotesize{\input{./Tables/repeat_loans.tex}}
+\end{center}
+\end{table}    
+\begin{itemize}
+    \item Client forced into commitment is 20\% more likely to come back again and pawn.
+    \item Not mechanically from having recovered the pawned, since also pawn other pieces.
+    \item Not within the life of the loan, but after. So unlikely that is a liquidity story.
+    \item Conditional on recovery (endogenous), ``effect'' twice as big.
 \end{itemize}
 
-   \vfill
-
-   \hyperlink{mechanism_appendix}{\beamerbutton{Details}}
 \end{frame}
@@
        \pause \item If the effect of commitment were homogeneous, this would be enough to conclude that the 89\% who did not choose it would have been financially better off if they had.
-       \item However, we test and reject the null hypothesis of homogeneous treatment effects (Chernozhuvok et. al. 2018).
+       \item However, we test and reject the null hypothesis of homogeneous treatment effects (Chernozhukov et. al. 2018).
     \end{itemize}
@@
     \vfill \item The borrowers who did not choose commitment could simply be those who don’t need it?
-    \pause \vfill \ item The distribution of TE (i.e.
+    \pause \vfill \item The distribution of TE (i.e.
 $Y_{1i}-Y_{0i}$) is not identified, as one person is only observed in one treatment.
 However, it can be bounded using the two marginal dist $F_1$ and $F_0$.
-\hyperlink{fan_park_bounds}{\beamerbutton{Fan \& Park bounds}}
-    \vfill \item \textbf{Many with benefits did not demand:} We find that at least 30\% of individual borrowers benefit from commitment $\implies$ many did not demand even though TE is positive for them.
-    \vfill \item Given our 3-armed experiment (+ imposing a mean exclusion restriction) allow us to estimate average TuT$>0$.
-%Furthermore, imposing the restriction for each cell of covariates and using Causal Forests gets us $F_{TUT}^{-1}(0.72)>0$.
+
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
+
+\begin{figure}[H]
+    \caption{Fan \& Park bounds for benefit in APR\% }
+    \label{fig:FanPark}
+    \begin{center}
+        \caption{APR}
+        \centering
+        \includegraphics[width=0.7\textwidth]{Figuras/fan_park_bounds_apr.pdf}
+    \end{center}
+
+%\textit{Do file: } \texttt{fan\_park\_bnds.do}       
+\end{figure}
+
+\begin{itemize}
+        \vfill \item \textbf{Many with benefits did not demand:} Making no parametric assumptions, we find that at least 30\% of individual borrowers benefit from commitment $\implies$ many did not demand even though TE is positive for them.
+
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}{Outline}
+     \begin{itemize}
+         \vfill\item Experimental Design
+         \vfill\item Main results
+          \vfill\item \textbf{Exploiting the Controlled Choice Design}
+         \vfill\item Paternalism 
      \end{itemize}
@@
 
+Our 3-armed experiment + dual exclusion restriction allows us to estimate: 
+\begin {itemize}
+ \item Treatment Effect on the Treated (ToT), as with standard IV on one-sided non-compliance.
+ \item Treatment on the Untreated (TUT), symmetric instrumentation for \textit{not} complying as compared to forcing arm.
+\end{itemize}
 \vspace{.2in}
@@
 \vspace{.2in}
+
 Assumptions:
@@
 \end{itemize}
+\end{frame}
 
-\vspace{.2in}
-Therefore:
+\begin{frame}{The Double Exclusion Restriction:}
+
+With both of these exclusion restrictions in place:
+\begin{itemize}
+    \item Effect of (Control = Not Choosing) for non-choosers
+    \item Effect of (Forcing = Choosing) for choosers.
+    \end{itemize}
 \begin{itemize}
@@
 \vspace{.2in}
+
 Prop:
@@
      \item TuT := $\mathbbm{E}(Y_{i1} - Y_{i0} | C_i = 0)$ is point-identified, and equals $\frac{\mathbbm{E}(Y_i|Z_i=1) - \mathbbm{E}(Y_i|Z_i =2)}{1-\mathbbm{E}(D_i|Z_i=2)} $
-     \item Also identified: $ASG:=ToT-TuT$, $ASB:= \E[Y_0 | C=1]-\E[Y_0 | C=0]$, and $ASL:= \E[Y_1 | C=1]-\E[Y_1 | C=0]$. 
+     \item Also identified: 
+     \begin{itemize}
+         \item Average Selection on Gains $ASG:=ToT-TuT$
+         \item Average Seletion Bias $ASB:= \E[Y_0 | C=1]-\E[Y_0 | C=0]$
+         \item Average Selection on Levels $ASL:= \E[Y_1 | C=1]-\E[Y_1 | C=0]$
+     \end{itemize}
 \end{itemize}
@@
  \vfill
-\hyperlink{identification_randomized_choice}{\beamerbutton{Identification}}
+%\hyperlink{identification_randomized_choice}{\beamerbutton{Identification}}
 \end{frame}
@@
 
-\begin{frame}{Fraction that forgo benefit}
+\section{Outline}
+\begin{frame}{Outline}
+     \begin{itemize}
+         \vfill\item Experimental Design
+         \vfill\item Main results
+          \vfill\item Exploiting the Controlled Choice Design
+         \vfill\item \textbf{Paternalism}
+     \end{itemize}
+\end{frame}
 
-    \label{choose_wrong}
-
-        \begin{figure}{\textwidth}
-        \caption{Mistakes in choice arm}
-        \centering
-        \includegraphics[width=0.65\textwidth]{Figuras/line_cw_apr_tot_tut.pdf}
-        \end{figure}
-
+\begin{frame}{If commitment works, why don't people choose it?}
     \begin{itemize}
-    \item   Use Random Forest to estimate ToT, TUT conditional on covariates.
-    \item $>$ 70\% of non-choosers would have seen some benefit from assignment to commitment.
-    \item  $<$ 20\% of choosers made a mistake.
+         \onslide<1>{\item Need to learn about it}
+         \onslide<2>{\item Discounting}
+        \onslide<3-4>{\item Present-Bias}
     \end{itemize}
 
-\end{frame}
+\vfill
 
-\begin{frame}{Effects on clients coming back}
+\only<1>{
 
+    \textbf{Do people learn from Forced exposure to the program that they benefit from it? } 
+    \vspace{.1in}
     \begin{itemize}
-    \item Client forced into commitment is 20\% more likely to come back again and pawn.
-    \item Not mechanically from having recovered the pawned, since also pawn other pieces.
-    \item Not within the life of the loan, but after. So unlikely that is a liquidity story.
-    \item Conditional on recovery (endogenous), ``effect'' twice as big.
-\end{itemize}
-
-\vspace{.2in}
-\begin{table}[H]
-\begin{center}
-\footnotesize{\input{./Tables/repeat_loans.tex}}
-\end{center}
-\end{table}    
-\end{frame}
-
-\begin{frame}{Learning}
-    \label{learning_table}
-    \begin{itemize}
-    \item  Do people learn from Forced exposure to the program that they benefit from it?  
-    \vspace{.1in}
     \item  Small sample (small power): focus on those that, after being either forced to commitment contract or to status quo, come back within a few months and are subject to choice arm.
@@
  %\hyperlink{learning}{\beamerbutton{Back}}
-\end{frame}
+}
 
-\begin{frame}{If commitment works, why don't people choose it?}
-    \begin{itemize}
-        \onslide<1>{\item Discounting}
-        \onslide<2-3>{\item Present-Bias}
-    \end{itemize}
 \vfill
-\only<1>{  
- \begin{itemize}
- \item Can impatience explain why not take up a contract that decreases overall cost?
-     \end{itemize}
+\only<2>{
+
+\textbf{Can impatience explain why not take up a contract that decreases overall cost?}
+
 \begin{figure}[H]
@@
 
-\only<2>{
+\only<3>{
 
-    \begin{itemize}
-    \item   Standard behavioral angle:  compliers are sophisticated time-inconsistent, non-compliers are a mix of naifs and the time consistent (who don't need commitment).  
-    \end{itemize}
+ \textbf{Standard behavioral angle:}  compliers are sophisticated time-inconsistent, non-compliers are a mix of naifs and the time consistent (who don't need commitment).
+
 \begin{figure}[H]
@@
 
-\only<3>{
+\only<4>{
 
     \begin{itemize}
-    \item   We estimate the TuT conditional on $X_i=1 or X_i=1$ (say $X_i= PB_i$ or $=Confidence_i$) and see which subpouplations have larger TuT.
+    \item   We estimate the TuT conditional on $X_i=1$ or $X_i=1$ (say $X_i= PB_i$ or $=Confidence_i$) and see which subppulations have larger TuT.
 
@@
     \begin{align*}
-        1=& \frac{\mathbb{E}[Y_{1i}-Y_{0i} | D_i=0, X_i=1]}{TuT}\Pr(X_i=1 | D_i=0) \\
-        \quad &+ \frac{\mathbb{E}[Y_{1i}-Y_{0i}| D_i=0, X_i=0]}{TuT}\Pr(X_i=0 | D_i=0)
+        1=& \frac{\mathbb{E}[Y_{1i}-Y_{0i} | C_i=0, X_i=1]}{TuT}\Pr(X_i=1 | C_i=0) \\
+        \quad &+ \frac{\mathbb{E}[Y_{1i}-Y_{0i}| C_i=0, X_i=0]}{TuT}\Pr(X_i=0 | C_i=0)
     \end{align*}
@@
 }
+
 \end{frame}
@@
 
+\begin{frame}{Determinants of Sure Confidence}
+
+        \begin{figure}
+        \caption{What attributes correlate with Sure Confidence?}
+        \centering
+        \includegraphics[width=0.65\textwidth]{Figuras/determinants_confidence_100.pdf}
+        \end{figure}
+
+The Sure-Confident are:
+\begin{itemize}
+    \item   Older, more educated men who
+    \item   Have savings and do not report financial stress or trouble meeting bills, and 
+    \item   Are likely to be relied upon by family members.
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}{Understanding Heterogeneity with a Causal Forest}
+\label{HTE}
+\begin{itemize}
+
+\item We use (Athey et.al. 2019) GRF to estimate CATE (causal RF), CTUT and CTOT (instrumental RF).
+
+\begin{itemize}	
+	\item We split the data that produce the biggest difference in TE across leaves, by still producing accurate estimates of the TE.
+Moreover, the splits are made honest by taking the training data and splitting it into two subsamples: a splitting subsample and an estimating subsample.
+\hyperlink{honest_causal_tree}{\beamerbutton{Honest Causal Tree}}
+\end{itemize}
+
+\item Estimated TE in each leaf is aysmptotically normal. 
+\end{itemize}
+
+    \begin{figure}
+        \caption{CATE (APR)}
+        \centering
+        \includegraphics[width=0.5\textwidth]{Figuras/he_dist_apr_pro_2.pdf}
+        \end{figure}
+
+ \begin{itemize}
+\item We test and reject the null hypothesis of homogeneous treatment effects (Chernozhukov et. al. 2018)
+ \end{itemize}       
+\end{frame}
+
+\begin{frame}{Example of a Causal Tree}
+
+    \begin{figure}
+        \caption{Causal Tree}
+        \centering
+\includegraphics[width=0.8\textwidth]{Figuras/ct_eff.pdf}
+        \end{figure}
+
+\end{frame}
+
+\begin{frame}{Fraction that forgo benefit:  Choice Arm}
+
+        \begin{figure}
+        \label{choose_wrong}
+        \caption{Mistakes in choice arm}
+        \centering
+        \includegraphics[width=0.65\textwidth]{Figuras/line_cw_apr_tot_tut.pdf}
+        \end{figure}
+
+\begin{itemize}
+    \item   Use Random Forest to estimate ToT, TUT conditional on covariates.
+    \item   Those making either choice make mistakes if benefit of other choice is higher.
+    \item $>$ 70\% of non-choosers would have seen some benefit from assignment to commitment.
+    \item  $<$ 20\% of choosers made a mistake.
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}{Fraction that forgo benefit:  Forcing Arm}
+
+        \begin{figure}
+         \label{better_forceall}
+        \caption{Effect of forcing everyone}
+        \centering
+        \includegraphics[width=0.65\textwidth]{Figuras/line_better_forceall_apr_te_cf.pdf}
+        \end{figure}
+
+\begin{itemize}
+    \item   Now use Random Forest to estimate the CATE of forcing, examine heterogeneity in ATE.
+    \item   Because CATE>CTUT, we now find fully 91\% of individuals better off being forced into commitment than staying in control.
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}{How well can we target paternalism?}
+
+\begin{itemize}
+    \item   Why be paternalistic to everyone if we have a strong ability to predict those who lose and we can assign them to control?
+
+     \vspace{.2in}
+
+    \item   Standard targeting analysis, except need to consider covariates carefully given context.
+    \item   Private sector lender, competitive market, part of attraction of pawning is no application!  
+    \begin{itemize}
+        \item Only use readily observable and non-falsifiable covariates.
+    \item   Cannot use any behavioral covariates for which truthful reporting becomes non-incentive-compatible if incentivized.
+    \item   Cannot use choice and then compel compliance among non-choosers in a commercial context.  
+    \end{itemize}
+
+     \vspace{.2in}
+
+    \item Which leaves us with:
+    \begin{itemize}
+    \item   Age
+    \item   Gender
+    \item   HS Education or above
+    \item   Ever pawned before 
+    \end{itemize}
+
+     \vspace{.2in}
+
+    \item  We call these our `narrow' targeting criteria, while the full set of covariates used in the RF are `wide'.
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}{Comparing `Wide' and `Narrow' Heterogeneity}
+
+    \label{wide_v_narrow}
+
+        \begin{figure}
+        \caption{Scatterplot of Predicted Heterogeneity}
+        \centering
+        \includegraphics[width=0.75\textwidth]{Figuras/scatter_hist_wide_narrow.pdf}
+        \end{figure}
+
+\begin{itemize}
+    \item   Substantially less heterogeneity fitting APR CATE with `narrow' than `wide'
+    \item Test of homogeneity (Chernozhukov et. al. 2018) no longer rejected with `narrow'
+    \item   However, overall fitted relationship shows `narrow' adjusts to the mean TE.
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}{Comparison of Targeting Performance:  CDFs}
+
+        \begin{figure}
+        \label{targeting_CDFs}
+        \caption{Distribution of Benefits under Different Targeting Rules}
+        \centering
+        \includegraphics[width=0.70\textwidth]{Figuras/wide_narrow_rule.pdf}
+        \end{figure}
+
+\begin{itemize}
+    \item   Even using the Random Forest to target, our four `narrow' variables only increase the fraction benefitting from 91\% (all Forced) to ~93\% (targeted).
+    \item  Using a Logit with the `narrow' variables actually worsens performance relative to universal Forcing because Logit matches benefit/loss fraction, has both Type 1 and Type 2 errors.
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}{Comparison of Targeting Performance:  Hit-Miss Table}
+
+\begin{table}[H]
+\caption{Type I \& II errors using targeting narrow rules}
+\label{hit_miss_rule}
+\begin{center}
+\resizebox{0.95\textwidth}{!}{
+\small{\input{./Tables/hit_miss_rule.tex}}
+}
+\end{center}
+\end{table}
+
+\begin{itemize}
+    \item   As seen above, even RF with `narrow' variables results in very modest increase in targeting efficiency relative to universal paternalism.
+    \item  Logit performs very poorly because it makes symmetric Type I and Type II errors and hence assigns many to control who would have been better off with commitment.
+    \item  \textbf{Takeaway:}  In this context, with these variables, targeting paternalism relatively ineffective.
+\end{itemize}
+
+\end{frame}
+
 \section{Conclusion}
@@
         \vfill \item Mystery of low take-up combined with large TuT seems best explained by sure-confidence among pawnshop customers.
-
-        %\vfill \item   Are those with a greater experience of pawning less sure-confident?  
+        \vfill\item  Ability to target paternalism using objective covariates is poor; even using RF without cross-validation gains from targeting are small and with logit actually makes things worse.
         \vfill \item Suggests mandated commitment-based contract structures in payday/pawnshop loans as a form of pro-poor regulation?
-        \vfill\item Finally:  how to target and who would be hurt if we instituted  paternalism?
-
     \end{itemize}  
@@
 
-\begin{frame}{Several definitions of cost}
-\label{several_def_cost}
-\begin{table}[H]
-\caption{Effects on several definitions of cost}
-\label{table_robustness_fc}
-\begin{center}
-\resizebox{0.95\textwidth}{!}{
-\small{\input{./Tables/fc_robustness_pres.tex}}
-}
-\end{center}
- \scriptsize
-
-%\textit{Do file: } \texttt{fc\_robustness.do}
-\end{table}
-    \hyperlink{main_results}{\beamerbutton{Back}}
-
-\end{frame}
-
 \begin{frame}{Survival Graph}
@@
 
-\begin{frame}{Intermediate outcomes}
-\label{mechanism_appendix}
-
-\begin{table}[H]
-\caption{Intermediate outcomes}
-\begin{center}
-\footnotesize{\input{./Tables/mechanism1_pres.tex}}
-\end{center}
-\end{table}
-\vfill
-\hyperlink{intermediate_outcomes}{\beamerbutton{Back}}
-\end{frame}
-
-\begin{frame}{Intermediate outcomes}
-
-\begin{table}[H]
-\caption{Intermediate outcomes}
-\begin{center}
-\footnotesize{\input{./Tables/mechanism2_pres.tex}}
-\end{center}
-\end{table}
-\vfill
-\hyperlink{intermediate_outcomes}{\beamerbutton{Back}}
-\end{frame}
-
-\begin{frame}{Intermediate outcomes}
-
-    \begin{table}[H]
-\caption{Intermediate outcomes}
-\begin{center}
-\footnotesize{\input{./Tables/mechanism3_pres.tex}}
-\end{center}
-\end{table}
-\vfill
-\hyperlink{intermediate_outcomes}{\beamerbutton{Back}}
-\end{frame}
-
 \begin{frame}{Bounding Individual Treatment Effects}
@@
 
+\begin{frame}{Honest Causal Tree construction}
+\label{honest_causal_tree}
+Given a dataset with an outcome $Y$, covariates $X$, and a randomized condition $T$ that takes on the value of 0 for control and 1 for treatment:
+
+\begin{enumerate}
+\item Split the data into subsample $I$ and subsample $J$
+
+\item Train a decision tree on subsample $I$ predicting $Y$ from $X$, with the requirement that each terminal node has at least $k$ observations from each condition in subsample $J$
+
+\item Apply the decision tree constructed on subsample $I$ to subsample $J$
+
+\item At each terminal node, get the mean of predictions for the $T = 1$ cases from subsample $J$ and subtract the mean of predictions for the $T = 0$ cases from subsample $J$; the resulting difference is the estimated treatment effect.
+
+\end{enumerate}
+
+This is then applied to a causal random forest by using bagging or bootstrapping.
+\hyperlink{HTE}{\beamerbutton{Back}}\\
+
+\end{frame}
+
 \end{document}

### 2023-06-08 RScripts/grf.R

@@ -10,7 +10,7 @@ library(rattle)
 library(broom)
 
 # SET WORKING DIRECTORY
-setwd('C:/Users/isaac/Dropbox/Apps/Overleaf/Donde2020')
+setwd('C:/Users/isaac/Dropbox/Apps/Overleaf/Donde2022')
 set.seed(1)
 
 source("./RScripts/best_tree.R")
@@ -48,11 +48,6 @@ heterogeneity_effect <- function(data_in,treatment_var,outcome_var,writedata,ext
       "dummy_suc4",
       "dummy_suc5",
       "dummy_suc6",
-      "num_arms_d2",
-      "num_arms_d3",
-      "num_arms_d4",
-      "num_arms_d5",
-      "num_arms_d6", 
       "suc_x_dia",
       "edad",
       "faltas",
@@ -61,7 +56,8 @@ heterogeneity_effect <- function(data_in,treatment_var,outcome_var,writedata,ext
       "pres_antes",
       "plan_gasto",
       "masqueprepa",
-      "pb"
+      "pb",
+      "confidence_100"
     ),
     c(
       "tuesday",
@@ -74,11 +70,6 @@ heterogeneity_effect <- function(data_in,treatment_var,outcome_var,writedata,ext
       "branch.4",
       "branch.5",
       "branch.6",
-      "num.exp.arms.2",
-      "num.exp.arms.3",
-      "num.exp.arms.4",
-      "num.exp.arms.5",
-      "num.exp.arms.6",
       "suc_x_dia",
       "age",
       "income.index",
@@ -87,7 +78,8 @@ heterogeneity_effect <- function(data_in,treatment_var,outcome_var,writedata,ext
       "pawn.before",
       "makes.budget",
       "more.high.school",
-      "p.bias"
+      "p.bias",
+      "sure.confidence"
     ))
   }
   

### 2023-06-08 RScripts/te_grf.R

@@ -10,8 +10,10 @@ library(rattle)
 library(broom)
 
 # SET WORKING DIRECTORY
-setwd('C:/Users/isaac/Dropbox/Apps/Overleaf/Donde2020')
+setwd('C:/Users/isaac/Dropbox/Apps/Overleaf/Donde2022')
 set.seed(1)
+
+source("./RScripts/best_tree.R")
 
 fun_threshold_alpha = function(alpha, g) {
   lambda = 1/(alpha*(1-alpha))
@@ -39,19 +41,23 @@ te_grf <- function(data_in, outcome_var, name) {
     "dummy_suc4",
     "dummy_suc5",
     "dummy_suc6",
-    "num_arms_d2",
-    "num_arms_d3",
-    "num_arms_d4",
-    "num_arms_d5",
-    "num_arms_d6", 
     "edad",
     "faltas",
-    "val_pren_std",
-    "genero",
+    "c_trans",
+    "t_llegar",
+    "fam_pide",
+    "ahorros",
+    "t_consis1",
+    "t_consis2", 
+    "confidence_100",
+    "hace_presupuesto",
+    "tentado",
+    "rec_cel",
     "pres_antes",
-    "plan_gasto",
+    "cta_tanda",
+    "genero",
     "masqueprepa",
-    "pb"
+    "estresado_seguido"
   ),
   c(
     "tuesday",
@@ -64,19 +70,23 @@ te_grf <- function(data_in, outcome_var, name) {
     "branch.4",
     "branch.5",
     "branch.6",
-    "num.exp.arms.2",
-    "num.exp.arms.3",
-    "num.exp.arms.4",
-    "num.exp.arms.5",
-    "num.exp.arms.6",
     "age",
-    "income.index",
-    "subj.loan.value",
-    "female",
-    "pawn.before",
+    "trouble.paying.bills",
+    "transport.cost",
+    "transport.time",
+    "fam.asks",
+    "savings",
+    "patience",
+    "future.patience", 
+    "sure.confidence",
     "makes.budget",
+    "tempted",
+    "sms.reminder",
+    "pawn.before",
+    "rosca",
+    "female",
     "more.high.school",
-    "p.bias"
+    "stressed"
   ))
   
   require("dplyr")
@@ -224,8 +234,16 @@ te_grf <- function(data_in, outcome_var, name) {
   write_csv(ate, filename_ate)
   print(ate)
   
+  # BEST TREE
[…]

### 2023-06-08 RScripts/te_narrow_grf.R

@@ -1,0 +1,219 @@
+library(gdata)
+library(tidyverse)
+library(grf)
+library(ggplot2)
+library(ggthemes)
+library(causalTree)
+library(DiagrammeR)
+library(DiagrammeRsvg)
+library(rattle)
+library(broom)
+
+# SET WORKING DIRECTORY
+setwd('C:/Users/isaac/Dropbox/Apps/Overleaf/Donde2022')
+set.seed(1)
+
+source("./RScripts/best_tree.R")
+
+fun_threshold_alpha = function(alpha, g) {
+  lambda = 1/(alpha*(1-alpha))
+  ind = (g<=lambda)
+  den = sum(ind)
+  num = ind*g
+  return((2*sum(num)/den-lambda)^2)
+}
+
+
+te_narrow_grf <- function(data_in, outcome_var, name) {
+  
+  require("dplyr")
+  data_in <- data_in %>%
+    mutate_all(~ifelse(is.na(.), median(., na.rm = TRUE), .))  
+  data_copy <- data_in
+  data_in <- rename.vars(data_in, c(
+    "edad",
+    "genero",
+    "pres_antes",
+    "masqueprepa"
+  ),
+  c(
+    "age",
+    "female",
+    "pawn.before",
+    "more.high.school"
+  ))
+  
+  require("dplyr")
+  
+  data_train <- data_in %>% 
+    filter(insample == 1) 
+  
+  data_test <- data_in %>% 
+    select(-c(outcome_var, fee_arms, prenda, insample))
+  
+  ###################################################################  
+  ###################################################################  
+  
+  
+  # PREPARE VARIABLES
+  X <- select(data_train,-c(outcome_var, fee_arms, prenda, insample))
+  Y <- select(data_train,outcome_var)
+  W <- as.numeric(data_train$fee_arms == 1)
+  
+  ###################################################################  
+  ###################################################################  
+
+  
+  # OVERLAP ASSUMPTION
+  propensity.forest = regression_forest(X, W)
+  propensity_score = predict(propensity.forest)$predictions
+  propensity_score[propensity_score==1] <- 0.99
+  propensity_score[propensity_score==0] <- 0.01
+  hist(propensity_score, xlab = "propensity score")
+  
+  # Dropping observations with extreme values of the propensity score - CHIM (2009)
+  g <- 1/(propensity_score*(1-propensity_score))
+  
[…]

### 2023-06-08 RScripts/tot_tut_instr_forest.R

@@ -10,7 +10,7 @@ library(rattle)
 library(broom)
 
 # SET WORKING DIRECTORY
-setwd('C:/Users/isaac/Dropbox/Apps/Overleaf/Donde2020')
+setwd('C:/Users/isaac/Dropbox/Apps/Overleaf/Donde2022')
 set.seed(1)
 
 
@@ -26,19 +26,23 @@ rename_var = function(df) {
     "dummy_suc4",
     "dummy_suc5",
     "dummy_suc6",
-    "num_arms_d2",
-    "num_arms_d3",
-    "num_arms_d4",
-    "num_arms_d5",
-    "num_arms_d6", 
     "edad",
     "faltas",
-    "val_pren_std",
-    "genero",
+    "c_trans",
+    "t_llegar",
+    "fam_pide",
+    "ahorros",
+    "t_consis1",
+    "t_consis2", 
+    "confidence_100",
+    "hace_presupuesto",
+    "tentado",
+    "rec_cel",
     "pres_antes",
-    "plan_gasto",
+    "cta_tanda",
+    "genero",
     "masqueprepa",
-    "pb"
+    "estresado_seguido"
   ),
   c(
     "tuesday",
@@ -51,19 +55,23 @@ rename_var = function(df) {
     "branch.4",
     "branch.5",
     "branch.6",
-    "num.exp.arms.2",
-    "num.exp.arms.3",
-    "num.exp.arms.4",
-    "num.exp.arms.5",
-    "num.exp.arms.6",
     "age",
-    "income.index",
-    "subj.loan.value",
-    "female",
-    "pawn.before",
+    "trouble.paying.bills",
+    "transport.cost",
+    "transport.time",
+    "fam.asks",
+    "savings",
+    "patience",
+    "future.patience", 
+    "sure.confidence",
     "makes.budget",
+    "tempted",
+    "sms.reminder",
+    "pawn.before",
+    "rosca",
+    "female",
     "more.high.school",
-    "p.bias"
+    "stressed"
   ))
 }
 
@@ -146,6 +154,8 @@ fit_instr_forest = function(xvar, wvar, yvar, zvar, dta, nme) {
   write_csv(data.out, filename_out)
 }  
 
+
+
 ###################################################################  
 ###################################################################  
 
@@ -167,22 +177,18 @@ tut_copy <- tut
 rename_var(tot)
 rename_var(tut)
 
-###################################################################  
[…]

### 2023-06-29 OA.tex
add row to hit-miss table for chocie rule & text editing

@@
 
+\subsection{Pictures}
+
 \begin{figure}[H]
@@
 
-\subsection{Surveys}
+\subsection{Survey}
 
@@
 \newpage
-\subsection{Main treatment effects: Additional material}
-
+\section{Main treatment effects: Additional material}
+
+\begin{landscape}
+\subsection{Multiple loans}
+
+\begin{table}[H]
+\caption{Multiple-loans robustness check}
+\label{multiple_loans}
+\begin{center}
+\scriptsize{\input{./Tables/multiple_loans.tex}}
+\end{center}
+ \scriptsize
+%\textit{Do file: } \texttt{multiple\_loans.do}
+\end{table}
+
+\end{landscape}
+
+\subsection{Censoring} \label{App_censoring}
+
+\vspace{.2in}
+\normalsize
+The approach taken in the paper for censored loans is a conservative one in that it inherently assumes that all of the loans outstanding at the end of the observation window will be repaid, making it so that the acceleration of payment observed in the Forced arm does not translate mechanically into a treatment effect on default.
+This appendix delves into it more detail.
+One way of considering the effect that this issue could have on our results is to make extreme assumptions about the outcome of these loans in the treatment and control so as to bound the possible influence of censoring.
+In Table \ref{mns} we compare the Forced and Control arms, making the bracketing assumptions about repayment on censored loans.
+Panel A assumes all censored loans are repaid, and Panel D that all default.
+Panel B provides the lower bound for the treatment effect by assuming censored control loans are always repaid and treatment loans never are, and Panel C the upper bound by making the reverse assumption.
+Comfortingly, even with these extreme assumptions the significance on the main treatment effects never flips and treatment effects on financial cost and interests payments remain negative and significant in all scenarios.
+So there appears to be no scope for the censoring issue to overturn our main results.
+
+Finally, Panel E of this table conducts a logit prediction model that uses all of the available information on loans that were completed to predict the outcome of loans that were not.
+This is a best guess of the outcome on censored loans.
+Using this prediction, we replicate the main experimental results and find that the treatment effect on financial cost increases from -378 (main results) to -525 (censored loans predicted), and the APR from -34\% to -62\%.
+Hence, while the censoring issue does have a substantial influence on the magnitude of our estimated treatment effects, these  checks confirm that a) the core results are robust to censoring, and b) the headline approach that we take to the issue is conservative and is likely understating the true magnitude of impacts.
+
+\vspace{.3in}
 \begin{table}[H]
@@
 \begin{figure}[H]
+        \caption{Survival graph}
+    \label{survival_graph}
+    \begin{center}
+   \begin{subfigure}{0.49\textwidth}
+   \caption{Ended contract}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/survival_graph_ended.pdf}
+    \end{subfigure} 
+   \begin{subfigure}{0.49\textwidth}
+   \caption{Recovery}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/survival_graph_unpledge.pdf}
+    \end{subfigure}     
+    \end{center}
+     \scriptsize  This Figure shows the accumulated percentage of recovery in time by treatment arm. 
+     %\textit{Do file: }  \texttt{survival\_graph.do}
+\end{figure}
+
+\begin{figure}[H]
+        \caption{\% of payment over time}
+    \label{porc_payment_over_time}
+    \begin{center}
+   \begin{subfigure}{0.49\textwidth}
+        \caption{Unconditional}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/cumulative_porc_pay_time.pdf}
+    \end{subfigure} 
+   \begin{subfigure}{0.49\textwidth}
+        \caption{Conditional on default}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/cumulative_porc_pay_time_default.pdf}
+    \end{subfigure}     
+    \end{center}
+     \scriptsize  This Figure shows the accumulated percentage of recovery in time by treatment arm. 
+     %\textit{Do file: }  \texttt{cumulative\_porc\_pay\_time.do}
+\end{figure}
+
+\newpage
+\section{Alternative explanations}
+
+\vspace{.2in}
+\subsection{Learning}
+
+\vspace{.1in}
+\begin{table}[H]
+        \caption{Effect of Prior Assignment on Subsequent Choice}
+    \label{learning_table}
+\begin{center}
+\scriptsize{\input{./Tables/learning_exp_pres.tex}}
+\end{center}
+ \scriptsize  This table uses a Linear Probability Model to examine whether randomized treatment assignment on a prior loan taken during the experimental period drives the likelihood of selecting into the commitment product for individuals who go to a branch featuring Choice after the experiment.
+\end{table}
+
+\vspace{.3in}
+
+\subsection{Discount rates}
+
+\begin{figure}[H]
         \caption{Financial cost TUT effect for different discount rates}
@@
 
-\begin{figure}[H]
-    \caption{Partition of TuT \& ToT effect by behavioral variables.}
+\vspace{.3in}
+\subsection{Sure confidence and present bias}
+
+\begin{figure}[H]
+    \caption{Partition of TuT by behavioral variables.}
     \label{tut_beh_partition}
     \begin{center}
-    \begin{subfigure}{0.475\textwidth}
-        \caption{TuT}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/tut_beh_partition.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.475\textwidth}
-        \caption{ToT}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/tot_beh_partition.pdf}
-    \end{subfigure}
-
-    \end{center}
-     \scriptsize    \\
+        \centering
+        \includegraphics[width=0.55\textwidth]{Figuras/tut_beh_partition.pdf} 
+    \end{center}
+     \scriptsize  This figure performs a partition of the Treatment on the Untreated, estimating the share of the effect that arises within each of two binary categories.
+The top bars examine present bias (individuals are more impatient over one-month time horizon than they are between three and four months).
+The bottom bars examine sure confidence (individual reports 100\% probability of repaying at time of taking loan).
+Blue bar is the component arising from those without the trait, orange bar from those with the trait.
       %\footnotesize{ \textit{Do file: }  \texttt{partition_tot_tut.do}
@@
 
-\cleardoublepage
-
-\begin{landscape}
-
-\begin{table}[H]
-\caption{Multiple-loans robustness check}
-\label{multiple_loans}
-\begin{center}
-\scriptsize{\input{./Tables/multiple_loans.tex}}
-\end{center}
- \scriptsize
-
-%\textit{Do file: } \texttt{multiple\_loans.do}
-\end{table}
-
-\end{landscape}
-
-\begin{figure}[H]
-        \caption{Survival graph}
-    \label{survival_graph}
-    \begin{center}
-   \begin{subfigure}{0.49\textwidth}
-   \caption{Ended contract}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/survival_graph_ended.pdf}
-    \end{subfigure} 
-   \begin{subfigure}{0.49\textwidth}
-   \caption{Recovery}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/survival_graph_unpledge.pdf}
-    \end{subfigure}     
-    \end{center}
-     \scriptsize  This Figure shows the accumulated percentage of recovery in time by treatment arm. 
-     %\textit{Do file: }  \texttt{survival\_graph.do}
-\end{figure}
-
-\begin{figure}[H]
-        \caption{\% of payment over time}
-    \label{porc_payment_over_time}
-    \begin{center}
-   \begin{subfigure}{0.49\textwidth}
-        \caption{Unconditional}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/cumulative_porc_pay_time.pdf}
-    \end{subfigure} 
-   \begin{subfigure}{0.49\textwidth}
-        \caption{Conditional on default}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/cumulative_porc_pay_time_default.pdf}
-    \end{subfigure}     
-    \end{center}
-     \scriptsize  This Figure shows the accumulated percentage of recovery in time by treatment arm. 
-     %\textit{Do file: }  \texttt{cumulative\_porc\_pay\_time.do}
-\end{figure}
-
-\cleardoublepage
-
+\vspace{.3in}
+\subsection{Risk aversion and first order stochastic dominance} \label{App_FOSD}
+\normalsize
 \vspace{.2in}
-\begin{figure}[H]
-        \caption{Empirical CDF of Financial Cost: fee-focing vs status-quo}
+We do not have measures of risk aversion in our short survey, which makes it hard to assess the hypothesis that risk aversion limits take-up of the fee frequent payment contract.
+One way to proceed is to take the empirical distribution of financing cost ---$F_{fee}(FC)$--- as one the client would have faced had she chosen the status quo contract.
+We could then ask what would risk aversion have to be in order to justify the client choosing the fee-commitment contract distribution of costs over the distribution associated with the status quo contract, $F_{sq}(FC)$.
+Framed as a choice among cost distributions, we can calculate what risk aversion is needed to rationalize the overwhelming choice of the status quo contract over the fee-commitment contract.
+This exercise of course assumes --as is common in economics-- that clients know the distribution of financial cost, that the distribution is common across consumers (although this can be relaxed), and that this cost distribution is the only difference among contracts.
+
+Fortunately for us, it turns out that one distribution first-order-stochastically dominates the other, obviating the need to calibrate a specific utility function or use a parametric distribution function in order to rank them in terms of expected utility.
+We use the fact that if the utility $u(FC)$ is decreasing in $FC$ (i.e.
+clients dislike paying higher financing cost) and $F_{fee}(FC) \geq F_{sq}(FC)$ for all $FC$, which we actually verify in our data, then $E_{fee}[u(FC)] \geq E_{sq}[u(FC)]$, that is any expected utility maximizing client risk averse consumer should choose the Forced Commitment contract as a result of the distribution of cost payoffs.\footnote{Figure \ref{ecdf_fc} shows that indeed $F_{fee}(FC) \geq F_{sq}(FC)$.
+Table \ref{stochastic_dominance} shows that this holds also for sub-populations of different characteristics.}.
+Thus, risk aversion cannot explain the low demand for commitment under the assumptions of this exercise.
+
+\vspace{.2in}
+\begin{figure}[H]
+        \caption{Empirical CDF of Financial Cost: fee-forcing vs status-quo \textcolor{red}{\hl{MAY NEED UPDATING}}}
     \label{ecdf_fc}
@@
         \centering
-        \includegraphics[width=0.65\textwidth]{Figuras/cdf_fc_pro_2.pdf}
+        \includegraphics[width=0.55\textwidth]{Figuras/cdf_fc_pro_2.pdf}
     \end{center}
@@
 \begin{figure}[H]
-        \caption{Empirical CDF of APR: fee-focing vs status-quo}
+        \caption{Empirical CDF of APR: fee-focing vs status-quo \textcolor{red}{\hl{MAY NEED UPDATING}}}
     \label{ecdf_fc}
@@
         \centering
-        \includegraphics[width=0.65\textwidth]{Figuras/cdf_eff_pro_2.pdf}
+        \includegraphics[width=0.55\textwidth]{Figuras/cdf_eff_pro_2.pdf}
     \end{center}
@@
 \begin{table}[H]
-\caption{Clients who should prefer fee-forcing financial cost distribution}
+\caption{FOSD by demographic groups \textcolor{red}{\hl{MAY NEED UPDATING}}}
 \label{stochastic_dominance}
@@
 \newpage
+
 \vspace{.2in}
@@
 \label{lognormal_fosd}
-\footnotesize{
+
 Let $F$ and $G$ be the cumulative distributions of two alternative log-normal prospects. The following are equivalent:
@@
 \end{enumerate}
-}
 \end{prop}
@@
 \begin{proof}
-\footnotesize{
 See Theorem 4 in \cite{lognormal_dominance}.
-}
 \end{proof}
@@
 \label{eq_fosd}
-\footnotesize{
+
 This is a standard result. 
@@
 \end{enumerate}
-}
+
 \end{prop}
 \begin{proof} \;
-\footnotesize{
 
@@
 with $y(FC) = F_{sq}^{-1}F_{fee}(FC)$.
-}
+
 \end{proof}
-\footnotesize{
+
 Note the proof was done in the case of absolutely continuous and strictly increasing distribution functions $F_{sq}$ and $F_{fee}$.
-}
 
@@
 
-\subsection{Testing for heterogeneity}
+\begin{comment}
+\section{Causal Forest and individual predictions of `Mistakes'}
+
+    \begin{figure}[H]
+        \caption{Example of a Causal Tree \textcolor{red}{WHAT IS THE DIFFERENCE OF THIS AND FIGURE OA-17?}}
+        \label{causal_tree_example}
+        \begin{center}
+\includegraphics[width=\textwidth]{Figuras/ct_eff.pdf}
+\end{center}
+     \scriptsize This Figure shows an example of the splits for the leaves that emerge in our data for the Athey et al (2019) Causal Forest estimation.  
+        \end{figure}
+\end{comment}
+
+%Are we using any tables/figures after this point?
+
+\cleardoublepage
+
+\section{Testing for heterogeneity}
 \label{append:chernozhukov}
@@
 
-\subsection{Derivations for Section \ref{sec:randchoice}}
+\section{Derivations for Section \ref{sec:randchoice}}
 \label{append:randchoice}
@@
 \end{proof}
+
+\todo[inline]{It looks like I still need to paste in the derivations of the ``regression'' approach to identifying the effects of interest. I will do this pronto! -Frank}
 
@@
 
-\subsection{Testable Implications of the Exclusion Restriction}
+\section{Testable Implications of the Exclusion Restriction}
 \label{append:exclusion}
@@
 To consider possible violations of these conditions, it is helpful to introduce some additional notation.
-As in the body of the text, let $Y_0 \equiv Y(d=0,z=0)$ and $Y_1 \equiv Y(d=1,z=1)$ denote the potential outcomes under \emph{forced treatment}: $Y_0$ is the potential outcome when forced into the status quo contract and $Y_1$ when forced into the commitment contract.
+As above, let $Y_0 \equiv Y(d=0,z=0)$ and $Y_1 \equiv Y(d=1,z=1)$ denote the potential outcomes under \emph{forced treatment}: $Y_0$ is the potential outcome when forced into the status quo contract and $Y_1$ when forced into the commitment contract.
 Further let $Y_{0,2} \equiv Y(d=0,z=2)$ and $Y_{1,2} \equiv Y(d=1,z=2)$ denote the potential outcomes under \emph{free choice of treatment}: $Y_{0,2}$ is the potential outcome when choosing the status quo contract and $Y_{1,2}$ when choosing the commitment contract.
@@
 but parts (i) and (ii) continue to hold.
-Accordingly, parts (i)--(iii) of \ref{lem_randchoice} are unchanged, while parts (iv) and (v) become
+Accordingly, parts (i)--(iii) of Lemma \ref{lem_randchoice} are unchanged, while parts (iv) and (v) become
 \[
@@
 \]
-Using these expressions, the testable restrictions we consider here are 
+Using these expressions, the testable restrictions we consider here are as follows:
+\begin{align}
+\label{eq:exclusion_append0}
+\mathbbm{E}(Y_0|C=0) &= \mathbbm{E}(Y_{0,2}|C=0) \\
+\label{eq:exclusion_append1}
+\mathbbm{E}(Y_1|C=1) &= \mathbbm{E}(Y_{1,2}|C=1).
+\end{align}
+Equation \ref{eq:exclusion_append0} is a restriction on the potential outcomes of non-choosers that we use to point identify the TuT.
+In contrast, Equation \ref{eq:exclusion_append1} is a restriction on the potential outcomes of choosers that we use to point identify the ToT.
+Because they involve different groups of people, it is entirely possible for one of these equalities to hold when the other fails.
+For this reason, we consider each in turn.
+Our approach is closely related to a bounding approach used by \cite{huber_mellace} and \cite{BinaryRegressor}, among others.
+As such, the following is a heuristic explanation rather than a fully-rigorous proof.
+See the aforementioned papers for more details of how to make this argument fully rigorous.
+
+Consider first Equation \ref{eq:exclusion_append0}.
+Let $p \equiv \mathbbm{P}(C=1) = \mathbbm{P}(D=1|Z=2)$ denote the share of choosers in the population.
+This value is point identified regardless of whether the exclusion restriction holds.
+Because $Z$ was randomly assigned, a fraction $p$ of borrowers with $Z=0$ are choosers while the remaining $(1-p)$ are non-choosers.
+It follows that, regardless of whether the exclusion restriction holds, the observed distribution of $Y|Z=0$ is a mixture of $Y_0|C=0$ and $Y_0|C=1$ with mixing weights $(1-p)$ and $p$.
+This allows us to construct a pair of bounds for $\mathbb{E}(Y_0|C=0)$ as follows.
+The non-choosers must lie \emph{somewhere} in the distribution of $Y|Z=0$.
+Consider the two most extreme possibilities: they could occupy the bottom $(1-p)\times 100\%$ of the distribution or the top $(1-p)\times 100\%$ of the distribution.
+For this reason, computing the average of the the \emph{truncated} distribution of $Y|Z=0$, cutting out the top $p\times 100\%$, provides a lower bound for the average of $Y_0$ among non-choosers.
+Similarly, cutting out the bottom $p \times 100\%$ provides an upper bound.
+Let $y^0_{1-p}$ denote the $(1-p)$ quantile of $Y|Z=0$ and $y^0_{p}$ denote the $p$ quantile of the same distribution.
+Using this notation, the bounds are given by
 \[
-\mathbbm{E}(Y_0|C=0) = \mathbbm{E}(Y_{0,2}|C=0) \text{ and } \mathbbm{E}(Y_1|C=1) = \mathbbm{E}(Y_{1,2}|C=1).
+\mathbb{E}\left(Y|Z=0, Y\leq y^0_{1-p}\right)\leq \mathbb{E}(Y_0|C=0) \leq \mathbb{E}\left(Y|Z=0, Y \leq y^0_p\right) 
 \]
-\todo[inline]{Need to talk about how why these are restrictions for choosers and non-choosers respectively. It's because they're the only people we can observe in the relevant $Y{d,2}$ state.}
-
-Because our approach is closely related to that of \cite{huber_mellace}, the following is a heuristic explanation rather than a fully-rigorous proof.
-
-To begin, define the shorthand $p \equiv \mathbbm{E}(C=1) = \mathbbm{P}(D=1|Z=2)$.
-Because $Z$ was randomly assigned, a fraction $p$ of participants with $Z = 1$ have $C = 1$ and the distribution of $Y|Z=1$ is a mixture of $Y_1|C=1$ and $Y_1|C=0$ with mixing weights $p$ and $1 -p$.
-The participants with $C = 1$ must lie \emph{somewhere} in the distribution of $Y_0|Z=1$ so consider the two most extreme cases: they could occupy the bottom or the top $p\times 100\%$ of the distribution.
-It follows that
+These bounds do not rely on the exclusion restriction.
+Under Equation \ref{eq:exclusion_append0}, however, we know that $\mathbb{E}(Y_0|C=0)=\mathbb{E}(Y|D=0,Z=2)$.
+Therefore, if the exclusion restriction for non-choosers holds, we must have
+\begin{equation}
+\mathbb{E}\left(Y|Z=0, Y\leq y^0_{1-p}\right)\leq \mathbb{E}(Y|D=0,Z=2) \leq \mathbb{E}\left(Y|Z=0, Y \leq y^0_p\right).
+\label{eq:testable0}
+\end{equation}
+Equation \ref{eq:testable0} provides a pair of testable implications of Equation \ref{eq:exclusion_append0}.
+If either inequality is violated, then the exclusion restriction for non-choosers fails.
+
+We can use an analogous approach to construct testable implications for Equation \ref{eq:exclusion_append1}. 
+Because $Z$ was randomly assigned, a fraction $p$ of participants with $Z = 1$ are choosers so the distribution of $Y|Z=1$ is a mixture of $Y_1|C=1$ and $Y_1|C=0$ with mixing weights $p$ and $1 -p$.
+The participants with $C = 1$ must lie \emph{somewhere} in the distribution of $Y_0|Z=1$ so again consider the two most extreme cases: they could occupy the bottom or the top $p\times 100\%$ of the distribution.
+Hence,
 \[
-\mathbbm{E}(Y|Z=1,Y\leq y^1_{p}) \leq \mathbbm{E}(Y_1|C=1) \leq \mathbbm{E}(Y|Z=1,Y \geq y^1_{1-p})
+\mathbbm{E}\left(Y|Z=1,Y\leq y^1_{p}\right) \leq \mathbbm{E}(Y_1|C=1) \leq \mathbbm{E}\left(Y|Z=1,Y \geq y^1_{1-p}\right)
 \]
-where $y^1_p$ and $y^1_{1-p}$ are the $p$ and $1 - p$ quantiles of the distribution of $Y_1$.
-These quantiles are point identified since $Y|Z=1$ has the same distribution as $Y_1$ under random assignment of $Z$.
-If $Y_{1,2} = Y_1$ then it follows that $\mathbbm{E}(Y|D=1,Z=2) = \mathbbm{E}(Y_1|C=1)$ yielding the bounds
-\[
-\mathbbm{E}(Y|Z=1,Y\leq y^1_{p}) \leq \mathbbm{E}(Y|D=1,Z=2) \leq \mathbbm{E}(Y|Z=1,Y \geq y^1_{1-p}).
-\]
-If either of these is violated, the exclusion restriction does not hold.
+where $y^1_p$ and $y^1_{1-p}$ are the $p$ and $1 - p$ quantiles of the distribution of $Y|Z=1$.
+As above, these bounds do not rely on the exclusion restriction.
+If Equation \ref{eq:exclusion_append1} holds, however, we know that $\mathbb{E}(Y|D=1,Z=2) = \mathbb{E}(Y_1|C=1)$, yielding the following testable implications for choosers
+\begin{equation}
+\mathbbm{E}\left(Y|Z=1,Y\leq y^1_{p}\right) \leq \mathbbm{E}(Y|D=1,Z=2) \leq \mathbbm{E}\left(Y|Z=1,Y \geq y^1_{1-p}\right).
+\label{eq:testable1}
+\end{equation}
+If either inequality is violated, then the exclusion restriction from Equation \ref{eq:exclusion_append1} fails.
 
 \todo[inline]{Update from here down.}
-\[
-\mathbbm{E}(Y|Z=1,Y\leq ?) \leq \mathbbm{E}(Y|D=1,Z=2) \leq \mathbbm{E}(Y|Z=1,Y \geq ?)
-\]
-\[
-\mathbbm{E}(Y|Z=0,Y\leq ?) \leq \mathbbm{E}(Y|D=0,Z=2) \leq \mathbbm{E}(Y|Z=0,Y \geq ?)
-\]
-
-If $Y_1 = Y_{1,2}$ then $\mathbbm{E}(Y|D=1, Z=2)$ point identifies $\mathbbm{E}(Y_1|C=1)$.
-
-$D = 1, Z=2$ means $C = 1$; $D = 0, Z=2$ means $C = 0$;
-
-\todo[inline]{Update below here}
-Because the basic approach is similar to that of \cite{huber_mellace}, we give only a heuristic explanation here rather than a formal proof.
-
-In the absence of the exclusion restriction, the $Z=0$ arm of the experiment point identifies the distribution $F_{00}$ of $Y(d=0,z=0)$.
-This is a person's potential outcome when \emph{forced} into the no-commitment contract.
-Similarly, the $Z=1$ arm point identifies the distribution $F_{11}$ of $Y(d=1,z=0)$, the potential outcome when forced into the commitment contract.
-The $Z = 2$ arm point identifies $p_C \equiv \mathbbm{E}(C)$, the share of individuals who \emph{would choose commitment}, given the option.
-
-Because $Z$ is randomly assigned, $p_C = \mathbbm{E}(C) = \mathbbm{E}(C|Z=z)$ for any arm $z\in \{0, 1, 2\}$ of the experiment.
-This tells us that $F_{00}$ is a mixture distribution: a $p_C$
-
-\todo[inline]{Finish cleaning this up later...}
-This observation is useful for two reasons. First it allows us to bound the TuT and ToT effects without imposing the exclusion restriction.
-Second, by checking whether the TuT and ToT effects calculated under our exclusion restriction lie within the bounds, it allows us to potentially falsify \hl{XXXX}.
-
-Now, from the choice arm we know that around 90\% of people are $T=0$ types.
-Because choice was randomly assigned, the 90\% figure holds for all arms in the experiment.
-This tells us that $F_0$ is a 90\%-10\% mixture of $Y_0\;|\;T=0$ and $Y_0\;|\;T=1$.
-Cut out the bottom 10\% of $F_0$ and calculate the mean of this new distribution.
-Then cut out the top 10\% of $F_0$ and compute the mean of this new distribution.
-The result is an upper and lower bound for $\mathbb{E}[Y_0\;|\;T=0]$ that does not rely on the exclusion restriction.
-We can apply similar reasoning to bound $\mathbb{E}[Y_1\;|\;T=0]$ Combining the previous bounds gives a bound for the TuT that does not rely on the exclusion restriction, and analogous we can bound the ToT.
-\\
 
@@
 
-\subsection{LATE: ToT \& TuT}
+\section{LATE: ToT \& TuT}
 \vspace{.2in}
@@
 \newpage
-\subsection{Causal Random Forest and HTE}
+\section{Causal Random Forest, HTE, and `mistakes'}
 
@@
 
+\begin{comment}
+
+    \begin{figure}[H]
+        \caption{Conditional Average Treatment Effect from Random Forest}
+        \label{CATE}
+        \begin{center}
+\includegraphics[width=0.6\textwidth]{Figuras/he_dist_apr_pro_2.pdf}
+\end{center}
+     \scriptsize This Figure plots the densities of the CATE emerging from the Athey et al. (2019) random forest, along with the upper and lower confidence bounds.  
+        \end{figure}
+\end{comment}
+
+\cleardoublepage
+
+\vspace{.3in}
 \begin{figure}[H]
@@
          \scriptsize
-     plots the distribution of the heterogeneous treatment effects on financial cost, estimated using \cite{atheygrf}.
+     This Figure plots the densities of the CATE emerging from the Athey et al. (2019) random forest, along with the upper and lower confidence bounds.  
   %\footnotesize{ } \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}
@@
         \caption{Honest causal tree for the Forced-commitment contract heterogeneous treatment effects}
-    \label{casual_tree}
+    \label{causal_tree1}
     \begin{center}
@@
         \caption{Single causal tree for the Forced-commitment contract heterogeneous treatment effects}
-    \label{casual_tree}
+    \label{causal_tree2}
     \begin{center}
@@
 
-\begin{figure}[H]
-    \caption{Choice of contracts and treatment effects}
-    \label{choose_wrong}
-    \begin{center}
-        \begin{subfigure}{0.45\textwidth}
-        \caption{Mistakes in choice arm}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/line_cw_apr_te_cf.pdf}
-
-    \end{subfigure}
-        \begin{subfigure}{0.45\textwidth}
-        \caption{Financial value of mistake}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/money_cw_apr_te_cf.pdf}
-
-    \bigskip
-
-    \end{subfigure}
-        \begin{subfigure}{0.45\textwidth}
-        \caption{\% better when forced to forced commitment}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/line_better_forceall_apr_te_cf.pdf}
-
-    \end{subfigure}
+%\begin{figure}[H]
+%    \caption{Choice of contracts and treatment effects}
+%    \label{choose_wrong}
+%    \begin{center}
+%        \begin{subfigure}{0.45\textwidth}
+%        \caption{Mistakes in choice arm}
+%        \centering
+%        \includegraphics[width=\textwidth]{Figuras/line_cw_apr_te_cf.pdf}
+
+%   \end{subfigure}
+%        \begin{subfigure}{0.45\textwidth}
+%        \caption{Financial value of mistake}
+%        \centering
+%        \includegraphics[width=\textwidth]{Figuras/money_cw_apr_te_cf.pdf}
+
+%    \bigskip
+
+%    \end{subfigure}
+%        \begin{subfigure}{0.45\textwidth}
+%        \caption{\% better when forced to forced commitment}
+%        \centering
+%        \includegraphics[width=\textwidth]{Figuras/line_better_forceall_apr_te_cf.pdf}
+%        
+%    \end{subfigure}
     %     \begin{subfigure}{0.45\textwidth}
@@
 
-    \end{center}
-        \scriptsize
-        In Panel (a) we estimate what the treatment effect of the commitment contract \textit{would have been} for all subjects in the choice arm if they had been forced into the fee-commitment contract.
+%    \end{center}
+%        \scriptsize
+%        In Panel (a) we estimate what the treatment effect of the commitment contract \textit{would have been} for all subjects in the choice arm if they had been forced into the fee-commitment contract.
 To do this we proceed in two steps.
@@
         %\textit{Do file: }  \texttt{choose\_wrong\_quant\_wrong.do, choose\_wrong\_quant\_wrong\_decomposition.do}
-\end{figure}
-
+%\end{figure}
+
+\vspace{.3in}
+\begin{table}[H]
+\caption{Type I \& II errors using targeting narrow rules}
+\label{hit_miss_rule}
+\begin{center}
+\resizebox{0.95\textwidth}{!}{
+\small{\input{./Tables/hit_miss_rule.tex}}
+}
+\end{center}
+\scriptsize This table reports on the incidence of Type I and Type II error in different rules for allocating individuals to commitment.
+The first row allocates all units to control which, according to the `wide' RF estimation, results in 87\% of individuals losing by not receiving commitment.
+The second row is the Forcing arm, which has the mirror image errors.
+The third row considers the optimal case in which each individual receives the correct treatment.
+The fourth row uses the `narrow' RF to allocate, such that all individuals on a leaf for which the CATE of commitment is positive are assigned to treatment.
+The fifth row uses a Logit to estimate the propensity to benefit from treatment, and assigns such that the fraction allocated to treatment matches the correct sample fraction that benefit.
+\end{table}
+
+\cleardoublepage
+
+\vspace{.4in}
 \subsection{Take up}
@@
 \begin{table}[H]
-    \caption{Predicting Take-up: Goodness-of-Fit}
+    \caption{\textcolor{red}{DELETE--Predicting Take-up: Goodness-of-Fit}}
     \label{Table_compliance}
@@
 \begin{figure}[H]
-    \caption{Out of sample ROC curve}
+    \caption{\textcolor{red}{DELETE--Out of sample ROC curve}}
     \label{roc_curve}
@@
 
-\begin{figure}[H]
-    \caption{Predictors of commitment contract take-up}
+\vspace{.3in}
+\begin{figure}[H]
+    \caption{\textcolor{red}{\hl{ARE THESE MADE OBSOLETE BY THE NEXT FIGURE? } Predictors of commitment contract take-up}}
     \label{interactions_takeup}
     \begin{center}
-    \begin{subfigure}{0.45\textwidth}
+    \begin{subfigure}{0.7\textwidth}
         \caption{PLM}
@@
     \end{subfigure}
-    \begin{subfigure}{0.45\textwidth}
+    \begin{subfigure}{0.7\textwidth}
         \caption{Logit}
@@
 
+\normalsize
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 % APPENDIX B
-
+\begin{comment}
+
+\newpage
 \section{ Mechanisms }
@@
 
+\end{comment}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2023-06-29 donde.tex
add row to hit-miss table for chocie rule & text editing

@@
 Ricardo Olivares, Gerardo Melendez, and Alonso de Gortari provided excellent research assistance and Erick Molina helped with formatting.
-Jose Maria Barrero, Andrei Gomberg, Emilio Gutierrez, David Laibson, Aprajit Mahajan, Matt Rabin, Charlie Sprenger, and seminar participants at ITAM, USC, and UCSD provided valuable feedback.}}
+Jose Maria Barrero, Andrei Gomberg, Emilio Gutierrez, David Laibson, Aprajit Mahajan, Matt Rabin, Charlie Sprenger, and seminar participants at ITAM, USC, MSU, and UCSD provided valuable feedback.}}
 \author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira \and Francis J.\ DiTraglia   \thanks{Seira: ITAM/MSU, \url{enrique.seira@gmail.com} (corresponding author); McIntosh:  University of California San Diego, \url{ctmcintosh@ucsd.edu}; Meza: Harvard University, \url{isaacmezalopez@g.harvard.edu}; Sadka: ITAM, \url{jsadka@itam.mx}; DiTraglia: Oxford, \url{francis.ditraglia@economics.ox.ac.uk}} }
@@
 It involves comparing the causal effect of forcing a certain product characteristic versus the effect of letting people choose it.
-This is not a straightforward task because choice will be driven by unobservable factors, and to address the question fully we would want a counterfactual for the outcome of both choosers and non-choosers.
+Because choice may be correlated with unobservables, identification
+is challenging in observational studies.  %This is not a straightforward task because choice will be driven by unobservable factors, and to address the question fully 
+Moreover, to have a complete picture of the benefits of forcing, one would want a counterfactual for the outcome of both choosers and non-choosers.
 A large behavioral literature has illustrated that allowing borrowers or savers to choose commitment-style products increase savings in an Intention-to-Treat sense \citep{thaler2004save, prina2015banking, brune2016facilitating, callen2019headwaters, Pascaline, Ashraf}, but this literature has rarely inquired about the benefits of imposing commitment.\footnote{Selection on gains has such wide acceptance that economists often impose it in their models (for example, in the study of migration \cite{chiquiar2005international} and occupational choice \cite{heckman1990empirical}.
-In microfinance, a context close to ours, \citep{Murdoch} claims that positive selection exists, citing a positive correlation between displaying present biased preferences in surveys and selecting into microfinance as evidence of borrowers' actually demanding the discipline imposed by frequent payments.}   In this paper we illustrate how a three-armed, `controlled choice' design can be used to form counterfactuals for both choosers and non-choosers of commitment, providing a high-stakes and policy-relevant environment in which to test selection-on-gains as well as isolating the impact of paternalistic policies.
+In microfinance, a context close to ours, \citep{Murdoch} claims that positive selection exists, citing a positive correlation between displaying present biased preferences in surveys and selecting into microfinance as evidence of borrowers' actually demanding the discipline imposed by frequent payments.}  In this paper we illustrate how a three-armed, `controlled choice' design can be used to form counterfactuals for both choosers and non-choosers of commitment.
+We implement such a design in a high-stakes and policy-relevant environment, enabling us to test selection-on-gains as well as isolating the impact of paternalistic policies.
 
@@
 
-Here we study the benefits of private paternalism in the context of pawnbroker lending.
+We study the benefits of private paternalism in the context of pawnbroker lending.
 Pawn loans are one of the oldest, most understudied, and most prevalent forms of borrowing \citep{carter2012pawnshops}.
@@
 Our collaborating pawn lender (henceforth Lender P) gave 70\% of the value of the pawn in credit, and charged a monthly interest rate of 7\% for loans of a three-month duration, with a flexible no-reminders contract typical of the industry that can be paid back anytime before the loan comes due at no penalty.
+We call this the status-quo contract.
 This combination of features, and the fact that the gold pawn is highly liquid, means that the lender makes 90\% more profit over three months for a borrower who defaults than one who repays (30\% of collateral value recovered under default, 15.8\% of collateral value paid in interest if loan fully repaid).
@@
 Against this backdrop, we implement a multi-arm randomized control trial covering close to 10,000 pawnshop clients in 6 branches of Lender $P$ in Mexico City, using a design built to test the demand for and impact of payment structure in pawn repayment contracts.
-Our control arm illustrates the costs of the status quo contract; fully 57\% of borrowers default and so lose their pawn.\footnote{These high default rates are not uncommon, in the US default is also high at 15\% (\url{https://tinyurl.com/yc2x5bjf}).} We then implement a `commitment choice’ arm, in which borrowers are able at the time of taking a loan to opt in to a structured repayment contract, in which they are asked to make three monthly payments rather than one balloon payment at the end, with each monthly payment including the accrued interest at that time, and borrowers levied a nominal fee of 2\% of that month's payment in case of delinquency as a reminder/reinforcement of the importance of these interim payments.
+Our control arm illustrates the costs of the status quo contract; fully \textcolor{blue}{56\%} of borrowers default and so lose their pawn.\footnote{These high default rates are not uncommon, in the US default is also high at 15\% (\url{https://tinyurl.com/yc2x5bjf}).} We then implement a `commitment choice’ arm, in which borrowers are able at the time of taking a loan to opt into a structured repayment contract, in which they are asked to make three monthly payments rather than one balloon payment at the end, with each monthly payment including the accrued interest at that time, and borrowers levied a nominal fee of 2\% of that month's payment in case of delinquency as a reminder/reinforcement of the importance of these interim payments.
 In addition, we include a `forced commitment’ arm, in which all borrowers are required to repay using the monthly payment structure.
+We will use the terms monthly payments, structured payments, and commitment contract interchangeably.
 
@@
 First, does using more structured repayment contracts help pawnshop borrowers to save on financing cost.
-Second, do borrowers recognize this benefit, demanding commitment in sufficient numbers?
+Second, do borrowers recognize this benefit and demand commitment?
+% demanding commitment in sufficient numbers?
 Finally, and most uniquely, because we incorporate the forced commitment arm, we are able to ask whether the \textit{right} borrowers voluntarily demand commitment, gaining point identification for the Treatment on the Treated (ToT), the Treatment on the Untreated (TuT), and the average selection on gains.
@@
 In terms of Annual Percentage Rates, the financial cost of borrowing is reduced by 34 percentage points.
-That is, imposing commitment structure it is possible to save borrowers money by charging them fees!
+That is, imposing a commitment structure it is possible to save borrowers money by charging them fees.
 These results are robust qualitatively to including transport costs of going to the branch plus losing a day's wage for each visit, using the subjective instead of the gold value of the pawn, and imputing some adjustment for liquidity lost by requiring monthly payments.
 
-The monthly payment contract seems to be achieving these cost savings by speeding up payments and by generating an early bifurcation of borrowers into those that will recover the pawn and those that will not, saving the later payments towards recovery.
-In the treatment group, the first payment occurs 13 days earlier, the fraction recovering on the first visit by is 7.9 percentage point higher.
-Commitment contract decreases fraction of borrowers making a payment and not recovering by 7 percentage points.
+The monthly payment contract seems to be achieving these cost savings by speeding up payments and by generating an early bifurcation of borrowers into those that will recover the pawn and those that will not, saving the later payments towards recovery (which are lost in the case of default).
+In the treatment group, the first payment occurs 13 days earlier, and the fraction recovering on the first visit by is 7.9 percentage points higher.
+The commitment contract also decreases fraction of borrowers making a payment and not recovering by 7 percentage points.
 Treatment effects are concentrated in the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery.
@@
 
-In spite of a large average treatment effect documenting financial cost savings, given the opportunity in the choice arm, only 11\% of borrowers actually choose commitment.
-If the effect of commitment were homogeneous, this would be enough to conclude that the 89\%
-who did not choose it would have been financially better off if they had.
+In spite of a large average treatment effect documenting financial cost savings, given the opportunity in the choice arm, only 11\% of borrowers actually choose payment structure.
+If the effect of payment structure were homogeneous, this would be enough to conclude that the 89\% who did not choose it would have been financially better off if they had.
 However, we test and reject the null hypothesis of homogeneous treatment effects using the method of \cite{chernozhukov2018generic}.
@@
 
-We start by bounding the distribution of individual treatment effects as in \cite{fan2010sharp} and find that at least 30\% of individual borrowers benefit from commitment, implying many borrowers did not demand even though the treatment effect would be positive for them.
-Then, we impose the twin exclusion restrictions necessary for estimation of the ToT and Tut (that the effect of choosing or not choosing is the same as being assigned or not assigned the contract).\footnote{This is a frequently used assumption even if often implicit.
-For instance, a significant literature uses schooling compulsory laws to estimate the return of one more year of school, and then often interprets that schooling, in general, has this return.}  With these assumptions, both treatment effects are point identified as well as the average selection on gains, average selection on levels, and average selection bias.
+We start by not imposing assumptions and bounding the distribution of individual treatment effects as in \cite{fan2010sharp}.
+Using bounds we find that at least 30\% of individual borrowers benefit from commitment, implying many borrowers did not demand the structured payment contract even though the treatment effect would be positive for them.
+Then, we impose the twin exclusion restrictions necessary for estimation of the ToT and TuT ---that the effect of choosing or not choosing is the same as being assigned or not assigned the contract, i.e.
+that the act of choosing itself is irrelevant.\footnote{This is a frequently used assumption even if often implicit.
+For instance, a significant literature uses schooling compulsory laws to estimate the return of one more year of school, and then often interprets that schooling, in general, has this return.}  With these assumptions, both treatment effects are point identified, as is the average selection on gains, the average selection on levels, and the average selection bias.
 Our results indicate that while selection on gains are present in our sample, the financial cost savings of the TuT is still large (at \$356 pesos, it is equivalent to 24 percentage point savings in APR).
@@
 Next, we look at time inconsistent preferences, the workhorse behavioral explanation for the benefits of commitment.
-In our context, not only is time inconsistency only a weak driver of selection into commitment, but the TuT of forcing commitment arises almost entirely among those who are \textit{not} time inconsistent.
-In this pawnbroking sample we document substantial levels of over-optimism among borrowers, the attribute which we believe explains our results.
+In our context, not only is time inconsistency only a weak driver of selection into commitment, but the TuT of forcing commitment arises almost entirely among those who are \textit{not} time inconsistent.\footnote{\textcolor{blue}{Although telling, we acknowledge that our measure of present bias is simple (as its survey-based and the survey was necessarily short).
+For this reason this result needs to be interpreted with care.}}  In this pawnbroking sample we document substantial levels of over-optimism among borrowers, and it has predictive power for our results.
+%which we believe explains our results.
 Not only do 74\% of borrowers say that they will recover their pawn with perfect certainty (whereas only 43\% actually do), but the impact of forcing on those who would not choose commitment is almost perfectly confined to the sub-sample who reported sure confidence in recovery.
@@
 We find that those who are forced to the monthly payment product are 6.7 percentage points more likely to become repeat customers than those assigned to the status-quo contract.
-One way to interpret this is that that having experienced the frequent payment contract (and the lower financial cost of borrowing that come with it), they want to borrow more.\footnote{A second intepretation is that the iliquidity created by the monthly payment contract makes them want obtain second loan to pay the first one.
+One way to interpret this is \textcolor{blue}{as `learning they like pawn-borrowing', i.e.
+having experienced the frequent payment contract (and the lower financial cost of borrowing that come with it), they like pawning and pawn more.}\footnote{A second intepretation is that the iliquidity created by the monthly payment contract makes them want obtain second loan to pay the first one.
 This second explanation is unlikely since borrowers obtain a second loan not within the first 90 days of the first loan when payments are due; moreover, the correlation is also present conditional on having paid down the first loan.
-Borrowers tend to pledge a different piece for the second loan, so that recovery of the first pawn is also an unlikely explanation.} However, a stronger test of liking the monthly payment contract is whether conditional on coming again, they would choose frequent payments.
-We test this and we cannot reject that demand is not higher after experiencing the monthly payment contract, however sample sizes are small and \hl{the minimum detectable effect is XXX.}
+Borrowers tend to pledge a different piece for the second loan, so that recovery of the first pawn is also an unlikely explanation.
+\textcolor{blue}{A different test, about `learning they like monthly-payments'} is whether conditional on coming again, clients would choose frequent payments.
+We test this and we cannot reject that demand is \textit{not} higher after experiencing the monthly payment contract, \textcolor{blue}{consistent with no learning or slow learning that the monthly payment contract is better than the status quo contract}, however sample sizes are small and \hl{the minimum detectable effect is XXX.}} %\textcolor{blue}{making this more rigorous test of learning inconclusive and left for future research.
+Having said this, after more than 100 years in operation, the biggest pawn lender in Mexico and most others still do not offer structured payment contracts.}
 
@@
 Moreover, frequent payment requirements may decrease welfare of highly impatient borrowers.\footnote{The paper presents an back of the envelope exercise that suggests annual discount rates of 4000 are necessary to nullify the reductions in financial cost we estimate.
-\hl{Note also that since the fee for skipping payment is 2\%, the illiquidity imposed by the contract is bounded.}} %Second, given the non-standard nature of the finding, it is likely that we would have to adopt and estimate a particular behavioral model of demand for commitment, which we don't need to do to make the point that TuT is positive.
+\hl{Note also that since the fee for skipping payment is 2\% of the payment due, the illiquidity imposed by the contract is bounded.}} %Second, given the non-standard nature of the finding, it is likely that we would have to adopt and estimate a particular behavioral model of demand for commitment, which we don't need to do to make the point that TuT is positive.
 
@@
 In contrast to \cite{Walters} we use randomization while he needs a structural model and distance to school as an instrument.
-\hl{FRANK, can I say something more precise than ``a structural model''?}
+\todo[inline]{FRANK, can we say something more precise than ``a structural model''?}
 
@@
 
-\paragraph{Most borrowers lose their pawn.} Our context is also one with high borrower default: 60\% of clients lose their pawn in a time span of 230 days from the date of pawning.
+\paragraph{Most borrowers lose their pawn.} Our context is also one with high borrower default: \hl{60\%} of clients lose their pawn in a time span of 230 days from the date of pawning.
 One potential explanation for high default is that clients are really just knowingly selling their gold piece through a pawn contract on which they intend to default.
@@
 Transportation cost to go to the branch to pay is on the same order of magnitude as the fee on average.\footnote{%The lender was worried that if the fee was large, forgetting to pay could make the pawn unrecoverable.
-In contrast with \cite{John} we don't let the clients choose the size of the fee.
+%In contrast with \cite{John} we don't let the clients choose the size of the fee.
 \cite{John} shows that doing this results in costly choices by (partially) naive present biased consumers.
 Our fee is much smaller than the median in her experiment.
-%We also experimented with a contract where there was no pecuniary fee for paying late but where we clients made a personal promise to pay monthly.
 } To elicit demand for the monthly payment contract, we include an arm that allows borrowers to opt into this contract if they choose.
@@
 
+\paragraph{Who chooses commitment?}
+
+A natural starting point for understanding the role of voluntary commitment is the determinants of choice.
+Figure \ref{determinants_choose} provides coefficient plots for univariate and multivariate Linear Probability Models explaining takeup of commitment in the Choice arm.
+Contrary to the standard behavioral motivations, none of our measures of self control predict takeup, neither the metric arising from the paired discounting questions (e.g.
+those who are more impatient over immediate rather than future delays), nor a simple survey question asking whether they are tempted to mis-use money in their financial lives.
+Individuals who report having trouble paying bills are actually \textit{less} likely to take commitment, as are those who have pawned before.
+The only determinant in this figure that represents something like sophistication is that those with more education are more likely, in both univariate and multivariate regressions, to choose commitment.
+Overall, we observe few strong determinants of commitment choice and the story does not appear to be a behavioral one.
+
 \subsection{Experimental Integrity}
@@
 %\subsection{More on implementation} %\label{implementation}
-
-\paragraph{Who chooses commitment?}
-
-we estimate a flexible model of take-up of the commitment-fee contract \textit{in the Choice arm} using gradient boosting classification\footnote{Results are robust to other classification methods like Random Forest, SVM, etc.} and obtain for a client with characteristics $x_i$ a calibrated probability $P(x_i)$ of choosing the commitment contract.
 
@@
 
-\todo[inline]{Add a column with losing pawn. What about re-pawning?}
-\todo[inline]{How did we decide to deal with censoring?}
+%\todo[inline]{Add a column with losing pawn. What about re-pawning?}
+%\todo[inline]{How did we decide to deal with censoring?}
 
@@
 
-\todo[inline]{I think the re-pawn table should only have 4 columns.
+%\todo[inline]{I think the re-pawn table should only have 4 columns.
 Remove variables 3,4, and 7.
@@
 
-\subsection{Censoring of Loan Completion}
-
-The window of time during which we were able to observe borrower behavior was limited in each branch, meaning that there were loans that we do not see completed (particularly those pawns that were rolled over for one or two further 90-day spells).
-Overall, \hl{XX\%} of all experimental loans are censored, meaning that they neither default nor repay within the observation window.
+%\subsection{Censoring of Loan Completion}
+
+\paragraph{Censoring of Loan Completion.} The window of time during which we were able to observe borrower behavior was limited in each branch, meaning that there were loans that we do not see completed (particularly those pawns that were rolled over for one or two further 90-day spells).
+Overall, \hl{XX\%} of all experimental loans are censored, meaning that they neither default nor repaid within the observation window.
 In the prior analysis we handle this issue by using outcomes such as `did not default' which are defined even when we do not observe the completion of the loan, and only considering costs that we observe directly.
@@
 The first is the extent to which loan outcomes are observed more quickly in the forcing arm.
-This is primarily due to the the substantially higher rate of repayment of Forced Commitment loans at 120 days (~15 pp higher than the other arms).
+This is primarily due to the the substantially higher rate of repayment of Forced Commitment loans at 120 days ($\sim$15 pp higher than the other arms).
 The second is the very low rate at which loans are recovered in any arm after 120 days.
-In the 180 day window after the second rollover period we see a further ~10 percent of loans repaid in all arms, but these loans are largely dormant, suggesting that many of the censored loans will in fact be defaulted upon.
-
-The confluence of censoring and a treatment effect on censoring is problematic from an experimental point of view.
+In the 180 day window after the second rollover period we see a further $\sim$10 percent of loans repaid in all arms, but these loans are largely dormant, suggesting that many of the censored loans will in fact be defaulted upon.
+
+The approach taken so far is a conservative one in that it inherently assumes that all of the loans outstanding at the end of the observation window will be repaid, making it so that the acceleration of payment observed in the forced commitment arm does not translate mechanically into a treatment effect on default.
+\textcolor{blue}{Appendix \ref{App_censoring} imputes default predictions for censored loans and also performs a bounding exercise and reaches similar conclusions.}
+%The confluence of censoring and a treatment effect on censoring is problematic from an experimental point of view.
+
+\begin{comment}
 The approach taken so far is a conservative one in that it inherently assumes that all of the loans outstanding at the end of the observation window will be repaid, making it so that the acceleration of payment observed in the Forced arm does not translate mechanically into a treatment effect on default.
@@
 Hence, while the censoring issue does have a substantial influence on the magnitude of our estimated treatment effects, these  checks confirm that a) the core results are robust to censoring, and b) the headline approach that we take to the issue is conservative and is likely understating the true magnitude of impacts.
+\end{comment}
 
@@
 If the effect of commitment were homogeneous, this would be enough to conclude that the \hl{89\%} who did not choose it would have been financially better-off if they had.
-In a world of heterogeneous treatment effects, however, low demand for commitment could still be consistent with individual rationality.
+In a world of heterogeneous treatment effects, however, low demand for commitment could still be consistent with \textcolor{blue}{standard rational borrowers.}
 The borrowers who did not choose commitment could simply be those who don't need it. 
@@
 See \cite{fan2010sharp} for details.}
-\todo[inline]{Need a sentence saying what the results are: at least such and such percent benefit from forced commitment}
+\todo[inline]{@Isaac: Need a sentence saying what the results are: at least such and such percent benefit from forced commitment}
 
@@
 We maintain the stable unit treatment value assumption (SUTVA) throughout. 
-This means that borrower $i$'s outcomes depend only on her \emph{own} values of $Z_i$ and $D_i$, not those of any other person in the experiment: there are no \emph{spillovers}. 
+This means that borrower $i$'s outcomes depend only on her \emph{own} values of $Z_i$ and $D_i$, not those of any other person in the experiment. 
 Under this assumption, a fully general model for the potential outcomes in our experiment would take the form $Y_i(d, z)$ for $d\in \{0,1\}$ and $z \in \{0, 1, 2\}$, allowing participant $i$'s potential outcome to depend \emph{both} on the treatment she actually receives, $D_i$, and the experimental arm to which she is assigned, $Z_i$.
@@
 For details, see Appendix \ref{append:exclusion}.
+%\todo[inline]{@Frank, do we need to say a bit more about these testable implications or is it too technical? (Enrique)}
 
@@
 %By additionally examining \emph{outcome data} in the choice arm, it is possible to say more. 
-We now show how our experimental design, henceforth the ``controlled choice design,'' combined with the exclusion restrictions from \eqref{eq:exclusion0} and \eqref{eq:exclution1} can be used to point identify a number of interesting and economically-relevant causal quantities without the need for additional structural restrictions.
+We now show how our experimental design, henceforth the ``controlled choice design,'' combined with the exclusion restrictions from \eqref{eq:exclusion0} and \eqref{eq:exclusion1} can be used to point identify a number of interesting and economically-relevant causal quantities without the need for additional structural restrictions.
 First we identify the treatment on the treated (ToT) and treatment on the untreated (TuT) effects, defined as follows:
@@
 
-\section{Is there space for paternalism?}
+\section{Examining paternalism}
 \label{exploring}
@@
 From the lens of rational choice it is unsurprising that we find the $\text{ToT}>\text{TuT}$, but the argument for compulsory treatment centers on the more surprising result that we find $\text{TuT}>0$.
-Hence an investigation of the case for paternalism requires that we delve into understanding why individuals who should apparently have chosen the intervention did not do so.
-
-Discounting is one explanation for our results.
+We now investigate several potential explanations for why this might be the case in our context.
+
+\paragraph{Learning.} A first explanation involves learning.
+We were bringing a new contract into an environment that had not previously featured commitment; perhaps clients required experience to understand its benefits?
+Given the strongly positive impact of forcing, our clearest hypothesis would be that clients forced once would choose commitment if subsequently given the chance to do so.
+While the sample size for this is small, we do have a group of 240 clients who were exposed to the experiment in one round and then returned to take another loan at a branch where the choice of commitment was offered.
+Table \ref{learning_table} shows the results of this analysis.
+While this regression is underpowered, the point estimate on prior assignment to the commitment contract is actually negative.
+Hence the window available to us on learning provides little comfort that the lack of voluntary compliance is simply a matter of inexperience with commitment.\footnote{\textcolor{blue}{Risk could be another alternative potential explanation for low take up of the commitment contract.
+Appendix \ref{App_FOSD} shows however that the distribution of financial cost savings of the monthly payment contract first-order stochastically dominates that of the status quo contract, so that (assuming these are the distributions faced by borrowers) the former should be preferred by borrowers regardless of their degree of risk aversion.
+See the Appendix for more details.}}
+
+\paragraph{Time discounting.} Discounting is a second explanation for our results.
 Using no discounting we find a decrease in the financial cost of credit, but the intervention inherently imposes up-front costs (early payment) in return for delayed benefits (recovery of pawn).
-Highly impatient individuals might therefore rationally choose not comply although our measure would show a benefit for them.
-To investigate this we can calculate the Net Present Value of the $TUT$ on financial cost given the average timing of repayment and pawn recovery at different discount rates.
-Figure \ref{fc_discount_rates} shows the results of this exercise, illustrating that non-choosers continue to see significant decreases in NPV financial costs up to monthly discount rates of 40\%, and the NPV remains negative for rates up to 90\% per month.
-Given that only 30\% of the sample reports a monthly discount rate above 50\%, we think that discounting is unlikely to explain non-compliance among those who appear to benefit.
-
-%Remaining exercises will use baseline survey data. Explain why we think this is ok: treatment effects don't change much when restricting the sample.
-
-If commitment benefits among non-compliers cannot be explained by rational choice, the canonical behavioral story would center on time inconsistency.
+Highly impatient individuals might therefore rationally choose not comply although our measure would show a benefit for them in undiscounted returns.
+To investigate this we can calculate the Net Present Value of the $TUT$ on financial cost given the %average
+timing of repayment and pawn recovery, for different discount rates.
+Figure \ref{fc_discount_rates} shows the results of this exercise, illustrating that non-choosers continue to see significant decreases in NPV financial costs up to annual discount rates of 4,000\%, and the NPV remains negative at 10,000\% discount rates.
+Given this, we think that discounting is unlikely to explain non-compliance among those who appear to benefit.
+
+\paragraph{Present bias.} If commitment benefits among non-compliers cannot be explained by rational choice, the canonical behavioral story would center on time inconsistency.
 While commitment is useful to anyone with hyperbolic time preferences, only those who are sophisticated will demand it.
-A large share of naive hyperbolics in the population could therefore drive a large $TUT$.
-Our baseline survey included standard questions about discount rates between today and a month in the future versus discount rates between three and four months in the future.
-This allows us to classify borrowers who display more impatience over immediate delays as time inconsistent.
+A large share of naive hyperbolics in the population could therefore drive a large $TuT$.
+Our baseline survey included standard questions about discount rates between today and a month in the future versus discount rates between three and four months in the future.\footnote{The remaining exercises in the paper will use information from the intake survey, and hence use only the subset of individuals who responded to the survey.
+While this is a selected sample, we believe this to be benign in that the impacts estimated using the full and survey-respondent sample are very similar.}  This allows us to classify borrowers who display more impatience over immediate delays as time inconsistent.
 This measure of financial hyperbolicity is widely used in survey research, although it is not without problems.\footnote{Our measure is dichotomous, and is not incentivized.
@@
 If measurement of hyperbolicity were perfect, the sample should then be comprised of three groups:  the sophisticated hyperbolics who chose commitment, the time-consistent non-compliers (for whom forcing will not be effective) and the naive hyperbolic non-compliers (for whom it will).
-This would imply that the forcing effect should arise entirely from within hyperbolic non-compliers, a fact which can be checked by estimating the $TUT$ conditional on hyperbolicity.
-
-We can calculate the relative contributions of any two groups $X_i=1$ or $X_i=1$ to the TUT among the non-compliers as follows:
+This would imply that the forcing effect should arise entirely from within hyperbolic non-compliers, a fact which can be checked by estimating the $TuT$ conditional on hyperbolicity.
+
+We can calculate the relative contributions of any two groups $X_i=0$ or $X_i=1$ to the $TuT$ among the non-compliers as follows:
 
     \begin{align*}
-        1=& \frac{\mathbb{E}[Y_{1i}-Y_{0i} | D_i=0, X_i=1]}{TuT}\Pr(X_i=1 | D_i=0) \\
-        \quad &+ \frac{\mathbb{E}[Y_{1i}-Y_{0i}| D_i=0, X_i=0]}{TuT}\Pr(X_i=0 | D_i=0)
+        1=& \frac{\mathbb{E}[Y_{1i}-Y_{0i} | C_i=0, X_i=1]}{TuT}\Pr(X_i=1 | C_i=0) \\
+        \quad &+ \frac{\mathbb{E}[Y_{1i}-Y_{0i}| C_i=0, X_i=0]}{TuT}\Pr(X_i=0 | C_i=0)
     \end{align*}
 
-If, as theory would predict, the $TUT$ arises solely from hyperbolics then the former term will be 1 and the latter 0.
-
-A second behavioral explanation may arise from the fact that  \hl{XX\%} of the control participants believe they have a 100\% chance of recovering their pawn, while in truth only 56\% will do so.
+If, as theory would predict, the $TuT$ arises solely from hyperbolics then the former term will be 1 and the latter 0.
+
+\paragraph{Sure confidence.} A second behavioral explanation may arise from the fact that  74\% of the control participants believe they have a 100\% chance of recovering their pawn, while in truth only \hl{56\%} will do so.
 This suggests a market characterized by over-optimism.
@@
 
-Figure \ref{tut_beh_partition} shows the relative contributions of present bias and sure-confidence for the $TUT$, and Figure \ref{tot_beh_partition} the analagous contributions for the $TOT$.
+\todo[inline]{check in all the text we have used 56\% as the number that dont recover.}
+
+Figure \ref{tut_beh_partition} shows the relative contributions of present bias and sure-confidence for the $TuT$.
 In each figure the orange bar represents the contribution from those who do not possess the attribute, and the blue bar from those that do.
-Looking first at the $TUT$, we see that the forcing effect is localized mostly to those who are \textit{not} time inconsistent, contradicting naive hyperbolicity as the justification for paternalism.
-Instead, we see sure-confidence being a category that completely isolates the $TUT$, suggesting that forcing works for those who do not consider repayment structure because they don't think they need it.
-Turning to the $TOT$, sure-confidence reverses its contribution in an intuitive way:  having chosen the intervention, it is mostly those who understand they may not repay that benefit.\footnote{The contribution of present bias to the $TOT$ is hard to parse in that we might expect the compliers to be entirely sophisticated hyperbolics.
-This attribute is strongly correlated with compliance, but the TOT is mostly generated by the time consistent among choosers.}  Our measure of hyperbolicity is based on unincentivized responses in a short survey and so is likely to be noisy; nonetheless we see no evidence here that it drives the forcing effect.
+We see that the forcing effect is localized mostly to those who are \textit{not} time inconsistent, contradicting naive hyperbolicity as the justification for paternalism.
+Instead, we see sure-confidence being a category that completely isolates the $TuT$, suggesting that forcing works for those who do not consider repayment structure because they don't think they need it.
+Our measure of hyperbolicity is based on unincentivized responses in a short survey and so is likely to be noisy; nonetheless we see no evidence here that it drives the forcing effect.
 Rather, this analysis suggests that paternalism is effective in this case is because of a group of overconfident borrowers who, heedless of the possibility of default, do not choose commitment and yet would benefit substantially from receiving it.
 
-\subsection{Who are the winners and losers from paternalism?}
+If the attribute of `sure confidence' proves so important in explaining the TUT, what are the determinants of this characteristic?
+In Figure \ref{determinants_sure} we plot the coefficient estimates from a regression that explains sure confidence with a battery of individual-level characteristics.
+Older males are more likely to be sure confident, as are those with more education.
+Taken at face value, it also appears to be the case that it is those with less financial stress, those who have had less trouble paying bills, and those more relied upon financially by family members.
+However, through a behavioral lens it is also possible that the type of person who is over-confident in their ability to repay a loan is also maintaining financial fictions in other domains of life, providing answers to the baseline survey questions that exaggerate their degree of economic security.
+In any case it appears that this attribute may be difficult to target with objective demographic criteria, a point to which we return.
+
+\subsection{Analyzing Choice versus Paternalism Using a Causal Forest} \label{sec:RF}
+
+\paragraph{Causal forests.} Figure \ref{fig:FanPark} uses a completely non-parametric approach to understand winners and losers from paternalism at the individual level, but these bounds are relatively wide.
+To make more precise statements, we can invoke a selection on observables assumption and use the Random Forest approach of \cite{athey2019generalized} to estimate Conditional Average Treatment Effects (causal RF), or the Conditional TuT and ToT (instrumental RF).
+These impacts allow us to think about whether individuals made `mistakes' in their choices.
+Specifically, for each client in the choice arm we want to know how much cost savings would she have gained had she chosen the opposite contract.
+We do this in two steps.
+First, we use  \cite{atheygrf}'s generalized random forests methodology to estimate the impact of the forced commitment arm relative to the control (forced status quo) at the individual level.
+The method generates a partition of the space of characteristics $X$, where each element of the partition is a leaf, and each leaf contains treatment and control clients with similar characteristics $x \in X$ which are used to calculate unbiased treatment effects for that leaf.
+The optimal partition is that which minimizes expected mean squared error of treatment effects predictions out-of-sample.
+The tree is honest because it uses one sample to build the tree and another one to estimate treatment effects within that tree.
+\cite{atheygrf} show that their treatment effects are asymptotically normal, which allows us to construct confidence intervals for our treatment estimate in each leaf.
+This method gives us the causal effect on financing cost of getting the forced commitment contract instead of the status quo contract for a client $i$ with characteristics $x_i$; call it $TE^{F}_{i}(x_i)$.\footnote{Figure \ref{causal_tree1} and \ref{causal_tree2} provide an illustration of the splits (leaves) that emerge from our implementation of the RF.
+\todo[inline]{I think we should list in a footnote which are the `wide' variables we are using.}}
+
+\paragraph{Personalized benefit results.} Using the test provided by \cite{chernozhukov2018generic}, we reject the null of homogeneity in treatment effects and so begin our analysis of heterogeneity confident that it exists.
+Figure \ref{heterogeneous_effects} illustrates the substantial impact of the forced commitment arm on APR, financial cost and other outcomes.
+More than 90\% of the individuals have APR saving effects, and even in the upper bound confidence interval more than half of individuals benefit.
+
+\paragraph{Estimates of financial cost `mistakes'.} In a second step we predict treatment effects for clients \textit{in the Choice arm} using the partition into leaves and the treatment effect from step 1, that is client $j$ is imputed the treatment effect of the leaf corresponding to her characteristics $x_j$.
+We call this counterfactual treatment effect $\widehat{TE}^{F}_{j}(x_j)$.
+This is precisely the counterfactual we wanted, because it lets us relate observed individual choices with estimated individual-level treatment effects.\footnote{This extrapolation of the treatment effects assumes that choice itself --conditional on a given contract-- does not affect behavior (note the evidence in the prior section suggesting this is the case).
+Although the extrapolation is to another population, by randomization it is a statistically identical population with common support.} Armed with this, we say that a client made a ``mistake'' if either she chose the status quo contract and her $\widehat{TE}^{F}_{i}$ is negative (i.e.
+more cost saving from the Forced contract), or if she chose the Commitment contract and $\widehat{TE}^{F}_{i}$ is positive, (i.e.
+financial costs are larger for the Commitment contract).
+When a client made a choice mistake, we say that its money-metric values is the absolute value of $|\widehat{TE}^{F}_{i}|$.
+
+%Using the forcing arms and extrapolating to the choice arms.
+%Then, we predict these treatment effects for everybody in the choice arm using characteristics $x_i$.
+Let $\widehat{TE}^{fee}_{i}$ be the predicted financial cost savings for person $i$ of choosing the Forced Commitment contract rather than the status quo one, divided by the size of her loan (i.e.
+the negative value of the predicted treatment effect on financial cost for person $i$).
+$\widehat{TE}^{sq}_{i}$ is the analogous for the status quo contract.
+We define the choice of person $i$ to be a ``mistake'' if
+
+%\begin{equation}
+% \{ i \; \text{chose} \; sq \; \text{and} \; \;  \widehat{TE}^{fee}_{i}>\widehat{TE}^{sq}_{i} + z \} \; \text{or} \; \{ i \; \text{chose} \; fee \; \text{and} \; \;  \widehat{TE}^{fee}_{i}<\widehat{TE}^{sq}_{i} - z \}
+%\end{equation}
+
+Since the prediction of the treatment effect is an estimate and has noise, we do two things.
+First, we normalize $\widehat{TE}^{F}_{i}$ by the value of the loan of person $i$ and introduce a threshold parameter $z$ and say that a choice is a ``mistake'' if the alternative contract would generate greater than $z$ in savings.
+We vary this threshold from 0\% to 15\% of the value of the loan.
+Second, we take into account uncertainty in estimation of treatment effects and report results using the extremes of the 95\% confidence interval bounds for $\widehat{TE}^{F}_{i}$.
+
+%Figure \ref{choose_wrong}(a) plots on the Y axis the fraction of clients that made a choice ``mistake'' and on the X axis the threshold $z$.
+When $z=0$, we calculate that about 82\% of clients in the Choice arm chose contracts that induced \textit{higher} financial cost.
+Most mistakes are failures to choose the fee-commitment contract ({97}\%), while only {4}\% of those who chose the fee-commitment contract would have been better in the status-quo one.
+The average mistake in pesos is \$250.
+%(90\% confidence interval [140,390]).
+
+ Figure \ref{choose_wrong}, Panel A shows the results of this exercise, reinforcing the general superiority of commitment.
+Among choosers, only 25\% would have had superior outcomes had they not complied, whereas among non-choosers almost 80\% made a mistake according to this definition.
+Because this arm is comprised of 89\% non-choosers, the overall rate of mistake in the arm was around 70\%.
+As we increase the threshold on the size of the mistake necessary to be classified as having made the wrong choice, by definition the share in both groups falls, and among choosers the number making an error falls quite quickly to zero.
+
+ %However, the fraction of non-choosers making a mistake remains almost 20\% even at the highest threshold used (\$80 pesos), and panel b shows the \textcolor{red}{Complete this when understand figure}.
+Panel C conducts a related but distinct exercise, showing the fraction of the entire control sample who would do better if assigned to the Forced arm; using the smallest threshold this fraction is over 95\%, showing that in this context there is an almost across-the board welfare benefit arising from this arm.
+Since the only potential financial cost of the forced arm arises from individuals who would be induced to partially repay but then default anyways, this result suggests that very few such borrowers exist.
+
+Panel C of this figure replicates this exercise for the forced commitment arm, with the difference being that the relevant treatment effect to match is now the ATE of the forced commitment arm.
+This allows us to identify the winners and losers from paternalism in a nuanced manner, since members of groups with CATEs$<$0 are hurt and everyone else is helped.
+Because the ATE$>$TUT, this exercise results in an even larger fraction of individuals benefiting from commitment; here we find that fully 87\% of individuals are better off being forced into commitment than staying in the control.
+This now allows us to make a stronger statement in favor of paternalism; not only is the case that forcing commitment generates large benefits on average, but it is also generating benefits for almost 90\% of the forced population.
+
+\subsection{Can we target paternalism?}
+
+Despite having shown such a large majority of individuals benefit from paternalism, it is still natural to question whether we are able to target commitment in such a manner as to only force it upon those who benefit.
+For a financial firm to engage in this type of targeting under real-world circumstances, we must impose several constraints on the targeting rule.
+First, it will in general not be possible to use the numerous subjective and unverifiable questions we asked in the baseline survey as inputs to the rule because the answers to these questions can be manipulated by the clients, and would likely change when they become incentivized.
+Secondly, it will not be attractive for a commercial firm to ask individuals whether they want to voluntarily accept commitment and then to force upon those who say no against their will.
+So the choice variable itself cannot be used to target other than in a voluntary program.
+This leaves us with only a few objective covariates that could be used to target: age, gender, HS education or above, and whether that individual has ever pawned before.
+
+\paragraph{Narrow inputs targeting.} To  consider targeting effectiveness we must begin from an individual-specific ground truth, which we take from our estimated RF from Section \ref{sec:RF}  which used the `wide' set of covariates (wide RF).
+We then analyze how well we can predict the losers from paternalism using the `narrow' set of non-manipulable covariates listed above (narrow RF).
+Figure \ref{wide_narrow_forests} shows the relationship between the CATEs estimated from the RF using the `wide' and `narrow' covariates.
+Not only is it visually obvious from this figure that we generate substantially less heterogeneity when using the narrow covariate set, but in fact the Chernozhukov test for heterogeneity on the narrow RF is no longer significant.
+This constitutes preliminary evidence that the commercially feasible covariate set we collected will not be effective at targeting paternalism.
+
+\paragraph{Targeting assessment.} To more directly examine the implications of attempting to target commitment, we use two different techniques to predict who should be assigned to the commitment arm.
+The first of these is the narrow RF displayed above paired with the decision rule which assigns clients to forcing commitment in a  leaf if and only if  the CATE of the Forcing arm is positive.
+In the second we estimate a standard Logit model using as outcome an indicato of positive benefit from forcing commitment as estimated in the wide RF, and the narrow targeting variables as the explanatory variables.
+Figure \ref{targeting_rules} plots the same densities of net benefit as were shown before, where we now take the wide RF as the ground truth of the benefits of forcing everyone into commitment, and the welfare under the two targeting rules shown for comparison.
+Given the poor explanatory power of the narrow criteria it is unsurprising to see that the information gain from using these variables is small; the fraction of the whole sample benefiting when we go from universal forcing to narrow RF targeted forcing rises only marginally from 86.7\% to 88.4\%.
+When we look at the Logit targeting we see that it has actually made targeting substantially worse; this behavior is driven by the confluence of the poor explanatory power of the narrow variables with the fact that the Logit matches the correct sample fraction of ones, therefore making numerous Type II errors in an environment where commitment is beneficial for most.
+%and hence actually reduces the share benefiting.
+
+%The comparative points are illustrated in
+Table \ref{hit_miss_rule} shows Type I and Type II error rates for each of six rules:  all to control, all to treatment (Forcing), optimal, Narrow RF targeting, Logit targeting, and Choice.
+While the Narrow RF is able to correctly assign roughly half of those who do not benefit from commitment to control, it also incorrectly allocates 5.4\% of the sample that would have gained from treatment to control, and so on net it only improves the correct targeting rate by about 1.5 percentage points relative to universal Forcing.
+The Logit is less successful at predicting benefits and in particular makes many Type II errors, resulting in a net targeting performance that is actually worse than universal forcing.
+The underlying cause of the weak performance of targeting is that the attribute that predicts loss from forcing (not being sure confident and not choosing the commitment) is largely behavioral and not easily predicted with basic covariates.
+Self-targeting through choice proves to be little better than assigning everyone to the control, given the low take-up rate and the presence of both Type I and Type II errors in the Choice arm.
+Over 71\% of individuals in the Choice arm made a mistake, weighting the results among choosers and non-choosers by their frequency.
+The takeaway is that given low take-up, the large fraction of the sample benefiting from commitment, and the weak predictive power of the narrow covariates, in this case universal paternalism appears to be an attractive contract.
+
+%OLD SECTION 6 TEXT:
 
@@
 
-As shown above in Section \ref{experiment}, the ATE of the commitment contract from the forced arm is positive and significant, both economically and statistically.
+%As shown above in Section \ref{experiment}, the ATE of the commitment contract from the forced arm is positive and significant, both economically and statistically.
 But this is only an average effect: a positive ATE is still consistent with negative individual treatment effects for some borrowers.
-Unless she is a strict utilitarian, any policymaker who is considering outlawing the \emph{status quo} contract in favor of the commitment contract needs to consider the extent and magnitude of harm that such a paternalistic policy will cause to \emph{individual} borrowers.
+
+%Unless she is a strict utilitarian, any policymaker who is considering outlawing the \emph{status quo} contract in favor of the commitment contract needs to consider the extent and magnitude of harm that such a paternalistic policy will cause to \emph{individual} borrowers.
 Our TuT and ToT results from Section \ref{sec:randchoice} partially address this concern.
@@
 
-\subsubsection{Random Forest Bounds on Treatment Effects}
-
-\subsection{Relating Random Forest Impacts to Observed Choice}
-
-\todo[inline]{Frank/Issac: need to discuss confidence interval construction for the mistakes exercise.
+%\subsubsection{Random Forest Bounds on Treatment Effects}
+
+%\todo[inline]{Frank/Issac: need to discuss confidence interval construction for the mistakes exercise.
 I'm not 100\% sure about it.
@@
 
-\todo[inline]{Issac: add in the picture for the ToT/TuT version of the ``mistakes'' exercise \& histograms of treatment effects by groups.
+%\todo[inline]{Issac: add in the picture for the ToT/TuT version of the ``mistakes'' exercise \& histograms of treatment effects by groups.
 We already have the histogram in figure 15 for the ATE.
@@
 
-\todo[inline]{Frank draft: The first exercise looks at ``mistakes.'' These are defined by predicting treatment effects for the people in the \emph{choice} arm using their covariates.
+%\todo[inline]{Frank draft: The first exercise looks at ``mistakes.'' These are defined by predicting treatment effects for the people in the \emph{choice} arm using their covariates.
 If the treatment effect is positive and they don't choose treatment, this is a mistake.
@@
 
-To more directly interrogate self-selection in this context, we would like to be able to relate \textit{individual} choices over commitment to the \textit{individual} counterfactual outcomes that borrowers would have realized in different states of nature.
+%To more directly interrogate self-selection in this context, we would like to be able to relate \textit{individual} choices over commitment to the \textit{individual} counterfactual outcomes that borrowers would have realized in different states of nature.
 To achieve this, we can use the honest causal forest method to impute borrower-specific treatment effects of the assignment to Commitment, and then map this estimate to the choices individuals make in the Choice arm.
-
-Specifically, for each client in the choice arm we want to know how much cost savings would she have gained had she chosen the opposite contract.
-We do this in two steps.
-First, we use  \cite{atheygrf}'s generalized random forests methodology to estimate the impact of the Forced arm relative to the control at the individual level.
-The method generates a partition of the space of characteristics $X$, where each element of the partition is a leaf, and each leaf contains treatment and control clients with similar characteristics $x \in X$ which are used to calculate unbiased treatment effects for that leaf.
-The optimal partition is that which minimizes expected mean squared error of treatment effects predictions out-of-sample.
-The tree is honest because it uses one sample to build the tree and another one to estimate treatment effects within that tree.
-\cite{atheygrf} show that their treatment effects are asymptotically normal, which allows us to construct confidence intervals for our treatment estimate in each leaf.
-This method gives us the causal effect on financing cost of getting the Forced Commitment contract instead of the status quo contract for a client $i$ with characteristics $x_i$; call it $TE^{F}_{i}(x_i)$.
-Figure \ref{heterogeneous_effects} presents the PDFs of the estimated individual-level treatment effects for our three main outcomes, showing the estimated effect as well as the distributions of the upper and lower bounds.
-The figures illustrate the substantial impact of the Forced arm particularly on APR, for which more than 90\% of the individuals have positive treatment effects and even in the upper bound confidence interval more than half of individuals benefit.
-
-Then in step 2 we predict treatment effects for clients \textit{in the Choice arm} using the partition into leaves and the treatment effect from step 1, that is client $j$ is imputed the treatment effect of the leaf corresponding to her characteristics $x_j$.
-We call this counterfactual treatment effect $\widehat{TE}^{F}_{j}(x_j)$.
-This is precisely the counterfactual we wanted, because it lets us relate observed individual choices with estimated individual-level treatment effects.\footnote{This extrapolation of the treatment effects assumes that choice itself --conditional on a given contract-- does not affect behavior (note the evidence in the prior section suggesting this is the case).
-Although the extrapolation is to another population, by randomization it is a statistically identical population with common support.} Armed with this, we say that a client made a ``mistake'' if either she chose the status quo contract and her $\widehat{TE}^{F}_{i}$ is negative (i.e.
-more cost saving from the Forced contract), or if she chose the Commitment contract and $\widehat{TE}^{F}_{i}$ is positive, (i.e.
-financial costs are larger for the Commitment contract).
-When a client made a choice mistake, we say that its money-metric values is the absolute value of $|\widehat{TE}^{F}_{i}|$.
-
-%Using the forcing arms and extrapolating to the choice arms.
-%Then, we predict these treatment effects for everybody in the choice arm using characteristics $x_i$.
-Let $\widehat{TE}^{fee}_{i}$ be the predicted financial cost savings for person $i$ of choosing the Forced Commitment contract rather than the status quo one, divided by the size of her loan (i.e.
-the negative value of the predicted treatment effect on financial cost for person $i$).
-$\widehat{TE}^{sq}_{i}$ is the analogous for the status quo contract.
-We define the choice of person $i$ to be a ``mistake'' if
-
-%\begin{equation}
-% \{ i \; \text{chose} \; sq \; \text{and} \; \;  \widehat{TE}^{fee}_{i}>\widehat{TE}^{sq}_{i} + z \} \; \text{or} \; \{ i \; \text{chose} \; fee \; \text{and} \; \;  \widehat{TE}^{fee}_{i}<\widehat{TE}^{sq}_{i} - z \}
-%\end{equation}
-
-Since the prediction of the treatment effect is an estimate and has noise, we do two things.
-First, we normalize $\widehat{TE}^{F}_{i}$ by the value of the loan of person $i$ and introduce a threshold parameter $z$ and say that a choice is a ``mistake'' if the alternative contract would generate greater than $z$ in savings.
-We vary this threshold from 0\% to 15\% of the value of the loan.
-Second, we take into account uncertainty in estimation of treatment effects and report results using the extremes of the 95\% confidence interval bounds for $\widehat{TE}^{F}_{i}$.
-
-Figure \ref{choose_wrong}(a) plots on the Y axis the fraction of clients that made a choice ``mistake'' and on the X axis the threshold $z$.
-When $z=0$, we calculate that about 82\% of clients in the Choice arm chose contracts that induced \textit{higher} financial cost.
-Most mistakes are failures to choose the fee-commitment contract ({97}\%), while only {4}\% of those who chose the fee-commitment contract would have been better in the status-quo one.
-The average mistake in pesos is \$250.
-%(90\% confidence interval [140,390]).
-As we increase the threshold on the size of the mistake necessary to be classified as having made the wrong choice, by definition the share in both groups falls, and among Choosers the number making an error falls quite quickly to zero.
-However, the fraction of non-choosers making a mistake remains almost 20\% even at the highest threshold used (\$80 pesos), and panel b shows the \textcolor{red}{Complete this when understand figure}.
-Panel C conducts a related but distinct exercise, showing the fraction of the entire control sample who would do better if assigned to the Forced arm; using the smallest threshold this fraction is over 95\%, showing that in this context there is an almost across-the board welfare benefit arising from this arm.
-Since the only potential financial cost of the forced arm arises from individuals who would be induced to partially repay but then default anyways, this result suggests that very few such borrowers exist.
 
@@
 In a pawnshop borrowing context, we study whether forcing borrowers into frequent payment commitment contracts reduces their borrowing costs, compared to a contract that does not provide commitment to pay monthly.
-Even though we are charging them fees, their borrowing costs are actually reduced by 9.4\%, and they recover their pawn with 26\% higher likelihood.
-Moreover they themselves seem to like this contract, as they are 100\% more likely to come back and pawn again when they get it.
+Even though we are charging them fees,  borrowing costs under forced commitment are actually reduced by 9.4\%, and pawnrecovery is 26\% higher.
+Moreover they themselves seem to like this contract, as they are twice as likely to come back and pawn again when they are assigned to forced commitment.
 That is, commitment matters and it seems beneficial.
-Examining treatment heterogeneity we find that almost all clients benefit from the commitment contract.
-However when given choice between the commitment and the status quo contract only 10\% choose the former one and thus forgo important benefits.
+
+We examine treatment heterogeneity using a range of methods, from bounds that make no assumptions, exploiting a mild exclusion restrictions and the innovative controlled choice design to gain point identificatoin of TuT and ToT, and invoking seletion on observables to estimate treatment effects at the person level.
+We find that a large majority of clients benefit from the commitment contract, but that when given choice between the commitment and the status quo contract only 10\% choose the former one and thus forgo important financial benefits.
 We also find that overconfident clients experience larger treatment effect cost savings from the commitment contract but at the same time have smaller demand for it.
-
-A simple model shows that present bias with naivete parsimoniously explains all findings.
-This suggests that it is possible in our context to advance an individual's interests by restricting her freedom of choice ---although we caution that our outcome measure focuses on financing cost and is not a comprehensive measure of welfare.
-These results spurred --although we cannot show they caused-- Lender $P$ to offer frequent payment contacts, although Lender $P$ was uncomfortable forcing these contracts on clients.
+(\hl{Is it true that they have smaller demand?
+Which Figure shows this?
+If so we should say this above and not only in the conclusion})
+%A simple model shows that present bias with naivete parsimoniously explains all findings. 
+The analysis suggests that it is possible in our context to advance an individual's financial  by restricting her freedom of choice ---although we caution that our outcome measure focuses on financing cost and is not a comprehensive measure of welfare.
+%These results spurred --although we cannot show they caused-- Lender $P$ to offer frequent payment contacts, although Lender $P$ was uncomfortable forcing these contracts on clients.
 They hoped that clients would eventually learn which contract was better for them.
 
-Methodologically, to our knowledge this is the first paper in economics that uses machine learning methods and a combination of choice and forcing arms to estimate personalized counterfactual treatment gains to ask whether treatment take up is positively selected on benefits, a hypothesis we reject.
+%Methodologically, to our knowledge this is the first paper in economics that uses machine learning methods and a combination of choice and forcing arms to estimate personalized counterfactual treatment gains to ask whether treatment takeup is positively selected on benefits, a hypothesis we reject.
 
@@
 Choice may also fare better with other contracts besides the fee-commitment one we used.
-We experimented with a ``softer'' commitment contract in the form of a personal promise, and found that although Soft Commitment contracts do indeed elicit more interest they did not cause changes in behavior.
+We experimented with a ``softer'' commitment contract in the form of a personal promise, and found that although this soft commitment contract  elicited more interest, it did not cause changes in behavior.
 
@@
 First, it would be useful to tease out the roles played by naivete about self control problems and biased expectations about income shocks in driving low demand for commitment.
-Second, one could ask whether other types of contracts ---for instance those that provide some insurance against shocks---  induce larger demand and better performance than the ones we tried.
-Third, testing and quantifying selection to pawnshop lenders based on sophistication could be important for regulators.
+Second, one could ask whether other types of contracts %---for instance those that provide some insurance against shocks---
+induce larger demand and better performance than the ones we tried.
+Third, testing and quantifying of there is selection to pawnshop lenders based on unsophistication could be important for regulators.
 Fourth, collecting broader measures of welfare to use as outcomes --e.g.
@@
     \scriptsize
-    \hl{Add timeline figure}
+
 %\textit{Do file: }  \texttt{ss\_att.do}
@@
     \end{center}
-      \scriptsize
+      \scriptsize  This figure plots the relationship between the Athey-Wager heterogeneous treatment effects estimated using the `wide' set of determinants (all available covariates), versus the `narrow' set (only age, gender, HS education, and previous borrowing).
+The scatterplot graphs one estimate versus the other, and the histograms show the densities of the respective heterogeneity estimates.
 
@@
     \end{center}
-      \scriptsize
-
-%\textit{Do file: } \texttt{wide_narrow_forests.do}       
+      \scriptsize   This figure plots the (reversed) cumulative densities of the estimated benefits from the casual forest for three different rules.
+The blue line plots the HTEs from the `wide' random forest for the Forcing arm, which we take as the ground truth for actual impacts.
+The green line plots HTEs if we first target individuals using the variables in the `narrow' forest, and only assign individuals to commitment if they are on a leaf whose predicted forcing benefit is positive.
+The red line uses a Logit regression to predict which individuals benefit from treatment, and assigns all individuals to the arm predicted to be best for them.
+
 \end{figure}

### 2023-07-04 OA.tex
add loan as predictor in narrow and wide forest

@@
 \begin{center}
-\scriptsize{\input{./Tables/learning_exp_pres.tex}}
+\scriptsize{\input{./Tables/learning_exp.tex}}
 \end{center}
@@
 \begin{figure}[H]
-    \caption{Partition of TuT by behavioral variables.}
+    \caption{Partition of TUT by behavioral variables.}
     \label{tut_beh_partition}
@@
     \end{center}
-     \scriptsize  This figure performs a partition of the Treatment on the Untreated, estimating the share of the effect that arises within each of two binary categories.
+     \scriptsize  This figure performs a partition of the Treatment on the Untreated (FC), estimating the share of the effect that arises within each of two binary categories.
 The top bars examine present bias (individuals are more impatient over one-month time horizon than they are between three and four months).
@@
 \begin{figure}[H]
-        \caption{Empirical CDF of Financial Cost: fee-forcing vs status-quo \textcolor{red}{\hl{MAY NEED UPDATING}}}
+        \caption{Empirical CDF of Financial Cost: Forced commitment vs Control }
     \label{ecdf_fc}
-    \begin{center}
-        \centering
-        \includegraphics[width=0.55\textwidth]{Figuras/cdf_fc_pro_2.pdf}
+
+    \begin{center}
+       \begin{subfigure}{0.49\textwidth}
+        \caption{APR}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/cdf_apr.pdf}
+    \end{subfigure} 
+   \begin{subfigure}{0.49\textwidth}
+        \caption{Financial cost}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/cdf_fc_admin.pdf}
+    \end{subfigure} 
     \end{center}
@@
 It does this separately for the fee-forcing contract and for the status-quo contract.
-The doted line at the bottom is the difference of the status-quo CDF minus the fee-forcing CDF.
+The dotted line at the bottom is the difference of the control CDF minus the forced CDF arm.
 It shows that the CDF of the status quo contract is always below that of the fee-forcing (and this difference is significant for the points indicated by the blue line), and therefore that the former first-order stochastically dominates the later for weakly decreasing utility functions; see Proposition \ref{eq_fosd}.
-    % \texttt{ecdf\_fc.do}}
-\end{figure}
-
-\begin{figure}[H]
-        \caption{Empirical CDF of APR: fee-focing vs status-quo \textcolor{red}{\hl{MAY NEED UPDATING}}}
-    \label{ecdf_fc}
-    \begin{center}
-        \centering
-        \includegraphics[width=0.55\textwidth]{Figuras/cdf_eff_pro_2.pdf}
-    \end{center}
-    \scriptsize This figure plots the empirical cumulative distribution of financial cost.
-It does this separately for the fee-forcing contract and for the status-quo contract.
-The doted line at the bottom is the difference of the status-quo CDF minus the fee-forcing CDF.
-It shows that the CDF of the status quo contract is always below that of the fee-forcing (and this difference is significant for the points indicated by the blue line), and therefore that the former first-order stochastically dominates the later for weakly decreasing utility functions; see Proposition \ref{eq_fosd}.
-    % \texttt{ecdf\_eff.do}}
+    % \texttt{fosd_ecdf.do}}
 \end{figure}
@@
 
-\todo[inline]{Issac: re-run this exercise with removing the propensity score weights $p(Z)$. Presumably it shouldn't change anything, but it's simpler to explain what we do and probably less noisy
+\todo[inline]{Issac: re-run this exercise with removing the propensity score weights $p(Z)$. Presumably it shouldn't change anything, but it's simpler to explain what we do and probably less noisy}
 
@@
 \end{table}
-
-}
 
@@
 
-This appendix provides formal proofs of the results described in Section \ref{sec:randchoice}, using the notation and assumptions described in Section \ref{sec:potentialOutcomes}.
+This appendix provides proofs of the results described in Section \ref{sec:randchoice}, using the notation and assumptions described in Section \ref{sec:potentialOutcomes}. 
 To simplify the presentation, we omit $i$ subscripts throughout this section.
-The following assumption collects our exclusion restriction and the key features of our experimental design.
+We also use the shorthand $Z_0 \equiv \mathbbm{1}(Z=0)$, $Z_1 \equiv \mathbbm{1}(Z=1)$, and $Z_2 \equiv\mathbbm{1}(Z=2)$.
+For convenience, the following assumption collects our exclusion restriction and the key features of the constrained choice design.
 
@@
 
-\begin{lem}\mbox{}
+\subsection{Point Identification}
+
+We first show that the TOT, TUT, ASB, and ASL effects are point identified under the constrained choice design.
+It follows that the ASG effect, $(\text{TOT} - \text{TUT})$, is likewise point identified.
+
+\begin{lem}
+Under Assumption \ref{assump:randchoice},
 \label{lem_randchoice}
@@
        \item $\mathbbm{E}(Y|D=0,Z=2) = \mathbbm{E}(Y_0|C=0)$
-       \item $\mathbbm{E}(Y|D=1,Z=2) = \mathbbm{E}(Y_1|C=1)$
+       \item $\mathbbm{E}(Y|D=1,Z=2) = \mathbbm{E}(Y_1|C=1)$.
    \end{enumerate} 
@@
 establishing part (iv).
-Similarly, $Z=2$ implies that $D=1$ if and only if $C=1$ and hence
+For part (v) $Z=2$ implies that $D=1$ if and only if $C=1$ and hence
 \[
-\mathbbm{E}(Y|D=1, Z=2) = \mathbbm{E}(Y_1|D=1, Z=2) = \mathbbm{E}(Y_1|C=1, Z=2)= \mathbbm{E}(Y_1|C=1)
+\mathbbm{E}(Y|D=1, Z=2) = \mathbbm{E}(Y_1|D=1, Z=2) = \mathbbm{E}(Y_1|C=1, Z=2)= \mathbbm{E}(Y_1|C=1). %\qedhere
 \]
-establishing part (v).
 \end{proof}
 
-\begin{prop} \mbox{}
+\begin{prop} 
+Under Assumption \ref{assump:randchoice},
     \begin{enumerate}[(i)]
-        \item $\text{ToT} \equiv \mathbbm{E}(Y_1 - Y_0|C=1)  = \displaystyle \frac{\mathbbm{E}(Y|Z=2) - \mathbbm{E}(Y|Z=0)}{\mathbbm{E}(D|Z=2)}$
-        \item $\text{TuT} \equiv \mathbbm{E}(Y_1 - Y_0|C=0) = \displaystyle \frac{\mathbbm{E}(Y|Z=1) - \mathbbm{E}(Y|Z=2)}{1 - \mathbbm{E}(D|Z=2)}$
+        \item $\text{TOT} \equiv \mathbbm{E}(Y_1 - Y_0|C=1)  = \displaystyle \frac{\mathbbm{E}(Y|Z=2) - \mathbbm{E}(Y|Z=0)}{\mathbbm{E}(D|Z=2)}$
+        \item $\text{TUT} \equiv \mathbbm{E}(Y_1 - Y_0|C=0) = \displaystyle \frac{\mathbbm{E}(Y|Z=1) - \mathbbm{E}(Y|Z=2)}{1 - \mathbbm{E}(D|Z=2)}$
         \item $\text{ASB} \equiv \mathbbm{E}(Y_0|C=1) - \mathbbm{E}(Y_0|C=0) = \displaystyle \frac{\mathbbm{E}(Y|Z=0) - \mathbbm{E}(Y|Z=2,D=0)}{\mathbbm{E}(D|Z=2)}$
-        \item $\text{ASL} \equiv \mathbbm{E}(Y_1|C=1) - \mathbbm{E}(Y_1|C=0) = \displaystyle \frac{\mathbbm{E}(Y|Z=2,D=1) - \mathbbm{E}(Y|Z=1)}{1 - \mathbbm{E}(D|Z=2)}$
+        \item $\text{ASL} \equiv \mathbbm{E}(Y_1|C=1) - \mathbbm{E}(Y_1|C=0) = \displaystyle \frac{\mathbbm{E}(Y|Z=2,D=1) - \mathbbm{E}(Y|Z=1)}{1 - \mathbbm{E}(D|Z=2)}$.
     \end{enumerate}
@@
 Re-arranging and substituting Lemma \ref{lem_randchoice}(i) and (iv),
-\begin{equation}
-\mathbbm{E}(Y_0|C=1)  = \frac{\mathbbm{E}(Y|Z=0) - \mathbbm{E}(Y_0|C=0) \mathbbm{P}(C=0)}{\mathbbm{P}(C=1)} =  \frac{\mathbbm{E}(Y|Z=0) - \mathbbm{E}(Y|Z=2,D=0) \mathbbm{E}(1 - D|Z=2)}{\mathbbm{E}(D|Z=2)}.
+\begin{align}
+\mathbbm{E}(Y_0|C=1)  &= \frac{\mathbbm{E}(Y|Z=0) - \mathbbm{E}(Y_0|C=0) \mathbbm{P}(C=0)}{\mathbbm{P}(C=1)}\nonumber\\ 
+&=  \frac{\mathbbm{E}(Y|Z=0) - \mathbbm{E}(Y|Z=2,D=0) \mathbbm{E}(1 - D|Z=2)}{\mathbbm{E}(D|Z=2)}.
 \label{eq:Y0C1}
-\end{equation}
+\end{align}
 Part (i) follows by combining \eqref{eq:Y0C1} with Lemma \ref{lem_randchoice}(v) and simplifying; part (iii) follows by combining \eqref{eq:Y0C1} with Lemma \ref{lem_randchoice}(iv) and simplifying.
@@
 Re-arranging and substituting Lemma \ref{lem_randchoice}(i) and (v),
-\begin{equation}
+\begin{align}
 \mathbbm{E}(Y_1|C=0) 
-= \frac{\mathbbm{E}(Y|Z=1) - \mathbbm{E}(Y_1|C=1)\mathbbm{P}(C=1)}{\mathbb{P}(D=0)} =\frac{\mathbbm{E}(Y|Z=1) - \mathbbm{E}(Y|Z=2,D=1)\mathbbm{E}(D|Z=2)}{\mathbb{E}(1-D|Z=2)}.
+&= \frac{\mathbbm{E}(Y|Z=1) - \mathbbm{E}(Y_1|C=1)\mathbbm{P}(C=1)}{\mathbb{P}(D=0)} \nonumber\\
+&=\frac{\mathbbm{E}(Y|Z=1) - \mathbbm{E}(Y|Z=2,D=1)\mathbbm{E}(D|Z=2)}{\mathbb{E}(1-D|Z=2)}.
 \label{eq:Y1C0}
-\end{equation}
+\end{align}
 Part (ii) follows by combining \eqref{eq:Y1C0} with Lemma \ref{lem_randchoice}(iv) and simplifying; part (iv) follows by combining \eqref{eq:Y1C0} with Lemma \ref{lem_randchoice}(v) and simplifying.
@@
 
-\todo[inline]{It looks like I still need to paste in the derivations of the ``regression'' approach to identifying the effects of interest. I will do this pronto! -Frank}
+\subsection{Regression-based Estimation of TOT, TUT, ASG, ASL, and ASB}
+
+We now show how a collection of just-identified, linear IV regressions can be used to consistently estimate the ATE, TOT, and TUT effects, along with each of the ingredients needed to construct the ASL and ASB.
+These results are used below to provide a recipe for cluster-robust inference for the ASG, ASL, and ASB effects.
+The first result provides a regression-based approach to estimate the ATE and TOT.
+
+\begin{prop} 
+Under Assumption \ref{assump:randchoice},
+\[
+Y = \mathbbm{E}(Y_0) + \text{ATE}\times Z_1 + \text{TOT} \times Z_2 D + U
+\]
+where $\mathbb{E}(U|Z) = 0$.
+Therefore, under standard regularity conditions, an IV regression of $Y$ on an intercept, $Z_1$ and $Z_2 D$ with instruments $(1, Z_1, Z_2)$ provides a consistent estimator of the ATE and TOT effects.
+\end{prop}
+
+\begin{proof}
+By Assumption \ref{assump:randchoice} (iii),
+\begin{align*}
+Y &= Z_0 Y_0 + Z_1 Y_1 + Z_2[(1 - C) Y_0 + CY_1]\\
+&= (Z_0 + Z_2)Y_0 + Z_1 Y_1 + Z_2C(Y_1 - Y_0)\\
+&= (Z_0 + Z_1 + Z_2)Y_0 + Z_1 (Y_1 - Y_0) + Z_2D(Y_1 - Y_0)\\
+&= Y_0 + Z_1 (Y_1 - Y_0) + Z_2D(Y_1 - Y_0).
+\end{align*}
+since $Z_2 D = Z_2 C$ and $(Z_0 + Z_1 + Z_2) = 1$.
+Thus, defining 
+\[
+U \equiv [Y_0 - \mathbbm{E}(Y_0)] + Z_1[(Y_1 - Y_0) - \text{ATE}] + Z_2 D[(Y_1 - Y_0) - \text{TOT}]
+\]
+by construction we have
+\[
+Y = \mathbbm{E}(Y_0) + \text{ATE} \times Z_1 + \text{TOT} \times Z_2 D+ U.
+\]
+Now, since $Z_2 D = Z_2 C$ and $Z$ is independent of $(Y_1, Y_0)$ by Assumption \ref{assump:randchoice} (i), we have
+\begin{align*}
+\mathbbm{E}(U|Z) &= [\mathbbm{E}(Y_0|Z) - \mathbbm{E}(Y_0)]  + Z_1[\mathbbm{E}(Y_1 - Y_0|Z) - \text{ATE}] +  \mathbbm{E}\left[Z_2 D\left\{(Y_1 - Y_0) - \text{TOT}\right\}|Z\right]\\
+&= [\mathbbm{E}(Y_0) - \mathbbm{E}(Y_0)]  + Z_1[\mathbbm{E}(Y_1 - Y_0) - \text{ATE}] + Z_2 \mathbbm{E}\left[C\left\{(Y_1 - Y_0) - \text{TOT}\right\}|Z\right]\\
+&= Z_2 \mathbbm{E}\left[C\left\{(Y_1 - Y_0) - \text{TOT}\right\}|Z\right].
+\end{align*}
+Finally, by iterated expectations
+\begin{align*}
+\mathbbm{E}\left[C\left\{(Y_1 - Y_0) - \text{TOT}\right\}|Z\right] &=  \mathbbm{P}(C=1|Z) \left[\mathbbm{E}(Y_1 - Y_0|C=1,Z)  - \text{TOT}\right]\\
+&= \mathbbm{P}(C=1)\left[\mathbbm{E}(Y_1 - Y_0|C=1) - \text{TOT} \right]=0
+\end{align*}
+since $Z$ is conditionally independent of $(Y_0, Y_1)$ given $C$, an implication of \ref{assump:randchoice} (i).
+\end{proof}
+
+The next proposition provides regression-based estimates of the ATE and TUT.
+\begin{prop}
+Under Assumption \ref{assump:randchoice}
+\[
+Y = \mathbbm{E}(Y_1) + \text{ATE}\times -Z_0 + \text{TUT} \times -Z_2 (1 - D) + V
+\] 
+where $\mathbb{E}(V|Z) = 0$.
+Therefore, under standard regularity conditions, an IV regression of $Y$ on an intercept, $-Z_0$ and $-Z_2(1-D)$ with instruments $(1, Z_0, Z_2)$ provides consistent estimates of the ATE and TUT effects.
+\end{prop}
+
+\begin{proof}
+By Assumption \ref{assump:randchoice} (iii),
+\begin{align*}
+Y &= Z_0 Y_0 + Z_1 Y_1 + Z_2[(1 - C) Y_0 + CY_1]\\
+&= Z_0 Y_0 + Z_1 Y_1 + Z_2[(1 - C) (Y_0 - Y_1) + Y_1]\\
+&= Z_0 Y_0 + (Z_1 + Z_2) Y_1 + Z_2(1 - C) (Y_0 - Y_1) \\
+&= Z_0 Y_0 + (1 - Z_0) Y_1 + Z_2(1 - D) (Y_0 - Y_1) \\
+&= Y_1 - Z_0 (Y_1 - Y_0) - Z_2(1 - D) (Y_1 - Y_0)
+\end{align*}
+since $Z_2(1 - C)= Z_2(1 - D)$ and $(Z_1 + Z_2) = 1 - Z_0$.
+Thus, defining 
+\[
+V \equiv [Y_1 - \mathbb{E}(Y_1)] - Z_0[(Y_1 - Y_0) - \text{ATE}] - Z_2(1 - D)[(Y_1 - Y_0) - \text{TUT}]
+\]
+by construction we have
+\[
+Y = \mathbb{E}(Y_1) + \text{ATE} \times -Z_0 + \text{TUT} \times -Z_2(1 - D) + V.
+\]
+Now, since $Z_2(1 - D) = Z_2 (1 - C)$ and $Z$ is independent of $(Y_0, Y_1)$ by Assumption \ref{assump:randchoice} (i),
+\begin{align*}
+\mathbb{E}(V|Z) &= [\mathbb{E}(Y_1|Z) - \mathbb{E}(Y_1)] - Z_0[\mathbb{E}(Y_1 - Y_0|Z) - \text{ATE}] - \mathbb{E}[Z_2(1 - D)\left\{(Y_1 - Y_0) - \text{TUT}\right\}|Z]\\
+&= [\mathbb{E}(Y_1) - \mathbb{E}(Y_1)] - Z_0[\mathbb{E}(Y_1 - Y_0) - \text{ATE}] - Z_2\mathbb{E}[(1 - C)\left\{(Y_1 - Y_0) - \text{TUT}\right\}|Z]\\
+&= -Z_2\mathbb{E}[(1 - C)\left\{(Y_1 - Y_0) - \text{TUT}\right\}|Z].
+\end{align*}
+Finally, by iterated expectations,
+\begin{align*}
+\mathbb{E}[(1 - C)\left\{(Y_1 - Y_0) - \text{TUT}\right\}|Z]&= \mathbb{P}(C=0|Z)\left[ \mathbb{E}(Y_1 - Y_0|C=0, Z) - \text{TUT}\right]\\
+&= \mathbb{P}(C=0|Z) \left[ \mathbb{E}(Y_1 - Y_0|C=0) - \text{TUT}\right] = 0
+\end{align*}
+since $Z$ is conditionally independent of $(Y_0, Y_1)$ given $C$, an implication of Assumption \ref{assump:randchoice} (i).
+\end{proof}
+
+Since $\text{ASG} = \text{TOT} - \text{TUT}$, the preceding two propositions provide consistent estimates of $\text{ASG}$ effect.
+The $\text{ASB}$ effect, $\mathbbm{E}(Y_0|C=1) - \mathbb{E}(Y_0|C=0)$, can likewise be estimated by taking the difference of coefficients across two linear IV regressions, as shown in the following proposition.
+
+\begin{prop}
+Under Assumption \ref{assump:randchoice}
+\begin{align}
+\label{eq:ASB0}
+    (1 - D) Y &= \mathbbm{E}(Y_{0}) \times Z_0 + \mathbbm{E}(Y_{0}|C=0) \times (1 - D)Z_2 + U_{0}\\
+\label{eq:ASB1}
+    (1 - D) Y &= \mathbbm{E}(Y_{0}) \times(Z_0 + Z_2) + \mathbbm{E}(Y_{0}|C=1)\times -DZ_2 + U_{1}
+\end{align}
+where $\mathbbm{E}(U_0|Z) = \mathbbm{E}(U_1|Z) = 0$.
+Thus, under standard regularity conditions, an IV regression of $(1 - D)Y$ on $Z_0$ and $(1 - D)Z_2$ with instruments $(Z_0, Z_2)$ and no intercept provides consistent estimates of $\mathbb{E}(Y_0)$ and $\mathbb{E}(Y_0|C=0)$.
+Similarly, an IV regression of $(1 - D)Y$ on $(Z_0 + Z_2)$ and $-DZ_2$ with instruments $(Z_0, Z_2)$ and no intercept provides consistent estimates of $\mathbb{E}(Y_0)$ and $\mathbb{E}(Y_0|C=1)$.
+\end{prop}
+
+\begin{proof}
+Assumption \ref{assump:randchoice} (ii) implies $(1 - D) = Z_0 + Z_2(1 - C)$. Hence, by Assumption \ref{assump:randchoice} (iii),
+\begin{align*}
+(1 - D)Y &=  [Z_0 + Z_2 (1 - C)]\left\{Z_0 Y_0 + Z_1 Y_1 + Z_2[(1 - C) Y_0 + CY_1]\right\}\\
+&= Z_0 Y_0 + Z_2 (1 - C) [(1 - C) Y_0 + C Y_1]\\
+&= Z_0 Y_0 + Z_2 (1 - C) Y_0.
+\end{align*}
+because $Z_j^2 = Z_j$ for any $j$ and $Z_j Z_k = 0$ for any $j \neq k$ and, similarly, $(1 - C)^2 = (1 - C)$ and $C (1 - C) = 0$.
+Therefore, since $Z_2 (1 - C) = Z_2 (1 - D)$,
+\begin{align*}
+(1 - D)Y &= Z_0 Y_0 + Z_2 (1 - D) Y_0\\
+(1 - D)Y &= (Z_0 + Z_2) Y_0 + (-DZ_2) Y_0. 
+\end{align*}
+Now, defining
+\begin{align*}
+U_0 &\equiv Z_0 [Y_0 - \mathbbm{E}(Y_0)] + Z_2(1 - D)[Y_0 - \mathbbm{E}(Y_0|C=0)]\\
+U_1 &\equiv (Z_0 + Z_2)[Y_0 - \mathbbm{E}(Y_0)] + (-Z_2 D)[Y_0 - \mathbbm{E}(Y_0|C=1)]
+\end{align*}
+by construction, we have
+\begin{align*}
+Y &= \mathbbm{E}(Y_0) \times Z_0 + \mathbbm{E}(Y_0|C=0) \times Z_2(1 - D) + U_0\\
+Y &= \mathbbm{E}(Y_0) \times (Z_0 + Z_2)+ \mathbbm{E}(Y_0|C=1) (-Z_2D) + U_1.
+\end{align*}
+Finally, since $Z_2(1-D) = Z_2(1 - C)$, and $Z$ is independent of $Y_0$,  
+\begin{align*}
+\mathbbm{E}(U_0|Z) &= Z_0[\mathbbm{E}(Y_0|Z) - \mathbbm{E}(Y_0)] + Z_2\mathbbm{E}\{(1 - C) [Y_0 - \mathbbm{E}(Y_0|C=0) |Z\}\\
+&= Z_2 \mathbbm{E}[Y_0 - \mathbbm{E}(Y_0|C=0) | C = 0, Z] = 0
+\end{align*}
+where the final two steps follow by iterated expectations and the fact that  $Z$ is conditionally independent of $Y_0$ given $C$. 
+Since $Z_2 D = Z_2 C$, a nearly identical argument gives
+\begin{align*}
+\mathbbm{E}(U_1|Z) &= (Z_0 + Z_2)[Y_0 - \mathbbm{E}(Y_0|Z)] -Z_2\mathbbm{E}\{C [Y_0 - \mathbbm{E}(Y_0|C=1) |Z\}\\
+&= -Z_2 \mathbbm{E}[Y_0 - \mathbbm{E}(Y_0|C=0) | C = 1, Z] = 0. \qedhere
+\end{align*}
+\end{proof}
+
+The next results shows that the $\text{ASL}$ effect, $\mathbbm{E}(Y_1|C=1) - \mathbb{E}(Y_1|C=0)$, can be estimated as the difference of coefficients across two linear IV regressions, as shown in the following proposition.
+
+\begin{prop}
+Under Assumption \ref{assump:randchoice},
+\begin{align}
+\label{eq:ASL0}
+    D Y &= \mathbbm{E}(Y_{1}) \times(Z_1 + Z_2) + \mathbbm{E}(Y_{1}|C=0)\times (D - 1)Z_2 + V_{0}\\
+\label{eq:ASL1}
+    D Y &= \mathbbm{E}(Y_{1}) \times Z_1 + \mathbbm{E}(Y_{1}|C=1)\times D Z_2+ V_{1}
+\end{align}
+where $\mathbbm{E}(V_0|Z) = \mathbbm{E}(V_1|Z) = 0$.
+Thus, under standard regularity conditions, an IV regression of $DY$ on $(Z_1 + Z_2)$ and $-Z_2(1 - D)$ with instruments $(Z_1, Z_2)$ and no intercept provides consistent estimates of $\mathbb{E}(Y_1)$ and $\mathbb{E}(Y_1|C=1)$.
+Similarly, an IV regression of $DY$ on $Z_1$ and $DZ_2$ with instruments $(Z_1, Z_2)$ and no intercept provides consistent estimates of $\mathbb{E}(Y_1)$ and $\mathbb{E}(Y_1|C=1)$. 
+\end{prop}
+
+\begin{proof}
+By Assumption \ref{assump:randchoice}, $D = Z_1 + Z_2 C$. Hence, by Assumption \ref{assump:randchoice} (iii),
+\begin{align*}
+DY &=  (Z_1 + Z_2 C)\left\{Z_0 Y_0 + Z_1 Y_1 + Z_2[(1 - C) Y_0 + CY_1]\right\}\\
+&= Z_1 Y_1 + Z_2 C[(1 -C) Y_0 + C Y_1]\\
+&= Z_1 Y_1 + Z_2 C Y_1
+\end{align*}
+because $Z_j^2 = Z_j$ for any $j$ and $Z_j Z_k = 0$ for any $j \neq k$ and, similarly, $(1 - C)^2 = (1 - C)$ and $C (1 - C) = 0$. Therefore, since $Z_2 (1 - C) = Z_2 (1 - D)$,
+\begin{align*}
+ DY &= (Z_1 + Z_2)Y_1 + Z_2 (D - 1) Y_1\\
+ DY &= Z_1 Y_1 + Z_2 D Y_1.
+\end{align*}
+Now, defining
+\begin{align*}
+V_0 &= (Z_1 + Z_2)[Y_1 - \mathbbm{E}(Y_1)] + Z_2(D - 1)[Y_1 - \mathbbm{E}(Y_1|C=0)]\\
+V_1 &= Z_1[Y_1 - \mathbbm{E}(Y_1)] + Z_2D[Y_1 - \mathbbm{E}(Y_1|C=1)]
+\end{align*}
+by construction we have
+\begin{align*}
+Y &= \mathbbm{E}(Y_1) \times (Z_1 + Z_2) + \mathbbm{E}(Y_1 | C = 0) \times Z_2 (D - 1) + V_0\\
+Y &= \mathbbm{E}(Y_1) \times Z_1 + \mathbbm{E}(Y_1 | C = 1) \times Z_2 D + V _1.
+\end{align*}
+Finally, since $Z_2(1 - D) = Z_2(1 - C)$ and $Z$ is independent of $Y_1$,
+\begin{align*}
+\mathbbm{E}(V_0|Z) &= (Z_1 + Z_2) [\mathbbm{E}(Y_1|Z) - \mathbbm{E}(Y_1) ]  - Z_2 \mathbbm{E}\{(1 - C)  [Y_1 - \mathbbm{E}(Y_1 | C=0)|Z\} \\
+&= -Z_2 \mathbbm{E}[Y_1 - \mathbbm{E}(Y_1 | C=0)|C=0, Z] = 0
+\end{align*}
+where the final two steps follow by iterated expectations and the fact that  $Z$ is conditionally independent of $Y_1$ given $C$. 
+Since $Z_2 D = Z_2 C$, a nearly identical argument gives
+\begin{align*}
+\mathbbm{E}(V_1|Z) &= Z_1 [\mathbbm{E}(Y_1 | Z) - \mathbbm{E}(Y_1)]  + Z_2 \mathbbm{E}\{C  [Y_1 - \mathbbm{E}(Y_1 | C=1)|Z\} \\
+&= Z_2 \mathbbm{E}[Y_1 - \mathbbm{E}(Y_1 | C=1)|C=1, Z] = 0. \qedhere
+\end{align*}
+\end{proof}
+
+\todo[inline]{Update below here}
+
+\subsection{Inference for ASG, ASB, and ASL}
+We now explain how to carry out cluster-robust inference for the ASG, ASB, and ASL effects, as implemented in our companion STATA package.
+
+For purposes of inference, both the ASB and ASL can be re-written as the difference of coefficients from a pair of just-identified linear IV regressions, namely
+
+As in the case of the ASG, inference for the ASB and ASL can be carried out by saving the residuals from \eqref{eq:ASB0}--\eqref{eq:ASL1}.
+
+\todo[inline]{Add something about the TUT decomposition and covariates? Probably just a few sentences at most.}
 
@@
 \end{align}
-Equation \ref{eq:exclusion_append0} is a restriction on the potential outcomes of non-choosers that we use to point identify the TuT.
-In contrast, Equation \ref{eq:exclusion_append1} is a restriction on the potential outcomes of choosers that we use to point identify the ToT.
-Because they involve different groups of people, it is entirely possible for one of these equalities to hold when the other fails.
-For this reason, we consider each in turn.
-Our approach is closely related to a bounding approach used by \cite{huber_mellace} and \cite{BinaryRegressor}, among others.
+Equation \ref{eq:exclusion_append0} is a restriction on the average potential outcomes of non-choosers that we use to point identify the TUT effect.
+It says that someone who \emph{would} choose the control condition when given a choice, experiences the same potential outcome, on average, when \emph{assigned} to the control condition.
+Equation \ref{eq:exclusion_append1} is a restriction on the average potential outcomes of choosers that we use to point identify the TOT effect.
+It says that someone who \emph{would} choose the commitment contract when given a choice, experiences the same potential outcome, on average, when \emph{assigned} to this condition.
+Because they refer to different groups of people, either of \eqref{eq:exclusion_append0}  and \eqref{eq:exclusion_append1} could hold when the other is violated.
+For this reason we consider each in turn.
+Our approach is closely related arguments from \cite{huber_mellace} and \cite{BinaryRegressor}, among others.
 As such, the following is a heuristic explanation rather than a fully-rigorous proof.
@@
 
-Consider first Equation \ref{eq:exclusion_append0}.
+Consider first \eqref{eq:exclusion_append0}.
 Let $p \equiv \mathbbm{P}(C=1) = \mathbbm{P}(D=1|Z=2)$ denote the share of choosers in the population.
@@
 \end{equation}
-Equation \ref{eq:testable0} provides a pair of testable implications of Equation \ref{eq:exclusion_append0}.
+Equation \ref{eq:testable0} provides a pair of testable implications of \eqref{eq:exclusion_append0}.
 If either inequality is violated, then the exclusion restriction for non-choosers fails.
 
-We can use an analogous approach to construct testable implications for Equation \ref{eq:exclusion_append1}. 
+We can use an analogous approach to construct testable implications for \ref{eq:exclusion_append1}. 
 Because $Z$ was randomly assigned, a fraction $p$ of participants with $Z = 1$ are choosers so the distribution of $Y|Z=1$ is a mixture of $Y_1|C=1$ and $Y_1|C=0$ with mixing weights $p$ and $1 -p$.
@@
 
-\todo[inline]{Update from here down.}
-
-\todo[inline]{Presumably the numerical results and sentence that follows it need to be updated now that we've changed how we deal with censoring etc, yes? Which outcome are we looking at here} 
-The \cite{huber_mellace} bounds for the ToT \& TuT APR are respectively:
-\[\text{ToT} : [-481.8, 483.7]\quad\quad\quad\text{TuT} : [-17.9, 90.6]\]
-
-Because the Note that since both TuT and ToT estimates from the LATE approach lies inside these bounds, we do not falsify the exclusion restriction.
+\todo[inline]{@Issac: Presumably the numerical results and sentence that follows it need to be updated now that we've changed how we deal with censoring etc, yes?
+Which outcome are we looking at here}
+The \cite{huber_mellace} bounds for the TOT \& TUT APR are respectively:
+\[\text{TOT} : [-481.8, 483.7]\quad\quad\quad\text{TUT} : [-17.9, 90.6]\]
+
+Because the Note that since both TUT and ToT estimates from the LATE approach lies inside these bounds, we do not falsify the exclusion restriction.
 
@@
 
-\section{LATE: ToT \& TuT}
-\vspace{.2in}
-\normalsize
-\linespread{1.25}
-%Really force it to normal size and linespread
-\normalsize
-\linespread{1.25}
-
- Recall that $Z_i$ is the observed, randomly assigned experimental allocation, where $Z_i=0$ denotes the control arm, $Z_i=1$ denotes the forced-fee arm, and $Z_i=2$ is the choice arm.
+%\section{LATE: TOT \& TUT}
+%\vspace{.2in}
+%\normalsize
+%\linespread{1.25}
+%%Really force it to normal size and linespread
+%\normalsize
+%\linespread{1.25}
+%
+% Recall that $Z_i$ is the observed, randomly assigned experimental allocation, where $Z_i=0$ denotes the control arm, $Z_i=1$ denotes the forced-fee arm, and $Z_i=2$ is the choice arm.
 Let $C_i$ be the unobserved choice type.
@@
 Finally, $D_i = Z_i\times \mathds{1}(Z_i\neq 2) + C_i\times \mathds{1}(Z_i=2)$ is the observed treatment indicator, and $Y(d,z)$ is the potential outcome function for $d=0,1$, and $z=0,1,2$.
-
- To identify assortative selection we first need to estimate the following quantities: $\mathbb{E}(Y_1-Y_0\;|\;C=1)$ the Treatment on the Treated (ToT), and $\mathbb{E}(Y_1-Y_0\;|\;C=0)$ the Treatment on the Untreated (TuT).
-
- To point identify the above quantities, we make the following assumptions.
-
- \begin{assumption}[Exclusion Restriction]
-$Z$ only affects $Y$ through its effect on $D$ : $C(d,z) = C(d)$
- \end{assumption}
-
-  \begin{assumption}[Independence Assumption]
-$Z \perp (Y_0, Y_1, C)$
- \end{assumption}
-
-The following intermediate Lemmas will help us derive that both ToT and TuT are point identified.
-
-\begin{lem}
-$\Pr(C=1) = \E[D\;|\;Z=2]$
-\end{lem}
-\begin{proof}
-Since $C\perp Z$, 
-$$\E[D\;|\;Z=2] = \E[Z\times \mathds{1}(Z\neq 2)+ C\times\mathds{1}(Z=2)\;|Z=2] = \E[C\;|\;Z=2] = \E[C] = \Pr(C=1)$$
-\end{proof}
-
-\begin{lem}
-$\E[Y_0] = \E[Y\;|\;Z=0]$
-\end{lem}
-\begin{proof}
-Since $Z\perp Y_0$, 
-\begin{align*}
-\E[Y\;|\;Z=0] =& \E[\mathds{1}(Z=0)Y_0+\mathds{1}(Z=1)Y_1+\mathds{1}(Z=2)\{(1-C)Y_0+CY_1\})\;|\;Z=0]\\   
-=&\E[Y_0\;|\;Z=0] = \E[Y_0]
-\end{align*}
-\end{proof}
-
-\begin{lem}
-$\E[Y_1] = \E[Y\;|\;Z=1]$
-\end{lem}
-\begin{proof}
-Since $Z\perp Y_1$, 
-\begin{align*}
-\E[Y\;|\;Z=1] =\E[Y_1\;|\;Z=1] = \E[Y_1]
-\end{align*}
-\end{proof}
-
-\begin{lem}
-$\E[Y_0\;|\;C=0] = \E[Y\;|\; D=0,Z=2]$
-\end{lem}
-\begin{proof}
-If $Z=2$, then $D=0$ if and only if $C=0$. Hence,
-\[\E[Y\;|\;D=0, Z=2] = \E[Y_0\;|\;D=0, Z=2] = E[Y_0\;|\;C=0, Z=2]=\E[Y_0\;|\;C=0]\]
-since $Y_0\perp C\;|\;Z$
-\end{proof}
-
-\begin{lem}
-$\E[Y_1\;|\;C=1] = \E[Y\;|\; D=1,Z=2]$
-\end{lem}
-\begin{proof}
-If $Z=2$, then $D=1$ if and only if $C=1$. Hence,
-\[\E[Y\;|\;D=1, Z=2] = \E[Y_1\;|\;D=1, Z=2] = E[Y_1\;|\;C=1, Z=2]=\E[Y_1\;|\;C=1]\]
-since $Y_1\perp C\;|\;Z$
-\end{proof}
-
-\begin{theorem} $\E[Y_1-Y_0\;|\; C=1]$ is point identified
-\end{theorem}
-
-\begin{proof}
-Since $\E[Y_1\;|\; C=1] = \E[Y\;|\; D=1, Z=2]$ by Lemma 5, it suffices to show that $\E[Y_1\;|\;C=0]$ is point identified. By iterated expectations:
-\[E[Y_0] = \E_C\E[Y_0\;|\;C] = (1-p)\E[Y_0\;|\;C=0]+p\E[Y_0\;|\;C=1]\]
-where $p:=\E[C]=\Pr(C=1)$, and re-arranging,
-\[\E[Y_0\;|\;C=1] = \frac{1}{p}\left(E[Y_0] -(1-p)\E[Y_0\;|\;C=0]\right)\]
-Finally, substituting the result of Lemmas 1, 2, and 4, we obtain
-\[\E[Y_0\;|\;C=1] =\frac{1}{\E[D\;|\;Z=2]}\left\{\E[Y\;|\;Z=0]-(1-\E[D\;|\;Z=2])\E[Y\;|\;D=0, Z=2]\right\}\]
-and the RHS is a function of observed data only.
-\end{proof}
-
-\begin{theorem} $\E[Y_1-Y_0\;|\; C=0]$ is point identified
-\end{theorem}
-
-\begin{proof}
-Since $\E[Y_0\;|\; C=0] = \E[Y\;|\; D=0, Z=2]$ by Lemma 4, it suffices to show that $\E[Y_0\;|\;C=1]$ is point identified. By iterated expectations:
-\[E[Y_1] = \E_C\E[Y_1\;|\;C] = (1-p)\E[Y_1\;|\;C=0]+p\E[Y_1\;|\;C=1]\]
-where $p:=\E[C]=\Pr(C=1)$, and re-arranging,
-\[\E[Y_1\;|\;C=0] = \frac{1}{1-p}\left(E[Y_1] -p\E[Y_1\;|\;C=1]\right)\]
-Finally, substituting the result of Lemmas 1, 3, and 5, we obtain
-\[\E[Y_1\;|\;C=0] =\frac{1}{1-\E[D\;|\;Z=2]}\left\{\E[Y\;|\;Z=1]-\E[D\;|\;Z=2]\E[Y\;|\;D=1, Z=2]\right\}\]
-and the RHS is a function of observed data only.
-\end{proof}
-
-\begin{figure}[H]
-    \caption{Bootstrap inference for the difference between ToT-TuT}
-    \label{bootstrap_tot_tut}
-    \begin{center}
-    \begin{subfigure}{0.31\textwidth}
-        \caption{Simple}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/tot_tut_btsp1.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.31\textwidth}
-        \caption{Admin controls}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/tot_tut_btsp2.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.31\textwidth}
-        \caption{Admin + Survey controls}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/tot_tut_btsp3.pdf}
-    \end{subfigure}
-
-    \end{center}
-     \scriptsize  Given that all of the arms are effectively randomly sampled form the same pool, we can also estimate the ToT and TuT with the pooled regression: $Y_i = \beta_0\mathds{1}(Z_i=0)+\beta_1\mathds{1}(Z_i=1)+\beta_2\mathds{1}(Z_i=2)+ \epsilon_i$, and then this test statistic just becomes the F-test on $\frac{\widehat{\beta_2}-\widehat{\beta_0}}{p}$ for the ToT, $\frac{\widehat{\beta_1}-\widehat{\beta_2}}{1-p}$ for the TuT, and an F-test on the difference between these two quantities to test whether the gains are different between compliers and non-compliers.
+%
+% To identify assortative selection we first need to estimate the following quantities: $\mathbb{E}(Y_1-Y_0\;|\;C=1)$ the Treatment on the Treated (TOT), and $\mathbb{E}(Y_1-Y_0\;|\;C=0)$ the Treatment on the Untreated (TUT).
+%
+% To point identify the above quantities, we make the following assumptions.
+%
+% \begin{assumption}[Exclusion Restriction]
+%$Z$ only affects $Y$ through its effect on $D$ : $C(d,z) = C(d)$
+% \end{assumption}
+%
+%  \begin{assumption}[Independence Assumption]
+%$Z \perp (Y_0, Y_1, C)$
+% \end{assumption}
+%
+%The following intermediate Lemmas will help us derive that both TOT and TUT are point identified.
+%
+%\begin{lem}
+%$\Pr(C=1) = \E[D\;|\;Z=2]$
+%\end{lem}
+%\begin{proof}
+%Since $C\perp Z$, 
+%$$\E[D\;|\;Z=2] = \E[Z\times \mathds{1}(Z\neq 2)+ C\times\mathds{1}(Z=2)\;|Z=2] = \E[C\;|\;Z=2] = \E[C] = \Pr(C=1)$$
+%\end{proof}
+%
+%
+%\begin{lem}
+%$\E[Y_0] = \E[Y\;|\;Z=0]$
+%\end{lem}
+%\begin{proof}
+%Since $Z\perp Y_0$, 
+%\begin{align*}
+%\E[Y\;|\;Z=0] =& \E[\mathds{1}(Z=0)Y_0+\mathds{1}(Z=1)Y_1+\mathds{1}(Z=2)\{(1-C)Y_0+CY_1\})\;|\;Z=0]\\   
+%=&\E[Y_0\;|\;Z=0] = \E[Y_0]
+%\end{align*}
+%\end{proof}
+%
+%
+%\begin{lem}
+%$\E[Y_1] = \E[Y\;|\;Z=1]$
+%\end{lem}
+%\begin{proof}
+%Since $Z\perp Y_1$, 
+%\begin{align*}
+%\E[Y\;|\;Z=1] =\E[Y_1\;|\;Z=1] = \E[Y_1]
+%\end{align*}
+%\end{proof}
+%
+%
+%\begin{lem}
+%$\E[Y_0\;|\;C=0] = \E[Y\;|\; D=0,Z=2]$
+%\end{lem}
+%\begin{proof}
+%If $Z=2$, then $D=0$ if and only if $C=0$. Hence,
+%\[\E[Y\;|\;D=0, Z=2] = \E[Y_0\;|\;D=0, Z=2] = E[Y_0\;|\;C=0, Z=2]=\E[Y_0\;|\;C=0]\]
+%since $Y_0\perp C\;|\;Z$
+%\end{proof}
+%
+%\begin{lem}
+%$\E[Y_1\;|\;C=1] = \E[Y\;|\; D=1,Z=2]$
+%\end{lem}
+%\begin{proof}
+%If $Z=2$, then $D=1$ if and only if $C=1$. Hence,
+%\[\E[Y\;|\;D=1, Z=2] = \E[Y_1\;|\;D=1, Z=2] = E[Y_1\;|\;C=1, Z=2]=\E[Y_1\;|\;C=1]\]
+%since $Y_1\perp C\;|\;Z$
+%\end{proof}
+%
+%\begin{theorem} $\E[Y_1-Y_0\;|\; C=1]$ is point identified
+%\end{theorem}
+%
+%\begin{proof}
+%Since $\E[Y_1\;|\; C=1] = \E[Y\;|\; D=1, Z=2]$ by Lemma 5, it suffices to show that $\E[Y_1\;|\;C=0]$ is point identified. By iterated expectations:
+%\[E[Y_0] = \E_C\E[Y_0\;|\;C] = (1-p)\E[Y_0\;|\;C=0]+p\E[Y_0\;|\;C=1]\]
+%where $p:=\E[C]=\Pr(C=1)$, and re-arranging,
+%\[\E[Y_0\;|\;C=1] = \frac{1}{p}\left(E[Y_0] -(1-p)\E[Y_0\;|\;C=0]\right)\]
+%Finally, substituting the result of Lemmas 1, 2, and 4, we obtain
+%\[\E[Y_0\;|\;C=1] =\frac{1}{\E[D\;|\;Z=2]}\left\{\E[Y\;|\;Z=0]-(1-\E[D\;|\;Z=2])\E[Y\;|\;D=0, Z=2]\right\}\]
+%and the RHS is a function of observed data only.
+%\end{proof}
+%
+%\begin{theorem} $\E[Y_1-Y_0\;|\; C=0]$ is point identified
+%\end{theorem}
+%
+%\begin{proof}
+%Since $\E[Y_0\;|\; C=0] = \E[Y\;|\; D=0, Z=2]$ by Lemma 4, it suffices to show that $\E[Y_0\;|\;C=1]$ is point identified. By iterated expectations:
+%\[E[Y_1] = \E_C\E[Y_1\;|\;C] = (1-p)\E[Y_1\;|\;C=0]+p\E[Y_1\;|\;C=1]\]
+%where $p:=\E[C]=\Pr(C=1)$, and re-arranging,
+%\[\E[Y_1\;|\;C=0] = \frac{1}{1-p}\left(E[Y_1] -p\E[Y_1\;|\;C=1]\right)\]
+%Finally, substituting the result of Lemmas 1, 3, and 5, we obtain
+%\[\E[Y_1\;|\;C=0] =\frac{1}{1-\E[D\;|\;Z=2]}\left\{\E[Y\;|\;Z=1]-\E[D\;|\;Z=2]\E[Y\;|\;D=1, Z=2]\right\}\]
+%and the RHS is a function of observed data only.
+%\end{proof}
+%
+%
+%\begin{figure}[H]
+%    \caption{Bootstrap inference for the difference between TOT-TUT}
+%    \label{bootstrap_tot_tut}
+%    \begin{center}
+%    \begin{subfigure}{0.31\textwidth}
+%        \caption{Simple}
+%        \centering
+%        \includegraphics[width=\textwidth]{Figuras/tot_tut_btsp1.pdf}
+%    \end{subfigure}
+%    \begin{subfigure}{0.31\textwidth}
+%        \caption{Admin controls}
+%        \centering
+%        \includegraphics[width=\textwidth]{Figuras/tot_tut_btsp2.pdf}
+%    \end{subfigure}
+%    \begin{subfigure}{0.31\textwidth}
+%        \caption{Admin + Survey controls}
+%        \centering
+%        \includegraphics[width=\textwidth]{Figuras/tot_tut_btsp3.pdf}
+%    \end{subfigure}
+%  
+%    \end{center}
+%     \scriptsize  Given that all of the arms are effectively randomly sampled form the same pool, we can also estimate the TOT and TUT with the pooled regression: $Y_i = \beta_0\mathds{1}(Z_i=0)+\beta_1\mathds{1}(Z_i=1)+\beta_2\mathds{1}(Z_i=2)+ \epsilon_i$, and then this test statistic just becomes the F-test on $\frac{\widehat{\beta_2}-\widehat{\beta_0}}{p}$ for the TOT, $\frac{\widehat{\beta_1}-\widehat{\beta_2}}{1-p}$ for the TUT, and an F-test on the difference between these two quantities to test whether the gains are different between compliers and non-compliers.
 Recognizing the stochastic nature of the compliance rate, we also bootstrap this quantity before running the previous regression.
-The red line shows the point estimate for the difference between ToT-TuT, and the gray bar in the x-axis shows a 95\% confidence interval for this difference.
-Panel (a) shows the difference between the ToT and TuT without any controls, while panel (b) and (c) adds admin controls and admin + survey controls respectively.
-          %\footnotesize{ \textit{Do file: }  \texttt{tot\_tut.do}}
-\end{figure}
-
-\begin{figure}[H]
-     \caption{ToT-TuT CDF}
+The red line shows the point estimate for the difference between TOT-TUT, and the gray bar in the x-axis shows a 95\% confidence interval for this difference.
+Panel (a) shows the difference between the TOT and TUT without any controls, while panel (b) and (c) adds admin controls and admin + survey controls respectively.
+%          %\footnotesize{ \textit{Do file: }  \texttt{tot\_tut.do}}
+%\end{figure}
+
+\begin{figure}[H]
+     \caption{TOT-TUT CDF}
      \label{tot_tut_ecdf}
@@
     \scriptsize
-       Equipped with estimates for the ToT and TuT for each individual $i$ from an Instrumental Random Forest we compute the ECDF for this quantities.
-The solid line is the ECDF for the ToT, the dashed line is the ECDF for the TuT, and the dotted line plots the difference between the ToT and the TuT - the blue dashed line in the x-axis shows the points where this difference is significant.
-The bold black interval at the bottom of the graph is the mean for the ToT distribution (0.07), while the gray interval shows the mean for the TuT distribution (0.10).
+       Equipped with estimates for the TOT and TUT for each individual $i$ from an Instrumental Random Forest we compute the ECDF for this quantities.
+The solid line is the ECDF for the TOT, the dashed line is the ECDF for the TUT, and the dotted line plots the difference between the TOT and the TUT - the blue dashed line in the x-axis shows the points where this difference is significant.
+The bold black interval at the bottom of the graph is the mean for the TOT distribution (0.07), while the gray interval shows the mean for the TUT distribution (0.10).
 
@@
     \end{center}
-    \scriptsize This figure serves as a test for the exclusion restriction in the point identification for the ToT and the TuT.
+    \scriptsize This figure serves as a test for the exclusion restriction in the point identification for the TOT and the TUT.
 It shows the effect on the effective cost/loan ratio for the forced-fee arm and the choice arm, together with the decomposition of the choosers and non-choosers.
@@
         \centering
-        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin_pro_2.pdf}
+        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin.pdf}
     \end{subfigure}
@@
        \centering
-      \includegraphics[width=\textwidth]{Figuras/he_dist_apr_pro_2.pdf}
+      \includegraphics[width=\textwidth]{Figuras/he_dist_eff.pdf}
     \end{subfigure}
@@
        \centering
-      \includegraphics[width=\textwidth]{Figuras/he_dist_def_c_pro_2.pdf}
+      \includegraphics[width=\textwidth]{Figuras/he_dist_def_c.pdf}
     \end{subfigure}  
@@
        \centering
-      \includegraphics[width=\textwidth]{Figuras/he_dist_des_c_pro_2.pdf}
+      \includegraphics[width=\textwidth]{Figuras/he_dist_des_c.pdf}
     \end{subfigure}      
@@
      This Figure plots the densities of the CATE emerging from the Athey et al. (2019) random forest, along with the upper and lower confidence bounds.  
-  %\footnotesize{ } \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}
+  %\footnotesize{ } \textit{Do file: }  \texttt{cate_dist.do}
 \end{figure}

### 2023-07-04 donde.tex
add loan as predictor in narrow and wide forest

@@
 Firms limit their worker's freedom by requiring time-consuming progress reports,  schools impose deadlines and pop quizzes, and loan contracts often require monthly repayment.
-As pointed out by \cite{Laibson2018}, although these choice-restricting mechanisms may be beneficial to firms and clients, they are often disliked by the latter, and therefore ‘shrouded’ by firms, i.e.
+As pointed out by \cite{Laibson2018}, although these choice-restricting mechanisms may be beneficial to firms and clients, they are often disliked by the latter, and therefore ``shrouded'' by firms, i.e.
 not advertised but nonetheless embedded in products.
@@
 
-Substantiating a case for private paternalism is not easy.
-It involves comparing the causal effect of forcing a certain product characteristic versus the effect of letting people choose it.
-Because choice may be correlated with unobservables, identification
-is challenging in observational studies.  %This is not a straightforward task because choice will be driven by unobservable factors, and to address the question fully 
-Moreover, to have a complete picture of the benefits of forcing, one would want a counterfactual for the outcome of both choosers and non-choosers.
-A large behavioral literature has illustrated that allowing borrowers or savers to choose commitment-style products increase savings in an Intention-to-Treat sense \citep{thaler2004save, prina2015banking, brune2016facilitating, callen2019headwaters, Pascaline, Ashraf}, but this literature has rarely inquired about the benefits of imposing commitment.\footnote{Selection on gains has such wide acceptance that economists often impose it in their models (for example, in the study of migration \cite{chiquiar2005international} and occupational choice \cite{heckman1990empirical}.
-In microfinance, a context close to ours, \citep{Murdoch} claims that positive selection exists, citing a positive correlation between displaying present biased preferences in surveys and selecting into microfinance as evidence of borrowers' actually demanding the discipline imposed by frequent payments.}  In this paper we illustrate how a three-armed, `controlled choice' design can be used to form counterfactuals for both choosers and non-choosers of commitment.
-We implement such a design in a high-stakes and policy-relevant environment, enabling us to test selection-on-gains as well as isolating the impact of paternalistic policies.
+Making a case for private paternalism is not easy.
+It involves comparing the causal effect of forcing a certain product characteristic against the effect of letting people choose it.
+Because choice may be correlated with unobservables, identifying these two effects is challenging in observational studies.
+%This is not a straightforward task because choice will be driven by unobservable factors, and to address the question fully
+Moreover, painting a complete picture of the benefits of forcing requires requires counterfactuals for both choosers and non-choosers.
+A large behavioral literature has illustrated that allowing borrowers or savers to choose commitment-style products increase savings in an intention-to-treat (ITT) sense \citep{thaler2004save, prina2015banking, brune2016facilitating, callen2019headwaters, Pascaline, Ashraf}, but this literature has rarely addressed the benefits of imposing commitment.\footnote{Selection on gains has such wide acceptance that economists often impose it in their models} (Although the examples above are plausible, substantiating a case for private paternalism is not easy.
+It involves comparing the causal effect of forcing a certain product characteristic versus the effect of letting people choose on that characteristic.
+This is not an easy task because a given person wither has or does not have choice, and because choice induces selection, potentially biasing causal estimates.
+A large behavioral literature has illustrated that allocating borrowers to a commitment-savings product increase savings \citep{thaler2004save, prina2015banking, brune2016facilitating, callen2019headwaters, Pascaline, Ashraf}, but this literature does not show that commitment would not be chosen by those that would benefit from it, that is, that the treatment effect on the untreated (TUT) is positive.
+In fact, selection on gains has such wide acceptance that economists often impose it in their models \hl{CITES}.
+In microfinance, a context close to ours, \citep{Murdoch} claim that there exists positive selection, citing a positive correlation between displaying present biased preferences in surveys and selecting into microfinance as evidence of borrowers' actually demanding the discipline imposed by frequent payments.
+However, they are unable to show that borrowers indeed benefit or that they indeed positively select based on treatment effects.
 
@@
 
-We study the benefits of private paternalism in the context of pawnbroker lending.
+This paper studies the benefits of restricting choice in the context of pawnbroker lending.
 Pawn loans are one of the oldest, most understudied, and most prevalent forms of borrowing \citep{carter2012pawnshops}.
-There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues (in China it is a 43 billion dollar industry).\footnote{\url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.} Our partner pawn lender (henceforth Lender $P$) alone served more than 1 million clients in the last 3 years with more than 4 million contracts.\footnote{For comparison there were 2.3 million micro-finance clients in Mexico in 2009 (\cite{Pedroza:2010}).} Pawnshop lending presents an inverted lending case: since these loans are over-capitalized, the principal in the lending contract stands to gain the most when agents default.
+There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues (in China it is a \$43 billion industry).\footnote{\url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.} Our partner pawn lender (henceforth Lender $P$) alone served more than 1 million clients in the last 3 years with more than 4 million contracts.\footnote{For comparison there were 2.3 million micro-finance clients in Mexico in 2009 (\cite{Pedroza:2010}).} Pawnshop lending presents an inverted lending case: since these loans are over-capitalized, the principal in the lending contract stands to gain the most when agents default.
 
 Our collaborating pawn lender (henceforth Lender P) gave 70\% of the value of the pawn in credit, and charged a monthly interest rate of 7\% for loans of a three-month duration, with a flexible no-reminders contract typical of the industry that can be paid back anytime before the loan comes due at no penalty.
-We call this the status-quo contract.
 This combination of features, and the fact that the gold pawn is highly liquid, means that the lender makes 90\% more profit over three months for a borrower who defaults than one who repays (30\% of collateral value recovered under default, 15.8\% of collateral value paid in interest if loan fully repaid).
@@
 %When the lender desires default, the repayment-inducing features of commitment-style repayment contracts become undesirable and there may be incentives for the principal to create contracts with no structure, no reminders, and simple balloon payments.
-To repurpose the language of \cite{Laibson2018}, we suggest that pawn contracts effectively shroud their \textit{lack} of commitment features to induce default in a manner not obvious to borrowers.
+To repurpose the language of \cite{Laibson2018}, we suggest that pawn contracts effectively shroud their \textit{lack} of commitment features to induce default in a manner that is not obvious to borrowers.
 Given that pawnshops, moneylenders, and paycheck lending institutions are likely to face client pools disproportionately made up of impatient and time-inconsistent individuals, the design of such contracts may have serious consequences for the financial lives of the poor.
@@
 
-Against this backdrop, we implement a multi-arm randomized control trial covering close to 10,000 pawnshop clients in 6 branches of Lender $P$ in Mexico City, using a design built to test the demand for and impact of payment structure in pawn repayment contracts.
-Our control arm illustrates the costs of the status quo contract; fully \textcolor{blue}{56\%} of borrowers default and so lose their pawn.\footnote{These high default rates are not uncommon, in the US default is also high at 15\% (\url{https://tinyurl.com/yc2x5bjf}).} We then implement a `commitment choice’ arm, in which borrowers are able at the time of taking a loan to opt into a structured repayment contract, in which they are asked to make three monthly payments rather than one balloon payment at the end, with each monthly payment including the accrued interest at that time, and borrowers levied a nominal fee of 2\% of that month's payment in case of delinquency as a reminder/reinforcement of the importance of these interim payments.
-In addition, we include a `forced commitment’ arm, in which all borrowers are required to repay using the monthly payment structure.
-We will use the terms monthly payments, structured payments, and commitment contract interchangeably.
-
-We call this randomization of voluntary and forced commitment a controlled choice design, and it allows us to address several key questions.
-First, does using more structured repayment contracts help pawnshop borrowers to save on financing cost.
-Second, do borrowers recognize this benefit and demand commitment?
-% demanding commitment in sufficient numbers?
-Finally, and most uniquely, because we incorporate the forced commitment arm, we are able to ask whether the \textit{right} borrowers voluntarily demand commitment, gaining point identification for the Treatment on the Treated (ToT), the Treatment on the Untreated (TuT), and the average selection on gains.
+Against this backdrop, we implement a multi-arm randomized control trial covering close to 10,000 pawnshop clients in 6 branches of Lender $P$ in Mexico City, using a design built to test the demand for and impact of alternative payment structures in pawn repayment contracts.
+Our control arm illustrates the costs of the status quo contract: fully 57\% of borrowers default and so lose their pawn.\footnote{These high default rates are not uncommon, in the US default is also high at 15\% (\url{https://tinyurl.com/yc2x5bjf}).} We then implement a ``commitment choice'' arm, in which borrowers can opt into a structured repayment contract at the time of taking a loan.
+The structured contract requires borrowers to make three monthly payments rather than one balloon payment at the end, with each monthly payment including the accrued interest at that time, a nominal fee of 2\% of that month's payment in case of delinquency.
+This fee serves as a reminder and a means of reinforcing the importance of these interim payments.
+In addition, we include a ``forced commitment'' arm, in which all borrowers are \emph{required} to repay using the structured monthly contract that is offered on an opt-in basis in the commitment choice arm.
+
+The combination of voluntary and forced commitment within the RCT allows us to address several key questions.
+First, do structured repayment contracts lower financial costs for pawnshop borrowers?
+Second, do borrowers recognize this benefit, demanding commitment in sufficient numbers?
+Finally, and most uniquely given the presence of a forced commitment arm, we are able to ask whether the \textit{right} borrowers voluntarily demand commitment.
+In particular, we use the choice, control, and fored arms to point identify the Treatment on the Treated (TOT) and the Treatment on the Untreated (TUT) effects, along with the average selection on gains (ASG) and average selection bias (ASB).
 
@@
 In terms of Annual Percentage Rates, the financial cost of borrowing is reduced by 34 percentage points.
-That is, imposing a commitment structure it is possible to save borrowers money by charging them fees.
+That is, imposing commitment structure it is possible to save borrowers money by charging them fees!
 These results are robust qualitatively to including transport costs of going to the branch plus losing a day's wage for each visit, using the subjective instead of the gold value of the pawn, and imputing some adjustment for liquidity lost by requiring monthly payments.
 
-The monthly payment contract seems to be achieving these cost savings by speeding up payments and by generating an early bifurcation of borrowers into those that will recover the pawn and those that will not, saving the later payments towards recovery (which are lost in the case of default).
-In the treatment group, the first payment occurs 13 days earlier, and the fraction recovering on the first visit by is 7.9 percentage points higher.
-The commitment contract also decreases fraction of borrowers making a payment and not recovering by 7 percentage points.
-Treatment effects are concentrated in the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery.
-Instead, the commitment contract induces people who would otherwise pay something towards recovery to pay more and faster, as well as inducing others who would have made partial payments and anyways defaulted to instead pay nothing.
-Both groups save money.
-
-In spite of a large average treatment effect documenting financial cost savings, given the opportunity in the choice arm, only 11\% of borrowers actually choose payment structure.
-If the effect of payment structure were homogeneous, this would be enough to conclude that the 89\% who did not choose it would have been financially better off if they had.
+The monthly payment contract seems to be achieving these cost savings by speeding up payments and by generating an early bifurcation of borrowers into those that will recover the pawn and those that will not, saving the later payments towards recovery.
+In the treatment group, the first payment occurs 13 days earlier, the fraction recovering on the first visit by is 7.9 percentage point higher.
+Commitment contract decreases fraction of borrowers making a payment and not recovering by 7 percentage points.
+\hl{Treatment effects are concentrated in the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery.
+That is, the commitment contract induces people who would otherwise pay something towards recovery, to pay more and faster, making them more likely to recover their pawn at a lower financial cost.}
+
+In spite of a large average treatment effect documenting financial cost savings, given the opportunity in the choice arm, only 11\% of borrowers actually choose commitment.
+If the effect of commitment were homogeneous, this would be enough to conclude that the 89\%
+who did not choose it would have been financially better off if they had.
 However, we test and reject the null hypothesis of homogeneous treatment effects using the method of \cite{chernozhukov2018generic}.
@@
 
-We start by not imposing assumptions and bounding the distribution of individual treatment effects as in \cite{fan2010sharp}.
-Using bounds we find that at least 30\% of individual borrowers benefit from commitment, implying many borrowers did not demand the structured payment contract even though the treatment effect would be positive for them.
-Then, we impose the twin exclusion restrictions necessary for estimation of the ToT and TuT ---that the effect of choosing or not choosing is the same as being assigned or not assigned the contract, i.e.
-that the act of choosing itself is irrelevant.\footnote{This is a frequently used assumption even if often implicit.
-For instance, a significant literature uses schooling compulsory laws to estimate the return of one more year of school, and then often interprets that schooling, in general, has this return.}  With these assumptions, both treatment effects are point identified, as is the average selection on gains, the average selection on levels, and the average selection bias.
-Our results indicate that while selection on gains are present in our sample, the financial cost savings of the TuT is still large (at \$356 pesos, it is equivalent to 24 percentage point savings in APR).
-Hence, on average borrowers that did \textit{not} choose the frequent payment contract would have benefited from having that contract.\footnote{While our estimated ToT is roughly twice the TuT, it is imprecisely estimated due to the low compliance rate, and the hypothesis of ToT=TuT is rejected only with 13 percent confidence for the APR and 12 percent confidence for default.}  We also estimate that those that would not choose if given the opportunity would have lower status-quo outcomes (i.e.
+\hl{We start by bounding the distribution of treatment effects $Y_{1i}-Y_{0i}$ using the two marginal distribution } in the treatment and control arms as in \cite{fan2010sharp}.
+We find that at least 30\% of individual borrowers benefit from commitment, implying many borrowers did not demand even though the treatment effect would be positive for them.
+Then, we impose the mild exclusion restriction that the effect of the contract does not depend on how they got it, that is: choosing a contract has the same treatment effect as being assigned to the contract.\footnote{This is a frequently used assumption even if often implicit.
+For instance, a significant literature uses schooling compulsory laws to estimate the return of one more year of school, and then often interprets that schooling, in general, has this return.} We show that in this case our 3-armed experiment point identifies the TuT.
+We then estimate that the financial cost savings of the TuT is large, at \$356 pesos, equivalent to 24 percentage point savings in APR.
+That is, on average borrowers that did \textit{not} choose the frequent payment contract would have benefited from having that contract.\footnote{We estimate a positive TOT that is larger than the TuT, but it is imprecise\footnote{This results from the smaller sample size, given that few chose the monthly payment contract.}, and the hypothesis of TOT=TUT is rejeted only with 13 percent confidence for the APR and 12 percent confidence for default.}  We also estimate that those that would not choose if given the opportunity would have lower status-quo outcomes (i.e.
 the average selection bias is negative).
-Finally, assuming the exclusion restriction for subsets of observable characteristics splits generated by a causal forest allows us to establish that more than \hl{70\%} of would-be non-choosers would save on financial cost by being assigned to frequent payments.
+Finally, assuming the exclusion restriction for subsets of observable characteristics splits generated by a causal forest allows us to establish that \hl{70\%} of would-be non-choosers would save on financial cost by being assigned to frequent payments.
 That is, the benefits of imposing a monthly payment are distributed broadly.
-\hl{TuT benefits are particularly large for XXX CHARACTERISTICS, and ToT benefits for those with XXX.}
-
-%\textcolor{brown}{In a final step, we use the Causal Random Forest algorithm of \cite{atheygrf} to estimate individual-level treatment effects for the forced versus control arm, and show the benefits of forcing to be significantly negatively correlated with the propensity to choose commitment estimated from the choice arm.
+\hl{TuT benefits are particularly large for XXX CHARACTERISTICS, and TOT benefits for those with XXX.}
+
+\textcolor{brown}{In a final step, we use the Causal Random Forest algorithm of \cite{atheygrf} to estimate individual-level treatment effects for the forced versus control arm, and show the benefits of forcing to be significantly negatively correlated with the propensity to choose commitment estimated from the choice arm.
 93\% of those who did not opt for the commitment contract would have been better off with it, while only 1\% of those who chose commitment would have been better off without it.} \textcolor{blue}{Targeting frequent payment products to those that benefit the most is a policy that should be explored.
@@
 What explains the persistence of a contract so contrary to borrowers’ interests?
-First, we investigate whether simple impatience could explain the dissonance (our formula for financial does not use discounting, and the contract features near-term costs in return for longer-term benefits).
-A simple simulation exercise suggests that at discount rates up to 4,000 percent per annum our core impacts on financial cost remains significantly negative, suggesting that discounting is unlikely to explain our results.
-Next, we look at time inconsistent preferences, the workhorse behavioral explanation for the benefits of commitment.
-In our context, not only is time inconsistency only a weak driver of selection into commitment, but the TuT of forcing commitment arises almost entirely among those who are \textit{not} time inconsistent.\footnote{\textcolor{blue}{Although telling, we acknowledge that our measure of present bias is simple (as its survey-based and the survey was necessarily short).
-For this reason this result needs to be interpreted with care.}}  In this pawnbroking sample we document substantial levels of over-optimism among borrowers, and it has predictive power for our results.
-%which we believe explains our results.
-Not only do 74\% of borrowers say that they will recover their pawn with perfect certainty (whereas only 43\% actually do), but the impact of forcing on those who would not choose commitment is almost perfectly confined to the sub-sample who reported sure confidence in recovery.
-Hence, in this context it appears that the explanation for low demand for commitment among those who benefit arises from an incorrect belief that one has no need to work to avoid default.
-
-%Those most likely to benefit from the commitment contract and \textit{not} choose it are the individuals who most systematically over-estimate their own probability of repayment at the time of taking the loan.\footnote{More generally \hl{demand for commitment is higher among those with XXX characteristics.}}  Second, the existence of commitment-style repayment contracts in pawnshop lending is novel in Mexico.
+First, we show substantial levels of over-optimism among borrowers.
+Those most likely to benefit from the commitment contract and \textit{not} choose it are the individuals who most systematically over-estimate their own probability of repayment at the time of taking the loan.\footnote{More generally \hl{demand for commitment is higher among those with XXX characteristics.}}  Second, the existence of commitment-style repayment contracts in pawnshop lending is novel in Mexico.
 The dramatic improvements in borrower income arising from the commitment contract come directly from the pockets of lenders, reinforcing that the pawn industry as a whole has a strong interest in retaining the status quo.
 
-%do we want this paragraph on learning?
 Does learning eventually overcome the low demand for commitment?
 For learning to happen clients would need to experiment the frequent payment contract, and this was not the typical contract in the industry.
-But even if the contract was experienced, borrowers may fail to learn or learn only slowly.
-We find that those who are forced to the monthly payment product are 6.7 percentage points more likely to become repeat customers than those assigned to the status-quo contract.
-One way to interpret this is \textcolor{blue}{as `learning they like pawn-borrowing', i.e.
-having experienced the frequent payment contract (and the lower financial cost of borrowing that come with it), they like pawning and pawn more.}\footnote{A second intepretation is that the iliquidity created by the monthly payment contract makes them want obtain second loan to pay the first one.
+But even if the contract was experienced, borrower may fail to learn or learn only slowly.
+We find that those who are forced to the monthly payment product are 6.7 percentage points more likely to become repeat costumers than those assigned to the status-quo contract.
+One way to interpret this is that that having experienced the frequent payment contract (and the lower financial cost of borrowing that come with it), they want to borrow more.\footnote{A second intepretation is that the iliquidity created by the monthly payment contract makes them want obtain second loan to pay the first one.
 This second explanation is unlikely since borrowers obtain a second loan not within the first 90 days of the first loan when payments are due; moreover, the correlation is also present conditional on having paid down the first loan.
-Borrowers tend to pledge a different piece for the second loan, so that recovery of the first pawn is also an unlikely explanation.
-\textcolor{blue}{A different test, about `learning they like monthly-payments'} is whether conditional on coming again, clients would choose frequent payments.
-We test this and we cannot reject that demand is \textit{not} higher after experiencing the monthly payment contract, \textcolor{blue}{consistent with no learning or slow learning that the monthly payment contract is better than the status quo contract}, however sample sizes are small and \hl{the minimum detectable effect is XXX.}} %\textcolor{blue}{making this more rigorous test of learning inconclusive and left for future research.
-Having said this, after more than 100 years in operation, the biggest pawn lender in Mexico and most others still do not offer structured payment contracts.}
+Borrowers tend to pledge a different piece for the second loan, so that recovery of the first pawn is also an unlikely explanation.} However, a stronger test of liking the monthly payment contract is whether conditional on coming again, they would choose frequent payments.
+We test this and we cannot reject that demand is not higher after experiencing the monthly payment contract, however sample sizes are small and \hl{the minimum detectable effect is XXX.}
 
@@
 
-%Replace this paragraph with discussion of optimal targeting of paternalism
 Our results suggest that pawn lending markets capture borrower wealth in ways not well summarized by interest rates.
-By over-collateralizing and then structuring loan contracts in a manner encouraging of default, lenders are able to extract substantial value independent of the interest charged.
+By overcollateralizing and then structuring loan contracts in a manner encouraging of default, lenders are able to extract substantial value independent of the interest charged.
 Further, the `nudge’ approach generally favored by the behavioral literature (voluntary commitment) may not be adequate.
@@
 Moreover, frequent payment requirements may decrease welfare of highly impatient borrowers.\footnote{The paper presents an back of the envelope exercise that suggests annual discount rates of 4000 are necessary to nullify the reductions in financial cost we estimate.
-\hl{Note also that since the fee for skipping payment is 2\% of the payment due, the illiquidity imposed by the contract is bounded.}} %Second, given the non-standard nature of the finding, it is likely that we would have to adopt and estimate a particular behavioral model of demand for commitment, which we don't need to do to make the point that TuT is positive.
+\hl{Note also that since the fee for skipping payment is 2\%, the iliquidity imposed by the contract is bounded.}} %Second, given the non-standard nature of the finding, it is likely that we would have to adopt and estimate a particular behavioral model of demand for commitment, which we don't need to do to make the point that TuT is positive.
 
@@
 
-Our paper speaks to several strands of the literature.
-First, we contribute methodologically to the large literature on treatment effect heterogeneity by showing how an experimental design with two forcing arms and one choice arm allows for identification of the ToT, the TuT and other important parameters under minimal assumptions.
-A large literature inspired by \cite{heckman1979sample} and \cite{angrist1996identification} has used an exclusion restriction to instrument for the LATE; rarer are studies that have compared forcing to choice to instrument for the TUT (such as looking at compulsory high school requirements \citep{oreopoulos2006estimating}, and one at technology that defaults individuals into variable pricing of electricity \citep{fowlie2021default}.
-When the three arms (control, choice, and forcing) are randomized in the same environment we gain a clear and policy-relevant window into how selection into treatment relates to heterogeneity in treatment effects.
-This comparison of treatment effects across the compliance distribution is closely related to the evaluation of Marginal Treatment Effects, and hence speaks to the large observational literature using parametric assumptions and continuous instruments to estimate MTEs , such as \cite{heckman2007econometric} and \cite{cornelissen2018benefits}, and \cite{Walters}.
-
-%\cite{aronow2013beyond} and \cite{angrist2013extrapolate} assume no selection on gains to estimate \hl{XXX}.
-\cite{Walters} achieve identification of the TuT by using parametric model and a distance instrument, which requires the model to be correct and the instrument
-
-Second, we join a more nacent literature shedding light into private paternalism.
-In the context of food choice, \cite{Sprenger} elicit dynamic inconsistencies, and then find that demand for commitment is negatively correlated with such inconsistency.
-In the context of school choice, \cite{Walters} finds that students that select into more effective schools have smaller treatment effects from attending than those that select out.
-Besides being very different contexts from ours, we rely on very different methods.
-In contrast to \cite{Sprenger} we will directly point identify the TuT, obviating the need for elicitation of preferences to test for negative selection.
-In contrast to \cite{Walters} we use randomization while he needs a structural model and distance to school as an instrument.
-\todo[inline]{FRANK, can we say something more precise than ``a structural model''?}
-
-Finally, our results speak to the financial literature that examines the effect of contract structure on repayment.
+Our paper speaks to several strands of the literature.   %First, they suggest consequential ways in which different financial services draw client pools with distinct behavioral biases. 
+First, to research in microfinance studying the effect of payment frequency.
 While research in microfinance markets has not found the same benefits from providing a more regularized repayment environment \citep{Pande}, those experiments are performed on top of highly structured contracts and among borrower pools who may have selected into that type of lending precisely because it provides structure.
@@
 %Finally, we provide only the second case in the literature, and the first in the analysis of financial products, to illustrate the perverse result that those who opt into commitment are precisely the individuals who do not need it \citep{Sprenger}.
+
+Two recent papers that shed some light into private paternalism.
+In the context of food choice, \cite{Sprenger} elicit dynamic inconsistencies, and then find that demand for commitment is negatively correlated with such inconsistency.
+In the context of school choice, \cite{Walters} finds that students that select into more effective schools have smaller treatment effects from attending than those that select out.
+Besides being very different contexts from ours, we rely on very different methods.
+In contrast to \cite{Sprenger} we will directly point identify the TuT, obviating the need for elicitation of preferences to test for negative selection.
+In contrast to \cite{Walters} we use randomization while he needs a structural model and distance to school as an instrument.
+\hl{FRANK, can I say something more precise than ``a structural model''?}
+
+Methodologically we contribute to the large literature on treatment effect heterogeneity by showing how an experimental design with two forcing arms and one choice arm allows for identification of the TOT, the TUT and other important parameters under minimal assumptions.
+\cite{aronow2013beyond} and \cite{angrist2013extrapolate} assume no selection on gains to estimate \hl{XXX}.
+\cite{Walters} achieve identification of the TuT by using parametric model and a distance instrument, which requires the model to be correct and the instrument to be valid.
+TUT and ATE implied by LATE-and-re-weight differ sharply from his model-based estimates.
+The method of
+\cite{heckman2007econometric} and \cite{cornelissen2018benefits} require the availability of instrumental variable with rich support, and separability of observed and unobserved determinants of treatment effects.
 
@@
 
-\paragraph{Most borrowers lose their pawn.} Our context is also one with high borrower default: \hl{60\%} of clients lose their pawn in a time span of 230 days from the date of pawning.
+\paragraph{Most borrowers lose their pawn.} Our context is also one with high borrower default: 60\% of clients lose their pawn in a time span of 230 days from the date of pawning.
 One potential explanation for high default is that clients are really just knowingly selling their gold piece through a pawn contract on which they intend to default.
@@
 Transportation cost to go to the branch to pay is on the same order of magnitude as the fee on average.\footnote{%The lender was worried that if the fee was large, forgetting to pay could make the pawn unrecoverable.
-%In contrast with \cite{John} we don't let the clients choose the size of the fee.
+In contrast with \cite{John} we don't let the clients choose the size of the fee.
 \cite{John} shows that doing this results in costly choices by (partially) naive present biased consumers.
 Our fee is much smaller than the median in her experiment.
+%We also experimented with a contract where there was no pecuniary fee for paying late but where we clients made a personal promise to pay monthly.
 } To elicit demand for the monthly payment contract, we include an arm that allows borrowers to opt into this contract if they choose.
@@
 
-\paragraph{Who chooses commitment?}
-
-A natural starting point for understanding the role of voluntary commitment is the determinants of choice.
-Figure \ref{determinants_choose} provides coefficient plots for univariate and multivariate Linear Probability Models explaining takeup of commitment in the Choice arm.
-Contrary to the standard behavioral motivations, none of our measures of self control predict takeup, neither the metric arising from the paired discounting questions (e.g.
-those who are more impatient over immediate rather than future delays), nor a simple survey question asking whether they are tempted to mis-use money in their financial lives.
-Individuals who report having trouble paying bills are actually \textit{less} likely to take commitment, as are those who have pawned before.
-The only determinant in this figure that represents something like sophistication is that those with more education are more likely, in both univariate and multivariate regressions, to choose commitment.
-Overall, we observe few strong determinants of commitment choice and the story does not appear to be a behavioral one.
-
 \subsection{Experimental Integrity}
@@
 
-\section{Average Treatment Effects} 
-\label{experiment}
+\section{Average Treatment Effects} \label{experiment}
 
@@
 
-%\todo[inline]{Add a column with losing pawn. What about re-pawning?}
-%\todo[inline]{How did we decide to deal with censoring?}
+\todo[inline]{Add a column with losing pawn. What about re-pawning?}
+\todo[inline]{How did we decide to deal with censoring?}
 
@@
 
-%\todo[inline]{I think the re-pawn table should only have 4 columns.
+\todo[inline]{I think the re-pawn table should only have 4 columns.
 Remove variables 3,4, and 7.
@@
 
-%\subsection{Censoring of Loan Completion}
-
-\paragraph{Censoring of Loan Completion.} The window of time during which we were able to observe borrower behavior was limited in each branch, meaning that there were loans that we do not see completed (particularly those pawns that were rolled over for one or two further 90-day spells).
-Overall, \hl{XX\%} of all experimental loans are censored, meaning that they neither default nor repaid within the observation window.
+\subsection{Censoring of Loan Completion}
+
+The window of time during which we were able to observe borrower behavior was limited in each branch, meaning that there were loans that we do not see completed (particularly those pawns that were rolled over for one or two further 90-day spells).
+Overall, \hl{XX\%} of all experimental loans are censored, meaning that they neither default nor repay within the observation window.
 In the prior analysis we handle this issue by using outcomes such as `did not default' which are defined even when we do not observe the completion of the loan, and only considering costs that we observe directly.
@@
 The first is the extent to which loan outcomes are observed more quickly in the forcing arm.
-This is primarily due to the the substantially higher rate of repayment of Forced Commitment loans at 120 days ($\sim$15 pp higher than the other arms).
+This is primarily due to the the substantially higher rate of repayment of Forced Commitment loans at 120 days (~15 pp higher than the other arms).
 The second is the very low rate at which loans are recovered in any arm after 120 days.
-In the 180 day window after the second rollover period we see a further $\sim$10 percent of loans repaid in all arms, but these loans are largely dormant, suggesting that many of the censored loans will in fact be defaulted upon.
-
-The approach taken so far is a conservative one in that it inherently assumes that all of the loans outstanding at the end of the observation window will be repaid, making it so that the acceleration of payment observed in the forced commitment arm does not translate mechanically into a treatment effect on default.
-\textcolor{blue}{Appendix \ref{App_censoring} imputes default predictions for censored loans and also performs a bounding exercise and reaches similar conclusions.}
-%The confluence of censoring and a treatment effect on censoring is problematic from an experimental point of view.
-
-\begin{comment}
+In the 180 day window after the second rollover period we see a further ~10 percent of loans repaid in all arms, but these loans are largely dormant, suggesting that many of the censored loans will in fact be defaulted upon.
+
+The confluence of censoring and a treatment effect on censoring is problematic from an experimental point of view.
 The approach taken so far is a conservative one in that it inherently assumes that all of the loans outstanding at the end of the observation window will be repaid, making it so that the acceleration of payment observed in the Forced arm does not translate mechanically into a treatment effect on default.
@@
 Hence, while the censoring issue does have a substantial influence on the magnitude of our estimated treatment effects, these  checks confirm that a) the core results are robust to censoring, and b) the headline approach that we take to the issue is conservative and is likely understating the true magnitude of impacts.
-\end{comment}
+%\end{comment}
 
@@
 
-Figure \ref{fig:FanPark} plots the sharp bounds for $F_{\delta}$ based on the APR outcome defined above in Section \ref{costs}.
+Figure \ref{fan_park_bounds} plots the sharp bounds for $F_{\delta}$ based on the APR outcome defined above in Section \ref{costs}.
 Our point estimates of $\underline{F}(0)$ and $\overline{F}_0$ are \hl{XXXX} and \hl{XXXX} respectively, with associated 95\% confidence intervals of \hl{XXXX} and \hl{XXXX}.\footnote{Confidence intervals are constructed using \hl{XXXX} bootstrap.
@@
 Moreover, each has testable implications that we fail to reject.
-For details, see Appendix \ref{append:exclusion}.
+For details, see \ref{append:exclusion}.
 %\todo[inline]{@Frank, do we need to say a bit more about these testable implications or is it too technical? (Enrique)}
@@
 We now show how our experimental design, henceforth the ``controlled choice design,'' combined with the exclusion restrictions from \eqref{eq:exclusion0} and \eqref{eq:exclusion1} can be used to point identify a number of interesting and economically-relevant causal quantities without the need for additional structural restrictions.
-First we identify the treatment on the treated (ToT) and treatment on the untreated (TuT) effects, defined as follows:
+First we identify the treatment on the treated (TOT) and treatment on the untreated (TUT) effects, defined as follows:
 \[
-\text{ToT} \equiv \mathbbm{E}(Y_{i1} - Y_{i0} | C_i = 1), \quad
-\text{TuT} \equiv \mathbbm{E}(Y_{i1} - Y_{i0} | C_i = 0).
+\text{TOT} \equiv \mathbbm{E}(Y_{i1} - Y_{i0} | C_i = 1), \quad
+\text{TUT} \equiv \mathbbm{E}(Y_{i1} - Y_{i0} | C_i = 0).
 \]
-%The TuT and ToT effects are particularly interesting for understanding the importance of paternalism. 
-If the TuT is positive, this means that those who did not choose commitment would have experienced better outcomes, \emph{on average}, if they had. 
-In a canonical Roy model, the ToT should exceed both the TuT and average treatment effect (ATE).
-If the ToT is statistically distinguishable from and substantially larger than the TuT, this provides empirical support for the relevance of selection-on-gains in real-world decision-making.
+%The TuT and TOT effects are particularly interesting for understanding the importance of paternalism. 
+If the TUT is positive, this means that those who did not choose commitment would have experienced better outcomes, \emph{on average}, if they had. 
+In a canonical Roy model, the TOT should exceed both the TUT and average treatment effect (ATE).
+If the TOT is statistically distinguishable from and substantially larger than the TUT, this provides empirical support for the relevance of selection-on-gains in real-world decision-making.
 Because our design identifies all three quantities, it allows us to test this implication directly and to calculate the average selection on gains (ASG):
 \[
-\text{ASG} \equiv \mathbbm{E}[Y_{i1} - Y_{i0}|C_i = 1] - \mathbb{E}[Y_{i1} - Y_{i0} | C_i = 0] = \text{ToT} - \text{TuT}.
+\text{ASG} \equiv \mathbbm{E}[Y_{i1} - Y_{i0}|C_i = 1] - \mathbb{E}[Y_{i1} - Y_{i0} | C_i = 0] = \text{TOT} - \text{TUT}.
 \]
@@
 \]
-A companion STATA package accompanying this paper provides estimators of the ToT, TUT, ASG, ASB, and ASL, along with cluster-robust standard errors for each.\footnote{See Appendix \ref{append:randchoice} for more details.}
-
-A number of recent papers compare estimates of the ToT and TuT to better understand who selects into treatment and why, e.g.\ \cite{cornelissen2018benefits} and \cite{Walters}. 
-This line of work relies, at least to some extent, upon structural modeling assumptions to extrapolate from the reduced-form quantities that are identified by the data alone to more interesting, and economically relevant, causal parameters.\footnote{While the marginal treatment effects (MTE) approach \citep{heckman2007econometric} can in principle be used to identify the ToT and TuT without parametric restrictions, doing so requires an instrumental variable $Z$ with sufficiently rich support that the probability of treatment take-up given $Z$ varies continuously between zero and one.
+A companion STATA package accompanying this paper provides estimators of the TOT, TUT, ASG, ASB, and ASL, along with cluster-robust standard errors for each.\footnote{See Appendix \ref{append:randchoice} for more details.}
+
+A number of recent papers compare estimates of the TOT and TUT to better understand who selects into treatment and why, e.g.\ \cite{cornelissen2018benefits} and \cite{Walters}. 
+This line of work relies, at least to some extent, upon structural modeling assumptions to extrapolate from the reduced-form quantities that are identified by the data alone to more interesting, and economically relevant, causal parameters.\footnote{While the marginal treatment effects (MTE) approach \citep{heckman2007econometric} can in principle be used to identify the TOT and TUT without parametric restrictions, doing so requires an instrumental variable $Z$ with sufficiently rich support that the probability of treatment take-up given $Z$ varies continuously between zero and one.
 In practice, instrumental variables are usually discrete and, even when continuous, typically have a more modest effect on take-up.}
@@
 But there is no free lunch: this ``LATE-and-reweight'' approach relies upon assumptions of its own, most crucially the assumption that there is \emph{no selection-on-gains} conditional on $X$, i.e.\ that the conditional LATE equals the conditional ATE.
-In contrast to both approaches, the controlled choice design uses exogenous experimental variation to point identify the ATE, ToT, and TuT without ruling out unobserved selection-on-gains or relying on additional structural modeling assumptions.
+In contrast to both approaches, the controlled choice design uses exogenous experimental variation to point identify the ATE, TOT, and TUT without ruling out unobserved selection-on-gains or relying on additional structural modeling assumptions.
 
@@
 \frac{\mathbbm{E}(Y_i|Z_i=2) - \mathbbm{E}(Y_i|Z_i =0)}{\mathbbm{E}(D_i|Z_i=2)} = \mathbbm{E}(Y_{i1} - Y_{i0}|C_i = 1)
-\label{eq:ToT}
+\label{eq:TOT}
 \end{equation}
 since $\mathbbm{E}(D_i|Z_i=0)=0$ by \eqref{eq:potentialTreatments}. 
-A closely related argument can be used to construct a Wald estimand that identifies the TuT.
+A closely related argument can be used to construct a Wald estimand that identifies the TUT.
 Here we consider $Z_i = 1$ to be the ``encouragement'' and compare the outcomes for these individuals to those with $Z_i = 2$.
-If $Z_i = 1$ then $D_i = 1$ and we observe $Y_{i1}$; If $Z_i = 2$ then $D_i = C_i$ and we observe $(1 - C_i) Y_{i0} + C_i Y_{i1}$.
+If $Z_i = 1$ then $D_i = 1$ and we observe $Y_{i1}$.
+If instead $Z_i = 2$ then $D_i = C_i$ and we observe $(1 - C_i) Y_{i0} + C_i Y_{i1}$.
 Again, we can view this as an experiment with one-sided non-compliance, but now the situation is reversed.
@@
 \frac{\mathbbm{E}(Y_i|Z_i=1) - \mathbbm{E}(Y_i|Z_i =2)}{1 - \mathbbm{E}(D_i|Z_i=2)} = \mathbbm{E}(Y_{i1} - Y_{i0} | C_i = 0)
-\label{eq:TuT}
+\label{eq:TUT}
 \end{equation}
 since $\mathbbm{E}(D_i|Z_i = 1)= 1$ by \eqref{eq:potentialTreatments}.
-Equations \eqref{eq:ToT} and \eqref{eq:TuT} are useful for understanding why the controlled choice design identifies the ToT and TuT, but they are less convenient for estimation and inference.
-In Appendix \ref{append:randchoice}, we show that
+Equations \eqref{eq:TOT} and \eqref{eq:TUT} are useful for understanding why the controlled choice design identifies the TOT and TUT, but they are less convenient for estimation and inference.
+In \ref{append:randchoice}, we show that
 \begin{align}
-\label{eq:ToTreg}
-Y_i &= \mathbbm{E}(Y_{i0}) + (\text{ATE}) \mathbbm{1}(Z_i = 1) + (\text{ToT}) \left[\mathbbm{1}(Z_i = 2) \times D_i\right] + U_i \\
-\label{eq:TuTreg}
-Y_i &= \mathbbm{E}(Y_{i1}) + (\text{ATE}) \left[ -\mathbbm{1}(Z_i = 0)\right] + (\text{TuT}) \left[ -\mathbbm{1}(Z_i = 2) \times (1 - D_i)\right] + V_i 
+\label{eq:TOTreg}
+Y_i &= \mathbbm{E}(Y_{i0}) + (\text{ATE}) \mathbbm{1}(Z_i = 1) + (\text{TOT}) \left[\mathbbm{1}(Z_i = 2) \times D_i\right] + U_i \\
+\label{eq:TUTreg}
+Y_i &= \mathbbm{E}(Y_{i1}) + (\text{ATE}) \left[ -\mathbbm{1}(Z_i = 0)\right] + (\text{TUT}) \left[ -\mathbbm{1}(Z_i = 2) \times (1 - D_i)\right] + V_i 
 \end{align}
-where the error terms $U_i$ and $V_i$ satisfy 
-\[
-\mathbbm{E}(V_i) = \mathbbm{E}(U_i) = \mathbbm{E}[U_i \mathbbm{1}(Z_i = z)] = \mathbbm{E}[V_i \mathbbm{1}(Z_i = z)] = 0, \quad z = 0, 1, 2.
-\]
-It follows that a pair of just-identified, linear instrumental variables regressions can be used to estimate and carry out inference for the ATE, ToT, and TuT.
-To identify the ATE and ToT, run IV on \eqref{eq:ToTreg} with instruments $\mathbbm{1}(Z_i = 1)$ and $\mathbbm{1}(Z_i=2)$.
-An F-test based on this regression can then be used to test the restriction $\text{ATE} = \text{ToT}$, and the usual IV output can be used to carry out inference for the ToT.
-Similarly, to identify the ATE and TuT run IV on \ref{eq:TuTreg} with instruments $\mathbbm{1}(Z_i = 0)$ and $\mathbbm{1}(Z_i = 2)$.
-An F-test based on this regression can then be used to test the restriction $\text{ATE} = \text{TuT}$, and the usual IV output can be used to carry out inference for the TuT.
-
-Because they identify both the ToT and TuT, \eqref{eq:ToTreg} and \eqref{eq:TuTreg} also identify the average selection on gains: $\text{ASG} = \text{ToT} - \text{TuT}$.
-Carrying out inference for this quantity is a bit more involved, because $\text{ASG}$ a difference of coefficients from two separate IV regressions. 
-In Appendix \ref{append:randchoice} we show how to use the residuals from \eqref{eq:TuTreg} and \eqref{eq:ToTreg} to carry out cluster-robust inference for $\text{ASG}$, a procedure that is automated in our companion STATA package.
+where $\mathbbm{E}(U_i|Z_i) = \mathbbm{E}(V_i|Z_i) = 0$.
+It follows that a pair of just-identified, linear instrumental variables regressions can be used to estimate and carry out inference for the ATE, TOT, and TUT.
+To identify the ATE and TOT, run IV on \eqref{eq:TOTreg} with instruments $\mathbbm{1}(Z_i = 1)$ and $\mathbbm{1}(Z_i=2)$.
+An F-test based on this regression can then be used to test the restriction $\text{ATE} = \text{TOT}$, and the usual IV output can be used to carry out inference for the TOT.
+Similarly, to identify the ATE and TUT run IV on \ref{eq:TUTreg} with instruments $\mathbbm{1}(Z_i = 0)$ and $\mathbbm{1}(Z_i = 2)$.
+An F-test based on this regression can then be used to test the restriction $\text{ATE} = \text{TUT}$, and the usual IV output can be used to carry out inference for the TUT.
+
+Because they identify both the TOT and TUT, \eqref{eq:TOTreg} and \eqref{eq:TUTreg} also identify the average selection on gains: $\text{ASG} = \text{TOT} - \text{TUT}$.
+Carrying out inference for this quantity is a bit more involved, because $\text{ASG}$ is a difference of coefficients from two separate IV regressions. 
+In \ref{append:randchoice} we show how to use the residuals from \eqref{eq:TUTreg} and \eqref{eq:TOTreg} to carry out cluster-robust inference for $\text{ASG}$, a procedure that is automated in our companion STATA package.
 As mentioned above, the controlled choice design also identifies the average selection bias (ASB) and average selection on levels (ASL).
@@
 \end{align}
-as we show in Appendix \ref{append:randchoice}.
-For purposes of inference, both the ASB and ASL can be re-written as the difference of coefficients from a pair of just-identified linear IV regressions, namely
-\begin{align}
-\label{eq:ASB0}
-    \mathbbm{1}(Z_i\neq 1) (1 - D_i) Y_i &= \mathbbm{E}(Y_{i0}) \mathbbm{1}(Z_i = 0) + \mathbbm{E}(Y_{i0}|C_i=0)(1 - D_i)\mathbbm{1}(Z_i=2) + U_{i0}\\
-\label{eq:ASB1}
-    \mathbbm{1}(Z_i\neq 1) (1 - D_i) Y_i &= \mathbbm{E}(Y_{i0}) \mathbbm{1}(Z_i \neq 1) + \mathbbm{E}(Y_{i0}|C_i=1)(-D_i)\mathbbm{1}(Z_i = 2) + U_{i1}\\
-\label{eq:ASL0}
-    \mathbbm{1}(Z_i\neq 0) D_i Y_i &= \mathbbm{E}(Y_{i1}) \mathbbm{1}(Z_i \neq 0) + \mathbbm{E}(Y_{i1}|C_i=0)(D_i - 1)\mathbbm{1}(Z_i = 2) + V_{i0}\\
-\label{eq:ASL1}
-    \mathbbm{1}(Z_i\neq 0) D_i Y_i &= \mathbbm{E}(Y_{i1}) \mathbbm{1}(Z_i = 1) + \mathbbm{E}(Y_{i1}|C_i=1)D_i \mathbbm{1}(Z_i = 2) + V_{i1}
-\end{align}
-where the error terms $(U_{i0}, U_{i1})$ and $(V_{i0}, V_{i1})$ satisfy
-\[
-\mathbbm{E}
-\begin{pmatrix}
-V_{i0} \\ 
-V_{i1} \\ 
-\end{pmatrix} = 
-\mathbbm{E}\begin{pmatrix}
-U_{i0} \\ 
-U_{i1} \\ 
-\end{pmatrix}
-= \mathbbm{E}\left[
-\begin{pmatrix}
-V_{i0} \\ 
-V_{i1} \\ 
-\end{pmatrix} \mathbbm{1}(Z_i = z)
-\right]
-= \mathbbm{E}\left[
-\begin{pmatrix}
-U_{i0} \\ 
-U_{i1} \\ 
-\end{pmatrix} \mathbbm{1}(Z_i = z)
-\right] = 0
-, \quad z = 0, 1, 2.
-\]
-As in the case of the ASG from above, inference for the ASB and ASL can be carried out by saving the residuals from \eqref{eq:ASB0}--\eqref{eq:ASL1}. 
-These calculations are also automated in our companion STATA package.
-For details, see Appendix \ref{append:randchoice}.
+as shown in \ref{append:randchoice}.
+For purposes of inference, both the ASB and ASL can be re-written as the difference of coefficients from a pair of just-identified linear IV regressions.
+For details, along with a description of how our companion STATA package carries out cluster-robust inference for these quantities, see \ref{append:randchoice}.
 
@@
 %This structure allows us to observe the average value of both the treated and untreated potential outcomes, as well as the selection into treatment that would occur under choice.
-A starting point for how to exploit this structure is to apply the logic usually used to estimate the Treatment on the Treated (ToT) to also recover the Treatment on the Untreated (TuT).
+A starting point for how to exploit this structure is to apply the logic usually used to estimate the Treatment on the Treated (ToT) to also recover the Treatment on the Untreated (TUT).
 This approach assumes nothing about the decision to choose (other than random sampling generating counterfactual compliance rates that would have been the same in every arm), but imposes three exclusion restriction-style assumptions typical of Local Average Treatment Effect (LATE) analysis.
@@
 The observed outcome in the Choice arm is the weighted average of the treated and untreated outcomes; $p \times\mathbb{E}[Y_1\;|\;C=1] + (1-p)\times\mathbb{E}[Y_0\;|\;C=0]$.
-Given assumptions a) and c) above we can recover the ToT from the difference between the Choice and Control arms as is standard, and then symmetrically we can invoke b) and c) to recover the TuT from the difference between the Forced and Choice arms as follows:
+Given assumptions a) and c) above we can recover the ToT from the difference between the Choice and Control arms as is standard, and then symmetrically we can invoke b) and c) to recover the TUT from the difference between the Forced and Choice arms as follows:
 
@@
 
-Table \ref{tot_tut} calculates the causal quantities described above--ToT, TuT, ASG, ASB, and ASL--for our experimental data, along with robust standard errors for each. 
+Table \ref{tot_tut} calculates the causal quantities described above--TOT, TUT, ASG, ASB, and ASL--for our experimental data, along with robust standard errors for each. 
 For purposes of comparison, the table also presents the ATE results from Section \ref{experiment} above (row 1), along with the corresponding average potential outcomes $\mathbbm{E}[Y_0]$ and $\mathbbm{E}[Y_1]$ (rows 4--5).
 The columns of the table correspond to different outcome variables, defined as in Section \ref{costs} above.
-For all four outcome definitions, the TuT effect is positive, statistically and economically significant, and comparable in magnitude to the ATE.
+For all four outcome definitions, the TUT effect is positive, statistically and economically significant, and comparable in magnitude to the ATE.
 In other words: commitment is \emph{beneficial}, on average, to the people who \emph{would not choose it}, and these benefits are large.
-The estimated ToT effects are positive and larger still.
-Although we cannot quite reject the null hypothesis that the TuT and ToT effects are equal--our power is limited because of the low take-up rate of commitment in the choice arm--the pattern of coefficients is consistent with some degree of selection-on-gains.
+The estimated TOT effects are positive and larger still.
+Although we cannot quite reject the null hypothesis that the TUT and TOT effects are equal--our power is limited because of the low take-up rate of commitment in the choice arm--the pattern of coefficients is consistent with some degree of selection-on-gains.
 Commitment is more beneficial to people who are willing to choose it than it is to people who are not.
@@
 
-The behavioral literature has highlighted voluntary commitment as an attractive way of allowing the `right' people to self-select.
+The behavioral literature has highlighted voluntary commitment as an attractive way of allowing the ``right'' people to self-select.
 A discussion of compulsory commitment is necessarily paternalistic, and by its nature focuses on impacts among those who would not have selected commitment voluntarily.
-From the lens of rational choice it is unsurprising that we find the $\text{ToT}>\text{TuT}$, but the argument for compulsory treatment centers on the more surprising result that we find $\text{TuT}>0$.
+Viewed through the lens of rational choice theory, it is unsurprising that we estimate $\text{TOT}>\text{TUT}$.
+The argument for compulsory treatment, however, centers on the more surprising result that $\text{TUT}>0$.
 We now investigate several potential explanations for why this might be the case in our context.
@@
 \paragraph{Learning.} A first explanation involves learning.
-We were bringing a new contract into an environment that had not previously featured commitment; perhaps clients required experience to understand its benefits?
-Given the strongly positive impact of forcing, our clearest hypothesis would be that clients forced once would choose commitment if subsequently given the chance to do so.
-While the sample size for this is small, we do have a group of 240 clients who were exposed to the experiment in one round and then returned to take another loan at a branch where the choice of commitment was offered.
+Our experiment introduced a new contract into an environment that had not previously featured commitment; perhaps clients required experience to understand its benefits.
+Given the strongly positive impact of forcing, this explanation would suggest that clients who were forced once would subsequently choose commitment if given the chance to do so.
+A subset of \hl{240 clients} from our experiment who were exposed to the experiment in one round and then returned to take another loan at a branch where the choice of commitment was offered.
 Table \ref{learning_table} shows the results of this analysis.
-While this regression is underpowered, the point estimate on prior assignment to the commitment contract is actually negative.
+While this regression is underpowered, given the small sample size, the point estimate on prior assignment to the commitment contract is actually negative.
 Hence the window available to us on learning provides little comfort that the lack of voluntary compliance is simply a matter of inexperience with commitment.\footnote{\textcolor{blue}{Risk could be another alternative potential explanation for low take up of the commitment contract.
@@
 
-\paragraph{Time discounting.} Discounting is a second explanation for our results.
-Using no discounting we find a decrease in the financial cost of credit, but the intervention inherently imposes up-front costs (early payment) in return for delayed benefits (recovery of pawn).
-Highly impatient individuals might therefore rationally choose not comply although our measure would show a benefit for them in undiscounted returns.
-To investigate this we can calculate the Net Present Value of the $TUT$ on financial cost given the %average
-timing of repayment and pawn recovery, for different discount rates.
-Figure \ref{fc_discount_rates} shows the results of this exercise, illustrating that non-choosers continue to see significant decreases in NPV financial costs up to annual discount rates of 4,000\%, and the NPV remains negative at 10,000\% discount rates.
-Given this, we think that discounting is unlikely to explain non-compliance among those who appear to benefit.
-
-\paragraph{Present bias.} If commitment benefits among non-compliers cannot be explained by rational choice, the canonical behavioral story would center on time inconsistency.
-While commitment is useful to anyone with hyperbolic time preferences, only those who are sophisticated will demand it.
-A large share of naive hyperbolics in the population could therefore drive a large $TuT$.
-Our baseline survey included standard questions about discount rates between today and a month in the future versus discount rates between three and four months in the future.\footnote{The remaining exercises in the paper will use information from the intake survey, and hence use only the subset of individuals who responded to the survey.
-While this is a selected sample, we believe this to be benign in that the impacts estimated using the full and survey-respondent sample are very similar.}  This allows us to classify borrowers who display more impatience over immediate delays as time inconsistent.
-This measure of financial hyperbolicity is widely used in survey research, although it is not without problems.\footnote{Our measure is dichotomous, and is not incentivized.
-Recent empirical work has shown the superiority of more sophisticated measures such as Convex Time Budgets \citep{andreoni2015measuring} as well as questioning the interpretation of measures of hyperbolicity not based on consumption \citep{andreoni2012estimating, cohen2020measuring}, suggesting that real effort tasks provide a better measure \citep{augenblick2015working}.
+\paragraph{Time discounting.} Discounting is a second potential explanation for our results.
+Our estimated decrease in the financial cost of credit from above ignores discounting, but the intervention inherently imposes up-front costs (early payment) in return for delayed benefits (recovery of pawn).
+Highly impatient individuals might therefore rationally choose the \emph{status quo} contract, despite our results showing a benefit raw (undiscounted) returns.
+To investigate this explanationwe can calculate the Net Present Value of the $TUT$ on financial cost given the timing of repayment and pawn recovery for different hypothetical discount rates.
+Figure \ref{fc_discount_rates} presents the results of this exercise.
+We see that non-choosers continue to experience significant decreases in NPV financial costs up to annual discount rates of 4,000\%, and the NPV remains negative, although not significant, at 10,000\% discount rates.
+As such, discounting is unlikely to explain why those who benefit, on average, from commitment fail to choose it when offered.
+
+\paragraph{Present bias.} If commitment benefits among non-choosers cannot be explained by rational choice, the canonical behavioral story would center on time inconsistency.
+While commitment is useful to anyone with hyperbolic time preferences, only those who are sophisticated--i.e.\ aware that they are hyperbolic discounters--will demand it.
+A large share of naive hyperbolics in the population could therefore drive a large and positive $\text{TUT}$.
+Our baseline survey included standard questions about discount rates between today and a month in the future versus discount rates between three and four months in the future.\footnote{The remaining exercises in the paper require information from the intake survey, and hence use only the subset of individuals who responded to the survey.
+While this is a selected sample, estimates of the ATE, TOT, and TUT are nearly identical whether computed from the full sample survey-respondent sub-sample.}  This allows us to classify borrowers who display more impatience over immediate delays as time inconsistent.
+This measure of financial hyperbolicity is widely used in survey research, although it is not without problems.\footnote{Our measure is dichotomous, and it is not incentivized.
+Recent empirical work has shown the superiority of more elaborate measures such as ``convex time budgets'' \citep{andreoni2015measuring} while questioning the interpretation of measures of hyperbolicity that are not based on consumption \citep{andreoni2012estimating, cohen2020measuring}, suggesting that real effort tasks provide a better measure \citep{augenblick2015working}.
 Given that we had only a few minutes to interview real pawnshop clients prior to a commercial transaction, our simple measure was a necessary compromise.}
 
-If measurement of hyperbolicity were perfect, the sample should then be comprised of three groups:  the sophisticated hyperbolics who chose commitment, the time-consistent non-compliers (for whom forcing will not be effective) and the naive hyperbolic non-compliers (for whom it will).
-This would imply that the forcing effect should arise entirely from within hyperbolic non-compliers, a fact which can be checked by estimating the $TuT$ conditional on hyperbolicity.
-
-We can calculate the relative contributions of any two groups $X_i=0$ or $X_i=1$ to the $TuT$ among the non-compliers as follows:
-
-    \begin{align*}
-        1=& \frac{\mathbb{E}[Y_{1i}-Y_{0i} | C_i=0, X_i=1]}{TuT}\Pr(X_i=1 | C_i=0) \\
-        \quad &+ \frac{\mathbb{E}[Y_{1i}-Y_{0i}| C_i=0, X_i=0]}{TuT}\Pr(X_i=0 | C_i=0)
-    \end{align*}
-
-If, as theory would predict, the $TuT$ arises solely from hyperbolics then the former term will be 1 and the latter 0.
+If we could perfectly measure hyperbolicity, we could divide the sample into three groups: sophisticated hyperbolics who chose commitment, time-consistent non-chooser for whom forcing will not be effective, and naive hyperbolic non-choosers for whom it will.
+If hyperbolic discounting fully explains the low take-up rate of voluntary commitment, this would imply that the forcing effect should arise entirely from hyperbolic non-choosers.
+If our survey measure divides borrowers into the correct groups, this implication can be checked by estimating the $\text{TUT}$ conditional on hyperbolicity.
+
+For any binary pre-treatment covariate $X_i$, we can calculate the relative contributions of any two groups $X_i=0$ or $X_i=1$ to the overall $\text{TUT}$ effect using the following decomposition: 
+\begin{align}
+        1=& \frac{\mathbbm{E}[Y_{1i}-Y_{0i} | C_i=0, X_i=1]}{\text{TUT}}\mathbbm{P}(X_i=1 | C_i=0) \\
+        \quad &+ \frac{\mathbbm{E}[Y_{1i}-Y_{0i}| C_i=0, X_i=0]}{\text{TUT}}\mathbbm{P}(X_i=0 | C_i=0)
+        \label{eq:decomp}
+\end{align}
+where $\text{TUT}$ is the overall TUT effect and $\mathbbm{E}[Y_{1i} - Y_{0i}|C_i = 0, X_i = x]$ is the TUT conditional on $X_i = x$.    
+If, as the behavioral theory outlined above would predict, the $\text{TUT}$ arises solely from hyperbolics then term with $X_i=1$ the former term will be one and the term with $X_i = 0$ will be zero.
 
@@
 Hence over-optimistic expectations in recovery probabilities will translate directly into under-adoption of preventive measures.
-Similar to the definition of hyperbolicity above, we define a binary attribute we call `sure-confidence' which is individuals who say at the time of borrowing that they have a 100\% probability of recovering the loan.
+Similar to the definition of hyperbolicity above, we define a binary attribute we call ``sure-confidence.'' This measure equals one for any individuals who say at the time of borrowing that they have a 100\% probability of recovering their pawn.
+The same decomposition that we used above in our discussion of hyperbolic discounting, \eqref{eq:decomp}, can be used to explore the extent to which sure confidence explains our positive and significant TUT estimate by redefining the covariate $X_i$.
 
@@
 
-Figure \ref{tut_beh_partition} shows the relative contributions of present bias and sure-confidence for the $TuT$.
+Figure \ref{tut_beh_partition} shows the relative contributions of present bias and sure-confidence for the $TUT$.
 In each figure the orange bar represents the contribution from those who do not possess the attribute, and the blue bar from those that do.
 We see that the forcing effect is localized mostly to those who are \textit{not} time inconsistent, contradicting naive hyperbolicity as the justification for paternalism.
-Instead, we see sure-confidence being a category that completely isolates the $TuT$, suggesting that forcing works for those who do not consider repayment structure because they don't think they need it.
+Instead, we see sure-confidence being a category that completely isolates the $TUT$, suggesting that forcing works for those who do not consider repayment structure because they don't think they need it.
 Our measure of hyperbolicity is based on unincentivized responses in a short survey and so is likely to be noisy; nonetheless we see no evidence here that it drives the forcing effect.
@@
 
-If the attribute of `sure confidence' proves so important in explaining the TUT, what are the determinants of this characteristic?
+If the attribute of ``sure confidence'' proves so important in explaining the TUT, what are the determinants of this characteristic?
 In Figure \ref{determinants_sure} we plot the coefficient estimates from a regression that explains sure confidence with a battery of individual-level characteristics.
@@
 \paragraph{Causal forests.} Figure \ref{fig:FanPark} uses a completely non-parametric approach to understand winners and losers from paternalism at the individual level, but these bounds are relatively wide.
-To make more precise statements, we can invoke a selection on observables assumption and use the Random Forest approach of \cite{athey2019generalized} to estimate Conditional Average Treatment Effects (causal RF), or the Conditional TuT and ToT (instrumental RF).
-These impacts allow us to think about whether individuals made `mistakes' in their choices.
+To make more precise statements, we can invoke a selection on observables assumption and use the Random Forest approach of \cite{athey2019generalized} to estimate Conditional Average Treatment Effects (causal RF), or the Conditional TUT and TOT (instrumental RF).
+These impacts allow us to think about whether individuals made ``mistakes'' in their choices.
 Specifically, for each client in the choice arm we want to know how much cost savings would she have gained had she chosen the opposite contract.
@@
 \cite{atheygrf} show that their treatment effects are asymptotically normal, which allows us to construct confidence intervals for our treatment estimate in each leaf.
-This method gives us the causal effect on financing cost of getting the forced commitment contract instead of the status quo contract for a client $i$ with characteristics $x_i$; call it $TE^{F}_{i}(x_i)$.\footnote{Figure \ref{causal_tree1} and \ref{causal_tree2} provide an illustration of the splits (leaves) that emerge from our implementation of the RF.
+This method gives us the average causal effect on financing cost of getting the forced commitment contract instead of the status quo contract for a client $i$ with characteristics $x_i$; call it $TE^{F}_{i}(x_i)$.\footnote{Figure \ref{causal_tree1} and \ref{causal_tree2} provide an illustration of the splits (leaves) that emerge from our implementation of the RF.
 \todo[inline]{I think we should list in a footnote which are the `wide' variables we are using.}}
@@
 %Unless she is a strict utilitarian, any policymaker who is considering outlawing the \emph{status quo} contract in favor of the commitment contract needs to consider the extent and magnitude of harm that such a paternalistic policy will cause to \emph{individual} borrowers.
-Our TuT and ToT results from Section \ref{sec:randchoice} partially address this concern.
+Our TUT and ToT results from Section \ref{sec:randchoice} partially address this concern.
 In particular, our TuT estimates show that even those borrowers on whom a policy of paternalism would impose a binding constraint stand to benefit, on average, from commitment.
@@
 
-We examine treatment heterogeneity using a range of methods, from bounds that make no assumptions, exploiting a mild exclusion restrictions and the innovative controlled choice design to gain point identificatoin of TuT and ToT, and invoking seletion on observables to estimate treatment effects at the person level.
+We examine treatment heterogeneity using a range of methods, from bounds that make no assumptions, exploiting a mild exclusion restrictions and the innovative controlled choice design to gain point identification of TUT and TOT, and invoking seletion on observables to estimate treatment effects at the person level.
 We find that a large majority of clients benefit from the commitment contract, but that when given choice between the commitment and the status quo contract only 10\% choose the former one and thus forgo important financial benefits.
@@
 \begin{table}[H]
-\caption{Treatment on the Treated (ToT), Treatment on the Untreated (TuT), Selection-on-gains (ToT - TuT), Average Selection Bias (ASB), and Average Selection Bias, calculated using the results from Section \ref{sec:randchoice}.}
+\caption{Treatment on the Treated (TOT), Treatment on the Untreated (TUT), Selection-on-gains (TOT - TUT), Average Selection Bias (ASB), and Average Selection Bias, calculated using the results from Section \ref{sec:randchoice}.}
 \label{tot_tut}
@@
 \begin{figure}[H]
-     \caption{ToT \& TuT as LATE}
+     \caption{TOT \& TUT as LATE}
     \label{tot_tut_graph}
@@
 \begin{figure}[H]
-    \caption{Fan \& Park bounds for benefit in APR\% \hl{Is this without covariates? Are we going to show bounds for the other outcomes?}}
-    \label{fig:FanPark}
+    \caption{Fan \& Park bounds for benefit in APR\%}
+    \label{fan_park_bounds}
     \begin{center}
@@
 \begin{figure}[H]
-    \caption{Choice of contracts and treatment effects (ToT \& TuT)}
+    \caption{Choice of contracts and treatment effects (TOT \& TUT)}
     \label{choose_wrong}
@@
         \centering
-        \includegraphics[width=\textwidth]{Figuras/money_cw_apr_tot_tut.pdf}
+        \includegraphics[width=\textwidth]{Figuras/integral_cw_apr_tot_tut.pdf}
 

### 2023-07-04 RScripts/te_grf.R

@@ -41,6 +41,7 @@ te_grf <- function(data_in, outcome_var, name) {
     "dummy_suc4",
     "dummy_suc5",
     "dummy_suc6",
+    "prestamo",
     "edad",
     "faltas",
     "c_trans",
@@ -70,6 +71,7 @@ te_grf <- function(data_in, outcome_var, name) {
     "branch.4",
     "branch.5",
     "branch.6",
+    "loan.size",
     "age",
     "trouble.paying.bills",
     "transport.cost",
@@ -105,63 +107,6 @@ te_grf <- function(data_in, outcome_var, name) {
   X <- select(data_train,-c(outcome_var, fee_arms, prenda, insample))
   Y <- select(data_train,outcome_var)
   W <- as.numeric(data_train$fee_arms == 1)
-
-  ###################################################################  
-  ###################################################################  
-  
-  # Estimation of E[Y | X , W = 1] and E[Y | X , W = 0]
-  X1 = X[W==1,]
-  X0 = X[W==0,]
-  Y1 = as.numeric(unlist(Y[W==1,]))
-  Y0 = as.numeric(unlist(Y[W==0,]))
-  
-  mu.1 = regression_forest(X1,Y1,
-    num.trees = 3000,
-    sample.weights = NULL,
-    clusters = NULL,
-    equalize.cluster.weights = FALSE,
-    sample.fraction = 0.5,
-    mtry = min(ceiling(sqrt(ncol(X)) + 20), ncol(X)),
-    min.node.size = 5,
-    honesty = TRUE,
-    honesty.fraction = 0.5,
-    honesty.prune.leaves = TRUE,
-    alpha = 0.05,
-    imbalance.penalty = 0,
-    ci.group.size = 2,
-    tune.parameters = c("alpha", "imbalance.penalty"),
-    tune.num.trees = 500,
-    tune.num.reps = 200,
-    tune.num.draws = 2000,
-    compute.oob.predictions = TRUE,
-    num.threads = NULL,
-    seed = 1)
-  
-  pr_mu1 = predict(mu.1, data_test, estimate.variance = TRUE)
-  
-  mu.0 = regression_forest(X0,Y0,
-    num.trees = 3000,
-    sample.weights = NULL,
-    clusters = NULL,
-    equalize.cluster.weights = FALSE,
-    sample.fraction = 0.5,
-    mtry = min(ceiling(sqrt(ncol(X)) + 20), ncol(X)),
[…]

### 2023-07-04 RScripts/te_narrow_grf.R

@@ -31,12 +31,14 @@ te_narrow_grf <- function(data_in, outcome_var, name) {
     mutate_all(~ifelse(is.na(.), median(., na.rm = TRUE), .))  
   data_copy <- data_in
   data_in <- rename.vars(data_in, c(
+    "prestamo",
     "edad",
     "genero",
     "pres_antes",
     "masqueprepa"
   ),
   c(
+    "loan.size",
     "age",
     "female",
     "pawn.before",
@@ -82,6 +84,7 @@ te_narrow_grf <- function(data_in, outcome_var, name) {
   # (as the constraint is a monotone increasing function in alpha)
   
   alfa = optimize(fun_threshold_alpha, g, interval=c(0.001, 0.499))$minimum
+  print(alfa)
   
   X <- X[propensity_score>=alfa & propensity_score<=(1-alfa),]
   Y <- Y[propensity_score>=alfa & propensity_score<=(1-alfa),]

### 2023-07-04 RScripts/tot_tut_instr_forest.R

@@ -26,6 +26,7 @@ rename_var = function(df) {
     "dummy_suc4",
     "dummy_suc5",
     "dummy_suc6",
+    "prestamo",
     "edad",
     "faltas",
     "c_trans",
@@ -55,6 +56,7 @@ rename_var = function(df) {
     "branch.4",
     "branch.5",
     "branch.6",
+    "loan.size",
     "age",
     "trouble.paying.bills",
     "transport.cost",

### 2023-07-25 OA.tex
introduce NA in causal RF

@@
 
+\begin{comment}
+
 \begin{table}[H]
@@
 \end{table}
+\end{comment}
+%\todo[inline]{removed}
 
@@
 \begin{table}[H]
-\caption{Baseline survey}
+\caption{Baseline survey questions (translated to English)}
 \label{baseline_survey}
@@
 \end{center}
+\scriptsize
+Translation of the baseline questionnaire.
 \end{table}
@@
 \begin{table}[H]
-\caption{Balance table conditional on survey \& response rates}
+\caption{Balance: Admin data conditional on answering survey \& Survey data conditional a loan}
 \label{SS_cond_survet}
@@
 \end{center}
-
+\scriptsize
+\textcolor{blue}{This table is analogous to Table \ref{SS}, but it uses different sub-samples.
+Panel A reports regression results using administrative loan data, but conditioning on those borrowers who also responded the baseline survey.
+Panel B reports regression results using survey data, but conditioning on those borrowers who pawned \hl{the same day of the survey response}}.
 %\textit{Do file: } \texttt{ss\_att.do}
@@
 
+\todo[inline]{For Isaac to write the note.}
 \end{landscape}
@@
  \scriptsize 
+ \todo[inline]{For Isaac to write the note}
 %\textit{Do file: } \texttt{censoring_imp.do, censoring_imp_pr.do}
@@
 \end{center}
- \scriptsize  This table uses a Linear Probability Model to examine whether randomized treatment assignment on a prior loan taken during the experimental period drives the likelihood of selecting into the commitment product for individuals who go to a branch featuring Choice after the experiment.
+ \scriptsize  \textcolor{blue}{This table explores learning by focusing on a subsample of borrowers in the experiment and observing their subsequent behavior.
+Column 1 conditions the sample on borrowers who (a) pawned during the experiment a subsequent time after being assigned to control, forced commitment or choice (the regressors), and (b) when pawning again they went to a branch day when (randomly) choice was available, thus enabling us to observe if they chose the commitment contract or the status quo.
+in this sample it estimates a linear probability model where the dependent variable is equal to one if the borrower chose the commitment contract in that subsequent `choice' occasion and zero otherwise.
+The regressors are indicators for the treatment arms in their first pawn in the experiment.
+Column 1 conditions the sample on the (endogenous) event of pawning again.
+Column 2 does not condition the sample, but instead defined the dependent variable as equal to one \hl{if the borrower pawned subsequently and choice was available that day and chose commitment, and zero otherwise.}}
 \end{table}
@@
     \end{center}
-     \scriptsize This Figure estimates the treatment effect on financial cost for the untreated with different discount rates.  
+     \scriptsize This Figure estimates regression equation \ref{basic_reg} as in column 1 of Table \ref{main_impact_table} but it introduces a daily discount factor (time preference) in the definition of financial cost to discount payments.
+Payments done in the present are more costly for the borrower.
+It estimates the effect of the treatment arms  for different discount factors, where a discount factor of 1 corresponds exactly to the estimate of column 1 of Table \ref{main_impact_table}.
+Because the commitment contract induces earlier payments, this adjusted financial cost will be higher, and thus financial savings will be lower.
+This figure shows the range of estimated effects and their confidence intervals, where the discount rate used is ploted in the x-axis annualized.
 %\textit{Do file: }  \texttt{discounted\_noeffect.do}
@@
       %\footnotesize{ \textit{Do file: }  \texttt{partition_tot_tut.do}
+
+      \todo[inline]{This figure will change}
 \end{figure}
@@
 \vspace{.3in}
-\subsection{Risk aversion and first order stochastic dominance} \label{App_FOSD}
+\subsection{First order stochastic dominance} \label{App_FOSD}
 \normalsize
 \vspace{.2in}
-We do not have measures of risk aversion in our short survey, which makes it hard to assess the hypothesis that risk aversion limits take-up of the fee frequent payment contract.
-One way to proceed is to take the empirical distribution of financing cost ---$F_{fee}(FC)$--- as one the client would have faced had she chosen the status quo contract.
-We could then ask what would risk aversion have to be in order to justify the client choosing the fee-commitment contract distribution of costs over the distribution associated with the status quo contract, $F_{sq}(FC)$.
-Framed as a choice among cost distributions, we can calculate what risk aversion is needed to rationalize the overwhelming choice of the status quo contract over the fee-commitment contract.
-This exercise of course assumes --as is common in economics-- that clients know the distribution of financial cost, that the distribution is common across consumers (although this can be relaxed), and that this cost distribution is the only difference among contracts.
-
-Fortunately for us, it turns out that one distribution first-order-stochastically dominates the other, obviating the need to calibrate a specific utility function or use a parametric distribution function in order to rank them in terms of expected utility.
-We use the fact that if the utility $u(FC)$ is decreasing in $FC$ (i.e.
-clients dislike paying higher financing cost) and $F_{fee}(FC) \geq F_{sq}(FC)$ for all $FC$, which we actually verify in our data, then $E_{fee}[u(FC)] \geq E_{sq}[u(FC)]$, that is any expected utility maximizing client risk averse consumer should choose the Forced Commitment contract as a result of the distribution of cost payoffs.\footnote{Figure \ref{ecdf_fc} shows that indeed $F_{fee}(FC) \geq F_{sq}(FC)$.
-Table \ref{stochastic_dominance} shows that this holds also for sub-populations of different characteristics.}.
-Thus, risk aversion cannot explain the low demand for commitment under the assumptions of this exercise.
+\todo[inline]{Presumably we want to cut some of this text? In the body of the text we don't get into this in such detail.}
+%We plot the empirical distribution of financing cost $F_{commitment}(FC)$ and of the status quo contract, $F_{sq}(FC)$. Framed as a choice among cost distributions.
 
@@
 \begin{figure}[H]
-        \caption{Empirical CDF of Financial Cost: Forced commitment vs Control }
+        \caption{Empirical CDF of Financial Cost: Forced commitment vs Control}
     \label{ecdf_fc}
@@
 The dotted line at the bottom is the difference of the control CDF minus the forced CDF arm.
-It shows that the CDF of the status quo contract is always below that of the fee-forcing (and this difference is significant for the points indicated by the blue line), and therefore that the former first-order stochastically dominates the later for weakly decreasing utility functions; see Proposition \ref{eq_fosd}.
+It shows that the CDF of the status quo contract is always below that of the fee-forcing (and this difference is significant for the points indicated by the blue line).
     % \texttt{fosd_ecdf.do}}
 \end{figure}
+
+\begin{comment}
 
@@
 
+\end{comment}
+
 \newpage
@@
 \label{append:chernozhukov}
-Our approach relies on the following simple observation: if $\Delta_i$ is constant across $i$ then we must have 
+Our approach relies on the following simple observation: if $\Delta_i$ is constant across $i$, then 
 \[
@@
 \begin{prop} 
+\label{prop:TOTreg}
 Under Assumption \ref{assump:randchoice},
@@
 where $\mathbb{E}(U|Z) = 0$.
-Therefore, under standard regularity conditions, an IV regression of $Y$ on an intercept, $Z_1$ and $Z_2 D$ with instruments $(1, Z_1, Z_2)$ provides a consistent estimator of the ATE and TOT effects.
+Therefore, under standard regularity conditions, an IV regression of $Y$ on an intercept, $Z_1$ and $Z_2 D$ with instruments $(1, Z_0, Z_1)$ provides a consistent estimator of the ATE and TOT effects.
 \end{prop}
@@
 \begin{prop}
+\label{prop:TUTreg}
 Under Assumption \ref{assump:randchoice}
@@
 where $\mathbb{E}(V|Z) = 0$.
-Therefore, under standard regularity conditions, an IV regression of $Y$ on an intercept, $-Z_0$ and $-Z_2(1-D)$ with instruments $(1, Z_0, Z_2)$ provides consistent estimates of the ATE and TUT effects.
+Therefore, under standard regularity conditions, an IV regression of $Y$ on an intercept, $-Z_0$ and $-Z_2(1-D)$ with instruments $(1, Z_0, Z_1)$ provides consistent estimates of the ATE and TUT effects.
 \end{prop}
@@
 \begin{prop}
+\label{prop:ASBreg}
 Under Assumption \ref{assump:randchoice}
@@
 \begin{prop}
+\label{prop:ASLreg}
 Under Assumption \ref{assump:randchoice},
@@
 
-\todo[inline]{Update below here}
-
 \subsection{Inference for ASG, ASB, and ASL}
 We now explain how to carry out cluster-robust inference for the ASG, ASB, and ASL effects, as implemented in our companion STATA package.
-
-For purposes of inference, both the ASB and ASL can be re-written as the difference of coefficients from a pair of just-identified linear IV regressions, namely
-
-As in the case of the ASG, inference for the ASB and ASL can be carried out by saving the residuals from \eqref{eq:ASB0}--\eqref{eq:ASL1}.
-
-\todo[inline]{Add something about the TUT decomposition and covariates? Probably just a few sentences at most.}
-
-%\begin{proof}
-%For part (iii), note that 
-%\[
-%\mathbbm{E}(Y|Z=0) = \mathbbm{E}(Y_0) = \mathbbm{E}(Y_0|C=0) \mathbbm{P}(C=0) + \mathbbm{E}(Y_0|C=1) \mathbbm{P}(C=1)
-%\]
-%by Lemma \ref{lem_randchoice}(ii) and iterated expectations.
-%Re-arranging, 
-%\[
-%\mathbbm{E}(Y_0|C=1) = \frac{\mathbbm{E}(Y|Z=0) - \mathbbm{E}(Y_0|C=0) \mathbbm{P}(C=0)}{\mathbbm{P}(C=1)}.
-%\]
-%Therefore, by Lemma \ref{lem_randchoice} (i) and (iv)
-%\begin{align*}
-%\mathbbm{E}(Y_0|C=1) - \mathbbm{E}(Y_0|C=0) &= \frac{\mathbbm{E}(Y|Z=0) - \mathbbm{E}(Y|Z=2,D=0) \mathbbm{E}(1 - D|Z=2)}{\mathbbm{E}(D|Z=2)} - \mathbbm{E}(Y|Z=2, D=0)\\
-%&= \frac{\mathbbm{E}(Y|Z=0) - \mathbbm{E}(Y|Z=2,D=0)}{\mathbbm{E}(D|Z=2)}.
-%\end{align*}
-%
-%Similarly, for part (iv) note that
-%\[
-%\mathbbm{E}(Y|Z=1) = \mathbbm{E}(Y_1) = \mathbbm{E}(Y_1|C=0)\mathbbm{P}(C=0) + \mathbbm{E}(Y_1|C=1) \mathbbm{P}(C=1)
-%\]
-%by Lemma \ref{lem_randchoice}(iii) and iterated expectations.
-%Rearranging,
-%\[
-%\mathbbm{E}(Y_1|C=0) = \frac{\mathbbm{E}(Y|Z=1) - \mathbbm{E}(Y_1|C=1)\mathbbm{P}(C=1)}{\mathbb{P}(C=0)}.
-%\]
-%Therefore, by Lemma \ref{lem_randchoice} (i) and (v),
-%\begin{align*}
-%\mathbbm{E}(Y_1|C=1) - \mathbbm{E}(Y_1|C=0) &= \mathbbm{E}(Y|Z=2, D=1) - \frac{\mathbbm{E}(Y|Z=1) - \mathbbm{E}(Y|Z=2, D=1)\mathbbm{E}(D|Z=2)}{\mathbb{P}(C=0)} \\
-%&= \frac{\mathbbm{E}(Y|Z=2,D=1) - \mathbbm{E}(Y|Z=1)}{1 - \mathbbm{E}(D|Z=2)}.
-%\end{align*}
-%\end{proof}
-
-\newpage
+Each of these effects can be expressed as a difference of coefficients from two just-identified linear IV regressions.
+The ASG effect is the difference of the \text{TOT} effect from Proposition \ref{prop:TOTreg} and the \text{TUT} effect from Proposition \ref{prop:TUTreg}.
+Similarly, the ASB effect is the difference of $\mathbb{E}(Y_0|C=1)$ and $\mathbbm{E}(Y_0|C=0)$ from Proposition \ref{prop:ASBreg} while the ASL effect is the difference of $\mathbbm{E}(Y_1|C=1)$ and $\mathbbm{E}(Y_1|C=0)$ from Proposition \ref{prop:ASLreg}.
+Within each pair of IV regressions the outcome variable and instrument set is identical; only the regressors differ. 
+Since our estimators of all three effects share the same structure, our discussion of inference abstracts from the specific regressors and instruments used in each case to avoid duplication. 
+To implement these results in practice without relying on our STATA package, simply substitute supply the regressors and instruments specified in the relevant propositions.
+
+Let $g = 1, ..., G$ index clusters and $i = 1, ..., N_g$ index individuals within a particular cluster $g$. 
+In our experiment, a cluster is a branch-day combination and the experimentally-assigned treatment (control, forced, or choice arm) is assigned at the cluster level.
+We assume that observations are iid across clusters but potentially correlated within cluster.
+Now consider a pair of just-identified linear IV regressions given by
+\begin{align*}
+Y_{ig} &= \boldsymbol{X}_{1,ig}' \boldsymbol{\theta}_0 + U_{ig} \\
+Y_{ig} &= \boldsymbol{X}_{0,ig}' \boldsymbol{\theta}_1 + V_{ig}
+\end{align*}
+with common instrument vector $\boldsymbol{W}_{ig}$. 
+Stacking observations in the usual manner, e.g.\
+\[
+\mathbf{W}_g \equiv \begin{bmatrix}
+\boldsymbol{W}_{1g}' \\
+\vdots \\
+\boldsymbol{W}_{N_gg}' \\
+\end{bmatrix}, \quad
+\mathbf{W} = \begin{bmatrix}
+\mathbf{W}_1\\ \vdots \\ \mathbf{W}_G
+\end{bmatrix},
+\]
+we can write the preceding equations in matrix form as
+\begin{align*}
+\mathbf{Y} &= \mathbf{X}_1\boldsymbol{\theta_1} + \mathbf{U}\\
+\mathbf{Y} &= \mathbf{X}_0\boldsymbol{\theta_0} + \mathbf{V}
+\end{align*}
+with instrument matrix $\mathbf{W}$.
+Now, the IV estimators for $\boldsymbol{\theta}_1$ and $\boldsymbol{\theta}_0$ can be expressed as 
+\begin{align*}
+\widehat{\boldsymbol{\theta}}_1 
+&= \left(\mathbf{W}'\mathbf{X}_1\right)^{-1}\mathbf{W}'\mathbf{Y}  = \boldsymbol{\theta}_1 + \left(\mathbf{W}'\mathbf{X}_1\right)^{-1}\mathbf{W}'\mathbf{U}\\ 
+\widehat{\boldsymbol{\theta}}_0 
+&= \left(\mathbf{W}'\mathbf{X}_0\right)^{-1}\mathbf{W}'\mathbf{Y} = \boldsymbol{\theta}_0 + \left(\mathbf{W}'\mathbf{X}_0\right)^{-1}\mathbf{W}'\mathbf{V}.
+\end{align*}
+Our parameter of interest is an element of the difference $(\theta_1 - \theta_0)$, so  it suffices to calculate the asymptotic distribution of $(\widehat{\boldsymbol{\theta}}_1 - \widehat{\boldsymbol{\theta}}_0)$.
+
+Re-arranging the preceding two equations, we have
+\begin{align*}
+\sqrt{G} \left(\widehat{\boldsymbol{\theta}}_1  - \boldsymbol{\theta}_1\right) &= 
+ \left(\frac{\mathbf{W}'\mathbf{X}_1}{G}\right)^{-1}\left(\frac{\mathbf{W}'\mathbf{U}}{\sqrt{G}}\right) = \left( \frac{1}{G} \sum_{g=1}^G \mathbf{W}_g' \mathbf{X}_{1,g}\right)^{-1}\left(\frac{1}{\sqrt{G}} \sum_{g=1}^G\mathbf{W}_g' \mathbf{U}_g\right) \\
+\sqrt{G} \left(\widehat{\boldsymbol{\theta}}_0  - \boldsymbol{\theta}_0\right) &= 
+ \left(\frac{\mathbf{W}'\mathbf{X}_0}{G}\right)^{-1}\left(\frac{\mathbf{W}'\mathbf{V}}{\sqrt{G}}\right) = \left( \frac{1}{G} \sum_{g=1}^G \mathbf{W}_g' \mathbf{X}_{0,g}\right)^{-1}\left(\frac{1}{\sqrt{G}} \sum_{g=1}^G\mathbf{W}_g' \mathbf{V}_g\right).
+\end{align*}
+Now, define $\mathbf{Q}_0 \equiv \mathbb{E}[\mathbf{W}_g'\mathbf{X}_{0g}]$ and $\mathbf{Q}_1 \equiv \mathbb{E}[\mathbf{W}_g'\mathbf{X}_{1g}]$ and suppose that these expectations exist and that the matrices $\mathbf{Q}_0$ and $\mathbf{Q}_1$ are invertible.
+Then, as $G \rightarrow \infty$
+\[
+ \left( \frac{1}{G} \sum_{g=1}^G \mathbf{W}_g' \mathbf{X}_{0,g}\right)^{-1} \rightarrow_p \mathbf{Q}_0^{-1}, \quad
+ \left( \frac{1}{G} \sum_{g=1}^G \mathbf{W}_g' \mathbf{X}_{1,g}\right)^{-1} \rightarrow_p \mathbf{Q}_1^{-1} \quad
+\]
+by the continuous mapping theorem.
+Now, by our experimental design and exclusion restriction, $\mathbf{W}_{ig}$ is independent of $U_{ig}$ both unconditionally and conditional on cluster size. 
+Therefore,
+\begin{align*}
+\mathbb{E}[\mathbf{W}_g' \mathbf{U}_g] &=  \mathbb{E}\left[ \sum_{i=1}^{N_g} \mathbf{W}_{ig} U_{ig} \right] = \mathbb{E}_{N_g}\left[ \mathbb{E}\left\{\left.
+\sum_{i=1}^{N_g} \mathbf{W}_{ig} U_{ig} \right| N_g \right\}\right]\\
+&= \mathbb{E}_{N_g}\left[ \sum_{i=1}^{N_g} \mathbb{E}(\mathbf{W}_{ig} U_{ig}|N_g)\right] = \mathbb{E}_{N_g}\left[ \sum_{i=1}^{N_g} \mathbb{E}(\mathbf{W}_{ig}U_{ig})\right] = 0
+\end{align*}
+by iterated expectations, and similarly smilarly, $\mathbb{E}[\mathbf{W}_g'\mathbf{V}_g] = \mathbf{0}$. 
+Thus, under mild regularity conditions (e.g.\ finite fourth moments), as $G \rightarrow \infty$  we have
+\[
+\frac{1}{\sqrt{G}} \sum_{g=1}^G \mathbf{W}_g' \otimes \begin{bmatrix} \mathbf{U}_g \\ \mathbf{V}_g \end{bmatrix} \rightarrow_d \text{N}(\mathbf{0}, \boldsymbol{\Omega})
+\]
+where the heteroskedasticity-- and cluster--robust variance-covariance matrix $\boldsymbol{\Omega}$ is defined as
+\[
+\boldsymbol{\Omega} \equiv 
+ \mathbb{E} \left[\left(\mathbf{W}_g \mathbf{W}_g' \right)\otimes \begin{pmatrix}
+\mathbf{U}_g \mathbf{U}_g' & \mathbf{U}_g \mathbf{V}_g' \\
+\mathbf{V}_g \mathbf{U}_g' & \mathbf{V}_g \mathbf{V}_g'  
+\end{pmatrix} \right] \equiv \begin{bmatrix}
+\Omega_{UU} & \Omega_{UV} \\
+\Omega_{VU} & \Omega_{VV}
+\end{bmatrix}.
+\]
+Therefore, the joint limiting distribution of $\widehat{\boldsymbol{\theta}}_1$ and $\widehat{\boldsymbol{\theta}}_0$ is given by
+\[
+\begin{bmatrix}
+\sqrt{G}(\widehat{\boldsymbol{\theta}}_1 - \boldsymbol{\theta}_1)\\
+\sqrt{G}(\widehat{\boldsymbol{\theta}}_0 - \boldsymbol{\theta}_0)
+\end{bmatrix} \rightarrow_d
+\begin{bmatrix}
+\mathbf{Q}_1^{-1} & \mathbf{0} \\
+\mathbf{0} & \mathbf{Q}_0^{-1} 
+\end{bmatrix}
+\begin{bmatrix}
+\boldsymbol{\xi}_U \\ \boldsymbol{\xi}_V 
+\end{bmatrix}, \quad
+\begin{bmatrix}
+\boldsymbol{\xi}_U \\ \boldsymbol{\xi}_V 
+\end{bmatrix} \sim \text{N}\left(\begin{bmatrix} \mathbf{0} \\ \mathbf{0}\end{bmatrix},
+\begin{bmatrix}
+\Omega_{UU} & \Omega_{UV} \\
+\Omega_{VU} & \Omega_{VV}
+\end{bmatrix}\right)
+\]
+from which it follows by the continuous mapping theorem that
+\[
+\sqrt{G}\left[ (\widehat{\boldsymbol{\theta}}_1 - \widehat{\boldsymbol{\theta}}_0 ) - (\boldsymbol{\theta}_1 - \boldsymbol{\theta}_0)\right] 
+\rightarrow_d
+\begin{bmatrix}
+\mathbf{Q}_1^{-1} & -\mathbf{Q}_0^{-1}
+\end{bmatrix}
+\begin{bmatrix}
+\boldsymbol{\xi}_U \\ \boldsymbol{\xi}_V 
+\end{bmatrix}.
+\]
+To use this result in practice, we estimate the standard errors of  $(\widehat{\boldsymbol{\theta}}_1 - \widehat{\boldsymbol{\theta}}_0)$ as the square root of the diagonal elements of the matrix
+\[
+\widehat{\text{Avar}}(\widehat{\boldsymbol{\theta}}_1 - \widehat{\boldsymbol{\theta}}_0) 
+= \begin{bmatrix}
+\left(\mathbf{W}'\mathbf{X}_1\right)^{-1} &
+-\left(\mathbf{W}'\mathbf{X}_0\right)^{-1} 
+\end{bmatrix}
+\begin{bmatrix}
+\mathbf{S}_{UU}& \mathbf{S}_{UV}\\
+\mathbf{S}_{VU}& \mathbf{S}_{VV}
+\end{bmatrix} 
+\begin{bmatrix}
+\left(\mathbf{X}_1'\mathbf{W}\right)^{-1} \\
+-\left(\mathbf{X}_0'\mathbf{W}\right)^{-1} 
+\end{bmatrix}
+\]
+where
+\begin{align*}
+\mathbf{S}_{UU} &\equiv \sum_{g=1}^G \mathbf{W}_g' \widehat{\mathbf{U}}_g \widehat{\mathbf{U}}_g' \mathbf{W}_g\\
+\mathbf{S}_{UV} &\equiv \sum_{g=1}^G \mathbf{W}_g' \widehat{\mathbf{U}}_g \widehat{\mathbf{V}}_g' \mathbf{W}_g\\
+\mathbf{S}_{VU} &\equiv \mathbf{S}_{UV}'\\
+\mathbf{S}_{VV} &\equiv \sum_{g=1}^G \mathbf{W}_g' \widehat{\mathbf{V}}_g \widehat{\mathbf{V}}_g' \mathbf{W}_g
+\end{align*}
+and we define the IV residuals
+\begin{align*}
+\widehat{\mathbf{U}}_g &\equiv \mathbf{Y}_g - \mathbf{X}_{1,g}\widehat{\boldsymbol{\theta}}_1\\
+\widehat{\mathbf{V}}_g &\equiv \mathbf{Y}_g - \mathbf{X}_{0,g}\widehat{\boldsymbol{\theta}}_0.
+\end{align*}
+In our application the number of clusters, $G$, is large.
+If desired, an \emph{ad hoc} degrees of freedom correction can be applied by multiplying the standard errors by $\sqrt{G/(G-1)}$.
 
@@
 
+\begin{comment}
+
 \begin{figure}[H]
@@
 \section{Causal Random Forest, HTE, and `mistakes'}
-
-\vspace{.3in}
 
@@
 \end{figure}
+
+\todo[inline]{Some subfigures are not loading}
 
@@
 \vspace{.4in}
+
+\begin{comment}
+
 \subsection{Take up}
@@
 
+\end{comment}
+
 \subsection{Selection on gains}
@@
     \begin{center}
-    \begin{subfigure}{0.475\textwidth}
+    \begin{subfigure}{0.65\textwidth}
         \caption{Determinants of HTE}
@@
     \end{subfigure}
-    \begin{subfigure}{0.475\textwidth}
-        \caption{Determinants of propensity score}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/HE/ps_int_vertical_pr_gbc_1.pdf}
-    \end{subfigure}
-
-    \end{center}
-     \scriptsize   This figure estimates bivariate regressions of the estimated client-level (a) heterogeneous treatment effects, (b) propensity score, against the respective covariate from the baseline survey  $\widehat{HTE_i}, \widehat{P_i} = \alpha + \beta \: X_i + \epsilon_i$.
+    %\begin{subfigure}{0.475\textwidth}
+    %    \caption{Determinants of propensity score}
+    %    \centering
+    %    \includegraphics[width=\textwidth]{Figuras/HE/ps_int_vertical_pr_gbc_1.pdf}
+    %\end{subfigure}
+
+    \end{center}
+     \scriptsize   This figure estimates bivariate regressions of the estimated client-level (a) heterogeneous treatment effects, %(b) propensity score, against the respective covariate from the baseline survey  $\widehat{HTE_i}, \widehat{P_i} = \alpha + \beta \: X_i + \epsilon_i$.
 The regressors $X_i$ include (e.g if the family asks for money, if they have savings, if they are overconfident using the definition the text, etc.
@@
 \end{figure}
+\todo[inline]{@Isaac: reestimate this with the determinants we are using for the choice determinants. Based on that we decide if we cut}
 

### 2023-07-25 donde.tex
introduce NA in causal RF

@@
 Finally, and most uniquely given the presence of a forced commitment arm, we are able to ask whether the \textit{right} borrowers voluntarily demand commitment.
-In particular, we use the choice, control, and fored arms to point identify the Treatment on the Treated (TOT) and the Treatment on the Untreated (TUT) effects, along with the average selection on gains (ASG) and average selection bias (ASB).
+In particular, we use the choice, control, and forced arms to point identify the Treatment on the Treated (TOT) and the Treatment on the Untreated (TUT) effects, along with the average selection on gains (ASG) and average selection bias (ASB).
 
@@
 The top row of Table \ref{attrition_table} shows that the survey response rate is broadly similar across arms (about 77 percent).
-We can also examine differences in the fraction of borrowers who do respond to the survey and then do not end up taking a loan subsequent to completing the survey, we find that the share is close to as is the fraction of those 97\% across arms (p-value=\hl{XXX}).\footnote{We also tested if the number of pawns per day for the 6 branches that participated in the experiment was different 1 month before the experiment started or 1 month after the experiment ended, relative to the days the experiment was active.
-To this end we estimated the regression\footnote{We cluster the standard errors by branch.} $Pawns \: per \: day_{jt} = \alpha_j + \gamma f(t) + \beta_b \mathbbm{1}(t \in MB)_{t} +\beta_a \mathbbm{1}(t \in MA)_{t}$, where $\alpha_j$ are branch fixed effects, $f(t)$ is a third degree polynomial in time, $\beta_b$ measures a level effect in the number of pawns per branch a month before the experiment started, and $\beta_a$ a month after.
+We can also examine differences in the fraction of borrowers who do respond to the survey and then do not end up taking a loan subsequent to completing the survey, we find that the share is close to as is the fraction of those 97\% across arms (p-value=\hl{XXX}).%\footnote{We also tested if the number of pawns per day for the 6 branches that participated in the experiment was different 1 month before the experiment started or 1 month after the experiment ended, relative to the days the experiment was active.
+To this end we estimated the regression.
+We cluster the standard errors by branch.} $Pawns \: per \: day_{jt} = \alpha_j + \gamma f(t) + \beta_b \mathbbm{1}(t \in MB)_{t} +\beta_a \mathbbm{1}(t \in MA)_{t}$, where $\alpha_j$ are branch fixed effects, $f(t)$ is a third degree polynomial in time, $\beta_b$ measures a level effect in the number of pawns per branch a month before the experiment started, and $\beta_a$ a month after.
 We estimate no difference in the number of pawns, showing that people are not leaving the branch without pawning at larger rates during the experiment ($\beta_a=1.32$, $\beta_b=-0.65$, with p-values 0.11 and 0.83, respectively).
@@
 
-\todo[inline]{Add a column with losing pawn. What about re-pawning?}
-\todo[inline]{How did we decide to deal with censoring?}
-
 \paragraph{Results.} The results are stark.
@@
 Although the paper focuses on financial cost, we consider three additional costs here.
-First, We include the cost of going to the branch.
+First, we include the cost of going to the branch.
 This includes the self-reported transport cost (most use public transport), as well as the opportunity cost of time.
@@
 
+\todo[inline]{@Isaac, from Enrique: I would like to understand the liquidity adjustment better.}
+
 Table \ref{table_robustness_fc} shows results.
@@
 Forced commitment lowers financial costs even when we incorporate multiple subjective dimensions of the loan.
-
-\todo[inline]{I think the re-pawn table should only have 4 columns.
-Remove variables 3,4, and 7.
-In terms of the order: keep column 1, make 5 and 6  the new columns 2 and 3, and make the current column 2 the new column 4.
-I am goint to write the paragraphs assuming this.}
 
@@
 If the effect of commitment were homogeneous, this would be enough to conclude that the \hl{89\%} who did not choose it would have been financially better-off if they had.
-In a world of heterogeneous treatment effects, however, low demand for commitment could still be consistent with \textcolor{blue}{standard rational borrowers.}
+In a world of heterogeneous treatment effects, however, low demand for commitment could still be consistent with borrowers adhering to a standard model of rational choice. 
 The borrowers who did not choose commitment could simply be those who don't need it. 
-Indeed, we find strong evidence that the effect of forced commitment varies substantially across individuals in our experiment: Appendix \ref{append:chernozhukov} tests and rejects the null hypothesis of homogeneous treatment effects, following the methodology of \cite{chernozhukov2018generic}.
+Indeed, we find strong evidence that the effect of forced commitment varies substantially across individuals in our experiment: \ref{append:chernozhukov} tests and rejects the null hypothesis of homogeneous treatment effects, following the methodology of \cite{chernozhukov2018generic}.
 So the question remains: do the \hl{89\%} who do not choose commitment know something about their personal situations that we as researchers do not, or are most people in the choice arm making a costly mistake?
-In this section we present a number of econometric exercises that shed light on this question, leveraging unique features of our experimental design. 
-Despite substantial treatment effect heterogeneity, most borrowers would experience lower financial costs under a commitment contract. 
-Indeed, commitment lowers average financial costs even for the subset of borrowers who would \emph{not} choose to commit voluntarily.
+In this section we present of econometric exercises that shed light on this question, leveraging unique features of our experimental design. 
+Among other results, we show that commitment lowers average financial costs even for the subset of borrowers who would \emph{not} choose to commit voluntarily.
 To simplify the exposition in this and all sections that follow, we re-define all outcome variables so that \emph{beneficial} treatment effects are \emph{positive}.
@@
 \label{sec:bounds}
-
 If we knew the distribution of individual treatment effects, it would be easy assess how many individuals would win and lose under a policy of universal forced commitment, along with the magnitude of any individual harm.
@@
 \todo[inline]{@Isaac: Need a sentence saying what the results are: at least such and such percent benefit from forced commitment}
+
+The bounds we have just described are constructed by considering all possible joint distributions of $Y_0$ and $Y_1$ that are compatible with the observed marginal distributions $F_1$ and $F_0$. 
+With stronger assumptions, it is possible to say more.
+One such assumption is \emph{rank invariance}, which posits that a person's rank in the distribution of $Y_0$ equals her rank in the distribution of $Y_1$.
+While strong, this assumption or variants of it has appeared in a number of settings in the literature, e.g.\ \cite{chernozhukov2005iv}. 
+Under rank invariance, the distribution of treatment effects is point identified and given by 
+\[
+F_\Delta(\delta) = \int_0^1 \mathbbm{1}\{ F_1^{-1}(u) - F_0^{-1}(u)\leq \delta\}\,\mathrm{d}u 
+\]
+where $F_1^{-1}$ and $F_0^{-1}$ are the quantile functions of $Y_1$ and $Y_0$.
+As we show in Appendix \ref{App_FOSD}, $Y_1$ first-order stochastically dominates $Y_0$ in our experiment: every quantile of the distribution of financial cost savings under forced commitment is higher than the corresponding quantile under the control condition, and the same is true for the APR outcome.
+Since this implies that $F^{-1}_1(u) - F^{-1}_0(u)$ is always positive, rank invariance yields an extremely stark conclusion: all borrowers benefit from forced commitment. 
+\todo[inline]{@Everyone: do we want to plot the distribution of treatment effects under rank invariance and say something more about it? Or just add a snappy sentence to conclude this subsection?}
 
@@
 
-\section{Examining paternalism}
+\section{The Case for Paternalism}
 \label{exploring}
 
-\subsection{Why is paternalism working in this context?}
+\subsection{Why does paternalism work in this context?}
 \label{why_paternalism}
@@
 
-\paragraph{Learning.} A first explanation involves learning.
+\paragraph{Learning.} A first potential explanation involves learning.
 Our experiment introduced a new contract into an environment that had not previously featured commitment; perhaps clients required experience to understand its benefits.
 Given the strongly positive impact of forcing, this explanation would suggest that clients who were forced once would subsequently choose commitment if given the chance to do so.
-A subset of \hl{240 clients} from our experiment who were exposed to the experiment in one round and then returned to take another loan at a branch where the choice of commitment was offered.
+A subset of \hl{XXXX} clients from our sample returned to pawn again on another day before the end of the experiment.
+Whereas all of the analyses from above restrict attention to the first day on which a given individual pawned, Table \ref{learning_table} presents information about participants' \emph{subsequent} pawning behavior.
+Column (1) considers the 228 clients who returned to pawn again at a day/branch that was randomly assigned to the choice arm.
+Each of the two rows in this column presents a difference of mean commitment take-up rates, and associated standard error.
+The first row compares those who were \emph{initially} assigned to forced commitment against those where were assigned to control; the second row compares those who were initially assigned to the choice commitment arm to those who were assigned to the other two arms.
+In each case, there is no statistically discernible difference in the rates of commitment take-up.
+Granted, this is a selected sample because the decision to pawn again is potentially endogenous to the initial treatment allocation.
+For this reason, Column (2) considers the full sample of \hl{4436} by re-defining the ``outcome variable'' to be an indicator for returning to pawn again at a branch/day when commitment was offered \emph{and} choosing commitment.
+This composite outcome variable is not subject to the sample selection problem.
+The comparison in the two rows remains the same: forced commitment versus control in row one and choice commitment versus forced arms in row two.
+Again, there is no statistically discernible difference in commitment take-up rates in either row.
+While these exercises cannot completely exclude the possibility that learning plays a role, the provide no indication that the lack of voluntary compliance is simply a matter of inexperience with commitment.
+
+%a subset of 228 clients from our experiment who were exposed to the experiment in one round and then returned to take another loan at a branch where the choice of commitment was offered.
 Table \ref{learning_table} shows the results of this analysis.
-While this regression is underpowered, given the small sample size, the point estimate on prior assignment to the commitment contract is actually negative.
-Hence the window available to us on learning provides little comfort that the lack of voluntary compliance is simply a matter of inexperience with commitment.\footnote{\textcolor{blue}{Risk could be another alternative potential explanation for low take up of the commitment contract.
-Appendix \ref{App_FOSD} shows however that the distribution of financial cost savings of the monthly payment contract first-order stochastically dominates that of the status quo contract, so that (assuming these are the distributions faced by borrowers) the former should be preferred by borrowers regardless of their degree of risk aversion.
-See the Appendix for more details.}}
+The first column uses only the (endogenous) sample that took multiple loans, and the second column uses the whole experimental sample and defines the outcome as ``returned and chose commitment''.
+While the first column is under-powered, the point estimate is actually negative.
+The estimate in the second column is pushed upwards by the positive effect of Forcing on repeat borrowing shown in Table \ref{repeat_loans}, and yet the estimate here is very close to zero.
+Hence the window available to us on learning provides little comfort that the lack of voluntary compliance is simply a matter of inexperience with commitment.
+
+%Some people self-select into returning for another loan (endogenous).
+The people who return are randomized into the same three arms as before.
+Note that we have *not* used their second visits in any other data analysis so far, so this new data.
+For the self-selected sub-sample, we estimate the difference in commitment take-up across people who were initially assigned to forced commitment versus control: first row and first column.
+This is zero.
+The second row in the first column restricts attention to people who were initially assigned to either the choice or control arms, endogenously returned, and were exogenously assigned to choice a second time.
+We compare the commitment take-up rates the second time around across people who were initially assigned to choice versus those who were initially assigned to the status quo
+
+%Second column defines an outcome that equals one if and only if you *both* return *and* choose commitment the second time around.
+(Note that this requires you to have been randomly assigned to choice the second time.) The first row compares people who were assigned at random to commitment the first time around against those who were assigned to control.
+The second row compares those who were offered a choice the first time around to those who were forced into the status quo contract
 
@@
 Highly impatient individuals might therefore rationally choose the \emph{status quo} contract, despite our results showing a benefit raw (undiscounted) returns.
-To investigate this explanationwe can calculate the Net Present Value of the $TUT$ on financial cost given the timing of repayment and pawn recovery for different hypothetical discount rates.
+To investigate this explanation we can calculate the net present value (NPV) of the financial cost $\text{TUT}$ effect under different hypothetical discount rates, given the timing of repayment and pawn recovery.
 Figure \ref{fc_discount_rates} presents the results of this exercise.
@@
 
-\paragraph{Present bias.} If commitment benefits among non-choosers cannot be explained by rational choice, the canonical behavioral story would center on time inconsistency.
+\paragraph{Survey Data.}
+The remaining exercises in the paper require information from the intake survey, and hence use only the subset of individuals who responded to the survey. 
+Table \label{SS_cond_survet} presents information about survey non-response.
+Panel A is a balance table that compares loan amount and day of the week across treatment arms for the subset of borrowers who responded to \hl{at least one survey question}.
+The p-values in the fourth column are for the F-test of no difference of means across teratment arms. 
+Panel B presents response-rates by question for each arm of the experiment, along with p-values for the F-test of no difference in question-specific response rate across treatment arms. 
+While this is a selected sample, estimates of the ATE, TOT, and TUT are nearly identical whether computed from the full sample survey-respondent sub-sample.
+In exercises that rely on one survey question, we use the full sample of borrowers who answered that question.
+In the random forest exercises that follow, we use data for every borrower who answered at least one survey question.
+
+%\todo[inline]{@Issac: do we have a table of TOT/TUT/ATE results for the sub-sample of survey respondents?
+We should add this as Table OA-2.
+What should we take as our sub-sample?
+We'd like to have this for people who answered \emph{at least} one survey question since those are the people who appear in our random forest exercises.
+We'd also like to have it for people who answered the time inconsistency question, and for people who answered the sure confidence question.
+(Each as a separate number)}
+
+\paragraph{Present bias.} If the benefits of commitment among non-choosers cannot be explained by standard models of rational choice, the canonical behavioral story would center on time inconsistency.
 While commitment is useful to anyone with hyperbolic time preferences, only those who are sophisticated--i.e.\ aware that they are hyperbolic discounters--will demand it.
-A large share of naive hyperbolics in the population could therefore drive a large and positive $\text{TUT}$.
+A large share of ``na\"ive'' hyperbolics in the population--borrowers who are unaware that they are hyperbolic discounters--could therefore drive a large and positive $\text{TUT}$.
 Our baseline survey included standard questions about discount rates between today and a month in the future versus discount rates between three and four months in the future.\footnote{The remaining exercises in the paper require information from the intake survey, and hence use only the subset of individuals who responded to the survey.
@@
 
-If we could perfectly measure hyperbolicity, we could divide the sample into three groups: sophisticated hyperbolics who chose commitment, time-consistent non-chooser for whom forcing will not be effective, and naive hyperbolic non-choosers for whom it will.
+If we could perfectly measure hyperbolicity, we could divide the sample into three groups: sophisticated hyperbolics who chose commitment, time-consistent non-choosers for whom forcing will not be effective, and naive hyperbolic non-choosers for whom it will.
 If hyperbolic discounting fully explains the low take-up rate of voluntary commitment, this would imply that the forcing effect should arise entirely from hyperbolic non-choosers.
@@
 
+\todo[inline]{Among people who answer part of the survey, not all of them answer both the sure confidence and time inconsistency questions.
+In each of the two exercises below, we use the full sample of people who answered the relevant question.
+This means that the ``overall'' TUT for each exercise, namely the TUT that we decompose, could be different.
+Need to think about how to present / discuss this.}
+
+\todo[inline]{We decided to make a picture.
+The picture will show the overall TUT (for a given survey respondent sub-sample), along with the TUT for $X=0$ and $X = 1$, with SEs for the latter two.
+The distance from the overall to each ``endpoint'' encodes the share of each group.
+We want to see if, e.g.\ the $X=1$ group is above the overall TUT while the $X=0$ group is below and indistinguishable from zero.}
+
+\todo[inline]{There are two exercises, and we'll do each one in the same way: present bias and sure confidence.
+In each case, there's a binary indicator that creates two groups.
+We want to know if this grouping can ``explain'' the positive TUT.
+At minimum, should see that effect is concentrated on those with the indicator equal to one.
+Never totally convincing since there could be an unobserved characteristic that is correlated with our indicator variable.
+If we had a clean hyperbolicity story, we'd have four strata: rational, time inconsistent and naive, time inconsistent and sophisticated, and a fourth group that chooses commitment despite being time consistent.
+If time inconsistency is the whole story, the negative TUT should be entirely concentrated on the naive types.
+In other words, they should have a large positive TUT but everyone else should but everyone else should have something close to zero or negative.
+In terms of decomposing the TUT, we're already restricting attention to people who would not choose.
+So when we're looking at the TUT we really only have two of these strata: rational types who are not hyperbolic and don't choose commitment, and types who are hyperbolic and don't choose commitment (naives).
+So $C=0,X=1$ is naive and $C=0,X=0$ is rational.
+Should find positive effect for $C=0,X=1$ and zero or negative for $C=0,X=0$.
+To be clear: the point is that we assume by choosing or not choosing commitment, you reveal whether you are sophisticated or not, given that we know your $X$.
+First thing we could ask is, among non-choosers how many are ``rational'' versus how many are naive.
+These are the two probabilities in Eq 12.
+Second compare the treatment effects.
+Can do the same thing for sure confidence with a slight caveat that it's harder to use the language ``naive'' or ``rational'' here, but we can still think about it in a similar kind of way as long as we're careful with the language.}
+
+\todo[inline]{This stuff needs to be removed / updated / edited based on the todos listed above.}
 For any binary pre-treatment covariate $X_i$, we can calculate the relative contributions of any two groups $X_i=0$ or $X_i=1$ to the overall $\text{TUT}$ effect using the following decomposition: 
 \begin{align}
+\nonumber
         1=& \frac{\mathbbm{E}[Y_{1i}-Y_{0i} | C_i=0, X_i=1]}{\text{TUT}}\mathbbm{P}(X_i=1 | C_i=0) \\
@@
 \end{align}
-where $\text{TUT}$ is the overall TUT effect and $\mathbbm{E}[Y_{1i} - Y_{0i}|C_i = 0, X_i = x]$ is the TUT conditional on $X_i = x$.    
+where $\text{TUT}$ is the \emph{overall} treatment on the untreated effect and $\mathbbm{E}[Y_{1i} - Y_{0i}|C_i = 0, X_i = x]$ is the TUT for borrowers with $X_i = x$.    
 If, as the behavioral theory outlined above would predict, the $\text{TUT}$ arises solely from hyperbolics then term with $X_i=1$ the former term will be one and the term with $X_i = 0$ will be zero. 
-
-\paragraph{Sure confidence.} A second behavioral explanation may arise from the fact that  74\% of the control participants believe they have a 100\% chance of recovering their pawn, while in truth only \hl{56\%} will do so.
+We explore the empirical support for explanation below.
+But first we consider a second potential behavioral explanation.
+
+\paragraph{Sure confidence.} While 74\% of control participants believe they have a 100\% chance of recovering their pawn, in reality only \hl{56\%} will go on to do so.
 This suggests a market characterized by over-optimism.
-Incorrect expectations about recovery probabilities can explain low take-up in that individuals who believe they will repay are rationally uninterested in incurring costs to induce repayment.
+Incorrect expectations about recovery probabilities could explain low take-up in that individuals who believe they will repay may, rationally, choose to forgo the costs associated with commitment that are designed to induce repayment.
 Hence over-optimistic expectations in recovery probabilities will translate directly into under-adoption of preventive measures.
-Similar to the definition of hyperbolicity above, we define a binary attribute we call ``sure-confidence.'' This measure equals one for any individuals who say at the time of borrowing that they have a 100\% probability of recovering their pawn.
+Similar to our definition of hyperbolicity above, we define a binary attribute we call ``sure-confidence.'' This measure equals one for any individuals who say at the time of borrowing that they have a 100\% probability of recovering their pawn.
 The same decomposition that we used above in our discussion of hyperbolic discounting, \eqref{eq:decomp}, can be used to explore the extent to which sure confidence explains our positive and significant TUT estimate by redefining the covariate $X_i$.
@@
 
-Figure \ref{tut_beh_partition} shows the relative contributions of present bias and sure-confidence for the $TUT$.
+Figure \ref{tut_beh_partition} shows the relative contributions of present bias and sure-confidence for the $\text{TUT}$.
 In each figure the orange bar represents the contribution from those who do not possess the attribute, and the blue bar from those that do.
 We see that the forcing effect is localized mostly to those who are \textit{not} time inconsistent, contradicting naive hyperbolicity as the justification for paternalism.
-Instead, we see sure-confidence being a category that completely isolates the $TUT$, suggesting that forcing works for those who do not consider repayment structure because they don't think they need it.
+In contrast, sure-confidence being a category that completely isolates the $\text{TUT}$, suggesting that forcing works for those who do not consider repayment structure because they don't think they need it.
 Our measure of hyperbolicity is based on unincentivized responses in a short survey and so is likely to be noisy; nonetheless we see no evidence here that it drives the forcing effect.
@@
 
-If the attribute of ``sure confidence'' proves so important in explaining the TUT, what are the determinants of this characteristic?
+If the attribute of ``sure confidence'' proves so important in explaining the TUT, what are its determinants?
 In Figure \ref{determinants_sure} we plot the coefficient estimates from a regression that explains sure confidence with a battery of individual-level characteristics.
 Older males are more likely to be sure confident, as are those with more education.
-Taken at face value, it also appears to be the case that it is those with less financial stress, those who have had less trouble paying bills, and those more relied upon financially by family members.
-However, through a behavioral lens it is also possible that the type of person who is over-confident in their ability to repay a loan is also maintaining financial fictions in other domains of life, providing answers to the baseline survey questions that exaggerate their degree of economic security.
-In any case it appears that this attribute may be difficult to target with objective demographic criteria, a point to which we return.
+Taken at face value, the sure confident also appear to face less financial stress, to have less trouble paying bills, and to be more frequently relied upon financially by family members.
+However, through a behavioral lens it is also possible that the type of person who is over-confident in their ability to repay a loan also maintains fictions in other domains of their financial life, providing answers to the baseline survey questions that exaggerate their degree of economic security.
+In any case it appears that sure confidence may be difficult to predict with easily-observed and objective demographic criteria, a point to which we return below.
 
@@
 
-\paragraph{Causal forests.} Figure \ref{fig:FanPark} uses a completely non-parametric approach to understand winners and losers from paternalism at the individual level, but these bounds are relatively wide.
-To make more precise statements, we can invoke a selection on observables assumption and use the Random Forest approach of \cite{athey2019generalized} to estimate Conditional Average Treatment Effects (causal RF), or the Conditional TUT and TOT (instrumental RF).
+\paragraph{Causal forests.} 
+On average, the commitment contract benefits both those who would choose it and those who would not.
+In Section \ref{sec:bounds}, we went beyond average effects by presenting bounds on the distribution of individual treatment effects.
+Because they made no assumptions beyond random assignment, these bounds were relatively wide.
+Adding the assumption of rank invariance yielded a distribution of treatment effects that was bounded below by zero, implying that \emph{everyone} would benefit from treatment and hence that there would be \emph{no losers} from paternalism.
+Rank invariance, however, is an extremely strong assumption.
+In this section, we explore conditional average treatment effects given observed covariates. 
+In this section, we explore a middle way between the two extremes, by considering conditional average treatment effects and conditional TOT and TUT effects, given our survey measures.
+This exercise will allow us to determine whether there are groups of borrowers who are on average \emph{harmed} by commitment.
+Under the stronger assumption that our observed survey measures capture the main sources of treatment effect heterogeneity, this allows us to approximate individual-level counterfactuals, to consider whether particular borrowers made ``mistakes'' in their choice of contract.
+\todo[inline]{@Frank: read sections 6.1 and 7 of Athey et al 2019 and re-write this section as needed to explain what they do and we use.}
+To estimate conditional teratment effects, we adopt the random forest approach of \cite{athey2019generalized}.
+to estimate Conditional Average Treatment Effects (causal RF), or the Conditional TUT and TOT (instrumental RF).
 These impacts allow us to think about whether individuals made ``mistakes'' in their choices.
@@
 The optimal partition is that which minimizes expected mean squared error of treatment effects predictions out-of-sample.
-The tree is honest because it uses one sample to build the tree and another one to estimate treatment effects within that tree.
+The tree is ``honest'' in that uses one sub-sample to build the trees that make up the random forest and another one to estimate treatment effects within those trees.
 \cite{atheygrf} show that their treatment effects are asymptotically normal, which allows us to construct confidence intervals for our treatment estimate in each leaf.
@@
 More than 90\% of the individuals have APR saving effects, and even in the upper bound confidence interval more than half of individuals benefit.
+
+\todo[inline]{@Frank: note that we for the wide forest we use everyone who answered at least one survey question in the random forests.
+We have dummies for missingness of any of the predictors.
+We then take this as ground truth.
+For the narrow forest, we restrict to the sample for which we don't have missing values.
+Under certain assumptions, this ``controls'' for selection into the survey.
+Need to think a bit more about the interpretation here: it's slightly tricky.
+Question of external validity?
+Imagine another sample with the same pattern of non-response, then there's probably no concern.
+I think the issue here relates to whether the covariates that are missing for us would be missing in the hypothetical targeting exercise.
+It's a question of ``could we have targeted'' versus ``could you target'' in a setting where you have administrative data for everybody?}
 
@@
  Figure \ref{choose_wrong}, Panel A shows the results of this exercise, reinforcing the general superiority of commitment.
-Among choosers, only 25\% would have had superior outcomes had they not complied, whereas among non-choosers almost 80\% made a mistake according to this definition.
-Because this arm is comprised of 89\% non-choosers, the overall rate of mistake in the arm was around 70\%.
+Among choosers, only 18\% would have had superior outcomes had they not complied, whereas among non-choosers almost 80\% made a mistake according to this definition.
+Because this arm is comprised of 89\% non-choosers, the overall rate of mistake in the arm was around 68\%.
 As we increase the threshold on the size of the mistake necessary to be classified as having made the wrong choice, by definition the share in both groups falls, and among choosers the number making an error falls quite quickly to zero.
@@
 This allows us to identify the winners and losers from paternalism in a nuanced manner, since members of groups with CATEs$<$0 are hurt and everyone else is helped.
-Because the ATE$>$TUT, this exercise results in an even larger fraction of individuals benefiting from commitment; here we find that fully 87\% of individuals are better off being forced into commitment than staying in the control.
+Because the ATE$>$TUT, this exercise results in an even larger fraction of individuals benefiting from commitment; here we find that fully 91\% of individuals are better off being forced into commitment than staying in the control.
 This now allows us to make a stronger statement in favor of paternalism; not only is the case that forcing commitment generates large benefits on average, but it is also generating benefits for almost 90\% of the forced population.
@@
 So the choice variable itself cannot be used to target other than in a voluntary program.
-This leaves us with only a few objective covariates that could be used to target: age, gender, HS education or above, and whether that individual has ever pawned before.
+This leaves us with only a few objective covariates that could be used to target: age, gender, HS education or above, desired loan size, and whether that individual has ever pawned before.
 
@@
 Figure \ref{wide_narrow_forests} shows the relationship between the CATEs estimated from the RF using the `wide' and `narrow' covariates.
-Not only is it visually obvious from this figure that we generate substantially less heterogeneity when using the narrow covariate set, but in fact the Chernozhukov test for heterogeneity on the narrow RF is no longer significant.
-This constitutes preliminary evidence that the commercially feasible covariate set we collected will not be effective at targeting paternalism.
+It visually obvious from this figure that we generate substantially less heterogeneity when using the narrow covariate set, although the the Chernozhukov test on the narrow RF does still indicate significant heterogeneity.
 
@@
 Figure \ref{targeting_rules} plots the same densities of net benefit as were shown before, where we now take the wide RF as the ground truth of the benefits of forcing everyone into commitment, and the welfare under the two targeting rules shown for comparison.
-Given the poor explanatory power of the narrow criteria it is unsurprising to see that the information gain from using these variables is small; the fraction of the whole sample benefiting when we go from universal forcing to narrow RF targeted forcing rises only marginally from 86.7\% to 88.4\%.
+Given the poor explanatory power of the narrow criteria it is unsurprising to see that the information gain from using these variables is small; the fraction of the whole sample incorrectly targeted when we go from universal forcing to narrow RF targeted forcing falls only marginally from 8.8\% to 8.3\%.
 When we look at the Logit targeting we see that it has actually made targeting substantially worse; this behavior is driven by the confluence of the poor explanatory power of the narrow variables with the fact that the Logit matches the correct sample fraction of ones, therefore making numerous Type II errors in an environment where commitment is beneficial for most.
@@
 Table \ref{hit_miss_rule} shows Type I and Type II error rates for each of six rules:  all to control, all to treatment (Forcing), optimal, Narrow RF targeting, Logit targeting, and Choice.
-While the Narrow RF is able to correctly assign roughly half of those who do not benefit from commitment to control, it also incorrectly allocates 5.4\% of the sample that would have gained from treatment to control, and so on net it only improves the correct targeting rate by about 1.5 percentage points relative to universal Forcing.
+While the Narrow RF is able to correctly assign roughly half of those who do not benefit from commitment to control, it also incorrectly allocates 3.7\% of the sample that would have gained from treatment to control, and so on net it only improves the correct targeting rate by about a half of a percentage point relative to universal Forcing.
 The Logit is less successful at predicting benefits and in particular makes many Type II errors, resulting in a net targeting performance that is actually worse than universal forcing.
@@
 Self-targeting through choice proves to be little better than assigning everyone to the control, given the low take-up rate and the presence of both Type I and Type II errors in the Choice arm.
-Over 71\% of individuals in the Choice arm made a mistake, weighting the results among choosers and non-choosers by their frequency.
+68\% of individuals in the Choice arm made a mistake, weighting the results among choosers and non-choosers by their frequency.
 The takeaway is that given low take-up, the large fraction of the sample benefiting from commitment, and the weak predictive power of the narrow covariates, in this case universal paternalism appears to be an attractive contract.
@@
 \begin{table}[H]
-\caption{Attrition table}
+\caption{Limited and balanced attrition}
 \label{attrition_table}
@@
 \end{center}
- \scriptsize This table shows the survey response rate in the first row, while the second row displays the number of pawns in each arm.
-The fourth column shows a p-value of an F-test of equality of means, showing that both the response rate and the number of pawns is balanced across arms.
+ \scriptsize Each row in this table 
+ corresponds to a regression, where the level of observation is the individual loan originated.
+The dependent variables of these regressions are displayed in the first column.
+Each dependent variable is regressed in a multivariate OLS regression against the experimental arms indicators (control, forced commitment, choice).
+The table reports the coefficients on each of these indicators, as well as the p-value an F-test of the null hypothesis of equality of the three coefficients.
+The dependent variables are: the number of pawns-loans originated per day per branch.
+A variable indicating whether a person who answered the baseline survey (before knowing contract terms) ended up pawning.
+And an indicator of whether the person that obtained the loan answered the baseline survey.
+By design we had the choice arm be larger.
 %\textit{Do file: } \texttt{ss\_att.do}
@@
 
+\newpage
 \begin{table}[H]
@@
 \scriptsize {
-\noindent This table presents balance tests for the administrative data (Panel A) and survey data for those that pawned (Panel B).
-The first three columns shows summary stats for each arm separately.
-The last column shows the p-value of an F-test of the hypothesis that the mean across arms for that variable is the same across the three arms.
-Randomization was done at the branch-day level.
-By design the observations are not exactly equal across arms as we were more interested in detecting effects in the choice-commitment arm.
-Loan amount is the peso amount given to the client; Weekday is the fraction of loans given on a weekday, as opposed to weekends.
-In Panel B: woman indicated whether the client is female, age of the client is measured in years; subjective value is the self-reported value of the item, has pawned before is a dummy=1 if the client declares to have pawned before (although not necessarily with Lender $P$).
-The subjective probability of recovery was elicited a la Manski, from 0 to 100 what is the probability that you will recoup your pawn.
-+High-school is a dummy that indicates if the client has completed high school.
+\noindent This table has two panels.
+Panel A uses administrative data at the loan level, while Panel B uses survey data.
+Each row in this table corresponds to a regression, where the level of observation is the individual loan originated.
+The dependent variables of these regressions are displayed in the first column.
+Each dependent variable is regressed in a multivariate OLS regression against the experimental arms indicators (control, forced commitment, choice).
+The table reports the coefficients on each of these indicators, as well as the p-value an F-test of the null hypothesis of equality of the three coefficients.
+The admin data was a very limited set of pre-determined variables.
+The dependent variables in Panel A are the loan amount in pesos, and an indicator for whether the day of the loan origination was a weekday (as opposed to weekend).
+The dependent variables in Panel B from the survey (see the questions in Table \ref{baseline_survey}.
+Subjective value of the pawn (how much would the client be willing to sell it for (Q3), an indicator for having trouble paying bills in the last 6-months (Q28), present bias (constructed from questions Q10 and Q29 in the standard way as in \cite{Ashraf}), an indicator for whether they make expenses budget for the month ahead of time.
+The subjective probability of recovery was elicited a la Manski (from 0 to 100 what is the probability that you will recoup your pawn), pawned before is a dummy=1 if the client declares to have pawned before (although not necessarily with Lender $P$) age is in year, +High-school is a dummy that indicates if the client has completed high school.
 }
@@
 \begin{table}[H]
-\caption{Main treatment effects}
+\caption{Effects on Financial Cost}
 \label{main_impact_table}
@@
 \scriptsize This table shows the treatment effects for our core pecuniary outcomes.
-Columns (1) \& (7) analyses this core measure.
-Further columns decomposes the core measure in all of its components, according to the different costs we measure :
+Each column is a different regression for different outcomes on an indicator for the forced and choice arms, following specification in equation \ref{basic_reg}.
+Columns (1) \& (7) analyze our core financial cost measures, while the rest of the columns decompose these into finer components as follows:
 
@@
 
-Each regression includes branch and day-of-week FE. Standard errors are clustered at the branch-day level.
+\textcolor{blue}{A few borrowers have more than one loan.
+These are treated as different observations, but Table \ref{multiple_loans} shows our results are similar collapsing the data at the person level or using only the assignment of the first loan.} Each regression includes branch and day-of-week FE.
+Standard errors are clustered at the branch-day level.
 
@@
 \begin{table}[H]
-\caption{Intermediate outcomes}
+\caption{Effects on intermediate outcomes}
 \label{mechanisms}
@@
 \noindent This table explores treatment effects in ``intermediate variables''.
-Each column represents a different dependent variable following the main specification  (\ref{basic_reg}).
-The last row shows the mean of the dependent variable for the control group.
-Panel A talks about the speed of payment.
-Column (1) indicates the elapsed days toward the first payment.
-Column (2) shows the effect on the percentage of payments during the first visit.
-Column (3) records the probability of recovery in the first visit, and columns (4), (5) speak on the loan duration.
-Panel B are variables related to default.
-Column (6) is the probability of making a positive payment and defaulting.
-Column (7) is the percentage of payments conditional on defaulting.
-Column (8) reports the probability of selling the pawn, conditional on defaulting.
-Finally Panel C is related to the number of visits made to make payments.
-
-In sum, we find that the Forced commitment contract clients pays 13.8 days earlier in average, during this first visit, clients pay 7.7\% more of the loan amount, with a 8\% increase probability of recovery.
+Each column represents regression output for different dependent variables following equation (\ref{basic_reg}).
+Panel A focuses on variables related to the speed of payment.
+While Panel B focuses on variables related to default, and Panel C related to visits.
+The outcome variables are as follows:  number of days elapsed between origination and first payment (col 1); percentage of the loan paid in the first payment (col 2); probability of recovery in the first visit (col 3); \textcolor{blue}{loan duration is the number of days the borrower took to payoff her loan for those that recover, the number of days until default for those that default, and the maximum number of days we observe them in the sample for those that have not recovered or defaulted (col 4)}; loan duration conditional on recovery; an indicator for paying a positive amount towards recovery but nonetheless losing the pawn (col 6); the percentage or the loan paid, conditional on defaulting --`wasted payments' (col 7).
+Column 8 uses the phrase `selling the pawn' for a dummy variable indicating the borrower did not pay any amount towards recovery and lost the pawn.
+The dependent variable in column 9 is the number of day-visits to the branch (measured by the existence of transactions that day associated with our particular pawn), while column 10 conditions on borrowers that lost the pawn.
+Each regression includes branch and day-of-week FE.
+Standard errors are clustered at the branch-day level.
+%In sum, we find that the Forced commitment contract clients pays 13.8 days earlier in average, during this first visit, clients pay 7.7\% more of the loan amount, with a 8\% increase probability of recovery.
 Moreover, the forced commitment contract reduces the probability of defaulting and making a positive payment by 7\%, thus another channel for savings is that treatment helps avoid making payments toward recovery but defaulting.}
@@
 \begin{table}[H]
-\caption{Effects on several definitions of cost}
+\caption{Effects on more comprehensive cost measures}
 \label{table_robustness_fc}
@@
  \scriptsize 
+ This table augments the measure of financial cost presented in Table \ref{main_impact_table} with measures of transaction costs, subjective costs, and adjustments for liquidity costs.
+Column 1 replicates the result of column 1 of Table \ref{main_impact_table} to ease comparability.
+Column 2 uses the subjective value of the pawn instead of the assessed gold value.
+Column 3 uses the cost from column 1 but adds to it the self-reported transport cost (most use public transport, imputing missing values with the average) as well as a whole day's minimum wage as a proxy for lost time.
+Column 4 \hl{sums} to FC an extra imputed `liquidity' cost by adding interest of 7\% per month for each peso paid.
+Column 5 applies all these extra costs at the same time.
+Columns 6 to 10 apply the analogous changes to the APR formula.
+Each regression includes branch and day-of-week FE.
+Standard errors are clustered at the branch-day level.
+
+ \todo[inline]{@It is not very clear how exactly we do the liquidity adjustment.}
 
@@
 \begin{table}[H]
-\caption{Ever pawning again}
+\caption{Effects on Repeat Pawning}
 \label{repeat_loans}
@@
  \scriptsize
-
+This table estimates the specification of equation \ref{basic_reg} but at the level of the borrower (not the loan).
+Each column represents a regression with a different outcome variable.
+In column 1, the dependent variable indicates, for each borrower in the experiment, whether he/she pawned again after \hl{the first loan} in the experiment (up to the end period of our data set \hl{XXX} days after the experiment began).
+Column 2 is analogous, but only pawning after 90 days of the first loan is considered.
+Column 3 instead considers pawning before 90 days.
+Column 4 is analogous to column 1 but focuses on the pawning of a gold piece that is different from the one in \hl{the first experimental loan.} Column 5 is analogous to column 1, but conditioning on the sample that recovered the first loan.
+Each regression includes branch and day-of-week FE.
+Standard errors are clustered at the branch-day level.
 %\textit{Do file: } \texttt{repeat\_loans.do}
@@
 \end{center}
+
+\todo[inline]{For Frank}
  %\scriptsize This table shows estimates of the ToT and the TuT with an IV-LATE framework.
@@
          \scriptsize
-         Panel (a) presents a histogram of financial cost for the control group.
-Financial cost is defined as the sum of payments made by a client towards recovering her pawn + the cost of the pawned piece when she ends up losing it.
-We plot separately the financial cost for those who lose the pawn (blue) and those that recover it (transparent), and those who after many cycles have refinanced a continuing loan (pink).
+         Panel (a) presents a histogram of financial cost (defined as in Section \ref{{costs}}) for the control group.
+The figure plots  financial cost separately for borrowers who lose the pawn (blue) and those that recover it (transparent).
 Panel (b) is analogous but displays the APR.
@@
 First the title clearly indicated which contract the client has (arrow 1).
-Second, in the case of the fee contract it clearly indicates that there is a fee for paying late equivalent to 4\% of the value of the monthly payment (arrow 2).
+Second, in the case of the fee contract it clearly indicates that there is a fee for paying late equivalent to 2\% of the value of the monthly payment (arrow 2).
 Third, there is a calendar for payments clearly specifying the dates and amounts to pay each month.
@@
     \begin{center}
-    \begin{subfigure}{0.31\textwidth}
+    \begin{subfigure}{0.45\textwidth}
         \caption{Status-quo}
@@
     \end{subfigure}
-    \begin{subfigure}{0.31\textwidth}
+    \begin{subfigure}{0.45\textwidth}
         \caption{Forced commitment}
@@
     \end{subfigure}
-    \begin{subfigure}{0.31\textwidth}
+    \begin{subfigure}{0.45\textwidth}
         \caption{Choice commitment}
@@
      \scriptsize
-     \hl{ISAAC: CAN YOU DESCRIBE THESE? ALSO: I THINK IT IS BETTER TO USE PERCENT INSTEAD OF COUNT}
+     \todo[inline]{For Isaac}
       %\footnotesize{ \textit{Do file: }  \texttt{hist\_payments.do}}
@@
 \cleardoublepage
+
+\begin{comment}
 
@@
     \scriptsize
-   \hl{The above figure is outdated figure. Need to update}
+   \hl{REPLACE THIS ONE WITH THE ONE IN THE PRESENTATION}
      %\textit{Do file: }  \texttt{tot\_tut\_graph.do}
 \end{figure}
-
+\end{comment}
+
+\begin{figure}[H]
+\caption{TOT \& TUT as LATE}
+    \label{tot_tut_graph}
+    \begin{center}
+        \centering
+        \includegraphics[width=1.0\textwidth]{Figuras/tot_tut_intuition.png}
+    \end{center}
+    \scriptsize
+    \todo[inline]{For Frank}
+     %\textit{Do file: }  \texttt{tot\_tut\_graph.do}
+\end{figure}
+
+\vspace{.3in}
 \begin{figure}[H]
@@
     \end{center}
-
+        \scriptsize
+    \todo[inline]{For Frank}
 %\textit{Do file: } \texttt{fan\_park\_bnds.do}       
@@
 
-    \end{subfigure}
-        \begin{subfigure}{0.45\textwidth}
-        \caption{Financial value of mistake}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/integral_cw_apr_tot_tut.pdf}
+    %\end{subfigure}
+    %    \begin{subfigure}{0.45\textwidth}
+    %    \caption{Financial value of mistake}
+    %    \centering
+    %    \includegraphics[width=\textwidth]{Figuras/integral_cw_apr_tot_tut.pdf}
 
@@
     \end{subfigure}
-    %     \begin{subfigure}{0.45\textwidth}
-    %     \caption{\footnotesize{Effect of CATE benefit vs predicted take-up}}
-    %     \centering
-    %     \includegraphics[width=\textwidth]{Figuras/benefit_choice.pdf}% takeuppr_def.pdf 
-    % \end{subfigure}
 
@@
 
+\todo[inline]{Enrique deleted subfigure b}
+\todo[inline]{should we flip the x-axis, so they look for CDFs?}
+
 \cleardoublepage

### 2023-07-25 RScripts/te_grf.R

@@ -58,7 +58,24 @@ te_grf <- function(data_in, outcome_var, name) {
     "cta_tanda",
     "genero",
     "masqueprepa",
-    "estresado_seguido"
+    "estresado_seguido",
+    "na_edad",
+    "na_faltas",
+    "na_c_trans",
+    "na_t_llegar",
+    "na_fam_pide",
+    "na_ahorros",
+    "na_t_consis1",
+    "na_t_consis2", 
+    "na_confidence_100",
+    "na_hace_presupuesto",
+    "na_tentado",
+    "na_rec_cel",
+    "na_pres_antes",
+    "na_cta_tanda",
+    "na_genero",
+    "na_masqueprepa",
+    "na_estresado_seguido"    
   ),
   c(
     "tuesday",
@@ -88,7 +105,24 @@ te_grf <- function(data_in, outcome_var, name) {
     "rosca",
     "female",
     "more.high.school",
-    "stressed"
+    "stressed",
+    "na.age",
+    "na.trouble.paying.bills",
+    "na.transport.cost",
+    "na.transport.time",
+    "na.fam.asks",
+    "na.savings",
+    "na.patience",
+    "na.future.patience", 
+    "na.sure.confidence",
+    "na.makes.budget",
+    "na.tempted",
+    "na.sms.reminder",
+    "na.pawn.before",
+    "na.rosca",
+    "na.female",
+    "na.more.high.school",
+    "na.stressed"    
   ))
   
   require("dplyr")

### 2023-07-25 RScripts/tot_tut_instr_forest.R

@@ -43,7 +43,24 @@ rename_var = function(df) {
     "cta_tanda",
     "genero",
     "masqueprepa",
-    "estresado_seguido"
+    "estresado_seguido",
+    "na_edad",
+    "na_faltas",
+    "na_c_trans",
+    "na_t_llegar",
+    "na_fam_pide",
+    "na_ahorros",
+    "na_t_consis1",
+    "na_t_consis2", 
+    "na_confidence_100",
+    "na_hace_presupuesto",
+    "na_tentado",
+    "na_rec_cel",
+    "na_pres_antes",
+    "na_cta_tanda",
+    "na_genero",
+    "na_masqueprepa",
+    "na_estresado_seguido"    
   ),
   c(
     "tuesday",
@@ -73,7 +90,24 @@ rename_var = function(df) {
     "rosca",
     "female",
     "more.high.school",
-    "stressed"
+    "stressed",
+    "na.age",
+    "na.trouble.paying.bills",
+    "na.transport.cost",
+    "na.transport.time",
+    "na.fam.asks",
+    "na.savings",
+    "na.patience",
+    "na.future.patience", 
+    "na.sure.confidence",
+    "na.makes.budget",
+    "na.tempted",
+    "na.sms.reminder",
+    "na.pawn.before",
+    "na.rosca",
+    "na.female",
+    "na.more.high.school",
+    "na.stressed"    
   ))
 }
 
@@ -150,7 +184,7 @@ fit_instr_forest = function(xvar, wvar, yvar, zvar, dta, nme) {
     theme_few()
   ggsave(filename_vi)
   
-  # Save results
+    # Save results
   data.out <- add_column(dta, inst_hat_oob$predictions, inst_hat_oob$variance.estimates)
   filename_out <- paste("_aux/", nme, "_instr_forest.csv", sep="")
   write_csv(data.out, filename_out)

### 2023-07-26 OA.tex
tut conditional on survey & results with NA in causal RF

@@
 \begin{table}[H]
-\caption{Balance: Admin data conditional on answering survey \& Survey data conditional a loan}
+\caption{Balance conditional on survey response and question-by-question response rates by treatment arm}
 \label{SS_cond_survet}
@@
 \scriptsize
-\textcolor{blue}{This table is analogous to Table \ref{SS}, but it uses different sub-samples.
-Panel A reports regression results using administrative loan data, but conditioning on those borrowers who also responded the baseline survey.
-Panel B reports regression results using survey data, but conditioning on those borrowers who pawned \hl{the same day of the survey response}}.
+
+Panel A of this table presents the same information as Panel A of Table \ref{SS}, but restricts attention to the subsample of borrowers who answered \hl{at least one question???} in our baseline survey.
+Conditional on survey response, loan amount and weekday are balanced across treatment arms.
+Panel B presents response rates to each individual survey question across treatment arms, along with p-values for the F-test of no difference in response rates across survey arms.
+This panel uses data for borrowers who pawned on the \hl{same day as their survey response}.
+
 %\textit{Do file: } \texttt{ss\_att.do}
@@
 
+\begin{landscape}
+\begin{table}[H]
+\caption{Survey Non-response: TUT estimates for respondents to each survey question.}
+\label{TUT_cond_survet}
+\begin{center}
+\scriptsize{\input{./Tables/tut_cond_survey.tex}}
+\end{center}
+\scriptsize
+
+Some borrowers did not respond to our survey; others only completed part of the survey.
+This table computes the TUT effect for a number of sub-groups by survey response, and compares them against the overall TUT effect.
+The top panel uses financial cost as the outcome variable, while the bottom panel uses APR.
+Each group is defined by the borrowers who responded to a particular \emph{subset} of the survey questions. 
+For example, column (4) computes TUT effects for the subgroup of borrowers who responded to the two questions needed to compute our measure of present bias, while column (8) computes the TUT for the subgroup of borrowers who provided their age.
+The bottom row of the table counts the number of borrowers in each category.
+TUT estimates are quite stable across sub-groups and generally similar to the full-sample estimates.
+Because standard errors increase as sample size falls, some of the sub-group estimates are not statistically significant.
+%\textit{Do file: } \texttt{tut_cond_survey.do}
+\end{table}
+\end{landscape}
+
 \newpage
@@
 \begin{figure}[H]
-    \caption{Behavior of those who lost pawn}
+    \caption{Behavior of borrowers who lost their pawn}
     \label{proxy_naive}
@@
         \scriptsize 
-        This figure describes behavior for the subsample of clients whose pawn was not recovered (in the control group).
-Panel (a) shows days elapsed from the pawn to the first payment, while panel (b) displays the days elapsed to last payment.
-Some people pay after the day 105 when the grace period ends because the can ``restart'' the loan if they pay all interest owed.
-It amounts to starting a new loan with the same conditions and same pawn.
-Panel (c) shows the fraction of the loan that they paid (even when they ended up losing the pawn).
-Panel (d) displays the number of times they went to the branch to pay.
+        This figure provides more details on the behavior of clients who were assigned to the control group and did not recover their pawn.
+Panel (a) shows a histogram of days elapsed from the pawn to the first payment, while panel (b) displays a histogram of days elapsed until the last payment.
+Some borrowers make payments after day 105, the end of the grace period: if they pay all interest owed, they can ``restart'' the loan.
+This amounts to starting a new loan with the same conditions and same pawn.
+Panel (c) shows a histogram of the fraction of the loan paid, while panel (d) presents a barplot of the number of times that borrowers went to the branch to make payments.
       %\textit{Do file: }  \texttt{hist\_den\_default.do}
@@
 \normalsize
-The approach taken in the paper for censored loans is a conservative one in that it inherently assumes that all of the loans outstanding at the end of the observation window will be repaid, making it so that the acceleration of payment observed in the Forced arm does not translate mechanically into a treatment effect on default.
+
+Some loans in our sample are ``censored'' in that they continue beyond our observation period.
+For these loans, we do not know whether the borrower ultimately defaulted our recovered her pawn.
+In this appendix, we show that our main results are robust to different ways of addressing censoring.
+
+Our main results, presented above, assumed that all loans that were still outstanding at the end of the sample period were \emph{eventually repaid}.
+Because forced commitment causes borrowers to make payments earlier than they otherwise would have, this is a conservative assumption.
+To see why, suppose for the sake of argument that commitment affects payment timing, but does not not default.
+In other words, suppose that treatment makes censoring \emph{less likely} but has no effect on uncensored outcomes. 
+If we were to treat all outstanding loans as defaults--the opposite of our convention--this would artificially inflate the rate of default among control loans relative to treatment loans. 
+This is why we adopt the reverse convention above.
+We now consider some alternative approaches.
+
+\todo[inline]{@Frank: keep updating below after getting responses from @Issac.}
+
+%The approach taken in the paper for censored loans is a conservative one in that it inherently assumes that all of the loans outstanding at the end of the observation window will be repaid, making it so that the acceleration of payment observed in the Forced arm does not translate mechanically into a treatment effect on default.
 This appendix delves into it more detail.
+
 One way of considering the effect that this issue could have on our results is to make extreme assumptions about the outcome of these loans in the treatment and control so as to bound the possible influence of censoring.
-In Table \ref{mns} we compare the Forced and Control arms, making the bracketing assumptions about repayment on censored loans.
+In Table \ref{bounding_censoring} we compare the Forced and Control arms, making the bracketing assumptions about repayment on censored loans.
 Panel A assumes all censored loans are repaid, and Panel D that all default.
@@
 \end{center}
- \scriptsize  \textcolor{blue}{This table explores learning by focusing on a subsample of borrowers in the experiment and observing their subsequent behavior.
+ \scriptsize
+
+This table presents information about borrowers' \emph{future} pawning behavior.
+Column (1) reports results for the 228 borrowers who returned to pawn again at a day/branch that was randomly assigned to the choice arm, enabling us to observe whether they chose commitment or the status quo contract.
+Each row presents a difference in mean commitment take-up rates and associated standard errors.
+The first row (ATE) compares borrowers who were initially assigned to forced commitment against those were assigned to the control condition.
+The second row (ITT) compares borrowers who were initially assigned to the choice commitment condition to those who were not.
+Whereas column (1) conditions on the (endogenously) selected sample of borrowers who return to pawn again, column (2) considers the full sample by re-defining the ``outcome'' to be an indicator for whether a borrower pawned again on a day when choice was offered \emph{and} chose commitment.
+
+%This table explores learning by focusing on a subsample of borrowers in the experiment and observing their subsequent behavior.
 Column 1 conditions the sample on borrowers who (a) pawned during the experiment a subsequent time after being assigned to control, forced commitment or choice (the regressors), and (b) when pawning again they went to a branch day when (randomly) choice was available, thus enabling us to observe if they chose the commitment contract or the status quo.
@@
 Column 1 conditions the sample on the (endogenous) event of pawning again.
-Column 2 does not condition the sample, but instead defined the dependent variable as equal to one \hl{if the borrower pawned subsequently and choice was available that day and chose commitment, and zero otherwise.}}
+Column 2 does not condition the sample, but instead defined the dependent variable as equal to one \hl{if the borrower pawned subsequently and choice was available that day and chose commitment, and zero otherwise.}
+
 \end{table}
@@
 \begin{figure}[H]
-        \caption{Financial cost TUT effect for different discount rates}
+        \caption{Financial benefit TUT effect for different discount rates}
     \label{fc_discount_rates}
@@
     \end{center}
-     \scriptsize This Figure estimates regression equation \ref{basic_reg} as in column 1 of Table \ref{main_impact_table} but it introduces a daily discount factor (time preference) in the definition of financial cost to discount payments.
-Payments done in the present are more costly for the borrower.
-It estimates the effect of the treatment arms  for different discount factors, where a discount factor of 1 corresponds exactly to the estimate of column 1 of Table \ref{main_impact_table}.
+     \scriptsize This Figure re-estimates the treatment on the untreated (TUT) effect from Table \ref{tot_tut}, introducing a daily discount factor in the definition of financial benefit.
+The discount factor reflects time preference, i.e.\ the fact that payments made in the present are more costly for the borrower.
+At a given annual discount rate in percentage points (x-axis) the solid line gives the adjusted TUT and the shaded regions \hl{???
+confidence intervals}.
+A discount factor of one corresponds to the estimate from Table \ref{tot_tut}.
+For higher discount rates, the adjusted financial cost will be higher, so the financial cost \emph{savings} will be lower.
+As seen from the figure, borrowers would need to face unrealistically large discount rates to reverse our headline result of a large, positive, and statistically significant TUT effect.
+     %It estimates the effect of the treatment arms  for different discount factors, where a discount factor of 1 corresponds exactly to the estimate of column 1 of Table \ref{main_impact_table}.
 Because the commitment contract induces earlier payments, this adjusted financial cost will be higher, and thus financial savings will be lower.
@@
     \end{center}
-     \scriptsize  This figure performs a partition of the Treatment on the Untreated (FC), estimating the share of the effect that arises within each of two binary categories.
+     \scriptsize  Each panel in this figure shows how the estimated treatment on the untreated (TUT) effect varies with a binary survey variable $X_i$.
+In the left panel (Sure-confidence) $X_i = 1$ if  borrower $i$ reported that she was certain to recover her pawn, zero otherwise.
+In the right panel (P.B.), $X_i = 1$ if borrower $i$ is ``present-biased'' based on her responses to the time preference questions from our survey.
+Each panel depicts three estimates and associated \hl{standard errors???
+95 CI?}: the overall TUT (blue), the TUT for borrowers with $X = 1$ (green), and the TUT for borrowers with $X = 0$ (red).
+By the law of iterated expectations, the overall TUT in each panel must lie between the group-specific TUTs.
+The overall TUT is slightly different in each panel, because some borrowers only completed part of the survey.
+In each panel, we present results for the full set of borrowers who answered the survey question or questions needed to determine $X_i$.
+From the right panel, we see that TUT does not appear to vary with present bias.
+In contrast, the left panel suggests that the positive and significant overall TUT is driven by individuals who are ``sure-confident,'' i.e.\ borrowers who report that they are certain to recover their pawn.
+     %to be largely concentrated relevant survey question  according to her survey responses two binary performs a partition of the Treatment on the Untreated (FC), estimating the share of the effect that arises within each of two binary categories.
 The top bars examine present bias (individuals are more impatient over one-month time horizon than they are between three and four months).
@@
 Blue bar is the component arising from those without the trait, orange bar from those with the trait.
-      %\footnotesize{ \textit{Do file: }  \texttt{partition_tot_tut.do}
-
-      \todo[inline]{This figure will change}
+      %\footnotesize{ \textit{Do file: }  \texttt{partition_tut.do}
+
+      \todo[inline]{This figure has changed. Will have minor style modifications. @Issac: what's the purple stuff in the middle?}
 \end{figure}
@@
 \vspace{.2in}
-\todo[inline]{Presumably we want to cut some of this text? In the body of the text we don't get into this in such detail.}
+
+%\todo[inline]{Presumably we want to cut some of this text? In the body of the text we don't get into this in such detail.}
 %We plot the empirical distribution of financing cost $F_{commitment}(FC)$ and of the status quo contract, $F_{sq}(FC)$. Framed as a choice among cost distributions.
@@
     \end{center}
-    \scriptsize This figure plots the empirical cumulative distribution of financial cost.
+    \scriptsize This figure plots plots the empirical CDF of experimental outcomes separately for the control / status quo (dashed) and forced commitment contracts (solid).
+In panel (a), the outcome is APR; in panel (b) the outcome is Financial Cost.
+In each case, the empirical CDF under forced commitment first-order stochastically dominates the empirical CDF under the status quo.
+This can be seen by examining the dotted line at the bottom of panels (a) and (b), which shows the difference $(\text{Control} - \text{Commitment})$.
+    %The dotted line at the bottom of panels (a) and (b)   the empirical cumulative distribution function APR and financial cost of financial cost.
 It does this separately for the fee-forcing contract and for the status-quo contract.
@@
 \label{append:chernozhukov}
-Our approach relies on the following simple observation: if $\Delta_i$ is constant across $i$, then 
-\[
-\text{ATE}(X_i) \equiv \mathbbm{E}[\Delta_i |X_i] = \mathbbm{E}[\Delta_i] \equiv \text{ATE}
+If the treatment effects $Y_{i1} - Y_{i0}$ are constant across $i$, then we must have
+\[
+\text{ATE}(X_i) \equiv \mathbbm{E}[Y_{i1} - Y_{i0} |X_i] = \mathbbm{E}[Y_{i1} - Y_{i0}] \equiv \text{ATE}
 \]
@@
 We operationalize this idea using a two-step approach proposed by \cite{chernozhukov2018generic}.
-We begin by randomly dividing the participants in the forced arms of the experiment ($Z_i \neq 2$) into two groups: a ``training set'' and a \todo{80/20 split?}{``test set.''} In the first step, we apply random forests to the training set to estimate two proxy predictors: $\psi(\cdot|\text{Training})$ approximates the untreated potential outcome function, $\mathbbm{E}[Y_{i0}|X_i] = \mathbbm{E}[Y_i|Z_i=0,X_i]$, while  $\tau(\cdot|\text{Training})$, approximates the average treatment effect function
+We begin by randomly dividing the participants in the forced arms of the experiment ($Z_i \neq 2$) into two groups: a training set and a test set.
+These sets are constructed to ensure that all observations from a given branch-day cluster are allocated to the same set.
+This avoids inferential problems that could arise from correlated unobservables within clusters.
+In the first step, we apply the generalized random forest approach of \cite{athey2019generalized} to the training set to estimate two proxy predictors: $\psi(\cdot|\text{Training})$ approximates the untreated potential outcome function, $\mathbbm{E}[Y_{i0}|X_i] = \mathbbm{E}[Y_i|Z_i=0,X_i]$, while  $\tau(\cdot|\text{Training})$, approximates the ATE function
 \[
@@
 The proxy predictors need not be unbiased or even consistent estimators of the functions they aim to approximate: the goal of this exercise is merely to find a scalar function of $X_i$ that \emph{accurately predicts} $\text{ATE}(X_i)$.
-
 In the second step we fit a linear regression model to data from the training set using regressors constructed from the proxy functions $\psi(\cdot|\text{Training})$ and $\tau(\cdot|\text{Training})$ constructed in the first step.
@@
 \]
-If treatment effects are homogeneous we must have $\beta_2 = 0$.
-Rejecting this hypothesis establishes that $\tau_i$ predicts $\text{ATE}(X_i)$ and hence that $\Delta_i$ varies.
+If treatment effects are homogeneous we must have $\beta_2 = 0$. Rejecting this hypothesis establishes that $\tau_i$ predicts $\text{ATE}(X_i)$ and hence that $\Delta_i$ varies. 
 Since $\tau_i$ and $\psi_i$ do not depend on the test set, inference for the regression in \eqref{eq:chernreg} is straightforward conditional on the Training/Test split.  
-
-\todo[inline]{Discuss the results here.}
-
-\todo[inline]{Issac: re-run this exercise with removing the propensity score weights $p(Z)$. Presumably it shouldn't change anything, but it's simpler to explain what we do and probably less noisy}
-
-\begin{table}[H]
-\begin{center}
-\scriptsize{\input{./Tables/test_calibration_2.tex}}
-\end{center}
-\end{table}
-
-\todo[inline]{Some Questions for Issac: (1) How are we carrying out the sample splitting?
+Our estimate for $\beta_2$ is \hl{XXXX} with a cluster-robust standard error of \hl{XXXX}.
+Thus we easily reject the null hypothesis of homogenous treatment effects.
+
+%\todo[inline]{Discuss the results here.}
+
+%\todo[inline]{Issac: re-run this exercise with removing the propensity score weights $p(Z)$. Presumably it shouldn't change anything, but it's simpler to explain what we do and probably less noisy}
+
+%\begin{table}[H]
+%\begin{center}
+%\scriptsize{\input{./Tables/test_calibration_2.tex}}
+%\end{center}
+%\end{table}
+
+%\todo[inline]{Some Questions for Issac: (1) How are we carrying out the sample splitting?
 If we cluster standard errors at the branch-day level, we should take this into account when we split.
@@
        \centering
-      \includegraphics[width=\textwidth]{Figuras/he_dist_def_c.pdf}
+      \includegraphics[width=\textwidth]{Figuras/he_dist_def.pdf}
     \end{subfigure}  
@@
        \centering
-      \includegraphics[width=\textwidth]{Figuras/he_dist_des_c.pdf}
+      \includegraphics[width=\textwidth]{Figuras/he_dist_des.pdf}
     \end{subfigure}      
@@
 \end{figure}
-
-\todo[inline]{Some subfigures are not loading}
 

### 2023-07-26 donde.tex
tut conditional on survey & results with NA in causal RF

@@
 Granted, this is a selected sample because the decision to pawn again is potentially endogenous to the initial treatment allocation.
-For this reason, Column (2) considers the full sample of \hl{4436} by re-defining the ``outcome variable'' to be an indicator for returning to pawn again at a branch/day when commitment was offered \emph{and} choosing commitment.
+For this reason, Column (2) considers the full sample of \hl{4436} borrowers by re-defining the ``outcome variable'' to be an indicator for returning to pawn again at a branch/day when commitment was offered \emph{and} choosing commitment.
 This composite outcome variable is not subject to the sample selection problem.
@@
 Again, there is no statistically discernible difference in commitment take-up rates in either row.
-While these exercises cannot completely exclude the possibility that learning plays a role, the provide no indication that the lack of voluntary compliance is simply a matter of inexperience with commitment.
+While these exercises cannot completely exclude the possibility that learning plays a role, they provide no indication that the lack of voluntary compliance is simply a matter of inexperience with commitment.
 
@@
 \paragraph{Time discounting.} Discounting is a second potential explanation for our results.
-Our estimated decrease in the financial cost of credit from above ignores discounting, but the intervention inherently imposes up-front costs (early payment) in return for delayed benefits (recovery of pawn).
-Highly impatient individuals might therefore rationally choose the \emph{status quo} contract, despite our results showing a benefit raw (undiscounted) returns.
-To investigate this explanation we can calculate the net present value (NPV) of the financial cost $\text{TUT}$ effect under different hypothetical discount rates, given the timing of repayment and pawn recovery.
+Our estimated decrease in the financial cost of credit from above ignores discounting, but commitment up-front costs (early payment) in return for delayed benefits (recovery of pawn).
+Highly impatient individuals might therefore rationally choose the \emph{status quo} contract, despite the fact that commitment yields a benefit in raw (undiscounted) returns.
+To investigate this explanation we calculate the net present value (NPV) of the financial cost $\text{TUT}$ effect under different hypothetical discount rates, given the timing of repayment and pawn recovery.
 Figure \ref{fc_discount_rates} presents the results of this exercise.
-We see that non-choosers continue to experience significant decreases in NPV financial costs up to annual discount rates of 4,000\%, and the NPV remains negative, although not significant, at 10,000\% discount rates.
+The solid line gives the adjusted TUT effect at a specified annual discount rate, while the shaded region \hl{regions? what's the second one?} gives the associated \hl{XXXX} confidence interval.
+We see that non-choosers continue to experience significant decreases in NPV financial costs up to annual discount rates of 4,000\%, and the NPV remains positive, although not significant, at 10,000\% discount rates.
 As such, discounting is unlikely to explain why those who benefit, on average, from commitment fail to choose it when offered.
@@
 \paragraph{Survey Data.}
-The remaining exercises in the paper require information from the intake survey, and hence use only the subset of individuals who responded to the survey. 
-Table \label{SS_cond_survet} presents information about survey non-response.
+The remaining exercises in the paper require information from the intake survey, and hence restrict attention to the subset of individuals who responded to the survey. 
+Table \ref{SS_cond_survet} presents information about survey non-response.
 Panel A is a balance table that compares loan amount and day of the week across treatment arms for the subset of borrowers who responded to \hl{at least one survey question}.
-The p-values in the fourth column are for the F-test of no difference of means across teratment arms. 
-Panel B presents response-rates by question for each arm of the experiment, along with p-values for the F-test of no difference in question-specific response rate across treatment arms. 
-While this is a selected sample, estimates of the ATE, TOT, and TUT are nearly identical whether computed from the full sample survey-respondent sub-sample.
-In exercises that rely on one survey question, we use the full sample of borrowers who answered that question.
-In the random forest exercises that follow, we use data for every borrower who answered at least one survey question.
-
-%\todo[inline]{@Issac: do we have a table of TOT/TUT/ATE results for the sub-sample of survey respondents?
-We should add this as Table OA-2.
-What should we take as our sub-sample?
-We'd like to have this for people who answered \emph{at least} one survey question since those are the people who appear in our random forest exercises.
-We'd also like to have it for people who answered the time inconsistency question, and for people who answered the sure confidence question.
-(Each as a separate number)}
+The p-values in the fourth column are for the F-test of no difference of means across treatment arms. 
+Panel B presents response-rates by question for each arm of the experiment, along with p-values for the F-test of no difference in question-specific response rates across treatment arms. 
+This panel uses data from participants who answered \hl{at least one survey question} and went on to pawn on the same day as their survey response.
+From the table, we see that loan amount and weekday are balanced across treatment arms among survey respondents and that response rates are stable across treatment arms.
+Table \ref{TUT_cond_survet} shows how the estimated TUT effect changes when restrict our estimation sample based on survey response.
+The first row of the table presents TUT results for the financial cost outcome, while the second present TUT results for the APR outcome.
+In each row, column (1) presents the full-sample TUT estimate and standard error.
+The remaining columns restrict the sample to borrowers who answered a particular survey question or set of questions.
+For example, column (4) presents results for borrowers who answered the two questions needed to compute our measure of ``present bias'' discussed in the next paragraph, while column (9) present results restricted to participants who disclosed their sex.
+As seen from the table, our TUT estimates are quite stable across sub-samples defined by survey response.
+In each case they are positive and of the same magnitude as the corresponding full-sample estimate, although statistical significance varies depending on the size of the corresponding sub-sample. 
+For these reasons, we are comfortable relying on data for survey respondents in the empirical exercises that follow.
+In exercises that rely on a single survey question, we use data for every borrower who answered that question.
+In the random forest exercises described below, we use data for every borrower who answered at least one survey question.
 
@@
 Our baseline survey included standard questions about discount rates between today and a month in the future versus discount rates between three and four months in the future.\footnote{The remaining exercises in the paper require information from the intake survey, and hence use only the subset of individuals who responded to the survey.
-While this is a selected sample, estimates of the ATE, TOT, and TUT are nearly identical whether computed from the full sample survey-respondent sub-sample.}  This allows us to classify borrowers who display more impatience over immediate delays as time inconsistent.
+While this is a selected sample, estimates of the ATE, TOT, and TUT are nearly identical whether computed from the full sample survey-respondent sub-sample.}  This allows us to classify borrowers who display more impatience over immediate delays as present biased.
 This measure of financial hyperbolicity is widely used in survey research, although it is not without problems.\footnote{Our measure is dichotomous, and it is not incentivized.
@@
 
-If we could perfectly measure hyperbolicity, we could divide the sample into three groups: sophisticated hyperbolics who chose commitment, time-consistent non-choosers for whom forcing will not be effective, and naive hyperbolic non-choosers for whom it will.
-If hyperbolic discounting fully explains the low take-up rate of voluntary commitment, this would imply that the forcing effect should arise entirely from hyperbolic non-choosers.
-If our survey measure divides borrowers into the correct groups, this implication can be checked by estimating the $\text{TUT}$ conditional on hyperbolicity.
-
-\todo[inline]{Among people who answer part of the survey, not all of them answer both the sure confidence and time inconsistency questions.
-In each of the two exercises below, we use the full sample of people who answered the relevant question.
-This means that the ``overall'' TUT for each exercise, namely the TUT that we decompose, could be different.
-Need to think about how to present / discuss this.}
-
-\todo[inline]{We decided to make a picture.
-The picture will show the overall TUT (for a given survey respondent sub-sample), along with the TUT for $X=0$ and $X = 1$, with SEs for the latter two.
-The distance from the overall to each ``endpoint'' encodes the share of each group.
-We want to see if, e.g.\ the $X=1$ group is above the overall TUT while the $X=0$ group is below and indistinguishable from zero.}
-
-\todo[inline]{There are two exercises, and we'll do each one in the same way: present bias and sure confidence.
+If we could perfectly measure present bias, we could divide the sample into three groups: sophisticated hyperbolics (who chose commitment), time-consistent non-choosers (for whom forcing will not be effective), and naive hyperbolic non-choosers (who will benefit from forced commitment).
+If present bias fully explains the low take-up rate of voluntary commitment, we should find that the TUT for present-biased borrowers is positive while the TUT for all other borrowers is not.
+This is because TUT effects already restrict attention to borrowers who would not choose commitment.
+Within this group, a comparison of present-biased borrowers against everyone else is a comparison of na\"{i}ve hyperbolics against time-consistent non-choosers.
+The right panel of Figure \ref{tut_beh_partition} carries out a feasible version of this exercise using our survey measure of present bias.
+The overall TUT estimate for all borrowers who answered the present-bias questions is given in blue, along with a \hl{95?} confidence interval.
+The corresponding TUT estimate and confidence interval for present-biased borrowers is given in green, while TUT estimate and confidence interval for all other borrowers is given in red.
+All three estimates are positive and similar in magnitude, although imprecisely estimated given survey non-response.
+Taking our survey measure of present-vias at face value, we find no indication that present-bias explains our positive estimated TUT.
+
+%\todo[inline]{There are two exercises, and we'll do each one in the same way: present bias and sure confidence.
 In each case, there's a binary indicator that creates two groups.
@@
 
-\todo[inline]{This stuff needs to be removed / updated / edited based on the todos listed above.}
-For any binary pre-treatment covariate $X_i$, we can calculate the relative contributions of any two groups $X_i=0$ or $X_i=1$ to the overall $\text{TUT}$ effect using the following decomposition: 
-\begin{align}
-\nonumber
-        1=& \frac{\mathbbm{E}[Y_{1i}-Y_{0i} | C_i=0, X_i=1]}{\text{TUT}}\mathbbm{P}(X_i=1 | C_i=0) \\
-        \quad &+ \frac{\mathbbm{E}[Y_{1i}-Y_{0i}| C_i=0, X_i=0]}{\text{TUT}}\mathbbm{P}(X_i=0 | C_i=0)
-        \label{eq:decomp}
-\end{align}
-where $\text{TUT}$ is the \emph{overall} treatment on the untreated effect and $\mathbbm{E}[Y_{1i} - Y_{0i}|C_i = 0, X_i = x]$ is the TUT for borrowers with $X_i = x$.    
-If, as the behavioral theory outlined above would predict, the $\text{TUT}$ arises solely from hyperbolics then term with $X_i=1$ the former term will be one and the term with $X_i = 0$ will be zero. 
-We explore the empirical support for explanation below.
-But first we consider a second potential behavioral explanation.
+%\todo[inline]{This stuff needs to be removed / updated / edited based on the todos listed above.}
+%For any binary pre-treatment covariate $X_i$, we can calculate the relative contributions of any two groups $X_i=0$ or $X_i=1$ to the overall $\text{TUT}$ effect using the following decomposition: 
+%\begin{align}
+%\nonumber
+%        1=& \frac{\mathbbm{E}[Y_{1i}-Y_{0i} | C_i=0, X_i=1]}{\text{TUT}}\mathbbm{P}(X_i=1 | C_i=0) \\
+%        \quad &+ \frac{\mathbbm{E}[Y_{1i}-Y_{0i}| C_i=0, X_i=0]}{\text{TUT}}\mathbbm{P}(X_i=0 | C_i=0)
+%        \label{eq:decomp}
+%\end{align}
+%where $\text{TUT}$ is the \emph{overall} treatment on the untreated effect and $\mathbbm{E}[Y_{1i} - Y_{0i}|C_i = 0, X_i = x]$ is the TUT for borrowers with $X_i = x$.    
+%If, as the behavioral theory outlined above would predict, the $\text{TUT}$ arises solely from hyperbolics then term with $X_i=1$ the former term will be one and the term with $X_i = 0$ will be zero.
+%We explore the empirical support for explanation below.
+%But first we consider a second potential behavioral explanation.
 

### 2023-08-26 OA.tex
tot_tut_validity & edits to the main paper

@@
 
-\subsection{Survey}
-
-\afterpage{
+\newpage
+\subsection{Survey}   \label{app:survey_data}
+
+\vspace{.2in}
+
+\normalsize
+\linespread{1.25}
+%Really force it to normal size and linespread
+\normalsize
+\linespread{1.25}
+
+We now present analysis of the extent to which the survey-responding sample is representative and balanced.
+Table \ref{SS_cond_survet} presents information about survey non-response.
+Panel A is a balance table that compares loan amount and day of the week across treatment arms for the subset of borrowers who responded to at least one survey question.
+The p-values in the fourth column are for the F-test of no difference of means across treatment arms. 
+Panel B presents response-rates by question for each arm of the experiment, along with p-values for the F-test of no difference in question-specific response rates across treatment arms. 
+This panel uses data from participants who answered at least one survey question and went on to pawn on the same day as their survey response.
+From the table, we see that loan amount and weekday are balanced across treatment arms among survey respondents and that response rates are likewise stable across treatment arms.
+Table \ref{TUT_cond_survet} shows how the estimated TUT effect changes if we restrict our estimation sample based on survey response.
+The first row of the table presents TUT results for the financial cost outcome, while the second presents corresponding results for the APR outcome.
+In each row, column (1) presents the full-sample TUT estimate and standard error while the remaining columns restrict the sample to borrowers who answered a particular survey question or set of questions.
+For example, column (4) presents results for borrowers who answered the two questions needed to compute our measure of ``present bias'' discussed in the next paragraph, while column (9) present results restricted to participants who disclosed their sex.
+As seen from the table, our TUT estimates are quite stable across sub-samples defined by survey response.
+In each case they are positive and of the same magnitude as the corresponding full-sample estimate, although statistical significance varies depending on the size of the corresponding sub-sample. 
+For these reasons, we are comfortable relying on data for survey respondents in the empirical exercises that follow.
+In exercises that rely on a single survey question, we use data for every borrower who answered that question.
+In the random forest exercises described below, we use data for every borrower who answered at least one survey question.
+
+\cleardoublepage
+
 \begin{table}[H]
@@
 \end{table}
-}
+
+\cleardoublepage
 
@@
 
-Panel A of this table presents the same information as Panel A of Table \ref{SS}, but restricts attention to the subsample of borrowers who answered \hl{at least one question???} in our baseline survey.
+Panel A of this table presents the same information as Panel A of Table \ref{SS}, but restricts attention to the subsample of borrowers who answered at least one question in our baseline survey.
 Conditional on survey response, loan amount and weekday are balanced across treatment arms.
 Panel B presents response rates to each individual survey question across treatment arms, along with p-values for the F-test of no difference in response rates across survey arms.
-This panel uses data for borrowers who pawned on the \hl{same day as their survey response}.
+This panel uses data for borrowers who pawned on the same day as their survey response.
 
@@
  \scriptsize
+ An additional empirical issue generated by repeat pawning is the question of how to handle the treatment status of those who take multiple loans within the experiment.
+43\% of borrowers take more than one loan within the study period, and 19\% are assigned multiple treatment statuses on their different loans.
+The issue of sequential endogenous treatments has been extensively studied in the context of school lotteries, where the convention is to use the treatment status from the first exposure (ITT) \citep{cullen2006effect, abdulkadirouglu2011accountability}.\\
+
+ This table provides robustness for our main results for different ways to handling the multiplicity of loans.
+Columns 1-4 repeat the main analysis of financial cost and APR using the baseline approach from our main results,i.e.
+it only considers the first visit, while allowing multiple loans for the same-day.
+Columns 5-8 considers all loans including dummies for the order of pawns for an individual, essentially making the identification within-order.
+Columns 9-12 pursue the ITT strategy of always assigning the first treatment status to all subsequent pawns.
+The core treatment effects are robust to any of these ways of handling repeat pawning.
+
 %\textit{Do file: } \texttt{multiple\_loans.do}
@@
 
-\todo[inline]{For Isaac to write the note.}
 \end{landscape}
 
+\begin{figure}[H]
+    \caption{Determinants of choice}
+    \label{determinants_choose}
+    \begin{center}
+    \begin{subfigure}{0.75\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/determinants_choose_commitment.pdf}
+    \end{subfigure}
+    \end{center}
+      \scriptsize
+
+      The above figure shows the determinants in a bivariate and multivariate OLS regression of choosing commitment.
+Choice commitment is a binary variable equal to one, whenever subjects choose the forced commitment contract in the choice arm.
+%\textit{Do file: } \texttt{determinants_choice_sure_confidence.do}       
+\end{figure}
+
+\vspace{.2in}
+\begin{figure}[H]
+    \caption{Histogram of payments}
+    \label{hist_payments}
+    \begin{center}
+    \begin{subfigure}{0.45\textwidth}
+        \caption{Status-quo}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_payments_sq.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.45\textwidth}
+        \caption{Forced commitment}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_payments_fc.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.45\textwidth}
+        \caption{Choice commitment}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_payments_cc.pdf}
+    \end{subfigure}    
+    \end{center}
+     \scriptsize
+     This figure shows the schedule of payments for each treatment arm.
+In other words it records the time after the loan origination when the borrower makes a payment toward recovery of the pawn.
+We can see that for both the Forced commitment and Choice commitment arm, payments are bunching at the 30 and 60 days, while most payments are done around the due date of the loan (90 days).
+
+      %\footnotesize{ \textit{Do file: }  \texttt{hist\_payments.do}}
+\end{figure}
+
+\cleardoublepage
+
 \subsection{Censoring} \label{App_censoring}
@@
 \vspace{.2in}
+
 \normalsize
+\linespread{1.25}
+%Really force it to normal size and linespread
+\normalsize
+\linespread{1.25}
 
 Some loans in our sample are ``censored'' in that they continue beyond our observation period.
-For these loans, we do not know whether the borrower ultimately defaulted our recovered her pawn.
+For these loans, we do not know whether the borrower ultimately defaulted or recovered her pawn.
 In this appendix, we show that our main results are robust to different ways of addressing censoring.
 
-Our main results, presented above, assumed that all loans that were still outstanding at the end of the sample period were \emph{eventually repaid}.
-Because forced commitment causes borrowers to make payments earlier than they otherwise would have, this is a conservative assumption.
+Our main results, presented above, make no assumption on the default/recovery status of this loans.
+However, we compute the Financial Cost \& APR considering all the payments done so far.
+We now consider some alternative approaches.
+\\
+
+One way of considering the effect that this issue could have on our results is to make extreme assumptions about the outcome of these loans in the treatment and control so as to bound the possible influence of censoring.
+In Table \ref{bounding_censoring} we compare the Forced and Control arms, making the bracketing assumptions about repayment on censored loans.
+Panel A assumes all censored loans are repaid, and Panel D that all default.
+Because forced commitment causes borrowers to make payments earlier than they otherwise would have, In Panel A we make a conservative assumption.
 To see why, suppose for the sake of argument that commitment affects payment timing, but does not not default.
@@
 If we were to treat all outstanding loans as defaults--the opposite of our convention--this would artificially inflate the rate of default among control loans relative to treatment loans.
-This is why we adopt the reverse convention above.
-We now consider some alternative approaches.
-
-\todo[inline]{@Frank: keep updating below after getting responses from @Issac.}
-
-%The approach taken in the paper for censored loans is a conservative one in that it inherently assumes that all of the loans outstanding at the end of the observation window will be repaid, making it so that the acceleration of payment observed in the Forced arm does not translate mechanically into a treatment effect on default.
-This appendix delves into it more detail.
-
-One way of considering the effect that this issue could have on our results is to make extreme assumptions about the outcome of these loans in the treatment and control so as to bound the possible influence of censoring.
-In Table \ref{bounding_censoring} we compare the Forced and Control arms, making the bracketing assumptions about repayment on censored loans.
-Panel A assumes all censored loans are repaid, and Panel D that all default.
+
 Panel B provides the lower bound for the treatment effect by assuming censored control loans are always repaid and treatment loans never are, and Panel C the upper bound by making the reverse assumption.
@@
 
-Finally, Panel E of this table conducts a logit prediction model that uses all of the available information on loans that were completed to predict the outcome of loans that were not.
+Finally, Panel E of this table conducts a lasso logit prediction model that uses all of the available information on loans that were completed to predict the outcome of loans that were not.
 This is a best guess of the outcome on censored loans.
-Using this prediction, we replicate the main experimental results and find that the treatment effect on financial cost increases from -378 (main results) to -525 (censored loans predicted), and the APR from -34\% to -62\%.
+Using this prediction, we replicate the main experimental results and find that the treatment effect on financial cost increases from -378 (main results) to -530 (censored loans predicted), and the APR from -34\% to -62\%.
 Hence, while the censoring issue does have a substantial influence on the magnitude of our estimated treatment effects, these  checks confirm that a) the core results are robust to censoring, and b) the headline approach that we take to the issue is conservative and is likely understating the true magnitude of impacts.
@@
 \end{center}
+
+\end{table}
  \scriptsize 
- \todo[inline]{For Isaac to write the note}
-%\textit{Do file: } \texttt{censoring_imp.do, censoring_imp_pr.do}
-\end{table}
+ Given the censored loans, i.e.
+loans that have not finished by the end of the observation period, we estimate `a la Manski' bounds for these loans, meaning that we impute all loans to either \emph{default}$=1$ or \emph{recovery}$=0$ depending on the treatment arm.
+Different panels perform different imputations for the censored loans for all possible combinations for the imputation, and computes the ATE for the same outcomes of Table \ref{main_impact_table}.
+Panel A, for instance, assumes that all outstanding loans are fully payed.
+Panel B is the most conservative imputation since it assumes all outstanding loans in the control arm are payed, while all the outstanding loans in the forced commitment arm default.
+Panel C, on the other hand, is the most optimistic scenario opposite to that of Panel B.
+Panel D assumes all remaining loans default.
+The last panel makes the imputation to the censored loans according to the best prediction using a piecewise lasso logit model for default.
+In concrete, we build two logit models with lasso regularization, depending whether the loan duration is less than 220 days (two cycles) or more than 220 days.
+For prediction we use the former whenever the last recorded payment was done within 220 days, and the latter otherwise.
+Both models includes loan characteristics (loan size, branch), and payment behavior (loan duration so far, days to first payment, \% of first payment, \% of payments at 30, 60, 90, and 105 days, and \% of interest payed at 105 days), but the latter model also includes \% of payments at 150, 180, and 210 days.
+This predictive model achieves an accuracy rate of 92\% both in-sample and out-of-sample.
+
+ Note that in all panels we maintain significant results for Financial Cost as dependent variable, while only in the most conservative scenario (Panel B) we lose significance for the APR outcome.
 
@@
    \begin{subfigure}{0.49\textwidth}
+   \caption{Significance area for APR}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/frontera_sig_apr.pdf}
+    \end{subfigure}     
+    \begin{subfigure}{0.49\textwidth}
    \caption{Significance area for Default }
@@
         \includegraphics[width=\textwidth]{Figuras/frontera_sig_def_imp.pdf}
-    \end{subfigure} 
-   \begin{subfigure}{0.49\textwidth}
-   \caption{Significance area for APR}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/frontera_sig_apr.pdf}
     \end{subfigure} 
@@
 Each corner in the square will correspond to one of the panels from the Table \ref{bounding_censoring}.
-For instance, the origin is the best-case scenario (Panel C) and the point (100,100) (Panel D) is the worst-case scenario.
+For instance, the origin is the best-case scenario (Panel C) and the point (100,100) (Panel B) is the worst-case scenario.
 Thus we can think of this graph as an `interpolation' from the four extreme cases.
-The `x' indicates the proportions imputed by the lasso-logit model, and the different lines correspond to setting different significance levels.
-
-     %\textit{Do file: }  \texttt{interpolation_{censoring_imp.do}
+The `x' indicates the proportions imputed by the lasso logit model, and the different lines correspond to setting different significance levels.
+We do not include the plot for financial cost, since for any imputation we still have significant results.
+
+     %\textit{Do file: }  \texttt{interpolation_censoring_imp.do}
 \end{figure}
@@
 The discount factor reflects time preference, i.e.\ the fact that payments made in the present are more costly for the borrower.
-At a given annual discount rate in percentage points (x-axis) the solid line gives the adjusted TUT and the shaded regions \hl{???
-confidence intervals}.
+At a given annual discount rate in percentage points (x-axis) the solid line gives the adjusted TUT and the shaded regions 90\% \& 95\% confidence bands.
 A discount factor of one corresponds to the estimate from Table \ref{tot_tut}.
@@
 \vspace{.3in}
-\subsection{Sure confidence and present bias}
-
-\begin{figure}[H]
-    \caption{Partition of TUT by behavioral variables.}
-    \label{tut_beh_partition}
-    \begin{center}
-        \centering
-        \includegraphics[width=0.55\textwidth]{Figuras/tut_beh_partition.pdf} 
-    \end{center}
-     \scriptsize  Each panel in this figure shows how the estimated treatment on the untreated (TUT) effect varies with a binary survey variable $X_i$.
-In the left panel (Sure-confidence) $X_i = 1$ if  borrower $i$ reported that she was certain to recover her pawn, zero otherwise.
-In the right panel (P.B.), $X_i = 1$ if borrower $i$ is ``present-biased'' based on her responses to the time preference questions from our survey.
-Each panel depicts three estimates and associated \hl{standard errors???
-95 CI?}: the overall TUT (blue), the TUT for borrowers with $X = 1$ (green), and the TUT for borrowers with $X = 0$ (red).
-By the law of iterated expectations, the overall TUT in each panel must lie between the group-specific TUTs.
-The overall TUT is slightly different in each panel, because some borrowers only completed part of the survey.
-In each panel, we present results for the full set of borrowers who answered the survey question or questions needed to determine $X_i$.
-From the right panel, we see that TUT does not appear to vary with present bias.
-In contrast, the left panel suggests that the positive and significant overall TUT is driven by individuals who are ``sure-confident,'' i.e.\ borrowers who report that they are certain to recover their pawn.
-     %to be largely concentrated relevant survey question  according to her survey responses two binary performs a partition of the Treatment on the Untreated (FC), estimating the share of the effect that arises within each of two binary categories.
-The top bars examine present bias (individuals are more impatient over one-month time horizon than they are between three and four months).
-The bottom bars examine sure confidence (individual reports 100\% probability of repaying at time of taking loan).
-Blue bar is the component arising from those without the trait, orange bar from those with the trait.
-      %\footnotesize{ \textit{Do file: }  \texttt{partition_tut.do}
-
-      \todo[inline]{This figure has changed. Will have minor style modifications. @Issac: what's the purple stuff in the middle?}
-\end{figure}
-
-\vspace{.3in}
 \subsection{First order stochastic dominance} \label{App_FOSD}
@@
        \begin{subfigure}{0.49\textwidth}
-        \caption{APR}
+        \caption{APR benefit}
         \centering
@@
    \begin{subfigure}{0.49\textwidth}
-        \caption{Financial cost}
+        \caption{Financial benefit}
         \centering
@@
     \scriptsize This figure plots plots the empirical CDF of experimental outcomes separately for the control / status quo (dashed) and forced commitment contracts (solid).
-In panel (a), the outcome is APR; in panel (b) the outcome is Financial Cost.
+In panel (a), the outcome is APR benefit; in panel (b) the outcome is Financial benefit.
 In each case, the empirical CDF under forced commitment first-order stochastically dominates the empirical CDF under the status quo.
 This can be seen by examining the dotted line at the bottom of panels (a) and (b), which shows the difference $(\text{Control} - \text{Commitment})$.
+    %The dotted line at the bottom of panels (a) and (b)   the empirical cumulative distribution function APR and financial cost of financial cost.
+It does this separately for the fee-forcing contract and for the status-quo contract.
+The dotted line at the bottom is the difference of the control CDF minus the forced CDF arm.
+It shows that the CDF of the status quo contract is always below that of the fee-forcing (and this difference is significant for the points indicated by the blue line).
+    % \texttt{fosd_ecdf.do}}
+\end{figure}
+
+\cleardoublepage
+
+\begin{figure}[H]
+        \caption{Distribution of treatment effects under rank invariance.}
+    \label{te_rankinvariance}
+
+    \begin{center}
+       \begin{subfigure}{0.49\textwidth}
+        \caption{APR benefit}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/te_rankinvariance_apr.pdf}
+    \end{subfigure} 
+   \begin{subfigure}{0.49\textwidth}
+        \caption{Financial benefit}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/te_rankinvariance_fc_admin.pdf}
+    \end{subfigure} 
+    \end{center}
+    \scriptsize This figure show the distribution of treatment effects under rank invariance
+    \[F_\Delta(\delta) = \int_0^1 \mathbbm{1}\{ F_1^{-1}(u) - F_0^{-1}(u)\leq \delta\}\,\mathrm{d}u\]
+where $F_1^{-1}$ and $F_0^{-1}$ are the quantile functions of $Y_1$ and $Y_0$.
     %The dotted line at the bottom of panels (a) and (b)   the empirical cumulative distribution function APR and financial cost of financial cost.
@@
 
-%Are we using any tables/figures after this point?
+\begin{figure}[H]
+    \caption{Determinants sure confidence}
+    \label{determinants_sure}
+    \begin{center}
+    \begin{subfigure}{0.75\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/determinants_confidence_100.pdf}
+    \end{subfigure}
+    \end{center}
+      \scriptsize
+
+      The above figure shows the determinants in a bivariate and multivariate OLS regression of sure confidence among the non-choosers.
+Sure confidence is a binary variable defined to be one when people report a 100\% probability of recovery.
+%\textit{Do file: } \texttt{determinants_choice_sure_confidence.do}       
+\end{figure}
 
@@
 This avoids inferential problems that could arise from correlated unobservables within clusters.
-In the first step, we apply the generalized random forest approach of \cite{athey2019generalized} to the training set to estimate two proxy predictors: $\psi(\cdot|\text{Training})$ approximates the untreated potential outcome function, $\mathbbm{E}[Y_{i0}|X_i] = \mathbbm{E}[Y_i|Z_i=0,X_i]$, while  $\tau(\cdot|\text{Training})$, approximates the ATE function
+In the first step, we apply the generalized random forest approach of \cite{atheygrf} to the training set to estimate two proxy predictors: $\psi(\cdot|\text{Training})$ approximates the untreated potential outcome function, $\mathbbm{E}[Y_{i0}|X_i] = \mathbbm{E}[Y_i|Z_i=0,X_i]$, while  $\tau(\cdot|\text{Training})$, approximates the ATE function
 \[
@@
 Since $\tau_i$ and $\psi_i$ do not depend on the test set, inference for the regression in \eqref{eq:chernreg} is straightforward conditional on the Training/Test split.  
-Our estimate for $\beta_2$ is \hl{XXXX} with a cluster-robust standard error of \hl{XXXX}.
-Thus we easily reject the null hypothesis of homogenous treatment effects.
+Our estimate for $\beta_2$ is 1.68 with a one-sided heteroskedasticity-robust (HC3) of 0.50.
+Thus we easily reject the null hypothesis of homogeneous treatment effects.
 
@@
 \subsection{Inference for ASG, ASB, and ASL}
+\label{subsec:inference}
 We now explain how to carry out cluster-robust inference for the ASG, ASB, and ASL effects, as implemented in our companion STATA package.
@@
 
-\todo[inline]{@Issac: Presumably the numerical results and sentence that follows it need to be updated now that we've changed how we deal with censoring etc, yes?
-Which outcome are we looking at here}
+\todo[inline]{Add exercise about falsification of exclusion that Frank suggested.}
 The \cite{huber_mellace} bounds for the TOT \& TUT APR are respectively:
-\[\text{TOT} : [-481.8, 483.7]\quad\quad\quad\text{TUT} : [-17.9, 90.6]\]
-
-Because the Note that since both TUT and ToT estimates from the LATE approach lies inside these bounds, we do not falsify the exclusion restriction.
+\[\text{TOT} : [-366, 490]\quad\quad\quad\text{TUT} : [-19, 109]\]
+
+Since both TUT (24) and ToT (121) estimates from the LATE approach lies inside these bounds, we cannot falsify the exclusion restriction.
 
@@
 
-\begin{figure}[H]
-     \caption{Exclusion restriction}
-     \label{exclusion_restriction}
-    \begin{center}
-    \begin{subfigure}{0.6\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/exclusion_restriction.pdf}
-    \end{subfigure}
-    \end{center}
-    \scriptsize This figure serves as a test for the exclusion restriction in the point identification for the TOT and the TUT.
+% \begin{figure}[H]
+%      \caption{Exclusion restriction}
+%      \label{exclusion_restriction}
+%     \begin{center}
+%     \begin{subfigure}{0.6\textwidth}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/exclusion_restriction.pdf}
+%     \end{subfigure}
+%     \end{center}
+%     \scriptsize This figure serves as a test for the exclusion restriction in the point identification for the TOT and the TUT.
 It shows the effect on the effective cost/loan ratio for the forced-fee arm and the choice arm, together with the decomposition of the choosers and non-choosers.
@@
 
-          %\footnotesize{ \textit{Do file: }  \texttt{exclusion\_restriction.do}}
-\end{figure}
+%           %\footnotesize{ \textit{Do file: }  \texttt{exclusion\_restriction.do}}
+% \end{figure}
 
@@
 
-\cleardoublepage
-
-\vspace{.3in}
 \begin{figure}[H]
-     \caption{Heterogeneous Treatment Effects}
-    \label{heterogeneous_effects}
-    \begin{center}
-    \begin{subfigure}{.45\textwidth}
-      \caption{Financial cost (in MXN)}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/he_dist_fc_admin.pdf}
-    \end{subfigure}
-     \begin{subfigure}{0.45\textwidth}
-    \caption{Effective APR}
-       \centering
-      \includegraphics[width=\textwidth]{Figuras/he_dist_eff.pdf}
-    \end{subfigure}
-     \begin{subfigure}{0.45\textwidth}
-    \caption{Default}
-       \centering
-      \includegraphics[width=\textwidth]{Figuras/he_dist_def.pdf}
-    \end{subfigure}  
-     \begin{subfigure}{0.45\textwidth}
-    \caption{Recovery}
-       \centering
-      \includegraphics[width=\textwidth]{Figuras/he_dist_des.pdf}
-    \end{subfigure}      
-    \end{center}
-         \scriptsize
-     This Figure plots the densities of the CATE emerging from the Athey et al. (2019) random forest, along with the upper and lower confidence bounds.  
-  %\footnotesize{ } \textit{Do file: }  \texttt{cate_dist.do}
-\end{figure}
-
-\begin{figure}[H]
-        \caption{Honest causal tree for the Forced-commitment contract heterogeneous treatment effects}
+        \caption{Example Causal Tree}
     \label{causal_tree1}
@@
     \footnotesize 
-    This is one(it is chosen such that it minimizes the pruned cost, that is it is the tree with the smallest root-node impurity) of the honest causal trees in the random forest we use for the estimation of the heterogeneous treatment effect of the fee-forcing contract.
+    This figure shows an example of one of the regression trees used to compute the causal forest estimates described in Section \ref{sec:RF}.
+Each tree is constructed from a sequence of recursive binary partitions of the covariate space, with a splitting rule that is targeted to the causal quantity of interest, following the methodology of \cite{atheygrf}.
+    %This is one(it is chosen such that it minimizes the pruned cost, that is it is the tree with the smallest root-node impurity) of the honest causal trees in the random forest we use for the estimation of the heterogeneous treatment effect of the fee-forcing contract.
 It is meant only as an example of how these trees look like.
@@
 
-We use \cite{atheygrf} \texttt{causal\_forest} of the \texttt{grf} library in $R$. The parameters used were:
-\scriptsize{\textit{causal\_forest(
-  X, 
-  Y, 
-  W, 
-  Y.hat = NULL, 
-  W.hat = NULL, 
-  num.trees = 2000, 
-  sample.weights = NULL, 
-  clusters = NULL, 
-  equalize.cluster.weights = FALSE, 
-  sample.fraction = 0.5, 
-  mtry = min(ceiling(sqrt(ncol(X)) + 20),ncol(X)), 
-  min.node.size = 5, 
-  honesty = TRUE, 
-  honesty.fraction = 0.5, 
-  honesty.prune.leaves = TRUE, 
-  alpha = 0.05, 
-  imbalance.penalty = 0, 
-  stabilize.splits = TRUE, 
-  ci.group.size = 2, 
-  tune.parameters = "none", 
-  tune.num.trees = 200, 
-  tune.num.reps = 50, 
-  tune.num.draws = 1000, 
-  compute.oob.predictions = TRUE, 
-  orthog.boosting = FALSE, 
-  num.threads = NULL)}}
+%We use \cite{atheygrf} \texttt{causal\_forest} of the \texttt{grf} library in $R$. The parameters used were:
+%\scriptsize{\textit{causal\_forest(
+%  X, 
+%  Y, 
+%  W, 
+%  Y.hat = NULL,
+%    W.hat = NULL,
+%    clusters = NULL,
+%    num.trees = 5000,
+%    sample.weights = NULL,
+%    equalize.cluster.weights = FALSE,
+%    sample.fraction = 0.5,
+%    mtry = min(ceiling(sqrt(ncol(X)) + 20), ncol(X)),
+%    min.node.size = 5,
+%    honesty = TRUE,
+%    honesty.fraction = 0.5,
+%    honesty.prune.leaves = TRUE,
+%    alpha = 0.05,
+%    imbalance.penalty = 0,
+%    stabilize.splits = TRUE,
+%    ci.group.size = 2,
+%    tune.parameters = c("alpha", "imbalance.penalty"),
+%    tune.num.trees = 500,
+%    tune.num.reps = 200,
+%    tune.num.draws = 2000,
+%    compute.oob.predictions = TRUE,
+%    num.threads = NULL,
+%    seed = 1)}}
 
@@
 \vspace{.3in}
-\begin{table}[H]
-\caption{Type I \& II errors using targeting narrow rules}
-\label{hit_miss_rule}
-\begin{center}
-\resizebox{0.95\textwidth}{!}{
-\small{\input{./Tables/hit_miss_rule.tex}}
-}
-\end{center}
-\scriptsize This table reports on the incidence of Type I and Type II error in different rules for allocating individuals to commitment.
-The first row allocates all units to control which, according to the `wide' RF estimation, results in 87\% of individuals losing by not receiving commitment.
-The second row is the Forcing arm, which has the mirror image errors.
-The third row considers the optimal case in which each individual receives the correct treatment.
-The fourth row uses the `narrow' RF to allocate, such that all individuals on a leaf for which the CATE of commitment is positive are assigned to treatment.
-The fifth row uses a Logit to estimate the propensity to benefit from treatment, and assigns such that the fraction allocated to treatment matches the correct sample fraction that benefit.
-\end{table}
 
@@
 
-\subsection{Selection on gains}
-
-\begin{figure}[H]
-    \caption{Determinants of treatment effects and probability of choosing commitment}
-    \label{determinants_ps_hte}
-    \begin{center}
-    \begin{subfigure}{0.65\textwidth}
-        \caption{Determinants of HTE}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/HE/he_int_vertical_apr_pro_2.pdf}
-    \end{subfigure}
-    %\begin{subfigure}{0.475\textwidth}
-    %    \caption{Determinants of propensity score}
+%\subsection{Selection on gains}
+
+%\begin{figure}[H]
+%    \caption{Determinants of treatment effects}
+%    \label{determinants_cate}
+%    \begin{center}
+%    \begin{subfigure}{0.65\textwidth}
+%        \caption{Determinants of CATE}
 %        \centering
-    %    \includegraphics[width=\textwidth]{Figuras/HE/ps_int_vertical_pr_gbc_1.pdf}
-    %\end{subfigure}
-
-    \end{center}
-     \scriptsize   This figure estimates bivariate regressions of the estimated client-level (a) heterogeneous treatment effects, %(b) propensity score, against the respective covariate from the baseline survey  $\widehat{HTE_i}, \widehat{P_i} = \alpha + \beta \: X_i + \epsilon_i$.
-The regressors $X_i$ include (e.g if the family asks for money, if they have savings, if they are overconfident using the definition the text, etc.
-See this Appendix for a transcription of the survey).
-\\
-      %\footnotesize{ \textit{Do file: }  \texttt{analyze\_grf\_single\_arm.do}} \texttt{benefit\_choice.do}}
-\end{figure}
-\todo[inline]{@Isaac: reestimate this with the determinants we are using for the choice determinants. Based on that we decide if we cut}
+%        \includegraphics[width=\textwidth]{Figuras/blp_cate_apr.pdf}
+%    \end{subfigure}
+
+%    \end{center}
+%     \scriptsize   This figure estimates bivariate \& multivariate double-robust regressions of the estimated CATE of forcing.
+
+%\end{figure}
+%\todo[inline]{This is a figure that is not referenced yet in the paper, but there is a line highlighted in yellow that could use this information.
+While there appears to not be any effect, let's remember that the RF is considering nonlinear interactions between variables, as well as using information of missingness of some survey questions.}
 
@@
 
-\clearpage
-\bibliographystyle{authordate1}
+%\clearpage
+%\bibliographystyle{authordate1}
 %\bibliographystyle{amsalpha}
@@
 
-\bibliography{References}
+%\bibliography{References}
 

### 2023-08-26 donde.tex
tot_tut_validity & edits to the main paper

@@
 Jose Maria Barrero, Andrei Gomberg, Emilio Gutierrez, David Laibson, Aprajit Mahajan, Matt Rabin, Charlie Sprenger, and seminar participants at ITAM, USC, MSU, and UCSD provided valuable feedback.}}
-\author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira \and Francis J.\ DiTraglia   \thanks{Seira: ITAM/MSU, \url{enrique.seira@gmail.com} (corresponding author); McIntosh:  University of California San Diego, \url{ctmcintosh@ucsd.edu}; Meza: Harvard University, \url{isaacmezalopez@g.harvard.edu}; Sadka: ITAM, \url{jsadka@itam.mx}; DiTraglia: Oxford, \url{francis.ditraglia@economics.ox.ac.uk}} }
+\author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira \and Francis J.\ DiTraglia   \thanks{Seira:  MSU, \url{enrique.seira@gmail.com} (corresponding author); McIntosh:  University of California San Diego, \url{ctmcintosh@ucsd.edu}; Meza: Harvard University, \url{isaacmezalopez@g.harvard.edu}; Sadka: ITAM, \url{jsadka@itam.mx}; DiTraglia: Oxford, \url{francis.ditraglia@economics.ox.ac.uk}} }
 \date{This draft:  \today \\[2 cm]}
@@
 
-In the context of pawnbroker lending, we show that forcing people into commitment contracts with a regular repayment structure decreases their (fee-including) financial cost by 6\%, increases the likelihood of recovering their pawn by 15\%, and increases the likelihood of repeat business by 20\%.
-Using a multi-armed RCT that includes both a voluntary and a forced arm, we illustrate how to point-identify both the Treatment on the Untreated and the Treatment and the Treated.
+In the context of pawnbroker lending, we show that forcing people into commitment contracts with a regular repayment structure decreases their (fee-including) financial cost by 20\%, increases the likelihood of recovering their pawn by 15\%, and increases the likelihood of repeat business by 20\%.
+Using a multi-armed RCT that includes both a voluntary and a forced arm, we illustrate how to point-identify both the Treatment on the Untreated and the Treatment on the Treated.
 We find modest selection on gains but nonetheless significant positive benefits of commitment even for those who would not have chosen it.
-The justification for paternalistic commitment in this context appears to be over-optimism; 74\% of clients say they will certainly recover their pawn while in fact only 43\% do so.
+The justification for paternalistic commitment in this context appears to be over-optimism; 74\% of clients say they will certainly recover their pawn while in fact only 57\% do so.
 
@@
 %This is not a straightforward task because choice will be driven by unobservable factors, and to address the question fully
-Moreover, painting a complete picture of the benefits of forcing requires requires counterfactuals for both choosers and non-choosers.
-A large behavioral literature has illustrated that allowing borrowers or savers to choose commitment-style products increase savings in an intention-to-treat (ITT) sense \citep{thaler2004save, prina2015banking, brune2016facilitating, callen2019headwaters, Pascaline, Ashraf}, but this literature has rarely addressed the benefits of imposing commitment.\footnote{Selection on gains has such wide acceptance that economists often impose it in their models} (Although the examples above are plausible, substantiating a case for private paternalism is not easy.
+Moreover, painting a complete picture of the benefits of forcing requires counterfactuals for both choosers and non-choosers alike, since the differential benefit of forcing arises from impacts among those who do not freely choose commitment.
+While a large behavioral literature has illustrated that allowing borrowers or savers to choose commitment-style products increase savings in an intention-to-treat (ITT) sense \citep{thaler2004save, prina2015banking, brune2016facilitating, callen2019headwaters, Pascaline, Ashraf}, this literature has rarely addressed the benefits of imposing commitment or its differential impacts on those who would not independently choose commitment.
+%\footnote{Selection on gains has such wide acceptance that economists often impose it in their models} (Although the examples above are plausible, substantiating a case for private paternalism is not easy.
 It involves comparing the causal effect of forcing a certain product characteristic versus the effect of letting people choose on that characteristic.
@@
 A large behavioral literature has illustrated that allocating borrowers to a commitment-savings product increase savings \citep{thaler2004save, prina2015banking, brune2016facilitating, callen2019headwaters, Pascaline, Ashraf}, but this literature does not show that commitment would not be chosen by those that would benefit from it, that is, that the treatment effect on the untreated (TUT) is positive.
-In fact, selection on gains has such wide acceptance that economists often impose it in their models \hl{CITES}.
+Indeed, selection on gains has such wide acceptance that economists often impose it as a part of Roy models on topics as diverse as migration \citep{borjas1989economic}, job search \citep{lippman1976economics}, and program evaluation \citep{bjorklund1987estimation}.
 In microfinance, a context close to ours, \citep{Murdoch} claim that there exists positive selection, citing a positive correlation between displaying present biased preferences in surveys and selecting into microfinance as evidence of borrowers' actually demanding the discipline imposed by frequent payments.
@@
 Pawn loans are one of the oldest, most understudied, and most prevalent forms of borrowing \citep{carter2012pawnshops}.
-There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues (in China it is a \$43 billion industry).\footnote{\url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.} Our partner pawn lender (henceforth Lender $P$) alone served more than 1 million clients in the last 3 years with more than 4 million contracts.\footnote{For comparison there were 2.3 million micro-finance clients in Mexico in 2009 (\cite{Pedroza:2010}).} Pawnshop lending presents an inverted lending case: since these loans are over-capitalized, the principal in the lending contract stands to gain the most when agents default.
-
-Our collaborating pawn lender (henceforth Lender P) gave 70\% of the value of the pawn in credit, and charged a monthly interest rate of 7\% for loans of a three-month duration, with a flexible no-reminders contract typical of the industry that can be paid back anytime before the loan comes due at no penalty.
-This combination of features, and the fact that the gold pawn is highly liquid, means that the lender makes 90\% more profit over three months for a borrower who defaults than one who repays (30\% of collateral value recovered under default, 15.8\% of collateral value paid in interest if loan fully repaid).
-While an older literature considers the exploitative potential in over-collateralization and underpricing of collateral \citep{basu1984implicit}, the implication of such contracts has not been analyzed in the behavioral literature.
+There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues (in China it is a \$43 billion industry).\footnote{\url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.} Our partner pawn lender (henceforth Lender $P$) alone served more than 1 million clients in Mexico in the last 3 years with more than 4 million contracts.\footnote{For comparison there were 2.3 million micro-finance clients in Mexico in 2009 (\cite{Pedroza:2010}).} Pawnshop lending presents an inverted lending case: since these loans are over-capitalized, the lender in the contract stands to gain the most when borrowers default.
+
+Our partner's standard pawn contract gave 70\% of the value of gold collateral in credit, and charged a monthly interest rate of 7\% for loans of a three-month duration, with a flexible no-reminders contract typical of the industry that can be paid back anytime before the loan comes due at no penalty.
+This combination of features, and the fact that the gold pawn is highly liquid, means that the lender makes 90\% more profit over three months from a borrower who defaults than one who repays (30\% of collateral value recovered under default, 15.8\% of collateral value paid in interest if loan fully repaid).
+While an older literature considers the exploitative potential of over-collateralization and underpriced collateral \citep{basu1984implicit}, the implication of such contracts has not been analyzed in the behavioral literature.
 %When the lender desires default, the repayment-inducing features of commitment-style repayment contracts become undesirable and there may be incentives for the principal to create contracts with no structure, no reminders, and simple balloon payments.
@@
 Against this backdrop, we implement a multi-arm randomized control trial covering close to 10,000 pawnshop clients in 6 branches of Lender $P$ in Mexico City, using a design built to test the demand for and impact of alternative payment structures in pawn repayment contracts.
-Our control arm illustrates the costs of the status quo contract: fully 57\% of borrowers default and so lose their pawn.\footnote{These high default rates are not uncommon, in the US default is also high at 15\% (\url{https://tinyurl.com/yc2x5bjf}).} We then implement a ``commitment choice'' arm, in which borrowers can opt into a structured repayment contract at the time of taking a loan.
-The structured contract requires borrowers to make three monthly payments rather than one balloon payment at the end, with each monthly payment including the accrued interest at that time, a nominal fee of 2\% of that month's payment in case of delinquency.
+Our control arm illustrates the costs of the status quo contract: fully \emph{43\%} of borrowers default and so lose their pawn as well as any payments made towards principal.\footnote{These high default rates are not uncommon, in the US default is also high at 15\% (\url{https://tinyurl.com/yc2x5bjf}).} We then implement a ``commitment choice'' arm, in which borrowers can opt into a structured repayment contract at the time of taking a loan.
+The structured contract requires borrowers to make three monthly payments rather than one balloon payment at the end, with each monthly payment including the accrued interest at that time as well as a nominal fee of 2\% of that month's payment if that payment is delinquent.
 This fee serves as a reminder and a means of reinforcing the importance of these interim payments.
@@
 
-Our results suggest that the structure of the commitment is strongly effective in preventing default, with the average individual in the forced arm paying financing costs inclusive of fees that are \hl{20\%} lower than the control, while default decreases by 6.5 percentage points (15\% of the mean).
+Our results suggest that commitment is strongly effective in preventing default in pawnshop lending, with the average individual in the forced arm paying financing costs inclusive of fees that are 20\% lower than the control, while default decreases by 6.5 percentage points (15\% of the mean).
 In terms of Annual Percentage Rates, the financial cost of borrowing is reduced by 34 percentage points.
-That is, imposing commitment structure it is possible to save borrowers money by charging them fees!
-These results are robust qualitatively to including transport costs of going to the branch plus losing a day's wage for each visit, using the subjective instead of the gold value of the pawn, and imputing some adjustment for liquidity lost by requiring monthly payments.
-
-The monthly payment contract seems to be achieving these cost savings by speeding up payments and by generating an early bifurcation of borrowers into those that will recover the pawn and those that will not, saving the later payments towards recovery.
-In the treatment group, the first payment occurs 13 days earlier, the fraction recovering on the first visit by is 7.9 percentage point higher.
-Commitment contract decreases fraction of borrowers making a payment and not recovering by 7 percentage points.
-\hl{Treatment effects are concentrated in the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery.
-That is, the commitment contract induces people who would otherwise pay something towards recovery, to pay more and faster, making them more likely to recover their pawn at a lower financial cost.}
-
-In spite of a large average treatment effect documenting financial cost savings, given the opportunity in the choice arm, only 11\% of borrowers actually choose commitment.
-If the effect of commitment were homogeneous, this would be enough to conclude that the 89\%
-who did not choose it would have been financially better off if they had.
+That is, by imposing the structure of commitment it is possible to save borrowers money by charging them fees!
+These results are robust qualitatively to including transport costs of going to the branch plus losing a day's wage for each visit, using each borrower's subjective value of the pawn rather than the appraised value of the gold, and adjusting for lost liquidity from requiring monthly payments.
+
+The monthly payment contract seems to achieve these cost savings by speeding up payments and by generating an early bifurcation of borrowers into those that will recover the pawn and those that will not.
+By inducing borrowers either to fully recover or to default without making any payments it saves money that would otherwise have been paid towards loans that ultimately default, money which is lost to the borrower.
+In the treatment group, the first payment occurs 13 days earlier, and the fraction recovering on the first visit is 7.7 percentage points higher.
+Commitment contracts also decrease the fraction of borrowers who make a payment but ultimately fail to recover their pawn by 7 percentage points.
+Treatment effects are concentrated in the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery.
+That is, the commitment contract induces people who would otherwise pay something towards recovery but default to instead pay more and faster, making them more likely to recover their pawn at a lower financial cost.
+
+In spite of a large average treatment effect documenting financial cost savings, only 11\% of borrowers in the choice arm actually choose commitment.
+If the effect of commitment were homogeneous, this would be enough to conclude that the 89\% who did not choose it would have been financially better off if they had.
 However, we test and reject the null hypothesis of homogeneous treatment effects using the method of \cite{chernozhukov2018generic}.
 Can the borrowers who did not choose commitment be those who simply don’t need it?
-We address this question by sequentially imposing more structure in the problem.
-
-\hl{We start by bounding the distribution of treatment effects $Y_{1i}-Y_{0i}$ using the two marginal distribution } in the treatment and control arms as in \cite{fan2010sharp}.
-We find that at least 30\% of individual borrowers benefit from commitment, implying many borrowers did not demand even though the treatment effect would be positive for them.
-Then, we impose the mild exclusion restriction that the effect of the contract does not depend on how they got it, that is: choosing a contract has the same treatment effect as being assigned to the contract.\footnote{This is a frequently used assumption even if often implicit.
-For instance, a significant literature uses schooling compulsory laws to estimate the return of one more year of school, and then often interprets that schooling, in general, has this return.} We show that in this case our 3-armed experiment point identifies the TuT.
-We then estimate that the financial cost savings of the TuT is large, at \$356 pesos, equivalent to 24 percentage point savings in APR.
-That is, on average borrowers that did \textit{not} choose the frequent payment contract would have benefited from having that contract.\footnote{We estimate a positive TOT that is larger than the TuT, but it is imprecise\footnote{This results from the smaller sample size, given that few chose the monthly payment contract.}, and the hypothesis of TOT=TUT is rejeted only with 13 percent confidence for the APR and 12 percent confidence for default.}  We also estimate that those that would not choose if given the opportunity would have lower status-quo outcomes (i.e.
+We address this question by sequentially imposing more structure on the problem.
+
+We start our analysis of heterogeneity by bounding the distribution of treatment effects $Y_{1i}-Y_{0i}$ using the two marginal distributions in the treatment and control arms as in \cite{fan2010sharp}.
+We find that at least 24\% of individual borrowers benefit from commitment, implying many borrowers did not demand it even though their individual treatment effect is positive.
+Next, we impose the exclusion restriction that the effect of the contract does not depend on how they got it, that is: choosing a contract has the same treatment effect as being assigned to that contract.\footnote{This is a frequently used assumption even if often implicit.
+For instance, a significant literature uses schooling compulsory laws to estimate the return of one more year of school, and then often interprets that schooling, in general, has this return.} We show that in this case our 3-armed experiment point identifies the TUT.
+We then estimate that the financial cost savings of the TUT is large, at \$356 pesos, equivalent to 24 percentage point savings in APR.
+That is, on average borrowers that did \textit{not} choose the frequent payment contract would have benefited from having that contract.\footnote{We estimate a positive TOT that is larger than the TUT, but it is imprecise--this results from the smaller sample size, given that few chose the monthly payment contract--and the hypothesis of TOT=TUT is rejected only with 13 percent confidence for the APR and 12 percent confidence for default.}
+%We also estimate that those that would not choose if given the opportunity would have lower status-quo outcomes (i.e.
 the average selection bias is negative).
-Finally, assuming the exclusion restriction for subsets of observable characteristics splits generated by a causal forest allows us to establish that \hl{70\%} of would-be non-choosers would save on financial cost by being assigned to frequent payments.
+Finally, assuming the exclusion restriction for subsets of observable characteristics splits generated by a causal forest allows us to establish that 86\% of would-be non-choosers would save on financial cost by being assigned to frequent payments.
 That is, the benefits of imposing a monthly payment are distributed broadly.
 \hl{TuT benefits are particularly large for XXX CHARACTERISTICS, and TOT benefits for those with XXX.}
-
-\textcolor{brown}{In a final step, we use the Causal Random Forest algorithm of \cite{atheygrf} to estimate individual-level treatment effects for the forced versus control arm, and show the benefits of forcing to be significantly negatively correlated with the propensity to choose commitment estimated from the choice arm.
-93\% of those who did not opt for the commitment contract would have been better off with it, while only 1\% of those who chose commitment would have been better off without it.} \textcolor{blue}{Targeting frequent payment products to those that benefit the most is a policy that should be explored.
-In this context we calculate \hl{XXX}.}
+In a final step, we impose a selection-on-observables assumption and use the Causal Random Forest algorithm of \cite{atheygrf} to estimate conditional average treatment effects (both ATEs and TUTs) for the individual borrowers in our experiment.
+We estimate that 93\% of the borrowers who did not opt for the commitment contract have positive conditional TUT effects, while only 1\% of those who chose commitment have negative conditional TOT effects.
+While targeting commitment products to those that benefit the most is a policy that appears attractive, in this context we find that the usable targeting variables have relatively weak predictive power and hence even the random forest only reduces the overall mis-targeting rate from 8\% (all to Forcing) to 5.5\% (our best-case feasible targeting mechanism).
 
@@
 
-What explains the persistence of a contract so contrary to borrowers’ interests?
+What explains the persistence of no-commitment contracts so contrary to borrowers’ interests in the real world?
 First, we show substantial levels of over-optimism among borrowers.
-Those most likely to benefit from the commitment contract and \textit{not} choose it are the individuals who most systematically over-estimate their own probability of repayment at the time of taking the loan.\footnote{More generally \hl{demand for commitment is higher among those with XXX characteristics.}}  Second, the existence of commitment-style repayment contracts in pawnshop lending is novel in Mexico.
+Among borrowers who do not choose it, those with the largest benefits from commitment are the individuals who most systematically over-estimate their own probability of repayment at the time of taking the loan.
 The dramatic improvements in borrower income arising from the commitment contract come directly from the pockets of lenders, reinforcing that the pawn industry as a whole has a strong interest in retaining the status quo.
@@
 Does learning eventually overcome the low demand for commitment? 
-For learning to happen clients would need to experiment the frequent payment contract, and this was not the typical contract in the industry.
+%For learning to happen clients would need to experiment with the frequent payment contract, and this was not the typical contract in the industry.
 But even if the contract was experienced, borrower may fail to learn or learn only slowly.
-We find that those who are forced to the monthly payment product are 6.7 percentage points more likely to become repeat costumers than those assigned to the status-quo contract.
-One way to interpret this is that that having experienced the frequent payment contract (and the lower financial cost of borrowing that come with it), they want to borrow more.\footnote{A second intepretation is that the iliquidity created by the monthly payment contract makes them want obtain second loan to pay the first one.
-This second explanation is unlikely since borrowers obtain a second loan not within the first 90 days of the first loan when payments are due; moreover, the correlation is also present conditional on having paid down the first loan.
+We find that borrowers who are assigned the forced commitment contract are 6.7 percentage points more likely to become repeat costumers than those assigned to the status-quo contract.
+One potential interpretation of this result is that borrowers who experience the frequent payment contract rationally choose to borrow more later on because of the lower effective financial costs that this contract entails.\footnote{An alternative interpretation is that the monthly payments from the commitment contract sap borrowers liquidity, leading them to take a second loan to pay off the first.
+This is unlikely because subsequent loans fall outside the 90 day period within which payments for the first loan are due.
+Moreover, the correlation is also present conditional on having paid down the first loan.
 Borrowers tend to pledge a different piece for the second loan, so that recovery of the first pawn is also an unlikely explanation.} However, a stronger test of liking the monthly payment contract is whether conditional on coming again, they would choose frequent payments.
-We test this and we cannot reject that demand is not higher after experiencing the monthly payment contract, however sample sizes are small and \hl{the minimum detectable effect is XXX.}
-
+We test this and we cannot reject that demand is higher after experiencing the monthly payment contract, however sample sizes are small and power for this analysis is correspondingly low.
 %While forcing individuals into commitment does not cause them to demand it in subsequent loans, \textcolor{red}{in Table \ref{iv_pf}} we show observational evidence of `learning by not doing’:  individuals offered commitment who elect not to take it and subsequently default \textit{do} learn about the benefits of commitment, demanding commitment loans at higher rates on subsequent pawn contracts when given the choice.
@@
 The dramatic improvements in borrower income arising from the commitment contract come directly from the pockets of lenders, reinforcing that the pawn industry as a whole has a strong interest in retaining the status quo.
-
 Our results suggest that pawn lending markets capture borrower wealth in ways not well summarized by interest rates.
 By overcollateralizing and then structuring loan contracts in a manner encouraging of default, lenders are able to extract substantial value independent of the interest charged.
-Further, the `nudge’ approach generally favored by the behavioral literature (voluntary commitment) may not be adequate.
-We hesitate to give precise policy recommendations since we don't have good measures of welfare.
+Further, the `nudge’ approach generally favored by the behavioral literature (voluntary commitment) does not generate adequate demand in this context.
+
+%We hesitate to give precise policy recommendations since we don't have good measures of welfare.
 Even though the monthly payment contract dramatically reduces financial cost, it could potentially generate lower (or higher) anxiety.
@@
 
-Our paper speaks to several strands of the literature.   %First, they suggest consequential ways in which different financial services draw client pools with distinct behavioral biases. 
-First, to research in microfinance studying the effect of payment frequency.
-While research in microfinance markets has not found the same benefits from providing a more regularized repayment environment \citep{Pande}, those experiments are performed on top of highly structured contracts and among borrower pools who may have selected into that type of lending precisely because it provides structure.
-This may explain why there is almost no default in the control group in \citep{Pande}.
-Second, we broaden the analysis of the extent to which voluntary commitment mechanisms are taken up and effective.
-Like our study, commitment demand has been found to be low in a number of contexts (\cite{Ashraf}, \cite{Gine}, \cite{Ted}, \cite{Royer}, \cite{Sprenger}).
-Other papers have found more robust demand for commitment (\cite{Kremer},  \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}, \cite{Pascaline}).
-But unlike all these papers we can point identify the benefit the non-takers would have had if they had taken up and the benefit for the takers, and thus can talk more rigorously about private paternalism in this context.
-
-%Finally, we provide only the second case in the literature, and the first in the analysis of financial products, to illustrate the perverse result that those who opt into commitment are precisely the individuals who do not need it \citep{Sprenger}.
-
-Two recent papers that shed some light into private paternalism.
-In the context of food choice, \cite{Sprenger} elicit dynamic inconsistencies, and then find that demand for commitment is negatively correlated with such inconsistency.
-In the context of school choice, \cite{Walters} finds that students that select into more effective schools have smaller treatment effects from attending than those that select out.
-Besides being very different contexts from ours, we rely on very different methods.
-In contrast to \cite{Sprenger} we will directly point identify the TuT, obviating the need for elicitation of preferences to test for negative selection.
-In contrast to \cite{Walters} we use randomization while he needs a structural model and distance to school as an instrument.
-\hl{FRANK, can I say something more precise than ``a structural model''?}
-
-Methodologically we contribute to the large literature on treatment effect heterogeneity by showing how an experimental design with two forcing arms and one choice arm allows for identification of the TOT, the TUT and other important parameters under minimal assumptions.
-\cite{aronow2013beyond} and \cite{angrist2013extrapolate} assume no selection on gains to estimate \hl{XXX}.
-\cite{Walters} achieve identification of the TuT by using parametric model and a distance instrument, which requires the model to be correct and the instrument to be valid.
+Our paper makes a number of contributions to the literature. %First, they suggest consequential ways in which different financial services draw client pools with distinct behavioral biases. 
+First, it speaks to microfinance research on the effects of payment frequency.
+While experiments in microfinance markets have not shown the same benefits from providing a more regularized repayment environment as we find here \citep{Pande}, these experiments differ from ours in two important ways: they are performed on top of highly structured contracts, and they involve borrower pools who may have selected into that type of lending precisely because it provides structure.
+These differences may explain why \citep{Pande} finds almost no default in the control group, in stark contrast to our results.
+Second, we provide a deeper analysis of both the take-up and efficacy of voluntary commitment mechanisms.
+A number of papers have found low demand for commitment as we do (\cite{Ashraf}, \cite{Gine}, \cite{Ted}, \cite{Royer}, \cite{Sprenger}) while others have found more robust demand for commitment (\cite{Kremer},  \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}, \cite{Pascaline}).
+Unlike all of these papers, however, we separately point identify and estimate the effects of commitment for borrowers who would and would not choose it.
+This allows us to conduct a more rigorous and nuanced analysis of private paternalism in our empirical context.
+
+Two other recent papers also shed some light on private paternalism.
+In the context of food choice, \cite{Sprenger} elicit dynamic inconsistencies and show that demand for commitment is negatively correlated with these inconsistencies.
+In the context of school choice, \cite{Walters} finds that students who select into more effective schools have smaller treatment effects from attending than those who do not.
+Our paper differs from these in both its empirical setting and its methodology.
+As far as we are aware, ours is the first experiment to combine control, forced treatment, and treatment choice arms and explain how such a design can be used to point identify TUT effects and a range of other interesting causal parameters under minimal assumptions.
+We call this approach the ``Controlled Choice design'' for short.
+Other approaches to going beyond local average treatment effects (LATE) from the literature either assume no unobserved selection-on-gains \citep{aronow2013beyond,angrist2013extrapolate} (the ``LATE-and-reweight'' approach) or rely on a combination of instruments with rich support and additional structural assumptions such as additive separability of observed and unobserved determinants of treatment effect heterogeneity \citep{heckman2007econometric, cornelissen2018benefits} (the marginal treatment effects approach).
+\cite{Walters} takes the latter approach, combining a distance instrument with additional structural assumptions, obtaining model-based TUT and ATE estimates that differ substantially from those implied by a LATE-and-reweight approach.
+In contrast, we leverage our experimental design to point identify the TUT effect using a binary instrument without the need for a structural model, relying instead on relatively simple exclusion restrictions.
+This restriction has testable implications that we fail to reject.
+Rather than assuming away unobserved selection-on-gains, as in the LATE-and-reweight approach, we estimate it directly.
+Unlike \cite{Sprenger} we directly identify the TUT, obviating the need to first elicit preferences before testing for negative selection.
+
+%We illustrate here how experimental design can be used to form a simple test for selection on gains.
+
+%In contrast to the broader literature on Marginal Treatment Effects \citep{heckman2007econometric}), we exploit simple randomization and an exclusion restriction on choice rather than requiring a continuous instrument that can be used to build a structural model as in \cite{Walters}.
+
+%achieve identification of the TuT by using parametric model and a distance instrument, which requires the model to be correct and the instrument to be valid.
 TUT and ATE implied by LATE-and-re-weight differ sharply from his model-based estimates.
 The method of
-\cite{heckman2007econometric} and \cite{cornelissen2018benefits} require the availability of instrumental variable with rich support, and separability of observed and unobserved determinants of treatment effects.
-
-The remainder of the paper is structured as follows:  section \ref{context} provides context and defines our main outcome variables.
-Section \ref{Experiment} describes the experiment, data sources, and shows pre-treatment balance across arms.
-Section \hl{???} estimates the effect of forcing clients into the fee-commitment contract, while Section \hl{???} studies the effects of choice.
+
+%Methodologically we contribute to the large literature on treatment effect heterogeneity by showing how an experimental design with two forcing arms and one choice arm allows for identification of the TOT, the TUT and other important parameters under minimal assumptions.
+\cite{aronow2013beyond} and \cite{angrist2013extrapolate} assume no selection on gains to estimate \hl{XXX}.
+
+%\cite{heckman2007econometric} and \cite{cornelissen2018benefits} require the availability of instrumental variable with rich support, and separability of observed and unobserved determinants of treatment effects.
+
+The remainder of the paper is structured as follows:  Section \ref{context} provides context and defines our main outcome variables.
+Section \ref{Design} describes the experiment and data sources, and shows pre-treatment balance across arms.
+Section \ref{Experiment} provides the standard ITT analysis of the experiment, while Section \ref{Choice} presents our strategy for estimating ToT and TuT effects, and Section \ref{Paternalism} investigates why paternalism functions so well in this context and whether it can be more finely targeted.
 Section \ref{conclusion} concludes.
-
-%\section{Old Introduction}
-
-%Many institutions ---firms, schools, financial contracts--- restrict choice using built-in commitment mechanisms which help workers, students, borrowers overcome self-control problems.
-For instance, ``[mortgages restrict choice] with a fixed repayment stream and mandatory principal repayment'' \citep{Laibson2018}.\footnote{\cite{Laibson2018} also mentions that ``Firms do limit their workers' freedom with intermediate deadlines, progress reports, production targets'', and schools with ``pop quizzes, classroom attendance requirements, cold calling, graded problem sets, deadlines''.} At the same time  these same firms shroud and don't market these commitment features, presumably because students, workers and borrowers don't welcome these restrictions.
-\cite{Laibson2018} argues that this presents an important puzzle: clients that would benefit from commitment underestimate its value and thus have low demand for it.
-In such a case private paternalism may be beneficial.\footnote{Laibson defines paternalism as a policy that advances an individual's interests by restricting his or her freedom, and private paternalism as paternalism implemented by private institutions.
-%In this paper we will study the effect of restricting freedom of contract choice on two outcomes: pawn recovery and financing cost, not overall welfare.
-%We want to clarify that we are using the word ``paternalism'' in a restricted sense, meaning only that a large majority of clients would incur in lower financial costs from being forced into installment contracts instead of letting them choose.
-We are not making claims about overall welfare which is a slippery concept if we take into account the possibility of biased beliefs and preferences.}
-
-%This paper studies the benefits of restricting choice in the context of pawnbroker lending.
-Pawn loans are one of the oldest, most understudied, and most prevalent forms of borrowing.
-There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues.
-In China it is a 43 billion dollar industry.\footnote{\url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.} Our partner pawn lender (henceforth Lender $P$) alone served more than 1 million clients in the last 3 years with more than 4 million contracts.
-The key characteristic of pawn loans is that the borrower leaves personal property (a pawn) as collateral in exchange for an immediate cash loan of a smaller value.
-In our case Lender $P$ only accepts gold jewelry as collateral and approves all pawns, giving cash the equivalent of 70\% of the pawn's appraised value.
-The contract stipulates a 7\% monthly interest rate charged daily, a loan term of 90 days, and the flexibility to pay back the loan at anytime before the loan is due.
-In spite of this flexibility ---or perhaps because of it--- 60\% of clients lose their pawn\footnote{In the US default is also high at 15\% (\url{https://tinyurl.com/yc2x5bjf}).}, and among those that recover it almost all of them pay in the days just before the loan elapses.
-
-% About 85\% of borrower lose their pawn\footnote{https://nationalpawnbrokers.org/2017/06/19/pawnbroking-around-the-world/}
-
-%different prices: https://priceonomics.com/the-economics-of-pawn-shops/
-
-% pawnshops help the poor https://tinyurl.com/y9qr43j8
-%, with annual percentage rates above or close to 200\%.
-
-% Limite statustics and knowledge of pawnshops. World bank mentions them in passing: https://tinyurl.com/ydgob8pv
-
-%Borrowers typically turn to these loans when in desperate need to pay for an emergency.
-The vulnerability of these borrowers has sparked regulator's interest.\footnote{In 2013 Mexico's Consumer Protection Bureau (Profeco) is concerned about abuse.
-It forced Pawnshops to be more transparent in their pricing, register their contracts with them and issued regulation to protect clients.
-Congress has enacted laws in this regard.
-\url{http://www.diputados.gob.mx/LeyesBiblio/ref/lfpc.htm}.} One concern is that borrowers selecting into these loans may exhibit particularly strong behavioral biases.
-%Using a survey conducted by us in branches of Lender $P$, we indeed document some evidence consistent with these concerns: while pawnshop clients predict they will recover their pawn with 93\% probability on average, in reality only 40\% of them do, suggesting naivete.
-%Even conditional on paying a positive amount towards pawn recovery, 53\% lose their pawn and their payment.
-In our survey 69\% report self-control problems saying they often fall into temptation spending.
-%, but only gr{15\%} show inter-temporal inconsistencies in a classical present-bias question, a similar number to \cite{Ashaf}.
-%and {19\%} do not normally budget monthly expenses.
-%While this is suggestive of a present bias problem or overconfidence to save and pay, at the same time our subjects are experienced and not wholly uneducated, 66\% have completed at least high school and 90\% have pawned before.
-%and {38\%} have participated in a Rosca.
-
-%We implemented a large randomized control trial with close to 10,000 pawnshop clients in 6 branches of Lender $P$ in Mexico City.
-We answer five main questions using this experiment.
-First, would clients benefit  ---in terms of recovering their pawn and in terms of incurring in lower financing costs---  from having a frequent (monthly) payment commitment contract \textit{forced} on them, instead of the current 3-month pay-when-you-want contract?
-That is, we are asking whether \textit{charging} them a 2\% late payment fee for not paying a monthly installment on time can actually \textit{decrease} total (fee-inclusive) financing cost.
-Second, would there be demand for such an installment contract vis-a-vis the status quo one if given the choice?
-Note that any payment profile implemented in the commitment contract can be replicated by the borrower under the status quo contract, but the former provides commitment.
-Third, would clients who benefit from commitment the most (e.g.
-the present biased or overconfident) demand it more?
-Fourth, are late payment fees key to provide commitment or would a non-pecuniary but salient personal promise to pay provide a cost-reducing mix of commitment vs flexibility?
-Promises change behavior significantly in laboratory settings, but we know little about their effect in natural environments.\footnote{%Some papers in this space are \cite{PromisesPartnerships}, \cite{Vanberg}, \cite{Belot2010}, \cite{WhyDoPromises}, \cite{FurtherPromises}, \cite{Ismayilov2017}.
-%There is some actual policy around using promises for loans: the government Mexico has created a program called ``Loans on your word'' for uncollateralized borrowing (\url{http://tiny.cc/yfmnmz}), but unfortunately there is little information about them.} Finally, is \textit{giving choice} among contracts better than forcing clients into payment-commitment contracts in terms of minimizing financing costs incurred and the likelihood of recovering their pawn?
-Or on the contrary, is it better to force the installment contract paternalistically?
-
-%The experiment involved 5 arms, with randomization happening at the branch-day level.
-It is described in detail in Section \ref{Experiment}.
-Here let us briefly explain the main 3 arms.
-The first one involves a group of clients that were given only the status quo flexible payments contract (henceforth the \textit{status-quo forcing group}).
-The second arm (\textit{Forced Commitment group}) was given a monthly payment commitment contract, which stipulated that clients had to pay 1/3 of their loan plus accumulated interest in each of the 3 months of the term length.
-Failing to do this would result in a fee of 2\% of the amount due that month.
-A third group (\textit{Commitment Choice group}) gave clients a choice between these two contracts.
-
-%Results are striking.
-First, we find that forcing clients into frequent payment commitment contracts causes them on average to save on financing cost and to recover their pawn more.
-The effects are large: financing cost decreases by 9.4\% on average (from \$3157 to \$2860 MXN), while the likelihood of recovering their pawn increases by 26\% (from 43\% to 55\%).
-Results are robust qualitatively to including transport costs of going to the branch plus losing a day's wage for each visit.
-Importantly, the benefits are distributed broadly: almost the whole distribution of treatment effects shows cost savings; however those most economically vulnerable, and notably, those we classify as overconfident, experience larger gains.
-%The commitment contract also causes payments to start 8 days earlier and be 16\% more frequent, compared to the control group.
-%Treatment effects are concentrated in the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery.
-That is, the fee-commitment contract induces people who would otherwise pay something towards recovery, to pay more and faster and thus recover their pawn more at a cheaper financial cost.
-Finally, borrowers assigned to the forced fee-commitment contract are 5 percentage points (100\% of the mean) more likely than the control group to ask for another loan in the future, suggesting that they liked the commitment contract after experiencing it.
-
-%From this first comparison we conclude that penalizing borrowers for delinquency in a contract which has already has large penalties from default actually helps borrowers.
-In fact, we find that borrowers assigned to the forced fee-commitment contract are 5pp more likely to be repeat customer, suggesting that they themselves liked the the commitment contract more after experiencing it.\footnote{As it is well known, \textit{naivete} facilitates their exploitation by firms.
-\cite{Laibson2018} conjectures that this exploitation may be limited if consumers use experienced utility to choose among firms or contracts.}
-
-%Second, in spite of these estimated benefits for almost all clients, actual demand for the fee-commitment contract is low.
-Only 10\% of the group offered a choice between the monthly payment fee-commitment contract and the status-quo one chose the former.
-This is not likely driven by misunderstanding the (already simple) contract.\footnote{We posted two project assistants in each of the experimental branches every day for all branch opening hours to carefully explain the contracts; material was developed to explain the differences among the two contracts, and subjects spelled back to our team the loan differences.
-Furthermore take up is systematically predicted by baseline covariates, making it less likely that these are just random mistakes.} We show further that clients that most benefit from the contract (those who are overconfident about recovering) are \textit{less} likely to demand it, echoing a result by \cite{Sprenger} for grocery purchases and \cite{Walters} for schools.
-%is Low demand for commitment is consistent with a large literature (\cite{Laibson2015}, \cite{Laibson2018}, \cite{John}, \cite{Ted}, \cite{Rabin2018}).
-%\footnote{\cite{Alcohol} and \cite{Kremer} are some of the few instances of high demand for commitment.
-\cite{Alcohol} speculates that this difference may be explained by their subjects having more experience with their self control problem.
-Close to ninety percent of our subjects claim to have pawned before.
-We find that experience does not predict positive take up in our sample.}
-%\cite{Laibson2015} shows that the lost flexibility resulting from a commitment contract can severely limit take-up when agents are naive about their self control, even though commitment could be welfare improving for them.
-%Owing to this low take-up, we estimate zero average treatment effects of the \textit{Commitment Choice} arm on financial cost and on pawn recovery throughout the quantile distribution.
-
- %Using boosting we can predict who takes up with 92\% accuracy. This fact shows that the choice among contracts is not purely random.
-
-%Third, combining the forcing and the choice arms ---a unique feature of our experiment--- allows us to estimate the counterfactuals to answer the question of how much money is left on the table by giving choice to clients.
-We calculate that about {80}\% of clients in the Commitment Choice group chose contracts that induced \textit{higher} financial cost.
-On average they spend an extra \${238} MXN, close to {11}\% of the average loan value.
-In particular {92}\% of those that chose the status-quo contract would have been better in the fee-commitment contract, while only {8}\% of those who chose the fee-commitment contract would have been better in the status-quo one.
-This suggests that forcing clients into commitment contacts ---private paternalism--- may be beneficial for the overwhelming majority of clients.
-After seeing our results Lender $P$ introduced frequent payment contracts in their loans portfolio.
-
-%Inspired by a significant lab experiment literature on the effects of promises on behavior, and by research showing that a small fee could drastically reduce demand for commitment of (partly) naive present-biased borrowers (\cite{Laibson2015}), we implemented a ``psychological commitment'' product in the form of a salient promise to pay.
-\cite{PromisesPartnerships}, \cite{FurtherPromises}, \cite{Vanberg}, and \cite{Ismayilov2017} find that the ability to make a promise about behaving a certain way makes the individual more likely to adhere to the promised behavior.
-%and also induces trusting behavior by the recipients of the promise.
-
-%To measure the causal effect of promises we implemented two other treatment arms.
-A \textit{promise-forcing} arm exactly analogous to our \textit{Forced Commitment arm} except that instead of telling them that there was a fee if they didn't pay on time, we made borrowers promise that they would pay one third of the amount in each of the 3 months, and told them that if they didn't they would have broken their promise and not kept their word.
-Because salience is key we made them sign a (legally non-binding) personal promise and emphasized that we were counting on them to keep their promise.
-A final arm (\textit{promise-choice arm}) gave clients the opportunity to choose between the \textit{Promise} contract and the \textit{Status-quo} contract.
-
-%We document three main results in the promise arms.
-First, demand for the Soft Commitment contract is three times larger than for the fee-commitment contract, with {31}\% take-up.
-This difference shows that clients are indeed taking into account the contractual parameters when they choose, and that the fee commitment was probably too strong from their point of view.
-Second, in spite of this much higher take-up, the \textit{Promise-choice arm} had no effect on outcomes on average, or even for those who selected into promising.
-Third, being forced in to the \textit{Promise} contract also had zero effects on average and throughout the distribution on financing cost and pawn recovery.
-%\footnote{There is a decrease in financial cost in the 50th and 75th quantiles in the forced Soft Commitment arm however.} Promises did not provide enough commitment so as to be reflected in behavior.
-This is one of the first  experiments using promises in the field, and results are in striking contrast with those in the lab.
-
-%This paper contributes to several strands of literature.
-First, we focus on an important new context: pawnshop borrowing.
-Pawnshop borrowing is extremely prevalent in developing countries and very worrisome to regulators, yet severely understudied.\footnote{The World Bank's CGAP recognizes the importance of pawnshop borrowing worldwide but provides no statistics or analysis on it (\url{https://tinyurl.com/ydgob8pv}).
-We could not find peer-reviewed papers about it either.} It is different from microfinance in that it deals with emergency loans, and not loans for productive investment.
-Because of this, it may draw on a more vulnerable (and potentially more unsophisticated) population, and because it is not typically used for productive investment, the trade-off between loan rigidity and investment found for microfinance \citep{Field} may not be there.
-
-%Second, a significant literature has shown that demand for commitment exists.
-But while it is low in some contexts (\cite{Ashraf}, \cite{Gine}, \cite{Ted}, \cite{Royer}, \cite{Sprenger}), it is high in others (\cite{Kremer},  \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}, \cite{Pascaline}).
-We add to this literature by adding evidence from another market.
-Demand for commitment  is low, and very small fees\footnote{For instance our fees are 16 times smaller than than those of \cite{John} as a fraction of the loan/goal, and 5 times smaller converting peso values using exchange rates.} are enough to drastically reduce demand for commitment, even when commitment is cost-reducing.
-Softer commitment contracts in the form of promises do increase demand but did not change outcomes.
-%We also show that softer commitments in the form of non-pecuniary personal promises elicit higher demand but do not affect behavior or financing costs.
-
-%Third, and most importantly, we study both causal effects and selection into frequent payment commitment loan contracts at the same time and for the same population in a single experiment.
-We know of no other experiment in the credit market which simultaneously combines forcing and choice arms.
-This feature, when paired with new machine learning methods to estimate heterogeneous treatment effects \citep{atheygrf}, allows us to show whether there is positive or negative selection into beneficial contracts, and whether pawnshop clients forego money by not demanding commitment.
-In consonance with what \cite{Walters} finds in the school choice context, we find that it is \textit{not} those who benefit most from the contract that demand it more.
-\cite{Sprenger} find similar result in the context of grocery purchases.
-In contrast to \cite{Sprenger}, our context allows us to focus on money savings instead of estimated utility to proxy for benefits of commitment, a narrower but more transparent measure.
-This allows us to measure effects on cost outcomes beyond take up.\footnote{\cite{John} and \cite{Ted} show that the extent of commitment needed is underestimated.
-In contrast to them, we infer subjects underestimation of the value of commitment from their forgone treatment savings, instead of from subjects failing to reach a goal.}
-
-%Third, in consonance with \cite{Sprenger} and \cite{Walters} but in our very different context, we find that people who most need commitment (in our case the overconfident, as they have the larger treatment effects) are also the ones less likely to demand it when given choice.
-
-%Fourth, we provide new evidence on the payment frequency debate.
-The literature has found null effects on installment frequency loan default \cite{Pande}.
-This result is at odds with the prevalence of frequent payment contracts in markets.
-We find strong effects of payment frequency on decreased default.\footnote{There are many differences in context between the papers which may explain the different result.
-\cite{Pande} focus on group lending with very little default to start with (less than 1\%), while in our case almost half of loans end in default.
-We also have a larger sample and we focus on individualized loans, which may afford us stronger statistical power to detect effects.} Our result is consistent with \cite{Field} who show that delaying payment in microfinance loans increases default.\footnote{\cite{Craig} use the discipline of regular loan repayments in microfinance to remind people to save and make a savings plan, and find large increases in savings.}
-
-%We believe that taken together, our results (commitment matters, small fees have large effects on behavior, people don't choose the cost reducing contract) call for a behavioral explanation.
-Most of the literature tries to connect commitment problems with measures present biased preferences.
-Results are mixed, which is not surprising given how hard is to measure present bias naivete for instance.
-Instead of trying to measure those we focus on measuring biased predictions about payment, what we call overconfidence.
-Not only is it easier to measure, but also more general in the sense of being implied by present bias but not conversely.
-As in \cite{Rabin2018} we contrast subjects' \textit{own predictions} of their behavior with their actual behavior, but we do it in a natural setting.
-\cite{Murdoch} show that a robust positive correlation exists between displaying present biased preferences in surveys and selecting into microfinance, which they interpret as being due to high demand for the discipline imposed by frequent payments.
-However they acknowledge that this ``interpretation is suggestive...
-and needs to be confirmed by studies that establish causal links''.
-Our experiment is a test of this causal link.
-
-%\cite{Ghatak} state that ``high-frequency repayment, a feature in nearly all microfinance contracts, has been largely overlooked''.
-%\footnote{\cite{LittleAtAtime} also note that ``it is especially surprising that there is so little analytical discussion of the incentive effects of the installment system''.}
-%This paper fills part of this gap.
-
-%Finally, even though personal promises feature prominently in microfinance guidelines\footnote{e.g.
-\url{https://grameenfoundation.org/documents/GrameenGuidelines.pdf}, p.36.} we know of no other study that has tried to isolate their effects on loan repayment.
-In concordance with this literature we find that people are willing and indeed voluntarily choose to make promises.
-We find however that measured behavior was unchanged by promising.\footnote{This is of course not a refutation of the laboratory literature.
-%not least because the laboratory literature is implemented on more tightly controlled environments and focused on subtler aspects of promising, like their effects on second order beliefs and guilt aversion.
-The context is also different since The lab literature has focused on very structured investment games between two players and looked at the effects of promises on trust and cooperation.
-In our case the bank is not a strategic player that responds to the promise, or a person to which the client can feel guilt towards (although the teller is).
-However, our results do provide a first piece of evidence on the limitations of using promises to change behavior in loan contracts.}
-
-%, consistent with a significant fraction of clients displaying naivete about self control problems (see \cite{Rabin2018}).
-Our context is one in which private paternalism (\cite{Laibson2018}) could work since almost all pawnshop clients would benefit from frequent payment contract yet there it almost no demand for them.
-After our experiment ended, Lender P started to tie in installment payment components to some of their contracts themselves.
-
-%\footnote{This is consistent with \cite{Belot2010}, who emphasize that elicited promised may have lower effects than voluntary ones.}
-%\cite{Rabin2018} and \cite{Ted} show that naivete may lead to the choice of to little commitment. 
-%Before discussing results, let us mention why these questions are relevant and how they relate to the literature.
-Most of microfinance involves frequent payments/meeting with the group --sometimes weekly-- even though this increases transaction costs.
-Several hypothesis have been postulated to explain this, from increased group's cohesion and monitoring, to forming personal payment habits or serving as a commitment device.
-Most of the literature (e.g.
-\cite{Pande}) find however null effects of increasing frequency on default, and therefore on payment habits, commitment, or peer pressure.
-
-%The paper is organized as follows.
-Section \ref{context} provides context and describes the data sources.
-Section \ref{Data} presents summary statistics and defines our main outcome variables.
-Section \ref{Experiment} describes the experiment and shows pre-treatment balance across arms.
-Section \ref{fee-commitment} estimates the effect of forcing clients into the fee-commitment contract, while Section \ref{Commitment Choice} studies the effects of choice.
-Section \ref{model} collects all findings and presents a model to rationalize them qualitatively.
-Section \ref{promises} assesses if promises work in our context as commitment devices.
-Finally, Section \ref{conclusion} concludes.
 
@@
 As with payday lending, pawnshop lending is controversial.
-Regulators have concerns with the sophistication of borrowers using it\footnote{The US congress has actually banned the payday lending industry from serving active military personnel, and some States in the US have imposed zoning restrictions, interest caps, and restrictions on serial borrowing as consumer protection measures against payday lending \citep{Payday}.} speculating they may suffer from behavioral and cognitive deficiencies which lead to make sub-optimal choices.
-There is some evidence in support of this view for payday borrowers.\footnote{\cite{Bertrand} write that ``Under the view that the people borrowing from payday lenders are making an informed, utility-maximizing choice given the constraints that they face, one would not expect additional information disclosure about the payday product to alter their borrowing behavior'', but to the contrary, they find that simply disclosing how financing costs add up reduced demand by 11\%.
+Regulators have concerns with the sophistication of borrowers using it, speculating they may suffer from behavioral and cognitive deficiencies which lead to make sub-optimal choices.\footnote{The US congress has actually banned the payday lending industry from serving active military personnel, and some States in the US have imposed zoning restrictions, interest caps, and restrictions on serial borrowing as consumer protection measures against payday lending \citep{Payday}.} There is some evidence in support of this view for payday borrowers.\footnote{\cite{Bertrand} write that ``Under the view that the people borrowing from payday lenders are making an informed, utility-maximizing choice given the constraints that they face, one would not expect additional information disclosure about the payday product to alter their borrowing behavior'', but to the contrary, they find that simply disclosing how financing costs add up reduced demand by 11\%.
 \cite{Meltzer} finds that payday loan access leads to increased difficulty paying mortgage, rent and utilities bills.}  Our study reinforces the idea that a lack of sophistication may be an integral part of that way that standard pawn contracts are structured.
@@
 
-To study this market, we partnered with one of the largest pawn shops in Mexico, an institution with more than one hundred branches spanning multiple States in Mexico.
+To study this market, we partnered with one of the largest pawn shops in Mexico, an institution with more than one hundred branches spanning multiple states in Mexico.
 This lender (whom we refer to as `Lender P') has a simple and typical business model.
 
-\paragraph{Appraising and lending.} They take gold jewelry as collateral in exchange for a fraction the value of the piece, in cash.
+\paragraph{Appraising and lending.} Lender P takes gold jewelry as collateral in exchange for a fraction the value of the piece, in cash.
 No other collateral and no credit history checks are needed.
@@
 
-\paragraph{Borrowers.} The clients that pawned understood these terms well (as we verified in interviews).\footnote{90\% of clients report in our survey that they have pawned before.} These clients have little or no access to other types of loans and they value the convenience of pawn borrowing.
+\paragraph{Borrowers.} The clients that pawned understood these terms well (as we verified in interviews).\footnote{87\% of clients report in our survey that they have pawned before.} These clients have little or no access to other types of loans and they value the convenience of pawn borrowing.
 This population of pawn borrowers is economically vulnerable:  30\% of them could not pay either water, electricity \& gas or rent in the past 6 months; 87\% said they are pawning because of an emergency, and only 13\% stated it was to use in a `non-urgent expense'.
@@
 
-\paragraph{Most borrowers lose their pawn.} Our context is also one with high borrower default: 60\% of clients lose their pawn in a time span of 230 days from the date of pawning.
+\paragraph{Many borrowers lose their pawn.} Our context is also one with high borrower default: 43\% of clients lose their pawn in a time span of 230 days from the date of pawning.
 One potential explanation for high default is that clients are really just knowingly selling their gold piece through a pawn contract on which they intend to default.
@@
 Note that high default could be detrimental from the lender's point of view, since it may reduce the likelihood that the client becomes a return customer.
-Lender P was in fact explicitly interested in partnering with us to investigate how to reduce loan default, customer satisfaction, and repeat borrowing.
-
-\subsection{Measuring Borrowers Financial Costs} \label{costs}
+%Lender P was in fact explicitly interested in partnering with us to investigate how to reduce loan default, customer satisfaction, and repeat borrowing.
+
+\subsection{Measuring Borrowers Financial Costs} 
+\label{costs}
 
@@
 For each given loan we observe if the client lost her pawn ($\mathds{1}(\text{Default}_i)$) and when.
-If the client has renewed her loan several times such that the loan is continuing but has not defaulted, we code default as zero.
-In our data \hl{XX\%} of experimental loans are continuing (i.e.
+If the client has renewed her loan several times such that the loan is continuing but has not defaulted, we pursue the strategy of coding default as zero (this approach is conservative in our context in that it does not lead the reduction in repayment time to translate mechanically into a drop in default).
+In our data 13\% of experimental loans are continuing (i.e.
 censored) when the data period ends.
@@
 \begin{align*}
-    \text{Financial Cost}_i =&  \underbrace{\sum_t P^i_{it}}_{\text{Payments to interests}} + \underbrace{\sum_t P^f_{it}}_{\text{Payments of fees}}   \\
+    \text{Financial Cost}_i =&  \underbrace{\sum_t P^i_{it}}_{\text{Payments to interest}} + \underbrace{\sum_t P^f_{it}}_{\text{Payments of fees}}   \\
     &\quad\qquad + \underbrace{\mathds{1}(\text{Default}_i) \times (\text{Appraised Value}_i}_{\text{Cost of losing pawn}} + \underbrace{\sum_t P^c_{it}}_{\text{Payments to capital}})
@@
 
-As a second measure of cost we calculate the Annual Percentage Rate (APR) in order to express the cost as a percentage of the loan, per year, inclusive of default costs.\footnote{Loan term takes into account all the loan period, including those extended through refinancing}.
-The standard definition is given in the following formula:
+As a second measure of cost we calculate the Annual Percentage Rate (APR) in order to express the cost as a percentage of the loan, per year, inclusive of default costs.\footnote{Loan term takes into account the entire loan period, including extensions of the loan through refinancing.} The standard definition is given in the following formula:
 
@@
 
-Figure \ref{fc_hist}(a) plots a histogram of this financial cost in pesos for all loans in the experiment, distinguishing by whether we observed they defaulted (\hl{XXX\%}), recovered their pawn (\hl{XXX\%}), or whether they are censored in our data (\hl{XXX\%}).
+Figure \ref{fc_hist}(a) plots a histogram of this financial cost in pesos for all loans in the experiment, distinguishing by whether we observed they defaulted (43\%), recovered their pawn (44\%), or whether they are censored in our data (13\%).
 The first thing to note is that those that default incur in higher costs; part of this is mechanical as losing their collateral is part of the cost.
 The second thing to note is that those that are not closed at the end of our sample period have already incurred in substantial financial cost, even though they have not defaulted yet.
-Panel (b) shows the APR, which is normalized by loan size; most of the APR costs come from clients that do not recover their pawn.
+Panel (b) shows the APR; most of the APR costs come from clients that do not recover their pawn.
 %Of those who renew, 83\% lose the pawn.
@@
 
-\section{Experimental Design} \label{Experiment}
+\section{Experimental Design} \label{Design}
 
@@
 
-\noindent \textbf{The Commitment Contract.} For the purpose of the experiment we designed a new contract that is identical to the status quo contract except that, informed by the designed of micro-lending contracts, it enhances the regularity and salience of payments as a way to encourage repayment \citep{morduch1999microfinance, bauer2012behavioral}.
+\noindent \textbf{The Commitment Contract.} For the purpose of the experiment we designed a new contract that is identical to the status quo contract except that, informed by the design of micro-lending contracts, it enhances the regularity and salience of payments as a way to encourage repayment \citep{morduch1999microfinance, bauer2012behavioral}.
 It has the same interest rate (7\% \textit{per month}) which accumulates daily on outstanding debt, it has the same loan size/collateral ratio (70\%), it has the same loan term (90 days, and a grace period of 15 days), and the gold pawn gets appraised in the same way by the same appraisers.
@@
 The idea that the fee itself is not driving the treatment is reinforced later in the paper where we show financial benefits many times larger than the fee, as well as treatment effects even on those who would fail to recover pawns and hence not pay the fee.
-Transportation cost to go to the branch to pay is on the same order of magnitude as the fee on average.\footnote{%The lender was worried that if the fee was large, forgetting to pay could make the pawn unrecoverable.
-In contrast with \cite{John} we don't let the clients choose the size of the fee.
+Transportation cost to go to the branch to pay is on the same order of magnitude as the fee on average.
+%\footnote{%The lender was worried that if the fee was large, forgetting to pay could make the pawn unrecoverable. 
+%In contrast with \cite{John} we don't let the clients choose the size of the fee.
 \cite{John} shows that doing this results in costly choices by (partially) naive present biased consumers.
 Our fee is much smaller than the median in her experiment.
-%We also experimented with a contract where there was no pecuniary fee for paying late but where we clients made a personal promise to pay monthly.
-} To elicit demand for the monthly payment contract, we include an arm that allows borrowers to opt into this contract if they choose.
+%We also experimented with a contract where there was no pecuniary fee for paying late but where we clients made a personal promise to pay monthly.}
+To elicit demand for the monthly payment contract, we include an arm that allows borrowers to opt into this contract if they choose.
 The existence of both a non-optional ``forcing'' arm, and a choice arm in our design is key to estimate a battery of treatment effects above an average treatment effect under fairly mild assumptions.
@@
 \noindent \textbf{Treatment Arms.} Treatments were randomized at the branch-day level.
-Each day a computer randomly assigned which types of contracts were on offer that day in the branch, and therefore which contract the client signed.
+Each day a computer randomly assigned which types of contracts were on offer that day in the branch, and the IT system would only offer these.
 We have 3 different experimental arms\footnote{The experiment included other arms that involved no fee penalties and did not emphasize the structure of payments.
-These are being analyzed in a separate paper}:
+These are being analyzed in a separate paper.}
 
@@
 
-The existence of a choice arm allows us not only to measure if there is demand for such a contract, but who demands it, not only in demographic terms, but in terms of potential treatment effects.
+%The existence of a choice arm allows us not only to measure if there is demand for such a contract, but who demands it, not only in demographic terms, but in terms of potential treatment effects.
 One may worry for instance that low sophistication from pawn-loans users could lead to the `wrong' people choosing the structured commitment contract.
@@
 It also limits potential manipulation by appraisers, who in the presence of individual-level randomization could potentially pick their preferred customer from the line or tell them to wait until their desired contract shows up on the screen.
-Intra-branch day correlation on the probability of default (ICC) is small, at {0.08}, so we lose little power vis-a-vis individual-level randomization.
-
-Some clients pawned more than one time during the duration of the experiment, with \hl{XXX\%} pawning 2 times and \hl{XXX\%} more than 2 times.
+Intra-branch day correlation on the probability of default (ICC) is small, at {0.05}, so we lose little power vis-a-vis individual-level randomization.
+
+Some clients pawned more than one time during the duration of the experiment, with 14\% pawning 2 times and 8\% more than 2 times.
 To have a clean comparison we are considering only the first pawn in the experiment.
-It is also the case that \hl{XXX\%} of those first pawns involve more than 1 loan, as 2 or more pieces of gold were submitted.
+It is also the case that 30\% of those first pawns involve more than 1 loan, as 2 or more pieces of gold were submitted.
 We treat each of them as separate loans.
 
-\paragraph{Timeline.} Figure \ref{exp_description}(a) shows the timeline when the experiment happens and also the length of time for which we observe payments.
-For contracts in the first week, we observe up to \hl{XXX} days, with \hl{XXX\%} of contracts ending during our sample period (in default or recovery).
-For contracts in the last week we observe up to \hl{XXX} days, and \hl{XXX\%} of contracts ending observed.
-Figure \ref{exp_description}(b) shows the number branch-days per arm, the number of contracts, and the number of surveys.
+\paragraph{Timeline.} Figure \ref{exp_description} shows the timeline when the experiment happens and also the length of time for which we observe payments.
+For contracts in the first week, we observe up to 338 subsequent days, while for contracts in the last week we observe up to 235 days.
+Figure \ref{exp_description} also illustrates the number branch-days per arm, the number of contracts, and the number of surveys.
 %Not every contract has a survey for several reasons, we have survey information for \hl{XXX\%} of them.
@@
 One of the aspects emphasized was that the frequent payment contract involved the commitment to pay a third of the outstanding amount \underline{each month}, and the nature of the fees associated with the Commitment arm.
-Figure \ref{ExplanatoryMaterial} translates a piece of the materials we used to explain the contracts (in this case a comparison sheet used in the Promise-Choice days to compare contracts terms side to side).
+Figure \ref{ExplanatoryMaterial} translates a piece of the materials we used to explain the contracts.
 The explanation took about 3-5 minutes and was pursued until the client said she understood the contract terms.
@@
 The clients had to put their name on a slip of paper where they stated they promised to pay monthly.
-We are confident the overwhelming majority of clients understood the contracts and that those in the choice arm made informed choices.\footnote{That we can systematically predict demand based on consumer characteristics and measured beliefs suggest that take up is not random.}
+We are confident the overwhelming majority of clients understood the contracts and that those in the choice arm made informed choices.
+%\footnote{That we can systematically predict demand based on consumer characteristics and measured beliefs suggest that take up is not random.}
 
@@
 The survey was intentionally short to avoid discouraging the potential clients from pawning, but at the same time it aimed to measure the following: demographics, proxies for income/wealth, education, present-biased preferences, experience pawning, if family or friends commonly asked for money, how time consuming and costly it was to come to the branch, the subjective probability of recovering the piece that they intended to pawn, the subjective value of their piece in money terms (how much money they would sell it for), among others.
-We surveyed 10,437 clients, and the survey response rate was 78\%.\footnote{Appendix \ref{baseline_survey} transcribes the questionnaire in English.} %\footnote{We also surveyed clients before and after the experiment, so our survey covers a larger sample that we are not using in this paper.}.
+We surveyed 10,437 clients, and the survey response rate was 78\% among clients who took loans.\footnote{Appendix \ref{baseline_survey} transcribes the questionnaire in English.} %\footnote{We also surveyed clients before and after the experiment, so our survey covers a larger sample that we are not using in this paper.}.
 
@@
 To test for this, we examine the number of loans given per branch-day, with specific attention to whether the Forced Commitment arm led to a lower number of borrowers per day.
-The \hl{first} row of Table \ref{attrition_table} shows there is no difference between the Control and Forced Commitment arm in terms of the number of pawns per branch-day.\footnote{The Choice arm appears to have a somewhat larger number of borrowers than the Control arm (p-value=\hl{XXX}), but we cannot reject equality with the Forced Commitment arm (p-value=\hl{XXX}), or across all arms (p-value=\hl{XXX}).}  The second row makes the same point in a more focused way, given that the surveys were conducted prior to the revelation of treatment status.
-In no arm did more than three percent of individuals refuse loans subsequent to the survey, and neither these rates nor the rate of survey response are different across arms.
+The first row of Table \ref{attrition_table} shows there is no difference between the Control and Forced Commitment arm in terms of the number of pawns per branch-day.\footnote{The Choice arm appears to have a somewhat larger number of borrowers than the Control arm (p-value=0.06), but we cannot reject equality with the Forced Commitment arm (p-value=0.41), or across all arms (p-value=0.16).}  The second row makes the same point in a more focused way, given that the surveys were conducted prior to the revelation of treatment status.
+In no arm did more than three percent of individuals who responded to the survey go on to refuse loans, and neither these rates nor the rate of survey response are different across arms.
 Therefore it appears that the treatments have not induced any endogenous shifts in the composition of borrowers.
@@
 The survey was done before treatment status was revealed, and we observe loan outcomes regardless of whether the survey was conducted.
-Our core experimental estimates do not use the survey data as covariates, but the Random Forest analysis is restricted to the subset of borrowers who answered at least some survey questions.
-The top row of Table \ref{attrition_table} shows that the survey response rate is broadly similar across arms (about 77 percent).
-We can also examine differences in the fraction of borrowers who do respond to the survey and then do not end up taking a loan subsequent to completing the survey, we find that the share is close to as is the fraction of those 97\% across arms (p-value=\hl{XXX}).%\footnote{We also tested if the number of pawns per day for the 6 branches that participated in the experiment was different 1 month before the experiment started or 1 month after the experiment ended, relative to the days the experiment was active.
+Our core experimental estimates do not use the survey data as covariates, but the Random Forest analysis in Section \ref{Paternalism} is restricted to the subset of borrowers who answered at least some survey questions.
+The bottom row of Table \ref{attrition_table} shows that the survey response rate is broadly similar across arms (about 77 percent).
+%We can also examine differences in the fraction of borrowers who do respond to the survey and then do not end up taking a loan subsequent to completing the survey, we find that the share is close to 100\% as is the fraction of those 97\% across arms (p-value=0.62).
+%\footnote{We also tested if the number of pawns per day for the 6 branches that participated in the experiment was different 1 month before the experiment started or 1 month after the experiment ended, relative to the days the experiment was active.
 To this end we estimated the regression.
@@
 
-\paragraph{Balance.} Table \ref{SS} presents summary statistics for the sample of actual borrowers across arms, and illustrates that randomization worked to achieve balance across clients in the different experimental arms.
+\paragraph{Balance.} Table \ref{SS} presents summary statistics for the sample of actual borrowers across arms, and illustrates that randomization worked to achieve balance across the experimental arms.
 Panel A uses administrative data for the universe of borrowers in each arm, and shows that loan balances and the days on the week on which individuals pawned are comparable across arms.
-The average loan size is \hl{\$2197} MXN (\$105 USD).
+The average loan size is \$2267 MXN (\$130 USD).
 Panel B of Table \ref{SS} reports summary statistics across arms from our survey data.
-\hl{73\%} of clients are women, with an average age of \hl{43} years; \hl{66\%} of them have completed high school or more, and \hl{90\%} have pawned before, so that our sample has mostly experienced borrowers.
-Finally, the subjective probability of recovery is close to \hl{93\%} on average, which makes a stark contrast to the actual rate of recovery of \hl{42\%}; borrowers are highly overconfident on average.
-The average subjective value they report for the items they pawn is \hl{3069} MXN, much larger than the average appraised gold value of \hl{2197} MXN.
+73\% of clients are women, with an average age of 43 years; 66\% of them have completed high school or more, and 90\% have pawned before, so that our sample has mostly experienced borrowers.
+Finally, the subjective probability of recovery is close to 93\% on average, which makes a stark contrast to the actual rate of recovery of 43\%; borrowers are highly overconfident on average.
+The average subjective value they report for the items they pawn is 4084 MXN, much larger than the average appraised gold value of 3238 MXN.
 While this could arise either from overconfidence in valuation or from undervaluation by the lender, in any case it is \textit{prima facie} evidence that loss of the pawn should be undesirable relative to the quantity of liquidity leveraged by the asset.
@@
 
-\section{Average Treatment Effects} \label{experiment}
+\section{Average Treatment Effects} \label{Experiment}
 
 We begin by estimating average treatment effects of assignment to the Forced commitment and the Choice arms, relative to those assigned to the Control arm.
-As we explain below, only about \hl{XXX\%} of those in the choice arm chose the monthly payment option.
+As we explain below, only about 11\% of those in the choice arm chose the monthly payment option (Figure \ref{determinants_choose} shows coefficient plots for the characteristics that determine choosing commitment in the Choice arm).
 
@@
 Because our standard errors are clustered at the branch-day level, they automatically account for any dependence in error terms arising from multiple pawns by the same client on her first visit.}.
-The coefficients $\beta^F$ and $\beta^C$ are the ATEs of the forced commitment and choice treatments, respectively, on the outcome variable $y_{ij}$.\footnote{Note that $\beta^C$ can be viewed in two ways: as the the ATE of \emph{offering clients a choice} between the status quo and commitment contract or as the intent-to-treat effect of the commitment contract \emph{itself}.
+Given perfect compliance in the former, the coefficients $\beta^F$ is the ATE of the Forced arm and $\beta^C$ is the ITT of the Choice arm on the outcome variable $y_{ij}$.
+%\footnote{Note that $\beta^C$ can be viewed in two ways: as the the ATE of \emph{offering clients a choice} between the status quo and commitment contract or as the intent-to-treat effect of the commitment contract \emph{itself}.
 Here we adopt the former interpretation; below we use the latter to consider the relevance of selection-on-gains.}
@@
 The remaining columns decompose the financial cost and APR outcomes into their components: interest payments (col 2), payment towards any fees incurred (col 3), payments toward the principal (col 4).
-It is of interest to this research and to Lender P whether structured frequent payment decrease default.
+Column 5 shows the value of lost pawn conditional on losing it.
 In column 6 the dependent variable is a dummy indicating default.
-Column 5 shows the value of lost pawn conditional on losing it.
 Finally, column 7 rescales financial cost as a function of loan size to estimate causal effects on incurred APR.\footnote{As we explained above, loans can be extended for an additional 3 months by paying the interest owed and restarting the loan under the same treatment conditions.
@@
 The Forced Commitment arm yields large and significant decreases in the cost of loans to clients, as measured either by financial cost or APR.
-Despite causing an increase in fees, the Forced arm leads to a decrease of 379 pesos in the costs of borrowing (out of a group mean of 1851 in the status quo), that is equivalent to 20\% reduction as a fraction of mean cost.
-These cost savings arise from a 6.5 percentage point (pp) decrease in the probability of default (out of a baseline mean of 44pp), which implies cost savings of 254 pesos.
-But also from lower interest payments, since as we will document the treatment is effective at speeding up payments, with the benefits that the interest rate applies to a smaller principal.
+Despite causing an increase in fees, the Forced arm leads to a decrease of 379 pesos in the costs of borrowing (out of a group mean of 1851 in the status quo), equivalent to 20\% reduction as a fraction of mean cost.
+These cost savings arise from a 6.5 percentage point (pp) decrease in the probability of default (out of a baseline mean of 44pp,  implying cost savings of 254 pesos), and also from lower interest payments, since as we will document the treatment is effective at speeding up payments, with the benefit that the interest rate applies to a smaller principal.
 This translates into a large reduction in APR.
-A credit product that has an effective average APR of 184\% in the status quo arm (inclusive of default) is reduced to a cost of 34\% through the imposition of a more regularized payment structure.
+A credit product that has an effective average APR of 184\% in the status quo arm (inclusive of default) is reduced to a cost of 150\% through the imposition of a more regularized payment structure.
 
@@
 Giving borrowers the choice of contract did not decrease financial cost, whereas forcing them into a structured payment contract dramatically reduced it.
-As we explore later in the paper, the null effect of the Choice arm arises because few people had demand for it, with \hl{XXX\%} choosing the less effective status-quo contract.
+As we explore later in the paper, the null effect of the Choice arm arises because few people had demand for it, with 89\% choosing the less effective status-quo contract.
 
@@
 On the contrary,  7 percentage points fewer borrowers end up in this situation, compared to 12 percent in the status quo contract.
-Conditional on defaulting those assigned to the Force commitment contract have paid 3.9\% less of their loan (col 7), and 14 percentage higher proportion of borrowers pay zero conditional on defaulting, an outcome analogous to selling their pawn (col 8).
+Conditional on defaulting those assigned to the Forced commitment contract have paid 3.9\% less of their loan (col 7), and 14 percentage higher proportion of borrowers pay zero conditional on defaulting, an outcome analogous to selling their pawn (col 8).
 One interpretation of these results is that the Forced commitment contract forces borrowers to think earlier about whether they will indeed be able to eventually recover their pawn, and separates borrowers into those ``selling'' their pawn and those recovering it, reducing the share of undecided borrowers that end up paying interest and end up losing the pawn anyway.
-This mechanism may also help to explain why the Forced commitment contract does not increase the number of visits to the branch to pay (col 9): those recovering their pawn visit more, but those defaulting have 0.19 less visits (col 10).
+This mechanism may also help to explain why the Forced commitment contract does not increase the number of visits to the branch to pay (col 10): those recovering their pawn visit more, but those defaulting have 0.19 fewer visits (col 11).
+Figure \ref{hist_payments} plots the histogram of the timing of payments in each arm, and shows that the commitment does appear to bind in that it generates a highly regular pattern of payments at 30, 60, and 90 days after the loan is taken.
+Finally, observe that Column 9 shows that treatment effects are concentrated in the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery.
 
@@
 Second, we consider a rough proxy of the value of liquidity they lose by paying earlier.
-We act as if each payment they make comes from an additional loan they take, which incurs interest at the same rate as Lender P's loan (7\% per month).
-So far we have valued the collateral at the gold value appraised by the lender, but the piece may be worth more to the borrower than its gold value.
-For many of them the pawned jewelry has sentimental value as well.
-This is reflected in the subjective valuation they reported in the survey which is \hl{XXX\%} higher on average.
+To do this we add the interest costs on to the payments in the Forcing and recompute treatment effects with these payments compounding daily (as if they had to borrow in order to make the more rapid payments).
+Thirdly, so far we have valued the collateral at the gold value appraised by the lender, but the piece may be worth more to the borrower than its gold value.
+For many of them the pawned jewelry has sentimental value.
+This is reflected in the subjective valuation they reported in the survey which is 87\% higher on average.
 Our third extra cost considers this higher value.
-
-\todo[inline]{@Isaac, from Enrique: I would like to understand the liquidity adjustment better.}
 
@@
 Columns (2) and (7) of Table \ref{table_robustness_fc} use the subjective value of the pawn reported by the borrower rather than its appraised value.
-Columns (3) and (8) adjust for self-reported transport costs per visit plus an entire day's wage, both multiplied by the number of visits that each individual made.\footnote{For clients who did not complete the individual survey, we adjust using the mean self-reported transport cost among respondents of the respective branch.} Columns (4) and (9) adjust for our measure of liquidity cost.
+Columns (3) and (8) adjust for self-reported transport costs per visit plus an entire day's wage, both multiplied by the number of visits that each individual made.\footnote{For clients who did not complete the individual survey, we adjust using the mean self-reported transport cost among respondents of the respective branch.} Columns (4) and (9) adjust to consider the liquidity cost.
 Finally columns (5) and (10) include all three changes together.
@@
 Table \ref{repeat_loans} explores the effects of treatment on future pawning behavior.
-Column (1) shows that participants assigned to the the forced arm are 6.7\% more likely to be repeat clients.
+Column (1) shows that participants assigned to the the forced arm are 6.7\% more likely to be repeat clients later.
 %Those in the choice arm are 4\% more likely to pawn again and is not statistically distinct from zero.
@@
 This is unlikely to be the case given that the effect on re-pawning comes after 90 days (during the period of contract demanded payments) and not before  (see columns 2 and 3).
-Column 3 only considers new loans which use different collateral from that of the initial one.
+Column 4 only considers new loans which use different collateral from that of the initial one.
 We do this to foreclose the explanation that those in the Forced arm repeat more because they are more likely to have collateral, as they recover the collateral of the first loan more often.
@@
 
-\subsection{Censoring of Loan Completion}
-
+\paragraph{Censoring of Loan Completion}
 The window of time during which we were able to observe borrower behavior was limited in each branch, meaning that there were loans that we do not see completed (particularly those pawns that were rolled over for one or two further 90-day spells).
-Overall, \hl{XX\%} of all experimental loans are censored, meaning that they neither default nor repay within the observation window.
+Overall, 13\% of all experimental loans are censored, meaning that they neither default nor repay within the observation window.
 In the prior analysis we handle this issue by using outcomes such as `did not default' which are defined even when we do not observe the completion of the loan, and only considering costs that we observe directly.
 We have also showed, however, that one effect of the forcing arm is to accelerate repayment, meaning that it is less likely for loans in this arm to be censored.
-This issue is illustrated in Figure \ref{survival_graph}, which shows the CDF of loan completion (Panel (a)) and loan recovery (Panel (b)) by the number of days since first pawn.
+This issue is illustrated in Figure \ref{survival_graph}, which shows the CDF of loan completion (either default or recovery in Panel (a)) and loan recovery (Panel (b)) by the number of days since first pawn.
 Two features of these graphs are salient for our analysis.
 The first is the extent to which loan outcomes are observed more quickly in the forcing arm.
-This is primarily due to the the substantially higher rate of repayment of Forced Commitment loans at 120 days (~15 pp higher than the other arms).
+This is primarily due to the the substantially higher rate of repayment of Forced Commitment loans at 120 days (15 pp higher than the other arms).
 The second is the very low rate at which loans are recovered in any arm after 120 days.
-In the 180 day window after the second rollover period we see a further ~10 percent of loans repaid in all arms, but these loans are largely dormant, suggesting that many of the censored loans will in fact be defaulted upon.
+In the 180 day window after the second rollover period we see a further 10 percent of loans repaid in all arms, but these loans are largely dormant, suggesting that many of the censored loans will in fact be defaulted upon.
 
 The confluence of censoring and a treatment effect on censoring is problematic from an experimental point of view.
-The approach taken so far is a conservative one in that it inherently assumes that all of the loans outstanding at the end of the observation window will be repaid, making it so that the acceleration of payment observed in the Forced arm does not translate mechanically into a treatment effect on default.
+The approach taken so far is a conservative one in that it inherently assumes that all of the loans outstanding at the end of the observation window will be repaid, making it so that the acceleration of payment observed in the Forced arm does not translate mechanically into the treatments decreasing default.
 Given the centrality of this issue to the observed costs, we now delve into it more detail.
 One way of considering the effect that this issue could have on our results is to make extreme assumptions about the outcome of these loans in the treatment and control so as to bound the possible influence of censoring.
-In Table \ref{mns} we compare the Forced and Control arms, making the bracketing assumptions about repayment on censored loans.
+In Table \ref{bounding_censoring} we compare the Forced and Control arms, making the bracketing assumptions about repayment on censored loans.
 Panel A assumes all censored loans are repaid, and Panel D that all default.
@@
 Hence, while the censoring issue does have a substantial influence on the magnitude of our estimated treatment effects, these  checks confirm that a) the core results are robust to censoring, and b) the headline approach that we take to the issue is conservative and is likely understating the true magnitude of impacts.
-%\end{comment}
 
 \section{Choice and Heterogeneous Treatment Effects}
-\label{sec:choice}
-
-The results from Section \ref{experiment} show that commitment \emph{works}: clients who were assigned to the forced commitment arm experienced substantially lower financial costs on average.
-In spite of this, given the opportunity, only \hl{11\%} of borrowers chose commitment. 
-If the effect of commitment were homogeneous, this would be enough to conclude that the \hl{89\%} who did not choose it would have been financially better-off if they had.
+\label{Choice}
+
+The results from Section \ref{Experiment} show that commitment \emph{works}: clients who were assigned to the forced commitment arm experienced substantially lower financial costs on average.
+In spite of this, given the opportunity, only 11\% of borrowers chose commitment. 
+If the effect of commitment were homogeneous, this would be enough to conclude that the 89\% who did not choose it would have been financially better-off if they had.
 In a world of heterogeneous treatment effects, however, low demand for commitment could still be consistent with borrowers adhering to a standard model of rational choice. 
@@
 Indeed, we find strong evidence that the effect of forced commitment varies substantially across individuals in our experiment: \ref{append:chernozhukov} tests and rejects the null hypothesis of homogeneous treatment effects, following the methodology of \cite{chernozhukov2018generic}.
-So the question remains: do the \hl{89\%} who do not choose commitment know something about their personal situations that we as researchers do not, or are most people in the choice arm making a costly mistake?
+So the question remains: do the 89\% who do not choose commitment know something about their personal situations that we as researchers do not, or are most people in the choice arm making a costly mistake?
 In this section we present of econometric exercises that shed light on this question, leveraging unique features of our experimental design. 
@@
 Since $F_0$ and $F_1$ are point identified, so are $\underline{F}$ and $\overline{F}$.
-\cite{fan2010sharp} show that the sharp (best possible) pointwise bounds for $F_\Delta$ are given by $\underline{F}(\delta) \leq F_\Delta(\delta) \leq \overline{F}(\delta)$
+\cite{fan2010sharp} show that the sharp (best possible) pointwise bounds for $F_\Delta$ are given by $\underline{F}(\delta) \leq F_\Delta(\delta) \leq \overline{F}(\delta)$.
 These bounds are simple to compute, and can be surprisingly informative. 
@@
 Figure \ref{fan_park_bounds} plots the sharp bounds for $F_{\delta}$ based on the APR outcome defined above in Section \ref{costs}.
-Our point estimates of $\underline{F}(0)$ and $\overline{F}_0$ are \hl{XXXX} and \hl{XXXX} respectively, with associated 95\% confidence intervals of \hl{XXXX} and \hl{XXXX}.\footnote{Confidence intervals are constructed using \hl{XXXX} bootstrap.
+Our point estimates of $\underline{F}(0)$ and $\overline{F}_0$ are .03 and .76 respectively, with associated 95\% confidence intervals of [0.027, 0.040] and [0.73, 0.78], which says that at least 24\% of individual borrowers benefit from commitment (and at most 97\%).\footnote{Confidence intervals are constructed using the asymptotic distribution for the bounds.
 See \cite{fan2010sharp} for details.}
-\todo[inline]{@Isaac: Need a sentence saying what the results are: at least such and such percent benefit from forced commitment}
 
@@
 \]
-where $F_1^{-1}$ and $F_0^{-1}$ are the quantile functions of $Y_1$ and $Y_0$.
+where $F_1^{-1}$ and $F_0^{-1}$ are the quantile functions of $Y_1$ and $Y_0$. See figure \ref{te_rankinvariance} in Appendix \ref{App_FOSD}.
 As we show in Appendix \ref{App_FOSD}, $Y_1$ first-order stochastically dominates $Y_0$ in our experiment: every quantile of the distribution of financial cost savings under forced commitment is higher than the corresponding quantile under the control condition, and the same is true for the APR outcome.
 Since this implies that $F^{-1}_1(u) - F^{-1}_0(u)$ is always positive, rank invariance yields an extremely stark conclusion: all borrowers benefit from forced commitment. 
-\todo[inline]{@Everyone: do we want to plot the distribution of treatment effects under rank invariance and say something more about it? Or just add a snappy sentence to conclude this subsection?}
+%\todo[inline]{@Everyone: do we want to plot the distribution of treatment effects under rank invariance and say something more about it? Or just add a snappy sentence to conclude this subsection?}
 
@@
 
-Our assumption-free bounds from the preceding section show that more than 11\% of borrowers would benefit from a policy of forced commitment. 
+Our assumption-free bounds from the preceding section show that more than 24\% of borrowers would benefit from a policy of forced commitment. 
 Intuitively, this seems to suggest that some of the 89\% of borrowers in the choice arm who did \emph{not} choose commitment would have faced lower borrowing costs if they had.
@@
 Moreover, each has testable implications that we fail to reject.
-For details, see \ref{append:exclusion}.
+For details, see \ref{append:exclusion}
 %\todo[inline]{@Frank, do we need to say a bit more about these testable implications or is it too technical? (Enrique)}
@@
 If the TOT is statistically distinguishable from and substantially larger than the TUT, this provides empirical support for the relevance of selection-on-gains in real-world decision-making.
-Because our design identifies all three quantities, it allows us to test this implication directly and to calculate the average selection on gains (ASG):
+Because our design identifies all three quantities (as shown in Appendix \ref{append:randchoice}), it allows us to test this implication directly and to calculate the average selection on gains (ASG):
 \[
@@
 In contrast to both approaches, the controlled choice design uses exogenous experimental variation to point identify the ATE, TOT, and TUT without ruling out unobserved selection-on-gains or relying on additional structural modeling assumptions.
+Figure \ref{tot_tut_graph} provides graphical intuition for our identification approach; derivations appear in \ref{append:randchoice}
 
@@
 \end{align}
-as shown in \ref{append:randchoice}.
+as shown in \ref{append:randchoice}
 For purposes of inference, both the ASB and ASL can be re-written as the difference of coefficients from a pair of just-identified linear IV regressions.
-For details, along with a description of how our companion STATA package carries out cluster-robust inference for these quantities, see \ref{append:randchoice}.
+For details, along with a description of how our companion STATA package carries out cluster-robust inference for these quantities, see \ref{append:randchoice}
 
@@
 Table \ref{tot_tut} calculates the causal quantities described above--TOT, TUT, ASG, ASB, and ASL--for our experimental data, along with robust standard errors for each. 
-For purposes of comparison, the table also presents the ATE results from Section \ref{experiment} above (row 1), along with the corresponding average potential outcomes $\mathbbm{E}[Y_0]$ and $\mathbbm{E}[Y_1]$ (rows 4--5).
+For purposes of comparison, the table also presents the ATE results from Section \ref{Experiment} above (row 1), along with the corresponding average potential outcomes $\mathbbm{E}[Y_0]$ and $\mathbbm{E}[Y_1]$ (rows 4--5).
 The columns of the table correspond to different outcome variables, defined as in Section \ref{costs} above.
@@
 \section{The Case for Paternalism}
-\label{exploring}
+\label{Paternalism}
 
@@
 The argument for compulsory treatment, however, centers on the more surprising result that $\text{TUT}>0$.
-We now investigate several potential explanations for why this might be the case in our context.
-
-\paragraph{Learning.} A first potential explanation involves learning.
+We now investigate several potential explanations for this result.
+For simplicity, we focus on causal effects for the APR outcome throughout this section.
+
+We conduct an exploratory analysis that examines four potential explanations for the positive $\text{TOT}$:  the need to learn, time discounting, present bias, and overconfidence.
+To explore the last two dimensions we will use survey data for which our response rate was 78\%.
+Appendix \ref{app:survey_data} demonstrates that the subsample on whom we have survey data appears to be representative in terms of loan outcomes.
+
+\paragraph{Learning.} A first explanation involves learning.
 Our experiment introduced a new contract into an environment that had not previously featured commitment; perhaps clients required experience to understand its benefits.
 Given the strongly positive impact of forcing, this explanation would suggest that clients who were forced once would subsequently choose commitment if given the chance to do so.
-A subset of \hl{XXXX} clients from our sample returned to pawn again on another day before the end of the experiment.
-Whereas all of the analyses from above restrict attention to the first day on which a given individual pawned, Table \ref{learning_table} presents information about participants' \emph{subsequent} pawning behavior.
-Column (1) considers the 228 clients who returned to pawn again at a day/branch that was randomly assigned to the choice arm.
+A subset of 16\% clients from our sample returned to pawn again on another day before the end of the experiment.
+Whereas all of the analyses from above restrict attention to the first day on which a given individual pawned, Table \ref{learning_table} presents information about participants' \emph{immediate subsequent} pawning behavior.\footnote{In other words, for borrowers who returned to pawn again more than once, this analysis considers only their first repeat pawn.} Column (1) considers the 228 clients who returned (only a second time) to pawn again at a day/branch that was randomly assigned to the choice arm.
 Each of the two rows in this column presents a difference of mean commitment take-up rates, and associated standard error.
@@
 Granted, this is a selected sample because the decision to pawn again is potentially endogenous to the initial treatment allocation.
-For this reason, Column (2) considers the full sample of \hl{4436} borrowers by re-defining the ``outcome variable'' to be an indicator for returning to pawn again at a branch/day when commitment was offered \emph{and} choosing commitment.
-This composite outcome variable is not subject to the sample selection problem.
+For this reason, Column (2) considers the full sample of 4436 borrowers by re-defining the outcome variable to be an indicator for returning to pawn again at a branch/day when commitment was offered \emph{and} choosing commitment.
+This composite outcome variable is not subject to the sample selection problem (although it is directly driven by the decision to repeat borrow).
 The comparison in the two rows remains the same: forced commitment versus control in row one and choice commitment versus forced arms in row two.
@@
 \paragraph{Time discounting.} Discounting is a second potential explanation for our results.
-Our estimated decrease in the financial cost of credit from above ignores discounting, but commitment up-front costs (early payment) in return for delayed benefits (recovery of pawn).
-Highly impatient individuals might therefore rationally choose the \emph{status quo} contract, despite the fact that commitment yields a benefit in raw (undiscounted) returns.
+Our estimated decrease in the financial cost of credit from above ignores discounting, but commitment involves incurring up-front costs (early payment) in return for delayed benefits (a higher probability of recovering one's pawn).
+Highly impatient individuals might therefore rationally choose the \emph{status quo} contract, despite the benefits that commitment yields in terms of raw (undiscounted) returns.
 To investigate this explanation we calculate the net present value (NPV) of the financial cost $\text{TUT}$ effect under different hypothetical discount rates, given the timing of repayment and pawn recovery.
 Figure \ref{fc_discount_rates} presents the results of this exercise.
-The solid line gives the adjusted TUT effect at a specified annual discount rate, while the shaded region \hl{regions? what's the second one?} gives the associated \hl{XXXX} confidence interval.
+The solid line gives the TUT effect adjusted for a specified annual discount rate, while the shaded regions gives the associated 95\% \& 90\% confidence interval.
 We see that non-choosers continue to experience significant decreases in NPV financial costs up to annual discount rates of 4,000\%, and the NPV remains positive, although not significant, at 10,000\% discount rates.
 As such, discounting is unlikely to explain why those who benefit, on average, from commitment fail to choose it when offered.
-
-\paragraph{Survey Data.}
-The remaining exercises in the paper require information from the intake survey, and hence restrict attention to the subset of individuals who responded to the survey. 
-Table \ref{SS_cond_survet} presents information about survey non-response.
-Panel A is a balance table that compares loan amount and day of the week across treatment arms for the subset of borrowers who responded to \hl{at least one survey question}.
-The p-values in the fourth column are for the F-test of no difference of means across treatment arms. 
-Panel B presents response-rates by question for each arm of the experiment, along with p-values for the F-test of no difference in question-specific response rates across treatment arms. 
-This panel uses data from participants who answered \hl{at least one survey question} and went on to pawn on the same day as their survey response.
-From the table, we see that loan amount and weekday are balanced across treatment arms among survey respondents and that response rates are stable across treatment arms.
-Table \ref{TUT_cond_survet} shows how the estimated TUT effect changes when restrict our estimation sample based on survey response.
-The first row of the table presents TUT results for the financial cost outcome, while the second present TUT results for the APR outcome.
-In each row, column (1) presents the full-sample TUT estimate and standard error.
-The remaining columns restrict the sample to borrowers who answered a particular survey question or set of questions.
-For example, column (4) presents results for borrowers who answered the two questions needed to compute our measure of ``present bias'' discussed in the next paragraph, while column (9) present results restricted to participants who disclosed their sex.
-As seen from the table, our TUT estimates are quite stable across sub-samples defined by survey response.
-In each case they are positive and of the same magnitude as the corresponding full-sample estimate, although statistical significance varies depending on the size of the corresponding sub-sample. 
-For these reasons, we are comfortable relying on data for survey respondents in the empirical exercises that follow.
-In exercises that rely on a single survey question, we use data for every borrower who answered that question.
-In the random forest exercises described below, we use data for every borrower who answered at least one survey question.
 
@@
 A large share of ``na\"ive'' hyperbolics in the population--borrowers who are unaware that they are hyperbolic discounters--could therefore drive a large and positive $\text{TUT}$.
-Our baseline survey included standard questions about discount rates between today and a month in the future versus discount rates between three and four months in the future.\footnote{The remaining exercises in the paper require information from the intake survey, and hence use only the subset of individuals who responded to the survey.
-While this is a selected sample, estimates of the ATE, TOT, and TUT are nearly identical whether computed from the full sample survey-respondent sub-sample.}  This allows us to classify borrowers who display more impatience over immediate delays as present biased.
+Our baseline survey included standard questions about discount rates between today and a month in the future versus discount rates between three and four months in the future.
+This allows us to classify borrowers who display more impatience over immediate delays as present biased.
 This measure of financial hyperbolicity is widely used in survey research, although it is not without problems.\footnote{Our measure is dichotomous, and it is not incentivized.
@@
 
-If we could perfectly measure present bias, we could divide the sample into three groups: sophisticated hyperbolics (who chose commitment), time-consistent non-choosers (for whom forcing will not be effective), and naive hyperbolic non-choosers (who will benefit from forced commitment).
-If present bias fully explains the low take-up rate of voluntary commitment, we should find that the TUT for present-biased borrowers is positive while the TUT for all other borrowers is not.
+If we could perfectly measure present bias, we could divide the sample into three groups: sophisticated hyperbolics (who chose commitment), time-consistent non-choosers (for whom forcing will not be effective), and na\"{i}ve hyperbolic non-choosers (who will benefit from forced commitment).
+If present bias fully explains the low take-up rate of voluntary commitment, we should find that the TUT for present biased borrowers is positive while the TUT for all other borrowers is not.
 This is because TUT effects already restrict attention to borrowers who would not choose commitment.
@@
 The right panel of Figure \ref{tut_beh_partition} carries out a feasible version of this exercise using our survey measure of present bias.
-The overall TUT estimate for all borrowers who answered the present-bias questions is given in blue, along with a \hl{95?} confidence interval.
-The corresponding TUT estimate and confidence interval for present-biased borrowers is given in green, while TUT estimate and confidence interval for all other borrowers is given in red.
-All three estimates are positive and similar in magnitude, although imprecisely estimated given survey non-response.
-Taking our survey measure of present-vias at face value, we find no indication that present-bias explains our positive estimated TUT.
+The overall TUT estimate for all borrowers who answered our present-bias survey questions is given in blue, along with a 95\% confidence interval.
+The corresponding TUT estimate and confidence interval for present-biased borrowers is given in green; results for all other borrowers are shown in red.
+By the law of iterated expectations, the blue overall estimate must lie between the green and red sub-group estimates.
+In fact, all three estimates are positive and similar in magnitude, although imprecisely estimated given the extent of survey non-response for these questions.
+Taking our survey measure of hyperbolicity at face value, we find no indication that present-bias explains our positive estimated TUT.
 
@@
 
-%\todo[inline]{This stuff needs to be removed / updated / edited based on the todos listed above.}
-%For any binary pre-treatment covariate $X_i$, we can calculate the relative contributions of any two groups $X_i=0$ or $X_i=1$ to the overall $\text{TUT}$ effect using the following decomposition: 
-%\begin{align}
-%\nonumber
-%        1=& \frac{\mathbbm{E}[Y_{1i}-Y_{0i} | C_i=0, X_i=1]}{\text{TUT}}\mathbbm{P}(X_i=1 | C_i=0) \\
-%        \quad &+ \frac{\mathbbm{E}[Y_{1i}-Y_{0i}| C_i=0, X_i=0]}{\text{TUT}}\mathbbm{P}(X_i=0 | C_i=0)
-%        \label{eq:decomp}
-%\end{align}
-%where $\text{TUT}$ is the \emph{overall} treatment on the untreated effect and $\mathbbm{E}[Y_{1i} - Y_{0i}|C_i = 0, X_i = x]$ is the TUT for borrowers with $X_i = x$.    
-%If, as the behavioral theory outlined above would predict, the $\text{TUT}$ arises solely from hyperbolics then term with $X_i=1$ the former term will be one and the term with $X_i = 0$ will be zero.
-%We explore the empirical support for explanation below.
-%But first we consider a second potential behavioral explanation.
-
-\paragraph{Sure confidence.} While 74\% of control participants believe they have a 100\% chance of recovering their pawn, in reality only \hl{56\%} will go on to do so.
-This suggests a market characterized by over-optimism.
-Incorrect expectations about recovery probabilities could explain low take-up in that individuals who believe they will repay may, rationally, choose to forgo the costs associated with commitment that are designed to induce repayment.
-Hence over-optimistic expectations in recovery probabilities will translate directly into under-adoption of preventive measures.
-Similar to our definition of hyperbolicity above, we define a binary attribute we call ``sure-confidence.'' This measure equals one for any individuals who say at the time of borrowing that they have a 100\% probability of recovering their pawn.
-The same decomposition that we used above in our discussion of hyperbolic discounting, \eqref{eq:decomp}, can be used to explore the extent to which sure confidence explains our positive and significant TUT estimate by redefining the covariate $X_i$.
-
-\todo[inline]{check in all the text we have used 56\% as the number that dont recover.}
-
-Figure \ref{tut_beh_partition} shows the relative contributions of present bias and sure-confidence for the $\text{TUT}$.
+\paragraph{Sure confidence.} While 72\% of survey respondents believe they have a 100\% chance of recovering their pawn, in reality only 48\% will go on to do so.  
+This suggests a borrower pool characterized by over-optimism.
+Incorrect expectations about recovery probabilities could explain low take-up if individuals who \emph{believe} that they are certain to repay choose, rationally given their incorrect beliefs, to forgo the costs associated with commitment that are designed to induce repayment.
+We now explore whether over-optimistic expectations of recovery probability can explain our positive overall TUT estimate.
+To do this, we carry out an analysis that is analogous to our present bias exercise from the preceding paragraph, comparing the overall TUT estimate to estimates computed for two sub-groups.
+Here, however, the groups are defined by a binary variable that we call ``sure-confidence.''
+This measure equals one for any individuals who say at the time of borrowing that they have a 100\% probability of recovering their pawn, zero otherwise.
+The left panel of Figure \ref{tut_beh_partition} presents the results for this exercise.
+The overall TUT estimate for all borrowers who answered our sure-confidence survey questions is given in blue, along with a 95\% confidence interval.
+The corresponding TUT estimate and confidence interval for sure-confident borrowers is given in green; results for all other borrowers are shown in red.
+As above, the blue overall estimate must lie between the green and red sub-group estimates by the law of iterated expectations.
+In contrast to our results for present bias, shown in the right panel of Figure \ref{tut_beh_partition}, we estimate a higher TUT effect for sure-confident borrowers compared to all other borrowers and a negative, although insignificant, effect for borrowers who are not sure-confident.
+
+As discussed above, our measure of hyperbolicity is based on un-incentivized responses in a short survey and so is likely to be noisy; nonetheless we see no evidence here that it drives the forcing effect.
+Rather, the analysis from Figure \ref{tut_beh_partition} suggests that the effectiveness of paternalism in our experiment may be driven by a group of \emph{overconfident} borrowers who, heedless of the risk of default, fail to choose commitment despite benefiting substantially when they are forced to commit.
+
+%Figure \ref{tut_beh_partition} shows the relative contributions of present bias and sure-confidence for the $\text{TUT}$.
 In each figure the orange bar represents the contribution from those who do not possess the attribute, and the blue bar from those that do.
 We see that the forcing effect is localized mostly to those who are \textit{not} time inconsistent, contradicting naive hyperbolicity as the justification for paternalism.
-In contrast, sure-confidence being a category that completely isolates the $\text{TUT}$, suggesting that forcing works for those who do not consider repayment structure because they don't think they need it.
-Our measure of hyperbolicity is based on unincentivized responses in a short survey and so is likely to be noisy; nonetheless we see no evidence here that it drives the forcing effect.
-Rather, this analysis suggests that paternalism is effective in this case is because of a group of overconfident borrowers who, heedless of the possibility of default, do not choose commitment and yet would benefit substantially from receiving it.
-
-If the attribute of ``sure confidence'' proves so important in explaining the TUT, what are its determinants?
-In Figure \ref{determinants_sure} we plot the coefficient estimates from a regression that explains sure confidence with a battery of individual-level characteristics.
-Older males are more likely to be sure confident, as are those with more education.
-Taken at face value, the sure confident also appear to face less financial stress, to have less trouble paying bills, and to be more frequently relied upon financially by family members.
-However, through a behavioral lens it is also possible that the type of person who is over-confident in their ability to repay a loan also maintains fictions in other domains of their financial life, providing answers to the baseline survey questions that exaggerate their degree of economic security.
+Instead, we see sure-confidence being a category that completely isolates the $\text{TUT}$, suggesting that forcing works for those who do not consider repayment structure because they don't think they need it.
+
+If the attribute of ``sure confidence'' proves so important in explaining the positive TUT, what are its determinants?
+In Figure \ref{determinants_sure} we plot the coefficient estimates from a regression that predicts sure confidence with a battery of individual-level characteristics.
+Older males are more likely to be sure-confident, as are those with more education.
+Taken at face value, the sure-confident also appear to face less financial stress, to have less trouble paying bills, and to be more frequently relied upon financially by family members.
+Viewed through a behavioral lens, however, it is also possible that the type of person who is over-confident in their ability to repay a loan also maintains fictions in other domains of their financial life, providing answers to the baseline survey questions that exaggerate their degree of economic security.
 In any case it appears that sure confidence may be difficult to predict with easily-observed and objective demographic criteria, a point to which we return below.
 
-\subsection{Analyzing Choice versus Paternalism Using a Causal Forest} \label{sec:RF}
+\subsection{Analyzing Choice versus Paternalism Using Causal Forests} \label{sec:RF}
 
@@
 On average, the commitment contract benefits both those who would choose it and those who would not.
-In Section \ref{sec:bounds}, we went beyond average effects by presenting bounds on the distribution of individual treatment effects.
+In Section \ref{sec:bounds}, we briefly went \emph{beyond} average effects by presenting bounds on the distribution of individual treatment effects.
 Because they made no assumptions beyond random assignment, these bounds were relatively wide.
@@
 Rank invariance, however, is an extremely strong assumption.
-In this section, we explore conditional average treatment effects given observed covariates. 
-In this section, we explore a middle way between the two extremes, by considering conditional average treatment effects and conditional TOT and TUT effects, given our survey measures.
-This exercise will allow us to determine whether there are groups of borrowers who are on average \emph{harmed} by commitment.
-Under the stronger assumption that our observed survey measures capture the main sources of treatment effect heterogeneity, this allows us to approximate individual-level counterfactuals, to consider whether particular borrowers made ``mistakes'' in their choice of contract.
-\todo[inline]{@Frank: read sections 6.1 and 7 of Athey et al 2019 and re-write this section as needed to explain what they do and we use.}
-To estimate conditional teratment effects, we adopt the random forest approach of \cite{athey2019generalized}.
-to estimate Conditional Average Treatment Effects (causal RF), or the Conditional TUT and TOT (instrumental RF).
-These impacts allow us to think about whether individuals made ``mistakes'' in their choices.
-Specifically, for each client in the choice arm we want to know how much cost savings would she have gained had she chosen the opposite contract.
-We do this in two steps.
-First, we use  \cite{atheygrf}'s generalized random forests methodology to estimate the impact of the forced commitment arm relative to the control (forced status quo) at the individual level.
-The method generates a partition of the space of characteristics $X$, where each element of the partition is a leaf, and each leaf contains treatment and control clients with similar characteristics $x \in X$ which are used to calculate unbiased treatment effects for that leaf.
-The optimal partition is that which minimizes expected mean squared error of treatment effects predictions out-of-sample.
-The tree is ``honest'' in that uses one sub-sample to build the trees that make up the random forest and another one to estimate treatment effects within those trees.
-\cite{atheygrf} show that their treatment effects are asymptotically normal, which allows us to construct confidence intervals for our treatment estimate in each leaf.
-This method gives us the average causal effect on financing cost of getting the forced commitment contract instead of the status quo contract for a client $i$ with characteristics $x_i$; call it $TE^{F}_{i}(x_i)$.\footnote{Figure \ref{causal_tree1} and \ref{causal_tree2} provide an illustration of the splits (leaves) that emerge from our implementation of the RF.
+In this section, we explore a middle way between the two extremes, by considering conditional average treatment effects and conditional TOT and TUT effects, given our survey measures (note that this approach also imposes the exclusion restriction within each leaf of the tree).
+This exercise provides more fine-grained information about treatment effect heterogeneity.
+Among other things, it will potentially allow us to identify groups of borrowers who are on average \emph{harmed} by commitment.
+Under the stronger assumption that our observed survey measures capture the main sources of treatment effect heterogeneity, this exercise will allow us to approximate individual-level counterfactuals, to consider whether particular borrowers made ``mistakes'' in their choice of contract.
+
+To estimate conditional average treatment effects given administrative and survey data, we use the function \texttt{causal\_forest()} of the \texttt{grf} R package; to estimate conditional TOT and TUT effects we use the function \texttt{instrumental\_forest()} function from the same package.
+In each case, we use the default parameter values from the \texttt{grf} package with one exception: we increase the number of trees from the default value of 2000 to 5000.
+The functions \texttt{causal\_forest()} and \texttt{instrumental\_forest()} implement special cases of the ``generalized random forest'' methods of \cite{atheygrf}.
+In broad strokes, these functions combine a large number of regression trees that recursively partition the covariate space to estimate conditional average effects.
+Figure \ref{causal_tree1} illustrates the partition that emerges from one of the trees in our causal forest implementation.
+The trees are ``honest'' in that observations used to determine the optimal partition are not used to estimate effects, and vice-versa.
+While closely related to more familiar ``regression-tree'' random forests, the generalized random forest approach explicitly targets the parameter of interest--a conditional ATE or IV estimand--when choosing the optimal covariate partition.\footnote{For more details, see \cite{atheygrf} and the \texttt{grf} documentation: \url{https://grf-labs.github.io/grf/}.}
+When constructing our random forest estimates of heterogeneous treatment effects, we use observations for all borrowers who answered at least \emph{part} of the intake survey.
+We impute the median response for the missing values, while also including an indicator whether the variable originally had a missing value.\footnote{Results are similar if we manually include interactions between the original/imputed variable and an indicator for missingness.
+This is as expected, given that tree-based methods by their nature ``automatically'' consider interactions of arbitrary orders.}
+
+Figure \ref{heterogeneous_effects} plots densities of the estimated conditional ATE, TOT, and TUT effects from the generalized random forest models described above.
+In each case, the outcome variable is APR benefit, i.e.\ the reduction in APR from a commitment contract.
+As we see from the figure, the conditional average effects are overwhelmingly positive. 
+The TUT density is particularly interesting for the question of paternalism since, as emphasized above, it presents conditional average effects for borrowers who would not voluntarily choose commitment.
+Only 13\% of our estimated conditional TUTs are negative, with a 95\% confidence interval of [11\%, 17\%].\footnote{The generalized random forest approach of \cite{atheygrf} produces conditional average effect estimators that are asymptotically normal, and includes methods for computing correct standard errors.
+These methods are relatively straightforward because the trees are ``honest'' in that observations used to determine splits in the recursive partitioning algorithm are not used for causal effect estimation and vice-versa.
+Our inferences in this section are carried out by ``bootstrapping the limit experiment,'' i.e.\ simulating from the normal limit distributions using the estimated standard errors.}
+To be clear, this is a probability statement about conditional average effects over the distribution of \emph{covariates}.
+In particular, we estimate that   
+\[
+\int \mathbbm{1}\{\mathbb{E}[Y_1 - Y_0| X = \mathbf{x}, C = 0] > 0\} \, f(\mathbf{x}|C=0) \, \mathrm{d}\mathbf{x} 
+\]
+is approximately 0.13.
+The share of non-choosers with a positive conditional \emph{average} treatment effects need not equal the share with a positive \emph{individual} effects, i.e.\ $\mathbbm{P}(Y_1 > Y_0| C = 0)$.
+But the more treatment effect heterogeneity that $X_i$ explains, the closer these two values become.
+Figure \ref{heterogeneous_effects} strengthens our argument, introduced in section \ref{Choice}, that not enough borrowers choose commitment.
+
+Under the assumption that our instrumental forest estimates capture the main sources of treatment effect heterogeneity, we can use them to assess whether particular borrowers in the choice arm made ``mistakes'' in their decision to accept or refuse the commitment contract, in terms of predicted financial costs of the loan.
+To do this we use the same information that is depicted in Figure \ref{heterogeneous_effects}, but present it in a different way.
+For each non-chooser in the choice arm, we use our instrumental forest from above to estimate the conditional TUT effect, given her observed covariates.
+Of course conditional average effects need not equal individual treatment effects, and our APR outcome may not capture all of the costs and benefits that are relevant for individual borrowers' decisions.
+To account for this, we define a ``mistake'' for a non-chooser to be a conditional TUT estimate that significantly exceeds some large and positive APR threshold, e.g.\ 25\%. 
+At any such threshold, we can calculate the percentage of non-choosers in the choice arm who made a ``mistake'' by not choosing commitment.   
+(If treatment it beneficial, it should be chosen.)
+The results of this exercise can be read off from the green curve in Figure \ref{choose_wrong}.
+Defining $F_{\text{TUT}}(\delta)$ to be the CDF corresponding to the density of conditional TUT estimates from Figure \ref{heterogeneous_effects}, the green curve in Figure \ref{chose_wrong} is merely $[1 - F_{\text{TUT}}(\delta)] \times 100\%$.
+In other words, the green curve gives the percentage of non-choosers who made a ``mistake'' when mistakes are defined at a particular APR threshold.
+The green shaded region gives associated 95\% pointwise confidence bounds.
+
+For choosers we follow an analogous approach, defining a ``mistake'' as a \emph{negative} conditional TOT effect that exceeds a particular APR threshold.
+(If treatment is harmful, it should not be chosen.)
+The results for choosers can be read from the the red curve in Figure \ref{choose_wrong}.
+If $F_{\text{TOT}}(\delta)$ denotes the CDF corresponding to the density of conditional TOT estimates from Figure \ref{heterogeneous_effects}, then the red curve is merely $F_{\text{TOT}}(-\delta) \times 100\%$.
+In other words, the red curve gives the percentage of choosers who made a ``mistake'' when mistakes are defined at a particular APR threshold.
+The red shaded region gives associated 95\% pointwise confidence bounds.
+Note that we use a \emph{positive} APR threshold to denote a mistake for both choosers and non-choosers. 
+This ensures that bigger mistakes are always to the \emph{right} of smaller mistakes for both the green and red curves.
+The blue curve in Figure \ref{choose_wrong} gives the \emph{overall} percentage of borrowers in the choice arm who made a ``mistake'' at a particular APR threshold.
+This total is computed by taking a weighted average of the green (non-choosers) and red (choosers) curves, with weights equal to their shares in the choice arm.\footnote{The blue curve is very similar to the green curve because 89\% of borrowers in the choice arm are non-choosers.}
+
+The results in Figure \ref{choose_wrong} suggest that a large fraction of non-choosers made mistakes by not choosing commitment.
+Even at an APR threshold as large as 25\%, we estimate that more than half of them should have chosen commitment in order to lower financial costs.
+In contrast, relatively few choosers appear to have made mistakes by choosing commitment.
+This now allows us to make a stronger statement in favor of paternalism; not only does forced commitment generate large benefits on average, but it also benefits the vast majority of borrowers \emph{who would be coerced} under a policy of forced commitment.
+
+%As we increase the threshold on the size of the mistake necessary to be classified as having made the wrong choice, by definition the share of mistakes in both groups falls.
+
+%Among choosers, only 18\% would have had superior outcomes had they not complied, whereas among non-choosers almost 80\% made a mistake according to this definition.
+Because this arm is comprised of 89\% non-choosers, the overall rate of mistake in the arm was around 68\%.
+
+%benefit is the case that forcing commitment generates large benefits on average, but it is also generating benefits for almost 90\% of the forced population.
+
+%\todo[inline]{ 
+%Can read this from red curve (and error bars) in Figure \ref{choose_wrong}, simply $F(-x)$ for the conditional TOT.
+Comment on results.
+Relatively few negative conditional TOT estimates: around 20\% with wide confidence bounds.
+Again say APR threshold of 25\%.
+Then say something like 8\% to 27\% \hl{???} mistakes.
+%Blue curve: combine to understand mistakes overall across choosers and non-choosers.
+Weighted average of red (TOT/chooser) and green (TUT/non-chooser) with weights corresponding to shares of each type.
+Very similar to green curve since 89\% are non-choosers and we estimate that relatively few choosers had a negative conditional average treatment effect.}
+
+%These impacts allow us to think about whether individuals made ``mistakes'' in their choices.  
+%Specifically, for each client in the choice arm we want to know how much cost savings would she have gained had she chosen the opposite contract. 
+%We do this in two steps.  
+%First, we use  \cite{atheygrf}'s generalized random forests methodology to estimate the impact of the forced commitment arm relative to the control (forced status quo) at the individual level.  
+%The method generates a partition of the space of characteristics $X$, where each element of the partition is a leaf, and each leaf contains treatment and control clients with similar characteristics $x \in X$ which are used to calculate unbiased treatment effects for that leaf.
+%The optimal partition is that which minimizes expected mean squared error of treatment effects predictions out-of-sample. 
+%The tree is ``honest'' in that uses one sub-sample to build the trees that make up the random forest and another one to estimate treatment effects within those trees.
+%\cite{atheygrf} show that their treatment effects are asymptotically normal, which allows us to construct confidence intervals for our treatment estimate in each leaf. 
+%This method gives us the average causal effect on financing cost of getting the forced commitment contract instead of the status quo contract for a client $i$ with characteristics $x_i$; call it $TE^{F}_{i}(x_i)$.\footnote{Figure \ref{causal_tree1} and ???
+provide an illustration of the splits (leaves) that emerge from our implementation of the RF.
 \todo[inline]{I think we should list in a footnote which are the `wide' variables we are using.}}
 
-\paragraph{Personalized benefit results.} Using the test provided by \cite{chernozhukov2018generic}, we reject the null of homogeneity in treatment effects and so begin our analysis of heterogeneity confident that it exists.
+%\paragraph{Personalized benefit results.} Using the test provided by \cite{chernozhukov2018generic}, we reject the null of homogeneity in treatment effects and so begin our analysis of heterogeneity confident that it exists.
 Figure \ref{heterogeneous_effects} illustrates the substantial impact of the forced commitment arm on APR, financial cost and other outcomes.
@@
 
-\todo[inline]{@Frank: note that we for the wide forest we use everyone who answered at least one survey question in the random forests.
+%\paragraph{Estimates of financial cost `mistakes'.} In a second step we predict treatment effects for clients \textit{in the Choice arm} using the partition into leaves and the treatment effect from step 1, that is client $j$ is imputed the treatment effect of the leaf corresponding to her characteristics $x_j$.
+We call this counterfactual treatment effect $\widehat{TE}^{F}_{j}(x_j)$.
+This is precisely the counterfactual we wanted, because it lets us relate observed individual choices with estimated individual-level treatment effects.\footnote{This extrapolation of the treatment effects assumes that choice itself --conditional on a given contract-- does not affect behavior (note the evidence in the prior section suggesting this is the case).
+Although the extrapolation is to another population, by randomization it is a statistically identical population with common support.} Armed with this, we say that a client made a ``mistake'' if either she chose the status quo contract and her $\widehat{TE}^{F}_{i}$ is negative (i.e.
+more cost saving from the Forced contract), or if she chose the Commitment contract and $\widehat{TE}^{F}_{i}$ is positive, (i.e.
+financial costs are larger for the Commitment contract).
+When a client made a choice mistake, we say that its money-metric values is the absolute value of $|\widehat{TE}^{F}_{i}|$.
+
+%Using the forcing arms and extrapolating to the choice arms.
+%Then, we predict these treatment effects for everybody in the choice arm using characteristics $x_i$.
+Let $\widehat{TE}^{fee}_{i}$ be the predicted financial cost savings for person $i$ of choosing the Forced Commitment contract rather than the status quo one, divided by the size of her loan (i.e.
+the negative value of the predicted treatment effect on financial cost for person $i$).
+$\widehat{TE}^{sq}_{i}$ is the analogous for the status quo contract.
+We define the choice of person $i$ to be a ``mistake'' if
+
+%\begin{equation}
+% \{ i \; \text{chose} \; sq \; \text{and} \; \;  \widehat{TE}^{fee}_{i}>\widehat{TE}^{sq}_{i} + z \} \; \text{or} \; \{ i \; \text{chose} \; fee \; \text{and} \; \;  \widehat{TE}^{fee}_{i}<\widehat{TE}^{sq}_{i} - z \}
+%\end{equation}
+
+%Since the prediction of the treatment effect is an estimate and has noise, we do two things.
+First, we normalize $\widehat{TE}^{F}_{i}$ by the value of the loan of person $i$ and introduce a threshold parameter $z$ and say that a choice is a ``mistake'' if the alternative contract would generate greater than $z$ in savings.
+We vary this threshold from 0\% to 15\% of the value of the loan.
+Second, we take into account uncertainty in estimation of treatment effects and report results using the extremes of the 95\% confidence interval bounds for $\widehat{TE}^{F}_{i}$.
+
+%Figure \ref{choose_wrong}(a) plots on the Y axis the fraction of clients that made a choice ``mistake'' and on the X axis the threshold $z$.
+When $z=0$, we calculate that about 82\% of clients in the Choice arm chose contracts that induced \textit{higher} financial cost.
+Most mistakes are failures to choose the fee-commitment contract ({97}\%), while only {4}\% of those who chose the fee-commitment contract would have been better in the status-quo one.
+The average mistake in pesos is \$250.
+%(90\% confidence interval [140,390]).
+
+%However, the fraction of non-choosers making a mistake remains almost 20\% even at the highest threshold used (\$80 pesos), and panel b shows the \textcolor{red}{Complete this when understand figure}.
+Panel C conducts a related but distinct exercise, showing the fraction of the entire control sample who would do better if assigned to the Forced arm; using the smallest threshold this fraction is over 95\%, showing that in this context there is an almost across-the board welfare benefit arising from this arm.
+Since the only potential financial cost of the forced arm arises from individuals who would be induced to partially repay but then default anyways, this result suggests that very few such borrowers exist.
+
+%Panel C of this figure replicates this exercise for the forced commitment arm, with the difference being that the relevant treatment effect to match is now the ATE of the forced commitment arm.
+This allows us to identify the winners and losers from paternalism in a nuanced manner, since members of groups with CATEs$<$0 are hurt and everyone else is helped.
+Because the ATE$>$TUT, this exercise results in an even larger fraction of individuals benefiting from commitment; here we find that fully 91\% of individuals are better off being forced into commitment than staying in the control.
+.
+
+\subsection{Can we target paternalism?}
+
+%\todo[inline]{@Frank: note that we for the wide forest we use everyone who answered at least one survey question in the random forests.
 We have dummies for missingness of any of the predictors.
@@
 
-\paragraph{Estimates of financial cost `mistakes'.} In a second step we predict treatment effects for clients \textit{in the Choice arm} using the partition into leaves and the treatment effect from step 1, that is client $j$ is imputed the treatment effect of the leaf corresponding to her characteristics $x_j$.
-We call this counterfactual treatment effect $\widehat{TE}^{F}_{j}(x_j)$.
-This is precisely the counterfactual we wanted, because it lets us relate observed individual choices with estimated individual-level treatment effects.\footnote{This extrapolation of the treatment effects assumes that choice itself --conditional on a given contract-- does not affect behavior (note the evidence in the prior section suggesting this is the case).
-Although the extrapolation is to another population, by randomization it is a statistically identical population with common support.} Armed with this, we say that a client made a ``mistake'' if either she chose the status quo contract and her $\widehat{TE}^{F}_{i}$ is negative (i.e.
-more cost saving from the Forced contract), or if she chose the Commitment contract and $\widehat{TE}^{F}_{i}$ is positive, (i.e.
-financial costs are larger for the Commitment contract).
-When a client made a choice mistake, we say that its money-metric values is the absolute value of $|\widehat{TE}^{F}_{i}|$.
-
-%Using the forcing arms and extrapolating to the choice arms.
-%Then, we predict these treatment effects for everybody in the choice arm using characteristics $x_i$.
-Let $\widehat{TE}^{fee}_{i}$ be the predicted financial cost savings for person $i$ of choosing the Forced Commitment contract rather than the status quo one, divided by the size of her loan (i.e.
-the negative value of the predicted treatment effect on financial cost for person $i$).
-$\widehat{TE}^{sq}_{i}$ is the analogous for the status quo contract.
-We define the choice of person $i$ to be a ``mistake'' if
-
-%\begin{equation}
-% \{ i \; \text{chose} \; sq \; \text{and} \; \;  \widehat{TE}^{fee}_{i}>\widehat{TE}^{sq}_{i} + z \} \; \text{or} \; \{ i \; \text{chose} \; fee \; \text{and} \; \;  \widehat{TE}^{fee}_{i}<\widehat{TE}^{sq}_{i} - z \}
-%\end{equation}
-
-Since the prediction of the treatment effect is an estimate and has noise, we do two things.
-First, we normalize $\widehat{TE}^{F}_{i}$ by the value of the loan of person $i$ and introduce a threshold parameter $z$ and say that a choice is a ``mistake'' if the alternative contract would generate greater than $z$ in savings.
-We vary this threshold from 0\% to 15\% of the value of the loan.
-Second, we take into account uncertainty in estimation of treatment effects and report results using the extremes of the 95\% confidence interval bounds for $\widehat{TE}^{F}_{i}$.
-
-%Figure \ref{choose_wrong}(a) plots on the Y axis the fraction of clients that made a choice ``mistake'' and on the X axis the threshold $z$.
-When $z=0$, we calculate that about 82\% of clients in the Choice arm chose contracts that induced \textit{higher} financial cost.
-Most mistakes are failures to choose the fee-commitment contract ({97}\%), while only {4}\% of those who chose the fee-commitment contract would have been better in the status-quo one.
-The average mistake in pesos is \$250.
-%(90\% confidence interval [140,390]).
-
- Figure \ref{choose_wrong}, Panel A shows the results of this exercise, reinforcing the general superiority of commitment.
-Among choosers, only 18\% would have had superior outcomes had they not complied, whereas among non-choosers almost 80\% made a mistake according to this definition.
-Because this arm is comprised of 89\% non-choosers, the overall rate of mistake in the arm was around 68\%.
-As we increase the threshold on the size of the mistake necessary to be classified as having made the wrong choice, by definition the share in both groups falls, and among choosers the number making an error falls quite quickly to zero.
-
- %However, the fraction of non-choosers making a mistake remains almost 20\% even at the highest threshold used (\$80 pesos), and panel b shows the \textcolor{red}{Complete this when understand figure}.
-Panel C conducts a related but distinct exercise, showing the fraction of the entire control sample who would do better if assigned to the Forced arm; using the smallest threshold this fraction is over 95\%, showing that in this context there is an almost across-the board welfare benefit arising from this arm.
-Since the only potential financial cost of the forced arm arises from individuals who would be induced to partially repay but then default anyways, this result suggests that very few such borrowers exist.
-
-Panel C of this figure replicates this exercise for the forced commitment arm, with the difference being that the relevant treatment effect to match is now the ATE of the forced commitment arm.
-This allows us to identify the winners and losers from paternalism in a nuanced manner, since members of groups with CATEs$<$0 are hurt and everyone else is helped.
-Because the ATE$>$TUT, this exercise results in an even larger fraction of individuals benefiting from commitment; here we find that fully 91\% of individuals are better off being forced into commitment than staying in the control.
-This now allows us to make a stronger statement in favor of paternalism; not only is the case that forcing commitment generates large benefits on average, but it is also generating benefits for almost 90\% of the forced population.
-
-\subsection{Can we target paternalism?}
-
-Despite having shown such a large majority of individuals benefit from paternalism, it is still natural to question whether we are able to target commitment in such a manner as to only force it upon those who benefit.
+Despite having shown such a large majority of individuals benefit from paternalism, it is still natural to ask whether we are able to target commitment in such a manner as to only force it upon those who benefit.
 For a financial firm to engage in this type of targeting under real-world circumstances, we must impose several constraints on the targeting rule.
 First, it will in general not be possible to use the numerous subjective and unverifiable questions we asked in the baseline survey as inputs to the rule because the answers to these questions can be manipulated by the clients, and would likely change when they become incentivized.
+This leaves us with only a few objective covariates that could be used to target: age, gender, HS education or above, desired loan size, and whether that individual has ever pawned before.
+We call these the ``narrow'' covariate set below, to contrast with the full set of survey variables, which we call the ``wide'' covariate set.
 Secondly, it will not be attractive for a commercial firm to ask individuals whether they want to voluntarily accept commitment and then to force upon those who say no against their will.
 So the choice variable itself cannot be used to target other than in a voluntary program.
-This leaves us with only a few objective covariates that could be used to target: age, gender, HS education or above, desired loan size, and whether that individual has ever pawned before.
-
-\paragraph{Narrow inputs targeting.} To  consider targeting effectiveness we must begin from an individual-specific ground truth, which we take from our estimated RF from Section \ref{sec:RF}  which used the `wide' set of covariates (wide RF).
-We then analyze how well we can predict the losers from paternalism using the `narrow' set of non-manipulable covariates listed above (narrow RF).
-Figure \ref{wide_narrow_forests} shows the relationship between the CATEs estimated from the RF using the `wide' and `narrow' covariates.
-It visually obvious from this figure that we generate substantially less heterogeneity when using the narrow covariate set, although the the Chernozhukov test on the narrow RF does still indicate significant heterogeneity.
-
-\paragraph{Targeting assessment.} To more directly examine the implications of attempting to target commitment, we use two different techniques to predict who should be assigned to the commitment arm.
-The first of these is the narrow RF displayed above paired with the decision rule which assigns clients to forcing commitment in a  leaf if and only if  the CATE of the Forcing arm is positive.
-In the second we estimate a standard Logit model using as outcome an indicato of positive benefit from forcing commitment as estimated in the wide RF, and the narrow targeting variables as the explanatory variables.
-Figure \ref{targeting_rules} plots the same densities of net benefit as were shown before, where we now take the wide RF as the ground truth of the benefits of forcing everyone into commitment, and the welfare under the two targeting rules shown for comparison.
-Given the poor explanatory power of the narrow criteria it is unsurprising to see that the information gain from using these variables is small; the fraction of the whole sample incorrectly targeted when we go from universal forcing to narrow RF targeted forcing falls only marginally from 8.8\% to 8.3\%.
-When we look at the Logit targeting we see that it has actually made targeting substantially worse; this behavior is driven by the confluence of the poor explanatory power of the narrow variables with the fact that the Logit matches the correct sample fraction of ones, therefore making numerous Type II errors in an environment where commitment is beneficial for most.
-%and hence actually reduces the share benefiting.
-
-%The comparative points are illustrated in
-Table \ref{hit_miss_rule} shows Type I and Type II error rates for each of six rules:  all to control, all to treatment (Forcing), optimal, Narrow RF targeting, Logit targeting, and Choice.
-While the Narrow RF is able to correctly assign roughly half of those who do not benefit from commitment to control, it also incorrectly allocates 3.7\% of the sample that would have gained from treatment to control, and so on net it only improves the correct targeting rate by about a half of a percentage point relative to universal Forcing.
-The Logit is less successful at predicting benefits and in particular makes many Type II errors, resulting in a net targeting performance that is actually worse than universal forcing.
-The underlying cause of the weak performance of targeting is that the attribute that predicts loss from forcing (not being sure confident and not choosing the commitment) is largely behavioral and not easily predicted with basic covariates.
-Self-targeting through choice proves to be little better than assigning everyone to the control, given the low take-up rate and the presence of both Type I and Type II errors in the Choice arm.
-68\% of individuals in the Choice arm made a mistake, weighting the results among choosers and non-choosers by their frequency.
+For this reason, the relevant causal effect for this exercise is the conditional average treatment effect (ATE) rather than the conditional TUT or TOT as considered above.
+As shown in Figure \ref{fig:CATEsurvival}, an estimated 92\% of borrowers, with a 95\% confidence interval of [89\%, 94\%] have a positive conditional ATE as estimated from the causal forest from section \ref{sec:RF} above.
+In the remainder of this section we ask how accurately it is possible to identify these borrowers.
+
+\paragraph{Narrow inputs targeting.} To  consider targeting effectiveness we must begin from an individual-specific ground truth, which we take from our estimated conditional average treatment effects (CATEs) $\widehat{\text{ATE}}(X_i)$ from the causal forest described in Section \ref{sec:RF},  which used the ``wide'' set of covariates (wide RF) and data for all borrowers who replied to at least part of the intake survey.
+We then analyze how well we can predict the losers from paternalism using the ``narrow'' set of non-manipulable covariates listed above (narrow RF) for the same subset of borrowers.
+Figure \ref{wide_narrow_forests} shows the relationship between the CATEs estimated from the RF using the ``wide'' and ``narrow'' covariate sets.
+It is visually obvious from this figure that we generate substantially less heterogeneity when using the narrow covariate set, although we still reject the null hypothesis of no treatment effect heterogeneity, following the approach of \cite{chernozhukov2018generic}.\footnote{See \ref{append:chernozhukov} for details of this method.}
+
+\paragraph{Targeting assessment.}
+
+To more directly investigate our ability to target commitment, we use two different methods to predict who should be assigned to the commitment arm.
+In each, we estimate a classification model using the ``narrow'' set of covariates to predict whether the CATE from the wide random forest model is positive.
+The first method uses a simple logistic regression, while the second uses a random forest classification model.\footnote{We use the STATA package \textit{rforest} and use the default parameters for the estimation.
+For further detail see \cite{rforest_stata}.} Each of these methods yields an estimated probability of a positive CATE, allowing us to rank borrowers from highest to lowest probability.
+Since 92\% of borrowers have a positive CATE as estimated from the wide random forest model from above, we consider a decision rule that assigns a borrower to forced commitment if her estimated probability is in the top 92\% of the sample.
+%The first of these is the narrow RF displayed above paired with the decision rule which assigns clients to forcing commitment if the estimated CATE from the narrow covariate set is positive. 
+%In the second approach we estimate a logistic regression model with an outcome variable equal to one if the ``wide'' model CATE is positive, zero otherwise. 
+%The explanatory variables are the covariates from the ``narrow'' model. We assign a borrower to commitment if \hl{the probability that her CATE is positive is estimated to be above 0.5}.
+Figure \ref{targeting_rules} compares the in-sample performance of these targeting rules against a policy of universal forced commitment.
+The plot presents the estimated proportion of borrowers who benefit from a particular treatment assignment rule, along with associated 95\% confidence bands, where ``benefit'' is defined as having a conditional average treatment effect above a particular threshold.
+As above, we take the conditional average effects from the ``wide'' causal forest as ground truth for the purposes of this exercise.
+Because this is an in-sample exercise, the logistic and random forest classification rules have an unfair advantage: there is no adjustment for overfitting.
+In spite of this, their performance is quite unimpressive relative to a policy of universal forced commitment.
+The fraction of the whole sample incorrectly targeted when moving from universal forced commitment to targeting based on the narrow RF falls only from 8.07\% to 5.49\%.
+The logit targeting rule actually makes things marginally worse.
+Table \ref{hit_miss_rule} shows error rates for six possible assignment rules: assigning all borrowers to control, all to treatment (Forcing), the optimal (infeasible) assignment, narrow RF targeting, logit targeting, and we evaluate ex-post the voluntary choice.
+While the narrow RF correctly assigns roughly half of those who do not benefit from commitment to control, it also incorrectly allocates 3.7\% of the sample that would have gained from treatment to control.
+As such, it only improves the correct targeting rate by about a half of a percentage point on net relative to universal Forcing.
+The logit assignment rule is less successful at predicting benefits and harms, with a higher share of borrowers incorrectly assigned to both treatment and control.
+%In particular it makes many Type II errors, resulting in a net targeting performance that is actually worse than universal forcing. 
+The underlying cause of the weak performance of targeting is that the attribute that predicts gains from forcing (being sure confident and not choosing the commitment) is largely behavioral and not easily predicted with basic covariates, as seen in Figure \ref{tut_beh_partition}.
+Self-targeting through choice proves to be little better than assigning everyone to the control condition, given the low take-up rate and the presence of both Type I and Type II errors in the choice arm.
+Fully 79\% of individuals in the Choice arm made a ``mistake'', weighting the error rates among choosers and non-choosers by their relative frequency in the Choice arm.
 The takeaway is that given low take-up, the large fraction of the sample benefiting from commitment, and the weak predictive power of the narrow covariates, in this case universal paternalism appears to be an attractive contract.
+
+%Given the poor explanatory power of the narrow covariates, as shown in Figure \ref{wide_narrow_forests}, it is unsurprising to see that the information gain from using these variables is small;
+
+%This latter results is driven by the confluence of the poor explanatory power of the narrow variables, as shown in Figure \ref{wide_narrow_forests}, with the fact that the logit matches the correct sample fraction of ones, therefore making numerous Type \hl{II} errors \hl{(Should it be Type I?)} in an environment where commitment is beneficial for most.
 
@@
 
-In a pawnshop borrowing context, we study whether forcing borrowers into frequent payment commitment contracts reduces their borrowing costs, compared to a contract that does not provide commitment to pay monthly.
+\cite{Laibson2018} discusses the idea of ``veiled paternalism'', whereby principals embed forms of commitment into their products but mask this fact from consumers who may need but do not desire commitment.
+In the context of pawnbroking, over-collateralization means that lenders stand to make more money from unreliable borrowers than those who repay.
+The fact that a simple change to contract terms results in a substantial financial saving for borrowers implies that the pawn contract involves ``veiled non-paternalism'':   features that lead to high borrower costs are embedded in non-obvious ways.
+Potentially due to the nature of the borrower pool, voluntary commitment choice does not result in substantial improvements in borrower returns; a mandated reform to the contract induced significant cost savings for the overall group of clients.
+
+We are able to arrive at a nuanced set of conclusions about the relationship between take-up and heterogeneity in returns due to a novel experimental setup, the ``Controlled Choice'' design.
+This three-armed experiment, featuring a control group, an arm with borrower choice, and an arm with compulsory treatment, allows us to point-identify the impact of the treatment on those who would naturally choose it as well as those who only experience commitment when forced.
+While we find evidence of selection on gains (as would be expected from standard economic models) there remain substantial benefits of treatment even for non-choosers.
+Given that the rate of voluntary commitment in our sample is only 11\%, in order to achieve widespread benefits in this context compulsory commitment may be necessary.
+In the Forced arm the APR (inclusive of the cost of default) falls from 184\% to 150\%, and the fraction of borrowers defaulting on loans drops by 6.5 pp, or 15\%.
+Clients appear to prefer the forced commitment after they have experienced it, in that assignment to this arm increases the fraction of individuals who return to pawn again.
+
+Why do borrowers leave such substantial returns on the table?
+Our investigation of treatment effect heterogeneity suggests that over-optimism is the characteristic most strongly associated with benefiting from the intervention and yet not choosing it.
+Overall the borrower pool overestimates their own probability of repayment by more than 50\%, and we find that the positive TUT is almost entirely confined to borrowers who report that they are certain to repay.
+The takeaway is that inefficiently low demand for tools to remediate default is strongest among those who incorrectly believe that they have no chance of defaulting.
+More standard explanations such as discounting, learning, or time inconsistency find little support in our data.
+Importantly, we find that not only are the benefits of commitment close to universal, but the determinants that might allow us to target it more finely are primarily behavioral and hence not easily predicted in an fast incentive-compatible manner by lenders.
+Even a sophisticated machine learning-based exercise is only able to decrease the fraction of borrowers mis-targeted by about 2.5 percentage points relative to simply assigning everyone to commitment (from 8\% to 5.5\%), and a logit-based targeting rule actually does slightly worse than universal commitment.
+
+This result has immediate policy implications.
+Pawnshops, along with other over-collateralized credit products such as payday lending, exist in an environment where the bank may desire customers to lose their collateral on the loan.
+Given the high prevalence of the use of this form of credit by low-income households, this has an obviously detrimental effect on the dynamics of asset accumulation among the poor.
+Given that the specific items being pawned (such crucifixes and family jewelry) may have sentimental, non-pecuniary meaning to households, the efficiency implications of these contract terms may be even larger (as evidenced by the fact that borrowers' subjective value of their own pawns was 26\% higher than the appraised collateral value).
+With a now well-established toolkit of regular small payments and incentives delivering vanishingly small default rates in microfinance, regulators in the banking sector may fruitfully investigate the possibility of requiring pawnbrokers to embed features of commitment and regularity into their repayment structures in more consistent ways.
+If employed at scale in a competitive lending sector this could redistribute welfare from those who would have repaid (whose interest rates must now rise to cover lower returns from collateral seizure) towards those who would only repay in the presence of commitment.
+In a setting of lender market power however, some redistribution from lenders to borrowers could occur.
+
+Where banks have no incentive to engage in veiled paternalism and customers display inefficiently low demand for it, financial policy regulation may prove an attractive option.
+An important question for future research will be the extent to which borrowers are able to learn about the benefits of commitment over time, making it so that temporary, lighter-touch policies could achieve lasting benefits for borrowers.
+Pawning with commitment may provide an important mechanism to preserve flexible credit access while allowing more poor borrowers to retain their assets.
+
+%In a pawnshop borrowing context, we study whether forcing borrowers into frequent payment commitment contracts reduces their borrowing costs, compared to a contract that does not provide commitment to pay monthly.
 Even though we are charging them fees,  borrowing costs under forced commitment are actually reduced by 9.4\%, and pawnrecovery is 26\% higher.
@@
 
-We examine treatment heterogeneity using a range of methods, from bounds that make no assumptions, exploiting a mild exclusion restrictions and the innovative controlled choice design to gain point identification of TUT and TOT, and invoking seletion on observables to estimate treatment effects at the person level.
+%We examine treatment heterogeneity using a range of methods, from bounds that make no assumptions, exploiting a mild exclusion restrictions and the innovative controlled choice design to gain point identification of TUT and TOT, and invoking seletion on observables to estimate treatment effects at the person level.
 We find that a large majority of clients benefit from the commitment contract, but that when given choice between the commitment and the status quo contract only 10\% choose the former one and thus forgo important financial benefits.
@@
 %A simple model shows that present bias with naivete parsimoniously explains all findings. 
-The analysis suggests that it is possible in our context to advance an individual's financial  by restricting her freedom of choice ---although we caution that our outcome measure focuses on financing cost and is not a comprehensive measure of welfare.
+%The analysis suggests that it is possible in our context to advance an individual's financial  by restricting her freedom of choice ---although we caution that our outcome measure focuses on financing cost and is not a comprehensive measure of welfare.
 %These results spurred --although we cannot show they caused-- Lender $P$ to offer frequent payment contacts, although Lender $P$ was uncomfortable forcing these contracts on clients.
@@
 
-Pawnshop borrowing may attract particularly unsophisticated clients and freedom of choice may fare better in other contexts.
+%Pawnshop borrowing may attract particularly unsophisticated clients and freedom of choice may fare better in other contexts.
 Choice may also fare better with other contracts besides the fee-commitment one we used.
@@
 
-Our results suggest several avenues for future research.
+%Our results suggest several avenues for future research.
 First, it would be useful to tease out the roles played by naivete about self control problems and biased expectations about income shocks in driving low demand for commitment.
 Second, one could ask whether other types of contracts %---for instance those that provide some insurance against shocks---
-induce larger demand and better performance than the ones we tried.
+%induce larger demand and better performance than the ones we tried.
 Third, testing and quantifying of there is selection to pawnshop lenders based on unsophistication could be important for regulators.
@@
 The table reports the coefficients on each of these indicators, as well as the p-value an F-test of the null hypothesis of equality of the three coefficients.
-The dependent variables are: the number of pawns-loans originated per day per branch.
-A variable indicating whether a person who answered the baseline survey (before knowing contract terms) ended up pawning.
-And an indicator of whether the person that obtained the loan answered the baseline survey.
+The dependent variables are: the number of pawns-loans originated per day per branch, a variable indicating whether a person who answered the baseline survey (before knowing contract terms) ended up pawning, and an indicator of whether the person that obtained the loan answered the baseline survey.
 By design we had the choice arm be larger.
@@
 
-\textcolor{blue}{A few borrowers have more than one loan.
-These are treated as different observations, but Table \ref{multiple_loans} shows our results are similar collapsing the data at the person level or using only the assignment of the first loan.} Each regression includes branch and day-of-week FE.
+A few borrowers take more than one loan on the first day they appear in an experimental branch.
+These are treated as different observations.
+Table \ref{multiple_loans} shows our results are similar when dealing with the multiplicity of loans per borrower.
+Each regression includes branch and day-of-week FE.
 Standard errors are clustered at the branch-day level.
@@
 While Panel B focuses on variables related to default, and Panel C related to visits.
-The outcome variables are as follows:  number of days elapsed between origination and first payment (col 1); percentage of the loan paid in the first payment (col 2); probability of recovery in the first visit (col 3); \textcolor{blue}{loan duration is the number of days the borrower took to payoff her loan for those that recover, the number of days until default for those that default, and the maximum number of days we observe them in the sample for those that have not recovered or defaulted (col 4)}; loan duration conditional on recovery; an indicator for paying a positive amount towards recovery but nonetheless losing the pawn (col 6); the percentage or the loan paid, conditional on defaulting --`wasted payments' (col 7).
+The outcome variables are as follows:  number of days elapsed between origination and first payment (col 1); percentage of the loan paid in the first payment (col 2); probability of recovery in the first visit (col 3); loan duration is the number of days the borrower took to payoff her loan for those that recover, the number of days until default for those that default, and the maximum number of days we observe them in the sample for those that have not recovered or defaulted (col 4); loan duration conditional on recovery; an indicator for paying a positive amount towards recovery but nonetheless losing the pawn (col 6); the percentage or the loan paid, conditional on defaulting --`wasted payments' (col 7).
 Column 8 uses the phrase `selling the pawn' for a dummy variable indicating the borrower did not pay any amount towards recovery and lost the pawn.
-The dependent variable in column 9 is the number of day-visits to the branch (measured by the existence of transactions that day associated with our particular pawn), while column 10 conditions on borrowers that lost the pawn.
+Moreover, (col 9) shows that treatment effects are concentrated in the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery.
+The dependent variable in column 10 is the number of day-visits to the branch (measured by the existence of transactions that day associated with our particular pawn), while column 11 conditions on borrowers that lost the pawn.
 Each regression includes branch and day-of-week FE.
-Standard errors are clustered at the branch-day level.
+Standard errors are clustered at the branch-day level.}
 %In sum, we find that the Forced commitment contract clients pays 13.8 days earlier in average, during this first visit, clients pay 7.7\% more of the loan amount, with a 8\% increase probability of recovery.
@@
 Column 3 uses the cost from column 1 but adds to it the self-reported transport cost (most use public transport, imputing missing values with the average) as well as a whole day's minimum wage as a proxy for lost time.
-Column 4 \hl{sums} to FC an extra imputed `liquidity' cost by adding interest of 7\% per month for each peso paid.
+Column 4 ignores the `liquidity' cost in the financial cost formula by subtracting the interest of 7\% per month for each peso paid.
 Column 5 applies all these extra costs at the same time.
@@
 Standard errors are clustered at the branch-day level.
-
- \todo[inline]{@It is not very clear how exactly we do the liquidity adjustment.}
 
@@
 Each column represents a regression with a different outcome variable.
-In column 1, the dependent variable indicates, for each borrower in the experiment, whether he/she pawned again after \hl{the first loan} in the experiment (up to the end period of our data set \hl{XXX} days after the experiment began).
+In column 1, the dependent variable indicates, for each borrower in the experiment, whether he/she pawned again after the first loan in the experiment (up to the end period of our data set 338 days after the experiment began).
 Column 2 is analogous, but only pawning after 90 days of the first loan is considered.
 Column 3 instead considers pawning before 90 days.
-Column 4 is analogous to column 1 but focuses on the pawning of a gold piece that is different from the one in \hl{the first experimental loan.} Column 5 is analogous to column 1, but conditioning on the sample that recovered the first loan.
+Column 4 is analogous to column 1 but focuses on the pawning of a gold piece that is different from the one in the first experimental loan.
+Column 5 is analogous to column 1, but conditioning on the sample that recovered the first loan.
 Each regression includes branch and day-of-week FE.
@@
 \end{center}
-
-\todo[inline]{For Frank}
- %\scriptsize This table shows estimates of the ToT and the TuT with an IV-LATE framework.
-The ToT is computed as the usual LATE with one-sided non-compliance between the choice and control arm, and the TuT is the LATE on non-compliers.
+\scriptsize
+This table presents results computed using the derivations from Section \ref{sec:randchoice} and \ref{append:randchoice}. 
+Each column corresponds to an outcome variable: APR in column (1), financial cost in column (2), an indicator for \emph{not} defaulting in column (3), and an indicator for \emph{not} refinancing in column (4).
+The APR and financial cost outcomes have been multiplied by $-1$ so that a positive causal effect \emph{benefits} the borrower in each of the four columns.
+The top panel presents treatment on the treated (TOT) and treatment on the untreated (TUT) effect estimates, with standard errors clustered at the branch-day level.
+The average treatment effect (ATE) results from Section \ref{Experiment} are presented for purposes of comparison, along with average treated and untreated potential outcomes.
+The middle panel presents estimates of the average selection on gains $(\text{TOT} - \text{TUT})$, along with the average selection bias (ASB) and the average selection on levels (ASL), again with standard errors clustered at the branch-day level.
+See Appendix \ref{subsec:inference} for more details on how we compute standard errors for the middle panel.
+The bottom panel present sample sizes, and p-values for a number of null hypothesis tests of treatment effect heterogeneity. 
 %\textit{Do file: } \texttt{tot\_tut.do}
+\end{table}
+
+\begin{table}[H]
+\caption{Type I \& II errors using targeting narrow rules}
+\label{hit_miss_rule}
+\begin{center}
+\resizebox{0.95\textwidth}{!}{
+\small{\input{./Tables/hit_miss_rule.tex}}
+}
+\end{center}
+\scriptsize This table reports error rates for six different rules for allocating individuals to commitment.
+The first row allocates all borrowers to control.
+Taking the conditional ATE estimates from the ``wide'' causal forest, described in Section \ref{sec:RF} as ground truth, this results in 87\% of individuals losing by not receiving commitment.
+The second row assigns all borrowers to forced commitment, yielding error rates that are the exact mirror image of those from the first row.
+The third row considers the infeasible optimum in which each borrower is allocated the ``correct'' treatment, treating the estimate from the ``wide'' causal forest as ground truth.
+The fourth and fifth rows assign borrowers to commitment based on a classification model that uses the narrow covariate set to predict an indicator for whether the ``wide'' random forest CATE estimate is positive.
+Row four uses a random forest classification model while row five uses a simple logistic regression model.
+In each of these rows, the assignment rule ranks borrowers from highest to lowest by their estimated probability of having a positive CATE.
+The 91\% of borrowers with the highest estimated probabilities are assigned to treatment, matching the overall rate of positive CATE estimates from the ``wide'' RF model.
+The sixth row gives the percentage of miss-classification that would follow from the observed choice.
+%assigns the commitment contract to all borrowers with a positive conditional ATE estimate from the ``narrow'' RF.
+The fifth row uses a logistic regression to estimate the probability that a given borrower has a positive conditional ATE, assigning commitment to those with an estimated \hl{probability greater than 0.5}.
+
 \end{table}
@@
 
+\newpage
 \section{Figures}
@@
          \scriptsize
-         Panel (a) presents a histogram of financial cost (defined as in Section \ref{{costs}}) for the control group.
-The figure plots  financial cost separately for borrowers who lose the pawn (blue) and those that recover it (transparent).
+         Panel (a) presents a histogram of financial cost (defined as in Section \ref{costs}) for the control group.
+The figure plots separately the financial cost separately for borrowers who lose the pawn (blue) and those that recover it (transparent).
 Panel (b) is analogous but displays the APR.
@@
       %\footnotesize{ } \textit{Do file: }  \texttt{hist\_fc.do}
+\end{figure}
+
+\begin{figure}[H]
+     \caption{Experiment description}
+    \label{exp_description}
+\begin{center}
+\begin{subfigure}{\textwidth}
+        \includegraphics[width=\textwidth]{Figuras/consort.pdf}
+    \end{subfigure}
+  \end{center}
+    \scriptsize
+
+%\textit{Do file: }  \texttt{ss\_att.do}
 \end{figure}
@@
 \begin{figure}[H]
-     \caption{Experiment description}
-    \label{exp_description}
-\begin{center}
-\begin{subfigure}{\textwidth}
-        \includegraphics[width=\textwidth]{Figuras/consort.pdf}
-    \end{subfigure}
-  \end{center}
-    \scriptsize
-
-%\textit{Do file: }  \texttt{ss\_att.do}
-\end{figure}
-
-\begin{figure}[H]
      \caption{Explanatory Material}
@@
         This is a (translated) sample information slide shown to clients. The real ones were twice the size of this figure and were laminated. Different ones were shown for each treatment arm.
-\end{figure}
-
-\begin{figure}[H]
-    \caption{Determinants of choice}
-    \label{determinants_choose}
-    \begin{center}
-    \begin{subfigure}{0.75\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/determinants_choose_commitment.pdf}
-    \end{subfigure}
-    \end{center}
-      \scriptsize
-
-      The above figure shows the determinants in a bivariate and multivariate OLS regression of choosing commitment.
-Choice commitment is a binary variable equal to one, whenever subjects choose the forced commitment contract in the choice arm.
-%\textit{Do file: } \texttt{determinants_choice_sure_confidence.do}       
-\end{figure}
-
-\vspace{.2in}
-\begin{figure}[H]
-    \caption{Histogram of payments}
-    \label{hist_payments}
-    \begin{center}
-    \begin{subfigure}{0.45\textwidth}
-        \caption{Status-quo}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_payments_sq.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.45\textwidth}
-        \caption{Forced commitment}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_payments_fc.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.45\textwidth}
-        \caption{Choice commitment}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_payments_cc.pdf}
-    \end{subfigure}    
-    \end{center}
-     \scriptsize
-     \todo[inline]{For Isaac}
-      %\footnotesize{ \textit{Do file: }  \texttt{hist\_payments.do}}
 \end{figure}
@@
 
-\begin{figure}[H]
-\caption{TOT \& TUT as LATE}
-    \label{tot_tut_graph}
-    \begin{center}
-        \centering
-        \includegraphics[width=1.0\textwidth]{Figuras/tot_tut_intuition.png}
-    \end{center}
-    \scriptsize
-    \todo[inline]{For Frank}
-     %\textit{Do file: }  \texttt{tot\_tut\_graph.do}
-\end{figure}
-
 \vspace{.3in}
@@
         \scriptsize
-    \todo[inline]{For Frank}
+    This figure depicts the \cite{fan2010sharp} bounds on the distribution $F_\Delta$ of individual treatment effects $\Delta \equiv (Y_1 - Y_0)$, described in Section \ref{sec:bounds}, for the APR outcome.
+    The dark red curve and light red shaded region give the estimated upper bound function $\overline{F}$ for $F_\Delta$ and associated (pointwise) 95\% confidence interval. 
+    The dark blue curve and light blue shaded region give the estimated lower bound function $\underline{F}$ for $F_\Delta$ and associated (pointwise) 95\% confidence interval.
+    Confidence intervals are computed using the asymptotic distribution for the bounds. See \cite{fan2010sharp} for details.
+    The bounds are pointwise sharp: at any specified value of $\delta$ the bounds $\underline{F}(\delta) \leq F_\Delta(\delta) \leq \overline{F}(\delta)$ cannot be improved without imposing additional assumptions.
+    Evaluating the bounds at $\delta = 0$, we see that between 24\% and 97\% of borrowers have a positive individual treatment effect.
+    This is greater than the share of borrowers who chose commitment: 11\%.
 %\textit{Do file: } \texttt{fan\_park\_bnds.do}       
@@
 \begin{figure}[H]
-    \caption{Determinants sure confidence}
-    \label{determinants_sure}
+\caption{The Controlled Choice Design}
+    \label{tot_tut_graph}
     \begin{center}
-    \begin{subfigure}{0.75\textwidth}
         \centering
-        \includegraphics[width=\textwidth]{Figuras/determinants_confidence_100.pdf}
-    \end{subfigure}
+        \includegraphics[width=1.0\textwidth]{Figuras/tot_tut_intuition.png}
     \end{center}
     \scriptsize
-
-      The above figure shows the determinants in a bivariate and multivariate OLS regression of sure confidence among the non-choosers.
-Sure confidence is a binary variable defined to be one when people report a 100\% probability of recovery.
-%\textit{Do file: } \texttt{determinants_choice_sure_confidence.do}       
+    This figure provides graphical intuition for the way in which the controlled choice design from Section point identifies both the treatment on the treated (TOT) and treatment on the untreated (TUT) effects, as discussed in Section \ref{sec:randchoice} and \ref{append:randchoice}.
+    The gray shaded regions denote borrowers with a commitment contract; the white shaded regions denote borrowers with a status quo contract.
+    A comparison of means across control and forcing arms identifies the ATE of forcing  commitment.
+    The TOT and TUT effects of commitment are identified as follows.
+    In the choice arm, anyone with a commitment contract is a chooser; in the control and forcing arms, we do not know who is a chooser and who is not.
+    Because borrowers are randomly assigned to experimental treatment arms, however, the share of choosers will be the same, on average, across experimental arms.
+    This is depicted using dashed vertical lines in the control and forcing arms.
+    This overall share of choosers and non-choosers is point identified from the choice arm.
+    Now, the difference of mean outcomes across the choice and control arms gives the intent-to-treat effect of offering choice.
+    Under the exclusion restriction that moving non-choosers between the choice and forcing arms does not change their outcomes, this comparison ``nets out'' the non-choosers.
+    Hence, the ITT of offering choice equals the TOT multiplied by the share of choosers. 
+    Similarly, under the exclusion restriction that moving choosers between the choice and forcing arm does not affect their outcomes, the difference of means across the forcing and choice arms ``nets out'' the choosers and hence equals the TUT multiplied by the share of non-choosers.
+
+     %\textit{Do file: }  \texttt{tot\_tut\_graph.do}
 \end{figure}
@@
 \begin{figure}[H]
-    \caption{Choice of contracts and treatment effects (TOT \& TUT)}
-    \label{choose_wrong}
+    \caption{Partition of TUT by behavioral variables.}
+    \label{tut_beh_partition}
     \begin{center}
-        \begin{subfigure}{0.45\textwidth}
-        \caption{Mistakes in choice arm}
         \centering
-        \includegraphics[width=\textwidth]{Figuras/line_cw_apr_tot_tut.pdf}
-
-    %\end{subfigure}
-    %    \begin{subfigure}{0.45\textwidth}
-    %    \caption{Financial value of mistake}
-    %    \centering
-    %    \includegraphics[width=\textwidth]{Figuras/integral_cw_apr_tot_tut.pdf}
-
-    \bigskip
-
+        \includegraphics[width=0.75\textwidth]{Figuras/tut_beh_partition.pdf} 
+    \end{center}
+     \scriptsize  Each panel in this figure shows how the estimated treatment on the untreated (TUT) effect varies with a binary survey variable $X_i$.
+In the left panel (Sure-confidence) $X_i = 1$ if  borrower $i$ reported that she was certain to recover her pawn, zero otherwise.
+In the right panel (P.B.), $X_i = 1$ if borrower $i$ is ``present-biased'' based on her responses to the time preference questions from our survey.
+Each panel depicts three estimates and associated 95\% confidence bands: the overall TUT (blue), the TUT for borrowers with $X = 1$ (green), and the TUT for borrowers with $X = 0$ (red).
+By the law of iterated expectations, the overall TUT in each panel must lie between the group-specific TUTs.
+The overall TUT is slightly different in each panel, because some borrowers only completed part of the survey.
+In each panel, we present results for the full set of borrowers who answered the survey question or questions needed to determine $X_i$.
+From the right panel, we see that TUT does not appear to vary with present bias.
+In contrast, the left panel suggests that the positive and significant overall TUT is driven by individuals who are ``sure-confident,'' i.e.\ borrowers who report that they are certain to recover their pawn.
+     %to be largely concentrated relevant survey question  according to her survey responses two binary performs a partition of the Treatment on the Untreated (FC), estimating the share of the effect that arises within each of two binary categories.
+The top bars examine present bias (individuals are more impatient over one-month time horizon than they are between three and four months).
+The bottom bars examine sure confidence (individual reports 100\% probability of repaying at time of taking loan).
+Blue bar is the component arising from those without the trait, orange bar from those with the trait.
+      %\footnotesize{ \textit{Do file: }  \texttt{partition_tut.do}
+
+\end{figure}
+
+\begin{figure}[H]
+     \caption{Heterogeneous Treatment Effects}
+    \label{heterogeneous_effects}
+    \begin{center}
+     \begin{subfigure}{0.55\textwidth}
+    \caption{ToT}
+       \centering
+      \includegraphics[width=\textwidth]{Figuras/he_dist_tau_hat_tot.pdf}
     \end{subfigure}
-        \begin{subfigure}{0.45\textwidth}
-        \caption{\% better when forced to forced commitment}
+    \begin{subfigure}{0.55\textwidth}
+    \caption{TuT}
        \centering
-        \includegraphics[width=\textwidth]{Figuras/line_better_forceall_apr_te_cf.pdf}
-
+      \includegraphics[width=\textwidth]{Figuras/he_dist_tau_hat_tut.pdf}
+    \end{subfigure} 
+       \begin{subfigure}{.55\textwidth}
+      \caption{ATE}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/he_dist_tau_hat_eff.pdf}
     \end{subfigure}
@@
          \scriptsize
-        In Panel (a) we estimate what the treatment effect of the commitment contract \textit{would have been} for all subjects in the choice arm if they had been forced into the fee-commitment contract.
+     This Figure plots the densities of treatment on the untreated effects (TUT), treatment on the treated (TOT) effects, and conditional average treatment effects (ATE) based on the instrumental and causal forest models from Section \ref{sec:RF}.
+  %\footnotesize{ } \textit{Do file: }  \texttt{cate_dist.do}
+\end{figure}
+
+\begin{figure}[H]
+    \caption{``Mistakes'' in the choice arm}
+    \label{choose_wrong}
+   % \begin{center}
+   %     \begin{subfigure}{0.45\textwidth}
+   %     \caption{``Mistakes'' in choice arm}
+        \centering
+        \includegraphics[width=0.75\textwidth]{Figuras/line_cw_apr_tot_tut.pdf}
+  %  \end{subfigure}
+  %      \begin{subfigure}{0.45\textwidth}
+  %      \caption{\% with positive CATE from forced commitment}
+  %      \centering
+  %      \includegraphics[width=\textwidth]{Figuras/line_better_forceall_apr_te_cf.pdf}
+
+  %  \end{subfigure}
+
+  %  \end{center}
+        %\scriptsize
+        %In Panel (a) we estimate what the treatment effect of the commitment contract \textit{would have been} for all subjects in the choice arm if they had been forced into the fee-commitment contract.
 To do this we proceed in two steps.
@@
 
-\todo[inline]{Enrique deleted subfigure b}
-\todo[inline]{should we flip the x-axis, so they look for CDFs?}
+This figure presents conditional average TUT and TOT effects for the APR outcome from Figure \ref{heterogeneous_effects} in an alternative manner, to consider the fraction of borrowers in the choice arm who made ``mistakes'' in their decision to accept or refuse the commitment contract.
+A ``mistake'' for a non-chooser is defined as a positive conditional TUT effect that significantly exceeds a specified threshold APR value.
+The green curve equals $[1 - F_{\text{TUT}}(\delta)]\times 100\%$, where $F_{\text{TUT}}$ is the CDF corresponding to density of conditional TUT effects from Figure \ref{heterogeneous_effects}, computed using the instrumental forest approach from \cite{atheygrf}.
+Evaluated at any positive value on the horizontal axis, it gives the fraction of non-choosers in the choice arm who made a ``mistake'' by not choosing commitment.
+The green shaded region gives associated 95\% pointwise confidence bands.
+Analogously, a ``mistake'' for a chooser is defined as a negative conditional TOT effect that exceeds a specified threshold APR value.
+The red curve equals $F_{\text{TOT}}(-\delta)$ where $F_{\text{TOT}}$ is the CDF corresponding to the density of conditional TOT effects from Figure \ref{heterogeneous_effects}.
+The red shaded region gives associated 95\% pointwise confidence bands.
+For both the red and green curves, we define the APR threshold so that larger mistakes are to the \emph{right} of smaller mistakes.
+This allows us to construct the overall fraction of mistakes in the choice arm, the blue curve, as a weighted average of the green and red curves.
+The weights equal the share of choosers and non-choosers in the choice arm.
+
+%\todo[inline]{Panel (a).
+Green line: survival function computed using estimated TUT of non-choosers in the choice arm.
+Red line: $F(-x)$ where $F$ is the CDF of individual TOT estimates for the choosers in the choice arm.
+Blue curve is the weighted average of the green and red with weights equal to the share of choosers versus non-choosers in the choice arm.
+Panel (b) is the survival function for the ATE computed for who?
+We think it's for the choice arm.
+(Shouldn't make a difference because of randomization and fairly large sample sizes.) Confidence bands are computed how?
+Use asymptotic normality and variance for each ``cell''}
 
@@
 \begin{figure}[H]
-    \caption{Wide and narrow forests}
+    \centering
+  \caption{Cumulative Distribution Function of Conditional ATE Estimates}
+  \includegraphics[width=0.75\textwidth]{Figuras/line_better_forceall_apr_te_cf.pdf} 
+    \label{fig:CATEsurvival}
+\end{figure}
+
+This figure shows the share of borrowers who benefit from forced commitment, where ``benefit'' is defined as having an estimated conditional average treatment effect (ATE) above a specified threshold value.
+Results are based on the causal forest model from Section \ref{sec:RF}.
+The solid line equals $1 - F_\text{ATE}(\delta)$ where $F_\text{ATE}(\delta)$ denotes the CDF corresponding to the density of conditional ATE estimates from Figure \ref{heterogeneous_effects}.
+The blue shaded regions are associated 95\% confidence intervals.
+We estimate that at least 91\% of borrowers have a positive conditional ATE.
+
+\cleardoublepage
+
+\begin{figure}[H]
+    \caption{Conditional ATEs from ``wide'' and ``narrow'' covariate sets}
     \label{wide_narrow_forests}
@@
     \end{center}
-      \scriptsize  This figure plots the relationship between the Athey-Wager heterogeneous treatment effects estimated using the `wide' set of determinants (all available covariates), versus the `narrow' set (only age, gender, HS education, and previous borrowing).
-The scatterplot graphs one estimate versus the other, and the histograms show the densities of the respective heterogeneity estimates.
+      \scriptsize  This figure plots the relationship between the causal forest conditional ATE estimates from Section \ref{sec:RF} that use the ``wide'' set of covariates (all intake survey responses) and those based on a restricted ``narrow'' set of covariates (age, gender, HS education, and previous borrowing).
+The scatterplot graphs one estimate versus the other, with the ``wide'' covariate set on the horizontal axis and the ``narrow'' set on the vertical axis.
+The density plots on each axis show the estimated marginal distribution of conditional ATEs under each covariate set.
+The density for the ``wide'' covariate set is considerably more dispersed, as the causal forest based on this set of covariates captures considerably more treatment effect heterogeneity.
 
@@
     \end{center}
-      \scriptsize   This figure plots the (reversed) cumulative densities of the estimated benefits from the casual forest for three different rules.
+      \scriptsize   This figure plots the percentage of borrowers who would benefit from a program in which commitment is targeted using the ``narrow'' covariate set (age, gender, HS education, and previous borrowing).
+In this exercise ``benefit'' is defined to mean having a conditional ATE above a particular threshold, taking the estimated conditional effects from the ``wide'' causal forest as ground truth.
+The plot compares the estimated percentage of borrowers who benefit, along with associated 95\% confidence bands, for three targeting rules: universal forced commitment in blue, targeting based on a random forest classification model in green, and targeting based on the logit model in red.
+For each of the classification models, the outcome variable is an indicator for whether the CATE estimate from the ``wide'' random forest model is positive.
+Each of the classification models produces an estimated probability of a positive CATE.
+For each, the assignment rule ranks borrowers by this estimated probability, and assigns the highest 92\% to forced commitment, to match the overall percentage of borrowers with positive estimated CATEs from the ``wide'' random forest model.
+Because this is an in-sample exercise, it overstates the actual performance of logit and RF-based targeting.
+      %, the top \hl{XXX\%} of Both targeted Both of the targeted assignment rules are assigned by a the ``narrow'' causal forest in green, and targeting based on the logit model in red.
+The causal forest rule assigns a borrower to commitment if her estimated conditional ATE from the ``narrow'' covariate set is positive; the logistic regression rule assigns her to commitment if the estimated probability that her conditional effect is positive is greater than 0.5.
+      %\todo[inline]{@Issac: Have I described this correctly? Also, is this an out-of-sample exercise. In other words, are we using a holdout sample to make these comparisons?}
+
+      %This figure plots the (reversed) cumulative densities of the estimated benefits from the casual forest for three different rules.
 The blue line plots the HTEs from the `wide' random forest for the Forcing arm, which we take as the ground truth for actual impacts.
 The green line plots HTEs if we first target individuals using the variables in the `narrow' forest, and only assign individuals to commitment if they are on a leaf whose predicted forcing benefit is positive.
-The red line uses a Logit regression to predict which individuals benefit from treatment, and assigns all individuals to the arm predicted to be best for them.
+The red line uses a logit regression to predict which individuals benefit from treatment, and assigns all individuals to the arm predicted to be best for them.
 

### 2023-08-29 OA.tex
Implementation of validity tot_tut

@@
 
-\todo[inline]{Add exercise about falsification of exclusion that Frank suggested.}
-The \cite{huber_mellace} bounds for the TOT \& TUT APR are respectively:
-\[\text{TOT} : [-366, 490]\quad\quad\quad\text{TUT} : [-19, 109]\]
-
-Since both TUT (24) and ToT (121) estimates from the LATE approach lies inside these bounds, we cannot falsify the exclusion restriction.
+The \cite{huber_mellace} bounds for the TOT \& TUT APR are respectively:  $[-366, 490]$, and $[-19, 109]$.
+Since both TUT (24) and ToT (122) estimates from the LATE approach lies inside these bounds, we cannot falsify the exclusion restriction.
+Moreover, the p-values associated with testing violation of inequalities \ref{eq:testable0}, and \ref{eq:testable1} is equal to one in both cases\footnote{We include the implementation of the validity test for the exclusion restriction for choosers and non-choosers in our STATA package.}.
 

### 2023-08-29 Tables/transcribed.tex
table ss with pre-experiment data
Implementation of validity tot_tut

@@
       & \textbf{Where 0 is impossible and 100 is completely certain} \\
-      &  \\
-      &  \\
-3     & \textbf{How much would you sell the item you want to pawn for?       \_\_\_\_\_\_\_\_\_\_\_\_\_\_ pesos} \\
+3     & \textbf{How much do you think the item you plan to pawn is worth?       \_\_\_\_\_\_\_\_\_\_\_\_\_\_ pesos} \\
 4     & \textbf{Gender      } \\
@@
       & (a) NO\_\_\_    (b)  1-2 times \_\_\_    (c) 3-5 times\_\_\_\_   (d) More than 5\_\_\_\_ \\
-17    & \textbf{If you are saving money and a family member wants to use it for something } \\
-      & (a) I would only give him the money for an urgent expenze \\
-      & (b) I would give him the money even if it was not an urgent expense \\
-      & (c) I would not give him/her the money regardless \\
-      & (d) No one would ask me for my money \\
+17    & \multicolumn{1}{p{54.91em}}{\textbf{If you are saving money and a family member wants to use it for something }} \\
+      & \multicolumn{1}{p{54.91em}}{(a) I would only give him the money for an urgent expenze} \\
+      & \multicolumn{1}{p{54.91em}}{(b) I would give him the money even if it was not an urgent expense} \\
+      & \multicolumn{1}{p{54.91em}}{(c) I would not give him/her the money regardless} \\
+      & \multicolumn{1}{p{54.91em}}{(d) No one would ask me for my money} \\
 18    & \textbf{Do you make an expenses budget for the month ahead of time?} \\
       & (a) always, (b) very often, (c) sometimes, (d) never \\
-19    & \textbf{Do you have other items you could pawn?} \\
+19    & \multicolumn{1}{p{54.91em}}{\textbf{Do you have other items you could pawn?}} \\
       & (a) yes  (b) no \\

### 2023-08-29 donde.tex
Implementation of validity tot_tut

@@
 A large behavioral literature has illustrated that allocating borrowers to a commitment-savings product increase savings \citep{thaler2004save, prina2015banking, brune2016facilitating, callen2019headwaters, Pascaline, Ashraf}, but this literature does not show that commitment would not be chosen by those that would benefit from it, that is, that the treatment effect on the untreated (TUT) is positive.
-Indeed, selection on gains has such wide acceptance that economists often impose it as a part of Roy models on topics as diverse as migration \citep{borjas1989economic}, job search \citep{lippman1976economics}, and program evaluation \citep{bjorklund1987estimation}.
+Indeed, selection on gains has such wide acceptance that economists often impose it as a part of Roy models on topics as diverse as migration \citep{borjas1989economic} and job search \citep{lippman1976economics}.
+%, and program evaluation \citep{bjorklund1987estimation}. 
 In microfinance, a context close to ours, \citep{Murdoch} claim that there exists positive selection, citing a positive correlation between displaying present biased preferences in surveys and selecting into microfinance as evidence of borrowers' actually demanding the discipline imposed by frequent payments.
@@
 Two other recent papers also shed some light on private paternalism.
-In the context of food choice, \cite{Sprenger} elicit dynamic inconsistencies and show that demand for commitment is negatively correlated with these inconsistencies.
+In the context of food choice, \cite{Sprenger} show that individuals with the most time-inconsistent preferences are actually least likely to demand commitment, suggesting a lack of awareness as to self-control problems.
 In the context of school choice, \cite{Walters} finds that students who select into more effective schools have smaller treatment effects from attending than those who do not.
@@
 As far as we are aware, ours is the first experiment to combine control, forced treatment, and treatment choice arms and explain how such a design can be used to point identify TUT effects and a range of other interesting causal parameters under minimal assumptions.
-We call this approach the ``Controlled Choice design'' for short.
+While \cite{fowlie2021default} likewise exploited a three-armed experimental design in their study of the effect of electricity pricing, they identified two TOT effects for different groups of ``treated'' households, whereas we simultaneously identify the TOT and TUT effects defined with respect to a single ``treated'' group of borrowers.
+We call our approach the ``Controlled Choice design'' for short.
 Other approaches to going beyond local average treatment effects (LATE) from the literature either assume no unobserved selection-on-gains \citep{aronow2013beyond,angrist2013extrapolate} (the ``LATE-and-reweight'' approach) or rely on a combination of instruments with rich support and additional structural assumptions such as additive separability of observed and unobserved determinants of treatment effect heterogeneity \citep{heckman2007econometric, cornelissen2018benefits} (the marginal treatment effects approach).
@@
 Unlike \cite{Sprenger} we directly identify the TUT, obviating the need to first elicit preferences before testing for negative selection.
+In a returns-to-education setting, \cite{oreopoulos2006estimating}, uses a similar direct approach to identify a LATE \emph{nearly} equals a TUT effect: the 1944 Butler Act increased the share of British children who remained in school until age 15 from 43\% to over 90\%.
+Because 100\% of borrowers in our forced arm are treated, we identify the TUT rather than an approximation to it.
 
@@
 \]
-A companion STATA package accompanying this paper provides estimators of the TOT, TUT, ASG, ASB, and ASL, along with cluster-robust standard errors for each.\footnote{See Appendix \ref{append:randchoice} for more details.}
+A companion STATA package accompanying this paper provides estimators of the TOT, TUT, ASG, ASB, and ASL, along with cluster-robust standard errors for each, and a test for the validity of the exclusion restriction following \cite{huber_mellace} \footnote{See Appendix \ref{append:randchoice} for more details.}.
 
@@
 The results of this exercise can be read off from the green curve in Figure \ref{choose_wrong}.
-Defining $F_{\text{TUT}}(\delta)$ to be the CDF corresponding to the density of conditional TUT estimates from Figure \ref{heterogeneous_effects}, the green curve in Figure \ref{chose_wrong} is merely $[1 - F_{\text{TUT}}(\delta)] \times 100\%$.
+Defining $F_{\text{TUT}}(\delta)$ to be the CDF corresponding to the density of conditional TUT estimates from Figure \ref{heterogeneous_effects}, the green curve in Figure \ref{choose_wrong} is merely $[1 - F_{\text{TUT}}(\delta)] \times 100\%$.
 In other words, the green curve gives the percentage of non-choosers who made a ``mistake'' when mistakes are defined at a particular APR threshold.

### 2023-09-05 donde.tex
edits of figures before submission

@@
 We find modest selection on gains but nonetheless significant positive benefits of commitment even for those who would not have chosen it.
-The justification for paternalistic commitment in this context appears to be over-optimism; 74\% of clients say they will certainly recover their pawn while in fact only 57\% do so.
+%The justification for paternalistic commitment in this context appears to be over-optimism; 74\% of clients say they will certainly recover their pawn while in fact only 57\% do so.
 
@@
 
-\textbf{Keywords: } Private paternalism, choice, present bias, naivete, overconfidence, commitment, heterogeneous treatment effects.
+\textbf{Keywords: } Private paternalism, choice, heterogeneous treatment effects, commitment, overconfidence.
 
@@
 This measure equals one for any individuals who say at the time of borrowing that they have a 100\% probability of recovering their pawn, zero otherwise.
-The left panel of Figure \ref{tut_beh_partition} presents the results for this exercise.
+The right panel of Figure \ref{tut_beh_partition} presents the results for this exercise.
 The overall TUT estimate for all borrowers who answered our sure-confidence survey questions is given in blue, along with a 95\% confidence interval.
@@
 As above, the blue overall estimate must lie between the green and red sub-group estimates by the law of iterated expectations.
-In contrast to our results for present bias, shown in the right panel of Figure \ref{tut_beh_partition}, we estimate a higher TUT effect for sure-confident borrowers compared to all other borrowers and a negative, although insignificant, effect for borrowers who are not sure-confident.
+In contrast to our results for present bias, shown in the left panel of Figure \ref{tut_beh_partition}, we estimate a higher TUT effect for sure-confident borrowers compared to all other borrowers and a negative, although insignificant, effect for borrowers who are not sure-confident.
 
@@
     \begin{center}
-    \begin{subfigure}{0.6\textwidth}
+    \begin{subfigure}{0.75\textwidth}
         \caption{APR}
@@
      \scriptsize  Each panel in this figure shows how the estimated treatment on the untreated (TUT) effect varies with a binary survey variable $X_i$.
-In the left panel (Sure-confidence) $X_i = 1$ if  borrower $i$ reported that she was certain to recover her pawn, zero otherwise.
-In the right panel (P.B.), $X_i = 1$ if borrower $i$ is ``present-biased'' based on her responses to the time preference questions from our survey.
+In the left panel (P.B.), $X_i = 1$ if borrower $i$ is ``present-biased'' based on her responses to the time preference questions from our survey.
+In the right panel (Sure-confidence) $X_i = 1$ if  borrower $i$ reported that she was certain to recover her pawn, zero otherwise.
 Each panel depicts three estimates and associated 95\% confidence bands: the overall TUT (blue), the TUT for borrowers with $X = 1$ (green), and the TUT for borrowers with $X = 0$ (red).
@@
 In each panel, we present results for the full set of borrowers who answered the survey question or questions needed to determine $X_i$.
-From the right panel, we see that TUT does not appear to vary with present bias.
-In contrast, the left panel suggests that the positive and significant overall TUT is driven by individuals who are ``sure-confident,'' i.e.\ borrowers who report that they are certain to recover their pawn.
+From the left panel, we see that TUT does not appear to vary with present bias.
+In contrast, the right panel suggests that the positive and significant overall TUT is driven by individuals who are ``sure-confident,'' i.e.\ borrowers who report that they are certain to recover their pawn.
      %to be largely concentrated relevant survey question  according to her survey responses two binary performs a partition of the Treatment on the Untreated (FC), estimating the share of the effect that arises within each of two binary categories.

### 2023-10-15 OA.tex
edits of figures before submission
revision after jpe submission

@@
         \centering
-        \includegraphics[width=\textwidth]{Figuras/empenio9.png}
+        \includegraphics[width=\textwidth]{Figuras/empenio9_.png}
     \end{subfigure}
@@
         \centering
-        \includegraphics[width=\textwidth]{Figuras/empenio11.png}
+        \includegraphics[width=\textwidth]{Figuras/empenio11_.png}
     \end{subfigure}
@@
         \centering
-        \includegraphics[width=\textwidth]{Figuras/empenio2.png}
+        \includegraphics[width=\textwidth]{Figuras/empenio2_.png}
     \end{subfigure}
@@
         \centering
-        \includegraphics[width=\textwidth]{Figuras/empenio3.png}
+        \includegraphics[width=\textwidth]{Figuras/empenio3_.png}
     \end{subfigure}
@@
         \centering
-        \includegraphics[width=\textwidth]{Figuras/empenio7.png}
+        \includegraphics[width=\textwidth]{Figuras/empenio7_.png}
     \end{subfigure}
@@
         \centering
-        \includegraphics[width=\textwidth]{Figuras/empenio8.png}
+        \includegraphics[width=\textwidth]{Figuras/empenio8_.png}
     \end{subfigure}
@@
 Choice commitment is a binary variable equal to one, whenever subjects choose the forced commitment contract in the choice arm.
-%\textit{Do file: } \texttt{determinants_choice_sure_confidence.do}       
+%\textit{Do file: } \texttt{determinants_choice.do}       
 \end{figure}
@@
 It shows that the CDF of the status quo contract is always below that of the fee-forcing (and this difference is significant for the points indicated by the blue line).
-    % \texttt{fosd_ecdf.do}}
+    % \texttt{te_rankinvariance.do}}
 \end{figure}
@@
 
+\subsection{Sure Confidence} \label{App_sureconfidence}
+
 \begin{figure}[H]
@@
 Sure confidence is a binary variable defined to be one when people report a 100\% probability of recovery.
-%\textit{Do file: } \texttt{determinants_choice_sure_confidence.do}       
+%\textit{Do file: } \texttt{determinants_sure_confidence.do}       
 \end{figure}
@@
 Since $\tau_i$ and $\psi_i$ do not depend on the test set, inference for the regression in \eqref{eq:chernreg} is straightforward conditional on the Training/Test split.  
-Our estimate for $\beta_2$ is 1.68 with a one-sided heteroskedasticity-robust (HC3) of 0.50.
+Our estimate for $\beta_2$ is 2.5 with a one-sided heteroskedasticity-robust (HC3) of 0.43.
 Thus we easily reject the null hypothesis of homogeneous treatment effects.
@@
 
-The \cite{huber_mellace} bounds for the TOT \& TUT APR are respectively:  $[-366, 490]$, and $[-19, 109]$.
+The \cite{huber_mellace} bounds for the TOT \& TUT APR are respectively:  $[-119, 122]$, and $[-4.2, 24.6]$.
 Since both TUT (24) and ToT (122) estimates from the LATE approach lies inside these bounds, we cannot falsify the exclusion restriction.
@@
         \centering
-        \includegraphics[width=\textwidth]{Figuras/crf_pro_2_apr.pdf}
+        \includegraphics[width=\textwidth]{Figuras/crf_apr.pdf}
     \end{center}

### 2023-10-15 Tables/Attrition.tex
introduce NA in causal RF
tot_tut_validity & edits to the main paper
revision after jpe submission

@@
 \midrule
-Number of branch-day pawns & 34    & 34    & 36    & 0.52 \\
-      & (3)   & (2.9) & (1.8) &  \\
+Number of branch-day pawns & 32    & 34    & 37    & 0.57 \\
+      & (3.3) & (2.9) & (3.2) &  \\
 \multicolumn{1}{p{12.82em}}{Ended up pawning} & 0.98  & 0.97  & 0.97  & 0.62 \\
@@
 Survey response rate & 0.79  & 0.76  & 0.77  & 0.62 \\
-      & (0.02) & (0.02) & (0.01) &  \\
+      & (0.02) & (0.02) & (0.02) &  \\
 \midrule

### 2023-10-15 donde.tex
revision after jpe submission

@@
 We define a borrower's financial cost as the total monetary outflow --in cash or pawn value-- from the borrower to the lender.
-This includes all payments the borrower made toward interest and fees, but also the value of the pawn when there is default.
+This includes all payments the borrower made toward interest and fees, but also the net difference of the appraised value of the loan and the loan amount (VLD) when there is default.
 When there is no default the borrower gets her pawn back and there is no loss of value for the borrower.
@@
 Note however that when she does not default payments to capital are not an actual outflow, as they sum up to the value of the loan the lender disbursed in the first place.
-The formula for financial cost for person $i$ is thus as follows:
+The formula for financial cost for person $i$ is thus as follows\footnote{We can also define the financial cost formula as:
+\begin{align*}
+    \text{Financial Cost}_i =&  \underbrace{\sum_t P^i_{it}}_{\text{Payments to interest}} + \underbrace{\sum_t P^f_{it}}_{\text{Payments of fees}}    + \underbrace{\sum_t P^c_{it}}_{\text{Payments to capital}} + \underbrace{\mathds{1}(\text{Default}_i) \times (\text{Appraised value}_i}_{\text{Cost of losing pawn}})-\text{Loan amount}_i
+\end{align*}
+and our results will be equivalent if using this definition instead.
+}:
 
@@
     \text{Financial Cost}_i =&  \underbrace{\sum_t P^i_{it}}_{\text{Payments to interest}} + \underbrace{\sum_t P^f_{it}}_{\text{Payments of fees}}   \\
-    &\quad\qquad + \underbrace{\mathds{1}(\text{Default}_i) \times (\text{Appraised Value}_i}_{\text{Cost of losing pawn}} + \underbrace{\sum_t P^c_{it}}_{\text{Payments to capital}})
+    &\quad\qquad + \underbrace{\mathds{1}(\text{Default}_i) \times (\text{Val-Loan Difference}_i}_{\text{Cost of losing pawn}} + \underbrace{\sum_t P^c_{it}}_{\text{Payments to capital}})
 \end{align*}
@@
 Figure \ref{fan_park_bounds} plots the sharp bounds for $F_{\delta}$ based on the APR outcome defined above in Section \ref{costs}.
-Our point estimates of $\underline{F}(0)$ and $\overline{F}_0$ are .03 and .76 respectively, with associated 95\% confidence intervals of [0.027, 0.040] and [0.73, 0.78], which says that at least 24\% of individual borrowers benefit from commitment (and at most 97\%).\footnote{Confidence intervals are constructed using the asymptotic distribution for the bounds.
+Our point estimates of $\underline{F}(0)$ and $\overline{F}_0$ are .03 and .77 respectively, with associated 95\% confidence intervals of [0.024, 0.050] and [0.75, 0.80], which says that at least 23\% of individual borrowers benefit from commitment (and at most 97\%).\footnote{Confidence intervals are constructed using the asymptotic distribution for the bounds.
 See \cite{fan2010sharp} for details.}
@@
 \begin{align*}
-    \underbrace{\text{Financial Cost}_i}_{(1)} =&  \underbrace{\sum_t P^i_{it}}_{\underset{(2)}{\text{Payments to interests}}}  +\underbrace{\sum_t P^f_{it}}_{\underset{(3)}{\text{Payments of fees}}} + \underbrace{\overbrace{\mathds{1}(\text{Default}_i)}^{(6)}\times (\text{Appraised Value}_i}_{\underset{(5)}{\text{Cost of losing pawn}}} + \underbrace{\sum_t P^c_{it}}_{\underset{(4)}{\text{Payments to capital}}})
+    \underbrace{\text{Financial Cost}_i}_{(1)} =&  \underbrace{\sum_t P^i_{it}}_{\underset{(2)}{\text{Payments to interests}}}  +\underbrace{\sum_t P^f_{it}}_{\underset{(3)}{\text{Payments of fees}}} + \underbrace{\overbrace{\mathds{1}(\text{Default}_i)}^{(6)}\times (\text{Val-Loan Diff}_i}_{\underset{(5)}{\text{Cost of losing pawn}}} + \underbrace{\sum_t P^c_{it}}_{\underset{(4)}{\text{Payments to capital}}})
 \end{align*}
@@
 The first row allocates all borrowers to control.
-Taking the conditional ATE estimates from the ``wide'' causal forest, described in Section \ref{sec:RF} as ground truth, this results in 87\% of individuals losing by not receiving commitment.
+Taking the conditional ATE estimates from the ``wide'' causal forest, described in Section \ref{sec:RF} as ground truth, this results in 93\% of individuals losing by not receiving commitment.
 The second row assigns all borrowers to forced commitment, yielding error rates that are the exact mirror image of those from the first row.
@@
 In each of these rows, the assignment rule ranks borrowers from highest to lowest by their estimated probability of having a positive CATE.
-The 91\% of borrowers with the highest estimated probabilities are assigned to treatment, matching the overall rate of positive CATE estimates from the ``wide'' RF model.
+The 89\% of borrowers with the highest estimated probabilities are assigned to treatment, matching the overall rate of positive CATE estimates from the ``wide'' RF model.
 The sixth row gives the percentage of miss-classification that would follow from the observed choice.
@@
 \begin{figure}[H]
-    \caption{Partition of TUT by behavioral variables.}
+    \caption{Partition of TUT by behavioral variables}
     \label{tut_beh_partition}
@@
 Using the 80 right most points, we estimate a \textit{positive} relationship.
-        %\textit{Do file: }  \texttt{choose\_wrong\_quant\_wrong.do, choose\_wrong\_quant\_wrong\_decomposition.do}
+        %\textit{Do file: }  \texttt{choose\_wrong\_quant\_wrong\_tot\_tut.do, choose\_wrong\_quant\_wrong\_decomposition.do}
 \end{figure}
@@
   \caption{Cumulative Distribution Function of Conditional ATE Estimates}
-  \includegraphics[width=0.75\textwidth]{Figuras/line_better_forceall_apr_te_cf.pdf} 
+  \includegraphics[width=0.75\textwidth]{Figuras/cdf_CATE.pdf} 
     \label{fig:CATEsurvival}
@@
 We estimate that at least 91\% of borrowers have a positive conditional ATE.
+%\textit{Do file: }  \texttt{cdf_CATE.do}
 

### 2023-10-15 RScripts/te_grf.R

@@ -290,13 +290,8 @@ te_grf <- function(data_in, outcome_var, name) {
 
 # READ DATASET
 apr <- read_csv('./_aux/apr_te_heterogeneity.csv') 
-fc_admin <- read_csv('./_aux/fc_admin_te_heterogeneity.csv') 
-def_c <- read_csv('./_aux/def_c_te_heterogeneity.csv') 
-des_c <- read_csv('./_aux/des_c_te_heterogeneity.csv') 
 
 #####################################################
 te_grf(apr,"apr","apr") 
-te_grf(fc_admin,"fc_admin","fc_admin") 
-te_grf(def_c,"def_c","def_c") 
-te_grf(des_c,"des_c","des_c") 
+
 

### 2023-10-16 Tables/old/exp_arms.tex
cleaning of project folder - build replication files

% Table generated by Excel2LaTeX from sheet 'exp_arms'
\begin{tabular}{p{7.68em}ccccc}
\toprule
\multicolumn{1}{r}{} &       & \multicolumn{2}{c}{\cellcolor[rgb]{ .675,  .725,  .792}Fee arms} & \multicolumn{2}{c}{\cellcolor[rgb]{ .851,  .882,  .949}Promise arms} \\
\midrule
\multicolumn{1}{r}{} & \multicolumn{1}{p{4.045em}}{Control} & \multicolumn{1}{p{3.365em}}{Forced-fee} & \multicolumn{1}{p{4.045em}}{Choice} & \multicolumn{1}{p{4.045em}}{Forced} & \multicolumn{1}{p{4.045em}}{Choice } \\
\cmidrule{2-6}\rowcolor[rgb]{ .706,  .776,  .906} Randomization arms & \cellcolor[rgb]{ .851,  .882,  .949}2585 & \cellcolor[rgb]{ .851,  .882,  .949}2465 & \cellcolor[rgb]{ .851,  .882,  .949}3406 & \cellcolor[rgb]{ .851,  .882,  .949}2143 & \cellcolor[rgb]{ .851,  .882,  .949}2755 \\
Surveys & 2036  & 1907  & 2710  & 1757  & 2216 \\
\rowcolor[rgb]{ .706,  .776,  .906} Ended up pawning & \cellcolor[rgb]{ .851,  .882,  .949}1984 & \cellcolor[rgb]{ .851,  .882,  .949}1840 & \cellcolor[rgb]{ .851,  .882,  .949}2634 & \cellcolor[rgb]{ .851,  .882,  .949}1724 & \cellcolor[rgb]{ .851,  .882,  .949}2186 \\
\bottomrule
\bottomrule
\end{tabular}%

### 2023-10-16 donde.tex
cleaning of project folder - build replication files

@@
 Figure \ref{fan_park_bounds} plots the sharp bounds for $F_{\delta}$ based on the APR outcome defined above in Section \ref{costs}.
-Our point estimates of $\underline{F}(0)$ and $\overline{F}_0$ are .03 and .77 respectively, with associated 95\% confidence intervals of [0.024, 0.050] and [0.75, 0.80], which says that at least 23\% of individual borrowers benefit from commitment (and at most 97\%).\footnote{Confidence intervals are constructed using the asymptotic distribution for the bounds.
+Our point estimates of $\underline{F}(0)$ and $\overline{F}_0$ are .03 and .77 respectively, with associated 95\% confidence intervals of [0.025, 0.050] and [0.75, 0.80], which says that at least 23\% of individual borrowers benefit from commitment (and at most 97\%).\footnote{Confidence intervals are constructed using the asymptotic distribution for the bounds.
 See \cite{fan2010sharp} for details.}
@@
     The bounds are pointwise sharp: at any specified value of $\delta$ the bounds $\underline{F}(\delta) \leq F_\Delta(\delta) \leq \overline{F}(\delta)$ cannot be improved without imposing additional assumptions.
-    Evaluating the bounds at $\delta = 0$, we see that between 24\% and 97\% of borrowers have a positive individual treatment effect.
+    Evaluating the bounds at $\delta = 0$, we see that between 23\% and 97\% of borrowers have a positive individual treatment effect.
     This is greater than the share of borrowers who chose commitment: 11\%.

### 2023-10-16 presentation.tex
add row to hit-miss table for chocie rule & text editing
cleaning of project folder - build replication files

@@
     \caption{Pawnshop}
-        \includegraphics[width=0.95\textwidth]{Figuras/empenio2.png}
+        \includegraphics[width=0.95\textwidth]{Figuras/empenio2_.png}
     \end{center}
@@
     \caption{Appraisers  inside a pawnshop}
-        \includegraphics[width=0.95\textwidth]{Figuras/empenio9.png}
+        \includegraphics[width=0.95\textwidth]{Figuras/empenio9_.png}
     \end{center}
@@
     \caption{Waiting for appraisal}
-        \includegraphics[width=0.95\textwidth]{Figuras/empenio11.png}
+        \includegraphics[width=0.95\textwidth]{Figuras/empenio11_.png}
     \end{center}
@@
     \caption{Lost pawns which are for sale}
-        \includegraphics[width=0.95\textwidth]{Figuras/empenio3.png}
+        \includegraphics[width=0.95\textwidth]{Figuras/empenio3_.png}
     \end{center}
@@
     \begin{figure}[H]
-    \label{ExplanatoryMaterial}
+    \label{ExplanatoryMaterial1}
     \begin{center}
@@
          \begin{figure}[H]
-    \label{ExplanatoryMaterial}
+    \label{ExplanatoryMaterial2}
     \begin{center}
@@
    \begin{equation*}
-    \text{Financial Cost}_i =  \underbrace{\sum_t P^i_{it}}_{\text{Pay to Interest}} + \underbrace{\sum_t P^f_{it}}_{\text{Pay to Fees}}  + \mathds{1}(\text{Default}_i) \times \left[\text{Pawn Val}_i + \underbrace{\sum_t P^c_{it}}_{\text{Pay to Capital}} \right]
+    \text{Financial Cost}_i =  \underbrace{\sum_t P^i_{it}}_{\text{Pay to Interest}} + \underbrace{\sum_t P^f_{it}}_{\text{Pay to Fees}}  + \mathds{1}(\text{Default}_i) \times \left[\text{(Appr.
+value - Loan Diff)}_i + \underbrace{\sum_t P^c_{it}}_{\text{Pay to Capital}} \right]
    \end{equation*}
@@
 \resizebox{0.95\textwidth}{!}{
-\small{\input{./Tables/decomposition_main_te_pres1.tex}}
+\small{\input{./Tables/decomposition_main_te.tex}}
 }
@@
 \begin{center}
-\scriptsize{\input{./Tables/mechanism1_pres.tex}}
+\scriptsize{\input{./Tables/mechanism_pres1.tex}}
 \end{center}
@@
 \begin{center}
-\footnotesize{\input{./Tables/mechanism2_pres.tex}}
+\footnotesize{\input{./Tables/mechanism_pres2.tex}}
 \end{center}
@@
 \begin{center}
-\footnotesize{\input{./Tables/mechanism3_pres.tex}}
+\footnotesize{\input{./Tables/mechanism_pres3.tex}}
 \end{center}
@@
 \resizebox{0.95\textwidth}{!}{
-\small{\input{./Tables/fc_robustness_pres.tex}}
+\small{\input{./Tables/fc_robustness.tex}}
 }
@@
 \begin{center}
-\small{\input{./Tables/tot_tut_pres1.tex}}
+\small{\input{./Tables/tot_tut.tex}}
 \end{center}
@@
 \begin{center}
-\small{\input{./Tables/learning_exp_pres.tex}}
+\small{\input{./Tables/learning_exp.tex}}
 \end{center}
@@
     \begin{itemize}
-    \item   We estimate the TuT conditional on $X_i=1$ or $X_i=1$ (say $X_i= PB_i$ or $=Confidence_i$) and see which subppulations have larger TuT.
+    \item   We estimate the TuT conditional on $X_i=1$ or $X_i=1$ (say $X_i= PB_i$ or $=Confidence_i$) and see which sub-populations have larger TuT.
 
@@
 \end{itemize}
-\begin{columns}
-\begin{column}{.45\textwidth}
 \begin{figure}[H]
     \caption{TuT}
-        \includegraphics[width=1.1\textwidth]{Figuras/tut_beh_partition.pdf}
-\end{figure}
-\end{column}
-
-\begin{column}{.45\textwidth}
-    \begin{figure}[H]
-    \caption{ToT}
-        \includegraphics[width=1.1\textwidth]{Figuras/tot_beh_partition.pdf}
-\end{figure}
-\end{column}
-\end{columns}
+        \includegraphics[width=0.5\textwidth]{Figuras/tut_beh_partition.pdf}
+\end{figure}
 \end{frame}
@@
     \begin{figure}
-        \caption{CATE (APR)}
-        \centering
-        \includegraphics[width=0.5\textwidth]{Figuras/he_dist_apr_pro_2.pdf}
+        \caption{CATT (APR)}
+        \centering
+        \includegraphics[width=0.5\textwidth]{Figuras/he_dist_tau_hat_tut.pdf}
         \end{figure}
@@
         \centering
-\includegraphics[width=0.8\textwidth]{Figuras/ct_eff.pdf}
+\includegraphics[width=0.8\textwidth]{Figuras/crf_apr.pdf}
         \end{figure}
@@
         \begin{figure}
-        \label{choose_wrong}
+       % \label{choose_wrong}
         \caption{Mistakes in choice arm}
@@
         \centering
-        \includegraphics[width=0.65\textwidth]{Figuras/line_better_forceall_apr_te_cf.pdf}
+        \includegraphics[width=0.65\textwidth]{Figuras/cdf_CATE.pdf}
         \end{figure}
@@
 
-\begin{frame}{Appraiser FE}
-\label{clerk_fe}
-\begin{table}[H]
-\begin{center}
-\resizebox{0.95\textwidth}{!}{
-\small{\input{./Tables/clerk_fe.tex}}
-}
-\end{center}
- \scriptsize
-
-%\textit{Do file: } \texttt{clerk\_fe.do}
-\end{table}
-    \hyperlink{main_results}{\beamerbutton{Back}}
-
-\end{frame}
-
 \begin{frame}{Survival Graph}
@@
 \resizebox{0.9\textwidth}{!}{
-\footnotesize{\input{./Tables/censoring_imp_pres.tex}}
+\footnotesize{\input{./Tables/censoring_imp.tex}}
 }
@@
 % \end{frame}
-
-\begin{frame}{Bounding Individual Treatment Effects}
-\label{fan_park_bounds}
-
-\begin{figure}[H]
-    \caption{Fan \& Park bounds for benefit in effective FC }
-
-    \begin{center}
-        \includegraphics[width=0.75\textwidth]{Figuras/fan_park_bounds_fc_admin.pdf}
-    \end{center}
-
-\end{figure}
- \hyperlink{choice_hte}{\beamerbutton{Back}}
-\end{frame}
 

### 2023-10-16 MATLAB/eu.m

@@ -1,6 +1,0 @@
-function [y] = eu(x, mu, sigma)
-%Expected utility of log-normal distribution with degree of RRA x
-y = exp((1-x).*mu+0.5*((1-x).*sigma).^2)./(1-x);
-
-end
-

### 2023-10-16 MATLAB/lognormal_fit.m

@@ -1,48 +1,0 @@
-clear all 
-close all
-clc
-FC = readmatrix('../_aux/fc_admin_disc.csv');
-log_FC = log(FC); 
-
-%% MLE
-[pHat,pCI] = lognfit(FC,0.05);
-params.mu = pHat(1); params.sigma = pHat(2);
-[~,pCov] = lognlike(pHat,FC);
-
-%% Empirical/Theoretical CDF
-x_values = linspace(min(FC),max(FC));
-[p,pLo,pUp] = logncdf(x_values,params.mu,params.sigma,pCov);
-
-figure;
-hold on
-ecdf = cdfplot(FC);
-plot(x_values,p,'r-')
-plot(x_values,pLo,'r--')
-plot(x_values,pUp,'r--')
-legend('Empirical CDF','Log-normal CDF','Hi','Lo','Location','best')
-hold off
-
-%% Kolmogorov-Smirnov / Anderson-Darling
-log_FC_std = (log_FC-params.mu)/params.sigma;
-[h1,p1] = kstest(log_FC_std);
-[h2,p2] = adtest(log_FC);
-
-%% Expected Utlity
-eta = linspace(0,1,1000);
-U = eu(eta,params.mu,params.sigma);
-U1 = eu(eta,pCI(1,1),pCI(1,2)); U2 = eu(eta,pCI(1,1),pCI(2,2));
-U3 = eu(eta,pCI(2,1),pCI(1,2)); U4 = eu(eta,pCI(2,1),pCI(2,2));
-
-
-figure;
-hold on
-p = plot(eta,U,'b-');
-p1 = plot(eta,U1,'b--');
-p2 = plot(eta,U2,'b--');
-p3 = plot(eta,U3,'b--');
-p4 = plot(eta,U4,'b--');
-xlabel('RRA degree');
-ylabel('FC');
-hold off
-
-

### 2023-10-16 MATLAB/value_func.m

@@ -1,15 +1,0 @@
-function [z] = value_func(p, y, v, shocks, parms)
-% Value function
-
-if (p >= m)
-    val = parms.V;
-else
-    val = 0;
-end
-
-% Interpolation
-v_interp = chebfun(v,[0,1],'equi');
-z = val + log(y-p) + parms.delta*mean(v_interp(parms.mu + parms.rho*y + shocks));
-
-end
-

### 2023-10-16 donde.tex
checkpoint before text editing - here all the results are final

@@
 \begin{align*}
-    (\text{APR})_i =&\left( 1 + \frac{\frac{\text{Financial Cost}_i}{\text{Appraised Value}_i}}{\text{loan term}_i}\right)^{\text{loan term}_i}-1 
+    (\text{APR})_i =&\left( 1 + \frac{\frac{\text{Financial Cost}_i}{\text{Loan Value}_i}}{\text{loan term}_i}\right)^{\text{loan term}_i}-1 
 \end{align*}

### 2023-10-16 presentation.tex
checkpoint before text editing - here all the results are final

@@
    \begin{equation*}
-    (\text{APR})_i =\left( 1 + \frac{\frac{\text{Financial Cost}_i}{\text{Appraised Value}_i}}{\text{loan term}_i}\right)^{\text{loan term}_i}-1 
+    (\text{APR})_i =\left( 1 + \frac{\frac{\text{Financial Cost}_i}{\text{Loan Value}_i}}{\text{loan term}_i}\right)^{\text{loan term}_i}-1 
 \end{equation*}

### 2023-10-21 Tables/Attrition.tex
cleaning of project folder - build replication files
stabilize cleaning files & internal validity analysis for number of pawns balance

--- 2023-01-18 Tables/Attrition.tex
@@
 \midrule
-Number of branch-day pawns & 34    & 34    & 36    & 0.52 \\
-      & (3)   & (2.9) & (1.8) &  \\
-\multicolumn{1}{p{12.82em}}{Ended up pawning} & 0.98  & 0.97  & 0.97  & 0.62 \\
+Number of branch-day pawns & 31    & 31    & 36    & 0.19 \\
+      & (2)   & (2.1) & (2)   &  \\
+\multicolumn{1}{r}{median} & 27    & 28    & 31    & 0.15 \\
+\midrule
+Number of branch-day borrowers & 21    & 23    & 25    & 0.1 \\
+      & (1.2) & (1.4) & (1.3) &  \\
+\multicolumn{1}{r}{median} & 19    & 21    & 21    & 0.46 \\
+\midrule
+\multicolumn{1}{p{15.82em}}{Ended up pawning} & 0.98  & 0.97  & 0.97  & 0.62 \\
       & (0.01) & (0.01) & (0.01) &  \\
 Survey response rate & 0.79  & 0.76  & 0.77  & 0.62 \\
-      & (0.02) & (0.02) & (0.01) &  \\
+      & (0.02) & (0.02) & (0.02) &  \\
 \midrule
-Obs   & 1770  & 1954  & 2580  &  \\
+Obs   & 101   & 97    & 129   &  \\
 \bottomrule

### 2023-10-21 donde.tex
stabilize cleaning files & internal validity analysis for number of pawns balance

@@
 Second, do borrowers recognize this benefit, demanding commitment in sufficient numbers?
-Finally, and most uniquely given the presence of a forced commitment arm, we are able to ask whether the \textit{right} borrowers voluntarily demand commitment.
-In particular, we use the choice, control, and forced arms to point identify the Treatment on the Treated (TOT) and the Treatment on the Untreated (TUT) effects, along with the average selection on gains (ASG) and average selection bias (ASB).
+Finally, and most uniquely we are able to ask whether the \textit{right} borrowers voluntarily demand commitment.
+This ability comes from the unique three-armed experimental design, which we call the ``controlled choice design'' for short.
+As we show below, our design point identifies not only the overall effect of forced commitment--the average treatment effect (ATE)--but also the effect of commitment for borrowers who would \emph{voluntarily} choose it--the Treatment on the Treated (TOT) effect--along with the effect of commitment for borrowers who would \emph{not}--the Treatment on the Untreated (TUT) effect.
+Our design can be viewed as a juxtaposition of \emph{two} randomized encouragement designs, each with one-sided non-compliance; one of them identifies the TOT while the other identifies the TUT.
+By identifying both the TOT and TUT effects in the same experiment, the controlled choice design allows us to examine the empirical relevance of ``selection on gains'' also known as Roy-type selection into treatment: do borrowers who voluntarily choose commitment have higher average treatment effects than those who do not?
+The ``average selection on gains''--$\text{ASG} = \text{TOT} - \text{TUT}$ answers this question directly.
+The controlled choice design also point identifies the average selection bias (ASB)--the average difference in untreated potential outcomes for those who choose commitment relative to those who do not--along with the average selection on levels (ASL)--the analogous comparison for treated (commitment) potential outcomes.
+Taken together, these causal effects allow us to ``go under the hood'' of our baseline ATE results, and paint a more nuanced and economically-relevant picture of the effects of commitment.
+We are unaware of any other paper that simultaneously identifies all of these causal effects without recourse to additional structural modeling assumptions.
 
@@
 While \cite{fowlie2021default} likewise exploited a three-armed experimental design in their study of the effect of electricity pricing, they identified two TOT effects for different groups of ``treated'' households, whereas we simultaneously identify the TOT and TUT effects defined with respect to a single ``treated'' group of borrowers.
-We call our approach the ``Controlled Choice design'' for short.
+%We call our approach the ``Controlled Choice design'' for short.
 Other approaches to going beyond local average treatment effects (LATE) from the literature either assume no unobserved selection-on-gains \citep{aronow2013beyond,angrist2013extrapolate} (the ``LATE-and-reweight'' approach) or rely on a combination of instruments with rich support and additional structural assumptions such as additive separability of observed and unobserved determinants of treatment effect heterogeneity \citep{heckman2007econometric, cornelissen2018benefits} (the marginal treatment effects approach).

### 2023-11-15 OA.tex
cleaning of project folder - build replication files
limited and balanced attrition - analysis for internal validity

@@
 \vspace{.1in}
+\subsection{Internal Validity}
+
+\begin{figure}[H]
+     \caption{Box-plot across arms}
+    \label{boxplot_attrition}
+    \begin{center}
+    \begin{subfigure}{0.45\textwidth}
+    \caption{Number of pawns}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/box_plot_num_pawns.pdf}
+    \end{subfigure}
+        \begin{subfigure}{0.45\textwidth}
+    \caption{Number of borrowers}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/box_plot_num_pawns.pdf}
+    \end{subfigure}
+    \end{center}
+    \scriptsize
+        This figure presents box-plot for the number of pawns and borrowers per branch-day across different arms.
+The solid black line represent the median, while the gray line represent the mean.
+The dots on top of the box-plot represent an implicit CDF.
+\end{figure}
+
+% \begin{figure}[H]
+%      \caption{Number of pawns and borrowers before and after the experiment}
+%     \label{line_pawns_before_after}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/after_before_bal.pdf}
+%     \scriptsize
+%         This figure shows the number of pawns and borrowers before, during, and after the experiment for the different branches.
+% \end{figure}
+
+% \begin{figure}[H]
+%      \caption{No discontinuity in the number of pawns before and after experiment}
+%     \label{rd_pawns}
+%        \begin{center}
+%     \begin{subfigure}{0.45\textwidth}
+%     \caption{Number of pawns - before}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/rd_before_pawns.pdf}
+%     \end{subfigure}
+%         \begin{subfigure}{0.45\textwidth}
+%     \caption{Number of pawns - after}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/rd_after_pawns.pdf}
+%     \end{subfigure}
+%      \begin{subfigure}{0.42\textwidth}
+%     \caption{Number of borrowers - before}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/rd_before_borr.pdf}
+%     \end{subfigure}
+%         \begin{subfigure}{0.45\textwidth}
+%     \caption{Number of borrowers - after}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/rd_after_borr.pdf}
+%     \end{subfigure}
+%     \end{center}
+%     \scriptsize
+%         This figure shows the number of pawns and borrowers before, during, and after the experiment for the different branches.
+% \end{figure}
 
@@
     \begin{center}
-    \begin{subfigure}{0.42\textwidth}
+    \begin{subfigure}{0.405\textwidth}
     \caption{Appraiser/tellers inside a pawnshop}
@@
     \end{subfigure}
-    \begin{subfigure}{0.42\textwidth}
+    \begin{subfigure}{0.415\textwidth}
     \caption{Lost pawns which are for sale}
@@
 This is a best guess of the outcome on censored loans.
-Using this prediction, we replicate the main experimental results and find that the treatment effect on financial cost increases from -378 (main results) to -530 (censored loans predicted), and the APR from -34\% to -62\%.
+Using this prediction, we replicate the main experimental results and find that the treatment effect on financial cost increases from -204 (main results) to -264 (censored loans predicted), and the APR from -11\% to -17\%.
 Hence, while the censoring issue does have a substantial influence on the magnitude of our estimated treatment effects, these  checks confirm that a) the core results are robust to censoring, and b) the headline approach that we take to the issue is conservative and is likely understating the true magnitude of impacts.
@@
 Since $\tau_i$ and $\psi_i$ do not depend on the test set, inference for the regression in \eqref{eq:chernreg} is straightforward conditional on the Training/Test split.  
-Our estimate for $\beta_2$ is 2.5 with a one-sided heteroskedasticity-robust (HC3) of 0.43.
+Our estimate for $\beta_2$ is 2.56 with a one-sided heteroskedasticity-robust (HC3) of 0.43.
 Thus we easily reject the null hypothesis of homogeneous treatment effects.
@@
 
-The \cite{huber_mellace} bounds for the TOT \& TUT APR are respectively:  $[-119, 122]$, and $[-4.2, 24.6]$.
+The \cite{huber_mellace} bounds for the TOT \& TUT APR are respectively:  $[-119, 123]$, and $[-4.2, 24.8]$.
 Since both TUT (24) and ToT (122) estimates from the LATE approach lies inside these bounds, we cannot falsify the exclusion restriction.

### 2023-11-15 donde.tex
limited and balanced attrition - analysis for internal validity

@@
 
-In the context of pawnbroker lending, we show that forcing people into commitment contracts with a regular repayment structure decreases their (fee-including) financial cost by 20\%, increases the likelihood of recovering their pawn by 15\%, and increases the likelihood of repeat business by 20\%.
+In the context of pawnbroker lending, we show that forcing people into commitment contracts with a regular repayment structure decreases their (fee-including) financial cost by 22\%, increases the likelihood of recovering their pawn by 15\%, and increases the likelihood of repeat business by 19\%.
 Using a multi-armed RCT that includes both a voluntary and a forced arm, we illustrate how to point-identify both the Treatment on the Untreated and the Treatment on the Treated.
@@
 \section{Introduction}
+
+The behavioral finance literature has established an important role for commitment devices in helping consumers to achieve their own financial goals.
+While most of the academic studies on commitment focus on the role of voluntary self-commitment \citep{thaler2004save, prina2015banking, brune2016facilitating, callen2019headwaters, Pascaline, Ashraf}, in reality the predominant use of rigid structure in financial services is involuntary; firms only offer a product with these features embedded.
+\cite{Laibson2018} has referred to this implicit bundling of commitment devices as ‘private paternalism’, and its logic is that individuals may benefit from commitment and yet not explicitly demand it.
+Comparing voluntary versus paternalistic programs requires that we form counterfactuals for two different groups of people: those who would naturally choose commitment, and those who would not (since the latter group is treated only under paternalist policies).
+In this paper we present an experimental design and analysis structure that \textcolor{teal}{point-identifies} and provides estimates for both, the treatment on the treated (TOT), as well as the treatment on the untreated (TUT).
+This permits a clear window into the case for paternalistic (forced) rather than voluntary commitment in financial services.
+
+%The relationship between treatment effects and willingness to accept treatment is a core concern in the econometrics literature. 
+\textcolor{teal}{The literature has estimated the TOT and the TUT under a variety of techniques.}
+By relaxing the often restrictive parametric assumptions of classic sample selection models, the Marginal Treatment Effects (MTE) approach \citep{heckman2007econometric} provides a powerful toolbox for studying this relationship.
+In principle, MTE methods allow researchers to use observational data and a single excluded instrument to compare treatment effects across those who are willing and unwilling to accept treatment.
+In practice, however, unless the instrument has an extremely rich support set, this difference of treatment effects can only be point identified by using additional modeling assumptions to extrapolate beyond the information contained in the data \citep{mogstad2018using}.
+\textcolor{teal}{Another research strategy uses} Becker-Degroot-Marschak (BDM) mechanisms, incentivizing choice prior to treatment assignment to elicit willingness to pay (WTP) for treatment \citep{becker1964measuring}.
+%If subjects have standard preferences, then the BDM mechanism is incentive-compatible and the elicited distribution of WTP does not depend on the distribution from which prices were drawn.
+A number of studies, however, find that the elicited WTP changes arbitrarily with the distribution of prices used in the elicitation exercises \citep{bohm1997eliciting,banerji2014detection} %, casting considerable doubt on the assumption of standard preferences.
+\textcolor{teal}{making elicitation unreliable, and suggesting subjects have non-standard preferences, in which case BDM would lose the incentive-compatibility property} %In general, the BDM mechanism is no longer incentive compatible if subjects have non standard preferences
+\citep{mamadehussene2023reliability}. %For this reason, WTP elicited via the BDM mechanism may not provide a good proxy for real-world treatment take-up. 
+This study overcomes the two difficulties above by combining a novel three-armed randomized experiment (control, forced treatment, and treatment choice arms) with two mild and transparent exclusion restrictions, to point identify the relevant TOT and TUT in a real-world, high-stakes setting.
+This allows us to study the case for paternalistic commitment head-on, with minimal assumptions.
+
+We implement the study in an important and understudied context: that of pawnshop lending.
+We run an experiment covering close to 5,000 pawnshop clients in 6 branches of a lender in Mexico City.
+Our control arm illustrates the costs of the status quo contract: fully \emph{44\%} of borrowers default and so lose their pawn as well as any payments made towards principal.\footnote{These high default rates are not uncommon, in the US default is also high at 15\% (\url{https://tinyurl.com/yc2x5bjf}).} In this context we implement a ``commitment choice'' arm, in which borrowers can voluntarily opt into a structured repayment contract at the time of taking a loan.
+The structured contract requires borrowers to make three monthly payments rather than one balloon payment at the end, with each monthly payment including the accrued interest at that time as well as a nominal fee of 2\% of that month's payment if that payment is delinquent.
+This fee serves as a reminder and a means of reinforcing the importance of these interim payments.
+In addition, we include a ``forced commitment'' arm, in which all borrowers are \emph{required} to repay using the structured monthly contract, the one offered on an opt-in basis in the commitment choice arm.
+
+The combination of voluntary and forced commitment within the RCT allows us to address several key questions.
+First, do structured repayment contracts lower financial costs for pawnshop borrowers?
+Second, do borrowers recognize this benefit, demanding commitment in sufficient numbers?
+Finally, and most uniquely we are able to ask whether the \textit{right} borrowers voluntarily demand commitment.
+This ability comes from our unique three-armed experimental design, which we call the ``controlled choice design'' for short.
+We go beyond the average treatment effect (ATE).
+Our design can be viewed as a juxtaposition of \emph{two} randomized encouragement designs, each with one-sided non-compliance; one of them point identifies the effect of commitment for borrowers who would \emph{voluntarily} choose (TOT),
+while the other point identifies the effect of commitment for borrowers who would \emph{not} (TUT).
+
+%Our design point identifies not only the overall effect of forced commitment---the average treatment effect (ATE)---but also the effect of commitment for borrowers who would \emph{voluntarily} choose it (TOT) along with the effect of commitment for borrowers who would \emph{not} (TUT).
+By identifying both the TOT and TUT effects in the same experiment, the controlled choice design allows us to examine the empirical relevance of ``selection on gains'' also known as Roy-type selection into treatment by estimating the ``average selection on gains'' $\text{ASG} = \text{TOT} - \text{TUT}$.
+This enables us to test --not assume-- whether borrowers who voluntarily choose commitment have higher average treatment effects than those who do not.
+The controlled choice design also point identifies the average selection bias (ASB)--the average difference in untreated potential outcomes for those who choose commitment relative to those who do not--along with the average selection on levels (ASL)--the analogous comparison for treated (commitment) potential outcomes.
+Taken together, these causal effects allow us to ``go under the hood'' of our baseline ATE results, and paint a more complete and economically-relevant picture of the effects of commitment.
+We are unaware of any other paper that simultaneously identifies all of these causal effects without recourse to additional structural modeling assumptions.
+
+This controlled choice design is key to measuring the effects of mandated versus voluntary imposition of product features, \textcolor{teal}{and thus a first step in understanding what \cite{Laibson2018} calls `private paternalism'.
+This question is of interest in a large class of cases.
+Financial contracts for instance already have a high dose of private paternalism and forcing features: most contracts have built-in frequent payments for instance.
+But beyond finance, in education, most teachers mandate homework with deadlines to deal with procrastination \citep{Ariely}.
+In the workplace, firms monitor employee attendance,\footnote{\url{https://www.wsj.com/lifestyle/careers/attention-office-resisters-the-boss-is-counting-badge-swipes-5fa37ff7}.} but also set and monitor time-specific goals.
+In the public policy domain we have seatbelt mandates, age-dependent medical checkups, etc., which often go beyond nudging.
+Having a rigorous way to estimate the causal effects of mandates vs choice policies ---and not just for the average individual--- is critically important.}
+
+%categorized by \cite{Laibson2018} as possessing `private paternalism’ where commitment is involuntarily embedded into product features (classroom requirements and exams in schools, employee monitoring in the workplace, or highly structured financial contracts).
+The question of whether people choose what is right for themselves is particularly salient in pawn lending, \textcolor{teal}{as these pawn borrowers often need to borrow for emergencies under significant stress\footnote{There is a large literature showing that stress impairs cognitive function, e.g.
+\cite{StressReview}.}.
+They are also more likely to have little schooling, financial education, and formal credit market access.}  The Pawn loans industry is interesting in itself.
+It is one  of the oldest, most understudied, and most prevalent forms of borrowing \citep{carter2012pawnshops}.
+For example, there are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues (in China it is a \$43 billion industry).\footnote{\url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.} Our partner pawn lender (henceforth Lender $P$) alone served more than 1 million clients in Mexico in the last 3 years with more than 4 million contracts.\footnote{For comparison there were 2.3 million micro-finance clients in Mexico in 2009 (\cite{Pedroza:2010}).}
+
+One last highlight.
+Interestingly, pawnshop lending presents an inverted lending case: since these loans are over-collateralized, the lender in the contract stands to gain the most when borrowers default.
+Our partner's standard pawn contract gave 70\% of the value of gold collateral in credit, and charged a monthly interest rate of 7\% for loans of a three-month duration, with a flexible no-reminders contract, that can be paid back anytime before the loan comes due at no penalty.
+This contract, which may cause default, is the standard contract in the industry.
+This combination of features, and the fact that the gold pawn is highly liquid, means that the lender makes 90\% more profit over three months from a borrower who defaults than one who repays (30\% of collateral value recovered under default, 15.8\% of collateral value paid in interest if loan fully repaid).
+While an older literature considers the exploitative potential of over-collateralization and underpriced collateral \citep{basu1984implicit}, the implication of such contracts has not been analyzed in the behavioral literature.
+Thus, while our paper makes a methodological point, the substantive results in the application are important for this understudied industry, and could be applied more broadly whenever mandates vs choice is under consideration.
+%When the lender desires default, the repayment-inducing features of commitment-style repayment contracts become undesirable and there may be incentives for the principal to create contracts with no structure, no reminders, and simple balloon payments.
+To repurpose the language of \cite{Laibson2018}, we suggest that pawn contracts effectively shroud their \textit{lack} of commitment features to induce default in a manner that is not obvious to borrowers.
+Given that pawnshops, moneylenders, and paycheck lending institutions are likely to face client pools disproportionately made up of impatient and time-inconsistent individuals, the design of such contracts may have serious consequences for the financial lives of the poor.
+
+Coming to our results.
+We find that commitment is strongly effective in preventing default in pawnshop lending, with the average individual in the forced arm paying financing costs inclusive of fees that are 22\% lower than the control, while default decreases by 6.6 percentage points (15\% of the mean).
+In terms of Annual Percentage Rates, the financial cost of borrowing is reduced by 11 percentage points (19\% of the mean).
+That is, by imposing the structure of commitment it is possible to save borrowers money by charging them fees!
+These results are robust qualitatively to including transport costs of going to the branch plus losing a day's wage for each visit, using each borrower's subjective value of the pawn rather than the appraised value of the gold, and adjusting for lost liquidity from requiring monthly payments.
+
+The monthly payment contract seems to achieve these cost savings by speeding up payments and by generating an early bifurcation of borrowers into those that will recover the pawn and those that will not.
+By inducing borrowers either to fully recover, or to default without making any payments, the monthly payment contract saves money that would otherwise have been paid towards loans that ultimately default, money which is lost to the borrower.
+In the treatment group, the first payment occurs 13 days earlier, and the fraction recovering on the first visit is 7.9 percentage points higher.
+Commitment contracts also decrease by 7 percentage points the fraction of borrowers who make a payment but ultimately fail to recover their pawn.
+Treatment effects are concentrated in the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery.
+That is, the commitment contract induces people who would otherwise pay something towards recovery but default to instead pay more and faster, making them more likely to recover their pawn at a lower financial cost.
+We find this bifurcation mechanism interesting and little discussed in the literature.
+
+In spite of a large average treatment effect documenting financial cost savings, only 11\% of borrowers in the choice arm actually choose commitment.
+If the effect of commitment were homogeneous, this would be enough to conclude that the 89\% who did not choose it would have been financially better off if they had.
+However, we test and reject the null hypothesis of homogeneous treatment effects using the method of \cite{chernozhukov2018generic}.
+Can the borrowers who did not choose commitment be those who simply don’t need it?
+We address this question by sequentially imposing more structure on the problem.
+%We find that borrowers who are assigned the forced commitment contract are 6.7 percentage points more likely to become repeat costumers than those assigned to the status-quo contract.
+One potential interpretation of this result is that borrowers who experience the frequent payment contract rationally choose to borrow more later on because of the lower effective financial costs that this contract entails.\footnote{An alternative interpretation is that the monthly payments from the commitment contract sap borrowers liquidity, leading them to take a second loan to pay off the first.
+This is unlikely because subsequent loans fall outside the 90 day period within which payments for the first loan are due.
+Moreover, the correlation is also present conditional on having paid down the first loan.
+Borrowers tend to pledge a different piece for the second loan, so that recovery of the first pawn is also an unlikely explanation.} However, a stronger test of liking the monthly payment contract is whether conditional on coming again, they would choose frequent payments.
+We test this and we cannot reject that demand is higher after experiencing the monthly payment contract, however sample sizes are small and power for this analysis is correspondingly low.
+
+We start our analysis of heterogeneity by bounding the distribution of treatment effects $Y_{1i}-Y_{0i}$ using the two marginal distributions in the treatment and control arms as in \cite{fan2010sharp}.
+We find that at least 23\% of individual borrowers benefit from commitment, implying many borrowers did not demand it even though their individual treatment effect is positive.
+Next, we impose the exclusion restriction that the effect of the contract does not depend on how they got it, that is: choosing a contract has the same treatment effect as being assigned to that contract.\footnote{This is a frequently used assumption even if often implicit.
+For instance, a significant literature uses schooling compulsory laws to estimate the return of one more year of school, and then often interprets that schooling, in general, has this return.} We show that in this case our 3-armed experiment point identifies the TUT.
+We then estimate that the financial cost savings of the TUT is large, at \$192 pesos, equivalent to 10.6 percentage point savings in APR.
+That is, on average borrowers that did \textit{not} choose the frequent payment contract would have benefited from having that contract.%\footnote{We estimate a positive TOT that is larger than the TUT, but it is imprecise--this results from the smaller sample size, given that few chose the monthly payment contract--and the hypothesis of TOT=TUT is rejected only with 13 percent confidence for the APR and 12 percent confidence for default.}
+
+What explains the persistence of no-commitment contracts so contrary to borrowers’ interests in the real world?
+While a simple measure of time inconsistency does not predict heterogeneity in our study, we show substantial levels of over-optimism among borrowers.
+Among borrowers who do not choose it, those with the largest estimated benefits from commitment are the individuals who most systematically over-estimate their own probability of repayment at the time of taking the loan.
+The dramatic improvements in borrower income arising from the commitment contract come directly from the pockets of lenders, reinforcing that the pawn industry as a whole has a strong interest in retaining the status quo.
+
+In a final step, we impose a selection-on-observables assumption and use the Causal Random Forest algorithm of \cite{atheygrf} to estimate conditional average treatment effects (both ATEs and TUTs) for the individual borrowers in our experiment.
+We estimate that 93\% of the borrowers who did not opt for the commitment contract have positive conditional TUT effects, while only 37\% of those who chose commitment have negative conditional TOT effects.
+While targeting commitment products to those that benefit the most is a policy that appears attractive, in this context we find that the usable targeting variables have relatively weak predictive power and hence even the random forest only reduces the overall mis-targeting rate from 9.7\% (all to Forcing) to 9.5\% (our best-case feasible targeting mechanism).
+
+Our paper makes a number of contributions to the literature.
+Two other recent papers also shed some light on private paternalism.
+In the context of food choice, \cite{Sprenger} show that individuals with the most time-inconsistent preferences are actually least likely to demand commitment, suggesting a lack of awareness as to self-control problems.
+In the context of school choice, \cite{Walters} finds that students who select into more effective schools have smaller treatment effects from attending than those who do not.
+Our paper differs from these in both its empirical setting and its methodology.
+As far as we are aware, ours is the first experiment to combine control, forced treatment, and treatment choice arms and explain how such a design can be used to point identify TUT effects and a range of other interesting causal parameters under minimal assumptions.
+While \cite{fowlie2021default} likewise exploited a three-armed experimental design in their study of the effect of electricity pricing, they identified two TOT effects for different groups of ``treated'' households, whereas we simultaneously identify the TOT and TUT effects defined with respect to a single ``treated'' group of borrowers.
+
+Other approaches to going beyond local average treatment effects (LATE) from the literature either assume no unobserved selection-on-gains \citep{aronow2013beyond,angrist2013extrapolate} (the ``LATE-and-reweight'' approach) or rely on a combination of instruments with rich support and additional structural assumptions such as additive separability of observed and unobserved determinants of treatment effect heterogeneity \citep{heckman2007econometric, cornelissen2018benefits} (the marginal treatment effects approach).
+\cite{Walters} takes the latter approach, combining a distance instrument with additional structural assumptions, obtaining model-based TUT and ATE estimates that differ substantially from those implied by a LATE-and-reweight approach.
+In contrast, we leverage our experimental design to point identify the TUT effect using a binary instrument without the need for a structural model, relying instead on relatively weak exclusion restrictions.
+This restriction has testable implications that we fail to reject.
+Rather than assuming away unobserved selection-on-gains, as in the LATE-and-reweight approach, we estimate it directly.
+Unlike \cite{Sprenger} we directly identify the TUT, obviating the need to first elicit preferences before testing for negative selection.
+In a returns-to-education setting, \cite{oreopoulos2006estimating}, uses a similar direct approach to identify a LATE \emph{nearly} equals a TUT effect: the 1944 Butler Act increased the share of British children who remained in school until age 15 from 43\% to over 90\%.
+Because 100\% of borrowers in our forced arm are treated, we identify the TUT rather than an approximation to it.
+
+Our study also speaks to recent research on the effects of payment frequency.
+While experiments in microfinance markets have not shown the same benefits from providing a more regularized repayment environment as we find here \citep{Pande, barboni2023flexible}, these experiments differ from ours in two important ways: they are performed on top of already highly structured contracts, and they involve borrower pools who may have selected into that type of lending precisely because it provides structure.
+These differences may explain why \citep{Pande} finds almost no default in the control group, in stark contrast to our results.
+Second, we provide a deeper analysis of both the take-up and efficacy of voluntary commitment mechanisms.
+A number of papers have found low demand for commitment as we do (\cite{Ashraf}, \cite{Gine}, \cite{Ted}, \cite{Royer}, \cite{Sprenger}) while others have found more robust demand for commitment (\cite{Kremer},  \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}, \cite{Pascaline}).
+Unlike all of these papers, however, we separately point identify and estimate the effects of commitment for borrowers who would and would not choose it.
+This allows us to conduct a more rigorous and nuanced analysis of private paternalism in our empirical context.
+
+Our results suggest that pawn lending markets capture borrower wealth in ways not well summarized by interest rates.
+By overcollateralizing and then structuring loan contracts in a manner encouraging of default, lenders are able to extract substantial value independent of the interest charged.
+Further, the `nudge’ approach generally favored by the behavioral literature (voluntary commitment) does not generate adequate demand in this context.
+The remainder of the paper is structured as follows:  Section \ref{context} provides context and defines our main outcome variables.
+Section \ref{Design} describes the experiment and data sources, and shows pre-treatment balance across arms.
+Section \ref{Experiment} provides the standard ITT analysis of the experiment, while Section \ref{Choice} presents our strategy for estimating ToT and TuT effects, and Section \ref{Paternalism} investigates why paternalism functions so well in this context and whether it can be more finely targeted.
+Section \ref{conclusion} concludes.
+
+\begin{comment}
+%OLD INTRODUCTION:
 
@@
 
+\end{comment}
+
 \section{Context} \label{context}
@@
 If the client returns to pay the principal plus the accumulated interest within 105 days, she received back her pawn, otherwise the pawnbroker kept the piece \textit{and} any payments made.
-Before the contract expired, the client had the right to renew for another 3 months by going to the pawnshop, paying the accumulated interest, and signing a new contract with exactly the same terms and same piece as the original one a (26\% of borrowers renew at least once with a given pawn).
+Before the contract expired, the client had the right to renew for another 3 months by going to the pawnshop, paying the accumulated interest, and signing a new contract with exactly the same terms and same piece as the original one (38\% of borrowers renew at least once with a given pawn).
 This contract was standard in the industry.
@@
 \paragraph{Borrowers.} The clients that pawned understood these terms well (as we verified in interviews).\footnote{87\% of clients report in our survey that they have pawned before.} These clients have little or no access to other types of loans and they value the convenience of pawn borrowing.
-This population of pawn borrowers is economically vulnerable:  30\% of them could not pay either water, electricity \& gas or rent in the past 6 months; 87\% said they are pawning because of an emergency, and only 13\% stated it was to use in a `non-urgent expense'.
-When asked why they are pawning this piece, 5\% responded `lost a family member', `a medical emergency' (11\%), or `an urgent expense' (71\%).
+This population of pawn borrowers is economically vulnerable:  30\% of them could not pay either water, electricity \& gas or rent in the past 6 months; 89\% said they are pawning because of an emergency, and only 12\% stated it was to use in a `non-urgent expense'.
+When asked why they are pawning this piece, 5\% responded `lost a family member', `a medical emergency' (11\%), or `an urgent expense' (72\%).
 
@@
 One potential explanation for high default is that clients are really just knowingly selling their gold piece through a pawn contract on which they intend to default.
-This appears unlikely for several reasons: (a) clients can easily sell the gold and obtain a higher amount of instant cash at gold buying stores located close to almost all our pawnshop branches (see Figure \ref{GoldBuyers}), (b) the reported subjective value of the pawn is larger than the loan size for 86\% of clients, (c) among those that lose their pawn, 48\% paid a positive amount towards its recovery and on average paid 42\% of the value of their loan (see Figure \ref{proxy_naive} in Appendix) --- this can only be rationalized if they expected to recover their pawn, and (d) 74\% of borrowers report a 100\% probability of repaying their loan (and 98\% at least a 50\% chance of repaying) in our baseline survey at the time they take the loan.
+This appears unlikely for several reasons: (a) clients can easily sell the gold and obtain a higher amount of instant cash at gold buying stores located close to almost all our pawnshop branches (see Figure \ref{GoldBuyers}), (b) the reported subjective value of the pawn is larger than the appraised value for 83\% of clients, (c) among those that lose their pawn, 29\% paid a positive amount towards its recovery and on average paid 42\% of the value of their loan (see Figure \ref{proxy_naive} in Appendix) --- this can only be rationalized if they expected to recover their pawn, and (d) 72\% of borrowers report a 100\% probability of repaying their loan (and 98\% at least a 50\% chance of repaying) in our baseline survey at the time they take the loan.
 Note that high default could be detrimental from the lender's point of view, since it may reduce the likelihood that the client becomes a return customer.
@@
 
-Figure \ref{fc_hist}(a) plots a histogram of this financial cost in pesos for all loans in the experiment, distinguishing by whether we observed they defaulted (43\%), recovered their pawn (44\%), or whether they are censored in our data (13\%).
+Figure \ref{fc_hist}(a) plots a histogram of this financial cost in pesos for all loans in the experiment, distinguishing by whether we observed they defaulted (44\%), recovered their pawn (43\%), or whether they are censored in our data (13\%).
 The first thing to note is that those that default incur in higher costs; part of this is mechanical as losing their collateral is part of the cost.
@@
 The branches were selected by Lender $P$ to be dispersed across Mexico City and have varying sizes.
-In four of them the experiment ran for 107 days, and in 2 of them we ran it for a shorter time to economize on data collection costs once we realized we would not be constrained by sample size.
+In four of them the experiment ran for 102 days, and in 2 of them we ran it for a shorter time to economize on data collection costs once we realized we would not be constrained by sample size.
 %Thus we eliminated {the smallest} ones.
-Branches are more than 5 km apart from each other, and there is little substitution among them; only 1\% of consumers appear in more than one of our branches.
+Branches are more than 5 km apart from each other, and there is no substitution among them; none of the consumers appear in more than one of our branches.
 
@@
 Figure \ref{exp_description} shows the design and timing of the experiment, along with the sample sizes in each arm.
-The experiment comprises 13,446 pawns, and our administrative data cover a total of 23,974 pawns.
+The experiment comprises 8,519 pawns, and our administrative data cover a total of 26,180 pawns.
 
@@
 The survey was intentionally short to avoid discouraging the potential clients from pawning, but at the same time it aimed to measure the following: demographics, proxies for income/wealth, education, present-biased preferences, experience pawning, if family or friends commonly asked for money, how time consuming and costly it was to come to the branch, the subjective probability of recovering the piece that they intended to pawn, the subjective value of their piece in money terms (how much money they would sell it for), among others.
-We surveyed 10,437 clients, and the survey response rate was 78\% among clients who took loans.\footnote{Appendix \ref{baseline_survey} transcribes the questionnaire in English.} %\footnote{We also surveyed clients before and after the experiment, so our survey covers a larger sample that we are not using in this paper.}.
+We surveyed 7,210 clients, and the survey response rate was 78\% among clients who took loans.\footnote{Appendix \ref{baseline_survey} transcribes the questionnaire in English.} %\footnote{We also surveyed clients before and after the experiment, so our survey covers a larger sample that we are not using in this paper.}.
 
@@
 Anecdotally, appraisers told us that they did not think refusals differed across arms, and our enumerators informed us that potential clients rarely left the branch without pawning.
-Lender P also never complained to us that our different treatments were hurting sales.} If the treatments had induced demand-side selection, we would expect to see that the number of pawns successfully conducted differ in a systematic way across arms.
-To test for this, we examine the number of loans given per branch-day, with specific attention to whether the Forced Commitment arm led to a lower number of borrowers per day.
+Lender P also never complained to us that our different treatments were hurting sales.}
+
+If the treatments had induced demand-side selection, we would expect to see that the number of pawns successfully conducted differ in a systematic way across arms.
+That is, if potential borrowers disliked being forced into a commitment contract so much so as to leave the branch, we would expect a lower number of pawns on branch days where only the commitment contract is available.
+Table \ref{attrition_table} shows that this is not the case.
+There is no difference at all between the Control and Forced Commitment arm in terms of the number of pawns per branch-day.
+Although we cannot reject equality across the three arms (p-value=0.21), the Choice arm appears to have a somewhat larger number of borrowers than the Control and Forced arms\footnote{p-value=0.23 and 0.12 respectively.}.
+This seems to be due to sampling variance.
+The differences across arms are smaller when we look at medians, or when we look at the number of borrowers pawning (some borrowers pawn more than one piece).
+Figure \ref{boxplot_attrition} shows that entire distributions across arms overlay pretty well with one another, with the choice arm having a few more outliers.\footnote{If we winzorize at the 90th percentile, the mean number of branch-day pawns is numerically the same across arms.}
+
+The bottom panel of Table \ref{attrition_table} shows balance in a more focused way, given that the surveys were conducted prior to the revelation of treatment status.
+We find that in no arm did more than three percent of individuals who responded to the survey go on to refuse loans.
+That is, potential borrowers are not leaving the branch after hearing what the contract is.
+Moreover, the small fraction that leaves is balanced across arms.
+Therefore it appears that the treatments have not induced any endogenous shifts in the composition of borrowers.
+This is consistent with the findings of Table \ref{SS}.
+% To test for this, we examine the number of loans given per branch-day, with specific attention to whether the Forced Commitment arm led to a lower number of borrowers per day.
 The first row of Table \ref{attrition_table} shows there is no difference between the Control and Forced Commitment arm in terms of the number of pawns per branch-day.\footnote{The Choice arm appears to have a somewhat larger number of borrowers than the Control arm (p-value=0.06), but we cannot reject equality with the Forced Commitment arm (p-value=0.41), or across all arms (p-value=0.16).}  The second row makes the same point in a more focused way, given that the surveys were conducted prior to the revelation of treatment status.
@@
 Therefore it appears that the treatments have not induced any endogenous shifts in the composition of borrowers.
-
 A less critical form of attrition would be a differential refusal to answer the survey questions.
@@
 Our core experimental estimates do not use the survey data as covariates, but the Random Forest analysis in Section \ref{Paternalism} is restricted to the subset of borrowers who answered at least some survey questions.
-The bottom row of Table \ref{attrition_table} shows that the survey response rate is broadly similar across arms (about 77 percent).
+The bottom row of Table \ref{attrition_table} shows that the survey response rate is broadly similar across arms (about 78 percent).
 %We can also examine differences in the fraction of borrowers who do respond to the survey and then do not end up taking a loan subsequent to completing the survey, we find that the share is close to 100\% as is the fraction of those 97\% across arms (p-value=0.62).
@@
 Panel B of Table \ref{SS} reports summary statistics across arms from our survey data.
-73\% of clients are women, with an average age of 43 years; 66\% of them have completed high school or more, and 90\% have pawned before, so that our sample has mostly experienced borrowers.
-Finally, the subjective probability of recovery is close to 93\% on average, which makes a stark contrast to the actual rate of recovery of 43\%; borrowers are highly overconfident on average.
+73\% of clients are women, with an average age of 43 years; 66\% of them have completed high school or more, and 87\% have pawned before, so that our sample has mostly experienced borrowers.
+Finally, the subjective probability of recovery is close to 92\% on average, which makes a stark contrast to the actual rate of recovery of 43\%; borrowers are highly overconfident on average.
 The average subjective value they report for the items they pawn is 4084 MXN, much larger than the average appraised gold value of 3238 MXN.
@@
 where $i$ indexes client, $j$ indexes branch, $T_{i}^F$ and $T_{i}^C$ are indicator variables for receiving the Forced or Choice arms, $X_{ij}$ are branch and day-of-week fixed effects.
-Standard errors are clustered at the branch-day level, the unit of treatment assignment\footnote{A minority of clients pawned on more than one day during the experiment: 15\% pawned on two distinct days, and 7.5\% on three or more days.
+Standard errors are clustered at the branch-day level, the unit of treatment assignment\footnote{A minority of clients pawned on more than one day during the experiment: 14\% pawned on two distinct days, and 8\% on three or more days.
 To avoid contamination from earlier treatments to which these individuals were exposed, we restrict our sample to each client's \emph{first visit}.
@@
 The Forced Commitment arm yields large and significant decreases in the cost of loans to clients, as measured either by financial cost or APR.
-Despite causing an increase in fees, the Forced arm leads to a decrease of 379 pesos in the costs of borrowing (out of a group mean of 1851 in the status quo), equivalent to 20\% reduction as a fraction of mean cost.
-These cost savings arise from a 6.5 percentage point (pp) decrease in the probability of default (out of a baseline mean of 44pp,  implying cost savings of 254 pesos), and also from lower interest payments, since as we will document the treatment is effective at speeding up payments, with the benefit that the interest rate applies to a smaller principal.
+Despite causing an increase in fees, the Forced arm leads to a decrease of 204 pesos in the costs of borrowing (out of a group mean of 942 in the status quo), equivalent to 22\% reduction as a fraction of mean cost.
+These cost savings arise from a 6.6 percentage point (pp) decrease in the probability of default (out of a baseline mean of 44pp,  implying cost savings of 79 pesos), and also from lower interest payments, since as we will document the treatment is effective at speeding up payments, with the benefit that the interest rate applies to a smaller principal.
 This translates into a large reduction in APR.
-A credit product that has an effective average APR of 184\% in the status quo arm (inclusive of default) is reduced to a cost of 150\% through the imposition of a more regularized payment structure.
+A credit product that has an effective average APR of 57\% in the status quo arm (inclusive of default) is reduced to a cost of 46\% through the imposition of a more regularized payment structure.
 
@@
 While the first payment for borrowers in the status-quo contract occurs on average only on day 82 (on a 90 days contract), borrowers in the forced commitment arm start paying 13.8 days earlier on average (col 1).
-Not only do they start paying earlier, the first payment is also 7.9\% larger (col 2), and a larger fraction of 7.9\% actually pay in full and recover their pawn in the first payment , compared to 30\% in the status quo contract (col 3).
+Not only do they start paying earlier, the first payment is also 7.9\% larger (col 2), and a larger fraction of 9.7\% actually pay in full and recover their pawn in the first payment , compared to 30\% in the status quo contract (col 3).
 The resolution of the loan (either by payment or default) is shortened by 27.9 days (col 4), and conditional on recovery (an endogenous control) by 17.9 days (col 5).
@@
 On the contrary,  7 percentage points fewer borrowers end up in this situation, compared to 12 percent in the status quo contract.
-Conditional on defaulting those assigned to the Forced commitment contract have paid 3.9\% less of their loan (col 7), and 14 percentage higher proportion of borrowers pay zero conditional on defaulting, an outcome analogous to selling their pawn (col 8).
+Conditional on defaulting those assigned to the Forced commitment contract have paid 4.1\% less of their loan (col 7), and 14 percentage higher proportion of borrowers pay zero conditional on defaulting, an outcome analogous to selling their pawn (col 8).
 One interpretation of these results is that the Forced commitment contract forces borrowers to think earlier about whether they will indeed be able to eventually recover their pawn, and separates borrowers into those ``selling'' their pawn and those recovering it, reducing the share of undecided borrowers that end up paying interest and end up losing the pawn anyway.
-This mechanism may also help to explain why the Forced commitment contract does not increase the number of visits to the branch to pay (col 10): those recovering their pawn visit more, but those defaulting have 0.19 fewer visits (col 11).
+This mechanism may also help to explain why the Forced commitment contract does not increase the number of visits to the branch to pay (col 10): those recovering their pawn visit more, but those defaulting have 0.20 fewer visits (col 11).
 Figure \ref{hist_payments} plots the histogram of the timing of payments in each arm, and shows that the commitment does appear to bind in that it generates a highly regular pattern of payments at 30, 60, and 90 days after the loan is taken.
@@
 Table \ref{repeat_loans} explores the effects of treatment on future pawning behavior.
-Column (1) shows that participants assigned to the the forced arm are 6.7\% more likely to be repeat clients later.
+Column (1) shows that participants assigned to the the forced arm are 6.3\% more likely to be repeat clients later.
 %Those in the choice arm are 4\% more likely to pawn again and is not statistically distinct from zero.
@@
 Column 4 only considers new loans which use different collateral from that of the initial one.
-We do this to foreclose the explanation that those in the Forced arm repeat more because they are more likely to have collateral, as they recover the collateral of the first loan more often.
-Column 5 focuses on the (endogenous) subsample of those recovering their pawn in both arms of the experiment.
+We do this to foreclose the explanation that those in the Forced arm \textcolor{teal}{, being more liquidity-constraint, return to pawn to be able to pay their first loan.
+Since they appear to not return with a different collateral we can rule out this explanation.
+Moreover, in the endogenous subsample of those that recover, we do find that they do return with a different collateral, as they recover the collateral of the first loan more often.}  Column 5 focuses on the (endogenous) subsample of those recovering their pawn in both arms of the experiment.
 This means that both have the pawn to re-pawn and also that the liquidity demands from the monthly contract are not longer binding as the contract has been closed.
@@
 This is a best guess of the outcome on censored loans.
-Using this prediction, we replicate the main experimental results and find that the treatment effect on financial cost increases from -378 (main results) to -525 (censored loans predicted), and the APR from -34\% to -62\%.
+Using this prediction, we replicate the main experimental results and find that the treatment effect on financial cost increases from -204 (main results) to -264 (censored loans predicted), and the APR from -11\% to -17\%.
 Hence, while the censoring issue does have a substantial influence on the magnitude of our estimated treatment effects, these  checks confirm that a) the core results are robust to censoring, and b) the headline approach that we take to the issue is conservative and is likely understating the true magnitude of impacts.
@@
 
-Our assumption-free bounds from the preceding section show that more than 24\% of borrowers would benefit from a policy of forced commitment. 
+Our assumption-free bounds from the preceding section show that more than 23\% of borrowers would benefit from a policy of forced commitment. 
 Intuitively, this seems to suggest that some of the 89\% of borrowers in the choice arm who did \emph{not} choose commitment would have faced lower borrowing costs if they had.
@@
 In other words: commitment is \emph{beneficial}, on average, to the people who \emph{would not choose it}, and these benefits are large.
-The estimated TOT effects are positive and larger still.
-Although we cannot quite reject the null hypothesis that the TUT and TOT effects are equal--our power is limited because of the low take-up rate of commitment in the choice arm--the pattern of coefficients is consistent with some degree of selection-on-gains.
-Commitment is more beneficial to people who are willing to choose it than it is to people who are not.
-For the APR benefit and (1 - Default) outcomes, we have sufficient precision to conclude that the average selection bias (ASB) is large and \emph{negative}.
-This means that borrowers who choose commitment would have faced a \emph{higher} APR and probability of default under the status quo contract than borrowers who do not choose commitment. 
-Overall, Table \ref{tot_tut} suggests that commitment works and the ``right people'' choose to commit: those who are most likely to benefit from it and those whose outcomes are most adverse under the status quo.
-At the same time, \emph{not enough} people choose to commit: the commitment contract is beneficial on average even to those who would \emph{not} choose it voluntarily.
+Due to the low take-up rate of commitment in the choice arm, the corresponding TOT effects are imprecisely estimated. Only one of them, \%(1-Default) from column (3), is statistically significant. 
+This imprecision carries over into our estimates of the average selection on gains, TOT-TUT.
+Our point estimates are \emph{negative} for all but the (1 - Default) outcome, but none is statistically distinguishable from zero.
+%Although we cannot quite reject the null hypothesis that the TUT and TOT effects are equal--our power is limited because of the low take-up rate of commitment in the choice arm--the pattern of coefficients is consistent with some degree of selection-on-gains.
+%Commitment is more beneficial to people who are willing to choose it than it is to people who are not.
+For the (1 - Default) outcome, we have sufficient precision to conclude that the average selection bias (ASB) is large and \emph{negative}.
+This means that borrowers who choose commitment would have faced a \emph{higher} probability of default under the status quo contract than borrowers who do not choose commitment. 
+Overall, Table \ref{tot_tut} suggests that commitment works but that \emph{not enough} people choose to commit: the commitment contract is beneficial on average even to those who would \emph{not} choose it voluntarily.
 Below we explore possible explanations for this result.
+%and the ``right people'' choose to commit: those who are most likely to benefit from it and those whose outcomes are most adverse under the status quo.
 
@@
 A discussion of compulsory commitment is necessarily paternalistic, and by its nature focuses on impacts among those who would not have selected commitment voluntarily.
-Viewed through the lens of rational choice theory, it is unsurprising that we estimate $\text{TOT}>\text{TUT}$.
-The argument for compulsory treatment, however, centers on the more surprising result that $\text{TUT}>0$.
-We now investigate several potential explanations for this result.
+%Viewed through the lens of rational choice theory, it is unsurprising that we estimate $\text{TOT}>\text{TUT}$. 
+The argument for compulsory treatment, centers on the surprising result that $\text{TUT}>0$. We now investigate several potential explanations for this result.
 For simplicity, we focus on causal effects for the APR outcome throughout this section.
 
-We conduct an exploratory analysis that examines four potential explanations for the positive $\text{TOT}$:  the need to learn, time discounting, present bias, and overconfidence.
+We conduct an exploratory analysis that examines four potential explanations for the positive $\text{TUT}$:  the need to learn, time discounting, present bias, and overconfidence.
 To explore the last two dimensions we will use survey data for which our response rate was 78\%.
@@
 Given the strongly positive impact of forcing, this explanation would suggest that clients who were forced once would subsequently choose commitment if given the chance to do so.
-A subset of 16\% clients from our sample returned to pawn again on another day before the end of the experiment.
+A subset of 22\% clients from our sample returned to pawn again on another day before the end of the experiment.
 Whereas all of the analyses from above restrict attention to the first day on which a given individual pawned, Table \ref{learning_table} presents information about participants' \emph{immediate subsequent} pawning behavior.\footnote{In other words, for borrowers who returned to pawn again more than once, this analysis considers only their first repeat pawn.} Column (1) considers the 228 clients who returned (only a second time) to pawn again at a day/branch that was randomly assigned to the choice arm.
@@
 Granted, this is a selected sample because the decision to pawn again is potentially endogenous to the initial treatment allocation.
-For this reason, Column (2) considers the full sample of 4436 borrowers by re-defining the outcome variable to be an indicator for returning to pawn again at a branch/day when commitment was offered \emph{and} choosing commitment.
+For this reason, Column (2) considers the full sample of 4441 borrowers by re-defining the outcome variable to be an indicator for returning to pawn again at a branch/day when commitment was offered \emph{and} choosing commitment.
 This composite outcome variable is not subject to the sample selection problem (although it is directly driven by the decision to repeat borrow).
@@
 The solid line gives the TUT effect adjusted for a specified annual discount rate, while the shaded regions gives the associated 95\% \& 90\% confidence interval.
-We see that non-choosers continue to experience significant decreases in NPV financial costs up to annual discount rates of 4,000\%, and the NPV remains positive, although not significant, at 10,000\% discount rates.
+We see that non-choosers continue to experience significant decreases in NPV financial costs up to annual discount rates of 5,000\%, and the NPV remains positive, although not significant, at 1,000\% discount rates.
 As such, discounting is unlikely to explain why those who benefit, on average, from commitment fail to choose it when offered.
@@
 
-\paragraph{Sure confidence.} While 72\% of survey respondents believe they have a 100\% chance of recovering their pawn, in reality only 48\% will go on to do so.  
+\paragraph{Sure confidence.} While 72\% of survey respondents believe they have a 100\% chance of recovering their pawn, in reality only 43\% will go on to do so.  
 This suggests a borrower pool characterized by over-optimism.
@@
 As above, the blue overall estimate must lie between the green and red sub-group estimates by the law of iterated expectations.
-In contrast to our results for present bias, shown in the left panel of Figure \ref{tut_beh_partition}, we estimate a higher TUT effect for sure-confident borrowers compared to all other borrowers and a negative, although insignificant, effect for borrowers who are not sure-confident.
+In contrast to our results for present bias, shown in the left panel of Figure \ref{tut_beh_partition}, we estimate a higher TUT effect for sure-confident borrowers compared to all other borrowers and a insignificant effect for borrowers who are not sure-confident.
 
@@
 The TUT density is particularly interesting for the question of paternalism since, as emphasized above, it presents conditional average effects for borrowers who would not voluntarily choose commitment.
-Only 13\% of our estimated conditional TUTs are negative, with a 95\% confidence interval of [11\%, 17\%].\footnote{The generalized random forest approach of \cite{atheygrf} produces conditional average effect estimators that are asymptotically normal, and includes methods for computing correct standard errors.
+Only 7\% of our estimated conditional TUTs are negative, with a 95\% confidence interval of [4\%, 9\%].\footnote{The generalized random forest approach of \cite{atheygrf} produces conditional average effect estimators that are asymptotically normal, and includes methods for computing correct standard errors.
 These methods are relatively straightforward because the trees are ``honest'' in that observations used to determine splits in the recursive partitioning algorithm are not used for causal effect estimation and vice-versa.
@@
 \]
-is approximately 0.13.
+is approximately 0.07.
 The share of non-choosers with a positive conditional \emph{average} treatment effects need not equal the share with a positive \emph{individual} effects, i.e.\ $\mathbbm{P}(Y_1 > Y_0| C = 0)$.
@@
 Of course conditional average effects need not equal individual treatment effects, and our APR outcome may not capture all of the costs and benefits that are relevant for individual borrowers' decisions.
-To account for this, we define a ``mistake'' for a non-chooser to be a conditional TUT estimate that significantly exceeds some large and positive APR threshold, e.g.\ 25\%. 
+To account for this, we define a ``mistake'' for a non-chooser to be a conditional TUT estimate that significantly exceeds some large and positive APR threshold, e.g.\ 10\%. 
 At any such threshold, we can calculate the percentage of non-choosers in the choice arm who made a ``mistake'' by not choosing commitment.   
@@
 The results in Figure \ref{choose_wrong} suggest that a large fraction of non-choosers made mistakes by not choosing commitment.
-Even at an APR threshold as large as 25\%, we estimate that more than half of them should have chosen commitment in order to lower financial costs.
+Even at an APR threshold as large as 10\%, we estimate that more than half of them should have chosen commitment in order to lower financial costs.
 In contrast, relatively few choosers appear to have made mistakes by choosing commitment.
@@
 For this reason, the relevant causal effect for this exercise is the conditional average treatment effect (ATE) rather than the conditional TUT or TOT as considered above.
-As shown in Figure \ref{fig:CATEsurvival}, an estimated 92\% of borrowers, with a 95\% confidence interval of [89\%, 94\%] have a positive conditional ATE as estimated from the causal forest from section \ref{sec:RF} above.
+As shown in Figure \ref{fig:CATEsurvival}, an estimated 90\% of borrowers, with a 95\% confidence interval of [87\%, 92\%] have a positive conditional ATE as estimated from the causal forest from section \ref{sec:RF} above.
 In the remainder of this section we ask how accurately it is possible to identify these borrowers.
@@
 For further detail see \cite{rforest_stata}.} Each of these methods yields an estimated probability of a positive CATE, allowing us to rank borrowers from highest to lowest probability.
-Since 92\% of borrowers have a positive CATE as estimated from the wide random forest model from above, we consider a decision rule that assigns a borrower to forced commitment if her estimated probability is in the top 92\% of the sample.
+Since 90\% of borrowers have a positive CATE as estimated from the wide random forest model from above, we consider a decision rule that assigns a borrower to forced commitment if her estimated probability is in the top 90\% of the sample.
 %The first of these is the narrow RF displayed above paired with the decision rule which assigns clients to forcing commitment if the estimated CATE from the narrow covariate set is positive. 
@@
 In spite of this, their performance is quite unimpressive relative to a policy of universal forced commitment.
-The fraction of the whole sample incorrectly targeted when moving from universal forced commitment to targeting based on the narrow RF falls only from 8.07\% to 5.49\%.
+The fraction of the whole sample incorrectly targeted when moving from universal forced commitment to targeting based on the narrow RF falls only from 9.78\% to 5.21\%.
 The logit targeting rule actually makes things marginally worse.
 Table \ref{hit_miss_rule} shows error rates for six possible assignment rules: assigning all borrowers to control, all to treatment (Forcing), the optimal (infeasible) assignment, narrow RF targeting, logit targeting, and we evaluate ex-post the voluntary choice.
-While the narrow RF correctly assigns roughly half of those who do not benefit from commitment to control, it also incorrectly allocates 3.7\% of the sample that would have gained from treatment to control.
+While the narrow RF correctly assigns roughly half of those who do not benefit from commitment to control, it also incorrectly allocates 4.38\% of the sample that would have gained from treatment to control.
 As such, it only improves the correct targeting rate by about a half of a percentage point on net relative to universal Forcing.
@@
 Self-targeting through choice proves to be little better than assigning everyone to the control condition, given the low take-up rate and the presence of both Type I and Type II errors in the choice arm.
-Fully 79\% of individuals in the Choice arm made a ``mistake'', weighting the error rates among choosers and non-choosers by their relative frequency in the Choice arm.
+Fully 87\% of individuals in the Choice arm made a ``mistake'', weighting the error rates among choosers and non-choosers by their relative frequency in the Choice arm.
 The takeaway is that given low take-up, the large fraction of the sample benefiting from commitment, and the weak predictive power of the narrow covariates, in this case universal paternalism appears to be an attractive contract.
@@
 Given that the rate of voluntary commitment in our sample is only 11\%, in order to achieve widespread benefits in this context compulsory commitment may be necessary.
-In the Forced arm the APR (inclusive of the cost of default) falls from 184\% to 150\%, and the fraction of borrowers defaulting on loans drops by 6.5 pp, or 15\%.
+In the Forced arm the APR (inclusive of the cost of default) falls from 57\% to 46\%, and the fraction of borrowers defaulting on loans drops by 6.6 pp, or 15\%.
 Clients appear to prefer the forced commitment after they have experienced it, in that assignment to this arm increases the fraction of individuals who return to pawn again.
@@
 Importantly, we find that not only are the benefits of commitment close to universal, but the determinants that might allow us to target it more finely are primarily behavioral and hence not easily predicted in an fast incentive-compatible manner by lenders.
-Even a sophisticated machine learning-based exercise is only able to decrease the fraction of borrowers mis-targeted by about 2.5 percentage points relative to simply assigning everyone to commitment (from 8\% to 5.5\%), and a logit-based targeting rule actually does slightly worse than universal commitment.
+Even a sophisticated machine learning-based exercise is only able to decrease the fraction of borrowers mis-targeted less than 1 percentage points relative to simply assigning everyone to commitment (from 9.78\% to 9.59\%), and a logit-based targeting rule actually does slightly worse than universal commitment.
 
@@
 Given the high prevalence of the use of this form of credit by low-income households, this has an obviously detrimental effect on the dynamics of asset accumulation among the poor.
-Given that the specific items being pawned (such crucifixes and family jewelry) may have sentimental, non-pecuniary meaning to households, the efficiency implications of these contract terms may be even larger (as evidenced by the fact that borrowers' subjective value of their own pawns was 26\% higher than the appraised collateral value).
+Given that the specific items being pawned (such crucifixes and family jewelry) may have sentimental, non-pecuniary meaning to households, the efficiency implications of these contract terms may be even larger (as evidenced by the fact that borrowers' subjective value of their own pawns was 31\% higher than the appraised collateral value).
 With a now well-established toolkit of regular small payments and incentives delivering vanishingly small default rates in microfinance, regulators in the banking sector may fruitfully investigate the possibility of requiring pawnbrokers to embed features of commitment and regularity into their repayment structures in more consistent ways.
@@
  \scriptsize Each row in this table 
- corresponds to a regression, where the level of observation is the individual loan originated.
+ corresponds to a regression.
 The dependent variables of these regressions are displayed in the first column.
@@
 The table reports the coefficients on each of these indicators, as well as the p-value an F-test of the null hypothesis of equality of the three coefficients.
-The dependent variables are: the number of pawns-loans originated per day per branch, a variable indicating whether a person who answered the baseline survey (before knowing contract terms) ended up pawning, and an indicator of whether the person that obtained the loan answered the baseline survey.
+The dependent variables are: the number of pawns-loans originated per day per branch, the number of borrowers per day-branch, a variable indicating whether a person who answered the baseline survey (before knowing contract terms) ended up pawning, and an indicator of whether the person that obtained the loan answered the baseline survey.
 By design we had the choice arm be larger.
+Figure \ref{boxplot_attrition}, in the appendix shows a box-plot of the first two variables, showing the distribution across arms is balanced.
 %\textit{Do file: } \texttt{ss\_att.do}
 \end{table}
+
+% \begin{table}[H]
+% \caption{Number of pawns balance before and after the experiment}
+% \label{num_pawns_bal}
+% \begin{center}
+% \scriptsize{\input{./Tables/num_pawns_bal.tex}}
+% \end{center}
+%  \scriptsize We test if the number of pawns per day for the 6 branches that participated in the experiment was different before the experiment started or after the experiment ended.
+To this end we estimated the following regression, and cluster the standard errors by branch:
+%  $$Pawns \: per \: day_{jt} = \alpha_j + \gamma f(t) + \beta_b \mathbbm{1}(t \in MB)_{t} +\beta_a \mathbbm{1}(t \in MA)_{t}$$
+%  , where $\alpha_j$ are branch fixed effects, $f(t)$ is a third degree polynomial in time, $\beta_b$ measures a level effect in the number of pawns per branch before the experiment started, and $\beta_a$ after.
+We estimate no difference in the number of pawns, showing that people are not leaving the branch without pawning at larger rates during the experiment.
+Moreover, in appendix Figure \ref{rd_pawns} we also test for differences before and after the experiment using a regression discontinuity type plot for the number of pawns, and find there are no differences.
+% %\textit{Do file: } \texttt{num_pawns_bal.do}
+% \end{table}
 
@@
 The first row allocates all borrowers to control.
-Taking the conditional ATE estimates from the ``wide'' causal forest, described in Section \ref{sec:RF} as ground truth, this results in 93\% of individuals losing by not receiving commitment.
+Taking the conditional ATE estimates from the ``wide'' causal forest, described in Section \ref{sec:RF} as ground truth, this results in 90\% of individuals losing by not receiving commitment.
 The second row assigns all borrowers to forced commitment, yielding error rates that are the exact mirror image of those from the first row.
@@
 In each of these rows, the assignment rule ranks borrowers from highest to lowest by their estimated probability of having a positive CATE.
-The 89\% of borrowers with the highest estimated probabilities are assigned to treatment, matching the overall rate of positive CATE estimates from the ``wide'' RF model.
+The 90\% of borrowers with the highest estimated probabilities are assigned to treatment, matching the overall rate of positive CATE estimates from the ``wide'' RF model.
 The sixth row gives the percentage of miss-classification that would follow from the observed choice.
@@
 The blue shaded regions are associated 95\% confidence intervals.
-We estimate that at least 91\% of borrowers have a positive conditional ATE.
+We estimate that at least 90\% of borrowers have a positive conditional ATE.
 %\textit{Do file: }  \texttt{cdf_CATE.do}
@@
 Each of the classification models produces an estimated probability of a positive CATE.
-For each, the assignment rule ranks borrowers by this estimated probability, and assigns the highest 92\% to forced commitment, to match the overall percentage of borrowers with positive estimated CATEs from the ``wide'' random forest model.
+For each, the assignment rule ranks borrowers by this estimated probability, and assigns the highest 90\% to forced commitment, to match the overall percentage of borrowers with positive estimated CATEs from the ``wide'' random forest model.
 Because this is an in-sample exercise, it overstates the actual performance of logit and RF-based targeting.

### 2023-11-22 OA.tex
Prepare draft for submission

@@
 	\Large{Appendix $-$ For Online Publication} \\[1em]
-	\large \author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira}
+	\large \author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira \and Francis J.\ DiTraglia}
 \end{center}
@@
 
-\section{ }
+\section{Treatment Explanation Materials and Pictures}
 \vspace{.2in}
 
-\vspace{.1in}
-\subsection{Internal Validity}
+\subsection{Materials}
+
+\begin{figure}[H]
+     \caption{Contract Terms Summary}
+    \label{PaperSlip}
+    \begin{center}
+    %\begin{subfigure}{0.65\textwidth}
+    %\caption{Receipt for client}
+     %   \centering
+        \includegraphics[width=0.65\textwidth]{Figuras/TicketLenderP.png}
+    %\end{subfigure}
+
+    %\vspace{3ex}
+    %\begin{subfigure}{0.65\textwidth}
+    %\caption{Personal promise signed by client}
+     %   \centering
+    %    \includegraphics[width=\textwidth]{Figuras/Personal Promise2.png}
+    %\end{subfigure}
+    \end{center}
+    \scriptsize
+        We show a sample receipt that was given to clients that got assigned to the fee-forcing contract (the font and format were changed to protect Lender's P identity).
+We want to highlight the salience of some items.
+First the title clearly indicated which contract the client has (arrow 1).
+Second, in the case of the fee contract it clearly indicates that there is a fee for paying late equivalent to 2\% of the value of the monthly payment (arrow 2).
+Third, there is a calendar for payments clearly specifying the dates and amounts to pay each month.
+%The bottom panel of the figure shows a ``promise slip'', the paper that those who were assigned (or chose) to the monthly payment with promise had to sign to make the promise salient.
+It emphasizes that the client is giving his word, and that the promise is not a legal document.
+\end{figure}
+
+\begin{figure}[H]
+     \caption{Explanatory Material}
+    \label{ExplanatoryMaterial}
+    \begin{center}
+    \begin{subfigure}{\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/micas.pdf}
+    \end{subfigure}
+    \end{center}
+    \scriptsize
+        This is a (translated) sample information slide shown to clients. The real ones were twice the size of this figure and were laminated. Different ones were shown for each treatment arm.
+\end{figure}
+
+\cleardoublepage
+
+\subsection{Pictures}
+
+\begin{figure}[H]
+     \caption{Some Pawnshops}
+    \label{PawnshopPicture}
+    \begin{center}
+    \begin{subfigure}{0.405\textwidth}
+    \caption{Appraiser/tellers inside a pawnshop}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/empenio9_.png}
+    \end{subfigure}
+        \begin{subfigure}{0.45\textwidth}
+    \caption{Pawnshop}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/empenio11_.png}
+    \end{subfigure}
+
+        \vspace{3ex}
+
+    \begin{subfigure}{0.45\textwidth}
+    \caption{Pawnshop}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/empenio2_.png}
+    \end{subfigure}
+    \begin{subfigure}{0.415\textwidth}
+    \caption{Lost pawns which are for sale}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/empenio3_.png}
+    \end{subfigure}
+    \end{center}
+    \scriptsize
+        This figure  shows pictures of pawnshops in Mexico city. They do not necessarily coincide with Lender P for confidentiality. 
+\end{figure}
+
+\vspace{.1in}
+\begin{figure}[H]
+     \caption{Gold buyers next to pawnshops}
+    \label{GoldBuyers}
+    \begin{center}
+    \begin{subfigure}{.49\textwidth}
+    \caption{Gold buyer next to pawnshop 1}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/empenio7_.png}
+    \end{subfigure}
+    \begin{subfigure}{.49\textwidth}
+    \caption{Gold buyer next to pawnshop 1}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/empenio8_.png}
+    \end{subfigure}
+       \vspace{3ex}
+
+    \end{center}
+    \scriptsize
+        This figure shows pictures of gold buyers next to pawnshops in Mexico city. They do not necessarily coincide with Lender P for confidentiality. 
+\end{figure}
+
+\begin{comment}
+\\
+\begin{table}[H]
+\caption{Number of pawns balance before and after the experiment}
+\label{num_pawns_bal}
+\begin{center}
+\scriptsize{\input{./Tables/num_pawns_bal.tex}}
+\end{center}
+ \scriptsize 
+%\textit{Do file: } \texttt{num\_pawns\_bal.do}
+\end{table}
+\end{comment}
+%\todo[inline]{removed}
+
+\newpage
+\subsection{Survey}   \label{app:survey_data}
+
+\vspace{.2in}
+
+\normalsize
+\linespread{1.25}
+%Really force it to normal size and linespread
+\normalsize
+\linespread{1.25}
+
+We now present analysis of the extent to which the survey-responding sample is representative and balanced.
+Table \ref{SS_cond_survet} presents information about survey non-response.
+Panel A is a balance table that compares loan amount and day of the week across treatment arms for the subset of borrowers who responded to at least one survey question.
+The p-values in the fourth column are for the F-test of no difference of means across treatment arms. 
+Panel B presents response-rates by question for each arm of the experiment, along with p-values for the F-test of no difference in question-specific response rates across treatment arms. 
+This panel uses data from participants who answered at least one survey question and went on to pawn on the same day as their survey response.
+From the table, we see that loan amount and weekday are balanced across treatment arms among survey respondents and that response rates are likewise stable across treatment arms.
+Table \ref{TUT_cond_survet} shows how the estimated TUT effect changes if we restrict our estimation sample based on survey response.
+The first row of the table presents TUT results for the financial cost outcome, while the second presents corresponding results for the APR outcome.
+In each row, column (1) presents the full-sample TUT estimate and standard error while the remaining columns restrict the sample to borrowers who answered a particular survey question or set of questions.
+For example, column (4) presents results for borrowers who answered the two questions needed to compute our measure of ``present bias'' discussed in the next paragraph, while column (9) present results restricted to participants who disclosed their sex.
+As seen from the table, our TUT estimates are quite stable across sub-samples defined by survey response.
+In each case they are positive and of the same magnitude as the corresponding full-sample estimate, although statistical significance varies depending on the size of the corresponding sub-sample. 
+For these reasons, we are comfortable relying on data for survey respondents in the empirical exercises that follow.
+In exercises that rely on a single survey question, we use data for every borrower who answered that question.
+In the random forest exercises described below, we use data for every borrower who answered at least one survey question.
+
+\cleardoublepage
+
+\begin{table}[H]
+\caption{Baseline survey questions (translated to English)}
+\label{baseline_survey}
+\begin{center}
+\scriptsize{\input{./Tables/transcribed.tex}}
+\end{center}
+\scriptsize
+Translation of the baseline questionnaire.
+\end{table}
+
+\cleardoublepage
+
+\newpage
+\subsection{Descriptives consistent with overconfidence}
+
+\vspace{.2in}
+\begin{figure}[H]
+    \caption{Behavior of borrowers who lost their pawn}
+    \label{proxy_naive}
+    \begin{center}
+    \begin{subfigure}{0.40\textwidth}
+        \caption{Elapsed days to first payment}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_firstdays_default.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.40\textwidth}
+        \caption{Elapsed days to last payment}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_days_default.pdf}
+    \end{subfigure}
+        \begin{subfigure}{0.40\textwidth}
+        \caption{Payments as \% of loan}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_percpay_default.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.40\textwidth}
+        \caption{Number of payments}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_numpay_default.pdf}
+    \end{subfigure}
+    \end{center}
+        \scriptsize 
+        This figure provides more details on the behavior of clients who were assigned to the control group and did not recover their pawn.
+Panel (a) shows a histogram of days elapsed from the pawn to the first payment, while panel (b) displays a histogram of days elapsed until the last payment.
+Some borrowers make payments after day 105, the end of the grace period: if they pay all interest owed, they can ``restart'' the loan.
+This amounts to starting a new loan with the same conditions and same pawn.
+Panel (c) shows a histogram of the fraction of the loan paid, while panel (d) presents a barplot of the number of times that borrowers went to the branch to make payments.
+      %\textit{Do file: }  \texttt{hist\_den\_default.do}
+\end{figure}
+
+\vspace{.1in}
+\section{Internal Validity}
 
@@
 
-\subsection{Pictures}
-
-\begin{figure}[H]
-     \caption{Some Pawnshops}
-    \label{PawnshopPicture}
-    \begin{center}
-    \begin{subfigure}{0.405\textwidth}
-    \caption{Appraiser/tellers inside a pawnshop}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/empenio9_.png}
-    \end{subfigure}
-        \begin{subfigure}{0.45\textwidth}
-    \caption{Pawnshop}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/empenio11_.png}
-    \end{subfigure}
-
-        \vspace{3ex}
-
-    \begin{subfigure}{0.45\textwidth}
-    \caption{Pawnshop}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/empenio2_.png}
-    \end{subfigure}
-    \begin{subfigure}{0.415\textwidth}
-    \caption{Lost pawns which are for sale}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/empenio3_.png}
-    \end{subfigure}
-    \end{center}
-    \scriptsize
-        This figure  shows pictures of pawnshops in Mexico city. They do not necessarily coincide with Lender P for confidentiality. 
-\end{figure}
-
-\vspace{.1in}
-\begin{figure}[H]
-     \caption{Gold buyers next to pawnshops}
-    \label{GoldBuyers}
-    \begin{center}
-    \begin{subfigure}{.49\textwidth}
-    \caption{Gold buyer next to pawnshop 1}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/empenio7_.png}
-    \end{subfigure}
-    \begin{subfigure}{.49\textwidth}
-    \caption{Gold buyer next to pawnshop 1}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/empenio8_.png}
-    \end{subfigure}
-       \vspace{3ex}
-
-    \end{center}
-    \scriptsize
-        This figure shows pictures of gold buyers next to pawnshops in Mexico city. They do not necessarily coincide with Lender P for confidentiality. 
-\end{figure}
-
-\begin{comment}
-
-\begin{table}[H]
-\caption{Number of pawns balance before and after the experiment}
-\label{num_pawns_bal}
-\begin{center}
-\scriptsize{\input{./Tables/num_pawns_bal.tex}}
-\end{center}
- \scriptsize 
-%\textit{Do file: } \texttt{num\_pawns\_bal.do}
-\end{table}
-\end{comment}
-%\todo[inline]{removed}
-
-\newpage
-\subsection{Survey}   \label{app:survey_data}
-
-\vspace{.2in}
-
-\normalsize
-\linespread{1.25}
-%Really force it to normal size and linespread
-\normalsize
-\linespread{1.25}
-
-We now present analysis of the extent to which the survey-responding sample is representative and balanced.
-Table \ref{SS_cond_survet} presents information about survey non-response.
-Panel A is a balance table that compares loan amount and day of the week across treatment arms for the subset of borrowers who responded to at least one survey question.
-The p-values in the fourth column are for the F-test of no difference of means across treatment arms. 
-Panel B presents response-rates by question for each arm of the experiment, along with p-values for the F-test of no difference in question-specific response rates across treatment arms. 
-This panel uses data from participants who answered at least one survey question and went on to pawn on the same day as their survey response.
-From the table, we see that loan amount and weekday are balanced across treatment arms among survey respondents and that response rates are likewise stable across treatment arms.
-Table \ref{TUT_cond_survet} shows how the estimated TUT effect changes if we restrict our estimation sample based on survey response.
-The first row of the table presents TUT results for the financial cost outcome, while the second presents corresponding results for the APR outcome.
-In each row, column (1) presents the full-sample TUT estimate and standard error while the remaining columns restrict the sample to borrowers who answered a particular survey question or set of questions.
-For example, column (4) presents results for borrowers who answered the two questions needed to compute our measure of ``present bias'' discussed in the next paragraph, while column (9) present results restricted to participants who disclosed their sex.
-As seen from the table, our TUT estimates are quite stable across sub-samples defined by survey response.
-In each case they are positive and of the same magnitude as the corresponding full-sample estimate, although statistical significance varies depending on the size of the corresponding sub-sample. 
-For these reasons, we are comfortable relying on data for survey respondents in the empirical exercises that follow.
-In exercises that rely on a single survey question, we use data for every borrower who answered that question.
-In the random forest exercises described below, we use data for every borrower who answered at least one survey question.
-
-\cleardoublepage
-
-\begin{table}[H]
-\caption{Baseline survey questions (translated to English)}
-\label{baseline_survey}
-\begin{center}
-\scriptsize{\input{./Tables/transcribed.tex}}
-\end{center}
-\scriptsize
-Translation of the baseline questionnaire.
-\end{table}
-
-\cleardoublepage
-
 \begin{table}[H]
@@
 \end{landscape}
-
-\newpage
-\subsection{Some more evidence of overconfidence}
-
-\vspace{.2in}
-\begin{figure}[H]
-    \caption{Behavior of borrowers who lost their pawn}
-    \label{proxy_naive}
-    \begin{center}
-    \begin{subfigure}{0.40\textwidth}
-        \caption{Elapsed days to first payment}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_firstdays_default.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.40\textwidth}
-        \caption{Elapsed days to last payment}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_days_default.pdf}
-    \end{subfigure}
-        \begin{subfigure}{0.40\textwidth}
-        \caption{Payments as \% of loan}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_percpay_default.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.40\textwidth}
-        \caption{Number of payments}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_numpay_default.pdf}
-    \end{subfigure}
-    \end{center}
-        \scriptsize 
-        This figure provides more details on the behavior of clients who were assigned to the control group and did not recover their pawn.
-Panel (a) shows a histogram of days elapsed from the pawn to the first payment, while panel (b) displays a histogram of days elapsed until the last payment.
-Some borrowers make payments after day 105, the end of the grace period: if they pay all interest owed, they can ``restart'' the loan.
-This amounts to starting a new loan with the same conditions and same pawn.
-Panel (c) shows a histogram of the fraction of the loan paid, while panel (d) presents a barplot of the number of times that borrowers went to the branch to make payments.
-      %\textit{Do file: }  \texttt{hist\_den\_default.do}
-\end{figure}
 
@@
     \end{center}
-     \scriptsize  This Figure shows the accumulated percentage of recovery in time by treatment arm. 
+     \scriptsize  This Figure shows the CDF of loan completion either default or recovery in Panel (a), or loan recovery in Panel (b), by the number of days since first pawn.
      %\textit{Do file: }  \texttt{survival\_graph.do}
@@
 \subsection{Learning}
+\normalsize
+Table \ref{learning_table} presents information about borrowers' \emph{future} pawning behavior as a function of treatment assignment.
+Column (1) considers the 228 clients who returned only a second time to pawn again at a day/branch that was randomly assigned to the choice arm.
+Each of the two rows in this column presents a difference of mean commitment take-up rates, and associated standard error.
+The first row compares those who were \emph{initially} assigned to forced commitment against those where were assigned to control; the second row compares those who were initially assigned to the choice commitment arm to those who were assigned to the other two arms.
+In each case, there is no statistically discernible difference in the rates of commitment take-up.
+Granted, this is a selected sample because the decision to pawn again is potentially endogenous to the initial treatment allocation.
+For this reason, Column (2) considers the full sample of 4441 borrowers by re-defining the outcome variable to be an indicator for returning to pawn again at a branch/day when commitment was offered \emph{and} choosing commitment.
+This composite outcome variable is not subject to the sample selection problem (although it is directly driven by the decision to repeat borrow).
+The comparison in the two rows remains the same: forced commitment versus control in row one and choice commitment versus forced arms in row two.
+Again, there is no statistically discernible difference in commitment take-up rates in either row.
+While these exercises cannot completely exclude the possibility that learning plays a role, they provide no indication that the lack of voluntary compliance is simply a matter of inexperience with commitment.
 
@@
 
-This table presents information about borrowers' \emph{future} pawning behavior.
 Column (1) reports results for the 228 borrowers who returned to pawn again at a day/branch that was randomly assigned to the choice arm, enabling us to observe whether they chose commitment or the status quo contract.
@@
 %\textit{Do file: }  \texttt{discounted\_noeffect.do}
-\end{figure}
-
-\vspace{.3in}
-\subsection{First order stochastic dominance} \label{App_FOSD}
-\normalsize
-\vspace{.2in}
-
-%\todo[inline]{Presumably we want to cut some of this text? In the body of the text we don't get into this in such detail.}
-%We plot the empirical distribution of financing cost $F_{commitment}(FC)$ and of the status quo contract, $F_{sq}(FC)$. Framed as a choice among cost distributions.
-
-\vspace{.2in}
-\begin{figure}[H]
-        \caption{Empirical CDF of Financial Cost: Forced commitment vs Control}
-    \label{ecdf_fc}
-
-    \begin{center}
-       \begin{subfigure}{0.49\textwidth}
-        \caption{APR benefit}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/cdf_apr.pdf}
-    \end{subfigure} 
-   \begin{subfigure}{0.49\textwidth}
-        \caption{Financial benefit}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/cdf_fc_admin.pdf}
-    \end{subfigure} 
-    \end{center}
-    \scriptsize This figure plots plots the empirical CDF of experimental outcomes separately for the control / status quo (dashed) and forced commitment contracts (solid).
-In panel (a), the outcome is APR benefit; in panel (b) the outcome is Financial benefit.
-In each case, the empirical CDF under forced commitment first-order stochastically dominates the empirical CDF under the status quo.
-This can be seen by examining the dotted line at the bottom of panels (a) and (b), which shows the difference $(\text{Control} - \text{Commitment})$.
-    %The dotted line at the bottom of panels (a) and (b)   the empirical cumulative distribution function APR and financial cost of financial cost.
-It does this separately for the fee-forcing contract and for the status-quo contract.
-The dotted line at the bottom is the difference of the control CDF minus the forced CDF arm.
-It shows that the CDF of the status quo contract is always below that of the fee-forcing (and this difference is significant for the points indicated by the blue line).
-    % \texttt{fosd_ecdf.do}}
-\end{figure}
-
-\cleardoublepage
-
-\begin{figure}[H]
-        \caption{Distribution of treatment effects under rank invariance.}
-    \label{te_rankinvariance}
-
-    \begin{center}
-       \begin{subfigure}{0.49\textwidth}
-        \caption{APR benefit}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/te_rankinvariance_apr.pdf}
-    \end{subfigure} 
-   \begin{subfigure}{0.49\textwidth}
-        \caption{Financial benefit}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/te_rankinvariance_fc_admin.pdf}
-    \end{subfigure} 
-    \end{center}
-    \scriptsize This figure show the distribution of treatment effects under rank invariance
-    \[F_\Delta(\delta) = \int_0^1 \mathbbm{1}\{ F_1^{-1}(u) - F_0^{-1}(u)\leq \delta\}\,\mathrm{d}u\]
-where $F_1^{-1}$ and $F_0^{-1}$ are the quantile functions of $Y_1$ and $Y_0$.
-    %The dotted line at the bottom of panels (a) and (b)   the empirical cumulative distribution function APR and financial cost of financial cost.
-It does this separately for the fee-forcing contract and for the status-quo contract.
-The dotted line at the bottom is the difference of the control CDF minus the forced CDF arm.
-It shows that the CDF of the status quo contract is always below that of the fee-forcing (and this difference is significant for the points indicated by the blue line).
-    % \texttt{te_rankinvariance.do}}
 \end{figure}
@@
 
-\section{Testing for heterogeneity}
+\section{Heterogeneity and Bounds}
+
+\subsection{Testing for heterogeneity}
 \label{append:chernozhukov}
@@
 Since $\tau_i$ and $\psi_i$ do not depend on the test set, inference for the regression in \eqref{eq:chernreg} is straightforward conditional on the Training/Test split.  
-Our estimate for $\beta_2$ is 2.56 with a one-sided heteroskedasticity-robust (HC3) of 0.43.
+Our estimate for $\beta_2$ is 2.56 with a one-sided heteroskedasticity-robust (HC3) standard error of 0.43.
 Thus we easily reject the null hypothesis of homogeneous treatment effects.
@@
 (Tuning parameters choice, etc.) We should put them into the appendix.}
+
+\subsection{Bounds, FOSD and Rank Invariance} \label{bounds_FOSD}
+
+\vspace{.3in}
+\begin{figure}[H]
+    \caption{Fan \& Park bounds for benefit in APR\%}
+    \label{fan_park_bounds}
+    \begin{center}
+    \begin{subfigure}{0.75\textwidth}
+        \caption{APR}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/fan_park_bounds_apr.pdf}
+    \end{subfigure}
+    \end{center}
+        \scriptsize
+    This figure depicts the \cite{fan2010sharp} bounds on the distribution $F_\Delta$ of individual treatment effects $\Delta \equiv (Y_1 - Y_0)$, described in Section \ref{sec:bounds}, for the APR outcome.
+    The dark red curve and light red shaded region give the estimated upper bound function $\overline{F}$ for $F_\Delta$ and associated (pointwise) 95\% confidence interval. 
+    The dark blue curve and light blue shaded region give the estimated lower bound function $\underline{F}$ for $F_\Delta$ and associated (pointwise) 95\% confidence interval.
+    Confidence intervals are computed using the asymptotic distribution for the bounds. See \cite{fan2010sharp} for details.
+    The bounds are pointwise sharp: at any specified value of $\delta$ the bounds $\underline{F}(\delta) \leq F_\Delta(\delta) \leq \overline{F}(\delta)$ cannot be improved without imposing additional assumptions.
+    Evaluating the bounds at $\delta = 0$, we see that between 23\% and 97\% of borrowers have a positive individual treatment effect.
+    This is greater than the share of borrowers who chose commitment: 11\%.
+%\textit{Do file: } \texttt{fan\_park\_bnds.do}       
+\end{figure}
+
+\vspace{.2in}
+\begin{figure}[H]
+        \caption{Empirical CDF: Forced commitment vs Control FOSF}
+    \label{ecdf_fc}
+
+    \begin{center}
+        \begin{subfigure}{0.49\textwidth}
+         \caption{APR benefit}
+         \centering
+         \includegraphics[width=\textwidth]{Figuras/cdf_apr.pdf}
+     \end{subfigure} 
+   \begin{subfigure}{0.49\textwidth}
+        \caption{Financial benefit}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/cdf_fc_admin.pdf}
+    \end{subfigure} 
+    \end{center}
+    \scriptsize This figure plots the empirical CDF of experimental outcomes separately for the control (status quo) in dashes, and forced commitment contracts (solid).
+In panel (a), the outcome is APR benefit; in panel (b) the outcome is Financial benefit.
+    The empirical CDF under forced commitment first-order stochastically dominates the empirical CDF under the status quo.
+This can be seen by examining the dotted line, which shows the difference $(\text{Control} - \text{Commitment})$.
+    %The dotted line at the bottom of panels (a) and (b)   the empirical cumulative distribution function APR and financial cost of financial cost.
+It does this separately for the fee-forcing contract and for the status-quo contract.
+The dotted line at the bottom is the difference of the control CDF minus the forced CDF arm.
+It shows that the CDF of the status quo contract is always below that of the fee-forcing (and this difference is significant for the points indicated by the blue line).
+    % \texttt{fosd_ecdf.do}}
+\end{figure}
+
+\vspace{.2in}
+\begin{figure}[H]
+        \caption{Distribution of treatment effects under rank invariance.}
+    \label{te_rankinvariance}
+
+    \begin{center}
+       \begin{subfigure}{0.49\textwidth}
+        \caption{APR benefit}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/te_rankinvariance_apr.pdf}
+    \end{subfigure} 
+   \begin{subfigure}{0.49\textwidth}
+        \caption{Financial benefit}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/te_rankinvariance_fc_admin.pdf}
+    \end{subfigure} 
+    \end{center}
+    \scriptsize This figure shows the CDF of individual treatment effects under the assumption of rank invariance, computed from 
+    \[F_\Delta(\delta) = \int_0^1 \mathbbm{1}\{ F_1^{-1}(u) - F_0^{-1}(u)\leq \delta\}\,\mathrm{d}u\]
+where $F_1^{-1}$ and $F_0^{-1}$ are the quantile functions of $Y_1$ and $Y_0$.
+    %The dotted line at the bottom of panels (a) and (b)   the empirical cumulative distribution function APR and financial cost of financial cost.
+It does this separately for the fee-forcing contract and for the status-quo contract.
+The dotted line at the bottom is the difference of the control CDF minus the forced CDF arm.
+It shows that the CDF of the status quo contract is always below that of the fee-forcing (and this difference is significant for the points indicated by the blue line).
+    % \texttt{te_rankinvariance.do}}
+\end{figure}
 
@@
 For this reason we consider each in turn.
-Our approach is closely related arguments from \cite{huber_mellace} and \cite{BinaryRegressor}, among others.
+Our approach is closely related to arguments from \cite{huber_mellace} and \cite{BinaryRegressor}, among others.
 As such, the following is a heuristic explanation rather than a fully-rigorous proof.
@@
 Consider the two most extreme possibilities: they could occupy the bottom $(1-p)\times 100\%$ of the distribution or the top $(1-p)\times 100\%$ of the distribution.
-For this reason, computing the average of the the \emph{truncated} distribution of $Y|Z=0$, cutting out the top $p\times 100\%$, provides a lower bound for the average of $Y_0$ among non-choosers.
+For this reason, computing the average of the \emph{truncated} distribution of $Y|Z=0$, cutting out the top $p\times 100\%$, provides a lower bound for the average of $Y_0$ among non-choosers.
 Similarly, cutting out the bottom $p \times 100\%$ provides an upper bound.
@@
 \[
-\mathbb{E}\left(Y|Z=0, Y\leq y^0_{1-p}\right)\leq \mathbb{E}(Y_0|C=0) \leq \mathbb{E}\left(Y|Z=0, Y \leq y^0_p\right) 
+\mathbb{E}\left(Y|Z=0, Y\leq y^0_{1-p}\right)\leq \mathbb{E}(Y_0|C=0) \leq \mathbb{E}\left(Y|Z=0, Y \geq y^0_p\right) 
 \]
@@
 \begin{equation}
-\mathbb{E}\left(Y|Z=0, Y\leq y^0_{1-p}\right)\leq \mathbb{E}(Y|D=0,Z=2) \leq \mathbb{E}\left(Y|Z=0, Y \leq y^0_p\right).
+\mathbb{E}\left(Y|Z=0, Y\leq y^0_{1-p}\right)\leq \mathbb{E}(Y|D=0,Z=2) \leq \mathbb{E}\left(Y|Z=0, Y \geq y^0_p\right).
 \label{eq:testable0}
@@
 If either inequality is violated, then the exclusion restriction for non-choosers fails.
+In our experiment, $\widehat{p} = \widehat{\mathbbm{P}}(D=1|Z=2) = 0.11$. For the APR outcome we estimate
+\[
+\widehat{\mathbbm{E}}(Y_\text{APR}|Z=0,Y_\text{APR}\leq y^0_{0.89}) = 0.48, \quad
+\widehat{\mathbbm{E}}(Y_\text{APR}|Z=0, Y_\text{APR}\geq y^0_{0.11}) = 0.62.
+\]
+Since $\widehat{\mathbbm{E}}(Y_\text{APR}|D=0,Z=2) = 0.58$ falls between these bounds, we find no evidence against the exclusion restriction for non-choosers. 
+Repeating this exercise for the financial cost outcome, we see that $\widehat{\mathbbm{E}}(Y_\text{FC}|D=0,Z=2) = 973$ likewise falls between 
+\[
+\widehat{\mathbbm{E}}(Y_\text{FC}|Z=0,Y_\text{FC}\leq y^0_{0.89}) = 626, \quad
+\widehat{\mathbbm{E}}(Y_\text{FC}|Z=0, Y_\text{FC}\geq y^0_{0.11}) = 1046 
+\]
+so we again find no evidence against the exclusion restriction for non-choosers.
 
@@
 If either inequality is violated, then the exclusion restriction from Equation \ref{eq:exclusion_append1} fails.
-
-The \cite{huber_mellace} bounds for the TOT \& TUT APR are respectively:  $[-119, 123]$, and $[-4.2, 24.8]$.
-Since both TUT (24) and ToT (122) estimates from the LATE approach lies inside these bounds, we cannot falsify the exclusion restriction.
-Moreover, the p-values associated with testing violation of inequalities \ref{eq:testable0}, and \ref{eq:testable1} is equal to one in both cases\footnote{We include the implementation of the validity test for the exclusion restriction for choosers and non-choosers in our STATA package.}.
+Again, in our experiment $\widehat{p}=0.11$. For the APR outcome we estimate
+\[
+\widehat{\mathbbm{E}}(Y|Z=1,Y\leq y^1_{0.11}) = 0.06, \quad
+\widehat{\mathbbm{E}}(Y|Z=1,Y\geq y^1_{0.89}) = 1.28
+\]
+Since $\widehat{\mathbbm{E}}(Y_\text{APR}|D=1,Z=2) = 0.43$ falls between these bounds, we find no evidence against the exclusion restriction for the choosers. 
+Repeating this exercise for the financial cost outcome, we see  that $\widehat{\mathbbm{E}}(Y_\text{FC}|D=1,Z=2)= 570$ likewise falls between
+\[
+\widehat{\mathbbm{E}}(Y|Z=1,Y\leq y^1_{0.11}) = 53, \quad
+\widehat{\mathbbm{E}}(Y|Z=1,Y\geq y^1_{0.89}) = 2934
+\]
+so we again find no evidence against the exclusion restriction for the choosers.
+
+The aforementioned bounds for $\mathbbm{E}(Y_0|C=0)$ and $\mathbbm{E}(Y_1|C=1)$ can alternatively be used construct partial identification bounds for the TOT and TUT effects that do not rely on our exclusion restrictions.
+If the TOT or TUT expression from \ref{append:randchoice} fall \emph{outside} the partial identification bounds, this is equivalent to finding a violation of \ref{eq:testable0} or \ref{eq:testable1}.
+We implement these bounds for the TOT and TUT in our companion STATA package.
 
@@
 
-%\section{LATE: TOT \& TUT}
-%\vspace{.2in}
-%\normalsize
-%\linespread{1.25}
-%%Really force it to normal size and linespread
-%\normalsize
-%\linespread{1.25}
-%
-% Recall that $Z_i$ is the observed, randomly assigned experimental allocation, where $Z_i=0$ denotes the control arm, $Z_i=1$ denotes the forced-fee arm, and $Z_i=2$ is the choice arm.
-Let $C_i$ be the unobserved choice type.
-$C_i=0$ when individual $i$ does not choose commitment  given the choice and $C_i=1$ when chooses commitment given the choice.
-Finally, $D_i = Z_i\times \mathds{1}(Z_i\neq 2) + C_i\times \mathds{1}(Z_i=2)$ is the observed treatment indicator, and $Y(d,z)$ is the potential outcome function for $d=0,1$, and $z=0,1,2$.
-%
-% To identify assortative selection we first need to estimate the following quantities: $\mathbb{E}(Y_1-Y_0\;|\;C=1)$ the Treatment on the Treated (TOT), and $\mathbb{E}(Y_1-Y_0\;|\;C=0)$ the Treatment on the Untreated (TUT).
-%
-% To point identify the above quantities, we make the following assumptions.
-%
-% \begin{assumption}[Exclusion Restriction]
-%$Z$ only affects $Y$ through its effect on $D$ : $C(d,z) = C(d)$
-% \end{assumption}
-%
-%  \begin{assumption}[Independence Assumption]
-%$Z \perp (Y_0, Y_1, C)$
-% \end{assumption}
-%
-%The following intermediate Lemmas will help us derive that both TOT and TUT are point identified.
-%
-%\begin{lem}
-%$\Pr(C=1) = \E[D\;|\;Z=2]$
-%\end{lem}
-%\begin{proof}
-%Since $C\perp Z$, 
-%$$\E[D\;|\;Z=2] = \E[Z\times \mathds{1}(Z\neq 2)+ C\times\mathds{1}(Z=2)\;|Z=2] = \E[C\;|\;Z=2] = \E[C] = \Pr(C=1)$$
-%\end{proof}
-%
-%
-%\begin{lem}
-%$\E[Y_0] = \E[Y\;|\;Z=0]$
-%\end{lem}
-%\begin{proof}
-%Since $Z\perp Y_0$, 
-%\begin{align*}
-%\E[Y\;|\;Z=0] =& \E[\mathds{1}(Z=0)Y_0+\mathds{1}(Z=1)Y_1+\mathds{1}(Z=2)\{(1-C)Y_0+CY_1\})\;|\;Z=0]\\   
-%=&\E[Y_0\;|\;Z=0] = \E[Y_0]
-%\end{align*}
-%\end{proof}
-%
-%
-%\begin{lem}
-%$\E[Y_1] = \E[Y\;|\;Z=1]$
-%\end{lem}
-%\begin{proof}
-%Since $Z\perp Y_1$, 
-%\begin{align*}
-%\E[Y\;|\;Z=1] =\E[Y_1\;|\;Z=1] = \E[Y_1]
-%\end{align*}
-%\end{proof}
-%
-%
-%\begin{lem}
-%$\E[Y_0\;|\;C=0] = \E[Y\;|\; D=0,Z=2]$
-%\end{lem}
-%\begin{proof}
-%If $Z=2$, then $D=0$ if and only if $C=0$. Hence,
-%\[\E[Y\;|\;D=0, Z=2] = \E[Y_0\;|\;D=0, Z=2] = E[Y_0\;|\;C=0, Z=2]=\E[Y_0\;|\;C=0]\]
-%since $Y_0\perp C\;|\;Z$
-%\end{proof}
-%
-%\begin{lem}
-%$\E[Y_1\;|\;C=1] = \E[Y\;|\; D=1,Z=2]$
-%\end{lem}
-%\begin{proof}
-%If $Z=2$, then $D=1$ if and only if $C=1$. Hence,
-%\[\E[Y\;|\;D=1, Z=2] = \E[Y_1\;|\;D=1, Z=2] = E[Y_1\;|\;C=1, Z=2]=\E[Y_1\;|\;C=1]\]
-%since $Y_1\perp C\;|\;Z$
-%\end{proof}
-%
-%\begin{theorem} $\E[Y_1-Y_0\;|\; C=1]$ is point identified
-%\end{theorem}
-%
-%\begin{proof}
-%Since $\E[Y_1\;|\; C=1] = \E[Y\;|\; D=1, Z=2]$ by Lemma 5, it suffices to show that $\E[Y_1\;|\;C=0]$ is point identified. By iterated expectations:
-%\[E[Y_0] = \E_C\E[Y_0\;|\;C] = (1-p)\E[Y_0\;|\;C=0]+p\E[Y_0\;|\;C=1]\]
-%where $p:=\E[C]=\Pr(C=1)$, and re-arranging,
-%\[\E[Y_0\;|\;C=1] = \frac{1}{p}\left(E[Y_0] -(1-p)\E[Y_0\;|\;C=0]\right)\]
-%Finally, substituting the result of Lemmas 1, 2, and 4, we obtain
-%\[\E[Y_0\;|\;C=1] =\frac{1}{\E[D\;|\;Z=2]}\left\{\E[Y\;|\;Z=0]-(1-\E[D\;|\;Z=2])\E[Y\;|\;D=0, Z=2]\right\}\]
-%and the RHS is a function of observed data only.
-%\end{proof}
-%
-%\begin{theorem} $\E[Y_1-Y_0\;|\; C=0]$ is point identified
-%\end{theorem}
-%
-%\begin{proof}
-%Since $\E[Y_0\;|\; C=0] = \E[Y\;|\; D=0, Z=2]$ by Lemma 4, it suffices to show that $\E[Y_0\;|\;C=1]$ is point identified. By iterated expectations:
-%\[E[Y_1] = \E_C\E[Y_1\;|\;C] = (1-p)\E[Y_1\;|\;C=0]+p\E[Y_1\;|\;C=1]\]
-%where $p:=\E[C]=\Pr(C=1)$, and re-arranging,
-%\[\E[Y_1\;|\;C=0] = \frac{1}{1-p}\left(E[Y_1] -p\E[Y_1\;|\;C=1]\right)\]
-%Finally, substituting the result of Lemmas 1, 3, and 5, we obtain
-%\[\E[Y_1\;|\;C=0] =\frac{1}{1-\E[D\;|\;Z=2]}\left\{\E[Y\;|\;Z=1]-\E[D\;|\;Z=2]\E[Y\;|\;D=1, Z=2]\right\}\]
-%and the RHS is a function of observed data only.
-%\end{proof}
-%
-%
-%\begin{figure}[H]
-%    \caption{Bootstrap inference for the difference between TOT-TUT}
-%    \label{bootstrap_tot_tut}
-%    \begin{center}
-%    \begin{subfigure}{0.31\textwidth}
-%        \caption{Simple}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/tot_tut_btsp1.pdf}
-%    \end{subfigure}
-%    \begin{subfigure}{0.31\textwidth}
-%        \caption{Admin controls}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/tot_tut_btsp2.pdf}
-%    \end{subfigure}
-%    \begin{subfigure}{0.31\textwidth}
-%        \caption{Admin + Survey controls}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/tot_tut_btsp3.pdf}
-%    \end{subfigure}
-%  
-%    \end{center}
-%     \scriptsize  Given that all of the arms are effectively randomly sampled form the same pool, we can also estimate the TOT and TUT with the pooled regression: $Y_i = \beta_0\mathds{1}(Z_i=0)+\beta_1\mathds{1}(Z_i=1)+\beta_2\mathds{1}(Z_i=2)+ \epsilon_i$, and then this test statistic just becomes the F-test on $\frac{\widehat{\beta_2}-\widehat{\beta_0}}{p}$ for the TOT, $\frac{\widehat{\beta_1}-\widehat{\beta_2}}{1-p}$ for the TUT, and an F-test on the difference between these two quantities to test whether the gains are different between compliers and non-compliers.
-Recognizing the stochastic nature of the compliance rate, we also bootstrap this quantity before running the previous regression.
-The red line shows the point estimate for the difference between TOT-TUT, and the gray bar in the x-axis shows a 95\% confidence interval for this difference.
-Panel (a) shows the difference between the TOT and TUT without any controls, while panel (b) and (c) adds admin controls and admin + survey controls respectively.
-%          %\footnotesize{ \textit{Do file: }  \texttt{tot\_tut.do}}
-%\end{figure}
-
-\begin{comment}
-
-\begin{figure}[H]
-     \caption{TOT-TUT CDF}
-     \label{tot_tut_ecdf}
-    \begin{center}
-    \begin{subfigure}{0.6\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/cdf_tot_tut.pdf}
-    \end{subfigure}
-    \end{center}
-    \scriptsize
-       Equipped with estimates for the TOT and TUT for each individual $i$ from an Instrumental Random Forest we compute the ECDF for this quantities.
-The solid line is the ECDF for the TOT, the dashed line is the ECDF for the TUT, and the dotted line plots the difference between the TOT and the TUT - the blue dashed line in the x-axis shows the points where this difference is significant.
-The bold black interval at the bottom of the graph is the mean for the TOT distribution (0.07), while the gray interval shows the mean for the TUT distribution (0.10).
-
-          %\footnotesize{ \textit{Do file: }  \texttt{tot\_tut\_insforest.do}}
-\end{figure}
-\end{comment}
-
-% \begin{figure}[H]
-%      \caption{Exclusion restriction}
-%      \label{exclusion_restriction}
-%     \begin{center}
-%     \begin{subfigure}{0.6\textwidth}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/exclusion_restriction.pdf}
-%     \end{subfigure}
-%     \end{center}
-%     \scriptsize This figure serves as a test for the exclusion restriction in the point identification for the TOT and the TUT.
-It shows the effect on the effective cost/loan ratio for the forced-fee arm and the choice arm, together with the decomposition of the choosers and non-choosers.
-Note that a) being forced into the treatment (Forced fee) has the same effect as choosing it (Choosers), and b) not choosing the treatment (Non chooser) has no effect with respect to the control.
-
-%           %\footnotesize{ \textit{Do file: }  \texttt{exclusion\_restriction.do}}
-% \end{figure}
-
-%---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
-
-\newpage 
-\newpage
 \section{Causal Random Forest, HTE, and `mistakes'}
@@
 
+\subsection{Example of a Causal Tree}
+
+\vspace{.3in}
 \begin{figure}[H]
@@
 \end{figure}
+
+\newpage
+\subsection{Conditional ATE estimates}
+
+\vspace{.3in}
+\begin{figure}[H]
+    \begin{center}
+  \caption{Cumulative Distribution Function of Conditional ATE Estimates}
+  \includegraphics[width=0.75\textwidth]{Figuras/cdf_CATE.pdf} 
+    \label{fig:CATEsurvival}
+    \end{center}
+
+    \scriptsize This figure shows the share of borrowers who benefit from forced commitment, where ``benefit'' is defined as having an estimated conditional average treatment effect (ATE) above a specified threshold value.
+Results are based on the causal forest model from Section \ref{sec:RF}.
+The solid line equals $1 - F_\text{ATE}(\delta)$ where $F_\text{ATE}(\delta)$ denotes the CDF corresponding to the density of conditional ATE estimates from Figure \ref{heterogeneous_effects}.
+The blue shaded regions are associated 95\% confidence intervals.
+We estimate that at least 90\% of borrowers have a positive conditional ATE.
+%\textit{Do file: }  \texttt{cdf_CATE.do}
+\end{figure}
+
+\cleardoublepage
+
+\begin{figure}[H]
+    \caption{Conditional ATEs from ``wide'' and ``narrow'' covariate sets}
+    \label{wide_narrow_forests}
+    \begin{center}
+    \begin{subfigure}{0.75\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/scatter_hist_wide_narrow.pdf}
+    \end{subfigure}
+    \end{center}
+      \scriptsize  This figure plots the relationship between the causal forest conditional ATE estimates from Section \ref{sec:RF} that use the ``wide'' set of covariates (all intake survey responses) and those based on a restricted ``narrow'' set of covariates (age, gender, HS education, and previous borrowing).
+The scatterplot graphs one estimate versus the other, with the ``wide'' covariate set on the horizontal axis and the ``narrow'' set on the vertical axis.
+The density plots on each axis show the estimated marginal distribution of conditional ATEs under each covariate set.
+The density for the ``wide'' covariate set is considerably more dispersed, as the causal forest based on this set of covariates captures considerably more treatment effect heterogeneity.
+
+%\textit{Do file: } \texttt{wide_narrow_forests.do}       
+\end{figure}
+
+\newpage
+\subsection{Targeting rule comparisons}
+
+\vspace{.3in}
+
+\begin{figure}[H]
+    \caption{Targeting rules}
+    \label{targeting_rules}
+    \begin{center}
+    \begin{subfigure}{0.75\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/wide_narrow_rule.pdf}
+    \end{subfigure}
+    \end{center}
+      \scriptsize   This figure plots the percentage of borrowers who would benefit from a program in which commitment is targeted using the ``narrow'' covariate set (age, gender, HS education, and previous borrowing).
+In this exercise ``benefit'' is defined to mean having a conditional ATE above a particular threshold, taking the estimated conditional effects from the ``wide'' causal forest as ground truth.
+The plot compares the estimated percentage of borrowers who benefit, along with associated 95\% confidence bands, for three targeting rules: universal forced commitment in blue, targeting based on a random forest classification model in green, and targeting based on the logit model in red.
+For each of the classification models, the outcome variable is an indicator for whether the CATE estimate from the ``wide'' random forest model is positive.
+Each of the classification models produces an estimated probability of a positive CATE.
+For each, the assignment rule ranks borrowers by this estimated probability, and assigns the highest 90\% to forced commitment, to match the overall percentage of borrowers with positive estimated CATEs from the ``wide'' random forest model.
+Because this is an in-sample exercise, it overstates the actual performance of logit and RF-based targeting.
+      %, the top \hl{XXX\%} of Both targeted Both of the targeted assignment rules are assigned by a the ``narrow'' causal forest in green, and targeting based on the logit model in red.
+The causal forest rule assigns a borrower to commitment if her estimated conditional ATE from the ``narrow'' covariate set is positive; the logistic regression rule assigns her to commitment if the estimated probability that her conditional effect is positive is greater than 0.5.
+      %\todo[inline]{@Issac: Have I described this correctly? Also, is this an out-of-sample exercise. In other words, are we using a holdout sample to make these comparisons?}
+
+      %This figure plots the (reversed) cumulative densities of the estimated benefits from the casual forest for three different rules.
+The blue line plots the HTEs from the `wide' random forest for the Forcing arm, which we take as the ground truth for actual impacts.
+The green line plots HTEs if we first target individuals using the variables in the `narrow' forest, and only assign individuals to commitment if they are on a leaf whose predicted forcing benefit is positive.
+The red line uses a logit regression to predict which individuals benefit from treatment, and assigns all individuals to the arm predicted to be best for them.
+
+\end{figure}
+\vspace{.1in}
+
+Figure \ref{targeting_rules} compares the in-sample performance of these targeting rules against a policy of universal forced commitment.
+The plot presents the estimated proportion of borrowers who benefit from a particular treatment assignment rule, along with associated 95\% confidence bands, where ``benefit'' is defined as having a conditional average treatment effect above a particular threshold.
+As above, we take the conditional average effects from the ``wide'' causal forest as ground truth for the purposes of this exercise.
+Because this is an in-sample exercise, the logistic and random forest classification rules have an unfair advantage: there is no adjustment for overfitting.
+In spite of this, their performance is quite unimpressive relative to a policy of universal forced commitment.
+The fraction of the whole sample incorrectly targeted when moving from universal forced commitment to targeting based on the narrow RF falls only from 9.78\% to 9.59\%.
+The logit targeting rule actually makes things marginally worse.
 

### 2023-11-22 donde.tex
Prepare draft for submission

--- 2023-10-16 donde.tex
@@
 
-In the context of pawnbroker lending, we show that forcing people into commitment contracts with a regular repayment structure decreases their (fee-including) financial cost by 20\%, increases the likelihood of recovering their pawn by 15\%, and increases the likelihood of repeat business by 20\%.
-Using a multi-armed RCT that includes both a voluntary and a forced arm, we illustrate how to point-identify both the Treatment on the Untreated and the Treatment on the Treated.
-We find modest selection on gains but nonetheless significant positive benefits of commitment even for those who would not have chosen it.
+We use a novel three-armed RCT, including both forced and voluntary treatment arms, to provide a unique window into choice, heterogeneous treatment effects and paternalism in the context of pawnbroker lending.
+Forcing borrowers into commitment contracts with a regular repayment structure decreases the financial cost of pawn loans by 22\% inclusive of fees, increases the likelihood of recovering their pawn by 15\%, and increases the likelihood of repeat business by 19\%.
+Leveraging the special features of our experimental design, we go on to point-identify the effects of commitment on both the treated and the untreated simultaneously, along with the average selection on gains.
+We find large and significant effects of commitment even for borrowers who would not voluntarily choose it, and no evidence of selection on gains: borrowers who would freely choose commitment do not appear to benefit more than borrowers who would not.
+A detailed analysis of treatment effect heterogeneity suggests that the potential gains from targeting commitment based on observable characteristics are extremely small and that most borrowers stand to gain from a policy of universal forced commitment.
 %The justification for paternalistic commitment in this context appears to be over-optimism; 74\% of clients say they will certainly recover their pawn while in fact only 57\% do so.
@@
 
-\textbf{Keywords: } Private paternalism, choice, heterogeneous treatment effects, commitment, overconfidence.
+\textbf{Keywords: } Private paternalism, choice, treatment on the untreated, heterogeneous treatment effects, commitment, overconfidence.
 
@@
 
-Restrictions of choice are often surreptitiously imposed on consumers.
-Firms limit their worker's freedom by requiring time-consuming progress reports,  schools impose deadlines and pop quizzes, and loan contracts often require monthly repayment.
-As pointed out by \cite{Laibson2018}, although these choice-restricting mechanisms may be beneficial to firms and clients, they are often disliked by the latter, and therefore ``shrouded'' by firms, i.e.
-not advertised but nonetheless embedded in products.
-\cite{Laibson2018} coins the term ``private paternalism'' for cases when restrictions on the freedom of choice is implemented by a firm in a way that advances a client's interests.
-
-Making a case for private paternalism is not easy.
-It involves comparing the causal effect of forcing a certain product characteristic against the effect of letting people choose it.
-Because choice may be correlated with unobservables, identifying these two effects is challenging in observational studies.
-%This is not a straightforward task because choice will be driven by unobservable factors, and to address the question fully
-Moreover, painting a complete picture of the benefits of forcing requires counterfactuals for both choosers and non-choosers alike, since the differential benefit of forcing arises from impacts among those who do not freely choose commitment.
-While a large behavioral literature has illustrated that allowing borrowers or savers to choose commitment-style products increase savings in an intention-to-treat (ITT) sense \citep{thaler2004save, prina2015banking, brune2016facilitating, callen2019headwaters, Pascaline, Ashraf}, this literature has rarely addressed the benefits of imposing commitment or its differential impacts on those who would not independently choose commitment.
-%\footnote{Selection on gains has such wide acceptance that economists often impose it in their models} (Although the examples above are plausible, substantiating a case for private paternalism is not easy.
-It involves comparing the causal effect of forcing a certain product characteristic versus the effect of letting people choose on that characteristic.
-This is not an easy task because a given person wither has or does not have choice, and because choice induces selection, potentially biasing causal estimates.
-A large behavioral literature has illustrated that allocating borrowers to a commitment-savings product increase savings \citep{thaler2004save, prina2015banking, brune2016facilitating, callen2019headwaters, Pascaline, Ashraf}, but this literature does not show that commitment would not be chosen by those that would benefit from it, that is, that the treatment effect on the untreated (TUT) is positive.
-Indeed, selection on gains has such wide acceptance that economists often impose it as a part of Roy models on topics as diverse as migration \citep{borjas1989economic} and job search \citep{lippman1976economics}.
-%, and program evaluation \citep{bjorklund1987estimation}. 
-In microfinance, a context close to ours, \citep{Murdoch} claim that there exists positive selection, citing a positive correlation between displaying present biased preferences in surveys and selecting into microfinance as evidence of borrowers' actually demanding the discipline imposed by frequent payments.
-However, they are unable to show that borrowers indeed benefit or that they indeed positively select based on treatment effects.
-
-%Many people have a difficult time accumulating and retaining capital unless they are provided a structure within which to do so.
-The behavioral lens on intertemporal financial services has provided critical insights on this problem, suggesting that saving from cash-in-hand is challenging \citep{Ashraf, Pascaline}, that credit may be preferred to savings as a way of accumulating capital simply because credit repayment contracts provide more structure \cite{Murdoch}, and even that the absence of structured financial contracts may be a key barrier preventing the poor from climbing out of poverty \citep{bertrand2004behavioral, collins2009portfolios}.
-A large behavioral literature has illustrated that the addition of commitment-style product features improves the ability to accumulate savings \citep{thaler2004save, prina2015banking, brune2016facilitating, callen2019headwaters} and to retire debt \citep{Bertrand, heidhues2010exploiting}.
-As a consequence, credit markets featuring limited-liability loans such as small-business financing or microfinance typically take a highly structured approach to credit contracts with frequent repayments and reminders as a way of inducing repayment.
-As pointed out by \cite{Laibson2018}, because many of these forms of commitment may be desirable to principals but not demanded by agents (or by the right agents), these mechanisms are often ‘shrouded’, meaning that commitment is embedded in products in ways that are not advertised to clients as such.
-
-This paper studies the benefits of restricting choice in the context of pawnbroker lending.
-Pawn loans are one of the oldest, most understudied, and most prevalent forms of borrowing \citep{carter2012pawnshops}.
-There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues (in China it is a \$43 billion industry).\footnote{\url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.} Our partner pawn lender (henceforth Lender $P$) alone served more than 1 million clients in Mexico in the last 3 years with more than 4 million contracts.\footnote{For comparison there were 2.3 million micro-finance clients in Mexico in 2009 (\cite{Pedroza:2010}).} Pawnshop lending presents an inverted lending case: since these loans are over-capitalized, the lender in the contract stands to gain the most when borrowers default.
-
-Our partner's standard pawn contract gave 70\% of the value of gold collateral in credit, and charged a monthly interest rate of 7\% for loans of a three-month duration, with a flexible no-reminders contract typical of the industry that can be paid back anytime before the loan comes due at no penalty.
+The behavioral finance literature has established an important role for commitment devices in helping consumers to achieve their own financial goals.
+While most academic studies on commitment focus on the role of voluntary self-commitment \citep{thaler2004save, prina2015banking, brune2016facilitating, callen2019headwaters, Pascaline, Ashraf}, in reality the predominant use of rigid structure in financial services is involuntary; firms only offer a product with these features embedded.
+\cite{Laibson2018} has referred to this implicit bundling of commitment devices as ``private paternalism'', and its logic is that individuals may benefit from commitment and yet not explicitly demand it.
+Comparing voluntary versus paternalistic programs requires that we form counterfactuals for two different groups of people: those who would freely choose commitment, and those who would not (since the latter group is treated only under paternalist policies).
+In this paper we present an experimental design and econometric analysis that point-identifies and provides estimates for both the effect of treatment on the treated (TOT) and on the untreated (TUT).
+This permits a clear window into the case for paternalistic (forced) rather than voluntary commitment in financial services.
+
+The relationship between treatment effects and treatment take-up is a core concern in the econometrics literature.
+In principle, the Marginal Treatment Effect (MTE) approach allows researchers to use observational data and a single excluded instrument to study this relationship.
+In practice, however, unless the instrument has a rich support set, MTEs can only be point identified by using additional modeling assumptions \citep{mogstad2018using}.
+An alternative research strategy to study the relation between treatment effects and treatment take-up uses the Becker-Degroot-Marschak (BDM) mechanism, incentivizing choice prior to treatment assignment to elicit willingness to pay (WTP) for treatment \citep{becker1964measuring}.
+A number of studies, however, find that the WTP elicited under the BDM mechanism changes substantially with the distribution of prices used in the elicitation exercise \citep{bohm1997eliciting,banerji2014detection}.
+This falsifies the assumption of standard preferences that is required for BDM to be incentive-compatible \cite{mamadehussene2023reliability}, suggesting that the mechanism may not provide a reliable measure of actual compliance  in practice.
+Our study avoids the drawbacks of the MTE and BDM approaches by combining a novel three-armed randomized controlled experiment, including forced treatment and treatment choice arms, with two transparent exclusion restrictions.
+Together, these allow us to point identify the relevant TOT and TUT effects in a real-world, high-stakes setting and to study the case for paternalistic commitment head-on, with minimal assumptions.
+
+We apply this approach to an important and understudied context: pawnshop lending. 
+Pawn loans constitute one of the oldest and most prevalent forms of borrowing \citep{carter2012pawnshops}.
+Our partner lender, for example, made over 4 million loans to more than a million clients during the past three years.\footnote{For purposes of comparison, there were 2.3 million microfinance clients in Mexico in 2009 \citep{Pedroza:2010}.}
+The question of choice versus paternalism is particularly salient in this context, as choice mistakes could arise from borrowers' low education and the fact that they typically borrow for emergencies under significant stress.\footnote{There is a large literature showing that stress impairs cognitive function, e.g.
+\cite{StressReview}.}
+%\footnote{There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues (in China it is a \$43 billion industry).
+\url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.}
+Our experiment covers just under 5,000 pawnshop clients in 6 of our partner lender's Mexico City branches.
+Our control arm illustrates the costs of the status quo contract: fully \emph{44\%} of borrowers default, losing lose their pawn along with any payments made towards principal.\footnote{High pawn default rates are common, in the US they oscilate around 15\% (\url{https://tinyurl.com/yc2x5bjf}).} Our ``commitment choice'' arm gives borrowers the chance to opt into a structured repayment contract when taking a loan.
+The structured contract requires borrowers to make three monthly payments rather than one balloon payment at the end, with each monthly payment including the accrued interest at that time as well as a nominal fee of 2\% of that month's payment if the payment is delinquent.
+The fee serves as a reminder and a means of reinforcing the importance of these interim payments.
+In our ``forced commitment'' arm all borrowers are \emph{required} to repay using the same structured monthly contract offered on an opt-in basis in the commitment choice arm.
+
+%The combination of voluntary and forced commitment within the RCT allows us to address several key questions. 
+We address three key questions.
+First, do structured repayment contracts lower financial costs for pawnshop borrowers?
+Second, do borrowers recognize this benefit, demanding commitment in sufficient numbers?
+Finally, and most uniquely, do the \textit{right} borrowers voluntarily demand commitment?
+Our ability to answer the last question comes from our unique three-armed experimental design, which we call the ``controlled choice design'' for short.
+This design can be viewed as a juxtaposition of \emph{two} randomized encouragement designs, each with one-sided non-compliance.
+One of them point identifies the effect of commitment for borrowers who would \emph{voluntarily} choose commitment (TOT),
+while the other point identifies the effect of commitment for borrowers who would \emph{not} (TUT).
+By identifying both the TOT and TUT effects in the same experiment, the controlled choice design allows us to examine the empirical relevance of ``selection on gains'' also known as Roy-type selection into treatment by estimating the ``average selection on gains'' $\text{ASG} = \text{TOT} - \text{TUT}$.
+This enables us to test whether borrowers who voluntarily choose commitment have higher average treatment effects than those who do not, rather than assuming it.
+The controlled choice design also point identifies the average selection bias (ASB)--the average difference in untreated (status quo) potential outcomes for those who choose commitment relative to those who do not--along with the average selection on levels (ASL)--the analogous comparison for treated (commitment) potential outcomes.
+Taken together, these causal effects allow us to ``go under the hood'' of our baseline ATE results, and paint a more complete and economically relevant picture of the effects of commitment.
+We are unaware of any other paper that simultaneously identifies all of these causal effects without recourse to additional structural modeling assumptions.
+
+We find that commitment is strongly effective in lowering financial costs and preventing default in pawnshop lending: the average individual in the forced arm pays financing costs inclusive of fees that are 22\% lower than the control, and faces a probability of default that is 6.6 percentage points lower (15\% of the mean).
+In terms of Annual Percentage Rates, the financial cost of borrowing falls by 11 percentage points (19\% of the mean).
+In short, structured commitment saves borrowers money by charging them fees!
+Our results are qualitatively robust to deducting transport costs of visiting the branch to make interim payments along with a day of lost wages for each visit.
+They are also robust to using borrowers' \emph{subjective} values of their pawns rather than the appraised value of the gold, and to adjusting for lost liquidity from requiring monthly payments.
+The monthly payment contract seems to achieve these cost savings by speeding up payments and by generating an early bifurcation of borrowers into those that will recover the pawn and those that will not.
+The former are induced to pay faster, saving on interest; the latter pay less towards loans that ultimately default, hence losing less money when they do.
+
+Despite these large financial cost savings, only 11\% of borrowers in the choice arm choose commitment. 
+%If the effect of commitment were homogeneous, this would be enough to conclude that the 89\% who did not choose it would have been financially better off if they had.
+However, we test and reject the null hypothesis of homogeneous treatment effects using the method of \cite{chernozhukov2018generic}.
+Can the borrowers who did not choose commitment be those who simply don't need it? 
+To answer this question, we carry out a detailed analysis of treatment effect heterogeneity.
+%We address this question by sequentially imposing more structure on the problem. 
+We begin by bounding the distribution of individual treatment effects using the marginal outcome distributions from the forced commitment and control arms, following \cite{fan2010sharp}.
+This approach imposes no assumptions beyond the experimental randomization.
+We find that \textit{at least} 23\% of borrowers benefit from commitment.
+This implies that there must be many borrowers in the choice arm who did not demand commitment despite their \emph{individual treatment effect} from (forced) commitment being positive.
+Next, we impose an exclusion restriction positing that the effect of a given contract does not depend on \emph{how} borrowers obtain it.
+In other words, we assume that choosing a contract results in the same potential outcome as being assigned that contract.
+This is a relatively common if often implicit assumption in causal inference.\footnote{Papers that use variation in compulsory schooling laws to identify the returns to schooling, for example, typically interpret their results as the causal effect of additional \emph{education} rather than additional \emph{forced education}.
+\cite{chamberlain2011bayesian} uses a closely related assumption to develop a theory of optimal treatment choice.}
+It also has testable implications that we fail to reject in our empirical context.\footnote{See \ref{append:exclusion} for details.}
+Under this restriction, the controlled choice design point identifies the TOT, TUT, ASG, ASB, and ASL effects described above.
+Our estimated TUT effect on financial cost savings is large: \$192 pesos, equivalent to a 10.6 percentage point savings in APR.
+On average, the borrowers who would \textit{not} choose commitment, would have faced substantially lower financial costs if they had.
+Finally, we combine our experimental treatment and outcome data with survey responses collected for a subset of borrowers to estimate conditional average treatment effects, both TUTs and ATE, using the Causal Random Forest algorithm of \cite{atheygrf}.
+We estimate positive conditional average TUT effects for 93\% of the borrowers who did \textit{not} choose the commitment contract.
+In short, it is extremely difficult to find identifiable groups of borrowers who are \emph{harmed} by commitment, even when restricting attention to those who would not choose it voluntarily. 
+%while only 37\% of those who chose commitment have negative conditional TOT effects.
+While targeting commitment products to those that benefit the most is a policy that appears attractive, in this context we find that the usable targeting variables have relatively weak predictive power and hence even our best random forest targeting only reduces the overall mis-targeting rate from 9.7\% (all to Forcing) to 9.5\% (our best-case feasible targeting mechanism).
+
+What explains the persistence of no-commitment contracts so contrary to borrowers’ interests in the real world?
+From the demand side, while a simple measure of time inconsistency does not explain the large and positive TUT effect, we show substantial levels of over-optimism among borrowers.
+Among borrowers who do not choose commitment, those with the largest estimated benefits from commitment are the individuals who most systematically over-estimate their own probability of repayment without the need to commit, potentially decreasing their demand from commitment.
+From the supply side, because borrowers' financial savings come directly from the pockets of lenders, pawnshops have an interest in retaining the no-commitment contract.
+Indeed, pawnshop lending presents an inverted lending case: since these loans are over-collateralized, the lender in the contract stands to gain the most when borrowers default.
+Our partner's \emph{status quo} pawn contract gave 70\% of the value of gold collateral in credit, and charged a monthly interest rate of 7\% for loans of a three-month duration, with a flexible no-reminders contract, that could be paid back anytime before the loan comes due at no penalty.
+This contract is standard contract in the industry.
 This combination of features, and the fact that the gold pawn is highly liquid, means that the lender makes 90\% more profit over three months from a borrower who defaults than one who repays (30\% of collateral value recovered under default, 15.8\% of collateral value paid in interest if loan fully repaid).
 While an older literature considers the exploitative potential of over-collateralization and underpriced collateral \citep{basu1984implicit}, the implication of such contracts has not been analyzed in the behavioral literature.
-%When the lender desires default, the repayment-inducing features of commitment-style repayment contracts become undesirable and there may be incentives for the principal to create contracts with no structure, no reminders, and simple balloon payments.
-To repurpose the language of \cite{Laibson2018}, we suggest that pawn contracts effectively shroud their \textit{lack} of commitment features to induce default in a manner that is not obvious to borrowers.
-Given that pawnshops, moneylenders, and paycheck lending institutions are likely to face client pools disproportionately made up of impatient and time-inconsistent individuals, the design of such contracts may have serious consequences for the financial lives of the poor.
-
-%clients lose their pawn, and among those that recover it almost all of them pay in the last days, just before the loan elapses.\footnote{In the US default is also high at 15\% (\url{https://tinyurl.com/yc2x5bjf}).}
-
-%In this paper we examine pawn contracts, an understudied form of credit despite their relative ubiquity \citep{carter2012pawnshops}, and a major vehicle through which poor households may dis-accumulate savings.
-There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues.
-In China it is a 43 billion dollar industry.\footnote{\url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.} Our partner, a Mexican pawn lender (henceforth Lender $P$) alone served more than 1 million clients in the last 3 years with more than 4 million contracts.
-
-Against this backdrop, we implement a multi-arm randomized control trial covering close to 10,000 pawnshop clients in 6 branches of Lender $P$ in Mexico City, using a design built to test the demand for and impact of alternative payment structures in pawn repayment contracts.
-Our control arm illustrates the costs of the status quo contract: fully \emph{43\%} of borrowers default and so lose their pawn as well as any payments made towards principal.\footnote{These high default rates are not uncommon, in the US default is also high at 15\% (\url{https://tinyurl.com/yc2x5bjf}).} We then implement a ``commitment choice'' arm, in which borrowers can opt into a structured repayment contract at the time of taking a loan.
-The structured contract requires borrowers to make three monthly payments rather than one balloon payment at the end, with each monthly payment including the accrued interest at that time as well as a nominal fee of 2\% of that month's payment if that payment is delinquent.
-This fee serves as a reminder and a means of reinforcing the importance of these interim payments.
-In addition, we include a ``forced commitment'' arm, in which all borrowers are \emph{required} to repay using the structured monthly contract that is offered on an opt-in basis in the commitment choice arm.
-
-The combination of voluntary and forced commitment within the RCT allows us to address several key questions.
-First, do structured repayment contracts lower financial costs for pawnshop borrowers?
-Second, do borrowers recognize this benefit, demanding commitment in sufficient numbers?
-Finally, and most uniquely given the presence of a forced commitment arm, we are able to ask whether the \textit{right} borrowers voluntarily demand commitment.
-In particular, we use the choice, control, and forced arms to point identify the Treatment on the Treated (TOT) and the Treatment on the Untreated (TUT) effects, along with the average selection on gains (ASG) and average selection bias (ASB).
-
-Our results suggest that commitment is strongly effective in preventing default in pawnshop lending, with the average individual in the forced arm paying financing costs inclusive of fees that are 20\% lower than the control, while default decreases by 6.5 percentage points (15\% of the mean).
-In terms of Annual Percentage Rates, the financial cost of borrowing is reduced by 34 percentage points.
-That is, by imposing the structure of commitment it is possible to save borrowers money by charging them fees!
-These results are robust qualitatively to including transport costs of going to the branch plus losing a day's wage for each visit, using each borrower's subjective value of the pawn rather than the appraised value of the gold, and adjusting for lost liquidity from requiring monthly payments.
-
-The monthly payment contract seems to achieve these cost savings by speeding up payments and by generating an early bifurcation of borrowers into those that will recover the pawn and those that will not.
-By inducing borrowers either to fully recover or to default without making any payments it saves money that would otherwise have been paid towards loans that ultimately default, money which is lost to the borrower.
-In the treatment group, the first payment occurs 13 days earlier, and the fraction recovering on the first visit is 7.7 percentage points higher.
-Commitment contracts also decrease the fraction of borrowers who make a payment but ultimately fail to recover their pawn by 7 percentage points.
-Treatment effects are concentrated in the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery.
-That is, the commitment contract induces people who would otherwise pay something towards recovery but default to instead pay more and faster, making them more likely to recover their pawn at a lower financial cost.
-
-In spite of a large average treatment effect documenting financial cost savings, only 11\% of borrowers in the choice arm actually choose commitment.
-If the effect of commitment were homogeneous, this would be enough to conclude that the 89\% who did not choose it would have been financially better off if they had.
-However, we test and reject the null hypothesis of homogeneous treatment effects using the method of \cite{chernozhukov2018generic}.
-Can the borrowers who did not choose commitment be those who simply don’t need it?
-We address this question by sequentially imposing more structure on the problem.
-
-We start our analysis of heterogeneity by bounding the distribution of treatment effects $Y_{1i}-Y_{0i}$ using the two marginal distributions in the treatment and control arms as in \cite{fan2010sharp}.
-We find that at least 24\% of individual borrowers benefit from commitment, implying many borrowers did not demand it even though their individual treatment effect is positive.
-Next, we impose the exclusion restriction that the effect of the contract does not depend on how they got it, that is: choosing a contract has the same treatment effect as being assigned to that contract.\footnote{This is a frequently used assumption even if often implicit.
-For instance, a significant literature uses schooling compulsory laws to estimate the return of one more year of school, and then often interprets that schooling, in general, has this return.} We show that in this case our 3-armed experiment point identifies the TUT.
-We then estimate that the financial cost savings of the TUT is large, at \$356 pesos, equivalent to 24 percentage point savings in APR.
-That is, on average borrowers that did \textit{not} choose the frequent payment contract would have benefited from having that contract.\footnote{We estimate a positive TOT that is larger than the TUT, but it is imprecise--this results from the smaller sample size, given that few chose the monthly payment contract--and the hypothesis of TOT=TUT is rejected only with 13 percent confidence for the APR and 12 percent confidence for default.}
-%We also estimate that those that would not choose if given the opportunity would have lower status-quo outcomes (i.e.
-the average selection bias is negative).
-Finally, assuming the exclusion restriction for subsets of observable characteristics splits generated by a causal forest allows us to establish that 86\% of would-be non-choosers would save on financial cost by being assigned to frequent payments.
-That is, the benefits of imposing a monthly payment are distributed broadly.
-\hl{TuT benefits are particularly large for XXX CHARACTERISTICS, and TOT benefits for those with XXX.}
-In a final step, we impose a selection-on-observables assumption and use the Causal Random Forest algorithm of \cite{atheygrf} to estimate conditional average treatment effects (both ATEs and TUTs) for the individual borrowers in our experiment.
-We estimate that 93\% of the borrowers who did not opt for the commitment contract have positive conditional TUT effects, while only 1\% of those who chose commitment have negative conditional TOT effects.
-While targeting commitment products to those that benefit the most is a policy that appears attractive, in this context we find that the usable targeting variables have relatively weak predictive power and hence even the random forest only reduces the overall mis-targeting rate from 8\% (all to Forcing) to 5.5\% (our best-case feasible targeting mechanism).
-
-%however those most economically vulnerable, and those most overconfident about their probability of repayment, experience larger gains.
-
-%\footnote{As in \cite{Rabin2018} we contrast subjects' \textit{own predictions} of their behavior with their actual behavior, but we do it in a natural setting.}
-
-%Borrowers assigned to the forced commitment contract are 5 percentage points (100\% of the mean) more likely than the control group to ask for another loan in the future, suggesting that they liked the commitment contract after experiencing it.
-However, when offered the choice of commitment, very few borrowers elect to commit voluntarily.
-Only 10\% of the choice arm takes up the contract, and none of the core study outcomes are significantly improved by the ability to choose commitment.
-
-%This is not the first paper to find low demand for commitment, however it is the first we know of that can compare choice versus forcing with a money-metric outcome such as loan repayment.
-
-%Most importantly, our multi-arm design allows us to show that the \textit{wrong} people choose commitment when offered it.
-We illustrate this point in three distinct ways.
-First, we use a Random Forest algorithm \citep{atheygrf} to estimate individual-level treatment effects for the forced versus control arm, and show the benefits of forcing to be significantly negatively correlated with the propensity to choose commitment estimated from the choice arm.
-93\% of those who did not opt for the commitment contract would have been better off with it, while only 1\% of those who chose commitment would have been better off without it.
-Second, a Boosted Classification Algorithm arrives at a similar answer, showing that the borrowers naturally cluster into two groups, one of which is likely to choose commitment and does not benefit from it, and the other the reverse.
-Finally, estimating LATEs on compliers and non-compliers alike we show that the estimated treatment effect on non-compliers is larger than the treatment effect on compliers.
-That is, those choosing commitment benefit less from commitment than those not choosing it.
-Hence our results show clearly that a paternalistic policy forcing borrowers into a more rigid and structured repayment regimen is uniquely beneficial to them.
-While this perverse relationship between choice and benefits from commitment echo closely the findings of \cite{Sprenger} we are the first to be able to examine this relationship using a high-stakes, money-metric outcome in a natural field environment.
-
-What explains the persistence of no-commitment contracts so contrary to borrowers’ interests in the real world?
-First, we show substantial levels of over-optimism among borrowers.
-Among borrowers who do not choose it, those with the largest benefits from commitment are the individuals who most systematically over-estimate their own probability of repayment at the time of taking the loan.
-The dramatic improvements in borrower income arising from the commitment contract come directly from the pockets of lenders, reinforcing that the pawn industry as a whole has a strong interest in retaining the status quo.
-
-Does learning eventually overcome the low demand for commitment? 
-%For learning to happen clients would need to experiment with the frequent payment contract, and this was not the typical contract in the industry.
-But even if the contract was experienced, borrower may fail to learn or learn only slowly.
-We find that borrowers who are assigned the forced commitment contract are 6.7 percentage points more likely to become repeat costumers than those assigned to the status-quo contract.
-One potential interpretation of this result is that borrowers who experience the frequent payment contract rationally choose to borrow more later on because of the lower effective financial costs that this contract entails.\footnote{An alternative interpretation is that the monthly payments from the commitment contract sap borrowers liquidity, leading them to take a second loan to pay off the first.
-This is unlikely because subsequent loans fall outside the 90 day period within which payments for the first loan are due.
-Moreover, the correlation is also present conditional on having paid down the first loan.
-Borrowers tend to pledge a different piece for the second loan, so that recovery of the first pawn is also an unlikely explanation.} However, a stronger test of liking the monthly payment contract is whether conditional on coming again, they would choose frequent payments.
-We test this and we cannot reject that demand is higher after experiencing the monthly payment contract, however sample sizes are small and power for this analysis is correspondingly low.
-%While forcing individuals into commitment does not cause them to demand it in subsequent loans, \textcolor{red}{in Table \ref{iv_pf}} we show observational evidence of `learning by not doing’:  individuals offered commitment who elect not to take it and subsequently default \textit{do} learn about the benefits of commitment, demanding commitment loans at higher rates on subsequent pawn contracts when given the choice.
-Finally, while we are working with a lender who has a social mission and is interested in understanding how to help borrowers, there is no free lunch.
-The dramatic improvements in borrower income arising from the commitment contract come directly from the pockets of lenders, reinforcing that the pawn industry as a whole has a strong interest in retaining the status quo.
-Our results suggest that pawn lending markets capture borrower wealth in ways not well summarized by interest rates.
-By overcollateralizing and then structuring loan contracts in a manner encouraging of default, lenders are able to extract substantial value independent of the interest charged.
+
+%By overcollateralizing and then structuring loan contracts in a manner encouraging of default, lenders are able to extract substantial value independent of the interest charged.
+
+Our paper makes a number of contributions to the literature.
+First, we propose a way to use this three-armed experimental structure to recover treatment effects for choosers and non-choosers under minimal assumptions.\footnote{While \cite{fowlie2021default} likewise employ a three-armed experimental design in their study of the effect of electricity pricing, they identified \emph{two} TOT effects for different groups of ``treated'' households, whereas we simultaneously identify the TOT and TUT effects defined with respect to a single ``treated'' group of borrowers.
+This difference is what allows our design to point identify the ASG and related quantities.}
+We further provide simple, regression-based estimators for each of these causal parameters, along with procedures for computing associated cluster-robust standard errors.\footnote{See \ref{append:randchoice} for details.} A companion STATA package provides easy-to-use commands that implement our estimators and standard errors.
+The controlled choice design could be useful in other experimental settings where the question of interest centers on the merits of paternalism, public or private, or the relationship between choice and treatment effects.
+One obvious example is the design of other financial contracts beyond pawn loans.
+Another is education, where teachers typically mandate quizzes, homework, and other commitment mechanisms to mitigate student procrastination \citep{Ariely}.
+We further contribute to a relatively small existing literature that sheds light on private paternalism.
+In the context of food choice, \cite{Sprenger} show that individuals with the most time-inconsistent preferences are actually least likely to demand commitment.
+In contrast to their paper, we directly identify the TUT, obviating the need to first elicit preferences before testing for negative selection.
+In the context of school choice, \cite{Walters} combines a distance instrument with additional structural assumptions, obtaining model-based TUT and ATE estimates.
+He finds that students who select into more effective schools have smaller treatment effects from attending than those who do not select in.
+In contrast, our approach point identifies TUT and TOT and a range of other interesting causal parameters without the need for a structural model, relying instead on relatively weak exclusion restrictions whose testable implications we fail to reject.
+
+%This controlled choice design is key to measuring the effects of mandated versus voluntary imposition of product features.
+This question is of interest in a large class of cases.
+Financial contracts frequently feature dimensions of private paternalism, such as mandatory frequent payment structures for loans.
+But beyond finance, in education, most teachers mandate homework with deadlines to deal with procrastination \citep{Ariely}.
+In the workplace, firms monitor employee attendance,\footnote{\url{https://www.wsj.com/lifestyle/careers/attention-office-resisters-the-boss-is-counting-badge-swipes-5fa37ff7}.} but also set and monitor time-specific goals.
+In the public policy domain we have seat belt mandates, age-dependent medical checkups, etc., which often go beyond nudging.
+Having a rigorous way to estimate the causal effects of mandates vs choice policies ---and not just for the average individual--- is critically important.
+%\footnote{The ``LATE-and-reweight'' approach goes beyond LATE by assuming no unobserved selection-on-gains \citep{aronow2013beyond,angrist2013extrapolate}.
+In our approach, we estimate selection-on-gains directly.
+Finally, as the MTE literature relies on a combination of instruments with rich support and additional structural assumptions such as additive separability of observed and unobserved determinants of treatment effect heterogeneity \citep{heckman2007econometric, cornelissen2018benefits}.
+In a returns-to-education setting, \cite{oreopoulos2006estimating} uses a direct approach to identify a LATE.}
+
+%\cite{Walters} takes the latter approach, combining a distance instrument with additional structural assumptions, obtaining model-based TUT and ATE estimates that differ substantially from those implied by a LATE-and-reweight approach.
+
+%\footnote{In a returns-to-education setting, \cite{oreopoulos2006estimating} uses a direct approach to identify a LATE % \emph{nearly} equals a TUT effect: the 1944 Butler Act increased the share of British children who remained in school until age 15 from 43\% to over 90\%.
+Because 100\% of borrowers in our forced arm are treated, we identify the TUT rather than an approximation to it.}
+
+Our study also speaks to recent research on the effects of payment frequency.
+While experiments in microfinance markets have \textit{not} shown the same benefits from providing a more regularized repayment environment as we find here \citep{Pande, barboni2023flexible}, these experiments differ from ours in two important ways: they are performed on top of already highly structured micro-finance contracts, and they involve borrower pools who may have selected into that type of lending precisely because it provides structure \cite{Murdoch}.
+These differences may explain why \citep{Pande} finds almost no default in the control group, in stark contrast to our setting of high default.
+Second, we provide a deeper analysis of \textit{both} take-up and the efficacy of voluntary commitment mechanisms.
+A number of papers have found low demand for commitment as we do.\footnote{\cite{Ashraf}, \cite{Gine}, \cite{Ted}, \cite{Royer}, \cite{Sprenger}.
+Others have found more robust demand for commitment (\cite{Kremer},  \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}, \cite{Pascaline}).} Unlike all of these papers, however, we separately point-identify and estimate the effects of commitment for borrowers who would and \textit{would not} choose it.
+This allows us to conduct a more rigorous and nuanced analysis of private paternalism.
+
+%By overcollateralizing and then structuring loan contracts in a manner encouraging of default, lenders are able to extract substantial value independent of the interest charged.
 Further, the `nudge’ approach generally favored by the behavioral literature (voluntary commitment) does not generate adequate demand in this context.
-
-%We hesitate to give precise policy recommendations since we don't have good measures of welfare.
-Even though the monthly payment contract dramatically reduces financial cost, it could potentially generate lower (or higher) anxiety.
-Moreover, frequent payment requirements may decrease welfare of highly impatient borrowers.\footnote{The paper presents an back of the envelope exercise that suggests annual discount rates of 4000 are necessary to nullify the reductions in financial cost we estimate.
-\hl{Note also that since the fee for skipping payment is 2\%, the iliquidity imposed by the contract is bounded.}} %Second, given the non-standard nature of the finding, it is likely that we would have to adopt and estimate a particular behavioral model of demand for commitment, which we don't need to do to make the point that TuT is positive.
-
-%we estimate that over 50\% of the borrowers in our study are naïve hyperbolics in the sense that they would benefit from commitment but will not choose it.
-While our results are driven by the intersection of overcollateralization and a potential selection of the borrower pool towards myopia and short-term financial thinking, these attributes are likely to be present in many types of pro-poor financial markets where individuals lack the credit histories to be able to leverage short-term credit without collateral.
-This suggests that regulators of such markets should include what is paid through equilibrium default as part of the financing cost (not done now), and to consider imposing structured lending products that tilt the scales towards allowing borrowers to repay.
-While commitment-style repayment contracts decrease effective liquidity by requiring faster repayment of a given loan, the improvement in expected borrower returns are so substantial as to prove welfare improving at all but the most astronomical discount rates.
-
-Our paper makes a number of contributions to the literature. %First, they suggest consequential ways in which different financial services draw client pools with distinct behavioral biases. 
-First, it speaks to microfinance research on the effects of payment frequency.
-While experiments in microfinance markets have not shown the same benefits from providing a more regularized repayment environment as we find here \citep{Pande}, these experiments differ from ours in two important ways: they are performed on top of highly structured contracts, and they involve borrower pools who may have selected into that type of lending precisely because it provides structure.
-These differences may explain why \citep{Pande} finds almost no default in the control group, in stark contrast to our results.
-Second, we provide a deeper analysis of both the take-up and efficacy of voluntary commitment mechanisms.
-A number of papers have found low demand for commitment as we do (\cite{Ashraf}, \cite{Gine}, \cite{Ted}, \cite{Royer}, \cite{Sprenger}) while others have found more robust demand for commitment (\cite{Kremer},  \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}, \cite{Pascaline}).
-Unlike all of these papers, however, we separately point identify and estimate the effects of commitment for borrowers who would and would not choose it.
-This allows us to conduct a more rigorous and nuanced analysis of private paternalism in our empirical context.
-
-Two other recent papers also shed some light on private paternalism.
-In the context of food choice, \cite{Sprenger} show that individuals with the most time-inconsistent preferences are actually least likely to demand commitment, suggesting a lack of awareness as to self-control problems.
-In the context of school choice, \cite{Walters} finds that students who select into more effective schools have smaller treatment effects from attending than those who do not.
-Our paper differs from these in both its empirical setting and its methodology.
-As far as we are aware, ours is the first experiment to combine control, forced treatment, and treatment choice arms and explain how such a design can be used to point identify TUT effects and a range of other interesting causal parameters under minimal assumptions.
-While \cite{fowlie2021default} likewise exploited a three-armed experimental design in their study of the effect of electricity pricing, they identified two TOT effects for different groups of ``treated'' households, whereas we simultaneously identify the TOT and TUT effects defined with respect to a single ``treated'' group of borrowers.
-We call our approach the ``Controlled Choice design'' for short.
-Other approaches to going beyond local average treatment effects (LATE) from the literature either assume no unobserved selection-on-gains \citep{aronow2013beyond,angrist2013extrapolate} (the ``LATE-and-reweight'' approach) or rely on a combination of instruments with rich support and additional structural assumptions such as additive separability of observed and unobserved determinants of treatment effect heterogeneity \citep{heckman2007econometric, cornelissen2018benefits} (the marginal treatment effects approach).
-\cite{Walters} takes the latter approach, combining a distance instrument with additional structural assumptions, obtaining model-based TUT and ATE estimates that differ substantially from those implied by a LATE-and-reweight approach.
-In contrast, we leverage our experimental design to point identify the TUT effect using a binary instrument without the need for a structural model, relying instead on relatively simple exclusion restrictions.
-This restriction has testable implications that we fail to reject.
-Rather than assuming away unobserved selection-on-gains, as in the LATE-and-reweight approach, we estimate it directly.
-Unlike \cite{Sprenger} we directly identify the TUT, obviating the need to first elicit preferences before testing for negative selection.
-In a returns-to-education setting, \cite{oreopoulos2006estimating}, uses a similar direct approach to identify a LATE \emph{nearly} equals a TUT effect: the 1944 Butler Act increased the share of British children who remained in school until age 15 from 43\% to over 90\%.
-Because 100\% of borrowers in our forced arm are treated, we identify the TUT rather than an approximation to it.
-
-%We illustrate here how experimental design can be used to form a simple test for selection on gains.
-
-%In contrast to the broader literature on Marginal Treatment Effects \citep{heckman2007econometric}), we exploit simple randomization and an exclusion restriction on choice rather than requiring a continuous instrument that can be used to build a structural model as in \cite{Walters}.
-
-%achieve identification of the TuT by using parametric model and a distance instrument, which requires the model to be correct and the instrument to be valid.
-TUT and ATE implied by LATE-and-re-weight differ sharply from his model-based estimates.
-The method of
-
-%Methodologically we contribute to the large literature on treatment effect heterogeneity by showing how an experimental design with two forcing arms and one choice arm allows for identification of the TOT, the TUT and other important parameters under minimal assumptions.
-\cite{aronow2013beyond} and \cite{angrist2013extrapolate} assume no selection on gains to estimate \hl{XXX}.
-
-%\cite{heckman2007econometric} and \cite{cornelissen2018benefits} require the availability of instrumental variable with rich support, and separability of observed and unobserved determinants of treatment effects.
 
@@
 Section \ref{Design} describes the experiment and data sources, and shows pre-treatment balance across arms.
-Section \ref{Experiment} provides the standard ITT analysis of the experiment, while Section \ref{Choice} presents our strategy for estimating ToT and TuT effects, and Section \ref{Paternalism} investigates why paternalism functions so well in this context and whether it can be more finely targeted.
-Section \ref{conclusion} concludes.
+Section \ref{Experiment} provides the standard ITT analysis of the experiment, while Section \ref{Choice} shows how to identify, estimate and carry out inference for the TOT, TUT, ASG, ASB and ASL effects under the controlled choice design.
+Section \ref{Paternalism} investigates why paternalism functions so well in this context and whether it can be more finely targeted and Section \ref{conclusion} concludes.
 
@@
 Pawn loans involve individuals leaving valuable liquid assets, typically jewelry, as collateral in exchange for an immediate cash loan.
-Collateral is typically larger than the loan, allowing lenders to skip the checking of credit history and give the loan immediately.
+Collateral is typically more valuable than the loan amount, allowing lenders to give the loan immediately without checking a borrower's credit history.
 This makes pawn loans a popular way to get cash to pay for emergencies.
@@
 In spite of the high prevalence and long history, pawnshop borrowing has not received much attention in the economics literature.
-The closest widely studied product is payday loans.
+The closest widely studied product is payday lending.
 In developing countries, however, payday lending is likely small compared to pawnshop lending; the latter is faster and requires less documentation, making it more accessible to informal sector workers who receive their salaries in cash.
@@
 As with payday lending, pawnshop lending is controversial.
-Regulators have concerns with the sophistication of borrowers using it, speculating they may suffer from behavioral and cognitive deficiencies which lead to make sub-optimal choices.\footnote{The US congress has actually banned the payday lending industry from serving active military personnel, and some States in the US have imposed zoning restrictions, interest caps, and restrictions on serial borrowing as consumer protection measures against payday lending \citep{Payday}.} There is some evidence in support of this view for payday borrowers.\footnote{\cite{Bertrand} write that ``Under the view that the people borrowing from payday lenders are making an informed, utility-maximizing choice given the constraints that they face, one would not expect additional information disclosure about the payday product to alter their borrowing behavior'', but to the contrary, they find that simply disclosing how financing costs add up reduced demand by 11\%.
-\cite{Meltzer} finds that payday loan access leads to increased difficulty paying mortgage, rent and utilities bills.}  Our study reinforces the idea that a lack of sophistication may be an integral part of that way that standard pawn contracts are structured.
+Regulators have concerns with the sophistication of borrowers using it, speculating they may suffer from behavioral and cognitive deficiencies that lead to making sub-optimal choices, biases that are exacerbated by contract design.\footnote{The US congress has actually banned the payday lending industry from serving active military personnel, and some States in the US have imposed zoning restrictions, interest caps, and restrictions on serial borrowing as consumer protection measures against payday lending \citep{Payday}.} There is some evidence in support of this view for payday borrowers\footnote{\cite{Bertrand} write that ``Under the view that the people borrowing from payday lenders are making an informed, utility-maximizing choice given the constraints that they face, one would not expect additional information disclosure about the payday product to alter their borrowing behavior'', but to the contrary, they find that simply disclosing how financing costs add up reduced demand by 11\%.
+\cite{Meltzer} finds that payday loan access leads to increased difficulty paying mortgage, rent and utilities bills.} but none for the large pawn-lending industry.
+Our study reinforces the idea that a lack of sophistication may be an integral part of the way that standard pawn contracts are designed and structured by lenders.
 
@@
 
-\paragraph{Appraising and lending.} Lender P takes gold jewelry as collateral in exchange for a fraction the value of the piece, in cash.
+\paragraph{Appraising and lending.} Lender P takes gold jewelry as collateral in exchange for a fraction of the value of the piece, in cash.
 No other collateral and no credit history checks are needed.
@@
 The loan had a 90 days term with 15 days' grace period.
-The client could make payments at the branch at anytime with no penalty for pre-payment.
-No reminders or interim contact exists between the lender and the borrower.
-If the client returns to pay the principal plus the accumulated interest within 105 days, she received back her pawn, otherwise the pawnbroker kept the piece \textit{and} any payments made.
-Before the contract expired, the client had the right to renew for another 3 months by going to the pawnshop, paying the accumulated interest, and signing a new contract with exactly the same terms and same piece as the original one a (26\% of borrowers renew at least once with a given pawn).
-This contract was standard in the industry.
+The client could make payments at the branch at any time with no penalty for pre-payment.
+Under this status quo contract, there are no payment reminders or any other kind of interim contact between the lender and the borrower.
+If the client returns to pay the principal plus the accumulated interest within 105 days, she recovers her pawn, otherwise the pawnbroker keeps the piece \textit{and} any payments already made.
+Before the contract expires, the client had the right to renew for another 3 months by going to the pawnshop, paying the accumulated interest, and signing a new contract with exactly the same terms and the same piece as the original contract (38\% of borrowers renew at least once with a given pawn).
+This contract is standard in the industry.
 Pawnshops make money in three ways: by reselling the jewelry left as collateral on defaulted loans, by charging interest on non-defaulted loans, and by keeping the payments made on defaulted loans.
@@
 \paragraph{Borrowers.} The clients that pawned understood these terms well (as we verified in interviews).\footnote{87\% of clients report in our survey that they have pawned before.} These clients have little or no access to other types of loans and they value the convenience of pawn borrowing.
-This population of pawn borrowers is economically vulnerable:  30\% of them could not pay either water, electricity \& gas or rent in the past 6 months; 87\% said they are pawning because of an emergency, and only 13\% stated it was to use in a `non-urgent expense'.
-When asked why they are pawning this piece, 5\% responded `lost a family member', `a medical emergency' (11\%), or `an urgent expense' (71\%).
+This population of pawn borrowers is economically vulnerable:  30\% of them could not pay either water, electricity \& gas or rent in the past 6 months; 89\% said they are pawning because of an emergency, and only 12\% stated it was to use in a ``non-urgent expense''.
+When asked why they are pawning this piece, 5\% responded ``lost a family member'', ``a medical emergency'' (11\%), or ``an urgent expense'' (72\%).
 
@@
 One potential explanation for high default is that clients are really just knowingly selling their gold piece through a pawn contract on which they intend to default.
-This appears unlikely for several reasons: (a) clients can easily sell the gold and obtain a higher amount of instant cash at gold buying stores located close to almost all our pawnshop branches (see Figure \ref{GoldBuyers}), (b) the reported subjective value of the pawn is larger than the loan size for 86\% of clients, (c) among those that lose their pawn, 48\% paid a positive amount towards its recovery and on average paid 42\% of the value of their loan (see Figure \ref{proxy_naive} in Appendix) --- this can only be rationalized if they expected to recover their pawn, and (d) 74\% of borrowers report a 100\% probability of repaying their loan (and 98\% at least a 50\% chance of repaying) in our baseline survey at the time they take the loan.
-Note that high default could be detrimental from the lender's point of view, since it may reduce the likelihood that the client becomes a return customer.
+This appears unlikely for several reasons: (a) clients can easily sell the gold and obtain a higher amount of instant cash at gold-buying stores located close to almost all our pawnshop branches (see Figure \ref{GoldBuyers}), (b) the reported subjective value of the pawn is larger than the appraised value for 83\% of clients, (c) among those that lose their pawn, 29\% paid a positive amount towards its recovery and on average paid 42\% of the value of their loan (see Figure \ref{proxy_naive} in Appendix) --- this can only be rationalized if they expected to recover their pawn, and (d) 72\% of borrowers report a 100\% probability of repaying their loan (and 98\% at least a 50\% chance of repaying) in our baseline survey at the time they take the loan.
+%Note that high default could be detrimental from the lender's point of view, since it may reduce the likelihood that the client becomes a return customer.
 %Lender P was in fact explicitly interested in partnering with us to investigate how to reduce loan default, customer satisfaction, and repeat borrowing.
@@
 
-Borrowers' financial costs are composed of two main categories: the cost of losing their collateral, and the interest incurred during the life of the loan.
-For each given loan we observe if the client lost her pawn ($\mathds{1}(\text{Default}_i)$) and when.
-If the client has renewed her loan several times such that the loan is continuing but has not defaulted, we pursue the strategy of coding default as zero (this approach is conservative in our context in that it does not lead the reduction in repayment time to translate mechanically into a drop in default).
-In our data 13\% of experimental loans are continuing (i.e.
+Borrowers' financial costs are composed of two main categories: the cost of losing their collateral, and the interest and fees incurred during the life of the loan.
+For each given loan we observe if the client lost her pawn ($\mathds{1}(\text{Default}_i)$).
+If a loan has been rolled over and is still outstanding, we consider it to be non-defaulted.
+This approach is conservative in our context (biases treatment effects towards zero), as we show in detail in Section \ref{Experiment}.
+In our data 13\% of experimental loans are ongoing (i.e.
 censored) when the data period ends.
-Regarding interest, the administrative data classifies payments made in three types according to their payment allocation rules: payments to principal $P^c$, payments on generated interests $P^i$, and payments on penalty fees $P^f$.
+Regarding interest, our administrative data classifies payments made in three types according to their payment allocation rules: payments to principal $P^C$, payments on generated interests $P^I$, and payments on penalty fees $P^F$.
 We observe each and every payment made under each category, its amount and date.
@@
 We define a borrower's financial cost as the total monetary outflow --in cash or pawn value-- from the borrower to the lender.
-This includes all payments the borrower made toward interest and fees, but also the net difference of the appraised value of the loan and the loan amount (VLD) when there is default.
+This includes all payments the borrower made toward interest and fees, but also the net difference between the appraised value of the pawn and the loan amount (Value-Loan) in the event of default.
 When there is no default the borrower gets her pawn back and there is no loss of value for the borrower.
@@
 Note however that when she does not default payments to capital are not an actual outflow, as they sum up to the value of the loan the lender disbursed in the first place.
-The formula for financial cost for person $i$ is thus as follows\footnote{We can also define the financial cost formula as:
+The formula for financial cost for person $i$ is thus as follows: %\footnote{We alternatively defined financial cost as $\text{Financial Cost}_i = \sum_t P^I_{it} + \sum_t P^F_{it} + \sum_t P^C_{it} + \mathds{1}(\text{Default}_i) \times (\text{Value}_i)-\text{Loan}_i$, and obtained similar results.}:
+
 \begin{align*}
-    \text{Financial Cost}_i =&  \underbrace{\sum_t P^i_{it}}_{\text{Payments to interest}} + \underbrace{\sum_t P^f_{it}}_{\text{Payments of fees}}    + \underbrace{\sum_t P^c_{it}}_{\text{Payments to capital}} + \underbrace{\mathds{1}(\text{Default}_i) \times (\text{Appraised value}_i}_{\text{Cost of losing pawn}})-\text{Loan amount}_i
+    \text{Financial Cost}_i =&  \sum_t P^I_{it} +\sum_t P^F_{it}  
+     + \mathds{1}(\text{Default}_i) \times (\text{Value}_i-\text{Loan}_i + \sum_t P^c_{it})
 \end{align*}
-and our results will be equivalent if using this definition instead.
-}:
+
+\noindent where $t$ indexes days, and $\mathds{1}(\text{Default}_i)$ is an indicator function for defaulting.
+Because the period of the loan is only 90 days we do not apply discounting in calculating costs.
+In robustness checks reported below we show that our results are virtually unchanged when applying a wide range of time discounting factors.
+
+We consider the above to be an accurate measure of financial cost in pesos.
+However, we also report results incorporating two non-financial costs: (i) using the subjective value of the pawn reported by the borrower in place of its appraised gold value, and (ii) adding a measure of travel expenses and the opportunity cost of time, as clients have to go to the branch in order to make payments.
+
+As a second measure of cost we calculate the Annual Percentage Rate (APR) in order to express the cost as a percentage of the loan, per year, inclusive of default costs.\footnote{Loan term takes into account the entire loan period, including extensions of the loan through refinancing.} The standard definition is given in the following formula:
 
 \begin{align*}
-    \text{Financial Cost}_i =&  \underbrace{\sum_t P^i_{it}}_{\text{Payments to interest}} + \underbrace{\sum_t P^f_{it}}_{\text{Payments of fees}}   \\
-    &\quad\qquad + \underbrace{\mathds{1}(\text{Default}_i) \times (\text{Val-Loan Difference}_i}_{\text{Cost of losing pawn}} + \underbrace{\sum_t P^c_{it}}_{\text{Payments to capital}})
+    (\text{APR})_i =&\left( 1 + \frac{\frac{\text{Financial Cost}_i}{\text{Loan}_i}}{\text{loan term}_i}\right)^{\text{loan term}_i}-1 
 \end{align*}
 
-\noindent where $t$ indexes days, and $\mathds{1}(\text{Default}_i)$ is an indicator function for defaulting.
-Because the period of the loan is only 90 days we do not use discounting in calculating costs.
-In robustness checks we show that results are virtually unchanged when applying a wide range of time discounting factors.
-
-We believe the above measure captures financial cost in pesos accurately.
-However, we will also report results incorporating two costs that are not financial: (i) using the subjective value of the pawn reported by the borrower in place of its appraised gold value, and (ii) adding a measure of travel expenses and the opportunity cost of time, as clients have to go to the branch in order to make payments.
-
-As a second measure of cost we calculate the Annual Percentage Rate (APR) in order to express the cost as a percentage of the loan, per year, inclusive of default costs.\footnote{Loan term takes into account the entire loan period, including extensions of the loan through refinancing.} The standard definition is given in the following formula:
-
-\begin{align*}
-    (\text{APR})_i =&\left( 1 + \frac{\frac{\text{Financial Cost}_i}{\text{Loan Value}_i}}{\text{loan term}_i}\right)^{\text{loan term}_i}-1 
-\end{align*}
-
 \vspace{.1in}
 
-Figure \ref{fc_hist}(a) plots a histogram of this financial cost in pesos for all loans in the experiment, distinguishing by whether we observed they defaulted (43\%), recovered their pawn (44\%), or whether they are censored in our data (13\%).
-The first thing to note is that those that default incur in higher costs; part of this is mechanical as losing their collateral is part of the cost.
-The second thing to note is that those that are not closed at the end of our sample period have already incurred in substantial financial cost, even though they have not defaulted yet.
-Panel (b) shows the APR; most of the APR costs come from clients that do not recover their pawn.
+Figure \ref{fc_hist}(a) plots a histogram of this financial cost in pesos for all loans in the experiment, stratified by whether we observed that they ended in default or recovery of the pawn.
+Figure \ref{fc_hist}(b) shows the analogous histogram for the APR.
+%defaulted (44\%), recovered their pawn (43\%), or whether they are censored in our data (13\%). 
+We see that borrowers who default incur higher costs; part of this is mechanical as losing their collateral is part of the cost.
+Most of the APR costs indeed come from clients who do not recover their pawn.
+%The second thing to note is that those that are not closed at the end of our sample period have already incurred substantial financial cost, even though they have not defaulted yet.
+
 %Of those who renew, 83\% lose the pawn.
@@
 \noindent \textbf{The Commitment Contract.} For the purpose of the experiment we designed a new contract that is identical to the status quo contract except that, informed by the design of micro-lending contracts, it enhances the regularity and salience of payments as a way to encourage repayment \citep{morduch1999microfinance, bauer2012behavioral}.
-It has the same interest rate (7\% \textit{per month}) which accumulates daily on outstanding debt, it has the same loan size/collateral ratio (70\%), it has the same loan term (90 days, and a grace period of 15 days), and the gold pawn gets appraised in the same way by the same appraisers.
-The Commitment contract however requires the client to make regular monthly payments for the duration of the contract, with the principal and interest payments split evenly across the three months of the contract (day 30, 60 and 90 after loan disbursement).
+It has the same interest rate (7\% \textit{per month}) which accumulates daily on outstanding debt, the same loan size/collateral ratio (70\%), and the same loan term (90 days, and a grace period of 15 days).
+Borrowers' gold pawns are appraised in the same way by the same appraisers under both the new and status quo contracts.
+The commitment contract however requires the client to make regular monthly payments for the duration of the contract, with the principal and interest payments split evenly across the three months of the contract (day 30, 60 and 90 after loan disbursement).
 The importance of this monthly payment was made salient in the contract and payment receipts (see Figure \ref{PaperSlip}), and by the levying of a nominal fee (2\% of minimum due) on individuals who fell behind in their payments.
-The idea that the fee itself is not driving the treatment is reinforced later in the paper where we show financial benefits many times larger than the fee, as well as treatment effects even on those who would fail to recover pawns and hence not pay the fee.
-Transportation cost to go to the branch to pay is on the same order of magnitude as the fee on average.
+%\textcolor{red}{The idea that the fee itself is not driving the treatment is reinforced later in the paper where we show financial benefits many times larger than the fee, as well as treatment effects even on those who would fail to recover pawns and hence not pay the fee.}
+The fee was modest and intended to make the payment deadlines salient. As a benchmark, the transportation cost to visit the branch to make a payment is comparable to the fee, on average.
 %\footnote{%The lender was worried that if the fee was large, forgetting to pay could make the pawn unrecoverable. 
@@
 %We also experimented with a contract where there was no pecuniary fee for paying late but where we clients made a personal promise to pay monthly.}
+
 To elicit demand for the monthly payment contract, we include an arm that allows borrowers to opt into this contract if they choose.
-The existence of both a non-optional ``forcing'' arm, and a choice arm in our design is key to estimate a battery of treatment effects above an average treatment effect under fairly mild assumptions.
+The existence of both a non-optional ``forcing'' arm, and a choice arm in our design is key to estimating a battery of treatment effects above an average treatment effect under fairly mild assumptions.
+We next describe the three experimental arms in more detail.
 
@@
 Each day a computer randomly assigned which types of contracts were on offer that day in the branch, and the IT system would only offer these.
-We have 3 different experimental arms\footnote{The experiment included other arms that involved no fee penalties and did not emphasize the structure of payments.
+We have 3 different experimental arms\footnote{The experiment included other independent arms that involved no fee penalties and did not emphasize the structure of payments.
 These are being analyzed in a separate paper.}
@@
 \vspace{.2in}
-\noindent \textbf{Randomization.}  Starting September 6, 2012, we implemented the experiment in 6 branches of Lender $P$.
+\noindent \textbf{Randomization.}  We implemented the experiment in 6 branches of Lender $P$ beginning on September 6, 2012.
 The branches were selected by Lender $P$ to be dispersed across Mexico City and have varying sizes.
-In four of them the experiment ran for 107 days, and in 2 of them we ran it for a shorter time to economize on data collection costs once we realized we would not be constrained by sample size.
+In four of them the experiment ran for 102 days, and in 2 of them we ran it for a shorter time to economize on data collection costs once we realized we would not be constrained by sample size.
 %Thus we eliminated {the smallest} ones.
-Branches are more than 5 km apart from each other, and there is little substitution among them; only 1\% of consumers appear in more than one of our branches.
-
-Branch personnel did not know which treatment would happen on which day and were blind to the objective of the intervention.
-They were told that there were 3 different ``types of contract-days'', that the system chose randomly which applied on any given date, and that it could happen for instance that two consecutive dates had the same contract.
+Branches are more than 5 km apart from each other, and there is no substitution among them; none of the consumers appear in more than one of our branches.
+
+Branch personnel did not know which treatment would be assigned to each day and were blind to the objective of the intervention.
+They were told that there were 3 different ``types of contract-days'', that the system chose randomly for any given date, and that it could happen for instance that two or more consecutive dates had the same contract.
 They were also told that this way of operating was in place in several of Lender P's branches (they did not know which ones), and that it would be in place for several months.
@@
 Some clients pawned more than one time during the duration of the experiment, with 14\% pawning 2 times and 8\% more than 2 times.
-To have a clean comparison we are considering only the first pawn in the experiment.
+To have a clean comparison we are considering only the first pawn conducted during the experimental window.
 It is also the case that 30\% of those first pawns involve more than 1 loan, as 2 or more pieces of gold were submitted.
 We treat each of them as separate loans.
-
-\paragraph{Timeline.} Figure \ref{exp_description} shows the timeline when the experiment happens and also the length of time for which we observe payments.
-For contracts in the first week, we observe up to 338 subsequent days, while for contracts in the last week we observe up to 235 days.
-Figure \ref{exp_description} also illustrates the number branch-days per arm, the number of contracts, and the number of surveys.
+In the appendix we show that our results are robust to this analysis choice.
+
+\paragraph{Timeline.} Figure \ref{exp_description} shows the experimental timeline along with the length of time for which we observe payments.
+For loans made in the first week of the experiment, we observe up to 338 subsequent days of loan information; for loans made in the last week we observe up to 235 days.
+Figure \ref{exp_description} also illustrates the number branch-days per arm, the number of loans, and the number of surveys.
 %Not every contract has a survey for several reasons, we have survey information for \hl{XXX\%} of them.
@@
 
-\paragraph{Explanation.} Since we are interested in measuring the effect of different contract terms on client behavior, it is important that clients understand them.
-To ensure this, we built two `check-points'.
-First, two enumerators were present in each branch for the whole day during the duration of our experiment to explain the contract terms to clients.
-One of the aspects emphasized was that the frequent payment contract involved the commitment to pay a third of the outstanding amount \underline{each month}, and the nature of the fees associated with the Commitment arm.
-Figure \ref{ExplanatoryMaterial} translates a piece of the materials we used to explain the contracts.
-The explanation took about 3-5 minutes and was pursued until the client said she understood the contract terms.
-Enumerators then asked clients to explain back the contract terms and corrected any misunderstandings.
-The second check-point was that before the clients signed the contract, the appraiser made them read the ``Contract Terms Summary'' sheet shown in Figure \ref{PaperSlip}.
-It was a piece of paper given to clients after their piece had been appraised and the size of the loan determined, but before they signed their contract.
-The appraiser read it and asked the client to sign it as proof of understating.
+\paragraph{Explanation.} Since we are interested in measuring the effect of different contract terms on client behavior, it is important that clients understand these terms.
+To ensure this, we built two ``check-points'' as follows.
+Two enumerators were present in each branch for the whole day during the duration of our experiment.
+At the first checking, these enumerators explained the contract terms to clients, emphasizing that the frequent payment contract involved the commitment to pay a third of the outstanding amount \underline{each month}, along with the nature of the fees associated with the Commitment arm.
+Figure \ref{ExplanatoryMaterial} presents an excerpt of the materials we used to explain the contracts, translated into English.
+The explanation took about 3-5 minutes and continued until the client said she understood the contract terms.
+Enumerators then asked clients to explain the contract back to them before correcting any misunderstandings.
+At the second check-point the appraiser made clients read the ``Contract Terms Summary'' sheet shown in Figure \ref{PaperSlip} before they signed the contract.
+This summary was a piece of paper given to clients after their piece had been appraised and the size of the loan determined, but before they signed their contract.
+The appraiser read it aloud and then asked the client to sign it as proof of understating.
 %The sheet clearly indicates that this contract is a monthly payment one (numeral 1), that there is a penalty of 2\% for paying late (numeral 2), and the 3 payment dates (numeral 3).
@@
 
-\paragraph{Administrative data.} The study exploits two types of data: administrative data from the lender, and a short survey we implemented.
+\paragraph{Administrative data.} The study exploits two types of data: administrative data from the lender, and a short survey that we implemented.
 The administrative data contains a unique identifier for each client, an identifier for the piece she is pawning, and the transactions relating to that piece.
-These transactions include the value of the item as assessed by the appraiser, the amount of money loaned (70\% of the value), the date of the pawn transaction, and the type of contract for that pawn.
+These transactions include the value of the item as assessed by the appraiser, the amount of money loaned (70\% of the item's value), the date of the pawn transaction, and the type of contract for that pawn: commitment or status quo.
 Within the period of the loan, we followed each transaction related to that piece in the administrative data: when payments were made and for what amounts, whether there was default (i.e.\ the client lost her pawn), and whether any late-payment fees were imposed.
 After the experimental loan, we are able to track subsequent behavior and to see whether that borrower took a subsequent loan.
-We have this information for all the pawns that occurred in the experiment's 6 branches between August 2, 2012 and August 13, 2013, this includes all the pawns under our experiment but also those that happened 1 month before it started and up to 8 months after it ended.
+We have this information for all the pawns that occurred in the experiment's 6 branches between August 2, 2012 and August 13, 2013.
+This includes all the pawns that took place during our experiment along with those that one month before and eight months after our experiment.
 Figure \ref{exp_description} shows the design and timing of the experiment, along with the sample sizes in each arm.
-The experiment comprises 13,446 pawns, and our administrative data cover a total of 23,974 pawns.
-
-\paragraph{Survey data.} In addition, we had a team of enumerators in each branch collect surveys and clearly explain the contract terms to walk-in clients.
-The enumerators were inside the branch and asked clients to complete a 5-minute survey \textit{before} going to the teller window to appraise their piece and before treatment status was known to them.
-The survey was intentionally short to avoid discouraging the potential clients from pawning, but at the same time it aimed to measure the following: demographics, proxies for income/wealth, education, present-biased preferences, experience pawning, if family or friends commonly asked for money, how time consuming and costly it was to come to the branch, the subjective probability of recovering the piece that they intended to pawn, the subjective value of their piece in money terms (how much money they would sell it for), among others.
-We surveyed 10,437 clients, and the survey response rate was 78\% among clients who took loans.\footnote{Appendix \ref{baseline_survey} transcribes the questionnaire in English.} %\footnote{We also surveyed clients before and after the experiment, so our survey covers a larger sample that we are not using in this paper.}.
+The experiment comprises 8,519 pawns while our administrative data covers a total of 26,180 pawns.
+
+\paragraph{Survey data.} An additional team of enumerators stationed in each branch asked clients to complete a 5-minute survey \textit{before} going to the teller window to appraise their piece and before they learned which contracts would be available on that day.
+The survey was intentionally short to avoid discouraging the potential clients from pawning.
+It measured demographics, proxies for income/wealth, education, present-biased preferences, experience pawning, if family or friends commonly asked for money, how time-consuming and costly it was to come to the branch, the subjective probability of recovering the piece that they intended to pawn, the subjective value of their piece in money terms (how much money they would sell it for), among others.
+We surveyed 7,210 clients, and our survey response rate was 78\% among clients who took loans.\footnote{Appendix \ref{baseline_survey} transcribes the questionnaire in English.} %\footnote{We also surveyed clients before and after the experiment, so our survey covers a larger sample that we are not using in this paper.}.
+We only use the survey in Section \ref{Paternalism} of the paper.
 
@@
 \paragraph{Attrition.} There are two main channels through which attrition could complicate the interpretation of our results.
-The first, and more serious, is the possibility that clients might change their pawning decisions in response to the treatment they encounter in a given branch on the day they enter.
+The first, and more serious, is the possibility that clients might change their pawning decisions in response to the treatment they encounter in a given branch on the day they enter the branch.
 If this occurred it would introduce a self-selection dimension which would still reflect the overall impact of a treatment for the lender's portfolio but would no longer deliver \textit{ceteris paribus} effects of treatments on individual borrowers.
@@
 Anecdotally, appraisers told us that they did not think refusals differed across arms, and our enumerators informed us that potential clients rarely left the branch without pawning.
-Lender P also never complained to us that our different treatments were hurting sales.} If the treatments had induced demand-side selection, we would expect to see that the number of pawns successfully conducted differ in a systematic way across arms.
-To test for this, we examine the number of loans given per branch-day, with specific attention to whether the Forced Commitment arm led to a lower number of borrowers per day.
+Lender P also never complained to us that our different treatments were hurting sales.}
+
+If the treatments had induced demand-side selection, we would expect to see that the number of pawns successfully conducted differ in a systematic way across arms.
+That is, if potential borrowers disliked being forced into a commitment contract, we would expect a lower number of pawns on branch days where only the commitment contract is available compared to control days.
+Table \ref{attrition_table} shows that this is not the case.
+There is no difference at all between the Control and Forced Commitment arm in terms of the number of pawns per branch-day.
+Although we cannot reject equality across the three arms (p-value=0.21), the Choice arm appears to have a somewhat larger number of borrowers than the Control and Forced arms.\footnote{p-value=0.23 and 0.12 respectively.} This seems to be due to sampling variability.
+The differences across arms are smaller when we look at medians, or when we look at the number of borrowers pawning (some borrowers pawn more than one piece).
+Figure \ref{boxplot_attrition} shows that full distribution of loans per day is very similar across treatment arms.
+The only noticeable difference is that the choice arm has a few more positive outliers.\footnote{If we winzorize at the 90th percentile, the mean number of branch-day pawns identical across arms.}
+
+The bottom panel of Table \ref{attrition_table} shows balance in a more focused way, given that the surveys were conducted prior to the revelation of treatment status.
+We find that in no arm did more than three percent of individuals who responded to the survey go on to refuse loans.
+That is, the overwhelming marjority of potential borrowers did not leave the branch after learning which contract was on offer.
+Moreover, the extremely small fraction that did leave is balanced across arms.
+Therefore it appears that the treatments have not induced any endogenous shifts in the composition of borrowers.
+This is consistent with the findings of Table \ref{SS}.
+% To test for this, we examine the number of loans given per branch-day, with specific attention to whether the Forced Commitment arm led to a lower number of borrowers per day.
 The first row of Table \ref{attrition_table} shows there is no difference between the Control and Forced Commitment arm in terms of the number of pawns per branch-day.\footnote{The Choice arm appears to have a somewhat larger number of borrowers than the Control arm (p-value=0.06), but we cannot reject equality with the Forced Commitment arm (p-value=0.41), or across all arms (p-value=0.16).}  The second row makes the same point in a more focused way, given that the surveys were conducted prior to the revelation of treatment status.
@@
 Therefore it appears that the treatments have not induced any endogenous shifts in the composition of borrowers.
-
-A less critical form of attrition would be a differential refusal to answer the survey questions.
-The survey was done before treatment status was revealed, and we observe loan outcomes regardless of whether the survey was conducted.
-Our core experimental estimates do not use the survey data as covariates, but the Random Forest analysis in Section \ref{Paternalism} is restricted to the subset of borrowers who answered at least some survey questions.
-The bottom row of Table \ref{attrition_table} shows that the survey response rate is broadly similar across arms (about 77 percent).
+A less critical form of attrition is differential refusal to answer the survey questions.
+The survey was conducted before treatment status was revealed, and we observe loan outcomes regardless of whether the survey was conducted.
+Our core experimental estimates do not use the survey data as covariates, but the analysis in Section \ref{Paternalism} is restricted to the subset of borrowers who answered at least some survey questions.
+The bottom row of Table \ref{attrition_table} shows that the survey response rate is broadly similar across arms (about 78 percent).
 %We can also examine differences in the fraction of borrowers who do respond to the survey and then do not end up taking a loan subsequent to completing the survey, we find that the share is close to 100\% as is the fraction of those 97\% across arms (p-value=0.62).
@@
 A more subtle form of sample selection could arise if the treatments induce borrowers to re-pawn in different ways, especially given that their treatment status on subsequent loan/days may not be the same as that initially assigned.
-To handle this issue our analysis uses only the first loan taken by each individual during the experimental window.
+To address this issue our analysis uses only the first loan taken by each borrower during the experimental window.
 
@@
 
-\paragraph{Balance.} Table \ref{SS} presents summary statistics for the sample of actual borrowers across arms, and illustrates that randomization worked to achieve balance across the experimental arms.
+\paragraph{Balance.} Table \ref{SS} presents summary statistics for the sample of actual borrowers across arms, showing that our randomization succeeded in achieving balance across the experimental arms.
 Panel A uses administrative data for the universe of borrowers in each arm, and shows that loan balances and the days on the week on which individuals pawned are comparable across arms.
@@
 Panel B of Table \ref{SS} reports summary statistics across arms from our survey data.
-73\% of clients are women, with an average age of 43 years; 66\% of them have completed high school or more, and 90\% have pawned before, so that our sample has mostly experienced borrowers.
-Finally, the subjective probability of recovery is close to 93\% on average, which makes a stark contrast to the actual rate of recovery of 43\%; borrowers are highly overconfident on average.
+Among the 78\% of borrowers who completed our survey, 73\% of clients are women, the average age is 43 years, 66\% have completed at least a high school education, and 87\% have pawned before, suggesting that our sample largely consists of experienced borrowers.
+Finally, borrowers' subjective probability of recovering their pawn is close to 92\% on average, in stark contrast to the \emph{actual} recovery rate of 43\%; borrowers are highly overconfident on average.
 The average subjective value they report for the items they pawn is 4084 MXN, much larger than the average appraised gold value of 3238 MXN.
@@
 Because our standard errors are clustered at the branch-day level, they automatically account for any dependence in error terms arising from multiple pawns by the same client on her first visit.}.
-Given perfect compliance in the former, the coefficients $\beta^F$ is the ATE of the Forced arm and $\beta^C$ is the ITT of the Choice arm on the outcome variable $y_{ij}$.
-%\footnote{Note that $\beta^C$ can be viewed in two ways: as the the ATE of \emph{offering clients a choice} between the status quo and commitment contract or as the intent-to-treat effect of the commitment contract \emph{itself}.
+Given full compliance in the Forced arm, the coefficient $\beta^F$ is the ATE of forced commitment while $\beta^C$ is the ITT of commitment in the Choice arm on the outcome variable $y_{ij}$.
+%\footnote{Note that $\beta^C$ can be viewed in two ways: as the ATE of \emph{offering clients a choice} between the status quo and commitment contract or as the intent-to-treat effect of the commitment contract \emph{itself}.
 Here we adopt the former interpretation; below we use the latter to consider the relevance of selection-on-gains.}
 Our two primary outcome variables are financial cost in pesos and Annual Percentage Rate (APR), as defined in Section \ref{costs}. 
-Results for these outcomes appear in columns (1) and (6) of Table \ref{main_impact_table}.
+Results for these outcomes appear in columns (1) and (7) of Table \ref{main_impact_table}.
 The remaining columns decompose the financial cost and APR outcomes into their components: interest payments (col 2), payment towards any fees incurred (col 3), payments toward the principal (col 4).
@@
 This means that some loans extend for more than 3 months.
-We consider the entire flow of cost from the duration of our sample.}
+We consider the entire flow of cost for the duration of our sample.}
 
@@
 The Forced Commitment arm yields large and significant decreases in the cost of loans to clients, as measured either by financial cost or APR.
-Despite causing an increase in fees, the Forced arm leads to a decrease of 379 pesos in the costs of borrowing (out of a group mean of 1851 in the status quo), equivalent to 20\% reduction as a fraction of mean cost.
-These cost savings arise from a 6.5 percentage point (pp) decrease in the probability of default (out of a baseline mean of 44pp,  implying cost savings of 254 pesos), and also from lower interest payments, since as we will document the treatment is effective at speeding up payments, with the benefit that the interest rate applies to a smaller principal.
+Despite causing an increase in fees, the Forced arm leads to a decrease of 204 pesos in the costs of borrowing (out of a group mean of 942 in the status quo), equivalent to 22\% reduction as a fraction of mean cost.
+These cost savings arise from a 6.6 percentage point (pp) decrease in the probability of default (out of a baseline mean of 44pp,  implying cost savings of 79 pesos), and also from lower interest payments since, as we will document below, the commitment contract speeds up payments so the interest rate applies to a smaller principal.
 This translates into a large reduction in APR.
-A credit product that has an effective average APR of 184\% in the status quo arm (inclusive of default) is reduced to a cost of 150\% through the imposition of a more regularized payment structure.
-
-In contrast, to the impressive effectiveness of the Forced commitment arm, the Choice arm fails to deliver significant changes in any measure, with the exception of an increase in fees, for which we are highly powered since this outcome is zero for every control observation.
+A credit product that has an effective average APR of 57\% in the status quo arm (inclusive of default) is reduced to a cost of 46\% through the imposition of a more regularized payment structure.
+This is in stark contrast to \cite{Pande} for instance.
+
+In contrast, to the impressive effectiveness of the Forced commitment arm, the Choice arm fails to deliver significant changes in any measure, with the exception of an increase in fees, for which we are highly powered, since this outcome is zero for every control observation.
 Giving borrowers the choice of contract did not decrease financial cost, whereas forcing them into a structured payment contract dramatically reduced it.
-As we explore later in the paper, the null effect of the Choice arm arises because few people had demand for it, with 89\% choosing the less effective status-quo contract.
-
-\paragraph{Intermediate outcomes.} To shed light on the mechanisms behind the ATEs discussed above, Table \ref{mechanisms} shows how treatment affects a number of intermediate outcomes.
+As we explore later in the paper, the null effect of the Choice arm arises because few borrowers demanded commitment (consistent with \cite{Ashraf}, \cite{Gine}, \cite{Ted}, \cite{Royer}, \cite{Sprenger}), with 89\% choosing the less effective status-quo contract.
+
+\paragraph{Intermediate outcomes.} To shed light on the mechanisms behind the ATEs discussed above, Table \ref{mechanisms} shows how commitment affects a number of intermediate outcomes.
 One can group the types of intermediate outcomes into two categories: measures of the speed of pawn recovery, and measures of the decision of when to default.
 While the first payment for borrowers in the status-quo contract occurs on average only on day 82 (on a 90 days contract), borrowers in the forced commitment arm start paying 13.8 days earlier on average (col 1).
-Not only do they start paying earlier, the first payment is also 7.9\% larger (col 2), and a larger fraction of 7.9\% actually pay in full and recover their pawn in the first payment , compared to 30\% in the status quo contract (col 3).
+Not only do they start paying earlier, the first payment is also 7.9\% larger (col 2), and a larger fraction of 9.7\% actually pay in full and recover their pawn in the first payment, compared to 30\% in the status quo contract (col 3).
 The resolution of the loan (either by payment or default) is shortened by 27.9 days (col 4), and conditional on recovery (an endogenous control) by 17.9 days (col 5).
@@
 A very undesirable outcome from the borrower's perspective is to pay towards the loan without paying in full, i.e.
-defaulting on the loan.
+defaulting on the loan while still making some payments.
 In this case, they lose both the collateral and any payments made toward recovery.
-One could be concerned that by encouraging them to pay monthly, more borrowers could end up in this dire scenario in the Forced commitment contract.
+One could be concerned that by encouraging them to pay monthly, more borrowers might end up in this dire scenario in the Forced commitment contract.
 Column 6 shows this is not the case.
 On the contrary, 7 percentage points fewer borrowers end up in this situation, compared to 12 percent in the status quo contract.
-Conditional on defaulting those assigned to the Forced commitment contract have paid 3.9\% less of their loan (col 7), and 14 percentage higher proportion of borrowers pay zero conditional on defaulting, an outcome analogous to selling their pawn (col 8).
-One interpretation of these results is that the Forced commitment contract forces borrowers to think earlier about whether they will indeed be able to eventually recover their pawn, and separates borrowers into those ``selling'' their pawn and those recovering it, reducing the share of undecided borrowers that end up paying interest and end up losing the pawn anyway.
-This mechanism may also help to explain why the Forced commitment contract does not increase the number of visits to the branch to pay (col 10): those recovering their pawn visit more, but those defaulting have 0.19 fewer visits (col 11).
-Figure \ref{hist_payments} plots the histogram of the timing of payments in each arm, and shows that the commitment does appear to bind in that it generates a highly regular pattern of payments at 30, 60, and 90 days after the loan is taken.
-Finally, observe that Column 9 shows that treatment effects are concentrated in the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery.
-
-\paragraph{Other costs.} We have shown that forcing borrowers to take the monthly payment contract significantly reduces financial cost.
-Although the paper focuses on financial cost, we consider three additional costs here.
-First, we include the cost of going to the branch.
+Conditional on defaulting those assigned to the Forced commitment contract have paid 4.1\% less of their loan (col 7), and a 14 percent higher proportion of borrowers pay zero conditional on defaulting, an outcome analogous to ``selling their pawn'' (col 8).
+One interpretation of this bifurcation is that the Forced commitment contract forces borrowers to think earlier about whether they will indeed be able to eventually recover their pawn, and separates borrowers into those ``selling'' their pawn and those recovering it, reducing the share of undecided borrowers that end up paying interest and end up losing the pawn anyway.
+This mechanism may also help to explain why the Forced commitment contract does not increase the number of visits to the branch to pay (col 10): those recovering their pawn visit more, but those defaulting have 0.20 fewer visits (col 11).\footnote{Figure \ref{hist_payments} plots the histogram of the timing of payments in each arm, and shows that commitment does appear to bind in that it generates a highly regular pattern of payments at 30, 60, and 90 days after the loan is taken.} Finally, Column 9 shows that treatment effects are concentrated in the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery.
+
+\paragraph{Other costs.} We have shown that forcing borrowers to take the monthly payment contract significantly reduces their financial costs.
+Although the paper focuses on financial costs, we consider three additional costs here.
+First, we include the cost of visiting the branch to make a payment.
 This includes the self-reported transport cost (most use public transport), as well as the opportunity cost of time.
 To err on the conservative side, we subtract a whole day's minimum wage the day of the visit, instead of just the wage corresponding to a couple of hours.
-Second, we consider a rough proxy of the value of liquidity they lose by paying earlier.
-To do this we add the interest costs on to the payments in the Forcing and recompute treatment effects with these payments compounding daily (as if they had to borrow in order to make the more rapid payments).
+Second, we consider a rough proxy of the value of liquidity that borrowers lose by paying sooner.
+To do this we add the interest costs on to the payments in the forced commitment arm and recompute treatment effects with these payments compounding daily (as if they had to borrow in order to make the more rapid payments).
 Thirdly, so far we have valued the collateral at the gold value appraised by the lender, but the piece may be worth more to the borrower than its gold value.
@@
 Columns (3) and (8) adjust for self-reported transport costs per visit plus an entire day's wage, both multiplied by the number of visits that each individual made.\footnote{For clients who did not complete the individual survey, we adjust using the mean self-reported transport cost among respondents of the respective branch.} Columns (4) and (9) adjust to consider the liquidity cost.
-Finally columns (5) and (10) include all three changes together.
+Finally, columns (5) and (10) include all three changes together.
 The main takeaway from the table is that results are quite robust to including a much expanded measure of costs.
@@
 Table \ref{repeat_loans} explores the effects of treatment on future pawning behavior.
-Column (1) shows that participants assigned to the the forced arm are 6.7\% more likely to be repeat clients later.
+Column (1) shows that participants assigned to the forced arm are 6.3\% more likely to be repeat clients later.
 %Those in the choice arm are 4\% more likely to pawn again and is not statistically distinct from zero.
@@
 Column 4 only considers new loans which use different collateral from that of the initial one.
-We do this to foreclose the explanation that those in the Forced arm repeat more because they are more likely to have collateral, as they recover the collateral of the first loan more often.
+We do this to foreclose the explanation that those in the Forced arm, being more liquidity-constraint, return to pawn a second pawn to be able to pay the monthly payments of their first loan.
+However, we cannot reject a zero effect on pawning a different collateral.
 Column 5 focuses on the (endogenous) subsample of those recovering their pawn in both arms of the experiment.
-This means that both have the pawn to re-pawn and also that the liquidity demands from the monthly contract are not longer binding as the contract has been closed.
+This means that \textit{both} arms have recovered their pawn and could re-pawn if they so wish, and also that the liquidity demands from the monthly contract are \textit{no longer} there as the contract has been closed.
 We find that the difference between the Forcing contract and the status quo is even larger in this subsample, with the former having 11pp higher likelihood of being a repeat client during our sample period.
+
+%Moreover, in the (endogenous) subsample of those that recover, in Column 6 we do find that they return with a different collateral, as they recover the collateral of the first loan more often.
 
@@
 Overall, 13\% of all experimental loans are censored, meaning that they neither default nor repay within the observation window.
-In the prior analysis we handle this issue by using outcomes such as `did not default' which are defined even when we do not observe the completion of the loan, and only considering costs that we observe directly.
+In the prior analysis we handle this issue by using outcomes such as ``did not default'', which are well-defined even when we do not observe the completion of the loan, and by only considering costs that we observe directly.
 We have also showed, however, that one effect of the forcing arm is to accelerate repayment, meaning that it is less likely for loans in this arm to be censored.
@@
 Two features of these graphs are salient for our analysis.
-The first is the extent to which loan outcomes are observed more quickly in the forcing arm.
-This is primarily due to the the substantially higher rate of repayment of Forced Commitment loans at 120 days (15 pp higher than the other arms).
+The first is the extent to which loan outcomes are observed more quickly in the forced commitment arm.
+This is primarily due to the substantially higher rate of repayment of Forced Commitment loans at 120 days (15 pp higher than the other arms).
 The second is the very low rate at which loans are recovered in any arm after 120 days.
-In the 180 day window after the second rollover period we see a further 10 percent of loans repaid in all arms, but these loans are largely dormant, suggesting that many of the censored loans will in fact be defaulted upon.
-
-The confluence of censoring and a treatment effect on censoring is problematic from an experimental point of view.
-The approach taken so far is a conservative one in that it inherently assumes that all of the loans outstanding at the end of the observation window will be repaid, making it so that the acceleration of payment observed in the Forced arm does not translate mechanically into the treatments decreasing default.
-Given the centrality of this issue to the observed costs, we now delve into it more detail.
-One way of considering the effect that this issue could have on our results is to make extreme assumptions about the outcome of these loans in the treatment and control so as to bound the possible influence of censoring.
-In Table \ref{bounding_censoring} we compare the Forced and Control arms, making the bracketing assumptions about repayment on censored loans.
-Panel A assumes all censored loans are repaid, and Panel D that all default.
-Panel B provides the lower bound for the treatment effect by assuming censored control loans are always repaid and treatment loans never are, and Panel C the upper bound by making the reverse assumption.
-Comfortingly, even with these extreme assumptions the significance on the main treatment effects never flips and treatment effects on financial cost and interests payments remain negative and significant in all scenarios.
-So there appears to be no scope for the censoring issue to overturn our main results.
+In the 180-320 day window loans are largely dormant, suggesting that many of the censored loans will in fact end in default.
+
+The confluence of censoring and a treatment effect on censoring is potentially problematic from an experimental point of view.
+The approach taken so far is a conservative one in that it inherently assumes that all of the loans outstanding at the end of the observation window will be repaid, making it so that the acceleration of payment observed in the Forced arm does not translate mechanically into the that treatment decreasing default.
+Nonetheless, to be certain that this issue is not driving our results we conduct a bounding exercise to understand how large the effects of this problem can possibly be.
+In Table \ref{bounding_censoring} we compare the Forced and Control arms, bounding the censoring issue by reversing assumptions about the outcome of censored loans in the treatment versus the control.
+Panel B provides the lower bound for the treatment effect (closest to zero) by assuming censored control loans are always repaid and treatment loans never are; even in this lower-bound case the treatment effect is cost-reducing and significant at the 1\% significance level and indeed the magnitude of this lower bound estimate is only 6\% closer to zero than our headline result.
 
 Finally, Panel E of this table conducts a logit prediction model that uses all of the available information on loans that were completed to predict the outcome of loans that were not.
-This is a best guess of the outcome on censored loans.
-Using this prediction, we replicate the main experimental results and find that the treatment effect on financial cost increases from -378 (main results) to -525 (censored loans predicted), and the APR from -34\% to -62\%.
-Hence, while the censoring issue does have a substantial influence on the magnitude of our estimated treatment effects, these  checks confirm that a) the core results are robust to censoring, and b) the headline approach that we take to the issue is conservative and is likely understating the true magnitude of impacts.
+This is a ``best guess'' of the outcome on censored loans.
+Using this prediction, we replicate the main experimental results and find that the treatment effect on financial cost increases from -204 (main results) to -264 (censored loans predicted), and the APR from -11\% to -17\%.
+Hence, while the censoring issue does have an effect on the magnitude of our estimated treatment effects, these  checks confirm that (a) the core results are fully robust to censoring, and (b) the headline approach that we take to the issue is conservative and likely understates the true magnitude of impacts.
 
@@
 The borrowers who did not choose commitment could simply be those who don't need it. 
-Indeed, we find strong evidence that the effect of forced commitment varies substantially across individuals in our experiment: \ref{append:chernozhukov} tests and rejects the null hypothesis of homogeneous treatment effects, following the methodology of \cite{chernozhukov2018generic}.
-So the question remains: do the 89\% who do not choose commitment know something about their personal situations that we as researchers do not, or are most people in the choice arm making a costly mistake?
-In this section we present of econometric exercises that shed light on this question, leveraging unique features of our experimental design. 
-Among other results, we show that commitment lowers average financial costs even for the subset of borrowers who would \emph{not} choose to commit voluntarily.
+Indeed, we find strong evidence that the effect of forced commitment varies substantially across individuals in our experiment: Appendix \ref{append:chernozhukov} tests and rejects the null hypothesis of homogeneous treatment effects, following the methodology of \cite{chernozhukov2018generic}.
+So the question remains: do the 89\% who do not choose commitment know something about their personal situations that we as researchers do not, or are most people in the choice arm making a costly financial mistake?
+In this section we present of econometric exercises that sheds light on this question, leveraging unique features of our experimental design. 
+Among other results, we show that commitment would lower average financial costs even for the subset of borrowers who choose \emph{not} to commit voluntarily.
 To simplify the exposition in this and all sections that follow, we re-define all outcome variables so that \emph{beneficial} treatment effects are \emph{positive}.
@@
 If we knew the distribution of individual treatment effects, it would be easy assess how many individuals would win and lose under a policy of universal forced commitment, along with the magnitude of any individual harm.
-Because we can never simultaneously observe the same borrower in both the control and commitment arms, however, the distribution of individual treatment effects cannot be point identified.
+Because we can never simultaneously observe the same borrower in both the control and forced commitment arms, however, the distribution of individual treatment effects cannot be point identified.
 It can, however, be bounded.
@@
 
-Figure \ref{fan_park_bounds} plots the sharp bounds for $F_{\delta}$ based on the APR outcome defined above in Section \ref{costs}.
-Our point estimates of $\underline{F}(0)$ and $\overline{F}_0$ are .03 and .77 respectively, with associated 95\% confidence intervals of [0.025, 0.050] and [0.75, 0.80], which says that at least 23\% of individual borrowers benefit from commitment (and at most 97\%).\footnote{Confidence intervals are constructed using the asymptotic distribution for the bounds.
+Figure \ref{fan_park_bounds} plots the sharp bounds for $F_{\Delta}$ based on the APR outcome.
+Our point estimates of $\underline{F}(0)$ and $\overline{F}(0)$  are 0.03 and 0.77 respectively, with associated 95\% confidence intervals of [0.025, 0.050] and [0.75, 0.80].
+Since we are interested in $\mathbbm{P}(\Delta_i >0) = 1 - F_\Delta(0)$, this means that \textit{at least 23\%} of individual borrowers benefit from commitment (and at most 97\%).\footnote{Confidence intervals are constructed using the asymptotic distribution for the bounds.
 See \cite{fan2010sharp} for details.}
@@
 One such assumption is \emph{rank invariance}, which posits that a person's rank in the distribution of $Y_0$ equals her rank in the distribution of $Y_1$.
-While strong, this assumption or variants of it has appeared in a number of settings in the literature, e.g.\ \cite{chernozhukov2005iv}. 
+While strong, this assumption or variants of it have appeared in a number of settings in the literature, e.g.\ \cite{chernozhukov2005iv}, so we consider it here for purposes of comparison.
 Under rank invariance, the distribution of treatment effects is point identified and given by 
@@
 \]
-where $F_1^{-1}$ and $F_0^{-1}$ are the quantile functions of $Y_1$ and $Y_0$. See figure \ref{te_rankinvariance} in Appendix \ref{App_FOSD}.
-As we show in Appendix \ref{App_FOSD}, $Y_1$ first-order stochastically dominates $Y_0$ in our experiment: every quantile of the distribution of financial cost savings under forced commitment is higher than the corresponding quantile under the control condition, and the same is true for the APR outcome.
-Since this implies that $F^{-1}_1(u) - F^{-1}_0(u)$ is always positive, rank invariance yields an extremely stark conclusion: all borrowers benefit from forced commitment. 
-%\todo[inline]{@Everyone: do we want to plot the distribution of treatment effects under rank invariance and say something more about it? Or just add a snappy sentence to conclude this subsection?}
-
-%An alternative way of presenting the \cite{fan2010sharp} bounds is in terms of quantiles of the distribution of $\Delta$.
-Let $0 < q < 1$, and define $Q_0, Q_1, Q$ to be the quantile functions corresponding to $F_0, F_1$ and $F_\Delta$.\footnote{In other words, $Q_0(q) \equiv \inf \{x | F(x) \geq q\}$ and so on.} Then the sharp bound for $Q_\Delta(q)$ is given by $\underline{Q}(q) \leq Q(q) \leq \overline{Q}(q)$ where
-%\[
-%\overline{Q}(q) \equiv \inf_{u \in [q,1]} [Q_1(u) - Q_0(u - q)], \quad
-%\underline{Q}(q) \equiv \sup_{u\in [0,q]} [Q_1(u) - Q_0(1 + u - q)]
-%\]
-%By substituting $q = 0.11$, these expressions allow us to bound the 11th percentile of the distribution of $\Delta$.
-Under a stylized Roy model in which borrowers with the largest (negative) treatment effects choose commitment, $Q(0.11)$ equals the treatment effect for the borrower at the margin of indifference between choosing commitment.
-%Our point estimates for the lower and upper bounds $\underline{Q}(0.11)$ and $\overline{Q}(0.11)$ are \hl{XXXX} and \hl{XXXX} with corresponding 95\% confidence intervals \hl{XXXX} and \hl{XXXX}.\footnote{Again, confidence intervals are constructed using \hl{XXXX} bootstrap as describe in \cite{fan2010sharp}.}
-%%\todo[inline]{Issac: add the interval for $Q(0.11)$.
-Again, this needs to be without covariates and we need to be careful about the sign convention for our effects.
-Maybe we don't need a second figure with the confidence bands for the whole quantile function.
-Frank: add a sentence or two discussing the results.
-Presumably the aforementioned quantile is indeed negative and fairly large.}
-%Both ways of presenting the bounds yield the same conclusion: at least some borrowers who would benefit from commitment \emph{do not choose it} when offered.
+where $F_1^{-1}$ and $F_0^{-1}$ are the quantile functions of $Y_1$ and $Y_0$. Figure \ref{te_rankinvariance} in Appendix \ref{bounds_FOSD} plots our estimates of $F_\Delta$ under rank invariance.
+For the financial benefit outcome, $Y_1$ first-order stochastically dominates $Y_0$ in our experiment: every quantile of the distribution of financial cost savings under forced commitment is higher than the corresponding quantile under the control condition.
+Since this implies that $F^{-1}_1(u) - F^{-1}_0(u)$ is always positive, rank invariance yields an extremely stark conclusion: all borrowers have positive individual treatment effects of forced commitment.
+For the APR outcome, the results under rank invariance are slightly less stark: we estimate that just under 90\% of borrowers have positive individual treatment effects.
 
@@
 
-Our assumption-free bounds from the preceding section show that more than 24\% of borrowers would benefit from a policy of forced commitment. 
-Intuitively, this seems to suggest that some of the 89\% of borrowers in the choice arm who did \emph{not} choose commitment would have faced lower borrowing costs if they had.
+Our assumption-free bounds from the preceding section show that more than 23\% of borrowers would benefit from a policy of forced commitment. 
+This suggests that some of the 89\% of borrowers in the choice arm who did \emph{not} choose commitment would have faced lower borrowing costs if they had.
 Making this intuition precise, however, requires a careful consideration of the relationship between choice and heterogeneous treatment effects. 
@@
 Moreover, each has testable implications that we fail to reject.
-For details, see \ref{append:exclusion}
-%\todo[inline]{@Frank, do we need to say a bit more about these testable implications or is it too technical? (Enrique)}
+For details, see \ref{append:exclusion} \footnote{As mentioned above, this is a frequently used assumption even if often implicit.
+A significant literature uses schooling compulsory laws to estimate the return and then interprets that schooling in general has this return.
+Fertilizer yields are measured by researchers in experimental plots and then expected to have these returns regardless of whether farmers choose or the government provides these fertilizers.
+We are not the first paper to use this assumption, see \cite{chamberlain2011bayesian}.}
 
@@
 \]
-%The TuT and TOT effects are particularly interesting for understanding the importance of paternalism. 
+The TOT is the causal effect of commitment on borrowers who would voluntarily choose it, while the TUT is the causal effect on borrowers who would not.
 If the TUT is positive, this means that those who did not choose commitment would have experienced better outcomes, \emph{on average}, if they had. 
@@
 If the TOT is statistically distinguishable from and substantially larger than the TUT, this provides empirical support for the relevance of selection-on-gains in real-world decision-making.
-Because our design identifies all three quantities (as shown in Appendix \ref{append:randchoice}), it allows us to test this implication directly and to calculate the average selection on gains (ASG):
+Because our design identifies all three quantities (as discussed below and in  \ref{append:randchoice}), it allows us to test this implication directly and to calculate the average selection on gains (ASG), namely the difference between the TOT and TUT effects:
 \[
@@
 \]
-A companion STATA package accompanying this paper provides estimators of the TOT, TUT, ASG, ASB, and ASL, along with cluster-robust standard errors for each, and a test for the validity of the exclusion restriction following \cite{huber_mellace} \footnote{See Appendix \ref{append:randchoice} for more details.}.
+The ASB tells us whether borrowers who voluntarily choose commitment are those who are worse off, on average, under the status quo.
+Similarly, the ASL tells us whether borrowers who voluntarily choose commitment are those who are better off, on average, under the commitment contract.
+A companion STATA package accompanying this paper provides estimators of the TOT, TUT, ASG, ASB, and ASL, along with cluster-robust standard errors for each, and a test for the validity of the exclusion restriction following \cite{huber_mellace}.\footnote{See Appendix \ref{append:randchoice} for more details.}
 
@@
 In contrast to both approaches, the controlled choice design uses exogenous experimental variation to point identify the ATE, TOT, and TUT without ruling out unobserved selection-on-gains or relying on additional structural modeling assumptions.
-Figure \ref{tot_tut_graph} provides graphical intuition for our identification approach; derivations appear in \ref{append:randchoice}
+Figure \ref{tot_tut_graph} provides graphical intuition for our identification approach. % derivations appear in \ref{append:randchoice}
 
@@
     \label{eq:ASL}
-    \text{ASL} &\equiv \mathbbm{E}(Y_{i1}|C_i = 1) - \mathbbm{E}(Y_{i1}|C_i=0) = \frac{\mathbbm{E}(Y|Z=2,D=1) - \mathbbm{E}(Y|Z=1)}{1 - \mathbbm{E}(D|Z=2)}
+    \text{ASL} &\equiv \mathbbm{E}(Y_{i1}|C_i = 1) - \mathbbm{E}(Y_{i1}|C_i=0) = \frac{\mathbbm{E}(Y|Z=2,D=1) - \mathbbm{E}(Y|Z=1)}{1 - \mathbbm{E}(D|Z=2)}.
 \end{align}
-as shown in \ref{append:randchoice}
-For purposes of inference, both the ASB and ASL can be re-written as the difference of coefficients from a pair of just-identified linear IV regressions.
-For details, along with a description of how our companion STATA package carries out cluster-robust inference for these quantities, see \ref{append:randchoice}
+For purposes of inference, both the ASB and ASL can be re-written as the difference of coefficients from a pair of just-identified linear IV regressions.\footnote{For details, along with a description of how our companion STATA package carries out cluster-robust inference for these quantities, see \ref{append:randchoice}.}
 
@@
 
-Table \ref{tot_tut} calculates the causal quantities described above--TOT, TUT, ASG, ASB, and ASL--for our experimental data, along with robust standard errors for each. 
-For purposes of comparison, the table also presents the ATE results from Section \ref{Experiment} above (row 1), along with the corresponding average potential outcomes $\mathbbm{E}[Y_0]$ and $\mathbbm{E}[Y_1]$ (rows 4--5).
-The columns of the table correspond to different outcome variables, defined as in Section \ref{costs} above.
+\paragraph{TOT and TUT results.} Table \ref{tot_tut} calculates the causal quantities described above--TOT, TUT, ASG, ASB, and ASL--for our experimental data, along with robust standard errors for each.
+For purposes of comparison, the table also presents the ATE results from Section \ref{Experiment} above (row 1),\footnote{Coefficients are not exactly the same since Table 4 includes branch and day-of-week FE.} along with the corresponding average potential outcomes $\mathbbm{E}[Y_0]$ and $\mathbbm{E}[Y_1]$ (rows 4--5).
+The columns of the table correspond to different outcome variables defined above.
 For all four outcome definitions, the TUT effect is positive, statistically and economically significant, and comparable in magnitude to the ATE.
 In other words: commitment is \emph{beneficial}, on average, to the people who \emph{would not choose it}, and these benefits are large.
-The estimated TOT effects are positive and larger still.
-Although we cannot quite reject the null hypothesis that the TUT and TOT effects are equal--our power is limited because of the low take-up rate of commitment in the choice arm--the pattern of coefficients is consistent with some degree of selection-on-gains.
-Commitment is more beneficial to people who are willing to choose it than it is to people who are not.
-For the APR benefit and (1 - Default) outcomes, we have sufficient precision to conclude that the average selection bias (ASB) is large and \emph{negative}.
-This means that borrowers who choose commitment would have faced a \emph{higher} APR and probability of default under the status quo contract than borrowers who do not choose commitment. 
-Overall, Table \ref{tot_tut} suggests that commitment works and the ``right people'' choose to commit: those who are most likely to benefit from it and those whose outcomes are most adverse under the status quo.
-At the same time, \emph{not enough} people choose to commit: the commitment contract is beneficial on average even to those who would \emph{not} choose it voluntarily.
-Below we explore possible explanations for this result.
+Due to the low take-up rate of commitment in the choice arm, the corresponding TOT effects are imprecisely estimated. Only one of them, \%(1-Default) from column (3), is statistically significant. 
+This imprecision carries over into our estimates of the average selection on gains, TOT-TUT.
+Our point estimates are \emph{negative} for all but the (1 - Default) outcome, but none is statistically distinguishable from zero.
+%Although we cannot quite reject the null hypothesis that the TUT and TOT effects are equal--our power is limited because of the low take-up rate of commitment in the choice arm--the pattern of coefficients is consistent with some degree of selection-on-gains.
+%Commitment is more beneficial to people who are willing to choose it than it is to people who are not.
+For the (1 - Default) outcome, we have sufficient precision to conclude that the average selection bias (ASB) is large and \emph{negative}.
+This means that borrowers who choose commitment would have faced a \emph{higher} probability of default under the status quo contract than borrowers who do not choose commitment.
+We may not want to read too much into TOT vs TUT comparisons as they are imprecise.
+But taken at face value, the result that TOT$>$TUT for default, while the opposite is true for financial cost, suggests that, while voluntary commitment has a slightly stronger effect on allowing borrowers to avoid default, forcing \textit{reduces} payments in a strong enough manner as to overcome the default-benefits of choice.
+
+\vspace{.1in}
+Overall, Table \ref{tot_tut} suggests that commitment works but that \emph{not enough} people choose to commit: the commitment contract is beneficial on average even to those who would \emph{not} choose it voluntarily.
+We believe this result is new in the household finance literature.
+It also illustrates how the ``Controlled-Choice'' design can be used to study more generally whether low take-up of an intervention is problematic, based on the impacts among non-choosers.\footnote{For instance, in the debate on financial commitment take-up, some papers argue it is low (\cite{Ashraf}, \cite{Gine}, \cite{Ted}, \cite{Royer} while others argue it is high (\cite{Kremer}, \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}, \cite{Pascaline},), but none estimates the benefits for non-takers.
+In a different domain, doctors claim that medical treatment abandonment is too high in a broad range of diseases \citep{non_adherence}, without knowing the treatment benefits for those that abandon.}
+%Below we explore possible explanations for this result.
+%and the ``right people'' choose to commit: those who are most likely to benefit from it and those whose outcomes are most adverse under the status quo.
 
@@
 
-The behavioral literature has highlighted voluntary commitment as an attractive way of allowing the ``right'' people to self-select.
-A discussion of compulsory commitment is necessarily paternalistic, and by its nature focuses on impacts among those who would not have selected commitment voluntarily.
-Viewed through the lens of rational choice theory, it is unsurprising that we estimate $\text{TOT}>\text{TUT}$.
-The argument for compulsory treatment, however, centers on the more surprising result that $\text{TUT}>0$.
-We now investigate several potential explanations for this result.
+A behavioral literature has highlighted voluntary commitment as an attractive way of allowing the ``right'' people to self-select.
+% A discussion of compulsory commitment is necessarily paternalistic, and by its nature focuses on impacts among those who would not have selected commitment voluntarily.
+%Viewed through the lens of rational choice theory, it is unsurprising that we estimate $\text{TOT}>\text{TUT}$. 
+The argument for compulsory treatment, centers on the surprising result that $\text{TUT}>0$. We now investigate several potential explanations for this result.
 For simplicity, we focus on causal effects for the APR outcome throughout this section.
-
-We conduct an exploratory analysis that examines four potential explanations for the positive $\text{TOT}$:  the need to learn, time discounting, present bias, and overconfidence.
-To explore the last two dimensions we will use survey data for which our response rate was 78\%.
-Appendix \ref{app:survey_data} demonstrates that the subsample on whom we have survey data appears to be representative in terms of loan outcomes.
+We view this section as an exploratory analysis to stimulate ideas for future research.
+We examine four potential explanations for the positive $\text{TUT}$: the need to learn, time discounting, present bias, and overconfidence.
+To explore the last two dimensions we will use survey data.\footnote{Since merging with survey data reduces our sample, Table \ref{TUT_cond_survet} demonstrates that the subsample on whom we have survey data appears to be representative in terms of treatment effects.}
 
@@
 Our experiment introduced a new contract into an environment that had not previously featured commitment; perhaps clients required experience to understand its benefits.
-Given the strongly positive impact of forcing, this explanation would suggest that clients who were forced once would subsequently choose commitment if given the chance to do so.
-A subset of 16\% clients from our sample returned to pawn again on another day before the end of the experiment.
-Whereas all of the analyses from above restrict attention to the first day on which a given individual pawned, Table \ref{learning_table} presents information about participants' \emph{immediate subsequent} pawning behavior.\footnote{In other words, for borrowers who returned to pawn again more than once, this analysis considers only their first repeat pawn.} Column (1) considers the 228 clients who returned (only a second time) to pawn again at a day/branch that was randomly assigned to the choice arm.
+Are clients who experienced the commitment contract more likely to choose commitment subsequently than those assigned to the status-quo contract?
+To test this we look to the subset of 22\% clients from our experimental sample who returned to pawn again on another day before the end of the experiment.
+We have already shown above that those who experienced the Forcing contract were more likely to borrow again.
+We now ask whether the subset who were assigned to the Choice arm when they returned were more likely to choose commitment.
+We do this in Appendix Table \ref{learning_table}.\footnote{Table \ref{learning_table} presents information about participants' \emph{immediate subsequent} pawning behavior.
+For borrowers who returned to pawn again more than once, this analysis considers only their first repeat pawn.}
+We find no statistically discernible difference in commitment take-up rates for those assigned to forced commitment versus those assigned to status quo control.
+The implication is that while those who have experienced commitment feel more positively towards the pawn contract, the experience does not lead them to conclude that they need commitment on the subsequent loan.
+While these exercises cannot completely exclude the possibility that learning plays a role, they provide no indication that the lack of voluntary compliance is simply a matter of inexperience with commitment, but more research and larger samples are needed to test whether learning obviates the need for paternalism.
+
+%Column (1) considers the 228 clients who returned only a second time to pawn again at a day/branch that was randomly assigned to the choice arm.
 Each of the two rows in this column presents a difference of mean commitment take-up rates, and associated standard error.
@@
 
-%a subset of 228 clients from our experiment who were exposed to the experiment in one round and then returned to take another loan at a branch where the choice of commitment was offered.
-Table \ref{learning_table} shows the results of this analysis.
-The first column uses only the (endogenous) sample that took multiple loans, and the second column uses the whole experimental sample and defines the outcome as ``returned and chose commitment''.
-While the first column is under-powered, the point estimate is actually negative.
-The estimate in the second column is pushed upwards by the positive effect of Forcing on repeat borrowing shown in Table \ref{repeat_loans}, and yet the estimate here is very close to zero.
-Hence the window available to us on learning provides little comfort that the lack of voluntary compliance is simply a matter of inexperience with commitment.
-
-%Some people self-select into returning for another loan (endogenous).
-The people who return are randomized into the same three arms as before.
-Note that we have *not* used their second visits in any other data analysis so far, so this new data.
-For the self-selected sub-sample, we estimate the difference in commitment take-up across people who were initially assigned to forced commitment versus control: first row and first column.
-This is zero.
-The second row in the first column restricts attention to people who were initially assigned to either the choice or control arms, endogenously returned, and were exogenously assigned to choice a second time.
-We compare the commitment take-up rates the second time around across people who were initially assigned to choice versus those who were initially assigned to the status quo
-
-%Second column defines an outcome that equals one if and only if you *both* return *and* choose commitment the second time around.
-(Note that this requires you to have been randomly assigned to choice the second time.) The first row compares people who were assigned at random to commitment the first time around against those who were assigned to control.
-The second row compares those who were offered a choice the first time around to those who were forced into the status quo contract
-
 \paragraph{Time discounting.} Discounting is a second potential explanation for our results.
-Our estimated decrease in the financial cost of credit from above ignores discounting, but commitment involves incurring up-front costs (early payment) in return for delayed benefits (a higher probability of recovering one's pawn).
-Highly impatient individuals might therefore rationally choose the \emph{status quo} contract, despite the benefits that commitment yields in terms of raw (undiscounted) returns.
-To investigate this explanation we calculate the net present value (NPV) of the financial cost $\text{TUT}$ effect under different hypothetical discount rates, given the timing of repayment and pawn recovery.
+Highly impatient individuals might rationally choose the \emph{status quo} contract, despite the benefits that commitment yields returns, since monthly payments are front-loaded while pawn recovery is back-loaded, even if by only a few days.
+%those returns are realized at contract ending hile the cost of monthly payments are incurred  Our estimated decrease in the financial cost of credit from above ignores discounting, but commitment involves incurring up-front costs (early payment) in return for delayed benefits (a higher probability of recovering one's pawn).
+To investigate this explanation we calculate the net present value (NPV) of the financial cost $\text{TUT}$ effect under different hypothetical discount rates, given the actual timing of repayment and pawn recovery.
 Figure \ref{fc_discount_rates} presents the results of this exercise.
-The solid line gives the TUT effect adjusted for a specified annual discount rate, while the shaded regions gives the associated 95\% \& 90\% confidence interval.
-We see that non-choosers continue to experience significant decreases in NPV financial costs up to annual discount rates of 4,000\%, and the NPV remains positive, although not significant, at 10,000\% discount rates.
+The solid line gives the TUT effect adjusted for a specified annual discount rate, while the shaded regions give the associated 95\% \& 90\% confidence interval.
+We see that non-choosers continue to experience significant decreases in NPV financial costs up to annual discount rates of 1,000\%, and the NPV remains positive, although not significant, at 5,000\% discount rates.
 As such, discounting is unlikely to explain why those who benefit, on average, from commitment fail to choose it when offered.
@@
 
-If we could perfectly measure present bias, we could divide the sample into three groups: sophisticated hyperbolics (who chose commitment), time-consistent non-choosers (for whom forcing will not be effective), and na\"{i}ve hyperbolic non-choosers (who will benefit from forced commitment).
-If present bias fully explains the low take-up rate of voluntary commitment, we should find that the TUT for present biased borrowers is positive while the TUT for all other borrowers is not.
-This is because TUT effects already restrict attention to borrowers who would not choose commitment.
-Within this group, a comparison of present-biased borrowers against everyone else is a comparison of na\"{i}ve hyperbolics against time-consistent non-choosers.
-The right panel of Figure \ref{tut_beh_partition} carries out a feasible version of this exercise using our survey measure of present bias.
-The overall TUT estimate for all borrowers who answered our present-bias survey questions is given in blue, along with a 95\% confidence interval.
-The corresponding TUT estimate and confidence interval for present-biased borrowers is given in green; results for all other borrowers are shown in red.
-By the law of iterated expectations, the blue overall estimate must lie between the green and red sub-group estimates.
-In fact, all three estimates are positive and similar in magnitude, although imprecisely estimated given the extent of survey non-response for these questions.
-Taking our survey measure of hyperbolicity at face value, we find no indication that present-bias explains our positive estimated TUT.
+If we could perfectly measure present bias \textcolor{teal}{and sophistication}, we could divide the sample into three groups: sophisticated hyperbolics (who chose commitment), time-consistent non-choosers (for whom forcing will not be effective), and na\"{i}ve hyperbolic non-choosers (who will benefit from forced commitment).
+%If present bias fully explains the low take-up rate of voluntary commitment, we should find that the TUT for present-biased borrowers  is positive while the TUT for all other borrowers is not.
+If present bias fully explains the low take-up rate of voluntary commitment, we should find that the TUT for present-biased borrowers is positive.
+This is because among the group of non-takers, a comparison of present-biased borrowers against everyone else is a comparison of na\"{i}ve hyperbolics against time-consistent non-choosers.
+
+The left panel of Figure \ref{tut_beh_partition} carries out a feasible version of this exercise using our survey measure of present bias.
+The overall TUT estimate along with a 95\% confidence interval is given in blue.\footnote{For all borrowers who answered our present-bias survey questions.}
+The corresponding TUT estimate and confidence interval for present-biased borrowers identified with the survey question is given in green; results for all other borrowers are shown in red.
+The overall TUT is a weighted average of the impact in these two sub-groups.
+The TUT among the present biased is insignificant and less than half the size of the strongly significant TUT among those who are \textit{not} present biased.
+Therefore, taking our survey measure of hyperbolicity at face value, we find no indication that present-bias explains our positive estimated TUT.
 
@@
 The corresponding TUT estimate and confidence interval for sure-confident borrowers is given in green; results for all other borrowers are shown in red.
-As above, the blue overall estimate must lie between the green and red sub-group estimates by the law of iterated expectations.
-In contrast to our results for present bias, shown in the left panel of Figure \ref{tut_beh_partition}, we estimate a higher TUT effect for sure-confident borrowers compared to all other borrowers and a negative, although insignificant, effect for borrowers who are not sure-confident.
+In contrast to our results for present bias, the TUT is almost entirely confined to the sure confident individuals, with the effect among those saying they have some chance of defaulting at baseline being very close to zero.
 
 As discussed above, our measure of hyperbolicity is based on un-incentivized responses in a short survey and so is likely to be noisy; nonetheless we see no evidence here that it drives the forcing effect.
-Rather, the analysis from Figure \ref{tut_beh_partition} suggests that the effectiveness of paternalism in our experiment may be driven by a group of \emph{overconfident} borrowers who, heedless of the risk of default, fail to choose commitment despite benefiting substantially when they are forced to commit.
+Rather, the analysis from Figure \ref{tut_beh_partition} suggests that the effectiveness of paternalism in our experiment may be driven by \emph{overconfident} borrowers who, heedless of the risk of default, fail to choose commitment despite benefiting substantially when they are forced to commit.
 
@@
 Older males are more likely to be sure-confident, as are those with more education.
-Taken at face value, the sure-confident also appear to face less financial stress, to have less trouble paying bills, and to be more frequently relied upon financially by family members.
-Viewed through a behavioral lens, however, it is also possible that the type of person who is over-confident in their ability to repay a loan also maintains fictions in other domains of their financial life, providing answers to the baseline survey questions that exaggerate their degree of economic security.
-In any case it appears that sure confidence may be difficult to predict with easily-observed and objective demographic criteria, a point to which we return below.
+Taken at face value, the sure-confident also report less financial stress, less trouble paying bills, and to be more frequently relied upon financially by family members.
+Viewed through a behavioral lens, however, it is also possible that the type of person who is over-confident in their ability to repay a loan also %maintains fictions in other domains of their financial life, providing answers to the baseline survey questions that
+exaggerate their degree of economic security in their response to survey questions.
+In any case, it appears that sure confidence may be difficult to predict with easily-observed and objective demographic criteria, a point to which we return below.
 
@@
 Because they made no assumptions beyond random assignment, these bounds were relatively wide.
-Adding the assumption of rank invariance yielded a distribution of treatment effects that was bounded below by zero, implying that \emph{everyone} would benefit from treatment and hence that there would be \emph{no losers} from paternalism.
-Rank invariance, however, is an extremely strong assumption.
-In this section, we explore a middle way between the two extremes, by considering conditional average treatment effects and conditional TOT and TUT effects, given our survey measures (note that this approach also imposes the exclusion restriction within each leaf of the tree).
+Adding the assumption of rank invariance yielded a distribution of treatment effects in approximately 90\% of borrowers had positive individual treatment effects for the APR outcome, implying that \emph{practically everyone} would benefit from treatment and hence that there would be hardly any no losers from paternalism.
+Rank invariance, however, is an extremely strong assumption.\footnote{For the financial cost outcome, rank invariance implies that all invididual treatment effects are positive.}
+In this section, we explore a middle way between the two extremes, using a causal forest analysis to consider conditional average treatment effects and conditional TOT and TUT effects.\footnote{Note that this approach imposes our exclusion restriction from \ref{sec:randchoice} conditional on observed covariates: administrative data and survey responses.}
 This exercise provides more fine-grained information about treatment effect heterogeneity.
@@
 
-To estimate conditional average treatment effects given administrative and survey data, we use the function \texttt{causal\_forest()} of the \texttt{grf} R package; to estimate conditional TOT and TUT effects we use the function \texttt{instrumental\_forest()} function from the same package.
+To estimate conditional average treatment effects given administrative and survey data, we use the function \texttt{causal\_forest()} of the \texttt{grf} R package; to estimate conditional TOT and TUT effects we use the \texttt{instrumental\_forest()} function from the same package.
 In each case, we use the default parameter values from the \texttt{grf} package with one exception: we increase the number of trees from the default value of 2000 to 5000.
@@
 The trees are ``honest'' in that observations used to determine the optimal partition are not used to estimate effects, and vice-versa.
-While closely related to more familiar ``regression-tree'' random forests, the generalized random forest approach explicitly targets the parameter of interest--a conditional ATE or IV estimand--when choosing the optimal covariate partition.\footnote{For more details, see \cite{atheygrf} and the \texttt{grf} documentation: \url{https://grf-labs.github.io/grf/}.}
+While closely related to more familiar ``regression-tree'' random forests, the generalized random forest approach explicitly targets the parameter of interest--a conditional ATE or IV estimand--when choosing the optimal covariate partition.
+\footnote{For more details, see \cite{atheygrf} and the \texttt{grf} documentation: \url{https://grf-labs.github.io/grf/}.
 When constructing our random forest estimates of heterogeneous treatment effects, we use observations for all borrowers who answered at least \emph{part} of the intake survey.
-We impute the median response for the missing values, while also including an indicator whether the variable originally had a missing value.\footnote{Results are similar if we manually include interactions between the original/imputed variable and an indicator for missingness.
+We impute the median response for the missing values, while also including an indicator whether the variable originally had a missing value.
+Results are similar if we manually include interactions between the original/imputed variable and an indicator for missingness.
 This is as expected, given that tree-based methods by their nature ``automatically'' consider interactions of arbitrary orders.}
 
-Figure \ref{heterogeneous_effects} plots densities of the estimated conditional ATE, TOT, and TUT effects from the generalized random forest models described above.
+\paragraph{Treatment effect distributions.} Figure \ref{heterogeneous_effects} plots densities of the estimated conditional ATE, TOT, and TUT effects from the generalized random forest models described above.
 In each case, the outcome variable is APR benefit, i.e.\ the reduction in APR from a commitment contract.
@@
 The TUT density is particularly interesting for the question of paternalism since, as emphasized above, it presents conditional average effects for borrowers who would not voluntarily choose commitment.
-Only 13\% of our estimated conditional TUTs are negative, with a 95\% confidence interval of [11\%, 17\%].\footnote{The generalized random forest approach of \cite{atheygrf} produces conditional average effect estimators that are asymptotically normal, and includes methods for computing correct standard errors.
-These methods are relatively straightforward because the trees are ``honest'' in that observations used to determine splits in the recursive partitioning algorithm are not used for causal effect estimation and vice-versa.
+Only 7\% of our estimated conditional TUTs are negative, with a 95\% confidence interval of [4\%, 9\%].\footnote{The generalized random forest approach of \cite{atheygrf} produces conditional average effect estimators that are asymptotically normal, and includes methods for computing correct standard errors.
+%These methods are relatively straightforward because the trees are ``honest'' in that observations used to determine splits in the recursive partitioning algorithm are not used for causal effect estimation and vice-versa.
 Our inferences in this section are carried out by ``bootstrapping the limit experiment,'' i.e.\ simulating from the normal limit distributions using the estimated standard errors.} 
@@
 \[
-\int \mathbbm{1}\{\mathbb{E}[Y_1 - Y_0| X = \mathbf{x}, C = 0] > 0\} \, f(\mathbf{x}|C=0) \, \mathrm{d}\mathbf{x} 
+\int \mathbbm{1}\{\mathbb{E}[Y_1 - Y_0| X = \mathbf{x}, C = 0] < 0\} \, f(\mathbf{x}|C=0) \, \mathrm{d}\mathbf{x} 
 \]
-is approximately 0.13.
-The share of non-choosers with a positive conditional \emph{average} treatment effects need not equal the share with a positive \emph{individual} effects, i.e.\ $\mathbbm{P}(Y_1 > Y_0| C = 0)$.
-But the more treatment effect heterogeneity that $X_i$ explains, the closer these two values become.
-Figure \ref{heterogeneous_effects} strengthens our argument, introduced in section \ref{Choice}, that not enough borrowers choose commitment.
-
-Under the assumption that our instrumental forest estimates capture the main sources of treatment effect heterogeneity, we can use them to assess whether particular borrowers in the choice arm made ``mistakes'' in their decision to accept or refuse the commitment contract, in terms of predicted financial costs of the loan.
+is approximately 0.07.\footnote{The share of non-choosers with negative conditional \emph{average} treatment effects need not equal the share with a negative \emph{individual} effects, i.e.\ $\mathbbm{P}(Y_1 < Y_0| C = 0)$.
+But the more treatment effect heterogeneity that $X_i$ explains, the closer these two values become.}
+Figure \ref{heterogeneous_effects} strengthens our argument, introduced in Section \ref{Choice}, that not enough borrowers choose commitment.
+
+\paragraph{``Mistake'' tresholds.} Under the assumption that our instrumental forest estimates capture the main sources of treatment effect heterogeneity, we can use them to assess whether particular borrowers in the choice arm made ``mistakes'' in their decision to accept or refuse the commitment contract, in terms of predicted financial costs of the loan.
 To do this we use the same information that is depicted in Figure \ref{heterogeneous_effects}, but present it in a different way.
@@
 Of course conditional average effects need not equal individual treatment effects, and our APR outcome may not capture all of the costs and benefits that are relevant for individual borrowers' decisions.
-To account for this, we define a ``mistake'' for a non-chooser to be a conditional TUT estimate that significantly exceeds some large and positive APR threshold, e.g.\ 25\%. 
-At any such threshold, we can calculate the percentage of non-choosers in the choice arm who made a ``mistake'' by not choosing commitment.   
-(If treatment it beneficial, it should be chosen.)
+To account for this, we define a ``mistake'' for a non-chooser to be a conditional TUT estimate that significantly exceeds some large and positive APR threshold, e.g.\ 10\%. 
+At any such threshold, we can calculate the percentage of non-choosers in the choice arm who have benefited by more than that threshold from having chosen commitment.
+
 The results of this exercise can be read off from the green curve in Figure \ref{choose_wrong}.
 Defining $F_{\text{TUT}}(\delta)$ to be the CDF corresponding to the density of conditional TUT estimates from Figure \ref{heterogeneous_effects}, the green curve in Figure \ref{choose_wrong} is merely $[1 - F_{\text{TUT}}(\delta)] \times 100\%$.
-In other words, the green curve gives the percentage of non-choosers who made a ``mistake'' when mistakes are defined at a particular APR threshold.
+In other words, the green curve gives the percentage of non-choosers who made a ``mistake'' when mistakes are defined increasing APR by a given threshold.
 The green shaded region gives associated 95\% pointwise confidence bounds.
@@
 For choosers we follow an analogous approach, defining a ``mistake'' as a \emph{negative} conditional TOT effect that exceeds a particular APR threshold.
-(If treatment is harmful, it should not be chosen.)
-The results for choosers can be read from the the red curve in Figure \ref{choose_wrong}.
+The results for choosers can be read from the red curve in Figure \ref{choose_wrong}.
 If $F_{\text{TOT}}(\delta)$ denotes the CDF corresponding to the density of conditional TOT estimates from Figure \ref{heterogeneous_effects}, then the red curve is merely $F_{\text{TOT}}(-\delta) \times 100\%$.
@@
 The results in Figure \ref{choose_wrong} suggest that a large fraction of non-choosers made mistakes by not choosing commitment.
-Even at an APR threshold as large as 25\%, we estimate that more than half of them should have chosen commitment in order to lower financial costs.
+Even at an APR threshold as large as 10\%, we estimate that more than half of them should have chosen commitment in order to lower financial costs.
 In contrast, relatively few choosers appear to have made mistakes by choosing commitment.
-This now allows us to make a stronger statement in favor of paternalism; not only does forced commitment generate large benefits on average, but it also benefits the vast majority of borrowers \emph{who would be coerced} under a policy of forced commitment.
+This now allows us to make a stronger statement in favor of paternalism in our context; not only does forced commitment generate large benefits on average, but it also benefits the vast majority of borrowers \emph{who would be coerced} under a policy of forced commitment.
 
@@
 
-%\todo[inline]{@Frank: note that we for the wide forest we use everyone who answered at least one survey question in the random forests.
-We have dummies for missingness of any of the predictors.
-We then take this as ground truth.
-For the narrow forest, we restrict to the sample for which we don't have missing values.
-Under certain assumptions, this ``controls'' for selection into the survey.
-Need to think a bit more about the interpretation here: it's slightly tricky.
-Question of external validity?
-Imagine another sample with the same pattern of non-response, then there's probably no concern.
-I think the issue here relates to whether the covariates that are missing for us would be missing in the hypothetical targeting exercise.
-It's a question of ``could we have targeted'' versus ``could you target'' in a setting where you have administrative data for everybody?}
-
 Despite having shown such a large majority of individuals benefit from paternalism, it is still natural to ask whether we are able to target commitment in such a manner as to only force it upon those who benefit.
@@
 For this reason, the relevant causal effect for this exercise is the conditional average treatment effect (ATE) rather than the conditional TUT or TOT as considered above.
-As shown in Figure \ref{fig:CATEsurvival}, an estimated 92\% of borrowers, with a 95\% confidence interval of [89\%, 94\%] have a positive conditional ATE as estimated from the causal forest from section \ref{sec:RF} above.
+As shown in Figure \ref{fig:CATEsurvival}, an estimated 90\% of borrowers, with a 95\% confidence interval of [87\%, 92\%] have a positive conditional ATE as estimated from the causal forest from Section \ref{sec:RF} above.
 In the remainder of this section we ask how accurately it is possible to identify these borrowers.
 
-\paragraph{Narrow inputs targeting.} To  consider targeting effectiveness we must begin from an individual-specific ground truth, which we take from our estimated conditional average treatment effects (CATEs) $\widehat{\text{ATE}}(X_i)$ from the causal forest described in Section \ref{sec:RF},  which used the ``wide'' set of covariates (wide RF) and data for all borrowers who replied to at least part of the intake survey.
+\paragraph{Narrow inputs targeting.} To consider targeting effectiveness we must begin from an individual-specific ground truth, which we take from our estimated conditional average treatment effects (CATEs) $\widehat{\text{ATE}}(X_i)$ from the causal forest described in Section \ref{sec:RF},  which used the ``wide'' set of covariates (wide RF).% and data for all borrowers who replied to at least part of the intake survey.
 We then analyze how well we can predict the losers from paternalism using the ``narrow'' set of non-manipulable covariates listed above (narrow RF) for the same subset of borrowers.
 Figure \ref{wide_narrow_forests} shows the relationship between the CATEs estimated from the RF using the ``wide'' and ``narrow'' covariate sets.
-It is visually obvious from this figure that we generate substantially less heterogeneity when using the narrow covariate set, although we still reject the null hypothesis of no treatment effect heterogeneity, following the approach of \cite{chernozhukov2018generic}.\footnote{See \ref{append:chernozhukov} for details of this method.}
+We can generate substantially less heterogeneity when using the narrow covariate set, although we still reject the null hypothesis of no treatment effect heterogeneity, following the approach of \cite{chernozhukov2018generic}.\footnote{See \ref{append:chernozhukov} for details of this method.}
 
@@
 To more directly investigate our ability to target commitment, we use two different methods to predict who should be assigned to the commitment arm.
-In each, we estimate a classification model using the ``narrow'' set of covariates to predict whether the CATE from the wide random forest model is positive.
+In each, we estimate a classification model using the ``narrow'' set of covariates to predict whether the CATE estimated from the wide random forest model (using all available covariates) is positive.
 The first method uses a simple logistic regression, while the second uses a random forest classification model.\footnote{We use the STATA package \textit{rforest} and use the default parameters for the estimation.
 For further detail see \cite{rforest_stata}.} Each of these methods yields an estimated probability of a positive CATE, allowing us to rank borrowers from highest to lowest probability.
-Since 92\% of borrowers have a positive CATE as estimated from the wide random forest model from above, we consider a decision rule that assigns a borrower to forced commitment if her estimated probability is in the top 92\% of the sample.
-%The first of these is the narrow RF displayed above paired with the decision rule which assigns clients to forcing commitment if the estimated CATE from the narrow covariate set is positive. 
-%In the second approach we estimate a logistic regression model with an outcome variable equal to one if the ``wide'' model CATE is positive, zero otherwise. 
-%The explanatory variables are the covariates from the ``narrow'' model. We assign a borrower to commitment if \hl{the probability that her CATE is positive is estimated to be above 0.5}.
-Figure \ref{targeting_rules} compares the in-sample performance of these targeting rules against a policy of universal forced commitment.
+Since 90\% of borrowers have a positive CATE as estimated from the wide random forest model from above, we consider a decision rule that assigns a borrower to forced commitment if her estimated probability is in the top 90\% of the sample.
+
+%Figure \ref{targeting_rules} compares the in-sample performance of these targeting rules against a policy of universal forced commitment.
 The plot presents the estimated proportion of borrowers who benefit from a particular treatment assignment rule, along with associated 95\% confidence bands, where ``benefit'' is defined as having a conditional average treatment effect above a particular threshold.
@@
 In spite of this, their performance is quite unimpressive relative to a policy of universal forced commitment.
-The fraction of the whole sample incorrectly targeted when moving from universal forced commitment to targeting based on the narrow RF falls only from 8.07\% to 5.49\%.
+The fraction of the whole sample incorrectly targeted when moving from universal forced commitment to targeting based on the narrow RF falls only from 9.78\% to 9.59\%.
 The logit targeting rule actually makes things marginally worse.
-Table \ref{hit_miss_rule} shows error rates for six possible assignment rules: assigning all borrowers to control, all to treatment (Forcing), the optimal (infeasible) assignment, narrow RF targeting, logit targeting, and we evaluate ex-post the voluntary choice.
-While the narrow RF correctly assigns roughly half of those who do not benefit from commitment to control, it also incorrectly allocates 3.7\% of the sample that would have gained from treatment to control.
-As such, it only improves the correct targeting rate by about a half of a percentage point on net relative to universal Forcing.
-The logit assignment rule is less successful at predicting benefits and harms, with a higher share of borrowers incorrectly assigned to both treatment and control.
+
+We compare the in-sample performance of targeting rules against a policy of universal forced commitment.
+Table \ref{hit_miss_rule} shows error rates for six possible assignment rules: assigning all borrowers to control, all to treatment (Forcing), the optimal (infeasible) assignment, narrow RF targeting, Logit targeting, and we evaluate ex-post the voluntary choice, taking the wide RF as the ground truth.
+While the narrow RF correctly assigns roughly half of those who do not benefit from commitment to control, it also incorrectly allocates 4.38\% of the sample that would have gained from treatment to control.
+As such, it only improves the overall correct targeting rate by about half of a percentage point relative to universal Forcing.
+The Logit assignment rule is less successful at predicting benefits and harms, with a higher share of borrowers incorrectly assigned to both treatment and control, meaning that the overall correct targeting rate for the Logit is 5 pp lower than universal Forcing.
 %In particular it makes many Type II errors, resulting in a net targeting performance that is actually worse than universal forcing. 
 The underlying cause of the weak performance of targeting is that the attribute that predicts gains from forcing (being sure confident and not choosing the commitment) is largely behavioral and not easily predicted with basic covariates, as seen in Figure \ref{tut_beh_partition}.
+
 Self-targeting through choice proves to be little better than assigning everyone to the control condition, given the low take-up rate and the presence of both Type I and Type II errors in the choice arm.
-Fully 79\% of individuals in the Choice arm made a ``mistake'', weighting the error rates among choosers and non-choosers by their relative frequency in the Choice arm.
-The takeaway is that given low take-up, the large fraction of the sample benefiting from commitment, and the weak predictive power of the narrow covariates, in this case universal paternalism appears to be an attractive contract.
+Fully 87\% of individuals in the Choice arm made a ``mistake'', weighting the error rates among choosers and non-choosers by their relative frequency in the Choice arm.
+The takeaway is that given low take-up, the large fraction of the sample benefiting from commitment, and the weak predictive power of the narrow covariates, in this case universal paternalism assigning all borrowers to the commitment contract appears to be an attractive targeting method.
 
@@
 
-\cite{Laibson2018} discusses the idea of ``veiled paternalism'', whereby principals embed forms of commitment into their products but mask this fact from consumers who may need but do not desire commitment.
-In the context of pawnbroking, over-collateralization means that lenders stand to make more money from unreliable borrowers than those who repay.
-The fact that a simple change to contract terms results in a substantial financial saving for borrowers implies that the pawn contract involves ``veiled non-paternalism'':   features that lead to high borrower costs are embedded in non-obvious ways.
-Potentially due to the nature of the borrower pool, voluntary commitment choice does not result in substantial improvements in borrower returns; a mandated reform to the contract induced significant cost savings for the overall group of clients.
-
-We are able to arrive at a nuanced set of conclusions about the relationship between take-up and heterogeneity in returns due to a novel experimental setup, the ``Controlled Choice'' design.
-This three-armed experiment, featuring a control group, an arm with borrower choice, and an arm with compulsory treatment, allows us to point-identify the impact of the treatment on those who would naturally choose it as well as those who only experience commitment when forced.
-While we find evidence of selection on gains (as would be expected from standard economic models) there remain substantial benefits of treatment even for non-choosers.
-Given that the rate of voluntary commitment in our sample is only 11\%, in order to achieve widespread benefits in this context compulsory commitment may be necessary.
-In the Forced arm the APR (inclusive of the cost of default) falls from 184\% to 150\%, and the fraction of borrowers defaulting on loans drops by 6.5 pp, or 15\%.
-Clients appear to prefer the forced commitment after they have experienced it, in that assignment to this arm increases the fraction of individuals who return to pawn again.
+This paper makes several contributions.
+First, it analyzes the large but understudied industry of pawn loans, and shows that a simple change to contract terms results in substantial financial savings for pawn borrowers: forced commitment lowers the APR from 57\% to 46\%, and reduces the fraction of borrowers who default by 6.6 pp, or 15\%.
+That this new contract generated large benefits for borrowers and yet was not offered, and that a contract that generated default was the industry standard instead, is related to the idea of ``veiled paternalism'' \cite{Laibson2018}, put on its head.
+In ``veiled paternalism'' principals embed forms of commitment into their products but mask this fact from consumers who may need but do not desire commitment, in pawn lending, over-collateralization means that lenders stand to make more money from defaulting borrowers, generating incentives for ``veiled \textit{non}-paternalism,'' embedding features that lead to high borrower costs in non-obvious ways.
+
+%Potentially due to the nature of the borrower pool, 
+%In our context voluntary commitment choice does improve borrower outcomes, but forcing commitment did induce significant cost savings for the overall group of clients.
+
+Second, our novel  ``controlled choice'' design allows us to go beyond ATE results and draw an important set of conclusions about the relationship between take-up and heterogeneous treatment effects.
+In particular, we simultaneously point-identify the impact of commitment on those who would naturally choose it \emph{and} those who only experience commitment when forced.
+Estimating this later quantity is critical in thinking about paternalism.
+We find substantial benefits of treatment for non-choosers and no evidence of selection on gains by borrowers who choose commitment.
+Given that the rate of voluntary commitment in our sample is only 11\%, in order to achieve widespread benefits in this context compulsory commitment appears to be necessary.
+%Clients appear to prefer the forced commitment after they have experienced it, in that assignment to this arm increases the fraction of individuals who return to pawn again.
 
 Why do borrowers leave such substantial returns on the table?
-Our investigation of treatment effect heterogeneity suggests that over-optimism is the characteristic most strongly associated with benefiting from the intervention and yet not choosing it.
-Overall the borrower pool overestimates their own probability of repayment by more than 50\%, and we find that the positive TUT is almost entirely confined to borrowers who report that they are certain to repay.
-The takeaway is that inefficiently low demand for tools to remediate default is strongest among those who incorrectly believe that they have no chance of defaulting.
-More standard explanations such as discounting, learning, or time inconsistency find little support in our data.
-Importantly, we find that not only are the benefits of commitment close to universal, but the determinants that might allow us to target it more finely are primarily behavioral and hence not easily predicted in an fast incentive-compatible manner by lenders.
-Even a sophisticated machine learning-based exercise is only able to decrease the fraction of borrowers mis-targeted by about 2.5 percentage points relative to simply assigning everyone to commitment (from 8\% to 5.5\%), and a logit-based targeting rule actually does slightly worse than universal commitment.
-
-This result has immediate policy implications.
-Pawnshops, along with other over-collateralized credit products such as payday lending, exist in an environment where the bank may desire customers to lose their collateral on the loan.
-Given the high prevalence of the use of this form of credit by low-income households, this has an obviously detrimental effect on the dynamics of asset accumulation among the poor.
-Given that the specific items being pawned (such crucifixes and family jewelry) may have sentimental, non-pecuniary meaning to households, the efficiency implications of these contract terms may be even larger (as evidenced by the fact that borrowers' subjective value of their own pawns was 26\% higher than the appraised collateral value).
-With a now well-established toolkit of regular small payments and incentives delivering vanishingly small default rates in microfinance, regulators in the banking sector may fruitfully investigate the possibility of requiring pawnbrokers to embed features of commitment and regularity into their repayment structures in more consistent ways.
-If employed at scale in a competitive lending sector this could redistribute welfare from those who would have repaid (whose interest rates must now rise to cover lower returns from collateral seizure) towards those who would only repay in the presence of commitment.
-In a setting of lender market power however, some redistribution from lenders to borrowers could occur.
-
-Where banks have no incentive to engage in veiled paternalism and customers display inefficiently low demand for it, financial policy regulation may prove an attractive option.
+Our results suggest that over-optimism is the characteristic most strongly associated with benefiting from the commitment despite not having chosen it.
+Our borrower pool overestimates their probability of repayment by more than 50\%, and our positive TUT estimate is largely confined to borrowers who incorrectly believe that they have little chance of defaulting.
+%More standard explanations such as discounting, learning, or time inconsistency find little support in our data.
+
+Using machine learning methods, we find the benefits of commitment close to universal.
+The benefits of targeting commitment based on characteristics that lenders can observe and participants would truthfully reveal are extremely limited, suggesting that universal commitment is an attractive policy in our empirical setting.
+
+%but the determinants that might allow us to target it more finely are primarily behavioral and hence not easily predicted in a fast incentive-compatible manner by lenders, making universal assignment to commitment attractive.
+Of course, in other applications this would have to be decided on a case-by-case basis.
+%Even a sophisticated machine learning-based exercise is only able to decrease the fraction of borrowers mis-targeted less than half percentage points relative to simply assigning everyone to commitment (from 9.78\% to 9.59\%).
+and a logit-based targeting rule actually does slightly worse than universal commitment.
+
+Where lenders have no incentive to engage in veiled paternalism and customers display inefficiently low demand for it, financial policy regulation may prove an attractive option.
+Pawnshops, along with other over-collateralized credit products such as payday lending, exist in an environment where the lender may desire customers to lose their collateral on the loan, hurting especially low-income populations who are its main users.
+With a now well-established toolkit of regular small payments and incentives delivering small default rates in microfinance, regulators may fruitfully investigate the possibility of requiring pawnbrokers to embed features of commitment and regularity into their repayment structures in more consistent ways.\footnote{If employed at scale in a competitive lending sector this would redistribute welfare from those who would have repaid (whose interest rates must now rise to cover lower returns from collateral seizure) towards those who would only repay in the presence of commitment.
+In a setting of lender market power however, redistribution from lenders to borrowers could occur.}
 An important question for future research will be the extent to which borrowers are able to learn about the benefits of commitment over time, making it so that temporary, lighter-touch policies could achieve lasting benefits for borrowers.
@@
 Each column is a different regression for different outcomes on an indicator for the forced and choice arms, following specification in equation \ref{basic_reg}.
-Columns (1) \& (7) analyze our core financial cost measures, while the rest of the columns decompose these into finer components as follows:
-
-\begin{align*}
-    \underbrace{\text{Financial Cost}_i}_{(1)} =&  \underbrace{\sum_t P^i_{it}}_{\underset{(2)}{\text{Payments to interests}}}  +\underbrace{\sum_t P^f_{it}}_{\underset{(3)}{\text{Payments of fees}}} + \underbrace{\overbrace{\mathds{1}(\text{Default}_i)}^{(6)}\times (\text{Val-Loan Diff}_i}_{\underset{(5)}{\text{Cost of losing pawn}}} + \underbrace{\sum_t P^c_{it}}_{\underset{(4)}{\text{Payments to capital}}})
-\end{align*}
+Columns (1) \& (7) analyze our core financial cost measures, while the rest of the columns decompose these into finer components.
+
+% \begin{align*}
+%     \underbrace{\text{Financial Cost}_i}_{(1)} =&  \underbrace{\sum_t P^i_{it}}_{\underset{(2)}{\text{Payments to interests}}}  +\underbrace{\sum_t P^f_{it}}_{\underset{(3)}{\text{Payments of fees}}} + \underbrace{\overbrace{\mathds{1}(\text{Default}_i)}^{(6)}\times (\text{Val-Loan Diff}_i}_{\underset{(5)}{\text{Cost of losing pawn}}} + \underbrace{\sum_t P^c_{it}}_{\underset{(4)}{\text{Payments to capital}}})
+% \end{align*}
 
@@
 
-\begin{figure}[H]
-     \caption{Contract Terms Summary}
-    \label{PaperSlip}
-    \begin{center}
-    %\begin{subfigure}{0.65\textwidth}
-    %\caption{Receipt for client}
-     %   \centering
-        \includegraphics[width=0.65\textwidth]{Figuras/TicketLenderP.png}
-    %\end{subfigure}
-
-    %\vspace{3ex}
-    %\begin{subfigure}{0.65\textwidth}
-    %\caption{Personal promise signed by client}
-     %   \centering
-    %    \includegraphics[width=\textwidth]{Figuras/Personal Promise2.png}
-    %\end{subfigure}
-    \end{center}
-    \scriptsize
-        We show a sample receipt that was given to clients that got assigned to the fee-forcing contract (the font and format were changed to protect Lender's P identity).
-We want to highlight the salience of some items.
-First the title clearly indicated which contract the client has (arrow 1).
-Second, in the case of the fee contract it clearly indicates that there is a fee for paying late equivalent to 2\% of the value of the monthly payment (arrow 2).
-Third, there is a calendar for payments clearly specifying the dates and amounts to pay each month.
-%The bottom panel of the figure shows a ``promise slip'', the paper that those who were assigned (or chose) to the monthly payment with promise had to sign to make the promise salient.
-It emphasizes that the client is giving his word, and that the promise is not a legal document.
-\end{figure}
-
-\begin{figure}[H]
-     \caption{Explanatory Material}
-    \label{ExplanatoryMaterial}
-    \begin{center}
-    \begin{subfigure}{\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/micas.pdf}
-    \end{subfigure}
-    \end{center}
-    \scriptsize
-        This is a (translated) sample information slide shown to clients. The real ones were twice the size of this figure and were laminated. Different ones were shown for each treatment arm.
-\end{figure}
-
-\cleardoublepage
-
 \cleardoublepage
@@
 \end{comment}
-
-\vspace{.3in}
-\begin{figure}[H]
-    \caption{Fan \& Park bounds for benefit in APR\%}
-    \label{fan_park_bounds}
-    \begin{center}
-    \begin{subfigure}{0.75\textwidth}
-        \caption{APR}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/fan_park_bounds_apr.pdf}
-    \end{subfigure}
-    \end{center}
-        \scriptsize
-    This figure depicts the \cite{fan2010sharp} bounds on the distribution $F_\Delta$ of individual treatment effects $\Delta \equiv (Y_1 - Y_0)$, described in Section \ref{sec:bounds}, for the APR outcome.
-    The dark red curve and light red shaded region give the estimated upper bound function $\overline{F}$ for $F_\Delta$ and associated (pointwise) 95\% confidence interval. 
-    The dark blue curve and light blue shaded region give the estimated lower bound function $\underline{F}$ for $F_\Delta$ and associated (pointwise) 95\% confidence interval.
-    Confidence intervals are computed using the asymptotic distribution for the bounds. See \cite{fan2010sharp} for details.
-    The bounds are pointwise sharp: at any specified value of $\delta$ the bounds $\underline{F}(\delta) \leq F_\Delta(\delta) \leq \overline{F}(\delta)$ cannot be improved without imposing additional assumptions.
-    Evaluating the bounds at $\delta = 0$, we see that between 23\% and 97\% of borrowers have a positive individual treatment effect.
-    This is greater than the share of borrowers who chose commitment: 11\%.
-%\textit{Do file: } \texttt{fan\_park\_bnds.do}       
-\end{figure}
 
@@
 \begin{figure}[H]
-    \caption{Partition of TUT by behavioral variables}
+    \caption{Heterogeneity of the TUT by behavioral variables}
     \label{tut_beh_partition}
@@
 In each panel, we present results for the full set of borrowers who answered the survey question or questions needed to determine $X_i$.
-From the left panel, we see that TUT does not appear to vary with present bias.
+From the left panel, we see that TUT does not appear to be higher among present-biased borrowers.
 In contrast, the right panel suggests that the positive and significant overall TUT is driven by individuals who are ``sure-confident,'' i.e.\ borrowers who report that they are certain to recover their pawn.
@@
 
-\begin{figure}[H]
-    \centering
-  \caption{Cumulative Distribution Function of Conditional ATE Estimates}
-  \includegraphics[width=0.75\textwidth]{Figuras/cdf_CATE.pdf} 
-    \label{fig:CATEsurvival}
-\end{figure}
-
-This figure shows the share of borrowers who benefit from forced commitment, where ``benefit'' is defined as having an estimated conditional average treatment effect (ATE) above a specified threshold value.
-Results are based on the causal forest model from Section \ref{sec:RF}.
-The solid line equals $1 - F_\text{ATE}(\delta)$ where $F_\text{ATE}(\delta)$ denotes the CDF corresponding to the density of conditional ATE estimates from Figure \ref{heterogeneous_effects}.
-The blue shaded regions are associated 95\% confidence intervals.
-We estimate that at least 91\% of borrowers have a positive conditional ATE.
-%\textit{Do file: }  \texttt{cdf_CATE.do}
-
-\cleardoublepage
-
-\begin{figure}[H]
-    \caption{Conditional ATEs from ``wide'' and ``narrow'' covariate sets}
-    \label{wide_narrow_forests}
-    \begin{center}
-    \begin{subfigure}{0.75\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/scatter_hist_wide_narrow.pdf}
-    \end{subfigure}
-    \end{center}
-      \scriptsize  This figure plots the relationship between the causal forest conditional ATE estimates from Section \ref{sec:RF} that use the ``wide'' set of covariates (all intake survey responses) and those based on a restricted ``narrow'' set of covariates (age, gender, HS education, and previous borrowing).
-The scatterplot graphs one estimate versus the other, with the ``wide'' covariate set on the horizontal axis and the ``narrow'' set on the vertical axis.
-The density plots on each axis show the estimated marginal distribution of conditional ATEs under each covariate set.
-The density for the ``wide'' covariate set is considerably more dispersed, as the causal forest based on this set of covariates captures considerably more treatment effect heterogeneity.
-
-%\textit{Do file: } \texttt{wide_narrow_forests.do}       
-\end{figure}
-
-\begin{figure}[H]
-    \caption{Targeting rules}
-    \label{targeting_rules}
-    \begin{center}
-    \begin{subfigure}{0.75\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/wide_narrow_rule.pdf}
-    \end{subfigure}
-    \end{center}
-      \scriptsize   This figure plots the percentage of borrowers who would benefit from a program in which commitment is targeted using the ``narrow'' covariate set (age, gender, HS education, and previous borrowing).
-In this exercise ``benefit'' is defined to mean having a conditional ATE above a particular threshold, taking the estimated conditional effects from the ``wide'' causal forest as ground truth.
-The plot compares the estimated percentage of borrowers who benefit, along with associated 95\% confidence bands, for three targeting rules: universal forced commitment in blue, targeting based on a random forest classification model in green, and targeting based on the logit model in red.
-For each of the classification models, the outcome variable is an indicator for whether the CATE estimate from the ``wide'' random forest model is positive.
-Each of the classification models produces an estimated probability of a positive CATE.
-For each, the assignment rule ranks borrowers by this estimated probability, and assigns the highest 92\% to forced commitment, to match the overall percentage of borrowers with positive estimated CATEs from the ``wide'' random forest model.
-Because this is an in-sample exercise, it overstates the actual performance of logit and RF-based targeting.
-      %, the top \hl{XXX\%} of Both targeted Both of the targeted assignment rules are assigned by a the ``narrow'' causal forest in green, and targeting based on the logit model in red.
-The causal forest rule assigns a borrower to commitment if her estimated conditional ATE from the ``narrow'' covariate set is positive; the logistic regression rule assigns her to commitment if the estimated probability that her conditional effect is positive is greater than 0.5.
-      %\todo[inline]{@Issac: Have I described this correctly? Also, is this an out-of-sample exercise. In other words, are we using a holdout sample to make these comparisons?}
-
-      %This figure plots the (reversed) cumulative densities of the estimated benefits from the casual forest for three different rules.
-The blue line plots the HTEs from the `wide' random forest for the Forcing arm, which we take as the ground truth for actual impacts.
-The green line plots HTEs if we first target individuals using the variables in the `narrow' forest, and only assign individuals to commitment if they are on a leaf whose predicted forcing benefit is positive.
-The red line uses a logit regression to predict which individuals benefit from treatment, and assigns all individuals to the arm predicted to be best for them.
-
-\end{figure}
-
 % \begin{figure}[H]

### 2023-11-25 donde.tex
fix order of level in potential outcomes in tot-tut table

@@
 
-If we could perfectly measure present bias \textcolor{teal}{and sophistication}, we could divide the sample into three groups: sophisticated hyperbolics (who chose commitment), time-consistent non-choosers (for whom forcing will not be effective), and na\"{i}ve hyperbolic non-choosers (who will benefit from forced commitment).
+If we could perfectly measure present bias and sophistication, we could divide the sample into three groups: sophisticated hyperbolics (who chose commitment), time-consistent non-choosers (for whom forcing will not be effective), and na\"{i}ve hyperbolic non-choosers (who will benefit from forced commitment).
 %If present bias fully explains the low take-up rate of voluntary commitment, we should find that the TUT for present-biased borrowers  is positive while the TUT for all other borrowers is not.

### 2023-11-30 donde.tex
submissions

@@
 Ricardo Olivares, Gerardo Melendez, and Alonso de Gortari provided excellent research assistance and Erick Molina helped with formatting.
-Jose Maria Barrero, Andrei Gomberg, Emilio Gutierrez, David Laibson, Aprajit Mahajan, Matt Rabin, Charlie Sprenger, and seminar participants at ITAM, USC, MSU, and UCSD provided valuable feedback.}}
+Jose Maria Barrero, Andrei Gomberg, Emilio Gutierrez, David Laibson, Aprajit Mahajan, Matt Rabin, Charlie Sprenger, and seminar participants at ITAM, USC, MSU, and UCSD provided valuable feedback.
+Research assistance was financed through faculty grants at ITAM.
+Our research partner had no say in the results.}}
 \author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira \and Francis J.\ DiTraglia   \thanks{Seira:  MSU, \url{enrique.seira@gmail.com} (corresponding author); McIntosh:  University of California San Diego, \url{ctmcintosh@ucsd.edu}; Meza: Harvard University, \url{isaacmezalopez@g.harvard.edu}; Sadka: ITAM, \url{jsadka@itam.mx}; DiTraglia: Oxford, \url{francis.ditraglia@economics.ox.ac.uk}} }

### 2023-12-02 ECTA submission/OA_ecta.tex
prepare for ecta submission

--- 2023-11-22 OA.tex
@@
-%  \documentclass[oneside,11pt]{article}
-
-% \input{preamble.tex}
-% %%% HELPER CODE FOR DEALING WITH EXTERNAL REFERENCES
-% \usepackage{xr}
-% \makeatletter
-% \newcommand*{\addFileDependency}[1]{
-%   \typeout{(#1)}
-%   \@addtofilelist{#1}
-%   \IfFileExists{#1}{}{\typeout{No file #1.}}
-% }
-% \makeatother
-
-% \newcommand*{\myexternaldocument}[1]{
-%     \externaldocument{#1}
-%     \addFileDependency{#1.tex}
-%     \addFileDependency{#1.aux}
-% }
-
-% %\myexternaldocument{OA}
-
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% DOCUMENT
-% \begin{document}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% APPENDIX 
-\setcounter{table}{0}
-\setcounter{figure}{0}
-\setcounter{section}{0}
-\pagenumbering{gobble}
-
-\begin{center}
-	\LARGE The limits of self-commitment and private paternalism \\[0.5em]
-	\Large{Appendix $-$ For Online Publication} \\[1em]
-	\large \author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira \and Francis J.\ DiTraglia}
-\end{center}
-
-\appendix
 \pagenumbering{arabic}
@@
 
-%\renewcommand{\cftparskip}{0em} % NOT NEEDED
-\renewcommand\cftsecdotsep{\cftdotsep}
-\renewcommand\cftsubsecdotsep{\cftnodots}
-\renewcommand{\cftsecnumwidth}{6em}
- \renewcommand{\cftpnumalign}{r}
-%\renewcommand{\cftsecleader}{\normalfont\cftdotfill{\cftsecdotsep}}
-
-\renewcommand{\cftsecleader}{\cftdotfill{\cftsecdotsep}\hspace{1.8em}}
-%\renewcommand{\cftsecpagefont}{20em}
-%\renewcommand{\cftfignumwidth}{6em}
-%\renewcommand{\cfttabnumwidth}{3.3em}
-
-%\tableofcontents
-\etocdepthtag.toc{mtappendix}
-\etocsettagdepth{mtchapter}{none}
-\etocsettagdepth{mtappendix}{subsection}
-
-\setstretch{0.9}
-%\renewcommand\contentsname{} % the empty name
-
-\begingroup
-\let\clearpage\relax
-%\vspace{-1.5em} % the removed space. Set as appropriate
-\tableofcontents
-\endgroup
-
-\newpage
+\begin{frontmatter}
+
+\title{The controlled choice design and private paternalism in pawnshop borrowing - ONLINE APPENDIX}
+\runtitle{The controlled choice design and private paternalism}
+
+\begin{aug}
+% use \particle for den|der|de|van|von (only lc!)
+% [id=?,addressref=?,corref]{\fnms{}~\snm{}\ead[label=e?]{}\thanksref{}}
+%
+%% e-mail is mandatory for each author
+%
+%%% initials in fnms (if any) with spaces
+%
+\author[id=au1,addressref={add1}]{\fnms{Craig}~\snm{McIntosh}\ead[label=ee1]{ctmcintosh@ucsd.edu}}
+\author[id=au2,addressref={add2}]{\fnms{Isaac}~\snm{Meza}\ead[label=ee2]{isaacmezalopez@g.harvard.edu}}
+\author[id=au3,addressref={add3}]{\fnms{Joyce}~\snm{Sadka}\ead[label=ee3]{jsadka@itam.mx}}
+\author[id=au4,addressref={add4}]{\fnms{Enrique}~\snm{Seira}\ead[label=ee4]{enrique.seira@gmail.com}}
+\author[id=au5,addressref={add5}]{\fnms{Francis J.}~\snm{DiTraglia}\ead[label=ee5]{francis.ditraglia@economics.ox.ac.uk}}
+
+% Addresses
+\address[id=add1]{%
+\orgdiv{Department of Economics}
+\orgname{University of California San Diego}}
+
+\address[id=add2]{%
+\orgdiv{Department of Economics}
+\orgname{Harvard University}}
+
+\address[id=add3]{%
+\orgdiv{Department of Economics}
+\orgname{Instituto Tecnologico Autonomo de Mexico}}
+
+\address[id=add4]{%
+\orgdiv{Department of Economics}
+\orgname{Michigan State University}}
+
+\address[id=add5]{%
+\orgdiv{Department of Economics}
+\orgname{University of Oxford}}
+\end{aug}
+
+\end{frontmatter}
+
+\begin{appendix}
 
 \section{Treatment Explanation Materials and Pictures}
-\vspace{.2in}
 
@@
 
-\begin{figure}[H]
+\begin{figure}[!htb]
      \caption{Contract Terms Summary}
@@
     \begin{center}
-    %\begin{subfigure}{0.65\textwidth}
-    %\caption{Receipt for client}
-     %   \centering
-        \includegraphics[width=0.65\textwidth]{Figuras/TicketLenderP.png}
-    %\end{subfigure}
-
-    %\vspace{3ex}
-    %\begin{subfigure}{0.65\textwidth}
-    %\caption{Personal promise signed by client}
-     %   \centering
-    %    \includegraphics[width=\textwidth]{Figuras/Personal Promise2.png}
-    %\end{subfigure}
-    \end{center}
-    \scriptsize
-        We show a sample receipt that was given to clients that got assigned to the fee-forcing contract (the font and format were changed to protect Lender's P identity).
+        \includegraphics[width=0.7\textwidth]{Figuras/TicketLenderP.png}
+    \end{center}
+    \legend{We show a sample receipt that was given to clients that got assigned to the fee-forcing contract (the font and format were changed to protect Lender's P identity).
 We want to highlight the salience of some items.
@@
 Second, in the case of the fee contract it clearly indicates that there is a fee for paying late equivalent to 2\% of the value of the monthly payment (arrow 2).
-Third, there is a calendar for payments clearly specifying the dates and amounts to pay each month.
-%The bottom panel of the figure shows a ``promise slip'', the paper that those who were assigned (or chose) to the monthly payment with promise had to sign to make the promise salient.
-It emphasizes that the client is giving his word, and that the promise is not a legal document.
-\end{figure}
-
-\begin{figure}[H]
+Third, there is a calendar for payments clearly specifying the dates and amounts to pay each month.}
+\end{figure}
+
+\begin{figure}[!htb]
      \caption{Explanatory Material}
@@
         \centering
-        \includegraphics[width=\textwidth]{Figuras/micas.pdf}
-    \end{subfigure}
-    \end{center}
-    \scriptsize
-        This is a (translated) sample information slide shown to clients. The real ones were twice the size of this figure and were laminated. Different ones were shown for each treatment arm.
-\end{figure}
-
-\cleardoublepage
+        \includegraphics[width=0.7\textwidth]{Figuras/micas.pdf}
+    \end{subfigure}
+    \end{center}
+    \legend{ This is a (translated) sample information slide shown to clients. The real ones were twice the size of this figure and were laminated. Different ones were shown for each treatment arm.}
+\end{figure}
 
@@
 
-\begin{figure}[H]
+\begin{figure}[!htb]
      \caption{Some Pawnshops}
@@
     \end{center}
-    \scriptsize
-        This figure  shows pictures of pawnshops in Mexico city. They do not necessarily coincide with Lender P for confidentiality. 
-\end{figure}
-
-\vspace{.1in}
-\begin{figure}[H]
+   \legend{ This figure  shows pictures of pawnshops in Mexico city. They do not necessarily coincide with Lender P for confidentiality. }
+\end{figure}
+
+\begin{figure}[!htb]
      \caption{Gold buyers next to pawnshops}
@@
     \end{center}
-    \scriptsize
-        This figure shows pictures of gold buyers next to pawnshops in Mexico city. They do not necessarily coincide with Lender P for confidentiality. 
-\end{figure}
-
-\begin{comment}
-\\
-\begin{table}[H]
-\caption{Number of pawns balance before and after the experiment}
-\label{num_pawns_bal}
-\begin{center}
-\scriptsize{\input{./Tables/num_pawns_bal.tex}}
-\end{center}
- \scriptsize 
-%\textit{Do file: } \texttt{num\_pawns\_bal.do}
-\end{table}
-\end{comment}
-%\todo[inline]{removed}
-
-\newpage
+    \legend{  This figure shows pictures of gold buyers next to pawnshops in Mexico city. They do not necessarily coincide with Lender P for confidentiality. }
+\end{figure}
+
+\subsection{Descriptives consistent with overconfidence}
+
+\vspace{.2in}
+\begin{figure}[!htb]
+    \caption{Behavior of borrowers who lost their pawn}
+    \label{proxy_naive}
+    \begin{center}
+    \begin{subfigure}{0.40\textwidth}
+        \caption{Elapsed days to first payment}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_firstdays_default.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.40\textwidth}
+        \caption{Elapsed days to last payment}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_days_default.pdf}
+    \end{subfigure}
+        \begin{subfigure}{0.40\textwidth}
+        \caption{Payments as \% of loan}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_percpay_default.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.40\textwidth}
+        \caption{Number of payments}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_numpay_default.pdf}
+    \end{subfigure}
+    \end{center}
+       \legend{ This figure provides more details on the behavior of clients who were assigned to the control group and did not recover their pawn.
+Panel (a) shows a histogram of days elapsed from the pawn to the first payment, while panel (b) displays a histogram of days elapsed until the last payment.
+Some borrowers make payments after day 105, the end of the grace period: if they pay all interest owed, they can ``restart'' the loan.
+This amounts to starting a new loan with the same conditions and same pawn.
+Panel (c) shows a histogram of the fraction of the loan paid, while panel (d) presents a barplot of the number of times that borrowers went to the branch to make payments.}
+      %\textit{Do file: }  \texttt{hist\_den\_default.do}
+\end{figure}
+
+\section{Internal Validity}
+
 \subsection{Survey}   \label{app:survey_data}
-
-\vspace{.2in}
-
-\normalsize
-\linespread{1.25}
-%Really force it to normal size and linespread
-\normalsize
-\linespread{1.25}
 
@@
 
-\cleardoublepage
-
-\begin{table}[H]
+\begin{table}[!htb]
 \caption{Baseline survey questions (translated to English)}
@@
 \end{center}
-\scriptsize
-Translation of the baseline questionnaire.
+\legend{ Translation of the baseline questionnaire.}
 \end{table}
 
-\cleardoublepage
-
-\newpage
-\subsection{Descriptives consistent with overconfidence}
-
-\vspace{.2in}
-\begin{figure}[H]
-    \caption{Behavior of borrowers who lost their pawn}
-    \label{proxy_naive}
-    \begin{center}
-    \begin{subfigure}{0.40\textwidth}
-        \caption{Elapsed days to first payment}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_firstdays_default.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.40\textwidth}
-        \caption{Elapsed days to last payment}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_days_default.pdf}
-    \end{subfigure}
-        \begin{subfigure}{0.40\textwidth}
-        \caption{Payments as \% of loan}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_percpay_default.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.40\textwidth}
-        \caption{Number of payments}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_numpay_default.pdf}
-    \end{subfigure}
-    \end{center}
-        \scriptsize 
-        This figure provides more details on the behavior of clients who were assigned to the control group and did not recover their pawn.
-Panel (a) shows a histogram of days elapsed from the pawn to the first payment, while panel (b) displays a histogram of days elapsed until the last payment.
-Some borrowers make payments after day 105, the end of the grace period: if they pay all interest owed, they can ``restart'' the loan.
-This amounts to starting a new loan with the same conditions and same pawn.
-Panel (c) shows a histogram of the fraction of the loan paid, while panel (d) presents a barplot of the number of times that borrowers went to the branch to make payments.
-      %\textit{Do file: }  \texttt{hist\_den\_default.do}
-\end{figure}
-
-\vspace{.1in}
-\section{Internal Validity}
-
-\begin{figure}[H]
+\begin{figure}[!htb]
      \caption{Box-plot across arms}
@@
     \end{center}
-    \scriptsize
-        This figure presents box-plot for the number of pawns and borrowers per branch-day across different arms.
+    \legend{ This figure presents box-plot for the number of pawns and borrowers per branch-day across different arms.
 The solid black line represent the median, while the gray line represent the mean.
 The dots on top of the box-plot represent an implicit CDF.
-\end{figure}
-
-% \begin{figure}[H]
-%      \caption{Number of pawns and borrowers before and after the experiment}
-%     \label{line_pawns_before_after}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/after_before_bal.pdf}
-%     \scriptsize
-%         This figure shows the number of pawns and borrowers before, during, and after the experiment for the different branches.
-% \end{figure}
-
-% \begin{figure}[H]
-%      \caption{No discontinuity in the number of pawns before and after experiment}
-%     \label{rd_pawns}
-%        \begin{center}
-%     \begin{subfigure}{0.45\textwidth}
-%     \caption{Number of pawns - before}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/rd_before_pawns.pdf}
-%     \end{subfigure}
-%         \begin{subfigure}{0.45\textwidth}
-%     \caption{Number of pawns - after}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/rd_after_pawns.pdf}
-%     \end{subfigure}
-%      \begin{subfigure}{0.42\textwidth}
-%     \caption{Number of borrowers - before}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/rd_before_borr.pdf}
-%     \end{subfigure}
-%         \begin{subfigure}{0.45\textwidth}
-%     \caption{Number of borrowers - after}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/rd_after_borr.pdf}
-%     \end{subfigure}
-%     \end{center}
-%     \scriptsize
-%         This figure shows the number of pawns and borrowers before, during, and after the experiment for the different branches.
-% \end{figure}
-
-\begin{table}[H]
+}
+\end{figure}
+
+\begin{table}[!htb]
 \caption{Balance conditional on survey response and question-by-question response rates by treatment arm}
@@
 \end{center}
-\scriptsize
-
-Panel A of this table presents the same information as Panel A of Table \ref{SS}, but restricts attention to the subsample of borrowers who answered at least one question in our baseline survey.
+\legend{ Panel A of this table presents the same information as Panel A of Table \ref{SS}, but restricts attention to the subsample of borrowers who answered at least one question in our baseline survey.
 Conditional on survey response, loan amount and weekday are balanced across treatment arms.
@@
 This panel uses data for borrowers who pawned on the same day as their survey response.
+}
 
@@
 \begin{landscape}
-\begin{table}[H]
+\begin{table}[!htb]
 \caption{Survey Non-response: TUT estimates for respondents to each survey question.}
@@
 \end{center}
-\scriptsize
-
-Some borrowers did not respond to our survey; others only completed part of the survey.
+\legend{ Some borrowers did not respond to our survey; others only completed part of the survey.
 This table computes the TUT effect for a number of sub-groups by survey response, and compares them against the overall TUT effect.
@@
 TUT estimates are quite stable across sub-groups and generally similar to the full-sample estimates.
-Because standard errors increase as sample size falls, some of the sub-group estimates are not statistically significant.
+Because standard errors increase as sample size falls, some of the sub-group estimates are not statistically significant.}
 %\textit{Do file: } \texttt{tut_cond_survey.do}
@@
 
-\newpage
 \section{Main treatment effects: Additional material}
@@
 
-\begin{table}[H]
+\begin{table}[!htb]
 \caption{Multiple-loans robustness check}
@@
 \end{center}
- \scriptsize
- An additional empirical issue generated by repeat pawning is the question of how to handle the treatment status of those who take multiple loans within the experiment.
+ \legend{ An additional empirical issue generated by repeat pawning is the question of how to handle the treatment status of those who take multiple loans within the experiment.
 43\% of borrowers take more than one loan within the study period, and 19\% are assigned multiple treatment statuses on their different loans.
 The issue of sequential endogenous treatments has been extensively studied in the context of school lotteries, where the convention is to use the treatment status from the first exposure (ITT) \citep{cullen2006effect, abdulkadirouglu2011accountability}.\\
-
  This table provides robustness for our main results for different ways to handling the multiplicity of loans.
@@
 The core treatment effects are robust to any of these ways of handling repeat pawning.
+}
 
@@
 
-\begin{figure}[H]
+\begin{figure}[!htb]
     \caption{Determinants of choice}
@@
     \end{center}
-      \scriptsize
-
-      The above figure shows the determinants in a bivariate and multivariate OLS regression of choosing commitment.
+      \legend{  The above figure shows the determinants in a bivariate and multivariate OLS regression of choosing commitment.
 Choice commitment is a binary variable equal to one, whenever subjects choose the forced commitment contract in the choice arm.
+}
 %\textit{Do file: } \texttt{determinants_choice.do}       
@@
 \vspace{.2in}
-\begin{figure}[H]
+\begin{figure}[!htb]
     \caption{Histogram of payments}
@@
     \begin{center}
-    \begin{subfigure}{0.45\textwidth}
+    \begin{subfigure}{0.32\textwidth}
         \caption{Status-quo}
@@
     \end{subfigure}
-    \begin{subfigure}{0.45\textwidth}
+    \begin{subfigure}{0.32\textwidth}
         \caption{Forced commitment}
@@
     \end{subfigure}
-    \begin{subfigure}{0.45\textwidth}
+    \begin{subfigure}{0.32\textwidth}
         \caption{Choice commitment}
@@
     \end{center}
-     \scriptsize
-     This figure shows the schedule of payments for each treatment arm.
+     \legend{ This figure shows the schedule of payments for each treatment arm.
 In other words it records the time after the loan origination when the borrower makes a payment toward recovery of the pawn.
-We can see that for both the Forced commitment and Choice commitment arm, payments are bunching at the 30 and 60 days, while most payments are done around the due date of the loan (90 days).
+We can see that for both the Forced commitment and Choice commitment arm, payments are bunching at the 30 and 60 days, while most payments are done around the due date of the loan (90 days).}
 
@@
 
-\cleardoublepage
-
 \subsection{Censoring} \label{App_censoring}
-
-\vspace{.2in}
-
-\normalsize
-\linespread{1.25}
-%Really force it to normal size and linespread
-\normalsize
-\linespread{1.25}
 
@@
 
-\vspace{.3in}
-\begin{table}[H]
+\begin{table}[!htb]
 \caption{Bounding censoring} 
@@
 
-\end{table}
- \scriptsize 
- Given the censored loans, i.e.
+ \legend{  Given the censored loans, i.e.
 loans that have not finished by the end of the observation period, we estimate `a la Manski' bounds for these loans, meaning that we impute all loans to either \emph{default}$=1$ or \emph{recovery}$=0$ depending on the treatment arm.
@@
 This predictive model achieves an accuracy rate of 92\% both in-sample and out-of-sample.
-
- Note that in all panels we maintain significant results for Financial Cost as dependent variable, while only in the most conservative scenario (Panel B) we lose significance for the APR outcome.
-
-\begin{figure}[H]
+ Note that in all panels we maintain significant results for Financial Cost as dependent variable, while only in the most conservative scenario (Panel B) we lose significance for the APR outcome. }
+ \end{table}
+
+\begin{figure}[!htb]
         \caption{Interpolation on bounding censoring}
@@
     \end{center}
-     \scriptsize  The next figure aims to answer the following question: For how many loans in the control arm can we impute recovery, and for how many in the treatment arm can we impute default and still have significance?
+     \legend{  The next figure aims to answer the following question: For how many loans in the control arm can we impute recovery, and for how many in the treatment arm can we impute default and still have significance?
      This figure shows exactly the boundary separating significance when we vary the percentage of imputed censored loans with recovery and default respectively for control and treatment.
@@
 The `x' indicates the proportions imputed by the lasso logit model, and the different lines correspond to setting different significance levels.
-We do not include the plot for financial cost, since for any imputation we still have significant results.
+We do not include the plot for financial cost, since for any imputation we still have significant results.}
 
@@
 
-\begin{figure}[H]
+\begin{figure}[!htb]
         \caption{Survival graph}
@@
     \end{center}
-     \scriptsize  This Figure shows the CDF of loan completion either default or recovery in Panel (a), or loan recovery in Panel (b), by the number of days since first pawn.
+     \legend{  This Figure shows the CDF of loan completion either default or recovery in Panel (a), or loan recovery in Panel (b), by the number of days since first pawn.}
      %\textit{Do file: }  \texttt{survival\_graph.do}
@@
 
-\begin{figure}[H]
+\begin{figure}[!htb]
         \caption{\% of payment over time}
@@
     \end{center}
-     \scriptsize  This Figure shows the accumulated percentage of recovery in time by treatment arm. 
+     \legend{  This Figure shows the accumulated percentage of recovery in time by treatment arm. }
      %\textit{Do file: }  \texttt{cumulative\_porc\_pay\_time.do}
@@
 
-\newpage
 \section{Alternative explanations}
 
-\vspace{.2in}
 \subsection{Learning}
-\normalsize
+
 Table \ref{learning_table} presents information about borrowers' \emph{future} pawning behavior as a function of treatment assignment.
@@
 
-\vspace{.1in}
-\begin{table}[H]
+\begin{table}[!htb]
         \caption{Effect of Prior Assignment on Subsequent Choice}
@@
 \end{center}
- \scriptsize
-
-Column (1) reports results for the 228 borrowers who returned to pawn again at a day/branch that was randomly assigned to the choice arm, enabling us to observe whether they chose commitment or the status quo contract.
+ \legend{ Column (1) reports results for the 228 borrowers who returned to pawn again at a day/branch that was randomly assigned to the choice arm, enabling us to observe whether they chose commitment or the status quo contract.
 Each row presents a difference in mean commitment take-up rates and associated standard errors.
@@
 The second row (ITT) compares borrowers who were initially assigned to the choice commitment condition to those who were not.
-Whereas column (1) conditions on the (endogenously) selected sample of borrowers who return to pawn again, column (2) considers the full sample by re-defining the ``outcome'' to be an indicator for whether a borrower pawned again on a day when choice was offered \emph{and} chose commitment.
+Whereas column (1) conditions on the (endogenously) selected sample of borrowers who return to pawn again, column (2) considers the full sample by re-defining the ``outcome'' to be an indicator for whether a borrower pawned again on a day when choice was offered \emph{and} chose commitment.}
 
@@
 
-\vspace{.3in}
-
 \subsection{Discount rates}
 
-\begin{figure}[H]
+\begin{figure}[!htb]
         \caption{Financial benefit TUT effect for different discount rates}
@@
     \end{center}
-     \scriptsize This Figure re-estimates the treatment on the untreated (TUT) effect from Table \ref{tot_tut}, introducing a daily discount factor in the definition of financial benefit.
+     \legend{ This Figure re-estimates the treatment on the untreated (TUT) effect from Table \ref{tot_tut}, introducing a daily discount factor in the definition of financial benefit.
 The discount factor reflects time preference, i.e.\ the fact that payments made in the present are more costly for the borrower.
@@
 For higher discount rates, the adjusted financial cost will be higher, so the financial cost \emph{savings} will be lower.
-As seen from the figure, borrowers would need to face unrealistically large discount rates to reverse our headline result of a large, positive, and statistically significant TUT effect.
+As seen from the figure, borrowers would need to face unrealistically large discount rates to reverse our headline result of a large, positive, and statistically significant TUT effect.}
      %It estimates the effect of the treatment arms  for different discount factors, where a discount factor of 1 corresponds exactly to the estimate of column 1 of Table \ref{main_impact_table}.
@@
 
-\begin{comment}
-
-\vspace{.2in}
-\begin{table}[H]
-\caption{FOSD by demographic groups \textcolor{red}{\hl{MAY NEED UPDATING}}}
-\label{stochastic_dominance}
-\begin{center}
-\scriptsize{\input{./Tables/dominance.tex}}
-\end{center}
- \footnotesize
-This table does two things.
-First, it tests whether the observed empirical distribution of financial cost is well approximated by a log normal.
-It does this using two tests, the Anderson-Darling and the Kolmogorov-Smirnoff tests.
-Second, it fits a log normal distribution by maximum likelihood to observed empirical distribution of financial cost, separately for the fee-forcing arm and the status-quo arm.
-Using the fitted log normal, it tests whether the fee-forcing financial cost distribution would be preferred by any expected utility agent using Proposition \ref{lognormal_fosd} below.
-The different rows of the table do this for different sub-populations.
-The first row of the table does it for every client in the fee forcing and status quo arms.
-The ``*'' show that we cannot reject at the 5\% level that both distribution are log normal for any of the two tests.
-The column entitled ``Dominance'' shows whether any client that dislikes higher cost would prefer the fee-forcing cost distribution over the status quo one, with $\succeq_{1}$ meaning he should (with $\succeq_{1}^*$ indicating the difference is statistically significant).
-It turns out to be the case that for the overwhelming majority of sub-populations, the conditions of preferring the fee-forcing distribution hold.
-%\textit{Do file: } \texttt{stoch\_dominance.do}
-\end{table}
-
-\newpage
-
-\vspace{.2in}
-\begin{prop}
-\label{lognormal_fosd}
-
-Let $F$ and $G$ be the cumulative distributions of two alternative log-normal prospects. The following are equivalent:
-
-\begin{enumerate}[(a)]
-    \item For every weakly decreasing utility function $u$: $E_{F}(u(FC))\leq E_G(u(FC))$
-    \item $E_F \log(FC)\geq E_G\log(FC)$ and $Var_F \log(FC)= Var_G\log(FC)$
-\end{enumerate}
-\end{prop}
-
-\begin{proof}
-See Theorem 4 in \cite{lognormal_dominance}.
-\end{proof}
-
-\vspace{.1in}
-\begin{prop}
-\label{eq_fosd}
-
-This is a standard result. 
-\\
-\vspace{.1in}
-The following are equivalent:
-\begin{enumerate}[(a)]
-    \item For every weakly decreasing utility function $u$: $E_{sq}(u(FC))\leq E_{fee}(u(FC))$
-    \item $F_{sq}(FC)\leq F_{fee}(FC)$ 
-\end{enumerate}
-
-\end{prop}
-\begin{proof} \;
-
-[$(a)\Longrightarrow (b)$] Suppose  $(b)$ does not hold. So there exists $FC^*$ such that $F_{sq}(FC^*)>F_{fee}(FC^*)$, Define $u:=\mathds{1}_{FC\leq FC^*}$. Then
-\[E_{sq}(u(FC)) = \int u(FC)dF_{sq} = F_{sq}(FC^*)>F_{fee}(FC^*)= \int u(FC)dF_{fee} =E_{fee}(u(FC))\]
-which contradicts $(a)$.\\
-
-[$(a)\Longleftarrow (b)$] On the other hand for $u$ weakly decreasing,
-
-\[\int u(y(FC))dF_{sq}(y(FC)) = \int u(y(FC))dF_{fee}(FC) \leq \int u(FC)dF_{fee}(FC)\]
-with $y(FC) = F_{sq}^{-1}F_{fee}(FC)$.
-
-\end{proof}
-
-Note the proof was done in the case of absolutely continuous and strictly increasing distribution functions $F_{sq}$ and $F_{fee}$.
-
-\end{comment}
-
-\newpage
-
-\normalsize
-\linespread{1.25}
-%Really force it to normal size and linespread
-\normalsize
-\linespread{1.25}
-
-\begin{comment}
-\section{Causal Forest and individual predictions of `Mistakes'}
-
-    \begin{figure}[H]
-        \caption{Example of a Causal Tree \textcolor{red}{WHAT IS THE DIFFERENCE OF THIS AND FIGURE OA-17?}}
-        \label{causal_tree_example}
-        \begin{center}
-\includegraphics[width=\textwidth]{Figuras/ct_eff.pdf}
-\end{center}
-     \scriptsize This Figure shows an example of the splits for the leaves that emerge in our data for the Athey et al (2019) Causal Forest estimation.  
-        \end{figure}
-\end{comment}
-
 \subsection{Sure Confidence} \label{App_sureconfidence}
 
-\begin{figure}[H]
+\begin{figure}[!htb]
     \caption{Determinants sure confidence}
@@
     \end{center}
-      \scriptsize
-
-      The above figure shows the determinants in a bivariate and multivariate OLS regression of sure confidence among the non-choosers.
-Sure confidence is a binary variable defined to be one when people report a 100\% probability of recovery.
+     \legend{ The above figure shows the determinants in a bivariate and multivariate OLS regression of sure confidence among the non-choosers.
+Sure confidence is a binary variable defined to be one when people report a 100\% probability of recovery.}
 %\textit{Do file: } \texttt{determinants_sure_confidence.do}       
 \end{figure}
-
-\cleardoublepage
 
@@
 
-%\todo[inline]{Discuss the results here.}
-
-%\todo[inline]{Issac: re-run this exercise with removing the propensity score weights $p(Z)$. Presumably it shouldn't change anything, but it's simpler to explain what we do and probably less noisy}
-
-%\begin{table}[H]
-%\begin{center}
-%\scriptsize{\input{./Tables/test_calibration_2.tex}}
-%\end{center}
-%\end{table}
-
-%\todo[inline]{Some Questions for Issac: (1) How are we carrying out the sample splitting?
-If we cluster standard errors at the branch-day level, we should take this into account when we split.
-(2) How are you carrying out inference for $\beta_2$?
-Chernozhukov et al discuss two approaches: ``conditional'' and ``variational.'' The former is simpler as it conditions on the training/test split.
-The latter is a bit more involved, since one accounts for uncertainty arising from different splits.
-(3) What are the details of the random forest procedure employed here?
-(Tuning parameters choice, etc.) We should put them into the appendix.}
-
 \subsection{Bounds, FOSD and Rank Invariance} \label{bounds_FOSD}
 
-\vspace{.3in}
-\begin{figure}[H]
+\begin{figure}[!htb]
     \caption{Fan \& Park bounds for benefit in APR\%}
@@
     \begin{center}
-    \begin{subfigure}{0.75\textwidth}
+    \begin{subfigure}{0.5\textwidth}
         \caption{APR}
@@
     \end{center}
-        \scriptsize
-    This figure depicts the \cite{fan2010sharp} bounds on the distribution $F_\Delta$ of individual treatment effects $\Delta \equiv (Y_1 - Y_0)$, described in Section \ref{sec:bounds}, for the APR outcome.
+        \legend{ This figure depicts the \cite{fan2010sharp} bounds on the distribution $F_\Delta$ of individual treatment effects $\Delta \equiv (Y_1 - Y_0)$, described in Section \ref{sec:bounds}, for the APR outcome.
     The dark red curve and light red shaded region give the estimated upper bound function $\overline{F}$ for $F_\Delta$ and associated (pointwise) 95\% confidence interval. 
@@
     Evaluating the bounds at $\delta = 0$, we see that between 23\% and 97\% of borrowers have a positive individual treatment effect.
-    This is greater than the share of borrowers who chose commitment: 11\%.
+    This is greater than the share of borrowers who chose commitment: 11\%.}
 %\textit{Do file: } \texttt{fan\_park\_bnds.do}       
@@
 \vspace{.2in}
-\begin{figure}[H]
+\begin{figure}[!htb]
         \caption{Empirical CDF: Forced commitment vs Control FOSF}
@@
     \end{center}
-    \scriptsize This figure plots the empirical CDF of experimental outcomes separately for the control (status quo) in dashes, and forced commitment contracts (solid).
+   \legend{  This figure plots the empirical CDF of experimental outcomes separately for the control (status quo) in dashes, and forced commitment contracts (solid).
 In panel (a), the outcome is APR benefit; in panel (b) the outcome is Financial benefit.
@@
 This can be seen by examining the dotted line, which shows the difference $(\text{Control} - \text{Commitment})$.
+}
     %The dotted line at the bottom of panels (a) and (b)   the empirical cumulative distribution function APR and financial cost of financial cost.
@@
 \vspace{.2in}
-\begin{figure}[H]
+\begin{figure}[!htb]
         \caption{Distribution of treatment effects under rank invariance.}
@@
     \end{center}
-    \scriptsize This figure shows the CDF of individual treatment effects under the assumption of rank invariance, computed from 
+    \legend{  This figure shows the CDF of individual treatment effects under the assumption of rank invariance, computed from 
     \[F_\Delta(\delta) = \int_0^1 \mathbbm{1}\{ F_1^{-1}(u) - F_0^{-1}(u)\leq \delta\}\,\mathrm{d}u\]
-where $F_1^{-1}$ and $F_0^{-1}$ are the quantile functions of $Y_1$ and $Y_0$.
+where $F_1^{-1}$ and $F_0^{-1}$ are the quantile functions of $Y_1$ and $Y_0$.}
     %The dotted line at the bottom of panels (a) and (b)   the empirical cumulative distribution function APR and financial cost of financial cost.
@@
 
-\newpage
-
 \section{Causal Random Forest, HTE, and `mistakes'}
 
-\begin{comment}
-
-    \begin{figure}[H]
-        \caption{Conditional Average Treatment Effect from Random Forest}
-        \label{CATE}
-        \begin{center}
-\includegraphics[width=0.6\textwidth]{Figuras/he_dist_apr_pro_2.pdf}
-\end{center}
-     \scriptsize This Figure plots the densities of the CATE emerging from the Athey et al. (2019) random forest, along with the upper and lower confidence bounds.  
-        \end{figure}
-\end{comment}
-
-\subsection{Example of a Causal Tree}
-
-\vspace{.3in}
-\begin{figure}[H]
+\begin{figure}[!htb]
         \caption{Example Causal Tree}
@@
     \end{center}
-    \footnotesize 
+    \legend{ 
     This figure shows an example of one of the regression trees used to compute the causal forest estimates described in Section \ref{sec:RF}.
-Each tree is constructed from a sequence of recursive binary partitions of the covariate space, with a splitting rule that is targeted to the causal quantity of interest, following the methodology of \cite{atheygrf}.
+Each tree is constructed from a sequence of recursive binary partitions of the covariate space, with a splitting rule that is targeted to the causal quantity of interest, following the methodology of \cite{atheygrf}.}
     %This is one(it is chosen such that it minimizes the pruned cost, that is it is the tree with the smallest root-node impurity) of the honest causal trees in the random forest we use for the estimation of the heterogeneous treatment effect of the fee-forcing contract.
@@
 
-\newpage
-\subsection{Conditional ATE estimates}
-
-\vspace{.3in}
-\begin{figure}[H]
+\begin{figure}[!htb]
     \begin{center}
   \caption{Cumulative Distribution Function of Conditional ATE Estimates}
-  \includegraphics[width=0.75\textwidth]{Figuras/cdf_CATE.pdf} 
+  \includegraphics[width=0.7\textwidth]{Figuras/cdf_CATE.pdf} 
     \label{fig:CATEsurvival}
-    \end{center}
-
-    \scriptsize This figure shows the share of borrowers who benefit from forced commitment, where ``benefit'' is defined as having an estimated conditional average treatment effect (ATE) above a specified threshold value.
+     \legend{This figure shows the share of borrowers who benefit from forced commitment, where ``benefit'' is defined as having an estimated conditional average treatment effect (ATE) above a specified threshold value.
 Results are based on the causal forest model from Section \ref{sec:RF}.
@@
 The blue shaded regions are associated 95\% confidence intervals.
-We estimate that at least 90\% of borrowers have a positive conditional ATE.
+We estimate that at least 90\% of borrowers have a positive conditional ATE.}
+    \end{center}
+
 %\textit{Do file: }  \texttt{cdf_CATE.do}
@@
 
-\cleardoublepage
-
-\begin{figure}[H]
+\begin{figure}[!htb]
     \caption{Conditional ATEs from ``wide'' and ``narrow'' covariate sets}
@@
     \end{subfigure}
-    \end{center}
-      \scriptsize  This figure plots the relationship between the causal forest conditional ATE estimates from Section \ref{sec:RF} that use the ``wide'' set of covariates (all intake survey responses) and those based on a restricted ``narrow'' set of covariates (age, gender, HS education, and previous borrowing).
+    \legend{This figure plots the relationship between the causal forest conditional ATE estimates from Section \ref{sec:RF} that use the ``wide'' set of covariates (all intake survey responses) and those based on a restricted ``narrow'' set of covariates (age, gender, HS education, and previous borrowing).
 The scatterplot graphs one estimate versus the other, with the ``wide'' covariate set on the horizontal axis and the ``narrow'' set on the vertical axis.
 The density plots on each axis show the estimated marginal distribution of conditional ATEs under each covariate set.
-The density for the ``wide'' covariate set is considerably more dispersed, as the causal forest based on this set of covariates captures considerably more treatment effect heterogeneity.
+The density for the ``wide'' covariate set is considerably more dispersed, as the causal forest based on this set of covariates captures considerably more treatment effect heterogeneity.}
+    \end{center}
 
@@
 
-\newpage
 \subsection{Targeting rule comparisons}
 
-\vspace{.3in}
-
-\begin{figure}[H]
+\begin{figure}[!htb]
     \caption{Targeting rules}
@@
     \end{center}
-      \scriptsize   This figure plots the percentage of borrowers who would benefit from a program in which commitment is targeted using the ``narrow'' covariate set (age, gender, HS education, and previous borrowing).
+      \legend{ This figure plots the percentage of borrowers who would benefit from a program in which commitment is targeted using the ``narrow'' covariate set (age, gender, HS education, and previous borrowing).
 In this exercise ``benefit'' is defined to mean having a conditional ATE above a particular threshold, taking the estimated conditional effects from the ``wide'' causal forest as ground truth.
@@
 Because this is an in-sample exercise, it overstates the actual performance of logit and RF-based targeting.
-      %, the top \hl{XXX\%} of Both targeted Both of the targeted assignment rules are assigned by a the ``narrow'' causal forest in green, and targeting based on the logit model in red.
-The causal forest rule assigns a borrower to commitment if her estimated conditional ATE from the ``narrow'' covariate set is positive; the logistic regression rule assigns her to commitment if the estimated probability that her conditional effect is positive is greater than 0.5.
-      %\todo[inline]{@Issac: Have I described this correctly? Also, is this an out-of-sample exercise. In other words, are we using a holdout sample to make these comparisons?}
-
-      %This figure plots the (reversed) cumulative densities of the estimated benefits from the casual forest for three different rules.
-The blue line plots the HTEs from the `wide' random forest for the Forcing arm, which we take as the ground truth for actual impacts.
-The green line plots HTEs if we first target individuals using the variables in the `narrow' forest, and only assign individuals to commitment if they are on a leaf whose predicted forcing benefit is positive.
-The red line uses a logit regression to predict which individuals benefit from treatment, and assigns all individuals to the arm predicted to be best for them.
-
-\end{figure}
-\vspace{.1in}
+}
+
+\end{figure}
 
@@
 
-%We use \cite{atheygrf} \texttt{causal\_forest} of the \texttt{grf} library in $R$. The parameters used were:
-%\scriptsize{\textit{causal\_forest(
-%  X, 
-%  Y, 
-%  W, 
-%  Y.hat = NULL,
-%    W.hat = NULL,
-%    clusters = NULL,
-%    num.trees = 5000,
-%    sample.weights = NULL,
-%    equalize.cluster.weights = FALSE,
-%    sample.fraction = 0.5,
-%    mtry = min(ceiling(sqrt(ncol(X)) + 20), ncol(X)),
-%    min.node.size = 5,
-%    honesty = TRUE,
-%    honesty.fraction = 0.5,
-%    honesty.prune.leaves = TRUE,
-%    alpha = 0.05,
-%    imbalance.penalty = 0,
-%    stabilize.splits = TRUE,
-%    ci.group.size = 2,
-%    tune.parameters = c("alpha", "imbalance.penalty"),
-%    tune.num.trees = 500,
-%    tune.num.reps = 200,
-%    tune.num.draws = 2000,
-%    compute.oob.predictions = TRUE,
-%    num.threads = NULL,
-%    seed = 1)}}
-
-\begin{comment}
-
-\begin{figure}[H]
-        \caption{Single causal tree for the Forced-commitment contract heterogeneous treatment effects}
-    \label{causal_tree2}
-    \begin{center}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/ct_pro_2_apr.pdf}
-    \end{center}
-    \footnotesize
-
-     %\footnotesize{ \textit{RScript: }  \texttt{grf.R}
-\end{figure}
-\end{comment}
-
-%\begin{figure}[H]
-%    \caption{Choice of contracts and treatment effects}
-%    \label{choose_wrong}
-%    \begin{center}
-%        \begin{subfigure}{0.45\textwidth}
-%        \caption{Mistakes in choice arm}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/line_cw_apr_te_cf.pdf}
-
-%   \end{subfigure}
-%        \begin{subfigure}{0.45\textwidth}
-%        \caption{Financial value of mistake}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/money_cw_apr_te_cf.pdf}
-
-%    \bigskip
-
-%    \end{subfigure}
-%        \begin{subfigure}{0.45\textwidth}
-%        \caption{\% better when forced to forced commitment}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/line_better_forceall_apr_te_cf.pdf}
-%        
-%    \end{subfigure}
-    %     \begin{subfigure}{0.45\textwidth}
-    %     \caption{\footnotesize{Effect of CATE benefit vs predicted take-up}}
-    %     \centering
-    %     \includegraphics[width=\textwidth]{Figuras/benefit_choice.pdf}% takeuppr_def.pdf 
-    % \end{subfigure}
-
-%    \end{center}
-%        \scriptsize
-%        In Panel (a) we estimate what the treatment effect of the commitment contract \textit{would have been} for all subjects in the choice arm if they had been forced into the fee-commitment contract.
-To do this we proceed in two steps.
-First, we estimate treatment effects in the forcing arm by comparing the Forced Commitment arm against the status quo arm.
-We let these effects be heterogeneous as a function of our $x$'s using \cite{atheygrf}'s methodology of causal forests.
-Second, we extrapolate these treatment effects based on the choice arm using the same $x$'s.
-Once we have personalized counterfactual treatment effects in the choice arm we calculate what fraction of subjects in the choice arm incurred in financial costs that are  $> z$\% than if they had chosen the opposite contract of what they actually chose, were $z$\% is defined as a fraction of the loan.
-$z$\% is a level of tolerance we can vary and we plot it in the X-axis.
-The left Y-axis measures the fraction of subjects that would have been better by a margin of $z$\% if they changed their choice, and the right Y-axis measures the amount of money ``left on the table''.
-We use bootstrap to tighten the confidence intervals (CIs).
-\cite{atheygrf}'s heterogeneous treatment effect using GRF is asymptotically normal.
-We compute the HTE ($\mu$) together with standard errors ($\sigma$) .
-For every pledge, we draw a random effect from a normal distribution with parameters ($\mu$,$\sigma^2$), and compute via bootstrap the percentage that choose wrong, along normal-approximation CIs (results are robust if we use instead percentile CIs or bias-corrected CIs) .
-This allows us to estimate a distribution for the upper and lower bound CIs, which we then use to obtain a 95\% CI.
-Panel (b) is analogous to Panel (a) except that it does the exercise separately for clients we classified as overconfident ($OC_i:=\mathbbm{1}(P^s_i-\widehat{P_i(X_i)}>0))$ and those we classified as not overconfident.
-Panel (c) simulates what percentage would be better by at least $z$ if we forced everybody of those in the Commitment Choice arm into the fee-commitment contract.
-        % Panel (d) asks whether it is the case that people with larger causal benefits from the Forced Commitment contract would be more likely to select that contract.
-To do this we proceed in two steps as well.
-First we estimate a flexible model of take-up of the fee commitment contract \textit{in the choice arm} using random forests, and from this model obtain a probability $P(x_i)$ of choosing the Forced Commitment contract for a client with characteristics $x_i$.
-We extrapolate this model to clients in the Forced Commitment arm to estimate what would they have chosen if we had given them choice.
-        % Figure (d) plots $\widehat{P(x_i)}$ in the X-axis using a binscatter that splits the X-axis in 100 percentile bins.
-The Y-axis plots the heterogeneous treatment effects of the fee forcing contract on the probability of losing the pawns (more negative means then more likely to recover it), averaged for the respective x-axis bin.
-Positive assortative selection would mean a negative relationship: those who benefit more by treatment and lose the pawn less are \emph{less} likely to choose it.
-Using all bins we estimate a slope of zero in the relationship.
-Using the 80 right most points, we estimate a \textit{positive} relationship.
-        %\textit{Do file: }  \texttt{choose\_wrong\_quant\_wrong.do, choose\_wrong\_quant\_wrong\_decomposition.do}
-%\end{figure}
-
-\vspace{.3in}
-
-\cleardoublepage
-
-\vspace{.4in}
-
-\begin{comment}
-
-\subsection{Take up}
-
-\begin{table}[H]
-    \caption{\textcolor{red}{DELETE--Predicting Take-up: Goodness-of-Fit}}
-    \label{Table_compliance}
-    %\begin{subtable}{1\textwidth}
-    % \centering
-    %    \caption{Take up}
-    %    \scriptsize{\input{./Tables/oos_pago_frec_vol.tex}}
-    %\end{subtable}%
-
-    %\bigskip
-     \begin{subtable}{1\textwidth}
-      \centering
-        \caption{Take up: Choice-fee Arm}
-        \scriptsize{\input{./Tables/oos_pago_frec_vol_fee.tex}}
-    \end{subtable}
-
-      \bigskip
-    \begin{subtable}{1\textwidth}
-      \centering
-        \caption{Take up: Choice-promise Arm}
-        \scriptsize{\input{./Tables/oos_pago_frec_vol_promise.tex}}
-    \end{subtable}
-            \scriptsize
-           \\
-           \\
-           \\
-
-     %\textit{Scripts: } \texttt{pred\_take\_up.do, pfv\_pred.R}
-\end{table}
-
-\vspace{.1in}
-\begin{figure}[H]
-    \caption{\textcolor{red}{DELETE--Out of sample ROC curve}}
-    \label{roc_curve}
-    \begin{center}
-    \begin{subfigure}{0.45\textwidth}
-        \caption{Take-up in Fee Arm}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/Boost/ROC_curve_outsample_pago_frec_vol_fee.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.45\textwidth}
-        \caption{Take-up in Promise Arm}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/Boost/ROC_curve_outsample_pago_frec_vol_promise.pdf}
-    \end{subfigure}
-    \end{center}
-     \scriptsize 
-  %\footnotesize{ \textit{Do file: }  \texttt{pred\_take\_up.do}}
-\end{figure}
-
-\vspace{.3in}
-\begin{figure}[H]
-    \caption{\textcolor{red}{\hl{ARE THESE MADE OBSOLETE BY THE NEXT FIGURE? } Predictors of commitment contract take-up}}
-    \label{interactions_takeup}
-    \begin{center}
-    \begin{subfigure}{0.7\textwidth}
-        \caption{PLM}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/determinants_takeup_reg.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.7\textwidth}
-        \caption{Logit}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/determinants_takeup_logit.pdf}
-    \end{subfigure}
-    \end{center}
-     \scriptsize
-      %\footnotesize{ \textit{Do file: }  \texttt{determinants_takeup.do}}
-\end{figure}
-
-\scriptsize 
-\noindent This figure reports bivariate (and multivariate) regressions of the form $TakeUp = \alpha + \beta \: X_i + \epsilon_i$.
-The figure reports the $\beta$ coefficients for different $X_i$'s along with 95\% confidence intervals.
-Panel (a) uses a linear model.
-Panel (b) specifies a logit model.
-
-\end{comment}
-
-%\subsection{Selection on gains}
-
-%\begin{figure}[H]
-%    \caption{Determinants of treatment effects}
-%    \label{determinants_cate}
-%    \begin{center}
-%    \begin{subfigure}{0.65\textwidth}
-%        \caption{Determinants of CATE}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/blp_cate_apr.pdf}
-%    \end{subfigure}
-
-%    \end{center}
-%     \scriptsize   This figure estimates bivariate \& multivariate double-robust regressions of the estimated CATE of forcing.
-
-%\end{figure}
-%\todo[inline]{This is a figure that is not referenced yet in the paper, but there is a line highlighted in yellow that could use this information.
-While there appears to not be any effect, let's remember that the RF is considering nonlinear interactions between variables, as well as using information of missingness of some survey questions.}
-
-\normalsize
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% APPENDIX B
-\begin{comment}
-
-\newpage
-\section{ Mechanisms }
-
-\subsection{Optimism, Over-Optimism, and the Failure of Self-Commitment}
-\label{overconfidence}
-
-\textcolor{red}{Need to decide whether we want to try to plant our feet on Confidence/Overconfidence as the core `why' of the previous result
-.}
-%\subsubsection{Behavioral: overconfident borrowers demand less (but benefit more)} \label{behavioral}
-
-The leading behavioral explanation in the literature for low demand for commitment is present biased preferences with naivete (e.g.
-\cite{Rabin2018}, \cite{John}, \cite{Laibson2018})  \cite{Laibson2015} shows that the lost flexibility resulting from a commitment contract can limit take-up especially severely when agents are (partially) naive about their self control problem.
-In our context if consumers are (partially) naive about their present bias, they would plan to save more (or spend less) than what they actually end up saving, thus making it be harder to recover their pawn.
-This under-saving will be mitigated in the fee forcing contract since the fee makes them save money to pay part of the loan periodically.
-\ref{appendix_c} formalizes this in a model.
-Another behavioral explanation is that clients may underestimate the likelihood and severity of negative income shocks.
-Both of these explanations predict that clients will be overconfident about their likelihood of pawn recovery.
-Recall that in the control group the client's subjective probability of recovery is on average 93\%, while actual recovery is just 44\%.
-A further piece of evidence consistent with underestimating negative income shocks and with present bias with partial naivete is that a large number of people (25\%) in the control group pay a positive amount toward pawn recovery but end up losing their pawn anyway.
-
-So, overconfidence of recovering the pawn is implied by both present bias preferences with naivete and upward bias in their income expectations.
-But does overconfidence actually predict low demand for commitment empirically?
-It does.
-We define as overconfidence as the reported subjective probability of recovery minus the predicted probability based on the client's characteristics, $P^s_i-\widehat{P_i(X_i)}$.\footnote{We predict $\widehat{P_i(X_i)}$ in two steps.
-In step one we use Lasso with cross validation to tune the regularization parameter to select the most predictive variables $X$.
-The typical present bias question as in \cite{Ashraf} was eliminated in this step.
-In the second step we estimate $\widehat{P_i(X_i)}$ using those variables in a logit model.
-The Lasso selected variables were type of pawn, female, age, has pawned before, has savings, participates in rotating savings, often feels tempted to change plans, would like to have a reminder to pay, and an economic vulnerability index.
-We are careful not to include these variables as controls in Table  \ref{oc_reg}.} There is a large amount of overconfidence in our context.
-Figure \ref{oc_hist} plots a histogram of $OC_i$ and shows that the overwhelming majority display overconfidence, and a large fraction overestimate recovery by more than 50 percentage points.
-Our measure of overconfidence is useful especially when there is limited time for a detailed survey.\footnote{It may be more useful than a simple elicitation of present bias as in \cite{Ashraf}.
-We find that 15\% of clients are classified as present biased using this measure of preference reversal.
-This level is similar to the number \cite{Ashraf} find but small to explain no take-up of commitment for 90\% of clients.
-This measure was not correlated with take up of commitment in our sample.} First it is very prevalent, which makes it promising to explain the overwhelming prevalence of low take up.
-Second, it is easy to measure.
-Third, it is predictive of take-up in an intuitive way.
-Finally, overconfidence in recovery is implied by present bias with (partial) naivete but also by biased expectations of negative income shocks, thus capturing both kinds of bias.\footnote{\textcolor{red}{Another indication of overconfidence is that in our data, of those who renew, 83\% lose the pawn anyway.
-Our measure of overconfidence has a correlation of \hl{xxx}\% with a dummy for renewing and losing the pawn.
-}}
-
-\cite{Sprenger} have argued that it is critical to understand the link between beliefs and demand for commitment, yet the evidence is scarce.
-Table \ref{oc_reg} does this: it regresses an indicator of take up of the monthly payment contract against an indicator for overconfidence $OC_i:=\mathbbm{1}(P^s_i-\widehat{P_i(X_i)}>0)$ and controls.
-Controls $Z$ include branch and day of the week dummies, schooling, whether the client does a monthly budget plan, among others.
-We are careful not to include controls that were used in $\widehat{P_i(X_i)}$.
-% and a measure of intertemporal preference reversal analogous to that of \cite{Ashraf} as controls.\
-In the choice-fee arm, being overconfident decreases the likelihood of demanding commitment by 12 percentage points a result that this is robust to including controls  (columns 1 and 2).
-While overconfidence predicts lower take up in the Commitment Choice arm, this is not the case in the promise-choice arm (columns 3 and 4).
-One interpretation of the results is that the overconfident borrowers think they do not need commitment, and their demand decreases sharply as soon as there is even a small fee, and at the same time they perceive the promise as a low cost option.
-This provides evidence for \cite{Sprenger}'s conjecture that ``tepid demand for commitment outside controlled experimental settings is consistent with broad unawareness [of biases]''.
-
-How does overconfidence map to cost outcomes?
-Theory predicts that the more overconfident (naive) may be at the same time those that benefit more from commitment.
-Extrapolating individual treatment effects of the Forced Commitment contract vs the status quo one to the choice arm (see below for more detail), and using them as a dependent variable we find that overconfident borrowers benefit \textit{more} from the commitment contract, with {24.8}\% (=\${30}/\${121}) more savings (columns 5 and 6).
-Thus while we predict the overconfident benefit more from commitment, they demand less of it.
-
-\subsubsection{Neoclassical Alternatives} \label{neoclasical}
-
-\vspace{.1in}
-\noindent \textbf{Risk aversion.} We do not have measures of risk aversion in our short survey, which makes it hard to assess the hypothesis that risk aversion limits take-up of the fee frequent payment contract.
-One way to proceed is to take the empirical distribution of financing cost ---$F_{fee}(FC)$--- as one the client would have faced had she chosen the the fee-commitment contract.
-We could then ask what would risk aversion have to be in order to justify the client choosing the fee-commitment contract distribution of costs over the distribution associated with the status quo contract, $F_{sq}(FC)$.
-Framed as a choice among cost distributions, we can calculate what risk aversion is needed to rationalize the overwhelming choice of the status quo contract over the fee-commitment contract.
-This exercise of course assumes --as is common in economics-- that clients know the distribution of financial cost, that the distribution is common across consumers (although this can be relaxed), and that this cost distribution is the only difference among contracts.
-
-Fortunately for us, it turns out that one distribution first-order-stochastically dominates the other, obviating the need to calibrate a specific utility function or use a parametric distribution function in order to rank them in terms of expected utility.
-We use the fact that if the utility $u(FC)$ is decreasing in $FC$ (i.e.
-clients dislike paying higher financing cost) and $F_{fee}(FC) \geq F_{sq}(FC)$ for all $FC$, which we actually verify in our data, then $E_{fee}[u(FC)] \geq E_{sq}[u(FC)]$, that is any expected utility maximizing client risk averse consumer should choose the Forced Commitment contract as a result of the distribution of cost payoffs.\footnote{See the Appendix for the proof.
-Figure \ref{ecdf_fc} in the Appendix shows that indeed $F_{fee}(FC) \geq F_{sq}(FC)$.
-Table \ref{stochastic_dominance} shows that this holds also for sub-populations of different characteristics.}.
-Thus, risk aversion cannot explain the low demand for commitment under the assumptions of this exercise.
-
-\vspace{.1in}
-\noindent \textbf{Lost flexibility.} A second explanation for low take up is lost flexibility.
-That is, the fee-commitment contract may provide too much commitment which is costly because the client may be forced to incur in late payment fees if he experiences a negative income shock.\footnote{Note that income shocks that affect the ability to pay the entire loan are a worry for both the Forced Commitment contract and the status quo one, and should not make one contract more favorable than the other.} While we cannot rule out that income shocks combined with lost flexibility of the contract explain the low demand, we think it is unlikely.
-First, we showed above that clients report a subjective probability of recovery of 93\% on average, which suggests they are not too worried about income shocks.
-Second, the fear of incurring fees is quantitatively not enough of a concern when compared to the savings they are experiencing.
-%Note that fees for late payment are not that high.
-In an average loan of 2,000 pesos the monthly payment is close to 700 pesos, and a fee of 2\% of that is 14 pesos (less than \$1 dollar).
-This is about gr{1\%} of monthly per capita income of the first 3 deciles of Mexican {household's} income distribution.
-%This compares favorably to the gr{\$11.6 + \$62.3)} pesos transportation / transaction cost of one.
-
-To make this concrete, we calculated what the financing cost of the fee-commitment contract would be if \textit{all} its clients incurred in \textit{all} potential fees (while keeping payment profiles and pawn recovery constant) and added these fictitious fees to financing cost for those in the Forced Commitment arm, thus artificially inflating their cost.
-We then re-estimated the quantile treatment effects analogous to Figure \ref{fc_pro2}(b) with this inflated financial cost.
-%\footnote{Of course behavior may not be constant, but we believe this is a reasonable fist approximation.
-%It could be that having this small fee added to the balance discourages them to pay or makes it harder to pay back the loan.
-But the contrary may also happen, with the fee making them more determined to pay early.
-We would need a structural model of client behavior to estimate a full counterfactual.
-We suspect that such small fees would not generate large changes in behavior in a simple neoclassical model.}).
-Figure \ref{fc_allfee} presents the results.
-We find that even in this extreme scenario, tilted against the Forced Commitment contract, the estimated effect still implies cost savings from the Forced Commitment contract at the mean, 25$^{th}$, 50$^{th}$, and 75$^{th}$ percentiles.\footnote{Recall that the differences in financing cost already takes into account the fact that clients in the fee forcing contract sink more pre-payments than those in the status quo contract, and that those prepayments are lost if the loan is not fully paid back.}  Although these arguments are not definitive, they suggest that low demand for commitment may be driven by more than the anticipation of lost flexibility implied by a small fee.
-
-\vspace{.1in}
-\noindent \textbf{High time discounting.} We mentioned above that clients in the status quo contract tend to wait until the last moment to pay to recover their pawns.
-Even among those that recover their pawn, only 40\% pay before the 90$^{th}$ day.
-Table \ref{mechanisms} shows that clients assigned to the fee-commitment contract front load their payments, starting their first payment earlier and finishing paying earlier too.
-However, clients may dislike front loading payments if their time preference discount rate is high.
-They may be willing to trade off a higher probability of losing their pawn for more \textit{back} loaded payments.
-
-What would discount rates have to be in order for back loaded payments to offset the reductions in financial cost effects we observe?
-%We can calculate this number by looping across a grid of discount rates, incorporating this higher discount rate in the definition of financial cost, and reestimating equation \ref{basic_reg} with this modified financial cost measure as the dependent variable in equation 1, searching for the discount rate that makes $\beta$ equal zero.
-We did this and obtained
-We calculate that the discount rate that is necessary to compensate for the savings in financial cost (i.e.
-that makes the estimated $\beta$ in equation \ref{basic_reg} equal to zero when financing cost --using different $r$'s-- is the dependent variable) is a staggering 8,190 percent per year.
-We find this discount rate implausibly high even for this credit constrained population\footnote{For comparison, \cite{Levin} find that a discount rate of 1,415 per year for subprime borrowers in the US is too high to be believable.}, casting doubt on high discount rates as explanation for low demand for commitment.
-%\footnote{In the baseline survey we give respondents a hypothetical choice between $100$ pesos tomorrow or $150$ pesos in one month (an implicit yearly interest rate of {12,800\%}) and only 30\% chose the later one.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% APPENDIX C
-
-\newpage
-\section{ A simple model}
-\label{appendix_c}
-\vspace{.2in}
-\normalsize
-\linespread{1.25}
-
-Although the empirical results are striking and stand alone, this section refers to the model of \cite{John} to interpret our empirical results.
-The model is stylized but incorporates important features of our context.
-It allows for negative income shocks which we think are prevalent in this population.
-%The shock generates a cost of committing to monthly payments and could potentially be a reason for low take up.
-It also features clients with present biased time preferences --allowing for partial naivete-- choosing to save to pay for an expense, and with the opportunity to make a commitment to save and pay.
-These two features parsimoniously explain several facts about the context --like overconfidence in recovering the pawn--, and about the results --e.g.
-that forcing commitment seems to help.
-We intend the model only as a very stylized approximation to our context, and we use it only to help us organize the interpretation of the empirical results, not as a literal description of reality.
-%Third, it allows for a simple way to model commitment afforded by late payment fees.
-%Nonetheless, the model abstracts from several details of the context.
-Even with these abstraction it allows us to explain our six main results listed in Section \ref{explanations_recap} below.
-
-We use the model of \cite{John} and refer the reader to that paper for more detail, justification of assumptions and some of the proofs.
-The model has three periods and linear utility.\footnote{This does not map perfectly to our 3 period contract, but it is enough to generate the results we need.
-We also assume that the amount of the loan is used up to pay for the emergency.
-\cite{John_theory} provides a more general treatment.} Period $t=0$ is a planning period where the client is either allocated to the status quo, the fee-forcing contract, or a choice between the two.
-Period $t=1$ is the saving-for-the-monthly-payment  period, and $t=2$ in the pawn recovery (loan payment) period.
-In period 1 the client receives her income $y_1=1$, or gets zero with probability $\lambda$.
-She can consume ($c_1$) or save ($s_1$) part that income.
-In period 2 the client gets her savings from period 1, and again receives income of either $y_2=1$, or zero with independent probability $\lambda$.
-In this last period, she decides whether to use income and savings for consumption $c_2$ and/or for paying back the loan of size $p \in(1,2)$ to recover the pawned piece valued at $b>p$.
-In this simple set up we model the fee-commitment contract as a contract that imposes a fee of size $F$ if the client fails at $t=1$ to save $s_1=p-1$ pesos, which is what is needed to pay the loan back when there are no shocks.
-In period $t=0$ she evaluates her welfare as $E[c_1+c_2]$, were for simplicity we have set the time discount to one.
-We also assume the interest rate is one.
-We introduce present biased preferences by assuming the following utility function $U_t=c_t+\beta \: \sum_{k=t+1}^{2} E[c_k]$, with $\beta<1$ indicating present bias.
-A naive client perceives she is not so present biased and instead of $\beta$ uses $\hat{\beta} \in (\beta,1]$.
-
-Note that under these assumptions it is efficient at $t=0$ to recover the loan since $b>p$ and since there is no discounting at $t=0$.
-Because $b>1$, paying back the loan requires that there is no negative shock in any period and that $s_1>0$.
-Because $\beta<1$ at $t=1$ the client will not send savings in excess of what is needed to recover the loan: $s_1=p-1$.
-This parsimonious model implies the following results:
-
-\vspace{.2in}
-\noindent \textbf{Result 1: Present biased clients default more.} Under the status-quo contract, absent shock realizations, present biased clients (sophisticated or naive) with $\beta<\beta_{SQ}<1$ will lose their pawn, while clients with no present bias will not.\footnote{$\beta_{SQ}=\frac{p-1}{\lambda(p-1)+(1-\lambda)(b-1)}$.
-See Proposition 1 in \cite{John}.}
-
-\vspace{.1in}
-\noindent \textbf{Result 2: Forcing present-biased clients into the fee-commitment contract reduces default.} Imposing a fee $F>0$ for late payments weakly decreases default (for present biased clients only).
-It strictly decreases default if $F>F_{min}(\beta):=(p-1)-\beta[\lambda(p-1)+(1-\lambda)(b-1)]$.
-The larger the present bias the larger the $F$ required to induce pawn recovery.\footnote{$F_{min}(\beta)$ is derived from the incentive compatibility constraint needed to generate savings at $t=1$ to recover the pawn can be written as $1-(p-1)+\beta[\lambda(p-1)+(1-\lambda)(b-1)] \geq 1-F+\beta(1-\lambda)$.}
-
-\vspace{.1in}
-\noindent \textbf{Result 3: Demand for commitment.} Given $F>0$, (a) Neoclassical clients will never demand commitment.
-(b) Present-biased sophisticated clients will prefer the fee-forcing contract over the status quo contract $\iff$  $\lambda \: F<(1-\lambda)^2(b-p)$ and $F>F_{min}(\beta)$, that is $\iff$  $\beta \in [\beta_{min},\beta_{SQ}]$.\footnote{$\beta_{SQ}$ was determined in Result 1.
-$\beta_{min}$ is such that $F=F_{min}(\beta_{min})$.} (c) Analogously, naive clients will demand commitment $\iff$ $\hat{\beta} \in [\widehat{\beta_{min}},\beta_{SQ}]$, where $\widehat{\beta_{min}}<\beta_{min}$.
-So strongly naive clients will on the one hand demand more commitment than sophisticated clients since they believe (incorrectly) that a smaller fee will motivate them to pay.
-On the other hand they may demand less commitment since they think they can save and pay on their own.
-Whether they demand more or less than sophisticated clients depends on the empirical distribution of $\beta$ and $\hat{\beta}$.
-
-\vspace{.1in}
-\noindent \textbf{Result 4: Overconfidence.} Only naive clients will be overconfident about the probability of recovery.
-This will be true whether they have the status quo or the fee-forcing contract.
-Overconfidence is increasing in $\hat{\beta}$.
-
-\vspace{.1in}
-\noindent \textbf{Result 5: Welfare.} (a) Neoclassical consumers' welfare strictly decreases when we force clients into the fee-commitment contract instead of the status quo contract because of the risk of them not being able to pay for the installment, and does not change when we offer a choice between them.
-(b) The welfare of sophisticated present biased consumers weakly increases when we give them choice, and it strictly increases  $\iff$  $\beta \in [\beta_{min},\beta_{SQ}]$, that is when they would choose the fee-commitment contract themselves.
-Forcing them into the fee-commitment contract increases welfare $\iff$  $\beta \in [\beta_{min},\beta_{SQ}]$, otherwise it strictly decreases it.
-So choice is better than forcing for sophisticates.
-(c) Forcing can be welfare improving for the naive.
-Indeed if $\hat{\beta}>\beta_{SQ}>\beta$ then forcing the fee-commitment contract increases welfare, and if $\hat{\beta} \in (\widehat{\beta_{min}},\beta_{min})$ then forcing the status quo contract increases welfare.\footnote{This result is different from that in \cite{John}.
-Her context has individuals choosing the size of the fee.
-In that context naive clients will \textit{always} chose the wrong fee size and default later, therefore choice is always decreasing for the naive.
-In our context $F$ is fixed at 2\% of the balance due, and this implies that choice could be welfare improving for some naifs.} We want to highlight that only under certain parameters will forcing installment payments improve welfare, and that welfare will likely decrease for those with no present bias and the sophisticated present biased consumers.
-
-\vspace{.1in}
-\noindent \textbf{Result 6: Welfare and ex-post observed behavior.} If for a naive client $i$ the fee-forcing contract causes higher pawn recovery, then we know the fee $F$ made her IC constraint binding, and therefore that $\hat{\beta}_i>\widehat{\beta}_{min}$.
-If in addition if it was the case that $\beta_i<\beta_{SQ}$.
-%\footnote{\hl{Isaac, aqui tengo dos pregutas: (1) si es $\beta$ y no $\hat{\beta}$ verdad?
-(2) Para que una persona naive empenie en el status quo tiene que ser que cree que va a recuperar no?
-Es decir tiene que ser $\hat{\beta}>\beta_{SQ}$ correcto?}}
-then the fee-forcing contract would have increased welfare for the naive.
-That is, our finding that the fee-forcing contract increases pawn recovery is a sign of higher welfare (although not a sufficient condition).\footnote{It is not sufficient since ex-ante the commitment $F$ may have been too expensive given the income shocks, i.e.
-if $\lambda \: F>(1-\lambda)^2(b-p)$.}
-
-\subsection{Interpretation}
-
-The model is very parsimonious but powerful and it can potentially explain all our empirical findings qualitatively.\footnote{The model is sufficiently stylized that we think we would not gain much from estimating it.
-Furthermore we have no data on income shocks which figure prominently in the model.
-\cite{Ted} and \cite{Aprajit} are two very recent models that combine a field experiment with commitment contracts and estimation of present bias parameters.} First, it can explain why default is high in the status-quo contract, namely that clients are present biased and have no commitment devices.
-Second, it can explain why clients are overconfident in our data, namely by virtue of naivete about present bias.
-Under the model naivete is necessary to explain this.
-Third, it can also explain why the fee forcing contract induces lower default, but not for everyone: namely that it makes the incentive compatibility constraint for payment binding for the present biased, while it was not binding in the status quo contract.
-Fourth, it can also explain why there is low demand for commitment even if it seems to improve welfare: namely that there is a small share of neoclassical and sophisticated clients, and at the same time naifs have a present biased parameters values in the region in which they think they can save on their own.
-Fifth, it explains non-zero demand for commitment for a set of clients.
-Sixth, it can explain why clients exposed to the Forced Commitment contract are more likely to come back namely those naifs whose welfare increased as a result of being forced into the fee-commitment contract.\footnote{Those with $\hat{\beta_i}>\beta_{SQ}>\beta$.}
-
-\subsection{Other potential explanations: recap} \label{explanations_recap}
-
-There may be other interpretations of the empirical findings, but the bar is high. An alternative explanation will need to explain the 6 facts below:
-
-\begin{enumerate}
-\itemsep0em 
-\item High (although ex-post inefficient) default in status quo contract.
-\item Overconfidence about pawn recovery.
-\item Forcing commitment increases pawn recovery.
-\item Small demand for commitment...
-\item ...but positive demand for commitment.
-\item Forcing commitment makes clients more likely to come back.
-\end{enumerate}
-
-Let us consider alternative explanations in isolation (i.e. just considering one change or feature at a time with respect to a neoclassical model):
-
-\vspace{.1in}
-\noindent \textbf{Alternative 1: Strong prevalence of income shocks.} This could explain (4) and (1), but not why forcing helps, (3) and (6), nor why there is overconfidence, (1).
-It would also not explain why clients come to pawn in the first place and then default, (2), as they would weight in on the high chance of losing the pawn.
-
-\vspace{.1in}
-\noindent \textbf{Alternative 2: High time discounting}.
-This could not explain (1) nor (5) nor (6).
-It could qualitatively explain (4), but as we say in section \ref{sec:demand} quantitatively it would require unbelievably high discount rates.
-
-\vspace{.1in}
-\noindent \textbf{Alternative 3: Risk aversion.} We already discussed and rejected risk aversion in section \ref{sec:demand}, although using strong assumptions in the process.
-Risk or ambiguity aversion could still play a role in explaining 4 and should be investigated in future research.
-However it would hardly explain (1), (2), (5), or (6).
-
-\vspace{.1in}
-\noindent \textbf{Alternative 4: Misunderstanding the contracts.}\footnote{This is a potential criticism of \textit{any} paper offering choice, and one that is non-falsifiable if the critic has free reign to propose how the contracts are perceived in the subject's mind.} We were very aware of the importance of clients understanding the contract in order to infer preferences from choice.
-That is why we made a strong effort for clients to understand the contracts (see subsection \ref{implementation}).
-Note however that while clients making purely random mistakes could explain why 10\% demand commitment ---i.e.
-(4) and (5)--- it would not explain the rest of the findings, nor why the Soft Commitment (see below) had more take up that the fee-commitment, or why we can statistically predict take-up with significant accuracy (see Figure \ref{interactions_takeup} and Table \ref{Table_compliance}).
-
-\vspace{.1in}
-\noindent \textbf{Alternative 5 (behavioral): Forgetting to pay/salience.} Frequent payments may act as a reminder to save and recover the pawn.
-This would try to explain (1) by appealing to people forgetting to pay, and (3), (5), and (6) by appealing to frequent payment acting as reminders (i.e.
-there being demand for reminders).
-It would not explain (2) or (4) which are critical in the paper.
-However even for (1) it seems to us a stretch to explain people losing a valuable pawn by forgetting to pay it.
-Since the Soft Commitment installment contract did not change behavior (as shown below) this explanation would also require us to posit that only fees acts as reminders, not promises.
-
-\vspace{.1in}
-\noindent \textbf{Alternative 6 (behavioral): Income shocks overconfidence}.
-One could also easily introduce in the overconfidence about income shocks in the model of \ref{appendix_c}\footnote{Say with $\widehat{\lambda} <\lambda$.
-The effect on demand for commitment is uncertain since on the one hand it decreases $\beta_{SQ}$ decreasing demand, but on the other a smaller $F$ is needed to make the IC binding, making commitment less costly.}.
-This would leave default unchanged in both the status quo and the fee forcing contract thus would not explain (3), %since $F_{min}(\beta,\widehat{\lambda})<F_{min}(\beta,\lambda)$.
-% $\widehat{\lambda} <\lambda$ alone 
-It would not explain (5) or (6) either as demand for commitment would be zero without present bias.
-
-\vspace{.1in}
-We do not claim that the model in the Appendix is the only possible explanation of our empirical findings, but it is a parsimonious explanation of all of them.
-
-\end{comment}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\clearpage
-%\bibliographystyle{authordate1}
-%\bibliographystyle{amsalpha}
-%\bibliographystyle{AER}
-
-%\bibliography{References}
-
-% \end{document}
+\end{appendix}

### 2023-12-02 ECTA submission/donde_ecta.tex
prepare for ecta submission

--- 2023-11-30 donde.tex
@@
- \documentclass[oneside,11pt]{article}
-
-\input{preamble.tex}
-%%% HELPER CODE FOR DEALING WITH EXTERNAL REFERENCES
-\usepackage{xr}
-\makeatletter
-\newcommand*{\addFileDependency}[1]{
-  \typeout{(#1)}
-  \@addtofilelist{#1}
-  \IfFileExists{#1}{}{\typeout{No file #1.}}
-}
-\makeatother
-
-\newcommand*{\myexternaldocument}[1]{
-    \externaldocument{#1}
-    \addFileDependency{#1.tex}
-    \addFileDependency{#1.aux}
-}
-
-%\myexternaldocument{OA}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% DOCUMENT
+% use option [draft] for initial submission
+%            [final] for the prepublication
+\documentclass[ecta,nameyear,final]{econsocart}
+%
+%\usepackage{}
+\RequirePackage[colorlinks,citecolor=blue,linkcolor=blue,urlcolor=blue,pagebackref]{hyperref}
+
+\startlocaldefs
+
+\usepackage{booktabs}
+\usepackage{multirow}
+\usepackage{float}         
+\usepackage{amsmath}
+\usepackage{amscd}
+\usepackage{amsfonts}
+\usepackage{amssymb}
+\usepackage{bbm}
+\usepackage{dsfont}
+\usepackage{colortbl}
+\usepackage{comment}
+\usepackage{lscape}
+\usepackage{subcaption}
+\newtheorem{theorem}{Theorem}
+\newtheorem{claim}[theorem]{Claim}
+\newtheorem{prop}[theorem]{Proposition} 
+\newtheorem{cor}[theorem]{Corollary} 
+\newtheorem{assumption}{Assumption} 
+\newtheorem{lem}{Lemma}
+
+\newcommand{\wh}{\widehat}
+
+\newcommand{\E}{\mathbb{E}}
+
+\endlocaldefs
+
+\usepackage[section]{placeins}
+
 \begin{document}
 
-\title{The controlled choice design and private paternalism in pawnshop borrowing\thanks{We want to thank Mauricio Romero and Anett John for advice and encouragement.
+\begin{frontmatter}
+
+\title{The controlled choice design and private paternalism in pawnshop borrowing}
+\runtitle{The controlled choice design and private paternalism}
+
+\begin{aug}
+% use \particle for den|der|de|van|von (only lc!)
+% [id=?,addressref=?,corref]{\fnms{}~\snm{}\ead[label=e?]{}\thanksref{}}
+%
+%% e-mail is mandatory for each author
+%
+%%% initials in fnms (if any) with spaces
+%
+\author[id=au1,addressref={add1}]{\fnms{Craig}~\snm{McIntosh}\ead[label=e1]{ctmcintosh@ucsd.edu}}
+\author[id=au2,addressref={add2}]{\fnms{Isaac}~\snm{Meza}\ead[label=e2]{isaacmezalopez@g.harvard.edu}}
+\author[id=au3,addressref={add3}]{\fnms{Joyce}~\snm{Sadka}\ead[label=e3]{jsadka@itam.mx}}
+\author[id=au4,addressref={add4}]{\fnms{Enrique}~\snm{Seira}\ead[label=e4]{enrique.seira@gmail.com}}
+\author[id=au5,addressref={add5}]{\fnms{Francis J.}~\snm{DiTraglia}\ead[label=e5]{francis.ditraglia@economics.ox.ac.uk}}
+
+% Addresses
+\address[id=add1]{%
+\orgdiv{Department of Economics}
+\orgname{University of California San Diego}}
+
+\address[id=add2]{%
+\orgdiv{Department of Economics}
+\orgname{Harvard University}}
+
+\address[id=add3]{%
+\orgdiv{Department of Economics}
+\orgname{Instituto Tecnologico Autonomo de Mexico}}
+
+\address[id=add4]{%
+\orgdiv{Department of Economics}
+\orgname{Michigan State University}}
+
+\address[id=add5]{%
+\orgdiv{Department of Economics}
+\orgname{University of Oxford}}
+\end{aug}
+
+%% Put support info here. Reminder: do not thank the handling coeditor anonymously or by name
+\support{We want to thank Mauricio Romero and Anett John for advice and encouragement.
 Ricardo Olivares, Gerardo Melendez, and Alonso de Gortari provided excellent research assistance and Erick Molina helped with formatting.
@@
 Research assistance was financed through faculty grants at ITAM.
-Our research partner had no say in the results.}}
-\author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira \and Francis J.\ DiTraglia   \thanks{Seira:  MSU, \url{enrique.seira@gmail.com} (corresponding author); McIntosh:  University of California San Diego, \url{ctmcintosh@ucsd.edu}; Meza: Harvard University, \url{isaacmezalopez@g.harvard.edu}; Sadka: ITAM, \url{jsadka@itam.mx}; DiTraglia: Oxford, \url{francis.ditraglia@economics.ox.ac.uk}} }
-\date{This draft:  \today \\[2 cm]}
-
-%\vspace{.5in}
-
-\maketitle
-\thispagestyle{empty}
+Our research partner had no say in the results.}
+%
+\coeditor{\fnm{[Name} \snm{Surname}; will be inserted later]}
+
 \begin{abstract}
-
-%Many firms provide commitment devices that restrict individuals' choice, but shroud this.
-Shrouding suggests low demand for commitment.
-We show that private paternalism is beneficial in the pawnbroker context we study.
-
 We use a novel three-armed RCT, including both forced and voluntary treatment arms, to provide a unique window into choice, heterogeneous treatment effects and paternalism in the context of pawnbroker lending.
@@
 A detailed analysis of treatment effect heterogeneity suggests that the potential gains from targeting commitment based on observable characteristics are extremely small and that most borrowers stand to gain from a policy of universal forced commitment.
-%The justification for paternalistic commitment in this context appears to be over-optimism; 74\% of clients say they will certainly recover their pawn while in fact only 57\% do so.
-
-%In the context of pawnbroker lending, we show that forcing people into commitment contracts with financial penalties for not paying on time \textit{decreases} their (fee-including) financial cost by 9.4\%, increases the likelihood of recovering their pawn by 26\%, and increases the likelihood of repeat business by almost 100\%.
-Using machine learning methods for estimating heterogeneous treatment effects, we find that more than {70}\% clients would reduce their financing cost with the commitment contract, however only 10\% choose it.
-Those that \textit{don't} choose it are predicted to be the ones who would benefit more.
-Relying on personal promises instead of fees as commitment triples take-up but has no effects on outcomes.
-
-%and one of the most understudied.
-In our context more than on half of borrowers default and lose their pawn and whatever they have paid towards recovering it.
-Compared to the status quo pay-at-anytime 3-month contracts, forcing borrowers to pay monthly and charge a penalty if they didn't --i.e.
-a commitment contract-- increased recovery of pawn by about 30\% and financial costs by 10\%.
-However when offered a choice between the two contracts only 10\% took the monthly payment one.
-A pecuniary commitment seems necessary.
-In an alternative arm, we made them promise to pay but removed the pecuniary penalty.
-This increased take up to 31\%, but had zero effect on financing cost or default.
-The forcing contract may be better than choice for naive present biased consumers.
-
 \end{abstract}
 
-\vspace{.3in}
-
-\textbf{Keywords: } Private paternalism, choice, treatment on the untreated, heterogeneous treatment effects, commitment, overconfidence.
-
-\textbf{JEL codes:} G41, C93, O16, G21
-
-\newpage
-
-\pagenumbering{arabic}
-\etocdepthtag.toc{mtchapter}
-\etocsettagdepth{mtchapter}{subsection}
-\etocsettagdepth{mtappendix}{none}
-
-%NO MORAL HAZARD IN THE CONTRACT SINCE FULLY COLLATERALIZED
-%DOUBLE FAILURE: DEMAND LOW, AND DOES NOT WORK BY PEOPLE WHO TAKE IT.
-%PENALIZES THEM EVEN MORE ON SOMETHING THEY WERE ALREADY PENALIZED 
-%PROPENSITY TO CHOSE.
-%PULLING PUNISHMENT FORWARD --CHARGING RIGHT WHEN I MESS UP.
-%MAYBE ONLY IMPATIENT AND NAIVE END IN PAWNSHOPS
-%1) SELECT A RANDOM SAMPLE OF NEIGHBORHOODS, EXTERNAL VALIDITY, THE ONES THEY GO ARE NAIF AND
-%HYPERBOLIC
-%2) ASK TO CHOSE AMONG ALL CONTRACTS
-%3) CLASSIFY SOPHISTICATION AT BASELINE
-%4) HOW TO GET AT SHOCKS.  --BUT DOES NOT SQUARE WITH WHY CHARGING THEM FEES WORKE.
-%do shocks vary across strata, predict shocks.
-%DEEP BEHAVIORAL PAPER -- CAN WE REALLY PREDICT?
+\begin{keyword}
+\kwd{Private paternalism}
+\kwd{choice}
+\kwd{treatment on the untreated}
+\kwd{heterogeneous treatment effects}
+\kwd{commitment}
+\kwd{overconfidence}
+\end{keyword}
+
+\end{frontmatter}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%% Main text entry area:
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\paragraph{Appraising and lending.} Lender P takes gold jewelry as collateral in exchange for a fraction of the value of the piece, in cash.
+\noindent \textbf{Appraising and lending.} Lender P takes gold jewelry as collateral in exchange for a fraction of the value of the piece, in cash.
 No other collateral and no credit history checks are needed.
@@
 
-\paragraph{Contract.} Lender P had only one type of contract, henceforth the \textit{status quo} contract.
+\noindent \textbf{Contract.} Lender P had only one type of contract, henceforth the \textit{status quo} contract.
 It stipulated that the interest rate was 7\% \textit{per month} compounded daily on the outstanding amount of the loan.
@@
 
-\paragraph{Borrowers.} The clients that pawned understood these terms well (as we verified in interviews).\footnote{87\% of clients report in our survey that they have pawned before.} These clients have little or no access to other types of loans and they value the convenience of pawn borrowing.
+\noindent \textbf{Borrowers.} The clients that pawned understood these terms well (as we verified in interviews).\footnote{87\% of clients report in our survey that they have pawned before.} These clients have little or no access to other types of loans and they value the convenience of pawn borrowing.
 This population of pawn borrowers is economically vulnerable:  30\% of them could not pay either water, electricity \& gas or rent in the past 6 months; 89\% said they are pawning because of an emergency, and only 12\% stated it was to use in a ``non-urgent expense''.
@@
 
-\paragraph{Many borrowers lose their pawn.} Our context is also one with high borrower default: 43\% of clients lose their pawn in a time span of 230 days from the date of pawning.
+\noindent \textbf{Many borrowers lose their pawn.} Our context is also one with high borrower default: 43\% of clients lose their pawn in a time span of 230 days from the date of pawning.
 One potential explanation for high default is that clients are really just knowingly selling their gold piece through a pawn contract on which they intend to default.
@@
 The formula for financial cost for person $i$ is thus as follows: %\footnote{We alternatively defined financial cost as $\text{Financial Cost}_i = \sum_t P^I_{it} + \sum_t P^F_{it} + \sum_t P^C_{it} + \mathds{1}(\text{Default}_i) \times (\text{Value}_i)-\text{Loan}_i$, and obtained similar results.}:
-
 \begin{align*}
@@
 As a second measure of cost we calculate the Annual Percentage Rate (APR) in order to express the cost as a percentage of the loan, per year, inclusive of default costs.\footnote{Loan term takes into account the entire loan period, including extensions of the loan through refinancing.} The standard definition is given in the following formula:
-
 \begin{align*}
@@
 
-\vspace{.1in}
+\begin{figure}
+    \begin{center}
+    \begin{subfigure}{.45\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_fc.pdf}
+        \caption{}
+    \end{subfigure}
+     \begin{subfigure}{0.45\textwidth}
+       \centering
+      \includegraphics[width=\textwidth]{Figuras/hist_apr.pdf}
+      \caption{}
+    \end{subfigure}
+    \end{center}
+ \caption{Financial cost.
+Panel (a) presents a histogram of financial cost for the control group.
+The figure plots separately the financial cost separately for borrowers who lose the pawn (blue) and those that recover it (transparent).
+Panel (b) is analogous but displays the APR.}
+     \label{fc_hist}
+      %\footnotesize{ } \textit{Do file: }  \texttt{hist\_fc.do}
+\end{figure}
 
@@
 
-\vspace{.2in}
 \noindent \textbf{Treatment Arms.} Treatments were randomized at the branch-day level.
@@
 
-%The existence of a choice arm allows us not only to measure if there is demand for such a contract, but who demands it, not only in demographic terms, but in terms of potential treatment effects.
-One may worry for instance that low sophistication from pawn-loans users could lead to the `wrong' people choosing the structured commitment contract.
-To examine this issue, we included an arm that assigns all individuals to the commitment contract so that we are able in essence to form three counterfactual outcomes; no commitment, commitment, and the chosen commitment.
-This design allows us to investigate the repercussions of choice not only for those who \textit{do} choose (as is the case in a standard LATE design), but also the implications of choice for those who \textit{do not} choose.
-This design is innovative and critical for our purposes, as it enables us to explore whether or not forcing people into a structured payment contract could be more beneficial than allowing choice for a significant fraction of them.
+\begin{figure}     
+\begin{center}
+\begin{subfigure}{\textwidth}
+        \includegraphics[width=\textwidth]{Figuras/consort.pdf}
+    \end{subfigure}
+  \end{center}
+ \caption{Experiment description}
+     \label{exp_description}
+%\textit{Do file: }  \texttt{ss\_att.do}
+\end{figure}
 
@@
 
-\paragraph{Timeline.} Figure \ref{exp_description} shows the experimental timeline along with the length of time for which we observe payments.
+\noindent \textbf{Timeline.} Figure \ref{exp_description} shows the experimental timeline along with the length of time for which we observe payments.
 For loans made in the first week of the experiment, we observe up to 338 subsequent days of loan information; for loans made in the last week we observe up to 235 days.
@@
 
-\paragraph{Explanation.} Since we are interested in measuring the effect of different contract terms on client behavior, it is important that clients understand these terms.
+\noindent \textbf{Explanation.} Since we are interested in measuring the effect of different contract terms on client behavior, it is important that clients understand these terms.
 To ensure this, we built two ``check-points'' as follows.
@@
 
-\paragraph{Administrative data.} The study exploits two types of data: administrative data from the lender, and a short survey that we implemented.
+\noindent \textbf{Administrative data.} The study exploits two types of data: administrative data from the lender, and a short survey that we implemented.
 The administrative data contains a unique identifier for each client, an identifier for the piece she is pawning, and the transactions relating to that piece.
@@
 
-\paragraph{Survey data.} An additional team of enumerators stationed in each branch asked clients to complete a 5-minute survey \textit{before} going to the teller window to appraise their piece and before they learned which contracts would be available on that day.
+\noindent \textbf{Survey data.} An additional team of enumerators stationed in each branch asked clients to complete a 5-minute survey \textit{before} going to the teller window to appraise their piece and before they learned which contracts would be available on that day.
 The survey was intentionally short to avoid discouraging the potential clients from pawning.
@@
 
-\paragraph{Attrition.} There are two main channels through which attrition could complicate the interpretation of our results.
+\noindent \textbf{Attrition.} There are two main channels through which attrition could complicate the interpretation of our results.
 The first, and more serious, is the possibility that clients might change their pawning decisions in response to the treatment they encounter in a given branch on the day they enter the branch.
@@
 Figure \ref{boxplot_attrition} shows that full distribution of loans per day is very similar across treatment arms.
-The only noticeable difference is that the choice arm has a few more positive outliers.\footnote{If we winzorize at the 90th percentile, the mean number of branch-day pawns identical across arms.}
+The only noticeable difference is that the choice arm has a few more positive outliers.\footnote{If we winzorize at the 90th percentile, the mean number of branch-day pawns becomes identical across arms.}
+
+\begin{table}
+\caption{Limited and balanced attrition}
+\label{attrition_table}
+\begin{center}
+\scriptsize{\input{./Tables/Attrition.tex}}
+\end{center}
+\legend{Each row in this table 
+ corresponds to a regression.
+The dependent variables are: the number of pawns-loans originated per day per branch, the number of borrowers per day-branch, a variable indicating whether a person who answered the baseline survey (before knowing contract terms) ended up pawning, and an indicator of whether the person that obtained the loan answered the baseline survey.
+Each dependent variable is regressed in a multivariate OLS regression against the experimental arms indicators (control, forced commitment, choice).
+The table reports the coefficients on each of these indicators, as well as the p-value of an F-test of the null hypothesis of equality of the three coefficients.
+Figure \ref{boxplot_attrition}, in the appendix shows a box-plot of the first two variables, showing the distribution across arms is balanced.}
+%\textit{Do file: } \texttt{ss\_att.do}
+\end{table}
 
@@
 
-\paragraph{Balance.} Table \ref{SS} presents summary statistics for the sample of actual borrowers across arms, showing that our randomization succeeded in achieving balance across the experimental arms.
+\noindent \textbf{Balance.} Table \ref{SS} presents summary statistics for the sample of actual borrowers across arms, showing that our randomization succeeded in achieving balance across the experimental arms.
 Panel A uses administrative data for the universe of borrowers in each arm, and shows that loan balances and the days on the week on which individuals pawned are comparable across arms.
@@
 
-%Panel C repeats the exercise in Panel B, but now only for those borrowers answered the survey and then went on to take a loan.
-Since we have aready shown that the attrition rate of borrowers after completing the survey was very low (3\% on average) it is unsurprising that these two panels are similar.
-Overall, we find both the loan attributes and the survey attributes of borrowers to be similar across arms.
-The experiment appears to have been successful in generating a balanced sample for analysis.
-
-%Panel A describes variables from the administrative data.
-The average number of pawns per day per branch is 34.
-Only 42\% of clients recover their pawn.
-Even those that recover their pawn tend to pay it back at the last moment, with only 40\% paying before the 90th day.
+\begin{table}[htbp]
+\caption{Summary statistics and Balance}
+\label{SS}
+\begin{center}
+\scriptsize{\input{./Tables/SS.tex}}
+\end{center}
+\legend {This table has two panels.
+Panel A uses administrative data at the loan level, while Panel B uses survey data.
+Each row in this table corresponds to a regression, where the level of observation is the individual loan originated.
+The dependent variables of these regressions are displayed in the first column.
+Each dependent variable is regressed in a multivariate OLS regression against the experimental arms indicators (control, forced commitment, choice).
+The table reports the coefficients on each of these indicators, as well as the p-value an F-test of the null hypothesis of equality of the three coefficients.
+The admin data was a very limited set of pre-determined variables.
+The dependent variables in Panel A are the loan amount in pesos, and an indicator for whether the day of the loan origination was a weekday (as opposed to weekend).
+The dependent variables in Panel B from the survey (see the questions in Table \ref{baseline_survey}.
+Subjective value of the pawn (how much would the client be willing to sell it for (Q3), an indicator for having trouble paying bills in the last 6-months (Q28), present bias (constructed from questions Q10 and Q29 in the standard way as in \cite{Ashraf}), an indicator for whether they make expenses budget for the month ahead of time.
+The subjective probability of recovery was elicited a la Manski (from 0 to 100 what is the probability that you will recoup your pawn), pawned before is a dummy=1 if the client declares to have pawned before (although not necessarily with Lender $P$) age is in year, +High-school is a dummy that indicates if the client has completed high school.
+}
+%\textit{Do file: } \texttt{ss\_att.do}
+\end{table}
 
@@
 
-\paragraph{Specification.} Table \ref{main_impact_table} presents estimates and standard errors from a standard pooled experimental regression 
+\noindent \textbf{Specification.} Table \ref{main_impact_table} presents estimates and standard errors from a standard pooled experimental regression 
 \begin{equation} \label{basic_reg}
@@
 
-\paragraph{Results.} The results are stark.
+\begin{table}
+\caption{Effects on Financial Cost}
+\label{main_impact_table}
+\begin{center}
+\resizebox{0.9\textwidth}{!}{
+\scriptsize{\input{./Tables/decomposition_main_te.tex}}
+}
+\end{center}
+\legend{This table shows the treatment effects for our core pecuniary outcomes.
+Each column is a different regression for different outcomes on an indicator for the forced and choice arms, following specification in equation \ref{basic_reg}.
+Columns (1) \& (7) analyze our core financial cost measures, while the rest of the columns decompose these into finer components.
+A few borrowers take more than one loan on the first day they appear in an experimental branch.
+These are treated as different observations.
+Table \ref{multiple_loans} shows our results are similar when dealing with the multiplicity of loans per borrower.
+Each regression includes branch and day-of-week FE.
+Standard errors are clustered at the branch-day level.
+}
+
+%\textit{Do file: } \texttt{decomposition\_main\_te.do}
+\end{table}
+
+\noindent \textbf{Results.} The results are stark.
 The Forced Commitment arm yields large and significant decreases in the cost of loans to clients, as measured either by financial cost or APR.
@@
 
-\paragraph{Intermediate outcomes.} To shed light on the mechanisms behind the ATEs discussed above, Table \ref{mechanisms} shows how commitment affects a number of intermediate outcomes.
+\noindent \textbf{Intermediate outcomes.} To shed light on the mechanisms behind the ATEs discussed above, Table \ref{mechanisms} shows how commitment affects a number of intermediate outcomes.
 One can group the types of intermediate outcomes into two categories: measures of the speed of pawn recovery, and measures of the decision of when to default.
@@
 On the contrary, 7 percentage points fewer borrowers end up in this situation, compared to 12 percent in the status quo contract.
-Conditional on defaulting those assigned to the Forced commitment contract have paid 4.1\% less of their loan (col 7), and a 14 percent higher proportion of borrowers pay zero conditional on defaulting, an outcome analogous to ``selling their pawn'' (col 8).
+Conditional on defaulting those assigned to the Forced commitment contract have paid 4.1\% less of their loan (col 7), and a 14 percent higher proportion of borrowers pay zero conditional on defaulting, an outcome analogous to
+``selling their pawn'' (col 8).
 One interpretation of this bifurcation is that the Forced commitment contract forces borrowers to think earlier about whether they will indeed be able to eventually recover their pawn, and separates borrowers into those ``selling'' their pawn and those recovering it, reducing the share of undecided borrowers that end up paying interest and end up losing the pawn anyway.
-This mechanism may also help to explain why the Forced commitment contract does not increase the number of visits to the branch to pay (col 10): those recovering their pawn visit more, but those defaulting have 0.20 fewer visits (col 11).\footnote{Figure \ref{hist_payments} plots the histogram of the timing of payments in each arm, and shows that commitment does appear to bind in that it generates a highly regular pattern of payments at 30, 60, and 90 days after the loan is taken.} Finally, Column 9 shows that treatment effects are concentrated in the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery.
-
-\paragraph{Other costs.} We have shown that forcing borrowers to take the monthly payment contract significantly reduces their financial costs.
+This mechanism may also help to explain why the Forced commitment contract does not increase the number of visits to the branch to pay (col 10): those recovering their pawn visit more, but those defaulting have 0.20 fewer
+
+\begin{landscape}
+\begin{table}
+\caption{Effects on intermediate outcomes}
+\label{mechanisms}
+\begin{center}
+\resizebox{1.30\textwidth}{!}{
+\scriptsize{\input{./Tables/mechanism.tex}}
+}
+\end{center}
+\legend{This table explores treatment effects in ``intermediate variables''.
+Each column represents regression output for different dependent variables following equation (\ref{basic_reg}).
+Panel A focuses on variables related to the speed of payment.
+While Panel B focuses on variables related to default, and Panel C related to visits.
+% The outcome variables are as follows:  number of days elapsed between origination and first payment (col 1); percentage of the loan paid in the first payment (col 2); probability of recovery in the first visit (col 3); loan duration is the number of days the borrower took to payoff her loan for those that recover, the number of days until default for those that default, and the maximum number of days we observe them in the sample for those that have not recovered or defaulted (col 4); loan duration conditional on recovery; an indicator for paying a positive amount towards recovery but nonetheless losing the pawn (col 6); the percentage or the loan paid, conditional on defaulting --`wasted payments' (col 7).
+Column 8 uses the phrase `selling the pawn' for a dummy variable indicating the borrower did not pay any amount towards recovery and lost the pawn.
+Moreover, (col 9) shows that treatment effects are concentrated in the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery.
+The dependent variable in column 10 is the number of day-visits to the branch (measured by the existence of transactions that day associated with our particular pawn), while column 11 conditions on borrowers that lost the pawn.
+Each regression includes branch and day-of-week FE. Standard errors are clustered at the branch-day level.}
+%\textit{Do file: } \texttt{mechanisms.do}
+\end{table}
+
+\end{landscape}
+
+\noindent visits (col 11).\footnote{Figure \ref{hist_payments} plots the histogram of the timing of payments in each arm, and shows that commitment does appear to bind in that it generates a highly regular pattern of payments at 30, 60, and 90 days after the loan is taken.} Finally, Column 9 shows that treatment effects are concentrated in the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery.
+
+\noindent \textbf{Other costs.} We have shown that forcing borrowers to take the monthly payment contract significantly reduces their financial costs.
 Although the paper focuses on financial costs, we consider three additional costs here.
@@
 
-%Although adding a whole day's wage almost certainly exaggerates the travel costs associated with commitment contracts, we still find that forced commitment reduces both financial costs and APR.
-Columns (4) and (9) adjust for both travel costs and use the subjective rather than appraised value of the pawn.
-Finally, columns (5) and (10) remove saved interest payments from the calculation of the benefits.
-The rationale is that forcing borrowers to pay earlier reduces their liquidity, and they may need to borrow.
-We assume they borrow at the same interest rate.
-Thus considering other loans, they may not be paying less interest.
-The exercises in Table \ref{table_robustness_fc} show that results are quite robust to the inclusion and exclusion of components of benefits and costs.
-
-%Figure \label{fc_discount_rates} shows the effects of each of these adjustments on the estimate of financial cost and APR, and illustrates that even when we make all of these adjustment simultaneously the Forced arm generates benefits of 0.11 standard deviations, significant at the 95\% level.
-Forced commitment lowers financial costs even when we incorporate multiple subjective dimensions of the loan.
-
-\paragraph{Repeat Pawns.}
+\begin{table}
+\caption{Effects on more comprehensive cost measures}
+\label{table_robustness_fc}
+\begin{center}
+\scriptsize{\input{./Tables/fc_robustness.tex}}
+\end{center}
+ \legend{ This table augments the measure of financial cost presented in Table \ref{main_impact_table} with measures of transaction costs, subjective costs, and adjustments for liquidity costs. 
+ % Column 1 replicates the result of column 1 of Table \ref{main_impact_table} to ease comparability.
+Column 2 uses the subjective value of the pawn instead of the assessed gold value.
+Column 3 uses the cost from column 1 but adds to it the self-reported transport cost (most use public transport, imputing missing values with the average) as well as a whole day's minimum wage as a proxy for lost time.
+Column 4 ignores the `liquidity' cost in the financial cost formula by subtracting the interest of 7\% per month for each peso paid.
+Column 5 applies all these extra costs at the same time.
+Columns 6 to 10 apply the analogous changes to the APR formula.
+ Each regression includes branch and day-of-week FE. Standard errors are clustered at the branch-day level.}
+
+%\textit{Do file: } \texttt{fc\_robustness.do}
+\end{table}
+
+\noindent \textbf{Repeat Pawns.}
 %Another way to push the analysis towards a consideration of borrower welfare is the conjecture that if clients exposed to the installment contract like it, they will be more likely to come back vis-a-vis those that got status quo contract.\footnote{\cite{Laibson2018} hypothesizes that consumers use ``experienced utility'' as a guide to make future purchases in this way.} This is indeed what we find in the data.
@@
 
-%Moreover, in the (endogenous) subsample of those that recover, in Column 6 we do find that they return with a different collateral, as they recover the collateral of the first loan more often.
-
-%clients assigned to the forced commitment arm were more likely to recover their pawn, allowing them to re-pawn the same item in the future.
-We can explore this possibility in a number of ways.
-First, we can (endogenously) split the sample according to whether the individual defaulted on the experimental loan; here we find that the increase in subsequent borrowing is restricted to those who repaid the first one.
-Next, we can examine whether the probability that participants take another loan using \emph{different} collateral from the first.
-While the difference is not statistically significant, we find that the Forced arm elevates the probability of re-pawning with new collateral.
-We can also separately examine the probability of taking a new loan after the contract period of the original experimental loan (column 5) or before it (column 6).
-Here we find that the increase in subsequent pawning comes \emph{later}, significantly increasing the time to the subsequent loan (column 7).
-All of this evidence suggests that the effect on subsequent demand is `real' and not an artifact of improved retention of the collateral, consistent with \cite{Alcohol}'s conjecture that demand for commitment increases with experience with it.
-However, it remains possible that the additional demand for subsequent pawning comes from the fact that forcing earlier payments effectively reduces the credit available during the contract, and thus that clients may pawn again to compensate for the smaller loan.
-We are skeptical about this interpretation for several reasons.
-%First, typically the emergencies that trigger a pawn are short lived (e.g.
-needing to go to the hospital), and it is unclear why clients in the frequent payment arm wait for several months to re-pawn -- there is no effect of the monthly payment contract on repeat pawning in the first 30 or 60 days of the contract, (see Figure \ref{reincidence_before} in Appendix).
-First,  there are many alternative lenders in this market, and if they did not like frequent payments why do they come back to Lender $P$ for another loan?
-Second, the fee itself is mostly symbolic (2\% of 1/3 of the value of the loan) and so it is likely that if there were real financial costs to making an intermediate payment it would simply be skipped and the fee incurred.
-We also implemented an exit survey which clients filled when recovering their piece.
-Unfortunately it had low response rate (7\%), and we take its results with a grain of salt; however in this survey 63\% of clients said they liked the frequent payment contract more than the status-quo one, and that it allowed them to avoid unnecessary expenses.
-Finally and most importantly, the treatment effects on re-pawning are entirely confined to the period after the original loan term and so there is no obvious link between intermediate liquidity and demand for new credit.
-%Third, we find larger effects of repeat buying for clients that experienced larger treatment effects, which the alternative explanation cannot explain.
-Fourth, the effect is present if we condition on clients that recovered their pawn (so it's not driven by pawn recovery).
-Finally, we were able to obtain observational data for all Lender $P$'s branches for the period January 2016 to May 2020, during which Lender $P$ expanded the new frequent payment contract.
-Using an instrumental variable strategy that exploits the expansion and availability of the frequent payment contract across branches, we show that being exposed to the frequent payment contract leads to an increase of 50 percentage points in the likelihood that in the subsequent pawn the frequent payment contract is chosen when both the status-quo one and the frequent payment contract are available (see \ref{appendix_b}).
-This choice cannot be explained by the need of another loan, since it is about \textit{which specific type} of loan the clients chooses conditional on getting one.
-
-%An additional empirical issue generated by repeat pawning is the question of how to handle the treatment status of those who take multiple loans within the experiment.
-38\% of borrowers take more than one loan within the study period, and 19\% are assigned multiple treatment statuses on their different loans.
-The issue of sequential endogenous treatments has been extensively studied in the context of school lotteries, where the convention is to use the treatment status from the first exposure \citep{cullen2006effect, abdulkadirouglu2011accountability}.\footnote{That context provides a particularly severe version of the endogenous re-entry problem because only the losers from initial lotteries re-enter subsequent ones.
-Our selection problem is less draconian, but still potentially relevant since we do find treatment effects on pace of repayment and of pawning again.}  While our main impact tables simply use the assigned treatment status for every loan, in Table \ref{multiple_loans} we provide two straightforward robustness checks for the influence of this problem.
-Columns 1-2 repeat the main analysis of financial cost and APR using the baseline approach from our main results, including dummies for the order of pawns for an individual, essentially making the identification within-order.
-Columns 3-4 drop all loans other than the first, and Columns 5-6 pursue the ITT strategy of always assigning the first treatment status to all subsequent pawns.
-The core treatment effects are robust to any of these ways of handling repeat pawning, and the effect on the APR is actually larger when we consider first loans only.
-Hence endogenous re-entry to the experiment does not appear to be driving our results.
-
-\paragraph{Censoring of Loan Completion}
+\begin{table}
+\caption{Effects on Repeat Pawning}
+\label{repeat_loans}
+\begin{center}
+\scriptsize{\input{./Tables/repeat_loans.tex}}
+\end{center}
+ \legend{This table estimates the specification of equation \ref{basic_reg} but at the level of the borrower (not the loan). Each column represents a regression with a different outcome variable.
+ % In column 1, the dependent variable indicates, for each borrower in the experiment, whether he/she pawned again after the first loan in the experiment (up to the end period of our data set 338 days after the experiment began).
+Column 2 is analogous, but only pawning after 90 days of the first loan is considered.
+Column 3 instead considers pawning before 90 days.
+Column 4 is analogous to column 1 but focuses on the pawning of a gold piece that is different from the one in the first experimental loan.
+Column 5 is analogous to column 1, but conditioning on the sample that recovered the first loan.
+ Each regression includes branch and day-of-week FE. Standard errors are clustered at the branch-day level.}
+%\textit{Do file: } \texttt{repeat\_loans.do}
+\end{table}
+
+\noindent \textbf{Censoring of Loan Completion.}
 The window of time during which we were able to observe borrower behavior was limited in each branch, meaning that there were loans that we do not see completed (particularly those pawns that were rolled over for one or two further 90-day spells).
@@
 Figure \ref{tot_tut_graph} provides graphical intuition for our identification approach. % derivations appear in \ref{append:randchoice}
+
+\begin{figure}
+    \begin{center}
+        \centering
+        \includegraphics[width=1.0\textwidth]{Figuras/tot_tut_intuition.png}
+    \end{center}
+ \caption{The Controlled Choice Design.
+This figure provides graphical intuition for the way in which the controlled choice design from Section point identifies both the treatment on the treated (TOT) and treatment on the untreated (TUT) effects, as discussed in Section \ref{sec:randchoice} and \ref{append:randchoice}.
+    The gray shaded regions denote borrowers with a commitment contract; the white shaded regions denote borrowers with a status quo contract.
+    A comparison of means across control and forcing arms identifies the ATE of forcing  commitment.
+    The TOT and TUT effects of commitment are identified as follows.
+    In the choice arm, anyone with a commitment contract is a chooser; in the control and forcing arms, we do not know who is a chooser and who is not.
+    Because borrowers are randomly assigned to experimental treatment arms, however, the share of choosers will be the same, on average, across experimental arms.
+    This is depicted using dashed vertical lines in the control and forcing arms.
+    This overall share of choosers and non-choosers is point identified from the choice arm.
+    Now, the difference of mean outcomes across the choice and control arms gives the intent-to-treat effect of offering choice.
+    Under the exclusion restriction that moving non-choosers between the choice and forcing arms does not change their outcomes, this comparison ``nets out'' the non-choosers.
+    Hence, the ITT of offering choice equals the TOT multiplied by the share of choosers. 
+    Similarly, under the exclusion restriction that moving choosers between the choice and forcing arm does not affect their outcomes, the difference of means across the forcing and choice arms ``nets out'' the choosers and hence equals the TUT multiplied by the share of non-choosers.}
+    \label{tot_tut_graph}
+     %\textit{Do file: }  \texttt{tot\_tut\_graph.do}
+\end{figure}
 
@@
 
-\paragraph{TOT and TUT results.} Table \ref{tot_tut} calculates the causal quantities described above--TOT, TUT, ASG, ASB, and ASL--for our experimental data, along with robust standard errors for each.
+\begin{table}
+\caption{Treatment on the Treated (TOT), Treatment on the Untreated (TUT), Selection-on-gains (TOT - TUT), Average Selection Bias (ASB), and Average Selection Bias, calculated using the results from Section \ref{sec:randchoice}.}
+\label{tot_tut}
+\begin{center}
+\scriptsize{\input{./Tables/tot_tut.tex}}
+\end{center}
+\legend{This table presents results computed using the derivations from Section \ref{sec:randchoice} and \ref{append:randchoice}.
+The APR and financial cost outcomes have been multiplied by $-1$ so that a positive causal effect \emph{benefits} the borrower in each of the four columns.
+See Appendix \ref{subsec:inference} for more details on how we compute standard errors for the middle panel.
+The bottom panel present p-values for a number of null hypothesis tests of treatment effect heterogeneity. }
+%\textit{Do file: } \texttt{tot\_tut.do}
+\end{table}
+
+\noindent \textbf{TOT and TUT results.} Table \ref{tot_tut} calculates the causal quantities described above--TOT, TUT, ASG, ASB, and ASL--for our experimental data, along with robust standard errors for each.
 For purposes of comparison, the table also presents the ATE results from Section \ref{Experiment} above (row 1),\footnote{Coefficients are not exactly the same since Table 4 includes branch and day-of-week FE.} along with the corresponding average potential outcomes $\mathbbm{E}[Y_0]$ and $\mathbbm{E}[Y_1]$ (rows 4--5).
@@
 
-\vspace{.1in}
 Overall, Table \ref{tot_tut} suggests that commitment works but that \emph{not enough} people choose to commit: the commitment contract is beneficial on average even to those who would \emph{not} choose it voluntarily.
@@
 
-\paragraph{Learning.} A first explanation involves learning.
+\noindent \textbf{Learning.} A first explanation involves learning.
 Our experiment introduced a new contract into an environment that had not previously featured commitment; perhaps clients required experience to understand its benefits.
@@
 
-\paragraph{Time discounting.} Discounting is a second potential explanation for our results.
+\noindent \textbf{Time discounting.} Discounting is a second potential explanation for our results.
 Highly impatient individuals might rationally choose the \emph{status quo} contract, despite the benefits that commitment yields returns, since monthly payments are front-loaded while pawn recovery is back-loaded, even if by only a few days.
@@
 
-\paragraph{Present bias.} If the benefits of commitment among non-choosers cannot be explained by standard models of rational choice, the canonical behavioral story would center on time inconsistency.
+\noindent \textbf{Present bias.} If the benefits of commitment among non-choosers cannot be explained by standard models of rational choice, the canonical behavioral story would center on time inconsistency.
 While commitment is useful to anyone with hyperbolic time preferences, only those who are sophisticated--i.e.\ aware that they are hyperbolic discounters--will demand it.
@@
 
-%\todo[inline]{There are two exercises, and we'll do each one in the same way: present bias and sure confidence.
-In each case, there's a binary indicator that creates two groups.
-We want to know if this grouping can ``explain'' the positive TUT.
-At minimum, should see that effect is concentrated on those with the indicator equal to one.
-Never totally convincing since there could be an unobserved characteristic that is correlated with our indicator variable.
-If we had a clean hyperbolicity story, we'd have four strata: rational, time inconsistent and naive, time inconsistent and sophisticated, and a fourth group that chooses commitment despite being time consistent.
-If time inconsistency is the whole story, the negative TUT should be entirely concentrated on the naive types.
-In other words, they should have a large positive TUT but everyone else should but everyone else should have something close to zero or negative.
-In terms of decomposing the TUT, we're already restricting attention to people who would not choose.
-So when we're looking at the TUT we really only have two of these strata: rational types who are not hyperbolic and don't choose commitment, and types who are hyperbolic and don't choose commitment (naives).
-So $C=0,X=1$ is naive and $C=0,X=0$ is rational.
-Should find positive effect for $C=0,X=1$ and zero or negative for $C=0,X=0$.
-To be clear: the point is that we assume by choosing or not choosing commitment, you reveal whether you are sophisticated or not, given that we know your $X$.
-First thing we could ask is, among non-choosers how many are ``rational'' versus how many are naive.
-These are the two probabilities in Eq 12.
-Second compare the treatment effects.
-Can do the same thing for sure confidence with a slight caveat that it's harder to use the language ``naive'' or ``rational'' here, but we can still think about it in a similar kind of way as long as we're careful with the language.}
-
-\paragraph{Sure confidence.} While 72\% of survey respondents believe they have a 100\% chance of recovering their pawn, in reality only 43\% will go on to do so.  
+\begin{figure}
+    \begin{center}
+        \centering
+        \includegraphics[width=0.6\textwidth]{Figuras/tut_beh_partition.pdf} 
+    \end{center}
+     \scriptsize  
+\caption{Heterogeneity of the TUT by behavioral variables.
+Each panel in this figure shows how the estimated treatment on the untreated (TUT) effect varies with a binary survey variable $X_i$.
+In the left panel (P.B.), $X_i = 1$ if borrower $i$ is ``present-biased'' based on her responses to the time preference questions from our survey.
+In the right panel (Sure-confidence) $X_i = 1$ if  borrower $i$ reported that she was certain to recover her pawn, zero otherwise.
+% Each panel depicts three estimates and associated 95\% confidence bands: the overall TUT (blue), the TUT for borrowers with $X = 1$ (green), and the TUT for borrowers with $X = 0$ (red).
+By the law of iterated expectations, the overall TUT in each panel must lie between the group-specific TUTs.
+The overall TUT is slightly different in each panel, because some borrowers only completed part of the survey.
+In each panel, we present results for the full set of borrowers who answered the survey question or questions needed to determine $X_i$.
+From the left panel, we see that TUT does not appear to be higher among present-biased borrowers.
+In contrast, the right panel suggests that the positive and significant overall TUT is driven by individuals who are ``sure-confident,'' i.e.\ borrowers who report that they are certain to recover their pawn.
+}
+    \label{tut_beh_partition}
+      %\footnotesize{ \textit{Do file: }  \texttt{partition_tut.do}
+
+\end{figure}
+
+\noindent \textbf{Sure confidence.} While 72\% of survey respondents believe they have a 100\% chance of recovering their pawn, in reality only 43\% will go on to do so.  
 This suggests a borrower pool characterized by over-optimism.
@@
 
-\paragraph{Causal forests.} 
+\noindent \textbf{Causal forests.} 
 On average, the commitment contract benefits both those who would choose it and those who would not.
@@
 
-\paragraph{Treatment effect distributions.} Figure \ref{heterogeneous_effects} plots densities of the estimated conditional ATE, TOT, and TUT effects from the generalized random forest models described above.
+\noindent \textbf{Treatment effect distributions.} Figure \ref{heterogeneous_effects} plots densities of the estimated conditional ATE, TOT, and TUT effects from the generalized random forest models described above.
 In each case, the outcome variable is APR benefit, i.e.\ the reduction in APR from a commitment contract.
@@
 To be clear, this is a probability statement about conditional average effects over the distribution of \emph{covariates}.
-In particular, we estimate that   
-\[
-\int \mathbbm{1}\{\mathbb{E}[Y_1 - Y_0| X = \mathbf{x}, C = 0] < 0\} \, f(\mathbf{x}|C=0) \, \mathrm{d}\mathbf{x} 
-\]
-is approximately 0.07.\footnote{The share of non-choosers with negative conditional \emph{average} treatment effects need not equal the share with a negative \emph{individual} effects, i.e.\ $\mathbbm{P}(Y_1 < Y_0| C = 0)$.
+In particular, we estimate that  $\int \mathbbm{1}\{\mathbb{E}[Y_1 - Y_0| X = \mathbf{x}, C = 0] < 0\} \, f(\mathbf{x}|C=0) \, \mathrm{d}\mathbf{x}$ is approximately 0.07.\footnote{The share of non-choosers with negative conditional \emph{average} treatment effects need not equal the share with a negative \emph{individual} effects, i.e.\ $\mathbbm{P}(Y_1 < Y_0| C = 0)$.
 But the more treatment effect heterogeneity that $X_i$ explains, the closer these two values become.}
@@
 
-\paragraph{``Mistake'' tresholds.} Under the assumption that our instrumental forest estimates capture the main sources of treatment effect heterogeneity, we can use them to assess whether particular borrowers in the choice arm made ``mistakes'' in their decision to accept or refuse the commitment contract, in terms of predicted financial costs of the loan.
+\begin{figure}
+
+    \begin{center}
+     \begin{subfigure}{0.32\textwidth}
+       \centering
+      \includegraphics[width=\textwidth]{Figuras/he_dist_tau_hat_tot.pdf}
+          \caption{ToT}
+    \end{subfigure}
+    \begin{subfigure}{0.32\textwidth}
+       \centering
+      \includegraphics[width=\textwidth]{Figuras/he_dist_tau_hat_tut.pdf}
+          \caption{TuT}
+    \end{subfigure} 
+       \begin{subfigure}{.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/he_dist_tau_hat_eff.pdf}
+        \caption{ATE}
+    \end{subfigure} 
+    \end{center}
+    \caption{Heterogeneous Treatment Effects.}
+    \label{heterogeneous_effects}    
+  %\footnotesize{ } \textit{Do file: }  \texttt{cate_dist.do}
+\end{figure}
+\noindent \textbf{``Mistake'' tresholds.} Under the assumption that our instrumental forest estimates capture the main sources of treatment effect heterogeneity, we can use them to assess whether particular borrowers in the choice arm made ``mistakes'' in their decision to accept or refuse the commitment contract, in terms of predicted financial costs of the loan.
 To do this we use the same information that is depicted in Figure \ref{heterogeneous_effects}, but present it in a different way.
@@
 
+\begin{figure}[H]
+        \centering
+        \includegraphics[width=0.6\textwidth]{Figuras/line_cw_apr_tot_tut.pdf}
+ \caption{``Mistakes'' in the choice arm.
+This figure presents conditional average TUT and TOT effects for the APR outcome from Figure \ref{heterogeneous_effects} in an alternative manner, to consider the fraction of borrowers in the choice arm who made ``mistakes'' in their decision to accept or refuse the commitment contract.
+A ``mistake'' for a non-chooser is defined as a positive conditional TUT effect that significantly exceeds a specified threshold APR value.
+ The green curve equals $[1 - F_{\text{TUT}}(\delta)]\times 100\%$, where $F_{\text{TUT}}$ is the CDF corresponding to density of conditional TUT effects from Figure \ref{heterogeneous_effects}, computed using the instrumental forest approach from \cite{atheygrf}.
+Evaluated at any positive value on the horizontal axis, it gives the fraction of non-choosers in the choice arm who made a ``mistake'' by not choosing commitment.
+The green shaded region gives associated 95\% pointwise confidence bands.
+Analogously, a ``mistake'' for a chooser is defined as a negative conditional TOT effect that exceeds a specified threshold APR value.
+The red curve equals $F_{\text{TOT}}(-\delta)$ where $F_{\text{TOT}}$ is the CDF corresponding to the density of conditional TOT effects from Figure \ref{heterogeneous_effects}.
+The red shaded region gives associated 95\% pointwise confidence bands.
+For both the red and green curves, we define the APR threshold so that larger mistakes are to the \emph{right} of smaller mistakes.
+This allows us to construct the overall fraction of mistakes in the choice arm, the blue curve, as a weighted average of the green and red curves.
+The weights equal the share of choosers and non-choosers in the choice arm.}
+    \label{choose_wrong}
+\end{figure}
+
 The results in Figure \ref{choose_wrong} suggest that a large fraction of non-choosers made mistakes by not choosing commitment.
@@
 This now allows us to make a stronger statement in favor of paternalism in our context; not only does forced commitment generate large benefits on average, but it also benefits the vast majority of borrowers \emph{who would be coerced} under a policy of forced commitment.
-
-%As we increase the threshold on the size of the mistake necessary to be classified as having made the wrong choice, by definition the share of mistakes in both groups falls.
-
-%Among choosers, only 18\% would have had superior outcomes had they not complied, whereas among non-choosers almost 80\% made a mistake according to this definition.
-Because this arm is comprised of 89\% non-choosers, the overall rate of mistake in the arm was around 68\%.
-
-%benefit is the case that forcing commitment generates large benefits on average, but it is also generating benefits for almost 90\% of the forced population.
-
-%\todo[inline]{ 
-%Can read this from red curve (and error bars) in Figure \ref{choose_wrong}, simply $F(-x)$ for the conditional TOT.
-Comment on results.
-Relatively few negative conditional TOT estimates: around 20\% with wide confidence bounds.
-Again say APR threshold of 25\%.
-Then say something like 8\% to 27\% \hl{???} mistakes.
-%Blue curve: combine to understand mistakes overall across choosers and non-choosers.
-Weighted average of red (TOT/chooser) and green (TUT/non-chooser) with weights corresponding to shares of each type.
-Very similar to green curve since 89\% are non-choosers and we estimate that relatively few choosers had a negative conditional average treatment effect.}
-
-%These impacts allow us to think about whether individuals made ``mistakes'' in their choices.  
-%Specifically, for each client in the choice arm we want to know how much cost savings would she have gained had she chosen the opposite contract. 
-%We do this in two steps.  
-%First, we use  \cite{atheygrf}'s generalized random forests methodology to estimate the impact of the forced commitment arm relative to the control (forced status quo) at the individual level.  
-%The method generates a partition of the space of characteristics $X$, where each element of the partition is a leaf, and each leaf contains treatment and control clients with similar characteristics $x \in X$ which are used to calculate unbiased treatment effects for that leaf.
-%The optimal partition is that which minimizes expected mean squared error of treatment effects predictions out-of-sample. 
-%The tree is ``honest'' in that uses one sub-sample to build the trees that make up the random forest and another one to estimate treatment effects within those trees.
-%\cite{atheygrf} show that their treatment effects are asymptotically normal, which allows us to construct confidence intervals for our treatment estimate in each leaf. 
-%This method gives us the average causal effect on financing cost of getting the forced commitment contract instead of the status quo contract for a client $i$ with characteristics $x_i$; call it $TE^{F}_{i}(x_i)$.\footnote{Figure \ref{causal_tree1} and ???
-provide an illustration of the splits (leaves) that emerge from our implementation of the RF.
-\todo[inline]{I think we should list in a footnote which are the `wide' variables we are using.}}
-
-%\paragraph{Personalized benefit results.} Using the test provided by \cite{chernozhukov2018generic}, we reject the null of homogeneity in treatment effects and so begin our analysis of heterogeneity confident that it exists.
-Figure \ref{heterogeneous_effects} illustrates the substantial impact of the forced commitment arm on APR, financial cost and other outcomes.
-More than 90\% of the individuals have APR saving effects, and even in the upper bound confidence interval more than half of individuals benefit.
-
-%\paragraph{Estimates of financial cost `mistakes'.} In a second step we predict treatment effects for clients \textit{in the Choice arm} using the partition into leaves and the treatment effect from step 1, that is client $j$ is imputed the treatment effect of the leaf corresponding to her characteristics $x_j$.
-We call this counterfactual treatment effect $\widehat{TE}^{F}_{j}(x_j)$.
-This is precisely the counterfactual we wanted, because it lets us relate observed individual choices with estimated individual-level treatment effects.\footnote{This extrapolation of the treatment effects assumes that choice itself --conditional on a given contract-- does not affect behavior (note the evidence in the prior section suggesting this is the case).
-Although the extrapolation is to another population, by randomization it is a statistically identical population with common support.} Armed with this, we say that a client made a ``mistake'' if either she chose the status quo contract and her $\widehat{TE}^{F}_{i}$ is negative (i.e.
-more cost saving from the Forced contract), or if she chose the Commitment contract and $\widehat{TE}^{F}_{i}$ is positive, (i.e.
-financial costs are larger for the Commitment contract).
-When a client made a choice mistake, we say that its money-metric values is the absolute value of $|\widehat{TE}^{F}_{i}|$.
-
-%Using the forcing arms and extrapolating to the choice arms.
-%Then, we predict these treatment effects for everybody in the choice arm using characteristics $x_i$.
-Let $\widehat{TE}^{fee}_{i}$ be the predicted financial cost savings for person $i$ of choosing the Forced Commitment contract rather than the status quo one, divided by the size of her loan (i.e.
-the negative value of the predicted treatment effect on financial cost for person $i$).
-$\widehat{TE}^{sq}_{i}$ is the analogous for the status quo contract.
-We define the choice of person $i$ to be a ``mistake'' if
-
-%\begin{equation}
-% \{ i \; \text{chose} \; sq \; \text{and} \; \;  \widehat{TE}^{fee}_{i}>\widehat{TE}^{sq}_{i} + z \} \; \text{or} \; \{ i \; \text{chose} \; fee \; \text{and} \; \;  \widehat{TE}^{fee}_{i}<\widehat{TE}^{sq}_{i} - z \}
-%\end{equation}
-
-%Since the prediction of the treatment effect is an estimate and has noise, we do two things.
-First, we normalize $\widehat{TE}^{F}_{i}$ by the value of the loan of person $i$ and introduce a threshold parameter $z$ and say that a choice is a ``mistake'' if the alternative contract would generate greater than $z$ in savings.
-We vary this threshold from 0\% to 15\% of the value of the loan.
-Second, we take into account uncertainty in estimation of treatment effects and report results using the extremes of the 95\% confidence interval bounds for $\widehat{TE}^{F}_{i}$.
-
-%Figure \ref{choose_wrong}(a) plots on the Y axis the fraction of clients that made a choice ``mistake'' and on the X axis the threshold $z$.
-When $z=0$, we calculate that about 82\% of clients in the Choice arm chose contracts that induced \textit{higher} financial cost.
-Most mistakes are failures to choose the fee-commitment contract ({97}\%), while only {4}\% of those who chose the fee-commitment contract would have been better in the status-quo one.
-The average mistake in pesos is \$250.
-%(90\% confidence interval [140,390]).
-
-%However, the fraction of non-choosers making a mistake remains almost 20\% even at the highest threshold used (\$80 pesos), and panel b shows the \textcolor{red}{Complete this when understand figure}.
-Panel C conducts a related but distinct exercise, showing the fraction of the entire control sample who would do better if assigned to the Forced arm; using the smallest threshold this fraction is over 95\%, showing that in this context there is an almost across-the board welfare benefit arising from this arm.
-Since the only potential financial cost of the forced arm arises from individuals who would be induced to partially repay but then default anyways, this result suggests that very few such borrowers exist.
-
-%Panel C of this figure replicates this exercise for the forced commitment arm, with the difference being that the relevant treatment effect to match is now the ATE of the forced commitment arm.
-This allows us to identify the winners and losers from paternalism in a nuanced manner, since members of groups with CATEs$<$0 are hurt and everyone else is helped.
-Because the ATE$>$TUT, this exercise results in an even larger fraction of individuals benefiting from commitment; here we find that fully 91\% of individuals are better off being forced into commitment than staying in the control.
-.
 
@@
 
-\paragraph{Narrow inputs targeting.} To consider targeting effectiveness we must begin from an individual-specific ground truth, which we take from our estimated conditional average treatment effects (CATEs) $\widehat{\text{ATE}}(X_i)$ from the causal forest described in Section \ref{sec:RF},  which used the ``wide'' set of covariates (wide RF).% and data for all borrowers who replied to at least part of the intake survey.
+\noindent \textbf{Narrow inputs targeting.} To consider targeting effectiveness we must begin from an individual-specific ground truth, which we take from our estimated conditional average treatment effects (CATEs) $\widehat{\text{ATE}}(X_i)$ from the causal forest described in Section \ref{sec:RF},  which used the ``wide'' set of covariates (wide RF).% and data for all borrowers who replied to at least part of the intake survey.
 We then analyze how well we can predict the losers from paternalism using the ``narrow'' set of non-manipulable covariates listed above (narrow RF) for the same subset of borrowers.
@@
 
-\paragraph{Targeting assessment.}
-
-To more directly investigate our ability to target commitment, we use two different methods to predict who should be assigned to the commitment arm.
+\noindent \textbf{Targeting assessment.} To more directly investigate our ability to target commitment, we use two different methods to predict who should be assigned to the commitment arm.
 In each, we estimate a classification model using the ``narrow'' set of covariates to predict whether the CATE estimated from the wide random forest model (using all available covariates) is positive.
@@
 
-%Figure \ref{targeting_rules} compares the in-sample performance of these targeting rules against a policy of universal forced commitment.
-The plot presents the estimated proportion of borrowers who benefit from a particular treatment assignment rule, along with associated 95\% confidence bands, where ``benefit'' is defined as having a conditional average treatment effect above a particular threshold.
-As above, we take the conditional average effects from the ``wide'' causal forest as ground truth for the purposes of this exercise.
-Because this is an in-sample exercise, the logistic and random forest classification rules have an unfair advantage: there is no adjustment for overfitting.
-In spite of this, their performance is quite unimpressive relative to a policy of universal forced commitment.
-The fraction of the whole sample incorrectly targeted when moving from universal forced commitment to targeting based on the narrow RF falls only from 9.78\% to 9.59\%.
-The logit targeting rule actually makes things marginally worse.
-
-We compare the in-sample performance of targeting rules against a policy of universal forced commitment.
-Table \ref{hit_miss_rule} shows error rates for six possible assignment rules: assigning all borrowers to control, all to treatment (Forcing), the optimal (infeasible) assignment, narrow RF targeting, Logit targeting, and we evaluate ex-post the voluntary choice, taking the wide RF as the ground truth.
-While the narrow RF correctly assigns roughly half of those who do not benefit from commitment to control, it also incorrectly allocates 4.38\% of the sample that would have gained from treatment to control.
-As such, it only improves the overall correct targeting rate by about half of a percentage point relative to universal Forcing.
-The Logit assignment rule is less successful at predicting benefits and harms, with a higher share of borrowers incorrectly assigned to both treatment and control, meaning that the overall correct targeting rate for the Logit is 5 pp lower than universal Forcing.
-%In particular it makes many Type II errors, resulting in a net targeting performance that is actually worse than universal forcing. 
-The underlying cause of the weak performance of targeting is that the attribute that predicts gains from forcing (being sure confident and not choosing the commitment) is largely behavioral and not easily predicted with basic covariates, as seen in Figure \ref{tut_beh_partition}.
-
-Self-targeting through choice proves to be little better than assigning everyone to the control condition, given the low take-up rate and the presence of both Type I and Type II errors in the choice arm.
-Fully 87\% of individuals in the Choice arm made a ``mistake'', weighting the error rates among choosers and non-choosers by their relative frequency in the Choice arm.
-The takeaway is that given low take-up, the large fraction of the sample benefiting from commitment, and the weak predictive power of the narrow covariates, in this case universal paternalism assigning all borrowers to the commitment contract appears to be an attractive targeting method.
-
-%Given the poor explanatory power of the narrow covariates, as shown in Figure \ref{wide_narrow_forests}, it is unsurprising to see that the information gain from using these variables is small;
-
-%This latter results is driven by the confluence of the poor explanatory power of the narrow variables, as shown in Figure \ref{wide_narrow_forests}, with the fact that the logit matches the correct sample fraction of ones, therefore making numerous Type \hl{II} errors \hl{(Should it be Type I?)} in an environment where commitment is beneficial for most.
-
-%OLD SECTION 6 TEXT:
-
-%Moving more deeply into heterogeneity in treatment effects, we can try to understand the gains or losses from forcing at the individual level.
-To investigate this, we first use completely flexible non-parametric bounds, then add structure on to the individual heterogeneity via a random forest estimation, and finally we consider the optimal targeting of forced compliance.
-
-%As shown above in Section \ref{experiment}, the ATE of the commitment contract from the forced arm is positive and significant, both economically and statistically.
-But this is only an average effect: a positive ATE is still consistent with negative individual treatment effects for some borrowers.
-
-%Unless she is a strict utilitarian, any policymaker who is considering outlawing the \emph{status quo} contract in favor of the commitment contract needs to consider the extent and magnitude of harm that such a paternalistic policy will cause to \emph{individual} borrowers.
-Our TUT and ToT results from Section \ref{sec:randchoice} partially address this concern.
-In particular, our TuT estimates show that even those borrowers on whom a policy of paternalism would impose a binding constraint stand to benefit, on average, from commitment.
-Again, however, this is only an average effect: a positive TuT is perfectly consistent with negative treatment effects for \emph{some} of the untreated.
-This section takes a closer look at treatment effect heterogeneity, to better understand the gains and losses from a policy of forced commitment at the individual.
-First, we explore heterogeneity in the average effects reported in Sections \ref{experiment} and \ref{sec:randchoice} using random forests.
-Then we consider the problem of optimal targeting: how accurately can we determine which kinds of borrowers would benefit from commitment, based on their observed characteristics?
-
-%Now talk about paternalism.
-First, are people learning?
-Is it the case that people who have borrowed more in the past are less overconfident?
-Do people who were randomized into forced commitment later decide to choose commitment?
-Finally: how to target and who would be hurt if we instituted paternalism?
-The relevant counterfactual here it the TuT, since this is the causal effect of forcing the people who wouldn't choose voluntarily.
-Break down by covariates.
-Do we see any interesting patterns?
-
-%\subsubsection{Random Forest Bounds on Treatment Effects}
-
-%\todo[inline]{Frank/Issac: need to discuss confidence interval construction for the mistakes exercise.
-I'm not 100\% sure about it.
-There's question of what we can actually infer from the random forest exercise.
-We can't learn the distribution of treatment effects within a ``bin'' but we can learn the ATE in the bin along with its standard error, and we can treat that as approximately normal.
-Another issue concerns whether we do or do not use the observed outcomes for the people in the choice arm.
-At present we're not using this.
-But you might say that we should.
-This would entail predicting their \emph{counterfactual} outcome.
-What I mean here is that $\text{ATE}(X)$ is what you would use to assign someone to a particular treatment, given that you have observed their $X$.
-But what we have is a little different.
-We observe both their $X$ and either $Y_1$ or $Y_0$.
-I think there's an interesting question here about whether we're interested in something \emph{ex ante} or \emph{ex post}.
-It relates to the issue of ``mistakes.'' We should discuss briefly as a group so Frank \& Issac can make the appropriate adjustments if needed.}
-
-%\todo[inline]{Issac: add in the picture for the ToT/TuT version of the ``mistakes'' exercise \& histograms of treatment effects by groups.
-We already have the histogram in figure 15 for the ATE.
-Is it possible to say something about the covariates of the choosers for whom we estimate a negative ToT?}
-
-%\todo[inline]{Frank draft: The first exercise looks at ``mistakes.'' These are defined by predicting treatment effects for the people in the \emph{choice} arm using their covariates.
-If the treatment effect is positive and they don't choose treatment, this is a mistake.
-If the treatment effect is negative and they choose treatment this is a mistake.
-There are two ways of carrying out this exercise.
-The first way assumes that, conditional on $X$, there is no selection on gains.
-This version uses a model of heterogeneous treatment effects estimated using only people from the forced arms to create predicted ATEs for people in the choice arm.
-The second version calculates ToT and TuT versions of the same thing, but this involves using data from the choice arm, so it's less efficient because sample-splitting is required so we have to discard some people from the choice arm when calculating ``mistakes.'' Issac implements this with 5 partitions of 20/80, repeating five times and averaging over the result.
-Comparing the results of the two versions we find something interesting.
-For the non-choosers, the results are similar in both versions.
-Lots of mistakes and pretty big.
-For the choosers, we find very little evidence of mistakes using the ATE version and much more using the ToT version.
-What does this mean?
-It suggests some form of perverse selection on gains.
-These must be people who think commitment will help them but it actually hurts them.
-Question: what are their covariates like?
-What kind of people are they?
-This gets to Craig's question about who is hurt in each treatment regime.
-There aren't very many choosers (only 11\%) and something between 15 and 35\%, depending on the threshold, of them are ``hurt'' according to our model.
-So quantitatively it's not many people.
-What about with the ATE: what fraction of people \emph{overall} do we predict are hurt by the treatment?
-(We bounded it above, but now we have a model.) Seems like this is around 1-2\%.}
-
-%To more directly interrogate self-selection in this context, we would like to be able to relate \textit{individual} choices over commitment to the \textit{individual} counterfactual outcomes that borrowers would have realized in different states of nature.
-To achieve this, we can use the honest causal forest method to impute borrower-specific treatment effects of the assignment to Commitment, and then map this estimate to the choices individuals make in the Choice arm.
-
-\begin{comment}
-\subsection{Marginal Treatment Effects}
-As described above, our experimental design point identifies the ATE, TUT, and TOT without the need to carry out a marginal treatment effects (MTE) analysis that would rely, to some extent, on structural assumptions or shape restrictions.
-Nonetheless, researchers who are interested in learning more about essential heterogeneity can combine our design with an MTE approach.
-\todo[inline]{Need to flesh out a bit more, but in short: (1) can extend the results of Mogstad et al (2017) to use our ATE, TUT, and TOT as additional inequality restrictions that constrain partial identification bounds for MTEs; (2) Could allow more flexibility in the approach of Carneiro et al (2011) by recovering $\mu_0(x)$ and $\mu_1(x)$ from the forced arm.
-This permits richer forms of observed heterogeneity than the linear specification that is typically used in applied MTE papers.
-One could also combine (1) and (2) or use (1) as a specification test for (2).}
-
-\subsection{Relating Choice Probabilities to Benefits}
-
-The previous exercise consisted of extrapolating treatment effects from the no-choice arms to the Choice arm.
-Here we do the reverse.
-First, we estimate a flexible model of take-up of the commitment-fee contract \textit{in the Choice arm} using gradient boosting classification\footnote{Results are robust to other classification methods like Random Forest, SVM, etc.} and obtain for a client with characteristics $x_i$ a calibrated probability $P(x_i)$ of choosing the commitment contract.
-We then use this model to predict the counterfactual probability of a client with characteristics $x_j$ choosing the Commitment contract in the Forced arm if she had been given the choice, what we call $\widehat{P(x_j)}$.\footnote{Our gradient boosting take-up model has a good out-of-sample fit with an out-of-sample AUC of \colorbox{yellow}{0.85}.
-(accuracy 97\% in-sample and 90\% out-of-sample)} Now, armed with this propensity score in the Forced arm, we can ask whether people with larger Random Forest-estimated individual treatment effects (i.e.
-more cost savings) would have been more likely to choose it, as we would expect from a Roy model of treatment selection.
-
-We can represent the relationship between the HTEs from commitment and propensity scores in several ways.
-Most straightforward is Figure \ref{HTE_vs_propensity}, which plots the individually-estimated treatment effect from Forced versus Control treatments on the Y-axis, and the predicted probability of choosing commitment on the x-axis.
-The HTEs are very strongly downward-sloping over the part of the distribution that has heterogeneity in predicted propensities, the opposite of what we would expect from Roy-type selection.
-The sample with the lowest propensity of choosing commitment has a smoothed benefit of roughly twice those with a .2 change of choosing, measured both in terms of benefit/cost and in terms of probability of repayment.
-Hence the very large heterogeneous treatment effects are almost completely localized to the individuals who have the very lowest probability to select commitment.
-
-Second, we can turn the continuous propensity score into a binary predicted choice, such that the proportion of choosers matches the observed data, and then compute cumulative distribution functions of the heterogeneous conditional average treatment effects we estimated using the Causal Random Forest.
-Figure \ref{benefit_vs_choice_cdf} shows there is a first order stochastic dominance in treatment effects between the two predicted categories.
-This means those more likely to demand commitment are also those that had smaller benefits from commitment.
-
-Finally, a completely different approach to relating choice to HTEs arrives at a similar conclusion.
-We attempt to characterize the class that benefits more from commitment using a finite mixture model with two latent types.
-After estimation of this FMM, we find that the class more benefited from being forced is negatively correlated with demand for commitment (see Figure \ref{fmm_hte} in the appendix).
-We identify this class with the naive individuals, since choice is the core divider, and this class is predicted to default more (see Table \ref{fmm_table} in the appendix).
-This exercise emphasizes how important choice is as a segregator.
-
-Hence, we pursue several quite different techniques and all arrive at the same result.
-All of the treatment heterogeneity is found among individuals who did receive the Commitment contract, whether chosen or forced.
-Whether we exploit the point-identification of LATEs for compliers and non-compliers enabled by the Forcing arm, use HTEs to examine the `mistakes' made by choosers versus non-choosers in the Choice arm, estimate propensities and relate these to HTEs in the Forced arm, or use a non-parametric finite mixture model, the overall story is the same:  the wrong people are choosing commitment.
-
-These findings suggest that forcing clients into commitment contacts may reduce financial cost for the overwhelming majority of clients. 
-%Figure \ref{choose_wrong}(c) calculates what fraction of clients would be made better off if we forced them into the fee-commitment contract.
-We find that 85\% would be better off (using $z=0$), and they would on average have savings of 250MXN.
-This conclusion is in line with a recent paper by \cite{John}.
-In a savings context, she finds that when commitment is on the menu a majority of subjects wrongly choose too little commitment and fail to reach their savings goals.
-It is also in line with \cite{Sprenger} who show that the more naive about their present bias are the ones who demand less commitment.\footnote{This result is also similar to \cite{Walters}, who finds that students that select into more effective schools are the ones with smaller treatment effects from attending.
-That paper uses distance to school as an instrumental variable for choice, while we use randomization to choice vs no-choice groups as our empirical strategy.}
-
-\end{comment}
-
-\section{Conclusion} \label{conclusion}
-
-This paper makes several contributions.
-First, it analyzes the large but understudied industry of pawn loans, and shows that a simple change to contract terms results in substantial financial savings for pawn borrowers: forced commitment lowers the APR from 57\% to 46\%, and reduces the fraction of borrowers who default by 6.6 pp, or 15\%.
-That this new contract generated large benefits for borrowers and yet was not offered, and that a contract that generated default was the industry standard instead, is related to the idea of ``veiled paternalism'' \cite{Laibson2018}, put on its head.
-In ``veiled paternalism'' principals embed forms of commitment into their products but mask this fact from consumers who may need but do not desire commitment, in pawn lending, over-collateralization means that lenders stand to make more money from defaulting borrowers, generating incentives for ``veiled \textit{non}-paternalism,'' embedding features that lead to high borrower costs in non-obvious ways.
-
-%Potentially due to the nature of the borrower pool, 
-%In our context voluntary commitment choice does improve borrower outcomes, but forcing commitment did induce significant cost savings for the overall group of clients.
-
-Second, our novel  ``controlled choice'' design allows us to go beyond ATE results and draw an important set of conclusions about the relationship between take-up and heterogeneous treatment effects.
-In particular, we simultaneously point-identify the impact of commitment on those who would naturally choose it \emph{and} those who only experience commitment when forced.
-Estimating this later quantity is critical in thinking about paternalism.
-We find substantial benefits of treatment for non-choosers and no evidence of selection on gains by borrowers who choose commitment.
-Given that the rate of voluntary commitment in our sample is only 11\%, in order to achieve widespread benefits in this context compulsory commitment appears to be necessary.
-%Clients appear to prefer the forced commitment after they have experienced it, in that assignment to this arm increases the fraction of individuals who return to pawn again.
-
-Why do borrowers leave such substantial returns on the table?
-Our results suggest that over-optimism is the characteristic most strongly associated with benefiting from the commitment despite not having chosen it.
-Our borrower pool overestimates their probability of repayment by more than 50\%, and our positive TUT estimate is largely confined to borrowers who incorrectly believe that they have little chance of defaulting.
-%More standard explanations such as discounting, learning, or time inconsistency find little support in our data.
-
-Using machine learning methods, we find the benefits of commitment close to universal.
-The benefits of targeting commitment based on characteristics that lenders can observe and participants would truthfully reveal are extremely limited, suggesting that universal commitment is an attractive policy in our empirical setting.
-
-%but the determinants that might allow us to target it more finely are primarily behavioral and hence not easily predicted in a fast incentive-compatible manner by lenders, making universal assignment to commitment attractive.
-Of course, in other applications this would have to be decided on a case-by-case basis.
-%Even a sophisticated machine learning-based exercise is only able to decrease the fraction of borrowers mis-targeted less than half percentage points relative to simply assigning everyone to commitment (from 9.78\% to 9.59\%).
-and a logit-based targeting rule actually does slightly worse than universal commitment.
-
-Where lenders have no incentive to engage in veiled paternalism and customers display inefficiently low demand for it, financial policy regulation may prove an attractive option.
-Pawnshops, along with other over-collateralized credit products such as payday lending, exist in an environment where the lender may desire customers to lose their collateral on the loan, hurting especially low-income populations who are its main users.
-With a now well-established toolkit of regular small payments and incentives delivering small default rates in microfinance, regulators may fruitfully investigate the possibility of requiring pawnbrokers to embed features of commitment and regularity into their repayment structures in more consistent ways.\footnote{If employed at scale in a competitive lending sector this would redistribute welfare from those who would have repaid (whose interest rates must now rise to cover lower returns from collateral seizure) towards those who would only repay in the presence of commitment.
-In a setting of lender market power however, redistribution from lenders to borrowers could occur.}
-An important question for future research will be the extent to which borrowers are able to learn about the benefits of commitment over time, making it so that temporary, lighter-touch policies could achieve lasting benefits for borrowers.
-Pawning with commitment may provide an important mechanism to preserve flexible credit access while allowing more poor borrowers to retain their assets.
-
-%In a pawnshop borrowing context, we study whether forcing borrowers into frequent payment commitment contracts reduces their borrowing costs, compared to a contract that does not provide commitment to pay monthly.
-Even though we are charging them fees,  borrowing costs under forced commitment are actually reduced by 9.4\%, and pawnrecovery is 26\% higher.
-Moreover they themselves seem to like this contract, as they are twice as likely to come back and pawn again when they are assigned to forced commitment.
-That is, commitment matters and it seems beneficial.
-
-%We examine treatment heterogeneity using a range of methods, from bounds that make no assumptions, exploiting a mild exclusion restrictions and the innovative controlled choice design to gain point identification of TUT and TOT, and invoking seletion on observables to estimate treatment effects at the person level.
-We find that a large majority of clients benefit from the commitment contract, but that when given choice between the commitment and the status quo contract only 10\% choose the former one and thus forgo important financial benefits.
-We also find that overconfident clients experience larger treatment effect cost savings from the commitment contract but at the same time have smaller demand for it.
-(\hl{Is it true that they have smaller demand?
-Which Figure shows this?
-If so we should say this above and not only in the conclusion})
-%A simple model shows that present bias with naivete parsimoniously explains all findings. 
-%The analysis suggests that it is possible in our context to advance an individual's financial  by restricting her freedom of choice ---although we caution that our outcome measure focuses on financing cost and is not a comprehensive measure of welfare.
-%These results spurred --although we cannot show they caused-- Lender $P$ to offer frequent payment contacts, although Lender $P$ was uncomfortable forcing these contracts on clients.
-They hoped that clients would eventually learn which contract was better for them.
-
-%Methodologically, to our knowledge this is the first paper in economics that uses machine learning methods and a combination of choice and forcing arms to estimate personalized counterfactual treatment gains to ask whether treatment takeup is positively selected on benefits, a hypothesis we reject.
-
-%Pawnshop borrowing may attract particularly unsophisticated clients and freedom of choice may fare better in other contexts.
-Choice may also fare better with other contracts besides the fee-commitment one we used.
-We experimented with a ``softer'' commitment contract in the form of a personal promise, and found that although this soft commitment contract  elicited more interest, it did not cause changes in behavior.
-
-%Our results suggest several avenues for future research.
-First, it would be useful to tease out the roles played by naivete about self control problems and biased expectations about income shocks in driving low demand for commitment.
-Second, one could ask whether other types of contracts %---for instance those that provide some insurance against shocks---
-%induce larger demand and better performance than the ones we tried.
-Third, testing and quantifying of there is selection to pawnshop lenders based on unsophistication could be important for regulators.
-Fourth, collecting broader measures of welfare to use as outcomes --e.g.
-subjective well being and consumption-- would help to make broader claims about welfare than we can make in this paper.
-Finally, one would like to know which interventions could de-bias consumers, or whether learning alone would do the work.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\newpage
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%BIBLIOGRAPHY
-
-\clearpage
-\bibliographystyle{authordate1}
-%\bibliographystyle{amsalpha}
-%\bibliographystyle{AER}
-
-\bibliography{References}
-
-%\FloatBarrier
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\newpage
-\singlespacing
-
-\section{Tables}
-
-\begin{table}[H]
-\caption{Limited and balanced attrition}
-\label{attrition_table}
-\begin{center}
-\scriptsize{\input{./Tables/Attrition.tex}}
-\end{center}
- \scriptsize Each row in this table 
- corresponds to a regression.
-The dependent variables of these regressions are displayed in the first column.
-Each dependent variable is regressed in a multivariate OLS regression against the experimental arms indicators (control, forced commitment, choice).
-The table reports the coefficients on each of these indicators, as well as the p-value an F-test of the null hypothesis of equality of the three coefficients.
-The dependent variables are: the number of pawns-loans originated per day per branch, the number of borrowers per day-branch, a variable indicating whether a person who answered the baseline survey (before knowing contract terms) ended up pawning, and an indicator of whether the person that obtained the loan answered the baseline survey.
-By design we had the choice arm be larger.
-Figure \ref{boxplot_attrition}, in the appendix shows a box-plot of the first two variables, showing the distribution across arms is balanced.
-%\textit{Do file: } \texttt{ss\_att.do}
-\end{table}
-
-% \begin{table}[H]
-% \caption{Number of pawns balance before and after the experiment}
-% \label{num_pawns_bal}
-% \begin{center}
-% \scriptsize{\input{./Tables/num_pawns_bal.tex}}
-% \end{center}
-%  \scriptsize We test if the number of pawns per day for the 6 branches that participated in the experiment was different before the experiment started or after the experiment ended.
-To this end we estimated the following regression, and cluster the standard errors by branch:
-%  $$Pawns \: per \: day_{jt} = \alpha_j + \gamma f(t) + \beta_b \mathbbm{1}(t \in MB)_{t} +\beta_a \mathbbm{1}(t \in MA)_{t}$$
-%  , where $\alpha_j$ are branch fixed effects, $f(t)$ is a third degree polynomial in time, $\beta_b$ measures a level effect in the number of pawns per branch before the experiment started, and $\beta_a$ after.
-We estimate no difference in the number of pawns, showing that people are not leaving the branch without pawning at larger rates during the experiment.
-Moreover, in appendix Figure \ref{rd_pawns} we also test for differences before and after the experiment using a regression discontinuity type plot for the number of pawns, and find there are no differences.
-% %\textit{Do file: } \texttt{num_pawns_bal.do}
-% \end{table}
-
-\newpage
-\begin{table}[H]
-\caption{Summary statistics and Balance}
-\label{SS}
-\begin{center}
-\scriptsize{\input{./Tables/SS.tex}}
-\end{center}
-
-%\textit{Do file: } \texttt{ss\_att.do}
-\end{table}
-\vspace{-.3in}
-\scriptsize {
-\noindent This table has two panels.
-Panel A uses administrative data at the loan level, while Panel B uses survey data.
-Each row in this table corresponds to a regression, where the level of observation is the individual loan originated.
-The dependent variables of these regressions are displayed in the first column.
-Each dependent variable is regressed in a multivariate OLS regression against the experimental arms indicators (control, forced commitment, choice).
-The table reports the coefficients on each of these indicators, as well as the p-value an F-test of the null hypothesis of equality of the three coefficients.
-The admin data was a very limited set of pre-determined variables.
-The dependent variables in Panel A are the loan amount in pesos, and an indicator for whether the day of the loan origination was a weekday (as opposed to weekend).
-The dependent variables in Panel B from the survey (see the questions in Table \ref{baseline_survey}.
-Subjective value of the pawn (how much would the client be willing to sell it for (Q3), an indicator for having trouble paying bills in the last 6-months (Q28), present bias (constructed from questions Q10 and Q29 in the standard way as in \cite{Ashraf}), an indicator for whether they make expenses budget for the month ahead of time.
-The subjective probability of recovery was elicited a la Manski (from 0 to 100 what is the probability that you will recoup your pawn), pawned before is a dummy=1 if the client declares to have pawned before (although not necessarily with Lender $P$) age is in year, +High-school is a dummy that indicates if the client has completed high school.
-}
-
-\newpage
-
-\vspace{.2in}
-
-\begin{table}[H]
-\caption{Effects on Financial Cost}
-\label{main_impact_table}
-\begin{center}
-\scriptsize{\input{./Tables/decomposition_main_te.tex}}
-\end{center}
-\scriptsize This table shows the treatment effects for our core pecuniary outcomes.
-Each column is a different regression for different outcomes on an indicator for the forced and choice arms, following specification in equation \ref{basic_reg}.
-Columns (1) \& (7) analyze our core financial cost measures, while the rest of the columns decompose these into finer components.
-
-% \begin{align*}
-%     \underbrace{\text{Financial Cost}_i}_{(1)} =&  \underbrace{\sum_t P^i_{it}}_{\underset{(2)}{\text{Payments to interests}}}  +\underbrace{\sum_t P^f_{it}}_{\underset{(3)}{\text{Payments of fees}}} + \underbrace{\overbrace{\mathds{1}(\text{Default}_i)}^{(6)}\times (\text{Val-Loan Diff}_i}_{\underset{(5)}{\text{Cost of losing pawn}}} + \underbrace{\sum_t P^c_{it}}_{\underset{(4)}{\text{Payments to capital}}})
-% \end{align*}
-
-A few borrowers take more than one loan on the first day they appear in an experimental branch.
-These are treated as different observations.
-Table \ref{multiple_loans} shows our results are similar when dealing with the multiplicity of loans per borrower.
-Each regression includes branch and day-of-week FE.
-Standard errors are clustered at the branch-day level.
-
-%\textit{Do file: } \texttt{decomposition\_main\_te.do}
-\end{table}
-
-\newpage
-\begin{landscape}
-\begin{table}[H]
-\caption{Effects on intermediate outcomes}
-\label{mechanisms}
-\begin{center}
-\resizebox{1.30\textwidth}{!}{
-\scriptsize{\input{./Tables/mechanism.tex}}
-}
-\end{center}
-
-%\textit{Do file: } \texttt{mechanisms.do}
-\end{table}
-
-\scriptsize {
-\noindent This table explores treatment effects in ``intermediate variables''.
-Each column represents regression output for different dependent variables following equation (\ref{basic_reg}).
-Panel A focuses on variables related to the speed of payment.
-While Panel B focuses on variables related to default, and Panel C related to visits.
-The outcome variables are as follows:  number of days elapsed between origination and first payment (col 1); percentage of the loan paid in the first payment (col 2); probability of recovery in the first visit (col 3); loan duration is the number of days the borrower took to payoff her loan for those that recover, the number of days until default for those that default, and the maximum number of days we observe them in the sample for those that have not recovered or defaulted (col 4); loan duration conditional on recovery; an indicator for paying a positive amount towards recovery but nonetheless losing the pawn (col 6); the percentage or the loan paid, conditional on defaulting --`wasted payments' (col 7).
-Column 8 uses the phrase `selling the pawn' for a dummy variable indicating the borrower did not pay any amount towards recovery and lost the pawn.
-Moreover, (col 9) shows that treatment effects are concentrated in the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery.
-The dependent variable in column 10 is the number of day-visits to the branch (measured by the existence of transactions that day associated with our particular pawn), while column 11 conditions on borrowers that lost the pawn.
-Each regression includes branch and day-of-week FE.
-Standard errors are clustered at the branch-day level.}
-%In sum, we find that the Forced commitment contract clients pays 13.8 days earlier in average, during this first visit, clients pay 7.7\% more of the loan amount, with a 8\% increase probability of recovery.
-Moreover, the forced commitment contract reduces the probability of defaulting and making a positive payment by 7\%, thus another channel for savings is that treatment helps avoid making payments toward recovery but defaulting.}
-
-\vspace{3ex}
-
-\end{landscape}
-
-\begin{table}[H]
-\caption{Effects on more comprehensive cost measures}
-\label{table_robustness_fc}
-\begin{center}
-\scriptsize{\input{./Tables/fc_robustness.tex}}
-\end{center}
- \scriptsize 
- This table augments the measure of financial cost presented in Table \ref{main_impact_table} with measures of transaction costs, subjective costs, and adjustments for liquidity costs.
-Column 1 replicates the result of column 1 of Table \ref{main_impact_table} to ease comparability.
-Column 2 uses the subjective value of the pawn instead of the assessed gold value.
-Column 3 uses the cost from column 1 but adds to it the self-reported transport cost (most use public transport, imputing missing values with the average) as well as a whole day's minimum wage as a proxy for lost time.
-Column 4 ignores the `liquidity' cost in the financial cost formula by subtracting the interest of 7\% per month for each peso paid.
-Column 5 applies all these extra costs at the same time.
-Columns 6 to 10 apply the analogous changes to the APR formula.
-Each regression includes branch and day-of-week FE.
-Standard errors are clustered at the branch-day level.
-
-%\textit{Do file: } \texttt{fc\_robustness.do}
-\end{table}
-
-\cleardoublepage
-
-%\begin{landscape}
-
-\begin{table}[H]
-\caption{Effects on Repeat Pawning}
-\label{repeat_loans}
-\begin{center}
-\scriptsize{\input{./Tables/repeat_loans.tex}}
-\end{center}
- \scriptsize
-This table estimates the specification of equation \ref{basic_reg} but at the level of the borrower (not the loan).
-Each column represents a regression with a different outcome variable.
-In column 1, the dependent variable indicates, for each borrower in the experiment, whether he/she pawned again after the first loan in the experiment (up to the end period of our data set 338 days after the experiment began).
-Column 2 is analogous, but only pawning after 90 days of the first loan is considered.
-Column 3 instead considers pawning before 90 days.
-Column 4 is analogous to column 1 but focuses on the pawning of a gold piece that is different from the one in the first experimental loan.
-Column 5 is analogous to column 1, but conditioning on the sample that recovered the first loan.
-Each regression includes branch and day-of-week FE.
-Standard errors are clustered at the branch-day level.
-%\textit{Do file: } \texttt{repeat\_loans.do}
-\end{table}
-%\end{landscape}
-
-\cleardoublepage
-
-\begin{table}[H]
-\caption{Treatment on the Treated (TOT), Treatment on the Untreated (TUT), Selection-on-gains (TOT - TUT), Average Selection Bias (ASB), and Average Selection Bias, calculated using the results from Section \ref{sec:randchoice}.}
-\label{tot_tut}
-\begin{center}
-\scriptsize{\input{./Tables/tot_tut.tex}}
-\end{center}
-\scriptsize
-This table presents results computed using the derivations from Section \ref{sec:randchoice} and \ref{append:randchoice}. 
-Each column corresponds to an outcome variable: APR in column (1), financial cost in column (2), an indicator for \emph{not} defaulting in column (3), and an indicator for \emph{not} refinancing in column (4).
-The APR and financial cost outcomes have been multiplied by $-1$ so that a positive causal effect \emph{benefits} the borrower in each of the four columns.
-The top panel presents treatment on the treated (TOT) and treatment on the untreated (TUT) effect estimates, with standard errors clustered at the branch-day level.
-The average treatment effect (ATE) results from Section \ref{Experiment} are presented for purposes of comparison, along with average treated and untreated potential outcomes.
-The middle panel presents estimates of the average selection on gains $(\text{TOT} - \text{TUT})$, along with the average selection bias (ASB) and the average selection on levels (ASL), again with standard errors clustered at the branch-day level.
-See Appendix \ref{subsec:inference} for more details on how we compute standard errors for the middle panel.
-The bottom panel present sample sizes, and p-values for a number of null hypothesis tests of treatment effect heterogeneity. 
-%\textit{Do file: } \texttt{tot\_tut.do}
-\end{table}
-
-\begin{table}[H]
+\begin{table}
 \caption{Type I \& II errors using targeting narrow rules}
@@
 \end{center}
-\scriptsize This table reports error rates for six different rules for allocating individuals to commitment.
+\legend{This table reports error rates for six different rules for allocating individuals to commitment.
 The first row allocates all borrowers to control.
@@
 The sixth row gives the percentage of miss-classification that would follow from the observed choice.
-%assigns the commitment contract to all borrowers with a positive conditional ATE estimate from the ``narrow'' RF.
-The fifth row uses a logistic regression to estimate the probability that a given borrower has a positive conditional ATE, assigning commitment to those with an estimated \hl{probability greater than 0.5}.
-
+}
 \end{table}
 
-\vspace{.3in}
-
-%\begin{table}[H]
-%\caption{Overconfidence: Take-up and Treatment Effects}
-%\label{oc_reg}
-%\begin{center}
-%\scriptsize{\input{./Tables/oc_reg.tex}}
-%\end{center}
-% \footnotesize This table shows the parameter estimates of $y_i = \alpha + \beta \: OC_i + Z_i'\gamma + \epsilon_i$, where $OC_i:=\mathbbm{1}(P^s_i-\widehat{P_i(X_i)}>0)$ is an indicator for the subjective probability of recovery being larger than the predicted one.
-In columns 1-4 $y_i$ is a dummy for whether the client $i$ chose to have the commitment contract in the respective choice arm, and in columns 5 and 6 $y_i$ is the heterogeneous treatment effect for financial cost (in pesos) estimated by comparing the Forced Commitment vs status quo arms in Section \ref{TE_fee-forcing}.
-Columns 1 and 3 are estimated for the promise-choice arm, while columns 2 and 4 are estimated for the Commitment Choice arm.
-The low number of observations results from  our use of  covariates for $\widehat{P(x)}$ and in $Z$ in the regression, given that some of them are missing.
-%\textit{Do file: } \texttt{oc.do}
-%\end{table}
-
-%\begin{table}[H]
-%\caption{Overconfidence: Take-up and Treatment Effects}
-%\label{oc_reg}
-%\begin{center}
-%\scriptsize{\input{./Tables/oc_reg_dec.tex}}
-%\end{center}
-% \footnotesize This table shows the parameter estimates of $y_i = \alpha + \beta \: OC_i + Z_i'\gamma + \epsilon_i$, where $OC_i:=\mathbbm{1}(P^s_i-\widehat{P_i(X_i)}>0)$ is an indicator for the subjective probability of recovery being larger than the predicted one.
-In columns 1-4 $y_i$ is a dummy for whether the client $i$ chose to have the commitment contract in the respective choice arm, and in columns 5 and 6 $y_i$ is the heterogeneous treatment effect for financial cost (in pesos) estimated by comparing the Forced Commitment vs status quo arms in Section \ref{TE_fee-forcing}.
-Columns 1 and 3 are estimated for the promise-choice arm, while columns 2 and 4 are estimated for the Commitment Choice arm.
-The low number of observations results from  our use of  covariates for $\widehat{P(x)}$ and in $Z$ in the regression, given that some of them are missing.
-%\textit{Do file: } \texttt{oc.do}
-%\end{table}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+We compare the in-sample performance of targeting rules against a policy of universal forced commitment.
+Table \ref{hit_miss_rule} shows error rates for six possible assignment rules: assigning all borrowers to control, all to treatment (Forcing), the optimal (infeasible) assignment, narrow RF targeting, Logit targeting, and we evaluate ex-post the voluntary choice, taking the wide RF as the ground truth.
+While the narrow RF correctly assigns roughly half of those who do not benefit from commitment to control, it also incorrectly allocates 4.38\% of the sample that would have gained from treatment to control.
+As such, it only improves the overall correct targeting rate by about half of a percentage point relative to universal Forcing.
+The Logit assignment rule is less successful at predicting benefits and harms, with a higher share of borrowers incorrectly assigned to both treatment and control, meaning that the overall correct targeting rate for the Logit is 5 pp lower than universal Forcing.
+%In particular it makes many Type II errors, resulting in a net targeting performance that is actually worse than universal forcing. 
+The underlying cause of the weak performance of targeting is that the attribute that predicts gains from forcing (being sure confident and not choosing the commitment) is largely behavioral and not easily predicted with basic covariates, as seen in Figure \ref{tut_beh_partition}.
+
+Self-targeting through choice proves to be little better than assigning everyone to the control condition, given the low take-up rate and the presence of both Type I and Type II errors in the choice arm.
+Fully 87\% of individuals in the Choice arm made a ``mistake'', weighting the error rates among choosers and non-choosers by their relative frequency in the Choice arm.
+The takeaway is that given low take-up, the large fraction of the sample benefiting from commitment, and the weak predictive power of the narrow covariates, in this case universal paternalism assigning all borrowers to the commitment contract appears to be an attractive targeting method.
+
+\section{Conclusion} \label{conclusion}
+
+This paper makes several contributions.
+First, it analyzes the large but understudied industry of pawn loans, and shows that a simple change to contract terms results in substantial financial savings for pawn borrowers: forced commitment lowers the APR from 57\% to 46\%, and reduces the fraction of borrowers who default by 6.6 pp, or 15\%.
+That this new contract generated large benefits for borrowers and yet was not offered, and that a contract that generated default was the industry standard instead, is related to the idea of ``veiled paternalism'' \cite{Laibson2018}, put on its head.
+In ``veiled paternalism'' principals embed forms of commitment into their products but mask this fact from consumers who may need but do not desire commitment, in pawn lending, over-collateralization means that lenders stand to make more money from defaulting borrowers, generating incentives for ``veiled \textit{non}-paternalism,'' embedding features that lead to high borrower costs in non-obvious ways.
+
+%Potentially due to the nature of the borrower pool, 
+%In our context voluntary commitment choice does improve borrower outcomes, but forcing commitment did induce significant cost savings for the overall group of clients.
+
+Second, our novel  ``controlled choice'' design allows us to go beyond ATE results and draw an important set of conclusions about the relationship between take-up and heterogeneous treatment effects.
+In particular, we simultaneously point-identify the impact of commitment on those who would naturally choose it \emph{and} those who only experience commitment when forced.
+Estimating this later quantity is critical in thinking about paternalism.
+We find substantial benefits of treatment for non-choosers and no evidence of selection on gains by borrowers who choose commitment.
+Given that the rate of voluntary commitment in our sample is only 11\%, in order to achieve widespread benefits in this context compulsory commitment appears to be necessary.
+%Clients appear to prefer the forced commitment after they have experienced it, in that assignment to this arm increases the fraction of individuals who return to pawn again.
+
+Why do borrowers leave such substantial returns on the table?
+Our results suggest that over-optimism is the characteristic most strongly associated with benefiting from the commitment despite not having chosen it.
+Our borrower pool overestimates their probability of repayment by more than 50\%, and our positive TUT estimate is largely confined to borrowers who incorrectly believe that they have little chance of defaulting.
+%More standard explanations such as discounting, learning, or time inconsistency find little support in our data.
+
+Using machine learning methods, we find the benefits of commitment close to universal.
+The benefits of targeting commitment based on characteristics that lenders can observe and participants would truthfully reveal are extremely limited, suggesting that universal commitment is an attractive policy in our empirical setting.
+
+%but the determinants that might allow us to target it more finely are primarily behavioral and hence not easily predicted in a fast incentive-compatible manner by lenders, making universal assignment to commitment attractive.
+Of course, in other applications this would have to be decided on a case-by-case basis.
+%Even a sophisticated machine learning-based exercise is only able to decrease the fraction of borrowers mis-targeted less than half percentage points relative to simply assigning everyone to commitment (from 9.78\% to 9.59\%).
+and a logit-based targeting rule actually does slightly worse than universal commitment.
+
+Where lenders have no incentive to engage in veiled paternalism and customers display inefficiently low demand for it, financial policy regulation may prove an attractive option.
+Pawnshops, along with other over-collateralized credit products such as payday lending, exist in an environment where the lender may desire customers to lose their collateral on the loan, hurting especially low-income populations who are its main users.
+With a now well-established toolkit of regular small payments and incentives delivering small default rates in microfinance, regulators may fruitfully investigate the possibility of requiring pawnbrokers to embed features of commitment and regularity into their repayment structures in more consistent ways.\footnote{If employed at scale in a competitive lending sector this would redistribute welfare from those who would have repaid (whose interest rates must now rise to cover lower returns from collateral seizure) towards those who would only repay in the presence of commitment.
+In a setting of lender market power however, redistribution from lenders to borrowers could occur.}
+An important question for future research will be the extent to which borrowers are able to learn about the benefits of commitment over time, making it so that temporary, lighter-touch policies could achieve lasting benefits for borrowers.
+Pawning with commitment may provide an important mechanism to preserve flexible credit access while allowing more poor borrowers to retain their assets.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%BIBLIOGRAPHY
+
+\bibliographystyle{ecta-fullname} % Style BST file
+\bibliography{References}  % Bibliography file (usually '*.bib')
 
 \newpage
-\section{Figures}
-
-\vspace{.2in}
-\begin{figure}[H]
-     \caption{Financial cost}
-    \label{fc_hist}
-    \begin{center}
-    \begin{subfigure}{.45\textwidth}
-      \caption{In pesos MXN}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_fc.pdf}
-    \end{subfigure}
-     \begin{subfigure}{0.45\textwidth}
-    \caption{Effective APR}
-       \centering
-      \includegraphics[width=\textwidth]{Figuras/hist_apr.pdf}
-    \end{subfigure}
-    \end{center}
-         \scriptsize
-         Panel (a) presents a histogram of financial cost (defined as in Section \ref{costs}) for the control group.
-The figure plots separately the financial cost separately for borrowers who lose the pawn (blue) and those that recover it (transparent).
-Panel (b) is analogous but displays the APR.
-%Given that the loan lasts close to 90 days, bringing payments to present value makes little difference.
-
-      %\footnotesize{ } \textit{Do file: }  \texttt{hist\_fc.do}
-\end{figure}
-
-\begin{figure}[H]
-     \caption{Experiment description}
-    \label{exp_description}
-\begin{center}
-\begin{subfigure}{\textwidth}
-        \includegraphics[width=\textwidth]{Figuras/consort.pdf}
-    \end{subfigure}
-  \end{center}
-    \scriptsize
-
-%\textit{Do file: }  \texttt{ss\_att.do}
-\end{figure}
-
-\cleardoublepage
-
-\begin{comment}
-
-\begin{figure}[H]
-     \caption{TOT \& TUT as LATE}
-    \label{tot_tut_graph}
-    \begin{center}
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/tot_tut_apr.eps}
-    \end{subfigure}
-    \end{center}
-    \scriptsize
-   \hl{REPLACE THIS ONE WITH THE ONE IN THE PRESENTATION}
-     %\textit{Do file: }  \texttt{tot\_tut\_graph.do}
-\end{figure}
-\end{comment}
-
-\begin{figure}[H]
-\caption{The Controlled Choice Design}
-    \label{tot_tut_graph}
-    \begin{center}
-        \centering
-        \includegraphics[width=1.0\textwidth]{Figuras/tot_tut_intuition.png}
-    \end{center}
-    \scriptsize
-    This figure provides graphical intuition for the way in which the controlled choice design from Section point identifies both the treatment on the treated (TOT) and treatment on the untreated (TUT) effects, as discussed in Section \ref{sec:randchoice} and \ref{append:randchoice}.
-    The gray shaded regions denote borrowers with a commitment contract; the white shaded regions denote borrowers with a status quo contract.
-    A comparison of means across control and forcing arms identifies the ATE of forcing  commitment.
-    The TOT and TUT effects of commitment are identified as follows.
-    In the choice arm, anyone with a commitment contract is a chooser; in the control and forcing arms, we do not know who is a chooser and who is not.
-    Because borrowers are randomly assigned to experimental treatment arms, however, the share of choosers will be the same, on average, across experimental arms.
-    This is depicted using dashed vertical lines in the control and forcing arms.
-    This overall share of choosers and non-choosers is point identified from the choice arm.
-    Now, the difference of mean outcomes across the choice and control arms gives the intent-to-treat effect of offering choice.
-    Under the exclusion restriction that moving non-choosers between the choice and forcing arms does not change their outcomes, this comparison ``nets out'' the non-choosers.
-    Hence, the ITT of offering choice equals the TOT multiplied by the share of choosers. 
-    Similarly, under the exclusion restriction that moving choosers between the choice and forcing arm does not affect their outcomes, the difference of means across the forcing and choice arms ``nets out'' the choosers and hence equals the TUT multiplied by the share of non-choosers.
-
-     %\textit{Do file: }  \texttt{tot\_tut\_graph.do}
-\end{figure}
-
-\begin{figure}[H]
-    \caption{Heterogeneity of the TUT by behavioral variables}
-    \label{tut_beh_partition}
-    \begin{center}
-        \centering
-        \includegraphics[width=0.75\textwidth]{Figuras/tut_beh_partition.pdf} 
-    \end{center}
-     \scriptsize  Each panel in this figure shows how the estimated treatment on the untreated (TUT) effect varies with a binary survey variable $X_i$.
-In the left panel (P.B.), $X_i = 1$ if borrower $i$ is ``present-biased'' based on her responses to the time preference questions from our survey.
-In the right panel (Sure-confidence) $X_i = 1$ if  borrower $i$ reported that she was certain to recover her pawn, zero otherwise.
-Each panel depicts three estimates and associated 95\% confidence bands: the overall TUT (blue), the TUT for borrowers with $X = 1$ (green), and the TUT for borrowers with $X = 0$ (red).
-By the law of iterated expectations, the overall TUT in each panel must lie between the group-specific TUTs.
-The overall TUT is slightly different in each panel, because some borrowers only completed part of the survey.
-In each panel, we present results for the full set of borrowers who answered the survey question or questions needed to determine $X_i$.
-From the left panel, we see that TUT does not appear to be higher among present-biased borrowers.
-In contrast, the right panel suggests that the positive and significant overall TUT is driven by individuals who are ``sure-confident,'' i.e.\ borrowers who report that they are certain to recover their pawn.
-     %to be largely concentrated relevant survey question  according to her survey responses two binary performs a partition of the Treatment on the Untreated (FC), estimating the share of the effect that arises within each of two binary categories.
-The top bars examine present bias (individuals are more impatient over one-month time horizon than they are between three and four months).
-The bottom bars examine sure confidence (individual reports 100\% probability of repaying at time of taking loan).
-Blue bar is the component arising from those without the trait, orange bar from those with the trait.
-      %\footnotesize{ \textit{Do file: }  \texttt{partition_tut.do}
-
-\end{figure}
-
-\begin{figure}[H]
-     \caption{Heterogeneous Treatment Effects}
-    \label{heterogeneous_effects}
-    \begin{center}
-     \begin{subfigure}{0.55\textwidth}
-    \caption{ToT}
-       \centering
-      \includegraphics[width=\textwidth]{Figuras/he_dist_tau_hat_tot.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.55\textwidth}
-    \caption{TuT}
-       \centering
-      \includegraphics[width=\textwidth]{Figuras/he_dist_tau_hat_tut.pdf}
-    \end{subfigure} 
-       \begin{subfigure}{.55\textwidth}
-      \caption{ATE}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/he_dist_tau_hat_eff.pdf}
-    \end{subfigure}
-
-    \end{center}
-         \scriptsize
-     This Figure plots the densities of treatment on the untreated effects (TUT), treatment on the treated (TOT) effects, and conditional average treatment effects (ATE) based on the instrumental and causal forest models from Section \ref{sec:RF}.
-  %\footnotesize{ } \textit{Do file: }  \texttt{cate_dist.do}
-\end{figure}
-
-\begin{figure}[H]
-    \caption{``Mistakes'' in the choice arm}
-    \label{choose_wrong}
-   % \begin{center}
-   %     \begin{subfigure}{0.45\textwidth}
-   %     \caption{``Mistakes'' in choice arm}
-        \centering
-        \includegraphics[width=0.75\textwidth]{Figuras/line_cw_apr_tot_tut.pdf}
-  %  \end{subfigure}
-  %      \begin{subfigure}{0.45\textwidth}
-  %      \caption{\% with positive CATE from forced commitment}
-  %      \centering
-  %      \includegraphics[width=\textwidth]{Figuras/line_better_forceall_apr_te_cf.pdf}
-
-  %  \end{subfigure}
-
-  %  \end{center}
-        %\scriptsize
-        %In Panel (a) we estimate what the treatment effect of the commitment contract \textit{would have been} for all subjects in the choice arm if they had been forced into the fee-commitment contract.
-To do this we proceed in two steps.
-First, we estimate treatment effects in the forcing arm by comparing the Forced Commitment arm against the status quo arm.
-We let these effects be heterogeneous as a function of our $x$'s using \cite{atheygrf}'s methodology of causal forests.
-Second, we extrapolate these treatment effects based on the choice arm using the same $x$'s.
-Once we have personalized counterfactual treatment effects in the choice arm we calculate what fraction of subjects in the choice arm incurred in financial costs that are  $> z$\% than if they had chosen the opposite contract of what they actually chose, were $z$\% is defined as a fraction of the loan.
-$z$\% is a level of tolerance we can vary and we plot it in the X-axis.
-The left Y-axis measures the fraction of subjects that would have been better by a margin of $z$\% if they changed their choice, and the right Y-axis measures the amount of money ``left on the table''.
-We use bootstrap to tighten the confidence intervals (CIs).
-\cite{atheygrf}'s heterogeneous treatment effect using GRF is asymptotically normal.
-We compute the HTE ($\mu$) together with standard errors ($\sigma$) .
-For every pledge, we draw a random effect from a normal distribution with parameters ($\mu$,$\sigma^2$), and compute via bootstrap the percentage that choose wrong, along normal-approximation CIs (results are robust if we use instead percentile CIs or bias-corrected CIs) .
-This allows us to estimate a distribution for the upper and lower bound CIs, which we then use to obtain a 95\% CI.
-Panel (b) is analogous to Panel (a) except that it does the exercise separately for clients we classified as overconfident ($OC_i:=\mathbbm{1}(P^s_i-\widehat{P_i(X_i)}>0))$ and those we classified as not overconfident.
-Panel (c) simulates what percentage would be better by at least $z$ if we forced everybody of those in the Commitment Choice arm into the fee-commitment contract.
-        % Panel (d) asks whether it is the case that people with larger causal benefits from the Forced Commitment contract would be more likely to select that contract.
-To do this we proceed in two steps as well.
-First we estimate a flexible model of take-up of the fee commitment contract \textit{in the choice arm} using random forests, and from this model obtain a probability $P(x_i)$ of choosing the Forced Commitment contract for a client with characteristics $x_i$.
-We extrapolate this model to clients in the Forced Commitment arm to estimate what would they have chosen if we had given them choice.
-        % Figure (d) plots $\widehat{P(x_i)}$ in the X-axis using a binscatter that splits the X-axis in 100 percentile bins.
-The Y-axis plots the heterogeneous treatment effects of the fee forcing contract on the probability of losing the pawns (more negative means then more likely to recover it), averaged for the respective x-axis bin.
-Positive assortative selection would mean a negative relationship: those who benefit more by treatment and lose the pawn less are \emph{less} likely to choose it.
-Using all bins we estimate a slope of zero in the relationship.
-Using the 80 right most points, we estimate a \textit{positive} relationship.
-        %\textit{Do file: }  \texttt{choose\_wrong\_quant\_wrong\_tot\_tut.do, choose\_wrong\_quant\_wrong\_decomposition.do}
-\end{figure}
-
-This figure presents conditional average TUT and TOT effects for the APR outcome from Figure \ref{heterogeneous_effects} in an alternative manner, to consider the fraction of borrowers in the choice arm who made ``mistakes'' in their decision to accept or refuse the commitment contract.
-A ``mistake'' for a non-chooser is defined as a positive conditional TUT effect that significantly exceeds a specified threshold APR value.
-The green curve equals $[1 - F_{\text{TUT}}(\delta)]\times 100\%$, where $F_{\text{TUT}}$ is the CDF corresponding to density of conditional TUT effects from Figure \ref{heterogeneous_effects}, computed using the instrumental forest approach from \cite{atheygrf}.
-Evaluated at any positive value on the horizontal axis, it gives the fraction of non-choosers in the choice arm who made a ``mistake'' by not choosing commitment.
-The green shaded region gives associated 95\% pointwise confidence bands.
-Analogously, a ``mistake'' for a chooser is defined as a negative conditional TOT effect that exceeds a specified threshold APR value.
-The red curve equals $F_{\text{TOT}}(-\delta)$ where $F_{\text{TOT}}$ is the CDF corresponding to the density of conditional TOT effects from Figure \ref{heterogeneous_effects}.
-The red shaded region gives associated 95\% pointwise confidence bands.
-For both the red and green curves, we define the APR threshold so that larger mistakes are to the \emph{right} of smaller mistakes.
-This allows us to construct the overall fraction of mistakes in the choice arm, the blue curve, as a weighted average of the green and red curves.
-The weights equal the share of choosers and non-choosers in the choice arm.
-
-%\todo[inline]{Panel (a).
-Green line: survival function computed using estimated TUT of non-choosers in the choice arm.
-Red line: $F(-x)$ where $F$ is the CDF of individual TOT estimates for the choosers in the choice arm.
-Blue curve is the weighted average of the green and red with weights equal to the share of choosers versus non-choosers in the choice arm.
-Panel (b) is the survival function for the ATE computed for who?
-We think it's for the choice arm.
-(Shouldn't make a difference because of randomization and fairly large sample sizes.) Confidence bands are computed how?
-Use asymptotic normality and variance for each ``cell''}
-
-\cleardoublepage
-
-% \begin{figure}[H]
-%     \caption{Negative selection on treatment effects}
-%     \label{benefit_vs_choice_cdf}
-%     \begin{center}
-%     \begin{subfigure}{0.475\textwidth}
-%         \caption{APR benefit}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/cdf_predchoose_tau_apr.pdf}
-%     \end{subfigure}
-%     \begin{subfigure}{0.475\textwidth}
-%         \caption{Repayment}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/cdf_predchoose_tau_des.pdf}
-%     \end{subfigure}
-%     \begin{subfigure}{0.475\textwidth}
-%         \caption{Default}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/cdf_predchoose_tau_def.pdf}
-%     \end{subfigure}
-%     \end{center}
-%      \scriptsize    CDF of the heterogeneous treatment effect for choosers vs non-choosers.
-The dotted line below indicates the points where the difference in the distributions is significant.
-Instead of a single global null hypothesis (that the two CDFs are identical), there is a continuum of individual null hypotheses of CDF equality at each point.
-This methodology was proposed by \cite{GOLDMAN2018143}.
-
-%      \hl{Isaac : If I recall correctly we agreed to not work with the propensities.
-Besides this is giving us different results(?) - this was due to not using actual choosers and the prop.
-score model not being very good.
-Thus this will be removed?
-}
-%           %\footnotesize{ \textit{Do file: }  \texttt{benefit\_choice.do}}
-% \end{figure}
-
-\newpage
-\input{OA.tex}
-
+
+\input{ECTA submission/OA_ecta}
 \end{document}

### 2023-12-14 OA.tex
prepare for ecta submission
prepare for submission

@@
 \begin{center}
-	\LARGE The limits of self-commitment and private paternalism \\[0.5em]
+	\LARGE The controlled choice design and private paternalism in pawnshop borrowing \\[0.5em]
 	\Large{Appendix $-$ For Online Publication} \\[1em]
@@
 
-\section{Treatment Explanation Materials and Pictures}
+\linespread{1.05}
+
+\linespread{1.05}
+
+\section{ Treatment Explanation Materials and Pictures}
 \vspace{.2in}
@@
      %   \centering
-        \includegraphics[width=0.65\textwidth]{Figuras/TicketLenderP.png}
+        \includegraphics[width=0.5\textwidth]{Figuras/TicketLenderP.png}
     %\end{subfigure}
@@
     \end{center}
-    \scriptsize
+    \scriptsize{
         We show a sample receipt that was given to clients that got assigned to the fee-forcing contract (the font and format were changed to protect Lender's P identity).
@@
 It emphasizes that the client is giving his word, and that the promise is not a legal document.
+        }
 \end{figure}
@@
     \begin{center}
-    \begin{subfigure}{\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/micas.pdf}
-    \end{subfigure}
-    \end{center}
-    \scriptsize
-        This is a (translated) sample information slide shown to clients. The real ones were twice the size of this figure and were laminated. Different ones were shown for each treatment arm.
-\end{figure}
-
-\cleardoublepage
+        \centering
+        \includegraphics[width=0.6\textwidth]{Figuras/micas.pdf}
+
+    \end{center}
+    \scriptsize{
+        This is a (translated) sample information slide shown to clients. The real ones were twice the size of this figure and were laminated. Different ones were shown for each treatment arm.}
+\end{figure}
 
@@
     \end{center}
-    \scriptsize
-        This figure  shows pictures of pawnshops in Mexico city. They do not necessarily coincide with Lender P for confidentiality. 
+    \scriptsize{
+        This figure  shows pictures of pawnshops in Mexico city. They do not necessarily coincide with Lender P for confidentiality.} 
 \end{figure}
@@
     \end{center}
-    \scriptsize
-        This figure shows pictures of gold buyers next to pawnshops in Mexico city. They do not necessarily coincide with Lender P for confidentiality. 
+    \scriptsize{
+        This figure shows pictures of gold buyers next to pawnshops in Mexico city. They do not necessarily coincide with Lender P for confidentiality. }
 \end{figure}
@@
 
-\vspace{.2in}
-
 \normalsize
-\linespread{1.25}
+\linespread{1.05}
 %Really force it to normal size and linespread
 \normalsize
-\linespread{1.25}
+\linespread{1.05}
 
@@
 
-\cleardoublepage
-
 \begin{table}[H]
@@
 \end{center}
-\scriptsize
-Translation of the baseline questionnaire.
+\scriptsize{
+Translation of the baseline questionnaire.}
 \end{table}
 
-\cleardoublepage
-
 \newpage
-\subsection{Descriptives consistent with overconfidence}
-
-\vspace{.2in}
-\begin{figure}[H]
+\subsection{More descriptives}
+
+%The second thing to note is that those that are not closed at the end of our sample period have already incurred substantial financial cost, even though they have not defaulted yet.
+
+%Of those who renew, 83\% lose the pawn.
+Figure \ref{fc_hist}(a) suggest that financial cost is significant, even for those that do recover their pawn.
+Panel (b) normalizes the cost by loan size.
+It shows that as a percentage of their pawn, most of the cost comes from clients that do not recover their pawn.
+For them the cost is between 140\% and 250\% of the loan value.
+%{The difference between panel (a) and (b) arises since clients who lose their pawn tend to be those that pledge cheaper pieces.}
+
+\begin{figure}[!h]
+\caption{Financial cost.}
+  \label{fc_hist}
+    \begin{center}
+    \begin{subfigure}{.42\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/hist_fc.pdf}
+        \caption{}
+    \end{subfigure}
+     \begin{subfigure}{0.42\textwidth}
+       \centering
+      \includegraphics[width=\textwidth]{Figuras/hist_apr.pdf}
+      \caption{}
+    \end{subfigure}
+    \end{center}
+
+ \scriptsize{Panel (a) plots a histogram of this financial cost in pesos for all loans in the experiment, stratified by whether we observed that they ended in default or recovery of the pawn.
+Panel (b) shows the analogous histogram for the APR.
+%defaulted (44\%), recovered their pawn (43\%), or whether they are censored in our data (13\%). 
+We see that borrowers who default incur higher costs; part of this is mechanical as losing their collateral is part of the cost.
+Most of the APR costs indeed come from clients who do not recover their pawn.}
+
+      %\footnotesize{ } \textit{Do file: }  \texttt{hist\_fc.do}
+\end{figure}
+
+\begin{figure}[!h]
     \caption{Behavior of borrowers who lost their pawn}
@@
     \begin{center}
-    \begin{subfigure}{0.40\textwidth}
+    \begin{subfigure}{0.35\textwidth}
         \caption{Elapsed days to first payment}
@@
     \end{subfigure}
-    \begin{subfigure}{0.40\textwidth}
+    \begin{subfigure}{0.35\textwidth}
         \caption{Elapsed days to last payment}
@@
     \end{subfigure}
-        \begin{subfigure}{0.40\textwidth}
+        \begin{subfigure}{0.35\textwidth}
         \caption{Payments as \% of loan}
@@
     \end{subfigure}
-    \begin{subfigure}{0.40\textwidth}
+    \begin{subfigure}{0.35\textwidth}
         \caption{Number of payments}
@@
 
-\vspace{.1in}
-\section{Internal Validity}
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\section{ Internal Validity}
+
+If potential borrowers disliked being forced into a commitment contract, we would expect a lower number of pawns on branch days where only the commitment contract is available compared to control days.
+Table \ref{attrition_table} shows that this is not the case.
+There is no difference at all between the Control and Forced Commitment arm in terms of the number of pawns per branch-day.
+Although we cannot reject equality across the three arms (p-value=0.21), the Choice arm appears to have a somewhat larger number of borrowers than the Control and Forced arms.\footnote{p-value=0.23 and 0.12 respectively.} This seems to be due to sampling variability.
+The differences across arms are smaller when we look at medians, or when we look at the number of borrowers pawning (some borrowers pawn more than one piece).
+Figure \ref{boxplot_attrition} shows that full distribution of loans per day is very similar across treatment arms.
+The only noticeable difference is that the choice arm has a few more positive outliers.\footnote{If we winzorize at the 90th percentile, the mean number of branch-day pawns becomes identical across arms.}
+
+\begin{table}
+\caption{Limited and balanced attrition}
+\label{attrition_table}
+\begin{center}
+\scriptsize{\input{./Tables/Attrition.tex}}
+\end{center}
+\scriptsize{Each row in this table 
+ corresponds to a regression.
+The dependent variables are: the number of pawns-loans originated per day per branch, the number of borrowers per day-branch, a variable indicating whether a person who answered the baseline survey (before knowing contract terms) ended up pawning, and an indicator of whether the person that obtained the loan answered the baseline survey.
+Each dependent variable is regressed in a multivariate OLS regression against the experimental arms indicators (control, forced commitment, choice).
+The table reports the coefficients on each of these indicators, as well as the p-value of an F-test of the null hypothesis of equality of the three coefficients.
+Figure \ref{boxplot_attrition}, in the appendix shows a box-plot of the first two variables, showing the distribution across arms is balanced.}
+%\textit{Do file: } \texttt{ss\_att.do}
+\end{table}
+
+The bottom panel of Table \ref{attrition_table} shows balance in a more focused way, given that the surveys were conducted prior to the revelation of treatment status.
+We find that in no arm did more than three percent of individuals who responded to the survey go on to refuse loans.
+That is, the overwhelming marjority of potential borrowers did not leave the branch after learning which contract was on offer.
+Moreover, the extremely small fraction that did leave is balanced across arms.
+Therefore it appears that the treatments have not induced any endogenous shifts in the composition of borrowers.
+
+A less critical form of attrition is differential refusal to answer the survey questions.
+The survey was conducted before treatment status was revealed, and we observe loan outcomes regardless of whether the survey was conducted.
+Our core experimental estimates do not use the survey data as covariates, but the analysis in Section \ref{Paternalism} is restricted to the subset of borrowers who answered at least some survey questions.
+The bottom row of Table \ref{attrition_table} shows that the survey response rate is broadly similar across arms (about 78 percent).
+
+\vspace{.2in}
 \begin{figure}[H]
@@
     \begin{center}
-    \begin{subfigure}{0.45\textwidth}
+    \begin{subfigure}{0.35\textwidth}
     \caption{Number of pawns}
@@
     \end{subfigure}
-        \begin{subfigure}{0.45\textwidth}
+        \begin{subfigure}{0.35\textwidth}
     \caption{Number of borrowers}
@@
 \newpage
-\section{Main treatment effects: Additional material}
 
 \begin{landscape}
+\section{ Main treatment effects: Additional material}
 \subsection{Multiple loans}
@@
     \begin{center}
-    \begin{subfigure}{0.75\textwidth}
+    \begin{subfigure}{0.6\textwidth}
         \centering
@@
 
-\vspace{.2in}
 \begin{figure}[H]
@@
     \begin{center}
-    \begin{subfigure}{0.45\textwidth}
+    \begin{subfigure}{0.31\textwidth}
         \caption{Status-quo}
@@
     \end{subfigure}
-    \begin{subfigure}{0.45\textwidth}
+    \begin{subfigure}{0.31\textwidth}
         \caption{Forced commitment}
@@
     \end{subfigure}
-    \begin{subfigure}{0.45\textwidth}
+    \begin{subfigure}{0.31\textwidth}
         \caption{Choice commitment}
@@
 
-\cleardoublepage
-
 \subsection{Censoring} \label{App_censoring}
 
-\vspace{.2in}
-
 \normalsize
-\linespread{1.25}
+\linespread{1.05}
 %Really force it to normal size and linespread
 \normalsize
-\linespread{1.25}
+\linespread{1.05}
 
@@
 We now consider some alternative approaches.
-\\
 
@@
 
-\vspace{.3in}
 \begin{table}[H]
@@
 \begin{center}
-\resizebox{0.9\textwidth}{!}{
-\scriptsize{\input{./Tables/censoring_imp.tex}}
+\resizebox{1.0\textwidth}{!}{
+\scriptsize{\input{./Tables/censoring_imp_1.tex}}
 }
@@
 \end{table}
- \scriptsize 
+\begin{table}[H]
+\begin{center}
+\resizebox{1.0\textwidth}{!}{
+\scriptsize{\input{./Tables/censoring_imp_2.tex}}
+}
+\end{center}
+
+ \scriptsize {
  Given the censored loans, i.e.
@@
 
- Note that in all panels we maintain significant results for Financial Cost as dependent variable, while only in the most conservative scenario (Panel B) we lose significance for the APR outcome.
+\noindent Note that in all panels we maintain significant results for Financial Cost as dependent variable, while only in the most conservative scenario (Panel B) we lose significance for the APR outcome.
+}
+\end{table}
 
 \begin{figure}[H]
-        \caption{Interpolation on bounding censoring}
+        \caption{Interpolation on bounding censoring for Default}
     \label{interpolation_censoring_imp}
     \begin{center}
-   \begin{subfigure}{0.49\textwidth}
-   \caption{Significance area for APR}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/frontera_sig_apr.pdf}
-    \end{subfigure}     
-    \begin{subfigure}{0.49\textwidth}
-   \caption{Significance area for Default }
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/frontera_sig_def_imp.pdf}
-    \end{subfigure} 
-    \end{center}
-     \scriptsize  The next figure aims to answer the following question: For how many loans in the control arm can we impute recovery, and for how many in the treatment arm can we impute default and still have significance?
+   % \begin{subfigure}{0.49\textwidth}
+   % \caption{Significance area for APR}
+   %      \centering
+   %      \includegraphics[width=\textwidth]{Figuras/frontera_sig_apr.pdf}
+   %  \end{subfigure}     
+   %  \begin{subfigure}{0.49\textwidth}
+   % \caption{Significance area for Default }
+        \centering
+        \includegraphics[width=0.5\textwidth]{Figuras/frontera_sig_def_imp.pdf}
+    % \end{subfigure} 
+    \end{center}
+     \scriptsize  {The next figure aims to answer the following question: For how many loans in the control arm can we impute recovery, and for how many in the treatment arm can we impute default and still have significance?
      This figure shows exactly the boundary separating significance when we vary the percentage of imputed censored loans with recovery and default respectively for control and treatment.
@@
 The `x' indicates the proportions imputed by the lasso logit model, and the different lines correspond to setting different significance levels.
-We do not include the plot for financial cost, since for any imputation we still have significant results.
+We do not include the plot for APR nor financial cost, since for any imputation we still have significant results.}
 
@@
 
-\newpage
-\section{Alternative explanations}
-
-\vspace{.2in}
+\subsection{Robustness accounting for other costs}
+
+\begin{table}[!h]
+\caption{Effects on more comprehensive cost measures}
+\label{table_robustness_fc}
+\begin{center}
+\scriptsize{\input{./Tables/fc_robustness.tex}}
+\end{center}
+ \scriptsize{ This table augments the measure of financial cost presented in Table \ref{main_impact_table} with measures of transaction costs, subjective costs, and adjustments for liquidity costs.
+Panel A reports financial cost in pesos, while Panel B shows APR.
+Columns (1) and (6) replicate our previous results for comparability.
+Columns (2) and (7) of Table \ref{table_robustness_fc} use the subjective value of the pawn reported by the borrower rather than its appraised value.
+Columns (3) and (8) adjust for self-reported transport costs per visit plus an entire day's wage, both multiplied by the number of visits that each individual made.\footnote{For clients who did not complete the individual survey, we adjust using the mean self-reported transport cost among respondents of the respective branch.} Columns (4) and (9) adjust to consider the liquidity cost.
+Finally, columns (5) and (10) include all three changes together.
+The main takeaway from the table is that results are quite robust to including a much expanded measure of costs.
+Each regression includes branch and day-of-week FE.
+Standard errors are clustered at the branch-day level.}
+%\textit{Do file: } \texttt{fc\_robustness.do}
+\end{table}
+
+\section{ Alternative explanations}
+
 \subsection{Learning}
@@
 \vspace{.1in}
-\begin{table}[H]
+\begin{table}[!h]
         \caption{Effect of Prior Assignment on Subsequent Choice}
@@
 \end{table}
-
-\vspace{.3in}
 
@@
 
-\newpage
-
 \normalsize
-\linespread{1.25}
+\linespread{1.05}
 %Really force it to normal size and linespread
 \normalsize
-\linespread{1.25}
+\linespread{1.05}
 
 \begin{comment}
-\section{Causal Forest and individual predictions of `Mistakes'}
+\section{ Causal Forest and individual predictions of `Mistakes'}
 
@@
 
-\cleardoublepage
-
-\section{Heterogeneity and Bounds}
+\section{ Heterogeneity and Bounds}
 
@@
 
+\newpage
+
 \subsection{Bounds, FOSD and Rank Invariance} \label{bounds_FOSD}
 
-\vspace{.3in}
-\begin{figure}[H]
+\begin{figure}[!h]
     \caption{Fan \& Park bounds for benefit in APR\%}
@@
     \begin{center}
-    \begin{subfigure}{0.75\textwidth}
+    \begin{subfigure}{0.55\textwidth}
         \caption{APR}
@@
 
-\vspace{.2in}
-\begin{figure}[H]
+\begin{figure}[!h]
         \caption{Empirical CDF: Forced commitment vs Control FOSF}
     \label{ecdf_fc}
-
     \begin{center}
@@
 
-\vspace{.2in}
-\begin{figure}[H]
+\begin{figure}
         \caption{Distribution of treatment effects under rank invariance.}
@@
 
-\section{Derivations for Section \ref{sec:randchoice}}
+\section{ Derivations for Section \ref{sec:randchoice}}
 \label{append:randchoice}
@@
 
-\section{Testable Implications of the Exclusion Restriction}
+\section{ Testable Implications of the Exclusion Restriction}
 \label{append:exclusion}
@@
 \normalsize
-\linespread{1.25}
+\linespread{1.05}
 %Really force it to normal size and linespread
 \normalsize
-\linespread{1.25}
+\linespread{1.05}
 
@@
 
-\newpage
-
-\section{Causal Random Forest, HTE, and `mistakes'}
+\section{ Causal Random Forest, HTE, and `mistakes'}
 
@@
 
-\subsection{Example of a Causal Tree}
-
-\vspace{.3in}
-\begin{figure}[H]
-        \caption{Example Causal Tree}
-    \label{causal_tree1}
-    \begin{center}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/crf_apr.pdf}
-    \end{center}
-    \footnotesize 
-    This figure shows an example of one of the regression trees used to compute the causal forest estimates described in Section \ref{sec:RF}.
+% \subsection{Example of a Causal Tree}
+
+% \vspace{.3in}
+% \begin{figure}[H]
+%         \caption{Example Causal Tree}
+%     \label{causal_tree1}
+%     \begin{center}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/crf_apr.pdf}
+%     \end{center}
+%     \footnotesize 
+%     This figure shows an example of one of the regression trees used to compute the causal forest estimates described in Section \ref{sec:RF}.
 Each tree is constructed from a sequence of recursive binary partitions of the covariate space, with a splitting rule that is targeted to the causal quantity of interest, following the methodology of \cite{atheygrf}.
-    %This is one(it is chosen such that it minimizes the pruned cost, that is it is the tree with the smallest root-node impurity) of the honest causal trees in the random forest we use for the estimation of the heterogeneous treatment effect of the fee-forcing contract.
+%     %This is one(it is chosen such that it minimizes the pruned cost, that is it is the tree with the smallest root-node impurity) of the honest causal trees in the random forest we use for the estimation of the heterogeneous treatment effect of the fee-forcing contract.
 It is meant only as an example of how these trees look like.
 The forest was such that there are as many estimated treatment effects as there are clients.
-     %\footnotesize{ \textit{RScript: }  \texttt{grf.R}
-\end{figure}
-
-\newpage
+%      %\footnotesize{ \textit{RScript: }  \texttt{grf.R}
+% \end{figure}
+
 \subsection{Conditional ATE estimates}
 
-\vspace{.3in}
 \begin{figure}[H]
@@
   \caption{Cumulative Distribution Function of Conditional ATE Estimates}
-  \includegraphics[width=0.75\textwidth]{Figuras/cdf_CATE.pdf} 
+  \includegraphics[width=0.6\textwidth]{Figuras/cdf_CATE.pdf} 
     \label{fig:CATEsurvival}
@@
     \begin{center}
-    \begin{subfigure}{0.75\textwidth}
+    \begin{subfigure}{0.65\textwidth}
         \centering
@@
 
-\newpage
 \subsection{Targeting rule comparisons}
 
-\vspace{.3in}
-
-\begin{figure}[H]
+Figure \ref{targeting_rules} compares the in-sample performance of these targeting rules against a policy of universal forced commitment.
+The plot presents the estimated proportion of borrowers who benefit from a particular treatment assignment rule, along with associated 95\% confidence bands, where ``benefit'' is defined as having a CATE above a particular threshold.
+As above, we take the conditional average effects from the ``wide'' causal forest as ground truth for the purposes of this exercise.
+Because this is an in-sample exercise, the logistic and random forest classification rules have an unfair advantage: there is no adjustment for overfitting.
+In spite of this, their performance is unimpressive relative to a policy of universal forced commitment.
+The fraction of the whole sample incorrectly targeted when moving from universal forced commitment to targeting based on the narrow RF falls only from 9.78\% to 9.59\%.
+The logit targeting rule actually makes things marginally worse.
+
+\begin{figure}
     \caption{Targeting rules}
@@
 \end{figure}
-\vspace{.1in}
-
-Figure \ref{targeting_rules} compares the in-sample performance of these targeting rules against a policy of universal forced commitment.
-The plot presents the estimated proportion of borrowers who benefit from a particular treatment assignment rule, along with associated 95\% confidence bands, where ``benefit'' is defined as having a conditional average treatment effect above a particular threshold.
-As above, we take the conditional average effects from the ``wide'' causal forest as ground truth for the purposes of this exercise.
-Because this is an in-sample exercise, the logistic and random forest classification rules have an unfair advantage: there is no adjustment for overfitting.
-In spite of this, their performance is quite unimpressive relative to a policy of universal forced commitment.
-The fraction of the whole sample incorrectly targeted when moving from universal forced commitment to targeting based on the narrow RF falls only from 9.78\% to 9.59\%.
-The logit targeting rule actually makes things marginally worse.
 
@@
 \normalsize
-\linespread{1.25}
+\linespread{1.05}
 

### 2023-12-14 donde.tex
prepare for submission

@@
- \documentclass[oneside,11pt]{article}
+\documentclass[11pt, a4paper]{article}
 
@@
 \maketitle
-\thispagestyle{empty}
+\vspace{-0.75in}
+
 \begin{abstract}
-
 %Many firms provide commitment devices that restrict individuals' choice, but shroud this.
@@
 
-We use a novel three-armed RCT, including both forced and voluntary treatment arms, to provide a unique window into choice, heterogeneous treatment effects and paternalism in the context of pawnbroker lending.
+\small {We use a novel three-armed RCT, including both forced and voluntary treatment arms, to provide a unique window into choice, heterogeneous treatment effects and paternalism in the context of pawnbroker lending.
 Forcing borrowers into commitment contracts with a regular repayment structure decreases the financial cost of pawn loans by 22\% inclusive of fees, increases the likelihood of recovering their pawn by 15\%, and increases the likelihood of repeat business by 19\%.
-Leveraging the special features of our experimental design, we go on to point-identify the effects of commitment on both the treated and the untreated simultaneously, along with the average selection on gains.
+Leveraging the special features of our experimental design, we go on to point-identify the effects of commitment on both the choosers and the non-choosers simultaneously, along with the average selection on gains.
 We find large and significant effects of commitment even for borrowers who would not voluntarily choose it, and no evidence of selection on gains: borrowers who would freely choose commitment do not appear to benefit more than borrowers who would not.
-A detailed analysis of treatment effect heterogeneity suggests that the potential gains from targeting commitment based on observable characteristics are extremely small and that most borrowers stand to gain from a policy of universal forced commitment.
-%The justification for paternalistic commitment in this context appears to be over-optimism; 74\% of clients say they will certainly recover their pawn while in fact only 57\% do so.
+A detailed analysis of treatment effect heterogeneity suggests that the potential gains from targeting commitment based on observable characteristics are extremely small and that most borrowers stand to gain from a policy of universal forced commitment.} %The justification for paternalistic commitment in this context appears to be over-optimism; 74\% of clients say they will certainly recover their pawn while in fact only 57\% do so.
 
@@
 
-\vspace{.3in}
-
 \textbf{Keywords: } Private paternalism, choice, treatment on the untreated, heterogeneous treatment effects, commitment, overconfidence.
@@
 
-\newpage
+\vspace{3.75in}
 
@@
 
+\newpage
 \section{Introduction}
@@
 Pawn loans constitute one of the oldest and most prevalent forms of borrowing \citep{carter2012pawnshops}.
-Our partner lender, for example, made over 4 million loans to more than a million clients during the past three years.\footnote{For purposes of comparison, there were 2.3 million microfinance clients in Mexico in 2009 \citep{Pedroza:2010}.}
-The question of choice versus paternalism is particularly salient in this context, as choice mistakes could arise from borrowers' low education and the fact that they typically borrow for emergencies under significant stress.\footnote{There is a large literature showing that stress impairs cognitive function, e.g.
+Our partner lender, for example, made over 4 million loans to more than a million clients during the past three years.\footnote{For comparison, there were 2.3 million microfinance clients in Mexico in 2009 \citep{Pedroza:2010}.}
+The question of choice versus paternalism is particularly salient in this context, as choice mistakes could arise from borrowers' low education and the fact that they typically borrow for emergencies under significant stress.\footnote{A large literature shows  stress impairs cognitive function, e.g.
 \cite{StressReview}.}
@@
 Our experiment covers just under 5,000 pawnshop clients in 6 of our partner lender's Mexico City branches.
-Our control arm illustrates the costs of the status quo contract: fully \emph{44\%} of borrowers default, losing lose their pawn along with any payments made towards principal.\footnote{High pawn default rates are common, in the US they oscilate around 15\% (\url{https://tinyurl.com/yc2x5bjf}).} Our ``commitment choice'' arm gives borrowers the chance to opt into a structured repayment contract when taking a loan.
+Our control arm illustrates the costs of the status quo contract: fully \emph{44\%} of borrowers default, losing lose their pawn along with any payments made towards principal.\footnote{High pawn default rates are common, in the US they oscilate around 15\% (see \href{https://tinyurl.com/yc2x5bjf}{here}).} Our ``commitment choice'' arm gives borrowers the chance to opt into a structured repayment contract when taking a loan.
 The structured contract requires borrowers to make three monthly payments rather than one balloon payment at the end, with each monthly payment including the accrued interest at that time as well as a nominal fee of 2\% of that month's payment if the payment is delinquent.
@@
 In fact, they are one of the most prevalent forms of borrowing.
-There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues.\footnote{\url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.} Our partner pawn lender alone served more than 1 million clients in the last 3 years with more than 4 million contracts.
+There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion in yearly revenues.\footnote{See
+\href{https://tinyurl.com/ybm56dpe}{here}, \href{https://tinyurl.com/y9zdcgws}{here}, and \href{https://tinyurl.com/y59ptdam}{here}.}
+Our partner pawn lender alone served more than 1 million clients in the last 3 years with more than 4 million contracts.
 For comparison there were 2.3 million micro-finance clients across all lenders in Mexico in 2009 \citep{Pedroza:2010}.
@@
 
-\paragraph{Appraising and lending.} Lender P takes gold jewelry as collateral in exchange for a fraction of the value of the piece, in cash.
+\vspace{.2in}
+\noindent \textbf{Appraising and lending.} Lender P takes gold jewelry as collateral in exchange for a fraction of the value of the piece, in cash.
 No other collateral and no credit history checks are needed.
@@
 
-\paragraph{Contract.} Lender P had only one type of contract, henceforth the \textit{status quo} contract.
+\vspace{.2in}
+\noindent \textbf{Contract.} Lender P had only one type of contract, henceforth the \textit{status quo} contract.
 It stipulated that the interest rate was 7\% \textit{per month} compounded daily on the outstanding amount of the loan.
@@
 
-\paragraph{Borrowers.} The clients that pawned understood these terms well (as we verified in interviews).\footnote{87\% of clients report in our survey that they have pawned before.} These clients have little or no access to other types of loans and they value the convenience of pawn borrowing.
+\vspace{.2in}
+\noindent \textbf{Borrowers.} The clients that pawned understood these terms well (as we verified in interviews).\footnote{87\% of clients report in our survey that they have pawned before.} These clients have little or no access to other types of loans and they value the convenience of pawn borrowing.
 This population of pawn borrowers is economically vulnerable:  30\% of them could not pay either water, electricity \& gas or rent in the past 6 months; 89\% said they are pawning because of an emergency, and only 12\% stated it was to use in a ``non-urgent expense''.
@@
 
-\paragraph{Many borrowers lose their pawn.} Our context is also one with high borrower default: 43\% of clients lose their pawn in a time span of 230 days from the date of pawning.
+\vspace{.2in}
+\noindent \textbf{Many borrowers lose their pawn.} Our context is also one with high borrower default: 43\% of clients lose their pawn in a time span of 230 days from the date of pawning.
 One potential explanation for high default is that clients are really just knowingly selling their gold piece through a pawn contract on which they intend to default.
@@
 
-As a second measure of cost we calculate the Annual Percentage Rate (APR) in order to express the cost as a percentage of the loan, per year, inclusive of default costs.\footnote{Loan term takes into account the entire loan period, including extensions of the loan through refinancing.} The standard definition is given in the following formula:
+As a second measure of cost we calculate the Annual Percentage Rate (APR) in order to express the cost as a percentage of the loan, per year, inclusive of default costs.\footnote{Figures \ref{fc_hist}(a) and \ref{fc_hist}(b)  in the appendix display histograms for financial cost and APR.
+Loan term takes into account the entire loan period, including extensions of the loan through refinancing.} The standard definition is given in the following formula:
 
@@
 
-\vspace{.1in}
-
-Figure \ref{fc_hist}(a) plots a histogram of this financial cost in pesos for all loans in the experiment, stratified by whether we observed that they ended in default or recovery of the pawn.
-Figure \ref{fc_hist}(b) shows the analogous histogram for the APR.
-%defaulted (44\%), recovered their pawn (43\%), or whether they are censored in our data (13\%). 
-We see that borrowers who default incur higher costs; part of this is mechanical as losing their collateral is part of the cost.
-Most of the APR costs indeed come from clients who do not recover their pawn.
-%The second thing to note is that those that are not closed at the end of our sample period have already incurred substantial financial cost, even though they have not defaulted yet.
-
-%Of those who renew, 83\% lose the pawn.
-Figure \ref{fc_hist}(a) suggest that financial cost is significant, even for those that do recover their pawn.
-Panel (b) normalizes the cost by loan size.
-It shows that as a percentage of their pawn, most of the cost comes from clients that do not recover their pawn.
-For them the cost is between 140\% and 250\% of the loan value.
-%{The difference between panel (a) and (b) arises since clients who lose their pawn tend to be those that pledge cheaper pieces.}
-
 %We calculate an APR of 218\% on average for the control group.%\footnote{The Annual Percentage Rate (for pawn $j$) is calculated as the internal rate of return $i$ such that $\sum_t \frac{P_{jt}}{(1+i)^t} + \frac{\text{I}(Default \: Pawn_j) \times Pawn \: Value_j}{(1+i)^T} - Pawn \: Value_j = 0$, where $T$ is the date the pawn was lost, and $P_{jt} =P_{jt}^c+P_{jt}^f+P_{jt}^i $ is the sum of all payments.}
@@
 
+\vspace{.2in}
 \subsection{Treatment arms and randomization}
 
+\vspace{.2in}
 \noindent \textbf{The Commitment Contract.} For the purpose of the experiment we designed a new contract that is identical to the status quo contract except that, informed by the design of micro-lending contracts, it enhances the regularity and salience of payments as a way to encourage repayment \citep{morduch1999microfinance, bauer2012behavioral}.
@@
 
-%The existence of a choice arm allows us not only to measure if there is demand for such a contract, but who demands it, not only in demographic terms, but in terms of potential treatment effects.
-One may worry for instance that low sophistication from pawn-loans users could lead to the `wrong' people choosing the structured commitment contract.
-To examine this issue, we included an arm that assigns all individuals to the commitment contract so that we are able in essence to form three counterfactual outcomes; no commitment, commitment, and the chosen commitment.
-This design allows us to investigate the repercussions of choice not only for those who \textit{do} choose (as is the case in a standard LATE design), but also the implications of choice for those who \textit{do not} choose.
-This design is innovative and critical for our purposes, as it enables us to explore whether or not forcing people into a structured payment contract could be more beneficial than allowing choice for a significant fraction of them.
+\begin{figure}[htbp]    
+\begin{center}
+\includegraphics[width=0.9\textwidth]{Figuras/consort.pdf}
+  \end{center}
+ \caption{Experiment description}
+     \label{exp_description}
+%\textit{Do file: }  \texttt{ss\_att.do}
+\end{figure}
 
@@
 
-\paragraph{Timeline.} Figure \ref{exp_description} shows the experimental timeline along with the length of time for which we observe payments.
+\vspace{.2in}
+\noindent \textbf{Timeline.} Figure \ref{exp_description} shows the experimental timeline along with the length of time for which we observe payments.
 For loans made in the first week of the experiment, we observe up to 338 subsequent days of loan information; for loans made in the last week we observe up to 235 days.
@@
 
-\paragraph{Explanation.} Since we are interested in measuring the effect of different contract terms on client behavior, it is important that clients understand these terms.
+\vspace{.2in}
+\noindent \textbf{Explanation.} Since we are interested in measuring the effect of different contract terms on client behavior, it is important that clients understand these terms.
 To ensure this, we built two ``check-points'' as follows.
@@
 
-\paragraph{Administrative data.} The study exploits two types of data: administrative data from the lender, and a short survey that we implemented.
+\vspace{.2in}
+\noindent \textbf{Administrative data.} The study exploits two types of data: administrative data from the lender, and a short survey that we implemented.
 The administrative data contains a unique identifier for each client, an identifier for the piece she is pawning, and the transactions relating to that piece.
@@
 
-\paragraph{Survey data.} An additional team of enumerators stationed in each branch asked clients to complete a 5-minute survey \textit{before} going to the teller window to appraise their piece and before they learned which contracts would be available on that day.
+\vspace{.2in}
+\noindent \textbf{Survey data.} An additional team of enumerators stationed in each branch asked clients to complete a 5-minute survey \textit{before} going to the teller window to appraise their piece and before they learned which contracts would be available on that day.
 The survey was intentionally short to avoid discouraging the potential clients from pawning.
@@
 
-\paragraph{Attrition.} There are two main channels through which attrition could complicate the interpretation of our results.
+\vspace{.2in}
+\noindent \textbf{Attrition.} There are two main channels through which attrition could complicate the interpretation of our results.
 The first, and more serious, is the possibility that clients might change their pawning decisions in response to the treatment they encounter in a given branch on the day they enter the branch.
@@
 There is no difference at all between the Control and Forced Commitment arm in terms of the number of pawns per branch-day.
-Although we cannot reject equality across the three arms (p-value=0.21), the Choice arm appears to have a somewhat larger number of borrowers than the Control and Forced arms.\footnote{p-value=0.23 and 0.12 respectively.} This seems to be due to sampling variability.
+%Although we cannot reject equality across the three arms (p-value=0.21), the Choice arm appears to have a somewhat larger number of borrowers than the Control and Forced arms.\footnote{p-value=0.23 and 0.12 respectively.} This seems to be due to sampling variability.
 The differences across arms are smaller when we look at medians, or when we look at the number of borrowers pawning (some borrowers pawn more than one piece).
 Figure \ref{boxplot_attrition} shows that full distribution of loans per day is very similar across treatment arms.
-The only noticeable difference is that the choice arm has a few more positive outliers.\footnote{If we winzorize at the 90th percentile, the mean number of branch-day pawns identical across arms.}
-
-The bottom panel of Table \ref{attrition_table} shows balance in a more focused way, given that the surveys were conducted prior to the revelation of treatment status.
+The only noticeable difference is that the choice arm has a few more positive outliers.\footnote{If we winzorize at the 90th percentile, the mean number of branch-day pawns becomes identical across arms.}
+%The bottom panel of Table \ref{attrition_table} shows balance in a more focused way, given that the surveys were conducted prior to the revelation of treatment status.
 We find that in no arm did more than three percent of individuals who responded to the survey go on to refuse loans.
@@
 This is consistent with the findings of Table \ref{SS}.
+
+\begin{table}[!h]
+\caption{Summary statistics and Balance}
+\label{SS}
+\begin{center}
+\resizebox{0.65\textwidth}{!}{
+\scriptsize{\input{./Tables/SS.tex}}
+}
+\end{center}
+\scriptsize {This table has two panels.
+Panel A uses administrative data at the loan level, while Panel B uses survey data.
+Each row in this table corresponds to a regression, where the level of observation is the individual loan originated.
+The dependent variables of these regressions are displayed in the first column.
+Each dependent variable is regressed in a multivariate OLS regression against the experimental arms indicators (control, forced commitment, choice).
+The table reports the coefficients on each of these indicators, as well as the p-value an F-test of the null hypothesis of equality of the three coefficients.
+The admin data was a very limited set of pre-determined variables.
+The dependent variables in Panel A are the loan amount in pesos, and an indicator for whether the day of the loan origination was a weekday (as opposed to weekend).
+The dependent variables in Panel B from the survey (see the questions in Table \ref{baseline_survey}.
+Subjective value of the pawn (how much would the client be willing to sell it for (Q3), an indicator for having trouble paying bills in the last 6-months (Q28), present bias (constructed from questions Q10 and Q29 in the standard way as in \cite{Ashraf}), an indicator for whether they make expenses budget for the month ahead of time.
+The subjective probability of recovery was elicited a la Manski (from 0 to 100 what is the probability that you will recoup your pawn), pawned before is a dummy=1 if the client declares to have pawned before (although not necessarily with Lender $P$) age is in year, +High-school is a dummy that indicates if the client has completed high school.
+}
+%\textit{Do file: } \texttt{ss\_att.do}
+\end{table}
+
 % To test for this, we examine the number of loans given per branch-day, with specific attention to whether the Forced Commitment arm led to a lower number of borrowers per day.
@@
 Therefore it appears that the treatments have not induced any endogenous shifts in the composition of borrowers.
-A less critical form of attrition is differential refusal to answer the survey questions.
+
+% A less critical form of attrition is differential refusal to answer the survey questions.
 The survey was conducted before treatment status was revealed, and we observe loan outcomes regardless of whether the survey was conducted.
@@
 The bottom row of Table \ref{attrition_table} shows that the survey response rate is broadly similar across arms (about 78 percent).
+
 %We can also examine differences in the fraction of borrowers who do respond to the survey and then do not end up taking a loan subsequent to completing the survey, we find that the share is close to 100\% as is the fraction of those 97\% across arms (p-value=0.62).
@@
 
-\paragraph{Balance.} Table \ref{SS} presents summary statistics for the sample of actual borrowers across arms, showing that our randomization succeeded in achieving balance across the experimental arms.
+\vspace{.2in}
+\noindent \textbf{Balance.} Table \ref{SS} presents summary statistics for the sample of actual borrowers across arms, showing that our randomization succeeded in achieving balance across the experimental arms.
 Panel A uses administrative data for the universe of borrowers in each arm, and shows that loan balances and the days on the week on which individuals pawned are comparable across arms.
@@
 
-%Panel C repeats the exercise in Panel B, but now only for those borrowers answered the survey and then went on to take a loan.
-Since we have aready shown that the attrition rate of borrowers after completing the survey was very low (3\% on average) it is unsurprising that these two panels are similar.
-Overall, we find both the loan attributes and the survey attributes of borrowers to be similar across arms.
-The experiment appears to have been successful in generating a balanced sample for analysis.
-
-%Panel A describes variables from the administrative data.
-The average number of pawns per day per branch is 34.
-Only 42\% of clients recover their pawn.
-Even those that recover their pawn tend to pay it back at the last moment, with only 40\% paying before the 90th day.
-
 \section{Average Treatment Effects} \label{Experiment}
@@
 
-\paragraph{Specification.} Table \ref{main_impact_table} presents estimates and standard errors from a standard pooled experimental regression 
+\vspace{.2in}
+\noindent \textbf{Specification.} Table \ref{main_impact_table} presents estimates and standard errors from a standard pooled experimental regression 
 \begin{equation} \label{basic_reg}
@@
 
-\paragraph{Results.} The results are stark.
+\begin{table}
+\caption{Effects on Financial Cost}
+\label{main_impact_table}
+\begin{center}
+\resizebox{1.0\textwidth}{!}{
+\scriptsize{\input{./Tables/decomposition_main_te.tex}}
+}
+\end{center}
+\scriptsize{This table shows the treatment effects for our core pecuniary outcomes.
+Each column is a different regression for different outcomes on an indicator for the forced and choice arms, following specification in equation \ref{basic_reg}.
+Columns (1) \& (7) analyze our core financial cost measures, while the rest of the columns decompose these into finer components.
+A few borrowers take more than one loan on the first day they appear in an experimental branch.
+These are treated as different observations.
+Table \ref{multiple_loans} shows our results are similar when dealing with the multiplicity of loans per borrower.
+Each regression includes branch and day-of-week FE.
+Standard errors are clustered at the branch-day level.
+}
+
+%\textit{Do file: } \texttt{decomposition\_main\_te.do}
+\end{table}
+
+\vspace{.2in}
+\noindent \textbf{Results.} The results are stark.
 The Forced Commitment arm yields large and significant decreases in the cost of loans to clients, as measured either by financial cost or APR.
@@
 
-\paragraph{Intermediate outcomes.} To shed light on the mechanisms behind the ATEs discussed above, Table \ref{mechanisms} shows how commitment affects a number of intermediate outcomes.
+\vspace{.2in}
+\noindent \textbf{Intermediate outcomes.} To shed light on the mechanisms behind the ATEs discussed above, Table \ref{mechanisms} shows how commitment affects a number of intermediate outcomes.
 One can group the types of intermediate outcomes into two categories: measures of the speed of pawn recovery, and measures of the decision of when to default.
@@
 On the contrary, 7 percentage points fewer borrowers end up in this situation, compared to 12 percent in the status quo contract.
-Conditional on defaulting those assigned to the Forced commitment contract have paid 4.1\% less of their loan (col 7), and a 14 percent higher proportion of borrowers pay zero conditional on defaulting, an outcome analogous to ``selling their pawn'' (col 8).
+Conditional on defaulting those assigned to the Forced commitment contract have paid 4.1\% less of their loan (col 7), and a 14 percent higher proportion of borrowers pay zero conditional on defaulting, an outcome analogous to
+``selling their pawn'' (col 8).
 One interpretation of this bifurcation is that the Forced commitment contract forces borrowers to think earlier about whether they will indeed be able to eventually recover their pawn, and separates borrowers into those ``selling'' their pawn and those recovering it, reducing the share of undecided borrowers that end up paying interest and end up losing the pawn anyway.
@@
 
-\paragraph{Other costs.} We have shown that forcing borrowers to take the monthly payment contract significantly reduces their financial costs.
+\begin{landscape}
+
+\begin{table}
+\caption{Effects on intermediate outcomes}
+\label{mechanisms}
+\begin{center}
+
+\scriptsize{\input{./Tables/mechanism.tex}}
+
+\end{center}
+\scriptsize{This table explores treatment effects in ``intermediate variables''.
+Each column represents regression output for different dependent variables following equation (\ref{basic_reg}).
+Panel A focuses on variables related to the speed of payment.
+While Panel B focuses on variables related to default, and Panel C related to visits.
+% The outcome variables are as follows:  number of days elapsed between origination and first payment (col 1); percentage of the loan paid in the first payment (col 2); probability of recovery in the first visit (col 3); loan duration is the number of days the borrower took to payoff her loan for those that recover, the number of days until default for those that default, and the maximum number of days we observe them in the sample for those that have not recovered or defaulted (col 4); loan duration conditional on recovery; an indicator for paying a positive amount towards recovery but nonetheless losing the pawn (col 6); the percentage or the loan paid, conditional on defaulting --`wasted payments' (col 7).
+Column 8 uses the phrase `selling the pawn' for a dummy variable indicating the borrower did not pay any amount towards recovery and lost the pawn.
+Moreover, (col 9) shows that treatment effects are concentrated in the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery.
+The dependent variable in column 10 is the number of day-visits to the branch (measured by the existence of transactions that day associated with our particular pawn), while column 11 conditions on borrowers that lost the pawn.
+Each regression includes branch and day-of-week FE. Standard errors are clustered at the branch-day level.}
+%\textit{Do file: } \texttt{mechanisms.do}
+\end{table}
+\end{landscape}
+
+\noindent \textbf{Other costs.} We have shown that forcing borrowers to take the monthly payment contract significantly reduces their financial costs.
 Although the paper focuses on financial costs, we consider three additional costs here.
@@
 Our third extra cost considers this higher value.
-
-Table \ref{table_robustness_fc} shows results.
-Panel A reports financial cost in pesos, while Panel B shows APR.
-Columns (1) and (6) replicate our previous results for comparability.
-Columns (2) and (7) of Table \ref{table_robustness_fc} use the subjective value of the pawn reported by the borrower rather than its appraised value.
-Columns (3) and (8) adjust for self-reported transport costs per visit plus an entire day's wage, both multiplied by the number of visits that each individual made.\footnote{For clients who did not complete the individual survey, we adjust using the mean self-reported transport cost among respondents of the respective branch.} Columns (4) and (9) adjust to consider the liquidity cost.
-Finally, columns (5) and (10) include all three changes together.
-The main takeaway from the table is that results are quite robust to including a much expanded measure of costs.
-
-%Although adding a whole day's wage almost certainly exaggerates the travel costs associated with commitment contracts, we still find that forced commitment reduces both financial costs and APR.
-Columns (4) and (9) adjust for both travel costs and use the subjective rather than appraised value of the pawn.
-Finally, columns (5) and (10) remove saved interest payments from the calculation of the benefits.
-The rationale is that forcing borrowers to pay earlier reduces their liquidity, and they may need to borrow.
-We assume they borrow at the same interest rate.
-Thus considering other loans, they may not be paying less interest.
-The exercises in Table \ref{table_robustness_fc} show that results are quite robust to the inclusion and exclusion of components of benefits and costs.
-
-%Figure \label{fc_discount_rates} shows the effects of each of these adjustments on the estimate of financial cost and APR, and illustrates that even when we make all of these adjustment simultaneously the Forced arm generates benefits of 0.11 standard deviations, significant at the 95\% level.
-Forced commitment lowers financial costs even when we incorporate multiple subjective dimensions of the loan.
-
-\paragraph{Repeat Pawns.}
+Table \ref{table_robustness_fc} shows results are robust to all these changes.
+
+\vspace{.2in}
+\noindent \textbf{Repeat Pawns.}
 %Another way to push the analysis towards a consideration of borrower welfare is the conjecture that if clients exposed to the installment contract like it, they will be more likely to come back vis-a-vis those that got status quo contract.\footnote{\cite{Laibson2018} hypothesizes that consumers use ``experienced utility'' as a guide to make future purchases in this way.} This is indeed what we find in the data.
@@
 
-%Moreover, in the (endogenous) subsample of those that recover, in Column 6 we do find that they return with a different collateral, as they recover the collateral of the first loan more often.
-
-%clients assigned to the forced commitment arm were more likely to recover their pawn, allowing them to re-pawn the same item in the future.
-We can explore this possibility in a number of ways.
-First, we can (endogenously) split the sample according to whether the individual defaulted on the experimental loan; here we find that the increase in subsequent borrowing is restricted to those who repaid the first one.
-Next, we can examine whether the probability that participants take another loan using \emph{different} collateral from the first.
-While the difference is not statistically significant, we find that the Forced arm elevates the probability of re-pawning with new collateral.
-We can also separately examine the probability of taking a new loan after the contract period of the original experimental loan (column 5) or before it (column 6).
-Here we find that the increase in subsequent pawning comes \emph{later}, significantly increasing the time to the subsequent loan (column 7).
-All of this evidence suggests that the effect on subsequent demand is `real' and not an artifact of improved retention of the collateral, consistent with \cite{Alcohol}'s conjecture that demand for commitment increases with experience with it.
-However, it remains possible that the additional demand for subsequent pawning comes from the fact that forcing earlier payments effectively reduces the credit available during the contract, and thus that clients may pawn again to compensate for the smaller loan.
-We are skeptical about this interpretation for several reasons.
-%First, typically the emergencies that trigger a pawn are short lived (e.g.
-needing to go to the hospital), and it is unclear why clients in the frequent payment arm wait for several months to re-pawn -- there is no effect of the monthly payment contract on repeat pawning in the first 30 or 60 days of the contract, (see Figure \ref{reincidence_before} in Appendix).
-First,  there are many alternative lenders in this market, and if they did not like frequent payments why do they come back to Lender $P$ for another loan?
-Second, the fee itself is mostly symbolic (2\% of 1/3 of the value of the loan) and so it is likely that if there were real financial costs to making an intermediate payment it would simply be skipped and the fee incurred.
-We also implemented an exit survey which clients filled when recovering their piece.
-Unfortunately it had low response rate (7\%), and we take its results with a grain of salt; however in this survey 63\% of clients said they liked the frequent payment contract more than the status-quo one, and that it allowed them to avoid unnecessary expenses.
-Finally and most importantly, the treatment effects on re-pawning are entirely confined to the period after the original loan term and so there is no obvious link between intermediate liquidity and demand for new credit.
-%Third, we find larger effects of repeat buying for clients that experienced larger treatment effects, which the alternative explanation cannot explain.
-Fourth, the effect is present if we condition on clients that recovered their pawn (so it's not driven by pawn recovery).
-Finally, we were able to obtain observational data for all Lender $P$'s branches for the period January 2016 to May 2020, during which Lender $P$ expanded the new frequent payment contract.
-Using an instrumental variable strategy that exploits the expansion and availability of the frequent payment contract across branches, we show that being exposed to the frequent payment contract leads to an increase of 50 percentage points in the likelihood that in the subsequent pawn the frequent payment contract is chosen when both the status-quo one and the frequent payment contract are available (see \ref{appendix_b}).
-This choice cannot be explained by the need of another loan, since it is about \textit{which specific type} of loan the clients chooses conditional on getting one.
-
-%An additional empirical issue generated by repeat pawning is the question of how to handle the treatment status of those who take multiple loans within the experiment.
-38\% of borrowers take more than one loan within the study period, and 19\% are assigned multiple treatment statuses on their different loans.
-The issue of sequential endogenous treatments has been extensively studied in the context of school lotteries, where the convention is to use the treatment status from the first exposure \citep{cullen2006effect, abdulkadirouglu2011accountability}.\footnote{That context provides a particularly severe version of the endogenous re-entry problem because only the losers from initial lotteries re-enter subsequent ones.
-Our selection problem is less draconian, but still potentially relevant since we do find treatment effects on pace of repayment and of pawning again.}  While our main impact tables simply use the assigned treatment status for every loan, in Table \ref{multiple_loans} we provide two straightforward robustness checks for the influence of this problem.
-Columns 1-2 repeat the main analysis of financial cost and APR using the baseline approach from our main results, including dummies for the order of pawns for an individual, essentially making the identification within-order.
-Columns 3-4 drop all loans other than the first, and Columns 5-6 pursue the ITT strategy of always assigning the first treatment status to all subsequent pawns.
-The core treatment effects are robust to any of these ways of handling repeat pawning, and the effect on the APR is actually larger when we consider first loans only.
-Hence endogenous re-entry to the experiment does not appear to be driving our results.
-
-\paragraph{Censoring of Loan Completion}
+\begin{table}
+\caption{Effects on Repeat Pawning}
+\label{repeat_loans}
+\begin{center}
+\scriptsize{\input{./Tables/repeat_loans.tex}}
+\end{center}
+ \scriptsize{This table estimates the specification of equation \ref{basic_reg} but at the level of the borrower (not the loan). Each column represents a regression with a different outcome variable.
+ % In column 1, the dependent variable indicates, for each borrower in the experiment, whether he/she pawned again after the first loan in the experiment (up to the end period of our data set 338 days after the experiment began).
+Column 2 is analogous, but only pawning after 90 days of the first loan is considered.
+Column 3 instead considers pawning before 90 days.
+Column 4 is analogous to column 1 but focuses on the pawning of a gold piece that is different from the one in the first experimental loan.
+Column 5 is analogous to column 1, but conditioning on the sample that recovered the first loan.
+ Each regression includes branch and day-of-week FE. Standard errors are clustered at the branch-day level.}
+%\textit{Do file: } \texttt{repeat\_loans.do}
+\end{table}
+
+\vspace{.2in}
+\noindent \textbf{Censoring of Loan Completion.}
 The window of time during which we were able to observe borrower behavior was limited in each branch, meaning that there were loans that we do not see completed (particularly those pawns that were rolled over for one or two further 90-day spells).
@@
 So the question remains: do the 89\% who do not choose commitment know something about their personal situations that we as researchers do not, or are most people in the choice arm making a costly financial mistake?
-In this section we present of econometric exercises that sheds light on this question, leveraging unique features of our experimental design. 
+In this section we present a series of econometric exercises that sheds light on this question, leveraging unique features of our experimental design. 
 Among other results, we show that commitment would lower average financial costs even for the subset of borrowers who choose \emph{not} to commit voluntarily.
@@
 Figure \ref{tot_tut_graph} provides graphical intuition for our identification approach. % derivations appear in \ref{append:randchoice}
+
+\begin{figure}
+    \begin{center}
+        \centering
+        \includegraphics[width=1.0\textwidth]{Figuras/tot_tut_intuition.png}
+    \end{center}
+ \caption{The Controlled Choice Design.}
+ \scriptsize{This figure provides graphical intuition for the way in which the controlled choice design from Section point identifies both the treatment on the treated (TOT) and treatment on the untreated (TUT) effects, as discussed in Section \ref{sec:randchoice} and \ref{append:randchoice}.
+    The gray shaded regions denote borrowers with a commitment contract; the white shaded regions denote borrowers with a status quo contract.
+    A comparison of means across control and forcing arms identifies the ATE of forcing  commitment.
+    The TOT and TUT effects of commitment are identified as follows.
+    In the choice arm, anyone with a commitment contract is a chooser; in the control and forcing arms, we do not know who is a chooser and who is not.
+    Because borrowers are randomly assigned to experimental treatment arms, however, the share of choosers will be the same, on average, across experimental arms.
+    This is depicted using dashed vertical lines in the control and forcing arms.
+    This overall share of choosers and non-choosers is point identified from the choice arm.
+    Now, the difference of mean outcomes across the choice and control arms gives the intent-to-treat effect of offering choice.
+    Under the exclusion restriction that moving non-choosers between the choice and forcing arms does not change their outcomes, this comparison ``nets out'' the non-choosers.
+    Hence, the ITT of offering choice equals the TOT multiplied by the share of choosers. 
+    Similarly, under the exclusion restriction that moving choosers between the choice and forcing arm does not affect their outcomes, the difference of means across the forcing and choice arms ``nets out'' the choosers and hence equals the TUT multiplied by the share of non-choosers.}
+    \label{tot_tut_graph}
+     %\textit{Do file: }  \texttt{tot\_tut\_graph.do}
+\end{figure}
 
@@
 
-\paragraph{TOT and TUT results.} Table \ref{tot_tut} calculates the causal quantities described above--TOT, TUT, ASG, ASB, and ASL--for our experimental data, along with robust standard errors for each.
+\begin{table}[H]
+\caption{Treatment on the Treated (TOT), Treatment on the Untreated (TUT), Selection-on-gains (TOT - TUT), Average Selection Bias (ASB), and Average Selection Bias, calculated using the results from Section \ref{sec:randchoice}.}
+\label{tot_tut}
+\begin{center}
+\scriptsize{\input{./Tables/tot_tut.tex}}
+\end{center}
+\scriptsize{This table presents results computed using the derivations from Section \ref{sec:randchoice} and \ref{append:randchoice}.
+The APR and financial cost outcomes have been multiplied by $-1$ so that a positive causal effect \emph{benefits} the borrower in each of the four columns.
+See Appendix \ref{subsec:inference} for more details on how we compute standard errors for the middle panel.
+The bottom panel present p-values for a number of null hypothesis tests of treatment effect heterogeneity. }
+%\textit{Do file: } \texttt{tot\_tut.do}
+\end{table}
+
+\vspace{.2in}
+\noindent \textbf{TOT and TUT results.} Table \ref{tot_tut} calculates the causal quantities described above--TOT, TUT, ASG, ASB, and ASL--for our experimental data, along with robust standard errors for each.
 For purposes of comparison, the table also presents the ATE results from Section \ref{Experiment} above (row 1),\footnote{Coefficients are not exactly the same since Table 4 includes branch and day-of-week FE.} along with the corresponding average potential outcomes $\mathbbm{E}[Y_0]$ and $\mathbbm{E}[Y_1]$ (rows 4--5).
@@
 
-\paragraph{Learning.} A first explanation involves learning.
+\vspace{.2in}
+\noindent \textbf{Learning.} A first explanation involves learning.
 Our experiment introduced a new contract into an environment that had not previously featured commitment; perhaps clients required experience to understand its benefits.
@@
 
-\paragraph{Time discounting.} Discounting is a second potential explanation for our results.
+\vspace{.2in}
+\noindent \textbf{Time discounting.} Discounting is a second potential explanation for our results.
 Highly impatient individuals might rationally choose the \emph{status quo} contract, despite the benefits that commitment yields returns, since monthly payments are front-loaded while pawn recovery is back-loaded, even if by only a few days.
@@
 
-\paragraph{Present bias.} If the benefits of commitment among non-choosers cannot be explained by standard models of rational choice, the canonical behavioral story would center on time inconsistency.
+\vspace{.2in}
+\noindent \textbf{Present bias.} If the benefits of commitment among non-choosers cannot be explained by standard models of rational choice, the canonical behavioral story would center on time inconsistency.
 While commitment is useful to anyone with hyperbolic time preferences, only those who are sophisticated--i.e.\ aware that they are hyperbolic discounters--will demand it.
@@
 
-%\todo[inline]{There are two exercises, and we'll do each one in the same way: present bias and sure confidence.
-In each case, there's a binary indicator that creates two groups.
-We want to know if this grouping can ``explain'' the positive TUT.
-At minimum, should see that effect is concentrated on those with the indicator equal to one.
-Never totally convincing since there could be an unobserved characteristic that is correlated with our indicator variable.
-If we had a clean hyperbolicity story, we'd have four strata: rational, time inconsistent and naive, time inconsistent and sophisticated, and a fourth group that chooses commitment despite being time consistent.
-If time inconsistency is the whole story, the negative TUT should be entirely concentrated on the naive types.
-In other words, they should have a large positive TUT but everyone else should but everyone else should have something close to zero or negative.
-In terms of decomposing the TUT, we're already restricting attention to people who would not choose.
-So when we're looking at the TUT we really only have two of these strata: rational types who are not hyperbolic and don't choose commitment, and types who are hyperbolic and don't choose commitment (naives).
-So $C=0,X=1$ is naive and $C=0,X=0$ is rational.
-Should find positive effect for $C=0,X=1$ and zero or negative for $C=0,X=0$.
-To be clear: the point is that we assume by choosing or not choosing commitment, you reveal whether you are sophisticated or not, given that we know your $X$.
-First thing we could ask is, among non-choosers how many are ``rational'' versus how many are naive.
-These are the two probabilities in Eq 12.
-Second compare the treatment effects.
-Can do the same thing for sure confidence with a slight caveat that it's harder to use the language ``naive'' or ``rational'' here, but we can still think about it in a similar kind of way as long as we're careful with the language.}
-
-\paragraph{Sure confidence.} While 72\% of survey respondents believe they have a 100\% chance of recovering their pawn, in reality only 43\% will go on to do so.  
+\begin{figure}
+    \begin{center}
+        \centering
+        \includegraphics[width=0.7\textwidth]{Figuras/tut_beh_partition.pdf} 
+    \end{center}
+     \scriptsize  
+\caption{Heterogeneity of the TUT by behavioral variables.}
+\scriptsize{Each panel in this figure shows how the estimated treatment on the untreated (TUT) effect varies with a binary survey variable $X_i$.
+In the left panel (P.B.), $X_i = 1$ if borrower $i$ is ``present-biased'' based on her responses to the time preference questions from our survey.
+In the right panel (Sure-confidence) $X_i = 1$ if  borrower $i$ reported that she was certain to recover her pawn, zero otherwise.
+}
+
+    \label{tut_beh_partition}
+      %\footnotesize{ \textit{Do file: }  \texttt{partition_tut.do}
+
+\end{figure}
+
+\vspace{.2in}
+\noindent \textbf{Sure confidence.} While 72\% of survey respondents believe they have a 100\% chance of recovering their pawn, in reality only 43\% will go on to do so.  
 This suggests a borrower pool characterized by over-optimism.
@@
 In broad strokes, these functions combine a large number of regression trees that recursively partition the covariate space to estimate conditional average effects.
-Figure \ref{causal_tree1} illustrates the partition that emerges from one of the trees in our causal forest implementation.
+% Figure \ref{causal_tree1} illustrates the partition that emerges from one of the trees in our causal forest implementation.
 The trees are ``honest'' in that observations used to determine the optimal partition are not used to estimate effects, and vice-versa.
@@
 
-\paragraph{Treatment effect distributions.} Figure \ref{heterogeneous_effects} plots densities of the estimated conditional ATE, TOT, and TUT effects from the generalized random forest models described above.
+\vspace{.2in}
+\noindent \textbf{Treatment effect distributions.} Figure \ref{heterogeneous_effects} plots densities of the estimated conditional ATE, TOT, and TUT effects from the generalized random forest models described above.
 In each case, the outcome variable is APR benefit, i.e.\ the reduction in APR from a commitment contract.
@@
 
-\paragraph{``Mistake'' tresholds.} Under the assumption that our instrumental forest estimates capture the main sources of treatment effect heterogeneity, we can use them to assess whether particular borrowers in the choice arm made ``mistakes'' in their decision to accept or refuse the commitment contract, in terms of predicted financial costs of the loan.
+\begin{figure}
+
+    \begin{center}
+     \begin{subfigure}{0.32\textwidth}
+       \centering
+      \includegraphics[width=\textwidth]{Figuras/he_dist_tau_hat_tot.pdf}
+          \caption{ToT}
+    \end{subfigure}
+    \begin{subfigure}{0.32\textwidth}
+       \centering
+      \includegraphics[width=\textwidth]{Figuras/he_dist_tau_hat_tut.pdf}
+          \caption{TuT}
+    \end{subfigure} 
+       \begin{subfigure}{.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/he_dist_tau_hat_eff.pdf}
+        \caption{ATE}
+    \end{subfigure} 
+    \end{center}
+    \caption{Heterogeneous Treatment Effects.}
+    \label{heterogeneous_effects}    
+  %\footnotesize{ } \textit{Do file: }  \texttt{cate_dist.do}
+\end{figure}
+
+\vspace{.2in}
+\noindent \textbf{``Mistake'' tresholds.} Under the assumption that our instrumental forest estimates capture the main sources of treatment effect heterogeneity, we can use them to assess whether particular borrowers in the choice arm made ``mistakes'' in their decision to accept or refuse the commitment contract, in terms of predicted financial costs of the loan.
 To do this we use the same information that is depicted in Figure \ref{heterogeneous_effects}, but present it in a different way.
@@
 
-%As we increase the threshold on the size of the mistake necessary to be classified as having made the wrong choice, by definition the share of mistakes in both groups falls.
-
-%Among choosers, only 18\% would have had superior outcomes had they not complied, whereas among non-choosers almost 80\% made a mistake according to this definition.
-Because this arm is comprised of 89\% non-choosers, the overall rate of mistake in the arm was around 68\%.
-
-%benefit is the case that forcing commitment generates large benefits on average, but it is also generating benefits for almost 90\% of the forced population.
-
-%\todo[inline]{ 
-%Can read this from red curve (and error bars) in Figure \ref{choose_wrong}, simply $F(-x)$ for the conditional TOT.
-Comment on results.
-Relatively few negative conditional TOT estimates: around 20\% with wide confidence bounds.
-Again say APR threshold of 25\%.
-Then say something like 8\% to 27\% \hl{???} mistakes.
-%Blue curve: combine to understand mistakes overall across choosers and non-choosers.
-Weighted average of red (TOT/chooser) and green (TUT/non-chooser) with weights corresponding to shares of each type.
-Very similar to green curve since 89\% are non-choosers and we estimate that relatively few choosers had a negative conditional average treatment effect.}
-
-%These impacts allow us to think about whether individuals made ``mistakes'' in their choices.  
-%Specifically, for each client in the choice arm we want to know how much cost savings would she have gained had she chosen the opposite contract. 
-%We do this in two steps.  
-%First, we use  \cite{atheygrf}'s generalized random forests methodology to estimate the impact of the forced commitment arm relative to the control (forced status quo) at the individual level.  
-%The method generates a partition of the space of characteristics $X$, where each element of the partition is a leaf, and each leaf contains treatment and control clients with similar characteristics $x \in X$ which are used to calculate unbiased treatment effects for that leaf.
-%The optimal partition is that which minimizes expected mean squared error of treatment effects predictions out-of-sample. 
-%The tree is ``honest'' in that uses one sub-sample to build the trees that make up the random forest and another one to estimate treatment effects within those trees.
-%\cite{atheygrf} show that their treatment effects are asymptotically normal, which allows us to construct confidence intervals for our treatment estimate in each leaf. 
-%This method gives us the average causal effect on financing cost of getting the forced commitment contract instead of the status quo contract for a client $i$ with characteristics $x_i$; call it $TE^{F}_{i}(x_i)$.\footnote{Figure \ref{causal_tree1} and ???
-provide an illustration of the splits (leaves) that emerge from our implementation of the RF.
-\todo[inline]{I think we should list in a footnote which are the `wide' variables we are using.}}
-
-%\paragraph{Personalized benefit results.} Using the test provided by \cite{chernozhukov2018generic}, we reject the null of homogeneity in treatment effects and so begin our analysis of heterogeneity confident that it exists.
-Figure \ref{heterogeneous_effects} illustrates the substantial impact of the forced commitment arm on APR, financial cost and other outcomes.
-More than 90\% of the individuals have APR saving effects, and even in the upper bound confidence interval more than half of individuals benefit.
-
-%\paragraph{Estimates of financial cost `mistakes'.} In a second step we predict treatment effects for clients \textit{in the Choice arm} using the partition into leaves and the treatment effect from step 1, that is client $j$ is imputed the treatment effect of the leaf corresponding to her characteristics $x_j$.
-We call this counterfactual treatment effect $\widehat{TE}^{F}_{j}(x_j)$.
-This is precisely the counterfactual we wanted, because it lets us relate observed individual choices with estimated individual-level treatment effects.\footnote{This extrapolation of the treatment effects assumes that choice itself --conditional on a given contract-- does not affect behavior (note the evidence in the prior section suggesting this is the case).
-Although the extrapolation is to another population, by randomization it is a statistically identical population with common support.} Armed with this, we say that a client made a ``mistake'' if either she chose the status quo contract and her $\widehat{TE}^{F}_{i}$ is negative (i.e.
-more cost saving from the Forced contract), or if she chose the Commitment contract and $\widehat{TE}^{F}_{i}$ is positive, (i.e.
-financial costs are larger for the Commitment contract).
-When a client made a choice mistake, we say that its money-metric values is the absolute value of $|\widehat{TE}^{F}_{i}|$.
-
-%Using the forcing arms and extrapolating to the choice arms.
-%Then, we predict these treatment effects for everybody in the choice arm using characteristics $x_i$.
-Let $\widehat{TE}^{fee}_{i}$ be the predicted financial cost savings for person $i$ of choosing the Forced Commitment contract rather than the status quo one, divided by the size of her loan (i.e.
-the negative value of the predicted treatment effect on financial cost for person $i$).
-$\widehat{TE}^{sq}_{i}$ is the analogous for the status quo contract.
-We define the choice of person $i$ to be a ``mistake'' if
-
-%\begin{equation}
-% \{ i \; \text{chose} \; sq \; \text{and} \; \;  \widehat{TE}^{fee}_{i}>\widehat{TE}^{sq}_{i} + z \} \; \text{or} \; \{ i \; \text{chose} \; fee \; \text{and} \; \;  \widehat{TE}^{fee}_{i}<\widehat{TE}^{sq}_{i} - z \}
-%\end{equation}
-
-%Since the prediction of the treatment effect is an estimate and has noise, we do two things.
-First, we normalize $\widehat{TE}^{F}_{i}$ by the value of the loan of person $i$ and introduce a threshold parameter $z$ and say that a choice is a ``mistake'' if the alternative contract would generate greater than $z$ in savings.
-We vary this threshold from 0\% to 15\% of the value of the loan.
-Second, we take into account uncertainty in estimation of treatment effects and report results using the extremes of the 95\% confidence interval bounds for $\widehat{TE}^{F}_{i}$.
-
-%Figure \ref{choose_wrong}(a) plots on the Y axis the fraction of clients that made a choice ``mistake'' and on the X axis the threshold $z$.
-When $z=0$, we calculate that about 82\% of clients in the Choice arm chose contracts that induced \textit{higher} financial cost.
-Most mistakes are failures to choose the fee-commitment contract ({97}\%), while only {4}\% of those who chose the fee-commitment contract would have been better in the status-quo one.
-The average mistake in pesos is \$250.
-%(90\% confidence interval [140,390]).
-
-%However, the fraction of non-choosers making a mistake remains almost 20\% even at the highest threshold used (\$80 pesos), and panel b shows the \textcolor{red}{Complete this when understand figure}.
-Panel C conducts a related but distinct exercise, showing the fraction of the entire control sample who would do better if assigned to the Forced arm; using the smallest threshold this fraction is over 95\%, showing that in this context there is an almost across-the board welfare benefit arising from this arm.
-Since the only potential financial cost of the forced arm arises from individuals who would be induced to partially repay but then default anyways, this result suggests that very few such borrowers exist.
-
-%Panel C of this figure replicates this exercise for the forced commitment arm, with the difference being that the relevant treatment effect to match is now the ATE of the forced commitment arm.
-This allows us to identify the winners and losers from paternalism in a nuanced manner, since members of groups with CATEs$<$0 are hurt and everyone else is helped.
-Because the ATE$>$TUT, this exercise results in an even larger fraction of individuals benefiting from commitment; here we find that fully 91\% of individuals are better off being forced into commitment than staying in the control.
-.
+\begin{figure}[H]
+\begin{center}
+        \centering
+        \includegraphics[width=0.6\textwidth]{Figuras/line_cw_apr_tot_tut.pdf}
+
+ \end{center}       
+ \caption{``Mistakes'' in the choice arm.}
+
+ \scriptsize{This figure presents conditional average TUT and TOT effects for the APR outcome from Figure \ref{heterogeneous_effects} in an alternative manner, to consider the fraction of borrowers in the choice arm who made ``mistakes'' in their decision to accept or refuse the commitment contract.
+A ``mistake'' for a non-chooser is defined as a positive conditional TUT effect that significantly exceeds a specified threshold APR value.
+ The green curve equals $[1 - F_{\text{TUT}}(\delta)]\times 100\%$, where $F_{\text{TUT}}$ is the CDF corresponding to density of conditional TUT effects from Figure \ref{heterogeneous_effects}, computed using the instrumental forest approach from \cite{atheygrf}.
+Evaluated at any positive value on the horizontal axis, it gives the fraction of non-choosers in the choice arm who made a ``mistake'' by not choosing commitment.
+The green shaded region gives associated 95\% pointwise confidence bands.
+Analogously, a ``mistake'' for a chooser is defined as a negative conditional TOT effect that exceeds a specified threshold APR value.
+The red curve equals $F_{\text{TOT}}(-\delta)$ where $F_{\text{TOT}}$ is the CDF corresponding to the density of conditional TOT effects from Figure \ref{heterogeneous_effects}.
+The red shaded region gives associated 95\% pointwise confidence bands.
+For both the red and green curves, we define the APR threshold so that larger mistakes are to the \emph{right} of smaller mistakes.
+This allows us to construct the overall fraction of mistakes in the choice arm, the blue curve, as a weighted average of the green and red curves.
+The weights equal the share of choosers and non-choosers in the choice arm.}
+    \label{choose_wrong}
+\end{figure}
 
@@
 First, it will in general not be possible to use the numerous subjective and unverifiable questions we asked in the baseline survey as inputs to the rule because the answers to these questions can be manipulated by the clients, and would likely change when they become incentivized.
-This leaves us with only a few objective covariates that could be used to target: age, gender, HS education or above, desired loan size, and whether that individual has ever pawned before.
+This leaves us with only a few objective covariates that could be used to target: age, gender, high school education or above, desired loan size, and whether that individual has ever pawned before.
 We call these the ``narrow'' covariate set below, to contrast with the full set of survey variables, which we call the ``wide'' covariate set.
-Secondly, it will not be attractive for a commercial firm to ask individuals whether they want to voluntarily accept commitment and then to force upon those who say no against their will.
+Secondly, it will not be attractive for a commercial firm to ask individuals whether they want to voluntarily accept commitment, only to then force it upon those who say no.
 So the choice variable itself cannot be used to target other than in a voluntary program.
@@
 
-\paragraph{Narrow inputs targeting.} To consider targeting effectiveness we must begin from an individual-specific ground truth, which we take from our estimated conditional average treatment effects (CATEs) $\widehat{\text{ATE}}(X_i)$ from the causal forest described in Section \ref{sec:RF},  which used the ``wide'' set of covariates (wide RF).% and data for all borrowers who replied to at least part of the intake survey.
+\vspace{.2in}
+\noindent \textbf{Narrow inputs targeting.} To consider targeting effectiveness we must begin from an individual-specific ground truth, which we take from our estimated conditional average treatment effects (CATEs) $\widehat{\text{ATE}}(X_i)$ from the causal forest described in Section \ref{sec:RF},  which used the ``wide'' set of covariates (wide RF).% and data for all borrowers who replied to at least part of the intake survey.
 We then analyze how well we can predict the losers from paternalism using the ``narrow'' set of non-manipulable covariates listed above (narrow RF) for the same subset of borrowers.
@@
 
-\paragraph{Targeting assessment.}
-
-To more directly investigate our ability to target commitment, we use two different methods to predict who should be assigned to the commitment arm.
+\vspace{.2in}
+\noindent \textbf{Targeting assessment.} To more directly investigate our ability to target commitment, we use two different methods to predict who should be assigned to the commitment arm.
 In each, we estimate a classification model using the ``narrow'' set of covariates to predict whether the CATE estimated from the wide random forest model (using all available covariates) is positive.
@@
 \begin{center}
-\resizebox{0.95\textwidth}{!}{
-\small{\input{./Tables/hit_miss_rule.tex}}
-}
+
+\scriptsize{\input{./Tables/hit_miss_rule.tex}}
+
 \end{center}
-\scriptsize This table reports error rates for six different rules for allocating individuals to commitment.
+\scriptsize{This table reports error rates for six different rules for allocating individuals to commitment.
 The first row allocates all borrowers to control.
@@
 The sixth row gives the percentage of miss-classification that would follow from the observed choice.
-%assigns the commitment contract to all borrowers with a positive conditional ATE estimate from the ``narrow'' RF.
-The fifth row uses a logistic regression to estimate the probability that a given borrower has a positive conditional ATE, assigning commitment to those with an estimated \hl{probability greater than 0.5}.
-
+}
 \end{table}
 
-\vspace{.3in}
-
-%\begin{table}[H]
-%\caption{Overconfidence: Take-up and Treatment Effects}
-%\label{oc_reg}
-%\begin{center}
-%\scriptsize{\input{./Tables/oc_reg.tex}}
-%\end{center}
-% \footnotesize This table shows the parameter estimates of $y_i = \alpha + \beta \: OC_i + Z_i'\gamma + \epsilon_i$, where $OC_i:=\mathbbm{1}(P^s_i-\widehat{P_i(X_i)}>0)$ is an indicator for the subjective probability of recovery being larger than the predicted one.
-In columns 1-4 $y_i$ is a dummy for whether the client $i$ chose to have the commitment contract in the respective choice arm, and in columns 5 and 6 $y_i$ is the heterogeneous treatment effect for financial cost (in pesos) estimated by comparing the Forced Commitment vs status quo arms in Section \ref{TE_fee-forcing}.
-Columns 1 and 3 are estimated for the promise-choice arm, while columns 2 and 4 are estimated for the Commitment Choice arm.
-The low number of observations results from  our use of  covariates for $\widehat{P(x)}$ and in $Z$ in the regression, given that some of them are missing.
-%\textit{Do file: } \texttt{oc.do}
-%\end{table}
-
-%\begin{table}[H]
-%\caption{Overconfidence: Take-up and Treatment Effects}
-%\label{oc_reg}
-%\begin{center}
-%\scriptsize{\input{./Tables/oc_reg_dec.tex}}
-%\end{center}
-% \footnotesize This table shows the parameter estimates of $y_i = \alpha + \beta \: OC_i + Z_i'\gamma + \epsilon_i$, where $OC_i:=\mathbbm{1}(P^s_i-\widehat{P_i(X_i)}>0)$ is an indicator for the subjective probability of recovery being larger than the predicted one.
-In columns 1-4 $y_i$ is a dummy for whether the client $i$ chose to have the commitment contract in the respective choice arm, and in columns 5 and 6 $y_i$ is the heterogeneous treatment effect for financial cost (in pesos) estimated by comparing the Forced Commitment vs status quo arms in Section \ref{TE_fee-forcing}.
-Columns 1 and 3 are estimated for the promise-choice arm, while columns 2 and 4 are estimated for the Commitment Choice arm.
-The low number of observations results from  our use of  covariates for $\widehat{P(x)}$ and in $Z$ in the regression, given that some of them are missing.
-%\textit{Do file: } \texttt{oc.do}
-%\end{table}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\newpage
-\section{Figures}
-
-\vspace{.2in}
-\begin{figure}[H]
-     \caption{Financial cost}
-    \label{fc_hist}
-    \begin{center}
-    \begin{subfigure}{.45\textwidth}
-      \caption{In pesos MXN}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_fc.pdf}
-    \end{subfigure}
-     \begin{subfigure}{0.45\textwidth}
-    \caption{Effective APR}
-       \centering
-      \includegraphics[width=\textwidth]{Figuras/hist_apr.pdf}
-    \end{subfigure}
-    \end{center}
-         \scriptsize
-         Panel (a) presents a histogram of financial cost (defined as in Section \ref{costs}) for the control group.
-The figure plots separately the financial cost separately for borrowers who lose the pawn (blue) and those that recover it (transparent).
-Panel (b) is analogous but displays the APR.
-%Given that the loan lasts close to 90 days, bringing payments to present value makes little difference.
-
-      %\footnotesize{ } \textit{Do file: }  \texttt{hist\_fc.do}
-\end{figure}
-
-\begin{figure}[H]
-     \caption{Experiment description}
-    \label{exp_description}
-\begin{center}
-\begin{subfigure}{\textwidth}
-        \includegraphics[width=\textwidth]{Figuras/consort.pdf}
-    \end{subfigure}
-  \end{center}
-    \scriptsize
-
-%\textit{Do file: }  \texttt{ss\_att.do}
-\end{figure}
-
-\cleardoublepage
-
-\begin{comment}
-
-\begin{figure}[H]
-     \caption{TOT \& TUT as LATE}
-    \label{tot_tut_graph}
-    \begin{center}
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/tot_tut_apr.eps}
-    \end{subfigure}
-    \end{center}
-    \scriptsize
-   \hl{REPLACE THIS ONE WITH THE ONE IN THE PRESENTATION}
-     %\textit{Do file: }  \texttt{tot\_tut\_graph.do}
-\end{figure}
-\end{comment}
-
-\begin{figure}[H]
-\caption{The Controlled Choice Design}
-    \label{tot_tut_graph}
-    \begin{center}
-        \centering
-        \includegraphics[width=1.0\textwidth]{Figuras/tot_tut_intuition.png}
-    \end{center}
-    \scriptsize
-    This figure provides graphical intuition for the way in which the controlled choice design from Section point identifies both the treatment on the treated (TOT) and treatment on the untreated (TUT) effects, as discussed in Section \ref{sec:randchoice} and \ref{append:randchoice}.
-    The gray shaded regions denote borrowers with a commitment contract; the white shaded regions denote borrowers with a status quo contract.
-    A comparison of means across control and forcing arms identifies the ATE of forcing  commitment.
-    The TOT and TUT effects of commitment are identified as follows.
-    In the choice arm, anyone with a commitment contract is a chooser; in the control and forcing arms, we do not know who is a chooser and who is not.
-    Because borrowers are randomly assigned to experimental treatment arms, however, the share of choosers will be the same, on average, across experimental arms.
-    This is depicted using dashed vertical lines in the control and forcing arms.
-    This overall share of choosers and non-choosers is point identified from the choice arm.
-    Now, the difference of mean outcomes across the choice and control arms gives the intent-to-treat effect of offering choice.
-    Under the exclusion restriction that moving non-choosers between the choice and forcing arms does not change their outcomes, this comparison ``nets out'' the non-choosers.
-    Hence, the ITT of offering choice equals the TOT multiplied by the share of choosers. 
-    Similarly, under the exclusion restriction that moving choosers between the choice and forcing arm does not affect their outcomes, the difference of means across the forcing and choice arms ``nets out'' the choosers and hence equals the TUT multiplied by the share of non-choosers.
-
-     %\textit{Do file: }  \texttt{tot\_tut\_graph.do}
-\end{figure}
-
-\begin{figure}[H]
-    \caption{Heterogeneity of the TUT by behavioral variables}
-    \label{tut_beh_partition}
-    \begin{center}
-        \centering
-        \includegraphics[width=0.75\textwidth]{Figuras/tut_beh_partition.pdf} 
-    \end{center}
-     \scriptsize  Each panel in this figure shows how the estimated treatment on the untreated (TUT) effect varies with a binary survey variable $X_i$.
-In the left panel (P.B.), $X_i = 1$ if borrower $i$ is ``present-biased'' based on her responses to the time preference questions from our survey.
-In the right panel (Sure-confidence) $X_i = 1$ if  borrower $i$ reported that she was certain to recover her pawn, zero otherwise.
-Each panel depicts three estimates and associated 95\% confidence bands: the overall TUT (blue), the TUT for borrowers with $X = 1$ (green), and the TUT for borrowers with $X = 0$ (red).
-By the law of iterated expectations, the overall TUT in each panel must lie between the group-specific TUTs.
-The overall TUT is slightly different in each panel, because some borrowers only completed part of the survey.
-In each panel, we present results for the full set of borrowers who answered the survey question or questions needed to determine $X_i$.
-From the left panel, we see that TUT does not appear to be higher among present-biased borrowers.
-In contrast, the right panel suggests that the positive and significant overall TUT is driven by individuals who are ``sure-confident,'' i.e.\ borrowers who report that they are certain to recover their pawn.
-     %to be largely concentrated relevant survey question  according to her survey responses two binary performs a partition of the Treatment on the Untreated (FC), estimating the share of the effect that arises within each of two binary categories.
-The top bars examine present bias (individuals are more impatient over one-month time horizon than they are between three and four months).
-The bottom bars examine sure confidence (individual reports 100\% probability of repaying at time of taking loan).
-Blue bar is the component arising from those without the trait, orange bar from those with the trait.
-      %\footnotesize{ \textit{Do file: }  \texttt{partition_tut.do}
-
-\end{figure}
-
-\begin{figure}[H]
-     \caption{Heterogeneous Treatment Effects}
-    \label{heterogeneous_effects}
-    \begin{center}
-     \begin{subfigure}{0.55\textwidth}
-    \caption{ToT}
-       \centering
-      \includegraphics[width=\textwidth]{Figuras/he_dist_tau_hat_tot.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.55\textwidth}
-    \caption{TuT}
-       \centering
-      \includegraphics[width=\textwidth]{Figuras/he_dist_tau_hat_tut.pdf}
-    \end{subfigure} 
-       \begin{subfigure}{.55\textwidth}
-      \caption{ATE}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/he_dist_tau_hat_eff.pdf}
-    \end{subfigure}
-
-    \end{center}
-         \scriptsize
-     This Figure plots the densities of treatment on the untreated effects (TUT), treatment on the treated (TOT) effects, and conditional average treatment effects (ATE) based on the instrumental and causal forest models from Section \ref{sec:RF}.
-  %\footnotesize{ } \textit{Do file: }  \texttt{cate_dist.do}
-\end{figure}
-
-\begin{figure}[H]
-    \caption{``Mistakes'' in the choice arm}
-    \label{choose_wrong}
-   % \begin{center}
-   %     \begin{subfigure}{0.45\textwidth}
-   %     \caption{``Mistakes'' in choice arm}
-        \centering
-        \includegraphics[width=0.75\textwidth]{Figuras/line_cw_apr_tot_tut.pdf}
-  %  \end{subfigure}
-  %      \begin{subfigure}{0.45\textwidth}
-  %      \caption{\% with positive CATE from forced commitment}
-  %      \centering
-  %      \includegraphics[width=\textwidth]{Figuras/line_better_forceall_apr_te_cf.pdf}
-
-  %  \end{subfigure}
-
-  %  \end{center}
-        %\scriptsize
-        %In Panel (a) we estimate what the treatment effect of the commitment contract \textit{would have been} for all subjects in the choice arm if they had been forced into the fee-commitment contract.
-To do this we proceed in two steps.
-First, we estimate treatment effects in the forcing arm by comparing the Forced Commitment arm against the status quo arm.
-We let these effects be heterogeneous as a function of our $x$'s using \cite{atheygrf}'s methodology of causal forests.
-Second, we extrapolate these treatment effects based on the choice arm using the same $x$'s.
-Once we have personalized counterfactual treatment effects in the choice arm we calculate what fraction of subjects in the choice arm incurred in financial costs that are  $> z$\% than if they had chosen the opposite contract of what they actually chose, were $z$\% is defined as a fraction of the loan.
-$z$\% is a level of tolerance we can vary and we plot it in the X-axis.
-The left Y-axis measures the fraction of subjects that would have been better by a margin of $z$\% if they changed their choice, and the right Y-axis measures the amount of money ``left on the table''.
-We use bootstrap to tighten the confidence intervals (CIs).
-\cite{atheygrf}'s heterogeneous treatment effect using GRF is asymptotically normal.
-We compute the HTE ($\mu$) together with standard errors ($\sigma$) .
-For every pledge, we draw a random effect from a normal distribution with parameters ($\mu$,$\sigma^2$), and compute via bootstrap the percentage that choose wrong, along normal-approximation CIs (results are robust if we use instead percentile CIs or bias-corrected CIs) .
-This allows us to estimate a distribution for the upper and lower bound CIs, which we then use to obtain a 95\% CI.
-Panel (b) is analogous to Panel (a) except that it does the exercise separately for clients we classified as overconfident ($OC_i:=\mathbbm{1}(P^s_i-\widehat{P_i(X_i)}>0))$ and those we classified as not overconfident.
-Panel (c) simulates what percentage would be better by at least $z$ if we forced everybody of those in the Commitment Choice arm into the fee-commitment contract.
-        % Panel (d) asks whether it is the case that people with larger causal benefits from the Forced Commitment contract would be more likely to select that contract.
-To do this we proceed in two steps as well.
-First we estimate a flexible model of take-up of the fee commitment contract \textit{in the choice arm} using random forests, and from this model obtain a probability $P(x_i)$ of choosing the Forced Commitment contract for a client with characteristics $x_i$.
-We extrapolate this model to clients in the Forced Commitment arm to estimate what would they have chosen if we had given them choice.
-        % Figure (d) plots $\widehat{P(x_i)}$ in the X-axis using a binscatter that splits the X-axis in 100 percentile bins.
-The Y-axis plots the heterogeneous treatment effects of the fee forcing contract on the probability of losing the pawns (more negative means then more likely to recover it), averaged for the respective x-axis bin.
-Positive assortative selection would mean a negative relationship: those who benefit more by treatment and lose the pawn less are \emph{less} likely to choose it.
-Using all bins we estimate a slope of zero in the relationship.
-Using the 80 right most points, we estimate a \textit{positive} relationship.
-        %\textit{Do file: }  \texttt{choose\_wrong\_quant\_wrong\_tot\_tut.do, choose\_wrong\_quant\_wrong\_decomposition.do}
-\end{figure}
-
-This figure presents conditional average TUT and TOT effects for the APR outcome from Figure \ref{heterogeneous_effects} in an alternative manner, to consider the fraction of borrowers in the choice arm who made ``mistakes'' in their decision to accept or refuse the commitment contract.
-A ``mistake'' for a non-chooser is defined as a positive conditional TUT effect that significantly exceeds a specified threshold APR value.
-The green curve equals $[1 - F_{\text{TUT}}(\delta)]\times 100\%$, where $F_{\text{TUT}}$ is the CDF corresponding to density of conditional TUT effects from Figure \ref{heterogeneous_effects}, computed using the instrumental forest approach from \cite{atheygrf}.
-Evaluated at any positive value on the horizontal axis, it gives the fraction of non-choosers in the choice arm who made a ``mistake'' by not choosing commitment.
-The green shaded region gives associated 95\% pointwise confidence bands.
-Analogously, a ``mistake'' for a chooser is defined as a negative conditional TOT effect that exceeds a specified threshold APR value.
-The red curve equals $F_{\text{TOT}}(-\delta)$ where $F_{\text{TOT}}$ is the CDF corresponding to the density of conditional TOT effects from Figure \ref{heterogeneous_effects}.
-The red shaded region gives associated 95\% pointwise confidence bands.
-For both the red and green curves, we define the APR threshold so that larger mistakes are to the \emph{right} of smaller mistakes.
-This allows us to construct the overall fraction of mistakes in the choice arm, the blue curve, as a weighted average of the green and red curves.
-The weights equal the share of choosers and non-choosers in the choice arm.
-
-%\todo[inline]{Panel (a).
-Green line: survival function computed using estimated TUT of non-choosers in the choice arm.
-Red line: $F(-x)$ where $F$ is the CDF of individual TOT estimates for the choosers in the choice arm.
-Blue curve is the weighted average of the green and red with weights equal to the share of choosers versus non-choosers in the choice arm.
-Panel (b) is the survival function for the ATE computed for who?
-We think it's for the choice arm.
-(Shouldn't make a difference because of randomization and fairly large sample sizes.) Confidence bands are computed how?
-Use asymptotic normality and variance for each ``cell''}
-
-\cleardoublepage
-
-% \begin{figure}[H]
-%     \caption{Negative selection on treatment effects}
-%     \label{benefit_vs_choice_cdf}
-%     \begin{center}
-%     \begin{subfigure}{0.475\textwidth}
-%         \caption{APR benefit}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/cdf_predchoose_tau_apr.pdf}
-%     \end{subfigure}
-%     \begin{subfigure}{0.475\textwidth}
-%         \caption{Repayment}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/cdf_predchoose_tau_des.pdf}
-%     \end{subfigure}
-%     \begin{subfigure}{0.475\textwidth}
-%         \caption{Default}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/cdf_predchoose_tau_def.pdf}
-%     \end{subfigure}
-%     \end{center}
-%      \scriptsize    CDF of the heterogeneous treatment effect for choosers vs non-choosers.
-The dotted line below indicates the points where the difference in the distributions is significant.
-Instead of a single global null hypothesis (that the two CDFs are identical), there is a continuum of individual null hypotheses of CDF equality at each point.
-This methodology was proposed by \cite{GOLDMAN2018143}.
-
-%      \hl{Isaac : If I recall correctly we agreed to not work with the propensities.
-Besides this is giving us different results(?) - this was due to not using actual choosers and the prop.
-score model not being very good.
-Thus this will be removed?
-}
-%           %\footnotesize{ \textit{Do file: }  \texttt{benefit\_choice.do}}
-% \end{figure}
+We compare the in-sample performance of targeting rules against a policy of universal forced commitment.
+Table \ref{hit_miss_rule} shows error rates for six possible assignment rules: assigning all borrowers to control, all to treatment (Forcing), the optimal (infeasible) assignment, narrow RF targeting, Logit targeting, and we evaluate ex-post the voluntary choice, taking the wide RF as the ground truth.
+While the narrow RF correctly assigns roughly half of those who do not benefit from commitment to control, it also incorrectly allocates 4.38\% of the sample that would have gained from treatment to control.
+As such, it only improves the overall correct targeting rate by about half of a percentage point relative to universal Forcing.
+The Logit assignment rule is less successful at predicting benefits and harms, with a higher share of borrowers incorrectly assigned to both treatment and control, meaning that the overall correct targeting rate for the Logit is 5 pp lower than universal Forcing.
+%In particular it makes many Type II errors, resulting in a net targeting performance that is actually worse than universal forcing. 
+The underlying cause of the weak performance of targeting is that the attribute that predicts gains from forcing (being sure confident and not choosing the commitment) is largely behavioral and not easily predicted with basic covariates, as seen in Figure \ref{tut_beh_partition}.
+
+Self-targeting through choice proves to be little better than assigning everyone to the control condition, given the low take-up rate and the presence of both Type I and Type II errors in the choice arm.
+Fully 87\% of individuals in the Choice arm made a ``mistake'', weighting the error rates among choosers and non-choosers by their relative frequency in the Choice arm.
+The takeaway is that given low take-up, the large fraction of the sample benefiting from commitment, and the weak predictive power of the narrow covariates, in this case universal paternalism assigning all borrowers to the commitment contract appears to be an attractive targeting method.
+
+\section{Conclusion} \label{conclusion}
+
+This paper makes several contributions.
+First, it analyzes the large but understudied industry of pawn loans, and shows that a simple change to contract terms results in substantial financial savings for pawn borrowers: forced commitment lowers the APR from 57\% to 46\%, and reduces the fraction of borrowers who default by 6.6 pp, or 15\%.
+That this new contract generated large benefits for borrowers and yet was not offered, and that a contract that generated default was the industry standard instead, is related to the idea of ``veiled paternalism'' \cite{Laibson2018}, put on its head.
+In ``veiled paternalism'' principals embed forms of commitment into their products but mask this fact from consumers who may need but do not desire commitment, in pawn lending, over-collateralization means that lenders stand to make more money from defaulting borrowers, generating incentives for ``veiled \textit{non}-paternalism,'' embedding features that lead to high borrower costs in non-obvious ways.
+
+%Potentially due to the nature of the borrower pool, 
+%In our context voluntary commitment choice does improve borrower outcomes, but forcing commitment did induce significant cost savings for the overall group of clients.
+
+Second, our novel  ``controlled choice'' design allows us to go beyond ATE results and draw an important set of conclusions about the relationship between take-up and heterogeneous treatment effects.
+In particular, we simultaneously point-identify the impact of commitment on those who would naturally choose it \emph{and} those who only experience commitment when forced.
+Estimating this later quantity is critical in thinking about paternalism.
+We find substantial benefits of treatment for non-choosers and no evidence of selection on gains by borrowers who choose commitment.
+Given that the rate of voluntary commitment in our sample is only 11\%, in order to achieve widespread benefits in this context compulsory commitment appears to be necessary.
+%Clients appear to prefer the forced commitment after they have experienced it, in that assignment to this arm increases the fraction of individuals who return to pawn again.
+
+Why do borrowers leave such substantial returns on the table?
+Our results suggest that over-optimism is the characteristic most strongly associated with benefiting from the commitment despite not having chosen it.
+Our borrower pool overestimates their probability of repayment by more than 50\%, and our positive TUT estimate is largely confined to borrowers who incorrectly believe that they have little chance of defaulting.
+%More standard explanations such as discounting, learning, or time inconsistency find little support in our data.
+
+Using machine learning methods, we find the benefits of commitment close to universal.
+The benefits of targeting commitment based on characteristics that lenders can observe and participants would truthfully reveal are extremely limited, suggesting that universal commitment is an attractive policy in our empirical setting.
+
+%but the determinants that might allow us to target it more finely are primarily behavioral and hence not easily predicted in a fast incentive-compatible manner by lenders, making universal assignment to commitment attractive.
+Of course, in other applications this would have to be decided on a case-by-case basis.
+%Even a sophisticated machine learning-based exercise is only able to decrease the fraction of borrowers mis-targeted less than half percentage points relative to simply assigning everyone to commitment (from 9.78\% to 9.59\%).
+and a logit-based targeting rule actually does slightly worse than universal commitment.
+
+Where lenders have no incentive to engage in veiled paternalism and customers display inefficiently low demand for it, financial policy regulation may prove an attractive option.
+Pawnshops, along with other over-collateralized credit products such as payday lending, exist in an environment where the lender may desire customers to lose their collateral on the loan, hurting especially low-income populations who are its main users.
+With a now well-established toolkit of regular small payments and incentives delivering small default rates in microfinance, regulators may fruitfully investigate the possibility of requiring pawnbrokers to embed features of commitment and regularity into their repayment structures in more consistent ways.\footnote{If employed at scale in a competitive lending sector this would redistribute welfare from those who would have repaid (whose interest rates must now rise to cover lower returns from collateral seizure) towards those who would only repay in the presence of commitment.
+In a setting of lender market power however, redistribution from lenders to borrowers could occur.}
+An important question for future research will be the extent to which borrowers are able to learn about the benefits of commitment over time, making it so that temporary, lighter-touch policies could achieve lasting benefits for borrowers.
+Pawning with commitment may provide an important mechanism to preserve flexible credit access while allowing more poor borrowers to retain their assets.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%BIBLIOGRAPHY
+\begingroup
+\setstretch{1.10}
+\bibliographystyle{authordate1}
+%\bibliographystyle{amsalpha}
+%\bibliographystyle{AER}
+
+\bibliography{References}
+\endgroup
 

### 2023-12-17 OA.tex
edit for submission

@@
 
-\begin{center}
-	\LARGE The controlled choice design and private paternalism in pawnshop borrowing \\[0.5em]
-	\Large{Appendix $-$ For Online Publication} \\[1em]
+\newgeometry{margin=1in}
+
+\begin{center}
+	\LARGE Supplementary Appendix for ``The controlled choice design and private paternalism in pawnshop borrowing'' \\[0.5em]
+	%\Large{Appendix $-$ For Online Publication} \\[1em]
 	\large \author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira \and Francis J.\ DiTraglia}
@@
 
-\begingroup
-\let\clearpage\relax
-%\vspace{-1.5em} % the removed space. Set as appropriate
-\tableofcontents
-\endgroup
-
-\newpage
-
-\linespread{1.05}
-
-\linespread{1.05}
-
-\section{ Treatment Explanation Materials and Pictures}
-\vspace{.2in}
-
-\subsection{Materials}
+%\begingroup
+%\let\clearpage\relax
+%%\vspace{-1.5em} % the removed space. Set as appropriate
+%\tableofcontents
+%\endgroup
+
+%\newpage
+
+\linespread{1}
+
+%\section{ Treatment Explanation Materials and Pictures}
+\section{Treatment Explanation Materials} 
+%\vspace{.2in}
+
+%\subsection{Materials}
 
@@
 
-\subsection{Pictures}
-
-\begin{figure}[H]
-     \caption{Some Pawnshops}
-    \label{PawnshopPicture}
-    \begin{center}
-    \begin{subfigure}{0.405\textwidth}
-    \caption{Appraiser/tellers inside a pawnshop}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/empenio9_.png}
-    \end{subfigure}
-        \begin{subfigure}{0.45\textwidth}
-    \caption{Pawnshop}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/empenio11_.png}
-    \end{subfigure}
-
-        \vspace{3ex}
-
-    \begin{subfigure}{0.45\textwidth}
-    \caption{Pawnshop}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/empenio2_.png}
-    \end{subfigure}
-    \begin{subfigure}{0.415\textwidth}
-    \caption{Lost pawns which are for sale}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/empenio3_.png}
-    \end{subfigure}
-    \end{center}
-    \scriptsize{
-        This figure  shows pictures of pawnshops in Mexico city. They do not necessarily coincide with Lender P for confidentiality.} 
-\end{figure}
-
-\vspace{.1in}
-\begin{figure}[H]
-     \caption{Gold buyers next to pawnshops}
-    \label{GoldBuyers}
-    \begin{center}
-    \begin{subfigure}{.49\textwidth}
-    \caption{Gold buyer next to pawnshop 1}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/empenio7_.png}
-    \end{subfigure}
-    \begin{subfigure}{.49\textwidth}
-    \caption{Gold buyer next to pawnshop 1}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/empenio8_.png}
-    \end{subfigure}
-       \vspace{3ex}
-
-    \end{center}
-    \scriptsize{
-        This figure shows pictures of gold buyers next to pawnshops in Mexico city. They do not necessarily coincide with Lender P for confidentiality. }
-\end{figure}
+%\subsection{Pictures}
+%
+%\begin{figure}[H]
+%     \caption{Some Pawnshops}
+%    \label{PawnshopPicture}
+%    \begin{center}
+%    \begin{subfigure}{0.405\textwidth}
+%    \caption{Appraiser/tellers inside a pawnshop}
+%        \centering
+%        \includegraphics[width=\textwidth]{Figuras/empenio9_.png}
+%    \end{subfigure}
+%        \begin{subfigure}{0.45\textwidth}
+%    \caption{Pawnshop}
+%        \centering
+%        \includegraphics[width=\textwidth]{Figuras/empenio11_.png}
+%    \end{subfigure}
+%    
+%        \vspace{3ex}
+%
+%    \begin{subfigure}{0.45\textwidth}
+%    \caption{Pawnshop}
+%        \centering
+%        \includegraphics[width=\textwidth]{Figuras/empenio2_.png}
+%    \end{subfigure}
+%    \begin{subfigure}{0.415\textwidth}
+%    \caption{Lost pawns which are for sale}
+%        \centering
+%        \includegraphics[width=\textwidth]{Figuras/empenio3_.png}
+%    \end{subfigure}
+%    \end{center}
+%    \scriptsize{
+%        This figure  shows pictures of pawnshops in Mexico city. They do not necessarily coincide with Lender P for confidentiality.} 
+%\end{figure}
+
+%\vspace{.1in}
+%\begin{figure}[H]
+%     \caption{Gold buyers next to pawnshops}
+%    \label{GoldBuyers}
+%    \begin{center}
+%    \begin{subfigure}{.49\textwidth}
+%    \caption{Gold buyer next to pawnshop 1}
+%        \centering
+%        \includegraphics[width=\textwidth]{Figuras/empenio7_.png}
+%    \end{subfigure}
+%    \begin{subfigure}{.49\textwidth}
+%    \caption{Gold buyer next to pawnshop 1}
+%        \centering
+%        \includegraphics[width=\textwidth]{Figuras/empenio8_.png}
+%    \end{subfigure}
+%       \vspace{3ex}
+%       
+%    \end{center}
+%    \scriptsize{
+%        This figure shows pictures of gold buyers next to pawnshops in Mexico city. They do not necessarily coincide with Lender P for confidentiality. }
+%\end{figure}
 
@@
 \linespread{1.05}
+
+\begin{table}[H]
+\caption{Baseline survey questions (translated to English)}
+\label{baseline_survey}
+\begin{center}
+\scriptsize{\input{./Tables/transcribed.tex}}
+\end{center}
+\scriptsize{
+Translation of the baseline questionnaire.}
+\end{table}
+
+\newpage
 
@@
 
-\begin{table}[H]
-\caption{Baseline survey questions (translated to English)}
-\label{baseline_survey}
-\begin{center}
-\scriptsize{\input{./Tables/transcribed.tex}}
-\end{center}
-\scriptsize{
-Translation of the baseline questionnaire.}
-\end{table}
-
-\newpage
+%\newpage
 \subsection{More descriptives}
@@
 Although we cannot reject equality across the three arms (p-value=0.21), the Choice arm appears to have a somewhat larger number of borrowers than the Control and Forced arms.\footnote{p-value=0.23 and 0.12 respectively.} This seems to be due to sampling variability.
-The differences across arms are smaller when we look at medians, or when we look at the number of borrowers pawning (some borrowers pawn more than one piece).
-Figure \ref{boxplot_attrition} shows that full distribution of loans per day is very similar across treatment arms.
+Differences across arms are smaller when for medians, or when we compare the number of borrowers pawning (some borrowers pawn more than one piece).
+Figure \ref{boxplot_attrition} shows that distribution of loans per day is comparable across arms.
 The only noticeable difference is that the choice arm has a few more positive outliers.\footnote{If we winzorize at the 90th percentile, the mean number of branch-day pawns becomes identical across arms.}
@@
 The solid black line represent the median, while the gray line represent the mean.
-The dots on top of the box-plot represent an implicit CDF.
+The blue dots represent an implicit CDF.
 \end{figure}
@@
 
+\vspace{-1em}
+
 \begin{table}[H]
-\caption{Balance conditional on survey response and question-by-question response rates by treatment arm}
+\caption{Balance conditional on survey response and question-by-question response rates} %by treatment arm}
 \label{SS_cond_survet}
@@
 
-Panel A of this table presents the same information as Panel A of Table \ref{SS}, but restricts attention to the subsample of borrowers who answered at least one question in our baseline survey.
-Conditional on survey response, loan amount and weekday are balanced across treatment arms.
-Panel B presents response rates to each individual survey question across treatment arms, along with p-values for the F-test of no difference in response rates across survey arms.
-This panel uses data for borrowers who pawned on the same day as their survey response.
-
+Panel A of this table presents the same information as Panel A of Table \ref{SS}, restricted to the subsample of borrowers who answered at least one survey question.
+Conditional on survey response, loan amount and weekday are balanced across arms.
+Panel B presents response rates to each survey question across arms, along with p-values for the F-test of no difference in response rates across arms, using data for borrowers who pawned on the same day as their survey response.
 %\textit{Do file: } \texttt{ss\_att.do}
@@
 
-\begin{landscape}
 \section{ Main treatment effects: Additional material}
-\subsection{Multiple loans}
-
-\begin{table}[H]
-\caption{Multiple-loans robustness check}
-\label{multiple_loans}
-\begin{center}
-\scriptsize{\input{./Tables/multiple_loans.tex}}
-\end{center}
- \scriptsize
- An additional empirical issue generated by repeat pawning is the question of how to handle the treatment status of those who take multiple loans within the experiment.
+
+%\begin{landscape}
+%\subsection{Multiple loans}
+%
+%\begin{table}[H]
+%\caption{Multiple-loans robustness check}
+%\label{multiple_loans}
+%\begin{center}
+%\scriptsize{\input{./Tables/multiple_loans.tex}}
+%\end{center}
+% \scriptsize
+% An additional empirical issue generated by repeat pawning is the question of how to handle the treatment status of those who take multiple loans within the experiment.
 43\% of borrowers take more than one loan within the study period, and 19\% are assigned multiple treatment statuses on their different loans.
 The issue of sequential endogenous treatments has been extensively studied in the context of school lotteries, where the convention is to use the treatment status from the first exposure (ITT) \citep{cullen2006effect, abdulkadirouglu2011accountability}.\\
-
- This table provides robustness for our main results for different ways to handling the multiplicity of loans.
+% 
+% This table provides robustness for our main results for different ways to handling the multiplicity of loans.
 Columns 1-4 repeat the main analysis of financial cost and APR using the baseline approach from our main results,i.e.
@@
 The core treatment effects are robust to any of these ways of handling repeat pawning.
-
-%\textit{Do file: } \texttt{multiple\_loans.do}
-\end{table}
-
-\end{landscape}
+% 
+%%\textit{Do file: } \texttt{multiple\_loans.do}
+%\end{table}
+%
+%
+%\end{landscape}
 
@@
         \caption{Interpolation on bounding censoring for Default}
+        \vspace{-1em}
     \label{interpolation_censoring_imp}
@@
     \end{center}
+    \vspace{-1em}
      \scriptsize  {The next figure aims to answer the following question: For how many loans in the control arm can we impute recovery, and for how many in the treatment arm can we impute default and still have significance?
@@
         \caption{Survival graph}
+        \vspace{-2em}
     \label{survival_graph}
@@
     \end{center}
+    \vspace{-1em}
      \scriptsize  This Figure shows the CDF of loan completion either default or recovery in Panel (a), or loan recovery in Panel (b), by the number of days since first pawn.
@@
         \caption{\% of payment over time}
+        \vspace{-2em}
     \label{porc_payment_over_time}
@@
 
-\section{ Heterogeneity and Bounds}
-
-\subsection{Testing for heterogeneity}
-\label{append:chernozhukov}
-If the treatment effects $Y_{i1} - Y_{i0}$ are constant across $i$, then we must have
-\[
-\text{ATE}(X_i) \equiv \mathbbm{E}[Y_{i1} - Y_{i0} |X_i] = \mathbbm{E}[Y_{i1} - Y_{i0}] \equiv \text{ATE}
-\]
-for any covariates $X_i$ that vary across $i$.
+%\section{ Heterogeneity and Bounds}
+\section{Bounds, FOSD and Rank Invariance} \label{bounds_FOSD}
+
+%\subsection{Testing for heterogeneity}
+%\label{append:chernozhukov}
+%If the treatment effects $Y_{i1} - Y_{i0}$ are constant across $i$, then we must have
+%\[
+%\text{ATE}(X_i) \equiv \mathbbm{E}[Y_{i1} - Y_{i0} |X_i] = \mathbbm{E}[Y_{i1} - Y_{i0}] \equiv \text{ATE}
+%\]
+%for any covariates $X_i$ that vary across $i$.
 If, on the other hand, $\text{ATE}(X_i)$ can be predicted using some scalar function $\tau(\cdot)$ of $X_i$, then the average treatment effect function is not constant so there must be treatment effect heterogeneity.
-
-We operationalize this idea using a two-step approach proposed by \cite{chernozhukov2018generic}.
+%
+%We operationalize this idea using a two-step approach proposed by \cite{chernozhukov2018generic}.
 We begin by randomly dividing the participants in the forced arms of the experiment ($Z_i \neq 2$) into two groups: a training set and a test set.
-These sets are constructed to ensure that all observations from a given branch-day cluster are allocated to the same set.
-This avoids inferential problems that could arise from correlated unobservables within clusters.
-In the first step, we apply the generalized random forest approach of \cite{atheygrf} to the training set to estimate two proxy predictors: $\psi(\cdot|\text{Training})$ approximates the untreated potential outcome function, $\mathbbm{E}[Y_{i0}|X_i] = \mathbbm{E}[Y_i|Z_i=0,X_i]$, while  $\tau(\cdot|\text{Training})$, approximates the ATE function
-\[
-\text{ATE}(X_i) = \mathbbm{E}[Y_i|Z_i=1,X_i] - \mathbbm{E}[Y_i|Z_i=0, X_i].
-\]
-The proxy predictors need not be unbiased or even consistent estimators of the functions they aim to approximate: the goal of this exercise is merely to find a scalar function of $X_i$ that \emph{accurately predicts} $\text{ATE}(X_i)$.
-In the second step we fit a linear regression model to data from the training set using regressors constructed from the proxy functions $\psi(\cdot|\text{Training})$ and $\tau(\cdot|\text{Training})$ constructed in the first step.
+%These sets are constructed to ensure that all observations from a given branch-day cluster are allocated to the same set.
+%This avoids inferential problems that could arise from correlated unobservables within clusters.
+%In the first step, we apply the generalized random forest approach of \cite{atheygrf} to the training set to estimate two proxy predictors: $\psi(\cdot|\text{Training})$ approximates the untreated potential outcome function, $\mathbbm{E}[Y_{i0}|X_i] = \mathbbm{E}[Y_i|Z_i=0,X_i]$, while  $\tau(\cdot|\text{Training})$, approximates the ATE function
+%\[
+%\text{ATE}(X_i) = \mathbbm{E}[Y_i|Z_i=1,X_i] - \mathbbm{E}[Y_i|Z_i=0, X_i].
+%\]
+%The proxy predictors need not be unbiased or even consistent estimators of the functions they aim to approximate: the goal of this exercise is merely to find a scalar function of $X_i$ that \emph{accurately predicts} $\text{ATE}(X_i)$.
+%In the second step we fit a linear regression model to data from the training set using regressors constructed from the proxy functions $\psi(\cdot|\text{Training})$ and $\tau(\cdot|\text{Training})$ constructed in the first step.
 In particular, we estimate
-\begin{equation}
-Y_i = \alpha_0 + \alpha_1 \psi_i + \beta_1 (Z_i - \mathbbm{E}[Z_i]) + \beta_2 (Z_i - \mathbbm{E}[Z_i])(\tau_i - \mathbbm{E}[\tau_i]) + \epsilon_i
-\label{eq:chernreg}
-\end{equation}
-where $\psi_i \equiv \psi(X_i|\text{Training})$ and $\tau_i \equiv \tau(X_i|\text{Training})$.\footnote{This is a slightly simpler regression than the one proposed in equation (3.1) of \cite{chernozhukov2018generic}, which involves propensity score weights.
+%\begin{equation}
+%Y_i = \alpha_0 + \alpha_1 \psi_i + \beta_1 (Z_i - \mathbbm{E}[Z_i]) + \beta_2 (Z_i - \mathbbm{E}[Z_i])(\tau_i - \mathbbm{E}[\tau_i]) + \epsilon_i
+%\label{eq:chernreg}
+%\end{equation}
+%where $\psi_i \equiv \psi(X_i|\text{Training})$ and $\tau_i \equiv \tau(X_i|\text{Training})$.\footnote{This is a slightly simpler regression than the one proposed in equation (3.1) of \cite{chernozhukov2018generic}, which involves propensity score weights.
 Because the random assignment of $Z$ in our experiment does \emph{not} condition on $X$, the propensity score weights in our case are constant over $X$ and hence drop out.} As shown by \cite{chernozhukov2018generic}, the coefficients $\beta_1$ and $\beta_2$ from \eqref{eq:chernreg} identify the \emph{best linear predictor} of the conditional ATE based on $\tau(\cdot|\text{Training})$, namely
-\[
-\beta_1 = \mathbbm{E}[\text{ATE}(X_i)] = \text{ATE}, \quad
-\beta_2 = \frac{\text{Cov}[\text{ATE}(X_i), \tau_i]}{\text{Var}(\tau_i)}.
-\]
-If treatment effects are homogeneous we must have $\beta_2 = 0$. Rejecting this hypothesis establishes that $\tau_i$ predicts $\text{ATE}(X_i)$ and hence that $\Delta_i$ varies. 
-Since $\tau_i$ and $\psi_i$ do not depend on the test set, inference for the regression in \eqref{eq:chernreg} is straightforward conditional on the Training/Test split.  
-Our estimate for $\beta_2$ is 2.56 with a one-sided heteroskedasticity-robust (HC3) standard error of 0.43.
-Thus we easily reject the null hypothesis of homogeneous treatment effects.
+%\[
+%\beta_1 = \mathbbm{E}[\text{ATE}(X_i)] = \text{ATE}, \quad
+%\beta_2 = \frac{\text{Cov}[\text{ATE}(X_i), \tau_i]}{\text{Var}(\tau_i)}.
+%\]
+%If treatment effects are homogeneous we must have $\beta_2 = 0$. Rejecting this hypothesis establishes that $\tau_i$ predicts $\text{ATE}(X_i)$ and hence that $\Delta_i$ varies. 
+%Since $\tau_i$ and $\psi_i$ do not depend on the test set, inference for the regression in \eqref{eq:chernreg} is straightforward conditional on the Training/Test split.  
+%Our estimate for $\beta_2$ is 2.56 with a one-sided heteroskedasticity-robust (HC3) standard error of 0.43.
+%Thus we easily reject the null hypothesis of homogeneous treatment effects.
 
@@
 
-\newpage
-
-\subsection{Bounds, FOSD and Rank Invariance} \label{bounds_FOSD}
+%\newpage
 
@@
 These results are used below to provide a recipe for cluster-robust inference for the ASG, ASL, and ASB effects.
-The first result provides a regression-based approach to estimate the ATE and TOT.
+%The first result provides a regression-based approach to estimate the ATE and TOT.
 
@@
 \label{prop:TOTreg}
-Under Assumption \ref{assump:randchoice},
-\[
-Y = \mathbbm{E}(Y_0) + \text{ATE}\times Z_1 + \text{TOT} \times Z_2 D + U
-\]
-where $\mathbb{E}(U|Z) = 0$.
-Therefore, under standard regularity conditions, an IV regression of $Y$ on an intercept, $Z_1$ and $Z_2 D$ with instruments $(1, Z_0, Z_1)$ provides a consistent estimator of the ATE and TOT effects.
+Under Assumption \ref{assump:randchoice}, $Y = \mathbbm{E}(Y_0) + \text{ATE}\times Z_1 + \text{TOT} \times Z_2 D + U$ where $\mathbb{E}(U|Z) = 0$.
+Therefore, under standard regularity conditions, an IV regression of $Y$ on an intercept, $Z_1$ and $Z_2 D$ with instruments $(1, Z_0, Z_1)$ consistently estimates the ATE and TOT. 
 \end{prop}
@@
 \begin{align*}
-Y &= Z_0 Y_0 + Z_1 Y_1 + Z_2[(1 - C) Y_0 + CY_1]\\
-&= (Z_0 + Z_2)Y_0 + Z_1 Y_1 + Z_2C(Y_1 - Y_0)\\
-&= (Z_0 + Z_1 + Z_2)Y_0 + Z_1 (Y_1 - Y_0) + Z_2D(Y_1 - Y_0)\\
-&= Y_0 + Z_1 (Y_1 - Y_0) + Z_2D(Y_1 - Y_0).
+Y &= Z_0 Y_0 + Z_1 Y_1 + Z_2[(1 - C) Y_0 + CY_1] = (Z_0 + Z_2)Y_0 + Z_1 Y_1 + Z_2C(Y_1 - Y_0)\\
+&= (Z_0 + Z_1 + Z_2)Y_0 + Z_1 (Y_1 - Y_0) + Z_2D(Y_1 - Y_0) = Y_0 + Z_1 (Y_1 - Y_0) + Z_2D(Y_1 - Y_0).
 \end{align*}
@@
 \]
-by construction we have
-\[
-Y = \mathbbm{E}(Y_0) + \text{ATE} \times Z_1 + \text{TOT} \times Z_2 D+ U.
-\]
+by construction we have $Y = \mathbbm{E}(Y_0) + \text{ATE} \times Z_1 + \text{TOT} \times Z_2 D+ U$.
 Now, since $Z_2 D = Z_2 C$ and $Z$ is independent of $(Y_1, Y_0)$ by Assumption \ref{assump:randchoice} (i), we have
@@
 
-The next proposition provides regression-based estimates of the ATE and TUT.
+%The next proposition provides regression-based estimates of the ATE and TUT.
 \begin{prop}
 \label{prop:TUTreg}
-Under Assumption \ref{assump:randchoice}
-\[
-Y = \mathbbm{E}(Y_1) + \text{ATE}\times -Z_0 + \text{TUT} \times -Z_2 (1 - D) + V
-\] 
-where $\mathbb{E}(V|Z) = 0$.
+Under Assumption \ref{assump:randchoice} $Y = \mathbbm{E}(Y_1) + \text{ATE}\times -Z_0 + \text{TUT} \times -Z_2 (1 - D) + V$ where $\mathbb{E}(V|Z) = 0$.
 Therefore, under standard regularity conditions, an IV regression of $Y$ on an intercept, $-Z_0$ and $-Z_2(1-D)$ with instruments $(1, Z_0, Z_1)$ provides consistent estimates of the ATE and TUT effects.
@@
 \begin{align*}
-Y &= Z_0 Y_0 + Z_1 Y_1 + Z_2[(1 - C) Y_0 + CY_1]\\
-&= Z_0 Y_0 + Z_1 Y_1 + Z_2[(1 - C) (Y_0 - Y_1) + Y_1]\\
-&= Z_0 Y_0 + (Z_1 + Z_2) Y_1 + Z_2(1 - C) (Y_0 - Y_1) \\
-&= Z_0 Y_0 + (1 - Z_0) Y_1 + Z_2(1 - D) (Y_0 - Y_1) \\
+Y &= Z_0 Y_0 + Z_1 Y_1 + Z_2[(1 - C) Y_0 + CY_1] = Z_0 Y_0 + Z_1 Y_1 + Z_2[(1 - C) (Y_0 - Y_1) + Y_1]\\
+&= Z_0 Y_0 + (Z_1 + Z_2) Y_1 + Z_2(1 - C) (Y_0 - Y_1) = Z_0 Y_0 + (1 - Z_0) Y_1 + Z_2(1 - D) (Y_0 - Y_1) \\
 &= Y_1 - Z_0 (Y_1 - Y_0) - Z_2(1 - D) (Y_1 - Y_0)
@@
 \]
-by construction we have
-\[
-Y = \mathbb{E}(Y_1) + \text{ATE} \times -Z_0 + \text{TUT} \times -Z_2(1 - D) + V.
-\]
+by construction we have $Y = \mathbb{E}(Y_1) + \text{ATE} \times -Z_0 + \text{TUT} \times -Z_2(1 - D) + V$.
 Now, since $Z_2(1 - D) = Z_2 (1 - C)$ and $Z$ is independent of $(Y_0, Y_1)$ by Assumption \ref{assump:randchoice} (i),
@@
 Since $\text{ASG} = \text{TOT} - \text{TUT}$, the preceding two propositions provide consistent estimates of $\text{ASG}$ effect.
-The $\text{ASB}$ effect, $\mathbbm{E}(Y_0|C=1) - \mathbb{E}(Y_0|C=0)$, can likewise be estimated by taking the difference of coefficients across two linear IV regressions, as shown in the following proposition.
+The $\text{ASB}$ effect, $\mathbbm{E}(Y_0|C=1) - \mathbb{E}(Y_0|C=0)$, can likewise be estimated by taking the difference of coefficients across two linear IV regressions.
+%as shown in the following proposition.
 
@@
 where $\mathbbm{E}(U_0|Z) = \mathbbm{E}(U_1|Z) = 0$.
-Thus, under standard regularity conditions, an IV regression of $(1 - D)Y$ on $Z_0$ and $(1 - D)Z_2$ with instruments $(Z_0, Z_2)$ and no intercept provides consistent estimates of $\mathbb{E}(Y_0)$ and $\mathbb{E}(Y_0|C=0)$.
-Similarly, an IV regression of $(1 - D)Y$ on $(Z_0 + Z_2)$ and $-DZ_2$ with instruments $(Z_0, Z_2)$ and no intercept provides consistent estimates of $\mathbb{E}(Y_0)$ and $\mathbb{E}(Y_0|C=1)$.
+Thus, under standard regularity conditions, an IV regression of $(1 - D)Y$ on $Z_0$ and $(1 - D)Z_2$ with instruments $(Z_0, Z_2)$ and no intercept consistently estimates $\mathbb{E}(Y_0)$ and $\mathbb{E}(Y_0|C=0)$.
+Similarly, an IV regression of $(1 - D)Y$ on $(Z_0 + Z_2)$ and $-DZ_2$ with instruments $(Z_0, Z_2)$ and no intercept consistently estimates $\mathbb{E}(Y_0)$ and $\mathbb{E}(Y_0|C=1)$.
 \end{prop}
@@
 (1 - D)Y &=  [Z_0 + Z_2 (1 - C)]\left\{Z_0 Y_0 + Z_1 Y_1 + Z_2[(1 - C) Y_0 + CY_1]\right\}\\
-&= Z_0 Y_0 + Z_2 (1 - C) [(1 - C) Y_0 + C Y_1]\\
-&= Z_0 Y_0 + Z_2 (1 - C) Y_0.
+&= Z_0 Y_0 + Z_2 (1 - C) [(1 - C) Y_0 + C Y_1] = Z_0 Y_0 + Z_2 (1 - C) Y_0.
 \end{align*}
@@
 Therefore, since $Z_2 (1 - C) = Z_2 (1 - D)$,
-\begin{align*}
-(1 - D)Y &= Z_0 Y_0 + Z_2 (1 - D) Y_0\\
-(1 - D)Y &= (Z_0 + Z_2) Y_0 + (-DZ_2) Y_0. 
-\end{align*}
+\[
+(1 - D)Y = Z_0 Y_0 + Z_2 (1 - D) Y_0, \quad
+(1 - D)Y = (Z_0 + Z_2) Y_0 + (-DZ_2) Y_0. 
+\]
 Now, defining
@@
 
-The next results shows that the $\text{ASL}$ effect, $\mathbbm{E}(Y_1|C=1) - \mathbb{E}(Y_1|C=0)$, can be estimated as the difference of coefficients across two linear IV regressions, as shown in the following proposition.
+The next result shows that the $\text{ASL}$ effect, $\mathbbm{E}(Y_1|C=1) - \mathbb{E}(Y_1|C=0)$, can be estimated as the difference of coefficients across two linear IV regressions.
 
@@
 DY &=  (Z_1 + Z_2 C)\left\{Z_0 Y_0 + Z_1 Y_1 + Z_2[(1 - C) Y_0 + CY_1]\right\}\\
-&= Z_1 Y_1 + Z_2 C[(1 -C) Y_0 + C Y_1]\\
-&= Z_1 Y_1 + Z_2 C Y_1
+&= Z_1 Y_1 + Z_2 C[(1 -C) Y_0 + C Y_1] = Z_1 Y_1 + Z_2 C Y_1
 \end{align*}
 because $Z_j^2 = Z_j$ for any $j$ and $Z_j Z_k = 0$ for any $j \neq k$ and, similarly, $(1 - C)^2 = (1 - C)$ and $C (1 - C) = 0$. Therefore, since $Z_2 (1 - C) = Z_2 (1 - D)$,
-\begin{align*}
- DY &= (Z_1 + Z_2)Y_1 + Z_2 (D - 1) Y_1\\
- DY &= Z_1 Y_1 + Z_2 D Y_1.
-\end{align*}
+\[
+ DY = (Z_1 + Z_2)Y_1 + Z_2 (D - 1) Y_1, \quad
+ DY = Z_1 Y_1 + Z_2 D Y_1.
+\]
 Now, defining
@@
 Now consider a pair of just-identified linear IV regressions given by
-\begin{align*}
-Y_{ig} &= \boldsymbol{X}_{1,ig}' \boldsymbol{\theta}_0 + U_{ig} \\
-Y_{ig} &= \boldsymbol{X}_{0,ig}' \boldsymbol{\theta}_1 + V_{ig}
-\end{align*}
+\[
+Y_{ig} = \boldsymbol{X}_{1,ig}' \boldsymbol{\theta}_0 + U_{ig}, \quad
+Y_{ig} = \boldsymbol{X}_{0,ig}' \boldsymbol{\theta}_1 + V_{ig}
+\]
 with common instrument vector $\boldsymbol{W}_{ig}$. 
@@
 \[
-\mathbf{W}_g \equiv \begin{bmatrix}
-\boldsymbol{W}_{1g}' \\
-\vdots \\
-\boldsymbol{W}_{N_gg}' \\
+\mathbf{W}_g' \equiv \begin{bmatrix}
+\boldsymbol{W}_{1g} & \cdots & 
+\boldsymbol{W}_{N_gg} 
 \end{bmatrix}, \quad
-\mathbf{W} = \begin{bmatrix}
-\mathbf{W}_1\\ \vdots \\ \mathbf{W}_G
+\mathbf{W}' = \begin{bmatrix}
+\mathbf{W}_1' & \cdots & \mathbf{W}_G'
 \end{bmatrix},
@@
 we can write the preceding equations in matrix form as
-\begin{align*}
-\mathbf{Y} &= \mathbf{X}_1\boldsymbol{\theta_1} + \mathbf{U}\\
-\mathbf{Y} &= \mathbf{X}_0\boldsymbol{\theta_0} + \mathbf{V}
-\end{align*}
+\[
+\mathbf{Y} = \mathbf{X}_1\boldsymbol{\theta_1} + \mathbf{U}, \quad
+\mathbf{Y} = \mathbf{X}_0\boldsymbol{\theta_0} + \mathbf{V}
+\]
 with instrument matrix $\mathbf{W}$.
@@
 Our parameter of interest is an element of the difference $(\theta_1 - \theta_0)$, so  it suffices to calculate the asymptotic distribution of $(\widehat{\boldsymbol{\theta}}_1 - \widehat{\boldsymbol{\theta}}_0)$.
-
 Re-arranging the preceding two equations, we have
@@
 where
-\begin{align*}
-\mathbf{S}_{UU} &\equiv \sum_{g=1}^G \mathbf{W}_g' \widehat{\mathbf{U}}_g \widehat{\mathbf{U}}_g' \mathbf{W}_g\\
-\mathbf{S}_{UV} &\equiv \sum_{g=1}^G \mathbf{W}_g' \widehat{\mathbf{U}}_g \widehat{\mathbf{V}}_g' \mathbf{W}_g\\
-\mathbf{S}_{VU} &\equiv \mathbf{S}_{UV}'\\
-\mathbf{S}_{VV} &\equiv \sum_{g=1}^G \mathbf{W}_g' \widehat{\mathbf{V}}_g \widehat{\mathbf{V}}_g' \mathbf{W}_g
-\end{align*}
+\[
+\mathbf{S}_{UU} \equiv \sum_{g=1}^G \mathbf{W}_g' \widehat{\mathbf{U}}_g \widehat{\mathbf{U}}_g' \mathbf{W}_g, \quad
+\mathbf{S}_{UV} \equiv \sum_{g=1}^G \mathbf{W}_g' \widehat{\mathbf{U}}_g \widehat{\mathbf{V}}_g' \mathbf{W}_g, \quad
+\mathbf{S}_{VU} \equiv \mathbf{S}_{UV}', \quad
+\mathbf{S}_{VV} \equiv \sum_{g=1}^G \mathbf{W}_g' \widehat{\mathbf{V}}_g \widehat{\mathbf{V}}_g' \mathbf{W}_g
+\]
 and we define the IV residuals
-\begin{align*}
-\widehat{\mathbf{U}}_g &\equiv \mathbf{Y}_g - \mathbf{X}_{1,g}\widehat{\boldsymbol{\theta}}_1\\
-\widehat{\mathbf{V}}_g &\equiv \mathbf{Y}_g - \mathbf{X}_{0,g}\widehat{\boldsymbol{\theta}}_0.
-\end{align*}
+\[
+\widehat{\mathbf{U}}_g \equiv \mathbf{Y}_g - \mathbf{X}_{1,g}\widehat{\boldsymbol{\theta}}_1, \quad
+\widehat{\mathbf{V}}_g \equiv \mathbf{Y}_g - \mathbf{X}_{0,g}\widehat{\boldsymbol{\theta}}_0.
+\]
 In our application the number of clusters, $G$, is large.
@@
 
-\section{ Testable Implications of the Exclusion Restriction}
+\section{Testing the Exclusion Restriction}
 \label{append:exclusion}
@@
 Using this notation, \eqref{eq:exclusion0} becomes $Y_0 = Y_{0,2}$ and while \eqref{eq:exclusion1} becomes $Y_1 = Y_{1,2}$.
-If we do not impose this pair of equalities, part (iii) of Assumption \ref{assump:randchoice} becomes 
+Without imposing these, part (iii) of Assumption \ref{assump:randchoice} becomes 
 \[
@@
 Our approach is closely related to arguments from \cite{huber_mellace} and \cite{BinaryRegressor}, among others.
-As such, the following is a heuristic explanation rather than a fully-rigorous proof.
-See the aforementioned papers for more details of how to make this argument fully rigorous.
+%As such, the following is a heuristic explanation rather than a fully-rigorous proof.
+%See the aforementioned papers for more details of how to make this argument fully rigorous.
 
@@
     \label{wide_narrow_forests}
+    \vspace{-2em}
     \begin{center}
@@
     \end{center}
+    \vspace{-1em}
       \scriptsize  This figure plots the relationship between the causal forest conditional ATE estimates from Section \ref{sec:RF} that use the ``wide'' set of covariates (all intake survey responses) and those based on a restricted ``narrow'' set of covariates (age, gender, HS education, and previous borrowing).
@@
 
-Figure \ref{targeting_rules} compares the in-sample performance of these targeting rules against a policy of universal forced commitment.
+Figure \ref{targeting_rules} compares the in-sample performance of targeting rules against universal forced commitment.
 The plot presents the estimated proportion of borrowers who benefit from a particular treatment assignment rule, along with associated 95\% confidence bands, where ``benefit'' is defined as having a CATE above a particular threshold.
@@
 Because this is an in-sample exercise, the logistic and random forest classification rules have an unfair advantage: there is no adjustment for overfitting.
-In spite of this, their performance is unimpressive relative to a policy of universal forced commitment.
+In spite of this, their performance is unimpressive relative to of universal forced commitment.
 The fraction of the whole sample incorrectly targeted when moving from universal forced commitment to targeting based on the narrow RF falls only from 9.78\% to 9.59\%.
-The logit targeting rule actually makes things marginally worse.
+Logit targeting makes things marginally worse.
 
@@
     \end{center}
-      \scriptsize   This figure plots the percentage of borrowers who would benefit from a program in which commitment is targeted using the ``narrow'' covariate set (age, gender, HS education, and previous borrowing).
+    %\vspace{-2em}
+      %\scriptsize   This figure plots the percentage of borrowers who would benefit from a program in which commitment is targeted using the ``narrow'' covariate set (age, gender, HS education, and previous borrowing).
 In this exercise ``benefit'' is defined to mean having a conditional ATE above a particular threshold, taking the estimated conditional effects from the ``wide'' causal forest as ground truth.
@@
 Because this is an in-sample exercise, it overstates the actual performance of logit and RF-based targeting.
+
       %, the top \hl{XXX\%} of Both targeted Both of the targeted assignment rules are assigned by a the ``narrow'' causal forest in green, and targeting based on the logit model in red.

### 2023-12-17 donde.tex
edit for submission

@@
 The transaction takes less than 10 minutes and is conducted at the branch in person between the client and the appraiser (i.e.
-a teller, see Figure \ref{PawnshopPicture}).
+a teller).
+%, see Figure \ref{PawnshopPicture}). 
 The appraiser weighs the gold piece and runs tests on its purity.
@@
 One potential explanation for high default is that clients are really just knowingly selling their gold piece through a pawn contract on which they intend to default.
-This appears unlikely for several reasons: (a) clients can easily sell the gold and obtain a higher amount of instant cash at gold-buying stores located close to almost all our pawnshop branches (see Figure \ref{GoldBuyers}), (b) the reported subjective value of the pawn is larger than the appraised value for 83\% of clients, (c) among those that lose their pawn, 29\% paid a positive amount towards its recovery and on average paid 42\% of the value of their loan (see Figure \ref{proxy_naive} in Appendix) --- this can only be rationalized if they expected to recover their pawn, and (d) 72\% of borrowers report a 100\% probability of repaying their loan (and 98\% at least a 50\% chance of repaying) in our baseline survey at the time they take the loan.
+This appears unlikely for several reasons: (a) clients can easily sell the gold and obtain a higher amount of instant cash at gold-buying stores located close to almost all our pawnshop branches,
+%(see Figure \ref{GoldBuyers})
+(b) the reported subjective value of the pawn is larger than the appraised value for 83\% of clients, (c) among those that lose their pawn, 29\% paid a positive amount towards its recovery and on average paid 42\% of the value of their loan (see Figure \ref{proxy_naive} in Appendix) --- this can only be rationalized if they expected to recover their pawn, and (d) 72\% of borrowers report a 100\% probability of repaying their loan (and 98\% at least a 50\% chance of repaying) in our baseline survey at the time they take the loan.
 %Note that high default could be detrimental from the lender's point of view, since it may reduce the likelihood that the client becomes a return customer.
@@
 These are treated as different observations.
-Table \ref{multiple_loans} shows our results are similar when dealing with the multiplicity of loans per borrower.
+Additional results, available upon request, show that our results are robust to different ways of handling multiple loans for each borrower.
 Each regression includes branch and day-of-week FE.
@@
 }
+%Table \ref{multiple_loans} shows our results are similar when dealing with the multiplicity of loans per borrower.
 
@@
 The borrowers who did not choose commitment could simply be those who don't need it. 
-Indeed, we find strong evidence that the effect of forced commitment varies substantially across individuals in our experiment: Appendix \ref{append:chernozhukov} tests and rejects the null hypothesis of homogeneous treatment effects, following the methodology of \cite{chernozhukov2018generic}.
+Indeed, we find strong evidence that the effect of forced commitment varies substantially across individuals in our experiment: we test and
+%Appendix \ref{append:chernozhukov} tests and rejects 
+the null hypothesis of homogeneous treatment effects, following the methodology of \cite{chernozhukov2018generic}. (Details available upon request.)
 So the question remains: do the 89\% who do not choose commitment know something about their personal situations that we as researchers do not, or are most people in the choice arm making a costly financial mistake?
@@
 Figure \ref{wide_narrow_forests} shows the relationship between the CATEs estimated from the RF using the ``wide'' and ``narrow'' covariate sets.
-We can generate substantially less heterogeneity when using the narrow covariate set, although we still reject the null hypothesis of no treatment effect heterogeneity, following the approach of \cite{chernozhukov2018generic}.\footnote{See \ref{append:chernozhukov} for details of this method.}
+We can generate substantially less heterogeneity when using the narrow covariate set, although we still reject the null hypothesis of no treatment effect heterogeneity, following the approach of \cite{chernozhukov2018generic}.
+\footnote{Details available upon request.}%\footnote{See \ref{append:chernozhukov} for details of this method.}
 

### 2024-05-21 ECTA submission/OA_ecta.tex
ecta submission

@@
 
-\title{The controlled choice design and private paternalism in pawnshop borrowing - ONLINE APPENDIX}
+\title{ONLINE APPENDIX: The controlled choice design and private paternalism in pawnshop borrowing}
 \runtitle{The controlled choice design and private paternalism}
@@
 
+\newpage
+
 \begin{appendix}
 
-\section{Treatment Explanation Materials and Pictures}
-
-\subsection{Materials}
-
-\begin{figure}[!htb]
-     \caption{Contract Terms Summary}
-    \label{PaperSlip}
-    \begin{center}
-        \includegraphics[width=0.7\textwidth]{Figuras/TicketLenderP.png}
-    \end{center}
-    \legend{We show a sample receipt that was given to clients that got assigned to the fee-forcing contract (the font and format were changed to protect Lender's P identity).
-We want to highlight the salience of some items.
-First the title clearly indicated which contract the client has (arrow 1).
-Second, in the case of the fee contract it clearly indicates that there is a fee for paying late equivalent to 2\% of the value of the monthly payment (arrow 2).
-Third, there is a calendar for payments clearly specifying the dates and amounts to pay each month.}
-\end{figure}
-
-\begin{figure}[!htb]
-     \caption{Explanatory Material}
-    \label{ExplanatoryMaterial}
-    \begin{center}
-    \begin{subfigure}{\textwidth}
-        \centering
-        \includegraphics[width=0.7\textwidth]{Figuras/micas.pdf}
-    \end{subfigure}
-    \end{center}
-    \legend{ This is a (translated) sample information slide shown to clients. The real ones were twice the size of this figure and were laminated. Different ones were shown for each treatment arm.}
-\end{figure}
-
-\subsection{Pictures}
-
-\begin{figure}[!htb]
-     \caption{Some Pawnshops}
-    \label{PawnshopPicture}
-    \begin{center}
-    \begin{subfigure}{0.405\textwidth}
-    \caption{Appraiser/tellers inside a pawnshop}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/empenio9_.png}
-    \end{subfigure}
-        \begin{subfigure}{0.45\textwidth}
-    \caption{Pawnshop}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/empenio11_.png}
-    \end{subfigure}
-
-        \vspace{3ex}
-
-    \begin{subfigure}{0.45\textwidth}
-    \caption{Pawnshop}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/empenio2_.png}
-    \end{subfigure}
-    \begin{subfigure}{0.415\textwidth}
-    \caption{Lost pawns which are for sale}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/empenio3_.png}
-    \end{subfigure}
-    \end{center}
-   \legend{ This figure  shows pictures of pawnshops in Mexico city. They do not necessarily coincide with Lender P for confidentiality. }
-\end{figure}
-
-\begin{figure}[!htb]
-     \caption{Gold buyers next to pawnshops}
-    \label{GoldBuyers}
-    \begin{center}
-    \begin{subfigure}{.49\textwidth}
-    \caption{Gold buyer next to pawnshop 1}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/empenio7_.png}
-    \end{subfigure}
-    \begin{subfigure}{.49\textwidth}
-    \caption{Gold buyer next to pawnshop 1}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/empenio8_.png}
-    \end{subfigure}
-       \vspace{3ex}
-
-    \end{center}
-    \legend{  This figure shows pictures of gold buyers next to pawnshops in Mexico city. They do not necessarily coincide with Lender P for confidentiality. }
-\end{figure}
-
-\subsection{Descriptives consistent with overconfidence}
-
-\vspace{.2in}
-\begin{figure}[!htb]
-    \caption{Behavior of borrowers who lost their pawn}
-    \label{proxy_naive}
-    \begin{center}
-    \begin{subfigure}{0.40\textwidth}
+%\section{ Treatment Explanation Materials and Pictures}
+\section{Additional materials} 
+%\vspace{.2in}
+\begin{figure}[!h]
+
+    \begin{center}
+    \begin{subfigure}{0.35\textwidth}
         \caption{Elapsed days to first payment}
@@
     \end{center}
-       \legend{ This figure provides more details on the behavior of clients who were assigned to the control group and did not recover their pawn.
+        \caption{Behavior of borrowers who lost their pawn.
+This figure provides more details on the behavior of clients who were assigned to the control group and did not recover their pawn.
 Panel (a) shows a histogram of days elapsed from the pawn to the first payment, while panel (b) displays a histogram of days elapsed until the last payment.
@@
 Panel (c) shows a histogram of the fraction of the loan paid, while panel (d) presents a barplot of the number of times that borrowers went to the branch to make payments.}
+        \label{proxy_naive}
       %\textit{Do file: }  \texttt{hist\_den\_default.do}
@@
 
-\section{Internal Validity}
-
-\subsection{Survey}   \label{app:survey_data}
-
-We now present analysis of the extent to which the survey-responding sample is representative and balanced.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{ Internal Validity}
+
+\begin{table}[!h]
+\caption{Summary statistics and Balance}
+\label{SS}
+\begin{center}
+\resizebox{0.65\textwidth}{!}{
+\scriptsize{\input{./Tables/SS.tex}}
+}
+\end{center}
+\legend {This table has two panels.
+Panel A uses administrative data at the loan level, while Panel B uses survey data.
+Each row in this table corresponds to a regression, where the level of observation is the individual loan originated.
+The dependent variables of these regressions are displayed in the first column.
+Each dependent variable is regressed in a multivariate OLS regression against the experimental arms indicators (control, forced commitment, choice).
+The table reports the coefficients on each of these indicators, as well as the p-value an F-test of the null hypothesis of equality of the three coefficients.
+The admin data was a very limited set of pre-determined variables.
+The dependent variables in Panel A are the loan amount in pesos, and an indicator for whether the day of the loan origination was a weekday (as opposed to weekend).
+The dependent variables in Panel B from the survey.
+Subjective value of the pawn (how much would the client be willing to sell it for (Q3), an indicator for having trouble paying bills in the last 6-months (Q28), present bias (constructed from questions Q10 and Q29 in the standard way as in \cite{Ashraf}), an indicator for whether they make expenses budget for the month ahead of time.
+The subjective probability of recovery was elicited a la Manski (from 0 to 100 what is the probability that you will recoup your pawn), pawned before is a dummy=1 if the client declares to have pawned before (although not necessarily with Lender $P$) age is in year, +High-school is a dummy that indicates if the client has completed high school.
+}
+%\textit{Do file: } \texttt{ss\_att.do}
+\end{table}
+
+If potential borrowers disliked being forced into a commitment contract, we would expect a lower number of pawns on branch days where only the commitment contract is available compared to control days.
+Table \ref{attrition_table} shows that this is not the case.
+There is no difference at all between the Control and Forced Commitment arm in terms of the number of pawns per branch-day.
+Although we cannot reject equality across the three arms (p-value=0.21), the Choice arm appears to have a somewhat larger number of borrowers than the Control and Forced arms.\footnote{p-value=0.23 and 0.12 respectively.} This seems to be due to sampling variability.
+Differences across arms are smaller when for medians, or when we compare the number of borrowers pawning (some borrowers pawn more than one piece).
+% Figure \ref{boxplot_attrition} shows that distribution of loans per day is comparable across arms.
+The only noticeable difference is that the choice arm has a few more positive outliers.\footnote{If we winzorize at the 90th percentile, the mean number of branch-day pawns becomes identical across arms.}
+
+\begin{table}
+\caption{Limited and balanced attrition}
+\label{attrition_table}
+\begin{center}
+\scriptsize{\input{./Tables/Attrition.tex}}
+\end{center}
+\legend{Each row in this table 
+ corresponds to a regression.
+The dependent variables are: the number of pawns-loans originated per day per branch, the number of borrowers per day-branch, a variable indicating whether a person who answered the baseline survey (before knowing contract terms) ended up pawning, and an indicator of whether the person that obtained the loan answered the baseline survey.
+Each dependent variable is regressed in a multivariate OLS regression against the experimental arms indicators (control, forced commitment, choice).
+The table reports the coefficients on each of these indicators, as well as the p-value of an F-test of the null hypothesis of equality of the three coefficients.
+%Figure \ref{boxplot_attrition}, in the appendix shows a box-plot of the first two variables, showing the distribution across arms is balanced.
+ }
+%\textit{Do file: } \texttt{ss\_att.do}
+\end{table}
+
+The bottom panel of Table \ref{attrition_table} shows balance in a more focused way, given that the surveys were conducted prior to the revelation of treatment status.
+We find that in no arm did more than three percent of individuals who responded to the survey go on to refuse loans.
+That is, the overwhelming marjority of potential borrowers did not leave the branch after learning which contract was on offer.
+Moreover, the extremely small fraction that did leave is balanced across arms.
+Therefore it appears that the treatments have not induced any endogenous shifts in the composition of borrowers.
+
+A less critical form of attrition is differential refusal to answer the survey questions.
+The survey was conducted before treatment status was revealed, and we observe loan outcomes regardless of whether the survey was conducted.
+Our core experimental estimates do not use the survey data as covariates, but the analysis in Section \ref{Paternalism} is restricted to the subset of borrowers who answered at least some survey questions.
+The bottom row of Table \ref{attrition_table} shows that the survey response rate is broadly similar across arms (about 78 percent).
+
+%We now present an analysis of the extent to which the survey-responding sample is representative and balanced.
 Table \ref{SS_cond_survet} presents information about survey non-response.
@@
 From the table, we see that loan amount and weekday are balanced across treatment arms among survey respondents and that response rates are likewise stable across treatment arms.
-Table \ref{TUT_cond_survet} shows how the estimated TUT effect changes if we restrict our estimation sample based on survey response.
-The first row of the table presents TUT results for the financial cost outcome, while the second presents corresponding results for the APR outcome.
-In each row, column (1) presents the full-sample TUT estimate and standard error while the remaining columns restrict the sample to borrowers who answered a particular survey question or set of questions.
-For example, column (4) presents results for borrowers who answered the two questions needed to compute our measure of ``present bias'' discussed in the next paragraph, while column (9) present results restricted to participants who disclosed their sex.
-As seen from the table, our TUT estimates are quite stable across sub-samples defined by survey response.
-In each case they are positive and of the same magnitude as the corresponding full-sample estimate, although statistical significance varies depending on the size of the corresponding sub-sample. 
-For these reasons, we are comfortable relying on data for survey respondents in the empirical exercises that follow.
-In exercises that rely on a single survey question, we use data for every borrower who answered that question.
-In the random forest exercises described below, we use data for every borrower who answered at least one survey question.
-
-\begin{table}[!htb]
-\caption{Baseline survey questions (translated to English)}
-\label{baseline_survey}
-\begin{center}
-\scriptsize{\input{./Tables/transcribed.tex}}
-\end{center}
-\legend{ Translation of the baseline questionnaire.}
-\end{table}
-
-\begin{figure}[!htb]
-     \caption{Box-plot across arms}
-    \label{boxplot_attrition}
-    \begin{center}
-    \begin{subfigure}{0.45\textwidth}
-    \caption{Number of pawns}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/box_plot_num_pawns.pdf}
-    \end{subfigure}
-        \begin{subfigure}{0.45\textwidth}
-    \caption{Number of borrowers}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/box_plot_num_pawns.pdf}
-    \end{subfigure}
-    \end{center}
-    \legend{ This figure presents box-plot for the number of pawns and borrowers per branch-day across different arms.
-The solid black line represent the median, while the gray line represent the mean.
-The dots on top of the box-plot represent an implicit CDF.
+
+% Table \ref{TUT_cond_survet} shows how the estimated TUT effect changes if we restrict our estimation sample based on survey response.
+% The first row of the table presents TUT results for the financial cost outcome, while the second presents corresponding results for the APR outcome.
+% In each row, column (1) presents the full-sample TUT estimate and standard error while the remaining columns restrict the sample to borrowers who answered a particular survey question or set of questions.
+% For example, column (4) presents results for borrowers who answered the two questions needed to compute our measure of ``present bias'' discussed in the next paragraph, while column (9) present results restricted to participants who disclosed their sex.
+% As seen from the table, our TUT estimates are quite stable across sub-samples defined by survey response.
+% In each case they are positive and of the same magnitude as the corresponding full-sample estimate, although statistical significance varies depending on the size of the corresponding sub-sample. 
+% For these reasons, we are comfortable relying on data for survey respondents in the empirical exercises that follow.
+% In exercises that rely on a single survey question, we use data for every borrower who answered that question.
+% In the random forest exercises described below, we use data for every borrower who answered at least one survey question.
+
+% \begin{table}[H]
+% \caption{Survey Non-response: TUT estimates for respondents to each survey question.}
+% \label{TUT_cond_survet}
+% \begin{center}
+% \scriptsize{\input{./Tables/tut_cond_survey.tex}}
+% \end{center}
+% \legend{Some borrowers did not respond to our survey; others only completed part of the survey.
+% This table computes the TUT effect for a number of sub-groups by survey response, and compares them against the overall TUT effect.
+% The top panel uses financial cost as the outcome variable, while the bottom panel uses APR.
+% Each group is defined by the borrowers who responded to a particular \emph{subset} of the survey questions. 
+% For example, column (4) computes TUT effects for the subgroup of borrowers who responded to the two questions needed to compute our measure of present bias, while column (8) computes the TUT for the subgroup of borrowers who provided their age.
+% The bottom row of the table counts the number of borrowers in each category.
+% TUT estimates are quite stable across sub-groups and generally similar to the full-sample estimates.
+% Because standard errors increase as sample size falls, some of the sub-group estimates are not statistically significant.}
+% %\textit{Do file: } \texttt{tut_cond_survey.do}
+% \end{table}
+
+\section{ Main treatment effects: Additional material}
+
+\begin{figure}[H]
+
+    \begin{center}
+    \begin{subfigure}{0.6\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/determinants_choose_commitment.pdf}
+    \end{subfigure}
+    \end{center}
+\caption{Determinants of choice.
+The above figure shows the determinants in a bivariate and multivariate OLS regression of choosing commitment.
+Choice commitment is a binary variable equal to one, whenever subjects choose the forced commitment contract in the choice arm.
 }
+    \label{determinants_choose}
+%\textit{Do file: } \texttt{determinants_choice.do}       
 \end{figure}
 
-\begin{table}[!htb]
-\caption{Balance conditional on survey response and question-by-question response rates by treatment arm}
-\label{SS_cond_survet}
-\begin{center}
-\scriptsize{\input{./Tables/SS_cond_survey.tex}}
-\end{center}
-\legend{ Panel A of this table presents the same information as Panel A of Table \ref{SS}, but restricts attention to the subsample of borrowers who answered at least one question in our baseline survey.
-Conditional on survey response, loan amount and weekday are balanced across treatment arms.
-Panel B presents response rates to each individual survey question across treatment arms, along with p-values for the F-test of no difference in response rates across survey arms.
-This panel uses data for borrowers who pawned on the same day as their survey response.
-}
-
-%\textit{Do file: } \texttt{ss\_att.do}
-\end{table}
+\subsection{Intermediate Outcomes}
 
 \begin{landscape}
-\begin{table}[!htb]
-\caption{Survey Non-response: TUT estimates for respondents to each survey question.}
-\label{TUT_cond_survet}
-\begin{center}
-\scriptsize{\input{./Tables/tut_cond_survey.tex}}
-\end{center}
-\legend{ Some borrowers did not respond to our survey; others only completed part of the survey.
-This table computes the TUT effect for a number of sub-groups by survey response, and compares them against the overall TUT effect.
-The top panel uses financial cost as the outcome variable, while the bottom panel uses APR.
-Each group is defined by the borrowers who responded to a particular \emph{subset} of the survey questions. 
-For example, column (4) computes TUT effects for the subgroup of borrowers who responded to the two questions needed to compute our measure of present bias, while column (8) computes the TUT for the subgroup of borrowers who provided their age.
-The bottom row of the table counts the number of borrowers in each category.
-TUT estimates are quite stable across sub-groups and generally similar to the full-sample estimates.
-Because standard errors increase as sample size falls, some of the sub-group estimates are not statistically significant.}
-%\textit{Do file: } \texttt{tut_cond_survey.do}
+
+\begin{table}[!h]
+\caption{Effects on intermediate outcomes}
+\label{mechanisms}
+\begin{center}
+
+\scriptsize{\input{./Tables/mechanism.tex}}
+
+\end{center}
+\legend{This table explores treatment effects in ``intermediate variables''.
+Each column represents regression output for different dependent variables following equation (\ref{basic_reg}).
+Panel A focuses on variables related to the speed of payment.
+While Panel B focuses on variables related to default, and Panel C related to visits.
+% The outcome variables are as follows:  number of days elapsed between origination and first payment (col 1); percentage of the loan paid in the first payment (col 2); probability of recovery in the first visit (col 3); loan duration is the number of days the borrower took to payoff her loan for those that recover, the number of days until default for those that default, and the maximum number of days we observe them in the sample for those that have not recovered or defaulted (col 4); loan duration conditional on recovery; an indicator for paying a positive amount towards recovery but nonetheless losing the pawn (col 6); the percentage or the loan paid, conditional on defaulting --`wasted payments' (col 7).
+Column 8 uses the phrase `selling the pawn' for a dummy variable indicating the borrower did not pay any amount towards recovery and lost the pawn.
+Moreover, (col 9) shows that treatment effects are concentrated in the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery.
+The dependent variable in column 10 is the number of day-visits to the branch (measured by the existence of transactions that day associated with our particular pawn), while column 11 conditions on borrowers that lost the pawn.
+Each regression includes branch and day-of-week FE. Standard errors are clustered at the branch-day level.}
+%\textit{Do file: } \texttt{mechanisms.do}
 \end{table}
@@
 
-\section{Main treatment effects: Additional material}
-
-\begin{landscape}
-\subsection{Multiple loans}
-
-\begin{table}[!htb]
-\caption{Multiple-loans robustness check}
-\label{multiple_loans}
-\begin{center}
-\scriptsize{\input{./Tables/multiple_loans.tex}}
-\end{center}
- \legend{ An additional empirical issue generated by repeat pawning is the question of how to handle the treatment status of those who take multiple loans within the experiment.
-43\% of borrowers take more than one loan within the study period, and 19\% are assigned multiple treatment statuses on their different loans.
-The issue of sequential endogenous treatments has been extensively studied in the context of school lotteries, where the convention is to use the treatment status from the first exposure (ITT) \citep{cullen2006effect, abdulkadirouglu2011accountability}.\\
- This table provides robustness for our main results for different ways to handling the multiplicity of loans.
-Columns 1-4 repeat the main analysis of financial cost and APR using the baseline approach from our main results,i.e.
-it only considers the first visit, while allowing multiple loans for the same-day.
-Columns 5-8 considers all loans including dummies for the order of pawns for an individual, essentially making the identification within-order.
-Columns 9-12 pursue the ITT strategy of always assigning the first treatment status to all subsequent pawns.
-The core treatment effects are robust to any of these ways of handling repeat pawning.
-}
-
-%\textit{Do file: } \texttt{multiple\_loans.do}
-\end{table}
-
-\end{landscape}
-
-\begin{figure}[!htb]
-    \caption{Determinants of choice}
-    \label{determinants_choose}
-    \begin{center}
-    \begin{subfigure}{0.5\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/determinants_choose_commitment.pdf}
-    \end{subfigure}
-    \end{center}
-      \legend{  The above figure shows the determinants in a bivariate and multivariate OLS regression of choosing commitment.
-Choice commitment is a binary variable equal to one, whenever subjects choose the forced commitment contract in the choice arm.
-}
-%\textit{Do file: } \texttt{determinants_choice.do}       
-\end{figure}
-
-\vspace{.2in}
-\begin{figure}[!htb]
-    \caption{Histogram of payments}
-    \label{hist_payments}
-    \begin{center}
-    \begin{subfigure}{0.32\textwidth}
-        \caption{Status-quo}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_payments_sq.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.32\textwidth}
-        \caption{Forced commitment}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_payments_fc.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.32\textwidth}
-        \caption{Choice commitment}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_payments_cc.pdf}
-    \end{subfigure}    
-    \end{center}
-     \legend{ This figure shows the schedule of payments for each treatment arm.
-In other words it records the time after the loan origination when the borrower makes a payment toward recovery of the pawn.
-We can see that for both the Forced commitment and Choice commitment arm, payments are bunching at the 30 and 60 days, while most payments are done around the due date of the loan (90 days).}
-
-      %\footnotesize{ \textit{Do file: }  \texttt{hist\_payments.do}}
-\end{figure}
-
 \subsection{Censoring} \label{App_censoring}
@@
 For these loans, we do not know whether the borrower ultimately defaulted or recovered her pawn.
-In this appendix, we show that our main results are robust to different ways of addressing censoring.
-
-Our main results, presented above, make no assumption on the default/recovery status of this loans.
-However, we compute the Financial Cost \& APR considering all the payments done so far.
-We now consider some alternative approaches.
-\\
+We have also shown that one effect of the forcing arm is to accelerate repayment, meaning that it is less likely for loans in this arm to be censored.
+This issue is illustrated in Figure \ref{survival_graph}, which shows the CDF of loan completion (either default or recovery in Panel (a)) and loan recovery (Panel (b)) by the number of days since first pawn.
+Two features of these graphs are salient for our analysis.
+The first is the extent to which loan outcomes are observed more quickly in the forced commitment arm.
+This is primarily due to the substantially higher rate of repayment of Forced Commitment loans at 120 days (15 pp higher than the other arms).
+The second is the very low rate at which loans are recovered in any arm after 120 days.
+In the 180-320 day window loans are largely dormant, suggesting that many of the censored loans will in fact end in default.
+
+The confluence of censoring and a treatment effect on censoring is potentially problematic from an experimental point of view.
+The approach taken in the headline results is a conservative one in that it inherently assumes that all of the loans outstanding at the end of the observation window will be repaid, making it so that the acceleration of payment observed in the Forced arm does not translate mechanically into the that treatment decreasing default.
+Nonetheless, to be certain that this issue is not driving our results we conduct a bounding exercise to understand how large the effects of this problem can possibly be.
 
 One way of considering the effect that this issue could have on our results is to make extreme assumptions about the outcome of these loans in the treatment and control so as to bound the possible influence of censoring.
-In Table \ref{bounding_censoring} we compare the Forced and Control arms, making the bracketing assumptions about repayment on censored loans.
-Panel A assumes all censored loans are repaid, and Panel D that all default.
-Because forced commitment causes borrowers to make payments earlier than they otherwise would have, In Panel A we make a conservative assumption.
-To see why, suppose for the sake of argument that commitment affects payment timing, but does not not default.
-In other words, suppose that treatment makes censoring \emph{less likely} but has no effect on uncensored outcomes. 
-If we were to treat all outstanding loans as defaults--the opposite of our convention--this would artificially inflate the rate of default among control loans relative to treatment loans.
-
-Panel B provides the lower bound for the treatment effect by assuming censored control loans are always repaid and treatment loans never are, and Panel C the upper bound by making the reverse assumption.
+In Table \ref{bounding_censoring} we compare the Forced and Control arms, bounding the censoring issue by reversing assumptions about the outcome of censored loans in the treatment versus the control.
+Panel B provides the lower bound for the treatment effect (closest to zero) by assuming censored control loans are always repaid and treatment loans never are; even in this lower-bound case the treatment effect is cost-reducing and significant at the 1\% significance level and indeed the magnitude of this lower bound estimate is only 6\% closer to zero than our headline result.
+Panel C estimates the upper bound by making the reverse assumption.
 Comfortingly, even with these extreme assumptions the significance on the main treatment effects never flips and treatment effects on financial cost and interests payments remain negative and significant in all scenarios.
@@
 
-Finally, Panel E of this table conducts a lasso logit prediction model that uses all of the available information on loans that were completed to predict the outcome of loans that were not.
-This is a best guess of the outcome on censored loans.
+Finally, Panel E of this table conducts a logit prediction model that uses all of the available information on loans that were completed to predict the outcome of loans that were not.
+This is a ``best guess'' of the outcome on censored loans.
 Using this prediction, we replicate the main experimental results and find that the treatment effect on financial cost increases from -204 (main results) to -264 (censored loans predicted), and the APR from -11\% to -17\%.
-Hence, while the censoring issue does have a substantial influence on the magnitude of our estimated treatment effects, these  checks confirm that a) the core results are robust to censoring, and b) the headline approach that we take to the issue is conservative and is likely understating the true magnitude of impacts.
-
-\begin{table}[!htb]
+Hence, while the censoring issue does have an effect on the magnitude of our estimated treatment effects, these  checks confirm that (a) the core results are fully robust to censoring, and (b) the headline approach that we take to the issue is conservative and likely understates the true magnitude of impacts.
+
+\begin{table}[H]
 \caption{Bounding censoring} 
@@
 \begin{center}
-\resizebox{0.9\textwidth}{!}{
+\resizebox{0.75\textwidth}{!}{
 \scriptsize{\input{./Tables/censoring_imp.tex}}
@@
 \end{center}
+
+\end{table}
 
@@
  Note that in all panels we maintain significant results for Financial Cost as dependent variable, while only in the most conservative scenario (Panel B) we lose significance for the APR outcome. }
- \end{table}
-
-\begin{figure}[!htb]
-        \caption{Interpolation on bounding censoring}
-    \label{interpolation_censoring_imp}
-    \begin{center}
-   \begin{subfigure}{0.49\textwidth}
-   \caption{Significance area for APR}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/frontera_sig_apr.pdf}
-    \end{subfigure}     
-    \begin{subfigure}{0.49\textwidth}
-   \caption{Significance area for Default }
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/frontera_sig_def_imp.pdf}
-    \end{subfigure} 
-    \end{center}
-     \legend{  The next figure aims to answer the following question: For how many loans in the control arm can we impute recovery, and for how many in the treatment arm can we impute default and still have significance?
-     This figure shows exactly the boundary separating significance when we vary the percentage of imputed censored loans with recovery and default respectively for control and treatment.
+
+% \begin{figure}[H]
+
+%     \begin{center}
+%    % \begin{subfigure}{0.49\textwidth}
+%    % \caption{Significance area for APR}
+%    %      \centering
+%    %      \includegraphics[width=\textwidth]{Figuras/frontera_sig_apr.pdf}
+%    %  \end{subfigure}     
+%    %  \begin{subfigure}{0.49\textwidth}
+%    % \caption{Significance area for Default }
+%         \centering
+%         \includegraphics[width=0.5\textwidth]{Figuras/frontera_sig_def_imp.pdf}
+%     % \end{subfigure} 
+%     \end{center}
+%  \caption{Interpolation on bounding censoring for Default.
+This figure aims to answer the following question: For how many loans in the control arm can we impute recovery, and for how many in the treatment arm can we impute default and still have significance?
+%      This figure shows exactly the boundary separating significance when we vary the percentage of imputed censored loans with recovery and default respectively for control and treatment.
 Each corner in the square will correspond to one of the panels from the Table \ref{bounding_censoring}.
@@
 The `x' indicates the proportions imputed by the lasso logit model, and the different lines correspond to setting different significance levels.
-We do not include the plot for financial cost, since for any imputation we still have significant results.}
-
-     %\textit{Do file: }  \texttt{interpolation_censoring_imp.do}
-\end{figure}
-
-\begin{figure}[!htb]
-        \caption{Survival graph}
-    \label{survival_graph}
+We do not include the plot for APR nor financial cost, since for any imputation we still have significant results.}
+%  \label{interpolation_censoring_imp}
+%      %\textit{Do file: }  \texttt{interpolation_censoring_imp.do}
+% \end{figure}
+
+\begin{figure}[H]
     \begin{center}
@@
     \end{center}
-     \legend{  This Figure shows the CDF of loan completion either default or recovery in Panel (a), or loan recovery in Panel (b), by the number of days since first pawn.}
+      \caption{Survival graph. This Figure shows the CDF of loan completion either default or recovery in Panel (a), or loan recovery in Panel (b), by the number of days since first pawn.}
+      \label{survival_graph}
      %\textit{Do file: }  \texttt{survival\_graph.do}
@@
 
-\begin{figure}[!htb]
-        \caption{\% of payment over time}
-    \label{porc_payment_over_time}
-    \begin{center}
-   \begin{subfigure}{0.49\textwidth}
-        \caption{Unconditional}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/cumulative_porc_pay_time.pdf}
-    \end{subfigure} 
-   \begin{subfigure}{0.49\textwidth}
-        \caption{Conditional on default}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/cumulative_porc_pay_time_default.pdf}
-    \end{subfigure}     
-    \end{center}
-     \legend{  This Figure shows the accumulated percentage of recovery in time by treatment arm. }
-     %\textit{Do file: }  \texttt{cumulative\_porc\_pay\_time.do}
-\end{figure}
-
-\section{Alternative explanations}
-
+% \begin{figure}[H]
+%     \begin{center}
+%    \begin{subfigure}{0.49\textwidth}
+%         \caption{Unconditional}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/cumulative_porc_pay_time.pdf}
+%     \end{subfigure} 
+%    \begin{subfigure}{0.49\textwidth}
+%         \caption{Conditional on default}
+%         \centering
+%         \includegraphics[width=\textwidth]{Figuras/cumulative_porc_pay_time_default.pdf}
+%     \end{subfigure}     
+%     \end{center}
+%     \caption{\% of payment over time. This Figure shows the accumulated percentage of recovery in time by treatment arm. }
+%     \label{porc_payment_over_time}
+%      %\textit{Do file: }  \texttt{cumulative\_porc\_pay\_time.do}
+% \end{figure}
+
+\subsection{Robustness accounting for other costs}
+
+\begin{table}[!h]
+\caption{Effects on more comprehensive cost measures}
+\label{table_robustness_fc}
+\begin{center}
+\resizebox{0.9\textwidth}{!}{
+\scriptsize{\input{./Tables/fc_robustness.tex}}
+}
+\end{center}
+ \legend{ This table augments the measure of financial cost presented in Table \ref{main_impact_table} with measures of transaction costs, subjective costs, and adjustments for liquidity costs.
+Panel A reports financial cost in pesos, while Panel B shows APR.
+Columns (1) and (6) replicate our previous results for comparability.
+Columns (2) and (7) of Table \ref{table_robustness_fc} use the subjective value of the pawn reported by the borrower rather than its appraised value.
+Columns (3) and (8) adjust for self-reported transport costs per visit plus an entire day's wage, both multiplied by the number of visits that each individual made.\footnote{For clients who did not complete the individual survey, we adjust using the mean self-reported transport cost among respondents of the respective branch.} Columns (4) and (9) adjust to consider the liquidity cost.
+Finally, columns (5) and (10) include all three changes together.
+The main takeaway from the table is that results are quite robust to including a much expanded measure of costs.
+Each regression includes branch and day-of-week FE.
+Standard errors are clustered at the branch-day level.}
+%\textit{Do file: } \texttt{fc\_robustness.do}
+\end{table}
+
+\newpage
+
+\section{ Alternative explanations}
 \subsection{Learning}
@@
 
-\begin{table}[!htb]
+\begin{table}[H]
         \caption{Effect of Prior Assignment on Subsequent Choice}
@@
 \end{center}
- \legend{ Column (1) reports results for the 228 borrowers who returned to pawn again at a day/branch that was randomly assigned to the choice arm, enabling us to observe whether they chose commitment or the status quo contract.
+ \legend{Column (1) reports results for the 228 borrowers who returned to pawn again at a day/branch that was randomly assigned to the choice arm, enabling us to observe whether they chose commitment or the status quo contract.
 Each row presents a difference in mean commitment take-up rates and associated standard errors.
@@
 
-\begin{figure}[!htb]
-        \caption{Financial benefit TUT effect for different discount rates}
-    \label{fc_discount_rates}
+\vspace{-.3in}
+\begin{figure}[!h]
+
     \begin{center}
@@
     \end{center}
-     \legend{ This Figure re-estimates the treatment on the untreated (TUT) effect from Table \ref{tot_tut}, introducing a daily discount factor in the definition of financial benefit.
-The discount factor reflects time preference, i.e.\ the fact that payments made in the present are more costly for the borrower.
+      \caption{Financial benefit TUT effect for different discount rates.
+This Figure re-estimates the treatment on the untreated (TUT) effect from Table \ref{tot_tut}, introducing a daily discount factor in the definition of financial benefit.
 At a given annual discount rate in percentage points (x-axis) the solid line gives the adjusted TUT and the shaded regions 90\% \& 95\% confidence bands.
 A discount factor of one corresponds to the estimate from Table \ref{tot_tut}.
-For higher discount rates, the adjusted financial cost will be higher, so the financial cost \emph{savings} will be lower.
 As seen from the figure, borrowers would need to face unrealistically large discount rates to reverse our headline result of a large, positive, and statistically significant TUT effect.}
+        \label{fc_discount_rates}
      %It estimates the effect of the treatment arms  for different discount factors, where a discount factor of 1 corresponds exactly to the estimate of column 1 of Table \ref{main_impact_table}.
@@
 
+\subsection{Present Bias}\label{App_presentbias}
+
+\noindent \textbf{Present bias.} If the benefits of commitment among non-choosers cannot be explained by standard models of rational choice, the canonical behavioral story would center on time inconsistency.
+While commitment is useful to anyone with hyperbolic time preferences, only those who are sophisticated--i.e.\ aware that they are hyperbolic discounters--will demand it.
+A large share of ``na\"ive'' hyperbolics in the population--borrowers who are unaware that they are hyperbolic discounters--could therefore drive a large and positive $\text{TUT}$.
+Our baseline survey included standard questions about discount rates between today and a month in the future versus discount rates between three and four months in the future.
+This allows us to classify borrowers who display more impatience over immediate delays as present biased.
+This measure of financial hyperbolicity is widely used in survey research, although it is not without problems.\footnote{Our measure is dichotomous, and it is not incentivized.
+Recent empirical work has shown the superiority of more elaborate measures such as ``convex time budgets'' \citep{andreoni2015measuring} while questioning the interpretation of measures of hyperbolicity that are not based on consumption \citep{andreoni2012estimating, cohen2020measuring}, suggesting that real effort tasks provide a better measure \citep{augenblick2015working}.
+Given that we had only a few minutes to interview real pawnshop clients prior to a commercial transaction, our simple measure was a necessary compromise.}
+
+If we could perfectly measure present bias and sophistication, we could divide the sample into three groups: sophisticated hyperbolics (who chose commitment), time-consistent non-choosers (for whom forcing will not be effective), and na\"{i}ve hyperbolic non-choosers (who will benefit from forced commitment).
+%If present bias fully explains the low take-up rate of voluntary commitment, we should find that the TUT for present-biased borrowers  is positive while the TUT for all other borrowers is not.
+If present bias fully explains the low take-up rate of voluntary commitment, we should find that the TUT for present-biased borrowers is positive.
+This is because among the group of non-takers, a comparison of present-biased borrowers against everyone else is a comparison of na\"{i}ve hyperbolics against time-consistent non-choosers.
+
+The left panel of Figure \ref{tut_beh_partition} carries out a feasible version of this exercise using our survey measure of present bias.
+The overall TUT estimate along with a 95\% confidence interval is given in blue.\footnote{For all borrowers who answered our present-bias survey questions.}
+The corresponding TUT estimate and confidence interval for present-biased borrowers identified with the survey question is given in green; results for all other borrowers are shown in red.
+The overall TUT is a weighted average of the impact in these two sub-groups.
+The TUT among the present biased is insignificant and less than half the size of the strongly significant TUT among those who are \textit{not} present biased.
+Therefore, taking our survey measure of hyperbolicity at face value, we find no indication that present-bias explains our positive estimated TUT.
+
+\begin{figure}
+    \begin{center}
+        \centering
+        \includegraphics[width=0.7\textwidth]{Figuras/tut_beh_partition.pdf} 
+    \end{center}
+     \scriptsize  
+\caption{Heterogeneity of the TUT by behavioral variables.
+Each panel in this figure shows how the estimated treatment on the untreated (TUT) effect varies with a binary survey variable $X_i$.
+In the left panel (P.B.), $X_i = 1$ if borrower $i$ is ``present-biased'' based on her responses to the time preference questions from our survey.
+In the right panel (Sure-confidence) $X_i = 1$ if  borrower $i$ reported that she was certain to recover her pawn, zero otherwise.
+}
+
+    \label{tut_beh_partition}
+      %\footnotesize{ \textit{Do file: }  \texttt{partition_tut.do}
+
+\end{figure}
 \subsection{Sure Confidence} \label{App_sureconfidence}
 
-\begin{figure}[!htb]
-    \caption{Determinants sure confidence}
+\begin{figure}[H]
+    \begin{center}
+    \begin{subfigure}{0.6\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/determinants_confidence_100.pdf}
+    \end{subfigure}
+    \end{center}
+    \caption{Determinants sure confidence.
+The above figure shows the determinants in a bivariate and multivariate OLS regression of sure confidence among the non-choosers.
+Sure confidence is a binary variable defined to be one when people report a 100\% probability of recovery.}
     \label{determinants_sure}
-    \begin{center}
-    \begin{subfigure}{0.5\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/determinants_confidence_100.pdf}
-    \end{subfigure}
-    \end{center}
-     \legend{ The above figure shows the determinants in a bivariate and multivariate OLS regression of sure confidence among the non-choosers.
-Sure confidence is a binary variable defined to be one when people report a 100\% probability of recovery.}
 %\textit{Do file: } \texttt{determinants_sure_confidence.do}       
@@
 
-\section{Heterogeneity and Bounds}
-
-\subsection{Testing for heterogeneity}
-\label{append:chernozhukov}
-If the treatment effects $Y_{i1} - Y_{i0}$ are constant across $i$, then we must have
-\[
-\text{ATE}(X_i) \equiv \mathbbm{E}[Y_{i1} - Y_{i0} |X_i] = \mathbbm{E}[Y_{i1} - Y_{i0}] \equiv \text{ATE}
-\]
-for any covariates $X_i$ that vary across $i$.
+%\section{ Heterogeneity and Bounds}
+\section{Bounds, FOSD and Rank Invariance} \label{bounds_FOSD}
+
+%\subsection{Testing for heterogeneity}
+%\label{append:chernozhukov}
+%If the treatment effects $Y_{i1} - Y_{i0}$ are constant across $i$, then we must have
+%\[
+%\text{ATE}(X_i) \equiv \mathbbm{E}[Y_{i1} - Y_{i0} |X_i] = \mathbbm{E}[Y_{i1} - Y_{i0}] \equiv \text{ATE}
+%\]
+%for any covariates $X_i$ that vary across $i$.
 If, on the other hand, $\text{ATE}(X_i)$ can be predicted using some scalar function $\tau(\cdot)$ of $X_i$, then the average treatment effect function is not constant so there must be treatment effect heterogeneity.
-
-We operationalize this idea using a two-step approach proposed by \cite{chernozhukov2018generic}.
+%
+%We operationalize this idea using a two-step approach proposed by \cite{chernozhukov2018generic}.
 We begin by randomly dividing the participants in the forced arms of the experiment ($Z_i \neq 2$) into two groups: a training set and a test set.
-These sets are constructed to ensure that all observations from a given branch-day cluster are allocated to the same set.
-This avoids inferential problems that could arise from correlated unobservables within clusters.
-In the first step, we apply the generalized random forest approach of \cite{atheygrf} to the training set to estimate two proxy predictors: $\psi(\cdot|\text{Training})$ approximates the untreated potential outcome function, $\mathbbm{E}[Y_{i0}|X_i] = \mathbbm{E}[Y_i|Z_i=0,X_i]$, while  $\tau(\cdot|\text{Training})$, approximates the ATE function
-\[
-\text{ATE}(X_i) = \mathbbm{E}[Y_i|Z_i=1,X_i] - \mathbbm{E}[Y_i|Z_i=0, X_i].
-\]
-The proxy predictors need not be unbiased or even consistent estimators of the functions they aim to approximate: the goal of this exercise is merely to find a scalar function of $X_i$ that \emph{accurately predicts} $\text{ATE}(X_i)$.
-In the second step we fit a linear regression model to data from the training set using regressors constructed from the proxy functions $\psi(\cdot|\text{Training})$ and $\tau(\cdot|\text{Training})$ constructed in the first step.
+%These sets are constructed to ensure that all observations from a given branch-day cluster are allocated to the same set.
+%This avoids inferential problems that could arise from correlated unobservables within clusters.
+%In the first step, we apply the generalized random forest approach of \cite{atheygrf} to the training set to estimate two proxy predictors: $\psi(\cdot|\text{Training})$ approximates the untreated potential outcome function, $\mathbbm{E}[Y_{i0}|X_i] = \mathbbm{E}[Y_i|Z_i=0,X_i]$, while  $\tau(\cdot|\text{Training})$, approximates the ATE function
+%\[
+%\text{ATE}(X_i) = \mathbbm{E}[Y_i|Z_i=1,X_i] - \mathbbm{E}[Y_i|Z_i=0, X_i].
+%\]
+%The proxy predictors need not be unbiased or even consistent estimators of the functions they aim to approximate: the goal of this exercise is merely to find a scalar function of $X_i$ that \emph{accurately predicts} $\text{ATE}(X_i)$.
+%In the second step we fit a linear regression model to data from the training set using regressors constructed from the proxy functions $\psi(\cdot|\text{Training})$ and $\tau(\cdot|\text{Training})$ constructed in the first step.
 In particular, we estimate
-\begin{equation}
-Y_i = \alpha_0 + \alpha_1 \psi_i + \beta_1 (Z_i - \mathbbm{E}[Z_i]) + \beta_2 (Z_i - \mathbbm{E}[Z_i])(\tau_i - \mathbbm{E}[\tau_i]) + \epsilon_i
-\label{eq:chernreg}
-\end{equation}
-where $\psi_i \equiv \psi(X_i|\text{Training})$ and $\tau_i \equiv \tau(X_i|\text{Training})$.\footnote{This is a slightly simpler regression than the one proposed in equation (3.1) of \cite{chernozhukov2018generic}, which involves propensity score weights.
+%\begin{equation}
+%Y_i = \alpha_0 + \alpha_1 \psi_i + \beta_1 (Z_i - \mathbbm{E}[Z_i]) + \beta_2 (Z_i - \mathbbm{E}[Z_i])(\tau_i - \mathbbm{E}[\tau_i]) + \epsilon_i
+%\label{eq:chernreg}
+%\end{equation}
+%where $\psi_i \equiv \psi(X_i|\text{Training})$ and $\tau_i \equiv \tau(X_i|\text{Training})$.\footnote{This is a slightly simpler regression than the one proposed in equation (3.1) of \cite{chernozhukov2018generic}, which involves propensity score weights.
 Because the random assignment of $Z$ in our experiment does \emph{not} condition on $X$, the propensity score weights in our case are constant over $X$ and hence drop out.} As shown by \cite{chernozhukov2018generic}, the coefficients $\beta_1$ and $\beta_2$ from \eqref{eq:chernreg} identify the \emph{best linear predictor} of the conditional ATE based on $\tau(\cdot|\text{Training})$, namely
-\[
-\beta_1 = \mathbbm{E}[\text{ATE}(X_i)] = \text{ATE}, \quad
-\beta_2 = \frac{\text{Cov}[\text{ATE}(X_i), \tau_i]}{\text{Var}(\tau_i)}.
-\]
-If treatment effects are homogeneous we must have $\beta_2 = 0$. Rejecting this hypothesis establishes that $\tau_i$ predicts $\text{ATE}(X_i)$ and hence that $\Delta_i$ varies. 
-Since $\tau_i$ and $\psi_i$ do not depend on the test set, inference for the regression in \eqref{eq:chernreg} is straightforward conditional on the Training/Test split.  
-Our estimate for $\beta_2$ is 2.56 with a one-sided heteroskedasticity-robust (HC3) standard error of 0.43.
-Thus we easily reject the null hypothesis of homogeneous treatment effects.
-
-\subsection{Bounds, FOSD and Rank Invariance} \label{bounds_FOSD}
-
-\begin{figure}[!htb]
-    \caption{Fan \& Park bounds for benefit in APR\%}
-    \label{fan_park_bounds}
-    \begin{center}
-    \begin{subfigure}{0.5\textwidth}
-        \caption{APR}
+%\[
+%\beta_1 = \mathbbm{E}[\text{ATE}(X_i)] = \text{ATE}, \quad
+%\beta_2 = \frac{\text{Cov}[\text{ATE}(X_i), \tau_i]}{\text{Var}(\tau_i)}.
+%\]
+%If treatment effects are homogeneous we must have $\beta_2 = 0$. Rejecting this hypothesis establishes that $\tau_i$ predicts $\text{ATE}(X_i)$ and hence that $\Delta_i$ varies. 
+%Since $\tau_i$ and $\psi_i$ do not depend on the test set, inference for the regression in \eqref{eq:chernreg} is straightforward conditional on the Training/Test split.  
+%Our estimate for $\beta_2$ is 2.56 with a one-sided heteroskedasticity-robust (HC3) standard error of 0.43.
+%Thus we easily reject the null hypothesis of homogeneous treatment effects.
+
+%\todo[inline]{Discuss the results here.}
+
+%\todo[inline]{Issac: re-run this exercise with removing the propensity score weights $p(Z)$. Presumably it shouldn't change anything, but it's simpler to explain what we do and probably less noisy}
+
+%\begin{table}[H]
+%\begin{center}
+%\scriptsize{\input{./Tables/test_calibration_2.tex}}
+%\end{center}
+%\end{table}
+
+%\todo[inline]{Some Questions for Issac: (1) How are we carrying out the sample splitting?
+If we cluster standard errors at the branch-day level, we should take this into account when we split.
+(2) How are you carrying out inference for $\beta_2$?
+Chernozhukov et al discuss two approaches: ``conditional'' and ``variational.'' The former is simpler as it conditions on the training/test split.
+The latter is a bit more involved, since one accounts for uncertainty arising from different splits.
+(3) What are the details of the random forest procedure employed here?
+(Tuning parameters choice, etc.) We should put them into the appendix.}
+
+%\newpage
+
+\begin{figure}[!h]
+
+    \begin{center}
+    \begin{subfigure}{0.55\textwidth}
+        \caption{APR Bounds}
         \centering
@@
     \end{center}
-        \legend{ This figure depicts the \cite{fan2010sharp} bounds on the distribution $F_\Delta$ of individual treatment effects $\Delta \equiv (Y_1 - Y_0)$, described in Section \ref{sec:bounds}, for the APR outcome.
+        \caption{Fan \& Park bounds for benefit in APR\%.
+This figure depicts the \cite{fan2010sharp} bounds on the distribution $F_\Delta$ of individual treatment effects $\Delta \equiv (Y_1 - Y_0)$, described in Section \ref{sec:bounds}, for the APR outcome.
     The dark red curve and light red shaded region give the estimated upper bound function $\overline{F}$ for $F_\Delta$ and associated (pointwise) 95\% confidence interval. 
     The dark blue curve and light blue shaded region give the estimated lower bound function $\underline{F}$ for $F_\Delta$ and associated (pointwise) 95\% confidence interval.
-    Confidence intervals are computed using the asymptotic distribution for the bounds. See \cite{fan2010sharp} for details.
-    The bounds are pointwise sharp: at any specified value of $\delta$ the bounds $\underline{F}(\delta) \leq F_\Delta(\delta) \leq \overline{F}(\delta)$ cannot be improved without imposing additional assumptions.
-    Evaluating the bounds at $\delta = 0$, we see that between 23\% and 97\% of borrowers have a positive individual treatment effect.
-    This is greater than the share of borrowers who chose commitment: 11\%.}
+    Confidence intervals are computed using the asymptotic distribution for the bounds.
+Evaluating the bounds at $\delta = 0$, we see that between 23\% and 97\% of borrowers have a positive individual treatment effect.}
+     \label{fan_park_bounds}
 %\textit{Do file: } \texttt{fan\_park\_bnds.do}       
@@
 
-\vspace{.2in}
-\begin{figure}[!htb]
-        \caption{Empirical CDF: Forced commitment vs Control FOSF}
-    \label{ecdf_fc}
+\begin{figure}
 
@@
         \centering
-         \includegraphics[width=\textwidth]{Figuras/cdf_apr.pdf}
+        \includegraphics[width=\textwidth]{Figuras/te_rankinvariance_apr.pdf}
     \end{subfigure} 
@@
         \centering
-        \includegraphics[width=\textwidth]{Figuras/cdf_fc_admin.pdf}
-    \end{subfigure} 
-    \end{center}
-   \legend{  This figure plots the empirical CDF of experimental outcomes separately for the control (status quo) in dashes, and forced commitment contracts (solid).
-In panel (a), the outcome is APR benefit; in panel (b) the outcome is Financial benefit.
-    The empirical CDF under forced commitment first-order stochastically dominates the empirical CDF under the status quo.
-This can be seen by examining the dotted line, which shows the difference $(\text{Control} - \text{Commitment})$.
-}
-    %The dotted line at the bottom of panels (a) and (b)   the empirical cumulative distribution function APR and financial cost of financial cost.
-It does this separately for the fee-forcing contract and for the status-quo contract.
-The dotted line at the bottom is the difference of the control CDF minus the forced CDF arm.
-It shows that the CDF of the status quo contract is always below that of the fee-forcing (and this difference is significant for the points indicated by the blue line).
-    % \texttt{fosd_ecdf.do}}
-\end{figure}
-
-\vspace{.2in}
-\begin{figure}[!htb]
-        \caption{Distribution of treatment effects under rank invariance.}
+        \includegraphics[width=\textwidth]{Figuras/te_rankinvariance_fc_admin.pdf}
+    \end{subfigure} 
+    \end{center}
+    \caption{Distribution of treatment effects under rank invariance.
+This figure shows the CDF of individual treatment effects under the assumption of rank invariance, computed from $F_\Delta(\delta) = \int_0^1 \mathbbm{1}\{ F_1^{-1}(u) - F_0^{-1}(u)\leq \delta\}\,\mathrm{d}u$ where $F_1^{-1}$ and $F_0^{-1}$ are the quantile functions of $Y_1$ and $Y_0$.}
 \label{te_rankinvariance}
-
-    \begin{center}
-       \begin{subfigure}{0.49\textwidth}
-        \caption{APR benefit}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/te_rankinvariance_apr.pdf}
-    \end{subfigure} 
-   \begin{subfigure}{0.49\textwidth}
-        \caption{Financial benefit}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/te_rankinvariance_fc_admin.pdf}
-    \end{subfigure} 
-    \end{center}
-    \legend{  This figure shows the CDF of individual treatment effects under the assumption of rank invariance, computed from 
-    \[F_\Delta(\delta) = \int_0^1 \mathbbm{1}\{ F_1^{-1}(u) - F_0^{-1}(u)\leq \delta\}\,\mathrm{d}u\]
-where $F_1^{-1}$ and $F_0^{-1}$ are the quantile functions of $Y_1$ and $Y_0$.}
     %The dotted line at the bottom of panels (a) and (b)   the empirical cumulative distribution function APR and financial cost of financial cost.
@@
 
-\section{Derivations for Section \ref{sec:randchoice}}
-\label{append:randchoice}
-
-This appendix provides proofs of the results described in Section \ref{sec:randchoice}, using the notation and assumptions described in Section \ref{sec:potentialOutcomes}. 
-To simplify the presentation, we omit $i$ subscripts throughout this section.
-We also use the shorthand $Z_0 \equiv \mathbbm{1}(Z=0)$, $Z_1 \equiv \mathbbm{1}(Z=1)$, and $Z_2 \equiv\mathbbm{1}(Z=2)$.
-For convenience, the following assumption collects our exclusion restriction and the key features of the constrained choice design.
-
-\begin{assumption}\mbox{}
-\label{assump:randchoice}
-   \begin{enumerate}[(i)]
-   \item $Z$ is independent of $(Y_{0}, Y_{1}, C)$
-   \item $D = \mathbbm{1}(Z \neq 2)Z + \mathbbm{1}(Z = 2)C$
-   \item $Y = \mathbbm{1}(Z = 0) Y_{0} + \mathbbm{1}(Z = 1) Y_{1} + \mathbbm{1}(Z = 2) [ (1 - C) Y_{0} + C Y_{1}]$
-   \end{enumerate}
-\end{assumption}
-
-\subsection{Point Identification}
-
-We first show that the TOT, TUT, ASB, and ASL effects are point identified under the constrained choice design.
-It follows that the ASG effect, $(\text{TOT} - \text{TUT})$, is likewise point identified.
-
-\begin{lem}
-Under Assumption \ref{assump:randchoice},
-\label{lem_randchoice}
-   \begin{enumerate}[(i)]
-       \item $\mathbbm{E}(D|Z=2) = \mathbb{P}(C=1)$
-       \item $\mathbbm{E}(Y|Z=0) = \mathbbm{E}(Y_0)$
-       \item $\mathbbm{E}(Y|Z=1) = \mathbbm{E}(Y_1)$
-       \item $\mathbbm{E}(Y|D=0,Z=2) = \mathbbm{E}(Y_0|C=0)$
-       \item $\mathbbm{E}(Y|D=1,Z=2) = \mathbbm{E}(Y_1|C=1)$.
-   \end{enumerate} 
-\end{lem}
-
-\begin{proof}
-Part (i) follows because $Z=2$ implies $D=C$ and $Z$ is independent of $C$.  
-Parts (ii) and (iii) follow similarly: given $Z=0$ we have $Y = Y_0$, given $Z=1$ we have $Y = Y_1$, and $Z$ is independent of $(Y_0,Y_1)$.
-For parts (iv) and (v), first note that Assumption \ref{assump:randchoice} (iii) implies that $Z$ is conditionally independent of $(Y_0,Y_1)$ given $C$.
-Now, $Z=2$ implies that $D=0$ if and only if $C=0$. Hence,
-\[
-\mathbbm{E}(Y|D=0, Z=2) = \mathbbm{E}(Y_0|D=0, Z=2) = \mathbbm{E}(Y_0|C=0, Z=2)=\mathbbm{E}(Y_0|C=0)
-\]
-establishing part (iv).
-For part (v) $Z=2$ implies that $D=1$ if and only if $C=1$ and hence
-\[
-\mathbbm{E}(Y|D=1, Z=2) = \mathbbm{E}(Y_1|D=1, Z=2) = \mathbbm{E}(Y_1|C=1, Z=2)= \mathbbm{E}(Y_1|C=1). %\qedhere
-\]
-\end{proof}
-
-\begin{prop} 
-Under Assumption \ref{assump:randchoice},
-    \begin{enumerate}[(i)]
-        \item $\text{TOT} \equiv \mathbbm{E}(Y_1 - Y_0|C=1)  = \displaystyle \frac{\mathbbm{E}(Y|Z=2) - \mathbbm{E}(Y|Z=0)}{\mathbbm{E}(D|Z=2)}$
-        \item $\text{TUT} \equiv \mathbbm{E}(Y_1 - Y_0|C=0) = \displaystyle \frac{\mathbbm{E}(Y|Z=1) - \mathbbm{E}(Y|Z=2)}{1 - \mathbbm{E}(D|Z=2)}$
-        \item $\text{ASB} \equiv \mathbbm{E}(Y_0|C=1) - \mathbbm{E}(Y_0|C=0) = \displaystyle \frac{\mathbbm{E}(Y|Z=0) - \mathbbm{E}(Y|Z=2,D=0)}{\mathbbm{E}(D|Z=2)}$
-        \item $\text{ASL} \equiv \mathbbm{E}(Y_1|C=1) - \mathbbm{E}(Y_1|C=0) = \displaystyle \frac{\mathbbm{E}(Y|Z=2,D=1) - \mathbbm{E}(Y|Z=1)}{1 - \mathbbm{E}(D|Z=2)}$.
-    \end{enumerate}
-\end{prop}
-
-\begin{proof}
-For parts (i) and (iii) we require an expression for $\mathbbm{E}(Y_0|C=1)$ in terms of the observables $(Y, D, Z)$.
-By Lemma \ref{lem_randchoice}(ii) and iterated expectations 
-\[
-\mathbbm{E}(Y|Z=0) = \mathbbm{E}(Y_0) = \mathbbm{E}(Y_0|C=0) \mathbbm{P}(C=0) + \mathbbm{E}(Y_0|C=1) \mathbbm{P}(C=1).
-\]
-Re-arranging and substituting Lemma \ref{lem_randchoice}(i) and (iv),
-\begin{align}
-\mathbbm{E}(Y_0|C=1)  &= \frac{\mathbbm{E}(Y|Z=0) - \mathbbm{E}(Y_0|C=0) \mathbbm{P}(C=0)}{\mathbbm{P}(C=1)}\nonumber\\ 
-&=  \frac{\mathbbm{E}(Y|Z=0) - \mathbbm{E}(Y|Z=2,D=0) \mathbbm{E}(1 - D|Z=2)}{\mathbbm{E}(D|Z=2)}.
-\label{eq:Y0C1}
-\end{align}
-Part (i) follows by combining \eqref{eq:Y0C1} with Lemma \ref{lem_randchoice}(v) and simplifying; part (iii) follows by combining \eqref{eq:Y0C1} with Lemma \ref{lem_randchoice}(iv) and simplifying.
-Similarly, for parts (ii) and (iv) we require an expression for $\mathbbm{E}(Y_1|C=0)$ in terms of observables.
-By Lemma \ref{lem_randchoice}(iii) and iterated expectations,
-\[
-\mathbbm{E}(Y|Z=1) = \mathbbm{E}(Y_1) = \mathbbm{E}(Y_1|C=0)\mathbbm{P}(C=0) + \mathbbm{E}(Y_1|C=1) \mathbbm{P}(C=1).
-\]
-Re-arranging and substituting Lemma \ref{lem_randchoice}(i) and (v),
-\begin{align}
-\mathbbm{E}(Y_1|C=0) 
-&= \frac{\mathbbm{E}(Y|Z=1) - \mathbbm{E}(Y_1|C=1)\mathbbm{P}(C=1)}{\mathbb{P}(D=0)} \nonumber\\
-&=\frac{\mathbbm{E}(Y|Z=1) - \mathbbm{E}(Y|Z=2,D=1)\mathbbm{E}(D|Z=2)}{\mathbb{E}(1-D|Z=2)}.
-\label{eq:Y1C0}
-\end{align}
-Part (ii) follows by combining \eqref{eq:Y1C0} with Lemma \ref{lem_randchoice}(iv) and simplifying; part (iv) follows by combining \eqref{eq:Y1C0} with Lemma \ref{lem_randchoice}(v) and simplifying.
-\end{proof}
-
-\subsection{Regression-based Estimation of TOT, TUT, ASG, ASL, and ASB}
-
-We now show how a collection of just-identified, linear IV regressions can be used to consistently estimate the ATE, TOT, and TUT effects, along with each of the ingredients needed to construct the ASL and ASB.
-These results are used below to provide a recipe for cluster-robust inference for the ASG, ASL, and ASB effects.
-The first result provides a regression-based approach to estimate the ATE and TOT.
-
-\begin{prop} 
-\label{prop:TOTreg}
-Under Assumption \ref{assump:randchoice},
-\[
-Y = \mathbbm{E}(Y_0) + \text{ATE}\times Z_1 + \text{TOT} \times Z_2 D + U
-\]
-where $\mathbb{E}(U|Z) = 0$.
-Therefore, under standard regularity conditions, an IV regression of $Y$ on an intercept, $Z_1$ and $Z_2 D$ with instruments $(1, Z_0, Z_1)$ provides a consistent estimator of the ATE and TOT effects.
-\end{prop}
-
-\begin{proof}
-By Assumption \ref{assump:randchoice} (iii),
-\begin{align*}
-Y &= Z_0 Y_0 + Z_1 Y_1 + Z_2[(1 - C) Y_0 + CY_1]\\
-&= (Z_0 + Z_2)Y_0 + Z_1 Y_1 + Z_2C(Y_1 - Y_0)\\
-&= (Z_0 + Z_1 + Z_2)Y_0 + Z_1 (Y_1 - Y_0) + Z_2D(Y_1 - Y_0)\\
-&= Y_0 + Z_1 (Y_1 - Y_0) + Z_2D(Y_1 - Y_0).
-\end{align*}
-since $Z_2 D = Z_2 C$ and $(Z_0 + Z_1 + Z_2) = 1$.
-Thus, defining 
-\[
-U \equiv [Y_0 - \mathbbm{E}(Y_0)] + Z_1[(Y_1 - Y_0) - \text{ATE}] + Z_2 D[(Y_1 - Y_0) - \text{TOT}]
-\]
-by construction we have
-\[
-Y = \mathbbm{E}(Y_0) + \text{ATE} \times Z_1 + \text{TOT} \times Z_2 D+ U.
-\]
-Now, since $Z_2 D = Z_2 C$ and $Z$ is independent of $(Y_1, Y_0)$ by Assumption \ref{assump:randchoice} (i), we have
-\begin{align*}
-\mathbbm{E}(U|Z) &= [\mathbbm{E}(Y_0|Z) - \mathbbm{E}(Y_0)]  + Z_1[\mathbbm{E}(Y_1 - Y_0|Z) - \text{ATE}] +  \mathbbm{E}\left[Z_2 D\left\{(Y_1 - Y_0) - \text{TOT}\right\}|Z\right]\\
-&= [\mathbbm{E}(Y_0) - \mathbbm{E}(Y_0)]  + Z_1[\mathbbm{E}(Y_1 - Y_0) - \text{ATE}] + Z_2 \mathbbm{E}\left[C\left\{(Y_1 - Y_0) - \text{TOT}\right\}|Z\right]\\
-&= Z_2 \mathbbm{E}\left[C\left\{(Y_1 - Y_0) - \text{TOT}\right\}|Z\right].
-\end{align*}
-Finally, by iterated expectations
-\begin{align*}
-\mathbbm{E}\left[C\left\{(Y_1 - Y_0) - \text{TOT}\right\}|Z\right] &=  \mathbbm{P}(C=1|Z) \left[\mathbbm{E}(Y_1 - Y_0|C=1,Z)  - \text{TOT}\right]\\
-&= \mathbbm{P}(C=1)\left[\mathbbm{E}(Y_1 - Y_0|C=1) - \text{TOT} \right]=0
-\end{align*}
-since $Z$ is conditionally independent of $(Y_0, Y_1)$ given $C$, an implication of \ref{assump:randchoice} (i).
-\end{proof}
-
-The next proposition provides regression-based estimates of the ATE and TUT.
-\begin{prop}
-\label{prop:TUTreg}
-Under Assumption \ref{assump:randchoice}
-\[
-Y = \mathbbm{E}(Y_1) + \text{ATE}\times -Z_0 + \text{TUT} \times -Z_2 (1 - D) + V
-\] 
-where $\mathbb{E}(V|Z) = 0$.
-Therefore, under standard regularity conditions, an IV regression of $Y$ on an intercept, $-Z_0$ and $-Z_2(1-D)$ with instruments $(1, Z_0, Z_1)$ provides consistent estimates of the ATE and TUT effects.
-\end{prop}
-
-\begin{proof}
-By Assumption \ref{assump:randchoice} (iii),
-\begin{align*}
-Y &= Z_0 Y_0 + Z_1 Y_1 + Z_2[(1 - C) Y_0 + CY_1]\\
-&= Z_0 Y_0 + Z_1 Y_1 + Z_2[(1 - C) (Y_0 - Y_1) + Y_1]\\
-&= Z_0 Y_0 + (Z_1 + Z_2) Y_1 + Z_2(1 - C) (Y_0 - Y_1) \\
-&= Z_0 Y_0 + (1 - Z_0) Y_1 + Z_2(1 - D) (Y_0 - Y_1) \\
-&= Y_1 - Z_0 (Y_1 - Y_0) - Z_2(1 - D) (Y_1 - Y_0)
-\end{align*}
-since $Z_2(1 - C)= Z_2(1 - D)$ and $(Z_1 + Z_2) = 1 - Z_0$.
-Thus, defining 
-\[
-V \equiv [Y_1 - \mathbb{E}(Y_1)] - Z_0[(Y_1 - Y_0) - \text{ATE}] - Z_2(1 - D)[(Y_1 - Y_0) - \text{TUT}]
-\]
-by construction we have
-\[
-Y = \mathbb{E}(Y_1) + \text{ATE} \times -Z_0 + \text{TUT} \times -Z_2(1 - D) + V.
-\]
-Now, since $Z_2(1 - D) = Z_2 (1 - C)$ and $Z$ is independent of $(Y_0, Y_1)$ by Assumption \ref{assump:randchoice} (i),
-\begin{align*}
-\mathbb{E}(V|Z) &= [\mathbb{E}(Y_1|Z) - \mathbb{E}(Y_1)] - Z_0[\mathbb{E}(Y_1 - Y_0|Z) - \text{ATE}] - \mathbb{E}[Z_2(1 - D)\left\{(Y_1 - Y_0) - \text{TUT}\right\}|Z]\\
-&= [\mathbb{E}(Y_1) - \mathbb{E}(Y_1)] - Z_0[\mathbb{E}(Y_1 - Y_0) - \text{ATE}] - Z_2\mathbb{E}[(1 - C)\left\{(Y_1 - Y_0) - \text{TUT}\right\}|Z]\\
-&= -Z_2\mathbb{E}[(1 - C)\left\{(Y_1 - Y_0) - \text{TUT}\right\}|Z].
-\end{align*}
-Finally, by iterated expectations,
-\begin{align*}
-\mathbb{E}[(1 - C)\left\{(Y_1 - Y_0) - \text{TUT}\right\}|Z]&= \mathbb{P}(C=0|Z)\left[ \mathbb{E}(Y_1 - Y_0|C=0, Z) - \text{TUT}\right]\\
-&= \mathbb{P}(C=0|Z) \left[ \mathbb{E}(Y_1 - Y_0|C=0) - \text{TUT}\right] = 0
-\end{align*}
-since $Z$ is conditionally independent of $(Y_0, Y_1)$ given $C$, an implication of Assumption \ref{assump:randchoice} (i).
-\end{proof}
-
-Since $\text{ASG} = \text{TOT} - \text{TUT}$, the preceding two propositions provide consistent estimates of $\text{ASG}$ effect.
-The $\text{ASB}$ effect, $\mathbbm{E}(Y_0|C=1) - \mathbb{E}(Y_0|C=0)$, can likewise be estimated by taking the difference of coefficients across two linear IV regressions, as shown in the following proposition.
-
-\begin{prop}
-\label{prop:ASBreg}
-Under Assumption \ref{assump:randchoice}
-\begin{align}
-\label{eq:ASB0}
-    (1 - D) Y &= \mathbbm{E}(Y_{0}) \times Z_0 + \mathbbm{E}(Y_{0}|C=0) \times (1 - D)Z_2 + U_{0}\\
-\label{eq:ASB1}
-    (1 - D) Y &= \mathbbm{E}(Y_{0}) \times(Z_0 + Z_2) + \mathbbm{E}(Y_{0}|C=1)\times -DZ_2 + U_{1}
-\end{align}
-where $\mathbbm{E}(U_0|Z) = \mathbbm{E}(U_1|Z) = 0$.
-Thus, under standard regularity conditions, an IV regression of $(1 - D)Y$ on $Z_0$ and $(1 - D)Z_2$ with instruments $(Z_0, Z_2)$ and no intercept provides consistent estimates of $\mathbb{E}(Y_0)$ and $\mathbb{E}(Y_0|C=0)$.
-Similarly, an IV regression of $(1 - D)Y$ on $(Z_0 + Z_2)$ and $-DZ_2$ with instruments $(Z_0, Z_2)$ and no intercept provides consistent estimates of $\mathbb{E}(Y_0)$ and $\mathbb{E}(Y_0|C=1)$.
-\end{prop}
-
-\begin{proof}
-Assumption \ref{assump:randchoice} (ii) implies $(1 - D) = Z_0 + Z_2(1 - C)$. Hence, by Assumption \ref{assump:randchoice} (iii),
-\begin{align*}
-(1 - D)Y &=  [Z_0 + Z_2 (1 - C)]\left\{Z_0 Y_0 + Z_1 Y_1 + Z_2[(1 - C) Y_0 + CY_1]\right\}\\
-&= Z_0 Y_0 + Z_2 (1 - C) [(1 - C) Y_0 + C Y_1]\\
-&= Z_0 Y_0 + Z_2 (1 - C) Y_0.
-\end{align*}
-because $Z_j^2 = Z_j$ for any $j$ and $Z_j Z_k = 0$ for any $j \neq k$ and, similarly, $(1 - C)^2 = (1 - C)$ and $C (1 - C) = 0$.
-Therefore, since $Z_2 (1 - C) = Z_2 (1 - D)$,
-\begin{align*}
-(1 - D)Y &= Z_0 Y_0 + Z_2 (1 - D) Y_0\\
-(1 - D)Y &= (Z_0 + Z_2) Y_0 + (-DZ_2) Y_0. 
-\end{align*}
-Now, defining
-\begin{align*}
-U_0 &\equiv Z_0 [Y_0 - \mathbbm{E}(Y_0)] + Z_2(1 - D)[Y_0 - \mathbbm{E}(Y_0|C=0)]\\
-U_1 &\equiv (Z_0 + Z_2)[Y_0 - \mathbbm{E}(Y_0)] + (-Z_2 D)[Y_0 - \mathbbm{E}(Y_0|C=1)]
-\end{align*}
-by construction, we have
-\begin{align*}
-Y &= \mathbbm{E}(Y_0) \times Z_0 + \mathbbm{E}(Y_0|C=0) \times Z_2(1 - D) + U_0\\
-Y &= \mathbbm{E}(Y_0) \times (Z_0 + Z_2)+ \mathbbm{E}(Y_0|C=1) (-Z_2D) + U_1.
-\end{align*}
-Finally, since $Z_2(1-D) = Z_2(1 - C)$, and $Z$ is independent of $Y_0$,  
-\begin{align*}
-\mathbbm{E}(U_0|Z) &= Z_0[\mathbbm{E}(Y_0|Z) - \mathbbm{E}(Y_0)] + Z_2\mathbbm{E}\{(1 - C) [Y_0 - \mathbbm{E}(Y_0|C=0) |Z\}\\
-&= Z_2 \mathbbm{E}[Y_0 - \mathbbm{E}(Y_0|C=0) | C = 0, Z] = 0
-\end{align*}
-where the final two steps follow by iterated expectations and the fact that  $Z$ is conditionally independent of $Y_0$ given $C$. 
-Since $Z_2 D = Z_2 C$, a nearly identical argument gives
-\begin{align*}
-\mathbbm{E}(U_1|Z) &= (Z_0 + Z_2)[Y_0 - \mathbbm{E}(Y_0|Z)] -Z_2\mathbbm{E}\{C [Y_0 - \mathbbm{E}(Y_0|C=1) |Z\}\\
-&= -Z_2 \mathbbm{E}[Y_0 - \mathbbm{E}(Y_0|C=0) | C = 1, Z] = 0. \qedhere
-\end{align*}
-\end{proof}
-
-The next results shows that the $\text{ASL}$ effect, $\mathbbm{E}(Y_1|C=1) - \mathbb{E}(Y_1|C=0)$, can be estimated as the difference of coefficients across two linear IV regressions, as shown in the following proposition.
-
-\begin{prop}
-\label{prop:ASLreg}
-Under Assumption \ref{assump:randchoice},
-\begin{align}
-\label{eq:ASL0}
-    D Y &= \mathbbm{E}(Y_{1}) \times(Z_1 + Z_2) + \mathbbm{E}(Y_{1}|C=0)\times (D - 1)Z_2 + V_{0}\\
-\label{eq:ASL1}
-    D Y &= \mathbbm{E}(Y_{1}) \times Z_1 + \mathbbm{E}(Y_{1}|C=1)\times D Z_2+ V_{1}
-\end{align}
-where $\mathbbm{E}(V_0|Z) = \mathbbm{E}(V_1|Z) = 0$.
-Thus, under standard regularity conditions, an IV regression of $DY$ on $(Z_1 + Z_2)$ and $-Z_2(1 - D)$ with instruments $(Z_1, Z_2)$ and no intercept provides consistent estimates of $\mathbb{E}(Y_1)$ and $\mathbb{E}(Y_1|C=1)$.
-Similarly, an IV regression of $DY$ on $Z_1$ and $DZ_2$ with instruments $(Z_1, Z_2)$ and no intercept provides consistent estimates of $\mathbb{E}(Y_1)$ and $\mathbb{E}(Y_1|C=1)$. 
-\end{prop}
-
-\begin{proof}
-By Assumption \ref{assump:randchoice}, $D = Z_1 + Z_2 C$. Hence, by Assumption \ref{assump:randchoice} (iii),
-\begin{align*}
-DY &=  (Z_1 + Z_2 C)\left\{Z_0 Y_0 + Z_1 Y_1 + Z_2[(1 - C) Y_0 + CY_1]\right\}\\
-&= Z_1 Y_1 + Z_2 C[(1 -C) Y_0 + C Y_1]\\
-&= Z_1 Y_1 + Z_2 C Y_1
-\end{align*}
-because $Z_j^2 = Z_j$ for any $j$ and $Z_j Z_k = 0$ for any $j \neq k$ and, similarly, $(1 - C)^2 = (1 - C)$ and $C (1 - C) = 0$. Therefore, since $Z_2 (1 - C) = Z_2 (1 - D)$,
-\begin{align*}
- DY &= (Z_1 + Z_2)Y_1 + Z_2 (D - 1) Y_1\\
- DY &= Z_1 Y_1 + Z_2 D Y_1.
-\end{align*}
-Now, defining
-\begin{align*}
-V_0 &= (Z_1 + Z_2)[Y_1 - \mathbbm{E}(Y_1)] + Z_2(D - 1)[Y_1 - \mathbbm{E}(Y_1|C=0)]\\
-V_1 &= Z_1[Y_1 - \mathbbm{E}(Y_1)] + Z_2D[Y_1 - \mathbbm{E}(Y_1|C=1)]
-\end{align*}
-by construction we have
-\begin{align*}
-Y &= \mathbbm{E}(Y_1) \times (Z_1 + Z_2) + \mathbbm{E}(Y_1 | C = 0) \times Z_2 (D - 1) + V_0\\
-Y &= \mathbbm{E}(Y_1) \times Z_1 + \mathbbm{E}(Y_1 | C = 1) \times Z_2 D + V _1.
-\end{align*}
-Finally, since $Z_2(1 - D) = Z_2(1 - C)$ and $Z$ is independent of $Y_1$,
-\begin{align*}
-\mathbbm{E}(V_0|Z) &= (Z_1 + Z_2) [\mathbbm{E}(Y_1|Z) - \mathbbm{E}(Y_1) ]  - Z_2 \mathbbm{E}\{(1 - C)  [Y_1 - \mathbbm{E}(Y_1 | C=0)|Z\} \\
-&= -Z_2 \mathbbm{E}[Y_1 - \mathbbm{E}(Y_1 | C=0)|C=0, Z] = 0
-\end{align*}
-where the final two steps follow by iterated expectations and the fact that  $Z$ is conditionally independent of $Y_1$ given $C$. 
-Since $Z_2 D = Z_2 C$, a nearly identical argument gives
-\begin{align*}
-\mathbbm{E}(V_1|Z) &= Z_1 [\mathbbm{E}(Y_1 | Z) - \mathbbm{E}(Y_1)]  + Z_2 \mathbbm{E}\{C  [Y_1 - \mathbbm{E}(Y_1 | C=1)|Z\} \\
-&= Z_2 \mathbbm{E}[Y_1 - \mathbbm{E}(Y_1 | C=1)|C=1, Z] = 0. \qedhere
-\end{align*}
-\end{proof}
-
-\subsection{Inference for ASG, ASB, and ASL}
-\label{subsec:inference}
-We now explain how to carry out cluster-robust inference for the ASG, ASB, and ASL effects, as implemented in our companion STATA package.
-Each of these effects can be expressed as a difference of coefficients from two just-identified linear IV regressions.
-The ASG effect is the difference of the \text{TOT} effect from Proposition \ref{prop:TOTreg} and the \text{TUT} effect from Proposition \ref{prop:TUTreg}.
-Similarly, the ASB effect is the difference of $\mathbb{E}(Y_0|C=1)$ and $\mathbbm{E}(Y_0|C=0)$ from Proposition \ref{prop:ASBreg} while the ASL effect is the difference of $\mathbbm{E}(Y_1|C=1)$ and $\mathbbm{E}(Y_1|C=0)$ from Proposition \ref{prop:ASLreg}.
-Within each pair of IV regressions the outcome variable and instrument set is identical; only the regressors differ. 
-Since our estimators of all three effects share the same structure, our discussion of inference abstracts from the specific regressors and instruments used in each case to avoid duplication. 
-To implement these results in practice without relying on our STATA package, simply substitute supply the regressors and instruments specified in the relevant propositions.
-
-Let $g = 1, ..., G$ index clusters and $i = 1, ..., N_g$ index individuals within a particular cluster $g$. 
-In our experiment, a cluster is a branch-day combination and the experimentally-assigned treatment (control, forced, or choice arm) is assigned at the cluster level.
-We assume that observations are iid across clusters but potentially correlated within cluster.
-Now consider a pair of just-identified linear IV regressions given by
-\begin{align*}
-Y_{ig} &= \boldsymbol{X}_{1,ig}' \boldsymbol{\theta}_0 + U_{ig} \\
-Y_{ig} &= \boldsymbol{X}_{0,ig}' \boldsymbol{\theta}_1 + V_{ig}
-\end{align*}
-with common instrument vector $\boldsymbol{W}_{ig}$. 
-Stacking observations in the usual manner, e.g.\
-\[
-\mathbf{W}_g \equiv \begin{bmatrix}
-\boldsymbol{W}_{1g}' \\
-\vdots \\
-\boldsymbol{W}_{N_gg}' \\
-\end{bmatrix}, \quad
-\mathbf{W} = \begin{bmatrix}
-\mathbf{W}_1\\ \vdots \\ \mathbf{W}_G
-\end{bmatrix},
-\]
-we can write the preceding equations in matrix form as
-\begin{align*}
-\mathbf{Y} &= \mathbf{X}_1\boldsymbol{\theta_1} + \mathbf{U}\\
-\mathbf{Y} &= \mathbf{X}_0\boldsymbol{\theta_0} + \mathbf{V}
-\end{align*}
-with instrument matrix $\mathbf{W}$.
-Now, the IV estimators for $\boldsymbol{\theta}_1$ and $\boldsymbol{\theta}_0$ can be expressed as 
-\begin{align*}
-\widehat{\boldsymbol{\theta}}_1 
-&= \left(\mathbf{W}'\mathbf{X}_1\right)^{-1}\mathbf{W}'\mathbf{Y}  = \boldsymbol{\theta}_1 + \left(\mathbf{W}'\mathbf{X}_1\right)^{-1}\mathbf{W}'\mathbf{U}\\ 
-\widehat{\boldsymbol{\theta}}_0 
-&= \left(\mathbf{W}'\mathbf{X}_0\right)^{-1}\mathbf{W}'\mathbf{Y} = \boldsymbol{\theta}_0 + \left(\mathbf{W}'\mathbf{X}_0\right)^{-1}\mathbf{W}'\mathbf{V}.
-\end{align*}
-Our parameter of interest is an element of the difference $(\theta_1 - \theta_0)$, so  it suffices to calculate the asymptotic distribution of $(\widehat{\boldsymbol{\theta}}_1 - \widehat{\boldsymbol{\theta}}_0)$.
-
-Re-arranging the preceding two equations, we have
-\begin{align*}
-\sqrt{G} \left(\widehat{\boldsymbol{\theta}}_1  - \boldsymbol{\theta}_1\right) &= 
- \left(\frac{\mathbf{W}'\mathbf{X}_1}{G}\right)^{-1}\left(\frac{\mathbf{W}'\mathbf{U}}{\sqrt{G}}\right) = \left( \frac{1}{G} \sum_{g=1}^G \mathbf{W}_g' \mathbf{X}_{1,g}\right)^{-1}\left(\frac{1}{\sqrt{G}} \sum_{g=1}^G\mathbf{W}_g' \mathbf{U}_g\right) \\
-\sqrt{G} \left(\widehat{\boldsymbol{\theta}}_0  - \boldsymbol{\theta}_0\right) &= 
- \left(\frac{\mathbf{W}'\mathbf{X}_0}{G}\right)^{-1}\left(\frac{\mathbf{W}'\mathbf{V}}{\sqrt{G}}\right) = \left( \frac{1}{G} \sum_{g=1}^G \mathbf{W}_g' \mathbf{X}_{0,g}\right)^{-1}\left(\frac{1}{\sqrt{G}} \sum_{g=1}^G\mathbf{W}_g' \mathbf{V}_g\right).
-\end{align*}
-Now, define $\mathbf{Q}_0 \equiv \mathbb{E}[\mathbf{W}_g'\mathbf{X}_{0g}]$ and $\mathbf{Q}_1 \equiv \mathbb{E}[\mathbf{W}_g'\mathbf{X}_{1g}]$ and suppose that these expectations exist and that the matrices $\mathbf{Q}_0$ and $\mathbf{Q}_1$ are invertible.
-Then, as $G \rightarrow \infty$
-\[
- \left( \frac{1}{G} \sum_{g=1}^G \mathbf{W}_g' \mathbf{X}_{0,g}\right)^{-1} \rightarrow_p \mathbf{Q}_0^{-1}, \quad
- \left( \frac{1}{G} \sum_{g=1}^G \mathbf{W}_g' \mathbf{X}_{1,g}\right)^{-1} \rightarrow_p \mathbf{Q}_1^{-1} \quad
-\]
-by the continuous mapping theorem.
-Now, by our experimental design and exclusion restriction, $\mathbf{W}_{ig}$ is independent of $U_{ig}$ both unconditionally and conditional on cluster size. 
-Therefore,
-\begin{align*}
-\mathbb{E}[\mathbf{W}_g' \mathbf{U}_g] &=  \mathbb{E}\left[ \sum_{i=1}^{N_g} \mathbf{W}_{ig} U_{ig} \right] = \mathbb{E}_{N_g}\left[ \mathbb{E}\left\{\left.
-\sum_{i=1}^{N_g} \mathbf{W}_{ig} U_{ig} \right| N_g \right\}\right]\\
-&= \mathbb{E}_{N_g}\left[ \sum_{i=1}^{N_g} \mathbb{E}(\mathbf{W}_{ig} U_{ig}|N_g)\right] = \mathbb{E}_{N_g}\left[ \sum_{i=1}^{N_g} \mathbb{E}(\mathbf{W}_{ig}U_{ig})\right] = 0
-\end{align*}
-by iterated expectations, and similarly smilarly, $\mathbb{E}[\mathbf{W}_g'\mathbf{V}_g] = \mathbf{0}$. 
-Thus, under mild regularity conditions (e.g.\ finite fourth moments), as $G \rightarrow \infty$  we have
-\[
-\frac{1}{\sqrt{G}} \sum_{g=1}^G \mathbf{W}_g' \otimes \begin{bmatrix} \mathbf{U}_g \\ \mathbf{V}_g \end{bmatrix} \rightarrow_d \text{N}(\mathbf{0}, \boldsymbol{\Omega})
-\]
-where the heteroskedasticity-- and cluster--robust variance-covariance matrix $\boldsymbol{\Omega}$ is defined as
-\[
-\boldsymbol{\Omega} \equiv 
- \mathbb{E} \left[\left(\mathbf{W}_g \mathbf{W}_g' \right)\otimes \begin{pmatrix}
-\mathbf{U}_g \mathbf{U}_g' & \mathbf{U}_g \mathbf{V}_g' \\
-\mathbf{V}_g \mathbf{U}_g' & \mathbf{V}_g \mathbf{V}_g'  
-\end{pmatrix} \right] \equiv \begin{bmatrix}
-\Omega_{UU} & \Omega_{UV} \\
-\Omega_{VU} & \Omega_{VV}
-\end{bmatrix}.
-\]
-Therefore, the joint limiting distribution of $\widehat{\boldsymbol{\theta}}_1$ and $\widehat{\boldsymbol{\theta}}_0$ is given by
-\[
-\begin{bmatrix}
-\sqrt{G}(\widehat{\boldsymbol{\theta}}_1 - \boldsymbol{\theta}_1)\\
-\sqrt{G}(\widehat{\boldsymbol{\theta}}_0 - \boldsymbol{\theta}_0)
-\end{bmatrix} \rightarrow_d
-\begin{bmatrix}
-\mathbf{Q}_1^{-1} & \mathbf{0} \\
-\mathbf{0} & \mathbf{Q}_0^{-1} 
-\end{bmatrix}
-\begin{bmatrix}
-\boldsymbol{\xi}_U \\ \boldsymbol{\xi}_V 
-\end{bmatrix}, \quad
-\begin{bmatrix}
-\boldsymbol{\xi}_U \\ \boldsymbol{\xi}_V 
-\end{bmatrix} \sim \text{N}\left(\begin{bmatrix} \mathbf{0} \\ \mathbf{0}\end{bmatrix},
-\begin{bmatrix}
-\Omega_{UU} & \Omega_{UV} \\
-\Omega_{VU} & \Omega_{VV}
-\end{bmatrix}\right)
-\]
-from which it follows by the continuous mapping theorem that
-\[
-\sqrt{G}\left[ (\widehat{\boldsymbol{\theta}}_1 - \widehat{\boldsymbol{\theta}}_0 ) - (\boldsymbol{\theta}_1 - \boldsymbol{\theta}_0)\right] 
-\rightarrow_d
-\begin{bmatrix}
-\mathbf{Q}_1^{-1} & -\mathbf{Q}_0^{-1}
-\end{bmatrix}
-\begin{bmatrix}
-\boldsymbol{\xi}_U \\ \boldsymbol{\xi}_V 
-\end{bmatrix}.
-\]
-To use this result in practice, we estimate the standard errors of  $(\widehat{\boldsymbol{\theta}}_1 - \widehat{\boldsymbol{\theta}}_0)$ as the square root of the diagonal elements of the matrix
-\[
-\widehat{\text{Avar}}(\widehat{\boldsymbol{\theta}}_1 - \widehat{\boldsymbol{\theta}}_0) 
-= \begin{bmatrix}
-\left(\mathbf{W}'\mathbf{X}_1\right)^{-1} &
--\left(\mathbf{W}'\mathbf{X}_0\right)^{-1} 
-\end{bmatrix}
-\begin{bmatrix}
-\mathbf{S}_{UU}& \mathbf{S}_{UV}\\
-\mathbf{S}_{VU}& \mathbf{S}_{VV}
-\end{bmatrix} 
-\begin{bmatrix}
-\left(\mathbf{X}_1'\mathbf{W}\right)^{-1} \\
--\left(\mathbf{X}_0'\mathbf{W}\right)^{-1} 
-\end{bmatrix}
-\]
-where
-\begin{align*}
-\mathbf{S}_{UU} &\equiv \sum_{g=1}^G \mathbf{W}_g' \widehat{\mathbf{U}}_g \widehat{\mathbf{U}}_g' \mathbf{W}_g\\
-\mathbf{S}_{UV} &\equiv \sum_{g=1}^G \mathbf{W}_g' \widehat{\mathbf{U}}_g \widehat{\mathbf{V}}_g' \mathbf{W}_g\\
-\mathbf{S}_{VU} &\equiv \mathbf{S}_{UV}'\\
-\mathbf{S}_{VV} &\equiv \sum_{g=1}^G \mathbf{W}_g' \widehat{\mathbf{V}}_g \widehat{\mathbf{V}}_g' \mathbf{W}_g
-\end{align*}
-and we define the IV residuals
-\begin{align*}
-\widehat{\mathbf{U}}_g &\equiv \mathbf{Y}_g - \mathbf{X}_{1,g}\widehat{\boldsymbol{\theta}}_1\\
-\widehat{\mathbf{V}}_g &\equiv \mathbf{Y}_g - \mathbf{X}_{0,g}\widehat{\boldsymbol{\theta}}_0.
-\end{align*}
-In our application the number of clusters, $G$, is large.
-If desired, an \emph{ad hoc} degrees of freedom correction can be applied by multiplying the standard errors by $\sqrt{G/(G-1)}$.
-
-\section{Testable Implications of the Exclusion Restriction}
-\label{append:exclusion}
-
-\normalsize
-\linespread{1.25}
-%Really force it to normal size and linespread
-\normalsize
-\linespread{1.25}
-
-This section describes the testable implications of our exclusion restrictions: \eqref{eq:exclusion0} and \eqref{eq:exclusion1} from Section \ref{sec:potentialOutcomes}. 
-To consider possible violations of these conditions, it is helpful to introduce some additional notation.
+\section{ Causal Random Forest, CATE, and `mistakes'}\label{app:cate}
+
+To estimate conditional average treatment effects given administrative and survey data, we use the function \texttt{causal\_forest()} of the \texttt{grf} R package; to estimate conditional TOT and TUT effects we use the \texttt{instrumental\_forest()} function from the same package.
+In each case, we use the default parameter values from the \texttt{grf} package with one exception: we increase the number of trees from the default value of 2000 to 5000.
+The functions \texttt{causal\_forest()} and \texttt{instrumental\_forest()} implement special cases of the ``generalized random forest'' methods of \cite{atheygrf}.
+In broad strokes, these functions combine a large number of regression trees that recursively partition the covariate space to estimate conditional average effects.
+% Figure \ref{causal_tree1} illustrates the partition that emerges from one of the trees in our causal forest implementation.
+The trees are ``honest'' in that observations used to determine the optimal partition are not used to estimate effects, and vice-versa.
+While closely related to more familiar ``regression-tree'' random forests, the generalized random forest approach explicitly targets the parameter of interest--a conditional ATE or IV estimand--when choosing the optimal covariate partition.
+\footnote{For more details, see \cite{atheygrf} and the \texttt{grf} documentation: \url{https://grf-labs.github.io/grf/}.
+When constructing our random forest estimates of heterogeneous treatment effects, we use observations for all borrowers who answered at least \emph{part} of the intake survey.
+We impute the median response for the missing values, while also including an indicator whether the variable originally had a missing value.
+Results are similar if we manually include interactions between the original/imputed variable and an indicator for missingness.
+This is as expected, given that tree-based methods by their nature ``automatically'' consider interactions of arbitrary orders.}
+
+\begin{figure}
+
+    \begin{center}
+     \begin{subfigure}{0.32\textwidth}
+       \centering
+      \includegraphics[width=\textwidth]{Figuras/he_dist_tau_hat_tot.pdf}
+          \caption{ToT}
+    \end{subfigure}
+    \begin{subfigure}{0.32\textwidth}
+       \centering
+      \includegraphics[width=\textwidth]{Figuras/he_dist_tau_hat_tut.pdf}
+          \caption{TuT}
+    \end{subfigure} 
+       \begin{subfigure}{.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/he_dist_tau_hat_eff.pdf}
+        \caption{ATE}
+    \end{subfigure} 
+    \end{center}
+    \caption{Heterogeneous Treatment Effects.}
+    \label{heterogeneous_effects}    
+  %\footnotesize{ } \textit{Do file: }  \texttt{cate_dist.do}
+\end{figure}
+
+\begin{figure}[h!]
+
+    \begin{center}
+    \begin{subfigure}{0.75\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/scatter_hist_wide_narrow.pdf}
+    \end{subfigure}
+    \end{center}
+       \caption{Conditional ATEs from ``wide'' and ``narrow'' covariate sets.
+This figure plots the relationship between the causal forest conditional ATE estimates from Section \ref{sec:RF} that use the ``wide'' set of covariates (all intake survey responses) and those based on a restricted ``narrow'' set of covariates (age, gender, HS education, and previous borrowing).
+The scatterplot graphs one estimate versus the other, with the ``wide'' covariate set on the horizontal axis and the ``narrow'' set on the vertical axis.
+The density plots on each axis show the estimated marginal distribution of conditional ATEs under each covariate set.
+The density for the ``wide'' covariate set is considerably more dispersed, as the causal forest based on this set of covariates captures considerably more treatment effect heterogeneity.}
+    \label{wide_narrow_forests}
+
+%\textit{Do file: } \texttt{wide_narrow_forests.do}       
+\end{figure}
+
+\section{Testable Implications of the Exclusion Restriction} \label{sec:testing_exclusion}
+
+%This section describes the testable implications of our exclusion restrictions: \eqref{eq:exclusion0} and \eqref{eq:exclusion1} from Section \ref{sec:potentialOutcomes}. 
+%To consider possible violations of these conditions, we require some additional notation.
 As above, let $Y_0 \equiv Y(d=0,z=0)$ and $Y_1 \equiv Y(d=1,z=1)$ denote the potential outcomes under \emph{forced treatment}: $Y_0$ is the potential outcome when forced into the status quo contract and $Y_1$ when forced into the commitment contract.
@@
 Using this notation, \eqref{eq:exclusion0} becomes $Y_0 = Y_{0,2}$ and while \eqref{eq:exclusion1} becomes $Y_1 = Y_{1,2}$.
-If we do not impose this pair of equalities, part (iii) of Assumption \ref{assump:randchoice} becomes 
+Without imposing these, Assumption \ref{assump:randchoice}(iii) becomes 
 \[
@@
 \end{align}
-Equation \ref{eq:exclusion_append0} is a restriction on the average potential outcomes of non-choosers that we use to point identify the TUT effect.
-It says that someone who \emph{would} choose the control condition when given a choice, experiences the same potential outcome, on average, when \emph{assigned} to the control condition.
-Equation \ref{eq:exclusion_append1} is a restriction on the average potential outcomes of choosers that we use to point identify the TOT effect.
-It says that someone who \emph{would} choose the commitment contract when given a choice, experiences the same potential outcome, on average, when \emph{assigned} to this condition.
-Because they refer to different groups of people, either of \eqref{eq:exclusion_append0}  and \eqref{eq:exclusion_append1} could hold when the other is violated.
+%Equation \ref{eq:exclusion_append0} is a restriction on the average potential outcomes of non-choosers that we use to point identify the TUT effect.
+%It says that someone who \emph{would} choose the control condition when given a choice, experiences the same potential outcome, on average, when \emph{assigned} to the control condition.
+%Equation \ref{eq:exclusion_append1} is a restriction on the average potential outcomes of choosers that we use to point identify the TOT effect.
+%It says that someone who \emph{would} choose the commitment contract when given a choice, experiences the same potential outcome, on average, when \emph{assigned} to this condition.
+Because they refer to different groups of people--choosers versus non-choosers--either of \eqref{eq:exclusion_append0}  and \eqref{eq:exclusion_append1} could hold when the other is violated.
 For this reason we consider each in turn.
 Our approach is closely related to arguments from \cite{huber_mellace} and \cite{BinaryRegressor}, among others.
-As such, the following is a heuristic explanation rather than a fully-rigorous proof.
-See the aforementioned papers for more details of how to make this argument fully rigorous.
+%As such, the following is a heuristic explanation rather than a fully-rigorous proof.
+%See the aforementioned papers for more details of how to make this argument fully rigorous.
 
@@
 Since $\widehat{\mathbbm{E}}(Y_\text{APR}|D=0,Z=2) = 0.58$ falls between these bounds, we find no evidence against the exclusion restriction for non-choosers. 
-Repeating this exercise for the financial cost outcome, we see that $\widehat{\mathbbm{E}}(Y_\text{FC}|D=0,Z=2) = 973$ likewise falls between 
-\[
-\widehat{\mathbbm{E}}(Y_\text{FC}|Z=0,Y_\text{FC}\leq y^0_{0.89}) = 626, \quad
-\widehat{\mathbbm{E}}(Y_\text{FC}|Z=0, Y_\text{FC}\geq y^0_{0.11}) = 1046 
-\]
-so we again find no evidence against the exclusion restriction for non-choosers.
-
-We can use an analogous approach to construct testable implications for \ref{eq:exclusion_append1}. 
-Because $Z$ was randomly assigned, a fraction $p$ of participants with $Z = 1$ are choosers so the distribution of $Y|Z=1$ is a mixture of $Y_1|C=1$ and $Y_1|C=0$ with mixing weights $p$ and $1 -p$.
-The participants with $C = 1$ must lie \emph{somewhere} in the distribution of $Y_0|Z=1$ so again consider the two most extreme cases: they could occupy the bottom or the top $p\times 100\%$ of the distribution.
-Hence,
-\[
-\mathbbm{E}\left(Y|Z=1,Y\leq y^1_{p}\right) \leq \mathbbm{E}(Y_1|C=1) \leq \mathbbm{E}\left(Y|Z=1,Y \geq y^1_{1-p}\right)
-\]
-where $y^1_p$ and $y^1_{1-p}$ are the $p$ and $1 - p$ quantiles of the distribution of $Y|Z=1$.
-As above, these bounds do not rely on the exclusion restriction.
-If Equation \ref{eq:exclusion_append1} holds, however, we know that $\mathbb{E}(Y|D=1,Z=2) = \mathbb{E}(Y_1|C=1)$, yielding the following testable implications for choosers
+The same result holds for the financial cost outcome: results available upon request. 
+%Repeating this exercise for the financial cost outcome, we see that $\widehat{\mathbbm{E}}(Y_\text{FC}|D=0,Z=2) = 973$ likewise falls between 
+%\[
+%\widehat{\mathbbm{E}}(Y_\text{FC}|Z=0,Y_\text{FC}\leq y^0_{0.89}) = 626, \quad
+%\widehat{\mathbbm{E}}(Y_\text{FC}|Z=0, Y_\text{FC}\geq y^0_{0.11}) = 1046 
+%\]
+%so we again find no evidence against the exclusion restriction for non-choosers.
+
+We can use an analogous approach to construct testable implications for \ref{eq:exclusion_append1}, yielding 
+%Because $Z$ was randomly assigned, a fraction $p$ of participants with $Z = 1$ are choosers so the distribution of $Y|Z=1$ is a mixture of $Y_1|C=1$ and $Y_1|C=0$ with mixing weights $p$ and $1 -p$.
+%The participants with $C = 1$ must lie \emph{somewhere} in the distribution of $Y_0|Z=1$ so again consider the two most extreme cases: they could occupy the bottom or the top $p\times 100\%$ of the distribution.
+%\[
+%\mathbbm{E}\left(Y|Z=1,Y\leq y^1_{p}\right) \leq \mathbbm{E}(Y_1|C=1) \leq \mathbbm{E}\left(Y|Z=1,Y \geq y^1_{1-p}\right)
+%\]
+%As above, these bounds do not rely on the exclusion restriction.
+%If Equation \ref{eq:exclusion_append1} holds, however, we know that $\mathbb{E}(Y|D=1,Z=2) = \mathbb{E}(Y_1|C=1)$, yielding the following testable implications for choosers
 \begin{equation}
@@
 \end{equation}
+where $y^1_p$ and $y^1_{1-p}$ are the $p$ and $1 - p$ quantiles of the distribution of $Y|Z=1$.
 If either inequality is violated, then the exclusion restriction from Equation \ref{eq:exclusion_append1} fails.
@@
 Since $\widehat{\mathbbm{E}}(Y_\text{APR}|D=1,Z=2) = 0.43$ falls between these bounds, we find no evidence against the exclusion restriction for the choosers. 
-Repeating this exercise for the financial cost outcome, we see  that $\widehat{\mathbbm{E}}(Y_\text{FC}|D=1,Z=2)= 570$ likewise falls between
+The same holds for the financial cost outcome: results available upon request.
+%Repeating this exercise for the financial cost outcome, we see  that $\widehat{\mathbbm{E}}(Y_\text{FC}|D=1,Z=2)= 570$ likewise falls between
+%\[
+%\widehat{\mathbbm{E}}(Y|Z=1,Y\leq y^1_{0.11}) = 53, \quad
+%\widehat{\mathbbm{E}}(Y|Z=1,Y\geq y^1_{0.89}) = 2934
+%\]
+%so we again find no evidence against the exclusion restriction for the choosers.
+
+%The aforementioned bounds for $\mathbbm{E}(Y_0|C=0)$ and $\mathbbm{E}(Y_1|C=1)$ can alternatively be used construct partial identification bounds for the TOT and TUT effects that do not rely on our exclusion restrictions.
+If the TOT or TUT expressions from \eqref{eq:TOT} and \eqref{eq:TUT} fall \emph{outside} the partial identification bounds, this is equivalent to finding a violation of \ref{eq:testable0} or \ref{eq:testable1}.
+We implement these bounds for the TOT and TUT in our companion STATA package.
+
+\section{Estimation and Inference} 
+\label{sec:estimation_inference}
+
+\subsection{Regression-based Estimation of TOT, TUT, ASG, ASL, and ASB}
+
+Let $Z_0 \equiv \mathbbm{1}\{Z=0\}$, $Z_1 \equiv \mathbbm{1}\{Z=1\}$, and $Z_2 \equiv \mathbbm{1}\{Z=2\}$.
+Under standard regularity conditions, the following proposition shows that an IV regression of $Y$ on an intercept, $Z_1$ and $Z_2 D$ with instruments $(1, Z_0, Z_1)$ provides consistent estimates the ATE and TOT, while an IV regression of $Y$ on an intercept, $-Z_0$ and $-Z_2(1-D)$ with the same instrument set consistently estimates the ATE and TUT effects.
+
+\begin{prop} 
+\label{prop:TOTandTUTregs}
+Under Assumption \ref{assump:randchoice}, 
+\begin{enumerate}[(i)] 
+\item $Y = \mathbbm{E}(Y_0) + \text{ATE}\times Z_1 + \text{TOT} \times Z_2 D + U$
+\item $Y = \mathbbm{E}(Y_1) + \text{ATE}\times -Z_0 + \text{TUT} \times -Z_2 (1 - D) + V$
+\end{enumerate}
+where $\mathbbm{E}(U|Z) = \mathbbm{E}(V|Z) = 0$.
+\end{prop}
+
+\begin{proof}[Proof of Proposition \ref{prop:TOTandTUTregs}]
+For part (i), since $Z_2 D = Z_2 C$ and $(Z_0 + Z_1 + Z_2) = 1$, Assumption \ref{assump:randchoice} (iii) implies $Y= Y_0 + Z_1 (Y_1 - Y_0) + Z_2D(Y_1 - Y_0)$.
+Now define 
 \[
-\widehat{\mathbbm{E}}(Y|Z=1,Y\leq y^1_{0.11}) = 53, \quad
-\widehat{\mathbbm{E}}(Y|Z=1,Y\geq y^1_{0.89}) = 2934
+U \equiv [Y_0 - \mathbbm{E}(Y_0)] + Z_1[(Y_1 - Y_0) - \text{ATE}] + Z_2 D[(Y_1 - Y_0) - \text{TOT}].
 \]
-so we again find no evidence against the exclusion restriction for the choosers.
-
-The aforementioned bounds for $\mathbbm{E}(Y_0|C=0)$ and $\mathbbm{E}(Y_1|C=1)$ can alternatively be used construct partial identification bounds for the TOT and TUT effects that do not rely on our exclusion restrictions.
-If the TOT or TUT expression from \ref{append:randchoice} fall \emph{outside} the partial identification bounds, this is equivalent to finding a violation of \ref{eq:testable0} or \ref{eq:testable1}.
-We implement these bounds for the TOT and TUT in our companion STATA package.
-
-\section{Causal Random Forest, HTE, and `mistakes'}
-
-\begin{figure}[!htb]
-        \caption{Example Causal Tree}
-    \label{causal_tree1}
-    \begin{center}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/crf_apr.pdf}
-    \end{center}
-    \legend{ 
-    This figure shows an example of one of the regression trees used to compute the causal forest estimates described in Section \ref{sec:RF}.
-Each tree is constructed from a sequence of recursive binary partitions of the covariate space, with a splitting rule that is targeted to the causal quantity of interest, following the methodology of \cite{atheygrf}.}
-    %This is one(it is chosen such that it minimizes the pruned cost, that is it is the tree with the smallest root-node impurity) of the honest causal trees in the random forest we use for the estimation of the heterogeneous treatment effect of the fee-forcing contract.
-It is meant only as an example of how these trees look like.
-The forest was such that there are as many estimated treatment effects as there are clients.
-     %\footnotesize{ \textit{RScript: }  \texttt{grf.R}
-\end{figure}
-
-\begin{figure}[!htb]
-    \begin{center}
-  \caption{Cumulative Distribution Function of Conditional ATE Estimates}
-  \includegraphics[width=0.7\textwidth]{Figuras/cdf_CATE.pdf} 
-    \label{fig:CATEsurvival}
-     \legend{This figure shows the share of borrowers who benefit from forced commitment, where ``benefit'' is defined as having an estimated conditional average treatment effect (ATE) above a specified threshold value.
-Results are based on the causal forest model from Section \ref{sec:RF}.
-The solid line equals $1 - F_\text{ATE}(\delta)$ where $F_\text{ATE}(\delta)$ denotes the CDF corresponding to the density of conditional ATE estimates from Figure \ref{heterogeneous_effects}.
-The blue shaded regions are associated 95\% confidence intervals.
-We estimate that at least 90\% of borrowers have a positive conditional ATE.}
-    \end{center}
-
-%\textit{Do file: }  \texttt{cdf_CATE.do}
-\end{figure}
-
-\begin{figure}[!htb]
-    \caption{Conditional ATEs from ``wide'' and ``narrow'' covariate sets}
-    \label{wide_narrow_forests}
-    \begin{center}
-    \begin{subfigure}{0.7\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/scatter_hist_wide_narrow.pdf}
-    \end{subfigure}
-    \legend{This figure plots the relationship between the causal forest conditional ATE estimates from Section \ref{sec:RF} that use the ``wide'' set of covariates (all intake survey responses) and those based on a restricted ``narrow'' set of covariates (age, gender, HS education, and previous borrowing).
-The scatterplot graphs one estimate versus the other, with the ``wide'' covariate set on the horizontal axis and the ``narrow'' set on the vertical axis.
-The density plots on each axis show the estimated marginal distribution of conditional ATEs under each covariate set.
-The density for the ``wide'' covariate set is considerably more dispersed, as the causal forest based on this set of covariates captures considerably more treatment effect heterogeneity.}
-    \end{center}
-
-%\textit{Do file: } \texttt{wide_narrow_forests.do}       
-\end{figure}
-
-\subsection{Targeting rule comparisons}
-
-\begin{figure}[!htb]
-    \caption{Targeting rules}
-    \label{targeting_rules}
-    \begin{center}
-    \begin{subfigure}{0.7\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/wide_narrow_rule.pdf}
-    \end{subfigure}
-    \end{center}
-      \legend{ This figure plots the percentage of borrowers who would benefit from a program in which commitment is targeted using the ``narrow'' covariate set (age, gender, HS education, and previous borrowing).
-In this exercise ``benefit'' is defined to mean having a conditional ATE above a particular threshold, taking the estimated conditional effects from the ``wide'' causal forest as ground truth.
-The plot compares the estimated percentage of borrowers who benefit, along with associated 95\% confidence bands, for three targeting rules: universal forced commitment in blue, targeting based on a random forest classification model in green, and targeting based on the logit model in red.
-For each of the classification models, the outcome variable is an indicator for whether the CATE estimate from the ``wide'' random forest model is positive.
-Each of the classification models produces an estimated probability of a positive CATE.
-For each, the assignment rule ranks borrowers by this estimated probability, and assigns the highest 90\% to forced commitment, to match the overall percentage of borrowers with positive estimated CATEs from the ``wide'' random forest model.
-Because this is an in-sample exercise, it overstates the actual performance of logit and RF-based targeting.
-}
-
-\end{figure}
-
-Figure \ref{targeting_rules} compares the in-sample performance of these targeting rules against a policy of universal forced commitment.
-The plot presents the estimated proportion of borrowers who benefit from a particular treatment assignment rule, along with associated 95\% confidence bands, where ``benefit'' is defined as having a conditional average treatment effect above a particular threshold.
-As above, we take the conditional average effects from the ``wide'' causal forest as ground truth for the purposes of this exercise.
-Because this is an in-sample exercise, the logistic and random forest classification rules have an unfair advantage: there is no adjustment for overfitting.
-In spite of this, their performance is quite unimpressive relative to a policy of universal forced commitment.
-The fraction of the whole sample incorrectly targeted when moving from universal forced commitment to targeting based on the narrow RF falls only from 9.78\% to 9.59\%.
-The logit targeting rule actually makes things marginally worse.
+Since $Z_2 D = Z_2 C$ and $Z$ is independent of $(Y_1, Y_0)$ by Assumption \ref{assump:randchoice} (i), it follows that $\mathbbm{E}(U|Z) = Z_2 \mathbbm{E}\left[C\left\{(Y_1 - Y_0) - \text{TOT}\right\}|Z\right]$.
+Thus, by iterated expectations,
+\begin{align*}
+\mathbbm{E}\left[C\left\{(Y_1 - Y_0) - \text{TOT}\right\}|Z\right] 
+%&=  \mathbbm{P}(C=1|Z) \left[\mathbbm{E}(Y_1 - Y_0|C=1,Z)  - \text{TOT}\right]\\
+&= \mathbbm{P}(C=1)\left[\mathbbm{E}(Y_1 - Y_0|C=1) - \text{TOT} \right]=0
+\end{align*}
+since $Z$ is independent of $(Y_0, Y_1)$ given $C$, an implication of Assumption \ref{assump:randchoice} (i).
+
+For part (ii), since $Z_2(1 - C)= Z_2(1 - D)$ and $(Z_1 + Z_2) = 1 - Z_0$,  Assumption \ref{assump:randchoice} (iii) implies $Y= Y_1 - Z_0 (Y_1 - Y_0) - Z_2(1 - D) (Y_1 - Y_0)$.
+Define 
+\[
+V \equiv [Y_1 - \mathbb{E}(Y_1)] - Z_0[(Y_1 - Y_0) - \text{ATE}] - Z_2(1 - D)[(Y_1 - Y_0) - \text{TUT}].
+\]
+Since $Z_2(1 - D) = Z_2 (1 - C)$ and $Z$ is independent of $(Y_0, Y_1)$ by Assumption \ref{assump:randchoice} (i),
+$\mathbb{E}(V|Z) = -Z_2\mathbb{E}[(1 - C)\left\{(Y_1 - Y_0) - \text{TUT}\right\}|Z]$.
+Thus, by iterated expectations,
+\begin{align*}
+\mathbb{E}[(1 - C)\left\{(Y_1 - Y_0) - \text{TUT}\right\}|Z]
+%&= \mathbb{P}(C=0|Z)\left[ \mathbb{E}(Y_1 - Y_0|C=0, Z) - \text{TUT}\right]\\
+&= \mathbb{P}(C=0|Z) \left[ \mathbb{E}(Y_1 - Y_0|C=0) - \text{TUT}\right] = 0
+\end{align*}
+since $Z$ is independent of $(Y_0, Y_1)$ given $C$, an implication of Assumption \ref{assump:randchoice} (i).
+\end{proof}
+
+%\begin{prop} 
+%\label{prop:TOTreg}
+%Under Assumption \ref{assump:randchoice}, $Y = \mathbbm{E}(Y_0) + \text{ATE}\times Z_1 + \text{TOT} \times Z_2 D + U$ where $\mathbbm{E}(U|Z) = 0$.
+%\end{prop}
+%
+%\begin{proof}
+%By Assumption \ref{assump:randchoice} (iii),
+%$Y= Y_0 + Z_1 (Y_1 - Y_0) + Z_2D(Y_1 - Y_0)$
+%%\begin{align*}
+%%Y &= Z_0 Y_0 + Z_1 Y_1 + Z_2[(1 - C) Y_0 + CY_1] 
+%%= (Z_0 + Z_2)Y_0 + Z_1 Y_1 + Z_2C(Y_1 - Y_0)\\
+%%&= (Z_0 + Z_1 + Z_2)Y_0 + Z_1 (Y_1 - Y_0) + Z_2D(Y_1 - Y_0) 
+%%= Y_0 + Z_1 (Y_1 - Y_0) + Z_2D(Y_1 - Y_0).
+%%\end{align*}
+%because $Z_2 D = Z_2 C$ and $(Z_0 + Z_1 + Z_2) = 1$.
+%Thus, defining 
+%\[
+%U \equiv [Y_0 - \mathbbm{E}(Y_0)] + Z_1[(Y_1 - Y_0) - \text{ATE}] + Z_2 D[(Y_1 - Y_0) - \text{TOT}]
+%\]
+%by construction we have $Y = \mathbbm{E}(Y_0) + \text{ATE} \times Z_1 + \text{TOT} \times Z_2 D+ U$.
+%Since $Z_2 D = Z_2 C$ and $Z$ is independent of $(Y_1, Y_0)$ by Assumption \ref{assump:randchoice} (i), we have
+%\begin{align*}
+%\mathbbm{E}(U|Z) 
+%%&= [\mathbbm{E}(Y_0|Z) - \mathbbm{E}(Y_0)]  + Z_1[\mathbbm{E}(Y_1 - Y_0|Z) - \text{ATE}] +  \mathbbm{E}\left[Z_2 D\left\{(Y_1 - Y_0) - \text{TOT}\right\}|Z\right]\\
+%%&= [\mathbbm{E}(Y_0) - \mathbbm{E}(Y_0)]  + Z_1[\mathbbm{E}(Y_1 - Y_0) - \text{ATE}] + Z_2 \mathbbm{E}\left[C\left\{(Y_1 - Y_0) - \text{TOT}\right\}|Z\right]\\
+%&= Z_2 \mathbbm{E}\left[C\left\{(Y_1 - Y_0) - \text{TOT}\right\}|Z\right].
+%\end{align*}
+%Finally, by iterated expectations
+%\begin{align*}
+%\mathbbm{E}\left[C\left\{(Y_1 - Y_0) - \text{TOT}\right\}|Z\right] 
+%%&=  \mathbbm{P}(C=1|Z) \left[\mathbbm{E}(Y_1 - Y_0|C=1,Z)  - \text{TOT}\right]\\
+%&= \mathbbm{P}(C=1)\left[\mathbbm{E}(Y_1 - Y_0|C=1) - \text{TOT} \right]=0
+%\end{align*}
+%since $Z$ is conditionally independent of $(Y_0, Y_1)$ given $C$, an implication of \ref{assump:randchoice} (i).
+%\end{proof}
+%
+%%The next proposition provides regression-based estimates of the ATE and TUT.
+%\begin{prop}
+%\label{prop:TUTreg}
+%Under Assumption \ref{assump:randchoice}, $Y = \mathbbm{E}(Y_1) + \text{ATE}\times -Z_0 + \text{TUT} \times -Z_2 (1 - D) + V$ where $\mathbb{E}(V|Z) = 0$.
+%Thus, an IV regression of $Y$ on an intercept, $-Z_0$ and $-Z_2(1-D)$ with instruments $(1, Z_0, Z_1)$ provides consistent estimates of the ATE and TUT effects.
+%\end{prop}
+%
+%\begin{proof}
+%By Assumption \ref{assump:randchoice} (iii),
+%$Y= Y_1 - Z_0 (Y_1 - Y_0) - Z_2(1 - D) (Y_1 - Y_0)$
+%%\begin{align*}
+%%Y %&= Z_0 Y_0 + Z_1 Y_1 + Z_2[(1 - C) Y_0 + CY_1] 
+%%&= Z_0 Y_0 + Z_1 Y_1 + Z_2[(1 - C) (Y_0 - Y_1) + Y_1]
+%%&= Z_0 Y_0 + (Z_1 + Z_2) Y_1 + Z_2(1 - C) (Y_0 - Y_1) = Z_0 Y_0 + (1 - Z_0) Y_1 + Z_2(1 - D) (Y_0 - Y_1) \\
+%%= Y_1 - Z_0 (Y_1 - Y_0) - Z_2(1 - D) (Y_1 - Y_0)
+%%\end{align*}
+%since $Z_2(1 - C)= Z_2(1 - D)$ and $(Z_1 + Z_2) = 1 - Z_0$.
+%Thus, defining 
+%\[
+%V \equiv [Y_1 - \mathbb{E}(Y_1)] - Z_0[(Y_1 - Y_0) - \text{ATE}] - Z_2(1 - D)[(Y_1 - Y_0) - \text{TUT}]
+%\]
+%by construction we have $Y = \mathbb{E}(Y_1) + \text{ATE} \times -Z_0 + \text{TUT} \times -Z_2(1 - D) + V$.
+%Now, since $Z_2(1 - D) = Z_2 (1 - C)$ and $Z$ is independent of $(Y_0, Y_1)$ by Assumption \ref{assump:randchoice} (i),
+%\begin{align*}
+%\mathbb{E}(V|Z) 
+%%&= [\mathbb{E}(Y_1|Z) - \mathbb{E}(Y_1)] - Z_0[\mathbb{E}(Y_1 - Y_0|Z) - \text{ATE}] - \mathbb{E}[Z_2(1 - D)\left\{(Y_1 - Y_0) - \text{TUT}\right\}|Z]\\
+%%&= [\mathbb{E}(Y_1) - \mathbb{E}(Y_1)] - Z_0[\mathbb{E}(Y_1 - Y_0) - \text{ATE}] - Z_2\mathbb{E}[(1 - C)\left\{(Y_1 - Y_0) - \text{TUT}\right\}|Z]\\
+%&= -Z_2\mathbb{E}[(1 - C)\left\{(Y_1 - Y_0) - \text{TUT}\right\}|Z].
+%\end{align*}
+%Finally, by iterated expectations,
+%\begin{align*}
+%\mathbb{E}[(1 - C)\left\{(Y_1 - Y_0) - \text{TUT}\right\}|Z]
+%%&= \mathbb{P}(C=0|Z)\left[ \mathbb{E}(Y_1 - Y_0|C=0, Z) - \text{TUT}\right]\\
+%&= \mathbb{P}(C=0|Z) \left[ \mathbb{E}(Y_1 - Y_0|C=0) - \text{TUT}\right] = 0
+%\end{align*}
+%since $Z$ is independent of $(Y_0, Y_1)$ given $C$, an implication of Assumption \ref{assump:randchoice} (i).
+%\end{proof}
+
+Since $\text{ASG} = \text{TOT} - \text{TUT}$, the preceding proposition provides a consistent estimate of the $\text{ASG}$ effect.
+The $\text{ASB}$ effect, $\mathbbm{E}(Y_0|C=1) - \mathbb{E}(Y_0|C=0)$, can likewise be estimated by taking the difference of coefficients across two linear IV regressions with \emph{no intercept} and instrument sets $(Z_0, Z_2)$, as shown in the following proposition.
+
+\begin{prop}
+\label{prop:ASBreg}
+Under Assumption \ref{assump:randchoice}
+\begin{enumerate}[(i)]
+    \item $(1 - D) Y = \mathbbm{E}(Y_{0}) \times Z_0 + \mathbbm{E}(Y_{0}|C=0) \times (1 - D)Z_2 + U_{0}$
+    \item  $(1 - D) Y = \mathbbm{E}(Y_{0}) \times(Z_0 + Z_2) + \mathbbm{E}(Y_{0}|C=1)\times -DZ_2 + U_{1}$
+\end{enumerate}
+where $\mathbbm{E}(U_0|Z) = \mathbbm{E}(U_1|Z) = 0$.
+%Thus, an IV regression of $(1 - D)Y$ on $Z_0$ and $(1 - D)Z_2$ with instruments $(Z_0, Z_2)$ and no intercept consistently estimates $\mathbb{E}(Y_0)$ and $\mathbb{E}(Y_0|C=0)$. 
+%Similarly, an IV regression of $(1 - D)Y$ on $(Z_0 + Z_2)$ and $-DZ_2$ with instruments $(Z_0, Z_2)$ and no intercept consistently estimates $\mathbb{E}(Y_0)$ and $\mathbb{E}(Y_0|C=1)$.
+\end{prop}
+
+\begin{proof}
+Assumption \ref{assump:randchoice} (ii) implies $(1 - D) = Z_0 + Z_2(1 - C)$. Hence, 
+\begin{align*}
+(1 - D)Y 
+%&=  [Z_0 + Z_2 (1 - C)]\left\{Z_0 Y_0 + Z_1 Y_1 + Z_2[(1 - C) Y_0 + CY_1]\right\}\\
+&= Z_0 Y_0 + Z_2 (1 - C) [(1 - C) Y_0 + C Y_1] = Z_0 Y_0 + Z_2 (1 - C) Y_0
+\end{align*}
+by Assumption \ref{assump:randchoice} (iii), since $Z_j^2 = Z_j$ for any $j$ and $Z_j Z_k = 0$ for any $j \neq k$ and, similarly, $(1 - C)^2 = (1 - C)$ and $C (1 - C) = 0$.
+Therefore, since $Z_2 (1 - C) = Z_2 (1 - D)$,
+\[
+(1 - D)Y = Z_0 Y_0 + Z_2 (1 - D) Y_0, \quad
+(1 - D)Y = (Z_0 + Z_2) Y_0 + (-DZ_2) Y_0. 
+\]
+Now, define 
+\begin{align*}
+U_0 &\equiv Z_0 [Y_0 - \mathbbm{E}(Y_0)] + Z_2(1 - D)[Y_0 - \mathbbm{E}(Y_0|C=0)]\\
+U_1 &\equiv (Z_0 + Z_2)[Y_0 - \mathbbm{E}(Y_0)] + (-Z_2 D)[Y_0 - \mathbbm{E}(Y_0|C=1)].
+\end{align*}
+%by construction, we have
+%\begin{align*}
+%Y &= \mathbbm{E}(Y_0) \times Z_0 + \mathbbm{E}(Y_0|C=0) \times Z_2(1 - D) + U_0\\
+%Y &= \mathbbm{E}(Y_0) \times (Z_0 + Z_2)+ \mathbbm{E}(Y_0|C=1) (-Z_2D) + U_1.
+%\end{align*}
+Since $Z_2(1-D) = Z_2(1 - C)$, and $Z$ is independent of $Y_0$,  
+\begin{align*}
+\mathbbm{E}(U_0|Z) 
+%&= Z_0[\mathbbm{E}(Y_0|Z) - \mathbbm{E}(Y_0)] + Z_2\mathbbm{E}\{(1 - C) [Y_0 - \mathbbm{E}(Y_0|C=0) |Z\}\\
+&= Z_2 \mathbbm{E}[Y_0 - \mathbbm{E}(Y_0|C=0) | C = 0, Z] = 0
+\end{align*}
+by iterated expectations and the fact that $Z$ is conditionally independent of $Y_0$ given $C$. 
+Since $Z_2 D = Z_2 C$, a nearly identical argument gives
+\begin{align*}
+\mathbbm{E}(U_1|Z) 
+%&= (Z_0 + Z_2)[Y_0 - \mathbbm{E}(Y_0|Z)] -Z_2\mathbbm{E}\{C [Y_0 - \mathbbm{E}(Y_0|C=1) |Z\}\\
+&= -Z_2 \mathbbm{E}[Y_0 - \mathbbm{E}(Y_0|C=0) | C = 1, Z] = 0. \qedhere
+\end{align*}
+\end{proof}
+
+The final result in this section implies that the $\text{ASL}$ effect, $\mathbbm{E}(Y_1|C=1) - \mathbb{E}(Y_1|C=0)$, can be estimated as the difference of coefficients across two linear IV regressions with \emph{no intercept} and instrument set $(Z_1, Z_2)$.
+
+\begin{prop}
+\label{prop:ASLreg}
+Under Assumption \ref{assump:randchoice},
+\begin{enumerate}[(i)]
+\item $D Y = \mathbbm{E}(Y_{1}) \times(Z_1 + Z_2) + \mathbbm{E}(Y_{1}|C=0)\times (D - 1)Z_2 + V_{0}$
+\item  $D Y = \mathbbm{E}(Y_{1}) \times Z_1 + \mathbbm{E}(Y_{1}|C=1)\times D Z_2+ V_{1}$
+\end{enumerate}
+where $\mathbbm{E}(V_0|Z) = \mathbbm{E}(V_1|Z) = 0$.
+\end{prop}
+
+\begin{proof}
+By Assumption \ref{assump:randchoice}, $D = Z_1 + Z_2 C$. Hence, by Assumption \ref{assump:randchoice} (iii),
+\begin{align*}
+DY 
+%&=  (Z_1 + Z_2 C)\left\{Z_0 Y_0 + Z_1 Y_1 + Z_2[(1 - C) Y_0 + CY_1]\right\}\\
+&= Z_1 Y_1 + Z_2 C[(1 -C) Y_0 + C Y_1] = Z_1 Y_1 + Z_2 C Y_1
+\end{align*}
+because $Z_j^2 = Z_j$ for any $j$ and $Z_j Z_k = 0$ for any $j \neq k$ and, similarly, $(1 - C)^2 = (1 - C)$ and $C (1 - C) = 0$. Therefore, since $Z_2 (1 - C) = Z_2 (1 - D)$,
+\[
+ DY = (Z_1 + Z_2)Y_1 + Z_2 (D - 1) Y_1, \quad
+ DY = Z_1 Y_1 + Z_2 D Y_1.
+\]
+Now, define
+\begin{align*}
+V_0 &= (Z_1 + Z_2)[Y_1 - \mathbbm{E}(Y_1)] + Z_2(D - 1)[Y_1 - \mathbbm{E}(Y_1|C=0)]\\
+V_1 &= Z_1[Y_1 - \mathbbm{E}(Y_1)] + Z_2D[Y_1 - \mathbbm{E}(Y_1|C=1)].
+\end{align*}
+%by construction we have
+%\begin{align*}
+%Y &= \mathbbm{E}(Y_1) \times (Z_1 + Z_2) + \mathbbm{E}(Y_1 | C = 0) \times Z_2 (D - 1) + V_0\\
+%Y &= \mathbbm{E}(Y_1) \times Z_1 + \mathbbm{E}(Y_1 | C = 1) \times Z_2 D + V _1.
+%\end{align*}
+Since $Z_2(1 - D) = Z_2(1 - C)$ and $Z$ is independent of $Y_1$,
+\begin{align*}
+\mathbbm{E}(V_0|Z) 
+%&= (Z_1 + Z_2) [\mathbbm{E}(Y_1|Z) - \mathbbm{E}(Y_1) ]  - Z_2 \mathbbm{E}\{(1 - C)  [Y_1 - \mathbbm{E}(Y_1 | C=0)|Z\} \\
+&= -Z_2 \mathbbm{E}[Y_1 - \mathbbm{E}(Y_1 | C=0)|C=0, Z] = 0
+\end{align*}
+by iterated expectations and the fact that  $Z$ is conditionally independent of $Y_1$ given $C$. 
+Since $Z_2 D = Z_2 C$, a similar argument gives
+\begin{align*}
+\mathbbm{E}(V_1|Z) 
+%&= Z_1 [\mathbbm{E}(Y_1 | Z) - \mathbbm{E}(Y_1)]  + Z_2 \mathbbm{E}\{C  [Y_1 - \mathbbm{E}(Y_1 | C=1)|Z\} \\
+&= Z_2 \mathbbm{E}[Y_1 - \mathbbm{E}(Y_1 | C=1)|C=1, Z] = 0. \qedhere
+\end{align*}
+\end{proof}
+
+\subsection{Inference for ASG, ASB, and ASL}
+\label{subsec:inference}
+
+We now explain how to carry out cluster-robust inference for the ASG, ASB, and ASL effects, as implemented in our companion STATA package.
+Each of these effects can be expressed as a difference of coefficients from two just-identified linear IV regressions.
+The ASG effect is the difference of the \text{TOT} and \text{TUT} effects from Proposition \ref{prop:TOTandTUTregs}. 
+Similarly, the ASB effect is the difference of $\mathbb{E}(Y_0|C=1)$ and $\mathbbm{E}(Y_0|C=0)$ from Proposition \ref{prop:ASBreg} while the ASL effect is the difference of $\mathbbm{E}(Y_1|C=1)$ and $\mathbbm{E}(Y_1|C=0)$ from Proposition \ref{prop:ASLreg}.
+Within each pair of IV regressions the outcome variable and instrument set is identical; only the regressors differ. 
+Since our estimators of all three effects share the same structure, our discussion abstracts from the specific regressors and instruments used in each case.
+
+Let $g = 1, ..., G$ index clusters and $i = 1, ..., N_g$ index individuals within a particular cluster $g$. 
+In our experiment, a cluster is a branch-day combination and the experimentally-assigned treatment (control, forced, or choice arm) is assigned at the cluster level.
+We assume that observations are iid across clusters but potentially correlated within cluster.
+Now consider a pair of just-identified linear IV regressions given by
+$Y_{ig} = \boldsymbol{X}_{1,ig}' \boldsymbol{\theta}_0 + U_{ig}$ and $Y_{ig} = \boldsymbol{X}_{0,ig}' \boldsymbol{\theta}_1 + V_{ig}$ with common instrument vector $\boldsymbol{W}_{ig}$. 
+Stacking observations in the usual manner, e.g.\
+$\mathbf{W}_g' \equiv \begin{bmatrix}
+\boldsymbol{W}_{1g} & \cdots & 
+\boldsymbol{W}_{N_gg} 
+\end{bmatrix}$ and 
+$\mathbf{W}' = \begin{bmatrix}
+\mathbf{W}_1' & \cdots & \mathbf{W}_G'
+\end{bmatrix}$
+we can write the preceding equations in matrix form as $\mathbf{Y} = \mathbf{X}_1\boldsymbol{\theta_1} + \mathbf{U}$ and $\mathbf{Y} = \mathbf{X}_0\boldsymbol{\theta_0} + \mathbf{V}$ with instrument matrix $\mathbf{W}$.
+Now, the IV estimators for $\boldsymbol{\theta}_1$ and $\boldsymbol{\theta}_0$ can be expressed as 
+\begin{align*}
+\widehat{\boldsymbol{\theta}}_1 
+&= \left(\mathbf{W}'\mathbf{X}_1\right)^{-1}\mathbf{W}'\mathbf{Y}  = \boldsymbol{\theta}_1 + \left(\mathbf{W}'\mathbf{X}_1\right)^{-1}\mathbf{W}'\mathbf{U}\\ 
+\widehat{\boldsymbol{\theta}}_0 
+&= \left(\mathbf{W}'\mathbf{X}_0\right)^{-1}\mathbf{W}'\mathbf{Y} = \boldsymbol{\theta}_0 + \left(\mathbf{W}'\mathbf{X}_0\right)^{-1}\mathbf{W}'\mathbf{V}.
+\end{align*}
+
+%Our parameter of interest is an element of the difference $(\theta_1 - \theta_0)$, so it suffices to estimate the asymptotic variance of $(\widehat{\boldsymbol{\theta}}_1 - \widehat{\boldsymbol{\theta}}_0)$.
+%Re-arranging the preceding two equations, 
+%\begin{align*}
+%\sqrt{G} \left(\widehat{\boldsymbol{\theta}}_1  - \boldsymbol{\theta}_1\right) &= 
+% \left(\frac{\mathbf{W}'\mathbf{X}_1}{G}\right)^{-1}\left(\frac{\mathbf{W}'\mathbf{U}}{\sqrt{G}}\right) = \left( \frac{1}{G} \sum_{g=1}^G \mathbf{W}_g' \mathbf{X}_{1,g}\right)^{-1}\left(\frac{1}{\sqrt{G}} \sum_{g=1}^G\mathbf{W}_g' \mathbf{U}_g\right) \\
+%\sqrt{G} \left(\widehat{\boldsymbol{\theta}}_0  - \boldsymbol{\theta}_0\right) &= 
+% \left(\frac{\mathbf{W}'\mathbf{X}_0}{G}\right)^{-1}\left(\frac{\mathbf{W}'\mathbf{V}}{\sqrt{G}}\right) = \left( \frac{1}{G} \sum_{g=1}^G \mathbf{W}_g' \mathbf{X}_{0,g}\right)^{-1}\left(\frac{1}{\sqrt{G}} \sum_{g=1}^G\mathbf{W}_g' \mathbf{V}_g\right).
+%\end{align*}
+%Now, define $\mathbf{Q}_0 \equiv \mathbb{E}[\mathbf{W}_g'\mathbf{X}_{0g}]$ and $\mathbf{Q}_1 \equiv \mathbb{E}[\mathbf{W}_g'\mathbf{X}_{1g}]$ and suppose that these expectations exist and that the matrices $\mathbf{Q}_0$ and $\mathbf{Q}_1$ are invertible.
+Then, as $G \rightarrow \infty$
+%\[
+% \left( \frac{1}{G} \sum_{g=1}^G \mathbf{W}_g' \mathbf{X}_{0,g}\right)^{-1} \rightarrow_p \mathbf{Q}_0^{-1}, \quad
+% \left( \frac{1}{G} \sum_{g=1}^G \mathbf{W}_g' \mathbf{X}_{1,g}\right)^{-1} \rightarrow_p \mathbf{Q}_1^{-1} \quad
+%\]
+%by the continuous mapping theorem.
+By our experimental design and exclusion restriction, $\mathbf{W}_{ig}$ is independent of $U_{ig}$ both unconditionally and conditional on cluster size. 
+%Therefore,
+%\begin{align*}
+%\mathbb{E}[\mathbf{W}_g' \mathbf{U}_g] &=  \mathbb{E}\left[ \sum_{i=1}^{N_g} \mathbf{W}_{ig} U_{ig} \right] = \mathbb{E}_{N_g}\left[ \mathbb{E}\left\{\left.
+\sum_{i=1}^{N_g} \mathbf{W}_{ig} U_{ig} \right| N_g \right\}\right]\\
+%&= \mathbb{E}_{N_g}\left[ \sum_{i=1}^{N_g} \mathbb{E}(\mathbf{W}_{ig} U_{ig}|N_g)\right] = \mathbb{E}_{N_g}\left[ \sum_{i=1}^{N_g} \mathbb{E}(\mathbf{W}_{ig}U_{ig})\right] = 0
+%\end{align*}
+%by iterated expectations, and similarly smilarly, $\mathbb{E}[\mathbf{W}_g'\mathbf{V}_g] = \mathbf{0}$. 
+%Thus, under mild regularity conditions (e.g.\ finite fourth moments), as $G \rightarrow \infty$  we have
+%\[
+%\frac{1}{\sqrt{G}} \sum_{g=1}^G \mathbf{W}_g' \otimes \begin{bmatrix} \mathbf{U}_g \\ \mathbf{V}_g \end{bmatrix} \rightarrow_d \text{N}(\mathbf{0}, \boldsymbol{\Omega})
+%\]
+%where the heteroskedasticity-- and cluster--robust variance-covariance matrix $\boldsymbol{\Omega}$ is 
+%\[
+%\boldsymbol{\Omega} \equiv 
+% \mathbb{E} \left[\left(\mathbf{W}_g \mathbf{W}_g' \right)\otimes \begin{pmatrix}
+%\mathbf{U}_g \mathbf{U}_g' & \mathbf{U}_g \mathbf{V}_g' \\
+%\mathbf{V}_g \mathbf{U}_g' & \mathbf{V}_g \mathbf{V}_g'  
+%\end{pmatrix} \right] \equiv \begin{bmatrix}
+%\Omega_{UU} & \Omega_{UV} \\
+%\Omega_{VU} & \Omega_{VV}
+%\end{bmatrix}.
+%\]
+%Therefore, the joint limiting distribution of $\widehat{\boldsymbol{\theta}}_1$ and $\widehat{\boldsymbol{\theta}}_0$ is given by
+%\[
+%\begin{bmatrix}
+%\sqrt{G}(\widehat{\boldsymbol{\theta}}_1 - \boldsymbol{\theta}_1)\\
+%\sqrt{G}(\widehat{\boldsymbol{\theta}}_0 - \boldsymbol{\theta}_0)
+%\end{bmatrix} \rightarrow_d
+%\begin{bmatrix}
+%\mathbf{Q}_1^{-1} & \mathbf{0} \\
+%\mathbf{0} & \mathbf{Q}_0^{-1} 
+%\end{bmatrix}
+%\begin{bmatrix}
+%\boldsymbol{\xi}_U \\ \boldsymbol{\xi}_V 
+%\end{bmatrix}, \quad
+%\begin{bmatrix}
+%\boldsymbol{\xi}_U \\ \boldsymbol{\xi}_V 
+%\end{bmatrix} \sim \text{N}\left(\begin{bmatrix} \mathbf{0} \\ \mathbf{0}\end{bmatrix},
+%\begin{bmatrix}
+%\Omega_{UU} & \Omega_{UV} \\
+%\Omega_{VU} & \Omega_{VV}
+%\end{bmatrix}\right)
+%\]
+%from which it follows by the continuous mapping theorem that
+%\[
+%\sqrt{G}\left[ (\widehat{\boldsymbol{\theta}}_1 - \widehat{\boldsymbol{\theta}}_0 ) - (\boldsymbol{\theta}_1 - \boldsymbol{\theta}_0)\right] 
+%\rightarrow_d
+%\begin{bmatrix}
+%\mathbf{Q}_1^{-1} & -\mathbf{Q}_0^{-1}
+%\end{bmatrix}
+%\begin{bmatrix}
+%\boldsymbol{\xi}_U \\ \boldsymbol{\xi}_V 
+%\end{bmatrix}.
+%\]
+%To use this result in practice, we estimate the standard errors of  $(\widehat{\boldsymbol{\theta}}_1 - \widehat{\boldsymbol{\theta}}_0)$ as the square root of the diagonal elements of the matrix
+Hence, by a standard argument and under mild regularity conditions, the following expression provides a consistent, cluster robust estimator of $\widehat{\text{Avar}}(\widehat{\boldsymbol{\theta}}_1 - \widehat{\boldsymbol{\theta}}_0)$
+\[
+\widehat{\text{Avar}}(\widehat{\boldsymbol{\theta}}_1 - \widehat{\boldsymbol{\theta}}_0) 
+= \begin{bmatrix}
+\left(\mathbf{W}'\mathbf{X}_1\right)^{-1} &
+-\left(\mathbf{W}'\mathbf{X}_0\right)^{-1} 
+\end{bmatrix}
+\begin{bmatrix}
+\mathbf{S}_{UU}& \mathbf{S}_{UV}\\
+\mathbf{S}_{UV}'& \mathbf{S}_{VV}
+\end{bmatrix} 
+\begin{bmatrix}
+\left(\mathbf{X}_1'\mathbf{W}\right)^{-1} \\
+-\left(\mathbf{X}_0'\mathbf{W}\right)^{-1} 
+\end{bmatrix}
+\]
+where we define the IV residuals
+$\widehat{\mathbf{U}}_g \equiv \mathbf{Y}_g - \mathbf{X}_{1,g}\widehat{\boldsymbol{\theta}}_1$ and
+$\widehat{\mathbf{V}}_g \equiv \mathbf{Y}_g - \mathbf{X}_{0,g}\widehat{\boldsymbol{\theta}}_0$ along with the matrices
+$\mathbf{S}_{UU} \equiv \sum_{g=1}^G \mathbf{W}_g' \widehat{\mathbf{U}}_g \widehat{\mathbf{U}}_g' \mathbf{W}_g$,
+$\mathbf{S}_{UV} \equiv \sum_{g=1}^G \mathbf{W}_g' \widehat{\mathbf{U}}_g \widehat{\mathbf{V}}_g' \mathbf{W}_g$, and finally
+$\mathbf{S}_{VV} \equiv \sum_{g=1}^G \mathbf{W}_g' \widehat{\mathbf{V}}_g \widehat{\mathbf{V}}_g' \mathbf{W}_g$.
+In our application the number of clusters, $G$, is large.
+If desired, an \emph{ad hoc} degrees of freedom correction can be applied by multiplying the associated standard errors by $\sqrt{G/(G-1)}$.
 

### 2024-05-21 ECTA submission/donde_ecta.tex
ecta submission

@@
 %            [final] for the prepublication
-\documentclass[ecta,nameyear,final]{econsocart}
+\documentclass[ecta,nameyear,draft]{econsocart}
+%\documentclass[]{econsocart}
 %
@@
 \newtheorem{lem}{Lemma} 
+\usepackage{enumerate}
 
@@
 Our experiment covers just under 5,000 pawnshop clients in 6 of our partner lender's Mexico City branches.
-Our control arm illustrates the costs of the status quo contract: fully \emph{44\%} of borrowers default, losing lose their pawn along with any payments made towards principal.\footnote{High pawn default rates are common, in the US they oscilate around 15\% (\url{https://tinyurl.com/yc2x5bjf}).} Our ``commitment choice'' arm gives borrowers the chance to opt into a structured repayment contract when taking a loan.
+Our control arm illustrates the costs of the status quo contract: fully \emph{44\%} of borrowers default, losing lose their pawn along with any payments made towards principal.\footnote{High pawn default rates are common, in the US they oscillate around 15\% (see \href{https://tinyurl.com/yc2x5bjf}{here}).} Our ``commitment choice'' arm gives borrowers the chance to opt into a structured repayment contract when taking a loan.
 The structured contract requires borrowers to make three monthly payments rather than one balloon payment at the end, with each monthly payment including the accrued interest at that time as well as a nominal fee of 2\% of that month's payment if the payment is delinquent.
@@
 \cite{chamberlain2011bayesian} uses a closely related assumption to develop a theory of optimal treatment choice.}
-It also has testable implications that we fail to reject in our empirical context.\footnote{See \ref{append:exclusion} for details.}
+It also has testable implications that we fail to reject in our empirical context.\footnote{See \autoref{sec:testing_exclusion} for details.}
 Under this restriction, the controlled choice design point identifies the TOT, TUT, ASG, ASB, and ASL effects described above.
@@
 This difference is what allows our design to point identify the ASG and related quantities.}
-We further provide simple, regression-based estimators for each of these causal parameters, along with procedures for computing associated cluster-robust standard errors.\footnote{See \ref{append:randchoice} for details.} A companion STATA package provides easy-to-use commands that implement our estimators and standard errors.
+A companion STATA package provides simple, regression-based estimators for each of these causal parameters, along with appropriate cluster-robust standard errors.\footnote{See \autoref{sec:estimation_inference} for details.}
 The controlled choice design could be useful in other experimental settings where the question of interest centers on the merits of paternalism, public or private, or the relationship between choice and treatment effects.
@@
 Our study also speaks to recent research on the effects of payment frequency.
-While experiments in microfinance markets have \textit{not} shown the same benefits from providing a more regularized repayment environment as we find here \citep{Pande, barboni2023flexible}, these experiments differ from ours in two important ways: they are performed on top of already highly structured micro-finance contracts, and they involve borrower pools who may have selected into that type of lending precisely because it provides structure \cite{Murdoch}.
+While experiments in microfinance markets have \textit{not} shown the same benefits from providing a more regularized repayment environment as we find here \citep{Pande, barboni2023flexible}, these experiments differ from ours in two important ways: they are performed on top of already highly structured micro-finance contracts, and they involve borrower pools who may have selected into that type of lending precisely because it provides structure \cite{bauer2012behavioral}.
 These differences may explain why \citep{Pande} finds almost no default in the control group, in stark contrast to our setting of high default.
@@
 
-\noindent \textbf{Appraising and lending.} Lender P takes gold jewelry as collateral in exchange for a fraction of the value of the piece, in cash.
+%\hfill \newline
+%\noindent \textbf{Appraising and lending.} 
+\paragraph*{Appraising and Lending} Lender P takes gold jewelry as collateral in exchange for a fraction of the value of the piece, in cash.
 No other collateral and no credit history checks are needed.
 The transaction takes less than 10 minutes and is conducted at the branch in person between the client and the appraiser (i.e.
-a teller, see Figure \ref{PawnshopPicture}).
+a teller).
+%, see Figure \ref{PawnshopPicture}). 
 The appraiser weighs the gold piece and runs tests on its purity.
@@
 
-\noindent \textbf{Contract.} Lender P had only one type of contract, henceforth the \textit{status quo} contract.
+%\hfill \newline
+%\noindent \textbf{Contract.} 
+\paragraph*{Contract} Lender P had only one type of contract, henceforth the \textit{status quo} contract.
 It stipulated that the interest rate was 7\% \textit{per month} compounded daily on the outstanding amount of the loan.
@@
 
-\noindent \textbf{Borrowers.} The clients that pawned understood these terms well (as we verified in interviews).\footnote{87\% of clients report in our survey that they have pawned before.} These clients have little or no access to other types of loans and they value the convenience of pawn borrowing.
+%\hfill \newline
+%\noindent \textbf{Borrowers.} 
+\paragraph*{Borrowers} The clients that pawned understood these terms well (as we verified in interviews).\footnote{87\% of clients report in our survey that they have pawned before.} These clients have little or no access to other types of loans and they value the convenience of pawn borrowing.
 This population of pawn borrowers is economically vulnerable:  30\% of them could not pay either water, electricity \& gas or rent in the past 6 months; 89\% said they are pawning because of an emergency, and only 12\% stated it was to use in a ``non-urgent expense''.
@@
 
-\noindent \textbf{Many borrowers lose their pawn.} Our context is also one with high borrower default: 43\% of clients lose their pawn in a time span of 230 days from the date of pawning.
+%\hfill \newline
+%\noindent \textbf{Many borrowers lose their pawn.} 
+\paragraph*{Many borrowers lose their pawn.}
+Our context is also one with high borrower default: 43\% of clients lose their pawn in a time span of 230 days from the date of pawning.
 One potential explanation for high default is that clients are really just knowingly selling their gold piece through a pawn contract on which they intend to default.
-This appears unlikely for several reasons: (a) clients can easily sell the gold and obtain a higher amount of instant cash at gold-buying stores located close to almost all our pawnshop branches (see Figure \ref{GoldBuyers}), (b) the reported subjective value of the pawn is larger than the appraised value for 83\% of clients, (c) among those that lose their pawn, 29\% paid a positive amount towards its recovery and on average paid 42\% of the value of their loan (see Figure \ref{proxy_naive} in Appendix) --- this can only be rationalized if they expected to recover their pawn, and (d) 72\% of borrowers report a 100\% probability of repaying their loan (and 98\% at least a 50\% chance of repaying) in our baseline survey at the time they take the loan.
+This appears unlikely for several reasons: (a) clients can easily sell the gold and obtain a higher amount of instant cash at gold-buying stores located close to almost all our pawnshop branches,
+%(see Figure \ref{GoldBuyers})
+(b) the reported subjective value of the pawn is larger than the appraised value for 83\% of clients, (c) among those that lose their pawn, 29\% paid a positive amount towards its recovery and on average paid 42\% of the value of their loan (see Figure \ref{proxy_naive} in Appendix) --- this can only be rationalized if they expected to recover their pawn, and (d) 72\% of borrowers report a 100\% probability of repaying their loan (and 98\% at least a 50\% chance of repaying) in our baseline survey at the time they take the loan.
 %Note that high default could be detrimental from the lender's point of view, since it may reduce the likelihood that the client becomes a return customer.
@@
     \text{Financial Cost}_i =&  \sum_t P^I_{it} +\sum_t P^F_{it}  
-     + \mathds{1}(\text{Default}_i) \times (\text{Value}_i-\text{Loan}_i + \sum_t P^c_{it})
+     + \mathds{1}(\text{Default}_i) \times \left(\text{Value}_i-\text{Loan}_i + \sum_t P^c_{it}\right)
 \end{align*}
-
-\noindent where $t$ indexes days, and $\mathds{1}(\text{Default}_i)$ is an indicator function for defaulting.
+where $t$ indexes days, and $\mathds{1}(\text{Default}_i)$ is an indicator function for defaulting.
 Because the period of the loan is only 90 days we do not apply discounting in calculating costs.
@@
 
-As a second measure of cost we calculate the Annual Percentage Rate (APR) in order to express the cost as a percentage of the loan, per year, inclusive of default costs.\footnote{Loan term takes into account the entire loan period, including extensions of the loan through refinancing.} The standard definition is given in the following formula:
-\begin{align*}
-    (\text{APR})_i =&\left( 1 + \frac{\frac{\text{Financial Cost}_i}{\text{Loan}_i}}{\text{loan term}_i}\right)^{\text{loan term}_i}-1 
-\end{align*}
-
-\begin{figure}
-    \begin{center}
-    \begin{subfigure}{.45\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_fc.pdf}
-        \caption{}
-    \end{subfigure}
-     \begin{subfigure}{0.45\textwidth}
-       \centering
-      \includegraphics[width=\textwidth]{Figuras/hist_apr.pdf}
-      \caption{}
-    \end{subfigure}
-    \end{center}
- \caption{Financial cost.
-Panel (a) presents a histogram of financial cost for the control group.
-The figure plots separately the financial cost separately for borrowers who lose the pawn (blue) and those that recover it (transparent).
-Panel (b) is analogous but displays the APR.}
-     \label{fc_hist}
-      %\footnotesize{ } \textit{Do file: }  \texttt{hist\_fc.do}
-\end{figure}
-
-Figure \ref{fc_hist}(a) plots a histogram of this financial cost in pesos for all loans in the experiment, stratified by whether we observed that they ended in default or recovery of the pawn.
-Figure \ref{fc_hist}(b) shows the analogous histogram for the APR.
-%defaulted (44\%), recovered their pawn (43\%), or whether they are censored in our data (13\%). 
-We see that borrowers who default incur higher costs; part of this is mechanical as losing their collateral is part of the cost.
-Most of the APR costs indeed come from clients who do not recover their pawn.
-%The second thing to note is that those that are not closed at the end of our sample period have already incurred substantial financial cost, even though they have not defaulted yet.
-
-%Of those who renew, 83\% lose the pawn.
-Figure \ref{fc_hist}(a) suggest that financial cost is significant, even for those that do recover their pawn.
-Panel (b) normalizes the cost by loan size.
-It shows that as a percentage of their pawn, most of the cost comes from clients that do not recover their pawn.
-For them the cost is between 140\% and 250\% of the loan value.
-%{The difference between panel (a) and (b) arises since clients who lose their pawn tend to be those that pledge cheaper pieces.}
+As a second measure of cost we calculate the Annual Percentage Rate (APR) in order to express the cost as a percentage of the loan, per year, inclusive of default costs.
+The standard definition is given in the following formula: $(\text{APR})_i =\left( 1 + \frac{\frac{\text{Financial Cost}_i}{\text{Loan}_i}}{\text{loan term}_i}\right)^{\text{loan term}_i}-1 $
 
@@
 
+%\hfill \newline
 \subsection{Treatment arms and randomization}
 
-\noindent \textbf{The Commitment Contract.} For the purpose of the experiment we designed a new contract that is identical to the status quo contract except that, informed by the design of micro-lending contracts, it enhances the regularity and salience of payments as a way to encourage repayment \citep{morduch1999microfinance, bauer2012behavioral}.
+%\hfill \newline
+%\noindent \textbf{The Commitment Contract.} 
+\paragraph*{The Commitment Contract} For the purpose of the experiment we designed a new contract that is identical to the status quo contract except that, informed by the design of micro-lending contracts, it enhances the regularity and salience of payments as a way to encourage repayment \citep{morduch1999microfinance, bauer2012behavioral}.
 It has the same interest rate (7\% \textit{per month}) which accumulates daily on outstanding debt, the same loan size/collateral ratio (70\%), and the same loan term (90 days, and a grace period of 15 days).
@@
 The commitment contract however requires the client to make regular monthly payments for the duration of the contract, with the principal and interest payments split evenly across the three months of the contract (day 30, 60 and 90 after loan disbursement).
-The importance of this monthly payment was made salient in the contract and payment receipts (see Figure \ref{PaperSlip}), and by the levying of a nominal fee (2\% of minimum due) on individuals who fell behind in their payments.
+The importance of this monthly payment was made salient in the contract and payment receipts, and by the levying of a nominal fee (2\% of minimum due) on individuals who fell behind in their payments.
 %\textcolor{red}{The idea that the fee itself is not driving the treatment is reinforced later in the paper where we show financial benefits many times larger than the fee, as well as treatment effects even on those who would fail to recover pawns and hence not pay the fee.}
@@
 
-\noindent \textbf{Treatment Arms.} Treatments were randomized at the branch-day level.
+%\hfill \newline
+%\noindent \textbf{Treatment Arms.} 
+\paragraph*{Treatment Arms} 
+Treatments were randomized at the branch-day level.
 Each day a computer randomly assigned which types of contracts were on offer that day in the branch, and the IT system would only offer these.
@@
 
-\begin{figure}     
+\begin{figure}[htbp]    
 \begin{center}
-\begin{subfigure}{\textwidth}
-        \includegraphics[width=\textwidth]{Figuras/consort.pdf}
-    \end{subfigure}
+\includegraphics[width=0.9\textwidth]{Figuras/consort.pdf}
   \end{center}
@@
 
-\vspace{.2in}
-\noindent \textbf{Randomization.}  We implemented the experiment in 6 branches of Lender $P$ beginning on September 6, 2012.
+%\hfill \newline
+%\noindent \textbf{Randomization.}  
+\paragraph*{Randomization} We implemented the experiment in 6 branches of Lender $P$ beginning on September 6, 2012.
 The branches were selected by Lender $P$ to be dispersed across Mexico City and have varying sizes.
@@
 
-\noindent \textbf{Timeline.} Figure \ref{exp_description} shows the experimental timeline along with the length of time for which we observe payments.
+%\hfill \newline
+%\noindent \textbf{Timeline.} 
+\paragraph*{Timeline} Figure \ref{exp_description} shows the experimental timeline along with the length of time for which we observe payments.
 For loans made in the first week of the experiment, we observe up to 338 subsequent days of loan information; for loans made in the last week we observe up to 235 days.
@@
 
-\noindent \textbf{Explanation.} Since we are interested in measuring the effect of different contract terms on client behavior, it is important that clients understand these terms.
-To ensure this, we built two ``check-points'' as follows.
-Two enumerators were present in each branch for the whole day during the duration of our experiment.
-At the first checking, these enumerators explained the contract terms to clients, emphasizing that the frequent payment contract involved the commitment to pay a third of the outstanding amount \underline{each month}, along with the nature of the fees associated with the Commitment arm.
-Figure \ref{ExplanatoryMaterial} presents an excerpt of the materials we used to explain the contracts, translated into English.
+%\hfill \newline
+%\noindent \textbf{Explanation.} 
+\paragraph*{Explaining the Contracts}
+We made sure clients understood the contract terms.
+First, we had full-time enumerators explaining contract terms to clients.
 The explanation took about 3-5 minutes and continued until the client said she understood the contract terms.
 Enumerators then asked clients to explain the contract back to them before correcting any misunderstandings.
-At the second check-point the appraiser made clients read the ``Contract Terms Summary'' sheet shown in Figure \ref{PaperSlip} before they signed the contract.
-This summary was a piece of paper given to clients after their piece had been appraised and the size of the loan determined, but before they signed their contract.
-The appraiser read it aloud and then asked the client to sign it as proof of understating.
+Second, the appraiser gave clients the ``Contract Terms Summary'' and read it out loud to them before after their piece had been appraised but before they signed the contract.
 %The sheet clearly indicates that this contract is a monthly payment one (numeral 1), that there is a penalty of 2\% for paying late (numeral 2), and the 3 payment dates (numeral 3).
@@
 
-\noindent \textbf{Administrative data.} The study exploits two types of data: administrative data from the lender, and a short survey that we implemented.
+%\hfill \newline
+%\noindent \textbf{Administrative data.} 
+\paragraph*{Administrative Data}
+The study exploits two types of data: administrative data from the lender, and a short survey that we implemented.
 The administrative data contains a unique identifier for each client, an identifier for the piece she is pawning, and the transactions relating to that piece.
@@
 
-\noindent \textbf{Survey data.} An additional team of enumerators stationed in each branch asked clients to complete a 5-minute survey \textit{before} going to the teller window to appraise their piece and before they learned which contracts would be available on that day.
+%\hfill \newline
+%\noindent \textbf{Survey data.} 
+\paragraph*{Survey Data} An additional team of enumerators stationed in each branch asked clients to complete a 5-minute survey \textit{before} going to the teller window to appraise their piece and before they learned which contracts would be available on that day.
 The survey was intentionally short to avoid discouraging the potential clients from pawning.
 It measured demographics, proxies for income/wealth, education, present-biased preferences, experience pawning, if family or friends commonly asked for money, how time-consuming and costly it was to come to the branch, the subjective probability of recovering the piece that they intended to pawn, the subjective value of their piece in money terms (how much money they would sell it for), among others.
-We surveyed 7,210 clients, and our survey response rate was 78\% among clients who took loans.\footnote{Appendix \ref{baseline_survey} transcribes the questionnaire in English.} %\footnote{We also surveyed clients before and after the experiment, so our survey covers a larger sample that we are not using in this paper.}.
+We surveyed 7,210 clients, and our survey response rate was 78\% among clients who took loans.
+%\footnote{We also surveyed clients before and after the experiment, so our survey covers a larger sample that we are not using in this paper.}.
 We only use the survey in Section \ref{Paternalism} of the paper.
@@
 
-\noindent \textbf{Attrition.} There are two main channels through which attrition could complicate the interpretation of our results.
+%\hfill \newline
+%\noindent \textbf{Attrition.} 
+\paragraph*{Attrition} There are two main channels through which attrition could complicate the interpretation of our results.
 The first, and more serious, is the possibility that clients might change their pawning decisions in response to the treatment they encounter in a given branch on the day they enter the branch.
@@
 There is no difference at all between the Control and Forced Commitment arm in terms of the number of pawns per branch-day.
-Although we cannot reject equality across the three arms (p-value=0.21), the Choice arm appears to have a somewhat larger number of borrowers than the Control and Forced arms.\footnote{p-value=0.23 and 0.12 respectively.} This seems to be due to sampling variability.
+%Although we cannot reject equality across the three arms (p-value=0.21), the Choice arm appears to have a somewhat larger number of borrowers than the Control and Forced arms.\footnote{p-value=0.23 and 0.12 respectively.} This seems to be due to sampling variability.
 The differences across arms are smaller when we look at medians, or when we look at the number of borrowers pawning (some borrowers pawn more than one piece).
@@
 The only noticeable difference is that the choice arm has a few more positive outliers.\footnote{If we winzorize at the 90th percentile, the mean number of branch-day pawns becomes identical across arms.}
-
-\begin{table}
-\caption{Limited and balanced attrition}
-\label{attrition_table}
-\begin{center}
-\scriptsize{\input{./Tables/Attrition.tex}}
-\end{center}
-\legend{Each row in this table 
- corresponds to a regression.
-The dependent variables are: the number of pawns-loans originated per day per branch, the number of borrowers per day-branch, a variable indicating whether a person who answered the baseline survey (before knowing contract terms) ended up pawning, and an indicator of whether the person that obtained the loan answered the baseline survey.
-Each dependent variable is regressed in a multivariate OLS regression against the experimental arms indicators (control, forced commitment, choice).
-The table reports the coefficients on each of these indicators, as well as the p-value of an F-test of the null hypothesis of equality of the three coefficients.
-Figure \ref{boxplot_attrition}, in the appendix shows a box-plot of the first two variables, showing the distribution across arms is balanced.}
-%\textit{Do file: } \texttt{ss\_att.do}
-\end{table}
-
-The bottom panel of Table \ref{attrition_table} shows balance in a more focused way, given that the surveys were conducted prior to the revelation of treatment status.
+%The bottom panel of Table \ref{attrition_table} shows balance in a more focused way, given that the surveys were conducted prior to the revelation of treatment status.
 We find that in no arm did more than three percent of individuals who responded to the survey go on to refuse loans.
@@
 This is consistent with the findings of Table \ref{SS}.
+
 % To test for this, we examine the number of loans given per branch-day, with specific attention to whether the Forced Commitment arm led to a lower number of borrowers per day.
@@
 
-\noindent \textbf{Balance.} Table \ref{SS} presents summary statistics for the sample of actual borrowers across arms, showing that our randomization succeeded in achieving balance across the experimental arms.
+%\hfill \newline
+%\noindent \textbf{Balance.} 
+\paragraph*{Balance} Table \ref{SS} presents summary statistics for the sample of actual borrowers across arms, showing that our randomization succeeded in achieving balance across the experimental arms.
 Panel A uses administrative data for the universe of borrowers in each arm, and shows that loan balances and the days on the week on which individuals pawned are comparable across arms.
@@
 
-\begin{table}[htbp]
-\caption{Summary statistics and Balance}
-\label{SS}
-\begin{center}
-\scriptsize{\input{./Tables/SS.tex}}
-\end{center}
-\legend {This table has two panels.
-Panel A uses administrative data at the loan level, while Panel B uses survey data.
-Each row in this table corresponds to a regression, where the level of observation is the individual loan originated.
-The dependent variables of these regressions are displayed in the first column.
-Each dependent variable is regressed in a multivariate OLS regression against the experimental arms indicators (control, forced commitment, choice).
-The table reports the coefficients on each of these indicators, as well as the p-value an F-test of the null hypothesis of equality of the three coefficients.
-The admin data was a very limited set of pre-determined variables.
-The dependent variables in Panel A are the loan amount in pesos, and an indicator for whether the day of the loan origination was a weekday (as opposed to weekend).
-The dependent variables in Panel B from the survey (see the questions in Table \ref{baseline_survey}.
-Subjective value of the pawn (how much would the client be willing to sell it for (Q3), an indicator for having trouble paying bills in the last 6-months (Q28), present bias (constructed from questions Q10 and Q29 in the standard way as in \cite{Ashraf}), an indicator for whether they make expenses budget for the month ahead of time.
-The subjective probability of recovery was elicited a la Manski (from 0 to 100 what is the probability that you will recoup your pawn), pawned before is a dummy=1 if the client declares to have pawned before (although not necessarily with Lender $P$) age is in year, +High-school is a dummy that indicates if the client has completed high school.
-}
-%\textit{Do file: } \texttt{ss\_att.do}
-\end{table}
-
 \section{Average Treatment Effects} \label{Experiment}
@@
 
-\noindent \textbf{Specification.} Table \ref{main_impact_table} presents estimates and standard errors from a standard pooled experimental regression 
+%\hfill \newline
+%\noindent \textbf{Specification.} 
+\paragraph*{Specification} Table \ref{main_impact_table} presents estimates and standard errors from a standard pooled experimental regression 
 \begin{equation} \label{basic_reg}
@@
 \begin{center}
-\resizebox{0.9\textwidth}{!}{
+\resizebox{1.0\textwidth}{!}{
 \scriptsize{\input{./Tables/decomposition_main_te.tex}}
@@
 
-\noindent \textbf{Results.} The results are stark.
+%\hfill \newline
+%\noindent \textbf{Results.} 
+\paragraph*{Results} The results are stark.
 The Forced Commitment arm yields large and significant decreases in the cost of loans to clients, as measured either by financial cost or APR.
@@
 
-\noindent \textbf{Intermediate outcomes.} To shed light on the mechanisms behind the ATEs discussed above, Table \ref{mechanisms} shows how commitment affects a number of intermediate outcomes.
+%\hfill \newline
+%\noindent \textbf{Intermediate outcomes.} 
+\paragraph*{Intermediate Outcomes} To shed light on the mechanisms behind the ATEs discussed above, Table \ref{mechanisms} shows how commitment affects a number of intermediate outcomes.
 One can group the types of intermediate outcomes into two categories: measures of the speed of pawn recovery, and measures of the decision of when to default.
@@
 One interpretation of this bifurcation is that the Forced commitment contract forces borrowers to think earlier about whether they will indeed be able to eventually recover their pawn, and separates borrowers into those ``selling'' their pawn and those recovering it, reducing the share of undecided borrowers that end up paying interest and end up losing the pawn anyway.
-This mechanism may also help to explain why the Forced commitment contract does not increase the number of visits to the branch to pay (col 10): those recovering their pawn visit more, but those defaulting have 0.20 fewer
-
-\begin{landscape}
-\begin{table}
-\caption{Effects on intermediate outcomes}
-\label{mechanisms}
-\begin{center}
-\resizebox{1.30\textwidth}{!}{
-\scriptsize{\input{./Tables/mechanism.tex}}
-}
-\end{center}
-\legend{This table explores treatment effects in ``intermediate variables''.
-Each column represents regression output for different dependent variables following equation (\ref{basic_reg}).
-Panel A focuses on variables related to the speed of payment.
-While Panel B focuses on variables related to default, and Panel C related to visits.
-% The outcome variables are as follows:  number of days elapsed between origination and first payment (col 1); percentage of the loan paid in the first payment (col 2); probability of recovery in the first visit (col 3); loan duration is the number of days the borrower took to payoff her loan for those that recover, the number of days until default for those that default, and the maximum number of days we observe them in the sample for those that have not recovered or defaulted (col 4); loan duration conditional on recovery; an indicator for paying a positive amount towards recovery but nonetheless losing the pawn (col 6); the percentage or the loan paid, conditional on defaulting --`wasted payments' (col 7).
-Column 8 uses the phrase `selling the pawn' for a dummy variable indicating the borrower did not pay any amount towards recovery and lost the pawn.
-Moreover, (col 9) shows that treatment effects are concentrated in the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery.
-The dependent variable in column 10 is the number of day-visits to the branch (measured by the existence of transactions that day associated with our particular pawn), while column 11 conditions on borrowers that lost the pawn.
-Each regression includes branch and day-of-week FE. Standard errors are clustered at the branch-day level.}
-%\textit{Do file: } \texttt{mechanisms.do}
-\end{table}
-
-\end{landscape}
-
-\noindent visits (col 11).\footnote{Figure \ref{hist_payments} plots the histogram of the timing of payments in each arm, and shows that commitment does appear to bind in that it generates a highly regular pattern of payments at 30, 60, and 90 days after the loan is taken.} Finally, Column 9 shows that treatment effects are concentrated in the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery.
-
-\noindent \textbf{Other costs.} We have shown that forcing borrowers to take the monthly payment contract significantly reduces their financial costs.
+This mechanism may also help to explain why the Forced commitment contract does not increase the number of visits to the branch to pay (col 10): those recovering their pawn visit more, but those defaulting have 0.20 fewer visits (col 11).
+Finally, Column 9 shows that treatment effects are concentrated in the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery.
+
+%\noindent \textbf{Other costs.} 
+\paragraph*{Other Costs} We have shown that forcing borrowers to take the monthly payment contract significantly reduces their financial costs.
 Although the paper focuses on financial costs, we consider three additional costs here.
@@
 Our third extra cost considers this higher value.
-
-Table \ref{table_robustness_fc} shows results.
-Panel A reports financial cost in pesos, while Panel B shows APR.
-Columns (1) and (6) replicate our previous results for comparability.
-Columns (2) and (7) of Table \ref{table_robustness_fc} use the subjective value of the pawn reported by the borrower rather than its appraised value.
-Columns (3) and (8) adjust for self-reported transport costs per visit plus an entire day's wage, both multiplied by the number of visits that each individual made.\footnote{For clients who did not complete the individual survey, we adjust using the mean self-reported transport cost among respondents of the respective branch.} Columns (4) and (9) adjust to consider the liquidity cost.
-Finally, columns (5) and (10) include all three changes together.
-The main takeaway from the table is that results are quite robust to including a much expanded measure of costs.
-
-\begin{table}
-\caption{Effects on more comprehensive cost measures}
-\label{table_robustness_fc}
-\begin{center}
-\scriptsize{\input{./Tables/fc_robustness.tex}}
-\end{center}
- \legend{ This table augments the measure of financial cost presented in Table \ref{main_impact_table} with measures of transaction costs, subjective costs, and adjustments for liquidity costs. 
- % Column 1 replicates the result of column 1 of Table \ref{main_impact_table} to ease comparability.
-Column 2 uses the subjective value of the pawn instead of the assessed gold value.
-Column 3 uses the cost from column 1 but adds to it the self-reported transport cost (most use public transport, imputing missing values with the average) as well as a whole day's minimum wage as a proxy for lost time.
-Column 4 ignores the `liquidity' cost in the financial cost formula by subtracting the interest of 7\% per month for each peso paid.
-Column 5 applies all these extra costs at the same time.
-Columns 6 to 10 apply the analogous changes to the APR formula.
- Each regression includes branch and day-of-week FE. Standard errors are clustered at the branch-day level.}
-
-%\textit{Do file: } \texttt{fc\_robustness.do}
-\end{table}
-
-\noindent \textbf{Repeat Pawns.}
+Table \ref{table_robustness_fc} shows results are robust to all these changes.
+
+%\hfill \newline
+%\noindent \textbf{Repeat Pawns.}
 %Another way to push the analysis towards a consideration of borrower welfare is the conjecture that if clients exposed to the installment contract like it, they will be more likely to come back vis-a-vis those that got status quo contract.\footnote{\cite{Laibson2018} hypothesizes that consumers use ``experienced utility'' as a guide to make future purchases in this way.} This is indeed what we find in the data.
@@
 We can first ask whether the individual ever takes a loan after the initial study loan, an analysis which is simply experimental.
+\paragraph*{Repeat Pawns}
 Table \ref{repeat_loans} explores the effects of treatment on future pawning behavior.
@@
 
-\noindent \textbf{Censoring of Loan Completion.}
+%\hfill \newline
+%\noindent \textbf{Censoring of Loan Completion.}
+\paragraph*{Censoring of Loan Completion}
 The window of time during which we were able to observe borrower behavior was limited in each branch, meaning that there were loans that we do not see completed (particularly those pawns that were rolled over for one or two further 90-day spells).
 Overall, 13\% of all experimental loans are censored, meaning that they neither default nor repay within the observation window.
-In the prior analysis we handle this issue by using outcomes such as ``did not default'', which are well-defined even when we do not observe the completion of the loan, and by only considering costs that we observe directly.
-We have also showed, however, that one effect of the forcing arm is to accelerate repayment, meaning that it is less likely for loans in this arm to be censored.
-This issue is illustrated in Figure \ref{survival_graph}, which shows the CDF of loan completion (either default or recovery in Panel (a)) and loan recovery (Panel (b)) by the number of days since first pawn.
-Two features of these graphs are salient for our analysis.
-The first is the extent to which loan outcomes are observed more quickly in the forced commitment arm.
-This is primarily due to the substantially higher rate of repayment of Forced Commitment loans at 120 days (15 pp higher than the other arms).
-The second is the very low rate at which loans are recovered in any arm after 120 days.
-In the 180-320 day window loans are largely dormant, suggesting that many of the censored loans will in fact end in default.
-
-The confluence of censoring and a treatment effect on censoring is potentially problematic from an experimental point of view.
-The approach taken so far is a conservative one in that it inherently assumes that all of the loans outstanding at the end of the observation window will be repaid, making it so that the acceleration of payment observed in the Forced arm does not translate mechanically into the that treatment decreasing default.
-Nonetheless, to be certain that this issue is not driving our results we conduct a bounding exercise to understand how large the effects of this problem can possibly be.
-In Table \ref{bounding_censoring} we compare the Forced and Control arms, bounding the censoring issue by reversing assumptions about the outcome of censored loans in the treatment versus the control.
-Panel B provides the lower bound for the treatment effect (closest to zero) by assuming censored control loans are always repaid and treatment loans never are; even in this lower-bound case the treatment effect is cost-reducing and significant at the 1\% significance level and indeed the magnitude of this lower bound estimate is only 6\% closer to zero than our headline result.
-
-Finally, Panel E of this table conducts a logit prediction model that uses all of the available information on loans that were completed to predict the outcome of loans that were not.
-This is a ``best guess'' of the outcome on censored loans.
-Using this prediction, we replicate the main experimental results and find that the treatment effect on financial cost increases from -204 (main results) to -264 (censored loans predicted), and the APR from -11\% to -17\%.
-Hence, while the censoring issue does have an effect on the magnitude of our estimated treatment effects, these  checks confirm that (a) the core results are fully robust to censoring, and (b) the headline approach that we take to the issue is conservative and likely understates the true magnitude of impacts.
+In the prior analysis we handle this issue in a conservative way by using outcomes such as ``did not default'' which are well-defined even when we do not observe the completion of the loan, resulting in an estimate biased toward zero by the more rapid loan repayment observed in the Forcing arm.
+In the Online Appendix we consider this issue in more detail.
+Most importantly, Table \ref{bounding_censoring} conducts a bounding exercise that examines how large the effects of this censoring could possibly be by making bracketing assumptions about repayment on censored loans in the treatment and control, respectively.
+Comfortingly, Panel B of this table shows that even the most muted possible effect in the bounding exercise still recovers impacts of Forcing on financial costs and APR that are negative and significant at the 99\% level.
+Using a lasso-logit model to predict the outcome of censored loans, Panel E shows the APR impact of Forcing increases from a 14 pp reduction (headline results) to a 17 pp reduction.
+Hence there appears to be no scope for this censoring issue to overturn our results, and our core results (implicitly assuming censored loans are paid off) is almost certainly an under-estimate of the true impacts.
 
@@
 The borrowers who did not choose commitment could simply be those who don't need it. 
-Indeed, we find strong evidence that the effect of forced commitment varies substantially across individuals in our experiment: Appendix \ref{append:chernozhukov} tests and rejects the null hypothesis of homogeneous treatment effects, following the methodology of \cite{chernozhukov2018generic}.
+Indeed, we find strong evidence that the effect of forced commitment varies substantially across individuals in our experiment: we test and
+%Appendix \ref{append:chernozhukov} tests and rejects 
+the null hypothesis of homogeneous treatment effects, following the methodology of \cite{chernozhukov2018generic}. (Details available upon request.)
 So the question remains: do the 89\% who do not choose commitment know something about their personal situations that we as researchers do not, or are most people in the choice arm making a costly financial mistake?
-In this section we present of econometric exercises that sheds light on this question, leveraging unique features of our experimental design. 
+In this section we present a series of econometric exercises that sheds light on this question, leveraging unique features of our experimental design. 
 Among other results, we show that commitment would lower average financial costs even for the subset of borrowers who choose \emph{not} to commit voluntarily.
@@
 \label{sec:bounds}
-If we knew the distribution of individual treatment effects, it would be easy assess how many individuals would win and lose under a policy of universal forced commitment, along with the magnitude of any individual harm.
-Because we can never simultaneously observe the same borrower in both the control and forced commitment arms, however, the distribution of individual treatment effects cannot be point identified.
-It can, however, be bounded.
-We begin our exploration of heterogeneous treatment effects by computing assumption-free bounds on the share of individuals who benefit from forced commitment.
-
-Let $Y_{i0}$ be borrower $i$'s potential outcome under the control condition, $Y_{i1}$ be her potential outcome under forced commitment, and $\Delta_i \equiv Y_{i0} - Y_{i1}$.
-Because it randomly assigns borrowers to the control and forced arms, our experimental design point identifies the marginal distributions of $Y_{i0}$ and $Y_{i1}$, call them $F_0$ and $F_1$.
-Now, define the functions $\underline{F}$ and $\overline{F}$ as follows:
+
+Calculating the number of individuals who benefit from universal forced commitment requires the distribution of individual treatment effects.
+While this distribution cannot be point identified, it can be bounded.
+Let $(Y_{i0}, Y_{i1})$ be $i$'s potential outcomes under the control and forced commitment conditions and define $\Delta_i \equiv Y_{i0} - Y_{i1}$.
+Let $(F_0, F_1, F_\Delta)$ be the marginal distributions of $(Y_{i0}, Y_{i1}, \Delta)$ and define 
 \[
@@
 \]
-Since $F_0$ and $F_1$ are point identified, so are $\underline{F}$ and $\overline{F}$.
-\cite{fan2010sharp} show that the sharp (best possible) pointwise bounds for $F_\Delta$ are given by $\underline{F}(\delta) \leq F_\Delta(\delta) \leq \overline{F}(\delta)$.
-These bounds are simple to compute, and can be surprisingly informative. 
-Here we use them to bound the fraction of borrowers who benefit from forced commitment. 
-Given the way that we have defined our outcome variables, this is the share of borrowers whose treatment effect is positive, i.e.\ $\mathbb{P}(\Delta_i > 0) = 1 - F_\Delta(0)$. 
-To construct the sharp bounds for this quantity, we simply substitute $\delta = 0$ into the preceding equations and estimate $F_0$ and $F_1$ using their empirical analogues constructed from the forced commitment and forced no-commitment arms of the experiment.
-
-Figure \ref{fan_park_bounds} plots the sharp bounds for $F_{\Delta}$ based on the APR outcome.
+Since $F_0$ and $F_1$ are point identified under random assignment, so are $\underline{F}$ and $\overline{F}$, and the pointwise sharp bounds for $F_\Delta$ are $\underline{F}(\delta) \leq F_\Delta(\delta) \leq \overline{F}(\delta)$ \citep{fan2010sharp}.
+Figure \ref{fan_park_bounds} plots these bounds for the APR outcome in our experiment.  
+To bound the share of borrowers who benefit from forced commitment, we merely substitute $\delta=0$ into the preceding, since $\mathbb{P}(\Delta_i > 0) = 1 - F_\Delta(0)$.
+Our point estimates of $\underline{F}(0)$ and $\overline{F}(0)$ are 0.03 and 0.77 respectively, with 95\% confidence intervals of [0.025, 0.050] and [0.75, 0.80].
+Since we are interested in $\mathbbm{P}(\Delta_i >0) = 1 - F_\Delta(0)$, it follows that \textit{at least 23\%}, and at most 97\%, of individuals borrowers benefit from forced commitment.\footnote{Confidence intervals are constructed using the asymptotic distribution of $(\underline{F}, \overline{F})$.
+See \cite{fan2010sharp}.}
+These bounds allow all possible joint distributions for $(Y_{i0}, Y_{i1})$ that are compatible with the observed marginals $F_0$ and $F_1$.
+
+By adding assumptions it is possible to say more.
+For example, under rank invariance--i.e.\ if $i$'s rank in the distribution of $Y_0$ equals her rank in the distribution of $Y_1$--the distribution of treatment effects is point identified and given by $F_\Delta(\delta) = \int_0^1 \mathbbm{1}\{ F_1^{-1}(u) - F_0^{-1}(u)\leq \delta\}\,\mathrm{d}u$ where $F_1^{-1}$ and $F_0^{-1}$ are the quantile functions of $Y_1$ and $Y_0$.
+Figure \ref{te_rankinvariance} in Appendix \ref{bounds_FOSD} plots our estimates of $F_\Delta$ under rank invariance.
+For the financial benefit outcome, $Y_1$ first-order stochastically dominates $Y_0$.
+Since this implies that $F^{-1}_1(u) - F^{-1}_0(u)$ is always positive, all borrowers have $\Delta_i > 0$ for this outcome under rank invariance.
+The results are slightly less stark for the APR outcome: just under 90\% of borrowers have $\Delta_i > 0$ for this outcome under rank invariance.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Original Version before trimming for ECTA
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%If we knew the distribution of individual treatment effects, it would be easy assess how many individuals would win and lose under a policy of universal forced commitment, along with the magnitude of any individual harm.
+%Because we can never simultaneously observe the same borrower in both the control and forced commitment arms, however, the distribution of individual treatment effects cannot be point identified.
+%It can, however, be bounded.
+%We begin our exploration of heterogeneous treatment effects by computing assumption-free bounds on the share of individuals who benefit from forced commitment. 
+%
+%Let $Y_{i0}$ be borrower $i$'s potential outcome under the control condition, $Y_{i1}$ be her potential outcome under forced commitment, and $\Delta_i \equiv Y_{i0} - Y_{i1}$.
+%Because it randomly assigns borrowers to the control and forced arms, our experimental design point identifies the marginal distributions of $Y_{i0}$ and $Y_{i1}$, call them $F_0$ and $F_1$.
+%Now, define the functions $\underline{F}$ and $\overline{F}$ as follows:
+%\[
+%\underline{F}(\delta) \equiv \max \left\{0, \sup_y F_1(y) - F_0(y - \delta)  \right\}, \quad
+%\overline{F}(\delta) \equiv 1 + \min \left\{0, \inf_y F_1(y) - F_0(y-\delta) \right\}.
+%\]
+%Since $F_0$ and $F_1$ are point identified, so are $\underline{F}$ and $\overline{F}$.
+%\cite{fan2010sharp} show that the sharp (best possible) pointwise bounds for $F_\Delta$ are given by $\underline{F}(\delta) \leq F_\Delta(\delta) \leq \overline{F}(\delta)$.
+%These bounds are simple to compute, and can be surprisingly informative. 
+%Here we use them to bound the fraction of borrowers who benefit from forced commitment. 
+%Given the way that we have defined our outcome variables, this is the share of borrowers whose treatment effect is positive, i.e.\ $\mathbb{P}(\Delta_i > 0) = 1 - F_\Delta(0)$. 
+%To construct the sharp bounds for this quantity, we simply substitute $\delta = 0$ into the preceding equations and estimate $F_0$ and $F_1$ using their empirical analogues constructed from the forced commitment and forced no-commitment arms of the experiment.
+%
+%Figure \ref{fan_park_bounds} plots the sharp bounds for $F_{\Delta}$ based on the APR outcome.
 Our point estimates of $\underline{F}(0)$ and $\overline{F}(0)$  are 0.03 and 0.77 respectively, with associated 95\% confidence intervals of [0.025, 0.050] and [0.75, 0.80].
@@
 See \cite{fan2010sharp} for details.}
-
-The bounds we have just described are constructed by considering all possible joint distributions of $Y_0$ and $Y_1$ that are compatible with the observed marginal distributions $F_1$ and $F_0$. 
-With stronger assumptions, it is possible to say more.
-One such assumption is \emph{rank invariance}, which posits that a person's rank in the distribution of $Y_0$ equals her rank in the distribution of $Y_1$.
-While strong, this assumption or variants of it have appeared in a number of settings in the literature, e.g.\ \cite{chernozhukov2005iv}, so we consider it here for purposes of comparison.
-Under rank invariance, the distribution of treatment effects is point identified and given by 
-\[
-F_\Delta(\delta) = \int_0^1 \mathbbm{1}\{ F_1^{-1}(u) - F_0^{-1}(u)\leq \delta\}\,\mathrm{d}u 
-\]
-where $F_1^{-1}$ and $F_0^{-1}$ are the quantile functions of $Y_1$ and $Y_0$. Figure \ref{te_rankinvariance} in Appendix \ref{bounds_FOSD} plots our estimates of $F_\Delta$ under rank invariance.
-For the financial benefit outcome, $Y_1$ first-order stochastically dominates $Y_0$ in our experiment: every quantile of the distribution of financial cost savings under forced commitment is higher than the corresponding quantile under the control condition.
+%
+%The bounds we have just described are constructed by considering all possible joint distributions of $Y_0$ and $Y_1$ that are compatible with the observed marginal distributions $F_1$ and $F_0$. 
+%With stronger assumptions, it is possible to say more.
+%One such assumption is \emph{rank invariance}, which posits that a person's rank in the distribution of $Y_0$ equals her rank in the distribution of $Y_1$.
+%While strong, this assumption or variants of it have appeared in a number of settings in the literature, e.g.\ \cite{chernozhukov2005iv}, so we consider it here for purposes of comparison.
+%Under rank invariance, the distribution of treatment effects is point identified and given by 
+%\[
+%F_\Delta(\delta) = \int_0^1 \mathbbm{1}\{ F_1^{-1}(u) - F_0^{-1}(u)\leq \delta\}\,\mathrm{d}u 
+%\]
+%where $F_1^{-1}$ and $F_0^{-1}$ are the quantile functions of $Y_1$ and $Y_0$. Figure \ref{te_rankinvariance} in Appendix \ref{bounds_FOSD} plots our estimates of $F_\Delta$ under rank invariance.
+%For the financial benefit outcome, $Y_1$ first-order stochastically dominates $Y_0$ in our experiment.
 Since this implies that $F^{-1}_1(u) - F^{-1}_0(u)$ is always positive, rank invariance yields an extremely stark conclusion: all borrowers have positive individual treatment effects of forced commitment.
-For the APR outcome, the results under rank invariance are slightly less stark: we estimate that just under 90\% of borrowers have positive individual treatment effects.
+%For the APR outcome, the results under rank invariance are slightly less stark: we estimate that just under 90\% of borrowers have positive individual treatment effects. 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% End of original version before trimming for ECTA
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-Our assumption-free bounds from the preceding section show that more than 23\% of borrowers would benefit from a policy of forced commitment. 
+The assumption-free \cite{fan2010sharp} bounds from the preceding section show that more than 23\% of borrowers would benefit from a policy of forced commitment. 
 This suggests that some of the 89\% of borrowers in the choice arm who did \emph{not} choose commitment would have faced lower borrowing costs if they had.
 Making this intuition precise, however, requires a careful consideration of the relationship between choice and heterogeneous treatment effects. 
-To this end, we now provide a full definition of the potential outcomes in our empirical setting, and introduce a pair of assumptions that will allow us to go beyond the assumption-free bounds from above.
+To this end, we now provide a full definition of the potential outcomes in our empirical setting, and introduce a pair of assumptions that will allow us to go beyond these bounds.
 
@@
 Mathematically \eqref{eq:exclusion0} and \eqref{eq:exclusion1} have the same structure as the standard LATE exclusion restriction that $Y_i(d,z)$ depends only on $d$, not on $z$. 
-Substantively, however, they are slightly different, given that there is no explicit reference to the ``chosen'' versus ``forced'' treatment distinction in the usual LATE setup.\footnote{For related discussion, see \cite{chamberlain2011bayesian} who uses an assumption similar to our exclusion restrictions to develop a theory of optimal treatment choice for an individual who has access to data from an RCT.}
+Substantively, however, they are slightly different, given that there is no explicit reference to the ``chosen'' versus ``forced'' treatment distinction in the usual LATE setup.
 In essence, \eqref{eq:exclusion0} and \eqref{eq:exclusion1} assume that being assigned a particular treatment has the same result as choosing it for yourself, provided that you are assigned the same treatment that you \emph{would have chosen}.
@@
 For example, even someone who would have voluntarily chosen to undergo drug rehabilitation, given the choice, might respond differently when coerced.
-In our empirical setting, however, both \eqref{eq:exclusion0} and \eqref{eq:exclusion1} are plausible. 
-Moreover, each has testable implications that we fail to reject.
-For details, see \ref{append:exclusion} \footnote{As mentioned above, this is a frequently used assumption even if often implicit.
-A significant literature uses schooling compulsory laws to estimate the return and then interprets that schooling in general has this return.
-Fertilizer yields are measured by researchers in experimental plots and then expected to have these returns regardless of whether farmers choose or the government provides these fertilizers.
-We are not the first paper to use this assumption, see \cite{chamberlain2011bayesian}.}
-
-Under the exclusion restrictions from \eqref{eq:exclusion0} and \eqref{eq:exclusion1}, each participant's observed outcome $Y_i$ is related to her potential outcomes $(Y_{i0}, Y_{i1})$ according to  
+In our empirical setting, however, both \eqref{eq:exclusion0} and \eqref{eq:exclusion1} are plausible.\footnote{Closely related assumptions are common, if often tacit.
+\cite{chamberlain2011bayesian} explicitly assumes that choosing and being assigned a treatment have the same effect.
+A significant literature using compulsory schooling laws to estimate the returns to education tacitly assumes that schooling \emph{in general} has the same returns.
+Similarly, fertilizer yields measured by development economists in experimental plots are tacitly assumed to generate the same returns regardless of whether the fertilizer was chosen by farmers or provided by the government.}
+Moreover, each has testable implications that we fail to reject: see \autoref{sec:testing_exclusion}. 
+Under \eqref{eq:exclusion0} and \eqref{eq:exclusion1}, the observed outcome $Y_i$ is related to $(Y_{i0}, Y_{i1})$ by 
 \begin{equation}
@@
 Equation \ref{eq:potentialOutcomes} is the key to understanding the results that follows. 
-As noted above, by randomly assigning $Z_i=0$ and $Z_i = 1$ our experiment identifies the marginal distributions of $Y_{i0}$ and $Y_{i1}$ in the population as a whole. 
-By randomly assigning $Z_i=2$, it likewise point identifies the share of choosers ($C_i = 1$), the distribution of $Y_{i1}$ for choosers, and the distribution of $Y_{i0}$ for non-choosers ($C_i = 0$).
-Because $Z_i$ is assigned independently of pre-treatment covariates $X_i$, our design also identifies the corresponding \emph{conditional} distributions of $Y_{i0}$ and $Y_{i1}$ given $X_i$. 
+Random assignment of $Z_i=0$ and $Z_i = 1$ identifies the marginal distributions of $Y_{i0}$ and $Y_{i1}$ for the population as a whole. 
+Random assignment of $Z_i=2$ likewise point identifies the share of choosers ($C_i = 1$), the distribution of $Y_{i1}$ for choosers, and the distribution of $Y_{i0}$ for non-choosers ($C_i = 0$).
+Because $Z_i$ is assigned independently of pre-treatment covariates $X_i$, we also identify the \emph{conditional} distributions of $Y_{i0}$ and $Y_{i1}$ given $X_i$. 
 %These distributions are the ingredients that we use below to explore the importance of paternalism.
@@
 %Following two  paragraphs moved from old 'behavioral' choice section towards end of paper
-%\vspace{.2in}
+%\hfill \newline
 %\subsection{The effect of choice on pawn recovery and financial cost} \label{effect_choice}
@@
 %By additionally examining \emph{outcome data} in the choice arm, it is possible to say more. 
-We now show how our experimental design, henceforth the ``controlled choice design,'' combined with the exclusion restrictions from \eqref{eq:exclusion0} and \eqref{eq:exclusion1} can be used to point identify a number of interesting and economically-relevant causal quantities without the need for additional structural restrictions.
-First we identify the treatment on the treated (TOT) and treatment on the untreated (TUT) effects, defined as follows:
+As a direct consequence of \eqref{eq:potentialOutcomes}, our experimental design--henceforth the ``controlled choice design''--point identifies a number of interesting and economically-relevant causal quantities.
+First it identifies the treatment on the treated (TOT) and untreated (TUT) effects:  
 \[
@@
 The TOT is the causal effect of commitment on borrowers who would voluntarily choose it, while the TUT is the causal effect on borrowers who would not.
-If the TUT is positive, this means that those who did not choose commitment would have experienced better outcomes, \emph{on average}, if they had. 
+If the TUT is positive, then borrowers who did not choose commitment would have experienced better outcomes, \emph{on average}, if they had. 
 In a canonical Roy model, the TOT should exceed both the TUT and average treatment effect (ATE).
-If the TOT is statistically distinguishable from and substantially larger than the TUT, this provides empirical support for the relevance of selection-on-gains in real-world decision-making.
-Because our design identifies all three quantities (as discussed below and in  \ref{append:randchoice}), it allows us to test this implication directly and to calculate the average selection on gains (ASG), namely the difference between the TOT and TUT effects:
+If the TOT is statistically distinguishable from and larger than the TUT, this provides empirical support for the relevance of selection-on-gains in real-world decision-making.
+Because our design identifies all three quantities, it allows us to test this implication directly and to calculate the average selection on gains (ASG), namely the difference between the TOT and TUT effects:
 \[
@@
 \]
-The controlled choice design also identifies both the average selection bias (ASB) and the average selection on levels (ASL). 
-\[
-\text{ASB} \equiv \mathbbm{E}[Y_{i0}|C_i = 1] - \mathbbm{E}[Y_{i0}|C_i = 0], \quad 
-\text{ASL} \equiv \mathbbm{E}[Y_{i1}|C_i = 1] - \mathbbm{E}[Y_{i1}|C_i = 0].
-\]
-The ASB tells us whether borrowers who voluntarily choose commitment are those who are worse off, on average, under the status quo.
-Similarly, the ASL tells us whether borrowers who voluntarily choose commitment are those who are better off, on average, under the commitment contract.
-A companion STATA package accompanying this paper provides estimators of the TOT, TUT, ASG, ASB, and ASL, along with cluster-robust standard errors for each, and a test for the validity of the exclusion restriction following \cite{huber_mellace}.\footnote{See Appendix \ref{append:randchoice} for more details.}
 
@@
 In contrast to both approaches, the controlled choice design uses exogenous experimental variation to point identify the ATE, TOT, and TUT without ruling out unobserved selection-on-gains or relying on additional structural modeling assumptions.
-Figure \ref{tot_tut_graph} provides graphical intuition for our identification approach. % derivations appear in \ref{append:randchoice}
 
@@
     \end{center}
- \caption{The Controlled Choice Design.
-This figure provides graphical intuition for the way in which the controlled choice design from Section point identifies both the treatment on the treated (TOT) and treatment on the untreated (TUT) effects, as discussed in Section \ref{sec:randchoice} and \ref{append:randchoice}.
-    The gray shaded regions denote borrowers with a commitment contract; the white shaded regions denote borrowers with a status quo contract.
+ \caption{Graphical Intuition for the Controlled Choice Design. 
+     %This figure illustrates why the controlled choice design identifies the TOT and TUT effects.
+    Gray rectangles denote borrowers with a commitment contract; white rectangles denote borrowers with a status quo contract. 
     A comparison of means across control and forcing arms identifies the ATE of forcing commitment. 
-    The TOT and TUT effects of commitment are identified as follows.
-    In the choice arm, anyone with a commitment contract is a chooser; in the control and forcing arms, we do not know who is a chooser and who is not.
-    Because borrowers are randomly assigned to experimental treatment arms, however, the share of choosers will be the same, on average, across experimental arms.
-    This is depicted using dashed vertical lines in the control and forcing arms.
-    This overall share of choosers and non-choosers is point identified from the choice arm.
-    Now, the difference of mean outcomes across the choice and control arms gives the intent-to-treat effect of offering choice.
-    Under the exclusion restriction that moving non-choosers between the choice and forcing arms does not change their outcomes, this comparison ``nets out'' the non-choosers.
-    Hence, the ITT of offering choice equals the TOT multiplied by the share of choosers. 
-    Similarly, under the exclusion restriction that moving choosers between the choice and forcing arm does not affect their outcomes, the difference of means across the forcing and choice arms ``nets out'' the choosers and hence equals the TUT multiplied by the share of non-choosers.}
+    %In the choice arm, anyone with a commitment contract is a chooser; in the control and forcing arms, we do not know who is a chooser and who is not, but because borrowers are randomly assigned to experimental treatment arms, the share of choosers will be the same, on average (depicted using dashed vertical lines).
+    The difference of mean outcomes across the choice and control ``nets out'' the non-choosers, and hence equals the TOT multiplied by the share of choosers.
+    %arms gives the intent-to-treat effect of offering choice. 
+    %Under the exclusion restriction that moving non-choosers between the choice and forcing arms does not change their outcomes, this comparison ``nets out'' the non-choosers.
+    %Hence, the ITT of offering choice equals the TOT multiplied by the share of choosers. 
+    %Similarly, under the exclusion restriction that moving choosers between the choice and forcing arm does not affect their outcomes. 
+    Similarly, the difference of means across the forcing and choice arms ``nets out'' the choosers and equals the TUT multiplied by the share of non-choosers.
+        The share of choosers, illustrated using dashed vertical lines, is equal on average across arms under random assignment.}
     \label{tot_tut_graph}
@@
 
-The key insight can be read directly from \eqref{eq:potentialTreatments} and \eqref{eq:potentialOutcomes}. 
+The key insight can be read directly from \eqref{eq:potentialTreatments} and \eqref{eq:potentialOutcomes}; Figure \ref{tot_tut_graph} provides graphical intuition.
+%for our identification approach.
+% derivations appear in \ref{append:randchoice}
 Viewing $Z_i$ as an instrumental variable, the controlled choice design can be interpreted as a \emph{pair} of RCTs, each subject to one-sided non-compliance.
@@
 This is identical to a ``randomized encouragement'' design in which treatment is only available to those who are encouraged: $Z_i = 2$.
-Under this interpretation, those with $C_i = 1$ are ``the compliers'' and it follows that
+Under this interpretation, those with $C_i = 1$ are ``the compliers'' and it follows by a standard argument (see Section \ref{sec:proofs}) that
 \begin{equation}
 \frac{\mathbbm{E}(Y_i|Z_i=2) - \mathbbm{E}(Y_i|Z_i =0)}{\mathbbm{E}(D_i|Z_i=2)-\mathbbm{E}(D_i|Z_i=0)} = 
-\frac{\mathbbm{E}(Y_i|Z_i=2) - \mathbbm{E}(Y_i|Z_i =0)}{\mathbbm{E}(D_i|Z_i=2)} = \mathbbm{E}(Y_{i1} - Y_{i0}|C_i = 1)
+\frac{\mathbbm{E}(Y_i|Z_i=2) - \mathbbm{E}(Y_i|Z_i =0)}{\mathbbm{E}(D_i|Z_i=2)} = \text{TOT} 
 \label{eq:TOT}
@@
 \frac{\mathbbm{E}(Y_i|Z_i=1) - \mathbbm{E}(Y_i|Z_i =2)}{\mathbbm{E}(D_i|Z_i=1)-\mathbbm{E}(D_i|Z_i=2)} = 
-\frac{\mathbbm{E}(Y_i|Z_i=1) - \mathbbm{E}(Y_i|Z_i =2)}{1 - \mathbbm{E}(D_i|Z_i=2)} = \mathbbm{E}(Y_{i1} - Y_{i0} | C_i = 0)
+\frac{\mathbbm{E}(Y_i|Z_i=1) - \mathbbm{E}(Y_i|Z_i =2)}{1 - \mathbbm{E}(D_i|Z_i=2)} = \text{TUT}
 \label{eq:TUT}
@@
 since $\mathbbm{E}(D_i|Z_i = 1)= 1$ by \eqref{eq:potentialTreatments}. 
-Equations \eqref{eq:TOT} and \eqref{eq:TUT} are useful for understanding why the controlled choice design identifies the TOT and TUT, but they are less convenient for estimation and inference.
-In \ref{append:randchoice}, we show that
-\begin{align}
-\label{eq:TOTreg}
-Y_i &= \mathbbm{E}(Y_{i0}) + (\text{ATE}) \mathbbm{1}(Z_i = 1) + (\text{TOT}) \left[\mathbbm{1}(Z_i = 2) \times D_i\right] + U_i \\
-\label{eq:TUTreg}
-Y_i &= \mathbbm{E}(Y_{i1}) + (\text{ATE}) \left[ -\mathbbm{1}(Z_i = 0)\right] + (\text{TUT}) \left[ -\mathbbm{1}(Z_i = 2) \times (1 - D_i)\right] + V_i 
-\end{align}
-where $\mathbbm{E}(U_i|Z_i) = \mathbbm{E}(V_i|Z_i) = 0$.
-It follows that a pair of just-identified, linear instrumental variables regressions can be used to estimate and carry out inference for the ATE, TOT, and TUT.
-To identify the ATE and TOT, run IV on \eqref{eq:TOTreg} with instruments $\mathbbm{1}(Z_i = 1)$ and $\mathbbm{1}(Z_i=2)$.
-An F-test based on this regression can then be used to test the restriction $\text{ATE} = \text{TOT}$, and the usual IV output can be used to carry out inference for the TOT.
-Similarly, to identify the ATE and TUT run IV on \ref{eq:TUTreg} with instruments $\mathbbm{1}(Z_i = 0)$ and $\mathbbm{1}(Z_i = 2)$.
-An F-test based on this regression can then be used to test the restriction $\text{ATE} = \text{TUT}$, and the usual IV output can be used to carry out inference for the TUT.
-
-Because they identify both the TOT and TUT, \eqref{eq:TOTreg} and \eqref{eq:TUTreg} also identify the average selection on gains: $\text{ASG} = \text{TOT} - \text{TUT}$.
-Carrying out inference for this quantity is a bit more involved, because $\text{ASG}$ is a difference of coefficients from two separate IV regressions. 
-In \ref{append:randchoice} we show how to use the residuals from \eqref{eq:TUTreg} and \eqref{eq:TOTreg} to carry out cluster-robust inference for $\text{ASG}$, a procedure that is automated in our companion STATA package.
-As mentioned above, the controlled choice design also identifies the average selection bias (ASB) and average selection on levels (ASL).
-In particular,
+Because they identify both the TOT and TUT, \eqref{eq:TOT} and \eqref{eq:TUT} also identify the average selection on gains: $\text{ASG} = \text{TOT} - \text{TUT}$.
+
+The controlled choice design also identifies the average selection bias (ASB) and average selection on levels (ASL). In particular,
 \begin{align}
@@
     \label{eq:ASL}
-    \text{ASL} &\equiv \mathbbm{E}(Y_{i1}|C_i = 1) - \mathbbm{E}(Y_{i1}|C_i=0) = \frac{\mathbbm{E}(Y|Z=2,D=1) - \mathbbm{E}(Y|Z=1)}{1 - \mathbbm{E}(D|Z=2)}.
+    \text{ASL} &\equiv \mathbbm{E}(Y_{i1}|C_i = 1) - \mathbbm{E}(Y_{i1}|C_i=0) = \frac{\mathbbm{E}(Y|Z=2,D=1) - \mathbbm{E}(Y|Z=1)}{1 - \mathbbm{E}(D|Z=2)}
 \end{align}
-For purposes of inference, both the ASB and ASL can be re-written as the difference of coefficients from a pair of just-identified linear IV regressions.\footnote{For details, along with a description of how our companion STATA package carries out cluster-robust inference for these quantities, see \ref{append:randchoice}.}
+as shown in Section \ref{sec:proofs}.
+The ASB tells us whether borrowers who voluntarily choose commitment are those who are worse off, on average, under the status quo.
+Similarly, the ASL tells us whether borrowers who voluntarily choose commitment are those who are better off, on average, under the commitment contract.
+
+Equations \eqref{eq:TOT}--\eqref{eq:ASL} are useful for understanding why the controlled choice design identifies the TOT, TUT, ASG, ASB, and ASL but they are less convenient for estimation and inference.
+\autoref{sec:estimation_inference} explains how to compute each of these quantities from a small  number of just-identified, linear instrumental variables regressions, along with appropriate cluster-robust standard errors.
+These estimators and standard errors are implemented in our companion STATA package. %\textcolor{red}{Add a link to this package along with the documentation.}
 
@@
 
-\begin{table}
-\caption{Treatment on the Treated (TOT), Treatment on the Untreated (TUT), Selection-on-gains (TOT - TUT), Average Selection Bias (ASB), and Average Selection Bias, calculated using the results from Section \ref{sec:randchoice}.}
-\label{tot_tut}
-\begin{center}
-\scriptsize{\input{./Tables/tot_tut.tex}}
-\end{center}
-\legend{This table presents results computed using the derivations from Section \ref{sec:randchoice} and \ref{append:randchoice}.
-The APR and financial cost outcomes have been multiplied by $-1$ so that a positive causal effect \emph{benefits} the borrower in each of the four columns.
-See Appendix \ref{subsec:inference} for more details on how we compute standard errors for the middle panel.
-The bottom panel present p-values for a number of null hypothesis tests of treatment effect heterogeneity. }
-%\textit{Do file: } \texttt{tot\_tut.do}
-\end{table}
-
-\noindent \textbf{TOT and TUT results.} Table \ref{tot_tut} calculates the causal quantities described above--TOT, TUT, ASG, ASB, and ASL--for our experimental data, along with robust standard errors for each.
+%\hfill \newline
+%\noindent \textbf{TOT and TUT results.}
+
+Table \ref{tot_tut} calculates the causal quantities described above--TOT, TUT, ASG, ASB, and ASL--for our experimental data, along with robust standard errors for each. 
 For purposes of comparison, the table also presents the ATE results from Section \ref{Experiment} above (row 1),\footnote{Coefficients are not exactly the same since Table 4 includes branch and day-of-week FE.} along with the corresponding average potential outcomes $\mathbbm{E}[Y_0]$ and $\mathbbm{E}[Y_1]$ (rows 4--5).
@@
 
+\begin{table}[H]
+\caption{Treatment on the Treated (TOT), Treatment on the Untreated (TUT), Selection-on-gains (TOT - TUT), Average Selection Bias (ASB), and Average Selection Bias.}
+\label{tot_tut}
+\begin{center}
+\scriptsize{\input{./Tables/tot_tut.tex}}
+\end{center}
+\legend{This table presents results computed using the derivations from Section \ref{sec:randchoice}.
+The APR and financial cost outcomes have been multiplied by $-1$ so that a positive causal effect \emph{benefits} the borrower in each of the four columns.
+The bottom panel present p-values for a number of null hypothesis tests of treatment effect heterogeneity.
+}
+%\textit{Do file: } \texttt{tot\_tut.do}
+\end{table}
+
 Overall, Table \ref{tot_tut} suggests that commitment works but that \emph{not enough} people choose to commit: the commitment contract is beneficial on average even to those who would \emph{not} choose it voluntarily.
@@
 In a different domain, doctors claim that medical treatment abandonment is too high in a broad range of diseases \citep{non_adherence}, without knowing the treatment benefits for those that abandon.}
+
 %Below we explore possible explanations for this result.
@@
 %Viewed through the lens of rational choice theory, it is unsurprising that we estimate $\text{TOT}>\text{TUT}$. 
-The argument for compulsory treatment, centers on the surprising result that $\text{TUT}>0$. We now investigate several potential explanations for this result.
-For simplicity, we focus on causal effects for the APR outcome throughout this section.
-We view this section as an exploratory analysis to stimulate ideas for future research.
-We examine four potential explanations for the positive $\text{TUT}$: the need to learn, time discounting, present bias, and overconfidence.
-To explore the last two dimensions we will use survey data.\footnote{Since merging with survey data reduces our sample, Table \ref{TUT_cond_survet} demonstrates that the subsample on whom we have survey data appears to be representative in terms of treatment effects.}
-
-\noindent \textbf{Learning.} A first explanation involves learning.
+The argument for compulsory treatment, centers on the surprising result that $\text{TUT}>0$.
+We now investigate four potential explanations for the positive $\text{TUT}$: the need to learn, time discounting, present bias, and overconfidence.
+
+%\hfill \newline
+%\noindent \textbf{Learning.}
+
 Our experiment introduced a new contract into an environment that had not previously featured commitment; perhaps clients required experience to understand its benefits.
@@
 The implication is that while those who have experienced commitment feel more positively towards the pawn contract, the experience does not lead them to conclude that they need commitment on the subsequent loan.
-While these exercises cannot completely exclude the possibility that learning plays a role, they provide no indication that the lack of voluntary compliance is simply a matter of inexperience with commitment, but more research and larger samples are needed to test whether learning obviates the need for paternalism.
+While these exercises cannot completely exclude the possibility that learning plays a role, they provide no indication that the lack of voluntary compliance is simply a matter of inexperience with commitment.
 
@@
 
-\noindent \textbf{Time discounting.} Discounting is a second potential explanation for our results.
+%\hfill \newline
+%\noindent \textbf{Time discounting.}
+
 Highly impatient individuals might rationally choose the \emph{status quo} contract, despite the benefits that commitment yields returns, since monthly payments are front-loaded while pawn recovery is back-loaded, even if by only a few days.
@@
 We see that non-choosers continue to experience significant decreases in NPV financial costs up to annual discount rates of 1,000\%, and the NPV remains positive, although not significant, at 5,000\% discount rates.
-As such, discounting is unlikely to explain why those who benefit, on average, from commitment fail to choose it when offered.
-
-\noindent \textbf{Present bias.} If the benefits of commitment among non-choosers cannot be explained by standard models of rational choice, the canonical behavioral story would center on time inconsistency.
+As such, discounting is unlikely to explain why those who benefit, on average, from commitment fail to choose it.
+% when offered.
+
+%\hfill \newline
+%\noindent \textbf{Present bias.} 
+If the benefits of commitment among non-choosers cannot be explained by standard models of rational choice, the canonical behavioral story would center on time inconsistency.
 While commitment is useful to anyone with hyperbolic time preferences, only those who are sophisticated--i.e.\ aware that they are hyperbolic discounters--will demand it.
@@
 This is because among the group of non-takers, a comparison of present-biased borrowers against everyone else is a comparison of na\"{i}ve hyperbolics against time-consistent non-choosers.
-
-The left panel of Figure \ref{tut_beh_partition} carries out a feasible version of this exercise using our survey measure of present bias.
-The overall TUT estimate along with a 95\% confidence interval is given in blue.\footnote{For all borrowers who answered our present-bias survey questions.}
-The corresponding TUT estimate and confidence interval for present-biased borrowers identified with the survey question is given in green; results for all other borrowers are shown in red.
-The overall TUT is a weighted average of the impact in these two sub-groups.
+The left panel of Figure \ref{tut_beh_partition} in the Appendix carries out a feasible version of this exercise using our survey measure of present bias.
+%The overall TUT estimate along with a 95\% confidence interval is given in blue.\footnote{For all borrowers who answered our present-bias survey questions.}
+%The corresponding TUT estimate and confidence interval for present-biased borrowers identified with the survey question is given in green; results for all other borrowers are shown in red.
+%The overall TUT is a weighted average of the impact in these two sub-groups.
 The TUT among the present biased is insignificant and less than half the size of the strongly significant TUT among those who are \textit{not} present biased.
-Therefore, taking our survey measure of hyperbolicity at face value, we find no indication that present-bias explains our positive estimated TUT.
-
-\begin{figure}
-    \begin{center}
-        \centering
-        \includegraphics[width=0.6\textwidth]{Figuras/tut_beh_partition.pdf} 
-    \end{center}
-     \scriptsize  
-\caption{Heterogeneity of the TUT by behavioral variables.
-Each panel in this figure shows how the estimated treatment on the untreated (TUT) effect varies with a binary survey variable $X_i$.
-In the left panel (P.B.), $X_i = 1$ if borrower $i$ is ``present-biased'' based on her responses to the time preference questions from our survey.
-In the right panel (Sure-confidence) $X_i = 1$ if  borrower $i$ reported that she was certain to recover her pawn, zero otherwise.
-% Each panel depicts three estimates and associated 95\% confidence bands: the overall TUT (blue), the TUT for borrowers with $X = 1$ (green), and the TUT for borrowers with $X = 0$ (red).
-By the law of iterated expectations, the overall TUT in each panel must lie between the group-specific TUTs.
-The overall TUT is slightly different in each panel, because some borrowers only completed part of the survey.
-In each panel, we present results for the full set of borrowers who answered the survey question or questions needed to determine $X_i$.
-From the left panel, we see that TUT does not appear to be higher among present-biased borrowers.
-In contrast, the right panel suggests that the positive and significant overall TUT is driven by individuals who are ``sure-confident,'' i.e.\ borrowers who report that they are certain to recover their pawn.
-}
-    \label{tut_beh_partition}
-      %\footnotesize{ \textit{Do file: }  \texttt{partition_tut.do}
-
-\end{figure}
-
-\noindent \textbf{Sure confidence.} While 72\% of survey respondents believe they have a 100\% chance of recovering their pawn, in reality only 43\% will go on to do so.  
+Therefore, taking our survey measure of hyperbolicity at face value.
+We find no indication that present-bias explains our positive estimated TUT.
+
+%\hfill \newline
+%\noindent \textbf{Sure confidence.}
+
+While 72\% of survey respondents believe they have a 100\% chance of recovering their pawn, in reality only 43\% will go on to do so.  
 This suggests a borrower pool characterized by over-optimism.
@@
 This measure equals one for any individuals who say at the time of borrowing that they have a 100\% probability of recovering their pawn, zero otherwise.
-The right panel of Figure \ref{tut_beh_partition} presents the results for this exercise.
-The overall TUT estimate for all borrowers who answered our sure-confidence survey questions is given in blue, along with a 95\% confidence interval.
-The corresponding TUT estimate and confidence interval for sure-confident borrowers is given in green; results for all other borrowers are shown in red.
-In contrast to our results for present bias, the TUT is almost entirely confined to the sure confident individuals, with the effect among those saying they have some chance of defaulting at baseline being very close to zero.
+%The right panel of Figure \ref{tut_beh_partition} presents the results for this exercise.
+%The overall TUT estimate for all borrowers who answered our sure-confidence survey questions is given in blue, along with a 95\% confidence interval.
+%The corresponding TUT estimate and confidence interval for sure-confident borrowers is given in green; results for all other borrowers are shown in red.
+In contrast to our results for present bias, we find (Figure \ref{tut_beh_partition}) that the TUT is almost entirely confined to the sure confident individuals, with the effect among those saying they have some chance of defaulting at baseline being very close to zero.
 
 As discussed above, our measure of hyperbolicity is based on un-incentivized responses in a short survey and so is likely to be noisy; nonetheless we see no evidence here that it drives the forcing effect.
-Rather, the analysis from Figure \ref{tut_beh_partition} suggests that the effectiveness of paternalism in our experiment may be driven by \emph{overconfident} borrowers who, heedless of the risk of default, fail to choose commitment despite benefiting substantially when they are forced to commit.
-
-%Figure \ref{tut_beh_partition} shows the relative contributions of present bias and sure-confidence for the $\text{TUT}$.
-In each figure the orange bar represents the contribution from those who do not possess the attribute, and the blue bar from those that do.
-We see that the forcing effect is localized mostly to those who are \textit{not} time inconsistent, contradicting naive hyperbolicity as the justification for paternalism.
-Instead, we see sure-confidence being a category that completely isolates the $\text{TUT}$, suggesting that forcing works for those who do not consider repayment structure because they don't think they need it.
-
-If the attribute of ``sure confidence'' proves so important in explaining the positive TUT, what are its determinants?
-In Figure \ref{determinants_sure} we plot the coefficient estimates from a regression that predicts sure confidence with a battery of individual-level characteristics.
+Rather, it seems that the effectiveness of paternalism in our experiment may be driven by \emph{overconfident} borrowers who, heedless of the risk of default, fail to choose commitment despite benefiting substantially when they are forced to commit.\footnote{In Figure \ref{determinants_sure} we plot the coefficient estimates from a regression that predicts sure confidence with a battery of individual-level characteristics.
 Older males are more likely to be sure-confident, as are those with more education.
 Taken at face value, the sure-confident also report less financial stress, less trouble paying bills, and to be more frequently relied upon financially by family members.
-Viewed through a behavioral lens, however, it is also possible that the type of person who is over-confident in their ability to repay a loan also %maintains fictions in other domains of their financial life, providing answers to the baseline survey questions that
-exaggerate their degree of economic security in their response to survey questions.
-In any case, it appears that sure confidence may be difficult to predict with easily-observed and objective demographic criteria, a point to which we return below.
+Viewed through a behavioral lens, however, it is also possible that the type of person who is over-confident in their ability to repay a loan also exaggerate their degree of economic security in their response to survey questions.
+In any case, it appears that sure confidence may be difficult to predict with easily-observed and objective demographic criteria, a point to which we return below.}
 
@@
 
-\noindent \textbf{Causal forests.} 
+%\noindent \textbf{Causal forests.} 
 On average, the commitment contract benefits both those who would choose it and those who would not.
@@
 Under the stronger assumption that our observed survey measures capture the main sources of treatment effect heterogeneity, this exercise will allow us to approximate individual-level counterfactuals, to consider whether particular borrowers made ``mistakes'' in their choice of contract.
-
-To estimate conditional average treatment effects given administrative and survey data, we use the function \texttt{causal\_forest()} of the \texttt{grf} R package; to estimate conditional TOT and TUT effects we use the \texttt{instrumental\_forest()} function from the same package.
-In each case, we use the default parameter values from the \texttt{grf} package with one exception: we increase the number of trees from the default value of 2000 to 5000.
-The functions \texttt{causal\_forest()} and \texttt{instrumental\_forest()} implement special cases of the ``generalized random forest'' methods of \cite{atheygrf}.
-In broad strokes, these functions combine a large number of regression trees that recursively partition the covariate space to estimate conditional average effects.
-Figure \ref{causal_tree1} illustrates the partition that emerges from one of the trees in our causal forest implementation.
-The trees are ``honest'' in that observations used to determine the optimal partition are not used to estimate effects, and vice-versa.
-While closely related to more familiar ``regression-tree'' random forests, the generalized random forest approach explicitly targets the parameter of interest--a conditional ATE or IV estimand--when choosing the optimal covariate partition.
-\footnote{For more details, see \cite{atheygrf} and the \texttt{grf} documentation: \url{https://grf-labs.github.io/grf/}.
-When constructing our random forest estimates of heterogeneous treatment effects, we use observations for all borrowers who answered at least \emph{part} of the intake survey.
-We impute the median response for the missing values, while also including an indicator whether the variable originally had a missing value.
-Results are similar if we manually include interactions between the original/imputed variable and an indicator for missingness.
-This is as expected, given that tree-based methods by their nature ``automatically'' consider interactions of arbitrary orders.}
-
-\noindent \textbf{Treatment effect distributions.} Figure \ref{heterogeneous_effects} plots densities of the estimated conditional ATE, TOT, and TUT effects from the generalized random forest models described above.
+To estimate the conditional average treatment effects we use the ``generalized random forest'' methods of \cite{atheygrf} (see Appendix \ref{app:cate} for details).
+
+%\hfill \newline
+%\noindent \textbf{Treatment effect distributions.} 
+Figure \ref{heterogeneous_effects} plots densities of the estimated conditional ATE, TOT, and TUT effects from the generalized random forest models described above.
 In each case, the outcome variable is APR benefit, i.e.\ the reduction in APR from a commitment contract.
@@
 
-\begin{figure}
-
-    \begin{center}
-     \begin{subfigure}{0.32\textwidth}
-       \centering
-      \includegraphics[width=\textwidth]{Figuras/he_dist_tau_hat_tot.pdf}
-          \caption{ToT}
-    \end{subfigure}
-    \begin{subfigure}{0.32\textwidth}
-       \centering
-      \includegraphics[width=\textwidth]{Figuras/he_dist_tau_hat_tut.pdf}
-          \caption{TuT}
-    \end{subfigure} 
-       \begin{subfigure}{.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/he_dist_tau_hat_eff.pdf}
-        \caption{ATE}
-    \end{subfigure} 
-    \end{center}
-    \caption{Heterogeneous Treatment Effects.}
-    \label{heterogeneous_effects}    
-  %\footnotesize{ } \textit{Do file: }  \texttt{cate_dist.do}
-\end{figure}
-\noindent \textbf{``Mistake'' tresholds.} Under the assumption that our instrumental forest estimates capture the main sources of treatment effect heterogeneity, we can use them to assess whether particular borrowers in the choice arm made ``mistakes'' in their decision to accept or refuse the commitment contract, in terms of predicted financial costs of the loan.
+%\hfill \newline
+%\noindent \textbf{``Mistake'' thresholds.} 
+Under the assumption that our instrumental forest estimates capture the main sources of treatment effect heterogeneity, we can use them to assess whether particular borrowers in the choice arm made ``mistakes'' in their decision to accept or refuse the commitment contract, in terms of predicted financial costs of the loan.
 To do this we use the same information that is depicted in Figure \ref{heterogeneous_effects}, but present it in a different way.
@@
 \begin{figure}[H]
+\begin{center}
         \centering
         \includegraphics[width=0.6\textwidth]{Figuras/line_cw_apr_tot_tut.pdf}
+
+ \end{center}       
  \caption{``Mistakes'' in the choice arm.
@@
 A ``mistake'' for a non-chooser is defined as a positive conditional TUT effect that significantly exceeds a specified threshold APR value.
- The green curve equals $[1 - F_{\text{TUT}}(\delta)]\times 100\%$, where $F_{\text{TUT}}$ is the CDF corresponding to density of conditional TUT effects from Figure \ref{heterogeneous_effects}, computed using the instrumental forest approach from \cite{atheygrf}.
+%  The green curve equals $[1 - F_{\text{TUT}}(\delta)]\times 100\%$, where $F_{\text{TUT}}$ is the CDF corresponding to density of conditional TUT effects from Figure \ref{heterogeneous_effects}, computed using the instrumental forest approach from \cite{atheygrf}.
 Evaluated at any positive value on the horizontal axis, it gives the fraction of non-choosers in the choice arm who made a ``mistake'' by not choosing commitment.
 The green shaded region gives associated 95\% pointwise confidence bands.
-Analogously, a ``mistake'' for a chooser is defined as a negative conditional TOT effect that exceeds a specified threshold APR value.
+% Analogously, a ``mistake'' for a chooser is defined as a negative conditional TOT effect that exceeds a specified threshold APR value.
 The red curve equals $F_{\text{TOT}}(-\delta)$ where $F_{\text{TOT}}$ is the CDF corresponding to the density of conditional TOT effects from Figure \ref{heterogeneous_effects}.
-The red shaded region gives associated 95\% pointwise confidence bands.
-For both the red and green curves, we define the APR threshold so that larger mistakes are to the \emph{right} of smaller mistakes.
-This allows us to construct the overall fraction of mistakes in the choice arm, the blue curve, as a weighted average of the green and red curves.
-The weights equal the share of choosers and non-choosers in the choice arm.}
+% The red shaded region gives associated 95\% pointwise confidence bands.
+% For both the red and green curves, we define the APR threshold so that larger mistakes are to the \emph{right} of smaller mistakes.
+% This allows us to construct the overall fraction of mistakes in the choice arm, the blue curve, as a weighted average of the green and red curves.
+% The weights equal the share of choosers and non-choosers in the choice arm.
+}
     \label{choose_wrong}
@@
 
-Despite having shown such a large majority of individuals benefit from paternalism, it is still natural to ask whether we are able to target commitment in such a manner as to only force it upon those who benefit.
-For a financial firm to engage in this type of targeting under real-world circumstances, we must impose several constraints on the targeting rule.
-First, it will in general not be possible to use the numerous subjective and unverifiable questions we asked in the baseline survey as inputs to the rule because the answers to these questions can be manipulated by the clients, and would likely change when they become incentivized.
-This leaves us with only a few objective covariates that could be used to target: age, gender, HS education or above, desired loan size, and whether that individual has ever pawned before.
-We call these the ``narrow'' covariate set below, to contrast with the full set of survey variables, which we call the ``wide'' covariate set.
-Secondly, it will not be attractive for a commercial firm to ask individuals whether they want to voluntarily accept commitment and then to force upon those who say no against their will.
-So the choice variable itself cannot be used to target other than in a voluntary program.
-For this reason, the relevant causal effect for this exercise is the conditional average treatment effect (ATE) rather than the conditional TUT or TOT as considered above.
-As shown in Figure \ref{fig:CATEsurvival}, an estimated 90\% of borrowers, with a 95\% confidence interval of [87\%, 92\%] have a positive conditional ATE as estimated from the causal forest from Section \ref{sec:RF} above.
-In the remainder of this section we ask how accurately it is possible to identify these borrowers.
-
-\noindent \textbf{Narrow inputs targeting.} To consider targeting effectiveness we must begin from an individual-specific ground truth, which we take from our estimated conditional average treatment effects (CATEs) $\widehat{\text{ATE}}(X_i)$ from the causal forest described in Section \ref{sec:RF},  which used the ``wide'' set of covariates (wide RF).% and data for all borrowers who replied to at least part of the intake survey.
-We then analyze how well we can predict the losers from paternalism using the ``narrow'' set of non-manipulable covariates listed above (narrow RF) for the same subset of borrowers.
-Figure \ref{wide_narrow_forests} shows the relationship between the CATEs estimated from the RF using the ``wide'' and ``narrow'' covariate sets.
-We can generate substantially less heterogeneity when using the narrow covariate set, although we still reject the null hypothesis of no treatment effect heterogeneity, following the approach of \cite{chernozhukov2018generic}.\footnote{See \ref{append:chernozhukov} for details of this method.}
-
-\noindent \textbf{Targeting assessment.} To more directly investigate our ability to target commitment, we use two different methods to predict who should be assigned to the commitment arm.
-In each, we estimate a classification model using the ``narrow'' set of covariates to predict whether the CATE estimated from the wide random forest model (using all available covariates) is positive.
-The first method uses a simple logistic regression, while the second uses a random forest classification model.\footnote{We use the STATA package \textit{rforest} and use the default parameters for the estimation.
-For further detail see \cite{rforest_stata}.} Each of these methods yields an estimated probability of a positive CATE, allowing us to rank borrowers from highest to lowest probability.
-Since 90\% of borrowers have a positive CATE as estimated from the wide random forest model from above, we consider a decision rule that assigns a borrower to forced commitment if her estimated probability is in the top 90\% of the sample.
+Is it possible to target paternalism only towards those who would benefit from it?
+A financial firm engageing in this type of targeting under real-world circumstances would be unable to use the subjective and unverifiable questions from the survey, and would not use the commitment choice since it will be unattractive for a company to ask consumer preferences and then force a product on those who had refused it.
+This leaves us with only a few objective covariates that could be used to target: age, gender, high school education or above, desired loan size, and whether that individual has ever pawned before.
+We call these the ``narrow'' covariate set, to contrast with the full set of survey variables, which we call the ``wide'' covariate set.
+We take the estimated conditional average treatment effects (CATEs) $\widehat{\text{ATE}}(X_i)$ using the wide covariates as our ground truth, and now ask how well we can predict this benefit using the narrow covariate set.
+Figure \ref{wide_narrow_forests} shows the relationship between these two different  CATEs.
+We generate substantially less heterogeneity when using the narrow covariate set, although we still reject the null hypothesis of no treatment effect heterogeneity with the test from \cite{chernozhukov2018generic}.
+To investigate targeting, we can assign a dummy variable equal to one for the 90\% of borrowers who have a positive CATE using the wide covariate set, and then implement both a logistic regression and a random forest classification model using only the narrow covariate set to predict positive benefits at the individual level.
 
@@
 \begin{center}
-\resizebox{0.95\textwidth}{!}{
-\small{\input{./Tables/hit_miss_rule.tex}}
-}
+
+\scriptsize{\input{./Tables/hit_miss_rule.tex}}
+
 \end{center}
 \legend{This table reports error rates for six different rules for allocating individuals to commitment.
-The first row allocates all borrowers to control.
-Taking the conditional ATE estimates from the ``wide'' causal forest, described in Section \ref{sec:RF} as ground truth, this results in 90\% of individuals losing by not receiving commitment.
-The second row assigns all borrowers to forced commitment, yielding error rates that are the exact mirror image of those from the first row.
-The third row considers the infeasible optimum in which each borrower is allocated the ``correct'' treatment, treating the estimate from the ``wide'' causal forest as ground truth.
-The fourth and fifth rows assign borrowers to commitment based on a classification model that uses the narrow covariate set to predict an indicator for whether the ``wide'' random forest CATE estimate is positive.
-Row four uses a random forest classification model while row five uses a simple logistic regression model.
-In each of these rows, the assignment rule ranks borrowers from highest to lowest by their estimated probability of having a positive CATE.
-The 90\% of borrowers with the highest estimated probabilities are assigned to treatment, matching the overall rate of positive CATE estimates from the ``wide'' RF model.
-The sixth row gives the percentage of miss-classification that would follow from the observed choice.
-}
+Row 1 assigns all borrowers to control, Row 2 all to the Forcing arm.
+Row 3 uses `optimal targeting according to the CATE from the wide covariate set.
+Row 4 uses a random forest classification, and Row 5 a logit model, both with only the narrow covariate set.
+Row 6 uses the choices made by borrowers to assign to commitment.}
 \end{table}
@@
 We compare the in-sample performance of targeting rules against a policy of universal forced commitment.
-Table \ref{hit_miss_rule} shows error rates for six possible assignment rules: assigning all borrowers to control, all to treatment (Forcing), the optimal (infeasible) assignment, narrow RF targeting, Logit targeting, and we evaluate ex-post the voluntary choice, taking the wide RF as the ground truth.
+Table \ref{hit_miss_rule} shows error rates for six possible assignment rules: assigning all borrowers to control, all to treatment (Forcing), the optimal (infeasible) assignment, narrow RF targeting, Logit targeting, and the actual choice made by borrowers.
+All models taking the wide RF as the ground truth.
 While the narrow RF correctly assigns roughly half of those who do not benefit from commitment to control, it also incorrectly allocates 4.38\% of the sample that would have gained from treatment to control.
@@
 The Logit assignment rule is less successful at predicting benefits and harms, with a higher share of borrowers incorrectly assigned to both treatment and control, meaning that the overall correct targeting rate for the Logit is 5 pp lower than universal Forcing.
-%In particular it makes many Type II errors, resulting in a net targeting performance that is actually worse than universal forcing. 
-The underlying cause of the weak performance of targeting is that the attribute that predicts gains from forcing (being sure confident and not choosing the commitment) is largely behavioral and not easily predicted with basic covariates, as seen in Figure \ref{tut_beh_partition}.
-
 Self-targeting through choice proves to be little better than assigning everyone to the control condition, given the low take-up rate and the presence of both Type I and Type II errors in the choice arm.
-Fully 87\% of individuals in the Choice arm made a ``mistake'', weighting the error rates among choosers and non-choosers by their relative frequency in the Choice arm.
 The takeaway is that given low take-up, the large fraction of the sample benefiting from commitment, and the weak predictive power of the narrow covariates, in this case universal paternalism assigning all borrowers to the commitment contract appears to be an attractive targeting method.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Proofs below
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Proofs}
+\label{sec:proofs}
+
+This section gives a formal derivation of the identification results presented in Equations \eqref{eq:TOT}--\eqref{eq:ASL} of \autoref{sec:randchoice}.
+To simplify the presentation, we omit $i$ subscripts throughout.
+%and adopt the shorthand  $Z_0 \equiv \mathbbm{1}(Z=0)$, $Z_1 \equiv \mathbbm{1}(Z=1)$, and $Z_2 \equiv\mathbbm{1}(Z=2)$.
+%The following assumption collects our exclusion restriction and the key features of the constrained choice design.
+
+\begin{assumption}[Randomized Choice Design and Exclusion Restriction]\mbox{}
+\label{assump:randchoice}
+   \begin{enumerate}[(i)]
+   \item $Z$ is independent of $(Y_{0}, Y_{1}, C)$
+   \item $D = \mathbbm{1}(Z \neq 2)Z + \mathbbm{1}(Z = 2)C$
+   \item $Y = \mathbbm{1}(Z = 0) Y_{0} + \mathbbm{1}(Z = 1) Y_{1} + \mathbbm{1}(Z = 2) [ (1 - C) Y_{0} + C Y_{1}]$
+   \end{enumerate}
+\end{assumption}
+
+\begin{lem}
+Under Assumption \ref{assump:randchoice},
+\label{lem_randchoice}
+   \begin{enumerate}[(i)]
+       \item $\mathbbm{E}(D|Z=2) = \mathbb{P}(C=1)$
+       \item $\mathbbm{E}(Y|Z=0) = \mathbbm{E}(Y_0)$
+       \item $\mathbbm{E}(Y|Z=1) = \mathbbm{E}(Y_1)$
+       \item $\mathbbm{E}(Y|D=0,Z=2) = \mathbbm{E}(Y_0|C=0)$
+       \item $\mathbbm{E}(Y|D=1,Z=2) = \mathbbm{E}(Y_1|C=1)$.
+   \end{enumerate} 
+\end{lem}
+
+\begin{proof}
+Part (i) follows because $Z=2$ implies $D=C$ and $Z$ is independent of $C$.  
+Parts (ii) and (iii) follow similarly: given $Z=0$ we have $Y = Y_0$, given $Z=1$ we have $Y = Y_1$, and $Z$ is independent of $(Y_0,Y_1)$.
+For parts (iv) and (v), first note that Assumption \ref{assump:randchoice} (iii) implies that $Z$ is conditionally independent of $(Y_0,Y_1)$ given $C$.
+Now, $Z=2$ implies that $D=0$ if and only if $C=0$. Hence, $\mathbbm{E}(Y|D=0, Z=2) = \mathbbm{E}(Y_0|C=0)$ establishing part (iv).
+For part (v) $Z=2$ implies that $D=1$ if and only if $C=1$ from which it follows that $\mathbbm{E}(Y|D=1, Z=2) = \mathbbm{E}(Y_1|C=1)$.
+\end{proof}
+
+\begin{prop} 
+Under Assumption \ref{assump:randchoice},
+    \begin{enumerate}[(i)]
+        \item $\text{TOT} \equiv \mathbbm{E}(Y_1 - Y_0|C=1)  = \displaystyle \frac{\mathbbm{E}(Y|Z=2) - \mathbbm{E}(Y|Z=0)}{\mathbbm{E}(D|Z=2)}$
+        \item $\text{TUT} \equiv \mathbbm{E}(Y_1 - Y_0|C=0) = \displaystyle \frac{\mathbbm{E}(Y|Z=1) - \mathbbm{E}(Y|Z=2)}{1 - \mathbbm{E}(D|Z=2)}$
+        \item $\text{ASB} \equiv \mathbbm{E}(Y_0|C=1) - \mathbbm{E}(Y_0|C=0) = \displaystyle \frac{\mathbbm{E}(Y|Z=0) - \mathbbm{E}(Y|Z=2,D=0)}{\mathbbm{E}(D|Z=2)}$
+        \item $\text{ASL} \equiv \mathbbm{E}(Y_1|C=1) - \mathbbm{E}(Y_1|C=0) = \displaystyle \frac{\mathbbm{E}(Y|Z=2,D=1) - \mathbbm{E}(Y|Z=1)}{1 - \mathbbm{E}(D|Z=2)}$.
+    \end{enumerate}
+\end{prop}
+
+\begin{proof}
+Parts (i) and (iii) we require an expression for $\mathbbm{E}(Y_0|C=1)$ in terms of $(Y, D, Z)$.
+By Lemma \ref{lem_randchoice}(ii) and iterated expectations 
+\[
+\mathbbm{E}(Y|Z=0) = \mathbbm{E}(Y_0) = \mathbbm{E}(Y_0|C=0) \mathbbm{P}(C=0) + \mathbbm{E}(Y_0|C=1) \mathbbm{P}(C=1).
+\]
+Re-arranging and substituting Lemma \ref{lem_randchoice}(i) and (iv),
+\begin{align}
+\mathbbm{E}(Y_0|C=1)  
+%&= \frac{\mathbbm{E}(Y|Z=0) - \mathbbm{E}(Y_0|C=0) \mathbbm{P}(C=0)}{\mathbbm{P}(C=1)}\nonumber\\ 
+&=  \frac{\mathbbm{E}(Y|Z=0) - \mathbbm{E}(Y|Z=2,D=0) \mathbbm{E}(1 - D|Z=2)}{\mathbbm{E}(D|Z=2)}.
+\label{eq:Y0C1}
+\end{align}
+Part (i) follows by combining \eqref{eq:Y0C1} with Lemma \ref{lem_randchoice}(v) and simplifying; part (iii) follows by combining \eqref{eq:Y0C1} with Lemma \ref{lem_randchoice}(iv) and simplifying.
+Similarly, for parts (ii) and (iv) we require an expression for $\mathbbm{E}(Y_1|C=0)$ in terms of observables.
+By Lemma \ref{lem_randchoice}(iii) and iterated expectations,
+\[
+\mathbbm{E}(Y|Z=1) = \mathbbm{E}(Y_1) = \mathbbm{E}(Y_1|C=0)\mathbbm{P}(C=0) + \mathbbm{E}(Y_1|C=1) \mathbbm{P}(C=1).
+\]
+Re-arranging and substituting Lemma \ref{lem_randchoice}(i) and (v),
+\begin{align}
+\mathbbm{E}(Y_1|C=0) 
+%&= \frac{\mathbbm{E}(Y|Z=1) - \mathbbm{E}(Y_1|C=1)\mathbbm{P}(C=1)}{\mathbb{P}(D=0)} \nonumber\\
+&=\frac{\mathbbm{E}(Y|Z=1) - \mathbbm{E}(Y|Z=2,D=1)\mathbbm{E}(D|Z=2)}{\mathbb{E}(1-D|Z=2)}.
+\label{eq:Y1C0}
+\end{align}
+Part (ii) follows by combining \eqref{eq:Y1C0} with Lemma \ref{lem_randchoice}(iv) and simplifying; part (iv) follows by combining \eqref{eq:Y1C0} with Lemma \ref{lem_randchoice}(v) and simplifying.
+\end{proof}
+
 \newpage

### 2024-05-21 PacDev.tex
ecta submission

--- 2023-10-16 presentation.tex
@@
 \input{preambleBeamer.tex}
+\usepackage{comment}
 
@@
 
-\date{June 2023}
+\date{PACDEV, March 2023}
 
@@
 \begin{itemize}
-    \vfill \item Many institutions —firms, schools, financial contracts— restrict choice using built-in commitment mechanisms which help workers, students, borrowers overcome self-control problems
+    \item Many institutions —firms, schools, financial contracts— restrict choice using built-in commitment mechanisms which help workers, students, borrowers overcome self-control problems
     \begin{itemize}
@@
     \end{itemize}
-    \vfill \pause\item At the same time these firms hide these forcing mechanisms and don’t market their commitment features, potentially because demand for them is low.
-    \vfill  \item  Laibson (2018) argues that clients that benefit from commitment may underestimate its value, and that in such cases private paternalism (i.e.
+    \item At the same time these firms hide these forcing mechanisms and don’t market their commitment features, potentially because demand for them is low.
+     \item  Laibson (2018) argues that clients that benefit from commitment may underestimate its value, and that in such cases private paternalism (i.e.
 allocating them to commitment) could be beneficial.
-    \vfill  \pause\item  \textbf{We study the (a) benefits of imposing a structured repayment contract on financing cost, (b) whether there is demand for such structure, and (c) whether non-takers of such a commitment product would benefit from taking it.}
+    \item  \textbf{We study the (a) benefits of imposing a structured repayment contract on financing cost, (b) whether there is demand for such structure, and (c) whether non-takers of such a commitment product would benefit from taking it.}
 \end{itemize}
 
+\end{frame}
+
+\begin{frame}{Context}
+\begin{itemize}
+     \item Pawn loans involve borrowers leaving valuable liquid assets as collateral in exchange for an immediate cash loan
+     \item The loan is overcollateralized (loan is 70\% of appraised value) and collateral is liquid.
+    \begin{itemize}
+        \item The lender approves loans in a few minutes without income or credit history check $\rightarrow$ used for emergencies.
+    \end{itemize}
+  \item Because the loan is overcollateralized and collateral is liquid, the lender may gain if the borrower defaults on the loan, especially if the borrower pays towards recovery on the way to default.
+     \item Among those that lose their pawn (44\%), 48\% paid a positive amount towards its recovery and on average paid 42\% of loan.
+     \item This happens in spite (or because?) of 74\% of borrowers reporting a 100\% subjective probability recovery ex-ante. 
+    %\vfill   \item 13\% of borrowers are classified as present biased using the simple standard question.
+        \item In such an environment, one may ask if putting more structure/committment in payments may help borrowers recover their pawn.
+      \item Not only that: Will the structure/commitment be demanded by all (or most) people who benefit?
+
+\end{itemize}
 \end{frame}
@@
     \end{columns}
-\end{frame}
-
-\begin{frame}{Context}
-\begin{itemize}
-    \vfill \item Pawn loans involve borrowers leaving valuable liquid assets as collateral in exchange for an immediate cash loan
-    \vfill \pause \item The loan is overcollateralized (loan is 70\% of appraised value) and collateral is liquid.
-    \begin{itemize}
-        \item The lender approves loans in a few minutes without income or credit history check $\rightarrow$ used for emergencies.
-    \end{itemize}
-  \vfill \pause \item Because the loan is overcollateralized and collateral is liquid, the lender may gain if the borrower defaults on the loan, especially if the borrower pays towards recovery on the way to default.
-    \vfill \pause  \item Among those that lose their pawn (60\%), 48\% paid a positive amount towards its recovery and on average paid 42\% of loan.
-    \vfill      \item This happens in spite (or because?) of 74\% of borrowers reporting a 100\% subjective probability recovery ex-ante. 
-    %\vfill   \item 13\% of borrowers are classified as present biased using the simple standard question.
-     \vfill \pause    \item In such an environment, one may ask if putting more structure/committment in payments may help borrowers recover their pawn.
-     \vfill \pause    \item Not only that: Will the structure/commitment be demanded by all (or most) people who benefit?
-
-\end{itemize}
 \end{frame}
@@
 
-\section{Outline}
-\begin{frame}{Outline}
+\begin{frame}{Treatment arms}
+\label{treatment_arms}
    \begin{itemize}
-         \vfill\item \textbf{Experimental Design}
-         \vfill\item Main results
-          \vfill\item Exploiting the Controlled Choice Design
-         \vfill\item Paternalism
+    \vfill \item Randomization at the branch-day level.  Analysis at the pawn level.
+    \begin{itemize}
+        \vfill \item Control arm (1770 obs)
+       \vfill \item Forced Commitment arm (1954 obs)
+       \vfill \item Choice Commitment arm (2580 obs)
+    \end{itemize}
+    \vfill \item The existence of a choice arm allows us not only to measure if there is demand for such a contract, but who demands it, not only in demographic terms, but in terms of potential treatment effects (which include unobservables).
+   \vfill \item  This design is innovative and critical for our purposes, as it enables us to explore whether or not forcing people into a structured payment contract could be more beneficial than allowing choice for a significant fraction of them.
 \end{itemize}
 \end{frame}
-
-\section{Design}
-
-\begin{frame}{Pawn contract}
-    \begin{figure}[H]
-    \label{ExplanatoryMaterial1}
-    \begin{center}
-        \includegraphics[width=0.45\textwidth]{Figuras/sq_contract.png}
-    \end{center}
-\end{figure}
-\end{frame}
-
-\begin{frame}{Structured payments contract}
-   \begin{itemize}
-       \vfill \item We designed a new contract that is identical to the status quo contract except that it enhances the regularity and salience of payments as a way to encourage repayment.
-         \begin{figure}[H]
-    \label{ExplanatoryMaterial2}
-    \begin{center}
-        \includegraphics[width=0.40\textwidth]{Figuras/fc_contract.png}
-    \end{center}
-\end{figure}
-
-   \end{itemize}
-
-\end{frame}
-
-% \begin{frame}{Structured payments contract}
-%   \begin{itemize}
-
-%       \vfill\item The purpose of the small fee was to mainly to make the structured schedule salient, not to be a large disincentive to be late. 
-%       \begin{itemize}
-%           \item Transportation cost to go to the branch to pay is on the same order of magnitude as the fee in average.
-%       \end{itemize}
-%       \vfill\item  The empirical literature provides some guidance that such a contract may decrease default and elicit demand.
-%       \begin{itemize}
-%           \item Field \& Pande (2008) find null effects of payment frequency on loan default for group lending (but samples are small and there is almost no default in the control).
-
-%         \item  Bauer et al. (2012) estimate a positive correlation between measured present bias and selecting into microfinance, which they interpret as demand for structured payments.
-%       \end{itemize}
-
-%   \end{itemize}
-
-% \end{frame}
 
@@
 
-   \begin{equation*}
-    \text{Financial Cost}_i =  \underbrace{\sum_t P^i_{it}}_{\text{Pay to Interest}} + \underbrace{\sum_t P^f_{it}}_{\text{Pay to Fees}}  + \mathds{1}(\text{Default}_i) \times \left[\text{(Appr.
-value - Loan Diff)}_i + \underbrace{\sum_t P^c_{it}}_{\text{Pay to Capital}} \right]
-   \end{equation*}
+\begin{align*}
+    \text{Financial Cost}_i =&  \sum_t P^I_{it} +\sum_t P^F_{it}  
+     + \mathds{1}(\text{Default}_i) \times \left(\text{Value}_i-\text{Loan}_i + \sum_t P^c_{it}\right)
+\end{align*}
 
@@
 
-\begin{frame}{Treatment arms}
-\label{treatment_arms}
-   \begin{itemize}
-    \vfill \item Randomization at the branch-day level.  Analysis at the pawn level.
-    \begin{itemize}
-        \vfill \item Control arm (1770 obs)
-       \vfill \item Forced Commitment arm (1954 obs)
-       \vfill \item Choice Commitment arm (2580 obs)
-    \end{itemize}
-    \vfill \item The existence of a choice arm allows us not only to measure if there is demand for such a contract, but who demands it, not only in demographic terms, but in terms of potential treatment effects (which include unobservables).
-   \vfill \item  This design is innovative and critical for our purposes, as it enables us to explore whether or not forcing people into a structured payment contract could be more beneficial than allowing choice for a significant fraction of them.
-\end{itemize}
-\end{frame}
-
- \begin{frame}{Description}
- \label{consort}
- \begin{figure}[H]
-      \caption{Experiment description}
-     \label{exp_description}
- \begin{center}
-         \includegraphics[width=0.80\textwidth]{Figuras/consort.pdf}
-   \end{center}
- \end{figure}
- %\hyperlink{experimental_integrity}{\beamerbutton{Details}}
-
- \end{frame}
-
 \begin{frame}{Experimental integrity}
@@
 
-\begin{frame}{Balance and Summary statistics}
-    \begin{table}[H]
-%\caption{Summary statistics and Balance}
-\label{SS}
-\begin{center}
-\resizebox{.65\textwidth}{!}{
-\scriptsize{\input{./Tables/SS.tex}}
-}
-\end{center}
-%\textit{Do file: } \texttt{ss\_att.do}
-\end{table}
-% \hyperlink{data}{\beamerbutton{Back}}
-\end{frame}
-
-\begin{frame}{Outline}
-     \begin{itemize}
-         \vfill\item Experimental Design
-         \vfill\item \textbf{Main results}
-          \vfill\item Exploiting the Controlled Choice Design
-         \vfill\item Paternalism 
-     \end{itemize}
-\end{frame}
-
-\begin{frame}
-\textbf{Predictors of take-up : $\Pr(Take up)=11\%$} on average.
-
-\begin{figure}[H]
-    \begin{center}
-        \includegraphics[width=0.9\textwidth]{Figuras/determinants_choose_commitment.pdf}
-    \end{center}
-    \end{figure}
-\end{frame}
-
 \section{Main Results}
@@
 \begin{itemize}
-    \item Financial cost reduced by \$379 pesos (20\% of mean). That is: charging fee + structure \textit{decreased} cost.
-    \item Default decreases by 6.5pp (15\% of mean).
-    \item APR decreases by 34 points, from mean of 184.
+    \item  Takeup of commitment in Choice arm is only 11\%.
+    \item Financial cost reduced by \$204 pesos (20\% of mean). That is: charging fee + structure \textit{decreased} cost.
+    \item Default decreases by 6.5pp (15\% of mean), APR decreases by 11 points, from mean of 57\%.
 \end{itemize}
@@
  \begin{itemize}
-     \item \textbf{Speed of payment:} The first payment of the forced commitment contract  occurs 13 days earlier, increasing the fraction who recover on the first visit by 7.9 pp.
+     \item \textbf{Speed of payment:} The first payment of the forced commitment contract  occurs 14 days earlier, increasing the fraction who recover on the first visit by 7.9 pp.
 Conditional on recovering, they recover 28 days faster.
@@
 
-\begin{frame}{Intermediate outcomes (3)}
-
-    \begin{table}[H]
-\caption{Intermediate outcomes}
-\begin{center}
-\footnotesize{\input{./Tables/mechanism_pres3.tex}}
-\end{center}
-\end{table}
-\vfill
-%\hyperlink{intermediate_outcomes}{\beamerbutton{Back}}
- \begin{itemize}
-     \item \vfill \textbf{Frequency of visits:} Commitment induces a `parting of the waters' whereby those who were going to default visit the branch subsequently .2 fewer times.
-\end{itemize}
-\end{frame}
-
 %\begin{frame}{Intermediate outcomes: forced-commitment}
@@
 
-\begin{frame}{Costs fall from Forcing by multiple measures}
-\label{several_def_cost}
-\begin{table}[H]
-\caption{Effects on several definitions of cost}
-\label{table_robustness_fc}
-\begin{center}
-\resizebox{0.95\textwidth}{!}{
-\small{\input{./Tables/fc_robustness.tex}}
-}
-\end{center}
- \scriptsize
-
-%\textit{Do file: } \texttt{fc\_robustness.do}
-\end{table}
-   % \hyperlink{main_results}{\beamerbutton{Back}}
- \begin{itemize}
-     \item \vfill Significantly reduced costs even when we include:
-     \begin{itemize}
-         \item Subjective rather than objective value of pawn.
-         \item Travel costs.
-         \item Valuing lost liquidity using the interest rate.
-         \item All three at once.
-     \end{itemize}
-\end{itemize}
-\end{frame}
-
-\begin{frame}{Do borrowers value Forcing as measured by repeat business?}
-
-\vspace{.2in}
-\begin{table}[H]
-\begin{center}
-\footnotesize{\input{./Tables/repeat_loans.tex}}
-\end{center}
-\end{table}    
-\begin{itemize}
-    \item Client forced into commitment is 20\% more likely to come back again and pawn.
-    \item Not mechanically from having recovered the pawned, since also pawn other pieces.
-    \item Not within the life of the loan, but after. So unlikely that is a liquidity story.
-    \item Conditional on recovery (endogenous), ``effect'' twice as big.
-\end{itemize}
-
-\end{frame}
-
-\section{Paternalism}
-\begin{frame}{Choice and Heterogeneous Treatment Effects}
-\label{choice_hte}
-    \begin{itemize}
-    \vfill \item  So, forcing commitment decreases APR dramatically.
-
-    \vfill \item \textbf{Low demand:} In spite of this, given the opportunity, only 11\% of borrowers chose commitment.   
-    \begin{itemize}
-       \pause \item If the effect of commitment were homogeneous, this would be enough to conclude that the 89\% who did not choose it would have been financially better off if they had.
-       \item However, we test and reject the null hypothesis of homogeneous treatment effects (Chernozhukov et. al. 2018).
-    \end{itemize}
-
-    \vfill \item The borrowers who did not choose commitment could simply be those who don’t need it?
-    \pause \vfill \item The distribution of TE (i.e.
-$Y_{1i}-Y_{0i}$) is not identified, as one person is only observed in one treatment.
-However, it can be bounded using the two marginal dist $F_1$ and $F_0$.
-
-    \end{itemize}
-\end{frame}
-
-\begin{frame}
-
-\begin{figure}[H]
-    \caption{Fan \& Park bounds for benefit in APR\% }
-    \label{fig:FanPark}
-    \begin{center}
-        \caption{APR}
-        \centering
-        \includegraphics[width=0.7\textwidth]{Figuras/fan_park_bounds_apr.pdf}
-    \end{center}
-
-%\textit{Do file: } \texttt{fan\_park\_bnds.do}       
-\end{figure}
-
-\begin{itemize}
-        \vfill \item \textbf{Many with benefits did not demand:} Making no parametric assumptions, we find that at least 30\% of individual borrowers benefit from commitment $\implies$ many did not demand even though TE is positive for them.
-
-\end{itemize}
-
-\end{frame}
-
-\begin{frame}{Outline}
-     \begin{itemize}
-         \vfill\item Experimental Design
-         \vfill\item Main results
-          \vfill\item \textbf{Exploiting the Controlled Choice Design}
-         \vfill\item Paternalism 
-     \end{itemize}
-\end{frame}
-
-\begin{frame}{Identification afforded by experiment}
+\begin{frame}{Using a Double Exclusion Restriction}
 
@@
 \end{itemize}
-\vspace{.2in}
-Notation: 
-\begin{itemize}
-    \item Potential outcomes $(Y_0,Y_1,C)$
-    \item Assignment: $Z \in \{0,1,2\}$, i.e. \{SQ,Com,Choice\}.  
-    \item Treatment: $D \in \{0,1\} $, i.e. \{SQ,Com\}.
-\end{itemize}
-
 \vspace{.2in}
@@
 used in compulsory school attendance and returns to schooling lit).
-\end{itemize}
-\end{frame}
-
-\begin{frame}{The Double Exclusion Restriction:}
-
-With both of these exclusion restrictions in place:
-\begin{itemize}
-    \item Effect of (Control = Not Choosing) for non-choosers
-    \item Effect of (Forcing = Choosing) for choosers.
-    \end{itemize}
-\begin{itemize}
-    \item  $Y_i = \mathbbm{1}(Z_i =0) Y_{i0} + \mathbbm{1}(Z_i = 1)  Y_{i1}  + \mathbbm{1}(Z_i = 2) \left[(1 - C_i) Y_{i0} + C_i Y_{i1} \right].$
 \end{itemize}
@@
          \item Average Selection on Gains $ASG:=ToT-TuT$
-         \item Average Seletion Bias $ASB:= \E[Y_0 | C=1]-\E[Y_0 | C=0]$
+         \item Average Selection Bias $ASB:= \E[Y_0 | C=1]-\E[Y_0 | C=0]$
          \item Average Selection on Levels $ASL:= \E[Y_1 | C=1]-\E[Y_1 | C=0]$
@@
 \begin{itemize}
-    \vfill \item Commitment increases average financial benefit even for the subset of borrowers who \alert{don't choose to commit voluntarily}.
-    \vfill \item Coefficient ToT>TuT, but cannot reject equality due to large s.e. in ToT.
-    \vfill \item Results hold when imputing transport cost and lost wages per visit, and charge interest in amount paid (as a proxy for liquidity lost).
+    \vfill \item Commitment increases financial benefit even for borrowers who don't choose  it.
+    \vfill \item APR, FC ToT>TuT, but cannot reject equality due to large s.e. in ToT.
 \end{itemize}
@@
 
-\section{Outline}
-\begin{frame}{Outline}
-     \begin{itemize}
-         \vfill\item Experimental Design
-         \vfill\item Main results
-          \vfill\item Exploiting the Controlled Choice Design
-         \vfill\item \textbf{Paternalism}
-     \end{itemize}
-\end{frame}
-
 \begin{frame}{If commitment works, why don't people choose it?}
@@
          \onslide<2>{\item Discounting}
-        \onslide<3-4>{\item Present-Bias}
+        \onslide<3>{\item Present-Bias}
     \end{itemize}
@@
 
-\only<4>{
-
-    \begin{itemize}
-    \item   We estimate the TuT conditional on $X_i=1$ or $X_i=1$ (say $X_i= PB_i$ or $=Confidence_i$) and see which sub-populations have larger TuT.
-
-\vspace{.3in}
-    \begin{align*}
-        1=& \frac{\mathbb{E}[Y_{1i}-Y_{0i} | C_i=0, X_i=1]}{TuT}\Pr(X_i=1 | C_i=0) \\
-        \quad &+ \frac{\mathbb{E}[Y_{1i}-Y_{0i}| C_i=0, X_i=0]}{TuT}\Pr(X_i=0 | C_i=0)
-    \end{align*}
-
-%and we will say that the variable $B_i$ explains the ToT whenever one of the terms (ratio weighted by the probability) is statistically significant from zero, (close to one), and the other term is statistically zero.
-    \end{itemize}
-}
-
 \end{frame}
@@
 
-\begin{frame}{Determinants of Sure Confidence}
-
-        \begin{figure}
-        \caption{What attributes correlate with Sure Confidence?}
-        \centering
-        \includegraphics[width=0.65\textwidth]{Figuras/determinants_confidence_100.pdf}
-        \end{figure}
-
-The Sure-Confident are:
-\begin{itemize}
-    \item   Older, more educated men who
-    \item   Have savings and do not report financial stress or trouble meeting bills, and 
-    \item   Are likely to be relied upon by family members.
-\end{itemize}
-
-\end{frame}
-
 \begin{frame}{Understanding Heterogeneity with a Causal Forest}
@@
 \item We use (Athey et.al. 2019) GRF to estimate CATE (causal RF), CTUT and CTOT (instrumental RF).
-
-\begin{itemize}	
-	\item We split the data that produce the biggest difference in TE across leaves, by still producing accurate estimates of the TE.
-Moreover, the splits are made honest by taking the training data and splitting it into two subsamples: a splitting subsample and an estimating subsample.
-\hyperlink{honest_causal_tree}{\beamerbutton{Honest Causal Tree}}
 \end{itemize}
-
-\item Estimated TE in each leaf is aysmptotically normal. 
-\end{itemize}
-
-    \begin{figure}
-        \caption{CATT (APR)}
-        \centering
-        \includegraphics[width=0.5\textwidth]{Figuras/he_dist_tau_hat_tut.pdf}
-        \end{figure}
-
- \begin{itemize}
-\item We test and reject the null hypothesis of homogeneous treatment effects (Chernozhukov et. al. 2018)
- \end{itemize}       
-\end{frame}
-
-\begin{frame}{Example of a Causal Tree}
-
-    \begin{figure}
-        \caption{Causal Tree}
-        \centering
-\includegraphics[width=0.8\textwidth]{Figuras/crf_apr.pdf}
-        \end{figure}
-
-\end{frame}
-
-\begin{frame}{Fraction that forgo benefit:  Choice Arm}
 
@@
     \item  $<$ 20\% of choosers made a mistake.
-\end{itemize}
-
-\end{frame}
-
-\begin{frame}{Fraction that forgo benefit:  Forcing Arm}
-
-        \begin{figure}
-         \label{better_forceall}
-        \caption{Effect of forcing everyone}
-        \centering
-        \includegraphics[width=0.65\textwidth]{Figuras/cdf_CATE.pdf}
-        \end{figure}
-
-\begin{itemize}
-    \item   Now use Random Forest to estimate the CATE of forcing, examine heterogeneity in ATE.
-    \item   Because CATE>CTUT, we now find fully 91\% of individuals better off being forced into commitment than staying in control.
 \end{itemize}
@@
 
-\begin{frame}{Comparing `Wide' and `Narrow' Heterogeneity}
-
-    \label{wide_v_narrow}
-
-        \begin{figure}
-        \caption{Scatterplot of Predicted Heterogeneity}
-        \centering
-        \includegraphics[width=0.75\textwidth]{Figuras/scatter_hist_wide_narrow.pdf}
-        \end{figure}
-
-\begin{itemize}
-    \item   Substantially less heterogeneity fitting APR CATE with `narrow' than `wide'
-    \item Test of homogeneity (Chernozhukov et. al. 2018) no longer rejected with `narrow'
-    \item   However, overall fitted relationship shows `narrow' adjusts to the mean TE.
-\end{itemize}
-
-\end{frame}
-
-\begin{frame}{Comparison of Targeting Performance:  CDFs}
-
-        \begin{figure}
-        \label{targeting_CDFs}
-        \caption{Distribution of Benefits under Different Targeting Rules}
-        \centering
-        \includegraphics[width=0.70\textwidth]{Figuras/wide_narrow_rule.pdf}
-        \end{figure}
-
-\begin{itemize}
-    \item   Even using the Random Forest to target, our four `narrow' variables only increase the fraction benefitting from 91\% (all Forced) to ~93\% (targeted).
-    \item  Using a Logit with the `narrow' variables actually worsens performance relative to universal Forcing because Logit matches benefit/loss fraction, has both Type 1 and Type 2 errors.
-\end{itemize}
-
-\end{frame}
-
 \begin{frame}{Comparison of Targeting Performance:  Hit-Miss Table}
@@
         %\end{itemize}
-        \vfill \item  APR reduced by 34\% in the commitment arm
-        \vfill  \item Results suggest selection on gains, but still large effects of imposing commitment on non-takers.
+        \vfill \item  APR reduced by 19\% in the commitment arm
         \vfill \item Mystery of low take-up combined with large TuT seems best explained by sure-confidence among pawnshop customers.
@@
     \hyperlink{treatment_arms}{\beamerbutton{Back}}
+\end{frame}
+
+\begin{frame}{Costs fall from Forcing by multiple measures}
+\label{several_def_cost}
+\begin{table}[H]
+\caption{Effects on several definitions of cost}
+\label{table_robustness_fc}
+\begin{center}
+\resizebox{0.95\textwidth}{!}{
+\small{\input{./Tables/fc_robustness.tex}}
+}
+\end{center}
+ \scriptsize
+
+%\textit{Do file: } \texttt{fc\_robustness.do}
+\end{table}
+   % \hyperlink{main_results}{\beamerbutton{Back}}
+ \begin{itemize}
+     \item \vfill Significantly reduced costs even when we include:
+     \begin{itemize}
+         \item Subjective rather than objective value of pawn.
+         \item Travel costs.
+         \item Valuing lost liquidity using the interest rate.
+         \item All three at once.
+     \end{itemize}
+\end{itemize}
+\end{frame}
+
+\begin{frame}{Do borrowers value Forcing as measured by repeat business?}
+
+\vspace{.2in}
+\begin{table}[H]
+\begin{center}
+\footnotesize{\input{./Tables/repeat_loans.tex}}
+\end{center}
+\end{table}    
+\begin{itemize}
+    \item Client forced into commitment is 20\% more likely to come back again and pawn.
+    \item Not mechanically from having recovered the pawned, since also pawn other pieces.
+    \item Not within the life of the loan, but after. So unlikely that is a liquidity story.
+    \item Conditional on recovery (endogenous), ``effect'' twice as big.
+\end{itemize}
+
 \end{frame}

### 2024-05-21 donde.tex
ecta submission

@@
 Our experiment covers just under 5,000 pawnshop clients in 6 of our partner lender's Mexico City branches.
-Our control arm illustrates the costs of the status quo contract: fully \emph{44\%} of borrowers default, losing lose their pawn along with any payments made towards principal.\footnote{High pawn default rates are common, in the US they oscilate around 15\% (see \href{https://tinyurl.com/yc2x5bjf}{here}).} Our ``commitment choice'' arm gives borrowers the chance to opt into a structured repayment contract when taking a loan.
+Our control arm illustrates the costs of the status quo contract: fully \emph{44\%} of borrowers default, losing lose their pawn along with any payments made towards principal.\footnote{High pawn default rates are common, in the US they oscillate around 15\% (see \href{https://tinyurl.com/yc2x5bjf}{here}).} Our ``commitment choice'' arm gives borrowers the chance to opt into a structured repayment contract when taking a loan.
 The structured contract requires borrowers to make three monthly payments rather than one balloon payment at the end, with each monthly payment including the accrued interest at that time as well as a nominal fee of 2\% of that month's payment if the payment is delinquent.

### 2024-05-24 OA.tex
revisions for r3
new submission

@@
 We now present analysis of the extent to which the survey-responding sample is representative and balanced.
-Table \ref{SS_cond_survet} presents information about survey non-response.
+Table \ref{SS_cond_survey} presents information about survey non-response.
 Panel A is a balance table that compares loan amount and day of the week across treatment arms for the subset of borrowers who responded to at least one survey question.
@@
 From the table, we see that loan amount and weekday are balanced across treatment arms among survey respondents and that response rates are likewise stable across treatment arms.
-Table \ref{TUT_cond_survet} shows how the estimated TUT effect changes if we restrict our estimation sample based on survey response.
+Table \ref{TUT_cond_survey} shows how the estimated TUT effect changes if we restrict our estimation sample based on survey response.
 The first row of the table presents TUT results for the financial cost outcome, while the second presents corresponding results for the APR outcome.
@@
 \caption{Balance conditional on survey response and question-by-question response rates} %by treatment arm}
-\label{SS_cond_survet}
+\label{SS_cond_survey}
 \begin{center}
@@
 \caption{Survey Non-response: TUT estimates for respondents to each survey question.}
-\label{TUT_cond_survet}
+\label{TUT_cond_survey}
 \begin{center}

### 2024-05-24 Restud submission/OA_restud.tex
new submission

--- 2024-05-21 ECTA submission/OA_ecta.tex
@@
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\setcounter{table}{0}
+\setcounter{figure}{0}
+\setcounter{section}{0}
+\pagenumbering{gobble}
+% APPENDIX 
 \pagenumbering{arabic}
@@
 
-\begin{frontmatter}
-
-\title{ONLINE APPENDIX: The controlled choice design and private paternalism in pawnshop borrowing}
-\runtitle{The controlled choice design and private paternalism}
-
-\begin{aug}
-% use \particle for den|der|de|van|von (only lc!)
-% [id=?,addressref=?,corref]{\fnms{}~\snm{}\ead[label=e?]{}\thanksref{}}
-%
-%% e-mail is mandatory for each author
-%
-%%% initials in fnms (if any) with spaces
-%
-\author[id=au1,addressref={add1}]{\fnms{Craig}~\snm{McIntosh}\ead[label=ee1]{ctmcintosh@ucsd.edu}}
-\author[id=au2,addressref={add2}]{\fnms{Isaac}~\snm{Meza}\ead[label=ee2]{isaacmezalopez@g.harvard.edu}}
-\author[id=au3,addressref={add3}]{\fnms{Joyce}~\snm{Sadka}\ead[label=ee3]{jsadka@itam.mx}}
-\author[id=au4,addressref={add4}]{\fnms{Enrique}~\snm{Seira}\ead[label=ee4]{enrique.seira@gmail.com}}
-\author[id=au5,addressref={add5}]{\fnms{Francis J.}~\snm{DiTraglia}\ead[label=ee5]{francis.ditraglia@economics.ox.ac.uk}}
-
-% Addresses
-\address[id=add1]{%
-\orgdiv{Department of Economics}
-\orgname{University of California San Diego}}
-
-\address[id=add2]{%
-\orgdiv{Department of Economics}
-\orgname{Harvard University}}
-
-\address[id=add3]{%
-\orgdiv{Department of Economics}
-\orgname{Instituto Tecnologico Autonomo de Mexico}}
-
-\address[id=add4]{%
-\orgdiv{Department of Economics}
-\orgname{Michigan State University}}
-
-\address[id=add5]{%
-\orgdiv{Department of Economics}
-\orgname{University of Oxford}}
-\end{aug}
-
-\end{frontmatter}
-
-\newpage
+\newgeometry{margin=1in}
+\begin{center}
+	\Large ONLINE APPENDIX: The controlled choice design and private paternalism in pawnshop borrowing \\[0.5em]
+	%\Large{Appendix $-$ For Online Publication} \\[1em]
+	\large \author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira \and Francis J.\ DiTraglia}
+\end{center}
 
@@
 \begin{figure}[!h]
-
+     \caption{Behavior of borrowers who lost their pawn.}
     \begin{center}
@@
     \end{center}
-        \caption{Behavior of borrowers who lost their pawn.
-This figure provides more details on the behavior of clients who were assigned to the control group and did not recover their pawn.
+        \footnotesize{This figure provides more details on the behavior of clients who were assigned to the control group and did not recover their pawn.
 Panel (a) shows a histogram of days elapsed from the pawn to the first payment, while panel (b) displays a histogram of days elapsed until the last payment.
@@
 
+\begin{figure}[H]
+    \caption{Determinants of choice.}
+    \begin{center}
+    \begin{subfigure}{0.65\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/determinants_choose_commitment.pdf}
+    \end{subfigure}
+    \end{center}
+\footnotesize{The above figure shows the determinants in a bivariate and multivariate OLS regression of choosing commitment.
+Choice commitment is a binary variable equal to one, whenever subjects choose the forced commitment contract in the choice arm.
+}
+    \label{weekly_def_rates}
+%\textit{Do file: } \texttt{determinants_choice.do}       
+\end{figure}
+
+\normalsize
+%Really force it to normal size and linespread
+\normalsize
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \resizebox{0.65\textwidth}{!}{
-\scriptsize{\input{./Tables/SS.tex}}
+\footnotesize{\input{./Tables/SS.tex}}
 }
 \end{center}
-\legend {This table has two panels.
-Panel A uses administrative data at the loan level, while Panel B uses survey data.
-Each row in this table corresponds to a regression, where the level of observation is the individual loan originated.
+\footnotesize {Each row in this table corresponds to a regression, where the level of observation is the individual loan originated.
 The dependent variables of these regressions are displayed in the first column.
@@
 The admin data was a very limited set of pre-determined variables.
-The dependent variables in Panel A are the loan amount in pesos, and an indicator for whether the day of the loan origination was a weekday (as opposed to weekend).
-The dependent variables in Panel B from the survey.
-Subjective value of the pawn (how much would the client be willing to sell it for (Q3), an indicator for having trouble paying bills in the last 6-months (Q28), present bias (constructed from questions Q10 and Q29 in the standard way as in \cite{Ashraf}), an indicator for whether they make expenses budget for the month ahead of time.
+The dependent variables are: subjective value of the pawn (how much would the client be willing to sell it for (Q3), an indicator for having trouble paying bills in the last 6-months (Q28), present bias (constructed from questions Q10 and Q29 in the standard way as in \cite{Ashraf}), an indicator for whether they make expenses budget for the month ahead of time.
 The subjective probability of recovery was elicited a la Manski (from 0 to 100 what is the probability that you will recoup your pawn), pawned before is a dummy=1 if the client declares to have pawned before (although not necessarily with Lender $P$) age is in year, +High-school is a dummy that indicates if the client has completed high school.
 }
-%\textit{Do file: } \texttt{ss\_att.do}
+%\textit{Do file: } \texttt{ss\_balance.do}
 \end{table}
@@
 \begin{center}
-\scriptsize{\input{./Tables/Attrition.tex}}
-\end{center}
-\legend{Each row in this table 
+\footnotesize{\input{./Tables/Attrition.tex}}
+\end{center}
+\footnotesize{Each row in this table 
  corresponds to a regression.
@@
 We find that in no arm did more than three percent of individuals who responded to the survey go on to refuse loans.
-That is, the overwhelming marjority of potential borrowers did not leave the branch after learning which contract was on offer.
+That is, the overwhelming majority of potential borrowers did not leave the branch after learning which contract was on offer.
 Moreover, the extremely small fraction that did leave is balanced across arms.
@@
 %We now present an analysis of the extent to which the survey-responding sample is representative and balanced.
-Table \ref{SS_cond_survet} presents information about survey non-response.
+Table \ref{SS_cond_survey} presents information about survey non-response.
 Panel A is a balance table that compares loan amount and day of the week across treatment arms for the subset of borrowers who responded to at least one survey question.
@@
 
-% Table \ref{TUT_cond_survet} shows how the estimated TUT effect changes if we restrict our estimation sample based on survey response.
+% Table \ref{TUT_cond_survey} shows how the estimated TUT effect changes if we restrict our estimation sample based on survey response.
 % The first row of the table presents TUT results for the financial cost outcome, while the second presents corresponding results for the APR outcome.
@@
 % \caption{Survey Non-response: TUT estimates for respondents to each survey question.}
-% \label{TUT_cond_survet}
+% \label{TUT_cond_survey}
 % \begin{center}
-% \scriptsize{\input{./Tables/tut_cond_survey.tex}}
+% \footnotesize{\input{./Tables/tut_cond_survey.tex}}
 % \end{center}
-% \legend{Some borrowers did not respond to our survey; others only completed part of the survey.
+% \footnotesize{Some borrowers did not respond to our survey; others only completed part of the survey.
 % This table computes the TUT effect for a number of sub-groups by survey response, and compares them against the overall TUT effect.
@@
 \begin{figure}[H]
-
-    \begin{center}
-    \begin{subfigure}{0.6\textwidth}
+    \caption{Determinants of choice.}
+    \begin{center}
+    \begin{subfigure}{0.65\textwidth}
         \centering
@@
     \end{center}
-\caption{Determinants of choice.
-The above figure shows the determinants in a bivariate and multivariate OLS regression of choosing commitment.
+\footnotesize{The above figure shows the determinants in a bivariate and multivariate OLS regression of choosing commitment.
 Choice commitment is a binary variable equal to one, whenever subjects choose the forced commitment contract in the choice arm.
@@
 \end{center}
-\legend{This table explores treatment effects in ``intermediate variables''.
+\footnotesize{This table explores treatment effects in ``intermediate variables''.
 Each column represents regression output for different dependent variables following equation (\ref{basic_reg}).
@@
 
+\normalsize
+%Really force it to normal size and linespread
+\normalsize
+
 \subsection{Censoring} \label{App_censoring}
@@
 \resizebox{0.75\textwidth}{!}{
-\scriptsize{\input{./Tables/censoring_imp.tex}}
+\footnotesize{\input{./Tables/censoring_imp.tex}}
 }
@@
 \end{table}
-
- \legend{ Given the censored loans, i.e.
+ \footnotesize{ Given the censored loans, i.e.
 loans that have not finished by the end of the observation period, we estimate `a la Manski' bounds for these loans, meaning that we impute all loans to either \emph{default}$=1$ or \emph{recovery}$=0$ depending on the treatment arm.
@@
 \begin{figure}[H]
+\caption{Survival graph.}
     \begin{center}
@@
     \end{center}
-      \caption{Survival graph. This Figure shows the CDF of loan completion either default or recovery in Panel (a), or loan recovery in Panel (b), by the number of days since first pawn.}
+      \footnotesize{This Figure shows the CDF of loan completion either default or recovery in Panel (a), or loan recovery in Panel (b), by the number of days since first pawn.}
       \label{survival_graph}
@@
 \resizebox{0.9\textwidth}{!}{
-\scriptsize{\input{./Tables/fc_robustness.tex}}
+\footnotesize{\input{./Tables/fc_robustness.tex}}
 }
 \end{center}
- \legend{ This table augments the measure of financial cost presented in Table \ref{main_impact_table} with measures of transaction costs, subjective costs, and adjustments for liquidity costs.
+ \footnotesize{ This table augments the measure of financial cost presented in Table \ref{main_impact_table} with measures of transaction costs, subjective costs, and adjustments for liquidity costs.
 Panel A reports financial cost in pesos, while Panel B shows APR.
@@
 \newpage
+
+\normalsize
+
+%Really force it to normal size and linespread
+\normalsize
 
@@
 \begin{center}
-\scriptsize{\input{./Tables/learning_exp.tex}}
-\end{center}
- \legend{Column (1) reports results for the 228 borrowers who returned to pawn again at a day/branch that was randomly assigned to the choice arm, enabling us to observe whether they chose commitment or the status quo contract.
+\footnotesize{\input{./Tables/learning_exp.tex}}
+\end{center}
+ \footnotesize{Column (1) reports results for the 228 borrowers who returned to pawn again at a day/branch that was randomly assigned to the choice arm, enabling us to observe whether they chose commitment or the status quo contract.
 Each row presents a difference in mean commitment take-up rates and associated standard errors.
@@
 \end{table}
+\normalsize
+%Really force it to normal size and linespread
+\normalsize
+
+\newpage
 
@@
 
-\vspace{-.3in}
 \begin{figure}[!h]
-
-    \begin{center}
-        \centering
-        \includegraphics[width=0.55\textwidth]{Figuras/discount_effect_tut.pdf}
-    \end{center}
-      \caption{Financial benefit TUT effect for different discount rates.
-This Figure re-estimates the treatment on the untreated (TUT) effect from Table \ref{tot_tut}, introducing a daily discount factor in the definition of financial benefit.
+  \caption{Financial benefit TUT effect for different discount rates.}
+    \begin{center}
+        \centering
+        \includegraphics[width=0.65\textwidth]{Figuras/discount_effect_tut.pdf}
+    \end{center}
+       \footnotesize{This Figure re-estimates the treatment on the untreated (TUT) effect from Table \ref{tot_tut}, introducing a daily discount factor in the definition of financial benefit.
 At a given annual discount rate in percentage points (x-axis) the solid line gives the adjusted TUT and the shaded regions 90\% \& 95\% confidence bands.
@@
 
+\normalsize
+%Really force it to normal size and linespread
+\normalsize
+
 \subsection{Present Bias}\label{App_presentbias}
@@
 \begin{figure}
-    \begin{center}
-        \centering
-        \includegraphics[width=0.7\textwidth]{Figuras/tut_beh_partition.pdf} 
-    \end{center}
-     \scriptsize  
-\caption{Heterogeneity of the TUT by behavioral variables.
-Each panel in this figure shows how the estimated treatment on the untreated (TUT) effect varies with a binary survey variable $X_i$.
+\caption{Heterogeneity of the TUT by behavioral variables.}
+    \begin{center}
+        \centering
+        \includegraphics[width=0.65\textwidth]{Figuras/tut_beh_partition.pdf} 
+    \end{center}  
+ \footnotesize{Each panel in this figure shows how the estimated treatment on the untreated (TUT) effect varies with a binary survey variable $X_i$.
 In the left panel (P.B.), $X_i = 1$ if borrower $i$ is ``present-biased'' based on her responses to the time preference questions from our survey.
@@
 }
-
     \label{tut_beh_partition}
@@
 \begin{figure}[H]
-    \begin{center}
-    \begin{subfigure}{0.6\textwidth}
+\caption{Determinants sure confidence.}
+    \begin{center}
+    \begin{subfigure}{0.60\textwidth}
         \centering
@@
     \end{center}
-    \caption{Determinants sure confidence.
-The above figure shows the determinants in a bivariate and multivariate OLS regression of sure confidence among the non-choosers.
+     \footnotesize{The above figure shows the determinants in a bivariate and multivariate OLS regression of sure confidence among the non-choosers.
 Sure confidence is a binary variable defined to be one when people report a 100\% probability of recovery.}
@@
 \end{figure}
+
+\newpage
 
@@
 %\begin{center}
-%\scriptsize{\input{./Tables/test_calibration_2.tex}}
+%\footnotesize{\input{./Tables/test_calibration_2.tex}}
 %\end{center}
@@
 \begin{figure}[!h]
-
-    \begin{center}
-    \begin{subfigure}{0.55\textwidth}
+   \caption{Fan \& Park bounds for benefit in APR\%.}
+    \begin{center}
+    \begin{subfigure}{0.65\textwidth}
         \caption{APR Bounds}
@@
     \end{center}
-        \caption{Fan \& Park bounds for benefit in APR\%.
-This figure depicts the \cite{fan2010sharp} bounds on the distribution $F_\Delta$ of individual treatment effects $\Delta \equiv (Y_1 - Y_0)$, described in Section \ref{sec:bounds}, for the APR outcome.
+          \footnotesize{This figure depicts the \cite{fan2010sharp} bounds on the distribution $F_\Delta$ of individual treatment effects $\Delta \equiv (Y_1 - Y_0)$, described in Section \ref{sec:bounds}, for the APR outcome.
     The dark red curve and light red shaded region give the estimated upper bound function $\overline{F}$ for $F_\Delta$ and associated (pointwise) 95\% confidence interval. 
@@
 
-\begin{figure}
-
+\begin{figure}[!h]
+\caption{Distribution of treatment effects under rank invariance.}        
     \begin{center}
@@
     \end{center}
-    \caption{Distribution of treatment effects under rank invariance.
-This figure shows the CDF of individual treatment effects under the assumption of rank invariance, computed from $F_\Delta(\delta) = \int_0^1 \mathbbm{1}\{ F_1^{-1}(u) - F_0^{-1}(u)\leq \delta\}\,\mathrm{d}u$ where $F_1^{-1}$ and $F_0^{-1}$ are the quantile functions of $Y_1$ and $Y_0$.}
+    \footnotesize{This figure shows the CDF of individual treatment effects under the assumption of rank invariance, computed from $F_\Delta(\delta) = \int_0^1 \mathbbm{1}\{ F_1^{-1}(u) - F_0^{-1}(u)\leq \delta\}\,\mathrm{d}u$ where $F_1^{-1}$ and $F_0^{-1}$ are the quantile functions of $Y_1$ and $Y_0$.}
 \label{te_rankinvariance}
@@
 
-\begin{figure}
-
-    \begin{center}
-     \begin{subfigure}{0.32\textwidth}
+\begin{figure}[!h]
+     \caption{Heterogeneous Treatment Effects.} 
+     \label{heterogeneous_effects}    
+    \begin{center}
+     \begin{subfigure}{0.35\textwidth}
        \centering
@@
     \end{subfigure}
-    \begin{subfigure}{0.32\textwidth}
+    \begin{subfigure}{0.35\textwidth}
        \centering
@@
     \end{subfigure} 
-       \begin{subfigure}{.32\textwidth}
+       \begin{subfigure}{.35\textwidth}
         \centering
@@
     \end{center}
-    \caption{Heterogeneous Treatment Effects.}
-    \label{heterogeneous_effects}    
   %\footnotesize{ } \textit{Do file: }  \texttt{cate_dist.do}
@@
 \begin{figure}[h!]
-
+   \caption{Conditional ATEs from ``wide'' and ``narrow'' covariate sets.}
     \begin{center}
@@
     \end{center}
-       \caption{Conditional ATEs from ``wide'' and ``narrow'' covariate sets.
-This figure plots the relationship between the causal forest conditional ATE estimates from Section \ref{sec:RF} that use the ``wide'' set of covariates (all intake survey responses) and those based on a restricted ``narrow'' set of covariates (age, gender, HS education, and previous borrowing).
+        \footnotesize{This figure plots the relationship between the causal forest conditional ATE estimates from Section \ref{sec:RF} that use the ``wide'' set of covariates (all intake survey responses) and those based on a restricted ``narrow'' set of covariates (age, gender, HS education, and previous borrowing).
 The scatterplot graphs one estimate versus the other, with the ``wide'' covariate set on the horizontal axis and the ``narrow'' set on the vertical axis.
@@
 
+\normalsize
+%Really force it to normal size and linespread
+\normalsize
+
 \subsection{Inference for ASG, ASB, and ASL}

### 2024-05-24 Restud submission/STATA_documentation.tex
new submission

--- 2024-05-24 OA.tex
@@
-%  \documentclass[oneside,11pt]{article}
-
-% \input{preamble.tex}
-% %%% HELPER CODE FOR DEALING WITH EXTERNAL REFERENCES
-% \usepackage{xr}
-% \makeatletter
-% \newcommand*{\addFileDependency}[1]{
-%   \typeout{(#1)}
-%   \@addtofilelist{#1}
-%   \IfFileExists{#1}{}{\typeout{No file #1.}}
-% }
-% \makeatother
-
-% \newcommand*{\myexternaldocument}[1]{
-%     \externaldocument{#1}
-%     \addFileDependency{#1.tex}
-%     \addFileDependency{#1.aux}
-% }
-
-% %\myexternaldocument{OA}
-
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% DOCUMENT
-% \begin{document}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% APPENDIX 
-\setcounter{table}{0}
-\setcounter{figure}{0}
-\setcounter{section}{0}
-\pagenumbering{gobble}
+\documentclass[11pt, a4paper]{article}
+
+\input{preamble.tex}
+%%% HELPER CODE FOR DEALING WITH EXTERNAL REFERENCES
+\usepackage{xr}
+\makeatletter
+\newcommand*{\addFileDependency}[1]{
+  \typeout{(#1)}
+  \@addtofilelist{#1}
+  \IfFileExists{#1}{}{\typeout{No file #1.}}
+}
+\makeatother
+
+\newcommand*{\myexternaldocument}[1]{
+    \externaldocument{#1}
+    \addFileDependency{#1.tex}
+    \addFileDependency{#1.aux}
+}
 
 \newgeometry{margin=1in}
-
-\begin{center}
-	\LARGE Supplementary Appendix for ``The controlled choice design and private paternalism in pawnshop borrowing'' \\[0.5em]
-	%\Large{Appendix $-$ For Online Publication} \\[1em]
-	\large \author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira \and Francis J.\ DiTraglia}
-\end{center}
-
-\appendix
-\pagenumbering{arabic}
-\renewcommand\thefigure{OA-\arabic{figure}}
-\renewcommand\thetable{OA-\arabic{table}}
-\renewcommand*{\thepage}{OA - \arabic{page}}
-\renewcommand\thesection{Appendix \Alph{section}.}
-\renewcommand\thesubsection{\Alph{section}.\arabic{subsection}}
-
-%\renewcommand{\cftparskip}{0em} % NOT NEEDED
-\renewcommand\cftsecdotsep{\cftdotsep}
-\renewcommand\cftsubsecdotsep{\cftnodots}
-\renewcommand{\cftsecnumwidth}{6em}
- \renewcommand{\cftpnumalign}{r}
-%\renewcommand{\cftsecleader}{\normalfont\cftdotfill{\cftsecdotsep}}
-
-\renewcommand{\cftsecleader}{\cftdotfill{\cftsecdotsep}\hspace{1.8em}}
-%\renewcommand{\cftsecpagefont}{20em}
-%\renewcommand{\cftfignumwidth}{6em}
-%\renewcommand{\cfttabnumwidth}{3.3em}
-
-%\tableofcontents
-\etocdepthtag.toc{mtappendix}
-\etocsettagdepth{mtchapter}{none}
-\etocsettagdepth{mtappendix}{subsection}
-
-\setstretch{0.9}
-%\renewcommand\contentsname{} % the empty name
-
-%\begingroup
-%\let\clearpage\relax
-%%\vspace{-1.5em} % the removed space. Set as appropriate
-%\tableofcontents
-%\endgroup
-
-%\newpage
-
-\linespread{1}
-
-%\section{ Treatment Explanation Materials and Pictures}
-\section{Treatment Explanation Materials} 
-%\vspace{.2in}
-
-%\subsection{Materials}
-
-\begin{figure}[H]
-     \caption{Contract Terms Summary}
-    \label{PaperSlip}
-    \begin{center}
-    %\begin{subfigure}{0.65\textwidth}
-    %\caption{Receipt for client}
-     %   \centering
-        \includegraphics[width=0.5\textwidth]{Figuras/TicketLenderP.png}
-    %\end{subfigure}
-
-    %\vspace{3ex}
-    %\begin{subfigure}{0.65\textwidth}
-    %\caption{Personal promise signed by client}
-     %   \centering
-    %    \includegraphics[width=\textwidth]{Figuras/Personal Promise2.png}
-    %\end{subfigure}
-    \end{center}
-    \scriptsize{
-        We show a sample receipt that was given to clients that got assigned to the fee-forcing contract (the font and format were changed to protect Lender's P identity).
-We want to highlight the salience of some items.
-First the title clearly indicated which contract the client has (arrow 1).
-Second, in the case of the fee contract it clearly indicates that there is a fee for paying late equivalent to 2\% of the value of the monthly payment (arrow 2).
-Third, there is a calendar for payments clearly specifying the dates and amounts to pay each month.
-%The bottom panel of the figure shows a ``promise slip'', the paper that those who were assigned (or chose) to the monthly payment with promise had to sign to make the promise salient.
-It emphasizes that the client is giving his word, and that the promise is not a legal document.
-        }
-\end{figure}
-
-\begin{figure}[H]
-     \caption{Explanatory Material}
-    \label{ExplanatoryMaterial}
-    \begin{center}
-        \centering
-        \includegraphics[width=0.6\textwidth]{Figuras/micas.pdf}
-
-    \end{center}
-    \scriptsize{
-        This is a (translated) sample information slide shown to clients. The real ones were twice the size of this figure and were laminated. Different ones were shown for each treatment arm.}
-\end{figure}
-
-%\subsection{Pictures}
-%
-%\begin{figure}[H]
-%     \caption{Some Pawnshops}
-%    \label{PawnshopPicture}
-%    \begin{center}
-%    \begin{subfigure}{0.405\textwidth}
-%    \caption{Appraiser/tellers inside a pawnshop}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/empenio9_.png}
-%    \end{subfigure}
-%        \begin{subfigure}{0.45\textwidth}
-%    \caption{Pawnshop}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/empenio11_.png}
-%    \end{subfigure}
-%    
-%        \vspace{3ex}
-%
-%    \begin{subfigure}{0.45\textwidth}
-%    \caption{Pawnshop}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/empenio2_.png}
-%    \end{subfigure}
-%    \begin{subfigure}{0.415\textwidth}
-%    \caption{Lost pawns which are for sale}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/empenio3_.png}
-%    \end{subfigure}
-%    \end{center}
-%    \scriptsize{
-%        This figure  shows pictures of pawnshops in Mexico city. They do not necessarily coincide with Lender P for confidentiality.} 
-%\end{figure}
-
-%\vspace{.1in}
-%\begin{figure}[H]
-%     \caption{Gold buyers next to pawnshops}
-%    \label{GoldBuyers}
-%    \begin{center}
-%    \begin{subfigure}{.49\textwidth}
-%    \caption{Gold buyer next to pawnshop 1}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/empenio7_.png}
-%    \end{subfigure}
-%    \begin{subfigure}{.49\textwidth}
-%    \caption{Gold buyer next to pawnshop 1}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/empenio8_.png}
-%    \end{subfigure}
-%       \vspace{3ex}
-%       
-%    \end{center}
-%    \scriptsize{
-%        This figure shows pictures of gold buyers next to pawnshops in Mexico city. They do not necessarily coincide with Lender P for confidentiality. }
-%\end{figure}
-
-\begin{comment}
-\\
-\begin{table}[H]
-\caption{Number of pawns balance before and after the experiment}
-\label{num_pawns_bal}
-\begin{center}
-\scriptsize{\input{./Tables/num_pawns_bal.tex}}
-\end{center}
- \scriptsize 
-%\textit{Do file: } \texttt{num\_pawns\_bal.do}
-\end{table}
-\end{comment}
-%\todo[inline]{removed}
-
-\newpage
-\subsection{Survey}   \label{app:survey_data}
-
-\normalsize
-\linespread{1.05}
-%Really force it to normal size and linespread
-\normalsize
-\linespread{1.05}
-
-\begin{table}[H]
-\caption{Baseline survey questions (translated to English)}
-\label{baseline_survey}
-\begin{center}
-\scriptsize{\input{./Tables/transcribed.tex}}
-\end{center}
-\scriptsize{
-Translation of the baseline questionnaire.}
-\end{table}
-
-\newpage
-
-We now present analysis of the extent to which the survey-responding sample is representative and balanced.
-Table \ref{SS_cond_survey} presents information about survey non-response.
-Panel A is a balance table that compares loan amount and day of the week across treatment arms for the subset of borrowers who responded to at least one survey question.
-The p-values in the fourth column are for the F-test of no difference of means across treatment arms. 
-Panel B presents response-rates by question for each arm of the experiment, along with p-values for the F-test of no difference in question-specific response rates across treatment arms. 
-This panel uses data from participants who answered at least one survey question and went on to pawn on the same day as their survey response.
-From the table, we see that loan amount and weekday are balanced across treatment arms among survey respondents and that response rates are likewise stable across treatment arms.
-Table \ref{TUT_cond_survey} shows how the estimated TUT effect changes if we restrict our estimation sample based on survey response.
-The first row of the table presents TUT results for the financial cost outcome, while the second presents corresponding results for the APR outcome.
-In each row, column (1) presents the full-sample TUT estimate and standard error while the remaining columns restrict the sample to borrowers who answered a particular survey question or set of questions.
-For example, column (4) presents results for borrowers who answered the two questions needed to compute our measure of ``present bias'' discussed in the next paragraph, while column (9) present results restricted to participants who disclosed their sex.
-As seen from the table, our TUT estimates are quite stable across sub-samples defined by survey response.
-In each case they are positive and of the same magnitude as the corresponding full-sample estimate, although statistical significance varies depending on the size of the corresponding sub-sample. 
-For these reasons, we are comfortable relying on data for survey respondents in the empirical exercises that follow.
-In exercises that rely on a single survey question, we use data for every borrower who answered that question.
-In the random forest exercises described below, we use data for every borrower who answered at least one survey question.
-
-%\newpage
-\subsection{More descriptives}
-
-%The second thing to note is that those that are not closed at the end of our sample period have already incurred substantial financial cost, even though they have not defaulted yet.
-
-%Of those who renew, 83\% lose the pawn.
-Figure \ref{fc_hist}(a) suggest that financial cost is significant, even for those that do recover their pawn.
-Panel (b) normalizes the cost by loan size.
-It shows that as a percentage of their pawn, most of the cost comes from clients that do not recover their pawn.
-For them the cost is between 140\% and 250\% of the loan value.
-%{The difference between panel (a) and (b) arises since clients who lose their pawn tend to be those that pledge cheaper pieces.}
-
-\begin{figure}[!h]
-\caption{Financial cost.}
-  \label{fc_hist}
-    \begin{center}
-    \begin{subfigure}{.42\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_fc.pdf}
-        \caption{}
-    \end{subfigure}
-     \begin{subfigure}{0.42\textwidth}
-       \centering
-      \includegraphics[width=\textwidth]{Figuras/hist_apr.pdf}
-      \caption{}
-    \end{subfigure}
-    \end{center}
-
- \scriptsize{Panel (a) plots a histogram of this financial cost in pesos for all loans in the experiment, stratified by whether we observed that they ended in default or recovery of the pawn.
-Panel (b) shows the analogous histogram for the APR.
-%defaulted (44\%), recovered their pawn (43\%), or whether they are censored in our data (13\%). 
-We see that borrowers who default incur higher costs; part of this is mechanical as losing their collateral is part of the cost.
-Most of the APR costs indeed come from clients who do not recover their pawn.}
-
-      %\footnotesize{ } \textit{Do file: }  \texttt{hist\_fc.do}
-\end{figure}
-
-\begin{figure}[!h]
-    \caption{Behavior of borrowers who lost their pawn}
-    \label{proxy_naive}
-    \begin{center}
-    \begin{subfigure}{0.35\textwidth}
-        \caption{Elapsed days to first payment}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_firstdays_default.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.35\textwidth}
-        \caption{Elapsed days to last payment}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_days_default.pdf}
-    \end{subfigure}
-        \begin{subfigure}{0.35\textwidth}
-        \caption{Payments as \% of loan}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_percpay_default.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.35\textwidth}
-        \caption{Number of payments}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/hist_numpay_default.pdf}
-    \end{subfigure}
-    \end{center}
-        \scriptsize 
-        This figure provides more details on the behavior of clients who were assigned to the control group and did not recover their pawn.
-Panel (a) shows a histogram of days elapsed from the pawn to the first payment, while panel (b) displays a histogram of days elapsed until the last payment.
-Some borrowers make payments after day 105, the end of the grace period: if they pay all interest owed, they can ``restart'' the loan.
-This amounts to starting a new loan with the same conditions and same pawn.
-Panel (c) shows a histogram of the fraction of the loan paid, while panel (d) presents a barplot of the number of times that borrowers went to the branch to make payments.
-      %\textit{Do file: }  \texttt{hist\_den\_default.do}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-\section{ Internal Validity}
-
-If potential borrowers disliked being forced into a commitment contract, we would expect a lower number of pawns on branch days where only the commitment contract is available compared to control days.
-Table \ref{attrition_table} shows that this is not the case.
-There is no difference at all between the Control and Forced Commitment arm in terms of the number of pawns per branch-day.
-Although we cannot reject equality across the three arms (p-value=0.21), the Choice arm appears to have a somewhat larger number of borrowers than the Control and Forced arms.\footnote{p-value=0.23 and 0.12 respectively.} This seems to be due to sampling variability.
-Differences across arms are smaller when for medians, or when we compare the number of borrowers pawning (some borrowers pawn more than one piece).
-Figure \ref{boxplot_attrition} shows that distribution of loans per day is comparable across arms.
-The only noticeable difference is that the choice arm has a few more positive outliers.\footnote{If we winzorize at the 90th percentile, the mean number of branch-day pawns becomes identical across arms.}
-
-\begin{table}
-\caption{Limited and balanced attrition}
-\label{attrition_table}
-\begin{center}
-\scriptsize{\input{./Tables/Attrition.tex}}
-\end{center}
-\scriptsize{Each row in this table 
- corresponds to a regression.
-The dependent variables are: the number of pawns-loans originated per day per branch, the number of borrowers per day-branch, a variable indicating whether a person who answered the baseline survey (before knowing contract terms) ended up pawning, and an indicator of whether the person that obtained the loan answered the baseline survey.
-Each dependent variable is regressed in a multivariate OLS regression against the experimental arms indicators (control, forced commitment, choice).
-The table reports the coefficients on each of these indicators, as well as the p-value of an F-test of the null hypothesis of equality of the three coefficients.
-Figure \ref{boxplot_attrition}, in the appendix shows a box-plot of the first two variables, showing the distribution across arms is balanced.}
-%\textit{Do file: } \texttt{ss\_att.do}
-\end{table}
-
-The bottom panel of Table \ref{attrition_table} shows balance in a more focused way, given that the surveys were conducted prior to the revelation of treatment status.
-We find that in no arm did more than three percent of individuals who responded to the survey go on to refuse loans.
-That is, the overwhelming marjority of potential borrowers did not leave the branch after learning which contract was on offer.
-Moreover, the extremely small fraction that did leave is balanced across arms.
-Therefore it appears that the treatments have not induced any endogenous shifts in the composition of borrowers.
-
-A less critical form of attrition is differential refusal to answer the survey questions.
-The survey was conducted before treatment status was revealed, and we observe loan outcomes regardless of whether the survey was conducted.
-Our core experimental estimates do not use the survey data as covariates, but the analysis in Section \ref{Paternalism} is restricted to the subset of borrowers who answered at least some survey questions.
-The bottom row of Table \ref{attrition_table} shows that the survey response rate is broadly similar across arms (about 78 percent).
-
-\begin{figure}[H]
-     \caption{Box-plot across arms}
-    \label{boxplot_attrition}
-    \begin{center}
-    \begin{subfigure}{0.35\textwidth}
-    \caption{Number of pawns}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/box_plot_num_pawns.pdf}
-    \end{subfigure}
-        \begin{subfigure}{0.35\textwidth}
-    \caption{Number of borrowers}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/box_plot_num_pawns.pdf}
-    \end{subfigure}
-    \end{center}
-    \scriptsize
-        This figure presents box-plot for the number of pawns and borrowers per branch-day across different arms.
-The solid black line represent the median, while the gray line represent the mean.
-The blue dots represent an implicit CDF.
-\end{figure}
-
-% \begin{figure}[H]
-%      \caption{Number of pawns and borrowers before and after the experiment}
-%     \label{line_pawns_before_after}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/after_before_bal.pdf}
-%     \scriptsize
-%         This figure shows the number of pawns and borrowers before, during, and after the experiment for the different branches.
-% \end{figure}
-
-% \begin{figure}[H]
-%      \caption{No discontinuity in the number of pawns before and after experiment}
-%     \label{rd_pawns}
-%        \begin{center}
-%     \begin{subfigure}{0.45\textwidth}
-%     \caption{Number of pawns - before}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/rd_before_pawns.pdf}
-%     \end{subfigure}
-%         \begin{subfigure}{0.45\textwidth}
-%     \caption{Number of pawns - after}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/rd_after_pawns.pdf}
-%     \end{subfigure}
-%      \begin{subfigure}{0.42\textwidth}
-%     \caption{Number of borrowers - before}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/rd_before_borr.pdf}
-%     \end{subfigure}
-%         \begin{subfigure}{0.45\textwidth}
-%     \caption{Number of borrowers - after}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/rd_after_borr.pdf}
-%     \end{subfigure}
-%     \end{center}
-%     \scriptsize
-%         This figure shows the number of pawns and borrowers before, during, and after the experiment for the different branches.
-% \end{figure}
-
-\vspace{-1em}
-
-\begin{table}[H]
-\caption{Balance conditional on survey response and question-by-question response rates} %by treatment arm}
-\label{SS_cond_survey}
-\begin{center}
-\scriptsize{\input{./Tables/SS_cond_survey.tex}}
-\end{center}
-\scriptsize
-
-Panel A of this table presents the same information as Panel A of Table \ref{SS}, restricted to the subsample of borrowers who answered at least one survey question.
-Conditional on survey response, loan amount and weekday are balanced across arms.
-Panel B presents response rates to each survey question across arms, along with p-values for the F-test of no difference in response rates across arms, using data for borrowers who pawned on the same day as their survey response.
-%\textit{Do file: } \texttt{ss\_att.do}
-\end{table}
-
-\begin{landscape}
-\begin{table}[H]
-\caption{Survey Non-response: TUT estimates for respondents to each survey question.}
-\label{TUT_cond_survey}
-\begin{center}
-\scriptsize{\input{./Tables/tut_cond_survey.tex}}
-\end{center}
-\scriptsize
-
-Some borrowers did not respond to our survey; others only completed part of the survey.
-This table computes the TUT effect for a number of sub-groups by survey response, and compares them against the overall TUT effect.
-The top panel uses financial cost as the outcome variable, while the bottom panel uses APR.
-Each group is defined by the borrowers who responded to a particular \emph{subset} of the survey questions. 
-For example, column (4) computes TUT effects for the subgroup of borrowers who responded to the two questions needed to compute our measure of present bias, while column (8) computes the TUT for the subgroup of borrowers who provided their age.
-The bottom row of the table counts the number of borrowers in each category.
-TUT estimates are quite stable across sub-groups and generally similar to the full-sample estimates.
-Because standard errors increase as sample size falls, some of the sub-group estimates are not statistically significant.
-%\textit{Do file: } \texttt{tut_cond_survey.do}
-\end{table}
-\end{landscape}
-
-\newpage
-
-\section{ Main treatment effects: Additional material}
-
-%\begin{landscape}
-%\subsection{Multiple loans}
-%
-%\begin{table}[H]
-%\caption{Multiple-loans robustness check}
-%\label{multiple_loans}
-%\begin{center}
-%\scriptsize{\input{./Tables/multiple_loans.tex}}
-%\end{center}
-% \scriptsize
-% An additional empirical issue generated by repeat pawning is the question of how to handle the treatment status of those who take multiple loans within the experiment.
-43\% of borrowers take more than one loan within the study period, and 19\% are assigned multiple treatment statuses on their different loans.
-The issue of sequential endogenous treatments has been extensively studied in the context of school lotteries, where the convention is to use the treatment status from the first exposure (ITT) \citep{cullen2006effect, abdulkadirouglu2011accountability}.\\
-% 
-% This table provides robustness for our main results for different ways to handling the multiplicity of loans.
-Columns 1-4 repeat the main analysis of financial cost and APR using the baseline approach from our main results,i.e.
-it only considers the first visit, while allowing multiple loans for the same-day.
-Columns 5-8 considers all loans including dummies for the order of pawns for an individual, essentially making the identification within-order.
-Columns 9-12 pursue the ITT strategy of always assigning the first treatment status to all subsequent pawns.
-The core treatment effects are robust to any of these ways of handling repeat pawning.
-% 
-%%\textit{Do file: } \texttt{multiple\_loans.do}
-%\end{table}
-%
-%
-%\end{landscape}
-
-\begin{figure}[H]
-    \caption{Determinants of choice}
-    \label{determinants_choose}
-    \begin{center}
-    \begin{subfigure}{0.6\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/determinants_choose_commitment.pdf}
-    \end{subfigure}
-    \end{center}
-      \scriptsize
-
-      The above figure shows the determinants in a bivariate and multivariate OLS regression of choosing commitment.
-Choice commitment is a binary variable equal to one, whenever subjects choose the forced commitment contract in the choice arm.
-%\textit{Do file: } \texttt{determinants_choice.do}       
-\end{figure}
-
-\begin{figure}[H]
-    \caption{Histogram of payments}
-    \label{hist_payments}
-    \begin{center}
-    \begin{subfigure}{0.31\textwidth}
-        \caption{Status-quo}
-        \centering
-    \includegraphics[width=\textwidth]{Figuras/hist_payments_sq.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.31\textwidth}
-        \caption{Forced commitment}
-        \centering
-    \includegraphics[width=\textwidth]{Figuras/hist_payments_fc.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.31\textwidth}
-        \caption{Choice commitment}
-        \centering
-    \includegraphics[width=\textwidth]{Figuras/hist_payments_cc.pdf}
-    \end{subfigure}    
-    \end{center}
-     \scriptsize
-     This figure shows the schedule of payments for each treatment arm.
-In other words it records the time after the loan origination when the borrower makes a payment toward recovery of the pawn.
-We can see that for both the Forced commitment and Choice commitment arm, payments are bunching at the 30 and 60 days, while most payments are done around the due date of the loan (90 days).
-
-      %\footnotesize{ \textit{Do file: }  \texttt{hist\_payments.do}}
-\end{figure}
-
-\subsection{Censoring} \label{App_censoring}
-
-\normalsize
-\linespread{1.05}
-%Really force it to normal size and linespread
-\normalsize
-\linespread{1.05}
-
-Some loans in our sample are ``censored'' in that they continue beyond our observation period.
-For these loans, we do not know whether the borrower ultimately defaulted or recovered her pawn.
-In this appendix, we show that our main results are robust to different ways of addressing censoring.
-
-Our main results, presented above, make no assumption on the default/recovery status of this loans.
-However, we compute the Financial Cost \& APR considering all the payments done so far.
-We now consider some alternative approaches.
-
-One way of considering the effect that this issue could have on our results is to make extreme assumptions about the outcome of these loans in the treatment and control so as to bound the possible influence of censoring.
-In Table \ref{bounding_censoring} we compare the Forced and Control arms, making the bracketing assumptions about repayment on censored loans.
-Panel A assumes all censored loans are repaid, and Panel D that all default.
-Because forced commitment causes borrowers to make payments earlier than they otherwise would have, In Panel A we make a conservative assumption.
-To see why, suppose for the sake of argument that commitment affects payment timing, but does not not default.
-In other words, suppose that treatment makes censoring \emph{less likely} but has no effect on uncensored outcomes. 
-If we were to treat all outstanding loans as defaults--the opposite of our convention--this would artificially inflate the rate of default among control loans relative to treatment loans.
-
-Panel B provides the lower bound for the treatment effect by assuming censored control loans are always repaid and treatment loans never are, and Panel C the upper bound by making the reverse assumption.
-Comfortingly, even with these extreme assumptions the significance on the main treatment effects never flips and treatment effects on financial cost and interests payments remain negative and significant in all scenarios.
-So there appears to be no scope for the censoring issue to overturn our main results.
-
-Finally, Panel E of this table conducts a lasso logit prediction model that uses all of the available information on loans that were completed to predict the outcome of loans that were not.
-This is a best guess of the outcome on censored loans.
-Using this prediction, we replicate the main experimental results and find that the treatment effect on financial cost increases from -204 (main results) to -264 (censored loans predicted), and the APR from -11\% to -17\%.
-Hence, while the censoring issue does have a substantial influence on the magnitude of our estimated treatment effects, these  checks confirm that a) the core results are robust to censoring, and b) the headline approach that we take to the issue is conservative and is likely understating the true magnitude of impacts.
-
-\begin{table}[H]
-\caption{Bounding censoring} 
-\label{bounding_censoring}
-\begin{center}
-\resizebox{1.0\textwidth}{!}{
-\scriptsize{\input{./Tables/censoring_imp_1.tex}}
-}
-\end{center}
-
-\end{table}
-\begin{table}[H]
-\begin{center}
-\resizebox{1.0\textwidth}{!}{
-\scriptsize{\input{./Tables/censoring_imp_2.tex}}
-}
-\end{center}
-
- \scriptsize {
- Given the censored loans, i.e.
-loans that have not finished by the end of the observation period, we estimate `a la Manski' bounds for these loans, meaning that we impute all loans to either \emph{default}$=1$ or \emph{recovery}$=0$ depending on the treatment arm.
-Different panels perform different imputations for the censored loans for all possible combinations for the imputation, and computes the ATE for the same outcomes of Table \ref{main_impact_table}.
-Panel A, for instance, assumes that all outstanding loans are fully payed.
-Panel B is the most conservative imputation since it assumes all outstanding loans in the control arm are payed, while all the outstanding loans in the forced commitment arm default.
-Panel C, on the other hand, is the most optimistic scenario opposite to that of Panel B.
-Panel D assumes all remaining loans default.
-The last panel makes the imputation to the censored loans according to the best prediction using a piecewise lasso logit model for default.
-In concrete, we build two logit models with lasso regularization, depending whether the loan duration is less than 220 days (two cycles) or more than 220 days.
-For prediction we use the former whenever the last recorded payment was done within 220 days, and the latter otherwise.
-Both models includes loan characteristics (loan size, branch), and payment behavior (loan duration so far, days to first payment, \% of first payment, \% of payments at 30, 60, 90, and 105 days, and \% of interest payed at 105 days), but the latter model also includes \% of payments at 150, 180, and 210 days.
-This predictive model achieves an accuracy rate of 92\% both in-sample and out-of-sample.
-
-\noindent Note that in all panels we maintain significant results for Financial Cost as dependent variable, while only in the most conservative scenario (Panel B) we lose significance for the APR outcome.
-}
-\end{table}
-
-\begin{figure}[H]
-        \caption{Interpolation on bounding censoring for Default}
-        \vspace{-1em}
-    \label{interpolation_censoring_imp}
-    \begin{center}
-   % \begin{subfigure}{0.49\textwidth}
-   % \caption{Significance area for APR}
-   %      \centering
-   %      \includegraphics[width=\textwidth]{Figuras/frontera_sig_apr.pdf}
-   %  \end{subfigure}     
-   %  \begin{subfigure}{0.49\textwidth}
-   % \caption{Significance area for Default }
-        \centering
-        \includegraphics[width=0.5\textwidth]{Figuras/frontera_sig_def_imp.pdf}
-    % \end{subfigure} 
-    \end{center}
-    \vspace{-1em}
-     \scriptsize  {The next figure aims to answer the following question: For how many loans in the control arm can we impute recovery, and for how many in the treatment arm can we impute default and still have significance?
-     This figure shows exactly the boundary separating significance when we vary the percentage of imputed censored loans with recovery and default respectively for control and treatment.
-Each corner in the square will correspond to one of the panels from the Table \ref{bounding_censoring}.
-For instance, the origin is the best-case scenario (Panel C) and the point (100,100) (Panel B) is the worst-case scenario.
-Thus we can think of this graph as an `interpolation' from the four extreme cases.
-The `x' indicates the proportions imputed by the lasso logit model, and the different lines correspond to setting different significance levels.
-We do not include the plot for APR nor financial cost, since for any imputation we still have significant results.}
-
-     %\textit{Do file: }  \texttt{interpolation_censoring_imp.do}
-\end{figure}
-
-\begin{figure}[H]
-        \caption{Survival graph}
-        \vspace{-2em}
-    \label{survival_graph}
-    \begin{center}
-   \begin{subfigure}{0.49\textwidth}
-   \caption{Ended contract}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/survival_graph_ended.pdf}
-    \end{subfigure} 
-   \begin{subfigure}{0.49\textwidth}
-   \caption{Recovery}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/survival_graph_unpledge.pdf}
-    \end{subfigure}     
-    \end{center}
-    \vspace{-1em}
-     \scriptsize  This Figure shows the CDF of loan completion either default or recovery in Panel (a), or loan recovery in Panel (b), by the number of days since first pawn.
-     %\textit{Do file: }  \texttt{survival\_graph.do}
-\end{figure}
-
-\begin{figure}[H]
-        \caption{\% of payment over time}
-        \vspace{-2em}
-    \label{porc_payment_over_time}
-    \begin{center}
-   \begin{subfigure}{0.49\textwidth}
-        \caption{Unconditional}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/cumulative_porc_pay_time.pdf}
-    \end{subfigure} 
-   \begin{subfigure}{0.49\textwidth}
-        \caption{Conditional on default}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/cumulative_porc_pay_time_default.pdf}
-    \end{subfigure}     
-    \end{center}
-     \scriptsize  This Figure shows the accumulated percentage of recovery in time by treatment arm. 
-     %\textit{Do file: }  \texttt{cumulative\_porc\_pay\_time.do}
-\end{figure}
-
-\subsection{Robustness accounting for other costs}
-
-\begin{table}[!h]
-\caption{Effects on more comprehensive cost measures}
-\label{table_robustness_fc}
-\begin{center}
-\scriptsize{\input{./Tables/fc_robustness.tex}}
-\end{center}
- \scriptsize{ This table augments the measure of financial cost presented in Table \ref{main_impact_table} with measures of transaction costs, subjective costs, and adjustments for liquidity costs.
-Panel A reports financial cost in pesos, while Panel B shows APR.
-Columns (1) and (6) replicate our previous results for comparability.
-Columns (2) and (7) of Table \ref{table_robustness_fc} use the subjective value of the pawn reported by the borrower rather than its appraised value.
-Columns (3) and (8) adjust for self-reported transport costs per visit plus an entire day's wage, both multiplied by the number of visits that each individual made.\footnote{For clients who did not complete the individual survey, we adjust using the mean self-reported transport cost among respondents of the respective branch.} Columns (4) and (9) adjust to consider the liquidity cost.
-Finally, columns (5) and (10) include all three changes together.
-The main takeaway from the table is that results are quite robust to including a much expanded measure of costs.
-Each regression includes branch and day-of-week FE.
-Standard errors are clustered at the branch-day level.}
-%\textit{Do file: } \texttt{fc\_robustness.do}
-\end{table}
-
-\section{ Alternative explanations}
-
-\subsection{Learning}
-\normalsize
-Table \ref{learning_table} presents information about borrowers' \emph{future} pawning behavior as a function of treatment assignment.
-Column (1) considers the 228 clients who returned only a second time to pawn again at a day/branch that was randomly assigned to the choice arm.
-Each of the two rows in this column presents a difference of mean commitment take-up rates, and associated standard error.
-The first row compares those who were \emph{initially} assigned to forced commitment against those where were assigned to control; the second row compares those who were initially assigned to the choice commitment arm to those who were assigned to the other two arms.
-In each case, there is no statistically discernible difference in the rates of commitment take-up.
-Granted, this is a selected sample because the decision to pawn again is potentially endogenous to the initial treatment allocation.
-For this reason, Column (2) considers the full sample of 4441 borrowers by re-defining the outcome variable to be an indicator for returning to pawn again at a branch/day when commitment was offered \emph{and} choosing commitment.
-This composite outcome variable is not subject to the sample selection problem (although it is directly driven by the decision to repeat borrow).
-The comparison in the two rows remains the same: forced commitment versus control in row one and choice commitment versus forced arms in row two.
-Again, there is no statistically discernible difference in commitment take-up rates in either row.
-While these exercises cannot completely exclude the possibility that learning plays a role, they provide no indication that the lack of voluntary compliance is simply a matter of inexperience with commitment.
-
-\vspace{.1in}
-\begin{table}[!h]
-        \caption{Effect of Prior Assignment on Subsequent Choice}
-    \label{learning_table}
-\begin{center}
-\scriptsize{\input{./Tables/learning_exp.tex}}
-\end{center}
- \scriptsize
-
-Column (1) reports results for the 228 borrowers who returned to pawn again at a day/branch that was randomly assigned to the choice arm, enabling us to observe whether they chose commitment or the status quo contract.
-Each row presents a difference in mean commitment take-up rates and associated standard errors.
-The first row (ATE) compares borrowers who were initially assigned to forced commitment against those were assigned to the control condition.
-The second row (ITT) compares borrowers who were initially assigned to the choice commitment condition to those who were not.
-Whereas column (1) conditions on the (endogenously) selected sample of borrowers who return to pawn again, column (2) considers the full sample by re-defining the ``outcome'' to be an indicator for whether a borrower pawned again on a day when choice was offered \emph{and} chose commitment.
-
-%This table explores learning by focusing on a subsample of borrowers in the experiment and observing their subsequent behavior.
-Column 1 conditions the sample on borrowers who (a) pawned during the experiment a subsequent time after being assigned to control, forced commitment or choice (the regressors), and (b) when pawning again they went to a branch day when (randomly) choice was available, thus enabling us to observe if they chose the commitment contract or the status quo.
-in this sample it estimates a linear probability model where the dependent variable is equal to one if the borrower chose the commitment contract in that subsequent `choice' occasion and zero otherwise.
-The regressors are indicators for the treatment arms in their first pawn in the experiment.
-Column 1 conditions the sample on the (endogenous) event of pawning again.
-Column 2 does not condition the sample, but instead defined the dependent variable as equal to one \hl{if the borrower pawned subsequently and choice was available that day and chose commitment, and zero otherwise.}
-
-\end{table}
-
-\subsection{Discount rates}
-
-\begin{figure}[H]
-        \caption{Financial benefit TUT effect for different discount rates}
-    \label{fc_discount_rates}
-    \begin{center}
-        \centering
-        \includegraphics[width=0.55\textwidth]{Figuras/discount_effect_tut.pdf}
-    \end{center}
-     \scriptsize This Figure re-estimates the treatment on the untreated (TUT) effect from Table \ref{tot_tut}, introducing a daily discount factor in the definition of financial benefit.
-The discount factor reflects time preference, i.e.\ the fact that payments made in the present are more costly for the borrower.
-At a given annual discount rate in percentage points (x-axis) the solid line gives the adjusted TUT and the shaded regions 90\% \& 95\% confidence bands.
-A discount factor of one corresponds to the estimate from Table \ref{tot_tut}.
-For higher discount rates, the adjusted financial cost will be higher, so the financial cost \emph{savings} will be lower.
-As seen from the figure, borrowers would need to face unrealistically large discount rates to reverse our headline result of a large, positive, and statistically significant TUT effect.
-     %It estimates the effect of the treatment arms  for different discount factors, where a discount factor of 1 corresponds exactly to the estimate of column 1 of Table \ref{main_impact_table}.
-Because the commitment contract induces earlier payments, this adjusted financial cost will be higher, and thus financial savings will be lower.
-This figure shows the range of estimated effects and their confidence intervals, where the discount rate used is ploted in the x-axis annualized.
-%\textit{Do file: }  \texttt{discounted\_noeffect.do}
-\end{figure}
-
-\begin{comment}
-
-\vspace{.2in}
-\begin{table}[H]
-\caption{FOSD by demographic groups \textcolor{red}{\hl{MAY NEED UPDATING}}}
-\label{stochastic_dominance}
-\begin{center}
-\scriptsize{\input{./Tables/dominance.tex}}
-\end{center}
- \footnotesize
-This table does two things.
-First, it tests whether the observed empirical distribution of financial cost is well approximated by a log normal.
-It does this using two tests, the Anderson-Darling and the Kolmogorov-Smirnoff tests.
-Second, it fits a log normal distribution by maximum likelihood to observed empirical distribution of financial cost, separately for the fee-forcing arm and the status-quo arm.
-Using the fitted log normal, it tests whether the fee-forcing financial cost distribution would be preferred by any expected utility agent using Proposition \ref{lognormal_fosd} below.
-The different rows of the table do this for different sub-populations.
-The first row of the table does it for every client in the fee forcing and status quo arms.
-The ``*'' show that we cannot reject at the 5\% level that both distribution are log normal for any of the two tests.
-The column entitled ``Dominance'' shows whether any client that dislikes higher cost would prefer the fee-forcing cost distribution over the status quo one, with $\succeq_{1}$ meaning he should (with $\succeq_{1}^*$ indicating the difference is statistically significant).
-It turns out to be the case that for the overwhelming majority of sub-populations, the conditions of preferring the fee-forcing distribution hold.
-%\textit{Do file: } \texttt{stoch\_dominance.do}
-\end{table}
-
-\newpage
-
-\vspace{.2in}
-\begin{prop}
-\label{lognormal_fosd}
-
-Let $F$ and $G$ be the cumulative distributions of two alternative log-normal prospects. The following are equivalent:
-
-\begin{enumerate}[(a)]
-    \item For every weakly decreasing utility function $u$: $E_{F}(u(FC))\leq E_G(u(FC))$
-    \item $E_F \log(FC)\geq E_G\log(FC)$ and $Var_F \log(FC)= Var_G\log(FC)$
-\end{enumerate}
-\end{prop}
-
-\begin{proof}
-See Theorem 4 in \cite{lognormal_dominance}.
-\end{proof}
-
-\vspace{.1in}
-\begin{prop}
-\label{eq_fosd}
-
-This is a standard result. 
-\\
-\vspace{.1in}
-The following are equivalent:
-\begin{enumerate}[(a)]
-    \item For every weakly decreasing utility function $u$: $E_{sq}(u(FC))\leq E_{fee}(u(FC))$
-    \item $F_{sq}(FC)\leq F_{fee}(FC)$ 
-\end{enumerate}
-
-\end{prop}
-\begin{proof} \;
-
-[$(a)\Longrightarrow (b)$] Suppose  $(b)$ does not hold. So there exists $FC^*$ such that $F_{sq}(FC^*)>F_{fee}(FC^*)$, Define $u:=\mathds{1}_{FC\leq FC^*}$. Then
-\[E_{sq}(u(FC)) = \int u(FC)dF_{sq} = F_{sq}(FC^*)>F_{fee}(FC^*)= \int u(FC)dF_{fee} =E_{fee}(u(FC))\]
-which contradicts $(a)$.\\
-
-[$(a)\Longleftarrow (b)$] On the other hand for $u$ weakly decreasing,
-
-\[\int u(y(FC))dF_{sq}(y(FC)) = \int u(y(FC))dF_{fee}(FC) \leq \int u(FC)dF_{fee}(FC)\]
-with $y(FC) = F_{sq}^{-1}F_{fee}(FC)$.
-
-\end{proof}
-
-Note the proof was done in the case of absolutely continuous and strictly increasing distribution functions $F_{sq}$ and $F_{fee}$.
-
-\end{comment}
-
-\normalsize
-\linespread{1.05}
-%Really force it to normal size and linespread
-\normalsize
-\linespread{1.05}
-
-\begin{comment}
-\section{ Causal Forest and individual predictions of `Mistakes'}
-
-    \begin{figure}[H]
-        \caption{Example of a Causal Tree \textcolor{red}{WHAT IS THE DIFFERENCE OF THIS AND FIGURE OA-17?}}
-        \label{causal_tree_example}
-        \begin{center}
-\includegraphics[width=\textwidth]{Figuras/ct_eff.pdf}
-\end{center}
-     \scriptsize This Figure shows an example of the splits for the leaves that emerge in our data for the Athey et al (2019) Causal Forest estimation.  
-        \end{figure}
-\end{comment}
-
-\subsection{Sure Confidence} \label{App_sureconfidence}
-
-\begin{figure}[H]
-    \caption{Determinants sure confidence}
-    \label{determinants_sure}
-    \begin{center}
-    \begin{subfigure}{0.6\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/determinants_confidence_100.pdf}
-    \end{subfigure}
-    \end{center}
-      \scriptsize
-
-      The above figure shows the determinants in a bivariate and multivariate OLS regression of sure confidence among the non-choosers.
-Sure confidence is a binary variable defined to be one when people report a 100\% probability of recovery.
-%\textit{Do file: } \texttt{determinants_sure_confidence.do}       
-\end{figure}
-
-%\section{ Heterogeneity and Bounds}
-\section{Bounds, FOSD and Rank Invariance} \label{bounds_FOSD}
-
-%\subsection{Testing for heterogeneity}
-%\label{append:chernozhukov}
-%If the treatment effects $Y_{i1} - Y_{i0}$ are constant across $i$, then we must have
-%\[
-%\text{ATE}(X_i) \equiv \mathbbm{E}[Y_{i1} - Y_{i0} |X_i] = \mathbbm{E}[Y_{i1} - Y_{i0}] \equiv \text{ATE}
-%\]
-%for any covariates $X_i$ that vary across $i$.
-If, on the other hand, $\text{ATE}(X_i)$ can be predicted using some scalar function $\tau(\cdot)$ of $X_i$, then the average treatment effect function is not constant so there must be treatment effect heterogeneity.
-%
-%We operationalize this idea using a two-step approach proposed by \cite{chernozhukov2018generic}.
-We begin by randomly dividing the participants in the forced arms of the experiment ($Z_i \neq 2$) into two groups: a training set and a test set.
-%These sets are constructed to ensure that all observations from a given branch-day cluster are allocated to the same set.
-%This avoids inferential problems that could arise from correlated unobservables within clusters.
-%In the first step, we apply the generalized random forest approach of \cite{atheygrf} to the training set to estimate two proxy predictors: $\psi(\cdot|\text{Training})$ approximates the untreated potential outcome function, $\mathbbm{E}[Y_{i0}|X_i] = \mathbbm{E}[Y_i|Z_i=0,X_i]$, while  $\tau(\cdot|\text{Training})$, approximates the ATE function
-%\[
-%\text{ATE}(X_i) = \mathbbm{E}[Y_i|Z_i=1,X_i] - \mathbbm{E}[Y_i|Z_i=0, X_i].
-%\]
-%The proxy predictors need not be unbiased or even consistent estimators of the functions they aim to approximate: the goal of this exercise is merely to find a scalar function of $X_i$ that \emph{accurately predicts} $\text{ATE}(X_i)$.
-%In the second step we fit a linear regression model to data from the training set using regressors constructed from the proxy functions $\psi(\cdot|\text{Training})$ and $\tau(\cdot|\text{Training})$ constructed in the first step.
-In particular, we estimate
-%\begin{equation}
-%Y_i = \alpha_0 + \alpha_1 \psi_i + \beta_1 (Z_i - \mathbbm{E}[Z_i]) + \beta_2 (Z_i - \mathbbm{E}[Z_i])(\tau_i - \mathbbm{E}[\tau_i]) + \epsilon_i
-%\label{eq:chernreg}
-%\end{equation}
-%where $\psi_i \equiv \psi(X_i|\text{Training})$ and $\tau_i \equiv \tau(X_i|\text{Training})$.\footnote{This is a slightly simpler regression than the one proposed in equation (3.1) of \cite{chernozhukov2018generic}, which involves propensity score weights.
-Because the random assignment of $Z$ in our experiment does \emph{not} condition on $X$, the propensity score weights in our case are constant over $X$ and hence drop out.} As shown by \cite{chernozhukov2018generic}, the coefficients $\beta_1$ and $\beta_2$ from \eqref{eq:chernreg} identify the \emph{best linear predictor} of the conditional ATE based on $\tau(\cdot|\text{Training})$, namely
-%\[
-%\beta_1 = \mathbbm{E}[\text{ATE}(X_i)] = \text{ATE}, \quad
-%\beta_2 = \frac{\text{Cov}[\text{ATE}(X_i), \tau_i]}{\text{Var}(\tau_i)}.
-%\]
-%If treatment effects are homogeneous we must have $\beta_2 = 0$. Rejecting this hypothesis establishes that $\tau_i$ predicts $\text{ATE}(X_i)$ and hence that $\Delta_i$ varies. 
-%Since $\tau_i$ and $\psi_i$ do not depend on the test set, inference for the regression in \eqref{eq:chernreg} is straightforward conditional on the Training/Test split.  
-%Our estimate for $\beta_2$ is 2.56 with a one-sided heteroskedasticity-robust (HC3) standard error of 0.43.
-%Thus we easily reject the null hypothesis of homogeneous treatment effects.
-
-%\todo[inline]{Discuss the results here.}
-
-%\todo[inline]{Issac: re-run this exercise with removing the propensity score weights $p(Z)$. Presumably it shouldn't change anything, but it's simpler to explain what we do and probably less noisy}
-
-%\begin{table}[H]
-%\begin{center}
-%\scriptsize{\input{./Tables/test_calibration_2.tex}}
-%\end{center}
-%\end{table}
-
-%\todo[inline]{Some Questions for Issac: (1) How are we carrying out the sample splitting?
-If we cluster standard errors at the branch-day level, we should take this into account when we split.
-(2) How are you carrying out inference for $\beta_2$?
-Chernozhukov et al discuss two approaches: ``conditional'' and ``variational.'' The former is simpler as it conditions on the training/test split.
-The latter is a bit more involved, since one accounts for uncertainty arising from different splits.
-(3) What are the details of the random forest procedure employed here?
-(Tuning parameters choice, etc.) We should put them into the appendix.}
-
-%\newpage
-
-\begin{figure}[!h]
-    \caption{Fan \& Park bounds for benefit in APR\%}
-    \label{fan_park_bounds}
-    \begin{center}
-    \begin{subfigure}{0.55\textwidth}
-        \caption{APR}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/fan_park_bounds_apr.pdf}
-    \end{subfigure}
-    \end{center}
-        \scriptsize
-    This figure depicts the \cite{fan2010sharp} bounds on the distribution $F_\Delta$ of individual treatment effects $\Delta \equiv (Y_1 - Y_0)$, described in Section \ref{sec:bounds}, for the APR outcome.
-    The dark red curve and light red shaded region give the estimated upper bound function $\overline{F}$ for $F_\Delta$ and associated (pointwise) 95\% confidence interval. 
-    The dark blue curve and light blue shaded region give the estimated lower bound function $\underline{F}$ for $F_\Delta$ and associated (pointwise) 95\% confidence interval.
-    Confidence intervals are computed using the asymptotic distribution for the bounds. See \cite{fan2010sharp} for details.
-    The bounds are pointwise sharp: at any specified value of $\delta$ the bounds $\underline{F}(\delta) \leq F_\Delta(\delta) \leq \overline{F}(\delta)$ cannot be improved without imposing additional assumptions.
-    Evaluating the bounds at $\delta = 0$, we see that between 23\% and 97\% of borrowers have a positive individual treatment effect.
-    This is greater than the share of borrowers who chose commitment: 11\%.
-%\textit{Do file: } \texttt{fan\_park\_bnds.do}       
-\end{figure}
-
-\begin{figure}[!h]
-        \caption{Empirical CDF: Forced commitment vs Control FOSF}
-    \label{ecdf_fc}
-    \begin{center}
-        \begin{subfigure}{0.49\textwidth}
-         \caption{APR benefit}
-         \centering
-         \includegraphics[width=\textwidth]{Figuras/cdf_apr.pdf}
-     \end{subfigure} 
-   \begin{subfigure}{0.49\textwidth}
-        \caption{Financial benefit}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/cdf_fc_admin.pdf}
-    \end{subfigure} 
-    \end{center}
-    \scriptsize This figure plots the empirical CDF of experimental outcomes separately for the control (status quo) in dashes, and forced commitment contracts (solid).
-In panel (a), the outcome is APR benefit; in panel (b) the outcome is Financial benefit.
-    The empirical CDF under forced commitment first-order stochastically dominates the empirical CDF under the status quo.
-This can be seen by examining the dotted line, which shows the difference $(\text{Control} - \text{Commitment})$.
-    %The dotted line at the bottom of panels (a) and (b)   the empirical cumulative distribution function APR and financial cost of financial cost.
-It does this separately for the fee-forcing contract and for the status-quo contract.
-The dotted line at the bottom is the difference of the control CDF minus the forced CDF arm.
-It shows that the CDF of the status quo contract is always below that of the fee-forcing (and this difference is significant for the points indicated by the blue line).
-    % \texttt{fosd_ecdf.do}}
-\end{figure}
-
-\begin{figure}
-        \caption{Distribution of treatment effects under rank invariance.}
-    \label{te_rankinvariance}
-
-    \begin{center}
-       \begin{subfigure}{0.49\textwidth}
-        \caption{APR benefit}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/te_rankinvariance_apr.pdf}
-    \end{subfigure} 
-   \begin{subfigure}{0.49\textwidth}
-        \caption{Financial benefit}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/te_rankinvariance_fc_admin.pdf}
-    \end{subfigure} 
-    \end{center}
-    \scriptsize This figure shows the CDF of individual treatment effects under the assumption of rank invariance, computed from 
-    \[F_\Delta(\delta) = \int_0^1 \mathbbm{1}\{ F_1^{-1}(u) - F_0^{-1}(u)\leq \delta\}\,\mathrm{d}u\]
-where $F_1^{-1}$ and $F_0^{-1}$ are the quantile functions of $Y_1$ and $Y_0$.
-    %The dotted line at the bottom of panels (a) and (b)   the empirical cumulative distribution function APR and financial cost of financial cost.
-It does this separately for the fee-forcing contract and for the status-quo contract.
-The dotted line at the bottom is the difference of the control CDF minus the forced CDF arm.
-It shows that the CDF of the status quo contract is always below that of the fee-forcing (and this difference is significant for the points indicated by the blue line).
-    % \texttt{te_rankinvariance.do}}
-\end{figure}
-
-\newpage
+\linespread{1.25}
+\begin{document}
+
+\title{The controlled choice design and private paternalism in pawnshop borrowing - STATA documentation}
+\author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira \and Francis J.\ DiTraglia   \thanks{Seira:  MSU, \url{enrique.seira@gmail.com} (corresponding author); McIntosh:  University of California San Diego, \url{ctmcintosh@ucsd.edu}; Meza: Harvard University, \url{isaacmezalopez@g.harvard.edu}; Sadka: ITAM, \url{jsadka@itam.mx}; DiTraglia: Oxford, \url{francis.ditraglia@economics.ox.ac.uk}} }
+\date{}
+\maketitle
 
@@
 \label{append:exclusion}
-
-\normalsize
-\linespread{1.05}
-%Really force it to normal size and linespread
-\normalsize
-\linespread{1.05}
 
@@
 
-\section{ Causal Random Forest, HTE, and `mistakes'}
-
-\begin{comment}
-
-    \begin{figure}[H]
-        \caption{Conditional Average Treatment Effect from Random Forest}
-        \label{CATE}
-        \begin{center}
-\includegraphics[width=0.6\textwidth]{Figuras/he_dist_apr_pro_2.pdf}
-\end{center}
-     \scriptsize This Figure plots the densities of the CATE emerging from the Athey et al. (2019) random forest, along with the upper and lower confidence bounds.  
-        \end{figure}
-\end{comment}
-
-% \subsection{Example of a Causal Tree}
-
-% \vspace{.3in}
-% \begin{figure}[H]
-%         \caption{Example Causal Tree}
-%     \label{causal_tree1}
-%     \begin{center}
-%         \centering
-%         \includegraphics[width=\textwidth]{Figuras/crf_apr.pdf}
-%     \end{center}
-%     \footnotesize 
-%     This figure shows an example of one of the regression trees used to compute the causal forest estimates described in Section \ref{sec:RF}.
-Each tree is constructed from a sequence of recursive binary partitions of the covariate space, with a splitting rule that is targeted to the causal quantity of interest, following the methodology of \cite{atheygrf}.
-%     %This is one(it is chosen such that it minimizes the pruned cost, that is it is the tree with the smallest root-node impurity) of the honest causal trees in the random forest we use for the estimation of the heterogeneous treatment effect of the fee-forcing contract.
-It is meant only as an example of how these trees look like.
-The forest was such that there are as many estimated treatment effects as there are clients.
-%      %\footnotesize{ \textit{RScript: }  \texttt{grf.R}
-% \end{figure}
-
-\subsection{Conditional ATE estimates}
-
-\begin{figure}[H]
-    \begin{center}
-  \caption{Cumulative Distribution Function of Conditional ATE Estimates}
-  \includegraphics[width=0.6\textwidth]{Figuras/cdf_CATE.pdf} 
-    \label{fig:CATEsurvival}
-    \end{center}
-
-    \scriptsize This figure shows the share of borrowers who benefit from forced commitment, where ``benefit'' is defined as having an estimated conditional average treatment effect (ATE) above a specified threshold value.
-Results are based on the causal forest model from Section \ref{sec:RF}.
-The solid line equals $1 - F_\text{ATE}(\delta)$ where $F_\text{ATE}(\delta)$ denotes the CDF corresponding to the density of conditional ATE estimates from Figure \ref{heterogeneous_effects}.
-The blue shaded regions are associated 95\% confidence intervals.
-We estimate that at least 90\% of borrowers have a positive conditional ATE.
-%\textit{Do file: }  \texttt{cdf_CATE.do}
-\end{figure}
-
-\begin{figure}[H]
-    \caption{Conditional ATEs from ``wide'' and ``narrow'' covariate sets}
-    \label{wide_narrow_forests}
-    \vspace{-2em}
-    \begin{center}
-    \begin{subfigure}{0.65\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/scatter_hist_wide_narrow.pdf}
-    \end{subfigure}
-    \end{center}
-    \vspace{-1em}
-      \scriptsize  This figure plots the relationship between the causal forest conditional ATE estimates from Section \ref{sec:RF} that use the ``wide'' set of covariates (all intake survey responses) and those based on a restricted ``narrow'' set of covariates (age, gender, HS education, and previous borrowing).
-The scatterplot graphs one estimate versus the other, with the ``wide'' covariate set on the horizontal axis and the ``narrow'' set on the vertical axis.
-The density plots on each axis show the estimated marginal distribution of conditional ATEs under each covariate set.
-The density for the ``wide'' covariate set is considerably more dispersed, as the causal forest based on this set of covariates captures considerably more treatment effect heterogeneity.
-
-%\textit{Do file: } \texttt{wide_narrow_forests.do}       
-\end{figure}
-
-\subsection{Targeting rule comparisons}
-
-Figure \ref{targeting_rules} compares the in-sample performance of targeting rules against universal forced commitment.
-The plot presents the estimated proportion of borrowers who benefit from a particular treatment assignment rule, along with associated 95\% confidence bands, where ``benefit'' is defined as having a CATE above a particular threshold.
-As above, we take the conditional average effects from the ``wide'' causal forest as ground truth for the purposes of this exercise.
-Because this is an in-sample exercise, the logistic and random forest classification rules have an unfair advantage: there is no adjustment for overfitting.
-In spite of this, their performance is unimpressive relative to of universal forced commitment.
-The fraction of the whole sample incorrectly targeted when moving from universal forced commitment to targeting based on the narrow RF falls only from 9.78\% to 9.59\%.
-Logit targeting makes things marginally worse.
-
-\begin{figure}
-    \caption{Targeting rules}
-    \label{targeting_rules}
-    \begin{center}
-    \begin{subfigure}{0.6\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/wide_narrow_rule.pdf}
-    \end{subfigure}
-    \end{center}
-    %\vspace{-2em}
-      %\scriptsize   This figure plots the percentage of borrowers who would benefit from a program in which commitment is targeted using the ``narrow'' covariate set (age, gender, HS education, and previous borrowing).
-In this exercise ``benefit'' is defined to mean having a conditional ATE above a particular threshold, taking the estimated conditional effects from the ``wide'' causal forest as ground truth.
-The plot compares the estimated percentage of borrowers who benefit, along with associated 95\% confidence bands, for three targeting rules: universal forced commitment in blue, targeting based on a random forest classification model in green, and targeting based on the logit model in red.
-For each of the classification models, the outcome variable is an indicator for whether the CATE estimate from the ``wide'' random forest model is positive.
-Each of the classification models produces an estimated probability of a positive CATE.
-For each, the assignment rule ranks borrowers by this estimated probability, and assigns the highest 90\% to forced commitment, to match the overall percentage of borrowers with positive estimated CATEs from the ``wide'' random forest model.
-Because this is an in-sample exercise, it overstates the actual performance of logit and RF-based targeting.
-
-      %, the top \hl{XXX\%} of Both targeted Both of the targeted assignment rules are assigned by a the ``narrow'' causal forest in green, and targeting based on the logit model in red.
-The causal forest rule assigns a borrower to commitment if her estimated conditional ATE from the ``narrow'' covariate set is positive; the logistic regression rule assigns her to commitment if the estimated probability that her conditional effect is positive is greater than 0.5.
-      %\todo[inline]{@Issac: Have I described this correctly? Also, is this an out-of-sample exercise. In other words, are we using a holdout sample to make these comparisons?}
-
-      %This figure plots the (reversed) cumulative densities of the estimated benefits from the casual forest for three different rules.
-The blue line plots the HTEs from the `wide' random forest for the Forcing arm, which we take as the ground truth for actual impacts.
-The green line plots HTEs if we first target individuals using the variables in the `narrow' forest, and only assign individuals to commitment if they are on a leaf whose predicted forcing benefit is positive.
-The red line uses a logit regression to predict which individuals benefit from treatment, and assigns all individuals to the arm predicted to be best for them.
-
-\end{figure}
-
-%We use \cite{atheygrf} \texttt{causal\_forest} of the \texttt{grf} library in $R$. The parameters used were:
-%\scriptsize{\textit{causal\_forest(
-%  X, 
-%  Y, 
-%  W, 
-%  Y.hat = NULL,
-%    W.hat = NULL,
-%    clusters = NULL,
-%    num.trees = 5000,
-%    sample.weights = NULL,
-%    equalize.cluster.weights = FALSE,
-%    sample.fraction = 0.5,
-%    mtry = min(ceiling(sqrt(ncol(X)) + 20), ncol(X)),
-%    min.node.size = 5,
-%    honesty = TRUE,
-%    honesty.fraction = 0.5,
-%    honesty.prune.leaves = TRUE,
-%    alpha = 0.05,
-%    imbalance.penalty = 0,
-%    stabilize.splits = TRUE,
-%    ci.group.size = 2,
-%    tune.parameters = c("alpha", "imbalance.penalty"),
-%    tune.num.trees = 500,
-%    tune.num.reps = 200,
-%    tune.num.draws = 2000,
-%    compute.oob.predictions = TRUE,
-%    num.threads = NULL,
-%    seed = 1)}}
-
-\begin{comment}
-
-\begin{figure}[H]
-        \caption{Single causal tree for the Forced-commitment contract heterogeneous treatment effects}
-    \label{causal_tree2}
-    \begin{center}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/ct_pro_2_apr.pdf}
-    \end{center}
-    \footnotesize
-
-     %\footnotesize{ \textit{RScript: }  \texttt{grf.R}
-\end{figure}
-\end{comment}
-
-%\begin{figure}[H]
-%    \caption{Choice of contracts and treatment effects}
-%    \label{choose_wrong}
-%    \begin{center}
-%        \begin{subfigure}{0.45\textwidth}
-%        \caption{Mistakes in choice arm}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/line_cw_apr_te_cf.pdf}
-
-%   \end{subfigure}
-%        \begin{subfigure}{0.45\textwidth}
-%        \caption{Financial value of mistake}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/money_cw_apr_te_cf.pdf}
-
-%    \bigskip
-
-%    \end{subfigure}
-%        \begin{subfigure}{0.45\textwidth}
-%        \caption{\% better when forced to forced commitment}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/line_better_forceall_apr_te_cf.pdf}
-%        
-%    \end{subfigure}
-    %     \begin{subfigure}{0.45\textwidth}
-    %     \caption{\footnotesize{Effect of CATE benefit vs predicted take-up}}
-    %     \centering
-    %     \includegraphics[width=\textwidth]{Figuras/benefit_choice.pdf}% takeuppr_def.pdf 
-    % \end{subfigure}
-
-%    \end{center}
-%        \scriptsize
-%        In Panel (a) we estimate what the treatment effect of the commitment contract \textit{would have been} for all subjects in the choice arm if they had been forced into the fee-commitment contract.
-To do this we proceed in two steps.
-First, we estimate treatment effects in the forcing arm by comparing the Forced Commitment arm against the status quo arm.
-We let these effects be heterogeneous as a function of our $x$'s using \cite{atheygrf}'s methodology of causal forests.
-Second, we extrapolate these treatment effects based on the choice arm using the same $x$'s.
-Once we have personalized counterfactual treatment effects in the choice arm we calculate what fraction of subjects in the choice arm incurred in financial costs that are  $> z$\% than if they had chosen the opposite contract of what they actually chose, were $z$\% is defined as a fraction of the loan.
-$z$\% is a level of tolerance we can vary and we plot it in the X-axis.
-The left Y-axis measures the fraction of subjects that would have been better by a margin of $z$\% if they changed their choice, and the right Y-axis measures the amount of money ``left on the table''.
-We use bootstrap to tighten the confidence intervals (CIs).
-\cite{atheygrf}'s heterogeneous treatment effect using GRF is asymptotically normal.
-We compute the HTE ($\mu$) together with standard errors ($\sigma$) .
-For every pledge, we draw a random effect from a normal distribution with parameters ($\mu$,$\sigma^2$), and compute via bootstrap the percentage that choose wrong, along normal-approximation CIs (results are robust if we use instead percentile CIs or bias-corrected CIs) .
-This allows us to estimate a distribution for the upper and lower bound CIs, which we then use to obtain a 95\% CI.
-Panel (b) is analogous to Panel (a) except that it does the exercise separately for clients we classified as overconfident ($OC_i:=\mathbbm{1}(P^s_i-\widehat{P_i(X_i)}>0))$ and those we classified as not overconfident.
-Panel (c) simulates what percentage would be better by at least $z$ if we forced everybody of those in the Commitment Choice arm into the fee-commitment contract.
-        % Panel (d) asks whether it is the case that people with larger causal benefits from the Forced Commitment contract would be more likely to select that contract.
-To do this we proceed in two steps as well.
-First we estimate a flexible model of take-up of the fee commitment contract \textit{in the choice arm} using random forests, and from this model obtain a probability $P(x_i)$ of choosing the Forced Commitment contract for a client with characteristics $x_i$.
-We extrapolate this model to clients in the Forced Commitment arm to estimate what would they have chosen if we had given them choice.
-        % Figure (d) plots $\widehat{P(x_i)}$ in the X-axis using a binscatter that splits the X-axis in 100 percentile bins.
-The Y-axis plots the heterogeneous treatment effects of the fee forcing contract on the probability of losing the pawns (more negative means then more likely to recover it), averaged for the respective x-axis bin.
-Positive assortative selection would mean a negative relationship: those who benefit more by treatment and lose the pawn less are \emph{less} likely to choose it.
-Using all bins we estimate a slope of zero in the relationship.
-Using the 80 right most points, we estimate a \textit{positive} relationship.
-        %\textit{Do file: }  \texttt{choose\_wrong\_quant\_wrong.do, choose\_wrong\_quant\_wrong\_decomposition.do}
-%\end{figure}
-
-\vspace{.3in}
-
-\cleardoublepage
-
-\vspace{.4in}
-
-\begin{comment}
-
-\subsection{Take up}
-
-\begin{table}[H]
-    \caption{\textcolor{red}{DELETE--Predicting Take-up: Goodness-of-Fit}}
-    \label{Table_compliance}
-    %\begin{subtable}{1\textwidth}
-    % \centering
-    %    \caption{Take up}
-    %    \scriptsize{\input{./Tables/oos_pago_frec_vol.tex}}
-    %\end{subtable}%
-
-    %\bigskip
-     \begin{subtable}{1\textwidth}
-      \centering
-        \caption{Take up: Choice-fee Arm}
-        \scriptsize{\input{./Tables/oos_pago_frec_vol_fee.tex}}
-    \end{subtable}
-
-      \bigskip
-    \begin{subtable}{1\textwidth}
-      \centering
-        \caption{Take up: Choice-promise Arm}
-        \scriptsize{\input{./Tables/oos_pago_frec_vol_promise.tex}}
-    \end{subtable}
-            \scriptsize
-           \\
-           \\
-           \\
-
-     %\textit{Scripts: } \texttt{pred\_take\_up.do, pfv\_pred.R}
-\end{table}
-
-\vspace{.1in}
-\begin{figure}[H]
-    \caption{\textcolor{red}{DELETE--Out of sample ROC curve}}
-    \label{roc_curve}
-    \begin{center}
-    \begin{subfigure}{0.45\textwidth}
-        \caption{Take-up in Fee Arm}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/Boost/ROC_curve_outsample_pago_frec_vol_fee.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.45\textwidth}
-        \caption{Take-up in Promise Arm}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/Boost/ROC_curve_outsample_pago_frec_vol_promise.pdf}
-    \end{subfigure}
-    \end{center}
-     \scriptsize 
-  %\footnotesize{ \textit{Do file: }  \texttt{pred\_take\_up.do}}
-\end{figure}
-
-\vspace{.3in}
-\begin{figure}[H]
-    \caption{\textcolor{red}{\hl{ARE THESE MADE OBSOLETE BY THE NEXT FIGURE? } Predictors of commitment contract take-up}}
-    \label{interactions_takeup}
-    \begin{center}
-    \begin{subfigure}{0.7\textwidth}
-        \caption{PLM}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/determinants_takeup_reg.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.7\textwidth}
-        \caption{Logit}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/determinants_takeup_logit.pdf}
-    \end{subfigure}
-    \end{center}
-     \scriptsize
-      %\footnotesize{ \textit{Do file: }  \texttt{determinants_takeup.do}}
-\end{figure}
-
-\scriptsize 
-\noindent This figure reports bivariate (and multivariate) regressions of the form $TakeUp = \alpha + \beta \: X_i + \epsilon_i$.
-The figure reports the $\beta$ coefficients for different $X_i$'s along with 95\% confidence intervals.
-Panel (a) uses a linear model.
-Panel (b) specifies a logit model.
-
-\end{comment}
-
-%\subsection{Selection on gains}
-
-%\begin{figure}[H]
-%    \caption{Determinants of treatment effects}
-%    \label{determinants_cate}
-%    \begin{center}
-%    \begin{subfigure}{0.65\textwidth}
-%        \caption{Determinants of CATE}
-%        \centering
-%        \includegraphics[width=\textwidth]{Figuras/blp_cate_apr.pdf}
-%    \end{subfigure}
-
-%    \end{center}
-%     \scriptsize   This figure estimates bivariate \& multivariate double-robust regressions of the estimated CATE of forcing.
-
-%\end{figure}
-%\todo[inline]{This is a figure that is not referenced yet in the paper, but there is a line highlighted in yellow that could use this information.
-While there appears to not be any effect, let's remember that the RF is considering nonlinear interactions between variables, as well as using information of missingness of some survey questions.}
-
-\normalsize
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% APPENDIX B
-\begin{comment}
-
-\newpage
-\section{ Mechanisms }
-
-\subsection{Optimism, Over-Optimism, and the Failure of Self-Commitment}
-\label{overconfidence}
-
-\textcolor{red}{Need to decide whether we want to try to plant our feet on Confidence/Overconfidence as the core `why' of the previous result
-.}
-%\subsubsection{Behavioral: overconfident borrowers demand less (but benefit more)} \label{behavioral}
-
-The leading behavioral explanation in the literature for low demand for commitment is present biased preferences with naivete (e.g.
-\cite{Rabin2018}, \cite{John}, \cite{Laibson2018})  \cite{Laibson2015} shows that the lost flexibility resulting from a commitment contract can limit take-up especially severely when agents are (partially) naive about their self control problem.
-In our context if consumers are (partially) naive about their present bias, they would plan to save more (or spend less) than what they actually end up saving, thus making it be harder to recover their pawn.
-This under-saving will be mitigated in the fee forcing contract since the fee makes them save money to pay part of the loan periodically.
-\ref{appendix_c} formalizes this in a model.
-Another behavioral explanation is that clients may underestimate the likelihood and severity of negative income shocks.
-Both of these explanations predict that clients will be overconfident about their likelihood of pawn recovery.
-Recall that in the control group the client's subjective probability of recovery is on average 93\%, while actual recovery is just 44\%.
-A further piece of evidence consistent with underestimating negative income shocks and with present bias with partial naivete is that a large number of people (25\%) in the control group pay a positive amount toward pawn recovery but end up losing their pawn anyway.
-
-So, overconfidence of recovering the pawn is implied by both present bias preferences with naivete and upward bias in their income expectations.
-But does overconfidence actually predict low demand for commitment empirically?
-It does.
-We define as overconfidence as the reported subjective probability of recovery minus the predicted probability based on the client's characteristics, $P^s_i-\widehat{P_i(X_i)}$.\footnote{We predict $\widehat{P_i(X_i)}$ in two steps.
-In step one we use Lasso with cross validation to tune the regularization parameter to select the most predictive variables $X$.
-The typical present bias question as in \cite{Ashraf} was eliminated in this step.
-In the second step we estimate $\widehat{P_i(X_i)}$ using those variables in a logit model.
-The Lasso selected variables were type of pawn, female, age, has pawned before, has savings, participates in rotating savings, often feels tempted to change plans, would like to have a reminder to pay, and an economic vulnerability index.
-We are careful not to include these variables as controls in Table  \ref{oc_reg}.} There is a large amount of overconfidence in our context.
-Figure \ref{oc_hist} plots a histogram of $OC_i$ and shows that the overwhelming majority display overconfidence, and a large fraction overestimate recovery by more than 50 percentage points.
-Our measure of overconfidence is useful especially when there is limited time for a detailed survey.\footnote{It may be more useful than a simple elicitation of present bias as in \cite{Ashraf}.
-We find that 15\% of clients are classified as present biased using this measure of preference reversal.
-This level is similar to the number \cite{Ashraf} find but small to explain no take-up of commitment for 90\% of clients.
-This measure was not correlated with take up of commitment in our sample.} First it is very prevalent, which makes it promising to explain the overwhelming prevalence of low take up.
-Second, it is easy to measure.
-Third, it is predictive of take-up in an intuitive way.
-Finally, overconfidence in recovery is implied by present bias with (partial) naivete but also by biased expectations of negative income shocks, thus capturing both kinds of bias.\footnote{\textcolor{red}{Another indication of overconfidence is that in our data, of those who renew, 83\% lose the pawn anyway.
-Our measure of overconfidence has a correlation of \hl{xxx}\% with a dummy for renewing and losing the pawn.
-}}
-
-\cite{Sprenger} have argued that it is critical to understand the link between beliefs and demand for commitment, yet the evidence is scarce.
-Table \ref{oc_reg} does this: it regresses an indicator of take up of the monthly payment contract against an indicator for overconfidence $OC_i:=\mathbbm{1}(P^s_i-\widehat{P_i(X_i)}>0)$ and controls.
-Controls $Z$ include branch and day of the week dummies, schooling, whether the client does a monthly budget plan, among others.
-We are careful not to include controls that were used in $\widehat{P_i(X_i)}$.
-% and a measure of intertemporal preference reversal analogous to that of \cite{Ashraf} as controls.\
-In the choice-fee arm, being overconfident decreases the likelihood of demanding commitment by 12 percentage points a result that this is robust to including controls  (columns 1 and 2).
-While overconfidence predicts lower take up in the Commitment Choice arm, this is not the case in the promise-choice arm (columns 3 and 4).
-One interpretation of the results is that the overconfident borrowers think they do not need commitment, and their demand decreases sharply as soon as there is even a small fee, and at the same time they perceive the promise as a low cost option.
-This provides evidence for \cite{Sprenger}'s conjecture that ``tepid demand for commitment outside controlled experimental settings is consistent with broad unawareness [of biases]''.
-
-How does overconfidence map to cost outcomes?
-Theory predicts that the more overconfident (naive) may be at the same time those that benefit more from commitment.
-Extrapolating individual treatment effects of the Forced Commitment contract vs the status quo one to the choice arm (see below for more detail), and using them as a dependent variable we find that overconfident borrowers benefit \textit{more} from the commitment contract, with {24.8}\% (=\${30}/\${121}) more savings (columns 5 and 6).
-Thus while we predict the overconfident benefit more from commitment, they demand less of it.
-
-\subsubsection{Neoclassical Alternatives} \label{neoclasical}
-
-\vspace{.1in}
-\noindent \textbf{Risk aversion.} We do not have measures of risk aversion in our short survey, which makes it hard to assess the hypothesis that risk aversion limits take-up of the fee frequent payment contract.
-One way to proceed is to take the empirical distribution of financing cost ---$F_{fee}(FC)$--- as one the client would have faced had she chosen the the fee-commitment contract.
-We could then ask what would risk aversion have to be in order to justify the client choosing the fee-commitment contract distribution of costs over the distribution associated with the status quo contract, $F_{sq}(FC)$.
-Framed as a choice among cost distributions, we can calculate what risk aversion is needed to rationalize the overwhelming choice of the status quo contract over the fee-commitment contract.
-This exercise of course assumes --as is common in economics-- that clients know the distribution of financial cost, that the distribution is common across consumers (although this can be relaxed), and that this cost distribution is the only difference among contracts.
-
-Fortunately for us, it turns out that one distribution first-order-stochastically dominates the other, obviating the need to calibrate a specific utility function or use a parametric distribution function in order to rank them in terms of expected utility.
-We use the fact that if the utility $u(FC)$ is decreasing in $FC$ (i.e.
-clients dislike paying higher financing cost) and $F_{fee}(FC) \geq F_{sq}(FC)$ for all $FC$, which we actually verify in our data, then $E_{fee}[u(FC)] \geq E_{sq}[u(FC)]$, that is any expected utility maximizing client risk averse consumer should choose the Forced Commitment contract as a result of the distribution of cost payoffs.\footnote{See the Appendix for the proof.
-Figure \ref{ecdf_fc} in the Appendix shows that indeed $F_{fee}(FC) \geq F_{sq}(FC)$.
-Table \ref{stochastic_dominance} shows that this holds also for sub-populations of different characteristics.}.
-Thus, risk aversion cannot explain the low demand for commitment under the assumptions of this exercise.
-
-\vspace{.1in}
-\noindent \textbf{Lost flexibility.} A second explanation for low take up is lost flexibility.
-That is, the fee-commitment contract may provide too much commitment which is costly because the client may be forced to incur in late payment fees if he experiences a negative income shock.\footnote{Note that income shocks that affect the ability to pay the entire loan are a worry for both the Forced Commitment contract and the status quo one, and should not make one contract more favorable than the other.} While we cannot rule out that income shocks combined with lost flexibility of the contract explain the low demand, we think it is unlikely.
-First, we showed above that clients report a subjective probability of recovery of 93\% on average, which suggests they are not too worried about income shocks.
-Second, the fear of incurring fees is quantitatively not enough of a concern when compared to the savings they are experiencing.
-%Note that fees for late payment are not that high.
-In an average loan of 2,000 pesos the monthly payment is close to 700 pesos, and a fee of 2\% of that is 14 pesos (less than \$1 dollar).
-This is about gr{1\%} of monthly per capita income of the first 3 deciles of Mexican {household's} income distribution.
-%This compares favorably to the gr{\$11.6 + \$62.3)} pesos transportation / transaction cost of one.
-
-To make this concrete, we calculated what the financing cost of the fee-commitment contract would be if \textit{all} its clients incurred in \textit{all} potential fees (while keeping payment profiles and pawn recovery constant) and added these fictitious fees to financing cost for those in the Forced Commitment arm, thus artificially inflating their cost.
-We then re-estimated the quantile treatment effects analogous to Figure \ref{fc_pro2}(b) with this inflated financial cost.
-%\footnote{Of course behavior may not be constant, but we believe this is a reasonable fist approximation.
-%It could be that having this small fee added to the balance discourages them to pay or makes it harder to pay back the loan.
-But the contrary may also happen, with the fee making them more determined to pay early.
-We would need a structural model of client behavior to estimate a full counterfactual.
-We suspect that such small fees would not generate large changes in behavior in a simple neoclassical model.}).
-Figure \ref{fc_allfee} presents the results.
-We find that even in this extreme scenario, tilted against the Forced Commitment contract, the estimated effect still implies cost savings from the Forced Commitment contract at the mean, 25$^{th}$, 50$^{th}$, and 75$^{th}$ percentiles.\footnote{Recall that the differences in financing cost already takes into account the fact that clients in the fee forcing contract sink more pre-payments than those in the status quo contract, and that those prepayments are lost if the loan is not fully paid back.}  Although these arguments are not definitive, they suggest that low demand for commitment may be driven by more than the anticipation of lost flexibility implied by a small fee.
-
-\vspace{.1in}
-\noindent \textbf{High time discounting.} We mentioned above that clients in the status quo contract tend to wait until the last moment to pay to recover their pawns.
-Even among those that recover their pawn, only 40\% pay before the 90$^{th}$ day.
-Table \ref{mechanisms} shows that clients assigned to the fee-commitment contract front load their payments, starting their first payment earlier and finishing paying earlier too.
-However, clients may dislike front loading payments if their time preference discount rate is high.
-They may be willing to trade off a higher probability of losing their pawn for more \textit{back} loaded payments.
-
-What would discount rates have to be in order for back loaded payments to offset the reductions in financial cost effects we observe?
-%We can calculate this number by looping across a grid of discount rates, incorporating this higher discount rate in the definition of financial cost, and reestimating equation \ref{basic_reg} with this modified financial cost measure as the dependent variable in equation 1, searching for the discount rate that makes $\beta$ equal zero.
-We did this and obtained
-We calculate that the discount rate that is necessary to compensate for the savings in financial cost (i.e.
-that makes the estimated $\beta$ in equation \ref{basic_reg} equal to zero when financing cost --using different $r$'s-- is the dependent variable) is a staggering 8,190 percent per year.
-We find this discount rate implausibly high even for this credit constrained population\footnote{For comparison, \cite{Levin} find that a discount rate of 1,415 per year for subprime borrowers in the US is too high to be believable.}, casting doubt on high discount rates as explanation for low demand for commitment.
-%\footnote{In the baseline survey we give respondents a hypothetical choice between $100$ pesos tomorrow or $150$ pesos in one month (an implicit yearly interest rate of {12,800\%}) and only 30\% chose the later one.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% APPENDIX C
-
-\newpage
-\section{ A simple model}
-\label{appendix_c}
-\vspace{.2in}
-\normalsize
-\linespread{1.05}
-
-Although the empirical results are striking and stand alone, this section refers to the model of \cite{John} to interpret our empirical results.
-The model is stylized but incorporates important features of our context.
-It allows for negative income shocks which we think are prevalent in this population.
-%The shock generates a cost of committing to monthly payments and could potentially be a reason for low take up.
-It also features clients with present biased time preferences --allowing for partial naivete-- choosing to save to pay for an expense, and with the opportunity to make a commitment to save and pay.
-These two features parsimoniously explain several facts about the context --like overconfidence in recovering the pawn--, and about the results --e.g.
-that forcing commitment seems to help.
-We intend the model only as a very stylized approximation to our context, and we use it only to help us organize the interpretation of the empirical results, not as a literal description of reality.
-%Third, it allows for a simple way to model commitment afforded by late payment fees.
-%Nonetheless, the model abstracts from several details of the context.
-Even with these abstraction it allows us to explain our six main results listed in Section \ref{explanations_recap} below.
-
-We use the model of \cite{John} and refer the reader to that paper for more detail, justification of assumptions and some of the proofs.
-The model has three periods and linear utility.\footnote{This does not map perfectly to our 3 period contract, but it is enough to generate the results we need.
-We also assume that the amount of the loan is used up to pay for the emergency.
-\cite{John_theory} provides a more general treatment.} Period $t=0$ is a planning period where the client is either allocated to the status quo, the fee-forcing contract, or a choice between the two.
-Period $t=1$ is the saving-for-the-monthly-payment  period, and $t=2$ in the pawn recovery (loan payment) period.
-In period 1 the client receives her income $y_1=1$, or gets zero with probability $\lambda$.
-She can consume ($c_1$) or save ($s_1$) part that income.
-In period 2 the client gets her savings from period 1, and again receives income of either $y_2=1$, or zero with independent probability $\lambda$.
-In this last period, she decides whether to use income and savings for consumption $c_2$ and/or for paying back the loan of size $p \in(1,2)$ to recover the pawned piece valued at $b>p$.
-In this simple set up we model the fee-commitment contract as a contract that imposes a fee of size $F$ if the client fails at $t=1$ to save $s_1=p-1$ pesos, which is what is needed to pay the loan back when there are no shocks.
-In period $t=0$ she evaluates her welfare as $E[c_1+c_2]$, were for simplicity we have set the time discount to one.
-We also assume the interest rate is one.
-We introduce present biased preferences by assuming the following utility function $U_t=c_t+\beta \: \sum_{k=t+1}^{2} E[c_k]$, with $\beta<1$ indicating present bias.
-A naive client perceives she is not so present biased and instead of $\beta$ uses $\hat{\beta} \in (\beta,1]$.
-
-Note that under these assumptions it is efficient at $t=0$ to recover the loan since $b>p$ and since there is no discounting at $t=0$.
-Because $b>1$, paying back the loan requires that there is no negative shock in any period and that $s_1>0$.
-Because $\beta<1$ at $t=1$ the client will not send savings in excess of what is needed to recover the loan: $s_1=p-1$.
-This parsimonious model implies the following results:
-
-\vspace{.2in}
-\noindent \textbf{Result 1: Present biased clients default more.} Under the status-quo contract, absent shock realizations, present biased clients (sophisticated or naive) with $\beta<\beta_{SQ}<1$ will lose their pawn, while clients with no present bias will not.\footnote{$\beta_{SQ}=\frac{p-1}{\lambda(p-1)+(1-\lambda)(b-1)}$.
-See Proposition 1 in \cite{John}.}
-
-\vspace{.1in}
-\noindent \textbf{Result 2: Forcing present-biased clients into the fee-commitment contract reduces default.} Imposing a fee $F>0$ for late payments weakly decreases default (for present biased clients only).
-It strictly decreases default if $F>F_{min}(\beta):=(p-1)-\beta[\lambda(p-1)+(1-\lambda)(b-1)]$.
-The larger the present bias the larger the $F$ required to induce pawn recovery.\footnote{$F_{min}(\beta)$ is derived from the incentive compatibility constraint needed to generate savings at $t=1$ to recover the pawn can be written as $1-(p-1)+\beta[\lambda(p-1)+(1-\lambda)(b-1)] \geq 1-F+\beta(1-\lambda)$.}
-
-\vspace{.1in}
-\noindent \textbf{Result 3: Demand for commitment.} Given $F>0$, (a) Neoclassical clients will never demand commitment.
-(b) Present-biased sophisticated clients will prefer the fee-forcing contract over the status quo contract $\iff$  $\lambda \: F<(1-\lambda)^2(b-p)$ and $F>F_{min}(\beta)$, that is $\iff$  $\beta \in [\beta_{min},\beta_{SQ}]$.\footnote{$\beta_{SQ}$ was determined in Result 1.
-$\beta_{min}$ is such that $F=F_{min}(\beta_{min})$.} (c) Analogously, naive clients will demand commitment $\iff$ $\hat{\beta} \in [\widehat{\beta_{min}},\beta_{SQ}]$, where $\widehat{\beta_{min}}<\beta_{min}$.
-So strongly naive clients will on the one hand demand more commitment than sophisticated clients since they believe (incorrectly) that a smaller fee will motivate them to pay.
-On the other hand they may demand less commitment since they think they can save and pay on their own.
-Whether they demand more or less than sophisticated clients depends on the empirical distribution of $\beta$ and $\hat{\beta}$.
-
-\vspace{.1in}
-\noindent \textbf{Result 4: Overconfidence.} Only naive clients will be overconfident about the probability of recovery.
-This will be true whether they have the status quo or the fee-forcing contract.
-Overconfidence is increasing in $\hat{\beta}$.
-
-\vspace{.1in}
-\noindent \textbf{Result 5: Welfare.} (a) Neoclassical consumers' welfare strictly decreases when we force clients into the fee-commitment contract instead of the status quo contract because of the risk of them not being able to pay for the installment, and does not change when we offer a choice between them.
-(b) The welfare of sophisticated present biased consumers weakly increases when we give them choice, and it strictly increases  $\iff$  $\beta \in [\beta_{min},\beta_{SQ}]$, that is when they would choose the fee-commitment contract themselves.
-Forcing them into the fee-commitment contract increases welfare $\iff$  $\beta \in [\beta_{min},\beta_{SQ}]$, otherwise it strictly decreases it.
-So choice is better than forcing for sophisticates.
-(c) Forcing can be welfare improving for the naive.
-Indeed if $\hat{\beta}>\beta_{SQ}>\beta$ then forcing the fee-commitment contract increases welfare, and if $\hat{\beta} \in (\widehat{\beta_{min}},\beta_{min})$ then forcing the status quo contract increases welfare.\footnote{This result is different from that in \cite{John}.
-Her context has individuals choosing the size of the fee.
-In that context naive clients will \textit{always} chose the wrong fee size and default later, therefore choice is always decreasing for the naive.
-In our context $F$ is fixed at 2\% of the balance due, and this implies that choice could be welfare improving for some naifs.} We want to highlight that only under certain parameters will forcing installment payments improve welfare, and that welfare will likely decrease for those with no present bias and the sophisticated present biased consumers.
-
-\vspace{.1in}
-\noindent \textbf{Result 6: Welfare and ex-post observed behavior.} If for a naive client $i$ the fee-forcing contract causes higher pawn recovery, then we know the fee $F$ made her IC constraint binding, and therefore that $\hat{\beta}_i>\widehat{\beta}_{min}$.
-If in addition if it was the case that $\beta_i<\beta_{SQ}$.
-%\footnote{\hl{Isaac, aqui tengo dos pregutas: (1) si es $\beta$ y no $\hat{\beta}$ verdad?
-(2) Para que una persona naive empenie en el status quo tiene que ser que cree que va a recuperar no?
-Es decir tiene que ser $\hat{\beta}>\beta_{SQ}$ correcto?}}
-then the fee-forcing contract would have increased welfare for the naive.
-That is, our finding that the fee-forcing contract increases pawn recovery is a sign of higher welfare (although not a sufficient condition).\footnote{It is not sufficient since ex-ante the commitment $F$ may have been too expensive given the income shocks, i.e.
-if $\lambda \: F>(1-\lambda)^2(b-p)$.}
-
-\subsection{Interpretation}
-
-The model is very parsimonious but powerful and it can potentially explain all our empirical findings qualitatively.\footnote{The model is sufficiently stylized that we think we would not gain much from estimating it.
-Furthermore we have no data on income shocks which figure prominently in the model.
-\cite{Ted} and \cite{Aprajit} are two very recent models that combine a field experiment with commitment contracts and estimation of present bias parameters.} First, it can explain why default is high in the status-quo contract, namely that clients are present biased and have no commitment devices.
-Second, it can explain why clients are overconfident in our data, namely by virtue of naivete about present bias.
-Under the model naivete is necessary to explain this.
-Third, it can also explain why the fee forcing contract induces lower default, but not for everyone: namely that it makes the incentive compatibility constraint for payment binding for the present biased, while it was not binding in the status quo contract.
-Fourth, it can also explain why there is low demand for commitment even if it seems to improve welfare: namely that there is a small share of neoclassical and sophisticated clients, and at the same time naifs have a present biased parameters values in the region in which they think they can save on their own.
-Fifth, it explains non-zero demand for commitment for a set of clients.
-Sixth, it can explain why clients exposed to the Forced Commitment contract are more likely to come back namely those naifs whose welfare increased as a result of being forced into the fee-commitment contract.\footnote{Those with $\hat{\beta_i}>\beta_{SQ}>\beta$.}
-
-\subsection{Other potential explanations: recap} \label{explanations_recap}
-
-There may be other interpretations of the empirical findings, but the bar is high. An alternative explanation will need to explain the 6 facts below:
-
-\begin{enumerate}
-\itemsep0em 
-\item High (although ex-post inefficient) default in status quo contract.
-\item Overconfidence about pawn recovery.
-\item Forcing commitment increases pawn recovery.
-\item Small demand for commitment...
-\item ...but positive demand for commitment.
-\item Forcing commitment makes clients more likely to come back.
-\end{enumerate}
-
-Let us consider alternative explanations in isolation (i.e. just considering one change or feature at a time with respect to a neoclassical model):
-
-\vspace{.1in}
-\noindent \textbf{Alternative 1: Strong prevalence of income shocks.} This could explain (4) and (1), but not why forcing helps, (3) and (6), nor why there is overconfidence, (1).
-It would also not explain why clients come to pawn in the first place and then default, (2), as they would weight in on the high chance of losing the pawn.
-
-\vspace{.1in}
-\noindent \textbf{Alternative 2: High time discounting}.
-This could not explain (1) nor (5) nor (6).
-It could qualitatively explain (4), but as we say in section \ref{sec:demand} quantitatively it would require unbelievably high discount rates.
-
-\vspace{.1in}
-\noindent \textbf{Alternative 3: Risk aversion.} We already discussed and rejected risk aversion in section \ref{sec:demand}, although using strong assumptions in the process.
-Risk or ambiguity aversion could still play a role in explaining 4 and should be investigated in future research.
-However it would hardly explain (1), (2), (5), or (6).
-
-\vspace{.1in}
-\noindent \textbf{Alternative 4: Misunderstanding the contracts.}\footnote{This is a potential criticism of \textit{any} paper offering choice, and one that is non-falsifiable if the critic has free reign to propose how the contracts are perceived in the subject's mind.} We were very aware of the importance of clients understanding the contract in order to infer preferences from choice.
-That is why we made a strong effort for clients to understand the contracts (see subsection \ref{implementation}).
-Note however that while clients making purely random mistakes could explain why 10\% demand commitment ---i.e.
-(4) and (5)--- it would not explain the rest of the findings, nor why the Soft Commitment (see below) had more take up that the fee-commitment, or why we can statistically predict take-up with significant accuracy (see Figure \ref{interactions_takeup} and Table \ref{Table_compliance}).
-
-\vspace{.1in}
-\noindent \textbf{Alternative 5 (behavioral): Forgetting to pay/salience.} Frequent payments may act as a reminder to save and recover the pawn.
-This would try to explain (1) by appealing to people forgetting to pay, and (3), (5), and (6) by appealing to frequent payment acting as reminders (i.e.
-there being demand for reminders).
-It would not explain (2) or (4) which are critical in the paper.
-However even for (1) it seems to us a stretch to explain people losing a valuable pawn by forgetting to pay it.
-Since the Soft Commitment installment contract did not change behavior (as shown below) this explanation would also require us to posit that only fees acts as reminders, not promises.
-
-\vspace{.1in}
-\noindent \textbf{Alternative 6 (behavioral): Income shocks overconfidence}.
-One could also easily introduce in the overconfidence about income shocks in the model of \ref{appendix_c}\footnote{Say with $\widehat{\lambda} <\lambda$.
-The effect on demand for commitment is uncertain since on the one hand it decreases $\beta_{SQ}$ decreasing demand, but on the other a smaller $F$ is needed to make the IC binding, making commitment less costly.}.
-This would leave default unchanged in both the status quo and the fee forcing contract thus would not explain (3), %since $F_{min}(\beta,\widehat{\lambda})<F_{min}(\beta,\lambda)$.
-% $\widehat{\lambda} <\lambda$ alone 
-It would not explain (5) or (6) either as demand for commitment would be zero without present bias.
-
-\vspace{.1in}
-We do not claim that the model in the Appendix is the only possible explanation of our empirical findings, but it is a parsimonious explanation of all of them.
-
-\end{comment}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\clearpage
-%\bibliographystyle{authordate1}
-%\bibliographystyle{amsalpha}
-%\bibliographystyle{AER}
-
-%\bibliography{References}
-
-% \end{document}
+\end{document}

### 2024-05-24 Restud submission/donde_restud.tex
new submission

--- 2024-05-21 ECTA submission/donde_ecta.tex
@@
-% use option [draft] for initial submission
-%            [final] for the prepublication
-\documentclass[ecta,nameyear,draft]{econsocart}
-%\documentclass[]{econsocart}
-%
-%\usepackage{}
-\RequirePackage[colorlinks,citecolor=blue,linkcolor=blue,urlcolor=blue,pagebackref]{hyperref}
-
-\startlocaldefs
-
-\usepackage{booktabs}
-\usepackage{multirow}
-\usepackage{float}         
-\usepackage{amsmath}
-\usepackage{amscd}
-\usepackage{amsfonts}
-\usepackage{amssymb}
-\usepackage{bbm}
-\usepackage{dsfont}
-\usepackage{colortbl}
-\usepackage{comment}
-\usepackage{lscape}
-\usepackage{subcaption}
-\newtheorem{theorem}{Theorem}
-\newtheorem{claim}[theorem]{Claim}
-\newtheorem{prop}[theorem]{Proposition} 
-\newtheorem{cor}[theorem]{Corollary} 
-\newtheorem{assumption}{Assumption} 
-\newtheorem{lem}{Lemma} 
-\usepackage{enumerate}
-
-\newcommand{\wh}{\widehat}
-
-\newcommand{\E}{\mathbb{E}}
-
-\endlocaldefs
-
-\usepackage[section]{placeins}
-
+\documentclass[12pt, a4paper]{article}
+
+\input{preamble.tex}
+%%% HELPER CODE FOR DEALING WITH EXTERNAL REFERENCES
+\usepackage{xr}
+\makeatletter
+\newcommand*{\addFileDependency}[1]{
+  \typeout{(#1)}
+  \@addtofilelist{#1}
+  \IfFileExists{#1}{}{\typeout{No file #1.}}
+}
+\makeatother
+
+\newcommand*{\myexternaldocument}[1]{
+    \externaldocument{#1}
+    \addFileDependency{#1.tex}
+    \addFileDependency{#1.aux}
+}
+
+\newgeometry{margin=1in}
+\linespread{1.25}
 \begin{document}
 
-\begin{frontmatter}
-
-\title{The controlled choice design and private paternalism in pawnshop borrowing}
-\runtitle{The controlled choice design and private paternalism}
-
-\begin{aug}
-% use \particle for den|der|de|van|von (only lc!)
-% [id=?,addressref=?,corref]{\fnms{}~\snm{}\ead[label=e?]{}\thanksref{}}
-%
-%% e-mail is mandatory for each author
-%
-%%% initials in fnms (if any) with spaces
-%
-\author[id=au1,addressref={add1}]{\fnms{Craig}~\snm{McIntosh}\ead[label=e1]{ctmcintosh@ucsd.edu}}
-\author[id=au2,addressref={add2}]{\fnms{Isaac}~\snm{Meza}\ead[label=e2]{isaacmezalopez@g.harvard.edu}}
-\author[id=au3,addressref={add3}]{\fnms{Joyce}~\snm{Sadka}\ead[label=e3]{jsadka@itam.mx}}
-\author[id=au4,addressref={add4}]{\fnms{Enrique}~\snm{Seira}\ead[label=e4]{enrique.seira@gmail.com}}
-\author[id=au5,addressref={add5}]{\fnms{Francis J.}~\snm{DiTraglia}\ead[label=e5]{francis.ditraglia@economics.ox.ac.uk}}
-
-% Addresses
-\address[id=add1]{%
-\orgdiv{Department of Economics}
-\orgname{University of California San Diego}}
-
-\address[id=add2]{%
-\orgdiv{Department of Economics}
-\orgname{Harvard University}}
-
-\address[id=add3]{%
-\orgdiv{Department of Economics}
-\orgname{Instituto Tecnologico Autonomo de Mexico}}
-
-\address[id=add4]{%
-\orgdiv{Department of Economics}
-\orgname{Michigan State University}}
-
-\address[id=add5]{%
-\orgdiv{Department of Economics}
-\orgname{University of Oxford}}
-\end{aug}
-
-%% Put support info here. Reminder: do not thank the handling coeditor anonymously or by name
-\support{We want to thank Mauricio Romero and Anett John for advice and encouragement.
+\title{The controlled choice design and private paternalism in pawnshop borrowing\thanks{We want to thank Mauricio Romero and Anett John for advice and encouragement.
 Ricardo Olivares, Gerardo Melendez, and Alonso de Gortari provided excellent research assistance and Erick Molina helped with formatting.
@@
 Research assistance was financed through faculty grants at ITAM.
-Our research partner had no say in the results.}
-%
-\coeditor{\fnm{[Name} \snm{Surname}; will be inserted later]}
+Our research partner had no say in the results.}}
+\author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira \and Francis J.\ DiTraglia   \thanks{Seira:  MSU, \url{enrique.seira@gmail.com} (corresponding author); McIntosh:  University of California San Diego, \url{ctmcintosh@ucsd.edu}; Meza: Harvard University, \url{isaacmezalopez@g.harvard.edu}; Sadka: ITAM, \url{jsadka@itam.mx}; DiTraglia: Oxford, \url{francis.ditraglia@economics.ox.ac.uk}} }
+\date{This draft:  \today \\[2 cm]}
+
+%\vspace{.5in}
+
+\maketitle
+\vspace{-0.75in}
 
@@
 
-\begin{keyword}
-\kwd{Private paternalism}
-\kwd{choice}
-\kwd{treatment on the untreated}
-\kwd{heterogeneous treatment effects}
-\kwd{commitment}
-\kwd{overconfidence}
-\end{keyword}
-
-\end{frontmatter}
+\textbf{Keywords: } Private paternalism, choice, treatment on the untreated, heterogeneous treatment effects, commitment, overconfidence.
+
+\textbf{JEL codes:} G41, C93, O16, G21
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 As a second measure of cost we calculate the Annual Percentage Rate (APR) in order to express the cost as a percentage of the loan, per year, inclusive of default costs.
-The standard definition is given in the following formula: $(\text{APR})_i =\left( 1 + \frac{\frac{\text{Financial Cost}_i}{\text{Loan}_i}}{\text{loan term}_i}\right)^{\text{loan term}_i}-1 $
+The standard definition is given in the following formula:
+$$(\text{APR})_i =\left( 1 + \frac{\frac{\text{Financial Cost}_i}{\text{Loan}_i}}{\text{loan term}_i}\right)^{\text{loan term}_i}-1 $$
 
@@
 \begin{figure}[htbp]    
+ \caption{Experiment description}
 \begin{center}
@@
   \end{center}
- \caption{Experiment description}
      \label{exp_description}
-%\textit{Do file: }  \texttt{ss\_att.do}
+%\textit{Do file: }  \texttt{consort.do}
 \end{figure}
@@
 \resizebox{1.0\textwidth}{!}{
-\scriptsize{\input{./Tables/decomposition_main_te.tex}}
+\footnotesize{\input{./Tables/decomposition_main_te.tex}}
 }
 \end{center}
-\legend{This table shows the treatment effects for our core pecuniary outcomes.
+\footnotesize{This table shows the treatment effects for our core pecuniary outcomes.
 Each column is a different regression for different outcomes on an indicator for the forced and choice arms, following specification in equation \ref{basic_reg}.
@@
 \begin{center}
-\scriptsize{\input{./Tables/repeat_loans.tex}}
+\footnotesize{\input{./Tables/repeat_loans.tex}}
 \end{center}
- \legend{This table estimates the specification of equation \ref{basic_reg} but at the level of the borrower (not the loan). Each column represents a regression with a different outcome variable.
+ \footnotesize{This table estimates the specification of equation \ref{basic_reg} but at the level of the borrower (not the loan).
+Each column represents a regression with a different outcome variable.
  % In column 1, the dependent variable indicates, for each borrower in the experiment, whether he/she pawned again after the first loan in the experiment (up to the end period of our data set 338 days after the experiment began).
@@
 \begin{figure}
+\caption{Graphical Intuition for the Controlled Choice Design.} 
     \begin{center}
@@
     \end{center}
- \caption{Graphical Intuition for the Controlled Choice Design. 
+ \footnotesize{
      %This figure illustrates why the controlled choice design identifies the TOT and TUT effects.
@@
 \begin{center}
-\scriptsize{\input{./Tables/tot_tut.tex}}
+\footnotesize{\input{./Tables/tot_tut.tex}}
 \end{center}
-\legend{This table presents results computed using the derivations from Section \ref{sec:randchoice}.
+\footnotesize{This table presents results computed using the derivations from Section \ref{sec:randchoice}.
 The APR and financial cost outcomes have been multiplied by $-1$ so that a positive causal effect \emph{benefits} the borrower in each of the four columns.
@@
 \begin{figure}[H]
+ \caption{``Mistakes'' in the choice arm.}
 \begin{center}
         \centering
-        \includegraphics[width=0.6\textwidth]{Figuras/line_cw_apr_tot_tut.pdf}
-
+        \includegraphics[width=0.65\textwidth]{Figuras/line_cw_apr_tot_tut.pdf}
  \end{center}       
- \caption{``Mistakes'' in the choice arm.
-This figure presents conditional average TUT and TOT effects for the APR outcome from Figure \ref{heterogeneous_effects} in an alternative manner, to consider the fraction of borrowers in the choice arm who made ``mistakes'' in their decision to accept or refuse the commitment contract.
+ \footnotesize{This figure presents conditional average TUT and TOT effects for the APR outcome from Figure \ref{heterogeneous_effects} in an alternative manner, to consider the fraction of borrowers in the choice arm who made ``mistakes'' in their decision to accept or refuse the commitment contract.
 A ``mistake'' for a non-chooser is defined as a positive conditional TUT effect that significantly exceeds a specified threshold APR value.
@@
 \begin{center}
-
-\scriptsize{\input{./Tables/hit_miss_rule.tex}}
-
+\footnotesize{\input{./Tables/hit_miss_rule.tex}}
 \end{center}
-\legend{This table reports error rates for six different rules for allocating individuals to commitment.
+\footnotesize{This table reports error rates for six different rules for allocating individuals to commitment.
 Row 1 assigns all borrowers to control, Row 2 all to the Forcing arm.
@@
 %BIBLIOGRAPHY
-
-\bibliographystyle{ecta-fullname} % Style BST file
-\bibliography{References}  % Bibliography file (usually '*.bib')
+\begingroup
+\setstretch{1.10}
+\bibliographystyle{authordate1}
+%\bibliographystyle{amsalpha}
+%\bibliographystyle{AER}
+
+\bibliography{References}
+\endgroup
 
@@
 
-\input{ECTA submission/OA_ecta}
+\input{Restud submission/OA_restud}
 \end{document}

### 2024-05-31 Restud submission/OA_restud.tex
computation of lenders profit + minor edits

@@
 \begin{figure}[H]
-    \caption{Determinants of choice.}
+    \caption{Weekly default rates experimental branches and all branches}
+    \label{external_validity}
     \begin{center}
@@
         \centering
-        \includegraphics[width=\textwidth]{Figuras/determinants_choose_commitment.pdf}
-    \end{subfigure}
-    \end{center}
-\footnotesize{The above figure shows the determinants in a bivariate and multivariate OLS regression of choosing commitment.
-Choice commitment is a binary variable equal to one, whenever subjects choose the forced commitment contract in the choice arm.
+        \includegraphics[width=\textwidth]{Figuras/weekly_def_rates.pdf}
+    \end{subfigure}
+    \end{center}
+\footnotesize{The above figure shows the weekly default rates for our experimental sample, and for 4 years after our experiment.
+We show that the default rates in the experimental sample are not atypical.
 }
@@
 \normalsize
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{ Internal Validity}
-
-\begin{table}[!h]
-\caption{Summary statistics and Balance}
-\label{SS}
-\begin{center}
-\resizebox{0.65\textwidth}{!}{
-\footnotesize{\input{./Tables/SS.tex}}
-}
-\end{center}
-\footnotesize {Each row in this table corresponds to a regression, where the level of observation is the individual loan originated.
-The dependent variables of these regressions are displayed in the first column.
-Each dependent variable is regressed in a multivariate OLS regression against the experimental arms indicators (control, forced commitment, choice).
-The table reports the coefficients on each of these indicators, as well as the p-value an F-test of the null hypothesis of equality of the three coefficients.
-The admin data was a very limited set of pre-determined variables.
-The dependent variables are: subjective value of the pawn (how much would the client be willing to sell it for (Q3), an indicator for having trouble paying bills in the last 6-months (Q28), present bias (constructed from questions Q10 and Q29 in the standard way as in \cite{Ashraf}), an indicator for whether they make expenses budget for the month ahead of time.
-The subjective probability of recovery was elicited a la Manski (from 0 to 100 what is the probability that you will recoup your pawn), pawned before is a dummy=1 if the client declares to have pawned before (although not necessarily with Lender $P$) age is in year, +High-school is a dummy that indicates if the client has completed high school.
-}
-%\textit{Do file: } \texttt{ss\_balance.do}
-\end{table}
-
-If potential borrowers disliked being forced into a commitment contract, we would expect a lower number of pawns on branch days where only the commitment contract is available compared to control days.
-Table \ref{attrition_table} shows that this is not the case.
-There is no difference at all between the Control and Forced Commitment arm in terms of the number of pawns per branch-day.
-Although we cannot reject equality across the three arms (p-value=0.21), the Choice arm appears to have a somewhat larger number of borrowers than the Control and Forced arms.\footnote{p-value=0.23 and 0.12 respectively.} This seems to be due to sampling variability.
-Differences across arms are smaller when for medians, or when we compare the number of borrowers pawning (some borrowers pawn more than one piece).
-% Figure \ref{boxplot_attrition} shows that distribution of loans per day is comparable across arms.
-The only noticeable difference is that the choice arm has a few more positive outliers.\footnote{If we winzorize at the 90th percentile, the mean number of branch-day pawns becomes identical across arms.}
-
-\begin{table}
-\caption{Limited and balanced attrition}
-\label{attrition_table}
-\begin{center}
-\footnotesize{\input{./Tables/Attrition.tex}}
-\end{center}
-\footnotesize{Each row in this table 
- corresponds to a regression.
-The dependent variables are: the number of pawns-loans originated per day per branch, the number of borrowers per day-branch, a variable indicating whether a person who answered the baseline survey (before knowing contract terms) ended up pawning, and an indicator of whether the person that obtained the loan answered the baseline survey.
-Each dependent variable is regressed in a multivariate OLS regression against the experimental arms indicators (control, forced commitment, choice).
-The table reports the coefficients on each of these indicators, as well as the p-value of an F-test of the null hypothesis of equality of the three coefficients.
-%Figure \ref{boxplot_attrition}, in the appendix shows a box-plot of the first two variables, showing the distribution across arms is balanced.
- }
-%\textit{Do file: } \texttt{ss\_att.do}
-\end{table}
-
-The bottom panel of Table \ref{attrition_table} shows balance in a more focused way, given that the surveys were conducted prior to the revelation of treatment status.
-We find that in no arm did more than three percent of individuals who responded to the survey go on to refuse loans.
-That is, the overwhelming majority of potential borrowers did not leave the branch after learning which contract was on offer.
-Moreover, the extremely small fraction that did leave is balanced across arms.
-Therefore it appears that the treatments have not induced any endogenous shifts in the composition of borrowers.
-
-A less critical form of attrition is differential refusal to answer the survey questions.
-The survey was conducted before treatment status was revealed, and we observe loan outcomes regardless of whether the survey was conducted.
-Our core experimental estimates do not use the survey data as covariates, but the analysis in Section \ref{Paternalism} is restricted to the subset of borrowers who answered at least some survey questions.
-The bottom row of Table \ref{attrition_table} shows that the survey response rate is broadly similar across arms (about 78 percent).
-
-%We now present an analysis of the extent to which the survey-responding sample is representative and balanced.
-Table \ref{SS_cond_survey} presents information about survey non-response.
-Panel A is a balance table that compares loan amount and day of the week across treatment arms for the subset of borrowers who responded to at least one survey question.
-The p-values in the fourth column are for the F-test of no difference of means across treatment arms.
-Panel B presents response-rates by question for each arm of the experiment, along with p-values for the F-test of no difference in question-specific response rates across treatment arms.
-This panel uses data from participants who answered at least one survey question and went on to pawn on the same day as their survey response.
-From the table, we see that loan amount and weekday are balanced across treatment arms among survey respondents and that response rates are likewise stable across treatment arms.
-
-% Table \ref{TUT_cond_survey} shows how the estimated TUT effect changes if we restrict our estimation sample based on survey response.
-% The first row of the table presents TUT results for the financial cost outcome, while the second presents corresponding results for the APR outcome.
-% In each row, column (1) presents the full-sample TUT estimate and standard error while the remaining columns restrict the sample to borrowers who answered a particular survey question or set of questions.
-% For example, column (4) presents results for borrowers who answered the two questions needed to compute our measure of ``present bias'' discussed in the next paragraph, while column (9) present results restricted to participants who disclosed their sex.
-% As seen from the table, our TUT estimates are quite stable across sub-samples defined by survey response.
-% In each case they are positive and of the same magnitude as the corresponding full-sample estimate, although statistical significance varies depending on the size of the corresponding sub-sample. 
-% For these reasons, we are comfortable relying on data for survey respondents in the empirical exercises that follow.
-% In exercises that rely on a single survey question, we use data for every borrower who answered that question.
-% In the random forest exercises described below, we use data for every borrower who answered at least one survey question.
-
-% \begin{table}[H]
-% \caption{Survey Non-response: TUT estimates for respondents to each survey question.}
-% \label{TUT_cond_survey}
-% \begin{center}
-% \footnotesize{\input{./Tables/tut_cond_survey.tex}}
-% \end{center}
-% \footnotesize{Some borrowers did not respond to our survey; others only completed part of the survey.
-% This table computes the TUT effect for a number of sub-groups by survey response, and compares them against the overall TUT effect.
-% The top panel uses financial cost as the outcome variable, while the bottom panel uses APR.
-% Each group is defined by the borrowers who responded to a particular \emph{subset} of the survey questions. 
-% For example, column (4) computes TUT effects for the subgroup of borrowers who responded to the two questions needed to compute our measure of present bias, while column (8) computes the TUT for the subgroup of borrowers who provided their age.
-% The bottom row of the table counts the number of borrowers in each category.
-% TUT estimates are quite stable across sub-groups and generally similar to the full-sample estimates.
-% Because standard errors increase as sample size falls, some of the sub-group estimates are not statistically significant.}
-% %\textit{Do file: } \texttt{tut_cond_survey.do}
-% \end{table}
-
-\section{ Main treatment effects: Additional material}
 
@@
 
+\newpage
 \subsection{Intermediate Outcomes}
@@
 \begin{center}
-\resizebox{0.9\textwidth}{!}{
+\resizebox{0.95\textwidth}{!}{
 \footnotesize{\input{./Tables/fc_robustness.tex}}
@@
 
+\subsection{Repawning}
+
+We now estimate equation \ref{basic_reg} with Different dependent variables.
+In column 1, the dependent variable indicates, for each borrower in the experiment, whether he/she pawned again after the first loan in the
+experiment (up to the end period of our data set 338 days after the experiment began).
+The result is that the likelihood of repeat business increases by 6.7\%.
+While this appears to be \emph{prima facie} evidence of greater satisfaction among borrowers in the forced arm, the interpretation is complicated by the fact that monthly payments may themselves trigger more borrowing to pay them.
+Note that from the lender's perspective, why repeat pawning happens may not be as important as the fact that it happens.
+Illiquidity does not seem to drive this result, given that the effect on re-pawning comes after 90 days (during the period of contract demanded payments) and not before  (see columns 2 and 3).
+Column 4 only considers new loans that use different collateral from that of the initial one.
+We do this to foreclose the explanation that those in the Forced arm, being more liquidity-constrained, return to pawn a second pawn to be able to pay the monthly payments of their first loan.
+However, we cannot reject a zero effect on pawning a different collateral.
+Column 5 focuses on the (endogenous) subsample of those recovering their pawn in both arms of the experiment.
+This means that \textit{both} arms have recovered their pawn and could re-pawn if they so wish, and also that the liquidity demands from the monthly contract are \textit{no longer} there as the contract has been closed.
+We find that the difference between the Forcing contract and the status quo is even larger in this subsample, with the former having 11pp higher likelihood of being a repeat client during our sample period.
+
+\begin{table}[!h]
+\caption{Effects on Repeat Pawning}
+\label{repeat_loans}
+\begin{center}
+\footnotesize{\input{./Tables/repeat_loans.tex}}
+\end{center}
+ \footnotesize{This table estimates the specification of equation \ref{basic_reg} but at the level of the borrower (not the loan).
+Each column represents a regression with a different outcome variable.
+In column 1, the dependent variable indicates, for each borrower in the experiment, whether he/she pawned again after the first loan in the experiment (up to the end period of our data set 338 days after the experiment began).
+Column 2 is analogous, but only pawning after 90 days of the first loan is considered.
+Column 3 instead considers pawning before 90 days.
+Column 4 is analogous to column 1 but focuses on the pawning of a gold piece that is different from the one in the first experimental loan.
+Column 5 is analogous to column 1, but conditioning on the sample that recovered the first loan.
+Standard errors are clustered at the branch-day level.}
+%\textit{Do file: } \texttt{repeat\_loans.do}
+\end{table}
+
+\begin{table}[!h]
+\caption{Lender's Profit}
+\label{lenders_profit}
+\begin{center}
+ \footnotesize{\input{./Tables/lenders_profit.tex}}
+\end{center}
+ \footnotesize{ The dependent variable in column (1) is the profit formula in equation (\ref{profit_function}). Columns (2)-(3) are back-of-the-envelope computations of the lender's profit.
+ Standard errors are clustered at the branch-day level.}
+%\textit{Do file: } \texttt{lenders\_profit.do}
+\end{table}
+
+\newpage
+
 \section{ Alternative explanations}
@@
 \normalsize
-
-\newpage
 

### 2024-05-31 Restud submission/donde_restud.tex
computation of lenders profit + minor edits

@@
 
-\title{The controlled choice design and private paternalism in pawnshop borrowing\thanks{We want to thank Mauricio Romero and Anett John for advice and encouragement.
+\title{The forcing-choice design and paternalism in pawnshop borrowing\thanks{We want to thank Jose Maria Barrero, Andrei Gomberg, Emilio Gutierrez, Anett John David Laibson, Aprajit Mahajan, Matt Rabin, Mauricio Romero, Charlie Sprenger, Chris Udry, and seminar participants at ITAM, USC, MSU, and UCSD provided valuable feedback.
 Ricardo Olivares, Gerardo Melendez, and Alonso de Gortari provided excellent research assistance and Erick Molina helped with formatting.
-Jose Maria Barrero, Andrei Gomberg, Emilio Gutierrez, David Laibson, Aprajit Mahajan, Matt Rabin, Charlie Sprenger, and seminar participants at ITAM, USC, MSU, and UCSD provided valuable feedback.
 Research assistance was financed through faculty grants at ITAM.
-Our research partner had no say in the results.}}
+Our research partner had no say in the design or results of the experiment.}}
 \author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira \and Francis J.\ DiTraglia   \thanks{Seira:  MSU, \url{enrique.seira@gmail.com} (corresponding author); McIntosh:  University of California San Diego, \url{ctmcintosh@ucsd.edu}; Meza: Harvard University, \url{isaacmezalopez@g.harvard.edu}; Sadka: ITAM, \url{jsadka@itam.mx}; DiTraglia: Oxford, \url{francis.ditraglia@economics.ox.ac.uk}} }
@@
 \begin{abstract}
-We use a novel three-armed RCT, including both forced and voluntary treatment arms, to provide a unique window into choice, heterogeneous treatment effects and paternalism in the context of pawnbroker lending.
-Forcing borrowers into commitment contracts with a regular repayment structure decreases the financial cost of pawn loans by 22\% inclusive of fees, increases the likelihood of recovering their pawn by 15\%, and increases the likelihood of repeat business by 19\%.
-Leveraging the special features of our experimental design, we go on to point-identify the effects of commitment on both the treated and the untreated simultaneously, along with the average selection on gains.
-We find large and significant effects of commitment even for borrowers who would not voluntarily choose it, and no evidence of selection on gains: borrowers who would freely choose commitment do not appear to benefit more than borrowers who would not.
-A detailed analysis of treatment effect heterogeneity suggests that the potential gains from targeting commitment based on observable characteristics are extremely small and that most borrowers stand to gain from a policy of universal forced commitment.
+We explore paternalism in the important high-default pawnlending context.
+We use a novel one-stage, three-armed RCT, including forced and voluntary treatment arms, to point-identify the effects of commitment on both the treated \textit{and the untreated} simultaneously.
+We find that forcing borrowers into contracts with a regular repayment structure decreases the financial cost of pawn loans by 22\% and increases the likelihood of recovering their pawn by 15\%.
+However, only 11\% of borrowers choose such contracts.
+We find that borrowers who would not choose frequent payments would benefit substantially from getting such contracts, as much as those freely choosing them (no selection on gains).
+A paternalistic policy of universal forced commitment archives similar benefits to personalized ML targeting.
 \end{abstract}
 
-\textbf{Keywords: } Private paternalism, choice, treatment on the untreated, heterogeneous treatment effects, commitment, overconfidence.
-
-\textbf{JEL codes:} G41, C93, O16, G21
+\vspace{.8in}
+\noindent \textbf{Keywords: } Paternalism, choice, treatment on the untreated, payment frequency, overconfidence. \textbf{JEL codes:} G41, C93, O16, G21
 
@@
 
+\newpage
+
 \section{Introduction}
 
-The behavioral finance literature has established an important role for commitment devices in helping consumers to achieve their own financial goals.
+Financial institutions often restrict choice using built-in commitment mechanisms like fixed repayment streams.
+These widely used attributes are meant to lower default and increase lender profit.
+At the same time, these firms often shroud those features by embedding them as non-negotiable attributes of the loan contract, presumably because borrowers underestimate their value, a case referred to as ``private paternalism'' by \cite{Laibson2018}.
+While \cite{Laibson2018} focuses on situations where the incentives of the firm align with those of the client, with overcollateralized loans, the lender may have incentives to \textit{encourage} default---using balloon payments or unstructured repayment loan contracts---in detriment of the borrower.
+
+Do lenders have this incentive?
+Would structured payment features that commit borrowers to pay earlier lead to lower financial cost for borrowers?
+Would borrowers freely demand such features?
+How can researchers rigorously estimate the benefits for borrowers who would freely choose the feature and for those that \textit{would not} choose it, necessary to assess paternalism?
+This paper answers these questions and studies the benefits of restricting borrower choice  in the context of one of the most prevalent and understudied forms of over-collateralized borrowing: pawn loans.
+
+Pawn loans constitute one of the oldest and most prevalent forms of borrowing \citep{carter2012pawnshops}.
+Our partner lender, for example, made over 4 million loans to more than a million clients during in the three years adjacent to our experiment.\footnote{For comparison, there were 2.3 million microfinance clients in Mexico in 2009 \citep{Pedroza:2010}.}
+The question of choice versus paternalism is particularly salient in this context, as choice mistakes could arise from borrowers' low education and the fact that they typically borrow for emergencies under significant stress.\footnote{A large literature shows  stress impairs cognitive function, e.g.
+\cite{StressReview}.}
+%\footnote{There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues (in China it is a \$43 billion industry).
+\url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.}
+
+In our context, assessing a case for paternalism involves rigorously evaluating whether imposing contract terms on a borrower can achieve lower financial cost than letting the borrower choose whether to have it.
+Often models (e.g.
+Roy models) \textit{assume} that agents self-select into contracts that are best for them.
+Using a novel one-stage three-armed randomized controlled experiment, including forced treatment and treatment choice arms, allow us to point identify the relevant TOT and TUT effects and \textit{test} that assumption in a real-world, high-stakes setting.\footnote{We can also estimate the average selection on gains $\text{ASG} = \text{TOT} - \text{TUT}$, the average selection bias (ASB)---the average difference in untreated potential outcomes for those who choose commitment relative to those who do not, and the average selection on levels (ASL).}
+
+%In some contexts the positive sorting assumption is compelling, it is not obvious in ours.
+Demand for commitment can be particularly low \citep{Ashraf,Gine, Royer,Ted,Sprenger}, and pawn-based borrowers are often financially illiterate.
+
+%The behavioral finance literature has established an important role for commitment devices in helping consumers to achieve their own financial goals.
 While most academic studies on commitment focus on the role of voluntary self-commitment \citep{thaler2004save, prina2015banking, brune2016facilitating, callen2019headwaters, Pascaline, Ashraf}, in reality the predominant use of rigid structure in financial services is involuntary; firms only offer a product with these features embedded.
@@
 
-The relationship between treatment effects and treatment take-up is a core concern in the econometrics literature.
+%The relationship between treatment effects and treatment take-up is a core concern in the econometrics literature.
 In principle, the Marginal Treatment Effect (MTE) approach allows researchers to use observational data and a single excluded instrument to study this relationship.
@@
 
-We apply this approach to an important and understudied context: pawnshop lending. 
-Pawn loans constitute one of the oldest and most prevalent forms of borrowing \citep{carter2012pawnshops}.
-Our partner lender, for example, made over 4 million loans to more than a million clients during the past three years.\footnote{For comparison, there were 2.3 million microfinance clients in Mexico in 2009 \citep{Pedroza:2010}.}
-The question of choice versus paternalism is particularly salient in this context, as choice mistakes could arise from borrowers' low education and the fact that they typically borrow for emergencies under significant stress.\footnote{A large literature shows  stress impairs cognitive function, e.g.
-\cite{StressReview}.}
-%\footnote{There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues (in China it is a \$43 billion industry).
-\url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.}
 Our experiment covers just under 5,000 pawnshop clients in 6 of our partner lender's Mexico City branches.
-Our control arm illustrates the costs of the status quo contract: fully \emph{44\%} of borrowers default, losing lose their pawn along with any payments made towards principal.\footnote{High pawn default rates are common, in the US they oscillate around 15\% (see \href{https://tinyurl.com/yc2x5bjf}{here}).} Our ``commitment choice'' arm gives borrowers the chance to opt into a structured repayment contract when taking a loan.
+Our control arm illustrates the costs of the status quo contract: fully \emph{44\%} of borrowers default, losing lose their pawn along with any payments made towards principal, \hl{XX\%} of those made payments toward recovery.\footnote{High pawn default rates are common, in the US they oscillate around 15\% (see \href{https://tinyurl.com/yc2x5bjf}{here}).} Our ``commitment choice'' arm gives borrowers the chance to opt into a structured repayment contract when taking a loan.
 The structured contract requires borrowers to make three monthly payments rather than one balloon payment at the end, with each monthly payment including the accrued interest at that time as well as a nominal fee of 2\% of that month's payment if the payment is delinquent.
-The fee serves as a reminder and a means of reinforcing the importance of these interim payments.
 In our ``forced commitment'' arm all borrowers are \emph{required} to repay using the same structured monthly contract offered on an opt-in basis in the commitment choice arm.
-
-%The combination of voluntary and forced commitment within the RCT allows us to address several key questions. 
-We address three key questions.
+We use the labels commitment and structured payment contract interchangeably.
+
+This design allows us to measure the effects of structured payments, and also the demand for this contractual feature.
+We demonstrate that it allows us to estimate (under minimal assumptions) the relationship between treatment effects and treatment take-up, a core concern in the econometrics literature.
+Intuitively, our design can be seen as a two-sided encouragement design, encouraging some borrowers to take and others to not take up structured repayment.
+In principle, the marginal treatment effect approach allows researchers to use observational data and an excluded instrument to study the relationship between treatment effects and treatment take-up.
+In practice, unless the instrument has a rich support set, additional modeling assumptions \citep{mogstad2018using} are needed.
+BDM mechanisms incentivizing choice prior to treatment assignment \citep{becker1964measuring} could be used to tackle this question, with some limitations \citep{bohm1997eliciting,banerji2014detection}.
+Finally, two-stage designs in the spirit of \cite{KarlanZinman2009} have been used to study related questions \citep{Beaman2023}.
+Below we compare our novel one-stage design with two-stage ones.
+
+%We address three key questions.
 First, do structured repayment contracts lower financial costs for pawnshop borrowers?
@@
 This design can be viewed as a juxtaposition of \emph{two} randomized encouragement designs, each with one-sided non-compliance.
-One of them point identifies the effect of commitment for borrowers who would \emph{voluntarily} choose commitment (TOT),
-while the other point identifies the effect of commitment for borrowers who would \emph{not} (TUT).
+One of them point identifies the effect of commitment for borrowers who would \emph{voluntarily} choose commitment (TOT), while the other point identifies the effect of commitment for borrowers who would \emph{not} (TUT).
 By identifying both the TOT and TUT effects in the same experiment, the controlled choice design allows us to examine the empirical relevance of ``selection on gains'' also known as Roy-type selection into treatment by estimating the ``average selection on gains'' $\text{ASG} = \text{TOT} - \text{TUT}$.
@@
 
-We find that commitment is strongly effective in lowering financial costs and preventing default in pawnshop lending: the average individual in the forced arm pays financing costs inclusive of fees that are 22\% lower than the control, and faces a probability of default that is 6.6 percentage points lower (15\% of the mean).
+Turning to results, we find that commitment is strongly effective in lowering financial costs and preventing default in pawnshop lending: the average individual in the forced arm pays financing costs inclusive of fees that are 22\% lower than the control, and faces a probability of default that is 6.6 percentage points lower (15\% of the mean).
 In terms of Annual Percentage Rates, the financial cost of borrowing falls by 11 percentage points (19\% of the mean).
@@
 Our results are qualitatively robust to deducting transport costs of visiting the branch to make interim payments along with a day of lost wages for each visit.
-They are also robust to using borrowers' \emph{subjective} values of their pawns rather than the appraised value of the gold, and to adjusting for lost liquidity from requiring monthly payments.
-The monthly payment contract seems to achieve these cost savings by speeding up payments and by generating an early bifurcation of borrowers into those that will recover the pawn and those that will not.
+They are also robust to using borrowers' subjective values of their pawns rather than the appraised value of the gold, and to adjusting for lost liquidity from requiring monthly payments.
+Having said this, we don't have comprehensive measures of welfare and refrain from making welfare statements from the start.
+We focus exclusively on the cost of loan servicing, an important outcome.
+
+On mechanisms, the monthly payment contract seems to achieve these cost savings by speeding up payments and, interestingly, by generating an early \textit{bifurcation} of borrowers into those that will recover the pawn and those that will not.
 The former are induced to pay faster, saving on interest; the latter pay less towards loans that ultimately default, hence losing less money when they do.
+One interpretation is that requiring payments earlier accelerates learning about the feasibility of making such payments, thus reducing overconfidence, a mechanism not discussed much in the literature.
 
@@
 This approach imposes no assumptions beyond the experimental randomization.
-We find that \textit{at least} 23\% of borrowers benefit from commitment.
-This implies that there must be many borrowers in the choice arm who did not demand commitment despite their \emph{individual treatment effect} from (forced) commitment being positive.
-Next, we impose an exclusion restriction positing that the effect of a given contract does not depend on \emph{how} borrowers obtain it.
+We find that \textit{at least} 23\% of borrowers benefit from the structured payments contract.
+This implies that there must be many borrowers in the choice arm who did not demand this feature despite their \emph{individual treatment effect} from (forced) commitment being positive.
+
+Next, we impose a mild exclusion restriction positing that the effect of a given contract does not depend on \emph{how} borrowers obtain it.
 In other words, we assume that choosing a contract results in the same potential outcome as being assigned that contract.
@@
 On average, the borrowers who would \textit{not} choose commitment, would have faced substantially lower financial costs if they had.
-Finally, we combine our experimental treatment and outcome data with survey responses collected for a subset of borrowers to estimate conditional average treatment effects, both TUTs and ATE, using the Causal Random Forest algorithm of \cite{atheygrf}.
-We estimate positive conditional average TUT effects for 93\% of the borrowers who did \textit{not} choose the commitment contract.
+
+In a one-shot interaction, the game between the borrower and the lender is zero-sum.
+Decreasing financial costs for the borrower means decreasing the lender's profit.
+However, we find that experiencing the structured payments contract leads to a 6 percentage point increase in repeat borrowing from the lender.
+A back-of-the-envelope calculation shows that still, the contract reduces lender's profits by \hl{XX\%}, implying that lenders would not offer this contract (as was the case in Mexican pawnshops) if not forced in our context.\footnote{Our partner lender contacted us to evaluate structured payments for two reasons.
+First, they genuinely wanted to know the causal effects of structured payments but did not know how to estimate them rigorously.
+Second, our lender operates as a non-profit, donating their earnings to philanthropic aims.}
+
+Our results raise two natural questions.
+First, in terms of regulatory policy, to what extent can we predict treatment effects and use those predictions to target frequent payment contracts?
+Second, why do borrowers seem to be leaving money on the table?
+
+To address the first question, we combine our experimental treatment and outcome data with survey responses collected for a subset of borrowers to estimate conditional average treatment effects, both TUTs and ATE, using the Causal Random Forest algorithm of \cite{atheygrf}.
+This requires that we impose the exclusion restriction not just on average, but at the level of individual borrowers, allowing us to make more precise personalized statements.
+Importantly, we estimate positive conditional average TUT effects for 93\% of the borrowers who did \textit{not} choose the structured payment contract.
 In short, it is extremely difficult to find identifiable groups of borrowers who are \emph{harmed} by commitment, even when restricting attention to those who would not choose it voluntarily. 
 %while only 37\% of those who chose commitment have negative conditional TOT effects.
-While targeting commitment products to those that benefit the most is a policy that appears attractive, in this context we find that the usable targeting variables have relatively weak predictive power and hence even our best random forest targeting only reduces the overall mis-targeting rate from 9.7\% (all to Forcing) to 9.5\% (our best-case feasible targeting mechanism).
-
-What explains the persistence of no-commitment contracts so contrary to borrowers’ interests in the real world?
-From the demand side, while a simple measure of time inconsistency does not explain the large and positive TUT effect, we show substantial levels of over-optimism among borrowers.
+While targeting commitment products to those that benefit the most is a policy that appears attractive, in our context we find that the usable targeting variables have relatively weak predictive power and hence even our best random forest targeting only reduces the overall mis-targeting rate from 9.7\% (all to Forcing) to 9.5\% (our best-case feasible targeting mechanism).
+
+On the question of what explains the persistence of no-commitment contracts so contrary to borrowers’ interests, there are several candidates.
+From the demand side, while a simple measure of time inconsistency does not explain the large and positive TUT effect, we show substantial levels of over-optimism among borrowers, the average subjective probability of recovering their pawn is \hl{XX\%}, while the actual average is only \hl{XX\%}.
 Among borrowers who do not choose commitment, those with the largest estimated benefits from commitment are the individuals who most systematically over-estimate their own probability of repayment without the need to commit, potentially decreasing their demand from commitment.
-From the supply side, because borrowers' financial savings come directly from the pockets of lenders, pawnshops have an interest in retaining the no-commitment contract.
-Indeed, pawnshop lending presents an inverted lending case: since these loans are over-collateralized, the lender in the contract stands to gain the most when borrowers default.
-Our partner's \emph{status quo} pawn contract gave 70\% of the value of gold collateral in credit, and charged a monthly interest rate of 7\% for loans of a three-month duration, with a flexible no-reminders contract, that could be paid back anytime before the loan comes due at no penalty.
-This contract is standard contract in the industry.
-This combination of features, and the fact that the gold pawn is highly liquid, means that the lender makes 90\% more profit over three months from a borrower who defaults than one who repays (30\% of collateral value recovered under default, 15.8\% of collateral value paid in interest if loan fully repaid).
+From the supply side, because loans are over-collateralized, the lender in the contract stands to gain the most when borrowers default.
+Our partner's \emph{status quo} pawn contract (standard in the industry) gave 70\% of the value of gold collateral in credit, and charged a monthly interest rate of 7\% for loans of a three-month duration, with a flexible no-reminders contract, that could be paid back anytime before the loan comes due at no penalty.
+The fact that the gold pawn is highly liquid, means that the lender makes more profit over three months from a borrower who defaults than one who repays (30\% of collateral value recovered under default, 15.8\% of collateral value paid in interest if loan fully repaid).
 While an older literature considers the exploitative potential of over-collateralization and underpriced collateral \citep{basu1984implicit}, the implication of such contracts has not been analyzed in the behavioral literature.
@@
 Our paper makes a number of contributions to the literature.
-First, we propose a way to use this three-armed experimental structure to recover treatment effects for choosers and non-choosers under minimal assumptions.\footnote{While \cite{fowlie2021default} likewise employ a three-armed experimental design in their study of the effect of electricity pricing, they identified \emph{two} TOT effects for different groups of ``treated'' households, whereas we simultaneously identify the TOT and TUT effects defined with respect to a single ``treated'' group of borrowers.
-This difference is what allows our design to point identify the ASG and related quantities.}
-A companion STATA package provides simple, regression-based estimators for each of these causal parameters, along with appropriate cluster-robust standard errors.\footnote{See \autoref{sec:estimation_inference} for details.}
-The controlled choice design could be useful in other experimental settings where the question of interest centers on the merits of paternalism, public or private, or the relationship between choice and treatment effects.
-One obvious example is the design of other financial contracts beyond pawn loans.
-Another is education, where teachers typically mandate quizzes, homework, and other commitment mechanisms to mitigate student procrastination \citep{Ariely}.
-We further contribute to a relatively small existing literature that sheds light on private paternalism.
-In the context of food choice, \cite{Sprenger} show that individuals with the most time-inconsistent preferences are actually least likely to demand commitment.
-In contrast to their paper, we directly identify the TUT, obviating the need to first elicit preferences before testing for negative selection.
+First, %we propose a way to use three-armed experimental structure to recover treatment effects for choosers and non-choosers under minimal assumptions.\footnote{A companion STATA package provides simple, regression-based estimators for each of these causal parameters, along with appropriate cluster-robust standard errors.
+See \autoref{sec:estimation_inference} for details.}
+to a relatively small literature that sheds light on private paternalism and selection on gains.
+In the context of food choice, in an very creative paper \cite{Sprenger} show that individuals with the most time-inconsistent preferences are actually least likely to demand commitment.
+In contrast, we directly identify the TUT, obviating the need to first elicit preferences before testing for negative selection.
 In the context of school choice, \cite{Walters} combines a distance instrument with additional structural assumptions, obtaining model-based TUT and ATE estimates.
 He finds that students who select into more effective schools have smaller treatment effects from attending than those who do not select in.
-In contrast, our approach point identifies TUT and TOT and a range of other interesting causal parameters without the need for a structural model, relying instead on relatively weak exclusion restrictions whose testable implications we fail to reject.
+Our approach instead point identifies TUT and TOT and a range of other interesting causal parameters without the need for a structural model, relying instead on relatively weak exclusion restrictions whose testable implications we fail to reject.
+In the context of agriculture, \cite{Beaman2023} compare the average treatment effect on farm profits from providing \textit{cash grants} to a set of farmers that did not select into getting \textit{loans} to those of average farmers.
+They do this in a two-stage design, by first offering loans or not to a set of farmers, and then randomizing cash grants among those who would not have received loans.
+Our paper is complementary in several respects.
+Because we estimate the average effect of a given treatment for those who did and did not select into that \textit{same} treatment, our design allows us to estimate effects on non-compliers, but on compliers as well, allowing the estimation of selection on gains, selection bias and selection on levels.
+\cite{Beaman2023} find that those selecting out of loans have lower average returns to capital, consistent with positive selection.
+In contrast, we find no evidence of positive selection.
+Our design could be used in situations where two-stage randomization is not feasible or too costly.\footnote{\cite{fowlie2021default} likewise employ a three-armed experimental design in their study of the effect of electricity pricing, they identified \emph{two} TOT effects for different groups of ``treated'' households, whereas we simultaneously identify the TOT and TUT effects defined with respect to a single ``treated'' group of borrowers.
+This difference is what allows our design to point identify the ASG and related quantities.}
 
@@
 Our study also speaks to recent research on the effects of payment frequency.
-While experiments in microfinance markets have \textit{not} shown the same benefits from providing a more regularized repayment environment as we find here \citep{Pande, barboni2023flexible}, these experiments differ from ours in two important ways: they are performed on top of already highly structured micro-finance contracts, and they involve borrower pools who may have selected into that type of lending precisely because it provides structure \cite{bauer2012behavioral}.
+While experiments in microfinance markets have \textit{not} not found benefits from providing a more regularized repayment environment as we find here \citep{Pande, barboni2023flexible, Field}, these experiments differ from ours in two important ways: they are performed on top of already highly structured micro-finance contracts, and they involve borrower pools who may have selected into that type of lending precisely because it provides structure \cite{bauer2012behavioral}.
 These differences may explain why \citep{Pande} finds almost no default in the control group, in stark contrast to our setting of high default.
-Second, we provide a deeper analysis of \textit{both} take-up and the efficacy of voluntary commitment mechanisms.
+Second, we study \textit{both} take-up and the efficacy of voluntary commitment mechanisms.
 A number of papers have found low demand for commitment as we do.\footnote{\cite{Ashraf}, \cite{Gine}, \cite{Ted}, \cite{Royer}, \cite{Sprenger}.
 Others have found more robust demand for commitment (\cite{Kremer},  \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}, \cite{Pascaline}).} Unlike all of these papers, however, we separately point-identify and estimate the effects of commitment for borrowers who would and \textit{would not} choose it.
-This allows us to conduct a more rigorous and nuanced analysis of private paternalism.
 
@@
 Further, the `nudge’ approach generally favored by the behavioral literature (voluntary commitment) does not generate adequate demand in this context.
+
+Given their enormous prevalence and the vulnerability of their users, pawn loans are severely understudied; we believe the descriptive information and treatment effects estimates for pawn borrowing are an important contribution.
+We also believe that the forcing-choice RCT design provides a useful counterpoint to the widely used \cite{KarlanZinman2009} (KZ) designs.
+As far as we are aware, ours is the only experimental design in the literature simultaneously estimating both the TOT and TUT effects, along with the average selection on gains, without the need for auxiliary structural assumptions.
+Note that KZ designs do not estimate the TUT effect, which is crucial for evaluating the case for paternalism.\footnote{The KZ design is useful for separating moral hazard from adverse selection when a two-product comparison is relevant, with one being strictly preferable to consumers.
+Our design is useful in mapping marginal treatment effects to compliance with a single treatment, particularly in contexts where a) forcing is possible and b) selection subsequent to forcing is low, or is of direct interest to the principal (in that case, our design would still provide useful information to the principal but would not isolate agent-level heterogeneity in the way it does here).}
 
@@
 
-\section{Context} \label{context}
+\section{Context and stylized facts} \label{context}
 
@@
 The borrower signs a 2-page contract with the conditions of the loan and leaves with the cash.
+Appraisers were paid a flat monthly wage.
 
@@
 
+\subsection{Stylized facts}
+
 %\hfill \newline
 %\noindent \textbf{Borrowers.} 
-\paragraph*{Borrowers} The clients that pawned understood these terms well (as we verified in interviews).\footnote{87\% of clients report in our survey that they have pawned before.} These clients have little or no access to other types of loans and they value the convenience of pawn borrowing.
-This population of pawn borrowers is economically vulnerable:  30\% of them could not pay either water, electricity \& gas or rent in the past 6 months; 89\% said they are pawning because of an emergency, and only 12\% stated it was to use in a ``non-urgent expense''.
+\paragraph*{Borrowers.} Borrowers are not completely inexperienced: 87\% of clients in our survey report they have pawned before.
+%These clients have little or no access to other types of loans and they value the convenience of pawn borrowing.
+However they are economically vulnerable:  30\% of them could not pay either water, electricity \& gas or rent in the past 6 months.
+In terms of triggers and uses of the loan, 89\% said they are pawning because of an emergency, and only 12\% stated it was to be used in a ``non-urgent expense''.
 When asked why they are pawning this piece, 5\% responded ``lost a family member'', ``a medical emergency'' (11\%), or ``an urgent expense'' (72\%).
+Only \hl{XX\%} of borrowers have completed college, 73\% of are women, with an average age of 43 years.
 
@@
 One potential explanation for high default is that clients are really just knowingly selling their gold piece through a pawn contract on which they intend to default.
-This appears unlikely for several reasons: (a) clients can easily sell the gold and obtain a higher amount of instant cash at gold-buying stores located close to almost all our pawnshop branches,
+This appears unlikely for several reasons: clients can easily sell the gold and obtain a higher amount of instant cash at gold-buying stores located close to almost all our pawnshop branches;
 %(see Figure \ref{GoldBuyers}) 
-(b) the reported subjective value of the pawn is larger than the appraised value for 83\% of clients, (c) among those that lose their pawn, 29\% paid a positive amount towards its recovery and on average paid 42\% of the value of their loan (see Figure \ref{proxy_naive} in Appendix) --- this can only be rationalized if they expected to recover their pawn, and (d) 72\% of borrowers report a 100\% probability of repaying their loan (and 98\% at least a 50\% chance of repaying) in our baseline survey at the time they take the loan.
+the reported subjective value of the pawn is larger than the appraised value for 83\% of clients (this also means it is inefficient that they lose their pawns).
+The default rates for the experimental period and branches is similar to that observed for all branches in subsequent periods (see Figure \ref{external_validity}).
+
+\paragraph*{Gold buying shops.} Gold purchasing shops locate close to our Lender's branches. Branches have an average of \hl{XX} of these shops.
+
+\paragraph*{Paying without recovering.} Among those that lose their pawn, 29\% paid a positive amount towards its recovery, and on average paid 42\% of the value of their loan (see Figure \ref{proxy_naive} in Appendix) --- this can only be rationalized if they expected to recover their pawn.
+
+\paragraph*{Overconfidence.} We implemented a baseline survey to \hl{more than 10,000} respondents.
+In it, we asked borrowers for their subjective probability of recovering the pawn.
+The average recovery probability is \hl{XX\%}.
+This contrasts sharply with the actual recovery rate for these same borrowers, \hl{57\%}.
+Overall 72\% of borrowers report a 100\% probability of repaying their loan.
 %Note that high default could be detrimental from the lender's point of view, since it may reduce the likelihood that the client becomes a return customer.
@@
 Borrowers' financial costs are composed of two main categories: the cost of losing their collateral, and the interest and fees incurred during the life of the loan.
-For each given loan we observe if the client lost her pawn ($\mathds{1}(\text{Default}_i)$).
+For each given loan we observe if the client lost her pawn, $\mathds{1}(\text{Default}_i)$.
 If a loan has been rolled over and is still outstanding, we consider it to be non-defaulted.
@@
 censored) when the data period ends.
-Regarding interest, our administrative data classifies payments made in three types according to their payment allocation rules: payments to principal $P^C$, payments on generated interests $P^I$, and payments on penalty fees $P^F$.
+Regarding interest, our administrative data classifies payments made into three types according to their payment allocation rules: payments to principal $P^C$, payments on generated interests $P^I$, and payments on penalty fees $P^F$.
 We observe each and every payment made under each category, its amount and date.
 
-We define a borrower's financial cost as the total monetary outflow --in cash or pawn value-- from the borrower to the lender.
+We define a borrower's financial cost as the total monetary outflow---in cash or pawn value---from the borrower to the lender.
 This includes all payments the borrower made toward interest and fees, but also the net difference between the appraised value of the pawn and the loan amount (Value-Loan) in the event of default.
@@
 
-\section{Experimental Design} \label{Design}
+\vspace{.2in}
+\section{Experiment and Data} \label{Design}
 
@@
 %\noindent \textbf{The Commitment Contract.} 
-\paragraph*{The Commitment Contract} For the purpose of the experiment we designed a new contract that is identical to the status quo contract except that, informed by the design of micro-lending contracts, it enhances the regularity and salience of payments as a way to encourage repayment \citep{morduch1999microfinance, bauer2012behavioral}.
+\paragraph*{The Commitment contract} For the purpose of the experiment we designed a new contract that is identical to the status quo contract except that, informed by the design of micro-lending contracts, it enhances the regularity and salience of payments as a way to encourage repayment \citep{morduch1999microfinance, bauer2012behavioral}.
 It has the same interest rate (7\% \textit{per month}) which accumulates daily on outstanding debt, the same loan size/collateral ratio (70\%), and the same loan term (90 days, and a grace period of 15 days).
@@
 To elicit demand for the monthly payment contract, we include an arm that allows borrowers to opt into this contract if they choose.
-The existence of both a non-optional ``forcing'' arm, and a choice arm in our design is key to estimating a battery of treatment effects above an average treatment effect under fairly mild assumptions.
+The existence of both a non-optional ``forcing'' arm, and a choice arm in our design is key to estimating a battery of treatment effects under fairly mild assumptions.
 We next describe the three experimental arms in more detail.
@@
     \item \textit{Control} arm: consisted of branch-days offering the status quo contract described in Section \ref{context}, and only this contract. 
-    \item \textit{Forced Commitment} arm: consisted of branch-days requiring all borrowers to use the Commitment contract described above.  
-    \item \textit{Commitment Choice} arm: consisted of branch-days offering the client \textit{a choice} between the Commitment contract, and the status quo contract.
+    \item \textit{Forced structured payments} arm: consisted of branch-days requiring all borrowers to use the Commitment contract described above.  
+    \item \textit{Structured payments Choice} arm: consisted of branch-days offering the client \textit{a choice} between the structured payments contract, and the status quo contract.
     %\item \textit{Forced Soft Commitment} arm: consisted of branch-days in which borrowers were asked to sign a non-binding written commitment to pay monthly as in the Commitment contract, but no reminders or fees were imposed if they did not.\footnote{The client was made to sign a paper which said ``I promise to pay every month the corresponding sum of \_\_\_\_\_\_, on the dates \_\_\_\_\_\_, \_\_\_\_\_\_, and \_\_\_\_\_\_.
@@
 We did not allocate an equal number of days across arms, since we were interested in having more power in some of them.
-The number of branch days allocated to each were 84 to control, 80 to forced commitment, and 93 to choice.
+The number of branch days allocated to each were 84 to control, 80 to forced structured payments, and 93 to choice.
 See Figure \ref{exp_description} for a CONSORT-style diagram of the study design and recruitment.
+
+\vspace{.2in}
 
@@
 The administrative data contains a unique identifier for each client, an identifier for the piece she is pawning, and the transactions relating to that piece.
-These transactions include the value of the item as assessed by the appraiser, the amount of money loaned (70\% of the item's value), the date of the pawn transaction, and the type of contract for that pawn: commitment or status quo.
+These transactions include the value of the item as assessed by the appraiser, the amount of money loaned (70\% of the item's value), the date of the pawn transaction, and the type of contract for that pawn: structured payments or status quo.
 Within the period of the loan, we followed each transaction related to that piece in the administrative data: when payments were made and for what amounts, whether there was default (i.e.\ the client lost her pawn), and whether any late-payment fees were imposed.
@@
 %\noindent \textbf{Survey data.} 
-\paragraph*{Survey Data} An additional team of enumerators stationed in each branch asked clients to complete a 5-minute survey \textit{before} going to the teller window to appraise their piece and before they learned which contracts would be available on that day.
-The survey was intentionally short to avoid discouraging the potential clients from pawning.
+\paragraph*{Survey Data} An additional team of enumerators was stationed at the entrance of each branch; they asked clients to complete a 5-minute survey before going to the teller window to appraise their piece and \textit{before} they learned which contracts would be available on that day.
+The survey allows us to measure loan takeup since we know whether people entered the branch, completed the survey, and then, after learning the contract terms, decided not to pawn.
+As we will see, this is extremely infrequent; only about 2\% of borrowers did that.
+This is not very surprising, borrowers come determined to borrow, many of them to solve an emergency, and are not very sensitive to contract terms (that may explain why they accept high interest rates and over-collateralization in the first place).
+The survey was intentionally brief.
 It measured demographics, proxies for income/wealth, education, present-biased preferences, experience pawning, if family or friends commonly asked for money, how time-consuming and costly it was to come to the branch, the subjective probability of recovering the piece that they intended to pawn, the subjective value of their piece in money terms (how much money they would sell it for), among others.
-We surveyed 7,210 clients, and our survey response rate was 78\% among clients who took loans.
+We surveyed 7,210 clients.
+%, and our survey response rate was 78\% among clients who took loans.
 %\footnote{We also surveyed clients before and after the experiment, so our survey covers a larger sample that we are not using in this paper.}.
@@
 
-\subsection{Experimental Integrity}
+\subsection{No differential selection and balance}
 \label{sec:integrity}
@@
 %\noindent \textbf{Attrition.}
-\paragraph*{Attrition} There are two main channels through which attrition could complicate the interpretation of our results.
+
+We were aware that the major threat for this study was selection into borrowing based on contract terms.
+This did \textit{not} happen.
+We show this in three different ways.
+First, out of those coming into the branch and filling out the baseline survey, \hl{97\%} end up pawning.
+This rate is not only high but is also not different across treatment arms.
+Second, the number of loans per day is not different across arms, showing borrowers did not stop pawning when the forcing arm or choice arm was active.
+Third, borrower and loan characteristics are the same across arms, showing that there is no selection on observables.\footnote{Note that is borrowers self-selected based on contract terms, the results would still reflect the overall impact of a treatment for the lender's portfolio.
+In our case, there is no selection, so we can study the causal effects on borrowers.}
+
+An important implementation detail is that appraisers were paid a flat wage, independent of how many contracts or which types of contracts borrowers signed.
+They therefore had no incentive to influence borrower choice.
+Consistent with this, adding or removing appraiser fixed effects leaves results unchanged.
+%We should also recall that the lender's management team initiated this research collaboration and genuinely wanted to rigorously measure the effects of a structured payment contract.
+Our lender is a non-profit and donates all profits to philanthropy.
+They had no profit incentive to sway the results either way and could not do it anyway as researchers designed, implemented, and analyzed the data without intervention from the lender.
+
+Table \ref{attrition_table_final} shows there are no differences in the number of loans, borrowers, or amount borrowed across arms using administrative data.
+Each row corresponds to a regression of the dependent variable on indicators for treatment assignment (status quo/control, forced commitment, choice).
+In the first row (``Take-up'') we use the sample of those who answered the baseline survey (\hl{XXX} subjects) and check which of them pawned based on the administrative data.
+The dependent variable indicates whether the person pawned.
+Because this survey was implemented at the entrance of the branch before they knew their treatment assignment, it is a good measure of take-up.
+The first result is that the overwhelming majority (97\%) take the loan.
+Second, the same fraction of borrowers take up the loan across treatment arms.
+This is strong evidence that borrowers did not select deferentially according to the structured payments contractual feature.
+The remaining rows use only administrative data.
+For each branch day, we calculate the number of borrowers pawning, the number of pawns used, pawns per borrower, and the total amount borrowed and regress each of those on treatment arms.
+We again cannot reject that any of those measures of demand are the same across arms.
+We also report medians to reduce the influence of outliers.
+
+\begin{table}[H]
+\caption{No selection across arms}
+\label{attrition_table_final}
+\begin{center}
+\footnotesize{\input{./Tables/Attrition.tex}}
+\end{center}
+\scriptsize{Each row in this table 
+ corresponds to a regression \hl{at the branch-day level} of each dependent variable against the experimental arms indicators (control, forced commitment, choice).
+The table reports the coefficients on each of these indicators, as well as the p-value of an F-test of the null hypothesis of equality of the three coefficients.
+We also report \hl{raw medians} for each arm.
+\hl{ISAAC, could add not just pesos per loan, but real total lent per branch-day?} %Figure \ref{boxplot_attrition}, in the appendix shows a box-plot of the first two variables, showing the distribution across arms is balanced.
+ }
+%\textit{Do file: } \texttt{ss\_att.do}
+\end{table}
+
+%\paragraph*{Attrition} There are two main channels through which attrition could complicate the interpretation of our results.
 The first, and more serious, is the possibility that clients might change their pawning decisions in response to the treatment they encounter in a given branch on the day they enter the branch.
@@
 
-If the treatments had induced demand-side selection, we would expect to see that the number of pawns successfully conducted differ in a systematic way across arms.
-That is, if potential borrowers disliked being forced into a commitment contract, we would expect a lower number of pawns on branch days where only the commitment contract is available compared to control days.
+%If the treatments had induced demand-side selection, we would expect to see that the number of pawns successfully conducted differ in a systematic way across arms.
+That is, if potential borrowers disliked being forced into a structured payments contract, we would expect a lower number of pawns on branch days where only the structured payments contract is available compared to control days.
 Table \ref{attrition_table} shows that this is not the case.
-There is no difference at all between the Control and Forced Commitment arm in terms of the number of pawns per branch-day.
+There is no difference at all between the Control and Forced structured payments arm in terms of the number of pawns per branch-day.
 %Although we cannot reject equality across the three arms (p-value=0.21), the Choice arm appears to have a somewhat larger number of borrowers than the Control and Forced arms.\footnote{p-value=0.23 and 0.12 respectively.} This seems to be due to sampling variability.
@@
 Therefore it appears that the treatments have not induced any endogenous shifts in the composition of borrowers.
-This is consistent with the findings of Table \ref{SS}.
+%This is consistent with the findings of Table \ref{SS}.
 
@@
 
-A more subtle form of sample selection could arise if the treatments induce borrowers to re-pawn in different ways, especially given that their treatment status on subsequent loan/days may not be the same as that initially assigned.
+%A more subtle form of sample selection could arise if the treatments induce borrowers to re-pawn in different ways, especially given that their treatment status on subsequent loan/days may not be the same as that initially assigned.
 To address this issue our analysis uses only the first loan taken by each borrower during the experimental window.
@@
 %\noindent \textbf{Balance.} 
-\paragraph*{Balance} Table \ref{SS} presents summary statistics for the sample of actual borrowers across arms, showing that our randomization succeeded in achieving balance across the experimental arms.
-Panel A uses administrative data for the universe of borrowers in each arm, and shows that loan balances and the days on the week on which individuals pawned are comparable across arms.
+%\paragraph*{Balance}
+
+Table \ref{SS_final} presents summary statistics for the sample of actual borrowers across arms, showing that our randomization succeeded in achieving balance across the experimental arms.
+%Panel A uses administrative data for the universe of borrowers in each arm, and shows that loan balances and the days on the week on which individuals pawned are comparable across arms.
 The average loan size is \$2267 MXN (\$130 USD).
 Panel B of Table \ref{SS} reports summary statistics across arms from our survey data.
-Among the 78\% of borrowers who completed our survey, 73\% of clients are women, the average age is 43 years, 66\% have completed at least a high school education, and 87\% have pawned before, suggesting that our sample largely consists of experienced borrowers.
-Finally, borrowers' subjective probability of recovering their pawn is close to 92\% on average, in stark contrast to the \emph{actual} recovery rate of 43\%; borrowers are highly overconfident on average.
+%Among the 78\% of borrowers who completed our survey, 
+73\% of surveyed borrrowers are women, the average age is 43 years, 66\% have completed at least a high school education, and 87\% have pawned before.
+Finally, borrowers' subjective probability of recovering their pawn is close to 92\%.
 The average subjective value they report for the items they pawn is 4084 MXN, much larger than the average appraised gold value of 3238 MXN.
-While this could arise either from overconfidence in valuation or from undervaluation by the lender, in any case it is \textit{prima facie} evidence that loss of the pawn should be undesirable relative to the quantity of liquidity leveraged by the asset.
+%While this could arise either from overconfidence in valuation or from undervaluation by the lender, in any case it is \textit{prima facie} evidence that loss of the pawn should be undesirable relative to the quantity of liquidity leveraged by the asset.
+Importantly, all borrower's characteristics are balanced across arms, again consistent with no differential selection across arms.
+Tables \ref{attrition_table_final} and Table \ref{SS_final}  tests are the standard experimental integrity analysis.
+Together they constitute strong evidence of no borrower selection across arms.
+This was reinforced by reports from our enumerators and appraisers that those who entered the branch were determined to borrow and that there were no complaints about what loan contracts were available.
+Note that this does not mean that they did not care about contract terms, just that the outside option of leaving the branch without a loans seems less attractive.
+
+\begin{table}[H]
+\caption{Borrower's characteristics are balanced}
+\label{SS_final}
+\begin{center}
+\resizebox{0.65\textwidth}{!}{
+\footnotesize{\input{./Tables/SS.tex}}
+}
+\end{center}
+\scriptsize {Each row in this table corresponds to a regression, where the level of observation is a \hl{borrower that pawned} which we surveyed.
+\hl{Surveys were not conducted at the beginning of the experiment}.
+The dependent variables are displayed in the first column.
+Each dependent variable is regressed against the experimental arms indicators (control, forced commitment, choice).
+The table reports the coefficients on each of these indicators, as well as the p-value an F-test of the null hypothesis of equality of the three coefficients.
+``Subjective value'' of the pawn refers to how much would the client be willing to sell the pawn for in pesos, ``Trouble paying bills'' is an indicator for the borrower reporting having problems paying electricity, water and services in the last 6-months, present bias is constructed as in \cite{Ashraf}; ``Makes buget'' os an indicator for whether the household make expenses budget for the month ahead of time.
+The subjective probability of recovery was elicited a la Manski (from 0 to 100 what is the probability that you will recoup your pawn); pawned before is a dummy=1 if the client declares to have pawned before (although not necessarily with Lender $P$); age is age of the borrower in years, +High-school is a dummy that indicates if the client has completed high school.
+}
+%\textit{Do file: } \texttt{ss\_balance.do}
+\end{table}
 
@@
 
-We begin by estimating average treatment effects of assignment to the Forced commitment and the Choice arms, relative to those assigned to the Control arm.
-As we explain below, only about 11\% of those in the choice arm chose the monthly payment option (Figure \ref{determinants_choose} shows coefficient plots for the characteristics that determine choosing commitment in the Choice arm).
+We begin by estimating average treatment effects of assignment to the Forced structured payments and the Choice arms, relative to those assigned to the Control arm.
+As we explain below, only about 11\% of those in the choice arm chose the monthly payment option (Figure \ref{determinants_choose} shows coefficient plots for the characteristics that determine choosing structured payments in the Choice arm).
 
@@
 \end{equation}
-where $i$ indexes client, $j$ indexes branch, $T_{i}^F$ and $T_{i}^C$ are indicator variables for receiving the Forced or Choice arms, $X_{ij}$ are branch and day-of-week fixed effects.
-Standard errors are clustered at the branch-day level, the unit of treatment assignment\footnote{A minority of clients pawned on more than one day during the experiment: 14\% pawned on two distinct days, and 8\% on three or more days.
-To avoid contamination from earlier treatments to which these individuals were exposed, we restrict our sample to each client's \emph{first visit}.
-Note that a client may pawn multiple items her first visit.
+where $i$ indexes the borrower, $j$ indexes branch, $T_{i}^F$ and $T_{i}^C$ are indicator variables for receiving the Forced or Choice arms, $X_{ij}$ are branch and day-of-week fixed effects.
+Standard errors are clustered at the branch-day level, the unit of treatment assignment\footnote{A minority of borrowers pawned on more than one day during the experiment: 14\% pawned on two distinct days, and 8\% on three or more days.
+To avoid contamination from earlier treatments to which these individuals were exposed, we restrict our sample to each borrower's \emph{first visit}.
+Note that a borrower may pawn multiple items her first visit.
 We include these as separate observations.
-Because our standard errors are clustered at the branch-day level, they automatically account for any dependence in error terms arising from multiple pawns by the same client on her first visit.}.
+Because our standard errors are clustered at the branch-day level, they automatically account for any dependence in error terms arising from multiple pawns by the same borrower on her first visit.}.
 Given full compliance in the Forced arm, the coefficient $\beta^F$ is the ATE of forced commitment while $\beta^C$ is the ITT of commitment in the Choice arm on the outcome variable $y_{ij}$.
@@
 Our two primary outcome variables are financial cost in pesos and Annual Percentage Rate (APR), as defined in Section \ref{costs}.
+
 Results for these outcomes appear in columns (1) and (7) of Table \ref{main_impact_table}.
@@
 \end{center}
-\footnotesize{This table shows the treatment effects for our core pecuniary outcomes.
+\scriptsize{This table shows the treatment effects for our core pecuniary outcomes.
 Each column is a different regression for different outcomes on an indicator for the forced and choice arms, following specification in equation \ref{basic_reg}.
@@
 %\noindent \textbf{Intermediate outcomes.} 
-\paragraph*{Intermediate Outcomes} To shed light on the mechanisms behind the ATEs discussed above, Table \ref{mechanisms} shows how commitment affects a number of intermediate outcomes.
+\paragraph*{Payment speed} To shed light on the mechanisms behind the ATEs discussed above, Table \ref{mechanisms} shows how commitment affects a number of intermediate outcomes.
 One can group the types of intermediate outcomes into two categories: measures of the speed of pawn recovery, and measures of the decision of when to default.
@@
 
-A very undesirable outcome from the borrower's perspective is to pay towards the loan without paying in full, i.e.
+\paragraph*{Payment Bifurcation} A very undesirable outcome from the borrower's perspective is to pay towards the loan without paying in full, i.e.
 defaulting on the loan while still making some payments.
@@
 %\noindent \textbf{Other costs.} 
-\paragraph*{Other Costs} We have shown that forcing borrowers to take the monthly payment contract significantly reduces their financial costs.
-Although the paper focuses on financial costs, we consider three additional costs here.
+\paragraph*{Other Costs} Although the paper focuses on financial costs, we consider three additional costs here.
 First, we include the cost of visiting the branch to make a payment.
@@
 
+We want to be very clear that we are not measuring borrower welfare, for several obvious reasons.
+For example, requiring monthly payments may well increase stress we are not taking into account.
+We are not taking into account discounting given the short period, although in Section \ref{why_paternalism}, we show that to rationalize the findings, we would need unreasonably high discount rates.
+We are also not measuring financial cost on other loan products.\footnote{However, we think it is unlikely that borrowers ask for even more expensive loans to pay the monthly payment.
+The `punishment' from the monthly fee is small, less than the transport cost to go to the branch.
+It is likely better to incur the fee than go through the process of asking for an additional loan to avoid this fee.} Having said this, a large literature focuses on the cost of servicing loans.
+We follow in the steps of this literature.
+
 %\hfill \newline
@@
 We can first ask whether the individual ever takes a loan after the initial study loan, an analysis which is simply experimental.
-\paragraph*{Repeat Pawns}
-Table \ref{repeat_loans} explores the effects of treatment on future pawning behavior.
-Column (1) shows that participants assigned to the forced arm are 6.3\% more likely to be repeat clients later.
-%Those in the choice arm are 4\% more likely to pawn again and is not statistically distinct from zero.
-While this appears to be \emph{prima facie} evidence of greater satisfaction among borrowers in the forced arm, the interpretation is complicated by the fact that monthly payments may themselves trigger more borrowing to pay them.
-This is unlikely to be the case given that the effect on re-pawning comes after 90 days (during the period of contract demanded payments) and not before  (see columns 2 and 3).
-Column 4 only considers new loans which use different collateral from that of the initial one.
-We do this to foreclose the explanation that those in the Forced arm, being more liquidity-constraint, return to pawn a second pawn to be able to pay the monthly payments of their first loan.
-However, we cannot reject a zero effect on pawning a different collateral.
-Column 5 focuses on the (endogenous) subsample of those recovering their pawn in both arms of the experiment.
-This means that \textit{both} arms have recovered their pawn and could re-pawn if they so wish, and also that the liquidity demands from the monthly contract are \textit{no longer} there as the contract has been closed.
-We find that the difference between the Forcing contract and the status quo is even larger in this subsample, with the former having 11pp higher likelihood of being a repeat client during our sample period.
-
-\begin{table}
-\caption{Effects on Repeat Pawning}
-\label{repeat_loans}
-\begin{center}
-\footnotesize{\input{./Tables/repeat_loans.tex}}
-\end{center}
- \footnotesize{This table estimates the specification of equation \ref{basic_reg} but at the level of the borrower (not the loan).
-Each column represents a regression with a different outcome variable.
- % In column 1, the dependent variable indicates, for each borrower in the experiment, whether he/she pawned again after the first loan in the experiment (up to the end period of our data set 338 days after the experiment began).
-Column 2 is analogous, but only pawning after 90 days of the first loan is considered.
-Column 3 instead considers pawning before 90 days.
-Column 4 is analogous to column 1 but focuses on the pawning of a gold piece that is different from the one in the first experimental loan.
-Column 5 is analogous to column 1, but conditioning on the sample that recovered the first loan.
- Each regression includes branch and day-of-week FE. Standard errors are clustered at the branch-day level.}
-%\textit{Do file: } \texttt{repeat\_loans.do}
-\end{table}
 
@@
 
+\paragraph{Lender outcomes} One of the questions we are interested in is whether lender profits decrease with structured payment.
+If that is the case lenders have little incentive include this feature in their contracts.
+Showed above that per loan borrowers pay less to lenders under the structured payments contract.
+But this might mean that borrowers would be more willing to come back and pawn again.
+The experiment is not designed to measure the extensive margin or competitive responses of other lenders and we will not attempt a complete analysis here.
+We perform a simple back-of-the-envelope calculation that takes into account repeat business.
+
+We first assess whether being assigned to the structured payment contract causes more clients to come back.
+Table \ref{repeat_loans} estimates that participants assigned to the forced arm are 6.3\% more likely to repeat clients later during our sample period.
+We then calculate lender's profits in two ways.
+In the first, we just sum the total payments made by borrowers first assigned to the structured payment contract.
+This mechanically takes into account repeat borrowing.
+However, it does not allow us to extrapolate for longer periods, and it does not allow us to ``assign'' borrowers to future structured payment contracts.
+Our second method does.
+We use the estimates of the borrower's financial cost (which is lenders's revenue) from column 1 of Table \ref{main_impact_table} and repeat pawning from Table \ref{repeat_loans} and plug them into equation \ref{profit_function}
+
+\begin{equation}
+\label{profit_function}
+     \text{Profit}_j = \sum_{i}\sum_{t}\left\{P_{it}^I+P_{it}^F\right\}+0.3\times \text{Value-loan}_i \times\mathds{1}(\text{Def}_i=1)
+\end{equation}
+
+where $j$ indexes a borrower, and $i$ indexes a loan.
+The outer sum is taken over all loans that originated in the first 180 days.
+The profit's formula captures all interest and fees payments made for the first two loans -  to reflect the repeat pawning behavior, and the 30\% of the collateral whenever the borrower defaults that loan.
+Column (1) in Table \ref{lenders_profit} reflect the effect of the contract type (in the first assigned treatment) on the lender's profit.
+
 \section{Choice and Heterogeneous Treatment Effects}
@@
 The borrowers who did not choose commitment could simply be those who don't need it. 
-Indeed, we find strong evidence that the effect of forced commitment varies substantially across individuals in our experiment: we test and
+Indeed, we find strong evidence that the effect of forced commitment varies substantially across individuals in our experiment: we test and reject
 %Appendix \ref{append:chernozhukov} tests and rejects 
-the null hypothesis of homogeneous treatment effects, following the methodology of \cite{chernozhukov2018generic}. (Details available upon request.)
-So the question remains: do the 89\% who do not choose commitment know something about their personal situations that we as researchers do not, or are most people in the choice arm making a costly financial mistake?
-In this section we present a series of econometric exercises that sheds light on this question, leveraging unique features of our experimental design. 
-Among other results, we show that commitment would lower average financial costs even for the subset of borrowers who choose \emph{not} to commit voluntarily.
+the null hypothesis of homogeneous treatment effects using the methodology of \cite{chernozhukov2018generic} (details available upon request).
+So the question remains: can we explain the 89\% of borrowers not choosing commitment as being those that don't benefit financially from it?  
+In this section, importantly, we show that commitment would lower average financial costs even for the subset of borrowers who choose \emph{not} to commit voluntarily.
 To simplify the exposition in this and all sections that follow, we re-define all outcome variables so that \emph{beneficial} treatment effects are \emph{positive}.
@@
 Our point estimates of $\underline{F}(0)$ and $\overline{F}(0)$ are 0.03 and 0.77 respectively, with 95\% confidence intervals of [0.025, 0.050] and [0.75, 0.80].
-Since we are interested in $\mathbbm{P}(\Delta_i >0) = 1 - F_\Delta(0)$, it follows that \textit{at least 23\%}, and at most 97\%, of individuals borrowers benefit from forced commitment.\footnote{Confidence intervals are constructed using the asymptotic distribution of $(\underline{F}, \overline{F})$.
+Since we are interested in $\mathbbm{P}(\Delta_i >0) = 1 - F_\Delta(0)$, it follows that \textit{at least 23\%}, and at most 97\%, of individuals borrowers benefit from forced commitment.%\footnote{Confidence intervals are constructed using the asymptotic distribution of $(\underline{F}, \overline{F})$.
 See \cite{fan2010sharp}.}
-These bounds allow all possible joint distributions for $(Y_{i0}, Y_{i1})$ that are compatible with the observed marginals $F_0$ and $F_1$.
-
+That is, under general conditions, these bounds already provide evidence for depressed demand, in the sense that at least 12\% (=23\% benefit -11\% demand) of borrowers would incur a lower financial cost with structured payment and yet did not chose it.
+The bounds are wide however.
 By adding assumptions it is possible to say more.
-For example, under rank invariance--i.e.\ if $i$'s rank in the distribution of $Y_0$ equals her rank in the distribution of $Y_1$--the distribution of treatment effects is point identified and given by $F_\Delta(\delta) = \int_0^1 \mathbbm{1}\{ F_1^{-1}(u) - F_0^{-1}(u)\leq \delta\}\,\mathrm{d}u$ where $F_1^{-1}$ and $F_0^{-1}$ are the quantile functions of $Y_1$ and $Y_0$.
-Figure \ref{te_rankinvariance} in Appendix \ref{bounds_FOSD} plots our estimates of $F_\Delta$ under rank invariance.
-For the financial benefit outcome, $Y_1$ first-order stochastically dominates $Y_0$.
-Since this implies that $F^{-1}_1(u) - F^{-1}_0(u)$ is always positive, all borrowers have $\Delta_i > 0$ for this outcome under rank invariance.
-The results are slightly less stark for the APR outcome: just under 90\% of borrowers have $\Delta_i > 0$ for this outcome under rank invariance.
+We turn to this next.
+%For example, under rank invariance\footnote{i.e.\ if $i$'s rank in the distribution of $Y_0$ equals her rank in the distribution of $Y_1$} the distribution of treatment effects is point identified and given by $F_\Delta(\delta) = \int_0^1 \mathbbm{1}\{ F_1^{-1}(u) - F_0^{-1}(u)\leq \delta\}\,\mathrm{d}u$, where $F_1^{-1}$ and $F_0^{-1}$ are the quantile functions of $Y_1$ and $Y_0$.\footnote{Figure \ref{te_rankinvariance} in Appendix \ref{bounds_FOSD} plots our estimates of $F_\Delta$ under rank invariance.} Because in our data, $Y_1$ first-order stochastically dominates $Y_0$ for financial benefit ($F^{-1}_1(u) - F^{-1}_0(u) >0$), we conclude that all borrowers would benefit ($\Delta_i > 0$).
 
@@
 
-The assumption-free \cite{fan2010sharp} bounds from the preceding section show that more than 23\% of borrowers would benefit from a policy of forced commitment. 
-This suggests that some of the 89\% of borrowers in the choice arm who did \emph{not} choose commitment would have faced lower borrowing costs if they had.
-Making this intuition precise, however, requires a careful consideration of the relationship between choice and heterogeneous treatment effects. 
-To this end, we now provide a full definition of the potential outcomes in our empirical setting, and introduce a pair of assumptions that will allow us to go beyond these bounds.
-
+%The assumption-free \cite{fan2010sharp} bounds from the preceding section show that more than 23\% of borrowers would benefit from a policy of forced commitment.
+This suggests that some of the 89\% of borrowers in the choice arm who did \emph{not} choose commitment would have faced lower borrowing costs if they had.Making this intuition precise, however, requires a careful consideration of the relationship between choice and heterogeneous treatment effects.
+This section shows how our 3-arm RCT design point-identifies a range of treatment effects of interest, and in particular the treatment on the untreated, necessary to study the benefits mandating a contractual feature.
+To this end, we now provide a full definition of the potential outcomes in our empirical setting.
 Let $Z_i \in \{0, 1, 2\}$ denote the treatment arm to which to participant $i$ was assigned: $Z_i = 0$ denotes the forced no-commitment arm, $Z_i = 1$ denotes the forced commitment arm, and $Z_i = 2$ denotes the choice arm.
 Now let $D_i$ be the treatment that participant $i$ actually \emph{received}, where $D_i = 0$ denotes no-commitment and $D_i = 1$ denotes commitment. 
-We assume perfect compliance in the $Z_i = 0$ and $Z_i = 1$ arms.\footnote{For more discussion on this point, see Section \ref{sec:integrity} above.}
+We assume perfect compliance in the $Z_i = 0$ and $Z_i = 1$ arms. %\footnote{For more discussion on this point, see Section \ref{sec:integrity} above.}
 It is only in the $Z_i = 2$ arm that participants are free to choose between alternative contracts. 
@@
 This model is too general, however, to point identify meaningful causal effects. 
-For this reason, we consider two exclusion restrictions.
-
-Before stating these restrictions, we first define some additional notation.
+For this reason, we consider two mild exclusion restrictions.
+
+To state these restrictions we first define some additional notation.
 Because our experimental design implies that any borrower with with $Z_i = 0$ has $D_i = 0$, we abbreviate the potential outcome $Y_i(d=0,z=0)$ as $Y_{i0}$. 
 Similarly, since any borrower with $Z_i = 1$ has $D_i = 1$, we abbreviate $Y_i(d=1,z=1)$ as $Y_{i1}$. 
-This is in keeping with our notation from section \ref{sec:bounds} above.
+%This is in keeping with our notation from section \ref{sec:bounds} above.
 Using this notation, our first exclusion restriction is given by
@@
 \cite{chamberlain2011bayesian} explicitly assumes that choosing and being assigned a treatment have the same effect.
-A significant literature using compulsory schooling laws to estimate the returns to education tacitly assumes that schooling \emph{in general} has the same returns.
-Similarly, fertilizer yields measured by development economists in experimental plots are tacitly assumed to generate the same returns regardless of whether the fertilizer was chosen by farmers or provided by the government.}
+A significant literature using compulsory schooling laws to estimate the returns to education tacitly assumes that schooling \emph{in general} has the same returns, regardless of whether it is mandated or chosen freely.
+Similarly, fertilizer yields are tacitly assumed to generate the same returns regardless of whether the fertilizer was chosen by farmers or provided by the government, as long as it is the same fertilizer.}
 Moreover, each has testable implications that we fail to reject: see \autoref{sec:testing_exclusion}. 
@@
 
-\subsection{The ``Controlled Choice'' Design}
+\subsection{The ``Forcing-Choice'' Design}
 \label{sec:randchoice}
@@
 %By additionally examining \emph{outcome data} in the choice arm, it is possible to say more. 
-As a direct consequence of \eqref{eq:potentialOutcomes}, our experimental design--henceforth the ``controlled choice design''--point identifies a number of interesting and economically-relevant causal quantities.
+As a direct consequence of \eqref{eq:potentialOutcomes}, our experimental design---henceforth the ``forcing-choice design''---point identifies a number of interesting and economically-relevant causal quantities.
 First it identifies the treatment on the treated (TOT) and untreated (TUT) effects:  
@@
 If the TUT is positive, then borrowers who did not choose commitment would have experienced better outcomes, \emph{on average}, if they had.
-In a canonical Roy model, the TOT should exceed both the TUT and average treatment effect (ATE).
-If the TOT is statistically distinguishable from and larger than the TUT, this provides empirical support for the relevance of selection-on-gains in real-world decision-making.
+Selection on gains implies TOT$>$TUT$>$ATE, as it is typically assumed in canonical Roy models.
 Because our design identifies all three quantities, it allows us to test this implication directly and to calculate the average selection on gains (ASG), namely the difference between the TOT and TUT effects:
@@
 But there is no free lunch: this ``LATE-and-reweight'' approach relies upon assumptions of its own, most crucially the assumption that there is \emph{no selection-on-gains} conditional on $X$, i.e.\ that the conditional LATE equals the conditional ATE.
-In contrast to both approaches, the controlled choice design uses exogenous experimental variation to point identify the ATE, TOT, and TUT without ruling out unobserved selection-on-gains or relying on additional structural modeling assumptions.
+In contrast to both approaches, the forcing-choice design uses exogenous experimental variation to point identify the ATE, TOT, and TUT without ruling out unobserved selection-on-gains or relying on additional structural modeling assumptions.
 
@@
     \end{center}
- \footnotesize{
+ \scriptsize{
      %This figure illustrates why the controlled choice design identifies the TOT and TUT effects.
@@
 
-Table \ref{tot_tut} calculates the causal quantities described above--TOT, TUT, ASG, ASB, and ASL--for our experimental data, along with robust standard errors for each. 
+Table \ref{tot_tut} calculates the causal quantities described above---TOT, TUT, ASG, ASB, and ASL---for our experimental data, along with robust standard errors for each. 
 For purposes of comparison, the table also presents the ATE results from Section \ref{Experiment} above (row 1),\footnote{Coefficients are not exactly the same since Table 4 includes branch and day-of-week FE.} along with the corresponding average potential outcomes $\mathbbm{E}[Y_0]$ and $\mathbbm{E}[Y_1]$ (rows 4--5).
 The columns of the table correspond to different outcome variables defined above.
+We are now in a position to report one of the important results in the paper.
 For all four outcome definitions, the TUT effect is positive, statistically and economically significant, and comparable in magnitude to the ATE.
-In other words: commitment is \emph{beneficial}, on average, to the people who \emph{would not choose it}, and these benefits are large.
-Due to the low take-up rate of commitment in the choice arm, the corresponding TOT effects are imprecisely estimated. Only one of them, \%(1-Default) from column (3), is statistically significant. 
-This imprecision carries over into our estimates of the average selection on gains, TOT-TUT.
+In other words: the structured payments contract is on average \emph{beneficial} to the people who \emph{would not choose it}, and these benefits are large.
+That is, mandating structured payment contracts would decrease the financial cost.
+Borrowers are leaving money in the table by not choosing it.
+
+Some comments are in order.
+First, this result holds on average.
+Some non-choosers could lose from a mandate.
+Section \ref{sec:RF} assesses personalized targeting strategies.
+Second, financial cost is not welfare, and further work with more comprehensive measures (stress, consumption, performance in other loans) needs to be done.
+We provide proof of concept that at least financial cost may not be minimized by free choice and provide a method to rigorously compare take-up mandates against consumer choice.
+Third, given that providing such contracts may not be in the lender's interest, borrowers may not even be presented with this choice.
+
+Table \ref{tot_tut} also estimates TOT.
+Due to the low take-up rate of commitment in the choice arm, TOT effects are imprecisely estimated.
+Only one of them, \%(1-Default) from column (3), is statistically significant.
+This carries over into our estimates of the average selection on gains.
 Our point estimates are \emph{negative} for all but the (1 - Default) outcome, but none is statistically distinguishable from zero.
@@
 %Commitment is more beneficial to people who are willing to choose it than it is to people who are not.
-For the (1 - Default) outcome, we have sufficient precision to conclude that the average selection bias (ASB) is large and \emph{negative}.
-This means that borrowers who choose commitment would have faced a \emph{higher} probability of default under the status quo contract than borrowers who do not choose commitment.
-We may not want to read too much into TOT vs TUT comparisons as they are imprecise.
-But taken at face value, the result that TOT$>$TUT for default, while the opposite is true for financial cost, suggests that, while voluntary commitment has a slightly stronger effect on allowing borrowers to avoid default, forcing \textit{reduces} payments in a strong enough manner as to overcome the default-benefits of choice.
+For the (1 - Default) outcome, we have sufficient precision to conclude that the average selection bias (ASB) is large and negative.
+This means that borrowers who choose commitment would have faced a higher probability of default under the status quo contract than borrowers who do not choose commitment.\footnote{We may not want to read too much into TOT vs TUT comparisons as they are imprecise.
+But taken at face value, the result that TOT$>$TUT for default, while the opposite is true for financial cost, suggests that, while voluntary commitment has a slightly stronger effect on allowing borrowers to avoid default, forcing \textit{reduces} payments in a strong enough manner as to overcome the default-benefits of choice.}
+
+Overall, Table \ref{tot_tut} suggests that commitment works but that \emph{not enough} people choose to commit: the commitment contract is beneficial on average even to those who would \emph{not} choose it voluntarily.
+We believe this result is new in the household finance literature.
+It also illustrates how the ``Forcing-Choice'' design can be used to study more generally whether low take-up of an intervention is problematic, based on the impacts among non-choosers.\footnote{For instance, in the debate on financial commitment take-up, some papers argue it is low (\cite{Ashraf}, \cite{Gine}, \cite{Ted}, \cite{Royer} while others argue it is high (\cite{Kremer}, \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}, \cite{Pascaline}), but none estimates the benefits for non-takers.
+In a different domain, doctors claim that medical treatment abandonment is too high in a broad range of diseases \citep{non_adherence}, without knowing the treatment benefits for those that abandon.}
 
 \begin{table}[H]
-\caption{Treatment on the Treated (TOT), Treatment on the Untreated (TUT), Selection-on-gains (TOT - TUT), Average Selection Bias (ASB), and Average Selection Bias.}
+\caption{Five Treatment Effects Estimates: TOT, TUT, ASG, ASB, ASL}
 \label{tot_tut}
@@
 \end{center}
-\footnotesize{This table presents results computed using the derivations from Section \ref{sec:randchoice}.
+\scriptsize{This table presents results computed using the derivations from Section \ref{sec:randchoice}.
 The APR and financial cost outcomes have been multiplied by $-1$ so that a positive causal effect \emph{benefits} the borrower in each of the four columns.
-The bottom panel present p-values for a number of null hypothesis tests of treatment effect heterogeneity.
+The bottom panel presents p-values for a number of null hypothesis tests of treatment effect heterogeneity.
 }
@@
 \end{table}
-
-Overall, Table \ref{tot_tut} suggests that commitment works but that \emph{not enough} people choose to commit: the commitment contract is beneficial on average even to those who would \emph{not} choose it voluntarily.
-We believe this result is new in the household finance literature.
-It also illustrates how the ``Controlled-Choice'' design can be used to study more generally whether low take-up of an intervention is problematic, based on the impacts among non-choosers.\footnote{For instance, in the debate on financial commitment take-up, some papers argue it is low (\cite{Ashraf}, \cite{Gine}, \cite{Ted}, \cite{Royer} while others argue it is high (\cite{Kremer}, \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}, \cite{Pascaline},), but none estimates the benefits for non-takers.
-In a different domain, doctors claim that medical treatment abandonment is too high in a broad range of diseases \citep{non_adherence}, without knowing the treatment benefits for those that abandon.}
 
@@
 Are clients who experienced the commitment contract more likely to choose commitment subsequently than those assigned to the status-quo contract?
-To test this we look to the subset of 22\% clients from our experimental sample who returned to pawn again on another day before the end of the experiment.
-We have already shown above that those who experienced the Forcing contract were more likely to borrow again.
+%We have already shown above that those who experienced the Forcing contract were more likely to borrow again.
 We now ask whether the subset who were assigned to the Choice arm when they returned were more likely to choose commitment.
-We do this in Appendix Table \ref{learning_table}.\footnote{Table \ref{learning_table} presents information about participants' \emph{immediate subsequent} pawning behavior.
+Appendix Table \ref{learning_table} %\footnote{Table \ref{learning_table} presents information about participants' \emph{immediate subsequent} pawning behavior.
 For borrowers who returned to pawn again more than once, this analysis considers only their first repeat pawn.}
-We find no statistically discernible difference in commitment take-up rates for those assigned to forced commitment versus those assigned to status quo control.
-The implication is that while those who have experienced commitment feel more positively towards the pawn contract, the experience does not lead them to conclude that they need commitment on the subsequent loan.
-While these exercises cannot completely exclude the possibility that learning plays a role, they provide no indication that the lack of voluntary compliance is simply a matter of inexperience with commitment.
+shows \textit{no difference} in choosing commitment for those assigned to forced commitment versus those assigned to status quo control that came back to pawn again (22\% did).
+%The implication is that while those who have experienced commitment feel more positively towards the pawn contract, the experience does not lead them to conclude that they need commitment on the subsequent loan.
+While these exercises cannot completely exclude the possibility that learning would play a role with more exposure, they provide no indication that the lack of voluntary compliance is simply a matter of inexperience with commitment in the short run.
+Note also that there will be no learning if lenders don't provide a structured payment contract in the first place.
 
@@
 
-Highly impatient individuals might rationally choose the \emph{status quo} contract, despite the benefits that commitment yields returns, since monthly payments are front-loaded while pawn recovery is back-loaded, even if by only a few days.
+Can high borrower time discount rates explain low demand for structured payments?
+%Highly impatient individuals might rationally choose the \emph{status quo} contract, despite the benefits that commitment yields returns,
+After all, monthly payments are front-loaded while pawn recovery is back-loaded, even if by only a few days.  
 %those returns are realized at contract ending hile the cost of monthly payments are incurred  Our estimated decrease in the financial cost of credit from above ignores discounting, but commitment involves incurring up-front costs (early payment) in return for delayed benefits (a higher probability of recovering one's pawn).
-To investigate this explanation we calculate the net present value (NPV) of the financial cost $\text{TUT}$ effect under different hypothetical discount rates, given the actual timing of repayment and pawn recovery.
-Figure \ref{fc_discount_rates} presents the results of this exercise.
+Figure \ref{fc_discount_rates} calculates TUT effects for different borrower discount rates given the actual timing of repayment and pawn recovery.
 The solid line gives the TUT effect adjusted for a specified annual discount rate, while the shaded regions give the associated 95\% \& 90\% confidence interval.
-We see that non-choosers continue to experience significant decreases in NPV financial costs up to annual discount rates of 1,000\%, and the NPV remains positive, although not significant, at 5,000\% discount rates.
-As such, discounting is unlikely to explain why those who benefit, on average, from commitment fail to choose it.
+We see that non-choosers continue to experience significant decreases in the net present value of financial costs up to annual discount rates of 1,000\%, and the NPV remains positive, although not significant only at 5,000\% discount rates.
+These are huge discount rates.\footnote{In a similar exercise for subprime borrowers in the US, \cite{Levin} argue that even discount rates smaller than these would be too large to be reasonable and can be safely discarded as explanations.} As such, discounting is unlikely to explain why those who benefit, on average, from commitment fail to choose it.
 % when offered.
@@
 If the benefits of commitment among non-choosers cannot be explained by standard models of rational choice, the canonical behavioral story would center on time inconsistency.
-While commitment is useful to anyone with hyperbolic time preferences, only those who are sophisticated--i.e.\ aware that they are hyperbolic discounters--will demand it.
+While commitment is useful to anyone with hyperbolic time preferences, only those who are sophisticated---i.e.\ aware that they are hyperbolic discounters---will demand it.
 A large share of ``na\"ive'' hyperbolics in the population--borrowers who are unaware that they are hyperbolic discounters--could therefore drive a large and positive $\text{TUT}$.
@@
 
-While 72\% of survey respondents believe they have a 100\% chance of recovering their pawn, in reality only 43\% will go on to do so.  
-This suggests a borrower pool characterized by over-optimism.
-Incorrect expectations about recovery probabilities could explain low take-up if individuals who \emph{believe} that they are certain to repay choose, rationally given their incorrect beliefs, to forgo the costs associated with commitment that are designed to induce repayment.
-We now explore whether over-optimistic expectations of recovery probability can explain our positive overall TUT estimate.
-To do this, we carry out an analysis that is analogous to our present bias exercise from the preceding paragraph, comparing the overall TUT estimate to estimates computed for two sub-groups.
-Here, however, the groups are defined by a binary variable that we call ``sure-confidence.''
-This measure equals one for any individuals who say at the time of borrowing that they have a 100\% probability of recovering their pawn, zero otherwise.
+Finally, motivated by the high subjective probabilities of recovery we found in the baseline survey, and by the fact that a large fraction of borrowers pay towards recovery and then lose the pawn and these payments, we explore overconfidence in recovery as a potential explanation of low demand for structured payments.
+After all, recall that while 72\% of survey respondents believe they have a 100\% chance of recovering their pawn, in reality only 43\% will go on to do so.
+Borrowers who are certain to recover their pawn perceive no benefit of committing to repay under the threat of fees and, therefore, no benefit of choosing the structured payment contract.
+%if individuals who \emph{believe} that they are certain to repay, choose (rationally given their incorrect beliefs) to forgo the costs associated with commitment that are designed to induce repayment.
+To explore this, as in the preceding paragraph, we compare the overall TUT estimate to estimates computed for two sub-groups, defined by a binary variable that we call ``sure-confidence''.
+This measure equals one for any individual who says at the time of borrowing that they have a 100\% probability of recovering their pawn, and zero otherwise.
 %The right panel of Figure \ref{tut_beh_partition} presents the results for this exercise.
@@
 %The corresponding TUT estimate and confidence interval for sure-confident borrowers is given in green; results for all other borrowers are shown in red.
-In contrast to our results for present bias, we find (Figure \ref{tut_beh_partition}) that the TUT is almost entirely confined to the sure confident individuals, with the effect among those saying they have some chance of defaulting at baseline being very close to zero.
-
-As discussed above, our measure of hyperbolicity is based on un-incentivized responses in a short survey and so is likely to be noisy; nonetheless we see no evidence here that it drives the forcing effect.
-Rather, it seems that the effectiveness of paternalism in our experiment may be driven by \emph{overconfident} borrowers who, heedless of the risk of default, fail to choose commitment despite benefiting substantially when they are forced to commit.\footnote{In Figure \ref{determinants_sure} we plot the coefficient estimates from a regression that predicts sure confidence with a battery of individual-level characteristics.
+In contrast to our results for present bias, we find that sure-confidence \textit{is} a strong predictor of TUT.
+Figure \ref{tut_beh_partition} shows that the TUT is almost entirely confined to the sure confident individuals, while those that say they have some chance of defaulting have TUT close to zero.
+It seems that the effectiveness of paternalism in our experiment may be driven by \emph{overconfident} borrowers who, heedless of the risk of default, fail to choose commitment despite benefiting substantially when they are forced to commit.\footnote{In Figure \ref{determinants_sure} we plot the coefficient estimates from a regression that predicts sure confidence with a battery of individual-level characteristics.
 Older males are more likely to be sure-confident, as are those with more education.
@@
  \end{center}       
- \footnotesize{This figure presents conditional average TUT and TOT effects for the APR outcome from Figure \ref{heterogeneous_effects} in an alternative manner, to consider the fraction of borrowers in the choice arm who made ``mistakes'' in their decision to accept or refuse the commitment contract.
+ \scriptsize{This figure presents conditional average TUT and TOT effects for the APR outcome from Figure \ref{heterogeneous_effects} in an alternative manner, to consider the fraction of borrowers in the choice arm who made ``mistakes'' in their decision to accept or refuse the commitment contract.
 A ``mistake'' for a non-chooser is defined as a positive conditional TUT effect that significantly exceeds a specified threshold APR value.
@@
 \end{center}
-\footnotesize{This table reports error rates for six different rules for allocating individuals to commitment.
+\scriptsize{This table reports error rates for six different rules for allocating individuals to commitment.
 Row 1 assigns all borrowers to control, Row 2 all to the Forcing arm.

### 2024-06-07 Restud submission/OA_restud.tex
prepare for restud submission

@@
 \begin{center}
-	\Large ONLINE APPENDIX: The controlled choice design and private paternalism in pawnshop borrowing \\[0.5em]
+	\Large ONLINE APPENDIX: The forcing-choice design and paternalism in pawnshop borrowing \\[0.5em]
 	%\Large{Appendix $-$ For Online Publication} \\[1em]
@@
 %\vspace{.2in}
+
 \begin{figure}[!h]
@@
 \newpage
+
+\begin{table}[!h]
+\caption{Baseline survey questions (translated to English)}
+\label{baseline_survey}
+\begin{center}
+\scriptsize{\input{./Tables/transcribed.tex}}
+\end{center}
+\scriptsize{
+Translation of the baseline questionnaire. Highlighted questions were used in the wide forest.}
+\end{table}
+
+\newpage
+
+\begin{landscape}
 \subsection{Intermediate Outcomes}
-
-\begin{landscape}
 
@@
 \end{center}
- \footnotesize{ The dependent variable in column (1) is the profit formula in equation (\ref{profit_function}). Columns (2)-(3) are back-of-the-envelope computations of the lender's profit.
- Standard errors are clustered at the branch-day level.}
+ \footnotesize{ The dependent variable in column (1) is the profit formula in equation (\ref{profit_function}).
+For columns (2)-(3) we compute average profit for borrower in arm $j$ according to (\ref{profit_function}).
+We then extrapolate the flow of payments over several periods depending on their repeat pawning behavior.
+In column (2) the flow of profits is given by
+ \[\sum_{T=0}^{\infty}\text{Profit}_j\times\Pr(\text{Pawn}_j)^T\]
+ assuming independence of repeat pawning across periods. In column (3) the stream of profits is given by
+ \[\text{Profit}_j + \text{Profit}_j\times \Pr(\text{Pawn}_j) +\text{Profit}_j\times\Pr(\text{Pawn}_j) \]
+ assuming that once learning (and hence repeat pawning behavior) occurs the borrower keeps coming back (we only keep 2 further periods for the exercise).
+ For columns(2)-(3) we clustered-bootstrapped the standard error. All Standard errors are clustered at the branch-day level.}
 %\textit{Do file: } \texttt{lenders\_profit.do}
@@
 
-To estimate conditional average treatment effects given administrative and survey data, we use the function \texttt{causal\_forest()} of the \texttt{grf} R package; to estimate conditional TOT and TUT effects we use the \texttt{instrumental\_forest()} function from the same package.
+To estimate the conditional average treatment effects shown in Figure \ref{heterogeneous_effects}, we use administrative and survey data, and the function \texttt{causal\_forest()} of the \texttt{grf} R package; to estimate conditional TOT and TUT effects we use the \texttt{instrumental\_forest()} function from the same package.
 In each case, we use the default parameter values from the \texttt{grf} package with one exception: we increase the number of trees from the default value of 2000 to 5000.
@@
 This is as expected, given that tree-based methods by their nature ``automatically'' consider interactions of arbitrary orders.}
-
-\begin{figure}[!h]
-     \caption{Heterogeneous Treatment Effects.} 
-     \label{heterogeneous_effects}    
-    \begin{center}
-     \begin{subfigure}{0.35\textwidth}
-       \centering
-      \includegraphics[width=\textwidth]{Figuras/he_dist_tau_hat_tot.pdf}
-          \caption{ToT}
-    \end{subfigure}
-    \begin{subfigure}{0.35\textwidth}
-       \centering
-      \includegraphics[width=\textwidth]{Figuras/he_dist_tau_hat_tut.pdf}
-          \caption{TuT}
-    \end{subfigure} 
-       \begin{subfigure}{.35\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{Figuras/he_dist_tau_hat_eff.pdf}
-        \caption{ATE}
-    \end{subfigure} 
-    \end{center}
-  %\footnotesize{ } \textit{Do file: }  \texttt{cate_dist.do}
-\end{figure}
 

### 2024-06-07 Restud submission/donde_restud.tex
prepare for restud submission

@@
 
-\title{The forcing-choice design and paternalism in pawnshop borrowing\thanks{We want to thank Jose Maria Barrero, Andrei Gomberg, Emilio Gutierrez, Anett John David Laibson, Aprajit Mahajan, Matt Rabin, Mauricio Romero, Charlie Sprenger, Chris Udry, and seminar participants at ITAM, USC, MSU, and UCSD provided valuable feedback.
+\title{The forcing-choice design and paternalism in pawnshop borrowing\thanks{We want to thank Jose Maria Barrero, Andrei Gomberg, Emilio Gutierrez, Anett John, David Laibson, Aprajit Mahajan, Matt Rabin, Mauricio Romero, Charlie Sprenger, Chris Udry, and seminar participants at ITAM, USC, MSU, UC Davis,  UCSD, and USC who provided valuable feedback.
 Ricardo Olivares, Gerardo Melendez, and Alonso de Gortari provided excellent research assistance and Erick Molina helped with formatting.
@@
 \begin{abstract}
-We explore paternalism in the important high-default pawnlending context.
-We use a novel one-stage, three-armed RCT, including forced and voluntary treatment arms, to point-identify the effects of commitment on both the treated \textit{and the untreated} simultaneously.
-We find that forcing borrowers into contracts with a regular repayment structure decreases the financial cost of pawn loans by 22\% and increases the likelihood of recovering their pawn by 15\%.
+We explore paternalism in the understudied context of high-default pawn lending.
+We use a novel one-stage, three-armed RCT, including forced and voluntary treatment arms, to point-identify the effects of structured repayment contracts on both the treated and the untreated simultaneously.
+We find that forcing borrowers into commitment-style contracts decreases the financial cost of pawn loans by 22\% and increases the likelihood of recovering their pawn by 15\%.
 However, only 11\% of borrowers choose such contracts.
-We find that borrowers who would not choose frequent payments would benefit substantially from getting such contracts, as much as those freely choosing them (no selection on gains).
-A paternalistic policy of universal forced commitment archives similar benefits to personalized ML targeting.
+We find that borrowers who would not choose regular payments would benefit substantially from getting such contracts, as much as those freely choosing them (no selection on gains).
+A paternalistic policy of universal forced commitment archives similar benefits to personalized targeting.
 \end{abstract}
@@
 
-Pawn loans constitute one of the oldest and most prevalent forms of borrowing \citep{carter2012pawnshops}.
+Pawn loans constitute one of the oldest and most common forms of borrowing \citep{carter2012pawnshops}.
 Our partner lender, for example, made over 4 million loans to more than a million clients during in the three years adjacent to our experiment.\footnote{For comparison, there were 2.3 million microfinance clients in Mexico in 2009 \citep{Pedroza:2010}.}
@@
 Our experiment covers just under 5,000 pawnshop clients in 6 of our partner lender's Mexico City branches.
-Our control arm illustrates the costs of the status quo contract: fully \emph{44\%} of borrowers default, losing lose their pawn along with any payments made towards principal, \hl{XX\%} of those made payments toward recovery.\footnote{High pawn default rates are common, in the US they oscillate around 15\% (see \href{https://tinyurl.com/yc2x5bjf}{here}).} Our ``commitment choice'' arm gives borrowers the chance to opt into a structured repayment contract when taking a loan.
+Our control arm illustrates the costs of the status quo contract: fully \emph{44\%} of borrowers default, losing their pawn along with any payments made towards principal.
+Indeed, 13\% of those who default first made some payments toward recovery, all of which is lost to them.\footnote{High pawn default rates are common, in the US they oscillate around 15\% (see \href{https://tinyurl.com/yc2x5bjf}{here}).} Our ``commitment choice'' arm gives borrowers the chance to opt into a structured repayment contract when taking a loan.
 The structured contract requires borrowers to make three monthly payments rather than one balloon payment at the end, with each monthly payment including the accrued interest at that time as well as a nominal fee of 2\% of that month's payment if the payment is delinquent.
@@
 This design allows us to measure the effects of structured payments, and also the demand for this contractual feature.
-We demonstrate that it allows us to estimate (under minimal assumptions) the relationship between treatment effects and treatment take-up, a core concern in the econometrics literature.
+We demonstrate that it further allows us to estimate the relationship between treatment effects and treatment take-up, a core concern in the econometrics literature.
 Intuitively, our design can be seen as a two-sided encouragement design, encouraging some borrowers to take and others to not take up structured repayment.
@@
 BDM mechanisms incentivizing choice prior to treatment assignment \citep{becker1964measuring} could be used to tackle this question, with some limitations \citep{bohm1997eliciting,banerji2014detection}.
-Finally, two-stage designs in the spirit of \cite{KarlanZinman2009} have been used to study related questions \citep{Beaman2023}.
-Below we compare our novel one-stage design with two-stage ones.
+Two-stage Karlan-Zinman designs can be used to study a related question, namely isolating selection and incentive effects in comparing a more and less attractive intervention, such as low- and high-interest credit \citep{KarlanZinman2009} or cash grants versus loans \citep{Beaman2023}.
+Below we compare our novel one-stage design with these two-stage ones.
 
@@
 The former are induced to pay faster, saving on interest; the latter pay less towards loans that ultimately default, hence losing less money when they do.
-One interpretation is that requiring payments earlier accelerates learning about the feasibility of making such payments, thus reducing overconfidence, a mechanism not discussed much in the literature.
+One interpretation is that requiring payments earlier accelerates learning about the feasibility of making such payments, thus reducing overconfidence, a mechanism not much discussed in the literature but that appears to be important in our context.
 
@@
 
-Next, we impose a mild exclusion restriction positing that the effect of a given contract does not depend on \emph{how} borrowers obtain it.
+Next, we impose a two-sided exclusion restriction positing that the effect of a given contract does not depend on \emph{how} borrowers obtain it.
 In other words, we assume that choosing a contract results in the same potential outcome as being assigned that contract.
@@
 It also has testable implications that we fail to reject in our empirical context.\footnote{See \autoref{sec:testing_exclusion} for details.}
-Under this restriction, the controlled choice design point identifies the TOT, TUT, ASG, ASB, and ASL effects described above.
+Under this restriction, the forcing-choice design point-identifies the TOT, TUT, ASG, ASB, and ASL effects described above.
 Our estimated TUT effect on financial cost savings is large: \$192 pesos, equivalent to a 10.6 percentage point savings in APR.
@@
 However, we find that experiencing the structured payments contract leads to a 6 percentage point increase in repeat borrowing from the lender.
-A back-of-the-envelope calculation shows that still, the contract reduces lender's profits by \hl{XX\%}, implying that lenders would not offer this contract (as was the case in Mexican pawnshops) if not forced in our context.\footnote{Our partner lender contacted us to evaluate structured payments for two reasons.
+A back-of-the-envelope calculation shows that still, the contract reduces lender's profits by 11\%, implying that lenders would not offer this contract (as was the case in Mexican pawnshops) if not forced in our context.\footnote{Our partner lender contacted us to evaluate structured payments for two reasons.
 First, they genuinely wanted to know the causal effects of structured payments but did not know how to estimate them rigorously.
@@
 On the question of what explains the persistence of no-commitment contracts so contrary to borrowers’ interests, there are several candidates.
-From the demand side, while a simple measure of time inconsistency does not explain the large and positive TUT effect, we show substantial levels of over-optimism among borrowers, the average subjective probability of recovering their pawn is \hl{XX\%}, while the actual average is only \hl{XX\%}.
+From the demand side, while a simple measure of time inconsistency does not explain the large and positive TUT effect, we show substantial levels of over-optimism among borrowers, the average subjective probability of recovering their pawn is 92\%, while the actual average is only 44\%.
 Among borrowers who do not choose commitment, those with the largest estimated benefits from commitment are the individuals who most systematically over-estimate their own probability of repayment without the need to commit, potentially decreasing their demand from commitment.
@@
 See \autoref{sec:estimation_inference} for details.}
-to a relatively small literature that sheds light on private paternalism and selection on gains.
-In the context of food choice, in an very creative paper \cite{Sprenger} show that individuals with the most time-inconsistent preferences are actually least likely to demand commitment.
+we add to the relatively small literature that sheds light on private paternalism and selection on gains.
+In the context of food choice,  \cite{Sprenger} show that individuals with the most time-inconsistent preferences are actually least likely to demand commitment.
 In contrast, we directly identify the TUT, obviating the need to first elicit preferences before testing for negative selection.
@@
 In contrast, we find no evidence of positive selection.
-Our design could be used in situations where two-stage randomization is not feasible or too costly.\footnote{\cite{fowlie2021default} likewise employ a three-armed experimental design in their study of the effect of electricity pricing, they identified \emph{two} TOT effects for different groups of ``treated'' households, whereas we simultaneously identify the TOT and TUT effects defined with respect to a single ``treated'' group of borrowers.
+Our design can be used in situations where compulsion of the treatment is possible but two-stage randomization is infeasible or too costly.\footnote{\cite{fowlie2021default} likewise employ a three-armed experimental design in their study of the effect of electricity pricing, they identified \emph{two} TOT effects for different groups of ``treated'' households, whereas we simultaneously identify the TOT and TUT effects defined with respect to a single ``treated'' group of borrowers.
 This difference is what allows our design to point identify the ASG and related quantities.}
@@
 Others have found more robust demand for commitment (\cite{Kremer},  \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}, \cite{Pascaline}).} Unlike all of these papers, however, we separately point-identify and estimate the effects of commitment for borrowers who would and \textit{would not} choose it.
-
-%By overcollateralizing and then structuring loan contracts in a manner encouraging of default, lenders are able to extract substantial value independent of the interest charged.
-Further, the `nudge’ approach generally favored by the behavioral literature (voluntary commitment) does not generate adequate demand in this context.
-
 Given their enormous prevalence and the vulnerability of their users, pawn loans are severely understudied; we believe the descriptive information and treatment effects estimates for pawn borrowing are an important contribution.
-We also believe that the forcing-choice RCT design provides a useful counterpoint to the widely used \cite{KarlanZinman2009} (KZ) designs.
+
+%We also believe that the forcing-choice RCT design provides a useful counterpoint to the widely used \cite{KarlanZinman2009} (KZ) designs.
 As far as we are aware, ours is the only experimental design in the literature simultaneously estimating both the TOT and TUT effects, along with the average selection on gains, without the need for auxiliary structural assumptions.
@@
 Section \ref{Design} describes the experiment and data sources, and shows pre-treatment balance across arms.
-Section \ref{Experiment} provides the standard ITT analysis of the experiment, while Section \ref{Choice} shows how to identify, estimate and carry out inference for the TOT, TUT, ASG, ASB and ASL effects under the controlled choice design.
+Section \ref{Experiment} provides the standard ITT analysis of the experiment, while Section \ref{Choice} shows how to identify, estimate and carry out inference for the TOT, TUT, ASG, ASB and ASL effects under the forcing-choice design.
 Section \ref{Paternalism} investigates why paternalism functions so well in this context and whether it can be more finely targeted and Section \ref{conclusion} concludes.
@@
 When asked why they are pawning this piece, 5\% responded ``lost a family member'', ``a medical emergency'' (11\%), or ``an urgent expense'' (72\%).
-Only \hl{XX\%} of borrowers have completed college, 73\% of are women, with an average age of 43 years.
+Only 32\% of borrowers have completed college, 73\% of are women, with an average age of 43 years.
 
@@
 
-\paragraph*{Gold buying shops.} Gold purchasing shops locate close to our Lender's branches. Branches have an average of \hl{XX} of these shops.
+\paragraph*{Gold buying shops.} Gold purchasing shops locate close to our Lender's branches.
+Branches have an average of \hl{XX} of these shops.
+This fact is important given the high default rates which could indicate that borrowers are ex ante intending to `sell' their pawn.
+Given that they are receiving 70\% of the value of the pawn next door to shops that would give them 100\% of this value, we think this is prima facie unlikely.
 
@@
 
-\paragraph*{Overconfidence.} We implemented a baseline survey to \hl{more than 10,000} respondents.
+\paragraph*{Overconfidence.} We implemented a baseline survey to more than 6,000 respondents.
 In it, we asked borrowers for their subjective probability of recovering the pawn.
-The average recovery probability is \hl{XX\%}.
-This contrasts sharply with the actual recovery rate for these same borrowers, \hl{57\%}.
+The average recovery probability is 92\%.
+This contrasts sharply with the actual recovery rate for these same borrowers, 44\%.
 Overall 72\% of borrowers report a 100\% probability of repaying their loan.
@@
 
-\subsection{No differential selection and balance}
+\subsection{No differential selection or imbalance}
 \label{sec:integrity}
@@
 We show this in three different ways.
-First, out of those coming into the branch and filling out the baseline survey, \hl{97\%} end up pawning.
-This rate is not only high but is also not different across treatment arms.
+First, out of those coming into the branch and filling out the baseline survey (at which time they did not yet know their treatment status), 97\% end up pawning.
+This rate is not only high but is virtually identical across treatment arms.
 Second, the number of loans per day is not different across arms, showing borrowers did not stop pawning when the forcing arm or choice arm was active.
@@
 Each row corresponds to a regression of the dependent variable on indicators for treatment assignment (status quo/control, forced commitment, choice).
-In the first row (``Take-up'') we use the sample of those who answered the baseline survey (\hl{XXX} subjects) and check which of them pawned based on the administrative data.
+In the first row (``Take-up'') we use the sample of those who answered the baseline survey (6064 subjects) and check which of them pawned based on the administrative data.
 The dependent variable indicates whether the person pawned.
@@
 \scriptsize{Each row in this table 
- corresponds to a regression \hl{at the branch-day level} of each dependent variable against the experimental arms indicators (control, forced commitment, choice).
+ corresponds to a regression at the branch-day level of each dependent variable against the experimental arms indicators (control, forced commitment, choice).
 The table reports the coefficients on each of these indicators, as well as the p-value of an F-test of the null hypothesis of equality of the three coefficients.
-We also report \hl{raw medians} for each arm.
-\hl{ISAAC, could add not just pesos per loan, but real total lent per branch-day?} %Figure \ref{boxplot_attrition}, in the appendix shows a box-plot of the first two variables, showing the distribution across arms is balanced.
+We also report a median regression for each arm.
+%Figure \ref{boxplot_attrition}, in the appendix shows a box-plot of the first two variables, showing the distribution across arms is balanced.
  }
@@
 \end{center}
-\scriptsize {Each row in this table corresponds to a regression, where the level of observation is a \hl{borrower that pawned} which we surveyed.
+\scriptsize {Each row in this table corresponds to a regression, where the level of observation is a borrower that pawned which was surveyed.
 \hl{Surveys were not conducted at the beginning of the experiment}.
@@
 However, it does not allow us to extrapolate for longer periods, and it does not allow us to ``assign'' borrowers to future structured payment contracts.
-Our second method does.
+Column (1) in Table \ref{lenders_profit} reflect the effect of the contract type (in the first assigned treatment) on the lender's profit.
+In our second method we extrapolate.
 We use the estimates of the borrower's financial cost (which is lenders's revenue) from column 1 of Table \ref{main_impact_table} and repeat pawning from Table \ref{repeat_loans} and plug them into equation \ref{profit_function}
@@
 where $j$ indexes a borrower, and $i$ indexes a loan.
-The outer sum is taken over all loans that originated in the first 180 days.
-The profit's formula captures all interest and fees payments made for the first two loans -  to reflect the repeat pawning behavior, and the 30\% of the collateral whenever the borrower defaults that loan.
-Column (1) in Table \ref{lenders_profit} reflect the effect of the contract type (in the first assigned treatment) on the lender's profit.
+The profit's formula captures all interest and fee payments made for the first two loans -  to reflect the repeat pawning behavior, and the 30\% of the collateral whenever the borrower defaults that loan.
+Columns (2) and (3) of Table \ref{lenders_profit} reflect this extrapolation.
 
@@
 %This is in keeping with our notation from section \ref{sec:bounds} above.
-Using this notation, our first exclusion restriction is given by
+Using this notation, our first exclusion restriction, which we call the ``No-choosing warm-glow'' (NCW) assumption is given by
 \begin{equation}
@@
 In words, this condition assumes that every non-chooser experiences the same potential outcome regardless of whether she is assigned to the choice arm or the control arm.
-Similarly, our second exclusion restriction is given by
+Similarly, we assume a second NCW exclusion restriction is given by
 \begin{equation}
@@
 \begin{figure}
-\caption{Graphical Intuition for the Controlled Choice Design.} 
+\caption{Graphical Intuition for the Forcing-Choice Design.} 
     \begin{center}
@@
 % derivations appear in \ref{append:randchoice}
-Viewing $Z_i$ as an instrumental variable, the controlled choice design can be interpreted as a \emph{pair} of RCTs, each subject to one-sided non-compliance.
+Viewing $Z_i$ as an instrumental variable, the forcing-choice design can be interpreted as a \emph{pair} of RCTs, each subject to one-sided non-compliance.
 The first of these compares $Z_i=0$ to $Z_i = 2$.
@@
 
-The controlled choice design also identifies the average selection bias (ASB) and average selection on levels (ASL). In particular,
+The forcing-choice design also identifies the average selection bias (ASB) and average selection on levels (ASL). In particular,
 \begin{align}
@@
 
-Equations \eqref{eq:TOT}--\eqref{eq:ASL} are useful for understanding why the controlled choice design identifies the TOT, TUT, ASG, ASB, and ASL but they are less convenient for estimation and inference.
+Equations \eqref{eq:TOT}--\eqref{eq:ASL} are useful for understanding why the forcing-choice design identifies the TOT, TUT, ASG, ASB, and ASL but they are less convenient for estimation and inference.
 \autoref{sec:estimation_inference} explains how to compute each of these quantities from a small  number of just-identified, linear instrumental variables regressions, along with appropriate cluster-robust standard errors.
@@
 For the (1 - Default) outcome, we have sufficient precision to conclude that the average selection bias (ASB) is large and negative.
-This means that borrowers who choose commitment would have faced a higher probability of default under the status quo contract than borrowers who do not choose commitment.\footnote{We may not want to read too much into TOT vs TUT comparisons as they are imprecise.
+This means that borrowers who choose commitment would have faced a higher probability of default under the status quo contract than borrowers who do not choose commitment.%\footnote{We may not want to read too much into TOT vs TUT comparisons as they are imprecise.
 But taken at face value, the result that TOT$>$TUT for default, while the opposite is true for financial cost, suggests that, while voluntary commitment has a slightly stronger effect on allowing borrowers to avoid default, forcing \textit{reduces} payments in a strong enough manner as to overcome the default-benefits of choice.}
@@
 
-\subsection{Analyzing Choice versus Paternalism Using Causal Forests} \label{sec:RF}
+\subsection{Targeting Paternalism using Causal Forests} \label{sec:RF}
 
@@
 Because they made no assumptions beyond random assignment, these bounds were relatively wide.
-Adding the assumption of rank invariance yielded a distribution of treatment effects in approximately 90\% of borrowers had positive individual treatment effects for the APR outcome, implying that \emph{practically everyone} would benefit from treatment and hence that there would be hardly any no losers from paternalism.
+%Adding the assumption of rank invariance yielded a distribution of treatment effects in approximately 90\% of borrowers had positive individual treatment effects for the APR outcome, implying that \emph{practically everyone} would benefit from treatment and hence that there would be hardly any no losers from paternalism.
 Rank invariance, however, is an extremely strong assumption.\footnote{For the financial cost outcome, rank invariance implies that all invididual treatment effects are positive.}
-In this section, we explore a middle way between the two extremes, using a causal forest analysis to consider conditional average treatment effects and conditional TOT and TUT effects.\footnote{Note that this approach imposes our exclusion restriction from \ref{sec:randchoice} conditional on observed covariates: administrative data and survey responses.}
-This exercise provides more fine-grained information about treatment effect heterogeneity.
+We then applied NCW assumptions to estimate average treatment effects for choosers and non-choosers.
+
+In this section, we again impose NCW exclusions, but this time conditional on observed covariates, not just on average.
+This enables us to use causal forests to estimate \textit{conditional} average treatment effects (CATE) as well as CTOT and CTUT effects.
+This stronger assumption allows us to say more about personalized treatment effects and, therefore, to assess different ways to target structured payments.
+%This exercise provides more fine-grained information about treatment effect heterogeneity.
 Among other things, it will potentially allow us to identify groups of borrowers who are on average \emph{harmed} by commitment.
-Under the stronger assumption that our observed survey measures capture the main sources of treatment effect heterogeneity, this exercise will allow us to approximate individual-level counterfactuals, to consider whether particular borrowers made ``mistakes'' in their choice of contract.
-To estimate the conditional average treatment effects we use the ``generalized random forest'' methods of \cite{atheygrf} (see Appendix \ref{app:cate} for details).
+%Under the stronger assumption that our observed survey measures capture the main sources of treatment effect heterogeneity, this exercise will allow us to approximate individual-level counterfactuals, to consider whether particular borrowers made ``mistakes'' in their choice of contract.
+To estimate the conditional average treatment effects we use the ``generalized random forest'' methods of \cite{atheygrf} (see Appendix \ref{app:cate} for details).\footnote{The generalized random forest approach of \cite{atheygrf} produces conditional average effect estimators that are asymptotically normal.
+%These methods are relatively straightforward because the trees are ``honest'' in that observations used to determine splits in the recursive partitioning algorithm are not used for causal effect estimation and vice-versa.
+Our inferences in this section are carried out by simulating from the normal limit distributions using the estimated standard errors.
+As covariates, we use 22 questions in our survey (what we call the \textit{wide} set of covariates in Appendix \ref{app:cate}.
+The survey questionnaire (with the highlighted questions being the ones for the wide set of covariates) can be found in \ref{baseline_survey} in the Appendix.}
+
+\begin{figure}[!h]
+     \caption{Heterogeneous Treatment Effects.} 
+     \label{heterogeneous_effects}    
+    \begin{center}
+     \begin{subfigure}{0.35\textwidth}
+       \centering
+      \includegraphics[width=\textwidth]{Figuras/he_dist_tau_hat_tot.pdf}
+          \caption{ToT}
+    \end{subfigure}
+    \begin{subfigure}{0.35\textwidth}
+       \centering
+      \includegraphics[width=\textwidth]{Figuras/he_dist_tau_hat_tut.pdf}
+          \caption{TuT}
+    \end{subfigure} 
+       \begin{subfigure}{.35\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/he_dist_tau_hat_eff.pdf}
+        \caption{ATE}
+    \end{subfigure} 
+    \end{center}
+  \scriptsize{To estimate conditional average treatment effects given administrative and survey data and the function \texttt{causal\_forest()} of the \texttt{grf} R package; to estimate conditional TOT and TUT effects we use the \texttt{instrumental\_forest()} function from the same package.
+For more information see Appendix \ref{app:cate}.}
+  %\textit{Do file: }  \texttt{cate_dist.do}
+\end{figure}
 
@@
 %\noindent \textbf{Treatment effect distributions.} 
-Figure \ref{heterogeneous_effects} plots densities of the estimated conditional ATE, TOT, and TUT effects from the generalized random forest models described above.
-In each case, the outcome variable is APR benefit, i.e.\ the reduction in APR from a commitment contract.
-As we see from the figure, the conditional average effects are overwhelmingly positive. 
+Figure \ref{heterogeneous_effects} plots densities of the estimated CATE, CTOT, and CTUT effects from the generalized random forest models described above.
+In each case, the outcome variable is APR benefit, i.e.\ the reduction in APR from a structured payments contract.
+As we see from the figure, the conditional average effects are highly heterogeneous but overwhelmingly positive. 
 The TUT density is particularly interesting for the question of paternalism since, as emphasized above, it presents conditional average effects for borrowers who would not voluntarily choose commitment.
-Only 7\% of our estimated conditional TUTs are negative, with a 95\% confidence interval of [4\%, 9\%].\footnote{The generalized random forest approach of \cite{atheygrf} produces conditional average effect estimators that are asymptotically normal, and includes methods for computing correct standard errors.
-%These methods are relatively straightforward because the trees are ``honest'' in that observations used to determine splits in the recursive partitioning algorithm are not used for causal effect estimation and vice-versa.
-Our inferences in this section are carried out by ``bootstrapping the limit experiment,'' i.e.\ simulating from the normal limit distributions using the estimated standard errors.} 
-To be clear, this is a probability statement about conditional average effects over the distribution of \emph{covariates}.
-In particular, we estimate that  $\int \mathbbm{1}\{\mathbb{E}[Y_1 - Y_0| X = \mathbf{x}, C = 0] < 0\} \, f(\mathbf{x}|C=0) \, \mathrm{d}\mathbf{x}$ is approximately 0.07.\footnote{The share of non-choosers with negative conditional \emph{average} treatment effects need not equal the share with a negative \emph{individual} effects, i.e.\ $\mathbbm{P}(Y_1 < Y_0| C = 0)$.
+Only 7\% of our estimated conditional TUTs are negative (95\% confidence interval of [4\%, 9\%]).\footnote{To be clear, this is a probability statement about conditional average effects over the distribution of covariates.
+In particular, we estimate that  $\int \mathbbm{1}\{\mathbb{E}[Y_1 - Y_0| X = \mathbf{x}, C = 0] < 0\} \, f(\mathbf{x}|C=0) \, \mathrm{d}\mathbf{x}$ is approximately 0.07.
+The share of non-choosers with negative conditional \emph{average} treatment effects need not equal the share with a negative \emph{individual} effects, i.e.\ $\mathbbm{P}(Y_1 < Y_0| C = 0)$.
 But the more treatment effect heterogeneity that $X_i$ explains, the closer these two values become.}
-Figure \ref{heterogeneous_effects} strengthens our argument, introduced in Section \ref{Choice}, that not enough borrowers choose commitment.
+Figure \ref{heterogeneous_effects} strengthens the argument that many borrowers will save on financial cost by choosing the structured payment contract.
 
@@
 %\noindent \textbf{``Mistake'' thresholds.} 
-Under the assumption that our instrumental forest estimates capture the main sources of treatment effect heterogeneity, we can use them to assess whether particular borrowers in the choice arm made ``mistakes'' in their decision to accept or refuse the commitment contract, in terms of predicted financial costs of the loan.
-To do this we use the same information that is depicted in Figure \ref{heterogeneous_effects}, but present it in a different way.
-For each non-chooser in the choice arm, we use our instrumental forest from above to estimate the conditional TUT effect, given her observed covariates.
-Of course conditional average effects need not equal individual treatment effects, and our APR outcome may not capture all of the costs and benefits that are relevant for individual borrowers' decisions.
-To account for this, we define a ``mistake'' for a non-chooser to be a conditional TUT estimate that significantly exceeds some large and positive APR threshold, e.g.\ 10\%. 
+%Under the assumption that our instrumental forest estimates capture important sources of treatment effect heterogeneity, we can use them to assess whether particular borrowers in the choice arm made ``mistakes'' in their decision to accept or refuse the commitment contract, in terms of predicted financial costs of the loan.
+We now use the CTUT estimates to quantify how much extra financial cost would borrowers incur under different scenarios.
+To simplify language, we define a ``mistake'' for a non-chooser to be a conditional TUT estimate that significantly exceeds some large and positive APR threshold, e.g., \ 10 percentage points.
 At any such threshold, we can calculate the percentage of non-choosers in the choice arm who have benefited by more than that threshold from having chosen commitment.
+Again, we do not measure welfare, only financial cost.
 
 The results of this exercise can be read off from the green curve in Figure \ref{choose_wrong}.
-Defining $F_{\text{TUT}}(\delta)$ to be the CDF corresponding to the density of conditional TUT estimates from Figure \ref{heterogeneous_effects}, the green curve in Figure \ref{choose_wrong} is merely $[1 - F_{\text{TUT}}(\delta)] \times 100\%$.
-In other words, the green curve gives the percentage of non-choosers who made a ``mistake'' when mistakes are defined increasing APR by a given threshold.
+Defining $F_{\text{TUT}}(\delta)$ to be the CDF corresponding to the density of  CTUT estimates from Figure \ref{heterogeneous_effects}, the green curve in Figure \ref{choose_wrong} is merely $[1 - F_{\text{TUT}}(\delta)] \times 100\%$.
+In other words, the vertical axis for the green curve plots the percentage of non-choosers who made a ``mistake'' of a certain threshold from the horizontal axis.
+Note that we use a \emph{positive} APR threshold to denote a mistake for both choosers and non-choosers.
+This ensures that bigger mistakes are always to the \emph{right} of smaller mistakes.
 The green shaded region gives associated 95\% pointwise confidence bounds.
-
-For choosers we follow an analogous approach, defining a ``mistake'' as a \emph{negative} conditional TOT effect that exceeds a particular APR threshold.
-The results for choosers can be read from the red curve in Figure \ref{choose_wrong}.
-If $F_{\text{TOT}}(\delta)$ denotes the CDF corresponding to the density of conditional TOT estimates from Figure \ref{heterogeneous_effects}, then the red curve is merely $F_{\text{TOT}}(-\delta) \times 100\%$.
-In other words, the red curve gives the percentage of choosers who made a ``mistake'' when mistakes are defined at a particular APR threshold.
-The red shaded region gives associated 95\% pointwise confidence bounds.
-Note that we use a \emph{positive} APR threshold to denote a mistake for both choosers and non-choosers. 
-This ensures that bigger mistakes are always to the \emph{right} of smaller mistakes for both the green and red curves.
-The blue curve in Figure \ref{choose_wrong} gives the \emph{overall} percentage of borrowers in the choice arm who made a ``mistake'' at a particular APR threshold.
-This total is computed by taking a weighted average of the green (non-choosers) and red (choosers) curves, with weights equal to their shares in the choice arm.\footnote{The blue curve is very similar to the green curve because 89\% of borrowers in the choice arm are non-choosers.}
 
@@
 A ``mistake'' for a non-chooser is defined as a positive conditional TUT effect that significantly exceeds a specified threshold APR value.
+ %\textit{Do file: } \texttt{choose_wrong_quant_wrong_tot_tut.do}
+
 %  The green curve equals $[1 - F_{\text{TUT}}(\delta)]\times 100\%$, where $F_{\text{TUT}}$ is the CDF corresponding to density of conditional TUT effects from Figure \ref{heterogeneous_effects}, computed using the instrumental forest approach from \cite{atheygrf}.
@@
 
-The results in Figure \ref{choose_wrong} suggest that a large fraction of non-choosers made mistakes by not choosing commitment.
-Even at an APR threshold as large as 10\%, we estimate that more than half of them should have chosen commitment in order to lower financial costs.
-In contrast, relatively few choosers appear to have made mistakes by choosing commitment.
-This now allows us to make a stronger statement in favor of paternalism in our context; not only does forced commitment generate large benefits on average, but it also benefits the vast majority of borrowers \emph{who would be coerced} under a policy of forced commitment.
-
-\subsection{Can we target paternalism?}
-
+For choosers we follow an analogous approach, defining a ``mistake'' as a \emph{negative} CTOT exceeding a particular APR threshold.
+The results for choosers can be read from the red curve in Figure \ref{choose_wrong}.
+If $F_{\text{TOT}}(\delta)$ denotes the CDF corresponding to the density of conditional TOT estimates from Figure \ref{heterogeneous_effects}, then the red curve is merely $F_{\text{TOT}}(-\delta) \times 100\%$.
+%In other words, the red curve gives the percentage of choosers who made a ``mistake'' when mistakes are defined at a particular APR threshold.
+The red shaded region gives associated 95\% pointwise confidence bounds.
+The blue curve in Figure \ref{choose_wrong} gives the \emph{overall} percentage of borrowers in the choice arm who made a ``mistake'' at a particular APR threshold.
+This total is computed by taking a weighted average of the green (non-choosers) and red (choosers) curves, with weights equal to their shares in the choice arm.%\footnote{The blue curve is very similar to the green curve because 89\% of borrowers in the choice arm are non-choosers.}
+
+The results in Figure \ref{choose_wrong} suggest that a large fraction of non-choosers would have experienced lower financial costs had they chosen the structured payment contract, even at an APR threshold as large as 10 percentage points, we estimate that more than half of them should have chosen the structured payment contract to lower financial costs.
+In contrast, relatively few choosers appear to have made mistakes by choosing it.
+This now allows us to make a stronger statement in favor of paternalism in our context; not only does forced commitment generate large benefits \textit{on average}, but it also benefits the \emph{vast majority} of borrowers who would be coerced under a policy of forced commitment.
+
+\subsection{Can we target paternalism accurately?}
+
+Even though the overwhelming majority of borrowers would save on financing costs, not all of them would, according to our estimates.
 Is it possible to target paternalism only towards those who would benefit from it?
-A financial firm engageing in this type of targeting under real-world circumstances would be unable to use the subjective and unverifiable questions from the survey, and would not use the commitment choice since it will be unattractive for a company to ask consumer preferences and then force a product on those who had refused it.
-This leaves us with only a few objective covariates that could be used to target: age, gender, high school education or above, desired loan size, and whether that individual has ever pawned before.
+
+The answer depends on how predictive the covariate information is of treatment effects.
+Note that to implement a targeting protocol, the covariate information used in the model would need to be either verifiable or hard to manipulate.
+In our survey and administrative data, this leaves us with only a few covariates: age, gender, high school education or above, desired loan size, and whether that individual has ever pawned before.
 We call these the ``narrow'' covariate set, to contrast with the full set of survey variables, which we call the ``wide'' covariate set.
-We take the estimated conditional average treatment effects (CATEs) $\widehat{\text{ATE}}(X_i)$ using the wide covariates as our ground truth, and now ask how well we can predict this benefit using the narrow covariate set.
+We take the estimated   $\widehat{\text{CATE}}(X_i)$ using the wide covariates as our ground truth.\footnote{We assign a dummy variable equal to one for the 90\% of borrowers who have a positive CATE using the wide covariate set.
 Figure \ref{wide_narrow_forests} shows the relationship between these two different  CATEs.
-We generate substantially less heterogeneity when using the narrow covariate set, although we still reject the null hypothesis of no treatment effect heterogeneity with the test from \cite{chernozhukov2018generic}.
-To investigate targeting, we can assign a dummy variable equal to one for the 90\% of borrowers who have a positive CATE using the wide covariate set, and then implement both a logistic regression and a random forest classification model using only the narrow covariate set to predict positive benefits at the individual level.
-
-\begin{table}
+We generate substantially less heterogeneity when using the narrow covariate set, although we still reject the null hypothesis of no treatment effect heterogeneity with the test from \cite{chernozhukov2018generic}.}
+
+To investigate targeting we ask how well we can predict this ground truth using the narrow covariate set, which is the set of less-manipulable variables that the pawnlender has.
+We use both a logistic regression and a random forest classification model using the narrow covariate set to predict positive benefits at the individual level.
+We compare the in-sample performance of targeting rules against a policy of universal forced commitment.
+
+\begin{table}[H]
 \caption{Type I \& II errors using targeting narrow rules}
@@
 \scriptsize{This table reports error rates for six different rules for allocating individuals to commitment.
-Row 1 assigns all borrowers to control, Row 2 all to the Forcing arm.
+Row 1 assigns all borrowers to control, Row 2 all to structured payments.
 Row 3 uses `optimal targeting according to the CATE from the wide covariate set.
 Row 4 uses a random forest classification, and Row 5 a logit model, both with only the narrow covariate set.
-Row 6 uses the choices made by borrowers to assign to commitment.}
+Row 6 uses the choices made by borrowers.
+%DoFile : wide_narrow_forests.do
+}
 \end{table}
 
-We compare the in-sample performance of targeting rules against a policy of universal forced commitment.
-Table \ref{hit_miss_rule} shows error rates for six possible assignment rules: assigning all borrowers to control, all to treatment (Forcing), the optimal (infeasible) assignment, narrow RF targeting, Logit targeting, and the actual choice made by borrowers.
-All models taking the wide RF as the ground truth.
-While the narrow RF correctly assigns roughly half of those who do not benefit from commitment to control, it also incorrectly allocates 4.38\% of the sample that would have gained from treatment to control.
+Table \ref{hit_miss_rule} shows error rates for six possible assignment rules: assigning all borrowers to control, all to structured payments, the optimal (wide-fores), the random forest with narrow covariates, the Logistic model with narrow covariates, and the actual choice made by borrowers.
+All models take the wide RF as the ground truth.
+While the narrow RF correctly assigns to control roughly half of those who do not benefit from the structures payment contract, it also incorrectly allocates to control 4.38\%  that would gain from structured payments.
 As such, it only improves the overall correct targeting rate by about half of a percentage point relative to universal Forcing.
-The Logit assignment rule is less successful at predicting benefits and harms, with a higher share of borrowers incorrectly assigned to both treatment and control, meaning that the overall correct targeting rate for the Logit is 5 pp lower than universal Forcing.
+The Logit assignment rule is even less successful at predicting benefits and harms, with a higher share of borrowers incorrectly assigned to both treatment and control, meaning that the overall correct targeting rate for the Logit is 5 pp \textit{lower} than universal forcing to structured payments.
 Self-targeting through choice proves to be little better than assigning everyone to the control condition, given the low take-up rate and the presence of both Type I and Type II errors in the choice arm.
-The takeaway is that given low take-up, the large fraction of the sample benefiting from commitment, and the weak predictive power of the narrow covariates, in this case universal paternalism assigning all borrowers to the commitment contract appears to be an attractive targeting method.
+
+The takeaway is that given (a) low take-up, (b) the large fraction of the sample benefiting from commitment, (c) and the weak predictive power of the narrow covariates,universal paternalism assigning all borrowers to the commitment contract appears to be an attractive targeting method in our context.
 
@@
 This paper makes several contributions.
-First, it analyzes the large but understudied industry of pawn loans, and shows that a simple change to contract terms results in substantial financial savings for pawn borrowers: forced commitment lowers the APR from 57\% to 46\%, and reduces the fraction of borrowers who default by 6.6 pp, or 15\%.
-That this new contract generated large benefits for borrowers and yet was not offered, and that a contract that generated default was the industry standard instead, is related to the idea of ``veiled paternalism'' \cite{Laibson2018}, put on its head.
-In ``veiled paternalism'' principals embed forms of commitment into their products but mask this fact from consumers who may need but do not desire commitment, in pawn lending, over-collateralization means that lenders stand to make more money from defaulting borrowers, generating incentives for ``veiled \textit{non}-paternalism,'' embedding features that lead to high borrower costs in non-obvious ways.
+First, it analyzes the important but understudied industry of pawn loans.
+Likely, hundreds of millions of people use pawn loans, and yet economists have not studied them.
+We show that a simple change to contract terms results in substantial financial savings for pawn borrowers: forced commitment lowers the APR from 57\% to 46\%, and reduces the fraction of borrowers who default by 6.6 pp, or 15\%.
+That this new contract generated large benefits for borrowers and yet was not offered, and that a contract that generated default was the industry standard instead, is related to the idea of ``veiled paternalism'' \cite{Laibson2018}, put on its head, %In ``veiled paternalism'' principals embed forms of commitment into their products but mask this fact from consumers who may need but do not desire commitment, in pawn lending, over-collateralization means that lenders stand to make more money from defaulting borrowers, generating incentives for ``veiled \textit{non}-paternalism,''
+embedding features that lead to high borrower costs.
 
@@
 
-Second, our novel  ``controlled choice'' design allows us to go beyond ATE results and draw an important set of conclusions about the relationship between take-up and heterogeneous treatment effects.
-In particular, we simultaneously point-identify the impact of commitment on those who would naturally choose it \emph{and} those who only experience commitment when forced.
-Estimating this later quantity is critical in thinking about paternalism.
-We find substantial benefits of treatment for non-choosers and no evidence of selection on gains by borrowers who choose commitment.
-Given that the rate of voluntary commitment in our sample is only 11\%, in order to achieve widespread benefits in this context compulsory commitment appears to be necessary.
-%Clients appear to prefer the forced commitment after they have experienced it, in that assignment to this arm increases the fraction of individuals who return to pawn again.
-
-Why do borrowers leave such substantial returns on the table?
-Our results suggest that over-optimism is the characteristic most strongly associated with benefiting from the commitment despite not having chosen it.
-Our borrower pool overestimates their probability of repayment by more than 50\%, and our positive TUT estimate is largely confined to borrowers who incorrectly believe that they have little chance of defaulting.
+Second, a novel ``forcing-choice'' design paired with NCW assumptions allows us to go beyond ATE results and draw an important set of conclusions about the relationship between take-up and heterogeneous treatment effects, providing a complement to marginal treatment effects methods.
+%In particular, we simultaneously point-identify the impact of commitment on those who would naturally choose it \emph{and} those who only experience commitment when forced.
+Estimating treatment effects for non-takers is critical in thinking about paternalism, and we show one rigorous way to do it that is new in the literature and distinct from Karlan-Zinman designs.
+
+Third, in terms of our empirical results, we find substantial benefits of treatment for \textit{non-choosers} and no evidence of selection on gains by borrowers who choose commitment.
+This is the first such result in the household finance literature and a first step in thinking about paternalistically imposing frequent payment contracts.
+Our results show that over-optimism of pawn recovery is the characteristic most strongly associated with benefiting from the commitment despite not having chosen it, and it maybe an explanation for the low demand for commitment.
+Given that the rate of voluntary commitment in our sample is only 11\% and given the limited benefits from personalized targeting with our data, in order to achieve widespread benefits in this context compulsory commitment appears to be an attractive policy.
+With a now well-established toolkit of regular small payments and incentives delivering small default rates in microfinance, regulators may fruitfully investigate the possibility of requiring pawnbrokers to embed features of commitment and regularity into their repayment structures in more consistent ways.
+
+%Why do borrowers leave such substantial returns on the table?
+
+%Our borrower pool overestimates their probability of repayment by more than 50\%, and our positive TUT estimate is largely confined to borrowers who incorrectly believe that they have little chance of defaulting.
 %More standard explanations such as discounting, learning, or time inconsistency find little support in our data.
 
-Using machine learning methods, we find the benefits of commitment close to universal.
+%Using machine learning methods, we find the benefits of commitment close to universal.
 The benefits of targeting commitment based on characteristics that lenders can observe and participants would truthfully reveal are extremely limited, suggesting that universal commitment is an attractive policy in our empirical setting.
 
-%but the determinants that might allow us to target it more finely are primarily behavioral and hence not easily predicted in a fast incentive-compatible manner by lenders, making universal assignment to commitment attractive.
-Of course, in other applications this would have to be decided on a case-by-case basis.
-%Even a sophisticated machine learning-based exercise is only able to decrease the fraction of borrowers mis-targeted less than half percentage points relative to simply assigning everyone to commitment (from 9.78\% to 9.59\%).
-and a logit-based targeting rule actually does slightly worse than universal commitment.
-
-Where lenders have no incentive to engage in veiled paternalism and customers display inefficiently low demand for it, financial policy regulation may prove an attractive option.
+%Where lenders have no incentive to engage in veiled paternalism and customers display inefficiently low demand for it, financial policy regulation may prove an attractive option.
 Pawnshops, along with other over-collateralized credit products such as payday lending, exist in an environment where the lender may desire customers to lose their collateral on the loan, hurting especially low-income populations who are its main users.
@@
 In a setting of lender market power however, redistribution from lenders to borrowers could occur.}
-An important question for future research will be the extent to which borrowers are able to learn about the benefits of commitment over time, making it so that temporary, lighter-touch policies could achieve lasting benefits for borrowers.
-Pawning with commitment may provide an important mechanism to preserve flexible credit access while allowing more poor borrowers to retain their assets.
+
+There are several questions left for future research.
+Would results hold using more comprehensive measures of welfare?
+How fast would borrowers learn about the benefits of structured payments if regulators forced lenders to provide this contractual feature?
+How would lender competition affect the incentives to provide such a contract?
+Much needs to be done to improve the lives of the millions of borrowers using panw loans.
 

### 2024-06-07 Tables/transcribed.tex
edit for submission
prepare for restud submission

@@
       & (a) Inherite, (b) a gift, (c) bought by me, (d) lend to me, (e) other \_\_\_\_\_\_\_\_\_\_\_\_ \\
-2     & \textbf{Mark with an "X" in the line below how likely is that you recover your pawn. } \\
+\rowcolor[rgb]{ .682,  .667,  .667} 2     & \textbf{Mark with an "X" in the line below how likely is that you recover your pawn. } \\
       & \textbf{Where 0 is impossible and 100 is completely certain} \\
-3     & \textbf{How much do you think the item you plan to pawn is worth?       \_\_\_\_\_\_\_\_\_\_\_\_\_\_ pesos} \\
-4     & \textbf{Gender      } \\
-5     & \textbf{Age} \\
+\rowcolor[rgb]{ .682,  .667,  .667} 3     & \textbf{How much do you think the item you plan to pawn is worth?       \_\_\_\_\_\_\_\_\_\_\_\_\_\_ pesos} \\
+\rowcolor[rgb]{ .682,  .667,  .667} 4     & \textbf{Gender      } \\
+\rowcolor[rgb]{ .682,  .667,  .667} 5     & \textbf{Age} \\
 6     & \textbf{Civil Status } \\
@@
       & (a) employed, (b) own business, (c) houseshores, (d) don't work, (e) retired, (f) study \\
-8     & \textbf{Education} \\
+\rowcolor[rgb]{ .682,  .667,  .667} 8     & \textbf{Education} \\
       & (a) no formal education, (b) primary, (c) middle school, (d) highschool, (e) more than highschool \\
-9     & \textbf{In the last month, did a friend or family member asked you for money?} \\
+\rowcolor[rgb]{ .682,  .667,  .667} 9     & \textbf{In the last month, did a friend or family member asked you for money?} \\
       & (a) yes  (b) no \\
-10    & \textbf{What would you like to have: 100 pesos tomorrow or 150 pesos in one month?} \\
-11    & \textbf{How often do you feel stressed by your economic situation?} \\
+\rowcolor[rgb]{ .682,  .667,  .667} 10    & \textbf{What would you like to have: 100 pesos tomorrow or 150 pesos in one month?} \\
+\rowcolor[rgb]{ .682,  .667,  .667} 11    & \textbf{How often do you feel stressed by your economic situation?} \\
       & (a) always, (b) very often, (c) sometimes, (d) never \\
@@
       & (d) Need the money for some non urgent expense. \\
-13    & \textbf{How stressed do you feel from the situation that led to to pawn?} \\
+\rowcolor[rgb]{ .682,  .667,  .667} 13    & \textbf{How stressed do you feel from the situation that led to pawn?} \\
       & (a) very stressed, (b) somwhat stressed, (c) a little stressed, (d) not stressed  \\
-14    & \textbf{In 3 months, I expect to have a  \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ situation} \\
+\rowcolor[rgb]{ .682,  .667,  .667} 14    & \textbf{In 3 months, I expect to have a  \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ situation} \\
       & (a) better, (b) similar,  (c) worse \\
-15    & \textbf{Have you panwned before?} \\
+\rowcolor[rgb]{ .682,  .667,  .667} 15    & \textbf{Have you panwned before?} \\
       & (a) yes  (b) no \\
-16    & \textbf{How many times have you pawned on a Lender P branch?} \\
+\rowcolor[rgb]{ .682,  .667,  .667} 16    & \textbf{How many times have you pawned on a Lender P branch?} \\
       & (a) NO\_\_\_    (b)  1-2 times \_\_\_    (c) 3-5 times\_\_\_\_   (d) More than 5\_\_\_\_ \\
-17    & \multicolumn{1}{p{54.91em}}{\textbf{If you are saving money and a family member wants to use it for something }} \\
+\rowcolor[rgb]{ .682,  .667,  .667} 17    & \multicolumn{1}{p{54.91em}}{\textbf{If you are saving money and a family member wants to use it for something }} \\
       & \multicolumn{1}{p{54.91em}}{(a) I would only give him the money for an urgent expenze} \\
@@
       & \multicolumn{1}{p{54.91em}}{(d) No one would ask me for my money} \\
-18    & \textbf{Do you make an expenses budget for the month ahead of time?} \\
+\rowcolor[rgb]{ .682,  .667,  .667} 18    & \textbf{Do you make an expenses budget for the month ahead of time?} \\
       & (a) always, (b) very often, (c) sometimes, (d) never \\
@@
       & (a) yes  (b) no \\
-20    & \textbf{Do you have savings?} \\
+\rowcolor[rgb]{ .682,  .667,  .667} 20    & \textbf{Do you have savings?} \\
       & (a) yes  (b) no \\
-21    & \textbf{Do you participate in a ROSCA?} \\
+\rowcolor[rgb]{ .682,  .667,  .667} 21    & \textbf{Do you participate in a ROSCA?} \\
       & (a) yes  (b) no \\
-22    & \textbf{Is it common that family or friends ask for money?} \\
+\rowcolor[rgb]{ .682,  .667,  .667} 22    & \textbf{Is it common that family or friends ask for money?} \\
       & (a) yes  (b) no \\
-23    & \textbf{How much did you spend to come to the branch today?    \$\_\_\_\_\_\_\_\_\_\_\_\_\_\_ pesos} \\
-24    & \textbf{How much time does it usually take to come to this branch?    \_\_\_\_\_\_\_\_\_\_\_} \\
+\rowcolor[rgb]{ .682,  .667,  .667} 23    & \textbf{How much did you spend to come to the branch today?    \$\_\_\_\_\_\_\_\_\_\_\_\_\_\_ pesos} \\
+\rowcolor[rgb]{ .682,  .667,  .667} 24    & \textbf{How much time does it usually take to come to this branch?    \_\_\_\_\_\_\_\_\_\_\_} \\
 25    & \textbf{How much does your family spend in a normal week?   \$\_\_\_\_\_\_\_\_\_\_\_\_\_\_ pesos} \\
 26    & \textbf{How much do you manage to save in a normal week?   \$\_\_\_\_\_\_\_\_\_\_\_\_\_\_ pesos} \\
-27    & \textbf{Does it happen to you that you spend more than you wanted because you fall into temptation?} \\
+\rowcolor[rgb]{ .682,  .667,  .667} 27    & \textbf{Does it happen to you that you spend more than you wanted because you fall into temptation?} \\
       & (a) never, (b) almost never, (c) sometimes, (d) very often \\
-28    & \textbf{In the last 6 months, has it happened that at some point you lacked money to pay} \\
+\rowcolor[rgb]{ .682,  .667,  .667} 28    & \textbf{In the last 6 months, has it happened that at some point you lacked money to pay} \\
       & (a) rent?    (b) food    (c)food   (d) medicine  (e) electricity   (f) heating   (g) telephone    (i) water \\
-29    & \textbf{What would you like to have: 100 pesos in 3 months or 150 pesos in four months?} \\
-30    & \textbf{Would you like to receive (free) reminders for upcomming payments?} \\
+\rowcolor[rgb]{ .682,  .667,  .667} 29    & \textbf{What would you like to have: 100 pesos in 3 months or 150 pesos in four months?} \\
+\rowcolor[rgb]{ .682,  .667,  .667} 30    & \textbf{Would you like to receive (free) reminders for upcomming payments?} \\
       & (a) yes  (b) no \\

### 2025-04-25 Restud submission/Responses to 1st round ReStud/Response to Editor.tex
First set of edits after R&R

% !TeX root = editor_letter.tex
% !TEX TS-program = pdflatex
% !TEX encoding = UTF-8 Unicode
% !TEX output_directory = .texpadtmp

\documentclass[11pt, colorinlistoftodos]{article} % otra posibilidad es [openany]{book}

\input{preamble} % document preamble
%\input{commands}

% To-do commands (must go after authblk to avoid clash)
\usepackage{todonotes}
\usepackage{marginnote}
\renewcommand*{\marginfont}{\color{red}\sffamily\scriptsize}
\setlength{\marginparwidth}{2cm}  % prevent todo cutoff
\newcounter{todoListItems}
\newcommand{\todoLink}[2][ ]{
  \addtocounter{todoListItems}{1}
  \todo[caption={\protect\hypertarget{todo\thetodoListItems}{}Translation},size=\scriptsize,#1]{
    \scriptsize #2 \hfill \hyperlink{todo\thetodoListItems}{$\uparrow$}
  }
}
\newcommand{\forES}[1]{\todoLink[color=green!20,inline,caption={\thetodoListItems: For @Enrique}]{\textbf{@Enrique} -- #1}}
\newcommand{\forIM}[1]{\todoLink[color=blue!20,inline,caption={\thetodoListItems: For @Isaac}]{\textbf{@Isaac} -- #1}}
\newcommand{\forFdT}[1]{\todoLink[color=red!20,inline,caption={\thetodoListItems: For @Francis}]{\textbf{@Francis} -- #1}}
\newcommand{\forCM}[1]{\todoLink[color=violet!20,inline,caption={\thetodoListItems: For @Craig}]{\textbf{@Craig} -- #1}}
\newcommand{\forAll}[1]{\todoLink[color=orange!20,inline,caption={\thetodoListItems: For All}]{\textbf{@All} -- #1}}

\newcounter{point}
\setcounter{point}{0}
\def\thepoint{\alph{point}}

\newenvironment{point}{\refstepcounter{point}\noindent\textbf{Point~(\thepoint)~}\hrulefill\newline\itshape\small}{\par\vspace{-1.25em}\noindent\hrulefill}

%----------------------------------------------------------------------------------------
%	INICIO DEL DOCUMENTO
%----------------------------------------------------------------------------------------
\begin{document}

\listoftodos

\noindent \textbf{Letter to the Editor}
\vspace{.3in}

\noindent
Dear Editor,

\vspace{.4in}
\noindent \textbf{1. Mechanisms}
\vspace{.2in}

\textcolor{red}{Editor, }\begin{point} 
   R4 and R5 call into question your favored explanation of overconfidence, in that they fail to see why overconfident consumers would react to a structured contract. Both referees convincingly argue that it could be the opposite, actually. I think this is a major point to clarify.
\end{point}

\forAll{sss}

\textcolor{red}{Editor, }\begin{point}
Relatedly, Figure OA-7 is a major piece of evidence in favor of overconfidence, so it should appear in the main text. More importantly, you should also give the p-values of the tests of equality of the two corresponding conditional TUTs (I have the impression that one cannot reject at usual levels the null that the TUT of “sure” clients is the same as the TUT of the others).
\end{point}

\textcolor{red}{Editor, }\begin{point}
Given that the overconfidence interpretation of your results raises questions, I agree with R4 that you should include and discuss the other arm without a penalty fee. Also, please at least disclose the additional arms of the experiment.
\end{point}

\textcolor{red}{Editor, }\begin{point}
Another reason mentioned by R5 for why people prefer the status quo is liquidity concerns. I am more sanguine than R5 on this issue but I think it is important to discuss it.

\end{point}

\textcolor{red}{Editor, }\begin{point}
 The clients in the “choice” arm could be influenced by the appraisers, who could have discouraged the clients to make this choice. Even if the appraisers are not incentivized, the structure payment could, e.g., increase their workload. That the results do not change too much with appraisers fixed effects is reassuring in this respect but all appraisers could have reacted in a similar way. This issue should be discussed.
\end{point}

\textcolor{red}{Editor, }\begin{point}
 I agree with R4 that you should discuss more extensively your results in view of the related literature.
\end{point}

\vspace{.4in}
\noindent \textbf{2. Econometric Issues}
\vspace{.2in}
\setcounter{point}{0}

\textcolor{red}{Editor, }\begin{point}
I encourage you to shorten the discussion on the identification of TOT and TUT. I would just present identification of the TUT and explain that the same reasoning applies to the TOT.

\end{point}

\textcolor{red}{Editor, }\begin{point}
As a suggestion, you could investigate how your bounds on the distribution of treatment effects improve when you include covariates, following Fan, Guerre and Zhu (2017, Journal of Econometrics).
\end{point}

\textcolor{red}{Editor, }\begin{point}
 Obtaining a consistent estimator of the true distribution of the TOT, TUT and ATE is hard, because of the estimation noise. Specifically, for individual i, one has, for instance for the conditional TOT,
$\widehat{CTOT_i} = CTOT_i + \epsilon_i$, where, approximately, $\epsilon_i \sim N (0, \sigma^2)$ and $\sigma^2$ can be consistently estimated. Of course, ignoring that the $CTOT_i$ are estimated artificially increases the dispersion of the estimated distribution. Note that the problem above would be a standard (but already non-trivial) deconvolution problem if  can be consistently estimated. Of course,  was constant across individuals but here this is not the case. So I wonder how you obtain Figure 3 (and in turn, Figure 4).

\end{point}

\textcolor{red}{Editor, }\begin{point}
Related to the previous point, you indicate in Footnote 23, that your “inferences in this section are carried out by simulating from the normal limit distributions using the estimated standard errors”. This is not very precise, and I am not sure that this leads to correct inference. Why not use the bootstrap instead?
\end{point}

\textcolor{red}{Editor, }\begin{point}
Footnote 24 is important and should appear in the text. I would also clarify that Figure 4 can be interpreted as you do if one assumes that individual treatment effects are equal to conditional TOT/TUT 
(relatedly, you say p.23 that “By adding assumptions it is possible to say more”, but afterwards you do not consider the distribution of treatment effects anymore).

\end{point}

\vspace{.4in}
\noindent \textbf{3. Exposition}
\vspace{.2in}
\setcounter{point}{0}

\textcolor{red}{Editor, }\begin{point}
 I think R1’s suggestion (see their Comment 3) on the organization of your paper is very good.
\end{point}

\textcolor{red}{Editor, }\begin{point}
  An implication of several of the points above is that you should tone down some of your conclusions (see also, e.g., R1’s Comment 2 and R4’s Comment 1 in their “must do”).
\end{point}

\textcolor{red}{Editor, }\begin{point}
  I would consider moving to an online appendix Section 6.3. This seems less important to me than, e.g., the points mentioned in Section 1 above.
\end{point}

\vspace{.4in}
\noindent \textbf{4. Other points}
\vspace{.2in}
\setcounter{point}{0}

\textcolor{red}{Editor, }\begin{point}
Among the multiple (good) points of R4, Point 7 in their “Strongly consider doing” seems very important to me.
\end{point}

\textcolor{red}{Editor, }\begin{point}
You have very low power on TOTs since very few clients chose the structured contracts. So I suggest that you remain cautious about your related results. For instance, I cannot see any evidence that “the structured contract benefits both those who would choose it (...)”.
\end{point}

\textcolor{red}{Editor, }\begin{point}
 p.14, “Branches have an average of 2.8 of these shops in the vicinity”: how do you define the “vicinity”? And is it clear that clients are aware of that?
\end{point}

\textcolor{red}{Editor, }\begin{point}
  pp.16-17, how are the standard errors computed in Tables 1 and 2 (and same question for the tests of equality)?
\end{point}

\textcolor{red}{Editor, }\begin{point}
p.21, in the computation of profit, you also assume independence between repeat and the amounts. Also: couldn’t you simply model total financial costs as a function of the duration observed, to extrapolate?
\end{point}

\textcolor{red}{Editor, }\begin{point}
p.21, in {Financial Costj |Contract= X}, an expectation sign is missing.
\end{point}

\textcolor{red}{Editor, }\begin{point}
 p.24, consider simplifying the discussion by just assuming the standard exclusion restriction Y (d, z) = Y (d). Also, note that “Yi(d = 1, z = 1)” is not consistent with the previous notation Yi(d, z).
\end{point}

\textcolor{red}{Editor, }\begin{point}
p.25, “Selection on gains implies $TOT>TUT>ATE$”. These inequalities are impossible, since ATE satisfies $ATE = p TOT + (1 - p)$ TUT with p the probability of choosers. I guess you meant $TOT>ATE>TUT$?
\end{point}

\textcolor{red}{Editor, }\begin{point}
p.29, the hypotheses ATE = TOT and ATE=TUT are redundant given that ATE is a convex combination of TOT and TUT (and it would seem more natural to me to test for TOT = TUT, as these correspond to non-overlapping populations)
\end{point}

\textcolor{red}{Editor, }\begin{point}
 p.30, “ although not significant only at 5,000\% discount rates.” My reading of the figure is that it becomes non-significant at the 5\% level already for a discount rate of 1,000\%.
\end{point}

\textcolor{red}{Editor, }\begin{point}
 p.30, my impression is that “we should find that the TUT for present-biased borrowers is positive” should rather be “we should find that the TUT for present-biased borrowers is larger than for the others”.
\end{point}

\textcolor{red}{Editor, }\begin{point}
p.32, the titles of Figure 3 should reflect that these are conditional TOT, TUT and ATE.  Changed to say “Conditional” in front of each. 
\end{point}

\textcolor{red}{Editor, }\begin{point}
 p. 34, ``the red curve is merely $F_{TOT}(−\delta)$ $\times$ 100\%.'' Should not it rather be $[1 - F_{TOT}(\delta)]$ $\times$ 100\%? Also, the explanation of Figure 4 is repetitive and could be shortened. 
\end{point}

\textcolor{red}{Editor, }\begin{point}
p.34, “In contrast, relatively few choosers appear to have made mistakes by choosing it” I may have missed something but this is not my reading of the graph.
\end{point}

\textcolor{red}{Editor, }\begin{point}
 p.35, how is “Overall Error Rate” computed in Table 5? It’s always the sum of the previous columns except for the last row
\end{point}

\textcolor{red}{Editor, }\begin{point}
 Figure OA-3 is difficult to read; I would remove the results of the bivariate regressions.
\end{point}

%\begin{point} this is point a
%\end{point}

%\textcolor{red}{ENRIQUE}

% REFERENCES ======================================================
%\cleardoublepage
%\singlespacing
%\bibliographystyle{chicago}
%\bibliography{References.bib}
%\printbibliography
\end{document}

### 2025-04-25 Notes/model.tex
First set of edits after R&R

\documentclass[11pt]{article}
\usepackage{amsmath,amssymb,amsthm,fullpage}
\usepackage{bm}
\usepackage{mathtools}
\usepackage{color}
\usepackage{algorithm}
\usepackage{algpseudocode}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{remark}{Remark}

\begin{document}

\section{Model Setup}

\paragraph{Periods and Loan.}
Time is discrete, \(t \in \{1,2,3\}\). In period \(t=1\), the borrower receives a loan of size \(L > 0\). She has exogenous incomes \(\{y_1,y_2,y_3\}\) in each period. We allow for a \emph{prepayment} of size \(k \in [0, L]\) in period~2, and a final repayment decision in period~3. Two interest rates apply:
\[
R_2 > 0 
\quad (\text{applies to the period-2 prepayment}), \]
\[R_3 > 0 
\quad (\text{applies to the period-3 repayment of remaining balance}).
\]
Hence, if the borrower prepays \(k\) in period~2, she pays \(R_2 \cdot k\). If there remains \(L - k\) principal going into period~3, repaying it fully costs \(R_3 \cdot (L - k)\).

\paragraph{Preferences.}
We assume \emph{quasi-hyperbolic} discounting with parameters \((\beta, \delta)\), where \(0 < \delta < 1\) and \(0 < \beta \le 1\). The instantaneous utility is given by some \(u(\cdot)\). Thus, from the perspective of period~1, the total utility over consumption \(\{c_1, c_2, c_3\}\) plus an extra payoff \(v\) if she repays by \(t=3\) is
\begin{align}
U 
\;=\;
u(c_1) 
\;+\;
\beta\,\delta \, u(c_2)
\;+\;
\beta\,\delta^2 
\Bigl(
   u(c_3) 
   \;+\; 
   \mathbf{1}_{\{\text{repay at }t=3\}} \cdot v
\Bigr),
\tag{1}
\end{align}
where \(\mathbf{1}_{\{\text{repay at }t=3\}}\) indicates \(1\) if the borrower fully repays in period~3, and \(0\) otherwise.

\paragraph{Behavioral Types.}
\begin{itemize}
\item \emph{Rational}: \(\beta = 1\).  
\item \emph{Present-Biased Sophisticate}: \(0 < \beta < 1\) and \emph{foresees} that future selves also discount by \(\beta\).
\item \emph{Present-Biased Na\"{i}f}: \(0 < \beta < 1\) but \emph{believes (incorrectly)} that future selves use \(\beta=1\).
\end{itemize}
Moreover, the borrower may be \emph{overconfident} about future income, believing \((y_2,y_3)\sim \mathbb{P}'\) that is more optimistic than the true distribution \(\mathbb{P}\). A \emph{realistic} borrower uses the correct \(\mathbb{P}\).

\paragraph{Commitment vs.\ No Commitment.}
At period \(1\), the borrower chooses
\[
C 
\;\in\; 
\{\text{Commit},\, \text{No-Commit}\}.
\]
Under \textbf{No-Commit}, the borrower \emph{may} prepay \(k\) in \(t=2\), but faces no penalty for skipping it. Under \textbf{Commit}, if she skips \(k\) in \(t=2\), she must pay a fee \(\phi \ge 0\) in period~3 \emph{if} she ultimately repays.

\section{Period-by-Period Decisions}

\subsection{Period 3: Repay or Default}

Let the \emph{outstanding principal} be \(L-k\) if the borrower prepays \(k\) in period~2, or \(L\) if she does not. If she is in the commitment regime but skips \(k\), she also owes a fee \(\phi\) when repaying. Thus:

\[
\text{Consumption if Repay} 
\;=\; 
y_3 \;-\; R_3 \times (\text{outstanding}) 
\;-\; 
\phi \cdot \mathbf{1}_{\{\text{commit} \,\wedge\, \text{skipped }k\}},
\]
plus the continuation payoff \(v\). If she \textbf{defaults}, consumption is \(y_3\) with no \(v\). Hence she repays if and only if
\[
u\Bigl(
  y_3 - R_3 \cdot (\text{outstanding})
  \;-\; 
  \phi \cdot \mathbf{1}_{\{\text{commit}\,\wedge\,\text{skipped }k\}}
\Bigr)
\;+\; v
\quad>\quad
u(y_3).
\]

\subsection{Period 2: Pay $k$ or Not}

In period~2, the borrower’s discount factor toward period~3 is \(\beta\,\delta\).  Denote
\[
\text{Pay-$k$ Utility} 
\;=\; 
u\bigl(y_2 - R_2\,k\bigr)
\;+\;
\beta\,\delta\,
\mathbb{E}\Bigl[
  \max\{\,u(y_3 - R_3(L - k)) + v,\;u(y_3)\}
\Bigr],
\]
\[
\text{Not-Pay Utility (No-Commit)} 
\;=\;
u(y_2)
\;+\;
\beta\,\delta\,
\mathbb{E}\Bigl[
  \max\{\,u(y_3 - R_3\,L) + v,\;u(y_3)\}
\Bigr].
\]
Under \textbf{No-Commit}, she prepays \(k\) if and only if
\[
\text{Pay-$k$ Utility} 
\;>\;
\text{Not-Pay Utility (No-Commit)}.
\]
Under \textbf{Commit}, skipping \(k\) adds \(\phi\) if she repays at \(t=3\). Thus
\[
\text{Skip-$k$ Utility (Commit)}
\;=\;
u(y_2)
\;+\;
\beta\,\delta\,
\mathbb{E}\Bigl[
  \max\bigl\{
    u(y_3 - R_3\,L - \phi) + v,\;
    u(y_3)
  \bigr\}
\Bigr].
\]
So in \textbf{Commit}, she pays \(k\) iff
\[
\text{Pay-$k$ Utility} 
\;>\;
\text{Skip-$k$ Utility (Commit)}.
\]

\subsection{Period 1: Choose Commitment or Not}

At \(t=1\), the borrower compares the ex-ante \emph{perceived} expected utilities of \textbf{No-Commit} vs.\ \textbf{Commit}:
\[
U_{\text{NC}}
\;=\;
u(y_1)
\;+\;
\beta_{\text{hat}}\,\delta 
\;\mathbb{E}_{(y_2,y_3)}\Bigl[
   \max\{\text{Pay-$k$ Utility},\;\text{Not-Pay Utility (No-Commit)}\}
\Bigr],
\]
\[
U_{\text{C}}
\;=\;
u(y_1)
\;+\;
\beta_{\text{hat}}\,\delta 
\;\mathbb{E}_{(y_2,y_3)}\Bigl[
  \max\{\text{Pay-$k$ Utility},\;\text{Skip-$k$ Utility (Commit)}\}
\Bigr].
\]
Here, \(\beta_{\text{hat}}=1\) if the borrower is \emph{na\"{\i}ve} (incorrectly assuming future \(\beta=1\)), whereas \(\beta_{\text{hat}}=\beta\) if she is \emph{sophisticated} or rational (\(\beta=1\)). Also, \(\mathbb{E}_{(y_2,y_3)}\) might be taken under the true distribution \(\mathbb{P}\) (if realistic) or a biased \(\mathbb{P}'\) (if overconfident). She chooses \(\text{Commit}\) iff \(U_{\text{C}} > U_{\text{NC}}\).

% \section{Thresholds in Each Period}

% \paragraph{Period 3 (Repay vs.\ Default).} Define the function
% \[
% D_3(y_3,\text{outstanding},\phi_{\text{commit}}) 
% \;=\;
% u\bigl(y_3 - R_3\,(\text{outstanding}) - \phi_{\text{commit}}\bigr)
% \;+\; v 
% \;-\; 
% u(y_3).
% \]
% She repays iff \(D_3(\cdot) > 0\). Otherwise she defaults.

% \paragraph{Period 2 (Pay-$k$ vs.\ Not Pay).} 
% In either regime, define
% \[
% D_2^{\text{(pay)}}(y_2)
% \;=\;
% u(y_2 - R_2\,k)
% \;+\;
% \beta\,\delta \,
% \mathbb{E}\bigl[\text{repay-or-default payoff if outstanding }(L-k)\bigr]\]
% \[\qquad \;-\;
% \Bigl(
%   u(y_2)
%   \;+\;
%   \beta\,\delta \,
%   \mathbb{E}\bigl[\text{repay-or-default payoff if outstanding }L \bigr]
% \Bigr).
% \]
% Under \textbf{No-Commit}, she pays \(k\) iff \(D_2^{\text{(pay)}}(y_2) > 0\).  
% Under \textbf{Commit}, replace the “repay payoff” for the \((L\text{-skipped},\phi)\) case accordingly. She pays \(k\) iff
% \[
% D_2^{\text{(pay)}}(y_2) 
% \;>\; 
% D_2^{\text{(skip, commit)}}(y_2),
% \]
% where \(D_2^{\text{(skip, commit)}}\) includes the \(\phi\) penalty if repaying.

% \paragraph{Period 1 (Commit vs.\ No-Commit).}
% Define
% \[
% D_1 
% \;=\;
% U_{\text{C}} - U_{\text{NC}}
% \;\;=\;\;
% \bigl[u(y_1) + \beta_{\text{hat}}\delta \,\mathbb{E}(\dots)\bigr] 
% \;-\;
% \bigl[u(y_1) + \beta_{\text{hat}}\delta \,\mathbb{E}(\dots)\bigr].
% \]
% She chooses \(\text{Commit}\) iff \(D_1>0\).

\section{Outcomes of Interest}

Once the borrower’s type (rational, naive, or sophisticated; realistic or overconfident) is specified, along with the realized \((y_2,y_3)\), the above thresholds determine each period’s decision. We then define:

\begin{enumerate}
\item \textbf{Probability of Default}:
\[
\Pr[\text{default}] \;=\; \mathbb{E}\bigl[\mathbf{1}_{\{\text{default at }t=3\}}\bigr].
\]
\item \textbf{Average Payment}:
\[
\mathbb{E}\bigl[m_2 + m_3\bigr],
\]
where \(m_2 \in \{0,\,kR_2\}\) is the actual period-2 payment (including interest factor \(R_2\)), and \(m_3 \in \{0,\,(\!L\!-\!k\!)\,R_3, LR_3\}\) is the period-3 repayment if it occurs.
\item \textbf{Probability of Choosing Commitment}:
\[
\Pr[C = \text{Commit}]
\]
\item \textbf{Financial Cost} \(F\):
\[
F \;=\;
\begin{cases}
\displaystyle
\phi \cdot \mathbf{1}_{\{C=\text{commit} \,\wedge\, m_2=0\}}
\;+\;v \;-\;L \;+\;(m_2 + m_3),
&
\text{if default occurs at }t=3,
\\[6pt]
\displaystyle
\phi \cdot \mathbf{1}_{\{C=\text{commit} \,\wedge\, m_2=0\}}
\;+\;\bigl[\,(m_2 - k) + (m_3 - (L-k))\bigr],
&
\text{if repaying in full at }t=3.
\end{cases}
\]
\noindent
Here, \(m_2 = R_2\,k\) if the borrower prepays, else \(0\); \(m_3 = R_3\,(L - k)\) if the borrower repays in \(t=3\) and $m_2 =  R_2\,k$, if $m_2=0$, then \(m_3 = R_3\,L \), otherwise it is \(m_3=0\). The term \(\phi\) arises only if the borrower is in the commitment regime, skipped \(k\), and repays. In the event of default, we add \(\,(v - L + m_2 + m_3)\). In the event of repayment, we effectively sum the “interest” portions \(\,(m_2 - k) + (m_3 - (L-k))\).
\end{enumerate}

\end{document}

### 2025-04-25 Restud submission/OA_restud.tex
First set of edits after R&R

@@
 	%\Large{Appendix $-$ For Online Publication} \\[1em]
-	\large \author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira \and Francis J.\ DiTraglia}
+	\large \author{Francis J.\ DiTraglia \and Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira}
 \end{center}
@@
     \label{weekly_def_rates}
-%\textit{Do file: } \texttt{determinants_choice.do}       
+%\textit{Do file: } \texttt{weekly_def_rates.do}       
 \end{figure}
@@
 \footnotesize{The above figure shows the determinants in a bivariate and multivariate OLS regression of choosing commitment.
-Choice commitment is a binary variable equal to one, whenever subjects choose the forced commitment contract in the choice arm.
+Choice commitment is a binary variable equal to one, whenever subjects choose the mandatory commitment contract in the choice arm.
 }
@@
 \end{figure}
+\todo[inline]{The editor found this table ``Determinants of choice'' difficult to read and suggested removing the results of the bivariate regressions}
+
+\begin{figure}[H]
+    \caption{Profit difference Mandatory vs Control arm.}
+    \begin{center}
+    \begin{subfigure}{0.65\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{Figuras/profit_mandatory_control.pdf}
+    \end{subfigure}
+    \end{center}
+\footnotesize{The above figure shows the difference in profit $\text{Profit}_{j,X}  = \sum_{t=0}^T\delta^t\{\text{Financial Cost}_j | \text{Contract}=X\}\times\Pr(\text{Repeat} | \text{Contract}=X)^t$ for the Mandatory vs Control contracts for different values of the discount rate $\delta$ and time horizon $T$.
+}
+    \label{profit_mandatory_control}
+%\textit{Do file: } \texttt{profit_difference.do}       
+\end{figure}
 
@@
 \newpage
-
-\begin{landscape}
-\subsection{Intermediate Outcomes}
-
-\begin{table}[!h]
-\caption{Effects on intermediate outcomes}
-\label{mechanisms}
-\begin{center}
-
-\scriptsize{\input{./Tables/mechanism.tex}}
-
-\end{center}
-\footnotesize{This table explores treatment effects in ``intermediate variables''.
-Each column represents regression output for different dependent variables following equation (\ref{basic_reg}).
-Panel A focuses on variables related to the speed of payment.
-While Panel B focuses on variables related to default, and Panel C related to visits.
-% The outcome variables are as follows:  number of days elapsed between origination and first payment (col 1); percentage of the loan paid in the first payment (col 2); probability of recovery in the first visit (col 3); loan duration is the number of days the borrower took to payoff her loan for those that recover, the number of days until default for those that default, and the maximum number of days we observe them in the sample for those that have not recovered or defaulted (col 4); loan duration conditional on recovery; an indicator for paying a positive amount towards recovery but nonetheless losing the pawn (col 6); the percentage or the loan paid, conditional on defaulting --`wasted payments' (col 7).
-Column 8 uses the phrase `selling the pawn' for a dummy variable indicating the borrower did not pay any amount towards recovery and lost the pawn.
-Moreover, (col 9) shows that treatment effects are concentrated in the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery.
-The dependent variable in column 10 is the number of day-visits to the branch (measured by the existence of transactions that day associated with our particular pawn), while column 11 conditions on borrowers that lost the pawn.
-Each regression includes branch and day-of-week FE. Standard errors are clustered at the branch-day level.}
-%\textit{Do file: } \texttt{mechanisms.do}
-\end{table}
-\end{landscape}
-
-\normalsize
-%Really force it to normal size and linespread
-\normalsize
 
@@
 Two features of these graphs are salient for our analysis.
-The first is the extent to which loan outcomes are observed more quickly in the forced commitment arm.
-This is primarily due to the substantially higher rate of repayment of Forced Commitment loans at 120 days (15 pp higher than the other arms).
+The first is the extent to which loan outcomes are observed more quickly in the mandatory commitment arm.
+This is primarily due to the substantially higher rate of repayment of Mandatory Commitment loans at 120 days (15 pp higher than the other arms).
 The second is the very low rate at which loans are recovered in any arm after 120 days.
@@
 The confluence of censoring and a treatment effect on censoring is potentially problematic from an experimental point of view.
-The approach taken in the headline results is a conservative one in that it inherently assumes that all of the loans outstanding at the end of the observation window will be repaid, making it so that the acceleration of payment observed in the Forced arm does not translate mechanically into the that treatment decreasing default.
+The approach taken in the headline results is a conservative one in that it inherently assumes that all of the loans outstanding at the end of the observation window will be repaid, making it so that the acceleration of payment observed in the Mandatory arm does not translate mechanically into the that treatment decreasing default.
 Nonetheless, to be certain that this issue is not driving our results we conduct a bounding exercise to understand how large the effects of this problem can possibly be.
@@
 One way of considering the effect that this issue could have on our results is to make extreme assumptions about the outcome of these loans in the treatment and control so as to bound the possible influence of censoring.
-In Table \ref{bounding_censoring} we compare the Forced and Control arms, bounding the censoring issue by reversing assumptions about the outcome of censored loans in the treatment versus the control.
+In Table \ref{bounding_censoring} we compare the Mandatory and Control arms, bounding the censoring issue by reversing assumptions about the outcome of censored loans in the treatment versus the control.
 Panel B provides the lower bound for the treatment effect (closest to zero) by assuming censored control loans are always repaid and treatment loans never are; even in this lower-bound case the treatment effect is cost-reducing and significant at the 1\% significance level and indeed the magnitude of this lower bound estimate is only 6\% closer to zero than our headline result.
@@
 Panel A, for instance, assumes that all outstanding loans are fully payed.
-Panel B is the most conservative imputation since it assumes all outstanding loans in the control arm are payed, while all the outstanding loans in the forced commitment arm default.
+Panel B is the most conservative imputation since it assumes all outstanding loans in the control arm are payed, while all the outstanding loans in the mandatory commitment arm default.
 Panel C, on the other hand, is the most optimistic scenario opposite to that of Panel B.
@@
 
+\newpage
+
 \subsection{Robustness accounting for other costs}
@@
 The result is that the likelihood of repeat business increases by 6.7\%.
-While this appears to be \emph{prima facie} evidence of greater satisfaction among borrowers in the forced arm, the interpretation is complicated by the fact that monthly payments may themselves trigger more borrowing to pay them.
+While this appears to be \emph{prima facie} evidence of greater satisfaction among borrowers in the mandatory arm, the interpretation is complicated by the fact that monthly payments may themselves trigger more borrowing to pay them.
 Note that from the lender's perspective, why repeat pawning happens may not be as important as the fact that it happens.
@@
 Column 4 only considers new loans that use different collateral from that of the initial one.
-We do this to foreclose the explanation that those in the Forced arm, being more liquidity-constrained, return to pawn a second pawn to be able to pay the monthly payments of their first loan.
+We do this to foreclose the explanation that those in the Mandatory arm, being more liquidity-constrained, return to pawn a second pawn to be able to pay the monthly payments of their first loan.
 However, we cannot reject a zero effect on pawning a different collateral.
@@
 We find that the difference between the Forcing contract and the status quo is even larger in this subsample, with the former having 11pp higher likelihood of being a repeat client during our sample period.
+
+\newpage
 
@@
 
-\begin{table}[!h]
-\caption{Lender's Profit}
-\label{lenders_profit}
-\begin{center}
- \footnotesize{\input{./Tables/lenders_profit.tex}}
-\end{center}
- \footnotesize{ The dependent variable in column (1) is the profit formula in equation (\ref{profit_function}).
-For columns (2)-(3) we compute average profit for borrower in arm $j$ according to (\ref{profit_function}).
-We then extrapolate the flow of payments over several periods depending on their repeat pawning behavior.
-In column (2) the flow of profits is given by
- \[\sum_{T=0}^{\infty}\text{Profit}_j\times\Pr(\text{Pawn}_j)^T\]
- assuming independence of repeat pawning across periods. In column (3) the stream of profits is given by
- \[\text{Profit}_j + \text{Profit}_j\times \Pr(\text{Pawn}_j) +\text{Profit}_j\times\Pr(\text{Pawn}_j) \]
- assuming that once learning (and hence repeat pawning behavior) occurs the borrower keeps coming back (we only keep 2 further periods for the exercise).
- For columns(2)-(3) we clustered-bootstrapped the standard error. All Standard errors are clustered at the branch-day level.}
-%\textit{Do file: } \texttt{lenders\_profit.do}
-\end{table}
+% \begin{table}[!h]
+% \caption{Lender's Profit}
+% \label{lenders_profit}
+% \begin{center}
+%  \footnotesize{\input{./Tables/lenders_profit.tex}}
+% \end{center}
+%  \footnotesize{Column (1) is the same as column (1) in Table \ref{main_impact_table}.
+Columns (2) shows the difference in profit for the different contract types according to equation (\ref{profit_function}), which assumes independence of repeat pawning across periods.
+In column (3) we compute the stream of profits by
+%  \[\text{Financial Cost}_j + \text{Financial Cost}_j\times \Pr(\text{Repeat Pawn}_j) +\text{Financial Cost}_j\times\Pr(\text{Repeat Pawn}_j) \]
+%  assuming that once learning (and hence repeat pawning behavior) occurs the borrower keeps coming back (we only keep 2 further periods for the exercise).
+%  We clustered-bootstrapped the standard errors at the branch-day level.}
+% %\textit{Do file: } \texttt{lenders\_profit.do}
+% \end{table}
 
@@
 
-Table \ref{learning_table} presents information about borrowers' \emph{future} pawning behavior as a function of treatment assignment.
+\textcolor{red}{The experiment was not designed to study learning, and the short time frame and sample size limit what we can say.} Table \ref{learning_table} presents information about borrowers' \emph{future} pawning behavior as a function of treatment assignment.
 Column (1) considers the 228 clients who returned only a second time to pawn again at a day/branch that was randomly assigned to the choice arm.
 Each of the two rows in this column presents a difference of mean commitment take-up rates, and associated standard error.
-The first row compares those who were \emph{initially} assigned to forced commitment against those where were assigned to control; the second row compares those who were initially assigned to the choice commitment arm to those who were assigned to the other two arms.
+The first row compares those who were \emph{initially} assigned to mandatory structure against those where were assigned to control; the second row compares those who were initially assigned to the choice arm to those who were assigned to the other two arms.
 In each case, there is no statistically discernible difference in the rates of commitment take-up.
@@
 This composite outcome variable is not subject to the sample selection problem (although it is directly driven by the decision to repeat borrow).
-The comparison in the two rows remains the same: forced commitment versus control in row one and choice commitment versus forced arms in row two.
+The comparison in the two rows remains the same: mandatory structure versus control in row one and choice versus mandatory arms in row two.
 Again, there is no statistically discernible difference in commitment take-up rates in either row.
@@
 Each row presents a difference in mean commitment take-up rates and associated standard errors.
-The first row (ATE) compares borrowers who were initially assigned to forced commitment against those were assigned to the control condition.
+The first row (ATE) compares borrowers who were initially assigned to mandatory structure against those were assigned to the control condition.
 The second row (ITT) compares borrowers who were initially assigned to the choice commitment condition to those who were not.
@@
 \normalsize
+
+\newpage
 
@@
 
-If we could perfectly measure present bias and sophistication, we could divide the sample into three groups: sophisticated hyperbolics (who chose commitment), time-consistent non-choosers (for whom forcing will not be effective), and na\"{i}ve hyperbolic non-choosers (who will benefit from forced commitment).
+If we could perfectly measure present bias and sophistication, we could divide the sample into three groups: sophisticated hyperbolics (who chose commitment), time-consistent non-choosers (for whom forcing will not be effective), and na\"{i}ve hyperbolic non-choosers (who will benefit from mandatory structure).
 %If present bias fully explains the low take-up rate of voluntary commitment, we should find that the TUT for present-biased borrowers  is positive while the TUT for all other borrowers is not.
@@
 
+\clearpage
 \newpage
@@
 
-%This section describes the testable implications of our exclusion restrictions: \eqref{eq:exclusion0} and \eqref{eq:exclusion1} from Section \ref{sec:potentialOutcomes}. 
-%To consider possible violations of these conditions, we require some additional notation.
-As above, let $Y_0 \equiv Y(d=0,z=0)$ and $Y_1 \equiv Y(d=1,z=1)$ denote the potential outcomes under \emph{forced treatment}: $Y_0$ is the potential outcome when forced into the status quo contract and $Y_1$ when forced into the commitment contract.
-Further let $Y_{0,2} \equiv Y(d=0,z=2)$ and $Y_{1,2} \equiv Y(d=1,z=2)$ denote the potential outcomes under \emph{free choice of treatment}: $Y_{0,2}$ is the potential outcome when choosing the status quo contract and $Y_{1,2}$ when choosing the commitment contract.
-Using this notation, \eqref{eq:exclusion0} becomes $Y_0 = Y_{0,2}$ and while \eqref{eq:exclusion1} becomes $Y_1 = Y_{1,2}$.
+Let $Y_0 \equiv Y(0,0)$ and $Y_1 \equiv Y(1,1)$ denote the potential outcomes under \emph{mandatory treatment}: $Y_0$ is the potential outcome when assigned to the status quo contract and $Y_1$ when mandated to the structured contract.
+Further let $Y_{0,2} \equiv Y(0,2)$ and $Y_{1,2} \equiv Y(1,2)$ denote the potential outcomes under \emph{free choice of treatment}: $Y_{0,2}$ is the potential outcome when choosing the status quo contract and $Y_{1,2}$ when choosing the commitment contract.
+Using this notation, the exclusion restrictions upon which our TUT and TOT results rely are $Y_0 = Y_{0,2}$ and $Y_1 = Y_{1,2}$.\footnote{While we assume $Y_i(d,z) = Y_i(d)$ in the body of the paper for simplicity, our derivations only rely on these two equalities.}
 Without imposing these, Assumption \ref{assump:randchoice}(iii) becomes 
@@
 \end{align}
-%Equation \ref{eq:exclusion_append0} is a restriction on the average potential outcomes of non-choosers that we use to point identify the TUT effect.
-%It says that someone who \emph{would} choose the control condition when given a choice, experiences the same potential outcome, on average, when \emph{assigned} to the control condition.
-%Equation \ref{eq:exclusion_append1} is a restriction on the average potential outcomes of choosers that we use to point identify the TOT effect.
-%It says that someone who \emph{would} choose the commitment contract when given a choice, experiences the same potential outcome, on average, when \emph{assigned} to this condition.
 Because they refer to different groups of people--choosers versus non-choosers--either of \eqref{eq:exclusion_append0}  and \eqref{eq:exclusion_append1} could hold when the other is violated.
@@
 Our approach is closely related to arguments from \cite{huber_mellace} and \cite{BinaryRegressor}, among others.
-%As such, the following is a heuristic explanation rather than a fully-rigorous proof.
-%See the aforementioned papers for more details of how to make this argument fully rigorous.
 
@@
 The same result holds for the financial cost outcome: results available upon request. 
-%Repeating this exercise for the financial cost outcome, we see that $\widehat{\mathbbm{E}}(Y_\text{FC}|D=0,Z=2) = 973$ likewise falls between 
-%\[
-%\widehat{\mathbbm{E}}(Y_\text{FC}|Z=0,Y_\text{FC}\leq y^0_{0.89}) = 626, \quad
-%\widehat{\mathbbm{E}}(Y_\text{FC}|Z=0, Y_\text{FC}\geq y^0_{0.11}) = 1046 
-%\]
 %so we again find no evidence against the exclusion restriction for non-choosers.
@@
 We can use an analogous approach to construct testable implications for \ref{eq:exclusion_append1}, yielding 
-%Because $Z$ was randomly assigned, a fraction $p$ of participants with $Z = 1$ are choosers so the distribution of $Y|Z=1$ is a mixture of $Y_1|C=1$ and $Y_1|C=0$ with mixing weights $p$ and $1 -p$.
-%The participants with $C = 1$ must lie \emph{somewhere} in the distribution of $Y_0|Z=1$ so again consider the two most extreme cases: they could occupy the bottom or the top $p\times 100\%$ of the distribution.
-%\[
-%\mathbbm{E}\left(Y|Z=1,Y\leq y^1_{p}\right) \leq \mathbbm{E}(Y_1|C=1) \leq \mathbbm{E}\left(Y|Z=1,Y \geq y^1_{1-p}\right)
-%\]
-%As above, these bounds do not rely on the exclusion restriction.
-%If Equation \ref{eq:exclusion_append1} holds, however, we know that $\mathbb{E}(Y|D=1,Z=2) = \mathbb{E}(Y_1|C=1)$, yielding the following testable implications for choosers
 \begin{equation}
@@
 The same holds for the financial cost outcome: results available upon request.
-%Repeating this exercise for the financial cost outcome, we see  that $\widehat{\mathbbm{E}}(Y_\text{FC}|D=1,Z=2)= 570$ likewise falls between
-%\[
-%\widehat{\mathbbm{E}}(Y|Z=1,Y\leq y^1_{0.11}) = 53, \quad
-%\widehat{\mathbbm{E}}(Y|Z=1,Y\geq y^1_{0.89}) = 2934
-%\]
-%so we again find no evidence against the exclusion restriction for the choosers.
-
-%The aforementioned bounds for $\mathbbm{E}(Y_0|C=0)$ and $\mathbbm{E}(Y_1|C=1)$ can alternatively be used construct partial identification bounds for the TOT and TUT effects that do not rely on our exclusion restrictions.
-If the TOT or TUT expressions from \eqref{eq:TOT} and \eqref{eq:TUT} fall \emph{outside} the partial identification bounds, this is equivalent to finding a violation of \ref{eq:testable0} or \ref{eq:testable1}.
-We implement these bounds for the TOT and TUT in our companion STATA package.
-
+
+\clearpage
+\newpage
 \section{Estimation and Inference} 
@@
 Let $g = 1, ..., G$ index clusters and $i = 1, ..., N_g$ index individuals within a particular cluster $g$. 
-In our experiment, a cluster is a branch-day combination and the experimentally-assigned treatment (control, forced, or choice arm) is assigned at the cluster level.
+In our experiment, a cluster is a branch-day combination and the experimentally-assigned treatment (control, mandatory, or choice arm) is assigned at the cluster level.
 We assume that observations are iid across clusters but potentially correlated within cluster.
@@
 
+\section{Can we target paternalism accurately?} \label{targeting}
+\todo[inline]{Now that this is in the appendix, and given that some of the sections it refers to are set to be re-organized in a substantial way, this may need to be edited later.
+We should do this after we're already happy with the body of the paper.}
+
+Even though the overwhelming majority of borrowers would save on financing costs, not all of them would, according to our estimates.
+Is it possible to target paternalism only towards those who would benefit from it?
+
+The answer depends on how predictive the covariate information is of treatment effects.
+Note that to implement a targeting protocol, the covariate information used in the model would need to be either verifiable or hard to manipulate.
+In our survey and administrative data, this leaves us with only a few covariates: age, gender, high school education or above, desired loan size, and whether that individual has ever pawned before.
+We call these the ``narrow'' covariate set, to contrast with the full set of survey variables, which we call the ``wide'' covariate set.
+We take the estimated   $\widehat{\text{CATE}}(X_i)$ using the wide covariates as our ground truth.\footnote{We assign a dummy variable equal to one for the 90\% of borrowers who have a positive CATE using the wide covariate set.
+Figure \ref{wide_narrow_forests} shows the relationship between these two different  CATEs.
+We generate substantially less heterogeneity when using the narrow covariate set, although we still reject the null hypothesis of no treatment effect heterogeneity with the test from \cite{chernozhukov2018generic}.}
+
+To investigate targeting we ask how well we can predict this ground truth using the narrow covariate set, which is the set of less-manipulable variables that the pawnlender has.
+We use both a logistic regression and a random forest classification model using the narrow covariate set to predict positive benefits at the individual level.
+We compare the in-sample performance of targeting rules against a policy of universal mandated structure.
+
+\begin{table}[H]
+\caption{Type I \& II errors using targeting narrow rules}
+\label{hit_miss_rule}
+\begin{center}
+\footnotesize{\input{./Tables/hit_miss_rule.tex}}
+\end{center}
+\scriptsize{This table reports error rates for six different rules for allocating individuals to structured repayment.
+Row 1 assigns all borrowers to control, Row 2 all to structured payments.
+Row 3 uses `optimal targeting according to the CATE from the wide covariate set.
+Row 4 uses a random forest classification, and Row 5 a logit model, both with only the narrow covariate set.
+Row 6 uses the choices made by borrowers.
+%DoFile : wide_narrow_forests.do
+}
+\end{table}
+
+\todo[inline]{The editor asks: ``how is “Overall Error Rate” computed in Table 5?
+(Type I and II errors using targeting narrow rules) It’s always the sum of the previous columns except for the last row.''}
+
+Table \ref{hit_miss_rule} shows error rates for six possible assignment rules: assigning all borrowers to Status quo, all to structured payments, the optimal (wide-fores), the random forest with narrow covariates, the Logistic model with narrow covariates, and the actual choice made by borrowers.
+All models take the wide RF as the ground truth.
+While the narrow RF correctly assigns to control roughly half of those who do not benefit from the structures payment contract, it also incorrectly allocates to control 4.38\%  that would gain from structured payments.
+As such, it only improves the overall correct targeting rate by about half of a percentage point relative to universal structure.
+The Logit assignment rule is even less successful at predicting benefits and harms, with a higher share of borrowers incorrectly assigned to both treatment and control, meaning that the overall correct targeting rate for the Logit is 5 pp \textit{lower} than universal structure to structured payments.
+Self-targeting through choice proves to be little better than assigning everyone to the Status quo contract, given the low take-up rate and the presence of both Type I and Type II errors in the choice arm.
+
+The takeaway is that given (a) low take-up, (b) the large fraction of the sample benefiting from structure, (c) and the weak predictive power of the narrow covariates, universal paternalism assigning all borrowers to the strutured contract appears to be an attractive targeting method in our context.
+
 \end{appendix}

### 2025-04-25 Restud submission/Responses to 1st round ReStud/Response to R1.tex
First set of edits after R&R

% !TeX root = editor_letter.tex
% !TEX TS-program = pdflatex
% !TEX encoding = UTF-8 Unicode
% !TEX output_directory = .texpadtmp

\documentclass[11pt, colorinlistoftodos]{article} % otra posibilidad es [openany]{book}

\input{preamble} % document preamble
%\input{commands}

% To-do commands (must go after authblk to avoid clash)
\usepackage{todonotes}
\usepackage{marginnote}
\renewcommand*{\marginfont}{\color{red}\sffamily\scriptsize}
\setlength{\marginparwidth}{2cm}  % prevent todo cutoff
\newcounter{todoListItems}
\newcommand{\todoLink}[2][ ]{
  \addtocounter{todoListItems}{1}
  \todo[caption={\protect\hypertarget{todo\thetodoListItems}{}Translation},size=\scriptsize,#1]{
    \scriptsize #2 \hfill \hyperlink{todo\thetodoListItems}{$\uparrow$}
  }
}
\newcommand{\forES}[1]{\todoLink[color=green!20,inline,caption={\thetodoListItems: For @Enrique}]{\textbf{@Enrique} -- #1}}
\newcommand{\forIM}[1]{\todoLink[color=blue!20,inline,caption={\thetodoListItems: For @Isaac}]{\textbf{@Isaac} -- #1}}
\newcommand{\forFdT}[1]{\todoLink[color=red!20,inline,caption={\thetodoListItems: For @Francis}]{\textbf{@Francis} -- #1}}
\newcommand{\forCM}[1]{\todoLink[color=violet!20,inline,caption={\thetodoListItems: For @Craig}]{\textbf{@Craig} -- #1}}
\newcommand{\forAll}[1]{\todoLink[color=orange!20,inline,caption={\thetodoListItems: For All}]{\textbf{@All} -- #1}}

\newcounter{point}
\setcounter{point}{0}
\def\thepoint{\alph{point}}

\newenvironment{point}{\refstepcounter{point}\noindent\textbf{Point~(\thepoint)~}\hrulefill\newline\itshape\small}{\par\vspace{-1.25em}\noindent\hrulefill}
\setlength {\marginparwidth }{2cm} 
%----------------------------------------------------------------------------------------
%	INICIO DEL DOCUMENTO
%----------------------------------------------------------------------------------------
\begin{document}

\listoftodos

\noindent \textbf{Letter to Referee 1}
\vspace{.3in}

\noindent
Dear Referee 1,

 Thank you for your very encouraging review. We agree with your that ``the experiment is designed around an understudied and important market'' that ``It delivers credible results that speak both locally to the functioning of the market of interest and more broadly to consumer sophistication in general.'' And that ``the methodological component expands the potential impact of the manuscript beyond the current research questions in consumer finance and will likely inspire similar designs in other areas''.

You correctly point to several improvements in terms of structure, organization, and consistency of language. We agree with you and have closely followed your suggestions.

% \vspace{.4in}
% \noindent \textbf{1. Mechanisms}
% \vspace{.2in}

\vspace{.2in}
\textcolor{red}{R1, }\begin{point} 
Commitment Contracts or Structured Payment Plans: the manuscript jumps between describing their experimental pawn contract as a structured payment plan or as a commitment contract. The latter terminology is not sufficiently descriptive: even the status quo contract generates a cost (collateral forfeiture) upon failure to complete a future action (timely repayment) and so constitutes a commitment. Readers will benefit from a single term for the experimental pawn contract and `structured payment plan’ distinguishes it from the status quo and is easily understood.
\end{point}

Agreed. We don't use ``commitment contract'' as a label, and instead refer to it as structured payments or structured payment plan.

\vspace{.2in}
\textcolor{red}{R1, }\begin{point} 
Unsubstantiated Claims of Subject Comprehension: When describing the explanation of structured payment plans to subjects, the authors make several unsubstantiated claims that should be eliminated from the text. This includes saying “we made sure clients understood the contract terms” and “we are confident the overwhelming majority of clients understood the contracts and that those in the choice arm made informed choices.” It may be fair to say that the experiment made efforts to aid comprehension and describe the design details, but the text should stop short of claims such as those above. 
\end{point}

We agree also. We have now removed this language and focus on the objective steps the team took to deliver the information in a comprehensible way.

\vspace{.2in}
\textcolor{red}{R1, }\begin{point} 
Ordering of Results: The presentation of experimental results follows a somewhat jumpy path. After describing the basics of treatment balance, a standard experimental analysis is conducted examining average treatment and intent to treat effects. Then substantial discussion is provided of an online appendix table on intermediate outcomes. Then, the authors present a potential outcomes framework and discuss additional objects of interest such as the distribution of individual treatment effects, treatment on treated and untreated, selection effects, and then more details on the distribution of treatment effects. The manuscript would be more effective if there was an overarching framework for considering all (or most of) the results. This could be achieved by presenting the potential outcomes framework first along with the assumptions that deliver TOT and TUT as a way to understand the experimental design and what it can deliver (Figure 2 is particularly compelling for conveying what one gets from the mandates vs. choice design). Then one could proceed to results without interruption for presenting a new empirical framework. It would also seem natural to consider the headline aggregate findings before delving into the distributions of treatment effects. The discussion of intermediate outcomes may fit best in an appendix alongside table OA-2.

\end{point}

\forFdT{Frank can you take this?  --ES}

\vspace{.2in}
\textcolor{red}{R1, }\begin{point} 
Proofreading: The manuscript has quite a few remaining spelling and grammar errors and would benefit from a thorough proofread. It also seems that moving from section to section the tone changes from formal to conversational. And consistency of vocabulary would be desirable for things like TOT, TUT, “mandates vs. choice” vs. “universal vs. choice” vs “mandates-choice”

\end{point}

Thanks. We have converged on using ''mandates vs. choice'', have corrected typos, and now one person has edited all the sections for style.

\forCM{Craig, can you edit for section to section the tone changes?  --ES}

\vspace{.2in}
\textcolor{red}{R1, }\begin{point} 
Concluding Thoughts: Given that one of the primary contributions of the manuscript is the “mandates vs. choice”  experimental design, it might be helpful to say more about broader applicability in the conclusion beyond the second paragraph. Expanding on footnote 18 might be useful for making the case for the mandates vs choice approach.   
\end{point}

We believe that the design would be used profitably in many domains. The domain has to be such that some experimental arms are mandated and display high compliance, and other arms involve choice. For example, in medical research, new drugs are tested by allocating treatment and placebo with high compliance, but in some cases patients can have opt-out options. In environmental research, consumers are often faced with choices or mandates for energy-saving technologies, with costs and benefits on each side. In educational environments schools design core versus optional curricula to maximize learning. In financial settings, e.g. insurance products, consumers often decide on the sizes of deductibles and premia, but government could (and often do) mandate some minimum. In labor market settings, employers may mandate participation in default retirement savings plans or workplace wellness programs, while offering opt-out clauses. In digital platform design, users are sometimes required to accept some privacy terms while retaining discretion over others specific sharing settings (choice).

These examples suggest a broad applicability of the design to settings where institutional where take-up behavior and downstream effects can be studied under each regime.

Thank you for your thoughtful comments.

%\begin{point} this is point a
%\end{point}

%\textcolor{red}{ENRIQUE}

% REFERENCES ======================================================
%\cleardoublepage
%\singlespacing
%\bibliographystyle{chicago}
%\bibliography{References.bib}
%\printbibliography
\end{document}

### 2025-04-25 Restud submission/Responses to 1st round ReStud/Response to R4.tex
First set of edits after R&R

% !TeX root = editor_letter.tex
% !TEX TS-program = pdflatex
% !TEX encoding = UTF-8 Unicode
% !TEX output_directory = .texpadtmp

\documentclass[11pt, colorinlistoftodos]{article} % otra posibilidad es [openany]{book}

\input{preamble} % document preamble
%\input{commands}

% To-do commands (must go after authblk to avoid clash)
\usepackage{todonotes}
\usepackage{marginnote}
\renewcommand*{\marginfont}{\color{red}\sffamily}
\setlength{\marginparwidth}{2cm}  % prevent todo cutoff

\newcounter{todoListItems}
\newcommand{\todoLink}[2][ ]{
  \addtocounter{todoListItems}{1}
  \todo[caption={\protect\hypertarget{todo\thetodoListItems}{}Translation},#1]{
    #2 \hfill \hyperlink{todo\thetodoListItems}{$\uparrow$}
  }
}
\newcommand{\forES}[1]{\todoLink[color=green!20,inline,caption={\thetodoListItems: For @Enrique}]{\textbf{@Enrique} -- #1}}
\newcommand{\forIM}[1]{\todoLink[color=blue!20,inline,caption={\thetodoListItems: For @Isaac}]{\textbf{@Isaac} -- #1}}
\newcommand{\forFdT}[1]{\todoLink[color=red!20,inline,caption={\thetodoListItems: For @Francis}]{\textbf{@Francis} -- #1}}
\newcommand{\forCM}[1]{\todoLink[color=violet!20,inline,caption={\thetodoListItems: For @Craig}]{\textbf{@Craig} -- #1}}
\newcommand{\forAll}[1]{\todoLink[color=orange!20,inline,caption={\thetodoListItems: For All}]{\textbf{@All} -- #1}}

\newcounter{point}
\setcounter{point}{0}
\def\thepoint{\alph{point}}

\newenvironment{point}{\refstepcounter{point}\noindent\textbf{Point~(\thepoint)~}\hrulefill\newline\itshape\small}{\par\vspace{-1.25em}\noindent\hrulefill}
\setlength {\marginparwidth }{2cm} 
%----------------------------------------------------------------------------------------
%	INICIO DEL DOCUMENTO
%----------------------------------------------------------------------------------------
\begin{document}

\noindent \textbf{Letter to Referee 4}
\vspace{.3in}

\noindent
Dear Referee 4,

Thank you for the very encouraging revision. You write that ``This is a fascinating and rich paper that makes important contributions both substantively and methodologically. Either of these contributions is probably worthy of a top-tier econ journal placement on its own...I agree that the pawn market has been understudied in econ.'' You also write that you ``love the paper’s methods focus on using a relatively simple field experiment design to help identify treatment effects of vital importance for both basic and applied research'' and that ``that menus—what I mean here is giving people different choice sets—seem to be understudied and underutilized in applied economics''. We agree with all these statements.

We also agree that the paper could further improve along several dimensions which you mention. We now go through all your points and explain how we respond to each of them.

\vspace{.4in}
 \noindent \textbf{Must-do}
 \vspace{.2in}

\noindent  1. Be more judicious in inference about “null” results. (The paper is overconfident about some of its inferences haha.

\vspace{.2in}
\textcolor{red}{R4, }\begin{point} 
Statistically speaking, the paper focuses too much on point estimate and
arbitrary p-value cutoffs, and not nearly enough on confidence intervals. This
applies to both design integrity checks (Section 3.4) and treatment effect
inference.
\end{point}

\forCM{Include nuance and confidence intervals when we talk about results. Cite the new paragraphs here}.

\vspace{.2in}
\textcolor{red}{R4, }\begin{point} 
With respect to present bias in particular, there is the added issue of
measurement error that must be foregrounded if the lack of evidence for present bias present-bias mediating the results continues to be foregrounded. I agree with everything that is currently relegated to fn20, and would add that:
i. for theory about the primacy of present bias over consumption related to
your setting and application, see Heidhues and Koszegi (2010 AER) and Allcott et al (2022 RESTUD)
ii. additional cites re: innovations in measurement of discounting biases over money: Allcott et al and Carrera et al (2022 RESTUD)
\end{point}

\forES{Enrique brings the footnote to the text, acknowledges PB could have measurement error, and cites the 3 papers mentioned here.  --ES}

\vspace{.2in}
\textcolor{red}{R4, }\begin{point} 
The paper also claims a null (set) regarding previous work on pawn lending.
Caskey (1991 JMCB) would seem to falsify that—and his subsequent book,
which may have been more influential than the article—and some quick Google
Scholar searches turned up several other papers. You should position your
paper based on quality, and/or on more specific claims about what you’re the
first to do.
\end{point}

\forES{Enrique includes a paragraph citing Caskey (1991 JMCB) and Bos et al working paper  --ES}

\vspace{.2in}
\textcolor{red}{R4, }\begin{point} 
The paper also claims an institutional null, for motivation purposes: no other
standard credit contract offers flexibility comparable to pawns (see e.g., the first
sentence of Abstract). To establish this convincingly, I think you need to have
some discussion of the (lack of) prevalence of comparable flexibility in at least
two types of contracts that come to mind: i) line of credit without periodic min
payment requirements; ii) shorter-maturity installment loans, like payday loans,
that can be rolled over or refinanced indefinitely without any min repayment
requirement.
\end{point}

\forCM{I would just say it a very flexible contract, without saying which is more flexible, and not fight the referee.}

\vspace{.2in}
\noindent \textbf{ 2. Be more thorough in analyzing and discussing mechanisms underlying your results.}

\setcounter{point}{0}
\vspace{.2in}
\textcolor{red}{R4, }\begin{point} 
My main comment here is that it’s unclear, theoretically, how mandated repayment structure cures overconfidence. To me this highlights that, for your purposes, overconfidence about repayment may be too reduced-form of an object to infer much about mechanisms underlying your treatment effects and about related questions such as policy implications.

i. If I’m overconfident about scraping together the cash to make the balloon payment, why doesn’t that lead me to ignore the structure, particularly given the modest commitment provided by structure (indeed, it seems like there is basically zero financial commitment, in the sense that the cost of getting to the branch to make the payment cancels out benefit of avoiding the late fee).
\end{point}

\forAll{This is where Isaac's model will come in. It is a question about both: (a) how PB is different from overconfidence (i.e. the reduced form part); and (b) how theoretically OC can lead to large TUT. --ES}

\noindent Thanks. This is a very interesting comment that has several points to it. We will try to parse it into several parts.

\begin{enumerate}
    \item On ``overconfidence about repayment may be too reduced-form of an object to infer much about mechanisms''. We interpret this as saying that several models can generate borrowers over predicting payment. This is correct. One way to model overconfidence is by borrowers having stochastic income streams: while some borrowers have the correct beliefs about the distribution function generating this income, overconfident borrowers (incorrectly) believe their distribution is right-shifted.  It is not hard to write a simple model where this incorrect belief generates overprediction of recovery, more backloaded payments, and more default than correct beliefs would generate. We wrote one such model in Appendix \hl{XXX}. One can also generate those outcomes with a beta-delta present bias model with naivite. Indeed, \cite{heidhues2010} write such a model. Future work could more thoroughly test if present-bias or over-estimation of future income is more important. With our measures, we found present bias not to predict TUT.  Not that our experimental intervention requiring frequent payments would work theoretically under both present bias and overconfidence of income models. 
    \item The paper does not claim that ``mandated repayment structure cures overconfidence''. But it does show it modifies behavior towards paying earlier and defaulting less. Behavior changes not necessarily because beliefs change but potentially because constraints (payment structure) do. A treatment one could try to implement to correct overconfidence could be to inform people of personalized statistical predictions about payment and recovery.\footnote{Along the lines of one of these paper's cauthors here: \cite{sadka2024information}.}
    \item On  ``If I’m overconfident about scraping together the cash to make the balloon payment, why doesn’t that lead me to ignore the structure, particularly given the modest commitment provided by structure (indeed, it seems like there is basically zero financial commitment, in the sense that the cost of getting to the branch to make the payment cancels out benefit of avoiding the late fee).''  There is an empirical question and a theoretical question about mechanisms embedded here. First, the empirical fact is this ``modest'' commitment was sufficient to cause economically large and statistically significant changes in behavior and outcomes. Borrowers did \textit{not} ignore the structure, and in that sense, it was not modest for them. A second question is what mechanism can explain this fact. Let's start by focusing on the ATE. What structured payments do is, all else constant, impose a cost for not paying each month. In our typology: neoclassical, present biased sophisticated, present bias naives, or income-overconfidents would all pay more compared to the counterfactual of the status quo contract simply because we are making it more costly not to pay. That is, being overoptimistic about your future income does not imply that you ignore the cost of your actions today. Recall that we are here comparing two overconfident borrowers, one in the status quo arm and the other in the structured payments arm.
    \item Another way to interpret R4's question is Why would a modest fee have the significant effect the data revealed. Based on \cite{beshears2016beyond} we argue that a modest fee may matter as it could: 1) circumvent limited attention, 2) set a reference point, 3) fight forgetfulness, 4) be a trigger-cue acting as a recommendation to act, 5) set a goal (which have been shown to work even without punishment\footnote{See for instance \cite{locke1990theory, heath1999goals}.}), 6) increase salience \citep{bordalo2013salience}. Note that several papers show that making a plan with no pecuniary penalty has had significant effects on behavior in many domains \citep{nickerson2010voting,milkman2011using,milkman2013planning}. Although we cannot separately identify which of these potential mechanisms could be generating the effects, our result does not run counter to other findings in the literature. 
    \item R4 may be asking if overconfident borrowers would respond more to structure than other types of borrowers (i.e. a comparison across borrower types rather than across experimental arms)? There are two ways to answer this question. Empirically, we do find that the effects are, in fact, larger for those we classify as overconfident using our measure. Theoretically, we write a simple three-period model with concave consumption utility that generates this result. The intuition is the following. Start from period 2, where borrowers contemplate making an interim payment of size k, trading off lower liquidity in that period against lower debt (and therefore lower interest and larger probability of recovering). Take the marginal non-overconfident borrower who is indifferent in that tradeoff. If we now make this borrower overconfident and increase her expected period 3 income (all else constant), the borrower will now prefer not to pay the interim payment (or pay less) since the future self is richer and the cost of paying in terms of marginal utility will be lower for the future self. So R4 is correct that overconfident borrowers would postpone payment to the future and make less interim ones, only to find that they cannot pay. \forIM{Does sureconfidence predict default in levels $Y_0$?} That is precisely the reason why if they were forced do more interim payments their TUT would be larger. Now, they are not forced but encouraged through a fee.\forCM{My problem is that for the same reason as above, the overconfident will be \textit{more} willing to pay the fee than a non-overconfident since for their period 2 self liquidity is worth more than for their period 3 self.}

\end{enumerate}

\setcounter{point}{0}
\vspace{.2in}
\textcolor{red}{R4, }\begin{point}  \setcounter{point}{0}
Continued...
ii. Your informal theory here seems to be that the late penalty payment provides commitment, but see above about the lack of financial
commitment and also consider why accruing interest at 7\%, compounded daily, is not commitment enough.
iii. A related consideration is how your interpretation of a commitment effect
squares with your inference that present-bias is unimportant (see Allcott et al 2022 on this and the point above). Do you, or others, have some theory of how commitment operates on beliefs but not discounting?
\end{point}

Thanks. On point (ii): the payment structure we introduce may operate in several ways (we posited six possibilities based on the literature) as explained above, and not all of them are commitment-related (in fact, we have mostly eliminated the word commitment and focused on the word ``structure'' for this reason). We agree that accruing interest at 7\%, compounded daily, creates an incentive to pay early. However, that is held constant across experimental conditions.  The experimental result is that the extra payment structure (on top of the interest rate) generates earlier payments and more recovery.

On point (iii): we do not claim that present bias could not theoretically generate the results we observe. On the contrary, the model in Appendix \hl{XX} shows it can potentially deliver them, depending on exact parameter values. The modest claim we make in the paper is that our measure of present bias does not predict the TUT effect. This, of course, can be due to our measure being noisy. In the previous version of the paper we acknowledged this by writing in the paper that \hl{``...''}. Now we are more emphatic in indicating to the reader that this is a real and likely possibility and write the following: \hl{``...''}.

On the last part of the question on how commitment may operate on beliefs but not discounting, we understand that you are asking if we can write a model where structured payments could generate positive ATE and TUT effects for overconfident borrowers even if they are not present-biased. We show one model that generates this in the appendix. Commitment does not change beliefs in the model (recall that beliefs are not an outcome we measure), but it does change behavior in a way that could rationalize our empirical results qualitatively. The paper you cite above, \cite{predatory2022}, does talk in the introduction as if present-focus (preferences) were in principle separate from over-optimism of the financial situation\footnote{``if borrowers are “naive” about their present focus, over-optimistic about their future financial situation, or for some other reason do not anticipate their high likelihood of repeat borrowing, they could underestimate the costs of repaying a loan. In this case, restricting credit access might make borrowers better off''.} and this is indeed how we wrote the appendix model.

\setcounter{point}{0}
\vspace{.2in}
\textcolor{red}{R4, }\begin{point} 
Continued...
iv. Having a structured payment arm without a penalty fee would be useful
for interpreting the results. It sounds like you have such an arm, and
other related arms, but are saving those for another paper (fn 7). Seems
like those arms probably belong in this paper.
\end{point}

\setcounter{point}{0}
\vspace{.2in}
\textcolor{red}{R4, }\begin{point} 
Continued...
v. Usuallly our first thought for treating a mistaken or biased belief like
overconfidence is to treat the belief itself (e.g., Bertrand and Morse). Even
more so if the belief is not about preferences, broadly defined, as is the
case with present bias. So why the focus on structured payments and not
on, e.g., belief-focused treatments? This is something to tee up for future
work, in the Conclusion, if nothing else.
\end{point}

\vspace{.2in}
\textcolor{red}{R4, }\begin{point} 
Another comment is that it’s useful to engage with related literature on how
behavioral biases like overconfidence can persist, even in a high-stakes setting
with lots of feedback <-> opportunities for learning
i. Pfauti, Seyrich, and Zinman offer some discussion about this that is
specific to overconfidence.
ii. There is theory and empirical work specifically focused on (not) learning
about one’s specific biases... Josh Schwartzstein’s papers are a good
entry point. Heidhues, Koszegi, and co-authors also might have good
work on this.
iii. Enke and co-authors’ work, and the “cognitive turn” in behavioral econ
more generally, also seems relevant here: if many biases (like oc, and/or
present-bias) emerge from an underlying cognitive process like limited
processing power or cognitive noise, then the well-documented
persistence of cognitive skills could explain the persistence of emergent
biases.
\end{point}

\forAll{Craig and me should read these papers and discuss}

\vspace{.2in}
\noindent \textbf{3. Engage more with related results from other papers}

\setcounter{point}{0}
\vspace{.2in}
\textcolor{red}{R4, }\begin{point} 
Allcott et al offer a new debt reduction commitment contract in a similar market,
borrowers value it, but it does not seem to produce its intended effects. Seems
like you find the opposite, in some sense... what might explain the differences? Do you find any sort of gradient between forecast errors and
experience?
\end{point}

\forIM{Can you show in a regression if more experienced borrowers predict better?}

\vspace{.2in}
\textcolor{red}{R4, }\begin{point} 
Allcott et al find that experienced borrowers in a similar market are well-
calibrated about their repayment likelihood, even though their borrowers are predicting something that is plausibly more difficult to predict than paying off a
single loan. You find less sophistication overall. What might explain the
difference? Do you find any sort of gradient between forecast errors and
experience?
\end{point}

\vspace{.2in}
\textcolor{red}{R4, }\begin{point} 
Virhriala (JFE) on liquidity-constrained borrowers forgoing free mortgage
payment flexibility seems more consistent with your findings....
\end{point}

\vspace{.2in}
\textcolor{red}{R4, }\begin{point} 
See also my point below on costly failed commitment from partial adherence to
multi-payment commitment contracts in other domains
\end{point}

\vspace{.2in}
\noindent \textbf{4. Revisit your APR exposition and calculation}

\setcounter{point}{0}
\vspace{.2in}
\textcolor{red}{R4, }\begin{point} 
I think you are including the actual pecuniary cost of defaulting, not the expected
cost as stated on p.10. The expected cost would average across defaulters and
non-defaulters, and your notation on p. 10 is at the individual borrower or pawn
level.
\end{point}

\forCM{R4 is right that we are using realized rather than expected cost. We need to write here why. }

\vspace{.2in}
\textcolor{red}{R4, }\begin{point} 
I don’t understand how 7\% monthly interest, compounded daily, equates to a
sample mean APR of 57\%. 7\% monthly on declining balance should be at least
84\% APR, even before accounting for compounding and pecuniary default costs.
\end{point}

\forCM{R4 is right that we are using realized rather than expected cost. We need to write here why. }

\vspace{.2in}
\noindent \textbf{5. Did you pre-register? If yes, link to the relevant docs... if not, explain why not.}

\vspace{.2in}
\noindent \textbf{6. Clarify what you mean by the last two sentences on p. 20: “Having said this, a large literature focuses on the cost of servicing loans. We follow in the steps of that the
literature.”
}

\vspace{.2in}
\noindent \textbf{7. Athey et al. estimator. My understanding is that an essential first step here, omitted from the paper, is validating the model with tests of Mean Forest Prediction and
Differential Forest Prediction. For a recent implementation in household finance see,
e.g., Burke et al (2023 RFS).
}

\forFdT{Is this the same as the Chernusukov heterogeneity test? Can we make R4 happy by implementing the same test he implements in Burke et al (2023 RFS)? i.e. Mean Forest Prediction and
Differential Forest Prediction}

\vspace{.3in}
\noindent \textbf{STRONGLY CONSIDER DOING}

\vspace{.2in}
\noindent \textbf{1. Broadening the motivation to engage with the commitment vs. flexibility literature outside of loan contracting.}

\setcounter{point}{0}
\vspace{.2in}
\textcolor{red}{R4, }\begin{point} 
Broadly, “hard” commitments have come under fire, particularly when the target
market includes liquidity constrained consumers in risky environments (as is
clearly the case in your setting)—e.g., I think Laibson has a paper on this, and
several papers by Taubinsky and various co-authors—and/or when the
commitment contract is new and/or potentially confusing (Carrera et al
RESTUD).
\end{point}

\vspace{.2in}
\textcolor{red}{R4, }\begin{point} 
Also n.b. is the failed commitment accompanied by very costly partial
adherence to the contract is a common feature of other multi-payment
commitment contracts (see e.g., the literatures on savings, smoking cessation,
exercise....)
\end{point}

\vspace{.2in}
\noindent \textbf{2. Broaden the motivation to engage with nudging, including defaults. Seems like your design helps with, for example, identifying when to use a strong (sludgy) opt-out
default. }

\vspace{.2in}
\noindent \textbf{3. Add to motivation on commitment—or at least benefit of payment structure—in loan contracting... the Mortgages as Piggy Banks paper (QJE I think) seems relevant here.}

\vspace{.2in}
\noindent \textbf{4. Consider the importance of higher moments in the distribution of key outcomes. Allcott et al shows that accounting for risk aversion <-> concavity in the utility function is crucial.
}

\vspace{.2in}
\noindent \textbf{5. Adding a bit more detail on pawn shop cost structure. In particular, I’m wondering why interest rates are so high and LTV so low (especially if appraised value << market value, as suggested in a different section of the paper) ... is this mostly due to operating costs, or is there also a substantial component of risk re: gold prices?}

\vspace{.2in}
\noindent \textbf{6. Adding a bit more detail on borrowers’ high-cost credit (outside) options, to help with thinking about how closely your results map into welfare implications. What are the closest substitutes for pawning?}

\vspace{.2in}
\noindent \textbf{7. I may just be missing this, but I couldn’t find any confirmation of the other key aspect of treatment assignment compliance besides take-up: that borrowers in the no-choice arms got their assigned contract.}

\vspace{.2in}
\noindent \textbf{8. I think partial repayment (what you call “payment bifurcation” on p. 19) is the best welfare proxy you have. I would make this a main outcome.}

\forAll{I agree. Lets bring this table to the paper.}

\vspace{.2in}
\noindent \textbf{9. I would create a single standardized index of your main outcomes... otherwise you’re begging the question of why you’re not adjusting for multiple hypothesis testing.}

\vspace{.3in}
\noindent \textbf{OTHER COMMENTS}
\vspace{.2in}

\textbf{1. Fn 4 is missing cites}

\textbf{2. Define “CONSORT”}

\textbf{3. Fn17 is confusing, as it implies that at least one of your key estimates is done with
the randomization strata. Why not always include the strata?}

\forIM{Include strata in all results}

\textbf{4. Typo: “wide-fores”}

\textbf{5. Typo: “panw”}

\vspace{.2in}
Thank you for your thoughtful comments.

%\begin{point} this is point a
%\end{point}

%\textcolor{red}{ENRIQUE}

% REFERENCES ======================================================
\cleardoublepage
\singlespacing
\bibliographystyle{chicago}
\bibliography{References.bib}
%\printbibliography
\end{document}

### 2025-04-25 Restud submission/Responses to 1st round ReStud/Response to R5.tex
First set of edits after R&R

% !TeX root = editor_letter.tex
% !TEX TS-program = pdflatex
% !TEX encoding = UTF-8 Unicode
% !TEX output_directory = .texpadtmp

\documentclass[11pt, colorinlistoftodos]{article} % otra posibilidad es [openany]{book}

\input{preamble} % document preamble
%\input{commands}

% To-do commands (must go after authblk to avoid clash)
\usepackage{todonotes}
\usepackage{marginnote}
\renewcommand*{\marginfont}{\color{red}\sffamily}
\setlength{\marginparwidth}{2cm}  % prevent todo cutoff

\newcounter{todoListItems}
\newcommand{\todoLink}[2][ ]{
  \addtocounter{todoListItems}{1}
  \todo[caption={\protect\hypertarget{todo\thetodoListItems}{}Translation},#1]{
    #2 \hfill \hyperlink{todo\thetodoListItems}{$\uparrow$}
  }
}
\newcommand{\forES}[1]{\todoLink[color=green!20,inline,caption={\thetodoListItems: For @Enrique}]{\textbf{@Enrique} -- #1}}
\newcommand{\forIM}[1]{\todoLink[color=blue!20,inline,caption={\thetodoListItems: For @Isaac}]{\textbf{@Isaac} -- #1}}
\newcommand{\forFdT}[1]{\todoLink[color=red!20,inline,caption={\thetodoListItems: For @Francis}]{\textbf{@Francis} -- #1}}
\newcommand{\forCM}[1]{\todoLink[color=violet!20,inline,caption={\thetodoListItems: For @Craig}]{\textbf{@Craig} -- #1}}
\newcommand{\forAll}[1]{\todoLink[color=orange!20,inline,caption={\thetodoListItems: For All}]{\textbf{@All} -- #1}}

\newcounter{point}
\setcounter{point}{0}
\def\thepoint{\alph{point}}

\newenvironment{point}{\refstepcounter{point}\noindent\textbf{Point~(\thepoint)~}\hrulefill\newline\itshape\small}{\par\vspace{-1.25em}\noindent\hrulefill}
\setlength {\marginparwidth }{2cm} 
%----------------------------------------------------------------------------------------
%	INICIO DEL DOCUMENTO
%----------------------------------------------------------------------------------------
\begin{document}

\listoftodos

\noindent \textbf{Letter to Referee 5}
\vspace{.3in}

\noindent
Dear Referee 5,

Thank you for your very encouraging review. You write that ``This is a very interesting paper that I enjoyed reading.'' and that you ``think it should go in a good journal'' not that there is not enough for a journal like REStud, owing to lack of clarity on mechanisms/welfare/policy implications.

We took your comments to heart, and below, we made progress on some of them. However, we disagree about the contribution of the paper. We see the paper as having three core strengths: (1) to estimate TOT and TUT in a rigorous way with weaker assumptions that the literature now employs using a new experimental design that can be useful beyond this paper; (2) to provide much-needed information about the pawn lending industry which we think will draw the attention of researchers and regulators\footnote{Indeed R4 goes as far as suggesting that just the descriptives could merit publication in a top-5 journal.}; (3) to assess if there is consumer demand for structured payments.

The cost of doing the study in this industry with one of the largest lenders was that we did not have borrowers' contact information and could only implement a 5-minute survey. This limits preference elicitation and what we can do to study mechanisms, and that is why we were cautious and short in section 6.1. There are different kinds of papers in top-5 general publications, including papers that just present stylized facts unknown before, or document important consumer behavior. This paper studies an unstudied industry that affects tens of millions of people, uses high-quality data to describe its workings and striking stylized facts, innovates on RCT design, and estimates parameters that would be useful for considering policy (ATE, TOT, TUT, and others). These are significant contributions, but indeed, just the first word rather than the last one in a research agenda.

% \vspace{.4in}
% \noindent \textbf{1. Mechanisms}
% \vspace{.2in}

\vspace{.2in}
\textcolor{red}{R1, }\begin{point} 
In the structured contract, the penalty for not meeting the first or second installments was very small: 2 percentage points of the loan. This is truly small compared to the value of the pawn, so it's odd that this small penalty could decrease the probability of losing the pawn by 15\%, and overall decrease the costs relative to control by 22\%.

What could explain why repayment behavior was so elastic relative to such a relatively small incentive for starting repayment early? While overconfidence might explain extensive margin choice (i.e., the strong preference for unstructured contracts), it does not explain why the structured contract is effective in the first place. In fact, overconfidence might even imply the opposite: if I'm wildly over-optimistic and think I'm going to have a huge payday in 2 months, then I'll be willing to incur an additional small 2\% fee now, and wait to repay my loan until I have a lot more liquidity.

A simpler explanation for why behavior is so elastic might simply be that borrowers go to another lender, and take out a loan that covers the first and/or second installment. Since this paper is based on admin data from only one lender, this explanation cannot be ruled out. Of course, if this is the bulk of what's going on, then the implication probably is that the structured contract is highly inefficient.

\end{point}

\vspace{.2in}
\textcolor{red}{R1, }\begin{point} 
Minimizing fees paid without holding all else equal is not equivalent to increasing welfare. The structured contract gets people to start repaying the loan earlier, and that might be a costly inconvenience that is not taken into account in the paper's conclusion that the structured contract is great. To see my point as starkly as possible, imagine a loan that must be repaid the next day. With a 1-day deadline, most people would be able to repay it (and thus save on fees), because they would probably just use the amount they borrowed to repay. But then, that of course defeats the whole purpose of taking out the loan in the first place. While this example is obviously just for purposes of illustration, it does illustrate that when it comes to borrowing and repayment speed, you cannot evaluate which loan products are better or worse for people if you just look at total fees paid, without holding constant people's liquidity over the repayment cycle.
In sum, the headline conclusion of this paper, "We show that structured repayment benefits nearly all borrowers, including those who would not freely choose it, and find no evidence of selection on gains," is unfortunately not supported by the data and analysis.
\end{point}

\vspace{.2in}
\textcolor{red}{R1, }\begin{point} 
Minor: I don't think "A number of papers have found low demand for commitment" is an accurate description of the literature. Relative to what benchmark? I suggest the authors take a look at Carrera et al. (2022) "Who chooses commitment?" (That paper also extensively documents the relationship between choice, treatment effects, preferences, and beliefs, so probably worth discussing in that light as well).
\end{point}

\vspace{.3in}
Thank you for your thoughtful comments.

%\begin{point} this is point a
%\end{point}

%\textcolor{red}{ENRIQUE}

% REFERENCES ======================================================
%\cleardoublepage
%\singlespacing
%\bibliographystyle{chicago}
%\bibliography{References.bib}
%\printbibliography
\end{document}

### 2025-04-25 Restud submission/donde_restud-FIRST-DRAFT.tex
First set of edits after R&R

--- 2024-06-07 Restud submission/donde_restud.tex
@@
 
-\title{The forcing-choice design and paternalism in pawnshop borrowing\thanks{We want to thank Jose Maria Barrero, Andrei Gomberg, Emilio Gutierrez, Anett John, David Laibson, Aprajit Mahajan, Matt Rabin, Mauricio Romero, Charlie Sprenger, Chris Udry, and seminar participants at ITAM, USC, MSU, UC Davis,  UCSD, and USC who provided valuable feedback.
+\title{Structured Payment in Pawnshop Borrowing\thanks{We want to thank Jose Maria Barrero, Andrei Gomberg, Emilio Gutierrez, Anett John, David Laibson, Aprajit Mahajan, Matt Rabin, Mauricio Romero, Charlie Sprenger, Chris Udry, and seminar participants at ITAM, USC, MSU, UC Davis,  UCSD, and USC who provided valuable feedback.
 Ricardo Olivares, Gerardo Melendez, and Alonso de Gortari provided excellent research assistance and Erick Molina helped with formatting.
@@
 
-Financial institutions often restrict choice using built-in commitment mechanisms like fixed repayment streams.
-These widely used attributes are meant to lower default and increase lender profit.
-At the same time, these firms often shroud those features by embedding them as non-negotiable attributes of the loan contract, presumably because borrowers underestimate their value, a case referred to as ``private paternalism'' by \cite{Laibson2018}.
-While \cite{Laibson2018} focuses on situations where the incentives of the firm align with those of the client, with overcollateralized loans, the lender may have incentives to \textit{encourage} default---using balloon payments or unstructured repayment loan contracts---in detriment of the borrower.
-
-Do lenders have this incentive?
-Would structured payment features that commit borrowers to pay earlier lead to lower financial cost for borrowers?
-Would borrowers freely demand such features?
-How can researchers rigorously estimate the benefits for borrowers who would freely choose the feature and for those that \textit{would not} choose it, necessary to assess paternalism?
-This paper answers these questions and studies the benefits of restricting borrower choice  in the context of one of the most prevalent and understudied forms of over-collateralized borrowing: pawn loans.
-
-Pawn loans constitute one of the oldest and most common forms of borrowing \citep{carter2012pawnshops}.
-Our partner lender, for example, made over 4 million loans to more than a million clients during in the three years adjacent to our experiment.\footnote{For comparison, there were 2.3 million microfinance clients in Mexico in 2009 \citep{Pedroza:2010}.}
-The question of choice versus paternalism is particularly salient in this context, as choice mistakes could arise from borrowers' low education and the fact that they typically borrow for emergencies under significant stress.\footnote{A large literature shows  stress impairs cognitive function, e.g.
-\cite{StressReview}.}
-%\footnote{There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues (in China it is a \$43 billion industry).
-\url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.}
-
-In our context, assessing a case for paternalism involves rigorously evaluating whether imposing contract terms on a borrower can achieve lower financial cost than letting the borrower choose whether to have it.
-Often models (e.g.
-Roy models) \textit{assume} that agents self-select into contracts that are best for them.
-Using a novel one-stage three-armed randomized controlled experiment, including forced treatment and treatment choice arms, allow us to point identify the relevant TOT and TUT effects and \textit{test} that assumption in a real-world, high-stakes setting.\footnote{We can also estimate the average selection on gains $\text{ASG} = \text{TOT} - \text{TUT}$, the average selection bias (ASB)---the average difference in untreated potential outcomes for those who choose commitment relative to those who do not, and the average selection on levels (ASL).}
-
-%In some contexts the positive sorting assumption is compelling, it is not obvious in ours.
-Demand for commitment can be particularly low \citep{Ashraf,Gine, Royer,Ted,Sprenger}, and pawn-based borrowers are often financially illiterate.
-
-%The behavioral finance literature has established an important role for commitment devices in helping consumers to achieve their own financial goals.
-While most academic studies on commitment focus on the role of voluntary self-commitment \citep{thaler2004save, prina2015banking, brune2016facilitating, callen2019headwaters, Pascaline, Ashraf}, in reality the predominant use of rigid structure in financial services is involuntary; firms only offer a product with these features embedded.
-\cite{Laibson2018} has referred to this implicit bundling of commitment devices as ``private paternalism'', and its logic is that individuals may benefit from commitment and yet not explicitly demand it.
-Comparing voluntary versus paternalistic programs requires that we form counterfactuals for two different groups of people: those who would freely choose commitment, and those who would not (since the latter group is treated only under paternalist policies).
-In this paper we present an experimental design and econometric analysis that point-identifies and provides estimates for both the effect of treatment on the treated (TOT) and on the untreated (TUT).
-This permits a clear window into the case for paternalistic (forced) rather than voluntary commitment in financial services.
-
-%The relationship between treatment effects and treatment take-up is a core concern in the econometrics literature.
-In principle, the Marginal Treatment Effect (MTE) approach allows researchers to use observational data and a single excluded instrument to study this relationship.
-In practice, however, unless the instrument has a rich support set, MTEs can only be point identified by using additional modeling assumptions \citep{mogstad2018using}.
-An alternative research strategy to study the relation between treatment effects and treatment take-up uses the Becker-Degroot-Marschak (BDM) mechanism, incentivizing choice prior to treatment assignment to elicit willingness to pay (WTP) for treatment \citep{becker1964measuring}.
-A number of studies, however, find that the WTP elicited under the BDM mechanism changes substantially with the distribution of prices used in the elicitation exercise \citep{bohm1997eliciting,banerji2014detection}.
-This falsifies the assumption of standard preferences that is required for BDM to be incentive-compatible \cite{mamadehussene2023reliability}, suggesting that the mechanism may not provide a reliable measure of actual compliance  in practice.
-Our study avoids the drawbacks of the MTE and BDM approaches by combining a novel three-armed randomized controlled experiment, including forced treatment and treatment choice arms, with two transparent exclusion restrictions.
-Together, these allow us to point identify the relevant TOT and TUT effects in a real-world, high-stakes setting and to study the case for paternalistic commitment head-on, with minimal assumptions.
-
-Our experiment covers just under 5,000 pawnshop clients in 6 of our partner lender's Mexico City branches.
-Our control arm illustrates the costs of the status quo contract: fully \emph{44\%} of borrowers default, losing their pawn along with any payments made towards principal.
-Indeed, 13\% of those who default first made some payments toward recovery, all of which is lost to them.\footnote{High pawn default rates are common, in the US they oscillate around 15\% (see \href{https://tinyurl.com/yc2x5bjf}{here}).} Our ``commitment choice'' arm gives borrowers the chance to opt into a structured repayment contract when taking a loan.
-The structured contract requires borrowers to make three monthly payments rather than one balloon payment at the end, with each monthly payment including the accrued interest at that time as well as a nominal fee of 2\% of that month's payment if the payment is delinquent.
-In our ``forced commitment'' arm all borrowers are \emph{required} to repay using the same structured monthly contract offered on an opt-in basis in the commitment choice arm.
-We use the labels commitment and structured payment contract interchangeably.
-
-This design allows us to measure the effects of structured payments, and also the demand for this contractual feature.
-We demonstrate that it further allows us to estimate the relationship between treatment effects and treatment take-up, a core concern in the econometrics literature.
-Intuitively, our design can be seen as a two-sided encouragement design, encouraging some borrowers to take and others to not take up structured repayment.
-In principle, the marginal treatment effect approach allows researchers to use observational data and an excluded instrument to study the relationship between treatment effects and treatment take-up.
-In practice, unless the instrument has a rich support set, additional modeling assumptions \citep{mogstad2018using} are needed.
-BDM mechanisms incentivizing choice prior to treatment assignment \citep{becker1964measuring} could be used to tackle this question, with some limitations \citep{bohm1997eliciting,banerji2014detection}.
-Two-stage Karlan-Zinman designs can be used to study a related question, namely isolating selection and incentive effects in comparing a more and less attractive intervention, such as low- and high-interest credit \citep{KarlanZinman2009} or cash grants versus loans \citep{Beaman2023}.
-Below we compare our novel one-stage design with these two-stage ones.
-
-%We address three key questions.
-First, do structured repayment contracts lower financial costs for pawnshop borrowers?
-Second, do borrowers recognize this benefit, demanding commitment in sufficient numbers?
-Finally, and most uniquely, do the \textit{right} borrowers voluntarily demand commitment?
-Our ability to answer the last question comes from our unique three-armed experimental design, which we call the ``controlled choice design'' for short.
-This design can be viewed as a juxtaposition of \emph{two} randomized encouragement designs, each with one-sided non-compliance.
-One of them point identifies the effect of commitment for borrowers who would \emph{voluntarily} choose commitment (TOT), while the other point identifies the effect of commitment for borrowers who would \emph{not} (TUT).
-By identifying both the TOT and TUT effects in the same experiment, the controlled choice design allows us to examine the empirical relevance of ``selection on gains'' also known as Roy-type selection into treatment by estimating the ``average selection on gains'' $\text{ASG} = \text{TOT} - \text{TUT}$.
-This enables us to test whether borrowers who voluntarily choose commitment have higher average treatment effects than those who do not, rather than assuming it.
-The controlled choice design also point identifies the average selection bias (ASB)--the average difference in untreated (status quo) potential outcomes for those who choose commitment relative to those who do not--along with the average selection on levels (ASL)--the analogous comparison for treated (commitment) potential outcomes.
-Taken together, these causal effects allow us to ``go under the hood'' of our baseline ATE results, and paint a more complete and economically relevant picture of the effects of commitment.
-We are unaware of any other paper that simultaneously identifies all of these causal effects without recourse to additional structural modeling assumptions.
-
-Turning to results, we find that commitment is strongly effective in lowering financial costs and preventing default in pawnshop lending: the average individual in the forced arm pays financing costs inclusive of fees that are 22\% lower than the control, and faces a probability of default that is 6.6 percentage points lower (15\% of the mean).
-In terms of Annual Percentage Rates, the financial cost of borrowing falls by 11 percentage points (19\% of the mean).
-In short, structured commitment saves borrowers money by charging them fees!
-Our results are qualitatively robust to deducting transport costs of visiting the branch to make interim payments along with a day of lost wages for each visit.
-They are also robust to using borrowers' subjective values of their pawns rather than the appraised value of the gold, and to adjusting for lost liquidity from requiring monthly payments.
-Having said this, we don't have comprehensive measures of welfare and refrain from making welfare statements from the start.
-We focus exclusively on the cost of loan servicing, an important outcome.
-
-On mechanisms, the monthly payment contract seems to achieve these cost savings by speeding up payments and, interestingly, by generating an early \textit{bifurcation} of borrowers into those that will recover the pawn and those that will not.
+Pawnshop lending, where borrowers provide gold and other easily sold items to receive overcolleralized loans, are one of the most prevalent forms of credit in the world.
+loans are one of the oldest and most common forms of borrowing \citep{carter2012pawnshops}.
+In Mexico the scale of pawn lending rivals that of microfinance: during the past three years a single large lender in the country made over 4 million loans to more than a million clients.
+Compare this to a total of 2.3 million microfinance clients in all of Mexico during 2009 \citep{Pedroza:2010}.
+Pawn borrowers are not only numerous, they are also economically vulnerable.
+The vast majority of pawn loans are made to people with relatively low levels of education in times of significant stress.\footnote{A large literature shows stress impairs cognitive function, e.g.
+\cite{StressReview}.} Despite its prevalence and at-risk clientele, however, pawn lending has received little attention in the literature compared to other financial services.
+
+Financial institutions often use built-in commitment mechanisms like fixed repayment streams to lower default rates and increase their own profits.
+At the same time, they frequently ``shroud'' these attributes by embedding them as non-negotiable features of the loan contract, presumably because borrowers undervalue commitment and would not demand it, given the choice.
+\cite{Laibson2018} refers to this practice as ``private paternalism''.
+When the incentives of firm and client align, as they do in \cite{Laibson2018}, private paternalism can benefit both parties.
+Pawn lending, however, turns this idea on its head: since the value of the collateral--the pawn--exceeds that of the loan, lenders stand to gain the most when borrowers default.\footnote{An industry standard contract in Mexico City lends 70\% of the value of gold collateral at an interest rate of 7\% for three months.
+Because gold is highly liquid, the profit from a borrower who defaults is 30\% of the collateral value compared to 15.8\% in interest if a loan is paid in full on the last day.}
+Consistent with this idea, and in stark contrast to microfinance, pawn lenders in Mexico City neither send payment reminders to borrowers nor provide commitment features in their contracts.
+Default is common.\footnote{The default rate in the \emph{status quo} arm of our Mexico City experiment is 44\%.}
+
+This paper presents results from a randomized experiment that answers three key questions.
+First, does the absence of commitment-style contracts cause default in pawn lending?
+If so, to what extent does this benefit lenders?
+Second, if a commitment contract were available would pawn borrowers choose it?
+Even more importantly, would the \emph{right} borrowers choose it, i.e.\ those who would benefit the most?
+Third, is there a case for \emph{paternalism}, namely for mandating commitment in pawn lending?
+If so, should commitment be mandated for all borrowers or can it be effectively targeted?
+The question of choice versus paternalism is particularly salient in a setting with vulnerable borrowers.
+Yet comparing voluntary versus paternalistic policies is challenging.
+Even if commitment lowers financial costs on average, it may be ineffective or even harmful for borrowers who \emph{would not choose} to commit.
+To meet this challenge we introduce a novel three-armed design, the ``forcing-choice'' design, that allows us to shed light on these three questions in the important and under-studied context of pawn lending.
+
+Our experiment covers just under 5,000 pawnshop clients across six of our partner lender's Mexico City branches.
+The control arm illustrates the costs of the \emph{status quo} contract: fully 44\% of control borrowers default, losing their pawn along with any payments made towards principal.
+Worse still, 29\% of those who default do so after making at least one payment towards recovery, a payment that they forfeit upon default.
+The ``forced commitment'' arm requires borrowers to make three monthly payments, with each monthly payment including the accrued interest at that time as well as a nominal fee of 2\% of that month's payment if the payment is delinquent.
+Finally, the ``commitment choice'' arm offers borrowers the chance to opt in to the same structured monthly contract that is mandated for borrowers in the forced commitment arm.\footnote{When describing this new contract below, we use the terms ``commitment'' and ``structured payment'' interchangeably.}
+
+Because there is no selection into or out of the control (status quo) and forced commitment arms in our experiment, the forcing-choice design can be viewed as a \emph{juxtaposition} of three more familiar experimental designs.\footnote{See section \ref{sec:integrity} for a discussion of how we can be sure that there was no selection into or out of the treatment and forced commitment arms.} The first is a standard two-armed RCT with perfect compliance that point identifies the average treatment effect (ATE) of commitment.
+The other two are a pair of randomized encouragement designs, each with one-sided non-compliance: one point identifies the effect of commitment for borrowers who would \emph{voluntarily} choose commitment (treatment on the treated: TOT), while the other point identifies the effect of commitment for borrowers who would \emph{not} (treatment on the untreated: TUT).
+Fully evaluating the case for paternalism versus borrower choice requires policymakers to learn not only whether those who demand commitment benefit from it (TOT), but also whether those who \emph{do not} are better off without it (TUT).
+
+Our ATE results show that commitment is strongly effective in lowering financial costs and preventing default in pawnshop lending: the average borrower in the forced arm pays financing costs inclusive of fees that are 22\% lower than the control, and faces a probability of default that is 6.6 percentage points lower (15\% of the mean).
+In terms of Annual Percentage Rates (APR), the financial cost of borrowing falls by 11 percentage points per loan (19\% of the mean).
+In short, structured commitment saves borrowers money by charging them fees.
+The mechanism by which our monthly payment contract achieves these cost savings is intriguing: not only does it speed up payments, it also generates an early \emph{bifurcation} of borrowers into those that will recover their pawns and those that will not.
 The former are induced to pay faster, saving on interest; the latter pay less towards loans that ultimately default, hence losing less money when they do.
-One interpretation is that requiring payments earlier accelerates learning about the feasibility of making such payments, thus reducing overconfidence, a mechanism not much discussed in the literature but that appears to be important in our context.
-
-Despite these large financial cost savings, only 11\% of borrowers in the choice arm choose commitment. 
-%If the effect of commitment were homogeneous, this would be enough to conclude that the 89\% who did not choose it would have been financially better off if they had.
-However, we test and reject the null hypothesis of homogeneous treatment effects using the method of \cite{chernozhukov2018generic}.
-Can the borrowers who did not choose commitment be those who simply don't need it? 
+While we find that borrowers who experience structured payment contracts are 6 percentage points more likely borrow again from the same lender, a back-of-the-envelope calculation suggests that the commitment contract nevertheless lowers lender profits by \hl{11\% per borrower}.
+It is thus unsurprising that commitment contracts were unavailable in Mexico city pawnshops outside of our experiment: lenders profit from default.\footnote{Unlike most pawn lenders, our partner operates as a non-profit, donating all of their earnings to philanthropic causes.
+They approached us and requested help evaluating the causal effect of commitment.}
+
+Given the limited measures that are available to us, we refrain from making definitive welfare statements in this paper, focusing instead on the cost of loan servicing, an important outcome in credit markets.\footnote{\hl{Enrique will find citations for a defensive footnote that goes here, pointing out that lots of papers use this as an outcome measure.}} Nevertheless, we explore the sensitivity of our findings to broader notions of cost.
+For example, our results are qualitatively robust to deducting transport costs of visiting the branch to make interim payments along with a day of lost wages for each visit.
+They are also robust to using borrowers' \emph{subjective} values of their pawns rather than the appraised value and to adjusting for lost liquidity from requiring monthly payments.
+
+Despite the large financial cost savings of structured repayment, only 11\% of borrowers in the choice arm opt into the commitment contract. 
+Could it be that borrowers who do not choose commitment are those who simply don't need it? 
 To answer this question, we carry out a detailed analysis of treatment effect heterogeneity.
-%We address this question by sequentially imposing more structure on the problem. 
 We begin by bounding the distribution of individual treatment effects using the marginal outcome distributions from the forced commitment and control arms, following \cite{fan2010sharp}.
 This approach imposes no assumptions beyond the experimental randomization.
-We find that \textit{at least} 23\% of borrowers benefit from the structured payments contract.
+We find that \emph{at least} 23\% of borrowers benefit from the structured payment contract.
 This implies that there must be many borrowers in the choice arm who did not demand this feature despite their \emph{individual treatment effect} from (forced) commitment being positive.
 
-Next, we impose a two-sided exclusion restriction positing that the effect of a given contract does not depend on \emph{how} borrowers obtain it.
+Next, we impose a pair of exclusion restrictions positing that the effect of a given contract does not depend on \emph{how} borrowers obtain it.
 In other words, we assume that choosing a contract results in the same potential outcome as being assigned that contract.
@@
 \cite{chamberlain2011bayesian} uses a closely related assumption to develop a theory of optimal treatment choice.}
-It also has testable implications that we fail to reject in our empirical context.\footnote{See \autoref{sec:testing_exclusion} for details.}
-Under this restriction, the forcing-choice design point-identifies the TOT, TUT, ASG, ASB, and ASL effects described above.
+It also has testable implications that we fail to reject in our empirical context.\footnote{See\autoref{sec:testing_exclusion} \hl{for details--Frank will move some of this into the body of the text.}}
+Under these restrictions, the forcing-choice design point-identifies the TOT and TUT, described above, along with the average selection on gains $\text{ASG} = \text{TOT} - \text{TUT}$, a measure of the empirical relevance of Roy-type selection.
 Our estimated TUT effect on financial cost savings is large: \$192 pesos, equivalent to a 10.6 percentage point savings in APR.
-On average, the borrowers who would \textit{not} choose commitment, would have faced substantially lower financial costs if they had.
-
-In a one-shot interaction, the game between the borrower and the lender is zero-sum.
-Decreasing financial costs for the borrower means decreasing the lender's profit.
-However, we find that experiencing the structured payments contract leads to a 6 percentage point increase in repeat borrowing from the lender.
-A back-of-the-envelope calculation shows that still, the contract reduces lender's profits by 11\%, implying that lenders would not offer this contract (as was the case in Mexican pawnshops) if not forced in our context.\footnote{Our partner lender contacted us to evaluate structured payments for two reasons.
-First, they genuinely wanted to know the causal effects of structured payments but did not know how to estimate them rigorously.
-Second, our lender operates as a non-profit, donating their earnings to philanthropic aims.}
-
-Our results raise two natural questions.
-First, in terms of regulatory policy, to what extent can we predict treatment effects and use those predictions to target frequent payment contracts?
-Second, why do borrowers seem to be leaving money on the table?
-
-To address the first question, we combine our experimental treatment and outcome data with survey responses collected for a subset of borrowers to estimate conditional average treatment effects, both TUTs and ATE, using the Causal Random Forest algorithm of \cite{atheygrf}.
-This requires that we impose the exclusion restriction not just on average, but at the level of individual borrowers, allowing us to make more precise personalized statements.
-Importantly, we estimate positive conditional average TUT effects for 93\% of the borrowers who did \textit{not} choose the structured payment contract.
-In short, it is extremely difficult to find identifiable groups of borrowers who are \emph{harmed} by commitment, even when restricting attention to those who would not choose it voluntarily. 
-%while only 37\% of those who chose commitment have negative conditional TOT effects.
-While targeting commitment products to those that benefit the most is a policy that appears attractive, in our context we find that the usable targeting variables have relatively weak predictive power and hence even our best random forest targeting only reduces the overall mis-targeting rate from 9.7\% (all to Forcing) to 9.5\% (our best-case feasible targeting mechanism).
-
-On the question of what explains the persistence of no-commitment contracts so contrary to borrowers’ interests, there are several candidates.
-From the demand side, while a simple measure of time inconsistency does not explain the large and positive TUT effect, we show substantial levels of over-optimism among borrowers, the average subjective probability of recovering their pawn is 92\%, while the actual average is only 44\%.
-Among borrowers who do not choose commitment, those with the largest estimated benefits from commitment are the individuals who most systematically over-estimate their own probability of repayment without the need to commit, potentially decreasing their demand from commitment.
-From the supply side, because loans are over-collateralized, the lender in the contract stands to gain the most when borrowers default.
-Our partner's \emph{status quo} pawn contract (standard in the industry) gave 70\% of the value of gold collateral in credit, and charged a monthly interest rate of 7\% for loans of a three-month duration, with a flexible no-reminders contract, that could be paid back anytime before the loan comes due at no penalty.
-The fact that the gold pawn is highly liquid, means that the lender makes more profit over three months from a borrower who defaults than one who repays (30\% of collateral value recovered under default, 15.8\% of collateral value paid in interest if loan fully repaid).
-While an older literature considers the exploitative potential of over-collateralization and underpriced collateral \citep{basu1984implicit}, the implication of such contracts has not been analyzed in the behavioral literature.
-
-%By overcollateralizing and then structuring loan contracts in a manner encouraging of default, lenders are able to extract substantial value independent of the interest charged.
+On average, the borrowers who would \emph{not} choose commitment, would have faced substantially lower financial costs if they had.
+Finally, we combine our experimental treatment and outcome data with survey responses collected for a subset of borrowers to estimate conditional average treatment effects, both TUTs and ATEs, using the Causal Random Forest algorithm of \cite{atheygrf}.
+We estimate positive conditional average TUT effects for 93\% of the borrowers who did \textit{not} choose the commitment contract.
+In short, it is extremely difficult to find identifiable groups of borrowers who incur higher financial costs under a commitment contract, even when restricting attention to those who would not choose it voluntarily.
+
+So why do borrowers seem to be leaving money on the table? 
+While a simple measure of time inconsistency does not explain the large and positive TUT effect, we find that borrowers systematically overestimate the probability that they will recover their pawn: the average subjective probability of recovery is 92\% compared to a realized probability of 44\%.
+Indeed, among borrowers who choose not to commit, we estimate the largest gains from commitment for those who overestimate their probability of recovery \emph{the most}.
+This suggests that overconfidence may reduce the demand for commitment.
+
+According to our conditional TUT results discussed above, mandating commitment contracts for all borrowers runs the risk of increasing financial costs for 7\% of the untreated.
+This raises the question of whether it is possible to assign commitment contracts in a \emph{targeted} way to only those borrowers who are likely to benefit from them.
+To answer this question, we revisit the causal forest results described above for the subset of borrowers who completed our baseline survey.
+Importantly, some variables from our survey that predict treatment effect heterogeneity cannot be used for targeting in practice.
+For example, while overconfident borrowers are more likely to default, targeting based on subjective probability of recovery may incentivize borrowers to change their reports, causing the predictive relationship to break down.
+Accordingly, our exercise restricts attention to survey variables that would be hard to manipulate (``narrow'' targeting).
+With this restriction, all of the targeting rules that we explore have relatively weak predictive power.
+Our best-performing targeting rule only lower the overall mis-targeting rate from 9.7\%--the baseline when all borrowers are assigned to commitment--to 9.5\%.
 
 Our paper makes a number of contributions to the literature.
-First, %we propose a way to use three-armed experimental structure to recover treatment effects for choosers and non-choosers under minimal assumptions.\footnote{A companion STATA package provides simple, regression-based estimators for each of these causal parameters, along with appropriate cluster-robust standard errors.
-See \autoref{sec:estimation_inference} for details.}
-we add to the relatively small literature that sheds light on private paternalism and selection on gains.
-In the context of food choice,  \cite{Sprenger} show that individuals with the most time-inconsistent preferences are actually least likely to demand commitment.
-In contrast, we directly identify the TUT, obviating the need to first elicit preferences before testing for negative selection.
-In the context of school choice, \cite{Walters} combines a distance instrument with additional structural assumptions, obtaining model-based TUT and ATE estimates.
-He finds that students who select into more effective schools have smaller treatment effects from attending than those who do not select in.
-Our approach instead point identifies TUT and TOT and a range of other interesting causal parameters without the need for a structural model, relying instead on relatively weak exclusion restrictions whose testable implications we fail to reject.
-In the context of agriculture, \cite{Beaman2023} compare the average treatment effect on farm profits from providing \textit{cash grants} to a set of farmers that did not select into getting \textit{loans} to those of average farmers.
-They do this in a two-stage design, by first offering loans or not to a set of farmers, and then randomizing cash grants among those who would not have received loans.
-Our paper is complementary in several respects.
-Because we estimate the average effect of a given treatment for those who did and did not select into that \textit{same} treatment, our design allows us to estimate effects on non-compliers, but on compliers as well, allowing the estimation of selection on gains, selection bias and selection on levels.
-\cite{Beaman2023} find that those selecting out of loans have lower average returns to capital, consistent with positive selection.
-In contrast, we find no evidence of positive selection.
-Our design can be used in situations where compulsion of the treatment is possible but two-stage randomization is infeasible or too costly.\footnote{\cite{fowlie2021default} likewise employ a three-armed experimental design in their study of the effect of electricity pricing, they identified \emph{two} TOT effects for different groups of ``treated'' households, whereas we simultaneously identify the TOT and TUT effects defined with respect to a single ``treated'' group of borrowers.
-This difference is what allows our design to point identify the ASG and related quantities.}
-
-%This controlled choice design is key to measuring the effects of mandated versus voluntary imposition of product features.
-This question is of interest in a large class of cases.
-Financial contracts frequently feature dimensions of private paternalism, such as mandatory frequent payment structures for loans.
-But beyond finance, in education, most teachers mandate homework with deadlines to deal with procrastination \citep{Ariely}.
-In the workplace, firms monitor employee attendance,\footnote{\url{https://www.wsj.com/lifestyle/careers/attention-office-resisters-the-boss-is-counting-badge-swipes-5fa37ff7}.} but also set and monitor time-specific goals.
-In the public policy domain we have seat belt mandates, age-dependent medical checkups, etc., which often go beyond nudging.
-Having a rigorous way to estimate the causal effects of mandates vs choice policies ---and not just for the average individual--- is critically important.
-%\footnote{The ``LATE-and-reweight'' approach goes beyond LATE by assuming no unobserved selection-on-gains \citep{aronow2013beyond,angrist2013extrapolate}.
-In our approach, we estimate selection-on-gains directly.
-Finally, as the MTE literature relies on a combination of instruments with rich support and additional structural assumptions such as additive separability of observed and unobserved determinants of treatment effect heterogeneity \citep{heckman2007econometric, cornelissen2018benefits}.
-In a returns-to-education setting, \cite{oreopoulos2006estimating} uses a direct approach to identify a LATE.}
-
-%\cite{Walters} takes the latter approach, combining a distance instrument with additional structural assumptions, obtaining model-based TUT and ATE estimates that differ substantially from those implied by a LATE-and-reweight approach.
-
-%\footnote{In a returns-to-education setting, \cite{oreopoulos2006estimating} uses a direct approach to identify a LATE % \emph{nearly} equals a TUT effect: the 1944 Butler Act increased the share of British children who remained in school until age 15 from 43\% to over 90\%.
-Because 100\% of borrowers in our forced arm are treated, we identify the TUT rather than an approximation to it.}
-
-Our study also speaks to recent research on the effects of payment frequency.
-While experiments in microfinance markets have \textit{not} not found benefits from providing a more regularized repayment environment as we find here \citep{Pande, barboni2023flexible, Field}, these experiments differ from ours in two important ways: they are performed on top of already highly structured micro-finance contracts, and they involve borrower pools who may have selected into that type of lending precisely because it provides structure \cite{bauer2012behavioral}.
-These differences may explain why \citep{Pande} finds almost no default in the control group, in stark contrast to our setting of high default.
-Second, we study \textit{both} take-up and the efficacy of voluntary commitment mechanisms.
+First, we provide a detailed picture of pawn lending, a widespread and important financial service that, despite its prevalence and impact on economically vulnerable borrowers, has received little scholarly attention.
+While an older literature considers the exploitative potential of over-collateralization and underpriced collateral \citep{basu1984implicit}, the behavioral implications of such contracts remain largely unexplored.
+To our knowledge, ours is the first behavioral paper to focus on pawn lending specifically.
+
+Second, we contribute to the relatively small literature on paternalism and selection-on-gains.
+In contrast to \cite{Laibson2018}, who studies private paternalism from a theoretical perspective, we show empirically that pawn borrowers would benefit, and lenders would suffer, from a paternalistic policy that mandates commitment in the form of structured repayment contracts.
+Unlike \cite{Sprenger}, who shows that individuals with the most time-inconsistent preferences are the least likely to demand commitment, we directly identify the treatment effect on the untreated (TUT).
+This obviates the need to first elicit preferences before testing for negative selection.
+Furthermore, whereas \cite{Walters} combines a distance-based instrument with structural modeling assumptions to show that students who select into more effective schools have smaller treatment effects ($\text{TOT} < \text{TUT}$), we identify the TUT and TOT effects without the need for a structural model.
+Instead, we rely on relatively weak exclusion restrictions whose testable implications we fail to reject.
+
+Third, our paper makes a methodological contribution by introducing the ``forcing-choice'' design, a novel three-armed experiment that point identifies treatment effects for choosers (TOT) and non-choosers (TUT) under minimal assumptions.\footnote{A companion STATA package provides simple, regression-based estimators for each of the causal parameters that are identified under this design, along with appropriate cluster-robust standard errors.
+See \autoref{sec:estimation_inference} for more details.}
+To our knowledge, this is the first paper to simultaneously point identify both quantities in the same experiment without the need for a structural model.\footnote{The forcing-choice design also point identifies the average selection-on-gains $\text{ASG} = \text{TOT} - \text{TUT}$, the average selection bias (ASB)--the difference in untreated potential outcomes for choosers versus non-choosers--and the average selection on levels (ASL)--the analogous comparison for treated potential outcomes.
+See Section \ref{sec:randchoice}.}
+Our approach provides a valuable alternative to existing approaches for studying the relationship between treatment effects and treatment take-up.
+While the Marginal Treatment Effect (MTE) approach can be applied to either experimental or observational data provided that an instrumental variable is available, applying it requires additional modeling assumptions unless the instrument has a rich support set \citep{mogstad2018using}.
+The Becker-Degroot-Marschak (BDM) mechanism provides a theoretically attractive alternative that does not depend on structural modeling assumptions, but some recent studies have raised concerns about its reliability in practice \citep{bohm1997eliciting,banerji2014detection,mamadehussene2023reliability}.
+
+The forcing-choice design differs from and complements other multi-armed designs from the literature.
+As far as we are aware, our approach is the first to simultaneously identify both the TOT and TUT effects for within the same experiment, allowing us to study the empirical relevance of selection-on-gains.
+The TUT effect, in particular, is crucial for considering the case for paternalism.
+While \cite{fowlie2021default} likewise employ a three-armed experimental design in their study of the effect of electricity pricing, they instead identify \emph{two} TOT effects for different groups of ``treated'' households.
+The well-known \cite{KarlanZinman2009} design, which randomly assigns interest rates in two stages to separate adverse selection from moral hazard, does not identify a TUT effect.
+Like \cite{KarlanZinman2009}, \cite{Beaman2023} employ a two-stage randomization compared to the one-stage, three-armed approach in the forcing-choice design.
+And while they identify a number of interesting causal parameters that shed light on the relationship between take-up and treatment effect heterogeneity, \cite{Beaman2023} do not identify a TUT effect or the average selection-on-gains.\footnote{In particular: the identify the ATE of cash grants, the TOT of loans, and the average effect of cash grants for those who would and would not accept a loan.
+While interesting, these last two effects are not TOT and TUT effects, because effects and compliance are defined with respect ti \emph{different} treatments: grants versus loans.}
+
+Finally, we contribute to a growing literature on the effects of payment frequency in lending.
+Unlike previous experiments in microfinance markets \citep{Pande, barboni2023flexible, Field}, which find no benefits from regularized repayment environments, our experiment reveals significant positive effects in the context of pawn lending.
+The setting of these microfinance experiments differs from ours in an important way: they are performed on top of already highly structured microfinance contracts, and they involve borrower pools who may have selected into that type of lending precisely because it provides structure \citep{bauer2012behavioral}.
+This difference may explain why \cite{Pande} find almost no default in their control group, compared to 44\% in ours.
+In addition to studying the effects of payment frequency, we examine both take-up and the efficacy of voluntary commitment mechanisms.
 A number of papers have found low demand for commitment as we do.\footnote{\cite{Ashraf}, \cite{Gine}, \cite{Ted}, \cite{Royer}, \cite{Sprenger}.
-Others have found more robust demand for commitment (\cite{Kremer},  \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}, \cite{Pascaline}).} Unlike all of these papers, however, we separately point-identify and estimate the effects of commitment for borrowers who would and \textit{would not} choose it.
-Given their enormous prevalence and the vulnerability of their users, pawn loans are severely understudied; we believe the descriptive information and treatment effects estimates for pawn borrowing are an important contribution.
-
-%We also believe that the forcing-choice RCT design provides a useful counterpoint to the widely used \cite{KarlanZinman2009} (KZ) designs.
-As far as we are aware, ours is the only experimental design in the literature simultaneously estimating both the TOT and TUT effects, along with the average selection on gains, without the need for auxiliary structural assumptions.
-Note that KZ designs do not estimate the TUT effect, which is crucial for evaluating the case for paternalism.\footnote{The KZ design is useful for separating moral hazard from adverse selection when a two-product comparison is relevant, with one being strictly preferable to consumers.
-Our design is useful in mapping marginal treatment effects to compliance with a single treatment, particularly in contexts where a) forcing is possible and b) selection subsequent to forcing is low, or is of direct interest to the principal (in that case, our design would still provide useful information to the principal but would not isolate agent-level heterogeneity in the way it does here).}
+Others have found more robust demand for commitment (\cite{Kremer},  \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}, \cite{Pascaline}).} Unlike all of these papers, however, we separately point-identify and estimate the effects of commitment for borrowers who would and would not choose it.
 
@@
 Section \ref{Design} describes the experiment and data sources, and shows pre-treatment balance across arms.
-Section \ref{Experiment} provides the standard ITT analysis of the experiment, while Section \ref{Choice} shows how to identify, estimate and carry out inference for the TOT, TUT, ASG, ASB and ASL effects under the forcing-choice design.
+Section \ref{Experiment} provides the standard ITT analysis of the experiment, while Section \ref{Choice} shows how to identify, estimate and carry out inference for the TOT, TUT, ASG and related causal effects under the forcing-choice design.
 Section \ref{Paternalism} investigates why paternalism functions so well in this context and whether it can be more finely targeted and Section \ref{conclusion} concludes.
@@
 %\noindent \textbf{Randomization.}  
-\paragraph*{Randomization} We implemented the experiment in 6 branches of Lender $P$ beginning on September 6, 2012.
+\paragraph*{Randomization} We implemented the experiment in six branches of Lender $P$ beginning on September 9, 2012.
 The branches were selected by Lender $P$ to be dispersed across Mexico City and have varying sizes.
@@
 %\footnote{We also surveyed clients before and after the experiment, so our survey covers a larger sample that we are not using in this paper.}.
-We only use the survey in Section \ref{Paternalism} of the paper.
+Is it important to say that we do \textit{not} use the survey for our main results. We only use the survey in Section \ref{Paternalism} of the paper.
 
@@
 The table reports the coefficients on each of these indicators, as well as the p-value of an F-test of the null hypothesis of equality of the three coefficients.
-We also report a median regression for each arm.
+We also report results using median regression.
 %Figure \ref{boxplot_attrition}, in the appendix shows a box-plot of the first two variables, showing the distribution across arms is balanced.
@@
 This was reinforced by reports from our enumerators and appraisers that those who entered the branch were determined to borrow and that there were no complaints about what loan contracts were available.
-Note that this does not mean that they did not care about contract terms, just that the outside option of leaving the branch without a loans seems less attractive.
+Note that this does not mean that they did not care about contract terms.
+It means just that the outside option of leaving the branch without a loan is unattractive.
 
@@
 \end{center}
-\scriptsize {Each row in this table corresponds to a regression, where the level of observation is a borrower that pawned which was surveyed.
-\hl{Surveys were not conducted at the beginning of the experiment}.
+\scriptsize {The table uses survey data to show balance across arms.
+Survey data is not used for the main results of the paper.
+It is only used in Section \ref{Paternalism}.
+Each row in this table corresponds to a regression, where the level of observation is a borrower that pawned which was surveyed.
 The dependent variables are displayed in the first column.
@@
 While the first payment for borrowers in the status-quo contract occurs on average only on day 82 (on a 90 days contract), borrowers in the forced commitment arm start paying 13.8 days earlier on average (col 1).
-Not only do they start paying earlier, the first payment is also 7.9\% larger (col 2), and a larger fraction of 9.7\% actually pay in full and recover their pawn in the first payment, compared to 30\% in the status quo contract (col 3).
+Not only do they start paying earlier, the first payment is also 9.7\% larger (col 2), and a larger fraction (7.9\%)  actually pay in full and recover their pawn in the first payment, compared to 30\% in the status quo contract (col 3).
 The resolution of the loan (either by payment or default) is shortened by 27.9 days (col 4), and conditional on recovery (an endogenous control) by 17.9 days (col 5).
@@
 
-\paragraph{Lender outcomes} One of the questions we are interested in is whether lender profits decrease with structured payment.
-If that is the case lenders have little incentive include this feature in their contracts.
-Showed above that per loan borrowers pay less to lenders under the structured payments contract.
-But this might mean that borrowers would be more willing to come back and pawn again.
-The experiment is not designed to measure the extensive margin or competitive responses of other lenders and we will not attempt a complete analysis here.
-We perform a simple back-of-the-envelope calculation that takes into account repeat business.
-
-We first assess whether being assigned to the structured payment contract causes more clients to come back.
-Table \ref{repeat_loans} estimates that participants assigned to the forced arm are 6.3\% more likely to repeat clients later during our sample period.
-We then calculate lender's profits in two ways.
-In the first, we just sum the total payments made by borrowers first assigned to the structured payment contract.
-This mechanically takes into account repeat borrowing.
-However, it does not allow us to extrapolate for longer periods, and it does not allow us to ``assign'' borrowers to future structured payment contracts.
-Column (1) in Table \ref{lenders_profit} reflect the effect of the contract type (in the first assigned treatment) on the lender's profit.
-In our second method we extrapolate.
-We use the estimates of the borrower's financial cost (which is lenders's revenue) from column 1 of Table \ref{main_impact_table} and repeat pawning from Table \ref{repeat_loans} and plug them into equation \ref{profit_function}
-
-\begin{equation}
-\label{profit_function}
-     \text{Profit}_j = \sum_{i}\sum_{t}\left\{P_{it}^I+P_{it}^F\right\}+0.3\times \text{Value-loan}_i \times\mathds{1}(\text{Def}_i=1)
-\end{equation}
-
-where $j$ indexes a borrower, and $i$ indexes a loan.
-The profit's formula captures all interest and fee payments made for the first two loans -  to reflect the repeat pawning behavior, and the 30\% of the collateral whenever the borrower defaults that loan.
-Columns (2) and (3) of Table \ref{lenders_profit} reflect this extrapolation.
+\paragraph{Lender profit} One of the questions we are interested in is whether lender profits decrease with structured payment.
+If that is the case, lenders will have little incentive to include this feature in their contracts.
+For a single loan, lenders get what borrowers lose in a zero-sum way so that a borrower's Financial Cost$_i$ for loan $i$ is the profit from that loan for the lender.
+Table \ref{main_impact_table} showed that \textit{per loan} borrowers pay less to lenders under the structured payments contract.
+However, in Table \ref{repeat_loans} in the appendix, we show that borrowers assigned to the forced arm are 6.7\% more likely than in the status quo arm to be repeat customers during our sample period.
+This brings some extra benefit to lenders that we need to take into account in a simple back-of-the-envelope calculation.
+From column 1 of Table \ref{main_impact_table} we know \{Financial Cost$_i$ $|$ Contract=c\} for $c$= status quo or structured payment contracts are respectively \hl{XX} and \hl{XX}.
+From Table \ref{repeat_loans} we know $\Pr(\text{Repeat} | \text{Contract}=c)$ for $c$= status quo or structured payment contracts are respectively \hl{XX} and \hl{XX}.
+We can use these four numbers to calculate a discounted sum of profits for client $j$ comparing a scenario where only status quo loans are offered with a second scenario where only structured payment loans are offered.\footnote{We do this for simplicity.
+Otherwise, we would have to assume something about how borrowers switch dynamically across loans, and this is something we do not observe in the data.} One way to do a back-of-the-envelope calculation is by plugging those numbers in the following equation:
+ $\text{Profit}_{j,c} = \{\text{Financial Cost}_j | \text{Contract}=c\}\{1+n\times\Pr(\text{Repeat}_j)\}$ where $n$ is are exogenously arising need to borrower, which are lead to repeat pawning.
+A second possibility is to compound the probability of coming back to take into account that pawning may lead to more repeat pawning and this compounds: $\text{Profit}_{j,c}  = \sum_{T}\delta^T\{\text{Financial Cost}_j | \text{Contract}=c\}\times\Pr(\text{Repeat} | \text{Contract}=c)^T$, where $\delta$ is the discount rate.
+We find in the first case that the status quo contract dominates the structured payment contract for all $n$.
+\hl{For the second alternative, we find that for every  $\delta$ in [0,1] and for every $T$ the status quo also dominates.} That is, the extra repeat probability in the structured payment is not enough to compensate for the loss per each of those loans.
+Table \hl{XX} in the appendix shows the calculation for different values of $\delta, n, T$.
+
+% \begin{equation}
+% \label{profit_function}
+% \text{Profit}_{j,c}  = \sum_{T=0}^{\infty}\{\text{Financial Cost}_j | \text{Contract}=c\}\times\Pr(\text{Repeat Pawn}_j | \text{Contract}=c)^T 
+% \end{equation}
+
+% where $j$ indexes a borrower, and $c$ indicates the first assigned contract/treatment to borrower $j$.
+The profit for the status-quo contract is  \$1578, while that of the forced-commitment contract is \$1418, which results in less profit for the forced-commitment contract even when considering repeat pawning behavior.
 
@@
 This suggests that some of the 89\% of borrowers in the choice arm who did \emph{not} choose commitment would have faced lower borrowing costs if they had.Making this intuition precise, however, requires a careful consideration of the relationship between choice and heterogeneous treatment effects.
-This section shows how our 3-arm RCT design point-identifies a range of treatment effects of interest, and in particular the treatment on the untreated, necessary to study the benefits mandating a contractual feature.
+This section shows under an additional mild exclusion restriction assumption, our 3-arm RCT design point-identifies a range of treatment effects of interest, and in particular, the treatment on the untreated, necessary to study the benefits mandating a contractual feature.
 To this end, we now provide a full definition of the potential outcomes in our empirical setting.
@@
 To estimate the conditional average treatment effects we use the ``generalized random forest'' methods of \cite{atheygrf} (see Appendix \ref{app:cate} for details).\footnote{The generalized random forest approach of \cite{atheygrf} produces conditional average effect estimators that are asymptotically normal.
-%These methods are relatively straightforward because the trees are ``honest'' in that observations used to determine splits in the recursive partitioning algorithm are not used for causal effect estimation and vice-versa.
 Our inferences in this section are carried out by simulating from the normal limit distributions using the estimated standard errors.
@@
 The survey questionnaire (with the highlighted questions being the ones for the wide set of covariates) can be found in \ref{baseline_survey} in the Appendix.}
-
+We implement these estimates using the covariates from our survey.
+
+\vspace{.2in}
 \begin{figure}[!h]

### 2025-04-25 Restud submission/donde_restud-REAL-THING.tex
First set of edits after R&R

--- 2025-04-25 Restud submission/donde_restud-FIRST-DRAFT.tex
@@
-\documentclass[12pt, a4paper]{article}
+\documentclass[12pt, a4paper, colorinlistoftodos]{article}
 
 \input{preamble.tex}
+
 %%% HELPER CODE FOR DEALING WITH EXTERNAL REFERENCES
+\usepackage{authblk}
+\makeatletter
+\renewcommand\AB@affilsepx{, }
+\makeatother
+\renewcommand\Authands{ and }
+\renewcommand\Affilfont{\small}
+\setlength{\affilsep}{0em}
 \usepackage{xr}
@@
 \linespread{1.25}
+
+% To-do commands (must go after authblk to avoid clash)
+\usepackage{todonotes}
+\usepackage{marginnote}
+\renewcommand*{\marginfont}{\color{red}\sffamily\scriptsize}
+\setlength{\marginparwidth}{2cm}  % prevent todo cutoff
+\newcounter{todoListItems}
+\newcommand{\todoLink}[2][ ]{
+  \addtocounter{todoListItems}{1}
+  \todo[caption={\protect\hypertarget{todo\thetodoListItems}{}Translation},size=\tiny,#1]{
+    \tiny #2 \hfill \hyperlink{todo\thetodoListItems}{$\uparrow$}
+  }
+}
+\newcommand{\forES}[1]{\todoLink[color=green!20,inline,caption={\thetodoListItems: For @Enrique}]{\textbf{@Enrique} -- #1}}
+\newcommand{\forIM}[1]{\todoLink[color=blue!20,inline,caption={\thetodoListItems: For @Isaac}]{\textbf{@Isaac} -- #1}}
+\newcommand{\forFdT}[1]{\todoLink[color=red!20,inline,caption={\thetodoListItems: For @Francis}]{\textbf{@Francis} -- #1}}
+\newcommand{\forCM}[1]{\todoLink[color=violet!20,inline,caption={\thetodoListItems: For @Craig}]{\textbf{@Craig} -- #1}}
+\newcommand{\forAll}[1]{\todoLink[color=orange!20,inline,caption={\thetodoListItems: For All}]{\textbf{@All} -- #1}}
+
 \begin{document}
 
-\title{Structured Payment in Pawnshop Borrowing\thanks{We want to thank Jose Maria Barrero, Andrei Gomberg, Emilio Gutierrez, Anett John, David Laibson, Aprajit Mahajan, Matt Rabin, Mauricio Romero, Charlie Sprenger, Chris Udry, and seminar participants at ITAM, USC, MSU, UC Davis,  UCSD, and USC who provided valuable feedback.
+\listoftodos
+
+\title{Structured Payment in Pawnshop Borrowing: Mandates vs.\ Choice\thanks{We thank Jose Maria Barrero, Camilo García-Jimeno, Andrei Gomberg, Emilio Gutierrez, Anett John, David Laibson, Aprajit Mahajan, Matt Rabin, Mauricio Romero, Charlie Sprenger, Séverine Toussaert, Chris Udry, Jonathan Zinman, and seminar participants at Dartmouth, ITAM, MSU, USC, UC Davis, UCSD, and USC who provided valuable feedback.
 Ricardo Olivares, Gerardo Melendez, and Alonso de Gortari provided excellent research assistance and Erick Molina helped with formatting.
@@
 Our research partner had no say in the design or results of the experiment.}}
-\author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira \and Francis J.\ DiTraglia   \thanks{Seira:  MSU, \url{enrique.seira@gmail.com} (corresponding author); McIntosh:  University of California San Diego, \url{ctmcintosh@ucsd.edu}; Meza: Harvard University, \url{isaacmezalopez@g.harvard.edu}; Sadka: ITAM, \url{jsadka@itam.mx}; DiTraglia: Oxford, \url{francis.ditraglia@economics.ox.ac.uk}} }
-\date{This draft:  \today \\[2 cm]}
+\author[1]{Francis J.\ DiTraglia}
+\author[2]{Craig McIntosh}
+\author[3]{Isaac Meza}
+\author[4]{Joyce Sadka}
+\author[5]{Enrique Seira\thanks{Corresponding Author: \href{mailto:enrique.seira@gmail.com}{enrique.seira@gmail.com}}}
+\affil[1]{\normalsize University of Oxford} %\href{mailto:francis.ditraglia@economics.ox.ac.uk}{francis.ditraglia@economics.ox.ac.uk}}
+\affil[2]{\normalsize University of California San Diego}
+%\href{mailto:ctmcintosh@ucsd.edu}{ctmcintosh@ucsd.edu}}
+\affil[3]{\normalsize Harvard University}
+%\href{mailto:isaacmezalopez@g.harvard.edu}{isaacmezalopez@g.harvard.edu}}
+\affil[4]{\normalsize ITAM}
+%, \href{mailto:jsadka@itam.mx}{jsadka@itam.mx}}
+\affil[5]{\normalsize University of Notre Dame}
+
+\date{\today \\[2 cm]}
 
@@
 \begin{abstract}
-We explore paternalism in the understudied context of high-default pawn lending.
-We use a novel one-stage, three-armed RCT, including forced and voluntary treatment arms, to point-identify the effects of structured repayment contracts on both the treated and the untreated simultaneously.
-We find that forcing borrowers into commitment-style contracts decreases the financial cost of pawn loans by 22\% and increases the likelihood of recovering their pawn by 15\%.
-However, only 11\% of borrowers choose such contracts.
-We find that borrowers who would not choose regular payments would benefit substantially from getting such contracts, as much as those freely choosing them (no selection on gains).
-A paternalistic policy of universal forced commitment archives similar benefits to personalized targeting.
+%We explore the merits of structured repayment contracts in the understudied context of pawn lending.
+We use a novel one-stage, three-armed RCT, including mandatory and voluntary treatment arms, to point-identify the effects of regular monthly payments both for individuals who would freely choose, and would not freely choose, structured payments.
+We find that assigning borrowers to commitment-style contracts decreases the financial cost of pawn loans by 22\% and increases the likelihood of recovering their pawn by 15\%.
+However, only 11\% of borrowers choose such contracts voluntarily.
+We find that borrowers who would \textit{not} choose regular payments would benefit substantially from getting such contracts, as much as those freely choosing them (no selection on gains).
+A paternalistic policy mandating structured payments helps a sufficiently large fraction of borrowers that it cannot be improved upon by feasible personalized targeting.
+\singlespacing
+Pawn loans offer borrowers a high degree of repayment flexibility in exchange for a harsh penalty in case of default: forfeit of collateral worth more than the loan amount.
+Using a large RCT conducted in Mexico City, we document key stylized facts and explore the merits of replacing flexibility with structured repayment contracts in this important but understudied form of credit.
+A novel experimental design that includes a mandatory frequent-payments arm, a (status quo) flexible payments arm, and a choice between the two, point-identifies not only the average treatment effect, but also the effects of treatment on the treated and the untreated along with the average selection on gains, allowing a rigorous study of mandates versus choice.
+Although the average treatment effect of assigning borrowers to structured payments is a 22\% decrease in their financial cost and a 15\% increase the probability that they will recover their pawn, only 11\% of borrowers choose structured repayment contracts voluntarily.
+We show that structured repayment benefits nearly all borrowers, including those who would not freely choose it, and find no evidence of selection on gains.
+%Nonetheless, lenders' profits are lower under structured payments since they earn more from borrower default, giving lenders little incentive to offer such contracts.
+
 \end{abstract}
 
-\vspace{.8in}
-\noindent \textbf{Keywords: } Paternalism, choice, treatment on the untreated, payment frequency, overconfidence. \textbf{JEL codes:} G41, C93, O16, G21
+%\vspace{.6in}
+\noindent \textbf{Keywords: } Mandates versus choice, paternalism, treatment on the untreated, payment frequency, overconfidence.\\ \textbf{JEL codes:} G41, C93, O16, G21
 
@@
 
-Pawnshop lending, where borrowers provide gold and other easily sold items to receive overcolleralized loans, are one of the most prevalent forms of credit in the world.
-loans are one of the oldest and most common forms of borrowing \citep{carter2012pawnshops}.
-In Mexico the scale of pawn lending rivals that of microfinance: during the past three years a single large lender in the country made over 4 million loans to more than a million clients.
-Compare this to a total of 2.3 million microfinance clients in all of Mexico during 2009 \citep{Pedroza:2010}.
-Pawn borrowers are not only numerous, they are also economically vulnerable.
-The vast majority of pawn loans are made to people with relatively low levels of education in times of significant stress.\footnote{A large literature shows stress impairs cognitive function, e.g.
-\cite{StressReview}.} Despite its prevalence and at-risk clientele, however, pawn lending has received little attention in the literature compared to other financial services.
-
-Financial institutions often use built-in commitment mechanisms like fixed repayment streams to lower default rates and increase their own profits.
+\forES{Enrique please do this}
+
+\forIM{Please that}
+
+Pawn lending is one of the oldest and most prevalent forms of credit in the world \citep{carter2012pawnshops}.
+Pawn loans are typically small, and short-term.
+They involve no credit checks or proof of income, and are widely used by people without access to other forms of credit.
+Borrowers surrender highly liquid collateral as the pawn, typically gold, in return for a loan that is substantially smaller than their pawn's value.
+These loans are very flexible: there are no scheduled payments, no prepayment penalties, and interest is charged only on outstanding balance.
+Unlike mortgage lenders, pawn lenders retain the entire value of the collateral under default along with any payments already made, rather than simply recovering the outstanding value of the loan.
+There are more than 11,000 pawn shops across the US with 30 million clients and \$14 billion yearly revenues; in China pawn lending is a 43 billion dollar industry.\footnote{\url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.
+In Mexico the scale of pawn lending rivals that of microfinance: during the past three years a single large lender in the country made over 4 million loans to more than a million clients, compared to a total of 2.3 million microfinance clients in all of Mexico during 2009 \citep{Pedroza:2010}.}  Despite this, pawnshops have received little attention in the literature to date.
+
+Pawn loans are different from conventional credit in important ways.
+First, pawn loans typically default at much higher rates than other forms of credit.
+For example, 44\% of loans made by our partner lender are not repaid, and 29\% of those who fail to repay make payments prior to defaulting, money which is completely lost to them subsequently.
+Second, lender profits are higher under default than repayment.
+An industry standard contract in Mexico City lends 70\% of the value of gold collateral at an interest rate of 7\% for three months.
+Because gold is highly liquid, the profit from a borrower who defaults is 30\% of the collateral value compared to 22.5\% in interest if a loan is paid in full on the last day.
+Furthermore, pawn borrowers are typically economically vulnerable and, in our context, are also naively optimistic; borrowers report a subjective probability of repayment that averages 92\%.
+The unusual degree of flexibility in these contracts would benefit borrowers if they were neo-classical agents, but the prevalence of costly default that hurts borrowers but benefits lenders, combined with apparently naive borrowers, calls this into question.
+Other lending modalities with dramatically lower equilibrium default, such as microfinance, typically rely on highly structured repayment regimes.
+%Hence pawn lending features unusual dynamics, and lender incentives are quite different from other forms of lending.
+
+%Much of the literature on standard credit contracts has illustrated that structured repayment schedules help borrowers avoid default \citep{morduch1999microfinance}.
+Indeed, \cite{Laibson2018} has discussed the many ways in which forcing devices like structure and deadlines are embedded into schools, workplaces, and financial institutions so as to improve outcomes whether or not the customers would have freely elected these features.
+Pawn lending, in contrast with the highly structured contracts of microfinance lending, typically features no reminders or regular payment schedule, with borrowers required to remember to make a single balloon payment withing the contracted time or else lose the pawn.
+Given this combination of issues, it appears possible that the lack of structure in pawnshop lending is strategic on the part of lenders.
+This raises the possibility of potential gains to borrowers by introducing contracts with more regularized repayment structure.
+
+%Financial institutions often use built-in commitment mechanisms like fixed repayment streams to lower default rates and increase their own profits.
 At the same time, they frequently ``shroud'' these attributes by embedding them as non-negotiable features of the loan contract, presumably because borrowers undervalue commitment and would not demand it, given the choice.
@@
 When the incentives of firm and client align, as they do in \cite{Laibson2018}, private paternalism can benefit both parties.
-Pawn lending, however, turns this idea on its head: since the value of the collateral--the pawn--exceeds that of the loan, lenders stand to gain the most when borrowers default.\footnote{An industry standard contract in Mexico City lends 70\% of the value of gold collateral at an interest rate of 7\% for three months.
-Because gold is highly liquid, the profit from a borrower who defaults is 30\% of the collateral value compared to 15.8\% in interest if a loan is paid in full on the last day.}
-Consistent with this idea, and in stark contrast to microfinance, pawn lenders in Mexico City neither send payment reminders to borrowers nor provide commitment features in their contracts.
+Pawn lending, however, turns this idea on its head: since the value of the collateral--the pawn--exceeds that of the loan, lenders stand to gain the most when borrowers default.Consistent with this idea, and in stark contrast to microfinance, pawn lenders in Mexico City neither send payment reminders to borrowers nor provide commitment features in their contracts.
 Default is common.\footnote{The default rate in the \emph{status quo} arm of our Mexico City experiment is 44\%.}
 
-This paper presents results from a randomized experiment that answers three key questions.
+This paper asks whether structured repayments can help pawnshop borrowers avoid default.
+To do so, we present a unique three-armed experiment covering around 4,500 pawnshop clients across six of our partner lender's Mexico City branches.
+Borrowers in the Control arm received the standard status quo pawn contract (described above) which allows us to document payment trajectories and default in standard pawn markets.
+Borrowers in the `Structured' arm were required to make three monthly payments, with each monthly payment including the accrued interest at that time, and faced a nominal fee of 2\% of that month's payment if the payment was delinquent.
+Borrowers in the `Choice' arm were allowed to choose between the Standard and Structured contracts.
+A design that features both assignment and choice permits a nuanced understanding of how treatment effects relate to the choices that individuals freely make: because our context featured no differential selection of clients across arms, we can recover a unique combination of economically-relevant causal estimands.\footnote{See Section \ref{sec:integrity} for details.}
+
+Comparing the Structured and Control arms gives the Average Treatment Effect (ATE) of structured repayment in the pawnshop context.
+Comparing the Choice arm to the Control provides a standard Intention to Treat (ITT) effect of offering this option.
+The presence of all three arms in the same experiment then allows us to point identify treatment effects \emph{separately} for those who would and would not choose structure, given the choice.
+Consider only the Control and Choice arms.
+No one in the Control arm is treated, but some borrowers in the Choice arm choose to be treated: choosers.
+We can view the comparison of these two arms as an experiment with one-sided non-compliance.
+Here assignment to the choice arm serves as an instrumental variable for treatment receipt.
+Under an exclusion restriction, a familiar argument shows that the IV estimator identifies the causal effect for people who are shifted by the instrument: choosers.
+This is the Treatment on the Treated (TOT).
+Now consider only the Choice and Structured arms.
+Everyone in the Structured arm is treated, but some borrowers in the Choice arm choose not to be treated: non-choosers.
+We can view the comparison of these two arms as a separate experiment, also with one-sided non-compliance.
+Here assignment to the Structured arm serves as an instrumental variable for treatment receipt.
+Under a symmetric exclusion restriction, an almost identical argument shows that the IV estimator identifies the causal effect for people who are shifted by the instrument: non-choosers.
+This is the Treatment on the Untreated (TUT).
+As far as we are aware, this is the only experimental paper that provides a direct comparison of the TUT and TOT in the same context.
+This comparison is key for studying voluntary versus mandatory treatment.
+
+%\todo[inline]{Should add a bit more on the ``mandates versus choice'' design here, including some other possible scenarios where it could be employed: education experiment, 401k, online privacy settings.}
+
+This design reveals critical information about marginal treatment effects and selection on gains, and is useful for any circumstance in which we want to compare voluntary versus mandated compliance.
+In educational settings, it may be useful to understand whether providing optional exercises in advance of a major exam is sufficient, or whether it is more effective to require students to complete these.
+In the much-studied context of employer-based retirement savings plans, this design can be used to examine the relative benefits of providing options for higher and earlier employee contributions versus simply defaulting employees into more aggressive savings plans.
+Digital service providers trying to understand how digital privacy settings drive platform engagement and monetization could either provide choices to consumers or simply default them into stricter protections, and our design provides a way of comparing the relative benefits of these approaches.
+In general, our method for testing the TOT against the TUT provides a practical way of understanding how treatment effect heterogeneity relates to real-world compliance decisions.
+
+%while comparing.
+Invoking the standard exclusion restriction, we can calculate the Treatment on the Treated (TOT) for choosers in the Choice arm.
+Novel to this context is that we can then use a symmetric assumption to calculate the Treatment on the Untreated (TUT) by comparing the Choice and Assigned arms to each other.
+Thus, in a single context and with minimal assumptions, this design allows us to compare the treatment effects for individuals who would have and would not have freely chosen the treatment.
+%We provide Stata code to conduct correct inference on the comparison of the TOT and the TUT, which is the relevant comparison for any applied policy conversation about the relative benefit of offering a policy versus imposing it upon agents.
+%\textcolor{teal}{We explain in the paper why the estimation of TUT is essential to assess the pros and cons of mandating a contractual feature (in our lexicon, imposing a mandate and eliminating choice is a form of paternalism).}
+
+%ompared to the status quo arm that continues to receive the standard pawn contract, we that answers three key questions.
 First, does the absence of commitment-style contracts cause default in pawn lending?
@@
 
-Our experiment covers just under 5,000 pawnshop clients across six of our partner lender's Mexico City branches.
+%Our experiment covers just under 5,000 pawnshop clients across six of our partner lender's Mexico City branches.
 The control arm illustrates the costs of the \emph{status quo} contract: fully 44\% of control borrowers default, losing their pawn along with any payments made towards principal.
@@
 
-Because there is no selection into or out of the control (status quo) and forced commitment arms in our experiment, the forcing-choice design can be viewed as a \emph{juxtaposition} of three more familiar experimental designs.\footnote{See section \ref{sec:integrity} for a discussion of how we can be sure that there was no selection into or out of the treatment and forced commitment arms.} The first is a standard two-armed RCT with perfect compliance that point identifies the average treatment effect (ATE) of commitment.
+%Because there is no selection into or out of the control (status quo) and forced commitment arms in our experiment, the forcing-choice design can be viewed as a \emph{juxtaposition} of three more familiar experimental designs.\footnote{See section \ref{sec:integrity} for a discussion of how we can be sure that there was no selection into or out of the treatment and forced commitment arms.} The first is a standard two-armed RCT with perfect compliance that point identifies the average treatment effect (ATE) of commitment.
 The other two are a pair of randomized encouragement designs, each with one-sided non-compliance: one point identifies the effect of commitment for borrowers who would \emph{voluntarily} choose commitment (treatment on the treated: TOT), while the other point identifies the effect of commitment for borrowers who would \emph{not} (treatment on the untreated: TUT).
@@
 
-Our ATE results show that commitment is strongly effective in lowering financial costs and preventing default in pawnshop lending: the average borrower in the forced arm pays financing costs inclusive of fees that are 22\% lower than the control, and faces a probability of default that is 6.6 percentage points lower (15\% of the mean).
+Our ATE results show that mandatory structured payments are strongly effective in lowering financial costs to borrowers and preventing default in pawnshop lending: the average borrower in the Structured arm pays financing costs inclusive of fees that are 22\% lower than the control, and faces a probability of default that is 6.6 percentage points lower (15\% of the mean).
 In terms of Annual Percentage Rates (APR), the financial cost of borrowing falls by 11 percentage points per loan (19\% of the mean).
-In short, structured commitment saves borrowers money by charging them fees.
-The mechanism by which our monthly payment contract achieves these cost savings is intriguing: not only does it speed up payments, it also generates an early \emph{bifurcation} of borrowers into those that will recover their pawns and those that will not.
-The former are induced to pay faster, saving on interest; the latter pay less towards loans that ultimately default, hence losing less money when they do.
-While we find that borrowers who experience structured payment contracts are 6 percentage points more likely borrow again from the same lender, a back-of-the-envelope calculation suggests that the commitment contract nevertheless lowers lender profits by \hl{11\% per borrower}.
-It is thus unsurprising that commitment contracts were unavailable in Mexico city pawnshops outside of our experiment: lenders profit from default.\footnote{Unlike most pawn lenders, our partner operates as a non-profit, donating all of their earnings to philanthropic causes.
-They approached us and requested help evaluating the causal effect of commitment.}
-
-Given the limited measures that are available to us, we refrain from making definitive welfare statements in this paper, focusing instead on the cost of loan servicing, an important outcome in credit markets.\footnote{\hl{Enrique will find citations for a defensive footnote that goes here, pointing out that lots of papers use this as an outcome measure.}} Nevertheless, we explore the sensitivity of our findings to broader notions of cost.
+In short, structured repayment saves borrowers money by charging them fees.
+The mechanism by which our monthly payment contract achieves these cost savings is intriguing: not only does it improve repayment and speed up the pace of payments on average, but it also decreases the amount of money paid by borrowers who will ultimately go on to default.
+While we find that borrowers who experience structured payment contracts are 6 percentage points more likely to borrow again from the same lender, a back-of-the-envelope calculation suggests that the structured contract nevertheless lowers lender profits by at least 14\% per borrower.
+It is thus unsurprising that structured payment contracts were unavailable in Mexico city pawnshops outside of our experiment: lenders profit from default.\footnote{Unlike most pawn lenders, our partner operates as a non-profit, donating all of their earnings to philanthropic causes.}
+
+%Given the limited measures that are available to us, we refrain from making definitive welfare statements in this paper, focusing instead on the cost of loan servicing, an important outcome in credit markets.\footnote{\hl{Enrique will find citations for a defensive footnote that goes here, pointing out that lots of papers use this as an outcome measure.}} Nevertheless, we explore the sensitivity of our findings to broader notions of cost.
 For example, our results are qualitatively robust to deducting transport costs of visiting the branch to make interim payments along with a day of lost wages for each visit.
@@
 
-Despite the large financial cost savings of structured repayment, only 11\% of borrowers in the choice arm opt into the commitment contract. 
-Could it be that borrowers who do not choose commitment are those who simply don't need it? 
-To answer this question, we carry out a detailed analysis of treatment effect heterogeneity.
-We begin by bounding the distribution of individual treatment effects using the marginal outcome distributions from the forced commitment and control arms, following \cite{fan2010sharp}.
-This approach imposes no assumptions beyond the experimental randomization.
+Despite the large financial cost savings that it provides, there is low demand for structured repayment: only 11\% of borrowers in the choice arm choose structure.
+The mystery is then why so few people choose a contract that is financially beneficial on average.
+Could it be that this small fraction of ``choosers'' simply represents the only individuals who benefit from structure?
+The strongly significant difference between the Structured arm and the Choice arm suggests that this is not the case.
+More rigorously, an exercise that non-parametrically bounds the distribution of individual treatment effects, following \cite{fan2010sharp}, shows that structured repayment benefits more than twice the number of people who chose it, even under the most conservative assumptions.
+Imposing the two exclusion restrictions \hl{mentioned above} \forFdT{We did not mention them above} allows us to go further, point identifying the average treatment effects for choosers (TOT) and non-choosers (TUT) along with the average selection on gains ($\text{ASG} = \text{TOT} - \text{TUT}$), a measure of the empirical relevance of Roy-type selection.
+Our estimated TOT implies that choosers actually see a very small and insignificant increase in the cost of their loans from structure.
+\forCM{FC is not that small} The TUT effect, in contrast, suggests that the financial cost savings to non-choosers are large: \$192 pesos, equivalent to a 10.6 percentage point savings in APR.
+On average, the borrowers who would \emph{not} choose commitment, would have faced substantially lower financial costs if they had.
+We find no evidence of selection on gains.
+Finally, we combine our experimental treatment and outcome data with survey responses collected for a subset of borrowers to estimate conditional average treatment effects, both TUTs and ATEs, using the Causal Random Forest algorithm of \cite{atheygrf}.
+We estimate positive conditional average TUT effects for 93\% of the borrowers who did \textit{not} choose the structured contract.
+In short, it is extremely difficult to find identifiable groups of borrowers who incur higher financial costs under a structured contract, even when restricting attention to those who would not choose it voluntarily
+
+%The question that our design allows us to address is then whether the \textit{right} people selected into the structured contract, based on the treatment effects observed.
+To answer this question, and to think very carefully about the implications of imposing structure when some borrowers could be hurt by it, we carry out a detailed analysis of treatment effect heterogeneity.We begin by bounding the distribution of individual treatment effects using the marginal outcome distributions from Assigned commitment and Control arms, following \cite{fan2010sharp}.
+%This approach imposes no assumptions beyond the experimental randomization.
 We find that \emph{at least} 23\% of borrowers benefit from the structured payment contract.
-This implies that there must be many borrowers in the choice arm who did not demand this feature despite their \emph{individual treatment effect} from (forced) commitment being positive.
-
-Next, we impose a pair of exclusion restrictions positing that the effect of a given contract does not depend on \emph{how} borrowers obtain it.
-In other words, we assume that choosing a contract results in the same potential outcome as being assigned that contract.
-This is a relatively common if often implicit assumption in causal inference.\footnote{Papers that use variation in compulsory schooling laws to identify the returns to schooling, for example, typically interpret their results as the causal effect of additional \emph{education} rather than additional \emph{forced education}.
+This implies that there must be many borrowers in the choice arm who did not demand this feature despite their \emph{individual treatment effect} from (assigned) commitment being positive.
+
+%This is a relatively common if often implicit assumption in causal inference.\footnote{Papers that use variation in compulsory schooling laws to identify the returns to schooling, for example, typically interpret their results as the causal effect of additional \emph{education} rather than additional \emph{forced education}.
 \cite{chamberlain2011bayesian} uses a closely related assumption to develop a theory of optimal treatment choice.}
-It also has testable implications that we fail to reject in our empirical context.\footnote{See\autoref{sec:testing_exclusion} \hl{for details--Frank will move some of this into the body of the text.}}
-Under these restrictions, the forcing-choice design point-identifies the TOT and TUT, described above, along with the average selection on gains $\text{ASG} = \text{TOT} - \text{TUT}$, a measure of the empirical relevance of Roy-type selection.
-Our estimated TUT effect on financial cost savings is large: \$192 pesos, equivalent to a 10.6 percentage point savings in APR.
-On average, the borrowers who would \emph{not} choose commitment, would have faced substantially lower financial costs if they had.
-Finally, we combine our experimental treatment and outcome data with survey responses collected for a subset of borrowers to estimate conditional average treatment effects, both TUTs and ATEs, using the Causal Random Forest algorithm of \cite{atheygrf}.
-We estimate positive conditional average TUT effects for 93\% of the borrowers who did \textit{not} choose the commitment contract.
-In short, it is extremely difficult to find identifiable groups of borrowers who incur higher financial costs under a commitment contract, even when restricting attention to those who would not choose it voluntarily.
+%It also has testable implications that we fail to reject in our empirical context.\footnote{See\autoref{sec:testing_exclusion} \hl{for details--Frank will move some of this into the body of the text.}}
 
 So why do borrowers seem to be leaving money on the table?
-While a simple measure of time inconsistency does not explain the large and positive TUT effect, we find that borrowers systematically overestimate the probability that they will recover their pawn: the average subjective probability of recovery is 92\% compared to a realized probability of 44\%.
-Indeed, among borrowers who choose not to commit, we estimate the largest gains from commitment for those who overestimate their probability of recovery \emph{the most}.
-This suggests that overconfidence may reduce the demand for commitment.
-
-According to our conditional TUT results discussed above, mandating commitment contracts for all borrowers runs the risk of increasing financial costs for 7\% of the untreated.
-This raises the question of whether it is possible to assign commitment contracts in a \emph{targeted} way to only those borrowers who are likely to benefit from them.
+One possible explanation could be impatience: under a standard model of rational choice, a sufficiently impatient borrower might prefer the status quo contract in spite of the higher probability of default.
+%; our measures of profit are not discounted, and so could a sufficiently impatient borrower prefer the status quo contract? 
+We find, however, that discount rates of almost 4,000\% would be required to rationalize such a preference, making impatience an unlikely explanation for the low take-up of structured repayment contracts.
+Another potential explanation frequently raised in the literature is time inconsistency: hyperbolic borrowers might choose a contract that maximizes short-term liquidity.
+We find that a standard survey measure of time inconsistency does not predict larger TUT effects while pawn recovery overconfidence does.
+In particular, we find that among borrowers who choose not to commit to a structured repayment plan, those who overestimate their probability of recovery the most would also benefit the most from structure.
+Overconfident borrowers appear to be unwilling to use tools designed to prevent default because they incorrectly believe they are not at risk.
+
+\forCM{The targeting exercise and the 9.5\% and 9.7\% are no longer part of the paper. We may want to delete the entire paragraph below}
+
+\textcolor{red}{\st{While the results discussed above suggest that structure is broadly beneficial, even for those who would not choose it voluntarily, our estimated conditional TUT effects are negative for 7\% of the untreated.
+This raises the question of whether it is possible to assign structured contracts in a \emph{targeted} way to only those borrowers who are likely to benefit from them.
 To answer this question, we revisit the causal forest results described above for the subset of borrowers who completed our baseline survey.
-Importantly, some variables from our survey that predict treatment effect heterogeneity cannot be used for targeting in practice.
+%Importantly, some variables from our survey that predict treatment effect heterogeneity cannot be used for targeting in practice.
 For example, while overconfident borrowers are more likely to default, targeting based on subjective probability of recovery may incentivize borrowers to change their reports, causing the predictive relationship to break down.
-Accordingly, our exercise restricts attention to survey variables that would be hard to manipulate (``narrow'' targeting).
+Accordingly,
+Our exercise restricts attention to survey variables that would be hard to manipulate (``narrow'' targeting).
 With this restriction, all of the targeting rules that we explore have relatively weak predictive power.
-Our best-performing targeting rule only lower the overall mis-targeting rate from 9.7\%--the baseline when all borrowers are assigned to commitment--to 9.5\%.
-
-Our paper makes a number of contributions to the literature.
-First, we provide a detailed picture of pawn lending, a widespread and important financial service that, despite its prevalence and impact on economically vulnerable borrowers, has received little scholarly attention.
-While an older literature considers the exploitative potential of over-collateralization and underpriced collateral \citep{basu1984implicit}, the behavioral implications of such contracts remain largely unexplored.
-To our knowledge, ours is the first behavioral paper to focus on pawn lending specifically.
+Our best-performing targeting rule only lower the overall mis-targeting rate from 9.7\%--the baseline when all borrowers are assigned to structure--to 9.5\%.
+In short, it is difficult to beat a policy that imposes structured contracts for all borrowers.}}
+
+We make several contributions to the literature.
+First, as far as we are aware, ours is the first paper to simultaneously identify both TOT and TUT effects in a single experiment, without the need for auxiliary structural modeling assumptions.
+Our three-armed experimental design also identifies the average selection on gains (ASG = TOT - TUT), average selection bias (ASB)--the difference in untreated potential outcomes for choosers versus non-chooers--and the average selection on levels (ASL)--the analogous comparison for treated potential outcomes.
+Our design is new to the literature.
+Like us, \cite{fowlie2021default} employ a one-stage, three-armed experimental design.
+But because they identify two TOT effects for different treated groups, rather than a TUT and TOT effect, their design cannot speak to the question of selection-on-gains.
+The two-stage designs of \cite{KarlanZinman2009} and \cite{Beaman2023} likewise do not identify TUT effects.
+%While the Becker-Degroot-Marschak (BDM) is theoretically attractive, recent studies have raised reliability concerns \citep{bohm1997eliciting,banerji2014detection,mamadehussene2023reliability}.
+Our design is potentially transferable to other settings in which researchers aim to understand the relationship between treatment effects and compliance \hl{like ...}\footnote{
+We provide a companion STATA package that implements regression-based estimators for all identified causal parameters, along with cluster-robust standard errors.} 
+\forFdT{You had examples of other contexts where the mandates vs choice design may work. Put here? --ES}
+
+%The TUT effect is crucial for considering the case for paternalistic policies that impose product features on agents.
+%While \cite{fowlie2021default} likewise employ a three-armed experimental design in their study of the effect of time-varying electricity pricing, they identify \emph{two} TOT effects for different groups of ``treated'' households.
+%The well-known \cite{KarlanZinman2009} design, which randomly assigns interest rates in two stages to separate adverse selection from moral hazard, does not identify a TUT effect.
+%To study a related question,   \cite{Beaman2023} employ a two-stage randomization that first measures who would have received loans, and then offers cash grants to those who would and would not have gotten those loans.
+%And while they identify a number of interesting causal parameters that shed light on the relationship between loan take-up and cash grant treatment heterogeneity, \cite{Beaman2023} do not identify a TUT effect or the average selection-on-gains.\footnote{In particular: they identify the ATE of cash grants, the TOT of loans, and the average effect of cash grants for those who would and would not accept a loan.
+While interesting, these last two effects are not TOT and TUT effects, because effects and compliance are defined with respect to \emph{different} treatments: grants versus loans.}
 
 Second, we contribute to the relatively small literature on paternalism and selection-on-gains.
-In contrast to \cite{Laibson2018}, who studies private paternalism from a theoretical perspective, we show empirically that pawn borrowers would benefit, and lenders would suffer, from a paternalistic policy that mandates commitment in the form of structured repayment contracts.
-Unlike \cite{Sprenger}, who shows that individuals with the most time-inconsistent preferences are the least likely to demand commitment, we directly identify the treatment effect on the untreated (TUT).
-This obviates the need to first elicit preferences before testing for negative selection.
-Furthermore, whereas \cite{Walters} combines a distance-based instrument with structural modeling assumptions to show that students who select into more effective schools have smaller treatment effects ($\text{TOT} < \text{TUT}$), we identify the TUT and TOT effects without the need for a structural model.
-Instead, we rely on relatively weak exclusion restrictions whose testable implications we fail to reject.
-
-Third, our paper makes a methodological contribution by introducing the ``forcing-choice'' design, a novel three-armed experiment that point identifies treatment effects for choosers (TOT) and non-choosers (TUT) under minimal assumptions.\footnote{A companion STATA package provides simple, regression-based estimators for each of the causal parameters that are identified under this design, along with appropriate cluster-robust standard errors.
-See \autoref{sec:estimation_inference} for more details.}
-To our knowledge, this is the first paper to simultaneously point identify both quantities in the same experiment without the need for a structural model.\footnote{The forcing-choice design also point identifies the average selection-on-gains $\text{ASG} = \text{TOT} - \text{TUT}$, the average selection bias (ASB)--the difference in untreated potential outcomes for choosers versus non-choosers--and the average selection on levels (ASL)--the analogous comparison for treated potential outcomes.
-See Section \ref{sec:randchoice}.}
-Our approach provides a valuable alternative to existing approaches for studying the relationship between treatment effects and treatment take-up.
-While the Marginal Treatment Effect (MTE) approach can be applied to either experimental or observational data provided that an instrumental variable is available, applying it requires additional modeling assumptions unless the instrument has a rich support set \citep{mogstad2018using}.
-The Becker-Degroot-Marschak (BDM) mechanism provides a theoretically attractive alternative that does not depend on structural modeling assumptions, but some recent studies have raised concerns about its reliability in practice \citep{bohm1997eliciting,banerji2014detection,mamadehussene2023reliability}.
-
-The forcing-choice design differs from and complements other multi-armed designs from the literature.
-As far as we are aware, our approach is the first to simultaneously identify both the TOT and TUT effects for within the same experiment, allowing us to study the empirical relevance of selection-on-gains.
-The TUT effect, in particular, is crucial for considering the case for paternalism.
-While \cite{fowlie2021default} likewise employ a three-armed experimental design in their study of the effect of electricity pricing, they instead identify \emph{two} TOT effects for different groups of ``treated'' households.
-The well-known \cite{KarlanZinman2009} design, which randomly assigns interest rates in two stages to separate adverse selection from moral hazard, does not identify a TUT effect.
-Like \cite{KarlanZinman2009}, \cite{Beaman2023} employ a two-stage randomization compared to the one-stage, three-armed approach in the forcing-choice design.
-And while they identify a number of interesting causal parameters that shed light on the relationship between take-up and treatment effect heterogeneity, \cite{Beaman2023} do not identify a TUT effect or the average selection-on-gains.\footnote{In particular: the identify the ATE of cash grants, the TOT of loans, and the average effect of cash grants for those who would and would not accept a loan.
-While interesting, these last two effects are not TOT and TUT effects, because effects and compliance are defined with respect ti \emph{different} treatments: grants versus loans.}
+\cite{Laibson2018} studies private paternalism from a theoretical perspective and explains how principals may conceal commitment features that agents need but do not demand.
+Our results suggest that this picture may be inverted in the upside-down world of pawn lending:  principals provide unstructured contracts that \textit{induce} default, despite the fact that borrowers would benefit from the imposition of more structure.
+A pioneering paper in the relationship between choice and treatment effects is \cite{Sprenger}, who shows that individuals with the most time-inconsistent preferences are the least likely to demand commitment.
+Our papers are complementary; while they design the experiment to identify one particular mechanism generating low take up (i.e.
+time inconsistency), we can identify a money-metric value for the amount forgone by not taking up structure without the need to first elicit preferences before testing for negative selection.
+\textcolor{teal}{Our test can afford to be agnostic about the exact mechanism generating positive TUT}.
+Relatedly, whereas \cite{Walters} combines a distance-based instrument with structural modeling assumptions to show that students who select into more effective schools have smaller treatment effects ($\text{TOT} < \text{TUT}$), we identify TUT and TOT effects without the need for a structural model.
+%Second, as far as we are aware, our approach is the first to simultaneously identify both the TOT and TUT effects for within the same experiment, allowing us to study the empirical relevance of selection-on-gains in a high-stakes context.
+
+Third, our paper provides a detailed picture of pawn lending, a widespread and important financial service that, despite its prevalence and impact on economically vulnerable borrowers, has received little scholarly attention.\footnote{\textcolor{teal}{ \cite{Caskey1991} complained that ``economists have produced hundreds of theoretical and empirical studies of banks while completely ignoring pawnshops'', which, according to him, are used by 10\% of Americans.
+\cite{Bos2012} write that ``while controversy surrounds payday loans, pawnshops have stayed out of public scrutiny''.}} While \cite{Caskey1991} and \cite{Bos2012} \textcolor{teal}{produce summary statistics for the US and Swedish panwlending industry,} an older literature considers the exploitative potential of over-collateralization and underpriced collateral \citep{basu1984implicit}.
+However the behavioral implications of such contracts remain largely unexplored.
+%To our knowledge, ours is the first paper to focus specifically on pawn lending.
+\textcolor{teal}{In line with our results, \cite{heidhues2010exploiting} present a model where lenders design a contract that ``is flexible in a way that induces the borrower to unexpectedly change her mind regarding how she repays'', resulting in the postponement of payments and higher financial cost.
+In their model, naivete leads borrowers to overestimate their likelihood of repaying on time, to overuse credit, and ultimately lower welfare.}
+
+\textcolor{teal}{Provision of a payment structure under modest fees could operate through several behavioral mechanisms similar to those operating when making a plan, which has been shown to influence behavior in many domains \citep{nickerson2010voting,milkman2011using,milkman2013planning}.
+Following \cite{beshears2016beyond}, a modest fee could: circumvent limited attention, set a reference point, fight forgetfulness, be a cue operating as a recommendation to act, set a mental goal \citep{locke1990theory, heath1999goals}, increase salience of deadlines \citep{bordalo2013salience}.}
+While not exactly the same as structure, a number of papers study commitment.\footnote{\textcolor{red}{\st{as we do--structured payment contracts with late payment fees are a form of commitment.}}  \cite{Ashraf}, \cite{Gine}, \cite{Ted}, \cite{Royer}, \cite{Sprenger} find modest demand for commitment while (\cite{Kremer},  \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}, \cite{Pascaline}) find more robust demand.
+Unlike all of these papers, we estimate the effects of structure for borrowers who would and would not choose it.} \textcolor{teal}{A notable recent paper, \cite{CarreraEtAl2022} document over-optimism in people's gym attendance and low correlation between measured present bias and commitment take-up\footnote{\textcolor{teal}{Although they find willingness-to-pay for commitment does correlate with present bias.}}, in consonance with our findings.
+\cite{predatory2022} study payday loans %\footnote{\textcolor{teal}{Payday loans have very different contractual features (e.g., collateral) and outcomes.
+For instance in their study \cite{predatory2022} find that only 3\% of loans end in default, where 44\% of ours do.}},
+and find that while inexperienced borrowers are overoptimistic about the likelihood of paying the loan, experienced ones are not (in our case experience \hl{XX} predict overconfidence).
+One strength of these two papers is that they have detailed choice-based quantitative measures of time preferences (a luxury we don't have given very limited access to clients), which they use to identify parameters in beta-delta structural models to obtain welfare counterfactuals under the structural assumptions.}
+
+\forIM{Can you show me how experience correlates with OC in a regression? --ES}
 
 Finally, we contribute to a growing literature on the effects of payment frequency in lending.
-Unlike previous experiments in microfinance markets \citep{Pande, barboni2023flexible, Field}, which find no benefits from regularized repayment environments, our experiment reveals significant positive effects in the context of pawn lending.
-The setting of these microfinance experiments differs from ours in an important way: they are performed on top of already highly structured microfinance contracts, and they involve borrower pools who may have selected into that type of lending precisely because it provides structure \citep{bauer2012behavioral}.
+In the context of microfinance, \citep{Pande} find no effects from frequent repayment schemes on loan default.\footnote{\textcolor{teal}{In the context of Dutch mortgages, mandating a front-loaded payment structure generated higher asset accumulation and lower consumption \cite{BernsteinKoudijs2024}.}} Other studies find that increasing repayment flexibility in microfinance (by giving grace periods to pay or options to delay payment) improves business performance \citep{Field,barboni2023flexible,flexibilty2024}.
+Our experiment in contrast, highlights some of the dangers of flexibility in the context of overcollateralized pawn lending.
+The setting of microfinance experiments differs from ours in an additional way: they are performed on top of already highly structured microfinance contracts, and they involve borrower pools who may have selected into that type of lending precisely because it provides structure \citep{bauer2012behavioral}.
 This difference may explain why \cite{Pande} find almost no default in their control group, compared to 44\% in ours.
-In addition to studying the effects of payment frequency, we examine both take-up and the efficacy of voluntary commitment mechanisms.
-A number of papers have found low demand for commitment as we do.\footnote{\cite{Ashraf}, \cite{Gine}, \cite{Ted}, \cite{Royer}, \cite{Sprenger}.
-Others have found more robust demand for commitment (\cite{Kremer},  \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}, \cite{Pascaline}).} Unlike all of these papers, however, we separately point-identify and estimate the effects of commitment for borrowers who would and would not choose it.
-
-The remainder of the paper is structured as follows:  Section \ref{context} provides context and defines our main outcome variables.
+
+The remainder of the paper is structured as follows.
+Section \ref{context} provides context and defines our main outcome variables.
 Section \ref{Design} describes the experiment and data sources, and shows pre-treatment balance across arms.
-Section \ref{Experiment} provides the standard ITT analysis of the experiment, while Section \ref{Choice} shows how to identify, estimate and carry out inference for the TOT, TUT, ASG and related causal effects under the forcing-choice design.
-Section \ref{Paternalism} investigates why paternalism functions so well in this context and whether it can be more finely targeted and Section \ref{conclusion} concludes.
-
-\section{Context and stylized facts} \label{context}
+Section \ref{sec:randchoice} formally presents the assumptions required to recover the TOT and TUT, and  \ref{Experiment} provides the results the experiment.
+In Section \ref{why_paternalism} we examine the behavioral underpinnings that drive our results, and Section \ref{sec:RF} works to bound the treatment effects to understand how many individuals may have been harmed by mandated structure.
+Section \ref{conclusion} concludes.
+
+\section{Context} \label{context}
 
@@
 
-To study this market, we partnered with one of the largest pawn shops in Mexico, an institution with more than one hundred branches spanning multiple states in Mexico.
-This lender (whom we refer to as `Lender P') has a simple and typical business model.
+To study this market, we partnered with one of the largest pawn shops in Mexico, an institution with more than one hundred branches spanning multiple states.
+This lender (whom we refer to as ``Lender P'') has a simple and typical business model.
 
@@
 No other collateral and no credit history checks are needed.
-The transaction takes less than 10 minutes and is conducted at the branch in person between the client and the appraiser (i.e.
-a teller).
+The transaction takes less than 10 minutes and is conducted at the branch in person between the client and the appraiser (i.e.\ a teller).
 %, see Figure \ref{PawnshopPicture}). 
@@
 Under this status quo contract, there are no payment reminders or any other kind of interim contact between the lender and the borrower.
+Internal lender rules allocate payments first to interest and fees owed and up to the day of the payment, and to capital only after the first has been covered.
 If the client returns to pay the principal plus the accumulated interest within 105 days, she recovers her pawn, otherwise the pawnbroker keeps the piece \textit{and} any payments already made.
@@
 
-\subsection{Stylized facts}
-
-%\hfill \newline
-%\noindent \textbf{Borrowers.} 
-\paragraph*{Borrowers.} Borrowers are not completely inexperienced: 87\% of clients in our survey report they have pawned before.
-%These clients have little or no access to other types of loans and they value the convenience of pawn borrowing.
-However they are economically vulnerable:  30\% of them could not pay either water, electricity \& gas or rent in the past 6 months.
-In terms of triggers and uses of the loan, 89\% said they are pawning because of an emergency, and only 12\% stated it was to be used in a ``non-urgent expense''.
-When asked why they are pawning this piece, 5\% responded ``lost a family member'', ``a medical emergency'' (11\%), or ``an urgent expense'' (72\%).
-Only 32\% of borrowers have completed college, 73\% of are women, with an average age of 43 years.
-
-%\hfill \newline
-%\noindent \textbf{Many borrowers lose their pawn.} 
-\paragraph*{Many borrowers lose their pawn.}
-Our context is also one with high borrower default: 43\% of clients lose their pawn in a time span of 230 days from the date of pawning.
-One potential explanation for high default is that clients are really just knowingly selling their gold piece through a pawn contract on which they intend to default.
-This appears unlikely for several reasons: clients can easily sell the gold and obtain a higher amount of instant cash at gold-buying stores located close to almost all our pawnshop branches;
-%(see Figure \ref{GoldBuyers}) 
-the reported subjective value of the pawn is larger than the appraised value for 83\% of clients (this also means it is inefficient that they lose their pawns).
-The default rates for the experimental period and branches is similar to that observed for all branches in subsequent periods (see Figure \ref{external_validity}).
-
-\paragraph*{Gold buying shops.} Gold purchasing shops locate close to our Lender's branches.
-Branches have an average of \hl{XX} of these shops.
-This fact is important given the high default rates which could indicate that borrowers are ex ante intending to `sell' their pawn.
-Given that they are receiving 70\% of the value of the pawn next door to shops that would give them 100\% of this value, we think this is prima facie unlikely.
-
-\paragraph*{Paying without recovering.} Among those that lose their pawn, 29\% paid a positive amount towards its recovery, and on average paid 42\% of the value of their loan (see Figure \ref{proxy_naive} in Appendix) --- this can only be rationalized if they expected to recover their pawn.
-
-\paragraph*{Overconfidence.} We implemented a baseline survey to more than 6,000 respondents.
-In it, we asked borrowers for their subjective probability of recovering the pawn.
-The average recovery probability is 92\%.
-This contrasts sharply with the actual recovery rate for these same borrowers, 44\%.
-Overall 72\% of borrowers report a 100\% probability of repaying their loan.
-%Note that high default could be detrimental from the lender's point of view, since it may reduce the likelihood that the client becomes a return customer.
-%Lender P was in fact explicitly interested in partnering with us to investigate how to reduce loan default, customer satisfaction, and repeat borrowing.
-
-\subsection{Measuring Borrowers Financial Costs} 
+\subsection{Measuring Borrowers' Financial Costs} 
 \label{costs}
@@
 If a loan has been rolled over and is still outstanding, we consider it to be non-defaulted.
-This approach is conservative in our context (biases treatment effects towards zero), as we show in detail in Section \ref{Experiment}.
+This approach is conservative in our context (biases treatment effects towards zero), as we show in detail in \textcolor{red}{the appendix.} %Section \ref{Experiment}.
 In our data 13\% of experimental loans are ongoing (i.e.
@@
 This includes all payments the borrower made toward interest and fees, but also the net difference between the appraised value of the pawn and the loan amount (Value-Loan) in the event of default.
-When there is no default the borrower gets her pawn back and there is no loss of value for the borrower.
-Payments towards capital are considered a cost only when the borrower defaults, as she does not get reimbursed for these.
+When there is no default the borrower recovers her pawn and there is no loss of value for the borrower.
+Payments towards capital are considered a cost only when the borrower defaults, as she is not reimbursed for these payments.
 Note however that when she does not default payments to capital are not an actual outflow, as they sum up to the value of the loan the lender disbursed in the first place.
@@
 As a second measure of cost we calculate the Annual Percentage Rate (APR) in order to express the cost as a percentage of the loan, per year, inclusive of default costs.
-The standard definition is given in the following formula:
-$$(\text{APR})_i =\left( 1 + \frac{\frac{\text{Financial Cost}_i}{\text{Loan}_i}}{\text{loan term}_i}\right)^{\text{loan term}_i}-1 $$
+The standard definition is given in the formula below.
+Note that in contrast with the standard calculation of APR, our measure of financial cost includes the expected cost from defaulting, and important distinction in this context.
+$$(\text{APR})_i =\left( 1 + \frac{\frac{\text{Financial Cost}_i}{\text{Loan}_i}}{\text{loan term}_i}\right)^{\text{loan term}_i}-1 .$$
 
@@
 \vspace{.2in}
-\section{Experiment and Data} \label{Design}
+\section{Experiment, Data and Stylized Facts} \label{Design}
 
@@
 %\noindent \textbf{The Commitment Contract.} 
-\paragraph*{The Commitment contract} For the purpose of the experiment we designed a new contract that is identical to the status quo contract except that, informed by the design of micro-lending contracts, it enhances the regularity and salience of payments as a way to encourage repayment \citep{morduch1999microfinance, bauer2012behavioral}.
+\paragraph*{The Structured contract} For the purpose of the experiment we designed a new contract that is identical to the status quo contract except that, informed by the design of micro-lending contracts, it enhances the regularity and salience of payments as a way to encourage repayment \citep{morduch1999microfinance, bauer2012behavioral}.
 It has the same interest rate (7\% \textit{per month}) which accumulates daily on outstanding debt, the same loan size/collateral ratio (70\%), and the same loan term (90 days, and a grace period of 15 days).
 Borrowers' gold pawns are appraised in the same way by the same appraisers under both the new and status quo contracts.
-The commitment contract however requires the client to make regular monthly payments for the duration of the contract, with the principal and interest payments split evenly across the three months of the contract (day 30, 60 and 90 after loan disbursement).
+The Structured contract however requires the client to make regular monthly payments for the duration of the contract, with the principal and interest payments split evenly across the three months of the contract (day 30, 60 and 90 after loan disbursement).
 The importance of this monthly payment was made salient in the contract and payment receipts, and by the levying of a nominal fee (2\% of minimum due) on individuals who fell behind in their payments.
@@
 The fee was modest and intended to make the payment deadlines salient. As a benchmark, the transportation cost to visit the branch to make a payment is comparable to the fee, on average.
+
 %\footnote{%The lender was worried that if the fee was large, forgetting to pay could make the pawn unrecoverable. 
@@
 To elicit demand for the monthly payment contract, we include an arm that allows borrowers to opt into this contract if they choose.
-The existence of both a non-optional ``forcing'' arm, and a choice arm in our design is key to estimating a battery of treatment effects under fairly mild assumptions.
+The existence of both a non-optional ``structured'' arm, and a choice arm in our design is key to estimating a battery of treatment effects under fairly mild assumptions.
 We next describe the three experimental arms in more detail.
@@
     \item \textit{Control} arm: consisted of branch-days offering the status quo contract described in Section \ref{context}, and only this contract. 
-    \item \textit{Forced structured payments} arm: consisted of branch-days requiring all borrowers to use the Commitment contract described above.  
-    \item \textit{Structured payments Choice} arm: consisted of branch-days offering the client \textit{a choice} between the structured payments contract, and the status quo contract.
+    \item \textit{Mandatory structured payments} arm: consisted of branch-days requiring all borrowers to use the Structured contract described above.  
+    \item \textit{Choice} arm: consisted of branch-days offering the client \textit{a choice} between the structured payments contract, and the status quo contract.
     %\item \textit{Forced Soft Commitment} arm: consisted of branch-days in which borrowers were asked to sign a non-binding written commitment to pay monthly as in the Commitment contract, but no reminders or fees were imposed if they did not.\footnote{The client was made to sign a paper which said ``I promise to pay every month the corresponding sum of \_\_\_\_\_\_, on the dates \_\_\_\_\_\_, \_\_\_\_\_\_, and \_\_\_\_\_\_.
@@
 We did not allocate an equal number of days across arms, since we were interested in having more power in some of them.
-The number of branch days allocated to each were 84 to control, 80 to forced structured payments, and 93 to choice.
+The number of branch days allocated to each were 84 to control, 80 to mandated structured payments, and 93 to choice.
 See Figure \ref{exp_description} for a CONSORT-style diagram of the study design and recruitment.
@@
 \begin{center}
-\includegraphics[width=0.9\textwidth]{Figuras/consort.pdf}
+\includegraphics[width=0.9\textwidth]{Figuras/consort.png}
   \end{center}
@@
 %Thus we eliminated {the smallest} ones.
-Branches are more than 5 km apart from each other, and there is no substitution among them; none of the consumers appear in more than one of our branches.
+Branches are more than 5 km apart from each other, and there is no substitution among them; none of the borrowers appear in more than one of our branches.
 
@@
 Some clients pawned more than one time during the duration of the experiment, with 14\% pawning 2 times and 8\% more than 2 times.
-To have a clean comparison we are considering only the first pawn conducted during the experimental window.
-It is also the case that 30\% of those first pawns involve more than 1 loan, as 2 or more pieces of gold were submitted.
+To have a clean comparison we consider only the first pawn conducted during the experimental window.
+Moreover, 30\% of first pawns involve more than 1 loan, as 2 or more pieces of gold were submitted.
 We treat each of them as separate loans.
@@
 We have this information for all the pawns that occurred in the experiment's 6 branches between August 2, 2012 and August 13, 2013.
-This includes all the pawns that took place during our experiment along with those that one month before and eight months after our experiment.
+This includes all the pawns that took place during our experiment along with those that originated one month before and eight months after our experiment.
 Figure \ref{exp_description} shows the design and timing of the experiment, along with the sample sizes in each arm.
-The experiment comprises 8,519 pawns while our administrative data covers a total of 26,180 pawns.
+The experiment comprises 6,304 pawns while our administrative data covers a total of 26,180 pawns.
 
@@
 The survey allows us to measure loan takeup since we know whether people entered the branch, completed the survey, and then, after learning the contract terms, decided not to pawn.
-As we will see, this is extremely infrequent; only about 2\% of borrowers did that.
+As we will see, this is extremely infrequent; only about 3\% of borrowers did that.
 This is not very surprising, borrowers come determined to borrow, many of them to solve an emergency, and are not very sensitive to contract terms (that may explain why they accept high interest rates and over-collateralization in the first place).
@@
 It measured demographics, proxies for income/wealth, education, present-biased preferences, experience pawning, if family or friends commonly asked for money, how time-consuming and costly it was to come to the branch, the subjective probability of recovering the piece that they intended to pawn, the subjective value of their piece in money terms (how much money they would sell it for), among others.
-We surveyed 7,210 clients.
+%We surveyed 7,210 clients. 
 %, and our survey response rate was 78\% among clients who took loans.
 %\footnote{We also surveyed clients before and after the experiment, so our survey covers a larger sample that we are not using in this paper.}.
-Is it important to say that we do \textit{not} use the survey for our main results. We only use the survey in Section \ref{Paternalism} of the paper.
+%Is it important to say that we do \textit{not} use the survey for our main results. We only use the survey in Section \ref{Paternalism} of the paper.
+The reported surveys are at the pawn level. One same borrower can have multiple surveys, one for each pawn, resulting in over 6,000 surveys.
+
+\subsection{Stylized facts}
+
+%\hfill \newline
+%\noindent \textbf{Borrowers.}
+
+\textcolor{red}{Given the scarcity of evidence about pawn loans in economics,  documenting stylized facts is a useful contribution. This section provides some important ones.}
+
+\paragraph*{Borrowers.} Borrowers are not inexperienced: 87\% of clients in our survey report they have pawned before.
+%These clients have little or no access to other types of loans and they value the convenience of pawn borrowing.
+However they are economically vulnerable:  20\% of them could not pay either water, electricity \& gas or rent in the past 6 months.
+In terms of triggers and uses of the loan, 89\% said they are pawning because of an emergency, and only 12\% stated it was to be used in a ``non-urgent expense''.
+When asked why they are pawning this piece, 5\% responded ``lost a family member'', ``a medical emergency'' (11\%), or ``an urgent expense'' (72\%).
+Only 32\% of borrowers have completed college, 73\% are women, with an average age of 43 years.
+
+%\hfill \newline
+%\noindent \textbf{Many borrowers lose their pawn.} 
+\paragraph*{Many borrowers lose their pawn.}
+Our context is also one with high borrower default: 44\% of clients lose their pawn in a time span of 230 days from the date of pawning.
+One potential explanation for high default is that clients are really just knowingly selling their gold piece through a pawn contract on which they intend to default.
+This appears unlikely for several reasons: clients can easily sell the gold and obtain a higher amount of instant cash at gold-buying stores located close to almost all our pawnshop branches;
+%(see Figure \ref{GoldBuyers}) 
+the reported subjective value of the pawn is larger than the appraised value for 83\% of clients (this also means it is inefficient that they lose their pawns).
+The default rates for the experimental period and branches is similar to that observed for all branches in subsequent periods (see Figure \ref{external_validity}).
+
+\paragraph*{Gold buying shops.} Gold purchasing shops locate close to our Lender's branches.
+Branches have an average of 2.8 of these shops in the vicinity.
+This fact is important given the high default rates which could indicate that borrowers are ex ante intending to ``sell'' their pawn.
+Given that they are receiving 70\% of the value of the pawn next door to shops that would give them 100\% of this value, we think this is prima facie unlikely.
+\todo[inline]{Referee asks: ``how do you define the vicinity and is it clear that the clients are aware of this?''}
+
+\paragraph*{Paying without recovering.} Among those that lose their pawn, 29\% paid a positive amount towards its recovery.
+On average this subset of borrowers paid 34\% of the value of their loan (see Figure \ref{proxy_naive} in Appendix).
+This can only be rationalized if they expected to recover their pawn.
+
+\paragraph*{Overconfidence.} 
+Our baseline survey asked borrowers for their subjective probability of recovering the pawn.
+The average self-assessed recovery probability is 92\%.
+This contrasts sharply with the actual recovery rate for these same borrowers, 56\%.
+Overall 72\% of borrowers report a 100\% probability of repaying their loan.\footnote{\textcolor{red}{A recent paper by \cite{predatory2022} finds only the most inexperienced borrowers from a U.S.
+payday lender are overconfident, but their study examines priors about getting out of debt in the future rather than priors on repaying the current loan, as we do.}}    %Note that high default could be detrimental from the lender's point of view, since it may reduce the likelihood that the client becomes a return customer.
+%Lender P was in fact explicitly interested in partnering with us to investigate how to reduce loan default, customer satisfaction, and repeat borrowing.
 
@@
 
-We were aware that the major threat for this study was selection into borrowing based on contract terms.
-This did \textit{not} happen.
-We show this in three different ways.
-First, out of those coming into the branch and filling out the baseline survey (at which time they did not yet know their treatment status), 97\% end up pawning.
+We were aware that the major threat to experimental validity in this study was selection into borrowing based on contract terms.
+We now show in three different was that there was \emph{no such selection}.
+First, among borrowers who entered the branch and completed the baseline survey (at which time they did not yet know their treatment status), 96.5\% end up pawning.
 This rate is not only high but is virtually identical across treatment arms.
-Second, the number of loans per day is not different across arms, showing borrowers did not stop pawning when the forcing arm or choice arm was active.
-Third, borrower and loan characteristics are the same across arms, showing that there is no selection on observables.\footnote{Note that is borrowers self-selected based on contract terms, the results would still reflect the overall impact of a treatment for the lender's portfolio.
-In our case, there is no selection, so we can study the causal effects on borrowers.}
-
-An important implementation detail is that appraisers were paid a flat wage, independent of how many contracts or which types of contracts borrowers signed.
+Second, the number of loans per day did not differ across experimental arms, showing that borrowers did not stop pawning when the structured arm or choice arm was active.
+Third, borrower and loan characteristics are the same across arms, showing that there is no selection on observables.
+%\footnote{Note that even if borrowers self-selected based on contract terms, the results would still reflect the overall impact of a treatment for the lender's portfolio.
+In our case, however, there was no such self-selection, so we can study the causal effects on borrowers.}
+
+An important implementation detail, mentioned above, is that appraisers were paid a flat wage, independent of how many contracts or which types of contracts borrowers signed.
 They therefore had no incentive to influence borrower choice.
@@
 
-Table \ref{attrition_table_final} shows there are no differences in the number of loans, borrowers, or amount borrowed across arms using administrative data.
-Each row corresponds to a regression of the dependent variable on indicators for treatment assignment (status quo/control, forced commitment, choice).
-In the first row (``Take-up'') we use the sample of those who answered the baseline survey (6064 subjects) and check which of them pawned based on the administrative data.
+Table \ref{attrition_table_final} uses administrative data to show there are no differences in the number of loans, borrowers, or amount borrowed across arms.
+Each row corresponds to a regression of the dependent variable on indicators for treatment assignment (status quo/control, structured repayment, choice).
+In the first row (``Take-up'') we use the sample of those individuals who answered the baseline survey (3710 subjects) and check which of them pawned based on the administrative data.
 The dependent variable indicates whether the person pawned.
 Because this survey was implemented at the entrance of the branch before they knew their treatment assignment, it is a good measure of take-up.
-The first result is that the overwhelming majority (97\%) take the loan.
+The first result is that the overwhelming majority (96.5\%) take the loan.
 Second, the same fraction of borrowers take up the loan across treatment arms.
-This is strong evidence that borrowers did not select deferentially according to the structured payments contractual feature.
+This is strong evidence that borrowers did not select into treatment arms, which were announced between survey recruitment and contract completion.
 The remaining rows use only administrative data.
@@
 We also report medians to reduce the influence of outliers.
+\textcolor{red}{Overall, this strongly suggests that the treatments did not induce differential selection.}\footnote{Had we found differential selection, the cross-arm effects would still be relevant from the perspective of the lender, but would no longer represent intensive margin impacts on comparable groups of people.}
+
+%This suggests clients were determined to borrow, and that frequent payments do not present an important hurdle in their desire do it; 87\% of surveyed borrowers have pawned before with Lender P.
+
+\todo[inline]{The referee asks how the standard errors were computed in the Tables ``No Selection across arms'' and asks the same question for the ``tests of equality'' but I don't know what the latter refers to}
 
@@
 \begin{center}
+\resizebox{0.65\textwidth}{!}{
 \footnotesize{\input{./Tables/Attrition.tex}}
+}
 \end{center}
 \scriptsize{Each row in this table 
- corresponds to a regression at the branch-day level of each dependent variable against the experimental arms indicators (control, forced commitment, choice).
+ corresponds to a regression at the branch-day level of each dependent variable against the experimental arms indicators (control, mandatory structure , choice).
 The table reports the coefficients on each of these indicators, as well as the p-value of an F-test of the null hypothesis of equality of the three coefficients.
@@
 This was reinforced by reports from our enumerators and appraisers that those who entered the branch were determined to borrow and that there were no complaints about what loan contracts were available.
-Note that this does not mean that they did not care about contract terms.
-It means just that the outside option of leaving the branch without a loan is unattractive.
+Importantly, this does \emph{not imply} that borrowers had no preference over alternative contracts.
+It simply means that the outside option of leaving the branch without a loan is unattractive.
+
+\todo[inline]{The referee asks how the standard errors were computed in the Tables ``Borrower's characteristics are balanced'' and asks the same question for the ``tests of equality'' but I don't know what the latter refers to}
 
@@
 Survey data is not used for the main results of the paper.
-It is only used in Section \ref{Paternalism}.
+It is only used in Section \ref{why_paternalism}.
 Each row in this table corresponds to a regression, where the level of observation is a borrower that pawned which was surveyed.
 The dependent variables are displayed in the first column.
-Each dependent variable is regressed against the experimental arms indicators (control, forced commitment, choice).
+Each dependent variable is regressed against the experimental arms indicators (control, mandatory structure, choice).
 The table reports the coefficients on each of these indicators, as well as the p-value an F-test of the null hypothesis of equality of the three coefficients.
-``Subjective value'' of the pawn refers to how much would the client be willing to sell the pawn for in pesos, ``Trouble paying bills'' is an indicator for the borrower reporting having problems paying electricity, water and services in the last 6-months, present bias is constructed as in \cite{Ashraf}; ``Makes buget'' os an indicator for whether the household make expenses budget for the month ahead of time.
+``Subjective value'' of the pawn refers to how much would the client be willing to sell the pawn for in pesos, ``Trouble paying bills'' is an indicator for the borrower reporting having problems paying electricity, water and services in the last 6-months, present bias is constructed as in \cite{Ashraf}; ``Makes buget'' as an indicator for whether the household make expenses budget for the month ahead of time.
 The subjective probability of recovery was elicited a la Manski (from 0 to 100 what is the probability that you will recoup your pawn); pawned before is a dummy=1 if the client declares to have pawned before (although not necessarily with Lender $P$); age is age of the borrower in years, +High-school is a dummy that indicates if the client has completed high school.
@@
 
-\section{Average Treatment Effects} \label{Experiment}
-
-We begin by estimating average treatment effects of assignment to the Forced structured payments and the Choice arms, relative to those assigned to the Control arm.
+%\subsection*{Potential Outcomes and Exclusion}
+%\label{sec:potentialOutcomes}
+%\todo[inline]{This is a subsection that no longer exists but we need to go through and remove any cross-references to it.}
+
+\section{The ``Mandates vs.\ Choice'' Design}
+\label{sec:randchoice}
+
+%\todo[inline]{The first paragraph of this section will need to be changed a bit to reflect its new location in the document.
+Since it's now a standalone section, I named it after our experimental design.}
+
+We now develop more formally the assumptions that are required to translate the three-armed experiment of control, choice, and mandates into a structure that permits the point indentification of the Treatment on the Treated and the Treatment on the Untreated.
+%This section shows that, under an additional mild exclusion restriction assumption, our three-armed experimental design point-identifies a range of additional treatment effects of interest. 
+%Foremost among them is the effect of treatment on the \textit{untreated}--those who would not demand structured repayment contracts--which is needed to assess the benefits mandating a contractual feature.
+We begin by providing a full definition of the potential outcomes in our empirical setting.
+Let $Z_i \in \{0, 1, 2\}$ denote the treatment arm to which to participant $i$ was assigned: $Z_i = 0$ denotes the mandatory no-structure arm, $Z_i = 1$ denotes the mandatory structured arm, and $Z_i = 2$ denotes the choice arm.
+Now let $D_i$ be the treatment that participant $i$ actually \emph{received}, where $D_i = 0$ denotes no-structure and $D_i = 1$ denotes structure. 
+We assume perfect compliance in the $Z_i = 0$ and $Z_i = 1$ arms. %\footnote{For more discussion on this point, see Section \ref{sec:integrity} above.}
+It is only in the $Z_i = 2$ arm that participants are free to choose between alternative contracts. 
+Let $C_i \in \{0, 1 \}$ denote a participant's ``choice type.'' If $C_i = 1$ then participant $i$ \emph{would choose structure}, given the option; if $C_i = 0$ she would not. 
+As shorthand, we call borrowers with $C_i = 1$ ``choosers'' and those with $C_i = 0$ ``non-choosers.''
+Whereas a participant's choice type $C_i$ is only observed if she is allocated to the choice arm ($Z_i = 2$), her treatment $D_i$ and experimental arm $Z_i$ are always observed. 
+Given the design of our experiment, these quantities are related by
+\begin{equation}
+D_i = \mathbbm{1}(Z_i \neq 2) Z_i + \mathbbm{1}(Z_i = 2) C_i.
+\label{eq:potentialTreatments}
+\end{equation}
+
+We maintain the stable unit treatment value assumption (SUTVA) throughout. 
+This means that borrower $i$'s outcomes depend only on her \emph{own} values of $Z_i$ and $D_i$, not those of any other person in the experiment. 
+Under this assumption, a fully general model for the potential outcomes in our experiment would take the form $Y_i(d, z)$ for $d\in \{0,1\}$ and $z \in \{0, 1, 2\}$, allowing participant $i$'s potential outcome to depend \emph{both} on the treatment she actually receives, $D_i$, and the experimental arm to which she is assigned, $Z_i$.
+This model is too general, however, to point identify meaningful causal effects. 
+For this reason we impose a standard exclusion restriction, namely
+\begin{equation}
+Y_i(d,z) = Y_i(d) \equiv Y_{id},\quad z \in \{0, 1, 2\}, \quad d\in \{0, 1\}.
+\label{eq:exclusion}
+\end{equation}
+Mathematically \eqref{eq:exclusion} has the same structure as the standard LATE exclusion restriction. 
+Substantively, however, its interpretation is a bit more specific, given that there is no explicit reference to the ``chosen'' versus ``mandatory'' treatment distinction in the usual LATE setup.
+In our context, \eqref{eq:exclusion} implies that being assigned a particular treatment has the same result as choosing it for yourself.\footnote{Strictly speaking the results that follow \emph{only} require $Y_i(0,2)=Y_{i0}$ and $Y_i(1,2) = Y_{i1}$.
+In words: being assigned a particular treatment has the same result as choosing it for yourself, provided that that you are assigned the same treatment that you would have chosen freely.}
+If the mere fact of having been given a choice has a direct effect on outcomes this assumption fails. 
+For example: someone who, given the choice, would voluntarily choose to undergo drug rehabilitation, might respond differently when coerced.
+In our experiment, however \eqref{eq:exclusion} is plausible.\footnote{Closely related assumptions are common, if often tacit.
+\cite{chamberlain2011bayesian} explicitly assumes that choosing and being assigned a treatment have the same effect.
+A significant literature using compulsory schooling laws to estimate the returns to education tacitly assumes that schooling \emph{in general} has the same returns, regardless of whether it is mandated or chosen freely.
+Similarly, fertilizer yields are tacitly assumed to generate the same returns regardless of whether the fertilizer was chosen by farmers or provided by the government, as long as it is the same fertilizer.}
+Moreover, it has testable implications that we fail to reject: see \autoref{sec:testing_exclusion}. 
+Under \eqref{eq:exclusion}, the observed outcome $Y_i$ is related to $(Y_{i0}, Y_{i1})$ by 
+\begin{equation}
+    Y_i = \mathbbm{1}(Z_i =0) Y_{i0} + \mathbbm{1}(Z_i = 1)  Y_{i1}  + \mathbbm{1}(Z_i = 2) \left[(1 - C_i) Y_{i0} + C_i Y_{i1} \right].
+\label{eq:potentialOutcomes}
+\end{equation}
+
+Equation \ref{eq:potentialOutcomes} is the key to understanding the mandates versus choice design. 
+Random assignment of $Z_i=0$ and $Z_i = 1$ identifies the marginal distributions of $Y_{i0}$ and $Y_{i1}$ for the population as a whole. 
+Random assignment of $Z_i=2$ likewise point identifies the share of choosers ($C_i = 1$), the distribution of $Y_{i1}$ for choosers, and the distribution of $Y_{i0}$ for non-choosers ($C_i = 0$).
+Because $Z_i$ is assigned independently of pre-treatment covariates $X_i$, we also identify the \emph{conditional} distributions of $Y_{i0}$ and $Y_{i1}$ given $X_i$. 
+As a direct consequence, our design point identifies a number of interesting and economically-relevant causal quantities. 
+First among these are the treatment on the untreated (TUT) and treatment on the treated (TOT) effects:  
+\[
+\text{TUT} \equiv \mathbbm{E}(Y_{i1} - Y_{i0} | C_i = 0), \quad
+\text{TOT} \equiv \mathbbm{E}(Y_{i1} - Y_{i0} | C_i = 1).
+\]
+The TUT is the causal effect of structure on borrowers who would not voluntarily choose it; the TOT is the causal effect on borrowers who would choose structure.
+If the TUT is positive, this means that borrowers who did not choose structure would have experienced better outcomes, \emph{on average}, if they had.
+
+Figure \ref{tot_tut_graph} provides graphical intuition for why our design identifies the TUT and TOT. 
+Viewing $Z_i$ as an instrumental variable, the Mandates versus Choice design can be seen as a \emph{pair} of RCTs, each subject to one-sided non-compliance.
+The first compares $Z_i = 1$ to $Z_i=2$ and identifies the TUT.
+By a standard argument (see Appendix \ref{sec:proofs}), 
+\begin{equation}
+\frac{\mathbbm{E}(Y_i|Z_i=1) - \mathbbm{E}(Y_i|Z_i =2)}{\mathbbm{E}(D_i|Z_i=1)-\mathbbm{E}(D_i|Z_i=2)} = 
+\frac{\mathbbm{E}(Y_i|Z_i=1) - \mathbbm{E}(Y_i|Z_i =2)}{1 - \mathbbm{E}(D_i|Z_i=2)} = \text{TUT}.
+\label{eq:TUT}
+\end{equation}
+since everyone with $Z_i=1$ is treated.
+Similarly, since no one with $Z_i = 0$ is treated, a comparison of $Z_i=0$ to $Z_i = 2$ identifies the TOT:
+\begin{equation}
+\frac{\mathbbm{E}(Y_i|Z_i=2) - \mathbbm{E}(Y_i|Z_i =0)}{\mathbbm{E}(D_i|Z_i=2)-\mathbbm{E}(D_i|Z_i=0)} = 
+\frac{\mathbbm{E}(Y_i|Z_i=2) - \mathbbm{E}(Y_i|Z_i =0)}{\mathbbm{E}(D_i|Z_i=2)} = \text{TOT}.
+\label{eq:TOT}
+\end{equation}
+Because our design identifies by the TUT and TOT, it allows us to calculate the average selection on gains (ASG), the difference between the TOT and TUT effects:
+\[
+\text{ASG} \equiv \mathbbm{E}[Y_{i1} - Y_{i0}|C_i = 1] - \mathbb{E}[Y_{i1} - Y_{i0} | C_i = 0] = \text{TOT} - \text{TUT}.
+\]
+In a canonical Roy model $\text{TOT} > \text{TUT}$ so the ASG would be \emph{positive}.
+The Mandates versus Choice design allows us to test this implication directly.
+
+\begin{figure}
+\caption{Graphical Intuition for the Mandates vs.\ Choice Design.} 
+    \begin{center}
+        \centering
+        \includegraphics[width=1.0\textwidth]{Figuras/tot_tut_graph.png}
+    \end{center}
+ \scriptsize{
+     %This figure illustrates why the controlled choice design identifies the TOT and TUT effects.
+    Gray rectangles denote borrowers with a structured contract; white rectangles denote borrowers with a status quo contract. 
+    A comparison of means across control and Structured arms identifies the ATE of Structure. 
+    %In the choice arm, anyone with a commitment contract is a chooser; in the control and forcing arms, we do not know who is a chooser and who is not, but because borrowers are randomly assigned to experimental treatment arms, the share of choosers will be the same, on average (depicted using dashed vertical lines).
+    The difference of mean outcomes across the choice and control ``nets out'' the non-choosers, and hence equals the TOT multiplied by the share of choosers.
+    %arms gives the intent-to-treat effect of offering choice. 
+    %Under the exclusion restriction that moving non-choosers between the choice and forcing arms does not change their outcomes, this comparison ``nets out'' the non-choosers.
+    %Hence, the ITT of offering choice equals the TOT multiplied by the share of choosers. 
+    %Similarly, under the exclusion restriction that moving choosers between the choice and forcing arm does not affect their outcomes. 
+    Similarly, the difference of means across the structured and choice arms ``nets out'' the choosers and equals the TUT multiplied by the share of non-choosers.
+        The share of choosers, illustrated using dashed vertical lines, is equal on average across arms under random assignment.}
+    \label{tot_tut_graph}
+     %\textit{Do file: }  \texttt{tot\_tut\_graph.do}
+\end{figure}
+
+A number of recent papers compare estimates of the TOT and TUT to better understand who selects into treatment and why, e.g.\ \cite{cornelissen2018benefits} and \cite{Walters}. 
+This line of work relies, at least to some extent, upon structural modeling assumptions to extrapolate from the reduced-form quantities that are identified by the data alone to more interesting, and economically relevant, causal parameters.\footnote{While the marginal treatment effects (MTE) approach \citep{heckman2007econometric} can in principle be used to identify the TOT and TUT without parametric restrictions, doing so requires an instrumental variable $Z$ with sufficiently rich support that the probability of treatment take-up given $Z$ varies continuously between zero and one.
+In practice, instrumental variables are usually discrete and, even when continuous, typically have a more modest effect on take-up.}
+An alternative approach aims to avoid structural assumptions by calculating conditional local average treatment effects (LATE) given observed covariates $X$ and re-weighting them according to the distribution of covariates in some population of interest to yield, for example, an average treatment effect \citep{aronow2013beyond,angrist2013extrapolate}.
+%For example, one might re-weight using the distribution of $X$ in the population as a whole, rather than the sub-population of compliers, to extrapolate from LATE to ATE. 
+But there is no free lunch: this ``LATE-and-reweight'' approach relies upon assumptions of its own, most crucially the assumption that there is \emph{no selection-on-gains} conditional on $X$, i.e.\ that the conditional LATE equals the conditional ATE.
+In contrast to both approaches, the Mandates vs.\ Choice design uses exogenous experimental variation to point identify the ATE, TOT, and TUT without ruling out unobserved selection-on-gains or relying on additional structural modeling assumptions.
+
+In addition to the TUT, TOT and ASG, the Mandates vs.\ Choice design also identifies the average selection bias (ASB) and average selection on levels (ASL). In particular,
+\begin{align}
+\label{eq:ASB}
+    \text{ASB} &\equiv \mathbbm{E}(Y_{i0}|C_i=1) - \mathbbm{E}(Y_{i0}|C_i = 0) = \frac{\mathbbm{E}(Y|Z=0) - \mathbbm{E}(Y|Z=2,D=0)}{\mathbbm{E}(D|Z=2)}\\
+    \label{eq:ASL}
+    \text{ASL} &\equiv \mathbbm{E}(Y_{i1}|C_i = 1) - \mathbbm{E}(Y_{i1}|C_i=0) = \frac{\mathbbm{E}(Y|Z=2,D=1) - \mathbbm{E}(Y|Z=1)}{1 - \mathbbm{E}(D|Z=2)}
+\end{align}
+as shown in \autoref{sec:proofs}.
+The ASB tells us whether borrowers who voluntarily choose structure are those who are worse off, on average, under the status quo.
+Similarly, the ASL tells us whether borrowers who voluntarily choose structure are those who are better off, on average, under the structured contract.
+Equations \eqref{eq:TOT}--\eqref{eq:ASL} are useful for understanding why our experimental design identifies the TOT, TUT, ASG, ASB, and ASL but they are less convenient for estimation and inference. 
+\autoref{sec:estimation_inference} explains how to compute each of these quantities from a small  number of just-identified, linear instrumental variables regressions, along with appropriate cluster-robust standard errors.
+These estimators and standard errors are implemented in our companion STATA package. %\textcolor{red}{Add a link to this package along with the documentation.}
+
+\section{Results} \label{Experiment}
+
+%\todo[inline]{This section may need a new title: now it includes both ATE and TUT/TOT results.}
+
+\subsection{Simple Experimental Results}
+
+We begin our presentation of results with a standard estimation of experimental assignment to the Mandatory structured payments and the Choice arms, relative to the Control arm.
 As we explain below, only about 11\% of those in the choice arm chose the monthly payment option (Figure \ref{determinants_choose} shows coefficient plots for the characteristics that determine choosing structured payments in the Choice arm).
@@
 \begin{equation} \label{basic_reg}
-    y_{ij} = \alpha + \beta^F T_{i}^F + \beta^C T_{i}^C + \gamma X_{ij} + \epsilon_{ij}
+    y_{ij} = \alpha + \beta^M T_{i}^M + \beta^C T_{i}^C + \gamma X_{ij} + \epsilon_{ij}
 \end{equation}
-where $i$ indexes the borrower, $j$ indexes branch, $T_{i}^F$ and $T_{i}^C$ are indicator variables for receiving the Forced or Choice arms, $X_{ij}$ are branch and day-of-week fixed effects.
+where $i$ indexes the borrower, $j$ indexes branch, $T_{i}^M$ and $T_{i}^C$ are indicator variables for receiving the Mandatory or Choice arms, $X_{ij}$ are branch and day-of-week fixed effects.
 Standard errors are clustered at the branch-day level, the unit of treatment assignment\footnote{A minority of borrowers pawned on more than one day during the experiment: 14\% pawned on two distinct days, and 8\% on three or more days.
@@
 Because our standard errors are clustered at the branch-day level, they automatically account for any dependence in error terms arising from multiple pawns by the same borrower on her first visit.}.
-Given full compliance in the Forced arm, the coefficient $\beta^F$ is the ATE of forced commitment while $\beta^C$ is the ITT of commitment in the Choice arm on the outcome variable $y_{ij}$.
+Given full compliance in the Mandatory arm, the coefficient $\beta^M$ is the ATE of mandatory structure while $\beta^C$ is the ITT of structure in the Choice arm on the outcome variable $y_{ij}$.
 %\footnote{Note that $\beta^C$ can be viewed in two ways: as the ATE of \emph{offering clients a choice} between the status quo and commitment contract or as the intent-to-treat effect of the commitment contract \emph{itself}.
@@
 \scriptsize{This table shows the treatment effects for our core pecuniary outcomes.
-Each column is a different regression for different outcomes on an indicator for the forced and choice arms, following specification in equation \ref{basic_reg}.
+Each column is a different regression for different outcomes on an indicator for the mandated and choice arms, following specification in equation \ref{basic_reg}.
 Columns (1) \& (7) analyze our core financial cost measures, while the rest of the columns decompose these into finer components.
@@
 \paragraph*{Results} The results are stark.
-The Forced Commitment arm yields large and significant decreases in the cost of loans to clients, as measured either by financial cost or APR.
-Despite causing an increase in fees, the Forced arm leads to a decrease of 204 pesos in the costs of borrowing (out of a group mean of 942 in the status quo), equivalent to 22\% reduction as a fraction of mean cost.
-These cost savings arise from a 6.6 percentage point (pp) decrease in the probability of default (out of a baseline mean of 44pp,  implying cost savings of 79 pesos), and also from lower interest payments since, as we will document below, the commitment contract speeds up payments so the interest rate applies to a smaller principal.
+The mandatory structure arm yields large and significant decreases in the cost of loans to clients, as measured either by financial cost or APR.
+Despite causing an increase in fees, the Mandated arm leads to a decrease of 204 pesos in the costs of borrowing (out of a group mean of 942 in the status quo), equivalent to 22\% reduction as a fraction of mean cost.
+These cost savings arise from a 6.6 percentage point (pp) decrease in the probability of default (out of a baseline mean of 44pp,  implying cost savings of 79 pesos), and also from lower interest payments since, as we will document below, the commitment-style contract speeds up payments so the interest rate applies to a smaller principal.
 This translates into a large reduction in APR.
@@
 
-In contrast, to the impressive effectiveness of the Forced commitment arm, the Choice arm fails to deliver significant changes in any measure, with the exception of an increase in fees, for which we are highly powered, since this outcome is zero for every control observation.
+In contrast, to the impressive effectiveness of the mandatory structure arm, the Choice arm fails to deliver significant changes in any measure, with the exception of an increase in fees, for which we are highly powered, since this outcome is zero for every control observation.
 Giving borrowers the choice of contract did not decrease financial cost, whereas forcing them into a structured payment contract dramatically reduced it.
-As we explore later in the paper, the null effect of the Choice arm arises because few borrowers demanded commitment (consistent with \cite{Ashraf}, \cite{Gine}, \cite{Ted}, \cite{Royer}, \cite{Sprenger}), with 89\% choosing the less effective status-quo contract.
+As we explore later in the paper, the null effect of the Choice arm arises because few borrowers demanded structure (consistent with \cite{Ashraf}, \cite{Gine}, \cite{Ted}, \cite{Royer}, \cite{Sprenger}), with 89\% choosing the less effective status-quo contract.
+
+\begin{landscape}
+%\subsection{Intermediate Outcomes}
+
+\begin{table}[!h]
+\caption{Effects on intermediate outcomes}
+\label{mechanisms}
+\begin{center}
+
+\scriptsize{\input{./Tables/mechanism.tex}}
+
+\end{center}
+\footnotesize{This table explores treatment effects in ``intermediate variables''.
+Each column represents regression output for different dependent variables following equation (\ref{basic_reg}).
+Panel A focuses on variables related to the speed of payment.
+While Panel B focuses on variables related to default, and Panel C related to visits.
+% The outcome variables are as follows:  number of days elapsed between origination and first payment (col 1); percentage of the loan paid in the first payment (col 2); probability of recovery in the first visit (col 3); loan duration is the number of days the borrower took to payoff her loan for those that recover, the number of days until default for those that default, and the maximum number of days we observe them in the sample for those that have not recovered or defaulted (col 4); loan duration conditional on recovery; an indicator for paying a positive amount towards recovery but nonetheless losing the pawn (col 6); the percentage or the loan paid, conditional on defaulting --`wasted payments' (col 7).
+Column 8 uses the phrase `selling the pawn' for a dummy variable indicating the borrower did not pay any amount towards recovery and lost the pawn.
+Moreover, (col 9) shows that treatment effects are concentrated in the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery.
+The dependent variable in column 10 is the number of day-visits to the branch (measured by the existence of transactions that day associated with our particular pawn), while column 11 conditions on borrowers that lost the pawn.
+Each regression includes branch and day-of-week FE. Standard errors are clustered at the branch-day level.}
+%\textit{Do file: } \texttt{mechanisms.do}
+\end{table}
+\end{landscape}
+
+\normalsize
+%Really force it to normal size and linespread
+\normalsize
 
@@
 %\noindent \textbf{Intermediate outcomes.} 
-\paragraph*{Payment speed} To shed light on the mechanisms behind the ATEs discussed above, Table \ref{mechanisms} shows how commitment affects a number of intermediate outcomes.
+\paragraph*{Payment speed} To shed light on the mechanisms behind the ATEs discussed above, Table \ref{mechanisms} shows how structure affects a number of intermediate outcomes.
 One can group the types of intermediate outcomes into two categories: measures of the speed of pawn recovery, and measures of the decision of when to default.
-While the first payment for borrowers in the status-quo contract occurs on average only on day 82 (on a 90 days contract), borrowers in the forced commitment arm start paying 13.8 days earlier on average (col 1).
+While the first payment for borrowers in the status-quo contract occurs on average only on day 82 (on a 90 days contract), borrowers in the mandatory structure arm start paying 13.8 days earlier on average (col 1).
 Not only do they start paying earlier, the first payment is also 9.7\% larger (col 2), and a larger fraction (7.9\%)  actually pay in full and recover their pawn in the first payment, compared to 30\% in the status quo contract (col 3).
@@
 
-\paragraph*{Payment Bifurcation} A very undesirable outcome from the borrower's perspective is to pay towards the loan without paying in full, i.e.
-defaulting on the loan while still making some payments.
-In this case, they lose both the collateral and any payments made toward recovery.
-One could be concerned that by encouraging them to pay monthly, more borrowers might end up in this dire scenario in the Forced commitment contract.
+\paragraph*{Payment Bifurcation} A very undesirable outcome from the borrower's perspective is to pay towards the loan without paying in full, i.e.\ to default on the loan despite making some payments.
+In this case, borrowers lose both the collateral and any payments made toward recovery.
+One could be concerned that by encouraging them to pay monthly, more borrowers might end up in this dire scenario in the mandatory structure contract.
 Column 6 shows this is not the case.
-On the contrary, 7 percentage points fewer borrowers end up in this situation, compared to 12 percent in the status quo contract.
-Conditional on defaulting those assigned to the Forced commitment contract have paid 4.1\% less of their loan (col 7), and a 14 percent higher proportion of borrowers pay zero conditional on defaulting, an outcome analogous to
+On the contrary, 7 percentage points fewer borrowers end up in this situation, compared to a status quo contract mean of 12 percent.
+Conditional on defaulting those assigned to the mandatory structure contract have paid 4.1\% less of their loan (col 7), and a 14 percent higher proportion of borrowers pay zero conditional on defaulting, an outcome analogous to
 ``selling their pawn'' (col 8).
-One interpretation of this bifurcation is that the Forced commitment contract forces borrowers to think earlier about whether they will indeed be able to eventually recover their pawn, and separates borrowers into those ``selling'' their pawn and those recovering it, reducing the share of undecided borrowers that end up paying interest and end up losing the pawn anyway.
-This mechanism may also help to explain why the Forced commitment contract does not increase the number of visits to the branch to pay (col 10): those recovering their pawn visit more, but those defaulting have 0.20 fewer visits (col 11).
+One interpretation of this bifurcation is that the mandatory structure contract forces borrowers to think earlier about whether they will indeed be able to eventually recover their pawn, and separates borrowers into those ``selling'' their pawn and those recovering it, reducing the share of undecided borrowers that end up paying interest and end up losing the pawn anyway.
+This mechanism may also help to explain why the mandatory structure contract does not increase the number of visits to the branch to pay (col 10): those recovering their pawn visit more, but those defaulting have 0.20 fewer visits (col 11).
 Finally, Column 9 shows that treatment effects are concentrated in the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery.
@@
 This includes the self-reported transport cost (most use public transport), as well as the opportunity cost of time.
-To err on the conservative side, we subtract a whole day's minimum wage the day of the visit, instead of just the wage corresponding to a couple of hours.
+To err on the conservative side, we subtract a whole day's minimum wage for the day of the visit.
+%instead of just the wage corresponding to a couple of hours. 
 Second, we consider a rough proxy of the value of liquidity that borrowers lose by paying sooner.
-To do this we add the interest costs on to the payments in the forced commitment arm and recompute treatment effects with these payments compounding daily (as if they had to borrow in order to make the more rapid payments).
-Thirdly, so far we have valued the collateral at the gold value appraised by the lender, but the piece may be worth more to the borrower than its gold value.
+To do this we add the interest costs on to the payments in the mandatory structure arm and recompute treatment effects with these payments compounding daily (as if they had to borrow in order to make the more rapid payments).
+Third we consider the \emph{subjective} value of the pawn.
+All results presented thus far value the collateral as appraised by the lender, but the piece may be worth more to the borrower than its gold value.
 For many of them the pawned jewelry has sentimental value.
-This is reflected in the subjective valuation they reported in the survey which is 87\% higher on average.
-Our third extra cost considers this higher value.
-Table \ref{table_robustness_fc} shows results are robust to all these changes.
-
-We want to be very clear that we are not measuring borrower welfare, for several obvious reasons.
-For example, requiring monthly payments may well increase stress we are not taking into account.
-We are not taking into account discounting given the short period, although in Section \ref{why_paternalism}, we show that to rationalize the findings, we would need unreasonably high discount rates.
-We are also not measuring financial cost on other loan products.\footnote{However, we think it is unlikely that borrowers ask for even more expensive loans to pay the monthly payment.
+This is reflected in the subjective valuation they reported in the survey, which is almost twice as large as the appraised gold value of the pawn on average.
+Our third extra cost considers this higher subjective value.
+Table \ref{table_robustness_fc} shows that our results are robust to all these changes.
+
+It is worth emphasizing that our results do not directly measure borrower welfare. 
+Financial cost savings and welfare could diverge in a number of ways.
+%We want to be very clear that we are not measuring borrower welfare, for several obvious reasons. 
+For example, requiring monthly payments could cause an increase in borrowers' levels of stress, an effect that our measures do not take into account.
+Moreover, given the short time frame of pawn loans, we do not explicitly account for discounting.
+As shown in Section \ref{why_paternalism}, however, one would need to assume unreasonably high discount rates to cast doubt on our findings. 
+Similarly, we cannot measure the financial cost of other loans that borrowers may potentially take out to make interim payments on their initial pawn loan. 
+Given that the ``penalty'' from a missed interim payment is small--less than the transport cost to visit the branch--we consider it unlikely that borrowers will have taken out even more expensive loans to avoid the penalty.
+%However, we think it is unlikely that borrowers ask for even more expensive loans to pay the monthly payment.
 The `punishment' from the monthly fee is small, less than the transport cost to go to the branch.
-It is likely better to incur the fee than go through the process of asking for an additional loan to avoid this fee.} Having said this, a large literature focuses on the cost of servicing loans.
-We follow in the steps of this literature.
+It is likely better to incur the fee than go through the process of asking for an additional loan to avoid this fee.}
+Having said this, a large literature focuses on the cost of servicing loans. We follow in the steps of this literature.
 
@@
 Overall, 13\% of all experimental loans are censored, meaning that they neither default nor repay within the observation window.
-In the prior analysis we handle this issue in a conservative way by using outcomes such as ``did not default'' which are well-defined even when we do not observe the completion of the loan, resulting in an estimate biased toward zero by the more rapid loan repayment observed in the Forcing arm.
+In the prior analysis we handle this issue in a conservative way by using outcomes such as ``did not default'' which are well-defined even when we do not observe the completion of the loan, resulting in an estimate biased toward zero by the more rapid loan repayment observed in the Structured arm.
 In the Online Appendix we consider this issue in more detail.
 Most importantly, Table \ref{bounding_censoring} conducts a bounding exercise that examines how large the effects of this censoring could possibly be by making bracketing assumptions about repayment on censored loans in the treatment and control, respectively.
-Comfortingly, Panel B of this table shows that even the most muted possible effect in the bounding exercise still recovers impacts of Forcing on financial costs and APR that are negative and significant at the 99\% level.
-Using a lasso-logit model to predict the outcome of censored loans, Panel E shows the APR impact of Forcing increases from a 14 pp reduction (headline results) to a 17 pp reduction.
-Hence there appears to be no scope for this censoring issue to overturn our results, and our core results (implicitly assuming censored loans are paid off) is almost certainly an under-estimate of the true impacts.
+Comfortingly, Panel B of this table shows that even the most muted possible effect in the bounding exercise still recovers impacts of Structure on financial costs and APR that are negative and significant at the 99\% level.
+Using a lasso-logit model to predict the outcome of censored loans, Panel E shows the APR impact of Structure increases from a 11 pp reduction (headline results) to a 17 pp reduction.
+Hence there appears to be no scope for this censoring issue to overturn our results, and our core results (implicitly assuming censored loans are not defaulted) is almost certainly an under-estimate of the true impacts.
+
+\todo[inline]{Regarding the next paragraph on lender profit, the referee asks: ``in the computation of profit you also assume independence between repeat and the amounds.
+Couldn't you simply model total financial costs as a function of the duration observed to extrapolate?''}
 
@@
 For a single loan, lenders get what borrowers lose in a zero-sum way so that a borrower's Financial Cost$_i$ for loan $i$ is the profit from that loan for the lender.
-Table \ref{main_impact_table} showed that \textit{per loan} borrowers pay less to lenders under the structured payments contract.
-However, in Table \ref{repeat_loans} in the appendix, we show that borrowers assigned to the forced arm are 6.7\% more likely than in the status quo arm to be repeat customers during our sample period.
-This brings some extra benefit to lenders that we need to take into account in a simple back-of-the-envelope calculation.
-From column 1 of Table \ref{main_impact_table} we know \{Financial Cost$_i$ $|$ Contract=c\} for $c$= status quo or structured payment contracts are respectively \hl{XX} and \hl{XX}.
-From Table \ref{repeat_loans} we know $\Pr(\text{Repeat} | \text{Contract}=c)$ for $c$= status quo or structured payment contracts are respectively \hl{XX} and \hl{XX}.
+Table \ref{main_impact_table} showed that borrowers pay less to lenders \emph{per loan} under the structured payments contract.
+However, in Table \ref{repeat_loans} in the appendix, we show that borrowers assigned to the mandatory structure arm are 6.7\% more likely than in the status quo arm to be repeat customers during our sample period.
+This brings some extra benefit to lenders that we take into account in a simple back-of-the-envelope calculation.
+From column 1 of Table \ref{main_impact_table}, $\mathbbm{E}\left[\text{Financial Cost}_i | \text{Contract=X}\right]$ for $X$= \{status quo, structure\} contracts are approximately \$942MXN and \$738MXN.
+From Table \ref{repeat_loans} we know $\Pr(\text{Repeat} | \text{Contract}=X)$ for $X$= \{status quo, structure\} are 32\% and 38.7\%, respectively.
 We can use these four numbers to calculate a discounted sum of profits for client $j$ comparing a scenario where only status quo loans are offered with a second scenario where only structured payment loans are offered.\footnote{We do this for simplicity.
-Otherwise, we would have to assume something about how borrowers switch dynamically across loans, and this is something we do not observe in the data.} One way to do a back-of-the-envelope calculation is by plugging those numbers in the following equation:
- $\text{Profit}_{j,c} = \{\text{Financial Cost}_j | \text{Contract}=c\}\{1+n\times\Pr(\text{Repeat}_j)\}$ where $n$ is are exogenously arising need to borrower, which are lead to repeat pawning.
-A second possibility is to compound the probability of coming back to take into account that pawning may lead to more repeat pawning and this compounds: $\text{Profit}_{j,c}  = \sum_{T}\delta^T\{\text{Financial Cost}_j | \text{Contract}=c\}\times\Pr(\text{Repeat} | \text{Contract}=c)^T$, where $\delta$ is the discount rate.
-We find in the first case that the status quo contract dominates the structured payment contract for all $n$.
-\hl{For the second alternative, we find that for every  $\delta$ in [0,1] and for every $T$ the status quo also dominates.} That is, the extra repeat probability in the structured payment is not enough to compensate for the loss per each of those loans.
-Table \hl{XX} in the appendix shows the calculation for different values of $\delta, n, T$.
-
-% \begin{equation}
-% \label{profit_function}
-% \text{Profit}_{j,c}  = \sum_{T=0}^{\infty}\{\text{Financial Cost}_j | \text{Contract}=c\}\times\Pr(\text{Repeat Pawn}_j | \text{Contract}=c)^T 
-% \end{equation}
-
-% where $j$ indexes a borrower, and $c$ indicates the first assigned contract/treatment to borrower $j$.
-The profit for the status-quo contract is  \$1578, while that of the forced-commitment contract is \$1418, which results in less profit for the forced-commitment contract even when considering repeat pawning behavior.
-
-\section{Choice and Heterogeneous Treatment Effects}
-\label{Choice}
-
-The results from Section \ref{Experiment} show that commitment \emph{works}: clients who were assigned to the forced commitment arm experienced substantially lower financial costs on average.
-In spite of this, given the opportunity, only 11\% of borrowers chose commitment. 
-If the effect of commitment were homogeneous, this would be enough to conclude that the 89\% who did not choose it would have been financially better-off if they had.
-In a world of heterogeneous treatment effects, however, low demand for commitment could still be consistent with borrowers adhering to a standard model of rational choice. 
-The borrowers who did not choose commitment could simply be those who don't need it. 
-Indeed, we find strong evidence that the effect of forced commitment varies substantially across individuals in our experiment: we test and reject
+Otherwise, we would have to assume something about how borrowers switch dynamically across types loans, and this is something we do not observe in the data.}
+Assuming independence across repawning events within a given contract type gives  
+\[
+\text{Profit}_{j,X}  = \sum_{t=0}^T\delta^t\mathbbm{E}\left[\text{Financial Cost}_j | \text{Contract}=X\right]\times\Pr(\text{Repeat} | \text{Contract}=X)^t
+\] 
+where $\delta$ is the discount rate.
+We find that for every  $\delta$ $\in$ [0,1]    and for every $T$ the status quo results in higher profit for the lender.
+That is, the extra repeat probability for the structured payment contract is not enough to compensate for the loss in each of those loans.\footnote{An alternative calculation is as follows: $\text{Profit}_{j,X} = \{\text{Financial Cost}_j | \text{Contract}=X\}\{1+n\times\Pr(\text{Repeat}_j)\}$ where $n$ is are exogenously arising need to borrower, which are lead to repeat pawning.
+In this case, the status quo contract dominates (profit-wise) the structured payment contract for all $n$.} Figure \ref{profit_mandatory_control} in the appendix shows the examples for different values of $\delta, T$.
+
+%\section*{Choice and Heterogeneous Treatment Effects}
+%\label{Choice}
+
+%\todo[inline]{This title refers to the old version: we will need to remove cross-references to it}
+
+%\todo[inline]{The next paragraph needs to be revised given how we're restructuring things.
+Should the Chernozhukov stuff appear alongside all the other heterogeneous treatment effects material?
+Also, this paragraph used to \emph{precede} our introduction of the potential outcomes.
+Now that it follows it, it seems like a bit much.}
+
+%If the effect of structure were homogeneous, this would be enough to conclude that the 89\% who did not choose it would have been financially better-off if they had.
+%In a world of heterogeneous treatment effects, however, low demand for commitment could still be consistent with borrowers adhering to a standard model of rational choice. 
+%The borrowers who did not choose structure could simply be those who don't need it. 
+%Indeed, we find strong evidence that the effect of mandatory structure varies substantially across individuals in our experiment: we test and reject
 %Appendix \ref{append:chernozhukov} tests and rejects 
-the null hypothesis of homogeneous treatment effects using the methodology of \cite{chernozhukov2018generic} (details available upon request).
-So the question remains: can we explain the 89\% of borrowers not choosing commitment as being those that don't benefit financially from it?  
-In this section, importantly, we show that commitment would lower average financial costs even for the subset of borrowers who choose \emph{not} to commit voluntarily.
-To simplify the exposition in this and all sections that follow, we re-define all outcome variables so that \emph{beneficial} treatment effects are \emph{positive}.
-Using this convention, a positive treatment effect of commitment on financial cost, for example, reflects the average cost \emph{savings} caused by commitment.
+%the null hypothesis of homogeneous treatment effects using the methodology of \cite{chernozhukov2018generic} (details available upon request).
+%So the question remains: can we explain the 89\% of borrowers not choosing commitment as being those that don't benefit financially from it?  
+%In this section, importantly, we show that structure would lower average financial costs even for the subset of borrowers who choose \emph{not} to commit voluntarily.
+
+%\todo[inline]{We need a transition here}
+
+\subsection{Estimating Treatment Effects by Compliance}
+
+The results from above show that commitment \emph{works}: clients who were assigned to the mandatory structure arm experienced substantially lower financial costs on average.
+In spite of this, given the opportunity, only 11\% of borrowers chose this structure freely.
+The central question driving the relative benefits of mandatory versus voluntary compliance concerns the relationship between treatment effects and the choice to adopt the structured payments, or selection on gains.
+We now proceed to exploit the exclusion restrictions presented above to separately estimate treatment effects for the choosers and non-choosers of the structured payment contract.
+Table \ref{tot_tut} calculates the causal quantities described above---TOT, TUT, ASG, ASB, and ASL---for our experimental data, along with robust standard errors for each.\footnote{To simplify the exposition in this and all sections that follow, we re-define all outcome variables so that \emph{beneficial} treatment effects are \emph{positive}.
+Using this convention, a positive treatment effect of structure on financial cost, for example, reflects the average cost \emph{savings} caused by structure.}
+For purposes of comparison, the table also presents the ATE results from Section \ref{Experiment} above (row 1),\footnote{Coefficients are not exactly the same since Table 4 includes branch and day-of-week FE.} along with the corresponding average potential outcomes $\mathbbm{E}[Y_0]$ and $\mathbbm{E}[Y_1]$ (rows 4--5).
+The columns of the table correspond to different outcome variables defined above.
+We are now in a position to report one of the important results in the paper.
+For all four outcome definitions, the TUT effect is positive, statistically and economically significant, and comparable in magnitude to the ATE.
+In other words: the structured payments contract is on average \emph{beneficial} to the people who \emph{would not choose it}, and these benefits are large.
+That is, mandating structured payment contracts would decrease the financial cost.
+Borrowers are leaving money in the table by not choosing it.
+
+Some comments are in order.
+First, this result holds on average.
+Some non-choosers could lose from a mandate.
+Section \ref{sec:RF} assesses personalized targeting strategies.
+Second, financial cost is not welfare, and further work with more comprehensive measures (stress, consumption, performance in other loans) needs to be done.
+We provide proof of concept that at least financial cost may not be minimized by free choice and provide a method to rigorously compare take-up mandates against consumer choice.
+Third, given that providing such contracts may not be in the lender's interest, borrowers may not even be presented with this choice.
+
+Table \ref{tot_tut} also estimates the TOT effect.
+Due to the low take-up rate in the choice arm, TOT effects are imprecisely estimated.
+Only one of them, \%(1-Default) from column (3), is statistically significant.
+This carries over into our estimates of the average selection on gains.
+Our point estimates are \emph{negative} for all but the (1 - Default) outcome, but none is statistically distinguishable from zero.
+%Although we cannot quite reject the null hypothesis that the TUT and TOT effects are equal--our power is limited because of the low take-up rate of commitment in the choice arm--the pattern of coefficients is consistent with some degree of selection-on-gains.
+%Commitment is more beneficial to people who are willing to choose it than it is to people who are not.
+For the (1 - Default) outcome, we have sufficient precision to conclude that the average selection bias (ASB) is large and negative.
+This means that borrowers who choose structure would have faced a higher probability of default under the status quo contract than borrowers who do not choose structure.%\footnote{We may not want to read too much into TOT vs TUT comparisons as they are imprecise.
+But taken at face value, the result that TOT$>$TUT for default, while the opposite is true for financial cost, suggests that, while voluntary commitment has a slightly stronger effect on allowing borrowers to avoid default, forcing \textit{reduces} payments in a strong enough manner as to overcome the default-benefits of choice.}
+
+Overall, Table \ref{tot_tut} suggests that structure works but that \emph{not enough} people choose it: the structured contract saves money on average even to those who would \emph{not} choose it voluntarily.
+We believe this result is new in the household finance literature.
+It also illustrates how the ``Mandates vs.\ Choice'' design can be used more generally to understand the relationship between choice and treatment effect heterogeneity, in particular the causal effect among non-choosers.\footnote{For instance, in the debate on financial commitment take-up, some papers argue that this effect is low (\cite{Ashraf}, \cite{Gine}, \cite{Ted}, \cite{Royer} while others argue it is high (\cite{Kremer}, \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}, \cite{Pascaline}), but none estimates the benefits for non-takers.
+In a different domain, doctors claim that medical treatment abandonment is too high in a broad range of diseases \citep{non_adherence}, without knowing the treatment benefits for those that abandon.}
+
+\begin{table}[H]
+\caption{Five Treatment Effects Estimates: TOT, TUT, ASG, ASB, ASL}
+\label{tot_tut}
+\begin{center}
+\footnotesize{\input{./Tables/tot_tut.tex}}
+\end{center}
+\scriptsize{This table presents results computed using the derivations from Section \ref{sec:randchoice}.
+The APR and financial cost outcomes have been multiplied by $-1$ so that a positive causal effect \emph{benefits} the borrower in each of the four columns.
+The bottom panel presents p-values for a number of null hypothesis tests of treatment effect heterogeneity.
+}
+%\textit{Do file: } \texttt{tot\_tut.do}
+\end{table}
+
+%Below we explore possible explanations for this result.
+%and the ``right people'' choose to commit: those who are most likely to benefit from it and those whose outcomes are most adverse under the status quo.
+
+%Given that the ITT results for the Choice arm imply an insignificant worsening of outcomes relative to the control, our estimates of the Treatment on the Treated in the first row of the bottom panel show negative results that are larger in absolute magnitude (multiplied by ~9, the inverse of the compliance rate) and similarly insignificant.
+The Treatment on the Untreated (TuT), conversely, is strongly positive across the board, and indicates a significant improvement for all outcomes (here ITTs are effectively multiplied by 1.12, the inverse of the non-compliance rate).
+Most novel is the ability to form a test of the difference between the ToT and the TuT, which is conducted in the bottom rows of the table.
+We provide four different ways of estimating p-values for this comparison; the standard clustered estimates motivated by the experimental design, normal and percentile bootstraps, and randomization inference.
+The differences between treatment effects for compliers and non-compliers are of borderline significance in some of the unadjusted specifications, but are not significant once adjusted.\footnote{It is worth noting that the statistical power of these estimands is driven by the compliance rate; given our low overall compliance we are better powered to measure the TuT than the ToT, and the power for the difference between the two would be highest with a compliance rate of 50\%.}   Because of the large standard errors on the ToT coming from the low compliance rate in the Choice arm we are unable to state with statistical confidence that the TuT is higher than the ToT, but the TuT is strongly positive while the ToT is weakly negative, and so in both relative and absolute terms the choices being made are `wrong' relative to the potential outcomes.
+
+%\todo[inline]{Possibly add some discussion here of Craig's idea: using the controlled choice design to study ``targeting''}
+
+%A unique feature of our design is the randomized assignment to treatment (forced commitment), control (forced no-commitment), and choice of treatment.
+
+%This structure allows us to observe the average value of both the treated and untreated potential outcomes, as well as the selection into treatment that would occur under choice.
+A starting point for how to exploit this structure is to apply the logic usually used to estimate the Treatment on the Treated (ToT) to also recover the Treatment on the Untreated (TUT).
+This approach assumes nothing about the decision to choose (other than random sampling generating counterfactual compliance rates that would have been the same in every arm), but imposes three exclusion restriction-style assumptions typical of Local Average Treatment Effect (LATE) analysis.
+Namely, a) the typical assumption that an individual not choosing the treatment has the same potential outcome as one not offered it, then b) the mirror image assumption for the Forcing arm that an individual forced to take Commitment has the same potential outcome as an individual freely choosing it, and c) no spillovers from chooser to non-choosers in the choice arm.\footnote{\hl{For robustness we also try a Manski-type monotone IV approach with similar results.}}
+
+%More formally, let $Z_i$ be the observed, randomly assigned experimental allocation, where $Z_i=0$ denotes the control arm, $Z_i=1$ denotes the Forced arm, and $Z_i=2$ is the Choice arm.
+Let $C_i$ be the choice type; $C_i=0$ when individual $i$ does not choose commitment and $C_i=1$ when chooses commitment, observed in the Choice arm and latent in the other two arms.
+A fraction $p$ of individuals chooses the treatment in the Choice arm.
+Finally, $D_i = Z_i\times \mathds{1}(Z_i\neq 2) + C_i\times \mathds{1}(Z_i=2)$ is the observed treatment indicator, and $Y(d,z)$ is the potential outcome function for $d=0,1$, and $z=0,1,2$.
+
+%To test the difference between gains for choosers versus gains from non-choosers we need to identify $\mathbb{E}[Y_1-Y_0\;|\;C=1]$ (the Treatment on the Treated), and $\mathbb{E}[Y_1-Y_0\;|\;C=0]$ (the Treatment on the Untreated).
+The observed outcome in the Choice arm is the weighted average of the treated and untreated outcomes; $p \times\mathbb{E}[Y_1\;|\;C=1] + (1-p)\times\mathbb{E}[Y_0\;|\;C=0]$.
+Given assumptions a) and c) above we can recover the ToT from the difference between the Choice and Control arms as is standard, and then symmetrically we can invoke b) and c) to recover the TUT from the difference between the Forced and Choice arms as follows:
+
+%\begin{align*}
+%ToT \equiv \mathbb{E}[Y_1 - Y_0 \;\mid\; C=1]  &=   \frac{\mathbb{E}[Y \;\mid\; Z=2] - \mathbb{E}[Y \;\mid\; Z=0]}{p} \\
+%TuT \equiv \mathbb{E}[Y_1 - Y_0 \;\mid \;C=0]  &=  \frac{\mathbb{E}[Y \;\mid\; Z=1] - \mathbb{E}[Y \;\mid\; Z=2]}{(1-p)} 
+%\end{align*}
+
+%This estimate of the ToT is the standard one that would result from instrumenting for compliance with the offering of treatment as in \cite{angrist1996identification}.
+The TuT is the analogous estimator, which could be recovered in a regression pooling the forced and choice arms and instrumenting for \textit{not} complying with being assigned to the choice arm (for a more formal development, see the appendix).
+The advantage of representing the estimands via division of the relevant ITT by the compliance (non-compliance) rate is that it allows us to estimate all the necessary terms from the single pooled regression Equation \ref{basic_reg}, from which the significance levels for the ToT, the TuT, and the difference between them can all be estimated as single-equation F-tests:
+
+%\[ToT = \frac{\beta^C}{p}; \qquad\quad TuT = \frac{(\beta^F - \beta^C)}{(1-p)}; \qquad\quad (ToT-TuT) = \frac{\beta^C}{p}- \frac{(\beta^F - \beta^C)}{(1-p)}. \]
+
+%\hfill \newline
+%\noindent \textbf{TOT and TUT results.}
+
+%\section*{The Case for Mandating Structure} 
+%\label{Paternalism}
+%\todo[inline]{This section has been replaced, but we'll need to go through and remove / update the cross-references to it.}
+
+\section{Behavioral Drivers}
+\todo[inline]{This is a working title; we may well want to change it}
+\label{why_paternalism}
+
+A behavioral literature has highlighted voluntary commitment as an attractive way of allowing the ``right'' people to self-select.
+% A discussion of compulsory commitment is necessarily paternalistic, and by its nature focuses on impacts among those who would not have selected commitment voluntarily.
+%Viewed through the lens of rational choice theory, it is unsurprising that we estimate $\text{TOT}>\text{TUT}$. 
+The argument for compulsory treatment, centers on the surprising result that $\text{TUT}>0$.
+We now investigate four potential explanations for the positive $\text{TUT}$: the need to learn, time discounting, present bias, and overconfidence.
+
+%\hfill \newline
+%\noindent \textbf{Learning.}
+
+Our experiment introduced a new contract into an environment that had not previously featured structured repayment; perhaps clients required experience to understand its benefits.
+Are clients who experienced the commitment contract more likely to choose structure subsequently than those assigned to the status-quo contract?
+%We have already shown above that those who experienced the Forcing contract were more likely to borrow again.
+We now ask whether the subset who were assigned to the Choice arm when they returned were more likely to choose commitment.
+Appendix Table \ref{learning_table} compares borrower assigned to the mandatory versus status quo arms on an initial pawn who then return to take a subsequent loan at a branch offering choice.
+%\footnote{Table \ref{learning_table} presents information about participants' \emph{immediate subsequent} pawning behavior.
+For borrowers who returned to pawn again more than once, this analysis considers only their first repeat pawn.}
+This analysis shows \textit{no difference} in choosing structure for the 22\% of borrowers in these two initial arms who returned to pawn again and were offered choice.
+%The implication is that while those who have experienced commitment feel more positively towards the pawn contract, the experience does not lead them to conclude that they need commitment on the subsequent loan.
+While these exercises cannot completely exclude the possibility that learning would play a role with more exposure, they provide no indication that the lack of voluntary compliance is simply a matter of inexperience with structure in the short run.
+Note also that there will be no learning if lenders don't provide a structured payment contract in the first place.
+
+%Column (1) considers the 228 clients who returned only a second time to pawn again at a day/branch that was randomly assigned to the choice arm.
+Each of the two rows in this column presents a difference of mean commitment take-up rates, and associated standard error.
+The first row compares those who were \emph{initially} assigned to forced commitment against those where were assigned to control; the second row compares those who were initially assigned to the choice commitment arm to those who were assigned to the other two arms.
+In each case, there is no statistically discernible difference in the rates of commitment take-up.
+Granted, this is a selected sample because the decision to pawn again is potentially endogenous to the initial treatment allocation.
+For this reason, Column (2) considers the full sample of 4441 borrowers by re-defining the outcome variable to be an indicator for returning to pawn again at a branch/day when commitment was offered \emph{and} choosing commitment.
+This composite outcome variable is not subject to the sample selection problem (although it is directly driven by the decision to repeat borrow).
+The comparison in the two rows remains the same: forced commitment versus control in row one and choice commitment versus forced arms in row two.
+Again, there is no statistically discernible difference in commitment take-up rates in either row.
+While these exercises cannot completely exclude the possibility that learning plays a role, they provide no indication that the lack of voluntary compliance is simply a matter of inexperience with commitment.
+
+%\hfill \newline
+%\noindent \textbf{Time discounting.}
+
+Can high borrower time discount rates explain low demand for structured payments?
+%Highly impatient individuals might rationally choose the \emph{status quo} contract, despite the benefits that commitment yields returns,
+After all, monthly payments are front-loaded while pawn recovery is back-loaded, even if by only a few weeks.  
+%those returns are realized at contract ending hile the cost of monthly payments are incurred  Our estimated decrease in the financial cost of credit from above ignores discounting, but commitment involves incurring up-front costs (early payment) in return for delayed benefits (a higher probability of recovering one's pawn).
+Figure \ref{fc_discount_rates} calculates TUT effects for different borrower discount rates given the actual timing of repayment and pawn recovery.
+The solid line gives the TUT effect adjusted for a specified annual discount rate, while the shaded regions give the associated 95\% \& 90\% confidence interval.
+We see that non-choosers continue to experience significant decreases in the net present value of financial costs up to annual discount rates of 1,000\%, an extremely high level of impatience.\footnote{In a similar exercise for subprime borrowers in the US, \cite{Levin} argue that even discount rates smaller than these would be too large to be reasonable and can be safely discarded as explanations.} As such, discounting is unlikely to explain why those who benefit, on average, from structure fail to choose it.
+% when offered.
+
+%\hfill \newline
+%\noindent \textbf{Present bias.} 
+If the benefits of structure among non-choosers cannot be explained by standard models of rational choice, the canonical behavioral story would center on time inconsistency.
+While commitment is useful to anyone with hyperbolic time preferences, only those who are sophisticated---i.e.\ aware that they are hyperbolic discounters---will demand it.
+A large share of ``na\"ive'' hyperbolics in the population--borrowers who are unaware that they are hyperbolic discounters--could therefore drive a large and positive $\text{TUT}$.
+Our baseline survey included standard questions about discount rates between tomorrow and a month in the future versus discount rates between three and four months in the future.
+This allows us to classify borrowers who display more impatience over immediate delays as present biased.
+This measure of financial hyperbolicity is widely used in survey research, although it is not without problems.\footnote{\textcolor{red}{We also asked a simple self-reported question about temptation, and obtain similar answers with this alternate measure.} Recent empirical work has shown the superiority of more elaborate measures such as ``convex time budgets'' \citep{andreoni2015measuring} while questioning the interpretation of measures of hyperbolicity that are not based on consumption \citep{andreoni2012estimating, cohen2020measuring}, suggesting that real effort tasks provide a better measure \citep{augenblick2015working}.
+Given that we had only a few minutes to interview real pawnshop clients prior to a commercial transaction, our simple measure was a necessary compromise.}
+
+If we could perfectly measure present bias and sophistication, we could divide the sample into three groups: sophisticated hyperbolics (who chose structure), time-consistent non-choosers (for whom structure will not be effective), and na\"{i}ve hyperbolic non-choosers (who will benefit from structure even if not chosen by them).
+%If present bias fully explains the low take-up rate of voluntary commitment, we should find that the TUT for present-biased borrowers  is positive while the TUT for all other borrowers is not.
+If present bias explains the low take-up rate of voluntary commitment, we should find that the TUT for present-biased borrowers is larger than for other borrowers.
+This is because among the group of non-takers, a comparison of present-biased borrowers against everyone else is a comparison of na\"{i}ve hyperbolics against time-consistent non-choosers.
+The left panel of Figure \ref{tut_beh_partition} in the Appendix carries out a feasible version of this exercise using our survey measure of present bias.
+%The overall TUT estimate along with a 95\% confidence interval is given in blue.\footnote{For all borrowers who answered our present-bias survey questions.}
+%The corresponding TUT estimate and confidence interval for present-biased borrowers identified with the survey question is given in green; results for all other borrowers are shown in red.
+%The overall TUT is a weighted average of the impact in these two sub-groups.
+The TUT among the present biased is insignificant and less than half the size of the strongly significant TUT among those who are \textit{not} present biased.
+Therefore, taking our survey measure of hyperbolicity at face value.
+We find no indication that present-bias explains our positive estimated TUT.\footnote{Similarly, we find that experience pawning does not predict TUT.}
+
+%\hfill \newline
+%\noindent \textbf{Sure confidence.}
+
+Finally, motivated by the high subjective probabilities of recovery we found in the baseline survey, and by the fact that a large fraction of borrowers pay towards recovery and then lose the pawn and these payments, we explore overconfidence in recovery as a potential explanation of low demand for structured payments.
+After all, recall that while 72\% of survey respondents believe they have a 100\% chance of recovering their pawn, in reality only 43\% will go on to do so.
+Borrowers who are certain to recover their pawn perceive no benefit of committing to repay under the threat of fees and, therefore, no benefit of choosing the structured payment contract.
+%if individuals who \emph{believe} that they are certain to repay, choose (rationally given their incorrect beliefs) to forgo the costs associated with commitment that are designed to induce repayment.
+To explore this, as in the preceding paragraph, we compare the overall TUT estimate to estimates computed for two sub-groups, defined by a binary variable that we call ``sure-confidence''.
+This measure equals one for any individual who says at the time of borrowing that they have a 100\% probability of recovering their pawn, and zero otherwise.
+%The right panel of Figure \ref{tut_beh_partition} presents the results for this exercise.
+%The overall TUT estimate for all borrowers who answered our sure-confidence survey questions is given in blue, along with a 95\% confidence interval.
+%The corresponding TUT estimate and confidence interval for sure-confident borrowers is given in green; results for all other borrowers are shown in red.
+In contrast to our results for present bias, we find that sure-confidence \textit{is} a strong predictor of TUT.
+Figure \ref{tut_beh_partition} shows that the TUT is almost entirely confined to the sure confident individuals, while those that say they have some chance of defaulting have TUT close to zero.
+It seems that the effectiveness of paternalism in our experiment may be driven by \emph{overconfident} borrowers who, heedless of the risk of default, fail to choose structure despite benefiting substantially when it is mandated.\footnote{In Figure \ref{determinants_sure} we plot the coefficient estimates from a regression that predicts sure confidence with a battery of individual-level characteristics.
+Older males are more likely to be sure-confident, as are those with more education.
+Taken at face value, the sure-confident also report less financial stress, less trouble paying bills, and to be more frequently relied upon financially by family members.
+Viewed through a behavioral lens, however, it is also possible that the type of person who is over-confident in their ability to repay a loan also exaggerate their degree of economic security in their response to survey questions.
+In any case, it appears that sure confidence may be difficult to predict with easily-observed and objective demographic criteria, a point to which we return below.}
+
+\section{Understanding Treatment Effect Heterogeneity} \label{sec:RF}
+\todo[inline]{This is a working title; we may want to change it}
 
@@
 \label{sec:bounds}
-
-Calculating the number of individuals who benefit from universal forced commitment requires the distribution of individual treatment effects.
+\todo[inline]{Now that this section appears after we defined all of the potential outcomes, we don't need to define them: we just need to reference the section where they were defined.}
+
+Calculating the number of individuals who benefit from mandatory structure requires the distribution of individual treatment effects.
 While this distribution cannot be point identified, it can be bounded.
-Let $(Y_{i0}, Y_{i1})$ be $i$'s potential outcomes under the control and forced commitment conditions and define $\Delta_i \equiv Y_{i0} - Y_{i1}$.
+Let $(Y_{i0}, Y_{i1})$ be $i$'s potential outcomes under the control and mandatory structure conditions and define $\Delta_i \equiv Y_{i0} - Y_{i1}$.
 Let $(F_0, F_1, F_\Delta)$ be the marginal distributions of $(Y_{i0}, Y_{i1}, \Delta)$ and define 
@@
 Figure \ref{fan_park_bounds} plots these bounds for the APR outcome in our experiment.  
-To bound the share of borrowers who benefit from forced commitment, we merely substitute $\delta=0$ into the preceding, since $\mathbb{P}(\Delta_i > 0) = 1 - F_\Delta(0)$.
+To bound the share of borrowers who benefit from mandatory structure, we merely substitute $\delta=0$ into the preceding, since $\mathbb{P}(\Delta_i > 0) = 1 - F_\Delta(0)$.
 Our point estimates of $\underline{F}(0)$ and $\overline{F}(0)$ are 0.03 and 0.77 respectively, with 95\% confidence intervals of [0.025, 0.050] and [0.75, 0.80].
-Since we are interested in $\mathbbm{P}(\Delta_i >0) = 1 - F_\Delta(0)$, it follows that \textit{at least 23\%}, and at most 97\%, of individuals borrowers benefit from forced commitment.%\footnote{Confidence intervals are constructed using the asymptotic distribution of $(\underline{F}, \overline{F})$.
+Since we are interested in $\mathbbm{P}(\Delta_i >0) = 1 - F_\Delta(0)$, it follows that \textit{at least 23\%}, and at most 97\%, of individuals borrowers benefit from mandatory structure.\footnote{Confidence intervals are constructed using the asymptotic distribution of $(\underline{F}, \overline{F})$.
 See \cite{fan2010sharp}.}
-That is, under general conditions, these bounds already provide evidence for depressed demand, in the sense that at least 12\% (=23\% benefit -11\% demand) of borrowers would incur a lower financial cost with structured payment and yet did not chose it.
-The bounds are wide however.
+\todo[inline]{Need to add explanation of how we incorporated covariates in carrying out this exercise: see editor's comment.}
+That is, even under the most conservative possible assumptions, we find evidence of depressed demand: more than 23\% would benefit from structured repayment but only 11\% demand it. 
+These bounds are wide because they concern the distribution of \emph{individual treatment effects} and make no assumptions beyond our experimental randomization. 
 By adding assumptions it is possible to say more. 
-We turn to this next.
-%For example, under rank invariance\footnote{i.e.\ if $i$'s rank in the distribution of $Y_0$ equals her rank in the distribution of $Y_1$} the distribution of treatment effects is point identified and given by $F_\Delta(\delta) = \int_0^1 \mathbbm{1}\{ F_1^{-1}(u) - F_0^{-1}(u)\leq \delta\}\,\mathrm{d}u$, where $F_1^{-1}$ and $F_0^{-1}$ are the quantile functions of $Y_1$ and $Y_0$.\footnote{Figure \ref{te_rankinvariance} in Appendix \ref{bounds_FOSD} plots our estimates of $F_\Delta$ under rank invariance.} Because in our data, $Y_1$ first-order stochastically dominates $Y_0$ for financial benefit ($F^{-1}_1(u) - F^{-1}_0(u) >0$), we conclude that all borrowers would benefit ($\Delta_i > 0$).
+For example, under rank invariance\footnote{i.e.\ if $i$'s rank in the distribution of $Y_0$ equals her rank in the distribution of $Y_1$} the distribution of treatment effects is point identified and given by $F_\Delta(\delta) = \int_0^1 \mathbbm{1}\{ F_1^{-1}(u) - F_0^{-1}(u)\leq \delta\}\,\mathrm{d}u$, where $F_1^{-1}$ and $F_0^{-1}$ are the quantile functions of $Y_1$ and $Y_0$.\footnote{Figure \ref{te_rankinvariance} in Appendix \ref{bounds_FOSD} plots our estimates of $F_\Delta$ under rank invariance.} Because in our data, $Y_1$ first-order stochastically dominates $Y_0$ for financial benefit ($F^{-1}_1(u) - F^{-1}_0(u) >0$), we conclude that all borrowers would benefit ($\Delta_i > 0$).
 
@@
 
-\subsection{Potential Outcomes and Exclusion}
-\label{sec:potentialOutcomes}
-
-%The assumption-free \cite{fan2010sharp} bounds from the preceding section show that more than 23\% of borrowers would benefit from a policy of forced commitment.
-This suggests that some of the 89\% of borrowers in the choice arm who did \emph{not} choose commitment would have faced lower borrowing costs if they had.Making this intuition precise, however, requires a careful consideration of the relationship between choice and heterogeneous treatment effects.
-This section shows under an additional mild exclusion restriction assumption, our 3-arm RCT design point-identifies a range of treatment effects of interest, and in particular, the treatment on the untreated, necessary to study the benefits mandating a contractual feature.
-To this end, we now provide a full definition of the potential outcomes in our empirical setting.
-Let $Z_i \in \{0, 1, 2\}$ denote the treatment arm to which to participant $i$ was assigned: $Z_i = 0$ denotes the forced no-commitment arm, $Z_i = 1$ denotes the forced commitment arm, and $Z_i = 2$ denotes the choice arm.
-Now let $D_i$ be the treatment that participant $i$ actually \emph{received}, where $D_i = 0$ denotes no-commitment and $D_i = 1$ denotes commitment. 
-We assume perfect compliance in the $Z_i = 0$ and $Z_i = 1$ arms. %\footnote{For more discussion on this point, see Section \ref{sec:integrity} above.}
-It is only in the $Z_i = 2$ arm that participants are free to choose between alternative contracts. 
-Let $C_i \in \{0, 1 \}$ denote a participant's ``choice type.'' If $C_i = 1$ then participant $i$ \emph{would choose commitment}, given the option; if $C_i = 0$ she would not. 
-As shorthand, we call borrowers with $C_i = 1$ ``choosers'' and those with $C_i = 0$ ``non-choosers.''
-Whereas a participant's choice type $C_i$ is only observed if she is allocated to the choice arm ($Z_i = 2$), her treatment $D_i$ and experimental arm $Z_i$ are always observed. 
-Given the design of our experiment, these quantities are related by
-\begin{equation}
-D_i = \mathbbm{1}(Z_i \neq 2) Z_i + \mathbbm{1}(Z_i = 2) C_i.
-\label{eq:potentialTreatments}
-\end{equation}
-
-We maintain the stable unit treatment value assumption (SUTVA) throughout. 
-This means that borrower $i$'s outcomes depend only on her \emph{own} values of $Z_i$ and $D_i$, not those of any other person in the experiment. 
-Under this assumption, a fully general model for the potential outcomes in our experiment would take the form $Y_i(d, z)$ for $d\in \{0,1\}$ and $z \in \{0, 1, 2\}$, allowing participant $i$'s potential outcome to depend \emph{both} on the treatment she actually receives, $D_i$, and the experimental arm to which she is assigned, $Z_i$.
-This model is too general, however, to point identify meaningful causal effects. 
-For this reason, we consider two mild exclusion restrictions.
-
-To state these restrictions we first define some additional notation.
-Because our experimental design implies that any borrower with with $Z_i = 0$ has $D_i = 0$, we abbreviate the potential outcome $Y_i(d=0,z=0)$ as $Y_{i0}$. 
-Similarly, since any borrower with $Z_i = 1$ has $D_i = 1$, we abbreviate $Y_i(d=1,z=1)$ as $Y_{i1}$. 
-%This is in keeping with our notation from section \ref{sec:bounds} above.
-Using this notation, our first exclusion restriction, which we call the ``No-choosing warm-glow'' (NCW) assumption is given by
-\begin{equation}
-Y_i(d=0,z=2) = Y_i(d=0,z=0) \equiv Y_{i0}.
-\label{eq:exclusion0}
-\end{equation}
-Equation \ref{eq:exclusion0} only restricts the potential outcomes of non-choosers,  individuals with $C_i = 0$, because they are the only borrowers for whom $D_i = 0$ when $Z_i = 2$.
-In words, this condition assumes that every non-chooser experiences the same potential outcome regardless of whether she is assigned to the choice arm or the control arm.
-Similarly, we assume a second NCW exclusion restriction is given by
-\begin{equation}
-Y_i(d=1,z=2) = Y_i(d=1,z=1)\equiv Y_{i1}.
-\label{eq:exclusion1}
-\end{equation}
-Equation \ref{eq:exclusion1} only restricts the potential outcomes of choosers, individuals with $C_i =1$, because they are the only borrowers for whom $D_i = 1$ when $Z_i = 2$.
-In words, this condition assumes that every chooser experiences the same potential outcome regardless of whether she is assigned to the treatment arm or the choice arm.
-
-Mathematically \eqref{eq:exclusion0} and \eqref{eq:exclusion1} have the same structure as the standard LATE exclusion restriction that $Y_i(d,z)$ depends only on $d$, not on $z$. 
-Substantively, however, they are slightly different, given that there is no explicit reference to the ``chosen'' versus ``forced'' treatment distinction in the usual LATE setup.
-In essence, \eqref{eq:exclusion0} and \eqref{eq:exclusion1} assume that being assigned a particular treatment has the same result as choosing it for yourself, provided that you are assigned the same treatment that you \emph{would have chosen}.
-If the mere fact of having been given a choice has a direct effect on outcomes, one or both of our exclusion restrictions will be violated.
-One can imagine situations in which this might be the case.
-For example, even someone who would have voluntarily chosen to undergo drug rehabilitation, given the choice, might respond differently when coerced.
-In our empirical setting, however, both \eqref{eq:exclusion0} and \eqref{eq:exclusion1} are plausible.\footnote{Closely related assumptions are common, if often tacit.
-\cite{chamberlain2011bayesian} explicitly assumes that choosing and being assigned a treatment have the same effect.
-A significant literature using compulsory schooling laws to estimate the returns to education tacitly assumes that schooling \emph{in general} has the same returns, regardless of whether it is mandated or chosen freely.
-Similarly, fertilizer yields are tacitly assumed to generate the same returns regardless of whether the fertilizer was chosen by farmers or provided by the government, as long as it is the same fertilizer.}
-Moreover, each has testable implications that we fail to reject: see \autoref{sec:testing_exclusion}. 
-Under \eqref{eq:exclusion0} and \eqref{eq:exclusion1}, the observed outcome $Y_i$ is related to $(Y_{i0}, Y_{i1})$ by 
-\begin{equation}
-    Y_i = \mathbbm{1}(Z_i =0) Y_{i0} + \mathbbm{1}(Z_i = 1)  Y_{i1}  + \mathbbm{1}(Z_i = 2) \left[(1 - C_i) Y_{i0} + C_i Y_{i1} \right].
-\label{eq:potentialOutcomes}
-\end{equation}
-Equation \ref{eq:potentialOutcomes} is the key to understanding the results that follows. 
-Random assignment of $Z_i=0$ and $Z_i = 1$ identifies the marginal distributions of $Y_{i0}$ and $Y_{i1}$ for the population as a whole. 
-Random assignment of $Z_i=2$ likewise point identifies the share of choosers ($C_i = 1$), the distribution of $Y_{i1}$ for choosers, and the distribution of $Y_{i0}$ for non-choosers ($C_i = 0$).
-Because $Z_i$ is assigned independently of pre-treatment covariates $X_i$, we also identify the \emph{conditional} distributions of $Y_{i0}$ and $Y_{i1}$ given $X_i$. 
-%These distributions are the ingredients that we use below to explore the importance of paternalism.
-
-%The fact that the Forced Commitment contract lowers financial costs for almost all clients, together with the fact that only 11\% choose it must mean that many consumers are choosing contracts with higher financial costs for themselves.
-We now use several different techniques to shed further light on the idea that the `wrong' people are choosing commitment.
-
-%Our core impacts show that forced commitment is uniquely effective, a result that can only arise if those who would not have freely chosen commitment benefit from it.
-We now delve more deeply into this result.
-
-%\subsection{Treatment Effect Heterogeneity}
-
-%Defenders of choice make another subtler point: that even if take up of the commitment-fee contract is low, the sole fact of \textit{having} choice could potentially change behavior or welfare (\cite{Dalboetal:2010}, \cite{Sjostrometal:2018}, \cite{Tlaxcala}).
-
-%In spite of broadly distributed benefits of the Forced Commitment commitment contract we documented above, 90\% of clients chose \textit{not} to have it, preferring the status-quo contract.
-As explained above we are fairly confident this was not because a lack of understanding of the contracts.
-
-%\vspace{.1in}
-%\noindent What can explain this low demand?
-In the spirit of \cite{Blumenstock} we try to differentiate between explanations.
-One explanation could be risk.
-Even if the fee forcing contract generates cost savings on average, clients with risk averse preferences may not demand it if they perceive higher risk from it.
-Alternatively, even risk-neutral agents may not demand it if the cost of lost flexibility is high or if they have high temporal discount rates and prefer to pay later.
-%If clients, for instance, face large and frequent income shocks which make it hard to repay monthly.\footnote{We don't observe income shocks in our data, making is hard to quantify how important they are.
-91\% of those in the Forced Commitment arm incurred a fee, which suggests that shocks are not uncommon.}
-%Although the evidence that follows undermines several explanations, the tests we can conduct given the data are not sharp enough to leave a single explanation standing.
-Section \ref{model} lays our a simple theory (namely present bias with partial naivete) which fits all the 6 main findings of the paper.
-Given its parsimony and explanatory power, we submit that it is the most suitable explanation for our results.
-
-%Following two  paragraphs moved from old 'behavioral' choice section towards end of paper
-%\hfill \newline
-%\subsection{The effect of choice on pawn recovery and financial cost} \label{effect_choice}
-
-%Figure \ref{main_te} represents the  effect sizes (in standard deviations) of the two main study arms for three outcomes:  default, the financial cost of the loan, and the effective interest rate paid to acquire the borrowed capital.
-The Forced arm is significant for all three outcomes, with very substantial treatment effects in magnitudes for default and APR, and the commitment arm is never significant.\footnote{The slight increase in APR for the Choice arm seen in this picture arises from the fact that the APR calculation has the arm-specific loan size in the denominator, and the loans in the Choice arm turn out to be slightly smaller (although statistically equal) on average than the Control.}    In other words, voluntary commitment is ineffective but the use of forced commitment saves the average borrower an amount of money almost twice the APR of a normal US credit card loan.
-
-%Although we have shown that Forced Commitment reduces financial cost and increases pawn recovery, this does not imply that welfare increases.
-Clients could have disutility from the stress of having monthly installments for instance.
-%We don't need to make the strong claim of welfare for the purposes of this paper. The financing cost results are striking enough. But we
-
-%The panel labeled Forced Commitment in Figure \ref{reincidence} presents results of estimating equation (\ref{basic_reg}) with the dependent variable being a dummy for the client being a repeat customer.
-We define a client as a repeat customer if, after experiencing at least 75 days of the respective treatment arm, she came back and pawned a \textit{different} piece.\footnote{Results are robust to using number of days experiencing the contract larger than 75.
-We know it is a different piece from it having a different weight/value.}  The leftmost coefficient shows that the causal effect of the Forced Commitment contract on repeat pawning is an increase of 5 percentage points in the probability of being a repeat customer, this is twice the repeat purchasing happening in the status quo group.
-This effect is not explained by clients recovering their first pawn with higher probability in the Forced Commitment contract and re-pawning this same one since we make sure it is another piece; besides only 16\% recover their piece in the fist 75 days in the fee forcing contract.
-Experience with the frequent payment contract seems to be necessary as there is no effect of the monthly payment contract on repeat pawning in the first 30 or 60 days of the contract (see Figure \ref{reincidence_before} in the Appendix).
-
-%\hl{The second coefficient from the left focuses on the subsample who are predicted would have a treatment effect on financial cost savings above the median} treatment effect in their first pawn.\footnote{Since this is predicted using \cite{atheygrf} based on pre-determined covariates for treatment and control clients it is valid to split the sample this way.} It shows that for these clients the likelihood of coming back is twice as large.
-That is, those that benefit more from the Forced Commitment contract are more likely to repeat compare to their control group.
-The remaining coefficients of the ``Forced Commitment'' panel condition on endogenous outcomes and should be interpreted with care.
-The \hl{third} coefficient from the left restricts the sample to those that had not recovered their pawn in the first 75 days in both groups and finds similar results.
-The \hl{fourth} coefficient conditions on clients who recovered their pawn of the experiment, again on in both arms.
-Results from these two endogenous samples are similar to those for the whole sample.
-
-%The fourth coefficient \footnote{The second and third estimate must be interpreted with care as we are conditioning on a variable that may be affected by treatment.
-We view these 2 coefficients as suggestive correlations only.
-The fourth coefficient does not have that problem as it conditions on clients that by their pre-determined covariates are predicted to have above the median treatment effects (in both arms).}
-
-%The coefficient on repeat pawning is just as big when we focus only 2nd pawns happening after the first was recovered (third coefficient ``fnr'').
-This is consistent with \cite{Laibson2018}'s conjecture that clients could be making decisions based on experienced utility.\footnote{The third coefficient conditions on the subsample that did recover their first pawn in both arms and finds a coefficient of 4pp.
-This is not a causal estimate as recovery is influenced by treatment, but we found it telling that the differences were similar to the causal estimate for the full sample.}
-
-\subsection{The ``Forcing-Choice'' Design}
-\label{sec:randchoice}
-
-%Above we used outcome data from the forced arms ($Z_i\neq 2$) along with the commitment take-up rate in the choice arm ($Z_i = 2$) to argue that at least some of the \hl{89\%} of participants who did \emph{not} choose commitment would have been better off if they had.
-%By additionally examining \emph{outcome data} in the choice arm, it is possible to say more. 
-As a direct consequence of \eqref{eq:potentialOutcomes}, our experimental design---henceforth the ``forcing-choice design''---point identifies a number of interesting and economically-relevant causal quantities.
-First it identifies the treatment on the treated (TOT) and untreated (TUT) effects:  
-\[
-\text{TOT} \equiv \mathbbm{E}(Y_{i1} - Y_{i0} | C_i = 1), \quad
-\text{TUT} \equiv \mathbbm{E}(Y_{i1} - Y_{i0} | C_i = 0).
-\]
-The TOT is the causal effect of commitment on borrowers who would voluntarily choose it, while the TUT is the causal effect on borrowers who would not.
-If the TUT is positive, then borrowers who did not choose commitment would have experienced better outcomes, \emph{on average}, if they had.
-Selection on gains implies TOT$>$TUT$>$ATE, as it is typically assumed in canonical Roy models.
-Because our design identifies all three quantities, it allows us to test this implication directly and to calculate the average selection on gains (ASG), namely the difference between the TOT and TUT effects:
-\[
-\text{ASG} \equiv \mathbbm{E}[Y_{i1} - Y_{i0}|C_i = 1] - \mathbb{E}[Y_{i1} - Y_{i0} | C_i = 0] = \text{TOT} - \text{TUT}.
-\]
-
-A number of recent papers compare estimates of the TOT and TUT to better understand who selects into treatment and why, e.g.\ \cite{cornelissen2018benefits} and \cite{Walters}. 
-This line of work relies, at least to some extent, upon structural modeling assumptions to extrapolate from the reduced-form quantities that are identified by the data alone to more interesting, and economically relevant, causal parameters.\footnote{While the marginal treatment effects (MTE) approach \citep{heckman2007econometric} can in principle be used to identify the TOT and TUT without parametric restrictions, doing so requires an instrumental variable $Z$ with sufficiently rich support that the probability of treatment take-up given $Z$ varies continuously between zero and one.
-In practice, instrumental variables are usually discrete and, even when continuous, typically have a more modest effect on take-up.}
-An alternative approach aims to avoid structural assumptions by calculating conditional local average treatment effects (LATE) given observed covariates $X$ and re-weighting them according to the distribution of covariates in some population of interest to yield, for example, an average treatment effect \citep{aronow2013beyond,angrist2013extrapolate}.
-%For example, one might re-weight using the distribution of $X$ in the population as a whole, rather than the sub-population of compliers, to extrapolate from LATE to ATE. 
-But there is no free lunch: this ``LATE-and-reweight'' approach relies upon assumptions of its own, most crucially the assumption that there is \emph{no selection-on-gains} conditional on $X$, i.e.\ that the conditional LATE equals the conditional ATE.
-In contrast to both approaches, the forcing-choice design uses exogenous experimental variation to point identify the ATE, TOT, and TUT without ruling out unobserved selection-on-gains or relying on additional structural modeling assumptions.
-
-\begin{figure}
-\caption{Graphical Intuition for the Forcing-Choice Design.} 
-    \begin{center}
-        \centering
-        \includegraphics[width=1.0\textwidth]{Figuras/tot_tut_intuition.png}
-    \end{center}
- \scriptsize{
-     %This figure illustrates why the controlled choice design identifies the TOT and TUT effects.
-    Gray rectangles denote borrowers with a commitment contract; white rectangles denote borrowers with a status quo contract. 
-    A comparison of means across control and forcing arms identifies the ATE of forcing commitment. 
-    %In the choice arm, anyone with a commitment contract is a chooser; in the control and forcing arms, we do not know who is a chooser and who is not, but because borrowers are randomly assigned to experimental treatment arms, the share of choosers will be the same, on average (depicted using dashed vertical lines).
-    The difference of mean outcomes across the choice and control ``nets out'' the non-choosers, and hence equals the TOT multiplied by the share of choosers.
-    %arms gives the intent-to-treat effect of offering choice. 
-    %Under the exclusion restriction that moving non-choosers between the choice and forcing arms does not change their outcomes, this comparison ``nets out'' the non-choosers.
-    %Hence, the ITT of offering choice equals the TOT multiplied by the share of choosers. 
-    %Similarly, under the exclusion restriction that moving choosers between the choice and forcing arm does not affect their outcomes. 
-    Similarly, the difference of means across the forcing and choice arms ``nets out'' the choosers and equals the TUT multiplied by the share of non-choosers.
-        The share of choosers, illustrated using dashed vertical lines, is equal on average across arms under random assignment.}
-    \label{tot_tut_graph}
-     %\textit{Do file: }  \texttt{tot\_tut\_graph.do}
-\end{figure}
-
-The key insight can be read directly from \eqref{eq:potentialTreatments} and \eqref{eq:potentialOutcomes}; Figure \ref{tot_tut_graph} provides graphical intuition.
-%for our identification approach.
-% derivations appear in \ref{append:randchoice}
-Viewing $Z_i$ as an instrumental variable, the forcing-choice design can be interpreted as a \emph{pair} of RCTs, each subject to one-sided non-compliance.
-The first of these compares $Z_i=0$ to $Z_i = 2$.
-For each individual with $Z_i = 0$ we have $D_i = 0$ and observe $Y_{i0}$.
-For those with $Z_i = 2$ we have $D_i = C_i$ and observe $(1 - C_i) Y_{i0} + C_i Y_{i1}$.
-This is identical to a ``randomized encouragement'' design in which treatment is only available to those who are encouraged: $Z_i = 2$.
-Under this interpretation, those with $C_i = 1$ are ``the compliers'' and it follows by a standard argument (see Section \ref{sec:proofs}) that
-\begin{equation}
-\frac{\mathbbm{E}(Y_i|Z_i=2) - \mathbbm{E}(Y_i|Z_i =0)}{\mathbbm{E}(D_i|Z_i=2)-\mathbbm{E}(D_i|Z_i=0)} = 
-\frac{\mathbbm{E}(Y_i|Z_i=2) - \mathbbm{E}(Y_i|Z_i =0)}{\mathbbm{E}(D_i|Z_i=2)} = \text{TOT} 
-\label{eq:TOT}
-\end{equation}
-since $\mathbbm{E}(D_i|Z_i=0)=0$ by \eqref{eq:potentialTreatments}. 
-A closely related argument can be used to construct a Wald estimand that identifies the TUT.
-Here we consider $Z_i = 1$ to be the ``encouragement'' and compare the outcomes for these individuals to those with $Z_i = 2$.
-If $Z_i = 1$ then $D_i = 1$ and we observe $Y_{i1}$.
-If instead $Z_i = 2$ then $D_i = C_i$ and we observe $(1 - C_i) Y_{i0} + C_i Y_{i1}$.
-Again, we can view this as an experiment with one-sided non-compliance, but now the situation is reversed.
-Everyone with $Z_i = 1$ is treated, but some people with $Z_i = 2$ are ``always-takers'' who obtain the treatment ($D_i = 1$) despite having been allocated to the ``control'' arm $Z_i=2$.
-Under this interpretation, the ``compliers'' are those with $C_i = 0$: when $Z_i=1$ they take the treatment, and when $Z_i=2$, they do not.
-Thus,
-\begin{equation}
-\frac{\mathbbm{E}(Y_i|Z_i=1) - \mathbbm{E}(Y_i|Z_i =2)}{\mathbbm{E}(D_i|Z_i=1)-\mathbbm{E}(D_i|Z_i=2)} = 
-\frac{\mathbbm{E}(Y_i|Z_i=1) - \mathbbm{E}(Y_i|Z_i =2)}{1 - \mathbbm{E}(D_i|Z_i=2)} = \text{TUT}
-\label{eq:TUT}
-\end{equation}
-since $\mathbbm{E}(D_i|Z_i = 1)= 1$ by \eqref{eq:potentialTreatments}. 
-Because they identify both the TOT and TUT, \eqref{eq:TOT} and \eqref{eq:TUT} also identify the average selection on gains: $\text{ASG} = \text{TOT} - \text{TUT}$.
-
-The forcing-choice design also identifies the average selection bias (ASB) and average selection on levels (ASL). In particular,
-\begin{align}
-\label{eq:ASB}
-    \text{ASB} &\equiv \mathbbm{E}(Y_{i0}|C_i=1) - \mathbbm{E}(Y_{i0}|C_i = 0) = \frac{\mathbbm{E}(Y|Z=0) - \mathbbm{E}(Y|Z=2,D=0)}{\mathbbm{E}(D|Z=2)}\\
-    \label{eq:ASL}
-    \text{ASL} &\equiv \mathbbm{E}(Y_{i1}|C_i = 1) - \mathbbm{E}(Y_{i1}|C_i=0) = \frac{\mathbbm{E}(Y|Z=2,D=1) - \mathbbm{E}(Y|Z=1)}{1 - \mathbbm{E}(D|Z=2)}
-\end{align}
-as shown in Section \ref{sec:proofs}.
-The ASB tells us whether borrowers who voluntarily choose commitment are those who are worse off, on average, under the status quo.
-Similarly, the ASL tells us whether borrowers who voluntarily choose commitment are those who are better off, on average, under the commitment contract.
-
-Equations \eqref{eq:TOT}--\eqref{eq:ASL} are useful for understanding why the forcing-choice design identifies the TOT, TUT, ASG, ASB, and ASL but they are less convenient for estimation and inference.
-\autoref{sec:estimation_inference} explains how to compute each of these quantities from a small  number of just-identified, linear instrumental variables regressions, along with appropriate cluster-robust standard errors.
-These estimators and standard errors are implemented in our companion STATA package. %\textcolor{red}{Add a link to this package along with the documentation.}
-
-%\todo[inline]{Possibly add some discussion here of Craig's idea: using the controlled choice design to study ``targeting''}
-
-%A unique feature of our design is the randomized assignment to treatment (forced commitment), control (forced no-commitment), and choice of treatment.
-
-%This structure allows us to observe the average value of both the treated and untreated potential outcomes, as well as the selection into treatment that would occur under choice.
-A starting point for how to exploit this structure is to apply the logic usually used to estimate the Treatment on the Treated (ToT) to also recover the Treatment on the Untreated (TUT).
-This approach assumes nothing about the decision to choose (other than random sampling generating counterfactual compliance rates that would have been the same in every arm), but imposes three exclusion restriction-style assumptions typical of Local Average Treatment Effect (LATE) analysis.
-Namely, a) the typical assumption that an individual not choosing the treatment has the same potential outcome as one not offered it, then b) the mirror image assumption for the Forcing arm that an individual forced to take Commitment has the same potential outcome as an individual freely choosing it, and c) no spillovers from chooser to non-choosers in the choice arm.\footnote{\hl{For robustness we also try a Manski-type monotone IV approach with similar results.}}
-
-%More formally, let $Z_i$ be the observed, randomly assigned experimental allocation, where $Z_i=0$ denotes the control arm, $Z_i=1$ denotes the Forced arm, and $Z_i=2$ is the Choice arm.
-Let $C_i$ be the choice type; $C_i=0$ when individual $i$ does not choose commitment and $C_i=1$ when chooses commitment, observed in the Choice arm and latent in the other two arms.
-A fraction $p$ of individuals chooses the treatment in the Choice arm.
-Finally, $D_i = Z_i\times \mathds{1}(Z_i\neq 2) + C_i\times \mathds{1}(Z_i=2)$ is the observed treatment indicator, and $Y(d,z)$ is the potential outcome function for $d=0,1$, and $z=0,1,2$.
-
-%To test the difference between gains for choosers versus gains from non-choosers we need to identify $\mathbb{E}[Y_1-Y_0\;|\;C=1]$ (the Treatment on the Treated), and $\mathbb{E}[Y_1-Y_0\;|\;C=0]$ (the Treatment on the Untreated).
-The observed outcome in the Choice arm is the weighted average of the treated and untreated outcomes; $p \times\mathbb{E}[Y_1\;|\;C=1] + (1-p)\times\mathbb{E}[Y_0\;|\;C=0]$.
-Given assumptions a) and c) above we can recover the ToT from the difference between the Choice and Control arms as is standard, and then symmetrically we can invoke b) and c) to recover the TUT from the difference between the Forced and Choice arms as follows:
-
-%\begin{align*}
-%ToT \equiv \mathbb{E}[Y_1 - Y_0 \;\mid\; C=1]  &=   \frac{\mathbb{E}[Y \;\mid\; Z=2] - \mathbb{E}[Y \;\mid\; Z=0]}{p} \\
-%TuT \equiv \mathbb{E}[Y_1 - Y_0 \;\mid \;C=0]  &=  \frac{\mathbb{E}[Y \;\mid\; Z=1] - \mathbb{E}[Y \;\mid\; Z=2]}{(1-p)} 
-%\end{align*}
-
-%This estimate of the ToT is the standard one that would result from instrumenting for compliance with the offering of treatment as in \cite{angrist1996identification}.
-The TuT is the analogous estimator, which could be recovered in a regression pooling the forced and choice arms and instrumenting for \textit{not} complying with being assigned to the choice arm (for a more formal development, see the appendix).
-The advantage of representing the estimands via division of the relevant ITT by the compliance (non-compliance) rate is that it allows us to estimate all the necessary terms from the single pooled regression Equation \ref{basic_reg}, from which the significance levels for the ToT, the TuT, and the difference between them can all be estimated as single-equation F-tests:
-
-%\[ToT = \frac{\beta^C}{p}; \qquad\quad TuT = \frac{(\beta^F - \beta^C)}{(1-p)}; \qquad\quad (ToT-TuT) = \frac{\beta^C}{p}- \frac{(\beta^F - \beta^C)}{(1-p)}. \]
-
-%\hfill \newline
-%\noindent \textbf{TOT and TUT results.}
-
-Table \ref{tot_tut} calculates the causal quantities described above---TOT, TUT, ASG, ASB, and ASL---for our experimental data, along with robust standard errors for each. 
-For purposes of comparison, the table also presents the ATE results from Section \ref{Experiment} above (row 1),\footnote{Coefficients are not exactly the same since Table 4 includes branch and day-of-week FE.} along with the corresponding average potential outcomes $\mathbbm{E}[Y_0]$ and $\mathbbm{E}[Y_1]$ (rows 4--5).
-The columns of the table correspond to different outcome variables defined above.
-We are now in a position to report one of the important results in the paper.
-For all four outcome definitions, the TUT effect is positive, statistically and economically significant, and comparable in magnitude to the ATE.
-In other words: the structured payments contract is on average \emph{beneficial} to the people who \emph{would not choose it}, and these benefits are large.
-That is, mandating structured payment contracts would decrease the financial cost.
-Borrowers are leaving money in the table by not choosing it.
-
-Some comments are in order.
-First, this result holds on average.
-Some non-choosers could lose from a mandate.
-Section \ref{sec:RF} assesses personalized targeting strategies.
-Second, financial cost is not welfare, and further work with more comprehensive measures (stress, consumption, performance in other loans) needs to be done.
-We provide proof of concept that at least financial cost may not be minimized by free choice and provide a method to rigorously compare take-up mandates against consumer choice.
-Third, given that providing such contracts may not be in the lender's interest, borrowers may not even be presented with this choice.
-
-Table \ref{tot_tut} also estimates TOT.
-Due to the low take-up rate of commitment in the choice arm, TOT effects are imprecisely estimated.
-Only one of them, \%(1-Default) from column (3), is statistically significant.
-This carries over into our estimates of the average selection on gains.
-Our point estimates are \emph{negative} for all but the (1 - Default) outcome, but none is statistically distinguishable from zero.
-%Although we cannot quite reject the null hypothesis that the TUT and TOT effects are equal--our power is limited because of the low take-up rate of commitment in the choice arm--the pattern of coefficients is consistent with some degree of selection-on-gains.
-%Commitment is more beneficial to people who are willing to choose it than it is to people who are not.
-For the (1 - Default) outcome, we have sufficient precision to conclude that the average selection bias (ASB) is large and negative.
-This means that borrowers who choose commitment would have faced a higher probability of default under the status quo contract than borrowers who do not choose commitment.%\footnote{We may not want to read too much into TOT vs TUT comparisons as they are imprecise.
-But taken at face value, the result that TOT$>$TUT for default, while the opposite is true for financial cost, suggests that, while voluntary commitment has a slightly stronger effect on allowing borrowers to avoid default, forcing \textit{reduces} payments in a strong enough manner as to overcome the default-benefits of choice.}
-
-Overall, Table \ref{tot_tut} suggests that commitment works but that \emph{not enough} people choose to commit: the commitment contract is beneficial on average even to those who would \emph{not} choose it voluntarily.
-We believe this result is new in the household finance literature.
-It also illustrates how the ``Forcing-Choice'' design can be used to study more generally whether low take-up of an intervention is problematic, based on the impacts among non-choosers.\footnote{For instance, in the debate on financial commitment take-up, some papers argue it is low (\cite{Ashraf}, \cite{Gine}, \cite{Ted}, \cite{Royer} while others argue it is high (\cite{Kremer}, \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}, \cite{Pascaline}), but none estimates the benefits for non-takers.
-In a different domain, doctors claim that medical treatment abandonment is too high in a broad range of diseases \citep{non_adherence}, without knowing the treatment benefits for those that abandon.}
-
-\begin{table}[H]
-\caption{Five Treatment Effects Estimates: TOT, TUT, ASG, ASB, ASL}
-\label{tot_tut}
-\begin{center}
-\footnotesize{\input{./Tables/tot_tut.tex}}
-\end{center}
-\scriptsize{This table presents results computed using the derivations from Section \ref{sec:randchoice}.
-The APR and financial cost outcomes have been multiplied by $-1$ so that a positive causal effect \emph{benefits} the borrower in each of the four columns.
-The bottom panel presents p-values for a number of null hypothesis tests of treatment effect heterogeneity.
-}
-%\textit{Do file: } \texttt{tot\_tut.do}
-\end{table}
-
-%Below we explore possible explanations for this result.
-%and the ``right people'' choose to commit: those who are most likely to benefit from it and those whose outcomes are most adverse under the status quo.
-
-%Given that the ITT results for the Choice arm imply an insignificant worsening of outcomes relative to the control, our estimates of the Treatment on the Treated in the first row of the bottom panel show negative results that are larger in absolute magnitude (multiplied by ~9, the inverse of the compliance rate) and similarly insignificant.
-The Treatment on the Untreated (TuT), conversely, is strongly positive across the board, and indicates a significant improvement for all outcomes (here ITTs are effectively multiplied by 1.12, the inverse of the non-compliance rate).
-Most novel is the ability to form a test of the difference between the ToT and the TuT, which is conducted in the bottom rows of the table.
-We provide four different ways of estimating p-values for this comparison; the standard clustered estimates motivated by the experimental design, normal and percentile bootstraps, and randomization inference.
-The differences between treatment effects for compliers and non-compliers are of borderline significance in some of the unadjusted specifications, but are not significant once adjusted.\footnote{It is worth noting that the statistical power of these estimands is driven by the compliance rate; given our low overall compliance we are better powered to measure the TuT than the ToT, and the power for the difference between the two would be highest with a compliance rate of 50\%.}   Because of the large standard errors on the ToT coming from the low compliance rate in the Choice arm we are unable to state with statistical confidence that the TuT is higher than the ToT, but the TuT is strongly positive while the ToT is weakly negative, and so in both relative and absolute terms the choices being made are `wrong' relative to the potential outcomes.
-
-\section{The Case for Paternalism}
-\label{Paternalism}
-
-\subsection{Why does paternalism work in this context?}
-\label{why_paternalism}
-
-A behavioral literature has highlighted voluntary commitment as an attractive way of allowing the ``right'' people to self-select.
-% A discussion of compulsory commitment is necessarily paternalistic, and by its nature focuses on impacts among those who would not have selected commitment voluntarily.
-%Viewed through the lens of rational choice theory, it is unsurprising that we estimate $\text{TOT}>\text{TUT}$. 
-The argument for compulsory treatment, centers on the surprising result that $\text{TUT}>0$.
-We now investigate four potential explanations for the positive $\text{TUT}$: the need to learn, time discounting, present bias, and overconfidence.
-
-%\hfill \newline
-%\noindent \textbf{Learning.}
-
-Our experiment introduced a new contract into an environment that had not previously featured commitment; perhaps clients required experience to understand its benefits.
-Are clients who experienced the commitment contract more likely to choose commitment subsequently than those assigned to the status-quo contract?
-%We have already shown above that those who experienced the Forcing contract were more likely to borrow again.
-We now ask whether the subset who were assigned to the Choice arm when they returned were more likely to choose commitment.
-Appendix Table \ref{learning_table} %\footnote{Table \ref{learning_table} presents information about participants' \emph{immediate subsequent} pawning behavior.
-For borrowers who returned to pawn again more than once, this analysis considers only their first repeat pawn.}
-shows \textit{no difference} in choosing commitment for those assigned to forced commitment versus those assigned to status quo control that came back to pawn again (22\% did).
-%The implication is that while those who have experienced commitment feel more positively towards the pawn contract, the experience does not lead them to conclude that they need commitment on the subsequent loan.
-While these exercises cannot completely exclude the possibility that learning would play a role with more exposure, they provide no indication that the lack of voluntary compliance is simply a matter of inexperience with commitment in the short run.
-Note also that there will be no learning if lenders don't provide a structured payment contract in the first place.
-
-%Column (1) considers the 228 clients who returned only a second time to pawn again at a day/branch that was randomly assigned to the choice arm.
-Each of the two rows in this column presents a difference of mean commitment take-up rates, and associated standard error.
-The first row compares those who were \emph{initially} assigned to forced commitment against those where were assigned to control; the second row compares those who were initially assigned to the choice commitment arm to those who were assigned to the other two arms.
-In each case, there is no statistically discernible difference in the rates of commitment take-up.
-Granted, this is a selected sample because the decision to pawn again is potentially endogenous to the initial treatment allocation.
-For this reason, Column (2) considers the full sample of 4441 borrowers by re-defining the outcome variable to be an indicator for returning to pawn again at a branch/day when commitment was offered \emph{and} choosing commitment.
-This composite outcome variable is not subject to the sample selection problem (although it is directly driven by the decision to repeat borrow).
-The comparison in the two rows remains the same: forced commitment versus control in row one and choice commitment versus forced arms in row two.
-Again, there is no statistically discernible difference in commitment take-up rates in either row.
-While these exercises cannot completely exclude the possibility that learning plays a role, they provide no indication that the lack of voluntary compliance is simply a matter of inexperience with commitment.
-
-%\hfill \newline
-%\noindent \textbf{Time discounting.}
-
-Can high borrower time discount rates explain low demand for structured payments?
-%Highly impatient individuals might rationally choose the \emph{status quo} contract, despite the benefits that commitment yields returns,
-After all, monthly payments are front-loaded while pawn recovery is back-loaded, even if by only a few days.  
-%those returns are realized at contract ending hile the cost of monthly payments are incurred  Our estimated decrease in the financial cost of credit from above ignores discounting, but commitment involves incurring up-front costs (early payment) in return for delayed benefits (a higher probability of recovering one's pawn).
-Figure \ref{fc_discount_rates} calculates TUT effects for different borrower discount rates given the actual timing of repayment and pawn recovery.
-The solid line gives the TUT effect adjusted for a specified annual discount rate, while the shaded regions give the associated 95\% \& 90\% confidence interval.
-We see that non-choosers continue to experience significant decreases in the net present value of financial costs up to annual discount rates of 1,000\%, and the NPV remains positive, although not significant only at 5,000\% discount rates.
-These are huge discount rates.\footnote{In a similar exercise for subprime borrowers in the US, \cite{Levin} argue that even discount rates smaller than these would be too large to be reasonable and can be safely discarded as explanations.} As such, discounting is unlikely to explain why those who benefit, on average, from commitment fail to choose it.
-% when offered.
-
-%\hfill \newline
-%\noindent \textbf{Present bias.} 
-If the benefits of commitment among non-choosers cannot be explained by standard models of rational choice, the canonical behavioral story would center on time inconsistency.
-While commitment is useful to anyone with hyperbolic time preferences, only those who are sophisticated---i.e.\ aware that they are hyperbolic discounters---will demand it.
-A large share of ``na\"ive'' hyperbolics in the population--borrowers who are unaware that they are hyperbolic discounters--could therefore drive a large and positive $\text{TUT}$.
-Our baseline survey included standard questions about discount rates between today and a month in the future versus discount rates between three and four months in the future.
-This allows us to classify borrowers who display more impatience over immediate delays as present biased.
-This measure of financial hyperbolicity is widely used in survey research, although it is not without problems.\footnote{Our measure is dichotomous, and it is not incentivized.
-Recent empirical work has shown the superiority of more elaborate measures such as ``convex time budgets'' \citep{andreoni2015measuring} while questioning the interpretation of measures of hyperbolicity that are not based on consumption \citep{andreoni2012estimating, cohen2020measuring}, suggesting that real effort tasks provide a better measure \citep{augenblick2015working}.
-Given that we had only a few minutes to interview real pawnshop clients prior to a commercial transaction, our simple measure was a necessary compromise.}
-
-If we could perfectly measure present bias and sophistication, we could divide the sample into three groups: sophisticated hyperbolics (who chose commitment), time-consistent non-choosers (for whom forcing will not be effective), and na\"{i}ve hyperbolic non-choosers (who will benefit from forced commitment).
-%If present bias fully explains the low take-up rate of voluntary commitment, we should find that the TUT for present-biased borrowers  is positive while the TUT for all other borrowers is not.
-If present bias fully explains the low take-up rate of voluntary commitment, we should find that the TUT for present-biased borrowers is positive.
-This is because among the group of non-takers, a comparison of present-biased borrowers against everyone else is a comparison of na\"{i}ve hyperbolics against time-consistent non-choosers.
-The left panel of Figure \ref{tut_beh_partition} in the Appendix carries out a feasible version of this exercise using our survey measure of present bias.
-%The overall TUT estimate along with a 95\% confidence interval is given in blue.\footnote{For all borrowers who answered our present-bias survey questions.}
-%The corresponding TUT estimate and confidence interval for present-biased borrowers identified with the survey question is given in green; results for all other borrowers are shown in red.
-%The overall TUT is a weighted average of the impact in these two sub-groups.
-The TUT among the present biased is insignificant and less than half the size of the strongly significant TUT among those who are \textit{not} present biased.
-Therefore, taking our survey measure of hyperbolicity at face value.
-We find no indication that present-bias explains our positive estimated TUT.
-
-%\hfill \newline
-%\noindent \textbf{Sure confidence.}
-
-Finally, motivated by the high subjective probabilities of recovery we found in the baseline survey, and by the fact that a large fraction of borrowers pay towards recovery and then lose the pawn and these payments, we explore overconfidence in recovery as a potential explanation of low demand for structured payments.
-After all, recall that while 72\% of survey respondents believe they have a 100\% chance of recovering their pawn, in reality only 43\% will go on to do so.
-Borrowers who are certain to recover their pawn perceive no benefit of committing to repay under the threat of fees and, therefore, no benefit of choosing the structured payment contract.
-%if individuals who \emph{believe} that they are certain to repay, choose (rationally given their incorrect beliefs) to forgo the costs associated with commitment that are designed to induce repayment.
-To explore this, as in the preceding paragraph, we compare the overall TUT estimate to estimates computed for two sub-groups, defined by a binary variable that we call ``sure-confidence''.
-This measure equals one for any individual who says at the time of borrowing that they have a 100\% probability of recovering their pawn, and zero otherwise.
-%The right panel of Figure \ref{tut_beh_partition} presents the results for this exercise.
-%The overall TUT estimate for all borrowers who answered our sure-confidence survey questions is given in blue, along with a 95\% confidence interval.
-%The corresponding TUT estimate and confidence interval for sure-confident borrowers is given in green; results for all other borrowers are shown in red.
-In contrast to our results for present bias, we find that sure-confidence \textit{is} a strong predictor of TUT.
-Figure \ref{tut_beh_partition} shows that the TUT is almost entirely confined to the sure confident individuals, while those that say they have some chance of defaulting have TUT close to zero.
-It seems that the effectiveness of paternalism in our experiment may be driven by \emph{overconfident} borrowers who, heedless of the risk of default, fail to choose commitment despite benefiting substantially when they are forced to commit.\footnote{In Figure \ref{determinants_sure} we plot the coefficient estimates from a regression that predicts sure confidence with a battery of individual-level characteristics.
-Older males are more likely to be sure-confident, as are those with more education.
-Taken at face value, the sure-confident also report less financial stress, less trouble paying bills, and to be more frequently relied upon financially by family members.
-Viewed through a behavioral lens, however, it is also possible that the type of person who is over-confident in their ability to repay a loan also exaggerate their degree of economic security in their response to survey questions.
-In any case, it appears that sure confidence may be difficult to predict with easily-observed and objective demographic criteria, a point to which we return below.}
-
-\subsection{Targeting Paternalism using Causal Forests} \label{sec:RF}
-
 %\noindent \textbf{Causal forests.} 
-On average, the commitment contract benefits both those who would choose it and those who would not.
+On average, the structured contract benefits both those who would choose it and those who would not.
 In Section \ref{sec:bounds}, we briefly went \emph{beyond} average effects by presenting bounds on the distribution of individual treatment effects.
@@
 Rank invariance, however, is an extremely strong assumption.\footnote{For the financial cost outcome, rank invariance implies that all invididual treatment effects are positive.}
-We then applied NCW assumptions to estimate average treatment effects for choosers and non-choosers.
-
-In this section, we again impose NCW exclusions, but this time conditional on observed covariates, not just on average.
+We then applied NAE assumptions to estimate average treatment effects for choosers and non-choosers.
+
+In this section, we again impose NAE exclusions, but this time conditional on observed covariates, not just on average.
 This enables us to use causal forests to estimate \textit{conditional} average treatment effects (CATE) as well as CTOT and CTUT effects.
@@
 %This exercise provides more fine-grained information about treatment effect heterogeneity.
-Among other things, it will potentially allow us to identify groups of borrowers who are on average \emph{harmed} by commitment.
+Among other things, it will potentially allow us to identify groups of borrowers who are on average \emph{harmed} by structure.
 %Under the stronger assumption that our observed survey measures capture the main sources of treatment effect heterogeneity, this exercise will allow us to approximate individual-level counterfactuals, to consider whether particular borrowers made ``mistakes'' in their choice of contract.
@@
 As covariates, we use 22 questions in our survey (what we call the \textit{wide} set of covariates in Appendix \ref{app:cate}.
-The survey questionnaire (with the highlighted questions being the ones for the wide set of covariates) can be found in \ref{baseline_survey} in the Appendix.}
+The survey questionnaire (with the highlighted questions being the ones for the wide set of covariates) can be found in \ref{baseline_survey} in the Appendix.
+\textcolor{teal}{ \cite{burke2022credit} use a generalized random forest algorithm to explore heterogeneity in the effects of credit builder loans on the credit score.}}
 We implement these estimates using the covariates from our survey.
@@
       \includegraphics[width=\textwidth]{Figuras/he_dist_tau_hat_tot.pdf}
-          \caption{ToT}
+          \caption{Conditional TOT}
     \end{subfigure}
@@
       \includegraphics[width=\textwidth]{Figuras/he_dist_tau_hat_tut.pdf}
-          \caption{TuT}
+          \caption{Conditional TUT}
     \end{subfigure} 
@@
         \includegraphics[width=\textwidth]{Figuras/he_dist_tau_hat_eff.pdf}
-        \caption{ATE}
+        \caption{Conditional ATE}
     \end{subfigure} 
@@
 As we see from the figure, the conditional average effects are highly heterogeneous but overwhelmingly positive. 
-The TUT density is particularly interesting for the question of paternalism since, as emphasized above, it presents conditional average effects for borrowers who would not voluntarily choose commitment.
+The TUT density is particularly interesting for the question of paternalism since, as emphasized above, it presents conditional average effects for borrowers who would not voluntarily choose structure.
 Only 7\% of our estimated conditional TUTs are negative (95\% confidence interval of [4\%, 9\%]).\footnote{To be clear, this is a probability statement about conditional average effects over the distribution of covariates.
@@
 %\noindent \textbf{``Mistake'' thresholds.} 
-%Under the assumption that our instrumental forest estimates capture important sources of treatment effect heterogeneity, we can use them to assess whether particular borrowers in the choice arm made ``mistakes'' in their decision to accept or refuse the commitment contract, in terms of predicted financial costs of the loan.
-We now use the CTUT estimates to quantify how much extra financial cost would borrowers incur under different scenarios.
-To simplify language, we define a ``mistake'' for a non-chooser to be a conditional TUT estimate that significantly exceeds some large and positive APR threshold, e.g., \ 10 percentage points.
-At any such threshold, we can calculate the percentage of non-choosers in the choice arm who have benefited by more than that threshold from having chosen commitment.
-Again, we do not measure welfare, only financial cost.
-
-The results of this exercise can be read off from the green curve in Figure \ref{choose_wrong}.
-Defining $F_{\text{TUT}}(\delta)$ to be the CDF corresponding to the density of  CTUT estimates from Figure \ref{heterogeneous_effects}, the green curve in Figure \ref{choose_wrong} is merely $[1 - F_{\text{TUT}}(\delta)] \times 100\%$.
-In other words, the vertical axis for the green curve plots the percentage of non-choosers who made a ``mistake'' of a certain threshold from the horizontal axis.
-Note that we use a \emph{positive} APR threshold to denote a mistake for both choosers and non-choosers.
-This ensures that bigger mistakes are always to the \emph{right} of smaller mistakes.
-The green shaded region gives associated 95\% pointwise confidence bounds.
+%Under the assumption that our instrumental forest estimates capture important sources of treatment effect heterogeneity, 
+We now use the conditional TUT and TOT estimates described above to explore the extent to which borrowers in the choice arm could be said to have made a ``mistake'' by choosing to accept or refuse the structured repayment contract.
+For the purpose of this exercise, we say that a non-chooser has made a ``mistake'' if her estimated CTUT is large and \emph{positive}: she did not select structured repayment, but our generalized random forest estimates suggest that someone with her observed characteristics would benefit from it, on average, in terms of lower financial costs.\footnote{Our sign convention defines treatment effects that \emph{benefit} borrowers as positive: a decrease in APR is a \emph{positive} treatment effect.}
+We write the word mistake in quotation marks to highlight that we are using this term as a convenient shorthand for a specific pattern of conditional average treatment effects rather than making the stronger claim that a certain borrower made a choice contrary to her own welfare.
+There are two reasons why ``mistakes'' may not fully capture welfare.
+First, conditional average treatments are not equivalent to individual treatment effects: they only reflect observed sources of heterogeneity. 
+The closer our covariates come to capturing the relevant sources of variation in individual treatment effects, the less of a concern this poses.
+Second, our definition of a ``mistake'' does not incorporate all the costs and benefits that an individual borrower faces. 
+Above we presented a number of robustness checks to address this concern in the context of \emph{unconditional} average treatment effects, addressing discounting, liquidity, and the costs of visiting the branch to make an interim payment, for example.
+Here we take a similar but simpler approach in the case of \emph{conditional} average treatment effects, by considering ``mistakes'' at different APR \emph{thresholds}.
+At any such threshold, we can calculate the percentage of non-choosers in the choice arm who have benefited by more than that threshold from having chosen structure, according to our CTUT estimates. 
+Again: this does not directly measure welfare, only financial cost.
+
+The green curve in Figure \ref{choose_wrong} presents the results of this analysis.
+Defining $F_{\text{TUT}}(\delta)$ to be the CDF corresponding to the density of  CTUT estimates from Figure \ref{heterogeneous_effects}, the solid curve equals $[1 - F_{\text{TUT}}(\delta)] \times 100\%$ and the shaded region gives associated 95\% pointwise confidence bounds.
+In words: for any given APR threshold on the horizontal axis, the vertical axis for the green curve plots the percentage of non-choosers who made a ``mistake'' 
+ of at least that magnitude by \emph{not choosing} structured repayment.
+Again: a mistake is defined as an estimated CTUT that exceeds the specified APR threshold.
 
@@
  \end{center}       
- \scriptsize{This figure presents conditional average TUT and TOT effects for the APR outcome from Figure \ref{heterogeneous_effects} in an alternative manner, to consider the fraction of borrowers in the choice arm who made ``mistakes'' in their decision to accept or refuse the commitment contract.
+ \scriptsize{
+ %This figure presents conditional average TUT and TOT effects for the APR outcome from Figure \ref{heterogeneous_effects} in an alternative manner, to consider the fraction of borrowers in the choice arm who made ``mistakes'' in their decision to accept or refuse the structured contract.
 A ``mistake'' for a non-chooser is defined as a positive conditional TUT effect that significantly exceeds a specified threshold APR value.
+ This figure plots the fraction of borrowers who made a ``mistake'' in their decision to except or refuse the structured contract, defined as a positive conditional TUT effect that exceeds a specified threshold APR value.
  %\textit{Do file: } \texttt{choose_wrong_quant_wrong_tot_tut.do}
@@
 
-For choosers we follow an analogous approach, defining a ``mistake'' as a \emph{negative} CTOT exceeding a particular APR threshold.
-The results for choosers can be read from the red curve in Figure \ref{choose_wrong}.
-If $F_{\text{TOT}}(\delta)$ denotes the CDF corresponding to the density of conditional TOT estimates from Figure \ref{heterogeneous_effects}, then the red curve is merely $F_{\text{TOT}}(-\delta) \times 100\%$.
+We can carry out an analogous exercise using our estimated CTOT to explore ``mistakes'' by choosers in the choice arm, subject to the same caveats as above.
+Here the situation is reversed.
+We say that a chooser has made a ``mistake'' if her estimated CTOT is large and \emph{negative}: she chose structured repayment, but our generalized random forest estimates suggest that someone with her observed characteristics would face \emph{higher} financial costs, on average, with structure.\footnote{Our sign convention defines treatment effects that \emph{harm} borrowers as positive: an \emph{increase} in APR is a \emph{negative} treatment effect.}
+As we did for the non-choosers, we consider alternative APR thresholds to define ``mistakes''.
+For example, we can ask: what fraction of non-choosers would have faced an APR that was at least 10 percentage points more favorable if they \emph{had not} chosen structured repayment?
+The red curve in Figure \ref{choose_wrong} presents the results of this analysis.
+The solid curve equals $F_{\text{TOT}}(-\delta)$ where $F_{\text{TOT}}$ is the CDF corresponding to the density of conditional TOT effects from Figure \ref{heterogeneous_effects}, while the red shaded region gives pointwise 95\% confidence bands.
+Note that we use a \emph{positive} APR threshold to denote a mistake for both choosers (red) and non-choosers (green).
+This ensures that bigger mistakes are always to the \emph{right} of smaller mistakes and allows us to plot both curves in a single figure.
+In other words a \emph{positive} value of $\delta$ always denotes a mistake of a given magnitude, regardless of whether we are considering choosers or non-choosers.
+This convention allows us to compute present the \emph{overall} percentage of borrowers in the choice arm who made a ``mistake'' of a particular magnitude by taking a weighted average of the green and red curves: see the blue solid curve and associated pointwise 95\% confidence bands in Figure \ref{choose_wrong}.
+The blue curve is very similar to the green curve because 89\% of borrowers in the choice arm are non-choosers.
+
+%For choosers we follow an analogous approach, defining a ``mistake'' as a \emph{negative} CTOT exceeding a particular APR threshold.
+%The results for choosers can be read from the red curve in Figure \ref{choose_wrong}.
+%If $F_{\text{TOT}}(\delta)$ denotes the CDF corresponding to the density of conditional TOT estimates from Figure \ref{heterogeneous_effects}, then the red curve is merely $\left[1 - F_{\text{TOT}}(\delta)\right] \times 100\%$.
 %In other words, the red curve gives the percentage of choosers who made a ``mistake'' when mistakes are defined at a particular APR threshold.
-The red shaded region gives associated 95\% pointwise confidence bounds.
-The blue curve in Figure \ref{choose_wrong} gives the \emph{overall} percentage of borrowers in the choice arm who made a ``mistake'' at a particular APR threshold.
-This total is computed by taking a weighted average of the green (non-choosers) and red (choosers) curves, with weights equal to their shares in the choice arm.%\footnote{The blue curve is very similar to the green curve because 89\% of borrowers in the choice arm are non-choosers.}
+%The red shaded region gives associated 95\% pointwise confidence bounds.
 
 The results in Figure \ref{choose_wrong} suggest that a large fraction of non-choosers would have experienced lower financial costs had they chosen the structured payment contract, even at an APR threshold as large as 10 percentage points, we estimate that more than half of them should have chosen the structured payment contract to lower financial costs.
-In contrast, relatively few choosers appear to have made mistakes by choosing it.
-This now allows us to make a stronger statement in favor of paternalism in our context; not only does forced commitment generate large benefits \textit{on average}, but it also benefits the \emph{vast majority} of borrowers who would be coerced under a policy of forced commitment.
-
-\subsection{Can we target paternalism accurately?}
-
-Even though the overwhelming majority of borrowers would save on financing costs, not all of them would, according to our estimates.
-Is it possible to target paternalism only towards those who would benefit from it?
-
-The answer depends on how predictive the covariate information is of treatment effects.
-Note that to implement a targeting protocol, the covariate information used in the model would need to be either verifiable or hard to manipulate.
-In our survey and administrative data, this leaves us with only a few covariates: age, gender, high school education or above, desired loan size, and whether that individual has ever pawned before.
-We call these the ``narrow'' covariate set, to contrast with the full set of survey variables, which we call the ``wide'' covariate set.
-We take the estimated   $\widehat{\text{CATE}}(X_i)$ using the wide covariates as our ground truth.\footnote{We assign a dummy variable equal to one for the 90\% of borrowers who have a positive CATE using the wide covariate set.
-Figure \ref{wide_narrow_forests} shows the relationship between these two different  CATEs.
-We generate substantially less heterogeneity when using the narrow covariate set, although we still reject the null hypothesis of no treatment effect heterogeneity with the test from \cite{chernozhukov2018generic}.}
-
-To investigate targeting we ask how well we can predict this ground truth using the narrow covariate set, which is the set of less-manipulable variables that the pawnlender has.
-We use both a logistic regression and a random forest classification model using the narrow covariate set to predict positive benefits at the individual level.
-We compare the in-sample performance of targeting rules against a policy of universal forced commitment.
-
-\begin{table}[H]
-\caption{Type I \& II errors using targeting narrow rules}
-\label{hit_miss_rule}
-\begin{center}
-\footnotesize{\input{./Tables/hit_miss_rule.tex}}
-\end{center}
-\scriptsize{This table reports error rates for six different rules for allocating individuals to commitment.
-Row 1 assigns all borrowers to control, Row 2 all to structured payments.
-Row 3 uses `optimal targeting according to the CATE from the wide covariate set.
-Row 4 uses a random forest classification, and Row 5 a logit model, both with only the narrow covariate set.
-Row 6 uses the choices made by borrowers.
-%DoFile : wide_narrow_forests.do
-}
-\end{table}
-
-Table \ref{hit_miss_rule} shows error rates for six possible assignment rules: assigning all borrowers to control, all to structured payments, the optimal (wide-fores), the random forest with narrow covariates, the Logistic model with narrow covariates, and the actual choice made by borrowers.
-All models take the wide RF as the ground truth.
-While the narrow RF correctly assigns to control roughly half of those who do not benefit from the structures payment contract, it also incorrectly allocates to control 4.38\%  that would gain from structured payments.
-As such, it only improves the overall correct targeting rate by about half of a percentage point relative to universal Forcing.
-The Logit assignment rule is even less successful at predicting benefits and harms, with a higher share of borrowers incorrectly assigned to both treatment and control, meaning that the overall correct targeting rate for the Logit is 5 pp \textit{lower} than universal forcing to structured payments.
-Self-targeting through choice proves to be little better than assigning everyone to the control condition, given the low take-up rate and the presence of both Type I and Type II errors in the choice arm.
-
-The takeaway is that given (a) low take-up, (b) the large fraction of the sample benefiting from commitment, (c) and the weak predictive power of the narrow covariates,universal paternalism assigning all borrowers to the commitment contract appears to be an attractive targeting method in our context.
+In contrast, comparatively fewer choosers appear to have made mistakes by choosing structure, although our estimates for this group are more imprecise.
+This now allows us to make a stronger statement in favor of paternalism in our context; not only does structure generate large benefits \textit{on average}, but it also benefits the \emph{vast majority} of borrowers who would be coerced under a policy of mandatory structure.
+Indeed, in Appendix \ref{targeting} we show that given the relatively weak power of reliably collectible covariates in predicting variation in the TOT and TUT, an optimal feasible model of targeting results in only very minimal decreases in the fraction of the sample assigned to the `wrong' treatment relative to simply assigning everyone to mandated structure (the CATE estimates above suggest 9.8\% of the sample is harmed by universally mandated structure, and this fraction falls only to 9.6\% with optimal feasible targeting).
+Hence in this context there seems to be limited downside for borrowers in simply shifting the default contract for everyone.
 
@@
 First, it analyzes the important but understudied industry of pawn loans.
-Likely, hundreds of millions of people use pawn loans, and yet economists have not studied them.
-We show that a simple change to contract terms results in substantial financial savings for pawn borrowers: forced commitment lowers the APR from 57\% to 46\%, and reduces the fraction of borrowers who default by 6.6 pp, or 15\%.
-That this new contract generated large benefits for borrowers and yet was not offered, and that a contract that generated default was the industry standard instead, is related to the idea of ``veiled paternalism'' \cite{Laibson2018}, put on its head, %In ``veiled paternalism'' principals embed forms of commitment into their products but mask this fact from consumers who may need but do not desire commitment, in pawn lending, over-collateralization means that lenders stand to make more money from defaulting borrowers, generating incentives for ``veiled \textit{non}-paternalism,''
-embedding features that lead to high borrower costs.
+Likely, hundreds of millions of people use pawn loans, and yet few economic studies exist.
+We provide new stylized facts about pawn lending, and provide evidence as to how contract structure in this context drives repayment and borrower costs.
+We do this using a novel ``Mandates-Choice'' design, which paired with twin exclusion restrictions allows us to go beyond ATE results and draw an important set of conclusions about the relationship between take-up and heterogeneous treatment effects, providing a complement to marginal treatment effects methods.
+We show that a simple change to contract terms results in substantial financial savings for pawn borrowers: mandatory structure lowers the APR from 57\% to 46\%, and reduces the fraction of borrowers who default by 6.6 pp, or 15\%.
+
+In terms of relating impacts to selection we find substantial benefits of treatment for non-choosers and no evidence of selection on gains.
+This is the first such result in the household finance literature.
+Estimating treatment effects for non-takers is critical in thinking about paternalism, and we show one rigorous way to do it that is new in the literature and distinct from Karlan-Zinman designs.
+ The over-collateralization of pawn loans is a  potential explanation for why this relatively simple repayment-inducing contract is not offered (or required) in the status quo.
+Given that lender profits are higher under default, this may be a case of the `veiled paternalism' from \cite{Laibson2018} turned on its head:  principals \textit{do not} embed commitment into contracts in a manner that is not obvious to agents but shifts behavior in a manner that improves returns for the principal.
+
+We correlate TUT impacts with behavioral parameters to try to explain the fact that only 11\% of borrowers choose structured payments when virtually all of them would benefit from it.
+Our results suggest that over-optimism of pawn recovery is the characteristic most strongly associated with benefiting from the commitment despite not having chosen it, and may be an explanation for the low demand for structured repayment.
+Low take-up suggests that in order to achieve widespread benefits in this context compulsory structure appears to be an attractive policy.
+With a now well-established toolkit of regular small payments and incentives delivering small default rates in microfinance, regulators may fruitfully investigate the possibility of requiring pawnbrokers to embed features of commitment and regularity into their repayment structures in more consistent ways.
+
+%\textcolor{red}{Overcollateralization and sunk payments make pawn loans a product different than microfinance and payday loans in the incentives they create.
+In fact, while recent literature shows that more flexibility in payments may be beneficial in microfinance, this does not seem to be the case in our pawn lending context.} That this new contract generated large benefits for borrowers and yet was not offered, and that a contract that generated default was the industry standard instead, is related to the idea of ``veiled paternalism'' \cite{Laibson2018}, put on its head, %In ``veiled paternalism'' principals embed forms of commitment into their products but mask this fact from consumers who may need but do not desire commitment, in pawn lending, over-collateralization means that lenders stand to make more money from defaulting borrowers, generating incentives for ``veiled \textit{non}-paternalism,'' embedding features that lead to high borrower costs.
 
@@
 %In our context voluntary commitment choice does improve borrower outcomes, but forcing commitment did induce significant cost savings for the overall group of clients.
-
-Second, a novel ``forcing-choice'' design paired with NCW assumptions allows us to go beyond ATE results and draw an important set of conclusions about the relationship between take-up and heterogeneous treatment effects, providing a complement to marginal treatment effects methods.
-%In particular, we simultaneously point-identify the impact of commitment on those who would naturally choose it \emph{and} those who only experience commitment when forced.
-Estimating treatment effects for non-takers is critical in thinking about paternalism, and we show one rigorous way to do it that is new in the literature and distinct from Karlan-Zinman designs.
-
-Third, in terms of our empirical results, we find substantial benefits of treatment for \textit{non-choosers} and no evidence of selection on gains by borrowers who choose commitment.
-This is the first such result in the household finance literature and a first step in thinking about paternalistically imposing frequent payment contracts.
-Our results show that over-optimism of pawn recovery is the characteristic most strongly associated with benefiting from the commitment despite not having chosen it, and it maybe an explanation for the low demand for commitment.
-Given that the rate of voluntary commitment in our sample is only 11\% and given the limited benefits from personalized targeting with our data, in order to achieve widespread benefits in this context compulsory commitment appears to be an attractive policy.
-With a now well-established toolkit of regular small payments and incentives delivering small default rates in microfinance, regulators may fruitfully investigate the possibility of requiring pawnbrokers to embed features of commitment and regularity into their repayment structures in more consistent ways.
 
@@
 How would lender competition affect the incentives to provide such a contract?
-Much needs to be done to improve the lives of the millions of borrowers using panw loans.
+Much needs to be done to improve the lives of the millions of borrowers using pawn loans.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\appendix
 

### 2025-04-25 donde.tex
revisions for r3
First set of edits after R&R

@@
      \label{exp_description}
-%\textit{Do file: }  \texttt{ss\_att.do}
+%\textit{Do file: }  \texttt{consort.do}
 \end{figure}
@@
 }
-%\textit{Do file: } \texttt{ss\_att.do}
+%\textit{Do file: } \texttt{ss\_balance.do}
 \end{table}
@@
         \centering
-        \includegraphics[width=1.0\textwidth]{Figuras/tot_tut_intuition.png}
+        \includegraphics[width=1.0\textwidth]{Figuras/tot_tut_graph.png}
     \end{center}
@@
 We examine four potential explanations for the positive $\text{TUT}$: the need to learn, time discounting, present bias, and overconfidence.
-To explore the last two dimensions we will use survey data.\footnote{Since merging with survey data reduces our sample, Table \ref{TUT_cond_survet} demonstrates that the subsample on whom we have survey data appears to be representative in terms of treatment effects.}
+To explore the last two dimensions we will use survey data.\footnote{Since merging with survey data reduces our sample, Table \ref{TUT_cond_survey} demonstrates that the subsample on whom we have survey data appears to be representative in terms of treatment effects.}
 

### 2025-04-25 presentations/PresentationDartmouth2024.tex
First set of edits after R&R

\documentclass[9pt, aspectratio=169]{beamer}

%\input{preamble.tex}
\input{preambleESBbeamer.tex}

\title{Structured Payments in Pawnshop Borrowing:\\
Mandates vs. Choice}
\author{Craig McIntosh\inst{1} \and Isaac Meza\inst{2} \and Joyce Sadka\inst{3} \and Enrique Seira\inst{4} \and Francis J. DiTraglia\inst{5} }
\institute[UTran]{\inst{1} UCSD, \inst{2} Harvard , \inst{3} ITAM , \inst{4} MSU , \inst{5} Oxford}

\date{Sept 2024}

%\setbeamercolor{section in head/foot}{bg=darkcrimsonred}
\setbeamersize{text margin left=11pt, text margin right=11pt}
%\setbeamertemplate{section in toc}[square]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{frame}[c, noframenumbering]%{\phantom{title page}}
% The \phantom{title page} is a kludge to get the red bar on top
\titlepage
\end{frame}

\begin{frame}{Pawnshop loans: prevalent and understudied}

\begin{itemize}
     \item Pawn loans are small, short-term loans, typically used for emergencies.
    \begin{itemize}
        \item Used by borrowers who don't have much access to credit: no credit or income checks.
    \end{itemize}
    \vfill \item \textbf{Overcollateralized}. Those loans involve surrendering highly liquid collateral (gold), in return for an immediate loan of much smaller value.  
    \begin{itemize}
        \item Unlike mortgages, pawn lender retains the entire value of the collateral under default along with any payments.
        \item For a given loan, lenders earn more by default.
    \end{itemize}    
    \vfill \item Pawn lending is very prevalent in the world (Carter \& Skiba, 2012). 
    \begin{itemize}
        \item 11,000 pawn shops in US, with 30m clients and \$14b revenues; in China \$43b.
        \item Our partner lender: 1m clients in 3 yrs (2.3m microfinance clients in Mexico, Pedroza, 2010).
    \end{itemize}
\end{itemize}

\end{frame}

\begin{frame}{Flexibility and high default}
    \begin{itemize}
    \item Pawn loans are highly \textbf{flexible:} pay-when-you-want within 90 days, no structured payments, no reminders.
        \begin{itemize}
            \item This lack of structure contrasts with microfinance loans.
        \end{itemize}
    \vfill \item High default rates, 44\% in our data (an order of magnitude larger than microfinance).
    \begin{itemize}
        \item Subjective value higher than gold value $\Rightarrow$ inefficient to lose.
        \item Gold-buying stores (avg of 2.8) close to pawn shops (pay $\approx$ 100\% of its gold value).
    \end{itemize}
     \item \vfill \textbf{Optimistic borrowers}: In our data, borrowers are very optimistic about recovery: avg. subjective probability of recovery (0-100) in our data is 92\%.
     \begin{itemize}
         \item Conditional on default: more than 2/5 pay towards recovery (avg. 42\% loan value).
     \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}{Questions}
     \begin{enumerate}
         \item  Could borrowers benefit from \textbf{frequent payments}, but contract not be offered by lenders?
         \item \vfill If such a contract were offered, would it be demanded by borrowers?
        \item \vfill Would \textbf{mandating} frequent payments reduce financing costs more than giving a menu of \textbf{choices}?
        \item \vfill What is the treatment effect of frequent payments on those who would \textbf{not} choose them (TuT)? And, is there selection on gains for those choosing them?
     \end{enumerate}
\end{frame}

\begin{frame}{Outline}
     \large   
     \begin{itemize}
        \item \textbf{Context: Borrowers, contracts, data, outcomes}
         \item \vfill ``Mandates-Choice'' Experimental Design
         \vfill\item Main results
          \vfill\item Exploiting ``Mandates-Choice'' Design: ToT, TuT
         \vfill\item Why low demand
         %\vfill \item Targeting?
     \end{itemize}
\end{frame}

\begin{frame}{Context}
\vspace{-.4in}
\begin{columns}
\begin{column}{.45\textwidth}
\begin{figure}[H]
    \begin{center}
    \caption{Pawnshop}
        \includegraphics[width=0.75\textwidth]{Figuras/empenio2_.png}
    \end{center}
    \end{figure}
\begin{figure}[H]
    \begin{center}
    \caption{Appraisers  inside a pawnshop}
        \includegraphics[width=0.7\textwidth]{Figuras/empenio9_.png}
    \end{center}
    \end{figure}    
    \end{column}
\begin{column}{.45\textwidth}
\begin{figure}[H]
    \begin{center}
    \caption{Waiting for appraisal}
        \includegraphics[width=0.7\textwidth]{Figuras/empenio11_.png}
    \end{center}
    \end{figure}
\begin{figure}[H]
    \begin{center}
    \caption{Lost pawns which are for sale}
        \includegraphics[width=0.75\textwidth]{Figuras/empenio3_.png}
    \end{center}
    \end{figure}    
    \end{column}    
    \end{columns}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Context}

\begin{frame}{Status quo contract (control group)}

\begin{itemize}
    \item Loan: 70\% of gold value in cash. Avg loan $\approx$ \$100USD.
    \item Loan term:  90 days.
    \item Repossession: if payments do not cover interest + capital, the lender sells the pawn at gold value.
    \item Interest rate: 7\% monthly rate on outstanding balances accumulated daily.
    \item No pre-payment penalties, no reminders.
    \item Borrowers can refinance the loan under the same terms if they pay incurred interest.
    \item Payments are first allocated to cover interest and lastly to capital.
    \item \alert{Pay when you want} before 90 days $\Leftarrow$ \pause We will impose ``Structured payments'' --- 3 equal-size payments per month.
\end{itemize}

\end{frame}

\begin{frame}{Data}
\begin{itemize}
    \item \textbf{Administrative data} 
    \begin{itemize}
        \item 1 month before, during, and 8 months after  experiment.
        \item Unique identifier for each client and each pawn.
        \item Value of the item, money loaned, date of pawning.
        \item For all payments: date,  amounts, and allocation to interest and capital.
        \item Fees incurred.
        \item Whether the client lost the pawn, recovered it, or refinanced the contract and when.
    \end{itemize}

    \vfill \item \textbf{Survey data}
    \begin{itemize}
        \item During experiment, we asked clients to complete a 5-minute survey before going to the teller window to appraise their piece and before treatment status was known to them.
        \item Demographics, subjective probability of recovering, vulnerability, education, present-bias, experience pawning, cost of going to branch, the subjective value, etc.
        \item We use this data only in the last part to (a) estimate CATEs, (b) discuss some mechanisms.
    \end{itemize}
\end{itemize}    
\end{frame}

\begin{frame}{Main outcomes: financial cost and default}
\label{fc_outcome}
\begin{itemize}
    \item We are interested in measuring the financial cost of borrowing, which includes the cost of losing the pawn.
    \vfill \item We will measure loan default using an indicator $\mathds{1}(\text{Default}_i)$, and the cost in pesos using the following definition that capture borrower outlays:    
\end{itemize}

\vspace{-.1in}

\begin{equation*}
  \text{Financial Cost}_i =
  \begin{cases}
    \sum_t P^{I}_{it} + \sum_t P^{F}_{it}   & \text{if } \mathds{1}\text{(Default)}_i=0\\
     \sum_t P^{I}_{it} + \sum_t P^{F}_{it} + \sum_t P^{C}_{it} + (\text{Value}_i - \text{Loan}_i) & \text{if } \mathds{1}\text{(Default)}_i=1 
  \end{cases}
\end{equation*}

   % \begin{equation*}
   %  \text{Financial Cost}_i =  \underbrace{\sum_t P^i_{it}}_{\text{Pay to Interest}} + \underbrace{\sum_t P^f_{it}}_{\text{Pay to Fees}}  + \mathds{1}(\text{Default}_i) \times \left[(\text{Value}_i - \text{Loan}_i)+ \underbrace{\sum_t P^c_{it}}_{\text{Pay to Capital}} \right]
   % \end{equation*}

\vfill \begin{itemize}
    \item We also show results in APR-like ``effective'' yearly interest rate (norm. FC by loan value and term).
\end{itemize}

% \pause \vspace{.2in}
% \: \: \: \: APR: ``effective'' interest rate:
%    \begin{equation*}
%     (\text{APR})_i =\left( 1 + \frac{\frac{\text{Financial Cost}_i}{\text{Loan Value}_i}}{\text{loan term}_i}\right)^{\text{loan term}_i}-1 
% \end{equation*}

   \vspace{.1in}
\begin{itemize}
    \item We \alert{will not talk about welfare}, only financial cost.
    \begin{itemize}
        \item Welfare could depend on reduced liquidity, anxiety from monthly payments, etc.
        \item If you have ideas on how to do welfare let me know.
    \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}{Outline}
     \large   
     \begin{itemize}
        \item Context: Borrowers, contracts, data, outcomes
         \item \vfill \textbf{``Mandates-Choice'' Experimental Design}
         \vfill\item Main results
          \vfill\item Exploiting ``Mandates-Choice'' Design: ToT, TuT
         \vfill\item Why low demand

     \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{M-C design}

\begin{frame}{Mandates-Choice Design}
\label{treatment_arms}
   \begin{itemize}
    \vfill \item Randomization at the branch-day level.  Analysis at the pawn level.
    \begin{enumerate}
        \vfill \item Status quo contract (Control, 1770 obs)
       \vfill \item Structured payments (Frequent payments, 1954 obs)
       \vfill \item Choice between the two (2580 obs)
    \end{enumerate}
       \vfill \item  This design enables us to explore whether giving choice saves borrowers more money than assigning them to a Structured payment contract.
       \vfill \item The existence of a Choice arm allows us to measure if there is demand for such a contract. Will also allow more cool stuff... 
\end{itemize}
\end{frame}

\begin{frame}{More details on implementation}
    \begin{itemize}
        \item No person knew sequence of days-contract type.
        \item  Personnel were told that consecutive same contract-type could occur, and that randomization was happening in many if not all branches.
        \item We had materials to explain the contract in simple terms.
        \item Borrowers explained back the contract.
        \item Appraisers no incentive either way (paid flat wage). Enumerators were there every day all day.
        \item Virtually no borrower left the branch without pawning.
        \item They seem to like this lender: 87\% pawned there before.
        \item Stick to branch: we cannot find experimental subjects in 2 different experimental branches. 
    \end{itemize}
\end{frame}

\begin{frame}{Status quo contract}
\vspace{-.2in}
    \begin{figure}[H]
    \label{ExplanatoryMaterial1}
    \begin{center}
        \includegraphics[width=0.34\textwidth]{Figuras/sq_contract.png}
    \end{center}
\end{figure}
\end{frame}

\begin{frame}{Structured payments contract}
%\vspace{-.1in}
\begin{columns}
\begin{column}{.45\textwidth}
   \begin{itemize}
       \vfill \item We designed a new contract that is identical to the status quo contract except that it enhances the regularity of payments.
       \vspace{.2in}
       \vfill \item Penalty fee not large < 1 USD on avg loan; $\approx$avg. transport cost to go to branch.
       \vspace{.2in}
       \vfill \item We view it as a way to increase salience of monthly payment.
    \end{itemize}
    \end{column}
\begin{column}{.45\textwidth}
    \vspace{-.3in}
        \begin{figure}[H]
            \includegraphics[width=0.78\textwidth]{Figuras/fc_contract.png}
        \end{figure}
    \end{column}
    \end{columns}
\end{frame}

 \begin{frame}{Timeline and sample size}
\vspace{-.3in}
 \begin{figure}[H]
 \begin{center}
         \includegraphics[width=0.85\textwidth]{Figuras/consort.pdf}
   \end{center}
 \end{figure}
 %\hyperlink{experimental_integrity}{\beamerbutton{Details}}
 \end{frame}

\begin{frame}{No differential selection}
\vspace{.2in}
    \begin{table}[H]
\label{attrition_table}
\begin{center}
\small{\input{./Tables/Attrition.tex}}
\end{center}
\end{table}
\end{frame}

\begin{frame}{Same characteristics across arms}
    \begin{table}[H]
\begin{center}
\resizebox{.55\textwidth}{!}{
\scriptsize{\input{./Tables/SS.tex}}
}
\end{center}
%\textit{Do file: } \texttt{ss\_att.do}
\end{table}
% \hyperlink{data}{\beamerbutton{Back}}
\end{frame}

\begin{frame}{Outline}
     \large   
     \begin{itemize}
        \item Context: Borrowers, contracts, data, outcomes
         \item \vfill ``Mandates-Choice'' Experimental Design
         \vfill\item \textbf{Main results}
          \vfill\item Exploiting ``Mandates-Choice'' Design: ToT, TuT
         \vfill\item Why low demand

     \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}

\begin{frame}{Specification}
%\vspace{-1in}
\begin{equation} 
\Large
    y_{ij} = \alpha + \beta^S T_{i}^S + \beta^C T_{i}^C + \gamma X_{ij} + \epsilon_{ij}
\end{equation}

\begin{itemize}
    \vfill \item $i$-borrower, $j$-branch; $T_{i}^S$, $T_{i}^C$ indicator Structure or Choice arms; 
    \vfill\item Ommited category is the Status quo (pay-when-you-want).
    \vfill\item $X_{ij}$ branch + day-of-week fixed effects. Clustering branch-day level.
    \begin{itemize}
        \item 14\% pawned on two distinct days. We restrict our sample to each borrower's \emph{first visit}.
        \item A borrower (30\%) may pawn multiple items her visit. We include these as separate observations. Different contracts but the same contract type.
    \end{itemize}

    \vfill \item $\beta^C$ is the ATE of being given choice (or ITT of structure in the Choice arm).
    \vfill \item   $\beta^S$ is the ATE of mandatory structure (full compliance). 
\end{itemize}
\end{frame}

\begin{frame}{Large reductions in default and financial cost}
\label{main_results}
\begin{itemize}
    \item Financial cost reduced by \$204 pesos (22\% of mean). That is: charging fee + structure \textit{decreased} cost.
    \item Default decreases by 6.6pp (15\% of mean).
    \item APR decreases by 11$pp$, from mean of 57 percent yearly.
\end{itemize}
\vspace{.3in}
\begin{table}[H]
\begin{center}
\resizebox{0.95\textwidth}{!}{
\small{\input{./Tables/decomposition_main_te.tex}}
}
\end{center}
\end{table}
   \vfill 
  %\hyperlink{several_def_cost}{\beamerbutton{More}}
\end{frame}

\begin{frame}{Reduced costs even considering subjective value, travel, lost liquidity }

\vspace{-.1in}
\begin{itemize}
    \item Subjective value.
    \item Entire day's wage per visit + transport cost.
    \item Raw liquidity adjustment: as if she borrowed to pay us at 7\%  %~(removed $\sum_t P^{I}_{it}$)
\end{itemize}
%\vspace{-.4in}
\begin{table}[H]
\label{table_robustness_fc}
\begin{center}
\resizebox{0.85\textwidth}{!}{
\small{\input{Tables/fc_robustnessESB}}
}
\end{center}
 \scriptsize 
%\textit{Do file: } \texttt{fc\_robustness.do}
\end{table}
   % \hyperlink{main_results}{\beamerbutton{Back}}
\end{frame}

\begin{frame}{How savings come about: faster payments}
\begin{columns}
\begin{column}{.45\textwidth}
\begin{table}[H]
\begin{center}
\scriptsize{\input{./Tables/mechanism_pres1.tex}}
\end{center}
\end{table}
\end{column}
\begin{column}{.45\textwidth}
   \begin{itemize}
     \item The first payment occurs 13 days earlier, and they pay 9\% more.
     \vspace{.2in}
     \vfill \item Increasing the fraction who recover on the first visit by 7.9 pp. 
     \vspace{.2in}
     \vfill  \item Loan resolution 28 days faster.
\end{itemize} 
\end{column}
\end{columns}
%\hyperlink{intermediate_outcomes}{\beamerbutton{Back}}
\end{frame}

\begin{frame}{Payment Bifurcation: less paying without recovering}
\begin{table}[H]
\begin{center}
\footnotesize{\input{./Tables/mechanism_pres2.tex}}
\end{center}
\end{table}

%\hyperlink{intermediate_outcomes}{\beamerbutton{Back}}
   \vfill \item   %Mandatory structure decreases fraction of borrowers making a payment and \textit{not} recovering by 7.1pp.
   As if Structure made them realize they will end up losing pawn anyway, and to stop paying early.
    % \begin{itemize}
    %     \item Among those that default, those in the forced commitment arm are 14pp less likely to have paid towards recovery. 
    % \end{itemize}
\end{frame}

% \begin{frame}{Visit Frequency}
%     \begin{table}[H]
% \begin{center}
% \footnotesize{\input{./Tables/mechanism_pres3.tex}}
% \end{center}
% \end{table}
% \vfill
% %\hyperlink{intermediate_outcomes}{\beamerbutton{Back}}
%  \begin{itemize}
%      \item \vfill Commitment induces a ``parting of the waters'' whereby those who were going to default visit the branch subsequently 1/5 fewer times.
% \end{itemize}
% \end{frame}

\begin{frame}{Do lenders profit from Structure?}

\begin{itemize}
    \item On a given pawn, borrowers gain = lenders loss.
    \item But, borrowers may return if they like the product. Do they? \pause Yes = 6.7pp higher repeat business. 
\end{itemize}
\begin{table}[H]
\begin{center}
\footnotesize{\input{Tables/repeat_loans_ESB}}
\end{center}
\end{table}    
% \begin{itemize}
%     \item Client forced into commitment is 20\% more likely to come back again and pawn.
%     \item Not mechanically from having recovered the pawned, since also pawn other pieces.
%     \item Not within the life of the loan, but after. So unlikely that is a liquidity story.
%     \item Conditional on recovery (endogenous), ``effect'' twice as big.
% \end{itemize}

\end{frame}

\begin{frame}{Highly stylized Back-of-the-Envelope Profit }

\begin{itemize}
    \item Does repeat business compensate the loss per pawn? No, profit is at least 14\% \textit{lower} under structure.
    \vfill \item Calculate a discounted sum of profits for client $j$ comparing a scenario where (a) only status quo loans are offered with a second scenario where (b) only structured payment loans are offered.
    \vfill \item Let $\text{Profit}_{j,X}  = \sum_{t=0}^T\delta^t\{\text{Financial Cost}_j | \text{Contract}=X\}\times\Pr(\text{Repeat}_j | \text{Contract}=X)^t$, where $\delta$ is the discount rate, $X \in \{SQ, Structured\}$. 
    \begin{itemize}
        \item Going to the branch again assumed as independent events.
        \item We find that for every  $\delta$ $\in$ [0,1]  and for every $T$ the status quo results in at least 14\% higher profit for the lender.
    \end{itemize} 
    \vfill\item The extra repeat probability for the structured payment contract is insufficient to compensate for the loss in each loan.

    \vfill\item This may explain why lenders do not offer frequent payment contracts (in contrast with microfinance).
\end{itemize}

\end{frame}

\begin{frame}{Low demand for a feature that decreases financial cost?}
    \begin{itemize}
        \item Recap: structured payments save borrower's money, on average.
        \vfill \item  \textbf{However, only 11\% demand Structured payments contract}.
        \begin{itemize}
            \item More demand by: higher schooling, less experienced, less vulnerable, would like reminders.
        \end{itemize}
        \vfill\item Could it be that the 89\% \alert{who did not choose} would not benefit?
        \vfill\item Hard question, person level effects  $Y_{i1} - Y_{i0}$ are not identified.
        \begin{itemize}
            \item Non-parametric Fan and Park (2010) bounds imply \textcolor{green}{at least 23\% of borrowers would benefit}, so at least 12\% would have had lower FC and did not choose structure. 
        \end{itemize}
        \vfill\item Would like to know the avg. effect of non-choosers (\alert{Treatment on the Untreated}). 
    \end{itemize}
\end{frame}

\section{TuT vs ToT}

\begin{frame}{Outline}
     \large   
     \begin{itemize}
        \item Context: Borrowers, contracts, data, outcomes
         \item \vfill ``Mandates-Choice'' Experimental Design
         \vfill\item Main results
          \vfill\item \textbf{Exploiting ``Mandates-Choice'' Design: ToT, TuT, ASG}
         \vfill\item Why low demand

     \end{itemize}
\end{frame}

\begin{frame}{Identification afforded by experiment}
Our 3-arm experiment + exclusion restriction allows us to estimate: 
\begin {itemize}
 \item Treatment on the Treated (ToT).
 \item Treatment on the Untreated (TuT).
\end{itemize}
\vspace{.1in}
Notation: 
\begin{itemize}
    \item Potential outcomes $(Y_0,Y_1,C)$, where $C$ is borrower's ``choice-type'' $\in\{0,1\}$, i.e. $\{SQ,Structure\}$
    \item Assignment: $Z \in \{0,1,2\}$, i.e. $\{SQ,Structure,Choice\}$.  
    \item Treatment: $D \in \{0,1\} $, i.e. $\{SQ,Structure\}$.
\end{itemize}
\vspace{.1in}
Assumptions:
\begin{itemize}
    \item $Z \perp (Y_0,Y_1,C)$, achieved by randomization
    \item $D = \mathbbm{1}(Z_i \neq 2) Z + \mathbbm{1}(Z_i=2) C$.
\end{itemize}
\end{frame}

\begin{frame}{ToT and TuT are identified}
Exclusion restrictions (for a given person $i$):
\begin{itemize}
        \item No warm-glow 
        (NWG) from choosing: $Y_i(d=1,z=2)=Y_i(d=1,z=1) \equiv Y_{i1}$
        \item  No warm-glow from not choosing: $Y_i(d=0,z=2)=Y_i(d=0,z=0) \equiv Y_{i0}$
    \end{itemize}
\pause \vfill This allows us to write the effect for borrower $i$ as:
\begin{center}
    $Y_i = \mathbbm{1}(Z_i =0) Y_{i0} + \mathbbm{1}(Z_i = 1)  Y_{i1}  + \mathbbm{1}(Z_i = 2) \left[(1 - C_i) Y_{i0} + C_i Y_{i1} \right]$
\end{center}

\begin{itemize}
    \item Note $F_0$, $F_1$, and $C$ are identified.
\end{itemize}
\vspace{.1in}

\pause Prop:
\begin{itemize}
    \item ToT := $\mathbbm{E}(Y_{i1} - Y_{i0} | C_i = 1)$ is point-identified, and equals $\frac{\mathbbm{E}(Y_i|Z_i=2) - \mathbbm{E}(Y_i|Z_i =0)}{\mathbbm{E}(D_i|Z_i=2)} $
     \item TuT := $\mathbbm{E}(Y_{i1} - Y_{i0} | C_i = 0)$ is point-identified, and equals $\frac{\mathbbm{E}(Y_i|Z_i=1) - \mathbbm{E}(Y_i|Z_i =2)}{1-\mathbbm{E}(D_i|Z_i=2)} $
     %\item Also identified: 
     %\begin{itemize}
      %   \item Average Selection on Gains $ASG:=ToT-TuT$
         %\item Average Seletion Bias $ASB:= \E[Y_0 | C=1]-\E[Y_0 | C=0]$
         %\item Average Selection on Levels $ASL:= \E[Y_1 | C=1]-\E[Y_1 | C=0]$
     %\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}{The ``Mandates-Choice'' Design}

\begin{itemize}
    \vfill \item Recall that under one-sided non-compliance (no always-takers), LATE=ToT.
    \vfill\item ToT: encouraged to choose Strucutre. 
 \vfill\item TuT: encouraged NOT to choose Structure. 
\end{itemize}
%\vspace{.2in}
\begin{figure}[H]
    \begin{center}
        \centering
        \includegraphics[width=.8\textwidth]{Figuras/tot_tut_graph.png}
    \end{center}
\end{figure}   
 \vfill
%\hyperlink{identification_randomized_choice}{\beamerbutton{Identification}}
\end{frame}

\begin{frame}{On avg. those that do \textit{not} choose would benefit: TuT $>$ 0}
\begin{itemize}
    \vfill \item Structure increases avg. financial benefit those who \alert{would not} choose it.
    \vfill \item  No selection on gains (ToT=TuT), in fact FC coefficients are smaller for ToT than for TuT.
    %\vfill \item Results hold when imputing transport cost and lost wages per visit, and charge interest in amount paid (as a proxy for liquidity lost).
\end{itemize}
\vspace{.1in}
\begin{table}[H]
%those who are most likely to benefit from it and those whose outcomes are most adverse under the status quo.
\label{tot_tut}
\begin{center}
\small{\input{./Tables/tot_tut_beamer.tex}}
\end{center}
\end{table}
\begin{center}
\vspace{-.1in}
\scriptsize{\centering Written now as a benefit ($\times$ -1). Numbers differ slightly as we don't include branch and day FE.}  
\end{center}
\end{frame}

% Despite substantial treatment effect heterogeneity, most borrowers would experience higher financial benefits under a commitment contract : $F_{\operatorname{TUT}}^{-1}(0.72)>0$

\begin{frame}{Recap}
We have learned that:
\begin{itemize}
     \item Forcing Structure ATE > 0 $\Rightarrow$ leads to positive financial benefit. 
    \pause \vfill \item   Choice ATE = 0 $\Rightarrow$  giving choice does \textit{not} increase financial benefit. 
    \pause \vfill \item A large part of this is due to low demand for structure.
    \pause \vfill\item TuT>0 $\Rightarrow$ argument for compulsory treatment \alert{(paternalism)}
\end{itemize}
    \pause  \vfill Three obvious questions (evidence is weaker but suggestive here):
    \begin{itemize}
        \item Why is demand ``low''?
        \item Would they learn over time that structure saves cost? 
        \item Can we target structure only to those that benefit instead of implementing a universal mandate?
    \end{itemize}
\end{frame}

\section{Why would there be low demand?}

\begin{frame}{Outline}
     \large   
     \begin{itemize}
        \item Context: Borrowers, contracts, data, outcomes
         \item \vfill ``Mandates-Choice'' Experimental Design
         \vfill\item Main results
          \vfill\item Exploiting ``Mandates-Choice'' Design: ToT, TuT
         \vfill\item \textbf{Why low demand:} suggestive evidence

     \end{itemize}
\end{frame}

\begin{frame}{If structure works, why don't people choose it?}
\begin{itemize}
    \item \textbf{1. Learning?} one possibility is that they would eventually demand it as they try it.
    \begin{itemize}
        \item One problem is that lenders may not provide it.
    \end{itemize}
    \vfill \item  Test those assigned to Structure or Status quo return and have a choice (i.e. get choice arm).
        \begin{itemize}
        \item Problems: small sample and returning is endogenous.
    \end{itemize}
 \end{itemize}  
 \vspace{.1in}
\begin{table}[H]
\begin{center}
 \resizebox{0.65\textwidth}{!}{
\small{\input{Tables/learning_exp}}
}
\end{center}
\end{table}
 %\hyperlink{learning}{\beamerbutton{Back}}
\end{frame}

\begin{frame}{Can impatience explain it?}
    \begin{itemize}
    \item  Structured payments imposes up-front costs for later benefits (collateral recovery).  
    \item  Requires an interest rate > 4,000\% to make NPV TuT =0. 
    \end{itemize}
\vspace{.1in}
\begin{figure}[H]
    \begin{center}
        \centering
        \includegraphics[width=0.50\textwidth]{Figuras/discount_effect_tut.pdf}
    \end{center}
\end{figure}   
\end{frame}

\begin{frame}{Time inconsistency? (very stylized)}

 \textbf{Canonical behavioral angle: Present bias}  PB naifs may not demand structure, yet have TuT>0

\begin{figure}[H]
    \begin{center}
        \centering
        \includegraphics[width=0.4\textwidth]{Figuras/hyperbolicity_strata.png}
    \end{center}
\end{figure}   
    \pause \begin{itemize}
    \item Survey ``switching'' measure of time inconsistency. %(\$100 tomorrow or \$150 in one month; and then 3 vs 4 months).
    \begin{itemize}
        \item Also questions about them falling into spending ``temptation'', and wanting reminders.
    \end{itemize}

    \vfill \item  Prediction: because Structure should not help rationals, TuT should be positive only among the PB-non choosers (=naifs).   
    \item We don't find this,  but the PB measure may not be good.

    \end{itemize}
\end{frame}

% \begin{frame}{Over confidence?}
%     \begin{itemize}
%     \item   Recall that at baseline, people were, on average, overconfident about recovering pawns.
%     \item   We estimate the TuT conditional on $X_i=1$ or $X_i=1$ (say $X_i= PB_i$ or $=Confidence_i$) and see which sub-populations have larger TuT.
% \vspace{.3in}
%     \begin{align*}
%         1=& \frac{\mathbb{E}[Y_{1i}-Y_{0i} | C_i=0, X_i=1]}{TuT}\Pr(X_i=1 | C_i=0) \\
%         \quad &+ \frac{\mathbb{E}[Y_{1i}-Y_{0i}| C_i=0, X_i=0]}{TuT}\Pr(X_i=0 | C_i=0)
%     \end{align*}

% %and we will say that the variable $B_i$ explains the ToT whenever one of the terms (ratio weighted by the probability) is statistically significant from zero, (close to one), and the other term is statistically zero.
%     \end{itemize}
% \end{frame}

\begin{frame}{Overconfidence?}

\begin{itemize}
    \item   Recall that at baseline, people were, on average, overconfident about recovering pawns.
    \vfill \item We find that TuT>0 is concentrated on those that said they will recover with 100\% probability. 
    \begin{itemize}
        \item Conceptually, overconfidence could explain low take up and TuT>0.
    \end{itemize}
    %\vfill \item In contrast, we don't find this result for PB (as measured by us).
\end{itemize}
\begin{figure}[H]
        \includegraphics[width=0.5\textwidth]{Figuras/tut_beh_partition.pdf}
\end{figure}
\end{frame}

\begin{frame}{Determinants of Sure Confidence}
        % \begin{figure}
        % \caption{What attributes correlate with Sure Confidence?}
        % \centering
        % \includegraphics[width=0.65\textwidth]{Figuras/determinants_confidence_100.pdf}
        % \end{figure}

The Sure-Confident are:
\begin{itemize}
    \item   Older, more educated men who
    \item   Have savings and do not report financial stress or trouble meeting bills, and 
    \item   Are likely to be relied upon by family members.
\end{itemize}        
\end{frame}

\section{Targeting?}

\begin{frame}{Outline}
     \large   
     \begin{itemize}
        \item Context: Borrowers, contract, data, measures
         \item \vfill ``Mandates-Choice'' Experimental Design
         \vfill\item Main results
          \vfill\item Exploiting ``Mandates-Choice'' Design: ToT, TuT
         \vfill\item Why low demand
         \vfill \item \textbf{TE heterogeneity and targeting?}
     \end{itemize}
\end{frame}

\begin{frame}{TE heterogeneity in TuT}

\begin{columns}
\begin{column}{.43\textwidth}
\begin{figure}    
\centering
\includegraphics[width=0.99\textwidth]{Figuras/he_dist_tau_hat_tut.pdf}
\end{figure}
\end{column}
\begin{column}{.5\textwidth}
   \begin{itemize}
     \item Assuming NWG conditional on X's, we use (Athey et.al. 2019) causal forests to estimate $E[Y_1 - Y_0| X = \mathbf{x}, C = 0]$, i.e. CTuT
     \vspace{.1in}
     \begin{itemize}
	 \item Causal forest partition X to produce the biggest difference in TE across leaves, and gives a ``personalized'' TE according to the leaf borrowers are assigned to.
    \end{itemize}
    \vspace{.2in}
    \item Only 7\% of borrowers's estimated CTuT < 0.
    \vspace{.2in}
    \item >1/2 lose at least 10pp APR from not choosing.
    \end{itemize}
\end{column}
\end{columns}
\end{frame}

% \begin{frame}{Example of a Causal Tree}
%     \begin{figure}
%         \centering
% \includegraphics[width=0.7\textwidth]{Figuras/crf_apr.pdf}
%         \end{figure}
% \end{frame}

% \begin{frame}{Fraction that forgo benefit:  Choice Arm}
%         \begin{figure}
%        % \label{choose_wrong}
%         %\caption{Mistakes in choice arm}
%         \centering
%         \includegraphics[width=0.65\textwidth]{Figuras/line_cw_apr_tot_tut.pdf}
%         \end{figure}
% \begin{itemize}
%     \item   Use Random Forest to estimate ToT, TuT conditional on covariates.
%     \item   Those making either choice make mistakes if benefit of other choice is higher.
%     \item $>$ 70\% of non-choosers would have seen some benefit from assignment to commitment.
%     \item  $<$ 20\% of choosers made a mistake.
% \end{itemize}        
% \end{frame}

% \begin{frame}{91\% better off being forced into Structure}
%         \begin{figure}
%         \centering
%         \includegraphics[width=0.65\textwidth]{Figuras/cdf_CATE.pdf}
%         \end{figure}
% \end{frame}

\begin{frame}{How well can we target Structure}
\begin{itemize}
    \item   Can we predict who would lose from structure, to assign them to status quo?
        %\vfill \item   Standard targeting analysis, except need to consider covariates carefully given context.
    %\vfill \item   Private sector lender, competitive market, part of attraction of pawning is no application!  
    \vfill \item Take (wide) Causal RF estimate $(Y_{i1}-Y_{i0})^{wide}$ (CATE) as ground truth.
    \vfill \item Use ``narrow'' causal RF (verifiable: age, gender, schooling, pawned before) as a targeting model,  
     \begin{itemize}
         \item Assign based on estimated $(Y_{i1}-Y_{i0})^{narrow}$.
         \item Define assignment of borrower $i$ to Structure as error if : $(Y_{i1}-Y_{i0})^{wide}<0$, and analogously for status quo.
     \end{itemize}

    \vfill \item Finding: our best targeting has 9\% ``errors'', as large as assigning \textit{everyone} to Structure. 
    %\item   Cannot use choice and then compel compliance among non-choosers in a commercial context.  
    \vfill\item Observed Choice has 87\% errors. 
    \vfill\item Given low take up + large fraction benefits from Structure (CATE) + benefit hard to predict with narrow variables $\rightarrow$ paternalistic mandate may be attractive.
    % \vfill \item Which leaves us with:
    % \begin{itemize}
    % \item   Age
    % \item   Gender
    % \item   HS Education or above
    % \item   Ever pawned before 
    % \end{itemize}
\end{itemize}        
\end{frame}

% \begin{frame}{Predicted APR CATEs `Wide' and `Narrow' }

%         \begin{figure}
%         %\caption{Scatterplot of Predicted Heterogeneity}
%         \centering
%         \includegraphics[width=0.6\textwidth]{Figuras/scatter_hist_wide_narrow.pdf}
%         \end{figure}

%\begin{itemize}
   % \item   Substantially less heterogeneity fitting APR CATE with `narrow' than `wide'
    %\item Test of homogeneity (Chernozhukov et. al. 2018) no longer rejected with `narrow'
    %\item   However, overall fitted relationship shows `narrow' adjusts to the mean TE.
%\end{itemize}        
%\end{frame}

%\begin{frame}{Comparison of Targeting Performance:  CDFs} 
%         \begin{figure}
%         \label{targeting_CDFs}
%         \caption{Distribution of Benefits under Different Targeting Rules}
%         \centering
%         \includegraphics[width=0.70\textwidth]{Figuras/wide_narrow_rule.pdf}
%         \end{figure}
% \begin{itemize}
%     \item   Even using the Random Forest to target, our four `narrow' variables only increase the fraction benefitting from 91\% (all Forced) to ~93\% (targeted).
%     \item  Using a Logit with the `narrow' variables actually worsens performance relative to universal Forcing because Logit matches benefit/loss fraction, has both Type 1 and Type 2 errors.
% \end{itemize}        
% \end{frame}

% \begin{frame}{Type I \& II errors using targeting narrow rules}
% \begin{itemize}
%     \item Taking wide RF as the ground truth, compare Mandates vs choice, vs narrow targeting.
% \end{itemize}
% \vspace{.2in}
% \begin{table}[H]
% \begin{center}
% \resizebox{0.35\textwidth}{!}{
% \small{\input{./Tables/hit_miss_rule_presentation.tex}}
% }
% \end{center}
% \end{table} 
% \begin{itemize}
%     %\item   Even RF with `narrow' variables results in very modest increase in targeting efficiency relative to universal paternalism.
%     %\item  Logit performs very poorly because it makes symmetric Type I and Type II errors and hence assigns many to control who would have been better off with commitment.
%     \item  \textbf{Takeaway:}  With these variables, targeting mandated structure is ineffective; universal mandate achieves same outcome.
% \end{itemize}        
% \end{frame}

\section{Conclusion}
\begin{frame}{Conclusion}
    \begin{itemize}
     \item This paper analyzes the important but understudied industry of pawn loans, where over-collateralization and overconfidence may create a role for regulation.
     \vfill \item Simple change to contract terms results in substantial financial savings: mandatory structure lowers the APR from 57\% to 46\%, and reduces the fraction of borrowers who default by 6.6 pp.
    \vfill \item Novel RCT design to study take up and treatment heterogeneity (ToT, TuT, ASG): TuT>0, and no ASG. 
     \vfill \item Laibson has spoken of `\textit{private paternalism}', where firms supply commitment not demanded by consumers to the benefit of both. Pawn loans may be a contrary case, with lenders embedding features that \textit{hurt} borrowers.
     \vfill \item Q: (i) Would results hold using more comprehensive welfare measures? (ii) How would stronger lender competition affect the incentives to provide structured payment contracts? (iii) Would borrowers learn the benefits of structured payments in the longer run? 
    \end{itemize}  
\end{frame}

\end{document}

### 2025-04-25 presentations/PresentationWinsconsin2025.tex
First set of edits after R&R

--- 2025-04-25 presentations/PresentationDartmouth2024.tex
@@
 
-\date{Sept 2024}
+\date{April 2025}
 
@@
     \end{itemize}
-     \item \vfill \textbf{Optimistic borrowers}: In our data, borrowers are very optimistic about recovery: avg. subjective probability of recovery (0-100) in our data is 92\%.
+     \item \vfill \textbf{Optimistic borrowers}: In our data, borrowers are very optimistic about recovery: avg.
+subjective probability of recovery (0-100) in our data is 92\%, and 72\% say recovery is certain.
      \begin{itemize}
@@
      \begin{enumerate}
-         \item  Could borrowers benefit from \textbf{frequent payments}, but contract not be offered by lenders?
+         \item  Could borrowers benefit from \textbf{structured} (frequent) payments, but contract not be offered by lenders?
          \item \vfill If such a contract were offered, would it be demanded by borrowers?
         \item \vfill Would \textbf{mandating} frequent payments reduce financing costs more than giving a menu of \textbf{choices}?
-        \item \vfill What is the treatment effect of frequent payments on those who would \textbf{not} choose them (TuT)? And, is there selection on gains for those choosing them?
+        \item \vfill What is the treatment effect of structured payments on those who would \textbf{not} choose them (TuT)? 
+        \begin{itemize}
+            \item Are non choosers leaving money on the table?
+        \end{itemize} 
      \end{enumerate}
@@
           \vfill\item Exploiting ``Mandates-Choice'' Design: ToT, TuT
-         \vfill\item Why low demand
+         \vfill\item Why low demand (mostly speculative)
          %\vfill \item Targeting?
@@
     \end{enumerate}
-       \vfill \item  This design enables us to explore whether giving choice saves borrowers more money than assigning them to a Structured payment contract.
+       \vfill \item  This design enables us to explore whether giving Choice saves borrowers more money than assigning them to a Structured payment contract or Status-quo.
        \vfill \item The existence of a Choice arm allows us to measure if there is demand for such a contract. Will also allow more cool stuff... 
@@
     \begin{itemize}
+        \item Randomization built into IT system
         \item No person knew sequence of days-contract type.
-        \item  Personnel were told that consecutive same contract-type could occur, and that randomization was happening in many if not all branches.
+        \item  Personnel were told that consecutive same contract-type could occur, and that randomization was happening in many branches.
         \item We had materials to explain the contract in simple terms.
@@
 
-\begin{frame}{Status quo contract}
+\begin{frame}{Standard (status quo) contract}
 \vspace{-.2in}
@@
    \begin{itemize}
-       \vfill \item We designed a new contract that is identical to the status quo contract except that it enhances the regularity of payments.
+       \vfill \item New contract identical to the status quo contract, except that it enhances the regularity of payments.
        \vspace{.2in}
@@
     \item Entire day's wage per visit + transport cost.
-    \item Raw liquidity adjustment: as if she borrowed to pay us at 7\%  %~(removed $\sum_t P^{I}_{it}$)
+    \item Raw liquidity adjustment: as if she borrowed at 7\% to pay us.  %~(removed $\sum_t P^{I}_{it}$)
 \end{itemize}
@@
 \begin{itemize}
-    \item $Z \perp (Y_0,Y_1,C)$, achieved by randomization
-    \item $D = \mathbbm{1}(Z_i \neq 2) Z + \mathbbm{1}(Z_i=2) C$.
+     \item $Z \perp (Y_0,Y_1,C)$, achieved by randomization.
+    \item $D = I(Z_i \neq 2) Z + I(Z_i=2) C$.
 \end{itemize}
@@
 \begin{itemize}
-        \item No warm-glow 
-        (NWG) from choosing: $Y_i(d=1,z=2)=Y_i(d=1,z=1) \equiv Y_{i1}$
-        \item  No warm-glow from not choosing: $Y_i(d=0,z=2)=Y_i(d=0,z=0) \equiv Y_{i0}$
+        \item No agency effect 
+        (NAE) from choosing: $Y_i(d=1,z=2)=Y_i(d=1,z=1) \equiv Y_{i1}$
+        \item  No agency effect from not choosing: $Y_i(d=0,z=2)=Y_i(d=0,z=0) \equiv Y_{i0}$
     \end{itemize}
-\pause \vfill This allows us to write the effect for borrower $i$ as:
+\pause \vfill This allows us to write the outcome for borrower $i$ as:
 \begin{center}
-    $Y_i = \mathbbm{1}(Z_i =0) Y_{i0} + \mathbbm{1}(Z_i = 1)  Y_{i1}  + \mathbbm{1}(Z_i = 2) \left[(1 - C_i) Y_{i0} + C_i Y_{i1} \right]$
+    $Y_i = I(Z_i =0) Y_{i0} + I(Z_i = 1)  Y_{i1}  + I(Z_i = 2) \left[(1 - C_i) Y_{i0} + C_i Y_{i1} \right]$
 \end{center}
@@
 \begin{itemize}
-    \item ToT := $\mathbbm{E}(Y_{i1} - Y_{i0} | C_i = 1)$ is point-identified, and equals $\frac{\mathbbm{E}(Y_i|Z_i=2) - \mathbbm{E}(Y_i|Z_i =0)}{\mathbbm{E}(D_i|Z_i=2)} $
-     \item TuT := $\mathbbm{E}(Y_{i1} - Y_{i0} | C_i = 0)$ is point-identified, and equals $\frac{\mathbbm{E}(Y_i|Z_i=1) - \mathbbm{E}(Y_i|Z_i =2)}{1-\mathbbm{E}(D_i|Z_i=2)} $
+    \item ToT := $E(Y_{i1} - Y_{i0} | C_i = 1)$ is point-identified, and equals $\frac{E(Y_i|Z_i=2) - E(Y_i|Z_i =0)}{E(D_i|Z_i=2)} $
+     \item TuT := $E(Y_{i1} - Y_{i0} | C_i = 0)$ is point-identified, and equals $\frac{E(Y_i|Z_i=1) - E(Y_i|Z_i =2)}{1-E(D_i|Z_i=2)} $
      %\item Also identified: 
@@
         \item One problem is that lenders may not provide it.
+        \item (Experience pawning \textit{negatively} correlated with take up of structure).
     \end{itemize}
@@
     \item  Structured payments imposes up-front costs for later benefits (collateral recovery).  
-    \item  Requires an interest rate > 4,000\% to make NPV TuT =0. 
+    \item  Requires annual discounting > 4,000\% to make NPV TuT =0. 
     \end{itemize}
@@
 
-% \begin{frame}{Over confidence?}
-%     \begin{itemize}
-%     \item   Recall that at baseline, people were, on average, overconfident about recovering pawns.
-%     \item   We estimate the TuT conditional on $X_i=1$ or $X_i=1$ (say $X_i= PB_i$ or $=Confidence_i$) and see which sub-populations have larger TuT.
-% \vspace{.3in}
-%     \begin{align*}
-%         1=& \frac{\mathbb{E}[Y_{1i}-Y_{0i} | C_i=0, X_i=1]}{TuT}\Pr(X_i=1 | C_i=0) \\
-%         \quad &+ \frac{\mathbb{E}[Y_{1i}-Y_{0i}| C_i=0, X_i=0]}{TuT}\Pr(X_i=0 | C_i=0)
-%     \end{align*}
-
-% %and we will say that the variable $B_i$ explains the ToT whenever one of the terms (ratio weighted by the probability) is statistically significant from zero, (close to one), and the other term is statistically zero.
-%     \end{itemize}
-% \end{frame}
-
 \begin{frame}{Overconfidence?}
@@
     \item   Recall that at baseline, people were, on average, overconfident about recovering pawns.
-    \vfill \item We find that TuT>0 is concentrated on those that said they will recover with 100\% probability. 
+    \vfill \item We find that TuT>0 is concentrated on those (28\%) that said they will recover with 100\% probability. 
     \begin{itemize}
         \item Conceptually, overconfidence could explain low take up and TuT>0.
+        \item Intuitively: overconfidents underappreciate the benefit of structure.
     \end{itemize}
@@
 
-\begin{frame}{Determinants of Sure Confidence}
+\begin{frame}{Sure confidence and Present bias}
         % \begin{figure}
@@
         % \end{figure}
-
-The Sure-Confident are:
+Do we need to model overconfidence and PB?
+\begin{itemize}
+    \item We can think of borrower overconfidence of recovery arising from a belief that their distribution of future income is shifted to the right vis-a-vis the real one.
+    \item It can also come from PB naivete itself, as those types will spend more than expected and have less money to pay.
+\end{itemize}
+\vfill Determinants of Sure Confidence. The Sure-Confident are:
 \begin{itemize}
@@
 \end{itemize}
+
 \end{frame}
 
-\section{Targeting?}
+\begin{comment}
+
+\begin{frame}{Do we need to model overconfidence and PB? (sketch)}
+
+\begin{itemize}
+    \item We can think of borrower overconfidence of recovery arising from a belief that their distribution of future income is shifted to the right vis-a-vis the real one.
+    \begin{itemize}
+        \item It can also come from PB naivete itself, as those types will spend more than expected and have less money to pay.
+    \end{itemize}
+   \pause \vfill  \item Simple model features PB and overconfidence, 3 periods: 
+\begin{itemize}
+        \item Period 3 (default): Pay iff: $u\bigl(y_3 - R \cdot \mathit{\text{Outstanding  debt}}\bigr) + v 
+\;>\; u(y_3)$.   
+  \item Period 2: Pay interim $\kappa$ iff \[
+u(y_2 - k)
+\;+\;
+\beta\,\delta 
+\;\mathbb{E}_{y_3|y_2,y_1}\Bigl[\max\bigl\{\,u\bigl(y_3 - R(L - k)\bigr) + v,\;u(y_3)\bigr\}\Bigr]
+\quad\]
+\[>\quad
+u(y_2)
+\;+\;
+\beta\,\delta
+\;\mathbb{E}_{y_3|y_2,y_1}\Bigl[\max\bigl\{\,u\bigl(y_3 - R\,L\bigr) + v,\;u(y_3)\bigr\}\Bigr].
+\]
+        %\item Period 2: Get stochastic income $y_2$. In Structure contract pay $\kappa$; no payment required in SQ contract.
+        \item Period 1: Decide on contract $\in$ \{SQ,Structure\} to Max discounted expected utility. 
+    \end{itemize}
+    \vfill\item We plan to have income follow a distribution $f(y;\mu)$, and overconfidents think $\hat{\mu}>\mu$. Model PB in the standard ($\beta,\delta$) way. 
+    \pause \vfill\item Parameters: [L,R,$\kappa$,\delta$,$\beta$,$\hat{\beta},$\nu$,$\mu$]; Decisions: [$t_1$:(SQ or S), $t_2$:(pay $\kappa$ or not), $t_3$:(default and lose $\nu$)].
+    \vfill\item Show that both PB naivete and OC can explain TUT>0 in the model.
+\end{itemize}
+
+\end{frame}
+
+\end{comment}
+
+\begin{comment}
+
+% =======================
+% Period T=3: Default vs. Repay
+% =======================
+\subsection{Period 3}
+\[
+\text{Repay if and only if}\quad
+u\bigl(y_3 - R \cdot \mathit{\text{Outstanding  debt}}\bigr) + v 
+\;>\;
+u(y_3).
+\]
+\[
+\text{Otherwise, default.}
+\]
+\[\text{Outstanding debt} =\begin{cases}
+  L-k &\text{if pay in T=2}\\
+  L &\text{if not pay in T=2}
+\end{cases}\]
+
+% =======================
+% Period T=2: Pay k vs. Not Pay k
+% =======================
+\subsection{Period 2}
+\[
+u(y_2 - k)
+\;+\;
+\beta\,\delta 
+\;\mathbb{E}_{y_3|y_2,y_1}\Bigl[\max\bigl\{\,u\bigl(y_3 - R(L - k)\bigr) + v,\;u(y_3)\bigr\}\Bigr]
+\quad\]
+\[>\quad
+u(y_2)
+\;+\;
+\beta\,\delta
+\;\mathbb{E}_{y_3|y_2,y_1}\Bigl[\max\bigl\{\,u\bigl(y_3 - R\,L\bigr) + v,\;u(y_3)\bigr\}\Bigr].
+\]
+\[
+\text{If the left side is greater, pay } k; \text{ otherwise, do not pay } k.
+\]
+\vspace{5mm}
+
+For overconfident people:
+\[
+u(y_2 - k)
+\;+\;
+\beta\,\delta 
+\;\mathbb{E}_{y_3'|y_2,y_1}\Bigl[\max\bigl\{\,u\bigl(y_3 - R(L - k)\bigr) + v,\;u(y_3)\bigr\}\Bigr]
+\quad>\quad
+u(y_2)
+\;+\;
+\beta\,\delta
+\;\mathbb{E}_{y_3'|y_2,y_1}\Bigl[\max\bigl\{\,u\bigl(y_3 - R\,L\bigr) + v,\;u(y_3)\bigr\}\Bigr].
+\]
+
+% =======================
+% Period T=1: Commitment vs. No Commitment
+% =======================
+\subsection{Period 1}
+\[
+\underbrace{
+\beta\,\delta\,\mathbb{E}_{y_2|y_1}[\,u(y_2)\,] 
+\;+\;
+\beta\,\delta^2
+\,\mathbb{E}_{y_3|y_1}\Bigl[\max\bigl\{\,u\bigl(y_3 - R\,L\bigr)+v,\;u(y_3)\bigr\}\Bigr]
+}_{\text{No-Prepayment}}
+\quad\]
+
+\[<\quad
+\underbrace{
+\beta\,\delta\,\mathbb{E}_{y_2|y_1}[\,u(y_2 - k)\,]
+\;+\;
+\beta\,\delta^2
+\,\mathbb{E}_{y_3|y_1}\Bigl[\max\bigl\{\,u\bigl(y_3 - R(L-k)\bigr)+v,\;u(y_3)\bigr\}\Bigr]
+}_{\text{Prepayment}}.
+\]
+\[
+\text{Choose commitment if the right side is greater.}
+\]
+\end{comment}
 
@@
    \begin{itemize}
-     \item Assuming NWG conditional on X's, we use (Athey et.al. 2019) causal forests to estimate $E[Y_1 - Y_0| X = \mathbf{x}, C = 0]$, i.e. CTuT
+     \item Assuming NAE conditional on X's, we use (Athey et.al. 2019) causal forests to estimate $E[Y_1 - Y_0| X = \mathbf{x}, C = 0]$, i.e. CTuT
      \vspace{.1in}
@@
 \end{frame}
-
-% \begin{frame}{Example of a Causal Tree}
-%     \begin{figure}
-%         \centering
-% \includegraphics[width=0.7\textwidth]{Figuras/crf_apr.pdf}
-%         \end{figure}
-% \end{frame}
-
-% \begin{frame}{Fraction that forgo benefit:  Choice Arm}
-%         \begin{figure}
-%        % \label{choose_wrong}
-%         %\caption{Mistakes in choice arm}
-%         \centering
-%         \includegraphics[width=0.65\textwidth]{Figuras/line_cw_apr_tot_tut.pdf}
-%         \end{figure}
-% \begin{itemize}
-%     \item   Use Random Forest to estimate ToT, TuT conditional on covariates.
-%     \item   Those making either choice make mistakes if benefit of other choice is higher.
-%     \item $>$ 70\% of non-choosers would have seen some benefit from assignment to commitment.
-%     \item  $<$ 20\% of choosers made a mistake.
-% \end{itemize}        
-% \end{frame}
-
-% \begin{frame}{91\% better off being forced into Structure}
-%         \begin{figure}
-%         \centering
-%         \includegraphics[width=0.65\textwidth]{Figuras/cdf_CATE.pdf}
-%         \end{figure}
-% \end{frame}
 
@@
 
+\begin{frame}{Contributions to Literature}
+
+\begin{itemize}
+    \item  Few studies of pawn lending.
+    \vfill \item Mandates-vs-choice Design is new to the literature.
+Simultaneously identify both TOT, TUT, ASG without the need for auxiliary structural modeling assumptions.
+Fowlie et al (2021), Karlan and Zinman (2009), Beaman et al (2023) do not identify TUT effects.
+    \vfill \item Relatively small literature selection-on-gains and paternalism (e.g.
+Laibson 2018).
+Walters (2018): distance-based instrument with structural model, finds students who select into more effective schools have smaller treatment effects.
+Saddoff et al (2019) shows that individuals with the most time-inconsistent preferences in food choice are the least likely to demand commitment.
+    \vfill \item Contract design: Pande and Field (2008) find no effects from frequent repayment schemes.
+Field et al (2013), Barboni et al (2023) find productive benefit of flexibility in microfinance.
+    \vfill \item Large literature on demand for commitment.  We separately point-identify and estimate the effects of commitment for borrowers who would and would not choose it. 
+\end{itemize}
+
+\end{frame}
+
 \end{document}

### 2025-04-25 RScripts/prueba.R

@@ -1,0 +1,429 @@
+library(tidyverse)   # Loads dplyr, readr, etc.
+library(gdata)
+library(grf)
+library(MCMCpack)
+library(parallel)
+
+# SET WORKING DIRECTORY
+setwd('C:/Users/isaac/Dropbox/Apps/Overleaf/Donde2022')
+set.seed(1)
+
+
+rename_var = function(df) { 
+  df <- rename.vars(df, c(
+    "dummy_dow2",
+    "dummy_dow3",
+    "dummy_dow4",
+    "dummy_dow5",
+    "dummy_dow6",
+    "dummy_suc2",
+    "dummy_suc3",
+    "dummy_suc4",
+    "dummy_suc5",
+    "dummy_suc6",
+    "prestamo",
+    "edad",
+    "faltas",
+    "c_trans",
+    "t_llegar",
+    "fam_pide",
+    "ahorros",
+    "t_consis1",
+    "t_consis2", 
+    "confidence_100",
+    "hace_presupuesto",
+    "tentado",
+    "rec_cel",
+    "pres_antes",
+    "cta_tanda",
+    "genero",
+    "masqueprepa",
+    "estresado_seguido",
+    "na_edad",
+    "na_faltas",
+    "na_c_trans",
+    "na_t_llegar",
+    "na_fam_pide",
+    "na_ahorros",
+    "na_t_consis1",
+    "na_t_consis2", 
+    "na_confidence_100",
+    "na_hace_presupuesto",
+    "na_tentado",
+    "na_rec_cel",
+    "na_pres_antes",
+    "na_cta_tanda",
+    "na_genero",
+    "na_masqueprepa",
+    "na_estresado_seguido"    
+  ),
+  c(
+    "tuesday",
+    "wednesday",
+    "thurdsay",
+    "friday",
+    "saturday",
+    "branch.2",
+    "branch.3",
+    "branch.4",
+    "branch.5",
+    "branch.6",
+    "loan.size",
+    "age",
+    "trouble.paying.bills",
+    "transport.cost",
+    "transport.time",
+    "fam.asks",
+    "savings",
+    "patience",
+    "future.patience", 
+    "sure.confidence",
+    "makes.budget",
+    "tempted",
+    "sms.reminder",
+    "pawn.before",
+    "rosca",
+    "female",
+    "more.high.school",
+    "stressed",
+    "na.age",
+    "na.trouble.paying.bills",
+    "na.transport.cost",
[…]
